### 2023-07-28 Latex Templates/Generic Report/main.tex
>w<

\documentclass[]{article}
\usepackage{amsmath}
\usepackage{amsfonts} 
\usepackage[english]{babel}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{algorithmic}
\usepackage{algorithm}
% \usepackage{minted}

% Basic Type Settings ----------------------------------------------------------
\usepackage[margin=1in,footskip=0.25in]{geometry}
\linespread{1}  % double spaced or single spaced
\usepackage[fontsize=12pt]{fontsize}
\usepackage{authblk}

\theoremstyle{definition}
\newtheorem{theorem}{Theorem}       % Theorem counter global 
\newtheorem{prop}{Proposition}[section]  % proposition counter is section
\newtheorem{lemma}{Lemma}[subsection]  % lemma counter is subsection
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}[subsection]
{
    % \theoremstyle{plain}
    \newtheorem{assumption}{Assumption}
}
\numberwithin{equation}{subsection}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}
\usepackage[final]{graphicx}
\usepackage{listings}
\usepackage{courier}
\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
\newcommand{\indep}{\perp \!\!\! \perp}
\usepackage{wrapfig}
\graphicspath{{.}}
\usepackage{fancyvrb}

%%
%% Julia definition (c) 2014 Jubobs
%%
\usepackage[T1]{fontenc}
\usepackage{beramono}
\usepackage[usenames,dvipsnames]{xcolor}
\lstdefinelanguage{Julia}%
  {morekeywords={abstract,break,case,catch,const,continue,do, else, elseif,%
      end, export, false, for, function, immutable, import, importall, if, in,%
      macro, module, otherwise, quote, return, switch, true, try, type, typealias,%
      using, while},%
   sensitive=true,%
   alsoother={$},%
   morecomment=[l]\#,%
   morecomment=[n]{\#=}{=\#},%
   morestring=[s]{"}{"},%
   morestring=[m]{'}{'},%
}[keywords,comments,strings]%
\lstset{%
    language         = Julia,
    basicstyle       = \ttfamily,
    keywordstyle     = \bfseries\color{blue},
    stringstyle      = \color{magenta},
    commentstyle     = \color{ForestGreen},
    showstringspaces = false,
}

\title{This is The Title}
\author{Name of the Author}

\begin{document}
\maketitle

\begin{abstract}
    This is the Abstract
\end{abstract}

\section{Introduction}
    This is an introduction.

\section{Preliminaries}\label{sec:preliminaries}
    \hyperref[sec:preliminaries]{This} is the preliminary (hyperref without text labeling).

\section{Blah Blah Bleeeh}
    This is the blah blah bleeeh section. 
    \subsection{Blah Blah Blah Bleeh Bleeh Bleeh}
    Check out this cool Bibtext ref \cite[this]{texbook}, woooooooooah, also it's in plain style. For some mind altering psychodelic, read \hyperref[alg:mhc]{algorithm \ref*{alg:mhc}} for the experience. For some brain expanding julia code, read \hyperref[code:brain_expand]{brain expanding julia code}. 
    \begin{algorithm}
        \begin{algorithmic}[H]
            \STATE{\textbf{Input: $X^{(t)}$}}
            \STATE{$Y^{(t)} \sim q (\cdot | X^{(t)})$}
            \STATE{
                $ 
                \rho(x, y) := 
                \min\left\lbrace
                    \frac{f(y)}{f(x)}\frac{q(x|y)}{q(y|x)}, 1
                \right\rbrace
                $ 
            }
            \STATE{
                $
                X^{(t + 1)} := 
                \begin{cases}
                    Y^{(t)} & \text{w.p}:  \rho(X^{(t)}, Y^{(t)})
                    \\
                    X^{(t)} &  \text{otherwise}
                \end{cases}$
            }
        \end{algorithmic}
        \caption{Metropolis Chain}
        \label{alg:mhc}
    \end{algorithm}
    \label{code:brain_expand}
    \lstinputlisting[language=julia, basicstyle=\ttfamily\tiny,numbers=left]{Code/juliacode.jl}

\appendix
\section{Bleeh Bleeh Bleeh I am not Listening}
    This is the Bleeh Bleeh Bleeh I am not Listening section.

\section{This section is in another .tex file} 
    \input{Sections/section.tex}

\bibliographystyle{plain}
\bibliography{refs.bib}

\end{document}

### 2023-11-13 Latex Templates/Generic Latex Beam Presentation/Sections/sectionfile.tex
>w<

\subsection{LASSO}
\begin{frame}{Some Fancy Results}
    The plot of $\Delta_k$: 
    \begin{figure}[h]
        \centering
        \includegraphics[width=8cm]{Assets/simple_lass_obj.png}
        \caption{The left is the objective value of the function during all iterations.}
    \end{figure}
\end{frame}

\begin{frame}{Results}
    The plot of $\Vert y^{(k)} - x^{(k + 1)}\Vert_\infty$:
    \begin{figure}[h]
        \centering
        \includegraphics[width=8cm]{Assets/simple_lass_pgrad.png}
    \end{figure}
\end{frame}

\subsection{Image Deconvolution with Noise}
\begin{frame}{Experiment Setup}
    Given an image that is convoluted by a Guassian kernel with some guassian noise, we want to recover the image, given the parameters for convolutions. 
    \begin{itemize}
        \item [1.] Guassian blur with a discrete 15 by 15 kernel is a linear transform represented by a sparse matrix $A$ in the computer. 
        \item [2.] When an image is 500 by 500 with 3 color channels, $A$ is $750000 \times 750000$. 
        \item [3.] Let the noise be on all normalized colors values with $N(0, 10^{-2})$
        \item [4.] We let $\lambda = \alpha\times (3\times500^2)^{-1}$. 
        \item [5.] Implemented in Julia, and the code is too long to be shown here. 
    \end{itemize}        
\end{frame}
\begin{frame}{One Big Image for Some Fancy Results}
    We consider blurring the image of a pink unicorn that I own. 
    \begin{figure}[H]
        \centering
        \includegraphics[width=5cm]{Assets/blurred_img.jpg}
        \caption{The image is blurred by the Gaussian Blurred matrix $A$ with a tiny amount of noise on the level of $2\times 10^{-2}$ that is barely observable. Zoom in to observe the tiny amount of Gaussian noise on top of the blur.}
        \label{fig:blurred_alto}
    \end{figure}
\end{frame}
\begin{frame}{Moer Image to Show Impressive Results}
    \begin{figure}
        \subfloat[Graph 1]{
            \includegraphics[width=3cm]{Assets/inverse_linear_experiment1-soln_img.jpg}
            \label{fig:1a}
        }
        \subfloat[Graph 2]
        {
            \includegraphics[width=3cm]{Assets/inverse_linear_experiment2-soln_img.jpg}
            \label{fig:1b}
        }
        \subfloat[Graph 3]
        {
            \includegraphics[width=3cm]{Assets/inverse_linear_experiment3-soln_img.jpg}
            \label{fig:1c}
        }
        \caption{(a) $\alpha = 0$, without any one norm penalty, is not robust to the additional noise. (b) $\alpha = 0.01$, there is a tiny amount of $\lambda$. (c) $\alpha = 0.1$, it is more penalty compared to (a).}
        \label{fig:alto_deblurred}
    \end{figure}

\end{frame}

### 2023-11-13 Latex Templates/Generic Latex Beam Presentation/presentation.tex
>w<

\documentclass[11pt]{beamer}
\usetheme{Madrid}
\usepackage[utf8]{inputenc}

\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\DeclareMathOperator{\argmin}{argmin}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{wrapfig}
\usepackage{subcaption}
\graphicspath{{.}}

\author{Generic Name}
\title{Title for Super Fancy Stuff}
% Informe o seu email de contato no comando a seguir
% Por exemplo, alcebiades.col@ufes.br
\newcommand{\email}{lalala@lala.la}
\setbeamercovered{transparent}
\setbeamertemplate{navigation symbols}{}
%\logo{}
\institute[]{Some Super Fancy Institution}
\date{\today}
\subject{Subject Title }

% ---------------------------------------------------------
% Selecione um estilo de referência
\bibliographystyle{IEEEtran}

%\bibliographystyle{abbrv}
%\setbeamertemplate{bibliography item}{\insertbiblabel}
% ---------------------------------------------------------

% ---------------------------------------------------------
\newtheorem{remark}{Remark}
\newtheorem{assumption}{Assumption}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

\begin{frame}{ToC}
    \tableofcontents
\end{frame}

\section{This is the First Section}
    \subsection{Taxonomy of Proximal type of Methods}
        \begin{frame}{Frame Title}

            \begin{block}{Formula Presented in Block}
                \begin{align}
                    \min_{x} g(x) + h(x)
                \end{align}    
            \end{block}

            \begin{itemize}
                \item [1.]Throughout this presentation, we assume the objective of a function $f$ is the sum of 2 functions.
                \item [2.]We are interested in the paper: FISTA (Fast Iterative-Shrinkage Algorithm) by Beck and Teboulle \cite{paper:FISTA}. 
                \pause 
                \item [1.] When $h = \delta_Q$ with $Q$ closed and convex with $Q\subseteq \text{ri}\circ \text{dom}(g)$, we use projected subgradient. 
                \item [2.] When $g$ is \textbf{\emph{strongly smooth}} and $h$ is \textbf{closed convex proper} whose proximal oracle is easy to compute, we consider the use of FISTA. 
            \end{itemize}

        \end{frame}

    \subsection{The Proximal Operator}
        \begin{frame}{Frame Title}
            \begin{definition}[Definition of Something]
                Let $f$ be convex closed and proper, then the proximal operator parameterized by $\alpha > 0$ is a non-expansive mapping defined as: 
                \begin{align*}
                    \text{prox}_{f, \alpha}(x) := 
                    \arg\min_{y}\left\lbrace
                        f(y) + \frac{1}{2\alpha} \Vert y - x\Vert^2
                    \right\rbrace. 
                \end{align*}
            \end{definition}  
            \begin{remark}
                When $f$ is convex, closed, and proper, 
            \end{remark}
        \end{frame}

        \begin{frame}{Prox is the Resolvant of Subgradient}
            \begin{lemma}[The Lemma]\label{lemma:prox_alternative_form}
                When the function $f$ is convex closed and proper, the $\text{prox}_{\alpha, f}$ can be viewed as the following operator $(I + \alpha \partial f)^{-1}$. 
            \end{lemma}
            \begin{proof}
                Minimizer satisfies zero subgradient condition, 
                {\scriptsize
                \begin{align*}
                    \mathbf 0 &\in \partial
                    \left[
                        \left.
                            f(y) + \frac{1}{2\alpha} \Vert y - x\Vert^2 
                        \right| y
                    \right](y^+)
                    \\
                    \mathbf 0 &\in \partial f(y^+) + \frac{1}{\alpha}(y^+ - x)
                    \\
                    \frac{x}{\alpha} &\in 
                    (\partial f + \alpha^{-1}I)(y^+)
                    \\
                    x &\in 
                    (\alpha \partial f + I)(y^+)
                    \\
                    y &\in (\alpha\partial f+ I)^{-1}(x).
                \end{align*}
                }
            \end{proof}

        \end{frame}

    \subsection{Strong Smoothness}
        \begin{frame}{Equivalence of Strong Smoothness and Lipschitz Gradient}
            \begin{theorem}[Lipschitz Gradient Equivalence under Convexity]
                Suppose $g$ is differentiable on the entire of $\mathbb E$. It is closed convex proper. It is strongly smooth with parameter $\alpha$ if and only if the gradient $\nabla g$ is globally Lipschitz continuous with a parameter of $\alpha$ and $g$ is closed and convex. 
                \begin{align*}
                    \Vert \nabla g(x) -\nabla g(y)\Vert \le 
                    \alpha 
                    \Vert x - y \Vert\quad \forall x, y\in \mathbb E
                \end{align*}
            \end{theorem}
            \begin{proof}
                Using line integral, we can prove Lipschitz gradient implies strong smoothness without convexity. The converse requires convexity and applying generalized Cauchy Inequality to (iv) in Theorem 5.8 for Beck's textbook \cite{book:first_order_opt}. 
            \end{proof}

        \end{frame}
    \subsection{A Major Assumption}    
        \begin{frame}{A Major Assumption}
            \begin{assumption}[Convex Smooth Nonsmooth with Bounded Minimizers]\label{assumption:1}
                We will assume that $g:\mathbb E\mapsto \mathbb R$ is \textbf{strongly smooth} with constant $L_g$ and $h:\mathbb E \mapsto \bar{\mathbb R}$ \textbf{is closed convex and proper}. We define $f := g + h$ to be the summed function and $\text{ri}\circ \text{dom}(g) \cap \text{ri}\circ \text{dom}(h) \neq \emptyset$. We also assume that a set of minimizers exists for the function $f$ and that the set is bounded. Denote the minimizer using $\bar x$. 
            \end{assumption}
        \end{frame}

\section{A New Fancy Section}
    \subsection{A Fancy Subsetction for Algorithm}
        \begin{frame}{The Accelerated Proximal Gradient Method}
            \begin{block}{Momentum Template Method}
                \begin{algorithm}[H]
                    \begin{algorithmic}[1]
                        \STATE{\textbf{Input:} $x^{(0)}, x^{(-1)}, L, h, g$; 2 initial guesses and stepsize L}
                        \STATE{$y^{(0)} = x^{(0)} + \theta_k (x^{(0)} - x^{(-1)})$}
                        \FOR{$k = 1, \cdots, N$}
                            \STATE{$x^{(k)} = \text{prox}_{h, L^{-1}}(y^{(k)} + L^{-1}\nabla g(y^{(k)})) =: \mathcal P_{L^{-1}}^{g, h}(y^{(k)})$}
                            \STATE{$y^{(k + 1)} = x^{(k)} + \theta_k(x^{(k)} - x^{(k - 1)})$}
                        \ENDFOR
                    \end{algorithmic}
                    \caption{Template Proximal Gradient Method With Momentum}\label{alg:fista_template}
                \end{algorithm}
            \end{block}
        \end{frame}

\section{Numerical Experiments}
    \input{Sections/sectionfile.tex}

\section{References}
    \begin{frame}{References}

        \bibliography{refs.bib}
    \end{frame}

\end{document}

### 2024-03-19 Notebook LaTEX/Machine Learning/Sections/section.tex
>w< mcbr

This is a new section. 
\subsection{Subsection}
This is a subsection.

\subsection{Cute Subsection}
Check out this cute figure. In \hyperref[fig:cute_alto]{fig \ref*{fig:cute_alto}} is cute pink unicorn, and in \hyperref[fig:minty_and_alto]{fig \ref*{fig:minty_and_alto}}, the green earth pony is minty, a cookie pone. Theyare cute together. Read source to understand the use of ``subfloat'' and ``figure'' together with ``hyperref''.

\begin{figure}
    \subfloat[Cute Alto]{
        \includegraphics[width=10em]{Assets/Alto_Legato.png}
        \label{fig:cute_alto}
    }
    \hfil
    \subfloat[Minty and Alto]{
        \includegraphics[width=10em]{Assets/Minty_and_Alto.png}
        \label{fig:minty_and_alto}
    }
\end{figure}

### 2024-03-19 Latex Templates/Generic Report/Code/juliacode.jl
>w< mcbr

@@ -1,18 +1,0 @@
-"""
-A doubly stochastic chain sampler that uses wrapped guassian distributions on both directions in 2D 
-with a fixed variance. 
-"""
-function wrapped_gaussian_sampler_2d(
-    state::Vector{T},
-    lower_left::Tuple{Real, Real}, 
-    upper_right::Tuple{Real, Real};
-    sigma::Real=1
-) where {T<:Real}
-    lower = [lower_left[1], lower_left[2]]
-    upper = [upper_right[1], upper_right[2]]
-    function loop_back(x, l, u)  # assert periodic conditions on the rectangle. 
-        return mod(x, u - l) + l
-    end
-    N = Normal(0, sigma)
-    return loop_back.(state + rand(N, 2), lower, upper)
-end

### 2024-03-26 Notebook LaTEX/Machine Learning/main.tex
>w< wdkstp

\documentclass[]{article}
\usepackage{amsmath}
\usepackage{amsfonts} 
\usepackage[english]{babel}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{anyfontsize} % fix font size warning. 
\usepackage{url} 
\urlstyle{same} % fix wacky url links in bib entries. 
% \usepackage{minted}

% Basic Type Settings ----------------------------------------------------------
\usepackage[margin=1in,footskip=0.25in]{geometry}
\linespread{1}  % double spaced or single spaced
\usepackage[fontsize=12pt]{fontsize}
\usepackage{authblk}

\theoremstyle{definition}
\newtheorem{theorem}{Theorem}       % Theorem counter global 
\newtheorem{prop}{Proposition}[section]  % proposition counter is section
\newtheorem{lemma}{Lemma}[subsection]  % lemma counter is subsection
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}[subsection]
\newtheorem{remark}{Remark}[subsection]
{
    % \theoremstyle{plain}
    \newtheorem{assumption}{Assumption}
}
\numberwithin{equation}{subsection}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}
\usepackage[final]{graphicx}
\usepackage{listings}
\usepackage{courier}
\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
\newcommand{\indep}{\perp \!\!\! \perp}
\usepackage{wrapfig}
\graphicspath{{.}}
\usepackage{fancyvrb}

%%
%% Julia definition (c) 2014 Jubobs
%%
\usepackage[T1]{fontenc}
\usepackage{beramono}
\usepackage[usenames,dvipsnames]{xcolor}
\lstdefinelanguage{Julia}%
  {morekeywords={abstract,break,case,catch,const,continue,do, else, elseif,%
      end, export, false, for, function, immutable, import, importall, if, in,%
      macro, module, otherwise, quote, return, switch, true, try, type, typealias,%
      using, while},%
   sensitive=true,%
   alsoother={$},%
   morecomment=[l]\#,%
   morecomment=[n]{\#=}{=\#},%
   morestring=[s]{"}{"},%
   morestring=[m]{'}{'},%
}[keywords,comments,strings]%
\lstset{%
    language         = Julia,
    basicstyle       = \ttfamily,
    keywordstyle     = \bfseries\color{blue},
    stringstyle      = \color{magenta},
    commentstyle     = \color{ForestGreen},
    showstringspaces = false,
}

\title{Machine Learning, a Review for Tree Segmentations Tasks}
\author{Hongda Li}

\begin{document}
\maketitle

\begin{abstract}
    This is my own notes. 
\end{abstract}

\section{Introduction}
    Artificial Neural networks represents modes of numerical computations that are differentiable programs. 
    We skips the basics and assume the reader already know something about Deep Neural Network, their components, and the automatic differentiation program on modern deep learning frameworks. 
    For our discussion we introduce some definitions to make for a better presentation of computataional concepts occured in Artificial Neural Networks (ANNs). 
    \begin{definition}[Component]
        A component is a function $f(x; p|w): \mathbb R^m \mapsto \mathbb R^n$. 
        $x$ is the inputs and $w$ represent trainable parameters, usually in the form of a multi-dimensional array. 
        And $p$ represents parameters that are not trainable parameters.

    \end{definition}
    \begin{definition}[Connection]
        Let $f:\mathbb R^n \mapsto \mathbb R^m, g: \mathbb R^m \mapsto \mathbb R^k$ be two components, then a connection between is a $\mathbb R^m \mapsto \mathbb R^m$ function $h(x; p | w)$ with trainable parameters $w$, and parameter $p$. 
    \end{definition}

    \begin{example}[Dense Layer]
        Let $m, n \in \mathbb N$, let $A \in \mathbb R^{n\times m}$, $b \in \mathbb R^n$, then a Dense layer is a $\mathbb R^m \mapsto \mathbb R^n$ functions with a list of activation functions $\sigma_i$ for $i = 1, \cdots, n$. 
        Let $x \in \mathbb R^m$ be the input, then a dense layer is a component. We define its computation: 
        $$
        \begin{aligned}
            \text{DnsLyr}(x ; m, n | (A, b), \{\sigma_i\}_{i=1}^n) = 
            \left[
                z \mapsto \bigoplus_{i = 1}^n\sigma_i(z_i)
            \right]
            \left(
                Ax + b
            \right). 
        \end{aligned}
        $$
        Where, inside of $[\cdot]$, we denote the definition of a anonymous function. 
    \end{example}

    \begin{example}[Multi-Layer Perceptron]
        Let $l_1, l_2, \cdots, l_N$ be integers. 
        We define the Multi-Layer Perceptron to be a composition of dense layer mapping from $l_{i}$ to $l_{i + 1}$ for $i = 1, \cdots, N - 1$. 
        Let $\sigma_{i, j}$ represent the activation function for the $j$ th output in the $i$ th layer. 
        Then a Multi-Layer Perceptron (MLP) is a component admit representation
        $$
        \begin{aligned}
            & \text{MLP}\left(x ; l_1, \cdots, l_n | \{(A_i, b_i)\}_{i=1}^N\right): \mathbb R^{l_1} \mapsto \mathbb R^{l_N}
            \\
            :=&
            \left[
            \bigodot_{i = 1}^n \text{DnsLyr}
            \left(
                (\cdot) ; l_i, l_{i + 1} \left| (A_i, b_i), \{\sigma_{j, i}\}_{j=1}^{l_i} \right.
            \right)
            \right](x). 
        \end{aligned}
        $$
        Where $\bigodot$ is functional composition and it represents $\bigodot_{i=1}^n f_i = f_n\circ\cdots\circ f_1(x)$, and $(\cdot)$ represents the input of the anonymous function, in this case it's the dense layer. 
    \end{example}

\section{Preliminaries}
    These concepts and components are relevant to the architecture of Vision Networks. 
    \begin{definition}[Convolution 2D]
        Let $u, v$ be multi-array of dimension $m \times n$ and $k \times l$. 
        We assume that $m \le  k$ and $n \le l$.
        Then the convolution operator $*$ is a mapping from $(\mathbb C^M \times \mathbb C^n)\times (\mathbb C^k \times \mathbb C^l) \mapsto \mathbb C^{(m - k)\times (n - l)}$. 
        Then the convolution is defined as 
        $$
        \begin{aligned}
            (u* v)_{t, \tau} = 
            \sum_{i = 1}^{k}\sum_{j = 1}^{l}u_{i, j}v_{i + t, j + \tau}. 
        \end{aligned}
        $$
    \end{definition}

    \subsection{Convolutional Layers}
        In this section we talk about \href{https://pytorch.org/docs/stable/generated/torch.nn.Conv2d.html}{2D convolution component (pytorch link)} inside of an ANNs. 
        The convolution operations module contains more detailed parameters. 
        \begin{definition}[2D Convolution Layers]
            Assuming that we have a single sample. 
            Let $(C, H, W)$ be the shape of the input tensor. 
            $C$ is the number of channel, and $H, W$ are the height and width. 
            We use this because image tensors are usually in the shape of $(3, H, W)$. 
            Define the component to be a function, mapping from $(C', H', W')$. 
            Let $(C, K, L)$ denotes the dimension of the kernel: $\mathcal K$. 
            Then mathematically, the computation of the output tensor $Y$ given input tensor $X$ can be computed as
            $$
            \begin{aligned}
                Y_{c', h', w'} = 
                \text{ReLU}\left( b_{c'} + 
                \sum_{n = 1}^{C} (\mathcal K_{c'} * X)_{h', w'}\right). 
            \end{aligned}
            $$
        \end{definition}
        \begin{remark}
            Observe that each of the output channel is the sum of $C$ many kernels convluted with all inputs channels and summed up. 
        \end{remark}
        \begin{definition}[2D Max Pooling Layers]

        \end{definition}

\appendix
\section{Appendix Section 1}
    This is the appendix section.

\bibliographystyle{plain}
% \bibliography{refs.bib}

\end{document}

### 2024-04-02 Notebook LaTEX/Machine Learning/main.tex
>w< mcbr

@@
     For our discussion we introduce some definitions to make for a better presentation of computataional concepts occured in Artificial Neural Networks (ANNs). 
+    \par
+    \subsection{Note}
+        The index starts with ``1'' in our writings. 
+        But it starts with zero if we are using programming languages such as python.
+
     \begin{definition}[Component]
@@
         The convolution operations module contains more detailed parameters.
+
         \begin{definition}[2D Convolution Layers]
@@
             Observe that each of the output channel is the sum of $C$ many kernels convluted with all inputs channels and summed up. 
+            For more information about using it in pytorch, visit 
+            The following parameters are extra and can be used to alter the computations. 
+            \begin{enumerate}
+                \item ``stride'', striding means ignoring some of the element of the convoluted vectors. In the case of `stride=2', the dimension is odd or even will matter.
+
+                \item ``padding'', padding adds zero elements to the input vector/matrix.
+
+                \item ``dialation'', dilation dilate the filter, making it bigger and fills it with more zeros. The trainable weights will distributed with integers spacing between them.
+
+                \item  ``group'', see \href{https://towardsdatascience.com/conv2d-to-finally-understand-what-happens-in-the-forward-pass-1bbaafb0b148}{here} for an explanations.
+I am not sure what this parameter is doing really.
+            \end{enumerate}
+            The activaton function above is ``ReLU'', but it doesn't have to be. 
+            See \href{https://pytorch.org/docs/stable/generated/torch.nn.Conv2d.html}{here} for the pytorch documentations. 
         \end{remark}
+    \subsection{Pooling Layer}
+        Let's define these quantities 
+        \begin{enumerate}
+            \item $(N, C, H, W)$ is the size of the input signal. 
+            \item $(N, C, H', W')$ is the signal of the output layer.
+            \item $(k_1, k_2)$ is the size of the kernel. 
+            \item $N$ is usually the size of the Batched samples. 
+            \item $[s_1, s_2]$ be the stride parameters for the kernels. 
+        \end{enumerate}
+
         \begin{definition}[2D Max Pooling Layers]
-
+            Let $X$ be the signal of size $(N,C, H, W)$, let the output signal be $Y$ of size $(N, C, H', W')$, then the output can be precisely described by the following formula: 
+            {
+            \large
+            \[
+                \begin{aligned}
+                    Y_{i,c, h, w} = 
+                    \max_{
+                        \substack{m = 1, \;\cdots, H\\n = 1, \; \cdots \; , W}
+                    }
+                    \{
+                        X_{i, c, hs_1 + m, s_2w + n}
+                    \}. 
+                \end{aligned} 
+            \]
+            }
         \end{definition}

### 2024-04-03 Notebook LaTEX/Machine Learning/main.tex
>w< wdkstp

@@
 }
+\newtheorem{fact}{Fact}[subsection]
 \numberwithin{equation}{subsection}
@@
 \usepackage{fancyvrb}
+
+\newcommand{\inlinecode}[1]{\texttt{\footnotesize #1}}
+
+%% CUSTOMIZED MATHEMATICAL OPERATORS ===========================================
 
@@
 
-\title{Machine Learning, a Review for Tree Segmentations Tasks}
+\title{Machine Learning, a Review for Tree Segmentations Task}
 \author{Hongda Li}
@@
     \par
-    \subsection{Note}
+    \subsection{Notations, Common Operations}
         The index starts with ``1'' in our writings. 
         But it starts with zero if we are using programming languages such as python. 
-
+        To distinguish these 2 type of indexing on a tensor $X$, we use $X_{i_1, 1_2, \cdots}$ to denotes indexing using the natural number and we use $X_{[i_1, i_2, \cdots]}$ to denote indexing of the tensor using offset indices that starts with zero.
     \begin{definition}[Component]
@@
 
-\section{Preliminaries}
+\section{Basic of Neural Architecture}
     These concepts and components are relevant to the architecture of Vision Networks. 
@@
     \end{definition}
+    \subsection{The Input and Output of Multi-Channel Fixed Dimension Signal}
+        In this section, we discuss the shape of the output signal for a 2D/1D signal after 
+        \begin{enumerate}
+            \item Max/average Pooling,
+            \item Convolution. 
+        \end{enumerate}
+        Here we note that these above operations places the same type of constraints on the output shape of the signal given the shape of the input. 
+        We all these type of operations: ``Multi-Channel Fixed Dimenion Transform (MCFDT)''. 
+        This is not a name from the literature I just made it up. 
+        These operations share a common set of parameters that determine the shape of the output tensor given the shape of the output tensor. 
+        These are the list of parameters: 
+        \begin{enumerate}
+            \item \inlinecode{in\_channel}: Type integers. The number of channels expected for the input signal.
+
+            \item \inlinecode{Out\_channels}: Type integers. The number of channel expected for the output signal.
+
+            \item \inlinecode{kernel\_size}: The size of the kernel used for the 1D signal, for certain type of operations.
+The kernel represent the size of the window where an computations are going to carry out locally on the input signal.
+
+            \item \inlinecode{stride}: How many elements does the kernel skips with respect to the input signal for each of the adjacent output elements in the output signal.
+
+            \item \inlinecode{padding}: The numbers of zero/null/-inf elements added to the 2 side of the 1D signal. 
+                \begin{enumerate}
+                    \item \inlinecode{padding\_mode}: Determine different modes of padding the boundary of the input signal. 
+                    \begin{enumerate}
+                        \item  \inlinecode{zero}, (default)
+                        \item  \inlinecode{reflect}, 
+                        \item  \inlinecode{replicate}, 
+                        \item  \inlinecode{circular}. 
+                    \end{enumerate}
+                \end{enumerate}
+
+            \item \inlinecode{dilation}: Spacing between the elements of the kernels.
+
+            \item \inlinecode{blocks}: Number of blocked connections from intput channels to output channels, default to 1.
+
+            \item \inlinecode{bias}: Add learnable bias to the component, default to `true`. 
+        \end{enumerate}
+
+        \begin{fact}[MCFDT 1D]
+            Let input signal be a tensor of size $(N, C, L)$. 
+            \begin{enumerate}
+                \item $N$ is the number of samples from the batch. 
+                \item $C$ is the number of imput channels for the signal. 
+                \item $L$ is the length of the input signal. 
+            \end{enumerate}
+            Let $p, d, k, s$ denotes: "padding, dilation, kernel size, stride". 
+            Then the output signal is a tensor of size $(N, C', L')$ with 
+            \begin{align}
+                L' = \left\lfloor
+                    \frac{(L + 2p)- (d(k-1)+1)}{s} + 1
+                \right\rfloor. 
+            \end{align}
+            The parameter $C'$, is user defined. 
+        \end{fact}
+        \begin{remark}
+            The size of the input signal with paddin is $(L + 2p)$. 
+            The size of the dilated kernel is $d(k - 1)$. 
+            The $+1$ on the numerator of the fraction and the $+1$ at the outside of the fraction remains as a mystery to the writer. 
+            The process of computing the shape for an input signal of dimension $(N, C, [\cdots])$, is applying the same computations on all the dimensions to compute the output of the signal. 
+        \end{remark}
+        \begin{fact}[MCFDT 2D]\label{fact:MCFDT_2D}
+            Let $X$ be a tensor of shape $(C, N, L_1, L_2)$, then the output signal is of size $(C', N, L_1', L_2')$, where $C'$ is defined. 
+            \begin{enumerate}
+                \item $N$ is the number of samples from the batch. 
+                \item $C$ is the number of imput channels for the signal. 
+                \item $L$ is the length of the input signal. 
+            \end{enumerate}
+
+            Let $p_i,d_i,k_i,s_i, \; i \in \{1, 2\}$ be the ``padding, dilation, kernel size, stride'' along the $L_1$ and $L_2$ dimension of the input signal. 
+            Then the shape parameters $(L_1', L_2')$ can be computed by the formula: 
+            $$
+            \begin{aligned}
+                L'_i = \left\lfloor
+                \frac{(L_i + 2p_i)- (d_i(k_i-1)+1)}{s_i} + 1
+                \right\rfloor \quad \forall i \in \{1, 2\}. 
+            \end{aligned}
+            $$
+        \end{fact}
+        \begin{remark}
+            This is analogous to the 1D case and it's just applying the same formula to the corresponding dimension of the tensor to determine the shape of the output tensor. 
+        \end{remark}
 
@@
         The convolution operations module contains more detailed parameters. 
-
         \begin{definition}[2D Convolution Layers]
@@
             Define the component to be a function, mapping from $(C', H', W')$. 
-            Let $(C, K, L)$ denotes the dimension of the kernel: $\mathcal K$. 
+            Let $(C', C, K, L)$ denotes the dimension of the kernel tensor denoted by: $\mathcal K$. 
             Then mathematically, the computation of the output tensor $Y$ given input tensor $X$ can be computed as
-            $$
-            \begin{aligned}
+            {\large
+            \begin{align}
                 Y_{c', h', w'} = 
                 \text{ReLU}\left( b_{c'} + 
-                \sum_{n = 1}^{C} (\mathcal K_{c'} * X)_{h', w'}\right). 
-            \end{aligned}
-            $$
+                \sum_{k = 1}^{C} (\mathcal K_{c',k,:, :} * X)_{h', w'}\right). 
+            \end{align}
+            }
         \end{definition}
+
         \begin{remark}
-            Observe that each of the output channel is the sum of $C$ many kernels convluted with all inputs channels and summed up. 
-            For more information about using it in pytorch, visit 
-            The following parameters are extra and can be used to alter the computations. 
+            There is a bias term and an activation function for a specific channel. 
+            The kernel for an image, which is a 3D tensor, is also a 3D tensor. 
+            A single tensor is applied to all channels of the input channel, aggregated by summing up across these different channels. 
             \begin{enumerate}
-                \item ``stride'', striding means ignoring some of the element of the convoluted vectors. In the case of `stride=2', the dimension is odd or even will matter.
-
-                \item ``padding'', padding adds zero elements to the input vector/matrix.
-
-                \item ``dialation'', dilation dilate the filter, making it bigger and fills it with more zeros. The trainable weights will distributed with integers spacing between them.
 
                 \item  ``group'', see \href{https://towardsdatascience.com/conv2d-to-finally-understand-what-happens-in-the-forward-pass-1bbaafb0b148}{here} for an explanations. 
-I am not sure what this parameter is doing really.
             \end{enumerate}
@@
             See \href{https://pytorch.org/docs/stable/generated/torch.nn.Conv2d.html}{here} for the pytorch documentations. 
+            The size of the output tensor is determined by \hyperref[fact:MCFDT_2D]{fact \ref*{fact:MCFDT_2D}}. 
         \end{remark}
-    \subsection{Pooling Layer}
+
+    \subsection{Pooling Layers}
         Let's define these quantities 
@@
             \item $(k_1, k_2)$ is the size of the kernel. 
-            \item $N$ is usually the size of the Batched samples. 
+            \item $N$ is usually the size of the batched samples. 
             \item $[s_1, s_2]$ be the stride parameters for the kernels. 
@@
                     \max_{
-                        \substack{m = 1, \;\cdots, H\\n = 1, \; \cdots \; , W}
+                        \substack{m = 1, \;\cdots, k_1 - 1\\n = 1, \; \cdots \; , k_2-1}
                     }
@@
         \end{definition}
+        \begin{remark}
+            See \href{https://pytorch.org/docs/stable/generated/torch.nn.MaxPool2d.html}{max pool 2d} for pytorch documentation for this component. 
+        \end{remark}
+
+        \begin{definition}[2D Averge Pooling Layer]
+            Let $X$ be the input signal of size $(N, C, H, W)$, let output signal $Y$ be of size $(N, C, H', W')$, then the output for an average pooling layer can be computed as
+            {\large
+            \begin{align*}
+                Y_{[i, c, h, w]} = 
+                \operatorname{mean} \left(
+                    X_{[i, c, hs_1 + m, hs_2 + n]}, m \in \{ 0, \cdots, k_1 -1\}, n \in \{0 \cdots, k_2 -1\}
+                \right). 
+            \end{align*}
+            }
+        \end{definition}
+        \begin{remark}
+            See \href{https://pytorch.org/docs/stable/generated/torch.nn.AvgPool2d.html}{averaeg pool 2d} for pytorch documentation for this component. 
+        \end{remark}
+
+    \subsection{Inverted Operations}
+
+\section{Graphical Model and Probability Dependence}
+
+\section{Variational Autoencoder, Bayesian Learning}
+
+\section{Computer Vision Networks}
+
+\section{Case Study | Direct LiDAR Point Cloud Architecture}
+
+\section{Case Study | The Deepforest Project}
 

### 2024-04-04 Notebook LaTEX/Machine Learning/main.tex
>w< mcbr

@@
 \title{Machine Learning, a Review for Tree Segmentations Task}
-\author{Hongda Li}
+\author{}
 
@@
 \end{abstract}
+\tableofcontents
 
@@
 
-            \item \inlinecode{bias}: Add learnable bias to the component, default to `true`. 
+            \item \inlinecode{bias}: Add learnable bias to the component, default to `true'. 
         \end{enumerate}
@@
 \section{Graphical Model and Probability Dependence}
+    Graphical models are used to model probability dependence between random variables. 
+    In the context of deep learning, it helps with training hierarchical models.
 
@@
 
+\section{Case Study | Forest Allometrics Extractions, Predictions}
+
 \appendix

### 2024-04-08 Notebook LaTEX/Machine Learning/main.tex
>w< mcbr
mcbr

@@
         \end{remark}
+    \subsection{Convolution 2D Normalization Layer}
+        The convolution 2D Normalized layer sandwitch one batch normalization between layers of 2D convolutions. 
+        For more information visit \href{https://pytorch.org/vision/main/generated/torchvision.ops.Conv2dNormActivation.html}{Conv2DNormActivation}.
 
-    \subsection{Inverted Operations}
+    \subsection{Tranpose Convolution Layer}
+        A transpose convolution is a partial reverse of the convolution operations.
 

### 2024-04-10 Notebook LaTEX/Machine Learning/main.tex
>w< wdkstp

@@
     \subsection{Tranpose Convolution Layer}
-        A transpose convolution is a partial reverse of the convolution operations.
+        A transpose convolution is not a partial reverse of the convolution operations. 
+        It simply another convolution layer where parameters such as: ``\inlinecode{stride, padding, dilation}'' means different things. 
+        It increase the dimension of the input signal instead of decreasing it. 
+        It's usually used as a learnable upsample component inside of a Neural Network. 
+        For more information visit \href{https://pytorch.org/docs/stable/generated/torch.nn.ConvTranspose1d.html}{CONV2DTRANSPOSED} for pytorch documentations.
 
@@
 \section{Computer Vision Networks}
+    \subsection{ResNet}
 
-\section{Case Study | Direct LiDAR Point Cloud Architecture}
+\section{Image Instance Segmentations}
+    We introduce the problem of Image Instance Segmentations. 
+    Given an image that contains objects of interests, we want: 
+    \begin{enumerate}
+        \item [1.] Classify objects by the categories 
+        \item [2.] Segment/identify their locations on the images. 
+        \item [3.] Differentiate different instance of the objects that belong to category of interest. 
+    \end{enumerate}
+
+    \subsection{Faster RCNN}
+        In this section, we take a look at ``Faster RCNN'' proposed by Ren et al.\cite{ren_faster_2016}. 
+        Read \href{https://www.neuralception.com/objectdetection-fasterrcnn/}{this blog post} for a quick overview of the neural network. 
+        \subsubsection{Region Proposal Network}
+
+            The RPN takes input from convolutional feature map and propose rectangular back in the original images that may contain objects of intersts. 
+            It consists of a small network (referred as mini network) that slides through the convolution featuer map to produce output. 
+            In paper, the mini network takes in a  tensor from the convolutional feature map as the input. 
+            The output at each location is fed into two components, one for box regression, and the other one for box classifications. 
+            The feature maps are low dimensional laten features produced by any generic vision networks.
+            \par
+            The pytorch implementations of the Region proposal network can be found \href{https://github.com/pytorch/vision/blob/5181a854d8b127cf465cd22a67c1b5aaf6ccae05/torchvision/models/detection/rpn.py}{here}.
+            In MATLAB, it's implemented as one single atomic component and it's made by the function \href{https://www.mathworks.com/help/vision/ref/nnet.cnn.layer.regionproposallayer.html}{\inlinecode{regionProposalLayer}}.
 
 \section{Case Study | The Deepforest Project}
+\section{Case Study | Direct LiDAR Point Cloud Architecture}
 
@@
 \bibliographystyle{plain}
-% \bibliography{refs.bib}
+\bibliography{MLGeneral.bib}
 

### 2024-04-10 Notebook LaTEX/Machine Learning/main.tex
>w< mcbr

@@
 \end{abstract}
+
 \tableofcontents
@@
 
+    \subsection{Batch Normalization Layer}
+
 \section{Graphical Model and Probability Dependence}
@@
 \section{Computer Vision Networks}
-    \subsection{ResNet}
+    \subsection{Residual Net}
+        Residual net is one of the most phenomenal vision network. 
+        Back in the early day people use to train deeper and deeper convolutional networks, but the convergence of the error gets worse as the layer deepens. 
+        He et al.\cite{he_deep_2015} proposed a remedy. 
+        The remedy for low convergence of raining and test error to set up the neural network to learn perturbations on an identity map, they call it the residual neural network.
 
@@
         \subsubsection{Region Proposal Network}
-
-            The RPN takes input from convolutional feature map and propose rectangular back in the original images that may contain objects of intersts. 
-            It consists of a small network (referred as mini network) that slides through the convolution featuer map to produce output. 
-            In paper, the mini network takes in a  tensor from the convolutional feature map as the input. 
+            The RPN takes input from \textit{convolutional feature map} (hidden layer of another vision network) propose rectangular region back in the original images that may contain objects of intersts.
+            It consists of a small network (referred as the \textit{mini network}) that slides through the convolutional feature map to produce outputs. 
+            In paper, the mini network takes in a matrix from the convolutional feature map as the input. 
             The output at each location is fed into two components, one for box regression, and the other one for box classifications. 
             The feature maps are low dimensional laten features produced by any generic vision networks.
+            We clear up some key words here: 
+            \begin{enumerate}
+                \item [1.] \textit{Convolutional Feature Map}, in the paper, it refers to a 2 dimensional tensor that is the hidden layer of any vision network, i.e: VGG, AlexNet, or RestNet. 
+                \item [2.] \textit{Reception Field}.
+Take any outputs $(i, j, c)$ from the convolutional feature map, the ouput can be tranced back to a region in the original image, i.e: pixels $(i', j', c')$ in the original image where perturbing pixels values will change the output at $(i, j, c)$ in the convolutional feature map.
+                \item [3.] \textit{Mini Network}. It's the neural network that we slide through the center of every position in the convolutional feature map. 
+                The same mini-network is used for the convolutional feature map of the entire image. 
+            \end{enumerate}
             \par
@@
             In MATLAB, it's implemented as one single atomic component and it's made by the function \href{https://www.mathworks.com/help/vision/ref/nnet.cnn.layer.regionproposallayer.html}{\inlinecode{regionProposalLayer}}.
+            \begin{definition}[Anchor Boxes]
+                Let a tensor $X$ of shape $(H, W, C)$ be the feature map resulted from a single input sample.
+                The mini network takes in $X_{[i-1:i+1, j-1:j+1, :]}$, from the feature map and it produces \textit{anchor boxes} and classifications scores for each box. 
+                These \textit{anchors boxes} represent regions with a fixed set of ratios and sizes, corresponding to a region in the original image (it will be used by other components inside of RCNN neural network) centered at the center of the reception field of $X_{[i, j, :]}$.
+                The center of the reception field of any give output location $(i, j)$ in the convolutional feature map are referred to as \textit{anchor}. 
+            \end{definition}
+            \begin{remark}
+                Anchor boxes are produced by the mini network and it consists of $k$ boxes at each anchor. 
+                The mini network only predict predetermined type of anchor boxes.
+                We state the following facts associated with the anchor boxes.  
+                \begin{enumerate}
+                    \item [1.] The output for the bounding box are 4 of the coordinate related to the center of the anchor. 
+                    \item [2.] An anchor is in the input image, framing the object of interests and the parameters are the relevant coordinate. 
+                \end{enumerate}
+            \end{remark}
+            \par
+            We now discuss the mini network (RPN Head) component. 
+            In the paper, It takes in a $n\times n$ region from the feature map, pass it through several layers of convolutional network, branch into two $1\times 1$ convolution layer before. 
+            They are then flattened into a vector and feed into two dense stacked linear neural networks. These two dense networks are classifications, and regression network. 
+            The source code of this component is \href{https://github.com/pytorch/vision/blob/5181a854d8b127cf465cd22a67c1b5aaf6ccae05/torchvision/models/detection/rpn.py#L15}{line 15 here}. 
+            We will talk more about it when it comes to training the RPN using a loss function.
 
 \section{Case Study | The Deepforest Project}
+    Links: 
+    \begin{enumerate}
+        \item \href{https://github.com/weecology/DeepForest/blob/6b1c199ce65f95dc74c9e79d1e2c686e784910b2/deepforest/main.py}{Deepforest repo source code commit \inlinecode{7992b82}, main.py}. 
+        \item \href{https://deepforest.readthedocs.io/en/latest/getting_started.html}{Deep forest documentations. }
+    \end{enumerate}
+
 \section{Case Study | Direct LiDAR Point Cloud Architecture}

### 2024-04-23 Latex Templates/Generic Report/main.tex
>w<
>w< mcbr a lot of changes

@@
 \documentclass[]{article}
-\usepackage{amsmath}
-\usepackage{amsfonts} 
-\usepackage[english]{babel}
-\usepackage{amsthm}
-\usepackage{mathtools}
-\usepackage{subcaption}
-\usepackage{hyperref}
-\usepackage{algorithmic}
-\usepackage{algorithm}
-% \usepackage{minted}
 
-% Basic Type Settings ----------------------------------------------------------
-\usepackage[margin=1in,footskip=0.25in]{geometry}
-\linespread{1}  % double spaced or single spaced
-\usepackage[fontsize=12pt]{fontsize}
-\usepackage{authblk}
+\input{presets/presets_basics.tex}
 
-\theoremstyle{definition}
-\newtheorem{theorem}{Theorem}       % Theorem counter global 
-\newtheorem{prop}{Proposition}[section]  % proposition counter is section
-\newtheorem{lemma}{Lemma}[subsection]  % lemma counter is subsection
-\newtheorem{definition}{Definition}
-\newtheorem{remark}{Remark}[subsection]
-{
-    % \theoremstyle{plain}
-    \newtheorem{assumption}{Assumption}
-}
-\numberwithin{equation}{subsection}
-
-\hypersetup{
-    colorlinks=true,
-    linkcolor=blue,
-    filecolor=magenta,
-    urlcolor=cyan,
-}
-\usepackage[final]{graphicx}
-\usepackage{listings}
-\usepackage{courier}
-\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
-\newcommand{\indep}{\perp \!\!\! \perp}
-\usepackage{wrapfig}
-\graphicspath{{.}}
-\usepackage{fancyvrb}
-
-%%
-%% Julia definition (c) 2014 Jubobs
-%%
-\usepackage[T1]{fontenc}
-\usepackage{beramono}
-\usepackage[usenames,dvipsnames]{xcolor}
-\lstdefinelanguage{Julia}%
-  {morekeywords={abstract,break,case,catch,const,continue,do, else, elseif,%
-      end, export, false, for, function, immutable, import, importall, if, in,%
-      macro, module, otherwise, quote, return, switch, true, try, type, typealias,%
-      using, while},%
-   sensitive=true,%
-   alsoother={$},%
-   morecomment=[l]\#,%
-   morecomment=[n]{\#=}{=\#},%
-   morestring=[s]{"}{"},%
-   morestring=[m]{'}{'},%
-}[keywords,comments,strings]%
-\lstset{%
-    language         = Julia,
-    basicstyle       = \ttfamily,
-    keywordstyle     = \bfseries\color{blue},
-    stringstyle      = \color{magenta},
-    commentstyle     = \color{ForestGreen},
-    showstringspaces = false,
-}
-
-\title{This is The Title}
+\title{Generic Report}
 \author{Name of the Author}
@@
 \begin{abstract}
-    This is the Abstract
+    What is life? Why are we here? Where did we come from?
 \end{abstract}
@@
 For some brain expanding julia code, read \hyperref[code:brain_expand]{brain expanding julia code}.
-    \begin{algorithm}
-        \begin{algorithmic}[H]
+    \begin{algorithm}[H]
+        \begin{algorithmic}[t]
             \STATE{\textbf{Input: $X^{(t)}$}}
@@
     \label{code:brain_expand}
-    \lstinputlisting[language=julia, basicstyle=\ttfamily\tiny,numbers=left]{Code/juliacode.jl}
+    \lstinputlisting[language=julia, basicstyle=\ttfamily\scriptsize,numbers=left]{Code/juliacode.jl}
 

### 2024-04-23 Latex Templates/Scientific/main.tex
>w< mcbr a lot of changes

\documentclass[12pt]{article}

% \input{presets/wang_full.tex}
\input{presets/wang/input.tex}
\input{presets/misc.tex}
\input{presets/julia_lstlisting.tex}

\begin{document}

\title{{\fontfamily{ptm}\selectfont Lorum ipsum}}

\author{
    Author 1 Name, Author 2 Name
    \thanks{
        Subject type, Some Department of Some University, Location of the University,
        Country. E-mail: \texttt{author.name@university.edu}.
    }
}

\date{March 2, 2020}

\maketitle

% \vskip 8mm

\begin{abstract} 
    \noindent
    Lorem ipsum dolor sit amet, dicta iudicabit consequat ex vix, veniam legimus appetere has id, an pri graece epicuri detraxit. Ea aliquam expetendis posidonium eos, nam invenire corrumpit imperdiet ei. Et constituto dissentias usu, mel solum erant et. Mel dolorem menandri in.
\end{abstract}

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 47H05, 52A41, 90C25; Secondary 15A09, 26A51, 26B25, 26E60, 47H09, 47A63.
\noindent{\bfseries Keywords:}

% ==============================================================================
\input{sections/demo_notations.tex}
\input{sections/demo_code.tex}

% ==============================================================================

\section{Schur's Cone and Its Polar}
    \begin{example}
        Define
        \begin{equation}
            Q = \left\lbrace
                x\in \RR^n \left|
                    \sum_{i = 1}^{k} x_i
                    \ge 0, \;
                    k = 1 ,\cdots, n-1, \;
                    x_1 + \cdots + x_n = 0
                \right.
            \right\rbrace.
        \end{equation}
        Then
        \begin{align}
            Q^\circ &= \left\lbrace
               y\in\RR^n |
               \langle y, x\rangle \ge 0 \; \forall x \in Q
            \right\rbrace
            \\
            &=
            \left\lbrace
                y\in\RR^n | y_{1} \ge y_2\ge \cdots  \ge y_n
            \right\rbrace.
        \end{align}
    \end{example}
    \begin{proof}
        We have $Q = H(\RR^{n - 1}_+)$, where
        \begin{align}
            H =
            \begin{bmatrix}
                1 &  & &
                \\
                -1 & 1 & &
                \\
                 & -1 & &
                \\
                &  & \ddots&
                \\[-1em]
                &  & & 1
                \\
                &  && -1
            \end{bmatrix},
        \end{align}
        $H$ is a bi-diagonal matrix with zeros on the diagonal and -1 on its sub-diagonals. Indeed, for $x = (x_1, \cdots, x_{n - 1})\in \RR^{n - 1}_+$, we have
        \begin{align}
            y &= H x
            \\
            &=
            \begin{bmatrix}
                1 \\ -1 \\ 0 \\ \vdots \\ 0
            \end{bmatrix}x_1 +
            \begin{bmatrix}
                0 \\ 1 \\ -1 \\ \vdots \\ 0
            \end{bmatrix}x_2 +
            \cdots
            +
            \begin{bmatrix}
                0 \\ 0 \\ \vdots \\ 1 \\ -1
            \end{bmatrix} x_{n - 1}
            \\
            &=
            \begin{bmatrix}
                x_1 \\ x_2 - x_1 \\ x_3 - x_2
                \\ \vdots
                \\-x_{n - 2} + x_{n - 1}\\
                 - x_{n - 1}
            \end{bmatrix}
            = \begin{bmatrix}
                y_1 \\ y_2 \\ y_3 \\ \vdots \\ y_{n - 1} \\ y_n
            \end{bmatrix},
        \end{align}
        where $y_1 \ge 0, y_2 + y_1 \ge 0, \cdots, y_{n - 1}+ \cdots + y_1 \ge 0$, and $y_1 + \cdots + y_n = 0$. So $y\in Q$. Hence $H(\RR^{n - 1}_+)\subseteq Q$. Similarly, one can write for $y\in Q$, $\exists x \in \RR_+^{n- 1}$ with $y = Hx$. In fact, $x = y_1, x_2 = y_1 + y_2, \cdots, x_{n - 1} = y_1 + \cdots + y_{n - 1}, -x_{n - 1} = y_n$ because $y_1 + \cdots + y_n = 0$. In particular, $x\in \RR^{n - 1}_+$.
        \par
        Note that $y\in Q^\circ\iff y^{\intercal}a_i \ge 0$ for $i = 1,\cdots, n -1$. Where
        \begin{align}
            a_1 = \begin{bmatrix}
                1 \\ -1 \\ 0 \\ \vdots \\ 0,
            \end{bmatrix},
            a_2 = \begin{bmatrix}
                0 \\ 1 \\ -1 \\ \vdots \\ 0,
            \end{bmatrix},
            & \cdots,
            a_n =
            \begin{bmatrix}
                0 \\ \vdots \\ 0  \\ 1 \\ -1
            \end{bmatrix}.
        \end{align}
        Now $y^{\intercal} a_i \ge 0 \iff y_i - y_{i + 1}\ge 0$, for $i = 1,\cdots, n-1$. Hence $Q^\circ = \{ y\in \RR^n | y_1 \ge y_2 \ge \cdots \ge y_n\}$.

    \end{proof}
\section{Lorentz Cone and its Polar}
    \begin{example}
        \begin{equation}
            L = \left\lbrace
            (\xi, t) \in \RR^n \left| \;
                \Vert \xi\Vert \le t, \xi \in \RR^{n - 1}
            \right.
            \right\rbrace.
        \end{equation}
        Then the polar cone of $L$ is $L^\circ = \{(x, s) \;|\; \langle (x, s), (\xi, t)\rangle \ge 0\}\} = L$.
    \end{example}
    \begin{proof}
        \par
        Let $(x, s) \in L^\circ$. Then $\langle (x, s), (\xi, t)\rangle \ge 0$, $\forall (\xi, t) \in L$, i. e. $\langle x, \xi\rangle + st \ge 0$.
        \par
        For $t > 0$, we have $\langle x, \xi/t\rangle \ge -s$, i.e. $\langle x, - \xi/t\rangle \le s$. Using $\Vert \xi\Vert \le t$ and by taking supremum over $\Vert \xi/t\Vert\le 1$, we obtain  $\Vert x\Vert \le s$.
        \par
        Hence $L^\circ = L$.
    \end{proof}
    \begin{corollary}
        Let $A \in \RR^{n\times n}$ be positive definite. Define
        $$
            L_A =
            \left\lbrace
                (\xi, t)\in \RR^n \left|
                    \sqrt{\langle \xi, A\xi\rangle} \le t
                \right.
            \right\rbrace.
        $$
        Then $(L_A)^\circ = \{ (\xi, t) \;|\; \sqrt{\langle \xi, A^{-1}\xi\rangle}\le t\}$.
    \end{corollary}

\section*{Acknowledgments}
    XW were supported by NSERC Discovery grants.

\begin{thebibliography}{999}

    \bibitem{BC2017}
    H.H.\ Bauschke and P.L.\ Combettes,
    \emph{Convex Analysis and Monotone Operator Theory in Hilbert Spaces},
    second edition,
    Springer, 2017.

    \bibitem{cross}
    H.~H.\ Bauschke, M.\ Krishan Lal, and X.\ Wang, The projection onto the cross, (2021), \url{https://arxiv.org/abs/2108.04382}.

    \bibitem{Bertsekas}
    D.P.\ Bertsekas,
    \emph{Nonlinear Programming}, third edition, Athena Scientific, Belmont, Massachusetts, USA, 2016.

    \bibitem{burden2011analisis}
    R. L.\ Burden and J.D. \ Faires, \emph{Numerical Analysis}, 9th edition, 2011.
    \bibitem{quadrics} N.\ Chernov and H.\ Ma, Least squares fitting of quadratic curves and surfaces, \emph{Computer Vision} 285, p302, 2011.

    \bibitem{conics} N.\ Chernov and S.\ Wijewickrema,  Algorithms for projecting points onto conics, \emph{ Journal of Computational and Applied Mathematics}, 251, (2013), 8-21.

    \bibitem{robust} D.\ Eberly, \emph{Robust and Error-free Geometric Computing}, CRC Press, 2021.

    \bibitem{elser2019learning} V.\ Elser, Learning without loss,
    \emph{Fixed Point Theory and Algorithms for Sciences and Engineering} 2021, article~12 (2021).
    \url{https://doi.org/10.1186/s13663-021-00697-1}

    \bibitem{elser2017products}
    V.\ Elser, Matrix product constraints by projection methods, \emph{Journal of Global Optimization} 68, no 2, (2017), 329-355.

    \bibitem{PW16}
    Planiden C , Wang X . Strongly Convex Functions, Moreau Envelopes, and the Generic Nature of Convex Functions with Strong Minimizers[J]. \emph{SIAM Journal on Optimization}, 2015, 26(2):1341-1364.

    \bibitem{kreyszig} E.\ Kreyszig, \emph{Introductory Functional Analysis with Applications},
    John Wiley \& Sons, Inc., New York, 1989.

    \bibitem{Luenberger}
    D.G.\ Luenberger,
    \emph{Optimization by Vector Space Methods},
    Wiley, 1969.

    \bibitem{Luke2020}
    D.~R. Luke. and A.L. Martins, Convergence Analysis of the Relaxed Douglas--Rachford Algorithm. \newblock {\em SIAM Journal on Optimization}, 30(1), (2020), pp.542-584.

    \bibitem{Rock98}
    R.\ T.\ Rockafellar and R.\ J-B Wets,
    \emph{Variational Analysis},
    Springer-Verlag, New York, 1998.

\end{thebibliography}

\end{document}

### 2024-04-23 Latex Templates/Scientific/presets/julia_lstlisting.tex
>w< mcbr a lot of changes

--- 2024-04-08 Notebook LaTEX/Machine Learning/main.tex
@@
-\documentclass[]{article}
-\usepackage{amsmath}
-\usepackage{amsfonts} 
-\usepackage[english]{babel}
-\usepackage{amsthm}
-\usepackage{mathtools}
-\usepackage{subcaption}
-\usepackage{hyperref}
-\usepackage{algorithmic}
-\usepackage{algorithm}
-\usepackage{anyfontsize} % fix font size warning. 
-\usepackage{url} 
-\urlstyle{same} % fix wacky url links in bib entries. 
-% \usepackage{minted}
-
-% Basic Type Settings ----------------------------------------------------------
-\usepackage[margin=1in,footskip=0.25in]{geometry}
-\linespread{1}  % double spaced or single spaced
-\usepackage[fontsize=12pt]{fontsize}
-\usepackage{authblk}
-
-\theoremstyle{definition}
-\newtheorem{theorem}{Theorem}       % Theorem counter global 
-\newtheorem{prop}{Proposition}[section]  % proposition counter is section
-\newtheorem{lemma}{Lemma}[subsection]  % lemma counter is subsection
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}[subsection]
-\newtheorem{remark}{Remark}[subsection]
-{
-    % \theoremstyle{plain}
-    \newtheorem{assumption}{Assumption}
-}
-\newtheorem{fact}{Fact}[subsection]
-\numberwithin{equation}{subsection}
-
-\hypersetup{
-    colorlinks=true,
-    linkcolor=blue,
-    filecolor=magenta,
-    urlcolor=cyan,
-}
-\usepackage[final]{graphicx}
-\usepackage{listings}
-\usepackage{courier}
-\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
-\newcommand{\indep}{\perp \!\!\! \perp}
-\usepackage{wrapfig}
-\graphicspath{{.}}
-\usepackage{fancyvrb}
-
-\newcommand{\inlinecode}[1]{\texttt{\footnotesize #1}}
-
-%% CUSTOMIZED MATHEMATICAL OPERATORS ===========================================
-
-%%
-%% Julia definition (c) 2014 Jubobs
-%%
-\usepackage[T1]{fontenc}
-\usepackage{beramono}
-\usepackage[usenames,dvipsnames]{xcolor}
+\usepackage{listings} \lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
 \lstdefinelanguage{Julia}%
@@
 }
-
-\title{Machine Learning, a Review for Tree Segmentations Task}
-\author{}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-    This is my own notes. 
-\end{abstract}
-\tableofcontents
-
-\section{Introduction}
-    Artificial Neural networks represents modes of numerical computations that are differentiable programs. 
-    We skips the basics and assume the reader already know something about Deep Neural Network, their components, and the automatic differentiation program on modern deep learning frameworks. 
-    For our discussion we introduce some definitions to make for a better presentation of computataional concepts occured in Artificial Neural Networks (ANNs). 
-    \par
-    \subsection{Notations, Common Operations}
-        The index starts with ``1'' in our writings. 
-        But it starts with zero if we are using programming languages such as python. 
-        To distinguish these 2 type of indexing on a tensor $X$, we use $X_{i_1, 1_2, \cdots}$ to denotes indexing using the natural number and we use $X_{[i_1, i_2, \cdots]}$ to denote indexing of the tensor using offset indices that starts with zero.
-    \begin{definition}[Component]
-        A component is a function $f(x; p|w): \mathbb R^m \mapsto \mathbb R^n$. 
-        $x$ is the inputs and $w$ represent trainable parameters, usually in the form of a multi-dimensional array. 
-        And $p$ represents parameters that are not trainable parameters.
-
-    \end{definition}
-    \begin{definition}[Connection]
-        Let $f:\mathbb R^n \mapsto \mathbb R^m, g: \mathbb R^m \mapsto \mathbb R^k$ be two components, then a connection between is a $\mathbb R^m \mapsto \mathbb R^m$ function $h(x; p | w)$ with trainable parameters $w$, and parameter $p$.
-    \end{definition}
-
-    \begin{example}[Dense Layer]
-        Let $m, n \in \mathbb N$, let $A \in \mathbb R^{n\times m}$, $b \in \mathbb R^n$, then a Dense layer is a $\mathbb R^m \mapsto \mathbb R^n$ functions with a list of activation functions $\sigma_i$ for $i = 1, \cdots, n$.
-        Let $x \in \mathbb R^m$ be the input, then a dense layer is a component. We define its computation: 
-        $$
-        \begin{aligned}
-            \text{DnsLyr}(x ; m, n | (A, b), \{\sigma_i\}_{i=1}^n) = 
-            \left[
-                z \mapsto \bigoplus_{i = 1}^n\sigma_i(z_i)
-            \right]
-            \left(
-                Ax + b
-            \right). 
-        \end{aligned}
-        $$
-        Where, inside of $[\cdot]$, we denote the definition of a anonymous function. 
-    \end{example}
-
-    \begin{example}[Multi-Layer Perceptron]
-        Let $l_1, l_2, \cdots, l_N$ be integers. 
-        We define the Multi-Layer Perceptron to be a composition of dense layer mapping from $l_{i}$ to $l_{i + 1}$ for $i = 1, \cdots, N - 1$. 
-        Let $\sigma_{i, j}$ represent the activation function for the $j$ th output in the $i$ th layer. 
-        Then a Multi-Layer Perceptron (MLP) is a component admit representation
-        $$
-        \begin{aligned}
-            & \text{MLP}\left(x ; l_1, \cdots, l_n | \{(A_i, b_i)\}_{i=1}^N\right): \mathbb R^{l_1} \mapsto \mathbb R^{l_N}
-            \\
-            :=&
-            \left[
-            \bigodot_{i = 1}^n \text{DnsLyr}
-            \left(
-                (\cdot) ; l_i, l_{i + 1} \left| (A_i, b_i), \{\sigma_{j, i}\}_{j=1}^{l_i} \right.
-            \right)
-            \right](x). 
-        \end{aligned}
-        $$
-        Where $\bigodot$ is functional composition and it represents $\bigodot_{i=1}^n f_i = f_n\circ\cdots\circ f_1(x)$, and $(\cdot)$ represents the input of the anonymous function, in this case it's the dense layer.
-    \end{example}
-
-\section{Basic of Neural Architecture}
-    These concepts and components are relevant to the architecture of Vision Networks. 
-    \begin{definition}[Convolution 2D]
-        Let $u, v$ be multi-array of dimension $m \times n$ and $k \times l$. 
-        We assume that $m \le  k$ and $n \le l$.
-        Then the convolution operator $*$ is a mapping from $(\mathbb C^M \times \mathbb C^n)\times (\mathbb C^k \times \mathbb C^l) \mapsto \mathbb C^{(m - k)\times (n - l)}$. 
-        Then the convolution is defined as 
-        $$
-        \begin{aligned}
-            (u* v)_{t, \tau} = 
-            \sum_{i = 1}^{k}\sum_{j = 1}^{l}u_{i, j}v_{i + t, j + \tau}. 
-        \end{aligned}
-        $$
-    \end{definition}
-    \subsection{The Input and Output of Multi-Channel Fixed Dimension Signal}
-        In this section, we discuss the shape of the output signal for a 2D/1D signal after 
-        \begin{enumerate}
-            \item Max/average Pooling,
-            \item Convolution. 
-        \end{enumerate}
-        Here we note that these above operations places the same type of constraints on the output shape of the signal given the shape of the input. 
-        We all these type of operations: ``Multi-Channel Fixed Dimenion Transform (MCFDT)''. 
-        This is not a name from the literature I just made it up. 
-        These operations share a common set of parameters that determine the shape of the output tensor given the shape of the output tensor. 
-        These are the list of parameters: 
-        \begin{enumerate}
-            \item \inlinecode{in\_channel}: Type integers. The number of channels expected for the input signal.
-
-            \item \inlinecode{Out\_channels}: Type integers. The number of channel expected for the output signal.
-
-            \item \inlinecode{kernel\_size}: The size of the kernel used for the 1D signal, for certain type of operations.
-The kernel represent the size of the window where an computations are going to carry out locally on the input signal.
-
-            \item \inlinecode{stride}: How many elements does the kernel skips with respect to the input signal for each of the adjacent output elements in the output signal.
-
-            \item \inlinecode{padding}: The numbers of zero/null/-inf elements added to the 2 side of the 1D signal. 
-                \begin{enumerate}
-                    \item \inlinecode{padding\_mode}: Determine different modes of padding the boundary of the input signal. 
-                    \begin{enumerate}
-                        \item  \inlinecode{zero}, (default)
-                        \item  \inlinecode{reflect}, 
-                        \item  \inlinecode{replicate}, 
-                        \item  \inlinecode{circular}. 
-                    \end{enumerate}
-                \end{enumerate}
-
-            \item \inlinecode{dilation}: Spacing between the elements of the kernels.
-
-            \item \inlinecode{blocks}: Number of blocked connections from intput channels to output channels, default to 1.
-
-            \item \inlinecode{bias}: Add learnable bias to the component, default to `true'. 
-        \end{enumerate}
-
-        \begin{fact}[MCFDT 1D]
-            Let input signal be a tensor of size $(N, C, L)$. 
-            \begin{enumerate}
-                \item $N$ is the number of samples from the batch. 
-                \item $C$ is the number of imput channels for the signal. 
-                \item $L$ is the length of the input signal. 
-            \end{enumerate}
-            Let $p, d, k, s$ denotes: "padding, dilation, kernel size, stride". 
-            Then the output signal is a tensor of size $(N, C', L')$ with 
-            \begin{align}
-                L' = \left\lfloor
-                    \frac{(L + 2p)- (d(k-1)+1)}{s} + 1
-                \right\rfloor. 
-            \end{align}
-            The parameter $C'$, is user defined. 
-        \end{fact}
-        \begin{remark}
-            The size of the input signal with paddin is $(L + 2p)$. 
-            The size of the dilated kernel is $d(k - 1)$. 
-            The $+1$ on the numerator of the fraction and the $+1$ at the outside of the fraction remains as a mystery to the writer. 
-            The process of computing the shape for an input signal of dimension $(N, C, [\cdots])$, is applying the same computations on all the dimensions to compute the output of the signal. 
-        \end{remark}
-        \begin{fact}[MCFDT 2D]\label{fact:MCFDT_2D}
-            Let $X$ be a tensor of shape $(C, N, L_1, L_2)$, then the output signal is of size $(C', N, L_1', L_2')$, where $C'$ is defined. 
-            \begin{enumerate}
-                \item $N$ is the number of samples from the batch. 
-                \item $C$ is the number of imput channels for the signal. 
-                \item $L$ is the length of the input signal. 
-            \end{enumerate}
-
-            Let $p_i,d_i,k_i,s_i, \; i \in \{1, 2\}$ be the ``padding, dilation, kernel size, stride'' along the $L_1$ and $L_2$ dimension of the input signal. 
-            Then the shape parameters $(L_1', L_2')$ can be computed by the formula: 
-            $$
-            \begin{aligned}
-                L'_i = \left\lfloor
-                \frac{(L_i + 2p_i)- (d_i(k_i-1)+1)}{s_i} + 1
-                \right\rfloor \quad \forall i \in \{1, 2\}. 
-            \end{aligned}
-            $$
-        \end{fact}
-        \begin{remark}
-            This is analogous to the 1D case and it's just applying the same formula to the corresponding dimension of the tensor to determine the shape of the output tensor. 
-        \end{remark}
-
-    \subsection{Convolutional Layers}
-        In this section we talk about \href{https://pytorch.org/docs/stable/generated/torch.nn.Conv2d.html}{2D convolution component (pytorch link)} inside of an ANNs. 
-        The convolution operations module contains more detailed parameters. 
-        \begin{definition}[2D Convolution Layers]
-            Assuming that we have a single sample. 
-            Let $(C, H, W)$ be the shape of the input tensor. 
-            $C$ is the number of channel, and $H, W$ are the height and width. 
-            We use this because image tensors are usually in the shape of $(3, H, W)$. 
-            Define the component to be a function, mapping from $(C', H', W')$. 
-            Let $(C', C, K, L)$ denotes the dimension of the kernel tensor denoted by: $\mathcal K$. 
-            Then mathematically, the computation of the output tensor $Y$ given input tensor $X$ can be computed as
-            {\large
-            \begin{align}
-                Y_{c', h', w'} = 
-                \text{ReLU}\left( b_{c'} + 
-                \sum_{k = 1}^{C} (\mathcal K_{c',k,:, :} * X)_{h', w'}\right). 
-            \end{align}
-            }
-        \end{definition}
-
-        \begin{remark}
-            There is a bias term and an activation function for a specific channel. 
-            The kernel for an image, which is a 3D tensor, is also a 3D tensor. 
-            A single tensor is applied to all channels of the input channel, aggregated by summing up across these different channels. 
-            \begin{enumerate}
-
-                \item  ``group'', see \href{https://towardsdatascience.com/conv2d-to-finally-understand-what-happens-in-the-forward-pass-1bbaafb0b148}{here} for an explanations. 
-            \end{enumerate}
-            The activaton function above is ``ReLU'', but it doesn't have to be. 
-            See \href{https://pytorch.org/docs/stable/generated/torch.nn.Conv2d.html}{here} for the pytorch documentations. 
-            The size of the output tensor is determined by \hyperref[fact:MCFDT_2D]{fact \ref*{fact:MCFDT_2D}}. 
-        \end{remark}
-
-    \subsection{Pooling Layers}
-        Let's define these quantities 
-        \begin{enumerate}
-            \item $(N, C, H, W)$ is the size of the input signal. 
-            \item $(N, C, H', W')$ is the signal of the output layer.
-            \item $(k_1, k_2)$ is the size of the kernel. 
-            \item $N$ is usually the size of the batched samples. 
-            \item $[s_1, s_2]$ be the stride parameters for the kernels. 
-        \end{enumerate}
-
-        \begin{definition}[2D Max Pooling Layers]
-            Let $X$ be the signal of size $(N,C, H, W)$, let the output signal be $Y$ of size $(N, C, H', W')$, then the output can be precisely described by the following formula: 
-            {
-            \large
-            \[
-                \begin{aligned}
-                    Y_{i,c, h, w} = 
-                    \max_{
-                        \substack{m = 1, \;\cdots, k_1 - 1\\n = 1, \; \cdots \; , k_2-1}
-                    }
-                    \{
-                        X_{i, c, hs_1 + m, s_2w + n}
-                    \}. 
-                \end{aligned} 
-            \]
-            }
-        \end{definition}
-        \begin{remark}
-            See \href{https://pytorch.org/docs/stable/generated/torch.nn.MaxPool2d.html}{max pool 2d} for pytorch documentation for this component. 
-        \end{remark}
-
-        \begin{definition}[2D Averge Pooling Layer]
-            Let $X$ be the input signal of size $(N, C, H, W)$, let output signal $Y$ be of size $(N, C, H', W')$, then the output for an average pooling layer can be computed as
-            {\large
-            \begin{align*}
-                Y_{[i, c, h, w]} = 
-                \operatorname{mean} \left(
-                    X_{[i, c, hs_1 + m, hs_2 + n]}, m \in \{ 0, \cdots, k_1 -1\}, n \in \{0 \cdots, k_2 -1\}
-                \right). 
-            \end{align*}
-            }
-        \end{definition}
-        \begin{remark}
-            See \href{https://pytorch.org/docs/stable/generated/torch.nn.AvgPool2d.html}{averaeg pool 2d} for pytorch documentation for this component. 
-        \end{remark}
-    \subsection{Convolution 2D Normalization Layer}
-        The convolution 2D Normalized layer sandwitch one batch normalization between layers of 2D convolutions. 
-        For more information visit \href{https://pytorch.org/vision/main/generated/torchvision.ops.Conv2dNormActivation.html}{Conv2DNormActivation}.
-
-    \subsection{Tranpose Convolution Layer}
-        A transpose convolution is a partial reverse of the convolution operations.
-
-\section{Graphical Model and Probability Dependence}
-    Graphical models are used to model probability dependence between random variables. 
-    In the context of deep learning, it helps with training hierarchical models.
-
-\section{Variational Autoencoder, Bayesian Learning}
-
-\section{Computer Vision Networks}
-
-\section{Case Study | Direct LiDAR Point Cloud Architecture}
-
-\section{Case Study | The Deepforest Project}
-
-\section{Case Study | Forest Allometrics Extractions, Predictions}
-
-\appendix
-\section{Appendix Section 1}
-    This is the appendix section.
-
-\bibliographystyle{plain}
-% \bibliography{refs.bib}
-
-\end{document}

### 2024-05-09 Notebook LaTEX/Momentum Accelerations/code/juliacode.jl
>w< wdkstp

@@ -1,0 +1,18 @@
+"""
+A doubly stochastic chain sampler that uses wrapped guassian distributions on both directions in 2D 
+with a fixed variance. 
+"""
+function wrapped_gaussian_sampler_2d(
+    state::Vector{T},
+    lower_left::Tuple{Real, Real}, 
+    upper_right::Tuple{Real, Real};
+    sigma::Real=1
+) where {T<:Real}
+    lower = [lower_left[1], lower_left[2]]
+    upper = [upper_right[1], upper_right[2]]
+    function loop_back(x, l, u)  # assert periodic conditions on the rectangle. 
+        return mod(x, u - l) + l
+    end
+    N = Normal(0, sigma)
+    return loop_back.(state + rand(N, 2), lower, upper)
+end

### 2024-05-14 Notebook LaTEX/Momentum Accelerations/main.tex
>w< wdsktp

--- 2024-04-23 Latex Templates/Scientific/main.tex
@@
 \author{
-    Author 1 Name, Author 2 Name
+    Alto Legato
     \thanks{
@@
     \noindent
-    Lorem ipsum dolor sit amet, dicta iudicabit consequat ex vix, veniam legimus appetere has id, an pri graece epicuri detraxit.
-Ea aliquam expetendis posidonium eos, nam invenire corrumpit imperdiet ei.
-Et constituto dissentias usu, mel solum erant et.
-Mel dolorem menandri in.
+    These are ntoes for Nesterov Type Acceleration Methods, in the convex case. 
 \end{abstract}
-
 \noindent{\bfseries 2010 Mathematics Subject Classification:}
@@
 % ==============================================================================
-\input{sections/demo_notations.tex}
-\input{sections/demo_code.tex}
+\section{Preliminaries}
+    In this section we list fundational results that are important for proofs in coming sections. 
+    \subsection{Lipschitz Smoothness}
+    \subsection{Proximal Descent Inequality}
 
-% ==============================================================================
+\section{The Proximal Point Method in the Convex Case}
 
-\section{Schur's Cone and Its Polar}
-    \begin{example}
-        Define
-        \begin{equation}
-            Q = \left\lbrace
-                x\in \RR^n \left|
-                    \sum_{i = 1}^{k} x_i
-                    \ge 0, \;
-                    k = 1 ,\cdots, n-1, \;
-                    x_1 + \cdots + x_n = 0
-                \right.
-            \right\rbrace.
-        \end{equation}
-        Then
-        \begin{align}
-            Q^\circ &= \left\lbrace
-               y\in\RR^n |
-               \langle y, x\rangle \ge 0 \; \forall x \in Q
-            \right\rbrace
-            \\
-            &=
-            \left\lbrace
-                y\in\RR^n | y_{1} \ge y_2\ge \cdots  \ge y_n
-            \right\rbrace.
-        \end{align}
-    \end{example}
-    \begin{proof}
-        We have $Q = H(\RR^{n - 1}_+)$, where
-        \begin{align}
-            H =
-            \begin{bmatrix}
-                1 &  & &
-                \\
-                -1 & 1 & &
-                \\
-                 & -1 & &
-                \\
-                &  & \ddots&
-                \\[-1em]
-                &  & & 1
-                \\
-                &  && -1
-            \end{bmatrix},
-        \end{align}
-        $H$ is a bi-diagonal matrix with zeros on the diagonal and -1 on its sub-diagonals. Indeed, for $x = (x_1, \cdots, x_{n - 1})\in \RR^{n - 1}_+$, we have
-        \begin{align}
-            y &= H x
-            \\
-            &=
-            \begin{bmatrix}
-                1 \\ -1 \\ 0 \\ \vdots \\ 0
-            \end{bmatrix}x_1 +
-            \begin{bmatrix}
-                0 \\ 1 \\ -1 \\ \vdots \\ 0
-            \end{bmatrix}x_2 +
-            \cdots
-            +
-            \begin{bmatrix}
-                0 \\ 0 \\ \vdots \\ 1 \\ -1
-            \end{bmatrix} x_{n - 1}
-            \\
-            &=
-            \begin{bmatrix}
-                x_1 \\ x_2 - x_1 \\ x_3 - x_2
-                \\ \vdots
-                \\-x_{n - 2} + x_{n - 1}\\
-                 - x_{n - 1}
-            \end{bmatrix}
-            = \begin{bmatrix}
-                y_1 \\ y_2 \\ y_3 \\ \vdots \\ y_{n - 1} \\ y_n
-            \end{bmatrix},
-        \end{align}
-        where $y_1 \ge 0, y_2 + y_1 \ge 0, \cdots, y_{n - 1}+ \cdots + y_1 \ge 0$, and $y_1 + \cdots + y_n = 0$.
-So $y\in Q$.
-Hence $H(\RR^{n - 1}_+)\subseteq Q$.
-Similarly, one can write for $y\in Q$, $\exists x \in \RR_+^{n- 1}$ with $y = Hx$.
-In fact, $x = y_1, x_2 = y_1 + y_2, \cdots, x_{n - 1} = y_1 + \cdots + y_{n - 1}, -x_{n - 1} = y_n$ because $y_1 + \cdots + y_n = 0$.
-In particular, $x\in \RR^{n - 1}_+$.
-        \par
-        Note that $y\in Q^\circ\iff y^{\intercal}a_i \ge 0$ for $i = 1,\cdots, n -1$. Where
-        \begin{align}
-            a_1 = \begin{bmatrix}
-                1 \\ -1 \\ 0 \\ \vdots \\ 0,
-            \end{bmatrix},
-            a_2 = \begin{bmatrix}
-                0 \\ 1 \\ -1 \\ \vdots \\ 0,
-            \end{bmatrix},
-            & \cdots,
-            a_n =
-            \begin{bmatrix}
-                0 \\ \vdots \\ 0  \\ 1 \\ -1
-            \end{bmatrix}.
-        \end{align}
-        Now $y^{\intercal} a_i \ge 0 \iff y_i - y_{i + 1}\ge 0$, for $i = 1,\cdots, n-1$. Hence $Q^\circ = \{ y\in \RR^n | y_1 \ge y_2 \ge \cdots \ge y_n\}$.
+\section{Application of the Proximal Point Method}
 
-    \end{proof}
-\section{Lorentz Cone and its Polar}
-    \begin{example}
-        \begin{equation}
-            L = \left\lbrace
-            (\xi, t) \in \RR^n \left| \;
-                \Vert \xi\Vert \le t, \xi \in \RR^{n - 1}
-            \right.
-            \right\rbrace.
-        \end{equation}
-        Then the polar cone of $L$ is $L^\circ = \{(x, s) \;|\; \langle (x, s), (\xi, t)\rangle \ge 0\}\} = L$.
-    \end{example}
-    \begin{proof}
-        \par
-        Let $(x, s) \in L^\circ$. Then $\langle (x, s), (\xi, t)\rangle \ge 0$, $\forall (\xi, t) \in L$, i. e. $\langle x, \xi\rangle + st \ge 0$.
-        \par
-        For $t > 0$, we have $\langle x, \xi/t\rangle \ge -s$, i.e.
-$\langle x, - \xi/t\rangle \le s$.
-Using $\Vert \xi\Vert \le t$ and by taking supremum over $\Vert \xi/t\Vert\le 1$, we obtain  $\Vert x\Vert \le s$.
-        \par
-        Hence $L^\circ = L$.
-    \end{proof}
-    \begin{corollary}
-        Let $A \in \RR^{n\times n}$ be positive definite. Define
-        $$
-            L_A =
-            \left\lbrace
-                (\xi, t)\in \RR^n \left|
-                    \sqrt{\langle \xi, A\xi\rangle} \le t
-                \right.
-            \right\rbrace.
-        $$
-        Then $(L_A)^\circ = \{ (\xi, t) \;|\; \sqrt{\langle \xi, A^{-1}\xi\rangle}\le t\}$.
-    \end{corollary}
-
-\section*{Acknowledgments}
-    XW were supported by NSERC Discovery grants.
-
-\begin{thebibliography}{999}
-
-    \bibitem{BC2017}
-    H.H.\ Bauschke and P.L.\ Combettes,
-    \emph{Convex Analysis and Monotone Operator Theory in Hilbert Spaces},
-    second edition,
-    Springer, 2017.
-
-    \bibitem{cross}
-    H.~H.\ Bauschke, M.\ Krishan Lal, and X.\ Wang, The projection onto the cross, (2021), \url{https://arxiv.org/abs/2108.04382}.
-
-    \bibitem{Bertsekas}
-    D.P.\ Bertsekas,
-    \emph{Nonlinear Programming}, third edition, Athena Scientific, Belmont, Massachusetts, USA, 2016.
-
-    \bibitem{burden2011analisis}
-    R. L.\ Burden and J.D. \ Faires, \emph{Numerical Analysis}, 9th edition, 2011.
-    \bibitem{quadrics} N.\ Chernov and H.\ Ma, Least squares fitting of quadratic curves and surfaces, \emph{Computer Vision} 285, p302, 2011.
-
-    \bibitem{conics} N.\ Chernov and S.\ Wijewickrema,  Algorithms for projecting points onto conics, \emph{ Journal of Computational and Applied Mathematics}, 251, (2013), 8-21.
-
-    \bibitem{robust} D.\ Eberly, \emph{Robust and Error-free Geometric Computing}, CRC Press, 2021.
-
-    \bibitem{elser2019learning} V.\ Elser, Learning without loss,
-    \emph{Fixed Point Theory and Algorithms for Sciences and Engineering} 2021, article~12 (2021).
-    \url{https://doi.org/10.1186/s13663-021-00697-1}
-
-    \bibitem{elser2017products}
-    V.\ Elser, Matrix product constraints by projection methods, \emph{Journal of Global Optimization} 68, no 2, (2017), 329-355.
-
-    \bibitem{PW16}
-    Planiden C , Wang X . Strongly Convex Functions, Moreau Envelopes, and the Generic Nature of Convex Functions with Strong Minimizers[J]. \emph{SIAM Journal on Optimization}, 2015, 26(2):1341-1364.
-
-    \bibitem{kreyszig} E.\ Kreyszig, \emph{Introductory Functional Analysis with Applications},
-    John Wiley \& Sons, Inc., New York, 1989.
-
-    \bibitem{Luenberger}
-    D.G.\ Luenberger,
-    \emph{Optimization by Vector Space Methods},
-    Wiley, 1969.
-
-    \bibitem{Luke2020}
-    D.~R. Luke. and A.L. Martins, Convergence Analysis of the Relaxed Douglas--Rachford Algorithm. \newblock {\em SIAM Journal on Optimization}, 30(1), (2020), pp.542-584.
-
-    \bibitem{Rock98}
-    R.\ T.\ Rockafellar and R.\ J-B Wets,
-    \emph{Variational Analysis},
-    Springer-Verlag, New York, 1998.
-
-\end{thebibliography}
+\bibliographystyle{plain}
 

### 2024-05-28 Notebook LaTEX/Momentum Accelerations/main.tex
>w< mbp

@@
 
-\title{{\fontfamily{ptm}\selectfont Lorum ipsum}}
+\title{{\fontfamily{ptm}\selectfont Nesterov Type Momentum Methods}}
 
@@
 
-\date{March 2, 2020}
+\date{\today}
 
@@
     These are ntoes for Nesterov Type Acceleration Methods, in the convex case. 
+    They may get made into papers, proposal, and thesis in the future. 
 \end{abstract}
@@
     In this section we list fundational results that are important for proofs in coming sections. 
+    For this section, let the ambient space be $\RR^n$ and $\Vert \cdot\Vert$ be the Euclidean 2 norm until it's specified in the context. 
     \subsection{Lipschitz Smoothness}
+        \begin{definition}[Lipschitz Smooth]
+            Let $f$ be differentiable. 
+            It has Lipschitz smoothness with constant $L$ if for all $x, y$
+            $$
+                \Vert \nabla f(x) - \nabla f(y)\Vert 
+                \le 
+                L \Vert x - y\Vert. 
+            $$    
+        \end{definition}
+
+        \begin{theorem}[Lipschitz Smoothness Equivalence]
+            With $f$ convex, the following conditions are equivalent conditions for all $x, y$: 
+            \begin{enumerate}
+                \item $|f(y) - f(x) - \langle \nabla f(x), y - x\rangle| \le \frac{L}{2}\Vert y - x\Vert^2$. 
+                \item $|\langle \nabla f(y) - \nabla f(x), y - x\rangle| \le L\Vert y - x\Vert^2$. 
+                \item $x^+\in \arg\min_x{f(x)} \implies \frac{1}{2L}\Vert \nabla f(x)\Vert^2 \le f(x) - f(x^+) \le (L/2) \Vert x - x^+\Vert^2$
+                \item $ 1/(2L)\Vert x - y\Vert^2 \le  f(y) - f(x) - \langle \nabla f(x), y -x\rangle \le (L/2)\Vert x - y\Vert^2$
+            \end{enumerate}    
+        \end{theorem}
+        \begin{remark}
+            In the convex of operator theorem, Lipschitz smoothness of the gradient of a convex function is an example of a Firmly Nonexpansive operator. 
+        \end{remark}
+
+        \begin{definition}[Strong Convexity]
+            With $f: \RR^n \mapsto \overline \RR$, it is strongly convex with constant $\alpha$ if and only if $f - (\alpha/2)\Vert \cdot\Vert^2$ is a convex function. 
+        \end{definition}
+
+        \begin{theorem}[Strongly Convex Equivalent Results]
+            With $f:\RR^n \mapsto \overline \RR$ $\alpha$-strongly convex, the following conditions are equivalent conditions for all $x, y$: 
+            \begin{enumerate}
+                \item $f(y) - f(x) - \langle \partial f(x),y - x \rangle\ge \frac{\alpha}{2}\Vert y - x\Vert^2$
+                \item $\langle \partial f(y) - \partial f(x), y - x\rangle \ge \alpha\Vert y - x\Vert^2$. 
+                \item $f(\lambda x + (1 - \lambda)y) \le \lambda f(x) + (1 - \lambda)f(y) -\alpha\frac{\lambda(1 - \lambda)}{2}\Vert y - x\Vert^2, \forall \lambda \in [0, 1]$. 
+            \end{enumerate}
+        \end{theorem}
+
+        \begin{theorem}[Strong Convexity Implications]
+            With $f:\RR^n \mapsto \overline \RR$ $\alpha$-strongly convex, the following conditions are implied:
+
+        \end{theorem}
+        \begin{remark}
+            In the context of operator theory, the subgradient of a strongly convex function is an example of a Strongly Monotone Operator. 
+        \end{remark}
     \subsection{Proximal Descent Inequality}
+        \begin{theorem}[Proximal Descent Inequality]\label{thm:prox_descent_ineq}
+            With $f: \RR^n \mapsto \overline \RR^n$ convex, fix any $x \in \RR^n$, let $p = \hprox_\alpha f(x)$, then for all $y$ we have inequality 
+            $$
+                \left(f(p) + \frac{1}{2\alpha}\Vert x - p\Vert^2\right)
+                - 
+                \left(
+                    f(y) + \frac{1}{2\alpha}\Vert x - y\Vert^2 
+                \right)
+                \le 
+                - \frac{1}{2\alpha}\Vert y - p\Vert^2. 
+            $$
+            Recall $\hprox_\alpha f(x) = \argmin_{u}\left\lbrace f(u) + \frac{1}{2}\Vert u - x\Vert^2 \right\rbrace$. 
+        \end{theorem}
+        We make use of this theorem in the proof of convergence of proximal point method.     
+        \begin{remark}
+            This descent inequality can be generalized to bregman proximal mapping as well. 
+        \end{remark}
 
 \section{The Proximal Point Method in the Convex Case}
+    In this section we quickly go over the analysis of Proximal point method (PPM) in the convex case and see how the theories can be generalized into the cases where PPM is approximated. 
+    \par
+    With $f: \RR^n \mapsto \overline \RR$ lsc proper and convex, 
+    given any $x_0$ the PPM generates sequence $(x_n)_{n\in \NN}$ by $x_{k + 1} = \hprox_{\eta_{k + 1}}f(x_k)$ for all $k \in \NN$ where the sequence $(\eta_{k})_{k \in \NN}$ is a nonegative sequence of real numbers.
+    \subsection{The Lyapunov function of PPM}
+        \begin{theorem}
+            Define the quantity for all $u \in \RR^n$
+            $$
+                \Phi_t = 
+                \left(
+                    \sum_{i = 1}^{t} \eta_i
+                \right)(f(x_t) - f(u)) + \frac{1}{2} \Vert u - x_t\Vert^2 \quad \forall t \ge 1, 
+            $$
+            then it is a Lyapunov function for the PPM algorithm. 
+            Meaning for all $(x_k)_{k \in \NN}$ generated by PPM, it satisfies that $\Phi_{t + 1} - \Phi_t \le 0$. 
+            Additionally, by the definition we have 
+            \begin{align*}
+                \Phi_{t + 1} - \Phi_{t} = 
+                \eta_{t + 1}(f(x_{t + 1}) - f(u)) 
+                + 
+                \frac{1}{2}\Vert u - x_{t + 1}\Vert^2 
+                -
+                \frac{1}{2}\Vert u - x_t\Vert^2 
+                \le 
+                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2, 
+            \end{align*}
+            as a consequence of choosing $u = x_{t + 1}$
+            \begin{align*}
+                f(x_{t + 1}) - f(x_t) \le \frac{1}{\eta_{t + 1}}\Vert x_{t + 1} - x_t\Vert^2. 
+            \end{align*}
+        \end{theorem}
+        \begin{proof}
+            With $p, \alpha, y$ in theorem \ref*{thm:prox_descent_ineq} as $x_{t + 1}, \eta_{t + 1}, u$ we have for all $u$
+            \begin{align*}
+                \eta_{t + 1} (f(x_{t + 1}) - f(u)) + 
+                \frac{1}{2}(
+                    \Vert x_t - x_{t + 1} \Vert^2 
+                    - 
+                    \Vert x_t - u\Vert^2
+                ) &\le 
+                - \frac{1}{2}\Vert u - x_{t + 1}\Vert^2
+                \\
+                \eta_{t + 1}(f(x_{t + 1}) - f(u)) 
+                + 
+                \frac{1}{2}\Vert u - x_{t + 1}\Vert^2 
+                -
+                \frac{1}{2}\Vert u - x_t\Vert^2 
+                & \le 
+                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2, 
+            \end{align*}
+            next it's not hard to check that $\Phi_{t + 1} - \Phi_t$ equals to the above quantity. 
+        \end{proof}
+        \begin{remark}
+            This theorem act as a descent inequality and it can be generalized under a diverse context, such as all algorithms that are approximation to the PPM method. 
+        \end{remark}
 

### 2024-05-28 Notebook LaTEX/Momentum Accelerations/main.tex
>w< mbp

@@
             Define the quantity for all $u \in \RR^n$
-            $$
-                \Phi_t = 
+            \begin{align*}
+                \Phi_t &= 
                 \left(
                     \sum_{i = 1}^{t} \eta_i
-                \right)(f(x_t) - f(u)) + \frac{1}{2} \Vert u - x_t\Vert^2 \quad \forall t \ge 1, 
-            $$
+                \right)(f(x_t) - f(u)) + \frac{1}{2} \Vert u - x_t\Vert^2 \; \forall t \ge 1, 
+                \\
+                \Phi_0 &= (1/2)\Vert x_0 - u\Vert^2, 
+            \end{align*}
             then it is a Lyapunov function for the PPM algorithm. 
@@
 
+        \begin{theorem}[Convergence Rate of PPM]
+            The convergence rate of PPM applied to $f$, closed, convex proper, we have convergence rate of the function value: 
+            $$
+            f(x_T) - f(x_*) \le O\left(\left(\sum_{i=1}^{T}\eta_t\right)^{-1}\right). 
+            $$
+            Where $x_*$ is the minimizer of $f$. 
+        \end{theorem}
+        \begin{proof}
+            With $\Delta_t = f(x_t) - f(x_*), \Upsilon_t = \sum_{i = 1}^{t}\eta_i$ so $\Phi_t = \Upsilon_t\Delta_t + \frac{1}{2}\Vert x_t - x_*\Vert^2$ by consider $u = x_*$, invoking previous theorem and do
+            \begin{align*}
+                \Upsilon_T\Delta_T \le \Phi_T 
+                &\le 
+                \Phi_0 = \frac{1}{2}\Vert x_0 - x_*\Vert^2 
+                \\
+                \implies \Delta_T 
+                &\le 
+                \frac{1}{2\Upsilon_T} \Vert x_0 - x_*\Vert^2. 
+            \end{align*}
+            Hence, the convergence rate of PPM for all convex function is the above. 
+        \end{proof}
+        \begin{remark}
+            The analysis of the above is taken from (REFERENCE NEEDED). 
+        \end{remark}
 \section{Application of the Proximal Point Method}
+    The PPM method and the Lyaounov function derived above serves as tamplate for other algorithms. 
+    In optimizations, people uses lower and upper approximation of the objective function to approximate the PPM. 
+    Such an approach involves a diverse range of algorithms, including second order algorithms such as Newton's method. 
+    To demonstrate, assume that $f$ is a lsc convex function such that it can be approximated by an lower bounding function $l_f(x|\bar x)$ at $\bar x$ such that it satisfies for all $x$: 
+    \begin{align}
+        l_f(x| \bar x) 
+        \le f(x) \le l_f(x|\bar x) + \frac{L}{2}\Vert x - \bar x\Vert^2. 
+    \end{align}
+    The above characterization is generic enough to include the case where $l_f(x|\bar x)$ under approximates function that is non-smooth. 
+    To make use of the theorems discussed previously, we assume that $l_f(x|\bar x)$ is convex for all $x$, at all $\bar x$. 
+    \par 
+    The approximated proximal point method is applying PPM to the function $l_f(x|x_t)$ for each iteration, i.e: $x_{t +1} = \hprox_{\eta_{t + 1}}[u\mapsto l_f(u | x_t)](x_t)$.
 

### 2024-05-29 Notebook LaTEX/Momentum Accelerations/main.tex
>w< mbp, added new

@@
         \end{remark}
+        However, the convergence rate of the algorithm can be faster for the same choice of the sequence $(\eta_t)_{t \in \NN}$. 
+        \begin{theorem}[Convergence Rate of PPM (Strongly Convex)]
+
+        \end{theorem}
 \section{Application of the Proximal Point Method}
@@
 
+    \begin{theorem}[Convergence of Approximated PPM]\label{thm:lower_approx_ppm_convergence}
+        With $f$ be a function that has minimizer: $x_*$; $l_f(x; x_t)$ be a convex, lsc, proper lower-bounding function then the lower-bounding $\phi$ function satisfies inequality: 
+        $$
+        \phi_t(x) \le \eta_{t + 1}f(x) \le \phi_t(x) + \frac{L\eta_{n + 1}}{2}\Vert x - x_t\Vert^2 \quad \forall x \in \RR^n, 
+        $$ 
+        Assume an algorithm the makes: 
+        $$
+        \begin{aligned}
+            x_{t +1} = \argmin_{x} \left\lbrace
+                l_f(x; x_t) + \frac{1}{2\eta_{t + 1}}\Vert x - x_t\Vert^2
+            \right\rbrace, 
+        \end{aligned}
+        $$
+        Then the iterates satisfies: 
+        $$
+        \begin{aligned}
+            \eta_{t + 1}(f(x_{t + 1}) - f(x_*)) + \frac{1}{2}\Vert x_* - x_{t + 1}\Vert^2
+            - \frac{1}{2}\Vert x_* - x_t\Vert 
+            & \le 
+            \left(
+                \frac{L \eta_{n + 1}}{2} - \frac{1}{2}
+            \right)\Vert x_{t + 1} - x_t\Vert^2.
+        \end{aligned}
+        $$
+    \end{theorem}
+    \begin{proof}
+
+    \end{proof}
+
 \bibliographystyle{plain}

### 2024-06-02 Notebook LaTEX/Momentum Accelerations/main.tex
>w< fixes

--- 2024-05-28 Notebook LaTEX/Momentum Accelerations/main.tex
@@
 \author{
-    Alto Legato
+    Alto
     \thanks{
@@
         \begin{theorem}[Lipschitz Smoothness Equivalence]
-            With $f$ convex, the following conditions are equivalent conditions for all $x, y$: 
+            With $f$ convex and $L$-Lipschitz smooth, the following conditions are equivalent conditions for all $x, y$: 
             \begin{enumerate}
-                \item $|f(y) - f(x) - \langle \nabla f(x), y - x\rangle| \le \frac{L}{2}\Vert y - x\Vert^2$. 
-                \item $|\langle \nabla f(y) - \nabla f(x), y - x\rangle| \le L\Vert y - x\Vert^2$. 
-                \item $x^+\in \arg\min_x{f(x)} \implies \frac{1}{2L}\Vert \nabla f(x)\Vert^2 \le f(x) - f(x^+) \le (L/2) \Vert x - x^+\Vert^2$
-                \item $ 1/(2L)\Vert x - y\Vert^2 \le  f(y) - f(x) - \langle \nabla f(x), y -x\rangle \le (L/2)\Vert x - y\Vert^2$
+                \item $L^{-1}\Vert \nabla f(y) - \nabla f(x)\Vert^2 \le \langle \nabla f(y) - \nabla f(x), y - x\rangle \le L\Vert y - x\Vert^2$. 
+                \item $x^+\in \argmin_x f(x) \implies \frac{1}{2L}\Vert \nabla f(x)\Vert^2 \le f(x) - f(x^+) \le (L/2) \Vert x - x^+\Vert^2$, co-coersiveness. 
+                \item $ 1/(2L)\Vert \nabla f(x) - \nabla f(y)\Vert^2 \le  f(y) - f(x) - \langle \nabla f(x), y -x\rangle \le (L/2)\Vert x - y\Vert^2$
             \end{enumerate}    
@@
         \begin{remark}
-            In the convex of operator theorem, Lipschitz smoothness of the gradient of a convex function is an example of a Firmly Nonexpansive operator. 
+            Lipschitz smoothness of the gradient of a convex function is an example of a firmly nonexpansive operator.  
         \end{remark}
@@
             With $f:\RR^n \mapsto \overline \RR$ $\alpha$-strongly convex, the following conditions are implied: 
-
+            \begin{enumerate}
+                \item $\frac{1}{2}\operatorname{dist}(\mathbf 0; \partial f(x))^2 \ge \alpha (f(x) - f^+)$ where $f^+$ is a minimum of the function, and this is called the Polyak-Lojasiewicz (PL) inequality.
+                \item $\forall x, y\in \mathbb E, u\in \partial f(x), v\in \partial f(y): \Vert u - v\Vert\ge \alpha\Vert x - y\Vert$. 
+                \item $f(y) \le f(x) + \langle \partial f(x), y - x\rangle + \frac{1}{2\alpha}\Vert u - v\Vert^2, \forall u\in  \partial f(x), v\in \partial f(y)$. 
+                \item $\langle \partial f(x)-\partial f(y), x - y\rangle \le \frac{1}{\alpha}\Vert u - v\Vert^2, \forall u\in \partial f(x), v\in \partial f(y)$. 
+                \item if $x^+\in \arg\min_{x}f(x)$ then $f(x) - f(x^+) \ge \frac{\alpha}{2}\Vert x - x^+\Vert^2$ and $x^+$ is a unique minimizer. 
+            \end{enumerate}
         \end{theorem}
@@
         \end{remark}
+
     \subsection{Proximal Descent Inequality}
-        \begin{theorem}[Proximal Descent Inequality]\label{thm:prox_descent_ineq}
-            With $f: \RR^n \mapsto \overline \RR^n$ convex, fix any $x \in \RR^n$, let $p = \hprox_\alpha f(x)$, then for all $y$ we have inequality 
+        \begin{theorem}[Proximal Descent Inequality]\label{thm:ppm_descent_ineq}
+            With $f: \RR^n \mapsto \overline \RR^n$ $\beta$-convex where $\beta \ge 0$, fix any $x \in \RR^n$, let $p = \hprox_f(x)$, then for all $y$ we have inequality 
             $$
-                \left(f(p) + \frac{1}{2\alpha}\Vert x - p\Vert^2\right)
+                \left(f(p) + \frac{1}{2}\Vert x - p\Vert^2\right)
                 - 
                 \left(
-                    f(y) + \frac{1}{2\alpha}\Vert x - y\Vert^2 
+                    f(y) + \frac{1}{2}\Vert x - y\Vert^2 
                 \right)
                 \le 
-                - \frac{1}{2\alpha}\Vert y - p\Vert^2. 
+                - \frac{(1 + \beta)}{2}\Vert y - p\Vert^2. 
             $$
@@
 \section{The Proximal Point Method in the Convex Case}
-    In this section we quickly go over the analysis of Proximal point method (PPM) in the convex case and see how the theories can be generalized into the cases where PPM is approximated. 
+    In this section we go over the analysis of Proximal point method (PPM) in the convex case and see how the theories can be generalized into the cases where PPM is approximated. 
     \par
@@
     given any $x_0$ the PPM generates sequence $(x_n)_{n\in \NN}$ by $x_{k + 1} = \hprox_{\eta_{k + 1}}f(x_k)$ for all $k \in \NN$ where the sequence $(\eta_{k})_{k \in \NN}$ is a nonegative sequence of real numbers.
-    \subsection{The Lyapunov function of PPM}
+
+    \subsection{The Lyapunov function of Convex PPM}
         \begin{theorem}
-            Define the quantity for all $u \in \RR^n$
-            $$
-                \Phi_t = 
+            With $f$ being $\beta\ge 0$ strongly convex and $x_{t + 1} = \hprox_{\eta_{t + 1}f}$ generated by PPM. 
+            Define the Lyapunov function $\Phi_t$ for all $u \in \RR^n$: 
+            \begin{align*}
+                \Phi_t &:= 
                 \left(
@@
                 \right)(f(x_t) - f(u)) + \frac{1}{2} \Vert u - x_t\Vert^2 \quad \forall t \ge 1, 
-            $$
+                \\
+                \Phi_0 &:= (1/2)\Vert x_0 - u\Vert^2, 
+            \end{align*}
             then it is a Lyapunov function for the PPM algorithm. 
@@
             Additionally, by the definition we have 
+            {\small
                 \begin{align*}
-                \Phi_{t + 1} - \Phi_{t} = 
+                    \Phi_{t + 1} - \Phi_{t} 
+                    &= 
+                    \left(\sum_{i = 1}^{t}\eta_{i}\right)
+                    (f(x_{t + 1}) - f(x_t)) 
+                    + \frac{1}{2}\Vert x_{t + 1} - u\Vert^2 
+                    - \frac{1}{2}\Vert x_{t} - u\Vert^2
+                    +
                     \eta_{t + 1}(f(x_{t + 1}) - f(u))
+                    \\
+                    & \le 
+                    -\left(\sum_{i = 1}^{t}\eta_{i}\right)
+                    (1 + \beta\eta_{t + 1}/2)\Vert x_{t + 1} - x_t\Vert^2
                     + 
-                \frac{1}{2}\Vert u - x_{t + 1}\Vert^2 
-                -
-                \frac{1}{2}\Vert u - x_t\Vert^2 
-                \le 
-                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2, 
+                    \left(
+                        - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
+                        -\frac{\beta\eta_{t + 1}}{2}\Vert u - x_{t + 1}\Vert^2
+                    \right)
+                    \\
+                    & \le 0,
                 \end{align*}
-            as a consequence of choosing $u = x_{t + 1}$
+            }
+            and additionarlly, recovering the descent lemma: 
             \begin{align*}
-                f(x_{t + 1}) - f(x_t) \le \frac{1}{\eta_{t + 1}}\Vert x_{t + 1} - x_t\Vert^2. 
+                f(x_{t + 1}) - f(x_t) 
+                &\le
+                -\frac{1}{\eta_{t+1}} \Vert x_{t + 1} - x_t\Vert^2 
+                - \frac{\beta}{2}\Vert x_t - x_{t + 1}\Vert^2. 
             \end{align*}
@@
         \begin{proof}
-            With $p, \alpha, y$ in theorem \ref*{thm:prox_descent_ineq} as $x_{t + 1}, \eta_{t + 1}, u$ we have for all $u$
+            Let $\phi_{t + 1}: \RR^n \mapsto \overline \RR = \eta_{t + 1} f$ be convex,  consider proximal point method $x_{t + 1} = \hprox_{\phi}(x_t)$, apply \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}}, we have $\forall u \in \RR^n$
             \begin{align*}
-                \eta_{t + 1} (f(x_{t + 1}) - f(u)) + 
-                \frac{1}{2}(
-                    \Vert x_t - x_{t + 1} \Vert^2 
+                & \phi_{t + 1}(x_{t + 1}) 
+                + 
+                \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
+                - \phi_{t + 1}(u) - \frac{1}{2}\Vert u - x_t\Vert^2
+                \le 
                 - 
+                \frac{1}{2}(1 + \beta\eta_{t + 1})\Vert 
+                    u - x_{t + 1}
+                \Vert^2
+                \\
+                & \text{let } u = x_*
+                \\
+                &\quad 
+                \begin{aligned}
+                    \implies &
+                    \eta_{t + 1}(f(x_{t + 1}) - f(x_*)) 
+                    + 
+                    \frac{1}{2}\Vert x_* - x_{t + 1}\Vert^2 
+                    +  
+                    \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
+                    -
+                    \frac{1}{2}\Vert x_* - x_t\Vert^2 
+                    \\
+                    & \quad \le 
+                    -\frac{\beta\eta_{t + 1}}{2}\Vert x_* - x_{t + 1}\Vert^2
+                    \\
+                    \iff & 
+                    \eta_{t + 1}(f(x_{t + 1}) - f(x_*)) 
+                    + 
+                    \frac{1}{2}\Vert x_* - x_{t + 1}\Vert^2 
+                    -
+                    \frac{1}{2}\Vert x_* - x_t\Vert^2 
+                    \\
+                    & \quad \le 
+                    - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
+                    -\frac{\beta\eta_{t + 1}}{2}\Vert x_* - x_{t + 1}\Vert^2
+                    \le 0. 
+                \end{aligned}
+                \\
+                & \text{let } u = x_{t}
+                \\
+                &\quad  
+                \begin{aligned}
+                    \implies& 
+                    f(x_{t + 1}) - f(x_t)
+                    \le 
+                    -\frac{1}{\eta_{t+1}} \Vert x_{t + 1} - x_t\Vert^2 
+                    - \frac{\beta}{2}\Vert x_t - x_{t + 1}\Vert^2
+                    \le 0. 
+                \end{aligned}
+            \end{align*}
+            Let's define the following quantities for all $u, \beta\ge 0$: 
+            \begin{align*}
+                \Upsilon_{1, t + 1}(u) &= 
+                \eta_{t + 1}(f(x_{t + 1}) - f(u)) + \frac{1}{2}(
+                    \Vert x_{t + 1} - u\Vert^2 - 
                     \Vert x_t - u\Vert^2
-                ) &\le 
-                - \frac{1}{2}\Vert u - x_{t + 1}\Vert^2
+                )
                 \\
+                & \le 
+                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
+                -\frac{\beta\eta_{t + 1}}{2}\Vert u - x_{t + 1}\Vert^2, 
+                \\
+                \Upsilon_{2, t + 1}
+                &= 
+                \eta_{t + 1}(f(x_{t + 1}) - f(x_t))
+                \\
+                &\le 
+                - \Vert x_{t + 1} - x_t\Vert^2 - 
+                \frac{\beta\eta_{t + 1}}{2}
+                \Vert x_{t + 1} - x_t\Vert^2 
+                \\
+                &= 
+                -(1 + \beta\eta_{t + 1}/2)\Vert x_{t + 1} - x_t\Vert^2 \le 0. 
+            \end{align*}
+            With $\Phi_t$ as defined in the theorem, observe the following demonstration for all $u$, $\beta \ge 0$: 
+            {\small
+            \begin{align*}
+                \Phi_{t + 1} - \Phi_{t}
+                &= 
+                \left(
+                    \sum_{i = 1}^{t + 1}\eta_i
+                \right)(f(x_{t + 1}) - f(u)) + 
+                \frac{1}{2}\Vert x_{t + 1} - u\Vert^2 
+                - 
+                \left(
+                    \sum_{i = 1}^{t}\eta_i
+                \right)(f(x_{t}) - f(u))
+                - 
+                \frac{1}{2}\Vert x_{t} - u\Vert^2
+                \\
+                &= 
+                \left(\sum_{i = 1}^{t}\eta_{i}\right)
+                (f(x_{t + 1}) - f(x_t)) 
+                + \frac{1}{2}\Vert x_{t + 1} - u\Vert^2 
+                - \frac{1}{2}\Vert x_{t} - u\Vert^2
+                +
                 \eta_{t + 1}(f(x_{t + 1}) - f(u))
+                \\
+                &= 
+                \left(\sum_{i = 1}^{t}\eta_{i}\right)\Upsilon_{2, t + 1}
+                + \Upsilon_{1, t + 1}(u)
+                \\
+                &\le 
+                -\left(\sum_{i = 1}^{t}\eta_{i}\right)
+                (1 + \beta\eta_{t + 1}/2)\Vert x_{t + 1} - x_t\Vert^2
                 + 
-                \frac{1}{2}\Vert u - x_{t + 1}\Vert^2 
-                -
-                \frac{1}{2}\Vert u - x_t\Vert^2 
-                & \le 
-                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2, 
+                \left(
+                    - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
+                    -\frac{\beta\eta_{t + 1}}{2}\Vert u - x_{t + 1}\Vert^2
+                \right)
+                \le 0. 
             \end{align*}
-            next it's not hard to check that $\Phi_{t + 1} - \Phi_t$ equals to the above quantity. 
+            }
+            Therefore, $\Phi_t$ is a legitimate Lyapunov funtion for all $u, \beta \ge 0$. 
         \end{proof}
         \begin{remark}
-            This theorem act as a descent inequality and it can be generalized under a diverse context, such as all algorithms that are approximation to the PPM method. 
+            The above Lyapunov is not unique and it's not optimal for $\beta > 0$, striclty strongly convex functions.
+
         \end{remark}
 
-\section{Application of the Proximal Point Method}
+        \begin{theorem}[Convergence Rate of PPM]\label{thm:ppm_convergence_rate}
+            The convergence rate of PPM applied to $f$, closed, convex proper, we have convergence rate of the function value: 
+            $$
+            f(x_T) - f(x_*) \le O\left(\left(\sum_{i=1}^{T}\eta_t\right)^{-1}\right). 
+            $$
+            Where $x_*$ is the minimizer of $f$. 
+        \end{theorem}
+        \begin{proof}
+            With $\Delta_t = f(x_t) - f(x_*), \Upsilon_t = \sum_{i = 1}^{t}\eta_i$ so $\Phi_t = \Upsilon_t\Delta_t + \frac{1}{2}\Vert x_t - x_*\Vert^2$ by consideration $u = x_*$, invoking previous theorem and do
+            \begin{align*}
+                \Upsilon_T\Delta_T \le \Phi_T 
+                &\le 
+                \Phi_0 = \frac{1}{2}\Vert x_0 - x_*\Vert^2 
+                \\
+                \implies \Delta_T 
+                &\le 
+                \frac{1}{2\Upsilon_T} \Vert x_0 - x_*\Vert^2. 
+            \end{align*}
+        \end{proof}
+        \begin{remark}
+            The analysis of the above is taken from (REFERENCE NEEDED). 
+        \end{remark}
+        With the same choice of the sequence $(\eta_t)_{t \in \NN}$, convergence of PPM method of a strongly convex function is faster.
+
+        \begin{theorem}[Convergence Rate of PPM (Strongly Convex)]
+
+        \end{theorem}
+\section{Simple of the Proximal Point Method}
+    The PPM method and the Lyaounov function derived above serves as the tamplate for other algorithms. 
+    In optimizations, people use a lower, or an upper approximation of the objective function to approximate the PPM. 
+    The approaches are a diverse, including second order algorithms such as Newton's method. 
+    To demonstrate, assume that $f$ is a lsc convex function such that it can be approximated by an lower bounding function $l_f(x|\bar x)$ at $\bar x$ such that it satisfies for all $x$: 
+    \begin{align}
+        l_f(x| \bar x) 
+        \le f(x) \le l_f(x|\bar x) + \frac{L}{2}\Vert x - \bar x\Vert^2. 
+    \end{align}
+    The above characterization is generic enough to include the case where $l_f(x|\bar x)$, the under approximating function is nonsmooth. 
+    We assume that $l_f(x|\bar x)$ is convex for all $x$, at all $\bar x$ so that the previous theorems are applicable. 
+    \par 
+    The approximated proximal point method is applying PPM to the function $l_f(x|x_t)$ for each iteration, i.e: $x_{t +1} = \hprox_{\eta_{t + 1}l_f(\cdot | x_t)}(x_t)$. 
+    \subsection*{Generic Gradient Descent}
+        As a warm up, we consider deriving gradient descent via the PPM approach. 
+        Please pay attention to the remarks, it reveals parts of the proof that could inspirate the idea of non-monotone line search method in a practical settings. 
+        \begin{theorem}[Generic Approximated PPM]\label{thm:lower_approx_ppm_convergence}
+            With $f$ be a function that has minimizer: $x_*$; $l_f(x; x_t)$ be a convex, lsc, proper lower-bounding function, define lower-bounding $\phi_t = \eta_{t + 1}l_f(x; x_t)$. 
+            Assume the following estimates hold: 
+            $$
+            \phi_t(x) \le \eta_{t + 1}f(x) \le \phi_t(x) 
+            + 
+            \frac{L\eta_{t + 1}}{2}\Vert x - x_t\Vert^2 \quad \forall x \in \RR^n, 
+            $$ 
+            Fix any $x_0$, assume that the iterates $x_t$ defined for $t\in \NN$ satisfies
+            \begin{align*}
+                x_{t +1} = \argmin_{x} \left\lbrace
+                    l_f(x; x_t) + \frac{1}{2\eta_{t + 1}}\Vert x - x_t\Vert^2
+                \right\rbrace, 
+            \end{align*}
+            then the iterates satisfies: 
+            \begin{align*}
+                \eta_{t + 1}(f(x_{t + 1}) - f(x_*)) + \frac{1}{2}\Vert x_* - x_{t + 1}\Vert^2
+                - \frac{1}{2}\Vert x_* - x_t\Vert^2
+                & \le 
+                \left(
+                    \frac{L \eta_{n + 1}}{2} - \frac{1}{2}
+                \right)\Vert x_{t + 1} - x_t\Vert^2.
+            \end{align*}
+            And for all $\eta_{t} \in (\epsilon, 2L^{-1} - \epsilon)$ with $\epsilon > 0$, the algorithm has sublinear convergence rates of
+            \begin{align*}
+                \frac{L - \epsilon^{-1}}{TL\epsilon} &\le 
+                \frac{L - \epsilon^{-1}}{TL\epsilon} (f(x_0) - f(x_T))
+            \end{align*}
+        \end{theorem}
+        \begin{proof}
+            By $\phi_t$ convex, apply \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} with $\alpha = 1$ and $f = \phi_t$, $x = x_t$ making $x_{t + 1} = p$, yielding $\forall y$
+            {\footnotesize
+                \begin{align*}
+                    \phi_t(x_{t + 1}) + \frac{1}{2}\Vert x_t - x_{t + 1}\Vert^2 
+                    - 
+                    \phi_t(y) - \frac{1}{2}\Vert x_t - y\Vert^2
+                    &\le 
+                    - \frac{1}{2}\Vert y - x_{t + 1}\Vert^2
+                    \\
+                    \phi_t(x_{t + 1}) - \phi_t(y)
+                    + \frac{1}{2}(
+                        \Vert y - x_{t + 1}\Vert^2 - \Vert x_t - y\Vert^2 
+                    ) &\le 
+                    - \frac{1}{2} \Vert x_t - x_{t + 1}\Vert^2
+                    \\
+                    \left(
+                        \phi_t(x_{t + 1}) + \frac{L\eta_{t + 1}}{2}\Vert x_{t + 1} - x_t\Vert
+                    \right)
+                    - \phi_t(y)
+                    + \frac{1}{2}(
+                        \Vert y - x_{t + 1}\Vert^2 - \Vert x_t - y\Vert^2 
+                    ) &\le 
+                    \left(
+                        \frac{L\eta_{t + 1}}{2}- \frac{1}{2}
+                    \right) \Vert x_t - x_{t + 1}\Vert^2
+                    \\
+                    \implies 
+                    \eta_{t + 1}f(x_{t + 1}) - \eta_{t + 1}f(y) 
+                    + \frac{1}{2}(
+                        \Vert y - x_{t + 1}\Vert^2 - \Vert x_t - y\Vert^2 
+                    ) 
+                    &\le 
+                    \left(
+                        \frac{L\eta_{t + 1}}{2}- \frac{1}{2}
+                    \right) \Vert x_t - x_{t + 1}\Vert^2. 
+                \end{align*}
+            }
+            Setting $y = x_t$ yields
+            \begin{align*}
+                \eta_{t + 1}(f(x_{t + 1}) - f(x_t)) + 
+                \frac{1}{2}
+                    \Vert x_t - x_{t + 1}\Vert^2
+                &\le 
+                \left(
+                        \frac{L\eta_{t + 1}}{2}- \frac{1}{2}
+                \right) \Vert x_t - x_{t + 1}\Vert^2
+                \\
+                \iff 
+                \eta_{t + 1}(f(x_{t + 1}) - f(x_t))
+                &\le 
+                \left(
+                        \frac{L\eta_{t + 1}}{2} - 1
+                \right) 
+                \Vert x_t - x_{t + 1}\Vert^2. 
+            \end{align*}
+            In a similar manner to the derivation of Lyapunov function for PPM, we make for all $y$: 
+            \begin{align*}
+                \Upsilon_{1, t + 1}(y) &= 
+                \eta_{t + 1}(f(x_{t + 1}) - f(y)) + \frac{1}{2}(
+                    \Vert x_{t + 1} - y\Vert^2 - 
+                    \Vert x_t - y\Vert^2
+                )
+                \\
+                & \le 
+                \left(
+                    \frac{L\eta_{t + 1}}{2} - \frac{1}{2}
+                \right) \Vert x_t - x_{t + 1}\Vert^2, 
+                \\
+                \Upsilon_{2, t + 1}
+                &= 
+                \eta_{t + 1}(f(x_{t + 1}) - f(x_t))
+                \\
+                &\le 
+                \left(
+                    \frac{L\eta_{t + 1}}{2} - 1
+                \right) 
+                \Vert x_t - x_{t + 1}\Vert^2. 
+            \end{align*}
+            Now, consider defining $\Phi_t$ for all $y$: 
+            $$
+                \Phi_t = \left(
+                    \sum_{i = 1}^{t} \eta_{i}
+                \right)
+                (f(x_t) - f(y)) + \frac{1}{2}\Vert y - x_t\Vert^2, 
+            $$
+            which is previously proposed Lyapunov function for PPM, we define the basecase $\Phi_0 = \frac{1}{2}\Vert y - x_0\Vert^2$. 
+            Consider the difference $\forall y$: 
+            \begin{align*}
+                \Phi_{t + 1} - \Phi_t
+                &= 
+                \left(\sum_{i = 1}^{t}\eta_{i}\right)\Upsilon_{2, t + 1}
+                + \Upsilon_{1, t + 1}(y)
+                \\
+                &\le 
+                \left(\sum_{i = 1}^{t}\eta_{i}\right) 
+                \left(
+                    \frac{L\eta_{t + 1}}{2} - 1
+                \right) 
+                \Vert x_t - x_{t + 1}\Vert^2 + 
+                \left(
+                    \frac{L\eta_{t + 1}}{2}- \frac{1}{2}
+                \right) \Vert x_t - x_{t + 1}\Vert^2. 
+            \end{align*}
+            Observe that if $\eta_i \le L^{-1}$, then $\Phi_{t + 1} - \Phi_t \le 0$, hence the convergence rate of $\mathcal O\left((\sum_{i = 1}^{t}\eta_i)^{-1}\right)$ of PPM for $\Phi_t$ is applicable.
+            \par
+            Surprisingly, if $\eta_i \in (0, 2L^{-1})$, $\Phi_{t}$ still convergeces. 
+            For simplicity we make $\sigma_t = \sum_{i = 1}^{t}\eta_i$. 
+            It starts with considerations that $(L\eta_{t + 1}/2 - 1) < 0$, so that 
+            \begin{align*}
+                f(x_{t + 1}) - f(x_t) &\le 
+                \left(\frac{L\eta_{t + 1}}{2} - 1\right)\Vert x_{t + 1} - x_t\Vert^2
+                \\
+                f(x_T) - f(x_0)
+                &\le 
+                \underbrace{
+                \left(
+                    \frac{L\sigma_T}{2} - T
+                \right)
+                }_{< 0}
+                \sum_{t = 0}^{T - 1}\Vert x_{t + 1} - x_t\Vert^2
+                \\
+                \implies 
+                \sum_{t = 0}^{T -1}\Vert x_t - x_{t + 1}\Vert^2
+                &\le 
+                \left(
+                    \frac{L}{2}\sigma_T  - T
+                \right)^{-1} 
+                (f(x_T) - f(x_0))
+            \end{align*}
+            Continue on the RHS of $\Phi_{t + 1} - \Phi_t$ so 
+            \begin{align*}
+                \sum_{t = 0}^{T - 1}\Phi_{t + 1} - \Phi_t 
+                &\le 
+                \left(
+                    \frac{L}{2}\sigma_T - \frac{T}{2}
+                \right)\sum_{t = 0}^{T - 1}\Vert x_{t + 1} - x_t\Vert^2
+                \\
+                \Phi_T - \Phi_0 &\le 
+                \left(
+                    \frac{\frac{L}{2}\sigma_T - \frac{T}{2}}{
+                        \frac{L}{2}\sigma_T - T
+                    }
+                \right)
+                (f(x_T) - f(x_0))
+                \\
+                &= 
+                \left(
+                    \frac{L\sigma_T - T}{L\sigma_T - 2T}
+                \right)
+                (f(x_T) - f(x_0)), 
+            \end{align*}
+            implies
+            \begin{align*}
+                \sigma_T (f(x_t) - f(y)) + \frac{1}{2}\Vert y - x_t\Vert^2
+                - \frac{1}{2}\Vert y - x_0 \Vert^2 
+                &\le 
+                \left(
+                    \frac{L\sigma_T - T}{L\sigma_T - 2T}
+                \right)
+                (f(x_T) - f(x_0))
+                \\
+                \iff
+                f(x_t) - f(y) + 
+                \frac{1}{2\sigma_T}(\Vert y - x_t\Vert^2 - \Vert y - x_0\Vert^2)
+                &\le 
+                \left(
+                    \frac{L- T\sigma_T^{-1}}{2T - L\sigma_T}
+                \right)
+                (f(x_0) - f(x_T)), 
+            \end{align*}
+            therefore we obtain the bound: 
+            \begin{align*}
+                f(x_t) - f(y) &\le 
+                \left(
+                    \frac{L- T\sigma_T^{-1}}{2T - L\sigma_T}
+                \right)
+                (f(x_0) - f(x_T))
+                - 
+                \frac{1}{2\sigma_T}(\Vert y - x_t\Vert^2 - \Vert y - x_0\Vert^2)
+            \end{align*}
+            In the case where $\sup_{i\in \NN} \eta_i \le 2L^{-1} - \epsilon$, and $\inf_{i\in \NN}\eta_i \ge \epsilon$ with $\epsilon > 0$. 
+            Then we have 
+            \begin{align*}
+                \frac{L -T\sigma_T^{-1}}{2T - L\sigma_T}
+                &\le 
+                \frac{L - \epsilon^{-1}}{2T - LT(2L^{-1} - \epsilon)}
+                \\
+                &= 
+                \frac{L - \epsilon^{-1}}{2T - T(2 - L\epsilon)}
+                \\
+                &= 
+                \frac{L - \epsilon^{-1}}{TL\epsilon}. 
+            \end{align*}
+            With $y = x_*$, we get the claimed convergence rate. 
+        \end{proof}
+
+        \begin{remark}
+            We speculate based on observing that the inequality 
+            $$
+                \phi_t(x) \le \eta_{t + 1}f(x) \le \phi_t(x) 
+                + 
+                \frac{L\eta_{t + 1}}{2}\Vert x - x_t\Vert^2 \quad \forall x \in \RR^n, 
+            $$
+            was invoked with $x = x_{t + 1}$ for the PPM descent inequality, meaning that having $\forall x \in \RR^n$ can be relaxed into $\forall (x_t)_{t \in \NN}$ generated by the algorithm, $\exists (L_t)_{t \in \NN}$,
+            $$
+                \phi_t(x) \le \eta_{t + 1}f(x) \le \phi_t(x) 
+                + 
+                \frac{L_t\eta_{t + 1}}{2}\Vert x - x_t\Vert^2,
+            $$
+            where the sequence is generated by the algorithm. 
+            This can be achieved by choosing the function $\Phi_{t + 1}$ at each iteration smartly. 
+            \par
+            The convergence rate is loose and when function $f$ exhibits additional favorable properties, such as being strongly convex, the convergence rate can be faster. 
+        \end{remark}
+    \subsection{Examples}
+        \begin{example}[Proximal Gradient]
+            In this section, we illustrate algorithms that satisfies the lower and uppwer bound estimate used in the above proof. 
+            Consider $f = g + h$ with $h$ nonsmooth convex, and $g$ being $L$-Lipschitz smooth convex and differentiable. 
+            Define $D_g(x, y) = g(x) - g(y) - \langle \nabla f(x), y - x\rangle$, which is the Bregman divergence of the function $g$. 
+            Consider for all $x$: 
+            \begin{align*}
+                0 & \le 
+                D_g (x, y) \le  \frac{L}{2} \Vert x - y\Vert^2 
+                \\
+                l_g (x; y) &\le 
+                g(x) 
+                \le l_g(x; y) + \frac{L}{2} \Vert x - y\Vert^2 
+                \\
+                h(x) + l_g(x; y) &\le f(x) = g(x) + h(x)
+                \le 
+                l_g(x; y) + h(x) + \frac{L}{2}\Vert x - y\Vert^2. 
+            \end{align*}
+            Define $\phi_t (x) = \eta_{t + 1}(h(x) + l_g(x; x_t))$, then results from previous theorems apply.    
+        \end{example}
+        \begin{remark}
+            The envelope interpretation restricts the use of the theorem, since it requires that the proixmal operator is applied to the gradient of a function. 
+            Extending the usage of the PPM descent inequality to other context requires operator theories and creativities. 
+        \end{remark}
+
+\section{Accelerated gradient descent}
+    By recent works from (CITATION NEEDED), Nesterov accelerated gradient (CITATION NEEDED) can be interpreted as an approximation to the PPM method. 
+    Additionally, works on accelerating PPM had bey done by Guler (CITATION NEEDED) decades ago. 
+    The recent interpretations of Nesterov acceleration method via PPM focuses on the idea of a similar triangle, and unifying all varieties of Nesterov acceleration. 
+    \subsection{The varieties of Nesterov Accelerated gradient}
+        In this section, we list different varities of Nesterov accelerated method. 
+        Each of the varieties will be presented generically because we are only interested in the forms they take.
+
+    \subsection{Interpreting Nesterov accelerated gradient via PPM. }
 
@@
 
+\appendix
+\section*{Postponed Proofs}
+
 \end{document}

### 2024-06-03 Notebook LaTEX/Momentum Accelerations/main.tex
new stuff

@@
     For this section, let the ambient space be $\RR^n$ and $\Vert \cdot\Vert$ be the Euclidean 2 norm until it's specified in the context. 
-    \subsection{Lipschitz Smoothness}
+    \subsection{Lipschitz smoothness}
         \begin{definition}[Lipschitz Smooth]
@@
 
-    \subsection{Proximal Descent Inequality}
+    \subsection{Proximal descent inequality}
         \begin{theorem}[Proximal Descent Inequality]\label{thm:ppm_descent_ineq}
@@
     In this section we go over the analysis of Proximal point method (PPM) in the convex case and see how the theories can be generalized into the cases where PPM is approximated. 
+    \subsection{Literature reviews}
+
     \par
@@
 
-        \begin{theorem}[Convergence Rate of PPM (Strongly Convex)]
-
-        \end{theorem}
-\section{Simple of the Proximal Point Method}
+\section{Applying the analysis of PPM}
     The PPM method and the Lyaounov function derived above serves as the tamplate for other algorithms. 
@@
     The approximated proximal point method is applying PPM to the function $l_f(x|x_t)$ for each iteration, i.e: $x_{t +1} = \hprox_{\eta_{t + 1}l_f(\cdot | x_t)}(x_t)$. 
-    \subsection*{Generic Gradient Descent}
+    \subsection{Generic gradient descent}
         As a warm up, we consider deriving gradient descent via the PPM approach. 
@@
         \begin{theorem}[Generic Approximated PPM]\label{thm:lower_approx_ppm_convergence}
-            With $f$ be a function that has minimizer: $x_*$; $l_f(x; x_t)$ be a convex, lsc, proper lower-bounding function, define lower-bounding $\phi_t = \eta_{t + 1}l_f(x; x_t)$. 
+            With $f$ convex having minimizer: $x_*$; $l_f(\cdot; x_t)$ convex, lsc and proper, define $\phi_t = \eta_{t + 1}l_f(x; x_t)$. 
             Assume the following estimates hold: 
@@
             + 
-            \frac{L\eta_{t + 1}}{2}\Vert x - x_t\Vert^2 \quad \forall x \in \RR^n, 
+            \frac{L\eta_{t + 1}}{2}\Vert x - x_t\Vert^2 \quad \forall x \in \RR^n. 
             $$ 
-            Fix any $x_0$, assume that the iterates $x_t$ defined for $t\in \NN$ satisfies
+            Fix any $x_0$, let the iterates $x_t$ defined for $t\in \NN$ satisfies
             \begin{align*}
@@
             \end{align*}
-            then the iterates satisfies: 
+            then it has 
             \begin{align*}
@@
             \end{align*}
-            And for all $\eta_{t} \in (\epsilon, 2L^{-1} - \epsilon)$ with $\epsilon > 0$, the algorithm has sublinear convergence rates of
+            Additionally if $\exists \epsilon > 0: \eta_{t} \in (\epsilon, 2L^{-1} - \epsilon)$, for all $t \in \NN$, the algorithm has sublinear convergence rates of
             \begin{align*}
-                \frac{L - \epsilon^{-1}}{TL\epsilon} &\le 
+                f(x_T) - f(x_*)
+                &\le 
                 \frac{L - \epsilon^{-1}}{TL\epsilon} (f(x_0) - f(x_T)) 
+                \\
+                &\le 
+                \frac{L - \epsilon^{-1}}{TL\epsilon} (f(x_0) - f(x_*)) 
             \end{align*}
@@
             Observe that if $\eta_i \le L^{-1}$, then $\Phi_{t + 1} - \Phi_t \le 0$, hence the convergence rate of $\mathcal O\left((\sum_{i = 1}^{t}\eta_i)^{-1}\right)$ of PPM for $\Phi_t$ is applicable.
-            \par
+            \par\noindent
             Surprisingly, if $\eta_i \in (0, 2L^{-1})$, $\Phi_{t}$ still convergeces. 
-            For simplicity we make $\sigma_t = \sum_{i = 1}^{t}\eta_i$. 
+            For simplicity we set $\sigma_t := \sum_{i = 1}^{t}\eta_i$. 
             It starts with considerations that $(L\eta_{t + 1}/2 - 1) < 0$, so that 
@@
             \begin{align*}
-                \sigma_T (f(x_t) - f(y)) + \frac{1}{2}\Vert y - x_t\Vert^2
+                \sigma_T (f(x_T) - f(y)) + \frac{1}{2}\Vert y - x_t\Vert^2
                 - \frac{1}{2}\Vert y - x_0 \Vert^2 
@@
                 \iff
-                f(x_t) - f(y) + 
+                f(x_T) - f(y) + 
                 \frac{1}{2\sigma_T}(\Vert y - x_t\Vert^2 - \Vert y - x_0\Vert^2)
@@
             \begin{align*}
-                f(x_t) - f(y) &\le 
+                f(x_T) - f(y) &\le 
                 \left(
@@
             \end{align*}
-            With $y = x_*$, we get the claimed convergence rate. 
+            With $y = x_*$, we get the claimed convergence rate because $f(x_t)$ is strictly monotone decreasing. 
         \end{proof}
-
         \begin{remark}
-            We speculate based on observing that the inequality 
+            Observe that inequality 
             $$
@@
             $$
-            was invoked with $x = x_{t + 1}$ for the PPM descent inequality, meaning that having $\forall x \in \RR^n$ can be relaxed into $\forall (x_t)_{t \in \NN}$ generated by the algorithm, $\exists (L_t)_{t \in \NN}$,
+            was invoked with $x = x_{t + 1}$ for the PPM descent inequality in the above proof, meaning that if  $\forall (x_t)_{t \in \NN}$ generated by the algorithm, $\exists (L_t)_{t \in \NN}$ such that
             $$
@@
             where the sequence is generated by the algorithm. 
-            This can be achieved by choosing the function $\Phi_{t + 1}$ at each iteration smartly. 
+            This can be achieved by choosing the function $\phi_t{t + 1}$ at each iteration smartly, then it's possible to still have the same convergenace rate. 
+            In a practical setting, when $L_t = L$, and $\phi_{t + 1}(x) = \eta_{t + 1}f$, this is called a line search.
             \par
@@
     The recent interpretations of Nesterov acceleration method via PPM focuses on the idea of a similar triangle, and unifying all varieties of Nesterov acceleration. 
-    \subsection{The varieties of Nesterov Accelerated gradient}
+    \subsection{The varieties of Nesterov accelerated gradient}
         In this section, we list different varities of Nesterov accelerated method. 
@@
 
-    \subsection{Interpreting Nesterov accelerated gradient via PPM. }
+    \subsection{Interpreting Nesterov accelerated gradient via PPM}
 

### 2024-06-04 Notebook LaTEX/Momentum Accelerations/main.tex
>w< a lot of new stuff

@@
     In this section we list fundational results that are important for proofs in coming sections. 
-    For this section, let the ambient space be $\RR^n$ and $\Vert \cdot\Vert$ be the Euclidean 2 norm until it's specified in the context. 
+    For this section, let the ambient space be $\RR^n$ and $\Vert \cdot\Vert$ be the 2-norm until it's specified in the context. 
+    For a generate over views of smoothness and strong convexity in the Euclidean space, see \cite[theorem 2.1.5, theorem 2.1.10]{nesterov_lectures_2018} for full exposition of the topic. 
     \subsection{Lipschitz smoothness}
@@
 
-        \begin{theorem}[Strongly Convex Equivalent Results]
+        \begin{theorem}[Stong convexity equivalences]\label{thm:str_cvx_equiv}
             With $f:\RR^n \mapsto \overline \RR$ $\alpha$-strongly convex, the following conditions are equivalent conditions for all $x, y$: 
@@
 
-        \begin{theorem}[Strong Convexity Implications]
+        \begin{theorem}[Strong convexity implications]\label{thm:str_cvx_implied}
             With $f:\RR^n \mapsto \overline \RR$ $\alpha$-strongly convex, the following conditions are implied: 
@@
     \subsection{Proximal descent inequality}
+        The proximal descent inequality below is a crucial piece of inequality for deriving the behaviors of algorithms. 
         \begin{theorem}[Proximal Descent Inequality]\label{thm:ppm_descent_ineq}
@@
             $$
-            Recall $\hprox_\alpha f(x) = \argmin_{u}\left\lbrace f(u) + \frac{1}{2}\Vert u - x\Vert^2 \right\rbrace$. 
+            Recall: $\hprox_f(x) = \argmin_{u}\left\lbrace f(u) + \frac{1}{2}\Vert u - x\Vert^2 \right\rbrace$. 
         \end{theorem}
+        \begin{remark}
             We make use of this theorem in the proof of convergence of proximal point method. 
+            See the proof (\cite{bauschke_convex_2017}, theorem 12.26). 
+            The additional strong convexity index is a consequence of \hyperref[thm:str_cvx_implied]{theorem \ref*{thm:str_cvx_implied}}, item (v). 
+        \end{remark}
+
+        \begin{theorem}[The Bregman proximal descent inequality]\label{thm:ppm_breg_descent_ineq}
+            Let $\omega$ induce a Bregman Divergence $D_\omega$ in $\RR^n$ and assume that it satisfies Bregman Prox Admissibility conditions for function $\varphi: \RR^n \mapsto \overline \RR$.
+            Then we claim that for all $c \in \text{dom}(\omega), b \in \text{dom}(\partial \omega)$, 
+            If 
+            \begin{align*}
+                a = \argmin_{x}\left\lbrace
+                \varphi(x) + D_\omega(x, b)
+                \right\rbrace, 
+            \end{align*}
+            we have the inequality, 
+            \begin{align*}
+                (\varphi(c) + D_\omega(c, b)) - 
+                (\varphi(a) + D_\omega(a, b)) \ge 
+                D_\omega(c, a). 
+            \end{align*}
+        \end{theorem}
         \begin{remark}
-            This descent inequality can be generalized to bregman proximal mapping as well. 
+            For more information about what function $\omega$ can induce a bregman divergence and the admissibility conditions for Bremgna proximal mapping, consult (CITATION NEEDED for Heinz's NopLips Paper).
         \end{remark}
@@
     \subsection{Literature reviews}
+        Rockafellar \cite{rockafellar_monotone_1976} pioneered the analysis of the method of proximal point method in the convex case. 
+        The analysis is developed in the context of maximal monotone operators in Hilbert spaces. 
+        Applications in convex optimizations are covered. 
+        Using his theorems appropriately requires some opportunities, realizations, and characterizations of assumptions (A), (B) in his paper in the context of the applications.
 
-    \par
-    With $f: \RR^n \mapsto \overline \RR$ lsc proper and convex, 
-    given any $x_0$ the PPM generates sequence $(x_n)_{n\in \NN}$ by $x_{k + 1} = \hprox_{\eta_{k + 1}}f(x_k)$ for all $k \in \NN$ where the sequence $(\eta_{k})_{k \in \NN}$ is a nonegative sequence of real numbers.
+    \subsection{The proximal point method}
+        With $f: \RR^n \mapsto \overline \RR$ lsc proper and convex, given any $x_0$ the PPM generates sequence $(x_n)_{n\in \NN}$ by $x_{k + 1} = \hprox_{\eta_{k + 1}}f(x_k)$ for all $k \in \NN$ where the sequence $(\eta_{k})_{k \in \NN}$ is a nonegative sequence of real numbers.
 
     \subsection{The Lyapunov function of Convex PPM}
+        We present some theorems that illusrate the use of \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}}. 
+        The following analysis, techniques can be found in Guler's work \cite{guler_convergence_1991}. 
         \begin{theorem}
@@
         \begin{remark}
-            The analysis of the above is taken from (REFERENCE NEEDED). 
+            With the same choice of the sequence $(\eta_t)_{t \in \NN}$, convergence of PPM method of a strongly convex function is faster.     
         \end{remark}
-        With the same choice of the sequence $(\eta_t)_{t \in \NN}$, convergence of PPM method of a strongly convex function is faster.
 
@@
         \begin{theorem}[Generic Approximated PPM]\label{thm:lower_approx_ppm_convergence}
-            With $f$ convex having minimizer: $x_*$; $l_f(\cdot; x_t)$ convex, lsc and proper, define $\phi_t = \eta_{t + 1}l_f(x; x_t)$. 
+            With $f$ convex having minimizer: $x_*$; $l_f(\cdot; x_t)$ convex, lsc and proper, define $\phi_t(x) = \eta_{t + 1}l_f(x; x_t)$. 
             Assume the following estimates hold: 
@@
         \begin{proof}
-            By $\phi_t$ convex, apply \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} with $\alpha = 1$ and $f = \phi_t$, $x = x_t$ making $x_{t + 1} = p$, yielding $\forall y$
+            By $\phi_t$ convex, apply \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} with $f = \phi_t$, $x = x_t$, $x_{t + 1} = p$, yielding $\forall y$
             {\footnotesize
@@
             \par\noindent
-            Surprisingly, if $\eta_i \in (0, 2L^{-1})$, $\Phi_{t}$ still convergeces. 
+            Surprisingly, if $\eta_i \in (0, 2L^{-1})$, $\Phi_{t}$ still convergeces under mild conditions. 
             For simplicity we set $\sigma_t := \sum_{i = 1}^{t}\eta_i$. 
@@
             where the sequence is generated by the algorithm. 
-            This can be achieved by choosing the function $\phi_t{t + 1}$ at each iteration smartly, then it's possible to still have the same convergenace rate. 
-            In a practical setting, when $L_t = L$, and $\phi_{t + 1}(x) = \eta_{t + 1}f$, this is called a line search.
+            This can be achieved by choosing the function $\phi_{t + 1}$ at each iteration smartly, then it's possible to still have the same convergenace rate. 
+            In a practical setting, when $L_t = L$, and $\phi_{t}(x) = \eta_{t + 1}f$, this is called a line search.
             \par
@@
     \subsection{Examples}
-        \begin{example}[Proximal Gradient]
+        \begin{example}[Convergence of the proximal gradient method]
             In this section, we illustrate algorithms that satisfies the lower and uppwer bound estimate used in the above proof. 
             Consider $f = g + h$ with $h$ nonsmooth convex, and $g$ being $L$-Lipschitz smooth convex and differentiable. 
-            Define $D_g(x, y) = g(x) - g(y) - \langle \nabla f(x), y - x\rangle$, which is the Bregman divergence of the function $g$. 
+            Define $D_g(x, y) = g(x) - g(y) - \langle \nabla f(x), y - x\rangle$, $l_g(x; y) = g(y) + \langle \nabla g(y), y - x\rangle$, which is the Bregman divergence of the function $g$. 
             Consider for all $x$: 
@@
             \end{align*}
-            Define $\phi_t (x) = \eta_{t + 1}(h(x) + l_g(x; x_t))$, then results from previous theorems apply.    
+            Define $\phi_{t + 1} (x) = \eta_{t + 1}(h(x) + l_g(x; x_t))$, then results from previous theorems apply.    
         \end{example}
@@
 
-\section{Accelerated gradient descent}
-    By recent works from (CITATION NEEDED), Nesterov accelerated gradient (CITATION NEEDED) can be interpreted as an approximation to the PPM method. 
-    Additionally, works on accelerating PPM had bey done by Guler (CITATION NEEDED) decades ago. 
-    The recent interpretations of Nesterov acceleration method via PPM focuses on the idea of a similar triangle, and unifying all varieties of Nesterov acceleration. 
-    \subsection{The varieties of Nesterov accelerated gradient}
+        \begin{example}[The fundamental proximal gradient lemma]
+            The fundamental proximal gradient lemma was used heavily in the literatures to derive convergence results in the convex case. 
+            The "fundamental proximal gradient lemma" originate from Beck's writings\cite[theorem 10.16]{beck_first-order_nodate}. 
+            We demonstrate in this example that it's a consequence of \hyperref[thm:ppm_breg_descent_ineq]{theorem \ref*{thm:ppm_breg_descent_ineq}}. 
+            \par
+            With $f = g + h$, $h$ convex, lsc, $g$ be $L$-Lipschitz smooth, then for all $y\in \RR^n$, $x\in \RR^n$, $y^+ := \hprox_{L^{-1}h}(y - L^{-1}\nabla (y))$ satisfies: 
+            \begin{align*}
+                f(x) - f(y^+) \ge \frac{L}{2}\Vert x - y^+\Vert^2 - \frac{L}{2}\Vert x - y\Vert^2 + D_g(x, y).
+            \end{align*}
+            A similar analysis as \hyperref[thm:lower_approx_ppm_convergence]{ theorem \ref*{thm:lower_approx_ppm_convergence}} with \hyperref[thm:ppm_breg_descent_ineq]{theorem \ref*{thm:ppm_breg_descent_ineq}} obtains the same inquality.
+            With $\phi(y) = \eta(h(y) + g(x) + \langle \nabla g(x), y - x\rangle)$ as an lower bounding function of $f$. 
+            Let $x^+ = \hprox_\phi(x)$, then for all $u$:
+            \begin{align*}
+                & \phi(u) + \frac{1}{2}\Vert u - x\Vert^2 - \phi(x^+) - \frac{1}{2}\Vert x^+ - x\Vert^2 
+                \ge \frac{1}{2}\Vert x^+ - u\Vert^2, 
+                \\
+                \implies &
+                \eta\underbrace{(h(u) + g(x) + \langle \nabla g(x), u - x\rangle + \frac{L}{2}\Vert u - x\Vert^2)}_{\ge \phi(u)} 
+                - \eta \underbrace{f(x^+)}_{\le \phi(x^+)} - \frac{1}{2}\Vert x - x^+\Vert^2 
+                \\
+                &\quad  
+                + \left(
+                    \frac{1}{2} - \frac{\eta L}{2}
+                \right)\Vert u - x\Vert^2 
+                \ge 
+                \frac{1}{2}\Vert x^+ - u\Vert^2 
+                \\
+                \iff & 
+                f(u) + g(x) - g(u) + 
+                \langle \nabla g(x), u -x\rangle 
+                - f(x^+) + \frac{L}{2}\Vert u - x\Vert^2 - \frac{1}{2\eta}\Vert x - x^+\Vert^2
+                \\
+                & \quad 
+                + 
+                \left(
+                    \frac{1}{2\eta} - \frac{L}{2}
+                \right)\Vert u - x\Vert^2 
+                \ge 
+                \frac{1}{2\eta}\Vert x^+ - u\Vert^2 
+                \\
+                \iff 
+                & f(u) - f(x^+) - D_g(u, x)
+                + \frac{1}{2\eta} \Vert u - x\Vert^2 - \frac{1}{2\eta}\Vert x^+ - x\Vert^2
+                \ge 
+                \frac{1}{2\eta} \Vert x^+ - u\Vert^2. 
+            \end{align*}
+            Remove the negative term $-1/2\eta \Vert x - x^+\Vert^2$ makes LHS larger, which establish the fundamental proximal gradient lemma. 
+        \end{example}
+
+\section{Accelerated gradient descent and PPM}
+    This section is heavily inspired by recent works from Ahn \cite{ahn_understanding_2022}, Nesterov \cite{nesterov_lectures_2018}.
+    Ahn in his works explored the interpretation of Nesterov acceleration via PPM. 
+    They proposed the idea of ``similar triangle" for unifying all varieties of Nesterov accelerated gradient. 
+    The PPM is used as a tool to derive different variations of the Nesterov accelerated gradient algorithms. 
+    Finally, they refurnished \hyperref[thm:lower_approx_ppm_convergence]{Theorem \ref*{thm:lower_approx_ppm_convergence}} for the proof of convergece rate of accelerated gradient.
+    Their analysis results in relatively simple and exhibits powerful extension to several variants of Nesterov accelerated gradient. 
+    \par\noindent
+    Interestingly, Nesterov accelerated gradient is applicable for PPM.
+    It's been done by \cite{guler_new_1992} two decades ago. 
+    He uses the idea of a Nesterov acceleration sequence faithfully. 
+    One recent development of the accelerated PPM is an algorithmic framework named: ``Universial Catalyst accelreation", proposed by \cite{lin_universal_2015}.
+    It is an application of Guler work in the context of veriance-reduction stochatic gradient algorithms for machine learning.
+
+    \subsection{Varieties of Nesterov accelerated gradient}
         In this section, we list different varities of Nesterov accelerated method. 
-        Each of the varieties will be presented generically because we are only interested in the forms they take.
+        We present these varieties generically because the form of these algorithms are of interests.
 
-    \subsection{Interpreting Nesterov accelerated gradient via PPM}
+    \subsection{Nesterov accelerated gradient via PPM}
+    \subsection{Convergence rate of Nesterov accelerated gradient via PPM}
 
-\bibliographystyle{plain}
+\section{Classical analysis of Nesterov accelerated gradient}
+
+\printbibliography
 

### 2024-06-05 Notebook LaTEX/Momentum Accelerations/main.tex
>w< fixes

@@
     \noindent
-    These are ntoes for Nesterov Type Acceleration Methods, in the convex case. 
-    They may get made into papers, proposal, and thesis in the future. 
+    These are notes for Nesterov Type Acceleration Methods in the convex case. 
+    They can be made into papers, proposals, and a thesis in the future. 
 \end{abstract}
@@
 \section{Preliminaries}
-    In this section we list fundational results that are important for proofs in coming sections. 
-    For this section, let the ambient space be $\RR^n$ and $\Vert \cdot\Vert$ be the 2-norm until it's specified in the context. 
-    For a generate over views of smoothness and strong convexity in the Euclidean space, see \cite[theorem 2.1.5, theorem 2.1.10]{nesterov_lectures_2018} for full exposition of the topic. 
+    This section lists foundational results important for proof in the coming sections. 
+    For this section, let the ambient space be $\RR^n$ and $\Vert \cdot\Vert$ be the 2-norm until specified in the context. 
+    For a general overview of smoothness and strong convexity in the Euclidean space, see \cite[theorem 2.1.5, theorem 2.1.10]{nesterov_lectures_2018} for a full exposition of the topic. 
     \subsection{Lipschitz smoothness}
@@
         \begin{remark}
-            In the context of operator theory, the subgradient of a strongly convex function is an example of a Strongly Monotone Operator. 
+            In operator theory, the subgradient of a strongly convex function is an example of a Strongly Monotone Operator. 
         \end{remark}
@@
     \subsection{Proximal descent inequality}
-        The proximal descent inequality below is a crucial piece of inequality for deriving the behaviors of algorithms. 
+        The proximal descent inequality below is a crucial piece of inequality for deriving the behaviours of algorithms. 
         \begin{theorem}[Proximal Descent Inequality]\label{thm:ppm_descent_ineq}
@@
         \begin{remark}
-            We make use of this theorem in the proof of convergence of proximal point method. 
+            We use this theorem to prove the convergence of the proximal point method. 
             See the proof (\cite{bauschke_convex_2017}, theorem 12.26). 
@@
         \begin{theorem}[The Bregman proximal descent inequality]\label{thm:ppm_breg_descent_ineq}
-            Let $\omega$ induce a Bregman Divergence $D_\omega$ in $\RR^n$ and assume that it satisfies Bregman Prox Admissibility conditions for function $\varphi: \RR^n \mapsto \overline \RR$.
+            Let $\omega$ induce a Bregman Divergence $D_\omega$ in $\RR^n$ and assume that it satisfies Bregman Prox Admissibility conditions for the function $\varphi: \RR^n \mapsto \overline \RR$.
             Then we claim that for all $c \in \text{dom}(\omega), b \in \text{dom}(\partial \omega)$, 
@@
         \begin{remark}
-            For more information about what function $\omega$ can induce a bregman divergence and the admissibility conditions for Bremgna proximal mapping, consult (CITATION NEEDED for Heinz's NopLips Paper).
+            For more information about what function $\omega$ can induce a Bregman divergence and the admissibility conditions for Bremgna proximal mapping, consult (CITATION NEEDED for Heinz's NopLips Paper).
         \end{remark}
 
-\section{The Proximal Point Method in the Convex Case}
-    In this section we go over the analysis of Proximal point method (PPM) in the convex case and see how the theories can be generalized into the cases where PPM is approximated. 
+\section{The proximal point method with convexity}
+    This section reviews the convex case's Proximal point method (PPM) analysis and generalizes the theories to approximated PPM. 
     \subsection{Literature reviews}
-        Rockafellar \cite{rockafellar_monotone_1976} pioneered the analysis of the method of proximal point method in the convex case. 
-        The analysis is developed in the context of maximal monotone operators in Hilbert spaces. 
+        Rockafellar \cite{rockafellar_monotone_1976} pioneered the analysis of the proximal point method in the convex case. 
+        He developed the analysis in the context of maximal monotone operators in Hilbert spaces. 
         Applications in convex optimizations are covered. 
@@
 
-    \subsection{The Lyapunov function of Convex PPM}
-        We present some theorems that illusrate the use of \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}}. 
-        The following analysis, techniques can be found in Guler's work \cite{guler_convergence_1991}. 
+    \subsection{The Lyapunov function of convex PPM}
+        We present some theorems that illustrate the use of \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}}. 
+        The readers can find similar analyses and techniques in Guler's work \cite{guler_convergence_1991}. 
         \begin{theorem}
@@
             Meaning for all $(x_k)_{k \in \NN}$ generated by PPM, it satisfies that $\Phi_{t + 1} - \Phi_t \le 0$. 
-            Additionally, by the definition we have 
+            Additionally, by definition, we have 
             {\small
@@
             }
-            and additionarlly, recovering the descent lemma: 
+            And additionally, recovering the descent lemma: 
             \begin{align*}
@@
             }
-            Therefore, $\Phi_t$ is a legitimate Lyapunov funtion for all $u, \beta \ge 0$. 
+            Therefore, $\Phi_t$ is a legitimate Lyapunov function for all $u, \beta \ge 0$. 
         \end{proof}
         \begin{remark}
-            The above Lyapunov is not unique and it's not optimal for $\beta > 0$, striclty strongly convex functions.
+            The above Lyapunov is not unique, and it's not optimal for $\beta > 0$, strictly strongly convex functions.
 
@@
         \begin{theorem}[Convergence Rate of PPM]\label{thm:ppm_convergence_rate}
-            The convergence rate of PPM applied to $f$, closed, convex proper, we have convergence rate of the function value: 
+            The convergence rate of PPM applied to $f$, closed, convex proper, we have the convergence rate of the function value: 
             $$
@@
         \begin{remark}
-            With the same choice of the sequence $(\eta_t)_{t \in \NN}$, convergence of PPM method of a strongly convex function is faster.     
+            With the same choice of the sequence $(\eta_t)_{t \in \NN}$, convergence of the PPM method of a strongly convex function is faster.     
         \end{remark}
@@
 \section{Applying the analysis of PPM}
-    The PPM method and the Lyaounov function derived above serves as the tamplate for other algorithms. 
-    In optimizations, people use a lower, or an upper approximation of the objective function to approximate the PPM. 
-    The approaches are a diverse, including second order algorithms such as Newton's method. 
-    To demonstrate, assume that $f$ is a lsc convex function such that it can be approximated by an lower bounding function $l_f(x|\bar x)$ at $\bar x$ such that it satisfies for all $x$: 
+    The PPM method and the Lyaounov function derived above serve as the template for other algorithms. 
+    As an appetizer, we present an analysis of gradient descent using theorems related to the convergence of PPM
+    \par\noindent
+    In optimizations, people use a lower or an upper approximation of the objective function to approximate the PPM. 
+    The methodology includes a diverse range of approaches.
+    For example, it includes first-order optimization, such as gradient descents, and second-order algorithms, such as Newton's method. 
+    Its scope broadens to primal-dual optimization algorithms with creativities in the Lyapunov functions or theories in monotone operators. 
+    \par\noindent
+    To demonstrate, assume that $f$ is a lsc convex function such that it can be approximated by a lower bounding function $l_f(x|\bar x)$ at $\bar x$ such that it satisfies for all $x$: 
     \begin{align}
@@
     \end{align}
-    The above characterization is generic enough to include the case where $l_f(x|\bar x)$, the under approximating function is nonsmooth. 
-    We assume that $l_f(x|\bar x)$ is convex for all $x$, at all $\bar x$ so that the previous theorems are applicable. 
-    \par 
-    The approximated proximal point method is applying PPM to the function $l_f(x|x_t)$ for each iteration, i.e: $x_{t +1} = \hprox_{\eta_{t + 1}l_f(\cdot | x_t)}(x_t)$. 
+    The above characterization is generic enough to include the case where $l_f(x|\bar x)$, the under-approximating function is nonsmooth. 
+    We assume that $l_f(x|\bar x)$ is convex for all $x$, at all $\bar x$, so the previous theorems apply. 
+    \par\noindent
+    The approximated proximal point method applies PPM to the function $l_f(x|x_t)$ for each iteration, i.e.: $x_{t +1} = \hprox_{\eta_{t + 1}l_f(\cdot | x_t)}(x_t)$. 
     \subsection{Generic gradient descent}
-        As a warm up, we consider deriving gradient descent via the PPM approach. 
-        Please pay attention to the remarks, it reveals parts of the proof that could inspirate the idea of non-monotone line search method in a practical settings. 
+        We will consider deriving gradient descent via the PPM approach as a warm-up. 
+        Please pay attention to the remarks. They reveal parts of the proof that could inspire the idea of a non-monotone line search method in practical settings. 
         \begin{theorem}[Generic Approximated PPM]\label{thm:lower_approx_ppm_convergence}
@@
             \end{align*}
-            In a similar manner to the derivation of Lyapunov function for PPM, we make for all $y$: 
+            In a similar manner to the derivation of the Lyapunov function for PPM, we make for all $y$: 
             \begin{align*}
@@
             $$
-            which is previously proposed Lyapunov function for PPM, we define the basecase $\Phi_0 = \frac{1}{2}\Vert y - x_0\Vert^2$. 
+            it is the proposed Lyapunov function for PPM; we define the base case $\Phi_0 = \frac{1}{2}\Vert y - x_0\Vert^2$. 
             Consider the difference $\forall y$: 
@@
             \par\noindent
-            Surprisingly, if $\eta_i \in (0, 2L^{-1})$, $\Phi_{t}$ still convergeces under mild conditions. 
+            Surprisingly, if $\eta_i \in (0, 2L^{-1})$, $\Phi_{t}$ still converges under mild conditions. 
             For simplicity we set $\sigma_t := \sum_{i = 1}^{t}\eta_i$. 
@@
             \end{align*}
-            therefore we obtain the bound: 
+            therefore, we obtain the bound: 
             \begin{align*}
@@
             $$
-            where the sequence is generated by the algorithm. 
-            This can be achieved by choosing the function $\phi_{t + 1}$ at each iteration smartly, then it's possible to still have the same convergenace rate. 
+            where the algorithm generates the sequence. 
+            By smartly choosing the function $\phi_{t + 1}$ at each iteration, we can increase the stepsize while retaining a similar convergence proof. 
             In a practical setting, when $L_t = L$, and $\phi_{t}(x) = \eta_{t + 1}f$, this is called a line search.
             \par
-            The convergence rate is loose and when function $f$ exhibits additional favorable properties, such as being strongly convex, the convergence rate can be faster. 
+            The convergence rate is loose, and when $f$ exhibits additional favourable properties, such as being strongly convex, the convergence rate can be faster. 
         \end{remark}
@@
         \begin{example}[Convergence of the proximal gradient method]
-            In this section, we illustrate algorithms that satisfies the lower and uppwer bound estimate used in the above proof. 
+            This section illustrates algorithms that satisfy the above proof's lower and upper bound estimates. 
             Consider $f = g + h$ with $h$ nonsmooth convex, and $g$ being $L$-Lipschitz smooth convex and differentiable. 
@@
         \begin{remark}
-            The envelope interpretation restricts the use of the theorem, since it requires that the proixmal operator is applied to the gradient of a function. 
-            Extending the usage of the PPM descent inequality to other context requires operator theories and creativities. 
+            The envelope interpretation restricts the use of the theorem since it requires that the proximal operator be a resolvent of a gradient. 
+            Extending the usage of the PPM descent inequality to other contexts requires operator theories and creativities. 
         \end{remark}
@@
         \begin{example}[The fundamental proximal gradient lemma]
-            The fundamental proximal gradient lemma was used heavily in the literatures to derive convergence results in the convex case. 
-            The "fundamental proximal gradient lemma" originate from Beck's writings\cite[theorem 10.16]{beck_first-order_nodate}. 
+            The fundamental proximal gradient lemma was used heavily in the literature to derive convergence results in the convex case. 
+            The "fundamental proximal gradient lemma" originates from Beck's writings\cite[theorem 10.16]{beck_first-order_nodate}. 
             We demonstrate in this example that it's a consequence of \hyperref[thm:ppm_breg_descent_ineq]{theorem \ref*{thm:ppm_breg_descent_ineq}}. 
@@
             \end{align*}
-            Remove the negative term $-1/2\eta \Vert x - x^+\Vert^2$ makes LHS larger, which establish the fundamental proximal gradient lemma. 
+            Removing the negative term $-1/2\eta \Vert x - x^+\Vert^2$ makes LHS larger, establishing the fundamental proximal gradient lemma. 
         \end{example}
@@
 \section{Accelerated gradient descent and PPM}
-    This section is heavily inspired by recent works from Ahn \cite{ahn_understanding_2022}, Nesterov \cite{nesterov_lectures_2018}.
-    Ahn in his works explored the interpretation of Nesterov acceleration via PPM. 
+    Recent works from Ahn \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
+    In his works, Ahn explored the interpretation of Nesterov acceleration via PPM. 
     They proposed the idea of ``similar triangle" for unifying all varieties of Nesterov accelerated gradient. 
-    The PPM is used as a tool to derive different variations of the Nesterov accelerated gradient algorithms. 
-    Finally, they refurnished \hyperref[thm:lower_approx_ppm_convergence]{Theorem \ref*{thm:lower_approx_ppm_convergence}} for the proof of convergece rate of accelerated gradient.
-    Their analysis results in relatively simple and exhibits powerful extension to several variants of Nesterov accelerated gradient. 
+    They used PPM to derive different variations of the Nesterov accelerated gradient algorithms. 
+    Finally, they refurnished \hyperref[thm:lower_approx_ppm_convergence]{Theorem \ref*{thm:lower_approx_ppm_convergence}} for the proof of convergence rate of the accelerated gradient.
+    Their analysis results are relatively simple and exhibit powerful extensions to several variants of the Nesterov accelerated gradient. 
     \par\noindent
-    Interestingly, Nesterov accelerated gradient is applicable for PPM.
-    It's been done by \cite{guler_new_1992} two decades ago. 
+    Interestingly, the Nesterov accelerated gradient applies to PPM; Guler \cite{guler_new_1992} did it two decades ago. 
     He uses the idea of a Nesterov acceleration sequence faithfully. 
-    One recent development of the accelerated PPM is an algorithmic framework named: ``Universial Catalyst accelreation", proposed by \cite{lin_universal_2015}.
-    It is an application of Guler work in the context of veriance-reduction stochatic gradient algorithms for machine learning.
+    One recent development of the accelerated PPM is an algorithmic framework named: ``Universal Catalyst acceleration", proposed by \cite{lin_universal_2015}.
+    It is an application of Guler's work in the context of variance-reduction stochastic gradient algorithms for machine learning. 
+    \par\noindent
+    In this section, we
+    \begin{enumerate}
+        \item State Nesterov accelerated gradient and their varieties, and point to the literature discussing them. 
+        \item Derive the Nesterov accelerated gradient. 
+        \item Derive the popular step size choices along with the convergence rate. 
+    \end{enumerate}
+    Some content will differ from Ahn's works because we hope to generalize these ideas for our own use.
 
     \subsection{Varieties of Nesterov accelerated gradient}
-        In this section, we list different varities of Nesterov accelerated method. 
-        We present these varieties generically because the form of these algorithms are of interests.
+        In this section, we list different varieties of the Nesterov accelerated method. 
+        We present these varieties generically because these algorithms' forms are of interest.
 

### 2024-06-05 Notebook LaTEX/Momentum Accelerations/main.tex
>w< added new notes from mbp

@@
         \begin{remark}
-            For more information about what function $\omega$ can induce a Bregman divergence and the admissibility conditions for Bremgna proximal mapping, consult (CITATION NEEDED for Heinz's NopLips Paper).
+            For more information about what function $\omega$ can induce a Bregman divergence and the admissibility conditions for Bremgna proximal mapping, consult Heinz et.al \cite{bauschke_descent_2017}.
         \end{remark}
@@
     They proposed the idea of ``similar triangle" for unifying all varieties of Nesterov accelerated gradient. 
-    They used PPM to derive different variations of the Nesterov accelerated gradient algorithms. 
-    Finally, they refurnished \hyperref[thm:lower_approx_ppm_convergence]{Theorem \ref*{thm:lower_approx_ppm_convergence}} for the proof of convergence rate of the accelerated gradient.
-    Their analysis results are relatively simple and exhibit powerful extensions to several variants of the Nesterov accelerated gradient. 
+    They used PPM to derive several variations of the Nesterov accelerated gradient algorithms. 
+    Finally, they refurnished \hyperref[thm:lower_approx_ppm_convergence]{theorem \ref*{thm:lower_approx_ppm_convergence}} for the proof of convergence rate of the accelerated gradient.
+    Their analysis results in relatively simple arguments that exhibits powerful extensions to several variants of the Nesterov accelerated gradient. 
     \par\noindent
@@
     He uses the idea of a Nesterov acceleration sequence faithfully. 
-    One recent development of the accelerated PPM is an algorithmic framework named: ``Universal Catalyst acceleration", proposed by \cite{lin_universal_2015}.
+    One recent development of the accelerated PPM is an algorithmic framework named: ``Universal Catalyst acceleration", proposed by Lin et al \cite{lin_universal_2015}. 
     It is an application of Guler's work in the context of variance-reduction stochastic gradient algorithms for machine learning. 
@@
         We present these varieties generically because these algorithms' forms are of interest.  
+        \begin{definition}[Accelearted Gradient Generic Original Form]
+            Let $f$ be a $L$ Lipschitz smooth and $\mu\ge 0$ strongly convex function. 
+            Choose $x_0$, $\gamma_0 > 0$, set $v_0 = x_0$, for iteration $k\ge 0$, it
+            \begin{enumerate}
+                \item[1.] computes $\alpha_k \in (0, 1)$ by solving $L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \alpha_k \mu$; 
+                \item[2.] sets $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$;
+                \item[3.] chooses $y_k = (\gamma_k + \alpha_k \mu)(\alpha_k \gamma_k v_k + \gamma_{k + 1}x_k)$. Compute $f(y_k)$ and $\nabla f(y_k)$; 
+                \item[4.] finds $x_{k + 1}$ such that $f(x_{k + 1}) \le f(y_k) - (2L)^{-1} \Vert \nabla f(y_k)\Vert^2$; 
+                \item[5.] sets $v_{k + 1} = \gamma_{k+1}^{-1}((1 - \alpha_k)\gamma_kv_k + \alpha_k \mu y_k - \alpha_k \nabla f(y_k))$. 
+            \end{enumerate}
+        \end{definition}
+        \begin{remark}
+            This is in Nesterov's book \cite[(2.2.7)]{nesterov_lectures_2018}. 
+            It is the most generic algorithm in his book about accelerated gradient method. 
+            The genericity of the algorithm is provided by item 4., which is the a special case of the smooth descent lemma. 
+        \end{remark}
+
+        \begin{definition}[Accelerated Gradient Generic Triangular Form]
+
+        \end{definition}
+
+        \begin{definition}[Accelerated Gradient Generic PPM Form]
+
+        \end{definition}
 
@@
 \section{Classical analysis of Nesterov accelerated gradient}
+    In this section, we reproduce some of the analysis for Nesterov accelerated gradient method with excruciating details.
 

### 2024-06-06 Notebook LaTEX/Momentum Accelerations/main.tex
>w< fixes and updates

@@
     This section reviews the convex case's Proximal point method (PPM) analysis and generalizes the theories to approximated PPM. 
-    \subsection{Literature reviews}
+    \subsection{Convex PPM literature reviews}
         Rockafellar \cite{rockafellar_monotone_1976} pioneered the analysis of the proximal point method in the convex case. 
@@
         Using his theorems appropriately requires some opportunities, realizations, and characterizations of assumptions (A), (B) in his paper in the context of the applications. 
+        \par\noindent
+        In this section, we will use the result from Rockafellar that, if a monotone operator $A$ is $\beta$ strongly convex, then the resolvent operator $\mathcal J_A = [I + A]^{-1}$ is a $(1 + \beta)^{-1}$ Lipschitz operator, making $I - \mathcal J_A$ is a $1 - (1 + \beta)^{-1}$ a strongly monotone operator.
 
@@
         The readers can find similar analyses and techniques in Guler's work \cite{guler_convergence_1991}. 
-        \begin{theorem}
-            With $f$ being $\beta\ge 0$ strongly convex and $x_{t + 1} = \hprox_{\eta_{t + 1}f}$ generated by PPM. 
+        \begin{theorem}[PPM Lyapunov Function]\label{ppm_lyapunov}
+            With $f$ being $\beta\ge 0$ convex (it's strongly convex if $\beta > 0$, else it's just convex) and $x_{t + 1} = \hprox_{\eta_{t + 1}f}$ generated by PPM. 
             Define the Lyapunov function $\Phi_t$ for all $u \in \RR^n$: 
@@
             With the same choice of the sequence $(\eta_t)_{t \in \NN}$, convergence of the PPM method of a strongly convex function is faster. 
+            The above proof is the same for $\beta = 0$, or $\beta > 0$, because it didn't use the property that $\eta_{t + 1}f$ is a $\eta_{t + 1}\beta$ strongly convex function. 
+        \end{remark}
+
+        \begin{theorem}[PPM Strongly Convex Lyapunov Function]\label{ppm_lyapunov_scvx}
+            With $f$ being $\beta > 0$ strogly convex, with $x_{t + 1} = \hprox_{\eta_{t + 1}f}(x_t)$, then $\Phi_t = f(x_t) - f(x_*)$ is a Lyapunov function satisfying: 
+            \begin{align*}
+                f(x_{t + 1}) - f(x_*)
+                &\le 
+                -\frac{1}{2\eta_{t + 1}}(1 + \eta_{t + 1}\beta)\Vert x_{t + 1} - x_*\Vert^2
+                \\
+                & \quad 
+                + \frac{1}{2\eta_{t + 1}}\left(
+                    1 - (1 - (1 + \eta_{t + 1}\beta)^{-1})^2
+                \right)
+                \left(
+                    \prod_{i = 1}^{t}
+                        (1 + \eta_i \beta)^{-1}
+                \right)\Vert x_0 - x_*\Vert^2, 
+            \end{align*}
+            hence a convergence rate of $\mathcal O\left(
+                \prod_{i = 1}^{t}(1 + \eta_i \beta)^{-1}
+            \right)$ is prominent. 
+        \end{theorem}
+        \begin{proof}
+            With $\beta$-strongly convex $f$, let $\phi = \eta_{t + 1}f$, let $E_\phi(x)$ be: $\min_u \{\eta_{t + 1} f(u) + (1/2)\Vert u - x\Vert^2\}$ which is the Moreau envelope of $\phi$, let $P_\phi := [I + \eta_{t + 1}\partial f]^{-1}$.
+            For any $x_0$ let $x_{t + 1} = P_\phi(x_t)$, with $x_* \in \argmin_{x} \phi(x)$, we realize these consequences:
+            \begin{enumerate}
+                \item [1.] $I - P_\phi$ is a $1 - (1 + \eta_{t + 1}\beta)^{-1}$ strongly monotone operator;
+                \item [2.] $\nabla E_\phi = I - P_\phi$, meaning that $E_\phi$ is $1 - (1 + \eta_{t + 1}\beta)^{-1}$ strongly convex;
+                \item [3.] $P_\phi$ is a contractive mapping with constant $(1 + \beta\eta_{t + 1})^{-1}$. 
+            \end{enumerate}
+            Using strong convexity of the Moreau envelope it has 
+            \begin{align*}
+                \frac{1}{2}\Vert \nabla E_\phi(x_t)\Vert^2 
+                &\ge 
+                (1 - (1 + \beta\eta_{t + 1})^{-1}) (E_\phi(x_t) - E_\phi(x_*))
+                \\
+                &\ge 
+                (1 - (1 + \beta\eta_{t + 1})^{-1})\left(
+                    \frac{1}{2}(1 - (1 + \beta\eta_{t + 1})^{-1})
+                    \Vert x - x_*\Vert^2
+                \right)
+                \\
+                &= 
+                \frac{1}{2}\left(
+                    1 - (1 + \eta_{t + 1}\beta)^{-1}
+                \right)^2 \Vert x_t - x_*\Vert^2
+            \end{align*}
+            invoke PPM descent inequality on the function $\phi$, it has 
+            {\footnotesize
+            \begin{align*}
+                E_\phi(x_{t + 1}) - \phi(x_*) 
+                &\le 
+                \frac{1}{2}\Vert x_t - x_*\Vert^2 
+                -\frac{1 + \eta_{t + 1}\beta}{2}\Vert x_{t + 1} - x_*\Vert^2
+                \\
+                \iff 
+                \phi(x_{t + 1}) - \phi(x_*)
+                &\le 
+                -\frac{1}{2}(1 + \eta_{t + 1}\beta)\Vert x_{t + 1} - x_*\Vert^2
+                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+                + \frac{1}{2}\Vert x_t - x_*\Vert^2
+                \\
+                \implies 
+                \phi(x_{t + 1}) - \phi(x_*)
+                &\le 
+                -\frac{1}{2}(1 + \eta_{t + 1}\beta)\Vert x_{t + 1} - x_*\Vert^2
+                - \frac{1}{2}(1 - (1 + \eta_{t + 1}\beta)^{-1})^2\Vert x_t - x_*\Vert^2
+                + \frac{1}{2}\Vert x_t - x_*\Vert^2
+                \\
+                \iff
+                \phi(x_{t + 1}) - \phi(x_*)
+                &\le 
+                -\frac{1}{2}(1 + \eta_{t + 1}\beta)\Vert x_{t + 1} - x_*\Vert^2
+                + \frac{1}{2}\left(
+                    1 - (1 - (1 + \eta_{t + 1}\beta)^{-1})^2
+                \right)
+                \Vert x_t - x_*\Vert^2
+                \\
+                \implies
+                \phi(x_{t + 1}) - \phi(x_*)
+                &\le 
+                -\frac{1}{2}(1 + \eta_{t + 1}\beta)\Vert x_{t + 1} - x_*\Vert^2
+                \\
+                & \quad 
+                + \frac{1}{2}\left(
+                    1 - (1 - (1 + \eta_{t + 1}\beta)^{-1})^2
+                \right)
+                \left(
+                    \prod_{i = 1}^{t}
+                        (1 + \eta_i \beta)^{-1}
+                \right)\Vert x_0 - x_*\Vert^2. 
+            \end{align*}
+            }
+            $\phi$ is a $\eta_{t + 1}\beta$ strongly convex function, implying that 
+            $$
+                (1/2)\Vert x_{t} - x_*\Vert^2 \le (\eta_{t + 1}\beta)^{-1}(\phi(x_t) - \phi(x_*)). 
+            $$
+            Therefore at each iteration, the Lyapunov function would satisfy:
+
+        \end{proof}
+        \begin{remark}
+            In both Guler\cite{guler_convergence_1991} and Rockafellar's \cite{rockafellar_monotone_1976} for PPM, they didn't mention the convergence of function value for strongly convex function explicitly.
+            The lack of interests could be due to the triviality of it, or, the assumption of strongly convex is too strong. 
+            We do it here for completeness and pointing out the obvious.
+
         \end{remark}
@@
             The fundamental proximal gradient lemma was used heavily in the literature to derive convergence results in the convex case. 
-            The "fundamental proximal gradient lemma" originates from Beck's writings\cite[theorem 10.16]{beck_first-order_nodate}. 
+            The "fundamental proximal gradient lemma" originates from Beck's writings \cite[theorem 10.16]{beck_first-order_nodate}. 
             We demonstrate in this example that it's a consequence of \hyperref[thm:ppm_breg_descent_ineq]{theorem \ref*{thm:ppm_breg_descent_ineq}}. 
@@
         We present these varieties generically because these algorithms' forms are of interest.  
-        \begin{definition}[Accelearted Gradient Generic Original Form]
+        \begin{definition}[Accelearted Gradient Generic Original Form]\label{def:agg_original}
             Let $f$ be a $L$ Lipschitz smooth and $\mu\ge 0$ strongly convex function. 
@@
 
-        \begin{definition}[Accelerated Gradient Generic Triangular Form]
+        \begin{definition}[Accelerated Gradient Generic Triangular Form]\label{def:agg_tri}
 
@@
 
-        \begin{definition}[Accelerated Gradient Generic PPM Form]
+        \begin{definition}[Accelerated Gradient Generic PPM Form]\label{agg_ppm}
 

### 2024-06-07 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, fixes and new stuff

--- 2024-06-05 Notebook LaTEX/Momentum Accelerations/main.tex
@@
             With the same choice of the sequence $(\eta_t)_{t \in \NN}$, convergence of the PPM method of a strongly convex function is faster. 
+            The above proof is the same for $\beta = 0$, or $\beta > 0$, because it didn't use the property that $\eta_{t + 1}f$ is a $\eta_{t + 1}\beta$ strongly convex function. 
+        \end{remark}
+
+        \begin{theorem}[PPM Strongly Convex Lyapunov Function]\label{ppm_lyapunov_scvx}
+            With $f$ being $\beta > 0$ strogly convex, with $x_{t + 1} = \hprox_{\eta_{t + 1}f}(x_t)$, then $\Phi_t = \Vert x_{t} - x_*\Vert$ is a Lyapunov function satisfying: 
+            \begin{align*}
+                \frac{\Vert x_{t + 1} - x_*\Vert}{
+                    \Vert x_k - x_*\Vert
+                } &\le (1 + \eta_{t + 1}\beta)^{-1}. 
+            \end{align*}
+        \end{theorem}
+        \begin{proof}
+            This is a direct application that $\hprox_{\eta_{t + 1}f}$ is a contraction with constant $(1 + \beta\eta_{t +1})^{-1}$. 
+        \end{proof}
+        \begin{remark}
+            It's still a mystery on how to show $f(x_t) - f(x_*)$ is a Lyapunov function. 
+            Do observe that, by the choice of $x_*$, the contraction property of the proximal operator is strictly stronger than necessary. 
         \end{remark}

### 2024-06-10 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, fixes and new addition
>w< changes to latex notebook

@@
             It's still a mystery on how to show $f(x_t) - f(x_*)$ is a Lyapunov function. 
+            The answer is not realized by us, nor it is in Rockafellar \cite{rockafellar_monotone_1976} or Guler's\cite{guler_convergence_1991} writings. 
             Do observe that, by the choice of $x_*$, the contraction property of the proximal operator is strictly stronger than necessary. 
+            This inequality at the end is tighter than what we derived for gradient descent. 
         \end{remark}
@@
     To demonstrate, assume that $f$ is a lsc convex function such that it can be approximated by a lower bounding function $l_f(x|\bar x)$ at $\bar x$ such that it satisfies for all $x$: 
-    \begin{align}
+    \begin{align*}
         l_f(x| \bar x) 
         \le f(x) \le l_f(x|\bar x) + \frac{L}{2}\Vert x - \bar x\Vert^2. 
-    \end{align}
+    \end{align*}
     The above characterization is generic enough to include the case where $l_f(x|\bar x)$, the under-approximating function is nonsmooth. 
@@
             In a practical setting, when $L_t = L$, and $\phi_{t}(x) = \eta_{t + 1}f$, this is called a line search.
-            \par
+            \par\noindent
             The convergence rate is loose, and when $f$ exhibits additional favourable properties, such as being strongly convex, the convergence rate can be faster. 
+            Furthermore, if the choice of $y$ remains arbitrary, then the theorem is applicable for function without minimizers. 
         \end{remark}
+
     \subsection{Examples}
@@
             With $\phi(y) = \eta(h(y) + g(x) + \langle \nabla g(x), y - x\rangle)$ as an lower bounding function of $f$. 
-            Let $x^+ = \hprox_\phi(x)$, then for all $u$:
+            Choose any $x$, let $x^+ = \hprox_\phi(x)$, then for all $u$:
+            {\small
             \begin{align*}
                 & \phi(u) + \frac{1}{2}\Vert u - x\Vert^2 - \phi(x^+) - \frac{1}{2}\Vert x^+ - x\Vert^2 
-                \ge \frac{1}{2}\Vert x^+ - u\Vert^2, 
+                \ge \frac{1}{2}\Vert x^+ - u\Vert^2
                 \\
                 \implies &
-                \eta\underbrace{(h(u) + g(x) + \langle \nabla g(x), u - x\rangle + \frac{L}{2}\Vert u - x\Vert^2)}_{\ge \phi(u)} 
+                \eta\underbrace{
+                    \left(
+                        h(u) + g(x) + \langle \nabla g(x), u - x\rangle 
+                    \right)
+                }_{= \phi(u)} 
                 - \eta \underbrace{f(x^+)}_{\le \phi(x^+)} - \frac{1}{2}\Vert x - x^+\Vert^2 
-                \\
-                &\quad  
-                + \left(
-                    \frac{1}{2} - \frac{\eta L}{2}
-                \right)\Vert u - x\Vert^2 
+                + \frac{1}{2} \Vert u - x\Vert^2 
                 \ge 
@@
                 \iff & 
-                f(u) + g(x) - g(u) + 
-                \langle \nabla g(x), u -x\rangle 
-                - f(x^+) + \frac{L}{2}\Vert u - x\Vert^2 - \frac{1}{2\eta}\Vert x - x^+\Vert^2
-                \\
-                & \quad 
+                f(u) + \left(
+                    g(x) - g(u) + \langle \nabla g(x), u -x\rangle 
+                \right)
+                - f(x^+) - \frac{1}{2\eta}\Vert x - x^+\Vert^2
                 + 
-                \left(
-                    \frac{1}{2\eta} - \frac{L}{2}
-                \right)\Vert u - x\Vert^2 
+                \frac{1}{2}\Vert u - x\Vert^2 
                 \ge 
@@
             \end{align*}
+            }
+            \par\noindent
             Removing the negative term $-1/2\eta \Vert x - x^+\Vert^2$ makes LHS larger, establishing the fundamental proximal gradient lemma. 
         \end{example}
+        \begin{remark}
+            Linking the PPM descent inequality to the Bregman divergence of the smooth part of the function on parameters $u, x$ is a clever move. 
+        \end{remark}
 
@@
         We present these varieties generically because these algorithms' forms are of interest.  
-        \begin{definition}[Accelearted Gradient Generic Original Form]\label{def:agg_original}
+        \begin{definition}[AG Generic Original Form]\label{def:agg_original}
             Let $f$ be a $L$ Lipschitz smooth and $\mu\ge 0$ strongly convex function. 
@@
 
-        \begin{definition}[Accelerated Gradient Generic Triangular Form]\label{def:agg_tri}
-
+        \begin{definition}[AG Generic Triangular Form]\label{def:agg_tri}
+            With $f$ be $L$-Lipschitz smooth and $\mu \ge 0$  strongly convex, choose any $y_0 = x_0$, the algorithm admits form: 
+            \begin{align*}
+                x_{t + 1} &= x_t - \tilde \eta_{t + 1} \nabla f(y_t) 
+                \\
+                z_{t + 1} &= y_t - L^{-1} \nabla f(y_t) 
+                \\
+                y_{t + 1} &= 
+                (1 + L\eta_{t + 1})^{-1}
+                (
+                x_{t + 1} + L\eta_{t + 1}z_{t + 1}
+                ). 
+            \end{align*}
         \end{definition}
 
-        \begin{definition}[Accelerated Gradient Generic PPM Form]\label{agg_ppm}
+        \begin{definition}[AG Generic PPM Form]\label{agg_ppm}
 

### 2024-06-11 Notebook LaTEX/Momentum Accelerations/main.tex
>w< new updates on notes

@@
         \begin{example}[Convergence of the proximal gradient method]
-            This section illustrates algorithms that satisfy the above proof's lower and upper bound estimates. 
+            This section \\ illustrates algorithms that satisfy the above proof's lower and upper bound estimates. 
             Consider $f = g + h$ with $h$ nonsmooth convex, and $g$ being $L$-Lipschitz smooth convex and differentiable. 
@@
     They used PPM to derive several variations of the Nesterov accelerated gradient algorithms. 
-    Finally, they refurnished \hyperref[thm:lower_approx_ppm_convergence]{theorem \ref*{thm:lower_approx_ppm_convergence}} for the proof of convergence rate of the accelerated gradient.
+    Finally, they refurnished \hyperref[thm:lower_approx_ppm_convergence]{theorem \ref*{thm:lower_approx_ppm_convergence}} for the proof of convergence rate for the accelerated gradient.
     Their analysis results in relatively simple arguments that exhibits powerful extensions to several variants of the Nesterov accelerated gradient. 
     \par\noindent
-    Interestingly, the Nesterov accelerated gradient applies to PPM; Guler \cite{guler_new_1992} did it two decades ago. 
+    Interestingly, the Nesterov accelerated gradient applies to PPM too; Guler \cite{guler_new_1992} did it two decades ago. 
     He uses the idea of a Nesterov acceleration sequence faithfully. 
@@
             The genericity of the algorithm is provided by item 4., which is the a special case of the smooth descent lemma.
+
+        \end{remark}
+
+        \begin{definition}[AG Generic PPM Form]\label{def:agg_ppm}
+            With $f$ convex, the generic PPM form is formulated for strictly positive stepsizes $\tilde \eta_i,\eta_i$ such that: 
+            \begin{align*}
+                x_{t + 1} &= \argmin_{x} \left\lbrace
+                l_f(x; y_t) + \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
+                \right\rbrace, 
+                \\
+                y_{t + 1} &= \argmin_{x} 
+                \left\lbrace
+                    l_f(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
+                    \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
+                \right\rbrace. 
+            \end{align*}
+            where $l_f(x, \bar x)$ is a convex function satisfying
+            \begin{align*}
+                l_f(x, \bar x) \le f(x) \le f(\bar x) + \frac{L}{2}\Vert x - \bar x\Vert^2. 
+            \end{align*}
+        \end{definition}
+        \begin{remark}
+            With $l_f(x, \bar x) = f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle$, then the above is equivalent to AG Generic Triangular form. 
         \end{remark}
@@
         \begin{definition}[AG Generic Triangular Form]\label{def:agg_tri}
-            With $f$ be $L$-Lipschitz smooth and $\mu \ge 0$  strongly convex, choose any $y_0 = x_0$, the algorithm admits form: 
+            With $f$ be $L$-Lipschitz smooth and $\mu \ge 0$  strongly convex, choose any $y_0 = x_0=z_0$, the algorithm admits form: 
             \begin{align*}
@@
         \end{definition}
+        \begin{remark}
+            The parameter $\eta_t, \eta_{t + 1}$ are coming from the previous generic PPM. 
+            They are the same parameters for both algorithms. 
+        \end{remark}
 
-        \begin{definition}[AG Generic PPM Form]\label{agg_ppm}
+        \begin{definition}[AG Generic PPM Form with Strong Convexity]\label{def:agg_ppm_scvx}
+            Let $f$ be convex and differentiable with Lipschitz gradient and $\mu\ge0$-strongly convex, define $l_f(x; y)$ to be a function such that for all $x, \bar x \in \RR^n$: 
+            \begin{align*}
+               l_f(x; \bar x) + \frac{\mu}{2}\Vert x - \bar x\Vert^2
+               \le f(x; \bar x) 
+               \le l_f(x; \bar x) + \frac{L}{2}\Vert x - \bar x\Vert^2, 
+            \end{align*}
+            then for all $x_0 \in \RR^n$, and let $y_0 = x_0$, define the following variants of PPM for function $f$. 
+            \begin{align*}
+                x_{t + 1} &= \argmin_{x} \left\lbrace
+                l_f(x; y_t) + \frac{\mu}{2}\Vert x - y_t\Vert^2 + \frac{1}{\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
+                \right\rbrace, 
+                \\
+                y_{t + 1} &= \argmin_{x} 
+                \left\lbrace
+                    l_f(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
+                    \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
+                \right\rbrace. 
+            \end{align*}
+            Here we assume that $\eta_{t + 1} > 0$ for all $t \in \NN$. 
+        \end{definition}
+        \begin{remark}
+            Set $\mu = 0$, the above is the same as AG Generid Triangular Form. 
+        \end{remark}
 
-        \end{definition}
+        \begin{proposition}[Triangular Form via PPM Form]
+            with $f$ being $L$-Lipschitz continuous, let $l_f(x, \bar x) = f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle$, we can show that the AG generic triangular form is a consequence of th AG generic PPM form.
+        \end{proposition}
+        \begin{proof}
+            Solving the optimality on the first PPM yields: 
+            \begin{align*}
+                \mathbf 0 &= \nabla f(y_t) + 
+                \frac{1}{\tilde \eta_{t + 1}} (x - x_t)
+                \\
+                x &= x_t - \tilde \eta_{t + 1} \nabla f(y_t).
+            \end{align*}
 
-    \subsection{Nesterov accelerated gradient via PPM}
-    \subsection{Convergence rate of Nesterov accelerated gradient via PPM}
+            Therefore, $x_{t + 1} = x_t - \tilde \eta_{t + 1}\nabla f(y_y)$. 
+            Similarly, for the updates of $y_{t + 1}$, we have optimality condition of 
+            \begin{align*}
+                \mathbf 0 &= \nabla f (y_t) + L (x - y_t) + \eta_{t + 1}^{-1} (x - x_{t + 1})
+                \\
+                \mathbf 0 &= \eta_{t + 1}\nabla f (y_t) + \eta_{t + 1}L (x - y_t) + x - x_{t + 1}
+                \\
+                \mathbf 0 &= 
+                \eta_{t + 1}\nabla f(y_t) -\eta_{t + 1} Ly_t + (\eta_{t + 1}L + 1)x - x_{t + 1}
+                \\
+                (1 + \eta_{t + 1}L)x
+                &= 
+                x_{t + 1} - \eta_{t + 1}\nabla f(y_t) + \eta_{t + 1}L y_t
+                \\
+                \text{define: } y_{t + 1} &:= x. 
+            \end{align*}
+
+            In the above expression, it hides a step of gradient descent, continuing it we have 
+            \begin{align*}
+                (1 + \eta_{t + 1}L)y_{t + 1} &= 
+                x_{t + 1}  + \eta_{t + 1}L (-L^{-1}\nabla f(y_t) + y_t)
+                \\
+                \text{let: } z_{t + 1} &= y_t - L^{-1}\nabla f(y_t), \text{ so, }
+                \\
+                (1 + \eta_{t + 1}L)y_{t + 1} &= 
+                x_{t + 1} + L\eta_{t + 1}z_{t + 1}. 
+            \end{align*}
+
+            Combining it yields the tree points update format
+
+            \begin{align*}
+                x_{t + 1} &= x_t - \tilde \eta_{t + 1} \nabla f(y_t) 
+                \\
+                z_{t + 1} &= y_t - L^{-1} \nabla f(y_t) 
+                \\
+                y_{t + 1} &= 
+                (1 + L\eta_{t + 1})^{-1}
+                (
+                x_{t + 1} + L\eta_{t + 1}z_{t + 1}
+                ), 
+            \end{align*}
+            the ordering of $x_{t +1}, z_{t + 1}$ can be permuted. 
+            The base case is when $t = 0$, so then $x_0 = y_0$ for the initial guess.
+        \end{proof}
+
+    \subsection{Generic Lyapunov analysis for Accelerated gradient via PPM}
+        The first theorem states the generic convergence results when $f$ is differentiable with $L$-Lipschitz gradient, using \ref*{def:agg_ppm}. 
+        \begin{lemma}[Smooth Generic AG Lyapunov Analysis]
+            With $f$ having $L$-Lipschitz gradient and minimizer $x_*$, using \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} and \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} then these are the upper bounds for the RHS of the PPM descent inequality:
+            \begin{align*}
+                \Upsilon_{1, t + 1}^{\text{AG}}&= \tilde \eta_{t + 1} (f(z_{t + 1}) - f(x_*))
+                + \frac{1}{2}(
+                    \Vert x_{t + 1} - x_*\Vert^2 - \Vert x_t - x_* \Vert^2
+                )  
+                \\
+                & \quad \le 
+                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 + 
+                \frac{\tilde \eta_{t + 1} L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                - 
+                \langle \tilde \eta_{t + 1} \nabla f(y_t), x_{t + 1} - z_{t + 1} \rangle, 
+                \\
+                \Upsilon_{2, t + 1}^{\text{AG}} 
+                &= f(z_{t + 1}) - f(z_t) 
+                \le 
+                \langle \nabla f(y_t), z_{t + 1} - z_t\rangle + 
+                \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            Define $\phi_t(x) = \tilde \eta_{t +1}(f(y_t) + \langle \nabla f(y_t), x- y_t\rangle)$.  
+            With $L$-smoothness of $f$ in mind, consider the following sequence of inequalities: 
+            $$
+            \begin{aligned}
+                \phi_t(x_{t + 1}) 
+                &= 
+                \tilde\eta_{t + 1} (f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle)
+                \\
+                \phi_t (x_{t + 1}) &= \tilde \eta_{t + 1}(
+                    f(y_t) + \langle \nabla f(y_t), (x_{t +1} - z_{t + 1}) + (z_{t + 1} - y_t) \rangle
+                )
+                \\
+                &\ge 
+                \tilde \eta_{t + 1}
+                \left(
+                    f(z_{t + 1}) - \frac{L}{2} \Vert z_{t + 1} - y_t\Vert^2 + 
+                    \langle \nabla f(y_t), x_{t +1} - z_{t + 1}\rangle
+                \right), 
+            \end{aligned}
+            $$
+            performing PPM on the function produces the PPM Lyapunov inequality, substituting yields equivalences for all $x_*$: 
+            {\footnotesize
+            \begin{align*}
+                & \phi_t(x_{t + 1}) - \phi_t(x_*) + \frac{1}{2}\Vert x_* - x_{t + 1}\Vert^2 
+                - \frac{1}{2}\Vert x_* - x_t\Vert^2 
+                =: \Upsilon_{1, t + 1}^{\text{AG}}
+                \\
+                &\quad \le 
+                - \frac{1}{2} \Vert x_{t + 1} - x_t\Vert^2 
+                \\
+                \implies & 
+                \tilde \eta_{t + 1}\left(
+                    f(z_{t + 1}) - \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2 
+                    + 
+                    \langle \nabla f(y_t), x_{t + 1} - z_{t + 1}\rangle
+                \right) - \tilde \eta_{t + 1} f(x_*)
+                + 
+                \frac{1}{2}\left(
+                    \Vert x_{t + 1} - x_*\Vert^2 - \Vert x_{t} - x_*\Vert^2
+                \right)
+                \\
+                &\quad \le
+                 - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+                \\
+                \iff 
+                & 
+                \tilde \eta_{t + 1} \left(
+                    f(z_{t + 1}) - f(x_*)
+                \right) + \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2 
+                - \frac{1}{2}\Vert x_{t} - x_*\Vert^2 
+                \\
+                &\quad \le 
+                -\frac{1}{2} \Vert x_{t + 1 } - x_t\Vert^2 + 
+                \frac{\tilde \eta_{t + 1}}{2}\Vert z_{t + 1} - y_t\Vert^2 
+                - \langle \tilde \eta_{t + 1}\nabla f(y_t), x_{t + 1} - z_{t + 1} \rangle. 
+            \end{align*}
+            }
+
+            Observe that, the rhs and lhs of the Lyapunov inequality are anchored at $z_{t + 1}$. 
+            Similarly for the descent inequality we wish to obtain:
+
+            \begin{align*}
+                f(z_{t + 1}) - f(z_t) &= f(z_{t + 1}) - f(y_t) + f(y_t) - f(z_t) 
+                \\
+                &\le 
+                \langle \nabla f(y_t), z_{t + 1} - y_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2 
+                + 
+                \langle \nabla f(y_t), y_t - z_t\rangle
+                \\
+                &= 
+                \langle \nabla f(y_t), z_{t + 1} - z_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                \\
+                \text{let }\Upsilon_{2, t + 1}^{\text{AG}} 
+                &:= f(z_{t + 1}) - f(z_t)
+            \end{align*}
+
+            Which is the descent inequality anchored on $z_{t + 1}$. 
+            Merging the $(z_{t + 1} - y_t)$ with $y_t - z_t$ together yield the desired results. 
+        \end{proof}
+
+        \begin{theorem}[Generic AG Convergence]\label{thm:generic_smooth_ag_convergence}
+            If there is a choice of $\eta_i, \tilde \eta_i$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} such that we have 
+            \begin{align*}
+                \left(
+                    \sum_{i = 1}^{t} \tilde \eta_i
+                \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{2, t + 1}^{\text{AG}} \le 0, 
+            \end{align*}
+            then with 
+            \begin{align*}
+                \Phi_t &= \left(
+                    \sum_{i = 1}^{t} \tilde\eta_{t + 1}
+                \right) (f(z_t) - f(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \NN
+                \\
+                \Phi_0 &= \frac{1}{2}\Vert x_t - x_*\Vert^2, 
+            \end{align*}
+            we have $\Phi_{t + 1} - \Phi_t \le 0$, which allows for a convergence rate of $\mathcal O \left(\sum_{i = 1}^{T} \eta_i^{-1}\right)$ for $f(z_t) - f(x_*)$. 
+        \end{theorem}
+        \begin{proof}
+            The derivation is direct and very similar to \hyperref[thm:ppm_convergence_rate]{theorem \ref*{thm:ppm_convergence_rate}} which is 
+            {\footnotesize
+            \begin{align*}
+                \Phi_{t + 1} - \Phi_t 
+                &= 
+                \left(
+                    \sum_{i = 1}^{t+1} \tilde\eta_{i}
+                \right) (f(z_{t + 1}) - f(x_*)) 
+                - 
+                \left(
+                    \sum_{i = 1}^{t} \tilde\eta_{i}
+                \right) (f(z_{t}) - f(x_*)) 
+                + \frac{1}{2}\Vert x_t - x_*\Vert^2
+                - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
+                \\
+                &= 
+                \tilde \eta_{t + 1} (f(z_{t + 1}) - f(z_*))
+                +
+                \left(
+                    \sum_{i = 1}^{t} \tilde \eta_i
+                \right)(f(z_{t + 1}) - f(z_t))
+                + \frac{1}{2}\Vert x_t - x_*\Vert^2
+                - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
+                \\
+                &= \left(
+                    \sum_{i = 1}^{t} \tilde \eta_i
+                \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{2, t + 1}^{\text{AG}} \le 0. 
+            \end{align*}
+            }
+            Therefore, if we can identify parameter for the generic algorithm that asserts the condition above, then we have convergence for the algorithm. 
+        \end{proof}
+
+    \subsection{Scenario I}
+        In this scenario, we aim to recover the following variant of the Accelerated gradient algorithm from 12.1 in Ryu's writing \cite{ryu_large-scale_2022}, it is: 
+        \begin{align*}
+            z_{t + 1} &= y_k + L^{-1}\nabla f(y_t), 
+            \\
+            y_{t + 1} &= z_{t + 1} + \frac{t - 1}{t + 2}\left(
+                z_{k + 1} - z_k
+            \right). 
+        \end{align*}
+        An equivalent form of the above is also provided by Ryu: 
+        \begin{align*}
+            z_{t + 1} &= y_t + L^{-1}\nabla f(y_t), 
+            \\
+            x_{k + 1} &= x_t + (t + 1)(2L)^{-1}\nabla f(y_t), 
+            \\
+            y_{k + 1} &= \left(
+                1 - \frac{2}{k + 2} 
+            \right)z_{k + 1} + 
+            \left(
+                \frac{1}{k + 2}
+            \right)x_{k + 1}. 
+        \end{align*}
+        We advise the reader to read the Biliography notes by Ryu \cite[chapter 12]{ryu_large-scale_2022} of his book. 
+        It goes over the full context and history for this particular variant of gradient acceleration method. 
+        As the time of composing this notes, the writer is still reading on the topic of accelerated gradient.
+
+        \begin{proposition}
+            The above algorithm is a consequence of a specific choice of $\eta_t, \tilde \eta_t$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} where $\eta_{t + 1} = \tilde \eta_{t + 1} = (t - 1)/L$.
+        \end{proposition}
+        \begin{proof}
+            Consider the upper bounds of $\Upsilon_{1, t + 1}^\text{AG}, \Upsilon_{2, t + 1}^\text{AG}$, together with the updates of the Generic Triangular Form of the algorithm:  
+            \begin{align*}
+                x_{t + 1} - x_t &= \tilde \eta_{t + 1}\nabla f(y_t)
+                \\
+                z_{t +1} - y_t &= L^{-1}\nabla f(y_t), 
+            \end{align*}
+            we consider the upper bound of $\Upsilon_{1, t + 1}^{\text{AG}}$, with that we can simplify it: 
+            {\footnotesize
+            \begin{align*}
+                \Upsilon_{1, t + 1}^{\text{AG}}
+                &\le 
+                -\frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+                + 
+                \frac{\tilde \eta_{t + 1}L }{2} \Vert z_{t + 1} - y_t\Vert^2 
+                - 
+                \langle \tilde \eta_{t + 1} \nabla f(y_t), x_{t +1} - z_{t + 1}\rangle
+                \\
+                &\le 
+                - \frac{1}{2}\Vert \tilde \eta_{t + 1} \nabla f(y_t)\Vert^2 
+                + \frac{\tilde \eta_{t + 1} L}{2}\Vert L^{-1} \nabla f(y_t)\Vert^2 
+                + 
+                \langle 
+                    - \tilde \eta_{t + 1} \nabla f(y_t), 
+                    -L^{-1}\nabla f(y_t) + y_t - x_t + \tilde \eta_{t + 1}\nabla f(y_t)
+                \rangle
+                \\
+                &= 
+                \left(
+                    \frac{\tilde \eta_{t + 1}^2}{2} + 
+                    \frac{\tilde \eta_{t + 1}}{2L}
+                \right)
+                \Vert \nabla f(y_t)\Vert^2 
+                + \tilde \eta_{t + 1} 
+                \left\langle 
+                    \nabla f(y_t), 
+                    (\tilde \eta_{t + 1} - L^{-1})\nabla f(y_t) + y_t - x_t 
+                \right\rangle
+                \\
+                &= 
+                (1/2)(L^{-1}\tilde \eta_{t + 1} - \tilde \eta_{t + 1}^2)
+                \Vert \nabla f(y_t)\Vert^2
+                + 
+                \tilde \eta_{t + 1}(\tilde \eta_{t + 1} - L^{-1})
+                \Vert \nabla f(y_t)\Vert^2
+                + 
+                \tilde \eta_{t + 1}\langle \nabla f(y_t), y_t - x_t\rangle
+                \\
+                &= \frac{1}{2}\left(
+                    -L^{-1}\tilde \eta_{t + 1} + \tilde \eta_{t + 1}^2
+                \right)\Vert \nabla f(y_t)\Vert^2 
+                + 
+                \tilde\eta_{t + 1} \langle \nabla f(y_t), y_t - x_t\rangle. 
+            \end{align*}
+            }
+            For $\Upsilon_{2, t + 1}^\text{AG}$, we simplify it with the same updates relation in mind: 
+            \begin{align*}
+                \Upsilon_{2, t + 1}^\text{AG}
+                &\le 
+                \langle \nabla f(y_t), z_{t +1} - y_t\rangle + 
+                \frac{L}{2}\Vert z_{t +1} - y_{t} \Vert^2 
+                + 
+                \langle \nabla f(y_t), y_t - z_t\rangle
+                \\
+                &= 
+                \langle 
+                    \nabla f(y_t), -L^{-1} \nabla f(y_t)
+                \rangle + 
+                \frac{L}{2}\Vert L^{-1}\nabla f(y_t) \Vert^ 2
+                + 
+                \langle \nabla f(y_t), y_t - z_t\rangle
+                \\
+                &= -\frac{1}{2L}\Vert \nabla f(y_t)\Vert^2 
+                + \langle \nabla f(y_t), y_t - z_t\rangle. 
+            \end{align*}
+            Observe that the cross product term for $\Upsilon_{1, t + 1}^\text{AG}, \Upsilon_{2, t + 1}^\text{AG}$ doesn't match. 
+            Hence let's consider $y_t - x_t = L \eta_t (z_t - y_t)$ from the algorithm, we make the choice to do surgery on upper bound of $\Upsilon_{2, t + 1}^\text{AG}$, so $\langle \nabla f(y_t), y_t - x_t\rangle = \langle \nabla f(y_t), L \eta_t (z_t - y_t)\rangle$.
+            With this in mind, applying the RHS of \hyperref[thm:generic_smooth_ag_convergence]{theorem \ref*{thm:generic_smooth_ag_convergence}} yields inequality: 
+            {\footnotesize
+            \begin{align*}
+                & \Upsilon_{1, t + 1}^{\text{AG}} + \left(
+                    \sum_{i=1}^{t}\tilde\eta_i 
+                \right) \Upsilon_{2, t + 1}^{\text{AG}} 
+                \\
+                & \le 
+                \frac{1}{2}\left(
+                    -L^{-1}\tilde \eta_{t + 1} + \tilde \eta_{t + 1}^2
+                \right)\Vert \nabla f(y_t)\Vert^2 
+                + 
+                \tilde\eta_{t + 1} \langle \nabla f(y_t), y_t - x_t\rangle
+                + 
+                \left(
+                    \sum_{i = 1}^{t}\tilde \eta_i 
+                \right)\left(
+                    -\frac{1}{2L}\Vert \nabla f(y_t)\Vert^2 
+                    + \langle \nabla f(y_t), y_t - z_t\rangle
+                \right)
+                \\
+                & =
+                \left(
+                    \frac{1}{2}\tilde\eta_{t + 1}\left(
+                        \tilde \eta_{t +1} - L^{-1}
+                    \right)
+                    - 
+                    \frac{1}{2L}\sum_{i = 1}^{t}\tilde \eta_i
+                \right)\Vert \nabla f(y_t)\Vert^2
+                + 
+                \tilde \eta_{t + 1}\langle \nabla f(y_t), L\eta_t (z_t - y_t)\rangle
+                + 
+                \left(
+                    \sum_{i = 1}^{t}\tilde \eta_i
+                \right)
+                \langle \nabla f (y_t), y_t - z_t\rangle
+                \\
+                & = 
+                \left(
+                    \frac{1}{2}\tilde\eta_{t + 1}\left(
+                        \tilde \eta_{t +1} - L^{-1}
+                    \right)
+                    - 
+                    \frac{1}{2L}\sum_{i = 1}^{t}\tilde \eta_i
+                \right)\Vert \nabla f(y_t)\Vert^2
+                + 
+                \left(
+                    L\eta_t \tilde \eta_{t + 1} - \sum_{i = 1}^{t}\tilde \eta_i
+                \right)
+                \langle \nabla f(y_t), z_t - y_t\rangle. 
+            \end{align*}
+            }
+            Next, we select a choice for stepsize parameter $\eta_t, \tilde \eta_{t +1}$ such that the coefficient for the $\Vert \nabla f(y_t)\Vert^2$ is negative, and is zero for the cross product term.
+            In this scenario, we makes the choice of $\tilde \eta_t = \eta_t$. 
+            Continuting will simplify the upper bound so that it is: 
+            \begin{align*}
+                \frac{1}{2}\left(
+                    \eta_{t + 1}^2 - L^{-1}\eta_{t +1} - L^{-1}\sum_{i = 1}^{t}\eta_i
+                \right)\Vert \nabla f(y_t)\Vert^2
+                + 
+                \left(
+                    L\eta_t \eta_{t + 1} - \sum_{i = 1}^{t} \eta_i
+                \right)
+                \langle \nabla f(y_t), z_t - y_t\rangle 
+                &
+                \le 0. 
+            \end{align*}
+            Assuming the above inequality holds then one of the sufficient conditions would happen when the coefficient of the cross product term is zero and the coefficient for the normed term is negative, yielding the condition for all $t \in \NN$:
+            \begin{align*}
+                \begin{cases}
+                    L\eta_{t + 1}^2 + \eta_{t + 1} - \sum_{i = 1}^{t}\eta_i 
+                    \le 0, 
+                    \\
+                    L\eta_t \eta_{t + 1} - \sum_{i = 1}^{t} \eta_i 
+                    = 0. 
+                \end{cases}
+            \end{align*}
+            Substituting the sequence equality back to the first one yield: 
+            \begin{align*}
+                L\eta_{t + 1}^2 - (\eta_{t + 1} + L\eta_t\eta_{t + 1}) &\le 0 
+                \\
+                L\eta^2_{t + 1} - \eta_{t + 1}
+                &\le 
+                L\eta_t \eta_{t + 1} 
+                \\
+                \eta_{t + 1}(L\eta_{t + 1} - 1) 
+                &\le L\eta_t\eta_{t + 1}
+                \\
+                \eta_t > 0 
+                \implies 
+                L\eta_{t + 1} - 1 &\le 
+                L\eta_t 
+                \\
+                \eta_{t + 1} &\le \eta_t + L^{-1}. 
+            \end{align*}
+            To satisfies the equality, reader should verify that $\eta_{t + 1} = (t - 1)/ L$ is one of the options. 
+            And there are not many other options for the choice of the stepszies for the equality to be satisfied. 
+        \end{proof}
+
+    \subsection{Scenario II}
+
+    \subsection{Scenario III}
 
@@
     In this section, we reproduce some of the analysis for Nesterov accelerated gradient method with excruciating details.
+
+\section{Modern techniques in analysis of accelerated gradient algorithms}
 

### 2024-06-13 Notebook LaTEX/Momentum Accelerations/main.tex
/w\ Merge conflicts next

@@
             \\
-            x_{k + 1} &= x_t + (t + 1)(2L)^{-1}\nabla f(y_t), 
-            \\
-            y_{k + 1} &= \left(
-                1 - \frac{2}{k + 2} 
-            \right)z_{k + 1} + 
-            \left(
-                \frac{1}{k + 2}
-            \right)x_{k + 1}. 
-        \end{align*}
+            x_{t + 1} &= x_t + (t + 1)(2L)^{-1}\nabla f(y_t), 
+            \\
+            y_{t + 1} &= \left(
+                1 - \frac{2}{t + 2} 
+            \right)z_{t + 1} + 
+            \left(
+                \frac{1}{t + 2}
+            \right)x_{t + 1}. 
+        \end{align*}
+        The base case requires cares since it's not unique, and depending on how the base case is define, there even more representations of it. 
+        \begin{observation}
+            Observe that the second equivalent form is an example of \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
+            \par\noindent
+            It is stated in Ryu's writing that the base case is $x_0 = y_0 = z_0$, 
+            \textcolor{purple}{we think this is not the only options.} 
+            We remind the reader that there is not an obvious choice of $t\in \mathbb Z$ such that $x_t = y_t = z_t$ where the above algorithm remains consistent for all $t \ge -1$. 
+            The choice of base case presented in Ryu's writing is a choice and not a necessity. 
+            We state that one of the base case scenario only requires knowing $y_1$.
+
+            \par\noindent 
+            We need to observe the case where $t = 0$ to understand the base case of the algorithm. 
+            At each iteration $t$, Given $(x_t, y_t)$, the above formula maps to $(x_{t + 1}, y_{t + 1}, z_{t + 1})$. 
+            When $t= 0$, it has $y_1 = x_1$. 
+            Therefore, knowing only either $y_1$, or $x_1$ can initiate the algorithm. 
+            This is an alternative scenario of the base case. 
+            If, we wish to write $y_0 = x_0$ at $t = 0$ for the base case instead, then it creates the following algorithm 
+            \begin{align*}
+                y_{t} &= \left(
+                1 - \frac{2}{t + 2} 
+                \right)z_{t} + 
+                \left(
+                    \frac{1}{t + 2}
+                \right)x_{t}, 
+                \\
+                z_{t + 1} &= y_t + L^{-1}\nabla f(y_t), 
+                \\
+                x_{t + 1} &= x_t + (t + 1)(2L)^{-1}\nabla f(y_t). 
+            \end{align*}
+            It has a different representations due to a specific choice of the base case. 
+            \par\noindent
+            Finally, by the observation that given $(z_t, y_t)$ for any $t\ge -1$, we can solve for $x_t$ \newline via $y_t = (1 - 2/(1 + t))z_t + 1/(t + 1)x_t$, obtaining $(x_t, y_t, z_t)$, hence the algorithm can be reduced to a representations with only $(z_t, y_t)$ and an updates using only $(z_t, y_t)$ to $(z_{t + 1}, y_{t + 1})$.
+            That is the momentum form presented above.
+
+        \end{observation}
         We advise the reader to read the Biliography notes by Ryu \cite[chapter 12]{ryu_large-scale_2022} of his book. 

### 2024-06-13 Notebook LaTEX/Momentum Accelerations/main.tex
nope

--- 2024-06-11 Notebook LaTEX/Momentum Accelerations/main.tex
@@
 
-        \begin{proposition}[Triangular Form via PPM Form]
+        \begin{proposition}[Triangular Form via PPM Form]\label{prop:tri_form_via_ppm}
             with $f$ being $L$-Lipschitz continuous, let $l_f(x, \bar x) = f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle$, we can show that the AG generic triangular form is a consequence of th AG generic PPM form.
@@
             \end{align*}
-
             Therefore, $x_{t + 1} = x_t - \tilde \eta_{t + 1}\nabla f(y_y)$. 
@@
             \end{align*}
-
             In the above expression, it hides a step of gradient descent, continuing it we have 
@@
             \end{align*}
-
             Combining it yields the tree points update format 
-
             \begin{align*}
@@
         The first theorem states the generic convergence results when $f$ is differentiable with $L$-Lipschitz gradient, using \ref*{def:agg_ppm}. 
-        \begin{lemma}[Smooth Generic AG Lyapunov Analysis]
+        \begin{lemma}[Smooth Generic AG Lyapunov Analysis]\label{lemma:smooth_agg_lyapunov_upper_bound}
             With $f$ having $L$-Lipschitz gradient and minimizer $x_*$, using \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} and \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} then these are the upper bounds for the RHS of the PPM descent inequality:
@@
             }
-
             Observe that, the rhs and lhs of the Lyapunov inequality are anchored at $z_{t + 1}$. 
             Similarly for the descent inequality we wish to obtain: 
-
             \begin{align*}
@@
                 \text{let }\Upsilon_{2, t + 1}^{\text{AG}} 
-                &:= f(z_{t + 1}) - f(z_t)
-            \end{align*}
-
+                &:= f(z_{t + 1}) - f(z_t). 
+            \end{align*}
             Which is the descent inequality anchored on $z_{t + 1}$.
@@
             \end{align*}
-            we have $\Phi_{t + 1} - \Phi_t \le 0$, which allows for a convergence rate of $\mathcal O \left(\sum_{i = 1}^{T} \eta_i^{-1}\right)$ for $f(z_t) - f(x_*)$. 
+            we have $\Phi_{t + 1} - \Phi_t \le 0$, which allows for a convergence rate of $\mathcal O \left(\sum_{i = 1}^{T} \eta_i^{-1}\right)$ for $f(z_T) - f(x_*)$. 
         \end{theorem}
         \begin{proof}
-            The derivation is direct and very similar to \hyperref[thm:ppm_convergence_rate]{theorem \ref*{thm:ppm_convergence_rate}} which is 
+            By definition we have
             {\footnotesize
@@
             }
+            The derivation for the convergence raet is direct and similar to 
+            \hyperref[thm:ppm_convergence_rate]{theorem \ref*{thm:ppm_convergence_rate}} 
             Therefore, if we can identify parameter for the generic algorithm that asserts the condition above, then we have convergence for the algorithm. 
@@
     \subsection{Scenario I}
-        In this scenario, we aim to recover the following variant of the Accelerated gradient algorithm from 12.1 in Ryu's writing \cite{ryu_large-scale_2022}, it is: 
+        In this scenario, we aim to recover the following variant of the accelerated gradient algorithm from 12.1 in Ryu's writing \cite{ryu_large-scale_2022}, it is: 
         \begin{align*}
@@
         As the time of composing this notes, the writer is still reading on the topic of accelerated gradient. 
-
         \begin{proposition}
-            The above algorithm is a consequence of a specific choice of $\eta_t, \tilde \eta_t$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} where $\eta_{t + 1} = \tilde \eta_{t + 1} = (t - 1)/L$.
+            With $\eta_t, \tilde \eta_t$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} where $\eta_{t + 1} = \tilde \eta_{t + 1} = (t - 1)/L$, we derive the following algorithm: 
+            \begin{align*}
+            \end{align*}
+
         \end{proposition}
@@
             Hence let's consider $y_t - x_t = L \eta_t (z_t - y_t)$ from the algorithm, we make the choice to do surgery on upper bound of $\Upsilon_{2, t + 1}^\text{AG}$, so $\langle \nabla f(y_t), y_t - x_t\rangle = \langle \nabla f(y_t), L \eta_t (z_t - y_t)\rangle$.
-            With this in mind, applying the RHS of \hyperref[thm:generic_smooth_ag_convergence]{theorem \ref*{thm:generic_smooth_ag_convergence}} yields inequality: 
+            With this in mind, applying 
+            \hyperref[thm:generic_smooth_ag_convergence]{theorem \ref*{thm:generic_smooth_ag_convergence}} 
+            and upper bound from 
+            \hyperref[lemma:smooth_agg_lyapunov_upper_bound]{lemma \ref*{lemma:smooth_agg_lyapunov_upper_bound}} 
+            yields inequality: 
             {\footnotesize
@@
             \end{align*}
-            To satisfies the equality, reader should verify that $\eta_{t + 1} = (t - 1)/ L$ is one of the options. 
+            To satisfy the equality, reader should verify that $\eta_{t + 1} = (t - 1)/ L$ is one of the options. 
             And there are not many other options for the choice of the stepszies for the equality to be satisfied. 
@@
     \subsection{Scenario II}
+        With the choice of $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we can recover the seminal Nesterov accelerated gradient algorithm from 1983.
 
@@
     In this section, we reproduce some of the analysis for Nesterov accelerated gradient method with excruciating details. 
+    We will also go over some details about the history, development and motivations behind the accelerated gradient algorithm.
 

### 2024-06-13 Notebook LaTEX/Momentum Accelerations/main.tex
merged?

@@
         As the time of composing this notes, the writer is still reading on the topic of accelerated gradient.
+
         \begin{proposition}

### 2024-06-13 Notebook LaTEX/Momentum Accelerations/main.tex
manually merged fuck it
OcO, sanity check

@@
         As the time of composing this notes, the writer is still reading on the topic of accelerated gradient. 
-
         \begin{proposition}
@@
             \begin{align*}
-            \end{align*}
-
+                x_{t + 1} &= x_t - \frac{t + 1}{2L} \nabla f(y_t), 
+                \\
+                z_{t + 1} &= y_t - L^{-1} \nabla f(y_t), 
+                \\
+                y_{t + 1} &= 
+                \left(
+                    \frac{2}{t + 3}
+                \right)x_{t +1} + 
+                \left(
+                    1 - \frac{2}{t + 3}
+                \right)z_{t + 1}. 
+            \end{align*}
         \end{proposition}
+        \begin{observation}
+            Observe that this is the same algorithm as stated in Ryu's book but with an alternative choice of indexing for $y_t$ and initial condition. 
+        \end{observation}
         \begin{proof}
@@
             \end{align*}
-            To satisfy the equality, reader should verify that $\eta_{t + 1} = (t - 1)/ L$ is one of the options. 
+            To satisfy the equality, reader should verify that $\eta_{t + 1} = (t)/ L$ is one of the options. 
             And there are not many other options for the choice of the stepszies for the equality to be satisfied. 

### 2024-06-14 Notebook LaTEX/Momentum Accelerations/main.tex
>w< ok we are back

@@
             That is the momentum form presented above. 
-
         \end{observation}
@@
         As the time of composing this notes, the writer is still reading on the topic of accelerated gradient.
+
         \begin{proposition}
-            With $\eta_t, \tilde \eta_t$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} where $\eta_{t + 1} = \tilde \eta_{t + 1} = (t - 1)/L$, we derive the following algorithm: 
+            With $\eta_t, \tilde \eta_t$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} where $\eta_{t + 1} = \tilde \eta_{t + 1} = 2/(2L)$, we derive the following algorithm: 
             \begin{align*}
@@
             \end{align*}
-            To satisfy the equality, reader should verify that $\eta_{t + 1} = (t)/ L$ is one of the options. 
+            To satisfy the equality, reader should verify that $\eta_{t} = t/(2L)$ is one of the options. 
             And there are not many other options for the choice of the stepszies for the equality to be satisfied. 

### 2024-06-14 Notebook LaTEX/Momentum Accelerations/main.tex
>w< updates

@@
             The choice of base case presented in Ryu's writing is a choice and not a necessity. 
-            We state that one of the base case scenario only requires knowing $y_1$.
+            We state that one of the base case scenario that only requires knowing $y_1$.
 
@@
         \end{proof}
+        \begin{remark}
+            In the original writing by Ahn \cite[4.9]{ahn_understanding_2022}, they didn't list what exactly this algorithm is.
+Here we stated that it should be equivalent to the acceleration algorithm stated in Ryu \cite[algorithm 12.1]{ryu_large-scale_2022}.
+        \end{remark}
 
@@
         With the choice of $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we can recover the seminal Nesterov accelerated gradient algorithm from 1983. 
+        We will discuss how other choices of $\tilde \eta_{t +1}$ results in other varients of the Accelerated gradient such as the variants proposed by Chambolle \cite{chambolle_convergence_2015}.
 

### 2024-06-18 Notebook LaTEX/Momentum Accelerations/main.tex
>w<,added stuff to notes

@@
 \author{
-    Alto
+    The Alto Hivemind (My Pen name)
     \thanks{
@@
     For a general overview of smoothness and strong convexity in the Euclidean space, see \cite[theorem 2.1.5, theorem 2.1.10]{nesterov_lectures_2018} for a full exposition of the topic. 
+    \par\noindent
+    We assume the reader is well-versed in convex optimization and convex analysis. 
     \subsection{Lipschitz smoothness}
@@
                 x_{t + 1} &= \argmin_{x} \left\lbrace
-                l_f(x; y_t) + \frac{\mu}{2}\Vert x - y_t\Vert^2 + \frac{1}{\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
+                l_f(x; y_t) + \frac{\mu}{2}\Vert x - y_t\Vert^2 + \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
                 \right\rbrace, 
@@
         \begin{remark}
-            In the original writing by Ahn \cite[4.9]{ahn_understanding_2022}, they didn't list what exactly this algorithm is.
-Here we stated that it should be equivalent to the acceleration algorithm stated in Ryu \cite[algorithm 12.1]{ryu_large-scale_2022}.
+            In the original writing by Ahn \cite[equation (4.9)]{ahn_understanding_2022}, they didn't identify the algorithm in the literature. 
+            Here we identify it to be equivalent to the acceleration algorithm stated in Ryu \cite[algorithm 12.1]{ryu_large-scale_2022}. 
         \end{remark}
@@
         We will discuss how other choices of $\tilde \eta_{t +1}$ results in other varients of the Accelerated gradient such as the variants proposed by Chambolle \cite{chambolle_convergence_2015}. 
+        \par\noindent
+        To start, we make the claim that the new stepsizes results in a different algorithm. 
+        \begin{lemma}[Similar Triangular Form]
+            With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$ as in \ref*{def:agg_tri}, we have the following specific similar triangular form of the accelerated gradient algorithm: 
+            \begin{align*}
+                z_{t + 1} &= y_t - L^{-1} \nabla f(y_t) 
+                \\
+                x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
+                \\
+                y_{t + 1} &= 
+                (1 + L\eta_{t + 1})^{-1}
+                (
+                x_{t + 1} + L\eta_{t + 1}z_{t + 1}
+                ). 
+            \end{align*}
+            It also has an equivalent momentum form 
+            \begin{align*}
+                z_{t + 1} &= y_t - L^{-1}\nabla f(y_t)
+                \\
+                y_{t + 1} &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t). 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            To do, we show that updates sequence $x_{t + 1} = z_{t + 1} + L\eta_t (z_{t + 1} - z_t)$ is equivalent to $x_{t + 1} = x_t + \tilde\eta_{t + 1}\nabla f(y_t)$. 
+            Starting with the former, susbtitute definition of $z_{t + 1}$, $z_{t + 1} = z_t + L^{-1}\nabla f(y_t)$ expanding: 
+            \begin{align*}
+                x_{t + 1} &= y_t - L^{-1}\nabla f(y_t) 
+                + L \eta_t y_t - \eta_t \nabla f(y_t) - L\eta_t z_t
+                \\
+                &= 
+                (1 + L\eta_t)y_t - (\eta_t + L^{-1})\nabla f(y_t) - L\eta_t z_t
+                \\
+                &= \eta_t Lz_t + x_t -(\eta_t + L^{-1}) \nabla f(y_t)  - L\eta_t z_t
+                \\
+                &= x_t - (\eta_t + L^{-1})\nabla f(y_t). 
+            \end{align*}
+            By assumption $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we ends with $x_{t + 1} = x_t + \tilde \eta_{t + 1}\nabla f(y_t)$. 
+            Reducing it to the classic momentum form starts by 
+            \begin{align*}
+                y_{t + 1} &= (1 + L\eta_{t + 1})^{-1} (x_{t + 1} + L\eta_{t + 1}z_{t + 1})
+                \\
+                &= (1 + L\eta_{t + 1})^{-1} (
+                    z_{t + 1} + L\eta_t (z_{t + 1} - z_t) + L\eta_{t + 1} z_{t + 1}
+                )
+                \\
+                &= 
+                (1 + L\eta_{t + 1})^{-1} (
+                    (1 + L\eta_{t + 1})z_{t + 1} + L\eta_t(z_{t + 1} - z_t)
+                )
+                \\
+                &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t), 
+            \end{align*}
+            it negates the $x_t$ variables, therefore we have 
+            \begin{align*}
+                z_{t + 1} &= y_t - L^{-1}\nabla f(y_t)
+                \\
+                y_{t + 1} &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t).
+            \end{align*}
+        \end{proof}
+        \begin{remark}
+            In this remark we clarify the name "similar triangule" as given in the literatures. 
+            We think it is a fitting name, becaues it has a similar triangle in it. 
+            We list the following observations
+            \begin{enumerate}
+                \item 
+                The updates for $y_{t}$ from the algorithm has 
+                $$
+                    y_t = (1 + L\eta_t)^{-1} x_t + L\eta_t(1 + L\eta_t)^{-1} z_t, 
+                $$
+                therefore, $y_t$ is a convex combinations of $x_t, z_t$, so $z_t, y_t, x_t$ are three collinear points. 
+                We have the ratio $\Vert y_t - x_t\Vert/\Vert z_t - y_t\Vert = L\eta_t$. 
+                \item 
+                The updates for $z_{t + 1}, x_{t + 1}$ are based on $y_t, x_t$, therefore vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$. 
+                \item The updates for $x_{t + 1}$ has $x_{t + 1} - z_{t + 1} = L\eta_t \left(z_{t + 1} - z_t\right)$, therefore, the three points $z_t, x_{t + 1}, z_{t + 1}$ are collinear. 
+                The ratio between line segment has $\Vert x_{t + 1} - z_{t + 1}\Vert/\Vert z_{t + 1} - z_t\Vert = L\eta_t$. 
+            \end{enumerate}
+            By these tree observations, the triangle $z_{t}, z_{t + 1}, y_t$ similar to triangle $z_t, x_{t + 1}, x_t$. 
+        \end{remark}
+        The next lemma will determine one choice of the stepsize sequence $\eta_t$ that recovers the classical form of Nesterov accelerated gradient method.
+
+        \begin{lemma}[Deriving the Nesterov Sequence]
+            For all $t \in \mathbb N$
+            \begin{align*}
+                \left\lbrace
+                \begin{aligned}
+                    (1 + L\eta_{t + 1})^{-1}L \eta_t 
+                    &= \frac{a_t - 1}{a_{t + 1}} , 
+                    \\
+                    a_{t + 1}^2 - a_t &= a_t^2. 
+                \end{aligned} 
+                \right. 
+            \end{align*}
+            allows \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}} to converge at an optimal rate. 
+            The base case is $\eta_0 = 0$. 
+        \end{lemma}
+        \begin{proof}
+            Continue from \ref*{lemma:smooth_agg_lyapunov_upper_bound}, With $x_{t +1} - x_t = L\tilde\eta_{t+1}(z_{t + 1} - y_t)$ for $y_t$: 
+            \begin{align*}
+                \Upsilon_{1, t + 1}^\text{AG} &\le 
+                - \frac{1}{2}\Vert x_{t+1 } - x_t\Vert^2 + 
+                \frac{\tilde\eta_{t +1}L}{2}\Vert z_{t+1} - y_t\Vert^2
+                \\
+                &= 
+                - \frac{1}{2}\Vert L \tilde \eta_{t+} (z_{t+1} - y_t)\Vert^2 + 
+                \frac{\tilde\eta_{t +1}L}{2}\Vert z_{t+1} - y_t\Vert^2
+                \\
+                &= 
+                \left(
+                    \frac{L^2\tilde\eta_{t + 1}^2}{2}
+                    + 
+                    \frac{\tilde \eta_{t +1}}{2}
+                \right)
+                \Vert z_{t+1} - y_t\Vert^2
+                - 
+                \langle 
+                    \tilde \eta_{t+ 1} \nabla f(y_t), x_{t+1} - z_{t+1}
+                \rangle. 
+            \end{align*}
+            This completes the analysis for $\Upsilon_{1, t + 1}^\text{AG}$ with $\tilde\eta_{t+1}$. 
+            Next we consider 
+            \begin{align*}
+                \Upsilon_{2, t + 1}^{\text{AG}} &= 
+                \langle \nabla f(y_t), z_{t+1} - y_t\rangle
+                + 
+                \frac{L }{2} \Vert z_{t+1} - y_t\Vert^2 + 
+                \langle \nabla f(y_t), y_t - z_t\rangle
+                \\
+                &= 
+                \langle \nabla f(y_t), z_{t + 1} - z_t\rangle
+                + 
+                \frac{L }{2} \Vert z_{t+1} - y_t\Vert^2
+                \\
+                &= 
+                \langle \nabla f(y_t), L^{-1}\eta_t^{-1}(x_{t+1} - z_{t + 1})\rangle
+                + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
+            \end{align*}
+            Here we used $x_{t + 1} = z_{t + 1} + L\eta_t (z_{t + 1} - z_t)$, which was the consequence of $\tilde\eta_{t + 1} = \eta_t + L^{-1}$, as discussed from before. 
+            Hence, the upper bound of the Lyapunov function for smooth AG PPM 
+            (\hyperref[thm:generic_smooth_ag_convergence]{theorem \ref*{thm:generic_smooth_ag_convergence}}) 
+            has 
+            \begin{align*}
+                & \Upsilon_{1, t + 1}^{\text{AG}} + 
+                \left(
+                    \sum_{i = 1}^{t}\tilde \eta_i
+                \right)\Upsilon_{2, t + 1}^{\text{AG}}
+                \\
+                &\quad \le 
+                \left(
+                    - \frac{L^2\tilde \eta_{t + 1}^2}{2}
+                    + \frac{\tilde\eta_{t+1}L}{2}
+                \right)
+                \Vert z_{t+1} - y_t\Vert^2
+                - 
+                \langle \tilde \eta_{t+1} \nabla f(y_t), x_{t+1} - z_{t + 1}\rangle
+                \\
+                & \qquad + 
+                \left(
+                    \sum_{i = 1}^{t}\tilde \eta_i
+                \right)\left(
+                    \langle \nabla f(y_t), L^{-1}\eta_t^{-1}(x_{t+1} - z_{t + 1})\rangle
+                    + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                \right). 
+            \end{align*}
+            If the above quantity less than or equal to zero, it will allow for convergence of the algorithm. 
+            One sufficient condition is to have the coefficients for all the cross product terms to sum up to zero, and the squared normed term to sum up to a non-positive number for all $t \in \mathbb N$.
+            This gives relations 
+            \begin{align*}
+                - \frac{1}{2}\left(
+                    L^2 \tilde\eta_{t+1}^2 - \tilde\eta_{t+1}L 
+                \right) + 
+                \frac{L}{2}\left(
+                    \sum_{i = 1}^{t} \tilde \eta_i
+                \right) &\le 0
+                \\
+                - \left(
+                    L\tilde \eta_{t + 1}^2 
+                    - 
+                    \tilde\eta_{t + 1}
+                \right) + 
+                \sum_{i = 1}^{t}\tilde \eta_i 
+                &\le 0
+                \\
+                -L \tilde \eta_{t+1} + 
+                \sum_{i = 1}^{t + 1} \tilde \eta_i 
+                &\le 0
+                \\
+                \sum_{i = 1}^{t + 1}\tilde \eta_i 
+                &\le L \tilde \eta_{t + 1}^2, 
+            \end{align*}
+            and equations 
+            \begin{align*}
+                -\tilde \eta_{t + 1} + 
+                \left(
+                    \sum_{i = 1}^{t}\tilde \eta_i
+                \right)L^{-1}\eta_t^{-1} 
+                &= 0
+                \\
+                \sum_{i = 1}^{t}\tilde \eta_i 
+                &= 
+                L \eta_t \tilde \eta_{t + 1}. 
+            \end{align*}
+            Susbtituting the equality into the inequalites we have 
+            \begin{align*}
+                \tilde \eta_{t + 1} + \sum_{i = 1}^{t} \tilde \eta_i 
+                &\le L \tilde \eta_{t + 1}^2
+                \\
+                \tilde \eta_{t + 1} + L\eta_t \tilde \eta_{t + 1}
+                &\le L \tilde \eta_{t + 1}^2
+                \\
+                1 + L\eta_t &\le L \tilde\eta_{t + 1}. 
+            \end{align*}
+            The choice $\tilde \eta_{t + 1} = \eta_t + L^{-1}$ makes the inequality is an equality. 
+            Finally, to recover the momentum stepsizes for the classical Nesterov accelerated gradient, we consider relations 
+            \begin{align*}
+                L \sum_{i = 1}^{t + 1} \tilde \eta_i 
+                &= L \tilde \eta_{t + 1} + L \sum_{i = 1}^{t} \tilde \eta_i 
+                \\
+                &= 
+                L \tilde \eta_{t + 1} + L (L \eta_t \tilde \eta_{t + 1}) 
+                \\
+                &= L \tilde \eta_{t + 1} + L \eta_t (L \eta_t + 1)
+                \\
+                &= L (\eta_t + L^{-1}) + L\eta_t (L \eta_t + 1)
+                \\
+                &= (L\eta_t + 1)^2, 
+            \end{align*}
+            Simultanenously 
+            \begin{align*}
+                L \sum_{i = 1}^{t + 1} \tilde \eta_i 
+                &= L^2 \eta_{t + 1} \tilde \eta_{t + 1}
+                \\
+                &= L \eta_{t + 1}(1+ L \eta_{t + 1}), 
+            \end{align*}
+            Combining yeilds that 
+            \begin{align*}
+                (L\eta_t + 1)^2 
+                &= L\eta_{t + 1}(1 + L \eta_{t + 1})
+                \\
+                &= L\eta_{t + 1} + L^2 \eta_{t + 1}^2
+                \\
+                \iff 
+                (L\eta_t + 1)^2 + 1/4 &= 
+                1/4 + 2(1/2)L \eta_{t + 1} + (L \eta_{t + 1})^2
+                \\
+                \iff 
+                (L\eta_t + 1)^2 + 1/4 &= 
+                (L \eta_{t + 1} + 1/2)^2. 
+            \end{align*}
+            With $a_t = L\eta_t + 1 = L \tilde \eta_t$ this is 
+            \begin{align*}
+                a_t^2 + 1/4 &= (a_{t + 1} - 1/2)^2 
+                \\
+                a_t^2 + 1/4 &= a_{t + 1}^2 + 1/4 - a_{t + 1}
+                \\
+                a_t^2 + a_{t + 1} &= a_{t + 1}^2. 
+                \\
+                \implies 
+                a_{t + 1} &= 
+                \frac{1 + \sqrt{1 + 4a_t^2}}{2}
+            \end{align*}
+            And that is the updates for the Nesterov momentum, recall that the momentum term is linked to the PPM sequence via relation 
+            \begin{align*}
+                (1 + L \eta_{t+ 1})^{-1}L\eta_t = L\eta_t / a_{t + 1} = (a_t - 1)/a_{t + 1}. 
+            \end{align*}
+            We had recovered the classic Nesterov accelerated sequence method for the smooth gradient descent algorithm. 
+        \end{proof}
+        \begin{remark}
+            This variant is distinct from the variants proposed by Chambolled \cite{chambolle_convergence_2015}, but both of which fits into the same frameworks. 
+            At the time of writing, the writer is still investigating the relations between these variants of algorithms.. 
+        \end{remark}
 

### 2024-06-20 Notebook LaTEX/Momentum Accelerations/main.tex
>w< Latex note book upated

@@
     They can be made into papers, proposals, and a thesis in the future. 
+    They are tayped in \LaTeX\; so it's easier to work with. 
 \end{abstract}
@@
 
+\pagebreak
+\tableofcontents
+\pagebreak
 % ==============================================================================
@@
         With the choice of $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we can recover the seminal Nesterov accelerated gradient algorithm from 1983. 
-        We will discuss how other choices of $\tilde \eta_{t +1}$ results in other varients of the Accelerated gradient such as the variants proposed by Chambolle \cite{chambolle_convergence_2015}. 
+        The variants proposed by Chambolle Dossal \cite{chambolle_convergence_2015}, is distinct from the possibility proposed in this secenario. 
         \par\noindent
@@
                 \item 
-                The updates for $z_{t + 1}, x_{t + 1}$ are based on $y_t, x_t$, therefore vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$. 
+                The updates for $z_{t + 1}, x_{t + 1}$ are based on $y_t, x_t$ displaced by $L^{-1}\nabla f(y_t), \tilde\eta_{t +1}\nabla f(y_t)$, therefore vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$.
                 \item The updates for $x_{t + 1}$ has $x_{t + 1} - z_{t + 1} = L\eta_t \left(z_{t + 1} - z_t\right)$, therefore, the three points $z_t, x_{t + 1}, z_{t + 1}$ are collinear. 
@@
         \begin{remark}
-            This variant is distinct from the variants proposed by Chambolled \cite{chambolle_convergence_2015}, but both of which fits into the same frameworks. 
-            At the time of writing, the writer is still investigating the relations between these variants of algorithms.. 
+            This variant is distinct from the variants proposed by Chambolle \cite{chambolle_convergence_2015}, but both of which fits into the same frameworks. 
+            The variantis presented as 
+            \begin{align*}
+                y_n &= (1 - t_n^{-1})z_n + t_n^{-1} x_n
+                \\
+                z_{n + 1} &= y_n - L^{-1}\nabla f(y_n)
+                \\
+                x_{n + 1} &= z_n + t_{n + 1}(z_{n + 1} - z_n)
+            \end{align*}
+            They listed the choice of $t_n = (n + a - 1)/a$ for all $a > 2$. 
+            Under this choice, unfortunately, it's in no way obvious that this format reduces to \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
+            It fails the similar triangule description Without the explict representation $x_{n + 1} = z_n + \tilde\eta_{t + 1}\nabla f(y_t)$. 
+            \par\noindent
+            At the time of writing, we are still investigating the relations between these variants of algorithms.
         \end{remark}

### 2024-06-24 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, just sync

@@
     \subsection{Varieties of Nesterov accelerated gradient}
+        \subsubsection{AG Abstract Forms}
             In this section, we list different varieties of the Nesterov accelerated method. 
-        We present these varieties generically because these algorithms' forms are of interest.  
             \begin{definition}[AG Generic Original Form]\label{def:agg_original}
@@
             \begin{remark}
-            With $l_f(x, \bar x) = f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle$, then the above is equivalent to AG Generic Triangular form. 
+                This formulation of the Nesterov Accelerated gradient method is a second handed idea taken from Ahn \cite{ahn_understanding_2022}. 
+                It is claimed that this is an PPM formulation of a class of accelerated gradient method. 
             \end{remark}
@@
                 The parameter $\eta_t, \eta_{t + 1}$ are coming from the previous generic PPM. 
-            They are the same parameters for both algorithms. 
+                They are the same parameters for both algorithms and they are equivalent. 
+                This will be proved in the coming parts. 
             \end{remark}
@@
             \end{proof}
+        \subsubsection*{Specific Instances of Accelerated Gradient Method}
 
@@
         \end{proof}
+
+    \subsection{Specific Varieties of Accelerated Gradient Method}
+        In this section we state some specific variant of the Nesterov accelerated gradient method.
 

### 2024-06-25 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, a lot more notes added

@@
 \section{Accelerated gradient descent and PPM}
-    Recent works from Ahn \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
-    In his works, Ahn explored the interpretation of Nesterov acceleration via PPM. 
+    Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
+    Ahn explored the interpretation of Nesterov acceleration via PPM. 
     They proposed the idea of ``similar triangle" for unifying all varieties of Nesterov accelerated gradient. 

### 2024-07-02 Notebook LaTEX/Momentum Accelerations/main.tex
>w< updated latex, md notes

@@
     It is an application of Guler's work in the context of variance-reduction stochastic gradient algorithms for machine learning.
-    \par\noindent
-    In this section, we
-    \begin{enumerate}
-        \item State Nesterov accelerated gradient and their varieties, and point to the literature discussing them. 
-        \item Derive the Nesterov accelerated gradient. 
-        \item Derive the popular step size choices along with the convergence rate. 
-    \end{enumerate}
-    Some content will differ from Ahn's works because we hope to generalize these ideas for our own use.
 
@@
             In this section, we list different varieties of the Nesterov accelerated method. 
-            \begin{definition}[AG Generic Original Form]\label{def:agg_original}
+            \begin{definition}[Nestrov 2.2.7]\label{def:Nes2.2.7}
                 Let $f$ be a $L$ Lipschitz smooth and $\mu\ge 0$ strongly convex function. 
@@
                 This is in Nesterov's book \cite[(2.2.7)]{nesterov_lectures_2018}. 
+                For more context, the sequence $\alpha_k \in (0, 1)$ such that $\sum_{k = 1}^{\infty}\alpha_k = \infty$, and recursively we have $\lambda_{k + 1} = (1 - \alpha_k)\lambda_k$. 
+                the sequence $\lambda_k$ is called an Nesterov estimating sequence. 
                 It is the most generic algorithm in his book about accelerated gradient method. 
@@
 
-            \begin{definition}[AG Generic PPM Form]\label{def:agg_ppm}
-                With $f$ convex, the generic PPM form is formulated for strictly positive stepsizes $\tilde \eta_i,\eta_i$ such that: 
+            \begin{definition}[Ahn Sra 6.24]\label{def:agg_ppm}
+                With $f$ $\mu \ge 0$ strongly convex and $L$-Lipschitz smooth, the generic PPM form is formulated for strictly positive stepsizes $\tilde \eta_i,\eta_i$: 
                 \begin{align*}
                     x_{t + 1} &= \argmin_{x} \left\lbrace
-                    l_f(x; y_t) + \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
+                        l_f(x; y_t) 
+                        + 
+                        \frac{\mu}{2}\Vert x - y_t\Vert^2
+                        + 
+                        \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
                     \right\rbrace, 
@@
                 \end{align*}
-                where $l_f(x, \bar x)$ is a convex function satisfying
-                \begin{align*}
-                    l_f(x, \bar x) \le f(x) \le f(\bar x) + \frac{L}{2}\Vert x - \bar x\Vert^2. 
-                \end{align*}
             \end{definition}
             \begin{remark}
-                This formulation of the Nesterov Accelerated gradient method is a second handed idea taken from Ahn \cite{ahn_understanding_2022}. 
-                It is claimed that this is an PPM formulation of a class of accelerated gradient method. 
+                This algorithm is the same as algorithm (6.24) described by Ahn and Sra \cite{ahn_understanding_2022}. 
+                Observe that by setting $\mu = 0, \tilde \eta_{t + 1} = \eta_{t + 1}$ this recovers algorithm (4.8) described in Ahn and Sra \cite{ahn_understanding_2022}. 
             \end{remark}
 
-            \begin{definition}[AG Generic Triangular Form]\label{def:agg_tri}
-                With $f$ be $L$-Lipschitz smooth and $\mu \ge 0$  strongly convex, choose any $y_0 = x_0=z_0$, the algorithm admits form: 
+            \begin{definition}[Tri-points Generic Form]\label{def:agg_tri}
+                With $f$ be $L$-Lipschitz \\ 
+                smooth and convex, choose any $y_0 = x_0=z_0$ and a non-negative sequence $\eta_t, \tilde\eta_t$, the algorithm admits form: 
                 \begin{align*}
@@
             \begin{remark}
-                The parameter $\eta_t, \eta_{t + 1}$ are coming from the previous generic PPM. 
+                The parameter $\eta_t, \tilde\eta_{t + 1}$ are exactly the same as Ahn, Sra (6.24), but with the choice of $\mu = 0$. 
+                This form is not explictly stated by Ahn and Sra but it's trivial to realize its presence regardless. 
                 They are the same parameters for both algorithms and they are equivalent. 
@@
             \end{remark}
-
-            \begin{definition}[AG Generic PPM Form with Strong Convexity]\label{def:agg_ppm_scvx}
-                Let $f$ be convex and differentiable with Lipschitz gradient and $\mu\ge0$-strongly convex, define $l_f(x; y)$ to be a function such that for all $x, \bar x \in \RR^n$: 
-                \begin{align*}
-                l_f(x; \bar x) + \frac{\mu}{2}\Vert x - \bar x\Vert^2
-                \le f(x; \bar x) 
-                \le l_f(x; \bar x) + \frac{L}{2}\Vert x - \bar x\Vert^2, 
-                \end{align*}
-                then for all $x_0 \in \RR^n$, and let $y_0 = x_0$, define the following variants of PPM for function $f$. 
-                \begin{align*}
-                    x_{t + 1} &= \argmin_{x} \left\lbrace
-                    l_f(x; y_t) + \frac{\mu}{2}\Vert x - y_t\Vert^2 + \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
-                    \right\rbrace, 
-                    \\
-                    y_{t + 1} &= \argmin_{x} 
-                    \left\lbrace
-                        l_f(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
-                        \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
-                    \right\rbrace. 
-                \end{align*}
-                Here we assume that $\eta_{t + 1} > 0$ for all $t \in \NN$. 
+            \begin{definition}[Strongly Convex Tri-points Generic Form]
+                \quad 
+                With $f$ being $L$-Lipschitz smooth and $\mu > 0$ strongly convex then the Strongly convex Tri-Points generic form has updates of for iterates
+                \begin{align*}
+                    x_{t + 1} &= (1 + \mu\tilde \eta_{t + 1})^{-1}(x_t + \mu\tilde\eta_{t + 1}y_t^+), 
+                    \\
+                    z_{t + 1} &= y_t - L^{-1}\nabla f(y_t), 
+                    \\
+                    y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}(x_{t + 1} + L\eta_{t + 1}z_{t +1}). 
+                \end{align*}
             \end{definition}
-            \begin{remark}
-                Set $\mu = 0$, the above is the same as AG Generid Triangular Form. 
-            \end{remark}
-
-            \begin{proposition}[Triangular Form via PPM Form]\label{prop:tri_form_via_ppm}
-                with $f$ being $L$-Lipschitz continuous, let $l_f(x, \bar x) = f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle$, we can show that the AG generic triangular form is a consequence of th AG generic PPM form.
+
+        \subsubsection*{Useful Observations about these Generic forms}
+            In this section we list some incredibaly useful information about these forms of the Nestrov type accelerated gradient algorithm. 
+            \hyperref[prop:tri_form_via_ppm]{Proposition \ref*{prop:tri_form_via_ppm}}, 
+            \hyperref[prop:tri_scvx_from_ahn_sra_6.24]{proposition \ref*{prop:tri_scvx_from_ahn_sra_6.24}}, 
+            \hyperref[prop:Nes2.2.7_via_ahn_sra_6.24]{proposition \ref*{prop:Nes2.2.7_via_ahn_sra_6.24}}
+            are results assumed as true in Ahn, Sra. 
+            They are implicitly left as necessary exercises for the readers. 
+            Here, we fill out the blanks with our own interpretations. 
+            \begin{proposition}[Tri-points generic form via Ahn Sra 6.24]
+                \label{prop:tri_form_via_ppm}
+                with $f$ being \\
+                $L$-Lipschitz continuous, 
+                let $l_f(x, \bar x) = f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle$, we can show that the AG generic triangular form is a consequence of th AG generic PPM form. 
             \end{proposition}
@@
             \end{proof}
-        \subsubsection*{Specific Instances of Accelerated Gradient Method}
+            \begin{remark}
+                It is quite obvious to us that the choice of $z_{t + 1} = y_t - L^{-1}\nabla f(y_t)$ is deliberate. 
+                In fact, it's true that $z_{t + 1}$ is just a term such that it makes $y_{t +1}$ a convex combination between the vector $x_{t + 1}, z_{t + 1}$, and the choice here would be unique because of the consideration that
+                {\footnotesize
+                \begin{align*}
+                    & \quad 
+                    l_f(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 
+                    \\
+                    &= 
+                    f(y_t) + \langle \nabla f(y_t), x - y_t\rangle 
+                    + 
+                    \frac{L}{2}
+                    \left\Vert 
+                        x - (y_t - L^{-1}\nabla f(y_t)) - L^{-1}\nabla f(y_t)
+                    \right\Vert^2
+                    \\
+                    &= 
+                    f(y_t) + 
+                    \langle \nabla f(y_t), x - (y_t - L^{-1}\nabla f(y_t)) - L^{-1}\nabla f(y_t)\rangle 
+                    + 
+                    \frac{L}{2}
+                    \left\Vert 
+                        x - (y_t - L^{-1}\nabla f(y_t)) - L^{-1}\nabla f(y_t)
+                    \right\Vert^2
+                    \\
+                    &\quad  \text{Let }z_{t + 1} 
+                    = y_t - L^{-1}\nabla f(y_t)
+                    \\
+                    &= f(y_t) + \langle \nabla f(y_t), x - z_{t + 1} - L^{-1}\nabla f(y_t)\rangle
+                    + 
+                    \frac{L}{2}\left\Vert
+                        x - z_{t + 1} - L^{-1}\nabla f(y_t)
+                    \right\Vert^2
+                    \\
+                    &= 
+                    f(y_t) + \langle \nabla f(y_t), x - z_{t + 1}\rangle 
+                    - L^{-1}\Vert \nabla f(y_t)\Vert^2
+                    + 
+                    \frac{L}{2}\Vert x - z_{t + 1}\Vert^2 + 
+                    \frac{1}{2L}\Vert \nabla f(y_t)\Vert^2 - 
+                    L\langle L^{-1}\nabla f(y_t), x - z_{t + 1}\rangle
+                    \\
+                    &= f(y_t) + (1/(2L)- L^{-1})\Vert \nabla f(y_t) \Vert^2 + 
+                    \frac{L}{2}\Vert x - z_{t + 1}\Vert^2
+                    \\
+                    &= f(y_t) - \frac{1}{2L}\Vert \nabla f(y_t)\Vert^2 + \frac{L}{2}\Vert x - z_{t + 1}\Vert^2. 
+                \end{align*}
+                }
+                Therefore 
+                \begin{align*}
+                    y_{t + 1} &= \argmin_{x}\left\lbrace
+                        \frac{L}{2}\Vert x - z_{t + 1}\Vert^2 + 
+                        \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
+                    \right\rbrace
+                    \\
+                    &= \argmin_{x}\left\lbrace
+                        \left\Vert x - 
+                            \frac{Lz_{t + 1} + \eta_{t + 1}^{-1}x_{t + 1}}{
+                                L + \eta_{t + 1}^{-1}
+                            }
+                        \right\Vert^2
+                    \right\rbrace
+                    \\
+                    &= 
+                    \frac{
+                        L\eta_{t + 1}z_{t + 1} + 
+                        x_{t + 1}
+                    }{
+                        1 + L \eta_{t + 1}
+                    }. 
+                \end{align*}
+            \end{remark}
+
+            \begin{proposition}[Tripoints Strongly Convex Form via Ahn Sra 6.24]\label{prop:tri_scvx_from_ahn_sra_6.24}
+                Coninue \\ 
+                from \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} with but with $\mu > 0$, under the same set of assumptions it recovers a tri-points algorithm with the following updates: 
+                \begin{align*}
+                    y_t^+ &= y_t - \mu^{-1}\nabla f(y_t)
+                    \\
+                    x_{t + 1} &= \argmin_{x} 
+                    \left\lbrace
+                        l_f (x; y_t) + \frac{\mu}{2} \Vert x - y_t\Vert^2 + 
+                        \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2 
+                    \right\rbrace
+                    \\
+                    &= \argmin_{x}
+                    \left\lbrace
+                        f(y_t) - \frac{1}{2\mu} \Vert \nabla f(y_t)\Vert^2 
+                        + 
+                        \frac{\mu
+                        }{2}\Vert x - y_t^+\Vert^2
+                        + 
+                        \frac{1}{2\tilde \eta_{t + 1}}\Vert x - x_t\Vert^2
+                    \right\rbrace
+                    \\
+                    &= (1 + \mu\tilde \eta_{t + 1})^{-1}
+                    \left(
+                        x_t + \mu \tilde \eta_{t + 1}y_t^{+}
+                    \right)
+                    \\
+                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t)
+                    \\
+                    y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}(x_{t + 1} + L \eta_{t + 1} z_{t + 1})
+                \end{align*}
+            \end{proposition}
+            \begin{proof}
+                By a similar argument made in the remarks of \hyperref[prop:tri_form_via_ppm]{proposition \ref*{prop:tri_form_via_ppm}} we have 
+                \begin{align*}
+                    l_f(x; y_t) + \frac{\mu}{2}\Vert x - y_t\Vert^2
+                    &= 
+                    f(y_t) - \frac{1}{2\mu}\Vert \nabla f(y_t)\Vert^2 + \frac{\mu}{2}\Vert x - y_t^+\Vert^2
+                    \\
+                    \implies 
+                    x_{t + 1} &= 
+                    \argmin{x} 
+                    \left\lbrace
+                        f(y_t) - \frac{1}{2\mu}\Vert \nabla f(y_t)\Vert^2 + \frac{\mu}{2}\Vert x - y_t^+\Vert^2
+                        + 
+                        \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
+                    \right\rbrace
+                    \\
+                    &= 
+                    \argmin{x}
+                    \left\lbrace
+                        \frac{\mu}{2}\Vert x - y_t^+\Vert^2 + 
+                        \frac{2}{\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
+                    \right\rbrace
+                    \\
+                    &= (\mu + \tilde \eta_{t + 1})^{-1}
+                    (\mu y_t^+ + \tilde \eta_{t + 1}x_t)
+                    \\
+                    &= (1 + \tilde \eta_{t + 1}\mu)^{-1}
+                    (x_t + \mu\tilde \eta_{t + 1}y_t^+). 
+                \end{align*}
+                The updates for $y_{t + 1}, z_{t + 1}$ is the same as before because $\mu > 0$ only alters the update of the term $x_{t + 1}$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}. 
+            \end{proof}
+
+            \begin{proposition}[Nestrov 2.2.7 is Equivlant to Ahn Sra 6.24 in Form]
+            \label{prop:Nes2.2.7_via_ahn_sra_6.24}
+                The \hyperref[def:Nes2.2.7]{algorithm \ref*{def:Nes2.2.7}} is equivalent to \hyperref[def:agg_ppm]{\ref*{def:agg_ppm}} in form. 
+                So the updates for $y_{k + 1}, x_{k + 1}, v_{k + 1}$: 
+                \begin{align*}
+                    \text{find } &
+                    \alpha_k \in (0, 1) 
+                    \text{ s.t: } L\alpha_k^2 
+                    = (1 - \alpha_k)\gamma_k + \alpha_k \mu = \gamma_{k + 1} 
+                    \\
+                    y_k &= 
+                    \left(
+                        \gamma_k + \alpha_k \mu
+                    \right)^{-1} \left(
+                        \alpha_k \gamma_k v_k + \gamma_{k + 1}x_k
+                    \right)
+                    \\
+                    \text{find } & x_{k + 1} \text{ s.t: }
+                    f(x_{k + 1})
+                    = f(y_k) - (2L)^{-1}\Vert \nabla f(y_k)\Vert^2
+                    \\
+                    v_{k+1} &= 
+                    \gamma_{k + 1}^{-1} 
+                    \left(
+                        (1 - \alpha_k) \gamma_k v_k + 
+                        \alpha_k \mu y_k 
+                        - \alpha_k \nabla f(y_k)
+                    \right). 
+                \end{align*}
+                Is the same as $y_{t + 1}, z_{t + 1}, x_{t + 1}$ from below: 
+                \begin{align*}
+                    x_{t + 1} 
+                    & = 
+                    (1 + \tilde \eta_{t + 1}\mu)^{-1}
+                    (x_t + \mu\tilde \eta_{t + 1}y_t - \tilde \eta_{t + 1}\nabla f(y_t))
+                    \\
+                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t)
+                    \\
+                    y_{t + 1} &= 
+                    (1 + L\eta_{t + 1})^{-1}
+                    (x_{t + 1} + L \eta_{t + 1} z_{t + 1}).
+                \end{align*}
+                which is an equivalent representation of \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} as showned in \hyperref[prop:tri_scvx_from_ahn_sra_6.24]{propostion \ref*{prop:tri_scvx_from_ahn_sra_6.24}}.
+            \end{proposition}
+            \begin{proof}
+                We simplify the Nesterov form into the Strongly convex Generic Triangular Form. 
+                Consider update for $v_{k + 1}$ by substituting $\gamma_{k+1} = (1 - \alpha_k) \gamma_k + \alpha_k \mu$ as informed by the first step of the algorithm, we have 
+                \begin{align*}
+                    v_{k + 1} &= 
+                    ((1 - \alpha_k)\gamma_k + \alpha_k \mu)^{-1}
+                    \left(
+                        (1 - \alpha_k)\gamma_k v_k + \alpha_k \mu y_k - \alpha_k \nabla f(y_k)
+                    \right)
+                    \\
+                    &= ((1 - \alpha_k)\gamma_k + \alpha_k \mu)^{-1}
+                    (
+                        (1 - \alpha_k)\gamma_k v_k + \alpha_k \mu(y_k - \alpha_k \mu^{-1}\nabla f(y_k))
+                    )
+                    \\
+                    &= 
+                    \left(
+                        1 + \frac{\alpha_k \mu}{(1 - \alpha_k)\gamma_k}
+                    \right)^{-1}
+                    \left(
+                        v_k
+                        + 
+                        \left(
+                            \frac{\alpha_k \mu}{(1 - \alpha_k)\gamma_k} 
+                        \right)
+                        \left(
+                            y_k 
+                            - \alpha_k \mu^{-1}\nabla f(y_k)
+                        \right)
+                    \right). 
+                \end{align*}
+                Notice that the right hand size has the same form as $x_{t + 1}$. 
+                This is true by the observation that 
+                \begin{align*}
+                    x_{t + 1} &= 
+                    (1 + \tilde\eta_{t + 1}\mu)^{-1}
+                    \left( 
+                        x_t + \mu\tilde \eta_{t + 1}
+                        \left(y_t - \mu^{-1}\nabla f(y_t)\right)
+                    \right). 
+                \end{align*}
+                Similarly, when $\mu = 0$, we have from the first step that $v_{k + 1} = v_k - \alpha_k \nabla f(y_k)$, which is the same as the AG generic PPM form where 
+                $$
+                    x_{t + 1} = x_t - \tilde \eta_{t + 1}\nabla f(y_t). 
+                $$
+                Next, we consider $y_{k}$ iterate of Nesterov 2.2.7. 
+                We want to write it as a convex combination of the vector $v_k,x_k$. 
+                To show that the updates $y_k$ can are of the same form, start by considering that 
+                \begin{align*}
+                    \gamma_{k + 1 } &= (1 - \alpha_k)\gamma_k + \alpha_k \mu
+                    \\
+                    &= (\gamma_k + \alpha_k \mu) - \alpha_k \gamma_k, 
+                \end{align*}
+                with the grouping we have
+                \begin{align*}
+                    y_k &= \left(
+                        \gamma_k + \alpha_k \mu
+                        \right)^{-1} \left(
+                            \alpha_k \gamma_k v_k + \gamma_{k + 1}x_k
+                        \right)
+                    \\
+                    &= 
+                    \left(
+                        \gamma_k + \alpha_k \mu
+                    \right)^{-1}
+                    \left(
+                        \alpha_k \gamma_k v_k 
+                        + 
+                        ((\gamma_k + \alpha_k\mu) - \alpha_k\gamma_k)x_k
+                    \right)
+                    \\
+                    &= 
+                    \left(
+                        \frac{\alpha_k \gamma_k}{\gamma_k + \alpha_k \mu}
+                    \right)v_k
+                    + 
+                    \left(
+                        1 - \frac{\alpha_k\gamma_k }{\gamma_k + \alpha_k \mu}
+                    \right)x_k, 
+                \end{align*}
+
+                which is indeed, a convex combination of $v_k, x_k$, if, we assume that $(\alpha_k\gamma_k)(\gamma_k + \alpha_k \mu)^{-1}$ is in the interval $(0, 1)$. 
+                We can assume it by considering $\gamma_k = L\alpha_{k-1}^2$, simplifying so that 
+                \begin{align*}
+                    \frac{\alpha_k \gamma_k}{\gamma_k + \alpha_k \mu}
+                    &= 
+                    \frac{L\alpha_k \alpha_{k - 1}^2}{L\alpha_{k - 1}^2 + \mu \alpha_k}
+                    \\
+                    &= \frac{\alpha_k \alpha_{k - 1}^2}{1 + q_f \alpha_k \alpha_{k - 1}^{-2}} \in (0, 1), 
+                \end{align*}
+                where $q_f = \mu / L \in (0, 1)$ and we recall the fact that the sequence $(\alpha_k)_{k \in \NN}$ has $\alpha_k \in (0, 1)$ and $\sum_{i = 1}^{\infty} \alpha_k = \infty$. 
+                However, it would require more works to express $\eta_t, \tilde\eta$ from Ahn Sra 6.24 using $\gamma_k, \alpha_k$ from Nesterov 2.2.7. 
+            \end{proof}
 
@@
             $$
-            performing PPM on the function produces the PPM Lyapunov inequality, substituting yields equivalences for all $x_*$: 
+            performing PPM on $\phi_t$ produces the PPM Lyapunov inequality from 
+            \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}},
+            substituting yields equivalences for all $x_*$: 
             {\footnotesize

### 2024-07-04 Notebook LaTEX/Momentum Accelerations/main.tex
>w< good stuff are coming

@@
     Their analysis results in relatively simple arguments that exhibits powerful extensions to several variants of the Nesterov accelerated gradient.
+
     \par\noindent
@@
 
-    \subsection{Varieties of Nesterov accelerated gradient}
+    \par\noindent
+    \textcolor{red}{We state our contributions}. 
+    In \hyperref[sec:AG_varieties]{section \ref*{sec:AG_varieties}} 
+    We stated different forms of accelerated gradient that appeared in the literatures and the equivalences between their forms. 
+    They are abstract because the choice of stepsize parameters in the algorithms are unspecified. 
+    In \hyperref[sec:AG_useful_information]{section \ref*{sec:AG_useful_information}}
+    we prove and interpret some of the unproved claims made by Ahn, Sra \cite{ahn_understanding_2022} as good exercises and for the peace of the mind.
+    \hyperref[lemma:smooth_agg_lyapunov_upper_bound]{Lemma \ref*{lemma:smooth_agg_lyapunov_upper_bound}} 
+    rephrase content in the appendix in work by Ahn, Sra\cite{ahn_understanding_2022}. 
+    It is our attempt at rephrasing the proofs to create a layer of abstraction so it can be reused for multiple proofs for several variants.
+
+    \subsection{Preliminaries}
+        We introduce some additional lemma that are crucial to the derivations of non-smooth accelerated gradient method. 
+        \begin{definition}[The Gradient Mapping]
+            \label{def:gradient_mapping}
+            Let $g = f + g$ where $f$ is $L$-Lipschitz smooth and convex, $g$ is convex. 
+            Define the proximal gradient operator
+            $$
+                \mathcal T_L(x) := \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)),
+            $$
+            then the gradient mapping is defined as
+            $$
+                \mathcal G_L(x) = L(x - \mathcal T_L(x)). 
+            $$
+        \end{definition}
+        \begin{remark}
+            The name "gradient mapping" comes from \cite[(2.2.54)]{nesterov_lectures_2018}, however, Nesterov was referring to only the case when $g$ is an indicator function of a convex set in his writing.
+        \end{remark}
+
+        \begin{lemma}[Gradient Mapping Approximates Subgradient]
+            \label{lemma:grad_map_lemma_first}
+            Continue from 
+            \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}, 
+            the gradient mapping satisfies
+            \begin{align*}
+                x^+ &= \mathcal T_L(x), 
+                \\
+                L(x - x^+) &\in  \nabla f(x) + \partial g(x^+) \ni \mathcal G_L(x). 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            \begin{align*}
+                x^+ &= [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f](x)
+                \\
+                [I + L^{-1}\partial g](x^+) &\ni [I - L^{-1}\nabla f](x)
+                \\
+                x^+ + L^{-1}\partial g(x^+) &\ni x - L^{-1}\nabla f(x)
+                \\
+                x^+ - x + L^{-1}\partial g(x^+) &\ni L^{-1}\nabla f(x)
+                \\
+                L(x^+ - x) + \partial g(x^+) &\ni - \nabla f(x)
+                \\
+                L(x - x^+) &\in \nabla f(x) + \partial g(x^+)
+                \\
+                \mathcal G_L(x) &\in \nabla f(x) + \partial g(x^+). 
+            \end{align*}
+        \end{proof}
+
+        \begin{lemma}[Linearized Gradient Mapping Lower Bound]
+            Continue from 
+            \hyperref[lemma:grad_map_lemma_first]{definition \ref*{lemma:grad_map_lemma_first}}, 
+            with $x^+ = \mathcal T(x)$, the gradient mapping satisfies the inequality for all $z$: 
+            \begin{align*}
+                h(z) &\ge
+                h(z) - \frac{L}{2}\Vert x - x^+\Vert^2
+                \ge h(x^+) + \langle \mathcal G_L(x), z - x\rangle. 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            Directly from the $L$-smoothness of $f$, convexity of $g, f$, we have the list of inequalities: 
+            \begin{align*}
+                &f(x^+) \le 
+                f(x) + \langle \nabla f(x), x^+ - x\rangle
+                + \frac{L}{2}\Vert x - x^+\Vert^2, 
+                \\
+                &f(x) + \langle \nabla f(x), z - x\rangle 
+                \le f(z), 
+                \\
+                &g(x^+) \le 
+                g(z) + \langle \partial g(x^+), x^+ - z\rangle. 
+            \end{align*}
+        \end{proof}
+
+    \subsection{Varieties of Nesterov accelerated gradient}\label{sec:AG_varieties}
+        Here, the acrynonym: ``AG" stands for accelerated gradient. 
         \subsubsection{AG Abstract Forms}
@@
 
+            \begin{definition}[AG Proximal Gradient PPM Generic Form]
+
+            \end{definition}
+
             \begin{definition}[Tri-points Generic Form]\label{def:agg_tri}
@@
 
-        \subsubsection*{Useful Observations about these Generic forms}
+        \subsubsection*{Useful Observations about these Generic forms}\label{sec:AG_useful_information}
             In this section we list some incredibaly useful information about these forms of the Nestrov type accelerated gradient algorithm. 
@@
                 with $f$ being \\
-                $L$-Lipschitz continuous, 
+                $L$-Lipschitz smooth, 
                 let $l_f(x, \bar x) = f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle$, we can show that the AG generic triangular form is a consequence of th AG generic PPM form. 
@@
                 \end{align*}
-                Similarly, when $\mu = 0$, we have from the first step that $v_{k + 1} = v_k - \alpha_k \nabla f(y_k)$, which is the same as the AG generic PPM form where 
+                Similarly, when $\mu = 0$, we have from the first step that 
+                \begin{align*}
+                    v_{k + 1} 
+                    &= ((1 - \alpha_k)\gamma_k)^{-1}
+                    (
+                        (1 - \alpha_k)\gamma_k v_k
+                        + \alpha_k \mu y_k - \alpha_k \nabla f(y_k)
+                    )
+                    \\
+                    &= 
+                    v_k - \alpha_k((1 - \alpha_k)\gamma_k)^{-1}\nabla f(y_k)
+                \end{align*}
+                which is the same as the AG generic PPM form where 
                 $$
@@
             $$
-            performing PPM on $\phi_t$ produces the PPM Lyapunov inequality from 
-            \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}},
+            the AG generic performs PPM on $\phi_t$ to produce $x_{t + 1}$ so the PPM Lyapunov inequality from 
+            \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} applies,
             substituting yields equivalences for all $x_*$: 
@@
                 - \frac{1}{2}\Vert x_* - x_t\Vert^2 
-                =: \Upsilon_{1, t + 1}^{\text{AG}}
                 \\
@@
                 \right) + \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2 
-                - \frac{1}{2}\Vert x_{t} - x_*\Vert^2 
+                - \frac{1}{2}\Vert x_{t} - x_*\Vert^2  =: \Upsilon_{1, t + 1}^{\text{AG}}
                 \\
@@
                     \sum_{i = 1}^{t} \tilde \eta_i
-                \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{2, t + 1}^{\text{AG}} \le 0, 
+                \right)
+                \Upsilon_{2, t + 1}^{\text{AG}} + 
+                \Upsilon_{1, t + 1}^{\text{AG}} \le 0, 
             \end{align*}
@@
                 \Phi_t &= \left(
-                    \sum_{i = 1}^{t} \tilde\eta_{t + 1}
+                    \sum_{i = 1}^{t} \tilde\eta_{i}
                 \right) (f(z_t) - f(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \NN
@@
                     \sum_{i = 1}^{t} \tilde \eta_i
-                \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{2, t + 1}^{\text{AG}} \le 0. 
+                \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le 0. 
             \end{align*}
@@
         In this section we state some specific variant of the Nesterov accelerated gradient method. 
+        The "AG" stands for accelerated gradient.
 

### 2024-07-04 Notebook LaTEX/Momentum Accelerations/main.tex
>w< minor edits

@@
         \begin{lemma}[Linearized Gradient Mapping Lower Bound]
+        \label{lemma:grad_map_linearization}
             Continue from 
@@
             \end{align*}
+            Now, consider adding $g(x^+)$ to the first inequality from above we get 
+            {\footnotesize 
+            \begin{align*}
+                f(x^+) + g(x^+) 
+                &\le 
+                f(x) + g(x^+) + \langle \nabla f(x), x^+ - x\rangle 
+                + \frac{L}{2}\Vert x - x^+\Vert^2
+                \\
+                &\le 
+                (f(z) - \langle \nabla f(x), z - x\rangle) + 
+                \left(g(z) - \langle \partial g(x^+), x^+ - z\rangle\right)
+                + 
+                \langle \nabla f(x), x^+ - x\rangle + \frac{L}{2}\Vert x - x^+\Vert^2
+                \\
+                &= f(z) + g(z) + \langle \nabla f(x), x - z + x^+ - x\rangle
+                + 
+                \langle \partial g(x^+), x^+ - z\rangle + \frac{L}{2}\Vert x - x^+\Vert^2
+                \\
+                &= 
+                h(z) + \langle \nabla f(x), x^+ - z\rangle + 
+                \langle \partial g(x^+), x^+ - z\rangle
+                + \frac{L}{2}\Vert x - x^+\Vert^2
+                \\
+                &= h(z) + \langle \nabla f(x) + \partial g(x^+), x^+ - z\rangle 
+                + \frac{L}{2}\Vert x - x^+\Vert^2. 
+            \end{align*}
+            }
+            By $\mathcal G_L(x) = L(x - x^+) \in \nabla f(x) + \partial g(x^+)$ from previous dicussion, we have 
+            \begin{align*}
+                h(x^+) &\le 
+                h(z) + \langle \mathcal G_L(x), x^+ - z\rangle + \frac{L}{2}\Vert x - x^+\Vert^2
+                \\
+                &= h(z) - \langle L(x^+ - x), x^+ - x + x - z \rangle 
+                + 
+                \frac{L}{2}\Vert x - x^+\Vert^2
+                \\
+                &= 
+                h(z) - L\Vert x^+ - x\Vert^2 
+                + L \langle x^+ - x, x - z\rangle
+                + \frac{L}{2}\Vert x - x^+\Vert^2
+                \\
+                &= h(z) + \langle \mathcal G_L(x), x - z\rangle - 
+                \frac{L}{2}\Vert x - x^+\Vert^2. 
+            \end{align*}
+            Therefore, the inequality is justified. 
         \end{proof}
+        \begin{remark}
+            Observe that the linearization $h(x^+) + \langle \mathcal G_L(x), z - x\rangle$ is anchored at $x^+$, instead of $x$. 
+            Geometrically, it's tilted and it "prefers" the sharp corners of a convex function, if, $x$ is close to a sharp corner. 
+        \end{remark}
 
@@
             \begin{definition}[AG Proximal Gradient PPM Generic Form]
-
+            \label{def:ag_prox_grad_ppm}
+                Let $h=f + g$ be the sum of convex function $g$ and convex differentiable $f$ with $L$-Lipschitz gradient. 
+                Define the proximal gradient and gradient mapping operator operator: 
+                $$
+                \begin{aligned}
+                    \mathcal T_L^{g, f}(x) &:=  
+                    \hprox_{L^{-1}g}\left(x - L^{-1}\nabla f(x)\right)
+                    \\
+                    &= 
+                    \argmin_{u}
+                    \left\lbrace
+                        g(u) + f(x) + \langle \nabla f(x), u - x\rangle
+                        + 
+                        \frac{L}{2}\Vert u - x\Vert^2
+                    \right\rbrace,
+                    \\
+                    \mathcal G_L^{g, f}(x) &= 
+                    L(x - \mathcal T_L^{g, f}(x)). 
+                \end{aligned}
+                $$
+                Omitting the superscript $f, g$ on $\mathcal P, \mathcal G$ for simplicity since it's clear in the context. 
+                Define the linear lower bounding function for $f$ at $y$, for all $x$: 
+                $$
+                \begin{aligned}
+                    l_h(x; y) &= h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle \le f(x), 
+                \end{aligned}
+                $$
+                With that we define the algorithm:
+                $$
+                \begin{aligned}
+                    x_{t + 1} &= \argmin_{x} \left\lbrace
+                        l_h(x; y_t) + \frac{1}{2\tilde \eta_{t + 1}} 
+                        \Vert x - x_t\Vert^2
+                    \right\rbrace,
+                    \\
+                    y_{t + 1}&= 
+                    \argmin_{x}
+                    \left\lbrace
+                        g(x) + l_f(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
+                        \frac{1}{2\eta_{t + 1}} \Vert x - x_{t + 1}\Vert^2
+                    \right\rbrace.
+                \end{aligned}
+                $$
             \end{definition}
@@
                     x_{t + 1} &= 
-                    \argmin{x} 
+                    \argmin_{x} 
                     \left\lbrace
@@
                     &= 
-                    \argmin{x}
+                    \argmin_{x}
                     \left\lbrace

### 2024-07-04 Notebook LaTEX/Momentum Accelerations/main.tex
>w< new notes updated

@@
         \begin{remark}
-            The name "gradient mapping" comes from \cite[(2.2.54)]{nesterov_lectures_2018}, however, Nesterov was referring to only the case when $g$ is an indicator function of a convex set in his writing.
+            The name ``gradient mapping" comes from \cite[(2.2.54)]{nesterov_lectures_2018}, however, Nesterov was referring to only the case when $g$ is an indicator function of a convex set in his writing.
+            Of course, in Amir Beck \cite[10.3.2]{beck_first-order_nodate}, it has the exact same definition for gradient mapping as the above. 
         \end{remark}
@@
             \hyperref[lemma:grad_map_lemma_first]{definition \ref*{lemma:grad_map_lemma_first}}, 
-            with $x^+ = \mathcal T(x)$, the gradient mapping satisfies the inequality for all $z$: 
+            with $x^+ = \mathcal T_L(x)$, the gradient mapping satisfies the inequality for all $z$: 
             \begin{align*}
@@
                     \mathcal G_L^{g, f}(x) &= 
-                    L(x - \mathcal T_L^{g, f}(x)). 
+                    L\left(x - \mathcal T_L^{g, f}(x)\right). 
                 \end{aligned}
@@
 
+            \begin{definition}[AG Proximal Gradient Tri-Points Generic Form]
+            \label{def:ag_prox_grad_tri_pt}
+                With $h = f + g$, where $g$ is convex, $f$ is convex and $L$-Lipschitz smooth. 
+                Define proximal gradient and gradient mapping operator 
+                $$
+                \begin{aligned}
+                    \mathcal T_L(x) 
+                    &:= \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)), 
+                    \\
+                    x^+ &= \mathcal T_L(x), 
+                    \\
+                    \mathcal G_L(x) 
+                    &:= L(x -  x^+). 
+                \end{aligned}
+                $$
+                Then the algorithm updates $(y_t, x_{t + 1}, z_{t + 1})$ with expression: 
+                $$
+                \begin{aligned}
+                    y_t^+ &= \mathcal T_L(y_t)
+                    \\
+                    y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
+                    \\
+                    x_{t + 1} &= x_t - \tilde \eta \mathcal G_L(y_t)
+                    \\
+                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
+                \end{aligned}
+                $$
+                where the base case has $y_0 = x_0$. 
+            \end{definition}
+            \begin{remark}
+                Observe that $z_{t + 1} = y_t^+$. 
+            \end{remark}
+
             \begin{definition}[Tri-points Generic Form]\label{def:agg_tri}
@@
             \begin{remark}
-                The parameter $\eta_t, \tilde\eta_{t + 1}$ are exactly the same as Ahn, Sra (6.24), but with the choice of $\mu = 0$. 
+                The parameter $\eta_t, \tilde\eta_{t + 1}$ are exactly the same as Ahn, Sra \cite[(6.24)]{ahn_understanding_2022}, but with the choice of $\mu = 0$. 
                 This form is not explictly stated by Ahn and Sra but it's trivial to realize its presence regardless. 
@@
 
-        \subsubsection*{Useful Observations about these Generic forms}\label{sec:AG_useful_information}
+        \subsubsection{Useful Observations about these Generic forms}
+        \label{sec:AG_useful_information}
             In this section we list some incredibaly useful information about these forms of the Nestrov type accelerated gradient algorithm. 
@@
 
-            \begin{proposition}[Tripoints Strongly Convex Form via Ahn Sra 6.24]\label{prop:tri_scvx_from_ahn_sra_6.24}
+            \begin{proposition}[Tri-points Strongly Convex Form via Ahn Sra 6.24]\label{prop:tri_scvx_from_ahn_sra_6.24}
                 Coninue \\ 
@@
         \begin{lemma}[Smooth Generic AG Lyapunov Analysis]\label{lemma:smooth_agg_lyapunov_upper_bound}
-            With $f$ having $L$-Lipschitz gradient and minimizer $x_*$, using \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} and \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} then these are the upper bounds for the RHS of the PPM descent inequality:
-            \begin{align*}
-                \Upsilon_{1, t + 1}^{\text{AG}}&= \tilde \eta_{t + 1} (f(z_{t + 1}) - f(x_*))
+            With $f$ having $L$-Lipschitz gradient and minimizer $x_*$, using 
+            \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} with $\mu = 0$
+            and 
+            \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} ,
+            then we can derive the upper bounds for the RHS of the PPM descent inequality: 
+            \begin{align*}
+                \Upsilon_{1, t + 1}^{\text{AG}}
+                &= \tilde \eta_{t + 1} (f(z_{t + 1}) - f(x_*))
                 + \frac{1}{2}(
@@
         \end{proof}
+
+        \begin{lemma}[Nonsmooth Generic AG Lyapunov Analysis]
+        \label{lemma:nsmooth_agg_lyapunov_upper_bound}
+
+        \end{lemma}
 
@@
         \begin{remark}
-            In this remark we clarify the name "similar triangule" as given in the literatures. 
+            In this remark we clarify the name ``similar triangule" as given in the literatures. 
             We think it is a fitting name, becaues it has a similar triangle in it. 

### 2024-07-07 Notebook LaTEX/Momentum Accelerations/main.tex
>w< small updates to the notes

@@
     \par\noindent
-    \textcolor{red}{We state our contributions}. 
+    \textbf{We state our contributions}. 
     In \hyperref[sec:AG_varieties]{section \ref*{sec:AG_varieties}} 
@@
                 $$
-                where the base case has $y_0 = x_0$. 
+                for all $t\in \mathbb N$ where the base case has $y_0 = x_0$. 
             \end{definition}
@@
 
+        \subsubsection{AG Concrete Examples}
+            In this section we state some variants of the Nesterov accelerated gradient method found in the literatures.
+
+            \begin{definition}[AG Ryu 12.1]
+            \label{def:ag_ryu_12.1}
+                State in chapter 12 in Ryu's writing \cite{ryu_large-scale_2022} is the following variant of accelerated gradient algorithm: 
+                \begin{align*}
+                    z_{t + 1} &= y_k + L^{-1}\nabla f(y_t), 
+                    \\
+                    y_{t + 1} &= z_{t + 1} + \frac{t - 1}{t + 2}\left(
+                        z_{k + 1} - z_k
+                    \right). 
+                \end{align*}
+                An equivalent form of the above is also provided by Ryu: 
+                \begin{align*}
+                    z_{t + 1} &= y_t + L^{-1}\nabla f(y_t), 
+                    \\
+                    x_{t + 1} &= x_t + (t + 1)(2L)^{-1}\nabla f(y_t), 
+                    \\
+                    y_{t + 1} &= \left(
+                        1 - \frac{2}{t + 2} 
+                    \right)z_{t + 1} + 
+                    \left(
+                        \frac{1}{t + 2}
+                    \right)x_{t + 1}. 
+                \end{align*}
+            \end{definition}
+            \begin{observation}
+                The base case requires cares since it's not unique, there are more representations  depending on how the base case is define, 
+                Observe that the second equivalent form is an example of \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
+                \par\noindent
+                It is stated in Ryu's writing that the base case is $x_0 = y_0 = z_0$, 
+                \textcolor{purple}{we think this is not the only options.} 
+                We remind the reader that there is not an obvious choice of $t\in \mathbb Z$ such that $x_t = y_t = z_t$ where the above algorithm remains consistent for all $t \ge -1$. 
+                The choice of base case presented in Ryu's writing is a choice and not a necessity. 
+                We state that one of the base case scenario that only requires knowing $y_1$.
+
+                \par\noindent 
+                We need to observe the case where $t = 0$ to understand the base case of the algorithm. 
+                At each iteration $t$, Given $(x_t, y_t)$, the above formula maps to $(x_{t + 1}, y_{t + 1}, z_{t + 1})$. 
+                When $t= 0$, it has $y_1 = x_1$. 
+                Therefore, knowing only either $y_1$, or $x_1$ can initiate the algorithm. 
+                This is an alternative scenario of the base case. 
+                If, we wish to write $y_0 = x_0$ at $t = 0$ for the base case instead, then it creates the following algorithm 
+                \begin{align*}
+                    y_{t} &= \left(
+                    1 - \frac{2}{t + 2} 
+                    \right)z_{t} + 
+                    \left(
+                        \frac{1}{t + 2}
+                    \right)x_{t}, 
+                    \\
+                    z_{t + 1} &= y_t + L^{-1}\nabla f(y_t), 
+                    \\
+                    x_{t + 1} &= x_t + (t + 1)(2L)^{-1}\nabla f(y_t). 
+                \end{align*}
+                It has a different representations due to a specific choice of the base case. 
+                \par\noindent
+                Finally, by the observation that given $(z_t, y_t)$ for any $t\ge -1$, we can solve for $x_t$ \newline via $y_t = (1 - 2/(1 + t))z_t + 1/(t + 1)x_t$, obtaining $(x_t, y_t, z_t)$, hence the algorithm can be reduced to a representations with only $(z_t, y_t)$ and an updates using only $(z_t, y_t)$ to $(z_{t + 1}, y_{t + 1})$.
+                That is the momentum form presented above. 
+            \end{observation}
+            \begin{remark}
+                We advise the reader to read the Biliography notes by Ryu \cite[chapter 12]{ryu_large-scale_2022} of his book. 
+                It goes over the full context and history for this particular variant of gradient acceleration method. 
+                As the time of composing this notes, the writer is still reading on the topic of accelerated gradient.     
+            \end{remark}
+
+            \begin{definition}[Form Zero]
+            \label{def:ag_form_zero}
+
+            \end{definition}
+
+            \begin{definition}[Similar Triangle Form I]
+            \label{def:ag_form_similar_tria_I}
+
+            \end{definition}
+
+            \begin{definition}[Similar Triangle Form II]
+            \label{def:ag_form_similar_tria_II}
+
+            \end{definition}
+
         \subsubsection{Useful Observations about these Generic forms}
         \label{sec:AG_useful_information}
+
             In this section we list some incredibaly useful information about these forms of the Nestrov type accelerated gradient algorithm. 
@@
             Here, we fill out the blanks with our own interpretations. 
+            \hyperref[prop:derive_ag_prox_grad_tript]{Proposition \ref*{prop:derive_ag_prox_grad_tript}} 
+            is our contribution where we intorduce non-smooth ness to the objective function while still retaining the PPM interpretation of accelerated gradient.
+
             \begin{proposition}[Tri-points generic form via Ahn Sra 6.24]
@@
 
+            \begin{proposition}[Deriving Proximal Gradient Tri-Points Generic Form]
+            \label{prop:derive_ag_prox_grad_tript}
+                \quad \\
+                Continue from the proximal point interpretation of the proximal gradient 
+                (\hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}})
+                we have the equalities 
+                \begin{align*}
+                    x_{t + 1} &= \argmin_{x}
+                    \left\lbrace
+                        l_h(x, y_t) + \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
+                    \right\rbrace
+                    \\
+                    &= x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+                    \\
+                    y_{t + 1} &= \argmin_{x}
+                    \left\lbrace
+                          h(y_t^+) + \langle \mathcal G_L(y_t), x - y_t\rangle + \frac{L}{2}\Vert x -y_t\Vert^2 + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
+                    \right\rbrace
+                    \\
+                    &= (1 + L\eta_{t + 1})^{-1}
+                    (x_{t + 1} + L\eta_{t + 1}(y_t - L^{-1}\mathcal  G_L(y_t))). 
+                \end{align*}
+                Therefore, the algorithm 
+                \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}
+                is equivalent to 
+                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
+            \end{proposition}
+            \begin{proof}
+                Let $y_t^+ = \mathcal T_L(y_t)$, recall that $l_h(x; y_t) = h(y_t^+) + \langle \mathcal G_L(y_t), x -y_t\rangle \le f(x)$ by the definition of algorithm. 
+                Since $l_h(x; y_t)$ is a simple linear function wrt $x$, it's not hard to minimize the quandratic where we can get $x_{t + 1} = x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t)$. 
+                For $y_{t + 1}$, observe that we can complete the square on the second and the third terms: 
+                \begin{align*}
+                    & \frac{L}{2}\left(
+                        2\langle L^{-1}\mathcal G_L(y_t), x - y_t\rangle + 
+                        \Vert x - y_t\Vert^2
+                    \right)
+                    \\
+                    &= 
+                    \frac{L}{2}
+                    \left(
+                        - \Vert L^{-1} \mathcal G_L(y_t)\Vert^2  
+                        + \Vert L^{-1} \mathcal G_L(y_t)\Vert^2 
+                        + 
+                        2\langle L^{-1} \mathcal G_L(y_t), x - y_t\rangle + 
+                        \Vert x - y_t\Vert^2
+                    \right)
+                    \\
+                    &= \frac{L}{2}\left(
+                        - \Vert L^{-1}\mathcal G_L(y_t)\Vert^2  
+                        + \Vert x - (y_t - L^{-1}\mathcal G_L(y_t))
+                        \Vert^2
+                    \right), 
+                \end{align*}
+                therefore it transforms into 
+                \begin{align*}
+                    y_{t + 1} &=\argmin_{x} \left\lbrace
+                        \frac{L}{2}\left\Vert 
+                            x - (y_t - L^{-1}\mathcal G_L(y_t))
+                        \right\Vert^2
+                        + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
+                    \right\rbrace
+                    \\
+                    &=
+                    \frac{(y_t - L^{-1}\mathcal G_L(y_t)) + x_{t + 1}}{L + \eta_{t + 1}^{-1}}.
+                \end{align*}
+                Define $z_{t + 1} = y_t - \mathcal G_L(y_t) = \mathcal T_L(y_t)$, which is the proximal gradient set, then the above expression simplifies to 
+                $$
+                y_{t + 1} = (1 + L\eta_{t +1})^{-1}(x_{t + 1}+ L\eta_{t + 1}z_{t + 1}). 
+                $$
+                As a sanity checks, notice that when 
+                $h \equiv 0$, 
+                $\mathcal G_L(x) = \nabla f(x)$ 
+                by definition, making it the same as 
+                \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
+            \end{proof}
+            \begin{remark}
+                $y_{t + 1}$ is the minimizer of a simple quadratic. 
+                Given that the original function $h$ is potentially non-smooth, therefore it's not always an upper bound of $h(x)$. 
+                The upper bound interpretation of the smooth case as proposed by Ahn, Sra for the update of $y_{t + 1}$ fails when $h$ is non-smooth! 
+            \end{remark}
+
     \subsection{Generic Lyapunov analysis for Accelerated gradient via PPM}
-        The first theorem states the generic convergence results when $f$ is differentiable with $L$-Lipschitz gradient, using \ref*{def:agg_ppm}. 
+        The first theorem states the generic convergence results when $f$ is differentiable with $L$-Lipschitz gradient, using \hyperref[def:agg_ppm]{definition\ref*{def:agg_ppm}}. 
         \begin{lemma}[Smooth Generic AG Lyapunov Analysis]\label{lemma:smooth_agg_lyapunov_upper_bound}
@@
         \label{lemma:nsmooth_agg_lyapunov_upper_bound}
-
+            Continue from 
+            \hyperref[prop:derive_ag_prox_grad_tript]
+            {definition \ref*{prop:derive_ag_prox_grad_tript}},
+            we derive the non-smooth analogous case of the Lyapunov upper bound: 
+            \begin{align*}
+                \Upsilon_{1, t + 1}^\text{AG}
+                &= 
+                \tilde\eta_{t + 1} (h(z_{t + 1}) - h(x_*)) + 
+                \frac{1}{2} (
+                    \Vert x_{t + 1} - x_*\Vert^2
+                    - 
+                    \Vert x_t - x_*\Vert^2
+                )
+                \\
+                &\le 
+                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+                + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                - \langle 
+                    \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+                    x_{t + 1} - z_{t + 1}
+                \rangle
+                \\
+                \Upsilon_{2, t + 1}^\text{AG}
+                &= 
+                h(z_{t + 1}) - h(z_t) 
+                \le 
+                \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
+                \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
+            \end{align*}
         \end{lemma}
+        \begin{proof}
+            Define 
+            \begin{align*}
+                \phi_t(u) &:= 
+                \tilde \eta_{t + 1} 
+                \left(
+                    f(y_t) + g(y_t) + \langle \nabla f(y_t) + \partial g(y_t^+), u - y_t\rangle
+                    + 
+                    \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
+                \right)\\
+                &= 
+                \tilde \eta_{t + 1} \left(
+                    f(y_t) + \langle \nabla f(y_t), u - y_t\rangle + 
+                    \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
+                    + 
+                    g(y_t) + \langle \partial g(y_t^+), u - y_t\rangle
+                \right). 
+            \end{align*}
+            Then the update in the Generic Tri-Point algorithm 
+            (\hyperref[def:ag_prox_grad_ppm]
+                {definition \ref*{def:ag_prox_grad_ppm}}) 
+            has $x_{t + 1} = \prox{\phi_t}(x_t)$ and therefore we can use the Lyapunov inequality for PPM (\hyperref[thm:ppm_descent_ineq]
+                {theorem \ref*{thm:ppm_descent_ineq}})
+            which gives for all $x_*$: 
+            \begin{align*}
+                & \phi_t(x_{t + 1}) - \phi_t(x_*) + 
+                \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
+                \frac{1}{2}\Vert x_t - x_*\Vert^2
+                \le \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2, 
+                \\
+                & \text{where }
+                \phi_t(x_{t + 1}) =
+                \\
+                & \quad 
+                \tilde \eta_{t + 1}
+                \left(
+                    f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle + 
+                    \frac{1}{2\tilde \eta_{t + 1}}\Vert x_{t + 1} - x_t\Vert^2
+                    + 
+                    g(y_t) + \langle \partial g(y_t^+), x_{t + 1} - y_t\rangle
+                \right). 
+            \end{align*}
+            to simplify, consider using the $L$-smoothness of $f$, we have the inequality: 
+            \begin{align*}
+                \begin{aligned}
+                    f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle
+                    &=
+                    f(y_t) + \langle \nabla f(y_t), (x_{t +1} - z_{t + 1}) + (z_{t + 1} - y_t) \rangle
+                    \\
+                    &\ge 
+                    f(z_{t + 1}) - \frac{L}{2} \Vert z_{t + 1} - y_t\Vert^2 + 
+                    \langle \nabla f(y_t), x_{t +1} - z_{t + 1}\rangle
+                    \\
+                    &= 
+                    f(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2
+                    + \langle \nabla f(y_t), x_{t + 1} - y_t^+\rangle.     
+                \end{aligned}
+                \tag{$[*]$}
+            \end{align*}
+            further consider
+            \begin{align*}
+                \begin{aligned}
+                    g(y_t) + \langle \partial g(y_t^+), x_{t + 1} - y_t\rangle 
+                    &= g(y_t) + 
+                    \langle \partial g(y_t^+), 
+                    x_{t + 1} - y_t^+ + y_t^+ - y_t
+                    \rangle
+                    \\
+                    &= g(y_t) 
+                    + \langle \partial g (y_t^+),
+                        x_{t + 1} - y_t^+
+                    \rangle
+                    + 
+                    \langle 
+                        \partial g(y_t^+), y_t^+ - y_t
+                    \rangle
+                    \\
+                    g \text{ convex }\implies 
+                    &\ge 
+                    g(y_t^+) + 
+                    \langle \partial g(y_t^+), x_{t + 1} - y_t^+\rangle. 
+                \end{aligned}
+                \tag{$[\star]$}
+            \end{align*}
+            In the $([\star])$ derivation, we used the convexity of $g$ where 
+            \begin{align*}
+                \langle \partial g(y_t^+), y_t - y_t^+\rangle
+                &\le g(y_t) - g(y_t^+)
+                \\
+                \langle \partial g (y_t^+), y_t^+ - y_t \rangle
+                &\le 
+                g(y_t^+) - g(y_t). 
+            \end{align*}
+            Now, adding $([*]), ([\star])$, multiply their sum by $\tilde\eta_{t + 1}$ makes it equals to $\phi_t(x_{t +1 })$ , we can establish a lower bound for $\phi_t(x_{t + 1})$, yielding inequality
+            {\small
+                \begin{align*}
+                    \phi_t(x_{t + 1})
+                    &\ge 
+                    \tilde\eta_{t + 1}
+                    \left(
+                        f(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2 
+                        +
+                        \langle \nabla f(y_t), x_{t + 1} - y_t^+\rangle
+                        + 
+                        g(y_t^+) + 
+                        \langle \partial g(y_t^+), x_{t + 1} - y_t^+\rangle
+                    \right) 
+                    \\
+                    &= 
+                    \tilde\eta_{t + 1}
+                    \left(
+                        h(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2 
+                        + 
+                        \langle \partial g(y_t^+) + \nabla f(y_t), x_{t + 1} - y_t^+\rangle
+                    \right).
+                \end{align*}
+            }
+            Apply
+            \hyperref[lemma:grad_map_lemma_first]{lemma \ref*{lemma:grad_map_lemma_first}} 
+            we have $\partial g(y_t^+) + \nabla f(y_t) \ni \mathcal G_L(y_t)$, and by the algorithm updates $y_t^+ = z_{t + 1}$, therefore the above inequality simplifies to 
+            \begin{align*}
+                \phi_t(x_{t + 1}) &\ge 
+                \tilde\eta_{t + 1} 
+                \left(
+                    h(z_{t + 1}) - 
+                    \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                    + 
+                    \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
+                \right). 
+            \end{align*}
+            Finally, from (\hyperref[lemma:grad_map_linearization]
+                {lemma \ref*{lemma:grad_map_linearization}})
+            we have $\phi_t(u) \le \tilde\eta_{t + 1}h(u)$ for all $u$. 
+            With that we lower bound the LHS of the PPM Lyapunov inequality of $\phi_t(u)$, making: 
+            {\footnotesize
+            \begin{align*}
+                & \phi_t(x_{t + 1}) - \phi_t(x_*) + 
+                \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
+                \frac{1}{2}\Vert x_t - x_*\Vert^2
+                \le
+                \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+                \\
+                \implies &
+                \tilde \eta_{t + 1}
+                \left(
+                    h(z_{t + 1}) - 
+                    \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                    + 
+                    \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
+                \right) - \tilde \eta_{t + 1} h(x_*)
+                +
+                \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
+                \frac{1}{2}\Vert x_t - x_*\Vert^2
+                \\
+                & \quad \le
+                \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+                \\
+                \iff &
+                \tilde\eta_{t + 1}(h(z_{t + 1}) - h(x_*))
+                + \frac{1}{2}\left(
+                    \Vert x_{t + 1} - x_*\Vert^2 
+                    - 
+                    \Vert x_t - x_*\Vert^2
+                \right) := \Upsilon_{1, t + 1}^\text{AG}
+                \\
+                &\quad \le 
+                \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+                - 
+                \tilde\eta_{t + 1}
+                \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
+                + 
+                \frac{L \tilde\eta_{t + 1}}{2}\Vert z_{t + 1} - y_t\Vert^2. 
+            \end{align*}
+            }
+            It established the first inequality that we wish to prove. 
+            Next, the smoothness of $f$ establish inequality: 
+            \begin{align*}
+                \begin{aligned}
+                    f(z_{t + 1}) - f(z_t) &= f(z_{t + 1}) - f(y_t) + f(y_t) - f(z_t) 
+                    \\
+                    &\le 
+                    \langle \nabla f(y_t), z_{t + 1} - y_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2 
+                    + 
+                    \langle \nabla f(y_t), y_t - z_t\rangle
+                    \\
+                    &= 
+                    \langle \nabla f(y_t), z_{t + 1} - z_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
+                \end{aligned}
+                \tag{$[**]$}
+            \end{align*}
+            The convexity of $h$ establish 
+            \begin{align*}
+                \begin{aligned}
+                    g(z_{t + 1}) + 
+                    \langle \partial g(z_{t + 1}), z_t - z_{t + 1}\rangle
+                    &\le g(z_t)
+                    \\
+                    g(z_{t + 1}) - g(z_t)
+                    &\le 
+                    \langle 
+                        \partial g (z_{t +1}), 
+                        z_{t + 1} - z_t
+                    \rangle. 
+                \end{aligned}
+                \tag{$[\star *]$}    
+            \end{align*}
+            Adding $([**]), ([\star *])$ yields 
+            \begin{align*}
+                \begin{aligned}
+                    \Upsilon_{2, t + 1}^{\text{AG}} := 
+                    h(z_{t + 1}) - h(z_t) 
+                    &\le 
+                    \langle 
+                        \nabla f(y_t) + \partial g(z_{t+1}), 
+                        z_{t + 1} - z_t
+                    \rangle + 
+                    \frac{L}{2}
+                    \Vert 
+                        z_{t + 1} - y_t
+                    \Vert^2. 
+                \end{aligned}
+            \end{align*}
+            Using the property of gradient mapping (\hyperref[lemma:grad_map_lemma_first]
+                {lemma \ref*{lemma:grad_map_lemma_first}}), 
+            $\mathcal G_L(y_t) \in \nabla f(y_t) + \partial g(z_{t + 1})$, substituting it, we proved all we want to show. 
+        \end{proof}
 
@@
 
-    \subsection{Specific Varieties of Accelerated Gradient Method}
-        In this section we state some specific variant of the Nesterov accelerated gradient method. 
-        The "AG" stands for accelerated gradient.
-
     \subsection{Scenario I}
-        In this scenario, we aim to recover the following variant of the accelerated gradient algorithm from 12.1 in Ryu's writing \cite{ryu_large-scale_2022}, it is: 
-        \begin{align*}
-            z_{t + 1} &= y_k + L^{-1}\nabla f(y_t), 
-            \\
-            y_{t + 1} &= z_{t + 1} + \frac{t - 1}{t + 2}\left(
-                z_{k + 1} - z_k
-            \right). 
-        \end{align*}
-        An equivalent form of the above is also provided by Ryu: 
-        \begin{align*}
-            z_{t + 1} &= y_t + L^{-1}\nabla f(y_t), 
-            \\
-            x_{t + 1} &= x_t + (t + 1)(2L)^{-1}\nabla f(y_t), 
-            \\
-            y_{t + 1} &= \left(
-                1 - \frac{2}{t + 2} 
-            \right)z_{t + 1} + 
-            \left(
-                \frac{1}{t + 2}
-            \right)x_{t + 1}. 
-        \end{align*}
-        The base case requires cares since it's not unique, and depending on how the base case is define, there even more representations of it. 
-        \begin{observation}
-            Observe that the second equivalent form is an example of \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
-            \par\noindent
-            It is stated in Ryu's writing that the base case is $x_0 = y_0 = z_0$, 
-            \textcolor{purple}{we think this is not the only options.} 
-            We remind the reader that there is not an obvious choice of $t\in \mathbb Z$ such that $x_t = y_t = z_t$ where the above algorithm remains consistent for all $t \ge -1$. 
-            The choice of base case presented in Ryu's writing is a choice and not a necessity. 
-            We state that one of the base case scenario that only requires knowing $y_1$.
-
-            \par\noindent 
-            We need to observe the case where $t = 0$ to understand the base case of the algorithm. 
-            At each iteration $t$, Given $(x_t, y_t)$, the above formula maps to $(x_{t + 1}, y_{t + 1}, z_{t + 1})$. 
-            When $t= 0$, it has $y_1 = x_1$. 
-            Therefore, knowing only either $y_1$, or $x_1$ can initiate the algorithm. 
-            This is an alternative scenario of the base case. 
-            If, we wish to write $y_0 = x_0$ at $t = 0$ for the base case instead, then it creates the following algorithm 
-            \begin{align*}
-                y_{t} &= \left(
-                1 - \frac{2}{t + 2} 
-                \right)z_{t} + 
-                \left(
-                    \frac{1}{t + 2}
-                \right)x_{t}, 
-                \\
-                z_{t + 1} &= y_t + L^{-1}\nabla f(y_t), 
-                \\
-                x_{t + 1} &= x_t + (t + 1)(2L)^{-1}\nabla f(y_t). 
-            \end{align*}
-            It has a different representations due to a specific choice of the base case. 
-            \par\noindent
-            Finally, by the observation that given $(z_t, y_t)$ for any $t\ge -1$, we can solve for $x_t$ \newline via $y_t = (1 - 2/(1 + t))z_t + 1/(t + 1)x_t$, obtaining $(x_t, y_t, z_t)$, hence the algorithm can be reduced to a representations with only $(z_t, y_t)$ and an updates using only $(z_t, y_t)$ to $(z_{t + 1}, y_{t + 1})$.
-            That is the momentum form presented above. 
-        \end{observation}
-        We advise the reader to read the Biliography notes by Ryu \cite[chapter 12]{ryu_large-scale_2022} of his book. 
-        It goes over the full context and history for this particular variant of gradient acceleration method. 
-        As the time of composing this notes, the writer is still reading on the topic of accelerated gradient.
+        In this scenario, we aim to recover AG Ryu 12.1 conceret variant algorithm stated back in 
+        \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}.
 

### 2024-07-07 Notebook LaTEX/Momentum Accelerations/main.tex
>w< more small updates to the notes

@@
                 Observe that by setting $\mu = 0, \tilde \eta_{t + 1} = \eta_{t + 1}$ this recovers algorithm (4.8) described in Ahn and Sra \cite{ahn_understanding_2022}. 
+                Finally, Ahn, Sra 6.24 has the same form as Nesterov 2.2.7. 
+                See 
+                \hyperref[prop:Nes2.2.7_via_ahn_sra_6.24]{proposition \ref*{prop:Nes2.2.7_via_ahn_sra_6.24}} for a demonstration. 
             \end{remark}
@@
             \end{definition}
+            \begin{observation}
+                With $g \equiv 0$, the above definition reduces to 
+                \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}
+                where $\mu = 0$. 
+            \end{observation}
 
@@
                 They are the same parameters for both algorithms and they are equivalent. 
-                This will be proved in the coming parts. 
+                For a demonstration, see 
+                \hyperref[prop:tri_form_via_ppm]{proposition \ref*{prop:tri_form_via_ppm}}. 
             \end{remark}
+
             \begin{definition}[Strongly Convex Tri-points Generic Form]
-                \quad 
+                \quad \\
                 With $f$ being $L$-Lipschitz smooth and $\mu > 0$ strongly convex then the Strongly convex Tri-Points generic form has updates of for iterates
@@
             \end{definition}
+            \begin{remark}
+                This algorithm is equivalent to 
+                \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}. 
+                See \ref*{prop:tri_scvx_from_ahn_sra_6.24} for a demonstration. 
+            \end{remark}
 
@@
                     \left(
-                        \frac{1}{t + 2}
+                        \frac{2}{t + 2}
                     \right)x_{t + 1}. 
@@
                 It is stated in Ryu's writing that the base case is $x_0 = y_0 = z_0$, 
-                \textcolor{purple}{we think this is not the only options.} 
+                we think this is not the only options. 
                 We remind the reader that there is not an obvious choice of $t\in \mathbb Z$ such that $x_t = y_t = z_t$ where the above algorithm remains consistent for all $t \ge -1$. 
@@
                     \left(
-                        \frac{1}{t + 2}
+                        \frac{2}{t + 2}
                     \right)x_{t}, 
@@
 
-            \begin{definition}[Form Zero]
-            \label{def:ag_form_zero}
-
+            \begin{definition}[Proximal Gradient Tri-Points Form E]
+            \label{def:ag_tri_pt_form_E}
+                Form E is a special case of 
+                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
+                with the condition that $\tilde \eta_t = \eta_t$ for all $t \in \mathbb N$. 
+                As a consequence, the algorithm has the following updates for iterates $(y_t, x_{t + 1}, z_{t + 1})$. 
+                Giving us: 
+                \begin{align*}
+                    y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
+                    \\
+                    x_{t + 1} &= x_t - \eta_t \mathcal G_L(y_t)
+                    \\
+                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t).
+                \end{align*}
             \end{definition}
+            \begin{remark}
+
+            \end{remark}
 

### 2024-07-08 Notebook LaTEX/Momentum Accelerations/main.tex
>w< lots of updates to the notes

@@
             \end{definition}
-            \begin{remark}
-
-            \end{remark}
 
@@
             \label{def:ag_form_similar_tria_I}
-
+                It updates iterates $(y_t, x_{t + 1}, z_{t + 1})$ using 
+                \begin{align*}
+                    z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t) 
+                    \\
+                    x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
+                    \\
+                    y_{t + 1} &= 
+                    (1 + L\eta_{t + 1})^{-1}
+                    (
+                    x_{t + 1} + L\eta_{t + 1}z_{t + 1}
+                    ). 
+                \end{align*}
             \end{definition}
+            \begin{observation}
+                There are a lot of observations about this form to unpack. 
+                Let's list the following observations
+                \begin{enumerate}
+                    \item Observe that $y_t = (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)$ is a convex combination between $x_t, z_t$.
+Hence $z_t, y_t, x_t$ are three collinear points.
+Additionally, we have $y_t - x_t = L\eta_t (z_t - y_t)$, hence $\Vert y_t - x_t\Vert/\Vert z_t - y_t\Vert = L\eta_t$.
+                    \item By the algorithm, we have $z_{t + 1} - y_t = - L^{-1} \nabla f(y_t)$, and $x_{t + 1} - x_t = - \tilde \eta_{t + 1} \nabla f(y_t)$, hence vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$.
+                    \item Finally, with update $x_{t +1} - z_{t + 1} = L\eta_t (z_{t +1} - z_t)$, we have three colinear points $(z_t, z_{t + 1}, x_t)$ with $\Vert z_{t + 1} - z_t\Vert/\Vert z_{t +1 } - z_t\Vert = L\eta_t$.
+                \end{enumerate}
+                From the above results, we can conclude that triangle $(y_t, z_t, z_{t + 1})$ is similar to $(x_t, z_t, x_{t + 1})$ because they share colinear points $z_t, y_t, x_t$ and $z_t, z_{t + 1}, x_{t + 1}$, and their sides $z_{t + 1} - y_t$ parallels to $x_{t + 1} - z_t$.
+            \end{observation}
 
@@
 
-    \subsection{Generic Lyapunov analysis for Accelerated gradient via PPM}
-        The first theorem states the generic convergence results when $f$ is differentiable with $L$-Lipschitz gradient, using \hyperref[def:agg_ppm]{definition\ref*{def:agg_ppm}}. 
-        \begin{lemma}[Smooth Generic AG Lyapunov Analysis]\label{lemma:smooth_agg_lyapunov_upper_bound}
-            With $f$ having $L$-Lipschitz gradient and minimizer $x_*$, using 
-            \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} with $\mu = 0$
-            and 
-            \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} ,
-            then we can derive the upper bounds for the RHS of the PPM descent inequality: 
-            \begin{align*}
-                \Upsilon_{1, t + 1}^{\text{AG}}
-                &= \tilde \eta_{t + 1} (f(z_{t + 1}) - f(x_*))
-                + \frac{1}{2}(
-                    \Vert x_{t + 1} - x_*\Vert^2 - \Vert x_t - x_* \Vert^2
-                )  
-                \\
-                & \quad \le 
-                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 + 
-                \frac{\tilde \eta_{t + 1} L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                - 
-                \langle \tilde \eta_{t + 1} \nabla f(y_t), x_{t + 1} - z_{t + 1} \rangle, 
-                \\
-                \Upsilon_{2, t + 1}^{\text{AG}} 
-                &= f(z_{t + 1}) - f(z_t) 
-                \le 
-                \langle \nabla f(y_t), z_{t + 1} - z_t\rangle + 
-                \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-            \end{align*}
-        \end{lemma}
-        \begin{proof}
-            Define $\phi_t(x) = \tilde \eta_{t +1}(f(y_t) + \langle \nabla f(y_t), x- y_t\rangle)$.  
-            With $L$-smoothness of $f$ in mind, consider the following sequence of inequalities: 
-            $$
-            \begin{aligned}
-                \phi_t(x_{t + 1}) 
-                &= 
-                \tilde\eta_{t + 1} (f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle)
-                \\
-                \phi_t (x_{t + 1}) &= \tilde \eta_{t + 1}(
-                    f(y_t) + \langle \nabla f(y_t), (x_{t +1} - z_{t + 1}) + (z_{t + 1} - y_t) \rangle
-                )
-                \\
-                &\ge 
-                \tilde \eta_{t + 1}
-                \left(
-                    f(z_{t + 1}) - \frac{L}{2} \Vert z_{t + 1} - y_t\Vert^2 + 
-                    \langle \nabla f(y_t), x_{t +1} - z_{t + 1}\rangle
-                \right), 
-            \end{aligned}
-            $$
-            the AG generic performs PPM on $\phi_t$ to produce $x_{t + 1}$ so the PPM Lyapunov inequality from 
-            \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} applies,
-            substituting yields equivalences for all $x_*$: 
-            {\footnotesize
-            \begin{align*}
-                & \phi_t(x_{t + 1}) - \phi_t(x_*) + \frac{1}{2}\Vert x_* - x_{t + 1}\Vert^2 
-                - \frac{1}{2}\Vert x_* - x_t\Vert^2 
-                \\
-                &\quad \le 
-                - \frac{1}{2} \Vert x_{t + 1} - x_t\Vert^2 
-                \\
-                \implies & 
-                \tilde \eta_{t + 1}\left(
-                    f(z_{t + 1}) - \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2 
-                    + 
-                    \langle \nabla f(y_t), x_{t + 1} - z_{t + 1}\rangle
-                \right) - \tilde \eta_{t + 1} f(x_*)
-                + 
-                \frac{1}{2}\left(
-                    \Vert x_{t + 1} - x_*\Vert^2 - \Vert x_{t} - x_*\Vert^2
-                \right)
-                \\
-                &\quad \le
-                 - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-                \\
-                \iff 
-                & 
-                \tilde \eta_{t + 1} \left(
-                    f(z_{t + 1}) - f(x_*)
-                \right) + \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2 
-                - \frac{1}{2}\Vert x_{t} - x_*\Vert^2  =: \Upsilon_{1, t + 1}^{\text{AG}}
-                \\
-                &\quad \le 
-                -\frac{1}{2} \Vert x_{t + 1 } - x_t\Vert^2 + 
-                \frac{\tilde \eta_{t + 1}}{2}\Vert z_{t + 1} - y_t\Vert^2 
-                - \langle \tilde \eta_{t + 1}\nabla f(y_t), x_{t + 1} - z_{t + 1} \rangle. 
-            \end{align*}
-            }
-            Observe that, the rhs and lhs of the Lyapunov inequality are anchored at $z_{t + 1}$. 
-            Similarly for the descent inequality we wish to obtain: 
-            \begin{align*}
-                f(z_{t + 1}) - f(z_t) &= f(z_{t + 1}) - f(y_t) + f(y_t) - f(z_t) 
-                \\
-                &\le 
-                \langle \nabla f(y_t), z_{t + 1} - y_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2 
-                + 
-                \langle \nabla f(y_t), y_t - z_t\rangle
-                \\
-                &= 
-                \langle \nabla f(y_t), z_{t + 1} - z_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                \\
-                \text{let }\Upsilon_{2, t + 1}^{\text{AG}} 
-                &:= f(z_{t + 1}) - f(z_t). 
-            \end{align*}
-            Which is the descent inequality anchored on $z_{t + 1}$.
-            Merging the $(z_{t + 1} - y_t)$ with $y_t - z_t$ together yield the desired results. 
-        \end{proof}
-
-        \begin{lemma}[Nonsmooth Generic AG Lyapunov Analysis]
-        \label{lemma:nsmooth_agg_lyapunov_upper_bound}
-            Continue from 
-            \hyperref[prop:derive_ag_prox_grad_tript]
-            {definition \ref*{prop:derive_ag_prox_grad_tript}},
-            we derive the non-smooth analogous case of the Lyapunov upper bound: 
-            \begin{align*}
-                \Upsilon_{1, t + 1}^\text{AG}
-                &= 
-                \tilde\eta_{t + 1} (h(z_{t + 1}) - h(x_*)) + 
-                \frac{1}{2} (
-                    \Vert x_{t + 1} - x_*\Vert^2
-                    - 
-                    \Vert x_t - x_*\Vert^2
-                )
-                \\
-                &\le 
-                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-                + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                - \langle 
-                    \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                    x_{t + 1} - z_{t + 1}
-                \rangle
-                \\
-                \Upsilon_{2, t + 1}^\text{AG}
-                &= 
-                h(z_{t + 1}) - h(z_t) 
-                \le 
-                \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
-                \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-            \end{align*}
-        \end{lemma}
-        \begin{proof}
-            Define 
-            \begin{align*}
-                \phi_t(u) &:= 
-                \tilde \eta_{t + 1} 
-                \left(
-                    f(y_t) + g(y_t) + \langle \nabla f(y_t) + \partial g(y_t^+), u - y_t\rangle
-                    + 
-                    \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
-                \right)\\
-                &= 
-                \tilde \eta_{t + 1} \left(
-                    f(y_t) + \langle \nabla f(y_t), u - y_t\rangle + 
-                    \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
-                    + 
-                    g(y_t) + \langle \partial g(y_t^+), u - y_t\rangle
-                \right). 
-            \end{align*}
-            Then the update in the Generic Tri-Point algorithm 
-            (\hyperref[def:ag_prox_grad_ppm]
-                {definition \ref*{def:ag_prox_grad_ppm}}) 
-            has $x_{t + 1} = \prox{\phi_t}(x_t)$ and therefore we can use the Lyapunov inequality for PPM (\hyperref[thm:ppm_descent_ineq]
-                {theorem \ref*{thm:ppm_descent_ineq}})
-            which gives for all $x_*$: 
-            \begin{align*}
-                & \phi_t(x_{t + 1}) - \phi_t(x_*) + 
-                \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
-                \frac{1}{2}\Vert x_t - x_*\Vert^2
-                \le \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2, 
-                \\
-                & \text{where }
-                \phi_t(x_{t + 1}) =
-                \\
-                & \quad 
-                \tilde \eta_{t + 1}
-                \left(
-                    f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle + 
-                    \frac{1}{2\tilde \eta_{t + 1}}\Vert x_{t + 1} - x_t\Vert^2
-                    + 
-                    g(y_t) + \langle \partial g(y_t^+), x_{t + 1} - y_t\rangle
-                \right). 
-            \end{align*}
-            to simplify, consider using the $L$-smoothness of $f$, we have the inequality: 
-            \begin{align*}
-                \begin{aligned}
-                    f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle
-                    &=
-                    f(y_t) + \langle \nabla f(y_t), (x_{t +1} - z_{t + 1}) + (z_{t + 1} - y_t) \rangle
-                    \\
-                    &\ge 
-                    f(z_{t + 1}) - \frac{L}{2} \Vert z_{t + 1} - y_t\Vert^2 + 
-                    \langle \nabla f(y_t), x_{t +1} - z_{t + 1}\rangle
-                    \\
-                    &= 
-                    f(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2
-                    + \langle \nabla f(y_t), x_{t + 1} - y_t^+\rangle.     
-                \end{aligned}
-                \tag{$[*]$}
-            \end{align*}
-            further consider
-            \begin{align*}
-                \begin{aligned}
-                    g(y_t) + \langle \partial g(y_t^+), x_{t + 1} - y_t\rangle 
-                    &= g(y_t) + 
-                    \langle \partial g(y_t^+), 
-                    x_{t + 1} - y_t^+ + y_t^+ - y_t
-                    \rangle
-                    \\
-                    &= g(y_t) 
-                    + \langle \partial g (y_t^+),
-                        x_{t + 1} - y_t^+
-                    \rangle
-                    + 
-                    \langle 
-                        \partial g(y_t^+), y_t^+ - y_t
-                    \rangle
-                    \\
-                    g \text{ convex }\implies 
-                    &\ge 
-                    g(y_t^+) + 
-                    \langle \partial g(y_t^+), x_{t + 1} - y_t^+\rangle. 
-                \end{aligned}
-                \tag{$[\star]$}
-            \end{align*}
-            In the $([\star])$ derivation, we used the convexity of $g$ where 
-            \begin{align*}
-                \langle \partial g(y_t^+), y_t - y_t^+\rangle
-                &\le g(y_t) - g(y_t^+)
-                \\
-                \langle \partial g (y_t^+), y_t^+ - y_t \rangle
-                &\le 
-                g(y_t^+) - g(y_t). 
-            \end{align*}
-            Now, adding $([*]), ([\star])$, multiply their sum by $\tilde\eta_{t + 1}$ makes it equals to $\phi_t(x_{t +1 })$ , we can establish a lower bound for $\phi_t(x_{t + 1})$, yielding inequality
-            {\small
-                \begin{align*}
-                    \phi_t(x_{t + 1})
-                    &\ge 
-                    \tilde\eta_{t + 1}
-                    \left(
-                        f(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2 
-                        +
-                        \langle \nabla f(y_t), x_{t + 1} - y_t^+\rangle
-                        + 
-                        g(y_t^+) + 
-                        \langle \partial g(y_t^+), x_{t + 1} - y_t^+\rangle
-                    \right) 
-                    \\
-                    &= 
-                    \tilde\eta_{t + 1}
-                    \left(
-                        h(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2 
-                        + 
-                        \langle \partial g(y_t^+) + \nabla f(y_t), x_{t + 1} - y_t^+\rangle
-                    \right).
-                \end{align*}
-            }
-            Apply
-            \hyperref[lemma:grad_map_lemma_first]{lemma \ref*{lemma:grad_map_lemma_first}} 
-            we have $\partial g(y_t^+) + \nabla f(y_t) \ni \mathcal G_L(y_t)$, and by the algorithm updates $y_t^+ = z_{t + 1}$, therefore the above inequality simplifies to 
-            \begin{align*}
-                \phi_t(x_{t + 1}) &\ge 
-                \tilde\eta_{t + 1} 
-                \left(
-                    h(z_{t + 1}) - 
-                    \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                    + 
-                    \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
-                \right). 
-            \end{align*}
-            Finally, from (\hyperref[lemma:grad_map_linearization]
-                {lemma \ref*{lemma:grad_map_linearization}})
-            we have $\phi_t(u) \le \tilde\eta_{t + 1}h(u)$ for all $u$. 
-            With that we lower bound the LHS of the PPM Lyapunov inequality of $\phi_t(u)$, making: 
-            {\footnotesize
-            \begin{align*}
-                & \phi_t(x_{t + 1}) - \phi_t(x_*) + 
-                \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
-                \frac{1}{2}\Vert x_t - x_*\Vert^2
-                \le
-                \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-                \\
-                \implies &
-                \tilde \eta_{t + 1}
-                \left(
-                    h(z_{t + 1}) - 
-                    \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                    + 
-                    \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
-                \right) - \tilde \eta_{t + 1} h(x_*)
-                +
-                \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
-                \frac{1}{2}\Vert x_t - x_*\Vert^2
-                \\
-                & \quad \le
-                \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-                \\
-                \iff &
-                \tilde\eta_{t + 1}(h(z_{t + 1}) - h(x_*))
-                + \frac{1}{2}\left(
-                    \Vert x_{t + 1} - x_*\Vert^2 
-                    - 
-                    \Vert x_t - x_*\Vert^2
-                \right) := \Upsilon_{1, t + 1}^\text{AG}
-                \\
-                &\quad \le 
-                \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-                - 
-                \tilde\eta_{t + 1}
-                \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
-                + 
-                \frac{L \tilde\eta_{t + 1}}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-            \end{align*}
-            }
-            It established the first inequality that we wish to prove. 
-            Next, the smoothness of $f$ establish inequality: 
-            \begin{align*}
-                \begin{aligned}
-                    f(z_{t + 1}) - f(z_t) &= f(z_{t + 1}) - f(y_t) + f(y_t) - f(z_t) 
-                    \\
-                    &\le 
-                    \langle \nabla f(y_t), z_{t + 1} - y_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2 
-                    + 
-                    \langle \nabla f(y_t), y_t - z_t\rangle
-                    \\
-                    &= 
-                    \langle \nabla f(y_t), z_{t + 1} - z_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-                \end{aligned}
-                \tag{$[**]$}
-            \end{align*}
-            The convexity of $h$ establish 
-            \begin{align*}
-                \begin{aligned}
-                    g(z_{t + 1}) + 
-                    \langle \partial g(z_{t + 1}), z_t - z_{t + 1}\rangle
-                    &\le g(z_t)
-                    \\
-                    g(z_{t + 1}) - g(z_t)
-                    &\le 
-                    \langle 
-                        \partial g (z_{t +1}), 
-                        z_{t + 1} - z_t
-                    \rangle. 
-                \end{aligned}
-                \tag{$[\star *]$}    
-            \end{align*}
-            Adding $([**]), ([\star *])$ yields 
-            \begin{align*}
-                \begin{aligned}
-                    \Upsilon_{2, t + 1}^{\text{AG}} := 
-                    h(z_{t + 1}) - h(z_t) 
-                    &\le 
-                    \langle 
-                        \nabla f(y_t) + \partial g(z_{t+1}), 
-                        z_{t + 1} - z_t
-                    \rangle + 
-                    \frac{L}{2}
-                    \Vert 
-                        z_{t + 1} - y_t
-                    \Vert^2. 
-                \end{aligned}
-            \end{align*}
-            Using the property of gradient mapping (\hyperref[lemma:grad_map_lemma_first]
-                {lemma \ref*{lemma:grad_map_lemma_first}}), 
-            $\mathcal G_L(y_t) \in \nabla f(y_t) + \partial g(z_{t + 1})$, substituting it, we proved all we want to show. 
-        \end{proof}
-
-        \begin{theorem}[Generic AG Convergence]\label{thm:generic_smooth_ag_convergence}
-            If there is a choice of $\eta_i, \tilde \eta_i$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} such that we have 
-            \begin{align*}
-                \left(
-                    \sum_{i = 1}^{t} \tilde \eta_i
-                \right)
-                \Upsilon_{2, t + 1}^{\text{AG}} + 
-                \Upsilon_{1, t + 1}^{\text{AG}} \le 0, 
-            \end{align*}
-            then with 
-            \begin{align*}
-                \Phi_t &= \left(
-                    \sum_{i = 1}^{t} \tilde\eta_{i}
-                \right) (f(z_t) - f(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \NN
-                \\
-                \Phi_0 &= \frac{1}{2}\Vert x_t - x_*\Vert^2, 
-            \end{align*}
-            we have $\Phi_{t + 1} - \Phi_t \le 0$, which allows for a convergence rate of $\mathcal O \left(\sum_{i = 1}^{T} \eta_i^{-1}\right)$ for $f(z_T) - f(x_*)$. 
-        \end{theorem}
-        \begin{proof}
-            By definition we have
-            {\footnotesize
-            \begin{align*}
-                \Phi_{t + 1} - \Phi_t 
-                &= 
-                \left(
-                    \sum_{i = 1}^{t+1} \tilde\eta_{i}
-                \right) (f(z_{t + 1}) - f(x_*)) 
-                - 
-                \left(
-                    \sum_{i = 1}^{t} \tilde\eta_{i}
-                \right) (f(z_{t}) - f(x_*)) 
-                + \frac{1}{2}\Vert x_t - x_*\Vert^2
-                - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
-                \\
-                &= 
-                \tilde \eta_{t + 1} (f(z_{t + 1}) - f(z_*))
-                +
-                \left(
-                    \sum_{i = 1}^{t} \tilde \eta_i
-                \right)(f(z_{t + 1}) - f(z_t))
-                + \frac{1}{2}\Vert x_t - x_*\Vert^2
-                - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
-                \\
-                &= \left(
-                    \sum_{i = 1}^{t} \tilde \eta_i
-                \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le 0. 
-            \end{align*}
-            }
-            The derivation for the convergence raet is direct and similar to 
-            \hyperref[thm:ppm_convergence_rate]{theorem \ref*{thm:ppm_convergence_rate}} 
-            Therefore, if we can identify parameter for the generic algorithm that asserts the condition above, then we have convergence for the algorithm. 
-        \end{proof}
-
-    \subsection{Scenario I}
-        In this scenario, we aim to recover AG Ryu 12.1 conceret variant algorithm stated back in 
-        \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}.
-
-        \begin{proposition}
-            With $\eta_t, \tilde \eta_t$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} where $\eta_{t + 1} = \tilde \eta_{t + 1} = 2/(2L)$, we derive the following algorithm: 
-            \begin{align*}
-                x_{t + 1} &= x_t - \frac{t + 1}{2L} \nabla f(y_t), 
-                \\
-                z_{t + 1} &= y_t - L^{-1} \nabla f(y_t), 
-                \\
-                y_{t + 1} &= 
-                \left(
-                    \frac{2}{t + 3}
-                \right)x_{t +1} + 
-                \left(
-                    1 - \frac{2}{t + 3}
-                \right)z_{t + 1}. 
-            \end{align*}
-        \end{proposition}
-        \begin{observation}
-            Observe that this is the same algorithm as stated in Ryu's book but with an alternative choice of indexing for $y_t$ and initial condition. 
-        \end{observation}
-        \begin{proof}
-            Consider the upper bounds of $\Upsilon_{1, t + 1}^\text{AG}, \Upsilon_{2, t + 1}^\text{AG}$, together with the updates of the Generic Triangular Form of the algorithm:  
-            \begin{align*}
-                x_{t + 1} - x_t &= \tilde \eta_{t + 1}\nabla f(y_t)
-                \\
-                z_{t +1} - y_t &= L^{-1}\nabla f(y_t), 
-            \end{align*}
-            we consider the upper bound of $\Upsilon_{1, t + 1}^{\text{AG}}$, with that we can simplify it: 
-            {\footnotesize
-            \begin{align*}
-                \Upsilon_{1, t + 1}^{\text{AG}}
-                &\le 
-                -\frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-                + 
-                \frac{\tilde \eta_{t + 1}L }{2} \Vert z_{t + 1} - y_t\Vert^2 
-                - 
-                \langle \tilde \eta_{t + 1} \nabla f(y_t), x_{t +1} - z_{t + 1}\rangle
-                \\
-                &\le 
-                - \frac{1}{2}\Vert \tilde \eta_{t + 1} \nabla f(y_t)\Vert^2 
-                + \frac{\tilde \eta_{t + 1} L}{2}\Vert L^{-1} \nabla f(y_t)\Vert^2 
-                + 
-                \langle 
-                    - \tilde \eta_{t + 1} \nabla f(y_t), 
-                    -L^{-1}\nabla f(y_t) + y_t - x_t + \tilde \eta_{t + 1}\nabla f(y_t)
-                \rangle
-                \\
-                &= 
-                \left(
-                    \frac{\tilde \eta_{t + 1}^2}{2} + 
-                    \frac{\tilde \eta_{t + 1}}{2L}
-                \right)
-                \Vert \nabla f(y_t)\Vert^2 
-                + \tilde \eta_{t + 1} 
-                \left\langle 
-                    \nabla f(y_t), 
-                    (\tilde \eta_{t + 1} - L^{-1})\nabla f(y_t) + y_t - x_t 
-                \right\rangle
-                \\
-                &= 
-                (1/2)(L^{-1}\tilde \eta_{t + 1} - \tilde \eta_{t + 1}^2)
-                \Vert \nabla f(y_t)\Vert^2
-                + 
-                \tilde \eta_{t + 1}(\tilde \eta_{t + 1} - L^{-1})
-                \Vert \nabla f(y_t)\Vert^2
-                + 
-                \tilde \eta_{t + 1}\langle \nabla f(y_t), y_t - x_t\rangle
-                \\
-                &= \frac{1}{2}\left(
-                    -L^{-1}\tilde \eta_{t + 1} + \tilde \eta_{t + 1}^2
-                \right)\Vert \nabla f(y_t)\Vert^2 
-                + 
-                \tilde\eta_{t + 1} \langle \nabla f(y_t), y_t - x_t\rangle. 
-            \end{align*}
-            }
-            For $\Upsilon_{2, t + 1}^\text{AG}$, we simplify it with the same updates relation in mind: 
-            \begin{align*}
-                \Upsilon_{2, t + 1}^\text{AG}
-                &\le 
-                \langle \nabla f(y_t), z_{t +1} - y_t\rangle + 
-                \frac{L}{2}\Vert z_{t +1} - y_{t} \Vert^2 
-                + 
-                \langle \nabla f(y_t), y_t - z_t\rangle
-                \\
-                &= 
-                \langle 
-                    \nabla f(y_t), -L^{-1} \nabla f(y_t)
-                \rangle + 
-                \frac{L}{2}\Vert L^{-1}\nabla f(y_t) \Vert^ 2
-                + 
-                \langle \nabla f(y_t), y_t - z_t\rangle
-                \\
-                &= -\frac{1}{2L}\Vert \nabla f(y_t)\Vert^2 
-                + \langle \nabla f(y_t), y_t - z_t\rangle. 
-            \end{align*}
-            Observe that the cross product term for $\Upsilon_{1, t + 1}^\text{AG}, \Upsilon_{2, t + 1}^\text{AG}$ doesn't match. 
-            Hence let's consider $y_t - x_t = L \eta_t (z_t - y_t)$ from the algorithm, we make the choice to do surgery on upper bound of $\Upsilon_{2, t + 1}^\text{AG}$, so $\langle \nabla f(y_t), y_t - x_t\rangle = \langle \nabla f(y_t), L \eta_t (z_t - y_t)\rangle$.
-            With this in mind, applying 
-            \hyperref[thm:generic_smooth_ag_convergence]{theorem \ref*{thm:generic_smooth_ag_convergence}} 
-            and upper bound from 
-            \hyperref[lemma:smooth_agg_lyapunov_upper_bound]{lemma \ref*{lemma:smooth_agg_lyapunov_upper_bound}} 
-            yields inequality: 
-            {\footnotesize
-            \begin{align*}
-                & \Upsilon_{1, t + 1}^{\text{AG}} + \left(
-                    \sum_{i=1}^{t}\tilde\eta_i 
-                \right) \Upsilon_{2, t + 1}^{\text{AG}} 
-                \\
-                & \le 
-                \frac{1}{2}\left(
-                    -L^{-1}\tilde \eta_{t + 1} + \tilde \eta_{t + 1}^2
-                \right)\Vert \nabla f(y_t)\Vert^2 
-                + 
-                \tilde\eta_{t + 1} \langle \nabla f(y_t), y_t - x_t\rangle
-                + 
-                \left(
-                    \sum_{i = 1}^{t}\tilde \eta_i 
-                \right)\left(
-                    -\frac{1}{2L}\Vert \nabla f(y_t)\Vert^2 
-                    + \langle \nabla f(y_t), y_t - z_t\rangle
-                \right)
-                \\
-                & =
-                \left(
-                    \frac{1}{2}\tilde\eta_{t + 1}\left(
-                        \tilde \eta_{t +1} - L^{-1}
-                    \right)
-                    - 
-                    \frac{1}{2L}\sum_{i = 1}^{t}\tilde \eta_i
-                \right)\Vert \nabla f(y_t)\Vert^2
-                + 
-                \tilde \eta_{t + 1}\langle \nabla f(y_t), L\eta_t (z_t - y_t)\rangle
-                + 
-                \left(
-                    \sum_{i = 1}^{t}\tilde \eta_i
-                \right)
-                \langle \nabla f (y_t), y_t - z_t\rangle
-                \\
-                & = 
-                \left(
-                    \frac{1}{2}\tilde\eta_{t + 1}\left(
-                        \tilde \eta_{t +1} - L^{-1}
-                    \right)
-                    - 
-                    \frac{1}{2L}\sum_{i = 1}^{t}\tilde \eta_i
-                \right)\Vert \nabla f(y_t)\Vert^2
-                + 
-                \left(
-                    L\eta_t \tilde \eta_{t + 1} - \sum_{i = 1}^{t}\tilde \eta_i
-                \right)
-                \langle \nabla f(y_t), z_t - y_t\rangle. 
-            \end{align*}
-            }
-            Next, we select a choice for stepsize parameter $\eta_t, \tilde \eta_{t +1}$ such that the coefficient for the $\Vert \nabla f(y_t)\Vert^2$ is negative, and is zero for the cross product term.
-            In this scenario, we makes the choice of $\tilde \eta_t = \eta_t$. 
-            Continuting will simplify the upper bound so that it is: 
-            \begin{align*}
-                \frac{1}{2}\left(
-                    \eta_{t + 1}^2 - L^{-1}\eta_{t +1} - L^{-1}\sum_{i = 1}^{t}\eta_i
-                \right)\Vert \nabla f(y_t)\Vert^2
-                + 
-                \left(
-                    L\eta_t \eta_{t + 1} - \sum_{i = 1}^{t} \eta_i
-                \right)
-                \langle \nabla f(y_t), z_t - y_t\rangle 
-                &
-                \le 0. 
-            \end{align*}
-            Assuming the above inequality holds then one of the sufficient conditions would happen when the coefficient of the cross product term is zero and the coefficient for the normed term is negative, yielding the condition for all $t \in \NN$:
-            \begin{align*}
-                \begin{cases}
-                    L\eta_{t + 1}^2 + \eta_{t + 1} - \sum_{i = 1}^{t}\eta_i 
-                    \le 0, 
-                    \\
-                    L\eta_t \eta_{t + 1} - \sum_{i = 1}^{t} \eta_i 
-                    = 0. 
-                \end{cases}
-            \end{align*}
-            Substituting the sequence equality back to the first one yield: 
-            \begin{align*}
-                L\eta_{t + 1}^2 - (\eta_{t + 1} + L\eta_t\eta_{t + 1}) &\le 0 
-                \\
-                L\eta^2_{t + 1} - \eta_{t + 1}
-                &\le 
-                L\eta_t \eta_{t + 1} 
-                \\
-                \eta_{t + 1}(L\eta_{t + 1} - 1) 
-                &\le L\eta_t\eta_{t + 1}
-                \\
-                \eta_t > 0 
-                \implies 
-                L\eta_{t + 1} - 1 &\le 
-                L\eta_t 
-                \\
-                \eta_{t + 1} &\le \eta_t + L^{-1}. 
-            \end{align*}
-            To satisfy the equality, reader should verify that $\eta_{t} = t/(2L)$ is one of the options. 
-            And there are not many other options for the choice of the stepszies for the equality to be satisfied. 
-        \end{proof}
-        \begin{remark}
-            In the original writing by Ahn \cite[equation (4.9)]{ahn_understanding_2022}, they didn't identify the algorithm in the literature. 
-            Here we identify it to be equivalent to the acceleration algorithm stated in Ryu \cite[algorithm 12.1]{ryu_large-scale_2022}. 
-        \end{remark}
-
-    \subsection{Scenario II}
-        With the choice of $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we can recover the seminal Nesterov accelerated gradient algorithm from 1983. 
-        The variants proposed by Chambolle Dossal \cite{chambolle_convergence_2015}, is distinct from the possibility proposed in this secenario. 
-        \par\noindent
-        To start, we make the claim that the new stepsizes results in a different algorithm. 
-        \begin{lemma}[Similar Triangular Form]
-            With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$ as in \ref*{def:agg_tri}, we have the following specific similar triangular form of the accelerated gradient algorithm: 
+            \begin{lemma}[Similar Triangule Form I via Generic Tri Points]
+                \quad \\
+                With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$ 
+                in 
+                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
+                We can derive similar triangle form I as stated back in
+                \hyperref[def:ag_form_similar_tria_I]{definition \ref*{def:ag_form_similar_tria_I}}. 
                 \begin{align*}
@@
 
+    \subsection{Generic Lyapunov analysis for Accelerated gradient via PPM}
+        The first theorem states the generic convergence results when $f$ is differentiable with $L$-Lipschitz gradient, using \hyperref[def:agg_ppm]{definition\ref*{def:agg_ppm}}. 
+        \begin{lemma}[Smooth Generic AG Lyapunov Analysis]\label{lemma:smooth_agg_lyapunov_upper_bound}
+            With $f$ having $L$-Lipschitz gradient and minimizer $x_*$, using 
+            \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} with $\mu = 0$
+            and 
+            \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} ,
+            then we can derive the upper bounds for the RHS of the PPM descent inequality: 
+            \begin{align*}
+                \Upsilon_{1, t + 1}^{\text{AG}}
+                &= \tilde \eta_{t + 1} (f(z_{t + 1}) - f(x_*))
+                + \frac{1}{2}(
+                    \Vert x_{t + 1} - x_*\Vert^2 - \Vert x_t - x_* \Vert^2
+                )  
+                \\
+                & \quad \le 
+                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 + 
+                \frac{\tilde \eta_{t + 1} L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                - 
+                \langle \tilde \eta_{t + 1} \nabla f(y_t), x_{t + 1} - z_{t + 1} \rangle, 
+                \\
+                \Upsilon_{2, t + 1}^{\text{AG}} 
+                &= f(z_{t + 1}) - f(z_t) 
+                \le 
+                \langle \nabla f(y_t), z_{t + 1} - z_t\rangle + 
+                \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            Define $\phi_t(x) = \tilde \eta_{t +1}(f(y_t) + \langle \nabla f(y_t), x- y_t\rangle)$.  
+            With $L$-smoothness of $f$ in mind, consider the following sequence of inequalities: 
+            $$
+            \begin{aligned}
+                \phi_t(x_{t + 1}) 
+                &= 
+                \tilde\eta_{t + 1} (f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle)
+                \\
+                \phi_t (x_{t + 1}) &= \tilde \eta_{t + 1}(
+                    f(y_t) + \langle \nabla f(y_t), (x_{t +1} - z_{t + 1}) + (z_{t + 1} - y_t) \rangle
+                )
+                \\
+                &\ge 
+                \tilde \eta_{t + 1}
+                \left(
+                    f(z_{t + 1}) - \frac{L}{2} \Vert z_{t + 1} - y_t\Vert^2 + 
+                    \langle \nabla f(y_t), x_{t +1} - z_{t + 1}\rangle
+                \right), 
+            \end{aligned}
+            $$
+            the AG generic performs PPM on $\phi_t$ to produce $x_{t + 1}$ so the PPM Lyapunov inequality from 
+            \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} applies,
+            substituting yields equivalences for all $x_*$: 
+            {\footnotesize
+            \begin{align*}
+                & \phi_t(x_{t + 1}) - \phi_t(x_*) + \frac{1}{2}\Vert x_* - x_{t + 1}\Vert^2 
+                - \frac{1}{2}\Vert x_* - x_t\Vert^2 
+                \\
+                &\quad \le 
+                - \frac{1}{2} \Vert x_{t + 1} - x_t\Vert^2 
+                \\
+                \implies & 
+                \tilde \eta_{t + 1}\left(
+                    f(z_{t + 1}) - \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2 
+                    + 
+                    \langle \nabla f(y_t), x_{t + 1} - z_{t + 1}\rangle
+                \right) - \tilde \eta_{t + 1} f(x_*)
+                + 
+                \frac{1}{2}\left(
+                    \Vert x_{t + 1} - x_*\Vert^2 - \Vert x_{t} - x_*\Vert^2
+                \right)
+                \\
+                &\quad \le
+                 - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+                \\
+                \iff 
+                & 
+                \tilde \eta_{t + 1} \left(
+                    f(z_{t + 1}) - f(x_*)
+                \right) + \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2 
+                - \frac{1}{2}\Vert x_{t} - x_*\Vert^2  =: \Upsilon_{1, t + 1}^{\text{AG}}
+                \\
+                &\quad \le 
+                -\frac{1}{2} \Vert x_{t + 1 } - x_t\Vert^2 + 
+                \frac{\tilde \eta_{t + 1}}{2}\Vert z_{t + 1} - y_t\Vert^2 
+                - \langle \tilde \eta_{t + 1}\nabla f(y_t), x_{t + 1} - z_{t + 1} \rangle. 
+            \end{align*}
+            }
+            Observe that, the rhs and lhs of the Lyapunov inequality are anchored at $z_{t + 1}$. 
+            Similarly for the descent inequality we wish to obtain: 
+            \begin{align*}
+                f(z_{t + 1}) - f(z_t) &= f(z_{t + 1}) - f(y_t) + f(y_t) - f(z_t) 
+                \\
+                &\le 
+                \langle \nabla f(y_t), z_{t + 1} - y_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2 
+                + 
+                \langle \nabla f(y_t), y_t - z_t\rangle
+                \\
+                &= 
+                \langle \nabla f(y_t), z_{t + 1} - z_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                \\
+                \text{let }\Upsilon_{2, t + 1}^{\text{AG}} 
+                &:= f(z_{t + 1}) - f(z_t). 
+            \end{align*}
+            Which is the descent inequality anchored on $z_{t + 1}$.
+            Merging the $(z_{t + 1} - y_t)$ with $y_t - z_t$ together yield the desired results. 
+        \end{proof}
+
+        \begin{lemma}[Nonsmooth Generic AG Lyapunov Analysis]
+        \label{lemma:nsmooth_agg_lyapunov_upper_bound}
+            Continue from 
+            \hyperref[prop:derive_ag_prox_grad_tript]
+            {definition \ref*{prop:derive_ag_prox_grad_tript}},
+            we derive the non-smooth analogous case of the Lyapunov upper bound: 
+            \begin{align*}
+                \Upsilon_{1, t + 1}^\text{AG}
+                &= 
+                \tilde\eta_{t + 1} (h(z_{t + 1}) - h(x_*)) + 
+                \frac{1}{2} (
+                    \Vert x_{t + 1} - x_*\Vert^2
+                    - 
+                    \Vert x_t - x_*\Vert^2
+                )
+                \\
+                &\le 
+                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+                + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                - \langle 
+                    \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+                    x_{t + 1} - z_{t + 1}
+                \rangle
+                \\
+                \Upsilon_{2, t + 1}^\text{AG}
+                &= 
+                h(z_{t + 1}) - h(z_t) 
+                \le 
+                \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
+                \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            Define 
+            \begin{align*}
+                \phi_t(u) &:= 
+                \tilde \eta_{t + 1} 
+                \left(
+                    f(y_t) + g(y_t) + \langle \nabla f(y_t) + \partial g(y_t^+), u - y_t\rangle
+                    + 
+                    \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
+                \right)\\
+                &= 
+                \tilde \eta_{t + 1} \left(
+                    f(y_t) + \langle \nabla f(y_t), u - y_t\rangle + 
+                    \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
+                    + 
+                    g(y_t) + \langle \partial g(y_t^+), u - y_t\rangle
+                \right). 
+            \end{align*}
+            Then the update in the Generic Tri-Point algorithm 
+            (\hyperref[def:ag_prox_grad_ppm]
+                {definition \ref*{def:ag_prox_grad_ppm}}) 
+            has $x_{t + 1} = \prox{\phi_t}(x_t)$ and therefore we can use the Lyapunov inequality for PPM (\hyperref[thm:ppm_descent_ineq]
+                {theorem \ref*{thm:ppm_descent_ineq}})
+            which gives for all $x_*$: 
+            \begin{align*}
+                & \phi_t(x_{t + 1}) - \phi_t(x_*) + 
+                \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
+                \frac{1}{2}\Vert x_t - x_*\Vert^2
+                \le \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2, 
+                \\
+                & \text{where }
+                \phi_t(x_{t + 1}) =
+                \\
+                & \quad 
+                \tilde \eta_{t + 1}
+                \left(
+                    f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle + 
+                    \frac{1}{2\tilde \eta_{t + 1}}\Vert x_{t + 1} - x_t\Vert^2
+                    + 
+                    g(y_t) + \langle \partial g(y_t^+), x_{t + 1} - y_t\rangle
+                \right). 
+            \end{align*}
+            to simplify, consider using the $L$-smoothness of $f$, we have the inequality: 
+            \begin{align*}
+                \begin{aligned}
+                    f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle
+                    &=
+                    f(y_t) + \langle \nabla f(y_t), (x_{t +1} - z_{t + 1}) + (z_{t + 1} - y_t) \rangle
+                    \\
+                    &\ge 
+                    f(z_{t + 1}) - \frac{L}{2} \Vert z_{t + 1} - y_t\Vert^2 + 
+                    \langle \nabla f(y_t), x_{t +1} - z_{t + 1}\rangle
+                    \\
+                    &= 
+                    f(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2
+                    + \langle \nabla f(y_t), x_{t + 1} - y_t^+\rangle.     
+                \end{aligned}
+                \tag{$[*]$}
+            \end{align*}
+            further consider
+            \begin{align*}
+                \begin{aligned}
+                    g(y_t) + \langle \partial g(y_t^+), x_{t + 1} - y_t\rangle 
+                    &= g(y_t) + 
+                    \langle \partial g(y_t^+), 
+                    x_{t + 1} - y_t^+ + y_t^+ - y_t
+                    \rangle
+                    \\
+                    &= g(y_t) 
+                    + \langle \partial g (y_t^+),
+                        x_{t + 1} - y_t^+
+                    \rangle
+                    + 
+                    \langle 
+                        \partial g(y_t^+), y_t^+ - y_t
+                    \rangle
+                    \\
+                    g \text{ convex }\implies 
+                    &\ge 
+                    g(y_t^+) + 
+                    \langle \partial g(y_t^+), x_{t + 1} - y_t^+\rangle. 
+                \end{aligned}
+                \tag{$[\star]$}
+            \end{align*}
+            In the $([\star])$ derivation, we used the convexity of $g$ where 
+            \begin{align*}
+                \langle \partial g(y_t^+), y_t - y_t^+\rangle
+                &\le g(y_t) - g(y_t^+)
+                \\
+                \langle \partial g (y_t^+), y_t^+ - y_t \rangle
+                &\le 
+                g(y_t^+) - g(y_t). 
+            \end{align*}
+            Now, adding $([*]), ([\star])$, multiply their sum by $\tilde\eta_{t + 1}$ makes it equals to $\phi_t(x_{t +1 })$ , we can establish a lower bound for $\phi_t(x_{t + 1})$, yielding inequality
+            {\small
+                \begin{align*}
+                    \phi_t(x_{t + 1})
+                    &\ge 
+                    \tilde\eta_{t + 1}
+                    \left(
+                        f(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2 
+                        +
+                        \langle \nabla f(y_t), x_{t + 1} - y_t^+\rangle
+                        + 
+                        g(y_t^+) + 
+                        \langle \partial g(y_t^+), x_{t + 1} - y_t^+\rangle
+                    \right) 
+                    \\
+                    &= 
+                    \tilde\eta_{t + 1}
+                    \left(
+                        h(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2 
+                        + 
+                        \langle \partial g(y_t^+) + \nabla f(y_t), x_{t + 1} - y_t^+\rangle
+                    \right).
+                \end{align*}
+            }
+            Apply
+            \hyperref[lemma:grad_map_lemma_first]{lemma \ref*{lemma:grad_map_lemma_first}} 
+            we have $\partial g(y_t^+) + \nabla f(y_t) \ni \mathcal G_L(y_t)$, and by the algorithm updates $y_t^+ = z_{t + 1}$, therefore the above inequality simplifies to 
+            \begin{align*}
+                \phi_t(x_{t + 1}) &\ge 
+                \tilde\eta_{t + 1} 
+                \left(
+                    h(z_{t + 1}) - 
+                    \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                    + 
+                    \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
+                \right). 
+            \end{align*}
+            Finally, from (\hyperref[lemma:grad_map_linearization]
+                {lemma \ref*{lemma:grad_map_linearization}})
+            we have $\phi_t(u) \le \tilde\eta_{t + 1}h(u)$ for all $u$. 
+            With that we lower bound the LHS of the PPM Lyapunov inequality of $\phi_t(u)$, making: 
+            {\footnotesize
+            \begin{align*}
+                & \phi_t(x_{t + 1}) - \phi_t(x_*) + 
+                \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
+                \frac{1}{2}\Vert x_t - x_*\Vert^2
+                \le
+                \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+                \\
+                \implies &
+                \tilde \eta_{t + 1}
+                \left(
+                    h(z_{t + 1}) - 
+                    \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                    + 
+                    \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
+                \right) - \tilde \eta_{t + 1} h(x_*)
+                +
+                \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
+                \frac{1}{2}\Vert x_t - x_*\Vert^2
+                \\
+                & \quad \le
+                \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+                \\
+                \iff &
+                \tilde\eta_{t + 1}(h(z_{t + 1}) - h(x_*))
+                + \frac{1}{2}\left(
+                    \Vert x_{t + 1} - x_*\Vert^2 
+                    - 
+                    \Vert x_t - x_*\Vert^2
+                \right) := \Upsilon_{1, t + 1}^\text{AG}
+                \\
+                &\quad \le 
+                \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+                - 
+                \tilde\eta_{t + 1}
+                \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
+                + 
+                \frac{L \tilde\eta_{t + 1}}{2}\Vert z_{t + 1} - y_t\Vert^2. 
+            \end{align*}
+            }
+            It established the first inequality that we wish to prove. 
+            Next, the smoothness of $f$ establish inequality: 
+            \begin{align*}
+                \begin{aligned}
+                    f(z_{t + 1}) - f(z_t) &= f(z_{t + 1}) - f(y_t) + f(y_t) - f(z_t) 
+                    \\
+                    &\le 
+                    \langle \nabla f(y_t), z_{t + 1} - y_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2 
+                    + 
+                    \langle \nabla f(y_t), y_t - z_t\rangle
+                    \\
+                    &= 
+                    \langle \nabla f(y_t), z_{t + 1} - z_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
+                \end{aligned}
+                \tag{$[**]$}
+            \end{align*}
+            The convexity of $h$ establish 
+            \begin{align*}
+                \begin{aligned}
+                    g(z_{t + 1}) + 
+                    \langle \partial g(z_{t + 1}), z_t - z_{t + 1}\rangle
+                    &\le g(z_t)
+                    \\
+                    g(z_{t + 1}) - g(z_t)
+                    &\le 
+                    \langle 
+                        \partial g (z_{t +1}), 
+                        z_{t + 1} - z_t
+                    \rangle. 
+                \end{aligned}
+                \tag{$[\star *]$}    
+            \end{align*}
+            Adding $([**]), ([\star *])$ yields 
+            \begin{align*}
+                \begin{aligned}
+                    \Upsilon_{2, t + 1}^{\text{AG}} := 
+                    h(z_{t + 1}) - h(z_t) 
+                    &\le 
+                    \langle 
+                        \nabla f(y_t) + \partial g(z_{t+1}), 
+                        z_{t + 1} - z_t
+                    \rangle + 
+                    \frac{L}{2}
+                    \Vert 
+                        z_{t + 1} - y_t
+                    \Vert^2. 
+                \end{aligned}
+            \end{align*}
+            Using the property of gradient mapping (\hyperref[lemma:grad_map_lemma_first]
+                {lemma \ref*{lemma:grad_map_lemma_first}}), 
+            $\mathcal G_L(y_t) \in \nabla f(y_t) + \partial g(z_{t + 1})$, substituting it, we proved all we want to show. 
+        \end{proof}
+
+        \begin{theorem}[Generic AG Convergence]
+        \label{thm:generic_ag_convergence}
+            If there is a choice of $\eta_i, \tilde \eta_i$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} such that we have 
+            \begin{align*}
+                \left(
+                    \sum_{i = 1}^{t} \tilde \eta_i
+                \right)
+                \Upsilon_{2, t + 1}^{\text{AG}} + 
+                \Upsilon_{1, t + 1}^{\text{AG}} \le 0, 
+            \end{align*}
+            then with 
+            \begin{align*}
+                \Phi_t &= \left(
+                    \sum_{i = 1}^{t} \tilde\eta_{i}
+                \right) (f(z_t) - f(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \NN
+                \\
+                \Phi_0 &= \frac{1}{2}\Vert x_t - x_*\Vert^2, 
+            \end{align*}
+            we have $\Phi_{t + 1} - \Phi_t \le 0$, which allows for a convergence rate of $\mathcal O \left(\sum_{i = 1}^{T} \eta_i^{-1}\right)$ for $f(z_T) - f(x_*)$. 
+        \end{theorem}
+        \begin{proof}
+            By definition we have
+            {\footnotesize
+            \begin{align*}
+                \Phi_{t + 1} - \Phi_t 
+                &= 
+                \left(
+                    \sum_{i = 1}^{t+1} \tilde\eta_{i}
+                \right) (f(z_{t + 1}) - f(x_*)) 
+                - 
+                \left(
+                    \sum_{i = 1}^{t} \tilde\eta_{i}
+                \right) (f(z_{t}) - f(x_*)) 
+                + \frac{1}{2}\Vert x_t - x_*\Vert^2
+                - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
+                \\
+                &= 
+                \tilde \eta_{t + 1} (f(z_{t + 1}) - f(z_*))
+                +
+                \left(
+                    \sum_{i = 1}^{t} \tilde \eta_i
+                \right)(f(z_{t + 1}) - f(z_t))
+                + \frac{1}{2}\Vert x_t - x_*\Vert^2
+                - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
+                \\
+                &= \left(
+                    \sum_{i = 1}^{t} \tilde \eta_i
+                \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le 0. 
+            \end{align*}
+            }
+            The derivation for the convergence raet is direct and similar to 
+            \hyperref[thm:ppm_convergence_rate]{theorem \ref*{thm:ppm_convergence_rate}} 
+            Therefore, if we can identify parameter for the generic algorithm that asserts the condition above, then we have convergence for the algorithm. 
+        \end{proof}
+
+    \subsection{Scenario I}
+        In this scenario, we aim to recover AG Ryu 12.1 conceret variant algorithm stated back in 
+        \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}. 
+        \begin{proposition}
+            Continue from
+            \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}, 
+            set $\eta_{t + 1} = \tilde \eta_{t + 1} = (t)/(2L)$, we derive the following algorithm: 
+            \begin{align*}
+                x_{t + 1} &= x_t - \frac{t + 1}{2L} \mathcal G_L(y_t), 
+                \\
+                z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t), 
+                \\
+                y_{t + 1} &= 
+                \left(
+                    \frac{2}{t + 3}
+                \right)x_{t +1} + 
+                \left(
+                    1 - \frac{2}{t + 3}
+                \right)z_{t + 1}. 
+            \end{align*}
+            This algorithm has convergence rate of $\mathcal O(1/T^2)$ for all $h = f + g$ where $f$ is convex $L$-Lipschitz smooth and $g$ is convex. 
+        \end{proposition}
+        \begin{observation}
+            Observe that when $g \equiv 0$ this is the same algorithm as 
+            \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}
+            but with an alternative choice of indexing for $y_t$ and initial condition. 
+        \end{observation}
+        \begin{proof}
+            Recall that for the proximal gradient PPM generic form we have iterate updates for $t\in \mathbb N$: 
+            \begin{align*}
+                y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
+                \\
+                x_{t + 1} &= x_t - \tilde \eta_{t + 1} \mathcal G_L(y_t)
+                \\
+                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t). 
+            \end{align*}
+            and generic Lyapunov upper bound 
+            \begin{align*}
+                \Upsilon_{1, t + 1}^\text{AG}
+                &= 
+                \tilde\eta_{t + 1} (h(z_{t + 1}) - h(x_*)) + 
+                \frac{1}{2} (
+                    \Vert x_{t + 1} - x_*\Vert^2
+                    - 
+                    \Vert x_t - x_*\Vert^2
+                )
+                \\
+                &\le 
+                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+                + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                - \langle 
+                    \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+                    x_{t + 1} - z_{t + 1}
+                \rangle
+                \\
+                \Upsilon_{2, t + 1}^\text{AG}
+                &= 
+                h(z_{t + 1}) - h(z_t) 
+                \le 
+                \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
+                \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
+            \end{align*}
+            By the updates, vector $x_{t + 1} - x_t$ and $z_{t + 1} - y_t$ are parallel by observations 
+            \begin{align*}
+                x_{t + 1} - x_t &= -\tilde\eta_{t + 1}\mathcal G_L(y_t), 
+                \\
+                z_{t + 1} - y_t &= -L^{-1}\mathcal G_L(y_t). 
+            \end{align*}
+            This setup allows for: 
+            \begin{align*}
+                \Upsilon_{1, t + 1}^{\text{AG}} 
+                &\le 
+                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 + 
+                \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2 
+                - 
+                \langle \tilde\eta_{t + 1}\mathcal G_L (y_t), x_{t + 1} - z_{t + 1} \rangle
+                \\
+                &= 
+                - \frac{1}{2}\Vert \tilde\eta_{t + 1} \mathcal G_L\Vert^2 + 
+                \frac{\tilde\eta_{t + 1}L}{2}\Vert L^{-1} \mathcal G_L(y_t)\Vert^2
+                - 
+                \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), x_{t + 1} - z_{t + 1} \rangle
+                \\
+                &= 
+                \frac{1}{2}\left(
+                    - \tilde\eta_{t + 1}^2 + 
+                    L^{-1}\tilde\eta_{t + 1}
+                \right)\Vert \mathcal G_L(y_t)\Vert^2
+                - 
+                \langle 
+                    \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+                    (x_{t + 1} - x_{t}) + x_t
+                    + (y_t - z_{t + 1}) - y_t
+                \rangle
+                \\
+                &= 
+                \frac{1}{2}\left(
+                    L^{-1}\tilde\eta_{t + 1}
+                    - \tilde\eta_{t + 1}^2
+                \right)\Vert \mathcal G_L(y_t)\Vert^2
+                - 
+                \langle 
+                    \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+                    -\tilde\eta_{t + 1}\mathcal G_L(y_t) + x_t 
+                    + L^{-1}\mathcal G_L(y_t) - y_t
+                \rangle
+                \\
+                &= 
+                \frac{1}{2}\left(
+                    L^{-1}\tilde\eta_{t + 1}
+                    - \tilde\eta_{t + 1}^2
+                \right)\Vert \mathcal G_L(y_t)\Vert^2
+                - \langle 
+                    \tilde\eta_{t +1}\mathcal G_L(y_t), 
+                    (L^{-1} - \tilde\eta_{t + 1})\mathcal G_L(y_t) + x_t - y_t
+                \rangle
+                \\
+                &= \frac{1}{2}\left(
+                    L^{-1}\tilde\eta_{t + 1} - \tilde\eta_{t + 1}^2 
+                    + 2 \tilde\eta_{t + 1}^2 - 2\tilde\eta_{t + 1}L^{-1}
+                \right)\Vert \mathcal G_L(y_t)\Vert^2
+                - 
+                \langle 
+                    \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+                    x_t - y_t
+                \rangle
+                \\
+                &= 
+                \frac{1}{2}\left(
+                    \tilde\eta_{t + 1}^2 - \tilde\eta_{t + 1}L^{-1}
+                \right)\Vert \mathcal G_L(y_t)\Vert^2 
+                + \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), y_t - x_t\rangle
+            \end{align*}
+            similarly we also have upper bound 
+            \begin{align*}
+                \Upsilon_{2, t + 1}^{\text{AG}} 
+                &= 
+                \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
+                \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                \\
+                &= 
+                \langle \mathcal G_L(y_t), z_{t + 1} - y_t + y_t - z_t\rangle
+                + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                \\
+                &= 
+                \langle \mathcal G_L(y_t), - L^{-1} \mathcal G_L(y_t) + y_t - z_t\rangle
+                + 
+                \frac{L}{2}\Vert L^{-1}\mathcal G_L(y_t)\Vert^2
+                \\
+                &= 
+                -L^{-1}\Vert \mathcal G_L(y_t)\Vert^2 
+                + 
+                (1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2 
+                + 
+                \langle \mathcal G_L(y_t), y_t - z_t\rangle
+                \\
+                &= 
+                -(1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2
+                + 
+                \langle \mathcal G_L(y_t), y_t - z_t\rangle
+            \end{align*}
+            Observe that the cross product term for $\Upsilon_{1, t + 1}^\text{AG}, \Upsilon_{2, t + 1}^\text{AG}$ doesn't match. 
+            Hence let's consider the update for $y_t$, which can be written as $y_t - x_t = L \eta_t (z_t - y_t)$.
+We make the choice to do surgery on upper bound of $\Upsilon_{2, t + 1}^\text{AG}$, so $\langle \mathcal G_L(y_t), y_t - x_t\rangle = \langle \mathcal G_L(y_t), L \eta_t (z_t - y_t)\rangle$.
+            With this in mind, applying the RHS of $[(*)]$ yields: 
+            {\footnotesize
+            \begin{align*}
+                &\Upsilon_{1, t + 1}^\text{AG} + 
+                \left(
+                    \sum_{i = 1}^{t}\tilde\eta_i 
+                \right)\Upsilon_{1, t + 1}^{\text{AG}}
+                \\
+                &\le 
+                \frac{1}{2}\left(
+                    \tilde\eta_{t + 1}^2 - \tilde\eta_{t + 1}L^{-1}
+                \right)\Vert \mathcal G_L(y_t)\Vert^2 
+                + 
+                \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), L\eta_t(z_t - y_t)\rangle
+                \\
+                &\quad 
+                + 
+                \left(
+                    \sum_{i = 1}^{t}\tilde\eta_i 
+                \right)\left(
+                    -(1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2
+                    + 
+                    \langle \mathcal G_L(y_t), y_t - z_t\rangle
+                \right)
+                \\
+                &= 
+                \left(
+                    \frac{1}{2}\tilde\eta_{t + 1}\left(
+                        \tilde \eta_{t +1} - L^{-1}
+                    \right)
+                    - 
+                    \frac{1}{2L}\sum_{i = 1}^{t}\tilde \eta_i
+                \right)\Vert \mathcal G_L(y_t)\Vert^2 + 
+                \left(
+                    L\eta_t \tilde \eta_{t + 1} - \sum_{i = 1}^{t}\tilde \eta_i
+                \right)\langle \mathcal G_L(y_t), z_t - y_t\rangle
+            \end{align*}
+            }
+            If the algorithm were to have the abstract convergence rate as stated in 
+            \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}},
+            then one of the sufficient condition is to have the above quantity less than or equal to zero, one sufficient condition of that is to have the coefficient for $\Vert \mathcal G_L(y_t)\Vert$ be $\le 0$, and the coefficient of the cross term $\langle \mathcal G_L(y_t), z_t - y_t\rangle$ be zero.
+            To simplify, we make the assumption that $\tilde \eta_t = \eta_t$ for all $t \in \mathcal N$, making it to be a specific instance of 
+            \hyperref[def:ag_tri_pt_form_E]{definition \ref*{def:ag_tri_pt_form_E}}. 
+            These conditions translate to the following relations for $\eta_{t}$. 
+            \begin{align*}
+                \begin{cases}
+                    L\eta_{t + 1}^2 + \eta_{t + 1} - \sum_{i = 1}^{t}\eta_i 
+                    \le 0, 
+                    \\
+                    L\eta_t \eta_{t + 1} - \sum_{i = 1}^{t} \eta_i 
+                    = 0. 
+                \end{cases}
+            \end{align*}
+            Substituting the sequence equality back to the first one yield: 
+            \begin{align*}
+                L\eta_{t + 1}^2 - (\eta_{t + 1} + L\eta_t\eta_{t + 1}) &\le 0 
+                \\
+                L\eta^2_{t + 1} - \eta_{t + 1}
+                &\le 
+                L\eta_t \eta_{t + 1} 
+                \\
+                \eta_{t + 1}(L\eta_{t + 1} - 1) 
+                &\le L\eta_t\eta_{t + 1}
+                \\
+                \eta_t > 0 
+                \implies 
+                L\eta_{t + 1} - 1 &\le 
+                L\eta_t 
+                \\
+                \eta_{t + 1} &\le \eta_t + L^{-1}. 
+            \end{align*}
+            To satisfy the equality, reader should verify that $\eta_{t} = t/(2L)$ or $\eta_t = (t + 1)/2L$ are some of the options. 
+        \end{proof}
+        \begin{remark}
+            In the original writing by Ahn \cite[equation (4.9)]{ahn_understanding_2022}, they didn't identify this specific variant in the literature. 
+            Here we identify it to be equivalent to the acceleration algorithm stated in Ryu \cite[algorithm 12.1]{ryu_large-scale_2022}. 
+        \end{remark}
+
+    \subsection{Scenario II}
+        With the choice of $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we can recover the seminal Nesterov accelerated gradient algorithm from 1983. 
+        The variants proposed by Chambolle Dossal \cite{chambolle_convergence_2015}, is distinct from the possibility proposed in this secenario. 
+        % Recall similar a lemma about similar triangle form here.
+
         \begin{lemma}[Deriving the Nesterov Sequence]
@@
             Hence, the upper bound of the Lyapunov function for smooth AG PPM 
-            (\hyperref[thm:generic_smooth_ag_convergence]{theorem \ref*{thm:generic_smooth_ag_convergence}}) 
+            (\hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}) 
             has 

### 2024-07-08 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, updated notes

@@
     They are abstract because the choice of stepsize parameters in the algorithms are unspecified. 
+    Abstract forms related to the proximal gradient method were our own inventions inspired by discussions in the literatures, which includes 
+    \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}, and 
+    \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}. 
     In \hyperref[sec:AG_useful_information]{section \ref*{sec:AG_useful_information}}
     we prove and interpret some of the unproved claims made by Ahn, Sra \cite{ahn_understanding_2022} as good exercises and for the peace of the mind. 
-    \hyperref[lemma:smooth_agg_lyapunov_upper_bound]{Lemma \ref*{lemma:smooth_agg_lyapunov_upper_bound}} 
-    rephrase content in the appendix in work by Ahn, Sra\cite{ahn_understanding_2022}. 
-    It is our attempt at rephrasing the proofs to create a layer of abstraction so it can be reused for multiple proofs for several variants.
+    In
+    \hyperref[sec:generic_ag_ppm_lyapunov_analysis]{section \ref*{sec:generic_ag_ppm_lyapunov_analysis}},
+    we state two important theorems for the derivation of convergences rate for various type of algorithm using an upper bound of a Lyapunov function. 
+    This part is inspired by works from Ahn, Sra \cite{ahn_understanding_2022}, but with the gradient mapping and proximal gradient added into the picture, making it distinct from all algorithms discussed in Ahn and Sra's paper.
+    \hyperref[sec:scenario_i]{Section \ref*{sec:scenario_i}} and 
+    \hyperref[sec:scenario_ii]{\ref*{sec:scenario_ii}} derive the convergence rate and determine the parameters for the step sizes needed to achieve an optimal convergence rate. 
+    In each section, we recover a specific variant of the Accelerated gradient and identify their appearances in the literature.
 
@@
             \end{observation}
+            \begin{remark}
+                For more information about the specific choice of $\eta_t$ allows for an optimal convergence rates, see 
+                \hyperref[sec:scenario_ii]{section \ref*{sec:scenario_ii}} for more information. 
+            \end{remark}
 
@@
 
-            \begin{lemma}[Similar Triangule Form I via Generic Tri Points]
+            \begin{lemma}[Similar Triangle Form I via Generic Tri Points]
                 \quad \\
@@
                 \begin{align*}
-                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t) 
+                    z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t)
                     \\
@@
                 \begin{align*}
-                    z_{t + 1} &= y_t - L^{-1}\nabla f(y_t)
+                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
                     \\
@@
                 \begin{align*}
-                    x_{t + 1} &= y_t - L^{-1}\nabla f(y_t) 
-                    + L \eta_t y_t - \eta_t \nabla f(y_t) - L\eta_t z_t
-                    \\
-                    &= 
-                    (1 + L\eta_t)y_t - (\eta_t + L^{-1})\nabla f(y_t) - L\eta_t z_t
-                    \\
-                    &= \eta_t Lz_t + x_t -(\eta_t + L^{-1}) \nabla f(y_t)  - L\eta_t z_t
-                    \\
-                    &= x_t - (\eta_t + L^{-1})\nabla f(y_t). 
-                \end{align*}
-                By assumption $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we ends with $x_{t + 1} = x_t + \tilde \eta_{t + 1}\nabla f(y_t)$. 
+                    x_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t) 
+                    + L \eta_t y_t - \eta_t \mathcal G_L(y_t) - L\eta_t z_t
+                    \\
+                    &= 
+                    (1 + L\eta_t)y_t - (\eta_t + L^{-1})\mathcal G_L(y_t) - L\eta_t z_t
+                    \\
+                    &= \eta_t Lz_t + x_t -(\eta_t + L^{-1}) \mathcal G_L(y_t)  - L\eta_t z_t
+                    \\
+                    &= x_t - (\eta_t + L^{-1})\mathcal G_L(y_t). 
+                \end{align*}
+                So $x_{t + 1} = x_t + \tilde \eta_{t + 1}\mathcal G_L(y_t)$, by assumption $\tilde \eta_{t + 1} = \eta_t + L^{-1}$
                 Reducing it to the classic momentum form starts by 
@@
                 \begin{align*}
-                    z_{t + 1} &= y_t - L^{-1}\nabla f(y_t)
+                    z_{t + 1} &= y_t - L^{-1} \mathcal G_L f(y_t)
                     \\
@@
             \begin{remark}
-                In this remark we clarify the name ``similar triangule" as given in the literatures. 
+                In this remark we clarify the name ``similar triangle" as given in the literatures. 
                 We think it is a fitting name, becaues it has a similar triangle in it. 
@@
                     \item 
-                    The updates for $z_{t + 1}, x_{t + 1}$ are based on $y_t, x_t$ displaced by $L^{-1}\nabla f(y_t), \tilde\eta_{t +1}\nabla f(y_t)$, therefore vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$.
+                    The updates for $z_{t + 1}, x_{t + 1}$ are based on $y_t, x_t$ displaced by $L^{-1} \mathcal G_L(y_t), \tilde\eta_{t +1} \mathcal G_L(y_t)$, therefore vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$.
                     \item The updates for $x_{t + 1}$ has $x_{t + 1} - z_{t + 1} = L\eta_t \left(z_{t + 1} - z_t\right)$, therefore, the three points $z_t, x_{t + 1}, z_{t + 1}$ are collinear. 
@@
                 By these tree observations, the triangle $z_{t}, z_{t + 1}, y_t$ similar to triangle $z_t, x_{t + 1}, x_t$. 
+                Finally, similar remarks about the similar triangle form can be found in Ahn, Sra's paper \cite{ahn_understanding_2022} as well. 
             \end{remark}
-            The next lemma will determine one choice of the stepsize sequence $\eta_t$ that recovers the classical form of Nesterov accelerated gradient method.
 
     \subsection{Generic Lyapunov analysis for Accelerated gradient via PPM}
+    \label{sec:generic_ag_ppm_lyapunov_analysis}
         The first theorem states the generic convergence results when $f$ is differentiable with $L$-Lipschitz gradient, using \hyperref[def:agg_ppm]{definition\ref*{def:agg_ppm}}.
-        \begin{lemma}[Smooth Generic AG Lyapunov Analysis]\label{lemma:smooth_agg_lyapunov_upper_bound}
-            With $f$ having $L$-Lipschitz gradient and minimizer $x_*$, using 
-            \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} with $\mu = 0$
-            and 
-            \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} ,
-            then we can derive the upper bounds for the RHS of the PPM descent inequality: 
-            \begin{align*}
-                \Upsilon_{1, t + 1}^{\text{AG}}
-                &= \tilde \eta_{t + 1} (f(z_{t + 1}) - f(x_*))
-                + \frac{1}{2}(
-                    \Vert x_{t + 1} - x_*\Vert^2 - \Vert x_t - x_* \Vert^2
-                )  
-                \\
-                & \quad \le 
-                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 + 
-                \frac{\tilde \eta_{t + 1} L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                - 
-                \langle \tilde \eta_{t + 1} \nabla f(y_t), x_{t + 1} - z_{t + 1} \rangle, 
-                \\
-                \Upsilon_{2, t + 1}^{\text{AG}} 
-                &= f(z_{t + 1}) - f(z_t) 
-                \le 
-                \langle \nabla f(y_t), z_{t + 1} - z_t\rangle + 
-                \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-            \end{align*}
-        \end{lemma}
-        \begin{proof}
-            Define $\phi_t(x) = \tilde \eta_{t +1}(f(y_t) + \langle \nabla f(y_t), x- y_t\rangle)$.  
-            With $L$-smoothness of $f$ in mind, consider the following sequence of inequalities: 
-            $$
-            \begin{aligned}
-                \phi_t(x_{t + 1}) 
-                &= 
-                \tilde\eta_{t + 1} (f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle)
-                \\
-                \phi_t (x_{t + 1}) &= \tilde \eta_{t + 1}(
-                    f(y_t) + \langle \nabla f(y_t), (x_{t +1} - z_{t + 1}) + (z_{t + 1} - y_t) \rangle
-                )
-                \\
-                &\ge 
-                \tilde \eta_{t + 1}
-                \left(
-                    f(z_{t + 1}) - \frac{L}{2} \Vert z_{t + 1} - y_t\Vert^2 + 
-                    \langle \nabla f(y_t), x_{t +1} - z_{t + 1}\rangle
-                \right), 
-            \end{aligned}
-            $$
-            the AG generic performs PPM on $\phi_t$ to produce $x_{t + 1}$ so the PPM Lyapunov inequality from 
-            \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} applies,
-            substituting yields equivalences for all $x_*$: 
-            {\footnotesize
-            \begin{align*}
-                & \phi_t(x_{t + 1}) - \phi_t(x_*) + \frac{1}{2}\Vert x_* - x_{t + 1}\Vert^2 
-                - \frac{1}{2}\Vert x_* - x_t\Vert^2 
-                \\
-                &\quad \le 
-                - \frac{1}{2} \Vert x_{t + 1} - x_t\Vert^2 
-                \\
-                \implies & 
-                \tilde \eta_{t + 1}\left(
-                    f(z_{t + 1}) - \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2 
-                    + 
-                    \langle \nabla f(y_t), x_{t + 1} - z_{t + 1}\rangle
-                \right) - \tilde \eta_{t + 1} f(x_*)
-                + 
-                \frac{1}{2}\left(
-                    \Vert x_{t + 1} - x_*\Vert^2 - \Vert x_{t} - x_*\Vert^2
-                \right)
-                \\
-                &\quad \le
-                 - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-                \\
-                \iff 
-                & 
-                \tilde \eta_{t + 1} \left(
-                    f(z_{t + 1}) - f(x_*)
-                \right) + \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2 
-                - \frac{1}{2}\Vert x_{t} - x_*\Vert^2  =: \Upsilon_{1, t + 1}^{\text{AG}}
-                \\
-                &\quad \le 
-                -\frac{1}{2} \Vert x_{t + 1 } - x_t\Vert^2 + 
-                \frac{\tilde \eta_{t + 1}}{2}\Vert z_{t + 1} - y_t\Vert^2 
-                - \langle \tilde \eta_{t + 1}\nabla f(y_t), x_{t + 1} - z_{t + 1} \rangle. 
-            \end{align*}
-            }
-            Observe that, the rhs and lhs of the Lyapunov inequality are anchored at $z_{t + 1}$. 
-            Similarly for the descent inequality we wish to obtain: 
-            \begin{align*}
-                f(z_{t + 1}) - f(z_t) &= f(z_{t + 1}) - f(y_t) + f(y_t) - f(z_t) 
-                \\
-                &\le 
-                \langle \nabla f(y_t), z_{t + 1} - y_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2 
-                + 
-                \langle \nabla f(y_t), y_t - z_t\rangle
-                \\
-                &= 
-                \langle \nabla f(y_t), z_{t + 1} - z_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                \\
-                \text{let }\Upsilon_{2, t + 1}^{\text{AG}} 
-                &:= f(z_{t + 1}) - f(z_t). 
-            \end{align*}
-            Which is the descent inequality anchored on $z_{t + 1}$.
-            Merging the $(z_{t + 1} - y_t)$ with $y_t - z_t$ together yield the desired results. 
-        \end{proof}
 
@@
 
-    \subsection{Scenario I}
+    \subsection{Scenario I}\label{sec:scenario_i}
         In this scenario, we aim to recover AG Ryu 12.1 conceret variant algorithm stated back in 
@@
 
-    \subsection{Scenario II}
+    \subsection{Scenario II}\label{sec:scenario_ii}
         With the choice of $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we can recover the seminal Nesterov accelerated gradient algorithm from 1983. 
         The variants proposed by Chambolle Dossal \cite{chambolle_convergence_2015}, is distinct from the possibility proposed in this secenario.
-        % Recall similar a lemma about similar triangle form here.
 
@@
             \end{align*}
-            allows \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}} to converge at an optimal rate. 
+            allows \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}} to converge at an optimal rate. 
             The base case is $\eta_0 = 0$. 
@@
         \begin{proof}
-            Continue from \ref*{lemma:smooth_agg_lyapunov_upper_bound}, With $x_{t +1} - x_t = L\tilde\eta_{t+1}(z_{t + 1} - y_t)$ for $y_t$: 
+            Continue from 
+            \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]{lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}, 
+            With $x_{t +1} - x_t = L\tilde\eta_{t+1}(z_{t + 1} - y_t)$ for $y_t$: 
             \begin{align*}
                 \Upsilon_{1, t + 1}^\text{AG} &\le 
-                - \frac{1}{2}\Vert x_{t+1 } - x_t\Vert^2 + 
-                \frac{\tilde\eta_{t +1}L}{2}\Vert z_{t+1} - y_t\Vert^2
+                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+                    + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                    - \langle 
+                        \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+                        x_{t + 1} - z_{t + 1}
+                    \rangle
                     \\
@@
                     \frac{\tilde\eta_{t +1}L}{2}\Vert z_{t+1} - y_t\Vert^2
+                    - \langle 
+                        \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+                        x_{t + 1} - z_{t + 1}
+                    \rangle
                     \\
@@
                     \langle 
-                    \tilde \eta_{t+ 1} \nabla f(y_t), x_{t+1} - z_{t+1}
+                        \tilde \eta_{t+ 1} \mathcal G_L(y_t), x_{t+1} - z_{t+1}
                     \rangle. 
@@
             \begin{align*}
-                \Upsilon_{2, t + 1}^{\text{AG}} &= 
-                \langle \nabla f(y_t), z_{t+1} - y_t\rangle
-                + 
-                \frac{L }{2} \Vert z_{t+1} - y_t\Vert^2 + 
-                \langle \nabla f(y_t), y_t - z_t\rangle
-                \\
-                &= 
-                \langle \nabla f(y_t), z_{t + 1} - z_t\rangle
+                \Upsilon_{2, t + 1}^{\text{AG}} 
+                &= 
+                \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle
                 + 
@@
                 &= 
-                \langle \nabla f(y_t), L^{-1}\eta_t^{-1}(x_{t+1} - z_{t + 1})\rangle
+                \langle \mathcal G_L(y_t), L^{-1}\eta_t^{-1}(x_{t+1} - z_{t + 1})\rangle
                 + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
@@
             has 
+            {\footnotesize
             \begin{align*}
@@
                     + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                \right). 
-            \end{align*}
-            If the above quantity less than or equal to zero, it will allow for convergence of the algorithm. 
+                \right)
+                \\
+                &= 
+                \frac{L}{2}
+                \left(
+                -\tilde\eta_{t + 1}^2 + \tilde\eta_{t + 1}
+                    + \sum_{i = 1}^{t}\tilde\eta_i
+                \right)\Vert z_{t + 1} - y_t\Vert^2
+                +
+                \left(
+                    L^{-1}\eta_t^{-1} 
+                    \left(
+                        \sum_{i = 1}^{t}\tilde \eta_i
+                    \right)
+                    -
+                    \tilde \eta_{t + 1}
+                \right)\langle \mathcal G_L (y_t), x_{t + 1} - z_{t + 1}\rangle
+            \end{align*}
+            }
+            If the above quantity less than or equal to zero, it will allow for convergence of the algorithm by 
+            \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}.
             One sufficient condition is to have the coefficients for all the cross product terms to sum up to zero, and the squared normed term to sum up to a non-positive number for all $t \in \mathbb N$.
@@
             \end{align*}
-            Combining yeilds that 
+            Combining yields that 
             \begin{align*}
@@
             \end{align*}
-            We had recovered the classic Nesterov accelerated sequence method for the smooth gradient descent algorithm. 
+            We had recovered the classic Nesterov acceleration sequence method for the smooth gradient descent algorithm. 
         \end{proof}
@@
             Under this choice, unfortunately, it's in no way obvious that this format reduces to \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
-            It fails the similar triangule description Without the explict representation $x_{n + 1} = z_n + \tilde\eta_{t + 1}\nabla f(y_t)$. 
+            It fails the similar triangle description Without the explict representation $x_{n + 1} = z_n + \tilde\eta_{t + 1}\nabla f(y_t)$. 
             \par\noindent

### 2024-07-17 Notebook LaTEX/Momentum Accelerations/main.tex
>w< motes updates

@@
                     \item[2.] sets $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$;
-                    \item[3.] chooses $y_k = (\gamma_k + \alpha_k \mu)(\alpha_k \gamma_k v_k + \gamma_{k + 1}x_k)$. Compute $f(y_k)$ and $\nabla f(y_k)$; 
+                    \item[3.] chooses $y_k = (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \gamma_{k + 1}x_k)$. Compute $f(y_k)$ and $\nabla f(y_k)$; 
                     \item[4.] finds $x_{k + 1}$ such that $f(x_{k + 1}) \le f(y_k) - (2L)^{-1} \Vert \nabla f(y_k)\Vert^2$; 
@@
                 $$
-                Omitting the superscript $f, g$ on $\mathcal P, \mathcal G$ for simplicity since it's clear in the context. 
+                Omitting the superscript $f, g$ on $\mathcal T, \mathcal G$ for simplicity since it's clear in the context. 
                 Define the linear lower bounding function for $f$ at $y$, for all $x$: 
@@
                 \begin{aligned}
-                    l_h(x; y) &= h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle \le f(x), 
+                    l_h(x; y) &= h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle \le h(x), 
                 \end{aligned}
                 $$
-                With that we define the algorithm:
+                with that we define the algorithm:
                 $$
@@
                     \left\lbrace
-                        g(x) + l_f(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
+                        l_h(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
                         \frac{1}{2\eta_{t + 1}} \Vert x - x_{t + 1}\Vert^2
@@
         \subsubsection{AG Concrete Examples}
-            In this section we state some variants of the Nesterov accelerated gradient method found in the literatures.
+            In this section we state variants of the Nesterov accelerated gradient method found in the literatures which are not generic.
 
@@
                 It goes over the full context and history for this particular variant of gradient acceleration method. 
-                As the time of composing this notes, the writer is still reading on the topic of accelerated gradient.     
+                At the time of composing this notes, the writer is still reading on the topic of accelerated gradient.     
             \end{remark}
@@
                 with the condition that $\tilde \eta_t = \eta_t$ for all $t \in \mathbb N$. 
-                As a consequence, the algorithm has the following updates for iterates $(y_t, x_{t + 1}, z_{t + 1})$. 
-                Giving us: 
+                As a consequence, the algorithm has the following updates for iterates $(y_t, x_{t + 1}, z_{t + 1})$: 
                 \begin{align*}
@@
                 \end{enumerate}
-                From the above results, we can conclude that triangle $(y_t, z_t, z_{t + 1})$ is similar to $(x_t, z_t, x_{t + 1})$ because they share colinear points $z_t, y_t, x_t$ and $z_t, z_{t + 1}, x_{t + 1}$, and their sides $z_{t + 1} - y_t$ parallels to $x_{t + 1} - z_t$.
+                From the above results, we can conclude that triangle $(y_t, z_t, z_{t + 1})$ is similar to $(x_t, z_t, x_{t + 1})$ because they share colinear points $z_t, y_t, x_t$ and $z_t, z_{t + 1}, x_{t + 1}$, and their sides $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$.
             \end{observation}
@@
                 Finally, similar remarks about the similar triangle form can be found in Ahn, Sra's paper \cite{ahn_understanding_2022} as well.
+
             \end{remark}
@@
     \label{sec:generic_ag_ppm_lyapunov_analysis}
-        The first theorem states the generic convergence results when $f$ is differentiable with $L$-Lipschitz gradient, using \hyperref[def:agg_ppm]{definition\ref*{def:agg_ppm}}.
+        The first theorem states the generic convergence results when $f$ is differentiable with $L$-Lipschitz gradient, using \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}.
 
@@
                 {definition \ref*{def:ag_prox_grad_ppm}}) 
-            has $x_{t + 1} = \prox{\phi_t}(x_t)$ and therefore we can use the Lyapunov inequality for PPM (\hyperref[thm:ppm_descent_ineq]
+            has $x_{t + 1} = \hprox_{\phi_t}(x_t)$ and therefore we can use the Lyapunov inequality for PPM (\hyperref[thm:ppm_descent_ineq]
                 {theorem \ref*{thm:ppm_descent_ineq}})

### 2024-08-01 Notebook LaTEX/Momentum Accelerations/main.tex
>w< home, work sync
>w< work home sync

@@
                 + 
-                \langle \mathcal G_L(y_t), y_t - z_t\rangle
+                \langle \mathcal G_L(y_t), y_t - z_t\rangle. 
             \end{align*}
@@
 \section{Classical analysis of Nesterov accelerated gradient}
-    In this section, we reproduce some of the analysis for Nesterov accelerated gradient method with excruciating details. 
+    In this section, we reproduce some of the analysis for Nesterov accelerated gradient method with excruciating details, in the appendix. 
+    We will introduce the method of estimating sequence invented by Nesterov. 
     We will also go over some details about the history, development and motivations behind the accelerated gradient algorithm. 
+    \subsection{Method of Estimating Sequence}
+        In this section we introduce the method of estimating sequence.
 

### 2024-08-01 Notebook LaTEX/Momentum Accelerations/main.tex
>w< work, home sync

@@
                     f(y_t) + g(y_t) + \langle \nabla f(y_t) + \partial g(y_t^+), u - y_t\rangle
-                    + 
-                    \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
+                    % + 
+                    % \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
                 \right)\\
@@
                     f(y_t) + \langle \nabla f(y_t), u - y_t\rangle + 
-                    \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
-                    + 
+                    % \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
+                    % + 
                     g(y_t) + \langle \partial g(y_t^+), u - y_t\rangle
@@
                 {definition \ref*{def:ag_prox_grad_ppm}}) 
-            has $x_{t + 1} = \hprox_{\phi_t}(x_t)$ and therefore we can use the Lyapunov inequality for PPM (\hyperref[thm:ppm_descent_ineq]
+            has $x_{t + 1} = \hprox_{\phi_t}(x_t)$ if we ignore the difference between the constant terms $h(y_t^+)$, $f(y_t) + g(y_t)$ from above. 
+            Therefore we can use the Lyapunov inequality for PPM (\hyperref[thm:ppm_descent_ineq]
                 {theorem \ref*{thm:ppm_descent_ineq}})
@@
                     f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle + 
-                    \frac{1}{2\tilde \eta_{t + 1}}\Vert x_{t + 1} - x_t\Vert^2
-                    + 
+                    % \frac{1}{2\tilde \eta_{t + 1}}\Vert x_{t + 1} - x_t\Vert^2
+                    % + 
                     g(y_t) + \langle \partial g(y_t^+), x_{t + 1} - y_t\rangle
@@
                     \Vert x_t - x_*\Vert^2
-                \right) := \Upsilon_{1, t + 1}^\text{AG}
+                \right) =: \Upsilon_{1, t + 1}^\text{AG}
                 \\

### 2024-08-01 Notebook LaTEX/Momentum Accelerations/main.tex
>w< desktop, laptop sync

@@
     We will also go over some details about the history, development and motivations behind the accelerated gradient algorithm. 
-    \subsection{Method of Estimating Sequence}
+    \subsection{Method of Nesterov's estimating sequence}
         In this section we introduce the method of estimating sequence.
+
+    \subsubsection{The estimating sequence and function}
+        \begin{definition}[Nesterov's Estimating Functions]
+            Define  $\{\phi_t\}_{t\in \mathbb N}$ to be a sequence of function where it recursively satisfies for all $k\in \mathbb N$: 
+            \begin{align*}
+                \phi_{k} (x) - f(x) \le 
+                (1 - \alpha_k)(\phi_k(x) - f(x)) \quad \forall x 
+            \end{align*}
+            Where $\alpha \in [0, 1)$. 
+        \end{definition}
+        \begin{observation}
+            Expands recursively we have 
+            \begin{align*}
+                \phi_{k}(x) - f(x) &\le 
+                \left(
+                    \prod_{i = 0}^{k} 
+                    (1 - \alpha_i)
+                \right)(\phi_0(x) - f(x)). 
+            \end{align*}
+        \end{observation}
+        So it motivates the definition of a sequence: $\lambda_k = \prod_{i=0}^k(1 - \alpha_i)$.
+
+        \begin{definition}[The estimating Sequence]
+            Continue from the above definition of a estimating functions, we consider a sequence $\{x_k\}$ satisfying 
+            \begin{align*}
+                f(x_k) &\le \phi_k^* := \min_z(\phi_k(z)). 
+            \end{align*}
+        \end{definition}
+
+        \begin{lemma}[The Lyapunov function from estimating sequence and function]
+            \;\\
+            Assume that $f$ bounded below with $f_* = \min_x f(x)$ and there exists minimizer $x_*$. 
+            With $\phi_k$ being an estimating functions and convex, $\{x_k\}$ an estimating sequence for $\phi_k$, then it satisfies
+            \begin{align*}
+                f(x_k) - f_*
+                &\le 
+                \lambda_k(\phi_0(x_*) - f_*). 
+            \end{align*}
+            for all $k\in \mathbb N\cup \{0\}$. 
+        \end{lemma}
+        \begin{proof}
+            Directly by the property of estimating sequence $x_k$, we have for all $k, x$
+            \begin{align*}
+                \phi_k(x) - f(x) \ge \phi_k^* - f(x) \ge f(x_k) - f(x), 
+            \end{align*}
+            so 
+            \begin{align*}
+                f(x_k) - f(x) \le \lambda_k (\phi_0(x) - f(x))
+                \\
+                \implies 
+                f(x_k) - f_* \le \lambda_k (\phi_0(x_*) - f(x_*)). 
+            \end{align*}
+            This establishes the convergence rate of $f(x_k)$ assuming that $\lambda_k$ is sequence that converges to zero. 
+        \end{proof}
+    \subsection{Construction of the estimating sequence and function}
+        The construction of the Nesterov estimating sequence and function is where most creativities are involved. 
+        For convex $f$ that is differentiable with $L$-Lipschitz gradient and strong convexity constant $\mu \ge 0$, Nesterov suggested in his book \cite{nesterov_lectures_2018} that there exists sequence $y_k$, $\gamma_k$, where
+        \begin{align*}
+            l_f(x, y_k) &= 
+            f(y_k) + \langle \nabla f(y_k), x - y_k\rangle + 
+            \frac{\mu}{2}\Vert x - y_k\Vert^2
+            \\
+            \phi_0 (x) &= 
+            f(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2
+            \\
+            \phi_{k + 1}(x) &= 
+            (1 - \alpha_k)\phi_k(x) + \alpha_k l_f(x; y_k)
+            \\
+            &= \phi_{k + 1}^2 + \frac{\gamma_k}{2}\Vert x - v_{k + 1}\Vert^2
+        \end{align*}
+        will verify as a Nesterov's estimating sequence and functions. 
+        The derivation for the parameters: $\gamma_k, x_k, y_k$ for $k \in \mathbb N \cup \{0\}$, will produce the Nesterov acclerated gradient as presented in
+        \hyperref[def:Nes2.2.7]{definition \ref*{def:Nes2.2.7}}
+        if correctly conducted. 
+        In this case, $\phi_k$ are simple quadratic centered $v_k$ with value $\phi_k$ with curvature $\gamma_k$. 
+        \par
+        However, the construction exhibits variations for different variants of the accelerated gradient algorithm. 
+        A different construction of $\phi_k$ yield a different algorithm. 
+        As shown in Nesterov's book \cite*[(2.2.63)]{nesterov_lectures_2018}, a projected gradient variant of the accelerated gradient method make use of the following estimating functions, sequence: 
+        \begin{align*}
+            \phi_0 (x) &= f(x_0) + \frac{\gamma_0}{2}\Vert x - x_0\Vert^2
+            \\
+            l_f(x; y_k) &= f(\mathcal T_ly_k) + 
+            \frac{1}{2L}\Vert \mathcal G_L(y_k)\Vert^2 + 
+            \langle \mathcal G_L(y_k), x - y_k\rangle + 
+            \frac{\mu}{2}\Vert x - y_k\Vert^2
+            \\
+            \phi_{k + 1}(x) &= 
+            (1 - \alpha_k)\phi_k + 
+            \alpha_k l_f(x; y_k)
+        \end{align*}
 

### 2024-08-02 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, aaa

@@
                     (1 + L\eta_{t + 1})^{-1}
-                    (
-                    x_{t + 1} + L\eta_{t + 1}z_{t + 1}
-                    ). 
+                    (x_{t + 1} + L\eta_{t + 1}z_{t + 1}). 
                 \end{align*}
@@
 Additionally, we have $y_t - x_t = L\eta_t (z_t - y_t)$, hence $\Vert y_t - x_t\Vert/\Vert z_t - y_t\Vert = L\eta_t$.
-                    \item By the algorithm, we have $z_{t + 1} - y_t = - L^{-1} \nabla f(y_t)$, and $x_{t + 1} - x_t = - \tilde \eta_{t + 1} \nabla f(y_t)$, hence vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$.
+                    \item By the algorithm, we have $z_{t + 1} - y_t = - L^{-1} \mathcal G_L(y_t)$, and $x_{t + 1} - x_t = - \tilde \eta_{t + 1} \mathcal G_L(y_t)$, hence vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$.
                     \item Finally, with update $x_{t +1} - z_{t + 1} = L\eta_t (z_{t +1} - z_t)$, we have three colinear points $(z_t, z_{t + 1}, x_t)$ with $\Vert z_{t + 1} - z_t\Vert/\Vert z_{t +1 } - z_t\Vert = L\eta_t$.
@@
             (1 - \alpha_k)\phi_k + 
-            \alpha_k l_f(x; y_k)
-        \end{align*}
+            \alpha_k l_f(x; y_k), 
+        \end{align*}
+        Here, $G_L(x) = L(x - \mathcal T_L(x))$ and $T_L(x) = \Pi_Q(x - L^{-1}\nabla f(x))$, where $Q$ is a convex set. 
+        It's equivalent to applying proximal gradient method with $h = f + g$ where $g = \delta_Q$.
 

### 2024-08-05 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, some changes and updates to the notebooks

@@
 
-            \begin{definition}[AG Proximal Gradient Tri-Points Generic Form]
+            \begin{definition}[AG Proximal Gradient Generic Form]
             \label{def:ag_prox_grad_tri_pt}
@@
 
-            \begin{definition}[Tri-points Generic Form]\label{def:agg_tri}
+            \begin{definition}[Generic Form]\label{def:agg_tri}
                 With $f$ be $L$-Lipschitz \\ 
@@
 
-            \begin{definition}[Strongly Convex Tri-points Generic Form]
+            \begin{definition}[Strongly Convex Generic Form]
                 \quad \\
-                With $f$ being $L$-Lipschitz smooth and $\mu > 0$ strongly convex then the Strongly convex Tri-Points generic form has updates of for iterates
+                With $f$ being $L$-Lipschitz smooth and $\mu > 0$ strongly convex then the Strongly convex generic form has updates of for iterates
                 \begin{align*}
@@
 
-            \begin{lemma}[Similar Triangle Form I via Generic Tri Points]
+            \begin{lemma}[Deriving Similar Triangle Form I]
                 \quad \\
@@
                 \begin{align*}
-                    z_{t + 1} &= y_t - L^{-1} \mathcal G_L f(y_t)
+                    z_{t + 1} &= y_t - L^{-1} \mathcal G_L (y_t)
                     \\

### 2024-08-06 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, a lot of new updates

@@
 
-\title{{\fontfamily{ptm}\selectfont Nesterov Type Momentum Methods}}
+\title{{\fontfamily{ptm}\selectfont A Proximal Point framework of Nesterov type accelerated gradient}}
 
@@
 
-            \begin{definition}[Proximal Gradient Tri-Points Form E]
+            \begin{definition}[Proximal Gradient variant of Ryu 12.1]
             \label{def:ag_tri_pt_form_E}
-                Form E is a special case of 
+                The method appeared in Ryu's text is a special case of 
                 \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
-                with the condition that $\tilde \eta_t = \eta_t$ for all $t \in \mathbb N$. 
+                with the condition that $\tilde \eta_t = \eta_t$ for all $t \in \mathbb N$ and $g \equiv 0$ for the non-smooth part of the objective. 
                 As a consequence, the algorithm has the following updates for iterates $(y_t, x_{t + 1}, z_{t + 1})$: 
@@
             \label{def:ag_form_similar_tria_I}
+                The similar triangle form is equivalent to the classic nesterov accelerated gradient proposed back in 1983. 
                 It updates iterates $(y_t, x_{t + 1}, z_{t + 1})$ using 
@@
             \begin{remark}
-                For more information about the specific choice of $\eta_t$ allows for an optimal convergence rates, see 
+                The above algorithm is a special case of 
+                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}, 
+                see 
                 \hyperref[sec:scenario_ii]{section \ref*{sec:scenario_ii}} for more information. 
@@
     \label{sec:generic_ag_ppm_lyapunov_analysis}
-        The first theorem states the generic convergence results when $f$ is differentiable with $L$-Lipschitz gradient, using \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}.
+        The lemma theorem states targets
+        \hyperref[prop:derive_ag_prox_grad_tript]
+        {definition \ref*{prop:derive_ag_prox_grad_tript}}.
 
@@
             {definition \ref*{prop:derive_ag_prox_grad_tript}},
-            we derive the non-smooth analogous case of the Lyapunov upper bound: 
+            we derive the non-smooth analogous case of the Lyapunov upper bound for all $t \in \mathbb N \cup \{0\}$: 
             \begin{align*}
@@
                 \Upsilon_{2, t + 1}^{\text{AG}} + 
-                \Upsilon_{1, t + 1}^{\text{AG}} \le 0, 
+                \Upsilon_{1, t + 1}^{\text{AG}} 
+                &\le \delta_{t + 1} \quad 
+                \forall t \in \mathbb N, 
+                \\
+                \Upsilon_{1, 1}^{\text{AG}} &\le \delta_1. 
             \end{align*}
@@
             \begin{align*}
+                S_t &:= \sum_{i = 1}^{t} \delta_i
+                \\
+                \sigma_t &:= \sum_{i = 1}^{t}\tilde \eta_i
+                \\
                 \Phi_t &= \left(
@@
                 \\
-                \Phi_0 &= \frac{1}{2}\Vert x_t - x_*\Vert^2, 
-            \end{align*}
-            we have $\Phi_{t + 1} - \Phi_t \le 0$, which allows for a convergence rate of $\mathcal O \left(\sum_{i = 1}^{T} \eta_i^{-1}\right)$ for $f(z_T) - f(x_*)$. 
+                \Phi_0 &= \frac{1}{2}\Vert x_0 - x_*\Vert^2, 
+            \end{align*}
+            we have $\Phi_{t + 1} - \Phi_t \le \delta_{t + 1}$, which allows for a convergence rate of $\mathcal O \left(\sigma_T^{-1}S_T\right)$ of $f(z_T) - f(x_*)$ when $S_T \neq 0$ and a rate of $\mathcal O(\sigma_T^{-1})$ when $S_T = 0$.
         \end{theorem}
@@
                     \sum_{i = 1}^{t} \tilde \eta_i
-                \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le 0. 
+                \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le \delta_{t + 1}. 
             \end{align*}
             }
-            The derivation for the convergence raet is direct and similar to 
-            \hyperref[thm:ppm_convergence_rate]{theorem \ref*{thm:ppm_convergence_rate}} 
-            Therefore, if we can identify parameter for the generic algorithm that asserts the condition above, then we have convergence for the algorithm. 
+            Telescoping we have 
+            \begin{align*}
+                \Phi_{t + 1} - \Phi_t &\le \delta_{t + 1}
+                \\
+                \sum_{i = 0}^{T - 1}\Phi_{i + 1} - \Phi_i &\le \sum_{i = 0}^{T - 1}\delta_{i + 1}
+                \\
+                \Phi_T - \Phi_0 &\le 
+                \sum_{i = 1}^{T}\delta_i = S_{T}. 
+            \end{align*}
+            So then $\Phi_T - \Phi_0$ yields: 
+            $$
+            \begin{aligned}
+                \sigma_T (f(z_t) - f(x_*)) 
+                + \frac{1}{2}\Vert x_t - x_*\Vert^2 
+                - \frac{1}{2}\Vert x_0 - x_*\Vert^2 
+                &\le S_{T}
+                \\
+                \implies 
+                \sigma_T(f(z_t) - f(x_*))
+                &\le 
+                S_T + \frac{1}{2}\Vert x_0 - x_*\Vert^2
+                \\
+                f(z_t) - f(x_*) &\le 
+                \sigma_T^{-1}\left(
+                    S_{T} + \frac{1}{2}\Vert x_0 - x_*\Vert^2
+                \right),
+            \end{aligned}
+            $$
+            which yields a convergence rate $\mathcal O(\sigma_T^{-1}S_{T})$. 
+            When $S_T = 0$, the convergence rate is $O(\sigma_T^{-1})$ instead. 
         \end{proof}
+
+        \begin{theorem}[Constraints on PPM stepsizes]
+            Algorithm proposed back in 
+            \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
+            converges if the stepsize parameter. 
+        \end{theorem}
 

### 2024-08-06 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, work home sync.

@@
 
-            \begin{proposition}[Deriving Proximal Gradient Tri-Points Generic Form]
+            \begin{proposition}[Deriving Proximal Gradient Generic Form]
             \label{prop:derive_ag_prox_grad_tript}
@@
 
-        \begin{theorem}[Constraints on PPM stepsizes]
+        \begin{theorem}[Constraints on the PPM stepsize sequence]
+            \;\\
             Algorithm proposed back in 
             \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
-            converges if the stepsize parameter. 
+            converges if the stepsize sequence $\eta_i, \tilde \eta_{i}$ satisfies
+            \begin{align*}
+                \begin{cases}
+                    \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
+                    - L^{-1} \sum_{i= 1}^{t}\tilde \eta_i 
+                    = 
+                    \epsilon_{t + 1} \tilde \eta_{t + 1}
+                    & \forall t \in \mathbb N, 
+                    \\
+                    L \eta_t \tilde \eta_{t + 1} = \sum_{i=1}^{t}\tilde \eta_i 
+                    & \forall t \in \mathbb N. 
+                \end{cases}
+            \end{align*}
+            Here $\epsilon_{t + 1}$ is an arbitrary sequence made represent the quantity in the left hand side. 
+            Then such a sequence creates 
+            \begin{align*}
+                \Phi_{t + 1} - \Phi_t =
+                \Upsilon_{1, t + 1}^\text{AG} + 
+                \sigma_t\Upsilon_{1, t + 1}^{\text{AG}} 
+                &\le \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}
+            \end{align*}
+
         \end{theorem}
-
-    \subsection{Scenario I}\label{sec:scenario_i}
-        In this scenario, we aim to recover AG Ryu 12.1 conceret variant algorithm stated back in 
-        \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}. 
-        \begin{proposition}
-            Continue from
-            \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}, 
-            set $\eta_{t + 1} = \tilde \eta_{t + 1} = (t)/(2L)$, we derive the following algorithm: 
-            \begin{align*}
-                x_{t + 1} &= x_t - \frac{t + 1}{2L} \mathcal G_L(y_t), 
-                \\
-                z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t), 
-                \\
-                y_{t + 1} &= 
-                \left(
-                    \frac{2}{t + 3}
-                \right)x_{t +1} + 
-                \left(
-                    1 - \frac{2}{t + 3}
-                \right)z_{t + 1}. 
-            \end{align*}
-            This algorithm has convergence rate of $\mathcal O(1/T^2)$ for all $h = f + g$ where $f$ is convex $L$-Lipschitz smooth and $g$ is convex. 
-        \end{proposition}
-        \begin{observation}
-            Observe that when $g \equiv 0$ this is the same algorithm as 
-            \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}
-            but with an alternative choice of indexing for $y_t$ and initial condition. 
-        \end{observation}
         \begin{proof}
-            Recall that for the proximal gradient PPM generic form we have iterate updates for $t\in \mathbb N$: 
-            \begin{align*}
-                y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
-                \\
-                x_{t + 1} &= x_t - \tilde \eta_{t + 1} \mathcal G_L(y_t)
-                \\
-                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t). 
-            \end{align*}
-            and generic Lyapunov upper bound 
-            \begin{align*}
-                \Upsilon_{1, t + 1}^\text{AG}
-                &= 
-                \tilde\eta_{t + 1} (h(z_{t + 1}) - h(x_*)) + 
-                \frac{1}{2} (
-                    \Vert x_{t + 1} - x_*\Vert^2
-                    - 
-                    \Vert x_t - x_*\Vert^2
-                )
-                \\
-                &\le 
-                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-                + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                - \langle 
-                    \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                    x_{t + 1} - z_{t + 1}
-                \rangle
-                \\
-                \Upsilon_{2, t + 1}^\text{AG}
-                &= 
-                h(z_{t + 1}) - h(z_t) 
-                \le 
-                \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
-                \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-            \end{align*}
-            By the updates, vector $x_{t + 1} - x_t$ and $z_{t + 1} - y_t$ are parallel by observations 
-            \begin{align*}
-                x_{t + 1} - x_t &= -\tilde\eta_{t + 1}\mathcal G_L(y_t), 
-                \\
-                z_{t + 1} - y_t &= -L^{-1}\mathcal G_L(y_t). 
-            \end{align*}
-            This setup allows for: 
-            \begin{align*}
-                \Upsilon_{1, t + 1}^{\text{AG}} 
-                &\le 
-                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 + 
-                \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2 
-                - 
-                \langle \tilde\eta_{t + 1}\mathcal G_L (y_t), x_{t + 1} - z_{t + 1} \rangle
-                \\
-                &= 
-                - \frac{1}{2}\Vert \tilde\eta_{t + 1} \mathcal G_L\Vert^2 + 
-                \frac{\tilde\eta_{t + 1}L}{2}\Vert L^{-1} \mathcal G_L(y_t)\Vert^2
-                - 
-                \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), x_{t + 1} - z_{t + 1} \rangle
-                \\
-                &= 
-                \frac{1}{2}\left(
-                    - \tilde\eta_{t + 1}^2 + 
-                    L^{-1}\tilde\eta_{t + 1}
-                \right)\Vert \mathcal G_L(y_t)\Vert^2
-                - 
-                \langle 
-                    \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                    (x_{t + 1} - x_{t}) + x_t
-                    + (y_t - z_{t + 1}) - y_t
-                \rangle
-                \\
-                &= 
-                \frac{1}{2}\left(
-                    L^{-1}\tilde\eta_{t + 1}
-                    - \tilde\eta_{t + 1}^2
-                \right)\Vert \mathcal G_L(y_t)\Vert^2
-                - 
-                \langle 
-                    \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                    -\tilde\eta_{t + 1}\mathcal G_L(y_t) + x_t 
-                    + L^{-1}\mathcal G_L(y_t) - y_t
-                \rangle
-                \\
-                &= 
-                \frac{1}{2}\left(
-                    L^{-1}\tilde\eta_{t + 1}
-                    - \tilde\eta_{t + 1}^2
-                \right)\Vert \mathcal G_L(y_t)\Vert^2
-                - \langle 
-                    \tilde\eta_{t +1}\mathcal G_L(y_t), 
-                    (L^{-1} - \tilde\eta_{t + 1})\mathcal G_L(y_t) + x_t - y_t
-                \rangle
-                \\
-                &= \frac{1}{2}\left(
-                    L^{-1}\tilde\eta_{t + 1} - \tilde\eta_{t + 1}^2 
-                    + 2 \tilde\eta_{t + 1}^2 - 2\tilde\eta_{t + 1}L^{-1}
-                \right)\Vert \mathcal G_L(y_t)\Vert^2
-                - 
-                \langle 
-                    \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                    x_t - y_t
-                \rangle
-                \\
-                &= 
-                \frac{1}{2}\left(
-                    \tilde\eta_{t + 1}^2 - \tilde\eta_{t + 1}L^{-1}
-                \right)\Vert \mathcal G_L(y_t)\Vert^2 
-                + \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), y_t - x_t\rangle
-            \end{align*}
-            similarly we also have upper bound 
-            \begin{align*}
-                \Upsilon_{2, t + 1}^{\text{AG}} 
-                &= 
-                \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
-                \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                \\
-                &= 
-                \langle \mathcal G_L(y_t), z_{t + 1} - y_t + y_t - z_t\rangle
-                + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                \\
-                &= 
-                \langle \mathcal G_L(y_t), - L^{-1} \mathcal G_L(y_t) + y_t - z_t\rangle
-                + 
-                \frac{L}{2}\Vert L^{-1}\mathcal G_L(y_t)\Vert^2
-                \\
-                &= 
-                -L^{-1}\Vert \mathcal G_L(y_t)\Vert^2 
-                + 
-                (1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2 
-                + 
-                \langle \mathcal G_L(y_t), y_t - z_t\rangle
-                \\
-                &= 
-                -(1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2
-                + 
-                \langle \mathcal G_L(y_t), y_t - z_t\rangle. 
-            \end{align*}
-            Observe that the cross product term for $\Upsilon_{1, t + 1}^\text{AG}, \Upsilon_{2, t + 1}^\text{AG}$ doesn't match. 
-            Hence let's consider the update for $y_t$, which can be written as $y_t - x_t = L \eta_t (z_t - y_t)$.
+
+        \end{proof}
+
+    % \subsection{Scenario I}\label{sec:scenario_i}
+    %     In this scenario, we aim to recover AG Ryu 12.1 conceret variant algorithm stated back in 
+    %     \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}. 
+    %     \begin{proposition}
+    %         Continue from
+    %         \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}, 
+    %         set $\eta_{t + 1} = \tilde \eta_{t + 1} = (t)/(2L)$, we derive the following algorithm: 
+    %         \begin{align*}
+    %             x_{t + 1} &= x_t - \frac{t + 1}{2L} \mathcal G_L(y_t), 
+    %             \\
+    %             z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t), 
+    %             \\
+    %             y_{t + 1} &= 
+    %             \left(
+    %                 \frac{2}{t + 3}
+    %             \right)x_{t +1} + 
+    %             \left(
+    %                 1 - \frac{2}{t + 3}
+    %             \right)z_{t + 1}. 
+    %         \end{align*}
+    %         This algorithm has convergence rate of $\mathcal O(1/T^2)$ for all $h = f + g$ where $f$ is convex $L$-Lipschitz smooth and $g$ is convex. 
+    %     \end{proposition}
+    %     \begin{observation}
+    %         Observe that when $g \equiv 0$ this is the same algorithm as 
+    %         \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}
+    %         but with an alternative choice of indexing for $y_t$ and initial condition. 
+    %     \end{observation}
+    %     \begin{proof}
+    %         Recall that for the proximal gradient PPM generic form we have iterate updates for $t\in \mathbb N$: 
+    %         \begin{align*}
+    %             y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
+    %             \\
+    %             x_{t + 1} &= x_t - \tilde \eta_{t + 1} \mathcal G_L(y_t)
+    %             \\
+    %             z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t). 
+    %         \end{align*}
+    %         and generic Lyapunov upper bound 
+    %         \begin{align*}
+    %             \Upsilon_{1, t + 1}^\text{AG}
+    %             &= 
+    %             \tilde\eta_{t + 1} (h(z_{t + 1}) - h(x_*)) + 
+    %             \frac{1}{2} (
+    %                 \Vert x_{t + 1} - x_*\Vert^2
+    %                 - 
+    %                 \Vert x_t - x_*\Vert^2
+    %             )
+    %             \\
+    %             &\le 
+    %             - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+    %             + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
+    %             - \langle 
+    %                 \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+    %                 x_{t + 1} - z_{t + 1}
+    %             \rangle
+    %             \\
+    %             \Upsilon_{2, t + 1}^\text{AG}
+    %             &= 
+    %             h(z_{t + 1}) - h(z_t) 
+    %             \le 
+    %             \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
+    %             \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
+    %         \end{align*}
+    %         By the updates, vector $x_{t + 1} - x_t$ and $z_{t + 1} - y_t$ are parallel by observations 
+    %         \begin{align*}
+    %             x_{t + 1} - x_t &= -\tilde\eta_{t + 1}\mathcal G_L(y_t), 
+    %             \\
+    %             z_{t + 1} - y_t &= -L^{-1}\mathcal G_L(y_t). 
+    %         \end{align*}
+    %         This setup allows for: 
+    %         \begin{align*}
+    %             \Upsilon_{1, t + 1}^{\text{AG}} 
+    %             &\le 
+    %             - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 + 
+    %             \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2 
+    %             - 
+    %             \langle \tilde\eta_{t + 1}\mathcal G_L (y_t), x_{t + 1} - z_{t + 1} \rangle
+    %             \\
+    %             &= 
+    %             - \frac{1}{2}\Vert \tilde\eta_{t + 1} \mathcal G_L\Vert^2 + 
+    %             \frac{\tilde\eta_{t + 1}L}{2}\Vert L^{-1} \mathcal G_L(y_t)\Vert^2
+    %             - 
+    %             \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), x_{t + 1} - z_{t + 1} \rangle
+    %             \\
+    %             &= 
+    %             \frac{1}{2}\left(
+    %                 - \tilde\eta_{t + 1}^2 + 
+    %                 L^{-1}\tilde\eta_{t + 1}
+    %             \right)\Vert \mathcal G_L(y_t)\Vert^2
+    %             - 
+    %             \langle 
+    %                 \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+    %                 (x_{t + 1} - x_{t}) + x_t
+    %                 + (y_t - z_{t + 1}) - y_t
+    %             \rangle
+    %             \\
+    %             &= 
+    %             \frac{1}{2}\left(
+    %                 L^{-1}\tilde\eta_{t + 1}
+    %                 - \tilde\eta_{t + 1}^2
+    %             \right)\Vert \mathcal G_L(y_t)\Vert^2
+    %             - 
+    %             \langle 
+    %                 \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+    %                 -\tilde\eta_{t + 1}\mathcal G_L(y_t) + x_t 
+    %                 + L^{-1}\mathcal G_L(y_t) - y_t
+    %             \rangle
+    %             \\
+    %             &= 
+    %             \frac{1}{2}\left(
+    %                 L^{-1}\tilde\eta_{t + 1}
+    %                 - \tilde\eta_{t + 1}^2
+    %             \right)\Vert \mathcal G_L(y_t)\Vert^2
+    %             - \langle 
+    %                 \tilde\eta_{t +1}\mathcal G_L(y_t), 
+    %                 (L^{-1} - \tilde\eta_{t + 1})\mathcal G_L(y_t) + x_t - y_t
+    %             \rangle
+    %             \\
+    %             &= \frac{1}{2}\left(
+    %                 L^{-1}\tilde\eta_{t + 1} - \tilde\eta_{t + 1}^2 
+    %                 + 2 \tilde\eta_{t + 1}^2 - 2\tilde\eta_{t + 1}L^{-1}
+    %             \right)\Vert \mathcal G_L(y_t)\Vert^2
+    %             - 
+    %             \langle 
+    %                 \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+    %                 x_t - y_t
+    %             \rangle
+    %             \\
+    %             &= 
+    %             \frac{1}{2}\left(
+    %                 \tilde\eta_{t + 1}^2 - \tilde\eta_{t + 1}L^{-1}
+    %             \right)\Vert \mathcal G_L(y_t)\Vert^2 
+    %             + \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), y_t - x_t\rangle
+    %         \end{align*}
+    %         similarly we also have upper bound 
+    %         \begin{align*}
+    %             \Upsilon_{2, t + 1}^{\text{AG}} 
+    %             &= 
+    %             \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
+    %             \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
+    %             \\
+    %             &= 
+    %             \langle \mathcal G_L(y_t), z_{t + 1} - y_t + y_t - z_t\rangle
+    %             + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
+    %             \\
+    %             &= 
+    %             \langle \mathcal G_L(y_t), - L^{-1} \mathcal G_L(y_t) + y_t - z_t\rangle
+    %             + 
+    %             \frac{L}{2}\Vert L^{-1}\mathcal G_L(y_t)\Vert^2
+    %             \\
+    %             &= 
+    %             -L^{-1}\Vert \mathcal G_L(y_t)\Vert^2 
+    %             + 
+    %             (1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2 
+    %             + 
+    %             \langle \mathcal G_L(y_t), y_t - z_t\rangle
+    %             \\
+    %             &= 
+    %             -(1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2
+    %             + 
+    %             \langle \mathcal G_L(y_t), y_t - z_t\rangle. 
+    %         \end{align*}
+    %         Observe that the cross product term for $\Upsilon_{1, t + 1}^\text{AG}, \Upsilon_{2, t + 1}^\text{AG}$ doesn't match. 
+    %         Hence let's consider the update for $y_t$, which can be written as $y_t - x_t = L \eta_t (z_t - y_t)$.
 We make the choice to do surgery on upper bound of $\Upsilon_{2, t + 1}^\text{AG}$, so $\langle \mathcal G_L(y_t), y_t - x_t\rangle = \langle \mathcal G_L(y_t), L \eta_t (z_t - y_t)\rangle$.
-            With this in mind, applying the RHS of $[(*)]$ yields: 
-            {\footnotesize
-            \begin{align*}
-                &\Upsilon_{1, t + 1}^\text{AG} + 
-                \left(
-                    \sum_{i = 1}^{t}\tilde\eta_i 
-                \right)\Upsilon_{1, t + 1}^{\text{AG}}
-                \\
-                &\le 
-                \frac{1}{2}\left(
-                    \tilde\eta_{t + 1}^2 - \tilde\eta_{t + 1}L^{-1}
-                \right)\Vert \mathcal G_L(y_t)\Vert^2 
-                + 
-                \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), L\eta_t(z_t - y_t)\rangle
-                \\
-                &\quad 
-                + 
-                \left(
-                    \sum_{i = 1}^{t}\tilde\eta_i 
-                \right)\left(
-                    -(1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2
-                    + 
-                    \langle \mathcal G_L(y_t), y_t - z_t\rangle
-                \right)
-                \\
-                &= 
-                \left(
-                    \frac{1}{2}\tilde\eta_{t + 1}\left(
-                        \tilde \eta_{t +1} - L^{-1}
-                    \right)
-                    - 
-                    \frac{1}{2L}\sum_{i = 1}^{t}\tilde \eta_i
-                \right)\Vert \mathcal G_L(y_t)\Vert^2 + 
-                \left(
-                    L\eta_t \tilde \eta_{t + 1} - \sum_{i = 1}^{t}\tilde \eta_i
-                \right)\langle \mathcal G_L(y_t), z_t - y_t\rangle
-            \end{align*}
-            }
-            If the algorithm were to have the abstract convergence rate as stated in 
-            \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}},
-            then one of the sufficient condition is to have the above quantity less than or equal to zero, one sufficient condition of that is to have the coefficient for $\Vert \mathcal G_L(y_t)\Vert$ be $\le 0$, and the coefficient of the cross term $\langle \mathcal G_L(y_t), z_t - y_t\rangle$ be zero.
-            To simplify, we make the assumption that $\tilde \eta_t = \eta_t$ for all $t \in \mathcal N$, making it to be a specific instance of 
-            \hyperref[def:ag_tri_pt_form_E]{definition \ref*{def:ag_tri_pt_form_E}}. 
-            These conditions translate to the following relations for $\eta_{t}$. 
-            \begin{align*}
-                \begin{cases}
-                    L\eta_{t + 1}^2 + \eta_{t + 1} - \sum_{i = 1}^{t}\eta_i 
-                    \le 0, 
-                    \\
-                    L\eta_t \eta_{t + 1} - \sum_{i = 1}^{t} \eta_i 
-                    = 0. 
-                \end{cases}
-            \end{align*}
-            Substituting the sequence equality back to the first one yield: 
-            \begin{align*}
-                L\eta_{t + 1}^2 - (\eta_{t + 1} + L\eta_t\eta_{t + 1}) &\le 0 
-                \\
-                L\eta^2_{t + 1} - \eta_{t + 1}
-                &\le 
-                L\eta_t \eta_{t + 1} 
-                \\
-                \eta_{t + 1}(L\eta_{t + 1} - 1) 
-                &\le L\eta_t\eta_{t + 1}
-                \\
-                \eta_t > 0 
-                \implies 
-                L\eta_{t + 1} - 1 &\le 
-                L\eta_t 
-                \\
-                \eta_{t + 1} &\le \eta_t + L^{-1}. 
-            \end{align*}
-            To satisfy the equality, reader should verify that $\eta_{t} = t/(2L)$ or $\eta_t = (t + 1)/2L$ are some of the options. 
-        \end{proof}
-        \begin{remark}
-            In the original writing by Ahn \cite[equation (4.9)]{ahn_understanding_2022}, they didn't identify this specific variant in the literature. 
-            Here we identify it to be equivalent to the acceleration algorithm stated in Ryu \cite[algorithm 12.1]{ryu_large-scale_2022}. 
-        \end{remark}
-
-    \subsection{Scenario II}\label{sec:scenario_ii}
-        With the choice of $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we can recover the seminal Nesterov accelerated gradient algorithm from 1983. 
-        The variants proposed by Chambolle Dossal \cite{chambolle_convergence_2015}, is distinct from the possibility proposed in this secenario.
-
-        \begin{lemma}[Deriving the Nesterov Sequence]
-            For all $t \in \mathbb N$
-            \begin{align*}
-                \left\lbrace
-                \begin{aligned}
-                    (1 + L\eta_{t + 1})^{-1}L \eta_t 
-                    &= \frac{a_t - 1}{a_{t + 1}} , 
-                    \\
-                    a_{t + 1}^2 - a_t &= a_t^2. 
-                \end{aligned} 
-                \right. 
-            \end{align*}
-            allows \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}} to converge at an optimal rate. 
-            The base case is $\eta_0 = 0$. 
-        \end{lemma}
-        \begin{proof}
-            Continue from 
-            \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]{lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}, 
-            With $x_{t +1} - x_t = L\tilde\eta_{t+1}(z_{t + 1} - y_t)$ for $y_t$: 
-            \begin{align*}
-                \Upsilon_{1, t + 1}^\text{AG} &\le 
-                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-                    + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                    - \langle 
-                        \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                        x_{t + 1} - z_{t + 1}
-                    \rangle
-                    \\
-                    &= 
-                    - \frac{1}{2}\Vert L \tilde \eta_{t+} (z_{t+1} - y_t)\Vert^2 + 
-                    \frac{\tilde\eta_{t +1}L}{2}\Vert z_{t+1} - y_t\Vert^2
-                    - \langle 
-                        \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                        x_{t + 1} - z_{t + 1}
-                    \rangle
-                    \\
-                    &= 
-                    \left(
-                        \frac{L^2\tilde\eta_{t + 1}^2}{2}
-                        + 
-                        \frac{\tilde \eta_{t +1}}{2}
-                    \right)
-                    \Vert z_{t+1} - y_t\Vert^2
-                    - 
-                    \langle 
-                        \tilde \eta_{t+ 1} \mathcal G_L(y_t), x_{t+1} - z_{t+1}
-                    \rangle. 
-            \end{align*}
-            This completes the analysis for $\Upsilon_{1, t + 1}^\text{AG}$ with $\tilde\eta_{t+1}$. 
-            Next we consider 
-            \begin{align*}
-                \Upsilon_{2, t + 1}^{\text{AG}} 
-                &= 
-                \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle
-                + 
-                \frac{L }{2} \Vert z_{t+1} - y_t\Vert^2
-                \\
-                &= 
-                \langle \mathcal G_L(y_t), L^{-1}\eta_t^{-1}(x_{t+1} - z_{t + 1})\rangle
-                + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-            \end{align*}
-            Here we used $x_{t + 1} = z_{t + 1} + L\eta_t (z_{t + 1} - z_t)$, which was the consequence of $\tilde\eta_{t + 1} = \eta_t + L^{-1}$, as discussed from before. 
-            Hence, the upper bound of the Lyapunov function for smooth AG PPM 
-            (\hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}) 
-            has 
-            {\footnotesize
-            \begin{align*}
-                & \Upsilon_{1, t + 1}^{\text{AG}} + 
-                \left(
-                    \sum_{i = 1}^{t}\tilde \eta_i
-                \right)\Upsilon_{2, t + 1}^{\text{AG}}
-                \\
-                &\quad \le 
-                \left(
-                    - \frac{L^2\tilde \eta_{t + 1}^2}{2}
-                    + \frac{\tilde\eta_{t+1}L}{2}
-                \right)
-                \Vert z_{t+1} - y_t\Vert^2
-                - 
-                \langle \tilde \eta_{t+1} \nabla f(y_t), x_{t+1} - z_{t + 1}\rangle
-                \\
-                & \qquad + 
-                \left(
-                    \sum_{i = 1}^{t}\tilde \eta_i
-                \right)\left(
-                    \langle \nabla f(y_t), L^{-1}\eta_t^{-1}(x_{t+1} - z_{t + 1})\rangle
-                    + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                \right)
-                \\
-                &= 
-                \frac{L}{2}
-                \left(
-                -\tilde\eta_{t + 1}^2 + \tilde\eta_{t + 1}
-                    + \sum_{i = 1}^{t}\tilde\eta_i
-                \right)\Vert z_{t + 1} - y_t\Vert^2
-                +
-                \left(
-                    L^{-1}\eta_t^{-1} 
-                    \left(
-                        \sum_{i = 1}^{t}\tilde \eta_i
-                    \right)
-                    -
-                    \tilde \eta_{t + 1}
-                \right)\langle \mathcal G_L (y_t), x_{t + 1} - z_{t + 1}\rangle
-            \end{align*}
-            }
-            If the above quantity less than or equal to zero, it will allow for convergence of the algorithm by 
-            \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}.
-            One sufficient condition is to have the coefficients for all the cross product terms to sum up to zero, and the squared normed term to sum up to a non-positive number for all $t \in \mathbb N$.
-            This gives relations 
-            \begin{align*}
-                - \frac{1}{2}\left(
-                    L^2 \tilde\eta_{t+1}^2 - \tilde\eta_{t+1}L 
-                \right) + 
-                \frac{L}{2}\left(
-                    \sum_{i = 1}^{t} \tilde \eta_i
-                \right) &\le 0
-                \\
-                - \left(
-                    L\tilde \eta_{t + 1}^2 
-                    - 
-                    \tilde\eta_{t + 1}
-                \right) + 
-                \sum_{i = 1}^{t}\tilde \eta_i 
-                &\le 0
-                \\
-                -L \tilde \eta_{t+1} + 
-                \sum_{i = 1}^{t + 1} \tilde \eta_i 
-                &\le 0
-                \\
-                \sum_{i = 1}^{t + 1}\tilde \eta_i 
-                &\le L \tilde \eta_{t + 1}^2, 
-            \end{align*}
-            and equations 
-            \begin{align*}
-                -\tilde \eta_{t + 1} + 
-                \left(
-                    \sum_{i = 1}^{t}\tilde \eta_i
-                \right)L^{-1}\eta_t^{-1} 
-                &= 0
-                \\
-                \sum_{i = 1}^{t}\tilde \eta_i 
-                &= 
-                L \eta_t \tilde \eta_{t + 1}. 
-            \end{align*}
-            Susbtituting the equality into the inequalites we have 
-            \begin{align*}
-                \tilde \eta_{t + 1} + \sum_{i = 1}^{t} \tilde \eta_i 
-                &\le L \tilde \eta_{t + 1}^2
-                \\
-                \tilde \eta_{t + 1} + L\eta_t \tilde \eta_{t + 1}
-                &\le L \tilde \eta_{t + 1}^2
-                \\
-                1 + L\eta_t &\le L \tilde\eta_{t + 1}. 
-            \end{align*}
-            The choice $\tilde \eta_{t + 1} = \eta_t + L^{-1}$ makes the inequality is an equality. 
-            Finally, to recover the momentum stepsizes for the classical Nesterov accelerated gradient, we consider relations 
-            \begin{align*}
-                L \sum_{i = 1}^{t + 1} \tilde \eta_i 
-                &= L \tilde \eta_{t + 1} + L \sum_{i = 1}^{t} \tilde \eta_i 
-                \\
-                &= 
-                L \tilde \eta_{t + 1} + L (L \eta_t \tilde \eta_{t + 1}) 
-                \\
-                &= L \tilde \eta_{t + 1} + L \eta_t (L \eta_t + 1)
-                \\
-                &= L (\eta_t + L^{-1}) + L\eta_t (L \eta_t + 1)
-                \\
-                &= (L\eta_t + 1)^2, 
-            \end{align*}
-            Simultanenously 
-            \begin{align*}
-                L \sum_{i = 1}^{t + 1} \tilde \eta_i 
-                &= L^2 \eta_{t + 1} \tilde \eta_{t + 1}
-                \\
-                &= L \eta_{t + 1}(1+ L \eta_{t + 1}), 
-            \end{align*}
-            Combining yields that 
-            \begin{align*}
-                (L\eta_t + 1)^2 
-                &= L\eta_{t + 1}(1 + L \eta_{t + 1})
-                \\
-                &= L\eta_{t + 1} + L^2 \eta_{t + 1}^2
-                \\
-                \iff 
-                (L\eta_t + 1)^2 + 1/4 &= 
-                1/4 + 2(1/2)L \eta_{t + 1} + (L \eta_{t + 1})^2
-                \\
-                \iff 
-                (L\eta_t + 1)^2 + 1/4 &= 
-                (L \eta_{t + 1} + 1/2)^2. 
-            \end{align*}
-            With $a_t = L\eta_t + 1 = L \tilde \eta_t$ this is 
-            \begin{align*}
-                a_t^2 + 1/4 &= (a_{t + 1} - 1/2)^2 
-                \\
-                a_t^2 + 1/4 &= a_{t + 1}^2 + 1/4 - a_{t + 1}
-                \\
-                a_t^2 + a_{t + 1} &= a_{t + 1}^2. 
-                \\
-                \implies 
-                a_{t + 1} &= 
-                \frac{1 + \sqrt{1 + 4a_t^2}}{2}
-            \end{align*}
-            And that is the updates for the Nesterov momentum, recall that the momentum term is linked to the PPM sequence via relation 
-            \begin{align*}
-                (1 + L \eta_{t+ 1})^{-1}L\eta_t = L\eta_t / a_{t + 1} = (a_t - 1)/a_{t + 1}. 
-            \end{align*}
-            We had recovered the classic Nesterov acceleration sequence method for the smooth gradient descent algorithm. 
-        \end{proof}
-        \begin{remark}
-            This variant is distinct from the variants proposed by Chambolle \cite{chambolle_convergence_2015}, but both of which fits into the same frameworks. 
-            The variantis presented as 
-            \begin{align*}
-                y_n &= (1 - t_n^{-1})z_n + t_n^{-1} x_n
-                \\
-                z_{n + 1} &= y_n - L^{-1}\nabla f(y_n)
-                \\
-                x_{n + 1} &= z_n + t_{n + 1}(z_{n + 1} - z_n)
-            \end{align*}
-            They listed the choice of $t_n = (n + a - 1)/a$ for all $a > 2$. 
-            Under this choice, unfortunately, it's in no way obvious that this format reduces to \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
-            It fails the similar triangle description Without the explict representation $x_{n + 1} = z_n + \tilde\eta_{t + 1}\nabla f(y_t)$. 
-            \par\noindent
-            At the time of writing, we are still investigating the relations between these variants of algorithms.
-        \end{remark}
-
-    \subsection{Scenario III}
+    %         With this in mind, applying the RHS of $[(*)]$ yields: 
+    %         {\footnotesize
+    %         \begin{align*}
+    %             &\Upsilon_{1, t + 1}^\text{AG} + 
+    %             \left(
+    %                 \sum_{i = 1}^{t}\tilde\eta_i 
+    %             \right)\Upsilon_{1, t + 1}^{\text{AG}}
+    %             \\
+    %             &\le 
+    %             \frac{1}{2}\left(
+    %                 \tilde\eta_{t + 1}^2 - \tilde\eta_{t + 1}L^{-1}
+    %             \right)\Vert \mathcal G_L(y_t)\Vert^2 
+    %             + 
+    %             \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), L\eta_t(z_t - y_t)\rangle
+    %             \\
+    %             &\quad 
+    %             + 
+    %             \left(
+    %                 \sum_{i = 1}^{t}\tilde\eta_i 
+    %             \right)\left(
+    %                 -(1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2
+    %                 + 
+    %                 \langle \mathcal G_L(y_t), y_t - z_t\rangle
+    %             \right)
+    %             \\
+    %             &= 
+    %             \left(
+    %                 \frac{1}{2}\tilde\eta_{t + 1}\left(
+    %                     \tilde \eta_{t +1} - L^{-1}
+    %                 \right)
+    %                 - 
+    %                 \frac{1}{2L}\sum_{i = 1}^{t}\tilde \eta_i
+    %             \right)\Vert \mathcal G_L(y_t)\Vert^2 + 
+    %             \left(
+    %                 L\eta_t \tilde \eta_{t + 1} - \sum_{i = 1}^{t}\tilde \eta_i
+    %             \right)\langle \mathcal G_L(y_t), z_t - y_t\rangle
+    %         \end{align*}
+    %         }
+    %         If the algorithm were to have the abstract convergence rate as stated in 
+    %         \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}},
+    %         then one of the sufficient condition is to have the above quantity less than or equal to zero, one sufficient condition of that is to have the coefficient for $\Vert \mathcal G_L(y_t)\Vert$ be $\le 0$, and the coefficient of the cross term $\langle \mathcal G_L(y_t), z_t - y_t\rangle$ be zero.
+    %         To simplify, we make the assumption that $\tilde \eta_t = \eta_t$ for all $t \in \mathcal N$, making it to be a specific instance of 
+    %         \hyperref[def:ag_tri_pt_form_E]{definition \ref*{def:ag_tri_pt_form_E}}. 
+    %         These conditions translate to the following relations for $\eta_{t}$. 
+    %         \begin{align*}
+    %             \begin{cases}
+    %                 L\eta_{t + 1}^2 + \eta_{t + 1} - \sum_{i = 1}^{t}\eta_i 
+    %                 \le 0, 
+    %                 \\
+    %                 L\eta_t \eta_{t + 1} - \sum_{i = 1}^{t} \eta_i 
+    %                 = 0. 
+    %             \end{cases}
+    %         \end{align*}
+    %         Substituting the sequence equality back to the first one yield: 
+    %         \begin{align*}
+    %             L\eta_{t + 1}^2 - (\eta_{t + 1} + L\eta_t\eta_{t + 1}) &\le 0 
+    %             \\
+    %             L\eta^2_{t + 1} - \eta_{t + 1}
+    %             &\le 
+    %             L\eta_t \eta_{t + 1} 
+    %             \\
+    %             \eta_{t + 1}(L\eta_{t + 1} - 1) 
+    %             &\le L\eta_t\eta_{t + 1}
+    %             \\
+    %             \eta_t > 0 
+    %             \implies 
+    %             L\eta_{t + 1} - 1 &\le 
+    %             L\eta_t 
+    %             \\
+    %             \eta_{t + 1} &\le \eta_t + L^{-1}. 
+    %         \end{align*}
+    %         To satisfy the equality, reader should verify that $\eta_{t} = t/(2L)$ or $\eta_t = (t + 1)/2L$ are some of the options. 
+    %     \end{proof}
+    %     \begin{remark}
+    %         In the original writing by Ahn \cite[equation (4.9)]{ahn_understanding_2022}, they didn't identify this specific variant in the literature. 
+    %         Here we identify it to be equivalent to the acceleration algorithm stated in Ryu \cite[algorithm 12.1]{ryu_large-scale_2022}. 
+    %     \end{remark}
+
+    % \subsection{Scenario II}\label{sec:scenario_ii}
+    %     With the choice of $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we can recover the seminal Nesterov accelerated gradient algorithm from 1983. 
+    %     The variants proposed by Chambolle Dossal \cite{chambolle_convergence_2015}, is distinct from the possibility proposed in this secenario.
+
+    %     \begin{lemma}[Deriving the Nesterov Sequence]
+    %         For all $t \in \mathbb N$
+    %         \begin{align*}
+    %             \left\lbrace
+    %             \begin{aligned}
+    %                 (1 + L\eta_{t + 1})^{-1}L \eta_t 
+    %                 &= \frac{a_t - 1}{a_{t + 1}} , 
+    %                 \\
+    %                 a_{t + 1}^2 - a_t &= a_t^2. 
+    %             \end{aligned} 
+    %             \right. 
+    %         \end{align*}
+    %         allows \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}} to converge at an optimal rate. 
+    %         The base case is $\eta_0 = 0$. 
+    %     \end{lemma}
+    %     \begin{proof}
+    %         Continue from 
+    %         \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]{lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}, 
+    %         With $x_{t +1} - x_t = L\tilde\eta_{t+1}(z_{t + 1} - y_t)$ for $y_t$: 
+    %         \begin{align*}
+    %             \Upsilon_{1, t + 1}^\text{AG} &\le 
+    %             - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+    %                 + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
+    %                 - \langle 
+    %                     \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+    %                     x_{t + 1} - z_{t + 1}
+    %                 \rangle
+    %                 \\
+    %                 &= 
+    %                 - \frac{1}{2}\Vert L \tilde \eta_{t+} (z_{t+1} - y_t)\Vert^2 + 
+    %                 \frac{\tilde\eta_{t +1}L}{2}\Vert z_{t+1} - y_t\Vert^2
+    %                 - \langle 
+    %                     \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+    %                     x_{t + 1} - z_{t + 1}
+    %                 \rangle
+    %                 \\
+    %                 &= 
+    %                 \left(
+    %                     \frac{L^2\tilde\eta_{t + 1}^2}{2}
+    %                     + 
+    %                     \frac{\tilde \eta_{t +1}}{2}
+    %                 \right)
+    %                 \Vert z_{t+1} - y_t\Vert^2
+    %                 - 
+    %                 \langle 
+    %                     \tilde \eta_{t+ 1} \mathcal G_L(y_t), x_{t+1} - z_{t+1}
+    %                 \rangle. 
+    %         \end{align*}
+    %         This completes the analysis for $\Upsilon_{1, t + 1}^\text{AG}$ with $\tilde\eta_{t+1}$. 
+    %         Next we consider 
+    %         \begin{align*}
+    %             \Upsilon_{2, t + 1}^{\text{AG}} 
+    %             &= 
+    %             \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle
+    %             + 
+    %             \frac{L }{2} \Vert z_{t+1} - y_t\Vert^2
+    %             \\
+    %             &= 
+    %             \langle \mathcal G_L(y_t), L^{-1}\eta_t^{-1}(x_{t+1} - z_{t + 1})\rangle
+    %             + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
+    %         \end{align*}
+    %         Here we used $x_{t + 1} = z_{t + 1} + L\eta_t (z_{t + 1} - z_t)$, which was the consequence of $\tilde\eta_{t + 1} = \eta_t + L^{-1}$, as discussed from before. 
+    %         Hence, the upper bound of the Lyapunov function for smooth AG PPM 
+    %         (\hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}) 
+    %         has 
+    %         {\footnotesize
+    %         \begin{align*}
+    %             & \Upsilon_{1, t + 1}^{\text{AG}} + 
+    %             \left(
+    %                 \sum_{i = 1}^{t}\tilde \eta_i
+    %             \right)\Upsilon_{2, t + 1}^{\text{AG}}
+    %             \\
+    %             &\quad \le 
+    %             \left(
+    %                 - \frac{L^2\tilde \eta_{t + 1}^2}{2}
+    %                 + \frac{\tilde\eta_{t+1}L}{2}
+    %             \right)
+    %             \Vert z_{t+1} - y_t\Vert^2
+    %             - 
+    %             \langle \tilde \eta_{t+1} \nabla f(y_t), x_{t+1} - z_{t + 1}\rangle
+    %             \\
+    %             & \qquad + 
+    %             \left(
+    %                 \sum_{i = 1}^{t}\tilde \eta_i
+    %             \right)\left(
+    %                 \langle \nabla f(y_t), L^{-1}\eta_t^{-1}(x_{t+1} - z_{t + 1})\rangle
+    %                 + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
+    %             \right)
+    %             \\
+    %             &= 
+    %             \frac{L}{2}
+    %             \left(
+    %             -\tilde\eta_{t + 1}^2 + \tilde\eta_{t + 1}
+    %                 + \sum_{i = 1}^{t}\tilde\eta_i
+    %             \right)\Vert z_{t + 1} - y_t\Vert^2
+    %             +
+    %             \left(
+    %                 L^{-1}\eta_t^{-1} 
+    %                 \left(
+    %                     \sum_{i = 1}^{t}\tilde \eta_i
+    %                 \right)
+    %                 -
+    %                 \tilde \eta_{t + 1}
+    %             \right)\langle \mathcal G_L (y_t), x_{t + 1} - z_{t + 1}\rangle
+    %         \end{align*}
+    %         }
+    %         If the above quantity less than or equal to zero, it will allow for convergence of the algorithm by 
+    %         \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}.
+    %         One sufficient condition is to have the coefficients for all the cross product terms to sum up to zero, and the squared normed term to sum up to a non-positive number for all $t \in \mathbb N$.
+    %         This gives relations 
+    %         \begin{align*}
+    %             - \frac{1}{2}\left(
+    %                 L^2 \tilde\eta_{t+1}^2 - \tilde\eta_{t+1}L 
+    %             \right) + 
+    %             \frac{L}{2}\left(
+    %                 \sum_{i = 1}^{t} \tilde \eta_i
+    %             \right) &\le 0
+    %             \\
+    %             - \left(
+    %                 L\tilde \eta_{t + 1}^2 
+    %                 - 
+    %                 \tilde\eta_{t + 1}
+    %             \right) + 
+    %             \sum_{i = 1}^{t}\tilde \eta_i 
+    %             &\le 0
+    %             \\
+    %             -L \tilde \eta_{t+1} + 
+    %             \sum_{i = 1}^{t + 1} \tilde \eta_i 
+    %             &\le 0
+    %             \\
+    %             \sum_{i = 1}^{t + 1}\tilde \eta_i 
+    %             &\le L \tilde \eta_{t + 1}^2, 
+    %         \end{align*}
+    %         and equations 
+    %         \begin{align*}
+    %             -\tilde \eta_{t + 1} + 
+    %             \left(
+    %                 \sum_{i = 1}^{t}\tilde \eta_i
+    %             \right)L^{-1}\eta_t^{-1} 
+    %             &= 0
+    %             \\
+    %             \sum_{i = 1}^{t}\tilde \eta_i 
+    %             &= 
+    %             L \eta_t \tilde \eta_{t + 1}. 
+    %         \end{align*}
+    %         Susbtituting the equality into the inequalites we have 
+    %         \begin{align*}
+    %             \tilde \eta_{t + 1} + \sum_{i = 1}^{t} \tilde \eta_i 
+    %             &\le L \tilde \eta_{t + 1}^2
+    %             \\
+    %             \tilde \eta_{t + 1} + L\eta_t \tilde \eta_{t + 1}
+    %             &\le L \tilde \eta_{t + 1}^2
+    %             \\
+    %             1 + L\eta_t &\le L \tilde\eta_{t + 1}. 
+    %         \end{align*}
+    %         The choice $\tilde \eta_{t + 1} = \eta_t + L^{-1}$ makes the inequality is an equality. 
+    %         Finally, to recover the momentum stepsizes for the classical Nesterov accelerated gradient, we consider relations 
+    %         \begin{align*}
+    %             L \sum_{i = 1}^{t + 1} \tilde \eta_i 
+    %             &= L \tilde \eta_{t + 1} + L \sum_{i = 1}^{t} \tilde \eta_i 
+    %             \\
+    %             &= 
+    %             L \tilde \eta_{t + 1} + L (L \eta_t \tilde \eta_{t + 1}) 
+    %             \\
+    %             &= L \tilde \eta_{t + 1} + L \eta_t (L \eta_t + 1)
+    %             \\
+    %             &= L (\eta_t + L^{-1}) + L\eta_t (L \eta_t + 1)
+    %             \\
+    %             &= (L\eta_t + 1)^2, 
+    %         \end{align*}
+    %         Simultanenously 
+    %         \begin{align*}
+    %             L \sum_{i = 1}^{t + 1} \tilde \eta_i 
+    %             &= L^2 \eta_{t + 1} \tilde \eta_{t + 1}
+    %             \\
+    %             &= L \eta_{t + 1}(1+ L \eta_{t + 1}), 
+    %         \end{align*}
+    %         Combining yields that 
+    %         \begin{align*}
+    %             (L\eta_t + 1)^2 
+    %             &= L\eta_{t + 1}(1 + L \eta_{t + 1})
+    %             \\
+    %             &= L\eta_{t + 1} + L^2 \eta_{t + 1}^2
+    %             \\
+    %             \iff 
+    %             (L\eta_t + 1)^2 + 1/4 &= 
+    %             1/4 + 2(1/2)L \eta_{t + 1} + (L \eta_{t + 1})^2
+    %             \\
+    %             \iff 
+    %             (L\eta_t + 1)^2 + 1/4 &= 
+    %             (L \eta_{t + 1} + 1/2)^2. 
+    %         \end{align*}
+    %         With $a_t = L\eta_t + 1 = L \tilde \eta_t$ this is 
+    %         \begin{align*}
+    %             a_t^2 + 1/4 &= (a_{t + 1} - 1/2)^2 
+    %             \\
+    %             a_t^2 + 1/4 &= a_{t + 1}^2 + 1/4 - a_{t + 1}
+    %             \\
+    %             a_t^2 + a_{t + 1} &= a_{t + 1}^2. 
+    %             \\
+    %             \implies 
+    %             a_{t + 1} &= 
+    %             \frac{1 + \sqrt{1 + 4a_t^2}}{2}
+    %         \end{align*}
+    %         And that is the updates for the Nesterov momentum, recall that the momentum term is linked to the PPM sequence via relation 
+    %         \begin{align*}
+    %             (1 + L \eta_{t+ 1})^{-1}L\eta_t = L\eta_t / a_{t + 1} = (a_t - 1)/a_{t + 1}. 
+    %         \end{align*}
+    %         We had recovered the classic Nesterov acceleration sequence method for the smooth gradient descent algorithm. 
+    %     \end{proof}
+    %     \begin{remark}
+    %         This variant is distinct from the variants proposed by Chambolle \cite{chambolle_convergence_2015}, but both of which fits into the same frameworks. 
+    %         The variantis presented as 
+    %         \begin{align*}
+    %             y_n &= (1 - t_n^{-1})z_n + t_n^{-1} x_n
+    %             \\
+    %             z_{n + 1} &= y_n - L^{-1}\nabla f(y_n)
+    %             \\
+    %             x_{n + 1} &= z_n + t_{n + 1}(z_{n + 1} - z_n)
+    %         \end{align*}
+    %         They listed the choice of $t_n = (n + a - 1)/a$ for all $a > 2$. 
+    %         Under this choice, unfortunately, it's in no way obvious that this format reduces to \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
+    %         It fails the similar triangle description Without the explict representation $x_{n + 1} = z_n + \tilde\eta_{t + 1}\nabla f(y_t)$. 
+    %         \par\noindent
+    %         At the time of writing, we are still investigating the relations between these variants of algorithms.
+    %     \end{remark}
+    % \subsection{Scenario III}
 

### 2024-08-07 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, work over, work home sync

@@
     \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}, and 
-    \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}. 
+    \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}. 
     In \hyperref[sec:AG_useful_information]{section \ref*{sec:AG_useful_information}}
@@
             \begin{definition}[AG Proximal Gradient Generic Form]
-            \label{def:ag_prox_grad_tri_pt}
+            \label{def:ag_prox_grad_generic}
                 With $h = f + g$, where $g$ is convex, $f$ is convex and $L$-Lipschitz smooth. 
@@
                 The method appeared in Ryu's text is a special case of 
-                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
+                \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
                 with the condition that $\tilde \eta_t = \eta_t$ for all $t \in \mathbb N$ and $g \equiv 0$ for the non-smooth part of the objective. 
@@
                 The above algorithm is a special case of 
-                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}, 
+                \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}, 
                 see 
-                \hyperref[sec:scenario_ii]{section \ref*{sec:scenario_ii}} for more information. 
+                \hyperref[thm:ag_generic_stepsize_constrants]{section \ref*{thm:ag_generic_stepsize_constrants}} 
+                for more information. 
             \end{remark}
@@
                 is equivalent to 
-                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
+                \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
             \end{proposition}
@@
                 in 
-                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
+                \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
                 We can derive similar triangle form I as stated back in
@@
         \label{thm:generic_ag_convergence}
-            If there is a choice of $\eta_i, \tilde \eta_i$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} such that we have 
-            \begin{align*}
-                \left(
-                    \sum_{i = 1}^{t} \tilde \eta_i
-                \right)
-                \Upsilon_{2, t + 1}^{\text{AG}} + 
-                \Upsilon_{1, t + 1}^{\text{AG}} 
-                &\le \delta_{t + 1} \quad 
-                \forall t \in \mathbb N, 
-                \\
-                \Upsilon_{1, 1}^{\text{AG}} &\le \delta_1. 
-            \end{align*}
-            then with 
-            \begin{align*}
-                S_t &:= \sum_{i = 1}^{t} \delta_i
-                \\
-                \sigma_t &:= \sum_{i = 1}^{t}\tilde \eta_i
-                \\
+            Define the Lyapunov function $\Phi_t\; \forall t \in \{0\}\cup \N$: 
+            \begin{align*}
                 \Phi_t &= \left(
@@
             \end{align*}
-            we have $\Phi_{t + 1} - \Phi_t \le \delta_{t + 1}$, which allows for a convergence rate of $\mathcal O \left(\sigma_T^{-1}S_T\right)$ of $f(z_T) - f(x_*)$ when $S_T \neq 0$ and a rate of $\mathcal O(\sigma_T^{-1})$ when $S_T = 0$.
+            if there is a choice of $\eta_i, \tilde \eta_i$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} such that we have 
+            \begin{align*}
+                & \Phi_{t + 1} - \Phi_{t}\left(
+                    \sum_{i = 1}^{t} \tilde \eta_i
+                \right) =
+                \Upsilon_{2, t + 1}^{\text{AG}} + 
+                \Upsilon_{1, t + 1}^{\text{AG}} 
+                \le \delta_{t + 1} \quad 
+                \forall t \in \mathbb N, 
+                \\
+                & \Upsilon_{1, 1}^{\text{AG}} \le \delta_1. 
+            \end{align*}
+            Then with
+            \begin{align*}
+                S_t &:= \sum_{i = 1}^{t} \delta_i
+                \\
+                \sigma_t &:= \sum_{i = 1}^{t}\tilde \eta_i
+            \end{align*}
+            we have $\Phi_{t + 1} - \Phi_t \le \delta_{t + 1}$, it allows for a convergence rate of $\mathcal O \left(\sigma_T^{-1}S_T\right)$ of $f(z_T) - f(x_*)$ when $S_T \neq 0$ and a rate of $\mathcal O(\sigma_T^{-1})$ when $S_T = 0$.
         \end{theorem}
@@
         \begin{theorem}[Constraints on the PPM stepsize sequence]
+            \label{thm:ag_generic_stepsize_constrants}
             \;\\
-            Algorithm proposed back in 
-            \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
+            Algorithm formulated in 
+            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
             converges if the stepsize sequence $\eta_i, \tilde \eta_{i}$ satisfies
@@
             \end{align*}
-            Here $\epsilon_{t + 1}$ is an arbitrary sequence made represent the quantity in the left hand side. 
-            Then such a sequence creates 
+            Here $\epsilon_{t + 1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$ is a sequence made characterizing the error between $\tilde \eta_{t + 1}, \eta_t - L^{-1}$. 
+            Then the convergence rate can be formulated by
             \begin{align*}
@@
                 \sigma_t\Upsilon_{1, t + 1}^{\text{AG}} 
-                &\le \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}
-            \end{align*}
+                &\le \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}.
+            \end{align*}
+            When $\eta_t - 0 \;\forall t\in \mathbb N$, the sequence $a_t:= a_t = 1 + L \eta_t = \tilde \eta_{t + 1} - \epsilon_{t + 1}$, the relation simplies to: 
+            \begin{align*}
+                \begin{cases}
+                    a_{t + 1} &= (1/2)\left(
+                    1 + \sqrt{1 + 4 c_{t + 1}}
+                    \right), 
+                    \\
+                    c_{t + 1} &= a_t^2.     
+                \end{cases}
+            \end{align*}
+            As a consequence: 
+            \begin{enumerate}
+                \item It makes $\delta_{t} = 0$ in the Lypunov analysis; 
+                \item it simplifies the algorithm to
+                \hyperref[def:ag_form_similar_tria_I]{definition\ref*{def:ag_form_similar_tria_I}}; 
+                \item and it is the famous Nesterov momentum sequence. 
+            \end{enumerate}
 
@@
         \begin{proof}
+            With $t \in \mathbb N \cup \{0\}$ fixed, 
+            recall that for the proximal gradient PPM generic form 
+            (as formulated in 
+            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
+            ) for $t\in \mathbb N$ it has: 
+            \begin{align*}
+                y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
+                \\
+                x_{t + 1} &= x_t - \tilde \eta_{t + 1} \mathcal G_L(y_t)
+                \\
+                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t). 
+            \end{align*}
+            Recall the upper bounds from 
+            \ref*{thm:generic_ag_convergence}, 
+            it has 
+            \begin{align*}
+                \Upsilon_{1, t + 1}^\text{AG}
+                &= 
+                \tilde\eta_{t + 1} (h(z_{t + 1}) - h(x_*)) + 
+                \frac{1}{2} (
+                    \Vert x_{t + 1} - x_*\Vert^2
+                    - 
+                    \Vert x_t - x_*\Vert^2
+                )
+                \\
+                &\le 
+                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
+                + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                - \langle 
+                    \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+                    x_{t + 1} - z_{t + 1}
+                \rangle
+                \\
+                \Upsilon_{2, t + 1}^\text{AG}
+                &= 
+                h(z_{t + 1}) - h(z_t) 
+                \le 
+                \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
+                \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
+            \end{align*}
+            By the updates, vector $x_{t + 1} - x_t$ and $z_{t + 1} - y_t$ are parallel by observations: 
+            \begin{align*}
+                x_{t + 1} - x_t &= -\tilde\eta_{t + 1}\mathcal G_L(y_t), 
+                \\
+                z_{t + 1} - y_t &= -L^{-1}\mathcal G_L(y_t). 
+            \end{align*}
+            This allows for 
+            \begin{align*}
+                \Upsilon_{1, t + 1}^{\text{AG}} 
+                &\le 
+                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 + 
+                \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2 
+                - 
+                \langle \tilde\eta_{t + 1}\mathcal G_L (y_t), x_{t + 1} - z_{t + 1} \rangle
+                \\
+                &= 
+                - \frac{1}{2}\Vert \tilde\eta_{t + 1} \mathcal G_L\Vert^2 + 
+                \frac{\tilde\eta_{t + 1}L}{2}\Vert L^{-1} \mathcal G_L(y_t)\Vert^2
+                - 
+                \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), x_{t + 1} - z_{t + 1} \rangle
+                \\
+                &= 
+                \frac{1}{2}\left(
+                    - \tilde\eta_{t + 1}^2 + 
+                    L^{-1}\tilde\eta_{t + 1}
+                \right)\Vert \mathcal G_L(y_t)\Vert^2
+                - 
+                \langle 
+                    \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+                    (x_{t + 1} - x_{t}) + x_t
+                    + (y_t - z_{t + 1}) - y_t
+                \rangle
+                \\
+                &= 
+                \frac{1}{2}\left(
+                    L^{-1}\tilde\eta_{t + 1}
+                    - \tilde\eta_{t + 1}^2
+                \right)\Vert \mathcal G_L(y_t)\Vert^2
+                - 
+                \langle 
+                    \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+                    -\tilde\eta_{t + 1}\mathcal G_L(y_t) + x_t 
+                    + L^{-1}\mathcal G_L(y_t) - y_t
+                \rangle
+                \\
+                &= 
+                \frac{1}{2}\left(
+                    L^{-1}\tilde\eta_{t + 1}
+                    - \tilde\eta_{t + 1}^2
+                \right)\Vert \mathcal G_L(y_t)\Vert^2
+                - \langle 
+                    \tilde\eta_{t +1}\mathcal G_L(y_t), 
+                    (L^{-1} - \tilde\eta_{t + 1})\mathcal G_L(y_t) + x_t - y_t
+                \rangle
+                \\
+                &= \frac{1}{2}\left(
+                    L^{-1}\tilde\eta_{t + 1} - \tilde\eta_{t + 1}^2 
+                    + 2 \tilde\eta_{t + 1}^2 - 2\tilde\eta_{t + 1}L^{-1}
+                \right)\Vert \mathcal G_L(y_t)\Vert^2
+                - 
+                \langle 
+                    \tilde\eta_{t + 1} \mathcal G_L(y_t), 
+                    x_t - y_t
+                \rangle
+                \\
+                &= 
+                \frac{1}{2}\left(
+                    \tilde\eta_{t + 1}^2 - \tilde\eta_{t + 1}L^{-1}
+                \right)\Vert \mathcal G_L(y_t)\Vert^2 
+                + \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), y_t - x_t\rangle.
+            \end{align*}
+            Similarly 
+            \begin{align*}
+                \Upsilon_{2, t + 1}^{\text{AG}} 
+                &= 
+                \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
+                \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                \\
+                &= 
+                \langle \mathcal G_L(y_t), z_{t + 1} - y_t + y_t - z_t\rangle
+                + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
+                \\
+                &= 
+                \langle \mathcal G_L(y_t), - L^{-1} \mathcal G_L(y_t) + y_t - z_t\rangle
+                + 
+                \frac{L}{2}\Vert L^{-1}\mathcal G_L(y_t)\Vert^2
+                \\
+                &= 
+                -L^{-1}\Vert \mathcal G_L(y_t)\Vert^2 
+                + 
+                (1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2 
+                + 
+                \langle \mathcal G_L(y_t), y_t - z_t\rangle
+                \\
+                &= 
+                -(1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2
+                + 
+                \langle \mathcal G_L(y_t), y_t - z_t\rangle. 
+            \end{align*}
+            Observe that the cross product term for $\Upsilon_{1, t + 1}^\text{AG}, \Upsilon_{2, t + 1}^\text{AG}$ doesn't match. 
+            Hence let's consider the update for $y_t$, which can be written as $y_t - x_t = L \eta_t (z_t - y_t)$.
+We make the choice to do surgery on upper bound of $\Upsilon_{2, t + 1}^\text{AG}$, so $\langle \mathcal G_L(y_t), y_t - x_t\rangle = \langle \mathcal G_L(y_t), L \eta_t (z_t - y_t)\rangle$.
+            With this in mind, RHS of $\phi_{t + 1} - \phi_t$ yields: 
+            {\footnotesize
+            \begin{align*}
+                &\Upsilon_{1, t + 1}^\text{AG} + 
+                \left(
+                    \sum_{i = 1}^{t}\tilde\eta_i 
+                \right)\Upsilon_{1, t + 1}^{\text{AG}}
+                \\
+                &\le 
+                \frac{1}{2}\left(
+                    \tilde\eta_{t + 1}^2 - \tilde\eta_{t + 1}L^{-1}
+                \right)\Vert \mathcal G_L(y_t)\Vert^2 
+                + 
+                \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), L\eta_t(z_t - y_t)\rangle
+                \\ 
+                &\quad 
+                + 
+                \left(
+                    \sum_{i = 1}^{t}\tilde\eta_i 
+                \right)\left(
+                    -(1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2
+                    + 
+                    \langle \mathcal G_L(y_t), y_t - z_t\rangle
+                \right)
+                \\
+                &= 
+                \left(
+                    \frac{1}{2}\tilde\eta_{t + 1}\left(
+                        \tilde \eta_{t +1} - L^{-1}
+                    \right)
+                    - 
+                    \frac{1}{2L}\sum_{i = 1}^{t}\tilde \eta_i
+                \right)\Vert \mathcal G_L(y_t)\Vert^2 + 
+                \left(
+                    L\eta_t \tilde \eta_{t + 1} - \sum_{i = 1}^{t}\tilde \eta_i
+                \right)\langle \mathcal G_L(y_t), z_t - y_t\rangle. 
+            \end{align*}
+            }
+            The non-negativity of $\Vert \mathcal G_L(y_t) \Vert^2$ characterize the culmulative error $\delta_{t + 1}$ in the Lypunov analysis through sequence $\epsilon_i$. 
+            Setting the coefficient of $\Vert \mathcal G_L(y_t) \Vert^2$ to be $\epsilon_{t + 1}\tilde \eta_{t + 1}$, it yields a system of inequality: 
+            \begin{align*}
+                \begin{cases}
+                    \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
+                    - L^{-1} \sum_{i= 1}^{t}\tilde \eta_i 
+                    = 
+                    \epsilon_{t + 1} \tilde \eta_{t + 1}
+                    & \forall t \in \N, 
+                    \\
+                    L \eta_t \tilde \eta_{t + 1} = \sum_{i=1}^{t}\tilde \eta_i 
+                    & \forall t \in \N. 
+                \end{cases}
+            \end{align*}
+            It requires base case $L\eta_0\tilde\eta_{1} = 0$, assume $\sigma_0 = 0$. 
+            We use $\sum_{i = 1}^t \tilde \eta_i = \sigma_t$, simplifying the first equation we have 
+            \begin{align*}
+                \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
+                - L^{-1} \sigma_t
+                &= 
+                \epsilon_{t + 1} \tilde \eta_{t + 1}
+                \\
+                \iff 
+                \tilde \eta_{t + 1} ^2 - L \tilde \eta_{t + 1} 
+                &= 
+                \epsilon_{t + 1} \tilde \eta_{t + 1} + L^{-1} \sigma_t
+                \\
+                &= 
+                \epsilon_{t + 1} \tilde \eta_{t + 1} 
+                + L^{-1}(L \eta_t \tilde \eta_{t + 1})
+                \\
+                \iff 
+                \tilde \eta_{t + 1} &= \epsilon_{t + 1} + \eta_t + L^{-1}. 
+            \end{align*}
+            At the last step, we divided both side of the equation by $\tilde \eta_{t + 1} > 0$.
+            The parameter gives relation $\epsilon_{t+1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$. 
+            Hence, it gives us the following system of equality to work with 
+            \begin{align*}
+                \forall t \in \N: 
+                \begin{cases}
+                    \tilde \eta_{t + 1} = \epsilon_{t + 1} + \eta_t + L^{-1}, 
+                    \\
+                    L \eta_t \tilde \eta_{t + 1} = \sigma_t.     
+                \end{cases}
+            \end{align*}
+            With that, we can solve a relation between $\eta_{t + 1}$ in terms of the sequence $\epsilon$ and $\eta_t$.
+            Consider the equality
+
+            \begin{align*}
+                L \sigma_{t + 1} &= L \tilde \eta_{t + 1} + L \sigma_t
+                \\
+                &=
+                L \tilde \eta_{t + 1}  + L (L \eta_t \tilde \eta_{t + 1})
+                \\
+                &= L \tilde \eta_{t+ 1} + L \eta_t (L \tilde \eta_{t + 1})
+                \\
+                &=  L \tilde \eta_{t+ 1} + L \eta_t (L \epsilon_{t + 1} + L \eta_t + 1)
+                \\
+                &=  L \tilde \eta_{t+ 1} + L \eta_t (L \eta_t + 1) + L^2 \eta_t \epsilon_{t + 1}
+                \\
+                &= L (\epsilon_{t +1} + \eta_t + L^{-1}) + L\eta_t(L \eta_t + 1) + L^2\eta_t \epsilon_{t + 1}
+                \\
+                &= L \epsilon_{t + 1} + (L\eta_t + 1)^2 + L^2\eta_t \epsilon_{t + 1}
+                \\
+                &= 
+                L \epsilon_{t + 1}(1 + L \eta_t) + (1 + L \eta_t)^2. 
+            \end{align*}
+
+            At the same time we have
+
+            \begin{align*}
+                L \sigma_{t + 1} &= L^2 \eta_{t + 1}\tilde \eta_{t + 1} 
+                \\
+                &= L\eta_{t + 1}(1 + L \eta_{t + 1} + \epsilon_{t + 2})
+                \\
+                &= L\eta_{t + 1}(1 + L \eta_{t + 1}) + \epsilon_{t + 2}L\eta_{t + 1}. 
+            \end{align*}
+
+            Therefore, it generates the following equation:
+
+            \begin{align*}
+                L\eta_{t + 1} (1 + L \eta_{t + 1}) 
+                + 
+                \epsilon_{t + 2} L \eta_{t + 1} 
+                &= 
+                L\epsilon_{t + 1}(1 + L \eta_t)  + (1 + L\eta_t)^2
+                \\
+                (L\eta_{t + 1} + L^2\eta_{t + 1}^2)
+                + 
+                \epsilon_{t + 2} L \eta_{t + 1} 
+                + 
+                \frac{1}{4}
+                &= 
+                L\epsilon_{t + 1}(1 + L \eta_t)  + (1 + L\eta_t)^2
+                + 
+                \frac{1}{4}
+                \\
+                (L\eta_{t + 1} + L^2\eta_{t + 1}^2 + 1/4)
+                + 
+                \epsilon_{t + 2} L \eta_{t + 1} 
+                + \epsilon_{t + 2}
+                &= 
+                L\epsilon_{t + 1}(1 + L \eta_t)  + (1 + L\eta_t)^2
+                + \frac{1}{4}
+                + \epsilon_{t + 2}
+                \\
+                (L\eta_{t + 1} + 1/2)^2 + \epsilon_{t + 2}(L \eta_{t + 1} + 1)
+                &= 
+                L \epsilon_{t + 1}(1 + L \eta_t) + (1 + L\eta_t)^2
+                + \frac{1}{4} + \epsilon_{t + 2}
+                \\
+                \text{ with: } & a_t = 1 + L \eta_t = \tilde \eta_{t + 1} - \epsilon_{t + 1}
+                \\
+                (a_{t + 1} - 1/2)^2 + \epsilon_{t + 2}a_{t + 1}
+                &= 
+                L \epsilon_{t + 1}a_t + a_t^2 + 1/4 + \epsilon_{t + 1}
+                \\
+                a_{t + 1}^2 + 1/4 - a_{t + 1} + \epsilon_{t + 2}a_{t + 1}
+                &= 
+                L \epsilon_{t + 1}a_t + a_t^2 + 1/4 + \epsilon_{t + 1}
+                \\
+                a_{t + 1}^2 + a_{t + 1}(\epsilon_{t + 2} - 1)
+                &= 
+                \underbrace{
+                    a_t(L \epsilon_{t + 1} + a_t) + \epsilon_{t + 1}
+                }_{c_{t + 1}}. 
+            \end{align*}
+
+            Solving reveals the relations:
+
+            \begin{align*}
+                \begin{cases}
+                    a_{t + 1} = (1/2)\left(
+                    1 - \epsilon_{t + 2} + \sqrt{(1 - \epsilon_{t + 2}) + 4 c_{t + 2}}
+                    \right), 
+                    \\
+                    c_{t + 1} = a_t (L \epsilon_{t + 1} + a_t) + \epsilon_{t + 1}. 
+                \end{cases}
+            \end{align*}
+
+            Observe that in the case where we choose $\epsilon_t = 0 \forall t \in \N$, the above relation simplifies to
+
+            \begin{align*}
+                a_{t + 1} &= (1/2)\left(
+                    1 + \sqrt{1 + 4 c_{t + 1}}
+                \right), 
+                \\
+                c_{t + 1} &= a_t^2. 
+            \end{align*}
+
+            This relation is the Famous Nesterov momentum sequence. 
+            At the same time, we can analyize the convergence rate of the algorithm by the abstract convergence lemma, producing:
+
+            \begin{align*}
+                \Phi_{t + 1} - \Phi_t =
+                \Upsilon_{1, t + 1}^\text{AG} + 
+                \sigma_t\Upsilon_{1, t + 1}^{\text{AG}} 
+                &\le \epsilon_{t + 1}\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}
+            \end{align*}
+
+            Telescoping yields:
+
+            \begin{align*}
+                S_{T} = 
+                \sum_{i = 0}^{T- 1} \delta_i 
+                &= 
+                \sum_{i = 0}^{T - 1} \epsilon_{i + 1}\tilde\eta_{i + 1}\Vert \mathcal G_L(y_i)\Vert^2
+                \\
+                &\le \sum_{i = 0}^{T - 1}\max(\epsilon_{i + 1} \tilde\eta_{i + 1}\Vert \mathcal G_L(y_i)\Vert^2, 0). 
+            \end{align*}
+
+            Under an ideal case where we wish to attain accelerations, we want $\lim_{T \rightarrow \infty} S_T < \infty$. 
+            One way to accomplish is choose the error sequence $\epsilon_i, i \in \N$ to be bounded by for all $i \in \N$, $\epsilon_i$ should satisfy:
+
+            \begin{align*}
+                \epsilon_{i + 1}\tilde \eta_{i + 1}
+                \Vert \mathcal G_L(y_i)\Vert^2 
+                &\le \delta_{i + 1}
+                \\
+                \iff 
+                \epsilon_{i + 1}
+                &\le 
+                \frac{\delta_{i + 1} }{\tilde\eta_{t + 1}\Vert \mathcal G_L(y_i)\Vert^2}. 
+            \end{align*}
+
+            for any $\sum_{i = 0}^{T - 1}\delta_{i + 1}$ converges to a limit as $T \rightarrow \infty$.
 
@@
     %         Continue from
-    %         \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}, 
+    %         \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}, 
     %         set $\eta_{t + 1} = \tilde \eta_{t + 1} = (t)/(2L)$, we derive the following algorithm: 
@@
     %         \end{align*}
-    %         allows \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}} to converge at an optimal rate. 
+    %         allows \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}} to converge at an optimal rate. 
     %         The base case is $\eta_0 = 0$. 

### 2024-08-07 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, work home sync

@@
             \end{align*}
-            When $\eta_t - 0 \;\forall t\in \mathbb N$, the sequence $a_t:= a_t = 1 + L \eta_t = \tilde \eta_{t + 1} - \epsilon_{t + 1}$, the relation simplies to: 
+            When $\epsilon_t = 0 \;\forall t\in \mathbb N$, the sequence $a_t:= a_t = 1 + L \eta_t = \tilde \eta_{t + 1} - \epsilon_{t + 1}$, the relation simplies to: 
             \begin{align*}
                 \begin{cases}
-                    a_{t + 1} &= (1/2)\left(
+                    a_{t + 1} = (1/2)\left(
                     1 + \sqrt{1 + 4 c_{t + 1}}
@@
                     \\
-                    c_{t + 1} &= a_t^2.     
+                    c_{t + 1} = a_t^2.     
                 \end{cases}
@@
         In this case, $\phi_k$ are simple quadratic centered $v_k$ with value $\phi_k$ with curvature $\gamma_k$.
+
         \par
@@
             \\
-            l_f(x; y_k) &= f(\mathcal T_ly_k) + 
+            l_f(x; y_k) &= f(\mathcal T_Ly_k) + 
             \frac{1}{2L}\Vert \mathcal G_L(y_k)\Vert^2 + 
@@
         \end{align*}
-        Here, $G_L(x) = L(x - \mathcal T_L(x))$ and $T_L(x) = \Pi_Q(x - L^{-1}\nabla f(x))$, where $Q$ is a convex set. 
-        It's equivalent to applying proximal gradient method with $h = f + g$ where $g = \delta_Q$.
+        Here, $\mathcal G_L(x) = L(x - \mathcal T_L(x))$ and $T_L(x) = \Pi_Q(x - L^{-1}\nabla f(x))$, where $Q$ is a convex set. 
+        It's equivalent to applying proximal gradient method with $h = f + g$ where $g = \delta_Q$. Finally, with $\mu = 0$, it reduces to ineuality appeared in 
+        \hyperref[lemma:grad_map_linearization]{lemma \ref*{lemma:grad_map_linearization}}.
+
+        \par
+        Finally, the following constructions appeared in Guller \cite{guler_new_1992} are used to prove the convergence rate of accelerated PPM: 
+        \begin{align*}
+        \end{align*}
 

### 2024-08-08 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, big updates

--- 2024-08-06 Notebook LaTEX/Momentum Accelerations/main.tex
@@
         \begin{theorem}[Proximal Descent Inequality]\label{thm:ppm_descent_ineq}
-            With $f: \RR^n \mapsto \overline \RR^n$ $\beta$-convex where $\beta \ge 0$, fix any $x \in \RR^n$, let $p = \hprox_f(x)$, then for all $y$ we have inequality 
+            With $f: \RR^n \mapsto \overline \RR^n$ $\beta$strongly convex where $\beta \ge 0$, fix any $x \in \RR^n$, let $p = \hprox_f(x)$, then for all $y$ we have inequality 
             $$
@@
 \section{Accelerated gradient descent and PPM}
-    Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
-    Ahn explored the interpretation of Nesterov acceleration via PPM. 
-    They proposed the idea of ``similar triangle" for unifying all varieties of Nesterov accelerated gradient. 
-    They used PPM to derive several variations of the Nesterov accelerated gradient algorithms. 
-    Finally, they refurnished \hyperref[thm:lower_approx_ppm_convergence]{theorem \ref*{thm:lower_approx_ppm_convergence}} for the proof of convergence rate for the accelerated gradient.
-    Their analysis results in relatively simple arguments that exhibits powerful extensions to several variants of the Nesterov accelerated gradient.
-
-    \par\noindent
-    Interestingly, the Nesterov accelerated gradient applies to PPM too; Guler \cite{guler_new_1992} did it two decades ago. 
-    He uses the idea of a Nesterov acceleration sequence faithfully. 
-    One recent development of the accelerated PPM is an algorithmic framework named: ``Universal Catalyst acceleration", proposed by Lin et al \cite{lin_universal_2015}. 
-    It is an application of Guler's work in the context of variance-reduction stochastic gradient algorithms for machine learning.
-
-    \par\noindent
-    \textbf{We state our contributions}. 
-    In \hyperref[sec:AG_varieties]{section \ref*{sec:AG_varieties}} 
-    We stated different forms of accelerated gradient that appeared in the literatures and the equivalences between their forms. 
-    They are abstract because the choice of stepsize parameters in the algorithms are unspecified. 
-    Abstract forms related to the proximal gradient method were our own inventions inspired by discussions in the literatures, which includes 
-    \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}, and 
-    \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}. 
-    In \hyperref[sec:AG_useful_information]{section \ref*{sec:AG_useful_information}}
-    we prove and interpret some of the unproved claims made by Ahn, Sra \cite{ahn_understanding_2022} as good exercises and for the peace of the mind. 
-    In
-    \hyperref[sec:generic_ag_ppm_lyapunov_analysis]{section \ref*{sec:generic_ag_ppm_lyapunov_analysis}},
-    we state two important theorems for the derivation of convergences rate for various type of algorithm using an upper bound of a Lyapunov function. 
-    This part is inspired by works from Ahn, Sra \cite{ahn_understanding_2022}, but with the gradient mapping and proximal gradient added into the picture, making it distinct from all algorithms discussed in Ahn and Sra's paper.
-    \hyperref[sec:scenario_i]{Section \ref*{sec:scenario_i}} and 
-    \hyperref[sec:scenario_ii]{\ref*{sec:scenario_ii}} derive the convergence rate and determine the parameters for the step sizes needed to achieve an optimal convergence rate. 
-    In each section, we recover a specific variant of the Accelerated gradient and identify their appearances in the literature.
-
-    \subsection{Preliminaries}
-        We introduce some additional lemma that are crucial to the derivations of non-smooth accelerated gradient method. 
-        \begin{definition}[The Gradient Mapping]
-            \label{def:gradient_mapping}
-            Let $g = f + g$ where $f$ is $L$-Lipschitz smooth and convex, $g$ is convex. 
-            Define the proximal gradient operator
-            $$
-                \mathcal T_L(x) := \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)),
-            $$
-            then the gradient mapping is defined as
-            $$
-                \mathcal G_L(x) = L(x - \mathcal T_L(x)). 
-            $$
-        \end{definition}
-        \begin{remark}
-            The name ``gradient mapping" comes from \cite[(2.2.54)]{nesterov_lectures_2018}, however, Nesterov was referring to only the case when $g$ is an indicator function of a convex set in his writing.
-            Of course, in Amir Beck \cite[10.3.2]{beck_first-order_nodate}, it has the exact same definition for gradient mapping as the above. 
-        \end{remark}
-
-        \begin{lemma}[Gradient Mapping Approximates Subgradient]
-            \label{lemma:grad_map_lemma_first}
-            Continue from 
-            \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}, 
-            the gradient mapping satisfies
-            \begin{align*}
-                x^+ &= \mathcal T_L(x), 
-                \\
-                L(x - x^+) &\in  \nabla f(x) + \partial g(x^+) \ni \mathcal G_L(x). 
-            \end{align*}
-        \end{lemma}
-        \begin{proof}
-            \begin{align*}
-                x^+ &= [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f](x)
-                \\
-                [I + L^{-1}\partial g](x^+) &\ni [I - L^{-1}\nabla f](x)
-                \\
-                x^+ + L^{-1}\partial g(x^+) &\ni x - L^{-1}\nabla f(x)
-                \\
-                x^+ - x + L^{-1}\partial g(x^+) &\ni L^{-1}\nabla f(x)
-                \\
-                L(x^+ - x) + \partial g(x^+) &\ni - \nabla f(x)
-                \\
-                L(x - x^+) &\in \nabla f(x) + \partial g(x^+)
-                \\
-                \mathcal G_L(x) &\in \nabla f(x) + \partial g(x^+). 
-            \end{align*}
-        \end{proof}
-
-        \begin{lemma}[Linearized Gradient Mapping Lower Bound]
-        \label{lemma:grad_map_linearization}
-            Continue from 
-            \hyperref[lemma:grad_map_lemma_first]{definition \ref*{lemma:grad_map_lemma_first}}, 
-            with $x^+ = \mathcal T_L(x)$, the gradient mapping satisfies the inequality for all $z$: 
-            \begin{align*}
-                h(z) &\ge
-                h(z) - \frac{L}{2}\Vert x - x^+\Vert^2
-                \ge h(x^+) + \langle \mathcal G_L(x), z - x\rangle. 
-            \end{align*}
-        \end{lemma}
-        \begin{proof}
-            Directly from the $L$-smoothness of $f$, convexity of $g, f$, we have the list of inequalities: 
-            \begin{align*}
-                &f(x^+) \le 
-                f(x) + \langle \nabla f(x), x^+ - x\rangle
-                + \frac{L}{2}\Vert x - x^+\Vert^2, 
-                \\
-                &f(x) + \langle \nabla f(x), z - x\rangle 
-                \le f(z), 
-                \\
-                &g(x^+) \le 
-                g(z) + \langle \partial g(x^+), x^+ - z\rangle. 
-            \end{align*}
-            Now, consider adding $g(x^+)$ to the first inequality from above we get 
-            {\footnotesize 
-            \begin{align*}
-                f(x^+) + g(x^+) 
-                &\le 
-                f(x) + g(x^+) + \langle \nabla f(x), x^+ - x\rangle 
-                + \frac{L}{2}\Vert x - x^+\Vert^2
-                \\
-                &\le 
-                (f(z) - \langle \nabla f(x), z - x\rangle) + 
-                \left(g(z) - \langle \partial g(x^+), x^+ - z\rangle\right)
-                + 
-                \langle \nabla f(x), x^+ - x\rangle + \frac{L}{2}\Vert x - x^+\Vert^2
-                \\
-                &= f(z) + g(z) + \langle \nabla f(x), x - z + x^+ - x\rangle
-                + 
-                \langle \partial g(x^+), x^+ - z\rangle + \frac{L}{2}\Vert x - x^+\Vert^2
-                \\
-                &= 
-                h(z) + \langle \nabla f(x), x^+ - z\rangle + 
-                \langle \partial g(x^+), x^+ - z\rangle
-                + \frac{L}{2}\Vert x - x^+\Vert^2
-                \\
-                &= h(z) + \langle \nabla f(x) + \partial g(x^+), x^+ - z\rangle 
-                + \frac{L}{2}\Vert x - x^+\Vert^2. 
-            \end{align*}
-            }
-            By $\mathcal G_L(x) = L(x - x^+) \in \nabla f(x) + \partial g(x^+)$ from previous dicussion, we have 
-            \begin{align*}
-                h(x^+) &\le 
-                h(z) + \langle \mathcal G_L(x), x^+ - z\rangle + \frac{L}{2}\Vert x - x^+\Vert^2
-                \\
-                &= h(z) - \langle L(x^+ - x), x^+ - x + x - z \rangle 
-                + 
-                \frac{L}{2}\Vert x - x^+\Vert^2
-                \\
-                &= 
-                h(z) - L\Vert x^+ - x\Vert^2 
-                + L \langle x^+ - x, x - z\rangle
-                + \frac{L}{2}\Vert x - x^+\Vert^2
-                \\
-                &= h(z) + \langle \mathcal G_L(x), x - z\rangle - 
-                \frac{L}{2}\Vert x - x^+\Vert^2. 
-            \end{align*}
-            Therefore, the inequality is justified. 
-        \end{proof}
-        \begin{remark}
-            Observe that the linearization $h(x^+) + \langle \mathcal G_L(x), z - x\rangle$ is anchored at $x^+$, instead of $x$. 
-            Geometrically, it's tilted and it "prefers" the sharp corners of a convex function, if, $x$ is close to a sharp corner. 
-        \end{remark}
-
-    \subsection{Varieties of Nesterov accelerated gradient}\label{sec:AG_varieties}
-        Here, the acrynonym: ``AG" stands for accelerated gradient. 
-        \subsubsection{AG Abstract Forms}
-            In this section, we list different varieties of the Nesterov accelerated method. 
-            \begin{definition}[Nestrov 2.2.7]\label{def:Nes2.2.7}
-                Let $f$ be a $L$ Lipschitz smooth and $\mu\ge 0$ strongly convex function. 
-                Choose $x_0$, $\gamma_0 > 0$, set $v_0 = x_0$, for iteration $k\ge 0$, it
-                \begin{enumerate}
-                    \item[1.] computes $\alpha_k \in (0, 1)$ by solving $L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \alpha_k \mu$; 
-                    \item[2.] sets $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$;
-                    \item[3.] chooses $y_k = (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \gamma_{k + 1}x_k)$. Compute $f(y_k)$ and $\nabla f(y_k)$; 
-                    \item[4.] finds $x_{k + 1}$ such that $f(x_{k + 1}) \le f(y_k) - (2L)^{-1} \Vert \nabla f(y_k)\Vert^2$; 
-                    \item[5.] sets $v_{k + 1} = \gamma_{k+1}^{-1}((1 - \alpha_k)\gamma_kv_k + \alpha_k \mu y_k - \alpha_k \nabla f(y_k))$. 
-                \end{enumerate}
-            \end{definition}
-            \begin{remark}
-                This is in Nesterov's book \cite[(2.2.7)]{nesterov_lectures_2018}. 
-                For more context, the sequence $\alpha_k \in (0, 1)$ such that $\sum_{k = 1}^{\infty}\alpha_k = \infty$, and recursively we have $\lambda_{k + 1} = (1 - \alpha_k)\lambda_k$. 
-                the sequence $\lambda_k$ is called an Nesterov estimating sequence. 
-                It is the most generic algorithm in his book about accelerated gradient method. 
-                The genericity of the algorithm is provided by item 4., which is the a special case of the smooth descent lemma.
-
-            \end{remark}
-
-            \begin{definition}[Ahn Sra 6.24]\label{def:agg_ppm}
-                With $f$ $\mu \ge 0$ strongly convex and $L$-Lipschitz smooth, the generic PPM form is formulated for strictly positive stepsizes $\tilde \eta_i,\eta_i$: 
-                \begin{align*}
-                    x_{t + 1} &= \argmin_{x} \left\lbrace
-                        l_f(x; y_t) 
-                        + 
-                        \frac{\mu}{2}\Vert x - y_t\Vert^2
-                        + 
-                        \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
-                    \right\rbrace, 
-                    \\
-                    y_{t + 1} &= \argmin_{x} 
-                    \left\lbrace
-                        l_f(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
-                        \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
-                    \right\rbrace. 
-                \end{align*}
-            \end{definition}
-            \begin{remark}
-                This algorithm is the same as algorithm (6.24) described by Ahn and Sra \cite{ahn_understanding_2022}. 
-                Observe that by setting $\mu = 0, \tilde \eta_{t + 1} = \eta_{t + 1}$ this recovers algorithm (4.8) described in Ahn and Sra \cite{ahn_understanding_2022}. 
-                Finally, Ahn, Sra 6.24 has the same form as Nesterov 2.2.7. 
-                See 
-                \hyperref[prop:Nes2.2.7_via_ahn_sra_6.24]{proposition \ref*{prop:Nes2.2.7_via_ahn_sra_6.24}} for a demonstration. 
-            \end{remark}
-
-            \begin{definition}[AG Proximal Gradient PPM Generic Form]
-            \label{def:ag_prox_grad_ppm}
-                Let $h=f + g$ be the sum of convex function $g$ and convex differentiable $f$ with $L$-Lipschitz gradient. 
-                Define the proximal gradient and gradient mapping operator operator: 
-                $$
-                \begin{aligned}
-                    \mathcal T_L^{g, f}(x) &:=  
-                    \hprox_{L^{-1}g}\left(x - L^{-1}\nabla f(x)\right)
-                    \\
-                    &= 
-                    \argmin_{u}
-                    \left\lbrace
-                        g(u) + f(x) + \langle \nabla f(x), u - x\rangle
-                        + 
-                        \frac{L}{2}\Vert u - x\Vert^2
-                    \right\rbrace,
-                    \\
-                    \mathcal G_L^{g, f}(x) &= 
-                    L\left(x - \mathcal T_L^{g, f}(x)\right). 
-                \end{aligned}
-                $$
-                Omitting the superscript $f, g$ on $\mathcal T, \mathcal G$ for simplicity since it's clear in the context. 
-                Define the linear lower bounding function for $f$ at $y$, for all $x$: 
-                $$
-                \begin{aligned}
-                    l_h(x; y) &= h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle \le h(x), 
-                \end{aligned}
-                $$
-                with that we define the algorithm:
-                $$
-                \begin{aligned}
-                    x_{t + 1} &= \argmin_{x} \left\lbrace
-                        l_h(x; y_t) + \frac{1}{2\tilde \eta_{t + 1}} 
-                        \Vert x - x_t\Vert^2
-                    \right\rbrace,
-                    \\
-                    y_{t + 1}&= 
-                    \argmin_{x}
-                    \left\lbrace
-                        l_h(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
-                        \frac{1}{2\eta_{t + 1}} \Vert x - x_{t + 1}\Vert^2
-                    \right\rbrace.
-                \end{aligned}
-                $$
-            \end{definition}
-            \begin{observation}
-                With $g \equiv 0$, the above definition reduces to 
-                \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}
-                where $\mu = 0$. 
-            \end{observation}
-
-            \begin{definition}[AG Proximal Gradient Generic Form]
-            \label{def:ag_prox_grad_tri_pt}
-                With $h = f + g$, where $g$ is convex, $f$ is convex and $L$-Lipschitz smooth. 
-                Define proximal gradient and gradient mapping operator 
-                $$
-                \begin{aligned}
-                    \mathcal T_L(x) 
-                    &:= \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)), 
-                    \\
-                    x^+ &= \mathcal T_L(x), 
-                    \\
-                    \mathcal G_L(x) 
-                    &:= L(x -  x^+). 
-                \end{aligned}
-                $$
-                Then the algorithm updates $(y_t, x_{t + 1}, z_{t + 1})$ with expression: 
-                $$
-                \begin{aligned}
-                    y_t^+ &= \mathcal T_L(y_t)
-                    \\
-                    y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
-                    \\
-                    x_{t + 1} &= x_t - \tilde \eta \mathcal G_L(y_t)
-                    \\
-                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
-                \end{aligned}
-                $$
-                for all $t\in \mathbb N$ where the base case has $y_0 = x_0$. 
-            \end{definition}
-            \begin{remark}
-                Observe that $z_{t + 1} = y_t^+$. 
-            \end{remark}
-
-            \begin{definition}[Generic Form]\label{def:agg_tri}
-                With $f$ be $L$-Lipschitz \\ 
-                smooth and convex, choose any $y_0 = x_0=z_0$ and a non-negative sequence $\eta_t, \tilde\eta_t$, the algorithm admits form: 
-                \begin{align*}
-                    x_{t + 1} &= x_t - \tilde \eta_{t + 1} \nabla f(y_t) 
-                    \\
-                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t) 
-                    \\
-                    y_{t + 1} &= 
-                    (1 + L\eta_{t + 1})^{-1}
-                    (
-                    x_{t + 1} + L\eta_{t + 1}z_{t + 1}
-                    ). 
-                \end{align*}
-            \end{definition}
-            \begin{remark}
-                The parameter $\eta_t, \tilde\eta_{t + 1}$ are exactly the same as Ahn, Sra \cite[(6.24)]{ahn_understanding_2022}, but with the choice of $\mu = 0$. 
-                This form is not explictly stated by Ahn and Sra but it's trivial to realize its presence regardless. 
-                They are the same parameters for both algorithms and they are equivalent. 
-                For a demonstration, see 
-                \hyperref[prop:tri_form_via_ppm]{proposition \ref*{prop:tri_form_via_ppm}}. 
-            \end{remark}
-
-            \begin{definition}[Strongly Convex Generic Form]
-                \quad \\
-                With $f$ being $L$-Lipschitz smooth and $\mu > 0$ strongly convex then the Strongly convex generic form has updates of for iterates
-                \begin{align*}
-                    x_{t + 1} &= (1 + \mu\tilde \eta_{t + 1})^{-1}(x_t + \mu\tilde\eta_{t + 1}y_t^+), 
-                    \\
-                    z_{t + 1} &= y_t - L^{-1}\nabla f(y_t), 
-                    \\
-                    y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}(x_{t + 1} + L\eta_{t + 1}z_{t +1}). 
-                \end{align*}
-            \end{definition}
-            \begin{remark}
-                This algorithm is equivalent to 
-                \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}. 
-                See \ref*{prop:tri_scvx_from_ahn_sra_6.24} for a demonstration. 
-            \end{remark}
-
-        \subsubsection{AG Concrete Examples}
-            In this section we state variants of the Nesterov accelerated gradient method found in the literatures which are not generic.
-
-            \begin{definition}[AG Ryu 12.1]
-            \label{def:ag_ryu_12.1}
-                State in chapter 12 in Ryu's writing \cite{ryu_large-scale_2022} is the following variant of accelerated gradient algorithm: 
-                \begin{align*}
-                    z_{t + 1} &= y_k + L^{-1}\nabla f(y_t), 
-                    \\
-                    y_{t + 1} &= z_{t + 1} + \frac{t - 1}{t + 2}\left(
-                        z_{k + 1} - z_k
-                    \right). 
-                \end{align*}
-                An equivalent form of the above is also provided by Ryu: 
-                \begin{align*}
-                    z_{t + 1} &= y_t + L^{-1}\nabla f(y_t), 
-                    \\
-                    x_{t + 1} &= x_t + (t + 1)(2L)^{-1}\nabla f(y_t), 
-                    \\
-                    y_{t + 1} &= \left(
-                        1 - \frac{2}{t + 2} 
-                    \right)z_{t + 1} + 
-                    \left(
-                        \frac{2}{t + 2}
-                    \right)x_{t + 1}. 
-                \end{align*}
-            \end{definition}
-            \begin{observation}
-                The base case requires cares since it's not unique, there are more representations  depending on how the base case is define, 
-                Observe that the second equivalent form is an example of \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
-                \par\noindent
-                It is stated in Ryu's writing that the base case is $x_0 = y_0 = z_0$, 
-                we think this is not the only options. 
-                We remind the reader that there is not an obvious choice of $t\in \mathbb Z$ such that $x_t = y_t = z_t$ where the above algorithm remains consistent for all $t \ge -1$. 
-                The choice of base case presented in Ryu's writing is a choice and not a necessity. 
-                We state that one of the base case scenario that only requires knowing $y_1$.
-
-                \par\noindent 
-                We need to observe the case where $t = 0$ to understand the base case of the algorithm. 
-                At each iteration $t$, Given $(x_t, y_t)$, the above formula maps to $(x_{t + 1}, y_{t + 1}, z_{t + 1})$. 
-                When $t= 0$, it has $y_1 = x_1$. 
-                Therefore, knowing only either $y_1$, or $x_1$ can initiate the algorithm. 
-                This is an alternative scenario of the base case. 
-                If, we wish to write $y_0 = x_0$ at $t = 0$ for the base case instead, then it creates the following algorithm 
-                \begin{align*}
-                    y_{t} &= \left(
-                    1 - \frac{2}{t + 2} 
-                    \right)z_{t} + 
-                    \left(
-                        \frac{2}{t + 2}
-                    \right)x_{t}, 
-                    \\
-                    z_{t + 1} &= y_t + L^{-1}\nabla f(y_t), 
-                    \\
-                    x_{t + 1} &= x_t + (t + 1)(2L)^{-1}\nabla f(y_t). 
-                \end{align*}
-                It has a different representations due to a specific choice of the base case. 
-                \par\noindent
-                Finally, by the observation that given $(z_t, y_t)$ for any $t\ge -1$, we can solve for $x_t$ \newline via $y_t = (1 - 2/(1 + t))z_t + 1/(t + 1)x_t$, obtaining $(x_t, y_t, z_t)$, hence the algorithm can be reduced to a representations with only $(z_t, y_t)$ and an updates using only $(z_t, y_t)$ to $(z_{t + 1}, y_{t + 1})$.
-                That is the momentum form presented above. 
-            \end{observation}
-            \begin{remark}
-                We advise the reader to read the Biliography notes by Ryu \cite[chapter 12]{ryu_large-scale_2022} of his book. 
-                It goes over the full context and history for this particular variant of gradient acceleration method. 
-                At the time of composing this notes, the writer is still reading on the topic of accelerated gradient.     
-            \end{remark}
-
-            \begin{definition}[Proximal Gradient variant of Ryu 12.1]
-            \label{def:ag_tri_pt_form_E}
-                The method appeared in Ryu's text is a special case of 
-                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
-                with the condition that $\tilde \eta_t = \eta_t$ for all $t \in \mathbb N$ and $g \equiv 0$ for the non-smooth part of the objective. 
-                As a consequence, the algorithm has the following updates for iterates $(y_t, x_{t + 1}, z_{t + 1})$: 
-                \begin{align*}
-                    y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
-                    \\
-                    x_{t + 1} &= x_t - \eta_t \mathcal G_L(y_t)
-                    \\
-                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t).
-                \end{align*}
-            \end{definition}
-
-            \begin{definition}[Similar Triangle Form I]
-            \label{def:ag_form_similar_tria_I}
-                The similar triangle form is equivalent to the classic nesterov accelerated gradient proposed back in 1983. 
-                It updates iterates $(y_t, x_{t + 1}, z_{t + 1})$ using 
-                \begin{align*}
-                    z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t) 
-                    \\
-                    x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
-                    \\
-                    y_{t + 1} &= 
-                    (1 + L\eta_{t + 1})^{-1}
-                    (x_{t + 1} + L\eta_{t + 1}z_{t + 1}). 
-                \end{align*}
-            \end{definition}
-            \begin{observation}
-                There are a lot of observations about this form to unpack. 
-                Let's list the following observations
-                \begin{enumerate}
-                    \item Observe that $y_t = (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)$ is a convex combination between $x_t, z_t$.
-Hence $z_t, y_t, x_t$ are three collinear points.
-Additionally, we have $y_t - x_t = L\eta_t (z_t - y_t)$, hence $\Vert y_t - x_t\Vert/\Vert z_t - y_t\Vert = L\eta_t$.
-                    \item By the algorithm, we have $z_{t + 1} - y_t = - L^{-1} \mathcal G_L(y_t)$, and $x_{t + 1} - x_t = - \tilde \eta_{t + 1} \mathcal G_L(y_t)$, hence vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$.
-                    \item Finally, with update $x_{t +1} - z_{t + 1} = L\eta_t (z_{t +1} - z_t)$, we have three colinear points $(z_t, z_{t + 1}, x_t)$ with $\Vert z_{t + 1} - z_t\Vert/\Vert z_{t +1 } - z_t\Vert = L\eta_t$.
-                \end{enumerate}
-                From the above results, we can conclude that triangle $(y_t, z_t, z_{t + 1})$ is similar to $(x_t, z_t, x_{t + 1})$ because they share colinear points $z_t, y_t, x_t$ and $z_t, z_{t + 1}, x_{t + 1}$, and their sides $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$.
-            \end{observation}
-            \begin{remark}
-                The above algorithm is a special case of 
-                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}, 
-                see 
-                \hyperref[sec:scenario_ii]{section \ref*{sec:scenario_ii}} for more information. 
-            \end{remark}
-
-            \begin{definition}[Similar Triangle Form II]
-            \label{def:ag_form_similar_tria_II}
-
-            \end{definition}
-
-        \subsubsection{Useful Observations about these Generic forms}
-        \label{sec:AG_useful_information}
-
-            In this section we list some incredibaly useful information about these forms of the Nestrov type accelerated gradient algorithm. 
-            \hyperref[prop:tri_form_via_ppm]{Proposition \ref*{prop:tri_form_via_ppm}}, 
-            \hyperref[prop:tri_scvx_from_ahn_sra_6.24]{proposition \ref*{prop:tri_scvx_from_ahn_sra_6.24}}, 
-            \hyperref[prop:Nes2.2.7_via_ahn_sra_6.24]{proposition \ref*{prop:Nes2.2.7_via_ahn_sra_6.24}}
-            are results assumed as true in Ahn, Sra. 
-            They are implicitly left as necessary exercises for the readers. 
-            Here, we fill out the blanks with our own interpretations. 
-            \hyperref[prop:derive_ag_prox_grad_tript]{Proposition \ref*{prop:derive_ag_prox_grad_tript}} 
-            is our contribution where we intorduce non-smooth ness to the objective function while still retaining the PPM interpretation of accelerated gradient.
-
-            \begin{proposition}[Tri-points generic form via Ahn Sra 6.24]
-                \label{prop:tri_form_via_ppm}
-                with $f$ being \\
-                $L$-Lipschitz smooth, 
-                let $l_f(x, \bar x) = f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle$, we can show that the AG generic triangular form is a consequence of th AG generic PPM form. 
-            \end{proposition}
-            \begin{proof}
-                Solving the optimality on the first PPM yields: 
-                \begin{align*}
-                    \mathbf 0 &= \nabla f(y_t) + 
-                    \frac{1}{\tilde \eta_{t + 1}} (x - x_t)
-                    \\
-                    x &= x_t - \tilde \eta_{t + 1} \nabla f(y_t).
-                \end{align*}
-                Therefore, $x_{t + 1} = x_t - \tilde \eta_{t + 1}\nabla f(y_y)$. 
-                Similarly, for the updates of $y_{t + 1}$, we have optimality condition of 
-                \begin{align*}
-                    \mathbf 0 &= \nabla f (y_t) + L (x - y_t) + \eta_{t + 1}^{-1} (x - x_{t + 1})
-                    \\
-                    \mathbf 0 &= \eta_{t + 1}\nabla f (y_t) + \eta_{t + 1}L (x - y_t) + x - x_{t + 1}
-                    \\
-                    \mathbf 0 &= 
-                    \eta_{t + 1}\nabla f(y_t) -\eta_{t + 1} Ly_t + (\eta_{t + 1}L + 1)x - x_{t + 1}
-                    \\
-                    (1 + \eta_{t + 1}L)x
-                    &= 
-                    x_{t + 1} - \eta_{t + 1}\nabla f(y_t) + \eta_{t + 1}L y_t
-                    \\
-                    \text{define: } y_{t + 1} &:= x. 
-                \end{align*}
-                In the above expression, it hides a step of gradient descent, continuing it we have 
-                \begin{align*}
-                    (1 + \eta_{t + 1}L)y_{t + 1} &= 
-                    x_{t + 1}  + \eta_{t + 1}L (-L^{-1}\nabla f(y_t) + y_t)
-                    \\
-                    \text{let: } z_{t + 1} &= y_t - L^{-1}\nabla f(y_t), \text{ so, }
-                    \\
-                    (1 + \eta_{t + 1}L)y_{t + 1} &= 
-                    x_{t + 1} + L\eta_{t + 1}z_{t + 1}. 
-                \end{align*}
-                Combining it yields the tree points update format 
-                \begin{align*}
-                    x_{t + 1} &= x_t - \tilde \eta_{t + 1} \nabla f(y_t) 
-                    \\
-                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t) 
-                    \\
-                    y_{t + 1} &= 
-                    (1 + L\eta_{t + 1})^{-1}
-                    (
-                    x_{t + 1} + L\eta_{t + 1}z_{t + 1}
-                    ), 
-                \end{align*}
-                the ordering of $x_{t +1}, z_{t + 1}$ can be permuted. 
-                The base case is when $t = 0$, so then $x_0 = y_0$ for the initial guess.
-            \end{proof}
-            \begin{remark}
-                It is quite obvious to us that the choice of $z_{t + 1} = y_t - L^{-1}\nabla f(y_t)$ is deliberate. 
-                In fact, it's true that $z_{t + 1}$ is just a term such that it makes $y_{t +1}$ a convex combination between the vector $x_{t + 1}, z_{t + 1}$, and the choice here would be unique because of the consideration that
-                {\footnotesize
-                \begin{align*}
-                    & \quad 
-                    l_f(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 
-                    \\
-                    &= 
-                    f(y_t) + \langle \nabla f(y_t), x - y_t\rangle 
-                    + 
-                    \frac{L}{2}
-                    \left\Vert 
-                        x - (y_t - L^{-1}\nabla f(y_t)) - L^{-1}\nabla f(y_t)
-                    \right\Vert^2
-                    \\
-                    &= 
-                    f(y_t) + 
-                    \langle \nabla f(y_t), x - (y_t - L^{-1}\nabla f(y_t)) - L^{-1}\nabla f(y_t)\rangle 
-                    + 
-                    \frac{L}{2}
-                    \left\Vert 
-                        x - (y_t - L^{-1}\nabla f(y_t)) - L^{-1}\nabla f(y_t)
-                    \right\Vert^2
-                    \\
-                    &\quad  \text{Let }z_{t + 1} 
-                    = y_t - L^{-1}\nabla f(y_t)
-                    \\
-                    &= f(y_t) + \langle \nabla f(y_t), x - z_{t + 1} - L^{-1}\nabla f(y_t)\rangle
-                    + 
-                    \frac{L}{2}\left\Vert
-                        x - z_{t + 1} - L^{-1}\nabla f(y_t)
-                    \right\Vert^2
-                    \\
-                    &= 
-                    f(y_t) + \langle \nabla f(y_t), x - z_{t + 1}\rangle 
-                    - L^{-1}\Vert \nabla f(y_t)\Vert^2
-                    + 
-                    \frac{L}{2}\Vert x - z_{t + 1}\Vert^2 + 
-                    \frac{1}{2L}\Vert \nabla f(y_t)\Vert^2 - 
-                    L\langle L^{-1}\nabla f(y_t), x - z_{t + 1}\rangle
-                    \\
-                    &= f(y_t) + (1/(2L)- L^{-1})\Vert \nabla f(y_t) \Vert^2 + 
-                    \frac{L}{2}\Vert x - z_{t + 1}\Vert^2
-                    \\
-                    &= f(y_t) - \frac{1}{2L}\Vert \nabla f(y_t)\Vert^2 + \frac{L}{2}\Vert x - z_{t + 1}\Vert^2. 
-                \end{align*}
-                }
-                Therefore 
-                \begin{align*}
-                    y_{t + 1} &= \argmin_{x}\left\lbrace
-                        \frac{L}{2}\Vert x - z_{t + 1}\Vert^2 + 
-                        \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
-                    \right\rbrace
-                    \\
-                    &= \argmin_{x}\left\lbrace
-                        \left\Vert x - 
-                            \frac{Lz_{t + 1} + \eta_{t + 1}^{-1}x_{t + 1}}{
-                                L + \eta_{t + 1}^{-1}
-                            }
-                        \right\Vert^2
-                    \right\rbrace
-                    \\
-                    &= 
-                    \frac{
-                        L\eta_{t + 1}z_{t + 1} + 
-                        x_{t + 1}
-                    }{
-                        1 + L \eta_{t + 1}
-                    }. 
-                \end{align*}
-            \end{remark}
-
-            \begin{proposition}[Tri-points Strongly Convex Form via Ahn Sra 6.24]\label{prop:tri_scvx_from_ahn_sra_6.24}
-                Coninue \\ 
-                from \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} with but with $\mu > 0$, under the same set of assumptions it recovers a tri-points algorithm with the following updates: 
-                \begin{align*}
-                    y_t^+ &= y_t - \mu^{-1}\nabla f(y_t)
-                    \\
-                    x_{t + 1} &= \argmin_{x} 
-                    \left\lbrace
-                        l_f (x; y_t) + \frac{\mu}{2} \Vert x - y_t\Vert^2 + 
-                        \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2 
-                    \right\rbrace
-                    \\
-                    &= \argmin_{x}
-                    \left\lbrace
-                        f(y_t) - \frac{1}{2\mu} \Vert \nabla f(y_t)\Vert^2 
-                        + 
-                        \frac{\mu
-                        }{2}\Vert x - y_t^+\Vert^2
-                        + 
-                        \frac{1}{2\tilde \eta_{t + 1}}\Vert x - x_t\Vert^2
-                    \right\rbrace
-                    \\
-                    &= (1 + \mu\tilde \eta_{t + 1})^{-1}
-                    \left(
-                        x_t + \mu \tilde \eta_{t + 1}y_t^{+}
-                    \right)
-                    \\
-                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t)
-                    \\
-                    y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}(x_{t + 1} + L \eta_{t + 1} z_{t + 1})
-                \end{align*}
-            \end{proposition}
-            \begin{proof}
-                By a similar argument made in the remarks of \hyperref[prop:tri_form_via_ppm]{proposition \ref*{prop:tri_form_via_ppm}} we have 
-                \begin{align*}
-                    l_f(x; y_t) + \frac{\mu}{2}\Vert x - y_t\Vert^2
-                    &= 
-                    f(y_t) - \frac{1}{2\mu}\Vert \nabla f(y_t)\Vert^2 + \frac{\mu}{2}\Vert x - y_t^+\Vert^2
-                    \\
-                    \implies 
-                    x_{t + 1} &= 
-                    \argmin_{x} 
-                    \left\lbrace
-                        f(y_t) - \frac{1}{2\mu}\Vert \nabla f(y_t)\Vert^2 + \frac{\mu}{2}\Vert x - y_t^+\Vert^2
-                        + 
-                        \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
-                    \right\rbrace
-                    \\
-                    &= 
-                    \argmin_{x}
-                    \left\lbrace
-                        \frac{\mu}{2}\Vert x - y_t^+\Vert^2 + 
-                        \frac{2}{\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
-                    \right\rbrace
-                    \\
-                    &= (\mu + \tilde \eta_{t + 1})^{-1}
-                    (\mu y_t^+ + \tilde \eta_{t + 1}x_t)
-                    \\
-                    &= (1 + \tilde \eta_{t + 1}\mu)^{-1}
-                    (x_t + \mu\tilde \eta_{t + 1}y_t^+). 
-                \end{align*}
-                The updates for $y_{t + 1}, z_{t + 1}$ is the same as before because $\mu > 0$ only alters the update of the term $x_{t + 1}$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}. 
-            \end{proof}
-
-            \begin{proposition}[Nestrov 2.2.7 is Equivlant to Ahn Sra 6.24 in Form]
-            \label{prop:Nes2.2.7_via_ahn_sra_6.24}
-                The \hyperref[def:Nes2.2.7]{algorithm \ref*{def:Nes2.2.7}} is equivalent to \hyperref[def:agg_ppm]{\ref*{def:agg_ppm}} in form. 
-                So the updates for $y_{k + 1}, x_{k + 1}, v_{k + 1}$: 
-                \begin{align*}
-                    \text{find } &
-                    \alpha_k \in (0, 1) 
-                    \text{ s.t: } L\alpha_k^2 
-                    = (1 - \alpha_k)\gamma_k + \alpha_k \mu = \gamma_{k + 1} 
-                    \\
-                    y_k &= 
-                    \left(
-                        \gamma_k + \alpha_k \mu
-                    \right)^{-1} \left(
-                        \alpha_k \gamma_k v_k + \gamma_{k + 1}x_k
-                    \right)
-                    \\
-                    \text{find } & x_{k + 1} \text{ s.t: }
-                    f(x_{k + 1})
-                    = f(y_k) - (2L)^{-1}\Vert \nabla f(y_k)\Vert^2
-                    \\
-                    v_{k+1} &= 
-                    \gamma_{k + 1}^{-1} 
-                    \left(
-                        (1 - \alpha_k) \gamma_k v_k + 
-                        \alpha_k \mu y_k 
-                        - \alpha_k \nabla f(y_k)
-                    \right). 
-                \end{align*}
-                Is the same as $y_{t + 1}, z_{t + 1}, x_{t + 1}$ from below: 
-                \begin{align*}
-                    x_{t + 1} 
-                    & = 
-                    (1 + \tilde \eta_{t + 1}\mu)^{-1}
-                    (x_t + \mu\tilde \eta_{t + 1}y_t - \tilde \eta_{t + 1}\nabla f(y_t))
-                    \\
-                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t)
-                    \\
-                    y_{t + 1} &= 
-                    (1 + L\eta_{t + 1})^{-1}
-                    (x_{t + 1} + L \eta_{t + 1} z_{t + 1}).
-                \end{align*}
-                which is an equivalent representation of \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} as showned in \hyperref[prop:tri_scvx_from_ahn_sra_6.24]{propostion \ref*{prop:tri_scvx_from_ahn_sra_6.24}}.
-            \end{proposition}
-            \begin{proof}
-                We simplify the Nesterov form into the Strongly convex Generic Triangular Form. 
-                Consider update for $v_{k + 1}$ by substituting $\gamma_{k+1} = (1 - \alpha_k) \gamma_k + \alpha_k \mu$ as informed by the first step of the algorithm, we have 
-                \begin{align*}
-                    v_{k + 1} &= 
-                    ((1 - \alpha_k)\gamma_k + \alpha_k \mu)^{-1}
-                    \left(
-                        (1 - \alpha_k)\gamma_k v_k + \alpha_k \mu y_k - \alpha_k \nabla f(y_k)
-                    \right)
-                    \\
-                    &= ((1 - \alpha_k)\gamma_k + \alpha_k \mu)^{-1}
-                    (
-                        (1 - \alpha_k)\gamma_k v_k + \alpha_k \mu(y_k - \alpha_k \mu^{-1}\nabla f(y_k))
-                    )
-                    \\
-                    &= 
-                    \left(
-                        1 + \frac{\alpha_k \mu}{(1 - \alpha_k)\gamma_k}
-                    \right)^{-1}
-                    \left(
-                        v_k
-                        + 
-                        \left(
-                            \frac{\alpha_k \mu}{(1 - \alpha_k)\gamma_k} 
-                        \right)
-                        \left(
-                            y_k 
-                            - \alpha_k \mu^{-1}\nabla f(y_k)
-                        \right)
-                    \right). 
-                \end{align*}
-                Notice that the right hand size has the same form as $x_{t + 1}$. 
-                This is true by the observation that 
-                \begin{align*}
-                    x_{t + 1} &= 
-                    (1 + \tilde\eta_{t + 1}\mu)^{-1}
-                    \left( 
-                        x_t + \mu\tilde \eta_{t + 1}
-                        \left(y_t - \mu^{-1}\nabla f(y_t)\right)
-                    \right). 
-                \end{align*}
-                Similarly, when $\mu = 0$, we have from the first step that 
-                \begin{align*}
-                    v_{k + 1} 
-                    &= ((1 - \alpha_k)\gamma_k)^{-1}
-                    (
-                        (1 - \alpha_k)\gamma_k v_k
-                        + \alpha_k \mu y_k - \alpha_k \nabla f(y_k)
-                    )
-                    \\
-                    &= 
-                    v_k - \alpha_k((1 - \alpha_k)\gamma_k)^{-1}\nabla f(y_k)
-                \end{align*}
-                which is the same as the AG generic PPM form where 
-                $$
-                    x_{t + 1} = x_t - \tilde \eta_{t + 1}\nabla f(y_t). 
-                $$
-                Next, we consider $y_{k}$ iterate of Nesterov 2.2.7. 
-                We want to write it as a convex combination of the vector $v_k,x_k$. 
-                To show that the updates $y_k$ can are of the same form, start by considering that 
-                \begin{align*}
-                    \gamma_{k + 1 } &= (1 - \alpha_k)\gamma_k + \alpha_k \mu
-                    \\
-                    &= (\gamma_k + \alpha_k \mu) - \alpha_k \gamma_k, 
-                \end{align*}
-                with the grouping we have
-                \begin{align*}
-                    y_k &= \left(
-                        \gamma_k + \alpha_k \mu
-                        \right)^{-1} \left(
-                            \alpha_k \gamma_k v_k + \gamma_{k + 1}x_k
-                        \right)
-                    \\
-                    &= 
-                    \left(
-                        \gamma_k + \alpha_k \mu
-                    \right)^{-1}
-                    \left(
-                        \alpha_k \gamma_k v_k 
-                        + 
-                        ((\gamma_k + \alpha_k\mu) - \alpha_k\gamma_k)x_k
-                    \right)
-                    \\
-                    &= 
-                    \left(
-                        \frac{\alpha_k \gamma_k}{\gamma_k + \alpha_k \mu}
-                    \right)v_k
-                    + 
-                    \left(
-                        1 - \frac{\alpha_k\gamma_k }{\gamma_k + \alpha_k \mu}
-                    \right)x_k, 
-                \end{align*}
-
-                which is indeed, a convex combination of $v_k, x_k$, if, we assume that $(\alpha_k\gamma_k)(\gamma_k + \alpha_k \mu)^{-1}$ is in the interval $(0, 1)$. 
-                We can assume it by considering $\gamma_k = L\alpha_{k-1}^2$, simplifying so that 
-                \begin{align*}
-                    \frac{\alpha_k \gamma_k}{\gamma_k + \alpha_k \mu}
-                    &= 
-                    \frac{L\alpha_k \alpha_{k - 1}^2}{L\alpha_{k - 1}^2 + \mu \alpha_k}
-                    \\
-                    &= \frac{\alpha_k \alpha_{k - 1}^2}{1 + q_f \alpha_k \alpha_{k - 1}^{-2}} \in (0, 1), 
-                \end{align*}
-                where $q_f = \mu / L \in (0, 1)$ and we recall the fact that the sequence $(\alpha_k)_{k \in \NN}$ has $\alpha_k \in (0, 1)$ and $\sum_{i = 1}^{\infty} \alpha_k = \infty$. 
-                However, it would require more works to express $\eta_t, \tilde\eta$ from Ahn Sra 6.24 using $\gamma_k, \alpha_k$ from Nesterov 2.2.7. 
-            \end{proof}
-
-            \begin{proposition}[Deriving Proximal Gradient Generic Form]
-            \label{prop:derive_ag_prox_grad_tript}
-                \quad \\
-                Continue from the proximal point interpretation of the proximal gradient 
-                (\hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}})
-                we have the equalities 
-                \begin{align*}
-                    x_{t + 1} &= \argmin_{x}
-                    \left\lbrace
-                        l_h(x, y_t) + \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
-                    \right\rbrace
-                    \\
-                    &= x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                    \\
-                    y_{t + 1} &= \argmin_{x}
-                    \left\lbrace
-                          h(y_t^+) + \langle \mathcal G_L(y_t), x - y_t\rangle + \frac{L}{2}\Vert x -y_t\Vert^2 + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
-                    \right\rbrace
-                    \\
-                    &= (1 + L\eta_{t + 1})^{-1}
-                    (x_{t + 1} + L\eta_{t + 1}(y_t - L^{-1}\mathcal  G_L(y_t))). 
-                \end{align*}
-                Therefore, the algorithm 
-                \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}
-                is equivalent to 
-                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
-            \end{proposition}
-            \begin{proof}
-                Let $y_t^+ = \mathcal T_L(y_t)$, recall that $l_h(x; y_t) = h(y_t^+) + \langle \mathcal G_L(y_t), x -y_t\rangle \le f(x)$ by the definition of algorithm. 
-                Since $l_h(x; y_t)$ is a simple linear function wrt $x$, it's not hard to minimize the quandratic where we can get $x_{t + 1} = x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t)$. 
-                For $y_{t + 1}$, observe that we can complete the square on the second and the third terms: 
-                \begin{align*}
-                    & \frac{L}{2}\left(
-                        2\langle L^{-1}\mathcal G_L(y_t), x - y_t\rangle + 
-                        \Vert x - y_t\Vert^2
-                    \right)
-                    \\
-                    &= 
-                    \frac{L}{2}
-                    \left(
-                        - \Vert L^{-1} \mathcal G_L(y_t)\Vert^2  
-                        + \Vert L^{-1} \mathcal G_L(y_t)\Vert^2 
-                        + 
-                        2\langle L^{-1} \mathcal G_L(y_t), x - y_t\rangle + 
-                        \Vert x - y_t\Vert^2
-                    \right)
-                    \\
-                    &= \frac{L}{2}\left(
-                        - \Vert L^{-1}\mathcal G_L(y_t)\Vert^2  
-                        + \Vert x - (y_t - L^{-1}\mathcal G_L(y_t))
-                        \Vert^2
-                    \right), 
-                \end{align*}
-                therefore it transforms into 
-                \begin{align*}
-                    y_{t + 1} &=\argmin_{x} \left\lbrace
-                        \frac{L}{2}\left\Vert 
-                            x - (y_t - L^{-1}\mathcal G_L(y_t))
-                        \right\Vert^2
-                        + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
-                    \right\rbrace
-                    \\
-                    &=
-                    \frac{(y_t - L^{-1}\mathcal G_L(y_t)) + x_{t + 1}}{L + \eta_{t + 1}^{-1}}.
-                \end{align*}
-                Define $z_{t + 1} = y_t - \mathcal G_L(y_t) = \mathcal T_L(y_t)$, which is the proximal gradient set, then the above expression simplifies to 
-                $$
-                y_{t + 1} = (1 + L\eta_{t +1})^{-1}(x_{t + 1}+ L\eta_{t + 1}z_{t + 1}). 
-                $$
-                As a sanity checks, notice that when 
-                $h \equiv 0$, 
-                $\mathcal G_L(x) = \nabla f(x)$ 
-                by definition, making it the same as 
-                \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
-            \end{proof}
-            \begin{remark}
-                $y_{t + 1}$ is the minimizer of a simple quadratic. 
-                Given that the original function $h$ is potentially non-smooth, therefore it's not always an upper bound of $h(x)$. 
-                The upper bound interpretation of the smooth case as proposed by Ahn, Sra for the update of $y_{t + 1}$ fails when $h$ is non-smooth! 
-            \end{remark}
-
-            \begin{lemma}[Deriving Similar Triangle Form I]
-                \quad \\
-                With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$ 
-                in 
-                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
-                We can derive similar triangle form I as stated back in
-                \hyperref[def:ag_form_similar_tria_I]{definition \ref*{def:ag_form_similar_tria_I}}. 
-                \begin{align*}
-                    z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t)
-                    \\
-                    x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
-                    \\
-                    y_{t + 1} &= 
-                    (1 + L\eta_{t + 1})^{-1}
-                    (
-                    x_{t + 1} + L\eta_{t + 1}z_{t + 1}
-                    ). 
-                \end{align*}
-                It also has an equivalent momentum form 
-                \begin{align*}
-                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
-                    \\
-                    y_{t + 1} &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t). 
-                \end{align*}
-            \end{lemma}
-            \begin{proof}
-                To do, we show that updates sequence $x_{t + 1} = z_{t + 1} + L\eta_t (z_{t + 1} - z_t)$ is equivalent to $x_{t + 1} = x_t + \tilde\eta_{t + 1}\nabla f(y_t)$. 
-                Starting with the former, susbtitute definition of $z_{t + 1}$, $z_{t + 1} = z_t + L^{-1}\nabla f(y_t)$ expanding: 
-                \begin{align*}
-                    x_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t) 
-                    + L \eta_t y_t - \eta_t \mathcal G_L(y_t) - L\eta_t z_t
-                    \\
-                    &= 
-                    (1 + L\eta_t)y_t - (\eta_t + L^{-1})\mathcal G_L(y_t) - L\eta_t z_t
-                    \\
-                    &= \eta_t Lz_t + x_t -(\eta_t + L^{-1}) \mathcal G_L(y_t)  - L\eta_t z_t
-                    \\
-                    &= x_t - (\eta_t + L^{-1})\mathcal G_L(y_t). 
-                \end{align*}
-                So $x_{t + 1} = x_t + \tilde \eta_{t + 1}\mathcal G_L(y_t)$, by assumption $\tilde \eta_{t + 1} = \eta_t + L^{-1}$
-                Reducing it to the classic momentum form starts by 
-                \begin{align*}
-                    y_{t + 1} &= (1 + L\eta_{t + 1})^{-1} (x_{t + 1} + L\eta_{t + 1}z_{t + 1})
-                    \\
-                    &= (1 + L\eta_{t + 1})^{-1} (
-                        z_{t + 1} + L\eta_t (z_{t + 1} - z_t) + L\eta_{t + 1} z_{t + 1}
-                    )
-                    \\
-                    &= 
-                    (1 + L\eta_{t + 1})^{-1} (
-                        (1 + L\eta_{t + 1})z_{t + 1} + L\eta_t(z_{t + 1} - z_t)
-                    )
-                    \\
-                    &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t), 
-                \end{align*}
-                it negates the $x_t$ variables, therefore we have 
-                \begin{align*}
-                    z_{t + 1} &= y_t - L^{-1} \mathcal G_L (y_t)
-                    \\
-                    y_{t + 1} &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t).
-                \end{align*}
-            \end{proof}
-            \begin{remark}
-                In this remark we clarify the name ``similar triangle" as given in the literatures. 
-                We think it is a fitting name, becaues it has a similar triangle in it. 
-                We list the following observations
-                \begin{enumerate}
-                    \item 
-                    The updates for $y_{t}$ from the algorithm has 
-                    $$
-                        y_t = (1 + L\eta_t)^{-1} x_t + L\eta_t(1 + L\eta_t)^{-1} z_t, 
-                    $$
-                    therefore, $y_t$ is a convex combinations of $x_t, z_t$, so $z_t, y_t, x_t$ are three collinear points. 
-                    We have the ratio $\Vert y_t - x_t\Vert/\Vert z_t - y_t\Vert = L\eta_t$. 
-                    \item 
-                    The updates for $z_{t + 1}, x_{t + 1}$ are based on $y_t, x_t$ displaced by $L^{-1} \mathcal G_L(y_t), \tilde\eta_{t +1} \mathcal G_L(y_t)$, therefore vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$.
-                    \item The updates for $x_{t + 1}$ has $x_{t + 1} - z_{t + 1} = L\eta_t \left(z_{t + 1} - z_t\right)$, therefore, the three points $z_t, x_{t + 1}, z_{t + 1}$ are collinear. 
-                    The ratio between line segment has $\Vert x_{t + 1} - z_{t + 1}\Vert/\Vert z_{t + 1} - z_t\Vert = L\eta_t$. 
-                \end{enumerate}
-                By these tree observations, the triangle $z_{t}, z_{t + 1}, y_t$ similar to triangle $z_t, x_{t + 1}, x_t$. 
-                Finally, similar remarks about the similar triangle form can be found in Ahn, Sra's paper \cite{ahn_understanding_2022} as well.
-
-            \end{remark}
-
-    \subsection{Generic Lyapunov analysis for Accelerated gradient via PPM}
-    \label{sec:generic_ag_ppm_lyapunov_analysis}
-        The lemma theorem states targets
-        \hyperref[prop:derive_ag_prox_grad_tript]
-        {definition \ref*{prop:derive_ag_prox_grad_tript}}.
-
-        \begin{lemma}[Nonsmooth Generic AG Lyapunov Analysis]
-        \label{lemma:nsmooth_agg_lyapunov_upper_bound}
-            Continue from 
-            \hyperref[prop:derive_ag_prox_grad_tript]
-            {definition \ref*{prop:derive_ag_prox_grad_tript}},
-            we derive the non-smooth analogous case of the Lyapunov upper bound for all $t \in \mathbb N \cup \{0\}$: 
-            \begin{align*}
-                \Upsilon_{1, t + 1}^\text{AG}
-                &= 
-                \tilde\eta_{t + 1} (h(z_{t + 1}) - h(x_*)) + 
-                \frac{1}{2} (
-                    \Vert x_{t + 1} - x_*\Vert^2
-                    - 
-                    \Vert x_t - x_*\Vert^2
-                )
-                \\
-                &\le 
-                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-                + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                - \langle 
-                    \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                    x_{t + 1} - z_{t + 1}
-                \rangle
-                \\
-                \Upsilon_{2, t + 1}^\text{AG}
-                &= 
-                h(z_{t + 1}) - h(z_t) 
-                \le 
-                \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
-                \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-            \end{align*}
-        \end{lemma}
-        \begin{proof}
-            Define 
-            \begin{align*}
-                \phi_t(u) &:= 
-                \tilde \eta_{t + 1} 
-                \left(
-                    f(y_t) + g(y_t) + \langle \nabla f(y_t) + \partial g(y_t^+), u - y_t\rangle
-                    % + 
-                    % \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
-                \right)\\
-                &= 
-                \tilde \eta_{t + 1} \left(
-                    f(y_t) + \langle \nabla f(y_t), u - y_t\rangle + 
-                    % \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
-                    % + 
-                    g(y_t) + \langle \partial g(y_t^+), u - y_t\rangle
-                \right). 
-            \end{align*}
-            Then the update in the Generic Tri-Point algorithm 
-            (\hyperref[def:ag_prox_grad_ppm]
-                {definition \ref*{def:ag_prox_grad_ppm}}) 
-            has $x_{t + 1} = \hprox_{\phi_t}(x_t)$ if we ignore the difference between the constant terms $h(y_t^+)$, $f(y_t) + g(y_t)$ from above. 
-            Therefore we can use the Lyapunov inequality for PPM (\hyperref[thm:ppm_descent_ineq]
-                {theorem \ref*{thm:ppm_descent_ineq}})
-            which gives for all $x_*$: 
-            \begin{align*}
-                & \phi_t(x_{t + 1}) - \phi_t(x_*) + 
-                \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
-                \frac{1}{2}\Vert x_t - x_*\Vert^2
-                \le \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2, 
-                \\
-                & \text{where }
-                \phi_t(x_{t + 1}) =
-                \\
-                & \quad 
-                \tilde \eta_{t + 1}
-                \left(
-                    f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle + 
-                    % \frac{1}{2\tilde \eta_{t + 1}}\Vert x_{t + 1} - x_t\Vert^2
-                    % + 
-                    g(y_t) + \langle \partial g(y_t^+), x_{t + 1} - y_t\rangle
-                \right). 
-            \end{align*}
-            to simplify, consider using the $L$-smoothness of $f$, we have the inequality: 
-            \begin{align*}
-                \begin{aligned}
-                    f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle
-                    &=
-                    f(y_t) + \langle \nabla f(y_t), (x_{t +1} - z_{t + 1}) + (z_{t + 1} - y_t) \rangle
-                    \\
-                    &\ge 
-                    f(z_{t + 1}) - \frac{L}{2} \Vert z_{t + 1} - y_t\Vert^2 + 
-                    \langle \nabla f(y_t), x_{t +1} - z_{t + 1}\rangle
-                    \\
-                    &= 
-                    f(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2
-                    + \langle \nabla f(y_t), x_{t + 1} - y_t^+\rangle.     
-                \end{aligned}
-                \tag{$[*]$}
-            \end{align*}
-            further consider
-            \begin{align*}
-                \begin{aligned}
-                    g(y_t) + \langle \partial g(y_t^+), x_{t + 1} - y_t\rangle 
-                    &= g(y_t) + 
-                    \langle \partial g(y_t^+), 
-                    x_{t + 1} - y_t^+ + y_t^+ - y_t
-                    \rangle
-                    \\
-                    &= g(y_t) 
-                    + \langle \partial g (y_t^+),
-                        x_{t + 1} - y_t^+
-                    \rangle
-                    + 
-                    \langle 
-                        \partial g(y_t^+), y_t^+ - y_t
-                    \rangle
-                    \\
-                    g \text{ convex }\implies 
-                    &\ge 
-                    g(y_t^+) + 
-                    \langle \partial g(y_t^+), x_{t + 1} - y_t^+\rangle. 
-                \end{aligned}
-                \tag{$[\star]$}
-            \end{align*}
-            In the $([\star])$ derivation, we used the convexity of $g$ where 
-            \begin{align*}
-                \langle \partial g(y_t^+), y_t - y_t^+\rangle
-                &\le g(y_t) - g(y_t^+)
-                \\
-                \langle \partial g (y_t^+), y_t^+ - y_t \rangle
-                &\le 
-                g(y_t^+) - g(y_t). 
-            \end{align*}
-            Now, adding $([*]), ([\star])$, multiply their sum by $\tilde\eta_{t + 1}$ makes it equals to $\phi_t(x_{t +1 })$ , we can establish a lower bound for $\phi_t(x_{t + 1})$, yielding inequality
-            {\small
-                \begin{align*}
-                    \phi_t(x_{t + 1})
-                    &\ge 
-                    \tilde\eta_{t + 1}
-                    \left(
-                        f(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2 
-                        +
-                        \langle \nabla f(y_t), x_{t + 1} - y_t^+\rangle
-                        + 
-                        g(y_t^+) + 
-                        \langle \partial g(y_t^+), x_{t + 1} - y_t^+\rangle
-                    \right) 
-                    \\
-                    &= 
-                    \tilde\eta_{t + 1}
-                    \left(
-                        h(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2 
-                        + 
-                        \langle \partial g(y_t^+) + \nabla f(y_t), x_{t + 1} - y_t^+\rangle
-                    \right).
-                \end{align*}
-            }
-            Apply
-            \hyperref[lemma:grad_map_lemma_first]{lemma \ref*{lemma:grad_map_lemma_first}} 
-            we have $\partial g(y_t^+) + \nabla f(y_t) \ni \mathcal G_L(y_t)$, and by the algorithm updates $y_t^+ = z_{t + 1}$, therefore the above inequality simplifies to 
-            \begin{align*}
-                \phi_t(x_{t + 1}) &\ge 
-                \tilde\eta_{t + 1} 
-                \left(
-                    h(z_{t + 1}) - 
-                    \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                    + 
-                    \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
-                \right). 
-            \end{align*}
-            Finally, from (\hyperref[lemma:grad_map_linearization]
-                {lemma \ref*{lemma:grad_map_linearization}})
-            we have $\phi_t(u) \le \tilde\eta_{t + 1}h(u)$ for all $u$. 
-            With that we lower bound the LHS of the PPM Lyapunov inequality of $\phi_t(u)$, making: 
-            {\footnotesize
-            \begin{align*}
-                & \phi_t(x_{t + 1}) - \phi_t(x_*) + 
-                \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
-                \frac{1}{2}\Vert x_t - x_*\Vert^2
-                \le
-                \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-                \\
-                \implies &
-                \tilde \eta_{t + 1}
-                \left(
-                    h(z_{t + 1}) - 
-                    \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                    + 
-                    \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
-                \right) - \tilde \eta_{t + 1} h(x_*)
-                +
-                \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
-                \frac{1}{2}\Vert x_t - x_*\Vert^2
-                \\
-                & \quad \le
-                \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-                \\
-                \iff &
-                \tilde\eta_{t + 1}(h(z_{t + 1}) - h(x_*))
-                + \frac{1}{2}\left(
-                    \Vert x_{t + 1} - x_*\Vert^2 
-                    - 
-                    \Vert x_t - x_*\Vert^2
-                \right) =: \Upsilon_{1, t + 1}^\text{AG}
-                \\
-                &\quad \le 
-                \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-                - 
-                \tilde\eta_{t + 1}
-                \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
-                + 
-                \frac{L \tilde\eta_{t + 1}}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-            \end{align*}
-            }
-            It established the first inequality that we wish to prove. 
-            Next, the smoothness of $f$ establish inequality: 
-            \begin{align*}
-                \begin{aligned}
-                    f(z_{t + 1}) - f(z_t) &= f(z_{t + 1}) - f(y_t) + f(y_t) - f(z_t) 
-                    \\
-                    &\le 
-                    \langle \nabla f(y_t), z_{t + 1} - y_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2 
-                    + 
-                    \langle \nabla f(y_t), y_t - z_t\rangle
-                    \\
-                    &= 
-                    \langle \nabla f(y_t), z_{t + 1} - z_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-                \end{aligned}
-                \tag{$[**]$}
-            \end{align*}
-            The convexity of $h$ establish 
-            \begin{align*}
-                \begin{aligned}
-                    g(z_{t + 1}) + 
-                    \langle \partial g(z_{t + 1}), z_t - z_{t + 1}\rangle
-                    &\le g(z_t)
-                    \\
-                    g(z_{t + 1}) - g(z_t)
-                    &\le 
-                    \langle 
-                        \partial g (z_{t +1}), 
-                        z_{t + 1} - z_t
-                    \rangle. 
-                \end{aligned}
-                \tag{$[\star *]$}    
-            \end{align*}
-            Adding $([**]), ([\star *])$ yields 
-            \begin{align*}
-                \begin{aligned}
-                    \Upsilon_{2, t + 1}^{\text{AG}} := 
-                    h(z_{t + 1}) - h(z_t) 
-                    &\le 
-                    \langle 
-                        \nabla f(y_t) + \partial g(z_{t+1}), 
-                        z_{t + 1} - z_t
-                    \rangle + 
-                    \frac{L}{2}
-                    \Vert 
-                        z_{t + 1} - y_t
-                    \Vert^2. 
-                \end{aligned}
-            \end{align*}
-            Using the property of gradient mapping (\hyperref[lemma:grad_map_lemma_first]
-                {lemma \ref*{lemma:grad_map_lemma_first}}), 
-            $\mathcal G_L(y_t) \in \nabla f(y_t) + \partial g(z_{t + 1})$, substituting it, we proved all we want to show. 
-        \end{proof}
-
-        \begin{theorem}[Generic AG Convergence]
-        \label{thm:generic_ag_convergence}
-            If there is a choice of $\eta_i, \tilde \eta_i$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} such that we have 
-            \begin{align*}
-                \left(
-                    \sum_{i = 1}^{t} \tilde \eta_i
-                \right)
-                \Upsilon_{2, t + 1}^{\text{AG}} + 
-                \Upsilon_{1, t + 1}^{\text{AG}} 
-                &\le \delta_{t + 1} \quad 
-                \forall t \in \mathbb N, 
-                \\
-                \Upsilon_{1, 1}^{\text{AG}} &\le \delta_1. 
-            \end{align*}
-            then with 
-            \begin{align*}
-                S_t &:= \sum_{i = 1}^{t} \delta_i
-                \\
-                \sigma_t &:= \sum_{i = 1}^{t}\tilde \eta_i
-                \\
-                \Phi_t &= \left(
-                    \sum_{i = 1}^{t} \tilde\eta_{i}
-                \right) (f(z_t) - f(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \NN
-                \\
-                \Phi_0 &= \frac{1}{2}\Vert x_0 - x_*\Vert^2, 
-            \end{align*}
-            we have $\Phi_{t + 1} - \Phi_t \le \delta_{t + 1}$, which allows for a convergence rate of $\mathcal O \left(\sigma_T^{-1}S_T\right)$ of $f(z_T) - f(x_*)$ when $S_T \neq 0$ and a rate of $\mathcal O(\sigma_T^{-1})$ when $S_T = 0$.
-        \end{theorem}
-        \begin{proof}
-            By definition we have
-            {\footnotesize
-            \begin{align*}
-                \Phi_{t + 1} - \Phi_t 
-                &= 
-                \left(
-                    \sum_{i = 1}^{t+1} \tilde\eta_{i}
-                \right) (f(z_{t + 1}) - f(x_*)) 
-                - 
-                \left(
-                    \sum_{i = 1}^{t} \tilde\eta_{i}
-                \right) (f(z_{t}) - f(x_*)) 
-                + \frac{1}{2}\Vert x_t - x_*\Vert^2
-                - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
-                \\
-                &= 
-                \tilde \eta_{t + 1} (f(z_{t + 1}) - f(z_*))
-                +
-                \left(
-                    \sum_{i = 1}^{t} \tilde \eta_i
-                \right)(f(z_{t + 1}) - f(z_t))
-                + \frac{1}{2}\Vert x_t - x_*\Vert^2
-                - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
-                \\
-                &= \left(
-                    \sum_{i = 1}^{t} \tilde \eta_i
-                \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le \delta_{t + 1}. 
-            \end{align*}
-            }
-            Telescoping we have 
-            \begin{align*}
-                \Phi_{t + 1} - \Phi_t &\le \delta_{t + 1}
-                \\
-                \sum_{i = 0}^{T - 1}\Phi_{i + 1} - \Phi_i &\le \sum_{i = 0}^{T - 1}\delta_{i + 1}
-                \\
-                \Phi_T - \Phi_0 &\le 
-                \sum_{i = 1}^{T}\delta_i = S_{T}. 
-            \end{align*}
-            So then $\Phi_T - \Phi_0$ yields: 
-            $$
-            \begin{aligned}
-                \sigma_T (f(z_t) - f(x_*)) 
-                + \frac{1}{2}\Vert x_t - x_*\Vert^2 
-                - \frac{1}{2}\Vert x_0 - x_*\Vert^2 
-                &\le S_{T}
-                \\
-                \implies 
-                \sigma_T(f(z_t) - f(x_*))
-                &\le 
-                S_T + \frac{1}{2}\Vert x_0 - x_*\Vert^2
-                \\
-                f(z_t) - f(x_*) &\le 
-                \sigma_T^{-1}\left(
-                    S_{T} + \frac{1}{2}\Vert x_0 - x_*\Vert^2
-                \right),
-            \end{aligned}
-            $$
-            which yields a convergence rate $\mathcal O(\sigma_T^{-1}S_{T})$. 
-            When $S_T = 0$, the convergence rate is $O(\sigma_T^{-1})$ instead. 
-        \end{proof}
-
-        \begin{theorem}[Constraints on the PPM stepsize sequence]
-            \;\\
-            Algorithm proposed back in 
-            \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
-            converges if the stepsize sequence $\eta_i, \tilde \eta_{i}$ satisfies
-            \begin{align*}
-                \begin{cases}
-                    \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
-                    - L^{-1} \sum_{i= 1}^{t}\tilde \eta_i 
-                    = 
-                    \epsilon_{t + 1} \tilde \eta_{t + 1}
-                    & \forall t \in \mathbb N, 
-                    \\
-                    L \eta_t \tilde \eta_{t + 1} = \sum_{i=1}^{t}\tilde \eta_i 
-                    & \forall t \in \mathbb N. 
-                \end{cases}
-            \end{align*}
-            Here $\epsilon_{t + 1}$ is an arbitrary sequence made represent the quantity in the left hand side. 
-            Then such a sequence creates 
-            \begin{align*}
-                \Phi_{t + 1} - \Phi_t =
-                \Upsilon_{1, t + 1}^\text{AG} + 
-                \sigma_t\Upsilon_{1, t + 1}^{\text{AG}} 
-                &\le \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}
-            \end{align*}
-
-        \end{theorem}
-        \begin{proof}
-
-        \end{proof}
-
-    % \subsection{Scenario I}\label{sec:scenario_i}
-    %     In this scenario, we aim to recover AG Ryu 12.1 conceret variant algorithm stated back in 
-    %     \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}. 
-    %     \begin{proposition}
-    %         Continue from
-    %         \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}, 
-    %         set $\eta_{t + 1} = \tilde \eta_{t + 1} = (t)/(2L)$, we derive the following algorithm: 
-    %         \begin{align*}
-    %             x_{t + 1} &= x_t - \frac{t + 1}{2L} \mathcal G_L(y_t), 
-    %             \\
-    %             z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t), 
-    %             \\
-    %             y_{t + 1} &= 
-    %             \left(
-    %                 \frac{2}{t + 3}
-    %             \right)x_{t +1} + 
-    %             \left(
-    %                 1 - \frac{2}{t + 3}
-    %             \right)z_{t + 1}. 
-    %         \end{align*}
-    %         This algorithm has convergence rate of $\mathcal O(1/T^2)$ for all $h = f + g$ where $f$ is convex $L$-Lipschitz smooth and $g$ is convex. 
-    %     \end{proposition}
-    %     \begin{observation}
-    %         Observe that when $g \equiv 0$ this is the same algorithm as 
-    %         \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}
-    %         but with an alternative choice of indexing for $y_t$ and initial condition. 
-    %     \end{observation}
-    %     \begin{proof}
-    %         Recall that for the proximal gradient PPM generic form we have iterate updates for $t\in \mathbb N$: 
-    %         \begin{align*}
-    %             y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
-    %             \\
-    %             x_{t + 1} &= x_t - \tilde \eta_{t + 1} \mathcal G_L(y_t)
-    %             \\
-    %             z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t). 
-    %         \end{align*}
-    %         and generic Lyapunov upper bound 
-    %         \begin{align*}
-    %             \Upsilon_{1, t + 1}^\text{AG}
-    %             &= 
-    %             \tilde\eta_{t + 1} (h(z_{t + 1}) - h(x_*)) + 
-    %             \frac{1}{2} (
-    %                 \Vert x_{t + 1} - x_*\Vert^2
-    %                 - 
-    %                 \Vert x_t - x_*\Vert^2
-    %             )
-    %             \\
-    %             &\le 
-    %             - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-    %             + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
-    %             - \langle 
-    %                 \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-    %                 x_{t + 1} - z_{t + 1}
-    %             \rangle
-    %             \\
-    %             \Upsilon_{2, t + 1}^\text{AG}
-    %             &= 
-    %             h(z_{t + 1}) - h(z_t) 
-    %             \le 
-    %             \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
-    %             \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-    %         \end{align*}
-    %         By the updates, vector $x_{t + 1} - x_t$ and $z_{t + 1} - y_t$ are parallel by observations 
-    %         \begin{align*}
-    %             x_{t + 1} - x_t &= -\tilde\eta_{t + 1}\mathcal G_L(y_t), 
-    %             \\
-    %             z_{t + 1} - y_t &= -L^{-1}\mathcal G_L(y_t). 
-    %         \end{align*}
-    %         This setup allows for: 
-    %         \begin{align*}
-    %             \Upsilon_{1, t + 1}^{\text{AG}} 
-    %             &\le 
-    %             - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 + 
-    %             \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2 
-    %             - 
-    %             \langle \tilde\eta_{t + 1}\mathcal G_L (y_t), x_{t + 1} - z_{t + 1} \rangle
-    %             \\
-    %             &= 
-    %             - \frac{1}{2}\Vert \tilde\eta_{t + 1} \mathcal G_L\Vert^2 + 
-    %             \frac{\tilde\eta_{t + 1}L}{2}\Vert L^{-1} \mathcal G_L(y_t)\Vert^2
-    %             - 
-    %             \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), x_{t + 1} - z_{t + 1} \rangle
-    %             \\
-    %             &= 
-    %             \frac{1}{2}\left(
-    %                 - \tilde\eta_{t + 1}^2 + 
-    %                 L^{-1}\tilde\eta_{t + 1}
-    %             \right)\Vert \mathcal G_L(y_t)\Vert^2
-    %             - 
-    %             \langle 
-    %                 \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-    %                 (x_{t + 1} - x_{t}) + x_t
-    %                 + (y_t - z_{t + 1}) - y_t
-    %             \rangle
-    %             \\
-    %             &= 
-    %             \frac{1}{2}\left(
-    %                 L^{-1}\tilde\eta_{t + 1}
-    %                 - \tilde\eta_{t + 1}^2
-    %             \right)\Vert \mathcal G_L(y_t)\Vert^2
-    %             - 
-    %             \langle 
-    %                 \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-    %                 -\tilde\eta_{t + 1}\mathcal G_L(y_t) + x_t 
-    %                 + L^{-1}\mathcal G_L(y_t) - y_t
-    %             \rangle
-    %             \\
-    %             &= 
-    %             \frac{1}{2}\left(
-    %                 L^{-1}\tilde\eta_{t + 1}
-    %                 - \tilde\eta_{t + 1}^2
-    %             \right)\Vert \mathcal G_L(y_t)\Vert^2
-    %             - \langle 
-    %                 \tilde\eta_{t +1}\mathcal G_L(y_t), 
-    %                 (L^{-1} - \tilde\eta_{t + 1})\mathcal G_L(y_t) + x_t - y_t
-    %             \rangle
-    %             \\
-    %             &= \frac{1}{2}\left(
-    %                 L^{-1}\tilde\eta_{t + 1} - \tilde\eta_{t + 1}^2 
-    %                 + 2 \tilde\eta_{t + 1}^2 - 2\tilde\eta_{t + 1}L^{-1}
-    %             \right)\Vert \mathcal G_L(y_t)\Vert^2
-    %             - 
-    %             \langle 
-    %                 \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-    %                 x_t - y_t
-    %             \rangle
-    %             \\
-    %             &= 
-    %             \frac{1}{2}\left(
-    %                 \tilde\eta_{t + 1}^2 - \tilde\eta_{t + 1}L^{-1}
-    %             \right)\Vert \mathcal G_L(y_t)\Vert^2 
-    %             + \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), y_t - x_t\rangle
-    %         \end{align*}
-    %         similarly we also have upper bound 
-    %         \begin{align*}
-    %             \Upsilon_{2, t + 1}^{\text{AG}} 
-    %             &= 
-    %             \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
-    %             \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-    %             \\
-    %             &= 
-    %             \langle \mathcal G_L(y_t), z_{t + 1} - y_t + y_t - z_t\rangle
-    %             + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-    %             \\
-    %             &= 
-    %             \langle \mathcal G_L(y_t), - L^{-1} \mathcal G_L(y_t) + y_t - z_t\rangle
-    %             + 
-    %             \frac{L}{2}\Vert L^{-1}\mathcal G_L(y_t)\Vert^2
-    %             \\
-    %             &= 
-    %             -L^{-1}\Vert \mathcal G_L(y_t)\Vert^2 
-    %             + 
-    %             (1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2 
-    %             + 
-    %             \langle \mathcal G_L(y_t), y_t - z_t\rangle
-    %             \\
-    %             &= 
-    %             -(1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2
-    %             + 
-    %             \langle \mathcal G_L(y_t), y_t - z_t\rangle. 
-    %         \end{align*}
-    %         Observe that the cross product term for $\Upsilon_{1, t + 1}^\text{AG}, \Upsilon_{2, t + 1}^\text{AG}$ doesn't match. 
-    %         Hence let's consider the update for $y_t$, which can be written as $y_t - x_t = L \eta_t (z_t - y_t)$.
-We make the choice to do surgery on upper bound of $\Upsilon_{2, t + 1}^\text{AG}$, so $\langle \mathcal G_L(y_t), y_t - x_t\rangle = \langle \mathcal G_L(y_t), L \eta_t (z_t - y_t)\rangle$.
-    %         With this in mind, applying the RHS of $[(*)]$ yields: 
-    %         {\footnotesize
-    %         \begin{align*}
-    %             &\Upsilon_{1, t + 1}^\text{AG} + 
-    %             \left(
-    %                 \sum_{i = 1}^{t}\tilde\eta_i 
-    %             \right)\Upsilon_{1, t + 1}^{\text{AG}}
-    %             \\
-    %             &\le 
-    %             \frac{1}{2}\left(
-    %                 \tilde\eta_{t + 1}^2 - \tilde\eta_{t + 1}L^{-1}
-    %             \right)\Vert \mathcal G_L(y_t)\Vert^2 
-    %             + 
-    %             \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), L\eta_t(z_t - y_t)\rangle
-    %             \\
-    %             &\quad 
-    %             + 
-    %             \left(
-    %                 \sum_{i = 1}^{t}\tilde\eta_i 
-    %             \right)\left(
-    %                 -(1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2
-    %                 + 
-    %                 \langle \mathcal G_L(y_t), y_t - z_t\rangle
-    %             \right)
-    %             \\
-    %             &= 
-    %             \left(
-    %                 \frac{1}{2}\tilde\eta_{t + 1}\left(
-    %                     \tilde \eta_{t +1} - L^{-1}
-    %                 \right)
-    %                 - 
-    %                 \frac{1}{2L}\sum_{i = 1}^{t}\tilde \eta_i
-    %             \right)\Vert \mathcal G_L(y_t)\Vert^2 + 
-    %             \left(
-    %                 L\eta_t \tilde \eta_{t + 1} - \sum_{i = 1}^{t}\tilde \eta_i
-    %             \right)\langle \mathcal G_L(y_t), z_t - y_t\rangle
-    %         \end{align*}
-    %         }
-    %         If the algorithm were to have the abstract convergence rate as stated in 
-    %         \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}},
-    %         then one of the sufficient condition is to have the above quantity less than or equal to zero, one sufficient condition of that is to have the coefficient for $\Vert \mathcal G_L(y_t)\Vert$ be $\le 0$, and the coefficient of the cross term $\langle \mathcal G_L(y_t), z_t - y_t\rangle$ be zero.
-    %         To simplify, we make the assumption that $\tilde \eta_t = \eta_t$ for all $t \in \mathcal N$, making it to be a specific instance of 
-    %         \hyperref[def:ag_tri_pt_form_E]{definition \ref*{def:ag_tri_pt_form_E}}. 
-    %         These conditions translate to the following relations for $\eta_{t}$. 
-    %         \begin{align*}
-    %             \begin{cases}
-    %                 L\eta_{t + 1}^2 + \eta_{t + 1} - \sum_{i = 1}^{t}\eta_i 
-    %                 \le 0, 
-    %                 \\
-    %                 L\eta_t \eta_{t + 1} - \sum_{i = 1}^{t} \eta_i 
-    %                 = 0. 
-    %             \end{cases}
-    %         \end{align*}
-    %         Substituting the sequence equality back to the first one yield: 
-    %         \begin{align*}
-    %             L\eta_{t + 1}^2 - (\eta_{t + 1} + L\eta_t\eta_{t + 1}) &\le 0 
-    %             \\
-    %             L\eta^2_{t + 1} - \eta_{t + 1}
-    %             &\le 
-    %             L\eta_t \eta_{t + 1} 
-    %             \\
-    %             \eta_{t + 1}(L\eta_{t + 1} - 1) 
-    %             &\le L\eta_t\eta_{t + 1}
-    %             \\
-    %             \eta_t > 0 
-    %             \implies 
-    %             L\eta_{t + 1} - 1 &\le 
-    %             L\eta_t 
-    %             \\
-    %             \eta_{t + 1} &\le \eta_t + L^{-1}. 
-    %         \end{align*}
-    %         To satisfy the equality, reader should verify that $\eta_{t} = t/(2L)$ or $\eta_t = (t + 1)/2L$ are some of the options. 
-    %     \end{proof}
-    %     \begin{remark}
-    %         In the original writing by Ahn \cite[equation (4.9)]{ahn_understanding_2022}, they didn't identify this specific variant in the literature. 
-    %         Here we identify it to be equivalent to the acceleration algorithm stated in Ryu \cite[algorithm 12.1]{ryu_large-scale_2022}. 
-    %     \end{remark}
-
-    % \subsection{Scenario II}\label{sec:scenario_ii}
-    %     With the choice of $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we can recover the seminal Nesterov accelerated gradient algorithm from 1983. 
-    %     The variants proposed by Chambolle Dossal \cite{chambolle_convergence_2015}, is distinct from the possibility proposed in this secenario.
-
-    %     \begin{lemma}[Deriving the Nesterov Sequence]
-    %         For all $t \in \mathbb N$
-    %         \begin{align*}
-    %             \left\lbrace
-    %             \begin{aligned}
-    %                 (1 + L\eta_{t + 1})^{-1}L \eta_t 
-    %                 &= \frac{a_t - 1}{a_{t + 1}} , 
-    %                 \\
-    %                 a_{t + 1}^2 - a_t &= a_t^2. 
-    %             \end{aligned} 
-    %             \right. 
-    %         \end{align*}
-    %         allows \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}} to converge at an optimal rate. 
-    %         The base case is $\eta_0 = 0$. 
-    %     \end{lemma}
-    %     \begin{proof}
-    %         Continue from 
-    %         \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]{lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}, 
-    %         With $x_{t +1} - x_t = L\tilde\eta_{t+1}(z_{t + 1} - y_t)$ for $y_t$: 
-    %         \begin{align*}
-    %             \Upsilon_{1, t + 1}^\text{AG} &\le 
-    %             - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-    %                 + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
-    %                 - \langle 
-    %                     \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-    %                     x_{t + 1} - z_{t + 1}
-    %                 \rangle
-    %                 \\
-    %                 &= 
-    %                 - \frac{1}{2}\Vert L \tilde \eta_{t+} (z_{t+1} - y_t)\Vert^2 + 
-    %                 \frac{\tilde\eta_{t +1}L}{2}\Vert z_{t+1} - y_t\Vert^2
-    %                 - \langle 
-    %                     \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-    %                     x_{t + 1} - z_{t + 1}
-    %                 \rangle
-    %                 \\
-    %                 &= 
-    %                 \left(
-    %                     \frac{L^2\tilde\eta_{t + 1}^2}{2}
-    %                     + 
-    %                     \frac{\tilde \eta_{t +1}}{2}
-    %                 \right)
-    %                 \Vert z_{t+1} - y_t\Vert^2
-    %                 - 
-    %                 \langle 
-    %                     \tilde \eta_{t+ 1} \mathcal G_L(y_t), x_{t+1} - z_{t+1}
-    %                 \rangle. 
-    %         \end{align*}
-    %         This completes the analysis for $\Upsilon_{1, t + 1}^\text{AG}$ with $\tilde\eta_{t+1}$. 
-    %         Next we consider 
-    %         \begin{align*}
-    %             \Upsilon_{2, t + 1}^{\text{AG}} 
-    %             &= 
-    %             \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle
-    %             + 
-    %             \frac{L }{2} \Vert z_{t+1} - y_t\Vert^2
-    %             \\
-    %             &= 
-    %             \langle \mathcal G_L(y_t), L^{-1}\eta_t^{-1}(x_{t+1} - z_{t + 1})\rangle
-    %             + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-    %         \end{align*}
-    %         Here we used $x_{t + 1} = z_{t + 1} + L\eta_t (z_{t + 1} - z_t)$, which was the consequence of $\tilde\eta_{t + 1} = \eta_t + L^{-1}$, as discussed from before. 
-    %         Hence, the upper bound of the Lyapunov function for smooth AG PPM 
-    %         (\hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}) 
-    %         has 
-    %         {\footnotesize
-    %         \begin{align*}
-    %             & \Upsilon_{1, t + 1}^{\text{AG}} + 
-    %             \left(
-    %                 \sum_{i = 1}^{t}\tilde \eta_i
-    %             \right)\Upsilon_{2, t + 1}^{\text{AG}}
-    %             \\
-    %             &\quad \le 
-    %             \left(
-    %                 - \frac{L^2\tilde \eta_{t + 1}^2}{2}
-    %                 + \frac{\tilde\eta_{t+1}L}{2}
-    %             \right)
-    %             \Vert z_{t+1} - y_t\Vert^2
-    %             - 
-    %             \langle \tilde \eta_{t+1} \nabla f(y_t), x_{t+1} - z_{t + 1}\rangle
-    %             \\
-    %             & \qquad + 
-    %             \left(
-    %                 \sum_{i = 1}^{t}\tilde \eta_i
-    %             \right)\left(
-    %                 \langle \nabla f(y_t), L^{-1}\eta_t^{-1}(x_{t+1} - z_{t + 1})\rangle
-    %                 + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-    %             \right)
-    %             \\
-    %             &= 
-    %             \frac{L}{2}
-    %             \left(
-    %             -\tilde\eta_{t + 1}^2 + \tilde\eta_{t + 1}
-    %                 + \sum_{i = 1}^{t}\tilde\eta_i
-    %             \right)\Vert z_{t + 1} - y_t\Vert^2
-    %             +
-    %             \left(
-    %                 L^{-1}\eta_t^{-1} 
-    %                 \left(
-    %                     \sum_{i = 1}^{t}\tilde \eta_i
-    %                 \right)
-    %                 -
-    %                 \tilde \eta_{t + 1}
-    %             \right)\langle \mathcal G_L (y_t), x_{t + 1} - z_{t + 1}\rangle
-    %         \end{align*}
-    %         }
-    %         If the above quantity less than or equal to zero, it will allow for convergence of the algorithm by 
-    %         \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}.
-    %         One sufficient condition is to have the coefficients for all the cross product terms to sum up to zero, and the squared normed term to sum up to a non-positive number for all $t \in \mathbb N$.
-    %         This gives relations 
-    %         \begin{align*}
-    %             - \frac{1}{2}\left(
-    %                 L^2 \tilde\eta_{t+1}^2 - \tilde\eta_{t+1}L 
-    %             \right) + 
-    %             \frac{L}{2}\left(
-    %                 \sum_{i = 1}^{t} \tilde \eta_i
-    %             \right) &\le 0
-    %             \\
-    %             - \left(
-    %                 L\tilde \eta_{t + 1}^2 
-    %                 - 
-    %                 \tilde\eta_{t + 1}
-    %             \right) + 
-    %             \sum_{i = 1}^{t}\tilde \eta_i 
-    %             &\le 0
-    %             \\
-    %             -L \tilde \eta_{t+1} + 
-    %             \sum_{i = 1}^{t + 1} \tilde \eta_i 
-    %             &\le 0
-    %             \\
-    %             \sum_{i = 1}^{t + 1}\tilde \eta_i 
-    %             &\le L \tilde \eta_{t + 1}^2, 
-    %         \end{align*}
-    %         and equations 
-    %         \begin{align*}
-    %             -\tilde \eta_{t + 1} + 
-    %             \left(
-    %                 \sum_{i = 1}^{t}\tilde \eta_i
-    %             \right)L^{-1}\eta_t^{-1} 
-    %             &= 0
-    %             \\
-    %             \sum_{i = 1}^{t}\tilde \eta_i 
-    %             &= 
-    %             L \eta_t \tilde \eta_{t + 1}. 
-    %         \end{align*}
-    %         Susbtituting the equality into the inequalites we have 
-    %         \begin{align*}
-    %             \tilde \eta_{t + 1} + \sum_{i = 1}^{t} \tilde \eta_i 
-    %             &\le L \tilde \eta_{t + 1}^2
-    %             \\
-    %             \tilde \eta_{t + 1} + L\eta_t \tilde \eta_{t + 1}
-    %             &\le L \tilde \eta_{t + 1}^2
-    %             \\
-    %             1 + L\eta_t &\le L \tilde\eta_{t + 1}. 
-    %         \end{align*}
-    %         The choice $\tilde \eta_{t + 1} = \eta_t + L^{-1}$ makes the inequality is an equality. 
-    %         Finally, to recover the momentum stepsizes for the classical Nesterov accelerated gradient, we consider relations 
-    %         \begin{align*}
-    %             L \sum_{i = 1}^{t + 1} \tilde \eta_i 
-    %             &= L \tilde \eta_{t + 1} + L \sum_{i = 1}^{t} \tilde \eta_i 
-    %             \\
-    %             &= 
-    %             L \tilde \eta_{t + 1} + L (L \eta_t \tilde \eta_{t + 1}) 
-    %             \\
-    %             &= L \tilde \eta_{t + 1} + L \eta_t (L \eta_t + 1)
-    %             \\
-    %             &= L (\eta_t + L^{-1}) + L\eta_t (L \eta_t + 1)
-    %             \\
-    %             &= (L\eta_t + 1)^2, 
-    %         \end{align*}
-    %         Simultanenously 
-    %         \begin{align*}
-    %             L \sum_{i = 1}^{t + 1} \tilde \eta_i 
-    %             &= L^2 \eta_{t + 1} \tilde \eta_{t + 1}
-    %             \\
-    %             &= L \eta_{t + 1}(1+ L \eta_{t + 1}), 
-    %         \end{align*}
-    %         Combining yields that 
-    %         \begin{align*}
-    %             (L\eta_t + 1)^2 
-    %             &= L\eta_{t + 1}(1 + L \eta_{t + 1})
-    %             \\
-    %             &= L\eta_{t + 1} + L^2 \eta_{t + 1}^2
-    %             \\
-    %             \iff 
-    %             (L\eta_t + 1)^2 + 1/4 &= 
-    %             1/4 + 2(1/2)L \eta_{t + 1} + (L \eta_{t + 1})^2
-    %             \\
-    %             \iff 
-    %             (L\eta_t + 1)^2 + 1/4 &= 
-    %             (L \eta_{t + 1} + 1/2)^2. 
-    %         \end{align*}
-    %         With $a_t = L\eta_t + 1 = L \tilde \eta_t$ this is 
-    %         \begin{align*}
-    %             a_t^2 + 1/4 &= (a_{t + 1} - 1/2)^2 
-    %             \\
-    %             a_t^2 + 1/4 &= a_{t + 1}^2 + 1/4 - a_{t + 1}
-    %             \\
-    %             a_t^2 + a_{t + 1} &= a_{t + 1}^2. 
-    %             \\
-    %             \implies 
-    %             a_{t + 1} &= 
-    %             \frac{1 + \sqrt{1 + 4a_t^2}}{2}
-    %         \end{align*}
-    %         And that is the updates for the Nesterov momentum, recall that the momentum term is linked to the PPM sequence via relation 
-    %         \begin{align*}
-    %             (1 + L \eta_{t+ 1})^{-1}L\eta_t = L\eta_t / a_{t + 1} = (a_t - 1)/a_{t + 1}. 
-    %         \end{align*}
-    %         We had recovered the classic Nesterov acceleration sequence method for the smooth gradient descent algorithm. 
-    %     \end{proof}
-    %     \begin{remark}
-    %         This variant is distinct from the variants proposed by Chambolle \cite{chambolle_convergence_2015}, but both of which fits into the same frameworks. 
-    %         The variantis presented as 
-    %         \begin{align*}
-    %             y_n &= (1 - t_n^{-1})z_n + t_n^{-1} x_n
-    %             \\
-    %             z_{n + 1} &= y_n - L^{-1}\nabla f(y_n)
-    %             \\
-    %             x_{n + 1} &= z_n + t_{n + 1}(z_{n + 1} - z_n)
-    %         \end{align*}
-    %         They listed the choice of $t_n = (n + a - 1)/a$ for all $a > 2$. 
-    %         Under this choice, unfortunately, it's in no way obvious that this format reduces to \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
-    %         It fails the similar triangle description Without the explict representation $x_{n + 1} = z_n + \tilde\eta_{t + 1}\nabla f(y_t)$. 
-    %         \par\noindent
-    %         At the time of writing, we are still investigating the relations between these variants of algorithms.
-    %     \end{remark}
-    % \subsection{Scenario III}
+    \input{sections/ag_ppm.tex}
 

### 2024-08-08 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, big updates

--- 2024-08-05 Notebook LaTEX/Momentum Accelerations/main.tex
@@
 
-\title{{\fontfamily{ptm}\selectfont Nesterov Type Momentum Methods}}
+\title{{\fontfamily{ptm}\selectfont The Proximal Point interpretation of Nesterov accelerated proximal gradient}}
 
 \author{
-    The Alto Hivemind (My Pen name)
+    Author 1 Name, Author 2 Name
     \thanks{
@@
 
-\date{\today}
+\date{March 2, 2020}
 
@@
     \noindent
-    These are notes for Nesterov Type Acceleration Methods in the convex case. 
-    They can be made into papers, proposals, and a thesis in the future. 
-    They are tayped in \LaTeX\; so it's easier to work with. 
+    Nesterov accelreated gradient method has been in the spotlight for the past decades due its wide spread applications and theories of optimal convergence. 
+    Decades later it still opens up new interpretations. 
+    Our work suggests a proximal point interpretation of accelerated gradient method for the method of accelerated proximal gradient method as a major extension to the interpretation proposed by Ahn and Sra \cite{ahn_understanding_2022}.
+    The proofs had been streamlined, extended and new error terms are added to allow a larger set of stepsize sequence for the PPM. 
+    Additionally, we proposed a line search method to dynamically adjust the strong convexity index $\mu$ and Lipschitz constant of the gradient in algorithm implementations based on the PPM understanding, presented numerical experiments.
+
 \end{abstract}
+
 \noindent{\bfseries 2010 Mathematics Subject Classification:}
@@
 
-\pagebreak
-\tableofcontents
-\pagebreak
-% ==============================================================================
-\section{Preliminaries}
-    This section lists foundational results important for proof in the coming sections. 
-    For this section, let the ambient space be $\RR^n$ and $\Vert \cdot\Vert$ be the 2-norm until specified in the context. 
-    For a general overview of smoothness and strong convexity in the Euclidean space, see \cite[theorem 2.1.5, theorem 2.1.10]{nesterov_lectures_2018} for a full exposition of the topic. 
-    \par\noindent
-    We assume the reader is well-versed in convex optimization and convex analysis. 
-    \subsection{Lipschitz smoothness}
-        \begin{definition}[Lipschitz Smooth]
-            Let $f$ be differentiable. 
-            It has Lipschitz smoothness with constant $L$ if for all $x, y$
-            $$
-                \Vert \nabla f(x) - \nabla f(y)\Vert 
-                \le 
-                L \Vert x - y\Vert. 
-            $$    
-        \end{definition}
-
-        \begin{theorem}[Lipschitz Smoothness Equivalence]
-            With $f$ convex and $L$-Lipschitz smooth, the following conditions are equivalent conditions for all $x, y$: 
-            \begin{enumerate}
-                \item $L^{-1}\Vert \nabla f(y) - \nabla f(x)\Vert^2 \le \langle \nabla f(y) - \nabla f(x), y - x\rangle \le L\Vert y - x\Vert^2$. 
-                \item $x^+\in \argmin_x f(x) \implies \frac{1}{2L}\Vert \nabla f(x)\Vert^2 \le f(x) - f(x^+) \le (L/2) \Vert x - x^+\Vert^2$, co-coersiveness. 
-                \item $ 1/(2L)\Vert \nabla f(x) - \nabla f(y)\Vert^2 \le  f(y) - f(x) - \langle \nabla f(x), y -x\rangle \le (L/2)\Vert x - y\Vert^2$
-            \end{enumerate}    
-        \end{theorem}
-        \begin{remark}
-            Lipschitz smoothness of the gradient of a convex function is an example of a firmly nonexpansive operator.  
-        \end{remark}
-
-        \begin{definition}[Strong Convexity]
-            With $f: \RR^n \mapsto \overline \RR$, it is strongly convex with constant $\alpha$ if and only if $f - (\alpha/2)\Vert \cdot\Vert^2$ is a convex function. 
-        \end{definition}
-
-        \begin{theorem}[Stong convexity equivalences]\label{thm:str_cvx_equiv}
-            With $f:\RR^n \mapsto \overline \RR$ $\alpha$-strongly convex, the following conditions are equivalent conditions for all $x, y$: 
-            \begin{enumerate}
-                \item $f(y) - f(x) - \langle \partial f(x),y - x \rangle\ge \frac{\alpha}{2}\Vert y - x\Vert^2$
-                \item $\langle \partial f(y) - \partial f(x), y - x\rangle \ge \alpha\Vert y - x\Vert^2$. 
-                \item $f(\lambda x + (1 - \lambda)y) \le \lambda f(x) + (1 - \lambda)f(y) -\alpha\frac{\lambda(1 - \lambda)}{2}\Vert y - x\Vert^2, \forall \lambda \in [0, 1]$. 
-            \end{enumerate}
-        \end{theorem}
-
-        \begin{theorem}[Strong convexity implications]\label{thm:str_cvx_implied}
-            With $f:\RR^n \mapsto \overline \RR$ $\alpha$-strongly convex, the following conditions are implied: 
-            \begin{enumerate}
-                \item $\frac{1}{2}\operatorname{dist}(\mathbf 0; \partial f(x))^2 \ge \alpha (f(x) - f^+)$ where $f^+$ is a minimum of the function, and this is called the Polyak-Lojasiewicz (PL) inequality.
-                \item $\forall x, y\in \mathbb E, u\in \partial f(x), v\in \partial f(y): \Vert u - v\Vert\ge \alpha\Vert x - y\Vert$. 
-                \item $f(y) \le f(x) + \langle \partial f(x), y - x\rangle + \frac{1}{2\alpha}\Vert u - v\Vert^2, \forall u\in  \partial f(x), v\in \partial f(y)$. 
-                \item $\langle \partial f(x)-\partial f(y), x - y\rangle \le \frac{1}{\alpha}\Vert u - v\Vert^2, \forall u\in \partial f(x), v\in \partial f(y)$. 
-                \item if $x^+\in \arg\min_{x}f(x)$ then $f(x) - f(x^+) \ge \frac{\alpha}{2}\Vert x - x^+\Vert^2$ and $x^+$ is a unique minimizer. 
-            \end{enumerate}
-        \end{theorem}
-        \begin{remark}
-            In operator theory, the subgradient of a strongly convex function is an example of a Strongly Monotone Operator. 
-        \end{remark}
-
-    \subsection{Proximal descent inequality}
-        The proximal descent inequality below is a crucial piece of inequality for deriving the behaviours of algorithms. 
+\section{Introduction}
+    Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
+    They explored the interpretation of Nesterov acceleration as a proximal of an upper surrogate function, and then a lower surrogate function. 
+    Inspired by such an interpretation, we generalize the framework to the case of $h = f + g$ with $f$ Lipschitz smooth and $g$ convex and friendly to a proximal operator. 
+    \par
+    Classical analysis and extension of Nesterov accelerated gradient existed. 
+    See \cite*{guler_new_1992} for an extension of the Nesterov accelerated gradient method to the proximal point method for convex programming. 
+    However the classical analysis found in \cite*[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and cherry picked Nesterov's estimating sequence to assist the proof for the parameters in the algorithm.
+    In Ahn's work however, the complexities are packaged into the PPM interpretation of accelerated gradient. 
+    It uses a lemma from Moreau envelope to derive the Lypunov analysis, the sizes, and parameters for several variants of the algorithm. 
+    \par
+    Numerous notable variations of Nesterov accelerated gradient exists. \cite*[(6.1.19)]{nesterov_lectures_2018} described a variant of accelerated gradient restricted to a convex domain $Q$. 
+    Beck and Toubolle \cite{beck_fast_2009} introduced a variant the problem type of smooth plus non-smooth, known as FISTA. 
+    For a variant of accelerated gradient where the iterates converge, see \cite{chambolle_convergence_2015}. 
+    Extension such as the Harpen acceleration for the resolvent operator in general is outside of the scope since doesn't have a Moreau envelope. 
+    \par
+    A wide varieties of interpretation for the Nesterov accelerated gradient exist in the literatures. 
+    Consult \cite{su_differential_2015} for a dynamical system interpretation of Nesterov acceleration. 
+    The dynamical system interpretation of the algorithm however, lead to the valuable insights that restarting the accerlated gradient algorithm would lead to faster convergence rate for the class of strongly convex function.
+    \par
+    % The paper is organized as follow: 
+    % \begin{enumerate}
+    %     \item Section 
+    % \end{enumerate}
+
+\section{Preliminaries}\label{sec:preliminaries}
+    Fristly, recall the theorem: 
     \begin{theorem}[Proximal Descent Inequality]\label{thm:ppm_descent_ineq}
-            With $f: \RR^n \mapsto \overline \RR^n$ $\beta$-convex where $\beta \ge 0$, fix any $x \in \RR^n$, let $p = \hprox_f(x)$, then for all $y$ we have inequality 
+        With $f: \RR^n \mapsto \overline \RR^n$ $\beta$ stronly convex where $\beta \ge 0$, fix any $x \in \RR^n$, let $p = \hprox_f(x)$, then for all $y$ we have inequality 
         $$
@@
         See the proof (\cite{bauschke_convex_2017}, theorem 12.26). 
-            The additional strong convexity index is a consequence of \hyperref[thm:str_cvx_implied]{theorem \ref*{thm:str_cvx_implied}}, item (v). 
     \end{remark}
-
-        \begin{theorem}[The Bregman proximal descent inequality]\label{thm:ppm_breg_descent_ineq}
-            Let $\omega$ induce a Bregman Divergence $D_\omega$ in $\RR^n$ and assume that it satisfies Bregman Prox Admissibility conditions for the function $\varphi: \RR^n \mapsto \overline \RR$.
-            Then we claim that for all $c \in \text{dom}(\omega), b \in \text{dom}(\partial \omega)$, 
-            If 
-            \begin{align*}
-                a = \argmin_{x}\left\lbrace
-                \varphi(x) + D_\omega(x, b)
-                \right\rbrace, 
-            \end{align*}
-            we have the inequality, 
-            \begin{align*}
-                (\varphi(c) + D_\omega(c, b)) - 
-                (\varphi(a) + D_\omega(a, b)) \ge 
-                D_\omega(c, a). 
-            \end{align*}
-        \end{theorem}
-        \begin{remark}
-            For more information about what function $\omega$ can induce a Bregman divergence and the admissibility conditions for Bremgna proximal mapping, consult Heinz et.al \cite{bauschke_descent_2017}.
-        \end{remark}
-
-\section{The proximal point method with convexity}
-    This section reviews the convex case's Proximal point method (PPM) analysis and generalizes the theories to approximated PPM. 
-    \subsection{Convex PPM literature reviews}
-        Rockafellar \cite{rockafellar_monotone_1976} pioneered the analysis of the proximal point method in the convex case. 
-        He developed the analysis in the context of maximal monotone operators in Hilbert spaces. 
-        Applications in convex optimizations are covered. 
-        Using his theorems appropriately requires some opportunities, realizations, and characterizations of assumptions (A), (B) in his paper in the context of the applications. 
-        \par\noindent
-        In this section, we will use the result from Rockafellar that, if a monotone operator $A$ is $\beta$ strongly convex, then the resolvent operator $\mathcal J_A = [I + A]^{-1}$ is a $(1 + \beta)^{-1}$ Lipschitz operator, making $I - \mathcal J_A$ is a $1 - (1 + \beta)^{-1}$ a strongly monotone operator.
-
-    \subsection{The proximal point method}
-        With $f: \RR^n \mapsto \overline \RR$ lsc proper and convex, given any $x_0$ the PPM generates sequence $(x_n)_{n\in \NN}$ by $x_{k + 1} = \hprox_{\eta_{k + 1}}f(x_k)$ for all $k \in \NN$ where the sequence $(\eta_{k})_{k \in \NN}$ is a nonegative sequence of real numbers.
-
-    \subsection{The Lyapunov function of convex PPM}
-        We present some theorems that illustrate the use of \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}}. 
-        The readers can find similar analyses and techniques in Guler's work \cite{guler_convergence_1991}. 
-        \begin{theorem}[PPM Lyapunov Function]\label{ppm_lyapunov}
-            With $f$ being $\beta\ge 0$ convex (it's strongly convex if $\beta > 0$, else it's just convex) and $x_{t + 1} = \hprox_{\eta_{t + 1}f}$ generated by PPM. 
-            Define the Lyapunov function $\Phi_t$ for all $u \in \RR^n$: 
-            \begin{align*}
-                \Phi_t &:= 
-                \left(
-                    \sum_{i = 1}^{t} \eta_i
-                \right)(f(x_t) - f(u)) + \frac{1}{2} \Vert u - x_t\Vert^2 \quad \forall t \ge 1, 
-                \\
-                \Phi_0 &:= (1/2)\Vert x_0 - u\Vert^2, 
-            \end{align*}
-            then it is a Lyapunov function for the PPM algorithm. 
-            Meaning for all $(x_k)_{k \in \NN}$ generated by PPM, it satisfies that $\Phi_{t + 1} - \Phi_t \le 0$. 
-            Additionally, by definition, we have 
-            {\small
-                \begin{align*}
-                    \Phi_{t + 1} - \Phi_{t} 
-                    &= 
-                    \left(\sum_{i = 1}^{t}\eta_{i}\right)
-                    (f(x_{t + 1}) - f(x_t)) 
-                    + \frac{1}{2}\Vert x_{t + 1} - u\Vert^2 
-                    - \frac{1}{2}\Vert x_{t} - u\Vert^2
-                    +
-                    \eta_{t + 1}(f(x_{t + 1}) - f(u))
-                    \\
-                    & \le 
-                    -\left(\sum_{i = 1}^{t}\eta_{i}\right)
-                    (1 + \beta\eta_{t + 1}/2)\Vert x_{t + 1} - x_t\Vert^2
-                    + 
-                    \left(
-                        - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
-                        -\frac{\beta\eta_{t + 1}}{2}\Vert u - x_{t + 1}\Vert^2
-                    \right)
-                    \\
-                    & \le 0,
-                \end{align*}
-            }
-            And additionally, recovering the descent lemma: 
-            \begin{align*}
-                f(x_{t + 1}) - f(x_t) 
-                &\le
-                -\frac{1}{\eta_{t+1}} \Vert x_{t + 1} - x_t\Vert^2 
-                - \frac{\beta}{2}\Vert x_t - x_{t + 1}\Vert^2. 
-            \end{align*}
-        \end{theorem}
-        \begin{proof}
-            Let $\phi_{t + 1}: \RR^n \mapsto \overline \RR = \eta_{t + 1} f$ be convex,  consider proximal point method $x_{t + 1} = \hprox_{\phi}(x_t)$, apply \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}}, we have $\forall u \in \RR^n$
-            \begin{align*}
-                & \phi_{t + 1}(x_{t + 1}) 
-                + 
-                \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
-                - \phi_{t + 1}(u) - \frac{1}{2}\Vert u - x_t\Vert^2
-                \le 
-                - 
-                \frac{1}{2}(1 + \beta\eta_{t + 1})\Vert 
-                    u - x_{t + 1}
-                \Vert^2
-                \\
-                & \text{let } u = x_*
-                \\
-                &\quad 
-                \begin{aligned}
-                    \implies &
-                    \eta_{t + 1}(f(x_{t + 1}) - f(x_*)) 
-                    + 
-                    \frac{1}{2}\Vert x_* - x_{t + 1}\Vert^2 
-                    +  
-                    \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
-                    -
-                    \frac{1}{2}\Vert x_* - x_t\Vert^2 
-                    \\
-                    & \quad \le 
-                    -\frac{\beta\eta_{t + 1}}{2}\Vert x_* - x_{t + 1}\Vert^2
-                    \\
-                    \iff & 
-                    \eta_{t + 1}(f(x_{t + 1}) - f(x_*)) 
-                    + 
-                    \frac{1}{2}\Vert x_* - x_{t + 1}\Vert^2 
-                    -
-                    \frac{1}{2}\Vert x_* - x_t\Vert^2 
-                    \\
-                    & \quad \le 
-                    - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
-                    -\frac{\beta\eta_{t + 1}}{2}\Vert x_* - x_{t + 1}\Vert^2
-                    \le 0. 
-                \end{aligned}
-                \\
-                & \text{let } u = x_{t}
-                \\
-                &\quad  
-                \begin{aligned}
-                    \implies& 
-                    f(x_{t + 1}) - f(x_t)
-                    \le 
-                    -\frac{1}{\eta_{t+1}} \Vert x_{t + 1} - x_t\Vert^2 
-                    - \frac{\beta}{2}\Vert x_t - x_{t + 1}\Vert^2
-                    \le 0. 
-                \end{aligned}
-            \end{align*}
-            Let's define the following quantities for all $u, \beta\ge 0$: 
-            \begin{align*}
-                \Upsilon_{1, t + 1}(u) &= 
-                \eta_{t + 1}(f(x_{t + 1}) - f(u)) + \frac{1}{2}(
-                    \Vert x_{t + 1} - u\Vert^2 - 
-                    \Vert x_t - u\Vert^2
-                )
-                \\
-                & \le 
-                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
-                -\frac{\beta\eta_{t + 1}}{2}\Vert u - x_{t + 1}\Vert^2, 
-                \\
-                \Upsilon_{2, t + 1}
-                &= 
-                \eta_{t + 1}(f(x_{t + 1}) - f(x_t))
-                \\
-                &\le 
-                - \Vert x_{t + 1} - x_t\Vert^2 - 
-                \frac{\beta\eta_{t + 1}}{2}
-                \Vert x_{t + 1} - x_t\Vert^2 
-                \\
-                &= 
-                -(1 + \beta\eta_{t + 1}/2)\Vert x_{t + 1} - x_t\Vert^2 \le 0. 
-            \end{align*}
-            With $\Phi_t$ as defined in the theorem, observe the following demonstration for all $u$, $\beta \ge 0$: 
-            {\small
-            \begin{align*}
-                \Phi_{t + 1} - \Phi_{t}
-                &= 
-                \left(
-                    \sum_{i = 1}^{t + 1}\eta_i
-                \right)(f(x_{t + 1}) - f(u)) + 
-                \frac{1}{2}\Vert x_{t + 1} - u\Vert^2 
-                - 
-                \left(
-                    \sum_{i = 1}^{t}\eta_i
-                \right)(f(x_{t}) - f(u))
-                - 
-                \frac{1}{2}\Vert x_{t} - u\Vert^2
-                \\
-                &= 
-                \left(\sum_{i = 1}^{t}\eta_{i}\right)
-                (f(x_{t + 1}) - f(x_t)) 
-                + \frac{1}{2}\Vert x_{t + 1} - u\Vert^2 
-                - \frac{1}{2}\Vert x_{t} - u\Vert^2
-                +
-                \eta_{t + 1}(f(x_{t + 1}) - f(u))
-                \\
-                &= 
-                \left(\sum_{i = 1}^{t}\eta_{i}\right)\Upsilon_{2, t + 1}
-                + \Upsilon_{1, t + 1}(u)
-                \\
-                &\le 
-                -\left(\sum_{i = 1}^{t}\eta_{i}\right)
-                (1 + \beta\eta_{t + 1}/2)\Vert x_{t + 1} - x_t\Vert^2
-                + 
-                \left(
-                    - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
-                    -\frac{\beta\eta_{t + 1}}{2}\Vert u - x_{t + 1}\Vert^2
-                \right)
-                \le 0. 
-            \end{align*}
-            }
-            Therefore, $\Phi_t$ is a legitimate Lyapunov function for all $u, \beta \ge 0$. 
-        \end{proof}
-        \begin{remark}
-            The above Lyapunov is not unique, and it's not optimal for $\beta > 0$, strictly strongly convex functions.
-
-        \end{remark}
-
-        \begin{theorem}[Convergence Rate of PPM]\label{thm:ppm_convergence_rate}
-            The convergence rate of PPM applied to $f$, closed, convex proper, we have the convergence rate of the function value: 
-            $$
-            f(x_T) - f(x_*) \le O\left(\left(\sum_{i=1}^{T}\eta_t\right)^{-1}\right). 
-            $$
-            Where $x_*$ is the minimizer of $f$. 
-        \end{theorem}
-        \begin{proof}
-            With $\Delta_t = f(x_t) - f(x_*), \Upsilon_t = \sum_{i = 1}^{t}\eta_i$ so $\Phi_t = \Upsilon_t\Delta_t + \frac{1}{2}\Vert x_t - x_*\Vert^2$ by consideration $u = x_*$, invoking previous theorem and do
-            \begin{align*}
-                \Upsilon_T\Delta_T \le \Phi_T 
-                &\le 
-                \Phi_0 = \frac{1}{2}\Vert x_0 - x_*\Vert^2 
-                \\
-                \implies \Delta_T 
-                &\le 
-                \frac{1}{2\Upsilon_T} \Vert x_0 - x_*\Vert^2. 
-            \end{align*}
-        \end{proof}
-        \begin{remark}
-            With the same choice of the sequence $(\eta_t)_{t \in \NN}$, convergence of the PPM method of a strongly convex function is faster. 
-            The above proof is the same for $\beta = 0$, or $\beta > 0$, because it didn't use the property that $\eta_{t + 1}f$ is a $\eta_{t + 1}\beta$ strongly convex function. 
-        \end{remark}
-
-        \begin{theorem}[PPM Strongly Convex Lyapunov Function]\label{ppm_lyapunov_scvx}
-            With $f$ being $\beta > 0$ strogly convex, with $x_{t + 1} = \hprox_{\eta_{t + 1}f}(x_t)$, then $\Phi_t = \Vert x_{t} - x_*\Vert$ is a Lyapunov function satisfying: 
-            \begin{align*}
-                \frac{\Vert x_{t + 1} - x_*\Vert}{
-                    \Vert x_k - x_*\Vert
-                } &\le (1 + \eta_{t + 1}\beta)^{-1}. 
-            \end{align*}
-        \end{theorem}
-        \begin{proof}
-            This is a direct application that $\hprox_{\eta_{t + 1}f}$ is a contraction with constant $(1 + \beta\eta_{t +1})^{-1}$. 
-        \end{proof}
-        \begin{remark}
-            It's still a mystery on how to show $f(x_t) - f(x_*)$ is a Lyapunov function. 
-            The answer is not realized by us, nor it is in Rockafellar \cite{rockafellar_monotone_1976} or Guler's\cite{guler_convergence_1991} writings. 
-            Do observe that, by the choice of $x_*$, the contraction property of the proximal operator is strictly stronger than necessary. 
-            This inequality at the end is tighter than what we derived for gradient descent. 
-        \end{remark}
-
-\section{Applying the analysis of PPM}
-    The PPM method and the Lyaounov function derived above serve as the template for other algorithms. 
-    As an appetizer, we present an analysis of gradient descent using theorems related to the convergence of PPM
-    \par\noindent
-    In optimizations, people use a lower or an upper approximation of the objective function to approximate the PPM. 
-    The methodology includes a diverse range of approaches.
-    For example, it includes first-order optimization, such as gradient descents, and second-order algorithms, such as Newton's method. 
-    Its scope broadens to primal-dual optimization algorithms with creativities in the Lyapunov functions or theories in monotone operators. 
-    \par\noindent
-    To demonstrate, assume that $f$ is a lsc convex function such that it can be approximated by a lower bounding function $l_f(x|\bar x)$ at $\bar x$ such that it satisfies for all $x$: 
-    \begin{align*}
-        l_f(x| \bar x) 
-        \le f(x) \le l_f(x|\bar x) + \frac{L}{2}\Vert x - \bar x\Vert^2. 
-    \end{align*}
-    The above characterization is generic enough to include the case where $l_f(x|\bar x)$, the under-approximating function is nonsmooth. 
-    We assume that $l_f(x|\bar x)$ is convex for all $x$, at all $\bar x$, so the previous theorems apply. 
-    \par\noindent
-    The approximated proximal point method applies PPM to the function $l_f(x|x_t)$ for each iteration, i.e.: $x_{t +1} = \hprox_{\eta_{t + 1}l_f(\cdot | x_t)}(x_t)$. 
-    \subsection{Generic gradient descent}
-        We will consider deriving gradient descent via the PPM approach as a warm-up. 
-        Please pay attention to the remarks. They reveal parts of the proof that could inspire the idea of a non-monotone line search method in practical settings. 
-        \begin{theorem}[Generic Approximated PPM]\label{thm:lower_approx_ppm_convergence}
-            With $f$ convex having minimizer: $x_*$; $l_f(\cdot; x_t)$ convex, lsc and proper, define $\phi_t(x) = \eta_{t + 1}l_f(x; x_t)$. 
-            Assume the following estimates hold: 
-            $$
-            \phi_t(x) \le \eta_{t + 1}f(x) \le \phi_t(x) 
-            + 
-            \frac{L\eta_{t + 1}}{2}\Vert x - x_t\Vert^2 \quad \forall x \in \RR^n. 
-            $$ 
-            Fix any $x_0$, let the iterates $x_t$ defined for $t\in \NN$ satisfies
-            \begin{align*}
-                x_{t +1} = \argmin_{x} \left\lbrace
-                    l_f(x; x_t) + \frac{1}{2\eta_{t + 1}}\Vert x - x_t\Vert^2
-                \right\rbrace, 
-            \end{align*}
-            then it has 
-            \begin{align*}
-                \eta_{t + 1}(f(x_{t + 1}) - f(x_*)) + \frac{1}{2}\Vert x_* - x_{t + 1}\Vert^2
-                - \frac{1}{2}\Vert x_* - x_t\Vert^2
-                & \le 
-                \left(
-                    \frac{L \eta_{n + 1}}{2} - \frac{1}{2}
-                \right)\Vert x_{t + 1} - x_t\Vert^2.
-            \end{align*}
-            Additionally if $\exists \epsilon > 0: \eta_{t} \in (\epsilon, 2L^{-1} - \epsilon)$, for all $t \in \NN$, the algorithm has sublinear convergence rates of
-            \begin{align*}
-                f(x_T) - f(x_*)
-                &\le 
-                \frac{L - \epsilon^{-1}}{TL\epsilon} (f(x_0) - f(x_T)) 
-                \\
-                &\le 
-                \frac{L - \epsilon^{-1}}{TL\epsilon} (f(x_0) - f(x_*)) 
-            \end{align*}
-        \end{theorem}
-        \begin{proof}
-            By $\phi_t$ convex, apply \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} with $f = \phi_t$, $x = x_t$, $x_{t + 1} = p$, yielding $\forall y$
-            {\footnotesize
-                \begin{align*}
-                    \phi_t(x_{t + 1}) + \frac{1}{2}\Vert x_t - x_{t + 1}\Vert^2 
-                    - 
-                    \phi_t(y) - \frac{1}{2}\Vert x_t - y\Vert^2
-                    &\le 
-                    - \frac{1}{2}\Vert y - x_{t + 1}\Vert^2
-                    \\
-                    \phi_t(x_{t + 1}) - \phi_t(y)
-                    + \frac{1}{2}(
-                        \Vert y - x_{t + 1}\Vert^2 - \Vert x_t - y\Vert^2 
-                    ) &\le 
-                    - \frac{1}{2} \Vert x_t - x_{t + 1}\Vert^2
-                    \\
-                    \left(
-                        \phi_t(x_{t + 1}) + \frac{L\eta_{t + 1}}{2}\Vert x_{t + 1} - x_t\Vert
-                    \right)
-                    - \phi_t(y)
-                    + \frac{1}{2}(
-                        \Vert y - x_{t + 1}\Vert^2 - \Vert x_t - y\Vert^2 
-                    ) &\le 
-                    \left(
-                        \frac{L\eta_{t + 1}}{2}- \frac{1}{2}
-                    \right) \Vert x_t - x_{t + 1}\Vert^2
-                    \\
-                    \implies 
-                    \eta_{t + 1}f(x_{t + 1}) - \eta_{t + 1}f(y) 
-                    + \frac{1}{2}(
-                        \Vert y - x_{t + 1}\Vert^2 - \Vert x_t - y\Vert^2 
-                    ) 
-                    &\le 
-                    \left(
-                        \frac{L\eta_{t + 1}}{2}- \frac{1}{2}
-                    \right) \Vert x_t - x_{t + 1}\Vert^2. 
-                \end{align*}
-            }
-            Setting $y = x_t$ yields
-            \begin{align*}
-                \eta_{t + 1}(f(x_{t + 1}) - f(x_t)) + 
-                \frac{1}{2}
-                    \Vert x_t - x_{t + 1}\Vert^2
-                &\le 
-                \left(
-                        \frac{L\eta_{t + 1}}{2}- \frac{1}{2}
-                \right) \Vert x_t - x_{t + 1}\Vert^2
-                \\
-                \iff 
-                \eta_{t + 1}(f(x_{t + 1}) - f(x_t))
-                &\le 
-                \left(
-                        \frac{L\eta_{t + 1}}{2} - 1
-                \right) 
-                \Vert x_t - x_{t + 1}\Vert^2. 
-            \end{align*}
-            In a similar manner to the derivation of the Lyapunov function for PPM, we make for all $y$: 
-            \begin{align*}
-                \Upsilon_{1, t + 1}(y) &= 
-                \eta_{t + 1}(f(x_{t + 1}) - f(y)) + \frac{1}{2}(
-                    \Vert x_{t + 1} - y\Vert^2 - 
-                    \Vert x_t - y\Vert^2
-                )
-                \\
-                & \le 
-                \left(
-                    \frac{L\eta_{t + 1}}{2} - \frac{1}{2}
-                \right) \Vert x_t - x_{t + 1}\Vert^2, 
-                \\
-                \Upsilon_{2, t + 1}
-                &= 
-                \eta_{t + 1}(f(x_{t + 1}) - f(x_t))
-                \\
-                &\le 
-                \left(
-                    \frac{L\eta_{t + 1}}{2} - 1
-                \right) 
-                \Vert x_t - x_{t + 1}\Vert^2. 
-            \end{align*}
-            Now, consider defining $\Phi_t$ for all $y$: 
-            $$
-                \Phi_t = \left(
-                    \sum_{i = 1}^{t} \eta_{i}
-                \right)
-                (f(x_t) - f(y)) + \frac{1}{2}\Vert y - x_t\Vert^2, 
-            $$
-            it is the proposed Lyapunov function for PPM; we define the base case $\Phi_0 = \frac{1}{2}\Vert y - x_0\Vert^2$. 
-            Consider the difference $\forall y$: 
-            \begin{align*}
-                \Phi_{t + 1} - \Phi_t
-                &= 
-                \left(\sum_{i = 1}^{t}\eta_{i}\right)\Upsilon_{2, t + 1}
-                + \Upsilon_{1, t + 1}(y)
-                \\
-                &\le 
-                \left(\sum_{i = 1}^{t}\eta_{i}\right) 
-                \left(
-                    \frac{L\eta_{t + 1}}{2} - 1
-                \right) 
-                \Vert x_t - x_{t + 1}\Vert^2 + 
-                \left(
-                    \frac{L\eta_{t + 1}}{2}- \frac{1}{2}
-                \right) \Vert x_t - x_{t + 1}\Vert^2. 
-            \end{align*}
-            Observe that if $\eta_i \le L^{-1}$, then $\Phi_{t + 1} - \Phi_t \le 0$, hence the convergence rate of $\mathcal O\left((\sum_{i = 1}^{t}\eta_i)^{-1}\right)$ of PPM for $\Phi_t$ is applicable.
-            \par\noindent
-            Surprisingly, if $\eta_i \in (0, 2L^{-1})$, $\Phi_{t}$ still converges under mild conditions. 
-            For simplicity we set $\sigma_t := \sum_{i = 1}^{t}\eta_i$. 
-            It starts with considerations that $(L\eta_{t + 1}/2 - 1) < 0$, so that 
-            \begin{align*}
-                f(x_{t + 1}) - f(x_t) &\le 
-                \left(\frac{L\eta_{t + 1}}{2} - 1\right)\Vert x_{t + 1} - x_t\Vert^2
-                \\
-                f(x_T) - f(x_0)
-                &\le 
-                \underbrace{
-                \left(
-                    \frac{L\sigma_T}{2} - T
-                \right)
-                }_{< 0}
-                \sum_{t = 0}^{T - 1}\Vert x_{t + 1} - x_t\Vert^2
-                \\
-                \implies 
-                \sum_{t = 0}^{T -1}\Vert x_t - x_{t + 1}\Vert^2
-                &\le 
-                \left(
-                    \frac{L}{2}\sigma_T  - T
-                \right)^{-1} 
-                (f(x_T) - f(x_0))
-            \end{align*}
-            Continue on the RHS of $\Phi_{t + 1} - \Phi_t$ so 
-            \begin{align*}
-                \sum_{t = 0}^{T - 1}\Phi_{t + 1} - \Phi_t 
-                &\le 
-                \left(
-                    \frac{L}{2}\sigma_T - \frac{T}{2}
-                \right)\sum_{t = 0}^{T - 1}\Vert x_{t + 1} - x_t\Vert^2
-                \\
-                \Phi_T - \Phi_0 &\le 
-                \left(
-                    \frac{\frac{L}{2}\sigma_T - \frac{T}{2}}{
-                        \frac{L}{2}\sigma_T - T
-                    }
-                \right)
-                (f(x_T) - f(x_0))
-                \\
-                &= 
-                \left(
-                    \frac{L\sigma_T - T}{L\sigma_T - 2T}
-                \right)
-                (f(x_T) - f(x_0)), 
-            \end{align*}
-            implies
-            \begin{align*}
-                \sigma_T (f(x_T) - f(y)) + \frac{1}{2}\Vert y - x_t\Vert^2
-                - \frac{1}{2}\Vert y - x_0 \Vert^2 
-                &\le 
-                \left(
-                    \frac{L\sigma_T - T}{L\sigma_T - 2T}
-                \right)
-                (f(x_T) - f(x_0))
-                \\
-                \iff
-                f(x_T) - f(y) + 
-                \frac{1}{2\sigma_T}(\Vert y - x_t\Vert^2 - \Vert y - x_0\Vert^2)
-                &\le 
-                \left(
-                    \frac{L- T\sigma_T^{-1}}{2T - L\sigma_T}
-                \right)
-                (f(x_0) - f(x_T)), 
-            \end{align*}
-            therefore, we obtain the bound: 
-            \begin{align*}
-                f(x_T) - f(y) &\le 
-                \left(
-                    \frac{L- T\sigma_T^{-1}}{2T - L\sigma_T}
-                \right)
-                (f(x_0) - f(x_T))
-                - 
-                \frac{1}{2\sigma_T}(\Vert y - x_t\Vert^2 - \Vert y - x_0\Vert^2)
-            \end{align*}
-            In the case where $\sup_{i\in \NN} \eta_i \le 2L^{-1} - \epsilon$, and $\inf_{i\in \NN}\eta_i \ge \epsilon$ with $\epsilon > 0$. 
-            Then we have 
-            \begin{align*}
-                \frac{L -T\sigma_T^{-1}}{2T - L\sigma_T}
-                &\le 
-                \frac{L - \epsilon^{-1}}{2T - LT(2L^{-1} - \epsilon)}
-                \\
-                &= 
-                \frac{L - \epsilon^{-1}}{2T - T(2 - L\epsilon)}
-                \\
-                &= 
-                \frac{L - \epsilon^{-1}}{TL\epsilon}. 
-            \end{align*}
-            With $y = x_*$, we get the claimed convergence rate because $f(x_t)$ is strictly monotone decreasing. 
-        \end{proof}
-        \begin{remark}
-            Observe that inequality 
-            $$
-                \phi_t(x) \le \eta_{t + 1}f(x) \le \phi_t(x) 
-                + 
-                \frac{L\eta_{t + 1}}{2}\Vert x - x_t\Vert^2 \quad \forall x \in \RR^n, 
-            $$
-            was invoked with $x = x_{t + 1}$ for the PPM descent inequality in the above proof, meaning that if  $\forall (x_t)_{t \in \NN}$ generated by the algorithm, $\exists (L_t)_{t \in \NN}$ such that
-            $$
-                \phi_t(x) \le \eta_{t + 1}f(x) \le \phi_t(x) 
-                + 
-                \frac{L_t\eta_{t + 1}}{2}\Vert x - x_t\Vert^2,
-            $$
-            where the algorithm generates the sequence. 
-            By smartly choosing the function $\phi_{t + 1}$ at each iteration, we can increase the stepsize while retaining a similar convergence proof. 
-            In a practical setting, when $L_t = L$, and $\phi_{t}(x) = \eta_{t + 1}f$, this is called a line search.
-            \par\noindent
-            The convergence rate is loose, and when $f$ exhibits additional favourable properties, such as being strongly convex, the convergence rate can be faster. 
-            Furthermore, if the choice of $y$ remains arbitrary, then the theorem is applicable for function without minimizers. 
-        \end{remark}
-
-    \subsection{Examples}
-        \begin{example}[Convergence of the proximal gradient method]
-            This section \\ illustrates algorithms that satisfy the above proof's lower and upper bound estimates. 
-            Consider $f = g + h$ with $h$ nonsmooth convex, and $g$ being $L$-Lipschitz smooth convex and differentiable. 
-            Define $D_g(x, y) = g(x) - g(y) - \langle \nabla f(x), y - x\rangle$, $l_g(x; y) = g(y) + \langle \nabla g(y), y - x\rangle$, which is the Bregman divergence of the function $g$. 
-            Consider for all $x$: 
-            \begin{align*}
-                0 & \le 
-                D_g (x, y) \le  \frac{L}{2} \Vert x - y\Vert^2 
-                \\
-                l_g (x; y) &\le 
-                g(x) 
-                \le l_g(x; y) + \frac{L}{2} \Vert x - y\Vert^2 
-                \\
-                h(x) + l_g(x; y) &\le f(x) = g(x) + h(x)
-                \le 
-                l_g(x; y) + h(x) + \frac{L}{2}\Vert x - y\Vert^2. 
-            \end{align*}
-            Define $\phi_{t + 1} (x) = \eta_{t + 1}(h(x) + l_g(x; x_t))$, then results from previous theorems apply.    
-        \end{example}
-        \begin{remark}
-            The envelope interpretation restricts the use of the theorem since it requires that the proximal operator be a resolvent of a gradient. 
-            Extending the usage of the PPM descent inequality to other contexts requires operator theories and creativities. 
-        \end{remark}
-
-        \begin{example}[The fundamental proximal gradient lemma]
-            The fundamental proximal gradient lemma was used heavily in the literature to derive convergence results in the convex case. 
-            The "fundamental proximal gradient lemma" originates from Beck's writings \cite[theorem 10.16]{beck_first-order_nodate}. 
-            We demonstrate in this example that it's a consequence of \hyperref[thm:ppm_breg_descent_ineq]{theorem \ref*{thm:ppm_breg_descent_ineq}}. 
-            \par
-            With $f = g + h$, $h$ convex, lsc, $g$ be $L$-Lipschitz smooth, then for all $y\in \RR^n$, $x\in \RR^n$, $y^+ := \hprox_{L^{-1}h}(y - L^{-1}\nabla (y))$ satisfies: 
-            \begin{align*}
-                f(x) - f(y^+) \ge \frac{L}{2}\Vert x - y^+\Vert^2 - \frac{L}{2}\Vert x - y\Vert^2 + D_g(x, y).
-            \end{align*}
-            A similar analysis as \hyperref[thm:lower_approx_ppm_convergence]{ theorem \ref*{thm:lower_approx_ppm_convergence}} with \hyperref[thm:ppm_breg_descent_ineq]{theorem \ref*{thm:ppm_breg_descent_ineq}} obtains the same inquality.
-            With $\phi(y) = \eta(h(y) + g(x) + \langle \nabla g(x), y - x\rangle)$ as an lower bounding function of $f$. 
-            Choose any $x$, let $x^+ = \hprox_\phi(x)$, then for all $u$:
-            {\small
-            \begin{align*}
-                & \phi(u) + \frac{1}{2}\Vert u - x\Vert^2 - \phi(x^+) - \frac{1}{2}\Vert x^+ - x\Vert^2 
-                \ge \frac{1}{2}\Vert x^+ - u\Vert^2
-                \\
-                \implies &
-                \eta\underbrace{
-                    \left(
-                        h(u) + g(x) + \langle \nabla g(x), u - x\rangle 
-                    \right)
-                }_{= \phi(u)} 
-                - \eta \underbrace{f(x^+)}_{\le \phi(x^+)} - \frac{1}{2}\Vert x - x^+\Vert^2 
-                + \frac{1}{2} \Vert u - x\Vert^2 
-                \ge 
-                \frac{1}{2}\Vert x^+ - u\Vert^2 
-                \\
-                \iff & 
-                f(u) + \left(
-                    g(x) - g(u) + \langle \nabla g(x), u -x\rangle 
-                \right)
-                - f(x^+) - \frac{1}{2\eta}\Vert x - x^+\Vert^2
-                + 
-                \frac{1}{2}\Vert u - x\Vert^2 
-                \ge 
-                \frac{1}{2\eta}\Vert x^+ - u\Vert^2 
-                \\
-                \iff 
-                & f(u) - f(x^+) - D_g(u, x)
-                + \frac{1}{2\eta} \Vert u - x\Vert^2 - \frac{1}{2\eta}\Vert x^+ - x\Vert^2
-                \ge 
-                \frac{1}{2\eta} \Vert x^+ - u\Vert^2. 
-            \end{align*}
-            }
-            \par\noindent
-            Removing the negative term $-1/2\eta \Vert x - x^+\Vert^2$ makes LHS larger, establishing the fundamental proximal gradient lemma. 
-        \end{example}
-        \begin{remark}
-            Linking the PPM descent inequality to the Bregman divergence of the smooth part of the function on parameters $u, x$ is a clever move. 
-        \end{remark}
-
-\section{Accelerated gradient descent and PPM}
-    Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
-    Ahn explored the interpretation of Nesterov acceleration via PPM. 
-    They proposed the idea of ``similar triangle" for unifying all varieties of Nesterov accelerated gradient. 
-    They used PPM to derive several variations of the Nesterov accelerated gradient algorithms. 
-    Finally, they refurnished \hyperref[thm:lower_approx_ppm_convergence]{theorem \ref*{thm:lower_approx_ppm_convergence}} for the proof of convergence rate for the accelerated gradient.
-    Their analysis results in relatively simple arguments that exhibits powerful extensions to several variants of the Nesterov accelerated gradient.
-
-    \par\noindent
-    Interestingly, the Nesterov accelerated gradient applies to PPM too; Guler \cite{guler_new_1992} did it two decades ago. 
-    He uses the idea of a Nesterov acceleration sequence faithfully. 
-    One recent development of the accelerated PPM is an algorithmic framework named: ``Universal Catalyst acceleration", proposed by Lin et al \cite{lin_universal_2015}. 
-    It is an application of Guler's work in the context of variance-reduction stochastic gradient algorithms for machine learning.
-
-    \par\noindent
-    \textbf{We state our contributions}. 
-    In \hyperref[sec:AG_varieties]{section \ref*{sec:AG_varieties}} 
-    We stated different forms of accelerated gradient that appeared in the literatures and the equivalences between their forms. 
-    They are abstract because the choice of stepsize parameters in the algorithms are unspecified. 
-    Abstract forms related to the proximal gradient method were our own inventions inspired by discussions in the literatures, which includes 
-    \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}, and 
-    \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}. 
-    In \hyperref[sec:AG_useful_information]{section \ref*{sec:AG_useful_information}}
-    we prove and interpret some of the unproved claims made by Ahn, Sra \cite{ahn_understanding_2022} as good exercises and for the peace of the mind. 
-    In
-    \hyperref[sec:generic_ag_ppm_lyapunov_analysis]{section \ref*{sec:generic_ag_ppm_lyapunov_analysis}},
-    we state two important theorems for the derivation of convergences rate for various type of algorithm using an upper bound of a Lyapunov function. 
-    This part is inspired by works from Ahn, Sra \cite{ahn_understanding_2022}, but with the gradient mapping and proximal gradient added into the picture, making it distinct from all algorithms discussed in Ahn and Sra's paper.
-    \hyperref[sec:scenario_i]{Section \ref*{sec:scenario_i}} and 
-    \hyperref[sec:scenario_ii]{\ref*{sec:scenario_ii}} derive the convergence rate and determine the parameters for the step sizes needed to achieve an optimal convergence rate. 
-    In each section, we recover a specific variant of the Accelerated gradient and identify their appearances in the literature.
-
-    \subsection{Preliminaries}
     We introduce some additional lemma that are crucial to the derivations of non-smooth accelerated gradient method. 
@@
         Observe that the linearization $h(x^+) + \langle \mathcal G_L(x), z - x\rangle$ is anchored at $x^+$, instead of $x$. 
-            Geometrically, it's tilted and it "prefers" the sharp corners of a convex function, if, $x$ is close to a sharp corner. 
+        Geometrically, it's tilted and it ``prefers" the sharp corners of a convex function, if, $x$ is close to a sharp corner. 
     \end{remark}
 
-    \subsection{Varieties of Nesterov accelerated gradient}\label{sec:AG_varieties}
-        Here, the acrynonym: ``AG" stands for accelerated gradient. 
-        \subsubsection{AG Abstract Forms}
-            In this section, we list different varieties of the Nesterov accelerated method. 
-            \begin{definition}[Nestrov 2.2.7]\label{def:Nes2.2.7}
-                Let $f$ be a $L$ Lipschitz smooth and $\mu\ge 0$ strongly convex function. 
-                Choose $x_0$, $\gamma_0 > 0$, set $v_0 = x_0$, for iteration $k\ge 0$, it
-                \begin{enumerate}
-                    \item[1.] computes $\alpha_k \in (0, 1)$ by solving $L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \alpha_k \mu$; 
-                    \item[2.] sets $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$;
-                    \item[3.] chooses $y_k = (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \gamma_{k + 1}x_k)$. Compute $f(y_k)$ and $\nabla f(y_k)$; 
-                    \item[4.] finds $x_{k + 1}$ such that $f(x_{k + 1}) \le f(y_k) - (2L)^{-1} \Vert \nabla f(y_k)\Vert^2$; 
-                    \item[5.] sets $v_{k + 1} = \gamma_{k+1}^{-1}((1 - \alpha_k)\gamma_kv_k + \alpha_k \mu y_k - \alpha_k \nabla f(y_k))$. 
-                \end{enumerate}
-            \end{definition}
-            \begin{remark}
-                This is in Nesterov's book \cite[(2.2.7)]{nesterov_lectures_2018}. 
-                For more context, the sequence $\alpha_k \in (0, 1)$ such that $\sum_{k = 1}^{\infty}\alpha_k = \infty$, and recursively we have $\lambda_{k + 1} = (1 - \alpha_k)\lambda_k$. 
-                the sequence $\lambda_k$ is called an Nesterov estimating sequence. 
-                It is the most generic algorithm in his book about accelerated gradient method. 
-                The genericity of the algorithm is provided by item 4., which is the a special case of the smooth descent lemma.
-
-            \end{remark}
-
-            \begin{definition}[Ahn Sra 6.24]\label{def:agg_ppm}
-                With $f$ $\mu \ge 0$ strongly convex and $L$-Lipschitz smooth, the generic PPM form is formulated for strictly positive stepsizes $\tilde \eta_i,\eta_i$: 
-                \begin{align*}
-                    x_{t + 1} &= \argmin_{x} \left\lbrace
-                        l_f(x; y_t) 
-                        + 
-                        \frac{\mu}{2}\Vert x - y_t\Vert^2
-                        + 
-                        \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
-                    \right\rbrace, 
-                    \\
-                    y_{t + 1} &= \argmin_{x} 
-                    \left\lbrace
-                        l_f(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
-                        \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
-                    \right\rbrace. 
-                \end{align*}
-            \end{definition}
-            \begin{remark}
-                This algorithm is the same as algorithm (6.24) described by Ahn and Sra \cite{ahn_understanding_2022}. 
-                Observe that by setting $\mu = 0, \tilde \eta_{t + 1} = \eta_{t + 1}$ this recovers algorithm (4.8) described in Ahn and Sra \cite{ahn_understanding_2022}. 
-                Finally, Ahn, Sra 6.24 has the same form as Nesterov 2.2.7. 
-                See 
-                \hyperref[prop:Nes2.2.7_via_ahn_sra_6.24]{proposition \ref*{prop:Nes2.2.7_via_ahn_sra_6.24}} for a demonstration. 
-            \end{remark}
-
+\section{The PPM interpreation of accelerated gradient}\label{sec:ppm_interp_of_ag}
+    In this section, we state the PPM formulation of the accelerated proximal gradient method. 
+    The formulation is abstract because the parameters are not yet determined. 
     \begin{definition}[AG Proximal Gradient PPM Generic Form]
@@
         Let $h=f + g$ be the sum of convex function $g$ and convex differentiable $f$ with $L$-Lipschitz gradient. 
-                Define the proximal gradient and gradient mapping operator operator: 
-                $$
-                \begin{aligned}
-                    \mathcal T_L^{g, f}(x) &:=  
-                    \hprox_{L^{-1}g}\left(x - L^{-1}\nabla f(x)\right)
-                    \\
-                    &= 
-                    \argmin_{u}
-                    \left\lbrace
-                        g(u) + f(x) + \langle \nabla f(x), u - x\rangle
-                        + 
-                        \frac{L}{2}\Vert u - x\Vert^2
-                    \right\rbrace,
-                    \\
-                    \mathcal G_L^{g, f}(x) &= 
-                    L\left(x - \mathcal T_L^{g, f}(x)\right). 
-                \end{aligned}
-                $$
-                Omitting the superscript $f, g$ on $\mathcal T, \mathcal G$ for simplicity since it's clear in the context. 
-                Define the linear lower bounding function for $f$ at $y$, for all $x$: 
+        With $\mathcal T_L, \mathcal G_L$ being the proximal gradient, and the gradient mapping operator. 
+        Define the linear lower bounding function for $h$ at $y$, for all $x$: 
         $$
@@
     \end{definition}
-            \begin{observation}
-                With $g \equiv 0$, the above definition reduces to 
-                \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}
-                where $\mu = 0$. 
-            \end{observation}
 
     \begin{definition}[AG Proximal Gradient Generic Form]
-            \label{def:ag_prox_grad_tri_pt}
+    \label{def:ag_prox_grad_generic}
         With $h = f + g$, where $g$ is convex, $f$ is convex and $L$-Lipschitz smooth. 
-                Define proximal gradient and gradient mapping operator 
-                $$
-                \begin{aligned}
-                    \mathcal T_L(x) 
-                    &:= \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)), 
-                    \\
-                    x^+ &= \mathcal T_L(x), 
-                    \\
-                    \mathcal G_L(x) 
-                    &:= L(x -  x^+). 
-                \end{aligned}
-                $$
-                Then the algorithm updates $(y_t, x_{t + 1}, z_{t + 1})$ with expression: 
+        Define $x^+ = \mathcal T_L(x)$, so that $\mathcal G_L(x) = L(x -  x^+)$, we define the algorithm updates $(y_t, x_{t + 1}, z_{t + 1})$ with expression: 
         $$
@@
 
-            \begin{definition}[Generic Form]\label{def:agg_tri}
-                With $f$ be $L$-Lipschitz \\ 
-                smooth and convex, choose any $y_0 = x_0=z_0$ and a non-negative sequence $\eta_t, \tilde\eta_t$, the algorithm admits form: 
-                \begin{align*}
-                    x_{t + 1} &= x_t - \tilde \eta_{t + 1} \nabla f(y_t) 
-                    \\
-                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t) 
-                    \\
-                    y_{t + 1} &= 
-                    (1 + L\eta_{t + 1})^{-1}
-                    (
-                    x_{t + 1} + L\eta_{t + 1}z_{t + 1}
-                    ). 
-                \end{align*}
-            \end{definition}
-            \begin{remark}
-                The parameter $\eta_t, \tilde\eta_{t + 1}$ are exactly the same as Ahn, Sra \cite[(6.24)]{ahn_understanding_2022}, but with the choice of $\mu = 0$. 
-                This form is not explictly stated by Ahn and Sra but it's trivial to realize its presence regardless. 
-                They are the same parameters for both algorithms and they are equivalent. 
-                For a demonstration, see 
-                \hyperref[prop:tri_form_via_ppm]{proposition \ref*{prop:tri_form_via_ppm}}. 
-            \end{remark}
-
-            \begin{definition}[Strongly Convex Generic Form]
-                \quad \\
-                With $f$ being $L$-Lipschitz smooth and $\mu > 0$ strongly convex then the Strongly convex generic form has updates of for iterates
-                \begin{align*}
-                    x_{t + 1} &= (1 + \mu\tilde \eta_{t + 1})^{-1}(x_t + \mu\tilde\eta_{t + 1}y_t^+), 
-                    \\
-                    z_{t + 1} &= y_t - L^{-1}\nabla f(y_t), 
-                    \\
-                    y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}(x_{t + 1} + L\eta_{t + 1}z_{t +1}). 
-                \end{align*}
-            \end{definition}
-            \begin{remark}
-                This algorithm is equivalent to 
-                \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}. 
-                See \ref*{prop:tri_scvx_from_ahn_sra_6.24} for a demonstration. 
-            \end{remark}
-
-        \subsubsection{AG Concrete Examples}
-            In this section we state variants of the Nesterov accelerated gradient method found in the literatures which are not generic.
-
-            \begin{definition}[AG Ryu 12.1]
-            \label{def:ag_ryu_12.1}
-                State in chapter 12 in Ryu's writing \cite{ryu_large-scale_2022} is the following variant of accelerated gradient algorithm: 
-                \begin{align*}
-                    z_{t + 1} &= y_k + L^{-1}\nabla f(y_t), 
-                    \\
-                    y_{t + 1} &= z_{t + 1} + \frac{t - 1}{t + 2}\left(
-                        z_{k + 1} - z_k
-                    \right). 
-                \end{align*}
-                An equivalent form of the above is also provided by Ryu: 
-                \begin{align*}
-                    z_{t + 1} &= y_t + L^{-1}\nabla f(y_t), 
-                    \\
-                    x_{t + 1} &= x_t + (t + 1)(2L)^{-1}\nabla f(y_t), 
-                    \\
-                    y_{t + 1} &= \left(
-                        1 - \frac{2}{t + 2} 
-                    \right)z_{t + 1} + 
-                    \left(
-                        \frac{2}{t + 2}
-                    \right)x_{t + 1}. 
-                \end{align*}
-            \end{definition}
-            \begin{observation}
-                The base case requires cares since it's not unique, there are more representations  depending on how the base case is define, 
-                Observe that the second equivalent form is an example of \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
-                \par\noindent
-                It is stated in Ryu's writing that the base case is $x_0 = y_0 = z_0$, 
-                we think this is not the only options. 
-                We remind the reader that there is not an obvious choice of $t\in \mathbb Z$ such that $x_t = y_t = z_t$ where the above algorithm remains consistent for all $t \ge -1$. 
-                The choice of base case presented in Ryu's writing is a choice and not a necessity. 
-                We state that one of the base case scenario that only requires knowing $y_1$.
-
-                \par\noindent 
-                We need to observe the case where $t = 0$ to understand the base case of the algorithm. 
-                At each iteration $t$, Given $(x_t, y_t)$, the above formula maps to $(x_{t + 1}, y_{t + 1}, z_{t + 1})$. 
-                When $t= 0$, it has $y_1 = x_1$. 
-                Therefore, knowing only either $y_1$, or $x_1$ can initiate the algorithm. 
-                This is an alternative scenario of the base case. 
-                If, we wish to write $y_0 = x_0$ at $t = 0$ for the base case instead, then it creates the following algorithm 
-                \begin{align*}
-                    y_{t} &= \left(
-                    1 - \frac{2}{t + 2} 
-                    \right)z_{t} + 
-                    \left(
-                        \frac{2}{t + 2}
-                    \right)x_{t}, 
-                    \\
-                    z_{t + 1} &= y_t + L^{-1}\nabla f(y_t), 
-                    \\
-                    x_{t + 1} &= x_t + (t + 1)(2L)^{-1}\nabla f(y_t). 
-                \end{align*}
-                It has a different representations due to a specific choice of the base case. 
-                \par\noindent
-                Finally, by the observation that given $(z_t, y_t)$ for any $t\ge -1$, we can solve for $x_t$ \newline via $y_t = (1 - 2/(1 + t))z_t + 1/(t + 1)x_t$, obtaining $(x_t, y_t, z_t)$, hence the algorithm can be reduced to a representations with only $(z_t, y_t)$ and an updates using only $(z_t, y_t)$ to $(z_{t + 1}, y_{t + 1})$.
-                That is the momentum form presented above. 
-            \end{observation}
-            \begin{remark}
-                We advise the reader to read the Biliography notes by Ryu \cite[chapter 12]{ryu_large-scale_2022} of his book. 
-                It goes over the full context and history for this particular variant of gradient acceleration method. 
-                At the time of composing this notes, the writer is still reading on the topic of accelerated gradient.     
-            \end{remark}
-
-            \begin{definition}[Proximal Gradient Tri-Points Form E]
-            \label{def:ag_tri_pt_form_E}
-                Form E is a special case of 
-                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
-                with the condition that $\tilde \eta_t = \eta_t$ for all $t \in \mathbb N$. 
-                As a consequence, the algorithm has the following updates for iterates $(y_t, x_{t + 1}, z_{t + 1})$: 
-                \begin{align*}
-                    y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
-                    \\
-                    x_{t + 1} &= x_t - \eta_t \mathcal G_L(y_t)
-                    \\
-                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t).
-                \end{align*}
-            \end{definition}
-
-            \begin{definition}[Similar Triangle Form I]
-            \label{def:ag_form_similar_tria_I}
-                It updates iterates $(y_t, x_{t + 1}, z_{t + 1})$ using 
-                \begin{align*}
-                    z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t) 
-                    \\
-                    x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
-                    \\
-                    y_{t + 1} &= 
-                    (1 + L\eta_{t + 1})^{-1}
-                    (x_{t + 1} + L\eta_{t + 1}z_{t + 1}). 
-                \end{align*}
-            \end{definition}
-            \begin{observation}
-                There are a lot of observations about this form to unpack. 
-                Let's list the following observations
-                \begin{enumerate}
-                    \item Observe that $y_t = (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)$ is a convex combination between $x_t, z_t$.
-Hence $z_t, y_t, x_t$ are three collinear points.
-Additionally, we have $y_t - x_t = L\eta_t (z_t - y_t)$, hence $\Vert y_t - x_t\Vert/\Vert z_t - y_t\Vert = L\eta_t$.
-                    \item By the algorithm, we have $z_{t + 1} - y_t = - L^{-1} \mathcal G_L(y_t)$, and $x_{t + 1} - x_t = - \tilde \eta_{t + 1} \mathcal G_L(y_t)$, hence vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$.
-                    \item Finally, with update $x_{t +1} - z_{t + 1} = L\eta_t (z_{t +1} - z_t)$, we have three colinear points $(z_t, z_{t + 1}, x_t)$ with $\Vert z_{t + 1} - z_t\Vert/\Vert z_{t +1 } - z_t\Vert = L\eta_t$.
-                \end{enumerate}
-                From the above results, we can conclude that triangle $(y_t, z_t, z_{t + 1})$ is similar to $(x_t, z_t, x_{t + 1})$ because they share colinear points $z_t, y_t, x_t$ and $z_t, z_{t + 1}, x_{t + 1}$, and their sides $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$.
-            \end{observation}
-            \begin{remark}
-                For more information about the specific choice of $\eta_t$ allows for an optimal convergence rates, see 
-                \hyperref[sec:scenario_ii]{section \ref*{sec:scenario_ii}} for more information. 
-            \end{remark}
-
-            \begin{definition}[Similar Triangle Form II]
-            \label{def:ag_form_similar_tria_II}
-
-            \end{definition}
-
-        \subsubsection{Useful Observations about these Generic forms}
-        \label{sec:AG_useful_information}
-
-            In this section we list some incredibaly useful information about these forms of the Nestrov type accelerated gradient algorithm. 
-            \hyperref[prop:tri_form_via_ppm]{Proposition \ref*{prop:tri_form_via_ppm}}, 
-            \hyperref[prop:tri_scvx_from_ahn_sra_6.24]{proposition \ref*{prop:tri_scvx_from_ahn_sra_6.24}}, 
-            \hyperref[prop:Nes2.2.7_via_ahn_sra_6.24]{proposition \ref*{prop:Nes2.2.7_via_ahn_sra_6.24}}
-            are results assumed as true in Ahn, Sra. 
-            They are implicitly left as necessary exercises for the readers. 
-            Here, we fill out the blanks with our own interpretations. 
-            \hyperref[prop:derive_ag_prox_grad_tript]{Proposition \ref*{prop:derive_ag_prox_grad_tript}} 
-            is our contribution where we intorduce non-smooth ness to the objective function while still retaining the PPM interpretation of accelerated gradient.
-
-            \begin{proposition}[Tri-points generic form via Ahn Sra 6.24]
-                \label{prop:tri_form_via_ppm}
-                with $f$ being \\
-                $L$-Lipschitz smooth, 
-                let $l_f(x, \bar x) = f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle$, we can show that the AG generic triangular form is a consequence of th AG generic PPM form. 
-            \end{proposition}
-            \begin{proof}
-                Solving the optimality on the first PPM yields: 
-                \begin{align*}
-                    \mathbf 0 &= \nabla f(y_t) + 
-                    \frac{1}{\tilde \eta_{t + 1}} (x - x_t)
-                    \\
-                    x &= x_t - \tilde \eta_{t + 1} \nabla f(y_t).
-                \end{align*}
-                Therefore, $x_{t + 1} = x_t - \tilde \eta_{t + 1}\nabla f(y_y)$. 
-                Similarly, for the updates of $y_{t + 1}$, we have optimality condition of 
-                \begin{align*}
-                    \mathbf 0 &= \nabla f (y_t) + L (x - y_t) + \eta_{t + 1}^{-1} (x - x_{t + 1})
-                    \\
-                    \mathbf 0 &= \eta_{t + 1}\nabla f (y_t) + \eta_{t + 1}L (x - y_t) + x - x_{t + 1}
-                    \\
-                    \mathbf 0 &= 
-                    \eta_{t + 1}\nabla f(y_t) -\eta_{t + 1} Ly_t + (\eta_{t + 1}L + 1)x - x_{t + 1}
-                    \\
-                    (1 + \eta_{t + 1}L)x
-                    &= 
-                    x_{t + 1} - \eta_{t + 1}\nabla f(y_t) + \eta_{t + 1}L y_t
-                    \\
-                    \text{define: } y_{t + 1} &:= x. 
-                \end{align*}
-                In the above expression, it hides a step of gradient descent, continuing it we have 
-                \begin{align*}
-                    (1 + \eta_{t + 1}L)y_{t + 1} &= 
-                    x_{t + 1}  + \eta_{t + 1}L (-L^{-1}\nabla f(y_t) + y_t)
-                    \\
-                    \text{let: } z_{t + 1} &= y_t - L^{-1}\nabla f(y_t), \text{ so, }
-                    \\
-                    (1 + \eta_{t + 1}L)y_{t + 1} &= 
-                    x_{t + 1} + L\eta_{t + 1}z_{t + 1}. 
-                \end{align*}
-                Combining it yields the tree points update format 
-                \begin{align*}
-                    x_{t + 1} &= x_t - \tilde \eta_{t + 1} \nabla f(y_t) 
-                    \\
-                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t) 
-                    \\
-                    y_{t + 1} &= 
-                    (1 + L\eta_{t + 1})^{-1}
-                    (
-                    x_{t + 1} + L\eta_{t + 1}z_{t + 1}
-                    ), 
-                \end{align*}
-                the ordering of $x_{t +1}, z_{t + 1}$ can be permuted. 
-                The base case is when $t = 0$, so then $x_0 = y_0$ for the initial guess.
-            \end{proof}
-            \begin{remark}
-                It is quite obvious to us that the choice of $z_{t + 1} = y_t - L^{-1}\nabla f(y_t)$ is deliberate. 
-                In fact, it's true that $z_{t + 1}$ is just a term such that it makes $y_{t +1}$ a convex combination between the vector $x_{t + 1}, z_{t + 1}$, and the choice here would be unique because of the consideration that
-                {\footnotesize
-                \begin{align*}
-                    & \quad 
-                    l_f(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 
-                    \\
-                    &= 
-                    f(y_t) + \langle \nabla f(y_t), x - y_t\rangle 
-                    + 
-                    \frac{L}{2}
-                    \left\Vert 
-                        x - (y_t - L^{-1}\nabla f(y_t)) - L^{-1}\nabla f(y_t)
-                    \right\Vert^2
-                    \\
-                    &= 
-                    f(y_t) + 
-                    \langle \nabla f(y_t), x - (y_t - L^{-1}\nabla f(y_t)) - L^{-1}\nabla f(y_t)\rangle 
-                    + 
-                    \frac{L}{2}
-                    \left\Vert 
-                        x - (y_t - L^{-1}\nabla f(y_t)) - L^{-1}\nabla f(y_t)
-                    \right\Vert^2
-                    \\
-                    &\quad  \text{Let }z_{t + 1} 
-                    = y_t - L^{-1}\nabla f(y_t)
-                    \\
-                    &= f(y_t) + \langle \nabla f(y_t), x - z_{t + 1} - L^{-1}\nabla f(y_t)\rangle
-                    + 
-                    \frac{L}{2}\left\Vert
-                        x - z_{t + 1} - L^{-1}\nabla f(y_t)
-                    \right\Vert^2
-                    \\
-                    &= 
-                    f(y_t) + \langle \nabla f(y_t), x - z_{t + 1}\rangle 
-                    - L^{-1}\Vert \nabla f(y_t)\Vert^2
-                    + 
-                    \frac{L}{2}\Vert x - z_{t + 1}\Vert^2 + 
-                    \frac{1}{2L}\Vert \nabla f(y_t)\Vert^2 - 
-                    L\langle L^{-1}\nabla f(y_t), x - z_{t + 1}\rangle
-                    \\
-                    &= f(y_t) + (1/(2L)- L^{-1})\Vert \nabla f(y_t) \Vert^2 + 
-                    \frac{L}{2}\Vert x - z_{t + 1}\Vert^2
-                    \\
-                    &= f(y_t) - \frac{1}{2L}\Vert \nabla f(y_t)\Vert^2 + \frac{L}{2}\Vert x - z_{t + 1}\Vert^2. 
-                \end{align*}
-                }
-                Therefore 
-                \begin{align*}
-                    y_{t + 1} &= \argmin_{x}\left\lbrace
-                        \frac{L}{2}\Vert x - z_{t + 1}\Vert^2 + 
-                        \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
-                    \right\rbrace
-                    \\
-                    &= \argmin_{x}\left\lbrace
-                        \left\Vert x - 
-                            \frac{Lz_{t + 1} + \eta_{t + 1}^{-1}x_{t + 1}}{
-                                L + \eta_{t + 1}^{-1}
-                            }
-                        \right\Vert^2
-                    \right\rbrace
-                    \\
-                    &= 
-                    \frac{
-                        L\eta_{t + 1}z_{t + 1} + 
-                        x_{t + 1}
-                    }{
-                        1 + L \eta_{t + 1}
-                    }. 
-                \end{align*}
-            \end{remark}
-
-            \begin{proposition}[Tri-points Strongly Convex Form via Ahn Sra 6.24]\label{prop:tri_scvx_from_ahn_sra_6.24}
-                Coninue \\ 
-                from \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} with but with $\mu > 0$, under the same set of assumptions it recovers a tri-points algorithm with the following updates: 
-                \begin{align*}
-                    y_t^+ &= y_t - \mu^{-1}\nabla f(y_t)
-                    \\
-                    x_{t + 1} &= \argmin_{x} 
-                    \left\lbrace
-                        l_f (x; y_t) + \frac{\mu}{2} \Vert x - y_t\Vert^2 + 
-                        \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2 
-                    \right\rbrace
-                    \\
-                    &= \argmin_{x}
-                    \left\lbrace
-                        f(y_t) - \frac{1}{2\mu} \Vert \nabla f(y_t)\Vert^2 
-                        + 
-                        \frac{\mu
-                        }{2}\Vert x - y_t^+\Vert^2
-                        + 
-                        \frac{1}{2\tilde \eta_{t + 1}}\Vert x - x_t\Vert^2
-                    \right\rbrace
-                    \\
-                    &= (1 + \mu\tilde \eta_{t + 1})^{-1}
-                    \left(
-                        x_t + \mu \tilde \eta_{t + 1}y_t^{+}
-                    \right)
-                    \\
-                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t)
-                    \\
-                    y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}(x_{t + 1} + L \eta_{t + 1} z_{t + 1})
-                \end{align*}
-            \end{proposition}
-            \begin{proof}
-                By a similar argument made in the remarks of \hyperref[prop:tri_form_via_ppm]{proposition \ref*{prop:tri_form_via_ppm}} we have 
-                \begin{align*}
-                    l_f(x; y_t) + \frac{\mu}{2}\Vert x - y_t\Vert^2
-                    &= 
-                    f(y_t) - \frac{1}{2\mu}\Vert \nabla f(y_t)\Vert^2 + \frac{\mu}{2}\Vert x - y_t^+\Vert^2
-                    \\
-                    \implies 
-                    x_{t + 1} &= 
-                    \argmin_{x} 
-                    \left\lbrace
-                        f(y_t) - \frac{1}{2\mu}\Vert \nabla f(y_t)\Vert^2 + \frac{\mu}{2}\Vert x - y_t^+\Vert^2
-                        + 
-                        \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
-                    \right\rbrace
-                    \\
-                    &= 
-                    \argmin_{x}
-                    \left\lbrace
-                        \frac{\mu}{2}\Vert x - y_t^+\Vert^2 + 
-                        \frac{2}{\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
-                    \right\rbrace
-                    \\
-                    &= (\mu + \tilde \eta_{t + 1})^{-1}
-                    (\mu y_t^+ + \tilde \eta_{t + 1}x_t)
-                    \\
-                    &= (1 + \tilde \eta_{t + 1}\mu)^{-1}
-                    (x_t + \mu\tilde \eta_{t + 1}y_t^+). 
-                \end{align*}
-                The updates for $y_{t + 1}, z_{t + 1}$ is the same as before because $\mu > 0$ only alters the update of the term $x_{t + 1}$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}. 
-            \end{proof}
-
-            \begin{proposition}[Nestrov 2.2.7 is Equivlant to Ahn Sra 6.24 in Form]
-            \label{prop:Nes2.2.7_via_ahn_sra_6.24}
-                The \hyperref[def:Nes2.2.7]{algorithm \ref*{def:Nes2.2.7}} is equivalent to \hyperref[def:agg_ppm]{\ref*{def:agg_ppm}} in form. 
-                So the updates for $y_{k + 1}, x_{k + 1}, v_{k + 1}$: 
-                \begin{align*}
-                    \text{find } &
-                    \alpha_k \in (0, 1) 
-                    \text{ s.t: } L\alpha_k^2 
-                    = (1 - \alpha_k)\gamma_k + \alpha_k \mu = \gamma_{k + 1} 
-                    \\
-                    y_k &= 
-                    \left(
-                        \gamma_k + \alpha_k \mu
-                    \right)^{-1} \left(
-                        \alpha_k \gamma_k v_k + \gamma_{k + 1}x_k
-                    \right)
-                    \\
-                    \text{find } & x_{k + 1} \text{ s.t: }
-                    f(x_{k + 1})
-                    = f(y_k) - (2L)^{-1}\Vert \nabla f(y_k)\Vert^2
-                    \\
-                    v_{k+1} &= 
-                    \gamma_{k + 1}^{-1} 
-                    \left(
-                        (1 - \alpha_k) \gamma_k v_k + 
-                        \alpha_k \mu y_k 
-                        - \alpha_k \nabla f(y_k)
-                    \right). 
-                \end{align*}
-                Is the same as $y_{t + 1}, z_{t + 1}, x_{t + 1}$ from below: 
-                \begin{align*}
-                    x_{t + 1} 
-                    & = 
-                    (1 + \tilde \eta_{t + 1}\mu)^{-1}
-                    (x_t + \mu\tilde \eta_{t + 1}y_t - \tilde \eta_{t + 1}\nabla f(y_t))
-                    \\
-                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t)
-                    \\
-                    y_{t + 1} &= 
-                    (1 + L\eta_{t + 1})^{-1}
-                    (x_{t + 1} + L \eta_{t + 1} z_{t + 1}).
-                \end{align*}
-                which is an equivalent representation of \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} as showned in \hyperref[prop:tri_scvx_from_ahn_sra_6.24]{propostion \ref*{prop:tri_scvx_from_ahn_sra_6.24}}.
-            \end{proposition}
-            \begin{proof}
-                We simplify the Nesterov form into the Strongly convex Generic Triangular Form. 
-                Consider update for $v_{k + 1}$ by substituting $\gamma_{k+1} = (1 - \alpha_k) \gamma_k + \alpha_k \mu$ as informed by the first step of the algorithm, we have 
-                \begin{align*}
-                    v_{k + 1} &= 
-                    ((1 - \alpha_k)\gamma_k + \alpha_k \mu)^{-1}
-                    \left(
-                        (1 - \alpha_k)\gamma_k v_k + \alpha_k \mu y_k - \alpha_k \nabla f(y_k)
-                    \right)
-                    \\
-                    &= ((1 - \alpha_k)\gamma_k + \alpha_k \mu)^{-1}
-                    (
-                        (1 - \alpha_k)\gamma_k v_k + \alpha_k \mu(y_k - \alpha_k \mu^{-1}\nabla f(y_k))
-                    )
-                    \\
-                    &= 
-                    \left(
-                        1 + \frac{\alpha_k \mu}{(1 - \alpha_k)\gamma_k}
-                    \right)^{-1}
-                    \left(
-                        v_k
-                        + 
-                        \left(
-                            \frac{\alpha_k \mu}{(1 - \alpha_k)\gamma_k} 
-                        \right)
-                        \left(
-                            y_k 
-                            - \alpha_k \mu^{-1}\nabla f(y_k)
-                        \right)
-                    \right). 
-                \end{align*}
-                Notice that the right hand size has the same form as $x_{t + 1}$. 
-                This is true by the observation that 
-                \begin{align*}
-                    x_{t + 1} &= 
-                    (1 + \tilde\eta_{t + 1}\mu)^{-1}
-                    \left( 
-                        x_t + \mu\tilde \eta_{t + 1}
-                        \left(y_t - \mu^{-1}\nabla f(y_t)\right)
-                    \right). 
-                \end{align*}
-                Similarly, when $\mu = 0$, we have from the first step that 
-                \begin{align*}
-                    v_{k + 1} 
-                    &= ((1 - \alpha_k)\gamma_k)^{-1}
-                    (
-                        (1 - \alpha_k)\gamma_k v_k
-                        + \alpha_k \mu y_k - \alpha_k \nabla f(y_k)
-                    )
-                    \\
-                    &= 
-                    v_k - \alpha_k((1 - \alpha_k)\gamma_k)^{-1}\nabla f(y_k)
-                \end{align*}
-                which is the same as the AG generic PPM form where 
-                $$
-                    x_{t + 1} = x_t - \tilde \eta_{t + 1}\nabla f(y_t). 
-                $$
-                Next, we consider $y_{k}$ iterate of Nesterov 2.2.7. 
-                We want to write it as a convex combination of the vector $v_k,x_k$. 
-                To show that the updates $y_k$ can are of the same form, start by considering that 
-                \begin{align*}
-                    \gamma_{k + 1 } &= (1 - \alpha_k)\gamma_k + \alpha_k \mu
-                    \\
-                    &= (\gamma_k + \alpha_k \mu) - \alpha_k \gamma_k, 
-                \end{align*}
-                with the grouping we have
-                \begin{align*}
-                    y_k &= \left(
-                        \gamma_k + \alpha_k \mu
-                        \right)^{-1} \left(
-                            \alpha_k \gamma_k v_k + \gamma_{k + 1}x_k
-                        \right)
-                    \\
-                    &= 
-                    \left(
-                        \gamma_k + \alpha_k \mu
-                    \right)^{-1}
-                    \left(
-                        \alpha_k \gamma_k v_k 
-                        + 
-                        ((\gamma_k + \alpha_k\mu) - \alpha_k\gamma_k)x_k
-                    \right)
-                    \\
-                    &= 
-                    \left(
-                        \frac{\alpha_k \gamma_k}{\gamma_k + \alpha_k \mu}
-                    \right)v_k
-                    + 
-                    \left(
-                        1 - \frac{\alpha_k\gamma_k }{\gamma_k + \alpha_k \mu}
-                    \right)x_k, 
-                \end{align*}
-
-                which is indeed, a convex combination of $v_k, x_k$, if, we assume that $(\alpha_k\gamma_k)(\gamma_k + \alpha_k \mu)^{-1}$ is in the interval $(0, 1)$. 
-                We can assume it by considering $\gamma_k = L\alpha_{k-1}^2$, simplifying so that 
-                \begin{align*}
-                    \frac{\alpha_k \gamma_k}{\gamma_k + \alpha_k \mu}
-                    &= 
-                    \frac{L\alpha_k \alpha_{k - 1}^2}{L\alpha_{k - 1}^2 + \mu \alpha_k}
-                    \\
-                    &= \frac{\alpha_k \alpha_{k - 1}^2}{1 + q_f \alpha_k \alpha_{k - 1}^{-2}} \in (0, 1), 
-                \end{align*}
-                where $q_f = \mu / L \in (0, 1)$ and we recall the fact that the sequence $(\alpha_k)_{k \in \NN}$ has $\alpha_k \in (0, 1)$ and $\sum_{i = 1}^{\infty} \alpha_k = \infty$. 
-                However, it would require more works to express $\eta_t, \tilde\eta$ from Ahn Sra 6.24 using $\gamma_k, \alpha_k$ from Nesterov 2.2.7. 
-            \end{proof}
-
-            \begin{proposition}[Deriving Proximal Gradient Tri-Points Generic Form]
+    \begin{proposition}[Deriving Proximal Gradient Generic Form]
         \label{prop:derive_ag_prox_grad_tript}
@@
         \end{align*}
-                Therefore, the algorithm 
+        Therefore, the algorithm in
         \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}
-                is equivalent to 
-                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
+        is equivalent to algorithm in
+        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
     \end{proposition}
@@
         Let $y_t^+ = \mathcal T_L(y_t)$, recall that $l_h(x; y_t) = h(y_t^+) + \langle \mathcal G_L(y_t), x -y_t\rangle \le f(x)$ by the definition of algorithm. 
-                Since $l_h(x; y_t)$ is a simple linear function wrt $x$, it's not hard to minimize the quandratic where we can get $x_{t + 1} = x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t)$. 
-                For $y_{t + 1}$, observe that we can complete the square on the second and the third terms: 
+        Since $l_h(x; y_t)$ is a simple linear function wrt $x$, minimizing the quandratic where to get $x_{t + 1} = x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t)$; for $y_{t + 1}$, complete the square on the second and the third terms:
         \begin{align*}
@@
             &=
-                    \frac{(y_t - L^{-1}\mathcal G_L(y_t)) + x_{t + 1}}{L + \eta_{t + 1}^{-1}}.
+            \frac{
+                \left(y_t - L^{-1}\mathcal G_L(y_t)\right) + x_{t + 1}
+            }{L + \eta_{t + 1}^{-1}}.
         \end{align*}
@@
         $$
-                As a sanity checks, notice that when 
-                $h \equiv 0$, 
-                $\mathcal G_L(x) = \nabla f(x)$ 
-                by definition, making it the same as 
-                \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
     \end{proof}
@@
         Given that the original function $h$ is potentially non-smooth, therefore it's not always an upper bound of $h(x)$. 
-                The upper bound interpretation of the smooth case as proposed by Ahn, Sra for the update of $y_{t + 1}$ fails when $h$ is non-smooth! 
+        The upper bound interpretation of the smooth case as proposed by Ahn \cite{ahn_understanding_2022}, Sra for the update of $y_{t + 1}$ fails when $h$ is non-smooth! 
     \end{remark}
 
-            \begin{lemma}[Deriving Similar Triangle Form I]
-                \quad \\
-                With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$ 
-                in 
-                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
-                We can derive similar triangle form I as stated back in
-                \hyperref[def:ag_form_similar_tria_I]{definition \ref*{def:ag_form_similar_tria_I}}. 
-                \begin{align*}
-                    z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t)
-                    \\
-                    x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
-                    \\
-                    y_{t + 1} &= 
-                    (1 + L\eta_{t + 1})^{-1}
-                    (
-                    x_{t + 1} + L\eta_{t + 1}z_{t + 1}
-                    ). 
-                \end{align*}
-                It also has an equivalent momentum form 
-                \begin{align*}
-                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
-                    \\
-                    y_{t + 1} &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t). 
-                \end{align*}
-            \end{lemma}
-            \begin{proof}
-                To do, we show that updates sequence $x_{t + 1} = z_{t + 1} + L\eta_t (z_{t + 1} - z_t)$ is equivalent to $x_{t + 1} = x_t + \tilde\eta_{t + 1}\nabla f(y_t)$. 
-                Starting with the former, susbtitute definition of $z_{t + 1}$, $z_{t + 1} = z_t + L^{-1}\nabla f(y_t)$ expanding: 
-                \begin{align*}
-                    x_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t) 
-                    + L \eta_t y_t - \eta_t \mathcal G_L(y_t) - L\eta_t z_t
-                    \\
-                    &= 
-                    (1 + L\eta_t)y_t - (\eta_t + L^{-1})\mathcal G_L(y_t) - L\eta_t z_t
-                    \\
-                    &= \eta_t Lz_t + x_t -(\eta_t + L^{-1}) \mathcal G_L(y_t)  - L\eta_t z_t
-                    \\
-                    &= x_t - (\eta_t + L^{-1})\mathcal G_L(y_t). 
-                \end{align*}
-                So $x_{t + 1} = x_t + \tilde \eta_{t + 1}\mathcal G_L(y_t)$, by assumption $\tilde \eta_{t + 1} = \eta_t + L^{-1}$
-                Reducing it to the classic momentum form starts by 
-                \begin{align*}
-                    y_{t + 1} &= (1 + L\eta_{t + 1})^{-1} (x_{t + 1} + L\eta_{t + 1}z_{t + 1})
-                    \\
-                    &= (1 + L\eta_{t + 1})^{-1} (
-                        z_{t + 1} + L\eta_t (z_{t + 1} - z_t) + L\eta_{t + 1} z_{t + 1}
-                    )
-                    \\
-                    &= 
-                    (1 + L\eta_{t + 1})^{-1} (
-                        (1 + L\eta_{t + 1})z_{t + 1} + L\eta_t(z_{t + 1} - z_t)
-                    )
-                    \\
-                    &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t), 
-                \end{align*}
-                it negates the $x_t$ variables, therefore we have 
-                \begin{align*}
-                    z_{t + 1} &= y_t - L^{-1} \mathcal G_L (y_t)
-                    \\
-                    y_{t + 1} &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t).
-                \end{align*}
-            \end{proof}
-            \begin{remark}
-                In this remark we clarify the name ``similar triangle" as given in the literatures. 
-                We think it is a fitting name, becaues it has a similar triangle in it. 
-                We list the following observations
-                \begin{enumerate}
-                    \item 
-                    The updates for $y_{t}$ from the algorithm has 
-                    $$
-                        y_t = (1 + L\eta_t)^{-1} x_t + L\eta_t(1 + L\eta_t)^{-1} z_t, 
-                    $$
-                    therefore, $y_t$ is a convex combinations of $x_t, z_t$, so $z_t, y_t, x_t$ are three collinear points. 
-                    We have the ratio $\Vert y_t - x_t\Vert/\Vert z_t - y_t\Vert = L\eta_t$. 
-                    \item 
-                    The updates for $z_{t + 1}, x_{t + 1}$ are based on $y_t, x_t$ displaced by $L^{-1} \mathcal G_L(y_t), \tilde\eta_{t +1} \mathcal G_L(y_t)$, therefore vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$.
-                    \item The updates for $x_{t + 1}$ has $x_{t + 1} - z_{t + 1} = L\eta_t \left(z_{t + 1} - z_t\right)$, therefore, the three points $z_t, x_{t + 1}, z_{t + 1}$ are collinear. 
-                    The ratio between line segment has $\Vert x_{t + 1} - z_{t + 1}\Vert/\Vert z_{t + 1} - z_t\Vert = L\eta_t$. 
-                \end{enumerate}
-                By these tree observations, the triangle $z_{t}, z_{t + 1}, y_t$ similar to triangle $z_t, x_{t + 1}, x_t$. 
-                Finally, similar remarks about the similar triangle form can be found in Ahn, Sra's paper \cite{ahn_understanding_2022} as well.
-
-            \end{remark}
-
-    \subsection{Generic Lyapunov analysis for Accelerated gradient via PPM}
+\section{Generic Lyapunov analysis for Accelerated gradient via PPM}
 \label{sec:generic_ag_ppm_lyapunov_analysis}
-        The first theorem states the generic convergence results when $f$ is differentiable with $L$-Lipschitz gradient, using \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}.
+    The lemma theorem states targets
+    \hyperref[prop:derive_ag_prox_grad_tript]
+    {definition \ref*{prop:derive_ag_prox_grad_tript}}.
 
     \begin{lemma}[Nonsmooth Generic AG Lyapunov Analysis]
-        \label{lemma:nsmooth_agg_lyapunov_upper_bound}
+    \label{lemma:nsmooth_agg_lyapunov_upper_bound}\;\\
         Continue from 
@@
         {definition \ref*{prop:derive_ag_prox_grad_tript}},
-            we derive the non-smooth analogous case of the Lyapunov upper bound: 
+        we derive the non-smooth analogous case of the Lyapunov upper bound for all $t \in \mathbb N \cup \{0\}$: 
         \begin{align*}
@@
     \label{thm:generic_ag_convergence}
-            If there is a choice of $\eta_i, \tilde \eta_i$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} such that we have 
-            \begin{align*}
-                \left(
-                    \sum_{i = 1}^{t} \tilde \eta_i
-                \right)
-                \Upsilon_{2, t + 1}^{\text{AG}} + 
-                \Upsilon_{1, t + 1}^{\text{AG}} \le 0, 
-            \end{align*}
-            then with 
+        Define the Lyapunov function $\Phi_t\; \forall t \in \{0\}\cup \N$: 
         \begin{align*}
@@
             \\
-                \Phi_0 &= \frac{1}{2}\Vert x_t - x_*\Vert^2, 
-            \end{align*}
-            we have $\Phi_{t + 1} - \Phi_t \le 0$, which allows for a convergence rate of $\mathcal O \left(\sum_{i = 1}^{T} \eta_i^{-1}\right)$ for $f(z_T) - f(x_*)$. 
+            \Phi_0 &= \frac{1}{2}\Vert x_0 - x_*\Vert^2, 
+        \end{align*}
+        if there is a choice of $\eta_i, \tilde \eta_i$ in 
+        \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}} such that we have 
+        \begin{align*}
+            & \Phi_{t + 1} - \Phi_{t}\left(
+                \sum_{i = 1}^{t} \tilde \eta_i
+            \right) =
+            \Upsilon_{2, t + 1}^{\text{AG}} + 
+            \Upsilon_{1, t + 1}^{\text{AG}} 
+            \le \delta_{t + 1} \quad 
+            \forall t \in \mathbb N, 
+            \\
+            & \Upsilon_{1, 1}^{\text{AG}} \le \delta_1. 
+        \end{align*}
+        Then with
+        \begin{align*}
+            S_t &:= \sum_{i = 1}^{t} \delta_i
+            \\
+            \sigma_t &:= \sum_{i = 1}^{t}\tilde \eta_i
+        \end{align*}
+        we have $\Phi_{t + 1} - \Phi_t \le \delta_{t + 1}$, it allows for a convergence rate of $\mathcal O \left(\sigma_T^{-1}S_T\right)$ of $f(z_T) - f(x_*)$ when $S_T \neq 0$ and a rate of $\mathcal O(\sigma_T^{-1})$ when $S_T = 0$.
     \end{theorem}
@@
                 \sum_{i = 1}^{t} \tilde \eta_i
-                \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le 0. 
+            \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le \delta_{t + 1}. 
         \end{align*}
         }
-            The derivation for the convergence raet is direct and similar to 
-            \hyperref[thm:ppm_convergence_rate]{theorem \ref*{thm:ppm_convergence_rate}} 
-            Therefore, if we can identify parameter for the generic algorithm that asserts the condition above, then we have convergence for the algorithm. 
+        Telescoping we have 
+        \begin{align*}
+            \Phi_{t + 1} - \Phi_t &\le \delta_{t + 1}
+            \\
+            \sum_{i = 0}^{T - 1}\Phi_{i + 1} - \Phi_i &\le \sum_{i = 0}^{T - 1}\delta_{i + 1}
+            \\
+            \Phi_T - \Phi_0 &\le 
+            \sum_{i = 1}^{T}\delta_i = S_{T}. 
+        \end{align*}
+        So then $\Phi_T - \Phi_0$ yields: 
+        $$
+        \begin{aligned}
+            \sigma_T (f(z_t) - f(x_*)) 
+            + \frac{1}{2}\Vert x_t - x_*\Vert^2 
+            - \frac{1}{2}\Vert x_0 - x_*\Vert^2 
+            &\le S_{T}
+            \\
+            \implies 
+            \sigma_T(f(z_t) - f(x_*))
+            &\le 
+            S_T + \frac{1}{2}\Vert x_0 - x_*\Vert^2
+            \\
+            f(z_t) - f(x_*) &\le 
+            \sigma_T^{-1}\left(
+                S_{T} + \frac{1}{2}\Vert x_0 - x_*\Vert^2
+            \right),
+        \end{aligned}
+        $$
+        which yields a convergence rate $\mathcal O(\sigma_T^{-1}S_{T})$. 
+        When $S_T = 0$, the convergence rate is $O(\sigma_T^{-1})$ instead. 
     \end{proof}
 
-    \subsection{Scenario I}\label{sec:scenario_i}
-        In this scenario, we aim to recover AG Ryu 12.1 conceret variant algorithm stated back in 
-        \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}. 
-        \begin{proposition}
-            Continue from
-            \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}, 
-            set $\eta_{t + 1} = \tilde \eta_{t + 1} = (t)/(2L)$, we derive the following algorithm: 
-            \begin{align*}
-                x_{t + 1} &= x_t - \frac{t + 1}{2L} \mathcal G_L(y_t), 
-                \\
-                z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t), 
-                \\
-                y_{t + 1} &= 
-                \left(
-                    \frac{2}{t + 3}
-                \right)x_{t +1} + 
-                \left(
-                    1 - \frac{2}{t + 3}
-                \right)z_{t + 1}. 
-            \end{align*}
-            This algorithm has convergence rate of $\mathcal O(1/T^2)$ for all $h = f + g$ where $f$ is convex $L$-Lipschitz smooth and $g$ is convex. 
-        \end{proposition}
-        \begin{observation}
-            Observe that when $g \equiv 0$ this is the same algorithm as 
-            \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}
-            but with an alternative choice of indexing for $y_t$ and initial condition. 
-        \end{observation}
+    \begin{theorem}[Constraints on the PPM stepsize sequence]
+        \label{thm:ag_generic_stepsize_constrants}
+        \;\\
+        Algorithm formulated in 
+        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
+        converges if the stepsize sequence $\eta_i, \tilde \eta_{i}$ satisfies
+        \begin{align*}
+            \begin{cases}
+                \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
+                - L^{-1} \sum_{i= 1}^{t}\tilde \eta_i 
+                = 
+                \epsilon_{t + 1} \tilde \eta_{t + 1}
+                & \forall t \in \mathbb N, 
+                \\
+                L \eta_t \tilde \eta_{t + 1} = \sum_{i=1}^{t}\tilde \eta_i 
+                & \forall t \in \mathbb N. 
+            \end{cases}
+        \end{align*}
+        Here $\epsilon_{t + 1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$ is a sequence made to characterizing the error between $\tilde \eta_{t + 1}, \eta_t - L^{-1}$. 
+        Then the convergence rate can be formulated by
+        \begin{align*}
+            \Phi_{t + 1} - \Phi_t =
+            \Upsilon_{1, t + 1}^\text{AG} + 
+            \sigma_t\Upsilon_{1, t + 1}^{\text{AG}} 
+            &\le \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}.
+        \end{align*}
+        When $\epsilon_t = 0 \;\forall t\in \mathbb N$, the sequence $a_t:= a_t = 1 + L \eta_t = \tilde \eta_{t + 1} - \epsilon_{t + 1}$, the relation simplies to: 
+        \begin{align*}
+            \begin{cases}
+                a_{t + 1} = (1/2)\left(
+                1 + \sqrt{1 + 4 c_{t + 1}}
+                \right), 
+                \\
+                c_{t + 1} = a_t^2.     
+            \end{cases}
+        \end{align*}
+        As a consequence: 
+        \begin{enumerate}
+            \item It makes $\delta_{t} = 0$ in the Lypunov analysis; 
+            \item it simplifies the algorithm to FISTA. 
+            \item and $a_t$ is the famous Nesterov momentum sequence. 
+        \end{enumerate}
+
+    \end{theorem}
     \begin{proof}
-            Recall that for the proximal gradient PPM generic form we have iterate updates for $t\in \mathbb N$: 
+        With $t \in \mathbb N \cup \{0\}$ fixed, 
+        recall that for the proximal gradient PPM generic form 
+        (as formulated in 
+        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
+        ) for $t\in \mathbb N$ it has: 
         \begin{align*}
@@
         \end{align*}
-            and generic Lyapunov upper bound 
+        Recall the upper bounds from 
+        \ref*{thm:generic_ag_convergence}, 
+        it has 
         \begin{align*}
@@
         \end{align*}
-            By the updates, vector $x_{t + 1} - x_t$ and $z_{t + 1} - y_t$ are parallel by observations 
+        By the updates, vector $x_{t + 1} - x_t$ and $z_{t + 1} - y_t$ are parallel by observations: 
         \begin{align*}
@@
         \end{align*}
-            This setup allows for: 
+        This allows for 
         \begin{align*}
@@
             \right)\Vert \mathcal G_L(y_t)\Vert^2 
-                + \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), y_t - x_t\rangle
-            \end{align*}
-            similarly we also have upper bound 
+            + \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), y_t - x_t\rangle.
+        \end{align*}
+        Similarly 
         \begin{align*}
@@
 We make the choice to do surgery on upper bound of $\Upsilon_{2, t + 1}^\text{AG}$, so $\langle \mathcal G_L(y_t), y_t - x_t\rangle = \langle \mathcal G_L(y_t), L \eta_t (z_t - y_t)\rangle$.
-            With this in mind, applying the RHS of $[(*)]$ yields: 
+        With this in mind, RHS of $\phi_{t + 1} - \phi_t$ yields: 
         {\footnotesize
@@
                 L\eta_t \tilde \eta_{t + 1} - \sum_{i = 1}^{t}\tilde \eta_i
-                \right)\langle \mathcal G_L(y_t), z_t - y_t\rangle
+            \right)\langle \mathcal G_L(y_t), z_t - y_t\rangle. 
         \end{align*}
         }
-            If the algorithm were to have the abstract convergence rate as stated in 
-            \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}},
-            then one of the sufficient condition is to have the above quantity less than or equal to zero, one sufficient condition of that is to have the coefficient for $\Vert \mathcal G_L(y_t)\Vert$ be $\le 0$, and the coefficient of the cross term $\langle \mathcal G_L(y_t), z_t - y_t\rangle$ be zero.
-            To simplify, we make the assumption that $\tilde \eta_t = \eta_t$ for all $t \in \mathcal N$, making it to be a specific instance of 
-            \hyperref[def:ag_tri_pt_form_E]{definition \ref*{def:ag_tri_pt_form_E}}. 
-            These conditions translate to the following relations for $\eta_{t}$. 
+        The non-negativity of $\Vert \mathcal G_L(y_t) \Vert^2$ characterize the culmulative error $\delta_{t + 1}$ in the Lypunov analysis through sequence $\epsilon_i$. 
+        Setting the coefficient of $\Vert \mathcal G_L(y_t) \Vert^2$ to be $\epsilon_{t + 1}\tilde \eta_{t + 1}$, it yields a system of inequality: 
         \begin{align*}
             \begin{cases}
-                    L\eta_{t + 1}^2 + \eta_{t + 1} - \sum_{i = 1}^{t}\eta_i 
-                    \le 0, 
-                    \\
-                    L\eta_t \eta_{t + 1} - \sum_{i = 1}^{t} \eta_i 
-                    = 0. 
+                \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
+                - L^{-1} \sum_{i= 1}^{t}\tilde \eta_i 
+                = 
+                \epsilon_{t + 1} \tilde \eta_{t + 1}
+                & \forall t \in \N, 
+                \\
+                L \eta_t \tilde \eta_{t + 1} = \sum_{i=1}^{t}\tilde \eta_i 
+                & \forall t \in \N. 
             \end{cases}
         \end{align*}
-            Substituting the sequence equality back to the first one yield: 
-            \begin{align*}
-                L\eta_{t + 1}^2 - (\eta_{t + 1} + L\eta_t\eta_{t + 1}) &\le 0 
-                \\
-                L\eta^2_{t + 1} - \eta_{t + 1}
+        It requires base case $L\eta_0\tilde\eta_{1} = 0$, assume $\sigma_0 = 0$. 
+        We use $\sum_{i = 1}^t \tilde \eta_i = \sigma_t$, simplifying the first equation we have 
+        \begin{align*}
+            \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
+            - L^{-1} \sigma_t
+            &= 
+            \epsilon_{t + 1} \tilde \eta_{t + 1}
+            \\
+            \iff 
+            \tilde \eta_{t + 1} ^2 - L \tilde \eta_{t + 1} 
+            &= 
+            \epsilon_{t + 1} \tilde \eta_{t + 1} + L^{-1} \sigma_t
+            \\
+            &= 
+            \epsilon_{t + 1} \tilde \eta_{t + 1} 
+            + L^{-1}(L \eta_t \tilde \eta_{t + 1})
+            \\
+            \iff 
+            \tilde \eta_{t + 1} &= \epsilon_{t + 1} + \eta_t + L^{-1}. 
+        \end{align*}
+        At the last step, we divided both side of the equation by $\tilde \eta_{t + 1} > 0$.
+        The parameter gives relation $\epsilon_{t+1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$. 
+        Hence, it gives us the following system of equality to work with 
+        \begin{align*}
+            \forall t \in \N: 
+            \begin{cases}
+                \tilde \eta_{t + 1} = \epsilon_{t + 1} + \eta_t + L^{-1}, 
+                \\
+                L \eta_t \tilde \eta_{t + 1} = \sigma_t.     
+            \end{cases}
+        \end{align*}
+        With that, we can solve a relation between $\eta_{t + 1}$ in terms of the sequence $\epsilon$ and $\eta_t$.
+        Consider the equality 
+        \begin{align*}
+            L \sigma_{t + 1} &= L \tilde \eta_{t + 1} + L \sigma_t
+            \\
+            &=
+            L \tilde \eta_{t + 1}  + L (L \eta_t \tilde \eta_{t + 1})
+            \\
+            &= L \tilde \eta_{t+ 1} + L \eta_t (L \tilde \eta_{t + 1})
+            \\
+            &=  L \tilde \eta_{t+ 1} + L \eta_t (L \epsilon_{t + 1} + L \eta_t + 1)
+            \\
+            &=  L \tilde \eta_{t+ 1} + L \eta_t (L \eta_t + 1) + L^2 \eta_t \epsilon_{t + 1}
+            \\
+            &= L (\epsilon_{t +1} + \eta_t + L^{-1}) + L\eta_t(L \eta_t + 1) + L^2\eta_t \epsilon_{t + 1}
+            \\
+            &= L \epsilon_{t + 1} + (L\eta_t + 1)^2 + L^2\eta_t \epsilon_{t + 1}
+            \\
+            &= 
+            L \epsilon_{t + 1}(1 + L \eta_t) + (1 + L \eta_t)^2. 
+        \end{align*}
+        At the same time we have 
+        \begin{align*}
+            L \sigma_{t + 1} &= L^2 \eta_{t + 1}\tilde \eta_{t + 1} 
+            \\
+            &= L\eta_{t + 1}(1 + L \eta_{t + 1} + \epsilon_{t + 2})
+            \\
+            &= L\eta_{t + 1}(1 + L \eta_{t + 1}) + \epsilon_{t + 2}L\eta_{t + 1}. 
+        \end{align*}
+        Therefore, it generates the following equation: 
+        \begin{align*}
+            L\eta_{t + 1} (1 + L \eta_{t + 1}) 
+            + 
+            \epsilon_{t + 2} L \eta_{t + 1} 
+            &= 
+            L\epsilon_{t + 1}(1 + L \eta_t)  + (1 + L\eta_t)^2
+            \\
+            (L\eta_{t + 1} + L^2\eta_{t + 1}^2)
+            + 
+            \epsilon_{t + 2} L \eta_{t + 1} 
+            + 
+            \frac{1}{4}
+            &= 
+            L\epsilon_{t + 1}(1 + L \eta_t)  + (1 + L\eta_t)^2
+            + 
+            \frac{1}{4}
+            \\
+            (L\eta_{t + 1} + L^2\eta_{t + 1}^2 + 1/4)
+            + 
+            \epsilon_{t + 2} L \eta_{t + 1} 
+            + \epsilon_{t + 2}
+            &= 
+            L\epsilon_{t + 1}(1 + L \eta_t)  + (1 + L\eta_t)^2
+            + \frac{1}{4}
+            + \epsilon_{t + 2}
+            \\
+            (L\eta_{t + 1} + 1/2)^2 + \epsilon_{t + 2}(L \eta_{t + 1} + 1)
+            &= 
+            L \epsilon_{t + 1}(1 + L \eta_t) + (1 + L\eta_t)^2
+            + \frac{1}{4} + \epsilon_{t + 2}
+            \\
+            \text{ with: } & a_t = 1 + L \eta_t = \tilde \eta_{t + 1} - \epsilon_{t + 1}
+            \\
+            (a_{t + 1} - 1/2)^2 + \epsilon_{t + 2}a_{t + 1}
+            &= 
+            L \epsilon_{t + 1}a_t + a_t^2 + 1/4 + \epsilon_{t + 1}
+            \\
+            a_{t + 1}^2 + 1/4 - a_{t + 1} + \epsilon_{t + 2}a_{t + 1}
+            &= 
+            L \epsilon_{t + 1}a_t + a_t^2 + 1/4 + \epsilon_{t + 1}
+            \\
+            a_{t + 1}^2 + a_{t + 1}(\epsilon_{t + 2} - 1)
+            &= 
+            \underbrace{
+                a_t(L \epsilon_{t + 1} + a_t) + \epsilon_{t + 1}
+            }_{c_{t + 1}}. 
+        \end{align*}
+        Solving reveals the relations: 
+        \begin{align*}
+            \begin{cases}
+                a_{t + 1} = (1/2)\left(
+                1 - \epsilon_{t + 2} + \sqrt{(1 - \epsilon_{t + 2}) + 4 c_{t + 2}}
+                \right), 
+                \\
+                c_{t + 1} = a_t (L \epsilon_{t + 1} + a_t) + \epsilon_{t + 1}. 
+            \end{cases}
+        \end{align*}
+        Observe that in the case where we choose $\epsilon_t = 0\; \forall t \in \N$, the above relation simplifies to 
+        \begin{align*}
+            a_{t + 1} &= (1/2)\left(
+                1 + \sqrt{1 + 4 c_{t + 1}}
+            \right), 
+            \\
+            c_{t + 1} &= a_t^2. 
+        \end{align*}
+        This relation is the Famous Nesterov momentum sequence. 
+        At the same time, we can analyize the convergence rate of the algorithm by the abstract convergence lemma, producing: 
+        \begin{align*}
+            \Phi_{t + 1} - \Phi_t =
+            \Upsilon_{1, t + 1}^\text{AG} + 
+            \sigma_t\Upsilon_{1, t + 1}^{\text{AG}} 
+            &\le \epsilon_{t + 1}\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}
+        \end{align*}
+        Telescoping yields: 
+        \begin{align*}
+            S_{T} = 
+            \sum_{i = 0}^{T- 1} \delta_i 
+            &= 
+            \sum_{i = 0}^{T - 1} \epsilon_{i + 1}\tilde\eta_{i + 1}\Vert \mathcal G_L(y_i)\Vert^2
+            \\
+            &\le \sum_{i = 0}^{T - 1}\max(\epsilon_{i + 1} \tilde\eta_{i + 1}\Vert \mathcal G_L(y_i)\Vert^2, 0). 
+        \end{align*}
+        Under an ideal case where we wish to attain accelerations, we want $\lim_{T \rightarrow \infty} S_T < \infty$. 
+        One way to accomplish is choose the error sequence $\epsilon_i, i \in \N$ to be bounded by for all $i \in \N$, $\epsilon_i$ should satisfy: 
+        \begin{align*}
+            \epsilon_{i + 1}\tilde \eta_{i + 1}
+            \Vert \mathcal G_L(y_i)\Vert^2 
+            &\le \delta_{i + 1}
+            \\
+            \iff 
+            \epsilon_{i + 1}
             &\le 
-                L\eta_t \eta_{t + 1} 
-                \\
-                \eta_{t + 1}(L\eta_{t + 1} - 1) 
-                &\le L\eta_t\eta_{t + 1}
-                \\
-                \eta_t > 0 
-                \implies 
-                L\eta_{t + 1} - 1 &\le 
-                L\eta_t 
-                \\
-                \eta_{t + 1} &\le \eta_t + L^{-1}. 
-            \end{align*}
-            To satisfy the equality, reader should verify that $\eta_{t} = t/(2L)$ or $\eta_t = (t + 1)/2L$ are some of the options. 
+            \frac{\delta_{i + 1} }{\tilde\eta_{t + 1}\Vert \mathcal G_L(y_i)\Vert^2}. 
+        \end{align*}
+        for any $\sum_{i = 0}^{T - 1}\delta_{i + 1}$ converges to a limit as $T \rightarrow \infty$.
+
+    \end{proof}
+
+\section{Recovering existing variants of Nesterov accelerated gradient}\label{sec:recovery}
+    \subsection{Recovering FISTA}
+        From 
+        \hyperref[thm:ag_generic_stepsize_constrants]{theorem \ref*{thm:ag_generic_stepsize_constrants}}, 
+        setting $\epsilon_i = 0$ for all $i$ yields $a_t = 1 + L\eta_t = \tilde \eta_{t + 1}$, for all $t \in \N$ where $a_t$ is the Nesterov sequence.
+        In this case, there exists a momentum form of the generic form and it reduces to FISTA from Beck and Toubolle, or Similar Triangle Method as referred to by Ahn and Sra.
+
+        \begin{lemma}[Deriving Similar Triangle Form I]
+            \quad \\
+            With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$ 
+            in 
+            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
+            \begin{align*}
+                z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t)
+                \\
+                x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
+                \\
+                y_{t + 1} &= 
+                (1 + L\eta_{t + 1})^{-1}
+                (
+                x_{t + 1} + L\eta_{t + 1}z_{t + 1}
+                ). 
+            \end{align*}
+            It also has an equivalent momentum form 
+            \begin{align*}
+                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
+                \\
+                y_{t + 1} &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t). 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            To do, we show that updates sequence $x_{t + 1} = z_{t + 1} + L\eta_t (z_{t + 1} - z_t)$ is equivalent to $x_{t + 1} = x_t + \tilde\eta_{t + 1}\nabla f(y_t)$. 
+            Starting with the former, susbtitute definition of $z_{t + 1}$, $z_{t + 1} = z_t + L^{-1}\nabla f(y_t)$ expanding: 
+            \begin{align*}
+                x_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t) 
+                + L \eta_t y_t - \eta_t \mathcal G_L(y_t) - L\eta_t z_t
+                \\
+                &= 
+                (1 + L\eta_t)y_t - (\eta_t + L^{-1})\mathcal G_L(y_t) - L\eta_t z_t
+                \\
+                &= \eta_t Lz_t + x_t -(\eta_t + L^{-1}) \mathcal G_L(y_t)  - L\eta_t z_t
+                \\
+                &= x_t - (\eta_t + L^{-1})\mathcal G_L(y_t). 
+            \end{align*}
+            So $x_{t + 1} = x_t + \tilde \eta_{t + 1}\mathcal G_L(y_t)$, by assumption $\tilde \eta_{t + 1} = \eta_t + L^{-1}$
+            Reducing it to the classic momentum form starts by 
+            \begin{align*}
+                y_{t + 1} &= (1 + L\eta_{t + 1})^{-1} (x_{t + 1} + L\eta_{t + 1}z_{t + 1})
+                \\
+                &= (1 + L\eta_{t + 1})^{-1} (
+                    z_{t + 1} + L\eta_t (z_{t + 1} - z_t) + L\eta_{t + 1} z_{t + 1}
+                )
+                \\
+                &= 
+                (1 + L\eta_{t + 1})^{-1} (
+                    (1 + L\eta_{t + 1})z_{t + 1} + L\eta_t(z_{t + 1} - z_t)
+                )
+                \\
+                &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t), 
+            \end{align*}
+            it negates the $x_t$ variables, therefore we have 
+            \begin{align*}
+                z_{t + 1} &= y_t - L^{-1} \mathcal G_L (y_t)
+                \\
+                y_{t + 1} &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t).
+            \end{align*}
+            This is FISTA by the relation $a_t = 1 + L\eta_t$, hence $(1 + L\eta_{t + 1})^{-1}L\eta_t$ is $(a_t - 1)/a_{t + 1}$.
+            Where we proved in 
+            \hyperref[thm:ag_generic_stepsize_constrants]
+                {theorem \ref*{thm:ag_generic_stepsize_constrants}}
+            that $a_t$ is the Nesterov momentum sequence. 
         \end{proof}
         \begin{remark}
-            In the original writing by Ahn \cite[equation (4.9)]{ahn_understanding_2022}, they didn't identify this specific variant in the literature. 
-            Here we identify it to be equivalent to the acceleration algorithm stated in Ryu \cite[algorithm 12.1]{ryu_large-scale_2022}. 
+            In this remark we clarify the name ``similar triangle" as given in the literatures. 
+            We think it is a fitting name, becaues it has a similar triangle in it. 
+            We list the following observations
+            \begin{enumerate}
+                \item 
+                The updates for $y_{t}$ from the algorithm has 
+                $$
+                    y_t = (1 + L\eta_t)^{-1} x_t + L\eta_t(1 + L\eta_t)^{-1} z_t, 
+                $$
+                therefore, $y_t$ is a convex combinations of $x_t, z_t$, so $z_t, y_t, x_t$ are three collinear points. 
+                We have the ratio $\Vert y_t - x_t\Vert/\Vert z_t - y_t\Vert = L\eta_t$. 
+                \item 
+                The updates for $z_{t + 1}, x_{t + 1}$ are based on $y_t, x_t$ displaced by $L^{-1} \mathcal G_L(y_t), \tilde\eta_{t +1} \mathcal G_L(y_t)$, therefore vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$.
+                \item The updates for $x_{t + 1}$ has $x_{t + 1} - z_{t + 1} = L\eta_t \left(z_{t + 1} - z_t\right)$, therefore, the three points $z_t, x_{t + 1}, z_{t + 1}$ are collinear. 
+                The ratio between line segment has $\Vert x_{t + 1} - z_{t + 1}\Vert/\Vert z_{t + 1} - z_t\Vert = L\eta_t$. 
+            \end{enumerate}
+            By these tree observations, the triangle $z_{t}, z_{t + 1}, y_t$ similar to triangle $z_t, x_{t + 1}, x_t$. 
+            Finally, similar remarks about the similar triangle form can be found in Ahn, Sra's paper \cite{ahn_understanding_2022} as well.
+
         \end{remark}
 
-    \subsection{Scenario II}\label{sec:scenario_ii}
-        With the choice of $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we can recover the seminal Nesterov accelerated gradient algorithm from 1983. 
-        The variants proposed by Chambolle Dossal \cite{chambolle_convergence_2015}, is distinct from the possibility proposed in this secenario.
-
-        \begin{lemma}[Deriving the Nesterov Sequence]
-            For all $t \in \mathbb N$
-            \begin{align*}
-                \left\lbrace
-                \begin{aligned}
-                    (1 + L\eta_{t + 1})^{-1}L \eta_t 
-                    &= \frac{a_t - 1}{a_{t + 1}} , 
-                    \\
-                    a_{t + 1}^2 - a_t &= a_t^2. 
-                \end{aligned} 
-                \right. 
-            \end{align*}
-            allows \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}} to converge at an optimal rate. 
-            The base case is $\eta_0 = 0$. 
-        \end{lemma}
-        \begin{proof}
-            Continue from 
-            \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]{lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}, 
-            With $x_{t +1} - x_t = L\tilde\eta_{t+1}(z_{t + 1} - y_t)$ for $y_t$: 
-            \begin{align*}
-                \Upsilon_{1, t + 1}^\text{AG} &\le 
-                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-                    + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                    - \langle 
-                        \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                        x_{t + 1} - z_{t + 1}
-                    \rangle
-                    \\
-                    &= 
-                    - \frac{1}{2}\Vert L \tilde \eta_{t+} (z_{t+1} - y_t)\Vert^2 + 
-                    \frac{\tilde\eta_{t +1}L}{2}\Vert z_{t+1} - y_t\Vert^2
-                    - \langle 
-                        \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                        x_{t + 1} - z_{t + 1}
-                    \rangle
-                    \\
-                    &= 
-                    \left(
-                        \frac{L^2\tilde\eta_{t + 1}^2}{2}
-                        + 
-                        \frac{\tilde \eta_{t +1}}{2}
-                    \right)
-                    \Vert z_{t+1} - y_t\Vert^2
-                    - 
-                    \langle 
-                        \tilde \eta_{t+ 1} \mathcal G_L(y_t), x_{t+1} - z_{t+1}
-                    \rangle. 
-            \end{align*}
-            This completes the analysis for $\Upsilon_{1, t + 1}^\text{AG}$ with $\tilde\eta_{t+1}$. 
-            Next we consider 
-            \begin{align*}
-                \Upsilon_{2, t + 1}^{\text{AG}} 
-                &= 
-                \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle
-                + 
-                \frac{L }{2} \Vert z_{t+1} - y_t\Vert^2
-                \\
-                &= 
-                \langle \mathcal G_L(y_t), L^{-1}\eta_t^{-1}(x_{t+1} - z_{t + 1})\rangle
-                + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-            \end{align*}
-            Here we used $x_{t + 1} = z_{t + 1} + L\eta_t (z_{t + 1} - z_t)$, which was the consequence of $\tilde\eta_{t + 1} = \eta_t + L^{-1}$, as discussed from before. 
-            Hence, the upper bound of the Lyapunov function for smooth AG PPM 
-            (\hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}) 
-            has 
-            {\footnotesize
-            \begin{align*}
-                & \Upsilon_{1, t + 1}^{\text{AG}} + 
-                \left(
-                    \sum_{i = 1}^{t}\tilde \eta_i
-                \right)\Upsilon_{2, t + 1}^{\text{AG}}
-                \\
-                &\quad \le 
-                \left(
-                    - \frac{L^2\tilde \eta_{t + 1}^2}{2}
-                    + \frac{\tilde\eta_{t+1}L}{2}
-                \right)
-                \Vert z_{t+1} - y_t\Vert^2
-                - 
-                \langle \tilde \eta_{t+1} \nabla f(y_t), x_{t+1} - z_{t + 1}\rangle
-                \\
-                & \qquad + 
-                \left(
-                    \sum_{i = 1}^{t}\tilde \eta_i
-                \right)\left(
-                    \langle \nabla f(y_t), L^{-1}\eta_t^{-1}(x_{t+1} - z_{t + 1})\rangle
-                    + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                \right)
-                \\
-                &= 
-                \frac{L}{2}
-                \left(
-                -\tilde\eta_{t + 1}^2 + \tilde\eta_{t + 1}
-                    + \sum_{i = 1}^{t}\tilde\eta_i
-                \right)\Vert z_{t + 1} - y_t\Vert^2
-                +
-                \left(
-                    L^{-1}\eta_t^{-1} 
-                    \left(
-                        \sum_{i = 1}^{t}\tilde \eta_i
-                    \right)
-                    -
-                    \tilde \eta_{t + 1}
-                \right)\langle \mathcal G_L (y_t), x_{t + 1} - z_{t + 1}\rangle
-            \end{align*}
-            }
-            If the above quantity less than or equal to zero, it will allow for convergence of the algorithm by 
-            \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}.
-            One sufficient condition is to have the coefficients for all the cross product terms to sum up to zero, and the squared normed term to sum up to a non-positive number for all $t \in \mathbb N$.
-            This gives relations 
-            \begin{align*}
-                - \frac{1}{2}\left(
-                    L^2 \tilde\eta_{t+1}^2 - \tilde\eta_{t+1}L 
-                \right) + 
-                \frac{L}{2}\left(
-                    \sum_{i = 1}^{t} \tilde \eta_i
-                \right) &\le 0
-                \\
-                - \left(
-                    L\tilde \eta_{t + 1}^2 
-                    - 
-                    \tilde\eta_{t + 1}
-                \right) + 
-                \sum_{i = 1}^{t}\tilde \eta_i 
-                &\le 0
-                \\
-                -L \tilde \eta_{t+1} + 
-                \sum_{i = 1}^{t + 1} \tilde \eta_i 
-                &\le 0
-                \\
-                \sum_{i = 1}^{t + 1}\tilde \eta_i 
-                &\le L \tilde \eta_{t + 1}^2, 
-            \end{align*}
-            and equations 
-            \begin{align*}
-                -\tilde \eta_{t + 1} + 
-                \left(
-                    \sum_{i = 1}^{t}\tilde \eta_i
-                \right)L^{-1}\eta_t^{-1} 
-                &= 0
-                \\
-                \sum_{i = 1}^{t}\tilde \eta_i 
-                &= 
-                L \eta_t \tilde \eta_{t + 1}. 
-            \end{align*}
-            Susbtituting the equality into the inequalites we have 
-            \begin{align*}
-                \tilde \eta_{t + 1} + \sum_{i = 1}^{t} \tilde \eta_i 
-                &\le L \tilde \eta_{t + 1}^2
-                \\
-                \tilde \eta_{t + 1} + L\eta_t \tilde \eta_{t + 1}
-                &\le L \tilde \eta_{t + 1}^2
-                \\
-                1 + L\eta_t &\le L \tilde\eta_{t + 1}. 
-            \end{align*}
-            The choice $\tilde \eta_{t + 1} = \eta_t + L^{-1}$ makes the inequality is an equality. 
-            Finally, to recover the momentum stepsizes for the classical Nesterov accelerated gradient, we consider relations 
-            \begin{align*}
-                L \sum_{i = 1}^{t + 1} \tilde \eta_i 
-                &= L \tilde \eta_{t + 1} + L \sum_{i = 1}^{t} \tilde \eta_i 
-                \\
-                &= 
-                L \tilde \eta_{t + 1} + L (L \eta_t \tilde \eta_{t + 1}) 
-                \\
-                &= L \tilde \eta_{t + 1} + L \eta_t (L \eta_t + 1)
-                \\
-                &= L (\eta_t + L^{-1}) + L\eta_t (L \eta_t + 1)
-                \\
-                &= (L\eta_t + 1)^2, 
-            \end{align*}
-            Simultanenously 
-            \begin{align*}
-                L \sum_{i = 1}^{t + 1} \tilde \eta_i 
-                &= L^2 \eta_{t + 1} \tilde \eta_{t + 1}
-                \\
-                &= L \eta_{t + 1}(1+ L \eta_{t + 1}), 
-            \end{align*}
-            Combining yields that 
-            \begin{align*}
-                (L\eta_t + 1)^2 
-                &= L\eta_{t + 1}(1 + L \eta_{t + 1})
-                \\
-                &= L\eta_{t + 1} + L^2 \eta_{t + 1}^2
-                \\
-                \iff 
-                (L\eta_t + 1)^2 + 1/4 &= 
-                1/4 + 2(1/2)L \eta_{t + 1} + (L \eta_{t + 1})^2
-                \\
-                \iff 
-                (L\eta_t + 1)^2 + 1/4 &= 
-                (L \eta_{t + 1} + 1/2)^2. 
-            \end{align*}
-            With $a_t = L\eta_t + 1 = L \tilde \eta_t$ this is 
-            \begin{align*}
-                a_t^2 + 1/4 &= (a_{t + 1} - 1/2)^2 
-                \\
-                a_t^2 + 1/4 &= a_{t + 1}^2 + 1/4 - a_{t + 1}
-                \\
-                a_t^2 + a_{t + 1} &= a_{t + 1}^2. 
-                \\
-                \implies 
-                a_{t + 1} &= 
-                \frac{1 + \sqrt{1 + 4a_t^2}}{2}
-            \end{align*}
-            And that is the updates for the Nesterov momentum, recall that the momentum term is linked to the PPM sequence via relation 
-            \begin{align*}
-                (1 + L \eta_{t+ 1})^{-1}L\eta_t = L\eta_t / a_{t + 1} = (a_t - 1)/a_{t + 1}. 
-            \end{align*}
-            We had recovered the classic Nesterov acceleration sequence method for the smooth gradient descent algorithm. 
-        \end{proof}
-        \begin{remark}
-            This variant is distinct from the variants proposed by Chambolle \cite{chambolle_convergence_2015}, but both of which fits into the same frameworks. 
-            The variantis presented as 
-            \begin{align*}
-                y_n &= (1 - t_n^{-1})z_n + t_n^{-1} x_n
-                \\
-                z_{n + 1} &= y_n - L^{-1}\nabla f(y_n)
-                \\
-                x_{n + 1} &= z_n + t_{n + 1}(z_{n + 1} - z_n)
-            \end{align*}
-            They listed the choice of $t_n = (n + a - 1)/a$ for all $a > 2$. 
-            Under this choice, unfortunately, it's in no way obvious that this format reduces to \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
-            It fails the similar triangle description Without the explict representation $x_{n + 1} = z_n + \tilde\eta_{t + 1}\nabla f(y_t)$. 
-            \par\noindent
-            At the time of writing, we are still investigating the relations between these variants of algorithms.
-        \end{remark}
-
-    \subsection{Scenario III}
-
-\section{Classical analysis of Nesterov accelerated gradient}
-    In this section, we reproduce some of the analysis for Nesterov accelerated gradient method with excruciating details, in the appendix. 
-    We will introduce the method of estimating sequence invented by Nesterov. 
-    We will also go over some details about the history, development and motivations behind the accelerated gradient algorithm. 
-    \subsection{Method of Nesterov's estimating sequence}
-        In this section we introduce the method of estimating sequence.
-
-    \subsubsection{The estimating sequence and function}
-        \begin{definition}[Nesterov's Estimating Functions]
-            Define  $\{\phi_t\}_{t\in \mathbb N}$ to be a sequence of function where it recursively satisfies for all $k\in \mathbb N$: 
-            \begin{align*}
-                \phi_{k} (x) - f(x) \le 
-                (1 - \alpha_k)(\phi_k(x) - f(x)) \quad \forall x 
-            \end{align*}
-            Where $\alpha \in [0, 1)$. 
-        \end{definition}
-        \begin{observation}
-            Expands recursively we have 
-            \begin{align*}
-                \phi_{k}(x) - f(x) &\le 
-                \left(
-                    \prod_{i = 0}^{k} 
-                    (1 - \alpha_i)
-                \right)(\phi_0(x) - f(x)). 
-            \end{align*}
-        \end{observation}
-        So it motivates the definition of a sequence: $\lambda_k = \prod_{i=0}^k(1 - \alpha_i)$.
-
-        \begin{definition}[The estimating Sequence]
-            Continue from the above definition of a estimating functions, we consider a sequence $\{x_k\}$ satisfying 
-            \begin{align*}
-                f(x_k) &\le \phi_k^* := \min_z(\phi_k(z)). 
-            \end{align*}
-        \end{definition}
-
-        \begin{lemma}[The Lyapunov function from estimating sequence and function]
-            \;\\
-            Assume that $f$ bounded below with $f_* = \min_x f(x)$ and there exists minimizer $x_*$. 
-            With $\phi_k$ being an estimating functions and convex, $\{x_k\}$ an estimating sequence for $\phi_k$, then it satisfies
-            \begin{align*}
-                f(x_k) - f_*
-                &\le 
-                \lambda_k(\phi_0(x_*) - f_*). 
-            \end{align*}
-            for all $k\in \mathbb N\cup \{0\}$. 
-        \end{lemma}
-        \begin{proof}
-            Directly by the property of estimating sequence $x_k$, we have for all $k, x$
-            \begin{align*}
-                \phi_k(x) - f(x) \ge \phi_k^* - f(x) \ge f(x_k) - f(x), 
-            \end{align*}
-            so 
-            \begin{align*}
-                f(x_k) - f(x) \le \lambda_k (\phi_0(x) - f(x))
-                \\
-                \implies 
-                f(x_k) - f_* \le \lambda_k (\phi_0(x_*) - f(x_*)). 
-            \end{align*}
-            This establishes the convergence rate of $f(x_k)$ assuming that $\lambda_k$ is sequence that converges to zero. 
-        \end{proof}
-    \subsection{Construction of the estimating sequence and function}
-        The construction of the Nesterov estimating sequence and function is where most creativities are involved. 
-        For convex $f$ that is differentiable with $L$-Lipschitz gradient and strong convexity constant $\mu \ge 0$, Nesterov suggested in his book \cite{nesterov_lectures_2018} that there exists sequence $y_k$, $\gamma_k$, where
-        \begin{align*}
-            l_f(x, y_k) &= 
-            f(y_k) + \langle \nabla f(y_k), x - y_k\rangle + 
-            \frac{\mu}{2}\Vert x - y_k\Vert^2
-            \\
-            \phi_0 (x) &= 
-            f(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2
-            \\
-            \phi_{k + 1}(x) &= 
-            (1 - \alpha_k)\phi_k(x) + \alpha_k l_f(x; y_k)
-            \\
-            &= \phi_{k + 1}^2 + \frac{\gamma_k}{2}\Vert x - v_{k + 1}\Vert^2
-        \end{align*}
-        will verify as a Nesterov's estimating sequence and functions. 
-        The derivation for the parameters: $\gamma_k, x_k, y_k$ for $k \in \mathbb N \cup \{0\}$, will produce the Nesterov acclerated gradient as presented in
-        \hyperref[def:Nes2.2.7]{definition \ref*{def:Nes2.2.7}}
-        if correctly conducted. 
-        In this case, $\phi_k$ are simple quadratic centered $v_k$ with value $\phi_k$ with curvature $\gamma_k$. 
-        \par
-        However, the construction exhibits variations for different variants of the accelerated gradient algorithm. 
-        A different construction of $\phi_k$ yield a different algorithm. 
-        As shown in Nesterov's book \cite*[(2.2.63)]{nesterov_lectures_2018}, a projected gradient variant of the accelerated gradient method make use of the following estimating functions, sequence: 
-        \begin{align*}
-            \phi_0 (x) &= f(x_0) + \frac{\gamma_0}{2}\Vert x - x_0\Vert^2
-            \\
-            l_f(x; y_k) &= f(\mathcal T_ly_k) + 
-            \frac{1}{2L}\Vert \mathcal G_L(y_k)\Vert^2 + 
-            \langle \mathcal G_L(y_k), x - y_k\rangle + 
-            \frac{\mu}{2}\Vert x - y_k\Vert^2
-            \\
-            \phi_{k + 1}(x) &= 
-            (1 - \alpha_k)\phi_k + 
-            \alpha_k l_f(x; y_k), 
-        \end{align*}
-        Here, $G_L(x) = L(x - \mathcal T_L(x))$ and $T_L(x) = \Pi_Q(x - L^{-1}\nabla f(x))$, where $Q$ is a convex set. 
-        It's equivalent to applying proximal gradient method with $h = f + g$ where $g = \delta_Q$.
-
-\section{Modern techniques in analysis of accelerated gradient algorithms}
+    \subsection{Recovering the accelerated gradient variant appeared in Ryu's Book}
+    \subsection{Recovering Chambolle, Dossal 2015}
+
+\section{Algorithmic Improvements}\label{sec:algorithm_improved}
+    In this section, we state a new variant of the accelerated gradient algorithm using the PPM interpretation to algorithmically conduct a line search routine for $L, \mu \ge 0$ the Lipschitz constant and strong convexity index of the smooth part of the objective function.
+    This variant will be parameter free while still retaining the optimal convergence rate for all convex functions.
+
+\section{Numerical Experiments}\label{sec:numerical_experiments}
+
+\appendix
 
 \printbibliography
-
-\appendix
-\section*{Postponed Proofs}
-
 \end{document}

### 2024-08-08 Notebook LaTEX/Momentum Accelerations/sections/ag_ppm.tex
>w<, big updates

--- 2024-08-05 Notebook LaTEX/Momentum Accelerations/main.tex
@@
-\documentclass[12pt]{article}
-
-% \input{presets/wang_full.tex}
-\input{presets/wang/input.tex}
-\input{presets/misc.tex}
-\input{presets/julia_lstlisting.tex}
-
-\begin{document}
-
-\title{{\fontfamily{ptm}\selectfont Nesterov Type Momentum Methods}}
-
-\author{
-    The Alto Hivemind (My Pen name)
-    \thanks{
-        Subject type, Some Department of Some University, Location of the University,
-        Country. E-mail: \texttt{author.name@university.edu}.
-    }
-}
-
-\date{\today}
-
-\maketitle
-
-% \vskip 8mm
-
-\begin{abstract} 
-    \noindent
-    These are notes for Nesterov Type Acceleration Methods in the convex case. 
-    They can be made into papers, proposals, and a thesis in the future. 
-    They are tayped in \LaTeX\; so it's easier to work with. 
-\end{abstract}
-\noindent{\bfseries 2010 Mathematics Subject Classification:}
-Primary 47H05, 52A41, 90C25; Secondary 15A09, 26A51, 26B25, 26E60, 47H09, 47A63.
-\noindent{\bfseries Keywords:}
-
-\pagebreak
-\tableofcontents
-\pagebreak
-% ==============================================================================
-\section{Preliminaries}
-    This section lists foundational results important for proof in the coming sections. 
-    For this section, let the ambient space be $\RR^n$ and $\Vert \cdot\Vert$ be the 2-norm until specified in the context. 
-    For a general overview of smoothness and strong convexity in the Euclidean space, see \cite[theorem 2.1.5, theorem 2.1.10]{nesterov_lectures_2018} for a full exposition of the topic. 
-    \par\noindent
-    We assume the reader is well-versed in convex optimization and convex analysis. 
-    \subsection{Lipschitz smoothness}
-        \begin{definition}[Lipschitz Smooth]
-            Let $f$ be differentiable. 
-            It has Lipschitz smoothness with constant $L$ if for all $x, y$
-            $$
-                \Vert \nabla f(x) - \nabla f(y)\Vert 
-                \le 
-                L \Vert x - y\Vert. 
-            $$    
-        \end{definition}
-
-        \begin{theorem}[Lipschitz Smoothness Equivalence]
-            With $f$ convex and $L$-Lipschitz smooth, the following conditions are equivalent conditions for all $x, y$: 
-            \begin{enumerate}
-                \item $L^{-1}\Vert \nabla f(y) - \nabla f(x)\Vert^2 \le \langle \nabla f(y) - \nabla f(x), y - x\rangle \le L\Vert y - x\Vert^2$. 
-                \item $x^+\in \argmin_x f(x) \implies \frac{1}{2L}\Vert \nabla f(x)\Vert^2 \le f(x) - f(x^+) \le (L/2) \Vert x - x^+\Vert^2$, co-coersiveness. 
-                \item $ 1/(2L)\Vert \nabla f(x) - \nabla f(y)\Vert^2 \le  f(y) - f(x) - \langle \nabla f(x), y -x\rangle \le (L/2)\Vert x - y\Vert^2$
-            \end{enumerate}    
-        \end{theorem}
-        \begin{remark}
-            Lipschitz smoothness of the gradient of a convex function is an example of a firmly nonexpansive operator.  
-        \end{remark}
-
-        \begin{definition}[Strong Convexity]
-            With $f: \RR^n \mapsto \overline \RR$, it is strongly convex with constant $\alpha$ if and only if $f - (\alpha/2)\Vert \cdot\Vert^2$ is a convex function. 
-        \end{definition}
-
-        \begin{theorem}[Stong convexity equivalences]\label{thm:str_cvx_equiv}
-            With $f:\RR^n \mapsto \overline \RR$ $\alpha$-strongly convex, the following conditions are equivalent conditions for all $x, y$: 
-            \begin{enumerate}
-                \item $f(y) - f(x) - \langle \partial f(x),y - x \rangle\ge \frac{\alpha}{2}\Vert y - x\Vert^2$
-                \item $\langle \partial f(y) - \partial f(x), y - x\rangle \ge \alpha\Vert y - x\Vert^2$. 
-                \item $f(\lambda x + (1 - \lambda)y) \le \lambda f(x) + (1 - \lambda)f(y) -\alpha\frac{\lambda(1 - \lambda)}{2}\Vert y - x\Vert^2, \forall \lambda \in [0, 1]$. 
-            \end{enumerate}
-        \end{theorem}
-
-        \begin{theorem}[Strong convexity implications]\label{thm:str_cvx_implied}
-            With $f:\RR^n \mapsto \overline \RR$ $\alpha$-strongly convex, the following conditions are implied: 
-            \begin{enumerate}
-                \item $\frac{1}{2}\operatorname{dist}(\mathbf 0; \partial f(x))^2 \ge \alpha (f(x) - f^+)$ where $f^+$ is a minimum of the function, and this is called the Polyak-Lojasiewicz (PL) inequality.
-                \item $\forall x, y\in \mathbb E, u\in \partial f(x), v\in \partial f(y): \Vert u - v\Vert\ge \alpha\Vert x - y\Vert$. 
-                \item $f(y) \le f(x) + \langle \partial f(x), y - x\rangle + \frac{1}{2\alpha}\Vert u - v\Vert^2, \forall u\in  \partial f(x), v\in \partial f(y)$. 
-                \item $\langle \partial f(x)-\partial f(y), x - y\rangle \le \frac{1}{\alpha}\Vert u - v\Vert^2, \forall u\in \partial f(x), v\in \partial f(y)$. 
-                \item if $x^+\in \arg\min_{x}f(x)$ then $f(x) - f(x^+) \ge \frac{\alpha}{2}\Vert x - x^+\Vert^2$ and $x^+$ is a unique minimizer. 
-            \end{enumerate}
-        \end{theorem}
-        \begin{remark}
-            In operator theory, the subgradient of a strongly convex function is an example of a Strongly Monotone Operator. 
-        \end{remark}
-
-    \subsection{Proximal descent inequality}
-        The proximal descent inequality below is a crucial piece of inequality for deriving the behaviours of algorithms. 
-        \begin{theorem}[Proximal Descent Inequality]\label{thm:ppm_descent_ineq}
-            With $f: \RR^n \mapsto \overline \RR^n$ $\beta$-convex where $\beta \ge 0$, fix any $x \in \RR^n$, let $p = \hprox_f(x)$, then for all $y$ we have inequality 
-            $$
-                \left(f(p) + \frac{1}{2}\Vert x - p\Vert^2\right)
-                - 
-                \left(
-                    f(y) + \frac{1}{2}\Vert x - y\Vert^2 
-                \right)
-                \le 
-                - \frac{(1 + \beta)}{2}\Vert y - p\Vert^2. 
-            $$
-            Recall: $\hprox_f(x) = \argmin_{u}\left\lbrace f(u) + \frac{1}{2}\Vert u - x\Vert^2 \right\rbrace$. 
-        \end{theorem}
-        \begin{remark}
-            We use this theorem to prove the convergence of the proximal point method. 
-            See the proof (\cite{bauschke_convex_2017}, theorem 12.26). 
-            The additional strong convexity index is a consequence of \hyperref[thm:str_cvx_implied]{theorem \ref*{thm:str_cvx_implied}}, item (v). 
-        \end{remark}
-
-        \begin{theorem}[The Bregman proximal descent inequality]\label{thm:ppm_breg_descent_ineq}
-            Let $\omega$ induce a Bregman Divergence $D_\omega$ in $\RR^n$ and assume that it satisfies Bregman Prox Admissibility conditions for the function $\varphi: \RR^n \mapsto \overline \RR$.
-            Then we claim that for all $c \in \text{dom}(\omega), b \in \text{dom}(\partial \omega)$, 
-            If 
-            \begin{align*}
-                a = \argmin_{x}\left\lbrace
-                \varphi(x) + D_\omega(x, b)
-                \right\rbrace, 
-            \end{align*}
-            we have the inequality, 
-            \begin{align*}
-                (\varphi(c) + D_\omega(c, b)) - 
-                (\varphi(a) + D_\omega(a, b)) \ge 
-                D_\omega(c, a). 
-            \end{align*}
-        \end{theorem}
-        \begin{remark}
-            For more information about what function $\omega$ can induce a Bregman divergence and the admissibility conditions for Bremgna proximal mapping, consult Heinz et.al \cite{bauschke_descent_2017}.
-        \end{remark}
-
-\section{The proximal point method with convexity}
-    This section reviews the convex case's Proximal point method (PPM) analysis and generalizes the theories to approximated PPM. 
-    \subsection{Convex PPM literature reviews}
-        Rockafellar \cite{rockafellar_monotone_1976} pioneered the analysis of the proximal point method in the convex case. 
-        He developed the analysis in the context of maximal monotone operators in Hilbert spaces. 
-        Applications in convex optimizations are covered. 
-        Using his theorems appropriately requires some opportunities, realizations, and characterizations of assumptions (A), (B) in his paper in the context of the applications. 
-        \par\noindent
-        In this section, we will use the result from Rockafellar that, if a monotone operator $A$ is $\beta$ strongly convex, then the resolvent operator $\mathcal J_A = [I + A]^{-1}$ is a $(1 + \beta)^{-1}$ Lipschitz operator, making $I - \mathcal J_A$ is a $1 - (1 + \beta)^{-1}$ a strongly monotone operator.
-
-    \subsection{The proximal point method}
-        With $f: \RR^n \mapsto \overline \RR$ lsc proper and convex, given any $x_0$ the PPM generates sequence $(x_n)_{n\in \NN}$ by $x_{k + 1} = \hprox_{\eta_{k + 1}}f(x_k)$ for all $k \in \NN$ where the sequence $(\eta_{k})_{k \in \NN}$ is a nonegative sequence of real numbers.
-
-    \subsection{The Lyapunov function of convex PPM}
-        We present some theorems that illustrate the use of \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}}. 
-        The readers can find similar analyses and techniques in Guler's work \cite{guler_convergence_1991}. 
-        \begin{theorem}[PPM Lyapunov Function]\label{ppm_lyapunov}
-            With $f$ being $\beta\ge 0$ convex (it's strongly convex if $\beta > 0$, else it's just convex) and $x_{t + 1} = \hprox_{\eta_{t + 1}f}$ generated by PPM. 
-            Define the Lyapunov function $\Phi_t$ for all $u \in \RR^n$: 
-            \begin{align*}
-                \Phi_t &:= 
-                \left(
-                    \sum_{i = 1}^{t} \eta_i
-                \right)(f(x_t) - f(u)) + \frac{1}{2} \Vert u - x_t\Vert^2 \quad \forall t \ge 1, 
-                \\
-                \Phi_0 &:= (1/2)\Vert x_0 - u\Vert^2, 
-            \end{align*}
-            then it is a Lyapunov function for the PPM algorithm. 
-            Meaning for all $(x_k)_{k \in \NN}$ generated by PPM, it satisfies that $\Phi_{t + 1} - \Phi_t \le 0$. 
-            Additionally, by definition, we have 
-            {\small
-                \begin{align*}
-                    \Phi_{t + 1} - \Phi_{t} 
-                    &= 
-                    \left(\sum_{i = 1}^{t}\eta_{i}\right)
-                    (f(x_{t + 1}) - f(x_t)) 
-                    + \frac{1}{2}\Vert x_{t + 1} - u\Vert^2 
-                    - \frac{1}{2}\Vert x_{t} - u\Vert^2
-                    +
-                    \eta_{t + 1}(f(x_{t + 1}) - f(u))
-                    \\
-                    & \le 
-                    -\left(\sum_{i = 1}^{t}\eta_{i}\right)
-                    (1 + \beta\eta_{t + 1}/2)\Vert x_{t + 1} - x_t\Vert^2
-                    + 
-                    \left(
-                        - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
-                        -\frac{\beta\eta_{t + 1}}{2}\Vert u - x_{t + 1}\Vert^2
-                    \right)
-                    \\
-                    & \le 0,
-                \end{align*}
-            }
-            And additionally, recovering the descent lemma: 
-            \begin{align*}
-                f(x_{t + 1}) - f(x_t) 
-                &\le
-                -\frac{1}{\eta_{t+1}} \Vert x_{t + 1} - x_t\Vert^2 
-                - \frac{\beta}{2}\Vert x_t - x_{t + 1}\Vert^2. 
-            \end{align*}
-        \end{theorem}
-        \begin{proof}
-            Let $\phi_{t + 1}: \RR^n \mapsto \overline \RR = \eta_{t + 1} f$ be convex,  consider proximal point method $x_{t + 1} = \hprox_{\phi}(x_t)$, apply \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}}, we have $\forall u \in \RR^n$
-            \begin{align*}
-                & \phi_{t + 1}(x_{t + 1}) 
-                + 
-                \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
-                - \phi_{t + 1}(u) - \frac{1}{2}\Vert u - x_t\Vert^2
-                \le 
-                - 
-                \frac{1}{2}(1 + \beta\eta_{t + 1})\Vert 
-                    u - x_{t + 1}
-                \Vert^2
-                \\
-                & \text{let } u = x_*
-                \\
-                &\quad 
-                \begin{aligned}
-                    \implies &
-                    \eta_{t + 1}(f(x_{t + 1}) - f(x_*)) 
-                    + 
-                    \frac{1}{2}\Vert x_* - x_{t + 1}\Vert^2 
-                    +  
-                    \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
-                    -
-                    \frac{1}{2}\Vert x_* - x_t\Vert^2 
-                    \\
-                    & \quad \le 
-                    -\frac{\beta\eta_{t + 1}}{2}\Vert x_* - x_{t + 1}\Vert^2
-                    \\
-                    \iff & 
-                    \eta_{t + 1}(f(x_{t + 1}) - f(x_*)) 
-                    + 
-                    \frac{1}{2}\Vert x_* - x_{t + 1}\Vert^2 
-                    -
-                    \frac{1}{2}\Vert x_* - x_t\Vert^2 
-                    \\
-                    & \quad \le 
-                    - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
-                    -\frac{\beta\eta_{t + 1}}{2}\Vert x_* - x_{t + 1}\Vert^2
-                    \le 0. 
-                \end{aligned}
-                \\
-                & \text{let } u = x_{t}
-                \\
-                &\quad  
-                \begin{aligned}
-                    \implies& 
-                    f(x_{t + 1}) - f(x_t)
-                    \le 
-                    -\frac{1}{\eta_{t+1}} \Vert x_{t + 1} - x_t\Vert^2 
-                    - \frac{\beta}{2}\Vert x_t - x_{t + 1}\Vert^2
-                    \le 0. 
-                \end{aligned}
-            \end{align*}
-            Let's define the following quantities for all $u, \beta\ge 0$: 
-            \begin{align*}
-                \Upsilon_{1, t + 1}(u) &= 
-                \eta_{t + 1}(f(x_{t + 1}) - f(u)) + \frac{1}{2}(
-                    \Vert x_{t + 1} - u\Vert^2 - 
-                    \Vert x_t - u\Vert^2
-                )
-                \\
-                & \le 
-                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
-                -\frac{\beta\eta_{t + 1}}{2}\Vert u - x_{t + 1}\Vert^2, 
-                \\
-                \Upsilon_{2, t + 1}
-                &= 
-                \eta_{t + 1}(f(x_{t + 1}) - f(x_t))
-                \\
-                &\le 
-                - \Vert x_{t + 1} - x_t\Vert^2 - 
-                \frac{\beta\eta_{t + 1}}{2}
-                \Vert x_{t + 1} - x_t\Vert^2 
-                \\
-                &= 
-                -(1 + \beta\eta_{t + 1}/2)\Vert x_{t + 1} - x_t\Vert^2 \le 0. 
-            \end{align*}
-            With $\Phi_t$ as defined in the theorem, observe the following demonstration for all $u$, $\beta \ge 0$: 
-            {\small
-            \begin{align*}
-                \Phi_{t + 1} - \Phi_{t}
-                &= 
-                \left(
-                    \sum_{i = 1}^{t + 1}\eta_i
-                \right)(f(x_{t + 1}) - f(u)) + 
-                \frac{1}{2}\Vert x_{t + 1} - u\Vert^2 
-                - 
-                \left(
-                    \sum_{i = 1}^{t}\eta_i
-                \right)(f(x_{t}) - f(u))
-                - 
-                \frac{1}{2}\Vert x_{t} - u\Vert^2
-                \\
-                &= 
-                \left(\sum_{i = 1}^{t}\eta_{i}\right)
-                (f(x_{t + 1}) - f(x_t)) 
-                + \frac{1}{2}\Vert x_{t + 1} - u\Vert^2 
-                - \frac{1}{2}\Vert x_{t} - u\Vert^2
-                +
-                \eta_{t + 1}(f(x_{t + 1}) - f(u))
-                \\
-                &= 
-                \left(\sum_{i = 1}^{t}\eta_{i}\right)\Upsilon_{2, t + 1}
-                + \Upsilon_{1, t + 1}(u)
-                \\
-                &\le 
-                -\left(\sum_{i = 1}^{t}\eta_{i}\right)
-                (1 + \beta\eta_{t + 1}/2)\Vert x_{t + 1} - x_t\Vert^2
-                + 
-                \left(
-                    - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2
-                    -\frac{\beta\eta_{t + 1}}{2}\Vert u - x_{t + 1}\Vert^2
-                \right)
-                \le 0. 
-            \end{align*}
-            }
-            Therefore, $\Phi_t$ is a legitimate Lyapunov function for all $u, \beta \ge 0$. 
-        \end{proof}
-        \begin{remark}
-            The above Lyapunov is not unique, and it's not optimal for $\beta > 0$, strictly strongly convex functions.
-
-        \end{remark}
-
-        \begin{theorem}[Convergence Rate of PPM]\label{thm:ppm_convergence_rate}
-            The convergence rate of PPM applied to $f$, closed, convex proper, we have the convergence rate of the function value: 
-            $$
-            f(x_T) - f(x_*) \le O\left(\left(\sum_{i=1}^{T}\eta_t\right)^{-1}\right). 
-            $$
-            Where $x_*$ is the minimizer of $f$. 
-        \end{theorem}
-        \begin{proof}
-            With $\Delta_t = f(x_t) - f(x_*), \Upsilon_t = \sum_{i = 1}^{t}\eta_i$ so $\Phi_t = \Upsilon_t\Delta_t + \frac{1}{2}\Vert x_t - x_*\Vert^2$ by consideration $u = x_*$, invoking previous theorem and do
-            \begin{align*}
-                \Upsilon_T\Delta_T \le \Phi_T 
-                &\le 
-                \Phi_0 = \frac{1}{2}\Vert x_0 - x_*\Vert^2 
-                \\
-                \implies \Delta_T 
-                &\le 
-                \frac{1}{2\Upsilon_T} \Vert x_0 - x_*\Vert^2. 
-            \end{align*}
-        \end{proof}
-        \begin{remark}
-            With the same choice of the sequence $(\eta_t)_{t \in \NN}$, convergence of the PPM method of a strongly convex function is faster. 
-            The above proof is the same for $\beta = 0$, or $\beta > 0$, because it didn't use the property that $\eta_{t + 1}f$ is a $\eta_{t + 1}\beta$ strongly convex function. 
-        \end{remark}
-
-        \begin{theorem}[PPM Strongly Convex Lyapunov Function]\label{ppm_lyapunov_scvx}
-            With $f$ being $\beta > 0$ strogly convex, with $x_{t + 1} = \hprox_{\eta_{t + 1}f}(x_t)$, then $\Phi_t = \Vert x_{t} - x_*\Vert$ is a Lyapunov function satisfying: 
-            \begin{align*}
-                \frac{\Vert x_{t + 1} - x_*\Vert}{
-                    \Vert x_k - x_*\Vert
-                } &\le (1 + \eta_{t + 1}\beta)^{-1}. 
-            \end{align*}
-        \end{theorem}
-        \begin{proof}
-            This is a direct application that $\hprox_{\eta_{t + 1}f}$ is a contraction with constant $(1 + \beta\eta_{t +1})^{-1}$. 
-        \end{proof}
-        \begin{remark}
-            It's still a mystery on how to show $f(x_t) - f(x_*)$ is a Lyapunov function. 
-            The answer is not realized by us, nor it is in Rockafellar \cite{rockafellar_monotone_1976} or Guler's\cite{guler_convergence_1991} writings. 
-            Do observe that, by the choice of $x_*$, the contraction property of the proximal operator is strictly stronger than necessary. 
-            This inequality at the end is tighter than what we derived for gradient descent. 
-        \end{remark}
-
-\section{Applying the analysis of PPM}
-    The PPM method and the Lyaounov function derived above serve as the template for other algorithms. 
-    As an appetizer, we present an analysis of gradient descent using theorems related to the convergence of PPM
-    \par\noindent
-    In optimizations, people use a lower or an upper approximation of the objective function to approximate the PPM. 
-    The methodology includes a diverse range of approaches.
-    For example, it includes first-order optimization, such as gradient descents, and second-order algorithms, such as Newton's method. 
-    Its scope broadens to primal-dual optimization algorithms with creativities in the Lyapunov functions or theories in monotone operators. 
-    \par\noindent
-    To demonstrate, assume that $f$ is a lsc convex function such that it can be approximated by a lower bounding function $l_f(x|\bar x)$ at $\bar x$ such that it satisfies for all $x$: 
-    \begin{align*}
-        l_f(x| \bar x) 
-        \le f(x) \le l_f(x|\bar x) + \frac{L}{2}\Vert x - \bar x\Vert^2. 
-    \end{align*}
-    The above characterization is generic enough to include the case where $l_f(x|\bar x)$, the under-approximating function is nonsmooth. 
-    We assume that $l_f(x|\bar x)$ is convex for all $x$, at all $\bar x$, so the previous theorems apply. 
-    \par\noindent
-    The approximated proximal point method applies PPM to the function $l_f(x|x_t)$ for each iteration, i.e.: $x_{t +1} = \hprox_{\eta_{t + 1}l_f(\cdot | x_t)}(x_t)$. 
-    \subsection{Generic gradient descent}
-        We will consider deriving gradient descent via the PPM approach as a warm-up. 
-        Please pay attention to the remarks. They reveal parts of the proof that could inspire the idea of a non-monotone line search method in practical settings. 
-        \begin{theorem}[Generic Approximated PPM]\label{thm:lower_approx_ppm_convergence}
-            With $f$ convex having minimizer: $x_*$; $l_f(\cdot; x_t)$ convex, lsc and proper, define $\phi_t(x) = \eta_{t + 1}l_f(x; x_t)$. 
-            Assume the following estimates hold: 
-            $$
-            \phi_t(x) \le \eta_{t + 1}f(x) \le \phi_t(x) 
-            + 
-            \frac{L\eta_{t + 1}}{2}\Vert x - x_t\Vert^2 \quad \forall x \in \RR^n. 
-            $$ 
-            Fix any $x_0$, let the iterates $x_t$ defined for $t\in \NN$ satisfies
-            \begin{align*}
-                x_{t +1} = \argmin_{x} \left\lbrace
-                    l_f(x; x_t) + \frac{1}{2\eta_{t + 1}}\Vert x - x_t\Vert^2
-                \right\rbrace, 
-            \end{align*}
-            then it has 
-            \begin{align*}
-                \eta_{t + 1}(f(x_{t + 1}) - f(x_*)) + \frac{1}{2}\Vert x_* - x_{t + 1}\Vert^2
-                - \frac{1}{2}\Vert x_* - x_t\Vert^2
-                & \le 
-                \left(
-                    \frac{L \eta_{n + 1}}{2} - \frac{1}{2}
-                \right)\Vert x_{t + 1} - x_t\Vert^2.
-            \end{align*}
-            Additionally if $\exists \epsilon > 0: \eta_{t} \in (\epsilon, 2L^{-1} - \epsilon)$, for all $t \in \NN$, the algorithm has sublinear convergence rates of
-            \begin{align*}
-                f(x_T) - f(x_*)
-                &\le 
-                \frac{L - \epsilon^{-1}}{TL\epsilon} (f(x_0) - f(x_T)) 
-                \\
-                &\le 
-                \frac{L - \epsilon^{-1}}{TL\epsilon} (f(x_0) - f(x_*)) 
-            \end{align*}
-        \end{theorem}
-        \begin{proof}
-            By $\phi_t$ convex, apply \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} with $f = \phi_t$, $x = x_t$, $x_{t + 1} = p$, yielding $\forall y$
-            {\footnotesize
-                \begin{align*}
-                    \phi_t(x_{t + 1}) + \frac{1}{2}\Vert x_t - x_{t + 1}\Vert^2 
-                    - 
-                    \phi_t(y) - \frac{1}{2}\Vert x_t - y\Vert^2
-                    &\le 
-                    - \frac{1}{2}\Vert y - x_{t + 1}\Vert^2
-                    \\
-                    \phi_t(x_{t + 1}) - \phi_t(y)
-                    + \frac{1}{2}(
-                        \Vert y - x_{t + 1}\Vert^2 - \Vert x_t - y\Vert^2 
-                    ) &\le 
-                    - \frac{1}{2} \Vert x_t - x_{t + 1}\Vert^2
-                    \\
-                    \left(
-                        \phi_t(x_{t + 1}) + \frac{L\eta_{t + 1}}{2}\Vert x_{t + 1} - x_t\Vert
-                    \right)
-                    - \phi_t(y)
-                    + \frac{1}{2}(
-                        \Vert y - x_{t + 1}\Vert^2 - \Vert x_t - y\Vert^2 
-                    ) &\le 
-                    \left(
-                        \frac{L\eta_{t + 1}}{2}- \frac{1}{2}
-                    \right) \Vert x_t - x_{t + 1}\Vert^2
-                    \\
-                    \implies 
-                    \eta_{t + 1}f(x_{t + 1}) - \eta_{t + 1}f(y) 
-                    + \frac{1}{2}(
-                        \Vert y - x_{t + 1}\Vert^2 - \Vert x_t - y\Vert^2 
-                    ) 
-                    &\le 
-                    \left(
-                        \frac{L\eta_{t + 1}}{2}- \frac{1}{2}
-                    \right) \Vert x_t - x_{t + 1}\Vert^2. 
-                \end{align*}
-            }
-            Setting $y = x_t$ yields
-            \begin{align*}
-                \eta_{t + 1}(f(x_{t + 1}) - f(x_t)) + 
-                \frac{1}{2}
-                    \Vert x_t - x_{t + 1}\Vert^2
-                &\le 
-                \left(
-                        \frac{L\eta_{t + 1}}{2}- \frac{1}{2}
-                \right) \Vert x_t - x_{t + 1}\Vert^2
-                \\
-                \iff 
-                \eta_{t + 1}(f(x_{t + 1}) - f(x_t))
-                &\le 
-                \left(
-                        \frac{L\eta_{t + 1}}{2} - 1
-                \right) 
-                \Vert x_t - x_{t + 1}\Vert^2. 
-            \end{align*}
-            In a similar manner to the derivation of the Lyapunov function for PPM, we make for all $y$: 
-            \begin{align*}
-                \Upsilon_{1, t + 1}(y) &= 
-                \eta_{t + 1}(f(x_{t + 1}) - f(y)) + \frac{1}{2}(
-                    \Vert x_{t + 1} - y\Vert^2 - 
-                    \Vert x_t - y\Vert^2
-                )
-                \\
-                & \le 
-                \left(
-                    \frac{L\eta_{t + 1}}{2} - \frac{1}{2}
-                \right) \Vert x_t - x_{t + 1}\Vert^2, 
-                \\
-                \Upsilon_{2, t + 1}
-                &= 
-                \eta_{t + 1}(f(x_{t + 1}) - f(x_t))
-                \\
-                &\le 
-                \left(
-                    \frac{L\eta_{t + 1}}{2} - 1
-                \right) 
-                \Vert x_t - x_{t + 1}\Vert^2. 
-            \end{align*}
-            Now, consider defining $\Phi_t$ for all $y$: 
-            $$
-                \Phi_t = \left(
-                    \sum_{i = 1}^{t} \eta_{i}
-                \right)
-                (f(x_t) - f(y)) + \frac{1}{2}\Vert y - x_t\Vert^2, 
-            $$
-            it is the proposed Lyapunov function for PPM; we define the base case $\Phi_0 = \frac{1}{2}\Vert y - x_0\Vert^2$. 
-            Consider the difference $\forall y$: 
-            \begin{align*}
-                \Phi_{t + 1} - \Phi_t
-                &= 
-                \left(\sum_{i = 1}^{t}\eta_{i}\right)\Upsilon_{2, t + 1}
-                + \Upsilon_{1, t + 1}(y)
-                \\
-                &\le 
-                \left(\sum_{i = 1}^{t}\eta_{i}\right) 
-                \left(
-                    \frac{L\eta_{t + 1}}{2} - 1
-                \right) 
-                \Vert x_t - x_{t + 1}\Vert^2 + 
-                \left(
-                    \frac{L\eta_{t + 1}}{2}- \frac{1}{2}
-                \right) \Vert x_t - x_{t + 1}\Vert^2. 
-            \end{align*}
-            Observe that if $\eta_i \le L^{-1}$, then $\Phi_{t + 1} - \Phi_t \le 0$, hence the convergence rate of $\mathcal O\left((\sum_{i = 1}^{t}\eta_i)^{-1}\right)$ of PPM for $\Phi_t$ is applicable.
-            \par\noindent
-            Surprisingly, if $\eta_i \in (0, 2L^{-1})$, $\Phi_{t}$ still converges under mild conditions. 
-            For simplicity we set $\sigma_t := \sum_{i = 1}^{t}\eta_i$. 
-            It starts with considerations that $(L\eta_{t + 1}/2 - 1) < 0$, so that 
-            \begin{align*}
-                f(x_{t + 1}) - f(x_t) &\le 
-                \left(\frac{L\eta_{t + 1}}{2} - 1\right)\Vert x_{t + 1} - x_t\Vert^2
-                \\
-                f(x_T) - f(x_0)
-                &\le 
-                \underbrace{
-                \left(
-                    \frac{L\sigma_T}{2} - T
-                \right)
-                }_{< 0}
-                \sum_{t = 0}^{T - 1}\Vert x_{t + 1} - x_t\Vert^2
-                \\
-                \implies 
-                \sum_{t = 0}^{T -1}\Vert x_t - x_{t + 1}\Vert^2
-                &\le 
-                \left(
-                    \frac{L}{2}\sigma_T  - T
-                \right)^{-1} 
-                (f(x_T) - f(x_0))
-            \end{align*}
-            Continue on the RHS of $\Phi_{t + 1} - \Phi_t$ so 
-            \begin{align*}
-                \sum_{t = 0}^{T - 1}\Phi_{t + 1} - \Phi_t 
-                &\le 
-                \left(
-                    \frac{L}{2}\sigma_T - \frac{T}{2}
-                \right)\sum_{t = 0}^{T - 1}\Vert x_{t + 1} - x_t\Vert^2
-                \\
-                \Phi_T - \Phi_0 &\le 
-                \left(
-                    \frac{\frac{L}{2}\sigma_T - \frac{T}{2}}{
-                        \frac{L}{2}\sigma_T - T
-                    }
-                \right)
-                (f(x_T) - f(x_0))
-                \\
-                &= 
-                \left(
-                    \frac{L\sigma_T - T}{L\sigma_T - 2T}
-                \right)
-                (f(x_T) - f(x_0)), 
-            \end{align*}
-            implies
-            \begin{align*}
-                \sigma_T (f(x_T) - f(y)) + \frac{1}{2}\Vert y - x_t\Vert^2
-                - \frac{1}{2}\Vert y - x_0 \Vert^2 
-                &\le 
-                \left(
-                    \frac{L\sigma_T - T}{L\sigma_T - 2T}
-                \right)
-                (f(x_T) - f(x_0))
-                \\
-                \iff
-                f(x_T) - f(y) + 
-                \frac{1}{2\sigma_T}(\Vert y - x_t\Vert^2 - \Vert y - x_0\Vert^2)
-                &\le 
-                \left(
-                    \frac{L- T\sigma_T^{-1}}{2T - L\sigma_T}
-                \right)
-                (f(x_0) - f(x_T)), 
-            \end{align*}
-            therefore, we obtain the bound: 
-            \begin{align*}
-                f(x_T) - f(y) &\le 
-                \left(
-                    \frac{L- T\sigma_T^{-1}}{2T - L\sigma_T}
-                \right)
-                (f(x_0) - f(x_T))
-                - 
-                \frac{1}{2\sigma_T}(\Vert y - x_t\Vert^2 - \Vert y - x_0\Vert^2)
-            \end{align*}
-            In the case where $\sup_{i\in \NN} \eta_i \le 2L^{-1} - \epsilon$, and $\inf_{i\in \NN}\eta_i \ge \epsilon$ with $\epsilon > 0$. 
-            Then we have 
-            \begin{align*}
-                \frac{L -T\sigma_T^{-1}}{2T - L\sigma_T}
-                &\le 
-                \frac{L - \epsilon^{-1}}{2T - LT(2L^{-1} - \epsilon)}
-                \\
-                &= 
-                \frac{L - \epsilon^{-1}}{2T - T(2 - L\epsilon)}
-                \\
-                &= 
-                \frac{L - \epsilon^{-1}}{TL\epsilon}. 
-            \end{align*}
-            With $y = x_*$, we get the claimed convergence rate because $f(x_t)$ is strictly monotone decreasing. 
-        \end{proof}
-        \begin{remark}
-            Observe that inequality 
-            $$
-                \phi_t(x) \le \eta_{t + 1}f(x) \le \phi_t(x) 
-                + 
-                \frac{L\eta_{t + 1}}{2}\Vert x - x_t\Vert^2 \quad \forall x \in \RR^n, 
-            $$
-            was invoked with $x = x_{t + 1}$ for the PPM descent inequality in the above proof, meaning that if  $\forall (x_t)_{t \in \NN}$ generated by the algorithm, $\exists (L_t)_{t \in \NN}$ such that
-            $$
-                \phi_t(x) \le \eta_{t + 1}f(x) \le \phi_t(x) 
-                + 
-                \frac{L_t\eta_{t + 1}}{2}\Vert x - x_t\Vert^2,
-            $$
-            where the algorithm generates the sequence. 
-            By smartly choosing the function $\phi_{t + 1}$ at each iteration, we can increase the stepsize while retaining a similar convergence proof. 
-            In a practical setting, when $L_t = L$, and $\phi_{t}(x) = \eta_{t + 1}f$, this is called a line search.
-            \par\noindent
-            The convergence rate is loose, and when $f$ exhibits additional favourable properties, such as being strongly convex, the convergence rate can be faster. 
-            Furthermore, if the choice of $y$ remains arbitrary, then the theorem is applicable for function without minimizers. 
-        \end{remark}
-
-    \subsection{Examples}
-        \begin{example}[Convergence of the proximal gradient method]
-            This section \\ illustrates algorithms that satisfy the above proof's lower and upper bound estimates. 
-            Consider $f = g + h$ with $h$ nonsmooth convex, and $g$ being $L$-Lipschitz smooth convex and differentiable. 
-            Define $D_g(x, y) = g(x) - g(y) - \langle \nabla f(x), y - x\rangle$, $l_g(x; y) = g(y) + \langle \nabla g(y), y - x\rangle$, which is the Bregman divergence of the function $g$. 
-            Consider for all $x$: 
-            \begin{align*}
-                0 & \le 
-                D_g (x, y) \le  \frac{L}{2} \Vert x - y\Vert^2 
-                \\
-                l_g (x; y) &\le 
-                g(x) 
-                \le l_g(x; y) + \frac{L}{2} \Vert x - y\Vert^2 
-                \\
-                h(x) + l_g(x; y) &\le f(x) = g(x) + h(x)
-                \le 
-                l_g(x; y) + h(x) + \frac{L}{2}\Vert x - y\Vert^2. 
-            \end{align*}
-            Define $\phi_{t + 1} (x) = \eta_{t + 1}(h(x) + l_g(x; x_t))$, then results from previous theorems apply.    
-        \end{example}
-        \begin{remark}
-            The envelope interpretation restricts the use of the theorem since it requires that the proximal operator be a resolvent of a gradient. 
-            Extending the usage of the PPM descent inequality to other contexts requires operator theories and creativities. 
-        \end{remark}
-
-        \begin{example}[The fundamental proximal gradient lemma]
-            The fundamental proximal gradient lemma was used heavily in the literature to derive convergence results in the convex case. 
-            The "fundamental proximal gradient lemma" originates from Beck's writings \cite[theorem 10.16]{beck_first-order_nodate}. 
-            We demonstrate in this example that it's a consequence of \hyperref[thm:ppm_breg_descent_ineq]{theorem \ref*{thm:ppm_breg_descent_ineq}}. 
-            \par
-            With $f = g + h$, $h$ convex, lsc, $g$ be $L$-Lipschitz smooth, then for all $y\in \RR^n$, $x\in \RR^n$, $y^+ := \hprox_{L^{-1}h}(y - L^{-1}\nabla (y))$ satisfies: 
-            \begin{align*}
-                f(x) - f(y^+) \ge \frac{L}{2}\Vert x - y^+\Vert^2 - \frac{L}{2}\Vert x - y\Vert^2 + D_g(x, y).
-            \end{align*}
-            A similar analysis as \hyperref[thm:lower_approx_ppm_convergence]{ theorem \ref*{thm:lower_approx_ppm_convergence}} with \hyperref[thm:ppm_breg_descent_ineq]{theorem \ref*{thm:ppm_breg_descent_ineq}} obtains the same inquality.
-            With $\phi(y) = \eta(h(y) + g(x) + \langle \nabla g(x), y - x\rangle)$ as an lower bounding function of $f$. 
-            Choose any $x$, let $x^+ = \hprox_\phi(x)$, then for all $u$:
-            {\small
-            \begin{align*}
-                & \phi(u) + \frac{1}{2}\Vert u - x\Vert^2 - \phi(x^+) - \frac{1}{2}\Vert x^+ - x\Vert^2 
-                \ge \frac{1}{2}\Vert x^+ - u\Vert^2
-                \\
-                \implies &
-                \eta\underbrace{
-                    \left(
-                        h(u) + g(x) + \langle \nabla g(x), u - x\rangle 
-                    \right)
-                }_{= \phi(u)} 
-                - \eta \underbrace{f(x^+)}_{\le \phi(x^+)} - \frac{1}{2}\Vert x - x^+\Vert^2 
-                + \frac{1}{2} \Vert u - x\Vert^2 
-                \ge 
-                \frac{1}{2}\Vert x^+ - u\Vert^2 
-                \\
-                \iff & 
-                f(u) + \left(
-                    g(x) - g(u) + \langle \nabla g(x), u -x\rangle 
-                \right)
-                - f(x^+) - \frac{1}{2\eta}\Vert x - x^+\Vert^2
-                + 
-                \frac{1}{2}\Vert u - x\Vert^2 
-                \ge 
-                \frac{1}{2\eta}\Vert x^+ - u\Vert^2 
-                \\
-                \iff 
-                & f(u) - f(x^+) - D_g(u, x)
-                + \frac{1}{2\eta} \Vert u - x\Vert^2 - \frac{1}{2\eta}\Vert x^+ - x\Vert^2
-                \ge 
-                \frac{1}{2\eta} \Vert x^+ - u\Vert^2. 
-            \end{align*}
-            }
-            \par\noindent
-            Removing the negative term $-1/2\eta \Vert x - x^+\Vert^2$ makes LHS larger, establishing the fundamental proximal gradient lemma. 
-        \end{example}
-        \begin{remark}
-            Linking the PPM descent inequality to the Bregman divergence of the smooth part of the function on parameters $u, x$ is a clever move. 
-        \end{remark}
-
-\section{Accelerated gradient descent and PPM}
+\subsection{Introduction}
     Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
@@
     \hyperref[sec:generic_ag_ppm_lyapunov_analysis]{section \ref*{sec:generic_ag_ppm_lyapunov_analysis}},
-    we state two important theorems for the derivation of convergences rate for various type of algorithm using an upper bound of a Lyapunov function. 
+    we state two theorems for the derivation of convergences rate for various type of algorithm using an upper bound of a Lyapunov function. 
     This part is inspired by works from Ahn, Sra \cite{ahn_understanding_2022}, but with the gradient mapping and proximal gradient added into the picture, making it distinct from all algorithms discussed in Ahn and Sra's paper.
-    \hyperref[sec:scenario_i]{Section \ref*{sec:scenario_i}} and 
-    \hyperref[sec:scenario_ii]{\ref*{sec:scenario_ii}} derive the convergence rate and determine the parameters for the step sizes needed to achieve an optimal convergence rate. 
+    \hyperref[sec:generic_ag_ppm_lyapunov_analysis]
+        {Section \ref*{sec:generic_ag_ppm_lyapunov_analysis}} 
+    derives the convergence rate and determine the parameters for the step sizes needed to achieve an optimal convergence rate. 
     In each section, we recover a specific variant of the Accelerated gradient and identify their appearances in the literature.
@@
         Observe that the linearization $h(x^+) + \langle \mathcal G_L(x), z - x\rangle$ is anchored at $x^+$, instead of $x$. 
-            Geometrically, it's tilted and it "prefers" the sharp corners of a convex function, if, $x$ is close to a sharp corner. 
+        Geometrically, it's tilted and it ``prefers" the sharp corners of a convex function, if, $x$ is close to a sharp corner. 
     \end{remark}
@@
             Let $h=f + g$ be the sum of convex function $g$ and convex differentiable $f$ with $L$-Lipschitz gradient. 
-                Define the proximal gradient and gradient mapping operator operator: 
-                $$
-                \begin{aligned}
-                    \mathcal T_L^{g, f}(x) &:=  
-                    \hprox_{L^{-1}g}\left(x - L^{-1}\nabla f(x)\right)
-                    \\
-                    &= 
-                    \argmin_{u}
-                    \left\lbrace
-                        g(u) + f(x) + \langle \nabla f(x), u - x\rangle
-                        + 
-                        \frac{L}{2}\Vert u - x\Vert^2
-                    \right\rbrace,
-                    \\
-                    \mathcal G_L^{g, f}(x) &= 
-                    L\left(x - \mathcal T_L^{g, f}(x)\right). 
-                \end{aligned}
-                $$
-                Omitting the superscript $f, g$ on $\mathcal T, \mathcal G$ for simplicity since it's clear in the context. 
-                Define the linear lower bounding function for $f$ at $y$, for all $x$: 
+            With $\mathcal T_L, \mathcal G_L$ being the proximal gradient, and the gradient mapping operator. 
+            Define the linear lower bounding function for $h$ at $y$, for all $x$: 
             $$
@@
         \begin{definition}[AG Proximal Gradient Generic Form]
-            \label{def:ag_prox_grad_tri_pt}
+        \label{def:ag_prox_grad_generic}
             With $h = f + g$, where $g$ is convex, $f$ is convex and $L$-Lipschitz smooth. 
@@
 
-            \begin{definition}[Proximal Gradient Tri-Points Form E]
+        \begin{definition}[Proximal Gradient variant of Ryu 12.1]
         \label{def:ag_tri_pt_form_E}
-                Form E is a special case of 
-                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
-                with the condition that $\tilde \eta_t = \eta_t$ for all $t \in \mathbb N$. 
+            The method appeared in Ryu's text is a special case of 
+            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
+            with the condition that $\tilde \eta_t = \eta_t$ for all $t \in \mathbb N$ and $g \equiv 0$ for the non-smooth part of the objective. 
             As a consequence, the algorithm has the following updates for iterates $(y_t, x_{t + 1}, z_{t + 1})$: 
@@
         \label{def:ag_form_similar_tria_I}
+            The similar triangle form is equivalent to the classic nesterov accelerated gradient proposed back in 1983. 
             It updates iterates $(y_t, x_{t + 1}, z_{t + 1})$ using 
@@
         \begin{remark}
-                For more information about the specific choice of $\eta_t$ allows for an optimal convergence rates, see 
-                \hyperref[sec:scenario_ii]{section \ref*{sec:scenario_ii}} for more information. 
+            The above algorithm is a special case of 
+            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}, 
+            see 
+            \hyperref[thm:ag_generic_stepsize_constrants]{section \ref*{thm:ag_generic_stepsize_constrants}} 
+            for more information. 
         \end{remark}
@@
 
-            \begin{proposition}[Deriving Proximal Gradient Tri-Points Generic Form]
+        \begin{proposition}[Deriving Proximal Gradient Generic Form]
         \label{prop:derive_ag_prox_grad_tript}
@@
             is equivalent to 
-                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
+            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
         \end{proposition}
@@
                 &=
-                    \frac{(y_t - L^{-1}\mathcal G_L(y_t)) + x_{t + 1}}{L + \eta_{t + 1}^{-1}}.
+                \frac{
+                    \left(y_t - L^{-1}\mathcal G_L(y_t)\right) + x_{t + 1}
+                }{L + \eta_{t + 1}^{-1}}.
             \end{align*}
@@
             in 
-                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
+            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
             We can derive similar triangle form I as stated back in
@@
 \label{sec:generic_ag_ppm_lyapunov_analysis}
-        The first theorem states the generic convergence results when $f$ is differentiable with $L$-Lipschitz gradient, using \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}.
+    The lemma theorem states targets
+    \hyperref[prop:derive_ag_prox_grad_tript]
+    {definition \ref*{prop:derive_ag_prox_grad_tript}}.
 
@@
             \\
-                \Phi_0 &= \frac{1}{2}\Vert x_t - x_*\Vert^2, 
-            \end{align*}
-            we have $\Phi_{t + 1} - \Phi_t \le 0$, which allows for a convergence rate of $\mathcal O \left(\sum_{i = 1}^{T} \eta_i^{-1}\right)$ for $f(z_T) - f(x_*)$. 
+            \Phi_0 &= \frac{1}{2}\Vert x_0 - x_*\Vert^2, 
+        \end{align*}
+        if there is a choice of $\eta_i, \tilde \eta_i$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} such that we have 
+        \begin{align*}
+            & \Phi_{t + 1} - \Phi_{t}\left(
+                \sum_{i = 1}^{t} \tilde \eta_i
+            \right) =
+            \Upsilon_{2, t + 1}^{\text{AG}} + 
+            \Upsilon_{1, t + 1}^{\text{AG}} 
+            \le \delta_{t + 1} \quad 
+            \forall t \in \mathbb N, 
+            \\
+            & \Upsilon_{1, 1}^{\text{AG}} \le \delta_1. 
+        \end{align*}
+        Then with
+        \begin{align*}
+            S_t &:= \sum_{i = 1}^{t} \delta_i
+            \\
+            \sigma_t &:= \sum_{i = 1}^{t}\tilde \eta_i
+        \end{align*}
+        we have $\Phi_{t + 1} - \Phi_t \le \delta_{t + 1}$, it allows for a convergence rate of $\mathcal O \left(\sigma_T^{-1}S_T\right)$ of $f(z_T) - f(x_*)$ when $S_T \neq 0$ and a rate of $\mathcal O(\sigma_T^{-1})$ when $S_T = 0$.
     \end{theorem}
@@
                 \sum_{i = 1}^{t} \tilde \eta_i
-                \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le 0. 
+            \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le \delta_{t + 1}. 
         \end{align*}
         }
-            The derivation for the convergence raet is direct and similar to 
-            \hyperref[thm:ppm_convergence_rate]{theorem \ref*{thm:ppm_convergence_rate}} 
-            Therefore, if we can identify parameter for the generic algorithm that asserts the condition above, then we have convergence for the algorithm. 
+        Telescoping we have 
+        \begin{align*}
+            \Phi_{t + 1} - \Phi_t &\le \delta_{t + 1}
+            \\
+            \sum_{i = 0}^{T - 1}\Phi_{i + 1} - \Phi_i &\le \sum_{i = 0}^{T - 1}\delta_{i + 1}
+            \\
+            \Phi_T - \Phi_0 &\le 
+            \sum_{i = 1}^{T}\delta_i = S_{T}. 
+        \end{align*}
+        So then $\Phi_T - \Phi_0$ yields: 
+        $$
+        \begin{aligned}
+            \sigma_T (f(z_t) - f(x_*)) 
+            + \frac{1}{2}\Vert x_t - x_*\Vert^2 
+            - \frac{1}{2}\Vert x_0 - x_*\Vert^2 
+            &\le S_{T}
+            \\
+            \implies 
+            \sigma_T(f(z_t) - f(x_*))
+            &\le 
+            S_T + \frac{1}{2}\Vert x_0 - x_*\Vert^2
+            \\
+            f(z_t) - f(x_*) &\le 
+            \sigma_T^{-1}\left(
+                S_{T} + \frac{1}{2}\Vert x_0 - x_*\Vert^2
+            \right),
+        \end{aligned}
+        $$
+        which yields a convergence rate $\mathcal O(\sigma_T^{-1}S_{T})$. 
+        When $S_T = 0$, the convergence rate is $O(\sigma_T^{-1})$ instead. 
     \end{proof}
 
-    \subsection{Scenario I}\label{sec:scenario_i}
-        In this scenario, we aim to recover AG Ryu 12.1 conceret variant algorithm stated back in 
-        \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}. 
-        \begin{proposition}
-            Continue from
-            \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}, 
-            set $\eta_{t + 1} = \tilde \eta_{t + 1} = (t)/(2L)$, we derive the following algorithm: 
-            \begin{align*}
-                x_{t + 1} &= x_t - \frac{t + 1}{2L} \mathcal G_L(y_t), 
-                \\
-                z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t), 
-                \\
-                y_{t + 1} &= 
-                \left(
-                    \frac{2}{t + 3}
-                \right)x_{t +1} + 
-                \left(
-                    1 - \frac{2}{t + 3}
-                \right)z_{t + 1}. 
-            \end{align*}
-            This algorithm has convergence rate of $\mathcal O(1/T^2)$ for all $h = f + g$ where $f$ is convex $L$-Lipschitz smooth and $g$ is convex. 
-        \end{proposition}
-        \begin{observation}
-            Observe that when $g \equiv 0$ this is the same algorithm as 
-            \hyperref[def:ag_ryu_12.1]{definition \ref*{def:ag_ryu_12.1}}
-            but with an alternative choice of indexing for $y_t$ and initial condition. 
-        \end{observation}
+    \begin{theorem}[Constraints on the PPM stepsize sequence]
+        \label{thm:ag_generic_stepsize_constrants}
+        \;\\
+        Algorithm formulated in 
+        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
+        converges if the stepsize sequence $\eta_i, \tilde \eta_{i}$ satisfies
+        \begin{align*}
+            \begin{cases}
+                \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
+                - L^{-1} \sum_{i= 1}^{t}\tilde \eta_i 
+                = 
+                \epsilon_{t + 1} \tilde \eta_{t + 1}
+                & \forall t \in \mathbb N, 
+                \\
+                L \eta_t \tilde \eta_{t + 1} = \sum_{i=1}^{t}\tilde \eta_i 
+                & \forall t \in \mathbb N. 
+            \end{cases}
+        \end{align*}
+        Here $\epsilon_{t + 1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$ is a sequence characterizing the error between $\tilde \eta_{t + 1}, \eta_t - L^{-1}$. 
+        Then the convergence rate can be formulated by
+        \begin{align*}
+            \Phi_{t + 1} - \Phi_t =
+            \Upsilon_{1, t + 1}^\text{AG} + 
+            \sigma_t\Upsilon_{1, t + 1}^{\text{AG}} 
+            &\le \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}.
+        \end{align*}
+        When $\epsilon_t = 0 \;\forall t\in \mathbb N$, the sequence $a_t:= a_t = 1 + L \eta_t = \tilde \eta_{t + 1} - \epsilon_{t + 1}$, the relation simplies to: 
+        \begin{align*}
+            \begin{cases}
+                a_{t + 1} = (1/2)\left(
+                1 + \sqrt{1 + 4 c_{t + 1}}
+                \right), 
+                \\
+                c_{t + 1} = a_t^2.     
+            \end{cases}
+        \end{align*}
+        As a consequence: 
+        \begin{enumerate}
+            \item It makes $\delta_{t} = 0$ in the Lypunov analysis; 
+            \item it simplifies the algorithm to
+            \hyperref[def:ag_form_similar_tria_I]{definition\ref*{def:ag_form_similar_tria_I}}; 
+            \item and it is the famous Nesterov momentum sequence. 
+        \end{enumerate}
+
+    \end{theorem}
     \begin{proof}
-            Recall that for the proximal gradient PPM generic form we have iterate updates for $t\in \mathbb N$: 
+        With $t \in \mathbb N \cup \{0\}$ fixed, 
+        recall that for the proximal gradient PPM generic form 
+        (as formulated in 
+        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
+        ) for $t\in \mathbb N$ it has: 
         \begin{align*}
@@
                 L\eta_t \tilde \eta_{t + 1} - \sum_{i = 1}^{t}\tilde \eta_i
-                \right)\langle \mathcal G_L(y_t), z_t - y_t\rangle
+            \right)\langle \mathcal G_L(y_t), z_t - y_t\rangle. 
         \end{align*}
         }
-            If the algorithm were to have the abstract convergence rate as stated in 
-            \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}},
-            then one of the sufficient condition is to have the above quantity less than or equal to zero, one sufficient condition of that is to have the coefficient for $\Vert \mathcal G_L(y_t)\Vert$ be $\le 0$, and the coefficient of the cross term $\langle \mathcal G_L(y_t), z_t - y_t\rangle$ be zero.
-            To simplify, we make the assumption that $\tilde \eta_t = \eta_t$ for all $t \in \mathcal N$, making it to be a specific instance of 
-            \hyperref[def:ag_tri_pt_form_E]{definition \ref*{def:ag_tri_pt_form_E}}. 
-            These conditions translate to the following relations for $\eta_{t}$. 
+        The non-negativity of $\Vert \mathcal G_L(y_t) \Vert^2$ characterize the culmulative error $\delta_{t + 1}$ in the Lypunov analysis through sequence $\epsilon_i$. 
+        Setting the coefficient of $\Vert \mathcal G_L(y_t) \Vert^2$ to be $\epsilon_{t + 1}\tilde \eta_{t + 1}$, it yields a system of inequality: 
         \begin{align*}
             \begin{cases}
-                    L\eta_{t + 1}^2 + \eta_{t + 1} - \sum_{i = 1}^{t}\eta_i 
-                    \le 0, 
-                    \\
-                    L\eta_t \eta_{t + 1} - \sum_{i = 1}^{t} \eta_i 
-                    = 0. 
+                \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
+                - L^{-1} \sum_{i= 1}^{t}\tilde \eta_i 
+                = 
+                \epsilon_{t + 1} \tilde \eta_{t + 1}
+                & \forall t \in \N, 
+                \\
+                L \eta_t \tilde \eta_{t + 1} = \sum_{i=1}^{t}\tilde \eta_i 
+                & \forall t \in \N. 
             \end{cases}
         \end{align*}
-            Substituting the sequence equality back to the first one yield: 
-            \begin{align*}
-                L\eta_{t + 1}^2 - (\eta_{t + 1} + L\eta_t\eta_{t + 1}) &\le 0 
-                \\
-                L\eta^2_{t + 1} - \eta_{t + 1}
+        It requires base case $L\eta_0\tilde\eta_{1} = 0$, assume $\sigma_0 = 0$. 
+        We use $\sum_{i = 1}^t \tilde \eta_i = \sigma_t$, simplifying the first equation we have 
+        \begin{align*}
+            \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
+            - L^{-1} \sigma_t
+            &= 
+            \epsilon_{t + 1} \tilde \eta_{t + 1}
+            \\
+            \iff 
+            \tilde \eta_{t + 1} ^2 - L \tilde \eta_{t + 1} 
+            &= 
+            \epsilon_{t + 1} \tilde \eta_{t + 1} + L^{-1} \sigma_t
+            \\
+            &= 
+            \epsilon_{t + 1} \tilde \eta_{t + 1} 
+            + L^{-1}(L \eta_t \tilde \eta_{t + 1})
+            \\
+            \iff 
+            \tilde \eta_{t + 1} &= \epsilon_{t + 1} + \eta_t + L^{-1}. 
+        \end{align*}
+        At the last step, we divided both side of the equation by $\tilde \eta_{t + 1} > 0$.
+        The parameter gives relation $\epsilon_{t+1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$. 
+        Hence, it gives us the following system of equality to work with 
+        \begin{align*}
+            \forall t \in \N: 
+            \begin{cases}
+                \tilde \eta_{t + 1} = \epsilon_{t + 1} + \eta_t + L^{-1}, 
+                \\
+                L \eta_t \tilde \eta_{t + 1} = \sigma_t.     
+            \end{cases}
+        \end{align*}
+        With that, we can solve a relation between $\eta_{t + 1}$ in terms of the sequence $\epsilon$ and $\eta_t$.
+        Consider the equality
+
+        \begin{align*}
+            L \sigma_{t + 1} &= L \tilde \eta_{t + 1} + L \sigma_t
+            \\
+            &=
+            L \tilde \eta_{t + 1}  + L (L \eta_t \tilde \eta_{t + 1})
+            \\
+            &= L \tilde \eta_{t+ 1} + L \eta_t (L \tilde \eta_{t + 1})
+            \\
+            &=  L \tilde \eta_{t+ 1} + L \eta_t (L \epsilon_{t + 1} + L \eta_t + 1)
+            \\
+            &=  L \tilde \eta_{t+ 1} + L \eta_t (L \eta_t + 1) + L^2 \eta_t \epsilon_{t + 1}
+            \\
+            &= L (\epsilon_{t +1} + \eta_t + L^{-1}) + L\eta_t(L \eta_t + 1) + L^2\eta_t \epsilon_{t + 1}
+            \\
+            &= L \epsilon_{t + 1} + (L\eta_t + 1)^2 + L^2\eta_t \epsilon_{t + 1}
+            \\
+            &= 
+            L \epsilon_{t + 1}(1 + L \eta_t) + (1 + L \eta_t)^2. 
+        \end{align*}
+        At the same time we have 
+        \begin{align*}
+            L \sigma_{t + 1} &= L^2 \eta_{t + 1}\tilde \eta_{t + 1} 
+            \\
+            &= L\eta_{t + 1}(1 + L \eta_{t + 1} + \epsilon_{t + 2})
+            \\
+            &= L\eta_{t + 1}(1 + L \eta_{t + 1}) + \epsilon_{t + 2}L\eta_{t + 1}. 
+        \end{align*}
+        Therefore, it generates the following equation: 
+        \begin{align*}
+            L\eta_{t + 1} (1 + L \eta_{t + 1}) 
+            + 
+            \epsilon_{t + 2} L \eta_{t + 1} 
+            &= 
+            L\epsilon_{t + 1}(1 + L \eta_t)  + (1 + L\eta_t)^2
+            \\
+            (L\eta_{t + 1} + L^2\eta_{t + 1}^2)
+            + 
+            \epsilon_{t + 2} L \eta_{t + 1} 
+            + 
+            \frac{1}{4}
+            &= 
+            L\epsilon_{t + 1}(1 + L \eta_t)  + (1 + L\eta_t)^2
+            + 
+            \frac{1}{4}
+            \\
+            (L\eta_{t + 1} + L^2\eta_{t + 1}^2 + 1/4)
+            + 
+            \epsilon_{t + 2} L \eta_{t + 1} 
+            + \epsilon_{t + 2}
+            &= 
+            L\epsilon_{t + 1}(1 + L \eta_t)  + (1 + L\eta_t)^2
+            + \frac{1}{4}
+            + \epsilon_{t + 2}
+            \\
+            (L\eta_{t + 1} + 1/2)^2 + \epsilon_{t + 2}(L \eta_{t + 1} + 1)
+            &= 
+            L \epsilon_{t + 1}(1 + L \eta_t) + (1 + L\eta_t)^2
+            + \frac{1}{4} + \epsilon_{t + 2}
+            \\
+            \text{ with: } & a_t = 1 + L \eta_t = \tilde \eta_{t + 1} - \epsilon_{t + 1}
+            \\
+            (a_{t + 1} - 1/2)^2 + \epsilon_{t + 2}a_{t + 1}
+            &= 
+            L \epsilon_{t + 1}a_t + a_t^2 + 1/4 + \epsilon_{t + 1}
+            \\
+            a_{t + 1}^2 + 1/4 - a_{t + 1} + \epsilon_{t + 2}a_{t + 1}
+            &= 
+            L \epsilon_{t + 1}a_t + a_t^2 + 1/4 + \epsilon_{t + 1}
+            \\
+            a_{t + 1}^2 + a_{t + 1}(\epsilon_{t + 2} - 1)
+            &= 
+            \underbrace{
+                a_t(L \epsilon_{t + 1} + a_t) + \epsilon_{t + 1}
+            }_{c_{t + 1}}. 
+        \end{align*}
+        Solving reveals the relations: 
+        \begin{align*}
+            \begin{cases}
+                a_{t + 1} = (1/2)\left(
+                1 - \epsilon_{t + 2} + \sqrt{(1 - \epsilon_{t + 2}) + 4 c_{t + 2}}
+                \right), 
+                \\
+                c_{t + 1} = a_t (L \epsilon_{t + 1} + a_t) + \epsilon_{t + 1}. 
+            \end{cases}
+        \end{align*}
+        Observe that in the case where we choose $\epsilon_t = 0 \forall t \in \N$, the above relation simplifies to 
+        \begin{align*}
+            a_{t + 1} &= (1/2)\left(
+                1 + \sqrt{1 + 4 c_{t + 1}}
+            \right), 
+            \\
+            c_{t + 1} &= a_t^2. 
+        \end{align*}
+        This relation is the Famous Nesterov momentum sequence. 
+        At the same time, we can analyize the convergence rate of the algorithm by the abstract convergence lemma, producing: 
+        \begin{align*}
+            \Phi_{t + 1} - \Phi_t =
+            \Upsilon_{1, t + 1}^\text{AG} + 
+            \sigma_t\Upsilon_{1, t + 1}^{\text{AG}} 
+            &\le \epsilon_{t + 1}\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}
+        \end{align*}
+        Telescoping yields: 
+        \begin{align*}
+            S_{T} = 
+            \sum_{i = 0}^{T- 1} \delta_i 
+            &= 
+            \sum_{i = 0}^{T - 1} \epsilon_{i + 1}\tilde\eta_{i + 1}\Vert \mathcal G_L(y_i)\Vert^2
+            \\
+            &\le \sum_{i = 0}^{T - 1}\max(\epsilon_{i + 1} \tilde\eta_{i + 1}\Vert \mathcal G_L(y_i)\Vert^2, 0). 
+        \end{align*}
+        Under an ideal case where we wish to attain accelerations, we want $\lim_{T \rightarrow \infty} S_T < \infty$. 
+        One way to accomplish is choose the error sequence $\epsilon_i, i \in \N$ to be bounded by for all $i \in \N$, $\epsilon_i$ should satisfy: 
+        \begin{align*}
+            \epsilon_{i + 1}\tilde \eta_{i + 1}
+            \Vert \mathcal G_L(y_i)\Vert^2 
+            &\le \delta_{i + 1}
+            \\
+            \iff 
+            \epsilon_{i + 1}
             &\le 
-                L\eta_t \eta_{t + 1} 
-                \\
-                \eta_{t + 1}(L\eta_{t + 1} - 1) 
-                &\le L\eta_t\eta_{t + 1}
-                \\
-                \eta_t > 0 
-                \implies 
-                L\eta_{t + 1} - 1 &\le 
-                L\eta_t 
-                \\
-                \eta_{t + 1} &\le \eta_t + L^{-1}. 
-            \end{align*}
-            To satisfy the equality, reader should verify that $\eta_{t} = t/(2L)$ or $\eta_t = (t + 1)/2L$ are some of the options. 
+            \frac{\delta_{i + 1} }{\tilde\eta_{t + 1}\Vert \mathcal G_L(y_i)\Vert^2}. 
+        \end{align*}
+        for any $\sum_{i = 0}^{T - 1}\delta_{i + 1}$ converges to a limit as $T \rightarrow \infty$.
+
     \end{proof}
-        \begin{remark}
-            In the original writing by Ahn \cite[equation (4.9)]{ahn_understanding_2022}, they didn't identify this specific variant in the literature. 
-            Here we identify it to be equivalent to the acceleration algorithm stated in Ryu \cite[algorithm 12.1]{ryu_large-scale_2022}. 
-        \end{remark}
-
-    \subsection{Scenario II}\label{sec:scenario_ii}
-        With the choice of $\tilde \eta_{t + 1} = \eta_t + L^{-1}$, we can recover the seminal Nesterov accelerated gradient algorithm from 1983. 
-        The variants proposed by Chambolle Dossal \cite{chambolle_convergence_2015}, is distinct from the possibility proposed in this secenario.
-
-        \begin{lemma}[Deriving the Nesterov Sequence]
-            For all $t \in \mathbb N$
-            \begin{align*}
-                \left\lbrace
-                \begin{aligned}
-                    (1 + L\eta_{t + 1})^{-1}L \eta_t 
-                    &= \frac{a_t - 1}{a_{t + 1}} , 
-                    \\
-                    a_{t + 1}^2 - a_t &= a_t^2. 
-                \end{aligned} 
-                \right. 
-            \end{align*}
-            allows \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}} to converge at an optimal rate. 
-            The base case is $\eta_0 = 0$. 
-        \end{lemma}
-        \begin{proof}
-            Continue from 
-            \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]{lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}, 
-            With $x_{t +1} - x_t = L\tilde\eta_{t+1}(z_{t + 1} - y_t)$ for $y_t$: 
-            \begin{align*}
-                \Upsilon_{1, t + 1}^\text{AG} &\le 
-                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-                    + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                    - \langle 
-                        \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                        x_{t + 1} - z_{t + 1}
-                    \rangle
-                    \\
-                    &= 
-                    - \frac{1}{2}\Vert L \tilde \eta_{t+} (z_{t+1} - y_t)\Vert^2 + 
-                    \frac{\tilde\eta_{t +1}L}{2}\Vert z_{t+1} - y_t\Vert^2
-                    - \langle 
-                        \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                        x_{t + 1} - z_{t + 1}
-                    \rangle
-                    \\
-                    &= 
-                    \left(
-                        \frac{L^2\tilde\eta_{t + 1}^2}{2}
-                        + 
-                        \frac{\tilde \eta_{t +1}}{2}
-                    \right)
-                    \Vert z_{t+1} - y_t\Vert^2
-                    - 
-                    \langle 
-                        \tilde \eta_{t+ 1} \mathcal G_L(y_t), x_{t+1} - z_{t+1}
-                    \rangle. 
-            \end{align*}
-            This completes the analysis for $\Upsilon_{1, t + 1}^\text{AG}$ with $\tilde\eta_{t+1}$. 
-            Next we consider 
-            \begin{align*}
-                \Upsilon_{2, t + 1}^{\text{AG}} 
-                &= 
-                \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle
-                + 
-                \frac{L }{2} \Vert z_{t+1} - y_t\Vert^2
-                \\
-                &= 
-                \langle \mathcal G_L(y_t), L^{-1}\eta_t^{-1}(x_{t+1} - z_{t + 1})\rangle
-                + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-            \end{align*}
-            Here we used $x_{t + 1} = z_{t + 1} + L\eta_t (z_{t + 1} - z_t)$, which was the consequence of $\tilde\eta_{t + 1} = \eta_t + L^{-1}$, as discussed from before. 
-            Hence, the upper bound of the Lyapunov function for smooth AG PPM 
-            (\hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}) 
-            has 
-            {\footnotesize
-            \begin{align*}
-                & \Upsilon_{1, t + 1}^{\text{AG}} + 
-                \left(
-                    \sum_{i = 1}^{t}\tilde \eta_i
-                \right)\Upsilon_{2, t + 1}^{\text{AG}}
-                \\
-                &\quad \le 
-                \left(
-                    - \frac{L^2\tilde \eta_{t + 1}^2}{2}
-                    + \frac{\tilde\eta_{t+1}L}{2}
-                \right)
-                \Vert z_{t+1} - y_t\Vert^2
-                - 
-                \langle \tilde \eta_{t+1} \nabla f(y_t), x_{t+1} - z_{t + 1}\rangle
-                \\
-                & \qquad + 
-                \left(
-                    \sum_{i = 1}^{t}\tilde \eta_i
-                \right)\left(
-                    \langle \nabla f(y_t), L^{-1}\eta_t^{-1}(x_{t+1} - z_{t + 1})\rangle
-                    + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                \right)
-                \\
-                &= 
-                \frac{L}{2}
-                \left(
-                -\tilde\eta_{t + 1}^2 + \tilde\eta_{t + 1}
-                    + \sum_{i = 1}^{t}\tilde\eta_i
-                \right)\Vert z_{t + 1} - y_t\Vert^2
-                +
-                \left(
-                    L^{-1}\eta_t^{-1} 
-                    \left(
-                        \sum_{i = 1}^{t}\tilde \eta_i
-                    \right)
-                    -
-                    \tilde \eta_{t + 1}
-                \right)\langle \mathcal G_L (y_t), x_{t + 1} - z_{t + 1}\rangle
-            \end{align*}
-            }
-            If the above quantity less than or equal to zero, it will allow for convergence of the algorithm by 
-            \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}.
-            One sufficient condition is to have the coefficients for all the cross product terms to sum up to zero, and the squared normed term to sum up to a non-positive number for all $t \in \mathbb N$.
-            This gives relations 
-            \begin{align*}
-                - \frac{1}{2}\left(
-                    L^2 \tilde\eta_{t+1}^2 - \tilde\eta_{t+1}L 
-                \right) + 
-                \frac{L}{2}\left(
-                    \sum_{i = 1}^{t} \tilde \eta_i
-                \right) &\le 0
-                \\
-                - \left(
-                    L\tilde \eta_{t + 1}^2 
-                    - 
-                    \tilde\eta_{t + 1}
-                \right) + 
-                \sum_{i = 1}^{t}\tilde \eta_i 
-                &\le 0
-                \\
-                -L \tilde \eta_{t+1} + 
-                \sum_{i = 1}^{t + 1} \tilde \eta_i 
-                &\le 0
-                \\
-                \sum_{i = 1}^{t + 1}\tilde \eta_i 
-                &\le L \tilde \eta_{t + 1}^2, 
-            \end{align*}
-            and equations 
-            \begin{align*}
-                -\tilde \eta_{t + 1} + 
-                \left(
-                    \sum_{i = 1}^{t}\tilde \eta_i
-                \right)L^{-1}\eta_t^{-1} 
-                &= 0
-                \\
-                \sum_{i = 1}^{t}\tilde \eta_i 
-                &= 
-                L \eta_t \tilde \eta_{t + 1}. 
-            \end{align*}
-            Susbtituting the equality into the inequalites we have 
-            \begin{align*}
-                \tilde \eta_{t + 1} + \sum_{i = 1}^{t} \tilde \eta_i 
-                &\le L \tilde \eta_{t + 1}^2
-                \\
-                \tilde \eta_{t + 1} + L\eta_t \tilde \eta_{t + 1}
-                &\le L \tilde \eta_{t + 1}^2
-                \\
-                1 + L\eta_t &\le L \tilde\eta_{t + 1}. 
-            \end{align*}
-            The choice $\tilde \eta_{t + 1} = \eta_t + L^{-1}$ makes the inequality is an equality. 
-            Finally, to recover the momentum stepsizes for the classical Nesterov accelerated gradient, we consider relations 
-            \begin{align*}
-                L \sum_{i = 1}^{t + 1} \tilde \eta_i 
-                &= L \tilde \eta_{t + 1} + L \sum_{i = 1}^{t} \tilde \eta_i 
-                \\
-                &= 
-                L \tilde \eta_{t + 1} + L (L \eta_t \tilde \eta_{t + 1}) 
-                \\
-                &= L \tilde \eta_{t + 1} + L \eta_t (L \eta_t + 1)
-                \\
-                &= L (\eta_t + L^{-1}) + L\eta_t (L \eta_t + 1)
-                \\
-                &= (L\eta_t + 1)^2, 
-            \end{align*}
-            Simultanenously 
-            \begin{align*}
-                L \sum_{i = 1}^{t + 1} \tilde \eta_i 
-                &= L^2 \eta_{t + 1} \tilde \eta_{t + 1}
-                \\
-                &= L \eta_{t + 1}(1+ L \eta_{t + 1}), 
-            \end{align*}
-            Combining yields that 
-            \begin{align*}
-                (L\eta_t + 1)^2 
-                &= L\eta_{t + 1}(1 + L \eta_{t + 1})
-                \\
-                &= L\eta_{t + 1} + L^2 \eta_{t + 1}^2
-                \\
-                \iff 
-                (L\eta_t + 1)^2 + 1/4 &= 
-                1/4 + 2(1/2)L \eta_{t + 1} + (L \eta_{t + 1})^2
-                \\
-                \iff 
-                (L\eta_t + 1)^2 + 1/4 &= 
-                (L \eta_{t + 1} + 1/2)^2. 
-            \end{align*}
-            With $a_t = L\eta_t + 1 = L \tilde \eta_t$ this is 
-            \begin{align*}
-                a_t^2 + 1/4 &= (a_{t + 1} - 1/2)^2 
-                \\
-                a_t^2 + 1/4 &= a_{t + 1}^2 + 1/4 - a_{t + 1}
-                \\
-                a_t^2 + a_{t + 1} &= a_{t + 1}^2. 
-                \\
-                \implies 
-                a_{t + 1} &= 
-                \frac{1 + \sqrt{1 + 4a_t^2}}{2}
-            \end{align*}
-            And that is the updates for the Nesterov momentum, recall that the momentum term is linked to the PPM sequence via relation 
-            \begin{align*}
-                (1 + L \eta_{t+ 1})^{-1}L\eta_t = L\eta_t / a_{t + 1} = (a_t - 1)/a_{t + 1}. 
-            \end{align*}
-            We had recovered the classic Nesterov acceleration sequence method for the smooth gradient descent algorithm. 
-        \end{proof}
-        \begin{remark}
-            This variant is distinct from the variants proposed by Chambolle \cite{chambolle_convergence_2015}, but both of which fits into the same frameworks. 
-            The variantis presented as 
-            \begin{align*}
-                y_n &= (1 - t_n^{-1})z_n + t_n^{-1} x_n
-                \\
-                z_{n + 1} &= y_n - L^{-1}\nabla f(y_n)
-                \\
-                x_{n + 1} &= z_n + t_{n + 1}(z_{n + 1} - z_n)
-            \end{align*}
-            They listed the choice of $t_n = (n + a - 1)/a$ for all $a > 2$. 
-            Under this choice, unfortunately, it's in no way obvious that this format reduces to \hyperref[def:agg_tri]{definition \ref*{def:agg_tri}}. 
-            It fails the similar triangle description Without the explict representation $x_{n + 1} = z_n + \tilde\eta_{t + 1}\nabla f(y_t)$. 
-            \par\noindent
-            At the time of writing, we are still investigating the relations between these variants of algorithms.
-        \end{remark}
-
-    \subsection{Scenario III}
-
-\section{Classical analysis of Nesterov accelerated gradient}
-    In this section, we reproduce some of the analysis for Nesterov accelerated gradient method with excruciating details, in the appendix. 
-    We will introduce the method of estimating sequence invented by Nesterov. 
-    We will also go over some details about the history, development and motivations behind the accelerated gradient algorithm. 
-    \subsection{Method of Nesterov's estimating sequence}
-        In this section we introduce the method of estimating sequence.
-
-    \subsubsection{The estimating sequence and function}
-        \begin{definition}[Nesterov's Estimating Functions]
-            Define  $\{\phi_t\}_{t\in \mathbb N}$ to be a sequence of function where it recursively satisfies for all $k\in \mathbb N$: 
-            \begin{align*}
-                \phi_{k} (x) - f(x) \le 
-                (1 - \alpha_k)(\phi_k(x) - f(x)) \quad \forall x 
-            \end{align*}
-            Where $\alpha \in [0, 1)$. 
-        \end{definition}
-        \begin{observation}
-            Expands recursively we have 
-            \begin{align*}
-                \phi_{k}(x) - f(x) &\le 
-                \left(
-                    \prod_{i = 0}^{k} 
-                    (1 - \alpha_i)
-                \right)(\phi_0(x) - f(x)). 
-            \end{align*}
-        \end{observation}
-        So it motivates the definition of a sequence: $\lambda_k = \prod_{i=0}^k(1 - \alpha_i)$.
-
-        \begin{definition}[The estimating Sequence]
-            Continue from the above definition of a estimating functions, we consider a sequence $\{x_k\}$ satisfying 
-            \begin{align*}
-                f(x_k) &\le \phi_k^* := \min_z(\phi_k(z)). 
-            \end{align*}
-        \end{definition}
-
-        \begin{lemma}[The Lyapunov function from estimating sequence and function]
-            \;\\
-            Assume that $f$ bounded below with $f_* = \min_x f(x)$ and there exists minimizer $x_*$. 
-            With $\phi_k$ being an estimating functions and convex, $\{x_k\}$ an estimating sequence for $\phi_k$, then it satisfies
-            \begin{align*}
-                f(x_k) - f_*
-                &\le 
-                \lambda_k(\phi_0(x_*) - f_*). 
-            \end{align*}
-            for all $k\in \mathbb N\cup \{0\}$. 
-        \end{lemma}
-        \begin{proof}
-            Directly by the property of estimating sequence $x_k$, we have for all $k, x$
-            \begin{align*}
-                \phi_k(x) - f(x) \ge \phi_k^* - f(x) \ge f(x_k) - f(x), 
-            \end{align*}
-            so 
-            \begin{align*}
-                f(x_k) - f(x) \le \lambda_k (\phi_0(x) - f(x))
-                \\
-                \implies 
-                f(x_k) - f_* \le \lambda_k (\phi_0(x_*) - f(x_*)). 
-            \end{align*}
-            This establishes the convergence rate of $f(x_k)$ assuming that $\lambda_k$ is sequence that converges to zero. 
-        \end{proof}
-    \subsection{Construction of the estimating sequence and function}
-        The construction of the Nesterov estimating sequence and function is where most creativities are involved. 
-        For convex $f$ that is differentiable with $L$-Lipschitz gradient and strong convexity constant $\mu \ge 0$, Nesterov suggested in his book \cite{nesterov_lectures_2018} that there exists sequence $y_k$, $\gamma_k$, where
-        \begin{align*}
-            l_f(x, y_k) &= 
-            f(y_k) + \langle \nabla f(y_k), x - y_k\rangle + 
-            \frac{\mu}{2}\Vert x - y_k\Vert^2
-            \\
-            \phi_0 (x) &= 
-            f(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2
-            \\
-            \phi_{k + 1}(x) &= 
-            (1 - \alpha_k)\phi_k(x) + \alpha_k l_f(x; y_k)
-            \\
-            &= \phi_{k + 1}^2 + \frac{\gamma_k}{2}\Vert x - v_{k + 1}\Vert^2
-        \end{align*}
-        will verify as a Nesterov's estimating sequence and functions. 
-        The derivation for the parameters: $\gamma_k, x_k, y_k$ for $k \in \mathbb N \cup \{0\}$, will produce the Nesterov acclerated gradient as presented in
-        \hyperref[def:Nes2.2.7]{definition \ref*{def:Nes2.2.7}}
-        if correctly conducted. 
-        In this case, $\phi_k$ are simple quadratic centered $v_k$ with value $\phi_k$ with curvature $\gamma_k$. 
-        \par
-        However, the construction exhibits variations for different variants of the accelerated gradient algorithm. 
-        A different construction of $\phi_k$ yield a different algorithm. 
-        As shown in Nesterov's book \cite*[(2.2.63)]{nesterov_lectures_2018}, a projected gradient variant of the accelerated gradient method make use of the following estimating functions, sequence: 
-        \begin{align*}
-            \phi_0 (x) &= f(x_0) + \frac{\gamma_0}{2}\Vert x - x_0\Vert^2
-            \\
-            l_f(x; y_k) &= f(\mathcal T_ly_k) + 
-            \frac{1}{2L}\Vert \mathcal G_L(y_k)\Vert^2 + 
-            \langle \mathcal G_L(y_k), x - y_k\rangle + 
-            \frac{\mu}{2}\Vert x - y_k\Vert^2
-            \\
-            \phi_{k + 1}(x) &= 
-            (1 - \alpha_k)\phi_k + 
-            \alpha_k l_f(x; y_k), 
-        \end{align*}
-        Here, $G_L(x) = L(x - \mathcal T_L(x))$ and $T_L(x) = \Pi_Q(x - L^{-1}\nabla f(x))$, where $Q$ is a convex set. 
-        It's equivalent to applying proximal gradient method with $h = f + g$ where $g = \delta_Q$.
-
-\section{Modern techniques in analysis of accelerated gradient algorithms}
-
-\printbibliography
-
-\appendix
-\section*{Postponed Proofs}
-
-\end{document}

### 2024-08-08 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, ready to sync

@@
     The proofs had been streamlined, extended and new error terms are added to allow a larger set of stepsize sequence for the PPM. 
-    Additionally, we proposed a line search method to dynamically adjust the strong convexity index $\mu$ and Lipschitz constant of the gradient in algorithm implementations based on the PPM understanding, presented numerical experiments.
+    Additionally, we proposed a line search method to dynamically adjust the strong convexity index $\mu$ and Lipschitz constant of the gradient in algorithm implementations based on the PPM understanding, with numerical experiments.
 

### 2024-08-14 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, updated fixes

@@
 \label{sec:generic_ag_ppm_lyapunov_analysis}
-    The lemma theorem states targets
-    \hyperref[prop:derive_ag_prox_grad_tript]
-    {definition \ref*{prop:derive_ag_prox_grad_tript}}.
-
-    \begin{lemma}[Nonsmooth Generic AG Lyapunov Analysis]
+    The following lemma establish an upper bound for quantities used in the Lypunov functions for the convergence rate of 
+    \hyperref[def:ag_prox_grad_generic]
+    {definition \ref*{def:ag_prox_grad_generic}}
+    \begin{lemma}[Lyapunov Inequality]
     \label{lemma:nsmooth_agg_lyapunov_upper_bound}\;\\
-        Continue from 
-        \hyperref[prop:derive_ag_prox_grad_tript]
-        {definition \ref*{prop:derive_ag_prox_grad_tript}},
-        we derive the non-smooth analogous case of the Lyapunov upper bound for all $t \in \mathbb N \cup \{0\}$: 
-        \begin{align*}
-            \Upsilon_{1, t + 1}^\text{AG}
-            &= 
-            \tilde\eta_{t + 1} (h(z_{t + 1}) - h(x_*)) + 
-            \frac{1}{2} (
-                \Vert x_{t + 1} - x_*\Vert^2
+        Let $h = f + g$ be a sum of $f$ that is $L$-Lipschitz smooth convex, and $g$ be convex.
+        Fix any $\bar x, x, \tilde\eta > 0$, define
+        \begin{align*}
+            \phi(u) &:= \tilde\eta
+            \left(
+                h( \mathcal T_L\bar x) + \langle \mathcal G_L\bar x, u - \bar x\rangle
+                + \frac{L}{2}\Vert \bar x - \mathcal T_L \bar x\Vert^2 
+            \right), 
+            \\
+            x^+ &:= 
+            \prox{\phi}(x) = x - \tilde \eta\mathcal G_L \bar x. 
+        \end{align*}
+        with $x_*$ being the minimizer of $h$, it has 
+        \begin{align*}
+            \Upsilon_{1}  &:= 
+            \tilde \eta(h(\mathcal T_L \bar x) - h(x_*))
+            + 
+            \frac{1}{2}(\Vert x^+ - x_*\Vert^2 - \Vert x - x_*\Vert^2)
+            \\
+            &\quad \le 
+            \tilde \eta 
+            \langle \mathcal G_L\bar x, x^+ - \mathcal T_L \bar x\rangle
+            + 
+            \frac{\tilde \eta L}{2} \Vert \bar x - \mathcal T_L \bar x\Vert^2
             - 
-                \Vert x_t - x_*\Vert^2
-            )
+            \frac{1}{2}\Vert x^+ - x\Vert^2, 
+            \\
+            \forall z':
+            \Upsilon_2 &:= 
+            h(\mathcal T_L \bar x) - h(z') 
+            \le 
+            \langle \mathcal G_L\bar x, \mathcal T_L \bar x - z'\rangle + 
+            \frac{L}{2}\Vert \mathcal T_L \bar x - \bar x\Vert^2. 
+        \end{align*}
+    \end{lemma}
+    \begin{observation}
+        Function $\phi$ is a linear function that qualifies as a lower bound of $\tilde \eta h$, anchored at $\bar x$ by 
+        \hyperref[lemma:grad_map_linearization]{lemma \ref*{lemma:grad_map_linearization}}.
+    \end{observation}
+    \begin{proof}
+        Directly observe that we have 
+        \begin{align*}
+            \quad &
+            h(\mathcal T_L\bar x) + 
+            \langle \mathcal G_L \bar x, u - \bar x\rangle + 
+            \frac{L}{2}\Vert \bar x - \mathcal T_L \bar x\Vert^2
+            \\
+            &= 
+            h(\mathcal T_L \bar x) + 
+            \langle \mathcal G_L \bar x, u - \mathcal T_L \bar x\rangle
+            + 
+            \langle \mathcal G_L \bar x, \mathcal T_L \bar x - \bar x\rangle
+            + 
+            \frac{L}{2}\Vert \bar x - \mathcal T_L \bar x \Vert^2
+            \\
+            &= 
+            h(\mathcal T_L \bar x) + 
+            \langle \mathcal G_L \bar x, u - \mathcal T_L \bar x\rangle
+            + 
+            \langle 
+                L (\bar x - \mathcal T_L \bar x)
+                , 
+                \mathcal T_L \bar x - \bar x
+            \rangle
+            + 
+            \frac{L}{2}\Vert \bar x - \mathcal T_L \bar x\Vert^2
+            \\
+            &= 
+            h(\mathcal T_L \bar x) + 
+            \langle \mathcal G_L \bar x, u - \mathcal T_L \bar x\rangle 
+            - \frac{L}{2} \Vert \bar x - \mathcal T_L \bar x\Vert^2. 
+        \end{align*}
+        By PPM descent inequality
+        \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}}
+        , let $x_*$ be a minimizer, it claims that 
+        {\small
+        \begin{align*}
+            & 
+            \phi(x^+) - \phi (x^*) + 
+            \frac{1}{2}\left(
+                \Vert x^+ - x_*\Vert^2 - 
+                \Vert x - x_*\Vert^2
+            \right)
+            \le 
+            - \frac{1}{2}\Vert x^+ - x\Vert^2
+            \\
+            \implies &
+            \tilde 
+            \eta 
+            \left(   
+                h(\mathcal T_L \bar x) + 
+                \langle \mathcal G_L \bar x, u - \mathcal T_L \bar x\rangle 
+                - \frac{L}{2} \Vert \bar x - \mathcal T_L \bar x\Vert^2
+            \right)
+            - \tilde \eta h (x_*)
+            +
+            \frac{1}{2}\left(
+                \Vert x^+ - x_*\Vert^2 - 
+                \Vert x - x_*\Vert^2
+            \right)
             \\
             &\le 
-            - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-            + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
-            - \langle 
-                \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                x_{t + 1} - z_{t + 1}
-            \rangle
-            \\
-            \Upsilon_{2, t + 1}^\text{AG}
-            &= 
-            h(z_{t + 1}) - h(z_t) 
-            \le 
-            \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
-            \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-        \end{align*}
-    \end{lemma}
-    \begin{proof}
-        Define 
-        \begin{align*}
-            \phi_t(u) &:= 
-            \tilde \eta_{t + 1} 
-            \left(
-                f(y_t) + g(y_t) + \langle \nabla f(y_t) + \partial g(y_t^+), u - y_t\rangle
-                % + 
-                % \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
-            \right)\\
-            &= 
-            \tilde \eta_{t + 1} \left(
-                f(y_t) + \langle \nabla f(y_t), u - y_t\rangle + 
-                % \frac{1}{2\tilde \eta_{t + 1}}\Vert u - x_t\Vert^2
-                % + 
-                g(y_t) + \langle \partial g(y_t^+), u - y_t\rangle
-            \right). 
-        \end{align*}
-        Then the update in the Generic Tri-Point algorithm 
-        (\hyperref[def:ag_prox_grad_ppm]
-            {definition \ref*{def:ag_prox_grad_ppm}}) 
-        has $x_{t + 1} = \hprox_{\phi_t}(x_t)$ if we ignore the difference between the constant terms $h(y_t^+)$, $f(y_t) + g(y_t)$ from above. 
-        Therefore we can use the Lyapunov inequality for PPM (\hyperref[thm:ppm_descent_ineq]
-            {theorem \ref*{thm:ppm_descent_ineq}})
-        which gives for all $x_*$: 
-        \begin{align*}
-            & \phi_t(x_{t + 1}) - \phi_t(x_*) + 
-            \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
-            \frac{1}{2}\Vert x_t - x_*\Vert^2
-            \le \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2, 
-            \\
-            & \text{where }
-            \phi_t(x_{t + 1}) =
-            \\
-            & \quad 
-            \tilde \eta_{t + 1}
-            \left(
-                f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle + 
-                % \frac{1}{2\tilde \eta_{t + 1}}\Vert x_{t + 1} - x_t\Vert^2
-                % + 
-                g(y_t) + \langle \partial g(y_t^+), x_{t + 1} - y_t\rangle
-            \right). 
-        \end{align*}
-        to simplify, consider using the $L$-smoothness of $f$, we have the inequality: 
-        \begin{align*}
-            \begin{aligned}
-                f(y_t) + \langle \nabla f(y_t), x_{t + 1} - y_t\rangle
-                &=
-                f(y_t) + \langle \nabla f(y_t), (x_{t +1} - z_{t + 1}) + (z_{t + 1} - y_t) \rangle
-                \\
-                &\ge 
-                f(z_{t + 1}) - \frac{L}{2} \Vert z_{t + 1} - y_t\Vert^2 + 
-                \langle \nabla f(y_t), x_{t +1} - z_{t + 1}\rangle
-                \\
-                &= 
-                f(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2
-                + \langle \nabla f(y_t), x_{t + 1} - y_t^+\rangle.     
-            \end{aligned}
-            \tag{$[*]$}
-        \end{align*}
-        further consider
-        \begin{align*}
-            \begin{aligned}
-                g(y_t) + \langle \partial g(y_t^+), x_{t + 1} - y_t\rangle 
-                &= g(y_t) + 
-                \langle \partial g(y_t^+), 
-                x_{t + 1} - y_t^+ + y_t^+ - y_t
-                \rangle
-                \\
-                &= g(y_t) 
-                + \langle \partial g (y_t^+),
-                    x_{t + 1} - y_t^+
-                \rangle
-                + 
-                \langle 
-                    \partial g(y_t^+), y_t^+ - y_t
-                \rangle
-                \\
-                g \text{ convex }\implies 
-                &\ge 
-                g(y_t^+) + 
-                \langle \partial g(y_t^+), x_{t + 1} - y_t^+\rangle. 
-            \end{aligned}
-            \tag{$[\star]$}
-        \end{align*}
-        In the $([\star])$ derivation, we used the convexity of $g$ where 
-        \begin{align*}
-            \langle \partial g(y_t^+), y_t - y_t^+\rangle
-            &\le g(y_t) - g(y_t^+)
-            \\
-            \langle \partial g (y_t^+), y_t^+ - y_t \rangle
-            &\le 
-            g(y_t^+) - g(y_t). 
-        \end{align*}
-        Now, adding $([*]), ([\star])$, multiply their sum by $\tilde\eta_{t + 1}$ makes it equals to $\phi_t(x_{t +1 })$ , we can establish a lower bound for $\phi_t(x_{t + 1})$, yielding inequality 
-        {\small
-            \begin{align*}
-                \phi_t(x_{t + 1})
-                &\ge 
-                \tilde\eta_{t + 1}
-                \left(
-                    f(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2 
-                    +
-                    \langle \nabla f(y_t), x_{t + 1} - y_t^+\rangle
-                    + 
-                    g(y_t^+) + 
-                    \langle \partial g(y_t^+), x_{t + 1} - y_t^+\rangle
+            - \frac{1}{2}\Vert x^+ - x\Vert^2
+            \\
+            \iff &
+            \tilde \eta (h(\mathcal T_L\bar x) - h(x_*))  
+            + 
+            \frac{1}{2}\left(
+                \Vert x^+ - x_*\Vert^2 - 
+                \Vert x - x_*\Vert^2
             \right)
             \\
-                &= 
-                \tilde\eta_{t + 1}
-                \left(
-                    h(y_t^+) - \frac{L}{2}\Vert y_t^+ - y_t\Vert^2 
-                    + 
-                    \langle \partial g(y_t^+) + \nabla f(y_t), x_{t + 1} - y_t^+\rangle
-                \right).
+            & \le 
+            \tilde \eta 
+            \langle \mathcal G_L\bar x, x^+ - \mathcal T_L \bar x\rangle
+            + 
+            \frac{\tilde \eta L}{2} \Vert \bar x - \mathcal T_L \bar x\Vert^2
+            - 
+            \frac{1}{2}\Vert x^+ - x\Vert^2. 
         \end{align*}
         }
-        Apply
-        \hyperref[lemma:grad_map_lemma_first]{lemma \ref*{lemma:grad_map_lemma_first}} 
-        we have $\partial g(y_t^+) + \nabla f(y_t) \ni \mathcal G_L(y_t)$, and by the algorithm updates $y_t^+ = z_{t + 1}$, therefore the above inequality simplifies to 
-        \begin{align*}
-            \phi_t(x_{t + 1}) &\ge 
-            \tilde\eta_{t + 1} 
-            \left(
-                h(z_{t + 1}) - 
-                \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                + 
-                \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
-            \right). 
-        \end{align*}
-        Finally, from (\hyperref[lemma:grad_map_linearization]
-            {lemma \ref*{lemma:grad_map_linearization}})
-        we have $\phi_t(u) \le \tilde\eta_{t + 1}h(u)$ for all $u$. 
-        With that we lower bound the LHS of the PPM Lyapunov inequality of $\phi_t(u)$, making: 
-        {\footnotesize
-        \begin{align*}
-            & \phi_t(x_{t + 1}) - \phi_t(x_*) + 
-            \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
-            \frac{1}{2}\Vert x_t - x_*\Vert^2
-            \le
-            \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-            \\
-            \implies &
-            \tilde \eta_{t + 1}
-            \left(
-                h(z_{t + 1}) - 
-                \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-                + 
-                \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
-            \right) - \tilde \eta_{t + 1} h(x_*)
-            +
-            \frac{1}{2}\Vert x_{t+1} - x_*\Vert^2 - 
-            \frac{1}{2}\Vert x_t - x_*\Vert^2
-            \\
-            & \quad \le
-            \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-            \\
-            \iff &
-            \tilde\eta_{t + 1}(h(z_{t + 1}) - h(x_*))
-            + \frac{1}{2}\left(
-                \Vert x_{t + 1} - x_*\Vert^2 
-                - 
-                \Vert x_t - x_*\Vert^2
-            \right) =: \Upsilon_{1, t + 1}^\text{AG}
-            \\
-            &\quad \le 
-            \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-            - 
-            \tilde\eta_{t + 1}
-            \langle \mathcal G_L(y_t), x_{t +1} - z_{t + 1}\rangle
-            + 
-            \frac{L \tilde\eta_{t + 1}}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-        \end{align*}
-        }
-        It established the first inequality that we wish to prove. 
-        Next, the smoothness of $f$ establish inequality: 
-        \begin{align*}
-            \begin{aligned}
-                f(z_{t + 1}) - f(z_t) &= f(z_{t + 1}) - f(y_t) + f(y_t) - f(z_t) 
-                \\
-                &\le 
-                \langle \nabla f(y_t), z_{t + 1} - y_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2 
-                + 
-                \langle \nabla f(y_t), y_t - z_t\rangle
-                \\
-                &= 
-                \langle \nabla f(y_t), z_{t + 1} - z_t\rangle + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-            \end{aligned}
-            \tag{$[**]$}
-        \end{align*}
-        The convexity of $h$ establish 
-        \begin{align*}
-            \begin{aligned}
-                g(z_{t + 1}) + 
-                \langle \partial g(z_{t + 1}), z_t - z_{t + 1}\rangle
-                &\le g(z_t)
-                \\
-                g(z_{t + 1}) - g(z_t)
+        Next, for all $z, z'$, it would have by smoothness of $f$: 
+        \begin{align*}
+            f(z) - f(z') &= 
+            f(z) - f(\bar x) + f(\bar x) - f(z')
+            \\
             &\le 
             \langle 
-                    \partial g (z_{t +1}), 
-                    z_{t + 1} - z_t
-                \rangle. 
-            \end{aligned}
-            \tag{$[\star *]$}    
-        \end{align*}
-        Adding $([**]), ([\star *])$ yields 
-        \begin{align*}
-            \begin{aligned}
-                \Upsilon_{2, t + 1}^{\text{AG}} := 
-                h(z_{t + 1}) - h(z_t) 
+                \nabla f(\bar x), z - \bar x
+            \rangle + 
+            \frac{L}{2}\Vert z - \bar x\Vert^2 
+            + 
+            \langle 
+                \nabla f(\bar x), 
+                \bar x - z'
+            \rangle
+            \\
+            &= 
+            \langle \nabla f(\bar x), z - z'\rangle
+            + 
+            \frac{L}{2}\Vert z - \bar x\Vert^2. 
+        \end{align*}
+        The convexity of $g$ yields: 
+        \begin{align*}
+            g(z) + 
+            \langle 
+                \partial g(z), z' - z
+            \rangle 
+            &\le g(z')
+            \\
+            g(z) - g(z') 
             &\le 
-                \langle 
-                    \nabla f(y_t) + \partial g(z_{t+1}), 
-                    z_{t + 1} - z_t
-                \rangle + 
-                \frac{L}{2}
+            \langle \partial g(z), z - z'\rangle. 
+        \end{align*}
+        Adding them yield 
+        \begin{align*}
+            h(z) - h(z') &\le 
+            \langle \nabla f(\bar x) + \partial g(z), z - z'\rangle + 
+            \frac{L}{2}\Vert z - \bar x\Vert^2. 
+        \end{align*}
+        Setting $z = \mathcal T_L \bar x$, we have the desired results. 
+    \end{proof}
+    \begin{remark}
+        This lemma is designed to work with 
+        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}.
+        Set $\bar x = y_t, x = x_t$, then 
+        \begin{align*}
+            x^+ &= x_t - \mathcal G_L y_t = x_{t + 1},
+            \\
+            z_{t + 1} &= \mathcal T_L y_t = \mathcal T_L \bar x.
+        \end{align*}
+        Set $z' = z_t, \tilde \eta = \tilde \eta_{t + 1}$, 
+        the results can be written as 
+        \begin{align*}
+            \Upsilon_{1, t + 1}^{\text{AG}}
+            &:= 
+            \tilde \eta_{t + 1}(h(z_{t + 1}) - h(x_*))
+            + 
+            \frac{1}{2}(\Vert x_{t + 1} - x_*\Vert^2 + \Vert x_t - x_*\Vert^2)
+            \\
+            &\quad \le 
+            \tilde \eta_{t + 1}\langle \mathcal G_L y_t, x_{t + 1} - z_{t + 1}\rangle
+            + 
+            \frac{\tilde \eta_{t + 1}L}{2}
             \Vert  
-                    z_{t + 1} - y_t
-                \Vert^2. 
-            \end{aligned}
-        \end{align*}
-        Using the property of gradient mapping (\hyperref[lemma:grad_map_lemma_first]
-            {lemma \ref*{lemma:grad_map_lemma_first}}), 
-        $\mathcal G_L(y_t) \in \nabla f(y_t) + \partial g(z_{t + 1})$, substituting it, we proved all we want to show. 
-    \end{proof}
+                y_t - z_{t + 1}
+            \Vert^2
+            - 
+            \frac{1}{2}
+            \Vert x_{t + 1} - x_t\Vert^2,  
+            \\ 
+            \Upsilon_{2, t + 1}^{\text{AG}}
+            &:= 
+            h(z_{t + 1}) - h(z_t) \le 
+            \langle \mathcal G_L \bar x, z_{t + 1} - z_t \rangle + 
+            \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
+        \end{align*}
+    \end{remark}
 
@@
         \begin{align*}
-            & \Phi_{t + 1} - \Phi_{t}\left(
+            & \Phi_{t + 1} - \Phi_{t} =
+            \left(
                 \sum_{i = 1}^{t} \tilde \eta_i
-            \right) =
-            \Upsilon_{2, t + 1}^{\text{AG}} + 
+            \right)\Upsilon_{2, t + 1}^{\text{AG}} + 
             \Upsilon_{1, t + 1}^{\text{AG}} 
@@
         \begin{align*}
-            S_t &:= \sum_{i = 1}^{t} \delta_i
-            \\
-            \sigma_t &:= \sum_{i = 1}^{t}\tilde \eta_i
-        \end{align*}
-        we have $\Phi_{t + 1} - \Phi_t \le \delta_{t + 1}$, it allows for a convergence rate of $\mathcal O \left(\sigma_T^{-1}S_T\right)$ of $f(z_T) - f(x_*)$ when $S_T \neq 0$ and a rate of $\mathcal O(\sigma_T^{-1})$ when $S_T = 0$.
+            S_t := \sum_{i = 1}^{t} \delta_i,
+            \quad 
+            \sigma_t := \sum_{i = 1}^{t}\tilde \eta_i, 
+        \end{align*}
+        we have $\Phi_{t + 1} - \Phi_t \le \delta_{t + 1}$, it allows for a convergence rate of $\mathcal O \left(\sigma_T^{-1}S_T\right)$ of $f(z_T) - f(x_*)$ when $S_T \neq 0$ and a rate of $\mathcal O(\sigma_T^{-1})$ when $S_T \le 0$.
     \end{theorem}
@@
         \end{enumerate}
-
     \end{theorem}

### 2024-08-14 Notebook LaTEX/Momentum Accelerations/paper.tex
/w\, fixes and changes

@@
         \hyperref[lemma:grad_map_lemma_first]{definition \ref*{lemma:grad_map_lemma_first}}, 
+        further assume that $f$ is strongly convex with index $\mu \ge 0$,
         with $x^+ = \mathcal T_L(x)$, the gradient mapping satisfies the inequality for all $z$: 
@@
             h(z) &\ge 
-            h(z) - \frac{L}{2}\Vert x - x^+\Vert^2
-            \ge h(x^+) + \langle \mathcal G_L(x), z - x\rangle. 
+            h(x^+) + \langle \mathcal G_L (x), z - x\rangle + 
+            \frac{L}{2}\Vert x - x^+\Vert^2 + \frac{\mu}{2}
+            \Vert z - x\Vert^2. 
         \end{align*}
@@
             \\
-            &f(x) + \langle \nabla f(x), z - x\rangle 
+            &
+            \frac{\mu}{2}\Vert z - x\Vert^2+ 
+            f(x) + \langle \nabla f(x), z - x\rangle 
             \le f(z), 
@@
         \end{align*}
-        Now, consider adding $g(x^+)$ to the first inequality from above we get 
-        {\footnotesize 
-        \begin{align*}
-            f(x^+) + g(x^+) 
+        Then we have the following sequence of relations 
+        \begin{align*}
+            h(x^+) &= f(x^+) + g(x^+)
+            \\&
+            \begin{aligned}
                 &\le 
-            f(x) + g(x^+) + \langle \nabla f(x), x^+ - x\rangle 
+                \left(
+                    f(x) + \langle \nabla f(x), x^+ - x\rangle
                     + \frac{L}{2}\Vert x - x^+\Vert^2
-            \\
+                \right)
+                \\
+                &\qquad  
+                + (g(z) + \langle \partial g(x^+), x^+ - z\rangle)
+            \end{aligned}
+            \\&
+            \begin{aligned}
                 &\le 
-            (f(z) - \langle \nabla f(x), z - x\rangle) + 
-            \left(g(z) - \langle \partial g(x^+), x^+ - z\rangle\right)
-            + 
-            \langle \nabla f(x), x^+ - x\rangle + \frac{L}{2}\Vert x - x^+\Vert^2
-            \\
-            &= f(z) + g(z) + \langle \nabla f(x), x - z + x^+ - x\rangle
-            + 
-            \langle \partial g(x^+), x^+ - z\rangle + \frac{L}{2}\Vert x - x^+\Vert^2
-            \\
-            &= 
-            h(z) + \langle \nabla f(x), x^+ - z\rangle + 
+                \left(
+                    f(z) - \langle \nabla f(x), z - x\rangle
+                    - \frac{\mu}{2}\Vert z - x\Vert^2
+                    + \langle \nabla f(x), x^+ - x\rangle
+                    + 
+                    \frac{L}{2}\Vert x - x^+\Vert^2
+                \right)
+                \\
+                &\qquad 
+                +
+                (g(z) + \langle \partial g(x^+), x^+ - z\rangle)
+            \end{aligned}
+            \\&
+            \begin{aligned}
+                &= 
+                (f(z) + h(z)) 
+                \\
+                &\qquad 
+                + \left(
+                    \langle \nabla f(x), x - z\rangle + 
+                    \langle \nabla f(x), x^+ - x\rangle + 
                     \langle \partial g(x^+), x^+ - z\rangle
+                \right) 
+                \\ 
+                &\qquad 
+                - \frac{\mu}{2}\Vert z - x\Vert^2
                 + \frac{L}{2}\Vert x - x^+\Vert^2
-            \\
-            &= h(z) + \langle \nabla f(x) + \partial g(x^+), x^+ - z\rangle 
-            + \frac{L}{2}\Vert x - x^+\Vert^2. 
-        \end{align*}
+            \end{aligned}
+            \\& 
+            \begin{aligned}
+                &= h(z) + 
+                \left(
+                    \langle \nabla f(x), x - x^+ + x^+ - z\rangle + 
+                    \langle \nabla f(x), x^+ - x\rangle + 
+                    \langle \partial g(x^+), x^+ - z\rangle
+                \right)
+                \\
+                &\qquad 
+                - \frac{\mu}{2}\Vert z - x\Vert^2
+                + \frac{L}{2}\Vert x - x^+\Vert^2
+            \end{aligned}
+            \\& 
+            \begin{aligned}
+                &= h(z) + 
+                \langle \nabla f(x) + \partial g(x^+), x^+ - z\rangle 
+                - \frac{\mu}{2}\Vert z - x\Vert^2
+                + \frac{L}{2}\Vert x - x^+\Vert^2
+            \end{aligned}
+            \\& 
+            \begin{aligned}
+                &= h(z) + 
+                    \langle \mathcal G_L(x), x^+ - z\rangle 
+                - \frac{\mu}{2}\Vert z - x\Vert^2
+                + \frac{L}{2}\Vert x - x^+\Vert^2
+            \end{aligned}
+            \\& 
+            \begin{aligned}
+                &= h(z) + \langle L(x - x^+), x^+ - x + x - z\rangle 
+                - \frac{\mu}{2}\Vert z - x\Vert^2
+                + \frac{L}{2}\Vert x - x^+\Vert^2
+            \end{aligned}
+            \\&
+            \begin{aligned}
+                &= h(z) + 
+                \underbrace{\langle L(x - x^+), x - z\rangle}_{
+                    = - \langle \mathcal G_L (x), z - x\rangle
                 }
-        By $\mathcal G_L(x) = L(x - x^+) \in \nabla f(x) + \partial g(x^+)$ from previous dicussion, we have 
-        \begin{align*}
-            h(x^+) &\le 
-            h(z) + \langle \mathcal G_L(x), x^+ - z\rangle + \frac{L}{2}\Vert x - x^+\Vert^2
-            \\
-            &= h(z) - \langle L(x^+ - x), x^+ - x + x - z \rangle 
-            + 
-            \frac{L}{2}\Vert x - x^+\Vert^2
-            \\
-            &= 
-            h(z) - L\Vert x^+ - x\Vert^2 
-            + L \langle x^+ - x, x - z\rangle
-            + \frac{L}{2}\Vert x - x^+\Vert^2
-            \\
-            &= h(z) + \langle \mathcal G_L(x), x - z\rangle - 
-            \frac{L}{2}\Vert x - x^+\Vert^2. 
-        \end{align*}
-        Therefore, the inequality is justified. 
+                - \frac{\mu}{2}\Vert z - x\Vert^2
+                - \frac{L}{2}\Vert x - x^+\Vert^2
+            \end{aligned}. 
+        \end{align*}
+        Moving everything except $h(z)$ from the RHS to the LHS yield the desired inequality. 
     \end{proof}
@@
         Geometrically, it's tilted and it ``prefers" the sharp corners of a convex function, if, $x$ is close to a sharp corner.
+
     \end{remark}
@@
         \begin{aligned}
-            l_h(x; y) &= h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle \le h(x), 
+            l_h(x; y) &= h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle 
+                + \frac{L}{2}\Vert y - \mathcal T_L y\Vert^2
+            \le h(x), 
         \end{aligned}
@@
         \end{align*}
+        It will be used next. 
     \end{remark}

### 2024-08-15 Notebook LaTEX/Momentum Accelerations/paper.tex
/w\, work home sync
=w=, a lot of changes

@@
     Classical analysis and extension of Nesterov accelerated gradient existed. 
-    See \cite*{guler_new_1992} for an extension of the Nesterov accelerated gradient method to the proximal point method for convex programming. 
-    However the classical analysis found in \cite*[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and cherry picked Nesterov's estimating sequence to assist the proof for the parameters in the algorithm.
+    See \cite{guler_new_1992} for an extension of the Nesterov accelerated gradient method to the proximal point method for convex programming. 
+    However the classical analysis found in \cite[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and cherry picked Nesterov's estimating sequence to assist the proof for the parameters in the algorithm.
     In Ahn's work however, the complexities are packaged into the PPM interpretation of accelerated gradient. 
@@
     \par
-    Numerous notable variations of Nesterov accelerated gradient exists. \cite*[(6.1.19)]{nesterov_lectures_2018} described a variant of accelerated gradient restricted to a convex domain $Q$. 
+    Numerous notable variations of Nesterov accelerated gradient exists. \cite[(6.1.19)]{nesterov_lectures_2018} described a variant of accelerated gradient restricted to a convex domain $Q$. 
     Beck and Toubolle \cite{beck_fast_2009} introduced a variant the problem type of smooth plus non-smooth, known as FISTA. 
@@
 \section{Preliminaries}\label{sec:preliminaries}
-    Fristly, recall the theorem: 
+    In this section we introduce the a descent lemma for Proximal Point Method (PPM) in the convex case. 
+    We define the proximal gradient mapping $\mathcal T_L$, and gradient mapping $\mathcal G_L$ for function satisfying assumption 
+    \ref*{assumption:smooth-nonsmooth-sum}. 
+    A lower bound function is identified using the gradient mapping operator and proved in lemma 
+    \ref*{lemma:grad_map_linearization}, 
+    this is a key component of the proximal point interpretation of the accelerated gradient method. 
+    \begin{assumption}\label{assumption:smooth-nonsmooth-sum}
+        Let $h = f + g$ where $f, g$ are convex and $f$ is Lipschitz-Smooth. 
+    \end{assumption}
+
     \begin{theorem}[Proximal Descent Inequality]\label{thm:ppm_descent_ineq}
-        With $f: \RR^n \mapsto \overline \RR^n$ $\beta$ stronly convex where $\beta \ge 0$, fix any $x \in \RR^n$, let $p = \hprox_f(x)$, then for all $y$ we have inequality 
+        Let $f: \RR^n \mapsto \overline \RR^n$ $\beta$ be strongly convex with $\beta \ge 0$, fix any $x \in \RR^n$, define $p = \hprox_f(x)$.
+        For all $y \in \RR$ it verifies
         $$
@@
     \end{remark}
-    We introduce some additional lemma that are crucial to the derivations of non-smooth accelerated gradient method. 
+
     \begin{definition}[The Gradient Mapping]
         \label{def:gradient_mapping}
-        Let $g = f + g$ where $f$ is $L$-Lipschitz smooth and convex, $g$ is convex. 
+        Suppose $h = f + g$ satisfies 
+        \hyperref[assumption:smooth-nonsmooth-sum]{assumption \ref*{assumption:smooth-nonsmooth-sum}}. 
         Define the proximal gradient operator
@@
         $$
-        then the gradient mapping is defined as
+        and the gradient mapping operator
         $$
@@
     \begin{lemma}[Gradient Mapping Approximates Subgradient]
-        \label{lemma:grad_map_lemma_first}
-        Continue from 
-        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}, 
-        the gradient mapping satisfies
+        Suppose $h = f + g$ satisfies 
+        \hyperref[assumption:smooth-nonsmooth-sum]{assumption \ref{assumption:smooth-nonsmooth-sum}}, 
+        let $\mathcal T_L, \mathcal G_L$ be given by 
+        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}.
+        Then for all $x$, the gradient mapping verifies
         \begin{align*}
@@
             \\
-            L(x - x^+) &\in  \nabla f(x) + \partial g(x^+) \ni \mathcal G_L(x). 
+            \mathcal G_L(x) = L(x - x^+) &\in  \nabla f(x) + \partial g(x^+). 
         \end{align*}
@@
     \begin{proof}
+        Using the resolvent definition of the proximal gradient operator and the fact that the single-valuedness in the convex settings, $x^+$ has relations: 
         \begin{align*}
@@
     \label{lemma:grad_map_linearization}
-        Continue from 
-        \hyperref[lemma:grad_map_lemma_first]{definition \ref*{lemma:grad_map_lemma_first}}, 
-        further assume that $f$ is strongly convex with index $\mu \ge 0$,
-        with $x^+ = \mathcal T_L(x)$, the gradient mapping satisfies the inequality for all $z$: 
+        Suppose that $h = f + g$ satisfies 
+        \hyperref[assumption:smooth-nonsmooth-sum]{assumption \ref*{assumption:smooth-nonsmooth-sum}}, 
+        further assume that $f$ is strongly convex with index $\mu \ge 0$. 
+        Let $x^+ = \mathcal T_L(x)$ as given in 
+        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}. 
+        Then for all $z \in \RR$, it satisfies
         \begin{align*}
@@
     \begin{proof}
-        Directly from the $L$-smoothness of $f$, convexity of $g, f$, we have the list of inequalities: 
+        Using the $L$-smoothness of $f$ and convexity of $g, f$, it has inequalities
         \begin{align*}
@@
         \end{align*}
-        Then we have the following sequence of relations 
+        Apply the above by considering the following sequence of relations
         \begin{align*}
@@
         Geometrically, it's tilted and it ``prefers" the sharp corners of a convex function, if, $x$ is close to a sharp corner. 
-
+        The inequality is analogous to \cite[(2.2.57)]{nesterov_lectures_2018}. 
     \end{remark}
@@
 \section{The PPM interpreation of accelerated gradient}\label{sec:ppm_interp_of_ag}
-    In this section, we state the PPM formulation of the accelerated proximal gradient method. 
-    The formulation is abstract because the parameters are not yet determined. 
+    In this section, we present the PPM formulation of the accelerated proximal gradient method. 
+    These interpretations of \cite{ahn_understanding_2022} are extension in the non-smooth context using the proximal gradient mapping operator. 
+    The next definition starts the discussion. 
+    \begin{definition}[Linear Lower Bounding Function]\label{def:gradmap-linear-lowerbnd-fxn}
+        Let $h = f+ g$ satisfies
+        \hyperref[assumption:smooth-nonsmooth-sum]{definition \ref*{assumption:smooth-nonsmooth-sum}}, 
+        $\mathcal G_L$ given by 
+        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}. 
+        Define for all $y$ the function
+        \begin{align*}
+            l_h(x; y) = h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle 
+            + \frac{L}{2}\Vert y - \mathcal T_L y\Vert^2. 
+        \end{align*}
+    \end{definition} 
+    \begin{remark}
+        The function satisfies $l_h(x; y) \le h(x)$ for all $x \in \RR, y \in \RR$ by 
+        \hyperref[lemma:grad_map_linearization]
+        {lemma \ref*{lemma:grad_map_linearization}}. 
+    \end{remark}
+    \par
+    With the above definition, it's possible to formulate a generic form of accelerated gradient method using $l_h(x,y)$ as two proximal point methods anchored at some iterates $x_t, x_{t + 1}$.
+    The formulation is generic because of undetermined stepsize parameter $\eta_t, \tilde \eta_t$ from the two proximal point. 
+    \par
+    We state the PPM interpretation of accelerated gradient in 
+    \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}, 
+    which has the equivalent form as presented in
+    \hyperref[def:ag_prox_grad_generic]
+    {definition \ref*{def:ag_prox_grad_generic}}. 
+    \hyperref[prop:derive_ag_prox_grad_tript]
+    {Proposition \ref*{prop:derive_ag_prox_grad_tript}} 
+    shows their equivalence. 
+    \par
+    Throughout this section, we assume 
+    \begin{enumerate}
+        \item $h=f + g$ satisfies 
+            \hyperref[assumption:smooth-nonsmooth-sum]
+            {assumption \ref*{assumption:smooth-nonsmooth-sum}}, 
+        \item Using $h$ as given from above, let $\mathcal T_L, \mathcal G_L$ be given by 
+            \hyperref[def:gradient_mapping]
+            {definition \ref*{def:gradient_mapping}}. 
+        \item Using all above, let $l_h$ be given by 
+            \hyperref[def:gradmap-linear-lowerbnd-fxn]
+            {definition \ref*{def:gradmap-linear-lowerbnd-fxn}}. 
+    \end{enumerate}
+
     \begin{definition}[AG Proximal Gradient PPM Generic Form]
     \label{def:ag_prox_grad_ppm}
-        Let $h=f + g$ be the sum of convex function $g$ and convex differentiable $f$ with $L$-Lipschitz gradient. 
-        With $\mathcal T_L, \mathcal G_L$ being the proximal gradient, and the gradient mapping operator. 
-        Define the linear lower bounding function for $h$ at $y$, for all $x$: 
-        $$
-        \begin{aligned}
-            l_h(x; y) &= h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle 
-                + \frac{L}{2}\Vert y - \mathcal T_L y\Vert^2
-            \le h(x), 
-        \end{aligned}
-        $$
-        with that we define the algorithm:
+        Define $\eta_t, \tilde \eta_t$ to be $> 0$ for all $t \in \N$. 
+        With initial iterate $x_0, y_0$, 
+        The generic form has iterates $x_t, y_t$ for all $t \in \N$ that satisfy: 
         $$
@@
         $$
+
     \end{definition}
@@
     \label{def:ag_prox_grad_generic}
-        With $h = f + g$, where $g$ is convex, $f$ is convex and $L$-Lipschitz smooth. 
-        Define $x^+ = \mathcal T_L(x)$, so that $\mathcal G_L(x) = L(x -  x^+)$, we define the algorithm updates $(y_t, x_{t + 1}, z_{t + 1})$ with expression: 
+        Define $\eta_t, \tilde \eta_t$ to be $> 0$ for all $t \in \N$. 
+        With initial iterate $x_0, y_0$.
+        The generic form has iterates $(y_t, x_{t + 1}, z_{t + 1})$ such that 
         $$
@@
             \\
-            x_{t + 1} &= x_t - \tilde \eta \mathcal G_L(y_t)
+            x_{t + 1} &= x_t - \tilde \eta_{t + 1} \mathcal G_L(y_t)
             \\
@@
         $$
-        for all $t\in \mathbb N$ where the base case has $y_0 = x_0$. 
+        for all $t\in \mathbb N$. 
     \end{definition}
@@
 
-    \begin{proposition}[Deriving Proximal Gradient Generic Form]
+    \begin{proposition}
     \label{prop:derive_ag_prox_grad_tript}
-        \quad \\
-        Continue from the proximal point interpretation of the proximal gradient 
-        (\hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}})
-        we have the equalities 
+       We have equalities
         \begin{align*}
@@
         \end{align*}
-        Therefore, the algorithm in
+        This thows
         \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}
-        is equivalent to algorithm in
+        and 
         \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}} 
+        are equivalent. 
     \end{proposition}
     \begin{proof}
-        Let $y_t^+ = \mathcal T_L(y_t)$, recall that $l_h(x; y_t) = h(y_t^+) + \langle \mathcal G_L(y_t), x -y_t\rangle \le f(x)$ by the definition of algorithm. 
+        Let $y_t^+ = \mathcal T_L(y_t)$, recall that $l_h(x; y_t) = h(y_t^+) + \langle \mathcal G_L(y_t), x -y_t\rangle \le f(x)$ by 
+        \hyperref[lemma:grad_map_linearization]
+        {lemma \ref*{lemma:grad_map_linearization}}
         Since $l_h(x; y_t)$ is a simple linear function wrt $x$, minimizing the quandratic where to get $x_{t + 1} = x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t)$; for $y_{t + 1}$, complete the square on the second and the third terms:
@@
     {definition \ref*{def:ag_prox_grad_generic}}
-    \begin{lemma}[Lyapunov Inequality]
+    \begin{lemma}[Lyapunov Inequality]. 
+    The Lypunov function in use is identical to Ahn and Sra \cite[section 4.2]{ahn_understanding_2022} except for the involvement of a gradient mapping. 
+    We present the results differently by compatifying results into 
+    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
+    {lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}. 
+    Theorem \ref*{thm:generic_ag_convergence} 
+    states new results that are extension to Ahn and Sra's works by introducing an error term to the Lypunov analysis, allowing for a weaker constraints for the stepsize paramters $\tilde \eta_i, \eta_i$ from
+    \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}. 
+    \par
+    Theorem \ref*{thm:ag_generic_stepsize_constrants} states the weakened constraints on the stepsize parameters $\tilde \eta_i, \eta_i$.
+
     \label{lemma:nsmooth_agg_lyapunov_upper_bound}\;\\
@@
             x^+ &:= 
-            \prox{\phi}(x) = x - \tilde \eta\mathcal G_L \bar x. 
+            \hprox_\phi(x) = x - \tilde \eta\mathcal G_L \bar x. 
         \end{align*}
@@
             &\quad \le 
-            \tilde \eta 
-            \langle \mathcal G_L\bar x, x^+ - \mathcal T_L \bar x\rangle
+            - \tilde \eta \langle \mathcal G_L\bar x, x^+ - \mathcal T_L \bar x\rangle
             + 
@@
             & \le 
-            \tilde \eta 
-            \langle \mathcal G_L\bar x, x^+ - \mathcal T_L \bar x\rangle
+            - \tilde \eta \langle \mathcal G_L\bar x, x^+ - \mathcal T_L \bar x\rangle
             + 
@@
             &\quad \le 
-            \tilde \eta_{t + 1}\langle \mathcal G_L y_t, x_{t + 1} - z_{t + 1}\rangle
+            - \tilde \eta_{t + 1}\langle \mathcal G_L y_t, x_{t + 1} - z_{t + 1}\rangle
             + 
@@
             &= 
-            - \frac{1}{2}\Vert \tilde\eta_{t + 1} \mathcal G_L\Vert^2 + 
+            - \frac{1}{2}\Vert \tilde\eta_{t + 1} \mathcal G_L(y_t)\Vert^2 + 
             \frac{\tilde\eta_{t + 1}L}{2}\Vert L^{-1} \mathcal G_L(y_t)\Vert^2
@@
                 a_{t + 1} = (1/2)\left(
-                1 - \epsilon_{t + 2} + \sqrt{(1 - \epsilon_{t + 2}) + 4 c_{t + 2}}
+                1 - \epsilon_{t + 2} + \sqrt{(1 - \epsilon_{t + 2}) + 4 c_{t + 1}}
                 \right), 
@@
 
-\printbibliography
+% \printbibliography
+
+\bibliographystyle{siam}
+\bibliography{references/refs}
+
 \end{document}

### 2024-08-15 Notebook LaTEX/Momentum Accelerations/paper.tex
TwT, a lot of changes

@@
         Subject type, Some Department of Some University, Location of the University,
-        Country. E-mail: \texttt{author.name@university.edu}.
+        Country. E-mail: \texttt{alto@mail.ubc.ca}.
     }
@@
 \label{sec:generic_ag_ppm_lyapunov_analysis}
-    The following lemma establish an upper bound for quantities used in the Lypunov functions for the convergence rate of 
-    \hyperref[def:ag_prox_grad_generic]
-    {definition \ref*{def:ag_prox_grad_generic}}
+    In this section we derive the generic convergence rate formuated by $\eta_i, \tilde \eta_i$. 
+    \par
+    The Lypunov function in 
+    \hyperref[thm:generic_ag_convergence]{\ref*{thm:generic_ag_convergence}}
+    is identical to Ahn and Sra 
+    \cite[section 4.2]{ahn_understanding_2022}, 
+    except for the involvement of the gradient mapping. 
+    We adapated it into the context of proximal gradient by 
+    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
+    {lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}
+    \par
+    We present the convergence rate by compatifying results into 
+    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
+    {lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}} 
+    to assist the proof of  
+    \hyperref[thm:generic_ag_convergence]
+    {Theorem \ref*{thm:generic_ag_convergence}} 
+    which states new results that are extension to Ahn and Sra's works by introducing an error term to the Lypunov analysis, allowing for a weaker constraints for the stepsize paramters $\tilde \eta_i, \eta_i$ from
+    \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}. 
+    \hyperref[thm:ag_generic_stepsize_constraints]{Theorem \ref*{thm:ag_generic_stepsize_constraints}}
+    states the weakened constraints on the stepsize parameters $\tilde \eta_i, \eta_i$. 
+    \par
+    Through out this section, we continue the assumption for $h = f + g$ and gradient mapping $\mathcal G_L$ the same as previous section.
+
     \begin{lemma}[Lyapunov Inequality]. 
-    The Lypunov function in use is identical to Ahn and Sra \cite[section 4.2]{ahn_understanding_2022} except for the involvement of a gradient mapping. 
-    We present the results differently by compatifying results into 
-    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
-    {lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}. 
-    Theorem \ref*{thm:generic_ag_convergence} 
-    states new results that are extension to Ahn and Sra's works by introducing an error term to the Lypunov analysis, allowing for a weaker constraints for the stepsize paramters $\tilde \eta_i, \eta_i$ from
-    \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}. 
-    \par
-    Theorem \ref*{thm:ag_generic_stepsize_constrants} states the weakened constraints on the stepsize parameters $\tilde \eta_i, \eta_i$.
-
     \label{lemma:nsmooth_agg_lyapunov_upper_bound}\;\\
-        Let $h = f + g$ be a sum of $f$ that is $L$-Lipschitz smooth convex, and $g$ be convex.
         Fix any $\bar x, x, \tilde\eta > 0$, define
@@
     \begin{remark}
-        This lemma is designed to work with 
-        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}.
+    \label{remark:upsilon-upperbound-for-iterates}
+        Let $y_t, x_t$ be given by
+        \hyperref[def:ag_prox_grad_generic]
+        {definition \ref*{def:ag_prox_grad_generic}}.
         Set $\bar x = y_t, x = x_t$, then 
@@
     \label{thm:generic_ag_convergence}
-        Define the Lyapunov function $\Phi_t\; \forall t \in \{0\}\cup \N$: 
-        \begin{align*}
-            \Phi_t &= \left(
+        Let $\Upsilon_{1, t + 1}^\text{AG}, \Upsilon_{2, t + 1}^\text{AG}$ be given by 
+        \hyperref[remark:upsilon-upperbound-for-iterates]
+        {remark \ref*{remark:upsilon-upperbound-for-iterates}}. 
+        Let $z_t$ be given by 
+        \hyperref[def:ag_prox_grad_generic]
+        {definition \ref*{def:ag_prox_grad_generic}}
+        Define the Lyapunov function $\Phi_t\; \forall t \in \{0\}\cup \N$, $S_t$ and $\sigma_t$: 
+        \begin{align*}
+            \Phi_t &:= \left(
                 \sum_{i = 1}^{t} \tilde\eta_{i}
-            \right) (f(z_t) - f(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \NN
-            \\
-            \Phi_0 &= \frac{1}{2}\Vert x_0 - x_*\Vert^2, 
-        \end{align*}
-        if there is a choice of $\eta_i, \tilde \eta_i$ in 
-        \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}} such that we have 
+            \right) (h(z_t) - h(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \N
+            \\
+            \Phi_0 &:= \frac{1}{2}\Vert x_0 - x_*\Vert^2, 
+            \\
+            S_t &:= \sum_{i = 1}^{t} \delta_i \quad \forall t \in \N,
+            \\
+            \sigma_t &:= \sum_{i = 1}^{t}\tilde \eta_i \quad \forall t \in \N. 
+        \end{align*}
+        If there exists a sequence of $\eta_i, \tilde \eta_i$ as defined in
+        \hyperref[def:ag_prox_grad_ppm]
+        {definition \ref*{def:ag_prox_grad_ppm}} 
+        such that
         \begin{align*}
@@
                 \sum_{i = 1}^{t} \tilde \eta_i
-            \right)\Upsilon_{2, t + 1}^{\text{AG}} + 
+            \right)\Upsilon_{2, t + 1}^{\text{AG}} 
+            + 
             \Upsilon_{1, t + 1}^{\text{AG}} 
@@
         \end{align*}
-        Then with
-        \begin{align*}
-            S_t := \sum_{i = 1}^{t} \delta_i,
-            \quad 
-            \sigma_t := \sum_{i = 1}^{t}\tilde \eta_i, 
-        \end{align*}
-        we have $\Phi_{t + 1} - \Phi_t \le \delta_{t + 1}$, it allows for a convergence rate of $\mathcal O \left(\sigma_T^{-1}S_T\right)$ of $f(z_T) - f(x_*)$ when $S_T \neq 0$ and a rate of $\mathcal O(\sigma_T^{-1})$ when $S_T \le 0$.
+        for some $\delta_i, i \in \N$. 
+        Then 
+        \begin{align*}
+            h(z_T) - h(x_*) &\le 
+            \sigma_T^{-1}\left(
+                S_{T} + \frac{1}{2}\Vert x_0 - x_*\Vert^2
+            \right). 
+        \end{align*}
+        Where $x_*$ is an minimizer of $h$. 
+        So $h(z_T) - h(x_*)$ has convergence rate $\mathcal O(\sigma_T^{-1})$ when $S_T \le 0$, and $\mathcal O(\sigma_T^{-1}S_T)$ when $S_T > 0$. 
     \end{theorem}
@@
                 \sum_{i = 1}^{t+1} \tilde\eta_{i}
-            \right) (f(z_{t + 1}) - f(x_*)) 
+            \right) (h(z_{t + 1}) - h(x_*)) 
             - 
@@
                 \sum_{i = 1}^{t} \tilde\eta_{i}
-            \right) (f(z_{t}) - f(x_*)) 
+            \right) (h(z_{t}) - h(x_*)) 
             + \frac{1}{2}\Vert x_t - x_*\Vert^2
@@
             &= 
-            \tilde \eta_{t + 1} (f(z_{t + 1}) - f(z_*))
+            \tilde \eta_{t + 1} (h(z_{t + 1}) - h(z_*))
             +
@@
                 \sum_{i = 1}^{t} \tilde \eta_i
-            \right)(f(z_{t + 1}) - f(z_t))
+            \right)(h(z_{t + 1}) - h(z_t))
             + \frac{1}{2}\Vert x_t - x_*\Vert^2
@@
         }
-        Telescoping we have 
-        \begin{align*}
-            \Phi_{t + 1} - \Phi_t &\le \delta_{t + 1}
-            \\
-            \sum_{i = 0}^{T - 1}\Phi_{i + 1} - \Phi_i &\le \sum_{i = 0}^{T - 1}\delta_{i + 1}
-            \\
-            \Phi_T - \Phi_0 &\le 
-            \sum_{i = 1}^{T}\delta_i = S_{T}. 
+        Telescoping for $t = 0, \cdots, T- 1$
+        \begin{align*}
+            \Phi_T - \Phi_0 = 
+            \sum_{i = 0}^{T - 1}\Phi_{i + 1} - \Phi_i 
+            &\le 
+            \sum_{i = 0}^{T - 1}\delta_{i + 1}
+            = S_{T}. 
         \end{align*}
@@
         \begin{aligned}
-            \sigma_T (f(z_t) - f(x_*)) 
+            \sigma_T (h(z_T) - h(x_*)) 
             + \frac{1}{2}\Vert x_t - x_*\Vert^2 
@@
             \implies 
-            \sigma_T(f(z_t) - f(x_*))
+            \sigma_T(h(z_T) - h(x_*))
             &\le 
@@
             \\
-            f(z_t) - f(x_*) &\le 
+            h(z_T) - h(x_*) &\le 
             \sigma_T^{-1}\left(
@@
 
-    \begin{theorem}[Constraints on the PPM stepsize sequence]
-        \label{thm:ag_generic_stepsize_constrants}
-        \;\\
-        Algorithm formulated in 
-        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
-        converges if the stepsize sequence $\eta_i, \tilde \eta_{i}$ satisfies
+    \begin{theorem}[Constraints of PPM stepsize sequence]
+    \label{thm:ag_generic_stepsize_constraints}\;\\
+        Let iterates: $z_t, x_t, y_t$. 
+        \hyperref[def:ag_prox_grad_generic]
+        {definition \ref*{def:ag_prox_grad_generic}}. 
+        If the stepsize $\eta_i, \tilde \eta_i$ satisfies relations 
         \begin{align*}
@@
         \end{align*}
-        Here $\epsilon_{t + 1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$ is a sequence made to characterizing the error between $\tilde \eta_{t + 1}, \eta_t - L^{-1}$. 
-        Then the convergence rate can be formulated by
+        Then for all $t \in \N$
+        $$
+            \epsilon_{t + 1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}, 
+        $$
+        and 
         \begin{align*}
@@
         \end{align*}
-        When $\epsilon_t = 0 \;\forall t\in \mathbb N$, the sequence $a_t:= a_t = 1 + L \eta_t = \tilde \eta_{t + 1} - \epsilon_{t + 1}$, the relation simplies to: 
-        \begin{align*}
-            \begin{cases}
-                a_{t + 1} = (1/2)\left(
-                1 + \sqrt{1 + 4 c_{t + 1}}
-                \right), 
-                \\
-                c_{t + 1} = a_t^2.     
-            \end{cases}
-        \end{align*}
-        As a consequence: 
-        \begin{enumerate}
-            \item It makes $\delta_{t} = 0$ in the Lypunov analysis; 
-            \item it simplifies the algorithm to FISTA. 
-            \item and $a_t$ is the famous Nesterov momentum sequence. 
-        \end{enumerate}
     \end{theorem}
@@
         From 
-        \hyperref[thm:ag_generic_stepsize_constrants]{theorem \ref*{thm:ag_generic_stepsize_constrants}}, 
+        \hyperref[thm:ag_generic_stepsize_constraints]
+        {theorem \ref*{thm:ag_generic_stepsize_constraints}}, 
         setting $\epsilon_i = 0$ for all $i$ yields $a_t = 1 + L\eta_t = \tilde \eta_{t + 1}$, for all $t \in \N$ where $a_t$ is the Nesterov sequence.
@@
             Where we proved in 
-            \hyperref[thm:ag_generic_stepsize_constrants]
-                {theorem \ref*{thm:ag_generic_stepsize_constrants}}
+            \hyperref[thm:ag_generic_stepsize_constraints]
+                {theorem \ref*{thm:ag_generic_stepsize_constraints}}
             that $a_t$ is the Nesterov momentum sequence. 

### 2024-08-15 Notebook LaTEX/Momentum Accelerations/paper.tex
/w\, work home sync

@@
     Our work suggests a proximal point interpretation of accelerated gradient method for the method of accelerated proximal gradient method as a major extension to the interpretation proposed by Ahn and Sra \cite{ahn_understanding_2022}.
-    The proofs had been streamlined, extended and new error terms are added to allow a larger set of stepsize sequence for the PPM. 
-    Additionally, we proposed a line search method to dynamically adjust the strong convexity index $\mu$ and Lipschitz constant of the gradient in algorithm implementations based on the PPM understanding, with numerical experiments.
+    The proofs had been streamlined, extended and new error terms are added to allow a larger set of stepsize sequence for the proximal point interpreation. 
+    Additionally, we conduct numerical experiment for a line search method that dynamically adjust the strong convexity index $\mu$ and Lipschitz constant of the gradient in for algorithm  using the proximal point understanding of accelerated gradient.
 
@@
     Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
-    They explored the interpretation of Nesterov acceleration as a proximal of an upper surrogate function, and then a lower surrogate function. 
-    Inspired by such an interpretation, we generalize the framework to the case of $h = f + g$ with $f$ Lipschitz smooth and $g$ convex and friendly to a proximal operator. 
+    Ahn and Sra explored the interpretation of Nesterov acceleration as the proximal point method applied to an upper surrogate function, and then a lower surrogate function. 
+    Inspired by the interpretation, we generalize the framework to the case of $h = f + g$ with $f$ Lipschitz smooth and $g$ convex whose proximal mapping can be evaluated exactly for algorithm implementations.
     \par
-    Classical analysis and extension of Nesterov accelerated gradient existed. 
+    Classical analysis and extension of Nesterov accelerated gradient exist in the literatures. 
     See \cite{guler_new_1992} for an extension of the Nesterov accelerated gradient method to the proximal point method for convex programming. 
     However the classical analysis found in \cite[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and cherry picked Nesterov's estimating sequence to assist the proof for the parameters in the algorithm.
-    In Ahn's work however, the complexities are packaged into the PPM interpretation of accelerated gradient. 
+    In Ahn's work however, the complexities are packaged into the proximal point interpretation of accelerated gradient. 
     It uses a lemma from Moreau envelope to derive the Lypunov analysis, the sizes, and parameters for several variants of the algorithm. 
@@
     For a variant of accelerated gradient where the iterates converge, see \cite{chambolle_convergence_2015}. 
-    Extension such as the Harpen acceleration for the resolvent operator in general is outside of the scope since doesn't have a Moreau envelope. 
+    Extension such as the Harpen acceleration for the resolvent operator in general is outside of the scope since it doesn't have a Moreau envelope. 
     \par
@@
     The dynamical system interpretation of the algorithm however, lead to the valuable insights that restarting the accerlated gradient algorithm would lead to faster convergence rate for the class of strongly convex function.
-    \par
+
+    % \par
     % The paper is organized as follow: 
@@
     In this section we introduce the a descent lemma for Proximal Point Method (PPM) in the convex case. 
-    We define the proximal gradient mapping $\mathcal T_L$, and gradient mapping $\mathcal G_L$ for function satisfying assumption 
-    \ref*{assumption:smooth-nonsmooth-sum}. 
-    A lower bound function is identified using the gradient mapping operator and proved in lemma 
-    \ref*{lemma:grad_map_linearization}, 
+    We define the proximal gradient mapping $\mathcal T_L$, and gradient mapping $\mathcal G_L$ for function satisfying 
+    \hyperref[assumption:smooth-nonsmooth-sum]
+    {assumption \ref*{assumption:smooth-nonsmooth-sum}}. 
+    A lower bound function is identified using the gradient mapping operator and proved in
+    \hyperref[lemma:grad_map_linearization]{lemma \ref*{lemma:grad_map_linearization}}, 
     this is a key component of the proximal point interpretation of the accelerated gradient method. 
@@
         We use this theorem to prove the convergence of the proximal point method. 
-        See the proof (\cite{bauschke_convex_2017}, theorem 12.26). 
+        The proof can be found in \cite[theorem 12.26]{bauschke_convex_2017}. 
     \end{remark}
@@
     \begin{lemma}[Gradient Mapping Approximates Subgradient]
+    \label{lemma:grad-map-approx-subgrad}\; \\
         Suppose $h = f + g$ satisfies 
@@
     \begin{lemma}[Linearized Gradient Mapping Lower Bound]
-    \label{lemma:grad_map_linearization}
+    \label{lemma:grad_map_linearization}\; \\
         Suppose that $h = f + g$ satisfies 
@@
         Geometrically, it's tilted and it ``prefers" the sharp corners of a convex function, if, $x$ is close to a sharp corner. 
-        The inequality is analogous to \cite[(2.2.57)]{nesterov_lectures_2018}. 
+        The inequality is analogous to \cite[(2.2.57)]{nesterov_lectures_2018}, however Nesterov stated it only for the case when $g$ is an indicator function of some convex set $Q$. 
     \end{remark}
@@
 \section{The PPM interpreation of accelerated gradient}\label{sec:ppm_interp_of_ag}
-    In this section, we present the PPM formulation of the accelerated proximal gradient method. 
-    These interpretations of \cite{ahn_understanding_2022} are extension in the non-smooth context using the proximal gradient mapping operator. 
-    The next definition starts the discussion. 
+    In this section, we present the generic PPM formulation of the accelerated proximal gradient method. 
+    This is general form presents us with a set of undetermine stepsize parameters $\eta_i, \tilde \eta_i$ that can be changed later to accomodate proofs that take Lypunov functions and phrase the convergence rate using the stepsizes sequence $\tilde \eta_i$.
+    These interpretations are extension in the non-smooth context of Ahn and Sra's work \cite{ahn_understanding_2022} using the proximal gradient mapping operator. 
+    The next definition will start the discussion. 
     \begin{definition}[Linear Lower Bounding Function]\label{def:gradmap-linear-lowerbnd-fxn}
@@
     \par
-    Through out this section, we continue the assumption for $h = f + g$ and gradient mapping $\mathcal G_L$ the same as previous section.
+    Throughout the section, we continue the assumption for $h = f + g$, gradient mapping $\mathcal G_L$ and proximal gradient mapping $\mathcal T_L$ from the previous section.
 
@@
         \end{align*}
-        Setting $z = \mathcal T_L \bar x$, we have the desired results. 
+        Setting $z = \mathcal T_L \bar x$, use 
+        \hyperref[lemma:grad-map-approx-subgrad]
+        {lemma \ref*{lemma:grad-map-approx-subgrad}}, 
+        to give the desired results. 
     \end{proof}
@@
         \hyperref[def:ag_prox_grad_generic]
-        {definition \ref*{def:ag_prox_grad_generic}}
+        {definition \ref*{def:ag_prox_grad_generic}}. 
         Define the Lyapunov function $\Phi_t\; \forall t \in \{0\}\cup \N$, $S_t$ and $\sigma_t$: 
         \begin{align*}
+            \Phi_0 &:= \frac{1}{2}\Vert x_0 - x_*\Vert^2, 
+            \\
             \Phi_t &:= \left(
                 \sum_{i = 1}^{t} \tilde\eta_{i}
-            \right) (h(z_t) - h(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \N
-            \\
-            \Phi_0 &:= \frac{1}{2}\Vert x_0 - x_*\Vert^2, 
+            \right) (h(z_t) - h(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \N,
             \\
@@
         \end{align*}
-        If there exists a sequence of $\eta_i, \tilde \eta_i$ as defined in
+        If there exists a sequence of $(\eta_i)_{i \in \N}$ as defined in
         \hyperref[def:ag_prox_grad_ppm]
@@
     \label{thm:ag_generic_stepsize_constraints}\;\\
-        Let iterates: $z_t, x_t, y_t$. 
+        Let iterates $z_t, x_t, y_t$ be given by
         \hyperref[def:ag_prox_grad_generic]
@@
             \sigma_t\Upsilon_{1, t + 1}^{\text{AG}}
-            &\le \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}.
-        \end{align*}
+            &\le
+            \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2.
+        \end{align*}
+        Define $\delta_{t + 1} = \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2$. 
+        Then the convergence rate stated in 
+        \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}
+        applies. 
     \end{theorem}
@@
         (as formulated in 
-        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
-        ) for $t\in \mathbb N$ it has: 
+        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}) 
+        for $t\in \mathbb N$ it has: 
         \begin{align*}
@@
         Recall the upper bounds from 
-        \ref*{thm:generic_ag_convergence}, 
+        \hyperref[remark:upsilon-upperbound-for-iterates]
+        {remark \ref*{remark:upsilon-upperbound-for-iterates}}
         it has 
@@
                 x_{t + 1} - z_{t + 1}
-            \rangle
+            \rangle, 
             \\
@@
         \end{align*}
-        By the updates, vector $x_{t + 1} - x_t$ and $z_{t + 1} - y_t$ are parallel by observations: 
+        Because the iterates are produced by 
+        \hyperref[def:ag_prox_grad_generic]
+        {definition \ref*{def:ag_prox_grad_generic}}
+        vector $x_{t + 1} - x_t$ and $z_{t + 1} - y_t$ are parallel by observations: 
         \begin{align*}
@@
             \Upsilon_{2, t + 1}^{\text{AG}} 
-            &= 
+            &\le 
             \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
@@
 We make the choice to do surgery on upper bound of $\Upsilon_{2, t + 1}^\text{AG}$, so $\langle \mathcal G_L(y_t), y_t - x_t\rangle = \langle \mathcal G_L(y_t), L \eta_t (z_t - y_t)\rangle$.
-        With this in mind, RHS of $\phi_{t + 1} - \phi_t$ yields: 
+        With this in mind, RHS of $\Phi_{t + 1} - \Phi_t$ yields: 
         {\footnotesize
@@
             \\
-            \iff 
+            \text{divide by } \tilde \eta_{t + 1} > 0
+            \implies 
             \tilde \eta_{t + 1} &= \epsilon_{t + 1} + \eta_t + L^{-1}. 
         \end{align*}
-        At the last step, we divided both side of the equation by $\tilde \eta_{t + 1} > 0$.
         The parameter gives relation $\epsilon_{t+1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$. 
@@
         \end{align*}
-        With that, we can solve a relation between $\eta_{t + 1}$ in terms of the sequence $\epsilon$ and $\eta_t$.
+        With that, we can solve a relation between $\eta_{t + 1}$ in terms of the sequence $\epsilon_t$ and $\eta_t$.
         Consider the equality 
@@
         \end{align*}
-        Observe that in the case where we choose $\epsilon_t = 0\; \forall t \in \N$, the above relation simplifies to 
-        \begin{align*}
-            a_{t + 1} &= (1/2)\left(
-                1 + \sqrt{1 + 4 c_{t + 1}}
-            \right), 
-            \\
-            c_{t + 1} &= a_t^2. 
-        \end{align*}
-        This relation is the Famous Nesterov momentum sequence. 
-        At the same time, we can analyize the convergence rate of the algorithm by the abstract convergence lemma, producing: 
-        \begin{align*}
-            \Phi_{t + 1} - \Phi_t =
-            \Upsilon_{1, t + 1}^\text{AG} + 
-            \sigma_t\Upsilon_{1, t + 1}^{\text{AG}} 
-            &\le \epsilon_{t + 1}\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}
-        \end{align*}
-        Telescoping yields: 
+        With $\delta_i$ given by
+        \hyperref[thm:generic_ag_convergence]
+        {theorem \ref*{thm:generic_ag_convergence}}. 
+        Define $\delta_i = \epsilon_{i} \tilde \eta_i$, then 
         \begin{align*}
@@
         \end{align*}
-        Under an ideal case where we wish to attain accelerations, we want $\lim_{T \rightarrow \infty} S_T < \infty$. 
+        Under an ideal case where we wish to attain the best convergence, we want $\lim_{T \rightarrow \infty} S_T < \infty$. 
         One way to accomplish is choose the error sequence $\epsilon_i, i \in \N$ to be bounded by for all $i \in \N$, $\epsilon_i$ should satisfy: 
@@
 \section{Recovering existing variants of Nesterov accelerated gradient}\label{sec:recovery}
+    In this section, we recovers several variants of the accelerated gradient in the literatures as a special case of 
+    \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}, 
+    we sate the choice of stepsize parameter $\eta_i, \tilde \eta_i$, verify that they satisfies 
+    \hyperref[thm:ag_generic_stepsize_constraints]
+    {theorem \ref*{thm:ag_generic_stepsize_constraints}}
+    and derive their convergence rate respectively.
+
     \subsection{Recovering FISTA} 
-        From 
+        Let $\epsilon_i$ be given by
         \hyperref[thm:ag_generic_stepsize_constraints]
         {theorem \ref*{thm:ag_generic_stepsize_constraints}}, 
-        setting $\epsilon_i = 0$ for all $i$ yields $a_t = 1 + L\eta_t = \tilde \eta_{t + 1}$, for all $t \in \N$ where $a_t$ is the Nesterov sequence.
-        In this case, there exists a momentum form of the generic form and it reduces to FISTA from Beck and Toubolle, or Similar Triangle Method as referred to by Ahn and Sra.
-
+        setting $\epsilon_i = 0$ for all $i$ yields $a_t = 1 + L\eta_t = \tilde \eta_{t + 1}$, for all $t \in \N$ where $a_t$ produces the relations 
+        \begin{align*}
+            a_{t + 1} &= (1/2)\left(
+                1 + \sqrt{1 + 4 c_{t + 1}}
+            \right), 
+            \\
+            c_{t + 1} &= a_t^2. 
+        \end{align*}
+        The recurrenct relations of $a_t$ indicates that it's the famous Nesterov momentum sequence. 
+        In this case, there exists a momentum form of the generic form and it reduces to FISTA from Beck and Toubolle \cite{beck_fast_2009-1}. 
+        The following lemma uses $a_t$ to establish equivalence between the generic form of the algorithm and FISTA, a specific variant of accelerated gradient method. 
         \begin{lemma}[Deriving Similar Triangle Form I]
             \quad \\
-            With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$ 
-            in 
-            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
+            With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$,
+            \hyperref[def:ag_prox_grad_generic]
+            {definition \ref*{def:ag_prox_grad_generic}}
+            simplifies into 
             \begin{align*}
@@
             \end{align*}
-            It also has an equivalent momentum form 
+            It is also equivalent to 
             \begin{align*}
@@
             \end{align*}
+            And this is the FISTA algorithm. 
         \end{lemma}
+
         \begin{proof}
-            To do, we show that updates sequence $x_{t + 1} = z_{t + 1} + L\eta_t (z_{t + 1} - z_t)$ is equivalent to $x_{t + 1} = x_t + \tilde\eta_{t + 1}\nabla f(y_t)$. 
-            Starting with the former, susbtitute definition of $z_{t + 1}$, $z_{t + 1} = z_t + L^{-1}\nabla f(y_t)$ expanding: 
+            Firstly, we show that updates sequence $x_{t + 1} = z_{t + 1} + L\eta_t (z_{t + 1} - z_t)$ is equivalent to $x_{t + 1} = x_t + \tilde\eta_{t + 1}\nabla f(y_t)$. 
+            Starting with the former, susbtitute $z_{t + 1} = y_t + L^{-1}\nabla f(y_t)$ as given by 
+            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}},
+            expanding: 
             \begin{align*}
@@
             \end{align*}
-            So $x_{t + 1} = x_t + \tilde \eta_{t + 1}\mathcal G_L(y_t)$, by assumption $\tilde \eta_{t + 1} = \eta_t + L^{-1}$
-            Reducing it to the classic momentum form starts by 
+            So $x_{t + 1} = x_t + \tilde \eta_{t + 1}\mathcal G_L(y_t)$, by assumption $\tilde \eta_{t + 1} = \eta_t + L^{-1}$. 
+            Next, consider the updates $y_{t + 1}$ as given by 
+            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
             \begin{align*}
@@
             \end{align*}
-            This is FISTA by the relation $a_t = 1 + L\eta_t$, hence $(1 + L\eta_{t + 1})^{-1}L\eta_t$ is $(a_t - 1)/a_{t + 1}$.
-            Where we proved in 
+            This is FISTA by the relation $a_t = 1 + L\eta_t$ by setting $\epsilon_i = 0$ in
             \hyperref[thm:ag_generic_stepsize_constraints]
-                {theorem \ref*{thm:ag_generic_stepsize_constraints}}
-            that $a_t$ is the Nesterov momentum sequence. 
+            {theorem \ref*{thm:ag_generic_stepsize_constraints}}, 
+            making $a_t$ the Nesterov momentum sequence. 
+            Observe that $(1 + L\eta_{t + 1})^{-1}L\eta_t$ is $(a_t - 1)/a_{t + 1}$.
+            Express using $a_t$, the above algorithm is equivalent to the FISTA algorithm. 
+            \par
+            By 
+            \hyperref[thm:ag_generic_stepsize_constraints]{theorem \ref*{thm:ag_generic_stepsize_constraints}}
+            and 
+            \hyperref[thm:generic_ag_convergence]{\ref*{thm:generic_ag_convergence}},
+            a convergence of $\mathcal O(\sigma_T^{-1})$ is possible. 
+            Since $a_t = \tilde \eta_t$, and the Nesterov sequence exhibits $a_{t} \ge (t + 2)/2$, the convergence becomes $\mathcal O(T^{-2})$. 
+            It is the optimal convergence rate for all convex functions. 
         \end{proof}

### 2024-08-20 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, a lot of updates to the notes

@@
         A different construction of $\phi_k$ yield a different algorithm. 
-        As shown in Nesterov's book \cite*[(2.2.63)]{nesterov_lectures_2018}, a projected gradient variant of the accelerated gradient method make use of the following estimating functions, sequence: 
+        As shown in Nesterov's book \cite[(2.2.63)]{nesterov_lectures_2018}, a projected gradient variant of the accelerated gradient method make use of the following estimating functions, sequence:
+
         \begin{align*}
@@
 
-\printbibliography
+\bibliographystyle{siam}
+\bibliography{references/refs}
 

### 2024-08-22 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, re-organized a lot of stuff in this part of notes
updated notes

@@
     Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
-    Ahn and Sra explored the interpretation of Nesterov acceleration as the proximal point method applied to an upper surrogate function, and then a lower surrogate function. 
+    Ahn and Sra explored the interpretation of Nesterov acceleration as the proximal point method (PPM) applied to an upper surrogate function, and then a lower surrogate function. 
     Inspired by the interpretation, we generalize the framework to the case of $h = f + g$ with $f$ Lipschitz smooth and $g$ convex whose proximal mapping can be evaluated exactly for algorithm implementations.
+    As a major extension, our work describes the method of proximal gradient using the PPM interpretations.
+We also compactify the Lypunov analysis with the introduction of an error terms for the convergence proof.
+Finally, we derive major variants of the accelerated gradient and find the match of the stepsize parameters in the PPM form.
     \par
@@
 
-    \begin{theorem}[Proximal Descent Inequality]\label{thm:ppm_descent_ineq}
+    \begin{theorem}[Proximal descent inequality]\label{thm:ppm_descent_ineq}
         Let $f: \RR^n \mapsto \overline \RR^n$ $\beta$ be strongly convex with $\beta \ge 0$, fix any $x \in \RR^n$, define $p = \hprox_f(x)$.
@@
 
-    \begin{definition}[The Gradient Mapping]
+    \begin{definition}[The gradient mapping]
         \label{def:gradient_mapping}
@@
 
-    \begin{lemma}[Gradient Mapping Approximates Subgradient]
+    \begin{lemma}[Gradient mapping approximates subgradient]
     \label{lemma:grad-map-approx-subgrad}\; \\
@@
 
-    \begin{lemma}[Linearized Gradient Mapping Lower Bound]
+    \begin{lemma}[Linearized gradient mapping lower bound]
     \label{lemma:grad_map_linearization}\; \\
@@
     \begin{remark}
-        Observe that the linearization $h(x^+) + \langle \mathcal G_L(x), z - x\rangle$ is anchored at $x^+$, instead of $x$. 
-        Geometrically, it's tilted and it ``prefers" the sharp corners of a convex function, if, $x$ is close to a sharp corner. 
         The inequality is analogous to \cite[(2.2.57)]{nesterov_lectures_2018}, however Nesterov stated it only for the case when $g$ is an indicator function of some convex set $Q$. 
@@
     The next definition will start the discussion. 
-    \begin{definition}[Linear Lower Bounding Function]\label{def:gradmap-linear-lowerbnd-fxn}
+    \begin{definition}[Linear lower bounding function]\label{def:gradmap-linear-lowerbnd-fxn}
         Let $h = f+ g$ satisfies
@@
 
-    \begin{definition}[AG Proximal Gradient PPM Generic Form]
+    \begin{definition}[AG proximal gradient PPM generic form]
     \label{def:ag_prox_grad_ppm}
@@
 
-    \begin{definition}[AG Proximal Gradient Generic Form]
+    \begin{definition}[AG proximal gradient generic form]
     \label{def:ag_prox_grad_generic}
@@
 
-\section{Generic Lyapunov analysis for Accelerated gradient via PPM}
+\section{Generic Lyapunov analysis for accelerated gradient via PPM}
 \label{sec:generic_ag_ppm_lyapunov_analysis}
@@
             \iff 
-            \tilde \eta_{t + 1} ^2 - L \tilde \eta_{t + 1} 
+            \tilde \eta_{t + 1} ^2 - L^{-1} \tilde \eta_{t + 1} 
             &= 
@@
             Finally, similar remarks about the similar triangle form can be found in Ahn, Sra's paper \cite{ahn_understanding_2022} as well. 
-
         \end{remark}
@@
     \subsection{Recovering the accelerated gradient variant appeared in Ryu's Book}
+
     \subsection{Recovering Chambolle, Dossal 2015}
 
-\section{Algorithmic Improvements}\label{sec:algorithm_improved}
+\section{Algorithm implementations using line search}\label{sec:algorithm_improved}
     In this section, we state a new variant of the accelerated gradient algorithm using the PPM interpretation to algorithmically conduct a line search routine for $L, \mu \ge 0$ the Lipschitz constant and strong convexity index of the smooth part of the objective function.
@@
 
-\section{Numerical Experiments}\label{sec:numerical_experiments}
+\section{Numerical experiments}\label{sec:numerical_experiments}
 

### 2024-08-23 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, changes

@@
     A lower bound function is identified using the gradient mapping operator and proved in
-    \hyperref[lemma:grad_map_linearization]{lemma \ref*{lemma:grad_map_linearization}}, 
+    \hyperref[lemma:grad_map_linearization]{Lemma \ref*{lemma:grad_map_linearization}}, 
     this is a key component of the proximal point interpretation of the accelerated gradient method. 
@@
         Suppose $h = f + g$ satisfies 
-        \hyperref[assumption:smooth-nonsmooth-sum]{assumption \ref*{assumption:smooth-nonsmooth-sum}}. 
+        \hyperref[assumption:smooth-nonsmooth-sum]{Assumption \ref*{assumption:smooth-nonsmooth-sum}}. 
         Define the proximal gradient operator
@@
         Suppose $h = f + g$ satisfies 
-        \hyperref[assumption:smooth-nonsmooth-sum]{assumption \ref{assumption:smooth-nonsmooth-sum}}, 
+        \hyperref[assumption:smooth-nonsmooth-sum]{Assumption \ref{assumption:smooth-nonsmooth-sum}}, 
         let $\mathcal T_L, \mathcal G_L$ be given by 
-        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}.
+        \hyperref[def:gradient_mapping]{Definition \ref*{def:gradient_mapping}}.
         Then for all $x$, the gradient mapping verifies
@@
         Suppose that $h = f + g$ satisfies 
-        \hyperref[assumption:smooth-nonsmooth-sum]{assumption \ref*{assumption:smooth-nonsmooth-sum}}, 
+        \hyperref[assumption:smooth-nonsmooth-sum]{Assumption \ref*{assumption:smooth-nonsmooth-sum}}, 
         further assume that $f$ is strongly convex with index $\mu \ge 0$. 
         Let $x^+ = \mathcal T_L(x)$ as given in 
-        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}. 
+        \hyperref[def:gradient_mapping]{Definition \ref*{def:gradient_mapping}}. 
         Then for all $z \in \RR$, it satisfies
@@
         Let $h = f+ g$ satisfies
-        \hyperref[assumption:smooth-nonsmooth-sum]{definition \ref*{assumption:smooth-nonsmooth-sum}}, 
+        \hyperref[assumption:smooth-nonsmooth-sum]{Definition \ref*{assumption:smooth-nonsmooth-sum}}, 
         $\mathcal G_L$ given by 
-        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}. 
+        \hyperref[def:gradient_mapping]{Definition \ref*{def:gradient_mapping}}. 
         Define for all $y$ the function
@@
         \hyperref[lemma:grad_map_linearization]
-        {lemma \ref*{lemma:grad_map_linearization}}. 
+        {Lemma \ref*{lemma:grad_map_linearization}}. 
     \end{remark}
@@
     We state the PPM interpretation of accelerated gradient in 
-    \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}, 
+    \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}, 
     which has the equivalent form as presented in
     \hyperref[def:ag_prox_grad_generic]
-    {definition \ref*{def:ag_prox_grad_generic}}. 
+    {Definition \ref*{def:ag_prox_grad_generic}}. 
     \hyperref[prop:derive_ag_prox_grad_tript]
@@
             \hyperref[assumption:smooth-nonsmooth-sum]
-            {assumption \ref*{assumption:smooth-nonsmooth-sum}}, 
+            {Assumption \ref*{assumption:smooth-nonsmooth-sum}}, 
         \item Using $h$ as given from above, let $\mathcal T_L, \mathcal G_L$ be given by 
             \hyperref[def:gradient_mapping]
-            {definition \ref*{def:gradient_mapping}}. 
+            {Definition \ref*{def:gradient_mapping}}. 
         \item Using all above, let $l_h$ be given by 
             \hyperref[def:gradmap-linear-lowerbnd-fxn]
-            {definition \ref*{def:gradmap-linear-lowerbnd-fxn}}. 
+            {Definition \ref*{def:gradmap-linear-lowerbnd-fxn}}. 
     \end{enumerate}
@@
         $$
-
     \end{definition}
@@
         This thows
-        \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}
+        \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}
         and 
-        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}} 
+        \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}} 
         are equivalent. 
@@
         \hyperref[lemma:grad_map_linearization]
-        {lemma \ref*{lemma:grad_map_linearization}}
+        {Lemma \ref*{lemma:grad_map_linearization}}
         Since $l_h(x; y_t)$ is a simple linear function wrt $x$, minimizing the quandratic where to get $x_{t + 1} = x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t)$; for $y_{t + 1}$, complete the square on the second and the third terms:
@@
     The Lypunov function in 
-    \hyperref[thm:generic_ag_convergence]{\ref*{thm:generic_ag_convergence}}
+    \hyperref[thm:generic_ag_convergence]{Theorem \ref*{thm:generic_ag_convergence}}
     is identical to Ahn and Sra 
@@
     \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
-    {lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}
+    {Lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}
     \par
@@
     \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
-    {lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}} 
+    {Lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}} 
     to assist the proof of  

### 2024-08-26 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, changes to the notes

@@
 We also compactify the Lypunov analysis with the introduction of an error terms for the convergence proof.
-Finally, we derive major variants of the accelerated gradient and find the match of the stepsize parameters in the PPM form.
+Finally, we derive major variants of the accelerated gradient(AG) and find the match of the stepsize parameters in the PPM form.
     \par
-    Classical analysis and extension of Nesterov accelerated gradient exist in the literatures. 
+    Some of the earlier examples for the extension of the Nesterov acceleration method make use of the classical analysis introduced by Nestrov. 
+    It uses the Nesterov acceleration sequence. 
     See \cite{guler_new_1992} for an extension of the Nesterov accelerated gradient method to the proximal point method for convex programming. 
-    However the classical analysis found in \cite[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and cherry picked Nesterov's estimating sequence to assist the proof for the parameters in the algorithm.
+    However the classical analysis found in \cite[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and a specific format of the Nesterov's estimating sequence to accomodate the proof for the relations between the parameters in the algorithm.
     In Ahn's work however, the complexities are packaged into the proximal point interpretation of accelerated gradient. 
@@
     Consult \cite{su_differential_2015} for a dynamical system interpretation of Nesterov acceleration. 
-    The dynamical system interpretation of the algorithm however, lead to the valuable insights that restarting the accerlated gradient algorithm would lead to faster convergence rate for the class of strongly convex function.
+    The dynamical system interpretation of the algorithm leads to the valuable insight that restarting the accerlated gradient algorithm would lead to faster convergence rate for the class of strongly convex function.
+    In work by \cite{allen-zhu_linear_2016}, they interpreted the idea of Nesterov acceleration as a combinations of gradient descent and mirror descent.
 
@@
     \begin{assumption}\label{assumption:smooth-nonsmooth-sum}
-        Let $h = f + g$ where $f, g$ are convex and $f$ is Lipschitz-Smooth. 
+        Let $h = f + g$ where $f, g$ are convex and $f$ is Lipschitz-Smooth with constant $L$. 
     \end{assumption}
@@
             h(z) &\ge 
-            h(x^+) + \langle \mathcal G_L (x), z - x\rangle + 
+            h(x^+) + 
+            \langle \mathcal G_L (x), z - x\rangle 
+            + 
             \frac{L}{2}\Vert x - x^+\Vert^2 + \frac{\mu}{2}
@@
             &g(x^+) \le 
-            g(z) + \langle \partial g(x^+), x^+ - z\rangle. 
-        \end{align*}
-        Apply the above by considering the following sequence of relations
+            g(z) + \langle v, x^+ - z\rangle\quad 
+            \forall v \in \partial g(x^+)
+        \end{align*}
+        For all $v \in \partial g (x^+)$, apply the above by considering the following sequence of relations
         \begin{align*}
@@
                 &\qquad  
-                + (g(z) + \langle \partial g(x^+), x^+ - z\rangle)
+                + (g(z) + \langle v, x^+ - z\rangle)
             \end{aligned}
@@
                 +
-                (g(z) + \langle \partial g(x^+), x^+ - z\rangle)
+                (g(z) + \langle v, x^+ - z\rangle)
             \end{aligned}
@@
                     \langle \nabla f(x), x^+ - x\rangle + 
-                    \langle \partial g(x^+), x^+ - z\rangle
+                    \langle v, x^+ - z\rangle
                 \right) 
@@
                     \langle \nabla f(x), x^+ - x\rangle + 
-                    \langle \partial g(x^+), x^+ - z\rangle
+                    \langle v, x^+ - z\rangle
                 \right)
@@
                 &= h(z) + 
-                \langle \nabla f(x) + \partial g(x^+), x^+ - z\rangle 
+                \langle \nabla f(x) + v, x^+ - z\rangle 
                 - \frac{\mu}{2}\Vert z - x\Vert^2
@@
             \end{aligned}
-            \\& 
-            \begin{aligned}
-                &= h(z) + 
-                    \langle \mathcal G_L(x), x^+ - z\rangle 
+            % \\& 
+            % \begin{aligned}
+            %     &= h(z) + 
+            %         \langle \mathcal G_L(x), x^+ - z\rangle 
+            %     - \frac{\mu}{2}\Vert z - x\Vert^2
+            %     + \frac{L}{2}\Vert x - x^+\Vert^2
+            % \end{aligned}
+            % \\& 
+            % \begin{aligned}
+            %     &= h(z) + \langle L(x - x^+), x^+ - x + x - z\rangle 
+            %     - \frac{\mu}{2}\Vert z - x\Vert^2
+            %     + \frac{L}{2}\Vert x - x^+\Vert^2
+            % \end{aligned}
+            % \\&
+            % \begin{aligned}
+            %     &= h(z) + 
+            %     \underbrace{\langle L(x - x^+), x - z\rangle}_{
+            %         = - \langle \mathcal G_L (x), z - x\rangle
+            %     }
+            %     - \frac{\mu}{2}\Vert z - x\Vert^2
+            %     - \frac{L}{2}\Vert x - x^+\Vert^2
+            % \end{aligned}
+        \end{align*}
+        Showed in  
+        \hyperref[lemma:grad-map-approx-subgrad]{Lemma \ref*{lemma:grad-map-approx-subgrad}}, 
+        we have $\mathcal G_L(x) \in \nabla f(x) + \partial g(x^+)$, choose $v \in \partial g(x^+)$ such that $G_L(x) = \nabla f(x) + \partial g(x^+)$, it yields
+        \begin{align*}
+            h(x^+) & 
+            \le h(z) + 
+            \langle \nabla f(x) + v, x^+ - z\rangle 
             - \frac{\mu}{2}\Vert z - x\Vert^2
             + \frac{L}{2}\Vert x - x^+\Vert^2
-            \end{aligned}
-            \\& 
-            \begin{aligned}
-                &= h(z) + \langle L(x - x^+), x^+ - x + x - z\rangle 
-                - \frac{\mu}{2}\Vert z - x\Vert^2
-                + \frac{L}{2}\Vert x - x^+\Vert^2
-            \end{aligned}
-            \\&
-            \begin{aligned}
-                &= h(z) + 
-                \underbrace{\langle L(x - x^+), x - z\rangle}_{
-                    = - \langle \mathcal G_L (x), z - x\rangle
-                }
-                - \frac{\mu}{2}\Vert z - x\Vert^2
-                - \frac{L}{2}\Vert x - x^+\Vert^2
-            \end{aligned}. 
         \end{align*}
@@
         \begin{aligned}
-            y_t^+ &= \mathcal T_L(y_t)
-            \\
             y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
@@
         \end{align*}
-        Define $z_{t + 1} = y_t - \mathcal G_L(y_t) = \mathcal T_L(y_t)$, which is the proximal gradient set, then the above expression simplifies to 
+        Define $z_{t + 1} = y_t - \mathcal G_L(y_t) = \mathcal T_L(y_t)$, then the above expression simplifies to 
         $$
@@
     which states new results that are extension to Ahn and Sra's works by introducing an error term to the Lypunov analysis, allowing for a weaker constraints for the stepsize paramters $\tilde \eta_i, \eta_i$ from
-    \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}. 
+    \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}. 
     \hyperref[thm:ag_generic_stepsize_constraints]{Theorem \ref*{thm:ag_generic_stepsize_constraints}}
@@
 
-    \begin{lemma}[Lyapunov Inequality]. 
+    \begin{lemma}[Lyapunov inequality]
     \label{lemma:nsmooth_agg_lyapunov_upper_bound}\;\\
-        Fix any $\bar x, x, \tilde\eta > 0$, define
+        Fix any $\bar x, x, z',\tilde\eta > 0$, define
         \begin{align*}
@@
             x^+ &:= 
-            \hprox_\phi(x) = x - \tilde \eta\mathcal G_L \bar x. 
-        \end{align*}
-        with $x_*$ being the minimizer of $h$, it has 
-        \begin{align*}
+            \hprox_\phi(x) = x - \tilde \eta\mathcal G_L \bar x,
+            \\
             \Upsilon_{1}  &:= 
@@
             + 
-            \frac{1}{2}(\Vert x^+ - x_*\Vert^2 - \Vert x - x_*\Vert^2)
-            \\
-            &\quad \le 
+            \frac{1}{2}(\Vert x^+ - x_*\Vert^2 - \Vert x - x_*\Vert^2), 
+            \\
+            \Upsilon_2 &:= 
+            h(\mathcal T_L \bar x) - h(z'). 
+        \end{align*}
+        with $x_*$ being the minimizer of $h$, it has 
+        \begin{align*}
+            \Upsilon_1 &\le 
             - \tilde \eta \langle \mathcal G_L\bar x, x^+ - \mathcal T_L \bar x\rangle
@@
             \\
-            \forall z':
-            \Upsilon_2 &:= 
-            h(\mathcal T_L \bar x) - h(z') 
-            \le 
+            \Upsilon_2 &\le 
             \langle \mathcal G_L\bar x, \mathcal T_L \bar x - z'\rangle + 
@@
     \begin{observation}
-        Function $\phi$ is a linear function that qualifies as a lower bound of $\tilde \eta h$, anchored at $\bar x$ by 
+        Function $\phi$ is a linear function that qualifies as a lower bound of $\tilde \eta h$, at $\bar x$ by 
         \hyperref[lemma:grad_map_linearization]{lemma \ref*{lemma:grad_map_linearization}}.
@@
     \begin{proof}
-        Directly observe that we have 
+        Observe that we have 
         \begin{align*}
@@
         \end{align*}
-        The convexity of $g$ yields: 
+        The convexity of $g$ yields for all $v \in \partial g(z)$: 
         \begin{align*}
@@
             \langle 
-                \partial g(z), z' - z
+                v, z' - z
             \rangle 
@@
             &\le 
-            \langle \partial g(z), z - z'\rangle. 
+            \langle v, z - z'\rangle. 
         \end{align*}
@@
             h(z) - h(z') &\le 
-            \langle \nabla f(\bar x) + \partial g(z), z - z'\rangle + 
+            \langle \nabla f(\bar x) +v, z - z'\rangle + 
             \frac{L}{2}\Vert z - \bar x\Vert^2. 
@@
         \hyperref[lemma:grad-map-approx-subgrad]
-        {lemma \ref*{lemma:grad-map-approx-subgrad}}, 
-        to give the desired results. 
+        {Lemma \ref*{lemma:grad-map-approx-subgrad}}, 
+        there exists $v \in \partial g (\mathcal T_L(\bar x))$ such that $\mathcal G_L(\bar x) = \nabla f(z) + v$, hence the theorem is proved. 
     \end{proof}
-    \begin{remark}
-    \label{remark:upsilon-upperbound-for-iterates}
+    \begin{remark}\label{remark:upsilon-upperbound-for-iterates}
         Let $y_t, x_t$ be given by
         \hyperref[def:ag_prox_grad_generic]
-        {definition \ref*{def:ag_prox_grad_generic}}.
+        {Definition \ref*{def:ag_prox_grad_generic}}.
         Set $\bar x = y_t, x = x_t$, then 
@@
         \end{align*}
-        Set $z' = z_t, \tilde \eta = \tilde \eta_{t + 1}$, 
-        the results can be written as 
+        Set $z' = z_t, \tilde \eta = \tilde \eta_{t + 1}$, we define the quantities: 
         \begin{align*}
@@
             + 
-            \frac{1}{2}(\Vert x_{t + 1} - x_*\Vert^2 + \Vert x_t - x_*\Vert^2)
-            \\
-            &\quad \le 
+            \frac{1}{2}(\Vert x_{t + 1} - x_*\Vert^2 + \Vert x_t - x_*\Vert^2),
+            \\
+            \Upsilon_{2, t + 1}^{\text{AG}}
+            &:= 
+            h(z_{t + 1}) - h(z_t). 
+        \end{align*}
+        It then produces the inequalities: 
+        \begin{align*}
+            \Upsilon_{1, t + 1}^{\text{AG}}
+            &\le 
             - \tilde \eta_{t + 1}\langle \mathcal G_L y_t, x_{t + 1} - z_{t + 1}\rangle
@@
             \Upsilon_{2, t + 1}^{\text{AG}}
-            &:= 
-            h(z_{t + 1}) - h(z_t) \le 
+            &\le 
             \langle \mathcal G_L \bar x, z_{t + 1} - z_t \rangle + 
@@
         \end{align*}
-        It will be used next. 
+        This is useful for the convergence proof of the algorithm. 
     \end{remark}
 
-    \begin{theorem}[Generic AG Convergence]
+    \begin{theorem}[Generic AG convergence]
     \label{thm:generic_ag_convergence}
@@
         \hyperref[remark:upsilon-upperbound-for-iterates]
-        {remark \ref*{remark:upsilon-upperbound-for-iterates}}. 
+        {Remark \ref*{remark:upsilon-upperbound-for-iterates}}. 
         Let $z_t$ be given by 
         \hyperref[def:ag_prox_grad_generic]
-        {definition \ref*{def:ag_prox_grad_generic}}. 
+        {Definition \ref*{def:ag_prox_grad_generic}}. 
         Define the Lyapunov function $\Phi_t\; \forall t \in \{0\}\cup \N$, $S_t$ and $\sigma_t$: 
@@
         \hyperref[def:ag_prox_grad_ppm]
-        {definition \ref*{def:ag_prox_grad_ppm}} 
+        {Definition \ref*{def:ag_prox_grad_ppm}} 
         such that
@@
         \hyperref[def:ag_prox_grad_generic]
-        {definition \ref*{def:ag_prox_grad_generic}}. 
+        {Definition \ref*{def:ag_prox_grad_generic}}. 
         If the stepsize $\eta_i, \tilde \eta_i$ satisfies relations 
@@
         Then the convergence rate stated in 
-        \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}
+        \hyperref[thm:generic_ag_convergence]
+        {Theorem \ref*{thm:generic_ag_convergence}}
         applies. 
@@
         (as formulated in 
-        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}) 
+        \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}) 
         for $t\in \mathbb N$ it has: 
@@
         \hyperref[remark:upsilon-upperbound-for-iterates]
-        {remark \ref*{remark:upsilon-upperbound-for-iterates}}
+        {Remark \ref*{remark:upsilon-upperbound-for-iterates}}
         it has 
@@
         \hyperref[def:ag_prox_grad_generic]
-        {definition \ref*{def:ag_prox_grad_generic}}
+        {Definition \ref*{def:ag_prox_grad_generic}}
         vector $x_{t + 1} - x_t$ and $z_{t + 1} - y_t$ are parallel by observations: 
@@
         \hyperref[thm:generic_ag_convergence]
-        {theorem \ref*{thm:generic_ag_convergence}}. 
+        {Theorem \ref*{thm:generic_ag_convergence}}. 
         Define $\delta_i = \epsilon_{i} \tilde \eta_i$, then 
@@
     In this section, we recovers several variants of the accelerated gradient in the literatures as a special case of 
-    \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}, 
+    \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}, 
     we sate the choice of stepsize parameter $\eta_i, \tilde \eta_i$, verify that they satisfies 
     \hyperref[thm:ag_generic_stepsize_constraints]
-    {theorem \ref*{thm:ag_generic_stepsize_constraints}}
+    {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
     and derive their convergence rate respectively.
@@
         \hyperref[thm:ag_generic_stepsize_constraints]
-        {theorem \ref*{thm:ag_generic_stepsize_constraints}}, 
+        {Theorem \ref*{thm:ag_generic_stepsize_constraints}}, 
         setting $\epsilon_i = 0$ for all $i$ yields $a_t = 1 + L\eta_t = \tilde \eta_{t + 1}$, for all $t \in \N$ where $a_t$ produces the relations 
@@
             \hyperref[def:ag_prox_grad_generic]
-            {definition \ref*{def:ag_prox_grad_generic}}
+            {Definition \ref*{def:ag_prox_grad_generic}}
             simplifies into 
@@
             Starting with the former, susbtitute $z_{t + 1} = y_t + L^{-1}\nabla f(y_t)$ as given by 
-            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}},
+            \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}},
             expanding: 
@@
             Next, consider the updates $y_{t + 1}$ as given by 
-            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
+            \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}
             \begin{align*}
@@
             \hyperref[thm:ag_generic_stepsize_constraints]
-            {theorem \ref*{thm:ag_generic_stepsize_constraints}}, 
+            {Theorem \ref*{thm:ag_generic_stepsize_constraints}}, 
             making $a_t$ the Nesterov momentum sequence. 
@@
             By 
-            \hyperref[thm:ag_generic_stepsize_constraints]{theorem \ref*{thm:ag_generic_stepsize_constraints}}
+            \hyperref[thm:ag_generic_stepsize_constraints]{Theorem \ref*{thm:ag_generic_stepsize_constraints}}
             and 
-            \hyperref[thm:generic_ag_convergence]{\ref*{thm:generic_ag_convergence}},
+            \hyperref[thm:generic_ag_convergence]{Theorem \ref*{thm:generic_ag_convergence}},
             a convergence of $\mathcal O(\sigma_T^{-1})$ is possible. 

### 2024-08-31 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, updated notes
>w<, changes

@@
     \end{assumption}
+    \begin{definition}[Strongly convex functions]
+        % TODO: FILL THIS ONE IN. 
+        %   The definition of a strongly convex function. 
+    \end{definition}
 
@@
         The proof can be found in \cite[theorem 12.26]{bauschke_convex_2017}. 
+        % TODO: Add the proof to the appendix. 
     \end{remark}
@@
             \\
-            \mathcal G_L(x) = L(x - x^+) &\in  \nabla f(x) + \partial g(x^+). 
-        \end{align*}
+            \mathcal G_L(x) := L(x - x^+) &\in  \nabla f(x) + \partial g(x^+). 
+        \end{align*}
+        Equivalently, $\exists v \in \partial g(x^+)$ such that $G_L(x) = \nabla f(x) + v = L(x - x^+)$. 
     \end{lemma}
@@
         The following lemma uses $a_t$ to establish equivalence between the generic form of the algorithm and FISTA, a specific variant of accelerated gradient method. 
-        \begin{lemma}[Deriving Similar Triangle Form I]
+        \begin{lemma}[Similar triangle form]
             \quad \\
@@
             We think it is a fitting name, becaues it has a similar triangle in it. 
-            We list the following observations
+            We list the following observations:
             \begin{enumerate}
@@
                 $$
-                therefore, $y_t$ is a convex combinations of $x_t, z_t$, so $z_t, y_t, x_t$ are three collinear points. 
-                We have the ratio $\Vert y_t - x_t\Vert/\Vert z_t - y_t\Vert = L\eta_t$. 
+                Rearrainging yields: 
+                $$
+                    y_t - x_t = L\eta_t (z_t - y_t). 
+                $$
+                So vector $y_t - x_t$, $z_t - y_t$ colinear and points in the same direction by $L\eta_t > 0$. 
                 \item 
                 The updates for $z_{t + 1}, x_{t + 1}$ are based on $y_t, x_t$ displaced by $L^{-1} \mathcal G_L(y_t), \tilde\eta_{t +1} \mathcal G_L(y_t)$, therefore vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$.
-                \item The updates for $x_{t + 1}$ has $x_{t + 1} - z_{t + 1} = L\eta_t \left(z_{t + 1} - z_t\right)$, therefore, the three points $z_t, x_{t + 1}, z_{t + 1}$ are collinear. 
-                The ratio between line segment has $\Vert x_{t + 1} - z_{t + 1}\Vert/\Vert z_{t + 1} - z_t\Vert = L\eta_t$. 
+                \item 
+                The updates for $x_{t + 1}$ has $x_{t + 1} - z_{t + 1} = L\eta_t \left(z_{t + 1} - z_t\right)$, therefore, the three points $z_t, x_{t + 1}, z_{t + 1}$ are collinear. 
             \end{enumerate}
-            By these tree observations, the triangle $z_{t}, z_{t + 1}, y_t$ similar to triangle $z_t, x_{t + 1}, x_t$. 
+            By these three observations, the triangle $z_{t}, z_{t + 1}, y_t$ similar to triangle $z_t, x_{t + 1}, x_t$. 
+            \begin{figure}[h]
+                \centering
+                \subfloat[][a]{
+                    \includegraphics*[width=10cm]{assets/drawing_Layer 1.png}
+                }
+                \caption{Similar triangle illustration}
+                \label{steady_state}
+            \end{figure}
+
             Finally, similar remarks about the similar triangle form can be found in Ahn, Sra's paper \cite{ahn_understanding_2022} as well. 
+            Finally, recall from 
+            \hyperref[thm:ag_generic_stepsize_constraints]
+            {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
+            that $\epsilon_{t + 1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$, setting $\epsilon_{t + 1} =0$ for all $t \in \N \cup \{0\}$. 
+            If we choose to incorperate $\epsilon_{t + 1}$, it yields: 
+            \begin{align*}
+                x_{t + 1} &= z_{t + 1} + L\eta_t(z_{t + 1} - z_t) - \epsilon_{t + 1}\mathcal G_L(y_t). 
+            \end{align*}
+            Where $\epsilon_{t + 1}\mathcal G_L(y_t)$ can be viewed as a perturbations from the similar triangle form of the algorithm. 
         \end{remark}
 
-    \subsection{Recovering the accelerated gradient variant appeared in Ryu's Book}
+    \subsection{Recovering the accelerated gradient variant in Ryu's book}
 
@@
 
+\begin{theorem}[strongly convex PPM descent lemma]
+
+\end{theorem}
+
 % \printbibliography

### 2024-08-31 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, updates

@@
             By these three observations, the triangle $z_{t}, z_{t + 1}, y_t$ similar to triangle $z_t, x_{t + 1}, x_t$. 
+            See \hyperref[fig:1a]{Figure \ref*{fig:1a}}
+            for an illustration. 
             \begin{figure}[h]
                 \centering
-                \subfloat[][a]{
-                    \includegraphics*[width=10cm]{assets/drawing_Layer 1.png}
+                \subfloat[a][similar triangle]{
+                    \includegraphics*[width=7cm]{assets/drawing_Layer 1.png}
+                    \label{fig:1a}
+                }
+                \subfloat[b][similar triangle with errors]{
+                    \includegraphics*[width=6cm]{assets/drawing_Layer 1 copy.png}
+                    \label{fig:1b}
                 }
                 \caption{Similar triangle illustration}
-                \label{steady_state}
             \end{figure}
-
             Finally, similar remarks about the similar triangle form can be found in Ahn, Sra's paper \cite{ahn_understanding_2022} as well. 
@@
             \begin{align*}
-                x_{t + 1} &= z_{t + 1} + L\eta_t(z_{t + 1} - z_t) - \epsilon_{t + 1}\mathcal G_L(y_t). 
+                x_{t + 1} &= z_{t + 1} + L\eta_t(z_{t + 1} - z_t) - \epsilon_{t + 1}\mathcal G_L(y_t) = x_t - (\eta_t + L^{-1} + \epsilon_{t + 1})\mathcal G_L(y_t). 
             \end{align*}
             Where $\epsilon_{t + 1}\mathcal G_L(y_t)$ can be viewed as a perturbations from the similar triangle form of the algorithm. 
+            See 
+            \hyperref[fig:1b]{Figure \ref*{fig:1b}}
+            for an illustration for some $\epsilon_{t + 1} > 0$. 
         \end{remark}

### 2024-09-01 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, updates to the notes

@@
     \begin{definition}[Strongly convex functions]
-        % TODO: FILL THIS ONE IN. 
-        %   The definition of a strongly convex function. 
+        A function $f: X \mapsto \RR$ is $\beta$-strongly convex
+        with $\beta\geq 0$ if $f - \beta \frac{\Vert \cdot\Vert^2}{2}$ is convex.
     \end{definition}
@@
     \end{theorem}
+    \begin{proof}
+
+    \end{proof}
     \begin{remark}
         We use this theorem to prove the convergence of the proximal point method. 
-        The proof can be found in \cite[theorem 12.26]{bauschke_convex_2017}. 
-        % TODO: Add the proof to the appendix. 
+        Observe that when $\beta = 0$, this reduces to \cite[theorem 12.26]{bauschke_convex_2017}. 
     \end{remark}
@@
         \begin{align*}
+            S_t &:= \sum_{i = 1}^{t} \delta_i \quad \forall t \in \N,
+            \\
+            \sigma_t &:= \sum_{i = 1}^{t}\tilde \eta_i \quad \forall t \in \N, 
+            \\
             \Phi_0 &:= \frac{1}{2}\Vert x_0 - x_*\Vert^2, 
             \\
-            \Phi_t &:= \left(
-                \sum_{i = 1}^{t} \tilde\eta_{i}
-            \right) (h(z_t) - h(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \N,
-            \\
-            S_t &:= \sum_{i = 1}^{t} \delta_i \quad \forall t \in \N,
-            \\
-            \sigma_t &:= \sum_{i = 1}^{t}\tilde \eta_i \quad \forall t \in \N. 
+            \Phi_t &:= 
+                \sigma_t(h(z_t) - h(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \N.
         \end{align*}
@@
             & \Phi_{t + 1} - \Phi_{t} =
-            \left(
-                \sum_{i = 1}^{t} \tilde \eta_i
-            \right)\Upsilon_{2, t + 1}^{\text{AG}} 
+            \sigma_t\Upsilon_{2, t + 1}^{\text{AG}} 
             + 
@@
             \begin{align*}
-                x_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t) 
+                x_{t + 1} &= 
+                (y_t - L^{-1}\mathcal G_L(y_t)) 
+                + L\eta_t ((y_t - \mathcal G_L(y_t)) - z_t)
+                \\
+                &= y_t - L^{-1}\mathcal G_L(y_t) 
                 + L \eta_t y_t - \eta_t \mathcal G_L(y_t) - L\eta_t z_t
@@
 
+\section{Postoned proof}
+    \begin{fact}[Equivalent characterization of strong convexity]
+    \label{appendix:fact:equiv_char_s-cvx}
+        $f$ is $\beta$-strongly convex if and only if
+        $$
+            (\forall y\in X)(\forall x^* \in \partial f(x))
+            \quad f(y) \ge f(x) + \langle x^*, y - x\rangle +
+            \frac{\beta}{2}\Vert y - x\Vert^2
+            .
+        $$
+    \end{fact}
+
+    \begin{theorem}[Quadratic growth]\label{appendix:thm:q_growth}
+        If $f$ is $\beta$-strongly convex, let $x^*$ be a minimizer of $f$ then 
+        \begin{align*}
+            (\forall y \in X) \quad 
+            f(y) &\ge 
+            f(x) + \frac{\beta}{2}\Vert y - x\Vert^2. 
+        \end{align*}
+    \end{theorem}
+    \begin{proof}
+        Fact \ref*{appendix:fact:equiv_char_s-cvx} 
+        implies a quadratic growth condition. 
+        By convexity $x^*$ is a minimizer of $f$ if and only if $x^*= \mathbf 0 \in \partial f(x^*)$, therefore it sets the inner product on the RHS to zero which yields the quadratic growth condition.
+    \end{proof}
+
     \begin{theorem}[strongly convex PPM descent lemma]
-
+    \label{appendix:proof_ppm_descent_lemma}
+        Let $f: \RR^n \mapsto \overline \RR^n$ $\beta$ be strongly convex with $\beta \ge 0$, fix any $x \in \RR^n$, define $p = \hprox_f(x)$.
+        For all $y \in \RR$ it verifies
+        $$
+            \left(f(p) + \frac{1}{2}\Vert x - p\Vert^2\right)
+            - 
+            \left(
+                f(y) + \frac{1}{2}\Vert x - y\Vert^2 
+            \right)
+            \le 
+            - \frac{(1 + \beta)}{2}\Vert y - p\Vert^2. 
+        $$
+        Recall: $\hprox_f(x) = \argmin_{u}\left\lbrace f(u) + \frac{1}{2}\Vert u - x\Vert^2 \right\rbrace$. 
     \end{theorem}
+    \begin{proof}
+        With $x$ being fixed,
+        consider the function
+        $$
+            y\mapsto h(y)=f(y)+\frac{\|y-x\|^2}{2}=f(y)+\frac{\|y\|^2}{2}-\scal{y}{x}+\frac{\|x\|^2}{2}.
+        $$
+        Because $f$ is $\beta$-strongly convex, the function
+        $y\mapsto f(y) + \frac{1}{2}\Vert y\Vert^2$ is $(\beta + 1)$-strongly convex.
+        Then $h$ is $(\beta + 1)$-strongly convex.
+        Since $(\forall y)\; h(y) \ge h(p)$, because $p = \hprox_f(x)$ 
+        \hyperref[appendix:thm:q_growth]{Theorem \ref*{appendix:thm:q_growth}}
+        (quadratic growth)
+        yields
+        \begin{align*}
+            h(y) &\ge
+            h(p) + \frac{\beta + 1}{2}\Vert y - p\Vert^2.
+        \end{align*}
+        That is,
+        \begin{align*}
+            f(y) + \frac{1}{2}\Vert y - x\Vert^2
+            \ge
+            f(p) + \frac{1}{2} \Vert p - x\Vert^2
+            + \frac{\beta + 1}{2}\Vert y - p\Vert^2.
+        \end{align*}
+        Rearraging yield the desired results. 
+    \end{proof}
 

### 2024-09-03 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, sync
>w<, updated notes

@@
 \author{
-    Author 1 Name, Author 2 Name
-    \thanks{
-        Subject type, Some Department of Some University, Location of the University,
-        Country. E-mail: \texttt{alto@mail.ubc.ca}.
-    }
+    Hongda Li
+    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
+    The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{alto@mail.ubc.ca}.}~ and~Xianfu Wang
+    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
+    The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{shawn.wang@ubc.ca}.}
 }
@@
 We also compactify the Lypunov analysis with the introduction of an error terms for the convergence proof.
-Finally, we derive major variants of the accelerated gradient(AG) and find the match of the stepsize parameters in the PPM form.
+Finally, we derive major variants of the accelerated gradient (AG) and find the match of the stepsize parameters in the PPM form.
     \par
@@
     See \cite{guler_new_1992} for an extension of the Nesterov accelerated gradient method to the proximal point method for convex programming. 
-    However the classical analysis found in \cite[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and a specific format of the Nesterov's estimating sequence to accomodate the proof for the relations between the parameters in the algorithm.
+    However the classical analysis found in \cite[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and a specific format of the Nesterov's estimating sequence to accomodate the proof.
     In Ahn's work however, the complexities are packaged into the proximal point interpretation of accelerated gradient. 
-    It uses a lemma from Moreau envelope to derive the Lypunov analysis, the sizes, and parameters for several variants of the algorithm. 
+    It uses a lemma from Moreau envelope for the Lypunov analysis.
+    The interpration allows choices of undetermined parameters to encompass several variants of the Nesterov accelerated gradient algorithm. 
+    Ahn and Sra's approach is inspired by works from Defazio \cite{defazio_curved_2019}, Zeyuan and Lorenzo \cite{allen-zhu_linear_2016}. 
+    Instead of a mirror descent step on the dual, they propose an alternative without the gradient of the dual. 
     \par
-    Numerous notable variations of Nesterov accelerated gradient exists. \cite[(6.1.19)]{nesterov_lectures_2018} described a variant of accelerated gradient restricted to a convex domain $Q$. 
+    Numerous notable variations of Nesterov accelerated gradient exists.
+\cite[(6.1.19)]{nesterov_lectures_2018} described a variant of accelerated gradient restricted to a convex domain $Q$ using Bregman Divergence.
     Beck and Toubolle \cite{beck_fast_2009} introduced a variant the problem type of smooth plus non-smooth, known as FISTA. 
-    For a variant of accelerated gradient where the iterates converge, see \cite{chambolle_convergence_2015}. 
-    Extension such as the Harpen acceleration for the resolvent operator in general is outside of the scope since it doesn't have a Moreau envelope. 
+    For a variant of accelerated gradient where the iterates converge, see Chambolle and Dossal \cite{chambolle_convergence_2015}. 
+    Extension such as the Harpen acceleration for the resolvent operator of a maximally monotone opreator in general is outside of the scope since it not all maximal monotone operator corresponds to a subgradient operator.
     \par
@@
     \begin{proof}
-
+        See 
+        \hyperref[appendix:proof_ppm_descent_lemma]
+            {Appendix \ref*{appendix:proof_ppm_descent_lemma}}. 
     \end{proof}
@@
             \Phi_t &:= 
-                \sigma_t(h(z_t) - h(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \N.
+                \sigma_t(h(z_t) - h(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 
+            \quad \forall t \in \N.
         \end{align*}
@@
         So then $\Phi_T - \Phi_0$ yields: 
-        $$
-        \begin{aligned}
+        \begin{align}
             \sigma_T (h(z_T) - h(x_*)) 
@@
             \right),
-        \end{aligned}
-        $$
+        \end{align}
         which yields a convergence rate $\mathcal O(\sigma_T^{-1}S_{T})$. 
@@
     \subsection{Recovering the accelerated gradient variant in Ryu's book}
+        In this section we should that the following algorithm which appeared in Ryu \cite[chapter 12]{ryu_large-scale_2022}, the next definition present the algorithm in our notations. 
+        \begin{definition}\label{def:ryu-ch12}
+            Assume that $f$ is a L-Smooth convex function, with initial condition $x_0 = y_0$ an algorithm that generates iterates satisfying: 
+            \begin{align*}
+                z_{t + 1} &= y_t - L^{-1}\nabla f(y_t) 
+                \\
+                x_{t + 1} &= x_t - \frac{t + 1}{2L} \nabla f(y_t) 
+                \\
+                y_{t + 1} &=
+                \left(
+                    1 - \frac{2}{t + 1}
+                \right)z_{t+ 1}
+                + 
+                \left(
+                    \frac{2}{t + 2}
+                \right)x_{t + 1}, 
+            \end{align*}
+            achieves an optimal convergence rate. 
+        \end{definition}
+
+        \begin{lemma}
+            Suppose that the generic form as given by 
+            \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}
+            admits stepsize $\tilde \eta_t, \eta_t$ as
+            \begin{align*}
+                \tilde \eta_{t} &= \frac{t}{2L},
+                \\
+                \eta_t &= (t - 1)/(2L). 
+            \end{align*}
+            Then it's algebraically equivalent to 
+            \hyperref[def:ryu-ch12]{Definition \ref*{def:ryu-ch12}}. 
+        \end{lemma}
+        \begin{proof}
+            Observe $\tilde \eta_t = t/(2L)$ admits a linear growth rate. 
+            If $\tilde \eta_i, \eta_i$ is a sequence that satisfies
+            \hyperref[thm:ag_generic_stepsize_constraints]
+            {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
+            then 
+            \hyperref[thm:generic_ag_convergence]
+            {Theorem \ref*{thm:generic_ag_convergence}}
+            asserts a convergence rate of $\mathcal O(1/T^2)$ for $h(z_T) - h(x_*)$, where $x_*$ is a minimizer assumed to exist. 
+            To show that the sequence satisfies 
+            \hyperref[thm:ag_generic_stepsize_constraints]
+            {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
+            first observe that $\epsilon_t = 0$ because 
+            \begin{align*}
+                L^{-1} + \eta_t 
+                &= 
+                L^{-1} + \frac{t - 1}{2L}
+                \\
+                &= \frac{t + 1}{2L}
+                \\
+                &= \tilde \eta_{t + 1}. 
+            \end{align*}
+            Therefore this is a similar triangle method. 
+            Next observe that conditions showed in 
+            \hyperref[thm:ag_generic_stepsize_constraints]
+            {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
+            can be simplified in this context because the two equalities reduces to just one when $\epsilon_t =0$ for all $t \in \N$ by 
+            \begin{align*}
+                \tilde \eta_{t + 1}(\tilde \eta_{t + 1} - L^{-1}) 
+                - L^{-1}\sigma_t &= 0
+                \\
+                \iff 
+                \tilde \eta_{t + 1}\eta_t &= L^{-1}\sigma_t. 
+            \end{align*}
+            Hence it only requires to verify the equality $\tilde \eta_{t + 1}\eta_t = L^{-1} \sigma_t$. 
+            With that we have 
+            \begin{align*}
+                \sigma_t &= \sum_{i = 1}^{t} \frac{i}{2L}
+                \\
+                &= \frac{1}{2L}\left(
+                    \frac{t(t + 1)}{2}
+                \right)
+                \\
+                &= \frac{t(1 + t)}{4L}
+                \\
+                \iff 
+                L^{-1}\sigma_t &= 
+                \frac{t(1 + t)}{4L}
+            \end{align*}
+            By definition of the stepsizes the LHS of the equality evaluates to
+            \begin{align*}
+                \tilde \eta_{t + 1} \eta_{t + 1}
+                &= \frac{t + 1}{2L} \frac{t}{2L} 
+                \\
+                &= L^{-1}\sigma_t. 
+            \end{align*}
+        \end{proof}
 

### 2024-09-07 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, sync

@@
 We also compactify the Lypunov analysis with the introduction of an error terms for the convergence proof.
-Finally, we derive major variants of the accelerated gradient (AG) and find the match of the stepsize parameters in the PPM form.
+We derive major variants of the Nesterov acceleation algorithm
+    \cite{chambolle_convergence_2015}, \cite{beck_fast_2009}, \cite[Chapter 12]{ryu_large-scale_2022}
+    of the accelerated gradient (AG) and find the match of the stepsize parameters in the PPM form.
+
     \par
@@
     Beck and Toubolle \cite{beck_fast_2009} introduced a variant the problem type of smooth plus non-smooth, known as FISTA. 
-    For a variant of accelerated gradient where the iterates converge, see Chambolle and Dossal \cite{chambolle_convergence_2015}. 
+    For a variant of accelerated gradient where the iterates converge (weakly in Hilbert space), see Chambolle and Dossal \cite{chambolle_convergence_2015}. 
     Extension such as the Harpen acceleration for the resolvent operator of a maximally monotone opreator in general is outside of the scope since it not all maximal monotone operator corresponds to a subgradient operator.
@@
     \begin{theorem}[Proximal descent inequality]\label{thm:ppm_descent_ineq}
-        Let $f: \RR^n \mapsto \overline \RR^n$ $\beta$ be strongly convex with $\beta \ge 0$, fix any $x \in \RR^n$, define $p = \hprox_f(x)$.
+        Let $f: \RR^n \mapsto \overline \RR$ be $\beta$ strongly convex with $\beta \ge 0$, fix any $x \in \RR^n$, define $p = \hprox_f(x)$.
         For all $y \in \RR$ it verifies
@@
     \label{def:ag_prox_grad_ppm}
-        Define $\eta_t, \tilde \eta_t$ to be $> 0$ for all $t \in \N$. 
+        Define $\eta_t, \tilde \eta_t$ to be strictly larger than zero for all $t \in \N$. 
         With initial iterate $x_0, y_0$, 
@@
         \end{align*}
-        It then produces the inequalities: 
+        Then it as inequalities: 
         \begin{align*}
@@
                 \sum_{i = 1}^{t}\tilde\eta_i 
-            \right)\Upsilon_{1, t + 1}^{\text{AG}}
+            \right)\Upsilon_{2, t + 1}^{\text{AG}}
             \\
@@
         The following lemma uses $a_t$ to establish equivalence between the generic form of the algorithm and FISTA, a specific variant of accelerated gradient method. 
-        \begin{lemma}[Similar triangle form]
+        \begin{lemma}[Similar triangle form]\label{lemma:sim_triangle_form}
             \quad \\
@@
 
-    \subsection{Recovering the accelerated gradient variant in Ryu's book}
-        In this section we should that the following algorithm which appeared in Ryu \cite[chapter 12]{ryu_large-scale_2022}, the next definition present the algorithm in our notations. 
-        \begin{definition}\label{def:ryu-ch12}
-            Assume that $f$ is a L-Smooth convex function, with initial condition $x_0 = y_0$ an algorithm that generates iterates satisfying: 
-            \begin{align*}
-                z_{t + 1} &= y_t - L^{-1}\nabla f(y_t) 
-                \\
-                x_{t + 1} &= x_t - \frac{t + 1}{2L} \nabla f(y_t) 
-                \\
-                y_{t + 1} &=
-                \left(
-                    1 - \frac{2}{t + 1}
-                \right)z_{t+ 1}
-                + 
-                \left(
-                    \frac{2}{t + 2}
-                \right)x_{t + 1}, 
-            \end{align*}
-            achieves an optimal convergence rate. 
-        \end{definition}
-
-        \begin{lemma}
-            Suppose that the generic form as given by 
-            \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}
-            admits stepsize $\tilde \eta_t, \eta_t$ as
-            \begin{align*}
-                \tilde \eta_{t} &= \frac{t}{2L},
-                \\
-                \eta_t &= (t - 1)/(2L). 
-            \end{align*}
-            Then it's algebraically equivalent to 
-            \hyperref[def:ryu-ch12]{Definition \ref*{def:ryu-ch12}}. 
-        \end{lemma}
-        \begin{proof}
-            Observe $\tilde \eta_t = t/(2L)$ admits a linear growth rate. 
-            If $\tilde \eta_i, \eta_i$ is a sequence that satisfies
-            \hyperref[thm:ag_generic_stepsize_constraints]
-            {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
-            then 
-            \hyperref[thm:generic_ag_convergence]
-            {Theorem \ref*{thm:generic_ag_convergence}}
-            asserts a convergence rate of $\mathcal O(1/T^2)$ for $h(z_T) - h(x_*)$, where $x_*$ is a minimizer assumed to exist. 
-            To show that the sequence satisfies 
-            \hyperref[thm:ag_generic_stepsize_constraints]
-            {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
-            first observe that $\epsilon_t = 0$ because 
-            \begin{align*}
-                L^{-1} + \eta_t 
-                &= 
-                L^{-1} + \frac{t - 1}{2L}
-                \\
-                &= \frac{t + 1}{2L}
-                \\
-                &= \tilde \eta_{t + 1}. 
-            \end{align*}
-            Therefore this is a similar triangle method. 
-            Next observe that conditions showed in 
-            \hyperref[thm:ag_generic_stepsize_constraints]
-            {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
-            can be simplified in this context because the two equalities reduces to just one when $\epsilon_t =0$ for all $t \in \N$ by 
-            \begin{align*}
-                \tilde \eta_{t + 1}(\tilde \eta_{t + 1} - L^{-1}) 
-                - L^{-1}\sigma_t &= 0
-                \\
-                \iff 
-                \tilde \eta_{t + 1}\eta_t &= L^{-1}\sigma_t. 
-            \end{align*}
-            Hence it only requires to verify the equality $\tilde \eta_{t + 1}\eta_t = L^{-1} \sigma_t$. 
-            With that we have 
-            \begin{align*}
-                \sigma_t &= \sum_{i = 1}^{t} \frac{i}{2L}
-                \\
-                &= \frac{1}{2L}\left(
-                    \frac{t(t + 1)}{2}
-                \right)
-                \\
-                &= \frac{t(1 + t)}{4L}
-                \\
-                \iff 
-                L^{-1}\sigma_t &= 
-                \frac{t(1 + t)}{4L}
-            \end{align*}
-            By definition of the stepsizes the LHS of the equality evaluates to
-            \begin{align*}
-                \tilde \eta_{t + 1} \eta_{t + 1}
-                &= \frac{t + 1}{2L} \frac{t}{2L} 
-                \\
-                &= L^{-1}\sigma_t. 
-            \end{align*}
-        \end{proof}
-
-    \subsection{Recovering Chambolle, Dossal 2015}
+    % \subsection{Recovering the accelerated gradient variant in Ryu's book}
+    %     In this section we should that the following algorithm which appeared in Ryu \cite[chapter 12]{ryu_large-scale_2022}, the next definition present the algorithm in our notations. 
+    %     \begin{definition}\label{def:ryu-ch12}
+    %         Assume that $f$ is a L-Smooth convex function, with initial condition $x_0 = y_0$ an algorithm that generates iterates satisfying: 
+    %         \begin{align*}
+    %             z_{t + 1} &= y_t - L^{-1}\nabla f(y_t) 
+    %             \\
+    %             x_{t + 1} &= x_t - \frac{t + 1}{2L} \nabla f(y_t) 
+    %             \\
+    %             y_{t + 1} &=
+    %             \left(
+    %                 1 - \frac{2}{t + 1}
+    %             \right)z_{t+ 1}
+    %             + 
+    %             \left(
+    %                 \frac{2}{t + 2}
+    %             \right)x_{t + 1}, 
+    %         \end{align*}
+    %         achieves an optimal convergence rate. 
+    %     \end{definition}
+
+    %     \begin{lemma}
+    %         Suppose that the generic form as given by 
+    %         \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}
+    %         admits stepsize $\tilde \eta_t, \eta_t$ as
+    %         \begin{align*}
+    %             \tilde \eta_{t} &= \frac{t}{2L},
+    %             \\
+    %             \eta_t &= (t - 1)/(2L). 
+    %         \end{align*}
+    %         Then it's algebraically equivalent to 
+    %         \hyperref[def:ryu-ch12]{Definition \ref*{def:ryu-ch12}}. 
+    %     \end{lemma}
+    %     \begin{proof}
+    %         Observe $\tilde \eta_t = t/(2L)$ admits a linear growth rate. 
+    %         If $\tilde \eta_i, \eta_i$ is a sequence that satisfies
+    %         \hyperref[thm:ag_generic_stepsize_constraints]
+    %         {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
+    %         then 
+    %         \hyperref[thm:generic_ag_convergence]
+    %         {Theorem \ref*{thm:generic_ag_convergence}}
+    %         asserts a convergence rate of $\mathcal O(1/T^2)$ for $h(z_T) - h(x_*)$, where $x_*$ is a minimizer assumed to exist. 
+    %         To show that the sequence satisfies 
+    %         \hyperref[thm:ag_generic_stepsize_constraints]
+    %         {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
+    %         first observe that $\epsilon_t = 0$ because 
+    %         \begin{align*}
+    %             L^{-1} + \eta_t 
+    %             &= 
+    %             L^{-1} + \frac{t - 1}{2L}
+    %             \\
+    %             &= \frac{t + 1}{2L}
+    %             \\
+    %             &= \tilde \eta_{t + 1}. 
+    %         \end{align*}
+    %         Therefore this is a similar triangle method. 
+    %         Next observe that conditions showed in 
+    %         \hyperref[thm:ag_generic_stepsize_constraints]
+    %         {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
+    %         can be simplified in this context because the two equalities reduces to just one when $\epsilon_t =0$ for all $t \in \N$ by 
+    %         \begin{align*}
+    %             \tilde \eta_{t + 1}(\tilde \eta_{t + 1} - L^{-1}) 
+    %             - L^{-1}\sigma_t &= 0
+    %             \\
+    %             \iff 
+    %             \tilde \eta_{t + 1}\eta_t &= L^{-1}\sigma_t. 
+    %         \end{align*}
+    %         Hence it only requires to verify the equality $\tilde \eta_{t + 1}\eta_t = L^{-1} \sigma_t$. 
+    %         With that we have 
+    %         \begin{align*}
+    %             \sigma_t &= \sum_{i = 1}^{t} \frac{i}{2L}
+    %             \\
+    %             &= \frac{1}{2L}\left(
+    %                 \frac{t(t + 1)}{2}
+    %             \right)
+    %             \\
+    %             &= \frac{t(1 + t)}{4L}
+    %             \\
+    %             \iff 
+    %             L^{-1}\sigma_t &= 
+    %             \frac{t(1 + t)}{4L^2}
+    %         \end{align*}
+    %         By definition of the stepsizes the LHS of the equality evaluates to
+    %         \begin{align*}
+    %             \tilde \eta_{t + 1} \eta_{t + 1}
+    %             &= \frac{t + 1}{2L} \frac{t}{2L} 
+    %             \\
+    %             &= L^{-1}\sigma_t. 
+    %         \end{align*}
+    %     \end{proof}
+
+    % \subsection{Recovering Chambolle, Dossal 2015}
+    %     In this section we show that the algorithm presented in the literature by Chambolle Dossal \cite{chambolle_convergence_2015} is an example of 
+    %     Definition \ref*{def:ag_prox_grad_generic}. 
+    %     The next definiton present the algorithm in our notations
+    %     \begin{definition}\label{def:chamb_dossal}
+    %         Assume that $h = f + g$ where $f$ is $L$-smooth, $f,g$ are convex. 
+    %         Let $t_n = (n + a - 1)/a$ for all $t \in \N$, $a > 2$. 
+    %         The algorithm by Chambolle Dossal has iterates $(x_n, y_n, z_n)$ satisfying for all $n \in \N$: 
+    %         \begin{align*}
+    %             z_{n + 1} &= y_n - L^{-1} \mathcal G_L(y_n), 
+    %             \\
+    %             x_{n + 1} &= z_n + t_{n +1} (z_{n + 1} - z_n), 
+    %             \\
+    %             y_{n + 1} &= \left(
+    %                 1 - \frac{1}{t_{n + 1}}
+    %             \right)z_{n + 1} + \left(
+    %                 \frac{1}{t_{n + 1}}
+    %             \right)x_{n + 1}. 
+    %         \end{align*}
+    %     \end{definition}
+    %     \begin{lemma}
+    %         Suppose that the generic form as given by 
+    %         \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}
+    %         admits stepsize $\tilde \eta_t, \eta_t$ as
+    %         \begin{align*}
+    %             L\eta_n = t_n - 1,
+    %             \\
+    %             \tilde \eta_{n + 1} = L^{-1} + \eta_n. 
+    %         \end{align*}
+    %         Then it's algebraically equivalent to 
+    %         \hyperref[def:chamb_dossal]{Definition \ref*{def:chamb_dossal}}. 
+    %     \end{lemma}
+    %     \begin{proof}
+    %         By second equality: $\tilde \eta_{n + 1} = \eta_n + L^{-1}$, we can use 
+    %         \hyperref[lemma:sim_triangle_form]{Lemma \ref*{lemma:sim_triangle_form}}. 
+    %         Therefore, substituting $L\eta_n = t_n - 1$, $x_{n + 1}, y_{n + 1}$ in the generic form has 
+    %         \begin{align*}
+    %             x_{n + 1} &= 
+    %             (1 + L\eta_n) z_{n + 1} - L\eta_n z_n
+    %             \\
+    %             & = 
+    %             t_n z_{n + 1} + (1 - t_n) z_n 
+    %             \\
+    %             &= z_n + t_n(z_{n +1} - z_n)
+    %             \\
+    %             y_{n + 1} &= (1 + L\eta_{n + 1})^{-1} (L\eta_{n + 1} z_{n + 1} + x_{n + 1})
+    %             \\
+    %             &= t^{-1}_{n + 1} ((t_{n + 1} - 1)z_n + x_{n + 1})
+    %             \\
+    %             &= (1 - t_{n + 1}^{-1})z_{n + 1} + t^{-1}x_{n + 1}. 
+    %         \end{align*}
+    %         This is the same as
+    %         \hyperref[def:chamb_dossal]{Definition \ref*{def:chamb_dossal}}. 
+    %     \end{proof}
+    %     \begin{remark}
+
+    %     \end{remark}
 

### 2024-09-09 Notebook LaTEX/Momentum Accelerations/paper.tex
=w=, fixes and shit

@@
             \end{aligned}
-            % \\& 
-            % \begin{aligned}
-            %     &= h(z) + 
-            %         \langle \mathcal G_L(x), x^+ - z\rangle 
-            %     - \frac{\mu}{2}\Vert z - x\Vert^2
-            %     + \frac{L}{2}\Vert x - x^+\Vert^2
-            % \end{aligned}
-            % \\& 
-            % \begin{aligned}
-            %     &= h(z) + \langle L(x - x^+), x^+ - x + x - z\rangle 
-            %     - \frac{\mu}{2}\Vert z - x\Vert^2
-            %     + \frac{L}{2}\Vert x - x^+\Vert^2
-            % \end{aligned}
-            % \\&
-            % \begin{aligned}
-            %     &= h(z) + 
-            %     \underbrace{\langle L(x - x^+), x - z\rangle}_{
-            %         = - \langle \mathcal G_L (x), z - x\rangle
-            %     }
-            %     - \frac{\mu}{2}\Vert z - x\Vert^2
-            %     - \frac{L}{2}\Vert x - x^+\Vert^2
-            % \end{aligned}
         \end{align*}
@@
         \hyperref[lemma:grad-map-approx-subgrad]{Lemma \ref*{lemma:grad-map-approx-subgrad}}, 
-        we have $\mathcal G_L(x) \in \nabla f(x) + \partial g(x^+)$, choose $v \in \partial g(x^+)$ such that $G_L(x) = \nabla f(x) + \partial g(x^+)$, it yields
+        we have $\mathcal G_L(x) \in \nabla f(x) + \partial g(x^+)$, choose $v \in \partial g(x^+)$ such that $G_L(x) = \nabla f(x) + v = L(x - x^+)$, so it yields
         \begin{align*}
             h(x^+) & 
-            \le h(z) + 
-            \langle \nabla f(x) + v, x^+ - z\rangle 
+            \le  
+            h(z) + \langle L(x - x^+), x^+ - x + x - z\rangle 
             - \frac{\mu}{2}\Vert z - x\Vert^2
             + \frac{L}{2}\Vert x - x^+\Vert^2
+            \\
+            &= h(z) + 
+            \underbrace{\langle L(x - x^+), x - z\rangle}_{
+                = - \langle \mathcal G_L (x), z - x\rangle
+            }
+            - \frac{\mu}{2}\Vert z - x\Vert^2
+            - \frac{L}{2}\Vert x - x^+\Vert^2
         \end{align*}
@@
     \begin{proof}
-        Observe that we have 
-        \begin{align*}
-            \quad &
+        Observe that we have for all $u$: 
+        \begin{align*}
+            h(u) &\ge 
             h(\mathcal T_L\bar x) + 
@@
             a convergence of $\mathcal O(\sigma_T^{-1})$ is possible. 
-            Since $a_t = \tilde \eta_t$, and the Nesterov sequence exhibits $a_{t} \ge (t + 2)/2$, the convergence becomes $\mathcal O(T^{-2})$. 
+            Since $a_t = L\tilde \eta_t$, and the Nesterov sequence exhibits $a_{t} \ge (t + 2)/2$, the convergence becomes $\mathcal O(T^{-2})$. 
             It is the optimal convergence rate for all convex functions. 

### 2024-09-16 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, updates the notes

@@
     \par
-    Throughout this section, we assume 
+    Through out this section, we assume 
     \begin{enumerate}
@@
 \appendix
+\section{Scratch paper stuff}
+    Throughout this subsection, we make the following list of assumptions: 
+    \begin{enumerate}
+        \item $h = f + g$, 
+        \item $f, g$ are convex functions, 
+        \item $f$ is differentiable with $L$-Lipschitz smooth gradient and it's $\mu \ge 0$ strongly convex,
+        \item Let $\mathcal T_L, \mathcal G_L$ be the proximal gradient and gradient mapping operator be given by \\
+        \hyperref[def:gradient_mapping]{Definition \ref*{def:gradient_mapping}}. 
+    \end{enumerate}
+
+    \subsection{Nesterov momentum with strong convexity}
+        \begin{definition}[generic S-CVX PPM form]\label{def:generic_s-cvx_form}
+            Define the lower bouding function at $x$: 
+            \begin{align*}
+                l_h(z; x) = h(\mathcal T_L x) + \langle \mathcal G_L (x), z - x\rangle
+                + 
+                \frac{L}{2}\Vert x - \mathcal T_L (x)\Vert^2 + \frac{\mu}{2}\Vert z - x\Vert^2
+            \end{align*}
+            We define the following algorithm. 
+            \begin{align*}
+                x_{t + 1} &= \argmin_{x} \left\lbrace
+                    l_h(x; y_t) + \frac{1}{2\tilde \eta_{t + 1}} 
+                    \Vert x - x_t\Vert^2 
+                \right\rbrace
+                \\
+                &= (\mu\tilde \eta_{t + 1} + 1)^{-1} 
+                (\mu\tilde \eta_{t + 1}y_t + x_t - \tilde \eta_{t + 1}\mathcal G_L(y_t))
+                \\
+                y_{t + 1}&= 
+                \argmin_{x}
+                \left\lbrace
+                    h(\mathcal T_L y_t) + \langle \mathcal G_L(y_t), x - y_t\rangle + \frac{L}{2}\Vert x -y_t\Vert^2
+                    + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
+                \right\rbrace
+                \\
+                &= (1 + L \eta_{t +1})^{-1}(L\eta_{t + 1}(y_t - L^{-1}\mathcal G_L(y_t)) + x_{t + 1})
+            \end{align*}
+        \end{definition}
+        \begin{proof}
+            The functions inside of ``argmin" is easy to solve because they are just quadratic functions. 
+            We write it here for future verifications and a peace of the mind. 
+            \begin{align*}
+                x_{t + 1} &= \argmin_{x}\left\lbrace
+                    \langle \mathcal G_L(y_t), x - y_t\rangle 
+                    + 
+                    \frac{\mu}{2}\Vert x - y_t\Vert^2 +  
+                    \frac{1}{2\tilde \eta_{t + 1}}\Vert x - x_t\Vert^2
+                \right\rbrace
+                \\
+                \iff 
+                \mathbf 0 & = 
+                \mathcal G_L(y_t) + \mu(x - y_t) + \tilde \eta_{t + 1}^{-1}(x - x_t)
+                \\
+                &= 
+                \mathcal G_L(y_t) + (\mu + \tilde \eta_{t + 1}^{-1}) x - \mu y_t - \tilde \eta_{t + 1}^{-1} x_t
+                \\
+                \iff 
+                (\mu + \tilde \eta_{t + 1}^{-1})x 
+                &= 
+                \mu y_t + \tilde \eta_{t + 1}^{-1} x_t - \mathcal G_L(y_t)
+                \\
+                \implies 
+                x &= (\mu + \tilde \eta_{t + 1}^{-1})^{-1 }
+                (\mu y_t + \tilde \eta_{t + 1}^{-1} x_t - \mathcal G_L(y_t)). 
+            \end{align*}
+            We can make the assumption that $\mu + \eta_{t + 1}^{-1} \neq 0$ because $\tilde\eta_t > 0$. 
+            Similarly for $y_{t + 1}$, it's solving a simple quadratic minimization problem, yielding: 
+            \begin{align*}
+                \mathbf 0 &= \mathcal G_L(y_t) + L(x - y_t) + \eta_{t + 1}^{-1}(x - x_{t + 1})
+                \\
+                &= (L + \eta_{t + 1}^{-1})x - L y_t - \eta_{t + 1}^{-1}x_{t + 1} + \mathcal G_L(y_t) 
+                \\
+                (L + \eta_{t + 1}^{-1})x &= 
+                Ly_t + \eta_{t + 1}^{-1} x_{t + 1} - \mathcal G_L(y_t)
+                \\
+                \implies 
+                x &= 
+                (L\eta_{t + 1} + 1)^{-1}(L\eta_{t + 1}(y_t - L^{-1}\mathcal G_L(y_t)) + x_{t + 1}). 
+            \end{align*}
+            And hence the results are verified for the peace of the mind. 
+        \end{proof}
+        \begin{remark}\label{remark:generic_s-cvx_ppm_alternative_representation}
+            In the literatures, people accenturate the term $z_{t + 1} = y_t - L^{-1} \mathcal G_L(y_t)$, as a step of gradient descent, and the term $w_t = (\mu\tilde \eta_{t + 1} + 1)^{-1}(\mu\tilde \eta_{t + 1}y_t + x_t)$ so the algorithm can be alternatively presented by the relation
+            \begin{align*}
+                w_{t} &= (\mu\tilde \eta_{t + 1} + 1)^{-1}(\mu \tilde \eta_{t + 1} y_t + x_t) 
+                \\
+                x_{t + 1}&= w_t - \tilde \eta_{t + 1}(\mu\tilde \eta_{t + 1} + 1)^{-1} \mathcal G_L(y_t)
+                \\
+                z_{t + 1}&= y_t - L^{-1}\mathcal G_L(y_t)
+                \\
+                y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}(L\eta_{t + 1}z_{t + 1} + x_{t + 1}). 
+            \end{align*}
+            When $\mu = 0$, it has $w_t = x_t$, producing a simpler relations 
+            \begin{align*}
+                x_{t + 1} &= 
+                x_t - \tilde \eta_{t + 1} \mathcal G_L(y_t)
+                \\
+                z_{t + 1}&= y_t - L^{-1}\mathcal G_L(y_t)
+                \\
+                y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}
+                (L\eta_{t + 1} z_{t + 1} + x_{t + 1}). 
+            \end{align*}
+            The above representation is the same as 
+            \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}.
+
+        \end{remark}
+
+        \begin{definition}[Similar triangle form]\label{def:s-cvx_similar_triangle_form}
+            Let $\mathcal G_L, \mathcal T_L$ be the gradient mapping and proixmal gradient operator of $h = f + g$. 
+            An algorithm is referred to as similar triangle form if its iterates $(x_t, y_t, z_t)$ satisfies the conditions: 
+            \begin{align*}
+                z_{t + 1} &= 
+                y_t - L^{-1}\mathcal G_L(y_t)
+                \\
+                x_{t + 1}&= 
+                z_{t + 1} + \frac{L\eta_t}{1 + \mu\tilde \eta_{t + 1}}(z_{t + 1} - z_t)
+                \\
+                y_{t + 1}&= 
+                (1 + L\eta_{t + 1})^{-1} (L\eta_{t + 1}z_{t + 1} + x_{t + 1}). 
+            \end{align*}
+        \end{definition}
+
+        \begin{definition}[Generic momentum form]\label{def:generic_momentum}
+            Let $\mathcal G_L, \mathcal T_L$ be the gradient mapping and the proximal gradient operator for $h$. 
+            Then the generic momentum form is an algorithm with iterates $(z_t, y_t)$ satisfying the relations 
+            \begin{align*}
+                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
+                \\
+                y_{t + 1 } &= z_{t + 1} + \theta_{t + 1}(z_{t + 1} - z_t)
+            \end{align*}
+            For some $\theta_t \ge 0$. 
+        \end{definition}
+        \begin{remark}
+            Sometimes in the literates the update is expressed differently and it's 
+            \begin{align*}
+                y_{t + 1} &= z_t + (1 + \theta_{t + 1})(z_{t + 1} - z_t). 
+            \end{align*}
+        \end{remark}
+
+        \begin{theorem}[Momentum is algebraically equivalent to similar triangle]
+        \label{thm:momentum_is_similar_triangle}
+            \;\\
+            Let $\tilde \eta_t, \eta_t$
+            satisfies 
+            \begin{align*}
+                \tilde\eta_{t + 1} &= \eta_t + L^{-1} + L^{-1} \mu \tilde\eta_{t + 1},
+            \end{align*}
+            then it reduces 
+            \hyperref[def:generic_s-cvx_form]{Definition \ref*{def:generic_s-cvx_form}}
+            into similar triangle form which is given by 
+            \hyperref[def:s-cvx_similar_triangle_form]
+            {Definition \ref*{def:s-cvx_similar_triangle_form}}, 
+            which is also algebraically equivalent 
+            \hyperref[def:generic_momentum]{Definition \ref*{def:generic_momentum}}
+            and it simplifies to
+            \begin{align*}
+                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t), 
+                \\
+                y_{t + 1} &= z_{t + 1} + 
+                \frac{L\eta_t}{(1 + \mu \tilde\eta_{t + 1})(1 + L\eta_{t + 1})}(z_{t + 1} - z_t)
+            \end{align*}
+        \end{theorem}
+        \begin{proof}
+            We work with the alternative representation listed in 
+            \hyperref[remark:generic_s-cvx_ppm_alternative_representation]
+            {Remark \ref*{remark:generic_s-cvx_ppm_alternative_representation}} which has iterates $(w_t, x_{t + 1}, z_{t + 1}, y_{t + 1})$. 
+            We start by showing that there exists a constant $\alpha \in \RR$ such that $z_{t + 1} - z_t = \alpha (x_{t + 1} - z_{t + 1})$ by $\tilde \eta_{t + 1} = \eta_t + L^{-1} + L^{-1} \mu \tilde \eta_{t + 1}$.
+            Firstly, we have the equality. 
+            \begin{align*}
+                z_{t + 1} - z_t
+                &= 
+                - (L\eta_t)^{-1} y_t 
+                - L^{-1}\mathcal G_L(y_t) + (L \eta_t)^{-1} x_t. 
+            \end{align*}
+            Because 
+            \begin{align*}
+                y_{t} &= (1 + L\eta_{t})^{-1}(L\eta_{t}z_{t} + x_{t})
+                \\
+                (1 + L\eta_t)y_t - x_t &= L\eta_t z_t
+                \\
+                z_t & = (L\eta_t)^{-1}((1 + L\eta_t)y_t - x_t), 
+                \\[1em]
+                z_{t + 1} - z_t 
+                &= \underbrace{ y_t - L^{-1}\mathcal G_L(y_t)}_{=z_{t + 1}}
+                - \underbrace{(L\eta_t)^{-1}((1 + L\eta_t)y_t - x_t)}_{=z_t}
+                \\
+                &= 
+                y_t - L^{-1} \mathcal G_L(y_t) - (L\eta_t)^{-1}y_t - y_t + (L\eta_t)^{-1} x_t
+                \\
+                &= 
+                -L^{-1}\mathcal G_L(y_t) + (L\eta_t)^{-1}(x_t - y_t)
+                \\
+                &= 
+                L^{-1}(\eta_t^{-1}(x_t - y_t) -\mathcal G_L(y_t)). 
+            \end{align*}
+            Next, we have 
+            \begin{align*}
+                x_{t + 1} - z_{t + 1}&= 
+                \left(
+                    (1 + \mu \tilde \eta_{t+ 1})^{-1} (\mu \tilde \eta_{t + 1}y_t + x_t)
+                    - \frac{\tilde \eta_{t + 1}}{1 + \mu\tilde \eta_{t + 1}}
+                    \mathcal G_L(y_t)
+                \right) - \left(
+                    y_t - L^{-1}\mathcal G_L(y_t)
+                \right)
+                \\
+                &= 
+                (1 + \mu \tilde \eta_{t + 1})^{-1}
+                \left(
+                    x_t + \mu \tilde \eta_{t + 1} y_t
+                    - \tilde \eta_{t + 1} \mathcal G_L(y_t)
+                    - (1 + \mu \tilde \eta_{t + 1})
+                    (y_t - L^{-1}\mathcal G_L(y_t))
+                \right)
+                \\
+                &= 
+                (1 + \mu\tilde \eta_{t + 1})^{-1}
+                \left(
+                    x_t - y_t + 
+                    (
+                        -\tilde \eta_{t + 1} + 
+                        (
+                            1 + \mu\tilde \eta_{t + 1})L^{-1}
+                        )
+                        \mathcal G_L(y_t)
+                    )
+                \right)
+                \\
+                &= 
+                (1 + \mu\tilde \eta_{t + 1})^{-1}
+                \left(
+                    x_t - y_t +     
+                    (
+                        - \tilde \eta_{t + 1} + L^{-1}
+                        + \mu \tilde \eta_{t + 1}L^{-1}
+                    )
+                    \mathcal G_L(y_t)
+                \right). 
+            \end{align*}
+            Since 
+            \begin{align*}
+                (1 - L^{-1}\mu)\tilde \eta_{t +1}
+                &= L^{-1} + \eta_t 
+                \\
+                - \tilde \eta_{t + 1} + L^{-1}\mu \tilde \eta_{t + 1}
+                + L^{-1}
+                &= - \eta_t, 
+            \end{align*}
+            so substituting 
+            \begin{align*}
+                x_{t + 1} - z_{t + 1}
+                &= 
+                (1 + \mu \tilde \eta_{t + 1})^{-1}
+                (x_t - y_t - \eta_t \mathcal G_L(y_t))
+                \\
+                &= (1 + \mu \tilde \eta_{t + 1})^{-1}
+                \eta_t(\eta_{t}^{-1}(x_t - y_t) - \mathcal G_L(y_t))
+                \\
+                &= (1 + \mu \tilde \eta_{t + 1})^{-1}
+                \eta_t L(z_{t + 1} - z_t), 
+            \end{align*}
+            therefore 
+            \begin{align*}
+                z_{t + 1} - z_t 
+                &= 
+                \eta^{-1}_tL^{-1}(1 + \mu \tilde \eta_{t + 1})(x_{t + 1} - z_{t + 1})
+                \\
+                \iff 
+                x_{t + 1} - z_{t + 1} &= 
+                \frac{L\eta_t}{1 + \mu \tilde \eta_{t + 1}} 
+                (z_{t + 1} - z_t). 
+            \end{align*}
+            This produces the new updates for $x_{t +1}$, making it the same as the stated similar triangle form. 
+            To attain momentum form, we consider the equation for $y_{t + 1}$, and susbtitute $x_{t + 1}$ producing 
+            \begin{align*}
+                y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}
+                (
+                    L\eta_{t + 1} z_{t + 1} + x_{t + 1}
+                )
+                \\
+                &= 
+                (1 + L\eta_{t + 1})^{-1}
+                \left(
+                    L\eta_{t + 1} z_{t + 1} + z_{t + 1}
+                    + 
+                    \frac{L\eta_t}{1 + \mu \tilde \eta_{t + 1}}
+                    (z_{t + 1} - z_t)
+                \right)
+                \\
+                &= z_{t + 1} 
+                + 
+                \frac{L\eta_t}{(1 + L\eta_{t + 1})(1 + \mu \tilde \eta_{t + 1})}
+                (z_{t + 1} - z_t). 
+            \end{align*}
+            The above exposes the 
+            $\theta_{t + 1} = L\eta_t(1 + L\eta_{t + 1})^{-1}(1 + \mu\tilde \eta_{t + 1})^{-1}$. 
+            Alternatively we also have: 
+            \begin{align*}
+                x_{t + 1} &= z_{t + 1} + (1 + \mu\tilde \eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t)
+                \\
+                &=  (1 + L\eta_t(1 + \mu \tilde \eta_{t + 1})^{-1})z_{t + 1}
+                - L\eta_t(1 + \mu\tilde \eta_{t + 1})z_t
+                \\
+                &= 
+                \left(
+                    \frac{1 + \mu\tilde \eta_{t + 1} + L \eta_t}{1 + \mu \tilde \eta_{t + 1}}
+                \right)z_{t + 1}
+                + 
+                z_t - 
+                \left(
+                    1 + \frac{ L\eta_t}{1 + \mu \tilde \eta_t + 1}
+                \right)z_t 
+                \\
+                &= 
+                \left(
+                    \frac{L\tilde \eta_{t+ 1}}{1 + \mu\tilde \eta_{t + 1}}
+                \right)z_{t + 1}
+                + 
+                z_t 
+                - 
+                \left(
+                    \frac{L\tilde \eta_{t + 1}}{1 + \mu \tilde \eta_{t + 1}}
+                \right)z_t 
+                \\
+                &= z_t + 
+                \left(
+                    \frac{L\tilde \eta_{t + 1}}{1 + \mu \tilde \eta_{t + 1}}
+                \right)
+                (z_{t + 1} - z_t). 
+            \end{align*}
+        \end{proof}
+
+    \subsection{The line search algorithm idea}
+        \par
+        The Nesterov acceleration algorithm can not achieve linear convergence rate for function that has a strongly convexity constant $\mu > 0$. 
+        This claim is showed in Aujol et.al \cite{aujol_optimal_2019}. 
+        Variants of the Nesterov accelerated gradient method that can achieve linear rate of convergence exists but it requires knowledge of $\mu, L$ a priori. 
+        \par
+        Literatures attempts at improving the convergence of FISTA under strong convexity, and other characterizations are vast. 
+        But it can be approximately categorized as two types: 
+        \begin{enumerate}
+            \item Heuristic and adaptive restart. 
+            \item Linear search and estaimating the parameters. 
+        \end{enumerate}
+        \par
+        Let $h = f + g$ where $f, g$ are convex and $f$ is $L$-Lipschitz and $\mu\ge 0$ strongly convex. 
+        List in Beck \cite[(10.7.7)]{beck_first-order_nodate}, the V-FISTA algorithm is: 
+        \begin{align*}
+            z_{n + 1} &= \mathcal T_L(y_n)
+            \\
+            y_{n + 1} &= z_{n + 1} + \frac{\sqrt{\kappa} - 1}{\sqrt{\kappa} + 1}(z_{n + 1} - z_n). 
+        \end{align*}
+        $\kappa = L/\mu$ is the condition number. 
+        The parameters $L, \mu$ can be estimated during the run time of the algorithm. 
+        To establish the estimation we first match the parameters $\tilde \eta_i, \eta_i$ to the momentum parameter presented in V-FISTA. 
+        Then we perform the estimation of $\tilde \eta_i, \eta_i$ using the PPM interpretation for the parameter $L, \mu$. 
+        The following theorem will reduce the generic S-CVX form of the PPM interpretations into the V-FISTA algorithm. 
+        \begin{theorem}[V-FISTA algorithm as similar triangle]
+            \;\\
+            If
+            \begin{align*}
+                \tilde \eta_t 
+                &= \frac{1}{\mu(\sqrt{\kappa} - 1)}
+                \quad \forall t \in \N, 
+                \\
+                \eta_t
+                &= 
+                \frac{1}{\mu\sqrt{\kappa}}
+                \quad \forall t \in \N. 
+            \end{align*}
+            Then the AG generic form simplifies to 
+            \begin{align*}
+                y_{t + 1} &= z_{t + 1} + 
+                \frac{\sqrt{\kappa} - 1}{\sqrt{\kappa} + 1}
+                (z_{t +1} - z_t)
+                \\
+                z_{t + 1} 
+                &= y_t - L^{-1}\mathcal G_L(y_t). 
+            \end{align*}
+            And it is a valid sequence that meaning that it satisfies 
+            \begin{align*}
+            \tilde \eta_{t + 1} = \eta_t + L^{-1} + L^{-1} \mu \tilde \eta_{t + 1}. 
+            \end{align*}
+        \end{theorem}
+        \begin{proof}
+            Observe that we have 
+            \begin{align*}
+                L\eta &= \frac{L}{\mu \sqrt{\kappa}} = \frac{\kappa}{\sqrt{\kappa}} = \sqrt{\kappa}, 
+                \\
+                \mu \tilde \eta &= 
+                \frac{1}{\sqrt{\kappa} - 1}, 
+                \\
+                L\tilde \eta_t &= 
+                \frac{\kappa}{\sqrt{\kappa} - 1}. 
+            \end{align*}
+            since it's a constant wrt to $t$, we use $\eta, \tilde \eta$ to ease the notations. 
+            With that it establishes relations
+            \begin{align*}
+                \frac{L\eta }{(1 + \mu \tilde \eta)(1 + L\eta)}
+                &= 
+                \frac{\sqrt{\kappa}}{
+                    \left(
+                        1 + \frac{1}{\sqrt{\kappa} - 1}
+                    \right)
+                    \left(
+                        1 + \sqrt{\kappa}
+                    \right)
+                }
+                \\
+                &= \frac{\sqrt{\kappa}}{
+                    \left(
+                        \frac{\sqrt{\kappa}}{\sqrt{\kappa} - 1}
+                    \right)(1 + \sqrt{\kappa})
+                }
+                \\
+                &=
+                \frac{\sqrt{\kappa}}{1 + \sqrt{\kappa}}\left(
+                    \frac{\sqrt{\kappa} - 1}{\sqrt{\kappa}}
+                \right)
+                \\
+                &= 
+                \frac{\sqrt{\kappa} - 1}{\sqrt{\kappa} + 1}. 
+            \end{align*}
+            The sequence is valid because 
+            \begin{align*}
+                \tilde \eta_{t + 1} 
+                &= \eta_t + L^{-1} + L^{-1} \mu \tilde \eta_{t + 1}
+                \\
+                (L - \mu)\tilde \eta_{t + 1}
+                &= 
+                1 + L \eta_t 
+                \\
+                L \tilde \eta_{t + 1} - 
+                \mu \tilde \eta_{t + 1}
+                &= 1 + L \eta_t. 
+            \end{align*}
+            Starting from the LHS it yields: 
+            \begin{align*}
+                L\tilde \eta - \mu \tilde \eta 
+                &= \frac{\kappa}{\sqrt{\kappa} - 1} - 
+                \frac{1}{\sqrt{\kappa} - 1}
+                \\
+                &= 
+                \frac{\kappa - 1}{\sqrt{\kappa} - 1}
+                \\
+                &= 
+                \frac{(\sqrt{\kappa} + 1)(\sqrt{\kappa} - 1)}{\sqrt{\kappa} - 1}
+                \\
+                &= 1 + \sqrt{\kappa} = 1 + L \eta. 
+            \end{align*}
+        \end{proof}
+        Therefore, when we have strong convexity constant $\mu > 0$ and Lipschitz parameters $L$, we have a fixed stepsizes $\tilde \eta, \eta$ for the generic form of the algorithm. 
+        When strong convexity doesn't exist locally during the computations of the algorithm, we have to resolve it back to the case when $\mu = 0$. 
+        To do that we have to match the parameters $\tilde \eta_i, \eta_i$ to the Nesterov's momentum used in FISTA.
 

### 2024-09-17 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, updated notes, work home sync
/w\, work home sync

@@
             \end{align*}
-            This produces the new updates for $x_{t +1}$, making it the same as the stated similar triangle form. 
+            This produces the new updates for $x_{t +1}$, making it the same as the stated similar triangle form as in 
+            \hyperref[def:s-cvx_similar_triangle_form]
+                {Definition \ref*{def:s-cvx_similar_triangle_form}}. 
             To attain momentum form, we consider the equation for $y_{t + 1}$, and susbtitute $x_{t + 1}$ producing 
@@
         \end{proof}
+        \par
         Therefore, when we have strong convexity constant $\mu > 0$ and Lipschitz parameters $L$, we have a fixed stepsizes $\tilde \eta, \eta$ for the generic form of the algorithm. 
@@
         To do that we have to match the parameters $\tilde \eta_i, \eta_i$ to the Nesterov's momentum used in FISTA. 
+        Proposed by Chambolle, Dossal \cite{chambolle_convergence_2015}, we have the following representation of the Nesterov accelerated gradient: 
+        \begin{definition}[FISTA]\label{def:fista}
+            The FISTA algorithm has iterates such that they satisfy the following conditions recursively: 
+            \begin{align*}
+                z_{n + 1} &= y_n - L^{-1}\mathcal G_L(y_n)
+                \\
+                x_{n + 1} &= z_n + t_{n +1} (z_{n + 1} - z_n), 
+                \\
+                y_{n + 1} &= \left(
+                    1 - \frac{1}{t_{n + 1}}
+                \right)z_{n + 1} + \left(
+                    \frac{1}{t_{n + 1}}
+                \right)x_{n + 1}
+            \end{align*}
+            where $(t_n)_{n\in \N}$ satisfies: $t_{n + 1}^2 - t_n^2 \le t_n$. 
+        \end{definition}
+        \begin{observation}
+            Observe the fact that the updates of the iterates resemble the similar triangle form in
+            \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}
+        \end{observation}
+        \begin{theorem}[FISTA as a special case of similar triangle form]
+        \label{thm:fista_spacial_case_of_similar_triangle}
+            \;\\
+            if the stepsize $L\eta_n = t_n - 1$, and $\tilde \eta_{n + 1} = L^{-1} + \eta_n$, then
+            \hyperref[def:fista]{Definition \ref*{def:fista}}
+            is an example of 
+            \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}, 
+        \end{theorem}
+        \begin{proof}
+
+        \end{proof}
 

### 2024-09-18 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, work home sync
>w<, updated

@@
 We derive major variants of the Nesterov acceleation algorithm
-    \cite{chambolle_convergence_2015}, \cite{beck_fast_2009}, \cite[Chapter 12]{ryu_large-scale_2022}
+    \cite{chambolle_convergence_2015}, \cite{beck_fast_2009-1}, \cite[Chapter 12]{ryu_large-scale_2022}
     of the accelerated gradient (AG) and find the match of the stepsize parameters in the PPM form.
@@
             \end{align*}
-            then it reduces 
+            then
             \hyperref[def:generic_s-cvx_form]{Definition \ref*{def:generic_s-cvx_form}}
-            into similar triangle form which is given by 
+            reduces into similar triangle form which is given by 
             \hyperref[def:s-cvx_similar_triangle_form]
@@
             \hyperref[def:generic_momentum]{Definition \ref*{def:generic_momentum}}
-            and it simplifies to
+            and it's presented as:
             \begin{align*}
@@
         \begin{enumerate}
-            \item Heuristic and adaptive restart. 
-            \item Linear search and estaimating the parameters. 
+            \item Heuristic regarding restarting the algorithm. 
+            \item Line search and estaimating the parameters: $L, \mu$. 
         \end{enumerate}
+        Beck and Toubolle \cite{beck_fast_2009} proposed the idea of line search for the Lipschitz constant and restarting the algorithm based on function value for assure monotone descending property.
+        Work by Su et.al \cite{su_differential_2015} proposed an ODE understanding and suggested provable linear convergence rate of Nesterov accelerated gradient algorithm under the presence of strong convexity.
+        The ODE understand provoked interest in the restart techniques of AG/FISTA and the approaches are diverse and fruitful.
+
         \par
@@
         \begin{proof}
+            By statement hypothesis we have $\tilde \eta_{n + 1} = L^{-1} + \eta_n$, using 
+            \hyperref[thm:momentum_is_similar_triangle]
+            {Theorem \ref*{thm:momentum_is_similar_triangle}}
+            by setting $\mu = 0$, then by similar triangle form the update for $x_{n + 1}$ is 
+            \begin{align*}
+                x_{n + 1} &= z_{n + 1} + L\eta_t(z_{n +1} - z_n)
+                \\
+                &= z_{n + 1} + (L\tilde \eta_{n + 1} - 1)(z_{n + 1} - z_t)
+                \\
+                &= z_n + L\tilde \eta_{n + 1}(z_{n + 1} - z_n)
+                \\
+                &= z_n + t_n(z_{n + 1} - z_n).
+            \end{align*}
+            At the last line it's simply because $L\tilde \eta_{n + 1} = 1 + L\eta_n = t_n$. 
+            Similarly for the updates for $y_{n + 1}$ we would have: 
+            \begin{align*}
+                y_{n + 1} &= \left(
+                    \frac{L\eta_{n + 1}}{1 + L \eta_{n + 1}}
+                \right)z_{n + 1} + 
+                \left(
+                    \frac{1}{1 + L \eta_{n + 1}}
+                \right) x_{n + 1}
+                \\
+                &= 
+                \left(
+                    1 - \frac{1}{1 + L\eta_{n + 1}}
+                \right)z_{n + 1} + 
+                \left(
+                    \frac{1}{1 + L \eta_{n + 1}}
+                \right)x_{n + 1}
+                \\
+                &= (1 - t_{n + 1}^{-1})z_{n + 1} + t_{n + 1}^{-1}x_{n + 1}. 
+            \end{align*}
 
         \end{proof}
+        \par
+        Define the $l_h$ to be the lower bounding function for $h$ parameterized by any fixed $x\in \RR^n$ as a function of $y$: 
+        \begin{align*}
+            l_h(z; x, \mu)&=  h(\mathcal T_Lx) + \langle \mathcal G_L, z- x\rangle + \frac{L}{2}\Vert x - \mathcal T_Lx\Vert^2 + 
+            \frac{\mu}{2}\Vert z - x\Vert^2
+        \end{align*}
+        Let the sequence $\theta_n$ be a momentum sequence such that it satisfies for all $n\in \N$: 
+        \begin{align*}
+            \theta_{n + 1}^2 - t_n^2 
+            &\le \theta_{n + 1}
+            \\
+            \theta_n &\ge \frac{n + 1}{2}.
+        \end{align*}
+        Define $\mathcal T_L^{h}, G_L^h$ to be the proximal gradient and gradient mapping operator for function $h = f + g$. 
+        Then consider the following algorithmic routine that estimates the strong convexity constant during its executions:
+
+        \begin{algorithm}
+            \caption{Routine 1}\label{alg:routine1}
+            \begin{algorithmic}[1]
+                \Procedure{Routine1}{$L, h=f+g, x_0 = y_0 = z_0, \epsilon > 0$} %\Comment{The gcd of $a$ and $b$}
+                    \State \textbf{Initialize} $\tilde \mu = 0, \eta_0 = 0, \tilde \eta_1 = L^{-1}$
+                    \For{$t = 1, \cdots, N$}
+                        \State $\tilde x \gets (\tilde \mu\tilde \eta_{t + 1} + 1)^{-1}(\tilde \mu \tilde \eta_{t + 1}y_t + x_t - \tilde \eta_{t + 1}\mathcal G_l(y_t))$
+                        \If{$\exists \tilde \mu \in [\epsilon, L]: l_h(\tilde x, x_t, \tilde \mu) \le h(\tilde x)$}
+                            \State \textbf{Find } $\tilde \mu \in [\epsilon, L]$ s.t: $l_h(\tilde x, x_t, \tilde \mu) \le h(\tilde x)$ \Comment{Use binary search}
+                            \State $\tilde \eta_{t + 1} \gets (\sqrt{L\tilde \mu} - \tilde \mu)^{-1}$
+                        \Else \Comment{$\tilde \mu = 0$}
+                            \State $\tilde \mu \gets 0$
+                            \State $\tilde \eta_{t + 1} \gets \theta_tL^{-1}$
+                        \EndIf
+                        \State $\eta_t \gets \tilde \eta_{t + 1} - L^{-1} - L^{-1}\mu\tilde\eta_{t + 1}$
+                        \State $z_{t + 1} \gets y_t - L^{-1}\mathcal G_L(y_t)$
+                        \State $x_{t + 1} \gets (\tilde \mu\tilde \eta_{t + 1} + 1)^{-1}(\tilde \mu \tilde \eta_{t + 1}y_t + x_t - \tilde \eta_{t + 1}\mathcal G_l(y_t))$
+                        \State $y_{t + 1} \gets (1 + L\eta_{t + 1})^{-1}(L\eta_{t + 1}z_{t + 1} + x_{t + 1})$
+                    \EndFor
+                \EndProcedure
+            \end{algorithmic}
+        \end{algorithm}
+        The quantity $\epsilon$ is the tolerance for line search to terminate if it can't find any such value.
 

### 2024-09-18 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, sync

@@
         Work by Su et.al \cite{su_differential_2015} proposed an ODE understanding and suggested provable linear convergence rate of Nesterov accelerated gradient algorithm under the presence of strong convexity.
-        The ODE understand provoked interest in the restart techniques of AG/FISTA and the approaches are diverse and fruitful.
+        The ODE understandings provoked interest in the restart techniques of AG/FISTA and the approaches are diverse and fruitful. 
+        For example Aujol et.al \cite{aujol_parameter-free_2023,aujol_fista_2022}, Luca et.al \cite{calatroni_backtracking_2019} proposed methods of restarting the FISTA algorithm with an estimate to the strong convexity constant.
+        They proved the convergence rate in $\bar L$ and $\rho$ which are the estimates of Lipschitz constant $L$ through out the algorithm and $\rho \in (0, 1)$ another parameter that assist with the search for strong convexity constant $\mu$.
 
@@
             \begin{algorithmic}[1]
-                \Procedure{Routine1}{$L, h=f+g, x_0 = y_0 = z_0, \epsilon > 0$} %\Comment{The gcd of $a$ and $b$}
-                    \State \textbf{Initialize} $\tilde \mu = 0, \eta_0 = 0, \tilde \eta_1 = L^{-1}$
-                    \For{$t = 1, \cdots, N$}
-                        \State $\tilde x \gets (\tilde \mu\tilde \eta_{t + 1} + 1)^{-1}(\tilde \mu \tilde \eta_{t + 1}y_t + x_t - \tilde \eta_{t + 1}\mathcal G_l(y_t))$
-                        \If{$\exists \tilde \mu \in [\epsilon, L]: l_h(\tilde x, x_t, \tilde \mu) \le h(\tilde x)$}
-                            \State \textbf{Find } $\tilde \mu \in [\epsilon, L]$ s.t: $l_h(\tilde x, x_t, \tilde \mu) \le h(\tilde x)$ \Comment{Use binary search}
-                            \State $\tilde \eta_{t + 1} \gets (\sqrt{L\tilde \mu} - \tilde \mu)^{-1}$
+                \Procedure{Routine1}{$L, \tilde \mu,h=f+g, (x_i, y_i), \epsilon > 0, N\in N, i \in \N$}
+                    \State \textbf{Initialize: } $\eta_i = 0, \tilde \eta_{i + 1} = \eta_i + L^{-1} + \tilde \mu L^{-1} \eta_t$
+                    \State $\tilde x \gets (\tilde \mu\tilde \eta_{i + 1} + 1)^{-1}(\tilde \mu \tilde \eta_{i + 1}y_i + x_i - \tilde \eta_{i + 1}\mathcal G_l(y_t))$
+                    \If{$\exists \tilde \mu \in [\epsilon, L]: l_h(\tilde x, x_t, \tilde \mu) \le h(\tilde x)$ }
+                        \State \textbf{find } $\tilde \mu \in [\epsilon, L]$ s.t: $l_h(\tilde x, x_t, \tilde \mu) \le h(\tilde x)$  
+                        \State \textbf{updates} $\tilde \mu$ accordingly. 
+                        \Comment{Use binary search}
+                        \For{$j = i, \cdots, N$} 
+                            \State $\tilde \eta_{t + j} \gets (\sqrt{L\tilde \mu} - \tilde \mu)^{-1}$
+                        \EndFor
                     \Else \Comment{$\tilde \mu = 0$}
                         \State $\tilde \mu \gets 0$
-                            \State $\tilde \eta_{t + 1} \gets \theta_tL^{-1}$
+                        \For{$j = i, \cdots, N$}
+                            \State $\tilde \eta_{t + i} \gets \theta_{j}L^{-1}$
+                        \EndFor
                     \EndIf
+                    \For{$t = i, \cdots, N$}
                         \State $\eta_t \gets \tilde \eta_{t + 1} - L^{-1} - L^{-1}\mu\tilde\eta_{t + 1}$
@@
         \end{algorithm}
-        The quantity $\epsilon$ is the tolerance for line search to terminate if it can't find any such value.
+        In above 
+        \hyperref[alg:routine1]
+            {Routine \ref*{alg:routine1}}
+        we have 
+        \begin{enumerate}
+            \item $\epsilon$ is the tolerance for line search to terminate if it can't find any such value. 
+            \item $(x_i, y_i)$ be any two iterates. 
+            \item $\tilde \mu$ is any estimate of the strong convexity constant. It should be less than $L$ which is the true Lipschitz smoothness. 
+            \item $i\in \N$ is an index that indicates $(x_i, y_i)$ could already be generated by Routine 1 in prior calls to the Routine 1. 
+        \end{enumerate}
+        Routine 1 estimates $\mu$ then performs accelerated gradient, the strong convexity index locally it then determine the stepsize for $\tilde \eta_t, \eta_t$ to fit either the traditional FISTA algorithm, or their strong convexity variants.
+        It executes for a fixed number of steps $N$ and it repeats periodically to check and update the strong convexity parameter. 
+        However, there are many alternative ways of determining the strong convexity index $\mu$ while performing AG. 
+        When evaluating function value is costly, alternatves that doesn't involve the use of function will accelerates the algorithm. 
+        We propose the following method of estimating the strong convexity constant without using the function value. 
+        Consider any fixed $x, y \in \RR^n$, then 
+        \begin{align*}
+            \tilde \mu = 
+            \frac{
+                \langle \mathcal G_L(x) - \mathcal G_L(y), x - y\rangle
+            }{\Vert x - y\Vert^2}
+        \end{align*}
+        provides an estimate.
 

### 2024-11-05 Notebook LaTEX/Catalyst Accelerations/presets/julia_lstlisting.tex
>w<, commence new latex notebook

--- 2024-04-23 Latex Templates/Scientific/presets/julia_lstlisting.tex
@@
 \usepackage{listings} \lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
+\usepackage{xcolor}
 \lstdefinelanguage{Julia}%
@@
     stringstyle      = \color{magenta},
-    commentstyle     = \color{ForestGreen},
+    commentstyle     = \color{gray},
     showstringspaces = false,

### 2024-11-05 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, updated contents

--- 2024-09-17 Notebook LaTEX/Momentum Accelerations/paper.tex
@@
 
-\title{{\fontfamily{ptm}\selectfont The Proximal Point interpretation of Nesterov accelerated proximal gradient}}
+\title{
+    {
+        \fontfamily{ptm}\selectfont 
+        A Title Here: A Sub Title Here
+    }
+    }
 
@@
     \noindent
-    Nesterov accelreated gradient method has been in the spotlight for the past decades due its wide spread applications and theories of optimal convergence. 
-    Decades later it still opens up new interpretations. 
-    Our work suggests a proximal point interpretation of accelerated gradient method for the method of accelerated proximal gradient method as a major extension to the interpretation proposed by Ahn and Sra \cite{ahn_understanding_2022}.
-    The proofs had been streamlined, extended and new error terms are added to allow a larger set of stepsize sequence for the proximal point interpreation. 
-    Additionally, we conduct numerical experiment for a line search method that dynamically adjust the strong convexity index $\mu$ and Lipschitz constant of the gradient in for algorithm  using the proximal point understanding of accelerated gradient.
+    Abstract example citation \cite{bezanson_julia_2017}.
 
@@
 \noindent{\bfseries 2010 Mathematics Subject Classification:}
-Primary 47H05, 52A41, 90C25; Secondary 15A09, 26A51, 26B25, 26E60, 47H09, 47A63.
-\noindent{\bfseries Keywords:}
+Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
+\noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method.
 
 \section{Introduction}
-    Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
-    Ahn and Sra explored the interpretation of Nesterov acceleration as the proximal point method (PPM) applied to an upper surrogate function, and then a lower surrogate function. 
-    Inspired by the interpretation, we generalize the framework to the case of $h = f + g$ with $f$ Lipschitz smooth and $g$ convex whose proximal mapping can be evaluated exactly for algorithm implementations.
-    As a major extension, our work describes the method of proximal gradient using the PPM interpretations.
-We also compactify the Lypunov analysis with the introduction of an error terms for the convergence proof.
-We derive major variants of the Nesterov acceleation algorithm
-    \cite{chambolle_convergence_2015}, \cite{beck_fast_2009}, \cite[Chapter 12]{ryu_large-scale_2022}
-    of the accelerated gradient (AG) and find the match of the stepsize parameters in the PPM form.
 
-    \par
-    Some of the earlier examples for the extension of the Nesterov acceleration method make use of the classical analysis introduced by Nestrov. 
-    It uses the Nesterov acceleration sequence. 
-    See \cite{guler_new_1992} for an extension of the Nesterov accelerated gradient method to the proximal point method for convex programming. 
-    However the classical analysis found in \cite[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and a specific format of the Nesterov's estimating sequence to accomodate the proof.
-    In Ahn's work however, the complexities are packaged into the proximal point interpretation of accelerated gradient. 
-    It uses a lemma from Moreau envelope for the Lypunov analysis.
-    The interpration allows choices of undetermined parameters to encompass several variants of the Nesterov accelerated gradient algorithm. 
-    Ahn and Sra's approach is inspired by works from Defazio \cite{defazio_curved_2019}, Zeyuan and Lorenzo \cite{allen-zhu_linear_2016}. 
-    Instead of a mirror descent step on the dual, they propose an alternative without the gradient of the dual. 
-    \par
-    Numerous notable variations of Nesterov accelerated gradient exists.
-\cite[(6.1.19)]{nesterov_lectures_2018} described a variant of accelerated gradient restricted to a convex domain $Q$ using Bregman Divergence.
-    Beck and Toubolle \cite{beck_fast_2009} introduced a variant the problem type of smooth plus non-smooth, known as FISTA. 
-    For a variant of accelerated gradient where the iterates converge (weakly in Hilbert space), see Chambolle and Dossal \cite{chambolle_convergence_2015}. 
-    Extension such as the Harpen acceleration for the resolvent operator of a maximally monotone opreator in general is outside of the scope since it not all maximal monotone operator corresponds to a subgradient operator.
-    \par
-    A wide varieties of interpretation for the Nesterov accelerated gradient exist in the literatures. 
-    Consult \cite{su_differential_2015} for a dynamical system interpretation of Nesterov acceleration. 
-    The dynamical system interpretation of the algorithm leads to the valuable insight that restarting the accerlated gradient algorithm would lead to faster convergence rate for the class of strongly convex function.
-    In work by \cite{allen-zhu_linear_2016}, they interpreted the idea of Nesterov acceleration as a combinations of gradient descent and mirror descent.
-
-    % \par
-    % The paper is organized as follow: 
-    % \begin{enumerate}
-    %     \item Section 
-    % \end{enumerate}
+    \subsection{Contributions}
 
 \section{Preliminaries}\label{sec:preliminaries}
-    In this section we introduce the a descent lemma for Proximal Point Method (PPM) in the convex case. 
-    We define the proximal gradient mapping $\mathcal T_L$, and gradient mapping $\mathcal G_L$ for function satisfying 
-    \hyperref[assumption:smooth-nonsmooth-sum]
-    {assumption \ref*{assumption:smooth-nonsmooth-sum}}. 
-    A lower bound function is identified using the gradient mapping operator and proved in
-    \hyperref[lemma:grad_map_linearization]{Lemma \ref*{lemma:grad_map_linearization}}, 
-    this is a key component of the proximal point interpretation of the accelerated gradient method. 
-    \begin{assumption}\label{assumption:smooth-nonsmooth-sum}
-        Let $h = f + g$ where $f, g$ are convex and $f$ is Lipschitz-Smooth with constant $L$. 
-    \end{assumption}
-    \begin{definition}[Strongly convex functions]
-        A function $f: X \mapsto \RR$ is $\beta$-strongly convex
-        with $\beta\geq 0$ if $f - \beta \frac{\Vert \cdot\Vert^2}{2}$ is convex.
-    \end{definition}
-
-    \begin{theorem}[Proximal descent inequality]\label{thm:ppm_descent_ineq}
-        Let $f: \RR^n \mapsto \overline \RR$ be $\beta$ strongly convex with $\beta \ge 0$, fix any $x \in \RR^n$, define $p = \hprox_f(x)$.
-        For all $y \in \RR$ it verifies
-        $$
-            \left(f(p) + \frac{1}{2}\Vert x - p\Vert^2\right)
-            - 
-            \left(
-                f(y) + \frac{1}{2}\Vert x - y\Vert^2 
-            \right)
-            \le 
-            - \frac{(1 + \beta)}{2}\Vert y - p\Vert^2. 
-        $$
-        Recall: $\hprox_f(x) = \argmin_{u}\left\lbrace f(u) + \frac{1}{2}\Vert u - x\Vert^2 \right\rbrace$. 
-    \end{theorem}
-    \begin{proof}
-        See 
-        \hyperref[appendix:proof_ppm_descent_lemma]
-            {Appendix \ref*{appendix:proof_ppm_descent_lemma}}. 
-    \end{proof}
-    \begin{remark}
-        We use this theorem to prove the convergence of the proximal point method. 
-        Observe that when $\beta = 0$, this reduces to \cite[theorem 12.26]{bauschke_convex_2017}. 
-    \end{remark}
-
-    \begin{definition}[The gradient mapping]
-        \label{def:gradient_mapping}
-        Suppose $h = f + g$ satisfies 
-        \hyperref[assumption:smooth-nonsmooth-sum]{Assumption \ref*{assumption:smooth-nonsmooth-sum}}. 
-        Define the proximal gradient operator
-        $$
-            \mathcal T_L(x) := \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)),
-        $$
-        and the gradient mapping operator
-        $$
-            \mathcal G_L(x) = L(x - \mathcal T_L(x)). 
-        $$
-    \end{definition}
-    \begin{remark}
-        The name ``gradient mapping" comes from \cite[(2.2.54)]{nesterov_lectures_2018}, however, Nesterov was referring to only the case when $g$ is an indicator function of a convex set in his writing.
-        Of course, in Amir Beck \cite[10.3.2]{beck_first-order_nodate}, it has the exact same definition for gradient mapping as the above. 
-    \end{remark}
-
-    \begin{lemma}[Gradient mapping approximates subgradient]
-    \label{lemma:grad-map-approx-subgrad}\; \\
-        Suppose $h = f + g$ satisfies 
-        \hyperref[assumption:smooth-nonsmooth-sum]{Assumption \ref{assumption:smooth-nonsmooth-sum}}, 
-        let $\mathcal T_L, \mathcal G_L$ be given by 
-        \hyperref[def:gradient_mapping]{Definition \ref*{def:gradient_mapping}}.
-        Then for all $x$, the gradient mapping verifies
-        \begin{align*}
-            x^+ &= \mathcal T_L(x), 
-            \\
-            \mathcal G_L(x) := L(x - x^+) &\in  \nabla f(x) + \partial g(x^+). 
-        \end{align*}
-        Equivalently, $\exists v \in \partial g(x^+)$ such that $G_L(x) = \nabla f(x) + v = L(x - x^+)$. 
-    \end{lemma}
-    \begin{proof}
-        Using the resolvent definition of the proximal gradient operator and the fact that the single-valuedness in the convex settings, $x^+$ has relations: 
-        \begin{align*}
-            x^+ &= [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f](x)
-            \\
-            [I + L^{-1}\partial g](x^+) &\ni [I - L^{-1}\nabla f](x)
-            \\
-            x^+ + L^{-1}\partial g(x^+) &\ni x - L^{-1}\nabla f(x)
-            \\
-            x^+ - x + L^{-1}\partial g(x^+) &\ni L^{-1}\nabla f(x)
-            \\
-            L(x^+ - x) + \partial g(x^+) &\ni - \nabla f(x)
-            \\
-            L(x - x^+) &\in \nabla f(x) + \partial g(x^+)
-            \\
-            \mathcal G_L(x) &\in \nabla f(x) + \partial g(x^+). 
-        \end{align*}
-    \end{proof}
-
-    \begin{lemma}[Linearized gradient mapping lower bound]
-    \label{lemma:grad_map_linearization}\; \\
-        Suppose that $h = f + g$ satisfies 
-        \hyperref[assumption:smooth-nonsmooth-sum]{Assumption \ref*{assumption:smooth-nonsmooth-sum}}, 
-        further assume that $f$ is strongly convex with index $\mu \ge 0$. 
-        Let $x^+ = \mathcal T_L(x)$ as given in 
-        \hyperref[def:gradient_mapping]{Definition \ref*{def:gradient_mapping}}. 
-        Then for all $z \in \RR$, it satisfies
-        \begin{align*}
-            h(z) &\ge 
-            h(x^+) + 
-            \langle \mathcal G_L (x), z - x\rangle 
-            + 
-            \frac{L}{2}\Vert x - x^+\Vert^2 + \frac{\mu}{2}
-            \Vert z - x\Vert^2. 
-        \end{align*}
-    \end{lemma}
-    \begin{proof}
-        Using the $L$-smoothness of $f$ and convexity of $g, f$, it has inequalities
-        \begin{align*}
-            &f(x^+) \le 
-            f(x) + \langle \nabla f(x), x^+ - x\rangle
-            + \frac{L}{2}\Vert x - x^+\Vert^2, 
-            \\
-            &
-            \frac{\mu}{2}\Vert z - x\Vert^2+ 
-            f(x) + \langle \nabla f(x), z - x\rangle 
-            \le f(z), 
-            \\
-            &g(x^+) \le 
-            g(z) + \langle v, x^+ - z\rangle\quad 
-            \forall v \in \partial g(x^+)
-        \end{align*}
-        For all $v \in \partial g (x^+)$, apply the above by considering the following sequence of relations
-        \begin{align*}
-            h(x^+) &= f(x^+) + g(x^+)
-            \\&
-            \begin{aligned}
-                &\le 
-                \left(
-                    f(x) + \langle \nabla f(x), x^+ - x\rangle
-                    + \frac{L}{2}\Vert x - x^+\Vert^2
-                \right)
-                \\
-                &\qquad  
-                + (g(z) + \langle v, x^+ - z\rangle)
-            \end{aligned}
-            \\&
-            \begin{aligned}
-                &\le 
-                \left(
-                    f(z) - \langle \nabla f(x), z - x\rangle
-                    - \frac{\mu}{2}\Vert z - x\Vert^2
-                    + \langle \nabla f(x), x^+ - x\rangle
-                    + 
-                    \frac{L}{2}\Vert x - x^+\Vert^2
-                \right)
-                \\
-                &\qquad 
-                +
-                (g(z) + \langle v, x^+ - z\rangle)
-            \end{aligned}
-            \\&
-            \begin{aligned}
-                &= 
-                (f(z) + h(z)) 
-                \\
-                &\qquad 
-                + \left(
-                    \langle \nabla f(x), x - z\rangle + 
-                    \langle \nabla f(x), x^+ - x\rangle + 
-                    \langle v, x^+ - z\rangle
-                \right) 
-                \\ 
-                &\qquad 
-                - \frac{\mu}{2}\Vert z - x\Vert^2
-                + \frac{L}{2}\Vert x - x^+\Vert^2
-            \end{aligned}
-            \\& 
-            \begin{aligned}
-                &= h(z) + 
-                \left(
-                    \langle \nabla f(x), x - x^+ + x^+ - z\rangle + 
-                    \langle \nabla f(x), x^+ - x\rangle + 
-                    \langle v, x^+ - z\rangle
-                \right)
-                \\
-                &\qquad 
-                - \frac{\mu}{2}\Vert z - x\Vert^2
-                + \frac{L}{2}\Vert x - x^+\Vert^2
-            \end{aligned}
-            \\& 
-            \begin{aligned}
-                &= h(z) + 
-                \langle \nabla f(x) + v, x^+ - z\rangle 
-                - \frac{\mu}{2}\Vert z - x\Vert^2
-                + \frac{L}{2}\Vert x - x^+\Vert^2
-            \end{aligned}
-        \end{align*}
-        Showed in  
-        \hyperref[lemma:grad-map-approx-subgrad]{Lemma \ref*{lemma:grad-map-approx-subgrad}}, 
-        we have $\mathcal G_L(x) \in \nabla f(x) + \partial g(x^+)$, choose $v \in \partial g(x^+)$ such that $G_L(x) = \nabla f(x) + v = L(x - x^+)$, so it yields
-        \begin{align*}
-            h(x^+) & 
-            \le  
-            h(z) + \langle L(x - x^+), x^+ - x + x - z\rangle 
-            - \frac{\mu}{2}\Vert z - x\Vert^2
-            + \frac{L}{2}\Vert x - x^+\Vert^2
-            \\
-            &= h(z) + 
-            \underbrace{\langle L(x - x^+), x - z\rangle}_{
-                = - \langle \mathcal G_L (x), z - x\rangle
-            }
-            - \frac{\mu}{2}\Vert z - x\Vert^2
-            - \frac{L}{2}\Vert x - x^+\Vert^2
-        \end{align*}
-        Moving everything except $h(z)$ from the RHS to the LHS yield the desired inequality. 
-    \end{proof}
-    \begin{remark}
-        The inequality is analogous to \cite[(2.2.57)]{nesterov_lectures_2018}, however Nesterov stated it only for the case when $g$ is an indicator function of some convex set $Q$. 
-    \end{remark}
-
-\section{The PPM interpreation of accelerated gradient}\label{sec:ppm_interp_of_ag}
-    In this section, we present the generic PPM formulation of the accelerated proximal gradient method. 
-    This is general form presents us with a set of undetermine stepsize parameters $\eta_i, \tilde \eta_i$ that can be changed later to accomodate proofs that take Lypunov functions and phrase the convergence rate using the stepsizes sequence $\tilde \eta_i$.
-    These interpretations are extension in the non-smooth context of Ahn and Sra's work \cite{ahn_understanding_2022} using the proximal gradient mapping operator. 
-    The next definition will start the discussion. 
-    \begin{definition}[Linear lower bounding function]\label{def:gradmap-linear-lowerbnd-fxn}
-        Let $h = f+ g$ satisfies
-        \hyperref[assumption:smooth-nonsmooth-sum]{Definition \ref*{assumption:smooth-nonsmooth-sum}}, 
-        $\mathcal G_L$ given by 
-        \hyperref[def:gradient_mapping]{Definition \ref*{def:gradient_mapping}}. 
-        Define for all $y$ the function
-        \begin{align*}
-            l_h(x; y) = h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle 
-            + \frac{L}{2}\Vert y - \mathcal T_L y\Vert^2. 
-        \end{align*}
-    \end{definition} 
-    \begin{remark}
-        The function satisfies $l_h(x; y) \le h(x)$ for all $x \in \RR, y \in \RR$ by 
-        \hyperref[lemma:grad_map_linearization]
-        {Lemma \ref*{lemma:grad_map_linearization}}. 
-    \end{remark}
-    \par
-    With the above definition, it's possible to formulate a generic form of accelerated gradient method using $l_h(x,y)$ as two proximal point methods anchored at some iterates $x_t, x_{t + 1}$.
-    The formulation is generic because of undetermined stepsize parameter $\eta_t, \tilde \eta_t$ from the two proximal point. 
-    \par
-    We state the PPM interpretation of accelerated gradient in 
-    \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}, 
-    which has the equivalent form as presented in
-    \hyperref[def:ag_prox_grad_generic]
-    {Definition \ref*{def:ag_prox_grad_generic}}. 
-    \hyperref[prop:derive_ag_prox_grad_tript]
-    {Proposition \ref*{prop:derive_ag_prox_grad_tript}} 
-    shows their equivalence. 
-    \par
-    Through out this section, we assume 
-    \begin{enumerate}
-        \item $h=f + g$ satisfies 
-            \hyperref[assumption:smooth-nonsmooth-sum]
-            {Assumption \ref*{assumption:smooth-nonsmooth-sum}}, 
-        \item Using $h$ as given from above, let $\mathcal T_L, \mathcal G_L$ be given by 
-            \hyperref[def:gradient_mapping]
-            {Definition \ref*{def:gradient_mapping}}. 
-        \item Using all above, let $l_h$ be given by 
-            \hyperref[def:gradmap-linear-lowerbnd-fxn]
-            {Definition \ref*{def:gradmap-linear-lowerbnd-fxn}}. 
-    \end{enumerate}
-
-    \begin{definition}[AG proximal gradient PPM generic form]
-    \label{def:ag_prox_grad_ppm}
-        Define $\eta_t, \tilde \eta_t$ to be strictly larger than zero for all $t \in \N$. 
-        With initial iterate $x_0, y_0$, 
-        The generic form has iterates $x_t, y_t$ for all $t \in \N$ that satisfy: 
-        $$
-        \begin{aligned}
-            x_{t + 1} &= \argmin_{x} \left\lbrace
-                l_h(x; y_t) + \frac{1}{2\tilde \eta_{t + 1}} 
-                \Vert x - x_t\Vert^2
-            \right\rbrace,
-            \\
-            y_{t + 1}&= 
-            \argmin_{x}
-            \left\lbrace
-                l_h(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
-                \frac{1}{2\eta_{t + 1}} \Vert x - x_{t + 1}\Vert^2
-            \right\rbrace.
-        \end{aligned}
-        $$
-    \end{definition}
-
-    \begin{definition}[AG proximal gradient generic form]
-    \label{def:ag_prox_grad_generic}
-        Define $\eta_t, \tilde \eta_t$ to be $> 0$ for all $t \in \N$. 
-        With initial iterate $x_0, y_0$.
-        The generic form has iterates $(y_t, x_{t + 1}, z_{t + 1})$ such that 
-        $$
-        \begin{aligned}
-            y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
-            \\
-            x_{t + 1} &= x_t - \tilde \eta_{t + 1} \mathcal G_L(y_t)
-            \\
-            z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
-        \end{aligned}
-        $$
-        for all $t\in \mathbb N$. 
-    \end{definition}
-    \begin{remark}
-        Observe that $z_{t + 1} = y_t^+$. 
-    \end{remark}
-
-    \begin{proposition}
-    \label{prop:derive_ag_prox_grad_tript}
-       We have equalities
-        \begin{align*}
-            x_{t + 1} &= \argmin_{x}
-            \left\lbrace
-                l_h(x, y_t) + \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
-            \right\rbrace
-            \\
-            &= x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-            \\
-            y_{t + 1} &= \argmin_{x}
-            \left\lbrace
-                    h(y_t^+) + \langle \mathcal G_L(y_t), x - y_t\rangle + \frac{L}{2}\Vert x -y_t\Vert^2 + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
-            \right\rbrace
-            \\
-            &= (1 + L\eta_{t + 1})^{-1}
-            (x_{t + 1} + L\eta_{t + 1}(y_t - L^{-1}\mathcal  G_L(y_t))). 
-        \end{align*}
-        This thows
-        \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}
-        and 
-        \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}} 
-        are equivalent. 
-    \end{proposition}
-    \begin{proof}
-        Let $y_t^+ = \mathcal T_L(y_t)$, recall that $l_h(x; y_t) = h(y_t^+) + \langle \mathcal G_L(y_t), x -y_t\rangle \le f(x)$ by 
-        \hyperref[lemma:grad_map_linearization]
-        {Lemma \ref*{lemma:grad_map_linearization}}
-        Since $l_h(x; y_t)$ is a simple linear function wrt $x$, minimizing the quandratic where to get $x_{t + 1} = x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t)$; for $y_{t + 1}$, complete the square on the second and the third terms:
-        \begin{align*}
-            & \frac{L}{2}\left(
-                2\langle L^{-1}\mathcal G_L(y_t), x - y_t\rangle + 
-                \Vert x - y_t\Vert^2
-            \right)
-            \\
-            &= 
-            \frac{L}{2}
-            \left(
-                - \Vert L^{-1} \mathcal G_L(y_t)\Vert^2  
-                + \Vert L^{-1} \mathcal G_L(y_t)\Vert^2 
-                + 
-                2\langle L^{-1} \mathcal G_L(y_t), x - y_t\rangle + 
-                \Vert x - y_t\Vert^2
-            \right)
-            \\
-            &= \frac{L}{2}\left(
-                - \Vert L^{-1}\mathcal G_L(y_t)\Vert^2  
-                + \Vert x - (y_t - L^{-1}\mathcal G_L(y_t))
-                \Vert^2
-            \right), 
-        \end{align*}
-        therefore it transforms into 
-        \begin{align*}
-            y_{t + 1} &=\argmin_{x} \left\lbrace
-                \frac{L}{2}\left\Vert 
-                    x - (y_t - L^{-1}\mathcal G_L(y_t))
-                \right\Vert^2
-                + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
-            \right\rbrace
-            \\
-            &=
-            \frac{
-                \left(y_t - L^{-1}\mathcal G_L(y_t)\right) + x_{t + 1}
-            }{L + \eta_{t + 1}^{-1}}.
-        \end{align*}
-        Define $z_{t + 1} = y_t - \mathcal G_L(y_t) = \mathcal T_L(y_t)$, then the above expression simplifies to 
-        $$
-            y_{t + 1} = (1 + L\eta_{t +1})^{-1}(x_{t + 1}+ L\eta_{t + 1}z_{t + 1}). 
-        $$
-    \end{proof}
-    \begin{remark}
-        $y_{t + 1}$ is the minimizer of a simple quadratic. 
-        Given that the original function $h$ is potentially non-smooth, therefore it's not always an upper bound of $h(x)$. 
-        The upper bound interpretation of the smooth case as proposed by Ahn \cite{ahn_understanding_2022}, Sra for the update of $y_{t + 1}$ fails when $h$ is non-smooth! 
-    \end{remark}
-
-\section{Generic Lyapunov analysis for accelerated gradient via PPM}
-\label{sec:generic_ag_ppm_lyapunov_analysis}
-    In this section we derive the generic convergence rate formuated by $\eta_i, \tilde \eta_i$. 
-    \par
-    The Lypunov function in 
-    \hyperref[thm:generic_ag_convergence]{Theorem \ref*{thm:generic_ag_convergence}}
-    is identical to Ahn and Sra 
-    \cite[section 4.2]{ahn_understanding_2022}, 
-    except for the involvement of the gradient mapping. 
-    We adapated it into the context of proximal gradient by 
-    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
-    {Lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}
-    \par
-    We present the convergence rate by compatifying results into 
-    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
-    {Lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}} 
-    to assist the proof of  
-    \hyperref[thm:generic_ag_convergence]
-    {Theorem \ref*{thm:generic_ag_convergence}} 
-    which states new results that are extension to Ahn and Sra's works by introducing an error term to the Lypunov analysis, allowing for a weaker constraints for the stepsize paramters $\tilde \eta_i, \eta_i$ from
-    \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}. 
-    \hyperref[thm:ag_generic_stepsize_constraints]{Theorem \ref*{thm:ag_generic_stepsize_constraints}}
-    states the weakened constraints on the stepsize parameters $\tilde \eta_i, \eta_i$. 
-    \par
-    Throughout the section, we continue the assumption for $h = f + g$, gradient mapping $\mathcal G_L$ and proximal gradient mapping $\mathcal T_L$ from the previous section.
-
-    \begin{lemma}[Lyapunov inequality]
-    \label{lemma:nsmooth_agg_lyapunov_upper_bound}\;\\
-        Fix any $\bar x, x, z',\tilde\eta > 0$, define
-        \begin{align*}
-            \phi(u) &:= \tilde\eta
-            \left(
-                h( \mathcal T_L\bar x) + \langle \mathcal G_L\bar x, u - \bar x\rangle
-                + \frac{L}{2}\Vert \bar x - \mathcal T_L \bar x\Vert^2 
-            \right), 
-            \\
-            x^+ &:= 
-            \hprox_\phi(x) = x - \tilde \eta\mathcal G_L \bar x,
-            \\
-            \Upsilon_{1}  &:= 
-            \tilde \eta(h(\mathcal T_L \bar x) - h(x_*))
-            + 
-            \frac{1}{2}(\Vert x^+ - x_*\Vert^2 - \Vert x - x_*\Vert^2), 
-            \\
-            \Upsilon_2 &:= 
-            h(\mathcal T_L \bar x) - h(z'). 
-        \end{align*}
-        with $x_*$ being the minimizer of $h$, it has 
-        \begin{align*}
-            \Upsilon_1 &\le 
-            - \tilde \eta \langle \mathcal G_L\bar x, x^+ - \mathcal T_L \bar x\rangle
-            + 
-            \frac{\tilde \eta L}{2} \Vert \bar x - \mathcal T_L \bar x\Vert^2
-            - 
-            \frac{1}{2}\Vert x^+ - x\Vert^2, 
-            \\
-            \Upsilon_2 &\le 
-            \langle \mathcal G_L\bar x, \mathcal T_L \bar x - z'\rangle + 
-            \frac{L}{2}\Vert \mathcal T_L \bar x - \bar x\Vert^2. 
-        \end{align*}
-    \end{lemma}
-    \begin{observation}
-        Function $\phi$ is a linear function that qualifies as a lower bound of $\tilde \eta h$, at $\bar x$ by 
-        \hyperref[lemma:grad_map_linearization]{lemma \ref*{lemma:grad_map_linearization}}.
-    \end{observation}
-    \begin{proof}
-        Observe that we have for all $u$: 
-        \begin{align*}
-            h(u) &\ge 
-            h(\mathcal T_L\bar x) + 
-            \langle \mathcal G_L \bar x, u - \bar x\rangle + 
-            \frac{L}{2}\Vert \bar x - \mathcal T_L \bar x\Vert^2
-            \\
-            &= 
-            h(\mathcal T_L \bar x) + 
-            \langle \mathcal G_L \bar x, u - \mathcal T_L \bar x\rangle
-            + 
-            \langle \mathcal G_L \bar x, \mathcal T_L \bar x - \bar x\rangle
-            + 
-            \frac{L}{2}\Vert \bar x - \mathcal T_L \bar x \Vert^2
-            \\
-            &= 
-            h(\mathcal T_L \bar x) + 
-            \langle \mathcal G_L \bar x, u - \mathcal T_L \bar x\rangle
-            + 
-            \langle 
-                L (\bar x - \mathcal T_L \bar x)
-                , 
-                \mathcal T_L \bar x - \bar x
-            \rangle
-            + 
-            \frac{L}{2}\Vert \bar x - \mathcal T_L \bar x\Vert^2
-            \\
-            &= 
-            h(\mathcal T_L \bar x) + 
-            \langle \mathcal G_L \bar x, u - \mathcal T_L \bar x\rangle 
-            - \frac{L}{2} \Vert \bar x - \mathcal T_L \bar x\Vert^2. 
-        \end{align*}
-        By PPM descent inequality
-        \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}}
-        , let $x_*$ be a minimizer, it claims that 
-        {\small
-        \begin{align*}
-            & 
-            \phi(x^+) - \phi (x^*) + 
-            \frac{1}{2}\left(
-                \Vert x^+ - x_*\Vert^2 - 
-                \Vert x - x_*\Vert^2
-            \right)
-            \le 
-            - \frac{1}{2}\Vert x^+ - x\Vert^2
-            \\
-            \implies &
-            \tilde 
-            \eta 
-            \left(   
-                h(\mathcal T_L \bar x) + 
-                \langle \mathcal G_L \bar x, u - \mathcal T_L \bar x\rangle 
-                - \frac{L}{2} \Vert \bar x - \mathcal T_L \bar x\Vert^2
-            \right)
-            - \tilde \eta h (x_*)
-            +
-            \frac{1}{2}\left(
-                \Vert x^+ - x_*\Vert^2 - 
-                \Vert x - x_*\Vert^2
-            \right)
-            \\
-            &\le 
-            - \frac{1}{2}\Vert x^+ - x\Vert^2
-            \\
-            \iff &
-            \tilde \eta (h(\mathcal T_L\bar x) - h(x_*))  
-            + 
-            \frac{1}{2}\left(
-                \Vert x^+ - x_*\Vert^2 - 
-                \Vert x - x_*\Vert^2
-            \right)
-            \\
-            & \le 
-            - \tilde \eta \langle \mathcal G_L\bar x, x^+ - \mathcal T_L \bar x\rangle
-            + 
-            \frac{\tilde \eta L}{2} \Vert \bar x - \mathcal T_L \bar x\Vert^2
-            - 
-            \frac{1}{2}\Vert x^+ - x\Vert^2. 
-        \end{align*}
-        }
-        Next, for all $z, z'$, it would have by smoothness of $f$: 
-        \begin{align*}
-            f(z) - f(z') &= 
-            f(z) - f(\bar x) + f(\bar x) - f(z')
-            \\
-            &\le 
-            \langle 
-                \nabla f(\bar x), z - \bar x
-            \rangle + 
-            \frac{L}{2}\Vert z - \bar x\Vert^2 
-            + 
-            \langle 
-                \nabla f(\bar x), 
-                \bar x - z'
-            \rangle
-            \\
-            &= 
-            \langle \nabla f(\bar x), z - z'\rangle
-            + 
-            \frac{L}{2}\Vert z - \bar x\Vert^2. 
-        \end{align*}
-        The convexity of $g$ yields for all $v \in \partial g(z)$: 
-        \begin{align*}
-            g(z) + 
-            \langle 
-                v, z' - z
-            \rangle 
-            &\le g(z')
-            \\
-            g(z) - g(z') 
-            &\le 
-            \langle v, z - z'\rangle. 
-        \end{align*}
-        Adding them yield 
-        \begin{align*}
-            h(z) - h(z') &\le 
-            \langle \nabla f(\bar x) +v, z - z'\rangle + 
-            \frac{L}{2}\Vert z - \bar x\Vert^2. 
-        \end{align*}
-        Setting $z = \mathcal T_L \bar x$, use 
-        \hyperref[lemma:grad-map-approx-subgrad]
-        {Lemma \ref*{lemma:grad-map-approx-subgrad}}, 
-        there exists $v \in \partial g (\mathcal T_L(\bar x))$ such that $\mathcal G_L(\bar x) = \nabla f(z) + v$, hence the theorem is proved. 
-    \end{proof}
-    \begin{remark}\label{remark:upsilon-upperbound-for-iterates}
-        Let $y_t, x_t$ be given by
-        \hyperref[def:ag_prox_grad_generic]
-        {Definition \ref*{def:ag_prox_grad_generic}}.
-        Set $\bar x = y_t, x = x_t$, then 
-        \begin{align*}
-            x^+ &= x_t - \mathcal G_L y_t = x_{t + 1},
-            \\
-            z_{t + 1} &= \mathcal T_L y_t = \mathcal T_L \bar x.
-        \end{align*}
-        Set $z' = z_t, \tilde \eta = \tilde \eta_{t + 1}$, we define the quantities: 
-        \begin{align*}
-            \Upsilon_{1, t + 1}^{\text{AG}}
-            &:= 
-            \tilde \eta_{t + 1}(h(z_{t + 1}) - h(x_*))
-            + 
-            \frac{1}{2}(\Vert x_{t + 1} - x_*\Vert^2 + \Vert x_t - x_*\Vert^2),
-            \\
-            \Upsilon_{2, t + 1}^{\text{AG}}
-            &:= 
-            h(z_{t + 1}) - h(z_t). 
-        \end{align*}
-        Then it as inequalities: 
-        \begin{align*}
-            \Upsilon_{1, t + 1}^{\text{AG}}
-            &\le 
-            - \tilde \eta_{t + 1}\langle \mathcal G_L y_t, x_{t + 1} - z_{t + 1}\rangle
-            + 
-            \frac{\tilde \eta_{t + 1}L}{2}
-            \Vert  
-                y_t - z_{t + 1}
-            \Vert^2
-            - 
-            \frac{1}{2}
-            \Vert x_{t + 1} - x_t\Vert^2,  
-            \\ 
-            \Upsilon_{2, t + 1}^{\text{AG}}
-            &\le 
-            \langle \mathcal G_L \bar x, z_{t + 1} - z_t \rangle + 
-            \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2.
-        \end{align*}
-        This is useful for the convergence proof of the algorithm. 
-    \end{remark}
-
-    \begin{theorem}[Generic AG convergence]
-    \label{thm:generic_ag_convergence}
-        Let $\Upsilon_{1, t + 1}^\text{AG}, \Upsilon_{2, t + 1}^\text{AG}$ be given by 
-        \hyperref[remark:upsilon-upperbound-for-iterates]
-        {Remark \ref*{remark:upsilon-upperbound-for-iterates}}. 
-        Let $z_t$ be given by 
-        \hyperref[def:ag_prox_grad_generic]
-        {Definition \ref*{def:ag_prox_grad_generic}}. 
-        Define the Lyapunov function $\Phi_t\; \forall t \in \{0\}\cup \N$, $S_t$ and $\sigma_t$: 
-        \begin{align*}
-            S_t &:= \sum_{i = 1}^{t} \delta_i \quad \forall t \in \N,
-            \\
-            \sigma_t &:= \sum_{i = 1}^{t}\tilde \eta_i \quad \forall t \in \N, 
-            \\
-            \Phi_0 &:= \frac{1}{2}\Vert x_0 - x_*\Vert^2, 
-            \\
-            \Phi_t &:= 
-                \sigma_t(h(z_t) - h(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 
-            \quad \forall t \in \N.
-        \end{align*}
-        If there exists a sequence of $(\eta_i)_{i \in \N}$ as defined in
-        \hyperref[def:ag_prox_grad_ppm]
-        {Definition \ref*{def:ag_prox_grad_ppm}} 
-        such that
-        \begin{align*}
-            & \Phi_{t + 1} - \Phi_{t} =
-            \sigma_t\Upsilon_{2, t + 1}^{\text{AG}} 
-            + 
-            \Upsilon_{1, t + 1}^{\text{AG}} 
-            \le \delta_{t + 1} \quad 
-            \forall t \in \mathbb N, 
-            \\
-            & \Upsilon_{1, 1}^{\text{AG}} \le \delta_1. 
-        \end{align*}
-        for some $\delta_i, i \in \N$. 
-        Then
-        \begin{align*}
-            h(z_T) - h(x_*) &\le 
-            \sigma_T^{-1}\left(
-                S_{T} + \frac{1}{2}\Vert x_0 - x_*\Vert^2
-            \right). 
-        \end{align*}
-        Where $x_*$ is an minimizer of $h$. 
-        So $h(z_T) - h(x_*)$ has convergence rate $\mathcal O(\sigma_T^{-1})$ when $S_T \le 0$, and $\mathcal O(\sigma_T^{-1}S_T)$ when $S_T > 0$. 
-    \end{theorem}
-    \begin{proof}
-        By definition we have
-        {\footnotesize
-        \begin{align*}
-            \Phi_{t + 1} - \Phi_t 
-            &= 
-            \left(
-                \sum_{i = 1}^{t+1} \tilde\eta_{i}
-            \right) (h(z_{t + 1}) - h(x_*)) 
-            - 
-            \left(
-                \sum_{i = 1}^{t} \tilde\eta_{i}
-            \right) (h(z_{t}) - h(x_*)) 
-            + \frac{1}{2}\Vert x_t - x_*\Vert^2
-            - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
-            \\
-            &= 
-            \tilde \eta_{t + 1} (h(z_{t + 1}) - h(z_*))
-            +
-            \left(
-                \sum_{i = 1}^{t} \tilde \eta_i
-            \right)(h(z_{t + 1}) - h(z_t))
-            + \frac{1}{2}\Vert x_t - x_*\Vert^2
-            - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
-            \\
-            &= \left(
-                \sum_{i = 1}^{t} \tilde \eta_i
-            \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le \delta_{t + 1}. 
-        \end{align*}
-        }
-        Telescoping for $t = 0, \cdots, T- 1$
-        \begin{align*}
-            \Phi_T - \Phi_0 = 
-            \sum_{i = 0}^{T - 1}\Phi_{i + 1} - \Phi_i 
-            &\le 
-            \sum_{i = 0}^{T - 1}\delta_{i + 1}
-            = S_{T}. 
-        \end{align*}
-        So then $\Phi_T - \Phi_0$ yields: 
-        \begin{align}
-            \sigma_T (h(z_T) - h(x_*)) 
-            + \frac{1}{2}\Vert x_t - x_*\Vert^2 
-            - \frac{1}{2}\Vert x_0 - x_*\Vert^2 
-            &\le S_{T}
-            \\
-            \implies 
-            \sigma_T(h(z_T) - h(x_*))
-            &\le 
-            S_T + \frac{1}{2}\Vert x_0 - x_*\Vert^2
-            \\
-            h(z_T) - h(x_*) &\le 
-            \sigma_T^{-1}\left(
-                S_{T} + \frac{1}{2}\Vert x_0 - x_*\Vert^2
-            \right),
-        \end{align}
-        which yields a convergence rate $\mathcal O(\sigma_T^{-1}S_{T})$. 
-        When $S_T = 0$, the convergence rate is $O(\sigma_T^{-1})$ instead. 
-    \end{proof}
-
-    \begin{theorem}[Constraints of PPM stepsize sequence]
-    \label{thm:ag_generic_stepsize_constraints}\;\\
-        Let iterates $z_t, x_t, y_t$ be given by
-        \hyperref[def:ag_prox_grad_generic]
-        {Definition \ref*{def:ag_prox_grad_generic}}. 
-        If the stepsize $\eta_i, \tilde \eta_i$ satisfies relations 
-        \begin{align*}
-            \begin{cases}
-                \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
-                - L^{-1} \sum_{i= 1}^{t}\tilde \eta_i 
-                = 
-                \epsilon_{t + 1} \tilde \eta_{t + 1}
-                & \forall t \in \mathbb N, 
-                \\
-                L \eta_t \tilde \eta_{t + 1} = \sum_{i=1}^{t}\tilde \eta_i 
-                & \forall t \in \mathbb N. 
-            \end{cases}
-        \end{align*}
-        Then for all $t \in \N$
-        $$
-            \epsilon_{t + 1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}, 
-        $$
-        and 
-        \begin{align*}
-            \Phi_{t + 1} - \Phi_t =
-            \Upsilon_{1, t + 1}^\text{AG} + 
-            \sigma_t\Upsilon_{1, t + 1}^{\text{AG}}
-            &\le
-            \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2.
-        \end{align*}
-        Define $\delta_{t + 1} = \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2$. 
-        Then the convergence rate stated in 
-        \hyperref[thm:generic_ag_convergence]
-        {Theorem \ref*{thm:generic_ag_convergence}}
-        applies. 
-    \end{theorem}
-    \begin{proof}
-        With $t \in \mathbb N \cup \{0\}$ fixed, 
-        recall that for the proximal gradient PPM generic form 
-        (as formulated in 
-        \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}) 
-        for $t\in \mathbb N$ it has: 
-        \begin{align*}
-            y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
-            \\
-            x_{t + 1} &= x_t - \tilde \eta_{t + 1} \mathcal G_L(y_t)
-            \\
-            z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t). 
-        \end{align*}
-        Recall the upper bounds from 
-        \hyperref[remark:upsilon-upperbound-for-iterates]
-        {Remark \ref*{remark:upsilon-upperbound-for-iterates}}
-        it has 
-        \begin{align*}
-            \Upsilon_{1, t + 1}^\text{AG}
-            &= 
-            \tilde\eta_{t + 1} (h(z_{t + 1}) - h(x_*)) + 
-            \frac{1}{2} (
-                \Vert x_{t + 1} - x_*\Vert^2
-                - 
-                \Vert x_t - x_*\Vert^2
-            )
-            \\
-            &\le 
-            - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 
-            + \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2
-            - \langle 
-                \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                x_{t + 1} - z_{t + 1}
-            \rangle, 
-            \\
-            \Upsilon_{2, t + 1}^\text{AG}
-            &= 
-            h(z_{t + 1}) - h(z_t) 
-            \le 
-            \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
-            \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2. 
-        \end{align*}
-        Because the iterates are produced by 
-        \hyperref[def:ag_prox_grad_generic]
-        {Definition \ref*{def:ag_prox_grad_generic}}
-        vector $x_{t + 1} - x_t$ and $z_{t + 1} - y_t$ are parallel by observations: 
-        \begin{align*}
-            x_{t + 1} - x_t &= -\tilde\eta_{t + 1}\mathcal G_L(y_t), 
-            \\
-            z_{t + 1} - y_t &= -L^{-1}\mathcal G_L(y_t). 
-        \end{align*}
-        This allows for 
-        \begin{align*}
-            \Upsilon_{1, t + 1}^{\text{AG}} 
-            &\le 
-            - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 + 
-            \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2 
-            - 
-            \langle \tilde\eta_{t + 1}\mathcal G_L (y_t), x_{t + 1} - z_{t + 1} \rangle
-            \\
-            &= 
-            - \frac{1}{2}\Vert \tilde\eta_{t + 1} \mathcal G_L(y_t)\Vert^2 + 
-            \frac{\tilde\eta_{t + 1}L}{2}\Vert L^{-1} \mathcal G_L(y_t)\Vert^2
-            - 
-            \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), x_{t + 1} - z_{t + 1} \rangle
-            \\
-            &= 
-            \frac{1}{2}\left(
-                - \tilde\eta_{t + 1}^2 + 
-                L^{-1}\tilde\eta_{t + 1}
-            \right)\Vert \mathcal G_L(y_t)\Vert^2
-            - 
-            \langle 
-                \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                (x_{t + 1} - x_{t}) + x_t
-                + (y_t - z_{t + 1}) - y_t
-            \rangle
-            \\
-            &= 
-            \frac{1}{2}\left(
-                L^{-1}\tilde\eta_{t + 1}
-                - \tilde\eta_{t + 1}^2
-            \right)\Vert \mathcal G_L(y_t)\Vert^2
-            - 
-            \langle 
-                \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                -\tilde\eta_{t + 1}\mathcal G_L(y_t) + x_t 
-                + L^{-1}\mathcal G_L(y_t) - y_t
-            \rangle
-            \\
-            &= 
-            \frac{1}{2}\left(
-                L^{-1}\tilde\eta_{t + 1}
-                - \tilde\eta_{t + 1}^2
-            \right)\Vert \mathcal G_L(y_t)\Vert^2
-            - \langle 
-                \tilde\eta_{t +1}\mathcal G_L(y_t), 
-                (L^{-1} - \tilde\eta_{t + 1})\mathcal G_L(y_t) + x_t - y_t
-            \rangle
-            \\
-            &= \frac{1}{2}\left(
-                L^{-1}\tilde\eta_{t + 1} - \tilde\eta_{t + 1}^2 
-                + 2 \tilde\eta_{t + 1}^2 - 2\tilde\eta_{t + 1}L^{-1}
-            \right)\Vert \mathcal G_L(y_t)\Vert^2
-            - 
-            \langle 
-                \tilde\eta_{t + 1} \mathcal G_L(y_t), 
-                x_t - y_t
-            \rangle
-            \\
-            &= 
-            \frac{1}{2}\left(
-                \tilde\eta_{t + 1}^2 - \tilde\eta_{t + 1}L^{-1}
-            \right)\Vert \mathcal G_L(y_t)\Vert^2 
-            + \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), y_t - x_t\rangle.
-        \end{align*}
-        Similarly 
-        \begin{align*}
-            \Upsilon_{2, t + 1}^{\text{AG}} 
-            &\le 
-            \langle \mathcal G_L(y_t), z_{t + 1} - z_t\rangle + 
-            \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-            \\
-            &= 
-            \langle \mathcal G_L(y_t), z_{t + 1} - y_t + y_t - z_t\rangle
-            + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
-            \\
-            &= 
-            \langle \mathcal G_L(y_t), - L^{-1} \mathcal G_L(y_t) + y_t - z_t\rangle
-            + 
-            \frac{L}{2}\Vert L^{-1}\mathcal G_L(y_t)\Vert^2
-            \\
-            &= 
-            -L^{-1}\Vert \mathcal G_L(y_t)\Vert^2 
-            + 
-            (1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2 
-            + 
-            \langle \mathcal G_L(y_t), y_t - z_t\rangle
-            \\
-            &= 
-            -(1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2
-            + 
-            \langle \mathcal G_L(y_t), y_t - z_t\rangle. 
-        \end{align*}
-        Observe that the cross product term for $\Upsilon_{1, t + 1}^\text{AG}, \Upsilon_{2, t + 1}^\text{AG}$ doesn't match. 
-        Hence let's consider the update for $y_t$, which can be written as $y_t - x_t = L \eta_t (z_t - y_t)$.
-We make the choice to do surgery on upper bound of $\Upsilon_{2, t + 1}^\text{AG}$, so $\langle \mathcal G_L(y_t), y_t - x_t\rangle = \langle \mathcal G_L(y_t), L \eta_t (z_t - y_t)\rangle$.
-        With this in mind, RHS of $\Phi_{t + 1} - \Phi_t$ yields: 
-        {\footnotesize
-        \begin{align*}
-            &\Upsilon_{1, t + 1}^\text{AG} + 
-            \left(
-                \sum_{i = 1}^{t}\tilde\eta_i 
-            \right)\Upsilon_{2, t + 1}^{\text{AG}}
-            \\
-            &\le 
-            \frac{1}{2}\left(
-                \tilde\eta_{t + 1}^2 - \tilde\eta_{t + 1}L^{-1}
-            \right)\Vert \mathcal G_L(y_t)\Vert^2 
-            + 
-            \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), L\eta_t(z_t - y_t)\rangle
-            \\ 
-            &\quad 
-            + 
-            \left(
-                \sum_{i = 1}^{t}\tilde\eta_i 
-            \right)\left(
-                -(1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2
-                + 
-                \langle \mathcal G_L(y_t), y_t - z_t\rangle
-            \right)
-            \\
-            &= 
-            \left(
-                \frac{1}{2}\tilde\eta_{t + 1}\left(
-                    \tilde \eta_{t +1} - L^{-1}
-                \right)
-                - 
-                \frac{1}{2L}\sum_{i = 1}^{t}\tilde \eta_i
-            \right)\Vert \mathcal G_L(y_t)\Vert^2 + 
-            \left(
-                L\eta_t \tilde \eta_{t + 1} - \sum_{i = 1}^{t}\tilde \eta_i
-            \right)\langle \mathcal G_L(y_t), z_t - y_t\rangle. 
-        \end{align*}
-        }
-        The non-negativity of $\Vert \mathcal G_L(y_t) \Vert^2$ characterize the culmulative error $\delta_{t + 1}$ in the Lypunov analysis through sequence $\epsilon_i$. 
-        Setting the coefficient of $\Vert \mathcal G_L(y_t) \Vert^2$ to be $\epsilon_{t + 1}\tilde \eta_{t + 1}$, it yields a system of inequality: 
-        \begin{align*}
-            \begin{cases}
-                \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
-                - L^{-1} \sum_{i= 1}^{t}\tilde \eta_i 
-                = 
-                \epsilon_{t + 1} \tilde \eta_{t + 1}
-                & \forall t \in \N, 
-                \\
-                L \eta_t \tilde \eta_{t + 1} = \sum_{i=1}^{t}\tilde \eta_i 
-                & \forall t \in \N. 
-            \end{cases}
-        \end{align*}
-        It requires base case $L\eta_0\tilde\eta_{1} = 0$, assume $\sigma_0 = 0$. 
-        We use $\sum_{i = 1}^t \tilde \eta_i = \sigma_t$, simplifying the first equation we have 
-        \begin{align*}
-            \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
-            - L^{-1} \sigma_t
-            &= 
-            \epsilon_{t + 1} \tilde \eta_{t + 1}
-            \\
-            \iff 
-            \tilde \eta_{t + 1} ^2 - L^{-1} \tilde \eta_{t + 1} 
-            &= 
-            \epsilon_{t + 1} \tilde \eta_{t + 1} + L^{-1} \sigma_t
-            \\
-            &= 
-            \epsilon_{t + 1} \tilde \eta_{t + 1} 
-            + L^{-1}(L \eta_t \tilde \eta_{t + 1})
-            \\
-            \text{divide by } \tilde \eta_{t + 1} > 0
-            \implies 
-            \tilde \eta_{t + 1} &= \epsilon_{t + 1} + \eta_t + L^{-1}. 
-        \end{align*}
-        The parameter gives relation $\epsilon_{t+1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$. 
-        Hence, it gives us the following system of equality to work with 
-        \begin{align*}
-            \forall t \in \N: 
-            \begin{cases}
-                \tilde \eta_{t + 1} = \epsilon_{t + 1} + \eta_t + L^{-1}, 
-                \\
-                L \eta_t \tilde \eta_{t + 1} = \sigma_t.     
-            \end{cases}
-        \end{align*}
-        With that, we can solve a relation between $\eta_{t + 1}$ in terms of the sequence $\epsilon_t$ and $\eta_t$.
-        Consider the equality 
-        \begin{align*}
-            L \sigma_{t + 1} &= L \tilde \eta_{t + 1} + L \sigma_t
-            \\
-            &=
-            L \tilde \eta_{t + 1}  + L (L \eta_t \tilde \eta_{t + 1})
-            \\
-            &= L \tilde \eta_{t+ 1} + L \eta_t (L \tilde \eta_{t + 1})
-            \\
-            &=  L \tilde \eta_{t+ 1} + L \eta_t (L \epsilon_{t + 1} + L \eta_t + 1)
-            \\
-            &=  L \tilde \eta_{t+ 1} + L \eta_t (L \eta_t + 1) + L^2 \eta_t \epsilon_{t + 1}
-            \\
-            &= L (\epsilon_{t +1} + \eta_t + L^{-1}) + L\eta_t(L \eta_t + 1) + L^2\eta_t \epsilon_{t + 1}
-            \\
-            &= L \epsilon_{t + 1} + (L\eta_t + 1)^2 + L^2\eta_t \epsilon_{t + 1}
-            \\
-            &= 
-            L \epsilon_{t + 1}(1 + L \eta_t) + (1 + L \eta_t)^2. 
-        \end{align*}
-        At the same time we have 
-        \begin{align*}
-            L \sigma_{t + 1} &= L^2 \eta_{t + 1}\tilde \eta_{t + 1} 
-            \\
-            &= L\eta_{t + 1}(1 + L \eta_{t + 1} + \epsilon_{t + 2})
-            \\
-            &= L\eta_{t + 1}(1 + L \eta_{t + 1}) + \epsilon_{t + 2}L\eta_{t + 1}. 
-        \end{align*}
-        Therefore, it generates the following equation: 
-        \begin{align*}
-            L\eta_{t + 1} (1 + L \eta_{t + 1}) 
-            + 
-            \epsilon_{t + 2} L \eta_{t + 1} 
-            &= 
-            L\epsilon_{t + 1}(1 + L \eta_t)  + (1 + L\eta_t)^2
-            \\
-            (L\eta_{t + 1} + L^2\eta_{t + 1}^2)
-            + 
-            \epsilon_{t + 2} L \eta_{t + 1} 
-            + 
-            \frac{1}{4}
-            &= 
-            L\epsilon_{t + 1}(1 + L \eta_t)  + (1 + L\eta_t)^2
-            + 
-            \frac{1}{4}
-            \\
-            (L\eta_{t + 1} + L^2\eta_{t + 1}^2 + 1/4)
-            + 
-            \epsilon_{t + 2} L \eta_{t + 1} 
-            + \epsilon_{t + 2}
-            &= 
-            L\epsilon_{t + 1}(1 + L \eta_t)  + (1 + L\eta_t)^2
-            + \frac{1}{4}
-            + \epsilon_{t + 2}
-            \\
-            (L\eta_{t + 1} + 1/2)^2 + \epsilon_{t + 2}(L \eta_{t + 1} + 1)
-            &= 
-            L \epsilon_{t + 1}(1 + L \eta_t) + (1 + L\eta_t)^2
-            + \frac{1}{4} + \epsilon_{t + 2}
-            \\
-            \text{ with: } & a_t = 1 + L \eta_t = \tilde \eta_{t + 1} - \epsilon_{t + 1}
-            \\
-            (a_{t + 1} - 1/2)^2 + \epsilon_{t + 2}a_{t + 1}
-            &= 
-            L \epsilon_{t + 1}a_t + a_t^2 + 1/4 + \epsilon_{t + 1}
-            \\
-            a_{t + 1}^2 + 1/4 - a_{t + 1} + \epsilon_{t + 2}a_{t + 1}
-            &= 
-            L \epsilon_{t + 1}a_t + a_t^2 + 1/4 + \epsilon_{t + 1}
-            \\
-            a_{t + 1}^2 + a_{t + 1}(\epsilon_{t + 2} - 1)
-            &= 
-            \underbrace{
-                a_t(L \epsilon_{t + 1} + a_t) + \epsilon_{t + 1}
-            }_{c_{t + 1}}. 
-        \end{align*}
-        Solving reveals the relations: 
-        \begin{align*}
-            \begin{cases}
-                a_{t + 1} = (1/2)\left(
-                1 - \epsilon_{t + 2} + \sqrt{(1 - \epsilon_{t + 2}) + 4 c_{t + 1}}
-                \right), 
-                \\
-                c_{t + 1} = a_t (L \epsilon_{t + 1} + a_t) + \epsilon_{t + 1}. 
-            \end{cases}
-        \end{align*}
-        With $\delta_i$ given by
-        \hyperref[thm:generic_ag_convergence]
-        {Theorem \ref*{thm:generic_ag_convergence}}. 
-        Define $\delta_i = \epsilon_{i} \tilde \eta_i$, then 
-        \begin{align*}
-            S_{T} = 
-            \sum_{i = 0}^{T- 1} \delta_i 
-            &= 
-            \sum_{i = 0}^{T - 1} \epsilon_{i + 1}\tilde\eta_{i + 1}\Vert \mathcal G_L(y_i)\Vert^2
-            \\
-            &\le \sum_{i = 0}^{T - 1}\max(\epsilon_{i + 1} \tilde\eta_{i + 1}\Vert \mathcal G_L(y_i)\Vert^2, 0). 
-        \end{align*}
-        Under an ideal case where we wish to attain the best convergence, we want $\lim_{T \rightarrow \infty} S_T < \infty$. 
-        One way to accomplish is choose the error sequence $\epsilon_i, i \in \N$ to be bounded by for all $i \in \N$, $\epsilon_i$ should satisfy: 
-        \begin{align*}
-            \epsilon_{i + 1}\tilde \eta_{i + 1}
-            \Vert \mathcal G_L(y_i)\Vert^2 
-            &\le \delta_{i + 1}
-            \\
-            \iff 
-            \epsilon_{i + 1}
-            &\le 
-            \frac{\delta_{i + 1} }{\tilde\eta_{t + 1}\Vert \mathcal G_L(y_i)\Vert^2}. 
-        \end{align*}
-        for any $\sum_{i = 0}^{T - 1}\delta_{i + 1}$ converges to a limit as $T \rightarrow \infty$.
-
-    \end{proof}
-
-\section{Recovering existing variants of Nesterov accelerated gradient}\label{sec:recovery}
-    In this section, we recovers several variants of the accelerated gradient in the literatures as a special case of 
-    \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}, 
-    we sate the choice of stepsize parameter $\eta_i, \tilde \eta_i$, verify that they satisfies 
-    \hyperref[thm:ag_generic_stepsize_constraints]
-    {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
-    and derive their convergence rate respectively.
-
-    \subsection{Recovering FISTA} 
-        Let $\epsilon_i$ be given by
-        \hyperref[thm:ag_generic_stepsize_constraints]
-        {Theorem \ref*{thm:ag_generic_stepsize_constraints}}, 
-        setting $\epsilon_i = 0$ for all $i$ yields $a_t = 1 + L\eta_t = \tilde \eta_{t + 1}$, for all $t \in \N$ where $a_t$ produces the relations 
-        \begin{align*}
-            a_{t + 1} &= (1/2)\left(
-                1 + \sqrt{1 + 4 c_{t + 1}}
-            \right), 
-            \\
-            c_{t + 1} &= a_t^2. 
-        \end{align*}
-        The recurrenct relations of $a_t$ indicates that it's the famous Nesterov momentum sequence. 
-        In this case, there exists a momentum form of the generic form and it reduces to FISTA from Beck and Toubolle \cite{beck_fast_2009-1}. 
-        The following lemma uses $a_t$ to establish equivalence between the generic form of the algorithm and FISTA, a specific variant of accelerated gradient method. 
-        \begin{lemma}[Similar triangle form]\label{lemma:sim_triangle_form}
-            \quad \\
-            With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$,
-            \hyperref[def:ag_prox_grad_generic]
-            {Definition \ref*{def:ag_prox_grad_generic}}
-            simplifies into 
-            \begin{align*}
-                z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t)
-                \\
-                x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
-                \\
-                y_{t + 1} &= 
-                (1 + L\eta_{t + 1})^{-1}
-                (
-                x_{t + 1} + L\eta_{t + 1}z_{t + 1}
-                ). 
-            \end{align*}
-            It is also equivalent to 
-            \begin{align*}
-                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
-                \\
-                y_{t + 1} &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t). 
-            \end{align*}
-            And this is the FISTA algorithm. 
-        \end{lemma}
-
-        \begin{proof}
-            Firstly, we show that updates sequence $x_{t + 1} = z_{t + 1} + L\eta_t (z_{t + 1} - z_t)$ is equivalent to $x_{t + 1} = x_t + \tilde\eta_{t + 1}\nabla f(y_t)$. 
-            Starting with the former, susbtitute $z_{t + 1} = y_t + L^{-1}\nabla f(y_t)$ as given by 
-            \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}},
-            expanding: 
-            \begin{align*}
-                x_{t + 1} &= 
-                (y_t - L^{-1}\mathcal G_L(y_t)) 
-                + L\eta_t ((y_t - \mathcal G_L(y_t)) - z_t)
-                \\
-                &= y_t - L^{-1}\mathcal G_L(y_t) 
-                + L \eta_t y_t - \eta_t \mathcal G_L(y_t) - L\eta_t z_t
-                \\
-                &= 
-                (1 + L\eta_t)y_t - (\eta_t + L^{-1})\mathcal G_L(y_t) - L\eta_t z_t
-                \\
-                &= \eta_t Lz_t + x_t -(\eta_t + L^{-1}) \mathcal G_L(y_t)  - L\eta_t z_t
-                \\
-                &= x_t - (\eta_t + L^{-1})\mathcal G_L(y_t). 
-            \end{align*}
-            So $x_{t + 1} = x_t + \tilde \eta_{t + 1}\mathcal G_L(y_t)$, by assumption $\tilde \eta_{t + 1} = \eta_t + L^{-1}$. 
-            Next, consider the updates $y_{t + 1}$ as given by 
-            \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}
-            \begin{align*}
-                y_{t + 1} &= (1 + L\eta_{t + 1})^{-1} (x_{t + 1} + L\eta_{t + 1}z_{t + 1})
-                \\
-                &= (1 + L\eta_{t + 1})^{-1} (
-                    z_{t + 1} + L\eta_t (z_{t + 1} - z_t) + L\eta_{t + 1} z_{t + 1}
-                )
-                \\
-                &= 
-                (1 + L\eta_{t + 1})^{-1} (
-                    (1 + L\eta_{t + 1})z_{t + 1} + L\eta_t(z_{t + 1} - z_t)
-                )
-                \\
-                &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t), 
-            \end{align*}
-            it negates the $x_t$ variables, therefore we have 
-            \begin{align*}
-                z_{t + 1} &= y_t - L^{-1} \mathcal G_L (y_t)
-                \\
-                y_{t + 1} &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t).
-            \end{align*}
-            This is FISTA by the relation $a_t = 1 + L\eta_t$ by setting $\epsilon_i = 0$ in
-            \hyperref[thm:ag_generic_stepsize_constraints]
-            {Theorem \ref*{thm:ag_generic_stepsize_constraints}}, 
-            making $a_t$ the Nesterov momentum sequence. 
-            Observe that $(1 + L\eta_{t + 1})^{-1}L\eta_t$ is $(a_t - 1)/a_{t + 1}$.
-            Express using $a_t$, the above algorithm is equivalent to the FISTA algorithm. 
-            \par
-            By 
-            \hyperref[thm:ag_generic_stepsize_constraints]{Theorem \ref*{thm:ag_generic_stepsize_constraints}}
-            and 
-            \hyperref[thm:generic_ag_convergence]{Theorem \ref*{thm:generic_ag_convergence}},
-            a convergence of $\mathcal O(\sigma_T^{-1})$ is possible. 
-            Since $a_t = L\tilde \eta_t$, and the Nesterov sequence exhibits $a_{t} \ge (t + 2)/2$, the convergence becomes $\mathcal O(T^{-2})$. 
-            It is the optimal convergence rate for all convex functions. 
-        \end{proof}
-        \begin{remark}
-            In this remark we clarify the name ``similar triangle" as given in the literatures. 
-            We think it is a fitting name, becaues it has a similar triangle in it. 
-            We list the following observations:
-            \begin{enumerate}
-                \item 
-                The updates for $y_{t}$ from the algorithm has 
-                $$
-                    y_t = (1 + L\eta_t)^{-1} x_t + L\eta_t(1 + L\eta_t)^{-1} z_t, 
-                $$
-                Rearrainging yields: 
-                $$
-                    y_t - x_t = L\eta_t (z_t - y_t). 
-                $$
-                So vector $y_t - x_t$, $z_t - y_t$ colinear and points in the same direction by $L\eta_t > 0$. 
-                \item 
-                The updates for $z_{t + 1}, x_{t + 1}$ are based on $y_t, x_t$ displaced by $L^{-1} \mathcal G_L(y_t), \tilde\eta_{t +1} \mathcal G_L(y_t)$, therefore vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$.
-                \item 
-                The updates for $x_{t + 1}$ has $x_{t + 1} - z_{t + 1} = L\eta_t \left(z_{t + 1} - z_t\right)$, therefore, the three points $z_t, x_{t + 1}, z_{t + 1}$ are collinear. 
-            \end{enumerate}
-            By these three observations, the triangle $z_{t}, z_{t + 1}, y_t$ similar to triangle $z_t, x_{t + 1}, x_t$. 
-            See \hyperref[fig:1a]{Figure \ref*{fig:1a}}
-            for an illustration. 
-            \begin{figure}[h]
-                \centering
-                \subfloat[a][similar triangle]{
-                    \includegraphics*[width=7cm]{assets/drawing_Layer 1.png}
-                    \label{fig:1a}
-                }
-                \subfloat[b][similar triangle with errors]{
-                    \includegraphics*[width=6cm]{assets/drawing_Layer 1 copy.png}
-                    \label{fig:1b}
-                }
-                \caption{Similar triangle illustration}
-            \end{figure}
-            Finally, similar remarks about the similar triangle form can be found in Ahn, Sra's paper \cite{ahn_understanding_2022} as well. 
-            Finally, recall from 
-            \hyperref[thm:ag_generic_stepsize_constraints]
-            {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
-            that $\epsilon_{t + 1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$, setting $\epsilon_{t + 1} =0$ for all $t \in \N \cup \{0\}$. 
-            If we choose to incorperate $\epsilon_{t + 1}$, it yields: 
-            \begin{align*}
-                x_{t + 1} &= z_{t + 1} + L\eta_t(z_{t + 1} - z_t) - \epsilon_{t + 1}\mathcal G_L(y_t) = x_t - (\eta_t + L^{-1} + \epsilon_{t + 1})\mathcal G_L(y_t). 
-            \end{align*}
-            Where $\epsilon_{t + 1}\mathcal G_L(y_t)$ can be viewed as a perturbations from the similar triangle form of the algorithm. 
-            See 
-            \hyperref[fig:1b]{Figure \ref*{fig:1b}}
-            for an illustration for some $\epsilon_{t + 1} > 0$. 
-        \end{remark}
-
-    % \subsection{Recovering the accelerated gradient variant in Ryu's book}
-    %     In this section we should that the following algorithm which appeared in Ryu \cite[chapter 12]{ryu_large-scale_2022}, the next definition present the algorithm in our notations. 
-    %     \begin{definition}\label{def:ryu-ch12}
-    %         Assume that $f$ is a L-Smooth convex function, with initial condition $x_0 = y_0$ an algorithm that generates iterates satisfying: 
-    %         \begin{align*}
-    %             z_{t + 1} &= y_t - L^{-1}\nabla f(y_t) 
-    %             \\
-    %             x_{t + 1} &= x_t - \frac{t + 1}{2L} \nabla f(y_t) 
-    %             \\
-    %             y_{t + 1} &=
-    %             \left(
-    %                 1 - \frac{2}{t + 1}
-    %             \right)z_{t+ 1}
-    %             + 
-    %             \left(
-    %                 \frac{2}{t + 2}
-    %             \right)x_{t + 1}, 
-    %         \end{align*}
-    %         achieves an optimal convergence rate. 
-    %     \end{definition}
-
-    %     \begin{lemma}
-    %         Suppose that the generic form as given by 
-    %         \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}
-    %         admits stepsize $\tilde \eta_t, \eta_t$ as
-    %         \begin{align*}
-    %             \tilde \eta_{t} &= \frac{t}{2L},
-    %             \\
-    %             \eta_t &= (t - 1)/(2L). 
-    %         \end{align*}
-    %         Then it's algebraically equivalent to 
-    %         \hyperref[def:ryu-ch12]{Definition \ref*{def:ryu-ch12}}. 
-    %     \end{lemma}
-    %     \begin{proof}
-    %         Observe $\tilde \eta_t = t/(2L)$ admits a linear growth rate. 
-    %         If $\tilde \eta_i, \eta_i$ is a sequence that satisfies
-    %         \hyperref[thm:ag_generic_stepsize_constraints]
-    %         {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
-    %         then 
-    %         \hyperref[thm:generic_ag_convergence]
-    %         {Theorem \ref*{thm:generic_ag_convergence}}
-    %         asserts a convergence rate of $\mathcal O(1/T^2)$ for $h(z_T) - h(x_*)$, where $x_*$ is a minimizer assumed to exist. 
-    %         To show that the sequence satisfies 
-    %         \hyperref[thm:ag_generic_stepsize_constraints]
-    %         {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
-    %         first observe that $\epsilon_t = 0$ because 
-    %         \begin{align*}
-    %             L^{-1} + \eta_t 
-    %             &= 
-    %             L^{-1} + \frac{t - 1}{2L}
-    %             \\
-    %             &= \frac{t + 1}{2L}
-    %             \\
-    %             &= \tilde \eta_{t + 1}. 
-    %         \end{align*}
-    %         Therefore this is a similar triangle method. 
-    %         Next observe that conditions showed in 
-    %         \hyperref[thm:ag_generic_stepsize_constraints]
-    %         {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
-    %         can be simplified in this context because the two equalities reduces to just one when $\epsilon_t =0$ for all $t \in \N$ by 
-    %         \begin{align*}
-    %             \tilde \eta_{t + 1}(\tilde \eta_{t + 1} - L^{-1}) 
-    %             - L^{-1}\sigma_t &= 0
-    %             \\
-    %             \iff 
-    %             \tilde \eta_{t + 1}\eta_t &= L^{-1}\sigma_t. 
-    %         \end{align*}
-    %         Hence it only requires to verify the equality $\tilde \eta_{t + 1}\eta_t = L^{-1} \sigma_t$. 
-    %         With that we have 
-    %         \begin{align*}
-    %             \sigma_t &= \sum_{i = 1}^{t} \frac{i}{2L}
-    %             \\
-    %             &= \frac{1}{2L}\left(
-    %                 \frac{t(t + 1)}{2}
-    %             \right)
-    %             \\
-    %             &= \frac{t(1 + t)}{4L}
-    %             \\
-    %             \iff 
-    %             L^{-1}\sigma_t &= 
-    %             \frac{t(1 + t)}{4L^2}
-    %         \end{align*}
-    %         By definition of the stepsizes the LHS of the equality evaluates to
-    %         \begin{align*}
-    %             \tilde \eta_{t + 1} \eta_{t + 1}
-    %             &= \frac{t + 1}{2L} \frac{t}{2L} 
-    %             \\
-    %             &= L^{-1}\sigma_t. 
-    %         \end{align*}
-    %     \end{proof}
-
-    % \subsection{Recovering Chambolle, Dossal 2015}
-    %     In this section we show that the algorithm presented in the literature by Chambolle Dossal \cite{chambolle_convergence_2015} is an example of 
-    %     Definition \ref*{def:ag_prox_grad_generic}. 
-    %     The next definiton present the algorithm in our notations
-    %     \begin{definition}\label{def:chamb_dossal}
-    %         Assume that $h = f + g$ where $f$ is $L$-smooth, $f,g$ are convex. 
-    %         Let $t_n = (n + a - 1)/a$ for all $t \in \N$, $a > 2$. 
-    %         The algorithm by Chambolle Dossal has iterates $(x_n, y_n, z_n)$ satisfying for all $n \in \N$: 
-    %         \begin{align*}
-    %             z_{n + 1} &= y_n - L^{-1} \mathcal G_L(y_n), 
-    %             \\
-    %             x_{n + 1} &= z_n + t_{n +1} (z_{n + 1} - z_n), 
-    %             \\
-    %             y_{n + 1} &= \left(
-    %                 1 - \frac{1}{t_{n + 1}}
-    %             \right)z_{n + 1} + \left(
-    %                 \frac{1}{t_{n + 1}}
-    %             \right)x_{n + 1}. 
-    %         \end{align*}
-    %     \end{definition}
-    %     \begin{lemma}
-    %         Suppose that the generic form as given by 
-    %         \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}
-    %         admits stepsize $\tilde \eta_t, \eta_t$ as
-    %         \begin{align*}
-    %             L\eta_n = t_n - 1,
-    %             \\
-    %             \tilde \eta_{n + 1} = L^{-1} + \eta_n. 
-    %         \end{align*}
-    %         Then it's algebraically equivalent to 
-    %         \hyperref[def:chamb_dossal]{Definition \ref*{def:chamb_dossal}}. 
-    %     \end{lemma}
-    %     \begin{proof}
-    %         By second equality: $\tilde \eta_{n + 1} = \eta_n + L^{-1}$, we can use 
-    %         \hyperref[lemma:sim_triangle_form]{Lemma \ref*{lemma:sim_triangle_form}}. 
-    %         Therefore, substituting $L\eta_n = t_n - 1$, $x_{n + 1}, y_{n + 1}$ in the generic form has 
-    %         \begin{align*}
-    %             x_{n + 1} &= 
-    %             (1 + L\eta_n) z_{n + 1} - L\eta_n z_n
-    %             \\
-    %             & = 
-    %             t_n z_{n + 1} + (1 - t_n) z_n 
-    %             \\
-    %             &= z_n + t_n(z_{n +1} - z_n)
-    %             \\
-    %             y_{n + 1} &= (1 + L\eta_{n + 1})^{-1} (L\eta_{n + 1} z_{n + 1} + x_{n + 1})
-    %             \\
-    %             &= t^{-1}_{n + 1} ((t_{n + 1} - 1)z_n + x_{n + 1})
-    %             \\
-    %             &= (1 - t_{n + 1}^{-1})z_{n + 1} + t^{-1}x_{n + 1}. 
-    %         \end{align*}
-    %         This is the same as
-    %         \hyperref[def:chamb_dossal]{Definition \ref*{def:chamb_dossal}}. 
-    %     \end{proof}
-    %     \begin{remark}
-
-    %     \end{remark}
-
-\section{Algorithm implementations using line search}\label{sec:algorithm_improved}
-    In this section, we state a new variant of the accelerated gradient algorithm using the PPM interpretation to algorithmically conduct a line search routine for $L, \mu \ge 0$ the Lipschitz constant and strong convexity index of the smooth part of the objective function.
-    This variant will be parameter free while still retaining the optimal convergence rate for all convex functions.
-
-\section{Numerical experiments}\label{sec:numerical_experiments}
-
-\appendix
-\section{Scratch paper stuff}
-    Throughout this subsection, we make the following list of assumptions: 
-    \begin{enumerate}
-        \item $h = f + g$, 
-        \item $f, g$ are convex functions, 
-        \item $f$ is differentiable with $L$-Lipschitz smooth gradient and it's $\mu \ge 0$ strongly convex,
-        \item Let $\mathcal T_L, \mathcal G_L$ be the proximal gradient and gradient mapping operator be given by \\
-        \hyperref[def:gradient_mapping]{Definition \ref*{def:gradient_mapping}}. 
-    \end{enumerate}
-
-    \subsection{Nesterov momentum with strong convexity}
-        \begin{definition}[generic S-CVX PPM form]\label{def:generic_s-cvx_form}
-            Define the lower bouding function at $x$: 
-            \begin{align*}
-                l_h(z; x) = h(\mathcal T_L x) + \langle \mathcal G_L (x), z - x\rangle
-                + 
-                \frac{L}{2}\Vert x - \mathcal T_L (x)\Vert^2 + \frac{\mu}{2}\Vert z - x\Vert^2
-            \end{align*}
-            We define the following algorithm. 
-            \begin{align*}
-                x_{t + 1} &= \argmin_{x} \left\lbrace
-                    l_h(x; y_t) + \frac{1}{2\tilde \eta_{t + 1}} 
-                    \Vert x - x_t\Vert^2 
-                \right\rbrace
-                \\
-                &= (\mu\tilde \eta_{t + 1} + 1)^{-1} 
-                (\mu\tilde \eta_{t + 1}y_t + x_t - \tilde \eta_{t + 1}\mathcal G_L(y_t))
-                \\
-                y_{t + 1}&= 
-                \argmin_{x}
-                \left\lbrace
-                    h(\mathcal T_L y_t) + \langle \mathcal G_L(y_t), x - y_t\rangle + \frac{L}{2}\Vert x -y_t\Vert^2
-                    + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
-                \right\rbrace
-                \\
-                &= (1 + L \eta_{t +1})^{-1}(L\eta_{t + 1}(y_t - L^{-1}\mathcal G_L(y_t)) + x_{t + 1})
-            \end{align*}
-        \end{definition}
-        \begin{proof}
-            The functions inside of ``argmin" is easy to solve because they are just quadratic functions. 
-            We write it here for future verifications and a peace of the mind. 
-            \begin{align*}
-                x_{t + 1} &= \argmin_{x}\left\lbrace
-                    \langle \mathcal G_L(y_t), x - y_t\rangle 
-                    + 
-                    \frac{\mu}{2}\Vert x - y_t\Vert^2 +  
-                    \frac{1}{2\tilde \eta_{t + 1}}\Vert x - x_t\Vert^2
-                \right\rbrace
-                \\
-                \iff 
-                \mathbf 0 & = 
-                \mathcal G_L(y_t) + \mu(x - y_t) + \tilde \eta_{t + 1}^{-1}(x - x_t)
-                \\
-                &= 
-                \mathcal G_L(y_t) + (\mu + \tilde \eta_{t + 1}^{-1}) x - \mu y_t - \tilde \eta_{t + 1}^{-1} x_t
-                \\
-                \iff 
-                (\mu + \tilde \eta_{t + 1}^{-1})x 
-                &= 
-                \mu y_t + \tilde \eta_{t + 1}^{-1} x_t - \mathcal G_L(y_t)
-                \\
-                \implies 
-                x &= (\mu + \tilde \eta_{t + 1}^{-1})^{-1 }
-                (\mu y_t + \tilde \eta_{t + 1}^{-1} x_t - \mathcal G_L(y_t)). 
-            \end{align*}
-            We can make the assumption that $\mu + \eta_{t + 1}^{-1} \neq 0$ because $\tilde\eta_t > 0$. 
-            Similarly for $y_{t + 1}$, it's solving a simple quadratic minimization problem, yielding: 
-            \begin{align*}
-                \mathbf 0 &= \mathcal G_L(y_t) + L(x - y_t) + \eta_{t + 1}^{-1}(x - x_{t + 1})
-                \\
-                &= (L + \eta_{t + 1}^{-1})x - L y_t - \eta_{t + 1}^{-1}x_{t + 1} + \mathcal G_L(y_t) 
-                \\
-                (L + \eta_{t + 1}^{-1})x &= 
-                Ly_t + \eta_{t + 1}^{-1} x_{t + 1} - \mathcal G_L(y_t)
-                \\
-                \implies 
-                x &= 
-                (L\eta_{t + 1} + 1)^{-1}(L\eta_{t + 1}(y_t - L^{-1}\mathcal G_L(y_t)) + x_{t + 1}). 
-            \end{align*}
-            And hence the results are verified for the peace of the mind. 
-        \end{proof}
-        \begin{remark}\label{remark:generic_s-cvx_ppm_alternative_representation}
-            In the literatures, people accenturate the term $z_{t + 1} = y_t - L^{-1} \mathcal G_L(y_t)$, as a step of gradient descent, and the term $w_t = (\mu\tilde \eta_{t + 1} + 1)^{-1}(\mu\tilde \eta_{t + 1}y_t + x_t)$ so the algorithm can be alternatively presented by the relation
-            \begin{align*}
-                w_{t} &= (\mu\tilde \eta_{t + 1} + 1)^{-1}(\mu \tilde \eta_{t + 1} y_t + x_t) 
-                \\
-                x_{t + 1}&= w_t - \tilde \eta_{t + 1}(\mu\tilde \eta_{t + 1} + 1)^{-1} \mathcal G_L(y_t)
-                \\
-                z_{t + 1}&= y_t - L^{-1}\mathcal G_L(y_t)
-                \\
-                y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}(L\eta_{t + 1}z_{t + 1} + x_{t + 1}). 
-            \end{align*}
-            When $\mu = 0$, it has $w_t = x_t$, producing a simpler relations 
-            \begin{align*}
-                x_{t + 1} &= 
-                x_t - \tilde \eta_{t + 1} \mathcal G_L(y_t)
-                \\
-                z_{t + 1}&= y_t - L^{-1}\mathcal G_L(y_t)
-                \\
-                y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}
-                (L\eta_{t + 1} z_{t + 1} + x_{t + 1}). 
-            \end{align*}
-            The above representation is the same as 
-            \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}.
-
-        \end{remark}
-
-        \begin{definition}[Similar triangle form]\label{def:s-cvx_similar_triangle_form}
-            Let $\mathcal G_L, \mathcal T_L$ be the gradient mapping and proixmal gradient operator of $h = f + g$. 
-            An algorithm is referred to as similar triangle form if its iterates $(x_t, y_t, z_t)$ satisfies the conditions: 
-            \begin{align*}
-                z_{t + 1} &= 
-                y_t - L^{-1}\mathcal G_L(y_t)
-                \\
-                x_{t + 1}&= 
-                z_{t + 1} + \frac{L\eta_t}{1 + \mu\tilde \eta_{t + 1}}(z_{t + 1} - z_t)
-                \\
-                y_{t + 1}&= 
-                (1 + L\eta_{t + 1})^{-1} (L\eta_{t + 1}z_{t + 1} + x_{t + 1}). 
-            \end{align*}
-        \end{definition}
-
-        \begin{definition}[Generic momentum form]\label{def:generic_momentum}
-            Let $\mathcal G_L, \mathcal T_L$ be the gradient mapping and the proximal gradient operator for $h$. 
-            Then the generic momentum form is an algorithm with iterates $(z_t, y_t)$ satisfying the relations 
-            \begin{align*}
-                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
-                \\
-                y_{t + 1 } &= z_{t + 1} + \theta_{t + 1}(z_{t + 1} - z_t)
-            \end{align*}
-            For some $\theta_t \ge 0$. 
-        \end{definition}
-        \begin{remark}
-            Sometimes in the literates the update is expressed differently and it's 
-            \begin{align*}
-                y_{t + 1} &= z_t + (1 + \theta_{t + 1})(z_{t + 1} - z_t). 
-            \end{align*}
-        \end{remark}
-
-        \begin{theorem}[Momentum is algebraically equivalent to similar triangle]
-        \label{thm:momentum_is_similar_triangle}
-            \;\\
-            Let $\tilde \eta_t, \eta_t$
-            satisfies 
-            \begin{align*}
-                \tilde\eta_{t + 1} &= \eta_t + L^{-1} + L^{-1} \mu \tilde\eta_{t + 1},
-            \end{align*}
-            then it reduces 
-            \hyperref[def:generic_s-cvx_form]{Definition \ref*{def:generic_s-cvx_form}}
-            into similar triangle form which is given by 
-            \hyperref[def:s-cvx_similar_triangle_form]
-            {Definition \ref*{def:s-cvx_similar_triangle_form}}, 
-            which is also algebraically equivalent 
-            \hyperref[def:generic_momentum]{Definition \ref*{def:generic_momentum}}
-            and it simplifies to
-            \begin{align*}
-                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t), 
-                \\
-                y_{t + 1} &= z_{t + 1} + 
-                \frac{L\eta_t}{(1 + \mu \tilde\eta_{t + 1})(1 + L\eta_{t + 1})}(z_{t + 1} - z_t)
-            \end{align*}
-        \end{theorem}
-        \begin{proof}
-            We work with the alternative representation listed in 
-            \hyperref[remark:generic_s-cvx_ppm_alternative_representation]
-            {Remark \ref*{remark:generic_s-cvx_ppm_alternative_representation}} which has iterates $(w_t, x_{t + 1}, z_{t + 1}, y_{t + 1})$. 
-            We start by showing that there exists a constant $\alpha \in \RR$ such that $z_{t + 1} - z_t = \alpha (x_{t + 1} - z_{t + 1})$ by $\tilde \eta_{t + 1} = \eta_t + L^{-1} + L^{-1} \mu \tilde \eta_{t + 1}$.
-            Firstly, we have the equality. 
-            \begin{align*}
-                z_{t + 1} - z_t
-                &= 
-                - (L\eta_t)^{-1} y_t 
-                - L^{-1}\mathcal G_L(y_t) + (L \eta_t)^{-1} x_t. 
-            \end{align*}
-            Because 
-            \begin{align*}
-                y_{t} &= (1 + L\eta_{t})^{-1}(L\eta_{t}z_{t} + x_{t})
-                \\
-                (1 + L\eta_t)y_t - x_t &= L\eta_t z_t
-                \\
-                z_t & = (L\eta_t)^{-1}((1 + L\eta_t)y_t - x_t), 
-                \\[1em]
-                z_{t + 1} - z_t 
-                &= \underbrace{ y_t - L^{-1}\mathcal G_L(y_t)}_{=z_{t + 1}}
-                - \underbrace{(L\eta_t)^{-1}((1 + L\eta_t)y_t - x_t)}_{=z_t}
-                \\
-                &= 
-                y_t - L^{-1} \mathcal G_L(y_t) - (L\eta_t)^{-1}y_t - y_t + (L\eta_t)^{-1} x_t
-                \\
-                &= 
-                -L^{-1}\mathcal G_L(y_t) + (L\eta_t)^{-1}(x_t - y_t)
-                \\
-                &= 
-                L^{-1}(\eta_t^{-1}(x_t - y_t) -\mathcal G_L(y_t)). 
-            \end{align*}
-            Next, we have 
-            \begin{align*}
-                x_{t + 1} - z_{t + 1}&= 
-                \left(
-                    (1 + \mu \tilde \eta_{t+ 1})^{-1} (\mu \tilde \eta_{t + 1}y_t + x_t)
-                    - \frac{\tilde \eta_{t + 1}}{1 + \mu\tilde \eta_{t + 1}}
-                    \mathcal G_L(y_t)
-                \right) - \left(
-                    y_t - L^{-1}\mathcal G_L(y_t)
-                \right)
-                \\
-                &= 
-                (1 + \mu \tilde \eta_{t + 1})^{-1}
-                \left(
-                    x_t + \mu \tilde \eta_{t + 1} y_t
-                    - \tilde \eta_{t + 1} \mathcal G_L(y_t)
-                    - (1 + \mu \tilde \eta_{t + 1})
-                    (y_t - L^{-1}\mathcal G_L(y_t))
-                \right)
-                \\
-                &= 
-                (1 + \mu\tilde \eta_{t + 1})^{-1}
-                \left(
-                    x_t - y_t + 
-                    (
-                        -\tilde \eta_{t + 1} + 
-                        (
-                            1 + \mu\tilde \eta_{t + 1})L^{-1}
-                        )
-                        \mathcal G_L(y_t)
-                    )
-                \right)
-                \\
-                &= 
-                (1 + \mu\tilde \eta_{t + 1})^{-1}
-                \left(
-                    x_t - y_t +     
-                    (
-                        - \tilde \eta_{t + 1} + L^{-1}
-                        + \mu \tilde \eta_{t + 1}L^{-1}
-                    )
-                    \mathcal G_L(y_t)
-                \right). 
-            \end{align*}
-            Since 
-            \begin{align*}
-                (1 - L^{-1}\mu)\tilde \eta_{t +1}
-                &= L^{-1} + \eta_t 
-                \\
-                - \tilde \eta_{t + 1} + L^{-1}\mu \tilde \eta_{t + 1}
-                + L^{-1}
-                &= - \eta_t, 
-            \end{align*}
-            so substituting 
-            \begin{align*}
-                x_{t + 1} - z_{t + 1}
-                &= 
-                (1 + \mu \tilde \eta_{t + 1})^{-1}
-                (x_t - y_t - \eta_t \mathcal G_L(y_t))
-                \\
-                &= (1 + \mu \tilde \eta_{t + 1})^{-1}
-                \eta_t(\eta_{t}^{-1}(x_t - y_t) - \mathcal G_L(y_t))
-                \\
-                &= (1 + \mu \tilde \eta_{t + 1})^{-1}
-                \eta_t L(z_{t + 1} - z_t), 
-            \end{align*}
-            therefore 
-            \begin{align*}
-                z_{t + 1} - z_t 
-                &= 
-                \eta^{-1}_tL^{-1}(1 + \mu \tilde \eta_{t + 1})(x_{t + 1} - z_{t + 1})
-                \\
-                \iff 
-                x_{t + 1} - z_{t + 1} &= 
-                \frac{L\eta_t}{1 + \mu \tilde \eta_{t + 1}} 
-                (z_{t + 1} - z_t). 
-            \end{align*}
-            This produces the new updates for $x_{t +1}$, making it the same as the stated similar triangle form as in 
-            \hyperref[def:s-cvx_similar_triangle_form]
-                {Definition \ref*{def:s-cvx_similar_triangle_form}}. 
-            To attain momentum form, we consider the equation for $y_{t + 1}$, and susbtitute $x_{t + 1}$ producing 
-            \begin{align*}
-                y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}
-                (
-                    L\eta_{t + 1} z_{t + 1} + x_{t + 1}
-                )
-                \\
-                &= 
-                (1 + L\eta_{t + 1})^{-1}
-                \left(
-                    L\eta_{t + 1} z_{t + 1} + z_{t + 1}
-                    + 
-                    \frac{L\eta_t}{1 + \mu \tilde \eta_{t + 1}}
-                    (z_{t + 1} - z_t)
-                \right)
-                \\
-                &= z_{t + 1} 
-                + 
-                \frac{L\eta_t}{(1 + L\eta_{t + 1})(1 + \mu \tilde \eta_{t + 1})}
-                (z_{t + 1} - z_t). 
-            \end{align*}
-            The above exposes the 
-            $\theta_{t + 1} = L\eta_t(1 + L\eta_{t + 1})^{-1}(1 + \mu\tilde \eta_{t + 1})^{-1}$. 
-            Alternatively we also have: 
-            \begin{align*}
-                x_{t + 1} &= z_{t + 1} + (1 + \mu\tilde \eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t)
-                \\
-                &=  (1 + L\eta_t(1 + \mu \tilde \eta_{t + 1})^{-1})z_{t + 1}
-                - L\eta_t(1 + \mu\tilde \eta_{t + 1})z_t
-                \\
-                &= 
-                \left(
-                    \frac{1 + \mu\tilde \eta_{t + 1} + L \eta_t}{1 + \mu \tilde \eta_{t + 1}}
-                \right)z_{t + 1}
-                + 
-                z_t - 
-                \left(
-                    1 + \frac{ L\eta_t}{1 + \mu \tilde \eta_t + 1}
-                \right)z_t 
-                \\
-                &= 
-                \left(
-                    \frac{L\tilde \eta_{t+ 1}}{1 + \mu\tilde \eta_{t + 1}}
-                \right)z_{t + 1}
-                + 
-                z_t 
-                - 
-                \left(
-                    \frac{L\tilde \eta_{t + 1}}{1 + \mu \tilde \eta_{t + 1}}
-                \right)z_t 
-                \\
-                &= z_t + 
-                \left(
-                    \frac{L\tilde \eta_{t + 1}}{1 + \mu \tilde \eta_{t + 1}}
-                \right)
-                (z_{t + 1} - z_t). 
-            \end{align*}
-        \end{proof}
-
-    \subsection{The line search algorithm idea}
-        \par
-        The Nesterov acceleration algorithm can not achieve linear convergence rate for function that has a strongly convexity constant $\mu > 0$. 
-        This claim is showed in Aujol et.al \cite{aujol_optimal_2019}. 
-        Variants of the Nesterov accelerated gradient method that can achieve linear rate of convergence exists but it requires knowledge of $\mu, L$ a priori. 
-        \par
-        Literatures attempts at improving the convergence of FISTA under strong convexity, and other characterizations are vast. 
-        But it can be approximately categorized as two types: 
-        \begin{enumerate}
-            \item Heuristic and adaptive restart. 
-            \item Linear search and estaimating the parameters. 
-        \end{enumerate}
-        \par
-        Let $h = f + g$ where $f, g$ are convex and $f$ is $L$-Lipschitz and $\mu\ge 0$ strongly convex. 
-        List in Beck \cite[(10.7.7)]{beck_first-order_nodate}, the V-FISTA algorithm is: 
-        \begin{align*}
-            z_{n + 1} &= \mathcal T_L(y_n)
-            \\
-            y_{n + 1} &= z_{n + 1} + \frac{\sqrt{\kappa} - 1}{\sqrt{\kappa} + 1}(z_{n + 1} - z_n). 
-        \end{align*}
-        $\kappa = L/\mu$ is the condition number. 
-        The parameters $L, \mu$ can be estimated during the run time of the algorithm. 
-        To establish the estimation we first match the parameters $\tilde \eta_i, \eta_i$ to the momentum parameter presented in V-FISTA. 
-        Then we perform the estimation of $\tilde \eta_i, \eta_i$ using the PPM interpretation for the parameter $L, \mu$. 
-        The following theorem will reduce the generic S-CVX form of the PPM interpretations into the V-FISTA algorithm. 
-        \begin{theorem}[V-FISTA algorithm as similar triangle]
-            \;\\
-            If
-            \begin{align*}
-                \tilde \eta_t 
-                &= \frac{1}{\mu(\sqrt{\kappa} - 1)}
-                \quad \forall t \in \N, 
-                \\
-                \eta_t
-                &= 
-                \frac{1}{\mu\sqrt{\kappa}}
-                \quad \forall t \in \N. 
-            \end{align*}
-            Then the AG generic form simplifies to 
-            \begin{align*}
-                y_{t + 1} &= z_{t + 1} + 
-                \frac{\sqrt{\kappa} - 1}{\sqrt{\kappa} + 1}
-                (z_{t +1} - z_t)
-                \\
-                z_{t + 1} 
-                &= y_t - L^{-1}\mathcal G_L(y_t). 
-            \end{align*}
-            And it is a valid sequence that meaning that it satisfies 
-            \begin{align*}
-            \tilde \eta_{t + 1} = \eta_t + L^{-1} + L^{-1} \mu \tilde \eta_{t + 1}. 
-            \end{align*}
-        \end{theorem}
-        \begin{proof}
-            Observe that we have 
-            \begin{align*}
-                L\eta &= \frac{L}{\mu \sqrt{\kappa}} = \frac{\kappa}{\sqrt{\kappa}} = \sqrt{\kappa}, 
-                \\
-                \mu \tilde \eta &= 
-                \frac{1}{\sqrt{\kappa} - 1}, 
-                \\
-                L\tilde \eta_t &= 
-                \frac{\kappa}{\sqrt{\kappa} - 1}. 
-            \end{align*}
-            since it's a constant wrt to $t$, we use $\eta, \tilde \eta$ to ease the notations. 
-            With that it establishes relations
-            \begin{align*}
-                \frac{L\eta }{(1 + \mu \tilde \eta)(1 + L\eta)}
-                &= 
-                \frac{\sqrt{\kappa}}{
-                    \left(
-                        1 + \frac{1}{\sqrt{\kappa} - 1}
-                    \right)
-                    \left(
-                        1 + \sqrt{\kappa}
-                    \right)
-                }
-                \\
-                &= \frac{\sqrt{\kappa}}{
-                    \left(
-                        \frac{\sqrt{\kappa}}{\sqrt{\kappa} - 1}
-                    \right)(1 + \sqrt{\kappa})
-                }
-                \\
-                &=
-                \frac{\sqrt{\kappa}}{1 + \sqrt{\kappa}}\left(
-                    \frac{\sqrt{\kappa} - 1}{\sqrt{\kappa}}
-                \right)
-                \\
-                &= 
-                \frac{\sqrt{\kappa} - 1}{\sqrt{\kappa} + 1}. 
-            \end{align*}
-            The sequence is valid because 
-            \begin{align*}
-                \tilde \eta_{t + 1} 
-                &= \eta_t + L^{-1} + L^{-1} \mu \tilde \eta_{t + 1}
-                \\
-                (L - \mu)\tilde \eta_{t + 1}
-                &= 
-                1 + L \eta_t 
-                \\
-                L \tilde \eta_{t + 1} - 
-                \mu \tilde \eta_{t + 1}
-                &= 1 + L \eta_t. 
-            \end{align*}
-            Starting from the LHS it yields: 
-            \begin{align*}
-                L\tilde \eta - \mu \tilde \eta 
-                &= \frac{\kappa}{\sqrt{\kappa} - 1} - 
-                \frac{1}{\sqrt{\kappa} - 1}
-                \\
-                &= 
-                \frac{\kappa - 1}{\sqrt{\kappa} - 1}
-                \\
-                &= 
-                \frac{(\sqrt{\kappa} + 1)(\sqrt{\kappa} - 1)}{\sqrt{\kappa} - 1}
-                \\
-                &= 1 + \sqrt{\kappa} = 1 + L \eta. 
-            \end{align*}
-        \end{proof}
-        \par
-        Therefore, when we have strong convexity constant $\mu > 0$ and Lipschitz parameters $L$, we have a fixed stepsizes $\tilde \eta, \eta$ for the generic form of the algorithm. 
-        When strong convexity doesn't exist locally during the computations of the algorithm, we have to resolve it back to the case when $\mu = 0$. 
-        To do that we have to match the parameters $\tilde \eta_i, \eta_i$ to the Nesterov's momentum used in FISTA. 
-        Proposed by Chambolle, Dossal \cite{chambolle_convergence_2015}, we have the following representation of the Nesterov accelerated gradient: 
-        \begin{definition}[FISTA]\label{def:fista}
-            The FISTA algorithm has iterates such that they satisfy the following conditions recursively: 
-            \begin{align*}
-                z_{n + 1} &= y_n - L^{-1}\mathcal G_L(y_n)
-                \\
-                x_{n + 1} &= z_n + t_{n +1} (z_{n + 1} - z_n), 
-                \\
-                y_{n + 1} &= \left(
-                    1 - \frac{1}{t_{n + 1}}
-                \right)z_{n + 1} + \left(
-                    \frac{1}{t_{n + 1}}
-                \right)x_{n + 1}
-            \end{align*}
-            where $(t_n)_{n\in \N}$ satisfies: $t_{n + 1}^2 - t_n^2 \le t_n$. 
-        \end{definition}
-        \begin{observation}
-            Observe the fact that the updates of the iterates resemble the similar triangle form in
-            \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}
-        \end{observation}
-        \begin{theorem}[FISTA as a special case of similar triangle form]
-        \label{thm:fista_spacial_case_of_similar_triangle}
-            \;\\
-            if the stepsize $L\eta_n = t_n - 1$, and $\tilde \eta_{n + 1} = L^{-1} + \eta_n$, then
-            \hyperref[def:fista]{Definition \ref*{def:fista}}
-            is an example of 
-            \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}, 
-        \end{theorem}
-        \begin{proof}
-
-        \end{proof}
-
-\section{Postoned proof}
-    \begin{fact}[Equivalent characterization of strong convexity]
-    \label{appendix:fact:equiv_char_s-cvx}
-        $f$ is $\beta$-strongly convex if and only if
-        $$
-            (\forall y\in X)(\forall x^* \in \partial f(x))
-            \quad f(y) \ge f(x) + \langle x^*, y - x\rangle +
-            \frac{\beta}{2}\Vert y - x\Vert^2
-            .
-        $$
-    \end{fact}
-
-    \begin{theorem}[Quadratic growth]\label{appendix:thm:q_growth}
-        If $f$ is $\beta$-strongly convex, let $x^*$ be a minimizer of $f$ then 
-        \begin{align*}
-            (\forall y \in X) \quad 
-            f(y) &\ge 
-            f(x) + \frac{\beta}{2}\Vert y - x\Vert^2. 
-        \end{align*}
-    \end{theorem}
-    \begin{proof}
-        Fact \ref*{appendix:fact:equiv_char_s-cvx} 
-        implies a quadratic growth condition. 
-        By convexity $x^*$ is a minimizer of $f$ if and only if $x^*= \mathbf 0 \in \partial f(x^*)$, therefore it sets the inner product on the RHS to zero which yields the quadratic growth condition.
-    \end{proof}
-
-    \begin{theorem}[strongly convex PPM descent lemma]
-    \label{appendix:proof_ppm_descent_lemma}
-        Let $f: \RR^n \mapsto \overline \RR^n$ $\beta$ be strongly convex with $\beta \ge 0$, fix any $x \in \RR^n$, define $p = \hprox_f(x)$.
-        For all $y \in \RR$ it verifies
-        $$
-            \left(f(p) + \frac{1}{2}\Vert x - p\Vert^2\right)
-            - 
-            \left(
-                f(y) + \frac{1}{2}\Vert x - y\Vert^2 
-            \right)
-            \le 
-            - \frac{(1 + \beta)}{2}\Vert y - p\Vert^2. 
-        $$
-        Recall: $\hprox_f(x) = \argmin_{u}\left\lbrace f(u) + \frac{1}{2}\Vert u - x\Vert^2 \right\rbrace$. 
-    \end{theorem}
-    \begin{proof}
-        With $x$ being fixed,
-        consider the function
-        $$
-            y\mapsto h(y)=f(y)+\frac{\|y-x\|^2}{2}=f(y)+\frac{\|y\|^2}{2}-\scal{y}{x}+\frac{\|x\|^2}{2}.
-        $$
-        Because $f$ is $\beta$-strongly convex, the function
-        $y\mapsto f(y) + \frac{1}{2}\Vert y\Vert^2$ is $(\beta + 1)$-strongly convex.
-        Then $h$ is $(\beta + 1)$-strongly convex.
-        Since $(\forall y)\; h(y) \ge h(p)$, because $p = \hprox_f(x)$ 
-        \hyperref[appendix:thm:q_growth]{Theorem \ref*{appendix:thm:q_growth}}
-        (quadratic growth)
-        yields
-        \begin{align*}
-            h(y) &\ge
-            h(p) + \frac{\beta + 1}{2}\Vert y - p\Vert^2.
-        \end{align*}
-        That is,
-        \begin{align*}
-            f(y) + \frac{1}{2}\Vert y - x\Vert^2
-            \ge
-            f(p) + \frac{1}{2} \Vert p - x\Vert^2
-            + \frac{\beta + 1}{2}\Vert y - p\Vert^2.
-        \end{align*}
-        Rearraging yield the desired results. 
-    \end{proof}
-
-% \printbibliography
 
@@
 
+\appendix
+\section{Postoned proofs}
+
 \end{document}

### 2024-11-07 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
         \fontfamily{ptm}\selectfont 
-        A Title Here: A Sub Title Here
+        Catalyst Meta Acceleration Framework: The Gist of its Theories
     }
@@
     The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{alto@mail.ubc.ca}.}~ and~Xianfu Wang
-    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
-    The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{shawn.wang@ubc.ca}.}
+    % \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
+    % The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{shawn.wang@ubc.ca}.}
 }
@@
     \noindent
-    Abstract example citation \cite{bezanson_julia_2017}.
+    Nesterov's accelerated gradient first appeared back in the 1983 has sparked numerous theoretical and pratical advancedments in Mathematics programming literatures. 
+    The idea behind Nesterov's acceleration is universal in the convex case and it has concrete extension in the non-convex case. 
+    In this paper we survey specifically the Catalyst Acceleration that incorperated ideas from the Accelerated Proximal Point Method proposed by Guller back in 1993. 
+    We will review Nesterov's classical analysis of accelerated gradient in the convex case. 
+    We summarize key aspect of the theoretical innovations involved to achieve the design of the algorithm in convex, and non-convex case. 
+    \cite{bezanson_julia_2017}.
 
@@
 \section{Introduction}
-
+    \subsection{Literature reviews}    
     \subsection{Contributions}
@@
 \section{Preliminaries}\label{sec:preliminaries}
+    \subsection{Method of Nesterov's Estimating Sequence}
+
+\section{Nesterov's Accelerated Proximal Gradient}
+\section{Guller 1993}
+\section{H.Lin 2015}
+
+\section{Nonconvex Extension of Catalyst Acceleration}
 

### 2024-11-07 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

--- 2024-11-05 Notebook LaTEX/Catalyst Accelerations/main.tex
@@
     \noindent
-    Abstract example citation \cite{bezanson_julia_2017}.
+    Nesterov's accelerated gradient first appeared back in the 1983 has sparked numerous theoretical and practical advancements in Mathematics programming literatures. 
+    The idea behind Nesterov's acceleration is universal in the convex case it has concrete extension in the non-convex case. 
+    In this paper we survey specifically the Catalyst Acceleration that incorperated ideas from the Accelerated Proximal Point Method proposed by Guler back in 1993. 
+    The paper reviews Nesterov's classical analysis of accelerated gradient in the convex case.
+    The paper will describe key aspects of the theoretical innovations involved to achieve the design of the algorithm in convex, and non-convex case.
 
@@
 \section{Introduction}
+    Nesterov first proposed the idea of an optimal algorithm named accelerated gradient descent method in his seminal work back in 1983 \cite{nesterov_method_1983}. 
+    It was seminal at the time because the algorithm's upper bound on the iteration complexity sealed the gap between the lower bound for all first order Lipschitz smooth convex function and the upper bound for this class of functions.
+    For a specific definition of the class of algorithms that are considered ``First Order'', we refer reader to Chapter 2 of Nesterov's new book \cite{nesterov_lecture_2018} for more information. 
+    In brief the method of gradient descent has an upper bound of $\mathcal O(1/k)$ in iteration complexity. 
+    It doesn't achieve the $\mathcal O(1/k^2)$ lower iteration complexity bound for first order optimization algorithms.
+    The method of accelerated gradient descent has an upper bound of $\mathcal O(1/k^2)$, making it optimal.
+
+    On first judgement, it's tempting to think that the existence of this optimal algorithm sealed the ceiling for the theoretical development for the entire class of convex first-order smooth optimization.
+    The judgement is correct but lacks the nuance in understanding. 
+    The missing piece here is the fact that Nesterov's accelerated gradient is a system of analysis technique instead of any specific design patterns in algorithms.
+
+    To demonstrate, the introduction of Guler's works in 1993 \cite{guler_new_1992} proposed an accelerated scheme using the technique of Nesterov's estimating sequence for Proximal Point Method (PPM) in the convex case.
+    Let $(\lambda_k)_{k \ge 0}$ be the sequence of scalars used for regularizing the proximal point method which generates sequence $(x_k)_{k\ge 0}$ given any initial guess $x_0$. 
+    Guler's prior work \cite{guler_convergence_1991} showed that convergence of PPM method in the convex case has $\mathcal O\left(1/\sum^{n}_{i = 1}\lambda_i\right)$. 
+    His new algorithm using the technique introduced in Nesterov's accelerated gradient achieves a convergence rate of $\mathcal O\left(1/(\sum_{i = 1}^{n} \sqrt{\lambda_i})^2\right)$. 
+    In addition, he also proposed together an inexact Accelerated PPM method using conditions described in Rockafellar's works in 1976 \cite{rockafellar_monotone_1976}.
+
+    One would be tempting to conclude that this has sealed the ceiling for research on the topic of extending Nesterov's acceleration. 
+    That is indeed correct, but not from a practical point of view. 
+    Let $F: \RR^n \mapsto \RR$ be our objective function, $\mathcal J_\lambda := (I + \lambda \partial F)^{-1}$ and $\mathcal M^{\lambda}(x; y):= F(x) + \frac{1}{2\lambda}\Vert x - y\Vert^2$ then the inexact proximal point considers with error $\epsilon_k$ has the following characterizations of inexactness as put forward by Guler \cite{guler_new_1992}:
+    \begin{align*}
+        & \tilde x \approx \mathcal J_\lambda y
+        \\
+        & 
+        \dist(\partial\mathcal{M}^{\lambda}(\tilde x; y))
+        \le \frac{\epsilon_k}{\lambda_k}
+    \end{align*}
+    However, this is troublesome because if we need to approximate the resolvent operator $\mathcal J_\lambda$, then it's probably difficult to compute the subgradient $\partial\mathcal M(\cdot; y)$, which make it difficult to know when we achieved the required exactness for a PPM evaluation.
+    Otherwise, if we already know the subgradient well, then why approximate it in the first place?
+
+    Introduced in Lin et al.
+\cite{lin_universal_2015}\cite{lin_catalyst_2018} is a series of papers on a concrete meta algorithm called Catalyst (It's called 4WD Catalyst for the non-convex extension in works by Paquette, Lin et al.
+\cite{paquette_catalyst_2018}).
+    It's called a meta algorithm because it uses other first order algorithm to evaluate inexact proximal point method and then performs the accelerated PPM using Nesterov's acceleration. 
+    Their innovations are tracking and controlling the errors made in the inexact PPM throughout the algorithm and some original example usages of the Catalyst framework.
+
+    One would be tempting to assert that this has sealed the ceiling for both theories and practice of Nesterov's acceleration hence it must be the center of discussion in this report. 
+    The conclusion is indeed correct which it will happen in the sections that follow while the assertion remains open.
 
     \subsection{Contributions}
+        The writing is expository and won't contain major results. 
+        We reviewed the literatures and faithfully reproduced some claims, in addition we give insights into understanding the claim in relations to other papers and foundational ideas in optimization.
 
 \section{Preliminaries}\label{sec:preliminaries}
+
+    \subsection{Method of Nesterov's Estimating Sequence}
+
+\section{Nesterov's Accelerated Proximal Gradient}
+
+\section{Guler 1993}
+\section{H.Lin 2015}
+
+\section{Non-convex Extension of Catalyst Acceleration}
 
@@
 \appendix
-\section{Postoned proofs}
+\section{Postponed proofs}
 

### 2024-11-08 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
     Hongda Li
-    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
-    The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{alto@mail.ubc.ca}.}~ and~Xianfu Wang
+    % \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
+    % The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{alto@mail.ubc.ca}.}~ and~Xianfu Wang
     % \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
@@
     The idea behind Nesterov's acceleration is universal in the convex case it has concrete extension in the non-convex case. 
-    In this paper we survey specifically the Catalyst Acceleration that incorperated ideas from the Accelerated Proximal Point Method proposed by Guler back in 1993. 
+    In this paper we survey specifically the Catalyst Acceleration that incorporated ideas from the Accelerated Proximal Point Method proposed by Guler back in 1993. 
     The paper reviews Nesterov's classical analysis of accelerated gradient in the convex case.
@@
     It was seminal at the time because the algorithm's upper bound on the iteration complexity sealed the gap between the lower bound for all first order Lipschitz smooth convex function and the upper bound for this class of functions.
-    For a specific definition of the class of algorithms that are considered ``First Order'', we refer reader to Chapter 2 of Nesterov's new book \cite{nesterov_lecture_2018} for more information. 
+    For a specific definition of the class of algorithms that are considered ``First Order'', we refer reader to Chapter 2 of Nesterov's new book \cite{nesterov_lectures_2018} for more information. 
     In brief the method of gradient descent has an upper bound of $\mathcal O(1/k)$ in iteration complexity. 
@@
         \dist(\partial\mathcal{M}^{\lambda}(\tilde x; y))
-        \le \frac{\epsilon_k}{\lambda_k}
+        \le \frac{\epsilon}{\lambda}
     \end{align*}
@@
 \section{Preliminaries}\label{sec:preliminaries}
-
+    Throughout the entire writing, let our ambient space is $\RR^n$. 
+    We assume the optimization problem of: 
+    \begin{align*}
+        \min_{x \in \RR^n} F(x). 
+    \end{align*}
+    In this section we introduce the idea of Nesterov's estimating sequence. 
+    Nesterov's estimating sequence is fundamental to works in Guler's accelerated PPM method, and Catalyst meta acceleration as a whole. 
     \subsection{Method of Nesterov's Estimating Sequence}
+        \begin{definition}[Nesterov's estimating sequence]\label{def:nes-est-seq}
+            Let $(\phi_k : \RR^n \mapsto \RR)_{k \ge 0}$ be a sequence of functions. 
+            We call this sequence of function a Nesterov's estimating sequence when it satisfies the conditions that: 
+            \begin{enumerate}
+                \item There exists another sequence $(x_k)_{k \ge 0}$ such that for all $k \ge 0$ it has $F(x_k) \le \phi_k^*$. 
+                \item There exists a sequence of $(\alpha_k)_{k \ge 0}$ such that for all $x \in \RR^n$, $\phi_{k + 1}(x) - \phi_k(x) \le - \alpha_k(\phi_k(x) - F(x))$. 
+            \end{enumerate}
+        \end{definition}
+        \begin{observation} 
+            If we define $\phi_k$, $\Delta_k(x) := \phi_k (x) - F(x)$ for all $x \in \RR^n$ and assume that $F$ has minimizer $x^*$. 
+            Then observe that $\forall k \ge 0$:  
+            \begin{align*}
+                \Delta_k(x) 
+                &= \phi_k(x) - f(x) \ge \phi_k^* - f(x)
+                \\
+                x = x_k\implies 
+                \Delta_k(x_k) 
+                &\ge 
+                \phi_k^* - f(x_k) \ge 0
+                \\
+                x = x_* \implies 
+                \Delta_k(x_*)
+                &\ge \phi_k^* - f_* \ge f(x_k) - f_* \ge 0
+            \end{align*}
+            The function $\Delta_k(x)$ is non-negative specifically at the points: $x_*, x_k$.
+            Additionally, we can derive the convergence rate of $\Delta_k(x^*)$ because $\forall x \in \RR^n$: 
+            \begin{align*}
+                \phi_{k + 1}(x) - \phi_k(x) 
+                &\le - \alpha_k (\phi_k(x) - F(x))
+                \\
+                \iff 
+                \phi_{k + 1}(x) - F(x) - (\phi_k(x) - F(x))
+                &\le 
+                -\alpha_k(\phi_k(x) - F(x))
+                \\
+                \iff
+                \Delta_{k + 1}(x) - \Delta_k(x) &\le
+                - \alpha_k\Delta_k(x)
+                \\
+                \iff 
+                \Delta_{k + 1}(x) 
+                &\le 
+                (1 - \alpha_k)\Delta_k(x). 
+            \end{align*}
+            Unrolling the above recursion it yields: 
+            \begin{align*}
+                \Delta_{k + 1}(x) &\le 
+                (1 - \alpha_k)\Delta_k(x) \le \cdots \le 
+                \left(
+                    \prod_{i = 0}^k(1 - \alpha_i)
+                \right)\Delta_0(x). 
+            \end{align*}
+            Finally, by setting $x = x^*$, $\Delta_k(x^*)$ is non-negative and using the property of Nesterov's estimating sequence it gives: 
+            $$
+                f(x_k) - f(x^*) \le \phi_k^* - f(x^*) \le \Delta_k(x^*) = \phi_k(x^*) - f(x^*) \le \left(\prod_{i = 0}^k(1 - \alpha_i)\right)\Delta_0(x^*).
+            $$ 
+            Therefore, it yields a convergence of the sequence $f(x_k)\rightarrow f(x^*)$ with a rate relates to sequence $(\alpha_k)_{k \in \N}$. 
+        \end{observation}
+        Much of the analysis of convergence Nesterov's type accelerated gradient method inherit the idea of Nesterov's estimating sequence. 
+        Such a proof won't result in simple proof because the construction of $\phi_k$ is non-trivial, but it comes with the advantage too because we can put creativity into the construction of the estimating sequence $(\phi_k)_{k \ge 0}$.
 
 \section{Nesterov's Accelerated Proximal Gradient}
+    This section swiftly exposes the constructions of the Nesterov's estimating sequence for the algorithm FISTA, which is specific case of Algorithm (2.1.19), (2.1.20) in Nesterov's book \cite{nesterov_lectures_2018}.
+    Discussion on these algorithms are relevant because they share the same format as the Catalyst Acceleration framework and accelerated PPM.
+
+    Throughout this section we assume that: $F = f + g$ where $f$ is $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex and $g$ is convex. 
+    Define 
+    \begin{align*}
+        \mathcal M^{L^{-1}}(x; y) 
+        &:= g(x) + f(y) 
+        + 
+        \left\langle \nabla f(x), x - y\right\rangle 
+        + 
+        \frac{L}{2}\Vert x - y\Vert^2, 
+        \\
+        \widetilde{\mathcal J}_{L^{-1}}y 
+        &:= \argmin_{x} \mathcal M^{L^{-1}}(x; y), 
+        \\
+        \mathcal G_{L^{-1}}(y)
+        &:= L\left(I - \widetilde{\mathcal J}_{L^{-1}}\right)y. 
+    \end{align*}
+
+    In the literature, $\mathcal G_{L^{-1}}$ is commonly known as the gradient mapping. 
+    The definition follows, we define the Nesterov's estimating sequence used to derive the accelerated proximal gradient method. 
+    \begin{definition}[Proximal Gradient Nesterov's Estimating Sequence]\label{def:nes-est-seq-pg}
+        For some sequence of $(y_k)_{k\ge0}$, 
+        Define $(\phi_k)_{k \ge0}$ be the Nesterov's estimating sequence which is recursively given by: 
+        \begin{align*}
+            & l_F(x; y_k) := 
+                F\left(\widetilde{\mathcal J}_{L^{-1}} y_k \right) 
+                + \langle \mathcal G_{L^{-1}}y_k, x - y_k\rangle + 
+            \frac{1}{2L}\Vert \mathcal G_{L^{-1}}y_k\Vert^2, 
+            \\
+            & 
+            \phi_{k + 1}(x)
+            := (1 - \alpha_k)\phi_k (x) + 
+            \alpha_k 
+            \left(
+                l_F(x; y_k) + \frac{\mu}{2}\Vert x - y_k\Vert^2
+            \right). 
+        \end{align*}
+        And the sequence of vector $y_k, x_k$, and scalars $\alpha_k$ satisfies the following: 
+        \begin{align*}
+            &x_{k + 1} = \widetilde{\mathcal J}_{L^{-1}} y_k, 
+            \\
+            & \text{find } \alpha_{k + 1} \in (0, 1)
+            \alpha_{k + 1} = (1 - \alpha_{k + 1})\alpha_k^{2} + (\mu/L) \alpha_{k + 1}
+            \\
+            &y_{k + 1} = x_{k + 1} + \frac{\alpha_k(1 - \alpha_k)}{\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
+        \end{align*}
+        One of the possible base case can be $x_0 = y_0$ and any $\alpha_0 \in (0, 1)$. 
+    \end{definition}
+    \begin{observation}
+        One key component of the Nesterov's estimating sequence is the use of the proximal gradient inequality: $l_F(x; y_k) + \mu/2\Vert x - y_k\Vert^2$. 
+        In the convex case the function has the property $l_F(\cdot, y) \le F(\cdot)$ for all $y$. 
+        More precisely, if $f \equiv 0$ then $\widetilde{\mathcal J}_{L^{-1}}y_k$ becomes exactly the same as the resolvent on $F = g$, which makes $x_k$ being an exact evaluation of PPM.
+        And we have 
+        \begin{align*}
+            l_F(x; y_k) 
+            &= F(\mathcal J_{L^{-1}}y_k) 
+            + \langle L(y - \mathcal J_{L^{-1}} y), x - y_k\rangle + \frac{L}{2}\Vert y_k - \mathcal J_{L^{-1}}y_k\Vert^2
+            \\
+            &= F(\mathcal J_{L^{-1}}y_k) 
+            + \langle L(y - \mathcal J_{L^{-1}} y), x - \mathcal J_{L^{-1}}y_k\rangle. 
+        \end{align*}
+        This is the proximal inequality. 
+        The key takeaway here being the fact that using inexact PPM evaluations result in an inequality that is similar to the case of just having the smooth parts alone, and the convergence proof would still work out with the inexact PPM: $\widetilde{\mathcal J}_{L^{-1}}y_k$.
+        There is no obvious manifestations of an error term. 
+    \end{observation}
+    \begin{remark}
+        The definition is a generalization of Nesterov's estimating sequence comes from (2.2.63) from Nesterov's book \cite{nesterov_lectures_2018}. 
+        Compare to Nesterov's work, we used proximal gradient operator instead of projected gradient. 
+    \end{remark}
 
 \section{Guler 1993}
-\section{H.Lin 2015}
+    This section introduces the setup of the Nesterov's estimating sequence used in Guler's accelerated Proximal Point method. 
+    In addition, this section will highlight some observations and theoretical results accordingly. 
+\section{Lin 2015}
 
@@
 
+\subsection{Theorems and claims for accelerated proximal gradient}
+
 \end{document}

### 2024-11-10 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, new stuff
>w<, a lot of changes

@@
 \section{Nesterov's Accelerated Proximal Gradient}
-    This section swiftly exposes the constructions of the Nesterov's estimating sequence for the algorithm FISTA, which is specific case of Algorithm (2.1.19), (2.1.20) in Nesterov's book \cite{nesterov_lectures_2018}.
+    This section swiftly exposes the constructions of the Nesterov's estimating sequence for the FISTA algorithm by Beck\cite{beck_fast_2009-1}, which is specific case of Algorithm (2.2.63), in Nesterov's book \cite{nesterov_lectures_2018}.
     Discussion on these algorithms are relevant because they share the same format as the Catalyst Acceleration framework and accelerated PPM.
@@
     The definition follows, we define the Nesterov's estimating sequence used to derive the accelerated proximal gradient method. 
-    \begin{definition}[Proximal Gradient Nesterov's Estimating Sequence]\label{def:nes-est-seq-pg}
-        For some sequence of $(y_k)_{k\ge0}$, 
-        Define $(\phi_k)_{k \ge0}$ be the Nesterov's estimating sequence which is recursively given by: 
+    \begin{definition}[Accelerated proximal gradient estimating sequence]\label{def:nes-est-seq-pg}
+        Define $(\phi_k)_{k \ge0}$ be the Nesterov's estimating sequence recursively given by: 
         \begin{align*}
@@
         In the convex case the function has the property $l_F(\cdot, y) \le F(\cdot)$ for all $y$. 
-        More precisely, if $f \equiv 0$ then $\widetilde{\mathcal J}_{L^{-1}}y_k$ becomes exactly the same as the resolvent on $F = g$, which makes $x_k$ being an exact evaluation of PPM.
+        More precisely, if $f \equiv 0$ then $\widetilde{\mathcal J}_{L^{-1}}y_k$ becomes resolvent $(I + L^{-1}\partial F)^{-1}$, which makes $x_k$ being an exact evaluation of PPM.
         And we have 
@@
         This is the proximal inequality. 
-        The key takeaway here being the fact that using inexact PPM evaluations result in an inequality that is similar to the case of just having the smooth parts alone, and the convergence proof would still work out with the inexact PPM: $\widetilde{\mathcal J}_{L^{-1}}y_k$.
-        There is no obvious manifestations of an error term. 
+        Observe that the inequality with proximal gradient term can be interpreted as an example of inexact evaluation of the PPM and the inequality. 
     \end{observation}
+    To demonstrate the usage of Nesterov's estimating sequence here, consider sequence $(x_k)_{k \ge 0}$ such that $F(x_k) \le \phi_k^*$. 
+    Assume the existence of minimizer $x^*$ for $F$, by definition of $\phi_k$ let $x = x^*$ then $\forall k \ge 0$: 
+    {\small
+    \begin{align*}
+        \phi_{k + 1}(x^*)
+        &= (1 - \alpha_k)\phi_k (x^*) + 
+        \alpha_k 
+        \left(
+            l_F(x^*; y_k) + \frac{\mu}{2}\Vert x^* - y_k\Vert^2
+        \right)
+        \\
+        \phi_{k + 1}(x^*) - \phi_k(x^*) &= 
+        -\alpha_k\phi_k(x^*) 
+        +
+        \alpha_k
+        \left(
+            l_F(x^*; y_k) + \frac{\mu}{2}\Vert x^* - y_k\Vert^2
+        \right) 
+        \\
+        \implies
+        \phi_{k + 1}(x^*) - F(x^*) + F(x^*) - \phi_k(x^*) 
+        &\le -\alpha_k(\phi_k(x^*) - F(x^*))
+        \\
+        \implies 
+        F(x_{k + 1}) - F(x^*)
+        \le \phi_{k + 1}^* - F(x^*)
+        &\le \phi_{k + 1}(x^*) - F(x^*)
+        \le 
+        (1 - \alpha_k)(\phi_k(x^*) - F(x^*)). 
+    \end{align*}
+    }
+    On the first inequality we used the fact that $l_F(x; y_k) + \mu/2\Vert x - y_k\Vert^2\le F(x)$. 
+    Unrolling the recurrence, we can get the convergence rate of $F(x_k) - F(x^*)$ to be on Big O of $\prod_{i = 1}^k(1 - \alpha_i)$. 
     \begin{remark}
@@
         Compare to Nesterov's work, we used proximal gradient operator instead of projected gradient. 
+        The same inequality is called ``Fundamental Proximal Gradient Inequality'' in Amir Beck's book \cite{beck_first-order_2017}, Theorem 10.16. 
     \end{remark}
@@
     In addition, this section will highlight some observations and theoretical results accordingly. 
+    \begin{definition}[Accelerated PPM estimating sequence]\label{def:nes-est-seq-acc-ppm}
+
+    \end{definition}
+
 \section{Lin 2015}
@@
 
-\subsection{Theorems and claims for accelerated proximal gradient}
+\subsection{Theorems and claims for accelerated proximal gradient}\label{app:sec:thm-claim-acc-prox-grad}
+
+    \begin{theorem}[Fundamental theorem of proximal gradient]\label{thm:fun-thm-prox-grad}
+
+    \end{theorem}
+    \begin{theorem}[Cannonical form of proximal gradient estimating sequence]
+
+    \end{theorem}
 

### 2024-11-11 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, catalyst report

@@
 
-\section{Nesterov's Accelerated Proximal Gradient}
+\section{Nesterov's accelerated proximal gradient}
     This section swiftly exposes the constructions of the Nesterov's estimating sequence for the FISTA algorithm by Beck\cite{beck_fast_2009-1}, which is specific case of Algorithm (2.2.63), in Nesterov's book \cite{nesterov_lectures_2018}.
@@
     \end{remark}
+    \begin{definition}[Accelerated proixmal gradient algorithm]\label{def:acc-prox-grad-alg}
+        The algorithm of accelerated proximal gradient generates sequence of iterates $(x_k, y_k)_{k \ge 0}$ which satisfies for all $k\ge 0$: 
+        \begin{align*}
+            &x_{k + 1} = \widetilde{\mathcal J}_{L^{-1}} y_k, 
+            \\
+            & \text{find } \alpha_{k + 1} \in (0, 1)
+            \alpha_{k + 1} = (1 - \alpha_{k + 1})\alpha_k^{2} + (\mu/L) \alpha_{k + 1}
+            \\
+            &y_{k + 1} = x_{k + 1} + \frac{\alpha_k(1 - \alpha_k)}{\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
+        \end{align*}
+
+    \end{definition}
+    \begin{remark}
+        The simple case of accelerated gradient descent is stated as (2.2.63) in Nesterov's book \cite{nesterov_lectures_2018}. 
+    \end{remark}
+    For a proof that proves 
+    \hyperref[def:nes-est-seq-pg]{Definition \ref*{def:nes-est-seq-pg}}
+    is an estimating sequence, and 
+    \hyperref[def:acc-prox-grad-alg]{Definition \ref{def:acc-prox-grad-alg}}
+    is the accelerated proximal gradient algorithm, please visit 
+    \hyperref[app:sec:thm-claim-acc-prox-grad]{Appendix \ref*{app:sec:thm-claim-acc-prox-grad}}. 
+    We warn the readers that the proof is long.
 
@@
     In addition, this section will highlight some observations and theoretical results accordingly.
+
+    Throughout this section, we assume that $F:\RR^n \mapsto \overline \RR$ is a convex function. 
+    We use the following list of notations: 
+    \begin{align*}
+        \mathcal M^{\lambda} (x; y) &:= F(x) + \frac{1}{2\lambda}\Vert x - y\Vert^2
+        \\
+        \mathcal J_\lambda y &:= \argmin_x \mathcal M^{\lambda} (x; y)
+        \\
+        \mathcal G_\lambda &:= \lambda^{-1}(I - \mathcal J_\lambda). 
+    \end{align*}
+    For notations simplicity, we use $\mathcal G_k, \mathcal J_k$ to denote the gradient mapping and the proximal point operator because under the context of the algorithm, the proximal point step is conductive iteratively with some arbitrary sequence that $(\lambda)_{k \ge 0}$ which we fixed at the start.
+
     \begin{definition}[Accelerated PPM estimating sequence]\label{def:nes-est-seq-acc-ppm}
-
+        The Nesterov's estimating sequence $(\phi_k)_{k \ge0}$ for the accelerated proximal point method is defined by the following recurrence for all $k \ge0$, any $A \ge 0$: 
+        \begin{align*}
+            \phi_0 &:= f(x_0) + \frac{A}{2}\Vert x - x_0\Vert^2, 
+            \\
+            \phi_{k + 1}(x) &:= 
+            (1 - \alpha_k)\phi_k(x)
+            + 
+            \alpha_k(F(\mathcal J_k y_k) + \langle \mathcal G_k y_k, x - \mathcal J_k y_k\rangle).    
+        \end{align*}
+        Let $(\lambda_k)_{k \ge 0}$ be the step size which defines the descent sequence $x_k = \mathcal J_\lambda y_k$. 
+        Then the descent sequence $x_k$, along with the auxiliary vector sequence $(y_k, v_k)$, scalar sequence $(\alpha_k, A_k)_{k\ge 0}$ will be made to satisfy for all $k\ge0$, the conditions: 
+        \begin{align*}
+            \alpha_k &= \frac{1}{2}\left(
+                \sqrt{(A_k\lambda_k)^2 + 4A_k \lambda_k}
+                - A_k\lambda_k
+            \right) 
+            \\
+            y_k &= (1 - \alpha_k)x_k + \alpha_k v_k
+            \\
+            v_{k + 1}
+            &= 
+            v_k - \frac{\alpha_k}{A_{k + 1}\lambda_k}(y_k - \mathcal J_k y_k)
+            \\
+            A_{k + 1} &= (1 - \alpha_k)A_k, 
+        \end{align*}
     \end{definition}
+    \begin{remark}
+        The auxiliary sequences $(A_k, v_k)$ parameterizes a canonical representation of the estimating sequence $(\phi_k)_{k \ge0}$. 
+        Guler didn't simplify his results compare to what Nesterov did in his book. 
+    \end{remark}
+    Next, we discuss the procedures Guler did to allow the inexact evaluation of proximal method for the accelerated proximal point method.
 
@@
 \subsection{Theorems and claims for accelerated proximal gradient}\label{app:sec:thm-claim-acc-prox-grad}
+    Throughout this section, $F = g + f$ is an additive composite objective function with $g$ convex, $f$ $L$-lipschitz smooth and $\mu \ge0$ strongly convex. 
+    The notations here are 
+    \begin{align*}
+        \mathcal M^{L^{-1}}(x; y) 
+        &:= 
+        F(x) + \frac{L}{2}\Vert x - y\Vert^2
+        \\
+        \widetilde{ \mathcal M}^{L^{-1}}(x; y) 
+        &:= g(x) + f(y) 
+        + 
+        \left\langle \nabla f(x), x - y\right\rangle 
+        + 
+        \frac{L}{2}\Vert x - y\Vert^2
+        \\
+        \widetilde{\mathcal J}_{L^{-1}}y 
+        &:= \argmin_{x} \widetilde{\mathcal M}^{L^{-1}}(x; y)
+        \\
+        \widetilde{\mathcal G}_{L^{-1}}(y)
+        &:= L\left(I - \widetilde{\mathcal J}_{L^{-1}}\right)y. 
+    \end{align*}
 
-    \begin{theorem}[Fundamental theorem of proximal gradient]\label{thm:fun-thm-prox-grad}
+    \begin{theorem}[Fundamental theorem of proximal gradient]
+    \label{thm:fun-thm-prox-grad}
+        Let $h = f + g$ and proximal gradient operator $T$ be given as in this section. 
+        Fix any $y$, we have for all $x \in \RR^n$: 
+        \begin{align*}
+            h(x) - h(Ty) - 
+            \left\langle 
+                L(y - \widetilde{\mathcal J}_{L^{-1}} y),
+                x - \widetilde {\mathcal J}_{L^{-1}}y
+            \right\rangle
+            &\ge  D_f(x, y) . 
+        \end{align*}  
+    \end{theorem}
+    \begin{proof}
+        By a direct observation: 
+        \begin{align*}
+            \widetilde{\mathcal M}^{L^{-1}}(x; y) 
+            &= 
+            g(x) + f(y) + \langle \nabla f(y), x - y\rangle + \frac{L}{2}\Vert x - y\Vert^2
+            \\
+            &= 
+            g(x) + f(x) - f(x) + f(y) 
+            + \langle \nabla f(y), x - y\rangle + \frac{L}{2}\Vert x - y\Vert^2
+            \\
+            &= 
+            h(x) - D_f(x, y) + \frac{L}{2}\Vert x - y\Vert^2 
+            \\
+            &= \mathcal M^{L^{-1}}(x; y) - D_f(x, y). 
+        \end{align*}
+        Next, since $\widetilde{\mathcal M}^{L^{-1}}(\cdot, y)$ is strongly convex, it has quadratic growth conditions on its minimizer. 
+        Denote $y^+ = \widetilde{\mathcal J}_{L^{-1}}y$ then: 
+        {\small
+        \begin{align*}
+            \widetilde{\mathcal M}^{L^{-1}}(x; y) - 
+            \widetilde{\mathcal M}^{L^{-1}}(y^+; y)
+            - 
+            \frac{L}{2}\Vert x - y^+\Vert^2
+            &\ge 
+            0
+            \\
+            \implies 
+            \left(
+                \mathcal M^{L^{-1}}(x; y) - D_f(x, y)
+            \right) - 
+            \mathcal M^{L^{-1}}(y^+; y) 
+            - 
+            \frac{L}{2}\Vert x - y^+\Vert^2
+            &\ge 0
+            \\
+            \iff 
+            \left(
+                \mathcal M^{L^{-1}}(x; y)
+                - 
+                \mathcal M^{L^{-1}}(y^+; y)
+            \right)
+            - 
+            D_f(x, y) 
+            - \frac{L}{2}\Vert x - y^+\Vert^2
+            &\ge 0
+            \\
+            \iff 
+            \left(
+                F(x) - F(y^+) 
+                + 
+                \frac{L}{2}\Vert x - y\Vert^2 - 
+                \frac{L}{2}\Vert y^+ - y\Vert^2
+            \right)
+            - 
+            D_f(x, y) 
+            - \frac{L}{2}\Vert x - y^+\Vert^2
+            &\ge 0
+            \\
+            \iff 
+            \left(
+                F(x) - F(y^+) 
+                + 
+                \frac{L}{2}
+                \left(
+                    \Vert x - y^+ + y^+ - y\Vert^2
+                    - 
+                    \Vert y - y^+\Vert^2
+                \right)
+            \right)
+            - 
+            D_f(x, y) 
+            - \frac{L}{2}\Vert x - y^+\Vert^2
+            &\ge 0
+            \\
+            \iff 
+            \left(
+                F(x) - F(y^+) 
+                + 
+                \frac{L}{2}
+                \left(
+                    \Vert x - y^+\Vert^2 + 
+                    2\langle x - y^+, y^+ - y\rangle
+                \right)
+            \right)
+            - 
+            D_f(x, y) 
+            - \frac{L}{2}\Vert x - y^+\Vert^2
+            &\ge 0
+            \\
+            \iff
+            \left(
+                F(x) - F(y^+) + \frac{L}{2}\Vert x - y^+\Vert^2 
+                - L\langle  x - y^+, y - y^+\rangle
+            \right)
+            - 
+            D_f(x, y) 
+            - \frac{L}{2}\Vert x - y^+\Vert^2
+            &\ge 0
+            \\
+            \iff 
+            F(x) - F(y^+)
+            - \langle L(y - y^+), x - y^+\rangle
+            - D_f(x, y) 
+            &\ge 0. 
+        \end{align*}
+        }
+    \end{proof}
 
+    \begin{theorem}[Cannonical form of proximal gradient estimating sequence]
+    \label{thm:canon-prox-grad-est-seq}
+        \; \\
+        Denote $\phi_k:\RR^n \mapsto \RR$ as a sequence of functions such that it satisfies recursively for all $k\ge 0$ the following conditions 
+        \begin{align*}
+            & g_k := L(y_k - \widetilde{\mathcal J}_{L^{-1}} y_k)
+            \\
+            & l_F(x; y_k) := 
+                F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) 
+                + \langle g_k, x - y_k\rangle 
+                + \frac{1}{2L}\Vert g_k\Vert^2, 
+            \\
+            & \alpha_k \in (0, 1)
+            \\
+            & 
+            \phi_{k + 1}(x)
+            := (1 - \alpha_k)\phi_k (x) + 
+            \alpha_k (l_h(x; y_k) + \mu/2\Vert x - y_k\Vert^2). 
+        \end{align*}
+        Where $(y_k)_{k\ge 0}$ is any auxiliary sequence. 
+        If we define the canonical form for $\phi_k$ as convex quadratic parameterized by positive sequence $(\gamma_k), \phi_k^*$ and 
+        \begin{align*}
+            \phi_k^* := \min_{x} \phi_k(x)
+            \\
+            \phi_k(x) := \phi_k^* + \frac{\gamma_k}{2}\Vert x - v_k\Vert^2.
+        \end{align*}
+        Then the auxiliary sequence $y_k, v_k$, parameters for the canonical form of estimating sequence must satisfy for all $k\ge 0$ these inequalities: 
+        {\small
+        \begin{align*}      
+            \gamma_{k + 1} &= (1 - \alpha_k) \gamma_k + \mu \alpha_k
+            \\
+            v_{k + 1} &= \gamma_{k + 1}^{-1}
+            (\gamma_k(1 - \alpha_k)v_k - \alpha_k g_k + \mu \alpha_k y_k)
+            \\
+            \phi_{k + 1}^* &= 
+            (1 - \alpha_k)\phi_k^*
+            + \alpha_k\left(
+                F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) 
+                + \frac{1}{2L}\Vert g_k\Vert^2 
+            \right) 
+            \\
+            &\quad 
+            - \frac{\alpha_k^2}{2 \gamma_{k + 1}} \Vert g_k\Vert^2 
+            + 
+            \frac{\alpha_k(1 - \alpha_k)\gamma_k}{\gamma_{k + 1}} 
+            \left(
+                \frac{\mu}{2}\Vert v_k - y_k\Vert^2 
+                + \langle v_k - y_k , g_k\rangle
+            \right). 
+        \end{align*}
+        }
     \end{theorem}
-    \begin{theorem}[Cannonical form of proximal gradient estimating sequence]
+    \begin{proof}
+        By the recursive definition of $\phi_k$: 
+        \begin{align*}
+            \phi_{k + 1}(x) 
+            &= 
+            (1 - \alpha_k)\phi_k(x) + \alpha_k (l_F(x; y_k) + \mu/2\Vert x - y_k\Vert^2)
+            \\
+            &= 
+            (1 -\alpha_k)
+            \left(
+                \phi_k^* + \gamma_k/2\Vert x - v_k\Vert^2
+            \right) 
+            + 
+            \alpha_k
+            \left(
+                l_h(x; y_k) + \mu/2\Vert x - y_k\Vert^2
+            \right)
+            \rightarrow \textcolor{red}{(\text{eqn1})}; 
+            \\
+            \nabla \phi_{k + 1}(x) 
+            &= 
+            (1 - \alpha_k)\gamma_k(x - v_k) + \alpha_k(g_k + \mu (x - y_k));
+            \\
+            \nabla^2 \phi_{k + 1}(x) &= 
+            \underbrace{((1 - \alpha_k)\gamma_k + \alpha_k \mu)}_{=\gamma_{k + 1}}I. 
+        \end{align*}
+        The first recurrence for is discovered as $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$. 
+        Because $v_{k + 1}$ is the minimizer of $\phi_{k+ 1}$ by definition of the canonical form, solving $\nabla \phi_{k + 1}(x) = \mathbf 0 $ yields $v_{k + 1}$. 
+        This is obtained by considering the following: 
+        \begin{align*}
+            \mathbf 0 &= 
+            \gamma_k(1 - \alpha_k)(x - v_k) + \alpha_k g_k + \mu \alpha_k(x - y_k)
+            \\
+            &= (\gamma_k(1 - \alpha_k) + \mu \alpha_k)x - 
+            \gamma_k(1 - \alpha_k)v_k + \alpha_k g_k - \mu \alpha_k y_k
+            \\
+            \iff 
+            v_{k + 1} &:= x=
+            \gamma_{k +1}^{-1} 
+            \left(
+                \gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k
+            \right). 
+        \end{align*}
+        From the second and third equality we used $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$. 
+        Substituting the canonical form of $\phi_{k + 1}$ back to \textcolor{red}{eqn1}, choose $x = y_k$, it gives the following: 
+        \begin{align*}
+            \phi_{k + 1}^* 
+            &= (1 - \alpha_k)\phi_k^* + \frac{(1 - \alpha_k)\gamma_k}{2}\Vert y_k - v_k\Vert^2   
+            \\
+            & \quad 
+            - \frac{\gamma_{k + 1}}{2}\Vert y_k - v_{k + 1}\Vert^2 
+            + 
+            \alpha_k\left(
+                F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) 
+                + 
+                \frac{1}{2L} \Vert g_k\Vert^2
+            \right)
+            \rightarrow 
+            \textcolor{red}{(\text{eqn2})}. 
+        \end{align*}
+        Next move is to simplify the term $\Vert v_{k + 1} - y_k\Vert^2$. 
+        With that it produces: 
+        \begin{align*}
+            v_{k + 1} - y_k 
+            &= 
+            \gamma_{k + 1}^{-1}
+            \left(
+                \gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k
+            \right) - y_k
+            \\
+            &= 
+            \gamma_{k + 1}^{-1}
+            \left(
+                \alpha_k(1 - \alpha_k)v_k - \alpha_k g_k 
+                + (-\gamma_{k + 1} + \mu\alpha_k)y_k
+            \right)
+            \\
+            &
+            \textcolor{gray}{
+                \begin{aligned}
+                    \gamma_{k + 1} &=    
+                    (1 - \alpha_k)\gamma_k + \mu \alpha_k
+                    \\
+                    \gamma_{k + 1} - \mu \alpha_k &= (1 - \alpha_k)\gamma_k
+                \end{aligned}
+            }
+            \\
+            &=
+            \gamma_{k + 1}^{-1}
+            \left(
+                \alpha_k(1 - \alpha_k)v_k - \alpha_k g_k 
+                (1 - \alpha_k)\gamma_ky_k
+            \right)
+            \\
+            &= 
+            \gamma_{k + 1}^{-1}(
+                \alpha_k(1 - \alpha_k)(v_k - y_k) 
+                - \alpha_k g_k
+            ).
+        \end{align*}
+        Taking the norm of that we have: 
+        \begin{align*}
+            \Vert v_{k + 1} - y_k\Vert^2 
+            &= 
+            \Vert 
+                \gamma_{k + 1}^{-1}(
+                    \alpha_k(1 - \alpha_k)(v_k - y_k) 
+                    - \alpha_k g_k
+                )
+            \Vert^2
+            \\
+            \frac{- \gamma_{k + 1}}{2}
+            \Vert v_{k + 1} - y_k\Vert^2
+            &= 
+            - \frac{1}{2\gamma_{k + 1}}
+            \Vert 
+                \gamma_k(1 - \alpha_k)(v_k - y_k) - \alpha_k g_k
+            \Vert^2
+            \\
+            &= 
+            -\frac{\gamma_k^2 (1 - \alpha_k)^2}{2 \gamma_{k + 1}} 
+            \Vert v_k - y_k\Vert^2 - 
+            \frac{\alpha_k^2}{2 \gamma_{k + 1}} \Vert g_k\Vert^2
+            \\&\quad 
+                + 
+                \gamma_k(1 - \alpha_k)\gamma_{k + 1}^{-1} \langle v_k - y_k, \alpha_k g_k\rangle. 
+        \end{align*}
+        Substitute it back to \textcolor{red}{eqn2} we have 
+        \begin{align*}
+            \phi_{k + 1}^* &= 
+            (1 - \alpha)\phi_k^* + 
+            \alpha_k
+            \left(
+                F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) + 
+                \frac{1}{2L}\Vert g_k\Vert^2
+            \right)
+            \\
+            &\quad 
+            + \frac{(1 - \alpha_k)\gamma_k}{2}\Vert y_k - v_k\Vert^2
+            - \frac{\gamma_k^2(1 - \alpha_k)^2}{2\gamma_{k + 1}}\Vert v_k - y_k\Vert^2
+            - \frac{\alpha_k^2}{2\gamma_{k + 1}}\Vert g_k\Vert^2
+            \\
+            &\quad 
+            + \alpha_k\gamma_k(1 - \alpha_k)\gamma_{k + 1}^{-1}\langle v_k -y_k, g_k\rangle
+            \\
+            &= 
+                (1 - \alpha)\phi_k^* + 
+                \alpha_k
+                \left(
+                    F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) + 
+                    \frac{1}{2L}\Vert g_k\Vert^2
+                \right)
+                \\
+                &\quad 
+                + 
+                \left(
+                    \frac{(1 - \alpha_k)\gamma_k}{2}
+                    - 
+                    \frac{\gamma_k^2(1 - \alpha_k)^2}{2\gamma_{k + 1}}
+                \right)
+                \Vert v_k - y_k\Vert^2
+                - \frac{\alpha_k^2}{2\gamma_{k + 1}}\Vert g_k\Vert^2
+                \\
+                &\quad 
+                + \alpha_k\gamma_k(1 - \alpha_k)\gamma_{k + 1}^{-1}\langle v_k -y_k, g_k\rangle
+            \\
+            & \quad 
+            \textcolor{gray}{  
+                \begin{aligned}
+                    \frac{(1 - \alpha_k)\gamma_k}{2}
+                    - 
+                    \frac{\gamma_k^2(1 - \alpha_k)^2}{2\gamma_{k + 1}}   
+                    &= 
+                    \frac{(1 - \alpha_k)\gamma_k}{2}
+                    \left(
+                        1 - \frac{\gamma_k (1 - \alpha_k)}{\gamma_{k + 1}}
+                    \right)
+                    \\
+                    &= 
+                    \frac{(1 - \alpha_k)\gamma_k}{2}
+                    \left(
+                        \frac{\gamma_{k + 1} - \gamma_k(1 - \alpha_k)}{\gamma_{k + 1}}
+                    \right)
+                    \\
+                    &= 
+                    \frac{(1 - \alpha_k)\gamma_k}{2}
+                    \left(
+                        \frac{\mu \alpha_k}{\gamma_{k + 1}}
+                    \right). 
+                \end{aligned}
+            }
+            \\
+            \iff 
+            &= 
+                (1 - \alpha)\phi_k^* + 
+                \alpha_k
+                \left(
+                    F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) + 
+                    \frac{1}{2L}\Vert g_k\Vert^2
+                \right)
+                \\
+                &\quad 
+                + 
+                \frac{(1 - \alpha_k)\gamma_k}{2}
+                \left(
+                    \frac{\mu \alpha_k}{\gamma_{k + 1}}
+                \right)
+                \Vert v_k - y_k\Vert^2
+                - \frac{\alpha_k^2}{2\gamma_{k + 1}}\Vert g_k\Vert^2
+                \\
+                & \quad 
+                + \alpha_k\gamma_k(1 - \alpha_k)\gamma_{k + 1}^{-1}\langle v_k -y_k, g_k\rangle
+            \\
+            &= 
+                (1 - \alpha)\phi_k^* 
+                + 
+                \alpha_k
+                \left(
+                    F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) + 
+                    \frac{1}{2L}\Vert g_k\Vert^2
+                \right)
+                \\
+                &\quad 
+                - 
+                \frac{\alpha_k^2}{2\gamma_{k + 1}}\Vert g_k\Vert^2
+                + 
+                \frac{(1 - \alpha_k)\gamma_k\alpha_k}{\gamma_{k + 1}}
+                \left(
+                    \frac{\mu}{2}\Vert v_k - y_k\Vert^2
+                    + \langle v_k - y_k, g_k\rangle
+                \right). 
+        \end{align*}
+        The second and third inequality used the equality $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \mu \alpha_k$. 
+    \end{proof}
 
+    \begin{theorem}[Verifying the conditions of implicit descent]\;\\
+        Let estimating sequence $\phi_k$ and auxiliary sequence $y_k, v_k,\gamma_k, \alpha_k$  be given by 
+        \hyperref[thm:canon-prox-grad-est-seq]{Theorem \ref*{thm:canon-prox-grad-est-seq}}. 
+        If for all $k\ge 0$ they verify: 
+        \begin{align*}
+            \frac{1}{2L} - \frac{\alpha_k^2}{2 \gamma_{k + 1}} &\ge 0, 
+            \\
+            \frac{\alpha_k \gamma_k }{\gamma_{k + 1}} 
+            (v_k - y_k) + (T_L y_k - y_k) &= \mathbf 0, 
+        \end{align*}
+        then $\phi_{k}$ is an estimating sequence that verifies $\forall x \in \RR^n, k \ge 0$: 
+        \begin{align*}
+            F\left(
+                \widetilde{\mathcal J}_{L^{-1}} y_{k - 1}
+            \right)\le \phi_k^*
+            \\
+            \phi_{k + 1}(x) - \phi_k(x) &\le -\alpha(\phi_k(x) - F(x)). 
+        \end{align*}
     \end{theorem}
+    \begin{proof}
+        Inductively assume that $x_k = \widetilde{\mathcal J}_{L^{-1}}y_{k - 1}$ so $F(x_k) \le \phi_k^*$. 
+        Substituting the $x_k$ into the equation for $\phi_{k + 1}$: 
+        {\small
+        \begin{align*}
+            \phi_{k + 1}^* &= 
+            (1 - \alpha_k) \phi_k^*
+            + 
+            \alpha_k
+            \left(
+                F(x_k) + \frac{1}{2L}\Vert g_k\Vert^2
+            \right)
+            \\&\quad 
+                - \frac{\alpha_k^2}{2\gamma_{k + 1}}\Vert g_k\Vert^2
+                + \frac{\alpha_k (1 - \alpha_k)\gamma_k}{\gamma_{k + 1}}
+                \left(
+                    \frac{\mu}{2}\Vert v_k - y_k\Vert^2 + \langle v_k - y_k, g_k\rangle
+                \right)
+            \\
+            \implies 
+            &\ge 
+            (1 - \alpha_k)h(x_k)
+            + 
+            \alpha_k
+            \left(
+                h(x_k) + \frac{1}{2L}\Vert g_k\Vert^2
+            \right)
+            \\&\quad
+                - \frac{\alpha_k^2}{2\gamma_{k + 1}}\Vert g_k\Vert^2
+                + \frac{\alpha_k (1 - \alpha_k)\gamma_k}{\gamma_{k + 1}}
+                \left(
+                    \frac{\mu}{2}\Vert v_k - y_k\Vert^2 + \langle v_k - y_k, g_k\rangle
+                \right)
+            \\
+            \implies
+            &\ge 
+            (1 - \alpha_k)h(x_k)
+            + 
+            \alpha_k
+            \left(
+                h(x_k) + \frac{1}{2L}\Vert g_k\Vert^2
+            \right)
+            - \frac{\alpha_k^2}{2\gamma_{k + 1}}\Vert g_k\Vert^2
+            + 
+            \frac{\alpha_k (1 - \alpha_k)\gamma_k}{\gamma_{k + 1}}
+            \langle v_k - y_k, g_k\rangle. 
+        \end{align*}
+        }
+        The first inequality comes from the inductive hypothesis. 
+        The second inequality comes from the non-negativity of the term $\frac{\mu}{2}\Vert v_k - y_k\Vert^2$. 
+        Now, recall from the fundamental proximal gradient inequality in the convex settings, we have $\forall z\in \RR^n$: 
+        \begin{align*}
+            F(z) &\ge 
+            F\left(\widetilde{\mathcal J}_{L^{-1}}y_k\right)
+            + \left\langle 
+                L(y - \widetilde{\mathcal J}_{L^{-1}}y_k), 
+                z - \widetilde{\mathcal J}_{L^{-1}}y_k
+            \right\rangle + D_f(z, y)
+            \\
+            & \text{set: }x_{k + 1} := \widetilde{\mathcal J}_{L^{-1}}y_k
+            \\
+            &\ge 
+            F(x_{k + 1}) + \langle g_k, z - x_k\rangle + \frac{\mu}{2}\Vert z - y\Vert^2
+            \\
+            &=
+            F(x_{k + 1}) + \langle g_k, z - y + y - x_k\rangle + \frac{\mu}{2}\Vert z - y\Vert^2
+            \\
+            &\ge
+            F(x_{k + 1}) + \langle g_k, z - y\rangle 
+            + \frac{1}{2L}\Vert g_k\Vert^2. 
+        \end{align*}
+        Now we set $z = x_{k}$ and substitute it back to RHS of $\phi_{k + 1}$ which yields: 
+        \begin{align*}
+            \phi_{k + 1}^*
+            &\ge 
+            (1 - \alpha_k)
+            \left(
+                F(x_{k + 1}) + \langle g_k, x_k - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2
+            \right)
+            \\
+            &\quad 
+            + 
+            \alpha_k
+            \left(
+                F(x_{k + 1}) + \frac{1}{2L}\Vert g_k\Vert^2
+            \right)
+            - \frac{\alpha_k^2}{2\gamma_{k + 1}}\Vert g_k\Vert^2
+            + 
+            \frac{\alpha_k (1 - \alpha_k)\gamma_k}{\gamma_{k + 1}}
+            \langle v_k - y_k, g_k\rangle
+            \\
+            &\ge 
+            F(x_{k + 1})
+            + 
+            \left(
+                \frac{1}{2L} - \frac{\alpha_k^2}{2\gamma_{k + 1}}
+            \right)\Vert g_k\Vert^2
+            + 
+            (1 - \alpha_k)
+            \left\langle 
+                g_k, \frac{\alpha_k\gamma_k}{\gamma_{k + 1}}(v_k - y_k) + (x_k - y_k)
+            \right\rangle. 
+        \end{align*}
+        To assert $\phi_{k + 1}^* \ge F(x_k)$, one set of sufficient conditions are 
+        \begin{align*}
+            \left(
+                \frac{1}{2L} - \frac{\alpha_k^2}{2\gamma_{k + 1}}
+            \right) &\ge 0
+            \\
+            \frac{\alpha_k\gamma_k}{\gamma_{k + 1}}(v_k - y_k) + (x_k - y_k) 
+            &= \mathbf 0. 
+        \end{align*}
+    \end{proof}
 

### 2024-11-12 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
 \section{Introduction}
+    \textcolor{red}{THIS REPORT IS CURRENTLY: UNFINISHED}
+
     Nesterov first proposed the idea of an optimal algorithm named accelerated gradient descent method in his seminal work back in 1983 \cite{nesterov_method_1983}. 
@@
     The definition follows, we define the Nesterov's estimating sequence used to derive the accelerated proximal gradient method. 
-    \begin{definition}[Accelerated proximal gradient estimating sequence]\label{def:nes-est-seq-pg}
+    \begin{definition}[Accelerated proximal gradient estimating sequence]
+    \label{def:nes-est-seq-pg}\;\\
         Define $(\phi_k)_{k \ge0}$ be the Nesterov's estimating sequence recursively given by: 
@@
     Next, we discuss the procedures Guler did to allow the inexact evaluation of proximal method for the accelerated proximal point method. 
+    Right out of the Batch he cited Rockafellar\cite{rockafellar_monotone_1976} on the following conditions for exact evaluations of resolvent on the subgradient of a convex function (Condition (A') in Rockafellar's text):
+    \begin{align*}
+        x_{k + 1}\approx \mathcal J_{\lambda_k} y_k \text{ be such that: }
+        \dist\left(
+            \mathbf 0, \partial \mathcal M_{\lambda_k}(x_{k + 1}; y_k)
+        \right) &\le \frac{\epsilon_k}{\lambda_k}
+        \\
+        \implies 
+        \Vert x_{k + 1} - \mathcal J_{\lambda_k}y_k\Vert 
+        &\le \epsilon_k. 
+    \end{align*}
+    Condition A' also characterize the property of sequence $\epsilon_k$ for convergence of the inexact proximal point method. 
+    Guler strengthens it in his context and proved the following theorem, which we state it using our notations: 
+    \begin{theorem}[Guler's inexact proximal point error bound]
+        Consider defining minimum for the envelope function given by $\mathcal M_k^* := \min_z \mathcal {M}^{\lambda_k}(z; y_k)$. 
+        If $x_{k +1}$ is an inexact evaluation under condition (A'), then the estimating sequence admits the conditions that: 
+        \begin{align*}
+            \frac{1}{2\lambda_k} \Vert x_{k + 1} - \mathcal J_{\lambda_k} y_k\Vert^2
+            &= 
+            \mathcal M^{\lambda_k}(x_{k + 1}, y_k) - \mathcal M^*_k
+            \le \frac{\epsilon_k^2}{2\lambda_k}. 
+        \end{align*}
+    \end{theorem}
+    We now state the major results (Theorem 3.3) of Guler's 1993 papers on inexact accelerated proximal point method. 
+    \begin{theorem}[Guler's accelerated inexact PPM convergence results]
+        If the error sequence $(\epsilon_k)_{k \ge0}$ for condition A' is bounded by $\mathcal O(1/k^\sigma)$ for some $\sigma > 1/2$, then the accelerated proximal point method has for any feasible $x \in \RR^n$:
+        \begin{align*}
+            f(x_k) - f(x) \le \mathcal O(1/k^2) + \mathcal (1 / k^{2\sigma - 1}). 
+        \end{align*}    
+    \end{theorem}
+    The theorem may sound exciting, but as pointed out in Lin 2015 \cite{lin_universal_2015} page 11  that the quantities $\mathcal G_k^*, \mathcal J_{\lambda_k} y_k$ are both intractable. 
+    If we use the inexact formulation from Guler, it would inevitably result in any algorithm whose definition contains the vector $\mathcal J_{\lambda_k} y_k$ exact evaluations of proximal point method.
 
 \section{Lin 2015}
+    This section introduced the setup of Nesterov's estimating sequence in Lin 2015 \cite{lin_universal_2015}. 
+    Right at the beginning we warn the readers about the following: 
+    \begin{enumerate}
+        \item The proofs in HongZhou Lin's original paper of Universal Catalyst is depressingly long and complicated.
+This is a result of using the constructive approach of Nesterov's estimating sequence.
+        \item It's context specific for controlling the errors of inexact proximal point evaluations are being controlled.
+He hinted at the way of controlling and tracking the errors from inexact proximal point evaluations, but it's context specific.
+He only illustrated the use of the meta acceleration on their own method called: ``Proximal MISO", but in general the problem still remains open.
+        \item We will provide proofs to clarify some of their proofs and compare with existing proofs and drawing references in the literatures in the appendix. 
+    \end{enumerate}
+    Let's assume $F$ is a $\mu \ge 0$ strongly convex function. 
+    Throughout this section we make the following notations
+    \begin{align*}
+        \mathcal M^{\kappa^{-1}}(x; y) &:= F(x) + \frac{\kappa}{2}\Vert x - y\Vert^2, 
+        \\
+        \mathcal J_{\kappa^{-1}} y &:= \argmin_x \mathcal M^{\kappa^{-1}} (x, y). 
+    \end{align*}
+    Their algorithm is almost exactly the same as Nesterov's 2.2.20 \cite{nesterov_lectures_2018} which we stated in the definition below: 
+    \begin{definition}[Lin's accelerated proximal point method]
+        Let the initial estimate be $x_0 \in \RR^n$, fix parameters $\kappa$ and $\alpha_0$. 
+        Let $(\epsilon_k)_{k \ge 0}$ be an error sequence chosen for the evaluation for inexact proximal point method. 
+        Initialize $x_0 = y_0$, then the algorithm generates $(x_k, y_k)$ satisfies for all $k \ge 1$
+        \begin{align*}
+            & \text{find } x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1} \text{ such that } \mathcal M^{\kappa^{-1}}(x_k, y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}}y_{k - 1}, y_{k - 1}) \le \epsilon_k
+            \\
+            & \text{find } \alpha_k \in (0, 1) \text{ such that } \alpha_k^2 = (1 - \alpha_k)\alpha_{k - 1}^2 + (\mu/(\mu + \kappa)) 
+            \\
+            & 
+            y_{k} = x_k + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})}{\alpha_{k - 1}^2 + \alpha_k}(x_k - x_{k - 1}). 
+        \end{align*}
+    \end{definition}
+    \begin{remark}
+        The most exciting thing about this algorithm is the similarity it has compares to 
+        \hyperref[def:acc-prox-grad-alg]{Definition \ref*{def:acc-prox-grad-alg}}. 
+        The only difference here is the inclusion of an inexact proximal point step, and the Lipschitz constant $L$ is absent instead it has $\kappa + \mu$.
+
+        Lin 2015 \cite{lin_universal_2015} commented on the second last paragraph on page 4, and here we quote:
+        \par
+        ``The choice of the sequence $(\epsilon_k)_{k \ge 0}$ is also subjected to discussion since the quantity $F(x_0) - F^*$ is unknown beforehand.
+Nevertheless, an upper bound may be used instead, which will only affects the corresponding constant in (7).
+Such an upper bounds can typically be obtained by computing a duality gap at $x_0$, or by using additional knowledge about the objective.
+For instance, when $F$ is non-negative, we may simply choose $\epsilon_k = (2/9)F(x_0)(1 - \rho)^k$".
+
+        This comment has upmost practical importance because it tells us how to bound the error $\epsilon_k$ to achieve accelerated convergence rate. 
+        However, it's still elusive for general in practical applications. 
+        To see how the error is controlled for the inexact proximal point evaluation, we refer the readers to Lemma B.1 in Lin's 2015 paper \cite{lin_universal_2015}. 
+    \end{remark}
+    For theoretical interests, there is a major difference between Lin's approach and Guler's approach. 
+    Lin didn't formulate any of the intractable quantities in the definitions for his Nesterov's estimating sequence $\phi_k$. 
+    One major innovations here is Lemma A.7 in Lin's 2015 paper \cite{lin_universal_2015}.
 
 \section{Non-convex Extension of Catalyst Acceleration}
+    The non-convex extension of Catalyst acceleration by Lin 2018\cite{lin_catalyst_2018} remains similar to the algorithm in the convex case in his 2015 paper \cite{lin_universal_2015}. 
+    The algorithm is now adapted to handle function with unknown weak convexity constant $\rho$ using the process called Auto Adapt subroutine. 
+    There is no accelerated rate for the non-convex case since it's impossible, but the theoretical convergence to stationary point is claimed for the non-convex case.
 
@@
     \begin{theorem}[Fundamental theorem of proximal gradient]
-    \label{thm:fun-thm-prox-grad}
+    \label{app:thm:fun-thm-prox-grad}
         Let $h = f + g$ and proximal gradient operator $T$ be given as in this section. 
@@
     \end{proof}
+    \begin{remark}
+        The quadratic growth with respect to minimizer of the Moreau Envelope is used to derive the inequality, please take caution that this condition is strictly weaker than strong convexity of the Moreau Envelope, which could be made weaker than the strong convexity of $F$.
+        Compare the same theorems in older literatures, this proof doesn't use the subgradient inequality, making it appealing for generalizations outside convexity context. 
+    \end{remark}
 
@@
         \end{align*}
+        Before we finish it, re-arranging should give use the equivalent representations 
+        \begin{align*}
+            -(\alpha_k \gamma_k\alpha_{k + 1}^{-1} + 1)y_k
+            &= 
+            - \alpha_k \gamma_k \gamma_{k + 1}^{-1}v_k - x_k
+            \\
+            y_k &= 
+            \frac{
+                \alpha_k \gamma_k \gamma_{k + 1}^{-1}v_k + x_k
+            }{1 + \alpha_k \gamma_k \gamma_{k + 1}^{-1}}
+            \\
+            & 
+            \textcolor{gray}{
+                \gamma_{k + 1} + \alpha_k \gamma_k 
+                = 
+                \gamma_k + \alpha_k \mu
+            }
+            \\
+            &=  
+            \frac{\alpha_k \gamma_k v_k + \gamma_{k + 1}x_k}{\gamma_k + \alpha_k \mu}. 
+        \end{align*}
+        And $\alpha_k, \gamma_k$, we have the equivalent representation of 
+        \begin{align*}
+            1 - \frac{L \alpha_k^2}{\gamma_{k + 1}}
+            &\ge 0
+            \\
+            1 &\ge L \alpha_k^2 / \gamma_{k + 1}
+            \\
+            \gamma_{k + 1} &\ge L \alpha_k^2
+            \\
+            L\alpha_k^2 
+            &\le
+            \gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \mu \alpha_k. 
+        \end{align*}
     \end{proof}
 
+    \begin{definition}[Nesterov's accelerated proximal gradient raw form]
+    \label{app:def:acc-prox-grad-raw-form}
+        The accelerated proximal gradient algorithm generates vector iterates $x_k, y_k, v_k$ using auxiliary sequence $\alpha_k, \gamma_k$ such that for all $k\ge0$ they satisfy conditions: 
+        \begin{align*}
+            L\alpha_k^2 
+            &\le 
+            (1 - \alpha_k)\gamma_k + \alpha_k\mu = \gamma_{k + 1}; \alpha_k \in (0, 1), 
+            \\
+            y_k &= (\gamma_k + \alpha_k \mu)^{-1}
+            (\alpha_k \gamma_k v_k + \gamma_{k + 1}x_k),
+            \\
+            x_{k + 1}&= 
+            \widetilde{\mathcal J}_{L^{-1}} y_k
+            \\
+            v_{k + 1} &= 
+            \gamma_{k + 1}^{-1}
+            \left(
+                (1 - \alpha_k)\gamma_k v_k + \alpha_k \mu y_k - \alpha_k g_k
+            \right). 
+        \end{align*}
+    \end{definition}
+
+    \begin{theorem}[Intermediate form of accelerated proximal gradient]\label{app:theorem:acc-prox-grad-intermediate}\; \\
+        Let iterates $(x_k, y_k, v_k)$ be given by the raw form of Nesterov's accelerated proximal gradient. 
+        If we assume that $L\alpha_k^2 = \gamma_{k + 1}$, then it simplifies into the following representation without parameter $\gamma_k$: 
+        \begin{align*}
+            y_k &= 
+            \left(
+                1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
+            \right)^{-1}
+            \left(
+                v_k + 
+                \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
+            \right)
+            \\
+            x_{k + 1} &= 
+            y_k - L^{-1}  g_k
+            \\
+            v_{k + 1} &= 
+            \left(
+                1 + \frac{\mu}{L \alpha_k - \mu}
+            \right)^{-1}
+            \left(
+                v_k + 
+                \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
+            \right) - \frac{1}{L\alpha_{k}} g_k
+            \\
+            0 &= \alpha_k^2 - \left(\mu/L - \alpha_{k -1}^2\right) \alpha_k - \alpha_{k - 1}^2. 
+        \end{align*}
+        Here we have $g_k = \widetilde{\mathcal G}_{L^{-1}}y_k$. 
+    \end{theorem}
+    \begin{proof}
+
+        From definition,  we have equality: $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$, so $\gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$, with that in mind we can simplify the expression for $y_k$ by
+        \begin{align*}
+            y_{k} &= 
+            (\gamma_k + \alpha_k \mu)^{-1}
+            (\alpha_k \gamma_k v_k + \gamma_{k + 1}x_k)
+            \\
+            &= 
+            (\gamma_{k + 1} + \alpha_k \gamma_k)^{-1}
+            (\alpha_k \gamma_k v_k + \gamma_{k + 1}x_k)
+            \\
+            &= 
+            \left(
+                \frac{\gamma_{k + 1}}{\alpha_k\gamma_k} + 1
+            \right)^{-1}
+            \left(
+                v_k + \frac{\gamma_{k + 1}}{\alpha_k \gamma_k} x_k
+            \right)
+            \\
+            &= 
+            \left(
+                1 + \frac{L\alpha_k^2}{\alpha_kL\alpha_{k - 1}^2} 
+            \right)^{-1}
+            \left(
+                v_k + \frac{L\alpha_k^2}{\alpha_k L\alpha_{k - 1}^2} x_k
+            \right)
+            \\
+            &= 
+            \left(
+                1 + \frac{\alpha_k}{\alpha_{k - 1}^2}
+            \right)^{-1}
+            \left(
+                v_k + 
+                \frac{\alpha_k}{\alpha_{k - 1}^2} x_k
+            \right). 
+        \end{align*}
+        For $v_{k + 1}$ we use $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \mu \alpha_k$ which gives us: 
+        \begin{align*}
+            v_{k + 1} &= 
+            \gamma_{k + 1}^{-1}
+            ((1 - \alpha_k)\gamma_k v_k + \mu\alpha_k y_k)
+            - \alpha_k\gamma_{k + 1}^{-1}\mathcal L y_k
+            \\
+            &= 
+            ((1 - \alpha_k)\gamma_k + \alpha_k \mu)^{-1}
+            \left(
+                (1 - \alpha_k)\gamma_k v_k + \mu\alpha_k y_k
+            \right)
+            - \alpha_k\gamma_{k + 1}^{-1}\mathcal G_L y_k
+            \\
+            &= 
+            \left(
+                1 + \frac{\alpha_k\mu}{(1 - \alpha_k)\gamma_k}
+            \right)^{-1}
+            \left(
+                v_k + 
+                \frac{\alpha_k\mu}{(1 - \alpha_k)\gamma_k} y_k
+            \right)
+            - \alpha_k\gamma_{k + 1}^{-1}\mathcal G_L y_k
+            \\
+            &= 
+            \left(
+                1 + \frac{\alpha_k\mu}{(1 -\alpha_k)L\alpha_{k - 1}^2}
+            \right)^{-1}
+            \left(
+                v_k + 
+                \frac{\alpha_k\mu}{(1 - \alpha_k)L\alpha_{k - 1}^2} y_k
+            \right)
+            - \frac{1}{L\alpha_{k}}\mathcal G_L y_k
+        \end{align*}
+        We can eliminate the $\gamma_k$ which defines the $\alpha_k$ by considering 
+        \begin{align*}
+            L\alpha_k^2 &= 
+            (1 - \alpha_k)\gamma_k + \alpha_k \mu 
+            \\
+            &= 
+            (1 - \alpha_k)L\alpha_{k - 1}^2 
+            + \alpha_k \mu
+            \\
+            L\alpha_k^2 &= 
+            L \alpha_{k - 1}^2 + 
+            (\mu - L \alpha_{k - 1}^2)\alpha_k
+            \\
+            \iff     
+            0
+            &=  
+            L \alpha_k^2 - (\mu - L \alpha_{k - 1}^2)\alpha_k 
+            - L \alpha_{k -1}^2. 
+        \end{align*}
+        Next, we simplify the coefficients using the above relations further. 
+        From the above results we have the relation $(1 - \alpha_k)L\alpha_{k - 1}^2 = L \alpha_k^2 - \alpha_k \mu$. 
+        Therefore,  it gives 
+        \begin{align*}
+            \frac{\alpha_k\mu}{(1 - \alpha_k)L \alpha_{k - 1}^2}
+            &= 
+            \frac{\alpha_k\mu}{L \alpha_k^2 - \alpha_k \mu}
+            = \frac{\mu}{L \alpha_k - \mu}. 
+        \end{align*}
+        Next we have: 
+        \begin{align*}
+            L\alpha_k^2 &= 
+            (1 - \alpha_k)L\alpha_{k - 1}^2 + \alpha_k \mu 
+            \\
+            L \alpha_k^2 - \alpha_k\mu &= 
+            (1 - \alpha_k)L \alpha_{k - 1}^2
+            \\
+            \alpha_{k - 1}^2
+            &= 
+            \frac{L \alpha_k^2 - \alpha_k\mu}{L (1 - \alpha_k)}
+            \\
+            \frac{1}{\alpha_{k - 1}^2}
+            &= 
+            \frac{L (1 - \alpha_k)}{L \alpha_k^2 - \alpha_k\mu}
+            \\
+            \frac{\alpha_k}{\alpha_{k - 1}^2}
+            &= 
+            \frac{L - L\alpha_k}{L\alpha_k - \mu}. 
+        \end{align*}
+        Substitute these results back to the expression for $y_k, v_{k + 1}$, it gives what we want.
+
+    \end{proof}
+    \begin{remark}
+        This intermediate form representation of the algorithm eliminated the sequence $(\gamma_k)_{k \ge0}$ which were used for the Nesterov's estimating sequence. 
+    \end{remark}
+
+    \begin{theorem}[Nesterov's accelerated proximal gradient momentum form]
+        \; \\
+        Let the sequence $\alpha_k$, and vectors $y_k, x_k, v_k$ be given by the intermediate form of the Nesterov's accelerated proximal gradient, then it can be simplified to void of $v_k$. 
+        The algorithm generates $y_k, x_k, \alpha_k$ such that it satisfies for all $k \ge 0$: 
+        \begin{align*}
+            & \text{find } \alpha_{k + 1} \text{ such that: }L \alpha_{k + 1}^2 = (1 - \alpha_{k + 1})L \alpha_{k - 1} + \mu \alpha_{k + 1}
+            \\
+            & x_{k + 1} = \widetilde {\mathcal J}_{L^{-1}} y_k
+            \\
+            & y_{k + 1} = \frac{\alpha_k(1 - \alpha_k)}{\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
+        \end{align*}
+        Initially we choose $x_0 = y_0, \alpha_0 \in (0, 1)$. 
+    \end{theorem}
+    \begin{proof}
+
+    \end{proof}
+
+\section{Proofs for accelerated PPM}
+
+\section{Proofs for Catalyst Meta Acceleration}
+
+\section{Proofs for 4WD Catalyst Acceleration}
+
 \end{document}

### 2024-11-12 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes and new results

@@
         \fontfamily{ptm}\selectfont 
-        Catalyst Meta Acceleration Framework: The Gist of its Theories
+        Catalyst Meta Acceleration Framework: The history and the gist of it
     }
@@
 
-\noindent{\bfseries 2010 Mathematics Subject Classification:}
-Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
-\noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method.
+% \noindent{\bfseries 2010 Mathematics Subject Classification:}
+% Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
+% \noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method.
 
@@
         \dist(\partial\mathcal{M}^{\lambda}(\tilde x; y))
-        \le \frac{\epsilon}{\lambda}
+        \le \frac{\epsilon}{\lambda}. 
     \end{align*}
@@
     \subsection{Contributions}
-        The writing is expository and won't contain major results. 
+        The writing is expository and comprehensive. 
         We reviewed the literatures and faithfully reproduced some claims, in addition we give insights into understanding the claim in relations to other papers and foundational ideas in optimization.
+        Three papers by Guler \cite{guler_new_1992} and Lin \cite{lin_universal_2015} and Paquette et al.
+\cite{lin_catalyst_2018} together with Nesterov's \cite{nesterov_lectures_2018} method of estimating sequence which is introduced in his book will be covered in detail for this report.
+
+        We only cover innovations in the theoretical aspect of Catalyst Acceleration. 
+        Detailed applications and specific examples will be out of the scope of this paper simply because there will be too many and requires a comprehensive understanding on a different collection of papers.
 
@@
     The theorem may sound exciting, but as pointed out in Lin 2015 \cite{lin_universal_2015} page 11  that the quantities $\mathcal G_k^*, \mathcal J_{\lambda_k} y_k$ are both intractable. 
+    In Guler's work, these intractable quantities were built into the Nesterov's estimating sequence which means it impossible to control how $\epsilon_k \rightarrow 0$. 
     If we use the inexact formulation from Guler, it would inevitably result in any algorithm whose definition contains the vector $\mathcal J_{\lambda_k} y_k$ exact evaluations of proximal point method.
@@
         The only difference here is the inclusion of an inexact proximal point step, and the Lipschitz constant $L$ is absent instead it has $\kappa + \mu$. 
-
+        Evaluating $x_k \approx \mathcal J_{\kappa^{-1}}y_{k - 1}$ is also possible because the function $\mathcal M^{\kappa^{-1}}(\cdot, y_{k - 1})$ is strongly convex, hence its optimality gap can be bounded via trackable quantity $\partial \mathcal M^{\kappa^{-1}}(x_k, y_{k - 1})$.
+
+        Controlling the error sequence $\epsilon_k$ however is a whole new business. 
         Lin 2015 \cite{lin_universal_2015} commented on the second last paragraph on page 4, and here we quote:
@@
         This comment has upmost practical importance because it tells us how to bound the error $\epsilon_k$ to achieve accelerated convergence rate. 
-        However, it's still elusive for general in practical applications. 
+        In theory, $\epsilon_k$ decreases at a rate related to $F(x_0) - F^*$. 
+        It requires some knowledge about $F^*$ in prior. 
+        Therefore, controlling $\epsilon_k$ is still elusive in general in a practical context. 
         To see how the error is controlled for the inexact proximal point evaluation, we refer the readers to Lemma B.1 in Lin's 2015 paper \cite{lin_universal_2015}. 
@@
     Lin didn't formulate any of the intractable quantities in the definitions for his Nesterov's estimating sequence $\phi_k$. 
-    One major innovations here is Lemma A.7 in Lin's 2015 paper \cite{lin_universal_2015}.
+    One major innovation is Lemma A.7 in Lin's 2015 paper \cite{lin_universal_2015}. 
+    The lemma allows the analysis Nesterov's estimating sequence to be carried through without using intractable quantities: $\mathcal M^{\kappa^{-1}}(\mathcal J_{k^{-1}}y_{k - 1}, y_{k - 1}), \mathcal J_{\kappa^{-1}}y_{k - 1}$.
 
 \section{Non-convex Extension of Catalyst Acceleration}
-    The non-convex extension of Catalyst acceleration by Lin 2018\cite{lin_catalyst_2018} remains similar to the algorithm in the convex case in his 2015 paper \cite{lin_universal_2015}. 
+    The non-convex extension of Catalyst acceleration by Lin 2018 \cite{lin_catalyst_2018} remains similar to the algorithm in the convex case in his 2015 paper \cite{lin_universal_2015}. 
     The algorithm is now adapted to handle function with unknown weak convexity constant $\rho$ using the process called Auto Adapt subroutine. 

### 2024-11-12 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
 
-    Nesterov first proposed the idea of an optimal algorithm named accelerated gradient descent method in his seminal work back in 1983 \cite{nesterov_method_1983}. 
-    It was seminal at the time because the algorithm's upper bound on the iteration complexity sealed the gap between the lower bound for all first order Lipschitz smooth convex function and the upper bound for this class of functions.
-    For a specific definition of the class of algorithms that are considered ``First Order'', we refer reader to Chapter 2 of Nesterov's new book \cite{nesterov_lectures_2018} for more information. 
-    In brief the method of gradient descent has an upper bound of $\mathcal O(1/k)$ in iteration complexity. 
-    It doesn't achieve the $\mathcal O(1/k^2)$ lower iteration complexity bound for first order optimization algorithms.
-    The method of accelerated gradient descent has an upper bound of $\mathcal O(1/k^2)$, making it optimal.
+    The optimal algorithm named accelerated gradient descent method is proposed in Nesterov's seminal work back in 1983 \cite{nesterov_method_1983}. 
+    The algorithm closed the upper bound and lower bound on the iteration complexity for all first order Lipschitz smooth convex function among all first order algorithms. 
+    For a specific definition first order method, we refer reader to Chapter 2 of Nesterov's new book \cite{nesterov_lectures_2018} for more information. 
+    Gradient descent has an upper bound of $\mathcal O(1/k)$ in iteration complexity that is slower than
+    the lower iteration complexity $\mathcal O(1/k^2)$. 
+    Accelerated gradient descent has an upper bound of $\mathcal O(1/k^2)$, making it optimal.
 
@@
     \begin{observation}
-        One key component of the Nesterov's estimating sequence is the use of the proximal gradient inequality: $l_F(x; y_k) + \mu/2\Vert x - y_k\Vert^2$. 
-        In the convex case the function has the property $l_F(\cdot, y) \le F(\cdot)$ for all $y$. 
-        More precisely, if $f \equiv 0$ then $\widetilde{\mathcal J}_{L^{-1}}y_k$ becomes resolvent $(I + L^{-1}\partial F)^{-1}$, which makes $x_k$ being an exact evaluation of PPM.
-        And we have 
+        Fix any $y$, for all $x\in \RR^n$, $F(x) \ge l_F(x; y_k) + \mu/2\Vert x - y_k\Vert^2$ is the proximal gradient inequality. 
+        If $f \equiv 0$ then $\widetilde{\mathcal J}_{L^{-1}}y_k$ becomes resolvent $(I + L^{-1}\partial F)^{-1}$, which makes $x_k$ being an exact evaluation of PPM: 
         \begin{align*}
@@
         \end{align*}
-        This is the proximal inequality. 
-        Observe that the inequality with proximal gradient term can be interpreted as an example of inexact evaluation of the PPM and the inequality. 
+        This is the proximal inequality with constant a step size: $L^{-1}$. 
     \end{observation}
@@
     The non-convex extension of Catalyst acceleration by Lin 2018 \cite{lin_catalyst_2018} remains similar to the algorithm in the convex case in his 2015 paper \cite{lin_universal_2015}. 
-    The algorithm is now adapted to handle function with unknown weak convexity constant $\rho$ using the process called Auto Adapt subroutine. 
-    There is no accelerated rate for the non-convex case since it's impossible, but the theoretical convergence to stationary point is claimed for the non-convex case.
+    The new algorithm handles function with unknown weak convexity constant $\rho$ using the process called Auto Adapt subroutine. 
+    For the weakly convex case, only theoretical convergence to stationary point is claimed. 
+    \par 
+    Fixed the parameter $\kappa$ and throughout the section, we use the following notations: 
+    \begin{align*}
+       & \mathcal M (x; y) := F(x) + \frac{\kappa}{2}\Vert x - y\Vert^2 
+       \\
+       & \mathcal J y := \argmin_x \mathcal M (x; y). 
+    \end{align*}
+    We define the algorithm and then its convergence claim below. 
+    \begin{definition}[Basic 4WD Catalyst Algorithm]
+        Find any $x_0 \in \text{dom}(F)$. 
+        Initialize the algorithm with $\alpha_1 = 1, v_0 = x_0$. 
+        For $k \ge 1$, the iterates $(x_k, y_k, v_k)$ are generated by the procedures: 
+        \begin{align*}
+            &
+            \text{find } \bar x_k \approx \argmin{x}\left\lbrace
+                \mathcal M(x; x_{k - 1})
+            \right\rbrace
+            \text{ such that:  }
+                \left\lbrace
+                    \begin{aligned}
+                        & \text{dist}(\mathbf 0, \partial \mathcal M(\bar x_k; x_{k - 1})) 
+                        \le 
+                        \kappa\Vert \bar x_k - x_{k - 1}\Vert, 
+                        \\
+                        & \mathcal M(\bar x_k; x_{k - 1}) 
+                        \le F(x_{k - 1}). 
+                    \end{aligned}
+                \right.
+            \\
+            & y_k = \alpha_k v_{k - 1} + (1 - \alpha_k) x_{k - 1};
+            \\
+            & 
+            \text{find }\tilde x_k \approx \argmin{x} \left\lbrace
+                \mathcal M(x; y_k) 
+                : 
+                \text{dist}\left(
+                \mathbf 0, \partial \mathcal M(\tilde x_k; y_k)
+                \right) 
+                \le \frac{\kappa}{k + 1}\Vert \tilde x_k - y_k\Vert
+            \right\rbrace;
+            \\
+            & v_{k} = x_{k - 1} + \frac{1}{\alpha_k}(\tilde x_k - x_{k - 1});
+            \\
+            & 
+            \text{find } \alpha_{k + 1} \in (0, 1): 
+            \frac{1 - \alpha_{k + 1}}{\alpha_{k + 1}^2} = \frac{1}{\alpha_k^2};
+            \\
+            & \text{choose } x_k \text{ such that:  } f(x_k) = \min(f(\bar x_k), f(\tilde x_k)). 
+        \end{align*}
+    \end{definition}
+
+    \begin{theorem}[Basic 4WD Catalyst Convergence]
+        Let $(x_k, v_k, y_k)$ be generated by the basic Catalyst algorithm. 
+        If $F$ is weakly convex and bounded below, then $x_k$ converges to a stationary point where
+        \begin{align*}
+            \min_{j = 1, \cdots, N} \dist^2(\mathbf 0, \partial F(\bar x_j))
+            \le \frac{8 \kappa}{N}(F(x_0) - F^*). 
+        \end{align*}
+        And when $F$ is convex, $F(x_k) - F^*$ converges at a rate of $\mathcal O(k^{-2})$. 
+    \end{theorem}
+    \begin{remark}
+
+    \end{remark}
 

### 2024-11-12 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
 
-    On first judgement, it's tempting to think that the existence of this optimal algorithm sealed the ceiling for the theoretical development for the entire class of convex first-order smooth optimization.
-    The judgement is correct but lacks the nuance in understanding. 
-    The missing piece here is the fact that Nesterov's accelerated gradient is a system of analysis technique instead of any specific design patterns in algorithms.
-
-    To demonstrate, the introduction of Guler's works in 1993 \cite{guler_new_1992} proposed an accelerated scheme using the technique of Nesterov's estimating sequence for Proximal Point Method (PPM) in the convex case.
-    Let $(\lambda_k)_{k \ge 0}$ be the sequence of scalars used for regularizing the proximal point method which generates sequence $(x_k)_{k\ge 0}$ given any initial guess $x_0$. 
-    Guler's prior work \cite{guler_convergence_1991} showed that convergence of PPM method in the convex case has $\mathcal O\left(1/\sum^{n}_{i = 1}\lambda_i\right)$. 
-    His new algorithm using the technique introduced in Nesterov's accelerated gradient achieves a convergence rate of $\mathcal O\left(1/(\sum_{i = 1}^{n} \sqrt{\lambda_i})^2\right)$. 
-    In addition, he also proposed together an inexact Accelerated PPM method using conditions described in Rockafellar's works in 1976 \cite{rockafellar_monotone_1976}.
-
-    One would be tempting to conclude that this has sealed the ceiling for research on the topic of extending Nesterov's acceleration. 
-    That is indeed correct, but not from a practical point of view. 
+    It's tempting to believe that the existence of an optimal algorithm sealed the ceiling for the need of theories for convex first-order smooth optimization. 
+    It is correct but lacks the nuance in understanding because Nesterov's accelerated gradient is a system of analysis techniques which is not a specific design paradigm for algorithms.
+
+    Guler's accelerated Proximal Point Method(PPM) \cite{guler_new_1992} in 1993 used the technique of Nesterov's estimating sequence to accelerated PPM when the objective is convex. 
+    The algorithm uses $(\lambda_k)_{k \ge 0}$ in the PPM to generate $(x_k)_{k\ge 0}$ given any initial guess $x_0$.
+    Guler's prior work \cite{guler_convergence_1991} showed the convergence of PPM method in the convex without acceleration has convergence $\mathcal O\left(1/\sum^{n}_{i = 1}\lambda_i\right)$. 
+    His new algorithm with acceleration has a convergence rate of $\mathcal O\left(1/(\sum_{i = 1}^{n} \sqrt{\lambda_i})^2\right)$. 
+    An inexact Accelerated PPM method using conditions described in Rockafellar's works in 1976 \cite{rockafellar_monotone_1976} is also discussed in the paper.
+
+    It's tempting to conclude that the results has reached the ceiling for extending Nesterov's acceleration. 
+    It is correct, but not from a practical point of view. 
     Let $F: \RR^n \mapsto \RR$ be our objective function, $\mathcal J_\lambda := (I + \lambda \partial F)^{-1}$ and $\mathcal M^{\lambda}(x; y):= F(x) + \frac{1}{2\lambda}\Vert x - y\Vert^2$ then the inexact proximal point considers with error $\epsilon_k$ has the following characterizations of inexactness as put forward by Guler \cite{guler_new_1992}:
@@
         & 
-        \dist(\partial\mathcal{M}^{\lambda}(\tilde x; y))
+        \dist(\mathbf 0, \partial\mathcal{M}^{\lambda}(\tilde x; y))
         \le \frac{\epsilon}{\lambda}. 
     \end{align*}
-    However, this is troublesome because if we need to approximate the resolvent operator $\mathcal J_\lambda$, then it's probably difficult to compute the subgradient $\partial\mathcal M(\cdot; y)$, which make it difficult to know when we achieved the required exactness for a PPM evaluation.
-    Otherwise, if we already know the subgradient well, then why approximate it in the first place?
+    The difficulty comes from controlling the error $\epsilon$ at each iteration so that the overall convergence of accelerated PPM achieves optimal convergence rate. 
+    However, in the paper $\epsilon_k \rightarrow 0$, but in a specific rate. 
+    It requires knowledge about exact minimum of the Moreau envelope at each step and the optimal value of the Nesterov's estimating sequence. 
+    These quantities are intractable in practice.
 
     Introduced in Lin et al.
-\cite{lin_universal_2015}\cite{lin_catalyst_2018} is a series of papers on a concrete meta algorithm called Catalyst (It's called 4WD Catalyst for the non-convex extension in works by Paquette, Lin et al.
+\cite{lin_universal_2015}\cite{lin_catalyst_2018} is a series of papers describing a concrete meta algorithm called Catalyst (It's called 4WD Catalyst for the non-convex extension in works by Paquette, Lin et al.
 \cite{paquette_catalyst_2018}).
-    It's called a meta algorithm because it uses other first order algorithm to evaluate inexact proximal point method and then performs the accelerated PPM using Nesterov's acceleration. 
-    Their innovations are tracking and controlling the errors made in the inexact PPM throughout the algorithm and some original example usages of the Catalyst framework.
-
-    One would be tempting to assert that this has sealed the ceiling for both theories and practice of Nesterov's acceleration hence it must be the center of discussion in this report. 
-    The conclusion is indeed correct which it will happen in the sections that follow while the assertion remains open.
+    A meta algorithm because uses other first order algorithms to evaluate inexact proximal point method and then performs accelerated PPM based on the outputs of other algorithms. 
+    The innovations here are tracking and controlling the errors made in the inexact PPM throughout the algorithm and an algorithm called Proximal MISO.
 
     \subsection{Contributions}
-        The writing is expository and comprehensive. 
-        We reviewed the literatures and faithfully reproduced some claims, in addition we give insights into understanding the claim in relations to other papers and foundational ideas in optimization.
+        The writing is expository and comprehensive, it will survey the history and major results, and innovations involved in conceiving and designing the Catalyst algorithm. 
+        We reviewed the literatures and faithfully reproduced important claims.
+        In addition, we give insights and context to understand the claims in these papers and making connections to ideas in optimization. 
         Three papers by Guler \cite{guler_new_1992} and Lin \cite{lin_universal_2015} and Paquette et al.
-\cite{lin_catalyst_2018} together with Nesterov's \cite{nesterov_lectures_2018} method of estimating sequence which is introduced in his book will be covered in detail for this report.
-
-        We only cover innovations in the theoretical aspect of Catalyst Acceleration. 
-        Detailed applications and specific examples will be out of the scope of this paper simply because there will be too many and requires a comprehensive understanding on a different collection of papers.
+\cite{lin_catalyst_2018} together with Nesterov's \cite{nesterov_lectures_2018} method of estimating sequence are the targets of this report.
+
+        We will only cover innovations in the theoretical aspect of Catalyst Acceleration. 
+        Applications and specific example algorithms are out of the scope because there are too many papers on the separate topic of variance reduced stochastic algorithms.
 
 \section{Preliminaries}\label{sec:preliminaries}
-    Throughout the entire writing, let our ambient space is $\RR^n$. 
-    We assume the optimization problem of: 
+    Throughout the writing, let the ambient space is $\RR^n$. 
+    The optimization problem is
     \begin{align*}
@@
     \end{align*}
-    In this section we introduce the idea of Nesterov's estimating sequence. 
-    Nesterov's estimating sequence is fundamental to works in Guler's accelerated PPM method, and Catalyst meta acceleration as a whole. 
+    This section introduces the Nesterov's estimating sequence technique. 
+    This technique is fundamental for in Guler's accelerated PPM method and Catalyst meta acceleration in the convex/strongly convex case. 
     \subsection{Method of Nesterov's Estimating Sequence}
@@
             \end{align*}
-            The function $\Delta_k(x)$ is non-negative specifically at the points: $x_*, x_k$.
-            Additionally, we can derive the convergence rate of $\Delta_k(x^*)$ because $\forall x \in \RR^n$: 
+            The function $\Delta_k(x)$ is non-negative at points: $x_*, x_k$.
+            We can derive the convergence rate of $\Delta_k(x^*)$ because $\forall x \in \RR^n$: 
             \begin{align*}
@@
             $$ 
-            Therefore, it yields a convergence of the sequence $f(x_k)\rightarrow f(x^*)$ with a rate relates to sequence $(\alpha_k)_{k \in \N}$. 
         \end{observation}
-        Much of the analysis of convergence Nesterov's type accelerated gradient method inherit the idea of Nesterov's estimating sequence. 
-        Such a proof won't result in simple proof because the construction of $\phi_k$ is non-trivial, but it comes with the advantage too because we can put creativity into the construction of the estimating sequence $(\phi_k)_{k \ge 0}$.
+        Creativity is important in the construction of the estimating sequence $(\phi_k)_{k \ge 0}$.
 
@@
     This section swiftly exposes the constructions of the Nesterov's estimating sequence for the FISTA algorithm by Beck\cite{beck_fast_2009-1}, which is specific case of Algorithm (2.2.63), in Nesterov's book \cite{nesterov_lectures_2018}.
-    Discussion on these algorithms are relevant because they share the same format as the Catalyst Acceleration framework and accelerated PPM.
+    The accelerated proximal gradient algorithm has very similar formulation as the Catalyst Acceleration framework and accelerated PPM. 
+    Additionally, the estimating sequence can derive the algorithm and verify the convergence.
 
@@
         \end{align*}
-        And the sequence of vector $y_k, x_k$, and scalars $\alpha_k$ satisfies the following: 
+        The Algorithm generates a sequence of vectors $y_k, x_k$, and scalars $\alpha_k$ satisfies the following: 
         \begin{align*}
@@
     \end{remark}
-    \begin{definition}[Accelerated proixmal gradient algorithm]\label{def:acc-prox-grad-alg}
-        The algorithm of accelerated proximal gradient generates sequence of iterates $(x_k, y_k)_{k \ge 0}$ which satisfies for all $k\ge 0$: 
-        \begin{align*}
-            &x_{k + 1} = \widetilde{\mathcal J}_{L^{-1}} y_k, 
-            \\
-            & \text{find } \alpha_{k + 1} \in (0, 1)
-            \alpha_{k + 1} = (1 - \alpha_{k + 1})\alpha_k^{2} + (\mu/L) \alpha_{k + 1}
-            \\
-            &y_{k + 1} = x_{k + 1} + \frac{\alpha_k(1 - \alpha_k)}{\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
-        \end{align*}
-
-    \end{definition}
-    \begin{remark}
-        The simple case of accelerated gradient descent is stated as (2.2.63) in Nesterov's book \cite{nesterov_lectures_2018}. 
-    \end{remark}
-    For a proof that proves 
-    \hyperref[def:nes-est-seq-pg]{Definition \ref*{def:nes-est-seq-pg}}
-    is an estimating sequence, and 
-    \hyperref[def:acc-prox-grad-alg]{Definition \ref{def:acc-prox-grad-alg}}
-    is the accelerated proximal gradient algorithm, please visit 
+    % \begin{definition}[Accelerated proixmal gradient algorithm]\label{def:acc-prox-grad-alg}
+    %     The algorithm of accelerated proximal gradient generates sequence of iterates $(x_k, y_k)_{k \ge 0}$ which satisfies for all $k\ge 0$: 
+    %     \begin{align*}
+    %         &x_{k + 1} = \widetilde{\mathcal J}_{L^{-1}} y_k, 
+    %         \\
+    %         & \text{find } \alpha_{k + 1} \in (0, 1)
+    %         \alpha_{k + 1} = (1 - \alpha_{k + 1})\alpha_k^{2} + (\mu/L) \alpha_{k + 1}
+    %         \\
+    %         &y_{k + 1} = x_{k + 1} + \frac{\alpha_k(1 - \alpha_k)}{\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
+    %     \end{align*}
+
+    % \end{definition}
+    % \begin{remark}
+    %     The simple case of accelerated gradient descent is stated as (2.2.63) in Nesterov's book \cite{nesterov_lectures_2018}. 
+    % \end{remark}
+    For a proof for the Nesterov's estimating sequence $\phi_k$ and a derivation of the algorithm, see
     \hyperref[app:sec:thm-claim-acc-prox-grad]{Appendix \ref*{app:sec:thm-claim-acc-prox-grad}}. 
@@
     \end{remark}
-    Next, we discuss the procedures Guler did to allow the inexact evaluation of proximal method for the accelerated proximal point method. 
-    Right out of the Batch he cited Rockafellar\cite{rockafellar_monotone_1976} on the following conditions for exact evaluations of resolvent on the subgradient of a convex function (Condition (A') in Rockafellar's text):
+    To handle the inexact evaluation of the PPM, Guler cited Rockafellar \cite{rockafellar_monotone_1976} for condition (A') in his text which is the following: 
     \begin{align*}
@@
     \end{align*}
-    Condition A' also characterize the property of sequence $\epsilon_k$ for convergence of the inexact proximal point method. 
-    Guler strengthens it in his context and proved the following theorem, which we state it using our notations: 
+    Condition A' also characterizes the property of $(\epsilon_k)_{k\ge 0}$ so inexact PPM converges. 
+    Guler strengthens it in his context and proved the following: 
     \begin{theorem}[Guler's inexact proximal point error bound]
@@
     \end{theorem}
-    We now state the major results (Theorem 3.3) of Guler's 1993 papers on inexact accelerated proximal point method. 
+    The next theorem is Theorem 3.3 of Guler's 1993 papers which is a major result for inexact accelerated PPM method. 
     \begin{theorem}[Guler's accelerated inexact PPM convergence results]
@@
     \end{theorem}
-    The theorem may sound exciting, but as pointed out in Lin 2015 \cite{lin_universal_2015} page 11  that the quantities $\mathcal G_k^*, \mathcal J_{\lambda_k} y_k$ are both intractable. 
-    In Guler's work, these intractable quantities were built into the Nesterov's estimating sequence which means it impossible to control how $\epsilon_k \rightarrow 0$. 
-    If we use the inexact formulation from Guler, it would inevitably result in any algorithm whose definition contains the vector $\mathcal J_{\lambda_k} y_k$ exact evaluations of proximal point method.
+    The theorem looks exciting, but Lin 2015 \cite{lin_universal_2015} page 11 pointed out that $\mathcal G_k^*, \mathcal J_{\lambda_k} y_k$ are both intractable quantities. 
+    In Guler's work, these intractable quantities were built into the Nesterov's estimating sequence making it unclear how to control $\epsilon_k \rightarrow 0$. 
+    If we use the inexact formulation from Guler and his estimating sequence, it will result in algorithm that contains intractable quantities $\mathcal J_{\lambda_k} y_k$.
 
@@
 \section{Non-convex Extension of Catalyst Acceleration}
-    The non-convex extension of Catalyst acceleration by Lin 2018 \cite{lin_catalyst_2018} remains similar to the algorithm in the convex case in his 2015 paper \cite{lin_universal_2015}. 
-    The new algorithm handles function with unknown weak convexity constant $\rho$ using the process called Auto Adapt subroutine. 
-    For the weakly convex case, only theoretical convergence to stationary point is claimed. 
+    The non-convex extension of Catalyst acceleration by Lin 2018 \cite{lin_catalyst_2018} is similar to the convex case in his 2015 paper \cite{lin_universal_2015}. 
+    The new algorithm handles function with unknown weak convexity constant $\rho$ using a process called Auto Adapt subroutine. 
+    They only claimed convergence to stationary point is claimed for the weakly convex objective. 
     \par 

### 2024-11-12 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, syncing

@@
                 \Delta_k(x) 
-                &= \phi_k(x) - f(x) \ge \phi_k^* - f(x)
+                &= \phi_k(x) - F(x) \ge \phi_k^* - F(x)
                 \\
@@
                 &\ge 
-                \phi_k^* - f(x_k) \ge 0
+                \phi_k^* - F(x_k) \ge 0
                 \\
@@
                 \Delta_k(x_*)
-                &\ge \phi_k^* - f_* \ge f(x_k) - f_* \ge 0
+                &\ge \phi_k^* - F_* \ge F(x_k) - F_* \ge 0
             \end{align*}
@@
             $$
-                f(x_k) - f(x^*) \le \phi_k^* - f(x^*) \le \Delta_k(x^*) = \phi_k(x^*) - f(x^*) \le \left(\prod_{i = 0}^k(1 - \alpha_i)\right)\Delta_0(x^*).
+                F(x_k) - F(x^*) \le \phi_k^* - F(x^*) \le \Delta_k(x^*) = \phi_k(x^*) - F(x^*) \le \left(\prod_{i = 0}^k(1 - \alpha_i)\right)\Delta_0(x^*).
             $$ 
@@
             \\
-            & \text{find } \alpha_{k + 1} \in (0, 1)
+            & \text{find } \alpha_{k + 1} \in (0, 1): 
             \alpha_{k + 1} = (1 - \alpha_{k + 1})\alpha_k^{2} + (\mu/L) \alpha_{k + 1}

### 2024-11-13 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes
>w<, syncing stuff

@@
     \begin{align*}
-        x_{k + 1}\approx \mathcal J_{\lambda_k} y_k \text{ be such that: }
+        x_{k + 1}\approx \mathcal J_{k} y_k \text{ be such that: }
         \dist\left(
-            \mathbf 0, \partial \mathcal M_{\lambda_k}(x_{k + 1}; y_k)
-        \right) &\le \frac{\epsilon_k}{\lambda_k}
+            \mathbf 0, \partial \mathcal M^{k}(x_{k + 1}; y_k)
+        \right) &\le \frac{\epsilon_k}{k}
         \\
         \implies 
-        \Vert x_{k + 1} - \mathcal J_{\lambda_k}y_k\Vert 
+        \Vert x_{k + 1} - \mathcal J_{k}y_k\Vert 
         &\le \epsilon_k. 
@@
         \begin{align*}
-            \frac{1}{2\lambda_k} \Vert x_{k + 1} - \mathcal J_{\lambda_k} y_k\Vert^2
-            &= 
-            \mathcal M^{\lambda_k}(x_{k + 1}, y_k) - \mathcal M^*_k
+            \frac{1}{2\lambda_k} \Vert x_{k + 1} - \mathcal J_k y_k\Vert^2
+            &= 
+            \mathcal M_k(x_{k + 1}, y_k) - \mathcal M^*_k
             \le \frac{\epsilon_k^2}{2\lambda_k}. 
@@
 This is a result of using the constructive approach of Nesterov's estimating sequence.
-        \item It's context specific for controlling the errors of inexact proximal point evaluations are being controlled.
-He hinted at the way of controlling and tracking the errors from inexact proximal point evaluations, but it's context specific.
-He only illustrated the use of the meta acceleration on their own method called: ``Proximal MISO", but in general the problem still remains open.
+        \item Controlling the errors of inexact proximal point evaluations is context specific.
+Lin hinted at ways to track the errors from inexact proximal point evaluations such as using duality and non-negativity assumption of the objective.
+He illustrated the use of the meta acceleration on their own method called: ``Proximal MISO", in general there is not a universal solution.
         \item We will provide proofs to clarify some of their proofs and compare with existing proofs and drawing references in the literatures in the appendix. 
@@
     \begin{remark}
-        The most exciting thing about this algorithm is the similarity it has compares to 
-        \hyperref[def:acc-prox-grad-alg]{Definition \ref*{def:acc-prox-grad-alg}}. 
-        The only difference here is the inclusion of an inexact proximal point step, and the Lipschitz constant $L$ is absent instead it has $\kappa + \mu$. 
+        the algorithm very similarity to
+        \hyperref[def:nes-est-seq-pg]{Definition \ref*{def:nes-est-seq-pg}}. 
+        In contrast, it has an inexact proximal point step controlled by $\epsilon_k$, and the Lipschitz constant $L$ is absent instead it has $\kappa + \mu$. 
         Evaluating $x_k \approx \mathcal J_{\kappa^{-1}}y_{k - 1}$ is also possible because the function $\mathcal M^{\kappa^{-1}}(\cdot, y_{k - 1})$ is strongly convex, hence its optimality gap can be bounded via trackable quantity $\partial \mathcal M^{\kappa^{-1}}(x_k, y_{k - 1})$.
@@
     The lemma allows the analysis Nesterov's estimating sequence to be carried through without using intractable quantities: $\mathcal M^{\kappa^{-1}}(\mathcal J_{k^{-1}}y_{k - 1}, y_{k - 1}), \mathcal J_{\kappa^{-1}}y_{k - 1}$.
-
-\section{Non-convex Extension of Catalyst Acceleration}
+    \begin{lemma}[Lin's inexact proximal inequality]
+        Let $F$ be a $\mu\ge 0$ strongly convex.
+        Suppose $x_k$ is an inexact proximal point evaluation of $x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1}$ with $\kappa$ fixed. 
+        Assume the approximation error is haracterized by $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k - 1}, y_{k - 1}) \le \epsilon_k$. 
+        Denote $x_k^* = \mathcal J_{\kappa^{-1}} y_{k - 1}$ to be the exact evaluation of the proximal point then for all $x$: 
+        \begin{align*}
+            F(x) &\ge 
+            F(x_k) + \kappa \langle y_{k - 1} - x_k, x - x_k\rangle
+            + \frac{\mu}{2}\Vert x - x_k\Vert^2 
+            + (\kappa + \mu)\langle  x_k - x_k^*, x - x_k\rangle 
+            - \epsilon_k.
+        \end{align*}
+    \end{lemma}
+    \begin{remark}
+        The lamma plays a key role and it allows Lin to denote his Nesterov's estimating sequence to be for all $k \ge0$: 
+        \begin{align*}
+            \phi_k(x) := 
+            (1 - \alpha_{k - 1})\phi_{k - 1}(x)
+            + \alpha_{k - 1}\left(
+                F(x_k) + \kappa\langle y_{k - 1} - x_k, x - x_k \rangle
+                + \frac{\mu}{2}\Vert x - x_k\Vert^2
+            \right). 
+        \end{align*}
+        It is void of intractable quantities. 
+    \end{remark}
+
+\section{Non-convex extension of Catalyst acceleration}
     The non-convex extension of Catalyst acceleration by Lin 2018 \cite{lin_catalyst_2018} is similar to the convex case in his 2015 paper \cite{lin_universal_2015}. 
@@
     \par 
-    Fixed the parameter $\kappa$ and throughout the section, we use the following notations: 
+    Fix $\kappa$ we use the following notations: 
     \begin{align*}
@@
             &
-            \text{find } \bar x_k \approx \argmin{x}\left\lbrace
+            \text{find } \bar x_k \approx \argmin_{x}\left\lbrace
                 \mathcal M(x; x_{k - 1})
@@
             & 
-            \text{find }\tilde x_k \approx \argmin{x} \left\lbrace
+            \text{find }\tilde x_k \approx \argmin_{x} \left\lbrace
                 \mathcal M(x; y_k) 
@@
         Let $(x_k, v_k, y_k)$ be generated by the basic Catalyst algorithm. 
-        If $F$ is weakly convex and bounded below, then $x_k$ converges to a stationary point where
+        If $F$ is $\kappa$ weakly convex and bounded below, then $x_k$ converges to a stationary point where
         \begin{align*}

### 2024-11-13 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, a lot of changes

@@
     Nesterov's accelerated gradient first appeared back in the 1983 has sparked numerous theoretical and practical advancements in Mathematics programming literatures. 
-    The idea behind Nesterov's acceleration is universal in the convex case it has concrete extension in the non-convex case. 
+    The idea behind Nesterov's acceleration is universal for convex objective and it has concrete extension in the non-convex case. 
     In this paper we survey specifically the Catalyst Acceleration that incorporated ideas from the Accelerated Proximal Point Method proposed by Guler back in 1993. 
@@
             Let $(\phi_k : \RR^n \mapsto \RR)_{k \ge 0}$ be a sequence of functions. 
-            We call this sequence of function a Nesterov's estimating sequence when it satisfies the conditions that: 
+            We call this sequence of function a Nesterov's estimating sequence when it satisfies the conditions: 
             \begin{enumerate}
-                \item There exists another sequence $(x_k)_{k \ge 0}$ such that for all $k \ge 0$ it has $F(x_k) \le \phi_k^*$. 
-                \item There exists a sequence of $(\alpha_k)_{k \ge 0}$ such that for all $x \in \RR^n$, $\phi_{k + 1}(x) - \phi_k(x) \le - \alpha_k(\phi_k(x) - F(x))$. 
+                \item There exists another sequence $(x_k)_{k \ge 0}$ such that for all $k \ge 0$ it has $F(x_k) \le \phi_k^*: =\min_{x}\phi_k^*(x)$. 
+                \item There exists a sequence of $(\alpha_k)_{k \ge 0}$ where $\alpha_k \in (0, 1)\; \forall k \ge0 $ such that for all $x \in \RR^n$ it has $\phi_{k + 1}(x) - \phi_k(x) \le - \alpha_k(\phi_k(x) - F(x))$.
             \end{enumerate}
@@
     Guler strengthens it in his context and proved the following: 
-    \begin{theorem}[Guler's inexact proximal point error bound]
-        Consider defining minimum for the envelope function given by $\mathcal M_k^* := \min_z \mathcal {M}^{\lambda_k}(z; y_k)$. 
-        If $x_{k +1}$ is an inexact evaluation under condition (A'), then the estimating sequence admits the conditions that: 
+    \begin{theorem}[Guler's inexact proximal point error bound]\label{thm:guler-inexact-ppm-bound}
+        \;\\
+        Define Moreau Envelope at $y_k$ as $\mathcal M_k^* := \min_z \mathcal {M}^{\lambda_k}(z; y_k)$. 
+        If $x_{k +1}$ is an inexact evaluation under condition (A'), then the estimating sequence admits the conditions: 
         \begin{align*}
@@
         \begin{align*}
-            f(x_k) - f(x) \le \mathcal O(1/k^2) + \mathcal (1 / k^{2\sigma - 1}). 
-        \end{align*}    
+            f(x_k) - f(x) \le \mathcal O(1/k^2) + \mathcal O (1 / k^{2\sigma - 1})\rightarrow 0. 
+        \end{align*}    
+        When $\sigma \ge 3/2$ then the method converges at a rate of $\mathcal O(1/k^2)$. 
     \end{theorem}
@@
 \section{Lin 2015}
-    This section introduced the setup of Nesterov's estimating sequence in Lin 2015 \cite{lin_universal_2015}. 
-    Right at the beginning we warn the readers about the following: 
+    The section introduces the Nesterov's estimating sequence in Lin 2015 \cite{lin_universal_2015}. 
+    We warn the readers about the followings: 
     \begin{enumerate}
         \item The proofs in HongZhou Lin's original paper of Universal Catalyst is depressingly long and complicated.
-This is a result of using the constructive approach of Nesterov's estimating sequence.
+It is a result of using the constructive approach of Nesterov's estimating sequence.
         \item Controlling the errors of inexact proximal point evaluations is context specific.
-Lin hinted at ways to track the errors from inexact proximal point evaluations such as using duality and non-negativity assumption of the objective.
-He illustrated the use of the meta acceleration on their own method called: ``Proximal MISO", in general there is not a universal solution.
+Lin hinted at ways to track the errors such as using duality and non-negativity assumption of the objective.
+He illustrated the use of the meta acceleration on their own method called: ``Accelerated MISO-Prox", in general there is not a universal solution.
         \item We will provide proofs to clarify some of their proofs and compare with existing proofs and drawing references in the literatures in the appendix. 
@@
     \begin{remark}
-        the algorithm very similarity to
+        The algorithm is similarity to
         \hyperref[def:nes-est-seq-pg]{Definition \ref*{def:nes-est-seq-pg}}. 
@@
 \bibliography{references/refs}
+\newpage
 
@@
             ((1 - \alpha_k)\gamma_k v_k + \mu\alpha_k y_k)
-            - \alpha_k\gamma_{k + 1}^{-1}\mathcal L y_k
+            - \alpha_k\gamma_{k + 1}^{-1}g_k
             \\
@@
             \right)
-            - \alpha_k\gamma_{k + 1}^{-1}\mathcal G_L y_k
+            - \alpha_k\gamma_{k + 1}^{-1} g_k
             \\
@@
             \right)
-            - \frac{1}{L\alpha_{k}}\mathcal G_L y_k
+            - \frac{1}{L\alpha_{k}} g_k
         \end{align*}
@@
     \begin{proof}
-
+        To show that, we write down the intermediate form with new symbols to make it easier to read: 
+        \begin{align*}
+            y_k &= (1 + \tau_k)^{-1}(v_k + \tau_k x_k),
+            \\
+            v_{k + 1} &= (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - (1 + \xi_k)^{-1}\delta_k g_k,
+            \\
+            x_{k + 1} &= y_k - L^{-1} g_k. 
+        \end{align*} 
+        Where for all $k \ge0$: 
+        \begin{align*}
+            \tau_k &= \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}, 
+            \xi_k = \frac{\mu}{L \alpha_k - \mu},
+            \\
+            (1 + \xi_k)^{-1}\delta_k &= \frac{1}{L\alpha_k}
+            \iff L \delta_k = \frac{1 + \xi_k}{\alpha_k}, 
+            \\
+            L\alpha_k^2 &= (1 - \alpha_k)L\alpha_{k - 1}^2 + \mu\alpha_k. 
+        \end{align*}
+        Next, we show that if $L\delta_k = 1 + \xi_k + \tau_k$ then $v_{k + 1} - x_{k + 1} = (1 + \xi_t)^{-1}\tau_t(x_{k + 1} - x_k)$. 
+        \begin{align*}
+            v_{k + 1} &= (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - (1 + \xi_k)^{-1}\delta_k g_k
+            \\
+            &= 
+            (1 + \xi_k)^{-1}((1 + \tau_k)y_k - \tau_k x_k + \xi_k y_k) - (1 + \xi_k)^{-1}\delta_k g_k
+            \\
+            &= 
+            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_k - \tau_k x_k) - (1 + \xi_k)^{-1}\delta_k g_k
+            \\
+            \iff 
+            v_{k + 1} - x_{k + 1} &= 
+            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_k - \tau_k x_k - \delta_k g_k) - y_k + L^{-1}g_k
+            \\
+            &= (1 + \xi_k)^{-1}(\tau_k y_k - \tau_k x_k - \delta_k g_k) + L^{-1}g_k
+            \\
+            &= (1 + \xi_k)^{-1}(\tau_k y_k - \tau_k x_k + (L^{-1}(1 + \xi_k) - \delta_k )g_k)
+            \\
+            &= (1 + \xi_k)^{-1}\tau_k(y_k - x_k + \tau_k^{-1}(L^{-1} + L^{-1}\xi_k - \delta_k )g_k)
+        \end{align*}
+        Next, consider $x_{k + 1} - x_{k}$: 
+        \begin{align*}
+            x_{k + 1} - x_k &= y_k - x_k - L^{-1}g_k. 
+        \end{align*}
+        Observe that, if we substitute $\delta_k = L^{-1}(1 + \xi_k) + L^{-1}\tau_k$, then 
+        \begin{align*}
+            v_{k + 1} - x_{k + 1} &= (1 + \xi_k)^{-1}\tau_k(y_k - x_k + \tau_k^{-1}(-L^{-1}\tau_k)g_k) 
+            \\
+            &= 
+            (1 + \xi_k)^{-1}\tau_k(y_k - x_k - L^{-1}g_k)
+            \\
+            &= (1 + \xi_k)^{-1}\tau_k(x_{k + 1} - x_k). 
+        \end{align*}
+        Next, it remains to verify that $L\delta_k = 1 + \xi_k + \tau_k$ is true. 
+        This is true because by definitions the RHS: 
+        \begin{align*}
+            1 + \tau_k + \xi_k &= 
+            1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
+            + \frac{\mu}{L \alpha_k - \mu}
+            \\
+            &= 
+            1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
+            \\
+            &= 
+            \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
+            \\
+            &= \frac{L}{L\alpha_k - \mu}. 
+        \end{align*}
+        And the LHS: 
+        \begin{align*}
+            \frac{1 + \xi_k}{\alpha_k}
+            &= 
+            \frac{1 + \frac{\mu}{L\alpha_k - \mu}}{\alpha_k}
+            = 
+            \frac{\frac{L\alpha_k - \mu + \mu}{L \alpha_k - \mu}}{\alpha_k}
+            = 
+            \frac{L}{L\alpha_k - \mu}. 
+        \end{align*}
+        They are matched and therefore we substitute $\xi_k, \tau_k$ into $v_{k + 1} = x_{k + 1} + (1 + \xi_k)^{-1}\gamma_k(x_{k + 1} - x_k)$: 
+        \begin{align*}
+            v_{k + 1} &= 
+            x_{k + 1} + \left(
+                1 + \frac{\mu}{L\alpha_k - \mu}
+            \right)^{-1}\left(
+                \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
+            \right)(x_{k + 1} - x_k)
+            \\
+            &= 
+            x_{k + 1} + \left(
+                \frac{L\alpha_k}{L\alpha_k - \mu}
+            \right)^{-1}\left(
+                \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
+            \right)(x_{k + 1} - x_k)
+            \\
+            &= 
+            x_{k + 1} + \left(
+                \frac{L\alpha_k - \mu}{L\alpha_k}
+            \right)\left(
+                \frac{L - L\alpha_k}{L\alpha_k - \mu}
+            \right)(x_{k + 1} - x_k)
+            \\
+            &= x_{k + 1} + \left(
+                \alpha_k^{-1} - 1
+            \right)(x_{k + 1} - x_k).
+        \end{align*}
+        With $v_{k +1}$ rid of $v_k$, the next step is to make $y_{k + 1}$ only using $x_k, x_{k + 1}$. 
+        By definition $y_{k + 1}$ is produced by: 
+        \begin{align*}
+            y_k &= 
+            \left(
+                1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
+            \right)^{-1}
+            \left(
+                v_k + 
+                \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
+            \right)
+            \\
+            &= 
+            \left(
+            \frac{L - \mu}{L\alpha_k - \mu} 
+            \right)^{-1}
+            \left(
+                v_k + 
+                \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
+            \right)
+            \\
+            &= 
+            \frac{L\alpha_k - \mu}{L - \mu} v_k
+            + 
+            \frac{L - L \alpha_k}{L - \mu} x_k. 
+        \end{align*}
+        Increment $k$ into $k + 1$ then 
+        {\footnotesize
+        \begin{align*}
+            v_{k + 1} &= 
+            x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
+            \\
+            (L \alpha_{k + 1} - \mu)v_{k + 1} 
+            &= 
+            (L \alpha_{k + 1} - \mu)x_{k + 1} + (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k), 
+            \\[0.5em]
+            y_{k + 1} &= 
+            (L - \mu)^{-1}((L\alpha_{k + 1} - \mu)v_{k + 1} + (L - L \alpha_{k + 1})x_{k + 1})
+            \\
+            &= (L - \mu)^{-1}
+            \left(
+                (L\alpha_{k + 1} - \mu)x_{k + 1} + 
+                (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
+                + (L - L \alpha_{k + 1})x_{k + 1}
+            \right)
+            \\
+            &= 
+            (L - \mu)^{-1}
+            \left(
+                (L - \mu)x_{k + 1} + (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
+            \right)
+            \\
+            &= x_{k + 1} + \frac{(L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)}{L - \mu}(x_{k + 1} - x_k). 
+        \end{align*}
+        }
+        We are closer than ever to proving it. 
+        This representation contains $L, \mu$ on the momentum coefficients, to get rid of that consider: 
+        \begin{align*}
+            \frac{(L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)}{L - \mu}
+            &= \frac{(L\alpha_{k + 1} - \mu)\alpha_k(1 - \alpha_k)}{\alpha_k^2(L - \mu)}
+            \\
+            &= 
+            \alpha_k(1 - \alpha_k)
+            \left(
+                \frac{\alpha_k^2(L - \mu)}{L\alpha_{k + 1} - \mu}
+            \right)^{-1}
+            \\
+            &= \alpha_k(1 - \alpha_k)
+            \left(
+                \frac{L\alpha_k^2 - \mu\alpha_k^2}{L\alpha_{k + 1} - \mu}
+            \right)^{-1}
+            \\
+            &= 
+            \alpha_k(1 - \alpha_k)
+            \left(
+                \frac{(L\alpha_{k + 1} - \mu)(\alpha_k^2 + \alpha_{k + 1})}
+                {L\alpha_{k + 1} - \mu}
+            \right)^{-1}
+            \\
+            &= \frac{\alpha_k(1 - \alpha_k)}{\alpha_k^2 + \alpha_{k + 1}}. 
+        \end{align*}
+        Here, on the third to the 4th equality, we used $L\alpha_{k + 1}^2 = (1 - \alpha_{k + 1})L\alpha_k^2 + \mu\alpha_{k + 1}$ in this way: 
+        \begin{align*}
+            (L\alpha_{k + 1} - \mu)(\alpha_k^2 + \alpha_{k + 1})
+            &= 
+            L\alpha_{k + 1}\alpha_k^2 - \mu \alpha_k^2 + L \alpha_{k + 1}^2 + \mu\alpha_{k + 1}
+            \\
+            &= 
+            L\alpha_{k + 1}\alpha_k^2 - \mu \alpha_k^2 + (
+                (1 - \alpha_{k + 1})L\alpha_k^2 - \mu\alpha_{k + 1}
+            ) - \mu\alpha_{k + 1}
+            \\
+            &= 
+            L\alpha_k^2 - \mu \alpha_k^2. 
+        \end{align*}
     \end{proof}
+    \begin{remark}
+        This proof is very long because we took a detour to an intermediate form without the $\gamma_k$ that the writer personally prefer more than a direct path. 
+    \end{remark}
 
 \section{Proofs for accelerated PPM}
+    \subsection{Exact accelerated PPM}
+        This setion contains all the proofs for the exact accelerated PPM method. 
+        It follows the same notation from the accelerated PPM section that $F$ is a convex function and the notations are $\mathcal J_k, \mathcal G_k$ for the proximal point evaluation and gradient mapping.
+        Recall the definition of the estimating sequence is: 
+        \begin{align*}
+            \phi_0 &:= f(x_0) + \frac{A}{2}\Vert x - x_0\Vert^2, 
+            \\
+            \phi_{k + 1}(x) &:= 
+            (1 - \alpha_k)\phi_k(x)
+            + 
+            \alpha_k(F(\mathcal J_k y_k) + \langle \mathcal G_k y_k, x - \mathcal J_k y_k\rangle). 
+        \end{align*}
+        Observe $\phi_k$ is a sequence of simple quadratic functions. 
+        We define the canonical representation to be: 
+        \begin{align*}
+            (\forall k \ge 0) \quad 
+            \phi_k(x) &= \phi_k^* + \frac{A_k}{2} \Vert x - v_k\Vert^2. 
+        \end{align*}
+        Subsituting back the cannonical form, we obtained a recursive definition of the Hessian and gradient of the estimating sequence:
+
+        \begin{align*}
+            &
+            \phi_{k+ 1}^* + \frac{A_{k + 1}}{2}\Vert x - v_{k + 1}\Vert^2
+            = 
+            (1 - \alpha_k)
+            \left(\phi_k^* + \frac{A_k}{2}\Vert x - v_k\Vert^2\right)
+            \\ & \hspace{12em}
+                + 
+                \alpha_k(F(\mathcal J_k y_k) + \langle \mathcal G_k y_k, x - \mathcal J_k y_k\rangle)
+            \\
+            \implies 
+            &
+            \left\lbrace
+            \begin{aligned}
+                A_{k + 1} 
+                &= (1 - \alpha_k)A_k, 
+                \\
+                \nabla \phi(x)
+                &= 
+                (1 - \alpha_k)A_k(x - v_k) + \alpha_k \mathcal G_ky_k. 
+            \end{aligned}
+            \right.
+        \end{align*}
+        In the canonical form, $v_{k + 1}$ is the minimizer of $\phi_{k + 1}$, it can be solved for by setting the gradient $\phi_{k + 1}(x)= \mathbf 0$ so for all $k\ge 0$: 
+        \begin{align*}
+            \mathbf 0 &= (1 - \alpha_k)A_k(v_{k + 1} - v_k) + \alpha_k \mathcal G_k y_k
+            \\
+            v_{k + 1} - v_k &= 
+            \frac{\alpha_k}{\lambda_k(1 - \alpha_k)A_k}
+            \left(
+                y_k - \mathcal J_k y_k
+            \right)
+            \\
+            &= \frac{\alpha_k}{\lambda_kA_{k + 1}}
+            \left(
+                y_k - \mathcal J_k y_k
+            \right). 
+        \end{align*}
+        \begin{theorem}[Estimating sequence for accelerated PPM]\label{app:thm:est-seq-acc-ppm}
+            The parameters for the estimating sequence: $(\phi_k^*)_{k\ge 0}, (v_k)_{k\ge 0}, (A_k)_{k\ge 0}$ satisfies for all $k \ge0 $ the following conditions:
+            \begin{align*}
+                A_{k + 1} &= (1 - \alpha_k)A_k, 
+                \\
+                v_{k + 1} - v_k
+                &= 
+                - \frac{\alpha_k}{A_{k + 1}\lambda_k}(y_k - \mathcal J_k y_k), 
+                \\
+                \phi_{k + 1}^*
+                &\ge 
+                F(\mathcal J_ky_k) + 
+                \frac{1}{2\lambda_k}\left(
+                    2 - \frac{\alpha_k^2}{A_{k + 1}\lambda_k}
+                \right)
+                \Vert y_k - \mathcal J_k y_k\Vert^2
+                \\
+                    & \quad 
+                    + 
+                    \lambda_k^{-1}
+                    \langle 
+                        y_k - \mathcal J_k y_k, (1 - \alpha_k)x_k + \alpha_k v_k - y_k
+                    \rangle.
+            \end{align*}
+            Additionally, the sequence $\alpha_k$ has $\forall k \ge0$: 
+            \begin{align*}
+                \alpha_k
+                &= 
+                \frac{1}{2}\left(
+                    \sqrt{(A_k\lambda_k)^2 + 4A_k \lambda_k}
+                    - A_k\lambda_k
+                \right). 
+            \end{align*}
+        \end{theorem}
+        \begin{proof}   
+            Using induction, we assume the inductive hypothesis: $\phi_k^* \ge f(x_k)$ for the sequence $(x_i)_{i \ge 0}$ up to and including $i = k$.
+            Proceed with the inductive hypothesis we have 
+            \begin{align*}
+                \phi_k^* 
+                &\ge F(x_k)
+                \ge F(\mathcal J_k y_k) + \langle \mathcal G_k y_k, x_k - \mathcal J_k y_k\rangle. 
+            \end{align*}
+            We used the proximal inequality of $F$. 
+            Inductively using the definition of the estimating sequence and substitute the canonical form we will have 
+            \begin{align*}
+                \phi_{k + 1}^*
+                &= \phi_{k + 1}(v_{k + 1})
+                \\
+                &= 
+                (1 - \alpha_k) \phi_k(v_{k + 1})
+                + \alpha_kF(\mathcal J_k y_k)
+                + \alpha_k\lambda_k^{-1}\langle 
+                    y_k - \mathcal J_k y_k, v_{k + 1} - y_{k + 1}
+                \rangle
+                \\
+                &= 
+                \left(
+                    1 - \alpha_k
+                \right)\left(
+                    \phi_k^* + \frac{A_k}{2}\Vert v_{k + 1} - v_k\Vert^2
+                \right)
+                + 
+                \alpha_k F(\mathcal J_k y_k) 
+                + 
+                \alpha_k\lambda_k^{-1}\langle 
+                    y_k - \mathcal J_k y_k, v_{k + 1} - y_{k + 1}
+                \rangle
+                \\
+                & \textcolor{gray}{
+                    A_{k + 1} = (1 - \alpha_k)A_k
+                }
+                \\
+                &=
+                (1 - \alpha_k)\phi_k^*
+                + 
+                \frac{A_{k + 1}}{2}\Vert v_{k + 1} - v_k\Vert^2
+                + \alpha_k F(\mathcal J_k y_k)
+                + \alpha_k\lambda_k^{-1}\langle 
+                    y_k - \mathcal J_k y_k, v_{k + 1} - y_{k + 1}
+                \rangle
+            \end{align*}
+            Next, we substitute the inequality by the inductive hypothesis which gives: 
+            {\small
+            \begin{align*}
+                \phi_{k + 1}^*
+                &\ge 
+                (1 - \alpha_k)
+                \left(
+                    F(\mathcal J_k y_k) + \langle \mathcal G_k y_k, x_k - \mathcal J_k y_k\rangle
+                \right)
+                \\
+                    &\quad 
+                    + 
+                    \frac{A_{k + 1}}{2}\Vert v_{k + 1} - v_k\Vert^2
+                    + \alpha_k F(\mathcal J_k y_k)
+                    + 
+                    \alpha_k\lambda_k^{-1}\langle 
+                        y_k - \mathcal J_k y_k, v_{k + 1} - y_{k + 1}
+                    \rangle
+                \\
+                &= 
+                F(\mathcal J_k y_k) + \frac{A_{k + 1}}{2}\Vert v_{k + 1} - v_k\Vert^2
+                + 
+                \lambda^{-1}_k
+                \left\langle 
+                    y_k - \mathcal J_k y_k, 
+                    (1 - \alpha_k)(x_k - \mathcal J_k y_k)
+                    + 
+                    \alpha_k(v_{k + 1} - \mathcal J_k y_k)
+                \right\rangle
+                \\
+                &= 
+                F(\mathcal J_k y_k) + \frac{A_{k + 1}}{2}\Vert v_{k + 1} - v_k\Vert^2
+                + 
+                \lambda^{-1}_k
+                \left\langle 
+                    y_k - \mathcal J_k y_k, 
+                    (1 - \alpha_k)x_k + \alpha_k v_{k + 1} -  \mathcal J_k y_k
+                \right\rangle. 
+            \end{align*}
+            }
+            This requires further simplifications. 
+            Rearranging the elements in the inner product we have: 
+            \begin{align*}
+                (1 - \alpha_k)x_k + \alpha_k v_{k + 1} - \mathcal J_k y_k
+                &= 
+                ((1 - \alpha_k)x_k + \alpha_k v_k - y_k)
+                + \alpha_k(v_{k + 1} - v_k) + (y_k - \mathcal J_k y_k). 
+            \end{align*}
+            We also use the equality: 
+            \begin{align*}
+                v_{k + 1} - v_k &= 
+                -\frac{\alpha_k}{A_{k + 1}\lambda_k}(y_k - \mathcal J_k y_k)
+                \\
+                \implies
+                \Vert v_{k + 1} - v_k\Vert^2 
+                &= 
+                \left\Vert
+                    - \frac{\alpha_k}{A_{k + 1}\lambda_k}
+                    \left(
+                        y_k - \mathcal J_k y_k
+                    \right)
+                \right\Vert^2
+                \\
+                \Vert v_{k + 1} - v_k\Vert^2 
+                &= 
+                \left(
+                    \frac{\alpha_k}{A_{k + 1}\lambda_k}
+                \right)^2
+                \left\Vert
+                    y_k - \mathcal J_k y_k
+                \right\Vert^2
+                \\
+                \frac{A_{k + 1}}{2}
+                \Vert v_{k + 1} - v_k\Vert^2 
+                &= 
+                \frac{\alpha_k^2}{2A_{k + 1} \lambda_k^2}
+                \left\Vert
+                    y_k - \mathcal J_k y_k
+                \right\Vert^2. 
+            \end{align*}
+            Substituting both equality we simplify the inequality into 
+            \begin{align*}
+                \phi_{k + 1}^* &\ge 
+                F(\mathcal J_k y_k)
+                + \frac{\alpha_k^2}{2A_{k + 1} \lambda_k^2}
+                \Vert y_k - \mathcal J_ky_k\Vert^2
+                \\
+                    & \quad 
+                    + 
+                    \lambda_k^{-1}
+                    \left\langle 
+                        y_k - \mathcal J_k y_k, 
+                        (1 - \alpha_k)x_k + \alpha_k v_k - y_k
+                    + \alpha_k(v_{k + 1} - v_k) + (y_k - \mathcal J_k y_k)
+                    \right\rangle
+                \\
+                &= 
+                F(\mathcal J_k y_k)
+                + \frac{\alpha_k^2}{2A_{k + 1} \lambda_k^2}
+                \Vert y_k - \mathcal J_ky_k\Vert^2
+                \\
+                    & \quad 
+                    + 
+                    \lambda_k^{-1}
+                    \left\langle 
+                        y_k - \mathcal J_k y_k, 
+                        (1 - \alpha_k)x_k + \alpha_k v_k - y_k
+                    \right\rangle
+                \\
+                    &\quad 
+                    + 
+                    \lambda_k^{-1}
+                    \langle
+                        y_k - \mathcal J_k y_k,
+                        \alpha_k(v_{k + 1} - v_k) + (y_k - \mathcal J_k y_k)
+                    \rangle
+                \tag{1}
+            \end{align*}
+            Simplifying the second cross term on the RHS of (1): 
+            \begin{align*}
+                & \lambda_k^{-1}
+                    \langle
+                        y_k - \mathcal J_k y_k,
+                        \alpha_k(v_{k + 1} - v_k) + (y_k - \mathcal J_k y_k)
+                    \rangle
+                \\
+                &= 
+                \lambda_k^{-1}
+                    \left\langle
+                        y_k - \mathcal J_k y_k,
+                        -\frac{\alpha_k^2}{A_{k + 1}\lambda_k}(y_k - \mathcal J_k y_k)
+                        + 
+                        (y_k - \mathcal J_k y_k)
+                    \right\rangle
+                \\
+                &= 
+                \lambda_k^{-1}
+                    \left\langle
+                        y_k - \mathcal J_k y_k,
+                        -\frac{\alpha_k^2}{A_{k + 1}\lambda_k}(y_k - \mathcal J_k y_k)
+                        + 
+                        (y_k - \mathcal J_k y_k)
+                    \right\rangle
+                \\
+                &=
+                \lambda_k^{-1} 
+                \left(
+                    1 - \frac{\alpha_k^2}{A_{k + 1}\lambda_k}
+                \right)
+                \Vert y_k - \mathcal J_k y_k\Vert^2. 
+            \end{align*}
+            The above term repeats with one of the term in (1), merging their coefficient it yields
+            \begin{align*}
+                & 
+                \lambda_k^{-1} 
+                \left(
+                    1 - \frac{\alpha_k^2}{A_{k + 1}\lambda_k}
+                \right) + 
+                \frac{\alpha_k^2}{2A_{k + 1} \lambda_k^2}
+                \\
+                & = 
+                \lambda_k^{-1}
+                - 
+                \frac{\alpha_k^2}{A_{k + 1}\lambda_k^2}
+                + 
+                \frac{\alpha_k^2}{2A_{k + 1}\lambda_k^2} 
+                \\
+                &= 
+                \frac{1}{2\lambda_k}
+                \left(
+                    2 - \frac{\alpha_k^2}{2A_{k + 1}\lambda_k}
+                \right). 
+            \end{align*}
+            By merging the terms, the 2 equality implifies the inequality in (1) into: 
+            \begin{align*}
+                \phi_{k + 1}^* 
+                &\ge 
+                F(\mathcal J_k y_k)
+                + \frac{\alpha_k^2}{2A_{k + 1} \lambda_k^2}
+                \Vert y_k - \mathcal J_ky_k\Vert^2
+                \\
+                    & \quad 
+                    + 
+                    \lambda_k^{-1}
+                    \left\langle 
+                        y_k - \mathcal J_k y_k, 
+                        (1 - \alpha_k)x_k + \alpha_k v_k - y_k
+                    \right\rangle
+                \\
+                    &\quad 
+                    + 
+                    \lambda_k^{-1}
+                    \langle
+                        y_k - \mathcal J_k y_k,
+                        \alpha_k(v_{k + 1} - v_k) + (y_k - \mathcal J_k y_k)
+                    \rangle
+                \\
+                &= 
+                F(\mathcal J_k y_k)
+                + 
+                \frac{1}{2\lambda_k}
+                \left(
+                    2 - \frac{\alpha_k^2}{A_{k + 1}\lambda_k}
+                \right)
+                \Vert y_k - \mathcal J_ky_k\Vert^2
+                \\
+                    & \quad 
+                    + 
+                    \lambda_k^{-1}
+                    \left\langle 
+                        y_k - \mathcal J_k y_k, 
+                        (1 - \alpha_k)x_k + \alpha_k v_k - y_k
+                    \right\rangle. 
+            \end{align*}
+            Next, to inductively assert the inequality we consider the choice of $y_k$ and scalar values $\alpha_k, \lambda_k$ which set the cross produce term zero, and the coefficient of the norm term larger than zero.
+            This would produce the following inequality, equality: 
+            \begin{align*}
+                & 
+                y_k = (1 - \alpha_k)x_k + \alpha_k v_k
+                \\
+                &
+                \frac{1}{2\lambda_k}
+                \left(
+                    2 - \frac{\alpha_k^2}{A_{k + 1}\lambda_k}
+                \right) 
+                \ge 0.
+            \end{align*}
+            Solving, the second inequality is equivalent to
+            \begin{align*}
+                \frac{\alpha_k^2}{A_{k + 1}\lambda_k} 
+                & 
+                \le 2
+                \\
+                \alpha_k
+                & 
+                \le
+                \sqrt{2A_{k + 1}\lambda_k}
+                = \sqrt{2A_k(1 - \alpha_k)\lambda_k}. 
+            \end{align*}
+            In Guler's paper, a strong inequality of $\alpha_k^2 = A_k(1 - \alpha_k)\lambda_k$ is used instead. 
+            Solving the quadratic it showed that the choice of sequence for $\alpha_k^2$ is 
+            \begin{align*}
+                \alpha_k
+                &= 
+                \frac{1}{2}\left(
+                    \sqrt{(A_k\lambda_k)^2 + 4A_k \lambda_k}
+                    - A_k\lambda_k
+                \right). 
+            \end{align*}
+        \end{proof}
+        \begin{remark}
+
+        \end{remark}
+    \subsection{Inexact accelerated PPM}
+        This section proofs the lemma that characterizes the inexact PPM errors for Guler's accelerated inexact PPM. 
+        Now, we prove 
+        \hyperref[thm:guler-inexact-ppm-bound]{Theorem \ref*{thm:guler-inexact-ppm-bound}}.
+
+        Denote $\mathcal M_k(x) = \mathcal M_k(x; y_k)$ for short. 
+        The proof is direct by considering the strong convexity of $\mathcal M_k(\cdot, y_k)$ together with the subgradient inequality. 
+        Choose any $w_k \in \partial \mathcal M_k(\mathcal J_{k} y_k)$ it has
+        \begin{align*}
+            \mathcal M_k(x_{k + 1}) - \mathcal M^*_k
+            &= 
+            \mathcal M_k(x_{k + 1}) - \mathcal M_k(\mathcal J_{k} y_k)
+            \\
+            &\ge 
+            \left(
+                \left\langle 
+                    w_k, 
+                    x_{k + 1} - \mathcal J_{k} y_k 
+                \right\rangle
+                + 
+                \mathcal M_k(\mathcal J_{k}y_k)
+                + \frac{1}{2\lambda_k}\Vert x_{k + 1} - \mathcal J_{k}y_k\Vert^2
+            \right)
+            - 
+            \mathcal M_k(\mathcal J_{\lambda_k}y_k) 
+            \\
+            &= \frac{1}{2\lambda_k}\Vert x_{k +1} - \mathcal J_{k}y_k\Vert^2. 
+        \end{align*}
+        We used $\mathbf 0 \in \partial M_k(\mathcal J_{\lambda_k}y_k)$ to get rid of the inner product. 
+        Consider inexact evaluation of $x_{k + 1}$ which results in $w_k \in \partial \mathcal M_k(x_{k + 1})$ with $\Vert w_k\Vert \le \epsilon_k/\lambda_k$. 
+        By $\lambda_k^{-1}$ strong convexity of $\mathcal M_k$, we have 
+        \begin{align*}
+            \mathcal M_k(\mathcal J_{k}y_k) - \mathcal M_k(x_{k + 1})
+            &\ge 
+            \langle w_k, \mathcal J_{k}y_k - x_{k + 1}\rangle
+            + \frac{1}{2\lambda_k}\Vert \mathcal J_{k} y_k - x_{k + 1}\Vert^2
+            \\
+            &\ge 
+            - \Vert w_k\Vert\Vert \mathcal J_{k}y_k - x_{k + 1}\Vert^2
+            + \frac{1}{2\lambda_k}\Vert \mathcal J_{k} y_k - x_{k + 1}\Vert^2
+            \\
+            &\ge 
+            - \frac{\epsilon_k}{\lambda_k}\Vert \mathcal J_{k}y_k - x_{k + 1}\Vert^2
+            + \frac{1}{2\lambda_k}\Vert \mathcal J_{k} y_k - x_{k + 1}\Vert^2
+            \\
+            &\ge \frac{1}{\lambda_k}
+            \min_{t \in \RR} \left\lbrace
+                \frac{1}{2}t^2 - \epsilon_k t
+            \right\rbrace = - \frac{\epsilon_k}{2\lambda_k}. 
+        \end{align*}
+
+        The upper bound is proved.
 
 \section{Proofs for Catalyst Meta Acceleration}
+    In this section, we prove the inexact proximal inequality and give the Nesterov's estimating sequence void of intractable quantities. 
+    The notation follows from:
 

### 2024-11-13 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes, sync

@@
 
-\section{Lin 2015}
+\section{Lin 2015}\label{sec:lin-2015}
     The section introduces the Nesterov's estimating sequence in Lin 2015 \cite{lin_universal_2015}. 
@@
         Suppose $x_k$ is an inexact proximal point evaluation of $x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1}$ with $\kappa$ fixed. 
-        Assume the approximation error is haracterized by $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k - 1}, y_{k - 1}) \le \epsilon_k$. 
+        Assume the approximation error is characterized by $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k - 1}, y_{k - 1}) \le \epsilon_k$. 
         Denote $x_k^* = \mathcal J_{\kappa^{-1}} y_{k - 1}$ to be the exact evaluation of the proximal point then for all $x$: 
@@
     \begin{remark}
-        The lamma plays a key role and it allows Lin to denote his Nesterov's estimating sequence to be for all $k \ge0$: 
+        The lemma plays a key role because it allows Lin to denote his Nesterov's estimating sequence to be for all $k \ge0$: 
         \begin{align*}
@@
     \begin{definition}[Basic 4WD Catalyst Algorithm]
-        Find any $x_0 \in \text{dom}(F)$. 
+        Find any $x_0 \in \dom(F)$. 
         Initialize the algorithm with $\alpha_1 = 1, v_0 = x_0$. 
@@
                     \begin{aligned}
-                        & \text{dist}(\mathbf 0, \partial \mathcal M(\bar x_k; x_{k - 1})) 
+                        & \dist(\mathbf 0, \partial \mathcal M(\bar x_k; x_{k - 1})) 
                         \le 
@@
                 : 
-                \text{dist}\left(
+                \dist\left(
                 \mathbf 0, \partial \mathcal M(\tilde x_k; y_k)
@@
 
-    \begin{theorem}[Basic 4WD Catalyst Convergence]
+    \begin{theorem}[Basic 4WD Catalyst Convergence]\label{thm:basic-4wd-catalyst}
         Let $(x_k, v_k, y_k)$ be generated by the basic Catalyst algorithm. 
@@
 \appendix
-\section{Postponed proofs}
+\section{Appendix}
 
@@
 
-    \begin{theorem}[Cannonical form of proximal gradient estimating sequence]
-    \label{thm:canon-prox-grad-est-seq}
+    \begin{theorem}[Cannonical form of proximal gradient estimating sequence]\label{thm:canon-prox-grad-est-seq}
         \; \\
@@
             := (1 - \alpha_k)\phi_k (x) + 
-            \alpha_k (l_h(x; y_k) + \mu/2\Vert x - y_k\Vert^2). 
+            \alpha_k (l_F(x; y_k) + \mu/2\Vert x - y_k\Vert^2). 
         \end{align*}
@@
     \end{theorem}
+
     \begin{proof}
@@
             \left(
-                l_h(x; y_k) + \mu/2\Vert x - y_k\Vert^2
+                l_F(x; y_k) + \mu/2\Vert x - y_k\Vert^2
             \right)
@@
         \end{align*}
-        They are matched and therefore we substitute $\xi_k, \tau_k$ into $v_{k + 1} = x_{k + 1} + (1 + \xi_k)^{-1}\gamma_k(x_{k + 1} - x_k)$: 
+        They are matched. Substitute $\xi_k, \tau_k$ into $v_{k + 1} = x_{k + 1} + (1 + \xi_k)^{-1}\gamma_k(x_{k + 1} - x_k)$: 
         \begin{align*}
@@
         \end{align*}
-        Subsituting back the cannonical form, we obtained a recursive definition of the Hessian and gradient of the estimating sequence:
-
+        Substituting the canonical form, we obtained a recursive definition of the Hessian and gradient of the estimating sequence: 
         \begin{align*}
@@
     In this section, we prove the inexact proximal inequality and give the Nesterov's estimating sequence void of intractable quantities. 
-    The notation follows from:
+    The notation follows from 
+    \hyperref[sec:lin-2015]{Section \ref*{sec:lin-2015}}. 
+    Let's now prove the inexact proximal inequality. 
+    Recall inexact evaluation $x_k \approx \mathcal J_{\kappa^{-1}}y_{k - 1}$ such that $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}}; y_{k - 1}) \le \epsilon_k$; $x_k^* = \mathcal J_{\kappa^{-1}}y_{k - 1}$ to be the exact evaluation.
 
 \section{Proofs for 4WD Catalyst Acceleration}
+    We prove
+    \hyperref[thm:basic-4wd-catalyst]{Theorem \ref*{thm:basic-4wd-catalyst}}
+    in this section. 
+    The lemma below characterize the lower and upper bound on the $(\alpha_k)_{k \ge 0}$ which ultimately control the convergence rate.
 

### 2024-11-14 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
     Nesterov's accelerated gradient first appeared back in the 1983 has sparked numerous theoretical and practical advancements in Mathematics programming literatures. 
-    The idea behind Nesterov's acceleration is universal for convex objective and it has concrete extension in the non-convex case. 
+    The idea behind Nesterov's acceleration is universal for convex objective, and it has concrete extension in the non-convex case. 
     In this paper we survey specifically the Catalyst Acceleration that incorporated ideas from the Accelerated Proximal Point Method proposed by Guler back in 1993. 
@@
     The algorithm closed the upper bound and lower bound on the iteration complexity for all first order Lipschitz smooth convex function among all first order algorithms. 
-    For a specific definition first order method, we refer reader to Chapter 2 of Nesterov's new book \cite{nesterov_lectures_2018} for more information. 
+    For a specific definition of first order method, we refer reader to Chapter 2 of Nesterov's new book \cite{nesterov_lectures_2018} for more information. 
     Gradient descent has an upper bound of $\mathcal O(1/k)$ in iteration complexity that is slower than
@@
 
-    Guler's accelerated Proximal Point Method(PPM) \cite{guler_new_1992} in 1993 used the technique of Nesterov's estimating sequence to accelerated PPM when the objective is convex. 
-    The algorithm uses $(\lambda_k)_{k \ge 0}$ in the PPM to generate $(x_k)_{k\ge 0}$ given any initial guess $x_0$.
-    Guler's prior work \cite{guler_convergence_1991} showed the convergence of PPM method in the convex without acceleration has convergence $\mathcal O\left(1/\sum^{n}_{i = 1}\lambda_i\right)$. 
-    His new algorithm with acceleration has a convergence rate of $\mathcal O\left(1/(\sum_{i = 1}^{n} \sqrt{\lambda_i})^2\right)$. 
+    Guler's accelerated Proximal Point Method (PPM) \cite{guler_new_1992} in 1993 used the technique of Nesterov's estimating sequence to accelerate PPM for convex objectives. 
+    Use $(\lambda_k)_{k \ge 0}$ to parameterize the proximal point evaluation to generate $(x_k)_{k\ge 0}$ given any initial guess $x_0$.
+    Guler's prior work \cite{guler_convergence_1991} showed the convergence of PPM method in the convex without acceleration is $\mathcal O\left(1/\sum^{n}_{i = 1}\lambda_i\right)$. 
+    His new algorithm with acceleration has a rate of $\mathcal O\left(1/(\sum_{i = 1}^{n} \sqrt{\lambda_i})^2\right)$. 
     An inexact Accelerated PPM method using conditions described in Rockafellar's works in 1976 \cite{rockafellar_monotone_1976} is also discussed in the paper.
@@
     \end{align*}
-    The difficulty comes from controlling the error $\epsilon$ at each iteration so that the overall convergence of accelerated PPM achieves optimal convergence rate. 
-    However, in the paper $\epsilon_k \rightarrow 0$, but in a specific rate. 
+    The difficulty comes from controlling the error $\epsilon$ at each iteration to ensure the overall convergence of accelerated PPM. 
+    In the paper $\epsilon_k \rightarrow 0$ at a specific rate. 
     It requires knowledge about exact minimum of the Moreau envelope at each step and the optimal value of the Nesterov's estimating sequence. 
-    These quantities are intractable in practice.
+    These quantities are intractable in practice making it impossible to formulate it to algorithms directly.
 
@@
 \cite{paquette_catalyst_2018}).
-    A meta algorithm because uses other first order algorithms to evaluate inexact proximal point method and then performs accelerated PPM based on the outputs of other algorithms. 
-    The innovations here are tracking and controlling the errors made in the inexact PPM throughout the algorithm and an algorithm called Proximal MISO.
+    The meta algorithm uses other first order algorithms to evaluate inexact proximal point method and then performs accelerated PPM based on the outputs of other algorithms, hence the umbrella term: ``meta algorithm''.
+    The innovations here are tracking and controlling the errors made in the inexact PPM using Nesterov's estimating sequence throughout and an algorithm called accelerated MISO-Prox by Lin. 
+    Prior to this paper, it was an open question on the conditions required to accelerate incremental method such as stochastic gradient descent can be accelerated.
 

### 2024-11-15 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
     Let's now prove the inexact proximal inequality. 
-    Recall inexact evaluation $x_k \approx \mathcal J_{\kappa^{-1}}y_{k - 1}$ such that $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}}; y_{k - 1}) \le \epsilon_k$; $x_k^* = \mathcal J_{\kappa^{-1}}y_{k - 1}$ to be the exact evaluation.
+    Recall inexact evaluation $x_k \approx \mathcal J_{\kappa^{-1}}y_{k - 1}$ such that $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}}y_{k - 1}; y_{k - 1}) \le \epsilon_k$; $x_k^* = \mathcal J_{\kappa^{-1}}y_{k - 1}$ to be the exact evaluation.
 

### 2024-11-15 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, fixed

@@
     Introduced in Lin et al.
-\cite{lin_universal_2015}\cite{lin_catalyst_2018} is a series of papers describing a concrete meta algorithm called Catalyst (It's called 4WD Catalyst for the non-convex extension in works by Paquette, Lin et al.
+\cite{lin_universal_2015,lin_catalyst_2018} is a series of papers on a concrete meta algorithm called Catalyst (It's called 4WD Catalyst for the non-convex extension in works by Paquette, Lin et al.
 \cite{paquette_catalyst_2018}).
-    The meta algorithm uses other first order algorithms to evaluate inexact proximal point method and then performs accelerated PPM based on the outputs of other algorithms, hence the umbrella term: ``meta algorithm''.
-    The innovations here are tracking and controlling the errors made in the inexact PPM using Nesterov's estimating sequence throughout and an algorithm called accelerated MISO-Prox by Lin. 
-    Prior to this paper, it was an open question on the conditions required to accelerate incremental method such as stochastic gradient descent can be accelerated.
+    The meta algorithm uses other first order algorithms to evaluate inexact proximal point method and then performs accelerated PPM, therefore the umbrella term: ``meta''. 
+    Major innovations include Tracking and controlling the errors made in the inexact PPM using Nesterov's estimating sequence throughout and an algorithm called accelerated MISO-Prox.  
+    Prior to Lin's paper, it was an open question on the conditions required to accelerate incremental method such as stochastic gradient descent can be accelerated.
 
@@
 \bibliographystyle{siam}
-\bibliography{references/refs}
+\bibliography{references/refs.bib}
 \newpage

### 2024-11-17 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
     It is correct, but not from a practical point of view. 
-    Let $F: \RR^n \mapsto \RR$ be our objective function, $\mathcal J_\lambda := (I + \lambda \partial F)^{-1}$ and $\mathcal M^{\lambda}(x; y):= F(x) + \frac{1}{2\lambda}\Vert x - y\Vert^2$ then the inexact proximal point considers with error $\epsilon_k$ has the following characterizations of inexactness as put forward by Guler \cite{guler_new_1992}:
+    Let $F: \RR^n \rightarrow\RR$ be our objective function, $\mathcal J_\lambda := (I + \lambda \partial F)^{-1}$ and $\mathcal M^{\lambda}(x; y):= F(x) + \frac{1}{2\lambda}\Vert x - y\Vert^2$ then the inexact proximal point considers with error $\epsilon_k$ has the following characterizations of inexactness as put forward by Guler \cite{guler_new_1992}:
     \begin{align*}
@@
         \begin{definition}[Nesterov's estimating sequence]\label{def:nes-est-seq}
-            Let $(\phi_k : \RR^n \mapsto \RR)_{k \ge 0}$ be a sequence of functions. 
+            Let $(\phi_k : \RR^n \rightarrow\RR)_{k \ge 0}$ be a sequence of functions. 
             We call this sequence of function a Nesterov's estimating sequence when it satisfies the conditions: 
@@
 \section{Nesterov's accelerated proximal gradient}
-    This section swiftly exposes the constructions of the Nesterov's estimating sequence for the FISTA algorithm by Beck\cite{beck_fast_2009-1}, which is specific case of Algorithm (2.2.63), in Nesterov's book \cite{nesterov_lectures_2018}.
-    The accelerated proximal gradient algorithm has very similar formulation as the Catalyst Acceleration framework and accelerated PPM. 
-    Additionally, the estimating sequence can derive the algorithm and verify the convergence.
+    This section swiftly exposes the constructions of the Nesterov's estimating sequence for accelerated proximal gradient method.
+A similar accelerated projected gradient is Algorithm (2.2.63) in Nesterov's book \cite{nesterov_lectures_2018}.
+    We use accelerated proximal gradient algorithm as an example because its formulation is similar to the Catalyst Acceleration framework.
 
@@
     This section introduces the setup of the Nesterov's estimating sequence used in Guler's accelerated Proximal Point method. 
-    In addition, this section will highlight some observations and theoretical results accordingly.
-
-    Throughout this section, we assume that $F:\RR^n \mapsto \overline \RR$ is a convex function. 
+    Guler showed Nesterov's estimating sequence technique can accelerate proximal point method from Rockafellar in the convex settings.
+
+    Throughout this section, we assume that $F:\RR^n \rightarrow \overline \RR$ is a convex function. 
     We use the following list of notations: 
@@
             \frac{1}{2\lambda_k} \Vert x_{k + 1} - \mathcal J_k y_k\Vert^2
-            &= 
+            &\le 
             \mathcal M_k(x_{k + 1}, y_k) - \mathcal M^*_k
@@
     \begin{definition}[Basic 4WD Catalyst Algorithm]
-        Find any $x_0 \in \dom(F)$. 
+        Find any $x_0 \in \text{dom}(F)$. 
         Initialize the algorithm with $\alpha_1 = 1, v_0 = x_0$. 
         For $k \ge 1$, the iterates $(x_k, y_k, v_k)$ are generated by the procedures: 
+        \vspace{-0.5em}
         \begin{align*}
             &
-            \text{find } \bar x_k \approx \argmin_{x}\left\lbrace
-                \mathcal M(x; x_{k - 1})
+            \textcolor{blue}{
+                \text{find } \bar x_k \approx 
+            }
+            \argmin_{x}\left\lbrace
+                    \mathcal M(x; \textcolor{violet}{x_{k - 1}})
+                \right\rbrace
+            \\ &\quad 
+            \text{such that: }
+                \text{dist}(\mathbf 0, \partial \mathcal M(\bar x_k; \textcolor{violet}{x_{k - 1}})) 
+                \le 
+                \kappa\Vert \textcolor{blue}{\bar x_k}- \textcolor{violet}{x_{k - 1}}\Vert, 
+                \mathcal M(\textcolor{blue}{\bar x_k}; \textcolor{violet}{x_{k - 1}}) 
+                \le F(\textcolor{violet}{x_{k - 1}}); 
+            \\
+            & y_k = \alpha_k v_{k - 1} + (1 - \alpha_k) \textcolor{violet}{x_{k - 1}};
+            \\
+            & 
+            \textcolor{red}{\text{find }\tilde x_k \approx}
+            \argmin_{x} \left\lbrace
+                \mathcal M(x; y_k) 
             \right\rbrace
             \text{ such that: }
-                \left\lbrace
-                    \begin{aligned}
-                        & \dist(\mathbf 0, \partial \mathcal M(\bar x_k; x_{k - 1})) 
-                        \le 
-                        \kappa\Vert \bar x_k - x_{k - 1}\Vert, 
-                        \\
-                        & \mathcal M(\bar x_k; x_{k - 1}) 
-                        \le F(x_{k - 1}). 
-                    \end{aligned}
-                \right.
-            \\
-            & y_k = \alpha_k v_{k - 1} + (1 - \alpha_k) x_{k - 1};
-            \\
-            & 
-            \text{find }\tilde x_k \approx \argmin_{x} \left\lbrace
-                \mathcal M(x; y_k) 
-                : 
                 \dist\left(
-                \mathbf 0, \partial \mathcal M(\tilde x_k; y_k)
-                \right) 
-                \le \frac{\kappa}{k + 1}\Vert \tilde x_k - y_k\Vert
-            \right\rbrace;
-            \\
-            & v_{k} = x_{k - 1} + \frac{1}{\alpha_k}(\tilde x_k - x_{k - 1});
+                    \mathbf 0, \partial \mathcal M(\textcolor{red}{\tilde x_k}; y_k)
+                \right) 
+                \le \frac{\kappa}{k + 1}\Vert \textcolor{red}{\tilde x_k} - y_k\Vert
+            ;
+            \\
+            & v_{k} = \textcolor{violet}{x_{k - 1}} + \frac{1}{\alpha_k}(
+                    \textcolor{red}{\tilde x_k} - \textcolor{violet}{x_{k - 1}}
+                );
             \\
@@
             \\
-            & \text{choose } x_k \text{ such that:  } f(x_k) = \min(f(\bar x_k), f(\tilde x_k)). 
+            & \text{choose } \textcolor{violet}{x_k} \text{ such that:  } 
+            f(\textcolor{violet}{x_k}) = \min(f(\textcolor{blue}{\bar x_k}), f(\textcolor{red}{\tilde x_k})). 
         \end{align*}
@@
         \; \\
-        Denote $\phi_k:\RR^n \mapsto \RR$ as a sequence of functions such that it satisfies recursively for all $k\ge 0$ the following conditions 
+        Denote $\phi_k:\RR^n \rightarrow\RR$ as a sequence of functions such that it satisfies recursively for all $k\ge 0$ the following conditions 
         \begin{align*}
@@
         From the second and third equality we used $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$. 
-        Substituting the canonical form of $\phi_{k + 1}$ back to \textcolor{red}{eqn1}, choose $x = y_k$, it gives the following: 
+        Substituting the canonical form of $\phi_{k + 1}$ back to \textcolor{red}{(eqn1)}, choose $x = y_k$, it gives the following: 
         \begin{align*}
@@
         Next move is to simplify the term $\Vert v_{k + 1} - y_k\Vert^2$. 
+        We are doing this in advance so that later on the implicit descent conditions $F(x_{k + 1}) \le \phi_k^*$ will have easier algebra. 
         With that it produces: 
@@
         \end{align*}
-        Substitute it back to \textcolor{red}{eqn2} we have 
+        Substitute it back to \textcolor{red}{(eqn2)} we have 
         \begin{align*}
@@
             \frac{\alpha_k \gamma_k }{\gamma_{k + 1}} 
-            (v_k - y_k) + (T_L y_k - y_k) &= \mathbf 0, 
+            (v_k - y_k) + (\widetilde {\mathcal J}_{L^{-1}} y_k - y_k) &= \mathbf 0, 
         \end{align*}
@@
             &\ge 
-            (1 - \alpha_k)h(x_k)
+            (1 - \alpha_k)F(x_k)
             + 
@@
             \left(
-                h(x_k) + \frac{1}{2L}\Vert g_k\Vert^2
+                F(x_k) + \frac{1}{2L}\Vert g_k\Vert^2
             \right)
@@
     \subsection{Exact accelerated PPM}
-        This setion contains all the proofs for the exact accelerated PPM method. 
+        This section contains all the proofs for the exact accelerated PPM method. 
         It follows the same notation from the accelerated PPM section that $F$ is a convex function and the notations are $\mathcal J_k, \mathcal G_k$ for the proximal point evaluation and gradient mapping.
@@
             \end{align*}
-            By merging the terms, the 2 equality implifies the inequality in (1) into: 
+            Substituting back to (1): 
             \begin{align*}
@@
             \end{align*}
-            Next, to inductively assert the inequality we consider the choice of $y_k$ and scalar values $\alpha_k, \lambda_k$ which set the cross produce term zero, and the coefficient of the norm term larger than zero.
-            This would produce the following inequality, equality: 
+            Next, if induction hypothesis $\phi_{k + 1}\ge F(\mathcal J_k y_k) = F(x_{k + 1})$ is true, it's sufficient to take the coefficient of $\Vert y_k - \mathcal J_k y_k\Vert^2$ to be greater than zero and make the inner product term zero which produces:
             \begin{align*}
@@
             \end{align*}
-            In Guler's paper, a strong inequality of $\alpha_k^2 = A_k(1 - \alpha_k)\lambda_k$ is used instead. 
-            Solving the quadratic it showed that the choice of sequence for $\alpha_k^2$ is 
+            Using $\alpha_k^2 = A_k(1 - \alpha_k)\lambda_k$ to solving the quadratic: 
             \begin{align*}
@@
         \begin{remark}
-
+            The approach by Guler is slightly different compare to Accelerated Proximal Gradient method completed in Section \ref*{app:sec:thm-claim-acc-prox-grad}. 
+            For the Accelerated Proximal Gradient, we simplified $\phi_{k + 1}^*$ prior to considering $F(x_{k + 1}) \le \phi_{k + 1}^*$. 
         \end{remark}
@@
     The lemma below characterize the lower and upper bound on the $(\alpha_k)_{k \ge 0}$ which ultimately control the convergence rate. 
+    \begin{lemma}{app:lemma:momentum-sequence-bounds}
+
+    \end{lemma}
 

### 2024-11-19 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
         Compare to Nesterov's work, we used proximal gradient operator instead of projected gradient. 
-        The same inequality is called ``Fundamental Proximal Gradient Inequality'' in Amir Beck's book \cite{beck_first-order_2017}, Theorem 10.16. 
     \end{remark}
@@
             \mathbf 0, \partial \mathcal M^{k}(x_{k + 1}; y_k)
-        \right) &\le \frac{\epsilon_k}{k}
+        \right) &\le \frac{\epsilon_k}{\lambda_k}
         \\
@@
     \end{theorem}
+    \begin{remark}
+        The inequalities are from PL-condition and strong convexity. 
+        They are now standard results in convex optimizations. 
+        For a proof of the theorem, see 
+        \hyperref[app:sec:inxt-acc-ppm]{Appendix \ref*{app:sec:inxt-acc-ppm}}. 
+    \end{remark}
     The next theorem is Theorem 3.3 of Guler's 1993 papers which is a major result for inexact accelerated PPM method. 
@@
     The lemma allows the analysis Nesterov's estimating sequence to be carried through without using intractable quantities: $\mathcal M^{\kappa^{-1}}(\mathcal J_{k^{-1}}y_{k - 1}, y_{k - 1}), \mathcal J_{\kappa^{-1}}y_{k - 1}$.
-    \begin{lemma}[Lin's inexact proximal inequality]
-        Let $F$ be a $\mu\ge 0$ strongly convex.
-        Suppose $x_k$ is an inexact proximal point evaluation of $x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1}$ with $\kappa$ fixed. 
-        Assume the approximation error is characterized by $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k - 1}, y_{k - 1}) \le \epsilon_k$. 
-        Denote $x_k^* = \mathcal J_{\kappa^{-1}} y_{k - 1}$ to be the exact evaluation of the proximal point then for all $x$: 
+    \begin{lemma}[Lin's inexact proximal inequality]\label{lemma:lin-ixct-prox-ineq}
+        Let $F$ be a $\mu\ge 0$ strongly convex and fix $\kappa$. 
+        If $x_k$ is an inexact proximal point evaluation of $x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1}$ such that there exists $\epsilon_k$ where $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k - 1}, y_{k - 1}) \le \epsilon_k$.
+        Denote $x_k^* = \mathcal J_{\kappa^{-1}} y_{k - 1}$ it has for all $x$: 
         \begin{align*}
@@
         \begin{align*}
-            \phi_k(x) := 
+            \phi_0 &:= F(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2, 
+            \\
+            \phi_k(x) &:= 
             (1 - \alpha_{k - 1})\phi_{k - 1}(x)
@@
         \end{align*}
-        Next move is to simplify the term $\Vert v_{k + 1} - y_k\Vert^2$. 
-        We are doing this in advance so that later on the implicit descent conditions $F(x_{k + 1}) \le \phi_k^*$ will have easier algebra. 
+        Next move from Nesterov was to simplify the term $\Vert v_{k + 1} - y_k\Vert^2$. 
         With that it produces: 
@@
             \left(
-                \alpha_k(1 - \alpha_k)v_k - \alpha_k g_k 
+                \gamma_k(1 - \alpha_k)v_k - \alpha_k g_k 
                 + (-\gamma_{k + 1} + \mu\alpha_k)y_k
@@
                     \\
-                    \gamma_{k + 1} - \mu \alpha_k &= (1 - \alpha_k)\gamma_k
+                    -(1 - \alpha_k)\gamma_k
+                    &= - \gamma_{k + 1} + \mu \alpha_k
                 \end{aligned}
@@
             \left(
-                \alpha_k(1 - \alpha_k)v_k - \alpha_k g_k 
+                \gamma_k(1 - \alpha_k)v_k - \alpha_k g_k - 
                 (1 - \alpha_k)\gamma_ky_k
@@
             \gamma_{k + 1}^{-1}(
-                \alpha_k(1 - \alpha_k)(v_k - y_k) 
+                \gamma_k(1 - \alpha_k)(v_k - y_k) 
                 - \alpha_k g_k
@@
         \end{align*}
-        Taking the norm of that we have: 
+        Next we have
         \begin{align*}
@@
                 \gamma_{k + 1}^{-1}(
-                    \alpha_k(1 - \alpha_k)(v_k - y_k) 
+                    \gamma_k(1 - \alpha_k)(v_k - y_k) 
                     - \alpha_k g_k
@@
             \frac{\alpha_k^2}{2 \gamma_{k + 1}} \Vert g_k\Vert^2
-            \\&\quad 
             + 
@@
         \end{align*}
+
         Substitute it back to \textcolor{red}{(eqn2)} we have 
@@
     \end{proof}
+    \begin{remark}
+        The goal of having $\phi_k^*$ represented by iterates $v_k, y_k, g_k$ is because it assists in the future when an inductive hypothesis $\phi_k^* \ge f(x_k) \ge l_F(x_k; y_k) + \frac{\mu}{2}\Vert x - y_k\Vert^2$ is made.
+        We did things in advance here, nothing more. 
+    \end{remark}
 
@@
 \section{Proofs for accelerated PPM}
-    \subsection{Exact accelerated PPM}
+    \subsection{Exact accelerated PPM}\label{sec:app:exct-acc-ppm}
         This section contains all the proofs for the exact accelerated PPM method. 
@@
             For the Accelerated Proximal Gradient, we simplified $\phi_{k + 1}^*$ prior to considering $F(x_{k + 1}) \le \phi_{k + 1}^*$. 
+            In here, we substitute the inductive hypothesis $\phi_k^* \ge f(x_k)$ and skipped the canonical representation of $\phi_k^*$.
+
+            A more critical observation here is the Nesterov's estimating sequence from 
+            \hyperref[app:sec:thm-claim-acc-prox-grad]{Section \ref*{app:sec:thm-claim-acc-prox-grad}} is the same as Guler's Accelerated PPM if we choose $L^{-1} = \lambda_k$,$\mu = 0$ and $g \equiv 0$ because:
+            \begin{align*}
+                l_F(x; y_k) 
+                &= 
+                F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) + 
+                \left\langle 
+                    L\left(y_k - \widetilde{\mathcal J}_{L^{-1}}y_k\right), 
+                    x - y_k
+                \right\rangle
+                + 
+                \frac{1}{2L} 
+                \left\Vert 
+                    L \left(y_k - \widetilde{\mathcal J}_{L^{-1}}y_k\right)
+                \right\Vert^2
+                \\
+                &= 
+                F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) + 
+                \left\langle 
+                    L\left(y_k - \widetilde{\mathcal J}_{L^{-1}}y_k\right), 
+                    x - \widetilde{\mathcal J}_{L^{-1}}y_k
+                \right\rangle
+            \end{align*}
+            When $g\equiv 0$, $L^{-1} = \lambda_k$, the proximal gradient operator has $\widetilde{\mathcal J}_{L^{-1}} = \mathcal J_{\lambda_k}(y_k)$, making $\phi_k(x)$ here the same as accelerated proximal gradient.
         \end{remark}
-    \subsection{Inexact accelerated PPM}
+    \subsection{Inexact accelerated PPM}\label{app:sec:inxt-acc-ppm}
         This section proofs the lemma that characterizes the inexact PPM errors for Guler's accelerated inexact PPM. 
@@
         The upper bound is proved. 
+        \begin{remark}
+            This is nothing new. 
+            First inequality is a direct consequence of strong convexity and the second inequality is the PL-inequality implied by strong convexity. 
+        \end{remark}
 
@@
     In this section, we prove the inexact proximal inequality and give the Nesterov's estimating sequence void of intractable quantities. 
-    The notation follows from 
+    The notation is the same as
     \hyperref[sec:lin-2015]{Section \ref*{sec:lin-2015}}. 
-    Let's now prove the inexact proximal inequality. 
     Recall inexact evaluation $x_k \approx \mathcal J_{\kappa^{-1}}y_{k - 1}$ such that $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}}y_{k - 1}; y_{k - 1}) \le \epsilon_k$; $x_k^* = \mathcal J_{\kappa^{-1}}y_{k - 1}$ to be the exact evaluation.
+
+    \subsection{Inexact proximal inequality}
+        \begin{proof}
+            This is the proof for 
+            \hyperref[lemma:lin-ixct-prox-ineq]{Lemma \ref*{lemma:lin-ixct-prox-ineq}}. 
+            Define $G_k := \mathcal M_F^{\kappa^{-1}}(\cdot, y_{k - 1}), G_k^* = \mathcal M_F^{\kappa^{-1}}(x_k^*, y_{k - 1})$. 
+        $G_k$ is a $\mu + \kappa$ convex function which implies quadratic growth over minimizer $x_k^*$: 
+        \begin{align*}
+            (\forall x)\quad G_k(x) &\ge G_k^* + \frac{\kappa + \mu}{2}\Vert x - x_k^*\Vert^2. 
+        \end{align*}
+        Substituting definitions:
+        {\small
+        \begin{align*}
+            F(x) &\ge 
+            G_k(x_k) + (G_k^* - G_k(x_k)) + 
+            \frac{\mu + \kappa}{2}\Vert x - x_k^*\Vert^2 
+            - \frac{\kappa}{2}\Vert x - y_{k - 1}\Vert^2
+            \\
+            &\ge 
+            G(x_k) - \epsilon_k + \frac{\kappa + \mu}{2}\Vert x - x_k^*\Vert^2
+            - \frac{\kappa}{2}\Vert x - y_{k - 1}\Vert^2
+            \\
+            &= G_k(x_k) - \epsilon_k + \frac{\kappa + \mu}{2}
+            \left(
+                \Vert x - x_k - x_k + x_k^*\Vert^2
+            \right)
+            - \frac{\kappa}{2}\Vert x - y_{k - 1}\Vert^2
+            \\
+            &= G_k(x_k) - \epsilon_k + \frac{\kappa + \mu}{2}
+            \left(
+                \Vert x - x_k\Vert^2 + \Vert x_k - x_k^*\Vert^2
+                + 
+                2\langle x - x_k, x_k - x_k^*\rangle
+            \right)
+            - \frac{\kappa}{2}\Vert x - y_{k - 1}\Vert^2
+            \\
+            &= 
+            \left(
+                G_k(x_k) + \frac{\kappa}{2}\Vert x - x_k\Vert^2 - \frac{\kappa}{2}\Vert x - y_{k - 1}\Vert^2
+            \right)
+            - \epsilon_k
+            \\ &\quad 
+                + \frac{\mu}{2}\Vert x - x_k\Vert^2
+                + \frac{\kappa + \mu}{2}\Vert x_k - x_k^*\Vert^2
+                + (\kappa + \mu)\langle x - x_k, x_k - x_k^*\rangle. 
+        \end{align*}
+        }
+        Simplify terms inside the parenthesis: 
+        \begin{align*}
+            &
+            G_k(x_k) 
+            + \frac{\kappa}{2}\Vert x - x_k\Vert^2 - \frac{\kappa}{2}\Vert x - y_{k - 1}\Vert^2
+            \\
+            &= 
+            F(x_k) + \frac{\kappa}{2}\Vert x_k - y_{k - 1}\Vert^2
+            + \frac{\kappa}{2}\Vert x - x_k\Vert^2 - \frac{\kappa}{2}\Vert x - y_{k - 1}\Vert^2
+            \\
+            &= 
+            F(x_k) + 
+            \frac{\kappa}{2}\left(
+                \Vert x_k - y_{k - 1}\Vert^2 - \Vert x - y_{k - 1}\Vert^2
+            \right)
+            + \frac{\kappa}{2} \Vert x - x_k\Vert^2
+            \\
+            &= 
+            F(x_k) + 
+            \frac{\kappa}{2}\left(
+                \Vert x_k - x\Vert^2 
+                + 
+                2\langle x_k - x, x - y_{k - 1} \rangle
+            \right)
+            + 
+            \frac{\kappa}{2} \Vert x - x_k\Vert^2
+            \\
+            &= 
+            F(x_k) + 
+            \kappa\Vert x_k - x\Vert^2
+            + 
+            \kappa\langle x_k - x, x - y_{k - 1}\rangle
+            \\
+            &= 
+            F(x_k) + 
+            \kappa\langle x_k - x, x - y_{k - 1} + x_k - x\rangle
+            \\
+            &= F(x_k) + \kappa\langle x_k - x, x_k - y_{k - 1} \rangle. 
+        \end{align*}
+        Therefore, it has the inequality: 
+        \begin{align*}
+            F(x) 
+            &\ge 
+            F(x_k) + \kappa\langle x_k - x, x_k - y_{k - 1} \rangle
+            - \epsilon_k
+            \\&\quad 
+                + \frac{\mu}{2}\Vert x - x_k\Vert^2
+                + \frac{\kappa + \mu}{2}\Vert x_k - x_k^*\Vert^2
+                + (\kappa + \mu)\langle x - x_k, x_k - x_k^*\rangle
+            \\
+            & \ge
+            F(x_k) + \kappa\langle x_k - x, x_k - y_{k - 1} \rangle
+            - \epsilon_k
+            + \frac{\mu}{2}\Vert x - x_k\Vert^2
+            + (\kappa + \mu)\langle x - x_k, x_k - x_k^*\rangle. 
+        \end{align*}
+        Re-arranging it to a form by the writer's preference:
+        \begin{align*}
+            F(x) - F(x_k) - \kappa\langle x_k - x, x_k - y_{k - 1} \rangle
+            - \frac{\mu}{2}\Vert x - x_k\Vert^2
+            &\ge 
+            - \epsilon_k
+            + (\kappa + \mu)\langle x - x_k, x_k - x_k^*\rangle. 
+        \end{align*}
+        Now we have the RHS to be exclusively about the inexact evaluation $x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1}$, and $G_k(x_k) - G^*_k \le \epsilon_k$.
+
+        \end{proof}
+        \begin{remark}
+
+        \end{remark}
 
@@
     The lemma below characterize the lower and upper bound on the $(\alpha_k)_{k \ge 0}$ which ultimately control the convergence rate. 
-    \begin{lemma}{app:lemma:momentum-sequence-bounds}
+    \begin{lemma}\label{app:lemma:momentum-sequence-bounds}
 

### 2024-11-19 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, change, sync

@@
     \end{remark}
+
     For theoretical interests, there is a major difference between Lin's approach and Guler's approach. 
@@
     The lemma allows the analysis Nesterov's estimating sequence to be carried through without using intractable quantities: $\mathcal M^{\kappa^{-1}}(\mathcal J_{k^{-1}}y_{k - 1}, y_{k - 1}), \mathcal J_{\kappa^{-1}}y_{k - 1}$.
+
     \begin{lemma}[Lin's inexact proximal inequality]\label{lemma:lin-ixct-prox-ineq}
@@
     \label{app:thm:fun-thm-prox-grad}
-        Let $h = f + g$ and proximal gradient operator $T$ be given as in this section. 
+        Let $F = f + g$, define the proximal gradient operator $\widetilde{\mathcal J}_{L^{-1}}$.  
         Fix any $y$, we have for all $x \in \RR^n$: 
         \begin{align*}
-            h(x) - h(Ty) - 
+            F(x) - F(Ty) - 
             \left\langle 
@@
             &= 
-            h(x) - D_f(x, y) + \frac{L}{2}\Vert x - y\Vert^2 
+            F(x) - D_f(x, y) + \frac{L}{2}\Vert x - y\Vert^2 
             \\
@@
         Now we have the RHS to be exclusively about the inexact evaluation $x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1}$, and $G_k(x_k) - G^*_k \le \epsilon_k$. 
-
         \end{proof}
         \begin{remark}
+            Two major things about this lemma: 
+            \begin{enumerate}
+                \item Set $\epsilon_k = 0$ so $x_k = x^*_k$, the lemma is the proximal inequality. 
+                \item It's not entirely obvious on its relations to the proximal gradient inequality. 
+            \end{enumerate}
+            For point (ii), observe that the proximal gradient inequality given by 
+            \hyperref[app:thm:fun-thm-prox-grad]{Theorem \ref*{app:thm:fun-thm-prox-grad}} 
+            has RHS that is completely different. 
+            We have made attempts at bridging the two inequalities. 
+            There are no obvious useful results and concrete claims. 
+            There are no choices of parameters that makes the two inequalities equivalent.
 
         \end{remark}
+    \subsection{Approximated Nesterov's Estimating sequence}
+        In this subsection, let $\phi_k$ be the Nesterov's estimating sequence for Catalyst. 
+        For all $k \ge0$, $\phi_k$ satisfies 
+        \begin{align*}
+            \phi_0 &:= F(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2
+            \\
+            \phi_k(x) &:= 
+            (1 - \alpha_{k - 1})\phi_{k - 1}(x) + 
+            \alpha_{k - 1}\left(
+                F(x_k) + \kappa\langle y_{k - 1} - x_k, x - x_k\rangle
+                + \frac{\mu}{2} \Vert x - x_k\Vert^2
+            \right). 
+        \end{align*}
+        We prove following theorem which is Lemma A.6 in Lin's writings on Catalyst \cite{lin_universal_2015}. 
+        \begin{theorem}[Canonical form of Catalyst estimating sequence]
+
+        \end{theorem}
 

### 2024-11-20 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
 \section{Introduction}
-    \textcolor{red}{THIS REPORT IS CURRENTLY: UNFINISHED}
+    \textcolor{red}{THIS REPORT IS CURRENTLY: FINISHED, BUT NOT YET POLISHED}
 
@@
         Guler didn't simplify his results compare to what Nesterov did in his book. 
+        For a detailed proofs of the estimating sequence with comparison to the accelerated proximal gradient method, see Appendix \ref*{sec:app:exct-acc-ppm}. 
     \end{remark}
@@
 
-\section{Non-convex extension of Catalyst acceleration}
+\section{Non-convex extension of Catalyst acceleration}\label{sec:4wd-catalyst}
     The non-convex extension of Catalyst acceleration by Lin 2018 \cite{lin_catalyst_2018} is similar to the convex case in his 2015 paper \cite{lin_universal_2015}. 
@@
     We define the algorithm and then its convergence claim below. 
-    \begin{definition}[Basic 4WD Catalyst Algorithm]
+    \begin{definition}[Basic 4WD Catalyst Algorithm]\label{def:basic-4wd-catalyst}
         Find any $x_0 \in \text{dom}(F)$. 
@@
         Next we have
+        {\small
         \begin{align*}
@@
         \end{align*}
+        }
 
@@
                 \widetilde{\mathcal J}_{L^{-1}} y_{k - 1}
-            \right)\le \phi_k^*
+            \right) 
+            &\le \phi_k^*
             \\
@@
             There are no choices of parameters that makes the two inequalities equivalent. 
+            We are not aware of any analogous results to this theorem in the literatures.
 
         \end{remark}
+
     \subsection{Approximated Nesterov's Estimating sequence}
@@
         \end{align*}
+        Observe that $\phi_k$ is a simple quadratic function. 
         We prove following theorem which is Lemma A.6 in Lin's writings on Catalyst \cite{lin_universal_2015}. 
-        \begin{theorem}[Canonical form of Catalyst estimating sequence]
-
+        \begin{theorem}[Canonical form of Catalyst estimating sequence]\;\\
+            Define $v_k, \gamma_k$ to be the parameters for the canonical form of $\phi_k$ as given by 
+            \begin{align*}
+                \phi_k^* &= \min_x \phi_k(x)
+                \\
+                \phi_k(x) &= \phi_k^* + \frac{\gamma_k}{2}\Vert x - v_k\Vert^2. 
+            \end{align*}
+            Then the parameters the canonical form $(\gamma_{k})_{k \ge0}, (v_k)_{k \ge 0}, (\phi_k^*)_{k\ge 0}$ satisfies for all $k \ge 1$
+            \begin{align*}
+                \gamma_k &= (1 - \alpha_{k - 1})\gamma_{k - 1} + \alpha_{k - 1}\mu, 
+                \\
+                v_k &= 
+                \gamma_k^{-1}(
+                    (1 - \alpha_{k - 1})\gamma_{k - 1}v_{k - 1}
+                    + \alpha_{k - 1}\mu x_k - \alpha_{k - 1}\kappa(y_{k - 1} - x_k)
+                ), 
+                \\
+                \phi_k^* &= (1 - \alpha_{k - 1})\phi_{k - 1}^*
+                + \alpha_{k - 1}F(x_k)
+                - \frac{\alpha_{k - 1}^2}{2\gamma_k}\Vert \kappa(y_{k - 1} - x_k)\Vert^2
+                \\
+                &\quad 
+                + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
+                \left(
+                    \frac{\mu}{2}\Vert x_k - v_{k - 1}\Vert^2 + 
+                    \langle \kappa(y_{k - 1} - x_k), v_{k - 1} - x_k\rangle
+                \right). 
+            \end{align*}
         \end{theorem}
+        \begin{proof}
+            For $v_{k + 1}$, solve for $\nabla \phi_k(v_k) = \mathbf 0$ using the recursive definition. 
+            For $\gamma_k$, consider the Hessian $\nabla^2 \phi_k$ using the recursive definition. 
+            The process is similar to derivations in 
+            \hyperref[app:sec:thm-claim-acc-prox-grad]{Section \ref*{app:sec:thm-claim-acc-prox-grad}}.
+
+            Next, we work on $\phi_k^*$. 
+            The goal of the canonical form is to simplify the process of solving for an implicit sequence $x_k$ such that $f(x_k) \le \phi_k^*$. 
+            To start consider for all $k \ge 1$: 
+            \begin{align*}
+                \phi_k(x_k) &= 
+                \phi_k^* + \frac{\gamma_k}{2}\Vert x_k - v_k\Vert^2
+                \\
+                & = (1 - \alpha_{k - 1})\left(
+                    \phi_{k - 1}^* + \frac{\gamma_{k - 1}}{2}\Vert x_k - v_{k - 1}\Vert^2
+                \right) + \alpha_{k - 1}F(x_k)
+                \\
+                \iff 
+                \phi_k^* &= 
+                (1 - \alpha_{k - 1})\left(
+                    \phi_{k - 1}^* + \frac{\gamma_{k - 1}}{2}\Vert x_k - v_{k - 1}\Vert^2
+                \right) + \alpha_{k - 1}F(x_k) - \frac{\gamma_k}{2}\Vert x_k - v_k\Vert^2
+                \\
+                &= 
+                (1 - \alpha_{k - 1})\phi_{k - 1}+ \alpha_{k - 1}F(x_k)
+                + 
+                \frac{(1 - \alpha_{k - 1})\gamma_{k - 1}}{2}\Vert x_k - v_{k - 1}\Vert^2
+                - \frac{\gamma_k}{2}\Vert x_k - v_k\Vert^2.
+            \end{align*}
+                Now, it would be great to express $\Vert x_k - v_k\Vert^2$, so it depends on the iterates from previous iteration. 
+                From the definition of $v_k$ we have 
+            \begin{align*}
+                v_k - x_k &= 
+                \gamma_k^{-1}(
+                (
+                    1 - \alpha_{k - 1})\gamma_{k - 1}v_{k - 1}
+                    + \alpha_{k - 1}\mu x_k - \alpha_{k - 1}\kappa(y_{k - 1} - x_k)
+                ) - x_k
+                \\
+                &= 
+                \gamma_k^{-1}(
+                    (1 - \alpha_{k - 1})\gamma_{k - 1}v_{k - 1}
+                    + (\alpha_{k - 1}\mu - \gamma_k) x_k - \alpha_{k - 1}\kappa(y_{k - 1} - x_k)
+                )
+                \\
+                &= 
+                \gamma_k^{-1}(
+                    (1 - \alpha_{k - 1})\gamma_{k - 1}v_{k - 1}
+                    - (1 - \alpha_{k - 1})\gamma_{k - 1} x_k - \alpha_{k - 1}\kappa(y_{k - 1} - x_k)
+                )
+                \\
+                &= \gamma_k^{-1}(
+                    (1 - \alpha_{k - 1})\gamma_{k - 1}(v_{k - 1} - x_k)
+                    - \alpha_{k - 1}\kappa(y_{k - 1} - x_k)
+                ).
+            \end{align*}
+            Taking the norm and multiplying by $\gamma_k/2$ to match the terms in (eqn1) then: 
+            \begin{align*}
+                \Vert v_k - x_k\Vert^2 &= 
+                \gamma_k^{-2}\Vert (1 - \alpha_{k - 1})\gamma_{k - 1}(v_{k - 1} - x_k) \Vert^2
+                + 
+                \gamma_k^{-2}\Vert \alpha_{k - 1}\kappa(y_{k - 1} - x_k)\Vert^2
+                \\
+                & \quad 
+                - 2\gamma_k^{-2}\gamma_{k - 1}(1 - \alpha_{k - 1})\alpha_{k - 1}\langle v_{k - 1} - x_k, \kappa(y_{k - 1} - x_k) \rangle
+                \\
+                \frac{\gamma_k}{2}
+                \Vert v_k - x_k\Vert^2 
+                &= 
+                \frac{(1 - \alpha_{k - 1})^{2}\gamma_{k - 1}^{2}}{2\gamma_k}\Vert x_k - v_{k - 1}\Vert^2
+                + 
+                \frac{\alpha_{k - 1}^2}{2\gamma_k} \Vert \kappa(y_{k - 1} - x_k)\Vert^2
+                \\
+                &\quad 
+                - 
+                \frac{
+                    \gamma_{k - 1}(1 - \alpha_{k - 1})\alpha_{k - 1}
+                }{\gamma_k}\langle v_{k - 1} - x_k, \kappa(y_{k - 1} - x_k)\rangle.  
+            \end{align*}
+            Substituting it back we have 
+            {\small
+            \begin{align*}
+                \phi_k^* &= 
+                (1 - \alpha_{k - 1})\phi_{k - 1}+ \alpha_{k - 1}F(x_k)
+                + 
+                \frac{(1 - \alpha_{k - 1})\gamma_{k - 1}}{2}\Vert x - v_{k - 1}\Vert^2
+                - 
+                \frac{(1 - \alpha_{k - 1})^{2}\gamma_{k - 1}^{2}}{2\gamma_k}\Vert x_k - v_{k - 1}\Vert^2
+                \\
+                & \quad 
+                    + \left(
+                        - 
+                        \frac{\alpha_{k - 1}^2}{2\gamma_k} \Vert \kappa(y_{k - 1} - x_k)\Vert^2
+                        + 
+                        \frac{
+                            \gamma_{k - 1}(1 - \alpha_{k - 1})\alpha_{k - 1}
+                        }{\gamma_k}\langle v_{k - 1} - x_k, \kappa(y_{k - 1} - x_k)\rangle
+                    \right)
+                \\
+                &= 
+                (1 - \alpha_{k - 1})\phi_{k - 1}+ \alpha_{k - 1}F(x_k)
+                + 
+                \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}\mu}{2\gamma_k}
+                \Vert x_k - v_{k - 1}\Vert^2
+                - 
+                \frac{\alpha_{k - 1}^2}{2\gamma_k} \Vert \kappa(y_{k - 1} - x_k)\Vert^2
+                \\
+                &\quad + 
+                \frac{\gamma_{k - 1}(1 - \alpha_{k - 1})\alpha_{k - 1}}{\gamma_k}
+                \langle v_{k - 1} - x_k, \kappa(y_{k - 1} - x_k)\rangle
+                \\
+                &= 
+                (1 - \alpha_{k - 1})\phi_{k - 1} + \alpha_{k - 1}F(x_k)
+                \\ &\quad 
+                + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
+                \left(
+                    \frac{\mu}{2}\Vert x_k - v_{k - 1}\Vert^2 
+                    + 
+                    \langle v_{k - 1} - x_k, \kappa(y_{k - 1} - x_k) \rangle. 
+                \right)
+            \end{align*}
+            }
+            On the second equality, we made use of the following to simplify the coefficients for ${\Vert x_k - v_{k - 1}\Vert^2}$: 
+            \begin{align*}
+                \frac{(1 - \alpha_{k - 1})\gamma_{k - 1}}{2} - 
+                \frac{(1 - \alpha_{k - 1})^{2}\gamma_{k - 1}^{2}}{2\gamma_k}
+                &= 
+                \frac{(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
+                \left(
+                    \frac{\gamma_k}{2} - \frac{(1 - \alpha_{k - 1})\gamma_{k - 1}}{2}
+                \right)
+                \\
+                &= 
+                \frac{(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
+                \left(
+                    \frac{\gamma_k - (1 - \alpha_{k - 1})\gamma_{k - 1}}{2}
+                \right)
+                \\
+                &= 
+                \frac{(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
+                \left(
+                    \frac{
+                        \alpha_{k - 1}\mu
+                    }{2}
+                \right). 
+            \end{align*}
+        \end{proof}
+        \begin{remark}
+            The differences of the Canonical form is cosmetic compare results from Guler, and Acceleration proximal gradient. 
+            The arrangement is different because the inexact proximal inequality from \hyperref[lemma:lin-ixct-prox-ineq]{Lemma \ref*{lemma:lin-ixct-prox-ineq}} 
+            are anchored on different iterates.  
+        \end{remark}
+    \subsection{Controlling the errors}
+        The following theorem is Theorem A.8 from Lin's writing of Catalyst \cite{lin_universal_2015}. 
+        It stated the propagation of errors $\epsilon_k$ from the inexact proximal inequality to the descent condition $F(x_k) \le \phi_k^*$. 
+        \begin{theorem}[Controlling the error in Nesterov's estimating sequence]\;\\
+            If the auxiliary sequences $v_k, y_k, \gamma_k, \alpha_k$ satisfies the conditions: 
+            \begin{align*}
+                \gamma_k - (\kappa + \mu)\alpha_{k - 1}^2 
+                &= 0
+                \\
+                (1 - \alpha_{k - 1})\gamma_{k - 1} + \alpha_{k - 1}\mu 
+                &= (\kappa + \mu)\alpha_{k - 1}^2. 
+            \end{align*}
+            Then the canonical representation of estimating sequence $\phi_k^*$ and the function value 
+            the inexact proximal point iterates $F(x_k)$ satisfy for all $k\ge 1$
+            \begin{align*}
+                F(x_k) &\le \phi_k^* + \xi_k, 
+                \\
+                \xi_k &= 
+                (1 - \alpha_{k - 1})(
+                    \xi_{k - 1} + \epsilon_k 
+                    - (\kappa + \mu)\langle x_k - x_k^*, x_{k - 1} - x_k\rangle
+                ). 
+            \end{align*}
+            Where we have the base case that $\xi_0 = 0$
+        \end{theorem}
+        \begin{proof}
+            We prove it via induction. 
+            Base case is trivially satisfied via $\phi_0^* = F(x_0)$ and $\xi_0 = 0$. 
+            Inductively we assume that $F(x_{k - 1}) \le \phi_{k - 1}^* + \xi_k$. 
+            By definition, it means 
+            \begin{align}
+                \phi_{k - 1}^* &\ge 
+                F(x_{k - 1}) - \xi_{k - 1} 
+                \nonumber
+                \\
+                &\ge 
+                F(x_k) + 
+                \langle \kappa(y_{k - 1} - x_k), x_{k - 1} - x_k\rangle
+                + 
+                (\kappa + \mu)\langle x_k - x_k^*, x_{k - 1} - x_k\rangle
+                - \epsilon_k - \xi_{k - 1}
+                \nonumber
+                \\
+                &= 
+                F(x_k) + 
+                \langle \kappa(y_{k - 1} - x_k), x_{k - 1} - x_k\rangle
+                - (1 - \alpha_{k - 1})^{-1}\xi_k. 
+            \end{align}\label{app:c3-1}
+            Substituting it into the canonical form representation of the estimating sequence derived from the previous section, it has 
+            {\small
+            \begin{align}\begin{split}
+                \phi_k^* &= 
+                (1 - \alpha_{k - 1})\phi_{k - 1}^* 
+                + 
+                \alpha_{k - 1}F(x_k)
+                - 
+                \frac{\alpha_{k - 1}}{2\gamma_k}
+                \Vert \kappa(y_{k - 1} - x_k)\Vert^2
+                \\
+                &\quad 
+                + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
+                \left(
+                    \frac{\mu}{2}\Vert x_k - v_{k - 1}\Vert^2
+                    + \langle \kappa(y_{k - 1} - x_k), v_{k - 1} - x_k\rangle
+                \right)
+                \\
+                &\ge 
+                (1 - \alpha_{k - 1})
+                \left(
+                    F(x_k) + 
+                    \langle \kappa(y_{k - 1} - x_k), x_{k - 1} - x_k\rangle
+                    - (1 - a_{k - 1})^{-1}\xi_k
+                \right)
+                + 
+                \alpha_{k - 1}F(x_k)
+                    \\
+                    &\quad 
+                    + 
+                    \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
+                    \left(
+                        \frac{\mu}{2}\Vert x_k - v_{k - 1}\Vert^2
+                        + \langle \kappa(y_{k - 1} - x_k), v_{k - 1} - x_k\rangle
+                    \right)
+                    -
+                    \frac{\alpha_{k - 1}}{2\gamma_k}
+                    \Vert \kappa(y_{k - 1} - x_k)\Vert^2
+                \\
+                &= 
+                (1 - \alpha_{k - 1})\langle \kappa(y_{k - 1} - x_k), x_{k - 1} - x_k \rangle
+                - \frac{\alpha_{k - 1}}{2\gamma_k}\Vert \kappa(y_{k - 1} - x_k)\Vert^2
+                    \\
+                    & \quad 
+                    + 
+                    \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
+                    \left(
+                        \frac{\mu}{2}\Vert x_k - v_{k - 1}\Vert^2
+                        + 
+                        \left\langle 
+                            \kappa(y_{k - 1} - x_k), v_{k - 1} - x_k
+                        \right\rangle
+                    \right)+ F(x_k) - \xi_k
+                \\
+                &= 
+                (1 - \alpha_{k - 1})\left\langle 
+                    \kappa(y_{k - 1} - x_k), 
+                    \frac{
+                        \alpha_{k - 1}\gamma_{k - 1}
+                    }{
+                        \gamma_k
+                    }(v_{k - 1} - x_k) + x_{k - 1} - x_k
+                \right\rangle
+                - \frac{\alpha_{k - 1}}{2\gamma_k}\Vert \kappa(y_{k - 1} - x_k)\Vert^2
+                \\
+                    &\quad 
+                    + \frac{\mu\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}}{2\gamma_k}
+                    \Vert x_k - v_{k - 1}\Vert^2 + F(x_k) - \xi_k. 
+                \end{split}\label{app:c3-2}\end{align}
+            }
+            Next, we need to focus on the first 2 terms on the RHS
+            \begin{align}
+                (1 - \alpha_{k - 1})\left\langle 
+                    \kappa(y_{k - 1} - x_k), 
+                    \frac{
+                        \alpha_{k - 1}\gamma_{k - 1}
+                    }{
+                        \gamma_k
+                    }(v_{k - 1} - x_k) + x_{k - 1} - x_k
+                \right\rangle
+                - \frac{\alpha_{k - 1}}{2\gamma_k}\Vert \kappa(y_{k - 1} - x_k)\Vert^2. 
+            \end{align}\label{app:c3-3}
+            The first inner product term in \ref*{app:c3-3} has
+            \begin{align*}
+                & 
+                \left\langle 
+                    \kappa(y_{k - 1} - x_k),
+                    x_{k - 1} - y_{k - 1} 
+                    + 
+                    \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
+                    (v_{k - 1} - y_{k - 1} + y_{k - 1} - x_k) 
+                \right\rangle
+                \\
+                &= 
+                \left\langle 
+                    \kappa(y_{k - 1} - x_k), 
+                    x_{k - 1} - y_{k - 1}
+                    + 
+                    \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
+                    (v_{k - 1} - y_{k - 1})  
+                \right\rangle
+                \\ 
+                &\quad 
+                    + 
+                    \left\langle 
+                        \kappa(y_{k - 1} - x_k), 
+                        y_{k - 1} - x_k + 
+                        \frac{\alpha_{k - 1}\gamma_{k - 1}}
+                        {\gamma_k}
+                        (y_{k - 1} - x_k)
+                    \right\rangle
+                \\
+                &= 
+                \left\langle 
+                    \kappa(y_{k - 1} - x_k), 
+                    x_{k - 1} - y_{k - 1}
+                    + 
+                    \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
+                    (v_{k - 1} - y_{k - 1})  
+                \right\rangle
+                \\ 
+                &\quad 
+                    + 
+                    \kappa\left(
+                        1 + \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
+                    \right)
+                    \Vert v_{k - 1} - y_{k - 1}\Vert^2. 
+            \end{align*}
+            With the above \ref*{app:c3-3} simplifies to
+            \begin{align*}
+                &
+                (1 - \alpha_{k - 1})\left\langle 
+                    \kappa(y_{k - 1} - x_k), 
+                    x_{k - 1} - y_{k - 1}
+                    + 
+                    \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
+                    (v_{k - 1} - y_{k - 1})  
+                \right\rangle
+                \\
+                    & 
+                    - \frac{\alpha_{k - 1}}{2\gamma_k}
+                    \Vert \kappa(y_{k - 1} - x_k)\Vert^2
+                    + 
+                    \kappa(1 - \alpha_{k - 1})\left(
+                        1 + \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
+                    \right)
+                    \Vert v_{k - 1} - y_{k - 1}\Vert^2
+                \\
+                &=
+                (1 - \alpha_{k - 1})
+                \left\langle 
+                    \kappa(y_{k - 1} - x_k), 
+                    x_{k - 1} - y_{k - 1}
+                    + 
+                    \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
+                    (v_{k - 1} - y_{k - 1})  
+                \right\rangle
+                    \\
+                    &\quad 
+                    + 
+                    (1 - \alpha_{k - 1})\kappa\left(
+                        1 + \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
+                        - \frac{\kappa\alpha_{k - 1}}{2\gamma_k}
+                    \right)
+                    \Vert y_{k - 1} - x_k\Vert^2. 
+            \end{align*}
+            We can simplify the coefficient of $\Vert y_{k - 1} - x_k\Vert^2$ in the above expression by the recurrence of parameter $\gamma_k$ from the canonical form of estimating sequence. 
+            \begin{align*}
+                &
+                (1 - \alpha_k)\kappa\left(
+                    1 + \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
+                    - \frac{\kappa\alpha_{k - 1}}{2\gamma_k}
+                \right)
+                \\
+                &=
+                \kappa\left(
+                    1 - \alpha_{k - 1} + 
+                    \frac{(1 - \alpha_{k - 1})\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
+                    - \frac{\alpha_{k - 1}^2\kappa}{2\gamma_k}
+                \right)
+                \\
+                & \text{Use: }\gamma_k - \alpha_{k - 1}\mu = (1 - \alpha_{k - 1})\gamma_{k - 1}
+                \\
+                &= 
+                \kappa\left(
+                    1 - \alpha_{k - 1} 
+                    + 
+                    \frac{(\gamma_k - \alpha_{k - 1}\mu)\alpha_{k - 1}}{\gamma_k}
+                    - 
+                    \frac{\alpha_{k - 1}^2\kappa}{2\gamma_k}
+                \right)
+                \\
+                &= \kappa
+                \left(
+                    1 + 
+                    \frac{
+                        -2\gamma_k\alpha_{k - 1}
+                        + 2(\gamma_k - \alpha_{k - 1}\mu)\alpha_{k - 1}
+                        - \alpha_{k - 1}^2\kappa
+                    }{
+                        2\gamma_k
+                    }
+                \right)
+                \\
+                &= \kappa
+                \left(
+                    1 + \frac{-2\alpha_{k + 1}^2\mu - \alpha_{k - 1}^2\kappa}{2\gamma_k}
+                \right)
+                \\
+                &= 
+                \kappa\left(
+                    1 - \frac{(2\mu + \kappa)\alpha_{k - 1}^2}{2\gamma_k}
+                \right)
+                \\
+                &= 
+                \kappa\left(
+                    1 - \frac{(\mu + \kappa/2)\alpha_{k - 1}^2}{\gamma_k}
+                \right). 
+            \end{align*}
+            Now, substitute the above back to \ref*{app:c3-3} and then substitute \ref*{app:c3-3} back to \ref*{app:c3-2} to get:
+            {\small
+            \begin{align*}
+                \phi_k^* 
+                &\ge 
+                (1 - \alpha_{k - 1})
+                \left\langle 
+                    \kappa(y_{k - 1} - x_k), 
+                    x_{k - 1} - y_{k - 1}
+                    + 
+                    \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
+                    (v_{k - 1} - y_{k - 1})  
+                \right\rangle
+                    \\
+                    &\quad 
+                    + 
+                    \kappa\left(
+                        1 - \frac{(\mu + \kappa/2)\alpha_{k - 1}^2}{\gamma_k}
+                    \right)
+                    \Vert y_{k - 1} - x_k\Vert^2
+                    + \frac{\mu\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}}{2\gamma_k}
+                    \Vert x_k - v_{k - 1}\Vert^2 + F(x_k) - \xi_k
+                \\
+                &\ge 
+                (1 - \alpha_{k - 1})
+                \left\langle 
+                    \kappa(y_{k - 1} - x_k), 
+                    x_{k - 1} - y_{k - 1}
+                    + 
+                    \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
+                    (v_{k - 1} - y_{k - 1})  
+                \right\rangle
+                    \\
+                    &\quad 
+                    + 
+                    \kappa\left(
+                        1 - \frac{(\mu + \kappa/2)\alpha_{k - 1}^2}{\gamma_k}
+                    \right)
+                    \Vert y_{k - 1} - x_k\Vert^2
+                    + 
+                    \Vert x_k - v_{k - 1}\Vert^2 + F(x_k) - \xi_k. 
+            \end{align*}
+            }
+            To assert the inductive hypothesis $F(x_k) \le \phi_k^*$ it's sufficient to have the inner product term equals to zero, and the coefficient of $\Vert y_k - x_k\Vert$ to be non-negative. 
+            Therefore, it suffices to consider 
+            \begin{align*}
+                x_{k - 1} - y_{k - 1}
+                + 
+                \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
+                (v_{k - 1} - y_{k - 1}) 
+                &= 
+                \mathbf 0, 
+                \\
+                1 - \frac{(\kappa/2 + \mu)\alpha_{k - 1}^2}{\gamma_k}
+                \le 
+                1 - (\kappa + \mu)\frac{\alpha_{k - 1}^2}{\gamma_k} 
+                & \le 0. 
+            \end{align*}
+            In addition, if we assume equality holds then it gives: 
+            \begin{align*}
+                \gamma_k - (\kappa + \mu)\alpha_{k - 1}^2 
+                &= 0
+                \\
+                (1 - \alpha_{k - 1})\gamma_{k - 1} + \alpha_{k - 1}\mu 
+                &= (\kappa + \mu)\alpha_{k - 1}^2. 
+            \end{align*}
+        \end{proof}
+        \begin{remark}
+            For all $k \ge 1$, with vector $x_k, v_k$ and scalar $\gamma_k, \alpha_k$ given, the updates for $x_{k + 1}, y_{k + 1}, v_{k + 1}$ and $\gamma_{k + 1}$ are produced by: 
+            \begin{align*}
+                \gamma_{k + 1} &= (1 - \alpha_{k})\gamma_k + \alpha_k \mu = (\kappa + \mu)\alpha_{k - 1}^2
+                \\
+                y_k &= (\gamma_k + \alpha_k \mu)^{-1}
+                (\alpha_k \gamma_k v_k + \gamma_{k + 1}x_k)
+                \\
+                \tilde x_{k + 1} &\approx \mathcal J_{\kappa^{-1}} y_{k} 
+                \text{ s.t: } 
+                \mathcal M^{\kappa^{-1}}(x_{k + 1}, y_k) - 
+                \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k} , y_k) \le \epsilon_k
+                \\
+                \widetilde{\mathcal G}_{\kappa^{-1}} y_k &= \kappa(y_k - \tilde x_{k + 1})
+                \\
+                x_{k + 1} &= y_k - \widetilde{\mathcal G}_{\kappa^{-1}} y_k
+                \\
+                v_{k + 1} &= 
+                \gamma_{k + 1}^{-1}\left(
+                    (1 - \alpha_k)\gamma_k v_k + 
+                    \alpha_k(\mu + \kappa)x_k 
+                    - \alpha_k \kappa y_k
+                \right)
+                \\
+                &= \gamma_{k + 1}^{-1}(
+                    (1 - \alpha_k)\gamma_k v_k + \alpha_k\mu x_k + 
+                    \alpha_k\kappa(x_k - y_k)
+                )
+                \\
+                &= 
+                \gamma_{k + 1}^{-1}\left(
+                    (1 - \alpha_k)\gamma_k v_k + \alpha_k\mu x_k - \alpha_k 
+                    \widetilde{\mathcal G}_{\kappa^{-1}}y_k
+                \right). 
+            \end{align*}
+            In terms of just the formatting of updates on $(v_k, y_k, x_k)$, $\alpha_k, \gamma_k$ are conducted, it's exactly the same as the Accelerated proximal gradient algorithm proved back in 
+            \hyperref[app:sec:thm-claim-acc-prox-grad]{Section \ref*{app:sec:thm-claim-acc-prox-grad}}, but with $L = \kappa + \mu$ and $\tilde x_{k + 1}$ produced by the inexact proximal point instead of proximal gradient.
+            The results on the equivalent representations of the accelerated proximal gradient algorithm from the previous section will apply for this the Catalyst as well. 
+            Therefore, by analysis from previous section, we also have for all $k \ge 0$: 
+            \begin{align*}
+                y_k &= x_k + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})}{\alpha_{k - 1}^2 + \alpha_k}
+                (x_k - x_{k - 1}).
+            \end{align*}
+            Lin's innovation of the inexact proximal inequality allows us to roll the error from the inexact proximal point into $\xi_k$ to characterize the descent of the sequence $x_k \approx \mathcal J_{\kappa^{-1}}y_{k - 1}$.
+            It undoubtedly improved the results from Lemma 3.2 of Guler's paper in 1992 \cite{guler_new_1992}. 
+        \end{remark}
 
 \section{Proofs for 4WD Catalyst Acceleration}
+    In this section we adopt the same notations as in 
+    \hyperref[sec:4wd-catalyst]{Section \ref*{sec:4wd-catalyst}}. 
     We prove
@@
     The lemma below characterize the lower and upper bound on the $(\alpha_k)_{k \ge 0}$ which ultimately control the convergence rate. 
-    \begin{lemma}\label{app:lemma:momentum-sequence-bounds}
-
+    \begin{lemma}[Bounds of the inverted FISTA sequence]\label{app:lemma:momentum-sequence-bounds}
+        With base case $\alpha_1 = 1$
+        If the sequence $\alpha_k$ has for all $k\ge 1$: 
+        \begin{align*}
+            \alpha_{k + 1} = \frac{\sqrt{\alpha_k^4 + 4\alpha_k^2} - \alpha_k^2}{2}, \alpha_1 = 1
+        \end{align*}
+        then for all $k \ge0$: 
+        \begin{align*}
+            \frac{\sqrt{2}}{k + 1} \le \alpha_k \le \frac{2}{k + 1}. 
+        \end{align*}
     \end{lemma}
+    \begin{proof}
+        The proof of the upper bound is by inductive hypothesis, assume $\alpha_k \ge 2/(k + 1)$ then consider
+        \begin{align*}
+            \alpha_{k + 1} &= 
+            \frac{\sqrt{\alpha_k^4 + 4 \alpha_k^2} - \alpha_k^2}{2}
+            = 
+            \frac{\sqrt{\alpha_k^4 + 4 \alpha_k^2} - \alpha_k^2}{2}
+            \frac{\sqrt{\alpha_k^4 + 4 \alpha_k^2} + \alpha_k^2}{\sqrt{\alpha_k^4 + 4 \alpha_k^2} + \alpha_k^2}
+            \\
+            &= \frac{\alpha_k^4 + 4\alpha_k^2 - \alpha_k^4}{2(\sqrt{\alpha_k^4 + 4 \alpha_k^2)} + \alpha_k^2)}
+            \\
+            &= \frac{2}{\sqrt{1 + 4 \alpha_k^{-2}} + 1} 
+            \le \frac{2}{\sqrt{1 + (k + 1)^2} + 1} \le \frac{2}{k + 2}. 
+        \end{align*}
+        The lower bound is given by the hidden recursive definition of $\alpha_k$: 
+        \begin{align*}
+            \alpha_{k + 1}^2 &= (1 - \alpha_{k + 1})\alpha_k^2 = \alpha_1^2
+            \\
+            &\ge \alpha_1^2 \prod_{i = 2}^{k + 1}(1 - \alpha_i)
+            \\
+            &\ge \prod_{i = 2}^{k + 1}\left(
+                1 - \frac{2}{i + 1}
+            \right) = \prod_{i = 2}^{k + 1} \left(\frac{i - 1}{i + 1}\right)
+            \\
+            &= \frac{2}{(k + 1)(k + 2)}  \ge \frac{2}{(k + 2)^2}. 
+        \end{align*}
+    \end{proof}
+    \begin{remark}
+        $a_k^{-1}$ would just be the FISTA sequence. 
+    \end{remark}
+
+    \begin{lemma}[Stationarity condition]\label{app:lemma:ncnvx-catalyst-stationary-cond}
+        Assume $F$ is $\rho$ weakly convex. 
+        Fix any $y$, suppose that $y^+$ satisfies $\dist(\mathbf 0,\partial \mathcal M^{k^{-1}}(y^+; y)) \le \epsilon$ then the following inequality holds: 
+        \begin{align*}
+            \dist(\mathbf 0; \partial F(y^+)) 
+            \le \epsilon + \kappa\Vert y^+ - y\Vert. 
+        \end{align*}
+    \end{lemma}
+    \begin{proof}
+        Take it as a fact that the limiting subgradient of a weakly convex function is a closed set. 
+        Fix any $y$, there exists $w \in \partial \mathcal M(y^+; y)$ such that $\dist(\mathbf 0; \partial {\mathcal M}(y^+; y)) = \Vert w\Vert$ because $\partial M(\cdot;y)$ is a $\rho - \kappa$ weakly convex function.
+        Next, by definition we have
+        \begin{align*}
+            w &\in \partial F(y^+) + \kappa(y^+ - y)
+            \\
+            \iff 
+            \exists v &
+            \in \partial  F(y^+): 
+            w = v + \kappa(y^+ - y)
+            \\
+            \implies 
+            \epsilon &= 
+            \Vert w\Vert = \Vert v + \kappa(y^+ - y)\Vert 
+            \ge \Vert v\Vert - \Vert \kappa(y^+ - y)\Vert
+            \\
+            \implies 
+            \dist(\mathbf 0, \partial F(y^+)) &\le 
+            \Vert v\Vert 
+            \le \epsilon + \Vert \kappa(y^+ - y)\Vert. 
+        \end{align*}
+
+    \end{proof}
+    \subsection{Convergence proof of the basic 4WD-Catalyst}
+        This subsection proves 
+        \hyperref[thm:basic-4wd-catalyst]{Theorem \ref*{thm:basic-4wd-catalyst}}
+        which is about the convergence of 
+        \hyperref[def:basic-4wd-catalyst]{Definition \ref*{def:basic-4wd-catalyst}}.
+
+        For any $k \ge 1$, the algorithm asserts 
+        \begin{align*}
+            F(x_{k - 1}) \ge \mathcal M(\bar x_k, x_{k - 1}) \ge 
+            F(x_k) + \frac{\kappa}{2}\Vert \bar x_k - x_{k - 1}\Vert^2. 
+        \end{align*}
+        Use Lemma \ref*{app:lemma:ncnvx-catalyst-stationary-cond} with $\epsilon = \kappa \Vert \bar x_k - x_{k - 1}\Vert$, $y = x_{k - 1}$, $y^+ = \bar x_k$ then 
+        \begin{align*}
+            \dist(\mathbf 0, \partial F(\bar x_k)) \le 2 \kappa \Vert \bar x_k - x_{k - 1} \Vert. 
+        \end{align*}
+        With $F$ bounded below, denote $F^*$ to be the minimum then using the two results above: 
+        \begin{align*}
+            F(x_{k - 1}) - F(x_k) 
+            &\ge \frac{\kappa}{2}\Vert \bar x_k - x_{k - 1}\Vert^2
+            \\
+            8 \kappa (F(x_{k - 1}) - F(x_k)) &\ge 4 \Vert \kappa (\bar x_k - x_{k - 1})\Vert^2 \ge 
+            \dist^2(\mathbf 0, \partial F(\bar x_k))
+            \\
+            \implies 
+            \dist^2(\mathbf 0, \partial F(\bar x_k)) 
+            &\le 
+            8 \kappa (F(x_{k - 1}) - F(x_k))
+            \\
+            \implies 
+            \min_{j = 1, \cdots, N} \dist^2(\mathbf 0, \partial F(\bar x_j))
+            &\le 
+            \frac{8\kappa}{N}
+            \sum_{j = 1}^{N} F(x_{j - 1}) - F(x_j)
+            \\
+            &\le 
+            \frac{8 \kappa}{N} (F(x_0) - F(x_N)) 
+            \le \frac{8 \kappa}{N}(F(x_0) - F^*). 
+        \end{align*}
+        Therefore, the set limits of $\partial F(\bar x_j)$ contains $\mathbf 0$. 
+        The second part of the claim about the convergence to optimality requires additional assumptions that 
+        \begin{enumerate}
+            \item $F$ is convex. 
+            \item $F$ is bounded below and has a minimizer $x^*$. 
+        \end{enumerate}
+        From the algorithm we have $\xi_k \in \partial \mathcal M(\tilde x_k, y_k)$ such that $\Vert \xi_k\Vert \le \frac{\kappa}{k + 1}\Vert \tilde x_k - y_k\Vert$. 
+        Then for any $x\in \RR^n$, $\kappa$ strong convexity of $\mathcal M(\cdot, y_k)$ yields inequality: 
+        {\small
+        \begin{align*}
+            0 &\le
+            F(x) + \frac{\kappa}{2}\Vert x - y_k\Vert^2 
+            - \left(
+                F(\tilde x) 
+                + \frac{\kappa}{2}\Vert \tilde x_k - y_k\Vert^2
+            \right)
+            - \frac{\kappa}{2}\Vert x - \tilde x_k\Vert^2 
+            - \langle \xi_k, x - \tilde x_k\rangle
+            , 
+            \\
+            F(x_k)
+            \le F(\tilde x_k) 
+            &\le 
+            F(x) + \frac{\kappa}{2}\left(
+                \Vert x - y_k\Vert^2 - \Vert x - \tilde x_k\Vert^2 - \Vert \tilde x_k - y_k\Vert^2
+            \right)
+            + \langle  \xi_k, \tilde x_k - x \rangle 
+            \\
+            &\le 
+            F(x) + \frac{\kappa}{2}\left(
+                \Vert x - y_k\Vert^2 - \Vert x - \tilde x_k\Vert^2 - \Vert \tilde x_k - y_k\Vert^2
+            \right)
+            + \frac{\kappa}{k + 1}\Vert \tilde x_k - y_k\Vert\Vert x - \tilde x_k\Vert. 
+        \end{align*}
+        }
+        Sure, now observe that with the substitutions $x = \alpha_k x^* + (1 - \alpha_k) x_{k-1}$ where $x^*$ is the minimizer then
+        \begin{align*}
+            x - y_k
+            &= 
+            \alpha_k x^* + (1 - \alpha_k) x_{k - 1} - y_k 
+            \\
+            &= \alpha_k x^* + (1 - \alpha_k) x_{k - 1} - (\alpha_k v_{k - 1} + (1 - \alpha_k)x_{k - 1})
+            \\
+            &= \alpha_k (x^* - v_{k - 1}), 
+            \\
+            x - \tilde x_k 
+            &= 
+            \alpha_k x^* + (1 - \alpha_k) x_{k - 1} - \tilde x_k
+            \\
+            &\quad 
+            \textcolor{gray}{
+            \begin{aligned}
+                v_{k} &= x_{k - 1} + \alpha_k^{-1}(\tilde x_k - x_{k - 1})
+                \\
+                \tilde x_k - x_{k - 1} &= \alpha_k(v_k - x_{k - 1})
+                \\
+                \tilde x_k &= x_{k - 1} + \alpha_k(v_k - x_{k - 1})
+            \end{aligned}
+            }
+            \\
+            &= 
+            \alpha_k x^* + (1 - \alpha_k) x_{k - 1} - (x_{k - 1} + \alpha_k(v_k - x_{k - 1}))
+            \\
+            &= \alpha_k x^* - \alpha_k x_{k - 1} - \alpha_k(v_k - x_{k - 1})
+            \\
+            &= \alpha_k (x^* - v_k). 
+        \end{align*}
+        Using convexity, it transform the inequality into 
+        \begin{align*}
+            F(x_k) &\le 
+            \alpha_k F(x^*) + (1 - \alpha_k) F(x_{k - 1}) 
+            + \frac{\alpha_k^2\kappa}{2}\left(
+                \Vert x^* - v_{k - 1}\Vert^2 - 
+                \Vert v_k - x^*\Vert^2
+            \right)
+            \\
+            &\quad 
+                - \frac{\kappa}{2}\Vert \tilde x_k - y_k\Vert^2 
+                + \frac{\kappa \alpha_k}{k + 1}\Vert \tilde x - y_k\Vert\Vert v_k - x^*\Vert
+            \\
+            &=
+            \alpha_k F(x^*) + (1 - \alpha_k) F(x_{k - 1}) 
+            + \frac{\alpha_k^2\kappa}{2}\left(
+                \Vert x^* - v_{k - 1}\Vert^2 - 
+                \Vert v_k - x^*\Vert^2
+            \right)
+                \\
+                &\quad 
+                - \frac{\kappa}{2}\left(
+                    \Vert \tilde x_k - y_k\Vert
+                    - \frac{\alpha_k}{k + 1}\Vert v_k - x^*\Vert
+                \right)^2 
+                + \frac{\kappa}{2}\left(\frac{\alpha_k}{k + 1}\right)^2\Vert v_k - x^*\Vert^2
+            \\ 
+            &\le 
+            \alpha_k F(x^*) + (1 - \alpha_k) F(x_{k - 1}) 
+            + \frac{\alpha_k^2 \kappa}{2}\left(
+                \Vert x^* - v_{k - 1}\Vert^2 - 
+                \Vert v_k - x^*\Vert^2
+            \right)
+                \\
+                &\quad  
+                + \frac{\kappa \alpha_k^2}{2}\left(\frac{1}{k + 1}\right)^2\Vert v_k - x^*\Vert^2
+            \\
+            \iff 
+            F(x_k) - F^*
+            &\le 
+            (1 - \alpha_k)(F(x_{k - 1}) - F^*)
+            \\ &\quad 
+                + 
+                \frac{\alpha_k^2\kappa}{2}
+                \left(
+                    \Vert x^* - v_{k - 1}\Vert^2
+                    - \left(
+                        1 - \frac{1}{(k + 1)^2}
+                    \right)\Vert v_k - x^*\Vert^2
+                \right)
+        \end{align*}
+        Denote $A_k := 1 - 1/(1 + k)^2$ to simplify the notations. 
+        Continue the simplifications of the above inequality
+        {\footnotesize
+        \begin{align*}
+            F(x_k) - F^* +
+            \frac{\alpha_k^2\kappa}{2}\left(
+                1 - \frac{1}{(k + 1)^2}
+            \right)
+            \Vert v_k - x^*\Vert^2
+            &\le 
+            (1 - \alpha_k)(F(x_{k - 1}) - F^*)
+            + 
+            \frac{\alpha_k^2\kappa}{2}
+            \Vert x^* - v_{k - 1}\Vert^2
+            \\
+            \iff 
+            \alpha_k^{-2}(F(x_k) - F^*)
+            + 
+            \frac{\kappa A_k}{2}\Vert v_k - x^*\Vert^2
+            &\le 
+            \alpha_k^{-2}(1 - \alpha_k)(F(x_{k - 1}) - F^*)
+            + 
+            \frac{\kappa}{2}
+            \Vert x^* - v_{k - 1}\Vert^2
+            \\
+            \iff
+            \alpha_k^{-2}(F(x_k) - F^*)
+            + 
+            \frac{\kappa A_k}{2}\Vert v_k - x^*\Vert^2
+            &\le 
+            \alpha_{k - 1}^{-2}(F(x_{k - 1}) - F^*)
+            + 
+            \frac{\kappa}{2}
+            \Vert x^* - v_{k - 1}\Vert^2
+            \\
+            & \le 
+            \frac{1}{A_{k - 1}}\left(
+                \alpha_{k - 1}^{-2}(F(x_{k - 1}) - F^*)
+                + 
+                \frac{\kappa A_{k - 1}}{2}
+                \Vert x^* - v_{k - 1}\Vert^2
+            \right). 
+        \end{align*}
+        }
+        The second last inequality use the fact that $(1 - \alpha_k)/\alpha_k^2 = \alpha_{k - 1}^{-2}$ and $\alpha_1 = 1$. 
+        The last inequality used the fact that $A_{k - 1} \in (0, 1]$. 
+        Simplifying a bit the above is the same as for all $k\ge 1$: 
+        \begin{align*}
+            \alpha_{k + 1}^{-2}(F(x_{k + 1}) - F^*) 
+            + \frac{\kappa A_k}{2}\Vert v_k - x^*\Vert^2
+            &\le 
+            \frac{1}{A_k}\left(
+                \alpha_k^{-2}(F(x_k) - F^*) + \frac{\kappa A_k}{2}\Vert v_{k} - x^*\Vert^2
+            \right)
+            \\
+            & \le
+            \left(
+                \prod_{i = 1}^k A_i^{-1}
+            \right)\left(
+                \underbrace{
+                    \alpha_1^2 (F(x_1) - F^*) + \frac{\kappa A_1}{2}\Vert v_1 - x^*\Vert^2
+                }
+                _{=:C}
+            \right)
+            \\
+            \implies 
+            \alpha_{k + 1}^{-2}(F(x_{k + 1}) - F^*)
+            &\le 
+            \left(
+                \prod_{i = 1}^k A_i^{-1}
+            \right) C
+            \\
+            F(x_{k + 1}) - F^* 
+            &\le 
+            \alpha_{k + 1}^2\left(
+                \prod_{i = 1}^k A_i^{-1}
+            \right) C. 
+        \end{align*}
+        Fortunately we have the big product bounded because 
+        \begin{align*}
+            \prod_{i = 1}^{k} A_{j}^{-1}
+            &= 
+            \prod_{i = 1}^{k} \left(
+                1 - \frac{1}{(i + 1)^2}
+            \right)^{-1}
+            \\
+            &= \left(
+                \prod_{i = 1}^{k} \left( \frac{(i + 1)^2 - 1}{(i + 1)^2}\right)
+            \right)^{-1} = 
+            \left(
+                \prod_{j = 2}^{k} 
+                \left(
+                    \frac{j^2 - 1}{j^2}
+                \right)
+            \right)^{-1}
+            \\
+            & = \exp\left(
+                \sum_{j = 2}^{k + 1}
+                \log\left(
+                    \frac{j + 1}{j}
+                \right) - \log\left(
+                    \frac{j}{j - 1}
+                \right)
+            \right)^{-1}
+            \\
+            &= \left(\exp\circ \log
+                \left(\frac{k + 3}{k + 2}\frac{1}{2}\right)\right)^{-1} 
+            \le \left(
+                \frac{1}{2}
+            \right)^{-1}= 2. 
+        \end{align*}
+        Therefore 
+        \begin{align*}
+            F(x_{k + 1}) - F^* \le \alpha_{k + 1}^2 2C\le \frac{4C}{(k + 1)^2}. 
+        \end{align*}
+        Which indicates that under controlled inexact evaluations of the inexact proximal step for $\tilde x_k$ and $\bar x_k$, the basic 4WD Catalyst achieves optimal convergence when $F$ is convex, and it can minimize the limiting subgradient when the function is weakly convex.
+        \begin{remark}
+            One may use KL-Convergence framworks to strengthens the convergence claim of the Catalyst by establishing convergence to a limiting stationary point. 
+        \end{remark}
 

### 2024-11-20 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
         \end{align*}
-        Using convexity, it transform the inequality into 
+        Using convexity, it transforms the inequality into 
         \begin{align*}
@@
         }
-        The second last inequality use the fact that $(1 - \alpha_k)/\alpha_k^2 = \alpha_{k - 1}^{-2}$ and $\alpha_1 = 1$. 
+        The second last inequality uses the fact that $(1 - \alpha_k)/\alpha_k^2 = \alpha_{k - 1}^{-2}$ and $\alpha_1 = 1$. 
         The last inequality used the fact that $A_{k - 1} \in (0, 1]$. 
@@
         \end{align*}
-        Therefore 
+        Therefore, 
         \begin{align*}
@@
         \begin{remark}
-            One may use KL-Convergence framworks to strengthens the convergence claim of the Catalyst by establishing convergence to a limiting stationary point. 
+            One may use KL-Convergence frameworks to strengthen the convergence claim of the Catalyst by establishing convergence to a limiting stationary point. 
         \end{remark}

### 2024-11-20 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
     \begin{remark}
-        The goal of having $\phi_k^*$ represented by iterates $v_k, y_k, g_k$ is because it assists in the future when an inductive hypothesis $\phi_k^* \ge f(x_k) \ge l_F(x_k; y_k) + \frac{\mu}{2}\Vert x - y_k\Vert^2$ is made.
+        The goal of having $\phi_k^*$ represented by iterates $v_k, y_k, g_k$ is because it assists in the future when an inductive hypothesis $\phi_k^* \ge F(x_k) \ge l_F(x_k; y_k) + \frac{\mu}{2}\Vert x - y_k\Vert^2$ is made.
         We did things in advance here, nothing more. 

### 2024-11-21 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
         Guler didn't simplify his results compare to what Nesterov did in his book. 
-        For a detailed proofs of the estimating sequence with comparison to the accelerated proximal gradient method, see Appendix \ref*{sec:app:exct-acc-ppm}. 
+        For a detailed proof of the estimating sequence with comparison to the accelerated proximal gradient method, see Appendix \ref*{sec:app:exct-acc-ppm}. 
     \end{remark}
@@
     The new algorithm handles function with unknown weak convexity constant $\rho$ using a process called Auto Adapt subroutine. 
-    They only claimed convergence to stationary point is claimed for the weakly convex objective. 
+    They only claimed convergence to stationarity for a weakly convex objective. 
     \par 
@@
         Let $(x_k, v_k, y_k)$ be generated by the basic Catalyst algorithm. 
-        If $F$ is $\kappa$ weakly convex and bounded below, then $x_k$ converges to a stationary point where
+        If $F$ is $\kappa$ weakly convex and bounded below, then $x_k$ converges to stationarity where
         \begin{align*}
@@
     \begin{remark}
-
+        Convergence to stationarity is strictly weaker than convergence to any stationarity point of $F$. 
+        Read 
+        \hyperref[app:sec:ncnvx-catalyst]{Section \ref*{app:sec:ncnvx-catalyst}} for more information on proof of this claim. 
     \end{remark}
@@
 \appendix
-\section{Appendix}
-
-\subsection{Theorems and claims for accelerated proximal gradient}\label{app:sec:thm-claim-acc-prox-grad}
+\section{Theorems and claims for accelerated proximal gradient}\label{app:sec:thm-claim-acc-prox-grad}
     Throughout this section, $F = g + f$ is an additive composite objective function with $g$ convex, $f$ $L$-lipschitz smooth and $\mu \ge0$ strongly convex. 
@@
 
-\section{Proofs for 4WD Catalyst Acceleration}
+\section{Proofs for 4WD Catalyst Acceleration}\label{app:sec:ncnvx-catalyst}
     In this section we adopt the same notations as in 
@@
     \end{proof}
+
     \subsection{Convergence proof of the basic 4WD-Catalyst}
@@
         \begin{remark}
-            One may use KL-Convergence frameworks to strengthen the convergence claim of the Catalyst by establishing convergence to a limiting stationary point. 
+            It's tempting to think whether KL conditions assists with convergence to a stationary point for Nesterov's accelerated gradient method. 
+            Surveys conducted by the writer in the literatures showed that this remains a huge mystery in general. 
         \end{remark}

### 2024-11-23 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, updated

@@
     This technique is fundamental for in Guler's accelerated PPM method and Catalyst meta acceleration in the convex/strongly convex case. 
-    \subsection{Method of Nesterov's Estimating Sequence}
+    Unlike proofs using a Lyapunov argument which requires knowing exactly the algorithm in advance to verify the convergence rate, Nesterov's estimating squence can produce an algorithm that generates iterates $(x_k)_{k \ge0}$ such that it converges at some rate.
+    \subsection{Nesterov's Estimating Sequence}
         \begin{definition}[Nesterov's estimating sequence]\label{def:nes-est-seq}
@@
             \begin{enumerate}
-                \item There exists another sequence $(x_k)_{k \ge 0}$ such that for all $k \ge 0$ it has $F(x_k) \le \phi_k^*: =\min_{x}\phi_k^*(x)$. 
+                \item There exists another sequence $(x_k)_{k \ge 0}$ such that for all $k \ge 0$ it has $F(x_k) \le \phi_k^*: =\min_{x}\phi_k(x)$. 
                 \item There exists a sequence of $(\alpha_k)_{k \ge 0}$ where $\alpha_k \in (0, 1)\; \forall k \ge0 $ such that for all $x \in \RR^n$ it has $\phi_{k + 1}(x) - \phi_k(x) \le - \alpha_k(\phi_k(x) - F(x))$.
@@
 
-\section{Guler 1993}
-    This section introduces the setup of the Nesterov's estimating sequence used in Guler's accelerated Proximal Point method. 
-    Guler showed Nesterov's estimating sequence technique can accelerate proximal point method from Rockafellar in the convex settings.
-
-    Throughout this section, we assume that $F:\RR^n \rightarrow \overline \RR$ is a convex function. 
-    We use the following list of notations: 
-    \begin{align*}
-        \mathcal M^{\lambda} (x; y) &:= F(x) + \frac{1}{2\lambda}\Vert x - y\Vert^2
-        \\
-        \mathcal J_\lambda y &:= \argmin_x \mathcal M^{\lambda} (x; y)
+\section{Guler's estimating sequence}
+    This section introduces the setup of the estimating sequence in Guler's accelerated Proximal Point method \cite{guler_new_1992}. 
+    Guler showed the technique can accelerate proximal point method in the convex settings. 
+    Throughout the section, assume that $F:\RR^n \rightarrow \overline \RR$ is a convex function. 
+    Define:
+    \begin{align*}
+        \mathcal M^{\lambda} (x; y) &:= F(x) + \frac{1}{2\lambda}\Vert x - y\Vert^2, 
+        \\
+        \mathcal J_\lambda y &:= \argmin_x \mathcal M^{\lambda} (x; y), 
         \\
@@
     \end{align*}
-    For notations simplicity, we use $\mathcal G_k, \mathcal J_k$ to denote the gradient mapping and the proximal point operator because under the context of the algorithm, the proximal point step is conductive iteratively with some arbitrary sequence that $(\lambda)_{k \ge 0}$ which we fixed at the start.
+    For simplicity, we use $\mathcal G_k, \mathcal J_k$ as short for $\mathcal G_{\lambda_k}, \mathcal J_{\lambda_k}$ where $(\lambda_k)_{k \ge 0}$ is a fixed sequence used in the proximal point on the $k$ iteration.
 
     \begin{definition}[Accelerated PPM estimating sequence]\label{def:nes-est-seq-acc-ppm}
-        The Nesterov's estimating sequence $(\phi_k)_{k \ge0}$ for the accelerated proximal point method is defined by the following recurrence for all $k \ge0$, any $A \ge 0$: 
-        \begin{align*}
-            \phi_0 &:= f(x_0) + \frac{A}{2}\Vert x - x_0\Vert^2, 
+        \; \\
+        The estimating sequence  $(\phi_k)_{k \ge0}$ for the accelerated proximal point method is defined by the following recurrence for all $k \ge0$, any $A \ge 0$: 
+        \begin{align*}
+            \phi_0(x) &:= f(x_0) + \frac{A}{2}\Vert x - x_0\Vert^2, 
             \\
@@
         Let $(\lambda_k)_{k \ge 0}$ be the step size which defines the descent sequence $x_k = \mathcal J_\lambda y_k$. 
-        Then the descent sequence $x_k$, along with the auxiliary vector sequence $(y_k, v_k)$, scalar sequence $(\alpha_k, A_k)_{k\ge 0}$ will be made to satisfy for all $k\ge0$, the conditions: 
+        Then for all $k \ge 0$, the descent sequence $x_k$, along with the auxiliary vector sequence $(y_k, v_k)$, scalar sequence $(\alpha_k, A_k)_{k\ge 0}$ are generated by: 
         \begin{align*}
@@
                 - A_k\lambda_k
-            \right) 
-            \\
-            y_k &= (1 - \alpha_k)x_k + \alpha_k v_k
+            \right), 
+            \\
+            y_k &= (1 - \alpha_k)x_k + \alpha_k v_k, 
             \\
@@
             &= 
-            v_k - \frac{\alpha_k}{A_{k + 1}\lambda_k}(y_k - \mathcal J_k y_k)
-            \\
-            A_{k + 1} &= (1 - \alpha_k)A_k, 
+            v_k - \frac{\alpha_k}{A_{k + 1}\lambda_k}(y_k - \mathcal J_k y_k), 
+            \\
+            A_{k + 1} &= (1 - \alpha_k)A_k. 
         \end{align*}
@@
     \end{remark}
-    To handle the inexact evaluation of the PPM, Guler cited Rockafellar \cite{rockafellar_monotone_1976} for condition (A') in his text which is the following: 
+    For the inexact evaluation of PPM, Guler cited Rockafellar \cite{rockafellar_monotone_1976} for condition (A') in his text which is the following: 
     \begin{align*}
@@
         If $x_k$ is an inexact proximal point evaluation of $x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1}$ such that there exists $\epsilon_k$ where $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k - 1}, y_{k - 1}) \le \epsilon_k$.
-        Denote $x_k^* = \mathcal J_{\kappa^{-1}} y_{k - 1}$ it has for all $x$: 
+        Denote $x_k^* = \mathcal J_{\kappa^{-1}} y_{k - 1}$, then it has for all $x$: 
         \begin{align*}
@@
         \begin{align*}
-            \phi_0 &:= F(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2, 
+            \phi_0(x) &:= F(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2, 
             \\
@@
         Let $(x_k, v_k, y_k)$ be generated by the basic Catalyst algorithm. 
-        If $F$ is $\kappa$ weakly convex and bounded below, then $x_k$ converges to stationarity where
+        If $F$ is $\kappa$ weakly convex and bounded below, then $x_k$ converges to stationary where
         \begin{align*}
@@
     \begin{remark}
-        Convergence to stationarity is strictly weaker than convergence to any stationarity point of $F$. 
+        Convergence to stationary is strictly weaker than convergence to any stationary point of $F$. 
         Read 
@@
     \begin{align*}
-        \mathcal M^{L^{-1}}(x; y) 
+        \mathcal M^{L^{-1}}(x; y),
         &:= 
-        F(x) + \frac{L}{2}\Vert x - y\Vert^2
-        \\
-        \widetilde{ \mathcal M}^{L^{-1}}(x; y) 
+        F(x) + \frac{L}{2}\Vert x - y\Vert^2,
+        \\
+        \widetilde{ \mathcal M}^{L^{-1}}(x; y) ,
         &:= g(x) + f(y) 
@@
         + 
-        \frac{L}{2}\Vert x - y\Vert^2
+        \frac{L}{2}\Vert x - y\Vert^2,
         \\
         \widetilde{\mathcal J}_{L^{-1}}y 
-        &:= \argmin_{x} \widetilde{\mathcal M}^{L^{-1}}(x; y)
+        &:= \argmin_{x} \widetilde{\mathcal M}^{L^{-1}}(x; y),
         \\
@@
         Let $F = f + g$, define the proximal gradient operator $\widetilde{\mathcal J}_{L^{-1}}$.  
-        Fix any $y$, we have for all $x \in \RR^n$: 
+        For any fixed $y$, we have for all $x \in \RR^n$: 
         \begin{align*}
@@
         \end{align*}
-        Next, since $\widetilde{\mathcal M}^{L^{-1}}(\cdot, y)$ is strongly convex, it has quadratic growth conditions on its minimizer. 
-        Denote $y^+ = \widetilde{\mathcal J}_{L^{-1}}y$ then: 
+        Next, since $\widetilde{\mathcal M}^{L^{-1}}(\cdot, y)$ is $L$-strongly convex, it has quadratic growth conditions on its minimizer $y^+$ where $y^+ := \widetilde{\mathcal J}_{L^{-1}}y$ so it implies:
         {\small
@@
             \\
-            \implies 
+            \iff
             \left(
@@
         The quadratic growth with respect to minimizer of the Moreau Envelope is used to derive the inequality, please take caution that this condition is strictly weaker than strong convexity of the Moreau Envelope, which could be made weaker than the strong convexity of $F$.
-        Compare the same theorems in older literatures, this proof doesn't use the subgradient inequality, making it appealing for generalizations outside convexity context. 
+        Compare the same theorem in older literatures, this proof doesn't use the subgradient inequality, making it appealing for generalizations outside convexity. 
     \end{remark}
@@
         \; \\
-        Denote $\phi_k:\RR^n \rightarrow\RR$ as a sequence of functions such that it satisfies recursively for all $k\ge 0$ the following conditions 
-        \begin{align*}
-            & g_k := L(y_k - \widetilde{\mathcal J}_{L^{-1}} y_k)
+        Denote $\phi_k:\RR^n \rightarrow\RR$ as a sequence of functions such that for all $k\ge 0$ it recursively satisfies the following conditions 
+        \begin{align*}
+            & g_k := L(y_k - \widetilde{\mathcal J}_{L^{-1}} y_k),
             \\
@@
             \\
-            & \alpha_k \in (0, 1)
+            & \alpha_k \in (0, 1),
             \\
@@
             := (1 - \alpha_k)\phi_k (x) + 
-            \alpha_k (l_F(x; y_k) + \mu/2\Vert x - y_k\Vert^2). 
-        \end{align*}
-        Where $(y_k)_{k\ge 0}$ is any auxiliary sequence. 
-        If we define the canonical form for $\phi_k$ as convex quadratic parameterized by positive sequence $(\gamma_k), \phi_k^*$ and 
-        \begin{align*}
-            \phi_k^* := \min_{x} \phi_k(x)
-            \\
-            \phi_k(x) := \phi_k^* + \frac{\gamma_k}{2}\Vert x - v_k\Vert^2.
-        \end{align*}
-        Then the auxiliary sequence $y_k, v_k$, parameters for the canonical form of estimating sequence must satisfy for all $k\ge 0$ these inequalities: 
+            \alpha_k (l_F(x; y_k) + \mu/2\Vert x - y_k\Vert^2), 
+        \end{align*}
+        where $(y_k)_{k\ge 0}$ any sequence. 
+        If we define the canonical form for $\phi_k$ as convex quadratic parameterized by positive sequence $(\gamma_k), \phi_k^*$:  
+        \begin{align*}
+            \phi_k(x) &:= \phi_k^* + \frac{\gamma_k}{2}\Vert x - v_k\Vert^2, 
+        \end{align*}
+        where $\phi_k^* := \min_{x} \phi_k(x)$. 
+        Then the auxiliary sequence $y_k, v_k$, parameters for the canonical form of estimating sequence must satisfy for all $k\ge 0$: 
         {\small
         \begin{align*}      
-            \gamma_{k + 1} &= (1 - \alpha_k) \gamma_k + \mu \alpha_k
+            \gamma_{k + 1} &= (1 - \alpha_k) \gamma_k + \mu \alpha_k,
             \\
             v_{k + 1} &= \gamma_{k + 1}^{-1}
-            (\gamma_k(1 - \alpha_k)v_k - \alpha_k g_k + \mu \alpha_k y_k)
+            (\gamma_k(1 - \alpha_k)v_k - \alpha_k g_k + \mu \alpha_k y_k),
             \\
@@
         The first recurrence for is discovered as $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$. 
-        Because $v_{k + 1}$ is the minimizer of $\phi_{k+ 1}$ by definition of the canonical form, solving $\nabla \phi_{k + 1}(x) = \mathbf 0 $ yields $v_{k + 1}$. 
-        This is obtained by considering the following: 
+        Because $v_{k + 1}$ is the minimizer of $\phi_{k+ 1}$ by definition of the canonical form, solving for $x$ in $\nabla \phi_{k + 1}(x) = \mathbf 0$ yields $v_{k + 1}$ by: 
         \begin{align*}
@@
             \iff 
-            v_{k + 1} &:= x=
+            v_{k + 1} := x&=
             \gamma_{k +1}^{-1} 
@@
         From the second and third equality we used $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$. 
-        Substituting the canonical form of $\phi_{k + 1}$ back to \textcolor{red}{(eqn1)}, choose $x = y_k$, it gives the following: 
+        Substituting the canonical form of $\phi_{k + 1}$ back to \textcolor{red}{(eqn1)}, choose $x = y_k$, it gives: 
         \begin{align*}
@@
         \end{align*}
-        Next move from Nesterov was to simplify the term $\Vert v_{k + 1} - y_k\Vert^2$. 
-        With that it produces: 
+        Next, we simplify $\Vert v_{k + 1} - y_k\Vert^2$ to get rid of $v_{k + 1}$. 
         \begin{align*}
@@
             \right)
-            \\
-            &
-            \textcolor{gray}{
-                \begin{aligned}
-                    \gamma_{k + 1} &=    
-                    (1 - \alpha_k)\gamma_k + \mu \alpha_k
-                    \\
-                    -(1 - \alpha_k)\gamma_k
-                    &= - \gamma_{k + 1} + \mu \alpha_k
-                \end{aligned}
-            }
             \\
@@
         \end{align*}
-        Next we have
+        From the second to third inequality, we used: 
+        \begin{align*}
+            \gamma_{k + 1} &=    
+                (1 - \alpha_k)\gamma_k + \mu \alpha_k
+                \\
+                \iff 
+                -(1 - \alpha_k)\gamma_k
+                &= - \gamma_{k + 1} + \mu \alpha_k. 
+        \end{align*}
+        Therefore, it has: 
         {\small
@@
         }
-
         Substitute it back to \textcolor{red}{(eqn2)} we have 
@@
                 + 
-                \left(
+                \frac{(1 - \alpha_k)\gamma_k}{2}
+                \left(
+                    \frac{\mu \alpha_k}{\gamma_{k + 1}}
+                \right)
+                \Vert v_k - y_k\Vert^2
+                - \frac{\alpha_k^2}{2\gamma_{k + 1}}\Vert g_k\Vert^2
+                \\
+                & \quad 
+                + \alpha_k\gamma_k(1 - \alpha_k)\gamma_{k + 1}^{-1}\langle v_k -y_k, g_k\rangle
+            \\
+            &= 
+                (1 - \alpha)\phi_k^* 
+                + 
+                \alpha_k
+                \left(
+                    F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) + 
+                    \frac{1}{2L}\Vert g_k\Vert^2
+                \right)
+                \\
+                &\quad 
+                - 
+                \frac{\alpha_k^2}{2\gamma_{k + 1}}\Vert g_k\Vert^2
+                + 
+                \frac{(1 - \alpha_k)\gamma_k\alpha_k}{\gamma_{k + 1}}
+                \left(
+                    \frac{\mu}{2}\Vert v_k - y_k\Vert^2
+                    + \langle v_k - y_k, g_k\rangle
+                \right). 
+        \end{align*}
+        From the second to third equality we added and then transformed the coefficient of $\Vert y_k - v_k\Vert$ using: 
+        \begin{align*}
             \frac{(1 - \alpha_k)\gamma_k}{2}
@@
             \frac{\gamma_k^2(1 - \alpha_k)^2}{2\gamma_{k + 1}}   
-                \right)
-                \Vert v_k - y_k\Vert^2
-                - \frac{\alpha_k^2}{2\gamma_{k + 1}}\Vert g_k\Vert^2
-                \\
-                &\quad 
-                + \alpha_k\gamma_k(1 - \alpha_k)\gamma_{k + 1}^{-1}\langle v_k -y_k, g_k\rangle
-            \\
-            & \quad 
-            \textcolor{gray}{  
-                \begin{aligned}
-                    \frac{(1 - \alpha_k)\gamma_k}{2}
-                    - 
-                    \frac{\gamma_k^2(1 - \alpha_k)^2}{2\gamma_{k + 1}}   
             &= 
@@
             \right). 
-                \end{aligned}
-            }
-            \\
-            \iff 
-            &= 
-                (1 - \alpha)\phi_k^* + 
-                \alpha_k
-                \left(
-                    F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) + 
-                    \frac{1}{2L}\Vert g_k\Vert^2
-                \right)
-                \\
-                &\quad 
-                + 
-                \frac{(1 - \alpha_k)\gamma_k}{2}
-                \left(
-                    \frac{\mu \alpha_k}{\gamma_{k + 1}}
-                \right)
-                \Vert v_k - y_k\Vert^2
-                - \frac{\alpha_k^2}{2\gamma_{k + 1}}\Vert g_k\Vert^2
-                \\
-                & \quad 
-                + \alpha_k\gamma_k(1 - \alpha_k)\gamma_{k + 1}^{-1}\langle v_k -y_k, g_k\rangle
-            \\
-            &= 
-                (1 - \alpha)\phi_k^* 
-                + 
-                \alpha_k
-                \left(
-                    F\left(\widetilde{\mathcal J}_{L^{-1}} y_k\right) + 
-                    \frac{1}{2L}\Vert g_k\Vert^2
-                \right)
-                \\
-                &\quad 
-                - 
-                \frac{\alpha_k^2}{2\gamma_{k + 1}}\Vert g_k\Vert^2
-                + 
-                \frac{(1 - \alpha_k)\gamma_k\alpha_k}{\gamma_{k + 1}}
-                \left(
-                    \frac{\mu}{2}\Vert v_k - y_k\Vert^2
-                    + \langle v_k - y_k, g_k\rangle
-                \right). 
-        \end{align*}
-        The second and third inequality used the equality $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \mu \alpha_k$. 
+        \end{align*}
+        From the second to the third line, $\mu \alpha_k$ is brought in by the equation $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \mu \alpha_k$.
+
     \end{proof}
@@
         The goal of having $\phi_k^*$ represented by iterates $v_k, y_k, g_k$ is because it assists in the future when an inductive hypothesis $\phi_k^* \ge F(x_k) \ge l_F(x_k; y_k) + \frac{\mu}{2}\Vert x - y_k\Vert^2$ is made.
-        We did things in advance here, nothing more. 
+        We did things in advance here and grouped together a set of transforms by equations, nothing more. 
     \end{remark}
@@
         {\small
-        \begin{align*}
+        \begin{align}
+            \begin{split}
                 \phi_{k + 1}^* &= 
@@
                 \langle v_k - y_k, g_k\rangle. 
-        \end{align*}
+            \end{split}
+            \label{app:acc-prox-grad-ineq1}
+        \end{align}
         }
@@
         The second inequality comes from the non-negativity of the term $\frac{\mu}{2}\Vert v_k - y_k\Vert^2$. 
-        Now, recall from the fundamental proximal gradient inequality in the convex settings, we have $\forall z\in \RR^n$: 
+        Now, recall from the fundamental proximal gradient inequality in the convex setting; define $x_{k + 1} := \widetilde{\mathcal J}_{L^{-1}}y_k$, we have $\forall z\in \RR^n$: 
         \begin{align*}
@@
             \\
-            & \text{set: }x_{k + 1} := \widetilde{\mathcal J}_{L^{-1}}y_k
-            \\
             &\ge 
@@
         \end{align*}
-        Now we set $z = x_{k}$ and substitute it back to RHS of $\phi_{k + 1}$ which yields: 
+        Next, set $z = x_{k}$ and substitute it back to RHS of $\phi_{k + 1}^*$ in 
+        \hyperref[app:acc-prox-grad-ineq1]{Inequality \ref*{app:acc-prox-grad-ineq1}}: 
         \begin{align*}
@@
         \end{align*}
-        To assert $\phi_{k + 1}^* \ge F(x_k)$, one set of sufficient conditions are 
+        To assert $\phi_{k + 1}^* \ge F(x_{k + 1})$, one set of sufficient conditions are 
         \begin{align*}
@@
                 \frac{1}{2L} - \frac{\alpha_k^2}{2\gamma_{k + 1}}
-            \right) &\ge 0
+            \right) &\ge 0, 
             \\
@@
         \end{align*}
-        Before we finish it, re-arranging should give use the equivalent representations 
+        Before finishing, re-arranging should give use the equivalent representations 
         \begin{align*}
@@
             \\
-            & 
-            \textcolor{gray}{
-                \gamma_{k + 1} + \alpha_k \gamma_k 
-                = 
-                \gamma_k + \alpha_k \mu
-            }
-            \\
             &=  
@@
         \end{align*}
-        And $\alpha_k, \gamma_k$, we have the equivalent representation of 
+        On the second to third equality, we multiplied the numerator and denominator by $\gamma_{k + 1}$ and then simplified the numerator using equation $\gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$.
+        For $\alpha_k, \gamma_k$, we have the equivalent representation of 
         \begin{align*}
@@
             \\
-            1 &\ge L \alpha_k^2 / \gamma_{k + 1}
-            \\
+            \iff 1 &\ge L \alpha_k^2 / \gamma_{k + 1}
+            \\
+            \iff 
             \gamma_{k + 1} &\ge L \alpha_k^2
             \\
+            \iff 
             L\alpha_k^2 
@@
     \end{definition}
-
     \begin{theorem}[Intermediate form of accelerated proximal gradient]\label{app:theorem:acc-prox-grad-intermediate}\; \\
-        Let iterates $(x_k, y_k, v_k)$ be given by the raw form of Nesterov's accelerated proximal gradient. 
-        If we assume that $L\alpha_k^2 = \gamma_{k + 1}$, then it simplifies into the following representation without parameter $\gamma_k$: 
+        Let iterates $(x_k, y_k, v_k)$ be given by the raw form of Nesterov's accelerated proximal gradient which is 
+        \hyperref[app:def:acc-prox-grad-raw-form]{Definition \ref*{app:def:acc-prox-grad-raw-form}}. 
+        Assume for all $k \ge 0$ it has $L\alpha_k^2 = \gamma_{k + 1}$, then Definition \ref*{app:def:acc-prox-grad-raw-form} is algebraically equivalent to the following form which doesn't have $\gamma_k$:
         \begin{align*}
@@
     \begin{proof}
-
         From definition,  we have equality: $\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$, so $\gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$, with that in mind we can simplify the expression for $y_k$ by
@@
         \begin{align*}
-            & \text{find } \alpha_{k + 1} \text{ such that: }L \alpha_{k + 1}^2 = (1 - \alpha_{k + 1})L \alpha_{k - 1} + \mu \alpha_{k + 1}
-            \\
-            & x_{k + 1} = \widetilde {\mathcal J}_{L^{-1}} y_k
+            & \text{find } \alpha_{k + 1} \text{ such that: }L \alpha_{k + 1}^2 = (1 - \alpha_{k + 1})L \alpha_{k - 1} + \mu \alpha_{k + 1}, 
+            \\
+            & x_{k + 1} = \widetilde {\mathcal J}_{L^{-1}} y_k, 
             \\
@@
         \begin{align*}
-            \phi_0 &:= f(x_0) + \frac{A}{2}\Vert x - x_0\Vert^2, 
+            \phi_0(x) &:= f(x_0) + \frac{A}{2}\Vert x - x_0\Vert^2, 
             \\
@@
         \end{align*}
-        In the canonical form, $v_{k + 1}$ is the minimizer of $\phi_{k + 1}$, it can be solved for by setting the gradient $\phi_{k + 1}(x)= \mathbf 0$ so for all $k\ge 0$: 
+        In the canonical form, $v_{k + 1}$ is the minimizer of $\phi_{k + 1}$, it can be solved for by setting the gradient $\phi_{k + 1}(v_{k + 1})= \mathbf 0$ so for all $k\ge 0$: 
         \begin{align*}
@@
             \\
+            \iff 
             v_{k + 1} - v_k &= 
@@
                 & 
-                y_k = (1 - \alpha_k)x_k + \alpha_k v_k
+                y_k = (1 - \alpha_k)x_k + \alpha_k v_k, 
                 \\
@@
         \begin{align*}
-            \phi_0 &:= F(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2
+            \phi_0(x) &:= F(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2, 
             \\
@@
             \begin{align*}
-                \phi_k^* &= \min_x \phi_k(x)
-                \\
-                \phi_k(x) &= \phi_k^* + \frac{\gamma_k}{2}\Vert x - v_k\Vert^2. 
-            \end{align*}
-            Then the parameters the canonical form $(\gamma_{k})_{k \ge0}, (v_k)_{k \ge 0}, (\phi_k^*)_{k\ge 0}$ satisfies for all $k \ge 1$
+                \phi_k(x) &= \phi_k^* + \frac{\gamma_k}{2}\Vert x - v_k\Vert^2, 
+            \end{align*}
+            where $\phi_k^* = \min_x \phi_k(x)$. 
+            Then the parameters of the canonical form $(\gamma_{k})_{k \ge0}, (v_k)_{k \ge 0}, (\phi_k^*)_{k\ge 0}$ satisfies for all $k \ge 1$: 
             \begin{align*}
@@
                 \gamma_k - (\kappa + \mu)\alpha_{k - 1}^2 
-                &= 0
+                &= 0, 
                 \\
@@
             \begin{align*}
-                \gamma_{k + 1} &= (1 - \alpha_{k})\gamma_k + \alpha_k \mu = (\kappa + \mu)\alpha_{k - 1}^2
+                \gamma_{k + 1} &= (1 - \alpha_{k})\gamma_k + \alpha_k \mu = (\kappa + \mu)\alpha_{k - 1}^2,
                 \\
                 y_k &= (\gamma_k + \alpha_k \mu)^{-1}
-                (\alpha_k \gamma_k v_k + \gamma_{k + 1}x_k)
+                (\alpha_k \gamma_k v_k + \gamma_{k + 1}x_k),
                 \\
@@
                 \mathcal M^{\kappa^{-1}}(x_{k + 1}, y_k) - 
-                \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k} , y_k) \le \epsilon_k
-                \\
-                \widetilde{\mathcal G}_{\kappa^{-1}} y_k &= \kappa(y_k - \tilde x_{k + 1})
-                \\
-                x_{k + 1} &= y_k - \widetilde{\mathcal G}_{\kappa^{-1}} y_k
+                \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k} , y_k) \le \epsilon_k,
+                \\
+                \widetilde{\mathcal G}_{\kappa^{-1}} y_k &= \kappa(y_k - \tilde x_{k + 1}),
+                \\
+                x_{k + 1} &= y_k - \widetilde{\mathcal G}_{\kappa^{-1}} y_k,
                 \\

### 2024-11-26 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
     This technique is fundamental for in Guler's accelerated PPM method and Catalyst meta acceleration in the convex/strongly convex case. 
-    Unlike proofs using a Lyapunov argument which requires knowing exactly the algorithm in advance to verify the convergence rate, Nesterov's estimating squence can produce an algorithm that generates iterates $(x_k)_{k \ge0}$ such that it converges at some rate.
+    Unlike proofs using a Lyapunov argument which requires knowing exactly the algorithm in advance to verify the convergence rate, Nesterov's estimating sequence can produce an algorithm that generates iterates $(x_k)_{k \ge0}$ such that it converges at some rate.
     \subsection{Nesterov's Estimating Sequence}
@@
                 &\ge 
-                \phi_k^* - F(x_k) \ge 0
+                \phi_k^* - F(x_k) \ge 0;
                 \\
@@
                 \Delta_k(x_*)
-                &\ge \phi_k^* - F_* \ge F(x_k) - F_* \ge 0
+                &\ge \phi_k^* - F_* \ge F(x_k) - F_* \ge 0. 
             \end{align*}
@@
             & \text{find } \alpha_{k + 1} \in (0, 1): 
-            \alpha_{k + 1} = (1 - \alpha_{k + 1})\alpha_k^{2} + (\mu/L) \alpha_{k + 1}
+            \alpha_{k + 1} = (1 - \alpha_{k + 1})\alpha_k^{2} + (\mu/L) \alpha_{k + 1}, 
             \\
@@
         Guler didn't simplify his results compare to what Nesterov did in his book. 
-        For a detailed proof of the estimating sequence with comparison to the accelerated proximal gradient method, see Appendix \ref*{sec:app:exct-acc-ppm}. 
+        For a detailed proof of the estimating sequence with comparison to the accelerated proximal gradient method, see 
+        \hyperref[sec:app:exct-acc-ppm]{Appendix \ref*{sec:app:exct-acc-ppm}}. 
     \end{remark}
-    For the inexact evaluation of PPM, Guler cited Rockafellar \cite{rockafellar_monotone_1976} for condition (A') in his text which is the following: 
+    Guler cited Rockafellar \cite{rockafellar_monotone_1976} for condition (A') in his text for inexact proximal evaluation: 
     \begin{align*}
@@
 
-\section{Lin 2015}\label{sec:lin-2015}
+\section{Lin's Estimating Sequence}\label{sec:lin-2015}
     The section introduces the Nesterov's estimating sequence in Lin 2015 \cite{lin_universal_2015}. 
@@
     \begin{definition}[Lin's accelerated proximal point method]
+        Define the estimating sequence $(\phi_k)_{k \ge0}$ recursively by: 
+        \begin{align*}
+            \phi_0(x) &:= F(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2, 
+            \\
+            \phi_k(x) &:= 
+            (1 - \alpha_{k - 1})\phi_{k - 1}(x)
+            + \alpha_{k - 1}\left(
+                F(x_k) + \kappa\langle y_{k - 1} - x_k, x - x_k \rangle
+                + \frac{\mu}{2}\Vert x - x_k\Vert^2
+            \right). 
+        \end{align*}
         Let the initial estimate be $x_0 \in \RR^n$, fix parameters $\kappa$ and $\alpha_0$. 
         Let $(\epsilon_k)_{k \ge 0}$ be an error sequence chosen for the evaluation for inexact proximal point method. 
-        Initialize $x_0 = y_0$, then the algorithm generates $(x_k, y_k)$ satisfies for all $k \ge 1$
+        Initialize $x_0 = y_0$, then the algorithm generates $(x_k, y_k)_{k\ge 0}$ for all $k \ge 1$ such that: 
         \begin{align*}
@@
     Lin didn't formulate any of the intractable quantities in the definitions for his Nesterov's estimating sequence $\phi_k$. 
-    One major innovation is Lemma A.7 in Lin's 2015 paper \cite{lin_universal_2015}. 
+    One major innovation is Lemma A.7 in Lin's 2015 paper \cite{lin_universal_2015} which is stated below. 
     The lemma allows the analysis Nesterov's estimating sequence to be carried through without using intractable quantities: $\mathcal M^{\kappa^{-1}}(\mathcal J_{k^{-1}}y_{k - 1}, y_{k - 1}), \mathcal J_{\kappa^{-1}}y_{k - 1}$.
@@
     \begin{remark}
-        The lemma plays a key role because it allows Lin to denote his Nesterov's estimating sequence to be for all $k \ge0$: 
-        \begin{align*}
-            \phi_0(x) &:= F(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2, 
-            \\
-            \phi_k(x) &:= 
-            (1 - \alpha_{k - 1})\phi_{k - 1}(x)
-            + \alpha_{k - 1}\left(
-                F(x_k) + \kappa\langle y_{k - 1} - x_k, x - x_k \rangle
-                + \frac{\mu}{2}\Vert x - x_k\Vert^2
-            \right). 
-        \end{align*}
-        It is void of intractable quantities. 
+        For a detailed proof of the lemma, see 
+        \hyperref[app:sec:inxct-pg-ineq]{Appendix\ref*{app:sec:inxct-pg-ineq}}.
+
     \end{remark}
+    Using this inexact proximal inequality, we showed the proof of Lemma A.8 in Lin's paper \cite{lin_universal_2015} in 
+    \hyperref[app:sec:appx-nes-est-seq]{Appendix \ref*{app:sec:appx-nes-est-seq}}
+    and 
+    \hyperref[app:sec:appx-nes-seq-errs-ctrl]{Appendix \ref*{app:sec:appx-nes-seq-errs-ctrl}}. 
+    These result construct the Nesterov's estimating sequence by rolling up the error in the recurrence while avoiding intractable quantities appearing in the algorithm.
 
@@
         \; \\
-        Denote $\phi_k:\RR^n \rightarrow\RR$ as a sequence of functions such that for all $k\ge 0$ it recursively satisfies the following conditions 
+        Fix any $x_0 \in \RR^n$ to, 
+        define $\phi_k:\RR^n \rightarrow\RR$ as a sequence of functions such that for all $k\ge 0$ it recursively satisfies the following conditions 
         \begin{align*}
@@
         \end{align*}
-        where $\phi_k^* := \min_{x} \phi_k(x)$. 
+        where $\phi_k^* := \min_{x} \phi_k(x)$, $\gamma_0 > 0$ and $x_0 = v_0$. 
         Then the auxiliary sequence $y_k, v_k$, parameters for the canonical form of estimating sequence must satisfy for all $k\ge 0$: 
@@
                 \\
-                & \textcolor{gray}{
-                    A_{k + 1} = (1 - \alpha_k)A_k
-                }
-                \\
                 &=
@@
                     y_k - \mathcal J_k y_k, v_{k + 1} - y_{k + 1}
-                \rangle
-            \end{align*}
+                \rangle. 
+            \end{align*}
+            Equality $A_{k + 1} = (1 - \alpha_k)A_k$ is used on the second last inequality for the above. 
             Next, we substitute the inequality by the inductive hypothesis which gives: 
@@
                         \alpha_k(v_{k + 1} - v_k) + (y_k - \mathcal J_k y_k)
-                    \rangle
+                    \rangle. 
                 \tag{1}
@@
 
-    \subsection{Inexact proximal inequality}
+    \subsection{Inexact proximal inequality}\label{app:sec:inxct-pg-ineq}
         \begin{proof}
@@
 
-    \subsection{Approximated Nesterov's Estimating sequence}
+    \subsection{Approximated Nesterov's Estimating sequence}\label{app:sec:appx-nes-est-seq}
         In this subsection, let $\phi_k$ be the Nesterov's estimating sequence for Catalyst. 
@@
         \end{remark}
-    \subsection{Controlling the errors}
+    \subsection{Controlling the errors}\label{app:sec:appx-nes-seq-errs-ctrl}
         The following theorem is Theorem A.8 from Lin's writing of Catalyst \cite{lin_universal_2015}. 

### 2024-11-26 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
 \section{Introduction}
-    \textcolor{red}{THIS REPORT IS CURRENTLY: FINISHED, BUT NOT YET POLISHED}
+    \textcolor{red}{THIS REPORT IS CURRENTLY: FIRST POLISHING DONE. }
 
@@
 
-\section{Lin's Estimating Sequence}\label{sec:lin-2015}
+\section{Lin's estimating sequence}\label{sec:lin-2015}
     The section introduces the Nesterov's estimating sequence in Lin 2015 \cite{lin_universal_2015}. 

### 2024-11-26 Latex Templates/Scientific 2/main.tex
>w<, changes

\documentclass[12pt]{article}
\input{presets/wang/input.tex}
\input{presets/misc.tex}
\input{presets/julia_lstlisting.tex}

% === TEMPLATE HOW TO USE ======
% To begine here is a list of things: 
% [ ]: Change title. 
% [ ]: Fill into the author names, affiliation and contact info. 
% [ ]: Fill in the abstract. 
% [ ]: Fill/change in AMS mathematics subject classification code, and the keywords.

\begin{document}

\title{
    {
        \fontfamily{ptm}\selectfont 
        A big title
    }
    }

\author{
    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
    The University of British Columbia, Kelowna, BC Canada V1V 1V7. 
    E-mail:  \texttt{alto@mail.ubc.ca}.}~ Author Name 1
    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
    The University of British Columbia, Kelowna, BC Canada V1V 1V7. 
    E-mail:  \texttt{shawn.wang@ubc.ca}.}~ and~Xianfu Wang
}

\date{\today}

\maketitle

% \vskip 8mm

\section{Section}
    Beck's book \cite{beck_first-order_2017}. 
\section{Section}

\begin{abstract} 
    \noindent
    Abstract abstract abstract.

\end{abstract}

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
\noindent{\bfseries Keywords: } Non-convex Optimizations, Proximal Point.

\bibliographystyle{siam}
\bibliography{references/refs.bib}
\newpage

\appendix

\end{document}

### 2024-11-28 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
         \begin{align*}
-            \phi_0(x) &:= f(x_0) + \frac{A}{2}\Vert x - x_0\Vert^2, 
+            \phi_0(x) &:= F(x_0) + \frac{A}{2}\Vert x - x_0\Vert^2, 
             \\
@@
         \hyperref[sec:app:exct-acc-ppm]{Appendix \ref*{sec:app:exct-acc-ppm}}. 
+        We note that the smoothness conditions here are not involved in the definition of Guler's estimating sequence, or the function $F$. 
     \end{remark}
@@
     \begin{lemma}[Lin's inexact proximal inequality]\label{lemma:lin-ixct-prox-ineq}
-        Let $F$ be a $\mu\ge 0$ strongly convex and fix $\kappa$. 
+        Let $F$ be a strongly convex with $\mu\ge 0$. 
+        Let $\kappa$ be fixed. 
         If $x_k$ is an inexact proximal point evaluation of $x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1}$ such that there exists $\epsilon_k$ where $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k - 1}, y_{k - 1}) \le \epsilon_k$.
@@
         For a detailed proof of the lemma, see 
-        \hyperref[app:sec:inxct-pg-ineq]{Appendix\ref*{app:sec:inxct-pg-ineq}}.
-
+        \hyperref[app:sec:inxct-pg-ineq]{Appendix \ref*{app:sec:inxct-pg-ineq}}. 
+        We note that it only uses the strong convexity of model function $\mathcal M^{\kappa^{-1}}(\cdot, y_{k - 1})$ (It's actually the quadratic growth condition around minimizer $x_k$ that is used in the proof), smoothness assumption of $F$ is not involved in here.
     \end{remark}
@@
             x_{k + 1}&= 
-            \widetilde{\mathcal J}_{L^{-1}} y_k
+            \widetilde{\mathcal J}_{L^{-1}} y_k, 
             \\

### 2024-11-28 Latex Templates/Scientific 2/main.tex
>w<, changes

@@
     The University of British Columbia, Kelowna, BC Canada V1V 1V7. 
-    E-mail:  \texttt{alto@mail.ubc.ca}.}~ Author Name 1
+    E-mail:  \texttt{alto@mail.ubc.ca}.}~Author Name 1
     \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
     The University of British Columbia, Kelowna, BC Canada V1V 1V7. 
-    E-mail:  \texttt{shawn.wang@ubc.ca}.}~ and~Xianfu Wang
+    E-mail:  \texttt{shawn.wang@ubc.ca}.}~ and~Author Name 2
 }
@@
 
-\section{Section}
-    Beck's book \cite{beck_first-order_2017}. 
-\section{Section}
-
 \begin{abstract} 
@@
     Abstract abstract abstract. 
+\end{abstract}
+% \noindent{\bfseries 2010 Mathematics Subject Classification:}
+% Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
+% \noindent{\bfseries Keywords: } Non-convex Optimizations, Proximal Point.
 
-\end{abstract}
+\tableofcontents
 
-\noindent{\bfseries 2010 Mathematics Subject Classification:}
-Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
-\noindent{\bfseries Keywords: } Non-convex Optimizations, Proximal Point.
+\section{Introduction}
+
+\section{Notations}
+    Beck's book \cite{beck_first-order_2017}. 
+\subsection{Foundamentals in convex analysis}
+\subsection{Canonical forms of Nesterov's accelerated methods}
+\section{Unifying variants of Nesterov's accelerated methods}
+\section{Generic convergence anlaysis of accelerated methods}
+\section{Catalyst accelerations and future works}
+\section{Performence estimation problems}
+\section{Methods of inexact proximal point}
+\section{Nestrov's acceleration in the non-convex case}
 

### 2024-12-05 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
     \noindent
-    Nesterov's accelerated gradient first appeared back in the 1983 has sparked numerous theoretical and practical advancements in Mathematics programming literatures. 
+    Nesterov's accelerated gradient appeared sparked numerous theoretical and practical advancements in Mathematics programming literatures since its conception back in 1983. 
     The idea behind Nesterov's acceleration is universal for convex objective, and it has concrete extension in the non-convex case. 
-    In this paper we survey specifically the Catalyst Acceleration that incorporated ideas from the Accelerated Proximal Point Method proposed by Guler back in 1993. 
+    In this paper we survey the Catalyst Acceleration method which is an modern practical realization of the Accelerated Proximal Point Method proposed by Guler back in 1993. 
     The paper reviews Nesterov's classical analysis of accelerated gradient in the convex case.
@@
 \section{Introduction}
-    \textcolor{red}{THIS REPORT IS CURRENTLY: FIRST POLISHING DONE. }
-
+    \par
     The optimal algorithm named accelerated gradient descent method is proposed in Nesterov's seminal work back in 1983 \cite{nesterov_method_1983}. 
@@
     Accelerated gradient descent has an upper bound of $\mathcal O(1/k^2)$, making it optimal. 
-
-    It's tempting to believe that the existence of an optimal algorithm sealed the ceiling for the need of theories for convex first-order smooth optimization. 
+    \par
+    It's tempting to believe that the existence of this optimal algorithm sealed the ceiling for the need of theories for convex first-order smooth optimization. 
     It is correct but lacks the nuance in understanding because Nesterov's accelerated gradient is a system of analysis techniques which is not a specific design paradigm for algorithms. 
-
+    \par
     Guler's accelerated Proximal Point Method (PPM) \cite{guler_new_1992} in 1993 used the technique of Nesterov's estimating sequence to accelerate PPM for convex objectives. 
@@
     An inexact Accelerated PPM method using conditions described in Rockafellar's works in 1976 \cite{rockafellar_monotone_1976} is also discussed in the paper. 
-
+    \par
     It's tempting to conclude that the results has reached the ceiling for extending Nesterov's acceleration. 
@@
     These quantities are intractable in practice making it impossible to formulate it to algorithms directly. 
-
+    \par
     Introduced in Lin et al.
@@
     \subsection{Contributions}
-        The writing is expository and comprehensive, it will survey the history and major results, and innovations involved in conceiving and designing the Catalyst algorithm. 
+        The writing is expository and comprehensive, it surveys historical major results and innovations in the conception and design of the Catalyst algorithm. 
         We reviewed the literatures and faithfully reproduced important claims.
-        In addition, we give insights and context to understand the claims in these papers and making connections to ideas in optimization. 
+        In addition, we give insights and context to understand the claims in these papers by making connections to ideas in optimization. 
         Three papers by Guler \cite{guler_new_1992} and Lin \cite{lin_universal_2015} and Paquette et al.
@@
         Applications and specific example algorithms are out of the scope because there are too many papers on the separate topic of variance reduced stochastic algorithms. 
+        If the readers are interested, consult Gower et al.
+\cite{gower_variance-reduced_2020} for more information about the usual candidates used to evaluate the inexact proximal point method in practice.
 
@@
     Unlike proofs using a Lyapunov argument which requires knowing exactly the algorithm in advance to verify the convergence rate, Nesterov's estimating sequence can produce an algorithm that generates iterates $(x_k)_{k \ge0}$ such that it converges at some rate.
+
+    The technique is universal in deriving accelerated algorithm in the convex case. 
+    In addition to Catalyst and accelerated PPM, it's used to derive an accelerated mirror descent in Nesterov's book \cite{nesterov_lectures_2018} (6.1.19); an accelerated regularized newton method for convex composite objectives by Geovani N.
+et al \cite{grapiglia_accelerated_2019} and an accelerated regularized cubic newton by Nesterov \cite{nesterov_accelerating_2008}.
+
     \subsection{Nesterov's Estimating Sequence}
@@
 
-\section{Nesterov's accelerated proximal gradient}
+\section{Estimating sequence for accelerated proximal gradient}
     This section swiftly exposes the constructions of the Nesterov's estimating sequence for accelerated proximal gradient method.
@@
     We use accelerated proximal gradient algorithm as an example because its formulation is similar to the Catalyst Acceleration framework. 
-
+    \par
     Throughout this section we assume that: $F = f + g$ where $f$ is $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex and $g$ is convex. 
@@
         Evaluating $x_k \approx \mathcal J_{\kappa^{-1}}y_{k - 1}$ is also possible because the function $\mathcal M^{\kappa^{-1}}(\cdot, y_{k - 1})$ is strongly convex, hence its optimality gap can be bounded via trackable quantity $\partial \mathcal M^{\kappa^{-1}}(x_k, y_{k - 1})$.
-
+        \par
         Controlling the error sequence $\epsilon_k$ however is a whole new business. 
@@
 For instance, when $F$ is non-negative, we may simply choose $\epsilon_k = (2/9)F(x_0)(1 - \rho)^k$".
-
+        \par
         This comment has upmost practical importance because it tells us how to bound the error $\epsilon_k$ to achieve accelerated convergence rate. 
@@
         Read 
-        \hyperref[app:sec:ncnvx-catalyst]{Section \ref*{app:sec:ncnvx-catalyst}} for more information on proof of this claim. 
+        \hyperref[app:sec:ncnvx-catalyst]{Section \ref*{app:sec:ncnvx-catalyst}} for a proof of this claim. 
     \end{remark}
@@
 \bibliographystyle{siam}
-\bibliography{references/refs.bib}
+\bibliography{references/590refs.bib}
 \newpage
@@
     \end{align*}
+    We also introduce Bregman Divergence. 
+    Let $h: Q \rightarrow \RR$ be a differentiable smooth convex function on a closed convex domain $Q \subseteq \RR^n$.
+    Define 
+    $$
+        D_h: Q \times \reli Q \rightarrow \RR^n
+        := (x, y) \mapsto h(x) - h(y) - \langle \nabla h(y), x - y\rangle. 
+    $$
 

### 2024-12-07 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
     \noindent
-    Nesterov's accelerated gradient appeared sparked numerous theoretical and practical advancements in Mathematics programming literatures since its conception back in 1983. 
+    Nesterov's accelerated gradient sparked numerous theoretical and practical advancements in Mathematics programming literatures since its conception back in 1983. 
     The idea behind Nesterov's acceleration is universal for convex objective, and it has concrete extension in the non-convex case. 
-    In this paper we survey the Catalyst Acceleration method which is an modern practical realization of the Accelerated Proximal Point Method proposed by Guler back in 1993. 
+    In this paper we survey the Catalyst Acceleration method which is a modern practical realization of the Accelerated Proximal Point Method proposed by Guler back in 1993. 
     The paper reviews Nesterov's classical analysis of accelerated gradient in the convex case.
-    The paper will describe key aspects of the theoretical innovations involved to achieve the design of the algorithm in convex, and non-convex case.
+    The paper will also describe key aspects of the theoretical innovations involved to achieve the design of the algorithm in convex, and non-convex case.
 
@@
     Use $(\lambda_k)_{k \ge 0}$ to parameterize the proximal point evaluation to generate $(x_k)_{k\ge 0}$ given any initial guess $x_0$.
-    Guler's prior work \cite{guler_convergence_1991} showed the convergence of PPM method in the convex without acceleration is $\mathcal O\left(1/\sum^{n}_{i = 1}\lambda_i\right)$. 
+    Guler's prior work \cite{guler_convergence_1991} showed the convergence of PPM method in the convex case without acceleration is $\mathcal O\left(1/\sum^{n}_{i = 1}\lambda_i\right)$. 
     His new algorithm with acceleration has a rate of $\mathcal O\left(1/(\sum_{i = 1}^{n} \sqrt{\lambda_i})^2\right)$. 
@@
     It is correct, but not from a practical point of view. 
-    Let $F: \RR^n \rightarrow\RR$ be our objective function, $\mathcal J_\lambda := (I + \lambda \partial F)^{-1}$ and $\mathcal M^{\lambda}(x; y):= F(x) + \frac{1}{2\lambda}\Vert x - y\Vert^2$ then the inexact proximal point considers with error $\epsilon_k$ has the following characterizations of inexactness as put forward by Guler \cite{guler_new_1992}:
+    Let $F: \RR^n \rightarrow\RR$ be our objective function, $\mathcal J_\lambda := (I + \lambda \partial F)^{-1}$ and $\mathcal M^{\lambda}(x; y):= F(x) + \frac{1}{2\lambda}\Vert x - y\Vert^2$.
+Then the inexact proximal point considers with error $\epsilon_k$ has the following characterizations of inexactness as put forward by Guler \cite{guler_new_1992}:
     \begin{align*}
@@
     \end{align*}
+    $\partial \mathcal M(\cdot; y)$ is the regular subgradient of the model function with respect  to $x$. 
     The difficulty comes from controlling the error $\epsilon$ at each iteration to ensure the overall convergence of accelerated PPM. 
@@
     The meta algorithm uses other first order algorithms to evaluate inexact proximal point method and then performs accelerated PPM, therefore the umbrella term: ``meta''. 
-    Major innovations include Tracking and controlling the errors made in the inexact PPM using Nesterov's estimating sequence throughout and an algorithm called accelerated MISO-Prox.  
+    Major innovations include tracking and controlling the errors made in the inexact PPM using Nesterov's estimating sequence throughout and an algorithm called accelerated MISO-Prox.  
     Prior to Lin's paper, it was an open question on the conditions required to accelerate incremental method such as stochastic gradient descent can be accelerated.
@@
 \section{Preliminaries}\label{sec:preliminaries}
-    Throughout the writing, let the ambient space is $\RR^n$. 
+    Throughout the writing, let the ambient space be $\RR^n$. 
     The optimization problem is
@@
     Unlike proofs using a Lyapunov argument which requires knowing exactly the algorithm in advance to verify the convergence rate, Nesterov's estimating sequence can produce an algorithm that generates iterates $(x_k)_{k \ge0}$ such that it converges at some rate.
-
+    \par
     The technique is universal in deriving accelerated algorithm in the convex case. 
@@
         + 
-        \left\langle \nabla f(x), x - y\right\rangle 
+        \left\langle \nabla f(y), x - y\right\rangle 
         + 
@@
     \end{align*}
-
-    In the literature, $\mathcal G_{L^{-1}}$ is commonly known as the gradient mapping. 
-    The definition follows, we define the Nesterov's estimating sequence used to derive the accelerated proximal gradient method. 
+    \par
+    $\mathcal G_{L^{-1}}$ is commonly known as the gradient mapping in the literature. 
+    We define the Nesterov's estimating sequence used to derive the accelerated proximal gradient method next. 
     \begin{definition}[Accelerated proximal gradient estimating sequence]
@@
     \begin{observation}
-        Fix any $y$, for all $x\in \RR^n$, $F(x) \ge l_F(x; y_k) + \mu/2\Vert x - y_k\Vert^2$ is the proximal gradient inequality. 
+        Fix any $y$. For all $x\in \RR^n$, $F(x) \ge l_F(x; y_k) + \mu/2\Vert x - y_k\Vert^2$ is the proximal gradient inequality. 
         If $f \equiv 0$ then $\widetilde{\mathcal J}_{L^{-1}}y_k$ becomes resolvent $(I + L^{-1}\partial F)^{-1}$, which makes $x_k$ being an exact evaluation of PPM: 
@@
     Guler showed the technique can accelerate proximal point method in the convex settings. 
-    Throughout the section, assume that $F:\RR^n \rightarrow \overline \RR$ is a convex function. 
+    Throughout the section, we assume that $F:\RR^n \rightarrow \overline \RR$ is a convex function. 
     Define:
@@
         The auxiliary sequences $(A_k, v_k)$ parameterizes a canonical representation of the estimating sequence $(\phi_k)_{k \ge0}$. 
-        Guler didn't simplify his results compare to what Nesterov did in his book. 
+        Guler didn't simplify comparing to Nesterov's result which is in his book. 
         For a detailed proof of the estimating sequence with comparison to the accelerated proximal gradient method, see 
@@
     \end{align*}
-    Condition A' also characterizes the property of $(\epsilon_k)_{k\ge 0}$ so inexact PPM converges. 
     Guler strengthens it in his context and proved the following: 
@@
     \begin{remark}
-        The inequalities are from PL-condition and strong convexity. 
-        They are now standard results in convex optimizations. 
         For a proof of the theorem, see 
@@
         Let $(\epsilon_k)_{k \ge 0}$ be an error sequence chosen for the evaluation for inexact proximal point method. 
-        Initialize $x_0 = y_0$, then the algorithm generates $(x_k, y_k)_{k\ge 0}$ for all $k \ge 1$ such that: 
-        \begin{align*}
-            & \text{find } x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1} \text{ such that } \mathcal M^{\kappa^{-1}}(x_k, y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}}y_{k - 1}, y_{k - 1}) \le \epsilon_k
-            \\
-            & \text{find } \alpha_k \in (0, 1) \text{ such that } \alpha_k^2 = (1 - \alpha_k)\alpha_{k - 1}^2 + (\mu/(\mu + \kappa)) 
+        Initialize $x_0 = y_0$. Then the algorithm generates $(x_k, y_k)_{k\ge 0}$ for all $k \ge 1$ such that: 
+        \begin{align*}
+            & \text{find } x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1} \text{ such that } \mathcal M^{\kappa^{-1}}(x_k, y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}}y_{k - 1}, y_{k - 1}) \le \epsilon_k,
+            \\
+            & \text{find } \alpha_k \in (0, 1) \text{ such that } \alpha_k^2 = (1 - \alpha_k)\alpha_{k - 1}^2 + (\mu/(\mu + \kappa)),
             \\
@@
         \hyperref[def:nes-est-seq-pg]{Definition \ref*{def:nes-est-seq-pg}}. 
-        In contrast, it has an inexact proximal point step controlled by $\epsilon_k$, and the Lipschitz constant $L$ is absent instead it has $\kappa + \mu$. 
+        In contrast, it has an inexact proximal point step controlled by $\epsilon_k$, and the Lipschitz constant $L$ is absent, instead it has $\kappa + \mu$. 
         Evaluating $x_k \approx \mathcal J_{\kappa^{-1}}y_{k - 1}$ is also possible because the function $\mathcal M^{\kappa^{-1}}(\cdot, y_{k - 1})$ is strongly convex, hence its optimality gap can be bounded via trackable quantity $\partial \mathcal M^{\kappa^{-1}}(x_k, y_{k - 1})$.
@@
     One major innovation is Lemma A.7 in Lin's 2015 paper \cite{lin_universal_2015} which is stated below. 
-    The lemma allows the analysis Nesterov's estimating sequence to be carried through without using intractable quantities: $\mathcal M^{\kappa^{-1}}(\mathcal J_{k^{-1}}y_{k - 1}, y_{k - 1}), \mathcal J_{\kappa^{-1}}y_{k - 1}$.
+    The lemma allows the analysis of Nesterov's estimating sequence to be carried through without using intractable quantities: $\mathcal M^{\kappa^{-1}}(\mathcal J_{k^{-1}}y_{k - 1}, y_{k - 1}), \mathcal J_{\kappa^{-1}}y_{k - 1}$.
 
     \begin{lemma}[Lin's inexact proximal inequality]\label{lemma:lin-ixct-prox-ineq}
-        Let $F$ be a strongly convex with $\mu\ge 0$. 
+        Let $F$ be a strongly convex function with $\mu\ge 0$. 
         Let $\kappa$ be fixed. 
         If $x_k$ is an inexact proximal point evaluation of $x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1}$ such that there exists $\epsilon_k$ where $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k - 1}, y_{k - 1}) \le \epsilon_k$.
-        Denote $x_k^* = \mathcal J_{\kappa^{-1}} y_{k - 1}$, then it has for all $x$: 
+        Denote $x_k^* = \mathcal J_{\kappa^{-1}} y_{k - 1}$. Then it has for all $x$: 
         \begin{align*}
@@
         \hyperref[app:sec:inxct-pg-ineq]{Appendix \ref*{app:sec:inxct-pg-ineq}}. 
-        We note that it only uses the strong convexity of model function $\mathcal M^{\kappa^{-1}}(\cdot, y_{k - 1})$ (It's actually the quadratic growth condition around minimizer $x_k$ that is used in the proof), smoothness assumption of $F$ is not involved in here.
+        We note that it only uses the strong convexity of model function $\mathcal M^{\kappa^{-1}}(\cdot, y_{k - 1})$, and the smoothness assumption of $F$ is not involved in here. 
     \end{remark}
@@
     \hyperref[app:sec:appx-nes-seq-errs-ctrl]{Appendix \ref*{app:sec:appx-nes-seq-errs-ctrl}}. 
-    These result construct the Nesterov's estimating sequence by rolling up the error in the recurrence while avoiding intractable quantities appearing in the algorithm.
+    These results construct the Nesterov's estimating sequence by rolling up the error in the recurrence while avoiding intractable quantities appearing in the algorithm.
 
@@
     \par 
-    Fix $\kappa$ we use the following notations: 
+    Fix $\kappa$. We use the following notations: 
     \begin{align*}
@@
     \end{definition}
-
+    For theorem follows, we note that a function is called $\rho$-weakly convex if and only if there exists $\rho \in \RR$ such that $f + \frac{\rho}{2}\Vert \cdot\Vert^2$ is a convex function. 
     \begin{theorem}[Basic 4WD Catalyst Convergence]\label{thm:basic-4wd-catalyst}
         Let $(x_k, v_k, y_k)$ be generated by the basic Catalyst algorithm. 
-        If $F$ is $\kappa$ weakly convex and bounded below, then $x_k$ converges to stationary where
+        If $F$ is weakly convex and bounded below, then $x_k$ converges to stationary where
         \begin{align*}
@@
 
+\section{Acknowledgement}
+    Thanks for Professor Shawn Wang's patiently reading through the manuscripts and giving constructive feedback.
+
 \bibliographystyle{siam}
@@
 
-    \begin{theorem}[Cannonical form of proximal gradient estimating sequence]\label{thm:canon-prox-grad-est-seq}
+    \begin{theorem}[Canonical form of proximal gradient estimating sequence]\label{thm:canon-prox-grad-est-seq}
         \; \\
-        Fix any $x_0 \in \RR^n$ to, 
-        define $\phi_k:\RR^n \rightarrow\RR$ as a sequence of functions such that for all $k\ge 0$ it recursively satisfies the following conditions 
+        Fix any $x_0 \in \RR^n$. 
+        Define $\phi_k:\RR^n \rightarrow\RR$ as a sequence of functions such that for all $k\ge 0$ it recursively satisfies the following conditions 
         \begin{align*}
@@
             \right)
-            \rightarrow \textcolor{red}{(\text{eqn1})}; 
+            \tag{\textcolor{red}{\text{eqn1}}}; 
             \\
@@
             \right)
-            \rightarrow 
-            \textcolor{red}{(\text{eqn2})}. 
+            \tag{\textcolor{red}{\text{eqn2}}}. 
         \end{align*}
@@
         Therefore, it has: 
-        {\small
+        {\footnotesize
         \begin{align*}
@@
             \\
+            \iff 
             \frac{- \gamma_{k + 1}}{2}
@@
         \hyperref[thm:canon-prox-grad-est-seq]{Theorem \ref*{thm:canon-prox-grad-est-seq}}. 
-        If for all $k\ge 0$ they verify: 
-        \begin{align*}
-            \frac{1}{2L} - \frac{\alpha_k^2}{2 \gamma_{k + 1}} &\ge 0, 
+        If for all $k\ge 0$: 
+        \begin{align*}
+            \frac{1}{2L} - \frac{\alpha_k^2}{2 \gamma_{k + 1}} &\ge 0, \text{ and }
             \\
@@
                 \\
-                \implies 
                 &\ge 
@@
                 \\
-                \implies
                 &\ge 
@@
         \end{align*}
-        Before finishing, re-arranging should give use the equivalent representations 
+        Re-arranging gives the equivalent representation: 
         \begin{align*}
@@
         \hyperref[app:def:acc-prox-grad-raw-form]{Definition \ref*{app:def:acc-prox-grad-raw-form}}. 
-        Assume for all $k \ge 0$ it has $L\alpha_k^2 = \gamma_{k + 1}$, then Definition \ref*{app:def:acc-prox-grad-raw-form} is algebraically equivalent to the following form which doesn't have $\gamma_k$:
+        Assume for all $k \ge 0$ it has $L\alpha_k^2 = \gamma_{k + 1}$ 
+        Then Definition \ref*{app:def:acc-prox-grad-raw-form} is algebraically equivalent to the following form which doesn't have $\gamma_k$: 
         \begin{align*}
@@
                 \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
-            \right)
+            \right),
             \\
@@
                 \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
-            \right) - \frac{1}{L\alpha_{k}} g_k
+            \right) - \frac{1}{L\alpha_{k}} g_k,
             \\
@@
         \; \\
-        Let the sequence $\alpha_k$, and vectors $y_k, x_k, v_k$ be given by the intermediate form of the Nesterov's accelerated proximal gradient, then it can be simplified to void of $v_k$. 
+        Let the sequence $\alpha_k$, and vectors $y_k, x_k, v_k$ be given by the intermediate form of the Nesterov's accelerated proximal gradient without using $v_k$. 
         The algorithm generates $y_k, x_k, \alpha_k$ such that it satisfies for all $k \ge 0$: 
@@
         \end{align*}
-        Increment $k$ into $k + 1$ then 
+        The above is true for all $k\ge 0$, so it's also true for $k + 1$ as well. 
+        Therefore it gives: 
         {\footnotesize
@@
         \begin{align*}
-            \alpha_{k + 1}^2 &= (1 - \alpha_{k + 1})\alpha_k^2 = \alpha_1^2
-            \\
-            &\ge \alpha_1^2 \prod_{i = 2}^{k + 1}(1 - \alpha_i)
+            \alpha_{k + 1}^2 &= (1 - \alpha_{k + 1})\alpha_k^2 
+            \\
+            &= \alpha_1^2 \prod_{i = 2}^{k + 1}(1 - \alpha_i)
             \\
@@
         \end{align*}
+        On the third step of the inequality, we used $\alpha_k \le 2/(k + 1)$ and $\alpha_1 = 1$. 
     \end{proof}
     \begin{remark}
-        $a_k^{-1}$ would just be the FISTA sequence. 
+        If $ \lambda_k = a_k^{-1}$, then $\lambda_k$ would be the FISTA sequence. 
     \end{remark}

### 2024-12-07 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
 \section{Theorems and claims for accelerated proximal gradient}\label{app:sec:thm-claim-acc-prox-grad}
-    Throughout this section, $F = g + f$ is an additive composite objective function with $g$ convex, $f$ $L$-lipschitz smooth and $\mu \ge0$ strongly convex. 
+    Throughout this section, $F = g + f$ is an additive composite objective function with $g$ convex, $f$ $L$-Lipschitz smooth and $\mu \ge0$ strongly convex. 
     The notations here are 
@@
     $$
-        D_h: Q \times \reli Q \rightarrow \RR^n
+        D_h: Q \times \inte Q \rightarrow \RR^n
         := (x, y) \mapsto h(x) - h(y) - \langle \nabla h(y), x - y\rangle. 
@@
         The above is true for all $k\ge 0$, so it's also true for $k + 1$ as well. 
-        Therefore it gives: 
+        Therefore, it gives: 
         {\footnotesize
@@
 \section{Proofs for Catalyst Meta Acceleration}
-    In this section, we prove the inexact proximal inequality and give the Nesterov's estimating sequence void of intractable quantities. 
+    In this section, we prove the inexact proximal inequality and give the Nesterov's estimating sequence without intractable quantities. 
     The notation is the same as
@@
             \\
-            &\quad 
-            \textcolor{gray}{
-            \begin{aligned}
+            &= 
+            \alpha_k x^* + (1 - \alpha_k) x_{k - 1} - (x_{k - 1} + \alpha_k(v_k - x_{k - 1}))
+            \\
+            &= \alpha_k x^* - \alpha_k x_{k - 1} - \alpha_k(v_k - x_{k - 1})
+            \\
+            &= \alpha_k (x^* - v_k). 
+        \end{align*}
+        On the first equality after $x - \tilde x_k$, we substituted $\tilde x_k$ using the definition of the algorithm which is 
+        \begin{align*}
             v_{k} &= x_{k - 1} + \alpha_k^{-1}(\tilde x_k - x_{k - 1})
@@
             \\
-                \tilde x_k &= x_{k - 1} + \alpha_k(v_k - x_{k - 1})
-            \end{aligned}
-            }
-            \\
-            &= 
-            \alpha_k x^* + (1 - \alpha_k) x_{k - 1} - (x_{k - 1} + \alpha_k(v_k - x_{k - 1}))
-            \\
-            &= \alpha_k x^* - \alpha_k x_{k - 1} - \alpha_k(v_k - x_{k - 1})
-            \\
-            &= \alpha_k (x^* - v_k). 
+            \tilde x_k &= x_{k - 1} + \alpha_k(v_k - x_{k - 1}). 
         \end{align*}

### 2024-12-08 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
     The section introduces the Nesterov's estimating sequence in Lin 2015 \cite{lin_universal_2015}.
-    We warn the readers about the followings: 
-    \begin{enumerate}
-        \item The proofs in HongZhou Lin's original paper of Universal Catalyst is depressingly long and complicated.
-It is a result of using the constructive approach of Nesterov's estimating sequence.
-        \item Controlling the errors of inexact proximal point evaluations is context specific.
-Lin hinted at ways to track the errors such as using duality and non-negativity assumption of the objective.
-He illustrated the use of the meta acceleration on their own method called: ``Accelerated MISO-Prox", in general there is not a universal solution.
-        \item We will provide proofs to clarify some of their proofs and compare with existing proofs and drawing references in the literatures in the appendix. 
-    \end{enumerate}
     Let's assume $F$ is a $\mu \ge 0$ strongly convex function. 
@@
     \end{align*}
-    Their algorithm is almost exactly the same as Nesterov's 2.2.20 \cite{nesterov_lectures_2018} which we stated in the definition below: 
+    The definition below states Lin's accelerated inexact proximal point method. 
+    Observe that it's similar to Nesterov's 2.2.20 \cite{nesterov_lectures_2018}. 
     \begin{definition}[Lin's accelerated proximal point method]
@@
     \end{remark}
-
+    \par
     For theoretical interests, there is a major difference between Lin's approach and Guler's approach. 

### 2024-12-09 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

\documentclass[12pt]{article}

% \input{presets/wang_full.tex}
\input{presets/wang/input.tex}
\input{presets/misc.tex}
\input{presets/julia_lstlisting.tex}

\begin{document}

\title{{\fontfamily{ptm}\selectfont 
        A Parameter Free Accelerated Proximal Gradient Method Without Restarting
    }}

\author{
    Hongda Li
    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
    The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{alto@mail.ubc.ca}.}~ and~Xianfu Wang
    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
    The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{shawn.wang@ubc.ca}.}
}

\date{\today}

\maketitle

% \vskip 8mm

\begin{abstract} 
    \noindent

    \cite{nesterov_lectures_2018}
\end{abstract}

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
\noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method.

\section{Preliminaries}
    Throughout, assume problem of types $F = f + g$ where $f: \RR \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: Q \rightarrow \overline \RR$ is convex. 
    We consider optimization problem of the form
    \begin{align*}
        \min_x \left\lbrace
            F(x) \defeq f(x) + g(x)
        \right\rbrace. 
    \end{align*}
    To start we define the following quantities
    \begin{enumerate}
        \item The proximal gradient model function: 
        $$
            \widetilde{\mathcal M}^{L^{-1}}
            (x; y) \defeq
            g(x) + f(y) + \langle \nabla f(y), x - y\rangle 
            + \frac{L}{2}\Vert x - y\Vert^2. 
        $$
        \item The proximal point model function: 
        $$
            \mathcal M^{L^{-1}}(x; y) := F(x) + \frac{L}{2}\Vert x - y\Vert^2
        $$
        \item The proximal gradient operator $T_L = [I + L^{-1}\partial g]\circ [I - L^{-1}\nabla f]$. Since $L$ is fixed throughout, the subscript may be omitted and become $T$ instead to make the notations simpler. 
    \end{enumerate}
    To state the following lemma, we define the Bregman divergence of $f$ to be 
    \begin{align*}
        D_f(x, y): \RR^n \times \RR^n \rightarrow \RR 
        \defeq f(x) - f(y) - \langle \nabla f(x), x - y\rangle. 
    \end{align*}

    \begin{lemma}[Proximal gradient envelope] 
        Fix any $y$, we will have for all $x \in \RR^n$ that: 
        \begin{align*}
            \widetilde{\mathcal M}^{L^{-1}}(x; y)
            &= 
            \mathcal M^{L^{-1}}(x; y)- D_f(x, y) \ge \mathcal M^{L^{-1}}(x; y). 
        \end{align*}
    \end{lemma}
    \begin{proof}
        \begin{align*}
            \widetilde{\mathcal M}^{L^{-1}}(x; y) 
            &= 
            g(x) + f(y) + \langle \nabla f(y), x - y\rangle + \frac{L}{2}\Vert x - y\Vert^2
            \\
            &= 
            g(x) + f(x) - f(x) + f(y) 
            + \langle \nabla f(y), x - y\rangle + \frac{L}{2}\Vert x - y\Vert^2
            \\
            &= 
            F(x) - D_f(x, y) + \frac{L}{2}\Vert x - y\Vert^2 
            \\
            &= \mathcal M^{L^{-1}}(x; y) - D_f(x, y). 
        \end{align*}
    \end{proof}

    \subsection{Proximal inequality}
    \begin{theorem}[Proximal inequality]\label{thm:prox-grad-ineq}
        Fix any $y$, we have for all $x$: 
        \begin{align*}
            F(x) - F(Ty) - \langle L(y - Ty), x - Ty\rangle
            &\ge  D_f(x, y). 
        \end{align*}
    \end{theorem}
    \begin{proof}
        $\widetilde {\mathcal M}(\cdot; x)$ is $L$ strongly convex with minimizer $Ty$
        {\small
        \begin{align*}
            \widetilde{\mathcal M}^{L^{-1}}(x; y) - 
            \widetilde{\mathcal M}^{L^{-1}}(Ty; y)
            - 
            \frac{L}{2}\Vert x - Ty\Vert^2
            &\ge 
            0
            \\
            \iff
            \left(
                \mathcal M^{L^{-1}}(x; y) - D_f(x, y)
            \right) - 
            \mathcal M^{L^{-1}}(Ty; y) 
            - 
            \frac{L}{2}\Vert x - Ty\Vert^2
            &\ge 0
            \\
            \iff 
            \left(
                \mathcal M^{L^{-1}}(x; y)
                - 
                \mathcal M^{L^{-1}}(Ty; y)
            \right)
            - 
            D_f(x, y) 
            - \frac{L}{2}\Vert x - Ty\Vert^2
            &\ge 0
            \\
            \iff 
            \left(
                F(x) - F(Ty) 
                + 
                \frac{L}{2}\Vert x - y\Vert^2 - 
                \frac{L}{2}\Vert Ty - y\Vert^2
            \right)
            - 
            D_f(x, y) 
            - \frac{L}{2}\Vert x - Ty\Vert^2
            &\ge 0
            \\
            \iff 
            \left(
                F(x) - F(Ty) 
                + 
                \frac{L}{2}
                \left(
                    \Vert x - Ty + Ty - y\Vert^2
                    - 
                    \Vert y - Ty\Vert^2
                \right)
            \right)
            - 
            D_f(x, y) 
            - \frac{L}{2}\Vert x - Ty\Vert^2
            &\ge 0
            \\
            \iff 
            \left(
                F(x) - F(Ty) 
                + 
                \frac{L}{2}
                \left(
                    \Vert x - Ty\Vert^2 + 
                    2\langle x - Ty, Ty - y\rangle
                \right)
            \right)
            - 
            D_f(x, y) 
            - \frac{L}{2}\Vert x - Ty\Vert^2
            &\ge 0
            \\
            \iff
            \left(
                F(x) - F(Ty) + \frac{L}{2}\Vert x - Ty\Vert^2 
                - L\langle  x - Ty, y - Ty\rangle
            \right)
            - 
            D_f(x, y) 
            - \frac{L}{2}\Vert x - Ty\Vert^2
            &\ge 0
            \\
            \iff 
            F(x) - F(Ty)
            - \langle L(y - Ty), x - Ty\rangle
            - D_f(x, y) 
            &\ge 0. 
        \end{align*}
        }
    \end{proof}
    \begin{remark}
        In our proof, we may use the following alternative representation of the above inequality which is 
        \begin{align*}
            F(x) - F(Ty) - \langle L(y - Ty), x - Ty\rangle - D_f(x, y) &\ge 0
            \\
            \iff
            F(x) - F(Ty)
            - \langle L(y - Ty), x - y + y - Ty\rangle - D_f(x, y) 
            &\ge 0
            \\
            \iff
            F(x) - F(Ty)
            - \langle L(y - Ty),x - y \rangle
            - L\Vert y - Ty\Vert^2
            - D_f(x, y) 
            &\ge 0
            \\
            \implies 
            F(x) - F(Ty)
            - \langle L(y - Ty),x - y \rangle
            - \frac{L}{2}\Vert y - Ty\Vert^2
            - D_f(x, y) 
            &\ge 0
            \\
            \implies
            F(x) - F(Ty)
            - \langle L(y - Ty),x - y \rangle
            - \frac{L}{2}\Vert y - Ty\Vert^2
            - \frac{\mu}{2}\Vert x - y\Vert^2
            &\ge 0. 
        \end{align*}

    \end{remark}

\section{Stepwise formulation of weak accelerated proximal gradient}
    In this section, we introduce the following new quantities and their notations. 
    It's there to make the notations simpler and easier to follow for the proofs that will come later. 
    The algorithm is parameterized by the sequence $y_k, x_k$. 
    We define for all $k \ge 0$ the following quantities: 
    \begin{assumption}
        Choose any integer $k\ge 0$. 
        Given $x_k, y_k, v_k$, we define the following quantities
        \begin{align}
            g_k &\defeq L(y_k - T_L y_k), 
            \label{eqn:grad-map}
            \\
            l_F(x; y_k) &= F(T_Ly_k) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
            \label{eqn:lower-linearization}
            \\
            \epsilon_{k} &\defeq F(x_k) - l_F(x_k; y_k), 
            \label{eqn:regret}
        \end{align}
        Observe that by convexity of $F$, $\epsilon_k \ge 0$ always. 
    \end{assumption}

    \begin{theorem}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
        Let $0 \le \mu \le L$ be the strong convexity and Lipschitz smoothness parameter of $f$. 
        Given iterates $(v_k, x_k)$, or equivalently $(y_k, x_k)$, $(x_k, y_k)$, any $\alpha_k \in (0, 1), \gamma > 0$. 
        Define scalar $\hat \gamma$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ by: 
        \begin{align*}
            \hat \gamma &:= (1 - \alpha_k)\gamma + \mu \alpha_k, 
            \\
            y_k &= 
            (\gamma + \alpha_k \mu)^{-1}(\alpha_k \gamma v_k + \hat\gamma x_k), 
            \\
            g_k &= \mathcal G_L y_k, 
            \\
            v_{k + 1} &= \hat\gamma^{-1}
            (\gamma(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            \\
            x_{k + 1} &= T_L y_k. 
        \end{align*}

    \end{theorem}
    \begin{observation}\label{obs:stepwise-wapg}
        Let's observe Definition \ref*{def:stepwise-wapg} closely. 
        We make two crucial observations here. 
        With the equalities, we define the following quantities associate with it. 
        Fix any integer $k \ge 0$. 
        To verify, we use the fundamental proximal gradient inequality. 
        Next, observe that we have $x_k, y_k, v_k$ lie on the same line because they have 
        \begin{align*}
            (Q1): 
            y_k - v_k &= 
            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k),
            \\
            (Q2): 
            y_k - x_k &= 
            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
        \end{align*}
    \end{observation}
        To see (Q1), observe 
        \begin{align*}
            y_k - v_k &= 
            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k)
            \\
            \iff 
            -(\alpha_k \gamma\hat \gamma^{-1} + 1)y_k
            &= 
            - \alpha_k \gamma \hat \gamma^{-1}v_k - x_k
            \\
            \iff 
            y_k &= 
            \frac{
                \alpha_k \gamma \hat \gamma^{-1}v_k + x_k
            }{1 + \alpha_k \gamma \hat \gamma^{-1}}
            \\
            &=  
            \frac{\alpha_k \gamma v_k + \hat \gamma x_k}{\gamma + \alpha_k \mu}.
        \end{align*}
        On the first equality (Q1), we multiplied both side of the equation by $\gamma_{k + 1}/\alpha_k \gamma_k$ and then group $y_k$ on the LHS. 
        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma$, leaving the numerator $\hat \gamma + \alpha_k \gamma = \gamma + \alpha_k \mu$. 
        We used the definition of $\hat \gamma$ here. 
        To see the second equality (Q2), consider: 
        \begin{align*}
            y_k &= (\gamma + \alpha_k \mu)^{-1}(\alpha_k \gamma v_k + \hat\gamma x_k)
            \\
            \iff
            y_k - x_k &= 
            (\gamma + \alpha_k \mu)^{-1}
            (\alpha_k \gamma_k v_k - (\gamma + \alpha_k \mu)x_k + \hat \gamma x_k)
            \\
            \iff 
            (\gamma + \alpha_k \mu)(y_k - x_k)
            &= 
            \alpha_k\gamma v_k + 
            (\hat \gamma - \gamma - \alpha_k \mu) x_k
            \\
            &= \alpha_k \gamma v_k - \alpha_k \gamma x_k 
            \\
            &= \alpha_k \gamma(v_k - x_k)
            \\
            \iff 
            y_k - x_k &= 
            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
        \end{align*}
        On the second equality that follows the second $\iff$ we just substituted $\hat\gamma = (1 - \alpha_k)\gamma + \alpha_k \mu$. 
        Therefore, we discover that $x_k, v_k, y_k$ lies on the same line.

    \begin{proposition}[Stepwise lyapunov]\label{prop:stepwise-lyapunov}
        For all $k \ge 0$, given $v_k, x_k, \alpha_k, \gamma_k$, let $\mu \ge 0$ iterates: $y_k, v_{k + 1}, x_{k + 1}, \alpha_{k + 1},\gamma \ge 0$ be given by Definition \ref*{def:stepwise-wapg}. 
        Let $F^* = F(x^*)$ where is an arbitrary $x^* \in \RR^n$. 
        If we define $R_{k + 1}$ by some arbitrary $R_k \in \RR^n$: 
        \begin{align*}
            R_{k + 1}
            &\defeq 
            \frac{1}{2}\left(
                L^{-1} - \frac{\alpha_k^2}{\hat\gamma}
            \right)\Vert g_k\Vert^2
            + 
            (1 - \alpha_k)
            \left(
                \epsilon_k + R_k + 
                \frac{\mu\alpha_k\gamma}{2\hat\gamma}
                \Vert v_k - y_k\Vert^2
            \right). 
        \end{align*}
        Then we have the inequality: 
        \begin{align*}
            F(x_{k + 1}) - F^* + R_{k + 1} + \frac{\hat \gamma}{2}\Vert v_{k + 1} - x^*\Vert^2
            &\le 
            (1 - \alpha_k)
            \left(
                F(x_k) - F^* + R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
            \right). 
        \end{align*}
    \end{proposition}
    \begin{proof}
        Start by considering the first and the third term of the LHS of the inequality that we want to prove. 
        \begin{align*}
            F(x_{k + 1}) &= 
            F(x_k) - \epsilon_k - \langle  g_k, x_k - y_k\rangle - \frac{1}{2L}\Vert g_k\Vert^2, 
            \\
            R_{k + 1}
            &= 
            \frac{1}{2}\left(
                L^{-1} - \frac{\alpha_k^2}{\hat \gamma}
            \right)\Vert g_k\Vert^2
            + 
            (1 - \alpha_k)
            \left(
                \epsilon_k + R_k + 
                \frac{\mu\alpha_k\gamma}{2\hat \gamma}
                \Vert v_k - y_k\Vert^2
            \right), 
            \\
            \implies 
            F(x_{k + 1}) + R_{k + 1}
            &= 
            F(x_k) - \epsilon_k - \langle  g_k, x_k - y_k\rangle
            - \frac{\alpha_k^2}{2\hat \gamma}\Vert g_k\Vert^2
            \\
            &\quad 
                + 
                (1 - \alpha_k)
                \left(
                    \epsilon_k + R_k + 
                    \frac{\mu\alpha_k\gamma_k}{2\hat \gamma}
                    \Vert v_k - y_k\Vert^2
                \right). 
        \tag{1*}
        \end{align*}
        Coefficient of $\epsilon_k$ and $\Vert g_k\Vert^2$ are grouped. 
        Next, we have: 
        \begin{align*}
            \frac{\hat \gamma}{2}\Vert v_{k + 1} - x^* \Vert^2
            &= 
            \frac{\hat \gamma}{2}\Vert 
                \hat \gamma^{-1}
                (
                    \gamma_k(1 - \alpha_k)v_k - 
                    \alpha_k g_k + \mu \alpha_k y_k
                )
                - x^* 
            \Vert^2
            \\
            &=  
            \frac{\hat \gamma}{2}
            \Vert 
                \hat \gamma^{-1}
                (
                \hat \gamma v_k + \mu \alpha_k(y_k - v_k)
                    - \alpha_k g_k
                )
                - x^* 
            \Vert^2
            \\
            &= 
            \frac{\hat \gamma}{2}
            \Vert 
                v_k + \hat \gamma^{-1} \mu \alpha_k (y_k - v_k)
                - \hat \gamma^{-1}\alpha_k g_k
                - x^* 
            \Vert^2
            \\
            &= 
            \frac{\hat \gamma}{2}
            \Vert v_k - x^*\Vert^2 
            + 
            \frac{\alpha_k^2}{2\hat \gamma}\Vert \mu(y_k - v_k) - g_k\Vert^2 
            \\ &\quad 
                + 
                \langle v_k - x^*, \mu \alpha_k(y_k - v_k) - \alpha_k g_k\rangle
            \\
            &= 
            \left(
            \frac{(1 - \alpha_k)\gamma + \mu \alpha_k}{2} 
            \right)\Vert v_k - x^*\Vert^2
            \\ &\quad
                + 
                \frac{\alpha_k^2}{2\hat \gamma}
                \Vert \mu(y_k - v_k) - g_k\Vert^2 
                + 
                \langle v_k - x^*, \mu \alpha_k(y_k - v_k) - \alpha_k g_k\rangle. 
        \tag{2*}
        \end{align*}
        On the above derivation, the first equality is by definition of $v_{k + 1}$; the second equality is by $\hat \gamma = (1 - \alpha_k)\gamma + \mu \alpha_k$ the second equality comes by considering: 
        \begin{align*}
            \gamma(1 - \alpha_k) v_k &= 
            (\hat \gamma  - \mu \alpha_k)v_k
            = \hat \gamma v_k - \mu\alpha_k v_k
            \\
            \iff 
            \gamma(1 - \alpha_k) v_k + \mu \alpha_k y_k
            &= 
            \hat \gamma v_k + \mu \alpha_k(y_k - v_k). 
        \end{align*}
        Focusing on the last two terms by the end of expression (2*), we have  
        \begin{align*}
            \frac{\alpha^2_k}{2\hat \gamma} 
            \Vert \mu(y_k - v_k) - g_k\Vert^2
            & = 
            \frac{\alpha_k^2\mu}{\hat \gamma}
            \left(
                \frac{\mu}{2}\Vert y_k - v_k\Vert^2 
                - \langle y_k - v_k, g_k\rangle
            \right)
            + \frac{\alpha_k^2}{2\hat \gamma}\Vert g_k\Vert^2, 
            \\
            \langle v_k - x^*, \mu \alpha_k(y_k - v_k) - \alpha_k g_k\rangle
            &= 
            \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle 
            - \alpha_k \langle v_k - x^*, g_k\rangle. 
        \tag{2.1*}
        \end{align*}
        Adding the LHS of both equations above together gives: 
        {\small
        \begin{align*}
            & \quad 
            \frac{\alpha^2_k}{2\hat \gamma} 
            \Vert \mu(y_k - v_k) - g_k\Vert^2
            + 
            \langle v_k - x^*, \mu \alpha_k(y_k - v_k) - \alpha_k g_k\rangle
            \\
            &= 
            \left\langle g_k, 
                - \alpha_k(v_k - x^*) 
                - \frac{\alpha_k^2\mu}{\hat \gamma}(y_k - v_k)
            \right\rangle
            + \frac{\alpha_k^2}{2\hat \gamma}\Vert g_k\Vert^2
            + \frac{\alpha_k^2 \mu^2}{2\hat \gamma}\Vert y_k - v_k\Vert^2
            + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle. 
        \end{align*}
        }
        With the above we can conclude that (2*) simplifies to 
        {\small
        \begin{align*} 
            & 
            \left(
            \frac{(1 - \alpha_k)\gamma + \mu \alpha_k}{2} 
            \right)\Vert v_k - x^*\Vert^2
            + 
            \left\langle g_k, 
                - \alpha_k(v_k - x^*) 
                - \frac{\alpha_k^2\mu}{\hat \gamma}(y_k - v_k)
            \right\rangle
            \\
            & \quad 
                + \frac{\alpha_k^2}{2\hat \gamma}\Vert g_k\Vert^2
                + \frac{\alpha_k^2 \mu^2}{2\hat \gamma}\Vert y_k - v_k\Vert^2
                + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle. 
        \tag{2.2*}
        \end{align*}
        }
        Recall from 
        \hyperref[obs:stepwise-wapg]{Observations \ref*{obs:stepwise-wapg}} that: 
        \begin{align*}
            (Q1): 
            y_k - v_k &= 
            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k),
            \\
            (Q2): 
            y_k - x_k &= 
            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
        \end{align*}
        Ok that is a lot, we list the following equations to assist things: 
        \begin{align*}
            &  
            - \alpha_k(v_k - x^*) - \frac{\alpha_k^2 \mu}{\hat \gamma}(y_k - v_k) - (x_k - y_k)
            \\
            \text{use Q1}: & =
            -\alpha_k(v_k - x^*) -
            \frac{\alpha_k^2}{\hat \gamma}\frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k)
            - (x_k - y_k) 
            \\
            &= 
            -\alpha_k(v_k - x^*) -
            \frac{\alpha_k \mu}{\gamma}(x_k - y_k)
            - (x_k - y_k) 
            \\
            &= 
            -\alpha_k(v_k - x^*) -
            \left(
                1 + \frac{\alpha_k \mu}{\gamma}
            \right)(x_k - y_k)
            \\
            \text{use Q2}: 
            &= 
            -\alpha_k(v_k - x^*) - 
            \frac{\alpha_k \mu + \gamma}{\gamma}
            \frac{\alpha_k \gamma}{\gamma_k + \alpha_k \mu}(x_k - v_k)
            \\
            &= 
            -\alpha_k(v_k - x^*)
            - \alpha_k(x_k - v_k)
            \\
            &= \alpha_k(x^* - x_k). 
        \tag{Q3}
        \end{align*}
        Adding (2.2*) to (1*) gives: 
        \begin{align*}
            &
            F(x_k) - \epsilon_k - \langle  g_k, x_k - y_k\rangle
            - \frac{\alpha_k^2}{2\hat \gamma}\Vert g_k\Vert^2
            + (1 - \alpha_k)
            \left(
                \epsilon_k + R_k + 
                \frac{\mu\alpha_k\gamma}{2\hat \gamma}
                \Vert v_k - y_k\Vert^2
            \right)
            \\
            &\quad 
                + 
                \left(
                \frac{(1 - \alpha_k)\gamma + \mu \alpha_k}{2} 
                \right)\Vert v_k - x^*\Vert^2
                + 
                \left\langle g_k, 
                    - \alpha_k(v_k - x^*) 
                    - \frac{\alpha_k^2\mu}{\hat \gamma}(y_k - v_k)
                \right\rangle
            \\
            & \quad 
                + \frac{\alpha_k^2}{2\hat \gamma}\Vert g_k\Vert^2
                + \frac{\alpha_k^2 \mu^2}{2\hat \gamma}\Vert y_k - v_k\Vert^2
                + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle
            \\
            &= 
            F(x_k) - \epsilon_k 
            + \left\langle 
                g_k, 
                - \alpha_k(v_k - x^*) 
                - \frac{\alpha_k^2\mu}{\hat \gamma}(y_k - v_k)
                - (x_k - y_k)
            \right\rangle
            \\
            &\quad 
                + (1 - \alpha_k)
                \left(
                    \epsilon_k + R_k + 
                    \frac{\mu\alpha_k\gamma}{2\hat \gamma}
                    \Vert v_k - y_k\Vert^2
                \right)
                + 
                \left(
                \frac{(1 - \alpha_k)\gamma + \mu \alpha_k}{2} 
                \right)\Vert v_k - x^*\Vert^2
            \\
            & \quad 
                + \frac{\alpha_k^2 \mu^2}{2\hat \gamma}\Vert y_k - v_k\Vert^2
                + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle
            \\
            \text{Use Q3}&= 
            F(x_k) - \epsilon_k 
            + \alpha_k\left\langle 
                g_k, 
                x^* - x_k
            \right\rangle
            \\
            &\quad 
                + (1 - \alpha_k)
                \left(
                    \epsilon_k + R_k + 
                    \frac{\mu\alpha_k\gamma}{2\hat \gamma}
                    \Vert v_k - y_k\Vert^2
                \right)
                + 
                \left(
                \frac{(1 - \alpha_k)\gamma + \mu \alpha_k}{2} 
                \right)\Vert v_k - x^*\Vert^2
            \\
            & \quad 
                + \frac{\alpha_k^2 \mu^2}{2\hat \gamma}\Vert y_k - v_k\Vert^2
                + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle
            \\
            &= 
            F(x_k) - \alpha_k\epsilon_k + \alpha_k\langle g_k, x^* - x_k\rangle
            + 
            (1 - \alpha_k)\left(
                R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
            \right)
            \\&\quad 
                + \frac{(1 - \alpha_k)\mu\alpha_k\gamma}{2\hat \gamma}\Vert v_k - y_k\Vert^2
                + \frac{\mu \alpha_k}{2}\Vert v_k - x^*\Vert^2
            \\&\quad 
                + \frac{\alpha_k^2 \mu^2}{2\hat\gamma}\Vert y_k - v_k\Vert^2
                + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle. 
        \tag{3*}
        \end{align*}
        From the left to the right on the first equality, coefficients of $\Vert g_k\Vert^2$ cancels out to zero and the inner product containing $g_k$ are grouped. 
        Going from the left to the right of the third equality, we applied (Q3) derived earlier to simplify the inner product term. 
        The last equalities re-arranged terms and grouped the coefficients of $\epsilon_k$ together. 
        Taking a page break, continuing on (3*) we have
        \begin{align*}
            &
            F(x_k) - \alpha_k(\epsilon_k + \langle g_k, x_k - x^*\rangle)
            + 
            (1 - \alpha_k)\left(
                R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
            \right)
            \\&\quad 
                + \frac{(1 - \alpha_k)\mu\alpha_k\gamma}{2\hat \gamma}\Vert v_k - y_k\Vert^2
                + \frac{\mu \alpha_k}{2}\Vert v_k - x^*\Vert^2
            \\&\quad 
                + \frac{\alpha_k^2 \mu^2}{2\hat \gamma}\Vert y_k - v_k\Vert^2
                + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle
            \\
            &= 
            F(x_k) - \alpha_k(\epsilon_k + \langle g_k, x_k - x^*\rangle)
            + 
            (1 - \alpha_k)\left(
                R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
            \right)
            \\ &\quad 
                + 
                \left(
                    \frac{(1 - \alpha_k)\mu\alpha_k\gamma}{2\hat \gamma}
                    + 
                    \frac{\alpha_k^2 \mu^2}{2\hat \gamma}
                \right)\Vert y_k - v_k\Vert^2
                + \frac{\mu \alpha_k}{2}\Vert v_k - x^*\Vert^2 
                + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle
            \\
            & =
            F(x_k) - \alpha_k(\epsilon_k + \langle g_k, x_k - x^*\rangle)
            + 
            (1 - \alpha_k)\left(
                R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
            \right)
            \\ &\quad 
                + 
                \frac{\mu \alpha_k}{2}\Vert y_k - v_k\Vert^2
                + \frac{\mu \alpha_k}{2}\Vert v_k - x^*\Vert^2 
                + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle
            \\ &=
            F(x_k) - \alpha_k(\epsilon_k + \langle g_k, x_k - x^*\rangle)
            + 
            (1 - \alpha_k)\left(
                R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
            \right)
            \\ &\quad 
                +
                \frac{\mu\alpha_k}{2} \Vert y_k - x^*\Vert^2
            \\&= 
            F(x_k) - \alpha_k\left(
                \epsilon_k + \langle g_k, x_k - x^*\rangle
                - \frac{\mu}{2}\Vert y_k - x^*\Vert^2
            \right)
            + 
            (1 - \alpha_k)\left(
                R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
            \right). 
            \tag{3.1*}
        \end{align*}
        On the first equality, coefficients of $\Vert y_k - v_k\Vert^2$ are grouped together. 
        On the second to the third equality, the terms had been simplified by 
        \begin{align*}
            \frac{(1 - \alpha_k)\mu\alpha_k\gamma}{2\hat \gamma} + 
            \frac{\alpha_k^2 \mu^2}{2\hat \gamma}
            &= 
            \frac{\mu\alpha_k}{2}\left(
                \frac{(1 - \alpha_k)\gamma_k + \alpha_k \mu}{\hat \gamma}
            \right)
            \\
            &= \frac{\mu\alpha_k}{2}\left(
                \frac{\hat \gamma}{\hat \gamma}
            \right) = \frac{\mu\alpha_k}{2}. 
        \end{align*}
        (3.1*) was adding (1*) and (2.2*) together, which is the same as adding (1*) and (2*) together. 
        So that was all equal to (1*) + (2*) and it says: 
        \begin{align*}
            & F(x_{k + 1}) + R_{k + 1} + 
            \frac{\hat \gamma}{2}\Vert v_{k + 1} - x^*\Vert^2
            \\
            &= 
            F(x_k) - \alpha_k\left(
                \epsilon_k + \langle g_k, x_k - x^*\rangle
                - \frac{\mu}{2}\Vert y_k - x^*\Vert^2
            \right)
            + 
            (1 - \alpha_k)\left(
                R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
            \right)
            \\
            & \iff 
            \\
            & F(x_{k + 1}) - F(x^*) + R_{k + 1} + 
            \frac{\hat \gamma}{2}\Vert v_{k + 1} - x^*\Vert^2
            \\
            &= 
            F(x_k) - F(x^*) - \alpha_k\left(
                \epsilon_k + \langle g_k, x_k - x^*\rangle
                - \frac{\mu}{2}\Vert y_k - x^*\Vert^2
            \right)
            + 
            (1 - \alpha_k)\left(
                R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
            \right)
            \\
            &= (1 - \alpha_k)(F(x_k) - F(x^*))
            + \alpha_k\left(
                F(x_k) - F(x^*) - \epsilon_k - \langle g_k, x_k - x^*\rangle + \frac{\mu}{2}\Vert y_k - x^*\Vert^2
            \right)
            \\ &\quad 
                + 
                (1 - \alpha_k)\left(
                    R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
                \right). 
        \tag{3.2*}
        \end{align*}
        Focusing on the second term, we simplify the multiplier inside: 
        {\small
        \begin{align*}
            & F(x_k) - F(x^*) - \epsilon_k - \langle g_k, x_k - x^*\rangle + \frac{\mu}{2}\Vert y_k - x^*\Vert^2
            \\
            &= 
            F(x_k) - F(x^*) - \left(
                F(x_k) - F(T_L y_k) - \langle g_k, x_k - y_k\rangle - \frac{1}{2L}\Vert g_k\Vert^2
            \right)- \langle g_k, x_k - x^*\rangle + \frac{\mu}{2}\Vert y_k - x^*\Vert^2
            \\
            &= F(T_L y_k) - F(x^*) + \langle g_k, x^* - y_k\rangle + \frac{\mu}{2}\Vert y_k - x^*\Vert^2
            + \frac{1}{2L}\Vert g_k\Vert^2 \le 0. 
        \tag{4*}    
        \end{align*}
        }
        On the last line, we expand the definition of $g_k$ and then used 
        \hyperref[thm:prox-grad-ineq]{Theorem \ref*{thm:prox-grad-ineq}}. 
        Therefore, we conclude that: 
        {\small
        \begin{align*}
            F(x_{k + 1}) - F(x^*) + R_{k + 1} + 
            \frac{\hat \gamma}{2}\Vert v_{k + 1} - x^*\Vert^2
            &\le 
            (1 - \alpha_k)\left(
                F(x_k) - F(x^*) + R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
            \right). 
        \end{align*}
        }
    \end{proof}
    \begin{remark}
        \textcolor{red}
        {
        Use $\mu = D_f(x^*, y_k)/\Vert y_k - x^*\Vert^2$ also works, $\mu$ is a pessimistic choice for the inequality above. 
        }
    \end{remark}

\section{Formulation of WAPG and its convergence rates}

    \begin{definition}[Weak accelerated proximal gradient (WAPG)]\label{def:wapg}
        \;\\
        Choose any $\gamma_0$, $(x_0, v_0)$ or equivalently $(x_0, y_0), (y_0, v_0)$. 
        Given any sequence $(\rho_k)_{k\ge0}, (\alpha_k)_{k \ge0}$ such that for all integer $k\ge 0$, they have $\rho_k \in [0, 1], \alpha_k \in (0, 1)$. 
        The algorithm generates a sequence of $(x_k, y_k, v_k)$ such that they satisfy for all $k\ge 0$ recursively: 
        $$
        \begin{aligned}
            \gamma_k &:= \left.\begin{cases}
                \rho_{k - 1}L\alpha_{k - 1}^2 & k \ge 1,
                \\
                \gamma_0 & k = 0. 
            \end{cases}\right\rbrace,
            \\
            \hat \gamma_{k + 1} &:= L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \mu \alpha_k, 
            \\
            y_k &= 
            (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
            \\
            g_k &= \mathcal G_L y_k, 
            \\
            v_{k + 1} &= 
            \hat\gamma^{-1}_{k + 1}
            (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            \\
            x_{k + 1} &= T_L y_k. 
        \end{aligned}
        $$
    \end{definition}

    \begin{proposition}[WAPG convergence claim]\label{prop:wagp-convergence}
        Let vectors $(x_k, y_k, v_k)_{k \ge0}$ and scalars $\alpha_k$ be generated by the weak accelerated proximal gradient algorithm. 
        Define recursively for all $k\ge1$ by 
        $$
        \begin{aligned}
        R_{k + 1}
        := 
        \frac{1}{2}\left(
            L^{-1} - \frac{\alpha_k^2}{\hat \gamma_{k + 1}}
        \right)\Vert g_k\Vert^2
        + 
        (1 - \alpha_k)
        \left(
            \epsilon_k + R_k + 
            \frac{\mu\alpha_k\gamma_k}{2\hat \gamma_{k + 1}}
            \Vert v_k - y_k\Vert^2
        \right). 
        \end{aligned}
        $$
        Choose $R_0= 0$ to be the base case. 
        Choose any $x^* \in \RR^n$ then
        $$
        \begin{aligned}
            F(x_{k + 1}) - F(x^*) + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
            &\le 
            \left(
                \prod_{i = 0}^{k} \left(1  - \alpha_i\right)
            \right)
            \left(
                F(x_0) - F(x^*) + \frac{\gamma_0}{2}\Vert v_k - x^*\Vert^2
            \right). 
        \end{aligned}
        $$
    \end{proposition}
    \begin{proof}  
        Recall the 
        \hyperref[prop:stepwise-lyapunov]{Proposition \ref*{prop:stepwise-lyapunov}}, 
        since the choice of $\gamma, \hat \gamma$ is arbitrary choices for the theorem, we choose $\gamma = \rho_{k - 1} L \alpha_{k - 1}^2, \hat \gamma = L \alpha_k^2$, giving us: 
        {\footnotesize
        \begin{align*}
            F(x_{k + 1}) - F^* + R_{k + 1} + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
            &\le 
            (1 - \alpha_k)
            \left(
                F(x_k) - F^* + R_k + \frac{\rho_{k - 1}L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2
            \right)
            \\
            &\le 
            (1 - \alpha_k)
            \left(
                F(x_k) - F^* + R_k + \frac{L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2
            \right)
            \\
            &\le 
            \left(
                \prod_{i = 0}^{k} \left(1  - \alpha_i\right)
            \right)
            \left(
                F(x_0) - F^* + R_0 + \frac{\gamma_0}{2}\Vert v_k - x^*\Vert^2
            \right). 
        \end{align*}
        }
        Going from the left to the right on the second inequality, we used the fact that $\rho_{k - 1} \in [0, 1]$. 
        Additionally, the algorithm converges by considering $R_k$: 
        \begin{align*}
            R_{k + 1}
            &= 
            \frac{1}{2}\left(
                L^{-1} - \frac{\alpha_k^2}{\hat \gamma_{k + 1}}
            \right)\Vert g_k\Vert^2
            + 
            (1 - \alpha_k)
            \left(
                \epsilon_k + R_k + 
                \frac{\mu\alpha_k\gamma_k}{2\hat \gamma_{k + 1}}
                \Vert v_k - y_k\Vert^2
            \right)
            \\
            &= (1 - \alpha_k)
            \left(
                \epsilon_k + R_k 
                + \frac{\mu\alpha_k\gamma_k}{2\hat \gamma_{k + 1}}
                \Vert v_k - y_k\Vert^2
            \right)
            \\
            &\ge 
            (1 - \alpha_k) R_k
            \\
            &\ge R_0 \prod_{i = 0}^{k} \left(1 - \alpha_i\right) = 0. 
        \end{align*}
        Going from the left to the right on the first equality, we used the fact that $\hat \gamma_{k + 1} = L \alpha_{k}^2$.
        This makes coefficient of $\Vert g_k\Vert^2$ zero. 
        The fist inequality is by $\epsilon_k \ge 0$ and the non-negativity of the remaining terms. 
        The last equality is by the assumption that $R_0 = 0$. 
        Therefore: 
        \begin{align*}
            F(x_{k + 1}) - F^* +
            \frac{L\alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
            &\le 
            \left(
                \prod_{i = 0}^{k} \left(1  - \alpha_i\right)
            \right)
            \left(
                F(x_0) - F^* + \frac{\gamma_0}{2}\Vert v_k - x^*\Vert^2
            \right). 
        \end{align*}
    \end{proof}
    \begin{remark}        
        \textcolor{red}
        {
            The choice of $\rho_k \in (0, 1]$ is just a convenience for convergence analysis. 
            It's a belief that there exists sequence $\rho_k$ where $\rho_k \ge 1$ where the algorithm would have a chance at converging still. 
        }
    \end{remark}

\section{WAPG covers variants of APG in the literatures}
    Many variants of the accelerated proximal gradient algorithm fits into the following form which we called ``abstract similar triangle". 
    \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
        For all $k\ge 0$, iterates $(w_t, y_t, x_{t + 1}, z_{t + 1})$ satisfies recursively that: 
        \begin{align*}
            y_k &= (1 + \tau_k)^{-1}(v_k + \tau_k x_k),
            \\
            v_{k + 1} &= (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - (1 + \xi_k)^{-1}\delta_k g_k,
            \\
            x_{k + 1} &= y_k - L^{-1} g_k. 
        \end{align*}
        If $1 + \xi_t + \tau_t = L\delta_t$. Then 
        $$
            v_{k + 1} - x_{k + 1} = (1 + \xi_t)^{-1}\tau_t(x_{k + 1} - x_k). 
        $$
        Which makes the algorithm a similar triangle form. 
    \end{proposition}
    \begin{proof}
        We are interested in identifying the conditions required for the sequence of $\xi_t, \tau_t, \delta_t$ such that there exists $\theta_t$ satisfying: 
        \begin{align*}
            x_{t + 1} - z_{t + 1} 
            &= \theta_t(z_{t + 1} - z_t)
        \end{align*}
        To verify, do 
        \begin{align*}
            x_{t + 1} &= 
            (1 + \xi_t)^{-1}(x_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
            \\
            & \textcolor{gray}{
                x_t = (1 + \tau_t)y_t - \tau_t z_t
            }
            \\
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t)y_t - \tau_t z_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
            \\
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
            \\
            x_{t + 1} - z_{t + 1}
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
            - (y_t - L^{-1}\mathcal G_Ly_t)
            \\
            &= 
            (1 + \xi_t)^{-1}(\tau_ty_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
            + L^{-1}\mathcal G_Ly_t
            \\
            &= 
            (1 + \xi_t)^{-1}
            \left(
                \tau_ty_t - \tau_t z_t + (L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
            \right)
            \\
            &= 
            (1 + \xi_t)^{-1}\tau_t
            \left(
                y_t - z_t + 
                \tau_t^{-1}(L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
            \right)
        \end{align*}
        The RHS is can be verified through 
        \begin{align*}
            z_{t + 1} - z_t &= 
            y_t - L^{-1}\mathcal G_L(y_t) - z_t
            \\
            &= (y_t - z_t) - L^{-1}\mathcal G_L(y_t). 
        \end{align*}
        It necessitates the condition: 
        \begin{align*}
            \tau_t^{-1}(L^{-1}(1 + \xi_t) - \delta_t) 
            &= - L^{-1}
            \\
            (1 + \xi_t) - L\delta_t
            &= 
            - \tau_t
            \\
            1 + \xi_t + \tau_t
            &=
            L\delta_t. 
        \end{align*}
        Which allows for: 
        \begin{align*}
            x_{t + 1} - z_{t + 1} &= 
            (1 + \xi_t)^{-1}\tau_t
            \left(y_t - z_t - L^{-1}\mathcal G_L(y_t)\right) 
            = 
            (1 + \xi_t)^{-1}\tau_t(z_{t + 1} - z_t). 
        \end{align*}

    \end{proof}

    \subsection{Narrowing it down}
        \begin{proposition}[WAPG intermediate Form I]\label{prop:wapg-intermediate-form}
            Suppose that $(y_i, x_i, v_i)$ are generated by 
            \hyperref[def:wapg]{Definition \ref*{def:wapg}}
            for all $0 \le i \le k$. 
            Then the iterates can be expressed without the sequence $(\gamma_k)_{k \ge0}, (\rho_k)_{k\ge0}$, and they satisfy: 
            $$
            \begin{aligned}
                y_k &= 
                \left(
                    1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
                \right)^{-1}
                \left(
                    v_k + 
                    \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
                \right), 
                \\
                x_{k + 1} &= 
                y_k - L^{-1} \mathcal G_L y_k, 
                \\
                v_{k + 1} &= 
                \left(
                    1 + \frac{\mu}{L \alpha_k - \mu}
                \right)^{-1}
                \left(
                    v_k + 
                    \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k, 
                \\
                L &\alpha_k^2 \le (1 - \alpha_k)L \alpha_{k - 1} + \mu \alpha_k. 
            \end{aligned}
            $$
        \end{proposition}
        \begin{proof}
            \begin{align*}
                y_{k} &= 
                (\gamma_k + \alpha_k \mu)^{-1}
                (\alpha_k \gamma_k v_k + \hat \gamma_{k + 1}x_k)
                \\
                &= 
                (\hat \gamma_{k + 1} + \alpha_k \gamma_k)^{-1}
                (\alpha_k \gamma_k v_k + \hat \gamma_{k + 1}x_k)
                \\
                &= 
                \left(
                    \frac{\hat \gamma_{k + 1}}{\alpha_k\gamma_k} + 1
                \right)^{-1}
                \left(
                    v_k + \frac{\hat \gamma_{k + 1}}{\alpha_k \gamma_k} x_k
                \right)
                \\
                &= 
                \left(
                    1 + \frac{L\alpha_k^2}{\alpha_k \rho_{k - 1}L\alpha_{k - 1}^2} 
                \right)^{-1}
                \left(
                    v_k + \frac{L\alpha_k^2}{\alpha_k \rho_{k - 1}L\alpha_{k - 1}^2} x_k
                \right)
                \\
                &= 
                \left(
                    1 + \frac{\alpha_k}{\rho_{k - 1}\alpha_{k - 1}^2}
                \right)^{-1}
                \left(
                    v_k + 
                    \frac{\alpha_k}{\rho_{k - 1}\alpha_{k - 1}^2} x_k
                \right)
                \\
                &= 
                \left(
                    1 + \frac{L - L \alpha_k}{L \alpha_k - \mu}
                \right)^{-1}
                \left(
                    v_k + 
                    \frac{L - L \alpha_k}{L \alpha_k - \mu} x_k
                \right). 
            \end{align*}
            From the left to right of the second inequality, we used the fact that $\hat \gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k\mu$. 
            Going from the left to the right of the second last inequality, we did the following: 
            \begin{align*}
                L\alpha_k^2 &= 
                (1 - \alpha_k)L\rho_{k- 1}\alpha_{k - 1}^2 + \alpha_k \mu 
                \\
                \iff 
                L \alpha_k^2 - \alpha_k\mu &= 
                (1 - \alpha_k)L \rho_{k - 1}\alpha_{k - 1}^2
                \\
                \iff 
                \rho_{k - 1}\alpha_{k - 1}^2
                &= 
                \frac{L \alpha_k^2 - \alpha_k\mu}{L (1 - \alpha_k)}
                \\
                \iff 
                \frac{1}{\rho_{k - 1}\alpha_{k - 1}^2}
                &= 
                \frac{L (1 - \alpha_k)}{L \alpha_k^2 - \alpha_k\mu}
                \\
                \iff 
                \frac{\alpha_k}{\rho_{k - 1}\alpha_{k - 1}^2}
                &= 
                \frac{L - L\alpha_k}{L\alpha_k - \mu}. 
            \end{align*}
            For $v_{k + 1}$ considers 
            \begin{align*}
                v_{k + 1} &= 
                \hat \gamma_{k + 1}^{-1}
                ((1 - \alpha_k)\gamma_k v_k + \mu\alpha_k y_k)
                - \alpha_k\hat \gamma_{k + 1}^{-1}\mathcal G_L y_k
                \\
                &= 
                ((1 - \alpha_k)\gamma_k + \alpha_k \mu)^{-1}
                \left(
                    (1 - \alpha_k)\gamma_k v_k + \mu\alpha_k y_k
                \right)
                - \alpha_k\hat \gamma_{k + 1}^{-1}\mathcal G_L y_k
                \\
                &= 
                \left(
                    1 + \frac{\alpha_k\mu}{(1 - \alpha_k)\gamma_k}
                \right)^{-1}
                \left(
                    v_k + 
                    \frac{\alpha_k\mu}{(1 - \alpha_k)\gamma_k} y_k
                \right)
                - \alpha_k\hat \gamma_{k + 1}^{-1}\mathcal G_L y_k
                \\
                &= 
                \left(
                    1 + \frac{\alpha_k\mu}{(1 -\alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2}
                \right)^{-1}
                \left(
                    v_k + 
                    \frac{\alpha_k\mu}{(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2} y_k
                \right)
                - \frac{1}{L\alpha_{k}}\mathcal G_L y_k
                \\
                &= 
                \left(
                    1 + \frac{\alpha_k \mu}{L \alpha_k^2 - \alpha_k \mu}
                \right)^{-1}
                \left(
                    v_k + 
                    \frac{\alpha_k \mu}{L \alpha_k^2 - \alpha_k \mu} y_k
                \right)
                - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
            \end{align*}
            Going from the left to the right of the second equality, we substitute $\hat \gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \mu\alpha_k$. 
            Going from the left to right of the second last equality, we made the substitution $\hat \gamma_{k + 1} = L \alpha_k^2$, and $\gamma_k = \rho_{k - 1}L \alpha_{k - 1}^2$. 
            To arrive at the last equality, we considered substituting the denominator by the definition for $\hat\gamma_{k + 1}$. 
            \begin{align*}
                (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2
                &= 
                \hat \gamma_{k + 1} - \mu \alpha_k
                = 
                L\alpha_{k}^2 - \alpha_k\mu. 
            \end{align*}
            The proof of the intermediate form is no complete. 
            This form doesn't have $\rho_k, \gamma_k, \hat \gamma_k$ in it. 
            Finally, to see the inequality, consider the fact that $\rho_k \in [0, 1]$ so it has: 
            \begin{align*}
                \hat \gamma_{k + 1} = L\alpha_k^2 = (1 - \alpha_k)\rho_{k - 1}L \alpha_{k - 1}^2 + \alpha_k \mu 
                \le (1 - \alpha_k)L \alpha_{k - 1}^2 + \alpha_k \mu. 
            \end{align*}
            The only auxiliary sequence it needs is $\alpha_k$, which directly links to the convergence rate of the algorithm. 
        \end{proof}
        \begin{remark}
            Observe that this is fits the abstract similar triangle form described in Proposition \ref{prop:abs-st-form} perfectly by exchanging $x_k$ with $z_k$, $v_k$ with $x_k$. 
        \end{remark}

        \begin{proposition}[WAPG fits similar triangle form]\label{prop:wagp-st-form}
            Given any sequence $(\alpha_i)_{i \ge k}$ such that $\alpha_i \in (0, 1)$ for all $0\le i \le k$ and $L\alpha_k^2\le (1 - \alpha_k)L\alpha_{k - 1}^2 + \alpha_k \mu$. 
            Let $(x_k, y_k, v_k)$ to be generated as specified by Definition \ref{def:wapg} by the $(\alpha_k)_{k \ge0}$.
            Then the iterate $(v_k)$ can be expressed without $y_k, v_k$: 
            $$
            \begin{aligned}
                y_k &= 
                \left(
                    1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
                \right)^{-1}
                \left(
                    v_k + 
                    \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
                \right), 
                \\
                x_{k + 1} &= 
                y_k - L^{-1} \mathcal G_L y_k, 
                \\
                v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
            \end{aligned}
            $$
        \end{proposition}
        \begin{proof}
            From Proposition \ref{prop:wapg-intermediate-form}, set 
            \begin{align*}
                \tau_k &= \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}, 
                \\
                \xi_k &= \frac{\mu}{L \alpha_k - \mu},
                \\
                (1 + \xi_k)^{-1}\delta_k &= \frac{1}{L\alpha_k}
                \iff L \delta_k = \frac{1 + \xi_k}{\alpha_k}. 
            \end{align*}
            We claim that these parameters satisfy $L\delta_k = 1 + \tau_k + \xi_k$. 
            Hence $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}(x_{k + 1} - x_k)$. 
            To see, we have 
            \begin{align*}
                1 + \tau_k + \xi_k &= 
                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
                + \frac{\mu}{L \alpha_k - \mu}
                \\
                &= 
                1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
                \\
                &= 
                \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
                \\
                &= \frac{L}{L\alpha_k - \mu}. 
            \end{align*}
            Next
            \begin{align*}
                1 + \tau_k + \xi_k &= 
                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
                + \frac{\mu}{L \alpha_k - \mu}
                \\
                &= 
                1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
                \\
                &= 
                \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
                \\
                &= \frac{L}{L\alpha_k - \mu}. 
            \end{align*}
            Therefore, substituting it gives: 
            \begin{align*}
                v_{k + 1} &= 
                x_{k + 1} + \left(
                    1 + \frac{\mu}{L\alpha_k - \mu}
                \right)^{-1}\left(
                    \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= 
                x_{k + 1} + \left(
                    \frac{L\alpha_k}{L\alpha_k - \mu}
                \right)^{-1}\left(
                    \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= 
                x_{k + 1} + \left(
                    \frac{L\alpha_k - \mu}{L\alpha_k}
                \right)\left(
                    \frac{L - L\alpha_k}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
            \end{align*}
        \end{proof}

    \begin{proposition}[WAPG fits into Momentum Form]\label{prop:wapg-momentum-form}
        Suppose any sequence $(\alpha_k)_{k \ge 0}$ satisfies recursively the conditions
        $L\alpha_k^2 \le (1 - \alpha_k)L\alpha_{k - 1}^2 + \alpha_k \mu$. 
        If $\alpha_k$ is used in the Similtar triangle form to generate the iterates $(x_k, y_k v_k)$. 
        Then the iterates are algebraically equivalent to: 
        $$
        \begin{aligned}
            x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
            \\
            y_{k + 1} &= 
            x_{k + 1} + ???(x_{k + 1} - x_k). 
        \end{aligned}
        $$
    \end{proposition}
    \begin{remark}

    \end{remark}

\bibliographystyle{siam}
\bibliography{references/Spectral_Momentum.bib}

\end{document}

### 2024-12-09 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
     \begin{proposition}[Stepwise lyapunov]\label{prop:stepwise-lyapunov}
-        For all $k \ge 0$, given $v_k, x_k, \alpha_k, \gamma_k$, let $\mu \ge 0$ iterates: $y_k, v_{k + 1}, x_{k + 1}, \alpha_{k + 1},\gamma \ge 0$ be given by Definition \ref*{def:stepwise-wapg}. 
+        For all $k \ge 0$, given $v_k, x_k, \alpha_k, \gamma_k$, let $\mu \ge 0$ iterates: $y_k, v_{k + 1}, x_{k + 1}, \alpha_{k + 1},\gamma \ge 0$ be given by Definition \ref{def:stepwise-wapg}. 
         Let $F^* = F(x^*)$ where is an arbitrary $x^* \in \RR^n$. 
@@
     \begin{proof}  
-        Recall the 
-        \hyperref[prop:stepwise-lyapunov]{Proposition \ref*{prop:stepwise-lyapunov}}, 
+        Recall Proposition \ref{prop:stepwise-lyapunov},
         since the choice of $\gamma, \hat \gamma$ is arbitrary choices for the theorem, we choose $\gamma = \rho_{k - 1} L \alpha_{k - 1}^2, \hat \gamma = L \alpha_k^2$, giving us: 

### 2024-12-10 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
     \end{theorem}
-    The theorem looks exciting, but Lin 2015 \cite{lin_universal_2015} page 11 pointed out that $\mathcal G_k^*, \mathcal J_{\lambda_k} y_k$ are both intractable quantities. 
+    The theorem looks exciting, but Lin 2015 \cite{lin_universal_2015} page 11 pointed out that $\mathcal M_k^*, \mathcal J_{\lambda_k} y_k$ are both intractable quantities. 
     In Guler's work, these intractable quantities were built into the Nesterov's estimating sequence making it unclear how to control $\epsilon_k \rightarrow 0$. 
@@
         \end{align*}
-        Next, we show that if $L\delta_k = 1 + \xi_k + \tau_k$ then $v_{k + 1} - x_{k + 1} = (1 + \xi_t)^{-1}\tau_t(x_{k + 1} - x_k)$. 
+        Next, we show that if $L\delta_k = 1 + \xi_k + \tau_k$ then $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}\tau_t(x_{k + 1} - x_k)$. 
         \begin{align*}
@@
             &= 
-            L\alpha_{k + 1}\alpha_k^2 - \mu \alpha_k^2 + L \alpha_{k + 1}^2 + \mu\alpha_{k + 1}
+            L\alpha_{k + 1}\alpha_k^2 - \mu \alpha_k^2 + L \alpha_{k + 1}^2 - \mu\alpha_{k + 1}
             \\
@@
             L\alpha_{k + 1}\alpha_k^2 - \mu \alpha_k^2 + (
-                (1 - \alpha_{k + 1})L\alpha_k^2 - \mu\alpha_{k + 1}
+                (1 - \alpha_{k + 1})L\alpha_k^2 + \mu\alpha_{k + 1}
             ) - \mu\alpha_{k + 1}
@@
     \begin{proof}
-        Take it as a fact that the limiting subgradient of a weakly convex function is a closed set. 
+        Take it as a fact that the limiting subgradient of a weakly convex function is a closed bounded set. 
         Fix any $y$, there exists $w \in \partial \mathcal M(y^+; y)$ such that $\dist(\mathbf 0; \partial {\mathcal M}(y^+; y)) = \Vert w\Vert$ because $\partial M(\cdot;y)$ is a $\rho - \kappa$ weakly convex function.

### 2024-12-10 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
             \\
-            l_F(x; y_k) &= F(T_Ly_k) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
+            l_F(x; y_k) &\defeq F(T_Ly_k) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
             \label{eqn:lower-linearization}
@@
         \end{align*}
-
     \end{theorem}
     \begin{observation}\label{obs:stepwise-wapg}
-        Let's observe Definition \ref*{def:stepwise-wapg} closely. 
+        Let's observe Definition \ref{def:stepwise-wapg} closely. 
         We make two crucial observations here. 
@@
         }
+        But in general the choice of $\mu$ remains the strong convexity modulus or equivalently, any value that is smallar than the true strong convexity constant for claiming the convergence rate for all initial guesses.
     \end{remark}
 
-\section{Formulation of WAPG and its convergence rates}
-
-    \begin{definition}[Weak accelerated proximal gradient (WAPG)]\label{def:wapg}
+\section{Formulation of R-WAPG and its convergence rates}
+
+    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
         \;\\
-        Choose any $\gamma_0$, $(x_0, v_0)$ or equivalently $(x_0, y_0), (y_0, v_0)$. 
-        Given any sequence $(\rho_k)_{k\ge0}, (\alpha_k)_{k \ge0}$ such that for all integer $k\ge 0$, they have $\rho_k \in [0, 1], \alpha_k \in (0, 1)$. 
+        Initialize any $\gamma_0 >= 0$, $(x_0, v_0)$ or equivalently $(x_0, y_0), (y_0, v_0)$. 
+        Given any sequence $(\rho_k)_{k\ge0}, (\alpha_k)_{k \ge0}$ such that for all integer $k\ge 0$, $\textcolor{red}{\rho_k \ge 0}$, $\alpha_k \in (0, 1)$. 
         The algorithm generates a sequence of $(x_k, y_k, v_k)$ such that they satisfy for all $k\ge 0$ recursively: 
-        $$
-        \begin{aligned}
+        \begin{align*}
             \gamma_k &:= \left.\begin{cases}
-                \rho_{k - 1}L\alpha_{k - 1}^2 & k \ge 1,
+                \rho_{k -1}L\alpha_{k - 1}^2 & k \ge 1,
                 \\
@@
             x_{k + 1} &= T_L y_k. 
-        \end{aligned}
-        $$
+        \end{align*}
     \end{definition}
-
-    \begin{proposition}[WAPG convergence claim]\label{prop:wagp-convergence}
-        Let vectors $(x_k, y_k, v_k)_{k \ge0}$ and scalars $\alpha_k$ be generated by the weak accelerated proximal gradient algorithm. 
+    \begin{observation}
+        Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018}. 
+    \end{observation}
+
+    \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}
+        Let vectors $(x_k, y_k, v_k)_{k \ge0}$ and scalars $\alpha_k$ be generated by R-WAPG. 
         Define recursively for all $k\ge1$ by 
-        $$
-        \begin{aligned}
+        \begin{align*}
         R_{k + 1}
@@
         \right). 
-        \end{aligned}
-        $$
+        \end{align*}
         Choose $R_0= 0$ to be the base case. 
         Choose any $x^* \in \RR^n$ then
-        $$
-        \begin{aligned}
+        \begin{align*}
             F(x_{k + 1}) - F(x^*) + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
@@
             \right). 
-        \end{aligned}
-        $$
+        \end{align*}
     \end{proposition}
     \begin{proof}  
-        Recall Proposition \ref{prop:stepwise-lyapunov},
-        since the choice of $\gamma, \hat \gamma$ is arbitrary choices for the theorem, we choose $\gamma = \rho_{k - 1} L \alpha_{k - 1}^2, \hat \gamma = L \alpha_k^2$, giving us: 
-        {\footnotesize
-        \begin{align*}
-            F(x_{k + 1}) - F^* + R_{k + 1} + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
+        Recall the stepwise convergence theorem, since the choice of $\gamma, \hat \gamma$ is arbitrary choices for the theorem, we choose $\gamma = \rho_{k - 1} L \alpha_{k - 1}^2, \hat \gamma = L \alpha_k^2$, giving us:
+        {\small
+        \begin{align*}
+            &F(x_{k + 1}) - F^* + R_{k + 1} + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
+            \\
             &\le 
@@
             \left(
+                F(x_k) - F^* + R_k + \max(1, \rho_{k - 1})\frac{L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2
+            \right)
+            \\
+            &\le 
+            \max(1, \rho_{k - 1})(1 - \alpha_k)
+            \left(
                 F(x_k) - F^* + R_k + \frac{L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2
@@
             &\le 
+            \left(
+                \prod_{i = 0}^{k} \max(1, \rho_{k - 1})
+            \right)
             \left(
@@
         }
-        Going from the left to the right on the second inequality, we used the fact that $\rho_{k - 1} \in [0, 1]$. 
         Additionally, the algorithm converges by considering $R_k$: 
@@
         Therefore: 
-        \begin{align*}
-            F(x_{k + 1}) - F^* +
+        {\small
+        \begin{align*}
+            & F(x_{k + 1}) - F^* +
             \frac{L\alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
+            \\
             &\le 
             \left(
+                \prod_{i = 0}^{k} \max(1, \rho_{k - 1})
+            \right)
+            \left(
                 \prod_{i = 0}^{k} \left(1  - \alpha_i\right)
@@
             \left(
-                F(x_0) - F^* + \frac{\gamma_0}{2}\Vert v_k - x^*\Vert^2
+                F(x_0) - F^* + R_0 + \frac{\gamma_0}{2}\Vert v_k - x^*\Vert^2
             \right). 
         \end{align*}
+        }
     \end{proof}
@@
         {
-            The choice of $\rho_k \in (0, 1]$ is just a convenience for convergence analysis. 
-            It's a belief that there exists sequence $\rho_k$ where $\rho_k \ge 1$ where the algorithm would have a chance at converging still. 
+            The choice of $\rho_k$ allows for divergence to traditional choices of step sizes in the literatures. 
+            As we can see from the above convergence claim, there exists choices of $\rho_k\ge 1$ where convergence remains possible. 
         }
@@
 
-\section{WAPG covers variants of APG in the literatures}
+\section{R-WAPG covers variants of APG in the literatures}
     Many variants of the accelerated proximal gradient algorithm fits into the following form which we called ``abstract similar triangle". 
@@
         \end{align*}
-
     \end{proof}
@@
     \subsection{Narrowing it down}
-        \begin{proposition}[WAPG intermediate Form I]\label{prop:wapg-intermediate-form}
-            Suppose that $(y_i, x_i, v_i)$ are generated by 
-            \hyperref[def:wapg]{Definition \ref*{def:wapg}}
-            for all $0 \le i \le k$. 
+        \begin{proposition}[R-WAPG intermediate Form I]\label{prop:wapg-intermediate-form}
+            Assume $\mu < L$. 
+            Suppose that $(y_i, x_i, v_i)$ are generated by the WAPG algorithm for all $0 \le i \le k$ using sequence $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge0}$ such that for any integer $k\ge 0$, $\alpha_k \in (0, 1)$ and $\rho_k \ge 0$.
             Then the iterates can be expressed without the sequence $(\gamma_k)_{k \ge0}, (\rho_k)_{k\ge0}$, and they satisfy: 
-            $$
-            \begin{aligned}
+            \begin{align*}
                 y_k &= 
@@
                 \\
-                L &\alpha_k^2 \le (1 - \alpha_k)L \alpha_{k - 1} + \mu \alpha_k. 
-            \end{aligned}
-            $$
+                L &\alpha_k^2 = (1 - \alpha_k)L \rho_{k - 1}\alpha_{k - 1}^2 + \mu \alpha_k. 
+            \end{align*}
         \end{proposition}
@@
             \end{align*}
+            On the third $\iff$, we can assume $\alpha_k \neq \mu/L$ because $\alpha_k = \mu/L$ is impossible. 
+            For contradiction, assume $a_k = \mu/L$. 
+            Then
+            \begin{align*}
+                L \alpha_k^2 - \alpha_k\mu &= 
+                (1 - \alpha_k)L \rho_{k - 1}\alpha_{k - 1}^2 = 0 \implies \alpha_{k - 1} = 0. 
+            \end{align*}
+            Which contradict $\alpha_{k - 1} \in (0, 1)$. 
             For $v_{k + 1}$ considers 
@@
         \begin{proposition}[WAPG fits similar triangle form]\label{prop:wagp-st-form}
-            Given any sequence $(\alpha_i)_{i \ge k}$ such that $\alpha_i \in (0, 1)$ for all $0\le i \le k$ and $L\alpha_k^2\le (1 - \alpha_k)L\alpha_{k - 1}^2 + \alpha_k \mu$. 
-            Let $(x_k, y_k, v_k)$ to be generated as specified by Definition \ref{def:wapg} by the $(\alpha_k)_{k \ge0}$.
-            Then the iterate $(v_k)$ can be expressed without $y_k, v_k$: 
-            $$
-            \begin{aligned}
+            Given any sequence $(\alpha_i)_{i \ge k}$ such that $\alpha_i \in (0, 1)$, $\rho_k \ge 0$ for all $0 \le i \le k$ and $0 < L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu$.
+            Let $(x_k, y_k, v_k)$ to be generated as specified by Algorithm 2.2 by such $(\alpha_k)_{k \ge0}$. Then iterate $(v_k)$ can be expressed without $y_k, v_k$ by: 
+            \begin{align*}
                 y_k &= 
@@
                 v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
-            \end{aligned}
-            $$
+            \end{align*}
         \end{proposition}
@@
 
-    \begin{proposition}[WAPG fits into Momentum Form]\label{prop:wapg-momentum-form}
-        Suppose any sequence $(\alpha_k)_{k \ge 0}$ satisfies recursively the conditions
-        $L\alpha_k^2 \le (1 - \alpha_k)L\alpha_{k - 1}^2 + \alpha_k \mu$. 
-        If $\alpha_k$ is used in the Similtar triangle form to generate the iterates $(x_k, y_k v_k)$. 
+    \begin{proposition}[R-WAPG fits into Momentum Form]\label{prop:wapg-momentum-form}
+        \;\\
+        Suppose any sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ satisfies recursively the conditions
+        $L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu$ where $\rho_{k} \in \ge 0\; \forall k \ge0$. 
+        Assume that $0 \le \mu < L$. 
+        If $\alpha_k$ is used in the similar triangle form to generate the iterates $(x_k, y_k, v_k)$. 
         Then the iterates are algebraically equivalent to: 
-        $$
-        \begin{aligned}
+        \begin{align*}
             x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
@@
             y_{k + 1} &= 
-            x_{k + 1} + ???(x_{k + 1} - x_k). 
-        \end{aligned}
-        $$
+            x_{k + 1} + 
+            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
+        \end{align*}
+        In the special case when $\mu = 0$, the momentum term admits simpler representation 
+        \begin{align*}
+        \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
+        & = \alpha_{k + 1}(\alpha_k^{-1} - 1). 
+        \end{align*}
     \end{proposition}
+    \begin{proof}
+
+        Start by considering the update rule for $v_k$ from the similar triangle form of WAPG which is: 
+        \begin{align*}
+            v_{k + 1} &= 
+            x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
+            \\
+            \iff 
+            (L \alpha_{k + 1} - \mu)v_{k + 1} 
+            &= 
+            (L \alpha_{k + 1} - \mu)x_{k + 1} + (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
+        \end{align*}
+        Next, we simplify the update for the iterates $y_{k}$ by the similar triangle form of R-WAPG. 
+        \begin{align*}
+            y_k &= 
+            \left(
+                1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
+            \right)^{-1}
+            \left(
+                v_k + 
+                \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
+            \right)
+            \\
+            &= 
+            \left(
+            \frac{L - \mu}{L\alpha_k - \mu} 
+            \right)^{-1}
+            \left(
+                v_k + 
+                \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
+            \right)
+            \\
+            &= 
+            \frac{L\alpha_k - \mu}{L - \mu} v_k
+            + 
+            \frac{L - L \alpha_k}{L - \mu} x_k
+            \\
+            &= (L - \mu)^{-1}((L \alpha_k - \mu)v_k + (L - L \alpha_k)x_k). 
+        \end{align*}
+        Now considering substituting $v_{k + 1}$ into $y_{k + 1}$ so it has: 
+        {\small
+        \begin{align*}
+            y_{k + 1} &= 
+            (L - \mu)^{-1}((L\alpha_{k + 1} - \mu)v_{k + 1} + (L - L \alpha_{k + 1})x_{k + 1})
+            \\
+            &= (L - \mu)^{-1}
+            \left(
+                (L\alpha_{k + 1} - \mu)x_{k + 1} + 
+                (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
+                + (L - L \alpha_{k + 1})x_{k + 1}
+            \right)
+            \\
+            &= 
+            (L - \mu)^{-1}
+            \left(
+                (L - \mu)x_{k + 1} + (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
+            \right)
+            \\
+            &= x_{k + 1} + \frac{(L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)}{L - \mu}(x_{k + 1} - x_k). 
+        \end{align*}
+        }
+        The coefficient for $(x_{k + 1} - x_k)$ needs some works to formulate it without the parameter $\mu, L$. 
+        To do that we have: 
+        \begin{align*}
+            \frac{(L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)}{L - \mu}
+            &= \frac{(L\alpha_{k + 1} - \mu)\alpha_k(1 - \alpha_k)}{\alpha_k^2(L - \mu)}
+            \\
+            &= 
+            \alpha_k(1 - \alpha_k)
+            \left(
+                \frac{\alpha_k^2(L - \mu)}{L\alpha_{k + 1} - \mu}
+            \right)^{-1}
+            \\
+            &= \alpha_k(1 - \alpha_k)
+            \left(
+                \frac{L\alpha_k^2 - \mu\alpha_k^2}{L\alpha_{k + 1} - \mu}
+            \right)^{-1}
+            \\
+            &= 
+            \alpha_k(1 - \alpha_k)
+            \rho_k\left(
+                \frac{L\rho_k\alpha_k^2 - \mu\rho_k\alpha_k^2}{L\alpha_{k + 1} - \mu}
+            \right)^{-1}
+            \\
+            &= 
+            \rho_k\alpha_k(1 - \alpha_k)
+            \left(
+                \frac{(L\alpha_{k + 1} - \mu)(\rho_k\alpha_k^2 + \alpha_{k + 1})}
+                {L\alpha_{k + 1} - \mu}
+            \right)^{-1}
+            \\
+            &= \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}.
+        \end{align*}
+        Going from the left to right on the fourth equality, we used $L\alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_kL\alpha_k^2 + \mu \alpha_{k + 1}$ with 
+        \begin{align*}
+            L \rho_k \alpha_k^2 - \mu \rho_k \alpha_k^2 
+            &= 
+            (1 - \alpha_{k + 1})L \rho_k \alpha_k^2 + \alpha_{k + 1} L \rho_k \alpha_k^2 - \mu \rho_k \alpha_k^2
+            \\
+            &= 
+            ((1 - \alpha_{k + 1})L \rho_k \alpha_k^2 + \mu \alpha_{k + 1}) - \mu\alpha_{k + 1} + \alpha_{k + 1} L \rho_k \alpha_k^2 - \mu \rho_k \alpha_k^2
+            \\
+            &= L \alpha_{k + 1}^2 - \mu\alpha_{k + 1} + \alpha_{k + 1}L\rho_k\alpha_k^2 - \mu \rho_k \alpha_k^2
+            \\
+            &= 
+            L\alpha_{k + 1}(\alpha_{k + 1} + \rho_k \alpha_k^2) - \alpha_{k + 1}\mu - \mu \rho_k \alpha_k^2
+            \\
+            &= (L \alpha_{k + 1} - \mu)(\alpha_{k + 1} + \rho_k \alpha_k^2). 
+        \end{align*}
+        When $\mu = 0$, things simplify. 
+        Consider that $\alpha_{k +1}^2 = (1 - \alpha_{k + 1})\alpha_k^2$. 
+        \begin{align*}
+            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
+            &= 
+            \frac{\rho_k\alpha_{k + 1}\alpha_k(1 - \alpha_k)}
+            {\rho_k\alpha_{k + 1}\alpha_k^2 + \alpha_{k + 1}^2}
+            \\
+            &= 
+            \frac{\rho_k\alpha_{k + 1}\alpha_k(1 - \alpha_k)}
+            {\rho_k\alpha_{k + 1}\alpha_k^2 + \rho_k(1 - \alpha_{k + 1})\alpha_k^2}
+            \\
+            &= \frac{\rho_k\alpha_{k + 1}\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2}
+            \\
+            &= \alpha_{k + 1}(\alpha_k^{-1} - 1). 
+        \end{align*}
+    \end{proof}
     \begin{remark}
-
+        \textcolor{red}
+        {
+        There exists a choice of $\rho_k \in [0, 1), \mu = 0$ such that the above algorithm is equivalent to Chambolle Dossal 2015 \cite{chambolle_convergence_2015}. 
+        When $\rho_k = 1$, this becomes just FISTA \cite{beck_fast_2009}. 
+        When $L > \mu > 0$, then choosing $\rho_k = 1$ yields equation 
+        \begin{align*}
+            L \alpha_{k + 1}^2 = (1- \alpha_{k + 1})L \alpha_k^2 + \alpha_k \mu. 
+        \end{align*}
+        Here, if we assume sequence $\alpha_k$ is constant, then $\alpha_k = \sqrt{\mu/L}$ is a solution to the above iterative equation. 
+        Substituting it back to the momentum form of R-WAPG, we recovers the V-FISTA algorithm, which appears as (10.7.7) in Beck's Book \cite{beck_first-order_2017}. 
+        }
     \end{remark}

### 2024-12-10 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
         \;\\
-        Initialize any $\gamma_0 >= 0$, $(x_0, v_0)$ or equivalently $(x_0, y_0), (y_0, v_0)$. 
+        Initialize any $\gamma_0 \ge 0$, $(x_0, v_0)$ or equivalently $(x_0, y_0), (y_0, v_0)$. 
         Given any sequence $(\rho_k)_{k\ge0}, (\alpha_k)_{k \ge0}$ such that for all integer $k\ge 0$, $\textcolor{red}{\rho_k \ge 0}$, $\alpha_k \in (0, 1)$. 
@@
         \begin{align*}
-            F(x_{k + 1}) - F(x^*) + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
+            & F(x_{k + 1}) - F(x^*) + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
+            \\
             &\le 
+            \left(
+                \prod_{i = 0}^{k} \max(1, \rho_{k - 1})
+            \right)
             \left(
@@
         Suppose any sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ satisfies recursively the conditions
-        $L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu$ where $\rho_{k} \in \ge 0\; \forall k \ge0$. 
+        $L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu$ where $\rho_{k} \ge 0\; \forall k \ge0$. 
         Assume that $0 \le \mu < L$. 
@@
         \begin{align*}
-            L \alpha_{k + 1}^2 = (1- \alpha_{k + 1})L \alpha_k^2 + \alpha_k \mu. 
+            L \alpha_{k + 1}^2 = (1- \alpha_{k + 1})L \alpha_k^2 + \alpha_{k + 1} \mu. 
         \end{align*}

### 2024-12-11 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, work home sync

@@
 \section{Preliminaries}
-    Throughout, assume problem of types $F = f + g$ where $f: \RR \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: Q \rightarrow \overline \RR$ is convex. 
+    Throughout Section 1, 2, 3, we assume the problem of types $F = f + g$ where $f: \RR \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: Q \rightarrow \overline \RR$ is convex.
     We consider optimization problem of the form
@@
 
-    \begin{theorem}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
+    \begin{definition}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
         Let $0 \le \mu \le L$ be the strong convexity and Lipschitz smoothness parameter of $f$. 
-        Given iterates $(v_k, x_k)$, or equivalently $(y_k, x_k)$, $(x_k, y_k)$, any $\alpha_k \in (0, 1), \gamma > 0$. 
-        Define scalar $\hat \gamma$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ by: 
+        Given iterates $(v_k, x_k)$, or equivalently $(y_k, x_k)$, $(x_k, y_k)$, any $\alpha_k \ge 0, \gamma \ge 0$, the algorithm generates scalar $\hat \gamma$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ by equalities:
         \begin{align*}
@@
         \end{align*}
-    \end{theorem}
+    \end{definition}
     \begin{observation}\label{obs:stepwise-wapg}
@@
 
-    \begin{proposition}[Stepwise lyapunov]\label{prop:stepwise-lyapunov}
-        For all $k \ge 0$, given $v_k, x_k, \alpha_k, \gamma_k$, let $\mu \ge 0$ iterates: $y_k, v_{k + 1}, x_{k + 1}, \alpha_{k + 1},\gamma \ge 0$ be given by Definition \ref{def:stepwise-wapg}. 
-        Let $F^* = F(x^*)$ where is an arbitrary $x^* \in \RR^n$. 
-        If we define $R_{k + 1}$ by some arbitrary $R_k \in \RR^n$: 
+    \begin{proposition}[Stepwise lyapunov]\label{prop:stepwise-lyapunov}\;\\
+        Fix any integer $k \ge0$, suppose that $v_{k + 1}, x_{k + 1}, y_k, g_k, \gamma, \hat \gamma$ satisfies Definition \ref{def:stepwise-wapg}. 
+        Given any $R_k$.
+        Define: 
         \begin{align*}
             R_{k + 1}
-            &\defeq 
+            \defeq
             \frac{1}{2}\left(
-                L^{-1} - \frac{\alpha_k^2}{\hat\gamma}
+                L^{-1} - \frac{\alpha_k^2}{\hat \gamma}
             \right)\Vert g_k\Vert^2
@@
                 \epsilon_k + R_k + 
-                \frac{\mu\alpha_k\gamma}{2\hat\gamma}
+                \frac{\mu\alpha_k\gamma}{2\hat \gamma}
                 \Vert v_k - y_k\Vert^2
@@
         \end{align*}
-        Then we have the inequality: 
+        Then it has for all $x^* \in \RR^n$ where $F^* = F(x^*)$, the inequality: 
         \begin{align*}
@@
         \;\\
-        Initialize any $\gamma_0 \ge 0$, $(x_0, v_0)$ or equivalently $(x_0, y_0), (y_0, v_0)$. 
-        Given any sequence $(\rho_k)_{k\ge0}, (\alpha_k)_{k \ge0}$ such that for all integer $k\ge 0$, $\textcolor{red}{\rho_k \ge 0}$, $\alpha_k \in (0, 1)$. 
-        The algorithm generates a sequence of $(x_k, y_k, v_k)$ such that they satisfy for all $k\ge 0$ recursively: 
-        \begin{align*}
+        Initialize any $\gamma_0 \in [0, 1]$, $(x_0, v_0)$ or equivalently: $(x_0, y_0), (y_0, v_0)$. 
+        The algorithm generates a sequence of vector $(x_k, y_k, v_k)$ and auxiliary sequence $\alpha_k, \rho_k$ such that they satisfy for all $k\ge 0$: 
+        $$
+        \begin{aligned}
             \gamma_k &:= \left.\begin{cases}
@@
             \\
-            \hat \gamma_{k + 1} &:= L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \mu \alpha_k, 
+            \text{find }&\alpha_k \in [0, 1], \rho_k \ge 0: L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \mu \alpha_k  \;\wedge \; 0 \le \rho_k \alpha_k^2 \le 1, 
+            \\
+            \hat \gamma_{k + 1} &:= L\alpha_k^2, 
             \\
@@
             x_{k + 1} &= T_L y_k. 
-        \end{align*}
+        \end{aligned}
+        $$
     \end{definition}
@@
     \end{observation}
+    \begin{observation}\label{obs:r-wapg-observation-1}
+        The sequence $\alpha_k$ satisfies the condition that $\alpha_k \in [0, 1]$.
+        In addition, if $\alpha_0 \in (0, 1)$, then the entire sequence $\alpha_k \in (0, 1)$. 
+        Suppose inductively that $\alpha_{k - 1}, \rho_{k - 1}$ are given such that they satisfy $\alpha_{k -1} \in [0, 1]$ and $\rho_{k - 1} \alpha_{k - 1}^2 < 1$. 
+        Solving the quadratic $L\alpha_k^2=(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2 + \mu \alpha_k$ for $\alpha_k$ yields candidates 
+        $$
+        \begin{aligned}
+            \alpha_k &= 
+            \frac{1}{2}\left(
+                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
+                \pm
+                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
+            \right). 
+        \end{aligned}
+        $$
+        Choosing the positive sign which is the larger one of the roots of the quadratic. 
+        We have $\alpha_k \ge 0$ because: 
+        $$
+        \begin{aligned}
+            \alpha_k &=
+            \frac{1}{2}\left(
+                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
+                +
+                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
+            \right)
+            \\
+            &\ge 
+            \frac{1}{2}\left(
+                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
+                +
+                \left|\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L\right|
+            \right)
+            \\
+            & \ge 0. 
+        \end{aligned}
+        $$
+        If $\alpha> 0$, we would have $4\rho_{k - 1} \alpha_{k - 1}^2 > 0$ , which allows for $> 0$ instead. 
+        An upper bound can be identified by using inductive hypothesis and consdering: 
+        $$
+        \begin{aligned}
+            \alpha_k &= 
+            \frac{1}{2}\left(
+                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
+                +
+                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
+            \right)
+            \\
+            &\le 
+            \frac{1}{2}\left(
+                \frac{\mu}{L} - 1
+                +
+                \sqrt{(1 - \mu/L)^2 + 4}
+            \right)
+            \\
+            &\le \frac{1}{2}\left(
+                0 + \sqrt{0 + 4}
+            \right) = 1. 
+        \end{aligned}
+        $$
+        Going from the second to the third inequality, we maximized $\mu/L$ by monotonicity of the linear function and the square root function. 
+        Therefore, inductively, $\alpha_k \in [0, 1]$ holds. 
+        Additionally, if $\alpha_{k - 1} \in (0, 1)$, then the results can be strengthened and $\alpha_k \in (0, 1)$ as well.
+
+    \end{observation}
 
     \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}
-        Let vectors $(x_k, y_k, v_k)_{k \ge0}$ and scalars $\alpha_k$ be generated by R-WAPG. 
+        Let vectors $(x_k, y_k, v_k)_{k \ge0}$ and scalars $\alpha_k$ be generated by R-WAPG (Definition \ref{def:wapg}). 
         Define recursively for all $k\ge1$ by 
@@
     \subsection{Narrowing it down}
-        \begin{proposition}[R-WAPG intermediate Form I]\label{prop:wapg-intermediate-form}
+        \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\
             Assume $\mu < L$. 
-            Suppose that $(y_i, x_i, v_i)$ are generated by the WAPG algorithm for all $0 \le i \le k$ using sequence $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge0}$ such that for any integer $k\ge 0$, $\alpha_k \in (0, 1)$ and $\rho_k \ge 0$.
-            Then the iterates can be expressed without the sequence $(\gamma_k)_{k \ge0}, (\rho_k)_{k\ge0}$, and they satisfy: 
+            Choose any $\gamma_0 \in (0, 1)$ as the initial condition for R-WAPG to produce vectors sequence $(y_i)_{i \in \N}, (x_i)_{i \in \N}, (v_i)_{i \in \N}$ and $(\rho_k)_{i \in \N}, (\alpha_k)_{i \in \N}$.
+            Then the iterates can be expressed without $(\gamma_k)_{k \ge0}, (\rho_k)_{k\ge0}$, and for all $k\ge 0$ they are algebraically equivalent to
             \begin{align*}
@@
             \end{align*}
-            The proof of the intermediate form is no complete. 
+            The is now complete. 
             This form doesn't have $\rho_k, \gamma_k, \hat \gamma_k$ in it. 
@@
         \end{remark}
-
-        \begin{proposition}[WAPG fits similar triangle form]\label{prop:wagp-st-form}
-            Given any sequence $(\alpha_i)_{i \ge k}$ such that $\alpha_i \in (0, 1)$, $\rho_k \ge 0$ for all $0 \le i \le k$ and $0 < L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu$.
-            Let $(x_k, y_k, v_k)$ to be generated as specified by Algorithm 2.2 by such $(\alpha_k)_{k \ge0}$. Then iterate $(v_k)$ can be expressed without $y_k, v_k$ by: 
-            \begin{align*}
+        \begin{definition}[R-WAPG intermediate representation]\label{def:r-wapg-intermediate}\;\\
+            Given any initial $\alpha_0 \in (0, 1)$, $(x_0, y_0)$ or equivalently $(x_0, v_0), (y_0, v_0)$. 
+            Assume $\mu < L$. 
+            Assume that the auxiliary sequence $\rho_k$ has $\rho_k \alpha_k^2 < 1$ for all $k \ge 0$. 
+            The algorithm generate sequence of vector iterates $(x_k, v_k, y_k)_{k \ge0}$ by 
+            $$
+            \begin{aligned}
                 y_k &= 
@@
                 \\
+                v_{k + 1} &= 
+                \left(
+                    1 + \frac{\mu}{L \alpha_k - \mu}
+                \right)^{-1}
+                \left(
+                    v_k + 
+                    \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
+                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k, 
+                \\
+                \alpha_k &= 
+                \frac{1}{2}\left(
+                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
+                +
+                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
+                \right). 
+            \end{aligned}
+            $$
+        \end{definition}
+        \begin{proposition}[Second equivalent representation of R-WAPG]\label{prop:wagp-st-form}\;\\
+            Given any sequence $(\alpha_i)_{i \ge k}$ such that $\alpha_i \in (0, 1)$, $\rho_k \ge 0$ for all $0 \le i \le k$ and $0 < L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu$.
+            Let $(x_k, y_k, v_k)$ to be generated as specified by Algorithm 2.2 by such $(\alpha_k)_{k \ge0}$. Then iterate $(v_k)$ can be expressed without $y_k, v_k$ by: 
+            \begin{align*}
+                y_k &= 
+                \left(
+                    1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
+                \right)^{-1}
+                \left(
+                    v_k + 
+                    \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
+                \right), 
+                \\
+                x_{k + 1} &= 
+                y_k - L^{-1} \mathcal G_L y_k, 
+                \\
                 v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
@@
         \begin{proof}
-            From Proposition \ref{prop:wapg-intermediate-form}, set 
+            From Definition \ref{def:r-wapg-intermediate}, set 
             \begin{align*}

### 2024-12-12 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
 \noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method. 
+\section{Introduction}
+    \subsection{Literature reviews}
+    \subsection{Contributions}
+        Our contributions are two folds.
+
+        We present a theoretical unification through the formulation of ``Relaxed weak accelerated proximal gradient algorithm (R-WAPG)'' which we invented. 
+        It unifies convergence claim for accelerated method for the strongly convex objective and Lipschitz smooth but non-strongly convex case and it relaxes the conditions on the momentum sequence.
+
+        We connect the theories and practice by pointing out one practical exploits inspired the convergence proof of the algorithm which we called ``Spectral Momentum''. 
+        Numerical experiments are conducted to illustrate the theoretical convergence of R-WAPG and the performance of Spectral Momentum in with applications.
 
@@
 \section{Formulation of R-WAPG and its convergence rates}
+    Definition \ref{def:wapg} is an algorithm which generates iterates $(x_k, y_k, v_k)$ and admits potential convergence claim using Proposition \ref{prop:stepwise-lyapunov}. 
+    It is the backbone of multiple accelerated first order method in the literatures which fits all variants under the same convergence claim.
 
@@
 
-\section{R-WAPG covers variants of APG in the literatures}
-    Many variants of the accelerated proximal gradient algorithm fits into the following form which we called ``abstract similar triangle". 
+\section{Equivalent representations of R-WAPG}
+    This section reduces Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 
+    Proposition \ref{prop:wapg-first-equivalent-repr} simplifies Definition \ref{def:wapg} for the specific initial conditions $\gamma_0 \in(0, 1)$ and finds a representation without auxiliary sequence $\gamma_k, \hat \gamma_k$.
+    Definition \ref{def:r-wapg-intermediate} states the first simplified form of the R-WAPG algorithm which we call: ``R-WAPG intermediate form''. 
+    Following a similar pattern, Proposition \ref{prop:wagp-st-form}, \ref{prop:wagp-st-form} states two more equivalent representations under R-WAPG intermediate form which are formulated as Definition \ref{def:r-wapg-st-form}, \ref{def:r-wapg-momentum-form}.
+
+    To start, the following proposition on ``abstract similar triangle form'' were made to simplify arguments and notations to make nicer proofs.
+
     \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
@@
             Assume $\mu < L$. 
-            Choose any $\gamma_0 \in (0, 1)$ as the initial condition for R-WAPG to produce vectors sequence $(y_i)_{i \in \N}, (x_i)_{i \in \N}, (v_i)_{i \in \N}$ and $(\rho_k)_{i \in \N}, (\alpha_k)_{i \in \N}$.
+            Choose any $\gamma_0 \in (0, 1)$ as the initial condition for R-WAPG (Definition \ref{def:wapg}) to produce vectors sequence $(y_i)_{i \in \N}, (x_i)_{i \in \N}, (v_i)_{i \in \N}$ and $(\rho_k)_{i \in \N}, (\alpha_k)_{i \in \N}$.
             Then the iterates can be expressed without $(\gamma_k)_{k \ge0}, (\rho_k)_{k\ge0}$, and for all $k\ge 0$ they are algebraically equivalent to
@@
                     \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
-                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k, 
-                \\
-                L &\alpha_k^2 = (1 - \alpha_k)L \rho_{k - 1}\alpha_{k - 1}^2 + \mu \alpha_k. 
+                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
             \end{align*}
@@
         \end{proof}
-        \begin{remark}
-            Observe that this is fits the abstract similar triangle form described in Proposition \ref{prop:abs-st-form} perfectly by exchanging $x_k$ with $z_k$, $v_k$ with $x_k$. 
-        \end{remark}
-        \begin{definition}[R-WAPG intermediate representation]\label{def:r-wapg-intermediate}\;\\
+
+        \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
             Given any initial $\alpha_0 \in (0, 1)$, $(x_0, y_0)$ or equivalently $(x_0, v_0), (y_0, v_0)$. 
             Assume $\mu < L$. 
-            Assume that the auxiliary sequence $\rho_k$ has $\rho_k \alpha_k^2 < 1$ for all $k \ge 0$. 
-            The algorithm generate sequence of vector iterates $(x_k, v_k, y_k)_{k \ge0}$ by 
-            $$
-            \begin{aligned}
+            The algorithm generate sequence of vector iterates $(x_k, v_k, y_k)_{k \ge0}$ by the procedures: 
+            \begin{align*}
+                \text{find }& \rho_{k - 1}: 0 < \rho_{k - 1} < \alpha_{k - 1}^{-2},
+                \\
+                \alpha_k &= 
+                \frac{1}{2}\left(
+                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
+                +
+                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
+                \right), 
+                \\
                 y_k &= 
@@
                     \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
-                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k, 
-                \\
-                \alpha_k &= 
-                \frac{1}{2}\left(
-                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
-                +
-                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
-                \right). 
-            \end{aligned}
-            $$
+                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
+            \end{align*}
         \end{definition}
         \begin{proposition}[Second equivalent representation of R-WAPG]\label{prop:wagp-st-form}\;\\
-            Given any sequence $(\alpha_i)_{i \ge k}$ such that $\alpha_i \in (0, 1)$, $\rho_k \ge 0$ for all $0 \le i \le k$ and $0 < L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu$.
-            Let $(x_k, y_k, v_k)$ to be generated as specified by Algorithm 2.2 by such $(\alpha_k)_{k \ge0}$. Then iterate $(v_k)$ can be expressed without $y_k, v_k$ by: 
+            Let iterates $(x_k, v_k, y_k)_{k \ge 0}$ and sequence $(\alpha_k, \rho_k)_{k \ge0}$ be given by Definition \ref{def:r-wapg-intermediate}. 
+            Then for all $k \ge0$, iterate $(v_k)_{k \ge 0}, (x_k)_{k \ge 0}, (y_k)_{k \ge0}$ are algebraically equivalent to: 
             \begin{align*}
@@
         \end{proof}
-
-    \begin{proposition}[R-WAPG fits into Momentum Form]\label{prop:wapg-momentum-form}
+    \begin{definition}[R-WAPG similar triangle form]\label{def:r-wapg-st-form}
+        Given any initial $\alpha_0 \in (0, 1)$, $(x_0, y_0)$ or equivalently $(x_0, v_0), (y_0, v_0)$. 
+        Assume $\mu < L$. 
+        The algorithm generate sequence of vector iterates $(x_k, v_k, y_k)_{k \ge0}$ by the procedures: 
+        \begin{align*}
+            \text{find }& \rho_{k - 1}: 0 < \rho_{k - 1} < \alpha_{k - 1}^{-2},
+            \\
+            \alpha_k &= 
+            \frac{1}{2}\left(
+            \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
+            +
+            \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
+            \right), 
+            \\
+            y_k &= 
+            \left(
+                1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
+            \right)^{-1}
+            \left(
+                v_k + 
+                \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
+            \right), 
+            \\
+            x_{k + 1} &= 
+            y_k - L^{-1} \mathcal G_L y_k, 
+            \\
+            v_{k + 1} &= 
+            x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k). 
+        \end{align*}
+    \end{definition}
+
+    \begin{proposition}[Third equivalent representation of R-WAPG]\label{prop:r-wapg-momentum-repr}
         \;\\
-        Suppose any sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ satisfies recursively the conditions
-        $L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu$ where $\rho_{k} \ge 0\; \forall k \ge0$. 
-        Assume that $0 \le \mu < L$. 
-        If $\alpha_k$ is used in the similar triangle form to generate the iterates $(x_k, y_k, v_k)$. 
+        Let sequence $(\alpha_k, \rho_k)_{k \ge0}$ and iterates $(x_k, v_k, y_k)_{k\ge 0}$ given by R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}). 
         Then the iterates are algebraically equivalent to: 
@@
     \end{proposition}
+
     \begin{proof}
-
         Start by considering the update rule for $v_k$ from the similar triangle form of WAPG which is: 
@@
         }
+
         The coefficient for $(x_{k + 1} - x_k)$ needs some works to formulate it without the parameter $\mu, L$. 
@@
     \end{proof}
+
+    \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
+        Initialize any $\alpha_0 \in (0, 1)$. 
+        The algorithm generates iterates $(v_k, x_k, y_k)$ and auxiliary sequence $(\rho_k)_{k \ge0}$ by the following procedures: 
+        \begin{align*}
+            \text{find }& \rho_{k - 1}: 0 < \rho_{k - 1} < \alpha_{k - 1}^{-2},
+            \\
+            \alpha_k &= 
+            \frac{1}{2}\left(
+            \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
+            +
+            \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
+            \right), 
+            \\
+            x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
+            \\
+            y_{k + 1} &= 
+            x_{k + 1} + 
+            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
+        \end{align*}
+        In the special case $\mu = 0$, the momentum term can be represented without relaxation parameter $\rho_k$: 
+        $$
+        \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}} 
+        = \alpha_{k + 1}(\alpha_k^{-1} - 1).  
+        $$
+
+    \end{definition}
     \begin{remark}
@@
 
+\subsection{Representing algorithms in the literatures via R-WAPG}
+\subsection{The method of Spectral Momentum}
+\subsection{Numerical experiments and applications}
+
 \bibliographystyle{siam}

### 2024-12-12 Notebook LaTEX/Proposal/main.tex
>w<, changes

\documentclass[12pt]{article}
\input{presets/wang/input.tex}
\input{presets/misc.tex}
\input{presets/julia_lstlisting.tex}

% === TEMPLATE HOW TO USE ======
% To begine here is a list of things: 
% [ ]: Change title. 
% [ ]: Fill into the author names, affiliation and contact info. 
% [ ]: Fill in the abstract. 
% [ ]: Fill/change in AMS mathematics subject classification code, and the keywords.

\begin{document}

\title{
    {
        \fontfamily{ptm}\selectfont 
        First Order Nonsmooth Optimization: 
        Algorithm Design, Analysis, Convergence, and Applications
    }
    }

\author{
    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
    The University of British Columbia, Kelowna, BC Canada V1V 1V7. 
    E-mail:  \texttt{alto@mail.ubc.ca}.}~Author Name 1
    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
    The University of British Columbia, Kelowna, BC Canada V1V 1V7. 
    E-mail:  \texttt{shawn.wang@ubc.ca}.}~ and~Author Name 2
}

\date{\today}

\maketitle

% \vskip 8mm

\begin{abstract} 
    \noindent
    Abstract abstract abstract. 
\end{abstract}
% \noindent{\bfseries 2010 Mathematics Subject Classification:}
% Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
% \noindent{\bfseries Keywords: } Non-convex Optimizations, Proximal Point.

\tableofcontents

\section{Introduction}
    Let $\RR^n$ be the ambient space. We consider 
    \begin{align}
        \min_{x \in \RR^n} \left\lbrace
            F(x): f(x) + g(x)
        \right\rbrace.
    \end{align}\label{eqn:additive-comp-obj}
    Unless specified, assume $f$ is a smooth function with $L$-Lipschitz gradient operator. 
    Unless specified, assume $g$ is a convex function. 
    In the literatures this type of problems are referred to as additive composite problems.

    \par
    Our ongoing research concerns accelerated proximal gradient type method for solving (\ref{eqn:additive-comp-obj}). 
    In the expository writing by Walkington \cite{noel_nesterovs_nodate}, a variant for of accelerated gradient method for strongly convex function $f$ is discussed. 
    We had two lingering questions after reading it. 
    \begin{enumerate}
        \item Do there exist a unified description for the convergence for both variants of the algorithm. 
        \item Is it possible to attain faster convergence rate without knowledge about the strong convexity of function $f$. 
    \end{enumerate}
    The good news is we have definitive answers for both questions through our own efforts of research. 
    Section \ref{sec:unify-nes-acceleration}, \ref{sec:spectral-momentum} are our ongoing research which present the answers to the questions. 
    \par
    In Section \ref{sec:unify-nes-acceleration}, we proposed the method of ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)'' as the foundation to describe several variants of Accelerated proximal gradient method in the literatures. 
    The convergence theories of R-WAPG allows us to model convergence of accelerated proximal gradient method where the momentum sequence doesn't strictly follow the conditions presented in the literatures. 
    The descriptive power of R-WAPG allows convergence analysis for all the variants using one single theorem. 
    \par
    In Section \ref{sec:spectral-momentum} we propose a practical algorithm that exploits a specific term in the proof of R-WAPG to achieve faster convergence for solving (\ref{eqn:additive-comp-obj}) without knowing parameter $L, \mu$ in prior. 
    Results of numerical experiments are presented. 
    \par

\section{Preliminaries}
    Beck's book \cite{beck_first-order_2017}. 
    \subsection{Fundamentals in convex analysis}
    \subsection{Fundamentals in non-convex analysis}

\section{Unifying variants of Nesterov's accelerated methods}\label{sec:unify-nes-acceleration}

\section{Method of spectral momentum}\label{sec:spectral-momentum}

\section{Catalyst accelerations and future works}\label{sec:catalyst}

\section{Performance estimation problems}\label{sec:pep}

\section{Methods of inexact proximal point}\label{sec:inexact-prox}

\section{Nestrov's acceleration in the non-convex case}\label{sec:nes-acc-ncnvx}

\section{Using PostGreSQL and big data analytic method for species classification on Sentinel-2 Satelite remote sensing imagery}

\bibliographystyle{siam}
\bibliography{references/proposal.bib}
\newpage

\appendix

\end{document}

### 2024-12-12 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
             \left(
-                \prod_{i = 0}^{k} \max(1, \rho_{k - 1})
+                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
             \right)
@@
     \begin{proof}  
-        Recall the stepwise convergence theorem, since the choice of $\gamma, \hat \gamma$ is arbitrary choices for the theorem, we choose $\gamma = \rho_{k - 1} L \alpha_{k - 1}^2, \hat \gamma = L \alpha_k^2$, giving us:
+        Recall the stepwise convergence theorem, since the choice of $\gamma, \hat \gamma$ is arbitrary choices for the theorem, we choose $\gamma = \rho_{k - 1} L \alpha_{k - 1}^2, \hat \gamma = L \alpha_k^2$ at each step, giving us:
         {\small
@@
         This makes coefficient of $\Vert g_k\Vert^2$ zero. 
-        The fist inequality is by $\epsilon_k \ge 0$ and the non-negativity of the remaining terms. 
+        The first inequality is by $\epsilon_k \ge 0$ and the non-negativity of the remaining terms. 
         The last equality is by the assumption that $R_0 = 0$. 
@@
         \begin{align*}
-            x_{t + 1} - z_{t + 1} 
-            &= \theta_t(z_{t + 1} - z_t)
+            v_{t + 1} - x_{t + 1} 
+            &= \theta_t(x_{t + 1} - x_t)
         \end{align*}
@@
         \begin{align*}
-            x_{t + 1} &= 
-            (1 + \xi_t)^{-1}(x_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
+            v_{t + 1} &= 
+            (1 + \xi_t)^{-1}(v_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
             \\
             & \textcolor{gray}{
-                x_t = (1 + \tau_t)y_t - \tau_t z_t
+                v_t = (1 + \tau_t)y_t - \tau_t x_t
             }
@@
             &= 
-            (1 + \xi_t)^{-1}((1 + \tau_t)y_t - \tau_t z_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
-            \\
-            &= 
-            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
-            \\
-            x_{t + 1} - z_{t + 1}
-            &= 
-            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
+            (1 + \xi_t)^{-1}((1 + \tau_t)y_t - \tau_t x_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
+            \\
+            &= 
+            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t x_t - \delta_t \mathcal G_L(y_t))
+            \\
+            v_{t + 1} - x_{t + 1}
+            &= 
+            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t x_t - \delta_t \mathcal G_L(y_t))
             - (y_t - L^{-1}\mathcal G_Ly_t)
@@
             &= 
-            (1 + \xi_t)^{-1}(\tau_ty_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
+            (1 + \xi_t)^{-1}(\tau_ty_t - \tau_t x_t - \delta_t \mathcal G_L(y_t))
             + L^{-1}\mathcal G_Ly_t
@@
             \left(
-                \tau_ty_t - \tau_t z_t + (L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
+                \tau_ty_t - \tau_t x_t + (L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
             \right)
@@
             \left(
-                y_t - z_t + 
+                y_t - x_t + 
                 \tau_t^{-1}(L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
@@
         \begin{align*}
-            z_{t + 1} - z_t &= 
-            y_t - L^{-1}\mathcal G_L(y_t) - z_t
-            \\
-            &= (y_t - z_t) - L^{-1}\mathcal G_L(y_t). 
+            x_{t + 1} - x_t &= 
+            y_t - L^{-1}\mathcal G_L(y_t) - x_t
+            \\
+            &= (y_t - x_t) - L^{-1}\mathcal G_L(y_t). 
         \end{align*}
@@
         \begin{align*}
-            x_{t + 1} - z_{t + 1} &= 
+            v_{t + 1} - x_{t + 1} &= 
             (1 + \xi_t)^{-1}\tau_t
-            \left(y_t - z_t - L^{-1}\mathcal G_L(y_t)\right) 
+            \left(y_t - x_t - L^{-1}\mathcal G_L(y_t)\right) 
             = 
-            (1 + \xi_t)^{-1}\tau_t(z_{t + 1} - z_t). 
+            (1 + \xi_t)^{-1}\tau_t(x_{t + 1} - x_t). 
         \end{align*}
@@
         When $\mu = 0$, things simplify. 
-        Consider that $\alpha_{k +1}^2 = (1 - \alpha_{k + 1})\alpha_k^2$. 
+        Consider that $\alpha_{k +1}^2 = (1 - \alpha_{k + 1})\rho_k\alpha_k^2$. 
         \begin{align*}

### 2024-12-12 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
     The University of British Columbia, Kelowna, BC Canada V1V 1V7. 
-    E-mail:  \texttt{alto@mail.ubc.ca}.}~Author Name 1
-    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
-    The University of British Columbia, Kelowna, BC Canada V1V 1V7. 
-    E-mail:  \texttt{shawn.wang@ubc.ca}.}~ and~Author Name 2
+    E-mail:  \texttt{alto@mail.ubc.ca}.}~Hongda Li
+    % \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
+    % The University of British Columbia, Kelowna, BC Canada V1V 1V7. 
+    % E-mail:  \texttt{shawn.wang@ubc.ca}.}~ and~Author Name 2
 }
@@
     \noindent
-    Abstract abstract abstract. 
+    The research proposal focuses on the theories and practice in solving nonsmooth optimization. 
+    The theme of proposal highlight topics of interests that emphasize the computations and applications aspect of algorithms that exhibits both practical and theoretical importance. 
+    We summarize our ongoing research in unifying Nesterov-type accelerated proximal gradient method and proposes our method of spectral momentum. 
+    We survey literatures under the topic of Catalyst Meta Acceleration framework used in accelerating variance reduced methods in the settings of Data Science and Machine Learning. 
+    We present literatures and progress in topics such as Performance Estimation Problem, Inexact Proximal Point, acceleration without convexity. 
+    At the end there is a section summarizing a method we developed for tree species classifications using Sentinel-2 satellite remote sensing data using big data anlaytics by extract spectral signatures of ground vegegation covers.
+
 \end{abstract}
@@
     \par
+    Section \ref{sec:catalyst} are results of literatures review in MATH 590. 
+    It's based on a series of papers (CITATION HERE) in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
+    We will point out potential future direction of research of Catalyst acceleration. 
+    \par
 
@@
 
-\section{Nestrov's acceleration in the non-convex case}\label{sec:nes-acc-ncnvx}
+\section{Nestrov's acceleration in the non-convex case and momentum in general}\label{sec:nes-acc-ncnvx}
 

### 2024-12-12 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, a lot of changes

@@
         D_f(x, y): \RR^n \times \RR^n \rightarrow \RR 
-        \defeq f(x) - f(y) - \langle \nabla f(x), x - y\rangle. 
+        \defeq f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 
     \end{align*}
@@
         Observe that by convexity of $F$, $\epsilon_k \ge 0$ always. 
+        To see, consider the last inequality in the remark of Lemma \ref{thm:prox-grad-ineq} with $y = y_k, x = x_k$: 
+        \begin{align*}
+            F(x_k) - F(T_Ly_k)
+            - \langle L(y_k - T_Ly_k),x_k - y_k \rangle
+            - \frac{L}{2}\Vert y_k - T_Ly_k\Vert^2
+            - \frac{\mu}{2}\Vert x_k - y_k\Vert^2
+            &\ge 0
+            \\
+            \implies 
+            F(x_k) - F(T_Ly_k)
+            - \langle g_k,x_k - y_k \rangle
+            - \frac{1}{2L}\Vert g_k\Vert^2
+            &\ge 0. 
+        \end{align*}
     \end{assumption}
@@
         Let $0 \le \mu \le L$ be the strong convexity and Lipschitz smoothness parameter of $f$. 
-        Given iterates $(v_k, x_k)$, or equivalently $(y_k, x_k)$, $(x_k, y_k)$, any $\alpha_k \ge 0, \gamma \ge 0$, the algorithm generates scalar $\hat \gamma$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ by equalities:
+        Given iterates $(v_k, x_k)$, or equivalently $(y_k, x_k)$, $(x_k, y_k)$, any $\alpha_k > 0, \gamma > 0$, the algorithm generates scalar $\hat \gamma$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ by equalities:
         \begin{align*}
@@
         We make two crucial observations here. 
-        With the equalities, we define the following quantities associate with it. 
-        Fix any integer $k \ge 0$. 
-        To verify, we use the fundamental proximal gradient inequality. 
-        Next, observe that we have $x_k, y_k, v_k$ lie on the same line because they have 
+        We have $x_k, y_k, v_k$ lie on the same line because and they have the following equivalent equalities: 
         \begin{align*}
@@
         \end{align*}
-        On the first equality (Q1), we multiplied both side of the equation by $\gamma_{k + 1}/\alpha_k \gamma_k$ and then group $y_k$ on the LHS. 
+        On the first equality (Q1), we multiplied both side of the equation by $\hat\gamma/\alpha_k \gamma$ and then group $y_k$ on the LHS. 
         The last equality comes by multiplying both the numerator and denominator by $\hat \gamma$, leaving the numerator $\hat \gamma + \alpha_k \gamma = \gamma + \alpha_k \mu$. 
@@
         On the second equality that follows the second $\iff$ we just substituted $\hat\gamma = (1 - \alpha_k)\gamma + \alpha_k \mu$. 
-        Therefore, we discover that $x_k, v_k, y_k$ lies on the same line.
-
-    \begin{proposition}[Stepwise lyapunov]\label{prop:stepwise-lyapunov}\;\\
-        Fix any integer $k \ge0$, suppose that $v_{k + 1}, x_{k + 1}, y_k, g_k, \gamma, \hat \gamma$ satisfies Definition \ref{def:stepwise-wapg}. 
+        Therefore, we discover that $x_k, v_k, y_k$ lies on the same line because (Q1) indicates $y_k - v_k$ parallels to $-(y_k - x_k)$ and both vector shares the same head which anchors at $y_k$.
+
+    \begin{proposition}[Stepwise Lyapunov]\label{prop:stepwise-lyapunov}\;\\
+        Fix any integer $k \ge0$, assume $v_{k + 1}, x_{k + 1}, y_k, g_k, \hat \gamma$ are produced by Definition \ref{def:stepwise-wapg}. 
         Given any $R_k$.
@@
             \\
-            \text{use Q1}: & =
+            \text{use Q1 here } & =
             -\alpha_k(v_k - x^*) -
-            \frac{\alpha_k^2}{\hat \gamma}\frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k)
+            \frac{\alpha_k^2\mu}{\hat \gamma}\frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k)
             - (x_k - y_k) 
@@
             \\
-            \text{use Q2}: 
+            \text{use Q2 here}
             &= 
@@
             \frac{\alpha_k \mu + \gamma}{\gamma}
-            \frac{\alpha_k \gamma}{\gamma_k + \alpha_k \mu}(x_k - v_k)
+            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(x_k - v_k)
             \\
@@
         \;\\
-        Initialize any $\gamma_0 \in [0, 1]$, $(x_0, v_0)$ or equivalently: $(x_0, y_0), (y_0, v_0)$. 
+        Initialize any $\gamma_0 \in (0, 1)$, $(x_0, v_0)$ or equivalently: $(x_0, y_0), (y_0, v_0)$. 
         The algorithm generates a sequence of vector $(x_k, y_k, v_k)$ and auxiliary sequence $\alpha_k, \rho_k$ such that they satisfy for all $k\ge 0$: 
@@
             \\
-            \text{find }&\alpha_k \in [0, 1], \rho_k \ge 0: L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \mu \alpha_k  \;\wedge \; 0 \le \rho_k \alpha_k^2 \le 1, 
+            \text{find }&\alpha_k \in (0, 1), \rho_k > 0: L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \mu \alpha_k  \;\wedge \; 0 < \rho_k \alpha_k^2 < 1, 
             \\
@@
     \begin{observation}\label{obs:r-wapg-observation-1}
-        The sequence $\alpha_k$ satisfies the condition that $\alpha_k \in [0, 1]$.
-        In addition, if $\alpha_0 \in (0, 1)$, then the entire sequence $\alpha_k \in (0, 1)$. 
-        Suppose inductively that $\alpha_{k - 1}, \rho_{k - 1}$ are given such that they satisfy $\alpha_{k -1} \in [0, 1]$ and $\rho_{k - 1} \alpha_{k - 1}^2 < 1$. 
-        Solving the quadratic $L\alpha_k^2=(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2 + \mu \alpha_k$ for $\alpha_k$ yields candidates 
-        $$
-        \begin{aligned}
+        If $\alpha_0 \in (0, 1)$, then the entire sequence $\alpha_k \in (0, 1)$. 
+        Suppose inductively that $\alpha_{k - 1}, \rho_{k - 1}$ are given such that they satisfy $\alpha_{k -1} \in (0, 1)$ and $0 < \rho_{k - 1} \alpha_{k - 1}^2 < 1$. 
+        Solving the quadratic $L\alpha_k^2=(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2 + \mu \alpha_k$ for $\alpha_k$ yields candidates. 
+        \begin{align*}
             \alpha_k &= 
@@
             \right). 
-        \end{aligned}
-        $$
+        \end{align*}
         Choosing the positive sign which is the larger one of the roots of the quadratic. 
-        We have $\alpha_k \ge 0$ because: 
-        $$
-        \begin{aligned}
+        We have $\alpha_k > 0$ because: 
+        \begin{align*}
             \alpha_k &=
@@
                 \left|\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L\right|
-            \right)
-            \\
-            & \ge 0. 
-        \end{aligned}
-        $$
-        If $\alpha> 0$, we would have $4\rho_{k - 1} \alpha_{k - 1}^2 > 0$ , which allows for $> 0$ instead. 
-        An upper bound can be identified by using inductive hypothesis and consdering: 
-        $$
-        \begin{aligned}
+            \right) + \alpha_{k - 1}\sqrt{\rho_{k - 1}}
+            \\
+            & > 0. 
+        \end{align*}
+        On the last strict inequality we used the fact that $\rho_{k - 1}> 0, \alpha_{k - 1} > 0$. 
+        An upper bound can be identified by using inductive hypothesis and considering: 
+        \begin{align*}
             \alpha_k &= 
@@
             \\
-            &\le 
+            &<
             \frac{1}{2}\left(
-                \frac{\mu}{L} - 1
-                +
-                \sqrt{(1 - \mu/L)^2 + 4}
-            \right)
-            \\
-            &\le \frac{1}{2}\left(
-                0 + \sqrt{0 + 4}
-            \right) = 1. 
-        \end{aligned}
-        $$
-        Going from the second to the third inequality, we maximized $\mu/L$ by monotonicity of the linear function and the square root function. 
-        Therefore, inductively, $\alpha_k \in [0, 1]$ holds. 
-        Additionally, if $\alpha_{k - 1} \in (0, 1)$, then the results can be strengthened and $\alpha_k \in (0, 1)$ as well.
-
+                \frac{\mu}{L} + 
+                \sup_{x \in (0, 1)}
+                \left\lbrace
+                    -x + \sqrt{(x - \mu/L)^2 + x}
+                \right\rbrace
+            \right)
+            \\
+            & \le \frac{1}{2}\left(
+                \mu/L + \max\left(\mu/L, -1 + \sqrt{(1 - \mu/L)^2 + 1}\right)
+            \right) \le 1. 
+        \end{align*}
+        Going to the first inequality, we used $\rho_{k - 1} \alpha_{k - 1}^2 < 1$ to get the strict inequality. 
+        Going from the second to the third inequality, we maximized $\mu/L$ by monotone increasing of linear function and the square root function. 
+        Therefore, inductively, $\alpha_k \in (0, 1)$ holds. 
+        However, the limit of $\alpha_k$ could be 1. 
     \end{observation}
@@
     \begin{proof}  
-        Recall the stepwise convergence theorem, since the choice of $\gamma, \hat \gamma$ is arbitrary choices for the theorem, we choose $\gamma = \rho_{k - 1} L \alpha_{k - 1}^2, \hat \gamma = L \alpha_k^2$ at each step, giving us:
+        Recall the stepwise convergence theorem, since the choice of $\gamma, \hat \gamma$ is arbitrary choices for the theorem, we choose $\gamma = \rho_{k - 1} L \alpha_{k - 1}^2 > 0, \hat \gamma = L \alpha_k^2 > 0$ at each step.
+        Because $\alpha_k \in(0, 1)$ by Observation \ref{obs:r-wapg-observation-1}, we can use Proposition \ref{prop:stepwise-lyapunov}: 
         {\small

### 2024-12-13 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
             &= 
-            \mathcal M^{L^{-1}}(x; y)- D_f(x, y) \ge \mathcal M^{L^{-1}}(x; y). 
+            \mathcal M^{L^{-1}}(x; y)- D_f(x, y) \le \mathcal M^{L^{-1}}(x; y). 
         \end{align*}
@@
         {
-        Use $\mu = D_f(x^*, y_k)/\Vert y_k - x^*\Vert^2$ also works, $\mu$ is a pessimistic choice for the inequality above. 
+        Use $\mu = 2D_f(x^*, y_k)/\Vert y_k - x^*\Vert^2$ also works on (4*), $\mu$ is a pessimistic choice for the inequality above. 
         }
-        But in general the choice of $\mu$ remains the strong convexity modulus or equivalently, any value that is smallar than the true strong convexity constant for claiming the convergence rate for all initial guesses.
+        But in general the choice of $\mu$ remains the strong convexity modulus or equivalently, any value that is smaller than the true strong convexity constant for claiming the convergence rate for all initial guesses.
     \end{remark}
@@
         {
-            The choice of $\rho_k$ allows for divergence to traditional choices of step sizes in the literatures. 
+            The choice of $\rho_k$ allows for untraditional choices of step sizes in the literatures. 
             As we can see from the above convergence claim, there exists choices of $\rho_k\ge 1$ where convergence remains possible. 
@@
         \end{align*}
-        If $1 + \xi_t + \tau_t = L\delta_t$. Then 
+        If $1 + \xi_k + \tau_k = L\delta_k$. Then 
         $$
@@
     \begin{proof}
-        We are interested in identifying the conditions required for the sequence of $\xi_t, \tau_t, \delta_t$ such that there exists $\theta_t$ satisfying: 
-        \begin{align*}
-            v_{t + 1} - x_{t + 1} 
-            &= \theta_t(x_{t + 1} - x_t)
+        We are interested in identifying the conditions required for the sequence of $\xi_k, \tau_k, \delta_k$ such that there exists $\theta_k$ satisfying: 
+        \begin{align*}
+            v_{k + 1} - x_{k + 1} 
+            &= \theta_t(x_{k + 1} - x_k).
         \end{align*}
@@
         \begin{align*}
-            v_{t + 1} &= 
-            (1 + \xi_t)^{-1}(v_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
-            \\
-            & \textcolor{gray}{
-                v_t = (1 + \tau_t)y_t - \tau_t x_t
-            }
-            \\
-            &= 
-            (1 + \xi_t)^{-1}((1 + \tau_t)y_t - \tau_t x_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
-            \\
-            &= 
-            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t x_t - \delta_t \mathcal G_L(y_t))
-            \\
-            v_{t + 1} - x_{t + 1}
-            &= 
-            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t x_t - \delta_t \mathcal G_L(y_t))
-            - (y_t - L^{-1}\mathcal G_Ly_t)
-            \\
-            &= 
-            (1 + \xi_t)^{-1}(\tau_ty_t - \tau_t x_t - \delta_t \mathcal G_L(y_t))
-            + L^{-1}\mathcal G_Ly_t
-            \\
-            &= 
-            (1 + \xi_t)^{-1}
-            \left(
-                \tau_ty_t - \tau_t x_t + (L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
-            \right)
-            \\
-            &= 
-            (1 + \xi_t)^{-1}\tau_t
-            \left(
-                y_t - x_t + 
-                \tau_t^{-1}(L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
-            \right)
-        \end{align*}
+            v_{k + 1} &= 
+            (1 + \xi_k)^{-1}(v_k + \xi_t y_k - \delta_k \mathcal G_L(y_k))
+            \\
+            &= 
+            (1 + \xi_k)^{-1}((1 + \tau_k)y_k - \tau_t x_k + \xi_k y_k - \delta_k \mathcal G_L(y_k))
+            \\
+            &= 
+            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
+            \\
+            v_{k + 1} - x_{k + 1}
+            &= 
+            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_t - \tau_k x_k - \delta_t \mathcal G_L(y_k))
+            - (y_k - L^{-1}\mathcal G_Ly_k)
+            \\
+            &= 
+            (1 + \xi_k)^{-1}(\tau_ky_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
+            + L^{-1}\mathcal G_Ly_k
+            \\
+            &= 
+            (1 + \xi_k)^{-1}
+            \left(
+                \tau_ty_k - \tau_t x_k + (L^{-1}(1 + \xi_k) - \delta_k) \mathcal G_L(y_k)
+            \right)
+            \\
+            &= 
+            (1 + \xi_k)^{-1}\tau_k
+            \left(
+                y_k - x_k + 
+                \tau_k^{-1}(L^{-1}(1 + \xi_k) - \delta_k) \mathcal G_L(y_k)
+            \right).
+        \end{align*}
+        Going between the first and second inequality we used $v_k = (1 + \tau_k)y_k - \tau_k x_k$ which is an rearranged $y_k = (1 + \tau_k)^{-1}(v_k + \tau_k x_k)$. 
         The RHS is can be verified through 
         \begin{align*}
-            x_{t + 1} - x_t &= 
-            y_t - L^{-1}\mathcal G_L(y_t) - x_t
-            \\
-            &= (y_t - x_t) - L^{-1}\mathcal G_L(y_t). 
+            x_{k + 1} - x_k &= 
+            y_t - L^{-1}\mathcal G_L(y_k) - x_k
+            \\
+            &= (y_k - x_k) - L^{-1}\mathcal G_L(y_k). 
         \end{align*}
@@
         \begin{align*}
-            \tau_t^{-1}(L^{-1}(1 + \xi_t) - \delta_t) 
+            \tau_t^{-1}(L^{-1}(1 + \xi_k) - \delta_k) 
             &= - L^{-1}
             \\
-            (1 + \xi_t) - L\delta_t
-            &= 
-            - \tau_t
-            \\
-            1 + \xi_t + \tau_t
-            &=
-            L\delta_t. 
+            (1 + \xi_k) - L\delta_k
+            &= 
+            - \tau_k
+            \\
+            1 + \xi_k + \tau_k
+            &=
+            L\delta_k. 
         \end{align*}
@@
         \begin{align*}
-            v_{t + 1} - x_{t + 1} &= 
-            (1 + \xi_t)^{-1}\tau_t
-            \left(y_t - x_t - L^{-1}\mathcal G_L(y_t)\right) 
+            v_{k + 1} - x_{k + 1} &= 
+            (1 + \xi_k)^{-1}\tau_t
+            \left(y_k - x_k - L^{-1}\mathcal G_L(y_k)\right) 
             = 
-            (1 + \xi_t)^{-1}\tau_t(x_{t + 1} - x_t). 
+            (1 + \xi_k)^{-1}\tau_k(x_{k + 1} - x_k). 
         \end{align*}
@@
         {
-        There exists a choice of $\rho_k \in [0, 1), \mu = 0$ such that the above algorithm is equivalent to Chambolle Dossal 2015 \cite{chambolle_convergence_2015}. 
+        There exists a choice of $\rho_k \in (0, 1], \mu = 0$ such that the above algorithm is equivalent to Chambolle Dossal 2015 \cite{chambolle_convergence_2015}. 
         When $\rho_k = 1$, this becomes just FISTA \cite{beck_fast_2009}. 
@@
 \subsection{Representing algorithms in the literatures via R-WAPG}
+
 \subsection{The method of Spectral Momentum}
+
 \subsection{Numerical experiments and applications}

### 2024-12-13 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
     \par
+    Section \ref{sec:pep}, \ref{sec:inexact-prox}, \ref{sec:nes-acc-ncnvx} preview literatures in  nonsmooth optimization frontier research where progress and impacts can be made.
 
@@
 
-\section{Using PostGreSQL and big data analytic method for species classification on Sentinel-2 Satelite remote sensing imagery}
+\section{Using PostGreSQL and big data analytic method for species classification on Sentinel-2 Satellite remote sensing imagery}
 

### 2024-12-15 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
     \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
-    The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{alto@mail.ubc.ca}.}~ and~Xianfu Wang
+    The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{alto@mail.ubc.ca}.}~Xianfu Wang
     \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
     The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{shawn.wang@ubc.ca}.}
+    and ~Heinz H. Bauschke~
+    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
+    The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{heinz.bauschke@ubc.ca}.
+    }
 }
@@
         We present a theoretical unification through the formulation of ``Relaxed weak accelerated proximal gradient algorithm (R-WAPG)'' which we invented. 
-        It unifies convergence claim for accelerated method for the strongly convex objective and Lipschitz smooth but non-strongly convex case and it relaxes the conditions on the momentum sequence.
+        It unifies convergence claim for accelerated method for the strongly convex objective and Lipschitz smooth but non-strongly convex case, and it relaxes the conditions on the momentum sequence.
 
@@
         Numerical experiments are conducted to illustrate the theoretical convergence of R-WAPG and the performance of Spectral Momentum in with applications. 
+        We do net yet have a proof for the convergence of the algorithm in general.
 
@@
         \end{align}
-        Observe that by convexity of $F$, $\epsilon_k \ge 0$ always. 
-        To see, consider the last inequality in the remark of Lemma \ref{thm:prox-grad-ineq} with $y = y_k, x = x_k$: 
+        Observe that by convexity of $F$, $\epsilon_k \ge 0$ for all $x_k, L > 0$. 
+        To see, consider the last inequality in the remark of Theorem \ref{thm:prox-grad-ineq} with $y = y_k, x = x_k$: 
         \begin{align*}
@@
     \begin{definition}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
-        Let $0 \le \mu \le L$ be the strong convexity and Lipschitz smoothness parameter of $f$. 
-        Given iterates $(v_k, x_k)$, or equivalently $(y_k, x_k)$, $(x_k, y_k)$, any $\alpha_k > 0, \gamma > 0$, the algorithm generates scalar $\hat \gamma$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ by equalities:
+        Let $0 \le \mu < L$ be the strong convexity and Lipschitz smoothness parameter of $f$. 
+        Given iterates $(v_k, x_k)$, or equivalently $(y_k, x_k)$, $(x_k, y_k)$, any $\alpha_k \in (0, 1), \gamma > 0$, the algorithm generates scalar $\hat \gamma$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ by equalities:
         \begin{align*}
@@
             (\gamma + \alpha_k \mu)^{-1}
-            (\alpha_k \gamma_k v_k - (\gamma + \alpha_k \mu)x_k + \hat \gamma x_k)
+            (\alpha_k \gamma v_k - (\gamma + \alpha_k \mu)x_k + \hat \gamma x_k)
             \\
@@
                     \epsilon_k + R_k + 
-                    \frac{\mu\alpha_k\gamma_k}{2\hat \gamma}
+                    \frac{\mu\alpha_k\gamma}{2\hat \gamma}
                     \Vert v_k - y_k\Vert^2
@@
                 (
-                    \gamma_k(1 - \alpha_k)v_k - 
+                    \gamma(1 - \alpha_k)v_k - 
                     \alpha_k g_k + \mu \alpha_k y_k
@@
             \\
-            \text{use Q1 here } & =
+            & =
             -\alpha_k(v_k - x^*) -
@@
             - (x_k - y_k) 
+            &\text{by Q1} 
             \\
@@
             \\
-            \text{use Q2 here}
             &= 
@@
             \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(x_k - v_k)
+            &\text{by Q2}
             \\
@@
         }
-        On the last line, we expand the definition of $g_k$ and then used 
-        \hyperref[thm:prox-grad-ineq]{Theorem \ref*{thm:prox-grad-ineq}}. 
+        On the last line, we expand the definition of $g_k$ and then used the
+        \hyperref[thm:prox-grad-ineq]{remark of Theorem \ref*{thm:prox-grad-ineq}}. 
         Therefore, we conclude that: 
@@
         {
-        Use $\mu = 2D_f(x^*, y_k)/\Vert y_k - x^*\Vert^2$ also works on (4*), $\mu$ is a pessimistic choice for the inequality above. 
+        Given $y_k$, we may choose to increase $\mu_\kappa = 2D_f(x^*, y_k)/\Vert y_k - x^*\Vert^2 \ge \mu$ which also works on (4*), $\mu$ is a pessimistic choice for the inequality above. 
         }
@@
         \;\\
-        Initialize any $\gamma_0 \in (0, 1)$, $(x_0, v_0)$ or equivalently: $(x_0, y_0), (y_0, v_0)$. 
+        Initialize any $\gamma_0 \in (0, L]$, $(x_0, v_0)$ or equivalently: $(x_0, y_0), (y_0, v_0)$. 
         The algorithm generates a sequence of vector $(x_k, y_k, v_k)$ and auxiliary sequence $\alpha_k, \rho_k$ such that they satisfy for all $k\ge 0$: 
@@
     \begin{observation}\label{obs:r-wapg-observation-1}
-        If $\alpha_0 \in (0, 1)$, then the entire sequence $\alpha_k \in (0, 1)$. 
+        If $\alpha_0 \in (0, 1)$ (this is true by $\gamma_0 \in (0, L]$), then the entire sequence $\alpha_k \in (0, 1)$. 
         Suppose inductively that $\alpha_{k - 1}, \rho_{k - 1}$ are given such that they satisfy $\alpha_{k -1} \in (0, 1)$ and $0 < \rho_{k - 1} \alpha_{k - 1}^2 < 1$. 
@@
                 \left\lbrace
-                    -x + \sqrt{(x - \mu/L)^2 + x}
+                    -x + \sqrt{(x - \mu/L)^2 + 4x}
                 \right\rbrace
@@
             & \le \frac{1}{2}\left(
-                \mu/L + \max\left(\mu/L, -1 + \sqrt{(1 - \mu/L)^2 + 1}\right)
+                \mu/L + \max\left(\mu/L, -1 + \sqrt{(1 - \mu/L)^2 + 4}\right)
             \right) \le 1. 
@@
         This makes coefficient of $\Vert g_k\Vert^2$ zero. 
-        The first inequality is by $\epsilon_k \ge 0$ and the non-negativity of the remaining terms. 
+        The first inequality is by $\epsilon_k \ge 0$ and the non
+        -negativity of the remaining terms. 
         The last equality is by the assumption that $R_0 = 0$. 
@@
         {
-            The choice of $\rho_k$ allows for untraditional choices of step sizes in the literatures. 
+            The choice of $\rho_k$ allows for nontraditional choices of step sizes in the literatures. 
             As we can see from the above convergence claim, there exists choices of $\rho_k\ge 1$ where convergence remains possible. 
@@
         {
-        There exists a choice of $\rho_k \in (0, 1], \mu = 0$ such that the above algorithm is equivalent to Chambolle Dossal 2015 \cite{chambolle_convergence_2015}. 
+        There exists a choice of $\rho_k \in (0, 1], \mu = 0$ such that the above algorithm is equivalent to Chambolle, Dossal 2015 \cite{chambolle_convergence_2015}. 
         When $\rho_k = 1$, this becomes just FISTA \cite{beck_fast_2009}. 
@@
 
-\subsection{The method of Spectral Momentum}
+\subsection{The method of Inexact Momentum}
 
@@
 \bibliographystyle{siam}
-\bibliography{references/Spectral_Momentum.bib}
+\bibliography{references/Inexact_Momentum.bib}
 

### 2024-12-16 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
     \begin{observation}\label{obs:r-wapg-observation-1}
-        If $\alpha_0 \in (0, 1)$ (this is true by $\gamma_0 \in (0, L]$), then the entire sequence $\alpha_k \in (0, 1)$. 
+        If $\alpha_0 \in (0, 1)$ which is true by $\gamma_0 \in (0, L]$, then the entire sequence $\alpha_k \in (0, 1)$. 
         Suppose inductively that $\alpha_{k - 1}, \rho_{k - 1}$ are given such that they satisfy $\alpha_{k -1} \in (0, 1)$ and $0 < \rho_{k - 1} \alpha_{k - 1}^2 < 1$. 
@@
         Here, if we assume sequence $\alpha_k$ is constant, then $\alpha_k = \sqrt{\mu/L}$ is a solution to the above iterative equation. 
-        Substituting it back to the momentum form of R-WAPG, we recovers the V-FISTA algorithm, which appears as (10.7.7) in Beck's Book \cite{beck_first-order_2017}. 
+        Substituting it back to the momentum form of R-WAPG, we recover the V-FISTA algorithm, which appears as (10.7.7) in Beck's Book \cite{beck_first-order_2017}. 
         }

### 2024-12-17 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
 \subsection{The method of Inexact Momentum}
+    This section introduces an algorithm of our creation through the remark of Proposition \ref*{prop:stepwise-lyapunov}. 
+    The algorithm estimates the $\mu$ constant as the algorithm executes and pools the information using the Bregman Divergence of the smooth part function $f$.
 

### 2024-12-17 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
     The theme of proposal highlight topics of interests that emphasize the computations and applications aspect of algorithms that exhibits both practical and theoretical importance. 
-    We summarize our ongoing research in unifying Nesterov-type accelerated proximal gradient method and proposes our method of spectral momentum. 
+    We summarize our ongoing research in unifying Nesterov type accelerated proximal gradient method and proposes our method of spectral momentum. 
     We survey literatures under the topic of Catalyst Meta Acceleration framework used in accelerating variance reduced methods in the settings of Data Science and Machine Learning. 
     We present literatures and progress in topics such as Performance Estimation Problem, Inexact Proximal Point, acceleration without convexity. 
-    At the end there is a section summarizing a method we developed for tree species classifications using Sentinel-2 satellite remote sensing data using big data anlaytics by extract spectral signatures of ground vegegation covers.
+    At the end there is a section summarizing a method we developed for tree species classifications using Sentinel-2 satellite remote sensing data using big data anlaytics by extract spectral signatures of ground vegetation covers.
 

### 2024-12-17 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

@@
     For a specific definition of first order method, we refer reader to Chapter 2 of Nesterov's new book \cite{nesterov_lectures_2018} for more information. 
-    Gradient descent has an upper bound of $\mathcal O(1/k)$ in iteration complexity that is slower than
+    Gradient descent has an upper bound of $\mathcal O(1/k)$ in iteration complexity of function value that is slower than
     the lower iteration complexity $\mathcal O(1/k^2)$. 
-    Accelerated gradient descent has an upper bound of $\mathcal O(1/k^2)$, making it optimal. 
+    Accelerated gradient descent has an upper bound of $\mathcal O(1/k^2)$ in function value, making it optimal. 
     \par
@@
     This section swiftly exposes the constructions of the Nesterov's estimating sequence for accelerated proximal gradient method.
-A similar accelerated projected gradient is Algorithm (2.2.63) in Nesterov's book \cite{nesterov_lectures_2018}.
+A similar accelerated projected gradient is \\ Algorithm (2.2.63) in Nesterov's book \cite{nesterov_lectures_2018}.
     We use accelerated proximal gradient algorithm as an example because its formulation is similar to the Catalyst Acceleration framework. 

### 2024-12-17 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
         \;\\
-        Initialize any $\gamma_0 \in (0, L]$, $(x_0, v_0)$ or equivalently: $(x_0, y_0), (y_0, v_0)$. 
-        The algorithm generates a sequence of vector $(x_k, y_k, v_k)$ and auxiliary sequence $\alpha_k, \rho_k$ such that they satisfy for all $k\ge 0$: 
+        Initialize any $\gamma_1 \in (0, L]$, $(x_1, v_1)$ or equivalently: $(x_1, y_1), (y_1, v_1)$. 
+        The algorithm generates a sequence of vector $(x_k, y_k, v_k)$ and auxiliary sequence $\alpha_k, \rho_k$ such that they satisfy for all $k\ge 1$: 
         $$
@@
             \gamma_k &:= \left.\begin{cases}
-                \rho_{k -1}L\alpha_{k - 1}^2 & k \ge 1,
-                \\
-                \gamma_0 & k = 0. 
+                \rho_{k -1}L\alpha_{k - 1}^2 & k \ge 2,
+                \\
+                \gamma_1 & k = 1. 
             \end{cases}\right\rbrace,
@@
         Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018}. 
+        The initial condition is generic so it can describe accelerated proximal gradient method in the middle of its executions. 
+        \par
+        We only need any two of the intertes among $x_1, y_1, v_1$ because we can solve 
+        $y_1 = (\gamma_1 + \alpha_1\mu)^{-1}(\alpha_1 \gamma_1 v_1 + \hat \gamma_{2}x_1)$ for $x_1, y_1$ or $v_1$ given $(v_1, y_1), (v_1, x_1)$, or $(x_1, y_1)$. 
+        \par
+        % Usually, people initialize the method with one step of gradient descent. 
+        % For example, given any $y_0 = x_{0} = v_0\in \RR^n$, we can choose the initial condition $(x_1, v_1)$ to be $v_1 = x_1 = T_L y_{0}$,
+
     \end{observation}
     \begin{observation}\label{obs:r-wapg-observation-1}
-        If $\alpha_0 \in (0, 1)$ which is true by $\gamma_0 \in (0, L]$, then the entire sequence $\alpha_k \in (0, 1)$. 
+        If $\alpha_1 \in (0, 1)$ which is true by $\gamma_1 \in (0, L]$, then the entire sequence $\alpha_k \in (0, 1)$. 
         Suppose inductively that $\alpha_{k - 1}, \rho_{k - 1}$ are given such that they satisfy $\alpha_{k -1} \in (0, 1)$ and $0 < \rho_{k - 1} \alpha_{k - 1}^2 < 1$. 
@@
     \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}
-        Let vectors $(x_k, y_k, v_k)_{k \ge0}$ and scalars $\alpha_k$ be generated by R-WAPG (Definition \ref{def:wapg}). 
+        Let vectors $(x_k, y_k, v_k)_{k \ge 1}$ and scalars $\alpha_k$ be generated by R-WAPG (Definition \ref{def:wapg}). 
         Define recursively for all $k\ge1$ by 
@@
         \end{align*}
-        Choose $R_0= 0$ to be the base case. 
+        Choose $R_1= 0$ to be the base case. 
         Choose any $x^* \in \RR^n$ then
@@
             \left(
-                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
-            \right)
-            \left(
-                \prod_{i = 0}^{k} \left(1  - \alpha_i\right)
-            \right)
-            \left(
-                F(x_0) - F(x^*) + \frac{\gamma_0}{2}\Vert v_k - x^*\Vert^2
+                \prod_{i = 1}^{k - 1} \max(1, \rho_{k})
+            \right)
+            \left(
+                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
+            \right)
+            \left(
+                F(x_1) - F(x^*) + \frac{\gamma_1}{2}\Vert v_1 - x^*\Vert^2
             \right). 
@@
             \left(
-                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
-            \right)
-            \left(
-                \prod_{i = 0}^{k} \left(1  - \alpha_i\right)
-            \right)
-            \left(
-                F(x_0) - F^* + R_0 + \frac{\gamma_0}{2}\Vert v_k - x^*\Vert^2
+                \prod_{i = 1}^{k - 1} \max(1, \rho_{k})
+            \right)
+            \left(
+                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
+            \right)
+            \left(
+                F(x_1) - F^* + R_1 + \frac{\gamma_1}{2}\Vert v_1 - x^*\Vert^2
             \right). 
@@
             \\
-            &\ge R_0 \prod_{i = 0}^{k} \left(1 - \alpha_i\right) = 0. 
+            &\ge R_1 \prod_{i = 1}^{k} \left(1 - \alpha_i\right) = 0. 
         \end{align*}
@@
         -negativity of the remaining terms. 
-        The last equality is by the assumption that $R_0 = 0$. 
+        The last equality is by the assumption that $R_1 = 0$. 
         Therefore: 
@@
             \left(
-                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
-            \right)
-            \left(
-                \prod_{i = 0}^{k} \left(1  - \alpha_i\right)
-            \right)
-            \left(
-                F(x_0) - F^* + R_0 + \frac{\gamma_0}{2}\Vert v_k - x^*\Vert^2
+                \prod_{i = 1}^{k - 1} \max(1, \rho_{k})
+            \right)
+            \left(
+                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
+            \right)
+            \left(
+                F(x_1) - F^* + \frac{\gamma_1}{2}\Vert v_1 - x^*\Vert^2
             \right). 
@@
     \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
-        For all $k\ge 0$, iterates $(w_t, y_t, x_{t + 1}, z_{t + 1})$ satisfies recursively that: 
+        For all $k\ge 0$, iterates $(w_k, y_k, x_{k + 1}, z_{k + 1})$ satisfies recursively that: 
         \begin{align*}
@@
         \end{align*}
-        If $1 + \xi_k + \tau_k = L\delta_k$. Then 
+        If $1 + \xi_k + \tau_k = L\delta_k, \tau_k \neq 0$. Then 
         $$
@@
             v_{k + 1} - x_{k + 1} 
-            &= \theta_t(x_{k + 1} - x_k).
+            &= \theta_k(x_{k + 1} - x_k).
         \end{align*}
@@
         \end{align*}
-        Going between the first and second inequality we used $v_k = (1 + \tau_k)y_k - \tau_k x_k$ which is an rearranged $y_k = (1 + \tau_k)^{-1}(v_k + \tau_k x_k)$. 
+        Going between the first and second inequality we used $v_k = (1 + \tau_k)y_k - \tau_k x_k$ which is rearranged $y_k = (1 + \tau_k)^{-1}(v_k + \tau_k x_k)$. 
         The RHS is can be verified through 
@@
         \begin{align*}
-            \tau_t^{-1}(L^{-1}(1 + \xi_k) - \delta_k) 
+            \tau_k^{-1}(L^{-1}(1 + \xi_k) - \delta_k) 
             &= - L^{-1}
@@
             Assume $\mu < L$. 
-            Choose any $\gamma_0 \in (0, 1)$ as the initial condition for R-WAPG (Definition \ref{def:wapg}) to produce vectors sequence $(y_i)_{i \in \N}, (x_i)_{i \in \N}, (v_i)_{i \in \N}$ and $(\rho_k)_{i \in \N}, (\alpha_k)_{i \in \N}$.
-            Then the iterates can be expressed without $(\gamma_k)_{k \ge0}, (\rho_k)_{k\ge0}$, and for all $k\ge 0$ they are algebraically equivalent to
+            Choose any $\gamma_1 \in (0, L]$ as the initial condition for R-WAPG (Definition \ref{def:wapg}) to produce vectors sequence $(y_i)_{i \in \N}, (x_i)_{i \in \N}, (v_i)_{i \in \N}$ and $(\rho_k)_{i \in \N}, (\alpha_k)_{i \in \N}$.
+            Then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge1}$, and for all $k\ge 1$ they are algebraically equivalent to
             \begin{align*}
@@
         \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
-            Given any initial $\alpha_0 \in (0, 1)$, $(x_0, y_0)$ or equivalently $(x_0, v_0), (y_0, v_0)$. 
+            Given any initial $\alpha_1 \in (0, 1)$, $(x_1, y_1)$ or equivalently $(x_1, v_1), (y_1, v_1)$. 
             Assume $\mu < L$. 
-            The algorithm generate sequence of vector iterates $(x_k, v_k, y_k)_{k \ge0}$ by the procedures: 
-            \begin{align*}
-                \text{find }& \rho_{k - 1}: 0 < \rho_{k - 1} < \alpha_{k - 1}^{-2},
-                \\
-                \alpha_k &= 
-                \frac{1}{2}\left(
-                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
-                +
-                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
-                \right), 
-                \\
-                y_k &= 
+            The algorithm generate sequence of vector iterates $(x_k, v_k, y_k)_{k \ge 1}$ by the procedures: 
+            \begin{align*}
+                & y_k = 
                 \left(
@@
                 \\
-                x_{k + 1} &= 
+                & x_{k + 1} = 
                 y_k - L^{-1} \mathcal G_L y_k, 
                 \\
-                v_{k + 1} &= 
+                & v_{k + 1} = 
                 \left(
@@
                     \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
-                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
+                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k
+                \\
+                & \text{choose any } \rho_{k}: 0 < \rho_{k} < \alpha_{k}^{-2}, 
+                \\
+                & \alpha_{k + 1} = 
+                \frac{1}{2}\left(
+                \frac{\mu}{L} - \rho_{k}\alpha_{k}^2 
+                +
+                \sqrt{(\rho_{k}\alpha_{k}^2 - \mu/L)^2 + 4\rho_{k}\alpha_{k}^2}
+                \right). 
             \end{align*}
         \end{definition}
+
         \begin{proposition}[Second equivalent representation of R-WAPG]\label{prop:wagp-st-form}\;\\
-            Let iterates $(x_k, v_k, y_k)_{k \ge 0}$ and sequence $(\alpha_k, \rho_k)_{k \ge0}$ be given by Definition \ref{def:r-wapg-intermediate}. 
-            Then for all $k \ge0$, iterate $(v_k)_{k \ge 0}, (x_k)_{k \ge 0}, (y_k)_{k \ge0}$ are algebraically equivalent to: 
+            Let iterates $(x_k, v_k, y_k)_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge1}$ be given by Definition \ref{def:r-wapg-intermediate}. 
+            Then for all $k \ge 1$, iterate $(v_k)_{k \ge 1}, (x_k)_{k \ge 1}, (y_k)_{k \ge1}$ are algebraically equivalent to: 
             \begin{align*}
@@
         \end{proof}
-    \begin{definition}[R-WAPG similar triangle form]\label{def:r-wapg-st-form}
-        Given any initial $\alpha_0 \in (0, 1)$, $(x_0, y_0)$ or equivalently $(x_0, v_0), (y_0, v_0)$. 
+    \begin{definition}[R-WAPG similar triangle form]\label{def:r-wapg-st-form} \; \\
+        Given any initial $\alpha_1 \in (0, 1)$, $(x_1, v_1)$. 
         Assume $\mu < L$. 
-        The algorithm generate sequence of vector iterates $(x_k, v_k, y_k)_{k \ge0}$ by the procedures: 
-        \begin{align*}
-            \text{find }& \rho_{k - 1}: 0 < \rho_{k - 1} < \alpha_{k - 1}^{-2},
-            \\
-            \alpha_k &= 
-            \frac{1}{2}\left(
-            \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
-            +
-            \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
-            \right), 
-            \\
-            y_k &= 
+        The algorithm generates sequences of vector iterates $(x_k, v_k, y_k)_{k \ge 2}$ by the procedures: 
+        \begin{align*}
+            & y_k = 
             \left(
@@
             \\
-            x_{k + 1} &= 
+            & x_{k + 1} = 
             y_k - L^{-1} \mathcal G_L y_k, 
             \\
-            v_{k + 1} &= 
-            x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k). 
+            & v_{k + 1} = 
+            x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k), 
+            \\
+            & \text{choose any }   \rho_{k}: 0 < \rho_{k} < \alpha_{k}^{-2}, 
+            \\
+            &\alpha_{k + 1} = 
+            \frac{1}{2}\left(
+            \frac{\mu}{L} - \rho_{k}\alpha_{k}^2 
+            +
+            \sqrt{(\rho_{k}\alpha_{k}^2 - \mu/L)^2 + 4\rho_{k}\alpha_{k}^2}
+            \right). 
         \end{align*}
@@
         \;\\
-        Let sequence $(\alpha_k, \rho_k)_{k \ge0}$ and iterates $(x_k, v_k, y_k)_{k\ge 0}$ given by R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}). 
-        Then the iterates are algebraically equivalent to: 
+        Let sequence $(\alpha_k, \rho_k)_{k \ge 1}$ and iterates $(x_k, v_k, y_k)_{k\ge 1}$ given by R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}). 
+        Then for all $k \ge 1$, the iterates are algebraically equivalent to: 
         \begin{align*}
@@
     \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
-        Initialize any $\alpha_0 \in (0, 1)$. 
+        Initialize any $\alpha_1 \in (0, 1)$. 
         The algorithm generates iterates $(v_k, x_k, y_k)$ and auxiliary sequence $(\rho_k)_{k \ge0}$ by the following procedures: 

### 2024-12-17 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
     We survey literatures under the topic of Catalyst Meta Acceleration framework used in accelerating variance reduced methods in the settings of Data Science and Machine Learning. 
-    We present literatures and progress in topics such as Performance Estimation Problem, Inexact Proximal Point, acceleration without convexity. 
-    At the end there is a section summarizing a method we developed for tree species classifications using Sentinel-2 satellite remote sensing data using big data anlaytics by extract spectral signatures of ground vegetation covers.
+    Furthermore, we present literatures and progress in topics such as Performance Estimation Problem, Inexact Proximal Point, acceleration without convexity. 
+    At the end there is a section summarizing a method we developed for tree species classifications using Sentinel-2 satellite remote sensing data using big data analytics by extract spectral signatures of ground vegetation covers.
 
@@
 
+\newpage
 \tableofcontents

### 2024-12-18 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
 
-        We present a theoretical unification through the formulation of ``Relaxed weak accelerated proximal gradient algorithm (R-WAPG)'' which we invented. 
-        It unifies convergence claim for accelerated method for the strongly convex objective and Lipschitz smooth but non-strongly convex case, and it relaxes the conditions on the momentum sequence.
-
-        We connect the theories and practice by pointing out one practical exploits inspired the convergence proof of the algorithm which we called ``Spectral Momentum''. 
-        Numerical experiments are conducted to illustrate the theoretical convergence of R-WAPG and the performance of Spectral Momentum in with applications. 
-        We do net yet have a proof for the convergence of the algorithm in general.
+        % We present a theoretical unification through the formulation of ``Relaxed weak accelerated proximal gradient algorithm (R-WAPG)'' which we invented. 
+        % It unifies convergence claim for accelerated method for the strongly convex objective and Lipschitz smooth but non-strongly convex case, and it relaxes the conditions on the momentum sequence.
+
+        % We connect the theories and practice by pointing out one practical exploits inspired the convergence proof of the algorithm which we called ``Spectral Momentum''. 
+        % Numerical experiments are conducted to illustrate the theoretical convergence of R-WAPG and the performance of Spectral Momentum in with applications. 
+        % We do net yet have a proof for the convergence of the algorithm in general.
 
@@
     \begin{definition}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
-        Let $0 \le \mu < L$ be the strong convexity and Lipschitz smoothness parameter of $f$. 
-        Given iterates $(v_k, x_k)$, or equivalently $(y_k, x_k)$, $(x_k, y_k)$, any $\alpha_k \in (0, 1), \gamma > 0$, the algorithm generates scalar $\hat \gamma$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ by equalities:
-        \begin{align*}
-            \hat \gamma &:= (1 - \alpha_k)\gamma + \mu \alpha_k, 
+        Assume $0 \le \mu < L$.  
+        Fix any $k \in \mathbb Z$. 
+        For any $(v_k, x_k), \alpha_k \in (0, 1), \gamma > 0$, let $\hat \gamma$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ be given by: 
+        \begin{align*}
+            \hat \gamma &= (1 - \alpha_k)\gamma + \mu \alpha_k, 
             \\
@@
     \begin{proposition}[Stepwise Lyapunov]\label{prop:stepwise-lyapunov}\;\\
-        Fix any integer $k \ge0$, assume $v_{k + 1}, x_{k + 1}, y_k, g_k, \hat \gamma$ are produced by Definition \ref{def:stepwise-wapg}. 
-        Given any $R_k$.
+        Fix any integer $k \in \mathbb Z$, for any $v_k, x_k$, let $v_{k + 1}, x_{k + 1}, y_k, v_k, x_k, \hat \gamma$ be given by Definition \ref{def:stepwise-wapg}. 
+        Choose any arbitrary $R_k \in \RR$.
         Define: 
@@
         \;\\
-        Initialize any $\gamma_1 \in (0, L]$, $(x_1, v_1)$ or equivalently: $(x_1, y_1), (y_1, v_1)$. 
-        The algorithm generates a sequence of vector $(x_k, y_k, v_k)$ and auxiliary sequence $\alpha_k, \rho_k$ such that they satisfy for all $k\ge 1$: 
-        $$
-        \begin{aligned}
+        Initialize any $\gamma_1 \in (0, L]$, $(x_1, v_1)$. 
+        Given auxiliary sequences $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ satisfying for all $k \ge 2$ the conditions: 
+        \begin{align*}
+            &\alpha_k \in (0, 1), 
+            \\
+            &\rho_k > 0, 
+            \\
+            &L\alpha_k^2 = (1 - \alpha_k)\rho_{k - 1}L \alpha_{k - 1}^2 + \mu \alpha_k , 
+            \\
+            &0 < \rho_k \alpha_k^2 < 1. 
+        \end{align*}
+        With base case $k = 1$ given by $\alpha_1 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$. 
+        The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ such that they satisfy for all $k\ge 1$: 
+        \begin{align*}
             \gamma_k &:= \left.\begin{cases}
@@
             \end{cases}\right\rbrace,
-            \\
-            \text{find }&\alpha_k \in (0, 1), \rho_k > 0: L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \mu \alpha_k  \;\wedge \; 0 < \rho_k \alpha_k^2 < 1, 
             \\
@@
             x_{k + 1} &= T_L y_k. 
-        \end{aligned}
-        $$
+        \end{align*}
     \end{definition}
@@
         Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018}. 
-        The initial condition is generic so it can describe accelerated proximal gradient method in the middle of its executions. 
+        The initial condition is generic, so it can describe accelerated proximal gradient method in the middle of its executions. 
         \par
-        We only need any two of the intertes among $x_1, y_1, v_1$ because we can solve 
-        $y_1 = (\gamma_1 + \alpha_1\mu)^{-1}(\alpha_1 \gamma_1 v_1 + \hat \gamma_{2}x_1)$ for $x_1, y_1$ or $v_1$ given $(v_1, y_1), (v_1, x_1)$, or $(x_1, y_1)$. 
-        \par
-        % Usually, people initialize the method with one step of gradient descent. 
-        % For example, given any $y_0 = x_{0} = v_0\in \RR^n$, we can choose the initial condition $(x_1, v_1)$ to be $v_1 = x_1 = T_L y_{0}$,
-
+        Alternatively, any two of the vectors among $x_1, y_1, v_1$ can be used to initialize the algorithm because given $(v_1, y_1), (v_1, x_1)$, or $(x_1, y_1)$ we can solve 
+        $y_1 = (\gamma_1 + \alpha_1\mu)^{-1}(\alpha_1 \gamma_1 v_1 + \hat \gamma_{2}x_1)$ for $x_1, y_1$ or $v_1$. 
+        % \par
+        % If one initial condition $x_0$ is given. 
+        % Then $v_1 = x_0, x_1 = T_L x_0$ is considered a valid initial conditions. 
     \end{observation}
+
     \begin{observation}\label{obs:r-wapg-observation-1}
@@
 
-    \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}
-        Let vectors $(x_k, y_k, v_k)_{k \ge 1}$ and scalars $\alpha_k$ be generated by R-WAPG (Definition \ref{def:wapg}). 
+    \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}\; \\
+        Given any $(v_1, x_1)$, let vectors $(y_k, v_{k + 1}, x_{k + 1})_{k \ge 1}$ and scalars sequence $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ be generated by R-WAPG (Definition \ref{def:wapg}). 
         Define recursively for all $k\ge1$ by 
@@
     \begin{proof}  
-        Recall the stepwise convergence theorem, since the choice of $\gamma, \hat \gamma$ is arbitrary choices for the theorem, we choose $\gamma = \rho_{k - 1} L \alpha_{k - 1}^2 > 0, \hat \gamma = L \alpha_k^2 > 0$ at each step.
-        Because $\alpha_k \in(0, 1)$ by Observation \ref{obs:r-wapg-observation-1}, we can use Proposition \ref{prop:stepwise-lyapunov}: 
+        Recall the stepwise convergence theorem, since the choice of $\gamma, \hat \gamma$ is satisfies is strictly positive and for $i=2, 3, \cdots, k$, by Definition \ref{def:wapg} it has $\gamma = \rho_{i - 1} L \alpha_{i - 1}^2 > 0, \hat \gamma = L \alpha_i^2 > 0$ at each step, with the base case $i = 1$: $\gamma \in (0, L], \hat \gamma = (1 - \alpha_1)\gamma + \mu \alpha_1$.
+        Since $\alpha_i \in(0, 1)$ for all $i = 1, \cdots, k$, because of Observation \ref{obs:r-wapg-observation-1}, we can use Proposition \ref{prop:stepwise-lyapunov}, to show that for all $k \ge 1$:
         {\small
@@
         }
-        Additionally, the algorithm converges by considering $R_k$: 
+        Additionally, for all $k \ge 1$ the algorithm converges by considering $R_{k + 1}$: 
         \begin{align*}
@@
     Following a similar pattern, Proposition \ref{prop:wagp-st-form}, \ref{prop:wagp-st-form} states two more equivalent representations under R-WAPG intermediate form which are formulated as Definition \ref{def:r-wapg-st-form}, \ref{def:r-wapg-momentum-form}.
+    Proposition \ref{prop:wagp-convergence} applies to all these equivalent forms.
 
@@
     \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
-        For all $k\ge 0$, iterates $(w_k, y_k, x_{k + 1}, z_{k + 1})$ satisfies recursively that: 
+        Given any initial $(x_1, v_1)$, and a sequence $(\tau_k)_{k \ge 1}, (\xi_k)_{k \ge 1}$ such that for all $k \ge 1$ $\tau_k \in (0, 1), \xi_k \in (0, 1)$. 
+        for all $k\ge 1$, iterates $(y_k, z_{k + 1}, x_{k + 1})_{k \ge 1}$ satisfies recursively that: 
         \begin{align*}
@@
         \end{align*}
-        If $1 + \xi_k + \tau_k = L\delta_k, \tau_k \neq 0$. Then 
+        If $1 + \xi_k + \tau_k = L\delta_k, \tau_k \neq 0\; \forall k \ge 1$. 
+        Then for all $k \ge 1$: 
         $$
-            v_{k + 1} - x_{k + 1} = (1 + \xi_t)^{-1}\tau_t(x_{k + 1} - x_k). 
+            v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}\tau_k(x_{k + 1} - x_k). 
         $$
@@
             Assume $\mu < L$. 
-            Choose any $\gamma_1 \in (0, L]$ as the initial condition for R-WAPG (Definition \ref{def:wapg}) to produce vectors sequence $(y_i)_{i \in \N}, (x_i)_{i \in \N}, (v_i)_{i \in \N}$ and $(\rho_k)_{i \in \N}, (\alpha_k)_{i \in \N}$.
+            Choose any $\gamma_1 \in (0, L], x_1, v_1$ as the initial condition for R-WAPG (Definition \ref{def:wapg}) to produce vectors sequence $(y_k, v_{k + 1}, x_{k + 1})_{k \ge 1}$. 
             Then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge1}$, and for all $k\ge 1$ they are algebraically equivalent to
             \begin{align*}
-                y_k &= 
-                \left(
-                    1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
+                & 
+                y_{k} = 
+                \left(
+                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
                 \right)^{-1}
                 \left(
-                    v_k + 
-                    \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
+                    v_{k} + 
+                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
                 \right), 
                 \\
-                x_{k + 1} &= 
+                & x_{k + 1} = 
                 y_k - L^{-1} \mathcal G_L y_k, 
                 \\
-                v_{k + 1} &= 
+                & v_{k + 1} = 
                 \left(
@@
             \end{align*}
+
         \end{proposition}
         \begin{proof}
+            For all $k \ge 1$, by R-WAPG (Definition \ref{def:wapg}), it has: 
             \begin{align*}
@@
                 \left(
-                    1 + \frac{L\alpha_k^2}{\alpha_k \rho_{k - 1}L\alpha_{k - 1}^2} 
+                    \frac{L\alpha_k^2}{\alpha_k\gamma_k} + 1
                 \right)^{-1}
                 \left(
-                    v_k + \frac{L\alpha_k^2}{\alpha_k \rho_{k - 1}L\alpha_{k - 1}^2} x_k
-                \right)
-                \\
-                &= 
-                \left(
-                    1 + \frac{\alpha_k}{\rho_{k - 1}\alpha_{k - 1}^2}
+                    v_k + \frac{L\alpha_k^2}{\alpha_k \gamma_k} x_k
+                \right)
+                \\
+                &= 
+                \left(
+                    \frac{L\alpha_k}{\gamma_k} + 1
                 \right)^{-1}
                 \left(
-                    v_k + 
-                    \frac{\alpha_k}{\rho_{k - 1}\alpha_{k - 1}^2} x_k
+                    v_k + \frac{L\alpha_k}{ \gamma_k} x_k
                 \right)
@@
                 L\alpha_k^2 &= 
-                (1 - \alpha_k)L\rho_{k- 1}\alpha_{k - 1}^2 + \alpha_k \mu 
+                (1 - \alpha_k)\gamma_k + \alpha_k \mu 
                 \\
@@
                 L \alpha_k^2 - \alpha_k\mu &= 
-                (1 - \alpha_k)L \rho_{k - 1}\alpha_{k - 1}^2
-                \\
-                \iff 
-                \rho_{k - 1}\alpha_{k - 1}^2
+                (1 - \alpha_k)\gamma_k
+                \\
+                \iff 
+                \gamma_k/L
                 &= 
@@
                 \iff 
-                \frac{1}{\rho_{k - 1}\alpha_{k - 1}^2}
+                L/\gamma_k
                 &= 
@@
                 \iff 
-                \frac{\alpha_k}{\rho_{k - 1}\alpha_{k - 1}^2}
+                L\alpha_k/\gamma_k
                 &= 
@@
             \end{align*}
-            On the third $\iff$, we can assume $\alpha_k \neq \mu/L$ because $\alpha_k = \mu/L$ is impossible. 
-            For contradiction, assume $a_k = \mu/L$. 
-            Then
+            On the third $\iff$, we can assume $\alpha_k \neq \mu/L\; \forall k \ge 2$ because if $\alpha_k = \mu/L$ were impossible, it then has
             \begin{align*}
@@
             \end{align*}
-            Which contradict $\alpha_{k - 1} \in (0, 1)$. 
-            For $v_{k + 1}$ considers 
+            Which contradict $\alpha_{k - 1} \in (0, 1)\; \forall k \ge 2$ because $\alpha_1 \in (0, 1)$ is given to satisfy the condition in the base case, and $\alpha_k \in (0, 1)\; \forall k \ge 2$ by justifications in Observation \ref{obs:r-wapg-observation-1}.
+            \\
+            For all $k \ge 1$, $v_{k + 1}$ has: 
             \begin{align*}
@@
                 - \alpha_k\hat \gamma_{k + 1}^{-1}\mathcal G_L y_k
-                \\
-                &= 
-                \left(
-                    1 + \frac{\alpha_k\mu}{(1 -\alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2}
-                \right)^{-1}
-                \left(
-                    v_k + 
-                    \frac{\alpha_k\mu}{(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2} y_k
-                \right)
-                - \frac{1}{L\alpha_{k}}\mathcal G_L y_k
+                % \\
+                % &= 
+                % \left(
+                %     1 + \frac{\alpha_k\mu}{(1 -\alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2}
+                % \right)^{-1}
+                % \left(
+                %     v_k + 
+                %     \frac{\alpha_k\mu}{(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2} y_k
+                % \right)
+                % - \frac{1}{L\alpha_{k}}\mathcal G_L y_k
                 \\
@@
             Going from the left to the right of the second equality, we substitute $\hat \gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \mu\alpha_k$. 
-            Going from the left to right of the second last equality, we made the substitution $\hat \gamma_{k + 1} = L \alpha_k^2$, and $\gamma_k = \rho_{k - 1}L \alpha_{k - 1}^2$. 
-            To arrive at the last equality, we considered substituting the denominator by the definition for $\hat\gamma_{k + 1}$. 
-            \begin{align*}
-                (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2
+            At the end, recall that for all $k \ge 1$, it has $\hat \gamma_{k + 1} = L \alpha_k^2 = (1 - \alpha_k)\gamma_k + \alpha_k \mu$, so: 
+            \begin{align*}
+                (1 - \alpha_k)\gamma_k
                 &= 
@@
             This form doesn't have $\rho_k, \gamma_k, \hat \gamma_k$ in it. 
-            Finally, to see the inequality, consider the fact that $\rho_k \in [0, 1]$ so it has: 
-            \begin{align*}
-                \hat \gamma_{k + 1} = L\alpha_k^2 = (1 - \alpha_k)\rho_{k - 1}L \alpha_{k - 1}^2 + \alpha_k \mu 
-                \le (1 - \alpha_k)L \alpha_{k - 1}^2 + \alpha_k \mu. 
-            \end{align*}
-            The only auxiliary sequence it needs is $\alpha_k$, which directly links to the convergence rate of the algorithm. 
         \end{proof}
-
         \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
-            Given any initial $\alpha_1 \in (0, 1)$, $(x_1, y_1)$ or equivalently $(x_1, v_1), (y_1, v_1)$. 
+            Given any $\gamma_1 \in (0, L]$, $(x_1, v_1)$. 
             Assume $\mu < L$. 
-            The algorithm generate sequence of vector iterates $(x_k, v_k, y_k)_{k \ge 1}$ by the procedures: 
-            \begin{align*}
-                & y_k = 
-                \left(
-                    1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
+            Define 
+            \begin{align*}
+                \alpha_1 = \frac{1}{2}\left(
+                    \frac{\mu}{L} - \frac{\gamma_1}{L} + 
+                    \sqrt{
+                        \left(
+                            \frac{\gamma_1}{L} - \frac{\mu}{L}
+                        \right)^2 + 
+                        \frac{4\gamma_1}{L}
+                    }
+                \right). 
+            \end{align*}
+            For $k = 1, 2, \cdots $, the algorithm generates sequence of vector iterates $(y_{k}, v_{k + 1}, x_{k + 1})_{k \ge 1}$ and auxiliary sequence $(\alpha_{k + 1}, \rho_k)_{k \ge 1}$ by the procedures:
+            \begin{align*} 
+                & y_{k} = 
+                \left(
+                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
                 \right)^{-1}
                 \left(
-                    v_k + 
-                    \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
-                \right), 
+                    v_{k + 1} + 
+                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
+                \right)
                 \\
@@
                 \\
-                & \alpha_{k + 1} = 
+                & \alpha_{k + 1} := 
                 \frac{1}{2}\left(
@@
         \end{definition}
-
         \begin{proposition}[Second equivalent representation of R-WAPG]\label{prop:wagp-st-form}\;\\
-            Let iterates $(x_k, v_k, y_k)_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge1}$ be given by Definition \ref{def:r-wapg-intermediate}. 
-            Then for all $k \ge 1$, iterate $(v_k)_{k \ge 1}, (x_k)_{k \ge 1}, (y_k)_{k \ge1}$ are algebraically equivalent to: 
-            \begin{align*}
-                y_k &= 
-                \left(
-                    1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
+            Let iterates $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge1}$ be given by Definition \ref{def:r-wapg-intermediate}. 
+            Then for all $k \ge 1$, iterate $y_k, x_{k + 1}, v_{k + 1}$
+            satisfy: 
+            \begin{align*}
+                y_{k} &= 
+                \left(
+                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
                 \right)^{-1}
                 \left(
-                    v_k + 
-                    \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
+                    v_{k} + 
+                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
                 \right), 
@@
         \begin{proof}
-            From Definition \ref{def:r-wapg-intermediate}, set 
-            \begin{align*}
-                \tau_k &= \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}, 
-                \\
+            From Definition \ref{def:r-wapg-intermediate}, define $(\tau_k, \xi_k, \delta_k)_{k \ge 1}$ in Proposition \ref{prop:abs-st-form} to be
+            \begin{align*}
+                (\forall k \ge 1) \quad \tau_k &= \frac{L(1 - \alpha_k)}{L\alpha_k - \mu},
+                \\
+                (\forall k \ge 1)\quad 
                 \xi_k &= \frac{\mu}{L \alpha_k - \mu},
                 \\
-                (1 + \xi_k)^{-1}\delta_k &= \frac{1}{L\alpha_k}
-                \iff L \delta_k = \frac{1 + \xi_k}{\alpha_k}. 
+                (\forall k \ge 1)\quad 
+                \delta_k &\defeq \frac{1 + \xi_k}{L\alpha_k}. 
             \end{align*}
             We claim that these parameters satisfy $L\delta_k = 1 + \tau_k + \xi_k$. 
-            Hence $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}(x_{k + 1} - x_k)$. 
-            To see, we have 
+            To see, we have forall $k\ge 1$: 
             \begin{align*}
@@
             \end{align*}
-            Next
-            \begin{align*}
-                1 + \tau_k + \xi_k &= 
-                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
-                + \frac{\mu}{L \alpha_k - \mu}
-                \\
-                &= 
-                1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
-                \\
-                &= 
-                \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
-                \\
-                &= \frac{L}{L\alpha_k - \mu}. 
-            \end{align*}
+            Next, it also has for all $k \ge 1$: 
+            \begin{align*}
+                \frac{1 + \xi_k}{\alpha_k}
+                &= 
+                \frac{1 + \frac{\mu}{L\alpha_k - \mu}}{\alpha_k}
+                = 
+                \frac{\frac{L\alpha_k - \mu + \mu}{L \alpha_k - \mu}}{\alpha_k}
+                = 
+                \frac{L}{L\alpha_k - \mu}.
+            \end{align*}
+            Hence,  $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}(x_{k + 1} - x_k)\; \forall k \ge 1$ by Proposition \ref{prop:abs-st-form}.
             Therefore, substituting it gives: 
@@
         \end{proof}
+        \begin{remark}
+            We note that $x_1, v_1, y_1$ may not satisfy the inequalities since, 
+        \end{remark}
     \begin{definition}[R-WAPG similar triangle form]\label{def:r-wapg-st-form} \; \\
-        Given any initial $\alpha_1 \in (0, 1)$, $(x_1, v_1)$. 
+        Given any initial $L \in (0, L]$, $(x_1, v_1)$. 
         Assume $\mu < L$.
-        The algorithm generates sequences of vector iterates $(x_k, v_k, y_k)_{k \ge 2}$ by the procedures: 
+        Define $\alpha_1$ by 
+        \begin{align*}
+            \alpha_1 = \frac{1}{2}\left(
+                \frac{\mu}{L} - \frac{\gamma_1}{L} + 
+                \sqrt{
+                    \left(
+                        \frac{\gamma_1}{L} - \frac{\mu}{L}
+                    \right)^2 + 
+                    \frac{4\gamma_1}{L}
+                }
+            \right). 
+        \end{align*}
+        For $k = 1, 2, \cdots $, the algorithm generates sequences of vector iterates $(y_k, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by the procedures: 
         \begin{align*}
@@
         Let sequence $(\alpha_k, \rho_k)_{k \ge 1}$ and iterates $(x_k, v_k, y_k)_{k\ge 1}$ given by R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}). 
-        Then for all $k \ge 1$, the iterates are algebraically equivalent to: 
+        Then for all $k \ge 1$, the iterates $(x_{k + 1}, y_{k + 1})_{k \ge 1}$ are algebraically equivalent to: 
         \begin{align*}
@@
             x_{k + 1} + 
-            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
+            \frac{\rho_k\alpha_k(1 - \alpha_k)}
+            {\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
+        \end{align*}
+        If in addition, $v_1 = x_1$ then 
+        \begin{align*}
+            y_1 = \left(
+                1 + \frac{L - L \alpha_1}{L\alpha_1 - \mu}
+            \right)^{-1}\left(
+                v_1 + \left(
+                    \frac{L - L \alpha_1}{L \alpha_1 - \mu}
+                \right)x_1
+            \right) = x_1. 
         \end{align*}
@@
         \begin{align*}
+            (\forall k \ge 1) \quad 
             \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
@@
     \begin{proof}
-        Start by considering the update rule for $v_k$ from the similar triangle form of WAPG which is: 
+        Start by considering the update rule for $v_k$ from the Definition \ref{def:r-wapg-st-form} which has for all $k \ge 1$: 
         \begin{align*}
@@
         \end{align*}
-        Next, we simplify the update for the iterates $y_{k}$ by the similar triangle form of R-WAPG. 
+        Next, we simplify the update $y_{k}$ by Definition \ref{def:r-wapg-st-form} for all $k \ge 1$: 
         \begin{align*}
@@
         \end{align*}
-        Now considering substituting $v_{k + 1}$ into $y_{k + 1}$ so it has: 
+        We have $y_1 = x_1$ when $v_1 = x_1$ because substituting $v_1 = x_1$ for how $y_1$ is defined it has: 
+        \begin{align*}
+            y_1 &= (L - \mu)^{-1}(L(\alpha_1 - \mu)x_1 + (L - L\alpha_1)x_1)
+            \\
+            &= (L - \mu)^{-1}(L(\alpha_1 - \mu)x_1 + (L - L \alpha_1)x_1)
+            \\
+            &= (L - \mu)^{-1}((L - \mu)x_1) = x_1. 
+        \end{align*}
+        Now substituting $v_{k + 1}$ into $y_{k + 1}$ so it has for all $k\ge 1$ : 
         {\small
@@
             \left(
-                (L - \mu)x_{k + 1} + (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
+                (L\alpha_{k + 1} - \mu)x_{k + 1} + (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
             \right)
@@
         }
-
         The coefficient for $(x_{k + 1} - x_k)$ needs some works to formulate it without the parameter $\mu, L$. 
@@
         When $\mu = 0$, things simplify. 
-        Consider that $\alpha_{k +1}^2 = (1 - \alpha_{k + 1})\rho_k\alpha_k^2$. 
+        Consider that $\forall k \ge 1: \alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_k\alpha_k^2$. 
         \begin{align*}
@@
     \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
-        Initialize any $\alpha_1 \in (0, 1)$. 
-        The algorithm generates iterates $(v_k, x_k, y_k)$ and auxiliary sequence $(\rho_k)_{k \ge0}$ by the following procedures: 
-        \begin{align*}
-            \text{find }& \rho_{k - 1}: 0 < \rho_{k - 1} < \alpha_{k - 1}^{-2},
-            \\
-            \alpha_k &= 
+        Let $y_1 = x_1$. 
+        Given any $\gamma_1 \in (0, L]$, initialize any $\alpha_1 \in (0, 1)$ by: 
+        \begin{align*}
+            \alpha_1 = \frac{1}{2}\left(
+                \frac{\mu}{L} - \frac{\gamma_1}{L} + 
+                \sqrt{
+                    \left(
+                        \frac{\gamma_1}{L} - \frac{\mu}{L}
+                    \right)^2 + 
+                    \frac{4\gamma_1}{L}
+                }
+            \right). 
+        \end{align*}
+        For $k = 1, 2, \cdots $, the algorithm generates iterates $x_{k + 1}, y_{k + 1}$ and auxiliary sequence $(\rho_k)_{k \ge 1}, (\alpha_k)_{k \ge 2}$ by the procedures: 
+        \begin{align*}
+            & x_{k + 1} = y_k - L^{-1}\mathcal G_Ly_k, 
+            \\
+            & 
+            y_{k + 1} = 
+            x_{k + 1} + 
+            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k), 
+            \\
+            & \text{find } \rho_{k}: 0 < \rho_{k} < \alpha_{k}^{-2}, 
+            \\
+            & 
+            \alpha_{k + 1} = 
             \frac{1}{2}\left(
-            \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
-            +
-            \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
-            \right), 
-            \\
-            x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
-            \\
-            y_{k + 1} &= 
-            x_{k + 1} + 
-            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
+                \frac{\mu}{L} - \rho_{k}\alpha_{k}^2 
+                +
+                \sqrt{(\rho_{k}\alpha_{k}^2 - \mu/L)^2 + 4\rho_{k}\alpha_{k}^2}
+            \right). 
         \end{align*}
@@
         $$
-        \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}} 
+            (\forall k \ge 1)\quad \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}} 
             = \alpha_{k + 1}(\alpha_k^{-1} - 1).  
         $$
-
     \end{definition}
     \begin{remark}
-        \textcolor{red}
-        {
-        There exists a choice of $\rho_k \in (0, 1], \mu = 0$ such that the above algorithm is equivalent to Chambolle, Dossal 2015 \cite{chambolle_convergence_2015}. 
-        When $\rho_k = 1$, this becomes just FISTA \cite{beck_fast_2009}. 
-        When $L > \mu > 0$, then choosing $\rho_k = 1$ yields equation 
-        \begin{align*}
-            L \alpha_{k + 1}^2 = (1- \alpha_{k + 1})L \alpha_k^2 + \alpha_{k + 1} \mu. 
-        \end{align*}
-        Here, if we assume sequence $\alpha_k$ is constant, then $\alpha_k = \sqrt{\mu/L}$ is a solution to the above iterative equation. 
-        Substituting it back to the momentum form of R-WAPG, we recover the V-FISTA algorithm, which appears as (10.7.7) in Beck's Book \cite{beck_first-order_2017}. 
-        }
+        % \textcolor{red}
+        % {
+        % There exists a choice of $\rho_k \in (0, 1], \mu = 0$ such that the above algorithm is equivalent to Chambolle, Dossal 2015 \cite{chambolle_convergence_2015}. 
+        % When $\rho_k = 1$, this becomes just FISTA \cite{beck_fast_2009}. 
+        % When $L > \mu > 0$, then choosing $\rho_k = 1$ yields equation 
+        % \begin{align*}
+        %     L \alpha_{k + 1}^2 = (1- \alpha_{k + 1})L \alpha_k^2 + \alpha_{k + 1} \mu. 
+        % \end{align*}
+        % Here, if we assume sequence $\alpha_k$ is constant, then $\alpha_k = \sqrt{\mu/L}$ is a solution to the above iterative equation. 
+        % Substituting it back to the momentum form of R-WAPG, we recover the V-FISTA algorithm, which appears as (10.7.7) in Beck's Book \cite{beck_first-order_2017}. 
+        % }
     \end{remark}

### 2024-12-19 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w< writing the draft paper really

@@
     \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
-    The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{alto@mail.ubc.ca}.}~Xianfu Wang
+    The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{alto@mail.ubc.ca}.}~ and ~Xianfu Wang
     \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
     The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{shawn.wang@ubc.ca}.}
-    and ~Heinz H. Bauschke~
-    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
-    The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{heinz.bauschke@ubc.ca}.
-    }
+    % and ~Heinz H. Bauschke~
+    % \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
+    % The University of British Columbia, Kelowna, BC Canada V1V 1V7. E-mail:  \texttt{heinz.bauschke@ubc.ca}.
+    % }
 }
@@
 \section{Introduction}
-    \subsection{Literature reviews}
+    Suppose we are minimizing a differentiable convex function $F$ for simplicity. 
+    In addition, assuming the function is $\RR^n$ so it's full domain and $F$ is Lipschitz smooth meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$.
+    \par 
+    A good choice of a minimization algorithm is the Nesterov's acceleration schemes that originally proposed in 1983 \cite{nesterov_method_1983}.
+Initializing $x_0 = y_0$ the algorithm finds $(x_k)_{k \ge 1}$ and $t_1 = 1$ by
+    \begin{align*}
+        & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
+        \\
+        & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
+        \\
+        & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
+        \\
+        & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
+    \end{align*}
+    It's well known that if the minimizer $x^*$ exists, $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, faster than the gradient descent method which is $\mathcal O(1/k)$, and it's optimal.
+    See Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018}. 
+    However, everything is not sunshine and rainbow because the above scheme is associated with an issue. 
+    When $F$ is $\mu > 0$ strongly convex, the algorithm oscillates and converges sub-linearly, making it worse than gradient descent. See page 9 of Su et al. \cite{su_differential_2016}. 
+    \par
+    This issue motivated a vast amount of literatures aims at improving, interpreting, and extending this method. 
+    Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
+    Beck and Toubelle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it $\mathcal O(1/k^2)$ convergence rate is kept and it performs empirically better. 
+    See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm. 
+    \par
+    Inspired by prior works and the method of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, we present to you an alternative to restarting that performs well empirically and along with it, a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG).
+    The R-WAPG has a convergence claim of $F(x_k)- F(x^*)$ for a much flexible choice of $(\theta_t)_{t \ge 1}$ and the descriptive power to cover several variants of FISTA in the literatures.
+
     \subsection{Contributions}
-        Our contributions are two folds.
-
-        % We present a theoretical unification through the formulation of ``Relaxed weak accelerated proximal gradient algorithm (R-WAPG)'' which we invented. 
-        % It unifies convergence claim for accelerated method for the strongly convex objective and Lipschitz smooth but non-strongly convex case, and it relaxes the conditions on the momentum sequence.
-
-        % We connect the theories and practice by pointing out one practical exploits inspired the convergence proof of the algorithm which we called ``Spectral Momentum''. 
-        % Numerical experiments are conducted to illustrate the theoretical convergence of R-WAPG and the performance of Spectral Momentum in with applications. 
-        % We do net yet have a proof for the convergence of the algorithm in general.
+        Our contributions are two folds theoretical and practical. 
+        \par
+        Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''. 
+        The choices for $\theta_k$ varies. 
+        In Chamboolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ gives strong weak convergence of the iterates $x_k$ in Hilbert space. 
+        In Beck \cite{beck_first-order_2017}, it has constant $\theta_t = (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa = \mu/L$. 
+        \par
+        Firstly, we relaxed the traditional choice of the sequence $\theta_k$ and showed an upper bound of the optimal gap. 
+        Let $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$, given any $\gamma_1 \in (0, L]$ and define $\alpha_1$ by 
+        \begin{align*}
+            \alpha_1 = \frac{1}{2}\left(
+                \frac{\mu}{L} - \frac{\gamma_1}{L} + 
+                \sqrt{
+                    \left(
+                        \frac{\gamma_1}{L} - \frac{\mu}{L}
+                    \right)^2 + 
+                    \frac{4\gamma_1}{L}
+                }
+            \right). 
+        \end{align*}
+        We define $\alpha_k$ for $k \ge 2$ by: 
+        \begin{align*}
+            &\alpha_k \in (0, 1), 
+            \\
+            & 0 < \rho_k \alpha_k^2 < 1, 
+            \\
+            &\alpha_{k + 1} = 
+            \frac{1}{2}\left(
+                \frac{\mu}{L} - \rho_{k}\alpha_{k}^2 
+                +
+                \sqrt{(\rho_{k}\alpha_{k}^2 - \mu/L)^2 + 4\rho_{k}\alpha_{k}^2}
+            \right). 
+        \end{align*}
+        Our first main results shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed (Definition \ref{def:wapg}), we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
+        \begin{align*}
+            \mathcal O\left(
+                \left(
+                    \prod_{i = 1}^{k - 1} \max(1, \rho_{k})
+                \right)
+                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
+            \right). 
+        \end{align*}
+        Our second main results shows that there exists $\rho_k > 1$ such that our R-WAPG reduces perfectly to the variants proposed in Chambolle Dossal \cite{chambolle_convergence_2015}. 
+        And when $\rho_k = 1, \rho > 0$, R-WAPG reduces perfect to V-FISTA by Beck \cite{beck_first-order_2017} and it produces convergence claim consistent with the literatures. 
+        \par
+        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG''. 
+        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$.
+        We conducted ample amount of numerical experiments to show that it has favorable convergence rate in practice, and it behaves similarly to the FISTA with monotone restart. 
+    \subsection{Organizations}
 
 \section{Preliminaries}
-    Throughout Section 1, 2, 3, we assume the problem of types $F = f + g$ where $f: \RR \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: Q \rightarrow \overline \RR$ is convex.
-    We consider optimization problem of the form
-    \begin{align*}
-        \min_x \left\lbrace
-            F(x) \defeq f(x) + g(x)
-        \right\rbrace. 
-    \end{align*}
-    To start we define the following quantities
-    \begin{enumerate}
-        \item The proximal gradient model function: 
-        $$
+    Throughout, we assume the problem of types $F = f + g$ where $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: Q \rightarrow \overline \RR$ is convex. 
+    We consider optimization problem: $\min_x \left\lbrace F(x) \defeq f(x) + g(x)\right\rbrace$.
+    Fix arbitrary $y \in \RR^n$, define
+    \begin{align*}
         \widetilde{\mathcal M}^{L^{-1}}
@@
         g(x) + f(y) + \langle \nabla f(y), x - y\rangle 
-            + \frac{L}{2}\Vert x - y\Vert^2. 
-        $$
-        \item The proximal point model function: 
-        $$
-            \mathcal M^{L^{-1}}(x; y) := F(x) + \frac{L}{2}\Vert x - y\Vert^2
-        $$
-        \item The proximal gradient operator $T_L = [I + L^{-1}\partial g]\circ [I - L^{-1}\nabla f]$.
-Since $L$ is fixed throughout, the subscript may be omitted and become $T$ instead to make the notations simpler.
-    \end{enumerate}
-    To state the following lemma, we define the Bregman divergence of $f$ to be 
+        + \frac{L}{2}\Vert x - y\Vert^2, 
+        \\
+        \mathcal M^{L^{-1}}(x; y) := F(x) + \frac{L}{2}\Vert x - y\Vert^2, 
+    \end{align*}
+    and the proximal gradient operator $T_L = [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f]$. 
+    Define the Bregman divergence of $f$: 
     \begin{align*}
@@
     \end{align*}
-
+    The lemma follows explains equates between $\mathcal M(\cdot; y), \widetilde{\mathcal M}(\cdot; y)$. 
     \begin{lemma}[Proximal gradient envelope] 
@@
     \end{proof}
-
     \subsection{Proximal inequality}
@@
         \begin{align*}
-            F(x) - F(Ty) - \langle L(y - Ty), x - Ty\rangle
-            &\ge  D_f(x, y). 
+            F(x) - F(T_Ly) - \langle L(y - T_Ly), x - y\rangle
+            - L\Vert y - T_L y\Vert^2
+            - D_f(x, y)
+            &\ge  
+            0. 
+        \end{align*}
+        When $f$ is $\mu \ge 0$ strongly convex, it implies that 
+        \begin{align*}
+            F(x) - F(T_Ly) - \langle L(y - T_Ly), x - y\rangle
+            - \frac{L}{2}\Vert y - T_L y\Vert^2
+            - \frac{\mu}{2}\Vert x - y\Vert^2
+            &\ge  
+            0.
         \end{align*}
@@
     \begin{proof}
-        $\widetilde {\mathcal M}(\cdot; x)$ is $L$ strongly convex with minimizer $Ty$
+        Observe that the function $\widetilde {\mathcal M}(\cdot; x)$ is $L$ strongly convex with minimizer $T_Ly$. 
+        For all $x \in \RR^n$, it has quadratic growth condition at its minimizer $T_Ly$ which gives these equivalent inequalities: 
         {\small
@@
             \widetilde{\mathcal M}^{L^{-1}}(x; y) - 
-            \widetilde{\mathcal M}^{L^{-1}}(Ty; y)
+            \widetilde{\mathcal M}^{L^{-1}}(T_Ly; y)
             - 
-            \frac{L}{2}\Vert x - Ty\Vert^2
+            \frac{L}{2}\Vert x - T_Ly\Vert^2
             &\ge 
@@
             \right) - 
-            \mathcal M^{L^{-1}}(Ty; y) 
+            \mathcal M^{L^{-1}}(T_Ly; y) 
             - 
-            \frac{L}{2}\Vert x - Ty\Vert^2
+            \frac{L}{2}\Vert x - T_Ly\Vert^2
             &\ge 0
@@
                 - 
-                \mathcal M^{L^{-1}}(Ty; y)
+                \mathcal M^{L^{-1}}(T_Ly; y)
             \right)
@@
             D_f(x, y) 
-            - \frac{L}{2}\Vert x - Ty\Vert^2
+            - \frac{L}{2}\Vert x - T_Ly\Vert^2
             &\ge 0
@@
             \left(
-                F(x) - F(Ty) 
+                F(x) - F(T_Ly) 
                 + 
                 \frac{L}{2}\Vert x - y\Vert^2 - 
-                \frac{L}{2}\Vert Ty - y\Vert^2
+                \frac{L}{2}\Vert T_Ly - y\Vert^2
             \right)
@@
             \left(
-                F(x) - F(Ty) 
+                F(x) - F(T_Ly) 
                 + 
@@
                 \left(
-                    \Vert x - Ty + Ty - y\Vert^2
+                    \Vert x - T_Ly + T_Ly - y\Vert^2
                     - 
-                    \Vert y - Ty\Vert^2
+                    \Vert y - T_Ly\Vert^2
                 \right)
@@
                 \left(
-                    \Vert x - Ty\Vert^2 + 
-                    2\langle x - Ty, Ty - y\rangle
+                    \Vert x - T_Ly\Vert^2 + 
+                    2\langle x - T_Ly, T_Ly - y\rangle
                 \right)
@@
             \left(
-                F(x) - F(Ty) + \frac{L}{2}\Vert x - Ty\Vert^2 
-                - L\langle  x - Ty, y - Ty\rangle
+                F(x) - F(T_Ly) + \frac{L}{2}\Vert x - T_Ly\Vert^2 
+                - L\langle  x - T_Ly, y - T_Ly\rangle
             \right)
@@
             \iff 
-            F(x) - F(Ty)
-            - \langle L(y - Ty), x - Ty\rangle
+            F(x) - F(T_Ly)
+            - \langle L(y - T_Ly), x - T_Ly\rangle
             - D_f(x, y) 
@@
         }
-    \end{proof}
-    \begin{remark}
-        In our proof, we may use the following alternative representation of the above inequality which is 
-        \begin{align*}
-            F(x) - F(Ty) - \langle L(y - Ty), x - Ty\rangle - D_f(x, y) &\ge 0
-            \\
-            \iff
-            F(x) - F(Ty)
-            - \langle L(y - Ty), x - y + y - Ty\rangle - D_f(x, y) 
+        Continuing, it has: 
+        \begin{align*}
+            F(x) - F(T_Ly) - \langle L(y - T_Ly), x - T_Ly\rangle - D_f(x, y) &\ge 0
+            \\
+            \iff
+            F(x) - F(T_Ly)
+            - \langle L(y - T_Ly), x - y + y - T_Ly\rangle - D_f(x, y) 
             &\ge 0
@@
             \iff
-            F(x) - F(Ty)
-            - \langle L(y - Ty),x - y \rangle
-            - L\Vert y - Ty\Vert^2
+            F(x) - F(T_Ly)
+            - \langle L(y - T_Ly),x - y \rangle
+            - L\Vert y - T_Ly\Vert^2
             - D_f(x, y) 
@@
             \implies 
-            F(x) - F(Ty)
-            - \langle L(y - Ty),x - y \rangle
-            - \frac{L}{2}\Vert y - Ty\Vert^2
+            F(x) - F(T_Ly)
+            - \langle L(y - T_Ly),x - y \rangle
+            - \frac{L}{2}\Vert y - T_Ly\Vert^2
             - D_f(x, y) 
@@
             \implies
-            F(x) - F(Ty)
-            - \langle L(y - Ty),x - y \rangle
-            - \frac{L}{2}\Vert y - Ty\Vert^2
+            F(x) - F(T_Ly)
+            - \langle L(y - T_Ly),x - y \rangle
+            - \frac{L}{2}\Vert y - T_Ly\Vert^2
             - \frac{\mu}{2}\Vert x - y\Vert^2
@@
         \end{align*}
-
-    \end{remark}
+        Going from the second last inequality to the last inequality, we used the fact that $f$ is strongly convex hence for all $x, y$, it's true that $D_f(x, y) \ge \mu/2 \Vert x - y\Vert^2$. 
+    \end{proof}
 
 \section{Stepwise formulation of weak accelerated proximal gradient}
-    In this section, we introduce the following new quantities and their notations. 
-    It's there to make the notations simpler and easier to follow for the proofs that will come later. 
-    The algorithm is parameterized by the sequence $y_k, x_k$. 
-    We define for all $k \ge 0$ the following quantities: 
+    This entire section is building up the R-WAPG algorithm which is described in the Definition \ref{def:wapg} of the next section. 
+    \par 
+    Definition \ref{def:stepwise-wapg} which describes what happens at a single iteration of the R-WAPG algorithm. 
+    It defines a procedures of generating $x_{k + 1}, v_{k + 1}$ given any $x_k, v_k$. 
+    Propsotion \ref{prop:stepwise-lyapunov} states the inequality that describes a decreasing quantity that involves $F(x_k), F(x_{k + 1})$ at each single iteration.
+
     \begin{assumption}
@@
         Observe that by convexity of $F$, $\epsilon_k \ge 0$ for all $x_k, L > 0$. 
-        To see, consider the last inequality in the remark of Theorem \ref{thm:prox-grad-ineq} with $y = y_k, x = x_k$: 
+        To see, use Theorem \ref{thm:prox-grad-ineq} and let $y = y_k, x = x_k$ which gives: 
         \begin{align*}
@@
             \\
-            \implies 
+            \iff 
             F(x_k) - F(T_Ly_k)
@@
         Fix any $k \in \mathbb Z$. 
-        For any $(v_k, x_k), \alpha_k \in (0, 1), \gamma > 0$, let $\hat \gamma$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ be given by: 
-        \begin{align*}
-            \hat \gamma &= (1 - \alpha_k)\gamma + \mu \alpha_k, 
+        For any $(v_k, x_k), \alpha_k \in (0, 1), \gamma_k > 0$, let $\hat \gamma_{k + 1}$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ be given by: 
+        \begin{align*}
+            \hat \gamma_{k + 1} &= (1 - \alpha_k)\gamma_k + \mu \alpha_k, 
             \\
             y_k &= 
-            (\gamma + \alpha_k \mu)^{-1}(\alpha_k \gamma v_k + \hat\gamma x_k), 
+            (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
             \\
@@
             \\
-            v_{k + 1} &= \hat\gamma^{-1}
-            (\gamma(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
+            v_{k + 1} &= \hat\gamma^{-1}_{k + 1}
+            (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
             \\
@@
             y_k - v_k &= 
-            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k),
+            \frac{\hat \gamma_{k + 1}}{\alpha_k \gamma_k}(x_k - y_k),
             \\
@@
             y_k - x_k &= 
-            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
+            \frac{\alpha_k \gamma_k}{\gamma_k + \alpha_k \mu}(v_k - x_k). 
         \end{align*}
@@
             y_k - v_k &= 
-            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k)
-            \\
-            \iff 
-            -(\alpha_k \gamma\hat \gamma^{-1} + 1)y_k
-            &= 
-            - \alpha_k \gamma \hat \gamma^{-1}v_k - x_k
+            \frac{\hat \gamma_{k + 1}}{\alpha_k \gamma_k}(x_k - y_k)
+            \\
+            \iff 
+            -(\alpha_k \gamma_k \hat \gamma^{-1}_{k + 1} + 1)y_k
+            &= 
+            - \alpha_k \gamma_k \hat \gamma^{-1}_{k + 1}v_k - x_k
             \\
@@
             \frac{
-                \alpha_k \gamma \hat \gamma^{-1}v_k + x_k
-            }{1 + \alpha_k \gamma \hat \gamma^{-1}}
-            \\
-            &=  
-            \frac{\alpha_k \gamma v_k + \hat \gamma x_k}{\gamma + \alpha_k \mu}.
-        \end{align*}
-        On the first equality (Q1), we multiplied both side of the equation by $\hat\gamma/\alpha_k \gamma$ and then group $y_k$ on the LHS. 
-        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma$, leaving the numerator $\hat \gamma + \alpha_k \gamma = \gamma + \alpha_k \mu$. 
-        We used the definition of $\hat \gamma$ here. 
+                \alpha_k \gamma_k \hat \gamma_{k + 1}^{-1}v_k + x_k
+            }{1 + \alpha_k \gamma_k \hat \gamma_{k + 1}^{-1}}
+            \\
+            &=  
+            \frac{\alpha_k \gamma_k v_k + \hat \gamma_{k + 1} x_k}{\gamma_k + \alpha_k \mu}.
+        \end{align*}
+        On the first equality (Q1), we multiplied both side of the equation by $\hat\gamma_{k + 1}/\alpha_k \gamma_k$ and then group $y_k$ on the LHS. 
+        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma_{k + 1}$, leaving the numerator $\hat \gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$. 
+        We used the definition of $\hat \gamma_{k + 1}$ here. 
         To see the second equality (Q2), consider: 
         \begin{align*}
-            y_k &= (\gamma + \alpha_k \mu)^{-1}(\alpha_k \gamma v_k + \hat\gamma x_k)
+            y_k &= (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k)
             \\
@@
             y_k - x_k &= 
-            (\gamma + \alpha_k \mu)^{-1}
-            (\alpha_k \gamma v_k - (\gamma + \alpha_k \mu)x_k + \hat \gamma x_k)
-            \\
-            \iff 
-            (\gamma + \alpha_k \mu)(y_k - x_k)
-            &= 
-            \alpha_k\gamma v_k + 
-            (\hat \gamma - \gamma - \alpha_k \mu) x_k
-            \\
-            &= \alpha_k \gamma v_k - \alpha_k \gamma x_k 
-            \\
-            &= \alpha_k \gamma(v_k - x_k)
+            (\gamma_k + \alpha_k \mu)^{-1}
+            (\alpha_k \gamma_k v_k - (\gamma_k + \alpha_k \mu)x_k + \hat \gamma_{k + 1} x_k)
+            \\
+            \iff 
+            (\gamma_k + \alpha_k \mu)(y_k - x_k)
+            &= 
+            \alpha_k\gamma _kv_k + 
+            (\hat \gamma_k - \gamma_k - \alpha_k \mu) x_k
+            \\
+            &= \alpha_k \gamma_k v_k - \alpha_k \gamma_k x_k 
+            \\
+            &= \alpha_k \gamma_k(v_k - x_k)
             \\
@@
             y_k - x_k &= 
-            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
-        \end{align*}
-        On the second equality that follows the second $\iff$ we just substituted $\hat\gamma = (1 - \alpha_k)\gamma + \alpha_k \mu$. 
+            \frac{\alpha_k \gamma_k}{\gamma_k + \alpha_k \mu}(v_k - x_k). 
+        \end{align*}
+        On the second equality that follows the second $\iff$ we just substituted $\hat\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$. 
         Therefore, we discover that $x_k, v_k, y_k$ lies on the same line because (Q1) indicates $y_k - v_k$ parallels to $-(y_k - x_k)$ and both vector shares the same head which anchors at $y_k$.
@@
     \begin{proposition}[Stepwise Lyapunov]\label{prop:stepwise-lyapunov}\;\\
-        Fix any integer $k \in \mathbb Z$, for any $v_k, x_k$, let $v_{k + 1}, x_{k + 1}, y_k, v_k, x_k, \hat \gamma$ be given by Definition \ref{def:stepwise-wapg}. 
-        Choose any arbitrary $R_k \in \RR$.
+        Fix any integer $k \in \mathbb Z$.
+        Given any $v_k, x_k$ and $\gamma_k > 0$, invoke Definition \ref{def:stepwise-wapg} to obtain $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}$. 
+        Fix any arbitrary $R_k \in \RR$.
         Define: 
@@
             \frac{1}{2}\left(
-                L^{-1} - \frac{\alpha_k^2}{\hat \gamma}
+                L^{-1} - \frac{\alpha_k^2}{\hat \gamma_{k + 1}}
             \right)\Vert g_k\Vert^2
@@
                 \epsilon_k + R_k + 
-                \frac{\mu\alpha_k\gamma}{2\hat \gamma}
+                \frac{\mu\alpha_k\gamma_k}{2\hat \gamma_{k + 1}}
                 \Vert v_k - y_k\Vert^2
@@
         \begin{align*}
-            F(x_{k + 1}) - F^* + R_{k + 1} + \frac{\hat \gamma}{2}\Vert v_{k + 1} - x^*\Vert^2
+            F(x_{k + 1}) - F^* + R_{k + 1} + \frac{\hat \gamma_{k + 1}}{2}\Vert v_{k + 1} - x^*\Vert^2
             &\le 
@@
             \left(
-                F(x_k) - F^* + R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
+                F(x_k) - F^* + R_k + \frac{\gamma_{k}}{2}\Vert v_k - x^*\Vert^2
             \right). 
@@
     \begin{proof}
+        The proof is a direct proof. 
+        Here we drop the subscript $k$, $k + 1$ on $\gamma_{k}, \hat \gamma_{k + 1}$ because they are fixed throughout the proof and it makes for better readibility! 
+        \par 
+        We started with $F(x_{k + 1}) + R_{k + 1}$ as Equation (1*), and $\hat \gamma/2\Vert v_{k + 1} - x^*\Vert^2$ as (2*). 
+        In the proof that follows, we show (2*) equals to (2.2*). 
+        We added (2*), (2.2*) to produce (3*). 
+        Then we show (3*) equals to (3.1*). 
+        The content of the entire LHS of the conclusion of the claim is conclused in (3.2*). 
+        Going from (3.2*) to (4*) is an inequality which we used Theorem \ref{thm:prox-grad-ineq}. 
+        \par
         Start by considering the first and the third term of the LHS of the inequality that we want to prove. 
@@
         On the last line, we expand the definition of $g_k$ and then used the
-        \hyperref[thm:prox-grad-ineq]{remark of Theorem \ref*{thm:prox-grad-ineq}}. 
+        \hyperref[thm:prox-grad-ineq]{Theorem \ref*{thm:prox-grad-ineq}}. 
         Therefore, we conclude that: 
@@
         }
+        Adding back the $k$, $k + 1$ subscript for $\gamma$, $\hat \gamma$, it's proven. 
     \end{proof}
@@
 \section{Formulation of R-WAPG and its convergence rates}
-    Definition \ref{def:wapg} is an algorithm which generates iterates $(x_k, y_k, v_k)$ and admits potential convergence claim using Proposition \ref{prop:stepwise-lyapunov}. 
-    It is the backbone of multiple accelerated first order method in the literatures which fits all variants under the same convergence claim.
-
-    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
-        \;\\
-        Initialize any $\gamma_1 \in (0, L]$, $(x_1, v_1)$. 
-        Given auxiliary sequences $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ satisfying for all $k \ge 2$ the conditions: 
+    The sole focus of this section is Definition \ref{def:wapg}.
+    It describes the R-WAPG algorithm which generates iterates $(x_k, y_k, v_k)$ and admits potential convergence claim using Proposition \ref{prop:stepwise-lyapunov}. 
+    It introduces the procedures of making the sequence $\alpha_k \in (0, 1)$ which assists with claiming convergence of the algorithm using Proposition \ref{prop:stepwise-lyapunov} by connecting them together.
+    \begin{definition}[R-WAPG sequence]\label{def:rwapg-seq}
+        Assume $0 \le \mu < L$. 
+        For any $\gamma_1 \in (0, L]$, define $\alpha_1 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$. 
+        Then the sequence $(\alpha_{k + 1})_{k \ge 1}, (\rho_k)_{k \ge 1}$ satisfy for all $k \ge 2$
         \begin{align*}
@@
             \\
-            &\rho_k > 0, 
-            \\
-            &L\alpha_k^2 = (1 - \alpha_k)\rho_{k - 1}L \alpha_{k - 1}^2 + \mu \alpha_k , 
-            \\
-            &0 < \rho_k \alpha_k^2 < 1. 
-        \end{align*}
-        With base case $k = 1$ given by $\alpha_1 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$. 
-        The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ such that they satisfy for all $k\ge 1$: 
-        \begin{align*}
-            \gamma_k &:= \left.\begin{cases}
-                \rho_{k -1}L\alpha_{k - 1}^2 & k \ge 2,
-                \\
-                \gamma_1 & k = 1. 
-            \end{cases}\right\rbrace,
-            \\
-            \hat \gamma_{k + 1} &:= L\alpha_k^2, 
-            \\
-            y_k &= 
-            (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
-            \\
-            g_k &= \mathcal G_L y_k, 
-            \\
-            v_{k + 1} &= 
-            \hat\gamma^{-1}_{k + 1}
-            (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
-            \\
-            x_{k + 1} &= T_L y_k. 
+            & 0 < \rho_k \alpha_k^2 < 1, 
+            \\
+            &L\alpha_k^2 = (1 - \alpha_k)\rho_{k - 1}L \alpha_{k - 1}^2 + \mu \alpha_k. 
         \end{align*}
     \end{definition}
-    \begin{observation}
-        Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018}. 
-        The initial condition is generic, so it can describe accelerated proximal gradient method in the middle of its executions. 
-        \par
-        Alternatively, any two of the vectors among $x_1, y_1, v_1$ can be used to initialize the algorithm because given $(v_1, y_1), (v_1, x_1)$, or $(x_1, y_1)$ we can solve 
-        $y_1 = (\gamma_1 + \alpha_1\mu)^{-1}(\alpha_1 \gamma_1 v_1 + \hat \gamma_{2}x_1)$ for $x_1, y_1$ or $v_1$. 
-        % \par
-        % If one initial condition $x_0$ is given. 
-        % Then $v_1 = x_0, x_1 = T_L x_0$ is considered a valid initial conditions. 
-    \end{observation}
-
     \begin{observation}\label{obs:r-wapg-observation-1}
@@
     \end{observation}
+    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
+        \; \\
+        Choose any $x_1 \in \RR^n, v_1 \in \RR^n$. 
+        Let $(\alpha_k)_{k \ge1}, (\rho_k)_{k \ge 1}$ be given by Definition \ref{def:rwapg-seq}. 
+        The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ such that they satisfy for all $k\ge 1$: 
+        \begin{align*}
+            \gamma_k &:= \left.\begin{cases}
+                \rho_{k -1}L\alpha_{k - 1}^2 & k \ge 2,
+                \\
+                \gamma_1 & k = 1. 
+            \end{cases}\right\rbrace,
+            \\
+            \hat \gamma_{k + 1} & = (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2
+            \\
+            y_k &= 
+            (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
+            \\
+            g_k &= \mathcal G_L y_k, 
+            \\
+            v_{k + 1} &= 
+            \hat\gamma^{-1}_{k + 1}
+            (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
+            \\
+            x_{k + 1} &= T_L y_k. 
+        \end{align*}
+    \end{definition}
+    \begin{observation}
+        Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018} because $L\alpha_k^{2} = (1 - \alpha_k)L\alpha_{k - 1}^2 + \mu \alpha_k$.
+        \par
+        The algorithm chains together the sequence of $(\hat \gamma_{k+1})_{k \ge 1}$ and $(\gamma_k)_{k \ge 1}$ in Definition \ref{prop:stepwise-lyapunov} through the equalities: 
+        \begin{align*}
+            \hat \gamma_{k + 1} = L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \alpha_k \mu
+            &= (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu. 
+        \end{align*}
+
+    \end{observation}
 
     \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}\; \\
-        Given any $(v_1, x_1)$, let vectors $(y_k, v_{k + 1}, x_{k + 1})_{k \ge 1}$ and scalars sequence $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ be generated by R-WAPG (Definition \ref{def:wapg}). 
-        Define recursively for all $k\ge1$ by 
+        Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$. 
+        Let vector sequence $(y_k, v_{k}, x_{k})_{k \ge 1}$ and scalar sequences $\alpha_k, \rho_k$ be generated from Definition \ref{def:wapg}. 
+        Define $R_1 = 0$ and suppose that for $k = 1, 2, \cdots, N$, we have $R_k$ recursively given by: 
         \begin{align*}
@@
         \end{align*} 
-        Choose $R_1= 0$ to be the base case. 
-        Choose any $x^* \in \RR^n$ then
+        Then for all $k = 1, 2, \cdots, N$: 
         \begin{align*}
@@
     \begin{proof}  
-        Recall the stepwise convergence theorem, since the choice of $\gamma, \hat \gamma$ is satisfies is strictly positive and for $i=2, 3, \cdots, k$, by Definition \ref{def:wapg} it has $\gamma = \rho_{i - 1} L \alpha_{i - 1}^2 > 0, \hat \gamma = L \alpha_i^2 > 0$ at each step, with the base case $i = 1$: $\gamma \in (0, L], \hat \gamma = (1 - \alpha_1)\gamma + \mu \alpha_1$.
-        Since $\alpha_i \in(0, 1)$ for all $i = 1, \cdots, k$, because of Observation \ref{obs:r-wapg-observation-1}, we can use Proposition \ref{prop:stepwise-lyapunov}, to show that for all $k \ge 1$:
+        Since $\hat \gamma_2, \gamma_1$ has $\hat \gamma_2 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$ and $R_2$ is defined in the same manner as in Proposition \ref{prop:stepwise-lyapunov}, we can invoke Proposition \ref{prop:stepwise-lyapunov} and it gives:
+        \begin{align*}
+            F(x_{2}) - F(x^*) + R_2 + \frac{L \alpha_k^2}{2}\Vert v_{2} - x^*\Vert^2
+            &\le 
+            (1 - \alpha_1)\left(
+                F(x_1) - F(x^*) + R_1 + \frac{\gamma_1}{2}\Vert v_1 - x^*\Vert^2
+            \right). 
+        \end{align*}
+        We had demonstrated the base case. 
+        \par 
+        Next, for all $k = 2, 3, \cdots, N$, the R-WAPG described in \ref{def:wapg} has $\hat \gamma_{k + 1} = L\alpha_{k - 1}^2 = (1 - \alpha_k)\gamma_k + \mu\alpha_k$. 
+        We have also $\alpha_k \in (0, 1)$ by Observation \ref{obs:r-wapg-observation-1}. 
+        So $\gamma_k, \hat \gamma_{k + 1}, \alpha_k$ fits Definition \ref{def:stepwise-wapg}. 
+        The description of $R_k$ is the same as in Proposition \ref{prop:stepwise-lyapunov} hence we can use Proposition \ref{prop:stepwise-lyapunov}, to show that for all $k \ge 1$: 
         {\small
@@
         }
-        Additionally, for all $k \ge 1$ the algorithm converges by considering $R_{k + 1}$: 
+        We had demonstrated in the inductive case for $k=1, 2, \cdots, N$. 
+        Additionally, for all $k = 1, 2, \cdots, N$ it has $R_{k + 1} \ge 0$ because: 
         \begin{align*}
@@
         This makes coefficient of $\Vert g_k\Vert^2$ zero. 
-        The first inequality is by $\epsilon_k \ge 0$ and the non
-        -negativity of the remaining terms. 
+        The first inequality is by $\epsilon_k \ge 0$ and the non-negativity of the remaining terms. 
         The last equality is by the assumption that $R_1 = 0$. 
@@
     This section reduces Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 
-    Proposition \ref{prop:wapg-first-equivalent-repr} simplifies Definition \ref{def:wapg} for the specific initial conditions $\gamma_0 \in(0, 1)$ and finds a representation without auxiliary sequence $\gamma_k, \hat \gamma_k$.
+    In the literatures, variants of Accelerated Proximal Gradient algorithm such as FISTA, V-FISTA has different representations. 
+    This section carries out the tedious but necessary works for demonstrating the descriptive power of R-WAPG. 
+    We will formulate it into three generic forms that are commonly seemed in the literatures. 
+    These equivalent representations are listed in Definition \ref{def:r-wapg-intermediate}, \ref{def:r-wapg-st-form} and \ref{def:r-wapg-momentum-form}. 
+    \par 
+    Proposition \ref{prop:wapg-first-equivalent-repr} simplifies Definition \ref{def:wapg} and finds a representation without using auxiliary sequence $\gamma_k, \hat \gamma_k$. 
     Definition \ref{def:r-wapg-intermediate} states the first simplified form of the R-WAPG algorithm which we call: ``R-WAPG intermediate form''. 
-    Following a similar pattern, Proposition \ref{prop:wagp-st-form}, \ref{prop:wagp-st-form} states two more equivalent representations under R-WAPG intermediate form which are formulated as Definition \ref{def:r-wapg-st-form}, \ref{def:r-wapg-momentum-form}.
-    Proposition \ref{prop:wagp-convergence} applies to all these equivalent forms.
+    Following a similar pattern, Proposition \ref{prop:wagp-st-form}, \ref{prop:r-wapg-momentum-repr} demonstrates two more equivalent representations of the R-WAPG intermediate form (Definition \ref{def:r-wapg-intermediate}) which are formulated into Definition \ref{def:r-wapg-st-form}, \ref{def:r-wapg-momentum-form}.
+    Convergence results from Proposition \ref{prop:wagp-convergence} applies to all these equivalent forms of R-WAPG.
 
@@
             \\
-            & 
-            y_{k + 1} = 
-            x_{k + 1} + 
-            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k), 
             \\
@@
                 \sqrt{(\rho_{k}\alpha_{k}^2 - \mu/L)^2 + 4\rho_{k}\alpha_{k}^2}
-            \right). 
+            \right), 
+            \\
+            & 
+            y_{k + 1} = 
+            x_{k + 1} + 
+            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
         \end{align*}
@@
 
-\subsection{Representing algorithms in the literatures via R-WAPG}
+\subsection{R-WAPG describes existing accelerations scheme in the literatures}
 
@@
 
+\appendix
+
 \end{document}

### 2024-12-19 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
     Suppose we are minimizing a differentiable convex function $F$ for simplicity. 
-    In addition, assuming the function is $\RR^n$ so it's full domain and $F$ is Lipschitz smooth meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$.
+    In addition, assuming the function is $\RR^n$, so it's full domain and $F$ is Lipschitz smooth meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$.
     \par 
     A good choice of a minimization algorithm is the Nesterov's acceleration schemes that originally proposed in 1983 \cite{nesterov_method_1983}.
-Initializing $x_0 = y_0$ the algorithm finds $(x_k)_{k \ge 1}$ and $t_1 = 1$ by
-    \begin{align*}
+Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by:
+    \begin{align}
         & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
@@
         & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
-    \end{align*}
+    \end{align}\label{eqn:example_algorithm}
     It's well known that if the minimizer $x^*$ exists, $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, faster than the gradient descent method which is $\mathcal O(1/k)$, and it's optimal.
@@
     \par
-    Inspired by prior works and the method of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, we present to you an alternative to restarting that performs well empirically and along with it, a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG).
-    The R-WAPG has a convergence claim of $F(x_k)- F(x^*)$ for a much flexible choice of $(\theta_t)_{t \ge 1}$ and the descriptive power to cover several variants of FISTA in the literatures.
+    Inspired by prior works and the method of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, we present to you firstly, an alternative to restarting that performs well empirically and along with it.
+    Secondly, a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG). 
+    The R-WAPG has a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(\theta_t)_{t \ge 1}$. 
+    It also has descriptive power to describe several variants of FISTA in the literatures.
 
     \subsection{Contributions}
-        Our contributions are two folds theoretical and practical. 
-        \par
+        Our contributions are two folds, theoretical and practical. 
         Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''. 
@@
         \par
-        Firstly, we relaxed the traditional choice of the sequence $\theta_k$ and showed an upper bound of the optimal gap. 
+        Firstly, we relaxed the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example_algorithm} and showed an upper bound of the optimal gap. 
         Let $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$, given any $\gamma_1 \in (0, L]$ and define $\alpha_1$ by 
@@
         \end{align*}
-        Our first main results shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed (Definition \ref{def:wapg}), we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
+        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed (Definition \ref{def:wapg}), we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
         \begin{align*}
@@
         \end{align*}
-        Our second main results shows that there exists $\rho_k > 1$ such that our R-WAPG reduces perfectly to the variants proposed in Chambolle Dossal \cite{chambolle_convergence_2015}. 
-        And when $\rho_k = 1, \rho > 0$, R-WAPG reduces perfect to V-FISTA by Beck \cite{beck_first-order_2017} and it produces convergence claim consistent with the literatures. 
+        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces perfectly to the a variant proposed in Chambolle Dossal \cite{chambolle_convergence_2015}. 
+        And when $\rho_k = 1$, R-WAPG reduces perfectly to V-FISTA by Beck \cite{beck_first-order_2017}, and it produces convergence claim consistent with the literatures. 
+        We will also present a simplified convergence rate when $\rho_k \in (0, \alpha_{k - 1}^2), \mu = 0$ which is also consistent with the literatures. 
         \par
         Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG''. 
-        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$.
-        We conducted ample amount of numerical experiments to show that it has favorable convergence rate in practice, and it behaves similarly to the FISTA with monotone restart. 
+        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ with minimal computational cost.
+        We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart. 
+    \subsection{Prior works}
+
     \subsection{Organizations}
@@
     Definition \ref{def:stepwise-wapg} which describes what happens at a single iteration of the R-WAPG algorithm. 
-    It defines a procedures of generating $x_{k + 1}, v_{k + 1}$ given any $x_k, v_k$. 
-    Propsotion \ref{prop:stepwise-lyapunov} states the inequality that describes a decreasing quantity that involves $F(x_k), F(x_{k + 1})$ at each single iteration.
-
+    It defines a procedure of generating $x_{k + 1}, v_{k + 1}$ given any $x_k, v_k$. 
+    Proposition \ref{prop:stepwise-lyapunov} states the inequality that describes a decreasing quantity that involves $F(x_k), F(x_{k + 1})$ at each single iteration. 
     \begin{assumption}
@@
         The proof is a direct proof. 
-        Here we drop the subscript $k$, $k + 1$ on $\gamma_{k}, \hat \gamma_{k + 1}$ because they are fixed throughout the proof and it makes for better readibility! 
+        Here we drop the subscript $k$, $k + 1$ on $\gamma_{k}, \hat \gamma_{k + 1}$ because they are fixed throughout the proof, and it makes for better readability! 
         \par 
@@
         For any $\gamma_1 \in (0, L]$, define $\alpha_1 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$. 
-        Then the sequence $(\alpha_{k + 1})_{k \ge 1}, (\rho_k)_{k \ge 1}$ satisfy for all $k \ge 2$
+        Then the sequence $(\alpha_{k})_{k \ge 1}, (\rho_k)_{k \ge 1}$ satisfy for all $k \ge 2$: 
         \begin{align*}
@@
 
+    \begin{lemma}[Specialize convergence claim]\label{lemma:special-rwapg-convergence-claim}
+
+    \end{lemma}
+    \begin{lemma}[First example sequence]
+        Choose any $a \ge 2$. 
+        Define $\forall k \ge 1$ the sequence $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ by 
+        \begin{align*}
+            \alpha_k &= \alpha/(k + 1), 
+            \\
+            \rho_k &= \frac{(k + 1)(k + a)^2}{ak(k + a + 1)}. 
+        \end{align*}
+        Then $\alpha_k, \rho_k$ satisfies Definition \ref{def:rwapg-seq}. 
+        It is a valid choice of sequence for the R-WAPG algorithm, which means that they satisfy: 
+    \end{lemma}
+
 \subsection{The method of Inexact Momentum}
@@
 
-\subsection{Numerical experiments and applications}
+\subsection{Numerical experiments}
 

### 2024-12-19 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes, a lot

@@
         Firstly, we relaxed the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example_algorithm} and showed an upper bound of the optimal gap. 
-        Let $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$, given any $\gamma_1 \in (0, L]$ and define $\alpha_1$ by 
-        \begin{align*}
-            \alpha_1 = \frac{1}{2}\left(
-                \frac{\mu}{L} - \frac{\gamma_1}{L} + 
-                \sqrt{
-                    \left(
-                        \frac{\gamma_1}{L} - \frac{\mu}{L}
-                    \right)^2 + 
-                    \frac{4\gamma_1}{L}
-                }
-            \right). 
-        \end{align*}
-        We define $\alpha_k$ for $k \ge 2$ by: 
-        \begin{align*}
-            &\alpha_k \in (0, 1), 
-            \\
-            & 0 < \rho_k \alpha_k^2 < 1, 
-            \\
-            &\alpha_{k + 1} = 
-            \frac{1}{2}\left(
-                \frac{\mu}{L} - \rho_{k}\alpha_{k}^2 
-                +
-                \sqrt{(\rho_{k}\alpha_{k}^2 - \mu/L)^2 + 4\rho_{k}\alpha_{k}^2}
-            \right). 
-        \end{align*}
-        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed (Definition \ref{def:wapg}), we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
+        Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
+        \begin{align*}
+            \alpha_0 &\in (0, 1], 
+            \\
+            \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
+            \\
+            \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
+        \end{align*}
+        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wagp-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
         \begin{align*}
@@
                 \left(
-                    \prod_{i = 1}^{k - 1} \max(1, \rho_{k})
+                    \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
                 \right)
@@
         \end{align*}
-        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces perfectly to the a variant proposed in Chambolle Dossal \cite{chambolle_convergence_2015}. 
-        And when $\rho_k = 1$, R-WAPG reduces perfectly to V-FISTA by Beck \cite{beck_first-order_2017}, and it produces convergence claim consistent with the literatures. 
-        We will also present a simplified convergence rate when $\rho_k \in (0, \alpha_{k - 1}^2), \mu = 0$ which is also consistent with the literatures. 
+        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces perfectly to the a variant proposed in Chambolle Dossal \cite{chambolle_convergence_2015} and it has the same convergence claim as in the literatures.
+        And when $\rho_k = 1$, R-WAPG reduces perfectly to V-FISTA by Beck \cite{beck_first-order_2017} if $\mu > 0$ and FISTA if $\mu = 0$ and the convergence claim is consistent with the literatures.
         \par
@@
     It introduces the procedures of making the sequence $\alpha_k \in (0, 1)$ which assists with claiming convergence of the algorithm using Proposition \ref{prop:stepwise-lyapunov} by connecting them together.
-    \begin{definition}[R-WAPG sequence]\label{def:rwapg-seq}
+    \begin{definition}[R-WAPG sequence]\label{def:rwapg-seq}\;\\
         Assume $0 \le \mu < L$. 
-        For any $\gamma_1 \in (0, L]$, define $\alpha_1 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$. 
-        Then the sequence $(\alpha_{k})_{k \ge 1}, (\rho_k)_{k \ge 1}$ satisfy for all $k \ge 2$: 
-        \begin{align*}
-            &\alpha_k \in (0, 1), 
-            \\
-            & 0 < \rho_k \alpha_k^2 < 1, 
-            \\
-            &L\alpha_k^2 = (1 - \alpha_k)\rho_{k - 1}L \alpha_{k - 1}^2 + \mu \alpha_k. 
+        The sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge1}$ are valid for R-WAPG all the following holds: 
+        \begin{align*}
+            \alpha_0 &\in (0, 1], 
+            \\
+            \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
+            \\
+            \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
         \end{align*}
@@
     \begin{observation}\label{obs:r-wapg-observation-1}
-        If $\alpha_1 \in (0, 1)$ which is true by $\gamma_1 \in (0, L]$, then the entire sequence $\alpha_k \in (0, 1)$. 
-        Suppose inductively that $\alpha_{k - 1}, \rho_{k - 1}$ are given such that they satisfy $\alpha_{k -1} \in (0, 1)$ and $0 < \rho_{k - 1} \alpha_{k - 1}^2 < 1$. 
-        Solving the quadratic $L\alpha_k^2=(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2 + \mu \alpha_k$ for $\alpha_k$ yields candidates. 
-        \begin{align*}
-            \alpha_k &= 
-            \frac{1}{2}\left(
-                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
-                \pm
-                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
-            \right). 
-        \end{align*}
-        Choosing the positive sign which is the larger one of the roots of the quadratic. 
-        We have $\alpha_k > 0$ because: 
-        \begin{align*}
-            \alpha_k &=
-            \frac{1}{2}\left(
-                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
-                +
-                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
-            \right)
-            \\
-            &\ge 
-            \frac{1}{2}\left(
-                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
-                +
-                \left|\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L\right|
-            \right) + \alpha_{k - 1}\sqrt{\rho_{k - 1}}
-            \\
-            & > 0. 
-        \end{align*}
-        On the last strict inequality we used the fact that $\rho_{k - 1}> 0, \alpha_{k - 1} > 0$. 
-        An upper bound can be identified by using inductive hypothesis and considering: 
-        \begin{align*}
-            \alpha_k &= 
-            \frac{1}{2}\left(
-                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
-                +
-                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
-            \right)
-            \\
-            &<
-            \frac{1}{2}\left(
-                \frac{\mu}{L} + 
-                \sup_{x \in (0, 1)}
-                \left\lbrace
-                    -x + \sqrt{(x - \mu/L)^2 + 4x}
-                \right\rbrace
-            \right)
-            \\
-            & \le \frac{1}{2}\left(
-                \mu/L + \max\left(\mu/L, -1 + \sqrt{(1 - \mu/L)^2 + 4}\right)
-            \right) \le 1. 
-        \end{align*}
-        Going to the first inequality, we used $\rho_{k - 1} \alpha_{k - 1}^2 < 1$ to get the strict inequality. 
-        Going from the second to the third inequality, we maximized $\mu/L$ by monotone increasing of linear function and the square root function. 
-        Therefore, inductively, $\alpha_k \in (0, 1)$ holds. 
-        However, the limit of $\alpha_k$ could be 1. 
+        The following is true: 
+        \begin{enumerate}
+            \item $\rho_k > 0$ for all $k \ge 0$. 
+            \item $\forall k \ge 1: L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 +\mu\alpha_k$. 
+        \end{enumerate}
+
+        % If $\alpha_1 \in (0, 1)$ which is true by $\gamma_1 \in (0, L]$, then the entire sequence $\alpha_k \in (0, 1)$. 
+        % Suppose inductively that $\alpha_{k - 1}, \rho_{k - 1}$ are given such that they satisfy $\alpha_{k -1} \in (0, 1)$ and $0 < \rho_{k - 1} \alpha_{k - 1}^2 < 1$. 
+        % Solving the quadratic $L\alpha_k^2=(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2 + \mu \alpha_k$ for $\alpha_k$ yields candidates. 
+        % \begin{align*}
+        %     \alpha_k &= 
+        %     \frac{1}{2}\left(
+        %         \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
+        %         \pm
+        %         \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
+        %     \right). 
+        % \end{align*}
+        % Choosing the positive sign which is the larger one of the roots of the quadratic. 
+        % We have $\alpha_k > 0$ because: 
+        % \begin{align*}
+        %     \alpha_k &=
+        %     \frac{1}{2}\left(
+        %         \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
+        %         +
+        %         \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
+        %     \right)
+        %     \\
+        %     &\ge 
+        %     \frac{1}{2}\left(
+        %         \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
+        %         +
+        %         \left|\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L\right|
+        %     \right) + \alpha_{k - 1}\sqrt{\rho_{k - 1}}
+        %     \\
+        %     & > 0. 
+        % \end{align*}
+        % On the last strict inequality we used the fact that $\rho_{k - 1}> 0, \alpha_{k - 1} > 0$. 
+        % An upper bound can be identified by using inductive hypothesis and considering: 
+        % \begin{align*}
+        %     \alpha_k &= 
+        %     \frac{1}{2}\left(
+        %         \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
+        %         +
+        %         \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
+        %     \right)
+        %     \\
+        %     &<
+        %     \frac{1}{2}\left(
+        %         \frac{\mu}{L} + 
+        %         \sup_{x \in (0, 1)}
+        %         \left\lbrace
+        %             -x + \sqrt{(x - \mu/L)^2 + 4x}
+        %         \right\rbrace
+        %     \right)
+        %     \\
+        %     & \le \frac{1}{2}\left(
+        %         \mu/L + \max\left(\mu/L, -1 + \sqrt{(1 - \mu/L)^2 + 4}\right)
+        %     \right) \le 1. 
+        % \end{align*}
+        % Going to the first inequality, we used $\rho_{k - 1} \alpha_{k - 1}^2 < 1$ to get the strict inequality. 
+        % Going from the second to the third inequality, we maximized $\mu/L$ by monotone increasing of linear function and the square root function. 
+        % Therefore, inductively, $\alpha_k \in (0, 1)$ holds. 
+        % However, the limit of $\alpha_k$ could be 1. 
     \end{observation}
@@
         Choose any $x_1 \in \RR^n, v_1 \in \RR^n$. 
-        Let $(\alpha_k)_{k \ge1}, (\rho_k)_{k \ge 1}$ be given by Definition \ref{def:rwapg-seq}. 
+        Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}. 
         The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ such that they satisfy for all $k\ge 1$: 
         \begin{align*}
-            \gamma_k &:= \left.\begin{cases}
-                \rho_{k -1}L\alpha_{k - 1}^2 & k \ge 2,
-                \\
-                \gamma_1 & k = 1. 
-            \end{cases}\right\rbrace,
-            \\
-            \hat \gamma_{k + 1} & = (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2
+            \gamma_k &:= \rho_{k -1}L\alpha_{k - 1}^2, 
+            \\
+            \hat \gamma_{k + 1} & := (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2, 
             \\
@@
     \end{definition}
-    \begin{observation}
+    \begin{observation}\label{obs:r-wapg-observation-2}
         Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018} because $L\alpha_k^{2} = (1 - \alpha_k)L\alpha_{k - 1}^2 + \mu \alpha_k$.
         \par
-        The algorithm chains together the sequence of $(\hat \gamma_{k+1})_{k \ge 1}$ and $(\gamma_k)_{k \ge 1}$ in Definition \ref{prop:stepwise-lyapunov} through the equalities: 
-        \begin{align*}
-            \hat \gamma_{k + 1} = L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \alpha_k \mu
-            &= (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu. 
-        \end{align*}
-
+        For all $k \ge 1$, the algorithm chains together the sequence of $(\hat \gamma_{k+1})_{k \ge 1}$ and $(\gamma_k)_{k \ge 1}$ in Definition \ref{prop:stepwise-lyapunov} through the equalities: 
+        \begin{align*}
+            \hat \gamma_{k + 1} 
+            &= L\alpha_k^2 
+            \\
+            &= (1 - \alpha_k)\gamma_k + \alpha_k \mu
+            \\
+            &= (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu
+            \\
+            &= (1 - \alpha_k)\rho_{k - 1}\hat \gamma_{k} + \alpha_k \mu. 
+        \end{align*}
+        The third equality from Observation \ref{obs:r-wapg-observation-1}. 
     \end{observation}
@@
             \left(
-                \prod_{i = 1}^{k - 1} \max(1, \rho_{k})
+                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
             \right)
@@
     \begin{proof}  
-        Since $\hat \gamma_2, \gamma_1$ has $\hat \gamma_2 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$ and $R_2$ is defined in the same manner as in Proposition \ref{prop:stepwise-lyapunov}, we can invoke Proposition \ref{prop:stepwise-lyapunov} and it gives:
-        \begin{align*}
-            F(x_{2}) - F(x^*) + R_2 + \frac{L \alpha_k^2}{2}\Vert v_{2} - x^*\Vert^2
+        $\hat \gamma_2 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$ is true by Observation \ref{obs:r-wapg-observation-1}. 
+        Observe that $R_2$ is defined in the same manner as in Proposition \ref{prop:stepwise-lyapunov} with k = 1 so we can invoke Proposition \ref{prop:stepwise-lyapunov}, and it gives: 
+        \begin{align*}
+            & F(x_{2}) - F(x^*) + R_2 + \frac{L \alpha_1^2}{2}\Vert v_{2} - x^*\Vert^2
+            \\
+            & = F(x_{2}) - F(x^*) + R_2 + \frac{\hat \gamma_{2}}{2}\Vert v_{2} - x^*\Vert^2
+            & \hat \gamma_2 = L \alpha_1^2 , \text{ Definition \ref{def:wapg}}
+            \\
             &\le 
@@
                 F(x_1) - F(x^*) + R_1 + \frac{\gamma_1}{2}\Vert v_1 - x^*\Vert^2
+            \right) 
+            & \quad \text{By Proposition \ref{prop:stepwise-lyapunov}}
+            \\
+            &= 
+            (1 - \alpha_1)\left(
+                F(x_1) - F(x^*) + R_1 + \frac{L\rho_{0}\alpha_{0}^2}{2}\Vert v_1 - x^*\Vert^2
+            \right) 
+            \\
+            &= \max\left(\rho_0, 1\right)
+            (1 - \alpha_1)\left(
+                F(x_1) - F(x^*) + R_1 + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
             \right). 
@@
         \par 
-        Next, for all $k = 2, 3, \cdots, N$, the R-WAPG described in \ref{def:wapg} has $\hat \gamma_{k + 1} = L\alpha_{k - 1}^2 = (1 - \alpha_k)\gamma_k + \mu\alpha_k$. 
-        We have also $\alpha_k \in (0, 1)$ by Observation \ref{obs:r-wapg-observation-1}. 
+        Next, for all $k = 2, 3, \cdots, N$, from Observation \ref{obs:r-wapg-observation-2}: 
+        \begin{align*}
+            \hat \gamma_{k + 1} = L\alpha_{k}^2 
+            &=(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2 + \mu\alpha_k
+            \\
+            &= (1 - \alpha_k)\gamma_k + \mu\alpha_k. 
+        \end{align*}
         So $\gamma_k, \hat \gamma_{k + 1}, \alpha_k$ fits Definition \ref{def:stepwise-wapg}. 
-        The description of $R_k$ is the same as in Proposition \ref{prop:stepwise-lyapunov} hence we can use Proposition \ref{prop:stepwise-lyapunov}, to show that for all $k \ge 1$: 
+        The definition of $R_k$ given is the same as in Proposition \ref{prop:stepwise-lyapunov} hence we can use Proposition \ref{prop:stepwise-lyapunov} to un roll recursively for all $k \ge 1$: 
         {\small
         \begin{align*}
-            &F(x_{k + 1}) - F^* + R_{k + 1} + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
+            &
+            F(x_{k + 1}) - F^* + R_{k + 1} + \frac{\hat\gamma_{k + 1}}{2}\Vert v_{k + 1} - x^*\Vert^2 
+            \\
+            &=
+            F(x_{k + 1}) - F^* + R_{k + 1} + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
             \\
@@
         \begin{align*}
-            & F(x_{k + 1}) - F^* +
+            & 
+            F(x_{k + 1}) - F^* +
             \frac{L\alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
@@
         \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\
-            Assume $\mu < L$. 
-            Choose any $\gamma_1 \in (0, L], x_1, v_1$ as the initial condition for R-WAPG (Definition \ref{def:wapg}) to produce vectors sequence $(y_k, v_{k + 1}, x_{k + 1})_{k \ge 1}$. 
-            Then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge1}$, and for all $k\ge 1$ they are algebraically equivalent to
+            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}). 
+            Then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$, and for all $k\ge 1$ they are algebraically equivalent to
             \begin{align*}
@@
             \end{align*}
-            On the third $\iff$, we can assume $\alpha_k \neq \mu/L\; \forall k \ge 2$ because if $\alpha_k = \mu/L$ were impossible, it then has
-            \begin{align*}
-                L \alpha_k^2 - \alpha_k\mu &= 
-                (1 - \alpha_k)L \rho_{k - 1}\alpha_{k - 1}^2 = 0 \implies \alpha_{k - 1} = 0. 
-            \end{align*}
-            Which contradict $\alpha_{k - 1} \in (0, 1)\; \forall k \ge 2$ because $\alpha_1 \in (0, 1)$ is given to satisfy the condition in the base case, and $\alpha_k \in (0, 1)\; \forall k \ge 2$ by justifications in Observation \ref{obs:r-wapg-observation-1}.
+            On the third $\iff$, we can assume $\alpha_k \neq \mu/L\;  \forall k \ge 1$ because from Definition \ref{def:rwapg-seq}: $\alpha_k \in (\mu/L, 1)$ for all $k \ge 1$. 
+            % On the third $\iff$, we can assume $\alpha_k \neq \mu/L\; \forall k \ge 2$ because if $\alpha_k = \mu/L$ were impossible, it then has
+            % \begin{align*}
+            %     L \alpha_k^2 - \alpha_k\mu &= 
+            %     (1 - \alpha_k)L \rho_{k - 1}\alpha_{k - 1}^2 = 0 \implies \alpha_{k - 1} = 0. 
+            % \end{align*}
+            % Which contradict $\alpha_{k - 1} \in (0, 1)\; \forall k \ge 2$ because $\alpha_1 \in (0, 1)$ is given to satisfy the condition in the base case, and $\alpha_k \in (0, 1)\; \forall k \ge 2$ by justifications in Observation \ref{obs:r-wapg-observation-1}.
             \\
@@
         \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
-            Given any $\gamma_1 \in (0, L]$, $(x_1, v_1)$. 
-            Assume $\mu < L$. 
-            Define 
-            \begin{align*}
-                \alpha_1 = \frac{1}{2}\left(
-                    \frac{\mu}{L} - \frac{\gamma_1}{L} + 
-                    \sqrt{
-                        \left(
-                            \frac{\gamma_1}{L} - \frac{\mu}{L}
-                        \right)^2 + 
-                        \frac{4\gamma_1}{L}
-                    }
-                \right). 
-            \end{align*}
-            For $k = 1, 2, \cdots $, the algorithm generates sequence of vector iterates $(y_{k}, v_{k + 1}, x_{k + 1})_{k \ge 1}$ and auxiliary sequence $(\alpha_{k + 1}, \rho_k)_{k \ge 1}$ by the procedures:
+            Assume $\mu < L$ and let $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 
+            Initialize any $x_1, v_1$ in $\RR^n$. 
+            For $k = 1, 2, \cdots $, the algorithm generates sequence of vector iterates $(y_{k}, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by: 
             \begin{align*} 
@@
                     \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
-                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k
-                \\
-                & \text{choose any } \rho_{k}: 0 < \rho_{k} < \alpha_{k}^{-2}, 
-                \\
-                & \alpha_{k + 1} := 
-                \frac{1}{2}\left(
-                \frac{\mu}{L} - \rho_{k}\alpha_{k}^2 
-                +
-                \sqrt{(\rho_{k}\alpha_{k}^2 - \mu/L)^2 + 4\rho_{k}\alpha_{k}^2}
-                \right). 
+                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
             \end{align*}
@@
         \begin{proposition}[Second equivalent representation of R-WAPG]\label{prop:wagp-st-form}\;\\
-            Let iterates $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge1}$ be given by Definition \ref{def:r-wapg-intermediate}. 
+            Let iterates $(y_k, x_{k}, v_{k})_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge 0}$ be given by Definition \ref{def:r-wapg-intermediate}. 
             Then for all $k \ge 1$, iterate $y_k, x_{k + 1}, v_{k + 1}$
@@
         \end{proof}
-        \begin{remark}
-            We note that $x_1, v_1, y_1$ may not satisfy the inequalities since, 
-        \end{remark}
     \begin{definition}[R-WAPG similar triangle form]\label{def:r-wapg-st-form} \; \\
-        Given any initial $L \in (0, L]$, $(x_1, v_1)$. 
+        Given any $(x_1, v_1)$ in $\RR^n$. 
         Assume $\mu < L$.
-        Define $\alpha_1$ by 
-        \begin{align*}
-            \alpha_1 = \frac{1}{2}\left(
-                \frac{\mu}{L} - \frac{\gamma_1}{L} + 
-                \sqrt{
-                    \left(
-                        \frac{\gamma_1}{L} - \frac{\mu}{L}
-                    \right)^2 + 
-                    \frac{4\gamma_1}{L}
-                }
-            \right). 
-        \end{align*}
+        Let the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k\ge 0}$ be given by Definition \ref{def:rwapg-seq}. 
         For $k = 1, 2, \cdots $, the algorithm generates sequences of vector iterates $(y_k, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by the procedures: 
@@
             & v_{k + 1} = 
-            x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k), 
-            \\
-            & \text{choose any }   \rho_{k}: 0 < \rho_{k} < \alpha_{k}^{-2}, 
-            \\
-            &\alpha_{k + 1} = 
-            \frac{1}{2}\left(
-            \frac{\mu}{L} - \rho_{k}\alpha_{k}^2 
-            +
-            \sqrt{(\rho_{k}\alpha_{k}^2 - \mu/L)^2 + 4\rho_{k}\alpha_{k}^2}
-            \right). 
+            x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k). 
         \end{align*}
@@
     \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
-        Let $y_1 = x_1$. 
-        Given any $\gamma_1 \in (0, L]$, initialize any $\alpha_1 \in (0, 1)$ by: 
-        \begin{align*}
-            \alpha_1 = \frac{1}{2}\left(
-                \frac{\mu}{L} - \frac{\gamma_1}{L} + 
-                \sqrt{
-                    \left(
-                        \frac{\gamma_1}{L} - \frac{\mu}{L}
-                    \right)^2 + 
-                    \frac{4\gamma_1}{L}
-                }
-            \right). 
-        \end{align*}
-        For $k = 1, 2, \cdots $, the algorithm generates iterates $x_{k + 1}, y_{k + 1}$ and auxiliary sequence $(\rho_k)_{k \ge 1}, (\alpha_k)_{k \ge 2}$ by the procedures: 
+        For any $y_1 = x_1 \in \RR^n$, $(\rho_k)_{k \ge 0}, (\alpha_k)_{k\ge 0}$ given by Definition \ref{def:rwapg-seq}. 
+        The algorithm generates iterates $x_{k + 1}, y_{k + 1}$ For $k = 1, 2, \cdots $ by the procedures: 
         \begin{align*}
             & x_{k + 1} = y_k - L^{-1}\mathcal G_Ly_k, 
-            \\
-            \\
-            & \text{find } \rho_{k}: 0 < \rho_{k} < \alpha_{k}^{-2}, 
-            \\
-            & 
-            \alpha_{k + 1} = 
-            \frac{1}{2}\left(
-                \frac{\mu}{L} - \rho_{k}\alpha_{k}^2 
-                +
-                \sqrt{(\rho_{k}\alpha_{k}^2 - \mu/L)^2 + 4\rho_{k}\alpha_{k}^2}
-            \right), 
             \\
@@
         \end{align*}
-        In the special case $\mu = 0$, the momentum term can be represented without relaxation parameter $\rho_k$: 
+        In the special case where $\mu = 0$, the momentum term can be represented without relaxation parameter $\rho_k$: 
         $$
@@
 
-    \begin{lemma}[Specialize convergence claim]\label{lemma:special-rwapg-convergence-claim}
+    \begin{lemma}[First specialized R-WAPG sequence]\label{lemma:special-rwapg-convergence-claim}
 
     \end{lemma}
-    \begin{lemma}[First example sequence]
+
+    \begin{lemma}[Inverted Chambolle, Dossal 2015 sequence]
         Choose any $a \ge 2$.
-        Define $\forall k \ge 1$ the sequence $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ by 
-        \begin{align*}
-            \alpha_k &= \alpha/(k + 1), 
-            \\
-            \rho_k &= \frac{(k + 1)(k + a)^2}{ak(k + a + 1)}. 
-        \end{align*}
-        Then $\alpha_k, \rho_k$ satisfies Definition \ref{def:rwapg-seq}. 
-        It is a valid choice of sequence for the R-WAPG algorithm, which means that they satisfy: 
+        Define $\forall k \ge 1$ the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ by 
+        \begin{align*}
+            \alpha_k &= a/(k + a), 
+            \\
+            \rho_k &= \frac{(k + a)^2}{(k + 1)(k + a + 1)}. 
+        \end{align*}
+        If $\mu = 0$, then $\alpha_k, \rho_k$ satisfies Definition \ref{def:rwapg-seq}. 
+        It is a valid choice of sequence for the R-WAPG algorithm and it has $\rho_k \ge 1$ for all $k \ge 0$. 
     \end{lemma}
+    \begin{proof}
+
+    \end{proof}
 

### 2024-12-19 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
     It introduces the procedures of making the sequence $\alpha_k \in (0, 1)$ which assists with claiming convergence of the algorithm using Proposition \ref{prop:stepwise-lyapunov} by connecting them together.
-    \begin{definition}[R-WAPG sequence]\label{def:rwapg-seq}\;\\
+    \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}\;\\
         Assume $0 \le \mu < L$. 
@@
         \end{align*}
+        We call $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ the \textbf{R-WAPG Sequences}. 
     \end{definition}
@@
         Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}. 
-        The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ such that they satisfy for all $k\ge 1$: 
+        The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for $k\ge 1$ by the procedures:  
         \begin{align*}
@@
         \;\\
-        Let sequence $(\alpha_k, \rho_k)_{k \ge 1}$ and iterates $(x_k, v_k, y_k)_{k\ge 1}$ given by R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}). 
+        Let sequence $(\alpha_k, \rho_k)_{k \ge 0}$ and iterates $(x_k, v_k, y_k)_{k\ge 1}$ given by R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}). 
         Then for all $k \ge 1$, the iterates $(x_{k + 1}, y_{k + 1})_{k \ge 1}$ are algebraically equivalent to: 
@@
 
-    \begin{lemma}[First specialized R-WAPG sequence]\label{lemma:special-rwapg-convergence-claim}
+    \begin{lemma}[FISTA sequence as R-WAPG sequences]
 
@@
 
-    \begin{lemma}[Inverted Chambolle, Dossal 2015 sequence]
-        Choose any $a \ge 2$.
+    \begin{lemma}[Chambolle, Dossal 2015 sequences as R-WAPG sequences]
+        Fix rabitrary $a \ge 2$.
         Define $\forall k \ge 1$ the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ by 
@@
         \end{align*}
-        If $\mu = 0$, then $\alpha_k, \rho_k$ satisfies Definition \ref{def:rwapg-seq}. 
+        Then $\alpha_k, \rho_k$ satisfies Definition \ref{def:rwapg-seq} with $\mu = 0$. 
         It is a valid choice of sequence for the R-WAPG algorithm and it has $\rho_k \ge 1$ for all $k \ge 0$. 

### 2024-12-20 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
 
-    \cite{nesterov_lectures_2018}
+    \todoinline{Write this abstract when finishing. }
 \end{abstract}
@@
 \section{Introduction}
-    Suppose we are minimizing a differentiable convex function $F$ for simplicity. 
-    In addition, assuming the function is $\RR^n$, so it's full domain and $F$ is Lipschitz smooth meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$.
+    Suppose we are minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$ for simplicity. 
+    Let $F$ be Lipschitz smooth meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$. 
     \par 
@@
     \par
-    Inspired by prior works and the method of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, we present to you firstly, an alternative to restarting that performs well empirically and along with it.
+    Inspired by prior works and the method of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, we present to you firstly, an alternative to restarting that performs well empirically. 
     Secondly, a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG). 
@@
         \end{align*}
-        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces perfectly to the a variant proposed in Chambolle Dossal \cite{chambolle_convergence_2015} and it has the same convergence claim as in the literatures.
+        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces perfectly to a variant of FISTA proposed in Chambolle Dossal \cite{chambolle_convergence_2015} with the same convergence claim.
         And when $\rho_k = 1$, R-WAPG reduces perfectly to V-FISTA by Beck \cite{beck_first-order_2017} if $\mu > 0$ and FISTA if $\mu = 0$ and the convergence claim is consistent with the literatures.
@@
     It describes the R-WAPG algorithm which generates iterates $(x_k, y_k, v_k)$ and admits potential convergence claim using Proposition \ref{prop:stepwise-lyapunov}. 
-    It introduces the procedures of making the sequence $\alpha_k \in (0, 1)$ which assists with claiming convergence of the algorithm using Proposition \ref{prop:stepwise-lyapunov} by connecting them together.
+    Definition \ref{def:rwapg-seq} introduces the concept of an R-WAPG sequences which is crucially important. 
+    The sequence formulates the R-WAPG algorithm stated in Definition \ref{def:wapg}, it connects the step-wise formulation of R-WAPG (Definition \ref{def:stepwise-wapg}) and describes the convergence claim of R-WAPG in Proposition \ref{prop:wagp-convergence}.
+    In the next section, it continues to play a crucial role in describing several equivalent forms of the R-WAPG algorithm, and their convergence claim. 
     \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}\;\\
         Assume $0 \le \mu < L$. 
-        The sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge1}$ are valid for R-WAPG all the following holds: 
+        The sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge1}$ are sequences parameterized by $\mu, L$. 
+        They are valid for R-WAPG if all the following holds: 
         \begin{align*}
@@
         The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for $k\ge 1$ by the procedures:  
+        \begin{tcolorbox}
+            For $k=1, 2, 3, \cdots$
             \begin{align*}
@@
             \end{align*}    
+        \end{tcolorbox}
     \end{definition}
@@
         So $\gamma_k, \hat \gamma_{k + 1}, \alpha_k$ fits Definition \ref{def:stepwise-wapg}. 
-        The definition of $R_k$ given is the same as in Proposition \ref{prop:stepwise-lyapunov} hence we can use Proposition \ref{prop:stepwise-lyapunov} to un roll recursively for all $k \ge 1$: 
+        The definition of $R_k$ given is the same as in Proposition \ref{prop:stepwise-lyapunov} hence we can use Proposition \ref{prop:stepwise-lyapunov} to unroll recursively for all $k \ge 1$: 
         {\small
@@
             \left(
-                F(x_1) - F^* + R_1 + \frac{\gamma_1}{2}\Vert v_1 - x^*\Vert^2
+                F(x_1) - F^* + R_1 + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
             \right). 
@@
             \left(
-                F(x_1) - F^* + \frac{\gamma_1}{2}\Vert v_1 - x^*\Vert^2
+                F(x_1) - F^* + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
             \right). 
@@
         Given any initial $(x_1, v_1)$, and a sequence $(\tau_k)_{k \ge 1}, (\xi_k)_{k \ge 1}$ such that for all $k \ge 1$ $\tau_k \in (0, 1), \xi_k \in (0, 1)$. 
-        for all $k\ge 1$, iterates $(y_k, z_{k + 1}, x_{k + 1})_{k \ge 1}$ satisfies recursively that: 
+        For all $k\ge 1$, iterates $(y_k, z_{k + 1}, x_{k + 1})_{k \ge 1}$ satisfies recursively that: 
         \begin{align*}
@@
     \end{proof}
-
-    \subsection{Narrowing it down}
+    \subsection{Listing the euivalent representations of R-WAPG}
+        This section lists three equivalent representations of the R-WAPG algorithm. 
+        They are comparable to existing APG algorithms in the literatures. 
+        \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
+            Assume $\mu < L$ and let $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 
+            Initialize any $x_1, v_1$ in $\RR^n$. 
+            For $k \ge 1$, the algorithm generates sequence of vector iterates $(y_{k}, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by the procedures: 
+            \begin{tcolorbox}
+                For $k = 1, 2, \cdots$
+                \begin{align*} 
+                    & y_{k} = 
+                    \left(
+                        1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
+                    \right)^{-1}
+                    \left(
+                        v_{k + 1} + 
+                        \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
+                    \right), 
+                    \\
+                    & x_{k + 1} = 
+                    y_k - L^{-1} \mathcal G_L y_k, 
+                    \\
+                    & v_{k + 1} = 
+                    \left(
+                        1 + \frac{\mu}{L \alpha_k - \mu}
+                    \right)^{-1}
+                    \left(
+                        v_k + 
+                        \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
+                    \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
+                \end{align*}
+            \end{tcolorbox}
+        \end{definition}
+        \begin{definition}[R-WAPG similar triangle form]\label{def:r-wapg-st-form} \; \\
+            Given any $(x_1, v_1)$ in $\RR^n$. 
+            Assume $\mu < L$.
+            Let the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k\ge 0}$ be given by Definition \ref{def:rwapg-seq}. 
+            For $k \ge 1$, the algorithm generates sequences of vector iterates $(y_k, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by the procedures: 
+            \begin{tcolorbox}
+                For $k=1, 2, \cdots $
+                \begin{align*}
+                    & y_k = 
+                    \left(
+                        1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
+                    \right)^{-1}
+                    \left(
+                        v_k + 
+                        \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
+                    \right), 
+                    \\
+                    & x_{k + 1} = 
+                    y_k - L^{-1} \mathcal G_L y_k, 
+                    \\
+                    & v_{k + 1} = 
+                    x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k). 
+                \end{align*}    
+            \end{tcolorbox}
+        \end{definition}
+        \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
+            For any $y_1 = x_1 \in \RR^n$, $(\rho_k)_{k \ge 0}, (\alpha_k)_{k\ge 0}$ given by Definition \ref{def:rwapg-seq}. 
+            The algorithm generates iterates $x_{k + 1}, y_{k + 1}$ For $k = 1, 2, \cdots $ by the procedures: 
+            \begin{tcolorbox}
+                For $k=1, 2,\cdots $
+                \begin{align*}
+                    & x_{k + 1} = y_k - L^{-1}\mathcal G_Ly_k, 
+                    \\
+                    & 
+                    y_{k + 1} = 
+                    x_{k + 1} + 
+                    \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
+                \end{align*}    
+            \end{tcolorbox}
+
+            In the special case where $\mu = 0$, the momentum term can be represented without relaxation parameter $\rho_k$: 
+            $$
+                (\forall k \ge 1)\quad \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}} 
+                = \alpha_{k + 1}(\alpha_k^{-1} - 1).  
+            $$
+        \end{definition}
+        \begin{remark}
+           \todo[inline]{Consider adding a remark here on how this is similar in format to the Nesterov's accelerated gradient (2.2.19) in his book. }
+        \end{remark}
+
+    \subsection{Proving the equivalent representations of R-WAPG}
         \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\
@@
             \end{align*}
-
         \end{proposition}
@@
         \end{proof}
-        \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
-            Assume $\mu < L$ and let $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 
-            Initialize any $x_1, v_1$ in $\RR^n$. 
-            For $k = 1, 2, \cdots $, the algorithm generates sequence of vector iterates $(y_{k}, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by: 
-            \begin{align*} 
-                & y_{k} = 
-                \left(
-                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
-                \right)^{-1}
-                \left(
-                    v_{k + 1} + 
-                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
-                \right)
-                \\
-                & x_{k + 1} = 
-                y_k - L^{-1} \mathcal G_L y_k, 
-                \\
-                & v_{k + 1} = 
-                \left(
-                    1 + \frac{\mu}{L \alpha_k - \mu}
-                \right)^{-1}
-                \left(
-                    v_k + 
-                    \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
-                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
-            \end{align*}
-        \end{definition}
+
         \begin{proposition}[Second equivalent representation of R-WAPG]\label{prop:wagp-st-form}\;\\
@@
         \end{proof}
-    \begin{definition}[R-WAPG similar triangle form]\label{def:r-wapg-st-form} \; \\
-        Given any $(x_1, v_1)$ in $\RR^n$. 
-        Assume $\mu < L$.
-        Let the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k\ge 0}$ be given by Definition \ref{def:rwapg-seq}. 
-        For $k = 1, 2, \cdots $, the algorithm generates sequences of vector iterates $(y_k, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by the procedures: 
-        \begin{align*}
-            & y_k = 
-            \left(
-                1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
-            \right)^{-1}
-            \left(
-                v_k + 
-                \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
-            \right), 
-            \\
-            & x_{k + 1} = 
-            y_k - L^{-1} \mathcal G_L y_k, 
-            \\
-            & v_{k + 1} = 
-            x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k). 
-        \end{align*}
-    \end{definition}
 
@@
     \end{proposition}
-
     \begin{proof}
@@
 
-    \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
-        For any $y_1 = x_1 \in \RR^n$, $(\rho_k)_{k \ge 0}, (\alpha_k)_{k\ge 0}$ given by Definition \ref{def:rwapg-seq}. 
-        The algorithm generates iterates $x_{k + 1}, y_{k + 1}$ For $k = 1, 2, \cdots $ by the procedures: 
-        \begin{align*}
-            & x_{k + 1} = y_k - L^{-1}\mathcal G_Ly_k, 
-            \\
-            & 
-            y_{k + 1} = 
-            x_{k + 1} + 
-            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
-        \end{align*}
-        In the special case where $\mu = 0$, the momentum term can be represented without relaxation parameter $\rho_k$: 
-        $$
-            (\forall k \ge 1)\quad \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}} 
-            = \alpha_{k + 1}(\alpha_k^{-1} - 1).  
-        $$
-    \end{definition}
-    \begin{remark}
-        % \textcolor{red}
-        % {
-        % There exists a choice of $\rho_k \in (0, 1], \mu = 0$ such that the above algorithm is equivalent to Chambolle, Dossal 2015 \cite{chambolle_convergence_2015}. 
-        % When $\rho_k = 1$, this becomes just FISTA \cite{beck_fast_2009}. 
-        % When $L > \mu > 0$, then choosing $\rho_k = 1$ yields equation 
-        % \begin{align*}
-        %     L \alpha_{k + 1}^2 = (1- \alpha_{k + 1})L \alpha_k^2 + \alpha_{k + 1} \mu. 
-        % \end{align*}
-        % Here, if we assume sequence $\alpha_k$ is constant, then $\alpha_k = \sqrt{\mu/L}$ is a solution to the above iterative equation. 
-        % Substituting it back to the momentum form of R-WAPG, we recover the V-FISTA algorithm, which appears as (10.7.7) in Beck's Book \cite{beck_first-order_2017}. 
-        % }
-    \end{remark}
-
-\subsection{R-WAPG describes existing accelerations scheme in the literatures}
-
-    \begin{lemma}[FISTA sequence as R-WAPG sequences]
-
+\section{R-WAPG describes existing accelerations scheme in the literatures}
+    In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are also descriptive and they generalizes many existing sequences used in accelerated proximal gradient schemes.
+    \par
+    This section demonstrates that several variants of FISTA in the literatures reduces to the R-WAPG method by setting up the R-WAPG sequences with additional assumptions. 
+    This section will also demonstrates that the convergence claim (Proposition \ref{prop:wagp-convergence}) holds and it derives convergence rates consistent with results in the literatures.  
+    \begin{lemma}[R-WAPG sequences as Inverted FISTA sequence]
+        Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 
+        If $\mu = 0, \rho_k \ge 1\; \forall k \ge 0$, and $\alpha_0 = 1$, then: 
+        \begin{enumerate}
+            \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$
+            \item $\alpha_k \ge \alpha_{k + 1}; \forall k \ge 0$
+            \item Let $t_k := \alpha_k^{-1}$, then $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``Inverted FISTA sequence''. 
+            \item $\prod_{i = 1}^k\max(1, \rho_{k - 1})(1 - \alpha_k) = \alpha_k^2 \;(\forall k \ge 0)$. 
+        \end{enumerate}
     \end{lemma}
+    \begin{proof}
+
+    \end{proof}
 
@@
         \end{align*}
-        Then $\alpha_k, \rho_k$ satisfies Definition \ref{def:rwapg-seq} with $\mu = 0$. 
-        It is a valid choice of sequence for the R-WAPG algorithm and it has $\rho_k \ge 1$ for all $k \ge 0$. 
+        If $\mu = 0$, $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid R-WAPG sequence that satisfies Definition \ref{def:rwapg-seq}. 
+        Applying this sequence to Definition \ref{def:r-wapg-momentum-form}, which is the the momentum form of R-WAPG, then R-WAPG is reduced to the following scheme: 
+        \begin{align*}
+        \end{align*}
     \end{lemma}

### 2024-12-20 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
     Suppose we are minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$ for simplicity. 
-    Let $F$ be Lipschitz smooth meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$. 
+    Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ stronlyg convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$.
+
     \par 
-    A good choice of a minimization algorithm is the Nesterov's acceleration schemes that originally proposed in 1983 \cite{nesterov_method_1983}.
+    A good choice of a minimization algorithm is the Nesterov's acceleration scheme which was originally proposed in 1983 \cite{nesterov_method_1983}. 
     Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
@@
     Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
-    Beck and Toubelle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it $\mathcal O(1/k^2)$ convergence rate is kept and it performs empirically better. 
+    Beck and Toubelle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it $\mathcal O(1/k^2)$ convergence rate is kept, and it performs empirically better. 
     See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm. 
@@
         Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''. 
-        The choices for $\theta_k$ varies. 
-        In Chamboolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ gives strong weak convergence of the iterates $x_k$ in Hilbert space. 
-        In Beck \cite{beck_first-order_2017}, it has constant $\theta_t = (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa = \mu/L$. 
+        The choices for $\theta_k$ varies for different varints of the accelerated proximal gradient algorithm. 
+        In Chamboolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ gives weak convergence of the iterates $x_k$ in Hilbert space. 
+        In Chapter 10 of Beck's Book \cite{beck_first-order_2017}, a variant called V-FISTA can achieve the faster linear convergencec rate: $\mathcal O((1 - \sqrt{\mu/L})^k)$ on the optimality gap for $\mu > 0$ strongly convex $F$.
+        V-FISTA has $\theta_t = (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa = \mu/L$. 
         \par
@@
         \end{align*}
-        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces perfectly to a variant of FISTA proposed in Chambolle Dossal \cite{chambolle_convergence_2015} with the same convergence claim.
-        And when $\rho_k = 1$, R-WAPG reduces perfectly to V-FISTA by Beck \cite{beck_first-order_2017} if $\mu > 0$ and FISTA if $\mu = 0$ and the convergence claim is consistent with the literatures.
+        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate.
+        And when $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}, which is an optimal algorithm for a strongly convex $F$.
+        R-WAPG gives the a convergence claim, and it's consistent with the literatures. 
         \par

### 2024-12-20 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
         The choices for $\theta_k$ varies for different varints of the accelerated proximal gradient algorithm. 
-        In Chamboolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ gives weak convergence of the iterates $x_k$ in Hilbert space. 
+        In Chamboolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space. 
         In Chapter 10 of Beck's Book \cite{beck_first-order_2017}, a variant called V-FISTA can achieve the faster linear convergencec rate: $\mathcal O((1 - \sqrt{\mu/L})^k)$ on the optimality gap for $\mu > 0$ strongly convex $F$.
@@
         \par
-        Firstly, we relaxed the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example_algorithm} and showed an upper bound of the optimal gap. 
+        We relax the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example_algorithm} and showed an upper bound of the optimal gap. 
         Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
@@
 \section{R-WAPG describes existing accelerations scheme in the literatures}
-    In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are also descriptive and they generalizes many existing sequences used in accelerated proximal gradient schemes.
+    In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are descriptive. 
+    They generalizes many existing sequences used in accelerated proximal gradient schemes. 
     \par

### 2024-12-20 Notebook LaTEX/Momentum Accelerations/paper3.tex
TwT, fixes

@@
     \end{observation}
-    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
-        \; \\
+
+    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}\;\\
         Choose any $x_1 \in \RR^n, v_1 \in \RR^n$. 
@@
         Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$. 
-        Let vector sequence $(y_k, v_{k}, x_{k})_{k \ge 1}$ and scalar sequences $\alpha_k, \rho_k$ be generated from Definition \ref{def:wapg}. 
+        Let vector sequence $(y_k, v_{k}, x_{k})_{k \ge 1}$ and R-WAPG sequences $\alpha_k, \rho_k$ be given by Definition \ref{def:wapg}. 
         Define $R_1 = 0$ and suppose that for $k = 1, 2, \cdots, N$, we have $R_k$ recursively given by: 

### 2024-12-20 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
     \end{proof}
-    \subsection{Listing the euivalent representations of R-WAPG}
+    \subsection{A list of equivalent representations of R-WAPG}
         This section lists three equivalent representations of the R-WAPG algorithm. 
@@
         \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
-            For any $y_1 = x_1 \in \RR^n$, $(\rho_k)_{k \ge 0}, (\alpha_k)_{k\ge 0}$ given by Definition \ref{def:rwapg-seq}. 
+            Given any $y_1 = x_1 \in \RR^n$, and sequences $(\rho_k)_{k \ge 0}, (\alpha_k)_{k\ge 0}$ Definition \ref{def:rwapg-seq}. 
             The algorithm generates iterates $x_{k + 1}, y_{k + 1}$ For $k = 1, 2, \cdots $ by the procedures: 
@@
             \end{tcolorbox}
-
             In the special case where $\mu = 0$, the momentum term can be represented without relaxation parameter $\rho_k$: 
@@
         \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\
-            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}). 
-            Then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$, and for all $k\ge 1$ they are algebraically equivalent to
+            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}), 
+            then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$, and for all $k\ge 1$ they are algebraically equivalent to
             \begin{align*}
@@
                 - \alpha_k\hat \gamma_{k + 1}^{-1}\mathcal G_L y_k
-                % \\
-                % &= 
-                % \left(
-                %     1 + \frac{\alpha_k\mu}{(1 -\alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2}
-                % \right)^{-1}
-                % \left(
-                %     v_k + 
-                %     \frac{\alpha_k\mu}{(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2} y_k
-                % \right)
-                % - \frac{1}{L\alpha_{k}}\mathcal G_L y_k
                 \\

### 2024-12-20 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
     Convergence results from Proposition \ref{prop:wagp-convergence} applies to all these equivalent forms of R-WAPG. 
+    In brief, the relations of these Propositions and Definitions can be summarized by
+    \begin{align*}
+        & \text{Definition } \ref{def:wapg} 
+        \\
+        & \iff 
+        \text{Definition } \ref{def:r-wapg-intermediate} & \text{By Proposition }\ref{prop:wapg-first-equivalent-repr}
+        \\
+        & \iff \text{Definition }\ref{def:r-wapg-st-form} & \text{By Proposition }\ref{def:r-wapg-st-form} 
+        \\
+        & \;\implies 
+        \text{Definition }\ref{def:r-wapg-momentum-form}. 
+        & \text{By Proposition }\ref{prop:r-wapg-momentum-repr}
+    \end{align*}
 
@@
         \end{align*}
-        Now substituting $v_{k + 1}$ into $y_{k + 1}$ so it has for all $k\ge 1$ : 
+        Now substituting $v_{k + 1}$ into $y_{k + 1}$, so it has for all $k\ge 1$: 
         {\small
@@
     In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are descriptive. 
-    They generalizes many existing sequences used in accelerated proximal gradient schemes. 
+    They generalize many existing sequences used in accelerated proximal gradient schemes. 
     \par
     This section demonstrates that several variants of FISTA in the literatures reduces to the R-WAPG method by setting up the R-WAPG sequences with additional assumptions. 
-    This section will also demonstrates that the convergence claim (Proposition \ref{prop:wagp-convergence}) holds and it derives convergence rates consistent with results in the literatures.  
+    This section will also demonstrate that the convergence claim (Proposition \ref{prop:wagp-convergence}) holds, and it derives convergence rates consistent with results in the literatures.  
     \begin{lemma}[R-WAPG sequences as Inverted FISTA sequence]
@@
             \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$
-            \item $\alpha_k \ge \alpha_{k + 1}; \forall k \ge 0$
             \item Let $t_k := \alpha_k^{-1}$, then $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``Inverted FISTA sequence''. 
-            \item $\prod_{i = 1}^k\max(1, \rho_{k - 1})(1 - \alpha_k) = \alpha_k^2 \;(\forall k \ge 0)$. 
+            \item $\prod_{i = 1}^k\max(1, \rho_{k - 1})(1 - \alpha_k) = \alpha_k^2 \quad (\forall k \ge 1)$. 
         \end{enumerate}
@@
     \begin{proof}
+        We start proving (i). 
+        For all $k \ge 1$: 
+        \begin{align*}
+            \alpha_{k + 1}^2 
+            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 + (\mu/L) \alpha_k
+            \\
+            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 & \mu = 0 \text{ assumed } 
+            \\
+            \implies 
+            \alpha_{k + 1}^2 
+            & \ge (1 - \alpha_{k + 1})\alpha_k^2 
+            &  \rho_k \ge 1
+            \\
+            \iff 
+            \alpha_k^{-1} 
+            &\ge 
+            \alpha_{k + 1}^{-2} + \alpha_{k + 1}^{-1}. 
+        \end{align*}
+        When $k = 0$, it has $\alpha_0 = 1$. 
+        By definition of $\rho_0$ we have 
+        \begin{align*}
+            \alpha_1^2 &= 
+            (1 - \alpha_1)\alpha_0^2\rho_0 \underset{\mu = 0}{=}
+            \frac{\alpha_1^2}{\alpha_0^2(1 - \alpha_1)}(1 - \alpha_1)\alpha_0^2 = \alpha_1^2. 
+        \end{align*}
+        Therefore (i) holds. 
+        (i) is proved. 
+        \par
+        (i) $\implies$ (ii) because substituting $\alpha_k^{-1} = t_k$ changes (i) into $t_{k + 1}^2 - t_{k + 1} - t_{k}^2 \le 0$ for all $k \ge 0$. 
+        Solving the equality yields $t_{k + 1} = (1/2)\left(1 \pm \sqrt{1 + 4 t_k^2}\right)$ for all $k \ge 0$. 
+        Since $\alpha_k \in (0, 1)$, it means $t_k > 0$, hence the valid root is the larger root which gives the upper bound for $t_{k + 1}$ so: 
+        \begin{align*}
+            t_{k + 1} \in \left(
+                0, \frac{1}{2}\left(1 + \sqrt{1 + 4t_k^2}\right) 
+            \right]
+        \end{align*}
+        To prove (iii), because $\rho_k \ge 1$, we have $\prod_{i = 1}^{k} \max(1, \rho_{k - 1})(1 - 
+        \alpha_k)$ for all $k \ge 1 = \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)$. 
+        By definition $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ sequences they have for all $k \ge 1$: 
+        \begin{align*}
+            \alpha_k^2 &= \rho_{k - 1}(1 - \alpha_k)\alpha_{k - 1}^2
+            \\
+            \iff 
+            \alpha_k^2/\alpha_{k - 1}^2 &= \rho_{k - 1}(1 - \alpha_k)
+            \\
+            \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)
+            &= 
+            \prod_{i = 1}^{k}\alpha_k^2 /\alpha_{k - 1}^2= \alpha_k^2/\alpha_0. 
+        \end{align*}
+        Because $\alpha_0 = 1$, (iii) is justified.
 
@@
 
-    \begin{lemma}[Chambolle, Dossal 2015 sequences as R-WAPG sequences]
+    \begin{lemma}[Chambolle, Dossal 2015 sequences as R-WAPG sequences]\;\\
         Fix rabitrary $a \ge 2$.
@@
         If $\mu = 0$, $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid R-WAPG sequence that satisfies Definition \ref{def:rwapg-seq}. 
-        Applying this sequence to Definition \ref{def:r-wapg-momentum-form}, which is the the momentum form of R-WAPG, then R-WAPG is reduced to the following scheme: 
+        Applying this sequence to Definition \ref{def:r-wapg-momentum-form}, which is the momentum form of R-WAPG, then R-WAPG is reduced to the following scheme: 
         \begin{align*}

### 2024-12-20 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
     Suppose we are minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$ for simplicity. 
-    Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ stronlyg convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$.
+    Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$.
 
@@
     \end{align}\label{eqn:example_algorithm}
-    It's well known that if the minimizer $x^*$ exists, $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, faster than the gradient descent method which is $\mathcal O(1/k)$, and it's optimal.
+    It's well known that if the minimizer $x^*$ exists, then the optimality gap $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, faster than the gradient descent method which is $\mathcal O(1/k)$, and it's optimal.
     See Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018}. 
@@
         And when $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}, which is an optimal algorithm for a strongly convex $F$.
-        R-WAPG gives the a convergence claim, and it's consistent with the literatures. 
+        R-WAPG gives the convergence claim, and it's consistent with the literatures. 
         \par
@@
     \subsection{Prior works}
+        \todoinline{The following are notes to the writer.
+There is in fact little prior works in this regard.
+People tried to unify all the variants but all of them are trying to unify the convergence claims under one theorem.
+Flexible choices of the momentum parameters are the prime focus in heavy ball momentum, or FISTA with Hessian Damping.
+Their approaches are usually using dynamical system.
+}
 
     \subsection{Organizations}
+        \todoinline{This will be written once most of the contents in the paper are settled. }
 
 \section{Preliminaries}
-    Throughout, we assume the problem of types $F = f + g$ where $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: Q \rightarrow \overline \RR$ is convex. 
-    We consider optimization problem: $\min_x \left\lbrace F(x) \defeq f(x) + g(x)\right\rbrace$.
-    Fix arbitrary $y \in \RR^n$, define
+    Throughout, we define $F := f + g$ where $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: Q \rightarrow \overline \RR$ is convex. 
+    We consider optimization problem: $\min_x \left\lbrace f(x) + g(x)\right\rbrace$.
+    Fix any arbitrary $y \in \RR^n$, define for all $x \in Q$: 
     \begin{align*}
         \widetilde{\mathcal M}^{L^{-1}}
-        (x; y) \defeq
+        (x; y) 
+        &:=
         g(x) + f(y) + \langle \nabla f(y), x - y\rangle 
@@
         \\
-        \mathcal M^{L^{-1}}(x; y) := F(x) + \frac{L}{2}\Vert x - y\Vert^2, 
-    \end{align*}
-    and the proximal gradient operator $T_L = [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f]$. 
-    Define the Bregman divergence of $f$: 
+        \mathcal M^{L^{-1}}(x; y) &:= F(x) + \frac{L}{2}\Vert x - y\Vert^2, 
+    \end{align*}
+    and the proximal gradient operator $T_L := [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f]$. 
+    The proximal gradient operator $T_L$ admits 
+    $$
+        T_Ly = \argmin_x \left\lbrace
+            g(x) + \langle \nabla f(y), x\rangle + L/2\Vert x - y\Vert^2
+        \right\rbrace. 
+    $$
+    It is a single valued mapping and it has its domain on the entire $\RR^n$. 
+    Another operator often associated with $T_L$ is the gradient mapping operator $\mathcal G_L:= L(I - T_L)$. 
+    Finally, define the Bregman divergence of $f$: 
     \begin{align*}
@@
     \begin{lemma}[Proximal gradient envelope] 
-        Fix any $y$, we will have for all $x \in \RR^n$ that: 
+        Fix any $y \in \RR^n$, we will have for all $x \in Q$ that: 
         \begin{align*}
@@
     \begin{theorem}[Proximal inequality]\label{thm:prox-grad-ineq}
-        Fix any $y$, we have for all $x$: 
+        Fix any $y\in \RR^n$, we have for all $x \in Q$: 
         \begin{align*}
@@
     \begin{proof}
-        Observe that the function $\widetilde {\mathcal M}(\cdot; x)$ is $L$ strongly convex with minimizer $T_Ly$. 
-        For all $x \in \RR^n$, it has quadratic growth condition at its minimizer $T_Ly$ which gives these equivalent inequalities: 
+        Observe that the function $\widetilde {\mathcal M}(\cdot; y)$ is $L$ strongly convex with minimizer $T_Ly$. 
+        For all $x \in Q$, it has quadratic growth condition at its minimizer $T_Ly$ which gives these equivalent inequalities: 
         {\small
@@
         Then we show (3*) equals to (3.1*). 
-        The content of the entire LHS of the conclusion of the claim is conclused in (3.2*). 
+        The content of the entire LHS of the inequality we want to prove is in (3.2*). 
         Going from (3.2*) to (4*) is an inequality which we used Theorem \ref{thm:prox-grad-ineq}. 
@@
             \left(
-                F(x_1) - F(x^*) + \frac{\gamma_1}{2}\Vert v_1 - x^*\Vert^2
+                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
             \right). 
@@
     Convergence results from Proposition \ref{prop:wagp-convergence} applies to all these equivalent forms of R-WAPG. 
-    In brief, the relations of these Propositions and Definitions can be summarized by
+    In brief, the relations of these proposition and definitions can be summarized by
     \begin{align*}
@@
         & \iff 
-        \text{Definition } \ref{def:r-wapg-intermediate} & \text{By Proposition }\ref{prop:wapg-first-equivalent-repr}
-        \\
-        & \iff \text{Definition }\ref{def:r-wapg-st-form} & \text{By Proposition }\ref{def:r-wapg-st-form} 
+        \text{Definition } \ref{def:r-wapg-intermediate} & \text{By Proposition }\ref{prop:wapg-first-equivalent-repr}.
+        \\
+        & \iff \text{Definition }\ref{def:r-wapg-st-form} & \text{By Proposition }\ref{def:r-wapg-st-form}.
         \\
@@
         \text{Definition }\ref{def:r-wapg-momentum-form}. 
-        & \text{By Proposition }\ref{prop:r-wapg-momentum-repr}
+        & \text{By Proposition }\ref{prop:r-wapg-momentum-repr}.
     \end{align*}
@@
     This section will also demonstrate that the convergence claim (Proposition \ref{prop:wagp-convergence}) holds, and it derives convergence rates consistent with results in the literatures.  
-    \begin{lemma}[R-WAPG sequences as Inverted FISTA sequence]
+    \begin{lemma}[R-WAPG sequences as inverted FISTA sequence]\label{lemma:inverted-fista-seq}
         Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 
@@
         Because $\alpha_0 = 1$, (iii) is justified. 
-
     \end{proof}
-
-    \begin{lemma}[Chambolle, Dossal 2015 sequences as R-WAPG sequences]\;\\
-        Fix rabitrary $a \ge 2$.
+    \begin{remark}
+        The sequence $t_k$ is exactly the same as in Theorem 3.1 of Chmabolle, Dossal \cite{chambolle_convergence_2015}. 
+    \end{remark}
+
+    \begin{lemma}[Constant R-WAPG sequences]\label{lemma:constant-rwapg-seq}
+        Suppose $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are R-WAPG sequences given by Definition \ref{def:rwapg-seq} and they are constant meaning that there exists $\rho, \alpha$ such that $\alpha_k = \alpha$ and $\rho_k = \rho$ for all $k \ge 0$.
+        Define the momentum term $\theta = \rho\alpha(1 - \alpha)/(\rho\alpha^2 + \alpha)$. 
+        Then the constant R-WAPG sequence satisfies: 
+        \begin{enumerate}
+            \item $\rho = (1 - \mu/L\alpha^{-1})/(1 - \alpha)$. 
+            \item $\theta = (1 - \mu/L)(1 - \alpha)/(-\mu/L \alpha + 2\alpha - \alpha^2)$. 
+            \item If $\alpha = \sqrt{\mu/L}$, then $\rho = 1$, $\theta = (1 - \sqrt{\mu/L})/(1 + \sqrt{\mu/L})$. 
+        \end{enumerate}
+    \end{lemma}
+
+    \begin{theorem}[FISTA first variant Chambolle, Dossal 2015]\;\\
+        Fix arbitrary $a \ge 2$.
         Define $\forall k \ge 1$ the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ by 
@@
         \end{align*}
-        If $\mu = 0$, $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid R-WAPG sequence that satisfies Definition \ref{def:rwapg-seq}. 
-        Applying this sequence to Definition \ref{def:r-wapg-momentum-form}, which is the momentum form of R-WAPG, then R-WAPG is reduced to the following scheme: 
-        \begin{align*}
-        \end{align*}
-    \end{lemma}
+        Consider the algorithm given by: 
+        \begin{tcolorbox}
+            Initialize any $y_1 = x_1$. 
+            \\
+            For $k = 1, 2, \cdots$, update: 
+            \begin{align*}
+                & x_{k + 1} := y_k + L^{-1}\mathcal G_L(y_k), 
+                \\
+                & \theta_{t + 1} := \alpha_{k + 1}(\alpha_k^{-1} - 1),
+                \\
+                & y_{k + 1} := x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
+            \end{align*}    
+        \end{tcolorbox}
+        If $\mu = 0$, then $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid pair of R-WAPG sequence from Definition \ref{def:rwapg-seq} and the above algorithm is a valid form of R-WAPG. 
+        \par
+        Assume minimizer $x^*$ exists for function $F$. 
+        Then algorithm produces $(x_k)_{k \ge0}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O(1/k^2)$. 
+    \end{theorem}
     \begin{proof}
-
+        We only need to show that $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are valid R-WAPG sequences. 
+        To do that we verify equality $\alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_k \alpha_k^2$ because it's assumed $\mu = 0$ in this case. 
+        For all $k \ge 0$, the right side of the equality evaluates to 
+        \begin{align*}
+            \alpha_k^2 \rho_k(1 - \alpha_{k + 1}) &= 
+            \left(
+                \frac{\alpha}{k + 1}
+            \right)^2 \left(
+                \frac{(k + a)^2}{(k + 1)(k + a + 1)}
+            \right)
+            \left(
+                1 - \frac{a}{k + 1 + a}
+            \right)
+            \\
+            &= \left(
+                \frac{\alpha}{k + 1}
+            \right)^2 \left(
+                \frac{(k + a)^2}{(k + 1)(k + a + 1)}
+            \right)
+            \left(
+                \frac{k + 1}{k + 1 + a}
+            \right)
+            \\
+            &= \frac{a^2}{(k + a + 1)^2} = \alpha_{k + 1}^2. 
+        \end{align*}
+        Therefore, $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ is a pair of valid R-WAPG sequence. 
+        So, it can be used in the R-WAPG algorithm and represent it in R-WAPG Momentum Form in Definition \ref{def:r-wapg-momentum-form}. 
+        Using $\mu = 0$, it simplifies the momentum term in Definition \ref{def:r-wapg-momentum-form} and gives the rules of updates in the theorem statement. 
+        \par
+        Next, we show the convergence rate of the algorithm. 
+        Observe that $(\forall k \ge 0)(\forall a \ge 2)$, $\rho_k$ has 
+        \begin{align*}
+            \rho_k &= \frac{(k + a)^2}{(k + 1)(k + a + 1)} 
+            \\
+            &> \frac{(k + 1)^2}{(k + 1)(k + a + 1)} 
+            & \text{By } a \ge 2. 
+            \\
+            &= \frac{(k + 1)}{(k + a + 1)} 
+            \\
+            & > 1.   & \text{By } a > 2. 
+        \end{align*}
+        Hence (iii) in Lemma \ref{lemma:inverted-fista-seq} applies. 
+        We may use Proposition \ref{prop:wagp-convergence} by the validity of our $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ sequences, we have:
+        \begin{align*}
+            & F(x_{k + 1}) - F(x^*) + \frac{L\alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
+            \\
+            & = F(x_{k + 1}) - F(x^*) + \frac{L\alpha_k^2}{2}\Vert x_{k + 1} - x^* + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k)\Vert^2
+            \\
+            & \le 
+            \left(
+                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
+            \right)
+            \left(
+                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
+            \right)
+            \left(
+                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
+            \right)
+            \\
+            &= 
+            \alpha_k^2
+            \left(
+                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
+            \right) 
+            & \text{By Lemma \ref{lemma:inverted-fista-seq} (iii). }
+            \\
+            &= 
+            \left(\frac{a}{k + a}\right)^2
+            \left(
+                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert x_1 - x^*\Vert^2
+            \right). 
+        \end{align*}
+        We can replace $v_1$ to be $x_1$ by Proposition \ref{prop:r-wapg-momentum-repr}. 
     \end{proof}
-
-\subsection{The method of Inexact Momentum}
-    This section introduces an algorithm of our creation through the remark of Proposition \ref*{prop:stepwise-lyapunov}. 
+    \begin{remark}
+        This algorithm described here is exactly the same algorithm being analyzed in the paper by Chambolle, Dossal \cite{chambolle_convergence_2015}.
+
+    \end{remark}
+
+\subsection{The method of Free R-WAPG}
+    This section introduces an algorithm of our creation through the remark of Proposition \ref{prop:stepwise-lyapunov}. 
     The algorithm estimates the $\mu$ constant as the algorithm executes and pools the information using the Bregman Divergence of the smooth part function $f$. 
+    \begin{algorithm}
+    {\footnotesize
+        \label{alg:free-rwapg}
+        \begin{algorithmic}[1]
+        \STATE{\textbf{Input: } $f, g, x_0\in \RR^n, N \in \N$}
+        \STATE{\textbf{Initialize: }$x_1:= x_0; y_1 := x_0;L := 1; \mu := 1/2; \alpha_0 = 1;$}
+        \FOR{$k = 1, 2, \cdot, N$}
+            \STATE{\textbf{Compute: }$\nabla f(x_k); x^+:= [I + L^{-1}\partial g](x_k - L^{-1}\nabla f(x_k))$;}
+            \WHILE{$L/2\Vert x^+ - x\Vert^2 < D_f(x^+, x)$}
+                \STATE{$L:= L/2$;}
+                \STATE{$x^+ = [I + L^{-1}\partial g](x_k - L^{-1}\nabla f(x_k))$; }
+            \ENDWHILE
+            \STATE{$x_{k + 1} := x^+$;}
+            \STATE{$\mu:= \min(L, \mu)$;}
+            \STATE{$\alpha_{k} := (1/2)\left(\mu/L - \alpha_{k - 1}^2 + \sqrt{(\mu/L - \alpha_{k - 1}^2)^2 + 4\alpha_{k - 1}^2}\right)$;}
+            \STATE{$\theta_{k + 1} := \alpha_k(1 - \alpha_k)/(\alpha_k^2 + \alpha_{k + 1})$;}
+            \STATE{$y_{k + 1}:= x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$; }
+            \STATE{$\mu := (1/2)(2D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2) + (1/2)\mu$;}
+        \ENDFOR
+        \end{algorithmic}
+        \caption{Free R-WAPG}
+    }
+    \end{algorithm}
 

### 2024-12-20 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
     The theme of proposal highlight topics of interests that emphasize the computations and applications aspect of algorithms that exhibits both practical and theoretical importance. 
-    We summarize our ongoing research in unifying Nesterov type accelerated proximal gradient method and proposes our method of spectral momentum. 
+    We summarize our ongoing research in unifying Nesterov type accelerated proximal gradient method and proposes our Free R-WAPG method. 
     We survey literatures under the topic of Catalyst Meta Acceleration framework used in accelerating variance reduced methods in the settings of Data Science and Machine Learning. 
@@
 
-\section{Method of spectral momentum}\label{sec:spectral-momentum}
+\section{Method Free R-WAPG}\label{sec:spectral-momentum}
 

### 2024-12-20 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, big changes

@@
     However, everything is not sunshine and rainbow because the above scheme is associated with an issue. 
-    When $F$ is $\mu > 0$ strongly convex, the algorithm oscillates and converges sub-linearly, making it worse than gradient descent. See page 9 of Su et al. \cite{su_differential_2016}. 
+    When $F$ is $\mu > 0$ strongly convex, the optimality gap $F(x_k) - F(x^*)$ oscillates and converges sub-linearly, making it worse than gradient descent.
+See page 9 of Su et al.
+\cite{su_differential_2016}.
     \par
@@
     Secondly, a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG). 
-    The R-WAPG has a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(\theta_t)_{t \ge 1}$. 
+    The R-WAPG has a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(\theta_k)_{k \ge 1}$. 
     It also has descriptive power to describe several variants of FISTA in the literatures.
@@
         Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''. 
-        The choices for $\theta_k$ varies for different varints of the accelerated proximal gradient algorithm. 
+        The choices for $\theta_k$ varies for different variants of the accelerated proximal gradient algorithm. 
         In Chamboolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space. 
-        In Chapter 10 of Beck's Book \cite{beck_first-order_2017}, a variant called V-FISTA can achieve the faster linear convergencec rate: $\mathcal O((1 - \sqrt{\mu/L})^k)$ on the optimality gap for $\mu > 0$ strongly convex $F$.
+        In Chapter 10 of Beck's Book \cite{beck_first-order_2017}, a variant called V-FISTA can achieve the faster linear convergence rate: $\mathcal O((1 - \sqrt{\mu/L})^k)$ on the optimality gap for $\mu > 0$ strongly convex $F$.
         V-FISTA has $\theta_t = (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa = \mu/L$. 
@@
     \subsection{Prior works}
-        \todoinline{The following are notes to the writer.
-There is in fact little prior works in this regard.
-People tried to unify all the variants but all of them are trying to unify the convergence claims under one theorem.
-Flexible choices of the momentum parameters are the prime focus in heavy ball momentum, or FISTA with Hessian Damping.
-Their approaches are usually using dynamical system.
+        \todoinline{
+            Here is a list of papers that are relevant to generalizing the convergence claim for APG beyond just the traditional choices for the momentum sequence. 
+            \begin{enumerate}
+                \item Attouch H., Cabot A.: ``Convergence Rates of Inertial Forward-Backward Algorithms'', SIAM. 
+                \item Vassilis A., et al.: "Convergence rate of inertial Forward-Backward algorithm
+                beyond Nesterov’s rule"
+            \end{enumerate}
+            The following papers are related to stablizing, improving the acceleration scheme without monotone restarting. 
+            \begin{enumerate}
+                \item Attouch H., et al.: ``First-order optimization algorithms via inertial systems with Hessian driven damping'', Math Programming. 
+            \end{enumerate}
+
         }
@@
     \begin{lemma}[Constant R-WAPG sequences]\label{lemma:constant-rwapg-seq}
-        Suppose $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are R-WAPG sequences given by Definition \ref{def:rwapg-seq} and they are constant meaning that there exists $\rho, \alpha$ such that $\alpha_k = \alpha$ and $\rho_k = \rho$ for all $k \ge 0$.
+        Suppose $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are R-WAPG sequences given by Definition \ref{def:rwapg-seq}, and they are constant meaning that there exists $\rho, \alpha$ such that $\alpha_k := \alpha$ and $\rho_k := \rho$ for all $k \ge 0$.
         Define the momentum term $\theta = \rho\alpha(1 - \alpha)/(\rho\alpha^2 + \alpha)$. 
@@
             \item $\rho = (1 - \mu/L\alpha^{-1})/(1 - \alpha)$. 
-            \item $\theta = (1 - \mu/L)(1 - \alpha)/(-\mu/L \alpha + 2\alpha - \alpha^2)$. 
-            \item If $\alpha = \sqrt{\mu/L}$, then $\rho = 1$, $\theta = (1 - \sqrt{\mu/L})/(1 + \sqrt{\mu/L})$. 
+            \item $\theta = (1 - \alpha)(1 - \mu/L \alpha^{-1})/(1 - \mu/L)$. 
+            \item For any $r \in \left(\sqrt{\mu/L}, \sqrt{L/\mu}\right)$, let $\alpha = r \sqrt{\mu/L}$.
+If $\sqrt{L/\mu} > r > 1$, then $\rho > 1$ else if $\sqrt{\mu/L} < r \le 1$ then $\rho \in (0, 1]$.
+            \item If $\alpha = \sqrt{\mu/L}$, then $\rho = 1$, $\theta = \left(1 - \sqrt{\mu/L}\right)/\left(1 + \sqrt{\mu/L}\right)$. 
         \end{enumerate}
     \end{lemma}
+    \begin{proof}
+        It's direct to show (i). 
+        By the definition of $(\rho_k)_{k\ ge0}$ in the R-WAPG sequence definition, we have 
+        \begin{align*}
+            \rho_k &= 
+            \frac{\alpha_{k + 1}^2 - \mu/L \alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2}
+            = 
+            \frac{\alpha^2 - \mu/L \alpha}{(1 - \alpha)\alpha^2}
+            \\
+            &= \frac{1 - (\mu/L)\alpha^{-1}}{1 - \alpha}. 
+        \end{align*}
+        To see (ii), it's direct by the definition of $\theta$: 
+        \begin{align*}
+            \theta &= 
+            \frac{\rho \alpha(1 - \alpha)}{\rho \alpha^2 + \alpha} 
+            = 
+            (\rho \alpha)\frac{(1 - \alpha)}{\rho \alpha^2 + \alpha}
+            \\
+            &= \left(
+                \frac{\alpha - (\mu/L)}{1 - \alpha}
+            \right)\frac{(1 - \alpha)}{\alpha \frac{\alpha - \mu/L}{1 - \alpha} + \alpha}
+            = \frac{\alpha - \mu/L}{\alpha\left(\frac{\alpha - \mu/L}{1 - \alpha}\right)+ \alpha}
+            \\
+            &= \left(1 - \mu/L \alpha^{-1}\right)\left(
+                \frac{\alpha - \mu/L}{1 - \alpha} + 1
+            \right)^{-1} 
+            \\
+            &= 
+            \frac{(1 - \alpha)\left(1 - \mu/L \alpha^{-1}\right)}{1 - \mu/L}. 
+        \end{align*}
+        To see (iii), we substitute $\alpha = r \sqrt{\mu/L}$ into the expression for $\rho$ in (i) which gives: 
+        \begin{align*}
+            \rho_k &= \frac{1 - \mu/L\alpha^{-1}}{1 - \alpha} 
+            = \frac{1 - r^{-1}\left(\mu/L\sqrt{L/\mu}\right)}{1 - r \sqrt{\mu/L}} 
+            = \frac{1 - r^{-1}\sqrt{\mu/L}}{1 - r \sqrt{\mu/L}}. 
+        \end{align*}
+        If $\sqrt{L/\mu}> r > 1$ then $\rho > 1$ because 
+        \begin{align*}
+            \rho &= \frac{1 - r^{-1}\sqrt{\mu/L}}{1 - r \sqrt{\mu/L}} 
+            > \frac{1 - \sqrt{\mu/L}}{1 - \sqrt{\mu/L}} = 1. 
+        \end{align*}
+        When $\sqrt{\mu/L} < r < 1$, it has 
+        \begin{align*}
+            0 < 1 - r^{-1}\sqrt{\mu/L} < \frac{1 - r^{-1}\sqrt{\mu/L}}{1 - r\sqrt{\mu/L}} = \rho < \frac{1 - \sqrt{\mu/L}}{1 - \sqrt{\mu/L}} = 1. 
+        \end{align*}
+        The first inequality used $r > \sqrt{\mu/L}$. 
+        The third inequality used $r < 1$. 
+        To see (iv), substitute $\alpha = \sqrt{\mu/L}$ for $\rho$.
+
+    \end{proof}
 
@@
 
+    \begin{theorem}[Fixed momentum FISTA]\label{thm:fixed-momentum-fista}
+
+    \end{theorem}
+
 \subsection{The method of Free R-WAPG}
-    This section introduces an algorithm of our creation through the remark of Proposition \ref{prop:stepwise-lyapunov}. 
-    The algorithm estimates the $\mu$ constant as the algorithm executes and pools the information using the Bregman Divergence of the smooth part function $f$. 
+    This section introduces an algorithm of our creation inspired by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
+    Algorithm \ref{alg:free-rwapg} estimates the $\mu$ constant as the algorithm executes and pools the information using the Bregman Divergence of the smooth part function $f$. 
     \begin{algorithm}
+        \begin{algorithmic}[1]
         {\footnotesize
-        \label{alg:free-rwapg}
-        \begin{algorithmic}[1]
-        \STATE{\textbf{Input: } $f, g, x_0\in \RR^n, N \in \N$}
-        \STATE{\textbf{Initialize: }$x_1:= x_0; y_1 := x_0;L := 1; \mu := 1/2; \alpha_0 = 1;$}
-        \FOR{$k = 1, 2, \cdot, N$}
-            \STATE{\textbf{Compute: }$\nabla f(x_k); x^+:= [I + L^{-1}\partial g](x_k - L^{-1}\nabla f(x_k))$;}
-            \WHILE{$L/2\Vert x^+ - x\Vert^2 < D_f(x^+, x)$}
-                \STATE{$L:= L/2$;}
-                \STATE{$x^+ = [I + L^{-1}\partial g](x_k - L^{-1}\nabla f(x_k))$; }
+        \STATE{\textbf{Input: } $f, g, x_0, L > \mu \ge 0, \in \RR^n, N \in \N$}
+        \STATE{\textbf{Initialize: }$y_0 := x_0;L := 1; \mu := 1/2; \alpha_0 = 1;$}
+        \STATE{\textbf{Compute: } $f(y_k)$; }
+        \FOR{$k = 0, 1, 2, \cdot, N$}
+            \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$;}
+            \WHILE{$L/2\Vert x^+ - y\Vert^2 < D_f(x^+, y)$}
+                \STATE{$L:= 2L$;}
+                \STATE{$x^+ = [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$; }
             \ENDWHILE
             \STATE{$x_{k + 1} := x^+$;}
-            \STATE{$\mu:= \min(L, \mu)$;}
-            \STATE{$\alpha_{k} := (1/2)\left(\mu/L - \alpha_{k - 1}^2 + \sqrt{(\mu/L - \alpha_{k - 1}^2)^2 + 4\alpha_{k - 1}^2}\right)$;}
+            \STATE{$\alpha_{k + 1} := (1/2)\left(\mu/L - \alpha_{k}^2 + \sqrt{(\mu/L - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;}
             \STATE{$\theta_{k + 1} := \alpha_k(1 - \alpha_k)/(\alpha_k^2 + \alpha_{k + 1})$;}
             \STATE{$y_{k + 1}:= x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$; }
+            \STATE{\textbf{Compute: } $f(y_{k + 1})$}
             \STATE{$\mu := (1/2)(2D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2) + (1/2)\mu$;}
         \ENDFOR
+        }
         \end{algorithmic}
         \caption{Free R-WAPG}
-    }
+        \label{alg:free-rwapg}
     \end{algorithm}
+    \par
+    Line 5-8 estimates upper bound for the Lipschitz constant and find $x^+$, the next iterates produced by proximal gradient descent on previous $y_k$.
+    Line 9 updates $x_{k + 1}$ to be $x^+$, a successful iterate identified by the Lipschitz line search routine. 
+    Line 10 updates the R-WAPG sequence $\alpha_k$ for the iterates $y_{k + 1}$. 
+    Line 13 updates $\mu$ using the Bregman Divergence of $f$ from iterates $y_{k + 1}, y_k$. 
+    \par
+    Assume $L$ given is an upper bound of the Lipschitz smoothness constant of $f$, the algorithm computes $\nabla f(y_k)$ for $x^+$, $f(y_{k + 1})$ for Bregman Divergence and $f(y_{k})$ is evaluated from the previous iteration.
+    We note that $f(y_0)$ is computed before the start of the for loop. 
+    And finally, it evaluates proximal of $g$ at $y_k - L^{-1}\nabla f(y_k)$ once.
 

### 2024-12-21 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, phrasing things better, sync

@@
     \begin{lemma}[Constant R-WAPG sequences]\label{lemma:constant-rwapg-seq}
-        Suppose $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are R-WAPG sequences given by Definition \ref{def:rwapg-seq}, and they are constant meaning that there exists $\rho, \alpha$ such that $\alpha_k := \alpha$ and $\rho_k := \rho$ for all $k \ge 0$.
-        Define the momentum term $\theta = \rho\alpha(1 - \alpha)/(\rho\alpha^2 + \alpha)$. 
-        Then the constant R-WAPG sequence satisfies: 
-        \begin{enumerate}
-            \item $\rho = (1 - \mu/L\alpha^{-1})/(1 - \alpha)$. 
-            \item $\theta = (1 - \alpha)(1 - \mu/L \alpha^{-1})/(1 - \mu/L)$. 
-            \item For any $r \in \left(\sqrt{\mu/L}, \sqrt{L/\mu}\right)$, let $\alpha = r \sqrt{\mu/L}$.
+        Suppose $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are R-WAPG sequences given by Definition \ref{def:rwapg-seq} and assume $L > \mu > 0$.
+        Define $q := \mu/L$. 
+        Then $\forall r \in \left(\sqrt{q},\sqrt{q^{-1}}\right)$, the constant sequence $\alpha_k := r \sqrt{q}$ is a valid R-WAPG sequence and it has
+
+        % Define the momentum term $\theta = \rho\alpha(1 - \alpha)/(\rho\alpha^2 + \alpha)$. 
+        % Then the constant R-WAPG sequence satisfies: 
+        % \begin{enumerate}
+        %     \item $\rho = (1 - \mu/L\alpha^{-1})(1 - \alpha)^{-1}$. 
+        %     \item $\theta = (1 - \alpha)(1 - \mu/L \alpha^{-1})(1 - \mu/L)^{-1}$. 
+        %     \item For any $r \in \left(\sqrt{\mu/L}, \sqrt{L/\mu}\right)$, let $\alpha = r \sqrt{\mu/L}$.
 If $\sqrt{L/\mu} > r > 1$, then $\rho > 1$ else if $\sqrt{\mu/L} < r \le 1$ then $\rho \in (0, 1]$.
-            \item If $\alpha = \sqrt{\mu/L}$, then $\rho = 1$, $\theta = \left(1 - \sqrt{\mu/L}\right)/\left(1 + \sqrt{\mu/L}\right)$. 
-        \end{enumerate}
+        %     \item If $\alpha = \sqrt{\mu/L}$, then $\rho = 1$, $\theta = \left(1 - \sqrt{\mu/L}\right)/\left(1 + \sqrt{\mu/L}\right)$. 
+        % \end{enumerate}
     \end{lemma}
@@
         The third inequality used $r < 1$. 
-        To see (iv), substitute $\alpha = \sqrt{\mu/L}$ for $\rho$.
+        To see (iv), substitute $\alpha = \sqrt{\mu/L}$ for $\theta$ as defined in (i): 
+        \begin{align*}
+            \theta &= \frac{(1 - \alpha)(1 - \mu/L \alpha^{-1})}{1 - \mu/L}
+            = \frac{(1 - \sqrt{\mu/L})(1 - \sqrt{\mu/L})}{1 - \mu/L}
+            \\
+            &= \frac{1 - \sqrt{\mu/L}}{1 + \sqrt{\mu/L}}. 
+        \end{align*}
 

### 2024-12-21 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, exciting changes

--- 2024-12-20 Notebook LaTEX/Momentum Accelerations/paper3.tex
@@
 
-    \todoinline{Write this abstract when finishing. }
+    \todo{Write this abstract when finishing. }
 \end{abstract}
@@
         Our contributions are two folds, theoretical and practical. 
+        Our results is based the assumption $F = f + g$ where $g:Q \rightarrow \bar\RR^n$ is convex, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
+        \par
         Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''. 
@@
                 \item Attouch H., Cabot A.: ``Convergence Rates of Inertial Forward-Backward Algorithms'', SIAM. 
-                \item Vassilis A., et al.: "Convergence rate of inertial Forward-Backward algorithm
-                beyond Nesterov’s rule"
+                \item Vassilis A., et al.: ``Convergence rate of inertial Forward-Backward algorithm
+                beyond Nesterov's rule"
             \end{enumerate}
-            The following papers are related to stablizing, improving the acceleration scheme without monotone restarting. 
+            The following papers are related to stabiling, improving the acceleration scheme without monotone restarting. 
             \begin{enumerate}
@@
             \end{enumerate}
-
         }
@@
     $$
-    It is a single valued mapping and it has its domain on the entire $\RR^n$. 
+    It is a single-valued mapping, and it has its domain on the entire $\RR^n$. 
     Another operator often associated with $T_L$ is the gradient mapping operator $\mathcal G_L:= L(I - T_L)$. 
@@
     \begin{lemma}[Constant R-WAPG sequences]\label{lemma:constant-rwapg-seq}
-        Suppose $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are R-WAPG sequences given by Definition \ref{def:rwapg-seq}, and they are constant meaning that there exists $\rho, \alpha$ such that $\alpha_k := \alpha$ and $\rho_k := \rho$ for all $k \ge 0$.
-        Define the momentum term $\theta = \rho\alpha(1 - \alpha)/(\rho\alpha^2 + \alpha)$. 
-        Then the constant R-WAPG sequence satisfies: 
+        Suppose $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are R-WAPG sequences given by Definition \ref{def:rwapg-seq} and assume $L > \mu > 0$.
+        Define $q := \mu/L$. 
+        Then $\forall r \in \left(\sqrt{q},\sqrt{q^{-1}}\right)$, the constant sequence $\alpha_k := r \sqrt{q}$. 
         \begin{enumerate}
-            \item $\rho = (1 - \mu/L\alpha^{-1})/(1 - \alpha)$. 
-            \item $\theta = (1 - \alpha)(1 - \mu/L \alpha^{-1})/(1 - \mu/L)$. 
-            \item For any $r \in \left(\sqrt{\mu/L}, \sqrt{L/\mu}\right)$, let $\alpha = r \sqrt{\mu/L}$.
-If $\sqrt{L/\mu} > r > 1$, then $\rho > 1$ else if $\sqrt{\mu/L} < r \le 1$ then $\rho \in (0, 1]$.
-            \item If $\alpha = \sqrt{\mu/L}$, then $\rho = 1$, $\theta = \left(1 - \sqrt{\mu/L}\right)/\left(1 + \sqrt{\mu/L}\right)$. 
+            \item Fix any $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$ then the constant sequence $\alpha_k := \alpha \in (q, 1)$ and\\
+            $\rho_k := \rho=\left(1-r^{-1}\sqrt{q}\right)\left(1 - r \sqrt{q}\right)^{-1} > 0$, hence it's a pair of valid R-WAPG sequence. 
+            \item The momentum term in Definition \ref{def:r-wapg-momentum-form}, which we denoted by $\theta$ has:\\ $\theta = (1 - r^{-1}\sqrt{q})(1 - r\sqrt{q})(1- q)^{-1}$. 
+            \item When $r = 1$, $\theta = (1- \sqrt{q})(1 + \sqrt{q})^{-1}$. 
+            \item For all $r \in \left(1, \sqrt{q^{-1}}\right)$, $\rho > 1$; for all $r \in \left(\sqrt{q}, 1\right]$ $\rho \le 1$. 
+            \item For all $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, $\max(\rho, 1)(1 - \alpha) = \max\left(1 - r\sqrt{q}, 1 - r^{-1}q\right)$. 
         \end{enumerate}
@@
     \begin{proof}
-        It's direct to show (i). 
-        By the definition of $(\rho_k)_{k\ ge0}$ in the R-WAPG sequence definition, we have 
-        \begin{align*}
-            \rho_k &= 
-            \frac{\alpha_{k + 1}^2 - \mu/L \alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2}
+        To see (i), fix any $\sqrt{q} < r < \sqrt{q^{-1}}$, so
+        \begin{align*}
+            r &\in \left(\sqrt{q}, \sqrt{q^{-1}}\right)
+            \iff 
+            r\sqrt{q} \in 
+            \left(
+                q, 1
+            \right). 
+        \end{align*}
+        Therefore, $\alpha_k \in (\mu/L, 1)$. 
+        To see $\rho_k$, by definition it has 
+        \begin{align*}
+            \rho_k &= \frac{\alpha_{k + 1}^2 - q \alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} 
+            = \frac{\alpha^2 - q \alpha}{(1 - \alpha)\alpha^2} 
+            \\
+            &= \frac{1 - q\alpha^{-1}}{1 - \alpha}
+            \\
+            &= \frac{1 - q r^{-1}\sqrt{q^{-1}}}{1 - r \sqrt{q}}
+            \\
+            &= \frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}} > 0. 
+        \end{align*}
+        Simple algebra can show (ii). 
+        To start, we substitute the constant sequence $\alpha, \rho$ for $\alpha_k, \rho_k$ into the definition of $\theta$: 
+        \begin{align*}
+            \theta &= \frac{\rho\alpha(1 - \alpha)}{\rho \alpha^2 + \alpha}
+            = (\rho\alpha)\frac{1 - \alpha}{\rho \alpha^2 + \alpha} = \rho \frac{1 - \alpha}{\rho \alpha + 1}
+            \\
+            &= 
+            \frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}}
+            (1 - r\sqrt{q})
+            \left(
+                1 + r\sqrt{q}\frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}}
+            \right)^{-1}
+            \\
+            &= (1 - r^{-1} \sqrt{q})\left(
+                1 + \frac{r \sqrt{q} - q}{1 - r \sqrt{q}}
+            \right)^{-1}
+            \\
+            &= \left(1 - r^{-1} \sqrt{q}\right)\left(
+                \frac{1 - q}{1 - r \sqrt{q}}
+            \right)^{-1} = \frac{(1 - r^{-1}\sqrt{q})(1 - r \sqrt{q})}{1 - q}. 
+        \end{align*}
+        Now it's the perfect opportunity to show (iii) by substituting $r = 1$ which has 
+        \begin{align*}
+            \theta &= \frac{(1 - \sqrt{q})^2}{1 - q}
             =
-            \frac{\alpha^2 - \mu/L \alpha}{(1 - \alpha)\alpha^2}
-            \\
-            &= \frac{1 - (\mu/L)\alpha^{-1}}{1 - \alpha}. 
-        \end{align*}
-        To see (ii), it's direct by the definition of $\theta$: 
-        \begin{align*}
-            \theta &= 
-            \frac{\rho \alpha(1 - \alpha)}{\rho \alpha^2 + \alpha} 
-            = 
-            (\rho \alpha)\frac{(1 - \alpha)}{\rho \alpha^2 + \alpha}
-            \\
-            &= \left(
-                \frac{\alpha - (\mu/L)}{1 - \alpha}
-            \right)\frac{(1 - \alpha)}{\alpha \frac{\alpha - \mu/L}{1 - \alpha} + \alpha}
-            = \frac{\alpha - \mu/L}{\alpha\left(\frac{\alpha - \mu/L}{1 - \alpha}\right)+ \alpha}
-            \\
-            &= \left(1 - \mu/L \alpha^{-1}\right)\left(
-                \frac{\alpha - \mu/L}{1 - \alpha} + 1
-            \right)^{-1} 
-            \\
-            &= 
-            \frac{(1 - \alpha)\left(1 - \mu/L \alpha^{-1}\right)}{1 - \mu/L}. 
-        \end{align*}
-        To see (iii), we substitute $\alpha = r \sqrt{\mu/L}$ into the expression for $\rho$ in (i) which gives: 
-        \begin{align*}
-            \rho_k &= \frac{1 - \mu/L\alpha^{-1}}{1 - \alpha} 
-            = \frac{1 - r^{-1}\left(\mu/L\sqrt{L/\mu}\right)}{1 - r \sqrt{\mu/L}} 
-            = \frac{1 - r^{-1}\sqrt{\mu/L}}{1 - r \sqrt{\mu/L}}. 
-        \end{align*}
-        If $\sqrt{L/\mu}> r > 1$ then $\rho > 1$ because 
-        \begin{align*}
-            \rho &= \frac{1 - r^{-1}\sqrt{\mu/L}}{1 - r \sqrt{\mu/L}} 
-            > \frac{1 - \sqrt{\mu/L}}{1 - \sqrt{\mu/L}} = 1. 
-        \end{align*}
-        When $\sqrt{\mu/L} < r < 1$, it has 
-        \begin{align*}
-            0 < 1 - r^{-1}\sqrt{\mu/L} < \frac{1 - r^{-1}\sqrt{\mu/L}}{1 - r\sqrt{\mu/L}} = \rho < \frac{1 - \sqrt{\mu/L}}{1 - \sqrt{\mu/L}} = 1. 
-        \end{align*}
-        The first inequality used $r > \sqrt{\mu/L}$. 
-        The third inequality used $r < 1$. 
-        To see (iv), substitute $\alpha = \sqrt{\mu/L}$ for $\rho$.
+            \frac{(1 - \sqrt{q})}{(1 - \sqrt{q})(1 + \sqrt{q})}
+            = \frac{1 - \sqrt{q}}{1 + \sqrt{q}}. 
+        \end{align*}
+        Next for (iv), we determine when $\rho$ switches from $> 1$ to $ \le 1$. 
+        For any $r \in \left(1, \sqrt{q^{-1}}\right)$, we show $\rho > 1$: 
+        \begin{align*}
+            \rho &= \frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}} 
+            > \frac{1 - \sqrt{q}}{1 - r \sqrt{q}} > \frac{1 - \sqrt{q}}{1 - \sqrt{q}} = 1
+        \end{align*}
+        The first inequality comes from $r > 1 \iff -r^{-1} > -1$, the second inequality comes from $r > 1 \iff -r < 1$. 
+        For any $r \in \left(\sqrt{q}, 1\right]$, we have $\rho \le 1$ by 
+        \begin{align*}
+            \rho &= \frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}} 
+            \le \frac{1 - \sqrt{q}}{1 - r \sqrt{q}} \le \frac{1 - \sqrt{q}}{1 - \sqrt{q}} = 1. 
+        \end{align*}
+        The first inequality comes from $-r^{-1} \le - 1$; the second inequality comes from $-r \ge -1$. 
+        \par
+        Finally, to show (v), we consider by cases: 
+        \begin{enumerate}
+            \item[A:] When $r \in \left(1, \sqrt{q^{-1}}\right)$, we have $\rho > 1$ by (iii), meaning that $1 - r^{-1}\sqrt{q} > 1 - r \sqrt{q}$. $\rho > 1 \implies \max(\rho, 1) = \rho$ hence 
+                \begin{align*}
+                    \max(\rho, 1)(1 - \alpha) &= \rho(1- \alpha)
+                    = \frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}}(1 - r \sqrt{q}) = 1 - r^{-1}\sqrt{q}. 
+                \end{align*}
+                In this case, the larger one of the two values: $\left\lbrace1 - \rho^{-1}\sqrt{q}, 1 - r\sqrt{q}\right\rbrace$ is taken. 
+            \item[B:] When $r \in \left(\sqrt{q}, 1\right]$, we have $\rho \le 1$ by (iii); hence $1 - r^{-1}\sqrt{q} \le 1 - r \sqrt{q}$ and $\max(1,\rho) = 1$ therefore: 
+            \begin{align*}
+                \max(1, \rho)(1 - \alpha) = (1 - \alpha) = 1 - r \sqrt{q}. 
+            \end{align*}
+            Once again, the larger one of the quantity: $1 - r \sqrt{q}$ among $\{1 - r^{-1}\sqrt{q}, 1 - r\sqrt{q}\}$ is taken. 
+        \end{enumerate}
+        Therefore, for all vales of $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$ are completed by cases: (A), (B).
+        The larger of the value among $\{1 - r \sqrt{q}, 1 - r^{-1}\sqrt{q}\}$ is always taken. 
+        Therefore it has: 
+        \begin{align*}
+            \max(1, \rho)(1 - \alpha) = \max\left(1 - r\sqrt{q}, 1 - r^{-1}\sqrt{q}\right). 
+        \end{align*}
 
@@
     \begin{theorem}[Fixed momentum FISTA]\label{thm:fixed-momentum-fista}
-
+        Suppose a constant 
     \end{theorem}

### 2024-12-21 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
 
-    \begin{theorem}[Fixed momentum FISTA]\label{thm:fixed-momentum-fista}
-        Suppose a constant 
+    \begin{theorem}[Fixed momentum APG]\label{thm:fixed-momentum-fista}
+        Assume $L > \mu > 0$, let a pair of constant R-WAPG sequence: $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Lemma \ref{lemma:constant-rwapg-seq}.
+        Define $q := \mu/L$ and for any fixed $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, let $\alpha_k := \alpha = r \sqrt{q}$ be the constant R-WAPG sequence. 
+        Consider the algorithm with a constant momentum specified by the following: 
+        \begin{tcolorbox}
+            Define $\theta = \left(1 - r^{-1}\sqrt{q}\right)(1 - r\sqrt{q})(1 - q)^{-1}$. 
+            \\
+            Initialize $y_1 = x_1$; for $k = 1, 2, \cdots, N$, update: 
+            \begin{align*}
+                &x_{k + 1} = y_k + L^{-1}\mathcal G_L y_k, 
+                \\
+                & y_{k + 1} = x_{k + 1} + \theta(x_{k + 1} - x_k). 
+            \end{align*}
+        \end{tcolorbox}
+        Then the algorithm generates $(x_k)_{k \ge 1}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O\left(\max(1 - r\sqrt{q}, 1 - r^{-1}\sqrt{q})^k\right)$. 
     \end{theorem}
+    \begin{proof}
+        The constant sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid R-WAPG sequence by Lemma \ref{lemma:constant-rwapg-seq}. 
+        The algorithm presented here is the same as the R-WAPG momentum form because the term $\theta$ from Lemma \ref{lemma:constant-rwapg-seq} matches up with Definition \ref{def:r-wapg-momentum-form}.
+        Therefore by Proposition \ref{prop:wagp-convergence} we have: 
+        \begin{align*}
+            & F(x_{k + 1}) - F^* + \frac{L\alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
+            \\
+            &= 
+            F(x_{k + 1}) - F^* + \frac{L\alpha_k^2}{2}\Vert x_{k + 1}  - x^* + (\alpha^{-1} - 1)(x_{k + 1} - x_k)\Vert^2
+            \\
+            &\le 
+            \left(
+                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
+            \right)
+            \left(
+                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
+            \right)
+            \left(
+                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
+            \right)
+            \\
+            &= \left(
+                \prod_{i = 1}^{k - 1} \max(1, \rho)(1 - \alpha)
+            \right)
+            \left(
+                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
+            \right)
+            \\
+            &= \max(1 - r\sqrt{q}, 1 - r^{-1}\sqrt{q})^k
+            \left(
+                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert x_1 - x^*\Vert^2
+            \right). 
+            & \text{Lemma \ref{lemma:constant-rwapg-seq} (v)}
+        \end{align*}
+        The equivalency between the Momentum representation of R-WAPG (Definition \ref{def:r-wapg-momentum-form}) and the similar triangle representation (Definition \ref{def:r-wapg-st-form}) allows us to write $v_{k + 1} = x_{k + 1} + (\alpha^{-1} - 1)(x_{k + 1} - x_k)$.
+        By the initialization condition $v_1 = x_1$ specified back in Proposition \ref{prop:r-wapg-momentum-repr} when we derived the momentum form of R-WAPG, we can write $v_1$ as $x_1$.
+
+    \end{proof}
+    \begin{remark}
+
+    \end{remark}
 
@@
 
+        \subsubsection{Simple convex quadratic}
+        \subsubsection{LASSO}
+        \subsubsection{Logistic regression}
+
 \bibliographystyle{siam}

### 2024-12-21 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
     \end{align}\label{eqn:additive-comp-obj}
-    Unless specified, assume $f$ is a smooth function with $L$-Lipschitz gradient operator. 
-    Unless specified, assume $g$ is a convex function. 
-    In the literatures this type of problems are referred to as additive composite problems.
-
+    Unless specified, assume $f:\RR^n \rightarrow \RR$ is $L$-Lipscthiz smooth $\mu \ge 0$ strongly convex and $g:Q \rightarrow \overline \RR$ is convex. 
+    This type of problem is referred to as additive composite problems in the literature. 
     \par
@@
     \end{enumerate}
-    The good news is we have definitive answers for both questions through our own efforts of research. 
+    The good news is we have definitive answers for both questions by our own efforts of research. 
     Section \ref{sec:unify-nes-acceleration}, \ref{sec:spectral-momentum} are our ongoing research which present the answers to the questions. 

### 2024-12-21 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes applied
>w<, changes

@@
         Our contributions are two folds, theoretical and practical. 
-        Our results is based the assumption $F = f + g$ where $g:Q \rightarrow \bar\RR^n$ is convex, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
+        Our results are based the assumption $F = f + g$ where $g:Q \rightarrow \overline\RR$ is convex, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
         \par
@@
         Define $q := \mu/L$. 
-        Then $\forall r \in \left(\sqrt{q},\sqrt{q^{-1}}\right)$, the constant sequence $\alpha_k := r \sqrt{q}$. 
+        Then $\forall r \in \left(\sqrt{q},\sqrt{q^{-1}}\right)$, the constant sequence $\alpha_k := r \sqrt{q}$ has the following: 
         \begin{enumerate}
@@
     \begin{remark}
-
+        When $r = 1$, the algorithm described above is exactly the same as the V-FISTA algorithm specified in (10.7.7) of his book \cite{beck_first-order_2017}. 
     \end{remark}
@@
         \STATE{\textbf{Compute: } $f(y_k)$; }
-        \FOR{$k = 0, 1, 2, \cdot, N$}
+        \FOR{$k = 0, 1, 2, \cdots, N$}
             \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$;}
@@
     \par
-    Assume $L$ given is an upper bound of the Lipschitz smoothness constant of $f$, the algorithm computes $\nabla f(y_k)$ for $x^+$, $f(y_{k + 1})$ for Bregman Divergence and $f(y_{k})$ is evaluated from the previous iteration.
+    Assume $L$ given is an upper bound of the Lipschitz smoothness constant of $f$, then the algorithm calls $f(\cdot)$ two times, and $\nabla f(\cdot)$ once per iteration. 
+    The algorithm computes $\nabla f(y_k)$ once for $x^+$, $f(y_{k + 1})$ once for Bregman Divergence because $f(y_{k})$ is evaluated from the previous iteration, and $f(x^+)$ once for Lipschitz constant line search condition.
     We note that $f(y_0)$ is computed before the start of the for loop. 

### 2024-12-22 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
                 \item Vassilis A., et al.: ``Convergence rate of inertial Forward-Backward algorithm
-                beyond Nesterov's rule"
+                beyond Nesterov's rule". 
             \end{enumerate}
-            The following papers are related to stabiling, improving the acceleration scheme without monotone restarting. 
+            The following papers are related to stabilizing, improving the acceleration scheme without monotone restarting. 
             \begin{enumerate}
@@
     The lemma follows explains equates between $\mathcal M(\cdot; y), \widetilde{\mathcal M}(\cdot; y)$. 
-    \begin{lemma}[Proximal gradient envelope] 
+    \begin{lemma}[Proximal gradient envelope]\label{lemma:pg-envelope}
         Fix any $y \in \RR^n$, we will have for all $x \in Q$ that: 
@@
             \\
-            \iff
+            \implies
             \left(
@@
         }
+        The first $\implies$ comes from Lemma \ref{lemma:pg-envelope} where we had $- \widetilde{\mathcal M}^{L^{-1}}(x; y) \ge - \mathcal M^{L^{-1}}(x; y)$. 
+        \todoinline{THIS THIS PART IS WRONG WRONG WRONG!}. 
         Continuing, it has: 

### 2024-12-22 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
     We consider optimization problem: $\min_x \left\lbrace f(x) + g(x)\right\rbrace$.
-    Fix any arbitrary $y \in \RR^n$, define for all $x \in Q$: 
+    Fix any arbitrary $y \in \RR^n$, define the model functions for all $x \in Q$
     \begin{align*}
@@
     \end{align*}
-    and the proximal gradient operator $T_L := [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f]$. 
+    When $x \in \RR\setminus Q$, the model function takes $+\infty$ value. 
+    Define the proximal gradient operator and gradient mapping operator:  $T_L := [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f]$. 
     The proximal gradient operator $T_L$ admits 
-    $$
-        T_Ly = \argmin_x \left\lbrace
+    \begin{align*}
+        T_Ly &= \argmin_x \left\lbrace
             g(x) + \langle \nabla f(y), x\rangle + L/2\Vert x - y\Vert^2
-        \right\rbrace. 
-    $$
-    It is a single-valued mapping, and it has its domain on the entire $\RR^n$. 
-    Another operator often associated with $T_L$ is the gradient mapping operator $\mathcal G_L:= L(I - T_L)$. 
+        \right\rbrace,
+        \\
+        \mathcal G_L 
+        &:= L(I - T_L). 
+    \end{align*}
+    $T_L$ is a single-valued mapping, and it has its domain on the entire $\RR^n$. 
     Finally, define the Bregman divergence of $f$: 
@@
     \end{align*}
-    The lemma follows explains equates between $\mathcal M(\cdot; y), \widetilde{\mathcal M}(\cdot; y)$. 
+    The following lemma is an important property of $\mathcal M(\cdot; y), \widetilde{\mathcal M}(\cdot; y)$. 
     \begin{lemma}[Proximal gradient envelope]\label{lemma:pg-envelope}
-        Fix any $y \in \RR^n$, we will have for all $x \in Q$ that: 
+        Fix any $y \in \RR^n$, we will have for all $x \in \RR$ that: 
         \begin{align*}
@@
     \begin{proof}
+        Consider any $x \in Q$, by definition it has: 
         \begin{align*}
@@
         \end{align*}
+        The equality is trivially true when $x \in \RR \setminus Q$. 
     \end{proof}
@@
     \begin{theorem}[Proximal inequality]\label{thm:prox-grad-ineq}
-        Fix any $y\in \RR^n$, we have for all $x \in Q$: 
+        Fix any $y\in \RR^n$, we have for all $x \in \RR^n$: 
         \begin{align*}
@@
         \end{align*}
-        When $f$ is $\mu \ge 0$ strongly convex, it implies that 
+        Recall that $f$ is $\mu \ge 0$ strongly convex and $L$ Lipschitz smooth, hence the following is implied: 
         \begin{align*}
@@
     \begin{proof}
-        Observe that the function $\widetilde {\mathcal M}(\cdot; y)$ is $L$ strongly convex with minimizer $T_Ly$. 
-        For all $x \in Q$, it has quadratic growth condition at its minimizer $T_Ly$ which gives these equivalent inequalities: 
-        {\small
-        \begin{align*}
-            \widetilde{\mathcal M}^{L^{-1}}(x; y) - 
-            \widetilde{\mathcal M}^{L^{-1}}(T_Ly; y)
-            - 
-            \frac{L}{2}\Vert x - T_Ly\Vert^2
-            &\ge 
-            0
-            \\
-            \implies
-            \left(
-                \mathcal M^{L^{-1}}(x; y) - D_f(x, y)
-            \right) - 
-            \mathcal M^{L^{-1}}(T_Ly; y) 
-            - 
-            \frac{L}{2}\Vert x - T_Ly\Vert^2
-            &\ge 0
-            \\
-            \iff 
-            \left(
-                \mathcal M^{L^{-1}}(x; y)
-                - 
-                \mathcal M^{L^{-1}}(T_Ly; y)
-            \right)
-            - 
-            D_f(x, y) 
-            - \frac{L}{2}\Vert x - T_Ly\Vert^2
-            &\ge 0
-            \\
-            \iff 
-            \left(
-                F(x) - F(T_Ly) 
-                + 
-                \frac{L}{2}\Vert x - y\Vert^2 - 
-                \frac{L}{2}\Vert T_Ly - y\Vert^2
-            \right)
-            - 
-            D_f(x, y) 
-            - \frac{L}{2}\Vert x - T_Ly\Vert^2
-            &\ge 0
-            \\
-            \iff 
-            \left(
-                F(x) - F(T_Ly) 
-                + 
-                \frac{L}{2}
-                \left(
-                    \Vert x - T_Ly + T_Ly - y\Vert^2
-                    - 
-                    \Vert y - T_Ly\Vert^2
-                \right)
-            \right)
-            - 
-            D_f(x, y) 
-            - \frac{L}{2}\Vert x - T_Ly\Vert^2
-            &\ge 0
-            \\
-            \iff 
-            \left(
-                F(x) - F(T_Ly) 
-                + 
-                \frac{L}{2}
-                \left(
-                    \Vert x - T_Ly\Vert^2 + 
-                    2\langle x - T_Ly, T_Ly - y\rangle
-                \right)
-            \right)
-            - 
-            D_f(x, y) 
-            - \frac{L}{2}\Vert x - T_Ly\Vert^2
-            &\ge 0
-            \\
-            \iff
-            \left(
-                F(x) - F(T_Ly) + \frac{L}{2}\Vert x - T_Ly\Vert^2 
-                - L\langle  x - T_Ly, y - T_Ly\rangle
-            \right)
-            - 
-            D_f(x, y) 
-            - \frac{L}{2}\Vert x - T_Ly\Vert^2
-            &\ge 0
-            \\
-            \iff 
-            F(x) - F(T_Ly)
-            - \langle L(y - T_Ly), x - T_Ly\rangle
-            - D_f(x, y) 
-            &\ge 0. 
-        \end{align*}
-        }
-        The first $\implies$ comes from Lemma \ref{lemma:pg-envelope} where we had $- \widetilde{\mathcal M}^{L^{-1}}(x; y) \ge - \mathcal M^{L^{-1}}(x; y)$. 
-        \todoinline{THIS THIS PART IS WRONG WRONG WRONG!}. 
-        Continuing, it has: 
-        \begin{align*}
-            F(x) - F(T_Ly) - \langle L(y - T_Ly), x - T_Ly\rangle - D_f(x, y) &\ge 0
-            \\
-            \iff
-            F(x) - F(T_Ly)
-            - \langle L(y - T_Ly), x - y + y - T_Ly\rangle - D_f(x, y) 
-            &\ge 0
-            \\
-            \iff
-            F(x) - F(T_Ly)
-            - \langle L(y - T_Ly),x - y \rangle
-            - L\Vert y - T_Ly\Vert^2
-            - D_f(x, y) 
-            &\ge 0
-            \\
-            \implies 
-            F(x) - F(T_Ly)
-            - \langle L(y - T_Ly),x - y \rangle
-            - \frac{L}{2}\Vert y - T_Ly\Vert^2
-            - D_f(x, y) 
-            &\ge 0
-            \\
-            \implies
-            F(x) - F(T_Ly)
-            - \langle L(y - T_Ly),x - y \rangle
-            - \frac{L}{2}\Vert y - T_Ly\Vert^2
-            - \frac{\mu}{2}\Vert x - y\Vert^2
-            &\ge 0. 
-        \end{align*}
-        Going from the second last inequality to the last inequality, we used the fact that $f$ is strongly convex hence for all $x, y$, it's true that $D_f(x, y) \ge \mu/2 \Vert x - y\Vert^2$. 
+        For lighter notations in this proof, we use $\mathcal M(\cdot, y), \widetilde{\mathcal M}(\cdot, y)$ instead of $\mathcal M^{L^{-1}}(\cdot, y), \widetilde{\mathcal M}^{L^{-1}}(\cdot, y)$. 
+        And we denote $T$ for the proximal gradient operator instead of $T_L$. 
+        We can do this because the Lipschitz constant $L$ is fixed throughout the proof hence it can be omitted.
+
+        % Observe that the function $\widetilde {\mathcal M}(\cdot; y)$ is $L$ strongly convex with minimizer $T_Ly$. 
+        % For all $x \in Q$, it has quadratic growth condition at its minimizer $T_Ly$ which gives these equivalent inequalities: 
+        % {\small
+        % \begin{align*}
+        %     \widetilde{\mathcal M}^{L^{-1}}(x; y) - 
+        %     \widetilde{\mathcal M}^{L^{-1}}(T_Ly; y)
+        %     - 
+        %     \frac{L}{2}\Vert x - T_Ly\Vert^2
+        %     &\ge 
+        %     0
+        %     \\
+        %     \implies
+        %     \left(
+        %         \mathcal M^{L^{-1}}(x; y) - D_f(x, y)
+        %     \right) - 
+        %     \mathcal M^{L^{-1}}(T_Ly; y) 
+        %     - 
+        %     \frac{L}{2}\Vert x - T_Ly\Vert^2
+        %     &\ge 0
+        %     \\
+        %     \iff 
+        %     \left(
+        %         \mathcal M^{L^{-1}}(x; y)
+        %         - 
+        %         \mathcal M^{L^{-1}}(T_Ly; y)
+        %     \right)
+        %     - 
+        %     D_f(x, y) 
+        %     - \frac{L}{2}\Vert x - T_Ly\Vert^2
+        %     &\ge 0
+        %     \\
+        %     \iff 
+        %     \left(
+        %         F(x) - F(T_Ly) 
+        %         + 
+        %         \frac{L}{2}\Vert x - y\Vert^2 - 
+        %         \frac{L}{2}\Vert T_Ly - y\Vert^2
+        %     \right)
+        %     - 
+        %     D_f(x, y) 
+        %     - \frac{L}{2}\Vert x - T_Ly\Vert^2
+        %     &\ge 0
+        %     \\
+        %     \iff 
+        %     \left(
+        %         F(x) - F(T_Ly) 
+        %         + 
+        %         \frac{L}{2}
+        %         \left(
+        %             \Vert x - T_Ly + T_Ly - y\Vert^2
+        %             - 
+        %             \Vert y - T_Ly\Vert^2
+        %         \right)
+        %     \right)
+        %     - 
+        %     D_f(x, y) 
+        %     - \frac{L}{2}\Vert x - T_Ly\Vert^2
+        %     &\ge 0
+        %     \\
+        %     \iff 
+        %     \left(
+        %         F(x) - F(T_Ly) 
+        %         + 
+        %         \frac{L}{2}
+        %         \left(
+        %             \Vert x - T_Ly\Vert^2 + 
+        %             2\langle x - T_Ly, T_Ly - y\rangle
+        %         \right)
+        %     \right)
+        %     - 
+        %     D_f(x, y) 
+        %     - \frac{L}{2}\Vert x - T_Ly\Vert^2
+        %     &\ge 0
+        %     \\
+        %     \iff
+        %     \left(
+        %         F(x) - F(T_Ly) + \frac{L}{2}\Vert x - T_Ly\Vert^2 
+        %         - L\langle  x - T_Ly, y - T_Ly\rangle
+        %     \right)
+        %     - 
+        %     D_f(x, y) 
+        %     - \frac{L}{2}\Vert x - T_Ly\Vert^2
+        %     &\ge 0
+        %     \\
+        %     \iff 
+        %     F(x) - F(T_Ly)
+        %     - \langle L(y - T_Ly), x - T_Ly\rangle
+        %     - D_f(x, y) 
+        %     &\ge 0. 
+        % \end{align*}
+        % }
+        % The first $\implies$ comes from Lemma \ref{lemma:pg-envelope} where we had $- \widetilde{\mathcal M}^{L^{-1}}(x; y) \ge - \mathcal M^{L^{-1}}(x; y)$. 
+        % \todoinline{THIS THIS PART IS WRONG WRONG WRONG!}. 
+        % Continuing, it has: 
+        % \begin{align*}
+        %     F(x) - F(T_Ly) - \langle L(y - T_Ly), x - T_Ly\rangle - D_f(x, y) &\ge 0
+        %     \\
+        %     \iff
+        %     F(x) - F(T_Ly)
+        %     - \langle L(y - T_Ly), x - y + y - T_Ly\rangle - D_f(x, y) 
+        %     &\ge 0
+        %     \\
+        %     \iff
+        %     F(x) - F(T_Ly)
+        %     - \langle L(y - T_Ly),x - y \rangle
+        %     - L\Vert y - T_Ly\Vert^2
+        %     - D_f(x, y) 
+        %     &\ge 0
+        %     \\
+        %     \implies 
+        %     F(x) - F(T_Ly)
+        %     - \langle L(y - T_Ly),x - y \rangle
+        %     - \frac{L}{2}\Vert y - T_Ly\Vert^2
+        %     - D_f(x, y) 
+        %     &\ge 0
+        %     \\
+        %     \implies
+        %     F(x) - F(T_Ly)
+        %     - \langle L(y - T_Ly),x - y \rangle
+        %     - \frac{L}{2}\Vert y - T_Ly\Vert^2
+        %     - \frac{\mu}{2}\Vert x - y\Vert^2
+        %     &\ge 0. 
+        % \end{align*}
+        % Going from the second last inequality to the last inequality, we used the fact that $f$ is strongly convex hence for all $x, y$, it's true that $D_f(x, y) \ge \mu/2 \Vert x - y\Vert^2$.
+
     \end{proof}

### 2024-12-22 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
 \section{Preliminaries}
-    Beck's book \cite{beck_first-order_2017}. 
+    \todoinline{
+        Assumptions: Additive composite type convex objective until specified.  
+    }
     \subsection{Fundamentals in convex analysis}
+        \todoinline{
+            Definitions: 
+            \begin{enumerate}
+                \item The proximal gradient operator. 
+                \item The proximal mapping operator. 
+                \item The Bregman Divergence of function. 
+                \item Strong convexity. 
+            \end{enumerate}
+            Lemma: 
+            \begin{enumerate}
+                \item Quadratic growth conditions of a strongly convex function. 
+            \end{enumerate}
+            Theorems: 
+            \begin{enumerate}
+                \item The proximal gradient inequality, for additive composite objective where the smooth part is $\mu \ge 0$ strongly convex. 
+            \end{enumerate}
+        }
     \subsection{Fundamentals in non-convex analysis}

### 2024-12-22 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

--- 2024-12-22 Notebook LaTEX/Momentum Accelerations/paper3.tex
@@
         \end{align*}
+        The equality is trivially true when $x \in \RR \setminus Q$. 
     \end{proof}
-    \subsection{Proximal inequality}
+    \begin{remark}
+        This is true not just for fixed $L$ that is the Lipschitz smoothness constant of $f$, it's true for all value of $L$. 
+    \end{remark}
     \begin{theorem}[Proximal inequality]\label{thm:prox-grad-ineq}
-        Fix any $y\in \RR^n$, we have for all $x \in Q$: 
-        \begin{align*}
-            F(x) - F(T_Ly) - \langle L(y - T_Ly), x - y\rangle
-            - L\Vert y - T_L y\Vert^2
-            - D_f(x, y)
-            &\ge  
-            0. 
-        \end{align*}
-        When $f$ is $\mu \ge 0$ strongly convex, it implies that 
+        Fix any $y\in \RR^n$, we have for all $x \in \RR^n$: 
         \begin{align*}
@@
     \begin{proof}
-        Observe that the function $\widetilde {\mathcal M}(\cdot; y)$ is $L$ strongly convex with minimizer $T_Ly$. 
-        For all $x \in Q$, it has quadratic growth condition at its minimizer $T_Ly$ which gives these equivalent inequalities: 
-        {\small
+        We denote $T$ for the proximal gradient operator instead of $T_L$. 
+        We can do this because the Lipschitz constant $L$ is fixed throughout the proof hence it can be omitted. 
+        The model function $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is a $L$ strongly convex function, so it admites quadratic growth conditions over minimizer $Ty$ and for all $x \in \RR^n$: 
+        {\footnotesize
         \begin{align*}
             \widetilde{\mathcal M}^{L^{-1}}(x; y) - 
-            \widetilde{\mathcal M}^{L^{-1}}(T_Ly; y)
+            \widetilde{\mathcal M}^{L^{-1}}(Ty; y)
             - 
-            \frac{L}{2}\Vert x - T_Ly\Vert^2
+            \frac{L}{2}\Vert x - Ty\Vert^2
             &\ge 
@@
             \right) - 
-            \mathcal M^{L^{-1}}(T_Ly; y) 
+            \mathcal M^{L^{-1}}(Ty; y) 
             - 
-            \frac{L}{2}\Vert x - T_Ly\Vert^2
+            \frac{L}{2}\Vert x - Ty\Vert^2
+            + D_f(Ty; y)
             &\ge 0
@@
                 - 
-                \mathcal M^{L^{-1}}(T_Ly; y)
+                \mathcal M^{L^{-1}}(Ty; y)
             \right)
@@
             D_f(x, y) 
-            - \frac{L}{2}\Vert x - T_Ly\Vert^2
+            - \frac{L}{2}\Vert x - Ty\Vert^2
+            + D_f(Ty; y)
             &\ge 0
@@
             \left(
-                F(x) - F(T_Ly) 
+                F(x) - F(Ty) 
                 + 
                 \frac{L}{2}\Vert x - y\Vert^2 - 
-                \frac{L}{2}\Vert T_Ly - y\Vert^2
-            \right)
+                \frac{L}{2}\Vert Ty - y\Vert^2
+            \right)
+            - D_f(x, y) 
+            + D_f(Ty; y)
+            - \frac{L}{2}\Vert x - Ty\Vert^2
+            &\ge 0
+            \\
+            \iff 
+            \left(
+                F(x) - F(Ty) 
+                + 
+                \frac{L}{2}
+                \left(
+                    \Vert x - Ty + Ty - y\Vert^2
                     - 
-            D_f(x, y) 
-            - \frac{L}{2}\Vert x - T_Ly\Vert^2
+                    \Vert y - Ty\Vert^2
+                \right)
+            \right)
+            - D_f(x, y) 
+            + D_f(Ty; y)
+            - \frac{L}{2}\Vert x - Ty\Vert^2
             &\ge 0
@@
             \left(
-                F(x) - F(T_Ly) 
+                F(x) - F(Ty) 
                 + 
@@
                 \left(
-                    \Vert x - T_Ly + T_Ly - y\Vert^2
-                    - 
-                    \Vert y - T_Ly\Vert^2
-                \right)
-            \right)
-            - 
-            D_f(x, y) 
-            - \frac{L}{2}\Vert x - T_Ly\Vert^2
+                    \Vert x - Ty\Vert^2 + 
+                    2\langle x - Ty, Ty - y\rangle
+                \right)
+            \right)
+            - D_f(x, y) 
+            + D_f(Ty; y)
+            - \frac{L}{2}\Vert x - Ty\Vert^2
             &\ge 0
@@
             \left(
-                F(x) - F(T_Ly) 
-                + 
-                \frac{L}{2}
-                \left(
-                    \Vert x - T_Ly\Vert^2 + 
-                    2\langle x - T_Ly, T_Ly - y\rangle
-                \right)
-            \right)
-            - 
-            D_f(x, y) 
-            - \frac{L}{2}\Vert x - T_Ly\Vert^2
+                F(x) - F(Ty) + \frac{L}{2}\Vert x - Ty\Vert^2 
+                - L\langle  x - Ty, y - Ty\rangle
+            \right)
+            - D_f(x, y) 
+            + D_f(Ty; y)
+            - \frac{L}{2}\Vert x - Ty\Vert^2
             &\ge 0
@@
             \iff 
-            \left(
-                F(x) - F(T_Ly) + \frac{L}{2}\Vert x - T_Ly\Vert^2 
-                - L\langle  x - T_Ly, y - T_Ly\rangle
-            \right)
-            - 
-            D_f(x, y) 
-            - \frac{L}{2}\Vert x - T_Ly\Vert^2
-            &\ge 0
-            \\
-            \iff 
-            F(x) - F(T_Ly)
-            - \langle L(y - T_Ly), x - T_Ly\rangle
+            F(x) - F(Ty)
+            - \langle L(y - Ty), x - Ty\rangle
             - D_f(x, y) 
+            + D_f(Ty, y)
             &\ge 0. 
@@
         }
-        The first $\implies$ comes from Lemma \ref{lemma:pg-envelope} where we had $- \widetilde{\mathcal M}^{L^{-1}}(x; y) \ge - \mathcal M^{L^{-1}}(x; y)$. 
-        \todoinline{THIS THIS PART IS WRONG WRONG WRONG!}. 
-        Continuing, it has: 
-        \begin{align*}
-            F(x) - F(T_Ly) - \langle L(y - T_Ly), x - T_Ly\rangle - D_f(x, y) &\ge 0
-            \\
-            \iff
-            F(x) - F(T_Ly)
-            - \langle L(y - T_Ly), x - y + y - T_Ly\rangle - D_f(x, y) 
-            &\ge 0
-            \\
-            \iff
-            F(x) - F(T_Ly)
-            - \langle L(y - T_Ly),x - y \rangle
-            - L\Vert y - T_Ly\Vert^2
+        Now, consider the lower bound of $D_f(x, y) \ge \mu/2\Vert x - y\Vert^2$ by strong convexity of $f$ then 
+        \begin{align*}
+            0 &\le 
+            F(x) - F(Ty)
+            - \langle L(y - Ty), x - Ty\rangle
             - D_f(x, y) 
-            &\ge 0
-            \\
-            \implies 
-            F(x) - F(T_Ly)
-            - \langle L(y - T_Ly),x - y \rangle
-            - \frac{L}{2}\Vert y - T_Ly\Vert^2
-            - D_f(x, y) 
-            &\ge 0
-            \\
-            \implies
-            F(x) - F(T_Ly)
-            - \langle L(y - T_Ly),x - y \rangle
-            - \frac{L}{2}\Vert y - T_Ly\Vert^2
+            + D_f(Ty, y)
+            \\
+            &\le 
+            F(x) - F(Ty)
+            - \langle L(y - Ty), x - Ty\rangle
             - \frac{\mu}{2}\Vert x - y\Vert^2
-            &\ge 0. 
-        \end{align*}
-        Going from the second last inequality to the last inequality, we used the fact that $f$ is strongly convex hence for all $x, y$, it's true that $D_f(x, y) \ge \mu/2 \Vert x - y\Vert^2$. 
+            + \frac{L}{2}\Vert y - Ty\Vert^2
+            \\
+            &\le 
+            F(x) - F(Ty)
+            - \langle L(y - Ty), x - y  + y - Ty\rangle
+            - \frac{\mu}{2}\Vert x - y\Vert^2
+            + \frac{L}{2}\Vert y - Ty\Vert^2
+            \\
+            &\le 
+            F(x) - F(Ty) - \langle L(y - Ty), x - y\rangle - \frac{\mu}{2}\Vert x - y \Vert^2
+            - \frac{L}{2}\Vert y - Ty\Vert^2. 
+        \end{align*}
+        The proof is done. 
     \end{proof}

### 2024-12-22 Notebook LaTEX/Proposal/main.tex
>w<, changes

--- 2024-12-21 Notebook LaTEX/Proposal/main.tex
@@
     \begin{enumerate}
-        \item Do there exist a unified description for the convergence for both variants of the algorithm. 
-        \item Is it possible to attain faster convergence rate without knowledge about the strong convexity of function $f$. 
+        \item Do there exist a unified description for the convergence for both variants of the algorithms?
+        \item Is it possible to attain faster convergence rate without knowledge about the strong convexity of function $f$?
+        \item Is it possible to describe the convergence of function value for momentum sequences that are much weaker than the Nesterov's rule? 
     \end{enumerate}
@@
     Section \ref{sec:catalyst} are results of literatures review in MATH 590. 
-    It's based on a series of papers (CITATION HERE) in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
+    \todo{Add citations here. }{It's based on a series of papers} in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
     We will point out potential future direction of research of Catalyst acceleration. 
@@
 \section{Preliminaries}
-    Beck's book \cite{beck_first-order_2017}. 
+    \todoinline{
+        Assumptions: Additive composite type convex objective until specified.  
+    }
     \subsection{Fundamentals in convex analysis}
+        \todoinline{
+            Definitions: 
+            \begin{enumerate}
+                \item [$\square$]Strong convexity of a function. 
+                \item [$\square$]The proximal gradient operator. 
+                \item [$\square$]The proximal mapping operator. 
+                \item [$\square$]The Bregman Divergence of function. 
+            \end{enumerate}
+            Lemmas: 
+            \begin{enumerate}
+                \item [$\square$]Quadratic growth conditions of a strongly convex function. 
+                \item [$\square$]The proximal gradient envelope.
+                \item [$\square$]A property of gradient mapping. 
+            \end{enumerate}
+            Theorems: 
+            \begin{enumerate}
+                \item [$\square$]The proximal gradient inequality, for additive composite objective where the smooth part is $\mu \ge 0$ strongly convex. 
+            \end{enumerate}
+        }
+
     \subsection{Fundamentals in non-convex analysis}
@@
 \section{Unifying variants of Nesterov's accelerated methods}\label{sec:unify-nes-acceleration}
+    \todoinline{
+        This section is really about stating the results of the draft paper and no explaining will be done here. 
+        Along with the content of the draft paper, we will also explain the origin and inspirations of the ideas. 
+    }
+    \todoinline{
+        Definitions:
+        \begin{enumerate}
+            \item Method of Nesterov's estimating sequence.
+            \item R-WAPG Sequence.
+            \item R-WAPG algorithm .
+            \item R-WAPG Intermediate form.
+            \item R-WAPG Similar triangle form. 
+            \item R-WAPG Momentum form. 
+        \end{enumerate}
+    }
+    \todoinline{
+        Theorems: 
+        \begin{enumerate}
+            \item Convergence of the R-WAPG algorithm.
+            \item R-WAPG First equivalent form. 
+            \item R-WAPG Second equivalent form.
+            \item R-WAPG Third equivalent form.
+            \item Convergence with constant momentum. 
+            \item Convergence with Chambolle, Dossal Sequences.
+        \end{enumerate}
+        Lemmas
+        \begin{enumerate}
+            \item Inverted FISTA sequence is a R-WAPG sequence.
+            \item Constant R-WAPG sequence.
+        \end{enumerate}
+    }
 
 \section{Method Free R-WAPG}\label{sec:spectral-momentum}
-
+    \todoinline{
+        Algorithm, and results of numerical experiments with their descriptions. 
+    }
 \section{Catalyst accelerations and future works}\label{sec:catalyst}
+    \todoinline{\noindent
+        Literatures review of the topics in Catalyst acceleration method. 
+        Here is a list of topics: 
+        \begin{enumerate}
+            \item The original accelerated PPM. 
+            \item The Catalyst with weakly convex objectives. 
+        \end{enumerate}
+        After the literature reviews of the core literatures, move on and state new research directions and open problems.     
+    }
+    \todoinline{\noindent
+        A list of relevant literatures: 
+        \begin{enumerate}
+            \item 
+        \end{enumerate}
+    }
 
@@
 
-\section{Nestrov's acceleration in the non-convex case and momentum in general}\label{sec:nes-acc-ncnvx}
+\section{Nestrov's acceleration in the non-convex case}\label{sec:nes-acc-ncnvx}
 

### 2024-12-23 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
     Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$.
-
     \par 
@@
     Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
-    Beck and Toubelle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it $\mathcal O(1/k^2)$ convergence rate is kept, and it performs empirically better. 
+    Beck and Toubelle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it has a $\mathcal O(1/k^2)$ convergence still, but it performs empirically better. 
     See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm. 
@@
 \section{Preliminaries}
-    Throughout, we define $F := f + g$ where $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: Q \rightarrow \overline \RR$ is convex. 
+    Throughout, we define $F := f + g$ where $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: \RR^n \rightarrow \overline \RR$ is convex. 
     We consider optimization problem: $\min_x \left\lbrace f(x) + g(x)\right\rbrace$.
-    Fix any arbitrary $y \in \RR^n$, define the model functions for all $x \in Q$
+    Fix any arbitrary $y \in \RR^n$, define the model functions for all $x \in \dom g$: 
     \begin{align*}
@@
     \end{align*}
-    When $x \in \RR\setminus Q$, the model function takes $+\infty$ value. 
+    When $x \in \RR\setminus \dom g$, the model function takes $+\infty$ value. 
     Define the proximal gradient operator and gradient mapping operator:  $T_L := [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f]$. 
@@
     \begin{proof}
-        Consider any $x \in Q$, by definition it has: 
+        Consider any $x \in \dom g$, by definition it has: 
         \begin{align*}
@@
         \end{align*}
-        The equality is trivially true when $x \in \RR \setminus Q$. 
+        The equality is trivially true when $x \in \RR \setminus \dom g$. 
     \end{proof}
@@
     \end{proof}
+    \begin{remark}
+        This proof works for all $L$ that is larger than the smallest Lipschitz modulus of $f$. 
+    \end{remark}
 
@@
             \\
-            \text{Use Q3}&= 
+            &= 
             F(x_k) - \epsilon_k 
@@
             \right\rangle
+            & \text{Use Q3}
             \\

### 2024-12-23 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
 
-\begin{document}
-
 \title{
@@
         First Order Nonsmooth Optimization: 
-        Algorithm Design, Analysis, Convergence, and Applications
+        Algorithm Design, Variational analysis, and Applications
     }
 }
-
 \author{
-    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
-    The University of British Columbia, Kelowna, BC Canada V1V 1V7. 
-    E-mail:  \texttt{alto@mail.ubc.ca}.}~Hongda Li
+    % \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
+    % The University of British Columbia, Kelowna, BC Canada V1V 1V7. 
+    % E-mail:  \texttt{alto@mail.ubc.ca}.}~Hongda Li
     % \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
@@
     % E-mail:  \texttt{shawn.wang@ubc.ca}.}~ and~Author Name 2
+    Hongda Li\\[3ex]\\ Department of Mathematics\\
+	University of British Columbia,\\
+	Okanagan Campus.
 }
-
 \date{\today}
 
-\maketitle
-
+\begin{document}
+% \vspace{10ex}
 % \vskip 8mm
 
-\begin{abstract} 
-    \noindent
-    The research proposal focuses on the theories and practice in solving nonsmooth optimization. 
-    The theme of proposal highlight topics of interests that emphasize the computations and applications aspect of algorithms that exhibits both practical and theoretical importance. 
-    We summarize our ongoing research in unifying Nesterov type accelerated proximal gradient method and proposes our Free R-WAPG method. 
-    We survey literatures under the topic of Catalyst Meta Acceleration framework used in accelerating variance reduced methods in the settings of Data Science and Machine Learning. 
-    Furthermore, we present literatures and progress in topics such as Performance Estimation Problem, Inexact Proximal Point, acceleration without convexity. 
-    At the end there is a section summarizing a method we developed for tree species classifications using Sentinel-2 satellite remote sensing data using big data analytics by extract spectral signatures of ground vegetation covers.
+\maketitle
+\tableofcontents
+\pagebreak
 
-\end{abstract}
+% \begin{abstract} 
+%     \noindent
+%     The research proposal focuses on the theories and practice in solving nonsmooth optimization. 
+%     The theme of proposal highlight topics of interests that emphasize the computations and applications aspect of algorithms that exhibits both practical and theoretical importance. 
+%     We summarize our ongoing research in unifying Nesterov type accelerated proximal gradient method and proposes our Free R-WAPG method. 
+%     We survey literatures under the topic of Catalyst Meta Acceleration framework used in accelerating variance reduced methods in the settings of Data Science and Machine Learning. 
+%     Furthermore, we present literatures and progress in topics such as Performance Estimation Problem, Inexact Proximal Point, acceleration without convexity. 
+%     At the end there is a section summarizing a method we developed for tree species classifications using Sentinel-2 satellite remote sensing data using big data analytics by extract spectral signatures of ground vegetation covers.
+
+% \end{abstract}
 % \noindent{\bfseries 2010 Mathematics Subject Classification:}
@@
 % \noindent{\bfseries Keywords: } Non-convex Optimizations, Proximal Point.
-
-\newpage
-\tableofcontents
 
@@
     \end{enumerate}
-    The good news is we have definitive answers for both questions by our own efforts of research. 
+    The good news is we have definitive answers for all questions by our own efforts of research. 
     Section \ref{sec:unify-nes-acceleration}, \ref{sec:spectral-momentum} are our ongoing research which present the answers to the questions. 
@@
     Section \ref{sec:catalyst} are results of literatures review in MATH 590. 
-    \todo{Add citations here. }{It's based on a series of papers} in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
+    \todo{Add citations here. }{\hl{It's based on a series of papers}} in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
     We will point out potential future direction of research of Catalyst acceleration. 
@@
     Section \ref{sec:pep}, \ref{sec:inexact-prox}, \ref{sec:nes-acc-ncnvx} preview literatures in  nonsmooth optimization frontier research where progress and impacts can be made.  
+    \subsection{Theme of the research}
+        This section specify a theme of the research in this proposal. 
+        Out first objective is to explore the Goldilocks zones between these topics: theories of variational analysis, design of continuous optimization algorithm and applications in sciences, engineering, and statistics.
+        Our second objective is to identify the ``chemistry" occuring between properties of functions and the designs of continuous optimizations algorithm and how it impacts the convergence and behaviors of the algorithms.
 
@@
     \todoinline{
-        Assumptions: Additive composite type convex objective until specified.  
+        Clarify: Notations,
+        Organizations. 
     }
+    This section contains the basics of contents from convex optimization, and variational analysis. 
+    \begin{enumerate}
+        \item $\overline \RR := \RR \cup \{\infty, -\infty\}$
+    \end{enumerate}
+    \subsection{Fundamentals in non-convex analysis}
+        \todoinline{\noindent
+            We are in $\RR^n$, and the weakest assumption we are making for the objective function is Local Lipschitz continuity. 
+            Definitions: 
+            \begin{enumerate}
+                \item[$\blacksquare$] Local Lipschitz continuity. 
+                \item[$\square$]Regular subgradient. Remember to cite. 
+                \item[$\square$] Limiting subgradient. Remember to cite. 
+                \item[$\blacksquare$] Weakly convex function. 
+                \item[$\blacksquare$]The Bregman Divergence of function. 
+            \end{enumerate}
+            Take Limiting, Regular subgradient definitions from Cui, Pong's book, Definition 4.3.1. 
+        }
+        Let the ambient space be $\RR^n$ equipped with inner product and 2-norm. 
+        Let $O$ be an open subset of $\RR^n$, the weakest assumption we are making for the objective function $F: O \subseteq \RR^n \rightarrow \RR$ for optimization problem is Local Lipschitz Continuity.
+        The assumption of local Lipschitz continuity is weak enough to describe most problems in applications, and strong enough to avoid most pathologies in analysis.
+
+        \begin{definition}[Local Lipschitz continuity]
+            Let $F: O \subseteq \RR^n \rightarrow \RR$ be Locally Lipschitz and $O$ is an open set. 
+            Then for all $\bar x \in O$, there exists a Neighborhood: $\mathcal N(\bar x)$ and $K \in \RR$ such that for all $x, y \in \mathcal N(\bar x)$: $|F(x) - F(y)| \le K \Vert x - y\Vert$. 
+        \end{definition}
+        \begin{definition}[Regular subgradient]
+            Let $F: O \subseteq \RR^n \rightarrow \RR$ be locally Lipschitz and $\bar x \in O$. 
+            The regular subdifferential at $\bar x$ is defined as 
+            \begin{align*}
+                \widehat \partial F(\bar x) := 
+                \left\lbrace
+                    v \in \RR^n \left| 
+                        \liminf_{\bar x \neq x\rightarrow \bar x}
+                        \frac{F(x) - F(\bar x) - \langle v, x - \bar x\rangle}{\Vert x - \bar x\Vert} 
+                        \ge 0
+                    \right.
+                \right\rbrace
+            \end{align*}
+        \end{definition}
+        \begin{definition}[Limiting subgradient]
+            Let $F: O \subseteq \RR^n \rightarrow \RR$ be locally Lipschitz and $\bar x \in O$. 
+            The limiting subdifferential at $\bar x$ is defined as 
+            \begin{align*}
+                \partial F(\bar x) := 
+                \left\lbrace
+                    v \in \RR^n \left| 
+                        \exists x_k \rightarrow \bar x, v_k \rightarrow v: 
+                        v_k \in \widehat \partial F(x_k) \;\forall k \in \mathbb N
+                    \right.
+                \right\rbrace. 
+            \end{align*}
+        \end{definition}
+        \begin{definition}[Weakly convex function]
+            $F: \RR^n \rightarrow \overline \RR$ is $\mu$ weakly convex if and only if $F + \frac{\mu}{2}\Vert \cdot\Vert^2$ is convex. 
+        \end{definition}
+        \begin{definition}[Bregman divergence]
+            Let $F: O \subseteq \RR^n \rightarrow \RR$ be a differentiable function. 
+            Then the Bregman divergence of $F$ is defined as: 
+            \begin{align*}
+                D_F(x, y): O \times \dom(\partial F) \rightarrow \RR
+                := F(x) - F(y) - \langle \nabla F(y), x - y\rangle. 
+            \end{align*}
+        \end{definition}
     \subsection{Fundamentals in convex analysis}
         \todoinline{
+            Introduce 
+            \begin{enumerate}
+                \item[$\blacksquare$] Convexity, 
+                \item[$\blacksquare$] convex subgradient, 
+                \item[$\blacksquare$] Lipschitz smoothness. 
+            \end{enumerate}
             Definitions: 
             \begin{enumerate}
-                \item [$\square$]Strong convexity of a function. 
-                \item [$\square$]The proximal gradient operator. 
-                \item [$\square$]The proximal mapping operator. 
-                \item [$\square$]The Bregman Divergence of function. 
+                \item [$\blacksquare$]Strong convexity of a function. 
+                \item [$\blacksquare$]The proximal gradient operator. 
+                \item [$\blacksquare$]The proximal mapping operator. 
             \end{enumerate}
@@
             \begin{enumerate}
-                \item [$\square$]Quadratic growth conditions of a strongly convex function. 
-                \item [$\square$]The proximal gradient envelope.
-                \item [$\square$]A property of gradient mapping. 
+                \item [$\blacksquare$]Quadratic growth conditions of a strongly convex function. 
+            \end{enumerate}
+        }
+        This section introduces the classics and basics of convex analysis. 
+        Define $F$ to be convex in this section. 
+        When $F$ is convex, the limiting subgradient and the regular subgradient reduced to the following definition:
+        \begin{align*}
+            \partial F(x) := \left\lbrace
+                v \in \RR^n \left|
+                    (\forall y \in \RR^n)\;  F(y) - F(x)  \ge \langle v, y - x\rangle
+                \right.
+            \right\rbrace. 
+        \end{align*}
+        A convex function is locally Lipschitz in the relative interior of its domain, denoted as $\reli(\dom(F))$. 
+        So it has $\reli(\dom F)\subseteq \dom(\partial F) \subseteq \dom F$. 
+        \par
+        When we say $F:\RR^n \rightarrow \RR$ is $L$ Lipschitz smooth function, it means that there exists $L$ such that for all $x\in \RR^n, y \in \RR^n$, it has: 
+        \begin{align*}
+            \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y\Vert. 
+        \end{align*}
+        This condition is stronger than differentiability. 
+        When $F$ convex, it has descent lemma: 
+        \begin{align*}
+            (\forall x \in \RR^n)(\forall y \in \RR^n): 0 \le 
+            F(x) - F(y) - \langle \nabla f(y), x - y\rangle \le \frac{L}{2}\Vert x - y\Vert^2. 
+        \end{align*}
+        When $F$ is convex, the converse holds. 
+        The definitions that follow narrow things further for future discussions. 
+        \begin{definition}[Strong convexity]
+            A function $F:\RR^n \rightarrow \overline \RR$ is $\mu \ge 0$ strongly convex if and only if for any fixed $y \in \dom(\partial F)$, we have for all $x\in \RR^n$: 
+            \begin{align*}
+                (\forall v \in \partial F(x))\quad 
+                F(x) - F(y) \ge \langle v, x - y\rangle + \frac{\mu}{2}\Vert x - y\Vert^2. 
+            \end{align*}
+        \end{definition}
+        \begin{lemma}[Quadratic growth from strong convexity]
+            If $F$ is $\mu \ge 0$ strongly convex, $\bar x$ is a minimizer of $F$. 
+            Then for all $x \in \RR^n$
+            \begin{align*}
+                F(x) - F(\bar x) \ge \frac{\mu}{2}\Vert x - \bar x\Vert^2. 
+            \end{align*}
+        \end{lemma}
+        \begin{remark}
+            The minimizer is unique whenever $\mu > 0$. 
+            For contradiction, assume $x$ is another minimizer, then $F(x) \neq F(\bar x)$, which is a direct contradiction. 
+        \end{remark}
+
+        \subsubsection{Smooth, nonsmooth additive composite}\label{sssec:additive-composite}
+            \todoinline{\noindent
+                Introduce notations for the proximal gradient model function. 
+                Lemmas: 
+                \begin{enumerate}
+                    \item[$\blacksquare$] Proximal gradient envelope. 
+                    \item[$\blacksquare$] A property of gradient mapping. 
                 \end{enumerate}
@@
                 \begin{enumerate}
-                \item [$\square$]The proximal gradient inequality, for additive composite objective where the smooth part is $\mu \ge 0$ strongly convex. 
+                    \item[$\blacksquare$] The proximal gradient inequality. 
                 \end{enumerate}
@@
 
-    \subsection{Fundamentals in non-convex analysis}
+            In this section, we zoom in further. 
+            Suppose that $F:= f + g$ where $f:\RR^n \rightarrow \RR$ is convex, $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: \RR\rightarrow \overline \RR$ is convex. 
+            To make the discussion simpler, fix any $\beta \ge 0$ we define the following model functions as a $\RR^n \times \RR^n \rightarrow \overline \RR$: 
+            \begin{align*}
+                \widetilde{\mathcal M}^{\beta^{-1}}
+                (x; y)
+                &:= 
+                g(x) + f(y) + \langle \nabla f(y), x - y\rangle
+                + \frac{\beta}{2}\Vert x - y\Vert^2,
+                \\
+                \mathcal M^{\beta^{-1}}(x; y) 
+                &:= F(x) + \frac{\beta}{2}\Vert x - y\Vert^2.
+            \end{align*}
+            Under convexity assumption in this section, both $\widetilde {\mathcal M} (\cdot; y),  {\mathcal M}(\cdot;y )$ is at least $\beta \ge 0$ strongly convex. 
+            \begin{definition}[Proximal gradient operator]
+                Suppose that $F := f + g$ where $g: \RR^n \rightarrow \overline \RR$ is convex and $f: \RR^n \rightarrow \RR$ is a $L$ Lipschitz smooth function.
+                Define the proximal gradient operator $T_L$ on all $y \in \RR^n$: 
+                \begin{align*}
+                    T_L y := \argmin_{x \in \RR^n} \left\lbrace
+                        g(x) + f(y) + \langle \nabla f(y), x - y\rangle 
+                        + \frac{L}{2}\Vert x- y \Vert^2
+                    \right\rbrace. 
+                \end{align*}
+            \end{definition}
+            \begin{remark}
+                Under the assumption of this section, the mapping $T_L$ is a single-valued mapping, it has domain on the entire $\RR^n$, and it's a $3/2$ averaged operator. 
+            \end{remark}
+            \begin{definition}[Gradient mapping operator]
+                Take $F := f + g$ as defined in this section. 
+                Define the gradient mapping operator $\mathcal G_L$ on all $y \in \RR^n$: 
+                \begin{align*}
+                    \mathcal G_L y:= L(y - T_L y). 
+                \end{align*}
+            \end{definition}
 
-\section{Unifying variants of Nesterov's accelerated methods}\label{sec:unify-nes-acceleration}
-    \todoinline{
-        This section is really about stating the results of the draft paper and no explaining will be done here. 
+            \begin{lemma}[Proximal gradient model function]\;\\
+                Take $\widetilde{\mathcal M}^{L^{-1}}, \mathcal M^{L^{-1}}$ as defined in this section, we will have for all $x \in \RR^n$ that: 
+                \begin{align*}
+                    \widetilde{\mathcal M}^{L^{-1}}(x; y)
+                    &= 
+                    \mathcal M^{L^{-1}}(x; y)- D_f(x, y).
+                \end{align*}
+            \end{lemma}
+            \begin{lemma}[A favorable property of gradient mapping]
+                Take $F:= f + g$ as defined in this section. 
+                Fix any $x \in \RR^n$. 
+                Then there exists $v \in \partial g(T_L x)$ such that $\mathcal G_L (x) = v + \nabla f(x)$. 
+            \end{lemma}
+            \begin{remark}
+                This lemma still holds for non-convex $f$. 
+            \end{remark}
+            \begin{lemma}[The proximal gradient inequality]
+                Take $F:= f + g$ as defined in this section. 
+                Fix any $y \in \RR^n$, then for all $x$, the proximal gradient inequality is true: 
+                \begin{align*}
+                    (\forall x \in \RR^n)\quad 
+                    h(x)  - h(Ty) - \langle L(y - Ty), x - y\rangle
+                    - \frac{\mu}{2}\Vert x - y\Vert^2 - \frac{L}{2}\Vert y - Ty\Vert^2 
+                    &\ge 0. 
+                \end{align*}
+            \end{lemma}
+            \begin{remark}
+                This lemma is proved in our draft paper. 
+            \end{remark}
+
+\section{Unifying NAG, and weakening the sequence assumption for convergences}\label{sec:unify-nes-acceleration}
+    \todoinline{\noindent
+        This section is really about stating the results of the draft paper and no proofs will be done here. 
         Along with the content of the draft paper, we will also explain the origin and inspirations of the ideas. 
@@
             \item R-WAPG Sequence.
-            \item R-WAPG algorithm .
+            \item R-WAPG algorithm.
             \item R-WAPG Intermediate form.
@@
     }
+    This section is based on the theoretical aspects of our draft paper. 
+    It will introduce major results and claims achieved during our research in each of the subsections. 
+    All theorems and claims stated in this section have proofs. 
+    The proofs haven't been carefully verified by people other than the author yet. 
+    We will start introducing the context and ideas for our research next. 
+    \par
+    Assume we want to solve a convex optimization problem: $\min_{x \in \RR^n} \{F(x)\}$ and $F: \RR^n \rightarrow \RR$ is a $L$ Lipschitz smooth function. 
+    We made this assumption for now for a faster exposition. 
+    One of the prime candidate for solving the optimization problem is the Nesterov's Accelerated Gradient methods (NAG) finds extensions for nonsmooth function through the proximal gradient operator.
+    \todo{Cite Nesterov's original paper on this.
+}{\hl{Proposed back in 1983 the original Nesterov's acceleration method}} which uses the previous iterates to extrapolate the next iterate to evaluate the gradient.
+    It's well known that, if minimizer $x^*$ exists for $F$, the method achieves a $\mathcal O(1/k^2)$ convergence rate on the objective value $F(x_k)$. 
+    \todo{Cite Chapter 2 of Nesterov's new book. }{\hl{This convergence rate is considered optimal for all class of $L$ Lipschitz smooth convex function}}. 
+    The convergence rate gurantee is faster than $\mathcal O(1/k)$ exibited by gradient descent. 
+    \par
+    We cover the algorithm briefly. 
+    Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
+    \begin{align}
+        & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
+        \\
+        & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
+        \\
+        & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
+        \\
+        & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
+    \end{align}\label{eqn:nag_example}
+    Unfortunately, the algorithm sped up the convergence rate for all convex function, it becomes slower for the subset of $\mu > 0$ strongly convex function. 
+    This drawback inspired a vast amount of literatures aims at improving, extending, and analyzing NAG. 
+    Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
+    \todo{Cite Beck 2009 FISTA. }{\hl{Beck and Toubelle}} mitigate the issue by restarting and showed that it still has a $\mathcal O(1/k^2)$ convergence rate, and it performs empirically better. 
+    \todo{Cite Necoara linear convergence, and Aujol 2024 Parameter free FISTA restart. }{\hl{See}} and references within for recent advancements in restarting accelerated proximal gradient algorithm.
+    \par
+    Restarting the algorithm is not the entire picture. 
+    Let $F:\RR^n \rightarrow \RR$ be a $L$ Lipschitz smooth and $\mu > 0$ function. 
+    As introduced previously, in \todo{Cite Walkington's education stuff here.
+}{\hl{Walkington's writing}}, he showed that there exists a variant of the Nesterov's accelerated gradient method that achieved a linear convergence rate of $\mathcal O((1 - \sqrt{\mu/L})^k)$.
+    However, this variant has a fixed momentum parameter $\theta_{k + 1} = \frac{\sqrt{\kappa} - 1}{\sqrt{k} + 1}$ back in Equation \ref{eqn:nag_example}. 
+    \todo{Cite them.}{\hl{The same variant also appears in Beck's book as V-FISTA, and Nesterov's book as (2.2.22).}} 
+    \par
+    One final Mystery of the algorithm is the convergence of the iterates which also has much to do with the momentum sequence $(\theta_k)_{k\ge 0}$ displayed in Equation \ref{eqn:nag_example}. 
+    Chambolle, Dossal showed that by choosing sequence $(t_k)_{k \ge 1}$ to be $t_k = $
+
+    \subsection{Our Contributions}
 
@@
         After the literature reviews of the core literatures, move on and state new research directions and open problems. 
+        There are several directions for open problem: 
+        \begin{enumerate}
+            \item APPM method for monotone operators instead of just subgradient, whether the same framework exists in a greater context. 
+            \item Accelerated Proximal Bregman Method. 
+        \end{enumerate}  
     }
@@
         \begin{enumerate}
-            \item 
+            \item Güler's 1992 paper on Accelerated Proximal Point method. 
+            \item Lin's, and Payquette's three triology paper on Catalyst acceleration for convex, non-convex Variance reduced algorithm. 
         \end{enumerate}

### 2024-12-23 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
     Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
-    \begin{align}
+    \begin{align}\label{eqn:nag_example}
         & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
@@
         & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
-    \end{align}\label{eqn:nag_example}
+    \end{align}
     Unfortunately, the algorithm sped up the convergence rate for all convex function, it becomes slower for the subset of $\mu > 0$ strongly convex function. 
@@
     One final Mystery of the algorithm is the convergence of the iterates which also has much to do with the momentum sequence $(\theta_k)_{k\ge 0}$ displayed in Equation \ref{eqn:nag_example}. 
-    Chambolle, Dossal showed that by choosing sequence $(t_k)_{k \ge 1}$ to be $t_k = $
+    \todo{Cite them.
+}{\hl{Chambolle, Dossal}} showed that by choosing sequence $(t_k)_{k \ge 1}$ to be $t_k = (n + a - 1)/a$ where $a > 2$ instead would give $(x_k)_{k \ge 0}$ weak convergence in Hilbert space.
+    It's put as an open question on what happens to the iterates when $a = 2$. 
+    \par
+    All of these seemingly raises a crucial question: ``Is it possible to describe something about the NAG algorithm for a set of sequence that is non-traditional?''.
+    Or rephrase it more clearly: ``What is the weakest description of momentum sequence $(\theta_k)$ such that we can still claim something of value about the NAG algorithm?''
 

### 2024-12-23 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
         Our contributions are two folds, theoretical and practical. 
-        Our results are based the assumption $F = f + g$ where $g:Q \rightarrow \overline\RR$ is convex, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
+        Our results are based the assumption $F = f + g$ where $g:\RR^n \rightarrow \overline\RR$ is convex, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
         \par
@@
         \end{align*}
-        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate.
-        And when $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}, which is an optimal algorithm for a strongly convex $F$.
-        R-WAPG gives the convergence claim, and it's consistent with the literatures. 
+        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}.
+        When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
+        In Theorem \ref{thm:fixed-momentum-fista}, it demonsrate that R-WAPG frameworks gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex.
         \par
-        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG''. 
+        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}). 
         The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ with minimal computational cost.
@@
     \begin{align*}
-        T_Ly &= \argmin_x \left\lbrace
+        T_Ly &= \argmin_{x \in \RR^n} \left\lbrace
             g(x) + \langle \nabla f(y), x\rangle + L/2\Vert x - y\Vert^2
@@
         \end{align*}
-        The equality is trivially true when $x \in \RR \setminus \dom g$. 
+        The equality is trivially true when $x \in \RR^n \setminus \dom g$. 
     \end{proof}
@@
 
-    \begin{theorem}[FISTA first variant Chambolle, Dossal 2015]\;\\
+    \begin{theorem}[FISTA first variant Chambolle, Dossal 2015]\label{thm:r-wapg-on-cham-doss}\;\\
         Fix arbitrary $a \ge 2$.

### 2024-12-23 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
             \end{remark}
-            \begin{lemma}[The proximal gradient inequality]
+            \begin{lemma}[The proximal gradient inequality]\label{thm:prox-grad-ineq}
                 Take $F:= f + g$ as defined in this section. 
@@
         \begin{enumerate}
-            \item Method of Nesterov's estimating sequence.
+            \item \st{Method of Nesterov's estimating sequence.}
+            \item R-WAPG stepwise definition 
+            \item R-WAPG stepwise convergence claim
             \item R-WAPG Sequence.
@@
     It will introduce major results and claims achieved during our research in each of the subsections. 
-    All theorems and claims stated in this section have proofs. 
+    All theorems and claims stated in this section have proofs in the draft paper. 
     The proofs haven't been carefully verified by people other than the author yet. 
@@
 
-    \subsection{Our Contributions}
+    \subsection{Our Contributions, organizations}
+        Our contributions are two folds, theoretical and practical. 
+        Our results are based the assumption $F = f + g$ where $g:R^n \rightarrow \overline\RR$ is convex, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
+        We relax the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:nag_example} and showed an upper bound of the optimal gap. 
+        Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
+        \begin{align*}
+            \alpha_0 &\in (0, 1], 
+            \\
+            \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
+            \\
+            \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
+        \end{align*}
+        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wagp-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
+        \begin{align*}
+            \mathcal O\left(
+                \left(
+                    \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
+                \right)
+                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
+            \right). 
+        \end{align*}
+        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}.
+        When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
+        In Theorem \ref{thm:fixed-momentum-fista}, it demonsrate that R-WAPG frameworks gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex.
+        \par
+        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}). 
+        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ with minimal computational cost.
+        We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart. 
+        \par
+        Organization now follows. 
+        \todoinline{Finish the organizations here after this section is finished. }
+    \subsection{Building Blocks of R-WAPG}
+
+    \subsection{R-WAPG Sequence and R-WAPG algorithm}
+
+    \subsection{Equivalent forms of R-WAPG algorithm}
+
+    \subsection{The descriptive power of R-WAPG on existing variants}
 
@@
     }
+
 \section{Catalyst accelerations and future works}\label{sec:catalyst}

### 2024-12-23 Notebook LaTEX/Proposal/main.tex
>w<, a lot of changes

@@
     }
-    \todoinline{
-        Definitions:
-        \begin{enumerate}
-            \item \st{Method of Nesterov's estimating sequence.}
-            \item R-WAPG stepwise definition 
-            \item R-WAPG stepwise convergence claim
-            \item R-WAPG Sequence.
-            \item R-WAPG algorithm.
-            \item R-WAPG Intermediate form.
-            \item R-WAPG Similar triangle form. 
-            \item R-WAPG Momentum form. 
-        \end{enumerate}
-    }
-    \todoinline{
-        Theorems: 
-        \begin{enumerate}
-            \item Convergence of the R-WAPG algorithm.
-            \item R-WAPG First equivalent form. 
-            \item R-WAPG Second equivalent form.
-            \item R-WAPG Third equivalent form.
-            \item Convergence with constant momentum. 
-            \item Convergence with Chambolle, Dossal Sequences.
-        \end{enumerate}
-        Lemmas
-        \begin{enumerate}
-            \item Inverted FISTA sequence is a R-WAPG sequence.
-            \item Constant R-WAPG sequence.
-        \end{enumerate}
-    }
     This section is based on the theoretical aspects of our draft paper. 
@@
 }{\hl{Walkington's writing}}, he showed that there exists a variant of the Nesterov's accelerated gradient method that achieved a linear convergence rate of $\mathcal O((1 - \sqrt{\mu/L})^k)$.
-    However, this variant has a fixed momentum parameter $\theta_{k + 1} = \frac{\sqrt{\kappa} - 1}{\sqrt{k} + 1}$ back in Equation \ref{eqn:nag_example}. 
+    However, this variant has a fixed momentum parameter $\theta_{k + 1} = (\sqrt{\kappa} - 1)(\sqrt{\kappa} + 1)^{-1}$ back in Equation \ref{eqn:nag_example}. 
     \todo{Cite them.}{\hl{The same variant also appears in Beck's book as V-FISTA, and Nesterov's book as (2.2.22).}} 
@@
     \par
-    All of these seemingly raises a crucial question: ``Is it possible to describe something about the NAG algorithm for a set of sequence that is non-traditional?''.
-    Or rephrase it more clearly: ``What is the weakest description of momentum sequence $(\theta_k)$ such that we can still claim something of value about the NAG algorithm?''
+    All of these seemingly raises a crucial question: ``Is it possible to describe something about the NAG algorithm for a set of sequence that is non-traditional?''; rephrasing it int a more technical manner: ``What is the weakest description of the momentum sequence $(\theta_k)$ such that we can still claim something of value about the NAG algorithm?''
 
@@
         \end{align*}
-        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}.
+        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in \todo{Fix citation here.}{\hl{Chambolle, Dossal}} \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}.
         When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
@@
         \par
+        Notations, and assumptions now follows. 
+        For all the subsection that follows, we let $F:= f + g$ to take the same assumptions as in Section \ref{sssec:additive-composite}. 
+        Recall $T_L$, $\mathcal G_L$ denotes the proximal gradient operator and the gradient mapping operator. 
+        Additional notations are defined in the assumption below: 
+        \begin{assumption}
+            Choose any integer $k\ge 0$. 
+            Given $x_k, y_k, v_k$, we define the following quantities
+            \begin{align}
+                g_k &\defeq L(y_k - T_L y_k), 
+                \label{eqn:grad-map}
+                \\
+                l_F(x; y_k) &\defeq F(T_Ly_k) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
+                \label{eqn:lower-linearization}
+                \\
+                \epsilon_{k} &\defeq F(x_k) - l_F(x_k; y_k), 
+                \label{eqn:regret}
+            \end{align}
+            Observe that by convexity of $F$, $\epsilon_k \ge 0$ for all $x_k, L > 0$. 
+            To see, use Theorem \ref{thm:prox-grad-ineq} and let $y = y_k, x = x_k$ which gives: 
+            \begin{align*}
+                F(x_k) - F(T_Ly_k)
+                - \langle L(y_k - T_Ly_k),x_k - y_k \rangle
+                - \frac{L}{2}\Vert y_k - T_Ly_k\Vert^2
+                - \frac{\mu}{2}\Vert x_k - y_k\Vert^2
+                &\ge 0
+                \\
+                \iff 
+                F(x_k) - F(T_Ly_k)
+                - \langle g_k,x_k - y_k \rangle
+                - \frac{1}{2L}\Vert g_k\Vert^2
+                &\ge 0. 
+            \end{align*}
+        \end{assumption}
+        \par
         Organization now follows. 
@@
     \subsection{Building Blocks of R-WAPG}
+        \todoinline{\noindent
+            Definitions: 
+            \begin{enumerate}
+                \item[$\blacksquare$] R-WAPG stepwise definition.
+                \item[$\blacksquare$] R-WAPG stepwise convergence claim.
+            \end{enumerate}
+            Todo: 
+            \begin{enumerate}
+                \item Explain what is what. 
+            \end{enumerate}
+        }
+        \begin{definition}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
+            Assume $0 \le \mu < L$.
+            Fix any $k \in \mathbb Z$. 
+            For any $(v_k, x_k), \alpha_k \in (0, 1), \gamma_k > 0$, let $\hat \gamma_{k + 1}$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ be given by: 
+            \begin{align*}
+                \hat \gamma_{k + 1} &= (1 - \alpha_k)\gamma_k + \mu \alpha_k, 
+                \\
+                y_k &= 
+                (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
+                \\
+                g_k &= \mathcal G_L y_k, 
+                \\
+                v_{k + 1} &= \hat\gamma^{-1}_{k + 1}
+                (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
+                \\
+                x_{k + 1} &= T_L y_k. 
+            \end{align*}
+        \end{definition}
+
+        \begin{proposition}[Stepwise Lyapunov]\label{prop:stepwise-lyapunov}\;\\
+            Fix any integer $k \in \mathbb Z$.
+            Given any $v_k, x_k$ and $\gamma_k > 0$, invoke Definition \ref{def:stepwise-wapg} to obtain $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}$. 
+            Fix any arbitrary $R_k \in \RR$.
+            Define: 
+            \begin{align*}
+                R_{k + 1}
+                \defeq
+                \frac{1}{2}\left(
+                    L^{-1} - \frac{\alpha_k^2}{\hat \gamma_{k + 1}}
+                \right)\Vert g_k\Vert^2
+                + 
+                (1 - \alpha_k)
+                \left(
+                    \epsilon_k + R_k + 
+                    \frac{\mu\alpha_k\gamma_k}{2\hat \gamma_{k + 1}}
+                    \Vert v_k - y_k\Vert^2
+                \right). 
+            \end{align*}
+            Then it has for all $x^* \in \RR^n$ where $F^* = F(x^*)$, the inequality: 
+            \begin{align*}
+                F(x_{k + 1}) - F^* + R_{k + 1} + \frac{\hat \gamma_{k + 1}}{2}\Vert v_{k + 1} - x^*\Vert^2
+                &\le 
+                (1 - \alpha_k)
+                \left(
+                    F(x_k) - F^* + R_k + \frac{\gamma_{k}}{2}\Vert v_k - x^*\Vert^2
+                \right). 
+            \end{align*}
+        \end{proposition}
 
     \subsection{R-WAPG Sequence and R-WAPG algorithm}
+        \todoinline{\noindent
+            The R-WAPG Algorithm and convergence claim. 
+            Definitions: 
+            \begin{enumerate}
+                \item[$\blacksquare$] R-WAPG Sequence.
+                \item[$\blacksquare$] R-WAPG algorithm
+                \item[$\blacksquare$] Convergence of the R-WAPG algorithm.
+            \end{enumerate}
+            Todo: 
+            \begin{enumerate}
+                \item Explain what is what. 
+            \end{enumerate}
+        }
+        \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}\;\\
+            Assume $0 \le \mu < L$. 
+            The sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge1}$ are sequences parameterized by $\mu, L$. 
+            They are valid for R-WAPG if all the following holds: 
+            \begin{align*}
+                \alpha_0 &\in (0, 1], 
+                \\
+                \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
+                \\
+                \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
+            \end{align*}
+            We call $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ the \textbf{R-WAPG Sequences}. 
+        \end{definition}
+        \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}\;\\
+            Choose any $x_1 \in \RR^n, v_1 \in \RR^n$. 
+            Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}. 
+            The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for $k\ge 1$ by the procedures:  
+            \begin{tcolorbox}
+                For $k=1, 2, 3, \cdots$
+                \begin{align*}
+                    \gamma_k &:= \rho_{k -1}L\alpha_{k - 1}^2, 
+                    \\
+                    \hat \gamma_{k + 1} & := (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2, 
+                    \\
+                    y_k &= 
+                    (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
+                    \\
+                    g_k &= \mathcal G_L y_k, 
+                    \\
+                    v_{k + 1} &= 
+                    \hat\gamma^{-1}_{k + 1}
+                    (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
+                    \\
+                    x_{k + 1} &= T_L y_k. 
+                \end{align*}    
+            \end{tcolorbox}
+        \end{definition}
+        \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}\; \\
+            Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$. 
+            Let vector sequence $(y_k, v_{k}, x_{k})_{k \ge 1}$ and R-WAPG sequences $\alpha_k, \rho_k$ be given by Definition \ref{def:wapg}. 
+            Define $R_1 = 0$ and suppose that for $k = 1, 2, \cdots, N$, we have $R_k$ recursively given by: 
+            \begin{align*}
+                R_{k + 1}
+                := 
+                \frac{1}{2}\left(
+                    L^{-1} - \frac{\alpha_k^2}{\hat \gamma_{k + 1}}
+                \right)\Vert g_k\Vert^2
+                + 
+                (1 - \alpha_k)
+                \left(
+                    \epsilon_k + R_k + 
+                    \frac{\mu\alpha_k\gamma_k}{2\hat \gamma_{k + 1}}
+                    \Vert v_k - y_k\Vert^2
+                \right). 
+            \end{align*} 
+            Then for all $k = 1, 2, \cdots, N$: 
+            \begin{align*}
+                & F(x_{k + 1}) - F(x^*) + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
+                \\
+                &\le 
+                \left(
+                    \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
+                \right)
+                \left(
+                    \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
+                \right)
+                \left(
+                    F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
+                \right). 
+            \end{align*}
+        \end{proposition}
 
     \subsection{Equivalent forms of R-WAPG algorithm}
+        \todoinline{
+            Definitions:
+            \begin{enumerate}
+                \item[$\blacksquare$] R-WAPG Intermediate form.
+                \item[$\blacksquare$] R-WAPG Similar triangle form. 
+                \item[$\blacksquare$] R-WAPG Momentum form. 
+            \end{enumerate}
+        }
+        \todoinline{
+            Theorems: 
+            \begin{enumerate}
+                \item[$\blacksquare$] R-WAPG First equivalent form. 
+                \item[$\blacksquare$] R-WAPG Second equivalent form.
+                \item[$\blacksquare$] R-WAPG Third equivalent form.
+            \end{enumerate}
+            Lemmas
+            Todo: 
+            \begin{enumerate}
+                \item Explain what is what. 
+            \end{enumerate}
+        }
+        \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
+            Assume $\mu < L$ and let $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 
+            Initialize any $x_1, v_1$ in $\RR^n$. 
+            For $k \ge 1$, the algorithm generates sequence of vector iterates $(y_{k}, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by the procedures: 
+            \begin{tcolorbox}
+                For $k = 1, 2, \cdots$
+                \begin{align*} 
+                    & y_{k} = 
+                    \left(
+                        1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
+                    \right)^{-1}
+                    \left(
+                        v_{k + 1} + 
+                        \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
+                    \right), 
+                    \\
+                    & x_{k + 1} = 
+                    y_k - L^{-1} \mathcal G_L y_k, 
+                    \\
+                    & v_{k + 1} = 
+                    \left(
+                        1 + \frac{\mu}{L \alpha_k - \mu}
+                    \right)^{-1}
+                    \left(
+                        v_k + 
+                        \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
+                    \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
+                \end{align*}
+            \end{tcolorbox}
+        \end{definition}
+        \begin{definition}[R-WAPG similar triangle form]\label{def:r-wapg-st-form} \; \\
+            Given any $(x_1, v_1)$ in $\RR^n$. 
+            Assume $\mu < L$.
+            Let the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k\ge 0}$ be given by Definition \ref{def:rwapg-seq}. 
+            For $k \ge 1$, the algorithm generates sequences of vector iterates $(y_k, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by the procedures: 
+            \begin{tcolorbox}
+                For $k=1, 2, \cdots $
+                \begin{align*}
+                    & y_k = 
+                    \left(
+                        1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
+                    \right)^{-1}
+                    \left(
+                        v_k + 
+                        \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
+                    \right), 
+                    \\
+                    & x_{k + 1} = 
+                    y_k - L^{-1} \mathcal G_L y_k, 
+                    \\
+                    & v_{k + 1} = 
+                    x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k). 
+                \end{align*}    
+            \end{tcolorbox}
+        \end{definition}
+        \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
+            Given any $y_1 = x_1 \in \RR^n$, and sequences $(\rho_k)_{k \ge 0}, (\alpha_k)_{k\ge 0}$ Definition \ref{def:rwapg-seq}. 
+            The algorithm generates iterates $x_{k + 1}, y_{k + 1}$ For $k = 1, 2, \cdots $ by the procedures: 
+            \begin{tcolorbox}
+                For $k=1, 2,\cdots $
+                \begin{align*}
+                    & x_{k + 1} = y_k - L^{-1}\mathcal G_Ly_k, 
+                    \\
+                    & 
+                    y_{k + 1} = 
+                    x_{k + 1} + 
+                    \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
+                \end{align*}    
+            \end{tcolorbox}
+            In the special case where $\mu = 0$, the momentum term can be represented without relaxation parameter $\rho_k$: 
+            $$
+                (\forall k \ge 1)\quad \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}} 
+                = \alpha_{k + 1}(\alpha_k^{-1} - 1).  
+            $$
+        \end{definition}
+        \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\
+            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}), 
+            then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$, and for all $k\ge 1$ they are algebraically equivalent to
+            \begin{align*}
+                & 
+                y_{k} = 
+                \left(
+                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
+                \right)^{-1}
+                \left(
+                    v_{k} + 
+                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
+                \right), 
+                \\
+                & x_{k + 1} = 
+                y_k - L^{-1} \mathcal G_L y_k, 
+                \\
+                & v_{k + 1} = 
+                \left(
+                    1 + \frac{\mu}{L \alpha_k - \mu}
+                \right)^{-1}
+                \left(
+                    v_k + 
+                    \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
+                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
+            \end{align*}
+        \end{proposition}
+        \begin{proposition}[Second equivalent representation of R-WAPG]\label{prop:wagp-st-form}\;\\
+            Let iterates $(y_k, x_{k}, v_{k})_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge 0}$ be given by Definition \ref{def:r-wapg-intermediate}. 
+            Then for all $k \ge 1$, iterate $y_k, x_{k + 1}, v_{k + 1}$
+            satisfy: 
+            \begin{align*}
+                y_{k} &= 
+                \left(
+                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
+                \right)^{-1}
+                \left(
+                    v_{k} + 
+                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
+                \right), 
+                \\
+                x_{k + 1} &= 
+                y_k - L^{-1} \mathcal G_L y_k, 
+                \\
+                v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
+            \end{align*}
+        \end{proposition}
+        \begin{proposition}[Third equivalent representation of R-WAPG]\label{prop:r-wapg-momentum-repr}
+            \;\\
+            Let sequence $(\alpha_k, \rho_k)_{k \ge 0}$ and iterates $(x_k, v_k, y_k)_{k\ge 1}$ given by R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}). 
+            Then for all $k \ge 1$, the iterates $(x_{k + 1}, y_{k + 1})_{k \ge 1}$ are algebraically equivalent to: 
+            \begin{align*}
+                x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
+                \\
+                y_{k + 1} &= 
+                x_{k + 1} + 
+                \frac{\rho_k\alpha_k(1 - \alpha_k)}
+                {\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
+            \end{align*}
+            If in addition, $v_1 = x_1$ then 
+            \begin{align*}
+                y_1 = \left(
+                    1 + \frac{L - L \alpha_1}{L\alpha_1 - \mu}
+                \right)^{-1}\left(
+                    v_1 + \left(
+                        \frac{L - L \alpha_1}{L \alpha_1 - \mu}
+                    \right)x_1
+                \right) = x_1. 
+            \end{align*}
+            In the special case when $\mu = 0$, the momentum term admits simpler representation 
+            \begin{align*}
+                (\forall k \ge 1) \quad 
+                \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
+                & = \alpha_{k + 1}(\alpha_k^{-1} - 1). 
+            \end{align*}
+        \end{proposition}
 
     \subsection{The descriptive power of R-WAPG on existing variants}
+        \todoinline{\noindent
+            Lemmas: 
+            \begin{enumerate}
+                \item Inverted FISTA sequence is a R-WAPG sequence.
+                \item Constant R-WAPG sequence.
+            \end{enumerate}
+            Theorems: 
+            \begin{enumerate}
+                \item Convergence with constant momentum. 
+                \item Convergence with Chambolle, Dossal Sequences.
+            \end{enumerate}
+            Todo: 
+            \begin{enumerate}
+                \item Explain what is what. 
+            \end{enumerate}
+        }
+
+        \begin{lemma}[R-WAPG sequences as inverted FISTA sequence]\label{lemma:inverted-fista-seq}
+            Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 
+            If $\mu = 0, \rho_k \ge 1\; \forall k \ge 0$, and $\alpha_0 = 1$, then: 
+            \begin{enumerate}
+                \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$
+                \item Let $t_k := \alpha_k^{-1}$, then $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``Inverted FISTA sequence''. 
+                \item $\prod_{i = 1}^k\max(1, \rho_{k - 1})(1 - \alpha_k) = \alpha_k^2 \quad (\forall k \ge 1)$. 
+            \end{enumerate}
+        \end{lemma}
+        \begin{lemma}[Constant R-WAPG sequences]\label{lemma:constant-rwapg-seq}
+            Suppose $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are R-WAPG sequences given by Definition \ref{def:rwapg-seq} and assume $L > \mu > 0$.
+            Define $q := \mu/L$. 
+            Then $\forall r \in \left(\sqrt{q},\sqrt{q^{-1}}\right)$, the constant sequence $\alpha_k := r \sqrt{q}$ has the following: 
+            \begin{enumerate}
+                \item Fix any $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$ then the constant sequence $\alpha_k := \alpha \in (q, 1)$ and\\
+                $\rho_k := \rho=\left(1-r^{-1}\sqrt{q}\right)\left(1 - r \sqrt{q}\right)^{-1} > 0$, hence it's a pair of valid R-WAPG sequence. 
+                \item The momentum term in Definition \ref{def:r-wapg-momentum-form}, which we denoted by $\theta$ has:\\ $\theta = (1 - r^{-1}\sqrt{q})(1 - r\sqrt{q})(1- q)^{-1}$. 
+                \item When $r = 1$, $\theta = (1- \sqrt{q})(1 + \sqrt{q})^{-1}$. 
+                \item For all $r \in \left(1, \sqrt{q^{-1}}\right)$, $\rho > 1$; for all $r \in \left(\sqrt{q}, 1\right]$ $\rho \le 1$. 
+                \item For all $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, $\max(\rho, 1)(1 - \alpha) = \max\left(1 - r\sqrt{q}, 1 - r^{-1}q\right)$. 
+            \end{enumerate}
+        \end{lemma}
+        \begin{theorem}[FISTA first variant Chambolle, Dossal 2015]\label{thm:r-wapg-on-cham-doss}\;\\
+            Fix arbitrary $a \ge 2$.
+            Define $\forall k \ge 1$ the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ by 
+            \begin{align*}
+                \alpha_k &= a/(k + a), 
+                \\
+                \rho_k &= \frac{(k + a)^2}{(k + 1)(k + a + 1)}. 
+            \end{align*}
+            Consider the algorithm given by: 
+            \begin{tcolorbox}
+                Initialize any $y_1 = x_1$. 
+                \\
+                For $k = 1, 2, \cdots$, update: 
+                \begin{align*}
+                    & x_{k + 1} := y_k + L^{-1}\mathcal G_L(y_k), 
+                    \\
+                    & \theta_{t + 1} := \alpha_{k + 1}(\alpha_k^{-1} - 1),
+                    \\
+                    & y_{k + 1} := x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
+                \end{align*}    
+            \end{tcolorbox}
+            If $\mu = 0$, then $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid pair of R-WAPG sequence from Definition \ref{def:rwapg-seq} and the above algorithm is a valid form of R-WAPG. 
+            \par
+            Assume minimizer $x^*$ exists for function $F$. 
+            Then algorithm produces $(x_k)_{k \ge0}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O(\alpha_k^2)$. 
+        \end{theorem}
+        \begin{theorem}[Fixed momentum APG]\label{thm:fixed-momentum-fista}
+            Assume $L > \mu > 0$, let a pair of constant R-WAPG sequence: $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Lemma \ref{lemma:constant-rwapg-seq}.
+            Define $q := \mu/L$ and for any fixed $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, let $\alpha_k := \alpha = r \sqrt{q}$ be the constant R-WAPG sequence. 
+            Consider the algorithm with a constant momentum specified by the following: 
+            \begin{tcolorbox}
+                Define $\theta = \left(1 - r^{-1}\sqrt{q}\right)(1 - r\sqrt{q})(1 - q)^{-1}$. 
+                \\
+                Initialize $y_1 = x_1$; for $k = 1, 2, \cdots, N$, update: 
+                \begin{align*}
+                    &x_{k + 1} = y_k + L^{-1}\mathcal G_L y_k, 
+                    \\
+                    & y_{k + 1} = x_{k + 1} + \theta(x_{k + 1} - x_k). 
+                \end{align*}
+            \end{tcolorbox}
+            Then the algorithm generates $(x_k)_{k \ge 1}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O\left(\max(1 - r\sqrt{q}, 1 - r^{-1}\sqrt{q})^k\right)$. 
+        \end{theorem}
 
@@
     }
+    This section introduces an algorithm of our creation inspired by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
+    Algorithm \ref{alg:free-rwapg} estimates the $\mu$ constant as the algorithm executes and pools the information using the Bregman Divergence of the smooth part function $f$. 
+    \begin{algorithm}
+        \begin{algorithmic}[1]
+        {\footnotesize
+        \STATE{\textbf{Input: } $f, g, x_0, L > \mu \ge 0, \in \RR^n, N \in \N$}
+        \STATE{\textbf{Initialize: }$y_0 := x_0;L := 1; \mu := 1/2; \alpha_0 = 1;$}
+        \STATE{\textbf{Compute: } $f(y_k)$; }
+        \FOR{$k = 0, 1, 2, \cdots, N$}
+            \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$;}
+            \WHILE{$L/2\Vert x^+ - y\Vert^2 < D_f(x^+, y)$}
+                \STATE{$L:= 2L$;}
+                \STATE{$x^+ = [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$; }
+            \ENDWHILE
+            \STATE{$x_{k + 1} := x^+$;}
+            \STATE{$\alpha_{k + 1} := (1/2)\left(\mu/L - \alpha_{k}^2 + \sqrt{(\mu/L - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;}
+            \STATE{$\theta_{k + 1} := \alpha_k(1 - \alpha_k)/(\alpha_k^2 + \alpha_{k + 1})$;}
+            \STATE{$y_{k + 1}:= x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$; }
+            \STATE{\textbf{Compute: } $f(y_{k + 1})$}
+            \STATE{$\mu := (1/2)(2D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2) + (1/2)\mu$;}
+        \ENDFOR
+        }
+        \end{algorithmic}
+        \caption{Free R-WAPG}
+        \label{alg:free-rwapg}
+    \end{algorithm}
+    \par
+    Line 5-8 estimates upper bound for the Lipschitz constant and find $x^+$, the next iterates produced by proximal gradient descent on previous $y_k$.
+    Line 9 updates $x_{k + 1}$ to be $x^+$, a successful iterate identified by the Lipschitz line search routine. 
+    Line 10 updates the R-WAPG sequence $\alpha_k$ for the iterates $y_{k + 1}$. 
+    Line 13 updates $\mu$ using the Bregman Divergence of $f$ from iterates $y_{k + 1}, y_k$. 
+    \par
+    Assume $L$ given is an upper bound of the Lipschitz smoothness constant of $f$, then the algorithm calls $f(\cdot)$ two times, and $\nabla f(\cdot)$ once per iteration. 
+    The algorithm computes $\nabla f(y_k)$ once for $x^+$, $f(y_{k + 1})$ once for Bregman Divergence because $f(y_{k})$ is evaluated from the previous iteration, and $f(x^+)$ once for Lipschitz constant line search condition.
+    We note that $f(y_0)$ is computed before the start of the for loop. 
+    And finally, it evaluates proximal of $g$ at $y_k - L^{-1}\nabla f(y_k)$ once.
 

### 2024-12-24 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, a lot of changes
>w<, changes

@@
             \\
-            \implies
+            \iff
             \left(
@@
     \begin{remark}
-        \textcolor{red}
-        {
-        Given $y_k$, we may choose to increase $\mu_\kappa = 2D_f(x^*, y_k)/\Vert y_k - x^*\Vert^2 \ge \mu$ which also works on (4*), $\mu$ is a pessimistic choice for the inequality above. 
-        }
+        Given $y_k$, we can choose to increase $\mu_\kappa = 2D_f(x^*, y_k)/\Vert y_k - x^*\Vert^2 \ge \mu$ which also works on (4*).
+        This is true by the intermediate steps taken to prove Theorem \ref{thm:prox-grad-ineq}. 
+        $\mu$ is a pessimistic choice for the inequality above. 
         But in general the choice of $\mu$ remains the strong convexity modulus or equivalently, any value that is smaller than the true strong convexity constant for claiming the convergence rate for all initial guesses.
@@
             $\rho_k := \rho=\left(1-r^{-1}\sqrt{q}\right)\left(1 - r \sqrt{q}\right)^{-1} > 0$, hence it's a pair of valid R-WAPG sequence. 
-            \item The momentum term in Definition \ref{def:r-wapg-momentum-form}, which we denoted by $\theta$ has:\\ $\theta = (1 - r^{-1}\sqrt{q})(1 - r\sqrt{q})(1- q)^{-1}$. 
+            \item The momentum terms $\theta_{t + 1}$ in Definition \ref{def:r-wapg-momentum-form}, which we denoted by $\theta$ is the constant:\\ $\theta = (1 - r^{-1}\sqrt{q})(1 - r\sqrt{q})(1- q)^{-1}$
             \item When $r = 1$, $\theta = (1- \sqrt{q})(1 + \sqrt{q})^{-1}$. 
@@
         Assume minimizer $x^*$ exists for function $F$. 
-        Then algorithm produces $(x_k)_{k \ge0}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O(1/k^2)$. 
+        Then algorithm produces $(x_k)_{k \ge0}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O(\alpha_k^2)$. 
     \end{theorem}

### 2024-12-24 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
                     \right.
-                \right\rbrace
+                \right\rbrace. 
             \end{align*}
@@
             For contradiction, assume $x$ is another minimizer, then $F(x) \neq F(\bar x)$, which is a direct contradiction. 
+            The quadratic growth condition over a set of minimizer is much weaker than convexity. 
         \end{remark}
@@
             \begin{definition}[Proximal gradient operator]
-                Suppose that $F := f + g$ where $g: \RR^n \rightarrow \overline \RR$ is convex and $f: \RR^n \rightarrow \RR$ is a $L$ Lipschitz smooth function.
+                Take $F := f + g$ where $g: \RR^n \rightarrow \overline \RR$ as defined in this section. 
                 Define the proximal gradient operator $T_L$ on all $y \in \RR^n$: 
@@
 
+    \subsection{Nesterov's Estimating sequence technique}
+        \todoinline{\noindent
+            Do the following: 
+            \begin{enumerate}
+                \item What is Nesterov's estimating sequence. 
+                \item How is it used to derive the algorithm and convergence rate of algorithm. 
+                \item Where is it used and why is it important here. 
+            \end{enumerate}
+        }
+        \todoinline{
+            Examples
+            \begin{enumerate}
+                \item Example estimating sequence. 
+            \end{enumerate}
+        }
+
 \section{Unifying NAG, and weakening the sequence assumption for convergences}\label{sec:unify-nes-acceleration}
@@
     \todo{Cite Chapter 2 of Nesterov's new book. }{\hl{This convergence rate is considered optimal for all class of $L$ Lipschitz smooth convex function}}. 
-    The convergence rate gurantee is faster than $\mathcal O(1/k)$ exibited by gradient descent. 
+    The convergence rate guarantee is faster than $\mathcal O(1/k)$ exhibited by gradient descent. 
     \par
@@
     Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
-    \todo{Cite Beck 2009 FISTA. }{\hl{Beck and Toubelle}} mitigate the issue by restarting and showed that it still has a $\mathcal O(1/k^2)$ convergence rate, and it performs empirically better. 
+    \todo{Cite Beck 2009 FISTA. }{\hl{Beck and Toubelle}} mitigate the issue by restarting and showed that it still has a $\mathcal O(1/k^2)$ convergence rate, and it performs better empirically. 
     \todo{Cite Necoara linear convergence, and Aujol 2024 Parameter free FISTA restart. }{\hl{See}} and references within for recent advancements in restarting accelerated proximal gradient algorithm.
@@
     As introduced previously, in \todo{Cite Walkington's education stuff here.
-}{\hl{Walkington's writing}}, he showed that there exists a variant of the Nesterov's accelerated gradient method that achieved a linear convergence rate of $\mathcal O((1 - \sqrt{\mu/L})^k)$.
+}{\hl{Walkington's writing}}, he showed that there exists a variant of the Nesterov's accelerated gradient method that achieved a linear convergence rate of $\mathcal O((1 - \sqrt{\kappa})^k)$ where $\kappa = \mu/L$.
+    This convergence rate is strictly better than $\mathcal O((1 - \mu/L)^k)$ for the method of gradient descent. 
     However, this variant has a fixed momentum parameter $\theta_{k + 1} = (\sqrt{\kappa} - 1)(\sqrt{\kappa} + 1)^{-1}$ back in Equation \ref{eqn:nag_example}. 
@@
         Our contributions are two folds, theoretical and practical. 
-        Our results are based the assumption $F = f + g$ where $g:R^n \rightarrow \overline\RR$ is convex, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
+        The results are based the assumption $F = f + g$ where $g:R^n \rightarrow \overline\RR$ is convex, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
         We relax the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:nag_example} and showed an upper bound of the optimal gap. 
@@
         When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
-        In Theorem \ref{thm:fixed-momentum-fista}, it demonsrate that R-WAPG frameworks gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex.
+        In Theorem \ref{thm:fixed-momentum-fista}, it demonstrates that R-WAPG frameworks gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex.
         \par
@@
             \item Accelerated Proximal Bregman Method. 
+            \item Removing smoothness assumption in Catalyst acceleration framework. 
         \end{enumerate}  

### 2024-12-28 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
         Our contributions are two folds, theoretical and practical. 
-        Our results are based the assumption $F = f + g$ where $g:\RR^n \rightarrow \overline\RR$ is convex, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
+        Our results are based the assumption $F = f + g$ where $g:\RR^n \rightarrow \overline\RR$ is convex proper and closed, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function.
         \par
@@
 \section{Preliminaries}
-    Throughout, we define $F := f + g$ where $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: \RR^n \rightarrow \overline \RR$ is convex. 
-    We consider optimization problem: $\min_x \left\lbrace f(x) + g(x)\right\rbrace$.
+    Throughout, we define $F := f + g$ where $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: \RR^n \rightarrow \overline \RR$ is proper, closed and convex. 
+    We consider optimization problem: $\min_x \left\lbrace f(x) + g(x)\right\rbrace$ where the minimizer exists.
     Fix any arbitrary $y \in \RR^n$, define the model functions for all $x \in \dom g$: 
@@
         \\
-        \mathcal M^{L^{-1}}(x; y) &:= F(x) + \frac{L}{2}\Vert x - y\Vert^2, 
+        \mathcal M^{L^{-1}}(x; y) &:= F(x) + \frac{L}{2}\Vert x - y\Vert^2. 
     \end{align*}

### 2024-12-28 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
     \subsection{Theme of the research}
-        This section specify a theme of the research in this proposal. 
+        This section specifies a theme of the research in this proposal. 
         Out first objective is to explore the Goldilocks zones between these topics: theories of variational analysis, design of continuous optimization algorithm and applications in sciences, engineering, and statistics.
-        Our second objective is to identify the ``chemistry" occuring between properties of functions and the designs of continuous optimizations algorithm and how it impacts the convergence and behaviors of the algorithms.
+        Our second objective is to identify the ``chemistry" occurring between properties of functions and the designs of continuous optimizations algorithm and how it impacts the convergence and behaviors of the algorithms.
 
@@
         This section introduces the classics and basics of convex analysis. 
-        Define $F$ to be convex in this section. 
+        Define $F$ to be closed, proper and convex in this section. 
         When $F$ is convex, the limiting subgradient and the regular subgradient reduced to the following definition:
@@
             \partial F(x) := \left\lbrace
-                v \in \RR^n \left|
-                    (\forall y \in \RR^n)\;  F(y) - F(x)  \ge \langle v, y - x\rangle
+                v \in \RR^n \left|\; 
+                    \forall y \in \RR^n\; :  F(y) - F(x)  \ge \langle v, y - x\rangle
                 \right.
@@
             \begin{remark}
-                This lemma still holds for non-convex $f$. 
+                This lemma still holds for non-convex $f$ under prox-boundness and weak convexity and differentiability of $f$. 
             \end{remark}
@@
 \section{Performance estimation problems}\label{sec:pep}
+    \todoinline{\noindent
+        There are several foundational papers relevant.
+
+    }
 

### 2024-12-28 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
 \section{Preliminaries}
-    Throughout, we define $F := f + g$ where $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: \RR^n \rightarrow \overline \RR$ is proper, closed and convex. 
-    We consider optimization problem: $\min_x \left\lbrace f(x) + g(x)\right\rbrace$ where the minimizer exists.
+    Throughout, we make the following assumption unless specified. 
+    \begin{assumption}[Smooth nonsmooth additive]\label{ass:smooth-nsmooth-additive}
+        \;
+        \begin{enumerate}
+            \item Define $F := f + g$. 
+            \item $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex. 
+            \item $g: \RR^n \rightarrow \overline \RR$ is proper, closed and convex. 
+            \item Minimizer exists for the optimization problem: $\min_x \left\lbrace f(x) + g(x)\right\rbrace$. 
+        \end{enumerate}
+    \end{assumption}
     Fix any arbitrary $y \in \RR^n$, define the model functions for all $x \in \dom g$: 
@@
     \begin{theorem}[Proximal inequality]\label{thm:prox-grad-ineq}
+        Let $F$ be given by Assumption \ref{ass:smooth-nsmooth-additive}. 
         Fix any $y\in \RR^n$, we have for all $x \in \RR^n$: 

### 2024-12-29 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
 
-    \subsection{Nesterov's Estimating sequence technique}
+    \subsection{Nesterov's estimating sequence technique}
         \todoinline{\noindent
@@
         }
+        The method of Nesterov's estimating sequence for accelerated gradient method, and their nonsmooth counter parts assumes a convex function $F: \RR^n \rightarrow \overline{\RR}$. 
+        Further discussions would require giving an example of estimating sequence first. 
+        The definition follows gives an example of an estimating sequence. 
+        \begin{definition}[Nesterov's estimating sequence]
+
+        \end{definition}
 

### 2024-12-29 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
         }
+        One of the most relevant works is by 
+        \todo{$\square$ Add them \\ $\square$ Cite them.}{\hl{Apidopoulos et al. }}
+        They showed that a relaxed choice of the sequence that doesn't strictly follow the Nesterov's rule still leads to the convergence of the momentum algorithm. 
+        \par 
+        See \todo{$\square$ Add them \\ $\square$ Cite them.
+}{\hl{Attouch H et al.}} for a method inspired by Hessian Damping were used to stabilize the convergence of the Nesterov's momentum without restarting.
 
@@
         The model function $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is a $L$ strongly convex function, so it admites quadratic growth conditions over minimizer $Ty$ and for all $x \in \RR^n$: 
-        {\footnotesize
-        \begin{align*}
+        {\smaller
+        \begin{align*}
+            0 &\le 
             \widetilde{\mathcal M}^{L^{-1}}(x; y) - 
@@
             \frac{L}{2}\Vert x - Ty\Vert^2
-            &\ge 
-            0
-            \\
-            \iff
+            \\
+            &= 
             \left(
@@
             + D_f(Ty; y)
-            &\ge 0
-            \\
-            \iff 
+            \\
+            &=
             \left(
@@
             - \frac{L}{2}\Vert x - Ty\Vert^2
-            &\ge 0
-            \\
-            \iff 
+            \\
+            &=  
             \left(
@@
             - \frac{L}{2}\Vert x - Ty\Vert^2
-            &\ge 0
-            \\
-            \iff 
+            \\
+            &= 
             \left(
@@
             - \frac{L}{2}\Vert x - Ty\Vert^2
-            &\ge 0
-            \\
-            \iff
+            \\
+            & = 
             \left(
@@
             - \frac{L}{2}\Vert x - Ty\Vert^2
-            &\ge 0
-            \\
-            \iff 
+            \\
+            & =
             F(x) - F(Ty)
@@
             - D_f(x, y) 
-            + D_f(Ty, y)
-            &\ge 0. 
+            + D_f(Ty, y). 
         \end{align*}
         }
-        Now, consider the lower bound of $D_f(x, y) \ge \mu/2\Vert x - y\Vert^2$ by strong convexity of $f$ then 
+        Now, consider the lower bound of $D_f(x, y) \ge \mu/2\Vert x - y\Vert^2$ which is true for all $x, y \in \RR^n$ by strong convexity of $f$. 
+        Then it has for all $x \in \RR^n, y \in \RR^n$ that: 
         \begin{align*}
@@
         They are comparable to existing APG algorithms in the literatures. 
+        Specific instances of Accelerated Proximal Gradient algorithm that has the same form as the Definition \ref{def:r-wapg-intermediate}, Definition \ref{def:r-wapg-st-form} and Definition \ref{def:r-wapg-momentum-form} in the literatures are stated in the remarks that follows the definitions.
+
         \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
@@
         \end{definition}
+        \begin{remark}
+            This form of APG is rarely identified in the literatures. 
+            The closest algorithm that fits the form but with $\mu = 0$ is Chapter 12 of 
+            \todo{$\square$ Add them \\ $\square$ Cite them. }{\hl{in Ryu and Tao's Book}}, 
+            right after Theorem 17. 
+            We created this form which makes the math that follows simpler. 
+            The inspiration of using this as an intermediate representation was inspired by solving Exercise 12.1 in the same Ryu and Tao's Book. 
+        \end{remark}
         \begin{definition}[R-WAPG similar triangle form]\label{def:r-wapg-st-form} \; \\
@@
         \end{definition}
+        \begin{remark}
+            The word similar triangle form can be traced back to several literatures. 
+            The term ``Method of Similar Triangle" was used for Algorithm (6.1.19) in Nesterov's book \cite{nesterov_lectures_2018}, but without the necessary graphical illustrations to clarify it. 
+            Finally, a similar triangle for formulation of FISTA can be found in Equation (2), (3), (4) in \cite{chambolle_convergence_2015}. 
+            To see a graphical explanations on why such term is used to describe the APG algorithm in the literatures, see 
+            \todo{
+                $\square$ Add these. $\square$ Cite these. 
+            }{\hl{(3.1, 4.1) in Lee et al. and Ahn and Sra}}
+            \todoinline{\noindent
+                The term ``Method of Similar Triangle'' specific to this particular representation of AGM. 
+                For more information, see:  
+                \begin{enumerate}
+                    \item 3.1, 4.1 in Jongmin Lee et.al's paper ``A geometric structor of Acceleration and its role in mtakng gradients small''
+                    \item The entirety of Ahn and Sra's paper ``PPM interpretation of Nesterov's accelerated gradient. ''. 
+                \end{enumerate}
+            }
+
+        \end{remark}
         \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
@@
         \begin{remark}
-           \todo[inline]{Consider adding a remark here on how this is similar in format to the Nesterov's accelerated gradient (2.2.19) in his book. }
+            This format fits with (2.2.19) in Nesterov's book \cite{nesterov_lectures_2018}, however, the sequence $(\alpha_k)_{k \ge 0}$ would be given by a different rule. 
+            See Theorem \ref{thm:r-wapg-on-cham-doss} and Lemma \ref{lemma:inverted-fista-seq} to see a specific choice of $(\alpha_k)_{k \ge0}, (\rho_k)_{ k\ge 0}$ such this equivalent form of R-WAPG is in fact two possible variants of the FISTA algorithm.
         \end{remark}
@@
     \par
-    Line 5-8 estimates upper bound for the Lipschitz constant and find $x^+$, the next iterates produced by proximal gradient descent on previous $y_k$.
-    Line 9 updates $x_{k + 1}$ to be $x^+$, a successful iterate identified by the Lipschitz line search routine. 
-    Line 10 updates the R-WAPG sequence $\alpha_k$ for the iterates $y_{k + 1}$. 
+    Line 5-8 estimates upper bound for the Lipschitz constant and find $x^+$, the next iterates produced by proximal gradient descent on previous $y_k$; 
+    Line 9 updates $x_{k + 1}$ to be $x^+$, a successful iterate identified by the Lipschitz line search routine;
+    Line 10 updates the R-WAPG sequence $\alpha_k$ for the iterates $y_{k + 1}$;
     Line 13 updates $\mu$ using the Bregman Divergence of $f$ from iterates $y_{k + 1}, y_k$. 
@@
         \subsubsection{Simple convex quadratic}
+            Consider the minimization problem of $\min_x \{F(x):= f(x) + 0\}$ where the objective function is given by: 
+            \begin{align*}
+                F(x) = \langle x, A x\rangle. 
+            \end{align*}
+            The matrix $A$ is set to be positive definite and diagonal. 
+            Then the optimization problem admits unique minimizer $x^* = \mathbf 0$ and the minimum is zero. 
+            \par
+            We apply Algorithm \ref{alg:free-rwapg}, M-FISTA, and V-FISTA. 
+            The parameters for setting up the problem now follows. 
+            \begin{enumerate}
+                \item 
+            \end{enumerate}
+
         \subsubsection{LASSO}

### 2024-12-29 Notebook LaTEX/Proposal/main.tex
>w<, changes

--- 2024-12-28 Notebook LaTEX/Proposal/main.tex
@@
     Section \ref{sec:catalyst} are results of literatures review in MATH 590. 
-    \todo{Add citations here. }{\hl{It's based on a series of papers}} in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
+    \todo{$\square$ Add Lin's papers and Paquette's papers.  }{\hl{It's based on a series of papers}} in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
     We will point out potential future direction of research of Catalyst acceleration. 
@@
         Out first objective is to explore the Goldilocks zones between these topics: theories of variational analysis, design of continuous optimization algorithm and applications in sciences, engineering, and statistics.
-        Our second objective is to identify the ``chemistry" occurring between properties of functions and the designs of continuous optimizations algorithm and how it impacts the convergence and behaviors of the algorithms.
+        Our second objective is to identify the ``chemistry'' occurring between properties of functions and the designs of continuous optimizations algorithm and how it impacts the convergence and behaviors of the algorithms.
 
@@
     This section contains the basics of contents from convex optimization, and variational analysis. 
+    \par
+    Notations. 
     \begin{enumerate}
@@
                 \left\lbrace
-                    v \in \RR^n \left| 
+                    v \in \RR^n \left| \; 
                         \liminf_{\bar x \neq x\rightarrow \bar x}
@@
                 \left\lbrace
-                    v \in \RR^n \left| 
+                    v \in \RR^n \left| \; 
                         \exists x_k \rightarrow \bar x, v_k \rightarrow v: 
@@
             \begin{remark}
-                This lemma still holds for non-convex $f$ under prox-boundness and weak convexity and differentiability of $f$. 
+                This lemma still holds for non-convex $f$ under prox-boundedness and weak convexity and differentiability of $f$. 
             \end{remark}
@@
         }
+        The method of Nesterov's estimating sequence for accelerated gradient method, and their nonsmooth counterparts assumes a convex function $F: \RR^n \rightarrow \overline{\RR}$. 
+        The estimating sequence is a technique searching for candidate algorithm with extrapolated momentum, and proving their convergence rate if possible. 
+        \par
+        The method is widespread in the literatures, and the ideas behind it are tremendously useful. 
+        \todo{$\square$ Add Guler's 1992 new proximal point paper. \\ $\square$ Cite it. }{\hl{Güler}} 
+        used the method to design an accelerated proximal point method, which inspired and served as the foundation of Catalyst Acceleration for variance reduced method in machine learning. 
+        \todo{$\square$ Add the paper: ``Accelerating the cubic regularization of Newton’s method on convex
+        problems''\\ $\square$ Cite it.}{\hl{Nesterov}}
+        also used the techinique to design an accelerated cubic regularized Newton's method. 
+        In 
+        \todo{$\square$ Cite it. }\hl{Chapter 6 of Nesterov's book}, it's also used to derive a method of accelerated mirror descent. 
+        And finally, 
+        \todo{$\square$ Add paper: ``Accelerated regularized newton methods for
+        minimizing composite convex functions'' \\ $\square$ Cite it. }{\hl{Geovani N. et al}}
+        used the technique to derive a accelerated Newton's method for convex composite objective function. 
+        \par
+        The definition of the estimating sequence that follows is based on our own understanding of the estimating sequence. 
+        \begin{definition}[Nesterov's estimating sequence]\label{def:nes-est-seq}
+            Let $\phi_k : \RR^n \rightarrow\RR$ for all $k \ge 0$ be a sequence of functions. 
+            We call this sequence of function a Nesterov's estimating sequence when it satisfies the conditions: 
+            \begin{enumerate}
+                \item There exists another sequence $(x_k)_{k \ge 0}$ such that for all $k \ge 0$ it has $F(x_k) \le \phi_k^*: =\min_{x}\phi_k(x)$. 
+                \item There exists a sequence of $(\alpha_k)_{k \ge 0}$ where $\alpha_k \in (0, 1)\; \forall k \ge0 $ such that for all $x \in \RR^n$ it has $\phi_{k + 1}(x) - \phi_k(x) \le - \alpha_k(\phi_k(x) - F(x))$.
+            \end{enumerate}
+        \end{definition}
+        \begin{observation}
+            In general, identifying the sequence $(x_k)_{k \ge 0}$ is non-trivial. 
+            But in case it can be found, the method of estimating sequence gives us the convergence rate described by the sequence $(\alpha_k)_{k \ge 0}$, and a candidate algorithm that generates the sequence $(x_k)_{k \ge 0}$.
+            It's two birds with one stone. 
+            \par 
+            If we define $\phi_k$, $\Delta_k(x) := \phi_k (x) - F(x)$ for all $x \in \RR^n$ and assume that $F$ has minimizer $x^*$. 
+            Then observe that $\forall k \ge 0$:  
+            \begin{align*}
+                \Delta_k(x) 
+                &= \phi_k(x) - F(x) \ge \phi_k^* - F(x)
+                \\
+                x = x_k\implies 
+                \Delta_k(x_k) 
+                &\ge 
+                \phi_k^* - F(x_k) \ge 0;
+                \\
+                x = x_* \implies 
+                \Delta_k(x_*)
+                &\ge \phi_k^* - F_* \ge F(x_k) - F_* \ge 0. 
+            \end{align*}
+            The function $\Delta_k(x)$ is non-negative at points: $x_*, x_k$.
+            We can derive the convergence rate of $\Delta_k(x^*)$ because $\forall x \in \RR^n$: 
+            \begin{align*}
+                \phi_{k + 1}(x) - \phi_k(x) 
+                &\le - \alpha_k (\phi_k(x) - F(x))
+                \\
+                \iff 
+                \phi_{k + 1}(x) - F(x) - (\phi_k(x) - F(x))
+                &\le 
+                -\alpha_k(\phi_k(x) - F(x))
+                \\
+                \iff
+                \Delta_{k + 1}(x) - \Delta_k(x) &\le
+                - \alpha_k\Delta_k(x)
+                \\
+                \iff 
+                \Delta_{k + 1}(x) 
+                &\le 
+                (1 - \alpha_k)\Delta_k(x). 
+            \end{align*}
+            Unrolling the above recursion it yields: 
+            \begin{align*}
+                \Delta_{k + 1}(x) &\le 
+                (1 - \alpha_k)\Delta_k(x) \le \cdots \le 
+                \left(
+                    \prod_{i = 0}^k(1 - \alpha_i)
+                \right)\Delta_0(x). 
+            \end{align*}
+            Finally, by setting $x = x^*$, $\Delta_k(x^*)$ is non-negative and using the property of Nesterov's estimating sequence it gives: 
+            \begin{align*}
+                F(x_k) - F(x^*) \le \phi_k^* - F(x^*) \le \Delta_k(x^*) = \phi_k(x^*) - F(x^*) \le \left(\prod_{i = 0}^k(1 - \alpha_i)\right)\Delta_0(x^*).
+            \end{align*}
+
+        \end{observation}
 
@@
     All theorems and claims stated in this section have proofs in the draft paper. 
-    The proofs haven't been carefully verified by people other than the author yet. 
+    The proofs haven't been carefully verified by authoratative people other than the author yet. 
     We will start introducing the context and ideas for our research next. 
@@
     One of the prime candidate for solving the optimization problem is the Nesterov's Accelerated Gradient methods (NAG) finds extensions for nonsmooth function through the proximal gradient operator.
-    \todo{Cite Nesterov's original paper on this.
-}{\hl{Proposed back in 1983 the original Nesterov's acceleration method}} which uses the previous iterates to extrapolate the next iterate to evaluate the gradient.
-    It's well known that, if minimizer $x^*$ exists for $F$, the method achieves a $\mathcal O(1/k^2)$ convergence rate on the objective value $F(x_k)$. 
-    \todo{Cite Chapter 2 of Nesterov's new book. }{\hl{This convergence rate is considered optimal for all class of $L$ Lipschitz smooth convex function}}. 
+    \todo{$\square$ Add Nesterov's original paper. \\ $\square$ Cite it.  }{\hl{Proposed back in 1983 the original Nesterov's acceleration method}} 
+    which uses the previous iterates to extrapolate the next iterate to evaluate the gradient. 
+    It's well known that if minimizer $x^*$ exists for $F$, the method achieves a $\mathcal O(1/k^2)$ convergence rate on the objective value $F(x_k)$. 
+    \todo{$\square$ Add Nesterov's new book. \\ $\square$ Cite it.}{\hl{This convergence rate is considered optimal for all class of $L$ Lipschitz smooth convex function}}. 
     The convergence rate guarantee is faster than $\mathcal O(1/k)$ exhibited by gradient descent. 
@@
     Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
-    \todo{Cite Beck 2009 FISTA. }{\hl{Beck and Toubelle}} mitigate the issue by restarting and showed that it still has a $\mathcal O(1/k^2)$ convergence rate, and it performs better empirically. 
-    \todo{Cite Necoara linear convergence, and Aujol 2024 Parameter free FISTA restart. }{\hl{See}} and references within for recent advancements in restarting accelerated proximal gradient algorithm.
+    \todo{$\square$ Add Beck 2009 FISTA original paper. $\square$ Cite it.}{\hl{Beck and Toubelle}} 
+    mitigated the issue by restarting and showed that it still has a $\mathcal O(1/k^2)$ convergence rate, and it performs better empirically. 
+    \todo{$\square$ Add Necoara linear convergence \\ $\square$ Add Aujol 2024 Parameter free FISTA restart.
+\\ $\square$ Cite Section 5.2.2 for the former, cite the entirety for the later.
+}{\hl{See}}
+    and references within for recent advancements in restarting accelerated proximal gradient algorithm.
     \par
@@
     Let $F:\RR^n \rightarrow \RR$ be a $L$ Lipschitz smooth and $\mu > 0$ function. 
-    As introduced previously, in \todo{Cite Walkington's education stuff here.
-}{\hl{Walkington's writing}}, he showed that there exists a variant of the Nesterov's accelerated gradient method that achieved a linear convergence rate of $\mathcal O((1 - \sqrt{\kappa})^k)$ where $\kappa = \mu/L$.
+    As introduced previously, in 
+    \todo{$\square$ Add Neol J. Walkington's ``Nesterov’s Method for Convex  Optimization''. \\ $\square$ Cite it. }{\hl{Walkington's writing}}, 
+    he showed that there exists a variant of the Nesterov's accelerated gradient method that achieved a linear convergence rate of $\mathcal O((1 - \sqrt{\kappa})^k)$ where $\kappa = \mu/L$. 
     This convergence rate is strictly better than $\mathcal O((1 - \mu/L)^k)$ for the method of gradient descent. 
     However, this variant has a fixed momentum parameter $\theta_{k + 1} = (\sqrt{\kappa} - 1)(\sqrt{\kappa} + 1)^{-1}$ back in Equation \ref{eqn:nag_example}. 
-    \todo{Cite them.}{\hl{The same variant also appears in Beck's book as V-FISTA, and Nesterov's book as (2.2.22).}} 
+    \todo{$\square$ Add Beck's first order textbook\\ $\square$ Cite 10.7.7.
+\\ $\square$ Add Nesterov's textbook.
+\\ $\square$ Cite it.
+}{\hl{The same variant also appears in Beck's book as V-FISTA, and Nesterov's book as (2.2.22).}}
     \par
     One final Mystery of the algorithm is the convergence of the iterates which also has much to do with the momentum sequence $(\theta_k)_{k\ge 0}$ displayed in Equation \ref{eqn:nag_example}. 
-    \todo{Cite them.
-}{\hl{Chambolle, Dossal}} showed that by choosing sequence $(t_k)_{k \ge 1}$ to be $t_k = (n + a - 1)/a$ where $a > 2$ instead would give $(x_k)_{k \ge 0}$ weak convergence in Hilbert space.
+    \todo{$\square$ Add paper: ``On the convergence of the iterates of the...''\\ $\square$ Cite them. }{\hl{Chambolle, Dossal}} 
+    showed that by choosing sequence $(t_k)_{k \ge 1}$ to be $t_k = (n + a - 1)/a$ where $a > 2$ instead would give $(x_k)_{k \ge 0}$ weak convergence in Hilbert space. 
     It's put as an open question on what happens to the iterates when $a = 2$. 
@@
         \end{align*}
-        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in \todo{Fix citation here.}{\hl{Chambolle, Dossal}} \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}.
-        When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
+        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in 
+        \todo{$\square$ Add ``On the convergence of the iterates of...'' \\ $\square$ Cite them. }{\hl{Chambolle, Dossal}}, 
+        and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}. 
+        When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by in 
+        \todo{$\square$ Add beck's original FISTA Paper. \\$\square$ Cite it. }
+        {\hl{Beck}}. 
+        If $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
         In Theorem \ref{thm:fixed-momentum-fista}, it demonstrates that R-WAPG frameworks gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex.
@@
         \par
+        \todoinline{$\blacksquare$ Finish the organizations here after this section is finished. }
+
         Organization now follows. 
-        \todoinline{Finish the organizations here after this section is finished. }
-    \subsection{Building Blocks of R-WAPG}
+        Section \ref{ssec:building-block-rwapg} provides a stepwise description of the R-WAPG iterative algorithm along with an inequality crucial to proving the convergence rate later. 
+        Section \ref{ssec:rwpag-seq-and-alg} introduce the definition of an R-WAPG sequence, which constraints all possible parameters used permitted by the algorithm.
+        The section also states the full R-WAPG algorithm and an upper bound on $F(x_k) - F(x^*)$. 
+        Here, $x_k$ is generated by the R-WAPG algorithm and $x^*$ is the minimizer. 
+        Section \ref{ssec:quiv-repr-rwapg} bring forward three equivalent forms of the R-WAPG algorithm making it more comparable with other Acceerated Proximal Gradient method appeared in the literatures.
+        Section \ref{ssec:describe-variants-with-rwapg} gives characterizations of specific R-WAPG sequence that leads to convergence of the R-WAPG algorithm in terms of the optimality gap. 
+        The section also identifies specific instance of permissible R-WAPG sequences where it fits with the FISTA, V-FISTA, and the algorithm proposed by 
+        \todo{$\square$ Cite the Chambolle, Dossal 2015 paper here again. }{\hl{Chambolle Dossal}}.
+
+    \subsection{Building Blocks of R-WAPG}\label{ssec:building-block-rwapg}
         \todoinline{\noindent
@@
             \end{enumerate}
-            Todo: 
+            To do: 
             \begin{enumerate}
-                \item Explain what is what. 
+                \item[$\blacksquare$] Explain what is what. 
             \end{enumerate}
         }
+        Definition\ref{def:stepwise-wapg} describes the procedures of generating the iterates $(v_{k + 1}, x_{k + 1})$ given any $(v_k, x_k)$ and parameter $\alpha_k \in (0, 1), \gamma_k > 0$. 
+        Proposition \ref{prop:stepwise-lyapunov} gives an inequality instrumental to the convergence rate analysis, with the same assumption as the definition.
+
         \begin{definition}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
@@
 
-    \subsection{R-WAPG Sequence and R-WAPG algorithm}
+    \subsection{R-WAPG Sequence and R-WAPG algorithm}\label{ssec:rwpag-seq-and-alg}
         \todoinline{\noindent
@@
             \begin{enumerate}
-                \item Explain what is what. 
+                \item[$\blacksquare$] Explain what is what. 
             \end{enumerate}
         }
+        The Definition \ref{def:wapg} gives the definition of an iterative algorithm we called: Relaxed Weak Accelerated Proximal Gradient (R-WAPG) algorithm which generates sequence $(x_k, v_k)_{k \ge 1}$ using the R-WAPG sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given in Defintion \ref{def:rwapg-seq}.
+        Proposition \ref{prop:wagp-convergence} shows the upper bound of the optimality gap $F(x_k) - F(x^*)$ with $(x_k)$ generated by the R-WAPG algorithm.
+
         \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}\;\\
@@
 
-    \subsection{Equivalent forms of R-WAPG algorithm}
+    \subsection{Equivalent forms of R-WAPG algorithm}\label{ssec:quiv-repr-rwapg}
         \todoinline{
@@
         }
+        Definitions \ref{def:r-wapg-intermediate}, \ref{def:r-wapg-st-form} and \ref{def:r-wapg-momentum-form} are three equivalent representations of the R-WAPG algorithms. 
+        Propositions \ref{prop:wapg-first-equivalent-repr}, \ref{prop:wagp-st-form} and \ref{prop:r-wapg-momentum-repr} states the equivalences between the forms and the sufficient conditions for initial conditions of $x_1, v_1$ such equivalence holds.
+        \todo{$\square$ Add and explain this part. }{\hl{
+        The remarks of the definitions identifies specific instances in the literatures where the Accelerated Proximal Gradient method were presented under this specific form. 
+        }}
+
         \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
@@
 
-    \subsection{The descriptive power of R-WAPG on existing variants}
+    \subsection{The descriptive power of R-WAPG on existing variants}\label{ssec:describe-variants-with-rwapg}
         \todoinline{\noindent
@@
         }
+        Lemma \ref{lemma:inverted-fista-seq} indentifies a sequence $(\alpha_k)_{k \ge 0}$ such that $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}$ as an specific instance of R-WAPG sequence.
+        The lemma showed that sequence $(\alpha_k^{-1})_{k \ge 0}$ is the FISTA sequence which governs the momentum term and convergence claim in FISTA algorithms and variants alike. 
+        The lemma also provides a simplified convergence claim using the R-WAPG sequence on Proposition \ref{prop:wagp-convergence}. 
+        Theorem \ref{thm:r-wapg-on-cham-doss} stated that the sequences given in  
+        \todo{$\square$ Cite this paper again here. }{\hl{Chambolle, Dossal's}}
+        paper indeed is an instance of R-WAPG sequence, along with that, it indeed attains a convergence rate $\mathcal O(1/k^2)$. 
+        \par
 

### 2024-12-29 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

--- 2024-12-28 Notebook LaTEX/Momentum Accelerations/paper3.tex
@@
     Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
-    Beck and Toubelle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it has a $\mathcal O(1/k^2)$ convergence still, but it performs empirically better. 
+    Beck and Teboulle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it has an $\mathcal O(1/k^2)$ convergence still, but it performs empirically better. 
     See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm. 
@@
         The choices for $\theta_k$ varies for different variants of the accelerated proximal gradient algorithm. 
-        In Chamboolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space. 
+        In Chambolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space. 
         In Chapter 10 of Beck's Book \cite{beck_first-order_2017}, a variant called V-FISTA can achieve the faster linear convergence rate: $\mathcal O((1 - \sqrt{\mu/L})^k)$ on the optimality gap for $\mu > 0$ strongly convex $F$.
@@
     \subsection{Prior works}
-        \todoinline{
+        \todoinline{\noindent
             Here is a list of papers that are relevant to generalizing the convergence claim for APG beyond just the traditional choices for the momentum sequence. 
@@
                 \item Attouch H., Cabot A.: ``Convergence Rates of Inertial Forward-Backward Algorithms'', SIAM. 
-                \item Vassilis A., et al.: ``Convergence rate of inertial Forward-Backward algorithm
-                beyond Nesterov's rule". 
+                \item Vassilis A., et al.: ``Convergence rate of inertial Forward-Backward algorithm beyond Nesterov's rule". 
             \end{enumerate}
@@
             \end{enumerate}
+            \textcolor{red}{The prior works' section is too little, it requires some expansion in the future for sure.} 
         }
+        One of the most relevant works is by 
+        \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them.}{\hl{Apidopoulos et al. }\cite{apidopoulos_convergence_2018}}. 
+        They showed that a relaxed choice of the sequence that doesn't strictly follow the Nesterov's rule still leads to the convergence of the momentum algorithm. 
+        \par 
+        See \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them.
+}{\cite{attouch_first-order_2022}\cite{maulen_speed_2023}} and references within for  the idea of Hessian Damping used to to stabilize the convergence of the Nesterov's momentum without/with restarting.
 
@@
         We can do this because the Lipschitz constant $L$ is fixed throughout the proof hence it can be omitted. 
-        The model function $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is a $L$ strongly convex function, so it admites quadratic growth conditions over minimizer $Ty$ and for all $x \in \RR^n$: 
-        {\footnotesize
-        \begin{align*}
+        The model function $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is an $L$ strongly convex function, so it admits quadratic growth conditions over minimizer $Ty$ and for all $x \in \RR^n$: 
+        {\smaller
+        \begin{align*}
+            0 &\le 
             \widetilde{\mathcal M}^{L^{-1}}(x; y) - 
@@
         $\hat \gamma_2 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$ is true by Observation \ref{obs:r-wapg-observation-1}. 
-        Observe that $R_2$ is defined in the same manner as in Proposition \ref{prop:stepwise-lyapunov} with k = 1 so we can invoke Proposition \ref{prop:stepwise-lyapunov}, and it gives: 
+        Observe that $R_2$ is defined in the same manner as in Proposition \ref{prop:stepwise-lyapunov} with $k = 1$, we can invoke Proposition \ref{prop:stepwise-lyapunov}, and it gives: 
         \begin{align*}
@@
     \begin{remark}        
-        \textcolor{red}
-        {
-            The choice of $\rho_k$ allows for nontraditional choices of step sizes in the literatures. 
-            As we can see from the above convergence claim, there exists choices of $\rho_k\ge 1$ where convergence remains possible. 
-        }
+        The choice of $\rho_k = 0$ reproduces traditional choice of sequences for the APG algorithm. 
+        The above claim showed that there exists $\rho_k > 1$, or $\rho_k < 1$ where convergence of $F(x_k) - F(x^*)$ remains possible. 
     \end{remark}
@@
     \end{align*}
-
     To start, the following proposition on ``abstract similar triangle form'' were made to simplify arguments and notations to make nicer proofs. 
-
+    % SECTION INTRODUCTION ENDS 
     \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
@@
         \end{definition}
+        \begin{remark}
+            This form of APG is rarely identified in the literatures. 
+            The closest algorithm that fits the form but with $\mu = 0$ is Chapter 12 of 
+            \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them. }
+            {\hl{in Ryu and Yin's Book} \cite{ryu_large-scale_2022}}, 
+            right after Theorem 17. 
+            We created this form which makes the math that follows simpler. 
+            The inspiration of using this as an intermediate representation was inspired by solving Exercise 12.1 in the same Ryu and Yin's Book. 
+        \end{remark}
         \begin{definition}[R-WAPG similar triangle form]\label{def:r-wapg-st-form} \; \\
@@
         \end{definition}
+        \begin{remark}
+            The word similar triangle form can be traced back to several literatures. 
+            The term ``Method of Similar Triangle" was used for Algorithm (6.1.19) in Nesterov's book \cite{nesterov_lectures_2018}, but without the necessary graphical illustrations to clarify it. 
+            Finally, a similar triangle for formulation of FISTA can be found in Equation (2), (3), (4) in \cite{chambolle_convergence_2015}. 
+            To see graphical visualization on why such term is used to describe the APG algorithm in the literatures, see 
+            \todo{
+                $\blacksquare$ Add these. $\blacksquare$ Cite these. 
+            }{(3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}}. 
+            \todoinline{\noindent
+                The term ``Method of Similar Triangle'' specific to this particular representation of AGM. 
+                For more information, see:  
+                \begin{enumerate}
+                    \item 3.1, 4.1 in Jongmin Lee et al., ``A geometric structure of Acceleration and its role in making gradients small''
+                    \item The entirety of Ahn and Sra's paper ``PPM interpretation of Nesterov's accelerated gradient. ''. 
+                \end{enumerate}
+            }
+
+        \end{remark}
         \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
@@
             We claim that these parameters satisfy $L\delta_k = 1 + \tau_k + \xi_k$. 
-            To see, we have forall $k\ge 1$: 
+            To see, we have for all $k\ge 1$: 
             \begin{align*}
@@
         \end{align*}
-        Therefore (i) holds. 
+        Therefore, (i) holds. 
         (i) is proved. 
@@
     \begin{remark}
-        The sequence $t_k$ is exactly the same as in Theorem 3.1 of Chmabolle, Dossal \cite{chambolle_convergence_2015}. 
+        The sequence $t_k$ is exactly the same as in Theorem 3.1 of Chambolle, Dossal \cite{chambolle_convergence_2015}. 
     \end{remark}
@@
         Therefore, for all vales of $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$ are completed by cases: (A), (B).
-        The larger of the value among $\{1 - r \sqrt{q}, 1 - r^{-1}\sqrt{q}\}$ is always taken. 
-        Therefore it has: 
+        The largest of the value among $\{1 - r \sqrt{q}, 1 - r^{-1}\sqrt{q}\}$ is always taken. 
+        Therefore, it has: 
         \begin{align*}
@@
             \\
-            & > 1.   & \text{By } a > 2. 
-        \end{align*}
-        Hence (iii) in Lemma \ref{lemma:inverted-fista-seq} applies. 
+            & > 1.   & \text{By } a \ge 2. 
+        \end{align*}
+        Hence, (iii) in Lemma \ref{lemma:inverted-fista-seq} applies. 
         We may use Proposition \ref{prop:wagp-convergence} by the validity of our $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ sequences, we have:
-        \begin{align*}
+        {\small\begin{align*}
             & F(x_{k + 1}) - F(x^*) + \frac{L\alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
@@
             \right). 
-        \end{align*}
+        \end{align*}}
         We can replace $v_1$ to be $x_1$ by Proposition \ref{prop:r-wapg-momentum-repr}. 
@@
         This algorithm described here is exactly the same algorithm being analyzed in the paper by Chambolle, Dossal \cite{chambolle_convergence_2015}. 
-
     \end{remark}
@@
         The algorithm presented here is the same as the R-WAPG momentum form because the term $\theta$ from Lemma \ref{lemma:constant-rwapg-seq} matches up with Definition \ref{def:r-wapg-momentum-form}.
-        Therefore by Proposition \ref{prop:wagp-convergence} we have: 
+        Therefore, by Proposition \ref{prop:wagp-convergence} we have: 
         \begin{align*}
@@
     \subsection{Numerical experiments}
+        This section gives figures and visual for numerical experiments conducted on the R-WAPG algorithm, and other algorithms in the literatures such as the V-FISTA, and M-FISTA algorithm. 
+        We implemented and compare V-FISTA, M-FISTA from Beck, and Algorithm \ref{alg:free-rwapg} given this section. 
+        The results of the experiments are visualized and the setup of the numerical experiments are described  in the sections that follows. 
+        \par
+        The equivalences highlighted in Proposition \ref{prop:r-wapg-momentum-repr} allows us to compare the sequence of iterates $(x_k)_{k \ge 1}, (y_k)_{k \ge0}$ for R-WAPG, VISTA and M-FISTA. 
+        \par
+        Given the same randomized initial condition for all the algorithm, we measure the aggregate statistics of the base two logarithms of the normalized optimality gap (NOG), at each iteration $k$.
+        Given the iterates $x_k$, and the minimum $F^*$, the normalized optimality gap we defined is: 
+        \newcommand{\NOG}{\text{\textbf{NOG}}}
+        \begin{align*}
+            \delta_k := \log_2\left(
+                \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}
+            \right). 
+        \end{align*}
+        Since it's not the case that $F^*$ is always known in prior, we used the minimum of all $F(x_k)$ across all algorithms, all iterations $k$ as the surrogate for $F^*$. 
+        \par 
+        For the termination conditions of the algorithm, we consider the norm of the gradient mapping $\mathcal G_L(y_k) < \epsilon$. 
+        The $L$ can change during each iteration if it's obtained through the specified Lipschitz line search routine.
 
         \subsubsection{Simple convex quadratic}
+            Consider the minimization problem of $\min_x \{F(x):= f(x) + 0\}$ where the objective function is given by: 
+            \begin{align*}
+                F(x) = (1/2)\langle x, A x\rangle. 
+            \end{align*}
+            The matrix $A$ is set to be positive semi-definite and diagonal. 
+            Then the optimization problem admits unique minimizer $x^* = \mathbf 0$ and the minimum is zero. 
+            \par
+            We apply Algorithm \ref{alg:free-rwapg}, M-FISTA, and V-FISTA. 
+            The parameters for setting up the problem now follows. 
+            \begin{enumerate}
+                \item $N$, the dimension of the problem. 
+                \item $0 < \mu < L$, the strong convexity and Lipschitz smoothness constant. 
+                \item $A \in \RR^{N\times N}$, a diagonal matrix given by $N- 1$ linearly spaced with equal increment on the interval $[\mu, L]$, and an extra number $0$, i.e: $A = \text{diag}(0, \mu + (L-\mu)(N - 1)^{-1}, \mu + 2(L-\mu)(N - 1)^{-1}, \cdots, \mu + (N - 2)(L - \mu)^{-1}, L)$.
+                \item In this case $f = F = (1/2)\langle x, A x\rangle$ and $g \equiv 0$. 
+                \item $\epsilon > 0$, the tolerance value for termination criteria. 
+                \item $x_0 \sim \mathcal N(I, \mathbf 0)$ is a vector, and it's the initial condition for all the algorithm.
+In this case the initial guess is fixed for all R-WAPG, M-FISTA and M-FISTA, but it's randomly generated by the zero mean standard normal distribution for each element in the vector.
+            \end{enumerate}
+            The parameter $L=1, \mu=10^{-5}$ are given in prior to produce the diagonal matrix $A$ and we conduct many experiments for $N = 256$ and $N = 1024$. 
+            For all R-WAPG, M-FISTA and V-FISTA, 
+            we use a different initial guess each time, a set of 30 experiments are performed. 
+            The maximum, minimum and median values of $\delta_k$ are measured for all algorithm at each iteration and plotted as a ribbon. 
+            Results are shown in Figure \ref{fig:simple-quadratic-NOG}.
+            The solid line in the ribbon is the median value of $\delta_k$ across all experiment, the ribbon gives the maximum, minimum value of $\delta_k$ for each iteration across all experiments. 
+            R-WAPG initially behaves similar to M-FISTA, but as the iteration goes on, it started to behave like V-FISTA.  
+            \par 
+            The most surprising feature here is the monotone descent, however, it's being numerical verified that the method is not monotone in general, it just looks monotone on the figure. 
+            \begin{figure}[H]
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/simple_regression_batched-256.png}
+                    \caption{$N = 256$, simple convex quadratic.}
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/simple_regression_batched-1024.png}
+                    \caption{$N = 1024$, simple convex quadratic. }
+                \end{subfigure}
+                \caption{Simple convex quadratic experiments results for V-FISTA, M-FISTA, and R-WAPG. }
+                \label{fig:simple-quadratic-NOG}
+            \end{figure}
+            \par
+            Another quantity that maybe interesting other than $\delta_k$ would be the estimated value of $\mu$ during at each iteration $k$. 
+            This $\mu$ parameter should converge to the true value. 
+            One individual experiment is carried out for the R-WAPG algorithm and the value of $\mu$ at each iteration is being recorded as well. 
+            Figure \ref{fig:simple-quadratic-r-wapg-mu-estimates} showcases the results. 
+            The values oscillate and converges to the true $\mu$ value. 
+            Observe that the iteration when the estimates are nearing the true value corresponds to the iteration when the algorithm plateau away from its initial fast descent. 
+            \begin{figure}[H]
+                \centering
+                \includegraphics[width=0.64\textwidth]{assets/simple_regression_loss_sc_estimates_1024.png}
+                \caption{$N = 1024$, the $\mu$ estimates produced by Algorithm \ref{alg:free-rwapg} (R-WAPG) is recorded. }
+                \label{fig:simple-quadratic-r-wapg-mu-estimates}
+            \end{figure}
+
         \subsubsection{LASSO}
+            This section present results of numerical experiment for solving the LASSO problem proposed by 
+            \todo{
+                $\square$ Add reference ``Regression shrinkage and selection via the Lasso''
+                \\ $\square$ Cite it. 
+            }{\hl{Tibshirani}}. 
+            The problem of LASSO has smooth, nonsmooth additive and the problem is given by: 
+            \begin{align*}
+                \min_x
+                \left\lbrace
+                    \frac{1}{2}\Vert Ax - b\Vert^2 + \lambda\Vert x\Vert_1
+                \right\rbrace. 
+            \end{align*}
+            The smooth part is $f =\frac{1}{2}\Vert Ax - b\Vert^2$ and the nonsmooth is $g = \lambda\Vert x\Vert_1$. 
+            The objective function is coersive and the exact minimum, or minimizers are unknown. 
+            We perform numerical experiments using V-FISTA, M-FISTA and R-WAPG on this problem. 
+            The parameters for setting up the problem now follow. 
+            \begin{enumerate}
+                \item 
+            \end{enumerate}
+
         \subsubsection{Logistic regression}
@@
 \bibliographystyle{siam}
-\bibliography{references/Inexact_Momentum.bib}
+\bibliography{references/R-WAPG.bib}
 

### 2024-12-29 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
         \par 
-        See \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them.
-}{\cite{attouch_first-order_2022}\cite{maulen_speed_2023}} and references within for  the idea of Hessian Damping used to to stabilize the convergence of the Nesterov's momentum without/with restarting.
+        \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them. }{See Attouch, et al. \cite{attouch_first-order_2022}, Maulen and Peypouquet \cite{maulen_speed_2023}} 
+        and references within for the idea of Hessian Damping for stabilizing the Nesterov's accelerated gradient without/with restarting.
 
@@
             \end{enumerate}
-            The parameter $L=1, \mu=10^{-5}$ are given in prior to produce the diagonal matrix $A$ and we conduct many experiments for $N = 256$ and $N = 1024$. 
+            The parameter $L=1, \mu=10^{-5}$ are given in prior to produce the diagonal matrix $A$, and we conduct many experiments for $N = 256$ and $N = 1024$. 
             For all R-WAPG, M-FISTA and V-FISTA, 
@@
             \begin{enumerate}
-                \item 
+                \item $M, N$ are constants. 
+                \item $A \in \RR^{M\times N}$ is a matrix of i.i.d random variable, taken from a standard normal distributions. 
+                \item $x^+ = [1\; -1\; 1 \; \cdots ]^T \in \RR^N$, it's a vector with alternating $1, -1$ in it. 
+                \item Given $x^+$, it has $b = Ax^+ \in \RR^M$. 
+                \item Given $A$, estiamtions for $L,\mu$ are given by $L = \Vert A^TA\Vert$, $\mu = \Vert (A^TA)^{-1}\Vert^{-1}$. 
+                \item $x_0\in \RR^N$ is the initial guess. Its elements are random i.i.d variable realized from the standard normal distribution. 
+                \item $\epsilon > 0$ is the tolerance the controls the termination criteria for test algorithms. 
             \end{enumerate}
+            Experiments were conducted using V-FISTA, M-FISTA and R-WAPG with $(M, N) = (64, 256)$ and $(M, N) = (64, 128)$. 
+            Matrix $A$ is fixed and the for all test algorithms and all repetitions. 
+            The same experiment are repeated 30 times, but each time a different fixed randomized initial condition is picked for all test algorithms. 
+            The aggragated statistics of $\delta_k$ are collected for all repetitions, and then grouped by the respective algorithm. 
+            The results are showcased in Figure \ref{fig:batched-lasso}. 
+            \begin{figure}[H]
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/lasso_batched_statistics_64-256.png}
+                    \caption{LASSO experiment with $M = 64, N = 256$. Plots of minimum, maximum, and median $\delta_k$ with estimated $F^*$. }
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/lasso_batched_statistics_64-128.png}
+                    \caption{LASSO experiment with $M = 64, N = 128$. Plots of minimum, maximum, and median $\delta_k$ with estimated $F^*$. }
+                \end{subfigure}
+                \caption{LASSO experiments. }
+                \label{fig:batched-lasso}
+            \end{figure}
 

### 2024-12-30 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

@@
     \subsection{Organizations}
-        \todoinline{This will be written once most of the contents in the paper are settled. }
-
-\section{Preliminaries}
+        \todoinline{This will be written once most of the contents in the paper are settled. 
+        }
+        Section \ref{sec:preliminaries} introduces the proximal gradient inequality which is instrumental to developing the stepwise convergence claim in the next section. 
+        Section \ref{sec:stepwise-stuff} states and prove an inequality based on a generic iterative algorithm for just one iteration. 
+        Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG algorithm and characterize conditions for R-WAPG sequence sufficient to derive the optimality upper bound in Proposition \ref{prop:wagp-convergence}.
+        Section \ref{sec:rwapg-equiv-repr} gives 3 equivalent representations of the R-WAPG algorithms that are comparable to instances of Accelerated Proximal Gradient algorithm found in the literatures.
+        Section \ref{sec:rwapg-literatures} formulates FISTA, and V-FISTA sequences and proves the convergence rate of several variants  FISTA using the R-WAPG algorithm and its convergence rate developed in the previous sections.
+        Finally, in Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcaes the numerical experiments for regression, LASSO, and logistic regression.
+        The numerical experiments exposes very interesting behaviors of the algorithm of our own creativity.
+
+\section{Preliminaries}\label{sec:preliminaries}
     Throughout, we make the following assumption unless specified. 
@@
 
-\section{Stepwise formulation of weak accelerated proximal gradient}
+\section{Stepwise formulation of weak accelerated proximal gradient}\label{sec:stepwise-stuff}
     This entire section is building up the R-WAPG algorithm which is described in the Definition \ref{def:wapg} of the next section. 
@@
 
-\section{Formulation of R-WAPG and its convergence rates}
+\section{Formulation of R-WAPG and its convergence rates}\label{sec:rwapg-formulation-convergence}
     The sole focus of this section is Definition \ref{def:wapg}.
@@
 
-\section{Equivalent representations of R-WAPG}
+\section{Equivalent representations of R-WAPG}\label{sec:rwapg-equiv-repr}
     This section reduces Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 
@@
 
-\section{R-WAPG describes existing accelerations scheme in the literatures}
+\section{R-WAPG describes existing accelerations scheme in the literatures}\label{sec:rwapg-literatures}
     In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are descriptive. 
@@
 
-\subsection{The method of Free R-WAPG}
+\section{The method of Free R-WAPG}\label{sec:free-rwapg}
     This section introduces an algorithm of our creation inspired by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
@@
                 \item $N$, the dimension of the problem. 
-                \item $0 < \mu < L$, the strong convexity and Lipschitz smoothness constant. 
+                \item $0 < \mu < L$, the strong convexity and Lipschitz smoothness constant. They are given in prior to construct the problem. 
                 \item $A \in \RR^{N\times N}$, a diagonal matrix given by $N- 1$ linearly spaced with equal increment on the interval $[\mu, L]$, and an extra number $0$, i.e: $A = \text{diag}(0, \mu + (L-\mu)(N - 1)^{-1}, \mu + 2(L-\mu)(N - 1)^{-1}, \cdots, \mu + (N - 2)(L - \mu)^{-1}, L)$.
@@
                 \item $M, N$ are constants. 
-                \item $A \in \RR^{M\times N}$ is a matrix of i.i.d random variable, taken from a standard normal distributions. 
+                \item $A \in \RR^{M\times N}$ is a matrix of i.i.d random variable, taken from a standard normal distribution. 
+                \item $L, \mu$, the Lipschitz constant and the strong convexity constant for the smooth part of the objective are not known prior, and it's estimated through $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert^2$.
                 \item $x^+ = [1\; -1\; 1 \; \cdots ]^T \in \RR^N$, it's a vector with alternating $1, -1$ in it. 
                 \item Given $x^+$, it has $b = Ax^+ \in \RR^M$. 
-                \item Given $A$, estiamtions for $L,\mu$ are given by $L = \Vert A^TA\Vert$, $\mu = \Vert (A^TA)^{-1}\Vert^{-1}$. 
+                \item Given $A$, estimations for $L,\mu$ are given by $L = \Vert A^TA\Vert$, $\mu = \Vert (A^TA)^{-1}\Vert^{-1}$. 
                 \item $x_0\in \RR^N$ is the initial guess. Its elements are random i.i.d variable realized from the standard normal distribution. 
@@
             Matrix $A$ is fixed and the for all test algorithms and all repetitions. 
-            The same experiment are repeated 30 times, but each time a different fixed randomized initial condition is picked for all test algorithms. 
-            The aggragated statistics of $\delta_k$ are collected for all repetitions, and then grouped by the respective algorithm. 
+            The same experiment are repeated 30 times, but each time, we fix a different random initial condition $x_k$ for all test algorithms. 
+            The aggregate statistics of $\delta_k$ are collected for all repetitions, and then grouped by the respective algorithm. 
             The results are showcased in Figure \ref{fig:batched-lasso}. 
+            The bump on the curve is due to a subset of test instances of the 30 repetition where the algorithms take larger number of iterations to terminate. 
             \begin{figure}[H]
@@
             \end{figure}
+            \par
+            Another quantity of interest is the estimates of $\mu$ on each iteration of the algorithm. 
+            A single experiment were conducted and the estimates and $\delta_k$ are showcased in Figure \ref{fig:single-lass-mu-estimates}
+            \begin{figure}[H]
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \includegraphics[width=\textwidth]{assets/lasso_loss_256.png}
+                    \caption{Single lasso experiment plot of $\delta_k$ with.  }
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \includegraphics[width=\textwidth]{assets/lasso_sc_estimates_256.png}
+                    \caption{The $\mu$ estimated by test algorithms for one LASSO experiment. }
+                \end{subfigure}
+                \caption{A single LASSO experiment results, with $M = 64, 256$. }
+                \label{fig:single-lass-mu-estimates}
+            \end{figure}
+            For this specific experiment showed in the figure, the estimated value of $\mu, L$ which we feed into V-FISTA are $\mu = 7.432363627613958\times 10^{-18}$ and $L = 2321.737206983643$. 
+            One of the most important feature is that the estimate $\mu$ doesn't converge to the true value, but it didn't affect the convergence of $\delta_k$.
 

### 2024-12-30 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
     Section \ref{sec:catalyst} are results of literatures review in MATH 590. 
-    \todo{$\square$ Add Lin's papers and Paquette's papers.  }{\hl{It's based on a series of papers}} in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
+    \todo{$\blacksquare$ Add Lin's papers and Paquette's papers.  }{\hl{It's based on a series of papers}} in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
     We will point out potential future direction of research of Catalyst acceleration. 
@@
         \end{definition}
+        \begin{remark}
+            Definition taken from Definition 4.3.1 from 
+            \todo{$\blacksquare$ Add bib \\ $\square$ Cite. }\hl{Pang, Cui's book}
+        \end{remark}
         \begin{definition}[Limiting subgradient]
@@
         \end{definition}
+        \begin{remark}
+            Definition taken from Definition 4.3.1 from
+            \todo{$\blacksquare$ Add bib \\ $\square$ Cite. }\hl{Pang, Cui's book}
+        \end{remark}
         \begin{definition}[Weakly convex function]
@@
         The method is widespread in the literatures, and the ideas behind it are tremendously useful. 
-        \todo{$\square$ Add Guler's 1992 new proximal point paper. \\ $\square$ Cite it. }{\hl{Güler}} 
+        \todo{$\blacksquare$ Add Guler's 1992 new proximal point paper. \\ $\square$ Cite it. }
+        {\hl{Güler}} 
         used the method to design an accelerated proximal point method, which inspired and served as the foundation of Catalyst Acceleration for variance reduced method in machine learning. 
-        \todo{$\square$ Add the paper: ``Accelerating the cubic regularization of Newton’s method on convex
-        problems''\\ $\square$ Cite it.}{\hl{Nesterov}}
-        also used the techinique to design an accelerated cubic regularized Newton's method. 
+        \todo{$\blacksquare$ Add the paper: ``Accelerating the cubic regularization of Newton’s method on convex
+        problems''\\ $\square$ Cite it.}
+        {\hl{Nesterov}}
+        also used the technique to design an accelerated cubic regularized Newton's method. 
         In 
-        \todo{$\square$ Cite it. }\hl{Chapter 6 of Nesterov's book}, it's also used to derive a method of accelerated mirror descent. 
+        \todo{$\blacksquare$ Cite it. }\hl{(6.1.19) of Nesterov's book }\cite{nesterov_lectures_2018}, it's also used to derive a method of accelerated mirror descent. 
         And finally, 
-        \todo{$\square$ Add paper: ``Accelerated regularized newton methods for
-        minimizing composite convex functions'' \\ $\square$ Cite it. }{\hl{Geovani N. et al}}
+        \todo{$\blacksquare$ Add paper: ``Accelerated regularized newton methods for minimizing composite convex functions'' \\ $\square$ Cite it. }
+        {\hl{Geovani N. et al}}
         used the technique to derive a accelerated Newton's method for convex composite objective function. 
@@
     All theorems and claims stated in this section have proofs in the draft paper. 
-    The proofs haven't been carefully verified by authoratative people other than the author yet. 
+    The proofs haven't been carefully verified by authoritative people other than the author yet. 
     We will start introducing the context and ideas for our research next. 
@@
     One of the prime candidate for solving the optimization problem is the Nesterov's Accelerated Gradient methods (NAG) finds extensions for nonsmooth function through the proximal gradient operator.
-    \todo{$\square$ Add Nesterov's original paper. \\ $\square$ Cite it.  }{\hl{Proposed back in 1983 the original Nesterov's acceleration method}} 
+    \todo{$\blacksquare$ Add Nesterov's original paper. \\ $\square$ Cite it.  }
+    {\hl{Proposed back in 1983 the original Nesterov's acceleration method}} 
     which uses the previous iterates to extrapolate the next iterate to evaluate the gradient. 
     It's well known that if minimizer $x^*$ exists for $F$, the method achieves a $\mathcal O(1/k^2)$ convergence rate on the objective value $F(x_k)$. 
-    \todo{$\square$ Add Nesterov's new book. \\ $\square$ Cite it.}{\hl{This convergence rate is considered optimal for all class of $L$ Lipschitz smooth convex function}}. 
+    \todo{$\blacksquare$ Add Nesterov's new book. \\ $\blacksquare$ Cite it.}
+    {\hl{This convergence rate is considered optimal for all class of $L$ Lipschitz smooth convex function }}\cite{nesterov_lectures_2018}. 
     The convergence rate guarantee is faster than $\mathcal O(1/k)$ exhibited by gradient descent. 
@@
     Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
-    \todo{$\square$ Add Beck 2009 FISTA original paper. $\square$ Cite it.}{\hl{Beck and Toubelle}} 
+    \todo{$\blacksquare$ Add Beck 2009 FISTA original paper. $\square$ Cite it.}
+    {\hl{Beck and Toubelle}} 
     mitigated the issue by restarting and showed that it still has a $\mathcal O(1/k^2)$ convergence rate, and it performs better empirically. 
-    \todo{$\square$ Add Necoara linear convergence \\ $\square$ Add Aujol 2024 Parameter free FISTA restart.
-\\ $\square$ Cite Section 5.2.2 for the former, cite the entirety for the later.
-}{\hl{See}}
+    \todo{
+        $\blacksquare$ Add Necoara linear convergence 
+        \\ 
+        $\blacksquare$ Add Aujol 2024 Parameter free FISTA restart. 
+        \\ 
+        $\square$ Cite Section 5.2.2 for the former, cite the entirety for the later. 
+    }
+    {\hl{See} (5.2.2) Necoara et al. and Aujol et al. } 
     and references within for recent advancements in restarting accelerated proximal gradient algorithm.
@@
     As introduced previously, in 
-    \todo{$\square$ Add Neol J. Walkington's ``Nesterov’s Method for Convex  Optimization''. \\ $\square$ Cite it. }{\hl{Walkington's writing}}, 
+    \todo{
+        $\blacksquare$ Add Neol J. Walkington's ``Nesterov's Method for Convex  Optimization''. \\ $\square$ Cite it. 
+    }
+    {\hl{Walkington's writing}}, 
     he showed that there exists a variant of the Nesterov's accelerated gradient method that achieved a linear convergence rate of $\mathcal O((1 - \sqrt{\kappa})^k)$ where $\kappa = \mu/L$. 
@@
     However, this variant has a fixed momentum parameter $\theta_{k + 1} = (\sqrt{\kappa} - 1)(\sqrt{\kappa} + 1)^{-1}$ back in Equation \ref{eqn:nag_example}. 
-    \todo{$\square$ Add Beck's first order textbook\\ $\square$ Cite 10.7.7.
-\\ $\square$ Add Nesterov's textbook.
-\\ $\square$ Cite it.
-}{\hl{The same variant also appears in Beck's book as V-FISTA, and Nesterov's book as (2.2.22).}}
+    \todo{
+        $\blacksquare$ Add Beck's first order textbook
+        \\ $\square$ Cite 10.7.7. 
+        \\ $\blacksquare$ Add Nesterov's textbook. 
+        \\ $\square$ Cite it. }
+    {\hl{
+        The same variant also appears in Beck's book as V-FISTA, and Nesterov's book as (2.2.22).
+    }} 
     \par
     One final Mystery of the algorithm is the convergence of the iterates which also has much to do with the momentum sequence $(\theta_k)_{k\ge 0}$ displayed in Equation \ref{eqn:nag_example}. 
-    \todo{$\square$ Add paper: ``On the convergence of the iterates of the...''\\ $\square$ Cite them. }{\hl{Chambolle, Dossal}} 
+    \todo{
+        $\blacksquare$ Add paper: ``On the convergence of the iterates of the...''
+        \\ $\square$ Cite them. }
+    {\hl{Chambolle, Dossal}} 
     showed that by choosing sequence $(t_k)_{k \ge 1}$ to be $t_k = (n + a - 1)/a$ where $a > 2$ instead would give $(x_k)_{k \ge 0}$ weak convergence in Hilbert space. 
@@
         Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in 
-        \todo{$\square$ Add ``On the convergence of the iterates of...'' \\ $\square$ Cite them. }{\hl{Chambolle, Dossal}}, 
+        \todo{
+            $\blacksquare$ Add ``On the convergence of the iterates of...'' \\ $\square$ Cite them.}
+        {\hl{Chambolle, Dossal}}, 
         and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}. 
         When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by in 
-        \todo{$\square$ Add beck's original FISTA Paper. \\$\square$ Cite it. }
+        \todo{
+            $\blacksquare$ Add beck's original FISTA Paper. \\$\square$ Cite it.
+        }
         {\hl{Beck}}. 
@@
         Here, $x_k$ is generated by the R-WAPG algorithm and $x^*$ is the minimizer. 
-        Section \ref{ssec:quiv-repr-rwapg} bring forward three equivalent forms of the R-WAPG algorithm making it more comparable with other Acceerated Proximal Gradient method appeared in the literatures.
+        Section \ref{ssec:quiv-repr-rwapg} bring forward three equivalent forms of the R-WAPG algorithm making it more comparable with other Accelerated Proximal Gradient method appeared in the literatures.
         Section \ref{ssec:describe-variants-with-rwapg} gives characterizations of specific R-WAPG sequence that leads to convergence of the R-WAPG algorithm in terms of the optimality gap. 
         The section also identifies specific instance of permissible R-WAPG sequences where it fits with the FISTA, V-FISTA, and the algorithm proposed by 
-        \todo{$\square$ Cite the Chambolle, Dossal 2015 paper here again. }{\hl{Chambolle Dossal}}.
+        \todo{$\square$ Cite the Chambolle, Dossal 2015 paper here again. }
+        {\hl{Chambolle Dossal}}.
 
@@
         }}
-
         \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
@@
         \end{definition}
+        \begin{remark}
+            This form of APG is rarely identified in the literatures. 
+            The closest algorithm that fits the form but with $\mu = 0$ is Chapter 12 of 
+            \todo{$\blacksquare$ Add them \\ $\square$ Cite them. }
+            {\hl{in Ryu and Yin's Book} \cite{ryu_large-scale_2022}}, 
+            right after Theorem 17. 
+            We created this form which makes the math that follows simpler. 
+            The inspiration of using this as an intermediate representation was inspired by solving Exercise 12.1 in the same Ryu and Yin's Book. 
+        \end{remark}
         \begin{definition}[R-WAPG similar triangle form]\label{def:r-wapg-st-form} \; \\
@@
         \end{definition}
+        \begin{remark}
+            The word similar triangle form can be traced back to several literatures. 
+            The term ``Method of Similar Triangle" was used for Algorithm (6.1.19) in Nesterov's book \cite{nesterov_lectures_2018}, but without the necessary graphical illustrations to clarify it. 
+            Finally, a similar triangle for formulation of FISTA can be found in Equation (2), (3), (4) in 
+            \todo{$\square$ Cite Chambolle Dossal 2015 again. }
+            \cite{chambolle_convergence_2015}. 
+            To see graphical visualization on why such term is used to describe the APG algorithm in the literatures, see 
+            \todo{
+                $\blacksquare$ Add these. $\square$ Cite these. 
+            }
+            {(3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}}. 
+            \todoinline{\noindent
+                The term ``Method of Similar Triangle'' specific to this particular representation of AGM. 
+                For more information, see:  
+                \begin{enumerate}
+                    \item 3.1, 4.1 in Jongmin Lee et al., ``A geometric structure of Acceleration and its role in making gradients small''
+                    \item The entirety of Ahn and Sra's paper ``PPM interpretation of Nesterov's accelerated gradient. ''. 
+                \end{enumerate}
+            }
+        \end{remark}
         \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
@@
         \end{definition}
+        \begin{remark}
+            This format fits with (2.2.19) in Nesterov's book \cite{nesterov_lectures_2018}, however, the sequence $(\alpha_k)_{k \ge 0}$ would be given by a different rule. 
+            See Theorem \ref{thm:r-wapg-on-cham-doss} and Lemma \ref{lemma:inverted-fista-seq} to see a specific choice of $(\alpha_k)_{k \ge0}, (\rho_k)_{ k\ge 0}$ such this equivalent form of R-WAPG is in fact two possible variants of the FISTA algorithm.
+        \end{remark}
         \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\

### 2024-12-30 Notebook LaTEX/Proposal/main.tex
>w<, changess

@@
             Definition taken from Definition 4.3.1 from 
-            \todo{$\blacksquare$ Add bib \\ $\square$ Cite. }\hl{Pang, Cui's book}
+            \todo{$\blacksquare$ Add bib \\ $\blacksquare$ Cite. }
+            \hl{Pang, Cui's book} \cite{ying_modern_2021}
         \end{remark}
@@
             Definition taken from Definition 4.3.1 from
-            \todo{$\blacksquare$ Add bib \\ $\square$ Cite. }\hl{Pang, Cui's book}
+            \todo{$\blacksquare$ Add bib \\ $\blacksquare$ Cite. }
+            {\hl{Pang, Cui's book}} \cite{ying_modern_2021}
         \end{remark}
@@
         The method is widespread in the literatures, and the ideas behind it are tremendously useful. 
-        \todo{$\blacksquare$ Add Guler's 1992 new proximal point paper. \\ $\square$ Cite it. }
-        {\hl{Güler}} 
+        \todo{
+            $\blacksquare$ Add Guler's 1992 new proximal point paper. 
+            \\ $\blacksquare$ Cite it.}
+        {\hl{Güler}} \cite{guler_new_1992}
         used the method to design an accelerated proximal point method, which inspired and served as the foundation of Catalyst Acceleration for variance reduced method in machine learning. 
-        \todo{$\blacksquare$ Add the paper: ``Accelerating the cubic regularization of Newton’s method on convex
-        problems''\\ $\square$ Cite it.}
-        {\hl{Nesterov}}
+        \todo{
+            $\blacksquare$ Add the paper: ``Accelerating the cubic regularization of Newton’s method on convex
+            problems''\\ 
+            $\blacksquare$ Cite it.
+        }
+        {\hl{Nesterov}} \cite{nesterov_accelerating_2008}
         also used the technique to design an accelerated cubic regularized Newton's method. 
         In 
-        \todo{$\blacksquare$ Cite it. }\hl{(6.1.19) of Nesterov's book }\cite{nesterov_lectures_2018}, it's also used to derive a method of accelerated mirror descent. 
+        \todo{
+            $\blacksquare$ Cite it. 
+        }
+        \hl{(6.1.19) of Nesterov's book }\cite{nesterov_lectures_2018}, 
+        it's also used to derive a method of accelerated mirror descent. 
         And finally, 
-        \todo{$\blacksquare$ Add paper: ``Accelerated regularized newton methods for minimizing composite convex functions'' \\ $\square$ Cite it. }
-        {\hl{Geovani N. et al}}
-        used the technique to derive a accelerated Newton's method for convex composite objective function. 
+        \todo{
+            $\blacksquare$ Add paper: ``Accelerated regularized newton methods for minimizing composite convex functions'' \\ 
+            $\blacksquare$ Cite it. 
+        }
+        {\hl{Geovani N. et al}} \cite{grapiglia_accelerated_2019}
+        used the technique to derive an accelerated Newton's method for convex composite objective function. 
         \par
@@
     One of the prime candidate for solving the optimization problem is the Nesterov's Accelerated Gradient methods (NAG) finds extensions for nonsmooth function through the proximal gradient operator.
-    \todo{$\blacksquare$ Add Nesterov's original paper. \\ $\square$ Cite it.  }
-    {\hl{Proposed back in 1983 the original Nesterov's acceleration method}} 
+    \todo{
+        $\blacksquare$ Add Nesterov's original paper. \\ 
+        $\blacksquare$ Cite it.  
+    }
+    {\hl{Proposed back in 1983 the original Nesterov's acceleration method}} \cite{nesterov_method_1983}
     which uses the previous iterates to extrapolate the next iterate to evaluate the gradient. 
     It's well known that if minimizer $x^*$ exists for $F$, the method achieves a $\mathcal O(1/k^2)$ convergence rate on the objective value $F(x_k)$. 
-    \todo{$\blacksquare$ Add Nesterov's new book. \\ $\blacksquare$ Cite it.}
+    \todo{
+        $\blacksquare$ Add Nesterov's new book. 
+        \\ $\blacksquare$ Cite it.
+    }
     {\hl{This convergence rate is considered optimal for all class of $L$ Lipschitz smooth convex function }}\cite{nesterov_lectures_2018}. 
@@
     Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
-    \todo{$\blacksquare$ Add Beck 2009 FISTA original paper. $\square$ Cite it.}
-    {\hl{Beck and Toubelle}} 
+    \todo{
+        $\blacksquare$ Add Beck 2009 FISTA original paper. \\
+        $\blacksquare$ Cite it.
+    }
+    {\hl{Beck and Toubelle}} \cite{beck_fast_2009}
     mitigated the issue by restarting and showed that it still has a $\mathcal O(1/k^2)$ convergence rate, and it performs better empirically. 
@@
         \\ 
-        $\square$ Cite Section 5.2.2 for the former, cite the entirety for the later. 
-    }
-    {\hl{See} (5.2.2) Necoara et al. and Aujol et al. } 
+        $\blacksquare$ Cite Section 5.2.2 for the former, cite the entirety for the latter. 
+    }
+    {\hl{See} (5.2.2) Necoara et al. \cite{necoara_linear_2019} and Aujol et al. \cite{aujol_parameter-free_2024}}
     and references within for recent advancements in restarting accelerated proximal gradient algorithm.
@@
     \todo{
-        $\blacksquare$ Add Neol J. Walkington's ``Nesterov's Method for Convex  Optimization''. \\ $\square$ Cite it. 
+        $\blacksquare$ Add Neol J. Walkington's ``Nesterov's Method for Convex  Optimization''. \\ 
+        $\blacksquare$ Cite it. 
     }
@@
         \\ $\blacksquare$ Add Nesterov's textbook. 
-        \\ $\square$ Cite it. }
+        \\ $\blacksquare$ Cite it. }
     {\hl{
-        The same variant also appears in Beck's book as V-FISTA, and Nesterov's book as (2.2.22).
-    }} 
+        The same variant also appears in Beck's book as V-FISTA} \cite{beck_first-order_2017}, and \hl{Nesterov's book as (2.2.22)} \cite{nesterov_lectures_2018}.
+    }
     \par
@@
         $\blacksquare$ Add paper: ``On the convergence of the iterates of the...''
-        \\ $\square$ Cite them. }
-    {\hl{Chambolle, Dossal}} 
+        \\ 
+        $\blacksquare$ Cite them. }
+    {\hl{Chambolle, Dossal}} \cite{chambolle_convergence_2015}
     showed that by choosing sequence $(t_k)_{k \ge 1}$ to be $t_k = (n + a - 1)/a$ where $a > 2$ instead would give $(x_k)_{k \ge 0}$ weak convergence in Hilbert space. 
@@
         \todo{
-            $\blacksquare$ Add ``On the convergence of the iterates of...'' \\ $\square$ Cite them.}
-        {\hl{Chambolle, Dossal}}, 
+            $\blacksquare$ Add ``On the convergence of the iterates of...'' \\ $\blacksquare$ Cite them.}
+        {\hl{Chambolle, Dossal}} \cite{chambolle_convergence_2015},
         and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}. 
@@
         \todo{
-            $\blacksquare$ Add beck's original FISTA Paper. \\$\square$ Cite it.
-        }
-        {\hl{Beck}}. 
+            $\blacksquare$ Add beck's original FISTA Paper. 
+            \\$\blacksquare$ Cite it.
+        }
+        {\hl{Beck}} \cite{beck_fast_2009}.
         If $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
@@
         The section also identifies specific instance of permissible R-WAPG sequences where it fits with the FISTA, V-FISTA, and the algorithm proposed by 
-        \todo{$\square$ Cite the Chambolle, Dossal 2015 paper here again. }
-        {\hl{Chambolle Dossal}}.
+        \todo{
+            $\blacksquare$ Cite the Chambolle, Dossal 2015 paper here again. 
+        }
+        {\hl{Chambolle Dossal}} \cite{chambolle_convergence_2015}.
 
@@
         Propositions \ref{prop:wapg-first-equivalent-repr}, \ref{prop:wagp-st-form} and \ref{prop:r-wapg-momentum-repr} states the equivalences between the forms and the sufficient conditions for initial conditions of $x_1, v_1$ such equivalence holds.
-        \todo{$\square$ Add and explain this part. }{\hl{
+        \todo{$\blacksquare$ Add and explain this part. }{\hl{
         The remarks of the definitions identifies specific instances in the literatures where the Accelerated Proximal Gradient method were presented under this specific form. 
@@
             The closest algorithm that fits the form but with $\mu = 0$ is Chapter 12 of 
-            \todo{$\blacksquare$ Add them \\ $\square$ Cite them. }
+            \todo{
+                $\blacksquare$ Add them \\ 
+                $\blacksquare$ Cite them. 
+            }
             {\hl{in Ryu and Yin's Book} \cite{ryu_large-scale_2022}}, 
@@
             Finally, a similar triangle for formulation of FISTA can be found in Equation (2), (3), (4) in 
-            \todo{$\square$ Cite Chambolle Dossal 2015 again. }
+            \todo{$\blacksquare$ Cite Chambolle Dossal 2015 again. }
             \cite{chambolle_convergence_2015}. 
@@
         }
-        Lemma \ref{lemma:inverted-fista-seq} indentifies a sequence $(\alpha_k)_{k \ge 0}$ such that $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}$ as an specific instance of R-WAPG sequence.
+        Lemma \ref{lemma:inverted-fista-seq} identifies a sequence $(\alpha_k)_{k \ge 0}$ such that $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}$ as a specific instance of R-WAPG sequence.
         The lemma showed that sequence $(\alpha_k^{-1})_{k \ge 0}$ is the FISTA sequence which governs the momentum term and convergence claim in FISTA algorithms and variants alike. 
@@
         Theorem \ref{thm:r-wapg-on-cham-doss} stated that the sequences given in  
-        \todo{$\square$ Cite this paper again here. }{\hl{Chambolle, Dossal's}}
-        paper indeed is an instance of R-WAPG sequence, along with that, it indeed attains a convergence rate $\mathcal O(1/k^2)$. 
+        \todo{$\blacksquare$ Cite this paper again here. }
+        {\hl{Chambolle, Dossal's}}
+        paper \cite{chambolle_convergence_2015} indeed is an instance of R-WAPG sequence, along with that, it indeed attains a convergence rate $\mathcal O(1/k^2)$. 
         \par
@@
             \item Güler's 1992 paper on Accelerated Proximal Point method. 
-            \item Lin's, and Payquette's three triology paper on Catalyst acceleration for convex, non-convex Variance reduced algorithm. 
+            \item Lin's, and Payquette's three trilogy paper on Catalyst acceleration for convex, non-convex Variance reduced algorithm. 
         \end{enumerate}

### 2024-12-30 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
     Section \ref{sec:catalyst} are results of literatures review in MATH 590. 
-    \todo{$\blacksquare$ Add Lin's papers and Paquette's papers.  }{\hl{It's based on a series of papers}} in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
+    \todo{
+        $\blacksquare$ Add Lin's papers and Paquette's papers.
+    }
+    {\hl{It's based on a series of papers}} in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
     We will point out potential future direction of research of Catalyst acceleration. 
     \par
-    Section \ref{sec:pep}, \ref{sec:inexact-prox}, \ref{sec:nes-acc-ncnvx} preview literatures in  nonsmooth optimization frontier research where progress and impacts can be made.  
+    Section \ref{sec:inexact-prox}, \ref{sec:nes-acc-ncnvx} preview literatures in nonsmooth optimization frontier research where progress and impacts can be made.  
     \subsection{Theme of the research}
@@
         \par
-        \todoinline{$\blacksquare$ Finish the organizations here after this section is finished. }
+        \todoinline{
+            $\square$ Finish the organizations here after this section is finished. 
+            Still need to explain the numerical experiments section. 
+        }
 
@@
 
-\section{Method Free R-WAPG}\label{sec:spectral-momentum}
+    \subsection{Method Free R-WAPG}\label{sec:spectral-momentum}
         \todoinline{
@@
         And finally, it evaluates proximal of $g$ at $y_k - L^{-1}\nabla f(y_k)$ once. 
+    \subsection{Free R-WAPG numerical experiments}
+        \subsubsection{Simple regression}
+        \subsubsection{LASSO}
 
@@
 
-\section{Performance estimation problems}\label{sec:pep}
-    \todoinline{\noindent
-        There are several foundational papers relevant.
-
-    }
+% \section{Performance estimation problems}\label{sec:pep}
+%     \todoinline{\noindent
+%         There are several foundational papers relevant.
+
+%     }
 

### 2025-01-01 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
 
-    \subsection{Method Free R-WAPG}\label{sec:spectral-momentum}
-        \todoinline{
-            Algorithm, and results of numerical experiments with their descriptions. 
-        }
+    \subsection{Free R-WAPG}\label{sec:spectral-momentum}
         This section introduces an algorithm of our creation inspired by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
@@
     }
+    In this section, we assume that $F: \RR^n \rightarrow \overline \RR$ is a convex function. 
+    This section reports major results from literatures concerning the mthod of Catalyst Acceleration.
+
+    \subsection{Lin's original Catalyst}
+
+    \subsection{Catalyst Adapted to Non-convexity}
 

### 2025-01-03 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
             Under convexity assumption in this section, both $\widetilde {\mathcal M} (\cdot; y),  {\mathcal M}(\cdot;y )$ is at least $\beta \ge 0$ strongly convex. 
-            \begin{definition}[Proximal gradient operator]
+            \begin{definition}[Proximal gradient operator]\label{def:proximal-gradient-operator}
                 Take $F := f + g$ where $g: \RR^n \rightarrow \overline \RR$ as defined in this section. 
@@
             \end{remark}
-            \begin{definition}[Gradient mapping operator]
+            \begin{definition}[Gradient mapping operator]\label{def:gradient-mapping-operator}
                 Take $F := f + g$ as defined in this section. 
@@
 
-    \subsection{Free R-WAPG}\label{sec:spectral-momentum}
+\section{The method of Free R-WAPG}\label{sec:free-rwapg}
     This section introduces an algorithm of our creation inspired by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
@@
     \par
-        Line 5-8 estimates upper bound for the Lipschitz constant and find $x^+$, the next iterates produced by proximal gradient descent on previous $y_k$.
-        Line 9 updates $x_{k + 1}$ to be $x^+$, a successful iterate identified by the Lipschitz line search routine. 
-        Line 10 updates the R-WAPG sequence $\alpha_k$ for the iterates $y_{k + 1}$. 
+    Line 5-8 estimates upper bound for the Lipschitz constant and find $x^+$, the next iterates produced by proximal gradient descent on previous $y_k$; 
+    Line 9 updates $x_{k + 1}$ to be $x^+$, a successful iterate identified by the Lipschitz line search routine;
+    Line 10 updates the R-WAPG sequence $\alpha_k$ for the iterates $y_{k + 1}$;
     Line 13 updates $\mu$ using the Bregman Divergence of $f$ from iterates $y_{k + 1}, y_k$. 
@@
     And finally, it evaluates proximal of $g$ at $y_k - L^{-1}\nabla f(y_k)$ once.
-    \subsection{Free R-WAPG numerical experiments}
-        \subsubsection{Simple regression}
+
+    \subsection{Numerical experiments}
+        This section gives figures and visual for numerical experiments conducted on the R-WAPG algorithm, and other algorithms in the literatures such as the V-FISTA, and M-FISTA algorithm. 
+        We implemented and compare V-FISTA, M-FISTA from Beck, and Algorithm \ref{alg:free-rwapg} given this section. 
+        The results of the experiments are visualized and the setup of the numerical experiments are described  in the sections that follows. 
+        \par
+        The equivalences highlighted in Proposition \ref{prop:r-wapg-momentum-repr} allows us to compare the sequence of iterates $(x_k)_{k \ge 1}, (y_k)_{k \ge0}$ for R-WAPG, VISTA and M-FISTA. 
+        \par
+        Given the same randomized initial condition for all the algorithm, we measure the aggregate statistics of the base two logarithms of the normalized optimality gap (NOG), at each iteration $k$.
+        Given the iterates $x_k$, and the minimum $F^*$, the normalized optimality gap we defined is: 
+        \newcommand{\NOG}{\text{\textbf{NOG}}}
+        \begin{align*}
+            \delta_k := \log_2\left(
+                \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}
+            \right). 
+        \end{align*}
+        Since it's not the case that $F^*$ is always known in prior, we used the minimum of all $F(x_k)$ across all algorithms, all iterations $k$ as the surrogate for $F^*$. 
+        \par 
+        For the termination conditions of the algorithm, we consider the norm of the gradient mapping $\mathcal G_L(y_k) < \epsilon$. 
+        The $L$ can change during each iteration if it's obtained through the specified Lipschitz line search routine.
+
+    \subsubsection{Simple convex quadratic}
+        Consider the minimization problem of $\min_x \{F(x):= f(x) + 0\}$ where the objective function is given by: 
+        \begin{align*}
+            F(x) = (1/2)\langle x, A x\rangle. 
+        \end{align*}
+        The matrix $A$ is set to be positive semi-definite and diagonal. 
+        Then the optimization problem admits unique minimizer $x^* = \mathbf 0$ and the minimum is zero. 
+        \par
+        We apply Algorithm \ref{alg:free-rwapg}, M-FISTA, and V-FISTA. 
+        The parameters for setting up the problem now follows. 
+        \begin{enumerate}
+            \item $N$, the dimension of the problem. 
+            \item $0 < \mu < L$, the strong convexity and Lipschitz smoothness constant. They are given in prior to construct the problem. 
+            \item $A \in \RR^{N\times N}$, a diagonal matrix given by $N- 1$ linearly spaced with equal increment on the interval $[\mu, L]$, and an extra number $0$, i.e: $A = \text{diag}(0, \mu + (L-\mu)(N - 1)^{-1}, \mu + 2(L-\mu)(N - 1)^{-1}, \cdots, \mu + (N - 2)(L - \mu)^{-1}, L)$.
+            \item In this case $f = F = (1/2)\langle x, A x\rangle$ and $g \equiv 0$. 
+            \item $\epsilon > 0$, the tolerance value for termination criteria. 
+            \item $x_0 \sim \mathcal N(I, \mathbf 0)$ is a vector, and it's the initial condition for all the algorithm.
+In this case the initial guess is fixed for all R-WAPG, M-FISTA and M-FISTA, but it's randomly generated by the zero mean standard normal distribution for each element in the vector.
+        \end{enumerate}
+        The parameter $L=1, \mu=10^{-5}$ are given in prior to produce the diagonal matrix $A$, and we conduct many experiments for $N = 256$ and $N = 1024$. 
+        For all R-WAPG, M-FISTA and V-FISTA, 
+        we use a different initial guess each time, a set of 30 experiments are performed. 
+        The maximum, minimum and median values of $\delta_k$ are measured for all algorithm at each iteration and plotted as a ribbon. 
+        Results are shown in Figure \ref{fig:simple-quadratic-NOG}.
+        The solid line in the ribbon is the median value of $\delta_k$ across all experiment, the ribbon gives the maximum, minimum value of $\delta_k$ for each iteration across all experiments. 
+        R-WAPG initially behaves similar to M-FISTA, but as the iteration goes on, it started to behave like V-FISTA.  
+        \par 
+        The most surprising feature here is the monotone descent, however, it's being numerical verified that the method is not monotone in general, it just looks monotone on the figure. 
+        \begin{figure}[H]
+            \begin{subfigure}[b]{0.47\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{assets/simple_regression_batched-256.png}
+                \caption{$N = 256$, simple convex quadratic.}
+            \end{subfigure}
+            \hfill
+            \begin{subfigure}[b]{0.47\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{assets/simple_regression_batched-1024.png}
+                \caption{$N = 1024$, simple convex quadratic. }
+            \end{subfigure}
+            \caption{Simple convex quadratic experiments results for V-FISTA, M-FISTA, and R-WAPG. }
+            \label{fig:simple-quadratic-NOG}
+        \end{figure}
+        \par
+        Another quantity that maybe interesting other than $\delta_k$ would be the estimated value of $\mu$ during at each iteration $k$. 
+        This $\mu$ parameter should converge to the true value. 
+        One individual experiment is carried out for the R-WAPG algorithm and the value of $\mu$ at each iteration is being recorded as well. 
+        Figure \ref{fig:simple-quadratic-r-wapg-mu-estimates} showcases the results. 
+        The values oscillate and converges to the true $\mu$ value. 
+        Observe that the iteration when the estimates are nearing the true value corresponds to the iteration when the algorithm plateau away from its initial fast descent. 
+        \begin{figure}[H]
+            \centering
+            \includegraphics[width=0.64\textwidth]{assets/simple_regression_loss_sc_estimates_1024.png}
+            \caption{$N = 1024$, the $\mu$ estimates produced by Algorithm \ref{alg:free-rwapg} (R-WAPG) is recorded. }
+            \label{fig:simple-quadratic-r-wapg-mu-estimates}
+        \end{figure}
+
     \subsubsection{LASSO}
+        This section present results of numerical experiment for solving the (least absolute shrinkage and
+        selection operator) LASSO problem proposed by 
+        \todo{
+            $\blacksquare$ Add reference ``Regression shrinkage and selection via the Lasso''
+            \\ $\blacksquare$ Cite it. 
+        }{\hl{Tibshirani}} \cite{tibshirani_regression_1996}. 
+        The problem of LASSO has smooth, nonsmooth additive and the problem is given by: 
+        \begin{align*}
+            \min_x
+            \left\lbrace
+                \frac{1}{2}\Vert Ax - b\Vert^2 + \lambda\Vert x\Vert_1
+            \right\rbrace. 
+        \end{align*}
+        The smooth part is $f =\frac{1}{2}\Vert Ax - b\Vert^2$ and the nonsmooth is $g = \lambda\Vert x\Vert_1$. 
+        The objective function is coersive and the exact minimum, or minimizers are unknown. 
+        We perform numerical experiments using V-FISTA, M-FISTA and R-WAPG on this problem. 
+        The parameters for setting up the problem now follow. 
+        \begin{enumerate}
+            \item $M, N$ are constants. 
+            \item $A \in \RR^{M\times N}$ is a matrix of i.i.d random variable, taken from a standard normal distribution. 
+            \item $L, \mu$, the Lipschitz constant and the strong convexity constant for the smooth part of the objective are not known prior, and it's estimated through $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert^2$.
+            \item $x^+ = [1\; -1\; 1 \; \cdots ]^T \in \RR^N$, it's a vector with alternating $1, -1$ in it. 
+            \item Given $x^+$, it has $b = Ax^+ \in \RR^M$. 
+            \item Given $A$, estimations for $L,\mu$ are given by $L = \Vert A^TA\Vert$, $\mu = \Vert (A^TA)^{-1}\Vert^{-1}$. 
+            \item $x_0\in \RR^N$ is the initial guess. Its elements are random i.i.d variable realized from the standard normal distribution. 
+            \item $\epsilon > 0$ is the tolerance the controls the termination criteria for test algorithms. 
+        \end{enumerate}
+        Experiments were conducted using V-FISTA, M-FISTA and R-WAPG with $(M, N) = (64, 256)$ and $(M, N) = (64, 128)$. 
+        Matrix $A$ is fixed and the for all test algorithms and all repetitions. 
+        The same experiment are repeated 30 times, but each time, we fix a different random initial condition $x_k$ for all test algorithms. 
+        The aggregate statistics of $\delta_k$ are collected for all repetitions, and then grouped by the respective algorithm. 
+        The results are showcased in Figure \ref{fig:batched-lasso}. 
+        The bump on the curve is due to a subset of test instances of the 30 repetition where the algorithms take larger number of iterations to terminate. 
+        \begin{figure}[H]
+            \begin{subfigure}[b]{0.47\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{assets/lasso_batched_statistics_64-256.png}
+                \caption{LASSO experiment with $M = 64, N = 256$. Plots of minimum, maximum, and median $\delta_k$ with estimated $F^*$. }
+            \end{subfigure}
+            \hfill
+            \begin{subfigure}[b]{0.47\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{assets/lasso_batched_statistics_64-128.png}
+                \caption{LASSO experiment with $M = 64, N = 128$. Plots of minimum, maximum, and median $\delta_k$ with estimated $F^*$. }
+            \end{subfigure}
+            \caption{LASSO experiments. }
+            \label{fig:batched-lasso}
+        \end{figure}
+        \par
+        Another quantity of interest is the estimates of $\mu$ on each iteration of the algorithm. 
+        A single experiment were conducted and the estimates and $\delta_k$ are showcased in Figure \ref{fig:single-lass-mu-estimates}
+        \begin{figure}[H]
+            \begin{subfigure}[b]{0.47\textwidth}
+                \includegraphics[width=\textwidth]{assets/lasso_loss_256.png}
+                \caption{Single lasso experiment plot of $\delta_k$ with.  }
+            \end{subfigure}
+            \hfill
+            \begin{subfigure}[b]{0.47\textwidth}
+                \includegraphics[width=\textwidth]{assets/lasso_sc_estimates_256.png}
+                \caption{The $\mu$ estimated by test algorithms for one LASSO experiment. }
+            \end{subfigure}
+            \caption{A single LASSO experiment results, with $M = 64, 256$. }
+            \label{fig:single-lass-mu-estimates}
+        \end{figure}
+        For this specific experiment showed in the figure, the estimated value of $\mu, L$ which we feed into V-FISTA are $\mu = 7.432363627613958\times 10^{-18}$ and $L = 2321.737206983643$. 
+        One of the most important feature is that the estimate $\mu$ doesn't converge to the true value, but it didn't affect the convergence of $\delta_k$.
+
+        \subsubsection{Logistic regression}
 
@@
     This section reports major results from literatures concerning the mthod of Catalyst Acceleration. 
-
-    \subsection{Lin's original Catalyst}
-
-    \subsection{Catalyst Adapted to Non-convexity}
-
-% \section{Performance estimation problems}\label{sec:pep}
-%     \todoinline{\noindent
-%         There are several foundational papers relevant.
-
-%     }
+    \par
+    The notations all sections within this section follow. 
+    \begin{assumption}
+        Given any $\beta > 0$ and $y \in \RR^n$, and we assume that $F: \RR^n\rightarrow \overline \RR$ is a closed convex function. 
+        Define the model function for all $y\in \RR^n$ to be 
+        \begin{align*}
+            \mathcal M^{\beta^{-1}}(\cdot; y) &:= 
+            F(x) + \frac{\beta}{2}\Vert x - y\Vert^2.
+        \end{align*}
+        We define the Moreau Envelope at $y \in \RR^n$ to be $\mathcal M^*_{\beta^{-1}}(y) = \min_{x\in \RR^n} \mathcal M^{\beta^{-1}}(x; y)$. 
+        We denote $\mathcal J_{\beta^{-1}}$ to be the resolvent operator for subgradient of $F$, and $\mathcal J_{\beta^{-1}}^\epsilon$ to be the inexact resolvent operator. 
+        \begin{align*}
+            \mathcal J_{\beta^{-1}} y &= 
+            \left\lbrace
+            \right\rbrace
+        \end{align*}
+    \end{assumption}
+    Inspired by works from Güler \cite{guler_new_1992}, and Rockafellar 1976 \cite{rockafellar_monotone_1976}, Lin \cite{lin_universal_2015} proposed a generic method using the convergence claims of Accelerated proximal point method for first order variance reduced algorithms.
+    \par
+    The parts coming will introduce the algorithms, explain key innovations behind the algorithm, and key variants of the algorithm. 
+    The section at the end will give future works and extensions of the exisiting Catalyst framework.
+
+    \begin{definition}[Lin's Universal Catalyst Acceleration]\label{def:lin-catalyst}\; \\
+        Let the initial estimate be $x_0 \in \RR^n$, fix parameters $\kappa > 0$ and $\alpha_0 \in (0, 1]$. 
+        Let $(\epsilon_k)_{k \ge 0}$ be an error sequence chosen for the evaluation for inexact proximal point method. 
+        Initialize $x_0 = y_0$. Then the algorithm generates $(x_k, y_k)_{k\ge 0}$ for all $k \ge 1$ such that: 
+        \begin{align*}
+            & \text{find } x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1} \text{ such that } \mathcal M^{\kappa^{-1}}(x_k, y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}}y_{k - 1}, y_{k - 1}) \le \epsilon_k,
+            \\
+            & \text{find } \alpha_k \in (0, 1) \text{ such that } \alpha_k^2 = (1 - \alpha_k)\alpha_{k - 1}^2 + (\mu/(\mu + \kappa))\alpha_k,
+            \\
+            & 
+            y_{k} = x_k + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})}{\alpha_{k - 1}^2 + \alpha_k}(x_k - x_{k - 1}). 
+        \end{align*}
+    \end{definition}
+    \begin{remark}
+        \todoinline{\noindent 
+            Cite the original Definition in the paper for this one. 
+            \begin{itemize}
+                \item Give explicit formula for $\alpha_k$
+                \item Discuss the optimal choice of $\kappa$ as stated in the paper. 
+                \item Elucidate how the sub problem can be resolved. 
+            \end{itemize}
+        }
+    \end{remark}
+    Much of the heavy lifting of constructing the algorithms were done through The estimating sequence introduced back in Definition \ref{def:nes-est-seq}.
+
+    \subsection{Potential future research}
 

### 2025-01-03 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
         The definitions that follow narrow things further for future discussions. 
-        \begin{definition}[Strong convexity]
+        \begin{definition}[Strong convexity]\label{def:s-cnvx}
             A function $F:\RR^n \rightarrow \overline \RR$ is $\mu \ge 0$ strongly convex if and only if for any fixed $y \in \dom(\partial F)$, we have for all $x\in \RR^n$: 
@@
         \end{definition}
-        \begin{lemma}[Quadratic growth from strong convexity]
+        \begin{lemma}[Quadratic growth from strong convexity]\label{lemma:q-growth}
             If $F$ is $\mu \ge 0$ strongly convex, $\bar x$ is a minimizer of $F$. 
@@
         The smooth part is $f =\frac{1}{2}\Vert Ax - b\Vert^2$ and the nonsmooth is $g = \lambda\Vert x\Vert_1$. 
-        The objective function is coersive and the exact minimum, or minimizers are unknown. 
+        The objective function is coercive and the exact minimum, or minimizers are unknown. 
         We perform numerical experiments using V-FISTA, M-FISTA and R-WAPG on this problem. 
@@
     In this section, we assume that $F: \RR^n \rightarrow \overline \RR$ is a convex function. 
-    This section reports major results from literatures concerning the mthod of Catalyst Acceleration. 
-    \par
-    The notations all sections within this section follow. 
+    This section reports major results from literatures concerning the method of Catalyst Acceleration. 
     \begin{assumption}
-        Given any $\beta > 0$ and $y \in \RR^n$, and we assume that $F: \RR^n\rightarrow \overline \RR$ is a closed convex function. 
+        Given any $\beta > 0$ and $y \in \RR^n$, and $F: \RR^n\rightarrow \overline \RR$ is $\mu \ge 0$ strongly convex and closed. 
         Define the model function for all $y\in \RR^n$ to be 
@@
         We define the Moreau Envelope at $y \in \RR^n$ to be $\mathcal M^*_{\beta^{-1}}(y) = \min_{x\in \RR^n} \mathcal M^{\beta^{-1}}(x; y)$. 
-        We denote $\mathcal J_{\beta^{-1}}$ to be the resolvent operator for subgradient of $F$, and $\mathcal J_{\beta^{-1}}^\epsilon$ to be the inexact resolvent operator. 
-        \begin{align*}
-            \mathcal J_{\beta^{-1}} y &= 
+        We denote $\mathcal J_{\beta^{-1}}$ to be the resolvent operator for subgradient of $F$, and $\mathcal J_{\beta^{-1}}^\epsilon$ for any $\epsilon \ge 0$ to be the inexact resolvent operator. 
+        \begin{align*}
+            \mathcal J_{\beta^{-1}}^\epsilon y &:= 
             \left\lbrace
-            \right\rbrace
+                x \in \RR \left | 
+                    \mathcal M^{\beta^{-1}}(x; y) - 
+                    \mathcal M_{\beta^{-1}}^*(y) \le \epsilon
+                \right.
+            \right\rbrace. 
+        \end{align*}
+        Setting $\epsilon = 0$, we have the exact definition of the exact resolvent given as $\mathcal J_{\beta^{-1}}y = \mathcal J^0_{\beta}y$. 
+        Finally, suppose that $f: \RR^n \rightarrow \RR$ is a $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function, and $g: \RR^n \rightarrow \overline \RR$ is a closed convex function, we define the linearized model function:
+        \begin{align*}
+            \widetilde{\mathcal M}^{\beta^{-1}}(x; y) := 
+            g(x) + f(y) + \langle \nabla f(y), x - y\rangle + \frac{\beta}{2}\Vert x - y\Vert^2. 
         \end{align*}
     \end{assumption}
-    Inspired by works from Güler \cite{guler_new_1992}, and Rockafellar 1976 \cite{rockafellar_monotone_1976}, Lin \cite{lin_universal_2015} proposed a generic method using the convergence claims of Accelerated proximal point method for first order variance reduced algorithms.
+
+    Inspired by accelerated proximal point method from Güler \cite{guler_new_1992}, and inexact proximal point method of Rockafellar 1976 \cite{rockafellar_monotone_1976}, Lin \cite{lin_universal_2015} proposed a generic method taking inspirations from the convergence claims of Accelerated proximal point method to accelerated the convergence rate of first order variance reduced incremental method.
+    The class of variance reduced method is vast, but to use the most relevant feature of this class of first order method is that they are stochastic method that is not slower than full gradient descent in complexity.
+    \todo{
+        $\blacksquare$ Add the bib for Mark Schmidt introductory paper RV methods.  
+        \\ $\square$ Cite it. 
+    }{\hl{See Gower's guide}} for more information on variance reduced methods in machine learning. 
     \par
     The parts coming will introduce the algorithms, explain key innovations behind the algorithm, and key variants of the algorithm. 
-    The section at the end will give future works and extensions of the exisiting Catalyst framework.
+    The section at the end will give future works and extensions of the Catalyst framework.
 
@@
         \begin{align*}
-            & \text{find } x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1} \text{ such that } \mathcal M^{\kappa^{-1}}(x_k, y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}}y_{k - 1}, y_{k - 1}) \le \epsilon_k,
+            & \text{find } x_k \in \mathcal J_{\kappa^{-1}}^{\epsilon_k} y_{k - 1}, 
             \\
@@
     \begin{remark}
-        \todoinline{\noindent 
-            Cite the original Definition in the paper for this one. 
-            \begin{itemize}
-                \item Give explicit formula for $\alpha_k$
-                \item Discuss the optimal choice of $\kappa$ as stated in the paper. 
-                \item Elucidate how the sub problem can be resolved. 
-            \end{itemize}
-        }
+        The above algorithm is Algorithm 1 from Lin's first paper on Catalyst Acceleration \cite{lin_universal_2015}. 
+        The explicit formula for $\alpha_k$ is the larger root of solving the quadratic equation given by: 
+        \begin{align*}
+            \alpha_k &= 
+            \frac{1}{2}\left(
+                - \alpha_{k - 1}^2 - q + \sqrt{(q + \alpha_{k - 1})^2 + 4 \alpha_{k - 1}}
+            \right), 
+        \end{align*}
+        where $q = \mu/(k + \mu)$. 
+        Lin suggests different choices for the parameter $\kappa > 0$ depending on the algorithm chosen to evaluate the subroutine for $\mathcal J_{\kappa^{-1}}^{\epsilon_k}y_{k - 1}$. 
+        The choice of $\epsilon_k$ depends on the estimated optimality gap $F(x_0) - F^*$ where $F^*$ is the minimum of $F$ and whether $\mu > 0$ or $\mu = 0$. 
     \end{remark}
-    Much of the heavy lifting of constructing the algorithms were done through The estimating sequence introduced back in Definition \ref{def:nes-est-seq}.
+    Much of the heavy lifting of constructing the algorithms were done through the method of estimating sequence introduced back in Definition \ref{def:nes-est-seq}. 
+    The convergence of the algorithm made use of an inexact version of the proximal gradient inequality (similar to Theorem \ref{thm:prox-grad-ineq}) stated as Lemma A.7 in \cite{lin_universal_2015}. 
+    This lemma is instrumental for deriving an inexact variant of the estimating sequence $\phi_k^* \ge F(x_k) + \xi_k$. 
+    The sequence $\epsilon_k$ is compacted and bounded under an upper bound parameterized via the sequence $(\epsilon_k)_{k \ge 0}$. 
+    The convergence proof from Lin was inspired by 
+    \todo{\noindent
+        $\blacksquare$ Add bib, the paper is 
+        \\
+        $\square$ Cite. 
+    }{\hl{Schmidt's Inexact Proximal Gradient method. }} 
+    \par
+    The technique of Estimating sequence results in depressingly long proof making it unsuitable for exposition here, however every significant piece of innovation is covered in details in our most recent Fall Winter 2024 MATH 590 report.
+    \par 
+    The following parts will complement the report and describe ideas on Lin's idea for choosing,termination criteria of the inner loop to evaluate $\mathcal J_k^{\epsilon_k} y_k$ in his second paper on Catalyst Acceleration \cite{lin_catalyst_2018}.
 

### 2025-01-03 Notebook LaTEX/Proposal/main.tex
A lot of changes

@@
     \subsection{Fundamentals in non-convex analysis}
-        \todoinline{\noindent
-            We are in $\RR^n$, and the weakest assumption we are making for the objective function is Local Lipschitz continuity. 
-            Definitions: 
-            \begin{enumerate}
-                \item[$\blacksquare$] Local Lipschitz continuity. 
-                \item[$\square$]Regular subgradient. Remember to cite. 
-                \item[$\square$] Limiting subgradient. Remember to cite. 
-                \item[$\blacksquare$] Weakly convex function. 
-                \item[$\blacksquare$]The Bregman Divergence of function. 
-            \end{enumerate}
-            Take Limiting, Regular subgradient definitions from Cui, Pong's book, Definition 4.3.1. 
-        }
         Let the ambient space be $\RR^n$ equipped with inner product and 2-norm. 
@@
     \subsection{Fundamentals in convex analysis}
-        \todoinline{
-            Introduce 
-            \begin{enumerate}
-                \item[$\blacksquare$] Convexity, 
-                \item[$\blacksquare$] convex subgradient, 
-                \item[$\blacksquare$] Lipschitz smoothness. 
-            \end{enumerate}
-            Definitions: 
-            \begin{enumerate}
-                \item [$\blacksquare$]Strong convexity of a function. 
-                \item [$\blacksquare$]The proximal gradient operator. 
-                \item [$\blacksquare$]The proximal mapping operator. 
-            \end{enumerate}
-            Lemmas: 
-            \begin{enumerate}
-                \item [$\blacksquare$]Quadratic growth conditions of a strongly convex function. 
-            \end{enumerate}
-        }
         This section introduces the classics and basics of convex analysis. 
@@
         \subsubsection{Smooth, nonsmooth additive composite}\label{sssec:additive-composite}
-            \todoinline{\noindent
-                Introduce notations for the proximal gradient model function. 
-                Lemmas: 
-                \begin{enumerate}
-                    \item[$\blacksquare$] Proximal gradient envelope. 
-                    \item[$\blacksquare$] A property of gradient mapping. 
-                \end{enumerate}
-                Theorems: 
-                \begin{enumerate}
-                    \item[$\blacksquare$] The proximal gradient inequality. 
-                \end{enumerate}
-            }
-
             In this section, we zoom in further. 
@@
         Setting $\epsilon = 0$, we have the exact definition of the exact resolvent given as $\mathcal J_{\beta^{-1}}y = \mathcal J^0_{\beta}y$. 
-        Finally, suppose that $f: \RR^n \rightarrow \RR$ is a $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function, and $g: \RR^n \rightarrow \overline \RR$ is a closed convex function, we define the linearized model function:
-        \begin{align*}
-            \widetilde{\mathcal M}^{\beta^{-1}}(x; y) := 
-            g(x) + f(y) + \langle \nabla f(y), x - y\rangle + \frac{\beta}{2}\Vert x - y\Vert^2. 
-        \end{align*}
     \end{assumption}
@@
     }{\hl{See Gower's guide}} for more information on variance reduced methods in machine learning. 
+    In brief, a variance reduce method (VRM) is a type of stochastic gradient methods that stablizes the current estimate using information of the gradient at previous iterates. 
+    In each iteration, only the gradient of a few samples are accessed but attain overall better complexity because the variance of the estimated gradients are reduced. 
+    \todoinline{
+        We can then list some citations and references to commonly known variance reduced method here. 
+    }
     \par
@@
     \par 
-    The following parts will complement the report and describe ideas on Lin's idea for choosing,termination criteria of the inner loop to evaluate $\mathcal J_k^{\epsilon_k} y_k$ in his second paper on Catalyst Acceleration \cite{lin_catalyst_2018}.
-
+    The following parts will complement the report and describe ideas on Lin's idea for choosing, termination criteria of the inner loop to evaluate $\mathcal J_k^{\epsilon_k} y_k$ in his second paper on Catalyst Acceleration \cite{lin_catalyst_2018}.
+    To elucidate the matters consider the model function $\mathcal M^{\kappa^{-1}}(x; y)$ is $\mu + \kappa$ strongly convex, and therefore it admits the Polyak error bound condition: 
+    \begin{align*}
+        (\forall x\in \RR^n) \quad 
+        \mathcal M^{\kappa^{-1}}(x; y) -
+        \mathcal M_{\kappa^{-1}}^*(y) 
+        &\le (1 + \mu)\dist
+            \left(\mathbf 0, \partial \mathcal M^{\kappa^{-1}}(x; y)
+            \right). 
+    \end{align*}
+    By choosing $x$ such that $\dist(\mathbf 0, \partial \mathcal M^{\kappa^{-1}}(x; y)) \le \epsilon$, it ensures $x \in \mathcal J^\epsilon_{\kappa^{-1}}(y)$. 
+    Unfortunately in practice, this is not used because a full gradient evaluation on the model function $\mathcal M^{\kappa}(\cdot; y)$ is costly (compare to the small amount required for variance reduced incremental method), so Lin suggested alternatives of Inner Loop Termination Criteria to make Catalyst acceleration competitive in practice.
+    \todoinline{
+        Elucidate things by considering: 
+        \begin{enumerate}
+            \item What is the suggested error sequence $\epsilon_k$ for different type of objective function? 
+            \item What are some conditions for achieving inexact evaluation up to the given accuracy $\epsilon_k$? 
+            \item What are the convergence claims for these different types of termination criteria. 
+        \end{enumerate}
+    }
+    \subsection{Error sequence and convergence claims}
+    \subsection{Inner loop termination criteria}    
     \subsection{Potential future research}

### 2025-01-03 Notebook LaTEX/R-WAPG/paper3.tex
A lot of changes

--- 2024-12-30 Notebook LaTEX/Momentum Accelerations/paper3.tex
@@
         \subsubsection{LASSO}
-            This section present results of numerical experiment for solving the LASSO problem proposed by 
+            This section present results of numerical experiment for solving the (least absolute shrinkage and
+            selection operator) LASSO problem proposed by 
             \todo{
-                $\square$ Add reference ``Regression shrinkage and selection via the Lasso''
-                \\ $\square$ Cite it. 
-            }{\hl{Tibshirani}}. 
+                $\blacksquare$ Add reference ``Regression shrinkage and selection via the Lasso''
+                \\ $\blacksquare$ Cite it. 
+            }{\hl{Tibshirani}} \cite{tibshirani_regression_1996}. 
             The problem of LASSO has smooth, nonsmooth additive and the problem is given by: 

### 2025-01-04 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
 \section{Preliminaries}
-    \todoinline{
-        Clarify: Notations,
-        Organizations. 
-    }
     This section contains the basics of contents from convex optimization, and variational analysis. 
@@
     \begin{enumerate}
-        \item $\overline \RR := \RR \cup \{\infty, -\infty\}$
+        \item $\overline \RR := \RR \cup \{\infty, -\infty\}$. 
     \end{enumerate}
@@
     \subsection{Nesterov's estimating sequence technique}
-        \todoinline{\noindent
-            Do the following: 
-            \begin{enumerate}
-                \item What is Nesterov's estimating sequence. 
-                \item How is it used to derive the algorithm and convergence rate of algorithm. 
-                \item Where is it used and why is it important here. 
-            \end{enumerate}
-        }
-        \todoinline{
-            Examples
-            \begin{enumerate}
-                \item Example estimating sequence. 
-            \end{enumerate}
-        }
         The method of Nesterov's estimating sequence for accelerated gradient method, and their nonsmooth counterparts assumes a convex function $F: \RR^n \rightarrow \overline{\RR}$. 
@@
     }
-    {\hl{Walkington's writing}}, 
+    {\hl{Walkington's writing}} \cite{noel_nesterovs_nodate}, 
     he showed that there exists a variant of the Nesterov's accelerated gradient method that achieved a linear convergence rate of $\mathcal O((1 - \sqrt{\kappa})^k)$ where $\kappa = \mu/L$. 
@@
         $\blacksquare$ Add Beck's first order textbook
-        \\ $\square$ Cite 10.7.7. 
+        \\ $\blacksquare$ Cite 10.7.7. 
         \\ $\blacksquare$ Add Nesterov's textbook. 
@@
     {\hl{
-        The same variant also appears in Beck's book as V-FISTA} \cite{beck_first-order_2017}, and \hl{Nesterov's book as (2.2.22)} \cite{nesterov_lectures_2018}.
+        The same variant also appears in Beck's book as V-FISTA} \cite[(10.7.7)]{beck_first-order_2017}, and \hl{Nesterov's book as (2.2.22)} \cite{nesterov_lectures_2018}.
     }
@@
         {\hl{Chambolle Dossal}} \cite{chambolle_convergence_2015}. 
+        Section \ref{sec:free-rwapg} provides Algorithm \ref{alg:free-rwapg} (Free R-WAPG) which is a parameter free alternative to accelerated proximal gradient method formulated using the R-WAPG we proposed.
+        The algorithm dynamically adjusts the R-WAPG sequence $\alpha_k$ using the Bregman Divergence of smooth part of the objective function at successive extrapolated iterate $y_{k + 1}, y_k$ from the momentum method.
+        Numerical experiments are conducted repeatedly and statistics on the results are displayed.
 
     \subsection{Building Blocks of R-WAPG}\label{ssec:building-block-rwapg}
-        \todoinline{\noindent
-            Definitions: 
-            \begin{enumerate}
-                \item[$\blacksquare$] R-WAPG stepwise definition.
-                \item[$\blacksquare$] R-WAPG stepwise convergence claim.
-            \end{enumerate}
-            To do: 
-            \begin{enumerate}
-                \item[$\blacksquare$] Explain what is what. 
-            \end{enumerate}
-        }
         Definition\ref{def:stepwise-wapg} describes the procedures of generating the iterates $(v_{k + 1}, x_{k + 1})$ given any $(v_k, x_k)$ and parameter $\alpha_k \in (0, 1), \gamma_k > 0$. 
@@
     \subsection{R-WAPG Sequence and R-WAPG algorithm}\label{ssec:rwpag-seq-and-alg}
-        \todoinline{\noindent
-            The R-WAPG Algorithm and convergence claim. 
-            Definitions: 
-            \begin{enumerate}
-                \item[$\blacksquare$] R-WAPG Sequence.
-                \item[$\blacksquare$] R-WAPG algorithm
-                \item[$\blacksquare$] Convergence of the R-WAPG algorithm.
-            \end{enumerate}
-            Todo: 
-            \begin{enumerate}
-                \item[$\blacksquare$] Explain what is what. 
-            \end{enumerate}
-        }
-        The Definition \ref{def:wapg} gives the definition of an iterative algorithm we called: Relaxed Weak Accelerated Proximal Gradient (R-WAPG) algorithm which generates sequence $(x_k, v_k)_{k \ge 1}$ using the R-WAPG sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given in Defintion \ref{def:rwapg-seq}.
+        The Definition \ref{def:wapg} gives the definition of an iterative algorithm we called: Relaxed Weak Accelerated Proximal Gradient (R-WAPG) algorithm which generates sequence $(x_k, v_k)_{k \ge 1}$ using the R-WAPG sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given in Definition \ref{def:rwapg-seq}.
         Proposition \ref{prop:wagp-convergence} shows the upper bound of the optimality gap $F(x_k) - F(x^*)$ with $(x_k)$ generated by the R-WAPG algorithm.
@@
     \subsection{Equivalent forms of R-WAPG algorithm}\label{ssec:quiv-repr-rwapg}
-        \todoinline{
-            Definitions:
-            \begin{enumerate}
-                \item[$\blacksquare$] R-WAPG Intermediate form.
-                \item[$\blacksquare$] R-WAPG Similar triangle form. 
-                \item[$\blacksquare$] R-WAPG Momentum form. 
-            \end{enumerate}
-        }
-        \todoinline{
-            Theorems: 
-            \begin{enumerate}
-                \item[$\blacksquare$] R-WAPG First equivalent form. 
-                \item[$\blacksquare$] R-WAPG Second equivalent form.
-                \item[$\blacksquare$] R-WAPG Third equivalent form.
-            \end{enumerate}
-            Lemmas
-            Todo: 
-            \begin{enumerate}
-                \item Explain what is what. 
-            \end{enumerate}
-        }
         Definitions \ref{def:r-wapg-intermediate}, \ref{def:r-wapg-st-form} and \ref{def:r-wapg-momentum-form} are three equivalent representations of the R-WAPG algorithms. 
@@
             \todo{
-                $\blacksquare$ Add these. $\square$ Cite these. 
+                $\blacksquare$ Add these. $\blacksquare$ Cite these. 
             }
             {(3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}}. 
-            \todoinline{\noindent
-                The term ``Method of Similar Triangle'' specific to this particular representation of AGM. 
-                For more information, see:  
-                \begin{enumerate}
-                    \item 3.1, 4.1 in Jongmin Lee et al., ``A geometric structure of Acceleration and its role in making gradients small''
-                    \item The entirety of Ahn and Sra's paper ``PPM interpretation of Nesterov's accelerated gradient. ''. 
-                \end{enumerate}
-            }
         \end{remark}
@@
     \subsection{The descriptive power of R-WAPG on existing variants}\label{ssec:describe-variants-with-rwapg}
-        \todoinline{\noindent
-            Lemmas: 
-            \begin{enumerate}
-                \item Inverted FISTA sequence is a R-WAPG sequence.
-                \item Constant R-WAPG sequence.
-            \end{enumerate}
-            Theorems: 
-            \begin{enumerate}
-                \item Convergence with constant momentum. 
-                \item Convergence with Chambolle, Dossal Sequences.
-            \end{enumerate}
-            Todo: 
-            \begin{enumerate}
-                \item Explain what is what. 
-            \end{enumerate}
-        }
         Lemma \ref{lemma:inverted-fista-seq} identifies a sequence $(\alpha_k)_{k \ge 0}$ such that $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}$ as a specific instance of R-WAPG sequence.
@@
 
-        \subsubsection{Logistic regression}
+        % \subsubsection{Logistic regression}
 
 \section{Catalyst accelerations and future works}\label{sec:catalyst}
-    \todoinline{\noindent
-        Literatures review of the topics in Catalyst acceleration method. 
-        Here is a list of topics: 
-        \begin{enumerate}
-            \item The original accelerated PPM. 
-            \item The Catalyst with weakly convex objectives. 
-        \end{enumerate}
-        After the literature reviews of the core literatures, move on and state new research directions and open problems. 
-        There are several directions for open problem: 
-        \begin{enumerate}
-            \item APPM method for monotone operators instead of just subgradient, whether the same framework exists in a greater context. 
-            \item Accelerated Proximal Bregman Method. 
-            \item Removing smoothness assumption in Catalyst acceleration framework. 
-        \end{enumerate}  
-    }
-    \todoinline{\noindent
-        A list of relevant literatures: 
-        \begin{enumerate}
-            \item Güler's 1992 paper on Accelerated Proximal Point method. 
-            \item Lin's, and Payquette's three trilogy paper on Catalyst acceleration for convex, non-convex Variance reduced algorithm. 
-        \end{enumerate}
-    }
     In this section, we assume that $F: \RR^n \rightarrow \overline \RR$ is a convex function. 
-    This section reports major results from literatures concerning the method of Catalyst Acceleration. 
-    \begin{assumption}
+    This section introduces the ideas in Catalyst acceleration, elucidate the focuses in the research, and then discuss future research direction at the end. 
+    \begin{assumption}\label{ass:catalyst1}
         Given any $\beta > 0$ and $y \in \RR^n$, and $F: \RR^n\rightarrow \overline \RR$ is $\mu \ge 0$ strongly convex and closed. 
+        Assume that minimizer exists for $F$ and the minimum is $F^*$. 
         Define the model function for all $y\in \RR^n$ to be 
         \begin{align*}
-            \mathcal M^{\beta^{-1}}(\cdot; y) &:= 
+            \mathcal M^{\beta^{-1}}_F(x; y) &:= 
             F(x) + \frac{\beta}{2}\Vert x - y\Vert^2.
         \end{align*}
-        We define the Moreau Envelope at $y \in \RR^n$ to be $\mathcal M^*_{\beta^{-1}}(y) = \min_{x\in \RR^n} \mathcal M^{\beta^{-1}}(x; y)$. 
+        We define the Moreau Envelope at $y \in \RR^n$ to be $\mathcal M^*_{F,\beta^{-1}}(y) = \min_{x\in \RR^n} \mathcal M_F^{\beta^{-1}}(x; y)$. 
         We denote $\mathcal J_{\beta^{-1}}$ to be the resolvent operator for subgradient of $F$, and $\mathcal J_{\beta^{-1}}^\epsilon$ for any $\epsilon \ge 0$ to be the inexact resolvent operator. 
         \begin{align*}
-            \mathcal J_{\beta^{-1}}^\epsilon y &:= 
+            \mathcal J_{\beta^{-1}F}^\epsilon (y) &:= 
             \left\lbrace
-                x \in \RR \left | 
-                    \mathcal M^{\beta^{-1}}(x; y) - 
-                    \mathcal M_{\beta^{-1}}^*(y) \le \epsilon
+                x \in \RR \left | \; 
+                    \mathcal M^{\beta^{-1}}_F(x; y) - 
+                    \mathcal M_{\beta^{-1}, F}^*(y) \le \epsilon
                 \right.
@@
         \end{align*}
-        Setting $\epsilon = 0$, we have the exact definition of the exact resolvent given as $\mathcal J_{\beta^{-1}}y = \mathcal J^0_{\beta}y$. 
+        Setting $\epsilon = 0$, we have the exact definition of the exact resolvent given as $\mathcal J_{\beta^{-1}}y = \mathcal J^0_{\beta^{-1}}y$. 
     \end{assumption}
-
+    \subsection{Introduction to Catalyst}
         Inspired by accelerated proximal point method from Güler \cite{guler_new_1992}, and inexact proximal point method of Rockafellar 1976 \cite{rockafellar_monotone_1976}, Lin \cite{lin_universal_2015} proposed a generic method taking inspirations from the convergence claims of Accelerated proximal point method to accelerated the convergence rate of first order variance reduced incremental method.
@@
         }{\hl{See Gower's guide}} for more information on variance reduced methods in machine learning. 
-    In brief, a variance reduce method (VRM) is a type of stochastic gradient methods that stablizes the current estimate using information of the gradient at previous iterates. 
-    In each iteration, only the gradient of a few samples are accessed but attain overall better complexity because the variance of the estimated gradients are reduced. 
-    \todoinline{
+        \par
+        In brief, a variance reduce method (VRM) is a type of 
+        \todo{
+            $\blacksquare$ Add old Dima's paper on incremental methods here. Paper: ``Incremental gradient, subgradient, and proximal methods for convex optimization: A survey''. 
+            \\
+            $\square$ Cite them. 
+        }
+        {\hl{incremental methods}}
+        for solving a large sum problem: $F(x) = \sum_{i = 1}^{N} f_i(x)$ in machine learning.
+        It can be deterministic, or stochastic. 
+        When it's stochastic, the theories focuses on the expected optimality gap: $\mathbb E[F(x_k) - F^*]$, for the inner and outer loop. 
+        Let's assume for simplicity of discussion that it's deterministic and focus on: $F(x_k) - F^*$. 
+        \par 
+        The idea of VRM is to stabilize the estimate of gradient using information of the gradient (which can be estimated, or exact) from all or a subset at previous iterates. 
+        In each iteration, only the gradient of a few samples are accessed and uses simple calculations from previously stored gradient to attain overall better complexity 
+        It can achieve that because the variance of the estimated gradients are smaller when the iterates are close to the set of true minimizer. 
+        \todoinline{\noindent
             We can then list some citations and references to commonly known variance reduced method here. 
+            Let's list some here then. 
+            \begin{enumerate}
+                \item 
+            \end{enumerate}
         }
@@
         The section at the end will give future works and extensions of the Catalyst framework. 
-
-    \begin{definition}[Lin's Universal Catalyst Acceleration]\label{def:lin-catalyst}\; \\
+        \begin{definition}[Lin's Universal Catalyst Acceleration]\label{def:lin-catalyst-original}\; \\
+            Let $F:\RR \rightarrow \overline \RR$ be $\mu \ge 0$ strongly convex and closed. 
             Let the initial estimate be $x_0 \in \RR^n$, fix parameters $\kappa > 0$ and $\alpha_0 \in (0, 1]$. 
@@
             \begin{align*}
-            & \text{find } x_k \in \mathcal J_{\kappa^{-1}}^{\epsilon_k} y_{k - 1}, 
+                & \text{find } x_k \in \mathcal J_{\kappa^{-1}F}^{\epsilon_k} y_{k - 1}, 
                 \\
@@
         \begin{remark}
-        The above algorithm is Algorithm 1 from Lin's first paper on Catalyst Acceleration \cite{lin_universal_2015}. 
+            The above algorithm is Algorithm 1 from the first paper on Catalyst Acceleration by Lin et al. \cite{lin_universal_2015}. 
             The explicit formula for $\alpha_k$ is the larger root of solving the quadratic equation given by: 
@@
             where $q = \mu/(k + \mu)$. 
-        Lin suggests different choices for the parameter $\kappa > 0$ depending on the algorithm chosen to evaluate the subroutine for $\mathcal J_{\kappa^{-1}}^{\epsilon_k}y_{k - 1}$. 
+            Lin suggests different choices for the parameter $\kappa > 0$ depending on the algorithm chosen to evaluate the subroutine for $\mathcal J_{\kappa^{-1}F}^{\epsilon_k}y_{k - 1}$. 
             The choice of $\epsilon_k$ depends on the estimated optimality gap $F(x_0) - F^*$ where $F^*$ is the minimum of $F$ and whether $\mu > 0$ or $\mu = 0$. 
         \end{remark}
-    Much of the heavy lifting of constructing the algorithms were done through the method of estimating sequence introduced back in Definition \ref{def:nes-est-seq}. 
-    The convergence of the algorithm made use of an inexact version of the proximal gradient inequality (similar to Theorem \ref{thm:prox-grad-ineq}) stated as Lemma A.7 in \cite{lin_universal_2015}. 
+        Typically, an iterative scheme (i.e: VRM) with known complexity is assigned to find inexact proximal iterates $x_k \in {\mathcal J}_{\kappa^{-1}F}^{\epsilon_k} y_{k - 1}$. 
+        This algorithm is often referred to as the inner loop. 
+        The outer loop controls where the proximal point $y_{k}$ is evaluated at and computes Nesterov's momentum extrapolations. 
+        \par
+        The error sequence $(\epsilon_k)_{k \ge 0}$ depends on the properties of the objective function. 
+        For example, when $F$ has $\mu = 0$, 
+        \todo{
+            Lin's paper, Theorem 3.3
+        }
+        {\hl{Lin }}\cite[Theorem 3.3]{lin_universal_2015} suggested $\alpha_0 = (\sqrt{5} - 1)/2$, and 
+        \begin{align}
+            \epsilon_k = \frac{2(F(x_0) - F^*)}{9(k + 2)^{4 + \eta}}, 
+        \end{align}\label{eqn:catalyst-error-seq-cnvx}
+        where $\eta > 0$ is any number, i.e: $\eta = 0.1$. 
+        Then, the convergence of $F(x_k) - F^*$ with $(x_k)_{k \ge 0}$ produced by the outer loop is $\mathcal O(1/k^2)$. 
+        This makes the iteration complexity of just the outer loop optimal. 
+        In addition, to achieve optimal convergence for the outer loop when $\mu > 0$ for $F$, 
+        \todo{
+            Lin's first Catalyst, Theorem 3.1. 
+        }
+        {\hl{Lin }}\cite[Theorem 3.1]{lin_universal_2015}
+        suggested $\alpha_0 = \sqrt{\mu/(\kappa + \mu)}$ and the error sequence: 
+        \begin{align}
+            \epsilon_k = \frac{2}{9}(F(x_0) - F^*)(1 - \rho)^k \quad \text{with } \quad 
+            \rho < \sqrt{\frac{\mu}{\mu + \kappa}}. 
+        \end{align}\label{eqn:catalyst-error-seq-s-cnvx}
+        Take note that, the error sequence has $F^*$ the optimal value in both cases. 
+        It's not an issue in theoretical discussion for the convergence analysis and complexity analysis because it's assumed to exist. 
+        Unfortunately it's of upmost practical concern because the value $F^*$ is not accessible in practice and depends on the specific context of mathematical model of a practical problem. 
+        In the work by Lin et al., the example algorithm given is 
+        \todo{Cite this algorithm}
+        {\hl{MISO Prox}} which automatically builds a lower bound estimates on $F^*$ in the outer loop. 
+        In practice, achieving higher accuracies in $\epsilon_k$ in inner loop would validate the over all convergence claim, but results in slower algorithm. 
+        Therefore, we want to know how to achieve $\epsilon_k$ without over compensating. 
+        \par
+        The convergence of the outer loop made use of an inexact version of the proximal gradient inequality (similar to Theorem \ref{thm:prox-grad-ineq}) stated as Lemma A.7 in \cite{lin_universal_2015}.
         This lemma is instrumental for deriving an inexact variant of the estimating sequence $\phi_k^* \ge F(x_k) + \xi_k$. 
-    The sequence $\epsilon_k$ is compacted and bounded under an upper bound parameterized via the sequence $(\epsilon_k)_{k \ge 0}$. 
-    The convergence proof from Lin was inspired by 
+        The convergence proof (outer and inner loop together) from Lin was inspired by 
         \todo{\noindent
@@
         }{\hl{Schmidt's Inexact Proximal Gradient method. }} 
-    \par
-    The technique of Estimating sequence results in depressingly long proof making it unsuitable for exposition here, however every significant piece of innovation is covered in details in our most recent Fall Winter 2024 MATH 590 report.
-    \par 
-    The following parts will complement the report and describe ideas on Lin's idea for choosing, termination criteria of the inner loop to evaluate $\mathcal J_k^{\epsilon_k} y_k$ in his second paper on Catalyst Acceleration \cite{lin_catalyst_2018}.
-    To elucidate the matters consider the model function $\mathcal M^{\kappa^{-1}}(x; y)$ is $\mu + \kappa$ strongly convex, and therefore it admits the Polyak error bound condition: 
+        The technique of estimating sequence as defined back in Definition \ref{def:nes-est-seq} did the heavy lifting, but it results in depressingly long proof making it unsuitable for exposition here.
+        Significant pieces of theoretical innovations are covered in details in our most recent Fall Winter 2024 MATH 590 report. 
+        \par 
+        The following parts will complement the report and describe ideas on for choosing the termination criteria of the inner loop to evaluate $\mathcal J_{\kappa^{-1}F}^{\epsilon_k} y_k$ which is the focus of his second paper on Catalyst Acceleration \cite{lin_catalyst_2018}.
+        To elucidate the matters consider the model function $\mathcal M_F^{\kappa^{-1}}(x; y)$ is $\mu + \kappa$ strongly convex, and therefore it admits the Polyak error bound condition: 
         \begin{align*}
             (\forall x\in \RR^n) \quad 
-        \mathcal M^{\kappa^{-1}}(x; y) -
-        \mathcal M_{\kappa^{-1}}^*(y) 
-        &\le (1 + \mu)\dist
-            \left(\mathbf 0, \partial \mathcal M^{\kappa^{-1}}(x; y)
+            \mathcal M^{1/\kappa}_F(x; y) -
+            \mathcal M_{F, 1/\kappa}^*(y) 
+            &\le (\kappa + \mu)\dist
+                \left(
+                    \mathbf 0, \partial \mathcal M^{1/\kappa}_F(x; y)
                 \right). 
         \end{align*}
-    By choosing $x$ such that $\dist(\mathbf 0, \partial \mathcal M^{\kappa^{-1}}(x; y)) \le \epsilon$, it ensures $x \in \mathcal J^\epsilon_{\kappa^{-1}}(y)$. 
-    Unfortunately in practice, this is not used because a full gradient evaluation on the model function $\mathcal M^{\kappa}(\cdot; y)$ is costly (compare to the small amount required for variance reduced incremental method), so Lin suggested alternatives of Inner Loop Termination Criteria to make Catalyst acceleration competitive in practice.
-    \todoinline{
-        Elucidate things by considering: 
+        By choosing $x$ such that $\dist(\mathbf 0, \partial \mathcal M_F^{1/\kappa}(x; y)) \le \epsilon$, it ensures $x \in \mathcal J^\epsilon_{\kappa^{-1}F}(y)$. 
+        Unfortunately in practice, this is not used because a full gradient evaluation on the model function $\mathcal M^{1/\kappa}_F(\cdot; y)$ is costly (compare to the small amount required for VRM, which is just the gradient of a few samples.), so Lin suggested alternatives of inner loop termination criteria, and/or upper bounds of inner loop iteration to make Catalyst Acceleration competitive in practice.
+        \todoinline{Add more details about what they actually did in the original paper. }
+        \par
+        He also provided rigorous convergence claim under various scenarios of inner loop termination strategies. 
+        \par 
+        These raised conflicts in the theories and practice of the Catalyst Accelerations framework are the focuses of Lin's second Catalyst paper \cite{lin_catalyst_2018}. 
+        The paper is phenomenal at addressing the following: 
         \begin{enumerate}
-            \item What is the suggested error sequence $\epsilon_k$ for different type of objective function? 
-            \item What are some conditions for achieving inexact evaluation up to the given accuracy $\epsilon_k$? 
-            \item What are the convergence claims for these different types of termination criteria. 
+            \item Getting the error sequence $(\epsilon_k)_{k \ge 0}$ to asserts fast convergence of the outer loop. 
+            \item Two termination criteria for the inner loop given the desired accuracy which expedite the convergence and makes simpler proofs for the convergence of the overall algorithm. 
         \end{enumerate}
-    }
-    \subsection{Error sequence and convergence claims}
+
     \subsection{Inner loop termination criteria}
+        Denote the outer loop iteration algorithm by $\mathbb A$, and inner loop iteration algorithm by $\mathbb M$. 
+        This section discusses major contents in Lin's second Catalyst paper \cite{lin_catalyst_2018}. 
+        To expedite the execution of $\mathbb M$ in general given an error sequence $(\epsilon_k)_{k \ge 0}$ (or equivalently some lower bounds of it), Lin suggested two major strategies that are not necessarily mutually exclusive:
+        \begin{enumerate}
+            \item Use a warm start strategy, i.e: take the most recent iterates produced by $\mathbb A$ as the initial guess for $\mathbb M$. 
+            \item An absolute termination criterion C1 stated in Definition \ref{def:catalyst-termination-c1}, governed by the error sequence $(\epsilon_k)_{k \ge 0}$. 
+            \item A relative termination criterion C2 stated in Definition \ref{def:catalyst-termination-c2}, governed by the error sequence $(\delta_k)_{k \ge 0}$
+        \end{enumerate}
+        \par
+        We now introduce the early termination criteria for $\mathbb M$. 
+        In our notation, we define the absolute termination criterion, which are C1 and C2 directly taken from Lin's second Catalyst paper but in our notations. 
+        \begin{definition}[Absolute termination criterion C1]\label{def:catalyst-termination-c1}
+            Take $F$ as given by Assumption \ref{ass:catalyst1}.
+            Given any $\epsilon > 0, \kappa > 0$ and $x \in \RR^n$, the absolute criterion C1 characterizes the set of inexact proximal iterates as the set: 
+            \begin{align*}
+                \mathcal J_{\kappa^{-1} F}^\epsilon (x) := 
+                \left\lbrace
+                    y \in \RR^n \left | \; 
+                            \mathcal M^{1/\kappa}_F (y; x) - 
+                            \mathcal M^*_{F, 1/\kappa}(x) \le \epsilon
+                    \right.
+                \right\rbrace. 
+            \end{align*}
+        \end{definition}
+
+        \begin{definition}[Relative termination criterion C2]\label{def:catalyst-termination-c2}
+            Take $F$ as given by Assumption \ref{ass:catalyst1}. 
+            Given any $\delta \in (0, 1]$, $\kappa > 0$ and $x \in \RR^n$, the relative criterion C2 is characterized by the set: 
+            \begin{align*}
+                \widetilde{\mathcal J}_{\kappa^{-1}F}^\delta (x)
+                := 
+                \left\lbrace
+                    z \in \RR^n \left| \;
+                        \mathcal M_F^{\kappa^{-1}}(z; x) - 
+                        \mathcal M^*_{F, \kappa^{-1}}(z; x) 
+                        \le \frac{\kappa\delta}{2}\Vert x - z\Vert^2
+                    \right.
+                \right\rbrace. 
+            \end{align*}
+        \end{definition}
+        Stated by Lin, the following lemmas are the sufficient conditions and consequences of termination criteria C1, C2.
+
+        \begin{lemma}[Sufficient condition for C1]\label{lemma:sufficient-c1}
+            Consider smooth plus nonsmooth objective $F := f + g$ with $g:\RR^n \rightarrow \overline \RR, F:\RR^n \rightarrow \RR$ closed and convex, and $F$ is $\mu\ge 0$ strongly convex and $L$-Lipschitz smooth.
+            With arbitrary $x \in \RR^n$ fixed, the model function is additive composite of the form: 
+            \begin{align*}
+                \mathcal M_F^{\kappa^{-1}}(z; x) := 
+                \underbrace{f(z) + \frac{\kappa}{2}\Vert z - x\Vert^2}_{=: f_\kappa (z)}
+                 + g(z). 
+            \end{align*}
+            For any $z$ define proximal gradient point 
+            \begin{align*}
+                \bar z = \hprox_{\eta g}(z - \nabla f_\kappa(z)) 
+                \quad 
+                \text{ with } \quad  \eta = 1/(\kappa + L). 
+            \end{align*}
+            Then it has 
+            \begin{align*}
+                \frac{1}{\eta}\Vert z - \bar z\Vert
+                \le \sqrt{2\kappa \epsilon} \implies 
+                \bar z \in \mathcal 
+                J_{\kappa^{-1}F}^\epsilon (x). 
+            \end{align*}
+        \end{lemma}
+        \begin{remark}
+            This is Lin Lemma 2 \cite{lin_catalyst_2018}. 
+        \end{remark}
+
+    \subsection{Consequences of the inner loop termination criteria}
+        Lemma \ref{lemma:sufficient-c1} describes a sufficient conditions to verify the membership of $\bar z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$ through the proximal gradient operator on $F:= f_\kappa(z) + g(z)$ which of practical importance because it translates criterion C1 into something implementable, i.e: the proximal gradient operator.
+        For theoretical interests, the absolute and relative criteria C1, C2 places bound on the true error of the gradient of Moreau Envelope at the point $x$. 
+        \par 
+        The following are results proved in Lin's second Catalyst paper. 
+        Given any $\epsilon > 0$ if $z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$, define the approximated gradient mapping $\mathcal G_{\kappa^{-1}F}^\epsilon (z) := \kappa(x - z)$.
+        Then
+        \begin{align*}
+            \left\Vert z - \mathcal J_{\kappa^{-1}F} (x)\right\Vert
+            &\le \sqrt{\frac{2\epsilon}{\kappa}} 
+            \iff 
+            \left\Vert
+                \mathcal G_{\kappa^{-1}F}^\epsilon(z) 
+                - \nabla \mathcal M_{F, \kappa^{-1}}^*(x)
+            \right\Vert 
+            \le \sqrt{2\kappa\epsilon}. 
+        \end{align*}
+        Similarly, if $z \in \widetilde{\mathcal J}_{\kappa^{-1}F}^\delta(x)$, define the inexact gradient mapping $\widetilde{\mathcal G}_{\kappa^{-1}F}^\delta(x) = \kappa(x - z)$, we have: 
+        \begin{align*}
+            \Vert z - \mathcal J_{\kappa^{-1}F}(x)\Vert 
+            &\le \sqrt{\delta}\Vert x - z\Vert 
+            \le \sqrt{\delta}(
+                \Vert x - \mathcal J_{\kappa^{-1}F} (x) \Vert 
+                - \Vert z - \mathcal J_{\kappa^{-1}F} (x) \Vert
+            ), 
+            \\
+            \left\Vert 
+                \widetilde{\mathcal G}_{\kappa^{-1}F}^\delta(x) - 
+                \nabla \mathcal M^*_{F, \kappa^{-1}}(x) 
+            \right\Vert
+            &\le 
+            \delta' \Vert \nabla \mathcal M^*_{F, \kappa^{-1}}(x) \Vert \quad 
+            \text{with } \delta' = \sqrt{\delta}/(1 - \sqrt{\delta}). 
+        \end{align*}
+        \par 
+        For a more general development of characterizations of inexact oracles that is more comprehensive and rigorous, see 
+        \todo{
+            $\square$ Add paper: ``First-order methods of smooth convex optimization with inexact oracle'' \\
+            $\square$ Cite them. 
+        }
+        {\hl{Devolder et al.}}
+        \par
+        Finally, besides C1, C2 criteria which, the ``Fixed Budget" termination criterion assesses the optimality of results produced by $\mathbb M$, we can also terminate $\mathbb M$ after a fixed number of iteration.
+        This is the original strategy proposed by Lin et al. in their first Catalyst paper in 2015 \cite{lin_universal_2015}. 
+        It needs a precise bound on the complexity for $\mathbb M$ to achieve C1, or C2 of the strongly convex function $\mathcal M^{\kappa^{-1}}_F(\cdot; y)$. 
+        \par
+        To attain an optimal convergence rate for $\mathbb A$ on criterion C1, the error sequence $(\epsilon_k)_{k \ge 0}$ should be given by Equation \ref{eqn:catalyst-error-seq-cnvx} for convex $F$, and \ref{eqn:catalyst-error-seq-s-cnvx} for strongly convex $F$.
+        Amazingly, termination criterion C2 doesn't require knowledge on $F^*$ to achieve optimal convergence for $\mathbb A$. 
+        The following schedules for $(\delta_k)_{k \ge 0}$ are given in Lin, et al.'s second Catalyst paper, the error sequence $\delta_k$ for criterion C2 is given by: 
+        \begin{align*}\label{eqn:catalyst-rel-error-seq}
+            q &= \mu/(\mu + \kappa), 
+            \\
+            \delta_k 
+            &= \frac{\sqrt{q}}{2 - \sqrt{q}} \text{ if } \mu > 0, 
+            \\
+            \delta_k &= \frac{1}{(k + 1)^2} \text{ if }\mu = 0. 
+        \end{align*}
+        Let's pay particular attention to criterion C2.
+
+    \subsection{Complexity}
+
     \subsection{Potential future research}
@@
 \section{Methods of inexact proximal point}\label{sec:inexact-prox}
-
-\section{Nestrov's acceleration in the non-convex case}\label{sec:nes-acc-ncnvx}
+    Content of this section is primarily based on Khanh et al. \cite{duy_khanh_inexact_2023} on inexact proximal method for weakly convex functions.
+
+\section{Nestrov's acceleration in the nonconvex case}\label{sec:nes-acc-ncnvx}
+    The behavior of Nesterov's acceleration for function that are nonconvex are the holy grail and the absolute frontier. 
+    The approaches are incredibly diverse and therefore, this section will only list relevant references and briefly mention the ideas involved in those literatures. 
+    \todoinline{\noindent
+        Here, is a list of early attempted research of Nesterov's acceleration method in the nonconvex case.
+
+    }
 

### 2025-01-05 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
             \item $A \in \RR^{M\times N}$ is a matrix of i.i.d random variable, taken from a standard normal distribution. 
-            \item $L, \mu$, the Lipschitz constant and the strong convexity constant for the smooth part of the objective are not known prior, and it's estimated through $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert^2$.
+            \item $L, \mu$, the Lipschitz constant and the strong convexity constant for the smooth part of the objective are not known prior, and it's estimated through $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$.
             \item $x^+ = [1\; -1\; 1 \; \cdots ]^T \in \RR^N$, it's a vector with alternating $1, -1$ in it. 
@@
         Unfortunately in practice, this is not used because a full gradient evaluation on the model function $\mathcal M^{1/\kappa}_F(\cdot; y)$ is costly (compare to the small amount required for VRM, which is just the gradient of a few samples.), so Lin suggested alternatives of inner loop termination criteria, and/or upper bounds of inner loop iteration to make Catalyst Acceleration competitive in practice.
-        \todoinline{Add more details about what they actually did in the original paper. }
-        \par
-        He also provided rigorous convergence claim under various scenarios of inner loop termination strategies. 
+        \par
+        \todoinline{\noindent
+            Add more details about what they actually did in the original paper.
+            \begin{enumerate}
+                \item [$\square$] The condition of warm starting in the algorithm and complexity bound of the inner loop. 
+            \end{enumerate}
+        }
         \par 
         These raised conflicts in the theories and practice of the Catalyst Accelerations framework are the focuses of Lin's second Catalyst paper \cite{lin_catalyst_2018}. 
-        The paper is phenomenal at addressing the following: 
+        The paper has the following new ideas: 
         \begin{enumerate}
-            \item Getting the error sequence $(\epsilon_k)_{k \ge 0}$ to asserts fast convergence of the outer loop. 
-            \item Two termination criteria for the inner loop given the desired accuracy which expedite the convergence and makes simpler proofs for the convergence of the overall algorithm. 
+            \item A relative termination criteria that bounds the gradient of the problem in the inner loop, which results in a error sequence without $F^*$, and simplier proof without using the Nesterov's estimating sequence.
+            \item A more comprehensive convergence proof, for 2 different type of error bounds with, including the smooth plus nonsmooth compositie objective. 
         \end{enumerate}
@@
         {\hl{Devolder et al.}}
+        Their works were earlier and a Nesterov accelerated algorithm using estimating sequence and inexact oracles was derived. 
         \par

### 2025-01-06 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
             \left\lbrace
-                x \in \RR \left | \; 
+                x \in \RR^n \left | \; 
                     \mathcal M^{\beta^{-1}}_F(x; y) - 
@@
         \par
-        The parts coming will introduce the algorithms, explain key innovations behind the algorithm, and key variants of the algorithm. 
-        The section at the end will give future works and extensions of the Catalyst framework. 
+        The parts coming will introduce the algorithms, explain its key innovations. 
+        The last section reviews recent literatures on the topics and gives potential future works. 
         \begin{definition}[Lin's Universal Catalyst Acceleration]\label{def:lin-catalyst-original}\; \\
@@
         \end{remark}
+        With a fixed regularization parameter $\kappa > 0$, The outer loop (Definition \ref{def:lin-catalyst-original}) produces $(y_{k}, x_k)_{k \ge k}$ denote it by $\mathbb A$. 
         Typically, an iterative scheme (i.e: VRM) with known complexity is assigned to find inexact proximal iterates $x_k \in {\mathcal J}_{\kappa^{-1}F}^{\epsilon_k} y_{k - 1}$. 
-        This algorithm is often referred to as the inner loop. 
-        The outer loop controls where the proximal point $y_{k}$ is evaluated at and computes Nesterov's momentum extrapolations. 
-        \par
-        The error sequence $(\epsilon_k)_{k \ge 0}$ depends on the properties of the objective function. 
+        We refer this algorithm as the inner loop and denote it by $\mathbb M$. 
+        Without loss of generality assume it generates some convergence sequence $(z_{k, t})_{t \ge 0}$ where $k$ is the corresponding iteration counter of the outer loop. 
+        \par 
+        The choice of error sequence $(\epsilon_k)_{k \ge 0}$ determines iteration $\mathbb A, \mathbb M$. 
+        The total iteration complexity of the algorithm counts the total number of inner loop iteration. 
+        The term ``iteration complexity'' refers to the number of iterations required to achieve a desired accuracy, a concept related to the convergence rate of the algorithm. 
+        The term ``complexity'' refers to the total number of oracle calls, in our context it depends on the specific implementation of $\mathbb M$. 
+        Due to the fact that function $F$ is convex, we focus on the convergence rate of the optimality gap $F(x_k) - F^*\*$ for $\mathbb A$ and convergence of the model function $\mathcal M_F^{\kappa^{-1}}(\cdot, y_{k - 1})$ for $\mathbb M$ given $y_{k - 1}, \epsilon_k$ and initial guess $z_{k, 0}$.
+        \todoinline{\noindent
+            \begin{enumerate}
+                \item State outer loop iteration complexity given error sequence for 
+                \begin{enumerate}
+                    \item Strongly convex objective,
+                    \item Non-strongly but strongly convex objective. 
+                \end{enumerate}
+                \item State the linear convergence rate assumption of the inner function. 
+                \item State the iteration complexity of the inner loop given the specific error sequence.
+
+            \end{enumerate}
+        }
+        \par
+        \subsubsection{Outer loop iteration complexity}
+            The error sequence $(\epsilon_k)_{k \ge 0}$ governs the convergence rate of the outer loop for $F(x_k) - F^*$ to converge. 
+            Depending on either $\mu > 0$, or $\mu = 0$, the choice of $(\epsilon_k)_{k\ge 0}$ differs. 
+            The theorem that follows state the error sequence required for the outer loop to retain optimal convergence rate, they are Theorem 3.3, 3.1 in Lin et al. \cite{lin_universal_2015}. 
+            \begin{theorem}[Outer loop convergence strongly convex]
+
+            \end{theorem}
+            \begin{theorem}[Outer loop convergence convex but not strongly convex]
+
+            \end{theorem}
             For example, when $F$ has $\mu = 0$, 
@@
             }
-        {\hl{Lin }}\cite[Theorem 3.3]{lin_universal_2015} suggested $\alpha_0 = (\sqrt{5} - 1)/2$, and 
+            {\hl{Lin }}\cite[Theorem 3.3]{lin_universal_2015} suggested $\alpha_0 = \left(\sqrt{5} - 1\right)/2$, and 
             \begin{align}
@@
             \end{align}\label{eqn:catalyst-error-seq-cnvx}
+
             where $\eta > 0$ is any number, i.e: $\eta = 0.1$. 
             Then, the convergence of $F(x_k) - F^*$ with $(x_k)_{k \ge 0}$ produced by the outer loop is $\mathcal O(1/k^2)$. 
-        This makes the iteration complexity of just the outer loop optimal. 
-        In addition, to achieve optimal convergence for the outer loop when $\mu > 0$ for $F$, 
+            In this scenario, the iteration complexity of the outer loop optimal. 
+            To achieve optimal convergence for the outer loop when $\mu > 0$ for $F$, 
             \todo{
@@
             \end{align}\label{eqn:catalyst-error-seq-s-cnvx}
-        Take note that, the error sequence has $F^*$ the optimal value in both cases. 
+            Take note that, the error sequence requires knowledge on $F^*$. 
             It's not an issue in theoretical discussion for the convergence analysis and complexity analysis because it's assumed to exist. 
@@
             Significant pieces of theoretical innovations are covered in details in our most recent Fall Winter 2024 MATH 590 report. 
-        \par 
-        The following parts will complement the report and describe ideas on for choosing the termination criteria of the inner loop to evaluate $\mathcal J_{\kappa^{-1}F}^{\epsilon_k} y_k$ which is the focus of his second paper on Catalyst Acceleration \cite{lin_catalyst_2018}.
-        To elucidate the matters consider the model function $\mathcal M_F^{\kappa^{-1}}(x; y)$ is $\mu + \kappa$ strongly convex, and therefore it admits the Polyak error bound condition: 
+        \subsubsection{Inner loop complexity}
+            The following parts will complement the report and talk about the convergence of the inner loop, and the overall algorithm. 
+            \par
+            Denote the outer loop algorithm by $\mathbb A$, and the inner loop algorithm by $\mathbb M$. 
+            The outer loop iteration algorithm generates $(x_k, y_k)_{k \ge0}$ by Definition \ref{def:lin-catalyst-original} and, for genericity assume that the inner loop is an iterative generating $(z_{k, i})_{i \ge 0}$ where $k$ denotes the iteration index of the outer loop.
+            \par
+            Lemma B1, B2 and Appendix item B.4 from Lin et al. \cite{lin_universal_2015} shows the convergence of the inner loop. 
+            It requires an error sequence $(\epsilon_k)_{k \ge 0}$ given in prior to assert the convergence rate of the outer loop. 
+            With warm starting, it uses the most recent iterate $x_{k - 1}$ (or equivalently some extrapolation using the most recent iterates) to initialize the inner loop to find the next $x_k \in \mathcal J_{F, \kappa^{-1}}^{\epsilon_{k}} y_{k - 1}$.
+            Warm starting the inner loop couples its convergence rate with the outer loop, allowing for the overall complexity analysis.  
+            Given the error sequence in Equation \ref{eqn:catalyst-error-seq-s-cnvx}, if $\mu > 0$ so the outer loop has linear convergence on $F(x_k) - F^*$, then it demands a linear convergence rate on model function $\mathcal M^{\kappa^{-1}}_F(\cdot, y_{k - 1})$ for the inner loop to an optimal complexity overall.
+            If $\mu = 0$, and $(\epsilon_k)_{k \ge0}$ is given by Equation \ref{eqn:catalyst-error-seq-cnvx}, so the outer loop has $\mathcal O(1/k^2)$ convergence rate on $F(x_k) - F^*$. 
+            With the assumption $\argmin_x F(x)$ is a bounded set and the inner loop converges linearly, an optimal overall complexity is achievable. 
+            \par 
+            Lin et al.'s second paper on Catalyst Acceleration \cite{lin_catalyst_2018} describes new ideas to choose the termination criteria for the inner for evaluating $\mathcal J_{\kappa^{-1}F}^{\epsilon_k} y_k$.
+            To elucidate, consider the model function $\mathcal M_F^{\kappa^{-1}}(x; y)$ to be $\mu + \kappa$ strongly convex. 
+            Therefore, it has error bound condition: 
             \begin{align*}
@@
             \end{align*}
-        By choosing $x$ such that $\dist(\mathbf 0, \partial \mathcal M_F^{1/\kappa}(x; y)) \le \epsilon$, it ensures $x \in \mathcal J^\epsilon_{\kappa^{-1}F}(y)$. 
-        Unfortunately in practice, this is not used because a full gradient evaluation on the model function $\mathcal M^{1/\kappa}_F(\cdot; y)$ is costly (compare to the small amount required for VRM, which is just the gradient of a few samples.), so Lin suggested alternatives of inner loop termination criteria, and/or upper bounds of inner loop iteration to make Catalyst Acceleration competitive in practice.
+            By choosing $x$ such that $\dist\left(\mathbf 0, \partial \mathcal M_F^{1/\kappa}(x; y)\right) \le \epsilon$, it ensures $x \in \mathcal J^\epsilon_{\kappa^{-1}F}(y)$. 
+            Unfortunately in practice, this is a difficult strategy because a full gradient evaluation on the model function $\mathcal M^{1/\kappa}_F(\cdot; y)$ is costly (compare to the small amount required for VRM, which is just the gradient of a few samples.), so Lin suggested alternatives of inner loop termination criteria, and/or upper bounds of inner loop iteration to make Catalyst Acceleration competitive in practice.
             \par
@@
                     \item [$\square$] The condition of warm starting in the algorithm and complexity bound of the inner loop. 
+                    \item [$\square$] The assumption of bounded level set to show the convergence when objective is not strongly convex. 
                 \end{enumerate}
@@
             \begin{enumerate}
-            \item A relative termination criteria that bounds the gradient of the problem in the inner loop, which results in a error sequence without $F^*$, and simplier proof without using the Nesterov's estimating sequence.
-            \item A more comprehensive convergence proof, for 2 different type of error bounds with, including the smooth plus nonsmooth compositie objective. 
+                \item A relative termination criteria that bounds the gradient of the problem in the inner loop, which results in an error sequence without $F^*$, and simpler proof without using the Nesterov's estimating sequence.
+                \item A more comprehensive convergence proof, for 2 different type of error bounds with, including the smooth plus nonsmooth composite objective. 
             \end{enumerate}
+            The list above is not exhaustive.
 

### 2025-01-06 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

@@
                 \item $A \in \RR^{M\times N}$ is a matrix of i.i.d random variable, taken from a standard normal distribution. 
-                \item $L, \mu$, the Lipschitz constant and the strong convexity constant for the smooth part of the objective are not known prior, and it's estimated through $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert^2$.
+                \item $L, \mu$, the Lipschitz constant and the strong convexity constant for the smooth part of the objective are not known prior, and it's estimated through $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$.
                 \item $x^+ = [1\; -1\; 1 \; \cdots ]^T \in \RR^N$, it's a vector with alternating $1, -1$ in it. 

### 2025-01-06 Notebook LaTEX/Proposal/main.tex
>w<, more changes

@@
         \end{remark}
-        With a fixed regularization parameter $\kappa > 0$, The outer loop (Definition \ref{def:lin-catalyst-original}) produces $(y_{k}, x_k)_{k \ge k}$ denote it by $\mathbb A$. 
-        Typically, an iterative scheme (i.e: VRM) with known complexity is assigned to find inexact proximal iterates $x_k \in {\mathcal J}_{\kappa^{-1}F}^{\epsilon_k} y_{k - 1}$. 
+        \textbf{Notations now follows}. 
+        With a fixed regularization parameter $\kappa > 0$, the outer loop (Definition \ref{def:lin-catalyst-original}) produces $(y_{k}, x_k)_{k \ge k}$ denote it by $\mathbb A$. 
+        Typically, an iterative scheme (i.e: VRM) with a known complexity is assigned to find inexact proximal iterates $x_k \in {\mathcal J}_{\kappa^{-1}F}^{\epsilon_k} y_{k - 1}$. 
         We refer this algorithm as the inner loop and denote it by $\mathbb M$. 
@@
         Due to the fact that function $F$ is convex, we focus on the convergence rate of the optimality gap $F(x_k) - F^*\*$ for $\mathbb A$ and convergence of the model function $\mathcal M_F^{\kappa^{-1}}(\cdot, y_{k - 1})$ for $\mathbb M$ given $y_{k - 1}, \epsilon_k$ and initial guess $z_{k, 0}$.
-        \todoinline{\noindent
-            \begin{enumerate}
-                \item State outer loop iteration complexity given error sequence for 
-                \begin{enumerate}
-                    \item Strongly convex objective,
-                    \item Non-strongly but strongly convex objective. 
-                \end{enumerate}
-                \item State the linear convergence rate assumption of the inner function. 
-                \item State the iteration complexity of the inner loop given the specific error sequence.
-
-            \end{enumerate}
-        }
         \par
@@
             Depending on either $\mu > 0$, or $\mu = 0$, the choice of $(\epsilon_k)_{k\ge 0}$ differs. 
-            The theorem that follows state the error sequence required for the outer loop to retain optimal convergence rate, they are Theorem 3.3, 3.1 in Lin et al. \cite{lin_universal_2015}. 
-            \begin{theorem}[Outer loop convergence strongly convex]
-
+            The theorems that follows state the error sequence required for the outer loop to retain optimal convergence rate, they are Theorem 3.3, 3.1 in Lin et al. \cite{lin_universal_2015}. 
+            \begin{theorem}[Outer loop convergence strongly convex]\label{thm:err-seq-outer-s-cnvx}
+                For $\mathbb A$ with regularization parameter $\kappa > 0$. 
+                Assume that $F$ is $\mu > 0$ strongly convex. 
+                Choose $\alpha_0 = \sqrt{q}$ with $q = \mu/(\kappa + \mu)$ and the error sequence 
+                $$
+                \begin{aligned}
+                    \epsilon_k = \frac{2}{9}(F(x_0) - F^*)(1 - \rho)^k \quad \text{with }\quad 
+                    \rho < \sqrt{q}. 
+                \end{aligned}
+                $$
+                Then the $\mathbb A$ generates $(x_{k})_{k \ge 0}$ such that 
+                $$
+                \begin{aligned}
+                    F(x_k) - F^* &\le 
+                    C(1 - \rho)^{k + 1} (F(x_0) - F^*) \quad \text{ with }\quad 
+                    C = \frac{8}{(\sqrt{q} - \rho)^2}. 
+                \end{aligned}
+                $$
             \end{theorem}
-            \begin{theorem}[Outer loop convergence convex but not strongly convex]
-
+            \begin{remark}
+                Suggested by Lin t al., $\rho$ is at the discretion of the practioner, take for example $\rho = 0.9\sqrt{q}$ would work. 
+            \end{remark}
+            \begin{theorem}[Outer loop convergence convex but not strongly convex]\label{thm:erro-seq-outer-cnvx}\;\\
+                For $\mathbb A$ with regularization parameter $\kappa > 0$. 
+                Assume that $F$ is convex but with strong convexity constant $\mu = 0$. 
+                Choose $\alpha_0 = (\sqrt{5} - 1)/2$ and the error sequence 
+                \begin{align*}
+                    \epsilon_k &= \frac{2(F(x_0) - F^*)}{9(k + 2)^{4 + \eta}} \quad 
+                    \text{with}\quad \eta > 0. 
+                \end{align*}
+                Take $x^*$ to be a minimizer of $F$. 
+                Then algorithm $\mathbb A$ generates $(x_k)_{k \ge0}$ such that it has a convergence rate of 
+                \begin{align*}
+                    F(x_k) - F^* &\le 
+                    \frac{8}{(k + 2)^2}\left(
+                        \left(1 + \frac{2}{\eta}\right)^2(F(x_k) - F^*)
+                        + \frac{\kappa}{2}\Vert x_0 - x^*\Vert^2
+                    \right).
+                \end{align*}
             \end{theorem}
-            For example, when $F$ has $\mu = 0$, 
-            \todo{
-                Lin's paper, Theorem 3.3
-            }
-            {\hl{Lin }}\cite[Theorem 3.3]{lin_universal_2015} suggested $\alpha_0 = \left(\sqrt{5} - 1\right)/2$, and 
-            \begin{align}
-                \epsilon_k = \frac{2(F(x_0) - F^*)}{9(k + 2)^{4 + \eta}}, 
-            \end{align}\label{eqn:catalyst-error-seq-cnvx}
-
-            where $\eta > 0$ is any number, i.e: $\eta = 0.1$. 
-            Then, the convergence of $F(x_k) - F^*$ with $(x_k)_{k \ge 0}$ produced by the outer loop is $\mathcal O(1/k^2)$. 
-            In this scenario, the iteration complexity of the outer loop optimal. 
-            To achieve optimal convergence for the outer loop when $\mu > 0$ for $F$, 
-            \todo{
-                Lin's first Catalyst, Theorem 3.1. 
-            }
-            {\hl{Lin }}\cite[Theorem 3.1]{lin_universal_2015}
-            suggested $\alpha_0 = \sqrt{\mu/(\kappa + \mu)}$ and the error sequence: 
-            \begin{align}
-                \epsilon_k = \frac{2}{9}(F(x_0) - F^*)(1 - \rho)^k \quad \text{with } \quad 
-                \rho < \sqrt{\frac{\mu}{\mu + \kappa}}. 
-            \end{align}\label{eqn:catalyst-error-seq-s-cnvx}
-            Take note that, the error sequence requires knowledge on $F^*$. 
-            It's not an issue in theoretical discussion for the convergence analysis and complexity analysis because it's assumed to exist. 
-            Unfortunately it's of upmost practical concern because the value $F^*$ is not accessible in practice and depends on the specific context of mathematical model of a practical problem. 
+            \begin{remark}
+                Suggested by Lin et al., $\eta > 0$ is at the discretion of the practitioners, for an example, $\eta = 0.1$ would work. 
+            \end{remark}
+            The same convergence claims hold if smaller value of $\epsilon_k$ is taken, Theorem \ref{thm:err-seq-outer-s-cnvx}, \ref{thm:erro-seq-outer-cnvx} gives the largest possible error sequence $(\epsilon_k)_{k \ge 0}$ such that the convergence claim holds.
+            Of course, taking smaller values of $(\epsilon_k)_{k \ge0}$ as suggested by the above theorems for $\mathbb M$ will hinder its convergence. 
+            \par
+            Observe that the error sequence $(\epsilon_k)_{k \ge 0}$ requires prior knowledge of $F^*$. 
+            It's poses no theoretical concerns, but it's of upmost practical concern since $F^*$ may not be accessible in practice prior to executing the algorithm. 
             In the work by Lin et al., the example algorithm given is 
-            \todo{Cite this algorithm}
-            {\hl{MISO Prox}} which automatically builds a lower bound estimates on $F^*$ in the outer loop. 
-            In practice, achieving higher accuracies in $\epsilon_k$ in inner loop would validate the over all convergence claim, but results in slower algorithm. 
-            Therefore, we want to know how to achieve $\epsilon_k$ without over compensating. 
+            D.3 Accelerating MISO Prox.
+            It automatically builds a lower bound estimates on $F^*$ in the outer loop as the algorithm executes.
+            \par 
+            We are now ready to derive the convergence rate measured by the number of total iteration experience by $\mathbb M$. 
             \par 
@@
             Significant pieces of theoretical innovations are covered in details in our most recent Fall Winter 2024 MATH 590 report. 
+            The parts that come will complement content in the report, filling up some of the missing content and attempts to build a bigger picture of Catalyst Acceleration.
+
         \subsubsection{Inner loop complexity}
-            The following parts will complement the report and talk about the convergence of the inner loop, and the overall algorithm. 
-            \par
-            Denote the outer loop algorithm by $\mathbb A$, and the inner loop algorithm by $\mathbb M$. 
-            The outer loop iteration algorithm generates $(x_k, y_k)_{k \ge0}$ by Definition \ref{def:lin-catalyst-original} and, for genericity assume that the inner loop is an iterative generating $(z_{k, i})_{i \ge 0}$ where $k$ denotes the iteration index of the outer loop.
-            \par
-            Lemma B1, B2 and Appendix item B.4 from Lin et al. \cite{lin_universal_2015} shows the convergence of the inner loop. 
-            It requires an error sequence $(\epsilon_k)_{k \ge 0}$ given in prior to assert the convergence rate of the outer loop. 
-            With warm starting, it uses the most recent iterate $x_{k - 1}$ (or equivalently some extrapolation using the most recent iterates) to initialize the inner loop to find the next $x_k \in \mathcal J_{F, \kappa^{-1}}^{\epsilon_{k}} y_{k - 1}$.
-            Warm starting the inner loop couples its convergence rate with the outer loop, allowing for the overall complexity analysis.  
-            Given the error sequence in Equation \ref{eqn:catalyst-error-seq-s-cnvx}, if $\mu > 0$ so the outer loop has linear convergence on $F(x_k) - F^*$, then it demands a linear convergence rate on model function $\mathcal M^{\kappa^{-1}}_F(\cdot, y_{k - 1})$ for the inner loop to an optimal complexity overall.
-            If $\mu = 0$, and $(\epsilon_k)_{k \ge0}$ is given by Equation \ref{eqn:catalyst-error-seq-cnvx}, so the outer loop has $\mathcal O(1/k^2)$ convergence rate on $F(x_k) - F^*$. 
-            With the assumption $\argmin_x F(x)$ is a bounded set and the inner loop converges linearly, an optimal overall complexity is achievable. 
+            The iteration complexity of $M$ relates to the outer loop when warm start is used. 
+            The Catalyst Paper \cite{lin_universal_2015} sugguested the use of $z_{k, 0} = x_{k - 1}$ as the warm start condition. 
+            With Assumption \ref{ass:linear-convergence-inner-loop}, and the suggested warm start condition,  Lin et al.
+derived the upper bound of the iteration complexity of $\mathbb M$, which are statd in Proposition \ref{prop:inner-loop-complexity-cnvx}, \ref{prop:inner-loop-complexity-s-cnvx}.
+            \begin{assumption}[Linear convergence of inner loop]\label{ass:linear-convergence-inner-loop}
+                Fix any $k \in \N$, any $y \in \RR^n$. 
+                Suppose $\mathbb M$ generates iterates $(z_{k, t})_{t \ge 0}$ for the inner loop iteration such that there exists $A > 0$ and it has: 
+                \begin{align*}
+                    \mathcal M_F^{\kappa^{-1}}(z_{k, t}, y) - \mathcal M^*_{F, \kappa^{-1}}(y) 
+                    &\le 
+                    A(1 - \tau_{\mathbb M})^t
+                    \left(
+                        \mathcal M_{F}^{\kappa^{-1}}(z_{k,0})
+                        -
+                        \mathcal M^*_{F, \kappa^{-1}}(y)
+                    \right). 
+                \end{align*}
+            \end{assumption}
+            \begin{remark}
+                Assumption is mild given the fact that model function $\mathcal M(\cdot, y_{k - 1})$ is $\mu + \kappa$ strongly convex given Assumption \ref{ass:catalyst1}.
+                For example, with smoothness assumption on $F$, many VRMs, or gradient descent method can achieve linear convergence under strong convexity. 
+                Since $\kappa$ is fixed, this assumption can be applied for all $k$ for $\mathbb A$. 
+            \end{remark}
+            \begin{proposition}[Inner loop complexity strongly convex]\label{prop:inner-loop-complexity-s-cnvx}
+
+            \end{proposition}
+
+            \begin{proposition}[Inner loop, context but not strongly convex]\label{prop:inner-loop-complexity-cnvx}
+
+            \end{proposition}
+
             \par 

### 2025-01-06 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
             \par 
-            We are now ready to derive the convergence rate measured by the number of total iteration experience by $\mathbb M$. 
-            \par 
             The convergence of the outer loop made use of an inexact version of the proximal gradient inequality (similar to Theorem \ref{thm:prox-grad-ineq}) stated as Lemma A.7 in \cite{lin_universal_2015}.
@@
             With Assumption \ref{ass:linear-convergence-inner-loop}, and the suggested warm start condition,  Lin et al.
-derived the upper bound of the iteration complexity of $\mathbb M$, which are statd in Proposition \ref{prop:inner-loop-complexity-cnvx}, \ref{prop:inner-loop-complexity-s-cnvx}.
+derived the upper bound of the iteration complexity of $\mathbb M$ (Propsotion ), which are statd in Proposition 3.2, 3.3 in their text, and \ref{prop:inner-loop-complexity-cnvx}, \ref{prop:inner-loop-complexity-s-cnvx} restates things below in our notations.
+            These two theorems relate the convergence of $\mathbb M, \mathbb A$ and gives a convergence rate of $F(x_k) - F^*$ expressed using the total number of iteration underwent by $\mathbb M$. 
             \begin{assumption}[Linear convergence of inner loop]\label{ass:linear-convergence-inner-loop}
@@
             \begin{proposition}[Inner loop complexity strongly convex]\label{prop:inner-loop-complexity-s-cnvx}
-
+                Under the same settings of Theorem \ref{thm:err-seq-outer-s-cnvx}, suppose that 
+                \begin{enumerate}
+                    \item method $\mathbb M$ has linear convergence rate as as specified in Assumption \ref{ass:linear-convergence-inner-loop}, 
+                    \item Method $\mathbb M$ is initialized with  $z_{k, 0} = x_{k - 1}$. 
+                \end{enumerate}
+                Then, the precision $\epsilon_k$ is achived within a at most a number of iteration $T_{\mathbb M} \le \widetilde {\mathcal O}(1/ \tau_{\mathbb M})$. 
+                Here $\widetilde{\mathcal O}$ hides logarithmic complexity in $\mu, \kappa$ and other constants. 
             \end{proposition}
+            \begin{remark}
+                $T_{\mathbb M}$, an upper bound of the iteration of the inner loop, is a constant in this case. 
+            \end{remark}
 
             \begin{proposition}[Inner loop, context but not strongly convex]\label{prop:inner-loop-complexity-cnvx}
-
+                Under the settings of Theorem \ref{thm:erro-seq-outer-cnvx}, suppose that:
+                \begin{enumerate}
+                    \item method $\mathbb M$ has linear convergence rate as specified in Assumption \ref{ass:linear-convergence-inner-loop}, 
+                    \item the initial guess for $\mathbb M$ is $z_{0, k} = x_{k - 1}$, 
+                    \item $F$ has bounded level set.
+                \end{enumerate}
+                Then there exists $T_{\mathbb M} \le \widetilde{\mathcal O}(1 / \tau_{\mathbb M})$ such that for any $k \ge 1$. 
+                Then it requires at most\\ $T_{\mathbb M}\log(k + 2)$ iterations for $\mathbb M$ to achieve accuracy $\epsilon_k$.    
             \end{proposition}
-
-            \par 
-            Lin et al.'s second paper on Catalyst Acceleration \cite{lin_catalyst_2018} describes new ideas to choose the termination criteria for the inner for evaluating $\mathcal J_{\kappa^{-1}F}^{\epsilon_k} y_k$.
+            We are now ready to derive the convergence rate measured by the number of total iteration experience by $\mathbb M$. 
+            If $\mu > 0$, so Proposition \ref{prop:inner-loop-complexity-s-cnvx} gives total number of inner iteration is bounded by $m \le T_{\mathbb M}k$. 
+            Substituting $k \ge m/T_{\mathbb M}$ into Theorem \ref{thm:err-seq-outer-s-cnvx}, it gives description of convergence rate of the algorithm measured by the total number of iteration experience by $\mathbb M$:
+            \begin{align*}
+                F(x_k) - F^* &\le \mathcal O \left(
+                    (1 - \rho)^k 
+                \right) \le 
+                \mathcal O \left(
+                    (1 - \rho)^{m/ T_{\mathbb M}}
+                \right) \le 
+                \mathcal O\left(
+                    \left(1 - \rho/T_{\mathbb M}\right)^{m}
+                \right)
+                \\
+                &\le \widetilde{\mathcal O}\left(
+                    \tau_{\mathbb M}\sqrt{\mu}/(\mu + \kappa)
+                \right). 
+            \end{align*}
+            The secondinequality on the first line made use of the fact that $1 + x \le (1 + x/n)^n$ for all $n \ge 1$ and $|x| \le n$. 
+            The optimal value of $\kappa$ is suggusted by choosing the best $\kappa > 0$ that minimizes the above upper bound. 
+            \par
+            If $\mu = 0$, using Propostion \ref{prop:inner-loop-complexity-cnvx} the total number of inner loop iteration executed by $\mathbb M$ at the $k$ th iteration of $\mathbb A$ is bounded via:
+            \begin{align*}
+                m &\le \sum_{i - 1}^{k} k T_{\mathbb M} \log(i + 2) \le k T_{\mathbb M} \log(k + 2) 
+                \le T_{\mathbb M}k(k + 2) 
+                \le 
+                \mathcal O(T_{\mathbb M} k^2). 
+            \end{align*}
+            Therefore, using Theorem \ref{thm:erro-seq-outer-cnvx}, the convergence rate as measure by the total number of inner iteration is given by: 
+            \begin{align*}
+                F(x_k)- F^* &\le 
+                \mathcal O(k^{-2})\le 
+                \mathcal O
+                    \left(
+                        m^{-2}T_{\mathbb M}
+                    \right) 
+                    \le \widetilde{\mathcal O}
+                        \left(m^{-2}\tau_{\mathbb M}^{-1}\right). 
+            \end{align*}
+            In both cases, the convergence rate remains optimal as measure by the total number of $\mathbb M$. 
+            \par 
+            Lin et al.'s second paper on Catalyst Acceleration \cite{lin_catalyst_2018} describes new ideas to choose the termination criteria for the inner for evaluating $\mathcal J_{\kappa^{-1}F}^{\epsilon_k} y_k$ and gives alternatives to the error sequence $\epsilon_k$ based on those termination criteria.
             To elucidate, consider the model function $\mathcal M_F^{\kappa^{-1}}(x; y)$ to be $\mu + \kappa$ strongly convex. 
@@
                         \mathbf 0, \partial \mathcal M^{1/\kappa}_F(x; y)
-                    \right). 
-            \end{align*}
-            By choosing $x$ such that $\dist\left(\mathbf 0, \partial \mathcal M_F^{1/\kappa}(x; y)\right) \le \epsilon$, it ensures $x \in \mathcal J^\epsilon_{\kappa^{-1}F}(y)$. 
-            Unfortunately in practice, this is a difficult strategy because a full gradient evaluation on the model function $\mathcal M^{1/\kappa}_F(\cdot; y)$ is costly (compare to the small amount required for VRM, which is just the gradient of a few samples.), so Lin suggested alternatives of inner loop termination criteria, and/or upper bounds of inner loop iteration to make Catalyst Acceleration competitive in practice.
-            \par
-            \todoinline{\noindent
-                Add more details about what they actually did in the original paper.
-                \begin{enumerate}
-                    \item [$\square$] The condition of warm starting in the algorithm and complexity bound of the inner loop. 
-                    \item [$\square$] The assumption of bounded level set to show the convergence when objective is not strongly convex. 
-                \end{enumerate}
-            }
-            \par 
-            These raised conflicts in the theories and practice of the Catalyst Accelerations framework are the focuses of Lin's second Catalyst paper \cite{lin_catalyst_2018}. 
+                    \right)^2. 
+            \end{align*}
+            By choosing $x$ such that $\dist\left(\mathbf 0, \partial \mathcal M_F^{1/\kappa}(x; y)\right) \le \sqrt{\epsilon}$, it ensures $x \in \mathcal J^\epsilon_{\kappa^{-1}F}(y)$. 
+            Unfortunately, this is a difficult in practice because a full gradient evaluation on the model function $\mathcal M^{1/\kappa}_F(\cdot; y)$ is costly (compare to the small amount required for VRM, which is just the gradient of a few samples.), so Lin suggested alternatives of inner loop termination criteria, and/or upper bounds of inner loop iteration to make Catalyst Acceleration competitive in practice.
+            \par 
+            These conflicts in the theories and practice of the Catalyst Accelerations framework are the focuses of Lin's second Catalyst paper \cite{lin_catalyst_2018}. 
             The paper has the following new ideas: 
             \begin{enumerate}
-                \item A relative termination criteria that bounds the gradient of the problem in the inner loop, which results in an error sequence without $F^*$, and simpler proof without using the Nesterov's estimating sequence.
+                \item A relative termination criteria that bounds the gradient of the problem in the inner loop, which results in an error sequence without $F^*$, and simpler proof without using the Nesterov's estimating sequence, and getting rid of the bounded level set assumption in Proposition \ref{prop:inner-loop-complexity-cnvx}.
                 \item A more comprehensive convergence proof, for 2 different type of error bounds with, including the smooth plus nonsmooth composite objective. 
@@
 
-    \subsection{Inner loop termination criteria}
+    \subsection{The second Catalyst Acceleration paper}
         Denote the outer loop iteration algorithm by $\mathbb A$, and inner loop iteration algorithm by $\mathbb M$. 
@@
         \begin{remark}
-            This is Lin Lemma 2 \cite{lin_catalyst_2018}. 
+            This is Lemma 2 in Lin et al. \cite{lin_catalyst_2018}. 
         \end{remark}
 
-    \subsection{Consequences of the inner loop termination criteria}
+        \subsubsection{Consequences of the inner loop termination criteria}
             Lemma \ref{lemma:sufficient-c1} describes a sufficient conditions to verify the membership of $\bar z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$ through the proximal gradient operator on $F:= f_\kappa(z) + g(z)$ which of practical importance because it translates criterion C1 into something implementable, i.e: the proximal gradient operator.
@@
             \par
-        To attain an optimal convergence rate for $\mathbb A$ on criterion C1, the error sequence $(\epsilon_k)_{k \ge 0}$ should be given by Equation \ref{eqn:catalyst-error-seq-cnvx} for convex $F$, and \ref{eqn:catalyst-error-seq-s-cnvx} for strongly convex $F$.
-        Amazingly, termination criterion C2 doesn't require knowledge on $F^*$ to achieve optimal convergence for $\mathbb A$. 
-        The following schedules for $(\delta_k)_{k \ge 0}$ are given in Lin, et al.'s second Catalyst paper, the error sequence $\delta_k$ for criterion C2 is given by: 
-        \begin{align*}\label{eqn:catalyst-rel-error-seq}
-            q &= \mu/(\mu + \kappa), 
-            \\
-            \delta_k 
-            &= \frac{\sqrt{q}}{2 - \sqrt{q}} \text{ if } \mu > 0, 
-            \\
-            \delta_k &= \frac{1}{(k + 1)^2} \text{ if }\mu = 0. 
-        \end{align*}
-        Let's pay particular attention to criterion C2.
 

### 2025-01-06 Notebook LaTEX/Proposal/main.tex
>w<, changes, sync

@@
     In the expository writing by Walkington \cite{noel_nesterovs_nodate}, a variant for of accelerated gradient method for strongly convex function $f$ is discussed. 
-    We had two lingering questions after reading it. 
+    We had some lingering questions after reading it. 
     \begin{enumerate}
         \item Do there exist a unified description for the convergence for both variants of the algorithms?
-        \item Is it possible to attain faster convergence rate without knowledge about the strong convexity of function $f$?
+        \item Is it possible to attain fast convergence rate without knowledge about the strong convexity of function $f$?
         \item Is it possible to describe the convergence of function value for momentum sequences that are much weaker than the Nesterov's rule? 
@@
     The good news is we have definitive answers for all questions by our own efforts of research. 
-    Section \ref{sec:unify-nes-acceleration}, \ref{sec:spectral-momentum} are our ongoing research which present the answers to the questions. 
+    Section \ref{sec:unify-nes-acceleration}, \ref{sec:free-rwapg} are our ongoing research which present the answers to the questions. 
     \par
@@
     \par
-    In Section \ref{sec:spectral-momentum} we propose a practical algorithm that exploits a specific term in the proof of R-WAPG to achieve faster convergence for solving (\ref{eqn:additive-comp-obj}) without knowing parameter $L, \mu$ in prior.
+    In Section \ref{sec:free-rwapg} we propose a practical algorithm that exploits a specific term in the proof of R-WAPG to achieve faster convergence for solving (\ref{eqn:additive-comp-obj}) without knowing parameter $L, \mu$ in prior.
     Results of numerical experiments are presented. 
@@
 \section{Unifying NAG, and weakening the sequence assumption for convergences}\label{sec:unify-nes-acceleration}
-    \todoinline{\noindent
-        This section is really about stating the results of the draft paper and no proofs will be done here. 
-        Along with the content of the draft paper, we will also explain the origin and inspirations of the ideas. 
-    }
     This section is based on the theoretical aspects of our draft paper. 
@@
         We define the Moreau Envelope at $y \in \RR^n$ to be $\mathcal M^*_{F,\beta^{-1}}(y) = \min_{x\in \RR^n} \mathcal M_F^{\beta^{-1}}(x; y)$. 
-        We denote $\mathcal J_{\beta^{-1}}$ to be the resolvent operator for subgradient of $F$, and $\mathcal J_{\beta^{-1}}^\epsilon$ for any $\epsilon \ge 0$ to be the inexact resolvent operator. 
-        \begin{align*}
-            \mathcal J_{\beta^{-1}F}^\epsilon (y) &:= 
+        We denote $\mathcal J_{\beta^{-1}}$ to be the resolvent operator for subgradient of $F$. 
+    \end{assumption}
+    \begin{definition}[Absolute termination criterion C1]\label{def:catalyst-termination-c1}
+        Take $F$ as given by Assumption \ref{ass:catalyst1}.
+        Given any $\epsilon > 0, \kappa > 0$ and $x \in \RR^n$, the absolute criterion C1 characterizes the set of inexact proximal iterates as the set: 
+        \begin{align*}
+            \mathcal J_{\kappa^{-1} F}^\epsilon (x) := 
             \left\lbrace
-                x \in \RR^n \left | \; 
-                    \mathcal M^{\beta^{-1}}_F(x; y) - 
-                    \mathcal M_{\beta^{-1}, F}^*(y) \le \epsilon
+                y \in \RR^n \left | \; 
+                        \mathcal M^{1/\kappa}_F (y; x) - 
+                        \mathcal M^*_{F, 1/\kappa}(x) \le \epsilon
                 \right.
@@
         \end{align*}
+    \end{definition}
+    \begin{remark}
         Setting $\epsilon = 0$, we have the exact definition of the exact resolvent given as $\mathcal J_{\beta^{-1}}y = \mathcal J^0_{\beta^{-1}}y$. 
-    \end{assumption}
+    \end{remark}
     \subsection{Introduction to Catalyst}
@@
         \todo{
-            $\blacksquare$ Add old Dima's paper on incremental methods here. Paper: ``Incremental gradient, subgradient, and proximal methods for convex optimization: A survey''. 
+            $\blacksquare$ Add old Bertsekas's paper on incremental methods here. Paper: ``Incremental gradient, subgradient, and proximal methods for convex optimization: A survey''. 
             \\
@@
             Let $(\epsilon_k)_{k \ge 0}$ be an error sequence chosen for the evaluation for inexact proximal point method. 
+            \begin{tcolorbox}
                 Initialize $x_0 = y_0$. Then the algorithm generates $(x_k, y_k)_{k\ge 0}$ for all $k \ge 1$ such that: 
@@
                 \end{align*}
+            \end{tcolorbox}
         \end{definition}
@@
             Depending on either $\mu > 0$, or $\mu = 0$, the choice of $(\epsilon_k)_{k\ge 0}$ differs. 
-            The theorems that follows state the error sequence required for the outer loop to retain optimal convergence rate, they are Theorem 3.3, 3.1 in Lin et al. \cite{lin_universal_2015}. 
+            The theorems that follow state the error sequence required for the outer loop to retain optimal convergence rate, they are Theorem 3.3, 3.1 in Lin et al. \cite{lin_universal_2015}. 
             \begin{theorem}[Outer loop convergence strongly convex]\label{thm:err-seq-outer-s-cnvx}
@@
             \begin{remark}
-                Suggested by Lin t al., $\rho$ is at the discretion of the practioner, take for example $\rho = 0.9\sqrt{q}$ would work. 
+                Suggested by Lin et al., $\rho$ is at the discretion of the practitioner, take for example $\rho = 0.9\sqrt{q}$ would work. 
             \end{remark}
@@
             Significant pieces of theoretical innovations are covered in details in our most recent Fall Winter 2024 MATH 590 report. 
-            The parts that come will complement content in the report, filling up some of the missing content and attempts to build a bigger picture of Catalyst Acceleration.
+            The parts that come will complement content in the report, filling up missing content and attempts to build a bigger picture of Catalyst Acceleration.
 
@@
             The iteration complexity of $M$ relates to the outer loop when warm start is used. 
-            The Catalyst Paper \cite{lin_universal_2015} sugguested the use of $z_{k, 0} = x_{k - 1}$ as the warm start condition. 
+            The Catalyst Paper \cite{lin_universal_2015} suggested the use of $z_{k, 0} = x_{k - 1}$ as the warm start condition. 
             With Assumption \ref{ass:linear-convergence-inner-loop}, and the suggested warm start condition,  Lin et al.
-derived the upper bound of the iteration complexity of $\mathbb M$ (Propsotion ), which are statd in Proposition 3.2, 3.3 in their text, and \ref{prop:inner-loop-complexity-cnvx}, \ref{prop:inner-loop-complexity-s-cnvx} restates things below in our notations.
+derived the upper bound of the iteration complexity of $\mathbb M$, which are stated in Proposition 3.2, 3.3 in their text, and \ref{prop:inner-loop-complexity-cnvx}, \ref{prop:inner-loop-complexity-s-cnvx} restates things below in our notations.
             These two theorems relate the convergence of $\mathbb M, \mathbb A$ and gives a convergence rate of $F(x_k) - F^*$ expressed using the total number of iteration underwent by $\mathbb M$. 
@@
                 Fix any $k \in \N$, any $y \in \RR^n$. 
-                Suppose $\mathbb M$ generates iterates $(z_{k, t})_{t \ge 0}$ for the inner loop iteration such that there exists $A > 0$ and it has: 
+                Suppose $\mathbb M$ generates iterates $(z_{k, t})_{t \ge 0}$ for the inner loop iteration such that there exists $A > 0$, and it has: 
                 \begin{align*}
@@
                 \begin{enumerate}
-                    \item method $\mathbb M$ has linear convergence rate as as specified in Assumption \ref{ass:linear-convergence-inner-loop}, 
-                    \item Method $\mathbb M$ is initialized with  $z_{k, 0} = x_{k - 1}$. 
+                    \item $\mathbb M$ has linear convergence rate as specified in Assumption \ref{ass:linear-convergence-inner-loop}, 
+                    \item $\mathbb M$ is initialized with  $z_{k, 0} = x_{k - 1}$. 
                 \end{enumerate}
-                Then, the precision $\epsilon_k$ is achived within a at most a number of iteration $T_{\mathbb M} \le \widetilde {\mathcal O}(1/ \tau_{\mathbb M})$. 
+                Then, the precision $\epsilon_k$ is achieved within at most a number of iteration $T_{\mathbb M} \le \widetilde {\mathcal O}(1/ \tau_{\mathbb M})$. 
                 Here $\widetilde{\mathcal O}$ hides logarithmic complexity in $\mu, \kappa$ and other constants. 
@@
                 \begin{enumerate}
-                    \item method $\mathbb M$ has linear convergence rate as specified in Assumption \ref{ass:linear-convergence-inner-loop}, 
+                    \item $\mathbb M$ has linear convergence rate as specified in Assumption \ref{ass:linear-convergence-inner-loop}, 
                     \item the initial guess for $\mathbb M$ is $z_{0, k} = x_{k - 1}$, 
@@
             \end{proposition}
+            For a proof of Proposition \ref{prop:inner-loop-complexity-cnvx}, \ref{prop:inner-loop-complexity-s-cnvx}, see Appendix item B1, B2 in Lin et al. \cite{lin_universal_2015}. 
             We are now ready to derive the convergence rate measured by the number of total iteration experience by $\mathbb M$. 
@@
             \end{align*}
-            The secondinequality on the first line made use of the fact that $1 + x \le (1 + x/n)^n$ for all $n \ge 1$ and $|x| \le n$. 
-            The optimal value of $\kappa$ is suggusted by choosing the best $\kappa > 0$ that minimizes the above upper bound. 
-            \par
-            If $\mu = 0$, using Propostion \ref{prop:inner-loop-complexity-cnvx} the total number of inner loop iteration executed by $\mathbb M$ at the $k$ th iteration of $\mathbb A$ is bounded via:
+            The second inequality on the first line made use of the fact that $1 + x \le (1 + x/n)^n$ for all $n \ge 1$ and $|x| \le n$. 
+            The optimal value of $\kappa$ is suggested by choosing the best $\kappa > 0$ that minimizes the above upper bound. 
+            \par
+            If $\mu = 0$, using Proposition \ref{prop:inner-loop-complexity-cnvx} the total number of inner loop iteration executed by $\mathbb M$ at the $k$ th iteration of $\mathbb A$ is bounded via:
             \begin{align*}
@@
             \end{align*}
+            The last inequality is $T_{\mathbb M} < \widetilde{\mathcal O}(1/\tau_{\mathbb M})$ from Proposition \ref{prop:inner-loop-complexity-cnvx}. 
             In both cases, the convergence rate remains optimal as measure by the total number of $\mathbb M$. 
@@
             Unfortunately, this is a difficult in practice because a full gradient evaluation on the model function $\mathcal M^{1/\kappa}_F(\cdot; y)$ is costly (compare to the small amount required for VRM, which is just the gradient of a few samples.), so Lin suggested alternatives of inner loop termination criteria, and/or upper bounds of inner loop iteration to make Catalyst Acceleration competitive in practice.
-            \par 
-            These conflicts in the theories and practice of the Catalyst Accelerations framework are the focuses of Lin's second Catalyst paper \cite{lin_catalyst_2018}. 
-            The paper has the following new ideas: 
+            % \par 
+            % These conflicts in the theories and practice of the Catalyst Accelerations framework are the focuses of Lin's second Catalyst paper \cite{lin_catalyst_2018}. 
+            % The paper has the following new ideas: 
+            % \begin{enumerate}
+            %     \item A relative termination criteria that bounds the gradient of the problem in the inner loop, which results in an error sequence without $F^*$, and simpler proof without using the Nesterov's estimating sequence, and getting rid of the bounded level set assumption in Proposition \ref{prop:inner-loop-complexity-cnvx}.
+            %     \item A more comprehensive convergence proof, for 2 different type of error bounds with, including the smooth plus nonsmooth composite objective. 
+            % \end{enumerate}
+            % The list above is not exhaustive.
+
+    \subsection{The second Catalyst Acceleration paper}
+        This section discusses major contents in Lin's second Catalyst paper \cite{lin_catalyst_2018}. 
+        To expedite the execution of $\mathbb M$ in general given an error sequence $(\epsilon_k)_{k \ge 0}$ (or equivalently some lower bounds of it), Lin suggested the following new ideas which are not  mutually exclusive:
         \begin{enumerate}
-                \item A relative termination criteria that bounds the gradient of the problem in the inner loop, which results in an error sequence without $F^*$, and simpler proof without using the Nesterov's estimating sequence, and getting rid of the bounded level set assumption in Proposition \ref{prop:inner-loop-complexity-cnvx}.
-                \item A more comprehensive convergence proof, for 2 different type of error bounds with, including the smooth plus nonsmooth composite objective. 
-            \end{enumerate}
-            The list above is not exhaustive.
-
-    \subsection{The second Catalyst Acceleration paper}
-        Denote the outer loop iteration algorithm by $\mathbb A$, and inner loop iteration algorithm by $\mathbb M$. 
-        This section discusses major contents in Lin's second Catalyst paper \cite{lin_catalyst_2018}. 
-        To expedite the execution of $\mathbb M$ in general given an error sequence $(\epsilon_k)_{k \ge 0}$ (or equivalently some lower bounds of it), Lin suggested two major strategies that are not necessarily mutually exclusive:
-        \begin{enumerate}
-            \item Use a warm start strategy, i.e: take the most recent iterates produced by $\mathbb A$ as the initial guess for $\mathbb M$. 
+            \item An improved warm start strategy that improved the convergence rate under different termination criteria, and it supports smooth plus nonsmooth objective. 
             \item An absolute termination criterion C1 stated in Definition \ref{def:catalyst-termination-c1}, governed by the error sequence $(\epsilon_k)_{k \ge 0}$. 
@@
         \end{enumerate}
-        \par
         We now introduce the early termination criteria for $\mathbb M$. 
         In our notation, we define the absolute termination criterion, which are C1 and C2 directly taken from Lin's second Catalyst paper but in our notations.
-        \begin{definition}[Absolute termination criterion C1]\label{def:catalyst-termination-c1}
-            Take $F$ as given by Assumption \ref{ass:catalyst1}.
-            Given any $\epsilon > 0, \kappa > 0$ and $x \in \RR^n$, the absolute criterion C1 characterizes the set of inexact proximal iterates as the set: 
-            \begin{align*}
-                \mathcal J_{\kappa^{-1} F}^\epsilon (x) := 
-                \left\lbrace
-                    y \in \RR^n \left | \; 
-                            \mathcal M^{1/\kappa}_F (y; x) - 
-                            \mathcal M^*_{F, 1/\kappa}(x) \le \epsilon
-                    \right.
-                \right\rbrace. 
-            \end{align*}
-        \end{definition}
 
@@
         \end{definition}
+        Observe that, if we set $\epsilon_{k} = \delta\kappa/2\Vert x - z\Vert^2$ then $\widetilde{\mathcal J}_{\kappa^{-1}F}^{\delta} (x) = \mathcal J_{\kappa^{-1}F}^\epsilon (x)$. 
+        The relative inexact condition can be interpreted as an adaptive inexactness condition. 
         Stated by Lin, the following lemmas are the sufficient conditions and consequences of termination criteria C1, C2. 
-
         \begin{lemma}[Sufficient condition for C1]\label{lemma:sufficient-c1}
@@
                 \delta' \Vert \nabla \mathcal M^*_{F, \kappa^{-1}}(x) \Vert \quad 
-                \text{with } \delta' = \sqrt{\delta}/(1 - \sqrt{\delta}). 
+                \text{with } \delta' = \sqrt{\delta}/\left(1 - \sqrt{\delta}\right). 
             \end{align*}
@@
             \par
-            Finally, besides C1, C2 criteria which, the ``Fixed Budget" termination criterion assesses the optimality of results produced by $\mathbb M$, we can also terminate $\mathbb M$ after a fixed number of iteration.
-            This is the original strategy proposed by Lin et al. in their first Catalyst paper in 2015 \cite{lin_universal_2015}. 
+            Finally, besides C1, C2 criteria which, the ``Fixed Budget" termination criterion assesses the optimality of results produced by $\mathbb M$. 
+            Alternatively, terminating $\mathbb M$ after a fixed number of iteration is the original strategy proposed by Lin et al. in their first Catalyst paper in 2015 \cite{lin_universal_2015}. 
             It needs a precise bound on the complexity for $\mathbb M$ to achieve C1, or C2 of the strongly convex function $\mathcal M^{\kappa^{-1}}_F(\cdot; y)$. 
             \par
+            Developing the new relative termination criterion gives improvements on the complexity of inner loop $\mathbb M$, outer loop $\mathbb A$, and the relative error sequence $(\delta_k)_{k \ge0}$ for $\mathbb M$.
+            The theorems and commentaries that follow will illustrate. 
+            \begin{definition}[A better Catalyst Acceleration]\label{def:catalyst-relative}
+                Suppose that $F$ is a $\mu \ge 0$ strongly smooth under Assumption \ref{ass:catalyst1}. 
+                Initialize any $x_0 \in \mathbb \RR^n$, $\kappa > 0$. 
+                Given the relative error sequence $(\delta_k)_{k \ge 0}$, or equivalently some fixed budget number of iterations $T_{\mathbb M}$, or absolute error sequence $(\epsilon_k)_{k \ge 0}$: 
+                \begin{tcolorbox}
+                    Initialize $y_0 = x_0, q = \mu/(\kappa + \mu), k = 1$, and if $\mu > 0$, set $\alpha_0 = \sqrt{q}$ otherwise $\alpha_0 = 1$.  
+                    \textbf{While} desirable accuracy is not reached, \textbf{do}: 
+                    \begin{enumerate}
+                        \item Finds $x_k \approx \mathcal J_{\kappa^{-1}F} y_{k - 1}$ using warm start. 
+                        \item Pick one of the following fixed termination criterion: 
+                        \begin{enumerate}
+                            \item Determine the number of fixed budget depending on $T_{\mathbb M}$, terminate the above subroutine if fixed budget reached.
+                            \item C1 are satisfied through $\epsilon_k$. 
+                            \item C2 are satisfied through $\delta_k$. 
+                        \end{enumerate}
+                        \item Find $\alpha_k \in (0, 1)$ such that $\alpha_k^2 = (1 - \alpha_{k})\alpha_{k - 1}^2 + q\alpha_k$. 
+                        \item Compute extrapolation $y_k = x_k + \beta_k(x_k - x_{k - 1})$ with 
+                        $$
+                            \beta_{k} = \alpha_{k - 1}(1 - \alpha_{k - 1})/(\alpha_{k - 1}^2 + \alpha_k). 
+                        $$
+                        \item Increment $k := k + 1$
+                    \end{enumerate}
+                    \textbf{End while} 
+                \end{tcolorbox}
+            \end{definition}
+
+            \begin{theorem}[Outer loop complexity under criterion C2]\label{theorem:catalyst2-outer-loop}
+                For the iterates $(x_k)_{k \ge 0}$ generated by algorithm in Definition \ref{def:catalyst-relative}, we have 
+                \begin{enumerate}
+                    \item If $\mu > 0$, choose $\alpha_0 = \sqrt{q}$, $\delta_k = \sqrt{q}/(2 - \sqrt{q})$. 
+                    Then the iterates $(x_k)_{k \ge 0}$ satisfies $F(x_k) - F^* \le \mathcal O\left(1 - \sqrt{q}/2\right)^k$. 
+                    \item If $\mu = 0$, choose $\alpha_0 = 1$, $\delta_k = 1/(k + 1)^2$ satisfies $F(x_k) - F^* \le \mathcal O(k^{-2})$. 
+                \end{enumerate}
+            \end{theorem}
+            \begin{remark}
+                This is Proposition 8, 9 in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018}.
+                For a precise description of the upper bound, see Theorem 8. 
+            \end{remark}
+            The key improvement here compared to using absolute inexactness for $\mathbb M$ as stated by Theorem \ref{thm:err-seq-outer-s-cnvx}, \ref{thm:erro-seq-outer-cnvx} is that $(\delta_k)_{k \ge0}$ doesn't require knowledge on $F^*$.
+            Using termination criterion C2 and warm start, the inner loop complexity is stated in Corollary 16 in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018}. 
+            It's important to note that the upper complexity bounds are much better, and it doesn't require bounded level set compared to Theorem \ref{prop:inner-loop-complexity-cnvx}.
 

### 2025-01-06 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
         \begin{enumerate}
-            \item An improved warm start strategy that improved the convergence rate under different termination criteria, and it supports smooth plus nonsmooth objective. 
-            \item An absolute termination criterion C1 stated in Definition \ref{def:catalyst-termination-c1}, governed by the error sequence $(\epsilon_k)_{k \ge 0}$. 
-            \item A relative termination criterion C2 stated in Definition \ref{def:catalyst-termination-c2}, governed by the error sequence $(\delta_k)_{k \ge 0}$
+            \item An improved warm start strategy at the end of Section 3. 
+            It improved the convergence rate under different termination criteria, and it supports smooth plus nonsmooth objective. 
+            \item A relative termination criterion C2 stated in Definition \ref{def:catalyst-termination-c2}, governed by the error sequence $(\delta_k)_{k \ge 0}$. 
+            The sequence $\delta_k$ doesn't require knowledge on $F^*$, it simplifies the convergence proof, gives better bounds on the complexity for $\mathbb M$ without using bounded level set condition.
+            Recall that Theorem \ref{prop:inner-loop-complexity-cnvx} requires bounded level set assumption on $F$. 
         \end{enumerate}
-        We now introduce the early termination criteria for $\mathbb M$. 
-        In our notation, we define the absolute termination criterion, which are C1 and C2 directly taken from Lin's second Catalyst paper but in our notations.
-
+        In our notation, we define relative termination criterion C2.
         \begin{definition}[Relative termination criterion C2]\label{def:catalyst-termination-c2}
@@
             Their works were earlier and a Nesterov accelerated algorithm using estimating sequence and inexact oracles was derived. 
-            \par
-            Finally, besides C1, C2 criteria which, the ``Fixed Budget" termination criterion assesses the optimality of results produced by $\mathbb M$. 
-            Alternatively, terminating $\mathbb M$ after a fixed number of iteration is the original strategy proposed by Lin et al. in their first Catalyst paper in 2015 \cite{lin_universal_2015}. 
-            It needs a precise bound on the complexity for $\mathbb M$ to achieve C1, or C2 of the strongly convex function $\mathcal M^{\kappa^{-1}}_F(\cdot; y)$. 
-            \par
-            Developing the new relative termination criterion gives improvements on the complexity of inner loop $\mathbb M$, outer loop $\mathbb A$, and the relative error sequence $(\delta_k)_{k \ge0}$ for $\mathbb M$.
+            These results are instrumental to prove the convergence of $\mathbb M$ and giving convergence claim of $\mathbb A$ under certain assumption on $(\delta_k)_{k \ge 0}, (\epsilon_k)_{k \ge0}$.
+            \par
+            Finally, besides Definition \ref{def:catalyst-termination-c1}, \ref{def:catalyst-termination-c2}, there is the ``Fixed Budget" termination criterion. 
+            It terminates $\mathbb M$ after a fixed number of iteration. 
+            Criterion C1 used to prove the overall complexity in Lin et al. \cite{lin_universal_2015}, but the bound is deliberately loose to allow generality, making it extremely impractical. 
+            Criterion C2 places similar upper bound on the iteration complexity for $\mathbb M$, but it still remains impractical. 
+            \par
+            Interestingly, the new termination criterion C2 gives improvements on the complexity of inner loop $\mathbb M$, outer loop $\mathbb A$, and the relative error sequence $(\delta_k)_{k \ge0}$ for $\mathbb M$.
             The theorems and commentaries that follow will illustrate. 
@@
             The key improvement here compared to using absolute inexactness for $\mathbb M$ as stated by Theorem \ref{thm:err-seq-outer-s-cnvx}, \ref{thm:erro-seq-outer-cnvx} is that $(\delta_k)_{k \ge0}$ doesn't require knowledge on $F^*$.
-            Using termination criterion C2 and warm start, the inner loop complexity is stated in Corollary 16 in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018}. 
+            This innocent detail helps to develop a nonconvex variant of Catalyst call 4WD Catalyst which is the focus of the paper by Paguette \cite{paquette_catalyst_2018}. 
+            Corollary 16 in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018} gives complexity for $\mathbb M$ Using termination criterion C2 with a warm start specialized for $C2$. 
             It's important to note that the upper complexity bounds are much better, and it doesn't require bounded level set compared to Theorem \ref{prop:inner-loop-complexity-cnvx}.         
-
-    \subsection{Complexity}
-
     \subsection{Potential future research}
+        Now, we have enough context to understand the potential future directions of research regarding the Catalyst Acceleration framework.
 

### 2025-01-07 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
 \section{Nestrov's acceleration in the nonconvex case}\label{sec:nes-acc-ncnvx}
-    The behavior of Nesterov's acceleration for function that are nonconvex are the holy grail and the absolute frontier. 
-    The approaches are incredibly diverse and therefore, this section will only list relevant references and briefly mention the ideas involved in those literatures. 
-    \todoinline{\noindent
-        Here, is a list of early attempted research of Nesterov's acceleration method in the nonconvex case.
-
-    }
+    % The behavior of Nesterov's acceleration for function that are nonconvex are the holy grail and the absolute frontier. 
+    % The approaches are incredibly diverse and therefore, this section will only list relevant references and briefly mention the ideas involved in those literatures. 
+    % \todoinline{\noindent
+    %     Here, is a list of early attempted research of Nesterov's acceleration method in the nonconvex case. 
+    % }
 

### 2025-01-07 Notebook LaTEX/Proposal/main.tex
>w<, sync

@@
             \begin{enumerate}
-                \item 
+                \item SVRG: Proximal stochastic gradient with progressive variance reduction. 
+                \item Finito: A faster, permutable incremental gradient method for big data problems
+                \item SAG: Minimizing finite sums with the stochastic average gradient
+                \item SAGA: A fast increment al gradient method with support for non-strongly convex composite objectives. 
             \end{enumerate}

### 2025-01-07 Notebook LaTEX/R-WAPG/paper3.tex
>w<, sync

@@
         \todoinline{\noindent
-            Here is a list of papers that are relevant to generalizing the convergence claim for APG beyond just the traditional choices for the momentum sequence. 
-            \begin{enumerate}
-                \item Attouch H., Cabot A.: ``Convergence Rates of Inertial Forward-Backward Algorithms'', SIAM. 
-                \item Vassilis A., et al.: ``Convergence rate of inertial Forward-Backward algorithm beyond Nesterov's rule". 
-            \end{enumerate}
-            The following papers are related to stabilizing, improving the acceleration scheme without monotone restarting. 
-            \begin{enumerate}
-                \item Attouch H., et al.: ``First-order optimization algorithms via inertial systems with Hessian driven damping'', Math Programming. 
-            \end{enumerate}
-            \textcolor{red}{The prior works' section is too little, it requires some expansion in the future for sure.} 
+            The prior works' section is too little, it requires some expansion in the future for sure.
         }
@@
         Section \ref{sec:rwapg-literatures} formulates FISTA, and V-FISTA sequences and proves the convergence rate of several variants  FISTA using the R-WAPG algorithm and its convergence rate developed in the previous sections.
-        Finally, in Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcaes the numerical experiments for regression, LASSO, and logistic regression.
-        The numerical experiments exposes very interesting behaviors of the algorithm of our own creativity.
+        Finally, in Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcase the numerical experiments for regression, LASSO, and logistic regression.
+        The numerical experiments expose very interesting behaviors of the algorithm of our own creativity.
 

### 2025-01-08 Notebook LaTEX/Proposal/main.tex
>w<, changes, sync

--- 2025-01-07 Notebook LaTEX/Proposal/main.tex
@@
     The good news is we have definitive answers for all questions by our own efforts of research. 
+    \todoinline{\noindent
+        $\square$ Change all the organization parts here
+    }
     Section \ref{sec:unify-nes-acceleration}, \ref{sec:free-rwapg} are our ongoing research which present the answers to the questions. 
@@
         }
-        {\hl{incremental methods}}
+        {\hl{incremental methods}} \cite{bertsekas_incremental_2011,bertsekas_incremental_2017}
         for solving a large sum problem: $F(x) = \sum_{i = 1}^{N} f_i(x)$ in machine learning.
@@
         The idea of VRM is to stabilize the estimate of gradient using information of the gradient (which can be estimated, or exact) from all or a subset at previous iterates. 
-        In each iteration, only the gradient of a few samples are accessed and uses simple calculations from previously stored gradient to attain overall better complexity 
-        It can achieve that because the variance of the estimated gradients are smaller when the iterates are close to the set of true minimizer. 
+        In each iteration, only the gradient of a few samples are accessed and uses simple calculations from previously stored gradient to attain overall better complexity.
+        Compare to traditional stochastic gradient, a smaller variance of the estimated gradients near the minimizer gives faster convergence rate. 
+        Major examples of VRMs include SVRG by Xiao, Zhang \cite{xiao_proximal_2014}, Finito by Defazio et al.
+\cite{defazio_finito_2014}, SAG by Schmidt et al.
+\cite{schmidt_minimizing_2017}, and SAGA by \cite{defazio_saga_2014}.
         \todoinline{\noindent
@@
             \begin{enumerate}
-                \item 
+                \item[$\blacksquare$] SVRG: Proximal stochastic gradient with progressive variance reduction. 
+                \item[$\blacksquare$] Finito: A faster, permutable incremental gradient method for big data problems
+                \item[$\blacksquare$] SAG: Minimizing finite sums with the stochastic average gradient
+                \item[$\blacksquare$] SAGA: A fast incremental gradient method with support for non-strongly convex composite objectives. 
             \end{enumerate}

### 2025-01-08 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
     \end{remark}
+    \textbf{Organizations now follow}. 
     \subsection{Introduction to Catalyst}
@@
         The class of variance reduced method is vast, but to use the most relevant feature of this class of first order method is that they are stochastic method that is not slower than full gradient descent in complexity.
-        \todo{
-            $\blacksquare$ Add the bib for Mark Schmidt introductory paper RV methods.  
-            \\ $\square$ Cite it. 
-        }{\hl{See Gower's guide}} for more information on variance reduced methods in machine learning. 
+        See Gower's guide \cite{gower_variance-reduced_2020} for more information on variance reduced methods in machine learning. 
         \par
         In brief, a variance reduce method (VRM) is a type of 
-        \todo{
-            $\blacksquare$ Add old Bertsekas's paper on incremental methods here. Paper: ``Incremental gradient, subgradient, and proximal methods for convex optimization: A survey''. 
-            \\
-            $\square$ Cite them. 
-        }
-        {\hl{incremental methods}} \cite{bertsekas_incremental_2011,bertsekas_incremental_2017}
+        incremental methods
         for solving a large sum problem: $F(x) = \sum_{i = 1}^{N} f_i(x)$ in machine learning.
-        It can be deterministic, or stochastic. 
+        See Bertsekas's surveys \cite{bertsekas_incremental_2011,bertsekas_incremental_2017} on incremental method for more context. 
+        VRM can be deterministic, or stochastic. 
         When it's stochastic, the theories focuses on the expected optimality gap: $\mathbb E[F(x_k) - F^*]$, for the inner and outer loop. 
@@
         The idea of VRM is to stabilize the estimate of gradient using information of the gradient (which can be estimated, or exact) from all or a subset at previous iterates. 
-        In each iteration, only the gradient of a few samples are accessed and uses simple calculations from previously stored gradient to attain overall better complexity.
+        In each iteration, the gradient of just a few samples are used with simple calculations to attain better complexity than full gradient descent. 
         Compare to traditional stochastic gradient, a smaller variance of the estimated gradients near the minimizer gives faster convergence rate. 
@@
 \cite{schmidt_minimizing_2017}, and SAGA by \cite{defazio_saga_2014}.
-        \todoinline{\noindent
-            We can then list some citations and references to commonly known variance reduced method here. 
-            Let's list some here then. 
-            \begin{enumerate}
-                \item[$\blacksquare$] SVRG: Proximal stochastic gradient with progressive variance reduction. 
-                \item[$\blacksquare$] Finito: A faster, permutable incremental gradient method for big data problems
-                \item[$\blacksquare$] SAG: Minimizing finite sums with the stochastic average gradient
-                \item[$\blacksquare$] SAGA: A fast incremental gradient method with support for non-strongly convex composite objectives. 
-            \end{enumerate}
-        }
-        \par
-        The parts coming will introduce the algorithms, explain its key innovations. 
+        \par
+        The parts coming introduce the Catalyst algorithms and its key innovations. 
         The last section reviews recent literatures on the topics and gives potential future works. 
@@
             This lemma is instrumental for deriving an inexact variant of the estimating sequence $\phi_k^* \ge F(x_k) + \xi_k$. 
-            The convergence proof (outer and inner loop together) from Lin was inspired by 
-            \todo{\noindent
-                $\blacksquare$ Add bib, the paper is 
-                \\
-                $\square$ Cite. 
-            }{\hl{Schmidt's Inexact Proximal Gradient method. }} 
-            The technique of estimating sequence as defined back in Definition \ref{def:nes-est-seq} did the heavy lifting, but it results in depressingly long proof making it unsuitable for exposition here.
+            The convergence proof (outer and inner loop together) from Lin was inspired by Schmidt's Inexact Proximal Gradient method \cite{schmidt_convergence_2011}. 
+            The technique of estimating sequence introduced back in Definition \ref{def:nes-est-seq} did the heavy lifting, but it results in depressingly long proof making it unsuitable for exposition here.
             Significant pieces of theoretical innovations are covered in details in our most recent Fall Winter 2024 MATH 590 report. 
@@
             \end{align*}
-            \par 
+            These results are instrumental to prove the convergence of $\mathbb M$ and giving convergence claim of $\mathbb A$ under certain assumption on $(\delta_k)_{k \ge 0}, (\epsilon_k)_{k \ge0}$.
             For a more general development of characterizations of inexact oracles that is more comprehensive and rigorous, see 
-            \todo{
-                $\square$ Add paper: ``First-order methods of smooth convex optimization with inexact oracle'' \\
-                $\square$ Cite them. 
-            }
-            {\hl{Devolder et al.}}
-            Their works were earlier and a Nesterov accelerated algorithm using estimating sequence and inexact oracles was derived. 
-            These results are instrumental to prove the convergence of $\mathbb M$ and giving convergence claim of $\mathbb A$ under certain assumption on $(\delta_k)_{k \ge 0}, (\epsilon_k)_{k \ge0}$.
-            \par
-            Finally, besides Definition \ref{def:catalyst-termination-c1}, \ref{def:catalyst-termination-c2}, there is the ``Fixed Budget" termination criterion. 
-            It terminates $\mathbb M$ after a fixed number of iteration. 
+            Devolder et al. \cite{devolder_first-order_2014}. 
+            It's discusses a Nesterov accelerated algorithm using estimating sequence with inexact oracles. 
+            \par
+            Besides Definition \ref{def:catalyst-termination-c1}, \ref{def:catalyst-termination-c2}, the ``Fixed Budget" termination criterion terminates $\mathbb M$ after a fixed number of iteration given accuracy $\epsilon_k$.
             Criterion C1 used to prove the overall complexity in Lin et al. \cite{lin_universal_2015}, but the bound is deliberately loose to allow generality, making it extremely impractical. 
@@
             The theorems and commentaries that follow will illustrate. 
-            \begin{definition}[A better Catalyst Acceleration]\label{def:catalyst-relative}
+            \begin{definition}[Catalyst Acceleration with relative inexactness]\label{def:catalyst-relative}
                 Suppose that $F$ is a $\mu \ge 0$ strongly smooth under Assumption \ref{ass:catalyst1}. 
@@
             The key improvement here compared to using absolute inexactness for $\mathbb M$ as stated by Theorem \ref{thm:err-seq-outer-s-cnvx}, \ref{thm:erro-seq-outer-cnvx} is that $(\delta_k)_{k \ge0}$ doesn't require knowledge on $F^*$.
-            This innocent detail helps to develop a nonconvex variant of Catalyst call 4WD Catalyst which is the focus of the paper by Paguette \cite{paquette_catalyst_2018}. 
+            This innocent detail helps to develop a nonconvex variant of Catalyst call 4WD Catalyst which is the focus of the paper by Paquette \cite{paquette_catalyst_2018}. 
             Corollary 16 in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018} gives complexity for $\mathbb M$ Using termination criterion C2 with a warm start specialized for $C2$. 

### 2025-01-09 Notebook LaTEX/Proposal/main.tex
>w<, a lot of changes

@@
     \par
-    Section \ref{sec:catalyst} are results of literatures review in MATH 590. 
+    Section \ref{sec:catalyst} complements report completed for MATH 590 Fall Winter 2024. 
     \todo{
@@
     }
-    {\hl{It's based on a series of papers}} in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
-    We will point out potential future direction of research of Catalyst acceleration. 
-    \par
-    Section \ref{sec:inexact-prox}, \ref{sec:nes-acc-ncnvx} preview literatures in nonsmooth optimization frontier research where progress and impacts can be made.  
+    {\hl{It's based on a series of recent papers}} \cite{lin_universal_2015,lin_catalyst_2018,paquette_catalyst_2018} about Catalyst Meta Acceleration for First Order Variance Reduced Methods. 
+    The end of Section \ref{sec:catalyst} points out potential future direction of research of Catalyst Acceleration. 
+    % \par
+    % Section \ref{sec:inexact-prox}, \ref{sec:nes-acc-ncnvx} preview literatures in nonsmooth optimization frontier research where progress and impacts can be made.  
     \subsection{Theme of the research}
         This section specifies a theme of the research in this proposal. 
-        Out first objective is to explore the Goldilocks zones between these topics: theories of variational analysis, design of continuous optimization algorithm and applications in sciences, engineering, and statistics.
-        Our second objective is to identify the ``chemistry'' occurring between properties of functions and the designs of continuous optimizations algorithm and how it impacts the convergence and behaviors of the algorithms.
+        Firstly, we explore the Goldilocks zones between these topics: Nesterov's acceleration, algorithms with inexact evaluation of the proximal point operator, and applications.  
+        In doing so, we identify the ``chemistry'' between various properties of functions and the affect it has on the designs/behaviors of first order algorithm for continuous optimization.
 
@@
     \subsection{Nesterov's estimating sequence technique}
-        The method of Nesterov's estimating sequence for accelerated gradient method, and their nonsmooth counterparts assumes a convex function $F: \RR^n \rightarrow \overline{\RR}$. 
+        The method of Nesterov's estimating was used for deriving accelerated gradient method, and their nonsmooth counterparts assuming function $F: \RR^n \rightarrow \overline{\RR}$ is convex and Lipschitz smooth.
+        We emphasize that the techniques derives the algorithm as well as proving its convergence rate. 
         The estimating sequence is a technique searching for candidate algorithm with extrapolated momentum, and proving their convergence rate if possible. 
@@
         The method is widespread in the literatures, and the ideas behind it are tremendously useful. 
-        \todo{
-            $\blacksquare$ Add Guler's 1992 new proximal point paper. 
-            \\ $\blacksquare$ Cite it.}
-        {\hl{Güler}} \cite{guler_new_1992}
-        used the method to design an accelerated proximal point method, which inspired and served as the foundation of Catalyst Acceleration for variance reduced method in machine learning. 
-        \todo{
-            $\blacksquare$ Add the paper: ``Accelerating the cubic regularization of Newton’s method on convex
-            problems''\\ 
-            $\blacksquare$ Cite it.
-        }
-        {\hl{Nesterov}} \cite{nesterov_accelerating_2008}
-        also used the technique to design an accelerated cubic regularized Newton's method. 
-        In 
-        \todo{
-            $\blacksquare$ Cite it. 
-        }
-        \hl{(6.1.19) of Nesterov's book }\cite{nesterov_lectures_2018}, 
-        it's also used to derive a method of accelerated mirror descent. 
-        And finally, 
-        \todo{
-            $\blacksquare$ Add paper: ``Accelerated regularized newton methods for minimizing composite convex functions'' \\ 
-            $\blacksquare$ Cite it. 
-        }
-        {\hl{Geovani N. et al}} \cite{grapiglia_accelerated_2019}
-        used the technique to derive an accelerated Newton's method for convex composite objective function. 
+        Güler \cite{guler_new_1992} used the method to design an accelerated proximal point method, which was the foundation of Catalyst Acceleration for variance reduced method in machine learning. 
+        Nesterov \cite{nesterov_accelerating_2008} used the technique to design an accelerated cubic regularized Newton's method. 
+        In (6.1.19) of Nesterov's book \cite{nesterov_lectures_2018}, it's used to derive a method of accelerated mirror descent. 
+        Finally, Geovani N. et al \cite{grapiglia_accelerated_2019} used it to derive an accelerated Newton's method for convex composite objective function. 
         \par
@@
 \section{Catalyst accelerations and future works}\label{sec:catalyst}
-    In this section, we assume that $F: \RR^n \rightarrow \overline \RR$ is a convex function. 
-    This section introduces the ideas in Catalyst acceleration, elucidate the focuses in the research, and then discuss future research direction at the end. 
+    Section \ref{ssec:catalyst-intro} gives the main ideas behind the Catalyst Acceleration Framework. 
+    It follows Lin et al.'s first paper \cite{lin_universal_2015} on Catalyst Acceleration, the key innovations and what it can be used for together with a sketch over the complexity analysis of the entire frameworks.
+    Section \ref{ssec:catalyst-second-paper} introduces Lin et al.'s second paper \cite{lin_catalyst_2018} on Catalyst which considers an improved relative error condition stated in \ref{def:catalyst-termination-c2} that bounds the inexactness of the gradient on the Moreau Envelope.
+    This condition not only improves the overall complexity, but it also hints the development of nonconvex gradient based 4WD Catalyst by Paquette \cite{paquette_catalyst_2018}.
+
     \begin{assumption}\label{ass:catalyst1}
@@
     \textbf{Organizations now follow}.
-    \subsection{Introduction to Catalyst}
+
+    \subsection{Introduction to Catalyst}\label{ssec:catalyst-intro}
         Inspired by accelerated proximal point method from Güler \cite{guler_new_1992}, and inexact proximal point method of Rockafellar 1976 \cite{rockafellar_monotone_1976}, Lin \cite{lin_universal_2015} proposed a generic method taking inspirations from the convergence claims of Accelerated proximal point method to accelerated the convergence rate of first order variance reduced incremental method.
@@
         The idea of VRM is to stabilize the estimate of gradient using information of the gradient (which can be estimated, or exact) from all or a subset at previous iterates. 
-        In each iteration, the gradient of just a few samples are used with simple calculations to attain better complexity than full gradient descent. 
+        In each iteration, the gradient of just a few samples are used to attain a new estimate of the gradient with minimum additional calculations.
+It gives better complexity than full gradient descent.
         Compare to traditional stochastic gradient, a smaller variance of the estimated gradients near the minimizer gives faster convergence rate. 
@@
         \par
-        The parts coming introduce the Catalyst algorithms and its key innovations. 
+        The coming parts introduce the Catalyst algorithms and its key innovations. 
         The last section reviews recent literatures on the topics and gives potential future works. 
@@
 
-    \subsection{The second Catalyst Acceleration paper}
+    \subsection{The second Catalyst Acceleration paper}\label{ssec:catalyst-second-paper}
         This section discusses major contents in Lin's second Catalyst paper \cite{lin_catalyst_2018}. 
@@
             It's important to note that the upper complexity bounds are much better, and it doesn't require bounded level set compared to Theorem \ref{prop:inner-loop-complexity-cnvx}.         
-    \subsection{Potential future research}
+    \subsection{Potential future research}\label{ssec:catalyst-future}
         Now, we have enough context to understand the potential future directions of research regarding the Catalyst Acceleration framework. 
-
-\section{Methods of inexact proximal point}\label{sec:inexact-prox}
-    Content of this section is primarily based on Khanh et al. \cite{duy_khanh_inexact_2023} on inexact proximal method for weakly convex functions.
-
-\section{Nestrov's acceleration in the nonconvex case}\label{sec:nes-acc-ncnvx}
+        \subsubsection{Necoara et al.'s comments on Catalyst Acceleration}
+        \subsubsection{Our ideas on future works of Catalyst Acceleration}
+
+% \section{Methods of inexact proximal point}\label{sec:inexact-prox}
+%     Content of this section is primarily based on Khanh et al. \cite{duy_khanh_inexact_2023} on inexact proximal method for weakly convex functions.
+
+% \section{Nestrov's acceleration in the nonconvex case}\label{sec:nes-acc-ncnvx}
     % The behavior of Nesterov's acceleration for function that are nonconvex are the holy grail and the absolute frontier. 

### 2025-01-09 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
 
-        % \subsubsection{Logistic regression}
+    \subsection{Future works for R-WAPG}
+        There is one intriguing detail in the burried in the literatures but weren't realized in it. 
+        It has the potential to include more variants of the FISTA algorithms and their convergence proof. 
+        Our future works would be to extend the frameworks and weaken it further while retaining the goal of getting some type of upper bound on the value $F(x_k) - F^*$ and show that there are choices for the momentum parameter $\alpha_k$ such that convergence is possible.
+        \subsubsection{Nesterov's idea of strong convexity transfer}
+        \todoinline{\noindent
+            In terms of theories, it's possible to consider: 
+            \begin{enumerate}
+                \item Nesterov, 2013, ``Gradient methods for minimizing composite functions'', strong convexity transfer. 
+                \item ``An introduction to continuous optimization for imaging'', Algorithm 5, the same thing is there as well. 
+            \end{enumerate}
+        }
+        \subsubsection{Tying up some loose ends}
+        \todoinline{\noindent
+            In terms of practice, we missing convergence rate of Free-RWAPG, and the convergence of the norm of the gradient method for R-WAPG. 
+        }
 
 \section{Catalyst accelerations and future works}\label{sec:catalyst}
-    Section \ref{ssec:catalyst-intro} gives the main ideas behind the Catalyst Acceleration Framework. 
-    It follows Lin et al.'s first paper \cite{lin_universal_2015} on Catalyst Acceleration, the key innovations and what it can be used for together with a sketch over the complexity analysis of the entire frameworks.
-    Section \ref{ssec:catalyst-second-paper} introduces Lin et al.'s second paper \cite{lin_catalyst_2018} on Catalyst which considers an improved relative error condition stated in \ref{def:catalyst-termination-c2} that bounds the inexactness of the gradient on the Moreau Envelope.
-    This condition not only improves the overall complexity, but it also hints the development of nonconvex gradient based 4WD Catalyst by Paquette \cite{paquette_catalyst_2018}.
 
@@
     \textbf{Organizations now follow}. 
+    Section \ref{ssec:catalyst-intro} gives the main ideas behind the Catalyst Acceleration Framework. 
+    It follows Lin et al.'s first paper \cite{lin_universal_2015} on Catalyst Acceleration, the key innovations and what it can be used for together with a sketch over the complexity analysis of the entire frameworks.
+    Section \ref{ssec:catalyst-second-paper} introduces Lin et al.'s second paper \cite{lin_catalyst_2018} on Catalyst which considers an improved relative error condition stated in \ref{def:catalyst-termination-c2} that bounds the inexactness of the gradient on the Moreau Envelope.
+    This condition not only improves the overall complexity, but it also hints the development of nonconvex gradient based 4WD Catalyst by Paquette \cite{paquette_catalyst_2018}.
 
@@
         \subsubsection{Necoara et al.'s comments on Catalyst Acceleration}
+
         \subsubsection{Our ideas on future works of Catalyst Acceleration}

### 2025-01-10 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
                 \end{enumerate}
-        }
-        \subsubsection{Tying up some loose ends}
-        \todoinline{\noindent
-            In terms of practice, we missing convergence rate of Free-RWAPG, and the convergence of the norm of the gradient method for R-WAPG. 
-        }
+                In Nesterov's, take note of Algorithm: Accelerated Method (4.9) and the convergence claim: Theorem 6. 
+            }
+            We consider the case that $F = f + g$ where, $f$ is $L$ Lipschitz smooth, $\mu_f \ge 0$ strongly convex and $g$ is closed convex. 
+            In Nesterov's 2013 paper \cite{nesterov_gradient_2013}, he consider accelerated  minimization problem $\phi = f + \Psi$ with $f$ $L_f$ smooth and $\Psi$ being $\mu_\Psi \ge 0$ strongly convex.
+            \par
+            This detail on itself is not necessarily interesting, since without lost of generality, we can always do the splitting $f + \mu_\Psi/2 \Vert \cdot\Vert^2$ and $\Psi - \mu_\Psi/2\Vert \cdot\Vert^2$ instead so that the smooth part is $\mu_\Psi \ge 0$ strongly convex.
+            It's an interesting detail we should consider because: 
+            \begin{enumerate}
+                \item A strongly convex nonsmooth parts still gives linear convergence by Theorem 6 in Nesterov's 2013 \cite{nesterov_gradient_2013}. 
+                \item The strong convexity constant can be easily estimated via a routine specified as (5.14) in Nesterov 2013 \cite{nesterov_gradient_2013} and the complexity of the estimation is bounded precisely.
+            \end{enumerate}
+            (i) indicates that our theories of R-WAPG is incomplete, since it doesn't predict linear convergence when $g$ is strongly convex. 
+            (ii) indicates that splitting the strongly convex objective so that it's with the proximal operator exposes computational advantage. 
+            \par
+            Furthermore, Nesterov was not the only person who thought about it.
+            In 
+            Chambolle, Pock \cite{chambolle_introduction_2016} Algorithm 5, several variants of the FISTA algorithm were captured together into one formulation, and it assumes that $F = f + g$ where $f, g$ has strong convexity index $\mu_f \ge 0, \mu_g \ge 0$, and $F$ is $\mu := \mu_f + \mu_g \ge 0$ strongly convex.
+            It's not trivial on how the R-WAPG framework can be modified to include strong convexity presenting in the nonsmooth part.
+
+        % \subsubsection{Tying up some loose ends}
+        %     \todoinline{\noindent
+        %         In terms of practice, we are missing convergence rate of Free-RWAPG, and the convergence of the norm of the gradient method for R-WAPG. 
+        %     }
 
@@
         \subsubsection{Necoara et al.'s comments on Catalyst Acceleration}
-
+            Necoara et al. \cite{necoara_linear_2019} considered optimization problem $f^* = \min_{x \in X} f(x)$ with $f: X \subseteq \RR^n \rightarrow \RR$ and $X$ closed and convex. 
+            They extended the linear convergence results of accelerated gradient method such as Nesterov's acceleration with proximal gradient into a wider setting than strong convexity. 
+            \par
+            As a secondary objective, they introduced and stated the relations between several weakened characterizations of strong convexity on a closed convex set. 
+            Definition 1, 2, 3, 4, 5, introduced the ideas of: Quasi-strong convexity, Quadratic under approximation, Quadratic gradient growth, quadratic functional growth (recall that it was stated as a consequence of strong convexity in Lemma \ref{lemma:q-growth}), and Global error bound conditions.
+            \par
+            The content of their paper is very in-depth hence for our interests, we focus on their comments on the first Catalyst paper by Lin et al. \cite{lin_universal_2015}. 
+            They said, and here we quote: 
+            \begin{quote}
+                It is also worth to investigate the complexity bounds obtained when wrapping linearly-convergent algorithms under the proposed conditions in an outer-loop using a generic acceleration scheme such as Catalyst \cite{lin_universal_2015}.
+This would allow to extend to non-strongly convex settings a wide range of incremental optimization algorithms designed for large finite-sum problems arising in machine learning and statistics.
+            \end{quote}
+            We note that, their idea of extension can be applied to inner loop $\mathbb M$, or out loop $\mathbb A$, either, or both. 
         \subsubsection{Our ideas on future works of Catalyst Acceleration}
+            One intriguingly detail in the Catalyst framework eluded us. 
+            It may not be obvious to the readers, so we shall elucidate. 
+            \par
+            The concern starts by considering the necessary assumption in VRMs. 
+            Defazio et al.\cite{defazio_saga_2014} SAGA, Finito et al.
+\cite{defazio_finito_2014} requires Lipschitz continuous gradient on each individual $f_i$ in the objective function $F = \sum_{i = 1}^n f_i$.
+            Schimdt et al. \cite{schmidt_minimizing_2017} also requires Lipscthiz smoothness for the non-smooth part of a composite objective. 
+            Xiao, Zhang, SVRG \cite{xiao_proximal_2014} requires Lipscthiz gradient assumption as well. 
+            This seemingly raises a crucial question: ``Where does the Lipschitz continuous gradient of the smooth part make its presence in the Catalyst Framework?''
 

### 2025-01-10 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

@@
 \end{abstract}
-
+\todo{Remember to update these subject classificiations. }
+{
     \noindent{\bfseries 2010 Mathematics Subject Classification:}
@@
     \noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method. 
+}
 \section{Introduction}
@@
             The prior works' section is too little, it requires some expansion in the future for sure.
+            \begin{enumerate}
+                \item Paper: ``An introduction to continuous optimization for imaging'', Chambolle, Pock. 
+            \end{enumerate}
+
         }

### 2025-01-10 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
     \subsection{Future works for R-WAPG}
-        There is one intriguing detail in the burried in the literatures but weren't realized in it. 
+        There is one intriguing detail buried in literatures but weren't realized in it. 
         It has the potential to include more variants of the FISTA algorithms and their convergence proof. 
@@
         \subsubsection{Nesterov's idea of strong convexity transfer}
-            \todoinline{\noindent
-                In terms of theories, it's possible to consider: 
-                \begin{enumerate}
-                    \item Nesterov, 2013, ``Gradient methods for minimizing composite functions'', strong convexity transfer. 
-                    \item ``An introduction to continuous optimization for imaging'', Algorithm 5, the same thing is there as well. 
-                \end{enumerate}
-                In Nesterov's, take note of Algorithm: Accelerated Method (4.9) and the convergence claim: Theorem 6. 
-            }
             We consider the case that $F = f + g$ where, $f$ is $L$ Lipschitz smooth, $\mu_f \ge 0$ strongly convex and $g$ is closed convex. 
-            In Nesterov's 2013 paper \cite{nesterov_gradient_2013}, he consider accelerated  minimization problem $\phi = f + \Psi$ with $f$ $L_f$ smooth and $\Psi$ being $\mu_\Psi \ge 0$ strongly convex.
+            In Nesterov's 2013 paper \cite{nesterov_gradient_2013}, he considers accelerated  minimization problem $\phi = f + \Psi$ with $f$ $L_f$ smooth and $\Psi$ being $\mu_\Psi \ge 0$ strongly convex.
             \par
@@
             Chambolle, Pock \cite{chambolle_introduction_2016} Algorithm 5, several variants of the FISTA algorithm were captured together into one formulation, and it assumes that $F = f + g$ where $f, g$ has strong convexity index $\mu_f \ge 0, \mu_g \ge 0$, and $F$ is $\mu := \mu_f + \mu_g \ge 0$ strongly convex.
-            It's not trivial on how the R-WAPG framework can be modified to include strong convexity presenting in the nonsmooth part.
 
@@
             These results are instrumental to prove the convergence of $\mathbb M$ and giving convergence claim of $\mathbb A$ under certain assumption on $(\delta_k)_{k \ge 0}, (\epsilon_k)_{k \ge0}$.
-            For a more general development of characterizations of inexact oracles that is more comprehensive and rigorous, see 
-            Devolder et al. \cite{devolder_first-order_2014}. 
+            For a more general development of characterizations of inexact oracles that is more comprehensive and rigorous, see Devolder et al. \cite{devolder_first-order_2014}. 
             It's discusses a Nesterov accelerated algorithm using estimating sequence with inexact oracles. 
@@
 \cite{defazio_finito_2014} requires Lipschitz continuous gradient on each individual $f_i$ in the objective function $F = \sum_{i = 1}^n f_i$.
-            Schimdt et al. \cite{schmidt_minimizing_2017} also requires Lipscthiz smoothness for the non-smooth part of a composite objective. 
-            Xiao, Zhang, SVRG \cite{xiao_proximal_2014} requires Lipscthiz gradient assumption as well. 
+            Schmidt et al. \cite{schmidt_minimizing_2017} also requires Lipschitz smoothness for the non-smooth part of a composite objective. 
+            Xiao, Zhang, SVRG \cite{xiao_proximal_2014} requires Lipschitz gradient assumption as well. 
             This seemingly raises a crucial question: ``Where does the Lipschitz continuous gradient of the smooth part make its presence in the Catalyst Framework?''
+            \par
+            A careful reader should realize that Assumption \ref{ass:linear-convergence-inner-loop} encapsulates the Lipschitz smoothness assumption of VRMs. 
+            Furthermore, such an assumption is optimistic for the complexity of $\mathbb M$. 
+            Recall that with Lipschitz smoothness and strong convexity, a lower bound of exponential rate of convergence is established by Theorem 2.1.13 in Nesterov's book \cite{nesterov_lectures_2018}.
+            Removing the smoothness assumption for $\mathbb M$, the lower bound on convergence rate of any first order algorithm becomes $\mathcal O(1/k)$ by Theorem 3.2.5 for nonsmooth function that is strongly convex.
+            \par
+            From a complexity theoretical point of view, Catalyst acceleration didn't attempt at narrowing the lower complexity bound functions that are convex and nonsmooth and lack of any exact proximal oracle.
+            It is absolutely possible that, for any black box nonsmooth optimization problem, the same lower bound convergence rate $\mathcal O\left(1/\sqrt{k}\right)$ as stated in Theorem 3.2.1 in Nesterov's book \cite{nesterov_lectures_2018}.
+            Unfortunately it is absolutely nontrivial to see that is true because $\mathbb A$ optimizes Moreau Envelope $\mathcal M^*_{\kappa^{-1}F}(x)$ through inexact evaluation and the Moreau Envelope has Lipschitz gradient, for $\mathbb A$ Theorem 3.2.1 doesn't apply.
+            Whatever the true answer is, it's not obvious. 
+            So, here is what we think is worth investigating: 
+            \begin{quotation}
+                What if Assumption \ref{ass:linear-convergence-inner-loop} is false in the Catalyst Acceleration Framework? 
+                Would there exists any kind of regularization parameters $(\kappa_k)_{k \ge 0}$, error sequence $\epsilon_k$ such that the overall complexity still retains convergence rate equals or faster than $\mathcal O(1/\sqrt{k})$?
+            \end{quotation}
+            Nobody has yet answered the question in the literature, but a brief searched showed that in Nesterov 2014 \cite{nesterov_universal_2015}, he considers the method of accelerated gradient for function with Holder continuous gradient.
+            If anything, there are some insight to be gained about Catalyst on this question on this work of his. 
+            It remains to be seemed why this detail is neglected when developing the Catalyst Acceleration framework. 
+            If the answer is that it can be faster than the lower bound, then we had extended the Catalyst Framework, otherwise, it leads to the unintuitive result that lower bound $\mathcal O(1/\sqrt{k})$ still holds.
 
@@
 
-\section{Using PostGreSQL and big data analytic method for species classification on Sentinel-2 Satellite remote sensing imagery}
+% \section{Using PostGreSQL and big data analytic method for species classification on Sentinel-2 Satellite remote sensing imagery}
 

### 2025-01-10 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@
         \subsubsection{Our ideas on future works of Catalyst Acceleration}
-            One intriguingly detail in the Catalyst framework eluded us. 
+            One intriguing detail in the Catalyst framework eluded us. 
             It may not be obvious to the readers, so we shall elucidate. 
@@
             \par
-            From a complexity theoretical point of view, Catalyst acceleration didn't attempt at narrowing the lower complexity bound functions that are convex and nonsmooth and lack of any exact proximal oracle.
-            It is absolutely possible that, for any black box nonsmooth optimization problem, the same lower bound convergence rate $\mathcal O\left(1/\sqrt{k}\right)$ as stated in Theorem 3.2.1 in Nesterov's book \cite{nesterov_lectures_2018}.
-            Unfortunately it is absolutely nontrivial to see that is true because $\mathbb A$ optimizes Moreau Envelope $\mathcal M^*_{\kappa^{-1}F}(x)$ through inexact evaluation and the Moreau Envelope has Lipschitz gradient, for $\mathbb A$ Theorem 3.2.1 doesn't apply.
+            From a complexity theoretical point of view, Catalyst acceleration didn't attempt at narrowing the lower complexity bound bounds for functions that are convex and nonsmooth and lack of any exact proximal oracle.
+            It is absolutely possible that, for any black box nonsmooth optimization problem, the same lower bound convergence rate $\mathcal O\left(1/\sqrt{k}\right)$ as stated in Theorem 3.2.1 in Nesterov's book \cite{nesterov_lectures_2018} is true for Catalyst.
+            Unfortunately it is absolutely nontrivial to see that is true because $\mathbb A$ optimizes Moreau Envelope $\mathcal M^*_{\kappa^{-1}F}(x)$ through inexact evaluation and the Moreau Envelope has Lipschitz gradient.
+            For $\mathbb A$ Theorem 3.2.1 doesn't apply. 
             Whatever the true answer is, it's not obvious. 

### 2025-01-10 Notebook LaTEX/Proposal/main.tex
>w<, todonotes removed

@@
     Section \ref{sec:catalyst} complements report completed for MATH 590 Fall Winter 2024. 
-    \todo{
-        $\blacksquare$ Add Lin's papers and Paquette's papers.
-    }
-    {\hl{It's based on a series of recent papers}} \cite{lin_universal_2015,lin_catalyst_2018,paquette_catalyst_2018} about Catalyst Meta Acceleration for First Order Variance Reduced Methods. 
+    It's based on a series of recent papers \cite{lin_universal_2015,lin_catalyst_2018,paquette_catalyst_2018} about Catalyst Meta Acceleration for First Order Variance Reduced Methods. 
     The end of Section \ref{sec:catalyst} points out potential future direction of research of Catalyst Acceleration. 
@@
             Definition taken from Definition 4.3.1 from 
-            \todo{$\blacksquare$ Add bib \\ $\blacksquare$ Cite. }
-            \hl{Pang, Cui's book} \cite{ying_modern_2021}
+            Pang, Cui's book \cite{ying_modern_2021}
         \end{remark}
@@
             Definition taken from Definition 4.3.1 from
-            \todo{$\blacksquare$ Add bib \\ $\blacksquare$ Cite. }
-            {\hl{Pang, Cui's book}} \cite{ying_modern_2021}
+            Pang, Cui's book \cite{ying_modern_2021}
         \end{remark}
@@
     One of the prime candidate for solving the optimization problem is the Nesterov's Accelerated Gradient methods (NAG) finds extensions for nonsmooth function through the proximal gradient operator.
-    \todo{
-        $\blacksquare$ Add Nesterov's original paper. \\ 
-        $\blacksquare$ Cite it.  
-    }
-    {\hl{Proposed back in 1983 the original Nesterov's acceleration method}} \cite{nesterov_method_1983}
+    Proposed back in 1983 the original Nesterov's acceleration method \cite{nesterov_method_1983}
     which uses the previous iterates to extrapolate the next iterate to evaluate the gradient. 
     It's well known that if minimizer $x^*$ exists for $F$, the method achieves a $\mathcal O(1/k^2)$ convergence rate on the objective value $F(x_k)$.     
-    \todo{
-        $\blacksquare$ Add Nesterov's new book. 
-        \\ $\blacksquare$ Cite it.
-    }
-    {\hl{This convergence rate is considered optimal for all class of $L$ Lipschitz smooth convex function }}\cite{nesterov_lectures_2018}. 
+    This convergence rate is considered optimal for all class of $L$ Lipschitz smooth convex function \cite{nesterov_lectures_2018}. 
     The convergence rate guarantee is faster than $\mathcal O(1/k)$ exhibited by gradient descent. 
@@
     Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
-    \todo{
-        $\blacksquare$ Add Beck 2009 FISTA original paper. \\
-        $\blacksquare$ Cite it.
-    }
-    {\hl{Beck and Toubelle}} \cite{beck_fast_2009}
+    Beck and Toubelle \cite{beck_fast_2009}
     mitigated the issue by restarting and showed that it still has a $\mathcal O(1/k^2)$ convergence rate, and it performs better empirically. 
-    \todo{
-        $\blacksquare$ Add Necoara linear convergence 
-        \\ 
-        $\blacksquare$ Add Aujol 2024 Parameter free FISTA restart. 
-        \\ 
-        $\blacksquare$ Cite Section 5.2.2 for the former, cite the entirety for the latter. 
-    }
-    {\hl{See} (5.2.2) Necoara et al. \cite{necoara_linear_2019} and Aujol et al. \cite{aujol_parameter-free_2024}}
+    See (5.2.2) Necoara et al. \cite{necoara_linear_2019} and Aujol et al. \cite{aujol_parameter-free_2024}
     and references within for recent advancements in restarting accelerated proximal gradient algorithm.
@@
     As introduced previously, in 
-    \todo{
-        $\blacksquare$ Add Neol J. Walkington's ``Nesterov's Method for Convex  Optimization''. \\ 
-        $\blacksquare$ Cite it. 
-    }
-    {\hl{Walkington's writing}} \cite{noel_nesterovs_nodate}, 
+    Walkington's writing \cite{noel_nesterovs_nodate}, 
     he showed that there exists a variant of the Nesterov's accelerated gradient method that achieved a linear convergence rate of $\mathcal O((1 - \sqrt{\kappa})^k)$ where $\kappa = \mu/L$. 
@@
     However, this variant has a fixed momentum parameter $\theta_{k + 1} = (\sqrt{\kappa} - 1)(\sqrt{\kappa} + 1)^{-1}$ back in Equation \ref{eqn:nag_example}. 
-    \todo{
-        $\blacksquare$ Add Beck's first order textbook
-        \\ $\blacksquare$ Cite 10.7.7. 
-        \\ $\blacksquare$ Add Nesterov's textbook. 
-        \\ $\blacksquare$ Cite it. }
-    {\hl{
-        The same variant also appears in Beck's book as V-FISTA} \cite[(10.7.7)]{beck_first-order_2017}, and \hl{Nesterov's book as (2.2.22)} \cite{nesterov_lectures_2018}.
-    }
+    The same variant also appears in Beck's book as V-FISTA \cite[(10.7.7)]{beck_first-order_2017}, and \hl{Nesterov's book as (2.2.22)} \cite{nesterov_lectures_2018}.
     \par
     One final Mystery of the algorithm is the convergence of the iterates which also has much to do with the momentum sequence $(\theta_k)_{k\ge 0}$ displayed in Equation \ref{eqn:nag_example}. 
-    \todo{
-        $\blacksquare$ Add paper: ``On the convergence of the iterates of the...''
-        \\ 
-        $\blacksquare$ Cite them. }
-    {\hl{Chambolle, Dossal}} \cite{chambolle_convergence_2015}
+    Chambolle, Dossal \cite{chambolle_convergence_2015}
     showed that by choosing sequence $(t_k)_{k \ge 1}$ to be $t_k = (n + a - 1)/a$ where $a > 2$ instead would give $(x_k)_{k \ge 0}$ weak convergence in Hilbert space. 
@@
         Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in 
-        \todo{
-            $\blacksquare$ Add ``On the convergence of the iterates of...'' \\ $\blacksquare$ Cite them.}
-        {\hl{Chambolle, Dossal}} \cite{chambolle_convergence_2015},
-        and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}. 
-        When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by in 
-        \todo{
-            $\blacksquare$ Add beck's original FISTA Paper. 
-            \\$\blacksquare$ Cite it.
-        }
-        {\hl{Beck}} \cite{beck_fast_2009}.
+        Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}. 
+        When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by in Beck \cite{beck_fast_2009}.
         If $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
@@
         Section \ref{ssec:describe-variants-with-rwapg} gives characterizations of specific R-WAPG sequence that leads to convergence of the R-WAPG algorithm in terms of the optimality gap. 
-        The section also identifies specific instance of permissible R-WAPG sequences where it fits with the FISTA, V-FISTA, and the algorithm proposed by 
-        \todo{
-            $\blacksquare$ Cite the Chambolle, Dossal 2015 paper here again. 
-        }
-        {\hl{Chambolle Dossal}} \cite{chambolle_convergence_2015}. 
+        The section also identifies specific instance of permissible R-WAPG sequences where it fits with the FISTA, V-FISTA, and the algorithm proposed by Chambolle Dossal \cite{chambolle_convergence_2015}.
         Section \ref{sec:free-rwapg} provides Algorithm \ref{alg:free-rwapg} (Free R-WAPG) which is a parameter free alternative to accelerated proximal gradient method formulated using the R-WAPG we proposed.
@@
     \subsection{Building Blocks of R-WAPG}\label{ssec:building-block-rwapg}
-        Definition\ref{def:stepwise-wapg} describes the procedures of generating the iterates $(v_{k + 1}, x_{k + 1})$ given any $(v_k, x_k)$ and parameter $\alpha_k \in (0, 1), \gamma_k > 0$. 
+        Definition \ref{def:stepwise-wapg} describes the procedures of generating the iterates $(v_{k + 1}, x_{k + 1})$ given any $(v_k, x_k)$ and parameter $\alpha_k \in (0, 1), \gamma_k > 0$. 
         Proposition \ref{prop:stepwise-lyapunov} gives an inequality instrumental to the convergence rate analysis, with the same assumption as the definition.
@@
         Propositions \ref{prop:wapg-first-equivalent-repr}, \ref{prop:wagp-st-form} and \ref{prop:r-wapg-momentum-repr} states the equivalences between the forms and the sufficient conditions for initial conditions of $x_1, v_1$ such equivalence holds.
-        \todo{$\blacksquare$ Add and explain this part. }{\hl{
         The remarks of the definitions identifies specific instances in the literatures where the Accelerated Proximal Gradient method were presented under this specific form. 
-        }}
         \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
@@
             The closest algorithm that fits the form but with $\mu = 0$ is Chapter 12 of 
-            \todo{
-                $\blacksquare$ Add them \\ 
-                $\blacksquare$ Cite them. 
-            }
-            {\hl{in Ryu and Yin's Book} \cite{ryu_large-scale_2022}}, 
-            right after Theorem 17. 
+            in Ryu and Yin's Book \cite{ryu_large-scale_2022}, right after Theorem 17. 
             We created this form which makes the math that follows simpler. 
@@
             The term ``Method of Similar Triangle" was used for Algorithm (6.1.19) in Nesterov's book \cite{nesterov_lectures_2018}, but without the necessary graphical illustrations to clarify it. 
-            Finally, a similar triangle for formulation of FISTA can be found in Equation (2), (3), (4) in 
-            \todo{$\blacksquare$ Cite Chambolle Dossal 2015 again. }
-            \cite{chambolle_convergence_2015}. 
+            Finally, a similar triangle for formulation of FISTA can be found in Equation (2), (3), (4) in \cite{chambolle_convergence_2015}. 
             To see graphical visualization on why such term is used to describe the APG algorithm in the literatures, see 
-            \todo{
-                $\blacksquare$ Add these. $\blacksquare$ Cite these. 
-            }
-            {(3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}}. 
+            (3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}. 
         \end{remark}
@@
         The lemma also provides a simplified convergence claim using the R-WAPG sequence on Proposition \ref{prop:wagp-convergence}. 
-        Theorem \ref{thm:r-wapg-on-cham-doss} stated that the sequences given in  
-        \todo{$\blacksquare$ Cite this paper again here. }
-        {\hl{Chambolle, Dossal's}}
+        Theorem \ref{thm:r-wapg-on-cham-doss} stated that the sequences given in Chambolle, Dossal's
         paper \cite{chambolle_convergence_2015} indeed is an instance of R-WAPG sequence, along with that, it indeed attains a convergence rate $\mathcal O(1/k^2)$. 
         \par 
-
         \begin{lemma}[R-WAPG sequences as inverted FISTA sequence]\label{lemma:inverted-fista-seq}
@@
         selection operator) LASSO problem proposed by 
-        \todo{
-            $\blacksquare$ Add reference ``Regression shrinkage and selection via the Lasso''
-            \\ $\blacksquare$ Cite it. 
-        }{\hl{Tibshirani}} \cite{tibshirani_regression_1996}. 
+        Tibshirani \cite{tibshirani_regression_1996}. 
         The problem of LASSO has smooth, nonsmooth additive and the problem is given by: 

### 2025-01-10 Notebook LaTEX/Proposal/main.tex
>w<, sync

@@
     The good news is we have definitive answers for all questions by our own efforts of research. 
-    \todoinline{\noindent
-        $\square$ Change all the organization parts here
-    }
-    Section \ref{sec:unify-nes-acceleration}, \ref{sec:free-rwapg} are our ongoing research which present the answers to the questions. 
-    \par
-    In Section \ref{sec:unify-nes-acceleration}, we proposed the method of ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)'' as the foundation to describe several variants of Accelerated proximal gradient method in the literatures.
+    Section \ref{sec:unify-nes-acceleration}, proposes the method of ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)'' as the foundation to describe several variants of Accelerated proximal gradient method in the literatures.
     The convergence theories of R-WAPG allows us to model convergence of accelerated proximal gradient method where the momentum sequence doesn't strictly follow the conditions presented in the literatures.
@@
     \par
-    In Section \ref{sec:free-rwapg} we propose a practical algorithm that exploits a specific term in the proof of R-WAPG to achieve faster convergence for solving (\ref{eqn:additive-comp-obj}) without knowing parameter $L, \mu$ in prior.
+    Section \ref{sec:free-rwapg} proposes a practical algorithm that exploits a specific term in the proof of R-WAPG to achieve faster convergence for solving (\ref{eqn:additive-comp-obj}) without restarting and knowing parameter $L, \mu$ in prior.
     Results of numerical experiments are presented. 

### 2025-01-11 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes, sync

--- 2025-01-07 Notebook LaTEX/R-WAPG/paper3.tex
@@
     \noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method. 
+}
 \section{Introduction}
-    Suppose we are minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$ for simplicity. 
+    \subsection{Motivations}
+        For simplicity consider minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$ . 
         Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$.
         \par 
-    A good choice of a minimization algorithm is the Nesterov's acceleration scheme which was originally proposed in 1983 \cite{nesterov_method_1983}. 
+        The Nesterov's acceleration scheme which was originally proposed in 1983 \cite{nesterov_method_1983} is a celebrated first order method for solving the minimization problem. 
         Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
@@
         \end{align}\label{eqn:example_algorithm}
-    It's well known that if the minimizer $x^*$ exists, then the optimality gap $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, faster than the gradient descent method which is $\mathcal O(1/k)$, and it's optimal.
-    See Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018}. 
-    However, everything is not sunshine and rainbow because the above scheme is associated with an issue. 
-    When $F$ is $\mu > 0$ strongly convex, the optimality gap $F(x_k) - F(x^*)$ oscillates and converges sub-linearly, making it worse than gradient descent.
+        If the minimizer $x^*$ exists, then the optimality gap $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, a faster rate compared to gradient descent which is $\mathcal O(1/k)$. 
+        It's consider optimal in some sense and see Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018} for details. 
+        However, things are not sunshine and rainbow because the above scheme is associated with the following issue: 
+        If $F$ is $\mu > 0$ strongly convex, the optimality gap $F(x_k) - F(x^*)$ oscillates and converges sub-linearly, making it worse than gradient descent.
 See page 9 of Su et al.
@@
         This issue motivated a vast amount of literatures aims at improving, interpreting, and extending this method. 
-    Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
+        Restarting is a popular solution to address the issue of obtaining better convergence rate when the objective function is strongly convex. 
         Beck and Teboulle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it has an $\mathcal O(1/k^2)$ convergence still, but it performs empirically better. 
         See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm.
-    \par
-    Inspired by prior works and the method of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, we present to you firstly, an alternative to restarting that performs well empirically. 
-    Secondly, a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG). 
-    The R-WAPG has a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(\theta_k)_{k \ge 1}$. 
+
+        \subsection{Prior works}
+            \todoinline{\noindent
+                The prior works' section is too little, it requires some expansion in the future for sure.
+                \begin{enumerate}
+                    \item Paper: ``An introduction to continuous optimization for imaging'', Chambolle, Pock. 
+                \end{enumerate}
+
+            }
+            \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them.}{\hl{Apidopoulos et al. }\cite{apidopoulos_convergence_2018}}
+            showed that a relaxed choice of the sequence that doesn't strictly follow the Nesterov's rule still leads to the convergence of the momentum algorithm. 
+            Besides restarting, \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them.
+}{See Attouch, et al.
+\cite{attouch_first-order_2022}, Maulen and Peypouquet \cite{maulen_speed_2023}} and references within.
+            They present the idea of Hessian Damping for stabilizing the Nesterov's accelerated gradient without/with restarting.
+
+    \subsection{Contents}
+        Inspired specifically by the technique of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, firstly we present a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG) in Section \ref{sec:rwapg-formulation-convergence}.
+        It has the ability to upper bound $F(x_k) - F(x^*)$ for sequences $(t_k)_{k \ge 0}$ that follows a rule much weaker than Nester's update rule. 
+        Secondly, we present an alternative to restarting that performs well empirically inspired by a small detail in the convergence proof of R-WAPG. 
+        In addition to a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(t_k)_{k \ge 1}$. 
         It also has descriptive power to describe several variants of FISTA in the literatures.  
-
-    \subsection{Contributions}
+        \par
         Our contributions are two folds, theoretical and practical. 
@@
         \par
+        \textbf{A summary of our main results follow. } 
         Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''. 
@@
         \end{align*}
-        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}.
+        Our second main result shows that for any $\alpha_k \ge 0$ the choice of sequence $\alpha_k = a/(a + k)$ results in $\rho_k > 1$ for all $k \in \N$ such that R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}.
         When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
@@
         Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}). 
-        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ with minimal computational cost.
+        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ from the Bregman divergence of $f$ with minimal computational cost.
         We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart.
-    \subsection{Prior works}
-        \todoinline{\noindent
-            The prior works' section is too little, it requires some expansion in the future for sure.
-        }
-        One of the most relevant works is by 
-        \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them.}{\hl{Apidopoulos et al. }\cite{apidopoulos_convergence_2018}}. 
-        They showed that a relaxed choice of the sequence that doesn't strictly follow the Nesterov's rule still leads to the convergence of the momentum algorithm. 
-        \par 
-        \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them. }{See Attouch, et al. \cite{attouch_first-order_2022}, Maulen and Peypouquet \cite{maulen_speed_2023}} 
-        and references within for the idea of Hessian Damping for stabilizing the Nesterov's accelerated gradient without/with restarting.
-
-    \subsection{Organizations}
+
         \todoinline{This will be written once most of the contents in the paper are settled. 
         }
+        \par
+        \textbf{Organizations now follow.}
         Section \ref{sec:preliminaries} introduces the proximal gradient inequality which is instrumental to developing the stepwise convergence claim in the next section. 
@@
             \item $g: \RR^n \rightarrow \overline \RR$ is proper, closed and convex. 
-            \item Minimizer exists for the optimization problem: $\min_x \left\lbrace f(x) + g(x)\right\rbrace$. 
+            \item Minimizer exists for the optimization problem: $F^* = \min_x \left\lbrace f(x) + g(x)\right\rbrace$. 
         \end{enumerate}
     \end{assumption}
-    Fix any arbitrary $y \in \RR^n$, define the model functions for all $x \in \dom g$: 
+    $\forall x \in \RR^n,\forall y \in \RR^n$, define: 
     \begin{align*}
@@
     \end{align*}
-    When $x \in \RR\setminus \dom g$, the model function takes $+\infty$ value. 
     Define the proximal gradient operator and gradient mapping operator:  $T_L := [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f]$. 
@@
     \begin{lemma}[Proximal gradient envelope]\label{lemma:pg-envelope}
-        Fix any $y \in \RR^n$, we will have for all $x \in \RR$ that: 
+        Fix any $y \in \RR^n$, we will have for all $x \in \RR^n$ that
         \begin{align*}
@@
         We can do this because the Lipschitz constant $L$ is fixed throughout the proof hence it can be omitted. 
-        The model function $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is an $L$ strongly convex function, so it admits quadratic growth conditions over minimizer $Ty$ and for all $x \in \RR^n$: 
+        The model function $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is an $L + \mu$ strongly convex function, so it admits quadratic growth conditions over minimizer $Ty$ and for all $x \in \RR^n$:
         {\smaller
@@
             - 
-            \frac{L}{2}\Vert x - Ty\Vert^2
+            \frac{L + \mu}{2}\Vert x - Ty\Vert^2
             \\
@@
             - 
-            \frac{L}{2}\Vert x - Ty\Vert^2
+            \frac{L + \mu}{2}\Vert x - Ty\Vert^2
             + D_f(Ty; y)
@@
             D_f(x, y) 
-            - \frac{L}{2}\Vert x - Ty\Vert^2
+            - \frac{L + \mu}{2}\Vert x - Ty\Vert^2
             + D_f(Ty; y)
@@
             + D_f(Ty; y)
-            - \frac{L}{2}\Vert x - Ty\Vert^2
+            - \frac{L + \mu}{2}\Vert x - Ty\Vert^2
             \\
@@
             + D_f(Ty; y)
-            - \frac{L}{2}\Vert x - Ty\Vert^2
-            \\
-            & =
+            - \frac{L + \mu}{2}\Vert x - Ty\Vert^2
+            \\
+            &\le 
             F(x) - F(Ty)
@@
 \section{Stepwise formulation of weak accelerated proximal gradient}\label{sec:stepwise-stuff}
-    This entire section is building up the R-WAPG algorithm which is described in the Definition \ref{def:wapg} of the next section. 
+    This entire section is instrumental to build the R-WAPG algorithm which is described in the Definition \ref{def:wapg} of the next section. 
     \par 
@@
         For any $(v_k, x_k), \alpha_k \in (0, 1), \gamma_k > 0$, let $\hat \gamma_{k + 1}$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ be given by: 
-        \begin{align*}
-            \hat \gamma_{k + 1} &= (1 - \alpha_k)\gamma_k + \mu \alpha_k, 
+        \begin{align}
+            \hat \gamma_{k + 1} &= (1 - \alpha_k)\gamma_k + \mu \alpha_k, \label{eqn:stepwise-wapg-eqn1}
             \\
             y_k &= 
-            (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
-            \\
-            g_k &= \mathcal G_L y_k, 
+            (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), \label{eqn:stepwise-wapg-eqn2}
+            \\
+            g_k &= \mathcal G_L y_k, \label{eqn:stepwise-wapg-eqn3}
             \\
             v_{k + 1} &= \hat\gamma^{-1}_{k + 1}
-            (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
-            \\
-            x_{k + 1} &= T_L y_k. 
-        \end{align*}
+            (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), \label{eqn:stepwise-wapg-eqn4}
+            \\
+            x_{k + 1} &= T_L y_k. \label{eqn:stepwise-wapg-eqn5}
+        \end{align}
     \end{definition}
@@
         \begin{align*}
-            (Q1): 
             y_k - v_k &= 
             \frac{\hat \gamma_{k + 1}}{\alpha_k \gamma_k}(x_k - y_k), 
-            \\
-            (Q2): 
+            \tag{Q1}\label{eqn:Q1}
+            \\
             y_k - x_k &= 
             \frac{\alpha_k \gamma_k}{\gamma_k + \alpha_k \mu}(v_k - x_k). 
+            \tag{Q2}\label{eqn:Q2}
         \end{align*}
     \end{observation}
-        To see (Q1), observe 
+        To see \eqref{eqn:Q1}, observe 
         \begin{align*}
@@
         \end{align*}
-        On the first equality (Q1), we multiplied both side of the equation by $\hat\gamma_{k + 1}/\alpha_k \gamma_k$ and then group $y_k$ on the LHS. 
-        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma_{k + 1}$, leaving the numerator $\hat \gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$. 
-        We used the definition of $\hat \gamma_{k + 1}$ here. 
-        To see the second equality (Q2), consider: 
+        On the first equality \eqref{eqn:Q1}, we multiplied both side of the equation by $\hat\gamma_{k + 1}/\alpha_k \gamma_k$ and then grouped $y_k$. 
+        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma_{k + 1}$, then simplifies the numerator by rearranging \eqref{eqn:stepwise-wapg-eqn1} into $\hat \gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$.
+        To see the second equality \eqref{eqn:Q2}, consider \eqref{eqn:stepwise-wapg-eqn2}: 
         \begin{align*}
@@
         \end{align*}
-        On the second equality that follows the second $\iff$ we just substituted $\hat\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$. 
-        Therefore, we discover that $x_k, v_k, y_k$ lies on the same line because (Q1) indicates $y_k - v_k$ parallels to $-(y_k - x_k)$ and both vector shares the same head which anchors at $y_k$.
+        On the second equality that follows, we substituted $\hat\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$ given by \eqref{eqn:stepwise-wapg-eqn1}. 
+        Therefore, $x_k, v_k, y_k$ lies on the same line because \eqref{eqn:Q1} indicates $y_k - v_k$ parallels to $-(y_k - x_k)$ and both vector shares the same head which anchors at $y_k$.
 
     \begin{proposition}[Stepwise Lyapunov]\label{prop:stepwise-lyapunov}\;\\
-        Fix any integer $k \in \mathbb Z$.
-        Given any $v_k, x_k$ and $\gamma_k > 0$, invoke Definition \ref{def:stepwise-wapg} to obtain $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}$. 
-        Fix any arbitrary $R_k \in \RR$.
+        Fix any integer $k \in \mathbb Z$ and $R_k \in \RR$. 
+        Given any $v_k, x_k$ and $\gamma_k > 0$ and $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}$ that satisfies Definition \ref{def:stepwise-wapg}. 
         Define: 
-        \begin{align*}
+        \begin{align}
             R_{k + 1}
@@
             \right). 
-        \end{align*}
-        Then it has for all $x^* \in \RR^n$ where $F^* = F(x^*)$, the inequality: 
-        \begin{align*}
-            F(x_{k + 1}) - F^* + R_{k + 1} + \frac{\hat \gamma_{k + 1}}{2}\Vert v_{k + 1} - x^*\Vert^2
+        \end{align}\label{eqn:stepwise-lya-1}
+        Then it has for all $x^* \in \RR^n$, the inequality: 
+        {\small
+        \begin{align}\label{ineq:stepwise-lya-2}
+            F(x_{k + 1}) - F(x^*) + R_{k + 1} + \frac{\hat \gamma_{k + 1}}{2}\Vert v_{k + 1} - x^*\Vert^2
             &\le 
@@
             \left(
-                F(x_k) - F^* + R_k + \frac{\gamma_{k}}{2}\Vert v_k - x^*\Vert^2
+                F(x_k) - F(x^*) + R_k + \frac{\gamma_{k}}{2}\Vert v_k - x^*\Vert^2
             \right). 
-        \end{align*}
+        \end{align}
+        }
     \end{proposition}
@@
         \par 
-        We started with $F(x_{k + 1}) + R_{k + 1}$ as Equation (1*), and $\hat \gamma/2\Vert v_{k + 1} - x^*\Vert^2$ as (2*). 
-        In the proof that follows, we show (2*) equals to (2.2*). 
-        We added (2*), (2.2*) to produce (3*). 
+        We started with $F(x_{k + 1}) + R_{k + 1}$ as Equation \eqref{eqn:stepwise-lya-proof-eqn1}, and $\hat \gamma/2\Vert v_{k + 1} - x^*\Vert^2$ as Equation (\ref{eqn:stepwise-lya-proof-eqn2}). 
+        In the proof that follows, we show (\ref{eqn:stepwise-lya-proof-eqn2}) equals to (2.2*). 
+        We added (\ref{eqn:stepwise-lya-proof-eqn2}), (\ref{expr:stepwise-lya-expr2.2}) to produce (3*). 
         Then we show (3*) equals to (3.1*). 
@@
         \par
-        Start by considering the first and the third term of the LHS of the inequality that we want to prove. 
-        \begin{align*}
-            F(x_{k + 1}) &= 
+        Start by considering the first and the third term on LHS of \eqref{ineq:stepwise-lya-2} summed up: 
+        \begin{align}
+            F(x_{k + 1}) &\underset{\eqref{eqn:regret}}{=}
             F(x_k) - \epsilon_k - \langle  g_k, x_k - y_k\rangle - \frac{1}{2L}\Vert g_k\Vert^2,
+            \notag
             \\
             R_{k + 1}
-            &= 
+            &\underset{\eqref{eqn:stepwise-lya-1}}{=} 
             \frac{1}{2}\left(
@@
             \right), 
+            \notag
             \\
@@
             - \frac{\alpha_k^2}{2\hat \gamma}\Vert g_k\Vert^2
+            \notag
             \\
@@
                 \right). 
-        \tag{1*}
-        \end{align*}
+            \label{eqn:stepwise-lya-proof-eqn1}
+        \end{align}
         Coefficient of $\epsilon_k$ and $\Vert g_k\Vert^2$ are grouped. 
         Next, we have: 
-        \begin{align*}
+        \begin{align}
+            \begin{split}
                 \frac{\hat \gamma}{2}\Vert v_{k + 1} - x^* \Vert^2
@@
                     \langle v_k - x^*, \mu \alpha_k(y_k - v_k) - \alpha_k g_k\rangle. 
-        \tag{2*}
-        \end{align*}
-        On the above derivation, the first equality is by definition of $v_{k + 1}$; the second equality is by $\hat \gamma = (1 - \alpha_k)\gamma + \mu \alpha_k$ the second equality comes by considering:
+            \end{split}
+        \label{eqn:stepwise-lya-proof-eqn2}
+        \end{align}
+        On the above derivation, the first equality comes by substituting the definition of $v_{k + 1}$ given by \eqref{eqn:stepwise-wapg-eqn4}; the second equality simplifies using $\hat \gamma = (1 - \alpha_k)\gamma + \mu \alpha_k$ given by \eqref{eqn:stepwise-wapg-eqn1} and  because:
         \begin{align*}
@@
         \end{align*}
-        Focusing on the last two terms by the end of expression (2*), we have  
-        \begin{align*}
+        Focusing on the last two terms by the end of expression \eqref{eqn:stepwise-lya-proof-eqn2}, we have  
+        \begin{align}
+        \begin{split}
             \frac{\alpha^2_k}{2\hat \gamma} 
@@
             - \alpha_k \langle v_k - x^*, g_k\rangle. 
-        \tag{2.1*}
-        \end{align*}
-        Adding the LHS of both equations above together gives: 
+        \end{split} % \tag{2.1*}
+        \label{eqn:stepwise-lya-proof-eqn2.1}
+        \end{align}
+        Adding them gives: 
         {\small
@@
         }
-        With the above we can conclude that (2*) simplifies to 
+        With the above \eqref{eqn:stepwise-lya-proof-eqn2} simplifies to 
         {\small
-        \begin{align*} 
+        \begin{align} 
+            \begin{split}
                 & 
@@
                     + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle. 
-        \tag{2.2*}
-        \end{align*}
+            \end{split}
+            %\tag{2.2*}
+        \label{expr:stepwise-lya-expr2.2}
+        \end{align}
         }
-        Recall from 
+        Recall \eqref{eqn:Q1}, \eqref{eqn:Q2} from 
         \hyperref[obs:stepwise-wapg]{Observations \ref*{obs:stepwise-wapg}} that: 
@@
         \end{align*}
-        Ok that is a lot, we list the following equations to assist things: 
-        \begin{align*}
+        Then, it can simplifies the following:  
+        \begin{align}
+        \begin{split}
             &  
@@
             \\
-            & =
+            & \underset{\eqref{eqn:Q1}}{=}
             -\alpha_k(v_k - x^*) -
@@
             - (x_k - y_k) 
-            &\text{by Q1} 
             \\
@@
             \\
-            &= 
+            &\underset{\eqref{eqn:Q2}}{=}
             -\alpha_k(v_k - x^*) - 
@@
             \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(x_k - v_k)
-            &\text{by Q2}
             \\
@@
             &= \alpha_k(x^* - x_k). 
-        \tag{Q3}
-        \end{align*}
-        Adding (2.2*) to (1*) gives: 
-        \begin{align*}
+        \end{split}
+        \tag{Q3}\label{eqn:Q3}
+        \end{align}
+        Adding \eqref{expr:stepwise-lya-expr2.2} to \eqref{eqn:stepwise-lya-proof-eqn1} gives: 
+        \begin{align}
+        \begin{split}
             &
@@
             \\
-            &= 
+            &\underset{\eqref{eqn:Q3}}{=} 
             F(x_k) - \epsilon_k 
@@
             \right\rangle
-            & \text{Use Q3}
             \\
@@
                 + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle.     
-        \tag{3*}
-        \end{align*}
-        From the left to the right on the first equality, coefficients of $\Vert g_k\Vert^2$ cancels out to zero and the inner product containing $g_k$ are grouped. 
-        Going from the left to the right of the third equality, we applied (Q3) derived earlier to simplify the inner product term. 
-        The last equalities re-arranged terms and grouped the coefficients of $\epsilon_k$ together. 
-        Taking a page break, continuing on (3*) we have
-        \begin{align*}
+        \end{split}
+        %\tag{3*}
+        \label{eqn:stepwise-lya-proof-eqn3}
+        \end{align}
+        On the first equality, coefficients of $\Vert g_k\Vert^2$ cancels out to zero and the inner product containing $g_k$ are grouped
+        using \eqref{eqn:Q3} derived earlier. 
+        The last equality re-arranged terms and grouped the coefficients of $\epsilon_k$ together. 
+        Continuing on \eqref{eqn:stepwise-lya-proof-eqn3} we have
+        \begin{align}
+        \begin{split}
             &
@@
             \right).         
-            \tag{3.1*}
-        \end{align*}
+        \end{split}
+            % \tag{3.1*}
+            \label{eqn:stepwise-lya-eqn3.1}
+        \end{align}
         On the first equality, coefficients of $\Vert y_k - v_k\Vert^2$ are grouped together. 
-        On the second to the third equality, the terms had been simplified by 
+        On the second to the third equality, its coefficients simplified using: 
         \begin{align*}
@@
             \\
-            &= \frac{\mu\alpha_k}{2}\left(
+            &\underset{\eqref{eqn:stepwise-wapg-eqn1}}{=} \frac{\mu\alpha_k}{2}\left(
                 \frac{\hat \gamma}{\hat \gamma}
@@
         \end{align*}
-        (3.1*) was adding (1*) and (2.2*) together, which is the same as adding (1*) and (2*) together. 
-        So that was all equal to (1*) + (2*) and it says: 
+        We have \eqref{eqn:stepwise-lya-eqn3.1} = \eqref{eqn:stepwise-lya-proof-eqn1} + \eqref{expr:stepwise-lya-expr2.2}. 
+        By \eqref{eqn:stepwise-lya-proof-eqn2} = \eqref{expr:stepwise-lya-expr2.2}, \eqref{eqn:stepwise-lya-proof-eqn1} + \eqref{eqn:stepwise-lya-proof-eqn2} says: 
         \begin{align*}

### 2025-01-11 Notebook LaTEX/R-WAPG/paper3.tex
>w<, polishing

@@
         On the first equality \eqref{eqn:Q1}, we multiplied both side of the equation by $\hat\gamma_{k + 1}/\alpha_k \gamma_k$ and then grouped $y_k$. 
-        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma_{k + 1}$, then simplifies the numerator by rearranging \eqref{eqn:stepwise-wapg-eqn1} into $\hat \gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$.
+        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma_{k + 1}$, then simplifies the demoninator by rearranging \eqref{eqn:stepwise-wapg-eqn1} into $\hat \gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$.
         To see the second equality \eqref{eqn:Q2}, consider \eqref{eqn:stepwise-wapg-eqn2}: 
@@
         Therefore, $x_k, v_k, y_k$ lies on the same line because \eqref{eqn:Q1} indicates $y_k - v_k$ parallels to $-(y_k - x_k)$ and both vector shares the same head which anchors at $y_k$. 
-
+    \begin{lemma}[A useful lemma]\label{lemma:ineq-q3}
+        Let $v_k, x_k, y_k, v_{k + 1}, x_{k + 1}$ and $\alpha_k, \hat \gamma_{k + 1}, \gamma_{k}$ be given by Definition \ref{def:stepwise-wapg}. 
+        Then for any $x^* \in \RR^n$ it satisfies: 
+        \begin{align}
+            - \alpha_k(v_k - x^*) - \frac{\alpha_k^2 \mu}{\hat \gamma}(y_k - v_k) - (x_k - y_k)
+            &= \alpha_k(x^* - x_k). 
+            \tag{Q3}\label{eqn:Q3}
+        \end{align}
+    \end{lemma}
+    \begin{proof}
+        % Recall \eqref{eqn:Q1}, \eqref{eqn:Q2} from 
+        % \hyperref[obs:stepwise-wapg]{Observations \ref*{obs:stepwise-wapg}} that: 
+        % \begin{align*}
+        %     (Q1): 
+        %     y_k - v_k &= 
+        %     \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k),
+        %     \\
+        %     (Q2): 
+        %     y_k - x_k &= 
+        %     \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
+        % \end{align*}
+        The proof is direct algebra: 
+        \begin{align*}
+            &  
+            - \alpha_k(v_k - x^*) - \frac{\alpha_k^2 \mu}{\hat \gamma_{k + 1}}(y_k - v_k) - (x_k - y_k)
+            \\
+            & \underset{\eqref{eqn:Q1}}{=}
+            -\alpha_k(v_k - x^*) -
+            \frac{\alpha_k^2\mu}{\hat \gamma_{k + 1}}
+            \frac{\hat \gamma_{k + 1}}{\alpha_k \gamma_k}(x_k - y_k)
+            - (x_k - y_k) 
+            \\
+            &= 
+            -\alpha_k(v_k - x^*) -
+            \frac{\alpha_k \mu}{\gamma_k}(x_k - y_k)
+            - (x_k - y_k) 
+            \\
+            &= 
+            -\alpha_k(v_k - x^*) -
+            \left(
+                1 + \frac{\alpha_k \mu}{\gamma_k}
+            \right)(x_k - y_k)
+            \\
+            &\underset{\eqref{eqn:Q2}}{=}
+            -\alpha_k(v_k - x^*) - 
+            \frac{\alpha_k \mu + \gamma_k}{\gamma_k}
+            \frac{\alpha_k \gamma_k}{\gamma_k + \alpha_k \mu}(x_k - v_k)
+            \\
+            &= 
+            -\alpha_k(v_k - x^*)
+            - \alpha_k(x_k - v_k)
+            \\
+            &= \alpha_k(x^* - x_k). 
+        \end{align*}
+    \end{proof}
     \begin{proposition}[Stepwise Lyapunov]\label{prop:stepwise-lyapunov}\;\\
         Fix any integer $k \in \mathbb Z$ and $R_k \in \RR$. 
-        Given any $v_k, x_k$ and $\gamma_k > 0$ and $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}$ that satisfies Definition \ref{def:stepwise-wapg}. 
+        Given any $v_k, x_k$ and $\gamma_k > 0$ and $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}, \alpha_k$ that satisfies Definition \ref{def:stepwise-wapg}. 
         Define: 
@@
         We started with $F(x_{k + 1}) + R_{k + 1}$ as Equation \eqref{eqn:stepwise-lya-proof-eqn1}, and $\hat \gamma/2\Vert v_{k + 1} - x^*\Vert^2$ as Equation (\ref{eqn:stepwise-lya-proof-eqn2}). 
-        In the proof that follows, we show (\ref{eqn:stepwise-lya-proof-eqn2}) equals to (2.2*). 
-        We added (\ref{eqn:stepwise-lya-proof-eqn2}), (\ref{expr:stepwise-lya-expr2.2}) to produce (3*). 
-        Then we show (3*) equals to (3.1*). 
-        The content of the entire LHS of the inequality we want to prove is in (3.2*). 
-        Going from (3.2*) to (4*) is an inequality which we used Theorem \ref{thm:prox-grad-ineq}. 
+        In the proof that follows, we show (\ref{eqn:stepwise-lya-proof-eqn2}) equals to \eqref{expr:stepwise-lya-expr2.2}. 
+        We add (\ref{eqn:stepwise-lya-proof-eqn2}), (\ref{expr:stepwise-lya-expr2.2}) to produce \eqref{eqn:stepwise-lya-proof-eqn3}. 
+        Then we show \eqref{eqn:stepwise-lya-proof-eqn3} equals to \eqref{eqn:stepwise-lya-proof-eqn3.1}. 
+        Finally, the entire LHS of \eqref{ineq:stepwise-lya-2} equals to the RHS of \eqref{ineq:stepwise-lya-proof-ineq4}. 
+        Going from \eqref{eqn:stepwise-lya-proof-eqn3.2} to \eqref{ineq:stepwise-lya-proof-ineq4}, we used \ref{thm:prox-grad-ineq} which is all we need, and it is the same as the inequality that we want to prove.
         \par
@@
         }
-        Recall \eqref{eqn:Q1}, \eqref{eqn:Q2} from 
-        \hyperref[obs:stepwise-wapg]{Observations \ref*{obs:stepwise-wapg}} that: 
-        \begin{align*}
-            (Q1): 
-            y_k - v_k &= 
-            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k),
-            \\
-            (Q2): 
-            y_k - x_k &= 
-            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
-        \end{align*}
-        Then, it can simplifies the following:  
-        \begin{align}
-        \begin{split}
-            &  
-            - \alpha_k(v_k - x^*) - \frac{\alpha_k^2 \mu}{\hat \gamma}(y_k - v_k) - (x_k - y_k)
-            \\
-            & \underset{\eqref{eqn:Q1}}{=}
-            -\alpha_k(v_k - x^*) -
-            \frac{\alpha_k^2\mu}{\hat \gamma}\frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k)
-            - (x_k - y_k) 
-            \\
-            &= 
-            -\alpha_k(v_k - x^*) -
-            \frac{\alpha_k \mu}{\gamma}(x_k - y_k)
-            - (x_k - y_k) 
-            \\
-            &= 
-            -\alpha_k(v_k - x^*) -
-            \left(
-                1 + \frac{\alpha_k \mu}{\gamma}
-            \right)(x_k - y_k)
-            \\
-            &\underset{\eqref{eqn:Q2}}{=}
-            -\alpha_k(v_k - x^*) - 
-            \frac{\alpha_k \mu + \gamma}{\gamma}
-            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(x_k - v_k)
-            \\
-            &= 
-            -\alpha_k(v_k - x^*)
-            - \alpha_k(x_k - v_k)
-            \\
-            &= \alpha_k(x^* - x_k). 
-        \end{split}
-        \tag{Q3}\label{eqn:Q3}
-        \end{align}
+
         Adding \eqref{expr:stepwise-lya-expr2.2} to \eqref{eqn:stepwise-lya-proof-eqn1} gives: 
@@
             % \tag{3.1*}
-            \label{eqn:stepwise-lya-eqn3.1}
+            \label{eqn:stepwise-lya-proof-eqn3.1}
         \end{align}
@@
         \end{align*}
-        We have \eqref{eqn:stepwise-lya-eqn3.1} = \eqref{eqn:stepwise-lya-proof-eqn1} + \eqref{expr:stepwise-lya-expr2.2}. 
-        By \eqref{eqn:stepwise-lya-proof-eqn2} = \eqref{expr:stepwise-lya-expr2.2}, \eqref{eqn:stepwise-lya-proof-eqn1} + \eqref{eqn:stepwise-lya-proof-eqn2} says: 
+        We have \eqref{eqn:stepwise-lya-proof-eqn3.1} $\impliedby$ \eqref{eqn:stepwise-lya-proof-eqn1} + \eqref{expr:stepwise-lya-expr2.2}. 
+        By \eqref{eqn:stepwise-lya-proof-eqn2} $\iff$ \eqref{expr:stepwise-lya-expr2.2},
+        \eqref{eqn:stepwise-lya-proof-eqn3.1} says: 
         \begin{align*}
@@
             \\
-            & \iff 
+        \end{align*}
+        Subtracting $F(x^*)$ from both side of the equation it gives: 
+        \begin{align}
+            \begin{split}
                 \\
@@
                     \right).     
-        \tag{3.2*}
-        \end{align*}
+            \end{split}
+        % \tag{3.2*}
+        \label{eqn:stepwise-lya-proof-eqn3.2}
+        \end{align}
         Focusing on the second term, we simplify the multiplier inside: 
         {\small
-        \begin{align*}
+        \begin{align}
+        \begin{split}
             & F(x_k) - F(x^*) - \epsilon_k - \langle g_k, x_k - x^*\rangle + \frac{\mu}{2}\Vert y_k - x^*\Vert^2
@@
             &= F(T_L y_k) - F(x^*) + \langle g_k, x^* - y_k\rangle + \frac{\mu}{2}\Vert y_k - x^*\Vert^2
-            + \frac{1}{2L}\Vert g_k\Vert^2 \le 0. 
-        \tag{4*}    
-        \end{align*}
+            + \frac{1}{2L}\Vert g_k\Vert^2 \underset{\text{Theorem }\ref{thm:prox-grad-ineq}}{\le} 0.     
+        \end{split}
+        \label{ineq:stepwise-lya-proof-ineq4}
+        \end{align}
         }
-        On the last line, we expand the definition of $g_k$ and then used the
-        \hyperref[thm:prox-grad-ineq]{Theorem \ref*{thm:prox-grad-ineq}}. 
-        Therefore, we conclude that: 
+        % On the last line, we expand the definition of $g_k$ and then used the
+        % \hyperref[thm:prox-grad-ineq]{Theorem \ref*{thm:prox-grad-ineq}}. 
+        Therefore
         {\small

### 2025-01-13 Notebook LaTEX/R-WAPG/paper3.tex
>w<

@@
         We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart. 
-
-        \todoinline{This will be written once most of the contents in the paper are settled. 
-        }
         \par
@@
         On the first equality \eqref{eqn:Q1}, we multiplied both side of the equation by $\hat\gamma_{k + 1}/\alpha_k \gamma_k$ and then grouped $y_k$. 
-        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma_{k + 1}$, then simplifies the demoninator by rearranging \eqref{eqn:stepwise-wapg-eqn1} into $\hat \gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$.
+        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma_{k + 1}$, then simplifies the denominator by rearranging \eqref{eqn:stepwise-wapg-eqn1} into $\hat \gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$.
         To see the second equality \eqref{eqn:Q2}, consider \eqref{eqn:stepwise-wapg-eqn2}: 
@@
     \begin{remark}
-        Given $y_k$, we can choose to increase $\mu_\kappa = 2D_f(x^*, y_k)/\Vert y_k - x^*\Vert^2 \ge \mu$ which also works on (4*).
+        Given $y_k$, we can choose to increase $\mu_\kappa = 2D_f(x^*, y_k)/\Vert y_k - x^*\Vert^2 \ge \mu$ which also works on \eqref{ineq:stepwise-lya-proof-ineq4}.
         This is true by the intermediate steps taken to prove Theorem \ref{thm:prox-grad-ineq}. 
@@
     \end{proposition}
+
     \begin{proof}  
@@
             }{(3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}}.
-            \todoinline{\noindent
-                The term ``Method of Similar Triangle'' specific to this particular representation of AGM. 
-                For more information, see:  
-                \begin{enumerate}
-                    \item 3.1, 4.1 in Jongmin Lee et al., ``A geometric structure of Acceleration and its role in making gradients small''
-                    \item The entirety of Ahn and Sra's paper ``PPM interpretation of Nesterov's accelerated gradient. ''. 
-                \end{enumerate}
-            }
 
@@
         \subsubsection{LASSO}
-            This section present results of numerical experiment for solving the (least absolute shrinkage and
-            selection operator) LASSO problem proposed by 
-            \todo{
-                $\blacksquare$ Add reference ``Regression shrinkage and selection via the Lasso''
-                \\ $\blacksquare$ Cite it. 
-            }{\hl{Tibshirani}} \cite{tibshirani_regression_1996}. 
+            This section present results of numerical experiment for solving the (least absolute shrinkage and selection operator) LASSO problem proposed by \hl{Tibshirani} \cite{tibshirani_regression_1996}.
             The problem of LASSO has smooth, nonsmooth additive and the problem is given by: 

### 2025-01-14 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

--- 2025-01-11 Notebook LaTEX/R-WAPG/paper3.tex
@@
         It's consider optimal in some sense and see Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018} for details. 
-        However, things are not sunshine and rainbow because the above scheme is associated with the following issue: 
-        If $F$ is $\mu > 0$ strongly convex, the optimality gap $F(x_k) - F(x^*)$ oscillates and converges sub-linearly, making it worse than gradient descent.
+        However, things are not sunshine, rainbow and happily ever after because the above scheme is associated with the issue that if $F$ is $\mu > 0$ strongly convex, the optimality gap $F(x_k) - F(x^*)$ oscillates and converges sub-linearly, making it worse than gradient descent.
 See page 9 of Su et al.
@@
         \subsection{Prior works}
-            \todoinline{\noindent
-                The prior works' section is too little, it requires some expansion in the future for sure.
-                \begin{enumerate}
-                    \item Paper: ``An introduction to continuous optimization for imaging'', Chambolle, Pock. 
-                \end{enumerate}
-
-            }
-            \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them.}{\hl{Apidopoulos et al. }\cite{apidopoulos_convergence_2018}}
-            showed that a relaxed choice of the sequence that doesn't strictly follow the Nesterov's rule still leads to the convergence of the momentum algorithm. 
-            Besides restarting, \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them.
-}{See Attouch, et al.
-\cite{attouch_first-order_2022}, Maulen and Peypouquet \cite{maulen_speed_2023}} and references within.
+            Apidopoulos et al.
+\cite{apidopoulos_convergence_2018} showed that a relaxed choice of the sequence that doesn't strictly follow the Nesterov's rule still leads to the convergence of the momentum algorithm.
+            Besides restarting, See Attouch, et al. \cite{attouch_first-order_2022}, Maulen and Peypouquet \cite{maulen_speed_2023} and references within.
             They present the idea of Hessian Damping for stabilizing the Nesterov's accelerated gradient without/with restarting.
@@
         We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart. 
-
-        \todoinline{This will be written once most of the contents in the paper are settled. 
-        }
+        The theoretical analysis for the convergence of Free R-WAPG remains elusive.
+
         \par
@@
         Section \ref{sec:stepwise-stuff} states and prove an inequality based on a generic iterative algorithm for just one iteration. 
-        Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG algorithm and characterize conditions for R-WAPG sequence sufficient to derive the optimality upper bound in Proposition \ref{prop:wagp-convergence}.
-        Section \ref{sec:rwapg-equiv-repr} gives 3 equivalent representations of the R-WAPG algorithms that are comparable to instances of Accelerated Proximal Gradient algorithm found in the literatures.
-        Section \ref{sec:rwapg-literatures} formulates FISTA, and V-FISTA sequences and proves the convergence rate of several variants  FISTA using the R-WAPG algorithm and its convergence rate developed in the previous sections.
-        Finally, in Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcase the numerical experiments for regression, LASSO, and logistic regression.
+        Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG algorithm and characterize sufficient conditions for R-WAPG sequence to derive the optimality upper bound in Proposition \ref{prop:wagp-convergence}.
+        Section \ref{sec:rwapg-equiv-repr} gives three equivalent representations of the R-WAPG algorithms that are comparable to instances of Accelerated Proximal Gradient algorithm found in the literatures.
+        Section \ref{sec:rwapg-literatures} formulates FISTA, and V-FISTA sequences as instance of the R-WAPG sequences.
+        The section proves the convergence rate of several variants of FISTA using the equivalent forms introduced in Section \ref{sec:rwapg-equiv-repr} and the convergence rate developed Section \ref{sec:rwapg-formulation-convergence}.
+        Finally, in Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcase the numerical experiments for regression, LASSO. 
         The numerical experiments expose very interesting behaviors of the algorithm of our own creativity.
@@
     \end{align*}
-    Define the proximal gradient operator and gradient mapping operator:  $T_L := [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f]$. 
-    The proximal gradient operator $T_L$ admits 
+    Define the proximal gradient operator and gradient mapping operator: $T_L, \mathcal G_L$: 
     \begin{align*}
@@
             g(x) + \langle \nabla f(y), x\rangle + L/2\Vert x - y\Vert^2
-        \right\rbrace,
+        \right\rbrace = [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f], 
         \\
@@
     \begin{remark}
-        This proof works for all $L$ that is larger than the smallest Lipschitz modulus of $f$. 
+        This proof works for all $L$ that is larger than the smallest Lipschitz modulus of $f$ and $\mu$ less than the strong convexity modulus of $f$. 
     \end{remark}
@@
 
+        \begin{lemma}[A useful lemma]\label{lemma:ineq-q3}
+        Let $v_k, x_k, y_k, v_{k + 1}, x_{k + 1}$ and $\alpha_k, \hat \gamma_{k + 1}, \gamma_{k}$ be given by Definition \ref{def:stepwise-wapg}. 
+        Then for any $x^* \in \RR^n$ it satisfies: 
+        \begin{align}
+            - \alpha_k(v_k - x^*) - \frac{\alpha_k^2 \mu}{\hat \gamma}(y_k - v_k) - (x_k - y_k)
+            &= \alpha_k(x^* - x_k). 
+            \tag{Q3}\label{eqn:Q3}
+        \end{align}
+    \end{lemma}
+    \begin{proof}
+        The proof is direct algebra: 
+        \begin{align*}
+            &  
+            - \alpha_k(v_k - x^*) - \frac{\alpha_k^2 \mu}{\hat \gamma_{k + 1}}(y_k - v_k) - (x_k - y_k)
+            \\
+            & \underset{\eqref{eqn:Q1}}{=}
+            -\alpha_k(v_k - x^*) -
+            \frac{\alpha_k^2\mu}{\hat \gamma_{k + 1}}
+            \frac{\hat \gamma_{k + 1}}{\alpha_k \gamma_k}(x_k - y_k)
+            - (x_k - y_k) 
+            \\
+            &= 
+            -\alpha_k(v_k - x^*) -
+            \frac{\alpha_k \mu}{\gamma_k}(x_k - y_k)
+            - (x_k - y_k) 
+            \\
+            &= 
+            -\alpha_k(v_k - x^*) -
+            \left(
+                1 + \frac{\alpha_k \mu}{\gamma_k}
+            \right)(x_k - y_k)
+            \\
+            &\underset{\eqref{eqn:Q2}}{=}
+            -\alpha_k(v_k - x^*) - 
+            \frac{\alpha_k \mu + \gamma_k}{\gamma_k}
+            \frac{\alpha_k \gamma_k}{\gamma_k + \alpha_k \mu}(x_k - v_k)
+            \\
+            &= 
+            -\alpha_k(v_k - x^*)
+            - \alpha_k(x_k - v_k)
+            \\
+            &= \alpha_k(x^* - x_k). 
+        \end{align*}
+    \end{proof}
     \begin{proposition}[Stepwise Lyapunov]\label{prop:stepwise-lyapunov}\;\\
         Fix any integer $k \in \mathbb Z$ and $R_k \in \RR$. 
-        Given any $v_k, x_k$ and $\gamma_k > 0$ and $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}$ that satisfies Definition \ref{def:stepwise-wapg}. 
+        Given any $v_k, x_k$ and $\gamma_k > 0$ and $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}, \alpha_k$ that satisfies Definition \ref{def:stepwise-wapg}. 
         Define: 
-        \begin{align}
+        \begin{align}\label{eqn:stepwise-lya-1}
             R_{k + 1}
@@
             \right). 
-        \end{align}\label{eqn:stepwise-lya-1}
+        \end{align}
         Then it has for all $x^* \in \RR^n$, the inequality: 
@@
         \par 
-        We started with $F(x_{k + 1}) + R_{k + 1}$ as Equation \eqref{eqn:stepwise-lya-proof-eqn1}, and $\hat \gamma/2\Vert v_{k + 1} - x^*\Vert^2$ as Equation (\ref{eqn:stepwise-lya-proof-eqn2}). 
-        In the proof that follows, we show (\ref{eqn:stepwise-lya-proof-eqn2}) equals to (2.2*). 
-        We added (\ref{eqn:stepwise-lya-proof-eqn2}), (\ref{expr:stepwise-lya-expr2.2}) to produce (3*). 
-        Then we show (3*) equals to (3.1*). 
-        The content of the entire LHS of the inequality we want to prove is in (3.2*). 
-        Going from (3.2*) to (4*) is an inequality which we used Theorem \ref{thm:prox-grad-ineq}. 
+        We started with $F(x_{k + 1}) + R_{k + 1} \iff \eqref{eqn:stepwise-lya-proof-eqn1}$, 
+        then $\hat \gamma/2\Vert v_{k + 1} - x^*\Vert^2 \iff \eqref{expr:stepwise-lya-expr2.2}$ via \eqref{eqn:stepwise-lya-proof-eqn2}. 
+        We add (\ref{eqn:stepwise-lya-proof-eqn2}), (\ref{expr:stepwise-lya-expr2.2}) to get $\eqref{eqn:stepwise-lya-proof-eqn3.1} \iff \eqref{eqn:stepwise-lya-proof-eqn3}$.
+        Finally, the entire LHS of \eqref{ineq:stepwise-lya-2} equals to the RHS of \eqref{eqn:stepwise-lya-proof-eqn3.2}. 
+        Going from \eqref{eqn:stepwise-lya-proof-eqn3.2} to \eqref{ineq:stepwise-lya-proof-ineq4}, we used Theorem \ref{thm:prox-grad-ineq} which yields the inequality that we want to prove. 
         \par
         Start by considering the first and the third term on LHS of \eqref{ineq:stepwise-lya-2} summed up: 
-        \begin{align}
+        \begin{align}\label{eqn:stepwise-lya-proof-eqn1}
             F(x_{k + 1}) &\underset{\eqref{eqn:regret}}{=}
@@
                 \right). 
-            \label{eqn:stepwise-lya-proof-eqn1}
         \end{align}
@@
         \begin{align}
+        \label{eqn:stepwise-lya-proof-eqn2}
         \begin{split}
@@
         \end{split}
-        \label{eqn:stepwise-lya-proof-eqn2}
         \end{align}
@@
         \begin{align}
+         \label{eqn:stepwise-lya-proof-eqn2.1}
         \begin{split}
@@
         \end{split} % \tag{2.1*}
-        \label{eqn:stepwise-lya-proof-eqn2.1}
         \end{align}
@@
         {\small
-        \begin{align} 
+        \begin{align}\label{expr:stepwise-lya-expr2.2}
         \begin{split}
@@
         %\tag{2.2*}
-        \label{expr:stepwise-lya-expr2.2}
         \end{align}
         }
-        Recall \eqref{eqn:Q1}, \eqref{eqn:Q2} from 
-        \hyperref[obs:stepwise-wapg]{Observations \ref*{obs:stepwise-wapg}} that: 
-        \begin{align*}
-            (Q1): 
-            y_k - v_k &= 
-            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k),
-            \\
-            (Q2): 
-            y_k - x_k &= 
-            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
-        \end{align*}
-        Then, it can simplifies the following:  
-        \begin{align}
-        \begin{split}
-            &  
-            - \alpha_k(v_k - x^*) - \frac{\alpha_k^2 \mu}{\hat \gamma}(y_k - v_k) - (x_k - y_k)
-            \\
-            & \underset{\eqref{eqn:Q1}}{=}
-            -\alpha_k(v_k - x^*) -
-            \frac{\alpha_k^2\mu}{\hat \gamma}\frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k)
-            - (x_k - y_k) 
-            \\
-            &= 
-            -\alpha_k(v_k - x^*) -
-            \frac{\alpha_k \mu}{\gamma}(x_k - y_k)
-            - (x_k - y_k) 
-            \\
-            &= 
-            -\alpha_k(v_k - x^*) -
-            \left(
-                1 + \frac{\alpha_k \mu}{\gamma}
-            \right)(x_k - y_k)
-            \\
-            &\underset{\eqref{eqn:Q2}}{=}
-            -\alpha_k(v_k - x^*) - 
-            \frac{\alpha_k \mu + \gamma}{\gamma}
-            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(x_k - v_k)
-            \\
-            &= 
-            -\alpha_k(v_k - x^*)
-            - \alpha_k(x_k - v_k)
-            \\
-            &= \alpha_k(x^* - x_k). 
-        \end{split}
-        \tag{Q3}\label{eqn:Q3}
-        \end{align}
         Adding \eqref{expr:stepwise-lya-expr2.2} to \eqref{eqn:stepwise-lya-proof-eqn1} gives: 
-        \begin{align}
+        \begin{align}\label{eqn:stepwise-lya-proof-eqn3}
         \begin{split}
@@
         %\tag{3*}
-        \label{eqn:stepwise-lya-proof-eqn3}
         \end{align}
@@
         Continuing on \eqref{eqn:stepwise-lya-proof-eqn3} we have
-        \begin{align}
+        \begin{align}\label{eqn:stepwise-lya-proof-eqn3.1}
         \begin{split}
@@
             \right).         
-        \end{split}
-            % \tag{3.1*}
-            \label{eqn:stepwise-lya-eqn3.1}
+        \end{split} % \tag{3.1*}
         \end{align}
@@
             \\
-            & \iff 
+        \end{align*}
+        Subtracting $F(x^*)$ from both side of the equation it gives: 
+        \begin{align}\label{eqn:stepwise-lya-proof-eqn3.2}
+            \begin{split}
                 \\
@@
                     \right).     
-        \tag{3.2*}
-        \end{align*}
+            \end{split}
+        % \tag{3.2*}
+        \end{align}
         Focusing on the second term, we simplify the multiplier inside: 
         {\small
-        \begin{align*}
+        \begin{align}\label{ineq:stepwise-lya-proof-ineq4}
+        \begin{split}
             & F(x_k) - F(x^*) - \epsilon_k - \langle g_k, x_k - x^*\rangle + \frac{\mu}{2}\Vert y_k - x^*\Vert^2
@@
             &= F(T_L y_k) - F(x^*) + \langle g_k, x^* - y_k\rangle + \frac{\mu}{2}\Vert y_k - x^*\Vert^2
-            + \frac{1}{2L}\Vert g_k\Vert^2 \le 0. 
-        \tag{4*}    
-        \end{align*}
+            + \frac{1}{2L}\Vert g_k\Vert^2 \underset{\text{Theorem }\ref{thm:prox-grad-ineq}}{\le} 0.     
+        \end{split}
+        \end{align}
         }
-        On the last line, we expand the definition of $g_k$ and then used the
-        \hyperref[thm:prox-grad-ineq]{Theorem \ref*{thm:prox-grad-ineq}}. 
-        Therefore, we conclude that: 
+        % On the last line, we expand the definition of $g_k$ and then used the
+        % \hyperref[thm:prox-grad-ineq]{Theorem \ref*{thm:prox-grad-ineq}}. 
+        Therefore
         {\small
@@
 \section{Formulation of R-WAPG and its convergence rates}\label{sec:rwapg-formulation-convergence}
-    The sole focus of this section is Definition \ref{def:wapg}.
-    It describes the R-WAPG algorithm which generates iterates $(x_k, y_k, v_k)$ and admits potential convergence claim using Proposition \ref{prop:stepwise-lyapunov}. 
-    Definition \ref{def:rwapg-seq} introduces the concept of an R-WAPG sequences which is crucially important. 
-    The sequence formulates the R-WAPG algorithm stated in Definition \ref{def:wapg}, it connects the step-wise formulation of R-WAPG (Definition \ref{def:stepwise-wapg}) and describes the convergence claim of R-WAPG in Proposition \ref{prop:wagp-convergence}.
-    In the next section, it continues to play a crucial role in describing several equivalent forms of the R-WAPG algorithm, and their convergence claim. 
+    this section focuses on Definition \ref{def:wapg}.
+    R-WAPG algorithm generates iterates $(x_k, y_k, v_k)$ and admits an upper bound on $F(x_k) - F^*$ described in Proposition \ref{prop:stepwise-lyapunov}. 
+    Definition \ref{def:rwapg-seq} introduces the concept of an R-WAPG sequences: $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ which is crucial.
+    The sequences parameterize the R-WAPG algorithm stated in Definition \ref{def:wapg}, it connects the step-wise formulation of R-WAPG (Definition \ref{def:stepwise-wapg}) and can describe the convergence claim of R-WAPG in Proposition \ref{prop:wagp-convergence}.
+    In the next section, it continues to play a crucial role in describing several equivalent forms of the R-WAPG algorithm, and their corresponding convergence claim. 
     \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}\;\\
@@
         %     \\
-        %     &<
+        %     &
         %     \frac{1}{2}\left(
@@
     \begin{proof}  
-        $\hat \gamma_2 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$ is true by Observation \ref{obs:r-wapg-observation-1}. 
-        Observe that $R_2$ is defined in the same manner as in Proposition \ref{prop:stepwise-lyapunov} with $k = 1$, we can invoke Proposition \ref{prop:stepwise-lyapunov}, and it gives: 
+        The proof is a proof by induction. 
+        Let's first consider $k = 1$, $\hat \gamma_2 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$, $R_1 = 0$. 
+        From the above definition, $R_2$ is the same as \eqref{eqn:stepwise-lya-1} hence invoking Proposition \ref{prop:stepwise-lyapunov}: 
         \begin{align*}
@@
         We had demonstrated the base case. 
-        \par 
         Next, for all $k = 2, 3, \cdots, N$, from Observation \ref{obs:r-wapg-observation-2}: 
@@
         So $\gamma_k, \hat \gamma_{k + 1}, \alpha_k$ fits Definition \ref{def:stepwise-wapg}. 
-        The definition of $R_k$ given is the same as in Proposition \ref{prop:stepwise-lyapunov} hence we can use Proposition \ref{prop:stepwise-lyapunov} to unroll recursively for all $k \ge 1$: 
+        for all $k \ge 1$, $R_k$ satisfies \eqref{eqn:stepwise-lya-1}, hence using Proposition \ref{prop:stepwise-lyapunov} and unroll recursively : 
         {\small
@@
         This makes coefficient of $\Vert g_k\Vert^2$ zero. 
-        The first inequality is by $\epsilon_k \ge 0$ and the non-negativity of the remaining terms. 
+        The first inequality is by $\epsilon_k \ge 0$ and the non-negativity of the one remaining term. 
         The last equality is by the assumption that $R_1 = 0$. 
@@
     \begin{remark}        
-        The choice of $\rho_k = 0$ reproduces traditional choice of sequences for the APG algorithm. 
+        The choice of $\rho_k = 1$ reproduces traditional choice of sequences for the APG algorithm. 
         The above claim showed that there exists $\rho_k > 1$, or $\rho_k < 1$ where convergence of $F(x_k) - F(x^*)$ remains possible. 
@@
     This section carries out the tedious but necessary works for demonstrating the descriptive power of R-WAPG. 
-    We will formulate it into three generic forms that are commonly seemed in the literatures. 
+    We will formulate it into three generic forms. 
     These equivalent representations are listed in Definition \ref{def:r-wapg-intermediate}, \ref{def:r-wapg-st-form} and \ref{def:r-wapg-momentum-form}. 
+    These forms are equivalent under a subset of initial conditions. 
     \par 
@@
     \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
-        Given any initial $(x_1, v_1)$, and a sequence $(\tau_k)_{k \ge 1}, (\xi_k)_{k \ge 1}$ such that for all $k \ge 1$ $\tau_k \in (0, 1), \xi_k \in (0, 1)$. 
-        For all $k\ge 1$, iterates $(y_k, z_{k + 1}, x_{k + 1})_{k \ge 1}$ satisfies recursively that: 
+        Given any initial $(x_1, v_1)$, and a sequence $(\tau_k)_{k \ge 1}, (\xi_k)_{k \ge 1}$ such that for all $k \ge 1$ $\tau_k \in (0, 1), \xi_k \in (0, 1)$, and the iterates $(y_k, z_{k + 1}, x_{k + 1})_{k \ge 1}$ satisfies recursively that:
         \begin{align*}
@@
         \end{align*}
-        If $1 + \xi_k + \tau_k = L\delta_k, \tau_k \neq 0\; \forall k \ge 1$. 
+        If $1 + \xi_k + \tau_k = L\delta_k\; \forall k \ge 1$. 
         Then for all $k \ge 1$: 
@@
             This form of APG is rarely identified in the literatures. 
-            The closest algorithm that fits the form but with $\mu = 0$ is Chapter 12 of 
-            \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them. }
-            {\hl{in Ryu and Yin's Book} \cite{ryu_large-scale_2022}}, 
-            right after Theorem 17. 
+            The closest algorithm that fits the form but with $\mu = 0$ is Chapter 12 of in Ryu and Yin's Book \cite{ryu_large-scale_2022}, right after Theorem 17. 
             We created this form which makes the math that follows simpler. 
@@
             Finally, a similar triangle for formulation of FISTA can be found in Equation (2), (3), (4) in \cite{chambolle_convergence_2015}. 
-            To see graphical visualization on why such term is used to describe the APG algorithm in the literatures, see 
-            \todo{
-                $\blacksquare$ Add these. $\blacksquare$ Cite these. 
-            }{(3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}}. 
-            \todoinline{\noindent
-                The term ``Method of Similar Triangle'' specific to this particular representation of AGM. 
-                For more information, see:  
-                \begin{enumerate}
-                    \item 3.1, 4.1 in Jongmin Lee et al., ``A geometric structure of Acceleration and its role in making gradients small''
-                    \item The entirety of Ahn and Sra's paper ``PPM interpretation of Nesterov's accelerated gradient. ''. 
-                \end{enumerate}
-            }
+            To see graphical visualization on why such term is used to describe the APG algorithm in the literatures, see (3.1, 4.1) in Lee et al.
+\cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}.
 
@@
     \par
-    Assume $L$ given is an upper bound of the Lipschitz smoothness constant of $f$, then the algorithm calls $f(\cdot)$ two times, and $\nabla f(\cdot)$ once per iteration. 
+    Assume $L$ given is an upper bound of the Lipschitz smoothness constant of $f$ so th line search subroutine is never triggered. 
+    Then the algorithm calls $f(\cdot)$ two times, and $\nabla f(\cdot)$ once per iteration. 
     The algorithm computes $\nabla f(y_k)$ once for $x^+$, $f(y_{k + 1})$ once for Bregman Divergence because $f(y_{k})$ is evaluated from the previous iteration, and $f(x^+)$ once for Lipschitz constant line search condition.
@@
     \subsection{Numerical experiments}
-        This section gives figures and visual for numerical experiments conducted on the R-WAPG algorithm, and other algorithms in the literatures such as the V-FISTA, and M-FISTA algorithm. 
+        This section gives figures and visual for numerical experiments conducted using FR-WAPG algorithm (Algorithm \ref{alg:free-rwapg}), with other APG algorithms in the literatures: the V-FISTA, and M-FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}.
         We implemented and compare V-FISTA, M-FISTA from Beck, and Algorithm \ref{alg:free-rwapg} given this section. 
@@
 
-            \subsubsection{Logistic regression}
+        \subsubsection{Discussion}
+            We does not and cannot claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in the literatures. 
+            Our goal here is to show that this silly idea is absolutely ungrounded. 
+            However, two things are clear. FR-WAPG performs better than V-FISTA and it doesn't require prior knowledge on parameter $L, \mu$.
 

### 2025-01-14 Notebook LaTEX/R-WAPG/paper3.tex

@@
         We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart.
-        The theoretical analysis for the convergence of Free R-WAPG remains elusive.
-
+
+        \todoinline{This will be written once most of the contents in the paper are settled. 
+        }
         \par
@@
             Finally, a similar triangle for formulation of FISTA can be found in Equation (2), (3), (4) in \cite{chambolle_convergence_2015}. 
-            To see graphical visualization on why such term is used to describe the APG algorithm in the literatures, see (3.1, 4.1) in Lee et al.
-\cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}.
+            To see graphical visualization on why such term is used to describe the APG algorithm in the literatures, see 
+            \todo{
+                $\blacksquare$ Add these. $\blacksquare$ Cite these. 
+            }{(3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}}. 
+            \todoinline{\noindent
+                The term ``Method of Similar Triangle'' specific to this particular representation of AGM. 
+                For more information, see:  
+                \begin{enumerate}
+                    \item 3.1, 4.1 in Jongmin Lee et al., ``A geometric structure of Acceleration and its role in making gradients small''
+                    \item The entirety of Ahn and Sra's paper ``PPM interpretation of Nesterov's accelerated gradient. ''. 
+                \end{enumerate}
+            }
 

### 2025-01-14 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

@@
         \subsubsection{Discussion}
-            We does not and cannot claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in the literatures. 
+            We do not claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in the literatures. 
             Our goal here is to show that this silly idea is absolutely ungrounded. 
             However, two things are clear. FR-WAPG performs better than V-FISTA and it doesn't require prior knowledge on parameter $L, \mu$. 
+            \par
+            The results of R-WAPG is relevent because the sequence $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg} is an R-WAPG sequence. 
+            Let $\tilde \mu_k$ be an estimate produced by the algorithm then it satisfies that $\tilde \mu_k/ L \in (0, 1)$.
+            Let $q = \tilde \mu_k/L$, inductively assume that $\alpha_k \in (0, 1)$, then 
+            \begin{align*}
+                \alpha_{k + 1} 
+                &= 
+                (1/2)\left(
+                    q - \alpha_k^2 + \sqrt{(q - \alpha_k^2)^2 + 4 \alpha_k^2}
+                \right)
+                \\
+                &= 
+                (1/2)\left(
+                    q - \alpha_k^2 + \sqrt{
+                        (\alpha_k^2 - q + 2)^2 + 2q - 4
+                    }
+                \right)
+                \\
+                &< 
+                (1/2)\left(
+                    q - \alpha_k^2 + \sqrt{
+                        (\alpha_k^2 - q + 2)^2
+                    }
+                \right) \le 1. 
+            \end{align*}
+            Here we used the assumption that $q \in (0, 1)$ so $2q - 4 < 0$ always. 
+            Therefore, $\alpha_k \in (0, 1)$. 
+            In the very unlikely case when $q = 1$
 

### 2025-01-14 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

@@
         Finally, the entire LHS of \eqref{ineq:stepwise-lya-2} equals to the RHS of \eqref{eqn:stepwise-lya-proof-eqn3.2}. 
-        Going from \eqref{eqn:stepwise-lya-proof-eqn3.2} to \eqref{ineq:stepwise-lya-proof-ineq4}, we used Theorem \ref{thm:prox-grad-ineq} which yields the inequality that we want to prove. 
+        Going from \eqref{eqn:stepwise-lya-proof-eqn3.2} to \eqref{ineq:stepwise-lya-proof-ineq4}, we used Theorem \ref{thm:prox-grad-ineq} which yields the desired inequality. 
         \par
@@
             To see graphical visualization on why such term is used to describe the APG algorithm in the literatures, see 
-            \todo{
-                $\blacksquare$ Add these. $\blacksquare$ Cite these. 
-            }{(3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}}. 
-            \todoinline{\noindent
-                The term ``Method of Similar Triangle'' specific to this particular representation of AGM. 
-                For more information, see:  
-                \begin{enumerate}
-                    \item 3.1, 4.1 in Jongmin Lee et al., ``A geometric structure of Acceleration and its role in making gradients small''
-                    \item The entirety of Ahn and Sra's paper ``PPM interpretation of Nesterov's accelerated gradient. ''. 
-                \end{enumerate}
-            }
+            (3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}. 
+            % \todoinline{\noindent
+            %     The term ``Method of Similar Triangle'' specific to this particular representation of AGM. 
+            %     For more information, see:  
+            %     \begin{enumerate}
+            %         \item 3.1, 4.1 in Jongmin Lee et al., ``A geometric structure of Acceleration and its role in making gradients small''
+            %         \item The entirety of Ahn and Sra's paper ``PPM interpretation of Nesterov's accelerated gradient. ''. 
+            %     \end{enumerate}
+            % }
 
@@
         \subsubsection{LASSO}
-            This section present results of numerical experiment for solving the (least absolute shrinkage and selection operator) LASSO problem proposed by \hl{Tibshirani} \cite{tibshirani_regression_1996}.
+            This section present results of numerical experiment for solving the (least absolute shrinkage and selection operator) LASSO problem proposed by Tibshirani \cite{tibshirani_regression_1996}.
             The problem of LASSO has smooth, nonsmooth additive and the problem is given by: 
@@
             We do not claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in the literatures. 
-            Our goal here is to show that this silly idea is absolutely ungrounded. 
-            However, two things are clear. FR-WAPG performs better than V-FISTA and it doesn't require prior knowledge on parameter $L, \mu$. 
-            \par
-            The results of R-WAPG is relevent because the sequence $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg} is an R-WAPG sequence. 
+            Our numericaly experiments are explorative. 
+            Nontheless, two things are clear. FR-WAPG performs better than V-FISTA on the first hundreds of iterations and it doesn't require prior knowledge on parameter $L, \mu$. 
+            \par
+            From a theoretical perspective, the results of R-WAPG is relevent to some degree because the sequence $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg} is an R-WAPG sequence.
             Let $\tilde \mu_k$ be an estimate produced by the algorithm then it satisfies that $\tilde \mu_k/ L \in (0, 1)$.
@@
             Therefore, $\alpha_k \in (0, 1)$. 
-            In the very unlikely case when $q = 1$
+            In the very unlikely case when $q = 1$, Algorithm \ref{alg:free-rwapg} has $\theta_k = 0$, and it performs one step of proximal gradient descent. 
+            The difficulty here is that it's impossible to know the sequence $(\alpha_k)_{k \ge 0}$ without running the algorithm. 
+            It would require more knowledge about the trajectory taken for a specific initial guess. 
+            \par 
+            From a practical point of view, the numerical experiments shows that at the start, the estimate for $\mu$ can be very lose.
+            This is partially explained by the remark of of Proposition \ref{prop:stepwise-lyapunov}. 
+            It also showed that the function value gives very similar charactercteristics of M-FISTA. 
+            This hinted at the fact that the sequence $(\alpha_k)_{k \ge 0}$ may has something to do with restarting.
+            \par
+            Finally, we note that in practice, we observed that the convergence of gradient mapping $\mathcal G_L(y_k)$ becomes more difficult and the algorithm may not be able to terminate for certain objectives.
 

### 2025-01-14 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes, fixes

@@
     \noindent
-
-    \todo{Write this abstract when finishing. }
+    We analyze the accelerated proximal gradient method where the sequence that controls the momentum term is much weaker than the Nesterov's rule. 
+    Our setting is the convex optimization problem $F^* = \min_x\{f(x) + g(x)\}$ where $f$ is $L$ Lipschitz smooth and $\mu\ge 0$ strongly convex and $g$ is closed and convex. 
+    The new generic algorithm R-WAPG (Relaxed Weak Accelerated Proximal Gradient) shows an upper bound on the optimality gap $F(x_k) - F^*$ for any arbitrary choices of extrapolation parameters of updating $y_{k + 1} = x_{k + 1} - \theta_k(x_{k + 1} - x_k)$.
+    R-WAPG is a generic algorithm that has a has one convergence claim that unifies the convex and strongy convex cases. 
+    R-WAPG can describes major Euclidean variants of the FISTA. 
+    We showed convergence results for several notable variants of FISTA found in the literatures. 
+    Inspired by a small detailed in the proof, explorative numerical experiments were conducted to show the convergence of R-WAPG where the momentum sequence is produced by using Bregman Divergence of $f$ on sucessive iterate $y_{k + 1}, y_{k}$.
+
 \end{abstract}
-\todo{Remember to update these subject classificiations. }
-{
+\todo{Remember to update these subject classifications. }{
     \noindent{\bfseries 2010 Mathematics Subject Classification:}
-    Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
+    Primary 65K10, 90C25, 90C30; Secondary 65Y20. 
     \noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method. 
 }
+
 \section{Introduction}
     \subsection{Motivations}
-        For simplicity consider minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$ . 
+        For simplicity consider minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$. 
         Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$.
@@
         We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart.
-
-        \todoinline{This will be written once most of the contents in the paper are settled. 
-        }
         \par
@@
     \par
-    Assume $L$ given is an upper bound of the Lipschitz smoothness constant of $f$ so th line search subroutine is never triggered. 
+    Assume $L$ given is an upper bound of the Lipschitz smoothness constant of $f$, so the line search subroutine is never triggered. 
     Then the algorithm calls $f(\cdot)$ two times, and $\nabla f(\cdot)$ once per iteration. 
@@
     And finally, it evaluates proximal of $g$ at $y_k - L^{-1}\nabla f(y_k)$ once. 
-
+    \par 
+    From a theoretical perspective, the convergence result (Proposition \ref{prop:wagp-convergence}) of R-WAPG is relevant to some degree because the sequence $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg} is an R-WAPG sequence.
+    Let $\tilde \mu_k$ be an estimate produced by the algorithm then it satisfies that $\tilde \mu_k/ L \in (0, 1)$.
+    Let $q = \tilde \mu_k/L$, inductively assume that $\alpha_k \in (0, 1)$, then 
+    \begin{align*}
+        \alpha_{k + 1} 
+        &= 
+        (1/2)\left(
+            q - \alpha_k^2 + \sqrt{(q - \alpha_k^2)^2 + 4 \alpha_k^2}
+        \right)
+        \\
+        &= 
+        (1/2)\left(
+            q - \alpha_k^2 + \sqrt{
+                (\alpha_k^2 - q + 2)^2 + 2q - 4
+            }
+        \right)
+        \\
+        &< 
+        (1/2)\left(
+            q - \alpha_k^2 + \sqrt{
+                (\alpha_k^2 - q + 2)^2
+            }
+        \right) \le 1. 
+    \end{align*}
+    Here we used the assumption that $q \in (0, 1)$ so $2q - 4 < 0$ always. 
+    It is not hard to see that $\alpha_{k + 1} > 0$ as well. 
+    Therefore, $\alpha_k \in (0, 1)$. 
     \subsection{Numerical experiments}
@@
             The solid line in the ribbon is the median value of $\delta_k$ across all experiment, the ribbon gives the maximum, minimum value of $\delta_k$ for each iteration across all experiments. 
-            R-WAPG initially behaves similar to M-FISTA, but as the iteration goes on, it started to behave like V-FISTA.  
+            FR-WAPG initially behaves similar to M-FISTA, but as the iteration goes on, it started to behave like V-FISTA.  
             \par 
@@
             \end{enumerate}
-            Experiments were conducted using V-FISTA, M-FISTA and R-WAPG with $(M, N) = (64, 256)$ and $(M, N) = (64, 128)$. 
+            Experiments were conducted using V-FISTA, M-FISTA and FR-WAPG with $(M, N) = (64, 256)$ and $(M, N) = (64, 128)$. 
             Matrix $A$ is fixed and the for all test algorithms and all repetitions. 
@@
 
-        \subsubsection{Discussion}
-            We do not claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in the literatures. 
-            Our numericaly experiments are explorative. 
-            Nontheless, two things are clear. FR-WAPG performs better than V-FISTA on the first hundreds of iterations and it doesn't require prior knowledge on parameter $L, \mu$. 
-            \par
-            From a theoretical perspective, the results of R-WAPG is relevent to some degree because the sequence $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg} is an R-WAPG sequence.
-            Let $\tilde \mu_k$ be an estimate produced by the algorithm then it satisfies that $\tilde \mu_k/ L \in (0, 1)$.
-            Let $q = \tilde \mu_k/L$, inductively assume that $\alpha_k \in (0, 1)$, then 
-            \begin{align*}
-                \alpha_{k + 1} 
-                &= 
-                (1/2)\left(
-                    q - \alpha_k^2 + \sqrt{(q - \alpha_k^2)^2 + 4 \alpha_k^2}
-                \right)
-                \\
-                &= 
-                (1/2)\left(
-                    q - \alpha_k^2 + \sqrt{
-                        (\alpha_k^2 - q + 2)^2 + 2q - 4
-                    }
-                \right)
-                \\
-                &< 
-                (1/2)\left(
-                    q - \alpha_k^2 + \sqrt{
-                        (\alpha_k^2 - q + 2)^2
-                    }
-                \right) \le 1. 
-            \end{align*}
-            Here we used the assumption that $q \in (0, 1)$ so $2q - 4 < 0$ always. 
-            Therefore, $\alpha_k \in (0, 1)$. 
+\section{Discussion}
+    We do not claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in literatures. 
+    Our numerical experiments are explorative, and our theories are our best attempts at making sense of what is happening, and we did it directly with elementary algebra. 
+    Nonetheless, two things are clear from the numerical experiments.
+FR-WAPG performs better than V-FISTA on the first hundreds of iterations, and it doesn't require prior knowledge on parameter $L, \mu$.
+    \par
+
     In the very unlikely case when $q = 1$, Algorithm \ref{alg:free-rwapg} has $\theta_k = 0$, and it performs one step of proximal gradient descent. 
@@
     \par 
-            From a practical point of view, the numerical experiments shows that at the start, the estimate for $\mu$ can be very lose.
-            This is partially explained by the remark of of Proposition \ref{prop:stepwise-lyapunov}. 
+    From a practical point of view, the numerical experiments show that at the start of the few iterations, the estimate for $\mu$ can be overestimated.
+    This is partially explained by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
     It also showed that the function value gives very similar charactercteristics of M-FISTA. 
-            This hinted at the fact that the sequence $(\alpha_k)_{k \ge 0}$ may has something to do with restarting.
-            \par
-            Finally, we note that in practice, we observed that the convergence of gradient mapping $\mathcal G_L(y_k)$ becomes more difficult and the algorithm may not be able to terminate for certain objectives.
+    Which is interesting. 
+    \par
+    Finally, we observed that the convergence of gradient mapping $\mathcal G_L(y_k)$ becomes more difficult and the algorithm may not be able to terminate for certain objectives.
 

### 2025-01-15 Notebook LaTEX/R-WAPG/paper3.tex
>w<, updates

@@
     Our setting is the convex optimization problem $F^* = \min_x\{f(x) + g(x)\}$ where $f$ is $L$ Lipschitz smooth and $\mu\ge 0$ strongly convex and $g$ is closed and convex. 
-    The new generic algorithm R-WAPG (Relaxed Weak Accelerated Proximal Gradient) shows an upper bound on the optimality gap $F(x_k) - F^*$ for any arbitrary choices of extrapolation parameters of updating $y_{k + 1} = x_{k + 1} - \theta_k(x_{k + 1} - x_k)$.
+    A much weaker condition of extrapolation parameters in $y_{k + 1} = x_{k + 1} - \theta_k(x_{k + 1} - x_k)$ is precisely characterized to show an upper bound on the optimality gap $F(x_k) - F^*$ using a generic algorithm R-WAPG (Relaxed Weak Accelerated Proximal Gradient) we proposed.
     R-WAPG is a generic algorithm that has a has one convergence claim that unifies the convex and strongy convex cases. 
@@
     We showed convergence results for several notable variants of FISTA found in the literatures. 
-    Inspired by a small detailed in the proof, explorative numerical experiments were conducted to show the convergence of R-WAPG where the momentum sequence is produced by using Bregman Divergence of $f$ on sucessive iterate $y_{k + 1}, y_{k}$.
+    Inspired by a small detail in the proof, explorative numerical experiments were conducted to show the convergence of R-WAPG where the extrapolation sequence is generated using Bregman Divergence of $f$ on sucessive iterate $y_{k + 1}, y_{k}$.
 
 \end{abstract}
-\todo{Remember to update these subject classifications. }{
+
 \noindent{\bfseries 2010 Mathematics Subject Classification:}
-    Primary 65K10, 90C25, 90C30; Secondary 65Y20. 
-    \noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method. 
-}
+Primary 90C30, 90C25, 65K10; Secondary 65Y20. 
+\noindent{\bfseries Keywords: } Convex optimization, Nesterov's acceleration, Proximal gradient, Convergence rate.
 
@@
         In Theorem \ref{thm:fixed-momentum-fista}, it demonstrates that R-WAPG frameworks gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex.
+        Finally, we did the tedious work and present three equivalent forms of R-WAPG in Section \ref{sec:rwapg-equiv-repr} that are comparable to notable Euclidean variants of FISTA and beyond.
+This shows the descriptive power of our R-WAPG framework.
         \par
@@
         Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG algorithm and characterize sufficient conditions for R-WAPG sequence to derive the optimality upper bound in Proposition \ref{prop:wagp-convergence}.
-        Section \ref{sec:rwapg-equiv-repr} gives three equivalent representations of the R-WAPG algorithms that are comparable to instances of Accelerated Proximal Gradient algorithm found in the literatures.
+        Section \ref{sec:rwapg-equiv-repr} gives three equivalent representations of the R-WAPG algorithms that are comparable to instances of APG found in the literatures. 
         Section \ref{sec:rwapg-literatures} formulates FISTA, and V-FISTA sequences as instance of the R-WAPG sequences.
@@
     \begin{proof}
-        The proof is a direct proof. 
+        We use proof by induction. 
         Here we drop the subscript $k$, $k + 1$ on $\gamma_{k}, \hat \gamma_{k + 1}$ because they are fixed throughout the proof, and it makes for better readability! 
@@
         We started with $F(x_{k + 1}) + R_{k + 1} \iff \eqref{eqn:stepwise-lya-proof-eqn1}$, 
-        then $\hat \gamma/2\Vert v_{k + 1} - x^*\Vert^2 \iff \eqref{expr:stepwise-lya-expr2.2}$ via \eqref{eqn:stepwise-lya-proof-eqn2}. 
-        We add (\ref{eqn:stepwise-lya-proof-eqn2}), (\ref{expr:stepwise-lya-expr2.2}) to get $\eqref{eqn:stepwise-lya-proof-eqn3.1} \iff \eqref{eqn:stepwise-lya-proof-eqn3}$.
+        then $\hat \gamma/2\Vert v_{k + 1} - x^*\Vert^2 = \eqref{expr:stepwise-lya-expr2.2}$ via \eqref{eqn:stepwise-lya-proof-eqn2}. 
+        We add (\ref{eqn:stepwise-lya-proof-eqn1}), (\ref{expr:stepwise-lya-expr2.2}) to get \eqref{eqn:stepwise-lya-proof-eqn3.1}. 
         Finally, the entire LHS of \eqref{ineq:stepwise-lya-2} equals to the RHS of \eqref{eqn:stepwise-lya-proof-eqn3.2}. 
@@
         So $\gamma_k, \hat \gamma_{k + 1}, \alpha_k$ fits Definition \ref{def:stepwise-wapg}. 
-        for all $k \ge 1$, $R_k$ satisfies \eqref{eqn:stepwise-lya-1}, hence using Proposition \ref{prop:stepwise-lyapunov} and unroll recursively : 
+        for all $k \ge 1$, $R_k$ satisfies \eqref{eqn:stepwise-lya-1}, hence unroll recursively using Proposition \ref{prop:stepwise-lyapunov}: 
         {\small
@@
             \end{align*}
+            Then this fits into the format of abstract similar triangle form. 
             We claim that these parameters satisfy $L\delta_k = 1 + \tau_k + \xi_k$. 
@@
             \begin{align*}
-                \frac{1 + \xi_k}{\alpha_k}
+                L\delta_k = \frac{1 + \xi_k}{\alpha_k}
                 &= 
@@
             Hence,  $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}(x_{k + 1} - x_k)\; \forall k \ge 1$ by Proposition \ref{prop:abs-st-form}.
-            Therefore, substituting it gives: 
+            Therefore, substituting $\xi_k$ gives: 
             \begin{align*}
@@
         Start by considering the update rule for $v_k$ from the Definition \ref{def:r-wapg-st-form} which has for all $k \ge 1$: 
-        \begin{align*}
+        \begin{align}
             v_{k + 1} &= 
@@
             (L \alpha_{k + 1} - \mu)x_{k + 1} + (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k).
-        \end{align*}
+            \label{eqn:third-eqv-repr-eqn1} 
+        \end{align}
         Next, we simplify the update $y_{k}$ by Definition \ref{def:r-wapg-st-form} for all $k \ge 1$: 
@@
         \end{align*}
-        Now substituting $v_{k + 1}$ into $y_{k + 1}$, so it has for all $k\ge 1$: 
+        Using RHS of \eqref{eqn:third-eqv-repr-eqn1} to substitute $L\alpha_{k + 1} - \mu$ into $y_{k + 1}$, so it has for all $k\ge 1$: 
         {\small
@@
             \left(
-                (L\alpha_{k + 1} - \mu)x_{k + 1} + (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
+                (L - \mu)x_{k + 1} + (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
             \right)
@@
         \end{align*}
-        Going from the left to right on the fourth equality, we used $L\alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_kL\alpha_k^2 + \mu \alpha_{k + 1}$ with 
+        Going from the left to right on the fourth equality, we used $L\alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_kL\alpha_k^2 + \mu \alpha_{k + 1}$ established by: 
         \begin{align*}
@@
     Let $\tilde \mu_k$ be an estimate produced by the algorithm then it satisfies that $\tilde \mu_k/ L \in (0, 1)$.
-    Let $q = \tilde \mu_k/L$, inductively assume that $\alpha_k \in (0, 1)$, then 
+    Assuming inductively that $q = \tilde \mu_k/L$,  $\alpha_k \in (0, 1)$, then 
     \begin{align*}
@@
     Therefore, $\alpha_k \in (0, 1)$. 
+    In the very unlikely case when $q = 1$, Algorithm \ref{alg:free-rwapg} has $\theta_k = 0$, and it performs one step of proximal gradient descent. 
     \subsection{Numerical experiments}
         This section gives figures and visual for numerical experiments conducted using FR-WAPG algorithm (Algorithm \ref{alg:free-rwapg}), with other APG algorithms in the literatures: the V-FISTA, and M-FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}.
-        We implemented and compare V-FISTA, M-FISTA from Beck, and Algorithm \ref{alg:free-rwapg} given this section. 
-        The results of the experiments are visualized and the setup of the numerical experiments are described  in the sections that follows. 
+        We implemented in Julia \cite{bezanson_julia_2017} and compare V-FISTA, M-FISTA from Beck, and Algorithm \ref{alg:free-rwapg} given this section. 
+        Focusing on iteration complexities of the algorithm, the results of the experiments are visualized and the setup of the numerical experiments are described  in the sections that follows. 
         \par
@@
     We do not claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in literatures. 
-    Our numerical experiments are explorative, and our theories are our best attempts at making sense of what is happening, and we did it directly with elementary algebra. 
+    Our numerical experiments are explorative and we hope to inspire. 
+    The presented theories (Proposition \ref{prop:stepwise-lyapunov}, \ref{prop:wagp-convergence}) are our best attempts at making sense of what is happening, and we did it directly with elementary algebra.
+    In addition, we provided some helpful results on the equivalent representations of R-WAPG to illustrate the descriptive power of the R-WAPG framework. 
     Nonetheless, two things are clear from the numerical experiments. 
@@
     \par
-
-    In the very unlikely case when $q = 1$, Algorithm \ref{alg:free-rwapg} has $\theta_k = 0$, and it performs one step of proximal gradient descent. 
-    The difficulty here is that it's impossible to know the sequence $(\alpha_k)_{k \ge 0}$ without running the algorithm. 
-    It would require more knowledge about the trajectory taken for a specific initial guess. 
-    \par 
-    From a practical point of view, the numerical experiments show that at the start of the few iterations, the estimate for $\mu$ can be overestimated.
+    Our theories are somewhat relevant to FR-WAPG since it can partially describe an upper bound of the optimality gap with any sequence of $\alpha_k \in (0, 1)$. 
+    Unfortunately, it is difficult to know the sequence $(\alpha_k)_{k \ge 0}$ without running the algorithm. 
+    It would require knowledge about the trajectory taken for a specific initial guess, and the property of $D_f$, the Bregman Divergence of the smooth part. 
+    We feel that the breakthrough in understanding may not come from elementary results.  
+    \par 
+    From a practical point of view, the numerical experiments show that in the beginning of the algorithm, the estimate for $\mu$ can be overestimated.
     This is partially explained by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
-    It also showed that the function value gives very similar charactercteristics of M-FISTA. 
-    Which is interesting. 
-    \par
+    It also showed that the algorithm performs with mixed charactercteristics of M-FISTA and V-FISTA and it's just fascinating. 
     Finally, we observed that the convergence of gradient mapping $\mathcal G_L(y_k)$ becomes more difficult and the algorithm may not be able to terminate for certain objectives.

### 2025-01-16 Notebook LaTEX/Proposal/presentation.tex
>w<, changes, a lot

\documentclass[11pt]{beamer}
\usetheme{Madrid}
\usepackage[utf8]{inputenc}

\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\DeclareMathOperator{\argmin}{argmin}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{wrapfig}
\usepackage{subcaption}
\graphicspath{{.}}

\author{Generic Name}
\title{Title for Super Fancy Stuff}
% Informe o seu email de contato no comando a seguir
% Por exemplo, alcebiades.col@ufes.br
\newcommand{\email}{lalala@lala.la}
\setbeamercovered{transparent}
\setbeamertemplate{navigation symbols}{}
%\logo{}
\institute[]{Some Super Fancy Institution}
\date{\today}
\subject{Subject Title }

% ---------------------------------------------------------
% Selecione um estilo de referência
\bibliographystyle{IEEEtran}

%\bibliographystyle{abbrv}
%\setbeamertemplate{bibliography item}{\insertbiblabel}
% ---------------------------------------------------------

% ---------------------------------------------------------
\newtheorem{remark}{Remark}
\newtheorem{assumption}{Assumption}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

\begin{frame}{ToC}
    \tableofcontents
\end{frame}

% \section{This is the First Section}
%     \subsection{Taxonomy of Proximal type of Methods}
%         \begin{frame}{Frame Title}

%             \begin{block}{Formula Presented in Block}
%                 \begin{align}
%                     \min_{x} g(x) + h(x)
%                 \end{align}    
%             \end{block}

%             \begin{itemize}
%                 \item [1.]Throughout this presentation, we assume the objective of a function $f$ is the sum of 2 functions.
%                 \item [2.]We are interested in the paper: FISTA (Fast Iterative-Shrinkage Algorithm) by Beck and Teboulle \cite{paper:FISTA}. 
%                 \pause 
%                 \item [1.] When $h = \delta_Q$ with $Q$ closed and convex with $Q\subseteq \text{ri}\circ \text{dom}(g)$, we use projected subgradient. 
%                 \item [2.] When $g$ is \textbf{\emph{strongly smooth}} and $h$ is \textbf{closed convex proper} whose proximal oracle is easy to compute, we consider the use of FISTA. 
%             \end{itemize}

%         \end{frame}

%     \subsection{The Proximal Operator}
%         \begin{frame}{Frame Title}
%             \begin{definition}[Definition of Something]
%                 Let $f$ be convex closed and proper, then the proximal operator parameterized by $\alpha > 0$ is a non-expansive mapping defined as: 
%                 \begin{align*}
%                     \text{prox}_{f, \alpha}(x) := 
%                     \arg\min_{y}\left\lbrace
%                         f(y) + \frac{1}{2\alpha} \Vert y - x\Vert^2
%                     \right\rbrace. 
%                 \end{align*}
%             \end{definition}  
%             \begin{remark}
%                 When $f$ is convex, closed, and proper, 
%             \end{remark}
%         \end{frame}

%         \begin{frame}{Prox is the Resolvant of Subgradient}
%             \begin{lemma}[The Lemma]\label{lemma:prox_alternative_form}
%                 When the function $f$ is convex closed and proper, the $\text{prox}_{\alpha, f}$ can be viewed as the following operator $(I + \alpha \partial f)^{-1}$. 
%             \end{lemma}
%             \begin{proof}
%                 Minimizer satisfies zero subgradient condition, 
%                 {\scriptsize
%                 \begin{align*}
%                     \mathbf 0 &\in \partial
%                     \left[
%                         \left.
%                             f(y) + \frac{1}{2\alpha} \Vert y - x\Vert^2 
%                         \right| y
%                     \right](y^+)
%                     \\
%                     \mathbf 0 &\in \partial f(y^+) + \frac{1}{\alpha}(y^+ - x)
%                     \\
%                     \frac{x}{\alpha} &\in 
%                     (\partial f + \alpha^{-1}I)(y^+)
%                     \\
%                     x &\in 
%                     (\alpha \partial f + I)(y^+)
%                     \\
%                     y &\in (\alpha\partial f+ I)^{-1}(x).
%                 \end{align*}
%                 }
%             \end{proof}
%         \end{frame}

%     \subsection{Strong Smoothness}
%         \begin{frame}{Equivalence of Strong Smoothness and Lipschitz Gradient}
%             \begin{theorem}[Lipschitz Gradient Equivalence under Convexity]
%                 Suppose $g$ is differentiable on the entire of $\mathbb E$. It is closed convex proper. It is strongly smooth with parameter $\alpha$ if and only if the gradient $\nabla g$ is globally Lipschitz continuous with a parameter of $\alpha$ and $g$ is closed and convex. 
%                 \begin{align*}
%                     \Vert \nabla g(x) -\nabla g(y)\Vert \le 
%                     \alpha 
%                     \Vert x - y \Vert\quad \forall x, y\in \mathbb E
%                 \end{align*}
%             \end{theorem}
%             \begin{proof}
%                 Using line integral, we can prove Lipschitz gradient implies strong smoothness without convexity. The converse requires convexity and applying generalized Cauchy Inequality to (iv) in Theorem 5.8 for Beck's textbook \cite{book:first_order_opt}. 
%             \end{proof}

%         \end{frame}
%     \subsection{A Major Assumption}    
%         \begin{frame}{A Major Assumption}
%             \begin{assumption}[Convex Smooth Nonsmooth with Bounded Minimizers]\label{assumption:1}
%                 We will assume that $g:\mathbb E\mapsto \mathbb R$ is \textbf{strongly smooth} with constant $L_g$ and $h:\mathbb E \mapsto \bar{\mathbb R}$ \textbf{is closed convex and proper}. We define $f := g + h$ to be the summed function and $\text{ri}\circ \text{dom}(g) \cap \text{ri}\circ \text{dom}(h) \neq \emptyset$. We also assume that a set of minimizers exists for the function $f$ and that the set is bounded. Denote the minimizer using $\bar x$. 
%             \end{assumption}
%         \end{frame}

% \section{A New Fancy Section}
%     \subsection{A Fancy Subsetction for Algorithm}
%         \begin{frame}{The Accelerated Proximal Gradient Method}
%             \begin{block}{Momentum Template Method}
%                 \begin{algorithm}[H]
%                     \begin{algorithmic}[1]
%                         \STATE{\textbf{Input:} $x^{(0)}, x^{(-1)}, L, h, g$; 2 initial guesses and stepsize L}
%                         \STATE{$y^{(0)} = x^{(0)} + \theta_k (x^{(0)} - x^{(-1)})$}
%                         \FOR{$k = 1, \cdots, N$}
%                             \STATE{$x^{(k)} = \text{prox}_{h, L^{-1}}(y^{(k)} + L^{-1}\nabla g(y^{(k)})) =: \mathcal P_{L^{-1}}^{g, h}(y^{(k)})$}
%                             \STATE{$y^{(k + 1)} = x^{(k)} + \theta_k(x^{(k)} - x^{(k - 1)})$}
%                         \ENDFOR
%                     \end{algorithmic}
%                     \caption{Template Proximal Gradient Method With Momentum}\label{alg:fista_template}
%                 \end{algorithm}
%             \end{block}
%         \end{frame}

% \section{Numerical Experiments}
%     \input{Sections/sectionfile.tex}

\section{References}
    \begin{frame}{References}

        \bibliography{references/proposal.bib}
    \end{frame}

\end{document}

### 2025-01-16 Notebook LaTEX/Proposal/proposal.tex
>w<, changes, a lot

--- 2025-01-10 Notebook LaTEX/Proposal/main.tex
@@
         \min_{x \in \RR^n} \left\lbrace
-            F(x): f(x) + g(x)
+            F(x):= f(x) + g(x)
         \right\rbrace.
     \end{align}\label{eqn:additive-comp-obj}
-    Unless specified, assume $f:\RR^n \rightarrow \RR$ is $L$-Lipscthiz smooth $\mu \ge 0$ strongly convex and $g:Q \rightarrow \overline \RR$ is convex. 
+    Unless specified, assume $f:\RR^n \rightarrow \RR$ is $L$-Lipscthiz smooth $\mu \ge 0$ strongly convex and $g:\RR^n \rightarrow \overline \RR$ is convex. 
     This type of problem is referred to as additive composite problems in the literature. 
@@
     \end{enumerate}
-    The good news is we have definitive answers for all questions by our own efforts of research. 
-    Section \ref{sec:unify-nes-acceleration}, proposes the method of ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)'' as the foundation to describe several variants of Accelerated proximal gradient method in the literatures.
-    The convergence theories of R-WAPG allows us to model convergence of accelerated proximal gradient method where the momentum sequence doesn't strictly follow the conditions presented in the literatures.
-    The descriptive power of R-WAPG allows convergence analysis for all the variants using one single theorem. 
+    The good news is we have definitive answers for all questions in our complete draft paper. 
+    \par
+    In this proposal we explore the Goldilocks zones between these topics: Nesterov's acceleration, algorithms with inexact evaluation of the proximal point operator, and applications.  
+    We want to identify the ``chemistry'' between various properties of functions and the affect it has on the designs/behaviors of first order algorithm for continuous optimization. 
+    \par
+    \textbf{Organizations now follows.} 
+    Section \ref{sec:unify-nes-acceleration}, proposes the method of ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)'' as the foundation to describe several Euclidean variants of Accelerated Proximal Gradient (APG) method in the literatures.
+    The convergence analysis of R-WAPG gives convergence of APG the momentum is much weaker compare to the Nesterov's update rule. 
+    R-WAPG can is generic and can describe well-established variants of FISTA in the literatures with alternative choices of step sizes and beyond. 
     \par
     Section \ref{sec:free-rwapg} proposes a practical algorithm that exploits a specific term in the proof of R-WAPG to achieve faster convergence for solving (\ref{eqn:additive-comp-obj}) without restarting and knowing parameter $L, \mu$ in prior.
-    Results of numerical experiments are presented. 
+    Numerical experiments are presented which shows the competitiveness of our algorithm. 
+    Potential future direction of research is given by the end of the section for the R-WAPG framework. 
     \par
@@
     The end of Section \ref{sec:catalyst} points out potential future direction of research of Catalyst Acceleration.
-    % \par
-    % Section \ref{sec:inexact-prox}, \ref{sec:nes-acc-ncnvx} preview literatures in nonsmooth optimization frontier research where progress and impacts can be made.  
-    \subsection{Theme of the research}
-        This section specifies a theme of the research in this proposal. 
-        Firstly, we explore the Goldilocks zones between these topics: Nesterov's acceleration, algorithms with inexact evaluation of the proximal point operator, and applications.  
-        In doing so, we identify the ``chemistry'' between various properties of functions and the affect it has on the designs/behaviors of first order algorithm for continuous optimization.
 
@@
     This section contains the basics of contents from convex optimization, and variational analysis. 
-    \par
-    Notations. 
-    \begin{enumerate}
-        \item $\overline \RR := \RR \cup \{\infty, -\infty\}$. 
-    \end{enumerate}
+    Throughout, we adopt the notation $\overline \RR := \RR \cup \{\infty, -\infty\}$. 
     \subsection{Fundamentals in non-convex analysis}
-        Let the ambient space be $\RR^n$ equipped with inner product and 2-norm. 
-        Let $O$ be an open subset of $\RR^n$, the weakest assumption we are making for the objective function $F: O \subseteq \RR^n \rightarrow \RR$ for optimization problem is Local Lipschitz Continuity.
+        Let the ambient space be $\RR^n$ equipped with inner product $\langle \cdot, \cdot\rangle$ and 2-norm $\Vert \cdot\Vert$. 
+        Let $O$ be an open subset of $\RR^n$, the weakest assumption we make for objective function $F: O \subseteq \RR^n \rightarrow \RR$ of an optimization problem is local Lipschitz continuity. 
         The assumption of local Lipschitz continuity is weak enough to describe most problems in applications, and strong enough to avoid most pathologies in analysis.
@@
         Define $F$ to be closed, proper and convex in this section. 
-        When $F$ is convex, the limiting subgradient and the regular subgradient reduced to the following definition:
-        \begin{align*}
-            \partial F(x) := \left\lbrace
+        When $F$ is convex, the limiting subgradient and the regular subgradient reduced to the following: 
+        \begin{align*}
+            \partial F(x) = \left\lbrace
                 v \in \RR^n \left|\; 
@@
         A convex function is locally Lipschitz in the relative interior of its domain, denoted as $\reli(\dom(F))$. 
-        So it has $\reli(\dom F)\subseteq \dom(\partial F) \subseteq \dom F$. 
+        So it has 
+        \todo{
+            $\square$ Add Rockafellar's red book \\ $\square$ Cite Section 10 (pg 82) of that book
+        }
+        \hl{$\reli(\dom F)\subseteq \dom(\partial F) \subseteq \dom F$.} 
         \par
@@
         \end{align*}
-        This condition is stronger than differentiability. 
-        When $F$ convex, it has descent lemma: 
+        When $F$ convex, then it has descent lemma: 
         \begin{align*}
@@
         \end{align*}
-        When $F$ is convex, the converse holds. 
+        The converse holds under convexity as well. 
         The definitions that follow narrow things further for future discussions. 
         \begin{definition}[Strong convexity]\label{def:s-cnvx}
-            A function $F:\RR^n \rightarrow \overline \RR$ is $\mu \ge 0$ strongly convex if and only if for any fixed $y \in \dom(\partial F)$, we have for all $x\in \RR^n$: 
+            A function $F:\RR^n \rightarrow \overline \RR$ is $\mu \ge 0$ strongly convex if and only if for all $y \in \dom(\partial F)$, $x\in \RR^n$: 
             \begin{align*}
@@
             The minimizer is unique whenever $\mu > 0$. 
-            For contradiction, assume $x$ is another minimizer, then $F(x) \neq F(\bar x)$, which is a direct contradiction. 
-            The quadratic growth condition over a set of minimizer is much weaker than convexity. 
+            For contradiction, assume $x \neq \bar x$ is another minimizer, then $F(x) \neq F(\bar x)$, which is a direct contradiction. 
+            This condition is called quadratic growth over the set of minimizer, it is much weaker than strong convexity. 
         \end{remark}
@@
         \subsubsection{Smooth, nonsmooth additive composite}\label{sssec:additive-composite}
-            In this section, we zoom in further. 
-            Suppose that $F:= f + g$ where $f:\RR^n \rightarrow \RR$ is convex, $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: \RR\rightarrow \overline \RR$ is convex. 
-            To make the discussion simpler, fix any $\beta \ge 0$ we define the following model functions as a $\RR^n \times \RR^n \rightarrow \overline \RR$: 
-            \begin{align*}
-                \widetilde{\mathcal M}^{\beta^{-1}}
+            This section zooms in further into the case of additive composite objective $F:= f + g$. 
+            Assume $f$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex, $g: \RR\rightarrow \overline \RR$ is closed convex. 
+            For all $\beta \ge 0$, define the proximal gradient, proximal point model functions as a mapping of $\RR^n \times \RR^n \rightarrow \overline \RR$: 
+            \begin{align*}
+                \widetilde{\mathcal M}^{\beta^{-1}}_F
                 (x; y)
@@
                 \\
-                \mathcal M^{\beta^{-1}}(x; y) 
+                \mathcal M^{\beta^{-1}}_F(x; y) 
                 &:= F(x) + \frac{\beta}{2}\Vert x - y\Vert^2.
             \end{align*}
-            Under convexity assumption in this section, both $\widetilde {\mathcal M} (\cdot; y),  {\mathcal M}(\cdot;y )$ is at least $\beta \ge 0$ strongly convex. 
+            Under the assumptions of this section, $\widetilde {\mathcal M}_F^{\beta^{-1}} (\cdot; y),  {\mathcal M}_F^{\beta^{-1}}(\cdot;y )$ are both $\beta + \mu$ strongly convex. 
             \begin{definition}[Proximal gradient operator]\label{def:proximal-gradient-operator}
-                Take $F := f + g$ where $g: \RR^n \rightarrow \overline \RR$ as defined in this section. 
+                % Take $F := f + g$ where $g: \RR^n \rightarrow \overline \RR$ as defined in this section. 
                 Define the proximal gradient operator $T_L$ on all $y \in \RR^n$: 
@@
             \begin{remark}
-                Under the assumption of this section, the mapping $T_L$ is a single-valued mapping, it has domain on the entire $\RR^n$, and it's a $3/2$ averaged operator. 
+                Under the assumption of this section, the mapping $T_L$ is a single-valued mapping on $\RR^n$ and it's  a $3/2$ averaged operator. 
             \end{remark}
             \begin{definition}[Gradient mapping operator]\label{def:gradient-mapping-operator}
-                Take $F := f + g$ as defined in this section. 
+                % Take $F := f + g$ as defined in this section. 
                 Define the gradient mapping operator $\mathcal G_L$ on all $y \in \RR^n$: 
                 \begin{align*}
-                    \mathcal G_L y:= L(y - T_L y). 
-                \end{align*}
-            \end{definition}
-
+                    \mathcal G_L (y):= L(y - T_L y). 
+                \end{align*}
+            \end{definition}
             \begin{lemma}[Proximal gradient model function]\;\\
-                Take $\widetilde{\mathcal M}^{L^{-1}}, \mathcal M^{L^{-1}}$ as defined in this section, we will have for all $x \in \RR^n$ that: 
-                \begin{align*}
-                    \widetilde{\mathcal M}^{L^{-1}}(x; y)
+                % Take $\widetilde{\mathcal M}^{L^{-1}}, \mathcal M^{L^{-1}}$ as defined in this section, 
+                For all $x \in \RR^n$, $\beta > 0$, it has: 
+                \begin{align*}
+                    \widetilde{\mathcal M}^{\beta^{-1}}_F(x; y)
                     &= 
-                    \mathcal M^{L^{-1}}(x; y)- D_f(x, y).
+                    \mathcal M^{\beta^{-1}}_F(x; y)- D_f(x, y).
                 \end{align*}
@@
             \begin{lemma}[A favorable property of gradient mapping]
-                Take $F:= f + g$ as defined in this section. 
-                Fix any $x \in \RR^n$. 
+                % Take $F:= f + g$ as defined in this section. 
+                For any $x \in \RR^n$. 
                 Then there exists $v \in \partial g(T_L x)$ such that $\mathcal G_L (x) = v + \nabla f(x)$. 
             \end{lemma}
-            \begin{remark}
-                This lemma still holds for non-convex $f$ under prox-boundedness and weak convexity and differentiability of $f$. 
-            \end{remark}
             \begin{lemma}[The proximal gradient inequality]\label{thm:prox-grad-ineq}
-                Take $F:= f + g$ as defined in this section. 
-                Fix any $y \in \RR^n$, then for all $x$, the proximal gradient inequality is true: 
+                % Take $F:= f + g$ as defined in this section. 
+                For all $y \in \RR^n$, $x \in \RR^n$, it has: 
                 \begin{align*}
                     (\forall x \in \RR^n)\quad 
-                    h(x)  - h(Ty) - \langle L(y - Ty), x - y\rangle
-                    - \frac{\mu}{2}\Vert x - y\Vert^2 - \frac{L}{2}\Vert y - Ty\Vert^2 
+                    F(x)  - F(T_Ly) - \langle L(y - T_Ly), x - y\rangle
+                    - \frac{\mu}{2}\Vert x - y\Vert^2 - \frac{L}{2}\Vert y - T_Ly\Vert^2 
                     &\ge 0. 
@@
     \subsection{Nesterov's estimating sequence technique}
-        The method of Nesterov's estimating was used for deriving accelerated gradient method, and their nonsmooth counterparts assuming function $F: \RR^n \rightarrow \overline{\RR}$ is convex and Lipschitz smooth.
-        We emphasize that the techniques derives the algorithm as well as proving its convergence rate. 
-        The estimating sequence is a technique searching for candidate algorithm with extrapolated momentum, and proving their convergence rate if possible. 
+        The derivation of APG was originally conceived by Nesterov's estimating sequence technique. 
+        We emphasize that the technique derives the algorithm and proves its convergence rate. 
         \par
         The method is widespread in the literatures, and the ideas behind it are tremendously useful. 
-        Güler \cite{guler_new_1992} used the method to design an accelerated proximal point method, which was the foundation of Catalyst Acceleration for variance reduced method in machine learning. 
-        Nesterov \cite{nesterov_accelerating_2008} used the technique to design an accelerated cubic regularized Newton's method. 
+        Güler \cite{guler_new_1992} used it to derive an accelerated proximal point method, which was instrumental to develop the Catalyst Acceleration framework. 
+        Nesterov \cite{nesterov_accelerating_2008} used it to conceive the accelerated cubic regularized Newton's method. 
         In (6.1.19) of Nesterov's book \cite{nesterov_lectures_2018}, it's used to derive a method of accelerated mirror descent. 
-        Finally, Geovani N. et al \cite{grapiglia_accelerated_2019} used it to derive an accelerated Newton's method for convex composite objective function. 
+        Finally, in Geovani N. et al \cite{grapiglia_accelerated_2019}, they used it to derive an accelerated Newton's method for convex composite objective function. 
         \par
@@
         \begin{definition}[Nesterov's estimating sequence]\label{def:nes-est-seq}
-            Let $\phi_k : \RR^n \rightarrow\RR$ for all $k \ge 0$ be a sequence of functions. 
-            We call this sequence of function a Nesterov's estimating sequence when it satisfies the conditions: 
+            For all $k \ge 0$, let $\phi_k : \RR^n \rightarrow\RR$ be a sequence of functions. 
+            We call this sequence of functions a Nesterov's estimating sequence when it satisfies conditions: 
             \begin{enumerate}
@@
             \begin{align*}
-                \Delta_k(x) 
-                &= \phi_k(x) - F(x) \ge \phi_k^* - F(x)
+                (\forall x \in \RR^n) \; \Delta_k(x) 
+                &= \phi_k(x) - F(x) \ge \phi_k^* - F(x), 
                 \\
@@
             The function $\Delta_k(x)$ is non-negative at points: $x_*, x_k$.
-            We can derive the convergence rate of $\Delta_k(x^*)$ because $\forall x \in \RR^n$: 
-            \begin{align*}
-                \phi_{k + 1}(x) - \phi_k(x) 
+            We can derive the convergence rate of $\Delta_k(x^*)$ because (ii) says $\forall x \in \RR^n$: 
+            \begin{align*}
+                \phi_{k + 1}(x) - \phi_k(x) = \phi_{k + 1}(x) - F(x) - (\phi_k(x) - F(x))
                 &\le - \alpha_k (\phi_k(x) - F(x))
-                \\
-                \iff 
-                \phi_{k + 1}(x) - F(x) - (\phi_k(x) - F(x))
-                &\le 
-                -\alpha_k(\phi_k(x) - F(x))
                 \\
@@
             \end{align*}
-            Finally, by setting $x = x^*$, $\Delta_k(x^*)$ is non-negative and using the property of Nesterov's estimating sequence it gives: 
+            Finally, by setting $x = x^*$, $\Delta_k(x^*)$ is non-negative and using (i) it gives: 
             \begin{align*}
@@
 \section{Unifying NAG, and weakening the sequence assumption for convergences}\label{sec:unify-nes-acceleration}
-    This section is based on the theoretical aspects of our draft paper. 
+    This section gives results of the theoretical part  of our draft paper. 
     It will introduce major results and claims achieved during our research in each of the subsections. 
-    All theorems and claims stated in this section have proofs in the draft paper. 
-    The proofs haven't been carefully verified by authoritative people other than the author yet. 
-    We will start introducing the context and ideas for our research next. 
-    \par
-    Assume we want to solve a convex optimization problem: $\min_{x \in \RR^n} \{F(x)\}$ and $F: \RR^n \rightarrow \RR$ is a $L$ Lipschitz smooth function. 
-    We made this assumption for now for a faster exposition. 
-    One of the prime candidate for solving the optimization problem is the Nesterov's Accelerated Gradient methods (NAG) finds extensions for nonsmooth function through the proximal gradient operator.
-    Proposed back in 1983 the original Nesterov's acceleration method \cite{nesterov_method_1983}
-    which uses the previous iterates to extrapolate the next iterate to evaluate the gradient. 
-    It's well known that if minimizer $x^*$ exists for $F$, the method achieves a $\mathcal O(1/k^2)$ convergence rate on the objective value $F(x_k)$.     
-    This convergence rate is considered optimal for all class of $L$ Lipschitz smooth convex function \cite{nesterov_lectures_2018}. 
-    The convergence rate guarantee is faster than $\mathcal O(1/k)$ exhibited by gradient descent. 
-    \par
-    We cover the algorithm briefly. 
+    All theorems and claims stated in this section are proved in the draft paper. 
+    We will start by introducing the context of our research. 
+    \par
+    Assume we want to solve the convex optimization problem: $F^* = \min_{x \in \RR^n} \{F(x)\}$ and assume $F: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth for the simplicity of discussion. 
+    One appealing candidate method for solving it is the Nesterov's accelerated gradient methods (NAG) proposed back in 1983 \cite{nesterov_method_1983}. 
+    It's well known that if minimizer $x^*$ exists for $F$, the method achieves a convergence rate of $\mathcal O(1/k^2)$ for $F(x_k) - F^*$.     
+    It is considered optimal for all class of $L$ Lipschitz smooth convex function and see Chapter 2 of Nesterov \cite{nesterov_lectures_2018} for information. 
+    The guaranteed convergence rate is better than $\mathcal O(1/k)$ exhibited by gradient descent. 
+    \par
     Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
@@
     \end{align}
-    Unfortunately, the algorithm sped up the convergence rate for all convex function, it becomes slower for the subset of $\mu > 0$ strongly convex function. 
+    Unfortunately, this algorithm sped up the convergence rate for the class of all convex function, it becomes slower for the subset of $\mu > 0$ strongly convex function. 
     This drawback inspired a vast amount of literatures aims at improving, extending, and analyzing NAG. 
@@
     \par
-    Restarting the algorithm is not the entire picture. 
+    There are other alternatives to restarting if it's known in advance that $F$ would be $\mu > 0$ strongly convex. 
     Let $F:\RR^n \rightarrow \RR$ be a $L$ Lipschitz smooth and $\mu > 0$ function. 
-    As introduced previously, in 
-    Walkington's writing \cite{noel_nesterovs_nodate}, 
-    he showed that there exists a variant of the Nesterov's accelerated gradient method that achieved a linear convergence rate of $\mathcal O((1 - \sqrt{\kappa})^k)$ where $\kappa = \mu/L$. 
-    This convergence rate is strictly better than $\mathcal O((1 - \mu/L)^k)$ for the method of gradient descent. 
-    However, this variant has a fixed momentum parameter $\theta_{k + 1} = (\sqrt{\kappa} - 1)(\sqrt{\kappa} + 1)^{-1}$ back in Equation \ref{eqn:nag_example}. 
+    In Walkington's writing \cite{noel_nesterovs_nodate}, 
+    he showed that there exists a variant of NAG that achieves linear convergence rate of $\mathcal O((1 - \sqrt{\kappa})^k)$ where $\kappa = \mu/L$. 
+    This convergence rate is strictly better than $\mathcal O((1 - \mu/L)^k)$ from gradient descent. 
+    However, the variant has a fixed momentum parameter $\theta_{k + 1} = (\sqrt{\kappa} - 1)(\sqrt{\kappa} + 1)^{-1}$ in Equation \ref{eqn:nag_example} and has convergence claim for F with $\mu > 0$.
     The same variant also appears in Beck's book as V-FISTA \cite[(10.7.7)]{beck_first-order_2017}, and \hl{Nesterov's book as (2.2.22)} \cite{nesterov_lectures_2018}.
     \par
-    One final Mystery of the algorithm is the convergence of the iterates which also has much to do with the momentum sequence $(\theta_k)_{k\ge 0}$ displayed in Equation \ref{eqn:nag_example}. 
+    Some other researches in the literatures focus on the convergence of the iterates, and it has much to do with the momentum sequence $(\theta_k)_{k\ge 0}$ displayed in Equation \ref{eqn:nag_example}.
     Chambolle, Dossal \cite{chambolle_convergence_2015}
@@
     \par
-    All of these seemingly raises a crucial question: ``Is it possible to describe something about the NAG algorithm for a set of sequence that is non-traditional?''; rephrasing it int a more technical manner: ``What is the weakest description of the momentum sequence $(\theta_k)$ such that we can still claim something of value about the NAG algorithm?''
-
-    \subsection{Our Contributions, organizations}
-        Our contributions are two folds, theoretical and practical. 
-        The results are based the assumption $F = f + g$ where $g:R^n \rightarrow \overline\RR$ is convex, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
-        We relax the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:nag_example} and showed an upper bound of the optimal gap. 
-        Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
+    The content of our draft paper answers the question: ``Is it possible to describe something about the NAG algorithm for a set of sequence that is non-traditional?''.
+
+    \textbf{A summary of our contributions now follow.}
+    Our contributions are theoretical and practical. 
+    Out results are based the assumption $F = f + g$ where $g:\RR^n \rightarrow \overline\RR$ is convex, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex. 
+    We relax the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:nag_example} and showed an upper bound of the optimal gap for the sequences $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ that satisfy
     \begin{align*}
@@
     \end{align*}
-        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wagp-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
+    Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the generic algorithm R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wagp-convergence}, \ref{prop:r-wapg-momentum-repr}, it can show that the gap $F(x_k) - F(x^*)$ is bounded by:
     \begin{align*}
@@
     \end{align*}
-        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in 
-        Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}. 
-        When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by in Beck \cite{beck_fast_2009}.
-        If $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
-        In Theorem \ref{thm:fixed-momentum-fista}, it demonstrates that R-WAPG frameworks gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex.
+    Our second main result shows that, assuming $\mu = 0$ then there exists the choice of $(\alpha_k)_{k \ge 0}$ $\rho_k > 1$ such that our R-WAPG reduces to the variant of FISTA proposed by Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}.
+    In the special case where $(\alpha_k)_{k \ge 0}$ has $\rho_k = 1 \;\forall k \ge 0$, and assuming $\mu = 0$, R-WAPG reduces to the FISTA algorithm proposed in Beck \cite{beck_fast_2009}.
+    If $\mu > 0, \rho_k = 1\;\forall k \ge 0$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
+    In Theorem \ref{thm:fixed-momentum-fista}, we demonstrated that R-WAPG frameworks gives a linear convergence claim for all APG where $\alpha_k := \alpha \in (\mu/L, 1)$ is a fixed constant parameter and $F$ is $\mu > 0$ strongly convex.
     \par
     Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}). 
-        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ with minimal computational cost.
-        We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart. 
-        \par
-        Notations, and assumptions now follows. 
+    It doesn't require $L, \mu$ in prior, so it determines the value of $\theta_t$ by estimating $D_f$ on iterates $y_{k}, y_{k + 1}$ with minimal computational cost. 
+    We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and exposes its similarity in terms of behaviors to the FISTA with monotone restart under certain situations.
+    \par
+    \textbf{Notations, and assumptions now follows. }
     For all the subsection that follows, we let $F:= f + g$ to take the same assumptions as in Section \ref{sssec:additive-composite}. 
@@
     }
-
-        Organization now follows. 
+    \par
+    \textbf{Organization now follows. }
     Section \ref{ssec:building-block-rwapg} provides a stepwise description of the R-WAPG iterative algorithm along with an inequality crucial to proving the convergence rate later. 
@@
         \par 
-        For the termination conditions of the algorithm, we consider the norm of the gradient mapping $\mathcal G_L(y_k) < \epsilon$. 
+        For the termination conditions of the algorithm, we consider the norm of the gradient mapping $\Vert \mathcal G_L(y_k)\Vert < \epsilon$. 
         The $L$ can change during each iteration if it's obtained through the specified Lipschitz line search routine.
@@
     \subsection{Future works for R-WAPG}
-        There is one intriguing detail buried in literatures but weren't realized in it. 
+        The R-WAPG framework neglected one intriguing detail buried in the literatures. 
         It has the potential to include more variants of the FISTA algorithms and their convergence proof. 
@@
         We define the Moreau Envelope at $y \in \RR^n$ to be $\mathcal M^*_{F,\beta^{-1}}(y) = \min_{x\in \RR^n} \mathcal M_F^{\beta^{-1}}(x; y)$. 
-        We denote $\mathcal J_{\beta^{-1}}$ to be the resolvent operator for subgradient of $F$. 
+        We denote $\mathcal J_{\beta^{-1}F}$ to be the resolvent operator for subgradient of $F$. 
     \end{assumption}

### 2025-01-16 Notebook LaTEX/R-WAPG/paper3.tex
>w<, updates
>w<, changes, a lot

@@
     \end{assumption}
-    $\forall x \in \RR^n,\forall y \in \RR^n$, define: 
-    \begin{align*}
+    For $x \in \RR^n, y \in \RR^n$, we define: 
+    \begin{align}
         \widetilde{\mathcal M}^{L^{-1}}
@@
         g(x) + f(y) + \langle \nabla f(y), x - y\rangle 
-        + \frac{L}{2}\Vert x - y\Vert^2, 
+        + \frac{L}{2}\Vert x - y\Vert^2,  \label{eqn:pg_model-func}
         \\
         \mathcal M^{L^{-1}}(x; y) &:= F(x) + \frac{L}{2}\Vert x - y\Vert^2. 
-    \end{align*}
+        \label{eqn:pp_model-func}
+    \end{align}
     Define the proximal gradient operator and gradient mapping operator: $T_L, \mathcal G_L$: 
@@
     \end{align*}
-    The following lemma is an important property of $\mathcal M(\cdot; y), \widetilde{\mathcal M}(\cdot; y)$. 
+    The following lemma provides important properties of $\mathcal M^{L^{-1}}(\cdot; y), \widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$. 
     \begin{lemma}[Proximal gradient envelope]\label{lemma:pg-envelope}
-        Fix any $y \in \RR^n$, we will have for all $x \in \RR^n$ that
+        With $\mathcal M^{L^{-1}}, \widetilde{\mathcal M}^{L^{-1}}$ as given by \eqref{eqn:pg_model-func}, \eqref{eqn:pp_model-func}, 
+        we have for all $x \in \RR^n$, $y \in \RR^n$:
         \begin{align*}
@@
     \begin{proof}
-        Consider any $x \in \dom g$, by definition it has: 
+        For $x \in \dom g$, by definition we have: 
         \begin{align*}
@@
     \end{proof}
-    \begin{remark}
-        This is true not just for fixed $L$ that is the Lipschitz smoothness constant of $f$, it's true for all value of $L$. 
-    \end{remark}
     \begin{theorem}[Proximal inequality]\label{thm:prox-grad-ineq}
         Let $F$ be given by Assumption \ref{ass:smooth-nsmooth-additive}. 
-        Fix any $y\in \RR^n$, we have for all $x \in \RR^n$: 
+        For $x,y\in \RR^n$, we have: 
         \begin{align*}
@@
     \begin{proof}
-        We denote $T$ for the proximal gradient operator instead of $T_L$. 
-        We can do this because the Lipschitz constant $L$ is fixed throughout the proof hence it can be omitted. 
+        For simplicity of notations, we write $T$ for $T_L$. 
         The model function $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is an $L + \mu$ strongly convex function, so it admits quadratic growth conditions over minimizer $Ty$ and for all $x \in \RR^n$:
@@
         Now, consider the lower bound of $D_f(x, y) \ge \mu/2\Vert x - y\Vert^2$ which is true for all $x, y \in \RR^n$ by strong convexity of $f$. 
-        Then it has for all $x \in \RR^n, y \in \RR^n$ that: 
+        Then it has for all $x \in \RR^n, y \in \RR^n$: 
         \begin{align*}
@@
     \begin{assumption}
-        Choose any integer $k\ge 0$. 
-        Given $x_k, y_k, v_k$, we define the following quantities
+        Given $x_k, y_k, v_k$ where $k \in \mathbb Z_+$, we define the following quantities
         \begin{align}
@@
         Assume $0 \le \mu < L$.
-        Fix any $k \in \mathbb Z$. 
+        Fix any $k \in \mathbb Z_+$. 
         For any $(v_k, x_k), \alpha_k \in (0, 1), \gamma_k > 0$, let $\hat \gamma_{k + 1}$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ be given by: 
@@
 
-        \begin{lemma}[A useful lemma]\label{lemma:ineq-q3}
+        \begin{lemma}\label{lemma:ineq-q3}
         Let $v_k, x_k, y_k, v_{k + 1}, x_{k + 1}$ and $\alpha_k, \hat \gamma_{k + 1}, \gamma_{k}$ be given by Definition \ref{def:stepwise-wapg}. 
@@
     \begin{proposition}[Stepwise Lyapunov]\label{prop:stepwise-lyapunov}\;\\
-        Fix any integer $k \in \mathbb Z$ and $R_k \in \RR$. 
+        Let $k \in \mathbb Z_+$, $R_k \in \RR$. 
         Given any $v_k, x_k$ and $\gamma_k > 0$ and $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}, \alpha_k$ that satisfies Definition \ref{def:stepwise-wapg}. 
@@
         \end{align}
-        Then it has for all $x^* \in \RR^n$, the inequality: 
+        Then for all $x^* \in \RR^n$, we have:
         {\small
@@
         We use proof by induction. 
-        Here we drop the subscript $k$, $k + 1$ on $\gamma_{k}, \hat \gamma_{k + 1}$ because they are fixed throughout the proof, and it makes for better readability! 
+        For notation simplicity we drop the subscript $k$, $k + 1$ on $\gamma_{k}, \hat \gamma_{k + 1}$ because they are fixed throughout the proof. 
         \par 
@@
         \end{align}
-        Coefficient of $\epsilon_k$ and $\Vert g_k\Vert^2$ are grouped. 
+        % Coefficient of $\epsilon_k$ and $\Vert g_k\Vert^2$ are grouped. 
         Next, we have: 
@@
         \end{align*}
-        Subtracting $F(x^*)$ from both side of the equation it gives: 
+        Subtracting $F(x^*)$ from both side of the equation gives: 
         \begin{align}\label{eqn:stepwise-lya-proof-eqn3.2}
@@
         }
-        Adding back the $k$, $k + 1$ subscript for $\gamma$, $\hat \gamma$, it's proven. 
     \end{proof}
@@
 
-\section{Formulation of R-WAPG and its convergence rates}\label{sec:rwapg-formulation-convergence}
-    this section focuses on Definition \ref{def:wapg}.
+\section{R-WAPG and its convergence rates}\label{sec:rwapg-formulation-convergence}
+    In this section we propose R-WAPG  see Definition \ref{def:wapg}.
     R-WAPG algorithm generates iterates $(x_k, y_k, v_k)$ and admits an upper bound on $F(x_k) - F^*$ described in Proposition \ref{prop:stepwise-lyapunov}. 
@@
         Assume $0 \le \mu < L$. 
-        The sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge1}$ are sequences parameterized by $\mu, L$. 
-        They are valid for R-WAPG if all the following holds: 
+        The sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are valid for R-WAPG if all the following holds: 
         \begin{align*}
@@
     \end{observation}
-
+    Here is the main result of this section. 
     \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}\; \\
@@
         Let vector sequence $(y_k, v_{k}, x_{k})_{k \ge 1}$ and R-WAPG sequences $\alpha_k, \rho_k$ be given by Definition \ref{def:wapg}. 
-        Define $R_1 = 0$ and suppose that for $k = 1, 2, \cdots, N$, we have $R_k$ recursively given by: 
+        Define $R_1 = 0$ and suppose that for $k = 1, 2, \ldots, N$, we have $R_k$ recursively given by: 
         \begin{align*}
@@
         \end{align*}
-        Then for all $k = 1, 2, \cdots, N$: 
+        Then for all $k = 1, 2, \ldots, N$: 
         \begin{align*}
@@
     \begin{proof}  
-        The proof is a proof by induction. 
+        The proof is by induction. 
         Let's first consider $k = 1$, $\hat \gamma_2 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$, $R_1 = 0$. 
-        From the above definition, $R_2$ is the same as \eqref{eqn:stepwise-lya-1} hence invoking Proposition \ref{prop:stepwise-lyapunov}: 
+        From the above definition, $R_2$ is the same as \eqref{eqn:stepwise-lya-1}.
+        Invoking Proposition \ref{prop:stepwise-lyapunov}, we have: 
         \begin{align*}
@@
         We had demonstrated the base case. 
-        Next, for all $k = 2, 3, \cdots, N$, from Observation \ref{obs:r-wapg-observation-2}: 
+        Next, for all $k = 2, 3, \ldots, N$, from Observation \ref{obs:r-wapg-observation-2}: 
         \begin{align*}
@@
         }
-        We had demonstrated in the inductive case for $k=1, 2, \cdots, N$. 
-        Additionally, for all $k = 1, 2, \cdots, N$ it has $R_{k + 1} \ge 0$ because: 
+        We had demonstrated in the inductive case for $k=1, 2, \ldots, N$. 
+        Additionally, for all $k = 1, 2, \ldots, N$ it has $R_{k + 1} \ge 0$ because: 
         \begin{align*}
@@
     In the literatures, variants of Accelerated Proximal Gradient algorithm such as FISTA, V-FISTA has different representations. 
-    This section carries out the tedious but necessary works for demonstrating the descriptive power of R-WAPG. 
-    We will formulate it into three generic forms. 
+    This shows that R-WAPG provides a unified framework. 
     These equivalent representations are listed in Definition \ref{def:r-wapg-intermediate}, \ref{def:r-wapg-st-form} and \ref{def:r-wapg-momentum-form}. 
@@
     Convergence results from Proposition \ref{prop:wagp-convergence} applies to all these equivalent forms of R-WAPG. 
-    In brief, the relations of these proposition and definitions can be summarized by
-    \begin{align*}
-        & \text{Definition } \ref{def:wapg} 
-        \\
-        & \iff 
-        \text{Definition } \ref{def:r-wapg-intermediate} & \text{By Proposition }\ref{prop:wapg-first-equivalent-repr}.
-        \\
-        & \iff \text{Definition }\ref{def:r-wapg-st-form} & \text{By Proposition }\ref{def:r-wapg-st-form}.
-        \\
-        & \;\implies 
+    In brief, different equivalent reformulations are summarized as following: 
+    \begin{align*}
+        &\text{Definition \ref{def:wapg}}   \iff 
+        \text{Definition \ref{def:r-wapg-intermediate}}  & \text{By Proposition \ref{prop:wapg-first-equivalent-repr}.}
+        \\
+        & \text{Definition \ref{def:r-wapg-intermediate}}
+        \iff \text{Definition \ref{def:r-wapg-st-form}} & \text{By Proposition \ref{def:r-wapg-st-form}.}
+        \\
+        & 
+        \text{Definition \ref{def:r-wapg-st-form}}\implies 
         \text{Definition }\ref{def:r-wapg-momentum-form}. 
@@
         \end{align*}
-        If $1 + \xi_k + \tau_k = L\delta_k\; \forall k \ge 1$. 
-        Then for all $k \ge 1$: 
+        If $1 + \xi_k + \tau_k = L\delta_k\; \forall k \ge 1$, then for all $k \ge 1$: 
         $$
@@
         \end{align*}
-        To verify, do 
+        To verify, we consider:
         \begin{align*}
@@
     \end{proof}
-    \subsection{A list of equivalent representations of R-WAPG}
+    \subsection{Equivalent representations of R-WAPG}
         This section lists three equivalent representations of the R-WAPG algorithm. 
-        They are comparable to existing APG algorithms in the literatures. 
+        They are comparable to existing APG algorithms in the literatures such as Excersise 12.1 in Ryu, Yin \cite{ryu_large-scale_2022}, Similar Triangle from from Lee et al.
+\cite{lee_geometric_2021}, Ahn Sra \cite{ahn_understanding_2022} and momentum form of (2.2.19) in Nesterov \cite{nesterov_lectures_2018}.
         Specific instances of Accelerated Proximal Gradient algorithm that has the same form as the Definition \ref{def:r-wapg-intermediate}, Definition \ref{def:r-wapg-st-form} and Definition \ref{def:r-wapg-momentum-form} in the literatures are stated in the remarks that follows the definitions.
@@
             The term ``Method of Similar Triangle" was used for Algorithm (6.1.19) in Nesterov's book \cite{nesterov_lectures_2018}, but without the necessary graphical illustrations to clarify it. 
-            Finally, a similar triangle for formulation of FISTA can be found in Equation (2), (3), (4) in \cite{chambolle_convergence_2015}. 
+            Finally, a similar triangle for formulation of FISTA with $\mu = 0$ can be found in Equation (2), (3), (4) in \cite{chambolle_convergence_2015}. 
             To see graphical visualization on why such term is used to describe the APG algorithm in the literatures, see 
@@
 
-    \subsection{Proving the equivalent representations of R-WAPG}
+    \subsection{Proofs of equivalent representations of R-WAPG}
         \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\
             If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}), 
-            then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$, and for all $k\ge 1$ they are algebraically equivalent to
+            then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$, and for all $k\ge 1$ namely
             \begin{align*}
@@
             \end{align*}
-            From the left to right of the second inequality, we used the fact that $\hat \gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k\mu$. 
-            Going from the left to the right of the second last inequality, we did the following: 
+            From the left to right of the second equality, we used the fact that $\hat \gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k\mu$. 
+            Going from the left to the right of the second last equality, we did the following: 
             \begin{align*}
@@
             \end{align*}
-            The is now complete. 
+            The proof is now complete. 
             This form doesn't have $\rho_k, \gamma_k, \hat \gamma_k$ in it. 
@@
             We claim that these parameters satisfy $L\delta_k = 1 + \tau_k + \xi_k$. 
-            To see, we have for all $k\ge 1$: 
+            To see this, we have for all $k\ge 1$: 
             \begin{align*}
@@
     Let $\tilde \mu_k$ be an estimate produced by the algorithm then it satisfies that $\tilde \mu_k/ L \in (0, 1)$.
-    Assuming inductively that $q = \tilde \mu_k/L$,  $\alpha_k \in (0, 1)$, then 
+    Assuming inductively that $q = \tilde \mu_k/L$,  $\alpha_k \in (\mu/L, 1)$, then 
     \begin{align*}
@@
     Here we used the assumption that $q \in (0, 1)$ so $2q - 4 < 0$ always. 
-    It is not hard to see that $\alpha_{k + 1} > 0$ as well. 
+    It is not hard to see that $\alpha_{k + 1} > \mu/L$ as well. 
     Therefore, $\alpha_k \in (0, 1)$. 

### 2025-01-16 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

@@
         Let sequence $(\alpha_k, \rho_k)_{k \ge 0}$ and iterates $(x_k, v_k, y_k)_{k\ge 1}$ given by R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}). 
-        Then for all $k \ge 1$, the iterates $(x_{k + 1}, y_{k + 1})_{k \ge 1}$ are algebraically equivalent to: 
+        Then for all $k \ge 1$, the iterates $(x_{k + 1}, y_{k + 1})_{k \ge 1}$ satisfy: 
         \begin{align*}
@@
         \end{align*}
-        In the special case when $\mu = 0$, the momentum term admits simpler representation 
+        If in addition $\mu = 0$, then the momentum term admits a simpler representation 
         \begin{align*}
@@
         \end{align*}
-        We have $y_1 = x_1$ when $v_1 = x_1$ because substituting $v_1 = x_1$ for how $y_1$ is defined it has: 
+        We have $y_1 = x_1$ when $v_1 = x_1$ because
         \begin{align*}
@@
         \end{align*}
-        Going from the left to right on the fourth equality, we used $L\alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_kL\alpha_k^2 + \mu \alpha_{k + 1}$ established by: 
+        Going from the left to right on the fourth equality, we used $L\alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_kL\alpha_k^2 + \mu \alpha_{k + 1}$ to establish: 
         \begin{align*}
@@
 
-\section{R-WAPG describes existing accelerations scheme in the literatures}\label{sec:rwapg-literatures}
-    In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are descriptive. 
+\section{R-WAPG verifies existing accelerations scheme}\label{sec:rwapg-literatures}
+    In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are much more flexible. 
     They generalize many existing sequences used in accelerated proximal gradient schemes. 
@@
             \iff 
-            \alpha_k^{-1} 
+            \alpha_k^{-2} 
             &\ge 
-            \alpha_{k + 1}^{-2} + \alpha_{k + 1}^{-1}. 
+            \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}. 
         \end{align*}
@@
         \par
-        (i) $\implies$ (ii) because substituting $\alpha_k^{-1} = t_k$ changes (i) into $t_{k + 1}^2 - t_{k + 1} - t_{k}^2 \le 0$ for all $k \ge 0$. 
+        (i) $\implies$ (ii): Substituting $\alpha_k^{-1} = t_k$ changes (i) into $t_{k + 1}^2 - t_{k + 1} - t_{k}^2 \le 0$ for all $k \ge 0$. 
         Solving the equality yields $t_{k + 1} = (1/2)\left(1 \pm \sqrt{1 + 4 t_k^2}\right)$ for all $k \ge 0$. 
@@
         To prove (iii), because $\rho_k \ge 1$, we have $\prod_{i = 1}^{k} \max(1, \rho_{k - 1})(1 - 
-        \alpha_k)$ for all $k \ge 1 = \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)$. 
+        \alpha_k)= \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)$ for all $k \ge 1 $. 
         By definition $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ sequences they have for all $k \ge 1$: 
@@
         \begin{enumerate}
-            \item Fix any $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$ then the constant sequence $\alpha_k := \alpha \in (q, 1)$ and\\
+            \item FOr any $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, the constant sequence $\alpha_k := \alpha \in (q, 1)$ and\\
             $\rho_k := \rho=\left(1-r^{-1}\sqrt{q}\right)\left(1 - r \sqrt{q}\right)^{-1} > 0$, hence it's a pair of valid R-WAPG sequence. 
@@
         \begin{enumerate}
-            \item[A:] When $r \in \left(1, \sqrt{q^{-1}}\right)$, we have $\rho > 1$ by (iii), meaning that $1 - r^{-1}\sqrt{q} > 1 - r \sqrt{q}$. $\rho > 1 \implies \max(\rho, 1) = \rho$ hence 
+            \item[Case A:] When $r \in \left(1, \sqrt{q^{-1}}\right)$, we have $\rho > 1$ by (iii), meaning that $1 - r^{-1}\sqrt{q} > 1 - r \sqrt{q}$. $\rho > 1 \implies \max(\rho, 1) = \rho$ hence 
                 \begin{align*}
@@
                 In this case, the larger one of the two values: $\left\lbrace1 - \rho^{-1}\sqrt{q}, 1 - r\sqrt{q}\right\rbrace$ is taken. 
-            \item[B:] When $r \in \left(\sqrt{q}, 1\right]$, we have $\rho \le 1$ by (iii); hence $1 - r^{-1}\sqrt{q} \le 1 - r \sqrt{q}$ and $\max(1,\rho) = 1$ therefore: 
+            \item[Case B:] When $r \in \left(\sqrt{q}, 1\right]$, we have $\rho \le 1$ by (iii); hence $1 - r^{-1}\sqrt{q} \le 1 - r \sqrt{q}$ and $\max(1,\rho) = 1$ therefore: 
             \begin{align*}
@@
         Hence, (iii) in Lemma \ref{lemma:inverted-fista-seq} applies. 
-        We may use Proposition \ref{prop:wagp-convergence} by the validity of our $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ sequences, we have:
+        By Proposition \ref{prop:wagp-convergence}, we have:
         {\small\begin{align*}
@@
             \\
-            Initialize $y_1 = x_1$; for $k = 1, 2, \cdots, N$, update: 
+            Initialize $y_1 = x_1$; for $k = 1, 2, \ldots, N$, update: 
             \begin{align*}
@@
         \end{align*}
-        The equivalency between the Momentum representation of R-WAPG (Definition \ref{def:r-wapg-momentum-form}) and the similar triangle representation (Definition \ref{def:r-wapg-st-form}) allows us to write $v_{k + 1} = x_{k + 1} + (\alpha^{-1} - 1)(x_{k + 1} - x_k)$.
-        By the initialization condition $v_1 = x_1$ specified back in Proposition \ref{prop:r-wapg-momentum-repr} when we derived the momentum form of R-WAPG, we can write $v_1$ as $x_1$.
+        The equivalency between the momentum representation of R-WAPG (Definition \ref{def:r-wapg-momentum-form}) and the similar triangle representation (Definition \ref{def:r-wapg-st-form}) allows us to write $v_{k + 1} = x_{k + 1} + (\alpha^{-1} - 1)(x_{k + 1} - x_k)$.
+        By the initialization condition $v_1 = x_1$ specified in Proposition \ref{prop:r-wapg-momentum-repr}, we can write $v_1$ as $x_1$.
 

### 2025-01-16 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes done

@@
     \noindent
-    We analyze the accelerated proximal gradient method where the sequence that controls the momentum term is much weaker than the Nesterov's rule. 
-    Our setting is the convex optimization problem $F^* = \min_x\{f(x) + g(x)\}$ where $f$ is $L$ Lipschitz smooth and $\mu\ge 0$ strongly convex and $g$ is closed and convex. 
-    A much weaker condition of extrapolation parameters in $y_{k + 1} = x_{k + 1} - \theta_k(x_{k + 1} - x_k)$ is precisely characterized to show an upper bound on the optimality gap $F(x_k) - F^*$ using a generic algorithm R-WAPG (Relaxed Weak Accelerated Proximal Gradient) we proposed.
-    R-WAPG is a generic algorithm that has a has one convergence claim that unifies the convex and strongy convex cases. 
-    R-WAPG can describes major Euclidean variants of the FISTA. 
-    We showed convergence results for several notable variants of FISTA found in the literatures. 
-    Inspired by a small detail in the proof, explorative numerical experiments were conducted to show the convergence of R-WAPG where the extrapolation sequence is generated using Bregman Divergence of $f$ on sucessive iterate $y_{k + 1}, y_{k}$.
-
+    We study the accelerated proximal gradient method where the sequence that controls the momentum term doesn't follow the Nesterov's rule. 
+    The paper proposed R-WAPG, a generic algorithm that unifies the convergence results for strongly convex and convex where the extrapolation constant is characterized by a sequence that is much weaker than the Nesterov's rule.
+    The R-WAPG framework is able to describe several notable Euclidean variants of FISTA and verify their convergence. 
+    In addition we also proposed the convergence rate of strongly convex objective with a constant momentum term. 
+    Inspired by a small detail in the proof, we give a formuatlion of R-WAPG that doesn't require any parameter without using the idea of restarting which we call ``Free R-WAPG". 
+    Explorative numerical experiments were conducted to show its competitive convergence with numerical experiments. 
 \end{abstract}
@@
             \left(
-                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
+                \prod_{i = 0}^{k - 1} \max(1, \rho_{i})
             \right)
@@
         So $\gamma_k, \hat \gamma_{k + 1}, \alpha_k$ fits Definition \ref{def:stepwise-wapg}. 
-        for all $k \ge 1$, $R_k$ satisfies \eqref{eqn:stepwise-lya-1}, hence unroll recursively using Proposition \ref{prop:stepwise-lyapunov}: 
+        For all $k \ge 1$, $R_k$ satisfies \eqref{eqn:stepwise-lya-1}, hence unroll recursively using Proposition \ref{prop:stepwise-lyapunov}: 
         {\small
@@
     This section will also demonstrate that the convergence claim (Proposition \ref{prop:wagp-convergence}) holds, and it derives convergence rates consistent with results in the literatures.  
+    The table follows demonstrates the R-WAPG convergence results specialized into various settings. 
+    \begin{table}[H]
+        {\scriptsize
+        \begin{tabular}{|l|l|l|l|l|}
+        \hline
+            Algorithm & $\mu$ & $\alpha_k$ & $\rho_k$ & Convergence of $F(x_k) - F^*$ 
+        \\ \hline
+            R-WAPG in Definition \ref{def:wapg} & 
+            $\mu \ge 0$ &
+            $\alpha_k \in(\mu/L, 1)$ & 
+            $\rho_k > 0$ &  
+            \begin{tabular}{l}
+                $\mathcal O \left(\prod_{i = 0}^{k-1} \max(1, \rho_i)(1 - \alpha_{i + 1})\right)$
+                \\
+                (Proposition \ref{prop:wagp-convergence})
+            \end{tabular}
+        \\ \hline
+            Chambolle, Dossal 2015 \cite{chambolle_convergence_2015} &  
+            $\mu = 0$  &
+            $ 0< \alpha_k^{-2} \le \alpha_{k + 1}^{-1} - \alpha_{k + 1}^{-2}$ & 
+            $\rho_k \ge 1$ &  
+            \begin{tabular}{l}
+                $\mathcal O(\alpha_k^{2})$ \\ (Theorem \ref{thm:r-wapg-on-cham-doss})    
+            \end{tabular}
+        \\ \hline
+            V-FISTA Beck (10.7.7) \cite{beck_first-order_2017} &
+            $\mu > 0$&
+            $\alpha_k = \sqrt{\mu/L}$ & 
+            $\rho_k = 1$ &
+            \begin{tabular}{l}
+                $\mathcal O\left((1 - \sqrt{\mu/L})^k\right)$, 
+                \\
+                (Theorem \ref{thm:fixed-momentum-fista}, remark)
+            \end{tabular}
+        \\ \hline
+            R-WAPG in Definition \ref{def:wapg} &  
+            $\mu > 0$ &
+            $\alpha_k = \alpha \in (\mu/L, 1)$ &  
+            $\rho_k = \rho > 0$ & 
+            \begin{tabular}{l}
+                $\mathcal O \left(\max((1 - \alpha), 1 - \mu/(\alpha L))^{k} \right)$\\
+                (Theorem \ref{thm:fixed-momentum-fista})
+            \end{tabular}
+        \\ \hline
+        \end{tabular}
+        }
+    \end{table}
+    The lemma follows characterizes momentum sequences appears in the literatures using Definition \ref{def:rwapg-seq}. 
     \begin{lemma}[R-WAPG sequences as inverted FISTA sequence]\label{lemma:inverted-fista-seq}
@@
         By the initialization condition $v_1 = x_1$ specified in Proposition \ref{prop:r-wapg-momentum-repr}, we can write $v_1$ as $x_1$. 
-
     \end{proof}
@@
 \section{The method of Free R-WAPG}\label{sec:free-rwapg}
-    This section introduces an algorithm of our creation inspired by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
-    Algorithm \ref{alg:free-rwapg} estimates the $\mu$ constant as the algorithm executes and pools the information using the Bregman Divergence of the smooth part function $f$. 
+    In this section, we propose Algorithm \ref{alg:free-rwapg} which estimates the $\mu$ constant as the algorithm executes, and it pools the information using the Bregman Divergence of the smooth part function $f$.
+    It is called Free R-WAPG because it doesn't require any knowledge of $\mu, L$ in prior for the smooth part $f$, making it parameter-free. 
     \begin{algorithm}
@@
     \subsection{Numerical experiments}
-        This section gives figures and visual for numerical experiments conducted using FR-WAPG algorithm (Algorithm \ref{alg:free-rwapg}), with other APG algorithms in the literatures: the V-FISTA, and M-FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}.
+        This section we conduct numerical experiments conducted using FR-WAPG algorithm (Algorithm \ref{alg:free-rwapg}), and compare with other APG algorithms in the literatures: the V-FISTA, and M-FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}.
         We implemented in Julia \cite{bezanson_julia_2017} and compare V-FISTA, M-FISTA from Beck, and Algorithm \ref{alg:free-rwapg} given this section. 
@@
         \subsubsection{Simple convex quadratic}
-            Consider the minimization problem of $\min_x \{F(x):= f(x) + 0\}$ where the objective function is given by: 
+            Consider the minimization problem of $\min_{x \in \RR^n} \{F(x):= f(x) + 0\}$ where the objective function is given by: 
             \begin{align*}
@@
             \begin{align*}
-                \min_x
+                \min_{x \in \RR^n}
                 \left\lbrace
@@
             \end{align*}
-            The smooth part is $f =\frac{1}{2}\Vert Ax - b\Vert^2$ and the nonsmooth is $g = \lambda\Vert x\Vert_1$. 
+            The smooth part is $f(x) =\frac{1}{2}\Vert Ax - b\Vert^2$ and the nonsmooth is $g(x) = \lambda\Vert x\Vert_1$. 
             The objective function is coersive and the exact minimum, or minimizers are unknown. 
@@
 \section{Discussion}
-    We do not claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in literatures. 
-    Our numerical experiments are explorative and we hope to inspire. 
-    The presented theories (Proposition \ref{prop:stepwise-lyapunov}, \ref{prop:wagp-convergence}) are our best attempts at making sense of what is happening, and we did it directly with elementary algebra.
-    In addition, we provided some helpful results on the equivalent representations of R-WAPG to illustrate the descriptive power of the R-WAPG framework. 
-    Nonetheless, two things are clear from the numerical experiments. 
-    FR-WAPG performs better than V-FISTA on the first hundreds of iterations, and it doesn't require prior knowledge on parameter $L, \mu$. 
-    \par
-    Our theories are somewhat relevant to FR-WAPG since it can partially describe an upper bound of the optimality gap with any sequence of $\alpha_k \in (0, 1)$. 
-    Unfortunately, it is difficult to know the sequence $(\alpha_k)_{k \ge 0}$ without running the algorithm. 
-    It would require knowledge about the trajectory taken for a specific initial guess, and the property of $D_f$, the Bregman Divergence of the smooth part. 
-    We feel that the breakthrough in understanding may not come from elementary results.  
-    \par 
-    From a practical point of view, the numerical experiments show that in the beginning of the algorithm, the estimate for $\mu$ can be overestimated.
-    This is partially explained by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
-    It also showed that the algorithm performs with mixed charactercteristics of M-FISTA and V-FISTA and it's just fascinating. 
-    Finally, we observed that the convergence of gradient mapping $\mathcal G_L(y_k)$ becomes more difficult and the algorithm may not be able to terminate for certain objectives.
+    This paper provides the results of an upper bound (Proposition \ref{prop:wagp-convergence}) on the optimality gap $F(x_k) - F^*$ for smooth plus nonsmooth composite optimization problem with convex objectives where under the much weaker assumption for the momentum parameter specified by Definition \ref{def:rwapg-seq}.
+    The proposed R-WAPG unifies the convergence proof for major Euclidean variants of FISTA with strong convexity parameter $\mu \ge 0$. 
+    No analogous convergence framework had been identified yet in the literatures that proves the convergences of several variants (with and without strong convexity parameter) with momentum sequences that doesn't follow the Nesterov's rule.
+    \par
+    In addition, we proposed explorative numerical experiments for Free R-WAPG (Algorithm \ref{alg:free-rwapg}) showcasing a parameter free algorithm that doesn't use the idea of restarting to achieve competitive convergence rate.
+    Unfortunately a precise description of the convergence rate of Free R-WAPG remains a mystery. 
+    Our convergence framework gives an upper bound using the sequence $(\alpha_k)_{k \ge 0} \in (\mu/L, 1)$, but it requires knowing what the sequence would be in advanced given the initial conditions and the objective function.
+    \par
+    From a practical perspective, Algorithm \ref{alg:free-rwapg} shows competitive results of convergence of strongly convex function.  
+    The algorithm behaves in way having characteristics of both V-FISTA and M-FISTA which is fascinating. 
+    In addition, of being parameter free, the algorithm works well with auto-differentiation framework because it requires the function value at the same point where the gradient is evaluated at $y_k$.
+    We do note that in the case when function is not strongly convex, the function value converges without $\Vert \mathcal G_L(y_k)\Vert$ converging.
+
+    % We do not claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in literatures. 
+    % Our numerical experiments are explorative and we hope to inspire. 
+    % The presented theories (Proposition \ref{prop:stepwise-lyapunov}, \ref{prop:wagp-convergence}) are our best attempts at making sense of what is happening, and we did it directly with elementary algebra.
+    % In addition, we provided some helpful results on the equivalent representations of R-WAPG to illustrate the descriptive power of the R-WAPG framework. 
+    % Nonetheless, two things are clear from the numerical experiments. 
+    % FR-WAPG performs better than V-FISTA on the first hundreds of iterations, and it doesn't require prior knowledge on parameter $L, \mu$. 
+    % \par
+    % Our theories are somewhat relevant to FR-WAPG since it can partially describe an upper bound of the optimality gap with any sequence of $\alpha_k \in (0, 1)$. 
+    % Unfortunately, it is difficult to know the sequence $(\alpha_k)_{k \ge 0}$ without running the algorithm. 
+    % It would require knowledge about the trajectory taken for a specific initial guess, and the property of $D_f$, the Bregman Divergence of the smooth part. 
+    % We feel that the breakthrough in understanding may not come from elementary results.  
+    % \par 
+    % From a practical point of view, the numerical experiments show that in the beginning of the algorithm, the estimate for $\mu$ can be overestimated.
+    % This is partially explained by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
+    % It also showed that the algorithm performs with mixed charactercteristics of M-FISTA and V-FISTA and it's just fascinating. 
+    % Finally, we observed that the convergence of gradient mapping $\mathcal G_L(y_k)$ becomes more difficult and the algorithm may not be able to terminate for certain objectives.
 

### 2025-01-20 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

@@
             (3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}.
-            % \todoinline{\noindent
-            %     The term ``Method of Similar Triangle'' specific to this particular representation of AGM. 
-            %     For more information, see:  
-            %     \begin{enumerate}
-            %         \item 3.1, 4.1 in Jongmin Lee et al., ``A geometric structure of Acceleration and its role in making gradients small''
-            %         \item The entirety of Ahn and Sra's paper ``PPM interpretation of Nesterov's accelerated gradient. ''. 
-            %     \end{enumerate}
-            % }
 

### 2025-01-22 Notebook LaTEX/R-WAPG/paper3.tex
">w<, changes"
>w<, changes

@@
     The paper proposed R-WAPG, a generic algorithm that unifies the convergence results for strongly convex and convex where the extrapolation constant is characterized by a sequence that is much weaker than the Nesterov's rule.
-    The R-WAPG framework is able to describe several notable Euclidean variants of FISTA and verify their convergence. 
+    The R-WAPG provides a unified framework for several notable Euclidean variants of FISTA and verify their convergence. 
     In addition we also proposed the convergence rate of strongly convex objective with a constant momentum term. 
-    Inspired by a small detail in the proof, we give a formuatlion of R-WAPG that doesn't require any parameter without using the idea of restarting which we call ``Free R-WAPG". 
-    Explorative numerical experiments were conducted to show its competitive convergence with numerical experiments. 
+    We reformulate R-WAPG so that it doesn't require any parameter without using the idea of restarting which we call ``Free R-WAPG". 
+    Explorative numerical experiments were conducted to show its competitive convergence. 
 \end{abstract}
@@
 
-    \subsection{Contents}
+    \subsection{Contributions of this paper}
         Inspired specifically by the technique of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, firstly we present a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG) in Section \ref{sec:rwapg-formulation-convergence}.
-        It has the ability to upper bound $F(x_k) - F(x^*)$ for sequences $(t_k)_{k \ge 0}$ that follows a rule much weaker than Nester's update rule. 
+        It has the ability to upper bound $F(x_k) - F(x^*)$ for sequences $(t_k)_{k \ge 0}$ that follows a rule much weaker than Nesterov's update rule. 
+        In addition to a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(t_k)_{k \ge 1}$. 
         Secondly, we present an alternative to restarting that performs well empirically inspired by a small detail in the convergence proof of R-WAPG. 
-        In addition to a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(t_k)_{k \ge 1}$. 
         It also has descriptive power to describe several variants of FISTA in the literatures.  
@@
         \par
-        \textbf{Organizations now follow.}
         Section \ref{sec:preliminaries} introduces the proximal gradient inequality which is instrumental to developing the stepwise convergence claim in the next section. 
@@
     \end{assumption}
+    The extended real is defined as $\overline \RR := \RR \cup \{\infty, - \infty\}$. 
+    Using $\overline \RR$ we model a general convex function $g: Q \rightarrow \RR$ as a function on $\RR$. 
+    If $x \in \RR^n \setminus Q$ then $g(x) = \infty$ by definition. 
+    The domain has the definition $\dom(g) := \{x \in \RR^n : g(x) < \infty\}$. 
+    A proper function $g$ means that there exists some $x \in \dom(g)$ such that $g(x) > -\infty$. 
+    \par
     For $x \in \RR^n, y \in \RR^n$, we define: 
@@
     \end{align}
-    Define the proximal gradient operator and gradient mapping operator: $T_L, \mathcal G_L$: 
+    Define the proximal gradient operator and gradient mapping operator $T_L, \mathcal G_L$: 
     \begin{align*}
@@
 \section{Stepwise formulation of weak accelerated proximal gradient}\label{sec:stepwise-stuff}
-    This entire section is instrumental to build the R-WAPG algorithm which is described in the Definition \ref{def:wapg} of the next section. 
+    The goal of this section is to build the R-WAPG algorithm which is described in the Definition \ref{def:wapg} of the next section. 
     \par 
@@
     \begin{proof}
-        We use proof by induction. 
+        We prove by induction. 
         For notation simplicity we drop the subscript $k$, $k + 1$ on $\gamma_{k}, \hat \gamma_{k + 1}$ because they are fixed throughout the proof. 
@@
 \section{R-WAPG and its convergence rates}\label{sec:rwapg-formulation-convergence}
-    In this section we propose R-WAPG  see Definition \ref{def:wapg}.
+    In this section we propose Relaxed Weak Accelerated Accelerated Proximal Gradient (R-WAPG), see Definition \ref{def:wapg}.
     R-WAPG algorithm generates iterates $(x_k, y_k, v_k)$ and admits an upper bound on $F(x_k) - F^*$ described in Proposition \ref{prop:stepwise-lyapunov}. 
@@
     \end{observation}
-
+    We now give Relaxed Weak Accelerated Proximal Gradient in details.
     \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}\;\\
@@
             \begin{tcolorbox}
-                For $k = 1, 2, \cdots$
+                For $k = 1, 2, \ldots$
                 \begin{align*} 
@@
             \begin{tcolorbox}
-                For $k=1, 2, \cdots $
+                For $k=1, 2, \ldots $
                 \begin{align*}
@@
             The term ``Method of Similar Triangle" was used for Algorithm (6.1.19) in Nesterov's book \cite{nesterov_lectures_2018}, but without the necessary graphical illustrations to clarify it. 
-            Finally, a similar triangle for formulation of FISTA with $\mu = 0$ can be found in Equation (2), (3), (4) in \cite{chambolle_convergence_2015}. 
+            Equation (2), (3), (4) in \cite{chambolle_convergence_2015} is a similar triangle formulation of FISTA with $\mu = 0$. 
             To see graphical visualization on why such term is used to describe the APG algorithm in the literatures, see 
@@
             \begin{tcolorbox}
-                For $k=1, 2,\cdots $
+                For $k=1, 2,\ldots $
                 \begin{align*}
@@
 
-\section{R-WAPG verifies existing accelerations scheme}\label{sec:rwapg-literatures}
+\section{R-WAPG unifies existing accelerations scheme}\label{sec:rwapg-literatures}
     In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are much more flexible. 
@@
     This section will also demonstrate that the convergence claim (Proposition \ref{prop:wagp-convergence}) holds, and it derives convergence rates consistent with results in the literatures.  
-    The table follows demonstrates the R-WAPG convergence results specialized into various settings. 
+    The table below shows the R-WAPG convergence results specialized into various settings. 
     \begin{table}[H]
@@
             \begin{tabular}{l}
-                $\mathcal O \left(\max((1 - \alpha), 1 - \mu/(\alpha L))^{k} \right)$\\
+                $\mathcal O \left(\max(1 - \alpha, 1 - \mu/(\alpha L))^{k} \right)$\\
                 (Theorem \ref{thm:fixed-momentum-fista})
@@
     \end{table}
-    The lemma follows characterizes momentum sequences appears in the literatures using Definition \ref{def:rwapg-seq}. 
+    The lemma follows characterizes momentum sequences in the literatures using Definition \ref{def:rwapg-seq}. 
     \begin{lemma}[R-WAPG sequences as inverted FISTA sequence]\label{lemma:inverted-fista-seq}
@@
             \\
+            \implies 
             \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)
@@
         \begin{enumerate}
-            \item FOr any $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, the constant sequence $\alpha_k := \alpha \in (q, 1)$ and\\
+            \item For any $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, the constant sequence $\alpha_k := \alpha \in (q, 1)$ and\\
             $\rho_k := \rho=\left(1-r^{-1}\sqrt{q}\right)\left(1 - r \sqrt{q}\right)^{-1} > 0$, hence it's a pair of valid R-WAPG sequence. 
@@
             \\
-            For $k = 1, 2, \cdots$, update: 
+            For $k = 1, 2, \ldots$, update: 
             \begin{align*}
@@
             \left(
-                \frac{\alpha}{k + 1}
+                \frac{a}{k + 1}
             \right)^2 \left(
@@
             &= \left(
-                \frac{\alpha}{k + 1}
+                \frac{a}{k + 1}
             \right)^2 \left(
@@
         \begin{align*}
-            \rho_k &= \frac{(k + a)^2}{(k + 1)(k + a + 1)} 
-            \\
-            &> \frac{(k + 1)^2}{(k + 1)(k + a + 1)} 
-            & \text{By } a \ge 2. 
-            \\
-            &= \frac{(k + 1)}{(k + a + 1)} 
-            \\
-            & > 1.   & \text{By } a \ge 2. 
+            \rho_k &= \frac{(k + a)^2}{(k + 1)(k + a + 1)} = \frac{k^2 + a^2 + 2ak}{k^2 + ak + 2k + a + 1}
+            \\
+            &= (k^2 + a^2 + 2ak)(k^2 + 2ak - ak + 2k + a + 1)^{-1}
+            \\
+            &= (k^2 + a^2 + 2ak)(k^2 + 2ak + \underbrace{(2 - a)k + a + 1}_{\le a^2})^{-1} \ge 1. 
         \end{align*}
@@
             \right) 
-            & \text{By Lemma \ref{lemma:inverted-fista-seq} (iii). }
+            & \text{By Lemma \ref{lemma:inverted-fista-seq} (iii)}
             \\
@@
     \begin{remark}
-        When $r = 1$, the algorithm described above is exactly the same as the V-FISTA algorithm specified in (10.7.7) of his book \cite{beck_first-order_2017}. 
+        When $r = 1$, the algorithm described above is exactly the same as the V-FISTA algorithm specified in (10.7.7) of Beck's book \cite{beck_first-order_2017}. 
     \end{remark}
@@
     The proposed R-WAPG unifies the convergence proof for major Euclidean variants of FISTA with strong convexity parameter $\mu \ge 0$. 
-    No analogous convergence framework had been identified yet in the literatures that proves the convergences of several variants (with and without strong convexity parameter) with momentum sequences that doesn't follow the Nesterov's rule.
+    To the best of our knowledge, there is no framework had been identified yet in the literatures that proves the convergences of several variants (with and without strong convexity parameter) with momentum sequences that doesn't follow the Nesterov's rule.
     \par

### 2025-01-22 Notebook LaTEX/Proposal/proposal.tex
>w<, a lot of fixes

@@
 
-\section{Unifying NAG, and weakening the sequence assumption for convergences}\label{sec:unify-nes-acceleration}
-    This section gives results of the theoretical part  of our draft paper. 
-    It will introduce major results and claims achieved during our research in each of the subsections. 
-    All theorems and claims stated in this section are proved in the draft paper. 
-    We will start by introducing the context of our research. 
-    \par
-    Assume we want to solve the convex optimization problem: $F^* = \min_{x \in \RR^n} \{F(x)\}$ and assume $F: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth for the simplicity of discussion. 
-    One appealing candidate method for solving it is the Nesterov's accelerated gradient methods (NAG) proposed back in 1983 \cite{nesterov_method_1983}. 
-    It's well known that if minimizer $x^*$ exists for $F$, the method achieves a convergence rate of $\mathcal O(1/k^2)$ for $F(x_k) - F^*$.     
-    It is considered optimal for all class of $L$ Lipschitz smooth convex function and see Chapter 2 of Nesterov \cite{nesterov_lectures_2018} for information. 
-    The guaranteed convergence rate is better than $\mathcal O(1/k)$ exhibited by gradient descent. 
-    \par
-    Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
-    \begin{align}\label{eqn:nag_example}
-        & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
-        \\
-        & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
-        \\
-        & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
-        \\
-        & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
-    \end{align}
-    Unfortunately, this algorithm sped up the convergence rate for the class of all convex function, it becomes slower for the subset of $\mu > 0$ strongly convex function. 
-    This drawback inspired a vast amount of literatures aims at improving, extending, and analyzing NAG. 
-    Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
-    Beck and Toubelle \cite{beck_fast_2009}
-    mitigated the issue by restarting and showed that it still has a $\mathcal O(1/k^2)$ convergence rate, and it performs better empirically. 
-    See (5.2.2) Necoara et al. \cite{necoara_linear_2019} and Aujol et al. \cite{aujol_parameter-free_2024}
-    and references within for recent advancements in restarting accelerated proximal gradient algorithm.
-    \par
-    There are other alternatives to restarting if it's known in advance that $F$ would be $\mu > 0$ strongly convex. 
-    Let $F:\RR^n \rightarrow \RR$ be a $L$ Lipschitz smooth and $\mu > 0$ function. 
-    In Walkington's writing \cite{noel_nesterovs_nodate}, 
-    he showed that there exists a variant of NAG that achieves linear convergence rate of $\mathcal O((1 - \sqrt{\kappa})^k)$ where $\kappa = \mu/L$. 
-    This convergence rate is strictly better than $\mathcal O((1 - \mu/L)^k)$ from gradient descent. 
-    However, the variant has a fixed momentum parameter $\theta_{k + 1} = (\sqrt{\kappa} - 1)(\sqrt{\kappa} + 1)^{-1}$ in Equation \ref{eqn:nag_example} and has convergence claim for F with $\mu > 0$.
-    The same variant also appears in Beck's book as V-FISTA \cite[(10.7.7)]{beck_first-order_2017}, and \hl{Nesterov's book as (2.2.22)} \cite{nesterov_lectures_2018}.
-    \par
-    Some other researches in the literatures focus on the convergence of the iterates, and it has much to do with the momentum sequence $(\theta_k)_{k\ge 0}$ displayed in Equation \ref{eqn:nag_example}.
-    Chambolle, Dossal \cite{chambolle_convergence_2015}
-    showed that by choosing sequence $(t_k)_{k \ge 1}$ to be $t_k = (n + a - 1)/a$ where $a > 2$ instead would give $(x_k)_{k \ge 0}$ weak convergence in Hilbert space. 
-    It's put as an open question on what happens to the iterates when $a = 2$. 
-    \par
-    The content of our draft paper answers the question: ``Is it possible to describe something about the NAG algorithm for a set of sequence that is non-traditional?''.
-
-    \textbf{A summary of our contributions now follow.}
-    Our contributions are theoretical and practical. 
-    Out results are based the assumption $F = f + g$ where $g:\RR^n \rightarrow \overline\RR$ is convex, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex. 
-    We relax the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:nag_example} and showed an upper bound of the optimal gap for the sequences $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ that satisfy
+\section{Unifying NAG, and weakening the sequence assumption for convergences (WORK IN PROGRESS)}\label{sec:unify-nes-acceleration}
+    This section is based on our unpublished draft paper. 
+    \subsection{Contributions}
+        Inspired specifically by the technique of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, firstly we present a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG) in Section \ref{sec:rwapg-formulation-convergence}.
+        It has the ability to upper bound $F(x_k) - F(x^*)$ for sequences $(t_k)_{k \ge 0}$ that follows a rule much weaker than Nesterov's update rule. 
+        In addition to a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(t_k)_{k \ge 1}$. 
+        Secondly, we present an alternative to restarting that performs well empirically inspired by a small detail in the convergence proof of R-WAPG. 
+        It also has descriptive power to describe several variants of FISTA in the literatures.  
+        \par
+        Our contributions are two folds, theoretical and practical. 
+        Our results are based the assumption $F = f + g$ where $g:\RR^n \rightarrow \overline\RR$ is convex proper and closed, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function.
+        \par
+        \textbf{A summary of our main results follow. } 
+        Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''. 
+        The choices for $\theta_k$ varies for different variants of the accelerated proximal gradient algorithm. 
+        In Chambolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space. 
+        In Chapter 10 of Beck's Book \cite{beck_first-order_2017}, a variant called V-FISTA can achieve the faster linear convergence rate: $\mathcal O((1 - \sqrt{\mu/L})^k)$ on the optimality gap for $\mu > 0$ strongly convex $F$.
+        V-FISTA has $\theta_t = (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa = \mu/L$. 
+        \par
+        We relax the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example_algorithm} and showed an upper bound of the optimal gap. 
+        Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
         \begin{align*}
@@
         \end{align*}
-    Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the generic algorithm R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wagp-convergence}, \ref{prop:r-wapg-momentum-repr}, it can show that the gap $F(x_k) - F(x^*)$ is bounded by:
+        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wagp-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
         \begin{align*}
@@
         \end{align*}
-    Our second main result shows that, assuming $\mu = 0$ then there exists the choice of $(\alpha_k)_{k \ge 0}$ $\rho_k > 1$ such that our R-WAPG reduces to the variant of FISTA proposed by Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}.
-    In the special case where $(\alpha_k)_{k \ge 0}$ has $\rho_k = 1 \;\forall k \ge 0$, and assuming $\mu = 0$, R-WAPG reduces to the FISTA algorithm proposed in Beck \cite{beck_fast_2009}.
-    If $\mu > 0, \rho_k = 1\;\forall k \ge 0$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
-    In Theorem \ref{thm:fixed-momentum-fista}, we demonstrated that R-WAPG frameworks gives a linear convergence claim for all APG where $\alpha_k := \alpha \in (\mu/L, 1)$ is a fixed constant parameter and $F$ is $\mu > 0$ strongly convex.
+        Our second main result shows that for any $\alpha_k \ge 0$ the choice of sequence $\alpha_k = a/(a + k)$ results in $\rho_k > 1$ for all $k \in \N$ such that R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}.
+        When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
+        In Theorem \ref{thm:fixed-momentum-fista}, it demonstrates that R-WAPG frameworks gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex.
+        Finally, we did the tedious work and present three equivalent forms of R-WAPG in Section \ref{sec:rwapg-equiv-repr} that are comparable to notable Euclidean variants of FISTA and beyond.
+This shows the descriptive power of our R-WAPG framework.
         \par
         Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}). 
-    It doesn't require $L, \mu$ in prior, so it determines the value of $\theta_t$ by estimating $D_f$ on iterates $y_{k}, y_{k + 1}$ with minimal computational cost. 
-    We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and exposes its similarity in terms of behaviors to the FISTA with monotone restart under certain situations.
-    \par
-    \textbf{Notations, and assumptions now follows. }
-    For all the subsection that follows, we let $F:= f + g$ to take the same assumptions as in Section \ref{sssec:additive-composite}. 
-    Recall $T_L$, $\mathcal G_L$ denotes the proximal gradient operator and the gradient mapping operator. 
-    Additional notations are defined in the assumption below: 
+        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ from the Bregman divergence of $f$ with minimal computational cost.
+        We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart.
+        \par
+        Section \ref{sec:preliminaries} introduces the proximal gradient inequality which is instrumental to developing the stepwise convergence claim in the next section. 
+        Section \ref{sec:stepwise-stuff} states and prove an inequality based on a generic iterative algorithm for just one iteration. 
+        Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG algorithm and characterize sufficient conditions for R-WAPG sequence to derive the optimality upper bound in Proposition \ref{prop:wagp-convergence}.
+        Section \ref{sec:rwapg-equiv-repr} gives three equivalent representations of the R-WAPG algorithms that are comparable to instances of APG found in the literatures. 
+        Section \ref{sec:rwapg-literatures} formulates FISTA, and V-FISTA sequences as instance of the R-WAPG sequences.
+        The section proves the convergence rate of several variants of FISTA using the equivalent forms introduced in Section \ref{sec:rwapg-equiv-repr} and the convergence rate developed Section \ref{sec:rwapg-formulation-convergence}.
+        Finally, in Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcase the numerical experiments for regression, LASSO. 
+        The numerical experiments expose very interesting behaviors of the algorithm of our own creativity.
+
+    \subsection{Stepwise formulation of weak accelerated proximal gradient}\label{sec:stepwise-stuff}
+        The goal of this section is to build the R-WAPG algorithm which is described in the Definition \ref{def:wapg} of the next section. 
+        \par 
+        Definition \ref{def:stepwise-wapg} which describes what happens at a single iteration of the R-WAPG algorithm. 
+        It defines a procedure of generating $x_{k + 1}, v_{k + 1}$ given any $x_k, v_k$. 
+        Proposition \ref{prop:stepwise-lyapunov} states the inequality that describes a decreasing quantity that involves $F(x_k), F(x_{k + 1})$ at each single iteration. 
         \begin{assumption}
-        Choose any integer $k\ge 0$. 
-        Given $x_k, y_k, v_k$, we define the following quantities
+            Given $x_k, y_k, v_k$ where $k \in \mathbb Z_+$, we define the following quantities
             \begin{align}
@@
         \end{assumption}
-    \par
-    \todoinline{
-        $\square$ Finish the organizations here after this section is finished. 
-        Still need to explain the numerical experiments section. 
-    }
-    \par
-    \textbf{Organization now follows. }
-    Section \ref{ssec:building-block-rwapg} provides a stepwise description of the R-WAPG iterative algorithm along with an inequality crucial to proving the convergence rate later. 
-    Section \ref{ssec:rwpag-seq-and-alg} introduce the definition of an R-WAPG sequence, which constraints all possible parameters used permitted by the algorithm.
-    The section also states the full R-WAPG algorithm and an upper bound on $F(x_k) - F(x^*)$. 
-    Here, $x_k$ is generated by the R-WAPG algorithm and $x^*$ is the minimizer. 
-    Section \ref{ssec:quiv-repr-rwapg} bring forward three equivalent forms of the R-WAPG algorithm making it more comparable with other Accelerated Proximal Gradient method appeared in the literatures.
-    Section \ref{ssec:describe-variants-with-rwapg} gives characterizations of specific R-WAPG sequence that leads to convergence of the R-WAPG algorithm in terms of the optimality gap. 
-    The section also identifies specific instance of permissible R-WAPG sequences where it fits with the FISTA, V-FISTA, and the algorithm proposed by Chambolle Dossal \cite{chambolle_convergence_2015}.
-    Section \ref{sec:free-rwapg} provides Algorithm \ref{alg:free-rwapg} (Free R-WAPG) which is a parameter free alternative to accelerated proximal gradient method formulated using the R-WAPG we proposed.
-    The algorithm dynamically adjusts the R-WAPG sequence $\alpha_k$ using the Bregman Divergence of smooth part of the objective function at successive extrapolated iterate $y_{k + 1}, y_k$ from the momentum method.
-    Numerical experiments are conducted repeatedly and statistics on the results are displayed.
-
-    \subsection{Building Blocks of R-WAPG}\label{ssec:building-block-rwapg}
-        Definition \ref{def:stepwise-wapg} describes the procedures of generating the iterates $(v_{k + 1}, x_{k + 1})$ given any $(v_k, x_k)$ and parameter $\alpha_k \in (0, 1), \gamma_k > 0$. 
-        Proposition \ref{prop:stepwise-lyapunov} gives an inequality instrumental to the convergence rate analysis, with the same assumption as the definition.
-
+        The proposition follows provides upper bound to $F(x_{k + 1})$ in relations to $F(x_{k})$. 
         \begin{definition}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
             Assume $0 \le \mu < L$.
-            Fix any $k \in \mathbb Z$. 
+            Fix any $k \in \mathbb Z_+$. 
             For any $(v_k, x_k), \alpha_k \in (0, 1), \gamma_k > 0$, let $\hat \gamma_{k + 1}$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ be given by: 
-            \begin{align*}
-                \hat \gamma_{k + 1} &= (1 - \alpha_k)\gamma_k + \mu \alpha_k, 
+            \begin{align}
+                \hat \gamma_{k + 1} &= (1 - \alpha_k)\gamma_k + \mu \alpha_k, \label{eqn:stepwise-wapg-eqn1}
                 \\
                 y_k &= 
-                (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
-                \\
-                g_k &= \mathcal G_L y_k, 
+                (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), \label{eqn:stepwise-wapg-eqn2}
+                \\
+                g_k &= \mathcal G_L y_k, \label{eqn:stepwise-wapg-eqn3}
                 \\
                 v_{k + 1} &= \hat\gamma^{-1}_{k + 1}
-                (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
-                \\
-                x_{k + 1} &= T_L y_k. 
-            \end{align*}
-        \end{definition}
-
+                (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), \label{eqn:stepwise-wapg-eqn4}
+                \\
+                x_{k + 1} &= T_L y_k. \label{eqn:stepwise-wapg-eqn5}
+            \end{align}
+        \end{definition}
         \begin{proposition}[Stepwise Lyapunov]\label{prop:stepwise-lyapunov}\;\\
-            Fix any integer $k \in \mathbb Z$.
-            Given any $v_k, x_k$ and $\gamma_k > 0$, invoke Definition \ref{def:stepwise-wapg} to obtain $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}$. 
-            Fix any arbitrary $R_k \in \RR$.
+            Let $k \in \mathbb Z_+$, $R_k \in \RR$. 
+            Given any $v_k, x_k$ and $\gamma_k > 0$ and $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}, \alpha_k$ that satisfies Definition \ref{def:stepwise-wapg}. 
             Define: 
-            \begin{align*}
+            \begin{align}\label{eqn:stepwise-lya-1}
                 R_{k + 1}
@@
                 \right). 
-            \end{align*}
-            Then it has for all $x^* \in \RR^n$ where $F^* = F(x^*)$, the inequality: 
-            \begin{align*}
-                F(x_{k + 1}) - F^* + R_{k + 1} + \frac{\hat \gamma_{k + 1}}{2}\Vert v_{k + 1} - x^*\Vert^2
+            \end{align}
+            Then for all $x^* \in \RR^n$, we have:
+            {\small
+            \begin{align}\label{ineq:stepwise-lya-2}
+                F(x_{k + 1}) - F(x^*) + R_{k + 1} + \frac{\hat \gamma_{k + 1}}{2}\Vert v_{k + 1} - x^*\Vert^2
                 &\le 
@@
                 \left(
-                    F(x_k) - F^* + R_k + \frac{\gamma_{k}}{2}\Vert v_k - x^*\Vert^2
+                    F(x_k) - F(x^*) + R_k + \frac{\gamma_{k}}{2}\Vert v_k - x^*\Vert^2
                 \right). 
-            \end{align*}
+            \end{align}
+            }
         \end{proposition}
 
-    \subsection{R-WAPG Sequence and R-WAPG algorithm}\label{ssec:rwpag-seq-and-alg}
-        The Definition \ref{def:wapg} gives the definition of an iterative algorithm we called: Relaxed Weak Accelerated Proximal Gradient (R-WAPG) algorithm which generates sequence $(x_k, v_k)_{k \ge 1}$ using the R-WAPG sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given in Definition \ref{def:rwapg-seq}.
-        Proposition \ref{prop:wagp-convergence} shows the upper bound of the optimality gap $F(x_k) - F(x^*)$ with $(x_k)$ generated by the R-WAPG algorithm.
-
+    \subsection{R-WAPG and its convergence rates}\label{sec:rwapg-formulation-convergence}
+        In this section we propose Relaxed Weak Accelerated Proximal Gradient (R-WAPG), see Definition \ref{def:wapg}.
+        R-WAPG algorithm generates iterates $(x_k, y_k, v_k)$ and admits an upper bound on $F(x_k) - F^*$ described in Proposition \ref{prop:stepwise-lyapunov}. 
+        Definition \ref{def:rwapg-seq} introduces the concept of an R-WAPG sequences: $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ which is crucial.
+        The sequences parameterize the R-WAPG algorithm stated in Definition \ref{def:wapg}, it connects the step-wise formulation of R-WAPG (Definition \ref{def:stepwise-wapg}) and can describe the convergence claim of R-WAPG in Proposition \ref{prop:wagp-convergence}.
+        In the next section, it continues to play a crucial role in describing several equivalent forms of the R-WAPG algorithm, and their corresponding convergence claim. 
         \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}\;\\
             Assume $0 \le \mu < L$. 
-            The sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge1}$ are sequences parameterized by $\mu, L$. 
-            They are valid for R-WAPG if all the following holds: 
+            The sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are valid for R-WAPG if all the following holds: 
             \begin{align*}
@@
         \end{definition}
+        % \begin{observation}\label{obs:r-wapg-observation-1}
+        %     The following is true: 
+        %     \begin{enumerate}
+        %         \item $\rho_k > 0$ for all $k \ge 0$. 
+        %         \item $\forall k \ge 1: L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 +\mu\alpha_k$. 
+        %     \end{enumerate}
+        % \end{observation}
+        We now give Relaxed Weak Accelerated Proximal Gradient in details.
         \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}\;\\
@@
         \end{definition}
+        % \begin{observation}\label{obs:r-wapg-observation-2}
+        %     Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018} because $L\alpha_k^{2} = (1 - \alpha_k)L\alpha_{k - 1}^2 + \mu \alpha_k$.
+        %     \par
+        %     For all $k \ge 1$, the algorithm chains together the sequence of $(\hat \gamma_{k+1})_{k \ge 1}$ and $(\gamma_k)_{k \ge 1}$ in Definition \ref{prop:stepwise-lyapunov} through the equalities:
+        %     \begin{align*}
+        %         \hat \gamma_{k + 1} 
+        %         &= L\alpha_k^2 
+        %         \\
+        %         &= (1 - \alpha_k)\gamma_k + \alpha_k \mu
+        %         \\
+        %         &= (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu
+        %         \\
+        %         &= (1 - \alpha_k)\rho_{k - 1}\hat \gamma_{k} + \alpha_k \mu. 
+        %     \end{align*}
+        %     The third equality from Observation \ref{obs:r-wapg-observation-1}. 
+        % \end{observation}
+        Here is the main result of this section. 
         \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}\; \\
@@
             Let vector sequence $(y_k, v_{k}, x_{k})_{k \ge 1}$ and R-WAPG sequences $\alpha_k, \rho_k$ be given by Definition \ref{def:wapg}. 
-            Define $R_1 = 0$ and suppose that for $k = 1, 2, \cdots, N$, we have $R_k$ recursively given by: 
+            Define $R_1 = 0$ and suppose that for $k = 1, 2, \ldots, N$, we have $R_k$ recursively given by: 
             \begin{align*}
@@
             \end{align*}
-            Then for all $k = 1, 2, \cdots, N$: 
+            Then for all $k = 1, 2, \ldots, N$: 
             \begin{align*}
@@
                 \left(
-                    \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
+                    \prod_{i = 0}^{k - 1} \max(1, \rho_{i})
                 \right)
@@
 
-    \subsection{Equivalent forms of R-WAPG algorithm}\label{ssec:quiv-repr-rwapg}
-        Definitions \ref{def:r-wapg-intermediate}, \ref{def:r-wapg-st-form} and \ref{def:r-wapg-momentum-form} are three equivalent representations of the R-WAPG algorithms. 
-        Propositions \ref{prop:wapg-first-equivalent-repr}, \ref{prop:wagp-st-form} and \ref{prop:r-wapg-momentum-repr} states the equivalences between the forms and the sufficient conditions for initial conditions of $x_1, v_1$ such equivalence holds.
-        The remarks of the definitions identifies specific instances in the literatures where the Accelerated Proximal Gradient method were presented under this specific form. 
+    \subsection{Equivalent representations of R-WAPG}\label{sec:rwapg-equiv-repr}
+        This section reduces Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 
+        In the literatures, variants of Accelerated Proximal Gradient algorithm such as FISTA, V-FISTA has different representations. 
+        This shows that R-WAPG provides a unified framework. 
+        These equivalent representations are listed in Definition \ref{def:r-wapg-intermediate}, \ref{def:r-wapg-st-form} and \ref{def:r-wapg-momentum-form}. 
+        These forms are equivalent under a subset of initial conditions. 
+        \par
+        They are comparable to existing APG algorithms in the literatures such as Excersise 12.1 in Ryu, Yin \cite{ryu_large-scale_2022}, Similar Triangle from from Lee et al.
+\cite{lee_geometric_2021}, Ahn Sra \cite{ahn_understanding_2022} and momentum form of (2.2.19) in Nesterov \cite{nesterov_lectures_2018}.
+        Specific instances of Accelerated Proximal Gradient algorithm that has the same form as the Definition \ref{def:r-wapg-intermediate}, Definition \ref{def:r-wapg-st-form} and Definition \ref{def:r-wapg-momentum-form} in the literatures are stated in the remarks that follows the definitions.
+
         \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
@@
             This form of APG is rarely identified in the literatures. 
-            The closest algorithm that fits the form but with $\mu = 0$ is Chapter 12 of 
-            in Ryu and Yin's Book \cite{ryu_large-scale_2022}, right after Theorem 17. 
+            The closest algorithm that fits the form but with $\mu = 0$ is Chapter 12 of in Ryu and Yin's Book \cite{ryu_large-scale_2022}, right after Theorem 17. 
             We created this form which makes the math that follows simpler. 
@@
             The term ``Method of Similar Triangle" was used for Algorithm (6.1.19) in Nesterov's book \cite{nesterov_lectures_2018}, but without the necessary graphical illustrations to clarify it. 
-            Finally, a similar triangle for formulation of FISTA can be found in Equation (2), (3), (4) in \cite{chambolle_convergence_2015}. 
+            Equation (2), (3), (4) in \cite{chambolle_convergence_2015} is a similar triangle formulation of FISTA with $\mu = 0$. 
             To see graphical visualization on why such term is used to describe the APG algorithm in the literatures, see 
@@
         \end{remark}
-        \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\
-            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}), 
-            then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$, and for all $k\ge 1$ they are algebraically equivalent to
-            \begin{align*}
-                & 
-                y_{k} = 
-                \left(
-                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
-                \right)^{-1}
-                \left(
-                    v_{k} + 
-                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
-                \right), 
-                \\
-                & x_{k + 1} = 
-                y_k - L^{-1} \mathcal G_L y_k, 
-                \\
-                & v_{k + 1} = 
-                \left(
-                    1 + \frac{\mu}{L \alpha_k - \mu}
-                \right)^{-1}
-                \left(
-                    v_k + 
-                    \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
-                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
-            \end{align*}
-        \end{proposition}
-        \begin{proposition}[Second equivalent representation of R-WAPG]\label{prop:wagp-st-form}\;\\
-            Let iterates $(y_k, x_{k}, v_{k})_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge 0}$ be given by Definition \ref{def:r-wapg-intermediate}. 
-            Then for all $k \ge 1$, iterate $y_k, x_{k + 1}, v_{k + 1}$
-            satisfy: 
-            \begin{align*}
-                y_{k} &= 
-                \left(
-                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
-                \right)^{-1}
-                \left(
-                    v_{k} + 
-                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
-                \right), 
-                \\
-                x_{k + 1} &= 
-                y_k - L^{-1} \mathcal G_L y_k, 
-                \\
-                v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
-            \end{align*}
-        \end{proposition}
-        \begin{proposition}[Third equivalent representation of R-WAPG]\label{prop:r-wapg-momentum-repr}
-            \;\\
-            Let sequence $(\alpha_k, \rho_k)_{k \ge 0}$ and iterates $(x_k, v_k, y_k)_{k\ge 1}$ given by R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}). 
-            Then for all $k \ge 1$, the iterates $(x_{k + 1}, y_{k + 1})_{k \ge 1}$ are algebraically equivalent to: 
-            \begin{align*}
-                x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
-                \\
-                y_{k + 1} &= 
-                x_{k + 1} + 
-                \frac{\rho_k\alpha_k(1 - \alpha_k)}
-                {\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
-            \end{align*}
-            If in addition, $v_1 = x_1$ then 
-            \begin{align*}
-                y_1 = \left(
-                    1 + \frac{L - L \alpha_1}{L\alpha_1 - \mu}
-                \right)^{-1}\left(
-                    v_1 + \left(
-                        \frac{L - L \alpha_1}{L \alpha_1 - \mu}
-                    \right)x_1
-                \right) = x_1. 
-            \end{align*}
-            In the special case when $\mu = 0$, the momentum term admits simpler representation 
-            \begin{align*}
-                (\forall k \ge 1) \quad 
-                \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
-                & = \alpha_{k + 1}(\alpha_k^{-1} - 1). 
-            \end{align*}
-        \end{proposition}
-
-    \subsection{The descriptive power of R-WAPG on existing variants}\label{ssec:describe-variants-with-rwapg}
-        Lemma \ref{lemma:inverted-fista-seq} identifies a sequence $(\alpha_k)_{k \ge 0}$ such that $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}$ as a specific instance of R-WAPG sequence.
-        The lemma showed that sequence $(\alpha_k^{-1})_{k \ge 0}$ is the FISTA sequence which governs the momentum term and convergence claim in FISTA algorithms and variants alike. 
-        The lemma also provides a simplified convergence claim using the R-WAPG sequence on Proposition \ref{prop:wagp-convergence}. 
-        Theorem \ref{thm:r-wapg-on-cham-doss} stated that the sequences given in Chambolle, Dossal's
-        paper \cite{chambolle_convergence_2015} indeed is an instance of R-WAPG sequence, along with that, it indeed attains a convergence rate $\mathcal O(1/k^2)$. 
-        \par 
+
+    \section{R-WAPG unifies existing accelerations scheme}\label{sec:rwapg-literatures}
+        In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are much more flexible. 
+        They generalize many existing sequences used in accelerated proximal gradient schemes. 
+        \par
+        This section demonstrates that several variants of FISTA in the literatures reduces to the R-WAPG method by setting up the R-WAPG sequences with additional assumptions. 
+        This section will also demonstrate that the convergence claim (Proposition \ref{prop:wagp-convergence}) holds, and it derives convergence rates consistent with results in the literatures.  
+        The table below shows the R-WAPG convergence results specialized into various settings. 
+        \begin{table}[H]
+            {\scriptsize
+            \begin{tabular}{|l|l|l|l|l|}
+            \hline
+                Algorithm & $\mu$ & $\alpha_k$ & $\rho_k$ & Convergence of $F(x_k) - F^*$ 
+            \\ \hline
+                R-WAPG in Definition \ref{def:wapg} & 
+                $\mu \ge 0$ &
+                $\alpha_k \in(\mu/L, 1)$ & 
+                $\rho_k > 0$ &  
+                \begin{tabular}{l}
+                    $\mathcal O \left(\prod_{i = 0}^{k-1} \max(1, \rho_i)(1 - \alpha_{i + 1})\right)$
+                    \\
+                    (Proposition \ref{prop:wagp-convergence})
+                \end{tabular}
+            \\ \hline
+                Chambolle, Dossal 2015 \cite{chambolle_convergence_2015} &  
+                $\mu = 0$  &
+                $ 0< \alpha_k^{-2} \le \alpha_{k + 1}^{-1} - \alpha_{k + 1}^{-2}$ &
+                $\rho_k \ge 1$ &  
+                \begin{tabular}{l}
+                    $\mathcal O(\alpha_k^{2})$ \\ (Theorem \ref{thm:r-wapg-on-cham-doss})    
+                \end{tabular}
+            \\ \hline
+                V-FISTA Beck (10.7.7) \cite{beck_first-order_2017} &
+                $\mu > 0$&
+                $\alpha_k = \sqrt{\mu/L}$ & 
+                $\rho_k = 1$ &
+                \begin{tabular}{l}
+                    $\mathcal O\left((1 - \sqrt{\mu/L})^k\right)$, 
+                    \\
+                    (Theorem \ref{thm:fixed-momentum-fista}, remark)
+                \end{tabular}
+            \\ \hline
+                R-WAPG in Definition \ref{def:wapg} &  
+                $\mu > 0$ &
+                $\alpha_k = \alpha \in (\mu/L, 1)$ &  
+                $\rho_k = \rho > 0$ & 
+                \begin{tabular}{l}
+                    $\mathcal O \left(\max(1 - \alpha, 1 - \mu/(\alpha L))^{k} \right)$\\
+                    (Theorem \ref{thm:fixed-momentum-fista})
+                \end{tabular}
+            \\ \hline
+            \end{tabular}
+            }
+        \end{table}
+        The lemma follows characterizes momentum sequences in the literatures using Definition \ref{def:rwapg-seq}. 
         \begin{lemma}[R-WAPG sequences as inverted FISTA sequence]\label{lemma:inverted-fista-seq}
@@
         \end{lemma}
+        \begin{remark}
+            The sequence $t_k$ is exactly the same as in Theorem 3.1 of Chambolle, Dossal \cite{chambolle_convergence_2015}. 
+        \end{remark}
         \begin{lemma}[Constant R-WAPG sequences]\label{lemma:constant-rwapg-seq}
@@
             \begin{enumerate}
-                \item Fix any $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$ then the constant sequence $\alpha_k := \alpha \in (q, 1)$ and\\
+                \item For any $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, the constant sequence $\alpha_k := \alpha \in (q, 1)$ and\\
                 $\rho_k := \rho=\left(1-r^{-1}\sqrt{q}\right)\left(1 - r \sqrt{q}\right)^{-1} > 0$, hence it's a pair of valid R-WAPG sequence. 
-                \item The momentum term in Definition \ref{def:r-wapg-momentum-form}, which we denoted by $\theta$ has:\\ $\theta = (1 - r^{-1}\sqrt{q})(1 - r\sqrt{q})(1- q)^{-1}$. 
+                \item The momentum terms $\theta_{t + 1}$ in Definition \ref{def:r-wapg-momentum-form}, which we denoted by $\theta$ is the constant:\\ $\theta = (1 - r^{-1}\sqrt{q})(1 - r\sqrt{q})(1- q)^{-1}$
                 \item When $r = 1$, $\theta = (1- \sqrt{q})(1 + \sqrt{q})^{-1}$. 
@@
                 \\
-                For $k = 1, 2, \cdots$, update: 
+                For $k = 1, 2, \ldots$, update: 
                 \begin{align*}
@@
         \end{theorem}
+        \begin{remark}
+            This algorithm described here is exactly the same algorithm being analyzed in the paper by Chambolle, Dossal \cite{chambolle_convergence_2015}. 
+        \end{remark}
         \begin{theorem}[Fixed momentum APG]\label{thm:fixed-momentum-fista}
@@
                 \\
-                Initialize $y_1 = x_1$; for $k = 1, 2, \cdots, N$, update: 
+                Initialize $y_1 = x_1$; for $k = 1, 2, \ldots, N$, update: 
                 \begin{align*}
@@
         \end{theorem}
+        \begin{remark}
+            When $r = 1$, the algorithm described above is exactly the same as the V-FISTA algorithm specified in (10.7.7) of Beck's book \cite{beck_first-order_2017}. 
+        \end{remark}
 
@@
     \subsection{Future works for R-WAPG}
-        The R-WAPG framework neglected one intriguing detail buried in the literatures. 
-        It has the potential to include more variants of the FISTA algorithms and their convergence proof. 
-        Our future works would be to extend the frameworks and weaken it further while retaining the goal of getting some type of upper bound on the value $F(x_k) - F^*$ and show that there are choices for the momentum parameter $\alpha_k$ such that convergence is possible.
+        The R-WAPG framework neglected a detail in the literatures. 
+        Our future works would extend the frameworks and include this detail. 
         \subsubsection{Nesterov's idea of strong convexity transfer}

### 2025-01-22 Notebook LaTEX/R-WAPG/paper3.tex
>w<, a lot of fixes

@@
 \section{R-WAPG and its convergence rates}\label{sec:rwapg-formulation-convergence}
-    In this section we propose Relaxed Weak Accelerated Accelerated Proximal Gradient (R-WAPG), see Definition \ref{def:wapg}.
+    In this section we propose Relaxed Weak Accelerated Proximal Gradient (R-WAPG), see Definition \ref{def:wapg}.
     R-WAPG algorithm generates iterates $(x_k, y_k, v_k)$ and admits an upper bound on $F(x_k) - F^*$ described in Proposition \ref{prop:stepwise-lyapunov}. 
@@
 
-        % If $\alpha_1 \in (0, 1)$ which is true by $\gamma_1 \in (0, L]$, then the entire sequence $\alpha_k \in (0, 1)$. 
-        % Suppose inductively that $\alpha_{k - 1}, \rho_{k - 1}$ are given such that they satisfy $\alpha_{k -1} \in (0, 1)$ and $0 < \rho_{k - 1} \alpha_{k - 1}^2 < 1$. 
-        % Solving the quadratic $L\alpha_k^2=(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2 + \mu \alpha_k$ for $\alpha_k$ yields candidates. 
-        % \begin{align*}
-        %     \alpha_k &= 
-        %     \frac{1}{2}\left(
-        %         \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
-        %         \pm
-        %         \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
-        %     \right). 
-        % \end{align*}
-        % Choosing the positive sign which is the larger one of the roots of the quadratic. 
-        % We have $\alpha_k > 0$ because: 
-        % \begin{align*}
-        %     \alpha_k &=
-        %     \frac{1}{2}\left(
-        %         \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
-        %         +
-        %         \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
-        %     \right)
-        %     \\
-        %     &\ge 
-        %     \frac{1}{2}\left(
-        %         \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
-        %         +
-        %         \left|\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L\right|
-        %     \right) + \alpha_{k - 1}\sqrt{\rho_{k - 1}}
-        %     \\
-        %     & > 0. 
-        % \end{align*}
-        % On the last strict inequality we used the fact that $\rho_{k - 1}> 0, \alpha_{k - 1} > 0$. 
-        % An upper bound can be identified by using inductive hypothesis and considering: 
-        % \begin{align*}
-        %     \alpha_k &= 
-        %     \frac{1}{2}\left(
-        %         \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
-        %         +
-        %         \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
-        %     \right)
-        %     \\
-        %     &
-        %     \frac{1}{2}\left(
-        %         \frac{\mu}{L} + 
-        %         \sup_{x \in (0, 1)}
-        %         \left\lbrace
-        %             -x + \sqrt{(x - \mu/L)^2 + 4x}
-        %         \right\rbrace
-        %     \right)
-        %     \\
-        %     & \le \frac{1}{2}\left(
-        %         \mu/L + \max\left(\mu/L, -1 + \sqrt{(1 - \mu/L)^2 + 4}\right)
-        %     \right) \le 1. 
-        % \end{align*}
-        % Going to the first inequality, we used $\rho_{k - 1} \alpha_{k - 1}^2 < 1$ to get the strict inequality. 
-        % Going from the second to the third inequality, we maximized $\mu/L$ by monotone increasing of linear function and the square root function. 
-        % Therefore, inductively, $\alpha_k \in (0, 1)$ holds. 
-        % However, the limit of $\alpha_k$ could be 1. 
     \end{observation}
@@
         This section lists three equivalent representations of the R-WAPG algorithm. 
-        They are comparable to existing APG algorithms in the literatures such as Excersise 12.1 in Ryu, Yin \cite{ryu_large-scale_2022}, Similar Triangle from from Lee et al.
+        They are comparable to existing APG algorithms in the literatures such as Exercise 12.1 in Ryu, Yin \cite{ryu_large-scale_2022}, Similar Triangle form from Lee et al.
 \cite{lee_geometric_2021}, Ahn Sra \cite{ahn_understanding_2022} and momentum form of (2.2.19) in Nesterov \cite{nesterov_lectures_2018}.
@@
 
-    % We do not claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in literatures. 
-    % Our numerical experiments are explorative and we hope to inspire. 
-    % The presented theories (Proposition \ref{prop:stepwise-lyapunov}, \ref{prop:wagp-convergence}) are our best attempts at making sense of what is happening, and we did it directly with elementary algebra.
-    % In addition, we provided some helpful results on the equivalent representations of R-WAPG to illustrate the descriptive power of the R-WAPG framework. 
-    % Nonetheless, two things are clear from the numerical experiments. 
-    % FR-WAPG performs better than V-FISTA on the first hundreds of iterations, and it doesn't require prior knowledge on parameter $L, \mu$. 
-    % \par
-    % Our theories are somewhat relevant to FR-WAPG since it can partially describe an upper bound of the optimality gap with any sequence of $\alpha_k \in (0, 1)$. 
-    % Unfortunately, it is difficult to know the sequence $(\alpha_k)_{k \ge 0}$ without running the algorithm. 
-    % It would require knowledge about the trajectory taken for a specific initial guess, and the property of $D_f$, the Bregman Divergence of the smooth part. 
-    % We feel that the breakthrough in understanding may not come from elementary results.  
-    % \par 
-    % From a practical point of view, the numerical experiments show that in the beginning of the algorithm, the estimate for $\mu$ can be overestimated.
-    % This is partially explained by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
-    % It also showed that the algorithm performs with mixed charactercteristics of M-FISTA and V-FISTA and it's just fascinating. 
-    % Finally, we observed that the convergence of gradient mapping $\mathcal G_L(y_k)$ becomes more difficult and the algorithm may not be able to terminate for certain objectives.
-
 \bibliographystyle{siam}

### 2025-01-23 Notebook LaTEX/Proposal/proposal.tex
>w<, changes

@@
         First Order Nonsmooth Optimization: 
-        Algorithm Design, Variational analysis, and Applications
+        Unifying Nesterov's acceleration and its applications
     }
@@
     \end{enumerate}
-    The good news is we have definitive answers for all questions in our complete draft paper. 
-    \par
-    In this proposal we explore the Goldilocks zones between these topics: Nesterov's acceleration, algorithms with inexact evaluation of the proximal point operator, and applications.  
-    We want to identify the ``chemistry'' between various properties of functions and the affect it has on the designs/behaviors of first order algorithm for continuous optimization. 
+    The good news is we have definitive answers for all questions in our draft paper. 
+    \par
+    In this proposal we explore the Goldilocks zones between theories and practices of optimization algorithms. 
+    Our topics are Nesterov's acceleration and the method of Catalyst Acceleration which is realization of the theories of Nesterov's acceleration and inexact proximal point method in the settings of variance reduced method in Machine Learning.
     \par
     \textbf{Organizations now follows.} 
-    Section \ref{sec:unify-nes-acceleration}, proposes the method of ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)'' as the foundation to describe several Euclidean variants of Accelerated Proximal Gradient (APG) method in the literatures.
-    The convergence analysis of R-WAPG gives convergence of APG the momentum is much weaker compare to the Nesterov's update rule. 
-    R-WAPG can is generic and can describe well-established variants of FISTA in the literatures with alternative choices of step sizes and beyond. 
-    \par
-    Section \ref{sec:free-rwapg} proposes a practical algorithm that exploits a specific term in the proof of R-WAPG to achieve faster convergence for solving (\ref{eqn:additive-comp-obj}) without restarting and knowing parameter $L, \mu$ in prior.
-    Numerical experiments are presented which shows the competitiveness of our algorithm. 
-    Potential future direction of research is given by the end of the section for the R-WAPG framework. 
-    \par
-    Section \ref{sec:catalyst} complements report completed for MATH 590 Fall Winter 2024. 
-    It's based on a series of recent papers \cite{lin_universal_2015,lin_catalyst_2018,paquette_catalyst_2018} about Catalyst Meta Acceleration for First Order Variance Reduced Methods. 
+    In section \ref{sec:unify-nes-acceleration} we propose the method of ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)'' unifies the convergence results of several Euclidean variants of Accelerated Proximal Gradient (APG) method in the literatures and in addition to claiming the convergence when the momentum sequence doesn't follow the Nesterov's update rule.
+    \par
+    Section \ref{sec:free-rwapg} gives an algorithm which is a reformulation of R-WAPG and, it achieves competitive convergence results (\ref{eqn:additive-comp-obj}) without restarting and knowing parameter $L, \mu$ in prior.
+    Numerical experiments are presented and potential future direction of research is given by the end of the section for the R-WAPG framework. 
+    \par
+    Section \ref{sec:catalyst} reviews the series of papers \cite{lin_universal_2015,lin_catalyst_2018,paquette_catalyst_2018} on Catalyst Meta Acceleration for First Order Variance Reduced Methods. 
+    The content complements report completed for MATH 590 Fall Winter 2024. 
     The end of Section \ref{sec:catalyst} points out potential future direction of research of Catalyst Acceleration.
@@
         So it has 
-        \todo{
-            $\square$ Add Rockafellar's red book \\ $\square$ Cite Section 10 (pg 82) of that book
-        }
-        \hl{$\reli(\dom F)\subseteq \dom(\partial F) \subseteq \dom F$.} 
+        $\reli(\dom F)\subseteq \dom(\partial F) \subseteq \dom F$.
+        See Rockafellar's book \cite[pg 82]{rockafellar_convex_1997}. 
         \par
@@
         The converse holds under convexity as well. 
-        The definitions that follow narrow things further for future discussions. 
+        The definitions that follow narrow things further. 
         \begin{definition}[Strong convexity]\label{def:s-cnvx}
@@
             \end{definition}
-            \begin{lemma}[Proximal gradient model function]\;\\
-                % Take $\widetilde{\mathcal M}^{L^{-1}}, \mathcal M^{L^{-1}}$ as defined in this section, 
-                For all $x \in \RR^n$, $\beta > 0$, it has: 
-                \begin{align*}
-                    \widetilde{\mathcal M}^{\beta^{-1}}_F(x; y)
-                    &= 
-                    \mathcal M^{\beta^{-1}}_F(x; y)- D_f(x, y).
-                \end{align*}
-            \end{lemma}
-            \begin{lemma}[A favorable property of gradient mapping]
-                % Take $F:= f + g$ as defined in this section. 
-                For any $x \in \RR^n$. 
-                Then there exists $v \in \partial g(T_L x)$ such that $\mathcal G_L (x) = v + \nabla f(x)$. 
-            \end{lemma}
+            % \begin{lemma}[Proximal gradient model function]\;\\
+            %     % Take $\widetilde{\mathcal M}^{L^{-1}}, \mathcal M^{L^{-1}}$ as defined in this section, 
+            %     For all $x \in \RR^n$, $\beta > 0$, it has: 
+            %     \begin{align*}
+            %         \widetilde{\mathcal M}^{\beta^{-1}}_F(x; y)
+            %         &= 
+            %         \mathcal M^{\beta^{-1}}_F(x; y)- D_f(x, y).
+            %     \end{align*}
+            % \end{lemma}
+            % \begin{lemma}[A favorable property of gradient mapping]
+            %     % Take $F:= f + g$ as defined in this section. 
+            %     For any $x \in \RR^n$. 
+            %     Then there exists $v \in \partial g(T_L x)$ such that $\mathcal G_L (x) = v + \nabla f(x)$. 
+            % \end{lemma}
             \begin{lemma}[The proximal gradient inequality]\label{thm:prox-grad-ineq}
@@
         \end{definition}
-        \begin{observation}
-            In general, identifying the sequence $(x_k)_{k \ge 0}$ is non-trivial. 
-            But in case it can be found, the method of estimating sequence gives us the convergence rate described by the sequence $(\alpha_k)_{k \ge 0}$, and a candidate algorithm that generates the sequence $(x_k)_{k \ge 0}$.
-            It's two birds with one stone. 
-            \par 
-            If we define $\phi_k$, $\Delta_k(x) := \phi_k (x) - F(x)$ for all $x \in \RR^n$ and assume that $F$ has minimizer $x^*$. 
-            Then observe that $\forall k \ge 0$:  
-            \begin{align*}
-                (\forall x \in \RR^n) \; \Delta_k(x) 
-                &= \phi_k(x) - F(x) \ge \phi_k^* - F(x), 
-                \\
-                x = x_k\implies 
-                \Delta_k(x_k) 
-                &\ge 
-                \phi_k^* - F(x_k) \ge 0;
-                \\
-                x = x_* \implies 
-                \Delta_k(x_*)
-                &\ge \phi_k^* - F_* \ge F(x_k) - F_* \ge 0. 
-            \end{align*}
-            The function $\Delta_k(x)$ is non-negative at points: $x_*, x_k$.
-            We can derive the convergence rate of $\Delta_k(x^*)$ because (ii) says $\forall x \in \RR^n$: 
-            \begin{align*}
-                \phi_{k + 1}(x) - \phi_k(x) = \phi_{k + 1}(x) - F(x) - (\phi_k(x) - F(x))
-                &\le - \alpha_k (\phi_k(x) - F(x))
-                \\
-                \iff
-                \Delta_{k + 1}(x) - \Delta_k(x) &\le
-                - \alpha_k\Delta_k(x)
-                \\
-                \iff 
-                \Delta_{k + 1}(x) 
-                &\le 
-                (1 - \alpha_k)\Delta_k(x). 
-            \end{align*}
-            Unrolling the above recursion it yields: 
-            \begin{align*}
-                \Delta_{k + 1}(x) &\le 
-                (1 - \alpha_k)\Delta_k(x) \le \cdots \le 
-                \left(
-                    \prod_{i = 0}^k(1 - \alpha_i)
-                \right)\Delta_0(x). 
-            \end{align*}
-            Finally, by setting $x = x^*$, $\Delta_k(x^*)$ is non-negative and using (i) it gives: 
-            \begin{align*}
-                F(x_k) - F(x^*) \le \phi_k^* - F(x^*) \le \Delta_k(x^*) = \phi_k(x^*) - F(x^*) \le \left(\prod_{i = 0}^k(1 - \alpha_i)\right)\Delta_0(x^*).
-            \end{align*}
-
-        \end{observation}
-
-\section{Unifying NAG, and weakening the sequence assumption for convergences (WORK IN PROGRESS)}\label{sec:unify-nes-acceleration}
+        % \begin{observation}
+        %     In general, identifying the sequence $(x_k)_{k \ge 0}$ is non-trivial. 
+        %     But in case it can be found, the method of estimating sequence gives us the convergence rate described by the sequence $(\alpha_k)_{k \ge 0}$, and a candidate algorithm that generates the sequence $(x_k)_{k \ge 0}$.
+        %     It's two birds with one stone. 
+        %     \par 
+        %     If we define $\phi_k$, $\Delta_k(x) := \phi_k (x) - F(x)$ for all $x \in \RR^n$ and assume that $F$ has minimizer $x^*$. 
+        %     Then observe that $\forall k \ge 0$:  
+        %     \begin{align*}
+        %         (\forall x \in \RR^n) \; \Delta_k(x) 
+        %         &= \phi_k(x) - F(x) \ge \phi_k^* - F(x), 
+        %         \\
+        %         x = x_k\implies 
+        %         \Delta_k(x_k) 
+        %         &\ge 
+        %         \phi_k^* - F(x_k) \ge 0;
+        %         \\
+        %         x = x_* \implies 
+        %         \Delta_k(x_*)
+        %         &\ge \phi_k^* - F_* \ge F(x_k) - F_* \ge 0. 
+        %     \end{align*}
+        %     The function $\Delta_k(x)$ is non-negative at points: $x_*, x_k$.
+        %     We can derive the convergence rate of $\Delta_k(x^*)$ because (ii) says $\forall x \in \RR^n$: 
+        %     \begin{align*}
+        %         \phi_{k + 1}(x) - \phi_k(x) = \phi_{k + 1}(x) - F(x) - (\phi_k(x) - F(x))
+        %         &\le - \alpha_k (\phi_k(x) - F(x))
+        %         \\
+        %         \iff
+        %         \Delta_{k + 1}(x) - \Delta_k(x) &\le
+        %         - \alpha_k\Delta_k(x)
+        %         \\
+        %         \iff 
+        %         \Delta_{k + 1}(x) 
+        %         &\le 
+        %         (1 - \alpha_k)\Delta_k(x). 
+        %     \end{align*}
+        %     Unrolling the above recursion it yields: 
+        %     \begin{align*}
+        %         \Delta_{k + 1}(x) &\le 
+        %         (1 - \alpha_k)\Delta_k(x) \le \cdots \le 
+        %         \left(
+        %             \prod_{i = 0}^k(1 - \alpha_i)
+        %         \right)\Delta_0(x). 
+        %     \end{align*}
+        %     Finally, by setting $x = x^*$, $\Delta_k(x^*)$ is non-negative and using (i) it gives: 
+        %     \begin{align*}
+        %         F(x_k) - F(x^*) \le \phi_k^* - F(x^*) \le \Delta_k(x^*) = \phi_k(x^*) - F(x^*) \le \left(\prod_{i = 0}^k(1 - \alpha_i)\right)\Delta_0(x^*).
+        %     \end{align*} 
+        % \end{observation}
+
+\section{Unifying NAG, and weakening the sequence assumption for convergences}\label{sec:unify-nes-acceleration}
     This section is based on our unpublished draft paper. 
+    The Nesterov's acceleration scheme which was originally proposed in 1983 \cite{nesterov_method_1983} is a celebrated first order method for solving the minimization problem. 
+    Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
+    \begin{align}
+        & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
+        \\
+        & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
+        \\
+        & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
+        \\
+        & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
+    \end{align}\label{eqn:example_algorithm}
+    If the minimizer $x^*$ exists, then the optimality gap $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, a faster rate compared to gradient descent which is $\mathcal O(1/k)$. 
+    It's consider optimal in some sense and see Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018} for details. 
     \subsection{Contributions}
@@
         \par 
-        Section \ref{sec:preliminaries} introduces the proximal gradient inequality which is instrumental to developing the stepwise convergence claim in the next section. 
-        Section \ref{sec:stepwise-stuff} states and prove an inequality based on a generic iterative algorithm for just one iteration. 
-        Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG algorithm and characterize sufficient conditions for R-WAPG sequence to derive the optimality upper bound in Proposition \ref{prop:wagp-convergence}.
+        Section \ref{sec:stepwise-stuff} states and proves Proposition \ref{prop:stepwise-lyapunov}, an inequality based on a single generic iterative step that acts similar to a descent lemma. 
+        Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG in Definition \ref{def:wapg} and defines the R-WAPG sequence in Definition \ref{def:rwapg-seq}. 
+        Proposition \ref{prop:wagp-convergence} states the convergence rate of R-WAPG through Proposition \ref{prop:stepwise-lyapunov} and the R-WAPG sequence. 
         Section \ref{sec:rwapg-equiv-repr} gives three equivalent representations of the R-WAPG algorithms that are comparable to instances of APG found in the literatures. 
@@
         Finally, in Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcase the numerical experiments for regression, LASSO.
-        The numerical experiments expose very interesting behaviors of the algorithm of our own creativity.
 
@@
         \end{definition}
-        % \begin{observation}\label{obs:r-wapg-observation-1}
-        %     The following is true: 
-        %     \begin{enumerate}
-        %         \item $\rho_k > 0$ for all $k \ge 0$. 
-        %         \item $\forall k \ge 1: L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 +\mu\alpha_k$. 
-        %     \end{enumerate}
-        % \end{observation}
         We now give Relaxed Weak Accelerated Proximal Gradient in details.
@@
         \end{definition}
-        % \begin{observation}\label{obs:r-wapg-observation-2}
-        %     Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018} because $L\alpha_k^{2} = (1 - \alpha_k)L\alpha_{k - 1}^2 + \mu \alpha_k$.
-        %     \par
-        %     For all $k \ge 1$, the algorithm chains together the sequence of $(\hat \gamma_{k+1})_{k \ge 1}$ and $(\gamma_k)_{k \ge 1}$ in Definition \ref{prop:stepwise-lyapunov} through the equalities:
-        %     \begin{align*}
-        %         \hat \gamma_{k + 1} 
-        %         &= L\alpha_k^2 
-        %         \\
-        %         &= (1 - \alpha_k)\gamma_k + \alpha_k \mu
-        %         \\
-        %         &= (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu
-        %         \\
-        %         &= (1 - \alpha_k)\rho_{k - 1}\hat \gamma_{k} + \alpha_k \mu. 
-        %     \end{align*}
-        %     The third equality from Observation \ref{obs:r-wapg-observation-1}. 
-        % \end{observation}
         Here is the main result of this section. 
@@
         \par
-        They are comparable to existing APG algorithms in the literatures such as Excersise 12.1 in Ryu, Yin \cite{ryu_large-scale_2022}, Similar Triangle from from Lee et al.
+        They are comparable to existing APG algorithms in the literatures such as Exercise 12.1 in Ryu, Yin \cite{ryu_large-scale_2022}, Similar Triangle from Lee et al.
 \cite{lee_geometric_2021}, Ahn Sra \cite{ahn_understanding_2022} and momentum form of (2.2.19) in Nesterov \cite{nesterov_lectures_2018}.
@@
         \end{remark}
+
+        The following propositions state the relations between the three representation of R-WAPG and R-WAPG as stated in Definition \ref{def:wapg}. 
+        \par
+        Proposition \ref{prop:wapg-first-equivalent-repr} simplifies Definition \ref{def:wapg} and finds a representation without using auxiliary sequence $\gamma_k, \hat \gamma_k$. 
+        Definition \ref{def:r-wapg-intermediate} states the first simplified form of the R-WAPG algorithm which we call: ``R-WAPG intermediate form''. 
+        Following a similar pattern, Proposition \ref{prop:wagp-st-form}, \ref{prop:r-wapg-momentum-repr} demonstrates two more equivalent representations of the R-WAPG intermediate form (Definition \ref{def:r-wapg-intermediate}) which are formulated into Definition \ref{def:r-wapg-st-form}, \ref{def:r-wapg-momentum-form}.
+        Convergence results from Proposition \ref{prop:wagp-convergence} applies to all these equivalent forms of R-WAPG. 
+        In brief, different equivalent reformulations are summarized as following: 
+        \begin{align*}
+            &\text{Definition \ref{def:wapg}}   \iff 
+            \text{Definition \ref{def:r-wapg-intermediate}}  & \text{By Proposition \ref{prop:wapg-first-equivalent-repr}.}
+            \\
+            & \text{Definition \ref{def:r-wapg-intermediate}}
+            \iff \text{Definition \ref{def:r-wapg-st-form}} & \text{By Proposition \ref{def:r-wapg-st-form}.}
+            \\
+            & 
+            \text{Definition \ref{def:r-wapg-st-form}}\implies 
+            \text{Definition }\ref{def:r-wapg-momentum-form}. 
+            & \text{By Proposition }\ref{prop:r-wapg-momentum-repr}.
+        \end{align*}
+        \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\
+            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}), 
+            then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$, and for all $k\ge 1$ namely
+            \begin{align*}
+                & 
+                y_{k} = 
+                \left(
+                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
+                \right)^{-1}
+                \left(
+                    v_{k} + 
+                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
+                \right), 
+                \\
+                & x_{k + 1} = 
+                y_k - L^{-1} \mathcal G_L y_k, 
+                \\
+                & v_{k + 1} = 
+                \left(
+                    1 + \frac{\mu}{L \alpha_k - \mu}
+                \right)^{-1}
+                \left(
+                    v_k + 
+                    \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
+                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
+            \end{align*}
+        \end{proposition}
+        \begin{proposition}[Second equivalent representation of R-WAPG]\label{prop:wagp-st-form}\;\\
+            Let iterates $(y_k, x_{k}, v_{k})_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge 0}$ be given by Definition \ref{def:r-wapg-intermediate}. 
+            Then for all $k \ge 1$, iterate $y_k, x_{k + 1}, v_{k + 1}$
+            satisfy: 
+            \begin{align*}
+                y_{k} &= 
+                \left(
+                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
+                \right)^{-1}
+                \left(
+                    v_{k} + 
+                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
+                \right), 
+                \\
+                x_{k + 1} &= 
+                y_k - L^{-1} \mathcal G_L y_k, 
+                \\
+                v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
+            \end{align*}
+        \end{proposition}
+        \begin{proposition}[Third equivalent representation of R-WAPG]\label{prop:r-wapg-momentum-repr}
+            \;\\
+            Let sequence $(\alpha_k, \rho_k)_{k \ge 0}$ and iterates $(x_k, v_k, y_k)_{k\ge 1}$ given by R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}). 
+            Then for all $k \ge 1$, the iterates $(x_{k + 1}, y_{k + 1})_{k \ge 1}$ satisfy: 
+            \begin{align*}
+                x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
+                \\
+                y_{k + 1} &= 
+                x_{k + 1} + 
+                \frac{\rho_k\alpha_k(1 - \alpha_k)}
+                {\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
+            \end{align*}
+            If in addition, $v_1 = x_1$ then 
+            \begin{align*}
+                y_1 = \left(
+                    1 + \frac{L - L \alpha_1}{L\alpha_1 - \mu}
+                \right)^{-1}\left(
+                    v_1 + \left(
+                        \frac{L - L \alpha_1}{L \alpha_1 - \mu}
+                    \right)x_1
+                \right) = x_1. 
+            \end{align*}
+            If in addition $\mu = 0$, then the momentum term admits a simpler representation 
+            \begin{align*}
+                (\forall k \ge 1) \quad 
+                \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
+                & = \alpha_{k + 1}(\alpha_k^{-1} - 1). 
+            \end{align*}
+        \end{proposition}
 
@@
             (i) indicates that our theories of R-WAPG is incomplete, since it doesn't predict linear convergence when $g$ is strongly convex. 
-            (ii) indicates that splitting the strongly convex objective so that it's with the proximal operator exposes computational advantage. 
+            (ii) indicates that splitting the strongly convex objective so that it's with the proximal operator gives computational advantage. 
             \par
@@
 \section{Catalyst accelerations and future works}\label{sec:catalyst}
-
+    We start by introducing important assumptions and notations for the Catalyst Meta Acceleration Frameworks. 
     \begin{assumption}\label{ass:catalyst1}
@@
         Assume that minimizer exists for $F$ and the minimum is $F^*$. 
-        Define the model function for all $y\in \RR^n$ to be 
+        For all $x,y\in \RR^n, \beta > 0$ define the model function: 
         \begin{align*}
@@
         \end{align*}
-        We define the Moreau Envelope at $y \in \RR^n$ to be $\mathcal M^*_{F,\beta^{-1}}(y) = \min_{x\in \RR^n} \mathcal M_F^{\beta^{-1}}(x; y)$. 
-        We denote $\mathcal J_{\beta^{-1}F}$ to be the resolvent operator for subgradient of $F$. 
+        We define the Moreau Envelope at $y \in \RR^n$ to be $\mathcal M^*_{F,\beta^{-1}}(y) := \min_{x\in \RR^n} \mathcal M_F^{\beta^{-1}}(x; y)$. 
+        We denote $\mathcal J_{\beta^{-1}F}$ to be the resolvent operator for subgradient of $F$, which is also called the proximal operator. 
     \end{assumption}
@@
         Take $F$ as given by Assumption \ref{ass:catalyst1}.
-        Given any $\epsilon > 0, \kappa > 0$ and $x \in \RR^n$, the absolute criterion C1 characterizes the set of inexact proximal iterates as the set: 
+        For $\epsilon > 0, \kappa > 0$ and $x \in \RR^n$, the absolute criterion C1 characterizes the set of inexact proximal iterates by: 
         \begin{align*}
@@
     Section \ref{ssec:catalyst-intro} gives the main ideas behind the Catalyst Acceleration Framework. 
-    It follows Lin et al.'s first paper \cite{lin_universal_2015} on Catalyst Acceleration, the key innovations and what it can be used for together with a sketch over the complexity analysis of the entire frameworks.
-    Section \ref{ssec:catalyst-second-paper} introduces Lin et al.'s second paper \cite{lin_catalyst_2018} on Catalyst which considers an improved relative error condition stated in \ref{def:catalyst-termination-c2} that bounds the inexactness of the gradient on the Moreau Envelope.
-    This condition not only improves the overall complexity, but it also hints the development of nonconvex gradient based 4WD Catalyst by Paquette \cite{paquette_catalyst_2018}.
+    It follows Lin et al.'s first paper \cite{lin_universal_2015} on Catalyst Acceleration and summarizes the convergence analysis of the algorithm. 
+    Section \ref{ssec:catalyst-second-paper} introduces Lin et al.'s second paper \cite{lin_catalyst_2018} on Catalyst which considers the improved relative error condition stated in Definition \ref{def:catalyst-termination-c2} and discusses its significance.
+    This condition improves the overall complexity and inspired nonconvex gradient based 4WD Catalyst by Paquette \cite{paquette_catalyst_2018}.
 
     \subsection{Introduction to Catalyst}\label{ssec:catalyst-intro}
-        Inspired by accelerated proximal point method from Güler \cite{guler_new_1992}, and inexact proximal point method of Rockafellar 1976 \cite{rockafellar_monotone_1976}, Lin \cite{lin_universal_2015} proposed a generic method taking inspirations from the convergence claims of Accelerated proximal point method to accelerated the convergence rate of first order variance reduced incremental method.
-        The class of variance reduced method is vast, but to use the most relevant feature of this class of first order method is that they are stochastic method that is not slower than full gradient descent in complexity.
+        Inspired by accelerated proximal point Method (APPM) from Güler \cite{guler_new_1992}, and Inexact Proximal Point Method (IPPM) of Rockafellar 1976 \cite{rockafellar_monotone_1976}, Lin \cite{lin_universal_2015} proposed a generic method taking inspirations from the convergence claims   of (APPM) to accelerate Variance Reduced Method (VRM).
+        The fact that VRMs are incremental method that is not slower than full gradient descent in complexity is most relevant to our discussion. 
         See Gower's guide \cite{gower_variance-reduced_2020} for more information on variance reduced methods in machine learning. 
         \par
-        In brief, a variance reduce method (VRM) is a type of 
-        incremental methods
-        for solving a large sum problem: $F(x) = \sum_{i = 1}^{N} f_i(x)$ in machine learning.
-        See Bertsekas's surveys \cite{bertsekas_incremental_2011,bertsekas_incremental_2017} on incremental method for more context. 
+        In brief, VRM is a type of incremental methods for solving a large sum problem: $F(x) = \sum_{i = 1}^{N} f_i(x)$ in machine learning.
+        See Bertsekas's surveys \cite{bertsekas_incremental_2011,bertsekas_incremental_2017} for more context. 
         VRM can be deterministic, or stochastic. 
-        When it's stochastic, the theories focuses on the expected optimality gap: $\mathbb E[F(x_k) - F^*]$, for the inner and outer loop. 
-        Let's assume for simplicity of discussion that it's deterministic and focus on: $F(x_k) - F^*$. 
-        \par 
-        The idea of VRM is to stabilize the estimate of gradient using information of the gradient (which can be estimated, or exact) from all or a subset at previous iterates. 
-        In each iteration, the gradient of just a few samples are used to attain a new estimate of the gradient with minimum additional calculations.
-It gives better complexity than full gradient descent.
-        Compare to traditional stochastic gradient, a smaller variance of the estimated gradients near the minimizer gives faster convergence rate. 
+        When it's stochastic, the theories focus on the expected optimality gap: $\mathbb E[F(x_k) - F^*]$. 
+        Let's assume for simplicity of discussion that it's deterministic, so we focus on: $F(x_k) - F^*$. 
+        \par 
+        VRM stabilizes the estimate of gradient using information from all or a subset of gradients evaluated at previous iterates. 
+        In each iteration, it accesses the gradient of a few samples are used to attain a new estimate of the gradient with minimum additional calculations.  
+        This gives better complexity than full gradient descent over all. 
+        Compare to traditional stochastic gradient, VRM produces smaller variance of the estimated gradient near the minimizer which gives faster convergence rate. 
         Major examples of VRMs include SVRG by Xiao, Zhang \cite{xiao_proximal_2014}, Finito by Defazio et al.
@@
         \par
-        The coming parts introduce the Catalyst algorithms and its key innovations. 
-        The last section reviews recent literatures on the topics and gives potential future works. 
+        Next, we introduce the first Catalyst algorithm in \cite{lin_universal_2015}. 
         \begin{definition}[Lin's Universal Catalyst Acceleration]\label{def:lin-catalyst-original}\; \\
@@
             Let the initial estimate be $x_0 \in \RR^n$, fix parameters $\kappa > 0$ and $\alpha_0 \in (0, 1]$. 
-            Let $(\epsilon_k)_{k \ge 0}$ be an error sequence chosen for the evaluation for inexact proximal point method. 
+            Let $(\epsilon_k)_{k \ge 0}$ be an absolute error sequence chosen for the evaluation for inexact proximal point method. 
             \begin{tcolorbox}
@@
                 \frac{1}{2}\left(
-                    - \alpha_{k - 1}^2 - q + \sqrt{(q + \alpha_{k - 1})^2 + 4 \alpha_{k - 1}}
+                    q - \alpha_{k - 1}^2 + \sqrt{(q + \alpha_{k - 1})^2 + 4 \alpha_{k - 1}}
                 \right), 
@@
             where $q = \mu/(k + \mu)$. 
-            Lin suggests different choices for the parameter $\kappa > 0$ depending on the algorithm chosen to evaluate the subroutine for $\mathcal J_{\kappa^{-1}F}^{\epsilon_k}y_{k - 1}$. 
-            The choice of $\epsilon_k$ depends on the estimated optimality gap $F(x_0) - F^*$ where $F^*$ is the minimum of $F$ and whether $\mu > 0$ or $\mu = 0$. 
+            The choices for $\kappa, \epsilon_k$ will come later. 
         \end{remark}
         \textbf{Notations now follows}. 
-        With a fixed regularization parameter $\kappa > 0$, the outer loop (Definition \ref{def:lin-catalyst-original}) produces $(y_{k}, x_k)_{k \ge k}$ denote it by $\mathbb A$. 
-        Typically, an iterative scheme (i.e: VRM) with a known complexity is assigned to find inexact proximal iterates $x_k \in {\mathcal J}_{\kappa^{-1}F}^{\epsilon_k} y_{k - 1}$. 
-        We refer this algorithm as the inner loop and denote it by $\mathbb M$. 
-        Without loss of generality assume it generates some convergence sequence $(z_{k, t})_{t \ge 0}$ where $k$ is the corresponding iteration counter of the outer loop. 
-        \par 
-        The choice of error sequence $(\epsilon_k)_{k \ge 0}$ determines iteration $\mathbb A, \mathbb M$. 
-        The total iteration complexity of the algorithm counts the total number of inner loop iteration. 
+        With a fixed regularization parameter $\kappa > 0$, the outer loop (i.e: Definition \ref{def:lin-catalyst-original}) produces $(y_{k}, x_k)_{k \ge k}$ denote it by $\mathbb A$. 
+        Typically, an iterative scheme (i.e: VRM) with a known complexity is assigned to find inexact proximal iterates $x_k \in {\mathcal J}_{\kappa^{-1}F}^{\epsilon_k} (y_{k - 1})$. 
+        We refer to it as the inner loop and denote it by $\mathbb M$. 
+        Without loss of generality assume it generates some iterates $(z_{k, t})_{t \ge 0}$ where $k$ is the corresponding iteration counter of the outer loop and $t$ is the iteration counter of the inner loop.
+        \par 
+        The choice of absolute error sequence $(\epsilon_k)_{k \ge 0}$ determines the iteration complexity of both $\mathbb A, \mathbb M$. 
+        The total iteration complexity of Catalyst counts the total number of inner loop iteration given  the number of outer loop iterations. 
         The term ``iteration complexity'' refers to the number of iterations required to achieve a desired accuracy, a concept related to the convergence rate of the algorithm. 
-        The term ``complexity'' refers to the total number of oracle calls, in our context it depends on the specific implementation of $\mathbb M$. 
-        Due to the fact that function $F$ is convex, we focus on the convergence rate of the optimality gap $F(x_k) - F^*\*$ for $\mathbb A$ and convergence of the model function $\mathcal M_F^{\kappa^{-1}}(\cdot, y_{k - 1})$ for $\mathbb M$ given $y_{k - 1}, \epsilon_k$ and initial guess $z_{k, 0}$.
+        We adopt iteration complexity in the sections that follow. 
+        % The term ``complexity'' refers to the total number of oracle calls, in our context it depends on the specific implementation of $\mathbb M$. 
+        Since $F$ is convex, we focus on the convergence rate of the optimality gap $F(x_k) - F^*\*$ for $\mathbb A$ and convergence of the model function $\mathcal M_F^{\kappa^{-1}}(\cdot, y_{k - 1})$ for $\mathbb M$ given $y_{k - 1}, \epsilon_k$ and initial guess $z_{k, 0}$.
         \par
         \subsubsection{Outer loop iteration complexity}
-            The error sequence $(\epsilon_k)_{k \ge 0}$ governs the convergence rate of the outer loop for $F(x_k) - F^*$ to converge. 
+            The error sequence $(\epsilon_k)_{k \ge 0}$ controls the convergence rate of $F(x_k) - F^*$ of the outer loop $\mathbb A$. 
             Depending on either $\mu > 0$, or $\mu = 0$, the choice of $(\epsilon_k)_{k\ge 0}$ differs. 
@@
             \end{remark}
-            The same convergence claims hold if smaller value of $\epsilon_k$ is taken, Theorem \ref{thm:err-seq-outer-s-cnvx}, \ref{thm:erro-seq-outer-cnvx} gives the largest possible error sequence $(\epsilon_k)_{k \ge 0}$ such that the convergence claim holds.
-            Of course, taking smaller values of $(\epsilon_k)_{k \ge0}$ as suggested by the above theorems for $\mathbb M$ will hinder its convergence. 
-            \par
-            Observe that the error sequence $(\epsilon_k)_{k \ge 0}$ requires prior knowledge of $F^*$. 
+            The same convergence claims hold if smaller value of $\epsilon_k$ is taken, Theorem \ref{thm:err-seq-outer-s-cnvx}, \ref{thm:erro-seq-outer-cnvx} gives the largest possible absolute error sequence $(\epsilon_k)_{k \ge 0}$ such that the convergence claim holds.
+            Of course, the results still hold if we take smaller values of $(\epsilon_k)_{k \ge0}$ as suggested by the above theorems, but it will increase the iteration complexity of $\mathbb M$. 
+            \par
+            Observe the absolute error sequence $(\epsilon_k)_{k \ge 0}$ requires prior knowledge of $F^*$. 
             It's poses no theoretical concerns, but it's of upmost practical concern since $F^*$ may not be accessible in practice prior to executing the algorithm. 
-            In the work by Lin et al., the example algorithm given is 
-            D.3 Accelerating MISO Prox.
+            In the work by Lin et al. \cite{lin_universal_2015}, the example algorithm given is in appendix item D.3 called Accelerated MISO Prox.
             It automatically builds a lower bound estimates on $F^*$ in the outer loop as the algorithm executes.
             \par 
-            The convergence of the outer loop made use of an inexact version of the proximal gradient inequality (similar to Theorem \ref{thm:prox-grad-ineq}) stated as Lemma A.7 in \cite{lin_universal_2015}.
-            This lemma is instrumental for deriving an inexact variant of the estimating sequence $\phi_k^* \ge F(x_k) + \xi_k$. 
+            An inexact version of the proximal gradient inequality (similar to Theorem \ref{thm:prox-grad-ineq}) stated as Lemma A.7 in \cite{lin_universal_2015} derives the convergence of $\mathbb A$.
+            It is instrumental for formulating an inexact variant of the estimating sequence $\phi_k^* \ge F(x_k) + \xi_k$. 
             The convergence proof (outer and inner loop together) from Lin was inspired by Schmidt's Inexact Proximal Gradient method \cite{schmidt_convergence_2011}. 
             The technique of estimating sequence introduced back in Definition \ref{def:nes-est-seq} did the heavy lifting, but it results in depressingly long proof making it unsuitable for exposition here.
-            Significant pieces of theoretical innovations are covered in details in our most recent Fall Winter 2024 MATH 590 report. 
-            The parts that come will complement content in the report, filling up missing content and attempts to build a bigger picture of Catalyst Acceleration.
+            Significant pieces of theoretical innovations using Nesterov's estimating sequence are covered in details in our most recent Fall Winter 2024 MATH 590 report. 
+            The parts that come will complement the report to focus on the big picture of Catalyst Acceleration.
 
         \subsubsection{Inner loop complexity}
-            The iteration complexity of $M$ relates to the outer loop when warm start is used. 
+            The iteration complexity of $\mathbb M$ relates to the outer loop when warm start is used. 
             The Catalyst Paper \cite{lin_universal_2015} suggested the use of $z_{k, 0} = x_{k - 1}$ as the warm start condition. 
-            With Assumption \ref{ass:linear-convergence-inner-loop}, and the suggested warm start condition,  Lin et al.
-derived the upper bound of the iteration complexity of $\mathbb M$, which are stated in Proposition 3.2, 3.3 in their text, and \ref{prop:inner-loop-complexity-cnvx}, \ref{prop:inner-loop-complexity-s-cnvx} restates things below in our notations.
+            With Assumption \ref{ass:linear-convergence-inner-loop}, and the suggested warm start condition,  Lin et al. derived the upper bound of the iteration complexity of $\mathbb M$.
+            These results are stated as Proposition 3.2, 3.3 of their text.
+            Here, \ref{prop:inner-loop-complexity-cnvx}, \ref{prop:inner-loop-complexity-s-cnvx} restates them in our notations. 
             These two theorems relate the convergence of $\mathbb M, \mathbb A$ and gives a convergence rate of $F(x_k) - F^*$ expressed using the total number of iteration underwent by $\mathbb M$. 
             \begin{assumption}[Linear convergence of inner loop]\label{ass:linear-convergence-inner-loop}
-                Fix any $k \in \N$, any $y \in \RR^n$. 
+                For any $k \in \N$, $y \in \RR^n$. 
                 Suppose $\mathbb M$ generates iterates $(z_{k, t})_{t \ge 0}$ for the inner loop iteration such that there exists $A > 0$, and it has: 
@@
             \begin{remark}
-                Assumption is mild given the fact that model function $\mathcal M(\cdot, y_{k - 1})$ is $\mu + \kappa$ strongly convex given Assumption \ref{ass:catalyst1}.
-                For example, with smoothness assumption on $F$, many VRMs, or gradient descent method can achieve linear convergence under strong convexity. 
-                Since $\kappa$ is fixed, this assumption can be applied for all $k$ for $\mathbb A$. 
+                This assumption is legitimate for example VRMs discussed earlier. 
+                See Section \ref{ssec:catalyst-future} for concerns regarding this assumption. 
             \end{remark}
@@
                     \item $\mathbb M$ has linear convergence rate as specified in Assumption \ref{ass:linear-convergence-inner-loop}, 
-                    \item $\mathbb M$ is initialized with  $z_{k, 0} = x_{k - 1}$. 
+                    \item $\mathbb M$ is initialized with  $z_{k, 0} = x_{k - 1}$ for all $k \ge 2$. 
                 \end{enumerate}
@@
                 \end{enumerate}
-                Then there exists $T_{\mathbb M} \le \widetilde{\mathcal O}(1 / \tau_{\mathbb M})$ such that for any $k \ge 1$. 
-                Then it requires at most\\ $T_{\mathbb M}\log(k + 2)$ iterations for $\mathbb M$ to achieve accuracy $\epsilon_k$.    
+                Then there exists $T_{\mathbb M} \le \widetilde{\mathcal O}(1 / \tau_{\mathbb M})$ such that for any $k \ge 1$, it requires at most\\ $T_{\mathbb M}\log(k + 2)$ iterations for $\mathbb M$ to achieve accuracy $\epsilon_k$.
             \end{proposition}
@@
             The last inequality is $T_{\mathbb M} < \widetilde{\mathcal O}(1/\tau_{\mathbb M})$ from Proposition \ref{prop:inner-loop-complexity-cnvx}. 
-            In both cases, the convergence rate remains optimal as measure by the total number of $\mathbb M$. 
-            \par 
+            In both cases, the convergence rate remains in the same big O class as measure by the total number of $\mathbb M$.
+
+    \subsection{The second Catalyst Acceleration paper}\label{ssec:catalyst-second-paper}
         Lin et al.'s second paper on Catalyst Acceleration \cite{lin_catalyst_2018} describes new ideas to choose the termination criteria for the inner for evaluating $\mathcal J_{\kappa^{-1}F}^{\epsilon_k} y_k$ and gives alternatives to the error sequence $\epsilon_k$ based on those termination criteria.
-            To elucidate, consider the model function $\mathcal M_F^{\kappa^{-1}}(x; y)$ to be $\mu + \kappa$ strongly convex. 
-            Therefore, it has error bound condition: 
-            \begin{align*}
-                (\forall x\in \RR^n) \quad 
-                \mathcal M^{1/\kappa}_F(x; y) -
-                \mathcal M_{F, 1/\kappa}^*(y) 
-                &\le (\kappa + \mu)\dist
-                    \left(
-                        \mathbf 0, \partial \mathcal M^{1/\kappa}_F(x; y)
-                    \right)^2. 
-            \end{align*}
-            By choosing $x$ such that $\dist\left(\mathbf 0, \partial \mathcal M_F^{1/\kappa}(x; y)\right) \le \sqrt{\epsilon}$, it ensures $x \in \mathcal J^\epsilon_{\kappa^{-1}F}(y)$. 
-            Unfortunately, this is a difficult in practice because a full gradient evaluation on the model function $\mathcal M^{1/\kappa}_F(\cdot; y)$ is costly (compare to the small amount required for VRM, which is just the gradient of a few samples.), so Lin suggested alternatives of inner loop termination criteria, and/or upper bounds of inner loop iteration to make Catalyst Acceleration competitive in practice.
-            % \par 
-            % These conflicts in the theories and practice of the Catalyst Accelerations framework are the focuses of Lin's second Catalyst paper \cite{lin_catalyst_2018}. 
-            % The paper has the following new ideas: 
-            % \begin{enumerate}
-            %     \item A relative termination criteria that bounds the gradient of the problem in the inner loop, which results in an error sequence without $F^*$, and simpler proof without using the Nesterov's estimating sequence, and getting rid of the bounded level set assumption in Proposition \ref{prop:inner-loop-complexity-cnvx}.
-            %     \item A more comprehensive convergence proof, for 2 different type of error bounds with, including the smooth plus nonsmooth composite objective. 
-            % \end{enumerate}
-            % The list above is not exhaustive.
-
-    \subsection{The second Catalyst Acceleration paper}\label{ssec:catalyst-second-paper}
-        This section discusses major contents in Lin's second Catalyst paper \cite{lin_catalyst_2018}. 
-        To expedite the execution of $\mathbb M$ in general given an error sequence $(\epsilon_k)_{k \ge 0}$ (or equivalently some lower bounds of it), Lin suggested the following new ideas which are not  mutually exclusive:
+        % To elucidate, consider the model function $\mathcal M_F^{\kappa^{-1}}(x; y)$ to be $\mu + \kappa$ strongly convex. 
+        % Therefore, it has error bound condition: 
+        % \begin{align*}
+        %     (\forall x\in \RR^n) \quad 
+        %     \mathcal M^{1/\kappa}_F(x; y) -
+        %     \mathcal M_{F, 1/\kappa}^*(y) 
+        %     &\le (\kappa + \mu)\dist
+        %         \left(
+        %             \mathbf 0, \partial \mathcal M^{1/\kappa}_F(x; y)
+        %         \right)^2. 
+        % \end{align*}
+        % By choosing $x$ such that $\dist\left(\mathbf 0, \partial \mathcal M_F^{1/\kappa}(x; y)\right) \le \sqrt{\epsilon}$, it ensures $x \in \mathcal J^\epsilon_{\kappa^{-1}F}(y)$. 
+        % Unfortunately, this is a difficult in practice because a full gradient evaluation on the model function $\mathcal M^{1/\kappa}_F(\cdot; y)$ is costly (compare to the small amount required for VRM, which is just the gradient of a few samples.), so Lin suggested alternatives of inner loop termination criteria, and/or upper bounds of inner loop iteration to make Catalyst Acceleration competitive in practice.
+        \par
+        This section summarizes major results in Lin's second Catalyst paper \cite{lin_catalyst_2018}. 
+        To expedite the execution of $\mathbb M$ in general given some error sequence $(\epsilon_k)_{k \ge 0}$ (or equivalently some lower bounds of it), Lin et al.
+suggested the following new ideas which are not mutually exclusive:
         \begin{enumerate}
-            \item An improved warm start strategy at the end of Section 3. 
-            It improved the convergence rate under different termination criteria, and it supports smooth plus nonsmooth objective. 
-            \item A relative termination criterion C2 stated in Definition \ref{def:catalyst-termination-c2}, governed by the error sequence $(\delta_k)_{k \ge 0}$. 
-            The sequence $\delta_k$ doesn't require knowledge on $F^*$, it simplifies the convergence proof, gives better bounds on the complexity for $\mathbb M$ without using bounded level set condition.
+            \item They gave an improved warm start strategy at the end of Section 3 of their paper. 
+            It improved the convergence rate using relative termination criteria in Definition \ref{def:catalyst-termination-c2}, and it supports smooth plus nonsmooth objective. 
+            \item They gave a relative termination criterion C2 stated in Definition \ref{def:catalyst-termination-c2} which is controlled by the relative error sequence $(\delta_k)_{k \ge 0}$. 
+            The sequence $\delta_k$ doesn't require the knowledge of $F^*$, it simplifies the convergence proof and gives better bounds on the complexity of $\mathbb M$ without using bounded level set assumption.
             Recall that Theorem \ref{prop:inner-loop-complexity-cnvx} requires bounded level set assumption on $F$. 
@@
             Take $F$ as given by Assumption \ref{ass:catalyst1}. 
-            Given any $\delta \in (0, 1]$, $\kappa > 0$ and $x \in \RR^n$, the relative criterion C2 is characterized by the set: 
+            Given any $\delta \in (0, 1]$, $\kappa > 0$ and $x \in \RR^n$, the relative criterion C2 of the inexact resolvent is defined by: 
             \begin{align*}
@@
         \end{definition}
-        Observe that, if we set $\epsilon_{k} = \delta\kappa/2\Vert x - z\Vert^2$ then $\widetilde{\mathcal J}_{\kappa^{-1}F}^{\delta} (x) = \mathcal J_{\kappa^{-1}F}^\epsilon (x)$. 
+        \begin{remark}
+            Observe that, if we set $\epsilon = \delta\kappa/2\Vert x - z\Vert^2$ then $\widetilde{\mathcal J}_{\kappa^{-1}F}^{\delta} (x) = \mathcal J_{\kappa^{-1}F}^\epsilon (x)$. 
             The relative inexact condition can be interpreted as an adaptive inexactness condition.     
-        Stated by Lin, the following lemmas are the sufficient conditions and consequences of termination criteria C1, C2. 
+            Observe that $\mathcal J_{\kappa^{-1}F} (x) \subseteq \widetilde{\mathcal J}_{\kappa^{-1}F}^{\delta}(x)$ hence the set is nonempty. 
+        \end{remark}
+        Stated by Lin, the following lemmas gives the sufficient condition for evaluating inexact proximal point up to accuracy $\epsilon$. 
         \begin{lemma}[Sufficient condition for C1]\label{lemma:sufficient-c1}
@@
             \end{align*}
-            For any $z$ define proximal gradient point 
+            For any $z \in \RR^n$, define proximal gradient point 
             \begin{align*}
@@
         \subsubsection{Consequences of the inner loop termination criteria}
-            Lemma \ref{lemma:sufficient-c1} describes a sufficient conditions to verify the membership of $\bar z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$ through the proximal gradient operator on $F:= f_\kappa(z) + g(z)$ which of practical importance because it translates criterion C1 into something implementable, i.e: the proximal gradient operator.
+            Lemma \ref{lemma:sufficient-c1} describes a sufficient conditions to verify the membership of $\bar z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$ through the proximal gradient operator on $F:= f_\kappa(z) + g(z)$ which has practical importance because it translates criterion C1 into something implementable, i.e: the proximal gradient operator.
             For theoretical interests, the absolute and relative criteria C1, C2 places bound on the true error of the gradient of Moreau Envelope at the point $x$. 
@@
             The following are results proved in Lin's second Catalyst paper. 
-            Given any $\epsilon > 0$ if $z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$, define the approximated gradient mapping $\mathcal G_{\kappa^{-1}F}^\epsilon (z) := \kappa(x - z)$.
+            Given any $\epsilon > 0$ if $z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$, define the absolute inexact gradient mapping $\mathcal G_{\kappa^{-1}F}^\epsilon (z) := \kappa(x - z)$.
             Then
@@
             \end{align*}
-            Similarly, if $z \in \widetilde{\mathcal J}_{\kappa^{-1}F}^\delta(x)$, define the inexact gradient mapping $\widetilde{\mathcal G}_{\kappa^{-1}F}^\delta(x) = \kappa(x - z)$, we have: 
+            The above says that the gradient mapping $\mathcal G_{\kappa^{-1}F}^{\epsilon}(z)$ approximates the gradient of Moreau Envelope of $F$ at $x$. 
+            Similarly, if $z \in \widetilde{\mathcal J}_{\kappa^{-1}F}^\delta(x)$, define the relative inexact gradient mapping $\widetilde{\mathcal G}_{\kappa^{-1}F}^\delta(x) = \kappa(x - z)$, we have:
             \begin{align*}

### 2025-01-23 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

@@
     \subsection{Contributions of this paper}
-        Inspired specifically by the technique of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, firstly we present a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG) in Section \ref{sec:rwapg-formulation-convergence}.
-        It has the ability to upper bound $F(x_k) - F(x^*)$ for sequences $(t_k)_{k \ge 0}$ that follows a rule much weaker than Nesterov's update rule. 
-        In addition to a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(t_k)_{k \ge 1}$. 
-        Secondly, we present an alternative to restarting that performs well empirically inspired by a small detail in the convergence proof of R-WAPG. 
-        It also has descriptive power to describe several variants of FISTA in the literatures.  
-        \par
         Our contributions are two folds, theoretical and practical. 
         Our results are based the assumption $F = f + g$ where $g:\RR^n \rightarrow \overline\RR$ is convex proper and closed, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function.
+        \par
+        Inspired specifically by the technique of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, firstly we present a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG) in Section \ref{sec:rwapg-formulation-convergence}.
+        It can upper bound $F(x_k) - F(x^*)$ for sequences $(t_k)_{k \ge 0}$ that doesn't follow Nesterov's update rule and it unifies the convergence results of several Euclidean variants of FISTA. 
+        Secondly, we present an alternative to restarting that performs well empirically inspired by a detail in the convergence proof of R-WAPG with extensive numerical experiments. 
         \par
@@
         \par
-        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}). 
+        Our practical contribution is an algorithm inspired by a detail in the proof of Proposition \ref{prop:wagp-convergence} which is called ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}).
         The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ from the Bregman divergence of $f$ with minimal computational cost.
@@
         \par
-        Section \ref{sec:preliminaries} introduces the proximal gradient inequality which is instrumental to developing the stepwise convergence claim in the next section. 
-        Section \ref{sec:stepwise-stuff} states and prove an inequality based on a generic iterative algorithm for just one iteration. 
-        Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG algorithm and characterize sufficient conditions for R-WAPG sequence to derive the optimality upper bound in Proposition \ref{prop:wagp-convergence}.
+        Section \ref{sec:stepwise-stuff} states and proves Proposition \ref{prop:stepwise-lyapunov}, an inequality based on a single generic iterative step that acts similar to a descent lemma. 
+        Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG in Definition \ref{def:wapg} and defines the R-WAPG sequence in Definition \ref{def:rwapg-seq}. 
+        Proposition \ref{prop:wagp-convergence} states the convergence rate of R-WAPG through Proposition \ref{prop:stepwise-lyapunov} and the R-WAPG sequence. 
         Section \ref{sec:rwapg-equiv-repr} gives three equivalent representations of the R-WAPG algorithms that are comparable to instances of APG found in the literatures. 
@@
             (3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}.
-
         \end{remark}

### 2025-01-23 Notebook LaTEX/R-WAPG/paper3.tex
>w<, big fixes and changes

@@
         \par
+        \textbf{The remainder of this paper is organized as follows. }
         Section \ref{sec:stepwise-stuff} states and proves Proposition \ref{prop:stepwise-lyapunov}, an inequality based on a single generic iterative step that acts similar to a descent lemma. 
@@
     \begin{proof}
-        For $x \in \dom g$, by definition we have: 
+        The proof is direct using algebra and the definitions. 
+        For $x \in \dom g, y \in \RR^n$, using the definition of $\widetilde{\mathcal M}^{L^{-1}}(x; y)$ it has: 
         \begin{align*}
@@
         For simplicity of notations, we write $T$ for $T_L$. 
-        The model function $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is an $L + \mu$ strongly convex function, so it admits quadratic growth conditions over minimizer $Ty$ and for all $x \in \RR^n$:
+        The proof is direct algebra and it starts by deriving an intermediate inequality from the quadratic growth condition of the model function.
+        Then it uses the characterization of strong convexity to simplify it to obtain the desired results. 
+        \par
+        $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is $L + \mu$ strongly convex by Assumption \ref{ass:smooth-nsmooth-additive} and its definition. 
+        We see that it admits quadratic growth over the minimizer $Ty$ therefore for all $x \in \RR^n$ it follows that: 
         {\smaller
@@
             + D_f(Ty; y)
+            \quad 
+            \text{By Lemma \ref{lemma:pg-envelope}}
             \\
@@
             - D_f(x, y) 
-            + D_f(Ty, y). 
+            + D_f(Ty, y). \quad \text{By $\mu \ge 0$}
         \end{align*}
         }
-        Now, consider the lower bound of $D_f(x, y) \ge \mu/2\Vert x - y\Vert^2$ which is true for all $x, y \in \RR^n$ by strong convexity of $f$. 
-        Then it has for all $x \in \RR^n, y \in \RR^n$: 
+        From $\mu \ge 0$ strong convexity of $f$, it has $D_f(x, y) \ge \mu/2\Vert x - y\Vert^2$ which is true for all $x, y \in \RR^n$. 
+        Consequently, it has for all $x \in \RR^n, y \in \RR^n$: 
         \begin{align*}
@@
             \\
-            &\le 
+            &=
             F(x) - F(Ty)
@@
             \\
-            &\le 
+            &=
             F(x) - F(Ty) - \langle L(y - Ty), x - y\rangle - \frac{\mu}{2}\Vert x - y \Vert^2
@@
     \end{definition}
-    \begin{observation}\label{obs:stepwise-wapg}
-        Let's observe Definition \ref{def:stepwise-wapg} closely. 
-        We make two crucial observations here. 
-        We have $x_k, y_k, v_k$ lie on the same line because and they have the following equivalent equalities: 
-        \begin{align*}
-            y_k - v_k &= 
-            \frac{\hat \gamma_{k + 1}}{\alpha_k \gamma_k}(x_k - y_k), 
-            \tag{Q1}\label{eqn:Q1}
-            \\
-            y_k - x_k &= 
-            \frac{\alpha_k \gamma_k}{\gamma_k + \alpha_k \mu}(v_k - x_k). 
-            \tag{Q2}\label{eqn:Q2}
-        \end{align*}
-    \end{observation}
-        To see \eqref{eqn:Q1}, observe 
-        \begin{align*}
-            y_k - v_k &= 
-            \frac{\hat \gamma_{k + 1}}{\alpha_k \gamma_k}(x_k - y_k)
-            \\
-            \iff 
-            -(\alpha_k \gamma_k \hat \gamma^{-1}_{k + 1} + 1)y_k
-            &= 
-            - \alpha_k \gamma_k \hat \gamma^{-1}_{k + 1}v_k - x_k
-            \\
-            \iff 
-            y_k &= 
-            \frac{
-                \alpha_k \gamma_k \hat \gamma_{k + 1}^{-1}v_k + x_k
-            }{1 + \alpha_k \gamma_k \hat \gamma_{k + 1}^{-1}}
-            \\
-            &=  
-            \frac{\alpha_k \gamma_k v_k + \hat \gamma_{k + 1} x_k}{\gamma_k + \alpha_k \mu}.
-        \end{align*}
-        On the first equality \eqref{eqn:Q1}, we multiplied both side of the equation by $\hat\gamma_{k + 1}/\alpha_k \gamma_k$ and then grouped $y_k$. 
-        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma_{k + 1}$, then simplifies the denominator by rearranging \eqref{eqn:stepwise-wapg-eqn1} into $\hat \gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$.
-        To see the second equality \eqref{eqn:Q2}, consider \eqref{eqn:stepwise-wapg-eqn2}: 
-        \begin{align*}
-            y_k &= (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k)
-            \\
-            \iff
-            y_k - x_k &= 
-            (\gamma_k + \alpha_k \mu)^{-1}
-            (\alpha_k \gamma_k v_k - (\gamma_k + \alpha_k \mu)x_k + \hat \gamma_{k + 1} x_k)
-            \\
-            \iff 
-            (\gamma_k + \alpha_k \mu)(y_k - x_k)
-            &= 
-            \alpha_k\gamma _kv_k + 
-            (\hat \gamma_k - \gamma_k - \alpha_k \mu) x_k
-            \\
-            &= \alpha_k \gamma_k v_k - \alpha_k \gamma_k x_k 
-            \\
-            &= \alpha_k \gamma_k(v_k - x_k)
-            \\
-            \iff 
-            y_k - x_k &= 
-            \frac{\alpha_k \gamma_k}{\gamma_k + \alpha_k \mu}(v_k - x_k). 
-        \end{align*}
-        On the second equality that follows, we substituted $\hat\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$ given by \eqref{eqn:stepwise-wapg-eqn1}. 
-        Therefore, $x_k, v_k, y_k$ lies on the same line because \eqref{eqn:Q1} indicates $y_k - v_k$ parallels to $-(y_k - x_k)$ and both vector shares the same head which anchors at $y_k$.
+    % \begin{observation}\label{obs:stepwise-wapg}
+    %     Let's observe Definition \ref{def:stepwise-wapg} closely. 
+    %     We make two crucial observations here.     
+    % \end{observation}
 
@@
     \begin{proof}
-        The proof is direct algebra: 
+        The proof starts by showing that \eqref{eqn:Q1}, \eqref{eqn:Q2} follows from \ref{eqn:stepwise-wapg-eqn2}, then the desire results follows naturally using algebra.
+        We make the following observations from Definition \ref{def:stepwise-wapg}: 
+        \begin{align*}
+            y_k - v_k &= 
+            \frac{\hat \gamma_{k + 1}}{\alpha_k \gamma_k}(x_k - y_k), 
+            \tag{Q1}\label{eqn:Q1}
+            \\
+            y_k - x_k &= 
+            \frac{\alpha_k \gamma_k}{\gamma_k + \alpha_k \mu}(v_k - x_k). 
+            \tag{Q2}\label{eqn:Q2}
+        \end{align*}
+        It says that $x_k, y_k, v_k$ lie on the same line because \eqref{eqn:Q1} indicates $y_k - v_k$ parallels to $-(y_k - x_k)$ and both vector shares the same head which anchors at $y_k$. 
+        \par
+        To see \eqref{eqn:Q1}, we show that it's equivalent to \eqref{eqn:stepwise-wapg-eqn2} by considering: 
+        \begin{align*}
+            y_k - v_k &= 
+            \frac{\hat \gamma_{k + 1}}{\alpha_k \gamma_k}(x_k - y_k)
+            \\
+            \iff 
+            -(\alpha_k \gamma_k \hat \gamma^{-1}_{k + 1} + 1)y_k
+            &= 
+            - \alpha_k \gamma_k \hat \gamma^{-1}_{k + 1}v_k - x_k
+            \\
+            \iff 
+            y_k &= 
+            \frac{
+                \alpha_k \gamma_k \hat \gamma_{k + 1}^{-1}v_k + x_k
+            }{1 + \alpha_k \gamma_k \hat \gamma_{k + 1}^{-1}}
+            \\
+            &=  
+            \frac{\alpha_k \gamma_k v_k + \hat \gamma_{k + 1} x_k}{\gamma_k + \alpha_k \mu}.
+        \end{align*}
+        On the first equality \eqref{eqn:Q1}, we multiplied both side of the equation by $\hat\gamma_{k + 1}/\alpha_k \gamma_k$ and then grouped $y_k$. 
+        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma_{k + 1}$, then simplifies the denominator by rearranging \eqref{eqn:stepwise-wapg-eqn1} into $\hat \gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$.
+        \par
+        To see \eqref{eqn:Q2}, consider \eqref{eqn:stepwise-wapg-eqn2}: 
+        \begin{align*}
+            y_k &= (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k)
+            \\
+            \iff
+            y_k - x_k &= 
+            (\gamma_k + \alpha_k \mu)^{-1}
+            (\alpha_k \gamma_k v_k - (\gamma_k + \alpha_k \mu)x_k + \hat \gamma_{k + 1} x_k)
+            \\
+            \iff 
+            (\gamma_k + \alpha_k \mu)(y_k - x_k)
+            &= 
+            \alpha_k\gamma _kv_k + 
+            (\hat \gamma_k - \gamma_k - \alpha_k \mu) x_k
+            \\
+            &= \alpha_k \gamma_k v_k - \alpha_k \gamma_k x_k 
+            \\
+            &= \alpha_k \gamma_k(v_k - x_k)
+            \\
+            \iff 
+            y_k - x_k &= 
+            \frac{\alpha_k \gamma_k}{\gamma_k + \alpha_k \mu}(v_k - x_k). 
+        \end{align*}
+        On the second equality that follows, we substituted $\hat\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$ given by \eqref{eqn:stepwise-wapg-eqn1}. 
+        \par
+        Finally, we start by considering the LHS of \eqref{eqn:Q3} and it follows that: 
         \begin{align*}
@@
         For notation simplicity we drop the subscript $k$, $k + 1$ on $\gamma_{k}, \hat \gamma_{k + 1}$ because they are fixed throughout the proof. 
-        \par 
-        We started with $F(x_{k + 1}) + R_{k + 1} \iff \eqref{eqn:stepwise-lya-proof-eqn1}$, 
-        then $\hat \gamma/2\Vert v_{k + 1} - x^*\Vert^2 = \eqref{expr:stepwise-lya-expr2.2}$ via \eqref{eqn:stepwise-lya-proof-eqn2}. 
-        We add (\ref{eqn:stepwise-lya-proof-eqn1}), (\ref{expr:stepwise-lya-expr2.2}) to get \eqref{eqn:stepwise-lya-proof-eqn3.1}. 
-        Finally, the entire LHS of \eqref{ineq:stepwise-lya-2} equals to the RHS of \eqref{eqn:stepwise-lya-proof-eqn3.2}. 
-        Going from \eqref{eqn:stepwise-lya-proof-eqn3.2} to \eqref{ineq:stepwise-lya-proof-ineq4}, we used Theorem \ref{thm:prox-grad-ineq} which yields the desired inequality. 
+        % PROOF SUMMARIZATIONS STARTS ==================================================================================
+        \par
+        Proceeding stepwise, we show the following intermediate results: 
+        \begin{align}\tag{Step 1}\label{eqn:stepwise-lya-proof-step-1}
+            \begin{split}
+                F(x_{k + 1}) + R_{k + 1}
+                &= 
+                F(x_k) - \epsilon_k - \langle  g_k, x_k - y_k\rangle
+                - \frac{\alpha_k^2}{2\hat \gamma}\Vert g_k\Vert^2
+                \\
+                &\quad 
+                    + 
+                    (1 - \alpha_k)
+                    \left(
+                        \epsilon_k + R_k + 
+                        \frac{\mu\alpha_k\gamma}{2\hat \gamma}
+                        \Vert v_k - y_k\Vert^2
+                    \right), 
+            \end{split}
+        \end{align}
+        \begin{align}\tag{Step 2}\label{eqn:stepwise-lya-proof-step-2}
+            \begin{split}
+                \frac{\hat \gamma}{2}\Vert v_{k + 1} - x^* \Vert^2 
+                &= 
+                \left(
+                \frac{(1 - \alpha_k)\gamma + \mu \alpha_k}{2} 
+                \right)\Vert v_k - x^*\Vert^2
+                \\
+                & \quad 
+                    + 
+                    \left\langle g_k, 
+                        - \alpha_k(v_k - x^*) 
+                        - \frac{\alpha_k^2\mu}{\hat \gamma}(y_k - v_k)
+                    \right\rangle
+                \\
+                & \quad 
+                    + \frac{\alpha_k^2}{2\hat \gamma}\Vert g_k\Vert^2
+                    + \frac{\alpha_k^2 \mu^2}{2\hat \gamma}\Vert y_k - v_k\Vert^2
+                    + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle,     
+            \end{split}
+        \end{align}
+        \begin{align}\tag{Step 3}\label{eqn:stepwise-lya-proof-step-3}
+            \begin{split}
+                F(x_{k + 1}) + R_{k + 1} + 
+                \frac{\hat \gamma}{2}\Vert v_{k + 1} - x^*\Vert^2
+                &= 
+                F(x_k) - \alpha_k\left(
+                    \epsilon_k + \langle g_k, x_k - x^*\rangle
+                    - \frac{\mu}{2}\Vert y_k - x^*\Vert^2
+                \right)
+                \\
+                & \quad 
+                + 
+                (1 - \alpha_k)\left(
+                    R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
+                \right), 
+            \end{split}
+        \end{align}
+        % \par 
+        % We started with $F(x_{k + 1}) + R_{k + 1} \iff \eqref{eqn:stepwise-lya-proof-eqn1}$, 
+        % then $\hat \gamma/2\Vert v_{k + 1} - x^*\Vert^2 = \eqref{expr:stepwise-lya-expr2.2}$ via \eqref{eqn:stepwise-lya-proof-eqn2}. 
+        % We add (\ref{eqn:stepwise-lya-proof-eqn1}), (\ref{expr:stepwise-lya-expr2.2}) to get \eqref{eqn:stepwise-lya-proof-eqn3.1}. 
+        % Finally, the entire LHS of \eqref{ineq:stepwise-lya-2} equals to the RHS of \eqref{eqn:stepwise-lya-proof-eqn3.2}. 
+        % Going from \eqref{eqn:stepwise-lya-proof-eqn3.2} to \eqref{ineq:stepwise-lya-proof-ineq4}, we used Theorem \ref{thm:prox-grad-ineq} which yields the desired inequality.
+
         \par
@@
         Next, we have: 
-        \begin{align}
-        \label{eqn:stepwise-lya-proof-eqn2}
-        \begin{split}
+        \begin{align}\label{eqn:stepwise-lya-proof-eqn2}\begin{split}
             \frac{\hat \gamma}{2}\Vert v_{k + 1} - x^* \Vert^2
@@
                 \langle v_k - x^*, \mu \alpha_k(y_k - v_k) - \alpha_k g_k\rangle. 
-        \end{split}
-        \end{align}
+        \end{split}\end{align}
         On the above derivation, the first equality comes by substituting the definition of $v_{k + 1}$ given by \eqref{eqn:stepwise-wapg-eqn4}; the second equality simplifies using $\hat \gamma = (1 - \alpha_k)\gamma + \mu \alpha_k$ given by \eqref{eqn:stepwise-wapg-eqn1} and  because:
@@
             \right)
-            \\
         \end{align*}

### 2025-01-23 Notebook LaTEX/R-WAPG/paper3.tex
>w<, paper changes

@@
         \end{align*}
-        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wagp-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
+        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wapg-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
         \begin{align*}
@@
         \par
-        Our practical contribution is an algorithm inspired by a detail in the proof of Proposition \ref{prop:wagp-convergence} which is called ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}).
+        Our practical contribution is an algorithm inspired by a detail in the proof of Proposition \ref{prop:wapg-convergence} which is called ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}).
         The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ from the Bregman divergence of $f$ with minimal computational cost.
@@
         Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG in Definition \ref{def:wapg} and defines the R-WAPG sequence in Definition \ref{def:rwapg-seq}. 
-        Proposition \ref{prop:wagp-convergence} states the convergence rate of R-WAPG through Proposition \ref{prop:stepwise-lyapunov} and the R-WAPG sequence. 
+        Proposition \ref{prop:wapg-convergence} states the convergence rate of R-WAPG through Proposition \ref{prop:stepwise-lyapunov} and the R-WAPG sequence. 
         Section \ref{sec:rwapg-equiv-repr} gives three equivalent representations of the R-WAPG algorithms that are comparable to instances of APG found in the literatures. 
@@
     \end{definition}
-    % \begin{observation}\label{obs:stepwise-wapg}
-    %     Let's observe Definition \ref{def:stepwise-wapg} closely. 
-    %     We make two crucial observations here.     
-    % \end{observation}
-
+    The following lemma will simplifies the proof later on. 
     \begin{lemma}\label{lemma:ineq-q3}
@@
         % PROOF SUMMARIZATIONS STARTS ==================================================================================
-        \par
-        Proceeding stepwise, we show the following intermediate results: 
+        Proceeding stepwise, we will show the following intermediate results: 
         \begin{align}\tag{Step 1}\label{eqn:stepwise-lya-proof-step-1}
@@
                 &=                 
-                \left(
-                \frac{(1 - \alpha_k)\gamma + \mu \alpha_k}{2} 
-                \right)\Vert v_k - x^*\Vert^2
+                \frac{(1 - \alpha_k)\gamma + \mu \alpha_k}{2} \Vert v_k - x^*\Vert^2
                 \\
@@
         \end{align}
+        Simply adding both side of Equations \eqref{eqn:stepwise-lya-proof-step-1}, \eqref{eqn:stepwise-lya-proof-step-2}, it follows: 
         \begin{align}\tag{Step 3}\label{eqn:stepwise-lya-proof-step-3}
@@
         \end{align}
-        % \par 
-        % We started with $F(x_{k + 1}) + R_{k + 1} \iff \eqref{eqn:stepwise-lya-proof-eqn1}$, 
-        % then $\hat \gamma/2\Vert v_{k + 1} - x^*\Vert^2 = \eqref{expr:stepwise-lya-expr2.2}$ via \eqref{eqn:stepwise-lya-proof-eqn2}. 
-        % We add (\ref{eqn:stepwise-lya-proof-eqn1}), (\ref{expr:stepwise-lya-expr2.2}) to get \eqref{eqn:stepwise-lya-proof-eqn3.1}. 
-        % Finally, the entire LHS of \eqref{ineq:stepwise-lya-2} equals to the RHS of \eqref{eqn:stepwise-lya-proof-eqn3.2}. 
-        % Going from \eqref{eqn:stepwise-lya-proof-eqn3.2} to \eqref{ineq:stepwise-lya-proof-ineq4}, we used Theorem \ref{thm:prox-grad-ineq} which yields the desired inequality.
-
-        \par
-        Start by considering the first and the third term on LHS of \eqref{ineq:stepwise-lya-2} summed up: 
+        To show \eqref{ineq:stepwise-lya-2}, it follows by subtracting $F(x^*)$ on \eqref{eqn:stepwise-lya-proof-step-3} which gives: 
+        \begin{align}
+            \begin{split}\label{eqn:stepwise-lya-proof-eqn3.2}
+                & F(x_{k + 1}) - F(x^*) + R_{k + 1} + 
+                \frac{\hat \gamma}{2}\Vert v_{k + 1} - x^*\Vert^2
+                \\
+                &= 
+                F(x_k) - F(x^*) - \alpha_k\left(
+                    \epsilon_k + \langle g_k, x_k - x^*\rangle
+                    - \frac{\mu}{2}\Vert y_k - x^*\Vert^2
+                \right)
+                + 
+                (1 - \alpha_k)\left(
+                    R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
+                \right)
+                \\
+                &= (1 - \alpha_k)(F(x_k) - F(x^*))
+                + \alpha_k\left(
+                    F(x_k) - F(x^*) - \epsilon_k - \langle g_k, x_k - x^*\rangle + \frac{\mu}{2}\Vert y_k - x^*\Vert^2
+                \right)
+                \\ &\quad 
+                    + 
+                    (1 - \alpha_k)\left(
+                        R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
+                    \right).
+            \end{split}
+        \end{align}
+        Focusing on the second term, we simplify the multiplier inside: 
+        {\small
+        \begin{align}
+        \begin{split}\label{ineq:stepwise-lya-proof-ineq4}
+            & F(x_k) - F(x^*) - \epsilon_k - \langle g_k, x_k - x^*\rangle + \frac{\mu}{2}\Vert y_k - x^*\Vert^2
+            \\
+            &= 
+            F(x_k) - F(x^*) - \left(
+                F(x_k) - F(T_L y_k) - \langle g_k, x_k - y_k\rangle - \frac{1}{2L}\Vert g_k\Vert^2
+            \right)- \langle g_k, x_k - x^*\rangle + \frac{\mu}{2}\Vert y_k - x^*\Vert^2
+            \\
+            &= F(T_L y_k) - F(x^*) + \langle g_k, x^* - y_k\rangle + \frac{\mu}{2}\Vert y_k - x^*\Vert^2
+            + \frac{1}{2L}\Vert g_k\Vert^2 \underset{\text{Theorem }\ref{thm:prox-grad-ineq}}{\le} 0.     
+        \end{split}
+        \end{align}
+        }
+        Then, by $\alpha_k > 0$, it has:
+        {\small
+        \begin{align*}
+            F(x_{k + 1}) - F(x^*) + R_{k + 1} + 
+            \frac{\hat \gamma}{2}\Vert v_{k + 1} - x^*\Vert^2
+            &\le 
+            (1 - \alpha_k)\left(
+                F(x_k) - F(x^*) + R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
+            \right). 
+        \end{align*}
+        }
+        Now, it remains to show \eqref{eqn:stepwise-lya-proof-step-1}, \eqref{eqn:stepwise-lya-proof-step-2}, \eqref{eqn:stepwise-lya-proof-step-3}. 
+        \textbf{Proof of \eqref{eqn:stepwise-lya-proof-step-1}}:
+        Consider the first and the third term on LHS of \eqref{ineq:stepwise-lya-2} summed up: 
         \begin{align}\label{eqn:stepwise-lya-proof-eqn1}
@@
         \end{align}
-        % Coefficient of $\epsilon_k$ and $\Vert g_k\Vert^2$ are grouped. 
-        Next, we have: 
+        \textbf{Proof of \eqref{eqn:stepwise-lya-proof-step-2}}:
+        By definition of $v_{k + 1}$, it has: 
         \begin{align}\label{eqn:stepwise-lya-proof-eqn2}\begin{split}
@@
             &= 
-            \left(
-            \frac{(1 - \alpha_k)\gamma + \mu \alpha_k}{2} 
-            \right)\Vert v_k - x^*\Vert^2
+            \frac{(1 - \alpha_k)\gamma + \mu \alpha_k}{2} \Vert v_k - x^*\Vert^2
             \\ &\quad
@@
         \end{split}\end{align}
-        On the above derivation, the first equality comes by substituting the definition of $v_{k + 1}$ given by \eqref{eqn:stepwise-wapg-eqn4}; the second equality simplifies using $\hat \gamma = (1 - \alpha_k)\gamma + \mu \alpha_k$ given by \eqref{eqn:stepwise-wapg-eqn1} and  because:
+        The first equality above comes by substituting the definition of $v_{k + 1}$ given by \eqref{eqn:stepwise-wapg-eqn4}; the second equality simplifies using $\hat \gamma = (1 - \alpha_k)\gamma + \mu \alpha_k$ given by \eqref{eqn:stepwise-wapg-eqn1} and  because:
         \begin{align*}
@@
         \end{align*}
-        Focusing on the last two terms by the end of expression \eqref{eqn:stepwise-lya-proof-eqn2}, we have  
-        \begin{align}
-         \label{eqn:stepwise-lya-proof-eqn2.1}
-        \begin{split}
+        Focusing on the last two terms by the end of expression \eqref{eqn:stepwise-lya-proof-eqn2}, they can be written as: 
+        \begin{align}\label{eqn:stepwise-lya-proof-eqn2.1}\begin{split}
             \frac{\alpha^2_k}{2\hat \gamma} 
@@
         \begin{split}
-            & 
-            \left(
-            \frac{(1 - \alpha_k)\gamma + \mu \alpha_k}{2} 
-            \right)\Vert v_k - x^*\Vert^2
+            \frac{\hat \gamma}{2}\Vert v_{k + 1} - x^*\Vert^2 
+            &=
+            \frac{(1 - \alpha_k)\gamma + \mu \alpha_k}{2} \Vert v_k - x^*\Vert^2
             + 
@@
         }
-        Adding \eqref{expr:stepwise-lya-expr2.2} to \eqref{eqn:stepwise-lya-proof-eqn1} gives: 
+        \textbf{Proof for \eqref{eqn:stepwise-lya-proof-step-3}}: 
+        Adding the RHS of \eqref{expr:stepwise-lya-expr2.2}, \eqref{eqn:stepwise-lya-proof-eqn1} gives: 
         \begin{align}\label{eqn:stepwise-lya-proof-eqn3}
@@
                 + 
-                \left(
                 \frac{(1 - \alpha_k)\gamma + \mu \alpha_k}{2} 
-                \right)\Vert v_k - x^*\Vert^2
+                \Vert v_k - x^*\Vert^2
                 + 
@@
                 + 
-                \left(
-                \frac{(1 - \alpha_k)\gamma + \mu \alpha_k}{2} 
-                \right)\Vert v_k - x^*\Vert^2
+                \frac{(1 - \alpha_k)\gamma + \mu \alpha_k}{2} \Vert v_k - x^*\Vert^2
             \\
@@
                 + 
-                \left(
                 \frac{(1 - \alpha_k)\gamma + \mu \alpha_k}{2} 
-                \right)\Vert v_k - x^*\Vert^2
+                \Vert v_k - x^*\Vert^2
             \\
@@
         \end{split}
-        %\tag{3*}
         \end{align}
         On the first equality, coefficients of $\Vert g_k\Vert^2$ cancels out to zero and the inner product containing $g_k$ are grouped
-        using \eqref{eqn:Q3} derived earlier. 
+        using \eqref{eqn:Q3} from Lemma \ref{lemma:ineq-q3}. 
         The last equality re-arranged terms and grouped the coefficients of $\epsilon_k$ together. 
@@
         \end{align}
-        On the first equality, coefficients of $\Vert y_k - v_k\Vert^2$ are grouped together. 
-        On the second to the third equality, its coefficients simplified using: 
+        On the first equality, coefficients of $\Vert y_k - v_k\Vert^2$ are grouped together, on the second to the third equality, its coefficient is simplified via: 
         \begin{align*}
@@
         \end{align*}
-        We have \eqref{eqn:stepwise-lya-proof-eqn3.1} $\impliedby$ \eqref{eqn:stepwise-lya-proof-eqn1} + \eqref{expr:stepwise-lya-expr2.2}. 
-        By \eqref{eqn:stepwise-lya-proof-eqn2} $\iff$ \eqref{expr:stepwise-lya-expr2.2},
-        \eqref{eqn:stepwise-lya-proof-eqn3.1} says: 
+        We showed that \eqref{eqn:stepwise-lya-proof-eqn3.1} is the RHS of the sum \eqref{eqn:stepwise-lya-proof-step-1} + \eqref{eqn:stepwise-lya-proof-step-2}. 
+        Calling back to the LHS of the sum, it gives: 
         \begin{align*}
@@
                 R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
-            \right)
-        \end{align*}
-        Subtracting $F(x^*)$ from both side of the equation gives: 
-        \begin{align}\label{eqn:stepwise-lya-proof-eqn3.2}
-            \begin{split}
-                \\
-                & F(x_{k + 1}) - F(x^*) + R_{k + 1} + 
-                \frac{\hat \gamma}{2}\Vert v_{k + 1} - x^*\Vert^2
-                \\
-                &= 
-                F(x_k) - F(x^*) - \alpha_k\left(
-                    \epsilon_k + \langle g_k, x_k - x^*\rangle
-                    - \frac{\mu}{2}\Vert y_k - x^*\Vert^2
-                \right)
-                + 
-                (1 - \alpha_k)\left(
-                    R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
-                \right)
-                \\
-                &= (1 - \alpha_k)(F(x_k) - F(x^*))
-                + \alpha_k\left(
-                    F(x_k) - F(x^*) - \epsilon_k - \langle g_k, x_k - x^*\rangle + \frac{\mu}{2}\Vert y_k - x^*\Vert^2
-                \right)
-                \\ &\quad 
-                    + 
-                    (1 - \alpha_k)\left(
-                        R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
             \right). 
-            \end{split}
-        % \tag{3.2*}
-        \end{align}
-        Focusing on the second term, we simplify the multiplier inside: 
-        {\small
-        \begin{align}\label{ineq:stepwise-lya-proof-ineq4}
-        \begin{split}
-            & F(x_k) - F(x^*) - \epsilon_k - \langle g_k, x_k - x^*\rangle + \frac{\mu}{2}\Vert y_k - x^*\Vert^2
-            \\
-            &= 
-            F(x_k) - F(x^*) - \left(
-                F(x_k) - F(T_L y_k) - \langle g_k, x_k - y_k\rangle - \frac{1}{2L}\Vert g_k\Vert^2
-            \right)- \langle g_k, x_k - x^*\rangle + \frac{\mu}{2}\Vert y_k - x^*\Vert^2
-            \\
-            &= F(T_L y_k) - F(x^*) + \langle g_k, x^* - y_k\rangle + \frac{\mu}{2}\Vert y_k - x^*\Vert^2
-            + \frac{1}{2L}\Vert g_k\Vert^2 \underset{\text{Theorem }\ref{thm:prox-grad-ineq}}{\le} 0.     
-        \end{split}
-        \end{align}
-        }
-        % On the last line, we expand the definition of $g_k$ and then used the
-        % \hyperref[thm:prox-grad-ineq]{Theorem \ref*{thm:prox-grad-ineq}}. 
-        Therefore
-        {\small
-        \begin{align*}
-            F(x_{k + 1}) - F(x^*) + R_{k + 1} + 
-            \frac{\hat \gamma}{2}\Vert v_{k + 1} - x^*\Vert^2
-            &\le 
-            (1 - \alpha_k)\left(
-                F(x_k) - F(x^*) + R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
-            \right). 
-        \end{align*}
-        }
+        \end{align*}
+        \eqref{eqn:stepwise-lya-proof-step-3} is now justified.
+
     \end{proof}
@@
     Definition \ref{def:rwapg-seq} introduces the concept of an R-WAPG sequences: $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ which is crucial.
-    The sequences parameterize the R-WAPG algorithm stated in Definition \ref{def:wapg}, it connects the step-wise formulation of R-WAPG (Definition \ref{def:stepwise-wapg}) and can describe the convergence claim of R-WAPG in Proposition \ref{prop:wagp-convergence}.
+    The sequences parameterize the R-WAPG algorithm stated in Definition \ref{def:wapg}, it connects the step-wise formulation of R-WAPG (Definition \ref{def:stepwise-wapg}) and can describe the convergence claim of R-WAPG in Proposition \ref{prop:wapg-convergence}.
     In the next section, it continues to play a crucial role in describing several equivalent forms of the R-WAPG algorithm, and their corresponding convergence claim. 
@@
     Here is the main result of this section. 
-    \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}\; \\
+    \begin{proposition}[R-WAPG convergence claim]\label{prop:wapg-convergence}\; \\
         Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$. 
@@
     Following a similar pattern, Proposition \ref{prop:wagp-st-form}, \ref{prop:r-wapg-momentum-repr} demonstrates two more equivalent representations of the R-WAPG intermediate form (Definition \ref{def:r-wapg-intermediate}) which are formulated into Definition \ref{def:r-wapg-st-form}, \ref{def:r-wapg-momentum-form}.
-    Convergence results from Proposition \ref{prop:wagp-convergence} applies to all these equivalent forms of R-WAPG. 
+    Convergence results from Proposition \ref{prop:wapg-convergence} applies to all these equivalent forms of R-WAPG. 
     In brief, different equivalent reformulations are summarized as following: 
@@
             then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$, and for all $k\ge 1$ namely
-            \begin{align*}
-                & 
-                y_{k} = 
+            \begin{align}
+                & y_{k} = 
                 \left(
@@
                     \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
-                \right), 
+                \right), \label{eqn:rwapg-first-equiv-form-eqn-1}
                 \\
@@
                 \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
-            \end{align*}
+                \label{eqn:rwapg-first-equiv-form-eqn-2}
+            \end{align}
         \end{proposition}
         \begin{proof}
+            \textbf{We will show \eqref{eqn:rwapg-first-equiv-form-eqn-1} first.} 
             For all $k \ge 1$, by R-WAPG (Definition \ref{def:wapg}), it has: 
@@
             \end{align*}
-            From the left to right of the second equality, we used the fact that $\hat \gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k\mu$. 
+            From the left to right of the second equality, we used $\hat \gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k\mu$ which comes from \eqref{eqn:stepwise-wapg-eqn2}. 
             Going from the left to the right of the second last equality, we did the following: 
@@
             On the third $\iff$, we can assume $\alpha_k \neq \mu/L\;  \forall k \ge 1$ because from Definition \ref{def:rwapg-seq}: $\alpha_k \in (\mu/L, 1)$ for all $k \ge 1$. 
-            % On the third $\iff$, we can assume $\alpha_k \neq \mu/L\; \forall k \ge 2$ because if $\alpha_k = \mu/L$ were impossible, it then has
-            % \begin{align*}
-            %     L \alpha_k^2 - \alpha_k\mu &= 
-            %     (1 - \alpha_k)L \rho_{k - 1}\alpha_{k - 1}^2 = 0 \implies \alpha_{k - 1} = 0. 
-            % \end{align*}
-            % Which contradict $\alpha_{k - 1} \in (0, 1)\; \forall k \ge 2$ because $\alpha_1 \in (0, 1)$ is given to satisfy the condition in the base case, and $\alpha_k \in (0, 1)\; \forall k \ge 2$ by justifications in Observation \ref{obs:r-wapg-observation-1}.
-            \\
-            For all $k \ge 1$, $v_{k + 1}$ has: 
+            \par
+            \textbf{Next, we show \eqref{eqn:rwapg-first-equiv-form-eqn-2}.}
+            From the Definition \ref{def:wapg}, for all $k \ge 1$, $v_{k + 1}$ it follows that: 
             \begin{align*}
@@
             satisfy: 
-            \begin{align*}
+            \begin{align}
                 y_{k} &= 
@@
                 \right), 
+                \label{eqn:rwapg-st-form-eqn-1}
                 \\
@@
                 v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
-            \end{align*}
+                \label{eqn:rwapg-st-form-eqn-3}
+            \end{align}
         \end{proposition}
@@
             From Definition \ref{def:r-wapg-intermediate}, define $(\tau_k, \xi_k, \delta_k)_{k \ge 1}$ in Proposition \ref{prop:abs-st-form} to be
-            \begin{align*}
-                (\forall k \ge 1) \quad \tau_k &= \frac{L(1 - \alpha_k)}{L\alpha_k - \mu},
+            \begin{align}
+                (\forall k \ge 1) \quad 
+                \tau_k &= \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}, 
+                \label{eqn:rwapg-st-form-proof-tau}
                 \\
@@
                 \delta_k &\defeq \frac{1 + \xi_k}{L\alpha_k}. 
-            \end{align*}
-            Then this fits into the format of abstract similar triangle form. 
-            We claim that these parameters satisfy $L\delta_k = 1 + \tau_k + \xi_k$. 
-            To see this, we have for all $k\ge 1$: 
-            \begin{align*}
-                1 + \tau_k + \xi_k &= 
-                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
-                + \frac{\mu}{L \alpha_k - \mu}
-                \\
-                &= 
-                1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
-                \\
-                &= 
-                \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
-                \\
-                &= \frac{L}{L\alpha_k - \mu}. 
-            \end{align*}
-            Next, it also has for all $k \ge 1$: 
-            \begin{align*}
-                L\delta_k = \frac{1 + \xi_k}{\alpha_k}
-                &= 
-                \frac{1 + \frac{\mu}{L\alpha_k - \mu}}{\alpha_k}
-                = 
-                \frac{\frac{L\alpha_k - \mu + \mu}{L \alpha_k - \mu}}{\alpha_k}
-                = 
-                \frac{L}{L\alpha_k - \mu}.
-            \end{align*}
-            Hence,  $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}(x_{k + 1} - x_k)\; \forall k \ge 1$ by Proposition \ref{prop:abs-st-form}.
-            Therefore, substituting $\xi_k$ gives: 
+            \end{align}
+            Then, it fits into the format of abstract similar triangle form Proposition \ref{prop:abs-st-form} and it follows that $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}(x_{k + 1} - x_k)\; \forall k \ge 1$.
+            We shall verify the hypothesis that $L\delta_k = 1 + \tau_k + \xi_k$ later, for now substituting $\xi_k$ gives: 
             \begin{align*}
@@
             \end{align*}
+            It's easy to see that substituting $\tau_k$ as given by \eqref{eqn:rwapg-st-form-proof-tau} into $y_k = (1 + \tau_k)^{-1}(v_k + \tau_k x_k)$ as in Proposition \ref{prop:abs-st-form} produces \eqref{eqn:rwapg-st-form-eqn-1}.
+            It remains to show that $L\delta_k = 1 + \tau_k + \xi_k$. 
+            To see this, we have for all $k\ge 1$: 
+            \begin{align*}
+                1 + \tau_k + \xi_k &= 
+                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
+                + \frac{\mu}{L \alpha_k - \mu}
+                \\
+                &= 
+                1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
+                \\
+                &= 
+                \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
+                \\
+                &= \frac{L}{L\alpha_k - \mu}. 
+            \end{align*}
+            Next, it also has for all $k \ge 1$: 
+            \begin{align*}
+                L\delta_k = \frac{1 + \xi_k}{\alpha_k}
+                &= 
+                \frac{1 + \frac{\mu}{L\alpha_k - \mu}}{\alpha_k}
+                = 
+                \frac{\frac{L\alpha_k - \mu + \mu}{L \alpha_k - \mu}}{\alpha_k}
+                = 
+                \frac{L}{L\alpha_k - \mu}.
+            \end{align*}
+
         \end{proof}
@@
             Let sequence $(\alpha_k, \rho_k)_{k \ge 0}$ and iterates $(x_k, v_k, y_k)_{k\ge 1}$ given by R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}). 
-            Then for all $k \ge 1$, the iterates $(x_{k + 1}, y_{k + 1})_{k \ge 1}$ satisfy: 
+            Then it has: 
+            \begin{enumerate}
+                \item For all $k \ge 1$, the iterates $x_{k + 1}, y_{k + 1}$ satisfy:
                 \begin{align*}
@@
                 \end{align*}
-            If in addition, $v_1 = x_1$ then 
-            \begin{align*}
-                y_1 = \left(
-                    1 + \frac{L - L \alpha_1}{L\alpha_1 - \mu}
-                \right)^{-1}\left(
-                    v_1 + \left(
-                        \frac{L - L \alpha_1}{L \alpha_1 - \mu}
-                    \right)x_1
-                \right) = x_1. 
-            \end{align*}
-            If in addition $\mu = 0$, then the momentum term admits a simpler representation 
+                \item $v_1 = x_1$ if and only if $y = x_1$.  
+                \item If in addition $\mu = 0$, then the momentum term in (i) admits a simpler representation: 
                 \begin{align*}
@@
                 \end{align*}
+            \end{enumerate}
         \end{proposition}
@@
                 x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
+                \notag
                 \\
@@
                 (L \alpha_{k + 1} - \mu)x_{k + 1} + (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k).
-                \label{eqn:third-eqv-repr-eqn1} 
+                \label{eqn:third-eqv-repr-proof-step1} 
             \end{align}
-            Next, we simplify the update $y_{k}$ by Definition \ref{def:r-wapg-st-form} for all $k \ge 1$: 
-            \begin{align*}
+            The comming parts simplifies $y_k$ firstly for $k = 1$, then for all $k \ge 2$. 
+            by Definition \ref{def:r-wapg-st-form}, it follows that for all $k \ge 1$: 
+            \begin{align}\label{eqn:third-eqv-repr-proof-step2}
+                \begin{split}
                     y_k &= 
@@
                     &= (L - \mu)^{-1}((L \alpha_k - \mu)v_k + (L - L \alpha_k)x_k). 
-            \end{align*}
-            We have $y_1 = x_1$ when $v_1 = x_1$ because
-            \begin{align*}
-                y_1 &= (L - \mu)^{-1}(L(\alpha_1 - \mu)x_1 + (L - L\alpha_1)x_1)
-                \\
-                &= (L - \mu)^{-1}(L(\alpha_1 - \mu)x_1 + (L - L \alpha_1)x_1)
-                \\
-                &= (L - \mu)^{-1}((L - \mu)x_1) = x_1. 
-            \end{align*}
-            Using RHS of \eqref{eqn:third-eqv-repr-eqn1} to substitute $L\alpha_{k + 1} - \mu$ into $y_{k + 1}$, so it has for all $k\ge 1$: 
+                \end{split}
+            \end{align}
+            For all $k\ge 1$, substitute RHS of \eqref{eqn:third-eqv-repr-proof-step1} yields: 
             {\small
@@
             }
-            The coefficient for $(x_{k + 1} - x_k)$ needs some works to formulate it without the parameter $\mu, L$. 
-            To do that we have: 
+            To show (ii), we show $y_1 = x_1$ when $v_1 = x_1$. 
+            Set $k = 1$ in \eqref{eqn:third-eqv-repr-proof-step1}, it follows that: 
+            \begin{align*}
+                y_1 &= (L - \mu)^{-1}(L(\alpha_1 - \mu)x_1 + (L - L\alpha_1)x_1)
+                \\
+                &= (L - \mu)^{-1}(L(\alpha_1 - \mu)x_1 + (L - L \alpha_1)x_1)
+                \\
+                &= (L - \mu)^{-1}((L - \mu)x_1) = x_1. 
+            \end{align*}
+            Observe that, if $\mu = 0$, we can prove (iii) because:
+            \begin{align*}
+                \frac{(L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)}{L - \mu} = 
+                \frac{L\alpha_{k +1}(\alpha_k^{-1} - 1)}{L} = \alpha_{k +1}(\alpha_k^{-1} - 1). 
+            \end{align*}
+            Therefore, the special case had been justified. 
+            To prove (ii), it remains to show that the coefficient of $x_{k + 1} - x_k$ can be expressed without $\mu, L$: 
+            \begin{align*}
+                \frac{(L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)}{L - \mu}
+                &= \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}. 
+            \end{align*}
+            Consider: 
             \begin{align*}
@@
             \end{align*}
-            Going from the left to right on the fourth equality, we used $L\alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_kL\alpha_k^2 + \mu \alpha_{k + 1}$ to establish: 
+            Going from the left to right on the fourth equality, we used the property of R-WAPG sequence $L\alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_kL\alpha_k^2 + \mu \alpha_{k + 1}$ to establish: 
             \begin{align*}
@@
             \end{align*}
-            When $\mu = 0$, things simplify. 
-            Consider that $\forall k \ge 1: \alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_k\alpha_k^2$. 
-            \begin{align*}
-                \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
-                &= 
-                \frac{\rho_k\alpha_{k + 1}\alpha_k(1 - \alpha_k)}
-                {\rho_k\alpha_{k + 1}\alpha_k^2 + \alpha_{k + 1}^2}
-                \\
-                &= 
-                \frac{\rho_k\alpha_{k + 1}\alpha_k(1 - \alpha_k)}
-                {\rho_k\alpha_{k + 1}\alpha_k^2 + \rho_k(1 - \alpha_{k + 1})\alpha_k^2}
-                \\
-                &= \frac{\rho_k\alpha_{k + 1}\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2}
-                \\
-                &= \alpha_{k + 1}(\alpha_k^{-1} - 1). 
-            \end{align*}
+            % When $\mu = 0$, things simplify. 
+            % Consider that $\forall k \ge 1: \alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_k\alpha_k^2$. 
+            % \begin{align*}
+            %     \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
+            %     &= 
+            %     \frac{\rho_k\alpha_{k + 1}\alpha_k(1 - \alpha_k)}
+            %     {\rho_k\alpha_{k + 1}\alpha_k^2 + \alpha_{k + 1}^2}
+            %     \\
+            %     &= 
+            %     \frac{\rho_k\alpha_{k + 1}\alpha_k(1 - \alpha_k)}
+            %     {\rho_k\alpha_{k + 1}\alpha_k^2 + \rho_k(1 - \alpha_{k + 1})\alpha_k^2}
+            %     \\
+            %     &= \frac{\rho_k\alpha_{k + 1}\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2}
+            %     \\
+            %     &= \alpha_{k + 1}(\alpha_k^{-1} - 1). 
+            % \end{align*}
         \end{proof}
@@
     This section demonstrates that several variants of FISTA in the literatures reduces to the R-WAPG method by setting up the R-WAPG sequences with additional assumptions. 
-    This section will also demonstrate that the convergence claim (Proposition \ref{prop:wagp-convergence}) holds, and it derives convergence rates consistent with results in the literatures.  
+    This section will also demonstrate that the convergence claim (Proposition \ref{prop:wapg-convergence}) holds, and it derives convergence rates consistent with results in the literatures.  
     The table below shows the R-WAPG convergence results specialized into various settings. 
@@
                 \\
-                (Proposition \ref{prop:wagp-convergence})
+                (Proposition \ref{prop:wapg-convergence})
             \end{tabular}
@@
     \begin{proof}
-        We only need to show that $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are valid R-WAPG sequences. 
-        To do that we verify equality $\alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_k \alpha_k^2$ because it's assumed $\mu = 0$ in this case. 
+        Proceeding stepwise, we want to specialize the results of Proposition \ref{prop:wapg-convergence} for the above choice of sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$. 
+        \begin{enumerate}
+            \item $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are valid R-WAPG sequences, so we can use the convergence results. 
+            \item $\rho_k \ge 1$ so Lemma \ref{lemma:inverted-fista-seq} (iii) applies. 
+            \item Simplifies the conclusion of Proposition \ref{prop:wapg-convergence} by the previous two items. 
+        \end{enumerate}
+        To show (i), we verify equality $\alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_k \alpha_k^2$ because it's assumed $\mu = 0$ in this case. 
         For all $k \ge 0$, the right side of the equality evaluates to 
@@
         \par
-        Next, we show the convergence rate of the algorithm. 
+        Next, we show (ii). 
         Observe that $(\forall k \ge 0)(\forall a \ge 2)$, $\rho_k$ has 
@@
         Hence, (iii) in Lemma \ref{lemma:inverted-fista-seq} applies. 
-        By Proposition \ref{prop:wagp-convergence}, we have:
+        By Proposition \ref{prop:wapg-convergence}, we have:
         {\small\begin{align*}
@@
         The constant sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid R-WAPG sequence by Lemma \ref{lemma:constant-rwapg-seq}. 
-        The algorithm presented here is the same as the R-WAPG momentum form because the term $\theta$ from Lemma \ref{lemma:constant-rwapg-seq} matches up with Definition \ref{def:r-wapg-momentum-form}.
-        Therefore, by Proposition \ref{prop:wagp-convergence} we have: 
+        The algorithm presented here is the same as the R-WAPG momentum form as given by Definition \ref{def:r-wapg-momentum-form} because the term $\theta$ from Lemma \ref{lemma:constant-rwapg-seq} matches up with Definition \ref{def:r-wapg-momentum-form} by (ii) in Lemma \ref{lemma:constant-rwapg-seq}.
+        Then, Proposition \ref{prop:wapg-convergence} applies and it follows that: 
         \begin{align*}
@@
         \end{align*}
-        The equivalency between the momentum representation of R-WAPG (Definition \ref{def:r-wapg-momentum-form}) and the similar triangle representation (Definition \ref{def:r-wapg-st-form}) allows us to write $v_{k + 1} = x_{k + 1} + (\alpha^{-1} - 1)(x_{k + 1} - x_k)$.
-        By the initialization condition $v_1 = x_1$ specified in Proposition \ref{prop:r-wapg-momentum-repr}, we can write $v_1$ as $x_1$. 
+        Going from the second last to the last equality, we used the initialization condition $y_1 = x_1$ specified in Proposition \ref{prop:r-wapg-momentum-repr}, therefore it has $v_1 = x_1$. 
     \end{proof}
@@
     \par 
-    From a theoretical perspective, the convergence result (Proposition \ref{prop:wagp-convergence}) of R-WAPG is relevant to some degree because the sequence $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg} is an R-WAPG sequence.
+    From a theoretical perspective, the convergence result (Proposition \ref{prop:wapg-convergence}) of R-WAPG is relevant to some degree because the sequence $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg} is an R-WAPG sequence.
     Let $\tilde \mu_k$ be an estimate produced by the algorithm then it satisfies that $\tilde \mu_k/ L \in (0, 1)$.
@@
 \section{Discussion}
-    This paper provides the results of an upper bound (Proposition \ref{prop:wagp-convergence}) on the optimality gap $F(x_k) - F^*$ for smooth plus nonsmooth composite optimization problem with convex objectives where under the much weaker assumption for the momentum parameter specified by Definition \ref{def:rwapg-seq}.
+    This paper provides the results of an upper bound (Proposition \ref{prop:wapg-convergence}) on the optimality gap $F(x_k) - F^*$ for smooth plus nonsmooth composite optimization problem with convex objectives where under the much weaker assumption for the momentum parameter specified by Definition \ref{def:rwapg-seq}.
     The proposed R-WAPG unifies the convergence proof for major Euclidean variants of FISTA with strong convexity parameter $\mu \ge 0$. 

### 2025-01-23 Notebook LaTEX/R-WAPG/paper3.tex
>w<, fixes

@@
     \end{definition}
-    The following lemma will simplifies the proof later on. 
+    The following lemma will simplify the discussion later. 
     \begin{lemma}\label{lemma:ineq-q3}
@@
     \begin{proof}
-        We prove by induction. 
         For notation simplicity we drop the subscript $k$, $k + 1$ on $\gamma_{k}, \hat \gamma_{k + 1}$ because they are fixed throughout the proof. 
@@
     \begin{proof}  
-        The proof is by induction. 
+        We prove by induction. 
         Let's first consider $k = 1$, $\hat \gamma_2 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$, $R_1 = 0$. 
@@
             Therefore, the special case had been justified. 
-            To prove (ii), it remains to show that the coefficient of $x_{k + 1} - x_k$ can be expressed without $\mu, L$: 
+            To prove (ii), it remains to show that for all $k\ge 1$ the coefficient of $x_{k + 1} - x_k$ can be expressed without $\mu, L$: 
             \begin{align*}

### 2025-01-23 Latex Templates/Scientific/main.tex
>w< wdkstp
wdktp
>w< wdsktp
>w<, changes
>w<, latex changes on formatting

@@
 % \input{presets/wang_full.tex}
+\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{true}
 \input{presets/wang/input.tex}
@@
 \maketitle
-
+\todoinline{This paper is currently in draft mode. Check source to change options. }
 % \vskip 8mm
@@
 Mel dolorem menandri in.
+    \todo{This is just psuedo text. }
 \end{abstract}
@@
 % ==============================================================================
-\input{sections/demo_notations.tex}
-\input{sections/demo_code.tex}
-
-% ==============================================================================
 
@@
         Define
-        \begin{equation}
+        \begin{equation}\label{eqn:cone-1}
             Q = \left\lbrace
@@
     \end{proof}
+
 \section{Lorentz Cone and its Polar}
@@
 
+\section{Testing the references}
+    This book by Nesterov \cite{nesterov_lectures_2018}. 
+    This book by Heinz \cite{bauschke_convex_2017}.
+
+\section{Testing figures and images}
+    In Figure \ref{fig:two-test-figures}, it has Figure \ref{fig:two-test-fig-1} on the left and Figure \ref{fig:two-test-fig-2} on the right. 
+    \begin{figure}[H]
+        \begin{subfigure}[b]{0.47\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{assets/test-image-1.png}
+            \caption{Alto the unicorn. }
+            \label{fig:two-test-fig-1}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.47\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{assets/test-image-2.png}
+            \caption{Alto and Minty. }
+            \label{fig:two-test-fig-2}
+        \end{subfigure}
+        \caption{The above 2 images are test images for the figure, subfigure latex commands. }
+    \label{fig:two-test-figures}
+    \end{figure}
+
 \section*{Acknowledgments}
@@
 
-\begin{thebibliography}{999}
+\bibliographystyle{siam}
 
-    \bibitem{BC2017}
-    H.H.\ Bauschke and P.L.\ Combettes,
-    \emph{Convex Analysis and Monotone Operator Theory in Hilbert Spaces},
-    second edition,
-    Springer, 2017.
-
-    \bibitem{cross}
-    H.~H.\ Bauschke, M.\ Krishan Lal, and X.\ Wang, The projection onto the cross, (2021), \url{https://arxiv.org/abs/2108.04382}.
-
-    \bibitem{Bertsekas}
-    D.P.\ Bertsekas,
-    \emph{Nonlinear Programming}, third edition, Athena Scientific, Belmont, Massachusetts, USA, 2016.
-
-    \bibitem{burden2011analisis}
-    R. L.\ Burden and J.D. \ Faires, \emph{Numerical Analysis}, 9th edition, 2011.
-    \bibitem{quadrics} N.\ Chernov and H.\ Ma, Least squares fitting of quadratic curves and surfaces, \emph{Computer Vision} 285, p302, 2011.
-
-    \bibitem{conics} N.\ Chernov and S.\ Wijewickrema,  Algorithms for projecting points onto conics, \emph{ Journal of Computational and Applied Mathematics}, 251, (2013), 8-21.
-
-    \bibitem{robust} D.\ Eberly, \emph{Robust and Error-free Geometric Computing}, CRC Press, 2021.
-
-    \bibitem{elser2019learning} V.\ Elser, Learning without loss,
-    \emph{Fixed Point Theory and Algorithms for Sciences and Engineering} 2021, article~12 (2021).
-    \url{https://doi.org/10.1186/s13663-021-00697-1}
-
-    \bibitem{elser2017products}
-    V.\ Elser, Matrix product constraints by projection methods, \emph{Journal of Global Optimization} 68, no 2, (2017), 329-355.
-
-    \bibitem{PW16}
-    Planiden C , Wang X . Strongly Convex Functions, Moreau Envelopes, and the Generic Nature of Convex Functions with Strong Minimizers[J]. \emph{SIAM Journal on Optimization}, 2015, 26(2):1341-1364.
-
-    \bibitem{kreyszig} E.\ Kreyszig, \emph{Introductory Functional Analysis with Applications},
-    John Wiley \& Sons, Inc., New York, 1989.
-
-    \bibitem{Luenberger}
-    D.G.\ Luenberger,
-    \emph{Optimization by Vector Space Methods},
-    Wiley, 1969.
-
-    \bibitem{Luke2020}
-    D.~R. Luke. and A.L. Martins, Convergence Analysis of the Relaxed Douglas--Rachford Algorithm. \newblock {\em SIAM Journal on Optimization}, 30(1), (2020), pp.542-584.
-
-    \bibitem{Rock98}
-    R.\ T.\ Rockafellar and R.\ J-B Wets,
-    \emph{Variational Analysis},
-    Springer-Verlag, New York, 1998.
-
-\end{thebibliography}
+\bibliography{references/Books.bib}
 

### 2025-01-24 Notebook LaTEX/Proposal/presentation.tex
>w<, changes
>w<, fixes

@@
 \documentclass[11pt]{beamer}
+
 \usetheme{Madrid}
 \usepackage[utf8]{inputenc}
-
 \usepackage{hyperref}
@@
 \usepackage{graphicx}
-\DeclareMathOperator{\argmin}{argmin}
 \usepackage{algorithmic}
@@
 \graphicspath{{.}}
+\input{presets/wang/custom_commands.tex}
 
-\author{Generic Name}
-\title{Title for Super Fancy Stuff}
-% Informe o seu email de contato no comando a seguir
-% Por exemplo, alcebiades.col@ufes.br
+\author{Hongda Li}
+\title[Thesis Proposal Talk]{First Order Nonsmooth Optimization: Catalyst Acceleration and Unifying Nesterov's Acceleration}
 \newcommand{\email}{lalala@lala.la}
@@
 %\logo{}
-\institute[]{Some Super Fancy Institution}
+\institute[UBCO]{
+    University of British Columbia Okanagan
+}
 \date{\today}
-\subject{Subject Title }
+\subject{Nesterov's acceleration and its applications}
 
@@
 \end{frame}
-
+\begin{frame}{Overview}
+    This talks will be based on the content of our draft paper and selected content of the Catalyst Meta Acceleration Framework. 
+    Our preprint: 
+    \begin{enumerate}
+        \item X. Wang and H. Li, \textit{A Parameter Free Accelerated Proximal Gradient Method Without Restarting}, preprint, (2025).
+    \end{enumerate}
+    Catalyst Meta Acceleration:  
+    \begin{enumerate}
+        \item H. Lin, J. Mairal and Z. Harchaoui, \textit{A universal catalyst for first-order optimization}, in NISP, vol. 28, (2015). 
+        \item \underline{\hspace{4em}}, \textit{Catalyst acceleration for first-order convex optimization: from theory to practice}, JMLR, 18 (2018), pp. 1–54.
+    \end{enumerate}
+\end{frame}
 \begin{frame}{ToC}
@@
 
-% \section{This is the First Section}
-%     \subsection{Taxonomy of Proximal type of Methods}
-%         \begin{frame}{Frame Title}
+\section{Introduction}
+    \subsection{Notations and preliminaries}
+        \begin{frame}{Notations and preliminaries}
+            Throughout this talk, let $\RR^n$ be the ambient space equiped with Euclidean inner product and norm. 
+            We consider 
+            \begin{align}\label{eqn:additive-comp-obj}
+                \min_{x \in \RR^n} \left\lbrace
+                    F(x):= f(x) + g(x)
+                \right\rbrace.
+            \end{align}
+            Unless specified, assume: 
+            \begin{enumerate}
+                \item $f:\RR^n \rightarrow \RR$ is $L$-Lipscthiz smooth $\mu \ge 0$ strongly convex, 
+                \item $g:\RR^n \rightarrow \overline \RR$ is closed convex proper. 
+            \end{enumerate}
+        \end{frame}
+        \begin{frame}{Our works on R-WAPG}
 
-%             \begin{block}{Formula Presented in Block}
-%                 \begin{align}
-%                     \min_{x} g(x) + h(x)
-%                 \end{align}    
-%             \end{block}
+        \end{frame}
+        \begin{frame}{Introduction to Catalyst Acceleration}
 
-%             \begin{itemize}
-%                 \item [1.]Throughout this presentation, we assume the objective of a function $f$ is the sum of 2 functions.
-%                 \item [2.]We are interested in the paper: FISTA (Fast Iterative-Shrinkage Algorithm) by Beck and Teboulle \cite{paper:FISTA}. 
-%                 \pause 
-%                 \item [1.] When $h = \delta_Q$ with $Q$ closed and convex with $Q\subseteq \text{ri}\circ \text{dom}(g)$, we use projected subgradient. 
-%                 \item [2.] When $g$ is \textbf{\emph{strongly smooth}} and $h$ is \textbf{closed convex proper} whose proximal oracle is easy to compute, we consider the use of FISTA. 
-%             \end{itemize}
+        \end{frame}
+\section{Content of the draft paper}
 
-%         \end{frame}
+    \subsection{Direction of future works}
 
-%     \subsection{The Proximal Operator}
-%         \begin{frame}{Frame Title}
-%             \begin{definition}[Definition of Something]
-%                 Let $f$ be convex closed and proper, then the proximal operator parameterized by $\alpha > 0$ is a non-expansive mapping defined as: 
-%                 \begin{align*}
-%                     \text{prox}_{f, \alpha}(x) := 
-%                     \arg\min_{y}\left\lbrace
-%                         f(y) + \frac{1}{2\alpha} \Vert y - x\Vert^2
-%                     \right\rbrace. 
-%                 \end{align*}
-%             \end{definition}  
-%             \begin{remark}
-%                 When $f$ is convex, closed, and proper, 
-%             \end{remark}
-%         \end{frame}
-
-%         \begin{frame}{Prox is the Resolvant of Subgradient}
-%             \begin{lemma}[The Lemma]\label{lemma:prox_alternative_form}
-%                 When the function $f$ is convex closed and proper, the $\text{prox}_{\alpha, f}$ can be viewed as the following operator $(I + \alpha \partial f)^{-1}$. 
-%             \end{lemma}
-%             \begin{proof}
-%                 Minimizer satisfies zero subgradient condition, 
-%                 {\scriptsize
-%                 \begin{align*}
-%                     \mathbf 0 &\in \partial
-%                     \left[
-%                         \left.
-%                             f(y) + \frac{1}{2\alpha} \Vert y - x\Vert^2 
-%                         \right| y
-%                     \right](y^+)
-%                     \\
-%                     \mathbf 0 &\in \partial f(y^+) + \frac{1}{\alpha}(y^+ - x)
-%                     \\
-%                     \frac{x}{\alpha} &\in 
-%                     (\partial f + \alpha^{-1}I)(y^+)
-%                     \\
-%                     x &\in 
-%                     (\alpha \partial f + I)(y^+)
-%                     \\
-%                     y &\in (\alpha\partial f+ I)^{-1}(x).
-%                 \end{align*}
-%                 }
-%             \end{proof}
-%         \end{frame}
-
-%     \subsection{Strong Smoothness}
-%         \begin{frame}{Equivalence of Strong Smoothness and Lipschitz Gradient}
-%             \begin{theorem}[Lipschitz Gradient Equivalence under Convexity]
-%                 Suppose $g$ is differentiable on the entire of $\mathbb E$.
-It is closed convex proper.
-It is strongly smooth with parameter $\alpha$ if and only if the gradient $\nabla g$ is globally Lipschitz continuous with a parameter of $\alpha$ and $g$ is closed and convex.
-%                 \begin{align*}
-%                     \Vert \nabla g(x) -\nabla g(y)\Vert \le 
-%                     \alpha 
-%                     \Vert x - y \Vert\quad \forall x, y\in \mathbb E
-%                 \end{align*}
-%             \end{theorem}
-%             \begin{proof}
-%                 Using line integral, we can prove Lipschitz gradient implies strong smoothness without convexity.
-The converse requires convexity and applying generalized Cauchy Inequality to (iv) in Theorem 5.8 for Beck's textbook \cite{book:first_order_opt}.
-%             \end{proof}
-
-%         \end{frame}
-%     \subsection{A Major Assumption}    
-%         \begin{frame}{A Major Assumption}
-%             \begin{assumption}[Convex Smooth Nonsmooth with Bounded Minimizers]\label{assumption:1}
-%                 We will assume that $g:\mathbb E\mapsto \mathbb R$ is \textbf{strongly smooth} with constant $L_g$ and $h:\mathbb E \mapsto \bar{\mathbb R}$ \textbf{is closed convex and proper}.
-We define $f := g + h$ to be the summed function and $\text{ri}\circ \text{dom}(g) \cap \text{ri}\circ \text{dom}(h) \neq \emptyset$.
-We also assume that a set of minimizers exists for the function $f$ and that the set is bounded.
-Denote the minimizer using $\bar x$.
-%             \end{assumption}
-%         \end{frame}
-
-% \section{A New Fancy Section}
-%     \subsection{A Fancy Subsetction for Algorithm}
-%         \begin{frame}{The Accelerated Proximal Gradient Method}
-%             \begin{block}{Momentum Template Method}
-%                 \begin{algorithm}[H]
-%                     \begin{algorithmic}[1]
-%                         \STATE{\textbf{Input:} $x^{(0)}, x^{(-1)}, L, h, g$; 2 initial guesses and stepsize L}
-%                         \STATE{$y^{(0)} = x^{(0)} + \theta_k (x^{(0)} - x^{(-1)})$}
-%                         \FOR{$k = 1, \cdots, N$}
-%                             \STATE{$x^{(k)} = \text{prox}_{h, L^{-1}}(y^{(k)} + L^{-1}\nabla g(y^{(k)})) =: \mathcal P_{L^{-1}}^{g, h}(y^{(k)})$}
-%                             \STATE{$y^{(k + 1)} = x^{(k)} + \theta_k(x^{(k)} - x^{(k - 1)})$}
-%                         \ENDFOR
-%                     \end{algorithmic}
-%                     \caption{Template Proximal Gradient Method With Momentum}\label{alg:fista_template}
-%                 \end{algorithm}
-%             \end{block}
-%         \end{frame}
-
-% \section{Numerical Experiments}
-%     \input{Sections/sectionfile.tex}
+\section{Selected contents from Catalyst Meta Accelerations}
+    \subsection{Direction of future works}
 
 \section{References}
-    \begin{frame}{References}
-
+    \begin{frame}{Citation examples}
+        Citation examples \cite{chambolle_convergence_2015}
+    \end{frame}
+    \begin{frame}[allowframebreaks]{References}
+        % \bibliographystyle{apalike}
         \bibliography{references/proposal.bib}

### 2025-01-24 Notebook LaTEX/Proposal/proposal.tex
>w<, changes

@@
 \documentclass[12pt]{article}
+
+\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{true}
 \input{presets/wang/input.tex}
@@
     Let $\RR^n$ be the ambient space. We consider 
-    \begin{align}
+    \begin{align}\label{eqn:additive-comp-obj}
         \min_{x \in \RR^n} \left\lbrace
@@
         \right\rbrace.
-    \end{align}\label{eqn:additive-comp-obj}
-    Unless specified, assume $f:\RR^n \rightarrow \RR$ is $L$-Lipscthiz smooth $\mu \ge 0$ strongly convex and $g:\RR^n \rightarrow \overline \RR$ is convex. 
+    \end{align}
+    Unless specified, assume $f:\RR^n \rightarrow \RR$ is $L$-Lipscthiz smooth $\mu \ge 0$ strongly convex and $g:\RR^n \rightarrow \overline \RR$ is closed convex and proper. 
     This type of problem is referred to as additive composite problems in the literature. 
@@
     Throughout, we adopt the notation $\overline \RR := \RR \cup \{\infty, -\infty\}$.
+
     \subsection{Fundamentals in non-convex analysis}
@@
         \end{definition}
+
     \subsection{Fundamentals in convex analysis}
@@
             \end{lemma}
-            \begin{remark}
-                This lemma is proved in our draft paper. 
-            \end{remark}
+            The proof of the lemma appeals to Lemma \ref{lemma:q-growth} with the $L + \mu$ strong convexity of $\widetilde {\mathcal M}^{\beta^{-1}}_F(\cdot; y)$.
 
@@
         The proposition follows provides upper bound to $F(x_{k + 1})$ in relations to $F(x_{k})$. 
-        \begin{definition}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
+        \begin{definition}[Stepwise weak accelerated proximal gradient]\;\label{def:stepwise-wapg}\\
             Assume $0 \le \mu < L$.
@@
         \end{definition}
-        \begin{proposition}[Stepwise Lyapunov]\label{prop:stepwise-lyapunov}\;\\
+        \begin{proposition}[Stepwise Lyapunov]\;\label{prop:stepwise-lyapunov} \\
             Let $k \in \mathbb Z_+$, $R_k \in \RR$. 
@@
         \end{proposition}
+        The proof of the above proposition made extensive use of definition of $R_{k + 1}$, and it appeals to Theorem \ref{thm:prox-grad-ineq}.
 
@@
     \end{remark}
-    \textbf{Organizations now follow}. 
+    \textbf{The remainder of the proposal is organized as the follow}. 
     Section \ref{ssec:catalyst-intro} gives the main ideas behind the Catalyst Acceleration Framework. 

### 2025-01-24 Notebook LaTEX/R-WAPG/paper3.tex
>w<, latex changes on formatting
>w<, changes

@@
 % \input{presets/wang_full.tex}
+
+\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{true}
 \input{presets/wang/input.tex}
@@
             & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
-        \end{align}\label{eqn:example_algorithm}
+        \end{align}\label{eqn:example-algorithm}
         If the minimizer $x^*$ exists, then the optimality gap $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, a faster rate compared to gradient descent which is $\mathcal O(1/k)$. 
@@
         \par
-        We relax the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example_algorithm} and showed an upper bound of the optimal gap. 
+        We relax the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example-algorithm} and showed an upper bound of the optimal gap. 
         Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
@@
         g(x) + f(y) + \langle \nabla f(y), x - y\rangle 
-        + \frac{L}{2}\Vert x - y\Vert^2,  \label{eqn:pg_model-func}
+        + \frac{L}{2}\Vert x - y\Vert^2,  \label{eqn:pg-model-func}
         \\
         \mathcal M^{L^{-1}}(x; y) &:= F(x) + \frac{L}{2}\Vert x - y\Vert^2. 
-        \label{eqn:pp_model-func}
+        \label{eqn:pp-model-func}
     \end{align}
@@
     \begin{lemma}[Proximal gradient envelope]\label{lemma:pg-envelope}
-        With $\mathcal M^{L^{-1}}, \widetilde{\mathcal M}^{L^{-1}}$ as given by \eqref{eqn:pg_model-func}, \eqref{eqn:pp_model-func}, 
+        With $\mathcal M^{L^{-1}}, \widetilde{\mathcal M}^{L^{-1}}$ as given by \eqref{eqn:pg-model-func}, \eqref{eqn:pp-model-func}, 
         we have for all $x \in \RR^n$, $y \in \RR^n$:
@@
     \begin{proof}
-        Proceeding stepwise, we want to specialize the results of Proposition \ref{prop:wapg-convergence} for the above choice of sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$. 
+        Proceeding stepwise, we want to specialize the results of Proposition \ref{prop:wapg-convergence} for the above choice of sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$  by completing the following steps.
         \begin{enumerate}
-            \item $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are valid R-WAPG sequences, so we can use the convergence results. 
-            \item $\rho_k \ge 1$ so Lemma \ref{lemma:inverted-fista-seq} (iii) applies. 
-            \item Simplifies the conclusion of Proposition \ref{prop:wapg-convergence} by the previous two items. 
+            \item Show that the $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given are valid R-WAPG sequences, so we can use the convergence results. 
+            \item Show $\rho_k \ge 1$ so Lemma \ref{lemma:inverted-fista-seq} (iii) applies. 
+            \item Simplify the conclusion of Proposition \ref{prop:wapg-convergence} by the previous two items. 
         \end{enumerate}

### 2025-01-24 Notebook LaTEX/Proposal/presentation.tex
>w<, changes

@@
 \begin{frame}{Overview}
-    This talks will be based on the content of our draft paper and selected content of the Catalyst Meta Acceleration Framework. 
+    This talk will be based on the content of our draft paper and selected content of the Catalyst Meta Acceleration Framework. 
     Our preprint: 
@@
         \end{frame}
+        \begin{frame}{Notations and preliminaries}
+            \begin{definition}[Proximal gradient operator]\label{def:proximal-gradient-operator}
+                Define the proximal gradient operator $T_L$ on all $y \in \RR^n$: 
+                \begin{align*}
+                    T_L y := \argmin_{x \in \RR^n} \left\lbrace
+                        g(x) + f(y) + \langle \nabla f(y), x - y\rangle 
+                        + \frac{L}{2}\Vert x- y \Vert^2
+                    \right\rbrace. 
+                \end{align*}
+            \end{definition}
+            \begin{definition}[Gradient mapping operator]\label{def:gradient-mapping-operator}
+                % Take $F := f + g$ as defined in this section. 
+                Define the gradient mapping operator $\mathcal G_L$ on all $y \in \RR^n$: 
+                \begin{align*}
+                    \mathcal G_L (y):= L(y - T_L y). 
+                \end{align*}
+            \end{definition}
+        \end{frame}
+        \begin{frame}{Proximal gradient inequality}
+            \begin{lemma}[The proximal gradient inequality]\label{thm:prox-grad-ineq}
+                % Take $F:= f + g$ as defined in this section. 
+                For all $y \in \RR^n$, $x \in \RR^n$, it has: 
+                {\scriptsize
+                \begin{align*}
+                    (\forall x \in \RR^n)\quad 
+                    F(x)  - F(T_Ly) - \langle L(y - T_Ly), x - y\rangle
+                    - \frac{\mu}{2}\Vert x - y\Vert^2 - \frac{L}{2}\Vert y - T_Ly\Vert^2 
+                    &\ge 0. 
+                \end{align*}
+                }
+            \end{lemma}
+            This lemma is crucial to developing results in our current draft paper. 
+        \end{frame}
+        \begin{frame}{Nesterov's estimating sequence example}
+            \begin{definition}[Nesterov's estimating sequence]\label{def:nes-est-seq}
+                For all $k \ge 0$, let $\phi_k : \RR^n \rightarrow\RR$ be a sequence of functions. 
+                We call this sequence of functions a Nesterov's estimating sequence when it satisfies conditions: 
+                \begin{enumerate}
+                    \item There exists another sequence $(x_k)_{k \ge 0}$ such that for all $k \ge 0$ it has $F(x_k) \le \phi_k^*: =\min_{x}\phi_k(x)$. 
+                    \item There exists a sequence of $(\alpha_k)_{k \ge 0}$ where $\alpha_k \in (0, 1)\; \forall k \ge0 $ such that for all $x \in \RR^n$ it has $\phi_{k + 1}(x) - \phi_k(x) \le - \alpha_k(\phi_k(x) - F(x))$.
+                \end{enumerate}
+            \end{definition}
+            The technique is widespread in the literatures and it's used to derive the convergence rate of acceleration on first order method, and the numerical algorithm itself.
+It is a two birds one stone technique.
+        \end{frame}
         \begin{frame}{Our works on R-WAPG}
-
+            Here are contributions of our draft paper. 
+            Recall the Nesterov's acceleration has momentum extrapolation updates on $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$. 
+            We proposed the idea of R-WAPG, a generic method that: 
+            \begin{enumerate}
+                \item Describe for momentum sequences that doesn't follow Nesterov's rules.
+                \item Unifies the convergence rate analysis for several Euclidean variants of the FISTA method. 
+                \item A parameter free numerical algorithm: ``Free R-WAPG'' method that has competitive numerical performance in practical settings without restarting. 
+            \end{enumerate}
+            Our work is inspired by considering Nesterov's estimating sequence where $F(x_k) + R_k = \phi_k^*$. 
         \end{frame}

### 2025-01-25 Notebook LaTEX/Proposal/presentation.tex
>w<, changes

@@
 \documentclass[11pt]{beamer}
-
-\usetheme{Madrid}
+% PACKAGES =====================================================================
 \usepackage[utf8]{inputenc}
@@
 \usepackage{subcaption}
+\usepackage{tcolorbox}
+
+% THEMES AND BEAMER SETTINGS ===================================================
+% \usetheme{Madrid}
 \graphicspath{{.}}
-\input{presets/wang/custom_commands.tex}
+\input{presets/wang/custom_commands.tex} % IMPORT WANG'S LATEX CUSTOM COMMANDS. 
+\setbeamertemplate{theorems}[numbered] % ADD NUMBERING TO ALL AMS THEOREMS. 
+\setbeamertemplate{footline}[frame number] % ADD PAGE NUMBERS ON BOTTOM. 
+% \setbeamercovered{transparent}  % GREY OUT PAUSED FUTURE ITEMS IN SLID. 
+\setbeamertemplate{navigation symbols}{}
 
+% SLIDE INFORMATION ============================================================
 \author{Hongda Li}
 \title[Thesis Proposal Talk]{First Order Nonsmooth Optimization: Catalyst Acceleration and Unifying Nesterov's Acceleration}
-\newcommand{\email}{lalala@lala.la}
-\setbeamercovered{transparent}
-\setbeamertemplate{navigation symbols}{}
-%\logo{}
+% \newcommand{\email}{lalala@lala.la}
 \institute[UBCO]{
@@
 
-% ---------------------------------------------------------
-% Selecione um estilo de referência
-\bibliographystyle{IEEEtran}
+% SLIDES ELEMENTS CUSTOMIZATIONS ===============================================
+\theoremstyle{definition}
+\newtheorem{remark}{Remark}[section]
+\newtheorem{assumption}{Assumption}[section]
+\newtheorem{proposition}{Proposition}[section]
+\bibliographystyle{siam}
 
-%\bibliographystyle{abbrv}
-%\setbeamertemplate{bibliography item}{\insertbiblabel}
-% ---------------------------------------------------------
-
-% ---------------------------------------------------------
-\newtheorem{remark}{Remark}
-\newtheorem{assumption}{Assumption}
-
+% DOCUMENTS STARTS =============================================================
 \begin{document}
-
 \begin{frame}
@@
                 \begin{align*}
-                    (\forall x \in \RR^n)\quad 
                     F(x)  - F(T_Ly) - \langle L(y - T_Ly), x - y\rangle
@@
         \begin{frame}{Our works on R-WAPG}
-            Here are contributions of our draft paper. 
+            Here are the contributions of our draft paper. 
             Recall the Nesterov's acceleration has momentum extrapolation updates on $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$. 
@@
         \end{frame}
-        \begin{frame}{Introduction to Catalyst Acceleration}
+        \begin{frame}{Introducing Catalyst Part I}
+            \begin{block}{Introducing Catalyst}
+                Let $F:\RR \rightarrow \overline \RR$ be $\mu \ge 0$ strongly convex and closed. 
+                Let the initial estimate be $x_0 \in \RR^n$, fix parameters $\kappa > 0$ and $\alpha_0 \in (0, 1]$. 
+                {\small 
+                \begin{tcolorbox}
+                    Initialize $x_0 = y_0$. Then the algorithm generates $(x_k, y_k)_{k\ge 0}$ for all $k \ge 1$ such that: 
+                    \begin{align*}
+                        & \text{find } x_k \approx \argmin_{x \in \RR^n} \left\lbrace F(x) + (\kappa/2)\Vert x - y_{k - 1}\Vert^2\right\rbrace, 
+                        \\
+                        & \text{find } \alpha_k \in (0, 1) \text{ such that } \alpha_k^2 = (1 - \alpha_k)\alpha_{k - 1}^2 + (\mu/(\mu + \kappa))\alpha_k,
+                        \\
+                        & 
+                        y_{k} = x_k + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})}{\alpha_{k - 1}^2 + \alpha_k}(x_k - x_{k - 1}). 
+                    \end{align*}
+                \end{tcolorbox}
+                }
+            \end{block}
+            We will return to this in the later slides. 
+        \end{frame}
+        \begin{frame}{Introducing Catalyst Part II}
+            Catalyst by Lin, et al. \cite{lin_catalyst_2018, lin_universal_2015} has the theoretical and pratical importance: 
+            \begin{enumerate}
+                \item It's an early attempt at putting accelerated inexact proximal point method into a practical settings. 
+                \item It finds application in machine learning and it accelerates the convergence of Varianced Reduced Method (A type of incremental method that is not slower than the exact counter part).
+                \item It demonstrates crucial ideas on how prove convergence rate where the evaluation of proximal point method is inexact in the convex settings. 
+            \end{enumerate}
+        \end{frame}
+
+\section{Content of the draft paper}
+    \subsection{The method of R-WAPG and its convergence}
+        \begin{frame}{R-WAPG sequences}
+            \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}
+                Assume $0 \le \mu < L$. 
+                The sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are valid for R-WAPG if all the following holds: 
+                \begin{align*}
+                    \alpha_0 &\in (0, 1], 
+                    \\
+                    \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
+                    \\
+                    \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
+                \end{align*}
+                We call $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ the \textbf{R-WAPG Sequences}. 
+            \end{definition}
+        \end{frame}
+        \begin{frame}{The method of R-WAPG}
+            \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
+                Choose any $x_1 \in \RR^n, v_1 \in \RR^n$. 
+                Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}. 
+                The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for $k\ge 1$ by the procedures:  
+                \begin{tcolorbox}
+                    For $k=1, 2, 3, \ldots$
+                    \begin{align*}
+                        \gamma_k &:= \rho_{k -1}L\alpha_{k - 1}^2, 
+                        \\
+                        \hat \gamma_{k + 1} & := (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2, 
+                        \\
+                        y_k &= 
+                        (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
+                        \\
+                        g_k &= \mathcal G_L y_k, 
+                        \\
+                        v_{k + 1} &= 
+                        \hat\gamma^{-1}_{k + 1}
+                        (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
+                        \\
+                        x_{k + 1} &= T_L y_k. 
+                    \end{align*}    
+                \end{tcolorbox}
+            \end{definition}
+        \end{frame}
+        \begin{frame}{Convergence of R-WAPG}
+            The convergence claim of the method follows. 
+            \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}
+                Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$. 
+                Let vector sequence $(y_k, v_{k}, x_{k})_{k \ge 1}$ and R-WAPG sequences $\alpha_k, \rho_k$ be given by Definition \ref{def:wapg}. 
+                Define $R_1 = 0$ and suppose that for $k = 1, 2, \ldots, N$, we have $R_k$ recursively given by: 
+                {\scriptsize
+                \begin{align*}
+                    R_{k + 1}
+                    := 
+                    \frac{1}{2}\left(
+                        L^{-1} - \frac{\alpha_k^2}{\hat \gamma_{k + 1}}
+                    \right)\Vert g_k\Vert^2
+                    + 
+                    (1 - \alpha_k)
+                    \left(
+                        \epsilon_k + R_k + 
+                        \frac{\mu\alpha_k\gamma_k}{2\hat \gamma_{k + 1}}
+                        \Vert v_k - y_k\Vert^2
+                    \right). 
+                \end{align*}
+                }
+                Then for all $k = 1, 2, \ldots, N$: 
+                {\scriptsize
+                \begin{align*}
+                    & F(x_{k + 1}) - F(x^*) + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
+                    \\
+                    &\le 
+                    \left(
+                        \prod_{i = 0}^{k - 1} \max(1, \rho_{i})
+                    \right)
+                    \left(
+                        \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
+                    \right)
+                    \left(
+                        F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
+                    \right). 
+                \end{align*}
+                }
+            \end{proposition}
+        \end{frame}
+    \subsection{Equivalent forms of R-WAPG}
+        \begin{frame}{Equivalent forms of R-WAPG}
+            \begin{enumerate}
+                \item Equivalent forms of R-WAPG exists and resembles variants of FISTA in the literatures
+                \item We proved the equivalences in our draft papers and the convergence claim from previous applies to all the equivalent forms of R-WAPG which will follow. 
+            \end{enumerate}    
+        \end{frame}
+        \begin{frame}{R-WAPG intermediate form}
+            \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}
+                Assume $\mu < L$ and let $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 
+                Initialize any $x_1, v_1$ in $\RR^n$. 
+                For $k \ge 1$, the algorithm generates sequence of vector iterates $(y_{k}, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by the procedures: 
+                {\small
+                \begin{tcolorbox}
+                    For $k = 1, 2, \ldots$
+                    \begin{align*} 
+                        & y_{k} = 
+                        \left(
+                            1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
+                        \right)^{-1}
+                        \left(
+                            v_{k + 1} + 
+                            \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
+                        \right), 
+                        \\
+                        & x_{k + 1} = 
+                        y_k - L^{-1} \mathcal G_L y_k, 
+                        \\
+                        & v_{k + 1} = 
+                        \left(
+                            1 + \frac{\mu}{L \alpha_k - \mu}
+                        \right)^{-1}
+                        \left(
+                            v_k + 
+                            \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
+                        \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
+                    \end{align*}
+                \end{tcolorbox}
+                }
+            \end{definition}
+            \pause
+            \begin{enumerate}
+                \item If, $\mu = 0$, this is Chapter 12 of in Ryu and Yin's Book \cite{ryu_large-scale_2022}, right after Theorem 17.
+            \end{enumerate}
+        \end{frame}
+        \begin{frame}{R-WAPG similar triangle form}
+            \begin{definition}[R-WAPG similar triangle form]\label{def:r-wapg-st-form}
+            {\small
+                Given any $(x_1, v_1)$ in $\RR^n$. 
+                Assume $\mu < L$.
+                Let the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k\ge 0}$ be given by Definition \ref{def:rwapg-seq}. 
+                For $k \ge 1$, the algorithm generates sequences of vector iterates $(y_k, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by the procedures: 
+                \begin{tcolorbox}
+                    For $k=1, 2, \ldots $
+                    {\scriptsize
+                    \begin{align*}
+                        & y_k = 
+                        \left(
+                            1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
+                        \right)^{-1}
+                        \left(
+                            v_k + 
+                            \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
+                        \right), 
+                        \\
+                        & x_{k + 1} = 
+                        y_k - L^{-1} \mathcal G_L y_k, 
+                        \\
+                        & v_{k + 1} = 
+                        x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k). 
+                    \end{align*}   
+                    } 
+                \end{tcolorbox}
+            }
+            \end{definition}
+            \pause
+            {\small
+            \begin{enumerate}
+                \item Equation (2), (3), (4) in \cite{chambolle_convergence_2015} is a similar triangle formulation of FISTA with $\mu = 0$. 
+                \item see (3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022} for graphical visualization of similar triangle form. 
+            \end{enumerate}
+            }
+        \end{frame}
+
+        \begin{frame}{R-WAPG momentum form}
+            \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
+                Given any $y_1 = x_1 \in \RR^n$, and sequences $(\rho_k)_{k \ge 0}, (\alpha_k)_{k\ge 0}$ Definition \ref{def:rwapg-seq}. 
+                The algorithm generates iterates $x_{k + 1}, y_{k + 1}$ For $k = 1, 2, \cdots $ by the procedures: 
+                {\small
+                \begin{tcolorbox}
+                    For $k=1, 2,\ldots $
+                    \begin{align*}
+                        & x_{k + 1} = y_k - L^{-1}\mathcal G_Ly_k, 
+                        \\
+                        & 
+                        y_{k + 1} = 
+                        x_{k + 1} + 
+                        \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
+                    \end{align*}    
+                \end{tcolorbox}
+                }
+                In the special case where $\mu = 0$, the momentum term can be represented without parameter $\rho_k$: 
+                $$
+                    (\forall k \ge 1)\quad \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}} 
+                    = \alpha_{k + 1}(\alpha_k^{-1} - 1). 
+                $$
+            \end{definition}
+        \end{frame}
+
+    \subsection{Unified Convergence claim with relaxed Nesterov's sequence}
+        \begin{frame}{Summary of our results}
+            With the equivalent representations and the convergence claim for relaxed sequence $(\alpha_k)_{k \ge 0}$ of the R-WAPG, we are able to unifies: 
+            \begin{enumerate}
+                \item Several Euclidean variants of the FISTA algorithm. 
+                \item Nontraditional choices of momentum sequences. 
+            \end{enumerate}
+            The table below summarizes our major results. \begin{table}[H]
+            {\tiny
+            \begin{tabular}{|l|l|l|l|}
+            \hline
+                Algorithm & $\mu$ & $\alpha_k, \rho_k$ & $F(x_k) - F^* \le \mathcal O(\cdot)$ 
+            \\ \hline
+                Definition \ref{def:wapg} & 
+                $\mu \ge 0$ &
+                $\alpha_k \in(\mu/L, 1)$, $\rho_k > 0$ & 
+                \begin{tabular}{l}
+                    $\prod_{i = 0}^{k-1} \max(1, \rho_i)(1 - \alpha_{i + 1})$
+                    \\
+                    (Proposition \ref{prop:wagp-convergence})
+                \end{tabular}
+            \\ \hline
+                FISTA \cite{chambolle_convergence_2015} &  
+                $\mu = 0$  &
+                $ 0< \alpha_k^{-2} \le \alpha_{k + 1}^{-1} - \alpha_{k + 1}^{-2}$, $\rho_k \ge 1$ &
+                \begin{tabular}{l}
+                    $\alpha_k^{2}$ 
+                    % \\ 
+                    % (Theorem \ref{thm:r-wapg-on-cham-doss})    
+                \end{tabular}
+            \\ \hline
+                \hspace{-1em}\begin{tabular}{l}
+                    V-FISTA \\ (10.7.7) \cite{beck_first-order_2017} 
+                \end{tabular} &
+                $\mu > 0$ &
+                $\alpha_k = \sqrt{\mu/L}$, $\rho_k = 1$ & 
+                \begin{tabular}{l}
+                    $(1 - \sqrt{\mu/L})^k$, 
+                    % \\
+                    % (Theorem \ref{thm:fixed-momentum-fista}, remark)
+                \end{tabular}
+            \\ \hline
+                Definition \ref{def:wapg} &  
+                $\mu > 0$ &
+                $\alpha_k = \alpha \in (\mu/L, 1)$, $\rho_k = \rho > 0$ &  
+                \begin{tabular}{l}
+                    $\max(1 - \alpha, 1 - \mu/(\alpha L))^{k}$
+                    % \\
+                    % (Theorem \ref{thm:fixed-momentum-fista})
+                \end{tabular}
+            \\ \hline
+            \end{tabular}
+            }
+            \end{table}
+            These results are consistent of iteratures. 
+            To the best of our knowledge, the last variant is a and we have the convergence claim for it using R-WAPG. 
+        \end{frame}
+    \subsection{A parameter free formulation of R-WAPG}
+        \begin{frame}{Free R-WAPG}
 
         \end{frame}
-\section{Content of the draft paper}
-
     \subsection{Direction of future works}
@@
 \section{Selected contents from Catalyst Meta Accelerations}
+    \subsection{Error sequences and convergence}
     \subsection{Direction of future works}

### 2025-01-26 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

@@
     The R-WAPG provides a unified framework for several notable Euclidean variants of FISTA and verify their convergence. 
-    In addition we also proposed the convergence rate of strongly convex objective with a constant momentum term. 
+    In addition, we also proposed the convergence rate of strongly convex objective with a constant momentum term. 
     We reformulate R-WAPG so that it doesn't require any parameter without using the idea of restarting which we call ``Free R-WAPG". 
@@
         For simplicity of notations, we write $T$ for $T_L$. 
-        The proof is direct algebra and it starts by deriving an intermediate inequality from the quadratic growth condition of the model function.
+        The proof is direct algebra, and it starts by deriving an intermediate inequality from the quadratic growth condition of the model function.
         Then it uses the characterization of strong convexity to simplify it to obtain the desired results. 
@@
 \section{The method of Free R-WAPG}\label{sec:free-rwapg}
-    In this section, we propose Algorithm \ref{alg:free-rwapg} which estimates the $\mu$ constant as the algorithm executes, and it pools the information using the Bregman Divergence of the smooth part function $f$.
+    In this section, we propose Algorithm \ref{alg:free-rwapg} which estimates the $\mu$ constant as the algorithm executes using the Bregman divergence of $f$ estimated by previous iterates. 
     It is called Free R-WAPG because it doesn't require any knowledge of $\mu, L$ in prior for the smooth part $f$, making it parameter-free. 
@@
     Line 5-8 estimates upper bound for the Lipschitz constant and find $x^+$, the next iterates produced by proximal gradient descent on previous $y_k$; 
-    Line 9 updates $x_{k + 1}$ to be $x^+$, a successful iterate identified by the Lipschitz line search routine;
-    Line 10 updates the R-WAPG sequence $\alpha_k$ for the iterates $y_{k + 1}$;
-    Line 13 updates $\mu$ using the Bregman Divergence of $f$ from iterates $y_{k + 1}, y_k$. 
-    \par
-    Assume $L$ given is an upper bound of the Lipschitz smoothness constant of $f$, so the line search subroutine is never triggered. 
+    Line 8 updates $x_{k + 1}$ to be $x^+$, a successful iterate identified by the Lipschitz line search routine;
+    Line 11 updates the R-WAPG sequence $\alpha_k$ for the iterates $y_{k + 1}$;
+    Line 15 updates $\mu$ using the Bregman Divergence of $f$ from iterates $y_{k + 1}, y_k$. 
+    \par
+    Assume $L$ given to initialize the R-WAPG is an upper bound of the Lipschitz smoothness constant of $f$ hence preventing the line search subroutine to be triggered. 
     Then the algorithm calls $f(\cdot)$ two times, and $\nabla f(\cdot)$ once per iteration. 
@@
     \par 
-    From a theoretical perspective, the convergence result (Proposition \ref{prop:wapg-convergence}) of R-WAPG is relevant to some degree because the sequence $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg} is an R-WAPG sequence.
-    Let $\tilde \mu_k$ be an estimate produced by the algorithm then it satisfies that $\tilde \mu_k/ L \in (0, 1)$.
+    Sections of $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg} can be an R-WAPG sequence making the convergence result (Proposition \ref{prop:wapg-convergence}) of R-WAPG is relevant to a limited extend.
+    For the full sequence $(\alpha_k)_{k \ge0}$ to be an R-WAPG sequence requires additional assumption that none of the estimate has $\tilde \mu = L$. 
+    Let $\tilde \mu_k$ be an estimate produced by the algorithm and assume that it satisfies that $\tilde \mu_k/ L \in [0, 1)$ and $\alpha_k \in (\mu/L, 1)$.
     Assuming inductively that $q = \tilde \mu_k/L$,  $\alpha_k \in (\mu/L, 1)$, then 
@@
     \subsection{Numerical experiments}
-        This section we conduct numerical experiments conducted using FR-WAPG algorithm (Algorithm \ref{alg:free-rwapg}), and compare with other APG algorithms in the literatures: the V-FISTA, and M-FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}.
-        We implemented in Julia \cite{bezanson_julia_2017} and compare V-FISTA, M-FISTA from Beck, and Algorithm \ref{alg:free-rwapg} given this section. 
-        Focusing on iteration complexities of the algorithm, the results of the experiments are visualized and the setup of the numerical experiments are described  in the sections that follows. 
-        \par
+        This section showcases results for the numerical experiments conducted using FR-WAPG algorithm (Algorithm \ref{alg:free-rwapg}), and compare with other APG algorithms in the literatures: the V-FISTA, and M-FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}.
+        We implemented in Julia \cite{bezanson_julia_2017} and FR-WAPG (Algorithm \ref{alg:free-rwapg}) with V-FISTA, M-FISTA. 
         The equivalences highlighted in Proposition \ref{prop:r-wapg-momentum-repr} allows us to compare the sequence of iterates $(x_k)_{k \ge 1}, (y_k)_{k \ge0}$ for R-WAPG, VISTA and M-FISTA. 
         \par
-        Given the same randomized initial condition for all the algorithm, we measure the aggregate statistics of the base two logarithms of the normalized optimality gap (NOG), at each iteration $k$.
-        Given the iterates $x_k$, and the minimum $F^*$, the normalized optimality gap we defined is: 
+        We measure the aggregate statistics of the base two logarithms of the normalized optimality gap (NOG), at each iteration $k$ with the same initialization conditions given for all algorithms.
+        Given $x_k$, and minimum $F^*$, we define the normalized optimality gap: 
         \newcommand{\NOG}{\text{\textbf{NOG}}}
@@
         \end{align*}
-        Since it's not the case that $F^*$ is always known in prior, we used the minimum of all $F(x_k)$ across all algorithms, all iterations $k$ as the surrogate for $F^*$. 
-        \par 
-        For the termination conditions of the algorithm, we consider the norm of the gradient mapping $\Vert \mathcal G_L(y_k)\Vert < \epsilon$. 
+        Since it's not the case that $F^*$ is always known in prior, we will the minimum of all $F(x_k)$ across all algorithms, all iterations $k$ as the surrogate for $F^*$ when the true value is unavailable.
+        \par 
+        We consider the norm of the gradient mapping $\Vert \mathcal G_L(y_k)\Vert < \epsilon$ as a termination conditions for all test algorithms. 
         The $L$ can change during each iteration if it's obtained through the specified Lipschitz line search routine. 
-
         \subsubsection{Simple convex quadratic}
-            Consider the minimization problem of $\min_{x \in \RR^n} \{F(x):= f(x) + 0\}$ where the objective function is given by: 
-            \begin{align*}
-                F(x) = (1/2)\langle x, A x\rangle. 
-            \end{align*}
-            The matrix $A$ is set to be positive semi-definite and diagonal. 
-            Then the optimization problem admits unique minimizer $x^* = \mathbf 0$ and the minimum is zero. 
-            \par
+            Consider $\min_{x \in \RR^n} \{F(x):= f(x) + 0\}$ where 
+            \begin{align*}
+                f(x) = (1/2)\langle x, A x\rangle. 
+            \end{align*}
+            $A$ is set to be a positive semi-definite diagonal matrix so the problem admits unique minimizer $x^* = \mathbf 0$ with minimum being zero. 
             We apply Algorithm \ref{alg:free-rwapg}, M-FISTA, and V-FISTA. 
-            The parameters for setting up the problem now follows. 
+            The following parameters are used to setup the problem: 
             \begin{enumerate}
-                \item $N$, the dimension of the problem. 
-                \item $0 < \mu < L$, the strong convexity and Lipschitz smoothness constant. They are given in prior to construct the problem. 
-                \item $A \in \RR^{N\times N}$, a diagonal matrix given by $N- 1$ linearly spaced with equal increment on the interval $[\mu, L]$, and an extra number $0$, i.e: $A = \text{diag}(0, \mu + (L-\mu)(N - 1)^{-1}, \mu + 2(L-\mu)(N - 1)^{-1}, \cdots, \mu + (N - 2)(L - \mu)^{-1}, L)$.
-                \item In this case $f = F = (1/2)\langle x, A x\rangle$ and $g \equiv 0$. 
-                \item $\epsilon > 0$, the tolerance value for termination criteria. 
+                \item $N$, the dimension of the problem which defines $A \in \RR^{N\times N}$, a diagonal matrix given by $N- 1$ linearly spaced with equal increment on the interval $[\mu, L]$, and an extra number $0$, i.e: $A = \text{diag}(0, \mu + (L-\mu)(N - 1)^{-1}, \mu + 2(L-\mu)(N - 1)^{-1}, \cdots, \mu + (N - 2)(L - \mu)^{-1}, L)$.
+                \item The strong convexity and Lipschitz smoothness constant has $0 < \mu < L$. They are given in prior to construct the problem. 
+                \item $\epsilon > 0$ is the tolerance value and it's set to be $10^{-10}$. 
                 \item $x_0 \sim \mathcal N(I, \mathbf 0)$ is a vector, and it's the initial condition for all the algorithm.
@@
             The parameter $L=1, \mu=10^{-5}$ are given in prior to produce the diagonal matrix $A$, and we conduct many experiments for $N = 256$ and $N = 1024$. 
-            For all R-WAPG, M-FISTA and V-FISTA, 
-            we use a different initial guess each time, a set of 30 experiments are performed. 
-            The maximum, minimum and median values of $\delta_k$ are measured for all algorithm at each iteration and plotted as a ribbon. 
+            For all R-WAPG, M-FISTA and V-FISTA the same random initial guess is used for all test algorithms and 30 experiments are repeated with a different random initial guess each time. 
+            The maximum, minimum and median values of $\delta_k$ are measured for all algorithms at each iteration and plotted as a ribbon. 
             Results are shown in Figure \ref{fig:simple-quadratic-NOG}.
@@
             Another quantity that maybe interesting other than $\delta_k$ would be the estimated value of $\mu$ during at each iteration $k$. 
-            This $\mu$ parameter should converge to the true value. 
             One individual experiment is carried out for the R-WAPG algorithm and the value of $\mu$ at each iteration is being recorded as well. 
             Figure \ref{fig:simple-quadratic-r-wapg-mu-estimates} showcases the results. 
-            The values oscillate and converges to the true $\mu$ value. 
+            In this experiment, the values oscillate and converges to the true $\mu$ value. 
             Observe that the iteration when the estimates are nearing the true value corresponds to the iteration when the algorithm plateau away from its initial fast descent. 
@@
             \end{figure}
-
         \subsubsection{LASSO}
             This section present results of numerical experiment for solving the (least absolute shrinkage and selection operator) LASSO problem proposed by Tibshirani \cite{tibshirani_regression_1996}.
-            The problem of LASSO has smooth, nonsmooth additive and the problem is given by: 
+            The problem of LASSO has smooth, nonsmooth additive parts given by: 
             \begin{align*}
@@
             The objective function is coersive and the exact minimum, or minimizers are unknown. 
-            We perform numerical experiments using V-FISTA, M-FISTA and R-WAPG on this problem. 
-            The parameters for setting up the problem now follow. 
+            We perform numerical experiments using V-FISTA, M-FISTA and FR-WAPG on this problem. 
+            The setup of our parameters now follow. 
             \begin{enumerate}
-                \item $M, N$ are constants. 
-                \item $A \in \RR^{M\times N}$ is a matrix of i.i.d random variable, taken from a standard normal distribution. 
-                \item $L, \mu$, the Lipschitz constant and the strong convexity constant for the smooth part of the objective are not known prior, and it's estimated through $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$.
+                \item $M, N$ are constants. They define matrix $A \in \RR^{M\times N}$ which has entires of i.i.d random variable taken from a standard normal distribution. 
+                \item $L, \mu$, are Lipschitz constant and the strong convexity constant for the smooth part of the objective which are not known prior.
+Hence they are estimated by $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$ prior to experiment to assist the V-FISTA algorithm.
                 \item $x^+ = [1\; -1\; 1 \; \cdots ]^T \in \RR^N$, it's a vector with alternating $1, -1$ in it. 
@@
                 \item Given $A$, estimations for $L,\mu$ are given by $L = \Vert A^TA\Vert$, $\mu = \Vert (A^TA)^{-1}\Vert^{-1}$. 
-                \item $x_0\in \RR^N$ is the initial guess. Its elements are random i.i.d variable realized from the standard normal distribution. 
-                \item $\epsilon > 0$ is the tolerance the controls the termination criteria for test algorithms. 
+                \item $x_0\in \RR^N$ denotes the initial guess consist of i.i.d random variable realized from the standard normal distribution. 
+                \item $\epsilon = 10^{-6} > 0$ sets the tolerance for all test algorithm on $\Vert \mathcal G_L(x_k)\Vert$. 
             \end{enumerate}
-            Experiments were conducted using V-FISTA, M-FISTA and FR-WAPG with $(M, N) = (64, 256)$ and $(M, N) = (64, 128)$. 
-            Matrix $A$ is fixed and the for all test algorithms and all repetitions. 
-            The same experiment are repeated 30 times, but each time, we fix a different random initial condition $x_k$ for all test algorithms. 
+            Experiments were conducted using V-FISTA, M-FISTA and FR-WAPG with $(M, N) = (64, 256)$ and $(M, N) = (64, 128)$ respectively. 
+            A random matrix $A$ is realized and is fixed and the for all test algorithms and all repetitions. 
+            The same experiment are repeated 30 times on all algorithms with a fixed random initial condition $x_k$ realized from the distribution. 
             The aggregate statistics of $\delta_k$ are collected for all repetitions, and then grouped by the respective algorithm. 
@@
             Another quantity of interest is the estimates of $\mu$ on each iteration of the algorithm. 
-            A single experiment were conducted and the estimates and $\delta_k$ are showcased in Figure \ref{fig:single-lass-mu-estimates}
+            A single experiment were conducted and the estimates and $\delta_k$ are in Figure \ref{fig:single-lass-mu-estimates}
             \begin{figure}[H]

### 2025-01-27 Notebook LaTEX/Proposal/presentation.tex
>w<, shits need more works

@@
 \setbeamertemplate{footline}[frame number] % ADD PAGE NUMBERS ON BOTTOM. 
+% BIB STYLES SETTINGS ----------------------------------------------------------
+\setbeamerfont{bibliography item}{size=\footnotesize}
+\setbeamerfont{bibliography entry author}{size=\footnotesize}
+\setbeamerfont{bibliography entry title}{size=\footnotesize}
+\setbeamerfont{bibliography entry location}{size=\footnotesize}
+\setbeamerfont{bibliography entry note}{size=\footnotesize}
 % \setbeamercovered{transparent}  % GREY OUT PAUSED FUTURE ITEMS IN SLID. 
@@
 \end{frame}
-\begin{frame}{ToC}
+
+\begin{frame}[allowframebreaks]{ToC}
     \tableofcontents
@@
         \begin{frame}{Notations and preliminaries}
-            Throughout this talk, let $\RR^n$ be the ambient space equiped with Euclidean inner product and norm. 
+            Throughout this talk, let $\RR^n$ be the ambient space equipped with Euclidean inner product and norm. 
             We consider 
@@
                 \item $g:\RR^n \rightarrow \overline \RR$ is closed convex proper. 
+                \item Minimum exists $F^* = \min_{x\in \RR^n}\{f(x) + g(x)\}$ and minimizer exists. 
             \end{enumerate}
@@
         \begin{frame}{Our works on R-WAPG}
-            Here are the contributions of our draft paper. 
             Recall the Nesterov's acceleration has momentum extrapolation updates on $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$. 
@@
         \begin{frame}{Introducing Catalyst Part II}
-            Catalyst by Lin, et al. \cite{lin_catalyst_2018, lin_universal_2015} has the theoretical and pratical importance: 
+            Catalyst by Lin, et al. \cite{lin_catalyst_2018, lin_universal_2015} has the theoretical and practical importance: 
             \begin{enumerate}
-                \item It's an early attempt at putting accelerated inexact proximal point method into a practical settings. 
-                \item It finds application in machine learning and it accelerates the convergence of Varianced Reduced Method (A type of incremental method that is not slower than the exact counter part).
+                \item It's an early attempt at putting accelerated inexact proximal point method into a practical setting. 
+                \item It finds application in machine learning and it accelerates the convergence of Variance Reduced Method (A type of incremental method that is not slower than the exact counter part).
                 \item It demonstrates crucial ideas on how prove convergence rate where the evaluation of proximal point method is inexact in the convex settings. 
@@
             \end{table}
-            These results are consistent of iteratures. 
-            To the best of our knowledge, the last variant is a and we have the convergence claim for it using R-WAPG. 
+            These results are consistent of literatures. 
+            To the best of our knowledge, the last variant is, and we have the convergence claim for it using R-WAPG. 
         \end{frame}
@@
         \begin{frame}{Free R-WAPG}
+            We proposed the following implementation of R-WAPG which doesn't require parameters $\mu, L$ in advance.
 
+            \begin{algorithm}[H]
+            {\scriptsize
+                \begin{algorithmic}
+                \STATE{\textbf{Input: } $f, g, x_0, L > \mu \ge 0, \in \RR^n, N \in \N$}
+                \STATE{\textbf{Initialize: }$y_0 := x_0;L := 1; \mu := 1/2; \alpha_0 = 1;$}
+                \STATE{\textbf{Compute: } $f(y_k)$; }
+                \FOR{$k = 0, 1, 2, \cdots, N$}
+                    \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$;}
+                    \WHILE{$L/2\Vert x^+ - y\Vert^2 < D_f(x^+, y)$}
+                        \STATE{$L:= 2L$;}
+                        \STATE{$x^+ = [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$; }
+                    \ENDWHILE
+                    \STATE{$x_{k + 1} := x^+$;}
+                    \STATE{$\alpha_{k + 1} := (1/2)\left(\mu/L - \alpha_{k}^2 + \sqrt{(\mu/L - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;}
+                    \STATE{$\theta_{k + 1} := \alpha_k(1 - \alpha_k)/(\alpha_k^2 + \alpha_{k + 1})$;}
+                    \STATE{$y_{k + 1}:= x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$; }
+                    \STATE{\textbf{Compute: } $f(y_{k + 1})$}
+                    \STATE{$\mu := (1/2)(2D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2) + (1/2)\mu$;}
+                \ENDFOR
+                \end{algorithmic}
+                \caption{Free R-WAPG}
+                \label{alg:free-rwapg}
+            }
+            \end{algorithm}
         \end{frame}
-    \subsection{Direction of future works}
+
+    \subsection{Numerical experiments}
+        \begin{frame}{Simple quadratic optimizations}
+            Our metric is called normalized optimality gap: 
+            \newcommand{\NOG}{\text{\textbf{NOG}}}
+            {\footnotesize
+            \begin{align*}
+                \delta_k := \log_2\left(
+                    \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}
+                \right). 
+            \end{align*}
+            }
+            This is our first numerical experiment is: 
+            \begin{align*}
+                F(x) = (1/2)\langle x, A x\rangle. 
+            \end{align*}
+            Our setup has: 
+            \begin{enumerate}
+                \item Same initial guess shared by FR-WAPG from us, and  M-FISTA, V-FISTA in (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}.
+It's repeated for 30 different random initial guesses.
+                \item Min, max, and median of $\delta_k$ measured for all iterative method.
+                \item $\mu, L$ were given in prior to produce diagonal matrix $A = \text{diag}(0, \mu + (L-\mu)(N - 1)^{-1}, \mu + 2(L-\mu)(N - 1)^{-1}, \cdots, \mu + (N - 2)(L - \mu)^{-1}, L)$, but M-FISTA, FR-WAPG were not fed these parameters.
+            \end{enumerate}
+        \end{frame}
+        \begin{frame}{Simple quadratic optimizations results}
+            We had $L = 1, \mu = 10^{-5}$ and this is the results: 
+            \begin{figure}[H]
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering 
+                    \includegraphics[width=\textwidth]{assets/simple_regression_batched-256.png}
+                    \caption{$N = 256$, simple convex quadratic.}
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/simple_regression_batched-1024.png}
+                    \caption{$N = 1024$, simple convex quadratic. }
+                \end{subfigure}
+                \caption{Simple convex quadratic experiments results for V-FISTA, M-FISTA, and R-WAPG. }
+                \label{fig:simple-quadratic-NOG}
+            \end{figure}
+        \end{frame}
+        \begin{frame}{$\mu$ estimation graph by FR-WAPG}
+            FR-WAPG estimates the following for $\mu$ during its execution: 
+            \begin{figure}[H]
+                \centering
+                \includegraphics[width=0.64\textwidth]{assets/simple_regression_loss_sc_estimates_1024.png}
+                \caption{$N = 1024$, the $\mu$ estimates produced by Algorithm \ref{alg:free-rwapg} (R-WAPG) is recorded. }
+                \label{fig:simple-quadratic-r-wapg-mu-estimates}
+            \end{figure}
+        \end{frame}
+        \begin{frame}{LASSO numerical experiment}
+            Tibshirani \cite{tibshirani_regression_1996} proposed: 
+            \begin{align*}
+                \min_x
+                \left\lbrace
+                    \frac{1}{2}\Vert Ax - b\Vert^2 + \lambda\Vert x\Vert_1
+                \right\rbrace. 
+            \end{align*}
+            Our setup: 
+            \begin{enumerate}
+                \item $M, N$ are constants. $A \in \RR^{M\times N}$ ahs i.i.d random entries from a standard normal distribution. 
+                \item $L, \mu$, are estimated by $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$. 
+                \item The synthetic solution is $x^+ = [1\; -1\; 1 \; \cdots ]^T \in \RR^N$ and $b = Ax^+ \in \RR^M$.
+                \item $x_0\in \RR^N$ is the initial guess with i.i.d randomed variable from a standard normal distributions. Same initial guess shared by FR-WAPG, V-FISTA, M-FISTA. 
+            \end{enumerate}
+        \end{frame}
+        \begin{frame}{LASSO numerical experiment results}
+            Recorded statistics of $\delta_k$ for all algorithms. 
+            \begin{figure}[H]
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/lasso_batched_statistics_64-256.png}
+                    \caption{LASSO experiment with $M = 64, N = 256$. Plots of minimum, maximum, and median $\delta_k$ with estimated $F^*$. }
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/lasso_batched_statistics_64-128.png}
+                    \caption{LASSO experiment with $M = 64, N = 128$. Plots of minimum, maximum, and median $\delta_k$ with estimated $F^*$. }
+                \end{subfigure}
+                \caption{LASSO experiments. }
+                \label{fig:batched-lasso}
+            \end{figure}
+        \end{frame}
+        \begin{frame}{$\mu$ estimates produced from a single LASSO experiment}
+            FR-WAPG produces the following estimates for $\mu$ on one of the test instance of LASSO: 
+            \begin{figure}[H]
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \includegraphics[width=\textwidth]{assets/lasso_loss_256.png}
+                    \caption{Single lasso experiment plot of $\delta_k$ with.  }
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \includegraphics[width=\textwidth]{assets/lasso_sc_estimates_256.png}
+                    \caption{The $\mu$ estimated by test algorithms for one LASSO experiment. }
+                \end{subfigure}
+                \caption{
+                    A single LASSO experiment results, with $M = 64, 256$. 
+                    We had $\mu = 7.432363627613958\times 10^{-18}$ and $L = 2321.737206983643$.
+                }
+                \label{fig:single-lass-mu-estimates}
+            \end{figure}
+        \end{frame}
+    \subsection{Direction of future works for R-WAPG}
+        \begin{frame}{Nesterov's idea of strong convexity transfer}
+            There is one detail that our R-WAPG doesn't incorperate on all Euclidean variants of FISTA. 
+            We consider this a minor augmentation for the future. 
+            \begin{enumerate}
+                \item In Nesterov's 2013 paper \cite{nesterov_gradient_2013}, he considers accelerated  minimization problem $\phi = f + g$ with $f$ $L_f$ smooth and $g$ being $\mu_g \ge 0$ strongly convex.
+                \item Algorithm 5, Chambolle, Pock \cite{chambolle_introduction_2016} captures several variants of FISTA and it assumes that $F = f + g$ where $f, g$ has strong convexity constant $\mu_f \ge 0, \mu_g \ge 0$ respective so $F$ is $\mu := \mu_f + \mu_g \ge 0$ strongly convex.
+            \end{enumerate}
+            Fast linear convergence is possible if any one of $f, g$ of the function is strongly convex but this is not yet a prediction of R-WAPG. 
+        \end{frame}
 
 \section{Selected contents from Catalyst Meta Accelerations}
-    \subsection{Error sequences and convergence}
+    \subsection{Introduction to Catalyst}
+        \begin{frame}{Assumptions in Catalyst}
+            \begin{assumption}\label{ass:catalyst1}
+                Given any $\beta > 0$ and $y \in \RR^n$, and $F: \RR^n\rightarrow \overline \RR$ is $\mu \ge 0$ strongly convex and closed. 
+                Assume that minimizer exists for $F$ and the minimum is $F^*$. 
+                For all $x,y\in \RR^n, \beta > 0$ define the model function: 
+                \begin{align*}
+                    \mathcal M^{\beta^{-1}}_F(x; y) &:= 
+                    F(x) + \frac{\beta}{2}\Vert x - y\Vert^2.
+                \end{align*}
+                We define the Moreau Envelope at $y \in \RR^n$ to be $\mathcal M^*_{F,\beta^{-1}}(y) := \min_{x\in \RR^n} \mathcal M_F^{\beta^{-1}}(x; y)$. 
+                We denote $\mathcal J_{\beta^{-1}F}$ to be the resolvent operator for subgradient of $F$, which is also called the proximal operator. 
+            \end{assumption}
+        \end{frame}
+        \begin{frame}{Absolute termination criterion}
+            \begin{definition}[Absolute termination criterion C1]\label{def:catalyst-termination-c1}
+                Take $F$ as given by Assumption \ref{ass:catalyst1}.
+                For $\epsilon > 0, \kappa > 0$ and $x \in \RR^n$, the absolute criterion C1 characterizes the set of inexact proximal iterates by: 
+                \begin{align*}
+                    \mathcal J_{\kappa^{-1} F}^\epsilon (x) := 
+                    \left\lbrace
+                        y \in \RR^n \left | \; 
+                                \mathcal M^{1/\kappa}_F (y; x) - 
+                                \mathcal M^*_{F, 1/\kappa}(x) \le \epsilon
+                        \right.
+                    \right\rbrace. 
+                \end{align*}
+            \end{definition}
+            \begin{definition}[Relative termination criterion C2]\label{def:catalyst-termination-c2}
+                Take $F$ as given by Assumption \ref{ass:catalyst1}. 
+                Given any $\delta \in (0, 1]$, $\kappa > 0$ and $x \in \RR^n$, the relative criterion C2 of the inexact resolvent is defined by: 
+                {\small
+                \begin{align*}
+                    \widetilde{\mathcal J}_{\kappa^{-1}F}^\delta (x)
+                    := 
+                    \left\lbrace
+                        z \in \RR^n \left| \;
+                            \mathcal M_F^{\kappa^{-1}}(z; x) - 
+                            \mathcal M^*_{F, \kappa^{-1}}(z; x)
+                            \le \frac{\kappa\delta}{2}\Vert x - z\Vert^2
+                        \right.
+                    \right\rbrace. 
+                \end{align*}
+                }
+            \end{definition}
+        \end{frame}
+        \begin{frame}{Catalyst meta acceleration}
+            \begin{definition}[Lin's Universal Catalyst Acceleration]\label{def:lin-catalyst-original}
+                Let $F:\RR \rightarrow \overline \RR$ be $\mu \ge 0$ strongly convex and closed. 
+                Let the initial estimate be $x_0 \in \RR^n$, fix parameters $\kappa > 0$ and $\alpha_0 \in (0, 1]$. 
+                Let $(\epsilon_k)_{k \ge 0}$ be an absolute error sequence chosen for the evaluation for inexact proximal point method. 
+                {\small
+                \begin{tcolorbox}
+                    Initialize $x_0 = y_0$. Then the algorithm generates $(x_k, y_k)_{k\ge 0}$ for all $k \ge 1$ such that: 
+                    \begin{align*}
+                        & \text{find } x_k \in \mathcal J_{\kappa^{-1}F}^{\epsilon_k} y_{k - 1}, 
+                        \\
+                        & \text{find } \alpha_k \in (0, 1) \text{ such that } \alpha_k^2 = (1 - \alpha_k)\alpha_{k - 1}^2 + (\mu/(\mu + \kappa))\alpha_k,
+                        \\
+                        & 
+                        y_{k} = x_k + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})}{\alpha_{k - 1}^2 + \alpha_k}(x_k - x_{k - 1}). 
+                    \end{align*}
+                \end{tcolorbox}
+                }
+            \end{definition}
+            Denotes the outerloop algorithm, i.e: Definition \ref{def:lin-catalyst-original} by $\mathbb A$, denote the inner loop algorithm by $\mathbb M$. 
+        \end{frame}
+    \subsection{Complexity theoreis with absolute errors}
+        \begin{frame}{Inner loop complexity assumption}
+            The following assumption is crucial and we will return to it. 
+            \begin{assumption}[Linear convergence of inner loop]\label{ass:linear-convergence-inner-loop}
+                For any $k \in \N$, $y \in \RR^n$. 
+                Suppose $\mathbb M$ generates iterates $(z_{k, t})_{t \ge 0}$ for the inner loop iteration such that there exists $A > 0$, and it has: 
+                {\small
+                \begin{align*}
+                    \mathcal M_F^{\kappa^{-1}}(z_{k, t}, y) - \mathcal M^*_{F, \kappa^{-1}}(y) 
+                    &\le 
+                    A(1 - \tau_{\mathbb M})^t
+                    \left(
+                        \mathcal M_{F}^{\kappa^{-1}}(z_{k,0})
+                        -
+                        \mathcal M^*_{F, \kappa^{-1}}(y)
+                    \right). 
+                \end{align*}
+                }
+            \end{assumption}
+        \end{frame}
+        \begin{frame}{Outer loop complexity, strong convex case}
+            \begin{theorem}[]\label{thm:err-seq-outer-s-cnvx}
+            {\small
+                For $\mathbb A$ with regularization parameter $\kappa > 0$. 
+                Assume that $F$ is $\mu > 0$ strongly convex. 
+                Choose $\alpha_0 = \sqrt{q}$ with $q = \mu/(\kappa + \mu)$ and the absolute error sequence 
+                $$
+                \begin{aligned}
+                    \epsilon_k = \frac{2}{9}(F(x_0) - F^*)(1 - \rho)^k \quad \text{with }\quad 
+                    \rho < \sqrt{q}. 
+                \end{aligned}
+                $$
+                Then the $\mathbb A$ generates $(x_{k})_{k \ge 0}$ such that 
+                $$
+                \begin{aligned}
+                    F(x_k) - F^* &\le 
+                    C(1 - \rho)^{k + 1} (F(x_0) - F^*) \quad \text{ with }\quad 
+                    C = \frac{8}{(\sqrt{q} - \rho)^2}. 
+                \end{aligned}
+                $$
+            }
+            \end{theorem}
+        \end{frame}
+        \begin{frame}{Outer loop complexity, convex but not strongly convex case}
+            \begin{theorem}[]\label{thm:erro-seq-outer-cnvx}
+            {\small
+                For $\mathbb A$ with regularization parameter $\kappa > 0$. 
+                Assume that $F$ is convex but with strong convexity constant $\mu = 0$. 
+                Choose $\alpha_0 = (\sqrt{5} - 1)/2$ and the absolute error sequence 
+                \begin{align*}
+                    \epsilon_k &= \frac{2(F(x_0) - F^*)}{9(k + 2)^{4 + \eta}} \quad 
+                    \text{with}\quad \eta > 0. 
+                \end{align*}
+                Take $x^*$ to be a minimizer of $F$. 
+                Then algorithm $\mathbb A$ generates $(x_k)_{k \ge0}$ such that it has a convergence rate of 
+                \begin{align*}
+                    F(x_k) - F^* &\le 
+                    \frac{8}{(k + 2)^2}\left(
+                        \left(1 + \frac{2}{\eta}\right)^2(F(x_k) - F^*)
+                        + \frac{\kappa}{2}\Vert x_0 - x^*\Vert^2
+                    \right).
+                \end{align*}
+            }
+            \end{theorem}
+        \end{frame}
+        \begin{frame}{Inner loop complexity, absolute errors}
+            \begin{proposition}[Inner loop complexity strongly convex]\label{prop:inner-loop-complexity-s-cnvx}
+            {\footnotesize
+                Under the same settings of Theorem \ref{thm:err-seq-outer-s-cnvx}, suppose that 
+                \begin{enumerate}
+                    \item $\mathbb M$ has linear convergence rate as specified in Assumption \ref{ass:linear-convergence-inner-loop}, 
+                    \item $\mathbb M$ is initialized with  $z_{k, 0} = x_{k - 1}$ for all $k \ge 2$. 
+                \end{enumerate}
+                Then, the precision $\epsilon_k$ is achieved within at most a number of iteration $T_{\mathbb M} \le \widetilde {\mathcal O}(1/ \tau_{\mathbb M})$. 
+                Here $\widetilde{\mathcal O}$ hides logarithmic complexity in $\mu, \kappa$ and other constants. 
+            }
+            \end{proposition}
+            \begin{proposition}[Inner loop, context but not strongly convex]\label{prop:inner-loop-complexity-cnvx}
+            {\footnotesize
+                Under the settings of Theorem \ref{thm:erro-seq-outer-cnvx}, suppose that:
+                \begin{enumerate}
+                    \item $\mathbb M$ has linear convergence rate as specified in Assumption \ref{ass:linear-convergence-inner-loop}, 
+                    \item the initial guess for $\mathbb M$ is $z_{0, k} = x_{k - 1}$, 
+                    \item $F$ has bounded level set.
+                \end{enumerate}
+                Then there exists $T_{\mathbb M} \le \widetilde{\mathcal O}(1 / \tau_{\mathbb M})$ such that for any $k \ge 1$, it requires at most\\ $T_{\mathbb M}\log(k + 2)$ iterations for $\mathbb M$ to achieve accuracy $\epsilon_k$.
+            }
+            \end{proposition}
+        \end{frame}
+
+        \begin{frame}{Aggregated complexity}
+            We count $m$, the number of iteration experienced by $\mathbb M$ for the $k$ th iteration of $\mathbb A$. 
+            \begin{enumerate}
+                \item If $\mu > 0$, \ref{prop:inner-loop-complexity-s-cnvx} gives $m \le T_{\mathbb M}k$. 
+                Substituting $k \ge m/T_{\mathbb M}$ into Theorem \ref{thm:err-seq-outer-s-cnvx}: 
+                {\footnotesize
+                \begin{align*}
+                    F(x_k) - F^* &\le \mathcal O \left(
+                        (1 - \rho)^k 
+                    \right) \le 
+                    \mathcal O \left(
+                        (1 - \rho)^{m/ T_{\mathbb M}}
+                    \right) \le 
+                    \mathcal O\left(
+                        \left(1 - \rho/T_{\mathbb M}\right)^{m}
+                    \right)
+                    \\
+                    &\le \widetilde{\mathcal O}\left(
+                        \tau_{\mathbb M}\sqrt{\mu}/(\mu + \kappa)
+                    \right). 
+                \end{align*}
+                }
+                \item If $\mu = 0$, using Proposition \ref{prop:inner-loop-complexity-cnvx}, Theorem \ref{thm:erro-seq-outer-cnvx} it has 
+                {\footnotesize
+                \begin{align*}
+                    m &\le \sum_{i - 1}^{k} k T_{\mathbb M} \log(i + 2) \le k T_{\mathbb M} \log(k + 2) 
+                    \le T_{\mathbb M}k(k + 2) 
+                    \le 
+                    \mathcal O(T_{\mathbb M} k^2). 
+                \end{align*}
+                So: 
+                \begin{align*}
+                    F(x_k)- F^* &\le 
+                    \mathcal O(k^{-2})\le 
+                    \mathcal O
+                        \left(
+                            m^{-2}T_{\mathbb M}
+                        \right) 
+                        \le \widetilde{\mathcal O}
+                            \left(m^{-2}\tau_{\mathbb M}^{-1}\right). 
+                \end{align*}
+                }
+            \end{enumerate}
+        \end{frame}
+    \subsection{Complexity theories with relative errors}
+        \begin{frame}{Catalyst acceleration with relative errors}
+            \begin{definition}[Catalyst Acceleration with relative error]\label{def:catalyst-relative}
+            {\small
+                Let $F:\RR \rightarrow \overline \RR$ be $\mu \ge 0$ strongly convex and closed. 
+                Let the initial estimate be $x_0 \in \RR^n$, fix parameters $\kappa > 0$ and $\alpha_0 \in (0, 1]$. 
+                Let $(\delta_k)_{k \ge 0}$ be an absolute error sequence chosen for the evaluation for inexact proximal point method. 
+                \begin{tcolorbox}
+                    Initialize $x_0 = y_0$. Then the algorithm generates $(x_k, y_k)_{k\ge 0}$ for all $k \ge 1$ such that: 
+                    \begin{align*}
+                        & \text{find } x_k \in \widetilde{\mathcal J}_{\kappa^{-1}F}^{\delta_k} y_{k - 1}, 
+                        \\
+                        & \text{find } \alpha_k \in (0, 1) \text{ such that } \alpha_k^2 = (1 - \alpha_k)\alpha_{k - 1}^2 + (\mu/(\mu + \kappa))\alpha_k,
+                        \\
+                        & 
+                        y_{k} = x_k + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})}{\alpha_{k - 1}^2 + \alpha_k}(x_k - x_{k - 1}). 
+                    \end{align*}
+                \end{tcolorbox}
+            }
+            \end{definition}
+        \end{frame}
+        \begin{frame}{Outerloop complexity under relative errors}
+            \begin{theorem}[Outer loop complexity under criterion C2]\label{theorem:catalyst2-outer-loop}
+                For the iterates $(x_k)_{k \ge 0}$ generated by algorithm in Definition \ref{def:catalyst-relative}, we have 
+                \begin{enumerate}
+                    \item If $\mu > 0$, choose $\alpha_0 = \sqrt{q}$, $\delta_k = \sqrt{q}/(2 - \sqrt{q})$. 
+                    Then the iterates $(x_k)_{k \ge 0}$ satisfies $F(x_k) - F^* \le \mathcal O\left(1 - \sqrt{q}/2\right)^k$. 
+                    \item If $\mu = 0$, choose $\alpha_0 = 1$, $\delta_k = 1/(k + 1)^2$ satisfies $F(x_k) - F^* \le \mathcal O(k^{-2})$. 
+                \end{enumerate}
+            \end{theorem}
+            \begin{remark}
+                This is Proposition 8, 9 in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018}.
+                For a precise description of the upper bound, see Theorem 8. 
+            \end{remark}
+            Observe that it does't require knowledge about $F^*$. 
+        \end{frame}
+
     \subsection{Direction of future works}
@@
     \end{frame}
+
     \begin{frame}[allowframebreaks]{References}

### 2025-01-27 Notebook LaTEX/Proposal/proposal.tex
>w<, changes
>w<, shits need more works

@@
 
-    \section{R-WAPG unifies existing accelerations scheme}\label{sec:rwapg-literatures}
+    \subsection{R-WAPG unifies existing accelerations scheme}\label{sec:rwapg-literatures}
         In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are much more flexible. 
@@
     \subsection{Numerical experiments}
-        This section gives figures and visual for numerical experiments conducted on the R-WAPG algorithm, and other algorithms in the literatures such as the V-FISTA, and M-FISTA algorithm. 
-        We implemented and compare V-FISTA, M-FISTA from Beck, and Algorithm \ref{alg:free-rwapg} given this section. 
-        The results of the experiments are visualized and the setup of the numerical experiments are described  in the sections that follows. 
-        \par
+        This section showcases results for the numerical experiments conducted using FR-WAPG algorithm (Algorithm \ref{alg:free-rwapg}), and compare with other APG algorithms in the literatures: the V-FISTA, and M-FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}.
+        We implemented in Julia \cite{bezanson_julia_2017} and FR-WAPG (Algorithm \ref{alg:free-rwapg}) with V-FISTA, M-FISTA. 
         The equivalences highlighted in Proposition \ref{prop:r-wapg-momentum-repr} allows us to compare the sequence of iterates $(x_k)_{k \ge 1}, (y_k)_{k \ge0}$ for R-WAPG, VISTA and M-FISTA. 
         \par
-        Given the same randomized initial condition for all the algorithm, we measure the aggregate statistics of the base two logarithms of the normalized optimality gap (NOG), at each iteration $k$.
-        Given the iterates $x_k$, and the minimum $F^*$, the normalized optimality gap we defined is: 
+        We measure the aggregate statistics of the base two logarithms of the normalized optimality gap (NOG), at each iteration $k$ with the same initialization conditions given for all algorithms.
+        Given $x_k$, and minimum $F^*$, we define the normalized optimality gap: 
         \newcommand{\NOG}{\text{\textbf{NOG}}}
@@
         \end{align*}
-        Since it's not the case that $F^*$ is always known in prior, we used the minimum of all $F(x_k)$ across all algorithms, all iterations $k$ as the surrogate for $F^*$. 
-        \par 
-        For the termination conditions of the algorithm, we consider the norm of the gradient mapping $\Vert \mathcal G_L(y_k)\Vert < \epsilon$. 
+        Since it's not the case that $F^*$ is always known in prior, we will the minimum of all $F(x_k)$ across all algorithms, all iterations $k$ as the surrogate for $F^*$ when the true value is unavailable.
+        \par 
+        We consider the norm of the gradient mapping $\Vert \mathcal G_L(y_k)\Vert < \epsilon$ as a termination conditions for all test algorithms. 
         The $L$ can change during each iteration if it's obtained through the specified Lipschitz line search routine. 
-
         \subsubsection{Simple convex quadratic}
-        Consider the minimization problem of $\min_x \{F(x):= f(x) + 0\}$ where the objective function is given by: 
-        \begin{align*}
-            F(x) = (1/2)\langle x, A x\rangle. 
-        \end{align*}
-        The matrix $A$ is set to be positive semi-definite and diagonal. 
-        Then the optimization problem admits unique minimizer $x^* = \mathbf 0$ and the minimum is zero. 
-        \par
+            Consider $\min_{x \in \RR^n} \{F(x):= f(x) + 0\}$ where 
+            \begin{align*}
+                f(x) = (1/2)\langle x, A x\rangle. 
+            \end{align*}
+            $A$ is set to be a positive semi-definite diagonal matrix so the problem admits unique minimizer $x^* = \mathbf 0$ with minimum being zero. 
             We apply Algorithm \ref{alg:free-rwapg}, M-FISTA, and V-FISTA. 
-        The parameters for setting up the problem now follows. 
+            The following parameters are used to setup the problem: 
             \begin{enumerate}
-            \item $N$, the dimension of the problem. 
-            \item $0 < \mu < L$, the strong convexity and Lipschitz smoothness constant. They are given in prior to construct the problem. 
-            \item $A \in \RR^{N\times N}$, a diagonal matrix given by $N- 1$ linearly spaced with equal increment on the interval $[\mu, L]$, and an extra number $0$, i.e: $A = \text{diag}(0, \mu + (L-\mu)(N - 1)^{-1}, \mu + 2(L-\mu)(N - 1)^{-1}, \cdots, \mu + (N - 2)(L - \mu)^{-1}, L)$.
-            \item In this case $f = F = (1/2)\langle x, A x\rangle$ and $g \equiv 0$. 
-            \item $\epsilon > 0$, the tolerance value for termination criteria. 
+                \item $N$, the dimension of the problem which defines $A \in \RR^{N\times N}$, a diagonal matrix given by $N- 1$ linearly spaced with equal increment on the interval $[\mu, L]$, and an extra number $0$, i.e: $A = \text{diag}(0, \mu + (L-\mu)(N - 1)^{-1}, \mu + 2(L-\mu)(N - 1)^{-1}, \cdots, \mu + (N - 2)(L - \mu)^{-1}, L)$.
+                \item The strong convexity and Lipschitz smoothness constant has $0 < \mu < L$. They are given in prior to construct the problem. 
+                \item $\epsilon > 0$ is the tolerance value and it's set to be $10^{-10}$. 
                 \item $x_0 \sim \mathcal N(I, \mathbf 0)$ is a vector, and it's the initial condition for all the algorithm.
@@
             The parameter $L=1, \mu=10^{-5}$ are given in prior to produce the diagonal matrix $A$, and we conduct many experiments for $N = 256$ and $N = 1024$. 
-        For all R-WAPG, M-FISTA and V-FISTA, 
-        we use a different initial guess each time, a set of 30 experiments are performed. 
-        The maximum, minimum and median values of $\delta_k$ are measured for all algorithm at each iteration and plotted as a ribbon. 
+            For all R-WAPG, M-FISTA and V-FISTA the same random initial guess is used for all test algorithms and 30 experiments are repeated with a different random initial guess each time. 
+            The maximum, minimum and median values of $\delta_k$ are measured for all algorithms at each iteration and plotted as a ribbon. 
             Results are shown in Figure \ref{fig:simple-quadratic-NOG}.
             The solid line in the ribbon is the median value of $\delta_k$ across all experiment, the ribbon gives the maximum, minimum value of $\delta_k$ for each iteration across all experiments. 
-        R-WAPG initially behaves similar to M-FISTA, but as the iteration goes on, it started to behave like V-FISTA.  
+            FR-WAPG initially behaves similar to M-FISTA, but as the iteration goes on, it started to behave like V-FISTA.  
             \par 
@@
             Another quantity that maybe interesting other than $\delta_k$ would be the estimated value of $\mu$ during at each iteration $k$. 
-        This $\mu$ parameter should converge to the true value. 
             One individual experiment is carried out for the R-WAPG algorithm and the value of $\mu$ at each iteration is being recorded as well. 
             Figure \ref{fig:simple-quadratic-r-wapg-mu-estimates} showcases the results. 
-        The values oscillate and converges to the true $\mu$ value. 
+            In this experiment, the values oscillate and converges to the true $\mu$ value. 
             Observe that the iteration when the estimates are nearing the true value corresponds to the iteration when the algorithm plateau away from its initial fast descent. 
@@
             \end{figure}
-
         \subsubsection{LASSO}
-        This section present results of numerical experiment for solving the (least absolute shrinkage and
-        selection operator) LASSO problem proposed by 
-        Tibshirani \cite{tibshirani_regression_1996}. 
-        The problem of LASSO has smooth, nonsmooth additive and the problem is given by: 
-        \begin{align*}
-            \min_x
+            This section present results of numerical experiment for solving the (least absolute shrinkage and selection operator) LASSO problem proposed by Tibshirani \cite{tibshirani_regression_1996}.
+            The problem of LASSO has smooth, nonsmooth additive parts given by: 
+            \begin{align*}
+                \min_{x \in \RR^n}
                 \left\lbrace
@@
             \end{align*}
-        The smooth part is $f =\frac{1}{2}\Vert Ax - b\Vert^2$ and the nonsmooth is $g = \lambda\Vert x\Vert_1$. 
-        The objective function is coercive and the exact minimum, or minimizers are unknown. 
-        We perform numerical experiments using V-FISTA, M-FISTA and R-WAPG on this problem. 
-        The parameters for setting up the problem now follow. 
+            The smooth part is $f(x) =\frac{1}{2}\Vert Ax - b\Vert^2$ and the nonsmooth is $g(x) = \lambda\Vert x\Vert_1$. 
+            The objective function is coersive and the exact minimum, or minimizers are unknown. 
+            We perform numerical experiments using V-FISTA, M-FISTA and FR-WAPG on this problem. 
+            The setup of our parameters now follow. 
             \begin{enumerate}
-            \item $M, N$ are constants. 
-            \item $A \in \RR^{M\times N}$ is a matrix of i.i.d random variable, taken from a standard normal distribution. 
-            \item $L, \mu$, the Lipschitz constant and the strong convexity constant for the smooth part of the objective are not known prior, and it's estimated through $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$.
+                \item $M, N$ are constants. They define matrix $A \in \RR^{M\times N}$ which has entires of i.i.d random variable taken from a standard normal distribution. 
+                \item $L, \mu$, are Lipschitz constant and the strong convexity constant for the smooth part of the objective which are not known prior.
+Hence they are estimated by $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$ prior to experiment to assist the V-FISTA algorithm.
                 \item $x^+ = [1\; -1\; 1 \; \cdots ]^T \in \RR^N$, it's a vector with alternating $1, -1$ in it. 
@@
                 \item Given $A$, estimations for $L,\mu$ are given by $L = \Vert A^TA\Vert$, $\mu = \Vert (A^TA)^{-1}\Vert^{-1}$. 
-            \item $x_0\in \RR^N$ is the initial guess. Its elements are random i.i.d variable realized from the standard normal distribution. 
-            \item $\epsilon > 0$ is the tolerance the controls the termination criteria for test algorithms. 
+                \item $x_0\in \RR^N$ denotes the initial guess consist of i.i.d random variable realized from the standard normal distribution. 
+                \item $\epsilon = 10^{-6} > 0$ sets the tolerance for all test algorithm on $\Vert \mathcal G_L(x_k)\Vert$. 
             \end{enumerate}
-        Experiments were conducted using V-FISTA, M-FISTA and R-WAPG with $(M, N) = (64, 256)$ and $(M, N) = (64, 128)$. 
-        Matrix $A$ is fixed and the for all test algorithms and all repetitions. 
-        The same experiment are repeated 30 times, but each time, we fix a different random initial condition $x_k$ for all test algorithms. 
+            Experiments were conducted using V-FISTA, M-FISTA and FR-WAPG with $(M, N) = (64, 256)$ and $(M, N) = (64, 128)$ respectively. 
+            A random matrix $A$ is realized and is fixed and the for all test algorithms and all repetitions. 
+            The same experiment are repeated 30 times on all algorithms with a fixed random initial condition $x_k$ realized from the distribution. 
             The aggregate statistics of $\delta_k$ are collected for all repetitions, and then grouped by the respective algorithm. 
@@
             Another quantity of interest is the estimates of $\mu$ on each iteration of the algorithm. 
-        A single experiment were conducted and the estimates and $\delta_k$ are showcased in Figure \ref{fig:single-lass-mu-estimates}
+            A single experiment were conducted and the estimates and $\delta_k$ are in Figure \ref{fig:single-lass-mu-estimates}
             \begin{figure}[H]
@@
             In 
-            Chambolle, Pock \cite{chambolle_introduction_2016} Algorithm 5, several variants of the FISTA algorithm were captured together into one formulation, and it assumes that $F = f + g$ where $f, g$ has strong convexity index $\mu_f \ge 0, \mu_g \ge 0$, and $F$ is $\mu := \mu_f + \mu_g \ge 0$ strongly convex.
+            Algorithm 5, Chambolle, Pock \cite{chambolle_introduction_2016} captures several variants of FISTA and it assumes that $F = f + g$ where $f, g$ has strong convexity constant $\mu_f \ge 0, \mu_g \ge 0$ respective so $F$ is $\mu := \mu_f + \mu_g \ge 0$ strongly convex.
 
@@
             \end{remark}
-
             \begin{proposition}[Inner loop, context but not strongly convex]\label{prop:inner-loop-complexity-cnvx}

### 2025-01-27 Notebook LaTEX/Proposal/presentation.tex
>w<, fixing cringe shit

@@
             \end{definition}
-            Denotes the outerloop algorithm, i.e: Definition \ref{def:lin-catalyst-original} by $\mathbb A$, denote the inner loop algorithm by $\mathbb M$. 
         \end{frame}
-    \subsection{Complexity theoreis with absolute errors}
+        \begin{frame}{Notations and Variance Reduced Methods}
+            Denotes
+            \begin{enumerate}
+                \item the outer loop algorithm, i.e: Definition \ref{def:lin-catalyst-original} by $\mathbb A$, it generates $(x_k, y_k)_{k \ge 1}$; 
+                \item the inner loop algorithm by $\mathbb M$ that evaluates $x_k \in \mathcal J_{\kappa^{-1}}^{\epsilon_k} y_{k - 1}$, it generates $(z_{k, t})_{t \ge 0}$. 
+            \end{enumerate}
+            The class of variance reduced methods are often used for $\mathbb M$. 
+            Major examples of VRMs include SVRG by Xiao, Zhang \cite{xiao_proximal_2014}, Finito by Defazio et al.
+\cite{defazio_finito_2014}, SAG by Schmidt et al.
+\cite{schmidt_minimizing_2017}, and SAGA by \cite{defazio_saga_2014}.
+        \end{frame}
+    \subsection{Complexity theories with absolute errors}
         \begin{frame}{Inner loop complexity assumption}
-            The following assumption is crucial and we will return to it. 
+            The following assumption is crucial, and we will return to it. 
             \begin{assumption}[Linear convergence of inner loop]\label{ass:linear-convergence-inner-loop}

### 2025-01-27 Notebook LaTEX/Proposal/proposal.tex
>w<, fixing cringe shit

@@
         & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
-    \end{align}\label{eqn:example_algorithm}
+    \end{align}\label{eqn:example-algorithm}
     If the minimizer $x^*$ exists, then the optimality gap $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, a faster rate compared to gradient descent which is $\mathcal O(1/k)$. 
@@
             \end{align*}
-            $A$ is set to be a positive semi-definite diagonal matrix so the problem admits unique minimizer $x^* = \mathbf 0$ with minimum being zero. 
+            $A$ is set to be a positive semi-definite diagonal matrix, so the problem admits unique minimizer $x^* = \mathbf 0$ with minimum being zero. 
             We apply Algorithm \ref{alg:free-rwapg}, M-FISTA, and V-FISTA. 
-            The following parameters are used to setup the problem: 
+            The following parameters are used to set up the problem: 
             \begin{enumerate}
@@
                 \item The strong convexity and Lipschitz smoothness constant has $0 < \mu < L$. They are given in prior to construct the problem. 
-                \item $\epsilon > 0$ is the tolerance value and it's set to be $10^{-10}$. 
+                \item $\epsilon > 0$ is the tolerance value, and it's set to be $10^{-10}$. 
                 \item $x_0 \sim \mathcal N(I, \mathbf 0)$ is a vector, and it's the initial condition for all the algorithm.
@@
 
-\section{Catalyst accelerations and future works}\label{sec:catalyst}
-    We start by introducing important assumptions and notations for the Catalyst Meta Acceleration Frameworks. 
+\section{Catalyst accelerations}\label{sec:catalyst}
+    We introduce assumptions and notations for the Catalyst Meta Acceleration Frameworks. 
     \begin{assumption}\label{ass:catalyst1}
@@
         \end{align*}
-        We define the Moreau Envelope at $y \in \RR^n$ to be $\mathcal M^*_{F,\beta^{-1}}(y) := \min_{x\in \RR^n} \mathcal M_F^{\beta^{-1}}(x; y)$. 
-        We denote $\mathcal J_{\beta^{-1}F}$ to be the resolvent operator for subgradient of $F$, which is also called the proximal operator. 
+        We define the Moreau Envelope at $y \in \RR^n$ to be $\mathcal M^*_{F,\beta^{-1}}(y) := \min_{x\in \RR^n} \mathcal M_F^{\beta^{-1}}(x; y)$ and the resolvent operator for subgradient of $F$ to be $\mathcal J_{\beta^{-1}F}$, i.e: which is also called the proximal operator.
     \end{assumption}
@@
     \end{remark}
-    \textbf{The remainder of the proposal is organized as the follow}. 
+    \textbf{The remainder of this section is organized as the follow}. 
     Section \ref{ssec:catalyst-intro} gives the main ideas behind the Catalyst Acceleration Framework. 
     It follows Lin et al.'s first paper \cite{lin_universal_2015} on Catalyst Acceleration and summarizes the convergence analysis of the algorithm. 
-    Section \ref{ssec:catalyst-second-paper} introduces Lin et al.'s second paper \cite{lin_catalyst_2018} on Catalyst which considers the improved relative error condition stated in Definition \ref{def:catalyst-termination-c2} and discusses its significance.
-    This condition improves the overall complexity and inspired nonconvex gradient based 4WD Catalyst by Paquette \cite{paquette_catalyst_2018}.
+    Section \ref{ssec:catalyst-second-paper} introduces Lin et al.'s second paper \cite{lin_catalyst_2018} on Catalyst which considers the improved relative error condition stated in Definition \ref{def:catalyst-termination-c2}.
+    The relative error condition improves the overall complexity and inspired nonconvex gradient based 4WD Catalyst by Paquette \cite{paquette_catalyst_2018}.
 
     \subsection{Introduction to Catalyst}\label{ssec:catalyst-intro}
-        Inspired by accelerated proximal point Method (APPM) from Güler \cite{guler_new_1992}, and Inexact Proximal Point Method (IPPM) of Rockafellar 1976 \cite{rockafellar_monotone_1976}, Lin \cite{lin_universal_2015} proposed a generic method taking inspirations from the convergence claims   of (APPM) to accelerate Variance Reduced Method (VRM).
+        Inspired by accelerated proximal point Method (APPM) from Güler \cite{guler_new_1992}, and Inexact Proximal Point Method (IPPM) of Rockafellar 1976 \cite{rockafellar_monotone_1976}, Lin et al.
+\cite{lin_universal_2015} proposed a generic method taking inspirations from the convergence claims of (APPM) to accelerate Variance Reduced Method (VRM).
         The fact that VRMs are incremental method that is not slower than full gradient descent in complexity is most relevant to our discussion. 
@@
         In brief, VRM is a type of incremental methods for solving a large sum problem: $F(x) = \sum_{i = 1}^{N} f_i(x)$ in machine learning.
-        See Bertsekas's surveys \cite{bertsekas_incremental_2011,bertsekas_incremental_2017} for more context. 
+        See Bertsekas's surveys \cite{bertsekas_incremental_2011,Bertsekas_incremental_2017} for more context. 
         VRM can be deterministic, or stochastic. 
@@
         \par
-        Next, we introduce the first Catalyst algorithm in \cite{lin_universal_2015}. 
+        The following definition introduces the first Catalyst algorithm in \cite{lin_universal_2015}. 
         \begin{definition}[Lin's Universal Catalyst Acceleration]\label{def:lin-catalyst-original}\; \\ 
-            Let $F:\RR \rightarrow \overline \RR$ be $\mu \ge 0$ strongly convex and closed. 
-            Let the initial estimate be $x_0 \in \RR^n$, fix parameters $\kappa > 0$ and $\alpha_0 \in (0, 1]$. 
+            Let $F:\RR \rightarrow \overline \RR$ be $\mu \ge 0$ strongly convex and closed, $x_0 \in \RR^n$ be the initial condition and $\kappa > 0$, $\alpha_0 \in (0, 1]$ are fixed parameters for the algorithm.
             Let $(\epsilon_k)_{k \ge 0}$ be an absolute error sequence chosen for the evaluation for inexact proximal point method. 
             \begin{tcolorbox}
-                Initialize $x_0 = y_0$. Then the algorithm generates $(x_k, y_k)_{k\ge 0}$ for all $k \ge 1$ such that: 
+                Initialize $x_0 = y_0$. Then the algorithm generates $(x_k, y_k)_{k\ge 0}$ for all $k \ge 1$ by the procedures: 
                 \begin{align*}
@@
         \textbf{Notations now follows}. 
-        With a fixed regularization parameter $\kappa > 0$, the outer loop (i.e: Definition \ref{def:lin-catalyst-original}) produces $(y_{k}, x_k)_{k \ge k}$ denote it by $\mathbb A$. 
+        With a fixed regularization parameter $\kappa > 0$, the outer loop (i.e: Definition \ref{def:lin-catalyst-original}) produces $(y_{k}, x_k)_{k \ge 1}$ denote it by $\mathbb A$. 
         Typically, an iterative scheme (i.e: VRM) with a known complexity is assigned to find inexact proximal iterates $x_k \in {\mathcal J}_{\kappa^{-1}F}^{\epsilon_k} (y_{k - 1})$. 
@@
     \subsection{The second Catalyst Acceleration paper}\label{ssec:catalyst-second-paper}
-        Lin et al.'s second paper on Catalyst Acceleration \cite{lin_catalyst_2018} describes new ideas to choose the termination criteria for the inner for evaluating $\mathcal J_{\kappa^{-1}F}^{\epsilon_k} y_k$ and gives alternatives to the error sequence $\epsilon_k$ based on those termination criteria.
-        % To elucidate, consider the model function $\mathcal M_F^{\kappa^{-1}}(x; y)$ to be $\mu + \kappa$ strongly convex. 
-        % Therefore, it has error bound condition: 
-        % \begin{align*}
-        %     (\forall x\in \RR^n) \quad 
-        %     \mathcal M^{1/\kappa}_F(x; y) -
-        %     \mathcal M_{F, 1/\kappa}^*(y) 
-        %     &\le (\kappa + \mu)\dist
-        %         \left(
-        %             \mathbf 0, \partial \mathcal M^{1/\kappa}_F(x; y)
-        %         \right)^2. 
-        % \end{align*}
-        % By choosing $x$ such that $\dist\left(\mathbf 0, \partial \mathcal M_F^{1/\kappa}(x; y)\right) \le \sqrt{\epsilon}$, it ensures $x \in \mathcal J^\epsilon_{\kappa^{-1}F}(y)$. 
-        % Unfortunately, this is a difficult in practice because a full gradient evaluation on the model function $\mathcal M^{1/\kappa}_F(\cdot; y)$ is costly (compare to the small amount required for VRM, which is just the gradient of a few samples.), so Lin suggested alternatives of inner loop termination criteria, and/or upper bounds of inner loop iteration to make Catalyst Acceleration competitive in practice.
-        \par
-        This section summarizes major results in Lin's second Catalyst paper \cite{lin_catalyst_2018}. 
+        Lin et al.'s second paper on Catalyst Acceleration \cite{lin_catalyst_2018} describes the new option of relative termination criteria (which we stated here in Definition \ref{def:catalyst-termination-c2}) for $\mathbb M$ to evaluate the inexact solutions of $\mathcal J_{\kappa^{-1}F}^{\epsilon_k} y_k$.
+        This condition allows the the use of relative error sequence $\delta_k$ which has advantages that: it gives easier convergence anlaysis, it doesn't need knowledge of $F^*$ and it can be generalize to the nonconvex case.
+        \par
+        This section summarizes major results in Lin et al's second Catalyst paper \cite{lin_catalyst_2018}. 
         To expedite the execution of $\mathbb M$ in general given some error sequence $(\epsilon_k)_{k \ge 0}$ (or equivalently some lower bounds of it), Lin et al.
@@
         \subsubsection{Consequences of the inner loop termination criteria}
-            Lemma \ref{lemma:sufficient-c1} describes a sufficient conditions to verify the membership of $\bar z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$ through the proximal gradient operator on $F:= f_\kappa(z) + g(z)$ which has practical importance because it translates criterion C1 into something implementable, i.e: the proximal gradient operator.
-            For theoretical interests, the absolute and relative criteria C1, C2 places bound on the true error of the gradient of Moreau Envelope at the point $x$. 
-            \par 
-            The following are results proved in Lin's second Catalyst paper. 
+            Lemma \ref{lemma:sufficient-c1} describes a sufficient conditions to verify the membership of $\bar z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$ through the proximal gradient operator on $F:= f_\kappa(z) + g(z)$ which has practical importance because it translate criterion C1 into a implementable criteria in the algorithm with the proximal gradient operator.
+            It contribute to theoretical analysis because it bounds on the true error on the gradient of Moreau Envelope at the point $x$. 
+            \par 
+            The following results are proved in Lin et al second Catalyst paper \cite{lin_catalyst_2018}. 
             Given any $\epsilon > 0$ if $z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$, define the absolute inexact gradient mapping $\mathcal G_{\kappa^{-1}F}^\epsilon (z) := \kappa(x - z)$.
@@
             The theorems and commentaries that follow will illustrate. 
-            \begin{definition}[Catalyst Acceleration with relative inexactness]\label{def:catalyst-relative}
+            \begin{definition}[Catalyst Acceleration all in one]\label{def:catalyst-all-in-one}
                 Suppose that $F$ is a $\mu \ge 0$ strongly smooth under Assumption \ref{ass:catalyst1}. 
@@
             \end{definition}
-
-            \begin{theorem}[Outer loop complexity under criterion C2]\label{theorem:catalyst2-outer-loop}
-                For the iterates $(x_k)_{k \ge 0}$ generated by algorithm in Definition \ref{def:catalyst-relative}, we have 
+            \begin{assumption}[Warm start conditions for relative error C2]
+            \;\label{prop:warm-start-with-c2}\\ 
+            Assume
+
+            \end{assumption}
+
+            \begin{theorem}[Outer loop complexity under criterion C2]\; \label{theorem:catalyst2-outer-loop}\\
+                For the iterates $(x_k)_{k \ge 0}$ generated by algorithm in Definition \ref{def:catalyst-all-in-one}, we have 
                 \begin{enumerate}
@@
             \end{remark}
+            \begin{theorem}{Inner loop complexity with relative error C2}
+
+            \end{theorem}
+
             The key improvement here compared to using absolute inexactness for $\mathbb M$ as stated by Theorem \ref{thm:err-seq-outer-s-cnvx}, \ref{thm:erro-seq-outer-cnvx} is that $(\delta_k)_{k \ge0}$ doesn't require knowledge on $F^*$.

### 2025-01-27 Notebook LaTEX/Proposal/proposal.tex
>w<, fixing cringe shit

@@
                 For any $k \in \N$, $y \in \RR^n$. 
-                Suppose $\mathbb M$ generates iterates $(z_{k, t})_{t \ge 0}$ for the inner loop iteration such that there exists $A > 0$, and it has: 
+                Suppose $\mathbb M$ generates iterates $(z_{k, t})_{t \ge 0}$ for the inner loop iteration such that there exists $C_{\mathbb M} > 0$, and it has: 
                 \begin{align*}
@@
                     &\le 
-                    A(1 - \tau_{\mathbb M})^t
+                    C_{\mathbb M}(1 - \tau_{\mathbb M})^t
                     \left(
@@
             \begin{remark}
-                $T_{\mathbb M}$, an upper bound of the iteration of the inner loop, is a constant in this case. 
+                Here, $T_{\mathbb M}$ is a constant associated with just $\mathbb M$, it's not related to $k, \epsilon_k$. 
             \end{remark}
@@
     \subsection{The second Catalyst Acceleration paper}\label{ssec:catalyst-second-paper}
-        Lin et al.'s second paper on Catalyst Acceleration \cite{lin_catalyst_2018} describes the new option of relative termination criteria (which we stated here in Definition \ref{def:catalyst-termination-c2}) for $\mathbb M$ to evaluate the inexact solutions of $\mathcal J_{\kappa^{-1}F}^{\epsilon_k} y_k$.
-        This condition allows the the use of relative error sequence $\delta_k$ which has advantages that: it gives easier convergence anlaysis, it doesn't need knowledge of $F^*$ and it can be generalize to the nonconvex case.
-        \par
-        This section summarizes major results in Lin et al's second Catalyst paper \cite{lin_catalyst_2018}. 
-        To expedite the execution of $\mathbb M$ in general given some error sequence $(\epsilon_k)_{k \ge 0}$ (or equivalently some lower bounds of it), Lin et al.
-suggested the following new ideas which are not mutually exclusive:
-        \begin{enumerate}
-            \item They gave an improved warm start strategy at the end of Section 3 of their paper. 
-            It improved the convergence rate using relative termination criteria in Definition \ref{def:catalyst-termination-c2}, and it supports smooth plus nonsmooth objective. 
-            \item They gave a relative termination criterion C2 stated in Definition \ref{def:catalyst-termination-c2} which is controlled by the relative error sequence $(\delta_k)_{k \ge 0}$. 
-            The sequence $\delta_k$ doesn't require the knowledge of $F^*$, it simplifies the convergence proof and gives better bounds on the complexity of $\mathbb M$ without using bounded level set assumption.
-            Recall that Theorem \ref{prop:inner-loop-complexity-cnvx} requires bounded level set assumption on $F$. 
-        \end{enumerate}
-        In our notation, we define relative termination criterion C2.
+        Lin et al.'s second paper on Catalyst Acceleration \cite{lin_catalyst_2018} describes the new option of relative termination criterion (which we stated here in Definition \ref{def:catalyst-termination-c2}) for $\mathbb M$ to evaluate the inexact solutions of $\mathcal J_{\kappa^{-1}F}^{\epsilon_k} y_k$.
+        The relative termination condition has advantages: it gives easier convergence analysis, it doesn't need knowledge of $F^*$, and it can generalize to the nonconvex case. 
+        In addition, they also improved warm start strategies for $\mathbb M$ at the end of Section 3. 
+        Both these ideas together provides a tighter and easier complexity analysis for the Catalyst Acceleration. 
+        \par
+        We summarize these innovations in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018} in this section. 
+        The following definition defines relative termination criteria for $\mathbb M$. 
         \begin{definition}[Relative termination criterion C2]\label{def:catalyst-termination-c2}
@@
         \end{remark}
-        Stated by Lin, the following lemmas gives the sufficient condition for evaluating inexact proximal point up to accuracy $\epsilon$. 
+        Stated by Lin, the following lemma provides the sufficient condition for evaluating inexact proximal point up to accuracy $\epsilon$. 
         \begin{lemma}[Sufficient condition for C1]\label{lemma:sufficient-c1}
@@
         \subsubsection{Consequences of the inner loop termination criteria}
-            Lemma \ref{lemma:sufficient-c1} describes a sufficient conditions to verify the membership of $\bar z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$ through the proximal gradient operator on $F:= f_\kappa(z) + g(z)$ which has practical importance because it translate criterion C1 into a implementable criteria in the algorithm with the proximal gradient operator.
-            It contribute to theoretical analysis because it bounds on the true error on the gradient of Moreau Envelope at the point $x$. 
-            \par 
-            The following results are proved in Lin et al second Catalyst paper \cite{lin_catalyst_2018}. 
+            Lemma \ref{lemma:sufficient-c1} describes a sufficient conditions to verify the membership of $\bar z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$ through the proximal gradient operator on $F:= f_\kappa(z) + g(z)$ which has practical importance because it translates criterion C1 into an implementable criterion in the algorithm with the proximal gradient operator.
+            It contributes to theoretical analysis because it bounds on the true error on the gradient of Moreau Envelope at the point $x$. 
+            \par 
+            The following results are proved in Lin et al. second Catalyst paper \cite{lin_catalyst_2018}. 
             Given any $\epsilon > 0$ if $z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$, define the absolute inexact gradient mapping $\mathcal G_{\kappa^{-1}F}^\epsilon (z) := \kappa(x - z)$.
@@
             \par
-            Besides Definition \ref{def:catalyst-termination-c1}, \ref{def:catalyst-termination-c2}, the ``Fixed Budget" termination criterion terminates $\mathbb M$ after a fixed number of iteration given accuracy $\epsilon_k$.
-            Criterion C1 used to prove the overall complexity in Lin et al. \cite{lin_universal_2015}, but the bound is deliberately loose to allow generality, making it extremely impractical. 
-            Criterion C2 places similar upper bound on the iteration complexity for $\mathbb M$, but it still remains impractical. 
-            \par
-            Interestingly, the new termination criterion C2 gives improvements on the complexity of inner loop $\mathbb M$, outer loop $\mathbb A$, and the relative error sequence $(\delta_k)_{k \ge0}$ for $\mathbb M$.
+            Besides Definition \ref{def:catalyst-termination-c1}, \ref{def:catalyst-termination-c2}, the ``Fixed Budget" termination criterion terminates $\mathbb M$ after a fixed number of iteration given termination criterion C1, C2.
+            Unfortunately the bound is often too loose making it impractical. 
+            \par
+            Interestingly, the new termination criterion C2 improves the complexity of inner loop $\mathbb M$ and outer loop $\mathbb A$, and it gives a tighter bound with fewer assumptions. 
             The theorems and commentaries that follow will illustrate. 
@@
             \end{definition}
-            \begin{assumption}[Warm start conditions for relative error C2]
-            \;\label{prop:warm-start-with-c2}\\ 
-            Assume
-
+            \begin{assumption}[Warm start conditions for the inner loop using C2]\label{ass:warm-start-c2}\;\\
+                For minimization sub problem $\mathcal M^{\kappa^{-1}}_F(z; y_k)$ solved by $\mathbb M$, we use the following warm start condition for $z_{k, 0}$ under termination criterion C2 (Definition \ref{def:catalyst-termination-c2}):
+                \begin{enumerate}
+                    \item If $F$ is smooth then choose $z_k = y_k$. 
+                    \item Else it's composite, define $f_k(x) = f(x) + \frac{\kappa}{2}\Vert x - y_k\Vert^2$ and do 
+                    \begin{align*}
+                        z_{k, 0} = \hprox_{\eta g}\left(
+                            y_k - \eta\nabla f_\kappa(y_k)
+                        \right) \quad \text{with } \eta = 1/(\kappa + L). 
+                    \end{align*}
+                \end{enumerate}
             \end{assumption}
-
-            \begin{theorem}[Outer loop complexity under criterion C2]\; \label{theorem:catalyst2-outer-loop}\\
+            \begin{remark}
+                See pg 13 of Lin et al. for more detail about warm starting strategies of $\mathbb M$ under Termination criterion C1. 
+            \end{remark}
+
+            \begin{theorem}[Outer loop complexity under criterion C2]\label{thm:catalyst2-outer-comp}
                 For the iterates $(x_k)_{k \ge 0}$ generated by algorithm in Definition \ref{def:catalyst-all-in-one}, we have 
@@
             \end{remark}
-            \begin{theorem}{Inner loop complexity with relative error C2}
-
+            \begin{theorem}[Inner loop complexity with relative error C2]\label{thm:inner-loop-comp-c2}\; \\
+                Consider $\mathbb M$ under the settings of Assumption \ref{ass:linear-convergence-inner-loop} and Assumption \ref{ass:warm-start-c2}, let the relative error sequence $(\delta_k)_{k \ge0}$ be given by Theomrem \ref{thm:catalyst2-outer-comp}, and let $\mathbb A$ be defined as in Definition \ref{def:catalyst-all-in-one}.
+                Then the sequence $(z_{k, t})_{t \ge 0}$ generated by $\mathbb M$ has $T_{k + 1} = \min\left\lbrace t \ge 0 : z_{k, t} \in \widetilde{\mathcal J}_{\kappa^{-1}F}^\delta y_k\right\rbrace$ satisfies:
+                \begin{align*}
+                    T_{k + 1} &\le \tau_{\mathbb M}^{-1}
+                    \log\left(
+                        4 C_{\mathbb M}\frac{L + \kappa}{\kappa}\frac{2 - \sqrt{q}}{q}
+                    \right) \quad \text{when}\quad \mu > 0, 
+                    \\
+                    T_{k + 1} &\le \tau_{\mathbb M}^{-1}
+                    \log\left(
+                        4 C_{\mathbb M}\frac{L + \kappa}{\kappa}(k + 2)^2
+                    \right) \quad \text{when}\quad \mu = 0.  
+                \end{align*}
             \end{theorem}
-
+            \begin{remark}
+                This is Corollary 16 in Lin et al. \cite{lin_catalyst_2018} but phrased in our notations. 
+            \end{remark}
+            Using Theorem \ref{thm:inner-loop-comp-c2}, \ref{thm:inner-loop-comp-c2}, it's possible to derive the total complexity of the algorithm as counted by the total number of iterations of $\mathbb M$ at the $k$ iteration of $\mathbb A$.
+            Stated in Proposition 17, 18 in Lin et al. \cite{lin_catalyst_2018} is the following results.
+            The total number of iteration $N_{\mathbb M}$ experienced by $\mathbb M$ for $\mathbb A$ to produce $x_k$ such that $F(x_k) - F^* \le \epsilon$ when using termination criterion C2, warm start and error sequence strategies \ref{thm:catalyst2-outer-comp} has:
+            \begin{enumerate}
+                \item $N_{\mathbb M} \le \widetilde{\mathcal O}\left(\tau_{\mathbb M}^{-1}\sqrt{\kappa/\epsilon}\log(\epsilon^{-1})\right)$ if $\mu = 0$, 
+                \item $N_{\mathbb N}\le \widetilde{O}\left((\tau_{\mathbb M}\sqrt{q})^{-1}\log(\epsilon^{-1})\right)$ if $\mu > 0$. 
+            \end{enumerate}
+            \par
             The key improvement here compared to using absolute inexactness for $\mathbb M$ as stated by Theorem \ref{thm:err-seq-outer-s-cnvx}, \ref{thm:erro-seq-outer-cnvx} is that $(\delta_k)_{k \ge0}$ doesn't require knowledge on $F^*$.

### 2025-01-27 Notebook LaTEX/Proposal/presentation.tex
>w<, fixing cringe shit
>w<, changes and fixes

@@
                 \item It's an early attempt at putting accelerated inexact proximal point method into a practical setting. 
-                \item It finds application in machine learning and it accelerates the convergence of Variance Reduced Method (A type of incremental method that is not slower than the exact counter part).
+                \item It finds application in machine learning, and it accelerates the convergence of Variance Reduced Method (A type of incremental method that is not slower than the exact counterpart).
                 \item It demonstrates crucial ideas on how prove convergence rate where the evaluation of proximal point method is inexact in the convex settings. 
@@
                 \item Equation (2), (3), (4) in \cite{chambolle_convergence_2015} is a similar triangle formulation of FISTA with $\mu = 0$. 
-                \item see (3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022} for graphical visualization of similar triangle form. 
+                \item See (3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022} for graphical visualization of similar triangle form. 
             \end{enumerate}
@@
         \end{frame}
-        \begin{frame}{$\mu$ estimation graph by FR-WAPG}
+        \begin{frame}{FR-WAPG $\mu$ estimation graph}
             FR-WAPG estimates the following for $\mu$ during its execution: 
@@
             \begin{enumerate}
-                \item $M, N$ are constants. $A \in \RR^{M\times N}$ ahs i.i.d random entries from a standard normal distribution. 
+                \item $M, N$ are constants. $A \in \RR^{M\times N}$ has i.i.d random entries from a standard normal distribution. 
                 \item $L, \mu$, are estimated by $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$. 
                 \item The synthetic solution is $x^+ = [1\; -1\; 1 \; \cdots ]^T \in \RR^N$ and $b = Ax^+ \in \RR^M$.
-                \item $x_0\in \RR^N$ is the initial guess with i.i.d randomed variable from a standard normal distributions. Same initial guess shared by FR-WAPG, V-FISTA, M-FISTA. 
+                \item $x_0\in \RR^N$ is the initial guess with i.i.d random variable from a standard normal distribution. Same initial guess shared by FR-WAPG, V-FISTA, M-FISTA. 
             \end{enumerate}
@@
         \begin{frame}{Nesterov's idea of strong convexity transfer}
-            There is one detail that our R-WAPG doesn't incorperate on all Euclidean variants of FISTA. 
+            There is one detail that our R-WAPG doesn't incorporate on all Euclidean variants of FISTA. 
             We consider this a minor augmentation for the future. 
@@
                 \item In Nesterov's 2013 paper \cite{nesterov_gradient_2013}, he considers accelerated  minimization problem $\phi = f + g$ with $f$ $L_f$ smooth and $g$ being $\mu_g \ge 0$ strongly convex.
-                \item Algorithm 5, Chambolle, Pock \cite{chambolle_introduction_2016} captures several variants of FISTA and it assumes that $F = f + g$ where $f, g$ has strong convexity constant $\mu_f \ge 0, \mu_g \ge 0$ respective so $F$ is $\mu := \mu_f + \mu_g \ge 0$ strongly convex.
+                \item Algorithm 5, Chambolle, Pock \cite{chambolle_introduction_2016} captures several variants of FISTA, and it assumes that $F = f + g$ where $f, g$ has strong convexity constant $\mu_f \ge 0, \mu_g \ge 0$ respective so $F$ is $\mu := \mu_f + \mu_g \ge 0$ strongly convex.
             \end{enumerate}
-            Fast linear convergence is possible if any one of $f, g$ of the function is strongly convex but this is not yet a prediction of R-WAPG. 
+            Fast linear convergence is possible if any one of $f, g$ of the function is strongly convex, but this is not yet a prediction of R-WAPG. 
         \end{frame}
@@
         \begin{frame}{Outer loop complexity, strong convex case}
+            Ths is Theorem 3.1 in Lin et al. \cite{lin_universal_2015}. 
             \begin{theorem}[]\label{thm:err-seq-outer-s-cnvx}
@@
         \begin{frame}{Outer loop complexity, convex but not strongly convex case}
+            This is Theorem 3.3 from Lin et al. \cite{lin_universal_2015}. 
             \begin{theorem}[]\label{thm:erro-seq-outer-cnvx}
@@
         \begin{frame}{Inner loop complexity, absolute errors}
+            The followings are Proposition 3.2, 3.4 from Lin et al. \cite{lin_universal_2015}. 
             \begin{proposition}[Inner loop complexity strongly convex]\label{prop:inner-loop-complexity-s-cnvx}
@@
             \end{proposition}
-            \begin{proposition}[Inner loop, context but not strongly convex]\label{prop:inner-loop-complexity-cnvx}
+            \begin{proposition}[Inner loop, convex but not strongly convex]\label{prop:inner-loop-complexity-cnvx}
             {\footnotesize
@@
                     \item $\mathbb M$ has linear convergence rate as specified in Assumption \ref{ass:linear-convergence-inner-loop}, 
-                    \item the initial guess for $\mathbb M$ is $z_{0, k} = x_{k - 1}$, 
-                    \item $F$ has bounded level set.
+                    \item the initial guess for $\mathbb M$ is $z_{0, k} = x_{k - 1}$ and $F$ has bounded level set.
                 \end{enumerate}
@@
 
-        \begin{frame}{Aggregated complexity}
+        \begin{frame}{Total complexity}
             We count $m$, the number of iteration experienced by $\mathbb M$ for the $k$ th iteration of $\mathbb A$. 
@@
                 Let $F:\RR \rightarrow \overline \RR$ be $\mu \ge 0$ strongly convex and closed. 
-                Let the initial estimate be $x_0 \in \RR^n$, fix parameters $\kappa > 0$ and $\alpha_0 \in (0, 1]$. 
+                Let the initial estimate be $x_0 \in \RR^n$, fix parameters $\kappa > 0$ and $\alpha_0 = \sqrt{q}$ where $q = \mu/(\kappa + \mu)$. 
                 Let $(\delta_k)_{k \ge 0}$ be an absolute error sequence chosen for the evaluation for inexact proximal point method. 
@@
                         \\
-                        & \text{find } \alpha_k \in (0, 1) \text{ such that } \alpha_k^2 = (1 - \alpha_k)\alpha_{k - 1}^2 + (\mu/(\mu + \kappa))\alpha_k,
+                        & \text{find } \alpha_k \in (0, 1) \text{ such that } \alpha_k^2 = (1 - \alpha_k)\alpha_{k - 1}^2 + q\alpha_k,
                         \\
@@
         \end{frame}
-        \begin{frame}{Outerloop complexity under relative errors}
-            \begin{theorem}[Outer loop complexity under criterion C2]\label{theorem:catalyst2-outer-loop}
+        \begin{frame}{Outer loop complexity under relative errors}
+            \begin{theorem}[Outer loop complexity under criterion C2]\label{thm:catalyst2-outer-comp}
                 For the iterates $(x_k)_{k \ge 0}$ generated by algorithm in Definition \ref{def:catalyst-relative}, we have 
@@
             \end{remark}
-            Observe that it does't require knowledge about $F^*$. 
+            Observe that it doesn't require knowledge about $F^*$. 
         \end{frame}
-
-    \subsection{Direction of future works}
+        \begin{frame}{Inner loop warm start under criterion C2}
+            \begin{assumption}[Warm start conditions for the inner loop using C2]\label{ass:warm-start-c2}
+                For minimization sub problem $\mathcal M^{\kappa^{-1}}_F(z; y_k)$ solved by $\mathbb M$, we use the following warm start condition for $z_{k, 0}$ under termination criterion C2 (Definition \ref{def:catalyst-termination-c2}):
+                \begin{enumerate}
+                    \item If $F$ is smooth then choose $z_k = y_k$. 
+                    \item Else it's composite, define $f_k(x) = f(x) + \frac{\kappa}{2}\Vert x - y_k\Vert^2$ and do 
+                    \begin{align*}
+                        z_{k, 0} = \hprox_{\eta g}\left(
+                            y_k - \eta\nabla f_\kappa(y_k)
+                        \right) \quad \text{with } \eta = 1/(\kappa + L). 
+                    \end{align*}
+                \end{enumerate}
+            \end{assumption}
+            \begin{remark}
+                See pg 13 of Lin et al. for more detail about warm starting strategies of $\mathbb M$ under Termination criterion C1. 
+            \end{remark}
+        \end{frame}
+        \begin{frame}{Inner loop complexity under C2}
+            \begin{theorem}[Inner loop complexity with relative error C2]\label{thm:inner-loop-comp-c2}
+                Consider $\mathbb M$ under the settings of Assumption \ref{ass:linear-convergence-inner-loop} and Assumption \ref{ass:warm-start-c2}, let the relative error sequence $(\delta_k)_{k \ge0}$ be given by Theorem \ref{thm:catalyst2-outer-comp}, and let $\mathbb A$ be defined as in Definition \ref{def:catalyst-relative}.
+                Then the sequence $(z_{k, t})_{t \ge 0}$ generated by $\mathbb M$ has $T_{k + 1} = \min\left\lbrace t \ge 0 : z_{k, t} \in \widetilde{\mathcal J}_{\kappa^{-1}F}^\delta y_k\right\rbrace$ satisfies:
+                \begin{align*}
+                    T_{k + 1} &\le \tau_{\mathbb M}^{-1}
+                    \log\left(
+                        4 C_{\mathbb M}\frac{L + \kappa}{\kappa}\frac{2 - \sqrt{q}}{q}
+                    \right) \quad \text{when}\quad \mu > 0, 
+                    \\
+                    T_{k + 1} &\le \tau_{\mathbb M}^{-1}
+                    \log\left(
+                        4 C_{\mathbb M}\frac{L + \kappa}{\kappa}(k + 2)^2
+                    \right) \quad \text{when}\quad \mu = 0.  
+                \end{align*}
+            \end{theorem}
+            \begin{remark}
+                This is Corollary 16 in Lin et al. \cite{lin_catalyst_2018} but phrased in our notations. 
+            \end{remark}
+        \end{frame}
+        \begin{frame}{Total complexity under C2}
+            The total number of iteration $N_{\mathbb M}$ experienced by $\mathbb M$ for $\mathbb A$ to produce $x_k$ such that $F(x_k) - F^* \le \epsilon$ when using termination criterion C2, warm start and error sequence strategies in Theorem \ref{thm:catalyst2-outer-comp} has:
+            \begin{enumerate}
+                \item $N_{\mathbb M} \le \widetilde{\mathcal O}\left(\tau_{\mathbb M}^{-1}\sqrt{\kappa/\epsilon}\log(\epsilon^{-1})\right)$ if $\mu = 0$, 
+                \item $N_{\mathbb N}\le \widetilde{O}\left((\tau_{\mathbb M}\sqrt{q})^{-1}\log(\epsilon^{-1})\right)$ if $\mu > 0$. 
+            \end{enumerate}
+            In addition, termination criterion C2 has advantages: 
+            \begin{enumerate}
+                \item $\delta_k$ doesn't requite $F^*$. 
+                \item Doesn't require bounded level set assumption for inner loop complexity bound. 
+                \item Generalize to non-convex settings which was also the focus of Paquette's paper on Catalyst \cite{paquette_catalyst_2018}. 
+            \end{enumerate}
+        \end{frame}
+    \subsection{Future works for Catalyst Acceleration}
 

### 2025-01-27 Notebook LaTEX/Proposal/proposal.tex
>w<, changes and fixes

@@
     \subsection{The second Catalyst Acceleration paper}\label{ssec:catalyst-second-paper}
-        Lin et al.'s second paper on Catalyst Acceleration \cite{lin_catalyst_2018} describes the new option of relative termination criterion (which we stated here in Definition \ref{def:catalyst-termination-c2}) for $\mathbb M$ to evaluate the inexact solutions of $\mathcal J_{\kappa^{-1}F}^{\epsilon_k} y_k$.
+        Lin et al.'s second paper on Catalyst Acceleration \cite{lin_catalyst_2018} describes the new option of relative termination criterion (which we stated here in Definition \ref{def:catalyst-termination-c2}) for $\mathbb M$ to evaluate the inexact solution of $\mathcal J_{\kappa^{-1}F}^{} y_k$.
         The relative termination condition has advantages: it gives easier convergence analysis, it doesn't need knowledge of $F^*$, and it can generalize to the nonconvex case. 
-        In addition, they also improved warm start strategies for $\mathbb M$ at the end of Section 3. 
+        In addition, they also improved warm start strategies for $\mathbb M$ at the end of Section 3 for absolute termination criterion in Definition \ref{def:catalyst-termination-c1}.
         Both these ideas together provides a tighter and easier complexity analysis for the Catalyst Acceleration. 
         \par
-        We summarize these innovations in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018} in this section. 
+        In this section, we summarize results regarding criterion C2 in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018}. 
         The following definition defines relative termination criteria for $\mathbb M$. 
@@
             \begin{theorem}[Inner loop complexity with relative error C2]\label{thm:inner-loop-comp-c2}\; \\
-                Consider $\mathbb M$ under the settings of Assumption \ref{ass:linear-convergence-inner-loop} and Assumption \ref{ass:warm-start-c2}, let the relative error sequence $(\delta_k)_{k \ge0}$ be given by Theomrem \ref{thm:catalyst2-outer-comp}, and let $\mathbb A$ be defined as in Definition \ref{def:catalyst-all-in-one}.
+                Consider $\mathbb M$ under the settings of Assumption \ref{ass:linear-convergence-inner-loop} and Assumption \ref{ass:warm-start-c2}, let the relative error sequence $(\delta_k)_{k \ge0}$ be given by Theorem \ref{thm:catalyst2-outer-comp}, and let $\mathbb A$ be defined as in Definition \ref{def:catalyst-all-in-one}.
                 Then the sequence $(z_{k, t})_{t \ge 0}$ generated by $\mathbb M$ has $T_{k + 1} = \min\left\lbrace t \ge 0 : z_{k, t} \in \widetilde{\mathcal J}_{\kappa^{-1}F}^\delta y_k\right\rbrace$ satisfies:
@@
             Stated in Proposition 17, 18 in Lin et al. \cite{lin_catalyst_2018} is the following results.
-            The total number of iteration $N_{\mathbb M}$ experienced by $\mathbb M$ for $\mathbb A$ to produce $x_k$ such that $F(x_k) - F^* \le \epsilon$ when using termination criterion C2, warm start and error sequence strategies \ref{thm:catalyst2-outer-comp} has:
+            The total number of iteration $N_{\mathbb M}$ experienced by $\mathbb M$ for $\mathbb A$ to produce $x_k$ such that $F(x_k) - F^* \le \epsilon$ when using termination criterion C2, warm start and error sequence strategies in Theorem \ref{thm:catalyst2-outer-comp} has:
             \begin{enumerate}

### 2025-01-28 Notebook LaTEX/Proposal/presentation.tex
>w<, changes

@@
 \setbeamertemplate{footline}[frame number] % ADD PAGE NUMBERS ON BOTTOM. 
+\setbeamertemplate{blocks}[rounded][shadow=true]
+% \setbeamercolor{block title}{bg=cyan,fg=black} % CHANGE THE BLOCK STYLE IN BEAMER. 
+% \setbeamercolor{block body}{bg=lime,fg=black} % CHANGE THE BLOCK STYLE IN BEAMER.
+
 % BIB STYLES SETTINGS ----------------------------------------------------------
@@
             \end{enumerate}
+            These results are stated in Section 3.2 in Lin et al. \cite{lin_universal_2015}. 
         \end{frame}
@@
     \subsection{Future works for Catalyst Acceleration}
+        \begin{frame}{Comments on Catalyst from Necoara et al. }
+            Necoara et al.
+\cite{necoara_linear_2019} considered extending the linear convergence results for problem $f^* = \min_{x \in X} f(x)$ with $f: X \subseteq \RR^n \rightarrow \RR$ and $X$ closed and convex.
+            They characterize conditions: 
+            \begin{enumerate}
+                \item Quasi-strong convexity, 
+                \item Quadratic under approximation, 
+                \item Quadratic gradient growth,
+                \item quadratic functional growth, 
+                \item and Global error bound conditions. 
+            \end{enumerate}
+            Discussion at the end of their is summarized here as: 
+            \begin{block}{Future works}
+                Extend our results for variance reduced incremental methods such as the Catalyst Framework. 
+            \end{block}
+
+        \end{frame}
+        \begin{frame}{Our questions on Catalyst Acceleration}
+            \begin{block}{A key detail about Catalyst}
+                The smoothness assumption is baked into Assumption \ref{ass:linear-convergence-inner-loop}, where it states that the $\mathbb M$ needs to have linear convergence rate. 
+            \end{block}
+            All VRMs method in the literature requires Lipschitz smoothness and strong convexity to achieve linear convergence rate. 
+            No linear convergent first order algorithm exists for all strong convex function by Theorem 2.1.5 in Nesterov's book \cite{nesterov_lectures_2018}. 
+            Hence, here is our question: 
+            \begin{alertblock}{Our question}
+                Solving inexact proximal point doesn't necessarily need smoothness assumption on $F$ so what if we Assumption \ref{ass:linear-convergence-inner-loop} is false? 
+            \end{alertblock}
+            Next slide we explain why the answer is not trivial and why it's interesting. 
+        \end{frame}
+        \begin{frame}{The answer to our question is nontrivial}
+            Without smoothness assumption on $F$, the following considerations apply. 
+            \begin{enumerate}
+                \item $\mathbb A$ optimizes inexact Moreau Envelope $\mathcal M^*_{\kappa^{-1}, F}(y)$ which is smooth and strongly convex if $F$ is convex hence the $\mathcal O(1/\sqrt{k})$ lower bound of Theorem 3.2.1 \cite{nesterov_lectures_2018} complexity for all convex first order optimization doesn't apply for the total complexity.
+                \item Instead, Theorem 2.1.7 \cite{nesterov_lectures_2018} applies and the lower complexity bound $\mathbb A$ is $\mathcal O(1/k^2)$. 
+                \item Linear convergence of $\mathbb M$ Theorem 2.1.17 fails instead Theorem 3.2.5 applies and the lower bound is $\mathcal O(1/k)$. 
+            \end{enumerate}
+            We note that the question has practical importance because the method of subgradient descent with Polyak stepsizes are optimal for Smooth, strongly convex, and smooth plus strongly convex function on a compact domain.
+See Hazan and Kakade\cite{hazan_revisiting_2022}.
+        \end{frame}
 
 \section{References}
-    \begin{frame}{Citation examples}
-        Citation examples \cite{chambolle_convergence_2015}
-    \end{frame}
-
+    % \begin{frame}{Citation examples}
+    %     Citation examples \cite{chambolle_convergence_2015}
+    % \end{frame}
     \begin{frame}[allowframebreaks]{References}

### 2025-01-28 Notebook LaTEX/Proposal/presentation.tex
>w<, small changes sync

@@
         \begin{frame}{Notations and Variance Reduced Methods}
+            \begin{block}{Catalyst notations}
                 Denotes
@@
                 \end{enumerate}    
+            \end{block}
             The class of variance reduced methods are often used for $\mathbb M$. 
+            They are examples of incremental methods. 
             Major examples of VRMs include SVRG by Xiao, Zhang \cite{xiao_proximal_2014}, Finito by Defazio et al.
@@
             \end{enumerate}
-            Discussion at the end of their is summarized here as: 
-            \begin{block}{Future works}
-                Extend our results for variance reduced incremental methods such as the Catalyst Framework. 
-            \end{block}
+            Discussion about Catalyst future works is summarized here: 
+            \begin{alertblock}{Future works}
+                Extend linear convergence of accelerated gradient for variance reduced incremental methods such as the Catalyst Framework into a weaker settings. 
+            \end{alertblock}
 
         \end{frame}
-        \begin{frame}{Our questions on Catalyst Acceleration}
+        \begin{frame}{Our question on Catalyst Acceleration}
             \begin{block}{A key detail about Catalyst}

### 2025-02-01 Notebook LaTEX/Proposal/presentation.tex
>w<, changes

@@
             \end{definition}
-            The technique is widespread in the literatures and it's used to derive the convergence rate of acceleration on first order method, and the numerical algorithm itself.
+            The technique is widespread in the literatures, and it's used to derive the convergence rate of acceleration on first order method, and the numerical algorithm itself.
 It is a two birds one stone technique.
@@
         \begin{frame}{Outer loop complexity, strong convex case}
-            Ths is Theorem 3.1 in Lin et al. \cite{lin_universal_2015}. 
+            This is Theorem 3.1 in Lin et al. \cite{lin_universal_2015}. 
             \begin{theorem}[]\label{thm:err-seq-outer-s-cnvx}

### 2025-02-03 Notebook LaTEX/Proposal/proposal.tex
>w<, changes
>w<, a lot of changes

@@
         \fontfamily{ptm}\selectfont 
-        First Order Nonsmooth Optimization: 
-        Unifying Nesterov's acceleration and its applications
+        Nesterov's First Order Method Accelerations: Unifications, Applications  and Numerial Experiments
     }
@@
             Furthermore, Nesterov was not the only person who thought about it.
-            In 
-            Algorithm 5, Chambolle, Pock \cite{chambolle_introduction_2016} captures several variants of FISTA and it assumes that $F = f + g$ where $f, g$ has strong convexity constant $\mu_f \ge 0, \mu_g \ge 0$ respective so $F$ is $\mu := \mu_f + \mu_g \ge 0$ strongly convex.
+            In Algorithm 5, Chambolle, Pock \cite{chambolle_introduction_2016} captures several variants of FISTA, and it assumes that $F = f + g$ where $f, g$ has strong convexity constant $\mu_f \ge 0, \mu_g \ge 0$ respective so $F$ is $\mu := \mu_f + \mu_g \ge 0$ strongly convex.
+            \par
+            Upon first inspection and preliminary readings, we lay out the followings that may contribute to include strong convexity in the non-smooth part into our R-WAPG framework. 
+            The R-WAPG sequence $\alpha_k, \rho_k$ will have to describe the sequence in Chambolle, Pock \cite{chambolle_introduction_2016} Algorithm 5 which has 
+            \begin{align*}
+                q \alpha_{k + 1}^2 &= (1 - \alpha_{k + 1})q\alpha_k^2 + q \alpha_{k + 1}^2. 
+            \end{align*}
+            Where $q = L^{-1}(\mu_f + \mu_g)/(1 + L^{-1}\mu_g)$. 
+            Additionally, observe that in the special case where $f \equiv 0$, then proximal gradient becomes proximal point on the strongly convex objective $\mu_g \ge0$ alone and its convergence rate is included in the outer loop convergence analysis in the Catalyst Acceleration Framework by Lin et al.
+\cite{lin_universal_2015}, this provided us with a hint on an estimating sequence approach.
+            Of course, Lemma \ref{thm:prox-grad-ineq} requires a complete rework to include $\mu_g \ge0$. 
+            The recursive quantity $R_k$ would also require a complete rework because we invented the quantity $R_k$ just so the proof of Proposition \ref{prop:stepwise-lyapunov} falls through. 
+            The quantity is obtained from the Nesterov's estimating sequence of APG, to include such a change, the estimating sequence required to engineer $R_k$, which is the recursive quantity will also require rework.
+            The only part that may not require rework is the Definition \ref{def:stepwise-wapg} because the R-WAPG sequence is generic. 
+            We are quite certain about these required changes to achieve the open question because we invented R-WAPG.
 
@@
             It's important to note that the upper complexity bounds are much better, and it doesn't require bounded level set compared to Theorem \ref{prop:inner-loop-complexity-cnvx}.      
+            \todoinline{Show that there are other literatures that may also be relevant to this research question. }   
     \subsection{Potential future research}\label{ssec:catalyst-future}
@@
             We note that, their idea of extension can be applied to inner loop $\mathbb M$, or out loop $\mathbb A$, either, or both. 
+            \par
+            Finally, it's worth noting that in the years before and after Necoara et al.'s paper and Catalyst, there were parallel developments around the ideas of extending Nesterov's accelerations and Catalyst to the nonconvex settings.
+            Paquette et al.
+\cite{paquette_catalyst_2018} were inspired by \cite{ghadimi_accelerated_2016} and showed that the Catalyst algorithm with a different Termination criterion C2 that is based on the gradient (see equation (13), (14) in their paper) can adapt to nonconvex settings to convergence on the norm of the gradient.
+            However, it's at the expense of one additional evaluation of the proximal point method, and it requires knowledge of the function value for the outer loop. 
+            They used an analogous inner loop complexity to Assumption \ref{ass:linear-convergence-inner-loop} which is stated as Equation (16) in their paper. 
+            Convergences to stationarity, convergence of iterates are not claimed. 
+            \par
+            Attaining stronger convergence results on iterates, convergence to stationarity and function value for Nesterov's accelerated gradient methods in general requires intense amount of works. 
+            In fact, these type of convergences remains nontrivial in the convex settings in general. 
+            See Bauchke et al. for example, when the minimizer of $F$ doesn't exist. 
+            To limit the scope, we focus on Nesterov's acceleration which differs from inertial momentum from Polyak.
+            The relationship between Polyak and Nesterov momentum acceleration remains a non-trivial topics. 
+            In fact, both type of acceleration can present at the same time, see 
+            \par
+            There are three pillars that supported Catalyst Accelerations: 
+            \begin{enumerate}
+                \item Variance reduced algorithm with known complexities. 
+                \item Theories of inexact proximal point method and their convergences. 
+                \item Nesterov's accelerations and with inexact gradient oracles. 
+            \end{enumerate}
+
+            \todoinline{
+                Recent development regarding the theories of accelerated proximal point method. 
+                \begin{enumerate}
+                    \item Paquette et al. \cite{paquette_catalyst_2018}. 
+                    \item Ghadimi and Lan, ``Accelerated gradient methods for nonconvex nonlinear and stochastic programming". 
+                    \item ``Study of the behavior of Nesterov Accelerated Gradient in a nonconvex setting: the strongly quasar convex case."
+                    \item Bu, Mesbashi ``A Note on Nesterov's Accelerated Method in Nonconvex Optimization: a Weak Estimate Sequence Approach''. 
+                    \item Bauscke et al. ``Applying FISTA to optimization problems (with or) without minimizers"
+                \end{enumerate}
+            }
         \subsubsection{Our ideas on future works of Catalyst Acceleration}
-            One intriguing detail in the Catalyst framework eluded us. 
-            It may not be obvious to the readers, so we shall elucidate. 
+            Restricting ourselves to the convexity, this is our question: 
+            \begin{quote}
+                What if Assumption \ref{ass:linear-convergence-inner-loop} is false? 
+            \end{quote}
+            This is a detail in the Catalyst framework, and it may not be obvious to the readers that the complexity assumption is sufficient to accommodates objective functions $F$ to be the class of all $L$-Lipschitz smooth function.
+            The entire section will: 
+            \begin{enumerate}
+                \item elucidate the relation of $F$ being $L$-Lipschitz smooth and Assumption \ref{ass:linear-convergence-inner-loop}; 
+                \item show that removing the assumption will yield non-trivial answers for the complexity analysis of Catalyst as a whole by existing theorems in the Nesterov's lower bound complexity results for black box smooth/nonsmooth objectives;
+                \item show that some other the existing literatures that seems to hold the answer but actually doesn't address the question; 
+                \item discuss potential relevant literatures to addressing the question. 
+            \end{enumerate}
             \par
             The concern starts by considering the necessary assumption in VRMs. 
-            Defazio et al.\cite{defazio_saga_2014} SAGA, Finito et al.
+            Defazio et al.
+\cite{defazio_saga_2014} SAGA, Finito et al.
 \cite{defazio_finito_2014} requires Lipschitz continuous gradient on each individual $f_i$ in the objective function $F = \sum_{i = 1}^n f_i$.
@@
             \par
-            From a complexity theoretical point of view, Catalyst acceleration didn't attempt at narrowing the lower complexity bound bounds for functions that are convex and nonsmooth and lack of any exact proximal oracle.
+            From a complexity theory point of view, Catalyst acceleration didn't attempt at narrowing the lower complexity bound for functions that are convex and nonsmooth and lack of any exact proximal oracle.
             It is absolutely possible that, for any black box nonsmooth optimization problem, the same lower bound convergence rate $\mathcal O\left(1/\sqrt{k}\right)$ as stated in Theorem 3.2.1 in Nesterov's book \cite{nesterov_lectures_2018} is true for Catalyst.
@@
             Whatever the true answer is, it's not obvious. 
-            So, here is what we think is worth investigating: 
+            So, here is the refined question: 
             \begin{quotation}
-                What if Assumption \ref{ass:linear-convergence-inner-loop} is false in the Catalyst Acceleration Framework? 
-                Would there exists any kind of regularization parameters $(\kappa_k)_{k \ge 0}$, error sequence $\epsilon_k$ such that the overall complexity still retains convergence rate equals or faster than $\mathcal O(1/\sqrt{k})$?
+                Suppose that the objective function $F$ is no $L$-Lipschitz continuous hence Assumption \ref{ass:linear-convergence-inner-loop} is false. 
+                If we assume that $F$ is any convex function (potentially nonsmooth and without any smooth parts), would there exist any kind of regularization parameters $(\kappa_k)_{k \ge 0}$, error sequence $\epsilon_k$ such that the overall complexity of Catalyst retains convergence rate equals or faster than $\mathcal O\left(1/\sqrt{k}\right)$ (The lower bound of all first order blackbox convex optimization)?
             \end{quotation}
-            Nobody has yet answered the question in the literature, but a brief searched showed that in Nesterov 2014 \cite{nesterov_universal_2015}, he considers the method of accelerated gradient for function with Holder continuous gradient.
-            If anything, there are some insight to be gained about Catalyst on this question on this work of his. 
-            It remains to be seemed why this detail is neglected when developing the Catalyst Acceleration framework. 
             If the answer is that it can be faster than the lower bound, then we had extended the Catalyst Framework, otherwise, it leads to the unintuitive result that lower bound $\mathcal O(1/\sqrt{k})$ still holds.
+            \par
+            To the best of our knowledge, nobody has yet answered the question directly in the literature, but we found some relevant literatures after some preliminary research. 
+            Nesterov 2014 \cite{nesterov_universal_2015}, he considers the method of accelerated gradient for function with Holder continuous gradient.
+            Nesterov continued and expanded on the results obtained by Devolder et al.
+2014 \cite{devolder_first-order_2014} on inexact oracles for blackbox optimizations which showed that the inexact oracle for Lipschitz smooth function can be viewed as exact for another perturbed function with Holder continuous gradient.
+            He proposed three first order algorithms where the last one, a variant of accelerated gradient method that converges optimally for all functions with Holder continuous gradient without knowing the Holder continuity constant in advance.
+            His work is not considered directly relevant to Catalyst because it's not yet obvious because it's missing an inexact accelerated proximal point, and he uses the theories of inexact oracles from a purely theoretical standpoint.
+            \par
+            In a more recent development, 
+            \par
+            Of course, the class of holder continuous gradient doesn't encapsulate the class of all convex function where inexact proximal point can be applied.
+
+            \todoinline{Add research plans and literature reviews here. }
+
+        \subsubsection{Applications for Catalyst Accelerations and its variants}
+            \todoinline{
+                Considers some specific applications of the Catalyst Acceleration method in the literatures. 
+            }
 

### 2025-02-04 Notebook LaTEX/Proposal/proposal.tex
>w<, changes

@@
 
-\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{true}
+\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{false}
 \input{presets/wang/input.tex}
@@
     The Nesterov's acceleration scheme which was originally proposed in 1983 \cite{nesterov_method_1983} is a celebrated first order method for solving the minimization problem. 
+    Here, NAG stands for Nesterov's Accelerated Gradient. 
+    It refers to a general class of momentum method where the gradient are evaluated on an extrapolated iterate using the previous two iterates. 
     Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
@@
         We define the Moreau Envelope at $y \in \RR^n$ to be $\mathcal M^*_{F,\beta^{-1}}(y) := \min_{x\in \RR^n} \mathcal M_F^{\beta^{-1}}(x; y)$ and the resolvent operator for subgradient of $F$ to be $\mathcal J_{\beta^{-1}F}$, i.e: which is also called the proximal operator.
+        \par
+        We invent this notations because there are no consistent notations in the literatures and several of the Catalyst papers all use dratically different notations.  
     \end{assumption}
@@
     Section \ref{ssec:catalyst-second-paper} introduces Lin et al.'s second paper \cite{lin_catalyst_2018} on Catalyst which considers the improved relative error condition stated in Definition \ref{def:catalyst-termination-c2}.
-    The relative error condition improves the overall complexity and inspired nonconvex gradient based 4WD Catalyst by Paquette \cite{paquette_catalyst_2018}.
+    The relative error condition improves the total complexity and inspired nonconvex gradient based 4WD Catalyst by Paquette et al. \cite{paquette_catalyst_2018}.
 
@@
         Inspired by accelerated proximal point Method (APPM) from Güler \cite{guler_new_1992}, and Inexact Proximal Point Method (IPPM) of Rockafellar 1976 \cite{rockafellar_monotone_1976}, Lin et al.
-\cite{lin_universal_2015} proposed a generic method taking inspirations from the convergence claims of (APPM) to accelerate Variance Reduced Method (VRM).
-        The fact that VRMs are incremental method that is not slower than full gradient descent in complexity is most relevant to our discussion. 
+\cite{lin_universal_2015} proposed a generic method taking inspirations from the convergence claims of APPM to accelerate Variance Reduced Method (VRM).
+        VRMs are incremental method that is not slower than full gradient descent in complexity. 
         See Gower's guide \cite{gower_variance-reduced_2020} for more information on variance reduced methods in machine learning. 
@@
         When it's stochastic, the theories focus on the expected optimality gap: $\mathbb E[F(x_k) - F^*]$. 
-        Let's assume for simplicity of discussion that it's deterministic, so we focus on: $F(x_k) - F^*$. 
+        Let's assume for simplicity of discussion that it's deterministic, so from now on we focus on: $F(x_k) - F^*$ instead. 
         \par 
         VRM stabilizes the estimate of gradient using information from all or a subset of gradients evaluated at previous iterates. 
-        In each iteration, it accesses the gradient of a few samples are used to attain a new estimate of the gradient with minimum additional calculations.  
+        In each iteration, it accesses the gradient of a few samples to attain a new estimate of the gradient with minimum additional calculations.  
         This gives better complexity than full gradient descent over all. 
@@
         With a fixed regularization parameter $\kappa > 0$, the outer loop (i.e: Definition \ref{def:lin-catalyst-original}) produces $(y_{k}, x_k)_{k \ge 1}$ denote it by $\mathbb A$. 
-        Typically, an iterative scheme (i.e: VRM) with a known complexity is assigned to find inexact proximal iterates $x_k \in {\mathcal J}_{\kappa^{-1}F}^{\epsilon_k} (y_{k - 1})$. 
+        Typically, an iterative scheme (e.g: VRM) with a known complexity finds inexact proximal iterates $x_k \in {\mathcal J}_{\kappa^{-1}F}^{\epsilon_k} (y_{k - 1})$. 
         We refer to it as the inner loop and denote it by $\mathbb M$. 
@@
         The choice of absolute error sequence $(\epsilon_k)_{k \ge 0}$ determines the iteration complexity of both $\mathbb A, \mathbb M$. 
-        The total iteration complexity of Catalyst counts the total number of inner loop iteration given  the number of outer loop iterations. 
+        The overall iteration complexity of Catalyst algorithm counts the total number of inner loop iteration at the $k$ th iteration of outer loop. 
         The term ``iteration complexity'' refers to the number of iterations required to achieve a desired accuracy, a concept related to the convergence rate of the algorithm. 
@@
             \end{remark}
-            The same convergence claims hold if smaller value of $\epsilon_k$ is taken, Theorem \ref{thm:err-seq-outer-s-cnvx}, \ref{thm:erro-seq-outer-cnvx} gives the largest possible absolute error sequence $(\epsilon_k)_{k \ge 0}$ such that the convergence claim holds.
+            Theorem \ref{thm:err-seq-outer-s-cnvx}, \ref{thm:erro-seq-outer-cnvx} gives the largest possible absolute error sequence $(\epsilon_k)_{k \ge 0}$ such that the convergence claim holds. 
             Of course, the results still hold if we take smaller values of $(\epsilon_k)_{k \ge0}$ as suggested by the above theorems, but it will increase the iteration complexity of $\mathbb M$. 
@@
             Observe the absolute error sequence $(\epsilon_k)_{k \ge 0}$ requires prior knowledge of $F^*$. 
-            It's poses no theoretical concerns, but it's of upmost practical concern since $F^*$ may not be accessible in practice prior to executing the algorithm. 
+            It's poses no theoretical concerns, but it's of upmost practical concern since $F^*$ is not accessible in practice prior to executing the algorithm. 
             In the work by Lin et al. \cite{lin_universal_2015}, the example algorithm given is in appendix item D.3 called Accelerated MISO Prox.
@@
             \begin{remark}
-                This assumption is legitimate for example VRMs discussed earlier. 
-                See Section \ref{ssec:catalyst-future} for concerns regarding this assumption. 
+                VRMs listed earlier statsifies this assumption. 
+                Details about the consequence of this assumption is in Section \ref{ssec:catalyst-future}. 
             \end{remark}
@@
             We are now ready to derive the convergence rate measured by the number of total iteration experience by $\mathbb M$. 
-            If $\mu > 0$, so Proposition \ref{prop:inner-loop-complexity-s-cnvx} gives total number of inner iteration is bounded by $m \le T_{\mathbb M}k$. 
+            Let $k \in \N$ be the total number of iterations experienced by the outer loop $\mathbb A$, let $m$ be the total number of iterations underwent by $\mathbb M$. 
+            If $\mu > 0$, then Proposition \ref{prop:inner-loop-complexity-s-cnvx} gives the total number of inner iteration upper bound: $m \le T_{\mathbb M}k$. 
             Substituting $k \ge m/T_{\mathbb M}$ into Theorem \ref{thm:err-seq-outer-s-cnvx}, it gives description of convergence rate of the algorithm measured by the total number of iteration experience by $\mathbb M$:
@@
             The last inequality is $T_{\mathbb M} < \widetilde{\mathcal O}(1/\tau_{\mathbb M})$ from Proposition \ref{prop:inner-loop-complexity-cnvx}.
-            In both cases, the convergence rate remains in the same big O class as measure by the total number of $\mathbb M$.
 
@@
             \par 
-            The following results are proved in Lin et al. second Catalyst paper \cite{lin_catalyst_2018}. 
+            The following results are proved in Lin et al. second Catalyst paper \cite{lin_catalyst_2018} in Lemma 2 and the discussions that follow it. 
             Given any $\epsilon > 0$ if $z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$, define the absolute inexact gradient mapping $\mathcal G_{\kappa^{-1}F}^\epsilon (z) := \kappa(x - z)$.
-            Then
+            Then it satsifies: 
             \begin{align*}
@@
             The above says that the gradient mapping $\mathcal G_{\kappa^{-1}F}^{\epsilon}(z)$ approximates the gradient of Moreau Envelope of $F$ at $x$. 
-            Similarly, if $z \in \widetilde{\mathcal J}_{\kappa^{-1}F}^\delta(x)$, define the relative inexact gradient mapping $\widetilde{\mathcal G}_{\kappa^{-1}F}^\delta(x) = \kappa(x - z)$, we have:
+            Similarly, if $z \in \widetilde{\mathcal J}_{\kappa^{-1}F}^\delta(x)$, define the relative inexact gradient mapping $\widetilde{\mathcal G}_{\kappa^{-1}F}^\delta(x) := \kappa(x - z)$, we have:
             \begin{align*}
@@
             \end{align*}
-            These results are instrumental to prove the convergence of $\mathbb M$ and giving convergence claim of $\mathbb A$ under certain assumption on $(\delta_k)_{k \ge 0}, (\epsilon_k)_{k \ge0}$.
-            For a more general development of characterizations of inexact oracles that is more comprehensive and rigorous, see Devolder et al. \cite{devolder_first-order_2014}. 
+            These results are instrumental to proving the convergence of $\mathbb M$ and giving convergence claim of $\mathbb A$ under certain assumption on $(\delta_k)_{k \ge 0}, (\epsilon_k)_{k \ge0}$.
+            For a more general, rigorous and comprehensive development of the characterizations on inexact oracles, see Devolder et al. \cite{devolder_first-order_2014}. 
             It's discusses a Nesterov accelerated algorithm using estimating sequence with inexact oracles. 
@@
             It's important to note that the upper complexity bounds are much better, and it doesn't require bounded level set compared to Theorem \ref{prop:inner-loop-complexity-cnvx}.      
-            \todoinline{Show that there are other literatures that may also be relevant to this research question. }   
+            % \todoinline{Show that there are other literatures that may also be relevant to this research question. }   
     \subsection{Potential future research}\label{ssec:catalyst-future}
@@
             \par
-            As a secondary objective, they introduced and stated the relations between several weakened characterizations of strong convexity on a closed convex set. 
-            Definition 1, 2, 3, 4, 5, introduced the ideas of: Quasi-strong convexity, Quadratic under approximation, Quadratic gradient growth, quadratic functional growth (recall that it was stated as a consequence of strong convexity in Lemma \ref{lemma:q-growth}), and Global error bound conditions.
-            \par
-            The content of their paper is very in-depth hence for our interests, we focus on their comments on the first Catalyst paper by Lin et al. \cite{lin_universal_2015}. 
+            As a secondary objective, they introduced the relations between several weaker characterizations of strong convexity on a closed convex set. 
+            Definition 1, 2, 3, 4, 5, introduced the ideas of: Quasi-strong convexity, Quadratic under approximation, Quadratic gradient growth, quadratic functional growth (recall that it was stated as a consequence of strong convexity in Lemma \ref{lemma:q-growth}), and Global Error bound conditions.
+            \par
+            For our interests, we focus on one of their comments on the Catalyst by Lin et al. \cite{lin_universal_2015}. 
             They said, and here we quote: 
@@
             Paquette et al.
-\cite{paquette_catalyst_2018} were inspired by \cite{ghadimi_accelerated_2016} and showed that the Catalyst algorithm with a different Termination criterion C2 that is based on the gradient (see equation (13), (14) in their paper) can adapt to nonconvex settings to convergence on the norm of the gradient.
-            However, it's at the expense of one additional evaluation of the proximal point method, and it requires knowledge of the function value for the outer loop. 
+\cite{paquette_catalyst_2018} were inspired by \cite{ghadimi_accelerated_2016} and showed that the Catalyst algorithm based on the gradient termination criterion analogous similar to C2 (see equation (13), (14) in their paper) can adapt to nonconvex settings and the norm of the gradient converges.
+            However, it's at the expense of one additional evaluation of the proximal point method, and it requires evaluating the function value once per outer loop iteration. 
             They used an analogous inner loop complexity to Assumption \ref{ass:linear-convergence-inner-loop} which is stated as Equation (16) in their paper. 
@@
             \par
-            Attaining stronger convergence results on iterates, convergence to stationarity and function value for Nesterov's accelerated gradient methods in general requires intense amount of works. 
-            In fact, these type of convergences remains nontrivial in the convex settings in general. 
-            See Bauchke et al. for example, when the minimizer of $F$ doesn't exist. 
+            Attaining stronger convergence results on iterates, convergence to stationarity and function value for NAG in general requires intense amount of works. 
+            In fact, these type of convergences claims are nontrivial in the convex settings in general as well. 
+            For example, see Bauchke et al. \cite{bauschke_applying_2020}, when the minimizer of $F$ doesn't exist. 
             To limit the scope, we focus on Nesterov's acceleration which differs from inertial momentum from Polyak.
-            The relationship between Polyak and Nesterov momentum acceleration remains a non-trivial topics. 
-            In fact, both type of acceleration can present at the same time, see 
-            \par
+            Polyak momentum (also referred to as heavy-ball inertia in the literatures) differs from Nesterov's acceleration by evaluating the gradient at the current iterates and does the extrapolation after the gradient evaluation.
+            The relationship between Polyak and Nesterov momentum acceleration remains non-trivial. 
+            In fact, both type of acceleration can present at the same time, see Maulén and Peypouquet \cite{maulen_speed_2023}.
+            It is sometime referred to as ``Hessian Damping" in the literatures.  
             There are three pillars that supported Catalyst Accelerations: 
@@
                 \item Theories of inexact proximal point method and their convergences. 
-                \item Nesterov's accelerations and with inexact gradient oracles. 
+                \item Nesterov's accelerations or some other first order acceleration method with inexact oracles. 
             \end{enumerate}
-
-            \todoinline{
-                Recent development regarding the theories of accelerated proximal point method. 
-                \begin{enumerate}
-                    \item Paquette et al. \cite{paquette_catalyst_2018}. 
-                    \item Ghadimi and Lan, ``Accelerated gradient methods for nonconvex nonlinear and stochastic programming". 
-                    \item ``Study of the behavior of Nesterov Accelerated Gradient in a nonconvex setting: the strongly quasar convex case."
-                    \item Bu, Mesbashi ``A Note on Nesterov's Accelerated Method in Nonconvex Optimization: a Weak Estimate Sequence Approach''. 
-                    \item Bauscke et al. ``Applying FISTA to optimization problems (with or) without minimizers"
-                \end{enumerate}
-            }
+            To the best of our interpretation of Catalyst is through the theories of inexact proximal point because NAG is not the unque option and other acceleration techniques can be used as well. 
+            For example, see Cai et al. \cite{cai_variance_2023} for inexact Halpern acceleration for solving variational inequalities. 
+            Therefore, the theories of inexact proximal point and the algorithm used to evaluate lies deeper in the theoretical aspect of Catalyst. 
+            \par
+            We now list new developments for Nesterov's acceleration in the nonconvex settings with stronge convergence claim. 
+            Preprint by Hermant et al. \cite{hermant_study_2024} present results that the fixed momentum variant of NAG has linear convergence  on the class of strongly quasar convex functions. 
+            Preprint by Bu, Mesbashi \cite{bu_note_2020} discusses using an idea called weak estimating sequence to show the linear convergence of NAG for weakly quasi-strongly-convex functions. 
+            The perspectives on how to generalize NAG to the nonconvex settings are diverse, and the issue is compounded by the fact that many variants of NAG also exist. 
+            \par
+            For theories of inexact proximal point method see Khanh et al. \cite{khanh_inexact_2025} for an algorithmic framework of inexact proximal point method on weakly convex function. 
+            The class of weakly convex function is particularly interesting because it has general convergence claim in Ghadimi and Lan \cite{ghadimi_accelerated_2016}, and in Chapter 4 of the book preprint by Recht and Wright \cite{recht_optimization_nodate}.
+            It's unclear how their convergence theories can be combined with NAG in the non-convex case, but it's worth investigating. 
+            % \todoinline{
+            %     Recent development regarding the theories of accelerated proximal point method. 
+            %     \begin{enumerate}
+            %         \item Paquette et al. \cite{paquette_catalyst_2018}. 
+            %         \item Ghadimi and Lan, ``Accelerated gradient methods for nonconvex nonlinear and stochastic programming". 
+            %         \item Hermant et al. ``Study of the behavior of Nesterov Accelerated Gradient in a nonconvex setting: the strongly quasar convex case."
+            %         \item Bu, Mesbashi ``A Note on Nesterov's Accelerated Method in Nonconvex Optimization: a Weak Estimate Sequence Approach''. 
+            %         \item Bauscke et al. ``Applying FISTA to optimization problems (with or) without minimizers".
+            %         \item Maulén and Peypouquet, ``A speed restart scheme for a dynamics with hessian-driven damping''. 
+            %         \item  Cai et al. ``Variance Reduced Halpern Iteration for Finite-Sum Monotone Inclusions"
+            %         \item Khanh at al. ``Inexact proximal methods for weakly convex functions''. 
+            %     \end{enumerate}
+            % }
         \subsubsection{Our ideas on future works of Catalyst Acceleration}
@@
             \end{quote}
-            This is a detail in the Catalyst framework, and it may not be obvious to the readers that the complexity assumption is sufficient to accommodates objective functions $F$ to be the class of all $L$-Lipschitz smooth function.
-            The entire section will: 
+            This is a detail in the Catalyst framework, and it may not be obvious to the readers that the complexity assumption is sufficient to accommodate objective functions $F$ to be the class of all $L$-Lipschitz smooth function.
+            The remaining of this section will: 
             \begin{enumerate}
                 \item elucidate the relation of $F$ being $L$-Lipschitz smooth and Assumption \ref{ass:linear-convergence-inner-loop}; 
-                \item show that removing the assumption will yield non-trivial answers for the complexity analysis of Catalyst as a whole by existing theorems in the Nesterov's lower bound complexity results for black box smooth/nonsmooth objectives;
-                \item show that some other the existing literatures that seems to hold the answer but actually doesn't address the question; 
-                \item discuss potential relevant literatures to addressing the question. 
+                \item show that removing the assumption will yield non-trivial answers for the total complexity of Catalyst because theorems Nesterov's lower bound complexity results for black box smooth/nonsmooth objectives can't be applied to Catalyst as a whole;
+                \item show that some other the existing literatures that seems to hold the answer but actually doesn't fully address the question; 
+                \item discuss literatures relevant to the question. 
             \end{enumerate}
@@
 \cite{defazio_finito_2014} requires Lipschitz continuous gradient on each individual $f_i$ in the objective function $F = \sum_{i = 1}^n f_i$.
-            Schmidt et al. \cite{schmidt_minimizing_2017} also requires Lipschitz smoothness for the non-smooth part of a composite objective. 
+            Schmidt et al. \cite{schmidt_minimizing_2017} also requires Lipschitz smoothness for the gradient of the objective function. 
             Xiao, Zhang, SVRG \cite{xiao_proximal_2014} requires Lipschitz gradient assumption as well. 
@@
             \par
-            A careful reader should realize that Assumption \ref{ass:linear-convergence-inner-loop} encapsulates the Lipschitz smoothness assumption of VRMs. 
-            Furthermore, such an assumption is optimistic for the complexity of $\mathbb M$. 
-            Recall that with Lipschitz smoothness and strong convexity, a lower bound of exponential rate of convergence is established by Theorem 2.1.13 in Nesterov's book \cite{nesterov_lectures_2018}.
-            Removing the smoothness assumption for $\mathbb M$, the lower bound on convergence rate of any first order algorithm becomes $\mathcal O(1/k)$ by Theorem 3.2.5 for nonsmooth function that is strongly convex.
-            \par
-            From a complexity theory point of view, Catalyst acceleration didn't attempt at narrowing the lower complexity bound for functions that are convex and nonsmooth and lack of any exact proximal oracle.
-            It is absolutely possible that, for any black box nonsmooth optimization problem, the same lower bound convergence rate $\mathcal O\left(1/\sqrt{k}\right)$ as stated in Theorem 3.2.1 in Nesterov's book \cite{nesterov_lectures_2018} is true for Catalyst.
-            Unfortunately it is absolutely nontrivial to see that is true because $\mathbb A$ optimizes Moreau Envelope $\mathcal M^*_{\kappa^{-1}F}(x)$ through inexact evaluation and the Moreau Envelope has Lipschitz gradient.
+            A careful reader will realize that Assumption \ref{ass:linear-convergence-inner-loop} encapsulates the Lipschitz smoothness assumption of VRMs because the proximal point sub-problem is smooth and strongly convex and lower bound from Theorem 2.1.13 from Nesterov's book \cite{nesterov_lectures_2018} applies and it has a linear convergence rate.
+            Removing the smoothness assumption of $F$, $\mathbb M$ solves subproblem $\mathcal M_{\kappa^{-1}F}(\cdot, y_k)$ which is only strongly convex.
+            Then, lower bound on convergence rate of any first order algorithm becomes $\mathcal O(1/k)$ by Theorem 3.2.5 from Nesterov's book. 
+            \par
+            From a complexity theory point of view, Catalyst acceleration didn't attempt at narrowing the lower complexity bound for functions that are convex and nonsmooth. 
+            At the same time, the theories of lower bound on blackbox optimization also cannot be applied for Catalyst Accelerations because they are based on different computational oracles. 
+            It is possible that, for any blackbox nonsmooth optimization problem, the same lower bound convergence rate $\mathcal O\left(1/\sqrt{k}\right)$ as stated in Theorem 3.2.1 in Nesterov's book \cite{nesterov_lectures_2018} is true.
+            Unfortunately it is nontrivial to see it as true because $\mathbb A$ optimizes Moreau Envelope $\mathcal M^*_{\kappa^{-1}F}(x)$ through inexact evaluation and the Moreau Envelope has Lipschitz gradient.
             For $\mathbb A$ Theorem 3.2.1 doesn't apply. 
-            Whatever the true answer is, it's not obvious. 
             So, here is the refined question: 
             \begin{quotation}
-                Suppose that the objective function $F$ is no $L$-Lipschitz continuous hence Assumption \ref{ass:linear-convergence-inner-loop} is false. 
-                If we assume that $F$ is any convex function (potentially nonsmooth and without any smooth parts), would there exist any kind of regularization parameters $(\kappa_k)_{k \ge 0}$, error sequence $\epsilon_k$ such that the overall complexity of Catalyst retains convergence rate equals or faster than $\mathcal O\left(1/\sqrt{k}\right)$ (The lower bound of all first order blackbox convex optimization)?
+                If we assume that $F$ is any convex function (potentially nonsmooth with gradient that are not locally Lipschitz), would there exist any kind of regularization parameters $(\kappa_k)_{k \ge 0}$, error sequence $\epsilon_k$ such that the worst case total complexity of Catalyst retains convergence rate equals or faster than $\mathcal O\left(1/\sqrt{k}\right)$ (The lower bound of all first order blackbox convex optimization)?
+                I.e: Does the idea of an inexact proximal point computational oracle lift the theoretical lower bound complexity on first order blackbox convex optimization? 
             \end{quotation}
-            If the answer is that it can be faster than the lower bound, then we had extended the Catalyst Framework, otherwise, it leads to the unintuitive result that lower bound $\mathcal O(1/\sqrt{k})$ still holds.
-            \par
-            To the best of our knowledge, nobody has yet answered the question directly in the literature, but we found some relevant literatures after some preliminary research. 
-            Nesterov 2014 \cite{nesterov_universal_2015}, he considers the method of accelerated gradient for function with Holder continuous gradient.
+            If the answer is that it can be faster than the lower bound, then we had extended the Catalyst Framework to convex function without Lipschitz smooth gradient, otherwise, it leads to the unintuitive result that lower bound $\mathcal O(1/\sqrt{k})$ still holds which will prove a concept of universality of the lower bound results for blackbox convex optimizations.
+            \par
+            To the best of our knowledge, nobody has yet answered the question directly in the literature, but we found some relevant literatures nonetheless. 
+            In Nesterov 2014 \cite{nesterov_universal_2015}, he considered accelerated gradient for function with Hölder Continuous gradient.
             Nesterov continued and expanded on the results obtained by Devolder et al.
-2014 \cite{devolder_first-order_2014} on inexact oracles for blackbox optimizations which showed that the inexact oracle for Lipschitz smooth function can be viewed as exact for another perturbed function with Holder continuous gradient.
-            He proposed three first order algorithms where the last one, a variant of accelerated gradient method that converges optimally for all functions with Holder continuous gradient without knowing the Holder continuity constant in advance.
+\cite{devolder_first-order_2014} on inexact oracles for blackbox optimizations which showed that the inexact oracle for Lipschitz smooth function can be viewed as exact for another perturbed function with Hölder Continuous gradient.
+            He proposed three first order algorithms where the last one, a variant of accelerated gradient method that converges optimally for all functions with Hölder Continuous gradient without knowing the Holder continuity constant in advance.
             His work is not considered directly relevant to Catalyst because it's not yet obvious because it's missing an inexact accelerated proximal point, and he uses the theories of inexact oracles from a purely theoretical standpoint.
             \par
-            In a more recent development, 
-            \par
-            Of course, the class of holder continuous gradient doesn't encapsulate the class of all convex function where inexact proximal point can be applied.
-
-            \todoinline{Add research plans and literature reviews here. }
-
-        \subsubsection{Applications for Catalyst Accelerations and its variants}
-            \todoinline{
-                Considers some specific applications of the Catalyst Acceleration method in the literatures. 
-            }
+            A more recent development in Yang and Toh \cite{yang_bregman_2022} exposes the theories of Inexact Accelerated Bregman Proximal Point method in the context of applying it for optimal transport.
+            They showed that the lower bound remains $\mathcal O(1/k)$, and in the special case when the kernel function is strongly convex relative to some norm, the optimal convergence rate of $\mathcal O(1/k^2)$ is reached.
+            These results are consistent with Nesterov's book chapter 6 \cite{nesterov_lectures_2018} and Dragomir et al. \cite{dragomir_optimal_2022}. 
+            \par
+            Of course, the class of convex function with Hölder Continuous gradient (i.e: the class of function that is relatively smooth to some Bregman kernel) doesn't encapsulate the class of all convex functions where inexact proximal point is applicable.
+            The original question would remain open. 
+            \par
+            To tackle the problem worst case complexity problem in general, it's worth mentioning
+            Performance estimation problem (PEP). 
+            PEP puts the set of all convex function as their iterates, gradient, and function value and the algorithm all together into Semi-definite programming constraints (SPD) and it solves for the worst case convergence.
+            Proposed by Drori and Teboulle \cite{drori_performance_2014} is the method of PEP for worst case analysis for convex programming, they showed that QCQP (Quadratic Constrained Quadratic Program) for formulation of the first order worst case iteration complexity problem can be reduced to a SPD such that it's tight.
+            And Goujaud et al.
+\cite{goujaud_pepit_2024} gives a Python library with APIs\footnote{APIs: A plural acronym for Application Programming Interface.} to produce worst case convergence by simply implementing the algorithm and the program formulates the SDP and solves it in the back.
+            This library supports inexact gradient, exact/inexact proximal point, and many other computational oracles. 
+            These tools help us to formulate/verify complexity results if our questions on the total complexity of Catalyst can be put into the PEP framework. 
+            % \todoinline{
+            %     Add research plans and literature reviews here.     
+            %     \begin{enumerate}
+            %         \item Yang and Toh. ``Bregman proximal point algorithm revisited: A new inexact version and its inertial variant''
+            %         \item Dragomir et al. ``Optimal complexity and certification of Bregman first-order methods''
+            %         \item Goujaud et al. ``PEPit: computer-assisted worst-case analyses of first-order optimization methods in Python''
+            %         \item Drori and Teboulle. ``Performance of first-order methods for smooth convex minimization: a novel approach''
+            %     \end{enumerate}
+            % }
 

### 2025-02-07 Notebook LaTEX/Proposal/presentation.tex
>w<, changes to proposal.

@@
 \author{Hongda Li}
-\title[Thesis Proposal Talk]{First Order Nonsmooth Optimization: Catalyst Acceleration and Unifying Nesterov's Acceleration}
+\title[Thesis Proposal Talk]{Nesterov's First Order Method Accelerations: Unifications, Applications  and Numerial Experiments}
 % \newcommand{\email}{lalala@lala.la}
@@
 \section{Introduction}
+    \begin{frame}{Introduction}
+        \begin{block}{Upcoming Contents: }
+            \begin{itemize}
+                \item Notations, proximal gradient inequality, gradient mapping. 
+                \item Nesterov's estimating sequence.
+                \item Introducing R-WAPG (Content of our draft paper). 
+                \item Introducing the Catalyst metal acceleration framework. 
+            \end{itemize}
+        \end{block}
+    \end{frame}
     \subsection{Notations and preliminaries}
@@
             \begin{enumerate}
-                \item It's an early attempt at putting accelerated inexact proximal point method into a practical setting. 
+                \item It puts accelerated inexact proximal point method into a practical setting. 
                 \item It finds application in machine learning, and it accelerates the convergence of Variance Reduced Method (A type of incremental method that is not slower than the exact counterpart).
@@
 \section{Content of the draft paper}
+    \begin{frame}{Contents of our draft papers}
+        \begin{block}{Upcoming contents}
+            We explain results from our relaxed, weak accelerated proximal gradient (R-WAPG). 
+            \begin{enumerate}
+                \item The R-WAPG sequence and the method of R-WAPG. 
+                \item The generic convergence of R-WAPG. 
+                \item Three equivalent forms of R-WAPG. 
+                \item Specialized convergence results with for specific instances of FISTA variants in the literatures. 
+                \item A parameter free formulation of R-WAPG and the results of our preliminary numerical experiments. 
+                \item Nesterov's idea of strong convexity transfer and the R-WAPG framework. 
+            \end{enumerate}
+        \end{block}
+
+    \end{frame}
     \subsection{The method of R-WAPG and its convergence}
@@
                 \item Equivalent forms of R-WAPG exists and resembles variants of FISTA in the literatures
-                \item We proved the equivalences in our draft papers and the convergence claim from previous applies to all the equivalent forms of R-WAPG which will follow. 
+                \item We proved the upcoming equivalences forms of R-WAPG in the draft papers. 
+                \item Previous claimed generic convergence results will apply to all equivalent forms of R-WAPG will now come. 
             \end{enumerate}    
@@
 \section{Selected contents from Catalyst Meta Accelerations}
+    \begin{frame}{Selected contents from Catalyst Meta Accelerations}
+        \begin{block}{Upcoming Contents}
+            \begin{enumerate}
+                \item Notations, assumptions. 
+                \item Inexact proximal point evaluations criteria. 
+                \item Structure of Catalyst accelerations and inner/out loop complexity results from Lin et al's first Catalyst paper \cite{lin_universal_2015}. 
+                \item Catalyst acceleration with relative error crition, Lin et al's second paper \cite{lin_catalyst_2018}.
+                \item Comments on future works for Catalyst by Necoara et al. \cite{necoara_linear_2019} and our questions about the Catalyst Acceleration Framework. 
+            \end{enumerate}
+        \end{block}
+    \end{frame}
     \subsection{Introduction to Catalyst}
@@
         \end{frame}
-        \begin{frame}{Catalyst meta acceleration}
+        \begin{frame}{Catalyst Meta Acceleration}
             \begin{definition}[Lin's Universal Catalyst Acceleration]\label{def:lin-catalyst-original}

### 2025-02-07 Notebook LaTEX/Proposal/proposal.tex
>w<, changes to proposal.

@@
             \begin{enumerate}
-                \item $M, N$ are constants. They define matrix $A \in \RR^{M\times N}$ which has entires of i.i.d random variable taken from a standard normal distribution. 
+                \item $M, N$ are constants. They define matrix $A \in \RR^{M\times N}$ which has entries of i.i.d random variable taken from a standard normal distribution. 
                 \item $L, \mu$, are Lipschitz constant and the strong convexity constant for the smooth part of the objective which are not known prior.
-Hence they are estimated by $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$ prior to experiment to assist the V-FISTA algorithm.
+Hence, they are estimated by $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$ prior to experiment to assist the V-FISTA algorithm.
                 \item $x^+ = [1\; -1\; 1 \; \cdots ]^T \in \RR^N$, it's a vector with alternating $1, -1$ in it. 
@@
         \par
-        We invent this notations because there are no consistent notations in the literatures and several of the Catalyst papers all use dratically different notations.  
+        We invent the notations because there are no consistent notations in the literatures and several of the Catalyst papers all use different notations.  
     \end{assumption}
@@
     \begin{remark}
-        Setting $\epsilon = 0$, we have the exact definition of the exact resolvent given as $\mathcal J_{\beta^{-1}}y = \mathcal J^0_{\beta^{-1}}y$. 
+        Setting $\epsilon = 0$, we have the exact definition of the exact resolvent given as $\mathcal J_{\beta^{-1}F}y = \mathcal J^0_{\beta^{-1}F}y$. 
     \end{remark}
@@
     \subsection{Introduction to Catalyst}\label{ssec:catalyst-intro}
-        Inspired by accelerated proximal point Method (APPM) from Güler \cite{guler_new_1992}, and Inexact Proximal Point Method (IPPM) of Rockafellar 1976 \cite{rockafellar_monotone_1976}, Lin et al.
+        Inspired by Accelerated Proximal Point Method (APPM) from Güler \cite{guler_new_1992}, and Inexact Proximal Point Method (IPPM) of Rockafellar 1976 \cite{rockafellar_monotone_1976}, Lin et al.
 \cite{lin_universal_2015} proposed a generic method taking inspirations from the convergence claims of APPM to accelerate Variance Reduced Method (VRM).
@@
             \end{remark}
-            \begin{theorem}[Outer loop convergence convex but not strongly convex]\label{thm:erro-seq-outer-cnvx}\;\\
+            \begin{theorem}[Outer loop convergence not necessarily strongly convex]\label{thm:erro-seq-outer-cnvx}\;\\
                 For $\mathbb A$ with regularization parameter $\kappa > 0$. 
-                Assume that $F$ is convex but with strong convexity constant $\mu = 0$. 
+                Assume that $F$ is convex but with strong convexity constant $\mu \ge 0$. 
                 Choose $\alpha_0 = (\sqrt{5} - 1)/2$ and the error sequence 
@@
             \begin{remark}
-                VRMs listed earlier statsifies this assumption. 
+                VRMs listed earlier satisfy this assumption. 
                 Details about the consequence of this assumption is in Section \ref{ssec:catalyst-future}. 
@@
             \end{remark}
-            \begin{proposition}[Inner loop, context but not strongly convex]\label{prop:inner-loop-complexity-cnvx}
+            \begin{proposition}[Inner loop convergence not necessarily strongly convex]\label{prop:inner-loop-complexity-cnvx}\;\\
                 Under the settings of Theorem \ref{thm:erro-seq-outer-cnvx}, suppose that:

### 2025-02-09 Notebook LaTEX/Proposal/proposal.tex
>w<, changes

@@
         \fontfamily{ptm}\selectfont 
-        Nesterov's First Order Method Accelerations: Unifications, Applications  and Numerial Experiments
+        Nesterov's First Order Method Accelerations: Unification, Applications  and Numerical Experiments
     }
@@
             \begin{remark}
-                Under the assumption of this section, the mapping $T_L$ is a single-valued mapping on $\RR^n$ and it's  a $3/2$ averaged operator. 
+                Under the assumption of this section, the mapping $T_L$ is a single-valued mapping on $\RR^n$, and it's  a $3/2$ averaged operator. 
             \end{remark}
@@
         \par
-        The definition of the estimating sequence that follows is based on our own understanding of the estimating sequence. 
+        The definition of the estimating sequence that follows is one of the examples in the literatures. 
         \begin{definition}[Nesterov's estimating sequence]\label{def:nes-est-seq}
@@
     \begin{remark}
-        Setting $\epsilon = 0$, we have the exact definition of the exact resolvent given as $\mathcal J_{\beta^{-1}F}y = \mathcal J^0_{\beta^{-1}F}y$. 
+        Setting $\epsilon = 0$, we have the exact definition of the exact resolvent given as $\mathcal J_{\kappa^{-1}F}y = \mathcal J^0_{\kappa^{-1}F}y$. 
     \end{remark}
@@
         In each iteration, it accesses the gradient of a few samples to attain a new estimate of the gradient with minimum additional calculations.  
-        This gives better complexity than full gradient descent over all. 
+        This gives better overall complexity than full gradient descent. 
         Compare to traditional stochastic gradient, VRM produces smaller variance of the estimated gradient near the minimizer which gives faster convergence rate. 
@@
                 Assume that $F$ is convex but with strong convexity constant $\mu \ge 0$. 
-                Choose $\alpha_0 = (\sqrt{5} - 1)/2$ and the error sequence 
+                Choose $\alpha_0 = \left(\sqrt{5} - 1\right)/2$ and the error sequence 
                 \begin{align*}
@@
             Given any $\epsilon > 0$ if $z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$, define the absolute inexact gradient mapping $\mathcal G_{\kappa^{-1}F}^\epsilon (z) := \kappa(x - z)$.
-            Then it satsifies: 
+            Then it satisfies: 
             \begin{align*}

### 2025-02-10 Notebook LaTEX/Proposal/presentation.tex
>w<, changes

@@
     \begin{frame}{Introduction}
+        Part I: Introduction. 
         \begin{block}{Upcoming Contents: }
@@
                 \item It finds application in machine learning, and it accelerates the convergence of Variance Reduced Method (A type of incremental method that is not slower than the exact counterpart).
-                \item It demonstrates crucial ideas on how prove convergence rate where the evaluation of proximal point method is inexact in the convex settings. 
+                \item It demonstrates crucial ideas on convergence analysis involving nexact evaluation of proximal point method under the the convex settings. 
             \end{enumerate}
@@
 
-\section{Content of the draft paper}
+\section{Contents of the draft paper}
     \begin{frame}{Contents of our draft papers}
+        Part II: Contents of our current draft paper. 
         \begin{block}{Upcoming contents}
@@
                 \item The R-WAPG sequence and the method of R-WAPG. 
-                \item The generic convergence of R-WAPG. 
+                \item A generic convergence theorem of R-WAPG. 
                 \item Three equivalent forms of R-WAPG. 
@@
                 Given any $y_1 = x_1 \in \RR^n$, and sequences $(\rho_k)_{k \ge 0}, (\alpha_k)_{k\ge 0}$ Definition \ref{def:rwapg-seq}. 
-                The algorithm generates iterates $x_{k + 1}, y_{k + 1}$ For $k = 1, 2, \cdots $ by the procedures: 
+                The algorithm generates iterates $x_{k + 1}, y_{k + 1}$ For $k = 1, 2, \ldots $ by the procedures: 
                 {\small
@@
         \begin{frame}{Summary of our results}
-            With the equivalent representations and the convergence claim for relaxed sequence $(\alpha_k)_{k \ge 0}$ of the R-WAPG, we are able to unifies: 
+            With the equivalent representations and the convergence claim for relaxed sequence $(\alpha_k)_{k \ge 0}$ of the R-WAPG, we are able to unify the convergence rate of: 
             \begin{enumerate}
-                \item Several Euclidean variants of the FISTA algorithm. 
-                \item Nontraditional choices of momentum sequences. 
+                \item Three Euclidean variants of the FISTA algorithm. 
+                \item Constant momentum APG for strongly convex objective.  
             \end{enumerate}
@@
                     \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$;}
-                    \WHILE{$L/2\Vert x^+ - y\Vert^2 < D_f(x^+, y)$}
+                    \WHILE{$L/2\Vert x^+ - y_k\Vert^2 < D_f(x^+, y_k)$}
                         \STATE{$L:= 2L$;}
@@
                 \delta_k := \log_2\left(
+                    \NOG
+                \right)
+                \text{ with } 
                 \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}
-                \right). 
             \end{align*}
@@
             \begin{enumerate}
-                \item Same initial guess shared by FR-WAPG from us, and  M-FISTA, V-FISTA in (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}.
-It's repeated for 30 different random initial guesses.
+                \item Same initial guess $x_0$ shared by FR-WAPG,  M-FISTA and V-FISTA in (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017} repeated with 30 different random initial guesses. 
                 \item Min, max, and median of $\delta_k$ measured for all iterative method.
-                \item $\mu, L$ were given in prior to produce diagonal matrix $A = \text{diag}(0, \mu + (L-\mu)(N - 1)^{-1}, \mu + 2(L-\mu)(N - 1)^{-1}, \cdots, \mu + (N - 2)(L - \mu)^{-1}, L)$, but M-FISTA, FR-WAPG were not fed these parameters.
+                \item $\mu, L$ were given in prior to produce diagonal matrix 
+                {\footnotesize
+                \begin{align*}
+                    A = \text{diag}
+                    \left(0, 
+                        \mu + \frac{L - \mu}{N - 1},
+                        \mu + 2\frac{L - \mu}{N - 1}, 
+                        \ldots, 
+                        \mu + \frac{(N - 2)(L - \mu)}{N - 1}, 
+                        L
+                    \right). 
+                \end{align*}
+                }
+                M-FISTA, FR-WAPG were not fed these parameters. 
             \end{enumerate}
@@
     \begin{frame}{Selected contents from Catalyst Meta Accelerations}
+        Part III: Catalyst Acceleration and future works. 
         \begin{block}{Upcoming Contents}
@@
                 \item Inexact proximal point evaluations criteria. 
-                \item Structure of Catalyst accelerations and inner/out loop complexity results from Lin et al's first Catalyst paper \cite{lin_universal_2015}. 
-                \item Catalyst acceleration with relative error crition, Lin et al's second paper \cite{lin_catalyst_2018}.
+                \item Structure of Catalyst accelerations and inner/out loop complexity results from Lin et al.'s first Catalyst paper \cite{lin_universal_2015}. 
+                \item Catalyst acceleration with relative error criterion, Lin et al.'s second paper \cite{lin_catalyst_2018}.
                 \item Comments on future works for Catalyst by Necoara et al. \cite{necoara_linear_2019} and our questions about the Catalyst Acceleration Framework. 
@@
                         z \in \RR^n \left| \;
-                            \mathcal M_F^{\kappa^{-1}}(z; x) - 
-                            \mathcal M^*_{F, \kappa^{-1}}(z; x)
+                            \mathcal M_F^{1/\kappa}(z; x) - 
+                            \mathcal M^*_{F, 1/\kappa}(z; x)
                             \le \frac{\kappa\delta}{2}\Vert x - z\Vert^2
@@
                 For any $k \in \N$, $y \in \RR^n$. 
-                Suppose $\mathbb M$ generates iterates $(z_{k, t})_{t \ge 0}$ for the inner loop iteration such that there exists $A > 0$, and it has: 
+                Suppose $\mathbb M$ generates iterates $(z_{k, t})_{t \ge 0}$ for the inner loop iteration such that there exists $C_{\mathbb M} > 0$, and it has: 
                 {\small
@@
         \end{frame}
-        \begin{frame}{Outer loop complexity, strong convex case}
+        \begin{frame}{Outer loop complexity, $\mu > 0$}
             This is Theorem 3.1 in Lin et al. \cite{lin_universal_2015}. 
@@
         \end{frame}
-        \begin{frame}{Outer loop complexity, convex but not strongly convex case}
+        \begin{frame}{Outer loop complexity, $\mu \ge 0$}
             This is Theorem 3.3 from Lin et al. \cite{lin_universal_2015}. 
@@
                 For $\mathbb A$ with regularization parameter $\kappa > 0$.
-                Assume that $F$ is convex but with strong convexity constant $\mu = 0$. 
+                Assume that $F$ is convex but with strong convexity constant $\mu \ge 0$. 
                 Choose $\alpha_0 = (\sqrt{5} - 1)/2$ and the absolute error sequence 
@@
         \begin{frame}{Inner loop complexity, absolute errors}
-            The followings are Proposition 3.2, 3.4 from Lin et al. \cite{lin_universal_2015}. 
-            \begin{proposition}[Inner loop complexity strongly convex]\label{prop:inner-loop-complexity-s-cnvx}
+            The followings are Proposition 3.2, 3.4 from Lin et al. 
+            \cite{lin_universal_2015}. 
+            \begin{proposition}[Inner loop complexity $\mu > 0$]
+            \label{prop:inner-loop-complexity-s-cnvx}
             {\footnotesize
@@
                 Then, the precision $\epsilon_k$ is achieved within at most a number of iteration $T_{\mathbb M} \le \widetilde {\mathcal O}(1/ \tau_{\mathbb M})$. 
-                Here $\widetilde{\mathcal O}$ hides logarithmic complexity in $\mu, \kappa$ and other constants. 
+                Here $\widetilde{\mathcal O}$ hides logarithmic complexity, $\mu, \kappa$ and other constants. 
             }
             \end{proposition}
-            \begin{proposition}[Inner loop, convex but not strongly convex]\label{prop:inner-loop-complexity-cnvx}
+            \begin{proposition}[Inner loop complexity $\mu \ge 0$]
+            \label{prop:inner-loop-complexity-cnvx}
             {\footnotesize
@@
         \begin{frame}{Total complexity}
-            We count $m$, the number of iteration experienced by $\mathbb M$ for the $k$ th iteration of $\mathbb A$. 
+            We count $m$, the number of iteration experienced by $\mathbb M$ up to the $k$ iteration of $\mathbb A$. 
             \begin{enumerate}
@@
                 }
-                \item If $\mu = 0$, using Proposition \ref{prop:inner-loop-complexity-cnvx}, Theorem \ref{thm:erro-seq-outer-cnvx} it has 
+                \item If $\mu = 0$ so $F$ is not necessarily strongly convex, using Proposition \ref{prop:inner-loop-complexity-cnvx}, Theorem \ref{thm:erro-seq-outer-cnvx} it has 
                 {\footnotesize
@@
                 \item $N_{\mathbb M} \le \widetilde{\mathcal O}\left(\tau_{\mathbb M}^{-1}\sqrt{\kappa/\epsilon}\log(\epsilon^{-1})\right)$ if $\mu = 0$, 
-                \item $N_{\mathbb N}\le \widetilde{O}\left((\tau_{\mathbb M}\sqrt{q})^{-1}\log(\epsilon^{-1})\right)$ if $\mu > 0$. 
+                \item $N_{\mathbb N}\le \widetilde{\mathcal O}\left((\tau_{\mathbb M}\sqrt{q})^{-1}\log(\epsilon^{-1})\right)$ if $\mu > 0$. 
             \end{enumerate}
@@
             \begin{enumerate}
-                \item $\delta_k$ doesn't requite $F^*$. 
+                \item Relative error sequence $\delta_k$ doesn't requite $F^*$. 
                 \item Doesn't require bounded level set assumption for inner loop complexity bound. 
@@
             \begin{alertblock}{Future works}
-                Extend linear convergence of accelerated gradient for variance reduced incremental methods such as the Catalyst Framework into a weaker settings. 
+                Extend linear convergence of accelerated gradient for variance reduced incremental methods such as the Catalyst Framework into a weaker setting. 
             \end{alertblock}
@@
             \begin{enumerate}
-                \item $\mathbb A$ optimizes inexact Moreau Envelope $\mathcal M^*_{\kappa^{-1}, F}(y)$ which is smooth and strongly convex if $F$ is convex hence the $\mathcal O(1/\sqrt{k})$ lower bound of Theorem 3.2.1 \cite{nesterov_lectures_2018} complexity for all convex first order optimization doesn't apply for the total complexity.
-                \item Instead, Theorem 2.1.7 \cite{nesterov_lectures_2018} applies and the lower complexity bound $\mathbb A$ is $\mathcal O(1/k^2)$. 
-                \item Linear convergence of $\mathbb M$ Theorem 2.1.17 fails instead Theorem 3.2.5 applies and the lower bound is $\mathcal O(1/k)$. 
+                \item $\mathbb A$ optimizes inexact Moreau Envelope $\mathcal M^*_{\kappa^{-1}, F}(y)$ which is smooth and strongly convex if $F$ is convex hence $\mathcal O(1/\sqrt{k})$ from Theorem 3.2.1 \cite{nesterov_lectures_2018} doesn't apply for the total complexity.
+                \item Theorem 2.1.7 \cite{nesterov_lectures_2018} doesn't apply because the lower complexity bound $\mathbb A$ is $\mathcal O(1/k^2)$ assume exact gradient evaluations. 
+                \item Theorem 2.1.17 \cite{nesterov_lectures_2018} (Linear rate lower bound for strong convexity and smoothness) doesn't apply on $\mathbb M$. 
+                Instead Theorem 3.2.5 applies and the lower bound is $\mathcal O(1/k)$. 
             \end{enumerate}
-            We note that the question has practical importance because the method of subgradient descent with Polyak stepsizes are optimal for Smooth, strongly convex, and smooth plus strongly convex function on a compact domain.
-See Hazan and Kakade\cite{hazan_revisiting_2022}.
+            Subgradient descent with Polyak step size reaches the lower bound of worst case of Strongly convex, strongly convex and smooth.
+            See Hazan et al. \cite{hazan_revisiting_2022}.
+
         \end{frame}

### 2025-02-10 Notebook LaTEX/Proposal/proposal.tex
>w<, changes

@@
             \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$;}
-            \WHILE{$L/2\Vert x^+ - y\Vert^2 < D_f(x^+, y)$}
+            \WHILE{$L/2\Vert x^+ - y_k\Vert^2 < D_f(x^+, y_k)$}
                 \STATE{$L:= 2L$;}
@@
             \delta_k := \log_2\left(
+                \NOG
+            \right)
+            \text{ with } 
             \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}
-            \right). 
         \end{align*}
@@
             \begin{enumerate}
-                \item $N$, the dimension of the problem which defines $A \in \RR^{N\times N}$, a diagonal matrix given by $N- 1$ linearly spaced with equal increment on the interval $[\mu, L]$, and an extra number $0$, i.e: $A = \text{diag}(0, \mu + (L-\mu)(N - 1)^{-1}, \mu + 2(L-\mu)(N - 1)^{-1}, \cdots, \mu + (N - 2)(L - \mu)^{-1}, L)$.
+                \item $N$, the dimension of the problem which defines $A \in \RR^{N\times N}$, a diagonal matrix given by $N- 1$ linearly spaced with equal increment on the interval 
+                \begin{align*}
+                    A = \text{diag}
+                    \left(0, 
+                        \mu + \frac{L - \mu}{N - 1},
+                        \mu + 2\frac{L - \mu}{N - 1}, 
+                        \ldots, 
+                        \mu + \frac{(N - 2)(L - \mu)}{N - 1}, 
+                        L
+                    \right). 
+                \end{align*}
                 \item The strong convexity and Lipschitz smoothness constant has $0 < \mu < L$. They are given in prior to construct the problem. 
@@
             \end{align*}
-            The above says that the gradient mapping $\mathcal G_{\kappa^{-1}F}^{\epsilon}(z)$ approximates the gradient of Moreau Envelope of $F$ at $x$. 
-            Similarly, if $z \in \widetilde{\mathcal J}_{\kappa^{-1}F}^\delta(x)$, define the relative inexact gradient mapping $\widetilde{\mathcal G}_{\kappa^{-1}F}^\delta(x) := \kappa(x - z)$, we have:
+            The above says that the inexact gradient mapping $\mathcal G_{\kappa^{-1}F}^{\epsilon}(z)$ approximates the gradient of Moreau Envelope of $F$ at $x$. 
+            Similarly, if $z \in \widetilde{\mathcal J}_{\kappa^{-1}F}^\delta(x)$, define $\widetilde{\mathcal G}_{\kappa^{-1}F}^\delta(x) := \kappa(x - z)$. 
+            Then it has: 
             \begin{align*}
@@
             \par
-            For our interests, we focus on one of their comments on the Catalyst by Lin et al. \cite{lin_universal_2015}. 
+            We focus on one of their comments on Catalyst by Lin et al. \cite{lin_universal_2015}. 
             They said, and here we quote: 
@@
             \end{quote}
-            We note that, their idea of extension can be applied to inner loop $\mathbb M$, or out loop $\mathbb A$, either, or both. 
+            Their idea of extension can be applied to inner loop $\mathbb M$, or out loop $\mathbb A$, either, or both. 
             \par
@@
             Paquette et al.
-\cite{paquette_catalyst_2018} were inspired by \cite{ghadimi_accelerated_2016} and showed that the Catalyst algorithm based on the gradient termination criterion analogous similar to C2 (see equation (13), (14) in their paper) can adapt to nonconvex settings and the norm of the gradient converges.
+\cite{paquette_catalyst_2018} were inspired by \cite{ghadimi_accelerated_2016} and showed that the Catalyst algorithm based on the gradient termination criterion analogous to C2 (see equation (13), (14) in their paper) can adapt to nonconvex settings and the norm of the gradient converges.
             However, it's at the expense of one additional evaluation of the proximal point method, and it requires evaluating the function value once per outer loop iteration. 
@@
             \end{enumerate}
-            To the best of our interpretation of Catalyst is through the theories of inexact proximal point because NAG is not the unque option and other acceleration techniques can be used as well. 
+            To the best of our interpretation of Catalyst is through the theories of inexact proximal point because NAG is not the unique option and other acceleration techniques can be used as well. 
             For example, see Cai et al. \cite{cai_variance_2023} for inexact Halpern acceleration for solving variational inequalities. 
@@
             \par
-            We now list new developments for Nesterov's acceleration in the nonconvex settings with stronge convergence claim. 
+            We now list new developments for Nesterov's acceleration with convergence to stationarity, and convergence of the iterates in the nonconvex settings.
             Preprint by Hermant et al. \cite{hermant_study_2024} present results that the fixed momentum variant of NAG has linear convergence  on the class of strongly quasar convex functions. 
@@
             \par
-            For theories of inexact proximal point method see Khanh et al. \cite{khanh_inexact_2025} for an algorithmic framework of inexact proximal point method on weakly convex function. 
-            The class of weakly convex function is particularly interesting because it has general convergence claim in Ghadimi and Lan \cite{ghadimi_accelerated_2016}, and in Chapter 4 of the book preprint by Recht and Wright \cite{recht_optimization_nodate}.
+            See Khanh et al. \cite{khanh_inexact_2025} for an algorithmic framework of inexact proximal point method on weakly convex function. 
+            The class of weakly convex function is particularly interesting because it has convergance claim of the gradient norm in Ghadimi and Lan \cite{ghadimi_accelerated_2016}, and in Chapter 4 of the book preprint by Recht and Wright \cite{recht_optimization_nodate}.
             It's unclear how their convergence theories can be combined with NAG in the non-convex case, but it's worth investigating. 
@@
             \end{quotation}
-            If the answer is that it can be faster than the lower bound, then we had extended the Catalyst Framework to convex function without Lipschitz smooth gradient, otherwise, it leads to the unintuitive result that lower bound $\mathcal O(1/\sqrt{k})$ still holds which will prove a concept of universality of the lower bound results for blackbox convex optimizations.
-            \par
-            To the best of our knowledge, nobody has yet answered the question directly in the literature, but we found some relevant literatures nonetheless. 
+            If the worst case lower bound is faster, then we had extended the Catalyst Framework to convex function without Lipschitz smooth gradient, otherwise, it leads to the unintuitive result that lower bound $\mathcal O\left(1/\sqrt{k}\right)$ still holds which will show a concept of universality of the lower bound results for blackbox convex optimizations.
+            \par
+            To best of our knowledge, nobody has yet answered directly in the literature, however some literatures are relevant nonetheless. 
             In Nesterov 2014 \cite{nesterov_universal_2015}, he considered accelerated gradient for function with Hölder Continuous gradient.
@@
 \cite{devolder_first-order_2014} on inexact oracles for blackbox optimizations which showed that the inexact oracle for Lipschitz smooth function can be viewed as exact for another perturbed function with Hölder Continuous gradient.
-            He proposed three first order algorithms where the last one, a variant of accelerated gradient method that converges optimally for all functions with Hölder Continuous gradient without knowing the Holder continuity constant in advance.
+            He proposed three first order algorithms where the last one, a variant of accelerated gradient method that converges optimally for all functions with Hölder Continuous gradient without knowing the Hölder continuity constant in advance.
             His work is not considered directly relevant to Catalyst because it's not yet obvious because it's missing an inexact accelerated proximal point, and he uses the theories of inexact oracles from a purely theoretical standpoint.
             \par
-            A more recent development in Yang and Toh \cite{yang_bregman_2022} exposes the theories of Inexact Accelerated Bregman Proximal Point method in the context of applying it for optimal transport.
-            They showed that the lower bound remains $\mathcal O(1/k)$, and in the special case when the kernel function is strongly convex relative to some norm, the optimal convergence rate of $\mathcal O(1/k^2)$ is reached.
+            A more recent development in Yang and Toh \cite{yang_bregman_2022} exposes the theories of Inexact Accelerated Bregman Proximal Point method in the context of optimal transport. 
+            They showed that the worst case complexity is $\mathcal O(1/k)$, and in the special case when the kernel function is strongly convex relative to some norm, the algorithm has convergence rate of $\mathcal O(1/k^2)$ is reached.
             These results are consistent with Nesterov's book chapter 6 \cite{nesterov_lectures_2018} and Dragomir et al. \cite{dragomir_optimal_2022}. 
             \par
-            Of course, the class of convex function with Hölder Continuous gradient (i.e: the class of function that is relatively smooth to some Bregman kernel) doesn't encapsulate the class of all convex functions where inexact proximal point is applicable.
+            Of course, the class of convex function with Hölder Continuous gradient (i.e: the class of function that is relatively smooth with respect to a Bregman kernel) doesn't encapsulate the class of all convex functions where inexact proximal point is applicable.
             The original question would remain open. 
             \par
-            To tackle the problem worst case complexity problem in general, it's worth mentioning
-            Performance estimation problem (PEP). 
+            Finally, To tackle the problem worst case complexity problem in general, it's worth mentioning Performance estimation problem (PEP). 
             PEP puts the set of all convex function as their iterates, gradient, and function value and the algorithm all together into Semi-definite programming constraints (SPD) and it solves for the worst case convergence.
-            Proposed by Drori and Teboulle \cite{drori_performance_2014} is the method of PEP for worst case analysis for convex programming, they showed that QCQP (Quadratic Constrained Quadratic Program) for formulation of the first order worst case iteration complexity problem can be reduced to a SPD such that it's tight.
+            Proposed by Drori and Teboulle \cite{drori_performance_2014} is the method of PEP for worst case analysis for convex programming, they showed that QCQP (Quadratic Constrained Quadratic Program) for formulation of the first order the worst case iteration complexity problem can be reduced to a SPD such that it's tight.
             And Goujaud et al.
@@
             These tools help us to formulate/verify complexity results if our questions on the total complexity of Catalyst can be put into the PEP framework.
-            % \todoinline{
-            %     Add research plans and literature reviews here.     
-            %     \begin{enumerate}
-            %         \item Yang and Toh. ``Bregman proximal point algorithm revisited: A new inexact version and its inertial variant''
-            %         \item Dragomir et al. ``Optimal complexity and certification of Bregman first-order methods''
-            %         \item Goujaud et al. ``PEPit: computer-assisted worst-case analyses of first-order optimization methods in Python''
-            %         \item Drori and Teboulle. ``Performance of first-order methods for smooth convex minimization: a novel approach''
-            %     \end{enumerate}
-            % }
-
-% \section{Methods of inexact proximal point}\label{sec:inexact-prox}
-%     Content of this section is primarily based on Khanh et al. \cite{duy_khanh_inexact_2023} on inexact proximal method for weakly convex functions.
-
-% \section{Nestrov's acceleration in the nonconvex case}\label{sec:nes-acc-ncnvx}
-    % The behavior of Nesterov's acceleration for function that are nonconvex are the holy grail and the absolute frontier. 
-    % The approaches are incredibly diverse and therefore, this section will only list relevant references and briefly mention the ideas involved in those literatures. 
-    % \todoinline{\noindent
-    %     Here, is a list of early attempted research of Nesterov's acceleration method in the nonconvex case. 
-    % }
-
-% \section{Using PostGreSQL and big data analytic method for species classification on Sentinel-2 Satellite remote sensing imagery}
 

### 2025-02-10 Notebook LaTEX/Proposal/proposal.tex
>w<, changes

@@
             \par
-            A careful reader will realize that Assumption \ref{ass:linear-convergence-inner-loop} encapsulates the Lipschitz smoothness assumption of VRMs because the proximal point sub-problem is smooth and strongly convex and lower bound from Theorem 2.1.13 from Nesterov's book \cite{nesterov_lectures_2018} applies and it has a linear convergence rate.
+            A careful reader will realize that Assumption \ref{ass:linear-convergence-inner-loop} encapsulates the Lipschitz smoothness assumption of VRMs because the proximal point sub-problem is smooth and strongly convex and lower bound from Theorem 2.1.13 from Nesterov's book \cite{nesterov_lectures_2018} applies hence linear convergence rate is possible.
             Removing the smoothness assumption of $F$, $\mathbb M$ solves subproblem $\mathcal M_{\kappa^{-1}F}(\cdot, y_k)$ which is only strongly convex.
@@
                 If we assume that $F$ is any convex function (potentially nonsmooth with gradient that are not locally Lipschitz), would there exist any kind of regularization parameters $(\kappa_k)_{k \ge 0}$, error sequence $\epsilon_k$ such that the worst case total complexity of Catalyst retains convergence rate equals or faster than $\mathcal O\left(1/\sqrt{k}\right)$ (The lower bound of all first order blackbox convex optimization)?
-                I.e: Does the idea of an inexact proximal point computational oracle lift the theoretical lower bound complexity on first order blackbox convex optimization? 
+                I.e: Does the idea of an inexact proximal point computational oracle lift the theoretical lower bound of worst case complexity on first order blackbox convex optimization? 
             \end{quotation}

### 2025-02-10 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

@@
             \end{align*}
-            $A$ is set to be a positive semi-definite diagonal matrix so the problem admits unique minimizer $x^* = \mathbf 0$ with minimum being zero. 
+            $A$ is set to be a positive semi-definite diagonal matrix, so the problem admits unique minimizer $x^* = \mathbf 0$ with minimum being zero. 
             We apply Algorithm \ref{alg:free-rwapg}, M-FISTA, and V-FISTA. 
-            The following parameters are used to setup the problem: 
+            The following parameters are used to set up the problem: 
             \begin{enumerate}
-                \item $N$, the dimension of the problem which defines $A \in \RR^{N\times N}$, a diagonal matrix given by $N- 1$ linearly spaced with equal increment on the interval $[\mu, L]$, and an extra number $0$, i.e: $A = \text{diag}(0, \mu + (L-\mu)(N - 1)^{-1}, \mu + 2(L-\mu)(N - 1)^{-1}, \cdots, \mu + (N - 2)(L - \mu)^{-1}, L)$.
+                \item $N$, the dimension of the problem which defines $A \in \RR^{N\times N}$, a diagonal matrix given by $N- 1$ linearly spaced with equal increment on the interval $[\mu, L]$, and an extra number $0$, i.e:
+                \begin{align*}
+                    A = \text{diag}
+                    \left(0, 
+                        \mu + \frac{L - \mu}{N - 1},
+                        \mu + 2\frac{L - \mu}{N - 1}, 
+                        \ldots, 
+                        \mu + \frac{(N - 2)(L - \mu)}{N - 1}, 
+                        L
+                    \right). 
+                \end{align*}
                 \item The strong convexity and Lipschitz smoothness constant has $0 < \mu < L$. They are given in prior to construct the problem. 
-                \item $\epsilon > 0$ is the tolerance value and it's set to be $10^{-10}$. 
+                \item $\epsilon > 0$ is the tolerance value, and it's set to be $10^{-10}$. 
                 \item $x_0 \sim \mathcal N(I, \mathbf 0)$ is a vector, and it's the initial condition for all the algorithm.

### 2025-02-10 Notebook LaTEX/Proposal/proposal.tex
>w<, changes

@@
             A careful reader will realize that Assumption \ref{ass:linear-convergence-inner-loop} encapsulates the Lipschitz smoothness assumption of VRMs because the proximal point sub-problem is smooth and strongly convex and lower bound from Theorem 2.1.13 from Nesterov's book \cite{nesterov_lectures_2018} applies hence linear convergence rate is possible.
-            Removing the smoothness assumption of $F$, $\mathbb M$ solves subproblem $\mathcal M_{\kappa^{-1}F}(\cdot, y_k)$ which is only strongly convex.
+            Removing the smoothness assumption of $F$, then $\mathbb M$ solves $\mathcal M_{\kappa^{-1}F}(\cdot, y_k)$ which is $\kappa > 0$ strongly convex.
             Then, lower bound on convergence rate of any first order algorithm becomes $\mathcal O(1/k)$ by Theorem 3.2.5 from Nesterov's book. 
@@
             It is possible that, for any blackbox nonsmooth optimization problem, the same lower bound convergence rate $\mathcal O\left(1/\sqrt{k}\right)$ as stated in Theorem 3.2.1 in Nesterov's book \cite{nesterov_lectures_2018} is true.
-            Unfortunately it is nontrivial to see it as true because $\mathbb A$ optimizes Moreau Envelope $\mathcal M^*_{\kappa^{-1}F}(x)$ through inexact evaluation and the Moreau Envelope has Lipschitz gradient.
-            For $\mathbb A$ Theorem 3.2.1 doesn't apply. 
-            So, here is the refined question: 
+            Unfortunately it doesn't apply because $\mathbb A$ optimizes Moreau Envelope $\mathcal M^*_{\kappa^{-1}F}(x)$ through inexact evaluation and the Moreau Envelope has Lipschitz gradient. 
+            Here is the refined question: 
             \begin{quotation}

### 2025-02-13 Notebook LaTEX/R-WAPG/paper3.tex
>w<, fixing cringe shit

@@
 
-\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{false}
+\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{true}
 \input{presets/wang/input.tex}
@@
     The R-WAPG provides a unified framework for several notable Euclidean variants of FISTA and verify their convergence. 
-    In addition, we also proposed the convergence rate of strongly convex objective with a constant momentum term. 
+    In addition, we also study the convergence rate of strongly convex objective with a constant momentum term. 
     We reformulate R-WAPG so that it doesn't require any parameter without using the idea of restarting which we call ``Free R-WAPG". 
@@
 Primary 90C30, 90C25, 65K10; Secondary 65Y20. 
-\noindent{\bfseries Keywords: } Convex optimization, Nesterov's acceleration, Proximal gradient, Convergence rate.
+\noindent{\bfseries Keywords: } 
+\\
+Convex optimization, Nesterov's acceleration, Proximal gradient, Convergence rate.
 
@@
         In Theorem \ref{thm:fixed-momentum-fista}, it demonstrates that R-WAPG frameworks gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex.
-        Finally, we did the tedious work and present three equivalent forms of R-WAPG in Section \ref{sec:rwapg-equiv-repr} that are comparable to notable Euclidean variants of FISTA and beyond.
+        Finally, we did the necessary work and present three equivalent forms of R-WAPG in Section \ref{sec:rwapg-equiv-repr} that are comparable to notable Euclidean variants of FISTA and beyond.
 This shows the descriptive power of our R-WAPG framework.
@@
         The section proves the convergence rate of several variants of FISTA using the equivalent forms introduced in Section \ref{sec:rwapg-equiv-repr} and the convergence rate developed Section \ref{sec:rwapg-formulation-convergence}.
-        Finally, in Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcase the numerical experiments for regression, LASSO.
+        Finally, Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcase the numerical experiments for regression, LASSO.
 
@@
     The extended real is defined as $\overline \RR := \RR \cup \{\infty, - \infty\}$. 
-    Using $\overline \RR$ we model a general convex function $g: Q \rightarrow \RR$ as a function on $\RR$. 
-    If $x \in \RR^n \setminus Q$ then $g(x) = \infty$ by definition. 
+    Using $\overline \RR$ we model a general convex function $g: \RR^n \rightarrow \overline{\RR}$ as a function on $\RR$.  
     The domain has the definition $\dom(g) := \{x \in \RR^n : g(x) < \infty\}$. 
@@
     \par 
-    Definition \ref{def:stepwise-wapg} which describes what happens at a single iteration of the R-WAPG algorithm. 
-    It defines a procedure of generating $x_{k + 1}, v_{k + 1}$ given any $x_k, v_k$. 
-    Proposition \ref{prop:stepwise-lyapunov} states the inequality that describes a decreasing quantity that involves $F(x_k), F(x_{k + 1})$ at each single iteration. 
+    Definition \ref{def:stepwise-wapg} describes one iteration of the R-WAPG algorithm. 
+    It defines the procedure of generating $x_{k + 1}, v_{k + 1}$ given any $x_k, v_k$. 
+    Proposition \ref{prop:stepwise-lyapunov} states the inequality \eqref{ineq:stepwise-lya-2}  of a decreasing quantity involving $F(x_k), F(x_{k + 1})$ at each iteration.
+    \par
+    The assumption below is crucial to describing the convergence rate of the R-WAPG and it requires the convexity assumption on $F$. 
     \begin{assumption}
@@
         Proceeding stepwise, we will show the following intermediate results: 
+        \begin{enumerate}
+            \item Step 1: 
             \begin{align}\tag{Step 1}\label{eqn:stepwise-lya-proof-step-1}
@@
                             \Vert v_k - y_k\Vert^2
-                    \right), 
+                        \right). 
                 \end{split}
             \end{align}
+            \item Step 2: 
             \begin{align}\tag{Step 2}\label{eqn:stepwise-lya-proof-step-2}
@@
                         + \frac{\alpha_k^2 \mu^2}{2\hat \gamma}\Vert y_k - v_k\Vert^2
-                    + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle,     
+                        + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle. 
                 \end{split}
             \end{align}
-        Simply adding both side of Equations \eqref{eqn:stepwise-lya-proof-step-1}, \eqref{eqn:stepwise-lya-proof-step-2}, it follows: 
+            \item Step 3: adding both side of Equations \eqref{eqn:stepwise-lya-proof-step-1}, \eqref{eqn:stepwise-lya-proof-step-2}, it follows: 
             \begin{align}\tag{Step 3}\label{eqn:stepwise-lya-proof-step-3}
@@
                         R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
-                \right), 
+                    \right). 
                 \end{split}
             \end{align}
+        \end{enumerate}
         To show \eqref{ineq:stepwise-lya-2}, it follows by subtracting $F(x^*)$ on \eqref{eqn:stepwise-lya-proof-step-3} which gives: 
@@
         }
+        % PROOF SUMMARIZATION ENDS ===========================================================
         Now, it remains to show \eqref{eqn:stepwise-lya-proof-step-1}, \eqref{eqn:stepwise-lya-proof-step-2}, \eqref{eqn:stepwise-lya-proof-step-3}. 
+        \\
         \textbf{Proof of \eqref{eqn:stepwise-lya-proof-step-1}}:
@@
 \section{Equivalent representations of R-WAPG}\label{sec:rwapg-equiv-repr}
-    This section reduces Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 
+    The goal of this section is to reduce Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 
     In the literatures, variants of Accelerated Proximal Gradient algorithm such as FISTA, V-FISTA has different representations. 

### 2025-02-14 Notebook LaTEX/Proposal/proposal.tex
>w<, fix cringe shit

@@
         In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are much more flexible. 
-        They generalize many existing sequences used in accelerated proximal gradient schemes. 
-        \par
-        This section demonstrates that several variants of FISTA in the literatures reduces to the R-WAPG method by setting up the R-WAPG sequences with additional assumptions. 
-        This section will also demonstrate that the convergence claim (Proposition \ref{prop:wagp-convergence}) holds, and it derives convergence rates consistent with results in the literatures.  
-        The table below shows the R-WAPG convergence results specialized into various settings. 
+        They generalize existing sequences used in accelerated proximal gradient schemes. 
+        Choosing the sequence $\alpha_k, \rho_k$ with some specific rules, it yields convergence results found in the literatures for Euclidean variants of FISTA. 
+        Table \ref{table:unify-nag-results} shows convergence results specialized to some FISTA variants found in the literatures. 
         \begin{table}[H]
@@
             }
+            \caption{Table showing the results of this section.}
+            \label{table:unify-nag-results}
         \end{table}
@@
         \end{remark}
+        Using the above lemma about R-WAPG sequence, it can derive the convergence rate of a FISTA variable proposed by Chambolle, Dossal \cite{chambolle_introduction_2016}. 
+        \begin{theorem}[FISTA first variant Chambolle, Dossal 2015]\label{thm:r-wapg-on-cham-doss}\;\\
+            Fix arbitrary $a \ge 2$.
+            Define $\forall k \ge 1$ the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ by 
+            \begin{align*}
+                \alpha_k &= a/(k + a), 
+                \\
+                \rho_k &= \frac{(k + a)^2}{(k + 1)(k + a + 1)}. 
+            \end{align*}
+            Consider the algorithm given by: 
+            \begin{tcolorbox}
+                Initialize any $y_1 = x_1$. 
+                \\
+                For $k = 1, 2, \ldots$, update: 
+                \begin{align*}
+                    & x_{k + 1} := y_k + L^{-1}\mathcal G_L(y_k), 
+                    \\
+                    & \theta_{t + 1} := \alpha_{k + 1}(\alpha_k^{-1} - 1),
+                    \\
+                    & y_{k + 1} := x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
+                \end{align*}    
+            \end{tcolorbox}
+            If $\mu = 0$, then $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid pair of R-WAPG sequence from Definition \ref{def:rwapg-seq} and the above algorithm is a valid form of R-WAPG. 
+            \par
+            Assume minimizer $x^*$ exists for function $F$. 
+            Then algorithm produces $(x_k)_{k \ge0}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O(\alpha_k^2)$. 
+        \end{theorem}
+        \begin{remark}
+            This algorithm described here is exactly the same algorithm being analyzed in the paper by Chambolle, Dossal \cite{chambolle_convergence_2015}. 
+        \end{remark}
+        Following a similar pattern, the lemma follows characterize a constant sequence of $\alpha_k, \rho_k$ for the R-WAPG sequences which enable us to characterize the linear convergence rate of all $\mu > 0$ strongly convex function with a fixed momentum parameter.
         \begin{lemma}[Constant R-WAPG sequences]\label{lemma:constant-rwapg-seq}
@@
         \end{lemma}
-        \begin{theorem}[FISTA first variant Chambolle, Dossal 2015]\label{thm:r-wapg-on-cham-doss}\;\\
-            Fix arbitrary $a \ge 2$.
-            Define $\forall k \ge 1$ the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ by 
-            \begin{align*}
-                \alpha_k &= a/(k + a), 
-                \\
-                \rho_k &= \frac{(k + a)^2}{(k + 1)(k + a + 1)}. 
-            \end{align*}
-            Consider the algorithm given by: 
-            \begin{tcolorbox}
-                Initialize any $y_1 = x_1$. 
-                \\
-                For $k = 1, 2, \ldots$, update: 
-                \begin{align*}
-                    & x_{k + 1} := y_k + L^{-1}\mathcal G_L(y_k), 
-                    \\
-                    & \theta_{t + 1} := \alpha_{k + 1}(\alpha_k^{-1} - 1),
-                    \\
-                    & y_{k + 1} := x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
-                \end{align*}    
-            \end{tcolorbox}
-            If $\mu = 0$, then $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid pair of R-WAPG sequence from Definition \ref{def:rwapg-seq} and the above algorithm is a valid form of R-WAPG. 
-            \par
-            Assume minimizer $x^*$ exists for function $F$. 
-            Then algorithm produces $(x_k)_{k \ge0}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O(\alpha_k^2)$. 
-        \end{theorem}
-        \begin{remark}
-            This algorithm described here is exactly the same algorithm being analyzed in the paper by Chambolle, Dossal \cite{chambolle_convergence_2015}. 
-        \end{remark}
         \begin{theorem}[Fixed momentum APG]\label{thm:fixed-momentum-fista}
@@
             In Nesterov's 2013 paper \cite{nesterov_gradient_2013}, he considers accelerated  minimization problem $\phi = f + \Psi$ with $f$ $L_f$ smooth and $\Psi$ being $\mu_\Psi \ge 0$ strongly convex.
-            \par
-            This detail on itself is not necessarily interesting, since without lost of generality, we can always do the splitting $f + \mu_\Psi/2 \Vert \cdot\Vert^2$ and $\Psi - \mu_\Psi/2\Vert \cdot\Vert^2$ instead so that the smooth part is $\mu_\Psi \ge 0$ strongly convex.
-            It's an interesting detail we should consider because: 
+            Here would be our question: 
+            \begin{quote}
+                Is it possible to include the a $\mu_\Psi$ into our R-WAPG framework? 
+            \end{quote}
+            \par
+            Without lost of generality, we can always do the splitting $f + \mu_\Psi/2 \Vert \cdot\Vert^2$ and $\Psi - \mu_\Psi/2\Vert \cdot\Vert^2$ instead so that the smooth part is $\mu_\Psi \ge 0$ strongly convex.
+            It's an interesting detail we should consider including because: 
             \begin{enumerate}
@@
             \par
-            Furthermore, Nesterov was not the only person who thought about it.
-            In Algorithm 5, Chambolle, Pock \cite{chambolle_introduction_2016} captures several variants of FISTA, and it assumes that $F = f + g$ where $f, g$ has strong convexity constant $\mu_f \ge 0, \mu_g \ge 0$ respective so $F$ is $\mu := \mu_f + \mu_g \ge 0$ strongly convex.
+            Besides Nesterov's contributions, Chambolle, Pock \cite{chambolle_introduction_2016} captures several variants of FISTA In Algorithm 5.
+            They assumed $F = f + g$ with $f, g$ being strongly convexity with constants $\mu_f \ge 0, \mu_g \ge 0$ respectively so $F$ is $\mu := \mu_f + \mu_g \ge 0$ strongly convex. 
             \par
@@
             Definition 1, 2, 3, 4, 5, introduced the ideas of: Quasi-strong convexity, Quadratic under approximation, Quadratic gradient growth, quadratic functional growth (recall that it was stated as a consequence of strong convexity in Lemma \ref{lemma:q-growth}), and Global Error bound conditions.
-            \par
             We focus on one of their comments on Catalyst by Lin et al. \cite{lin_universal_2015}. 
@@
             \end{quote}
-            Their idea of extension can be applied to inner loop $\mathbb M$, or out loop $\mathbb A$, either, or both. 
-            \par
-            Finally, it's worth noting that in the years before and after Necoara et al.'s paper and Catalyst, there were parallel developments around the ideas of extending Nesterov's accelerations and Catalyst to the nonconvex settings.
+            Hence, this is what we would describe the open question to be: 
+            \begin{quote}
+                Can we extend the linear convergence results of inner loop or outer loop of Catalyst Acceleration into settings weaker than strong convexity (Potentially nonconvex)? 
+            \end{quote}
+            In the coming parts, we will focus on developments in the literatures adjacent to the open question above. 
+            Objectives will be summarized at the end. 
+            There were parallel developments around the ideas of Nesterov's accelerations and Catalyst in the nonconvex settings during the years before Necoara et al.'s paper and Catalyst to current date.
             Paquette et al.
-\cite{paquette_catalyst_2018} were inspired by \cite{ghadimi_accelerated_2016} and showed that the Catalyst algorithm based on the gradient termination criterion analogous to C2 (see equation (13), (14) in their paper) can adapt to nonconvex settings and the norm of the gradient converges.
+\cite{paquette_catalyst_2018} were inspired by Ghadimi \cite{ghadimi_accelerated_2016} and showed that the Catalyst algorithm based on the gradient termination criterion analogous to C2 (see equation (13), (14) in their paper) can adapt to nonconvex settings and the norm of the gradient converges.
             However, it's at the expense of one additional evaluation of the proximal point method, and it requires evaluating the function value once per outer loop iteration. 
@@
             It is sometime referred to as ``Hessian Damping" in the literatures.  
-            There are three pillars that supported Catalyst Accelerations: 
+            \par
+            Now that the scope had been settled, let's consider major components of Catalyst Acceleration where extensions to the nonconvex settings can be made. 
+            There are three pillars that support Catalyst Accelerations: 
             \begin{enumerate}
@@
             See Khanh et al. \cite{khanh_inexact_2025} for an algorithmic framework of inexact proximal point method on weakly convex function. 
-            The class of weakly convex function is particularly interesting because it has convergance claim of the gradient norm in Ghadimi and Lan \cite{ghadimi_accelerated_2016}, and in Chapter 4 of the book preprint by Recht and Wright \cite{recht_optimization_nodate}.
-            It's unclear how their convergence theories can be combined with NAG in the non-convex case, but it's worth investigating. 
+            The class of weakly convex function is particularly interesting because it has convergence claim of the gradient norm in Ghadimi and Lan \cite{ghadimi_accelerated_2016}, and in Chapter 4 of the book preprint by Recht and Wright \cite{recht_optimization_nodate}.
+            It's unclear how their convergence theories can be combined with NAG in the nonconvex case, but it's worth investigating. 
+            Finally, we can summarize a rough sketch of ideas to explore that will assist the open question we posed. 
+            \begin{enumerate}
+                \item Does the convergence results modestly extend to the non-strongly convex settings described by Necoara \cite{necoara_linear_2019} et al.? 
+                \item Is it possible to extend the Nesterov's acceleration to non-convex settings such as convergence of gradient norm as described in Ghadimi \cite{ghadimi_accelerated_2016} without restarting?
+If so, what are the trade offs here if we wish to attain stronger convergence claims on the final iterates, or the function value?
+                \item Do there exist a way of extending inexact proximal point method to the nonconvex settings that also include Nesterov's acceleration? 
+            \end{enumerate}
             % \todoinline{

### 2025-02-18 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

@@
     \subsection{Motivations}
-        For simplicity consider minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$. 
-        Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$.
-        \par 
-        The Nesterov's acceleration scheme which was originally proposed in 1983 \cite{nesterov_method_1983} is a celebrated first order method for solving the minimization problem. 
-        Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
-        \begin{align}
-            & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
-            \\
-            & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
-            \\
-            & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
-            \\
-            & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
-        \end{align}\label{eqn:example-algorithm}
+        The Nesterov's acceleration scheme originally proposed in 1983 \cite{nesterov_method_1983} is a celebrated first order method for solving the minimization problem. 
         If the minimizer $x^*$ exists, then the optimality gap $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, a faster rate compared to gradient descent which is $\mathcal O(1/k)$. 
-        It's consider optimal in some sense and see Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018} for details. 
+        It's consider optimal in a certain sense, see Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018} for details. 
         However, things are not sunshine, rainbow and happily ever after because the above scheme is associated with the issue that if $F$ is $\mu > 0$ strongly convex, the optimality gap $F(x_k) - F(x^*)$ oscillates and converges sub-linearly, making it worse than gradient descent.
@@
         See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm.
+        \par
+        In the convex settings, the Variants Nesterov's Accelerated Gradient optimal to for cases when $\mu \ge 0$ and $\mu > 0$ are different. 
+        In this paper, we will show a unified framework for the convergence proof of both cases with a much relaxed condition for the recurrence of the momentum parameters used to extrapolate the iterates.
+        \todoinline{
+            $\blacksquare$: Improves the motivation parts here by starting without the math and then move onto the mathematics. 
+        }
+        For simplicity consider minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$. 
+        Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$.
+        We will list the following example algorithm of Nesterov's Accelerated Gradient to refer to while introducing the context and prior works. 
+        Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
+        \begin{align}
+            & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
+            \\
+            & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
+            \\
+            & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
+            \\
+            & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
+        \end{align}\label{eqn:example-algorithm}
 
@@
         Inspired specifically by the technique of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, firstly we present a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG) in Section \ref{sec:rwapg-formulation-convergence}.
-        It can upper bound $F(x_k) - F(x^*)$ for sequences $(t_k)_{k \ge 0}$ that doesn't follow Nesterov's update rule and it unifies the convergence results of several Euclidean variants of FISTA. 
+        It can upper bound $F(x_k) - F(x^*)$ for sequences $(t_k)_{k \ge 0}$ that doesn't follow Nesterov's update rule, and it unifies the convergence results of several Euclidean variants of FISTA. 
         Secondly, we present an alternative to restarting that performs well empirically inspired by a detail in the convergence proof of R-WAPG with extensive numerical experiments. 
@@
         \end{enumerate}
-        To show \eqref{ineq:stepwise-lya-2}, it follows by subtracting $F(x^*)$ on \eqref{eqn:stepwise-lya-proof-step-3} which gives: 
+        \todoinline{
+            $\blacksquare$: Make it clear that we are going to prove the end results here from the listed intermediate results. 
+        }
+        We will prove the intermediate results above later. 
+        Building upon these intermediate results, we are able to claim \eqref{ineq:stepwise-lya-2}. 
+        It follows by subtracting $F(x^*)$ on \eqref{eqn:stepwise-lya-proof-step-3} which gives: 
         \begin{align}
@@
         \end{align*}
-        }
-        % PROOF SUMMARIZATION ENDS ===========================================================
+        } % PROOF SUMMARIZATION ENDS ===========================================================
         Now, it remains to show \eqref{eqn:stepwise-lya-proof-step-1}, \eqref{eqn:stepwise-lya-proof-step-2}, \eqref{eqn:stepwise-lya-proof-step-3}. 
-        \\
+        \par\noindent
         \textbf{Proof of \eqref{eqn:stepwise-lya-proof-step-1}}:
@@
     In the next section, it continues to play a crucial role in describing several equivalent forms of the R-WAPG algorithm, and their corresponding convergence claim. 
+    \todoinline{\noindent
+        $\blacksquare$: This definition below doesn't directly contribute to the convergence proof, the recurrence relation is more important to the convergence proof.
+The constraints on the sequence is used to show the equivalent representations.
+    }
     \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}\;\\
@@
     \end{definition}
-    \begin{observation}\label{obs:r-wapg-observation-1}
-        The following is true: 
+    % \begin{observation}\label{obs:r-wapg-observation-1}
+    %     The following is true: 
+    %     \begin{enumerate}
+    %         \item $\rho_k > 0$ for all $k \ge 0$. 
+    %         \item $\forall k \ge 1: L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 +\mu\alpha_k$. 
+    %     \end{enumerate}
+    % \end{observation}
+    Not all properties of the R-WAPG sequences are used in the convergence proof, some other of its properties such as $\alpha_k \in (\mu/L, 1)$ plays a role much later on in Section \ref{sec:rwapg-equiv-repr}.
+    The following lemma states two consequences of the definition of the R-WAPG sequences which will play a crucial role in the convergence proof immediately after. 
+    \begin{lemma}{Consequences from the definition of R-WAPG Sequences}\label{lemma:r-wapg-seq-consequences}
+        Let sequence $(\alpha_k)_{k\ge 0}$ and $(\rho_k)_{k \ge0}$ be given by Definition \ref{def:rwapg-seq}, then they have: 
         \begin{enumerate}
@@
         \end{enumerate}
-
-    \end{observation}
+    \end{lemma}
+    \begin{proof}
+        The first item is obvious by $\alpha_k \in (\mu/L, 1)$. 
+        The second item is direct by definition of $\rho_k$ which has for all $k \ge 1$: 
+        \begin{align*}
+            (1 - \alpha_k)L \rho_{k - 1}\alpha_{k - 1}^2 + \mu\alpha_k
+            &= (1 - \alpha_k)L \left(
+                \frac{\alpha_{k}^2 - (\mu/L)\alpha_{k}}{(1 - \alpha_{k})\alpha_{k - 1}^2}
+            \right)\alpha_{k - 1}^2 + \mu\alpha_k
+            \\
+            &= (L\alpha_k^2 - \mu \alpha_k) + \mu \alpha_k = L\alpha_k^2. 
+        \end{align*}
+    \end{proof}
+    \par
     We now give Relaxed Weak Accelerated Proximal Gradient in details.
@@
     \end{definition}
-    \begin{observation}\label{obs:r-wapg-observation-2}
+    \begin{remark}\label{remark:rwapg-def}
         Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018} because $L\alpha_k^{2} = (1 - \alpha_k)L\alpha_{k - 1}^2 + \mu \alpha_k$.
@@
         \end{align*}
-        The third equality from Observation \ref{obs:r-wapg-observation-1}. 
-    \end{observation}
+        Therefore, the sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ fits the same recurrence relation from Lemma \ref{lemma:r-wapg-seq-consequences} (ii). 
+    \end{remark}
     Here is the main result of this section. 
@@
         We had demonstrated the base case. 
-        Next, for all $k = 2, 3, \ldots, N$, from Observation \ref{obs:r-wapg-observation-2}: 
+        Next, for all $k = 2, 3, \ldots, N$, from Remark \ref{remark:rwapg-def}: 
         \begin{align*}
@@
 \section{Equivalent representations of R-WAPG}\label{sec:rwapg-equiv-repr}
-    The goal of this section is to reduce Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 
+    The goal of this section is to reduce Definition \ref{def:wapg} into simpler forms that are equivalent to what commonly appears in the literatures. 
     In the literatures, variants of Accelerated Proximal Gradient algorithm such as FISTA, V-FISTA has different representations. 
-    This shows that R-WAPG provides a unified framework. 
+    Sometimes the same algorithm include two iterates $(x_k, y_k)$, sometimes they inlcude three iterates $(x_k, y_k, z_k)$. 
+    In this section we simplify R-WAPG to these representations commonly found in the literatures and showed that they are equivalent.
     These equivalent representations are listed in Definition \ref{def:r-wapg-intermediate}, \ref{def:r-wapg-st-form} and \ref{def:r-wapg-momentum-form}. 
-    These forms are equivalent under a subset of initial conditions. 
+    These forms are equivalent and they are crucial for proving the convergence of existing variants found in the literatures in the upcoming Section \ref{sec:rwapg-literatures}. 
     \par 
@@
         Specific instances of Accelerated Proximal Gradient algorithm that has the same form as the Definition \ref{def:r-wapg-intermediate}, Definition \ref{def:r-wapg-st-form} and Definition \ref{def:r-wapg-momentum-form} in the literatures are stated in the remarks that follows the definitions.
-
         \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
@@
             \end{align}
-            Then, it fits into the format of abstract similar triangle form Proposition \ref{prop:abs-st-form} and it follows that $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}(x_{k + 1} - x_k)\; \forall k \ge 1$.
+            Then, it fits into the format of abstract similar triangle form Proposition \ref{prop:abs-st-form}, and it follows that $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}(x_{k + 1} - x_k)\; \forall k \ge 1$.
             We shall verify the hypothesis that $L\delta_k = 1 + \tau_k + \xi_k$ later, for now substituting $\xi_k$ gives: 
@@
             \end{align}
-            The comming parts simplifies $y_k$ firstly for $k = 1$, then for all $k \ge 2$. 
-            by Definition \ref{def:r-wapg-st-form}, it follows that for all $k \ge 1$: 
+            The coming parts simplifies $y_k$ firstly for $k = 1$, then for all $k \ge 2$. 
+            By Definition \ref{def:r-wapg-st-form}, it follows that for all $k \ge 1$: 
             \begin{align}\label{eqn:third-eqv-repr-proof-step2}
@@
     \par
-    This section demonstrates that several variants of FISTA in the literatures reduces to the R-WAPG method by setting up the R-WAPG sequences with additional assumptions. 
-    This section will also demonstrate that the convergence claim (Proposition \ref{prop:wapg-convergence}) holds, and it derives convergence rates consistent with results in the literatures.  
-    The table below shows the R-WAPG convergence results specialized into various settings. 
+    Using the results from Section \ref{sec:rwapg-equiv-repr}, this section will demonstrate that several Euclidean variants of FISTA in the literatures reduce to our R-WAPG definition if a specific R-WAPG sequences with additional constraints.
+    As a result, (Proposition \ref{prop:wapg-convergence}) holds hence, substituting specialized of R-WAPG sequence $(\alpha_k)_{k \ge 0}$, we derive convergence rates consistent with results in the literatures for these variants of FISTA.
+    \par
+    The table below shows the R-WAPG convergence results unify convergence claims for various settings. 
+    The first row shows the generic convergence results of our R-WAPG. 
+    The rows after are algorithms found in the literatures. 
+    First columns states the assumption made for parameter $\mu$, the second and third columns show the specific examples of $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ specialized from Definition \ref{def:rwapg-seq}.
+    Last column shows the convergence rate on $F(x_k) - F^*$ which is the optimality gap and a theorem that proves the claim. 
+    \todoinline{\noindent
+        $\blacksquare$: Explain what this table shows. 
+    }
     \begin{table}[H]
+        \centering
         {\scriptsize
@@
 
+    \begin{theorem}[FISTA first variant Chambolle, Dossal 2015]\label{thm:r-wapg-on-cham-doss}\;\\
+        Fix arbitrary $a \ge 2$.
+        Define $\forall k \ge 1$ the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ by 
+        \begin{align*}
+            \alpha_k &= a/(k + a), 
+            \\
+            \rho_k &= \frac{(k + a)^2}{(k + 1)(k + a + 1)}. 
+        \end{align*}
+        Consider the algorithm given by: 
+        \begin{tcolorbox}
+            Initialize any $y_1 = x_1$. 
+            \\
+            For $k = 1, 2, \ldots$, update: 
+            \begin{align*}
+                & x_{k + 1} := y_k + L^{-1}\mathcal G_L(y_k), 
+                \\
+                & \theta_{t + 1} := \alpha_{k + 1}(\alpha_k^{-1} - 1),
+                \\
+                & y_{k + 1} := x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
+            \end{align*}    
+        \end{tcolorbox}
+        If $\mu = 0$, then $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid pair of R-WAPG sequence from Definition \ref{def:rwapg-seq} and the above algorithm is a valid form of R-WAPG. 
+        \par
+        Assume minimizer $x^*$ exists for function $F$. 
+        Then algorithm produces $(x_k)_{k \ge0}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O(\alpha_k^2)$. 
+    \end{theorem}
+    \begin{proof}
+        Proceeding stepwise, we want to specialize the results of Proposition \ref{prop:wapg-convergence} for the above choice of sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$  by completing the following steps.
+        \begin{enumerate}
+            \item Show that the $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given are valid R-WAPG sequences, so we can use the convergence results. 
+            \item Show $\rho_k \ge 1$ so Lemma \ref{lemma:inverted-fista-seq} (iii) applies. 
+            \item Simplify the conclusion of Proposition \ref{prop:wapg-convergence} by the previous two items. 
+        \end{enumerate}
+        To show (i), we verify equality $\alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_k \alpha_k^2$ because it's assumed $\mu = 0$ in this case. 
+        For all $k \ge 0$, the right side of the equality evaluates to 
+        \begin{align*}
+            \alpha_k^2 \rho_k(1 - \alpha_{k + 1}) &= 
+            \left(
+                \frac{a}{k + 1}
+            \right)^2 \left(
+                \frac{(k + a)^2}{(k + 1)(k + a + 1)}
+            \right)
+            \left(
+                1 - \frac{a}{k + 1 + a}
+            \right)
+            \\
+            &= \left(
+                \frac{a}{k + 1}
+            \right)^2 \left(
+                \frac{(k + a)^2}{(k + 1)(k + a + 1)}
+            \right)
+            \left(
+                \frac{k + 1}{k + 1 + a}
+            \right)
+            \\
+            &= \frac{a^2}{(k + a + 1)^2} = \alpha_{k + 1}^2. 
+        \end{align*}
+        Therefore, $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ is a pair of valid R-WAPG sequence. 
+        So, it can be used in the R-WAPG algorithm and represent it in R-WAPG Momentum Form in Definition \ref{def:r-wapg-momentum-form}. 
+        Using $\mu = 0$, it simplifies the momentum term in Definition \ref{def:r-wapg-momentum-form} and gives the rules of updates in the theorem statement. 
+        \par
+        Next, we show (ii). 
+        Observe that $(\forall k \ge 0)(\forall a \ge 2)$, $\rho_k$ has 
+        \begin{align*}
+            \rho_k &= \frac{(k + a)^2}{(k + 1)(k + a + 1)} = \frac{k^2 + a^2 + 2ak}{k^2 + ak + 2k + a + 1}
+            \\
+            &= (k^2 + a^2 + 2ak)(k^2 + 2ak - ak + 2k + a + 1)^{-1}
+            \\
+            &= (k^2 + a^2 + 2ak)(k^2 + 2ak + \underbrace{(2 - a)k + a + 1}_{\le a^2})^{-1} \ge 1. 
+        \end{align*}
+        Hence, (iii) in Lemma \ref{lemma:inverted-fista-seq} applies. 
+        By Proposition \ref{prop:wapg-convergence}, we have:
+        {\small\begin{align*}
+            & F(x_{k + 1}) - F(x^*) + \frac{L\alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
+            \\
+            & = F(x_{k + 1}) - F(x^*) + \frac{L\alpha_k^2}{2}\Vert x_{k + 1} - x^* + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k)\Vert^2
+            \\
+            & \le 
+            \left(
+                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
+            \right)
+            \left(
+                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
+            \right)
+            \left(
+                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
+            \right)
+            \\
+            &= 
+            \alpha_k^2
+            \left(
+                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
+            \right) 
+            & \text{By Lemma \ref{lemma:inverted-fista-seq} (iii)}
+            \\
+            &= 
+            \left(\frac{a}{k + a}\right)^2
+            \left(
+                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert x_1 - x^*\Vert^2
+            \right). 
+        \end{align*}}
+        We can replace $v_1$ to be $x_1$ by Proposition \ref{prop:r-wapg-momentum-repr}. 
+    \end{proof}
+    \begin{remark}
+        This algorithm described here is exactly the same algorithm being analyzed in the paper by Chambolle, Dossal \cite{chambolle_convergence_2015}. 
+    \end{remark}
+    \todoinline{
+        $\blacksquare$: Add some explanations here to brief the readers on what is about to come. 
+    }
+    Following a similar pattern, the lemma and theorem follow show linear convergence for all $\mu > 0$ strongly convex function with R-WAPG sequence $\alpha_k = \alpha \in (\mu/L, 1)$ that is a fixed constant.
     \begin{lemma}[Constant R-WAPG sequences]\label{lemma:constant-rwapg-seq}
@@
         \end{align*}
-
     \end{proof}
-
-    \begin{theorem}[FISTA first variant Chambolle, Dossal 2015]\label{thm:r-wapg-on-cham-doss}\;\\
-        Fix arbitrary $a \ge 2$.
-        Define $\forall k \ge 1$ the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ by 
-        \begin{align*}
-            \alpha_k &= a/(k + a), 
-            \\
-            \rho_k &= \frac{(k + a)^2}{(k + 1)(k + a + 1)}. 
-        \end{align*}
-        Consider the algorithm given by: 
-        \begin{tcolorbox}
-            Initialize any $y_1 = x_1$. 
-            \\
-            For $k = 1, 2, \ldots$, update: 
-            \begin{align*}
-                & x_{k + 1} := y_k + L^{-1}\mathcal G_L(y_k), 
-                \\
-                & \theta_{t + 1} := \alpha_{k + 1}(\alpha_k^{-1} - 1),
-                \\
-                & y_{k + 1} := x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
-            \end{align*}    
-        \end{tcolorbox}
-        If $\mu = 0$, then $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid pair of R-WAPG sequence from Definition \ref{def:rwapg-seq} and the above algorithm is a valid form of R-WAPG. 
-        \par
-        Assume minimizer $x^*$ exists for function $F$. 
-        Then algorithm produces $(x_k)_{k \ge0}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O(\alpha_k^2)$. 
-    \end{theorem}
-    \begin{proof}
-        Proceeding stepwise, we want to specialize the results of Proposition \ref{prop:wapg-convergence} for the above choice of sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$  by completing the following steps.
-        \begin{enumerate}
-            \item Show that the $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given are valid R-WAPG sequences, so we can use the convergence results. 
-            \item Show $\rho_k \ge 1$ so Lemma \ref{lemma:inverted-fista-seq} (iii) applies. 
-            \item Simplify the conclusion of Proposition \ref{prop:wapg-convergence} by the previous two items. 
-        \end{enumerate}
-        To show (i), we verify equality $\alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_k \alpha_k^2$ because it's assumed $\mu = 0$ in this case. 
-        For all $k \ge 0$, the right side of the equality evaluates to 
-        \begin{align*}
-            \alpha_k^2 \rho_k(1 - \alpha_{k + 1}) &= 
-            \left(
-                \frac{a}{k + 1}
-            \right)^2 \left(
-                \frac{(k + a)^2}{(k + 1)(k + a + 1)}
-            \right)
-            \left(
-                1 - \frac{a}{k + 1 + a}
-            \right)
-            \\
-            &= \left(
-                \frac{a}{k + 1}
-            \right)^2 \left(
-                \frac{(k + a)^2}{(k + 1)(k + a + 1)}
-            \right)
-            \left(
-                \frac{k + 1}{k + 1 + a}
-            \right)
-            \\
-            &= \frac{a^2}{(k + a + 1)^2} = \alpha_{k + 1}^2. 
-        \end{align*}
-        Therefore, $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ is a pair of valid R-WAPG sequence. 
-        So, it can be used in the R-WAPG algorithm and represent it in R-WAPG Momentum Form in Definition \ref{def:r-wapg-momentum-form}. 
-        Using $\mu = 0$, it simplifies the momentum term in Definition \ref{def:r-wapg-momentum-form} and gives the rules of updates in the theorem statement. 
-        \par
-        Next, we show (ii). 
-        Observe that $(\forall k \ge 0)(\forall a \ge 2)$, $\rho_k$ has 
-        \begin{align*}
-            \rho_k &= \frac{(k + a)^2}{(k + 1)(k + a + 1)} = \frac{k^2 + a^2 + 2ak}{k^2 + ak + 2k + a + 1}
-            \\
-            &= (k^2 + a^2 + 2ak)(k^2 + 2ak - ak + 2k + a + 1)^{-1}
-            \\
-            &= (k^2 + a^2 + 2ak)(k^2 + 2ak + \underbrace{(2 - a)k + a + 1}_{\le a^2})^{-1} \ge 1. 
-        \end{align*}
-        Hence, (iii) in Lemma \ref{lemma:inverted-fista-seq} applies. 
-        By Proposition \ref{prop:wapg-convergence}, we have:
-        {\small\begin{align*}
-            & F(x_{k + 1}) - F(x^*) + \frac{L\alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
-            \\
-            & = F(x_{k + 1}) - F(x^*) + \frac{L\alpha_k^2}{2}\Vert x_{k + 1} - x^* + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k)\Vert^2
-            \\
-            & \le 
-            \left(
-                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
-            \right)
-            \left(
-                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
-            \right)
-            \left(
-                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
-            \right)
-            \\
-            &= 
-            \alpha_k^2
-            \left(
-                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
-            \right) 
-            & \text{By Lemma \ref{lemma:inverted-fista-seq} (iii)}
-            \\
-            &= 
-            \left(\frac{a}{k + a}\right)^2
-            \left(
-                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert x_1 - x^*\Vert^2
-            \right). 
-        \end{align*}}
-        We can replace $v_1$ to be $x_1$ by Proposition \ref{prop:r-wapg-momentum-repr}. 
-    \end{proof}
-    \begin{remark}
-        This algorithm described here is exactly the same algorithm being analyzed in the paper by Chambolle, Dossal \cite{chambolle_convergence_2015}. 
-    \end{remark}
 
@@
             We apply Algorithm \ref{alg:free-rwapg}, M-FISTA, and V-FISTA. 
-            The following parameters are used to set up the problem: 
+            The following parameters are used to set up the numerical experiments: 
             \begin{enumerate}
@@
             The maximum, minimum and median values of $\delta_k$ are measured for all algorithms at each iteration and plotted as a ribbon. 
+            \todoinline{\noindent
+                $\blacksquare$: Another important feature of the numerical results is the hybrid behavior of the algorithm. 
+            }
+            \par
             Results are shown in Figure \ref{fig:simple-quadratic-NOG}.
             The solid line in the ribbon is the median value of $\delta_k$ across all experiment, the ribbon gives the maximum, minimum value of $\delta_k$ for each iteration across all experiments. 
-            FR-WAPG initially behaves similar to M-FISTA, but as the iteration goes on, it started to behave like V-FISTA.  
-            \par 
-            The most surprising feature here is the monotone descent, however, it's being numerical verified that the method is not monotone in general, it just looks monotone on the figure. 
+            One significant feature here is that FR-WAPG initially behaves similar to M-FISTA, but as the iteration goes on, it started to behave like V-FISTA. 
+            The second surprising feature is the monotone descent it shows on the graph visually. 
+            Unfortunately it's numerically verified that the method is not monotone in general, and it just looks monotone on the graph. 
             \begin{figure}[H]
@@
             \begin{enumerate}
-                \item $M, N$ are constants. They define matrix $A \in \RR^{M\times N}$ which has entires of i.i.d random variable taken from a standard normal distribution. 
+                \item $M, N$ are constants. They define matrix $A \in \RR^{M\times N}$ which has entries of i.i.d random variable taken from a standard normal distribution. 
                 \item $L, \mu$, are Lipschitz constant and the strong convexity constant for the smooth part of the objective which are not known prior.
-Hence they are estimated by $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$ prior to experiment to assist the V-FISTA algorithm.
+Consequently, they are estimated by $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$ prior to experiment to assist the V-FISTA algorithm.
                 \item $x^+ = [1\; -1\; 1 \; \cdots ]^T \in \RR^N$, it's a vector with alternating $1, -1$ in it. 

### 2025-02-18 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

@@
         In this paper, we will show a unified framework for the convergence proof of both cases with a much relaxed condition for the recurrence of the momentum parameters used to extrapolate the iterates.
-        \todoinline{
-            $\blacksquare$: Improves the motivation parts here by starting without the math and then move onto the mathematics. 
-        }
         For simplicity consider minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$. 
@@
         \end{enumerate}
-        \todoinline{
-            $\blacksquare$: Make it clear that we are going to prove the end results here from the listed intermediate results. 
-        }
         We will prove the intermediate results above later. 
@@
     In the next section, it continues to play a crucial role in describing several equivalent forms of the R-WAPG algorithm, and their corresponding convergence claim. 
-    \todoinline{\noindent
-        $\blacksquare$: This definition below doesn't directly contribute to the convergence proof, the recurrence relation is more important to the convergence proof.
-The constraints on the sequence is used to show the equivalent representations.
-    }
     \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}\;\\
@@
     Last column shows the convergence rate on $F(x_k) - F^*$ which is the optimality gap and a theorem that proves the claim. 
-    \todoinline{\noindent
-        $\blacksquare$: Explain what this table shows. 
-    }
     \begin{table}[H]
@@
     \end{remark}
-    \todoinline{
-        $\blacksquare$: Add some explanations here to brief the readers on what is about to come. 
-    }
     Following a similar pattern, the lemma and theorem follow show linear convergence for all $\mu > 0$ strongly convex function with R-WAPG sequence $\alpha_k = \alpha \in (\mu/L, 1)$ that is a fixed constant.
@@
             The maximum, minimum and median values of $\delta_k$ are measured for all algorithms at each iteration and plotted as a ribbon. 
-            \todoinline{\noindent
-                $\blacksquare$: Another important feature of the numerical results is the hybrid behavior of the algorithm. 
-            }
             \par

### 2025-02-22 Notebook LaTEX/R-WAPG/paper3.tex
>w<, fixing cringe shit fast

@@
 Primary 90C30, 90C25, 65K10; Secondary 65Y20. 
-\noindent{\bfseries Keywords: } 
-\\
+\\{\bfseries Keywords: } 
 Convex optimization, Nesterov's acceleration, Proximal gradient, Convergence rate.
@@
             \item $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex. 
-            \item $g: \RR^n \rightarrow \overline \RR$ is proper, closed and convex. 
+            \item $g: \RR^n \rightarrow \overline \RR$ is proper, closed and convex. The extended real is defined as $\overline \RR := \RR \cup \{\infty\}$. 
             \item Minimizer exists for the optimization problem: $F^* = \min_x \left\lbrace f(x) + g(x)\right\rbrace$. 
@@
     \end{assumption}
-    The extended real is defined as $\overline \RR := \RR \cup \{\infty, - \infty\}$. 
-    Using $\overline \RR$ we model a general convex function $g: \RR^n \rightarrow \overline{\RR}$ as a function on $\RR$.  
-    The domain has the definition $\dom(g) := \{x \in \RR^n : g(x) < \infty\}$. 
-    A proper function $g$ means that there exists some $x \in \dom(g)$ such that $g(x) > -\infty$. 
-    \par
     For $x \in \RR^n, y \in \RR^n$, we define: 
@@
     \begin{align*}
-        T_Ly &= \argmin_{x \in \RR^n} \left\lbrace
+        T_L(y) &:= \argmin_{x \in \RR^n} \left\lbrace
             g(x) + \langle \nabla f(y), x\rangle + L/2\Vert x - y\Vert^2
-        \right\rbrace = [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f], 
+        \right\rbrace = [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f](y), 
         \\
@@
         D_f(x, y): \RR^n \times \RR^n \rightarrow \RR 
-        \defeq f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 
+        \defeq (x, y)\mapsto f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 
     \end{align*}
@@
     \begin{proof}
-        For simplicity of notations, we write $T$ for $T_L$. 
+        For simplicity, we write $T$ for $T_L$. 
         The proof is direct algebra, and it starts by deriving an intermediate inequality from the quadratic growth condition of the model function.
@@
         \par
-        $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is $L + \mu$ strongly convex by Assumption \ref{ass:smooth-nsmooth-additive} and its definition. 
-        We see that it admits quadratic growth over the minimizer $Ty$ therefore for all $x \in \RR^n$ it follows that: 
+        $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is $L$ strongly convex by Assumption \ref{ass:smooth-nsmooth-additive} and its definition. 
+        We see that it admits quadratic growth over the minimizer $Ty$, therefore for all $x \in \RR^n$ it follows that: 
         {\smaller
@@
             - 
-            \frac{L + \mu}{2}\Vert x - Ty\Vert^2
+            \frac{L}{2}\Vert x - Ty\Vert^2
             \\
@@
             - 
-            \frac{L + \mu}{2}\Vert x - Ty\Vert^2
+            \frac{L}{2}\Vert x - Ty\Vert^2
             + D_f(Ty; y)
@@
             D_f(x, y) 
-            - \frac{L + \mu}{2}\Vert x - Ty\Vert^2
+            - \frac{L}{2}\Vert x - Ty\Vert^2
             + D_f(Ty; y)
@@
             + D_f(Ty; y)
-            - \frac{L + \mu}{2}\Vert x - Ty\Vert^2
+            - \frac{L}{2}\Vert x - Ty\Vert^2
             \\
@@
             + D_f(Ty; y)
-            - \frac{L + \mu}{2}\Vert x - Ty\Vert^2
-            \\
-            &\le 
+            - \frac{L}{2}\Vert x - Ty\Vert^2
+            \\
+            &=
             F(x) - F(Ty)
@@
             - D_f(x, y) 
-            + D_f(Ty, y). \quad \text{By $\mu \ge 0$}
+            + D_f(Ty, y).
         \end{align*}
@@
         \begin{align}
-            g_k &\defeq L(y_k - T_L y_k), 
+            g_k &\defeq L(y_k - T_L(y_k)), 
             \label{eqn:grad-map}
             \\
-            l_F(x; y_k) &\defeq F(T_Ly_k) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
+            l_F(x; y_k) &\defeq F(T_L(y_k)) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
             \label{eqn:lower-linearization}
@@
         \end{align}
-        Observe that by convexity of $F$, $\epsilon_k \ge 0$ for all $x_k, L > 0$. 
-        To see, use Theorem \ref{thm:prox-grad-ineq} and let $y = y_k, x = x_k$ which gives: 
-        \begin{align*}
-            F(x_k) - F(T_Ly_k)
-            - \langle L(y_k - T_Ly_k),x_k - y_k \rangle
-            - \frac{L}{2}\Vert y_k - T_Ly_k\Vert^2
-            - \frac{\mu}{2}\Vert x_k - y_k\Vert^2
-            &\ge 0
-            \\
-            \iff 
-            F(x_k) - F(T_Ly_k)
-            - \langle g_k,x_k - y_k \rangle
-            - \frac{1}{2L}\Vert g_k\Vert^2
-            &\ge 0. 
-        \end{align*}
+        % To see $\epsilon_k \ge 0$, use Theorem \ref{thm:prox-grad-ineq} and let $y = y_k, x = x_k$, by the definition $g_k = L(y_k - T_L(y_k))$ it has: 
+        % \begin{align*}
+        %     F(x_k) - F(T_L(y_k))
+        %     - \langle L(y_k - T_L(y_k)),x_k - y_k \rangle
+        %     - \frac{L}{2}\Vert y_k - T_Ly_k\Vert^2
+        %     - \frac{\mu}{2}\Vert x_k - y_k\Vert^2
+        %     &\ge 0
+        %     \\
+        %     \iff 
+        %     F(x_k) - F(T_L(y_k))
+        %     - \langle g_k,x_k - y_k \rangle
+        %     - \frac{1}{2L}\Vert g_k\Vert^2
+        %     &\ge 0. 
+        % \end{align*}
     \end{assumption}
@@
         \end{align*}
-        On the first equality \eqref{eqn:Q1}, we multiplied both side of the equation by $\hat\gamma_{k + 1}/\alpha_k \gamma_k$ and then grouped $y_k$. 
-        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma_{k + 1}$, then simplifies the denominator by rearranging \eqref{eqn:stepwise-wapg-eqn1} into $\hat \gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$.
-        \par
+        % On the first equality \eqref{eqn:Q1}, we multiplied both side of the equation by $\hat\gamma_{k + 1}/\alpha_k \gamma_k$ and then grouped $y_k$. 
+        % The last equality comes by multiplying both the numerator and denominator by $\hat \gamma_{k + 1}$, then simplifies the denominator by rearranging \eqref{eqn:stepwise-wapg-eqn1} into $\hat \gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$.
+        % \par
         To see \eqref{eqn:Q2}, consider \eqref{eqn:stepwise-wapg-eqn2}: 
@@
             (\hat \gamma_k - \gamma_k - \alpha_k \mu) x_k 
+            & \text{by \eqref{eqn:stepwise-wapg-eqn1}}
             \\
@@
         \end{align*}
-        On the second equality that follows, we substituted $\hat\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$ given by \eqref{eqn:stepwise-wapg-eqn1}. 
-        \par
-        Finally, we start by considering the LHS of \eqref{eqn:Q3} and it follows that: 
+        % On the second equality that follows, we substituted $\hat\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$ given by \eqref{eqn:stepwise-wapg-eqn1}. 
+        \par
+        Using \eqref{eqn:Q1}, \eqref{eqn:Q2}, we can show \eqref{eqn:Q3}. 
+        Indeed,
         \begin{align*}
@@
         Let $k \in \mathbb Z_+$, $R_k \in \RR$. 
-        Given any $v_k, x_k$ and $\gamma_k > 0$ and $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}, \alpha_k$ that satisfies Definition \ref{def:stepwise-wapg}. 
-        Define: 
+        Given any $v_k, x_k$ and $\gamma_k > 0$ and $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}, \alpha_k$ that satisfy Definition \ref{def:stepwise-wapg}. 
+        With $\epsilon_k$ given by \eqref{eqn:regret}, define: 
         \begin{align}\label{eqn:stepwise-lya-1}
@@
         } % PROOF SUMMARIZATION ENDS ===========================================================
-        Now, it remains to show \eqref{eqn:stepwise-lya-proof-step-1}, \eqref{eqn:stepwise-lya-proof-step-2}, \eqref{eqn:stepwise-lya-proof-step-3}. 
-        \par\noindent
         \textbf{Proof of \eqref{eqn:stepwise-lya-proof-step-1}}:
@@
         Adding the RHS of \eqref{expr:stepwise-lya-expr2.2}, \eqref{eqn:stepwise-lya-proof-eqn1} gives: 
-        \begin{align}\label{eqn:stepwise-lya-proof-eqn3}
+        \begin{align}
         \begin{split}
@@
                 + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle
-            \\
+        \end{split}\nonumber
+        \\
+        \begin{split}  
             &= 
@@
                 + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle.     
-        \end{split}
+        \end{split}\label{eqn:stepwise-lya-proof-eqn3}
         \end{align}
@@
     \begin{remark}
-        Given $y_k$, we can choose to increase $\mu_\kappa = 2D_f(x^*, y_k)/\Vert y_k - x^*\Vert^2 \ge \mu$ which also works on \eqref{ineq:stepwise-lya-proof-ineq4}.
+        Given $y_k$, we can choose to increase $\mu_k = 2D_f(x^*, y_k)/\Vert y_k - x^*\Vert^2 \ge \mu$ which also works on \eqref{ineq:stepwise-lya-proof-ineq4}.
         This is true by the intermediate steps taken to prove Theorem \ref{thm:prox-grad-ineq}. 
@@
         \begin{tcolorbox}
-            For $k=1, 2, 3, \cdots$
-            \begin{align*}
-                \gamma_k &:= \rho_{k -1}L\alpha_{k - 1}^2, 
-                \\
-                \hat \gamma_{k + 1} & := (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2, 
-                \\
-                y_k &= 
+            For $k=1, 2, 3, \ldots$
+            \begin{align*}
+                \gamma_k &\defeq \rho_{k -1}L\alpha_{k - 1}^2, 
+                \\
+                \hat \gamma_{k + 1} & \defeq (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2, 
+                \\
+                y_k &\defeq 
                 (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
                 \\
-                g_k &= \mathcal G_L y_k, 
-                \\
-                v_{k + 1} &= 
+                g_k &\defeq \mathcal G_L (y_k), 
+                \\
+                v_{k + 1} &\defeq 
                 \hat\gamma^{-1}_{k + 1}
@@
                 \\
-                x_{k + 1} &= T_L y_k. 
+                x_{k + 1} &\defeq T_L y_k. 
             \end{align*}    
@@
     \begin{remark}\label{remark:rwapg-def}
-        Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018} because $L\alpha_k^{2} = (1 - \alpha_k)L\alpha_{k - 1}^2 + \mu \alpha_k$.
-        \par
         For all $k \ge 1$, the algorithm chains together the sequence of $(\hat \gamma_{k+1})_{k \ge 1}$ and $(\gamma_k)_{k \ge 1}$ in Definition \ref{prop:stepwise-lyapunov} through the equalities: 
@@
         Therefore, the sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ fits the same recurrence relation from Lemma \ref{lemma:r-wapg-seq-consequences} (ii). 
+        \par
+        Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018} because $L\alpha_k^{2} = (1 - \alpha_k)L\alpha_{k - 1}^2 + \mu \alpha_k$.
     \end{remark}
@@
         Let vector sequence $(y_k, v_{k}, x_{k})_{k \ge 1}$ and R-WAPG sequences $\alpha_k, \rho_k$ be given by Definition \ref{def:wapg}. 
+        Let $\epsilon_k$ be given by \eqref{eqn:regret}. 
         Define $R_1 = 0$ and suppose that for $k = 1, 2, \ldots, N$, we have $R_k$ recursively given by: 
@@
     \begin{remark}        
-        The choice of $\rho_k = 1$ reproduces traditional choice of sequences for the APG algorithm. 
-        The above claim showed that there exists $\rho_k > 1$, or $\rho_k < 1$ where convergence of $F(x_k) - F(x^*)$ remains possible. 
+        The choice of $\rho_k = 1$ reproduces traditional choice of sequences for the Accelerated Proximal Gradient (APG) algorithm. 
+        % The above claim showed that there exists $\rho_k > 1$, or $\rho_k < 1$ where convergence of $F(x_k) - F(x^*)$ remains possible. 
     \end{remark}
@@
     In the literatures, variants of Accelerated Proximal Gradient algorithm such as FISTA, V-FISTA has different representations. 
-    Sometimes the same algorithm include two iterates $(x_k, y_k)$, sometimes they inlcude three iterates $(x_k, y_k, z_k)$. 
+    Sometimes the same algorithm include two iterates $(x_k, y_k)$, sometimes they include three iterates $(x_k, y_k, z_k)$. 
     In this section we simplify R-WAPG to these representations commonly found in the literatures and showed that they are equivalent.
     These equivalent representations are listed in Definition \ref{def:r-wapg-intermediate}, \ref{def:r-wapg-st-form} and \ref{def:r-wapg-momentum-form}. 
-    These forms are equivalent and they are crucial for proving the convergence of existing variants found in the literatures in the upcoming Section \ref{sec:rwapg-literatures}. 
+    These forms are equivalent, and they are crucial for proving the convergence of existing variants found in the literatures in the upcoming Section \ref{sec:rwapg-literatures}. 
     \par 
@@
     \end{align*}
-    To start, the following proposition on ``abstract similar triangle form'' were made to simplify arguments and notations to make nicer proofs. 
+    To start, the following proposition on ``abstract similar triangle form'' were made to simplify arguments and notations and to make cleaner proofs. 
     % SECTION INTRODUCTION ENDS 
@@
         If $1 + \xi_k + \tau_k = L\delta_k\; \forall k \ge 1$, then for all $k \ge 1$: 
-        $$
+        \begin{align}\label{eqn:abs-st-key}
             v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}\tau_k(x_{k + 1} - x_k). 
-        $$
+        \end{align}
         Which makes the algorithm a similar triangle form. 
@@
             \\
+            \iff 
             v_{k + 1} - x_{k + 1}
@@
             (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_t - \tau_k x_k - \delta_t \mathcal G_L(y_k))
-            - (y_k - L^{-1}\mathcal G_Ly_k)
+            - (y_k - L^{-1}\mathcal G_L(y_k))
             \\
@@
             (1 + \xi_k)^{-1}(\tau_ky_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
-            + L^{-1}\mathcal G_Ly_k
+            + L^{-1}\mathcal G_L(y_k)
             \\
@@
                 \begin{align*} 
-                    & y_{k} = 
+                    & y_{k} \defeq 
                     \left(
@@
                     \left(
-                        v_{k + 1} + 
+                        v_{k} + 
                         \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
@@
                     \\
-                    & x_{k + 1} = 
+                    & x_{k + 1} \defeq 
                     y_k - L^{-1} \mathcal G_L y_k, 
                     \\
-                    & v_{k + 1} = 
+                    & v_{k + 1} \defeq 
                     \left(
@@
                 \begin{align*}
-                    & y_k = 
+                    & y_k \defeq 
                     \left(
@@
                     \\
-                    & x_{k + 1} = 
+                    & x_{k + 1} \defeq 
                     y_k - L^{-1} \mathcal G_L y_k, 
                     \\
-                    & v_{k + 1} = 
+                    & v_{k + 1} \defeq 
                     x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k). 
@@
             To see graphical visualization on why such term is used to describe the APG algorithm in the literatures, see 
-            (3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}.
+            Sections (3.1), (4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}.
         \end{remark}
@@
                 \begin{align*}
-                    & x_{k + 1} = y_k - L^{-1}\mathcal G_Ly_k, 
+                    & x_{k + 1} \defeq y_k - L^{-1}\mathcal G_Ly_k, 
                     \\
                     & 
-                    y_{k + 1} = 
+                    y_{k + 1} \defeq 
                     x_{k + 1} + 
@@
             This format fits with (2.2.19) in Nesterov's book \cite{nesterov_lectures_2018}, however, the sequence $(\alpha_k)_{k \ge 0}$ would be given by a different rule. 
-            See Theorem \ref{thm:r-wapg-on-cham-doss} and Lemma \ref{lemma:inverted-fista-seq} to see a specific choice of $(\alpha_k)_{k \ge0}, (\rho_k)_{ k\ge 0}$ such this equivalent form of R-WAPG is in fact two possible variants of the FISTA algorithm.
+            See Theorem \ref{thm:r-wapg-on-cham-doss} and Lemma \ref{lemma:inverted-fista-seq} for a specific choice of $(\alpha_k)_{k \ge0}, (\rho_k)_{ k\ge 0}$ such that this equivalent form of R-WAPG is in fact two possible variants of the FISTA algorithm.
         \end{remark}
 
-    \subsection{Proofs of equivalent representations of R-WAPG}
-        \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\
+    \subsection{Derivations of equivalent representations of R-WAPG}
+        \begin{proposition}[R-WAPG intermediate form]\label{prop:wapg-first-equivalent-repr}\;\\
             If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}), 
@@
 
-        \begin{proposition}[Second equivalent representation of R-WAPG]\label{prop:wagp-st-form}\;\\
+        \begin{proposition}[R-WAPG similar triangle form]\label{prop:wagp-st-form}\;\\
             Let iterates $(y_k, x_{k}, v_{k})_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge 0}$ be given by Definition \ref{def:r-wapg-intermediate}. 
@@
             Then, it fits into the format of abstract similar triangle form Proposition \ref{prop:abs-st-form}, and it follows that $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}(x_{k + 1} - x_k)\; \forall k \ge 1$.
-            We shall verify the hypothesis that $L\delta_k = 1 + \tau_k + \xi_k$ later, for now substituting $\xi_k$ gives: 
+            We shall verify the hypothesis that $L\delta_k = 1 + \tau_k + \xi_k$ later.
+            Substituting $\xi_k$ into \eqref{eqn:abs-st-key} gives: 
             \begin{align*}
@@
 
-        \begin{proposition}[Third equivalent representation of R-WAPG]\label{prop:r-wapg-momentum-repr}
+        \begin{proposition}[R-WAPG momentum form]\label{prop:r-wapg-momentum-repr}
             \;\\
@@
             \end{align}
-            The coming parts simplifies $y_k$ firstly for $k = 1$, then for all $k \ge 2$. 
+            Simplifying $y_k$ firstly for $k = 1$, then for all $k \ge 2$. 
             By Definition \ref{def:r-wapg-st-form}, it follows that for all $k \ge 1$: 
@@
             \end{align}
-            For all $k\ge 1$, substitute RHS of \eqref{eqn:third-eqv-repr-proof-step1} yields: 
+            For all $k\ge 1$, substitute RHS of \eqref{eqn:third-eqv-repr-proof-step1} into the above yields: 
             {\small
@@
             \begin{align*}
-                y_1 &= (L - \mu)^{-1}(L(\alpha_1 - \mu)x_1 + (L - L\alpha_1)x_1)
-                \\
-                &= (L - \mu)^{-1}(L(\alpha_1 - \mu)x_1 + (L - L \alpha_1)x_1)
+                y_1 &= (L - \mu)^{-1}((L\alpha_1 - \mu)x_1 + (L - L\alpha_1)x_1)
+                \\
+                &= (L - \mu)^{-1}((L\alpha_1 - \mu)x_1 + (L - L \alpha_1)x_1)
                 \\
@@
             \begin{tabular}{l}
-                $\mathcal O \left(\max(1 - \alpha, 1 - \mu/(\alpha L))^{k} \right)$\\
+                $\mathcal O \left(\left(1 - \min\left(\mu/(\alpha L), \alpha\right)\right)^{k}\right)$\\
                 (Theorem \ref{thm:fixed-momentum-fista})
@@
     \end{table}
-    The lemma follows characterizes momentum sequences in the literatures using Definition \ref{def:rwapg-seq}. 
+    The lemma follows characterizes momentum sequences in Chambolle and Dossal \cite{chambolle_convergence_2015} using Definition \ref{def:rwapg-seq}. 
     \begin{lemma}[R-WAPG sequences as inverted FISTA sequence]\label{lemma:inverted-fista-seq}
-        Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 
+        Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}. 
         If $\mu = 0, \rho_k \ge 1\; \forall k \ge 0$, and $\alpha_0 = 1$, then: 
         \begin{enumerate}
-            \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$
+            \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$.
             \item Let $t_k := \alpha_k^{-1}$, then $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``Inverted FISTA sequence''. 
@@
             \\
-            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 & \mu = 0 \text{ assumed } 
+            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 & 
+            (\mu = 0 \text{ assumed } )
             \\
@@
             & \ge (1 - \alpha_{k + 1})\alpha_k^2 
-            &  \rho_k \ge 1
+            &  (\rho_k \ge 1)
             \\
@@
         \end{align*}
-        When $k = 0$, it has $\alpha_0 = 1$. 
-        By definition of $\rho_0$ we have 
-        \begin{align*}
-            \alpha_1^2 &= 
-            (1 - \alpha_1)\alpha_0^2\rho_0 \underset{\mu = 0}{=}
-            \frac{\alpha_1^2}{\alpha_0^2(1 - \alpha_1)}(1 - \alpha_1)\alpha_0^2 = \alpha_1^2. 
+        We need to verify the base case for $k = 0$. 
+        Since $\alpha_0 = 1$, it has: 
+        \begin{align*}
+            \alpha_1^2 &= (1 - \alpha_1)\rho_0\alpha_0^2
+            \\
+            &\ge (1 - \alpha_1)\alpha_0^2
+            \\
+            &= (1 - \alpha_1)
+            \\
+            \iff 
+            1 &\ge \alpha_1^{-2} - \alpha_1^{-1}. 
         \end{align*}
@@
     \begin{remark}
-        The sequence $t_k$ is exactly the same as in Theorem 3.1 of Chambolle, Dossal \cite{chambolle_convergence_2015}. 
+        The sequence $t_k$ is exactly the same as in Chambolle, Dossal \cite[Theorem 3.1, 8]{chambolle_convergence_2015}. 
     \end{remark}
-
     \begin{theorem}[FISTA first variant Chambolle, Dossal 2015]\label{thm:r-wapg-on-cham-doss}\;\\
@@
                 \\
-                & \theta_{t + 1} := \alpha_{k + 1}(\alpha_k^{-1} - 1),
+                & \theta_{k + 1} := \alpha_{k + 1}(\alpha_k^{-1} - 1),
                 \\
@@
             \left(
-                \frac{a}{k + 1}
+                \frac{a}{k + a}
             \right)^2 \left(
@@
             &= \left(
-                \frac{a}{k + 1}
+                \frac{a}{k + a}
             \right)^2 \left(
@@
     Following a similar pattern, the lemma and theorem follow show linear convergence for all $\mu > 0$ strongly convex function with R-WAPG sequence $\alpha_k = \alpha \in (\mu/L, 1)$ that is a fixed constant.
+
     \begin{lemma}[Constant R-WAPG sequences]\label{lemma:constant-rwapg-seq}
@@
             $\rho_k := \rho=\left(1-r^{-1}\sqrt{q}\right)\left(1 - r \sqrt{q}\right)^{-1} > 0$, hence it's a pair of valid R-WAPG sequence. 
-            \item The momentum terms $\theta_{t + 1}$ in Definition \ref{def:r-wapg-momentum-form}, which we denoted by $\theta$ is the constant:\\ $\theta = (1 - r^{-1}\sqrt{q})(1 - r\sqrt{q})(1- q)^{-1}$
-            \item When $r = 1$, $\theta = (1- \sqrt{q})(1 + \sqrt{q})^{-1}$. 
-            \item For all $r \in \left(1, \sqrt{q^{-1}}\right)$, $\rho > 1$; for all $r \in \left(\sqrt{q}, 1\right]$ $\rho \le 1$. 
-            \item For all $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, $\max(\rho, 1)(1 - \alpha) = \max\left(1 - r\sqrt{q}, 1 - r^{-1}q\right)$. 
+            \item The momentum term $\theta_{k + 1}=\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1})$ in Definition \ref{def:r-wapg-momentum-form}, denoted by $\theta$ is the constant: $\theta = (1 - r^{-1}\sqrt{q})(1 - r\sqrt{q})(1- q)^{-1}$
+            \item When $r = 1$, we have $\theta = (1- \sqrt{q})(1 + \sqrt{q})^{-1}$. 
+            \item For all $r \in \left(1, \sqrt{q^{-1}}\right)$, we have $\rho > 1$; for all $r \in \left(\sqrt{q}, 1\right]$ we have $\rho \le 1$. 
+            \item For all $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, the equality $\max(\rho, 1)(1 - \alpha) = 1 - \min\left(\frac{\mu}{\alpha L}, \alpha\right)$ holds. 
         \end{enumerate}
@@
         \end{align*}
-        Therefore, $\alpha_k \in (\mu/L, 1)$. 
+        Therefore, $\alpha_k = \alpha \in (\mu/L, 1)$. 
         To see $\rho_k$, by definition it has 
@@
         \par
-        Finally, to show (v), we consider by cases: 
-        \begin{enumerate}
-            \item[Case A:] When $r \in \left(1, \sqrt{q^{-1}}\right)$, we have $\rho > 1$ by (iii), meaning that $1 - r^{-1}\sqrt{q} > 1 - r \sqrt{q}$. $\rho > 1 \implies \max(\rho, 1) = \rho$ hence 
-                \begin{align*}
-                    \max(\rho, 1)(1 - \alpha) &= \rho(1- \alpha)
-                    = \frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}}(1 - r \sqrt{q}) = 1 - r^{-1}\sqrt{q}. 
-                \end{align*}
-                In this case, the larger one of the two values: $\left\lbrace1 - \rho^{-1}\sqrt{q}, 1 - r\sqrt{q}\right\rbrace$ is taken. 
-            \item[Case B:] When $r \in \left(\sqrt{q}, 1\right]$, we have $\rho \le 1$ by (iii); hence $1 - r^{-1}\sqrt{q} \le 1 - r \sqrt{q}$ and $\max(1,\rho) = 1$ therefore: 
-            \begin{align*}
-                \max(1, \rho)(1 - \alpha) = (1 - \alpha) = 1 - r \sqrt{q}. 
-            \end{align*}
-            Once again, the larger one of the quantity: $1 - r \sqrt{q}$ among $\{1 - r^{-1}\sqrt{q}, 1 - r\sqrt{q}\}$ is taken. 
-        \end{enumerate}
-        Therefore, for all vales of $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$ are completed by cases: (A), (B).
-        The largest of the value among $\{1 - r \sqrt{q}, 1 - r^{-1}\sqrt{q}\}$ is always taken. 
-        Therefore, it has: 
-        \begin{align*}
-            \max(1, \rho)(1 - \alpha) = \max\left(1 - r\sqrt{q}, 1 - r^{-1}\sqrt{q}\right). 
+        Finally, to show (v), consider substituting $\rho, \alpha$ in terms of $r$: 
+        \begin{align*}
+            \max(\rho, 1)(1 - \alpha) &= 
+            \max(\rho(1 - \alpha), (1 - \alpha))
+            \\
+            &= \max\left(
+                \frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}}(1 - \alpha), (1 - \alpha)
+            \right) 
+            \\
+            &= 
+            \max\left(
+                \frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}}(1 - r\sqrt{q}), (1 - r\sqrt{q})
+            \right) 
+            \\
+            &= \max\left(1 - r^{-1}\sqrt{q}, 1 - r \sqrt{q}\right)
+            \\
+            &= 1 - \min(\sqrt{q}r^{-1}, r\sqrt{q}). 
+        \end{align*}
+        We used the fact that $(1 - \alpha) > 0, \sqrt{q} > 0$ and (i) for substituting $\rho$. 
+        Now, by definition $r = \alpha/\sqrt{q}$ and $q = \mu/L$, it can be represented by
+        \begin{align*}
+            1 - \min\left(
+                \sqrt{q}\left(\frac{\sqrt{q}}{\alpha}\right), \alpha
+            \right) &=
+            1 - \min\left(
+                q/\alpha, \alpha
+            \right) = 
+            1 - \min\left(\frac{\mu}{\alpha L}, \alpha\right). 
         \end{align*}
@@
         \end{tcolorbox}
-        Then the algorithm generates $(x_k)_{k \ge 1}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O\left(\max(1 - r\sqrt{q}, 1 - r^{-1}\sqrt{q})^k\right)$. 
+        Then the algorithm generates $(x_k)_{k \ge 1}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O\left(\left(1 - \min\left(\mu/(\alpha L), \alpha\right)\right)^k\right)$. 
     \end{theorem}
@@
         The algorithm presented here is the same as the R-WAPG momentum form as given by Definition \ref{def:r-wapg-momentum-form} because the term $\theta$ from Lemma \ref{lemma:constant-rwapg-seq} matches up with Definition \ref{def:r-wapg-momentum-form} by (ii) in Lemma \ref{lemma:constant-rwapg-seq}.
-        Then, Proposition \ref{prop:wapg-convergence} applies and it follows that: 
+        Then, Proposition \ref{prop:wapg-convergence} applies,and it follows that: 
         \begin{align*}
@@
             \\
-            &= \max(1 - r\sqrt{q}, 1 - r^{-1}\sqrt{q})^k
+            &= \left(1 - \min\left(\frac{\mu}{\alpha L}, \alpha\right)\right)^k
             \left(
@@
         When $r = 1$, the algorithm described above is exactly the same as the V-FISTA algorithm specified in (10.7.7) of Beck's book \cite{beck_first-order_2017}. 
+        The above theorem gives convergence rate for a much relax choice of momentum parameter $\theta$ generalizing the convergence of constant step size FISTA to all convex stronlgy convex function and all possible $\alpha_k \in (\mu/L, 1)$.
+        In addition, the convergence claim of R-WAPG holds for any $\mu$ smaller than the strong convexity modulus of $f$ that is not zero making the bounds $r \in (\sqrt{q}, \sqrt{q^{-1}})$ looser. 
     \end{remark}
@@
         {\footnotesize
-        \STATE{\textbf{Input: } $f, g, x_0, L > \mu \ge 0, \in \RR^n, N \in \N$}
-        \STATE{\textbf{Initialize: }$y_0 := x_0;L := 1; \mu := 1/2; \alpha_0 = 1;$}
+        \STATE{\textbf{Input: } $f, g, L > \mu \ge 0, x_0 \in \RR^n, N \in \N$}
+        \STATE{\textbf{Initialize: }$y_0 := x_0;L_0 := 1; \mu_0 := 1/2; \alpha_0 = 1$;}
         \STATE{\textbf{Compute: } $f(y_k)$; }
         \FOR{$k = 0, 1, 2, \cdots, N$}
-            \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$;}
-            \WHILE{$L/2\Vert x^+ - y_k\Vert^2 < D_f(x^+, y_k)$}
-                \STATE{$L:= 2L$;}
-                \STATE{$x^+ = [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$; }
+            \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L_k^{-1}\partial g]^{-1}(y_k - L_k^{-1}\nabla f(y_k))$;}
+            \WHILE{$L_k/2\Vert x^+ - y_k\Vert^2 < D_f(x^+, y_k)$}
+                \STATE{$L_k:= 2L_k$;}
+                \STATE{$x^+ = [I + L_k^{-1}\partial g]^{-1}(y_k - L_k^{-1}\nabla f(y_k))$; }
             \ENDWHILE
             \STATE{$x_{k + 1} := x^+$;}
-            \STATE{$\alpha_{k + 1} := (1/2)\left(\mu/L - \alpha_{k}^2 + \sqrt{(\mu/L - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;}
+            \STATE{$\alpha_{k + 1} := (1/2)\left(\mu_k/L_k - \alpha_{k}^2 + \sqrt{(\mu_k/L_k - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;}
             \STATE{$\theta_{k + 1} := \alpha_k(1 - \alpha_k)/(\alpha_k^2 + \alpha_{k + 1})$;}
@@
             \STATE{\textbf{Compute: } $f(y_{k + 1})$}
-            \STATE{$\mu := (1/2)(2D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2) + (1/2)\mu$;}
+            \STATE{$\mu_k := D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2 + (1/2)\mu_k$;}
         \ENDFOR
@@
     \par 
-    Sections of $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg} can be an R-WAPG sequence making the convergence result (Proposition \ref{prop:wapg-convergence}) of R-WAPG is relevant to a limited extend.
-    For the full sequence $(\alpha_k)_{k \ge0}$ to be an R-WAPG sequence requires additional assumption that none of the estimate has $\tilde \mu = L$. 
-    Let $\tilde \mu_k$ be an estimate produced by the algorithm and assume that it satisfies that $\tilde \mu_k/ L \in [0, 1)$ and $\alpha_k \in (\mu/L, 1)$.
-    Assuming inductively that $q = \tilde \mu_k/L$,  $\alpha_k \in (\mu/L, 1)$, then 
+    Suppose that initial $L$ given as input to Algorithm \ref{alg:free-rwapg} satisfies $L/2 \ge D_f(x, y)/\Vert x - y\Vert^2\;\forall x, y \in \RR^n$. 
+    Then, the Lipschitz line search is not triggered and $L_k = L$ for all $k = 1, \ldots, N$. 
+    Let $\mu = (1/2)L$ so it may not be a lower bound on the strong convexity constant for $f$. 
+    With the additional assumption that the estimated $\mu_k < L$, the sequence $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg}. 
+    Let's verify that $(\alpha_k)_{k \ge 0}$ is an R-WAPG sequence hence the convergence result (Proposition \ref{prop:wapg-convergence}) of R-WAPG applies. 
+    \par
+    Let $\mu_k$ be an estimate produced by the algorithm and assume that it satisfies that $\mu_k/ L \in [0, 1)$ and $\alpha_k \in (\mu/L, 1)$.
+    Assuming inductively that $q = \mu_k/L$,  $\alpha_k \in (\mu/L, 1)$, we have 
     \begin{align*}
@@
             q - \alpha_k^2 + \sqrt{
-                (\alpha_k^2 - q + 2)^2 + 2q - 4
+                (\alpha_k^2 - q + 2)^2 + 4q - 4
             }
@@
     \end{align*}
-    Here we used the assumption that $q \in (0, 1)$ so $2q - 4 < 0$ always. 
+    $q \in (0, 1)$ by assumption $\mu < L$ so $4q - 4 < 0$ always. 
     It is not hard to see that $\alpha_{k + 1} > \mu/L$ as well. 
     Therefore, $\alpha_k \in (0, 1)$. 
-    In the very unlikely case when $q = 1$, Algorithm \ref{alg:free-rwapg} has $\theta_k = 0$, and it performs one step of proximal gradient descent. 
+    To prvent the case $\alpha_k = 1$, we may always force the esimate $\mu = L/2$ whenever $\mu > L/2$. 
+    % In the very unlikely case when $q = 1$, Algorithm \ref{alg:free-rwapg} has $\theta_k = 0$, and it performs one step of proximal gradient descent. 
     \subsection{Numerical experiments}
         This section showcases results for the numerical experiments conducted using FR-WAPG algorithm (Algorithm \ref{alg:free-rwapg}), and compare with other APG algorithms in the literatures: the V-FISTA, and M-FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}.
-        We implemented in Julia \cite{bezanson_julia_2017} and FR-WAPG (Algorithm \ref{alg:free-rwapg}) with V-FISTA, M-FISTA. 
-        The equivalences highlighted in Proposition \ref{prop:r-wapg-momentum-repr} allows us to compare the sequence of iterates $(x_k)_{k \ge 1}, (y_k)_{k \ge0}$ for R-WAPG, VISTA and M-FISTA. 
+        We implemented in Julia \cite{bezanson_julia_2017}. 
+        The equivalences highlighted in Proposition \ref{prop:r-wapg-momentum-repr} allows us to compare the sequence of iterates $(x_k)_{k \ge 1}, (y_k)_{k \ge0}$ for R-WAPG, V-FISTA and M-FISTA. 
         \par
@@
             \delta_k := \log_2\left(
-                \NOG
+                \NOG_k
             \right)
             \text{ with } 
-            \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}
-        \end{align*}
-        Since it's not the case that $F^*$ is always known in prior, we will the minimum of all $F(x_k)$ across all algorithms, all iterations $k$ as the surrogate for $F^*$ when the true value is unavailable.
+            \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}.
+        \end{align*}
+        Since it's not the case that $F^*$ is always known in prior, we will use the minimum of all $F(x_k)$ across all algorithms, all iterations $k$ as the surrogate for $F^*$ when the true value is unavailable.
         \par 
@@
             \end{align*}
-            $A$ is set to be a positive semi-definite diagonal matrix, so the problem admits unique minimizer $x^* = \mathbf 0$ with minimum being zero. 
+            $A$ is set to be a positive semi-definite diagonal matrix, so the problem admits the minimizer $x^* = \mathbf 0$ (which is not unique) with minimum being zero. 
             We apply Algorithm \ref{alg:free-rwapg}, M-FISTA, and V-FISTA. 
@@
             \begin{enumerate}
-                \item $N$, the dimension of the problem which defines $A \in \RR^{N\times N}$, a diagonal matrix given by $N- 1$ linearly spaced with equal increment on the interval $[\mu, L]$, and an extra number $0$, i.e:
+                \item $N$, the dimension of the problem which defines $A \in \RR^{N\times N}$, a diagonal matrix given by $N- 1$ linearly spaced with equal increment on the interval $[\mu, L]$, and an extra number $0$, i.e.,
                 \begin{align*}
@@
                 \item $x_0 \sim \mathcal N(I, \mathbf 0)$ is a vector, and it's the initial condition for all the algorithm.
-In this case the initial guess is fixed for all R-WAPG, M-FISTA and M-FISTA, but it's randomly generated by the zero mean standard normal distribution for each element in the vector.
+In this case the initial guess is fixed for all R-WAPG, V-FISTA and M-FISTA, but it's randomly generated by the zero mean standard normal distribution for each element in the vector.
             \end{enumerate}
@@
             The solid line in the ribbon is the median value of $\delta_k$ across all experiment, the ribbon gives the maximum, minimum value of $\delta_k$ for each iteration across all experiments. 
-            One significant feature here is that FR-WAPG initially behaves similar to M-FISTA, but as the iteration goes on, it started to behave like V-FISTA. 
-            The second surprising feature is the monotone descent it shows on the graph visually. 
+            \par
+            The numerical experiment shows that FR-WAPG initially behaves similar to M-FISTA, but as the iteration goes on, it started to behave like V-FISTA. 
             Unfortunately it's numerically verified that the method is not monotone in general, and it just looks monotone on the graph. 
@@
                 \end{subfigure}
-                \caption{Simple convex quadratic experiments results for V-FISTA, M-FISTA, and R-WAPG. }
+                \caption{
+                    Statistics for experiments with simple convex quadratic for V-FISTA, M-FISTA, and R-WAPG. 
+                }
                 \label{fig:simple-quadratic-NOG}
@@
             Figure \ref{fig:simple-quadratic-r-wapg-mu-estimates} showcases the results. 
-            In this experiment, the values oscillate and converges to the true $\mu$ value. 
-            Observe that the iteration when the estimates are nearing the true value corresponds to the iteration when the algorithm plateau away from its initial fast descent. 
+            It shows that, the values oscillate and converges to the true $\mu$ value. 
             \begin{figure}[H]
                 \centering
-                \includegraphics[width=0.64\textwidth]{assets/simple_regression_loss_sc_estimates_1024.png}
-                \caption{$N = 1024$, the $\mu$ estimates produced by Algorithm \ref{alg:free-rwapg} (R-WAPG) is recorded. }
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/simple_regression_loss_sc_estimates_1024.png}
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/simple_regression_loss_1024.png}
+                \end{subfigure}
+                \caption{
+                    $N = 1024$, the $\mu$ estimates produced by Algorithm \ref{alg:free-rwapg} (R-WAPG) is recorded. 
+                }
                 \label{fig:simple-quadratic-r-wapg-mu-estimates}
@@
 Consequently, they are estimated by $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$ prior to experiment to assist the V-FISTA algorithm.
-                \item $x^+ = [1\; -1\; 1 \; \cdots ]^T \in \RR^N$, it's a vector with alternating $1, -1$ in it. 
+                \item $x^+ = [1,\; -1,\; 1, \; \cdots ]^T \in \RR^N$, it's a vector with alternating $1, -1$ in it. 
                 \item Given $x^+$, it has $b = Ax^+ \in \RR^M$. 
@@
                 \item $x_0\in \RR^N$ denotes the initial guess consist of i.i.d random variable realized from the standard normal distribution. 
-                \item $\epsilon = 10^{-6} > 0$ sets the tolerance for all test algorithm on $\Vert \mathcal G_L(x_k)\Vert$. 
+                \item $\epsilon = 10^{-6} > 0$ sets the tolerance for all test algorithm on $\Vert \mathcal G_L(y_k)\Vert$. 
             \end{enumerate}
@@
                 \end{subfigure}
-                \caption{LASSO experiments. }
+                \caption{LASSO experiments statistics for test algorithms. }
                 \label{fig:batched-lasso}
@@
                     \includegraphics[width=\textwidth]{assets/lasso_loss_256.png}
-                    \caption{Single lasso experiment plot of $\delta_k$ with.  }
+                    \caption
+                    {A single run of LASSO experiment displaying $F(x_k) - F^*$ for several test algorithms.
+                    }
                 \end{subfigure}
@@
                     \includegraphics[width=\textwidth]{assets/lasso_sc_estimates_256.png}
-                    \caption{The $\mu$ estimated by test algorithms for one LASSO experiment. }
+                    \caption{The $\mu_k$ estimated by FR-WAPG for one LASSO experiment. }
                 \end{subfigure}
-                \caption{A single LASSO experiment results, with $M = 64, 256$. }
+                \caption{A single LASSO experiment results, with $M = 64, N=256$. }
                 \label{fig:single-lass-mu-estimates}
@@
 
-\section{Discussion}
+\section{Discussions}
     This paper provides the results of an upper bound (Proposition \ref{prop:wapg-convergence}) on the optimality gap $F(x_k) - F^*$ for smooth plus nonsmooth composite optimization problem with convex objectives where under the much weaker assumption for the momentum parameter specified by Definition \ref{def:rwapg-seq}.

### 2025-02-23 Notebook LaTEX/R-WAPG/paper3.tex
>w<, fix cringe shit

@@
             \par
-            The numerical experiment shows that FR-WAPG initially behaves similar to M-FISTA, but as the iteration goes on, it started to behave like V-FISTA. 
-            Unfortunately it's numerically verified that the method is not monotone in general, and it just looks monotone on the graph. 
+            This numerical experiment shows that FR-WAPG initially behaves similar to M-FISTA, but it then started to behave like V-FISTA. 
+            It's numerically verified that the method is not monotone in general, and it just looks monotone in this experiment on this plot. 
             \begin{figure}[H]
@@
             \end{figure}
-            \par
             Another quantity that maybe interesting other than $\delta_k$ would be the estimated value of $\mu$ during at each iteration $k$. 
             One individual experiment is carried out for the R-WAPG algorithm and the value of $\mu$ at each iteration is being recorded as well. 
-            Figure \ref{fig:simple-quadratic-r-wapg-mu-estimates} showcases the results. 
-            It shows that, the values oscillate and converges to the true $\mu$ value. 
+            Figure \ref{fig:simple-quadratic-r-wapg-mu-estimates} shows the estimated $\mu_k$ of FR-WAPG on the left and the convergence rate of the test algorithms on the right for one specifice initial condition.
+            It shows the values of $\mu_k$ oscillates and converges to the true value of $\mu$. 
+            Observe that the initial fast descent slows and FR-WAPG diverges from M-FISTA as $\mu_k$ converged. 
             \begin{figure}[H]
@@
             This section present results of numerical experiment for solving the (least absolute shrinkage and selection operator) LASSO problem proposed by Tibshirani \cite{tibshirani_regression_1996}.
-            The problem of LASSO has smooth, nonsmooth additive parts given by: 
+            The problem of LASSO has smooth and nonsmooth additive parts given by: 
             \begin{align*}
@@
             Experiments were conducted using V-FISTA, M-FISTA and FR-WAPG with $(M, N) = (64, 256)$ and $(M, N) = (64, 128)$ respectively. 
-            A random matrix $A$ is realized and is fixed and the for all test algorithms and all repetitions. 
+            A random matrix $A$ is realized and is fixed for all test algorithms and all repetitions. 
             The same experiment are repeated 30 times on all algorithms with a fixed random initial condition $x_k$ realized from the distribution. 
             The aggregate statistics of $\delta_k$ are collected for all repetitions, and then grouped by the respective algorithm. 
-            The results are showcased in Figure \ref{fig:batched-lasso}. 
+            Figure \ref{fig:batched-lasso} shows the results of the two experiments.
             The bump on the curve is due to a subset of test instances of the 30 repetition where the algorithms take larger number of iterations to terminate. 
@@
             \end{figure}
-            \par
-            Another quantity of interest is the estimates of $\mu$ on each iteration of the algorithm. 
-            A single experiment were conducted and the estimates and $\delta_k$ are in Figure \ref{fig:single-lass-mu-estimates}
+            The experiment results shows faster convergence rate of FR-WAPG relative to V-FISTA, and it also shows that it behaves similarly to M-FISTA. 
+            In addition, an experiment were conducted to show the estimate $\mu_k$ and optimality gaph $F(x_k) - F^*$ in Figure \ref{fig:single-lass-mu-estimates}. 
             \begin{figure}[H]
@@
             For this specific experiment showed in the figure, the estimated value of $\mu, L$ which we feed into V-FISTA are $\mu = 7.432363627613958\times 10^{-18}$ and $L = 2321.737206983643$. 
-            One of the most important feature is that the estimate $\mu$ doesn't converge to the true value, but it didn't affect the convergence of $\delta_k$.
+            Make the important observation that $\mu_k$ didn't converge to the true value in this case, however it didn't affect the convergence of $F(x_k) - F^*$.
 
 \section{Discussions}
-    This paper provides the results of an upper bound (Proposition \ref{prop:wapg-convergence}) on the optimality gap $F(x_k) - F^*$ for smooth plus nonsmooth composite optimization problem with convex objectives where under the much weaker assumption for the momentum parameter specified by Definition \ref{def:rwapg-seq}.
+    This paper provides the results of an upper bound on the optimality gap $F(x_k) - F^*$ for smooth plus nonsmooth composite optimization problem with convex objectives where under the much weaker assumption for the momentum parameter specified by Definition \ref{def:rwapg-seq}.
     The proposed R-WAPG unifies the convergence proof for major Euclidean variants of FISTA with strong convexity parameter $\mu \ge 0$. 

### 2025-02-25 Notebook LaTEX/R-WAPG/paper3.tex
>w<, fix cringe shit

@@
     We study the accelerated proximal gradient method where the sequence that controls the momentum term doesn't follow the Nesterov's rule. 
-    The paper proposed R-WAPG, a generic algorithm that unifies the convergence results for strongly convex and convex where the extrapolation constant is characterized by a sequence that is much weaker than the Nesterov's rule.
+    The paper proposes Relaxed Weak Accelerated Proximal Gradient(R-WAPG), a generic algorithm that unifies the convergence results for strongly convex and convex problems where the extrapolation constant is characterized by a sequence that is much weaker than the Nesterov's rule.
     The R-WAPG provides a unified framework for several notable Euclidean variants of FISTA and verify their convergence. 
-    In addition, we also study the convergence rate of strongly convex objective with a constant momentum term. 
-    We reformulate R-WAPG so that it doesn't require any parameter without using the idea of restarting which we call ``Free R-WAPG". 
+    In addition, we also provide the convergence rate of strongly convex objective with a constant momentum term. 
+    We reformulate R-WAPG so that it doesn't require any parameter, without using the idea of restarting, which we call ``Free R-WAPG". 
     Explorative numerical experiments were conducted to show its competitive convergence. 
@@
         $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is $L$ strongly convex by Assumption \ref{ass:smooth-nsmooth-additive} and its definition. 
-        We see that it admits quadratic growth over the minimizer $Ty$, therefore for all $x \in \RR^n$ it follows that: 
+        We see that it admits quadratic growth over the minimizer $\bar y = T(y)$, therefore for all $x \in \RR^n$ it follows that: 
         {\smaller
@@
             \widetilde{\mathcal M}^{L^{-1}}(x; y) - 
-            \widetilde{\mathcal M}^{L^{-1}}(Ty; y)
+            \widetilde{\mathcal M}^{L^{-1}}(\bar y; y)
             - 
-            \frac{L}{2}\Vert x - Ty\Vert^2
+            \frac{L}{2}\Vert x - \bar y\Vert^2
             \\
@@
             \right) - 
-            \mathcal M^{L^{-1}}(Ty; y) 
+            \mathcal M^{L^{-1}}(\bar y; y) 
             - 
-            \frac{L}{2}\Vert x - Ty\Vert^2
-            + D_f(Ty; y)
+            \frac{L}{2}\Vert x - \bar y\Vert^2
+            + D_f(\bar y; y)
             \quad 
@@
                 - 
-                \mathcal M^{L^{-1}}(Ty; y)
+                \mathcal M^{L^{-1}}(\bar y; y)
             \right)
@@
             D_f(x, y) 
-            - \frac{L}{2}\Vert x - Ty\Vert^2
-            + D_f(Ty; y)
-            \\
-            &=
-            \left(
-                F(x) - F(Ty) 
+            - \frac{L}{2}\Vert x - \bar y\Vert^2
+            + D_f(\bar y; y)
+            \\
+            &=
+            \left(
+                F(x) - F(\bar y) 
                 + 
                 \frac{L}{2}\Vert x - y\Vert^2 - 
-                \frac{L}{2}\Vert Ty - y\Vert^2
+                \frac{L}{2}\Vert \bar y - y\Vert^2
             \right)
             - D_f(x, y) 
-            + D_f(Ty; y)
-            - \frac{L}{2}\Vert x - Ty\Vert^2
-            \\
-            &=  
-            \left(
-                F(x) - F(Ty) 
+            + D_f(\bar y; y)
+            - \frac{L}{2}\Vert x - \bar y\Vert^2
+            \\
+            &=  
+            \left(
+                F(x) - F(\bar y) 
                 + 
@@
                 \left(
-                    \Vert x - Ty + Ty - y\Vert^2
+                    \Vert x - \bar y + \bar y - y\Vert^2
                     - 
-                    \Vert y - Ty\Vert^2
+                    \Vert y - \bar y\Vert^2
                 \right)
@@
             - D_f(x, y) 
-            + D_f(Ty; y)
-            - \frac{L}{2}\Vert x - Ty\Vert^2
-            \\
-            &= 
-            \left(
-                F(x) - F(Ty) 
+            + D_f(\bar y; y)
+            - \frac{L}{2}\Vert x - \bar y\Vert^2
+            \\
+            &= 
+            \left(
+                F(x) - F(\bar y) 
                 + 
@@
                 \left(
-                    \Vert x - Ty\Vert^2 + 
-                    2\langle x - Ty, Ty - y\rangle
+                    \Vert x - \bar y\Vert^2 + 
+                    2\langle x - \bar y, \bar y - y\rangle
                 \right)
@@
             - D_f(x, y) 
-            + D_f(Ty; y)
-            - \frac{L}{2}\Vert x - Ty\Vert^2
+            + D_f(\bar y; y)
+            - \frac{L}{2}\Vert x - \bar y\Vert^2
             \\
@@
             \left(
-                F(x) - F(Ty) + \frac{L}{2}\Vert x - Ty\Vert^2 
-                - L\langle  x - Ty, y - Ty\rangle
+                F(x) - F(\bar y) + \frac{L}{2}\Vert x - \bar y\Vert^2 
+                - L\langle  x - \bar y, y - \bar y\rangle
             \right)
             - D_f(x, y) 
-            + D_f(Ty; y)
-            - \frac{L}{2}\Vert x - Ty\Vert^2
-            \\
-            &=
-            F(x) - F(Ty)
-            - \langle L(y - Ty), x - Ty\rangle
+            + D_f(\bar y; y)
+            - \frac{L}{2}\Vert x - \bar y\Vert^2
+            \\
+            &=
+            F(x) - F(\bar y)
+            - \langle L(y - \bar y), x - \bar y\rangle
             - D_f(x, y) 
-            + D_f(Ty, y).
+            + D_f(\bar y, y).
         \end{align*}
@@
             0 &\le 
-            F(x) - F(Ty)
-            - \langle L(y - Ty), x - Ty\rangle
+            F(x) - F(\bar y)
+            - \langle L(y - \bar y), x - \bar y\rangle
             - D_f(x, y) 
-            + D_f(Ty, y)
+            + D_f(\bar y, y)
             \\
             &\le 
-            F(x) - F(Ty)
-            - \langle L(y - Ty), x - Ty\rangle
+            F(x) - F(\bar y)
+            - \langle L(y - \bar y), x - \bar y\rangle
             - \frac{\mu}{2}\Vert x - y\Vert^2
-            + \frac{L}{2}\Vert y - Ty\Vert^2
-            \\
-            &=
-            F(x) - F(Ty)
-            - \langle L(y - Ty), x - y  + y - Ty\rangle
+            + \frac{L}{2}\Vert y - \bar y\Vert^2
+            \\
+            &=
+            F(x) - F(\bar y)
+            - \langle L(y - \bar y), x - y  + y - \bar y\rangle
             - \frac{\mu}{2}\Vert x - y\Vert^2
-            + \frac{L}{2}\Vert y - Ty\Vert^2
-            \\
-            &=
-            F(x) - F(Ty) - \langle L(y - Ty), x - y\rangle - \frac{\mu}{2}\Vert x - y \Vert^2
-            - \frac{L}{2}\Vert y - Ty\Vert^2. 
+            + \frac{L}{2}\Vert y - \bar y\Vert^2
+            \\
+            &=
+            F(x) - F(\bar y) - \langle L(y - \bar y), x - y\rangle - \frac{\mu}{2}\Vert x - y \Vert^2
+            - \frac{L}{2}\Vert y - \bar y\Vert^2. 
         \end{align*}
@@
     The assumption below is crucial to describing the convergence rate of the R-WAPG and it requires the convexity assumption on $F$. 
-    \begin{assumption}
+    \begin{assumption}\label{ass:regret-gap}
         Given $x_k, y_k, v_k$ where $k \in \mathbb Z_+$, we define the following quantities
@@
             \\
-            g_k &= \mathcal G_L y_k, \label{eqn:stepwise-wapg-eqn3}
+            g_k &= \mathcal G_L (y_k), \label{eqn:stepwise-wapg-eqn3}
             \\
@@
             \\
-            x_{k + 1} &= T_L y_k. \label{eqn:stepwise-wapg-eqn5}
+            x_{k + 1} &= T_L(y_k). \label{eqn:stepwise-wapg-eqn5}
         \end{align}
@@
         Given any $v_k, x_k$ and $\gamma_k > 0$ and $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}, \alpha_k$ that satisfy Definition \ref{def:stepwise-wapg}. 
-        With $\epsilon_k$ given by \eqref{eqn:regret}, define: 
+        With $\epsilon_k, y_k$ given by Assumption \ref{ass:regret-gap}, define: 
         \begin{align}\label{eqn:stepwise-lya-1}
@@
         Let vector sequence $(y_k, v_{k}, x_{k})_{k \ge 1}$ and R-WAPG sequences $\alpha_k, \rho_k$ be given by Definition \ref{def:wapg}. 
-        Let $\epsilon_k$ be given by \eqref{eqn:regret}. 
+        Let $\epsilon_k, y_k$ be given by Assumption \ref{ass:regret-gap}. 
         Define $R_1 = 0$ and suppose that for $k = 1, 2, \ldots, N$, we have $R_k$ recursively given by: 
@@
                     & x_{k + 1} \defeq 
-                    y_k - L^{-1} \mathcal G_L y_k, 
+                    y_k - L^{-1} \mathcal G_L (y_k), 
                     \\
@@
                         \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
-                    \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
+                    \right) - \frac{1}{L\alpha_{k}}\mathcal G_L (y_k). 
                 \end{align*}
@@
                 \begin{align*}
-                    & x_{k + 1} \defeq y_k - L^{-1}\mathcal G_Ly_k, 
+                    & x_{k + 1} \defeq y_k - L^{-1}\mathcal G_L (y_k), 
                     \\
@@
                 & x_{k + 1} = 
-                y_k - L^{-1} \mathcal G_L y_k, 
+                y_k - L^{-1} \mathcal G_L (y_k), 
                 \\
@@
                     \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
-                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
+                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L (y_k). 
                 \label{eqn:rwapg-first-equiv-form-eqn-2}
@@
                 ((1 - \alpha_k)\gamma_k v_k + \mu\alpha_k y_k)
-                - \alpha_k\hat \gamma_{k + 1}^{-1}\mathcal G_L y_k
+                - \alpha_k\hat \gamma_{k + 1}^{-1}\mathcal G_L (y_k)
                 \\
@@
                 \right)
-                - \alpha_k\hat \gamma_{k + 1}^{-1}\mathcal G_L y_k
+                - \alpha_k\hat \gamma_{k + 1}^{-1}\mathcal G_L (y_k)
                 \\
@@
                 \right)
-                - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
+                - \frac{1}{L\alpha_{k}}\mathcal G_L (y_k). 
             \end{align*}
@@
                 x_{k + 1} &= 
-                y_k - L^{-1} \mathcal G_L y_k, 
+                y_k - L^{-1} \mathcal G_L (y_k), 
                 \\
@@
                 \begin{align*}
-                    x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
+                    x_{k + 1} &= y_k - L^{-1}\mathcal G_L (y_k), 
                     \\
@@
             \begin{align*}
-                &x_{k + 1} = y_k + L^{-1}\mathcal G_L y_k, 
+                &x_{k + 1} = y_k + L^{-1}\mathcal G_L (y_k)
+                , 
                 \\
@@
 \section{Discussions}
-    This paper provides the results of an upper bound on the optimality gap $F(x_k) - F^*$ for smooth plus nonsmooth composite optimization problem with convex objectives where under the much weaker assumption for the momentum parameter specified by Definition \ref{def:rwapg-seq}.
+    This paper provides the results of an upper bound on the optimality gap $F(x_k) - F^*$ for smooth plus nonsmooth composite optimization problem with convex objectives where under much weaker assumption for the momentum parameter.
     The proposed R-WAPG unifies the convergence proof for major Euclidean variants of FISTA with strong convexity parameter $\mu \ge 0$. 
@@
     Unfortunately a precise description of the convergence rate of Free R-WAPG remains a mystery. 
+    It will be interesting to explore this line of research. 
     Our convergence framework gives an upper bound using the sequence $(\alpha_k)_{k \ge 0} \in (\mu/L, 1)$, but it requires knowing what the sequence would be in advanced given the initial conditions and the objective function.
     \par
-    From a practical perspective, Algorithm \ref{alg:free-rwapg} shows competitive results of convergence of strongly convex function.  
+    From a practical perspective, Algorithm \ref{alg:free-rwapg} shows competitive results of convergence for strongly convex function.  
     The algorithm behaves in way having characteristics of both V-FISTA and M-FISTA which is fascinating. 
@@
     We do note that in the case when function is not strongly convex, the function value converges without $\Vert \mathcal G_L(y_k)\Vert$ converging. 
+    This will be explored more in future work.
 

### 2025-02-27 Notebook LaTEX/Proposal/presentation.tex
>w<, changes

@@
 \usepackage[utf8]{inputenc}
-\usepackage{hyperref}
+\usepackage{algorithmic}
+\usepackage{algorithm}
 \usepackage{amsmath}
@@
 \usepackage{graphicx}
-\usepackage{algorithmic}
-\usepackage{algorithm}
-\usepackage{wrapfig}
+\usepackage{hyperref}
+\usepackage{mathtools}
 \usepackage{subcaption}
 \usepackage{tcolorbox}
+\usepackage{wrapfig}
 
@@
 \setbeamertemplate{blocks}[rounded][shadow=true]
+\setbeamertemplate{navigation symbols}{} 
 % \setbeamercolor{block title}{bg=cyan,fg=black} % CHANGE THE BLOCK STYLE IN BEAMER. 
@@
 % BIB STYLES SETTINGS ----------------------------------------------------------
+\setbeamertemplate{bibliography item}{\insertbiblabel}
 \setbeamerfont{bibliography item}{size=\footnotesize}
@@
 % \setbeamercovered{transparent}  % GREY OUT PAUSED FUTURE ITEMS IN SLID. 
-\setbeamertemplate{navigation symbols}{}
+\bibliographystyle{siam}
 
@@
 \newtheorem{proposition}{Proposition}[section]
-\bibliographystyle{siam}
 
@@
     \begin{enumerate}
-        \item X. Wang and H. Li, \textit{A Parameter Free Accelerated Proximal Gradient Method Without Restarting}, preprint, (2025).
+        \item H. Li and X. Wang, \textit{A Parameter Free Accelerated Proximal Gradient Method Without Restarting}, preprint, (2025).
     \end{enumerate}
@@
             \begin{enumerate}
-                \item Describe for momentum sequences that doesn't follow Nesterov's rules.
+                \item Gives upper bound for $F(x_k) - \inf_{x \in \RR^n} F(x)$ for momentum sequences that doesn't follow Nesterov's rules.
                 \item Unifies the convergence rate analysis for several Euclidean variants of the FISTA method. 
@@
                 The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for $k\ge 1$ by the procedures:  
+                {\small
                 \begin{tcolorbox}
@@
                 \end{tcolorbox}
+                }
             \end{definition}
+        \end{frame}
+        \begin{frame}{R-WAPG Assumptions and Notations}
+            \begin{assumption}\label{ass:regret-gap}
+                Given $x_k, y_k, v_k$ where $k \in \mathbb Z_+$, we define the following quantities
+                \begin{align}
+                    g_k &\defeq L(y_k - T_L(y_k)), 
+                    \label{eqn:grad-map}
+                    \\
+                    l_F(x; y_k) &\defeq F(T_L(y_k)) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
+                    \label{eqn:lower-linearization}
+                    \\
+                    \epsilon_{k} &\defeq F(x_k) - l_F(x_k; y_k). 
+                    \label{eqn:regret}
+                \end{align}
+            \end{assumption}
         \end{frame}
@@
             We proposed the following implementation of R-WAPG which doesn't require parameters $\mu, L$ in advance. 
-
             \begin{algorithm}[H]
+                \begin{algorithmic}[1]
                 {\scriptsize
-                \begin{algorithmic}
-                \STATE{\textbf{Input: } $f, g, x_0, L > \mu \ge 0, \in \RR^n, N \in \N$}
-                \STATE{\textbf{Initialize: }$y_0 := x_0;L := 1; \mu := 1/2; \alpha_0 = 1;$}
+                \STATE{\textbf{Input: } $f, g, L > \mu \ge 0, x_0 \in \RR^n, N \in \N$}
+                \STATE{\textbf{Initialize: }$y_0 := x_0;L_0 := 1; \mu_0 := 1/2; \alpha_0 = 1$;}
                 \STATE{\textbf{Compute: } $f(y_k)$; }
                 \FOR{$k = 0, 1, 2, \cdots, N$}
-                    \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$;}
-                    \WHILE{$L/2\Vert x^+ - y_k\Vert^2 < D_f(x^+, y_k)$}
-                        \STATE{$L:= 2L$;}
-                        \STATE{$x^+ = [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$; }
+                    \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L_k^{-1}\partial g]^{-1}(y_k - L_k^{-1}\nabla f(y_k))$;}
+                    \WHILE{$L_k/2\Vert x^+ - y_k\Vert^2 < D_f(x^+, y_k)$}
+                        \STATE{$L_k:= 2L_k$;}
+                        \STATE{$x^+ = [I + L_k^{-1}\partial g]^{-1}(y_k - L_k^{-1}\nabla f(y_k))$; }
                     \ENDWHILE
                     \STATE{$x_{k + 1} := x^+$;}
-                    \STATE{$\alpha_{k + 1} := (1/2)\left(\mu/L - \alpha_{k}^2 + \sqrt{(\mu/L - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;}
+                    \STATE{$\alpha_{k + 1} := (1/2)\left(\mu_k/L_k - \alpha_{k}^2 + \sqrt{(\mu_k/L_k - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;}
                     \STATE{$\theta_{k + 1} := \alpha_k(1 - \alpha_k)/(\alpha_k^2 + \alpha_{k + 1})$;}
@@
                     \STATE{\textbf{Compute: } $f(y_{k + 1})$}
-                    \STATE{$\mu := (1/2)(2D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2) + (1/2)\mu$;}
+                    \STATE{$\mu_k := D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2 + (1/2)\mu_k$;}
                 \ENDFOR
+                }
                 \end{algorithmic}
@@
                 \label{alg:free-rwapg}
-            }
             \end{algorithm}
@@
                 \delta_k := \log_2\left(
-                    \NOG
+                    \NOG_k
                 \right)
                 \text{ with } 
-                \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}
+                \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}.
             \end{align*}
             }
-            This is our first numerical experiment is: 
-            \begin{align*}
-                F(x) = (1/2)\langle x, A x\rangle. 
-            \end{align*}
+            Consider objective function: $F(x) = (1/2)\langle x, A x\rangle$. 
             Our setup has: 
@@
                     \includegraphics[width=\textwidth]{assets/simple_regression_batched-256.png}
-                    \caption{$N = 256$, simple convex quadratic.}
+                    \caption{$N = 256$.}
                 \end{subfigure}
@@
                     \includegraphics[width=\textwidth]{assets/simple_regression_batched-1024.png}
-                    \caption{$N = 1024$, simple convex quadratic. }
+                    \caption{$N = 1024$.}
                 \end{subfigure}
@@
         \begin{frame}{FR-WAPG $\mu$ estimation graph}
-            FR-WAPG estimates the following for $\mu$ during its execution: 
+            FR-WAPG estimates the following for $\mu_k$: 
             \begin{figure}[H]

### 2025-02-27 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

@@
 
-\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{true}
+\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{false}
 \input{presets/wang/input.tex}
-\input{presets/misc.tex}
-\input{presets/julia_lstlisting.tex}
+% \input{presets/misc.tex}
+% \input{presets/julia_lstlisting.tex}
 
@@
 \title{{\fontfamily{ptm}\selectfont 
-        A Parameter Free Accelerated Proximal Gradient Method Without Restarting
+        % A Parameter Free Accelerated Proximal Gradient Method Without Restarting
+        Relaxed Weak Accelerated Proximal Gradient method: a unified framework for Nesterov's acceleration
     }}
@@
     The following lemma provides important properties of $\mathcal M^{L^{-1}}(\cdot; y), \widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$. 
-    \begin{lemma}[Proximal gradient envelope]\label{lemma:pg-envelope}
+    \begin{lemma}\label{lemma:pg-envelope}
         With $\mathcal M^{L^{-1}}, \widetilde{\mathcal M}^{L^{-1}}$ as given by \eqref{eqn:pg-model-func}, \eqref{eqn:pp-model-func}, 
@@
             &= 
-            \mathcal M^{L^{-1}}(x; y)- D_f(x, y) \le \mathcal M^{L^{-1}}(x; y). 
+            \mathcal M^{L^{-1}}(x; y)- D_f(x, y). 
         \end{align*}
@@
             \\
-            \epsilon_{k} &\defeq F(x_k) - l_F(x_k; y_k), 
+            \epsilon_{k} &\defeq F(x_k) - l_F(x_k; y_k). 
             \label{eqn:regret}
@@
         The algorithm presented here is the same as the R-WAPG momentum form as given by Definition \ref{def:r-wapg-momentum-form} because the term $\theta$ from Lemma \ref{lemma:constant-rwapg-seq} matches up with Definition \ref{def:r-wapg-momentum-form} by (ii) in Lemma \ref{lemma:constant-rwapg-seq}.
-        Then, Proposition \ref{prop:wapg-convergence} applies,and it follows that: 
+        Then, Proposition \ref{prop:wapg-convergence} applies, and it follows that: 
         \begin{align*}
@@
         When $r = 1$, the algorithm described above is exactly the same as the V-FISTA algorithm specified in (10.7.7) of Beck's book \cite{beck_first-order_2017}. 
-        The above theorem gives convergence rate for a much relax choice of momentum parameter $\theta$ generalizing the convergence of constant step size FISTA to all convex stronlgy convex function and all possible $\alpha_k \in (\mu/L, 1)$.
+        The above theorem gives convergence rate for a much relax choice of momentum parameter $\theta$ generalizing the convergence of constant step size FISTA to all convex and strongly convex function and all possible $\alpha_k \in (\mu/L, 1)$.
         In addition, the convergence claim of R-WAPG holds for any $\mu$ smaller than the strong convexity modulus of $f$ that is not zero making the bounds $r \in (\sqrt{q}, \sqrt{q^{-1}})$ looser. 
@@
     Therefore, $\alpha_k \in (0, 1)$. 
-    To prvent the case $\alpha_k = 1$, we may always force the esimate $\mu = L/2$ whenever $\mu > L/2$. 
+    To prevent the case $\alpha_k = 1$, we may always force the estimate $\mu = L/2$ whenever $\mu > L/2$. 
     % In the very unlikely case when $q = 1$, Algorithm \ref{alg:free-rwapg} has $\theta_k = 0$, and it performs one step of proximal gradient descent. 
@@
             One individual experiment is carried out for the R-WAPG algorithm and the value of $\mu$ at each iteration is being recorded as well. 
-            Figure \ref{fig:simple-quadratic-r-wapg-mu-estimates} shows the estimated $\mu_k$ of FR-WAPG on the left and the convergence rate of the test algorithms on the right for one specifice initial condition.
+            Figure \ref{fig:simple-quadratic-r-wapg-mu-estimates} shows the estimated $\mu_k$ of FR-WAPG on the left and the convergence rate of the test algorithms on the right for one specific initial condition.
             It shows the values of $\mu_k$ oscillates and converges to the true value of $\mu$. 
@@
             The experiment results shows faster convergence rate of FR-WAPG relative to V-FISTA, and it also shows that it behaves similarly to M-FISTA. 
-            In addition, an experiment were conducted to show the estimate $\mu_k$ and optimality gaph $F(x_k) - F^*$ in Figure \ref{fig:single-lass-mu-estimates}. 
+            In addition, an experiment were conducted to show the estimate $\mu_k$ and optimality gap $F(x_k) - F^*$ in Figure \ref{fig:single-lass-mu-estimates}. 
             \begin{figure}[H]
@@
                 \end{subfigure}
-                \caption{A single LASSO experiment results, with $M = 64, N=256$. }
+                \caption{A single LASSO experiment results, with $M = 64, N=256$. f}
                 \label{fig:single-lass-mu-estimates}

### 2025-02-28 Notebook LaTEX/R-WAPG/paper3.tex
=w=, no comments

@@
     \par
-    The assumption below is crucial to describing the convergence rate of the R-WAPG and it requires the convexity assumption on $F$. 
+    The assumption below is crucial to describing the convergence rate of the R-WAPG, and it requires the convexity assumption on $F$. 
     \begin{assumption}\label{ass:regret-gap}
@@
     Then, the Lipschitz line search is not triggered and $L_k = L$ for all $k = 1, \ldots, N$. 
-    Let $\mu = (1/2)L$ so it may not be a lower bound on the strong convexity constant for $f$. 
+    Initialize $\mu = (1/2)L$ which it may not be a lower bound on the strong convexity constant for $f$. 
     With the additional assumption that the estimated $\mu_k < L$, the sequence $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg}. 

### 2025-02-28 Notebook LaTEX/R-WAPG/paper4.tex
=w=, no comments

--- 2025-02-28 Notebook LaTEX/R-WAPG/paper3.tex
@@
         % A Parameter Free Accelerated Proximal Gradient Method Without Restarting
-        Relaxed Weak Accelerated Proximal Gradient method: a unified framework for Nesterov's acceleration
+        Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations
     }}
@@
     \noindent
-    We study the accelerated proximal gradient method where the sequence that controls the momentum term doesn't follow the Nesterov's rule. 
-    The paper proposes Relaxed Weak Accelerated Proximal Gradient(R-WAPG), a generic algorithm that unifies the convergence results for strongly convex and convex problems where the extrapolation constant is characterized by a sequence that is much weaker than the Nesterov's rule.
-    The R-WAPG provides a unified framework for several notable Euclidean variants of FISTA and verify their convergence. 
-    In addition, we also provide the convergence rate of strongly convex objective with a constant momentum term. 
-    We reformulate R-WAPG so that it doesn't require any parameter, without using the idea of restarting, which we call ``Free R-WAPG". 
-    Explorative numerical experiments were conducted to show its competitive convergence. 
+    This paper is devoted to the study of accelerated proximal gradient methods where the sequence that controls the momentum term doesn't follow Nesterov's rule.
+    We propose a relaxed weak accelerated proximal gradient (R-WAPG) method, a generic algorithm that unifies the convergence results for strongly convex and convex problems where the extrapolation constant is characterized by a sequence that is much weaker than Nesterov's rule.
+    Our R-WAPG provides a unified framework for several notable Euclidean variants of FISTA and verifies their convergences.
+    In addition, we provide the convergence rate of strongly convex objective with a constant momentum term.
+    We also reformulate R-WAPG so that it doesn't require any parameter, without using the idea of restarting, which we call ``Free R-WAPG".
+    Explorative numerical experiments were conducted to show its competitive advantages.
 \end{abstract}
 
-\noindent{\bfseries 2010 Mathematics Subject Classification:}
+\noindent{\bfseries 2020 Mathematics Subject Classification:}
 Primary 90C30, 90C25, 65K10; Secondary 65Y20.
@@
         Beck and Teboulle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it has an $\mathcal O(1/k^2)$ convergence still, but it performs empirically better.
-        See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm.
+        See \cite{aujol_parameter-free_2024}, \cite{necoara_linear_2019} and references therein for recent advancements in restarting accelerated proximal gradient algorithm.
         \par
@@
         The choices for $\theta_k$ varies for different variants of the accelerated proximal gradient algorithm.
-        In Chambolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space. 
+        In Chambolle and Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space.
         In Chapter 10 of Beck's Book \cite{beck_first-order_2017}, a variant called V-FISTA can achieve the faster linear convergence rate: $\mathcal O((1 - \sqrt{\mu/L})^k)$ on the optimality gap for $\mu > 0$ strongly convex $F$.
@@
         \par
-        We relax the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example-algorithm} and showed an upper bound of the optimal gap. 
+        We relax the traditional choice of the sequence $\theta_k$ in Equation \eqref{eqn:example-algorithm} and showed an upper bound of the optimal gap.
         Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
@@
         \end{align*}
-        Our second main result shows that for any $\alpha_k \ge 0$ the choice of sequence $\alpha_k = a/(a + k)$ results in $\rho_k > 1$ for all $k \in \N$ such that R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}.
+        Our second main result shows that for any $\alpha_k \ge 0$ the choice of sequence $\alpha_k = a/(a + k)$ results in $\rho_k > 1$ for all $k \in \N$ such that R-WAPG reduces to a variant of FISTA proposed in Chambolle and Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}.
         When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}.
@@
         Our practical contribution is an algorithm inspired by a detail in the proof of Proposition \ref{prop:wapg-convergence} which is called ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}).
-        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ from the Bregman divergence of $f$ with minimal computational cost.
+        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_k$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ from the Bregman divergence of $f$ with minimal computational cost.
         We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart.
@@
         \textbf{The remainder of this paper is organized as follows. }
-        Section \ref{sec:stepwise-stuff} states and proves Proposition \ref{prop:stepwise-lyapunov}, an inequality based on a single generic iterative step that acts similar to a descent lemma. 
+        In Section~\ref{sec:preliminaries}, we formulate the composite optimization
+        problem considered in the paper and give a proximal inequality connecting the objective function
+         and the proximal gradient
+        operator and gradient mapping.
+        Section \ref{sec:stepwise-stuff} proves 
+        %Proposition \ref{prop:stepwise-lyapunov}, 
+        a key inequality based on a single generic iterative step that acts similar to a descent lemma.
         Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG in Definition \ref{def:wapg} and defines the R-WAPG sequence in Definition \ref{def:rwapg-seq}.
-        Proposition \ref{prop:wapg-convergence} states the convergence rate of R-WAPG through Proposition \ref{prop:stepwise-lyapunov} and the R-WAPG sequence. 
-        Section \ref{sec:rwapg-equiv-repr} gives three equivalent representations of the R-WAPG algorithms that are comparable to instances of APG found in the literatures. 
+Using Proposition \ref{prop:stepwise-lyapunov} from Section~\ref{sec:stepwise-stuff}
+         and the R-WAPG sequence, 
+        %Proposition \ref{prop:wapg-convergence} states 
+        we provide the convergence rate of R-WAPG.
+        Section \ref{sec:rwapg-equiv-repr} focuses on three equivalent representations of the R-WAPG algorithms that are comparable to instances of APG found in the literatures.
         Section \ref{sec:rwapg-literatures} formulates FISTA, and V-FISTA sequences as instance of the R-WAPG sequences.
-        The section proves the convergence rate of several variants of FISTA using the equivalent forms introduced in Section \ref{sec:rwapg-equiv-repr} and the convergence rate developed Section \ref{sec:rwapg-formulation-convergence}.
-        Finally, Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcase the numerical experiments for regression, LASSO.
+        This section proves the convergence rate of several variants of FISTA using the equivalent forms introduced in Section \ref{sec:rwapg-equiv-repr} and the convergence rate developed Section \ref{sec:rwapg-formulation-convergence}.
+        Finally, Section \ref{sec:free-rwapg} gives a parameter free version of R-WAPG algorithm and showcase its numerical experiments for regression, LASSO.
 
@@
     Throughout, we make the following assumption unless specified.
-    \begin{assumption}[Smooth nonsmooth additive]\label{ass:smooth-nsmooth-additive}
+    \begin{assumption}[Smooth and nonsmooth additives]\label{ass:smooth-nsmooth-additive}
         \;
@@
     \begin{proof}
-        The proof starts by showing that \eqref{eqn:Q1}, \eqref{eqn:Q2} follows from \ref{eqn:stepwise-wapg-eqn2}, then the desire results follows naturally using algebra.
+        The proof starts by showing that \eqref{eqn:Q1} and \eqref{eqn:Q2} below 
+        follow from \eqref{eqn:stepwise-wapg-eqn2}, then the desire results follows naturally using algebra.
         We make the following observations from Definition \ref{def:stepwise-wapg}:
@@
     \end{proof}
+
     \begin{proposition}[Stepwise Lyapunov]\label{prop:stepwise-lyapunov}\;\\
@@
         \begin{enumerate}
-            \item Step 1: 
+            \item
             \begin{align}\tag{Step 1}\label{eqn:stepwise-lya-proof-step-1}
@@
             \end{align}
-            \item Step 2: 
+            \item
             \begin{align}\tag{Step 2}\label{eqn:stepwise-lya-proof-step-2}
@@
             \end{align}
-            \item Step 3: adding both side of Equations \eqref{eqn:stepwise-lya-proof-step-1}, \eqref{eqn:stepwise-lya-proof-step-2}, it follows: 
+            \item Adding both side of Equations \eqref{eqn:stepwise-lya-proof-step-1}, \eqref{eqn:stepwise-lya-proof-step-2}, it follows:
             \begin{align}\tag{Step 3}\label{eqn:stepwise-lya-proof-step-3}
@@
     \end{align*}
-    To start, the following proposition on ``abstract similar triangle form'' were made to simplify arguments and notations and to make cleaner proofs. 
+    We start with the following result on ``abstract similar triangle form'' to make later proofs cleaner.
     % SECTION INTRODUCTION ENDS
@@
     First columns states the assumption made for parameter $\mu$, the second and third columns show the specific examples of $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ specialized from Definition \ref{def:rwapg-seq}.
-    Last column shows the convergence rate on $F(x_k) - F^*$ which is the optimality gap and a theorem that proves the claim. 
+    Last column shows the convergence rate on $F(x_k) - F^*$ (the optimality gap) and our theorem that proves the claim.
     \begin{table}[H]
@@
     \begin{remark}
-        The sequence $t_k$ is exactly the same as in Chambolle, Dossal \cite[Theorem 3.1, 8]{chambolle_convergence_2015}. 
+        The sequence $t_k$ is exactly the same as in Chambolle and Dossal 
+        \cite[Theorem 3.1]{chambolle_convergence_2015}.
     \end{remark}
@@
             For this specific experiment showed in the figure, the estimated value of $\mu, L$ which we feed into V-FISTA are $\mu = 7.432363627613958\times 10^{-18}$ and $L = 2321.737206983643$.
-            Make the important observation that $\mu_k$ didn't converge to the true value in this case, however it didn't affect the convergence of $F(x_k) - F^*$.
+            An important observation is that $\mu_k$ didn't converge to the true value in this case, however it didn't affect the convergence of $F(x_k) - F^*$.
 

### 2025-03-01 Notebook LaTEX/Proposal/presentation.tex
=w=, no comments
>w<, changes

@@
 \author{Hongda Li}
-\title[Thesis Proposal Talk]{Nesterov's First Order Method Accelerations: Unifications, Applications  and Numerial Experiments}
+\title[Thesis Proposal Talk]{Nesterov's First Order Method Accelerations: Unifications, Applications and Numerical Experiments}
 % \newcommand{\email}{lalala@lala.la}
@@
     \begin{frame}{Introduction}
-        Part I: Introduction. 
+        Part I: Introduction to Relaxed Weak Accelerated Proximal Gradient (R-WAPG). 
         \begin{block}{Upcoming Contents: }
@@
                 \item Introducing R-WAPG (Content of our draft paper). 
-                \item Introducing the Catalyst metal acceleration framework. 
+                \item Introducing the Catalyst meta acceleration framework. 
             \end{itemize}
@@
                 \item It finds application in machine learning, and it accelerates the convergence of Variance Reduced Method (A type of incremental method that is not slower than the exact counterpart).
-                \item It demonstrates crucial ideas on convergence analysis involving nexact evaluation of proximal point method under the the convex settings. 
+                \item It demonstrates crucial ideas on convergence analysis involving inexact evaluation of proximal point method under the convex settings. 
             \end{enumerate}
@@
         \begin{block}{Upcoming contents}
-            We explain results from our relaxed, weak accelerated proximal gradient (R-WAPG). 
+            We explain results from our draft paper on relaxed, weak accelerated proximal gradient (R-WAPG). 
             \begin{enumerate}
@@
                 \item Three equivalent forms of R-WAPG. 
-                \item Specialized convergence results with for specific instances of FISTA variants in the literatures. 
+                \item Specialized convergence results of Euclidean FISTA variants in the literatures. 
                 \item A parameter free formulation of R-WAPG and the results of our preliminary numerical experiments. 
@@
         \end{block}
-
     \end{frame}
@@
                         \\
-                        g_k &= \mathcal G_L y_k, 
-                        \\
+                        % g_k &= , 
+                        % \\
                         v_{k + 1} &= 
                         \hat\gamma^{-1}_{k + 1}
-                        (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
+                        (\gamma_k(1 - \alpha_k) v_k - \alpha_k \mathcal G_L y_k + \mu \alpha_k y_k), 
                         \\
@@
             \end{assumption}
+            \eqref{eqn:lower-linearization} Comes from Lemma \ref{thm:prox-grad-ineq}. 
         \end{frame}
@@
                         \left(
-                            v_{k + 1} + 
+                            v_{k} + 
                             \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
@@
             \\ \hline
-                Definition \ref{def:wapg} &  
+                \hspace{-1em}
+                \begin{tabular}{l}
+                    Constant\\ Momentum
+                \end{tabular}
+                &  
                 $\mu > 0$ &
@@
             These results are consistent of literatures. 
-            To the best of our knowledge, the last variant is, and we have the convergence claim for it using R-WAPG. 
+            To the best of our knowledge, the last variant is new, and we have the convergence claim for it using R-WAPG. 
         \end{frame}
@@
                     \STATE{\textbf{Compute: } $f(y_{k + 1})$}
-                    \STATE{$\mu_k := D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2 + (1/2)\mu_k$;}
+                    \STATE{$\mu_{k + 1} := D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2 + (1/2)\mu_k$;}
                 \ENDFOR
@@
                 \centering
-                \includegraphics[width=0.64\textwidth]{assets/simple_regression_loss_sc_estimates_1024.png}
-                \caption{$N = 1024$, the $\mu$ estimates produced by Algorithm \ref{alg:free-rwapg} (R-WAPG) is recorded. }
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/simple_regression_loss_sc_estimates_1024.png}
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/simple_regression_loss_1024.png}
+                \end{subfigure}
+                \caption{
+                    $N = 1024$, the $\mu$ estimates produced by Algorithm \ref{alg:free-rwapg} (R-WAPG) is recorded.
+                }
                 \label{fig:simple-quadratic-r-wapg-mu-estimates}
@@
         \begin{frame}{Nesterov's idea of strong convexity transfer}
-            There is one detail that our R-WAPG doesn't incorporate on all Euclidean variants of FISTA. 
+            There is one detail in the literatures that our R-WAPG doesn't incorporate.  
             We consider this a minor augmentation for the future. 

### 2025-03-03 Notebook LaTEX/R-WAPG/relaxed-wapg-02-03-2025.tex
>w<, changes

--- 2025-02-28 Notebook LaTEX/R-WAPG/paper4.tex
@@
 % \input{presets/wang_full.tex}
-
+\usepackage{amsmath}
+\allowdisplaybreaks
 \usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{false}
@@
     In addition, we provide the convergence rate of strongly convex objective with a constant momentum term.
-    We also reformulate R-WAPG so that it doesn't require any parameter, without using the idea of restarting, which we call ``Free R-WAPG".
+    Without using the idea of restarting, we also reformulate R-WAPG as ``Free R-WAPG" so that it doesn't require any parameter.
     Explorative numerical experiments were conducted to show its competitive advantages.
@@
     \subsection{Motivations}
-        The Nesterov's acceleration scheme originally proposed in 1983 \cite{nesterov_method_1983} is a celebrated first order method for solving the minimization problem.
-        If the minimizer $x^*$ exists, then the optimality gap $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, a faster rate compared to gradient descent which is $\mathcal O(1/k)$.
+        The Nesterov acceleration scheme, originally proposed in 1983 \cite{nesterov_method_1983}, is a celebrated first order method for solving the minimization problem.
+        If the minimizer $x^*$ exists, then the optimality gap sequence $(F(x_k) - F(x^*))_{k\geq 1}$ decreases at a rate of $\mathcal O(1/k^2)$, a faster rate compared to gradient descent which is $\mathcal O(1/k)$.
         It's consider optimal in a certain sense, see Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018} for details.
-        However, things are not sunshine, rainbow and happily ever after because the above scheme is associated with the issue that if $F$ is $\mu > 0$ strongly convex, the optimality gap $F(x_k) - F(x^*)$ oscillates and converges sub-linearly, making it worse than gradient descent.
+        However, things are not sunshine, rainbow and happily ever after because the above scheme is associated with the issue that if $F$ is $\mu > 0$ strongly convex, the optimality gap sequence $(F(x_k) - F(x^*))_{k\geq 1}$ oscillates and converges sub-linearly, making it worse than the gradient descent.
 See page 9 of Su et al.
@@
         Beck and Teboulle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it has an $\mathcal O(1/k^2)$ convergence still, but it performs empirically better.
-        See \cite{aujol_parameter-free_2024}, \cite{necoara_linear_2019} and references therein for recent advancements in restarting accelerated proximal gradient algorithm.
-        \par
-        In the convex settings, the Variants Nesterov's Accelerated Gradient optimal to for cases when $\mu \ge 0$ and $\mu > 0$ are different.
+        See \cite{aujol_parameter-free_2024}, \cite{necoara_linear_2019} and references therein for recent advancements in restarting accelerated proximal gradient algorithms.
+        \par
+        In the convex setting, the variants that Nesterov's Accelerated Gradient are optimal to for cases when $\mu \ge 0$ and $\mu > 0$ are different.
         In this paper, we will show a unified framework for the convergence proof of both cases with a much relaxed condition for the recurrence of the momentum parameters used to extrapolate the iterates.
@@
         \begin{align}
-            & x_{k + 1} = y_k - L^{-1}\nabla F(y_k),
-            \\
-            & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right),
-            \\
-            & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1},
-            \\
-            & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k).
-        \end{align}\label{eqn:example-algorithm}
+            & x_{k + 1} := y_k - L^{-1}\nabla F(y_k),
+            \\
+            & t_{k + 1} := 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right),
+            \\
+            & \theta_{k + 1} := (t_{k} - 1)/t_{k + 1}, \label{eqn:example-algorithm}
+            \\
+            & y_{k + 1} := x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k).
+        \end{align}
 
         \subsection{Prior works}
-            Apidopoulos et al.
-\cite{apidopoulos_convergence_2018} showed that a relaxed choice of the sequence that doesn't strictly follow the Nesterov's rule still leads to the convergence of the momentum algorithm.
-            Besides restarting, See Attouch, et al. \cite{attouch_first-order_2022}, Maulen and Peypouquet \cite{maulen_speed_2023} and references within.
-            They present the idea of Hessian Damping for stabilizing the Nesterov's accelerated gradient without/with restarting.
+            In \cite{apidopoulos_convergence_2018} Apidopoulos et al. showed that a relaxed choice of the sequence that doesn't strictly follow Nesterov's rule 
+            still leads to the convergence of the momentum algorithm. In \cite{aujol_parameter-free_2024}, Aujol et al. gave a parameter free FISTA by adaptive restart and backtracking. 
+           In Attouch, et al. \cite{attouch_first-order_2022}, Maulen and Peypouquet \cite{maulen_speed_2023}. the authors
+            present the idea of Hessian Damping for stabilizing Nesterov's accelerated gradient method without/with restarting.
 
     \subsection{Contributions of this paper}
-        Our contributions are two folds, theoretical and practical.
-        Our results are based the assumption $F = f + g$ where $g:\RR^n \rightarrow \overline\RR$ is convex proper and closed, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function.
+        Our are concerned with the composite model
+        $\min_{x\in\RR^n}\{F(x)= f(x) + g(x)\},$ 
+        where $g:\RR^n \rightarrow \overline\RR$ is a proper,  closed and convex function, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function.
+        Our contributions are two folds: theoretical and practical.
         \par
@@
         It can upper bound $F(x_k) - F(x^*)$ for sequences $(t_k)_{k \ge 0}$ that doesn't follow Nesterov's update rule, and it unifies the convergence results of several Euclidean variants of FISTA.
-        Secondly, we present an alternative to restarting that performs well empirically inspired by a detail in the convergence proof of R-WAPG with extensive numerical experiments.
-        \par
-        \textbf{A summary of our main results follow. }
-        Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''.
-        The choices for $\theta_k$ varies for different variants of the accelerated proximal gradient algorithm.
-        In Chambolle and Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space.
-        In Chapter 10 of Beck's Book \cite{beck_first-order_2017}, a variant called V-FISTA can achieve the faster linear convergence rate: $\mathcal O((1 - \sqrt{\mu/L})^k)$ on the optimality gap for $\mu > 0$ strongly convex $F$.
-        V-FISTA has $\theta_t = (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa = \mu/L$.
-        \par
-        We relax the traditional choice of the sequence $\theta_k$ in Equation \eqref{eqn:example-algorithm} and showed an upper bound of the optimal gap.
+        Secondly, as an alternative to restarting, we present the method of Free R-WAPG which estimates the modulus of convexity as the algorithm executes.
+Extensive numerical experiments illustrate that our method performs well empirically.
+        \par
+        \textbf{A summary of our main results follows. }
+        Nesterov's acceleration extrapolates $y_{k + 1} := x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} := (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''.
+        The choices for $\theta_k$ vary for different variants of the accelerated proximal gradient algorithm.
+        In Chambolle and Dossal \cite{chambolle_convergence_2015}, it has $t_k := (k + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space.
+        In Chapter 10 of Beck's Book \cite{beck_first-order_2017}, a variant called V-FISTA can achieve the faster linear convergence rate: $\mathcal O((1 - \sqrt{\mu/L})^k)$ on the optimality gap for $\mu > 0$ strongly convex $f$.
+        V-FISTA has $\theta_k := (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa := L/\mu$.
+        \par
+        We relax the traditional choice of the sequence $(\theta_k)_{k\geq 1}$ in equation \eqref{eqn:example-algorithm} and give an upper bound of the optimal gap.
         Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
@@
         \end{align*}
-        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wapg-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
+        Our first main result shows that if $\theta_{k + 1} := (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wapg-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
         \begin{align*}
@@
         \end{align*}
-        Our second main result shows that for any $\alpha_k \ge 0$ the choice of sequence $\alpha_k = a/(a + k)$ results in $\rho_k > 1$ for all $k \in \N$ such that R-WAPG reduces to a variant of FISTA proposed in Chambolle and Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}.
-        When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}.
-        In Theorem \ref{thm:fixed-momentum-fista}, it demonstrates that R-WAPG frameworks gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex.
-        Finally, we did the necessary work and present three equivalent forms of R-WAPG in Section \ref{sec:rwapg-equiv-repr} that are comparable to notable Euclidean variants of FISTA and beyond.
-This shows the descriptive power of our R-WAPG framework.
-        \par
-        Our practical contribution is an algorithm inspired by a detail in the proof of Proposition \ref{prop:wapg-convergence} which is called ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}).
-        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_k$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ from the Bregman divergence of $f$ with minimal computational cost.
-        We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart.
+        Our second main result shows that for any $a \ge 2$ the choice of sequence $\alpha_k := a/(a + k)$ results in $\rho_k \geq 1$ for all $k \in \N$ such that R-WAPG reduces to a variant of FISTA proposed in Chambolle and Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}.
+        When $\mu := 0, \rho_k := 1$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}; when $\mu > 0, \rho_k := 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}.
+        In Theorem \ref{thm:fixed-momentum-fista}, we demonstrate that R-WAPG framework gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex.
+        Finally, we present three equivalent forms of R-WAPG in Section \ref{sec:rwapg-equiv-repr} that are comparable to notable Euclidean variants of FISTA and beyond.
+This shows the enormous flexibility of our R-WAPG framework.
+        \par
+        Our practical contribution is an algorithm called ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}), and is is inspired by the proof of Proposition \ref{prop:wapg-convergence}.
+        The algorithm is parameter free because it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_k$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ from the Bregman divergence of $f$ with minimal computational cost.
+        We conduct ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart.
         \par
@@
         In Section~\ref{sec:preliminaries}, we formulate the composite optimization
-        problem considered in the paper and give a proximal inequality connecting the objective function
-         and the proximal gradient
+        problem considered in the paper and give a proximal inequality connecting the objective function,
+        the proximal gradient
         operator and gradient mapping.
@@
         %Proposition \ref{prop:stepwise-lyapunov}, 
-        a key inequality based on a single generic iterative step that acts similar to a descent lemma.
-        Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG in Definition \ref{def:wapg} and defines the R-WAPG sequence in Definition \ref{def:rwapg-seq}.
-Using Proposition \ref{prop:stepwise-lyapunov} from Section~\ref{sec:stepwise-stuff}
+        a key inequality based on a single generic iterative step that acts similar to a descent lemma; see Proposition \ref{prop:stepwise-lyapunov}.
+It is crucial for the convergence analysis of relaxed weak accelerated proximal gradient (R-WAPG) studied later.
+        Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG and defines the R-WAPG sequence. Using Proposition \ref{prop:stepwise-lyapunov} from Section~\ref{sec:stepwise-stuff}
          and the R-WAPG sequence, 
@@
         we provide the convergence rate of R-WAPG.
-        Section \ref{sec:rwapg-equiv-repr} focuses on three equivalent representations of the R-WAPG algorithms that are comparable to instances of APG found in the literatures.
-        Section \ref{sec:rwapg-literatures} formulates FISTA, and V-FISTA sequences as instance of the R-WAPG sequences.
-        This section proves the convergence rate of several variants of FISTA using the equivalent forms introduced in Section \ref{sec:rwapg-equiv-repr} and the convergence rate developed Section \ref{sec:rwapg-formulation-convergence}.
-        Finally, Section \ref{sec:free-rwapg} gives a parameter free version of R-WAPG algorithm and showcase its numerical experiments for regression, LASSO.
+        Section \ref{sec:rwapg-equiv-repr} focuses on three equivalent representations of the R-WAPG algorithm that are comparable to instances of APG found in the literatures.
+        Section \ref{sec:rwapg-literatures} formulates FISTA, and V-FISTA sequences as the instances of R-WAPG sequences.
+        This section proves the convergence rate of several variants of FISTA using the equivalent forms introduced in Section \ref{sec:rwapg-equiv-repr} and the convergence rate developed in Section \ref{sec:rwapg-formulation-convergence}.
+        In Section \ref{sec:free-rwapg} we give a parameter free version of R-WAPG algorithm and showcase its numerical experiments for regression, LASSO.
+We conclude with some discussions and perspectives of our results in Section~\ref{s:discussion}.
 
@@
     Throughout, we make the following assumption unless specified.
-    \begin{assumption}[Smooth and nonsmooth additives]\label{ass:smooth-nsmooth-additive}
+    \begin{assumption}[smooth and nonsmooth additives]\label{ass:smooth-nsmooth-additive}
         \;
@@
     \end{align*}
-    The following lemma provides important properties of $\mathcal M^{L^{-1}}(\cdot; y), \widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$.
+    The following lemma provides important properties of $\mathcal M^{L^{-1}}(\cdot; y)$ and $ \widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$.
     \begin{lemma}\label{lemma:pg-envelope}
@@
     \end{proof}
-    \begin{theorem}[Proximal inequality]\label{thm:prox-grad-ineq}
+    \begin{theorem}[proximal inequality]\label{thm:prox-grad-ineq}
         Let $F$ be given by Assumption \ref{ass:smooth-nsmooth-additive}.
@@
             \quad
-            \text{By Lemma \ref{lemma:pg-envelope}}
+            \text{(By Lemma \ref{lemma:pg-envelope})}
             \\
@@
 \section{Stepwise formulation of weak accelerated proximal gradient}\label{sec:stepwise-stuff}
-    The goal of this section is to build the R-WAPG algorithm which is described in the Definition \ref{def:wapg} of the next section.
-    \par
-    Definition \ref{def:stepwise-wapg} describes one iteration of the R-WAPG algorithm.
+    The goal of this section is to provide some preparatory results for the R-WAPG algorithm described in Definition \ref{def:wapg} of the next section.
+    Definition \ref{def:stepwise-wapg} below describes one iteration of the R-WAPG algorithm.
     It defines the procedure of generating $x_{k + 1}, v_{k + 1}$ given any $x_k, v_k$.
-    Proposition \ref{prop:stepwise-lyapunov} states the inequality \eqref{ineq:stepwise-lya-2}  of a decreasing quantity involving $F(x_k), F(x_{k + 1})$ at each iteration.
+    The main result of this section is Proposition \ref{prop:stepwise-lyapunov}, which states the key inequality \eqref{ineq:stepwise-lya-2}  of a decreasing quantity involving both $F(x_k)$ and $F(x_{k + 1})$ at each iteration.
     \par
@@
     \begin{assumption}\label{ass:regret-gap}
-        Given $x_k, y_k, v_k$ where $k \in \mathbb Z_+$, we define the following quantities
+        Given $x_k, y_k, v_k$ where $k \in \mathbb \NN$, we define the following quantities:
         \begin{align}
@@
 
-    \begin{definition}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
+    \begin{definition}[stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
         Assume $0 \le \mu < L$.
-        Fix any $k \in \mathbb Z_+$.
+        Fix any $k \in \NN$.
         For any $(v_k, x_k), \alpha_k \in (0, 1), \gamma_k > 0$, let $\hat \gamma_{k + 1}$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ be given by:
         \begin{align}
-            \hat \gamma_{k + 1} &= (1 - \alpha_k)\gamma_k + \mu \alpha_k, \label{eqn:stepwise-wapg-eqn1}
-            \\
-            y_k &=
+            \hat \gamma_{k + 1} &:= (1 - \alpha_k)\gamma_k + \mu \alpha_k, \label{eqn:stepwise-wapg-eqn1}
+            \\
+            y_k &:=
             (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), \label{eqn:stepwise-wapg-eqn2}
             \\
-            g_k &= \mathcal G_L (y_k), \label{eqn:stepwise-wapg-eqn3}
-            \\
-            v_{k + 1} &= \hat\gamma^{-1}_{k + 1}
+            g_k &:= \mathcal G_L (y_k), \label{eqn:stepwise-wapg-eqn3}
+            \\
+            v_{k + 1} &:= \hat\gamma^{-1}_{k + 1}
             (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), \label{eqn:stepwise-wapg-eqn4}
             \\
-            x_{k + 1} &= T_L(y_k). \label{eqn:stepwise-wapg-eqn5}
+            x_{k + 1} &:= T_L(y_k). \label{eqn:stepwise-wapg-eqn5}
         \end{align}
@@
         Let $v_k, x_k, y_k, v_{k + 1}, x_{k + 1}$ and $\alpha_k, \hat \gamma_{k + 1}, \gamma_{k}$ be given by Definition \ref{def:stepwise-wapg}.
-        Then for any $x^* \in \RR^n$ it satisfies:
+        Then for any $x^* \in \RR^n$ we have
         \begin{align}
@@
     \begin{proof}
-        The proof starts by showing that \eqref{eqn:Q1} and \eqref{eqn:Q2} below 
-        follow from \eqref{eqn:stepwise-wapg-eqn2}, then the desire results follows naturally using algebra.
-        We make the following observations from Definition \ref{def:stepwise-wapg}:
+        We start by showing that \eqref{eqn:Q1} and \eqref{eqn:Q2} below 
+        follow from \eqref{eqn:stepwise-wapg-eqn2}, and the desired result can be derived naturally using algebra.
+        By Definition \ref{def:stepwise-wapg}:
         \begin{align*}
@@
             }{1 + \alpha_k \gamma_k \hat \gamma_{k + 1}^{-1}}
-            \\
-            &=
+            =
             \frac{\alpha_k \gamma_k v_k + \hat \gamma_{k + 1} x_k}{\gamma_k + \alpha_k \mu}.
@@
             &= \alpha_k \gamma_k v_k - \alpha_k \gamma_k x_k
-            \\
-            &= \alpha_k \gamma_k(v_k - x_k)
+            = \alpha_k \gamma_k(v_k - x_k)
             \\
@@
             - \alpha_k(x_k - v_k)
-            \\
-            &= \alpha_k(x^* - x_k).
+            = \alpha_k(x^* - x_k).
         \end{align*}
@@
 
-    \begin{proposition}[Stepwise Lyapunov]\label{prop:stepwise-lyapunov}\;\\
+    Our main result is this section comes as follows.
+    \begin{proposition}[stepwise Lyapunov]\label{prop:stepwise-lyapunov}\;\\
         Let $k \in \mathbb Z_+$, $R_k \in \RR$.
@@
         We will prove the intermediate results above later.
-        Building upon these intermediate results, we are able to claim \eqref{ineq:stepwise-lya-2}.
-        It follows by subtracting $F(x^*)$ on \eqref{eqn:stepwise-lya-proof-step-3} which gives:
+        Building upon these intermediate results, we are able to claim \eqref{ineq:stepwise-lya-2}. Indeed,
+         subtracting $F(x^*)$ on \eqref{eqn:stepwise-lya-proof-step-3} gives:
         \begin{align}
@@
         } % PROOF SUMMARIZATION ENDS ===========================================================
-        \textbf{Proof of \eqref{eqn:stepwise-lya-proof-step-1}}:
+        \emph{Proof of \eqref{eqn:stepwise-lya-proof-step-1}}:
         Consider the first and the third term on LHS of \eqref{ineq:stepwise-lya-2} summed up:
@@
         \end{align}
-        \textbf{Proof of \eqref{eqn:stepwise-lya-proof-step-2}}:
+        \emph{Proof of \eqref{eqn:stepwise-lya-proof-step-2}}:
         By definition of $v_{k + 1}$, it has:
@@
         }
-        \textbf{Proof for \eqref{eqn:stepwise-lya-proof-step-3}}:
+        \emph{Proof of \eqref{eqn:stepwise-lya-proof-step-3}}:
         Adding the RHS of \eqref{expr:stepwise-lya-expr2.2}, \eqref{eqn:stepwise-lya-proof-eqn1} gives:
@@
         using \eqref{eqn:Q3} from Lemma \ref{lemma:ineq-q3}.
-        The last equality re-arranged terms and grouped the coefficients of $\epsilon_k$ together.
+        The last equality groups the coefficients of $\epsilon_k$ together.
         Continuing on \eqref{eqn:stepwise-lya-proof-eqn3} we have
         \begin{align}\label{eqn:stepwise-lya-proof-eqn3.1}
-        \begin{split}
+        %\begin{split}
             &
@@
                 R_k + \frac{\gamma}{2}\Vert v_k - x^*\Vert^2
-            \right)
+            \right)\nonumber
             \\&\quad
                 + \frac{(1 - \alpha_k)\mu\alpha_k\gamma}{2\hat \gamma}\Vert v_k - y_k\Vert^2
-                + \frac{\mu \alpha_k}{2}\Vert v_k - x^*\Vert^2
+                + \frac{\mu \alpha_k}{2}\Vert v_k - x^*\Vert^2 \nonumber
             \\&\quad
@@
                 + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle
-            \\
+            \nonumber\\
             &=
@@
             \right)
-            \\ &\quad
+            \nonumber\\ &\quad
                 +
@@
                 + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle
-            \\
+            \nonumber\\
             & =
@@
                 + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle
-            \\ &=
+            \nonumber\\ &=
             F(x_k) - \alpha_k(\epsilon_k + \langle g_k, x_k - x^*\rangle)
@@
             \right)
-            \\ &\quad
+            \nonumber\\ &\quad
                 +
                 \frac{\mu\alpha_k}{2} \Vert y_k - x^*\Vert^2
+            \nonumber
             \\&=
@@
             \right).
-        \end{split} % \tag{3.1*}
+        %\end{split} % \tag{3.1*}
         \end{align}
@@
         \end{align*}
-        \eqref{eqn:stepwise-lya-proof-step-3} is now justified.
-
+        Hence \eqref{eqn:stepwise-lya-proof-step-3} is justified.
     \end{proof}
@@
 \section{R-WAPG and its convergence rates}\label{sec:rwapg-formulation-convergence}
-    In this section we propose Relaxed Weak Accelerated Proximal Gradient (R-WAPG), see Definition \ref{def:wapg}.
-    R-WAPG algorithm generates iterates $(x_k, y_k, v_k)$ and admits an upper bound on $F(x_k) - F^*$ described in Proposition \ref{prop:stepwise-lyapunov}.
-    Definition \ref{def:rwapg-seq} introduces the concept of an R-WAPG sequences: $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ which is crucial.
-    The sequences parameterize the R-WAPG algorithm stated in Definition \ref{def:wapg}, it connects the step-wise formulation of R-WAPG (Definition \ref{def:stepwise-wapg}) and can describe the convergence claim of R-WAPG in Proposition \ref{prop:wapg-convergence}.
-    In the next section, it continues to play a crucial role in describing several equivalent forms of the R-WAPG algorithm, and their corresponding convergence claim.
+    In this section we propose \emph{Relaxed Weak Accelerated Proximal Gradient (R-WAPG)}, see Definition \ref{def:wapg}.
+    The R-WAPG algorithm generates iterates $(x_k, y_k, v_k)$ and admits an upper bound on $F(x_k) - F^*$ described in Proposition \ref{prop:stepwise-lyapunov}.
+    Definition \ref{def:rwapg-seq} introduces the R-WAPG sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ which are crucial for our analysis.
+    These sequences parameterize the R-WAPG algorithm, connect the step-wise formulation of R-WAPG (Definition \ref{def:stepwise-wapg}) and can guarantee the convergence of R-WAPG in Proposition \ref{prop:wapg-convergence}.
+    In the next section, they continue to play an 
+    essential role in describing several equivalent forms of the R-WAPG algorithm, and their corresponding convergence claims.
     \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}\;\\
@@
         \end{align*}
-        We call $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ the \textbf{R-WAPG Sequences}.
+        We call $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ as the {R-WAPG sequences}.
     \end{definition}
@@
     % \end{observation}
-    Not all properties of the R-WAPG sequences are used in the convergence proof, some other of its properties such as $\alpha_k \in (\mu/L, 1)$ plays a role much later on in Section \ref{sec:rwapg-equiv-repr}.
-    The following lemma states two consequences of the definition of the R-WAPG sequences which will play a crucial role in the convergence proof immediately after.
-    \begin{lemma}{Consequences from the definition of R-WAPG Sequences}\label{lemma:r-wapg-seq-consequences}
-        Let sequence $(\alpha_k)_{k\ge 0}$ and $(\rho_k)_{k \ge0}$ be given by Definition \ref{def:rwapg-seq}, then they have:
+    Not all properties of the R-WAPG sequences are used in the convergence proof, some other properties such as $\alpha_k \in (\mu/L, 1)$ plays a role much later on in Section \ref{sec:rwapg-equiv-repr}.
+    The following lemma states two consequences of the R-WAPG sequences, which will play a crucial role in the convergence proof immediately after.
+    \begin{lemma}\label{lemma:r-wapg-seq-consequences}
+        Let sequence $(\alpha_k)_{k\ge 0}$ and $(\rho_k)_{k \ge0}$ be given by Definition \ref{def:rwapg-seq}. Then 
         \begin{enumerate}
-            \item $\rho_k > 0$ for all $k \ge 0$.
-            \item $\forall k \ge 1: L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 +\mu\alpha_k$.
+            \item\label{i:rho} $\rho_k > 0$ for all $k \ge 0$.
+            \item\label{i:alpha} $\forall k \ge 1: L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 +\mu\alpha_k$.
         \end{enumerate}
@@
     \begin{proof}
-        The first item is obvious by $\alpha_k \in (\mu/L, 1)$.
-        The second item is direct by definition of $\rho_k$ which has for all $k \ge 1$:
+        \ref{i:rho} is obvious by $\alpha_k \in (\mu/L, 1)$.
+        \ref{i:alpha} is direct by definition of $\rho_k$ which has for all $k \ge 1$:
         \begin{align*}
@@
     We now give Relaxed Weak Accelerated Proximal Gradient in details.
-    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}\;\\
+    \begin{definition}[relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}\;\\
         Choose any $x_1 \in \RR^n, v_1 \in \RR^n$.
@@
             &= L\alpha_k^2
-            \\
-            &= (1 - \alpha_k)\gamma_k + \alpha_k \mu
+            = (1 - \alpha_k)\gamma_k + \alpha_k \mu
             \\
             &= (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu
-            \\
-            &= (1 - \alpha_k)\rho_{k - 1}\hat \gamma_{k} + \alpha_k \mu.
-        \end{align*}
-        Therefore, the sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ fits the same recurrence relation from Lemma \ref{lemma:r-wapg-seq-consequences} (ii).
+            = (1 - \alpha_k)\rho_{k - 1}\hat \gamma_{k} + \alpha_k \mu.
+        \end{align*}
+        Therefore, the sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ fits the ecurrence relation from Lemma \ref{lemma:r-wapg-seq-consequences}\ref{i:alpha}.
         \par
@@
     Here is the main result of this section.
-    \begin{proposition}[R-WAPG convergence claim]\label{prop:wapg-convergence}\; \\
+    \begin{proposition}[R-WAPG convergence]\label{prop:wapg-convergence}\; \\
         Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$.
@@
             & = F(x_{2}) - F(x^*) + R_2 + \frac{\hat \gamma_{2}}{2}\Vert v_{2} - x^*\Vert^2
-            & \hat \gamma_2 = L \alpha_1^2 , \text{ Definition \ref{def:wapg}}
+            & (\hat \gamma_2 = L \alpha_1^2 , \text{ Definition \ref{def:wapg}})
             \\
@@
             \right)
-            & \quad \text{By Proposition \ref{prop:stepwise-lyapunov}}
+            & \quad \text{(By Proposition \ref{prop:stepwise-lyapunov})}
             \\
@@
 \section{Equivalent representations of R-WAPG}\label{sec:rwapg-equiv-repr}
-    The goal of this section is to reduce Definition \ref{def:wapg} into simpler forms that are equivalent to what commonly appears in the literatures.
-    In the literatures, variants of Accelerated Proximal Gradient algorithm such as FISTA, V-FISTA has different representations.
-    Sometimes the same algorithm include two iterates $(x_k, y_k)$, sometimes they include three iterates $(x_k, y_k, z_k)$.
-    In this section we simplify R-WAPG to these representations commonly found in the literatures and showed that they are equivalent.
-    These equivalent representations are listed in Definition \ref{def:r-wapg-intermediate}, \ref{def:r-wapg-st-form} and \ref{def:r-wapg-momentum-form}.
-    These forms are equivalent, and they are crucial for proving the convergence of existing variants found in the literatures in the upcoming Section \ref{sec:rwapg-literatures}.
+    The goal of this section is to reduce Definition \ref{def:wapg} into various forms that are equivalent to what commonly appear in the literature.
+    Variants of Accelerated Proximal Gradient algorithm such as FISTA, V-FISTA have different representations.
+    Sometimes the same algorithm include two iterates $(x_k, y_k)$; sometimes they include three iterates $(x_k, y_k, z_k)$.
+    In this section we simplify R-WAPG to these representations commonly found in the literature and showed that they are equivalent.
+    These equivalent representations are listed in Definitions \ref{def:r-wapg-intermediate}, \ref{def:r-wapg-st-form} and \ref{def:r-wapg-momentum-form}.
+    These forms are equivalent, and they are crucial for proving the convergence of existing variants found in the literature; see Section \ref{sec:rwapg-literatures}.
     \par
@@
         &\text{Definition \ref{def:wapg}}   \iff
-        \text{Definition \ref{def:r-wapg-intermediate}}  & \text{By Proposition \ref{prop:wapg-first-equivalent-repr}.}
+        \text{Definition \ref{def:r-wapg-intermediate}}  & \text{(By Proposition \ref{prop:wapg-first-equivalent-repr}).}
         \\
         & \text{Definition \ref{def:r-wapg-intermediate}}
-        \iff \text{Definition \ref{def:r-wapg-st-form}} & \text{By Proposition \ref{def:r-wapg-st-form}.}
+        \iff \text{Definition \ref{def:r-wapg-st-form}} & \text{(By Proposition \ref{def:r-wapg-st-form}).}
         \\
@@
         \text{Definition }\ref{def:r-wapg-momentum-form}.
-        & \text{By Proposition }\ref{prop:r-wapg-momentum-repr}.
+        & \text{(By Proposition \ref{prop:r-wapg-momentum-repr})}.
     \end{align*}
@@
     % SECTION INTRODUCTION ENDS
-    \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
-        Given any initial $(x_1, v_1)$, and a sequence $(\tau_k)_{k \ge 1}, (\xi_k)_{k \ge 1}$ such that for all $k \ge 1$ $\tau_k \in (0, 1), \xi_k \in (0, 1)$, and the iterates $(y_k, z_{k + 1}, x_{k + 1})_{k \ge 1}$ satisfies recursively that:
+    \begin{proposition}[abstract similar triangle form]\label{prop:abs-st-form}\;\\
+        Given any initial $(x_1, v_1)$, and a sequence $(\tau_k)_{k \ge 1}, (\xi_k)_{k \ge 1}$ such that for all $k \ge 1$ $\tau_k \in (0, 1), \xi_k \in (0, 1)$, and the iterates $(y_k, z_{k + 1}, x_{k + 1})_{k \ge 1}$ satisfy recursively:
         \begin{align*}
@@
         \end{align*}
-        If $1 + \xi_k + \tau_k = L\delta_k\; \forall k \ge 1$, then for all $k \ge 1$:
+        If $1 + \xi_k + \tau_k = L\delta_k\; \forall k \ge 1$, then for all $k \ge 1$ we have
         \begin{align}\label{eqn:abs-st-key}
-            v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}\tau_k(x_{k + 1} - x_k).
+            v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}\tau_k(x_{k + 1} - x_k),
         \end{align}
-        Which makes the algorithm a similar triangle form.
+        which makes the algorithm a similar triangle form.
     \end{proposition}
@@
         \end{align*}
-        Which allows for:
+        Thus,
         \begin{align*}
@@
         This section lists three equivalent representations of the R-WAPG algorithm.
-        They are comparable to existing APG algorithms in the literatures such as Exercise 12.1 in Ryu, Yin \cite{ryu_large-scale_2022}, Similar Triangle form from Lee et al.
-\cite{lee_geometric_2021}, Ahn Sra \cite{ahn_understanding_2022} and momentum form of (2.2.19) in Nesterov \cite{nesterov_lectures_2018}.
-        Specific instances of Accelerated Proximal Gradient algorithm that has the same form as the Definition \ref{def:r-wapg-intermediate}, Definition \ref{def:r-wapg-st-form} and Definition \ref{def:r-wapg-momentum-form} in the literatures are stated in the remarks that follows the definitions.
+        They are comparable to existing APG algorithms in the literature such as Exercise 12.1 in Ryu, Yin \cite{ryu_large-scale_2022}, similar triangle form in Lee et al.
+\cite{lee_geometric_2021} and Ahn Sra \cite{ahn_understanding_2022}, and momentum form of (2.2.19) in Nesterov \cite{nesterov_lectures_2018}.
+        Specific instances of Accelerated Proximal Gradient algorithm that has the same form as the Definition \ref{def:r-wapg-intermediate}, Definition \ref{def:r-wapg-st-form} and Definition \ref{def:r-wapg-momentum-form} in the literature are stated in the remarks that follow the definitions.
         \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
@@
             If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}),
-            then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$, and for all $k\ge 1$ namely
+            then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$,  namely, for all $k\ge 1$,
             \begin{align}
@@
         \begin{proof}
-            \textbf{We will show \eqref{eqn:rwapg-first-equiv-form-eqn-1} first.}
+            {We will show \eqref{eqn:rwapg-first-equiv-form-eqn-1} first.}
             For all $k \ge 1$, by R-WAPG (Definition \ref{def:wapg}), it has:
@@
                 \right)
-                \\
-                &=
+                =
                 \left(
@@
             \par
-            \textbf{Next, we show \eqref{eqn:rwapg-first-equiv-form-eqn-2}.}
+            {Next, we show \eqref{eqn:rwapg-first-equiv-form-eqn-2}.}
             From the Definition \ref{def:wapg}, for all $k \ge 1$, $v_{k + 1}$ it follows that:
@@
             Let iterates $(y_k, x_{k}, v_{k})_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge 0}$ be given by Definition \ref{def:r-wapg-intermediate}.
-            Then for all $k \ge 1$, iterate $y_k, x_{k + 1}, v_{k + 1}$
+            Then for all $k \ge 1$, iterates $y_k, x_{k + 1}, v_{k + 1}$
             satisfy:
@@
                 1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
-                \\
-                &=
+                =
                 \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
@@
             \;\\
-            Let sequence $(\alpha_k, \rho_k)_{k \ge 0}$ and iterates $(x_k, v_k, y_k)_{k\ge 1}$ given by R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}).
+            Let sequence $(\alpha_k, \rho_k)_{k \ge 0}$ and iterates $(x_k, v_k, y_k)_{k\ge 1}$ be given by the R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}).
             Then it has:
@@
         \begin{proof}
-            Start by considering the update rule for $v_k$ from the Definition \ref{def:r-wapg-st-form} which has for all $k \ge 1$:
+            Start by considering the update rule for $v_k$ from Definition \ref{def:r-wapg-st-form} which has for all $k \ge 1$:
             \begin{align}
@@
             \end{align}
-            For all $k\ge 1$, substitute RHS of \eqref{eqn:third-eqv-repr-proof-step1} into the above yields:
+            For all $k\ge 1$, substitute RHS of \eqref{eqn:third-eqv-repr-proof-step1} into the above to obtain:
             {\small
@@
             To show (ii), we show $y_1 = x_1$ when $v_1 = x_1$.
-            Set $k = 1$ in \eqref{eqn:third-eqv-repr-proof-step1}, it follows that:
+            Put $k = 1$ in \eqref{eqn:third-eqv-repr-proof-step1} to obtain:
             \begin{align*}
@@
 
-\section{R-WAPG unifies existing accelerations scheme}\label{sec:rwapg-literatures}
+\section{R-WAPG unifies existing acceleration schemes}\label{sec:rwapg-literatures}
     In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are much more flexible.
-    They generalize many existing sequences used in accelerated proximal gradient schemes.
-    \par
-    Using the results from Section \ref{sec:rwapg-equiv-repr}, this section will demonstrate that several Euclidean variants of FISTA in the literatures reduce to our R-WAPG definition if a specific R-WAPG sequences with additional constraints.
-    As a result, (Proposition \ref{prop:wapg-convergence}) holds hence, substituting specialized of R-WAPG sequence $(\alpha_k)_{k \ge 0}$, we derive convergence rates consistent with results in the literatures for these variants of FISTA.
-    \par
-    The table below shows the R-WAPG convergence results unify convergence claims for various settings.
+    They significantly generalize many existing sequences used in accelerated proximal gradient schemes.
+    \par
+    Using results from Section \ref{sec:rwapg-equiv-repr}, this section will demonstrate that several Euclidean variants of FISTA in the literatures reduce to our R-WAPG for specific R-WAPG sequences with additional constraints.
+    As a result, Proposition \ref{prop:wapg-convergence} applies.
+By substituting specialized R-WAPG sequences $(\alpha_k)_{k \ge 0}$, we derive convergence rates consistent with results in the literature for these variants of FISTA (fast iterative shrinkage-thresholding algorithm).
+    \par
+    The table below shows that our R-WAPG convergence results unify convergence claims for various settings in the literature.
     The first row shows the generic convergence results of our R-WAPG.
-    The rows after are algorithms found in the literatures.
+    The rows after are algorithms found in the literature.
     First columns states the assumption made for parameter $\mu$, the second and third columns show the specific examples of $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ specialized from Definition \ref{def:rwapg-seq}.
-    Last column shows the convergence rate on $F(x_k) - F^*$ (the optimality gap) and our theorem that proves the claim.
+    Last column shows the convergence rate of $F(x_k) - F^*$ (the optimality gap) and our theorem that proves the claim.
     \begin{table}[H]
@@
     \end{table}
-    The lemma follows characterizes momentum sequences in Chambolle and Dossal \cite{chambolle_convergence_2015} using Definition \ref{def:rwapg-seq}.
-    \begin{lemma}[R-WAPG sequences as inverted FISTA sequence]\label{lemma:inverted-fista-seq}
+    The next lemma characterizes momentum sequences in Chambolle and Dossal \cite{chambolle_convergence_2015} using Definition \ref{def:rwapg-seq}.
+    \begin{lemma}[R-WAPG sequence as inverted FISTA sequence]\label{lemma:inverted-fista-seq}
         Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}.
@@
             \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$.
-            \item Let $t_k := \alpha_k^{-1}$, then $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``Inverted FISTA sequence''.
+            \item Let $t_k := \alpha_k^{-1}$, then $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``inverted FISTA sequence''.
             \item $\prod_{i = 1}^k\max(1, \rho_{k - 1})(1 - \alpha_k) = \alpha_k^2 \quad (\forall k \ge 1)$.
@@
             &\ge (1 - \alpha_1)\alpha_0^2
-            \\
-            &= (1 - \alpha_1)
+            = (1 - \alpha_1)
             \\
@@
         Therefore, (i) holds.
-        (i) is proved.
         \par
@@
         \alpha_k)= \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)$ for all $k \ge 1 $.
-        By definition $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ sequences they have for all $k \ge 1$:
+        By the definitions of $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ sequences they have for all $k \ge 1$:
         \begin{align*}
@@
     \begin{remark}
-        The sequence $t_k$ is exactly the same as in Chambolle and Dossal 
+        The sequence $(t_k)_{k\geq 1}$ in Lemma~\ref{lemma:inverted-fista-seq} is exactly the same as in Chambolle and Dossal 
         \cite[Theorem 3.1]{chambolle_convergence_2015}.
     \end{remark}
-    \begin{theorem}[FISTA first variant Chambolle, Dossal 2015]\label{thm:r-wapg-on-cham-doss}\;\\
+    \begin{theorem}[FISTA first variant Chambolle and Dossal 2015]\label{thm:r-wapg-on-cham-doss}\;\\
         Fix arbitrary $a \ge 2$.
@@
         Assume minimizer $x^*$ exists for function $F$.
-        Then algorithm produces $(x_k)_{k \ge0}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O(\alpha_k^2)$.
+        Then algorithm produces $(x_k)_{k \ge 0}$ such that $(F(x_{k}) - F(x^*))_{k\geq 0}$ converges at a rate of $\mathcal O(\alpha_k^2)$.
     \end{theorem}
     \begin{proof}
-        Proceeding stepwise, we want to specialize the results of Proposition \ref{prop:wapg-convergence} for the above choice of sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$  by completing the following steps.
+        Proceeding stepwise, we want to specialize the results of Proposition \ref{prop:wapg-convergence} for the above choice of sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$  by completing the following steps:
         \begin{enumerate}
             \item Show that the $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given are valid R-WAPG sequences, so we can use the convergence results.
-            \item Show $\rho_k \ge 1$ so Lemma \ref{lemma:inverted-fista-seq} (iii) applies.
+            \item Show $\rho_k \ge 1$, so Lemma \ref{lemma:inverted-fista-seq} (iii) applies.
             \item Simplify the conclusion of Proposition \ref{prop:wapg-convergence} by the previous two items.
@@
             \right)
-            & \text{By Lemma \ref{lemma:inverted-fista-seq} (iii)}
+            & \text{(By Lemma \ref{lemma:inverted-fista-seq}(iii))}
             \\
@@
     \begin{remark}
-        This algorithm described here is exactly the same algorithm being analyzed in the paper by Chambolle, Dossal \cite{chambolle_convergence_2015}.
+        This algorithm described here is exactly the same algorithm analyzed by Chambolle and Dossal in \cite{chambolle_convergence_2015}.
     \end{remark}
-    Following a similar pattern, the lemma and theorem follow show linear convergence for all $\mu > 0$ strongly convex function with R-WAPG sequence $\alpha_k = \alpha \in (\mu/L, 1)$ that is a fixed constant.
-
-    \begin{lemma}[Constant R-WAPG sequences]\label{lemma:constant-rwapg-seq}
+    Following a similar pattern, below we show linear convergences for all $\mu > 0$ strongly convex function with R-WAPG sequence 
+    $\alpha_k = \alpha \in (\mu/L, 1)$ that is a fixed constant.
+
+    \begin{lemma}[constant R-WAPG sequence]\label{lemma:constant-rwapg-seq}
         Suppose $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ are R-WAPG sequences given by Definition \ref{def:rwapg-seq} and assume $L > \mu > 0$.
@@
             &= \frac{1 - q\alpha^{-1}}{1 - \alpha}
-            \\
-            &= \frac{1 - q r^{-1}\sqrt{q^{-1}}}{1 - r \sqrt{q}}
+            = \frac{1 - q r^{-1}\sqrt{q^{-1}}}{1 - r \sqrt{q}}
             \\
@@
 
-    \begin{theorem}[Fixed momentum APG]\label{thm:fixed-momentum-fista}
+    \begin{theorem}[fixed momentum APG]\label{thm:fixed-momentum-fista}
         Assume $L > \mu > 0$, let a pair of constant R-WAPG sequence: $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Lemma \ref{lemma:constant-rwapg-seq}.
@@
         \end{tcolorbox}
-        Then the algorithm generates $(x_k)_{k \ge 1}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O\left(\left(1 - \min\left(\mu/(\alpha L), \alpha\right)\right)^k\right)$.
+        Then the algorithm generates $(x_k)_{k \ge 1}$ such that $(F(x_{k}) - F(x^*))_{k\geq 1}$ converges at a rate of $\mathcal O\left(\left(1 - \min\left(\mu/(\alpha L), \alpha\right)\right)^k\right)$.
     \end{theorem}
@@
             \right).
-            & \text{Lemma \ref{lemma:constant-rwapg-seq} (v)}
+            & \text{(Lemma \ref{lemma:constant-rwapg-seq}(v))}
         \end{align*}
@@
         When $r = 1$, the algorithm described above is exactly the same as the V-FISTA algorithm specified in (10.7.7) of Beck's book \cite{beck_first-order_2017}.
-        The above theorem gives convergence rate for a much relax choice of momentum parameter $\theta$ generalizing the convergence of constant step size FISTA to all convex and strongly convex function and all possible $\alpha_k \in (\mu/L, 1)$.
+        The above theorem gives convergence rate for a much relax choice of momentum parameter $\theta$, thus generalizing the convergence of constant step size FISTA to all convex and strongly convex functions and all possible $\alpha_k \in (\mu/L, 1)$.
         In addition, the convergence claim of R-WAPG holds for any $\mu$ smaller than the strong convexity modulus of $f$ that is not zero making the bounds $r \in (\sqrt{q}, \sqrt{q^{-1}})$ looser.
@@
     In this section, we propose Algorithm \ref{alg:free-rwapg} which estimates the $\mu$ constant as the algorithm executes using the Bregman divergence of $f$ estimated by previous iterates.
-    It is called Free R-WAPG because it doesn't require any knowledge of $\mu, L$ in prior for the smooth part $f$, making it parameter-free.
+    It is called \emph{Free R-WAPG} because it doesn't require any knowledge of $\mu, L$ in prior for the smooth part $f$, making it parameter-free.
     \begin{algorithm}
@@
     \par
-    Line 5-8 estimates upper bound for the Lipschitz constant and find $x^+$, the next iterates produced by proximal gradient descent on previous $y_k$;
+    In Algorithm \ref{alg:free-rwapg}, lines 5-8 estimate
+    upper bound for the Lipschitz constant and find $x^+$, the next iterates produced by proximal gradient descent on previous $y_k$;
     Line 8 updates $x_{k + 1}$ to be $x^+$, a successful iterate identified by the Lipschitz line search routine;
@@
             The solid line in the ribbon is the median value of $\delta_k$ across all experiment, the ribbon gives the maximum, minimum value of $\delta_k$ for each iteration across all experiments.
-            \par
             This numerical experiment shows that FR-WAPG initially behaves similar to M-FISTA, but it then started to behave like V-FISTA.
@@
         \subsubsection{LASSO}
-            This section present results of numerical experiment for solving the (least absolute shrinkage and selection operator) LASSO problem proposed by Tibshirani \cite{tibshirani_regression_1996}.
+            This section present results of numerical experiment for solving the LASSO (least absolute shrinkage and selection operator) problem proposed by Tibshirani \cite{tibshirani_regression_1996}.
             The problem of LASSO has smooth and nonsmooth additive parts given by:
@@
             \end{align*}
-            The smooth part is $f(x) =\frac{1}{2}\Vert Ax - b\Vert^2$ and the nonsmooth is $g(x) = \lambda\Vert x\Vert_1$.
+            The smooth part is $f(x) :=\frac{1}{2}\Vert Ax - b\Vert^2$ and the nonsmooth is $g(x) := \lambda\Vert x\Vert_1$.
             The objective function is coersive and the exact minimum, or minimizers are unknown.
@@
             For this specific experiment showed in the figure, the estimated value of $\mu, L$ which we feed into V-FISTA are $\mu = 7.432363627613958\times 10^{-18}$ and $L = 2321.737206983643$.
-            An important observation is that $\mu_k$ didn't converge to the true value in this case, however it didn't affect the convergence of $F(x_k) - F^*$.
-
-\section{Discussions}
-    This paper provides the results of an upper bound on the optimality gap $F(x_k) - F^*$ for smooth plus nonsmooth composite optimization problem with convex objectives where under much weaker assumption for the momentum parameter.
-    The proposed R-WAPG unifies the convergence proof for major Euclidean variants of FISTA with strong convexity parameter $\mu \ge 0$.
-    To the best of our knowledge, there is no framework had been identified yet in the literatures that proves the convergences of several variants (with and without strong convexity parameter) with momentum sequences that doesn't follow the Nesterov's rule.
-    \par
-    In addition, we proposed explorative numerical experiments for Free R-WAPG (Algorithm \ref{alg:free-rwapg}) showcasing a parameter free algorithm that doesn't use the idea of restarting to achieve competitive convergence rate.
+            An important observation is that $(\mu_k)_{k\geq 1}$ didn't converge to the true value in this case, however it didn't affect the convergence of $(F(x_k) - F^*)_{k\geq 1}$.
+
+\section{Discussions}\label{s:discussion}
+    This paper provides upper bounds on the optimality gap $F(x_k) - F^*$ for smooth plus nonsmooth composite optimization problems with convex objectives under much weaker assumptions for the momentum parameter.
+    The proposed R-WAPG unifies the convergence proof of major Euclidean variants of FISTA with strong convexity parameter $\mu \ge 0$.
+    To the best of our knowledge, there is no framework had been identified yet in the literature that proves the convergences of several variants (with and without strong convexity parameter) with momentum sequences that doesn't follow Nesterov's rule.
+    \par
+    In addition, we proposed explorative numerical experiments for Free R-WAPG showcasing a parameter free algorithm that doesn't use the idea of restarting to achieve competitive convergence rate.
     Unfortunately a precise description of the convergence rate of Free R-WAPG remains a mystery.
     It will be interesting to explore this line of research.
-    Our convergence framework gives an upper bound using the sequence $(\alpha_k)_{k \ge 0} \in (\mu/L, 1)$, but it requires knowing what the sequence would be in advanced given the initial conditions and the objective function.
-    \par
-    From a practical perspective, Algorithm \ref{alg:free-rwapg} shows competitive results of convergence for strongly convex function.
-    The algorithm behaves in way having characteristics of both V-FISTA and M-FISTA which is fascinating.
+    Our convergence framework gives an upper bound using the sequence $(\alpha_k)_{k \ge 0}$ in $(\mu/L, 1)$, but it requires knowing what the sequence would be in advanced given the initial conditions and the objective function.
+    \par
+    From a practical perspective, Free R-WAPG (Algorithm \ref{alg:free-rwapg}) shows competitive results of convergence for strongly convex functions.
+    The algorithm behaves in a way having characteristics of both V-FISTA and M-FISTA which is fascinating.
     In addition, of being parameter free, the algorithm works well with auto-differentiation framework because it requires the function value at the same point where the gradient is evaluated at $y_k$.
@@
 
+\section*{Acknowledgements}
+The research of HL and XW was partially supported by
+the NSERC Discovery Grant of Canada.
+
 \bibliographystyle{siam}

### 2025-03-04 Notebook LaTEX/Proposal/presentation.tex
>w<, changes

@@
     \begin{enumerate}
-        \item H. Li and X. Wang, \textit{A Parameter Free Accelerated Proximal Gradient Method Without Restarting}, preprint, (2025).
+        \item H. Li and X. Wang, \textit{Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations}, preprint, (2025).
     \end{enumerate}
@@
     \begin{frame}{Introduction}
-        Part I: Introduction to Relaxed Weak Accelerated Proximal Gradient (R-WAPG). 
+        Part I: Introduction to Relaxed Weak Accelerated Proximal Gradient (R-WAPG) and Catalyst Acceleration. 
         \begin{block}{Upcoming Contents: }
@@
                         \\
-                        y_k &= 
+                        y_k &:= 
                         (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
@@
                         % \\
-                        v_{k + 1} &= 
+                        v_{k + 1} &:= 
                         \hat\gamma^{-1}_{k + 1}
@@
                         \\
-                        x_{k + 1} &= T_L y_k. 
+                        x_{k + 1} &:= T_L y_k. 
                     \end{align*}    
@@
                 \item We proved the upcoming equivalences forms of R-WAPG in the draft papers. 
-                \item Previous claimed generic convergence results will apply to all equivalent forms of R-WAPG will now come. 
+                \item Previous claimed generic convergence results will apply to all equivalent forms of R-WAPG. 
             \end{enumerate}    
@@
                     \begin{align*} 
-                        & y_{k} = 
+                        & y_{k} := 
                         \left(
@@
                         \\
-                        & x_{k + 1} = 
+                        & x_{k + 1} := 
                         y_k - L^{-1} \mathcal G_L y_k, 
                         \\
-                        & v_{k + 1} = 
+                        & v_{k + 1} := 
                         \left(
@@
                     \begin{align*}
-                        & y_k = 
+                        & y_k := 
                         \left(
@@
                         \\
-                        & x_{k + 1} = 
+                        & x_{k + 1} := 
                         y_k - L^{-1} \mathcal G_L y_k, 
                         \\
-                        & v_{k + 1} = 
+                        & v_{k + 1} := 
                         x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k). 
@@
                     \begin{align*}
-                        & x_{k + 1} = y_k - L^{-1}\mathcal G_Ly_k, 
+                        & x_{k + 1} := y_k - L^{-1}\mathcal G_Ly_k, 
                         \\
                         & 
-                        y_{k + 1} = 
+                        y_{k + 1} := 
                         x_{k + 1} + 
@@
                     \left(0, 
+                        \mu, 
                         \mu + \frac{L - \mu}{N - 1},
@@
                 \item $L, \mu$, are estimated by $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$. 
-                \item The synthetic solution is $x^+ = [1\; -1\; 1 \; \cdots ]^T \in \RR^N$ and $b = Ax^+ \in \RR^M$.
+                \item The synthetic solution is $x^+ = [1\;, -1\;, 1 \;, \cdots ]^T \in \RR^N$ and $b = Ax^+ \in \RR^M$.
                 \item $x_0\in \RR^N$ is the initial guess with i.i.d random variable from a standard normal distribution. Same initial guess shared by FR-WAPG, V-FISTA, M-FISTA. 
@@
                 \caption{
-                    A single LASSO experiment results, with $M = 64, 256$. 
+                    A single LASSO experiment results, with $M = 64, N = 256$. 
                     We had $\mu = 7.432363627613958\times 10^{-18}$ and $L = 2321.737206983643$.
@@
             There is one detail in the literatures that our R-WAPG doesn't incorporate.  
-            We consider this a minor augmentation for the future. 
-            \begin{enumerate}
-                \item In Nesterov's 2013 paper \cite{nesterov_gradient_2013}, he considers accelerated  minimization problem $\phi = f + g$ with $f$ $L_f$ smooth and $g$ being $\mu_g \ge 0$ strongly convex.
-                \item Algorithm 5, Chambolle, Pock \cite{chambolle_introduction_2016} captures several variants of FISTA, and it assumes that $F = f + g$ where $f, g$ has strong convexity constant $\mu_f \ge 0, \mu_g \ge 0$ respective so $F$ is $\mu := \mu_f + \mu_g \ge 0$ strongly convex.
+            We consider this a minor augmentation in the future. 
+            \begin{enumerate}
+                \item In Nesterov's 2013 paper \cite{nesterov_gradient_2013}, he considered accelerated minimization problem $\phi = f + g$ where $f$ is $L_f$ smooth and $g$ is $\mu_g \ge 0$ strongly convex.
+                \item Algorithm 5, Chambolle and Pock \cite{chambolle_introduction_2016} captured some variants of FISTA, and they assumed that $F = f + g$ where $f, g$ has strong convexity constant $\mu_f \ge 0, \mu_g \ge 0$ respective so $F$ is $\mu := \mu_f + \mu_g \ge 0$ strongly convex.
             \end{enumerate}
@@
         \begin{frame}{Notations and Variance Reduced Methods}
+            Notations for inner loop, outer loop of Catalyst Acceleration. 
             \begin{block}{Catalyst notations}
@@
                 For any $k \in \N$, $y \in \RR^n$. 
-                Suppose $\mathbb M$ generates iterates $(z_{k, t})_{t \ge 0}$ for the inner loop iteration such that there exists $C_{\mathbb M} > 0$, and it has: 
-                {\small
-                \begin{align*}
-                    \mathcal M_F^{\kappa^{-1}}(z_{k, t}, y) - \mathcal M^*_{F, \kappa^{-1}}(y) 
+                Suppose $\mathbb M$ generates iterates $(z_{k, t})_{t \ge 0}$ for the inner loop iteration such that there exists $C_{\mathbb M} > 0, \tau_{\mathbb M} \in (0, 1)$, and it has: 
+                {\small
+                \begin{align*}
+                    \mathcal M_F^{1/\kappa}(z_{k, t}, y) - \mathcal M^*_{F, 1/\kappa}(y) 
                     &\le 
@@
                     \left(
-                        \mathcal M_{F}^{\kappa^{-1}}(z_{k,0})
+                        \mathcal M_{F}^{1/\kappa}(z_{k,0})
                         -
-                        \mathcal M^*_{F, \kappa^{-1}}(y)
+                        \mathcal M^*_{F, 1/\kappa}(y)
                     \right). 
@@
                 $$
-                Then the $\mathbb A$ generates $(x_{k})_{k \ge 0}$ such that 
+                Then $\mathbb A$ generates $(x_{k})_{k \ge 0}$ such that 
                 $$
@@
                     \frac{8}{(k + 2)^2}\left(
-                        \left(1 + \frac{2}{\eta}\right)^2(F(x_k) - F^*)
+                        \left(1 + \frac{2}{\eta}\right)^2(F(x_0) - F^*)
                         + \frac{\kappa}{2}\Vert x_0 - x^*\Vert^2
@@
         \begin{frame}{Total complexity}
-            We count $m$, the number of iteration experienced by $\mathbb M$ up to the $k$ iteration of $\mathbb A$. 
+            We count $m$, the number of total iterations experienced by $\mathbb M$ up to the $k$ iteration of $\mathbb A$. 
             \begin{enumerate}
@@
                     &\le \widetilde{\mathcal O}\left(
-                        \tau_{\mathbb M}\sqrt{\mu}/(\mu + \kappa)
-                    \right). 
+                        \left(
+                            1 - \tau_{\mathbb M}\sqrt{\mu/(\mu + \kappa)}
+                        \right)^m
+                    \right)
                 \end{align*}
@@
                 \begin{align*}
-                    m &\le \sum_{i - 1}^{k} k T_{\mathbb M} \log(i + 2) \le k T_{\mathbb M} \log(k + 2) 
+                    m 
+                    &\le 
+                    \sum_{i = 1}^{k} T_{\mathbb M} \log(i + 2) 
+                        \le k T_{\mathbb M} \log(k + 2) 
                     \le T_{\mathbb M}k(k + 2)
@@
                 Let the initial estimate be $x_0 \in \RR^n$, fix parameters $\kappa > 0$ and $\alpha_0 = \sqrt{q}$ where $q = \mu/(\kappa + \mu)$. 
-                Let $(\delta_k)_{k \ge 0}$ be an absolute error sequence chosen for the evaluation for inexact proximal point method. 
+                Let $(\delta_k)_{k \ge 0}$ be an relative error sequence chosen for the evaluation for inexact proximal point method. 
                 \begin{tcolorbox}
@@
                 \begin{enumerate}
-                    \item If $F$ is smooth then choose $z_k = y_k$. 
+                    \item If $F$ is smooth then choose $z_{k, 0} = y_k$. 
                     \item Else it's composite, define $f_k(x) = f(x) + \frac{\kappa}{2}\Vert x - y_k\Vert^2$ and do 
@@
                 \item $N_{\mathbb M} \le \widetilde{\mathcal O}\left(\tau_{\mathbb M}^{-1}\sqrt{\kappa/\epsilon}\log(\epsilon^{-1})\right)$ if $\mu = 0$, 
-                \item $N_{\mathbb N}\le \widetilde{\mathcal O}\left((\tau_{\mathbb M}\sqrt{q})^{-1}\log(\epsilon^{-1})\right)$ if $\mu > 0$. 
+                \item $N_{\mathbb M}\le \widetilde{\mathcal O}\left((\tau_{\mathbb M}\sqrt{q})^{-1}\log(\epsilon^{-1})\right)$ if $\mu > 0$. 
             \end{enumerate}
@@
             \begin{block}{A key detail about Catalyst}
-                The smoothness assumption is baked into Assumption \ref{ass:linear-convergence-inner-loop}, where it states that the $\mathbb M$ needs to have linear convergence rate. 
+                The smoothness assumption is used in Assumption \ref{ass:linear-convergence-inner-loop}, where it states that the $\mathbb M$ needs to have linear convergence rate. 
             \end{block}
             All VRMs method in the literature requires Lipschitz smoothness and strong convexity to achieve linear convergence rate. 
-            No linear convergent first order algorithm exists for all strong convex function by Theorem 2.1.5 in Nesterov's book \cite{nesterov_lectures_2018}. 
+            No linear convergent first order algorithm exists for all strongly convex function by Theorem 2.1.5 in Nesterov's book \cite{nesterov_lectures_2018}. 
             Hence, here is our question: 
@@
                 \item Theorem 2.1.17 \cite{nesterov_lectures_2018} (Linear rate lower bound for strong convexity and smoothness) doesn't apply on $\mathbb M$. 
-                Instead Theorem 3.2.5 applies and the lower bound is $\mathcal O(1/k)$. 
+                Instead, Theorem 3.2.5 applies and the lower bound is $\mathcal O(1/k)$. 
             \end{enumerate}

### 2025-03-04 Notebook LaTEX/Proposal/proposal.tex
>w<, changes

@@
 \section{Unifying NAG, and weakening the sequence assumption for convergences}\label{sec:unify-nes-acceleration}
-    This section is based on our unpublished draft paper. 
-    The Nesterov's acceleration scheme which was originally proposed in 1983 \cite{nesterov_method_1983} is a celebrated first order method for solving the minimization problem. 
-    Here, NAG stands for Nesterov's Accelerated Gradient. 
-    It refers to a general class of momentum method where the gradient are evaluated on an extrapolated iterate using the previous two iterates. 
+        The Nesterov acceleration scheme, originally proposed in 1983 \cite{nesterov_method_1983}, is a celebrated first order method for solving the minimization problem.
+        If the minimizer $x^*$ exists, then the optimality gap sequence $(F(x_k) - F(x^*))_{k\geq 1}$ decreases at a rate of $\mathcal O(1/k^2)$, a faster rate compared to gradient descent which is $\mathcal O(1/k)$.
+        It's consider optimal in a certain sense, see Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018} for details.
+        However, things are not sunshine, rainbow and happily ever after because the above scheme is associated with the issue that if $F$ is $\mu > 0$ strongly convex, the optimality gap sequence $(F(x_k) - F(x^*))_{k\geq 1}$ oscillates and converges sub-linearly, making it worse than the gradient descent.
+See page 9 of Su et al.
+\cite{su_differential_2016}.
+        \par
+        This issue motivated a vast amount of literatures aims at improving, interpreting, and extending this method.
+        Restarting is a popular solution to address the issue of obtaining better convergence rate when the objective function is strongly convex.
+        Beck and Teboulle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it has an $\mathcal O(1/k^2)$ convergence still, but it performs empirically better.
+        See \cite{aujol_parameter-free_2024}, \cite{necoara_linear_2019} and references therein for recent advancements in restarting accelerated proximal gradient algorithms.
+        \par
+        In the convex setting, the variants that Nesterov's Accelerated Gradient are optimal to for cases when $\mu \ge 0$ and $\mu > 0$ are different.
+        In this paper, we will show a unified framework for the convergence proof of both cases with a much relaxed condition for the recurrence of the momentum parameters used to extrapolate the iterates.
+        For simplicity consider minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$.
+        Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$.
+        We will list the following example algorithm of Nesterov's Accelerated Gradient to refer to while introducing the context and prior works.
         Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by:
         \begin{align}
-        & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
-        \\
-        & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
-        \\
-        & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
-        \\
-        & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
-    \end{align}\label{eqn:example-algorithm}
-    If the minimizer $x^*$ exists, then the optimality gap $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, a faster rate compared to gradient descent which is $\mathcal O(1/k)$. 
-    It's consider optimal in some sense and see Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018} for details. 
+            & x_{k + 1} := y_k - L^{-1}\nabla F(y_k),
+            \\
+            & t_{k + 1} := 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right),
+            \\
+            & \theta_{k + 1} := (t_{k} - 1)/t_{k + 1}, \label{eqn:example-algorithm}
+            \\
+            & y_{k + 1} := x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k).
+        \end{align}
         \subsection{Contributions}
+        Our are concerned with the composite model
+        $\min_{x\in\RR^n}\{F(x)= f(x) + g(x)\},$ 
+        where $g:\RR^n \rightarrow \overline\RR$ is a proper,  closed and convex function, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function.
+        Our contributions are two folds: theoretical and practical.
+        \par
         Inspired specifically by the technique of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, firstly we present a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG) in Section \ref{sec:rwapg-formulation-convergence}.
-        It has the ability to upper bound $F(x_k) - F(x^*)$ for sequences $(t_k)_{k \ge 0}$ that follows a rule much weaker than Nesterov's update rule. 
-        In addition to a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(t_k)_{k \ge 1}$. 
-        Secondly, we present an alternative to restarting that performs well empirically inspired by a small detail in the convergence proof of R-WAPG. 
-        It also has descriptive power to describe several variants of FISTA in the literatures.  
-        \par
-        Our contributions are two folds, theoretical and practical. 
-        Our results are based the assumption $F = f + g$ where $g:\RR^n \rightarrow \overline\RR$ is convex proper and closed, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function.
-        \par
-        \textbf{A summary of our main results follow. } 
-        Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''. 
-        The choices for $\theta_k$ varies for different variants of the accelerated proximal gradient algorithm. 
-        In Chambolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space. 
-        In Chapter 10 of Beck's Book \cite{beck_first-order_2017}, a variant called V-FISTA can achieve the faster linear convergence rate: $\mathcal O((1 - \sqrt{\mu/L})^k)$ on the optimality gap for $\mu > 0$ strongly convex $F$.
-        V-FISTA has $\theta_t = (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa = \mu/L$. 
-        \par
-        We relax the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example-algorithm} and showed an upper bound of the optimal gap. 
+        It can upper bound $F(x_k) - F(x^*)$ for sequences $(t_k)_{k \ge 0}$ that doesn't follow Nesterov's update rule, and it unifies the convergence results of several Euclidean variants of FISTA.
+        Secondly, as an alternative to restarting, we present the method of Free R-WAPG which estimates the modulus of convexity as the algorithm executes.
+Extensive numerical experiments illustrate that our method performs well empirically.
+        \par
+        \textbf{A summary of our main results follows. }
+        Nesterov's acceleration extrapolates $y_{k + 1} := x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} := (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''.
+        The choices for $\theta_k$ vary for different variants of the accelerated proximal gradient algorithm.
+        In Chambolle and Dossal \cite{chambolle_convergence_2015}, it has $t_k := (k + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space.
+        In Chapter 10 of Beck's Book \cite{beck_first-order_2017}, a variant called V-FISTA can achieve the faster linear convergence rate: $\mathcal O((1 - \sqrt{\mu/L})^k)$ on the optimality gap for $\mu > 0$ strongly convex $f$.
+        V-FISTA has $\theta_k := (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa := L/\mu$.
+        \par
+        We relax the traditional choice of the sequence $(\theta_k)_{k\geq 1}$ in equation \eqref{eqn:example-algorithm} and give an upper bound of the optimal gap.
         Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
@@
         \end{align*}
-        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wagp-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
+        Our first main result shows that if $\theta_{k + 1} := (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wapg-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
         \begin{align*}
@@
         \end{align*}
-        Our second main result shows that for any $\alpha_k \ge 0$ the choice of sequence $\alpha_k = a/(a + k)$ results in $\rho_k > 1$ for all $k \in \N$ such that R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}.
-        When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
-        In Theorem \ref{thm:fixed-momentum-fista}, it demonstrates that R-WAPG frameworks gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex.
-        Finally, we did the tedious work and present three equivalent forms of R-WAPG in Section \ref{sec:rwapg-equiv-repr} that are comparable to notable Euclidean variants of FISTA and beyond.
-This shows the descriptive power of our R-WAPG framework.
-        \par
-        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}). 
-        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ from the Bregman divergence of $f$ with minimal computational cost.
-        We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart.
-        \par 
-        Section \ref{sec:stepwise-stuff} states and proves Proposition \ref{prop:stepwise-lyapunov}, an inequality based on a single generic iterative step that acts similar to a descent lemma. 
-        Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG in Definition \ref{def:wapg} and defines the R-WAPG sequence in Definition \ref{def:rwapg-seq}. 
-        Proposition \ref{prop:wagp-convergence} states the convergence rate of R-WAPG through Proposition \ref{prop:stepwise-lyapunov} and the R-WAPG sequence. 
-        Section \ref{sec:rwapg-equiv-repr} gives three equivalent representations of the R-WAPG algorithms that are comparable to instances of APG found in the literatures. 
-        Section \ref{sec:rwapg-literatures} formulates FISTA, and V-FISTA sequences as instance of the R-WAPG sequences.
-        The section proves the convergence rate of several variants of FISTA using the equivalent forms introduced in Section \ref{sec:rwapg-equiv-repr} and the convergence rate developed Section \ref{sec:rwapg-formulation-convergence}.
-        Finally, in Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcase the numerical experiments for regression, LASSO.
+        Our second main result shows that for any $a \ge 2$ the choice of sequence $\alpha_k := a/(a + k)$ results in $\rho_k \geq 1$ for all $k \in \N$ such that R-WAPG reduces to a variant of FISTA proposed in Chambolle and Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}.
+        When $\mu := 0, \rho_k := 1$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}; when $\mu > 0, \rho_k := 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}.
+        In Theorem \ref{thm:fixed-momentum-fista}, we demonstrate that R-WAPG framework gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex.
+        Finally, we present three equivalent forms of R-WAPG in Section \ref{sec:rwapg-equiv-repr} that are comparable to notable Euclidean variants of FISTA and beyond.
+This shows the enormous flexibility of our R-WAPG framework.
+        \par
+        Our practical contribution is an algorithm called ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}), and is is inspired by the proof of Proposition \ref{prop:wapg-convergence}.
+        The algorithm is parameter free because it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_k$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ from the Bregman divergence of $f$ with minimal computational cost.
+        We conduct ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart.
+        \par 
+        \textbf{The remainder of this paper is organized as follows. }
+        Section \ref{sec:stepwise-stuff} proves 
+        %Proposition \ref{prop:stepwise-lyapunov}, 
+        a key inequality based on a single generic iterative step that acts similar to a descent lemma; see Proposition \ref{prop:stepwise-lyapunov}.
+It is crucial for the convergence analysis of relaxed weak accelerated proximal gradient (R-WAPG) studied later.
+        Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG and defines the R-WAPG sequence.
+Using Proposition \ref{prop:stepwise-lyapunov} from Section~\ref{sec:stepwise-stuff} and the R-WAPG sequence,
+        %Proposition \ref{prop:wapg-convergence} states 
+        we provide the convergence rate of R-WAPG.
+        Section \ref{sec:rwapg-equiv-repr} focuses on three equivalent representations of the R-WAPG algorithm that are comparable to instances of APG found in the literatures.
+        Section \ref{sec:rwapg-literatures} formulates FISTA, and V-FISTA sequences as the instances of R-WAPG sequences.
+        This section proves the convergence rate of several variants of FISTA using the equivalent forms introduced in Section \ref{sec:rwapg-equiv-repr} and the convergence rate developed in Section \ref{sec:rwapg-formulation-convergence}.
+        In Section \ref{sec:free-rwapg} we give a parameter free version of R-WAPG algorithm and showcase its numerical experiments for regression, LASSO. 
+        % We conclude with some discussions and perspectives of our results in Section~\ref{s:discussion}.
 
@@
         Proposition \ref{prop:stepwise-lyapunov} states the inequality that describes a decreasing quantity that involves $F(x_k), F(x_{k + 1})$ at each single iteration. 
-        \begin{assumption}
-            Given $x_k, y_k, v_k$ where $k \in \mathbb Z_+$, we define the following quantities
+        \begin{assumption}\label{ass:regret-gap}
+            Given $x_k, y_k, v_k$ where $k \in \mathbb \NN$, we define the following quantities:
             \begin{align}
-                g_k &\defeq L(y_k - T_L y_k), 
+                g_k &\defeq L(y_k - T_L(y_k)),
                 \label{eqn:grad-map}
                 \\
-                l_F(x; y_k) &\defeq F(T_Ly_k) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
+                l_F(x; y_k) &\defeq F(T_L(y_k)) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2,
                 \label{eqn:lower-linearization}
                 \\
-                \epsilon_{k} &\defeq F(x_k) - l_F(x_k; y_k), 
+                \epsilon_{k} &\defeq F(x_k) - l_F(x_k; y_k).
                 \label{eqn:regret}
             \end{align}
-            Observe that by convexity of $F$, $\epsilon_k \ge 0$ for all $x_k, L > 0$. 
-            To see, use Theorem \ref{thm:prox-grad-ineq} and let $y = y_k, x = x_k$ which gives: 
-            \begin{align*}
-                F(x_k) - F(T_Ly_k)
-                - \langle L(y_k - T_Ly_k),x_k - y_k \rangle
-                - \frac{L}{2}\Vert y_k - T_Ly_k\Vert^2
-                - \frac{\mu}{2}\Vert x_k - y_k\Vert^2
-                &\ge 0
-                \\
-                \iff 
-                F(x_k) - F(T_Ly_k)
-                - \langle g_k,x_k - y_k \rangle
-                - \frac{1}{2L}\Vert g_k\Vert^2
-                &\ge 0. 
-            \end{align*}
         \end{assumption}
         The proposition follows provides upper bound to $F(x_{k + 1})$ in relations to $F(x_{k})$. 
-        \begin{definition}[Stepwise weak accelerated proximal gradient]\;\label{def:stepwise-wapg}\\
+        \begin{definition}[stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}
             Assume $0 \le \mu < L$.
-            Fix any $k \in \mathbb Z_+$. 
+            Fix any $k \in \NN$.
             For any $(v_k, x_k), \alpha_k \in (0, 1), \gamma_k > 0$, let $\hat \gamma_{k + 1}$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ be given by:
             \begin{align}
-                \hat \gamma_{k + 1} &= (1 - \alpha_k)\gamma_k + \mu \alpha_k, \label{eqn:stepwise-wapg-eqn1}
-                \\
-                y_k &= 
+                \hat \gamma_{k + 1} &:= (1 - \alpha_k)\gamma_k + \mu \alpha_k, \label{eqn:stepwise-wapg-eqn1}
+                \\
+                y_k &:=
                 (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), \label{eqn:stepwise-wapg-eqn2}
                 \\
-                g_k &= \mathcal G_L y_k, \label{eqn:stepwise-wapg-eqn3}
-                \\
-                v_{k + 1} &= \hat\gamma^{-1}_{k + 1}
+                g_k &:= \mathcal G_L (y_k), \label{eqn:stepwise-wapg-eqn3}
+                \\
+                v_{k + 1} &:= \hat\gamma^{-1}_{k + 1}
                 (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), \label{eqn:stepwise-wapg-eqn4}
                 \\
-                x_{k + 1} &= T_L y_k. \label{eqn:stepwise-wapg-eqn5}
+                x_{k + 1} &:= T_L(y_k). \label{eqn:stepwise-wapg-eqn5}
             \end{align}
         \end{definition}
-        \begin{proposition}[Stepwise Lyapunov]\;\label{prop:stepwise-lyapunov} \\
-            Let $k \in \mathbb Z_+$, $R_k \in \RR$. 
-            Given any $v_k, x_k$ and $\gamma_k > 0$ and $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}, \alpha_k$ that satisfies Definition \ref{def:stepwise-wapg}. 
-            Define: 
+        \begin{proposition}[stepwise Lyapunov]
+            Let $k \in \mathbb Z_+$, $R_k \in \RR$. \label{prop:stepwise-lyapunov}
+            Given any $v_k, x_k$ and $\gamma_k > 0$ and $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}, \alpha_k$ that satisfy Definition \ref{def:stepwise-wapg}.
+            With $\epsilon_k, y_k$ given by Assumption \ref{ass:regret-gap}, define:
             \begin{align}\label{eqn:stepwise-lya-1}
@@
         Definition \ref{def:rwapg-seq} introduces the concept of an R-WAPG sequences: $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ which is crucial.
-        The sequences parameterize the R-WAPG algorithm stated in Definition \ref{def:wapg}, it connects the step-wise formulation of R-WAPG (Definition \ref{def:stepwise-wapg}) and can describe the convergence claim of R-WAPG in Proposition \ref{prop:wagp-convergence}.
+        The sequences parameterize the R-WAPG algorithm stated in Definition \ref{def:wapg}, it connects the step-wise formulation of R-WAPG (Definition \ref{def:stepwise-wapg}) and can describe the convergence claim of R-WAPG in Proposition \ref{prop:wapg-convergence}.
         In the next section, it continues to play a crucial role in describing several equivalent forms of the R-WAPG algorithm, and their corresponding convergence claim. 
@@
         We now give Relaxed Weak Accelerated Proximal Gradient in details.
-        \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}\;\\
+        \begin{definition}[relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}\;\\
             Choose any $x_1 \in \RR^n, v_1 \in \RR^n$.
@@
             \begin{tcolorbox}
-                For $k=1, 2, 3, \cdots$
-                \begin{align*}
-                    \gamma_k &:= \rho_{k -1}L\alpha_{k - 1}^2, 
-                    \\
-                    \hat \gamma_{k + 1} & := (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2, 
-                    \\
-                    y_k &= 
+                For $k=1, 2, 3, \ldots$
+                \begin{align*}
+                    \gamma_k &\defeq \rho_{k -1}L\alpha_{k - 1}^2,
+                    \\
+                    \hat \gamma_{k + 1} & \defeq (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2,
+                    \\
+                    y_k &\defeq
                     (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k),
                     \\
-                    g_k &= \mathcal G_L y_k, 
-                    \\
-                    v_{k + 1} &= 
+                    g_k &\defeq \mathcal G_L (y_k),
+                    \\
+                    v_{k + 1} &\defeq
                     \hat\gamma^{-1}_{k + 1}
@@
                     \\
-                    x_{k + 1} &= T_L y_k. 
+                    x_{k + 1} &\defeq T_L y_k.
                 \end{align*}
@@
         Here is the main result of this section. 
-        \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}\; \\
+        \begin{proposition}[R-WAPG convergence]\label{prop:wapg-convergence}
             Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$.
             Let vector sequence $(y_k, v_{k}, x_{k})_{k \ge 1}$ and R-WAPG sequences $\alpha_k, \rho_k$ be given by Definition \ref{def:wapg}.
+            Let $\epsilon_k, y_k$ be given by Assumption \ref{ass:regret-gap}.
             Define $R_1 = 0$ and suppose that for $k = 1, 2, \ldots, N$, we have $R_k$ recursively given by:
@@
     \subsection{Equivalent representations of R-WAPG}\label{sec:rwapg-equiv-repr}
-        This section reduces Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 
-        In the literatures, variants of Accelerated Proximal Gradient algorithm such as FISTA, V-FISTA has different representations. 
-        This shows that R-WAPG provides a unified framework. 
-        These equivalent representations are listed in Definition \ref{def:r-wapg-intermediate}, \ref{def:r-wapg-st-form} and \ref{def:r-wapg-momentum-form}. 
-        These forms are equivalent under a subset of initial conditions. 
-        \par
-        They are comparable to existing APG algorithms in the literatures such as Exercise 12.1 in Ryu, Yin \cite{ryu_large-scale_2022}, Similar Triangle from Lee et al.
-\cite{lee_geometric_2021}, Ahn Sra \cite{ahn_understanding_2022} and momentum form of (2.2.19) in Nesterov \cite{nesterov_lectures_2018}.
-        Specific instances of Accelerated Proximal Gradient algorithm that has the same form as the Definition \ref{def:r-wapg-intermediate}, Definition \ref{def:r-wapg-st-form} and Definition \ref{def:r-wapg-momentum-form} in the literatures are stated in the remarks that follows the definitions.
-
+        This section lists three equivalent representations of the R-WAPG algorithm.
+        They are comparable to existing APG algorithms in the literature such as Exercise 12.1 in Ryu, Yin \cite{ryu_large-scale_2022}, similar triangle form in Lee et al.
+\cite{lee_geometric_2021} and Ahn Sra \cite{ahn_understanding_2022}, and momentum form of (2.2.19) in Nesterov \cite{nesterov_lectures_2018}.
+        Specific instances of Accelerated Proximal Gradient algorithm that has the same form as the Definition \ref{def:r-wapg-intermediate}, Definition \ref{def:r-wapg-st-form} and Definition \ref{def:r-wapg-momentum-form} in the literature are stated in the remarks that follow the definitions.
         \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\
@@
                 \begin{align*}
-                    & y_{k} = 
+                    & y_{k} \defeq
                     \left(
@@
                     \left(
-                        v_{k + 1} + 
+                        v_{k} +
                         \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
@@
                     \\
-                    & x_{k + 1} = 
-                    y_k - L^{-1} \mathcal G_L y_k, 
-                    \\
-                    & v_{k + 1} = 
+                    & x_{k + 1} \defeq
+                    y_k - L^{-1} \mathcal G_L (y_k),
+                    \\
+                    & v_{k + 1} \defeq
                     \left(
@@
                         \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
-                    \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
+                    \right) - \frac{1}{L\alpha_{k}}\mathcal G_L (y_k).
                 \end{align*}
@@
                 \begin{align*}
-                    & y_k = 
+                    & y_k \defeq
                     \left(
@@
                     \\
-                    & x_{k + 1} = 
-                    y_k - L^{-1} \mathcal G_L y_k, 
-                    \\
-                    & v_{k + 1} = 
+                    & x_{k + 1} \defeq
+                    y_k - L^{-1} \mathcal G_L (y_k),
+                    \\
+                    & v_{k + 1} \defeq
                     x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k).
@@
             To see graphical visualization on why such term is used to describe the APG algorithm in the literatures, see
-            (3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}. 
+            Sections (3.1), (4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}.
         \end{remark}
@@
                 \begin{align*}
-                    & x_{k + 1} = y_k - L^{-1}\mathcal G_Ly_k, 
+                    & x_{k + 1} \defeq y_k - L^{-1}\mathcal G_L (y_k),
                     \\
                     &
-                    y_{k + 1} = 
+                    y_{k + 1} \defeq
                     x_{k + 1} +
@@
             This format fits with (2.2.19) in Nesterov's book \cite{nesterov_lectures_2018}, however, the sequence $(\alpha_k)_{k \ge 0}$ would be given by a different rule.
-            See Theorem \ref{thm:r-wapg-on-cham-doss} and Lemma \ref{lemma:inverted-fista-seq} to see a specific choice of $(\alpha_k)_{k \ge0}, (\rho_k)_{ k\ge 0}$ such this equivalent form of R-WAPG is in fact two possible variants of the FISTA algorithm.
+            See Theorem \ref{thm:r-wapg-on-cham-doss} and Lemma \ref{lemma:inverted-fista-seq} for a specific choice of $(\alpha_k)_{k \ge0}, (\rho_k)_{ k\ge 0}$ such that this equivalent form of R-WAPG is in fact two possible variants of the FISTA algorithm.
         \end{remark}
@@
         Following a similar pattern, Proposition \ref{prop:wagp-st-form}, \ref{prop:r-wapg-momentum-repr} demonstrates two more equivalent representations of the R-WAPG intermediate form (Definition \ref{def:r-wapg-intermediate}) which are formulated into Definition \ref{def:r-wapg-st-form}, \ref{def:r-wapg-momentum-form}.
-        Convergence results from Proposition \ref{prop:wagp-convergence} applies to all these equivalent forms of R-WAPG. 
+        Convergence results from Proposition \ref{prop:wapg-convergence} applies to all these equivalent forms of R-WAPG.
         In brief, different equivalent reformulations are summarized as following:
@@
             &\text{Definition \ref{def:wapg}}   \iff
-            \text{Definition \ref{def:r-wapg-intermediate}}  & \text{By Proposition \ref{prop:wapg-first-equivalent-repr}.}
+            \text{Definition \ref{def:r-wapg-intermediate}}  & \text{(By Proposition \ref{prop:wapg-first-equivalent-repr}).}
             \\
             & \text{Definition \ref{def:r-wapg-intermediate}}
-            \iff \text{Definition \ref{def:r-wapg-st-form}} & \text{By Proposition \ref{def:r-wapg-st-form}.}
+            \iff \text{Definition \ref{def:r-wapg-st-form}} & \text{(By Proposition \ref{def:r-wapg-st-form}).}
             \\
@@
             \text{Definition }\ref{def:r-wapg-momentum-form}.
-            & \text{By Proposition }\ref{prop:r-wapg-momentum-repr}.
+            & \text{(By Proposition \ref{prop:r-wapg-momentum-repr})}.
         \end{align*}
@@
                     \\
-                    (Proposition \ref{prop:wagp-convergence})
+                    (Proposition \ref{prop:wapg-convergence})
                 \end{tabular}
@@
     This section introduces an algorithm of our creation inspired by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
-    Algorithm \ref{alg:free-rwapg} estimates the $\mu$ constant as the algorithm executes and pools the information using the Bregman Divergence of the smooth part function $f$. 
+    In this section, we propose Algorithm \ref{alg:free-rwapg} which estimates the $\mu$ constant as the algorithm executes using the Bregman divergence of $f$ estimated by previous iterates.
+    It is called \emph{Free R-WAPG} because it doesn't require any knowledge of $\mu, L$ in prior for the smooth part $f$, making it parameter-free.
     \begin{algorithm}
@@
             \STATE{\textbf{Compute: } $f(y_{k + 1})$}
-            \STATE{$\mu := (1/2)(2D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2) + (1/2)\mu$;}
+            \STATE{$\mu_{k + 1} := D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2 + (1/2)\mu_k$;}
         \ENDFOR
@@
     \par
-    Line 5-8 estimates upper bound for the Lipschitz constant and find $x^+$, the next iterates produced by proximal gradient descent on previous $y_k$; 
-    Line 9 updates $x_{k + 1}$ to be $x^+$, a successful iterate identified by the Lipschitz line search routine;
-    Line 10 updates the R-WAPG sequence $\alpha_k$ for the iterates $y_{k + 1}$;
-    Line 13 updates $\mu$ using the Bregman Divergence of $f$ from iterates $y_{k + 1}, y_k$. 
-    \par
-    Assume $L$ given is an upper bound of the Lipschitz smoothness constant of $f$, then the algorithm calls $f(\cdot)$ two times, and $\nabla f(\cdot)$ once per iteration. 
+    In Algorithm \ref{alg:free-rwapg}, lines 5-8 estimate
+    upper bound for the Lipschitz constant and find $x^+$, the next iterates produced by proximal gradient descent on previous $y_k$;
+    Line 8 updates $x_{k + 1}$ to be $x^+$, a successful iterate identified by the Lipschitz line search routine;
+    Line 11 updates the R-WAPG sequence $\alpha_k$ for the iterates $y_{k + 1}$;
+    Line 15 updates $\mu$ using the Bregman Divergence of $f$ from iterates $y_{k + 1}, y_k$.
+    \par
+    Assume $L$ given to initialize the R-WAPG is an upper bound of the Lipschitz smoothness constant of $f$ hence preventing the line search subroutine to be triggered.
+    Then the algorithm calls $f(\cdot)$ two times, and $\nabla f(\cdot)$ once per iteration.
     The algorithm computes $\nabla f(y_k)$ once for $x^+$, $f(y_{k + 1})$ once for Bregman Divergence because $f(y_{k})$ is evaluated from the previous iteration, and $f(x^+)$ once for Lipschitz constant line search condition.
@@
     And finally, it evaluates proximal of $g$ at $y_k - L^{-1}\nabla f(y_k)$ once.
+    \par
+    Suppose that initial $L$ given as input to Algorithm \ref{alg:free-rwapg} satisfies $L/2 \ge D_f(x, y)/\Vert x - y\Vert^2\;\forall x, y \in \RR^n$.
+    Then, the Lipschitz line search is not triggered and $L_k = L$ for all $k = 1, \ldots, N$.
+    Initialize $\mu = (1/2)L$ which it may not be a lower bound on the strong convexity constant for $f$.
+    With the additional assumption that the estimated $\mu_k < L$, the sequence $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg}.
+    Let's verify that $(\alpha_k)_{k \ge 0}$ is an R-WAPG sequence hence the convergence result (Proposition \ref{prop:wapg-convergence}) of R-WAPG applies.
+    \par
+    Let $\mu_k$ be an estimate produced by the algorithm and assume that it satisfies that $\mu_k/ L \in [0, 1)$ and $\alpha_k \in (\mu/L, 1)$.
+    Assuming inductively that $q = \mu_k/L$,  $\alpha_k \in (\mu/L, 1)$, we have
+    \begin{align*}
+        \alpha_{k + 1}
+        &=
+        (1/2)\left(
+            q - \alpha_k^2 + \sqrt{(q - \alpha_k^2)^2 + 4 \alpha_k^2}
+        \right)
+        \\
+        &=
+        (1/2)\left(
+            q - \alpha_k^2 + \sqrt{
+                (\alpha_k^2 - q + 2)^2 + 4q - 4
+            }
+        \right)
+        \\
+        &<
+        (1/2)\left(
+            q - \alpha_k^2 + \sqrt{
+                (\alpha_k^2 - q + 2)^2
+            }
+        \right) \le 1.
+    \end{align*}
+    $q \in (0, 1)$ by assumption $\mu < L$ so $4q - 4 < 0$ always.
+    It is not hard to see that $\alpha_{k + 1} > \mu/L$ as well.
+    Therefore, $\alpha_k \in (0, 1)$.
+    To prevent the case $\alpha_k = 1$, we may always force the estimate $\mu = L/2$ whenever $\mu > L/2$.
 
@@
         This section showcases results for the numerical experiments conducted using FR-WAPG algorithm (Algorithm \ref{alg:free-rwapg}), and compare with other APG algorithms in the literatures: the V-FISTA, and M-FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}.
-        We implemented in Julia \cite{bezanson_julia_2017} and FR-WAPG (Algorithm \ref{alg:free-rwapg}) with V-FISTA, M-FISTA. 
-        The equivalences highlighted in Proposition \ref{prop:r-wapg-momentum-repr} allows us to compare the sequence of iterates $(x_k)_{k \ge 1}, (y_k)_{k \ge0}$ for R-WAPG, VISTA and M-FISTA. 
+        We implemented in Julia \cite{bezanson_julia_2017}.
+        The equivalences highlighted in Proposition \ref{prop:r-wapg-momentum-repr} allows us to compare the sequence of iterates $(x_k)_{k \ge 1}, (y_k)_{k \ge0}$ for R-WAPG, V-FISTA and M-FISTA.
         \par
@@
             \delta_k := \log_2\left(
-                \NOG
+                \NOG_k
             \right)
             \text{ with }
-            \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}
-        \end{align*}
-        Since it's not the case that $F^*$ is always known in prior, we will the minimum of all $F(x_k)$ across all algorithms, all iterations $k$ as the surrogate for $F^*$ when the true value is unavailable.
+            \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}.
+        \end{align*}
+        Since it's not the case that $F^*$ is always known in prior, we will use the minimum of all $F(x_k)$ across all algorithms, all iterations $k$ as the surrogate for $F^*$ when the true value is unavailable.
         \par
@@
             \end{align*}
-            $A$ is set to be a positive semi-definite diagonal matrix, so the problem admits unique minimizer $x^* = \mathbf 0$ with minimum being zero. 
+            $A$ is set to be a positive semi-definite diagonal matrix, so the problem admits the minimizer $x^* = \mathbf 0$ (which is not unique) with minimum being zero.
             We apply Algorithm \ref{alg:free-rwapg}, M-FISTA, and V-FISTA.
-            The following parameters are used to set up the problem: 
+            The following parameters are used to set up the numerical experiments:
             \begin{enumerate}
-                \item $N$, the dimension of the problem which defines $A \in \RR^{N\times N}$, a diagonal matrix given by $N- 1$ linearly spaced with equal increment on the interval 
+                \item $N$, the dimension of the problem which defines $A \in \RR^{N\times N}$, a diagonal matrix given by $N- 1$ linearly spaced with equal increment on the interval $[\mu, L]$, and an extra number $0$, i.e.,
                 \begin{align*}
@@
             The maximum, minimum and median values of $\delta_k$ are measured for all algorithms at each iteration and plotted as a ribbon.
+            \par
             Results are shown in Figure \ref{fig:simple-quadratic-NOG}.
             The solid line in the ribbon is the median value of $\delta_k$ across all experiment, the ribbon gives the maximum, minimum value of $\delta_k$ for each iteration across all experiments.
-            FR-WAPG initially behaves similar to M-FISTA, but as the iteration goes on, it started to behave like V-FISTA.  
-            \par 
-            The most surprising feature here is the monotone descent, however, it's being numerical verified that the method is not monotone in general, it just looks monotone on the figure. 
+            This numerical experiment shows that FR-WAPG initially behaves similar to M-FISTA, but it then started to behave like V-FISTA.
+            It's numerically verified that the method is not monotone in general, and it just looks monotone in this experiment on this plot.
             \begin{figure}[H]
@@
                 \end{subfigure}
-                \caption{Simple convex quadratic experiments results for V-FISTA, M-FISTA, and R-WAPG. }
+                \caption{
+                    Statistics for experiments with simple convex quadratic for V-FISTA, M-FISTA, and R-WAPG.
+                }
                 \label{fig:simple-quadratic-NOG}
             \end{figure}
-            \par
             Another quantity that maybe interesting other than $\delta_k$ would be the estimated value of $\mu$ during at each iteration $k$.
             One individual experiment is carried out for the R-WAPG algorithm and the value of $\mu$ at each iteration is being recorded as well.
-            Figure \ref{fig:simple-quadratic-r-wapg-mu-estimates} showcases the results. 
-            In this experiment, the values oscillate and converges to the true $\mu$ value. 
-            Observe that the iteration when the estimates are nearing the true value corresponds to the iteration when the algorithm plateau away from its initial fast descent. 
+            Figure \ref{fig:simple-quadratic-r-wapg-mu-estimates} shows the estimated $\mu_k$ of FR-WAPG on the left and the convergence rate of the test algorithms on the right for one specific initial condition.
+            It shows the values of $\mu_k$ oscillates and converges to the true value of $\mu$.
+            Observe that the initial fast descent slows and FR-WAPG diverges from M-FISTA as $\mu_k$ converged.
             \begin{figure}[H]
                 \centering
-                \includegraphics[width=0.64\textwidth]{assets/simple_regression_loss_sc_estimates_1024.png}
-                \caption{$N = 1024$, the $\mu$ estimates produced by Algorithm \ref{alg:free-rwapg} (R-WAPG) is recorded. }
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/simple_regression_loss_sc_estimates_1024.png}
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/simple_regression_loss_1024.png}
+                \end{subfigure}
+                \caption{
+                    $N = 1024$, the $\mu$ estimates produced by Algorithm \ref{alg:free-rwapg} (R-WAPG) is recorded.
+                }
                 \label{fig:simple-quadratic-r-wapg-mu-estimates}
@@
         \subsubsection{LASSO}
-            This section present results of numerical experiment for solving the (least absolute shrinkage and selection operator) LASSO problem proposed by Tibshirani \cite{tibshirani_regression_1996}.
-            The problem of LASSO has smooth, nonsmooth additive parts given by: 
+            This section present results of numerical experiment for solving the LASSO (least absolute shrinkage and selection operator) problem proposed by Tibshirani \cite{tibshirani_regression_1996}.
+            The problem of LASSO has smooth and nonsmooth additive parts given by:
             \begin{align*}
@@
             \end{align*}
-            The smooth part is $f(x) =\frac{1}{2}\Vert Ax - b\Vert^2$ and the nonsmooth is $g(x) = \lambda\Vert x\Vert_1$. 
+            The smooth part is $f(x) :=\frac{1}{2}\Vert Ax - b\Vert^2$ and the nonsmooth is $g(x) := \lambda\Vert x\Vert_1$.
             The objective function is coersive and the exact minimum, or minimizers are unknown.
@@
                 \item $L, \mu$, are Lipschitz constant and the strong convexity constant for the smooth part of the objective which are not known prior.
-Hence, they are estimated by $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$ prior to experiment to assist the V-FISTA algorithm.
-                \item $x^+ = [1\; -1\; 1 \; \cdots ]^T \in \RR^N$, it's a vector with alternating $1, -1$ in it. 
+Consequently, they are estimated by $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$ prior to experiment to assist the V-FISTA algorithm.
+                \item $x^+ = [1,\; -1,\; 1, \; \cdots ]^T \in \RR^N$, it's a vector with alternating $1, -1$ in it.
                 \item Given $x^+$, it has $b = Ax^+ \in \RR^M$.
@@
                 \item $x_0\in \RR^N$ denotes the initial guess consist of i.i.d random variable realized from the standard normal distribution.
-                \item $\epsilon = 10^{-6} > 0$ sets the tolerance for all test algorithm on $\Vert \mathcal G_L(x_k)\Vert$. 
+                \item $\epsilon = 10^{-6} > 0$ sets the tolerance for all test algorithm on $\Vert \mathcal G_L(y_k)\Vert$.
             \end{enumerate}
             Experiments were conducted using V-FISTA, M-FISTA and FR-WAPG with $(M, N) = (64, 256)$ and $(M, N) = (64, 128)$ respectively.
-            A random matrix $A$ is realized and is fixed and the for all test algorithms and all repetitions. 
+            A random matrix $A$ is realized and is fixed for all test algorithms and all repetitions.
             The same experiment are repeated 30 times on all algorithms with a fixed random initial condition $x_k$ realized from the distribution.
             The aggregate statistics of $\delta_k$ are collected for all repetitions, and then grouped by the respective algorithm.
-            The results are showcased in Figure \ref{fig:batched-lasso}. 
+            Figure \ref{fig:batched-lasso} shows the results of the two experiments.
             The bump on the curve is due to a subset of test instances of the 30 repetition where the algorithms take larger number of iterations to terminate.
@@
                 \end{subfigure}
-                \caption{LASSO experiments. }
+                \caption{LASSO experiments statistics for test algorithms. }
                 \label{fig:batched-lasso}
             \end{figure}
-            \par
-            Another quantity of interest is the estimates of $\mu$ on each iteration of the algorithm. 
-            A single experiment were conducted and the estimates and $\delta_k$ are in Figure \ref{fig:single-lass-mu-estimates}
+            The experiment results shows faster convergence rate of FR-WAPG relative to V-FISTA, and it also shows that it behaves similarly to M-FISTA.
+            In addition, an experiment were conducted to show the estimate $\mu_k$ and optimality gap $F(x_k) - F^*$ in Figure \ref{fig:single-lass-mu-estimates}.
             \begin{figure}[H]
@@
                     \includegraphics[width=\textwidth]{assets/lasso_sc_estimates_256.png}
-                    \caption{The $\mu$ estimated by test algorithms for one LASSO experiment. }
+                    \caption{The $\mu_k$ estimated by FR-WAPG for one LASSO experiment. }
                 \end{subfigure}
-                \caption{A single LASSO experiment results, with $M = 64, 256$. }
+                \caption{A single LASSO experiment results, with $M = 64, N=256$.}
                 \label{fig:single-lass-mu-estimates}
@@
             For this specific experiment showed in the figure, the estimated value of $\mu, L$ which we feed into V-FISTA are $\mu = 7.432363627613958\times 10^{-18}$ and $L = 2321.737206983643$.
-            One of the most important feature is that the estimate $\mu$ doesn't converge to the true value, but it didn't affect the convergence of $\delta_k$.
+            An important observation is that $(\mu_k)_{k\geq 1}$ didn't converge to the true value in this case, however it didn't affect the convergence of $(F(x_k) - F^*)_{k\geq 1}$.
 
@@
             \begin{quote}
-                Is it possible to include the a $\mu_\Psi$ into our R-WAPG framework? 
+                Is it possible to include the $\mu_\Psi$ into our R-WAPG framework? 
             \end{quote}
@@
             We are quite certain about these required changes to achieve the open question because we invented R-WAPG.
-
-        % \subsubsection{Tying up some loose ends}
-        %     \todoinline{\noindent
-        %         In terms of practice, we are missing convergence rate of Free-RWAPG, and the convergence of the norm of the gradient method for R-WAPG. 
-        %     }
 
@@
                 \\
-                &\le \widetilde{\mathcal O}\left(
-                    \tau_{\mathbb M}\sqrt{\mu}/(\mu + \kappa)
+                &\le 
+                \widetilde{\mathcal O}\left(
+                    \left(
+                        1 - \tau_{\mathbb M}\sqrt{\mu/(\mu + \kappa)}
+                    \right)^m
                 \right). 
@@
             \begin{align*}
-                m &\le \sum_{i - 1}^{k} k T_{\mathbb M} \log(i + 2) \le k T_{\mathbb M} \log(k + 2) 
+                m &\le \sum_{i - 1}^{k} T_{\mathbb M} \log(i + 2) \le k T_{\mathbb M} \log(k + 2) 
                 \le T_{\mathbb M}k(k + 2) 
@@
                 \item Is it possible to extend the Nesterov's acceleration to non-convex settings such as convergence of gradient norm as described in Ghadimi \cite{ghadimi_accelerated_2016} without restarting?
-If so, what are the trade offs here if we wish to attain stronger convergence claims on the final iterates, or the function value?
+If so, what are the trade-off here if we wish to attain stronger convergence claims on the final iterates, or the function value?
                 \item Do there exist a way of extending inexact proximal point method to the nonconvex settings that also include Nesterov's acceleration? 

### 2025-03-21 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

--- 2025-01-23 Latex Templates/Scientific/main.tex
@@
-\documentclass[12pt]{article}
+\documentclass[12pt]{report}
 
@@
 \begin{document}
-
-\title{{\fontfamily{ptm}\selectfont Lorum ipsum}}
+\title{{\fontfamily{ptm}\selectfont Reading Notes}}
 
 \author{
-    Author 1 Name, Author 2 Name
-    \thanks{
-        Subject type, Some Department of Some University, Location of the University,
-        Country. E-mail: \texttt{author.name@university.edu}.
-    }
+    Alto
+    % \thanks{
+    %     Subject type, Some Department of Some University, Location of the University,
+    %     Country. E-mail: \texttt{author.name@university.edu}.
+    % }
 }
@@
 \todoinline{This paper is currently in draft mode. Check source to change options. }
-% \vskip 8mm
 
 \begin{abstract} 
-    \noindent
-    Lorem ipsum dolor sit amet, dicta iudicabit consequat ex vix, veniam legimus appetere has id, an pri graece epicuri detraxit.
-Ea aliquam expetendis posidonium eos, nam invenire corrumpit imperdiet ei.
-Et constituto dissentias usu, mel solum erant et.
-Mel dolorem menandri in.
-    \todo{This is just psuedo text. }
+    Reports on papers read. 
+    \todo{This is just psuedo text. This is just psuedo text. This is just psuedo text. This is just psuedo text \cite{clarke_optimization_1990}. }
 \end{abstract}
 
-\noindent{\bfseries 2010 Mathematics Subject Classification:}
-Primary 47H05, 52A41, 90C25; Secondary 15A09, 26A51, 26B25, 26E60, 47H09, 47A63.
-\noindent{\bfseries Keywords:}
-
 % ==============================================================================
-
-\section{Schur's Cone and Its Polar}
-    \begin{example}
-        Define
-        \begin{equation}\label{eqn:cone-1}
-            Q = \left\lbrace
-                x\in \RR^n \left|
-                    \sum_{i = 1}^{k} x_i
-                    \ge 0, \;
-                    k = 1 ,\cdots, n-1, \;
-                    x_1 + \cdots + x_n = 0
-                \right.
-            \right\rbrace.
-        \end{equation}
-        Then
-        \begin{align}
-            Q^\circ &= \left\lbrace
-               y\in\RR^n |
-               \langle y, x\rangle \ge 0 \; \forall x \in Q
-            \right\rbrace
-            \\
-            &=
-            \left\lbrace
-                y\in\RR^n | y_{1} \ge y_2\ge \cdots  \ge y_n
-            \right\rbrace.
-        \end{align}
-    \end{example}
-    \begin{proof}
-        We have $Q = H(\RR^{n - 1}_+)$, where
-        \begin{align}
-            H =
-            \begin{bmatrix}
-                1 &  & &
-                \\
-                -1 & 1 & &
-                \\
-                 & -1 & &
-                \\
-                &  & \ddots&
-                \\[-1em]
-                &  & & 1
-                \\
-                &  && -1
-            \end{bmatrix},
-        \end{align}
-        $H$ is a bi-diagonal matrix with zeros on the diagonal and -1 on its sub-diagonals. Indeed, for $x = (x_1, \cdots, x_{n - 1})\in \RR^{n - 1}_+$, we have
-        \begin{align}
-            y &= H x
-            \\
-            &=
-            \begin{bmatrix}
-                1 \\ -1 \\ 0 \\ \vdots \\ 0
-            \end{bmatrix}x_1 +
-            \begin{bmatrix}
-                0 \\ 1 \\ -1 \\ \vdots \\ 0
-            \end{bmatrix}x_2 +
-            \cdots
-            +
-            \begin{bmatrix}
-                0 \\ 0 \\ \vdots \\ 1 \\ -1
-            \end{bmatrix} x_{n - 1}
-            \\
-            &=
-            \begin{bmatrix}
-                x_1 \\ x_2 - x_1 \\ x_3 - x_2
-                \\ \vdots
-                \\-x_{n - 2} + x_{n - 1}\\
-                 - x_{n - 1}
-            \end{bmatrix}
-            = \begin{bmatrix}
-                y_1 \\ y_2 \\ y_3 \\ \vdots \\ y_{n - 1} \\ y_n
-            \end{bmatrix},
-        \end{align}
-        where $y_1 \ge 0, y_2 + y_1 \ge 0, \cdots, y_{n - 1}+ \cdots + y_1 \ge 0$, and $y_1 + \cdots + y_n = 0$.
-So $y\in Q$.
-Hence $H(\RR^{n - 1}_+)\subseteq Q$.
-Similarly, one can write for $y\in Q$, $\exists x \in \RR_+^{n- 1}$ with $y = Hx$.
-In fact, $x = y_1, x_2 = y_1 + y_2, \cdots, x_{n - 1} = y_1 + \cdots + y_{n - 1}, -x_{n - 1} = y_n$ because $y_1 + \cdots + y_n = 0$.
-In particular, $x\in \RR^{n - 1}_+$.
-        \par
-        Note that $y\in Q^\circ\iff y^{\intercal}a_i \ge 0$ for $i = 1,\cdots, n -1$. Where
-        \begin{align}
-            a_1 = \begin{bmatrix}
-                1 \\ -1 \\ 0 \\ \vdots \\ 0,
-            \end{bmatrix},
-            a_2 = \begin{bmatrix}
-                0 \\ 1 \\ -1 \\ \vdots \\ 0,
-            \end{bmatrix},
-            & \cdots,
-            a_n =
-            \begin{bmatrix}
-                0 \\ \vdots \\ 0  \\ 1 \\ -1
-            \end{bmatrix}.
-        \end{align}
-        Now $y^{\intercal} a_i \ge 0 \iff y_i - y_{i + 1}\ge 0$, for $i = 1,\cdots, n-1$. Hence $Q^\circ = \{ y\in \RR^n | y_1 \ge y_2 \ge \cdots \ge y_n\}$.
-
-    \end{proof}
-
-\section{Lorentz Cone and its Polar}
-    \begin{example}
-        \begin{equation}
-            L = \left\lbrace
-            (\xi, t) \in \RR^n \left| \;
-                \Vert \xi\Vert \le t, \xi \in \RR^{n - 1}
-            \right.
-            \right\rbrace.
-        \end{equation}
-        Then the polar cone of $L$ is $L^\circ = \{(x, s) \;|\; \langle (x, s), (\xi, t)\rangle \ge 0\}\} = L$.
-    \end{example}
-    \begin{proof}
-        \par
-        Let $(x, s) \in L^\circ$. Then $\langle (x, s), (\xi, t)\rangle \ge 0$, $\forall (\xi, t) \in L$, i. e. $\langle x, \xi\rangle + st \ge 0$.
-        \par
-        For $t > 0$, we have $\langle x, \xi/t\rangle \ge -s$, i.e.
-$\langle x, - \xi/t\rangle \le s$.
-Using $\Vert \xi\Vert \le t$ and by taking supremum over $\Vert \xi/t\Vert\le 1$, we obtain  $\Vert x\Vert \le s$.
-        \par
-        Hence $L^\circ = L$.
-    \end{proof}
-    \begin{corollary}
-        Let $A \in \RR^{n\times n}$ be positive definite. Define
-        $$
-            L_A =
-            \left\lbrace
-                (\xi, t)\in \RR^n \left|
-                    \sqrt{\langle \xi, A\xi\rangle} \le t
-                \right.
-            \right\rbrace.
-        $$
-        Then $(L_A)^\circ = \{ (\xi, t) \;|\; \sqrt{\langle \xi, A^{-1}\xi\rangle}\le t\}$.
-    \end{corollary}
-
-\section{Testing the references}
-    This book by Nesterov \cite{nesterov_lectures_2018}. 
-    This book by Heinz \cite{bauschke_convex_2017}.
-
-\section{Testing figures and images}
-    In Figure \ref{fig:two-test-figures}, it has Figure \ref{fig:two-test-fig-1} on the left and Figure \ref{fig:two-test-fig-2} on the right. 
-    \begin{figure}[H]
-        \begin{subfigure}[b]{0.47\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{assets/test-image-1.png}
-            \caption{Alto the unicorn. }
-            \label{fig:two-test-fig-1}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.47\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{assets/test-image-2.png}
-            \caption{Alto and Minty. }
-            \label{fig:two-test-fig-2}
-        \end{subfigure}
-        \caption{The above 2 images are test images for the figure, subfigure latex commands. }
-    \label{fig:two-test-figures}
-    \end{figure}
-
-\section*{Acknowledgments}
-    XW were supported by NSERC Discovery grants.
 

### 2025-03-26 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes
>w<, taking notes

@@
 
-\date{March 2, 2020}
+\date{Last Compiled: \today}
 
 \maketitle
-\todoinline{This paper is currently in draft mode. Check source to change options. }
 
@@
     Reports on papers read. 
-    \todo{This is just psuedo text. This is just psuedo text. This is just psuedo text. This is just psuedo text \cite{clarke_optimization_1990}. }
+    This is a LaTEX file for my own notes taking. 
+    It may accelerate the process of writing my thesis for my PhD degree. 
+    \todo{
+        This is just pseudo text. This is just pseudo text. 
+        This is just pseudo text. This is just pseudo text \cite{necoara_linear_2019}. 
+    }
+    \todoinline{This paper is currently in draft mode. Check source to change options. }
 \end{abstract}
+\chapter{The Basics of Optimization Theories}
+
+\chapter{Linear Convergence of First Order Method}
+    In this chapter, we are specifically interested in characterizing linear convergence of well known first order optimization algorithms. 
+    \section{Necoara's et al's Paper}
+        \subsection{The Settings}
+            The assumption follows give the same setting as Necoara et al. \cite{necoara_linear_2019}. 
+            % NECOARA ASSUMPTIONS 
+            \begin{assumption}\label{ass:necoara-2019-settings}
+                Consider optimization problem: 
+                \begin{align}
+                    -\infty < f^+ = \min_{x \in X} f(x) . 
+                \end{align}\label{problem:necoara-2019}
+                $X\subseteq \RR^n$ is a closed convex set. 
+                Assume projection onto $X$, denoted by $\Pi_X$ is easy. 
+                Denote $X^+ = \argmin_{x \in X}f(x) \neq \emptyset$, assume it's a closed set. 
+                Assume $f$ has $L_f$ Lipschitz continuous gradient, i.e: for all $x, y\in X$: 
+                \begin{align*}
+                    \Vert \nabla f(x) - \nabla f(y)\Vert \le L_f\Vert x - y\Vert. 
+                \end{align*}
+            \end{assumption}
+            % BREGMAN DIV DEFINITION
+            \begin{definition}[Bregman Divergence]
+                Let $f:\RR^n \rightarrow \overline \RR$ be a differentiable function. 
+                Define Bregman Divergence: 
+                \begin{align*}
+                    D_f: \RR^n \times \dom \nabla f \rightarrow \overline \RR:= 
+                    (x, y) \mapsto f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 
+                \end{align*}
+            \end{definition}
+            Some immediate consequences of Assumption \ref{ass:necoara-2019-settings} now follows. 
+            The variational inequality characterizing optimal solution has: 
+            \begin{align*}
+                x^+ \in X^+ \implies 
+                (\forall x \in X)\; \langle \nabla f(x^+), x - x^+\rangle \ge 0. 
+            \end{align*}
+            The converse is true if $f$ is convex. 
+            The gradient mapping in this case is: 
+            \begin{align*}
+                \mathcal G_{L_f}x = L_f(x - \Pi_{X}x). 
+            \end{align*}
+            % STRONG CONVEXITY DEFINITION
+            \begin{definition}[Strong convexity]\label{def:necoara-scnvx}
+                Suppose $f$ satisfies Assumption \ref{ass:necoara-2019-settings}. 
+                Then $f \in \mathbb S(L_f, \kappa_f, X)$ is strongly convex iff 
+                \begin{align*}
+                    (\forall x, y\in X)\; 
+                    \kappa_f \Vert x - y\Vert^2 \le 
+                    D_f(x, y) \le L_f \Vert x - y\Vert^2. 
+                \end{align*}
+            \end{definition}
+            Then it's not hard to imagine the following natural relaxation of the above conditions. 
+            % DEFINITION OF WEAKER STRONG CONVEXITY
+            \begin{definition}[Relaxations of Strong convexity]\label{def:necoara-weaker-scnvx}
+                Suppose $f$ satisfies Assumption \ref{ass:necoara-2019-settings}. 
+                Let $L_f \ge \kappa_f \ge 0$ such that for all $x \in X$, $\bar x = \Pi_{X^+} x$. 
+                We define the following: 
+                \begin{enumerate}
+                    \item\label{def:neocara-qscnvx} Quasi-strong convexity (Q-SCNVX): $0 \le D_f(\bar x, x) - \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. Denoeted by $\mathbb S'(L_f, \kappa_f, X)$. 
+                    \item\label{def:necoara-qup} Quadratic under approximation (QUA): $0 \le D_f(x, \bar x) - \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. Denoeted by $\mathbb U(L_f, \kappa_f, X)$. 
+                    \item\label{def:necoara-qgg} Quadratic Gradient Growth (QGG): $0\le D_f(x, \bar x) + D_f(\bar x, x) - \kappa_f/2\Vert x - \bar x\Vert^2$. Denoted by $\mathbb G(L_f, \kappa_f, X)$. 
+                    \item\label{def:necoara-qfg} Quadratic Function Growth (QFG): $0 \le f(x) - f^* - \kappa_f/2\Vert x - \bar x\Vert^2$. Denoted by $\mathbb F(L_f, \kappa_f, X)$. 
+                    \item\label{def:necoara-eb} Error Bound (EB): $\Vert \mathcal G_{L_f}x\Vert \ge \Vert x - \bar x\Vert$. Denoted by $\mathbb E(L_f, \kappa_f, X)$. 
+                \end{enumerate}
+            \end{definition}
+
+        \subsection{Major Results in the paper}
+            In Necoara's et al, major results assume convexity of $f$. 
+            \begin{theorem}(Q-SCNVX implies QUA)\label{thm:qscnvx-means-qua}
+                Let $f$ satisfies Assumption \ref{ass:necoara-2019-settings} and assume $f$ is convex: 
+                \begin{align*}
+                    \mathbb S'(L_f, \kappa_f, X) \subseteq \mathbb U(L_f, \kappa_f, X). 
+                \end{align*}
+            \end{theorem}
+            \begin{proof}
+                We proof by induction. 
+                Convexity of $f$ makes $X^+$ convex and $\Pi_{X^+}X$ unique for all $x \in X$. 
+                Make inductive hypothesis that there exists $\kappa^{(k)} \ge 0$ such that 
+                \begin{align*}
+                    (\forall x \in X)\quad
+                    f(x) \ge f^+ + \langle \nabla f(\Pi_{X^+}x), x - \Pi_{X^+}x\rangle 
+                    + \kappa^{(k)}/2\Vert x - \Pi_{X^+}x \Vert^2. 
+                \end{align*}
+                The base case is true by convexity of $f$ with $\kappa_f^{(0)} = 0$. 
+                Choose any $x \in X$ define $\bar x = \Pi_{X^+}x$. 
+                Consider $x_\tau = \bar x + \tau(x - \bar x)$ for $\tau \in [0, 1]$. 
+                Calculus rule has 
+                \begin{align*}
+                    f(x) &= 
+                    f(\bar x) + \int_0^1 \langle \nabla f(x_\tau), x - \bar x\rangle d\tau
+                    \\
+                    &= 
+                    f(\bar x) + \int_0^1 \tau^{-1}\langle \nabla f(x_\tau), \tau(x - \bar x)\rangle d\tau
+                    \\
+                    &= 
+                    f(\bar x) + \int_0^1 \tau^{-1}\langle \nabla f(x_\tau), x_\tau - \bar x\rangle d\tau.
+                \end{align*}
+                $f$ is Q-SCNVX so
+                \begin{align*}
+                    f^+ - f(x_\tau) &\ge \langle \nabla f(x_\tau), \Pi_{X^+}x_\tau - x_\tau\rangle + 
+                    \kappa_f/2 \Vert x_\tau - \Pi_{X^+}x_\tau\Vert^2
+                    \\
+                    &= 
+                    \langle \nabla f(x_\tau), \bar x - x_\tau\rangle + 
+                    \kappa_f/2 \Vert x_\tau - \bar x\Vert^2
+                    \\
+                    \iff 
+                    \langle \nabla f(x_\tau), x_\tau - \bar x\rangle
+                    &\ge f(x_\tau) - f^+ + \kappa_f/2\Vert x_\tau -\bar x\Vert^2. 
+                \end{align*}
+                We used $\Pi_{X^+}x_\tau = \bar x$ by convexity of $f$. 
+                Therefore:
+                {\footnotesize
+                \begin{align*}
+                    f(x) &\ge 
+                    f(\bar x) + 
+                    \int_0^1 \tau^{-1} \left(
+                        f(x_\tau) - f^+ + \frac{\kappa_f}{2}\Vert x_\tau - \bar x\Vert^2
+                    \right) d\tau
+                    \\
+                    &= 
+                    f(\bar x) + 
+                    \int_0^1 
+                    \tau^{-1} \left(
+                            f(x_\tau) - f^+ 
+                        \right)
+                        + \frac{\tau\kappa_f}{2}\Vert x - \bar x\Vert^2
+                    d\tau
+                    \\
+                    &\ge 
+                    f(\bar x) + 
+                    \int_0^1 
+                    \tau^{-1} \left(
+                            \langle 
+                                \nabla f(\Pi_{X^+}x_\tau), x_\tau - \Pi_{X^+}x_\tau
+                            \rangle
+                            + \frac{\kappa_f^{(k)}}{2} \Vert x_\tau - \Pi_{X^+}x_\tau\Vert^2
+                        \right)
+                        + \frac{\tau\kappa_f}{2}\Vert x - \Pi_{X^+}x_\tau\Vert^2
+                    d\tau
+                    \\
+                    &= 
+                    f(\bar x) + 
+                    \int_0^1 
+                    \tau^{-1} \left(
+                            \langle 
+                                \nabla f(\bar x), x_\tau - \bar x
+                            \rangle
+                            + \frac{\kappa_f^{(k)}}{2} \Vert x_\tau - \bar x\Vert^2
+                        \right)
+                        + \frac{\tau\kappa_f}{2}\Vert x - \bar x\Vert^2
+                    d\tau
+                    \\
+                    &= 
+                    f(\bar x) + 
+                    \int_0^1 
+                        \langle 
+                            \nabla f(\bar x), x - \bar x
+                        \rangle
+                        + \frac{\tau\kappa_f^{(k)}}{2} \Vert x - \bar x\Vert^2
+                        + \frac{\tau\kappa_f}{2}\Vert x - \bar x\Vert^2
+                    d\tau
+                    \\
+                    &= 
+                    f(\bar x) + 
+                    \langle 
+                        \nabla f(\bar x), x - \bar x
+                    \rangle
+                    +
+                    \frac{\kappa^{(k)}_f + \kappa_f}{4}
+                    \Vert x - \bar x\Vert^2. 
+                \end{align*}
+                }
+                This is the new inductive hypothesis, and it has $\kappa_f^{(k + 1)} = (\kappa_f^{(k)} + \kappa_f)/2$. 
+                The induction admits recurrence: 
+                \begin{align*}
+                    \kappa_f^{(n)} = (1/2^n)(\kappa_f^{(0)} + (2^n - 1)\kappa_f). 
+                \end{align*}
+                Inductive hypothesis is true for $\kappa_f^{(0)} = 0$ and $f$ being convex is sufficient. 
+                It has $\lim_{n\rightarrow \infty} \kappa_f^{(n)} = \kappa_f$. 
+            \end{proof}
+            \begin{remark}
+                This is Theorem 1 in the paper. 
+                Convexity assumption of $f$ makes $X^+$ convex, so the projection is unique, and it has $\Pi_{X^+}x_\tau = \bar x$ for all $\tau \in [0, 1]$. 
+                In addition, the inductive hypothesis has $\kappa_f^{(n)} \ge 0$, which is not sufficient for convexity, but necessary. 
+                The projectin property remains true for nonconvex $X^+$, however the base case require rethinking. 
+            \end{remark}
+            \begin{theorem}[Q-SCNVX implies QGG]
+                Under Assumption \ref{ass:necoara-2019-settings} and convexity of $f$, it has 
+                \begin{align*}
+                    \mathbb S'(L_f, \kappa_f, X) \subseteq \mathbb G(L_f, \kappa_f, X). 
+                \end{align*}
+            \end{theorem}
+            \begin{proof}
+                If $f \in \mathbb S'(L_f, \kappa_f, X)$ then Theorem \ref{thm:qscnvx-means-qua} has $f \in \mathbb U(L_f, \kappa_f, X)$. 
+                Then, add \ref{def:necoara-qup}, \ref{def:neocara-qscnvx} in Definition \ref{def:necoara-weaker-scnvx} yield the results. 
+            \end{proof}
+            \begin{remark}
+                This is Theorem 2 in the Necoara et al. \cite{necoara_linear_2019}, right after it claims $\mathbb U(L_f, \kappa_f, X)\subseteq \mathbb G(L_f, \kappa_f/2, X)$ under convexity. 
+            \end{remark}
+            \begin{theorem}[sufficiency of QFG]\label{thm:qfg-suff}
+
+            \end{theorem}
 
@@
 
-\bibliography{references/Books.bib}
+\bibliography{references/refs.bib}
 

### 2025-03-26 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
                     \item\label{def:necoara-qfg} Quadratic Function Growth (QFG): $0 \le f(x) - f^* - \kappa_f/2\Vert x - \bar x\Vert^2$. Denoted by $\mathbb F(L_f, \kappa_f, X)$. 
-                    \item\label{def:necoara-eb} Error Bound (EB): $\Vert \mathcal G_{L_f}x\Vert \ge \Vert x - \bar x\Vert$. Denoted by $\mathbb E(L_f, \kappa_f, X)$. 
+                    \item\label{def:necoara-eb} Error Bound (EB): $\Vert \mathcal G_{L_f}x\Vert \ge \kappa_f\Vert x - \bar x\Vert$. Denoted by $\mathbb E(L_f, \kappa_f, X)$. 
                 \end{enumerate}
             \end{definition}
+            \begin{remark}
+                The error bound condition in Necoara et al. is sometimes referred to as the "Proximal Error Bound". 
+            \end{remark}
 
@@
             \begin{theorem}[sufficiency of QFG]\label{thm:qfg-suff}
-
+                Let $f$ satisfies Assumption \ref{ass:necoara-2019-settings}. 
+                For all $0 < \beta < 1$, $x \in X$, let $x^+ = \Pi_{X}(x - L^{-1}_f \nabla f(x))$. 
+                If 
+                \begin{align*}
+                    \Vert x^+ - \Pi_{X^+}x^+\Vert \le \beta \Vert x - \Pi_{X^+}x \Vert, 
+                \end{align*}
+                then $f$ satisfies the QFG condition with $\kappa_f = L_f(1 - \beta)^2$. 
             \end{theorem}
+            \begin{proof}
+                The proof is direct. 
+                \begin{align}
+                    \Vert x - \Pi_{X^+}x\Vert 
+                    &\le \Vert x - \Pi_{X^+}x^+\Vert
+                    \\
+                    &\le \Vert x - x^+\Vert + \Vert x^+ - \Pi_{X^+}x^+\Vert
+                    \\
+                    &\le \Vert x - x^+\Vert + \beta \Vert x - \Pi_{X^+}x\Vert
+                    \\
+                    \iff 
+                    0 &\le \Vert x - x^+\Vert - (1 - \beta) \Vert x - \Pi_{X^+}x\Vert. 
+                \end{align}
+                $x^+$ has descent lemma hence we have 
+                \begin{align*}
+                    f^+ - f(X) \le f(x^+) - f(x) 
+                    \le - \frac{L_f}{2}\Vert x^+ - x\Vert^2 
+                    \le - \frac{L_f}{2}(1 - \beta)^2 \Vert x - \Pi_{X^+}\Vert^2. 
+                \end{align*}
+                Hence it gives the quadratic growth condition. 
+            \end{proof}
+            \begin{remark}
+                It's unclear where convexity is used. 
+                However, it' still assumed in Necoara et al paper. 
+            \end{remark}
+            A few more words are needed before the theorem for the Error bound conditions and the quadratic growth condition.
 

### 2025-03-27 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
 \chapter{The Basics of Optimization Theories}
+    Notations in this chapter are not shared and they are for this chapter only.
 
@@
             \end{remark}
-            A few more words are needed before the theorem for the Error bound conditions and the quadratic growth condition.
+            The following theorems are about the relation between EB and QFG.
 

### 2025-03-28 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes, a lot

@@
             The assumption follows give the same setting as Necoara et al. \cite{necoara_linear_2019}. 
-            % NECOARA ASSUMPTIONS 
+            % NECOARA's ASSUMPTIONS ====================================================================================
             \begin{assumption}\label{ass:necoara-2019-settings}
@@
             \end{assumption}
-            % BREGMAN DIV DEFINITION
+            % BREGMAN DIV DEFINITION ===================================================================================
             \begin{definition}[Bregman Divergence]
@@
             \end{align*}
-            % STRONG CONVEXITY DEFINITION
+            % STRONG CONVEXITY DEFINITION ==============================================================================
             \begin{definition}[Strong convexity]\label{def:necoara-scnvx}
@@
             Then it's not hard to imagine the following natural relaxation of the above conditions. 
-            % DEFINITION OF WEAKER STRONG CONVEXITY
+            % DEFINITION OF WEAKER STRONG CONVEXITY ====================================================================
             \begin{definition}[Relaxations of Strong convexity]\label{def:necoara-weaker-scnvx}
@@
                 \begin{enumerate}
-                    \item\label{def:neocara-qscnvx} Quasi-strong convexity (Q-SCNVX): $0 \le D_f(\bar x, x) - \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. Denoeted by $\mathbb S'(L_f, \kappa_f, X)$. 
-                    \item\label{def:necoara-qup} Quadratic under approximation (QUA): $0 \le D_f(x, \bar x) - \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. Denoeted by $\mathbb U(L_f, \kappa_f, X)$. 
-                    \item\label{def:necoara-qgg} Quadratic Gradient Growth (QGG): $0\le D_f(x, \bar x) + D_f(\bar x, x) - \kappa_f/2\Vert x - \bar x\Vert^2$. Denoted by $\mathbb G(L_f, \kappa_f, X)$. 
-                    \item\label{def:necoara-qfg} Quadratic Function Growth (QFG): $0 \le f(x) - f^* - \kappa_f/2\Vert x - \bar x\Vert^2$. Denoted by $\mathbb F(L_f, \kappa_f, X)$. 
-                    \item\label{def:necoara-eb} Error Bound (EB): $\Vert \mathcal G_{L_f}x\Vert \ge \kappa_f\Vert x - \bar x\Vert$. Denoted by $\mathbb E(L_f, \kappa_f, X)$. 
+                    \item\label{def:neocara-qscnvx} Quasi-strong convexity (Q-SCNVX): $0 \le D_f(\bar x, x) - \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. 
+                    Denoeted by $\mathbb S'(L_f, \kappa_f, X)$. 
+                    \item\label{def:necoara-qup} Quadratic under approximation (QUA): $0 \le D_f(x, \bar x) - \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. 
+                    Denoeted by $\mathbb U(L_f, \kappa_f, X)$. 
+                    \item\label{def:necoara-qgg} Quadratic Gradient Growth (QGG): $0\le D_f(x, \bar x) + D_f(\bar x, x) - \kappa_f/2\Vert x - \bar x\Vert^2$. 
+                    Denoted by $\mathbb G(L_f, \kappa_f, X)$. 
+                    \item\label{def:necoara-qfg} Quadratic Function Growth (QFG): $0 \le f(x) - f^* - \kappa_f/2\Vert x - \bar x\Vert^2$. 
+                    Denoted by $\mathbb F(L_f, \kappa_f, X)$. 
+                    \item\label{def:necoara-peb} Proximal Error Bound (PEB): $\Vert \mathcal G_{L_f}x\Vert \ge \kappa_f\Vert x - \bar x\Vert$. 
+                    Denoted by $\mathbb E(L_f, \kappa_f, X)$. 
                 \end{enumerate}
@@
             In Necoara's et al, major results assume convexity of $f$. 
+            % THEOREM | Q-SCNVX IMPLIES QUA ============================================================================
             \begin{theorem}(Q-SCNVX implies QUA)\label{thm:qscnvx-means-qua}
@@
             \end{remark}
+            % THEOREM | QGG IMPLIES QUA ================================================================================
+            \begin{theorem}[QGG implies QUA]
+                Let $f$ satisfies Assumption \ref{ass:necoara-2019-settings}, under convexity it has 
+                \begin{align*}
+                    \mathbb G(L_f, \kappa_f, X)\subseteq \mathbb U(L_f, \kappa_f, X). 
+                \end{align*}
+            \end{theorem}
+            \begin{proof}
+                For all $x \in X$, define $\bar x = \Pi_{X^+}x$, $x_\tau = \bar x + \tau(x - \bar x)\; \forall \tau \in [0, 1]$. 
+                Observe that $\frac{d}{d\tau}x_\tau = x - \bar x$ and $\Pi_{X^+}x_\tau = \bar x\; \forall \tau \in [0, 1]$. 
+                Using calculus and Theorem \ref{def:necoara-weaker-scnvx} \ref{def:necoara-qgg}: 
+                \begin{align*}
+                    f(x) &= f(\bar x) + \int_0^1 \langle \nabla f(x_\tau), x - \bar x\rangle d\tau  
+                    \\
+                    &= f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle + 
+                    \int_0^1 \langle \nabla f(x_\tau) - \nabla f(\bar x), x - \bar x\rangle d \tau
+                    \\
+                    &= 
+                    f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle + 
+                    \int_0^1 \tau^{-1}\langle \nabla f(x_\tau) - \nabla f(\bar x), \tau(x - \bar x)\rangle d \tau
+                    \\
+                    &= 
+                    f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle + 
+                    \int_0^1 \tau^{-1}\langle \nabla f(x_\tau) - \nabla f(\bar x), x_\tau - \bar x\rangle d \tau
+                    \\
+                    &\ge
+                    f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle + 
+                    \int_0^1 \tau^{-1}\kappa_f\Vert \tau(x - \bar x)\Vert^2 d \tau
+                    \\
+                    &= 
+                    f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle + 
+                    \int_0^1 \tau\kappa_f\Vert x - \bar x \Vert^2 d \tau
+                    \\
+                    &= 
+                    f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle + 
+                    \frac{\kappa}{2}\Vert x - \bar x\Vert^2. 
+                \end{align*}
+            \end{proof}
+            \begin{remark}
+                This is Theorem 3 in Neocara et al. \cite{necoara_linear_2019}. 
+                There is no immediaet use of convexity besides that the projection $\bar x = \Pi_{X^+}x$ is a singleton.
+            \end{remark}
+            % THEOREM | QFC IMPLIES QGG  ===============================================================================
             \begin{theorem}[Q-SCNVX implies QGG]
@@
             \end{remark}
+            % THEOREM | SUFFICIENCY OF QFG =============================================================================
             \begin{theorem}[sufficiency of QFG]\label{thm:qfg-suff}
@@
             \end{remark}
-            The following theorems are about the relation between EB and QFG.
+            The following theorems are about the relation between PEB and QFG. 
+            \begin{theorem}{equivalence between QFG and PEB}
+
+            \end{theorem}
 

### 2025-03-29 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, fixes

@@
 \chapter{The Basics of Optimization Theories}
-    Notations in this chapter are not shared and they are for this chapter only.
+    Notations in this chapter are not shared, and they are for this chapter only. 
+    % BREGMAN DIV DEFINITION ===================================================================================
+    \begin{definition}[Bregman Divergence]\label{def:bregman-div}
+        Let $f:\RR^n \rightarrow \overline \RR$ be a differentiable function. 
+        Define Bregman Divergence: 
+        \begin{align*}
+            D_f: \RR^n \times \dom \nabla f \rightarrow \overline \RR:= 
+            (x, y) \mapsto f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 
+        \end{align*}
+    \end{definition}
+    \begin{assumption}[smooth plus nonsmooth]\label{ass:smooth-add-nonsmooth}
+        Let $F = f+ g$ where $f:\RR^n \rightarrow \overline \RR$ is differentiable and there exists $q\in \RR$ such that $g - q/2\Vert \cdot\Vert^2$ is convex.
+    \end{assumption}
+    \begin{definition}[proximal gradient operator]
+        Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-add-nonsmooth}. 
+        Define the proximal gradient operator by: 
+        \begin{align*}
+            T_{\beta^{-1}, f, g}(x) &= \hprox_{\beta^{-1}g} \left(
+                x - \beta^{-1} \nabla f(x)
+            \right)
+            \\
+            &= \argmin_{z}\left\lbrace
+                g(z) + f(x) + \langle \nabla f(x), z - x\rangle
+                + \frac{L}{2}\Vert x - z\Vert^2
+            \right\rbrace. 
+        \end{align*}
+    \end{definition}
+    % =================================================
+    % WEAKLY CONVEX GENERIC PROXIMAL GRADIENT INEQUALITY
+    % ==================================================
+    \begin{theorem}[weakly convex generic proximal gradient inequality]\label{thm:pg-ineq-wcnvx-generic}\;\\
+        Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-add-nonsmooth} with $\beta > 0$ and $q \in \RR$. 
+        Then for all $x \in \RR^n, z \in \RR^n$, define $\bar x = T_{\beta^{-1}, f, g}(x)$, it has: 
+        \begin{align*}
+            \frac{q}{2}\Vert z - x^+\Vert^2 
+            &\le 
+            F(z) - F(\bar x) - \langle \beta(x - \bar x), z - \bar x\rangle 
+            + D_f(x, \bar x ) - D_f(z, x).  
+        \end{align*}
+    \end{theorem}
+    \begin{proof}
+        Nonsmooth analysis calculus rules has 
+        \begin{align*}
+            \bar x &\in \argmin{z} \left\lbrace
+                g(z) + \langle \nabla f(x), z\rangle + \frac{\beta}{2}\Vert z - x\Vert^2
+            \right\rbrace
+            \\
+            \implies
+            \mathbf 0 
+            &\in \partial g(x^+) + \nabla f(x) + \beta(x^+ - x)
+            \\
+            \iff 
+            \partial g(x^+) &\ni
+            - \nabla f(x) - \beta(x^+ - x). 
+        \end{align*}
+        The subgradient inequality for weak convexity has 
+        \begin{align*}
+            \frac{q}{2}\Vert z - \bar x\Vert^2 
+            &\le 
+            g(z) - g(\bar x) + \langle \nabla f(x) + \beta(\bar x - x), z - \bar x\rangle
+            \\
+            &= 
+            g(z) - g(\bar x) + \langle \nabla f(x), z - \bar x\rangle + \langle \beta(\bar x - x), z - \bar x\rangle
+            \\
+            &= g(z) - g(\bar x) + \langle \nabla f(x), z - x\rangle
+            + \langle \nabla f(x), x - \bar x\rangle
+            + \langle \beta(\bar x - x), z - \bar x\rangle
+            \\
+            &= 
+            g(z) - g(\bar x) 
+            + (-D_f(z, x) + f(z) - f(x))
+            \\
+            & \quad 
+            + (D_f(\bar x, x) - f(\bar x) + f(x))
+            + \langle \beta(\bar x - x), z - \bar x\rangle
+            \\
+            &= F(z) - F(\bar x) - D_f(z, x) + D_f(\bar x, x) 
+            - \langle \beta(x - \bar x), z - \bar x\rangle. 
+        \end{align*}
+    \end{proof}
+    \begin{theorem}[convex proximal gradient inequality]\label{theorem:pg-ineq}
+        Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-add-nonsmooth} such that $q = \mu_g \ge 0$, $\beta \ge L_f$. 
+        In addition, suppose that $f:\RR^n\rightarrow \RR$ has $L_f$ Lipschitz continuous gradient, and it's $\mu_f \ge 0$ strongly convex. 
+        For all $x \in \RR^n, z \in \RR^n$, define $\bar x = T_{\beta^{-1}, f, g}(x)$ it has 
+        \begin{align*}
+            0 &\le 
+            F(z) - F(\bar x) + 
+            \frac{\beta - \mu_f}{2}\Vert z - x\Vert^2
+            - \frac{\beta + \mu_g}{2}\Vert z - \bar x\Vert^2. 
+        \end{align*}
+    \end{theorem}
+    \begin{proof}
+        The Bregman Divergence of $f$ has inequality 
+        \begin{align*}
+            \left(\forall x \in \RR^n, y \in \RR^n\right)\; 
+            \frac{\mu_f}{2}\Vert x - y\Vert^2 \le D_f(x, y) \le \frac{L_f}{2}\Vert x - y\Vert^2. 
+        \end{align*}
+        Specializing Theorem \ref{thm:pg-ineq-wcnvx-generic}, let $x \in \RR^n$ and define $\bar x = T_{\beta^{-1}, f, g}(x)$ it has $\forall z \in \RR^n:$
+        \begin{align*}
+            \frac{\mu_g}{2}\Vert z - \bar x \Vert^2 
+            &\le 
+            F(z) - F(\bar x) 
+            - D_f(z, x) + D_f(\bar x, x) 
+            - \langle \beta(x - \bar x), z - \bar x\rangle
+            \\
+            &\le 
+            F(z) - F(\bar x) 
+            - \frac{\mu_f}{2}\Vert z - x\Vert^2 
+            + \frac{L_f}{2}\Vert x - \bar x\Vert^2
+            - \langle \beta(x - \bar x), z - x + x - \bar x\rangle
+            \\
+            &= 
+            F(z) - F(\bar x) 
+            - \frac{\mu_f}{2}\Vert z - x\Vert^2 
+            + \left(
+                \frac{L_f}{2} - \beta
+            \right)\Vert x - \bar x\Vert^2
+            - \langle \beta(x - \bar x), z - x\rangle
+            \\
+            &\le 
+            F(z) - F(\bar x) 
+            - \frac{\mu_f}{2}\Vert z - x\Vert^2 
+            - \frac{\beta}{2}\Vert x - \bar x\Vert^2
+            - \langle \beta(x - \bar x), z - x\rangle
+            \\
+            &= 
+            F(z) - F(\bar x) 
+            - \frac{\mu_f}{2}\Vert z - x\Vert^2 
+            - \frac{\beta}{2}
+            \left(
+                \Vert x - \bar x\Vert^2
+                + 2\langle x - \bar x, z - x\rangle
+            \right)
+            \\
+            &= 
+            F(z) - F(\bar x) 
+            + \frac{\beta - \mu_f}{2}\Vert z - x\Vert^2 
+            - \frac{\beta}{2}\Vert z - \bar x\Vert^2. 
+        \end{align*}
+    \end{proof}
 
@@
     In this chapter, we are specifically interested in characterizing linear convergence of well known first order optimization algorithms. 
+    In this section, $D_f$ will denote the Bregman Divergence as defined in Definition \ref{def:bregman-div}. 
     \section{Necoara's et al's Paper}
@@
             The assumption follows give the same setting as Necoara et al. \cite{necoara_linear_2019}. 
-            % NECOARA's ASSUMPTIONS ====================================================================================
+            % =======================
+            % NECOARA's ASSUMPTIONS 
+            % =======================
             \begin{assumption}\label{ass:necoara-2019-settings}
@@
             \end{assumption}
-            % BREGMAN DIV DEFINITION ===================================================================================
-            \begin{definition}[Bregman Divergence]
-                Let $f:\RR^n \rightarrow \overline \RR$ be a differentiable function. 
-                Define Bregman Divergence: 
-                \begin{align*}
-                    D_f: \RR^n \times \dom \nabla f \rightarrow \overline \RR:= 
-                    (x, y) \mapsto f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 
-                \end{align*}
-            \end{definition}
             Some immediate consequences of Assumption \ref{ass:necoara-2019-settings} now follows. 
@@
             \end{align*}
-            % STRONG CONVEXITY DEFINITION ==============================================================================
+            % ==============================
+            % STRONG CONVEXITY DEFINITION
+            % ==============================
             \begin{definition}[Strong convexity]\label{def:necoara-scnvx}
@@
                 This is Theorem 3 in Neocara et al. \cite{necoara_linear_2019}. 
-                There is no immediaet use of convexity besides that the projection $\bar x = \Pi_{X^+}x$ is a singleton.
+                There is no immediate use of convexity besides that the projection $\bar x = \Pi_{X^+}x$ is a singleton.
             \end{remark}
@@
                 \end{align*}
-                Hence it gives the quadratic growth condition. 
+                Hence, it gives the quadratic growth condition. 
             \end{proof}
@@
                 It's unclear where convexity is used. 
-                However, it' still assumed in Necoara et al paper. 
+                However, it' still assumed in Necoara et al. paper. 
             \end{remark}
+            Before we start, we will specialize Theorem \ref{theorem:pg-ineq} in our context because it will be used in later proofs. 
+            In Assumption \ref{ass:necoara-2019-settings}, it can be seemed as $F = f + g$ in Assumption \ref{ass:smooth-add-nonsmooth} with $g = \delta_{X}$. 
+            In this case $\mu_g = 0$ and assuming $f$ is convex we have only $\mu_f = 0$. 
+            Therefore the theorem specializes into the following inequality.
+
+            \par
             The following theorems are about the relation between PEB and QFG. 
-            \begin{theorem}{equivalence between QFG and PEB}
+            \begin{theorem}[equivalence between QFG and PEB]
 

### 2025-04-04 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
     It may accelerate the process of writing my thesis for my PhD degree. 
-    \todo{
-        This is just pseudo text. This is just pseudo text. 
-        This is just pseudo text. This is just pseudo text \cite{necoara_linear_2019}. 
-    }
     \todoinline{This paper is currently in draft mode. Check source to change options. }
@@
     Notations in this chapter are not shared, and they are for this chapter only. 
-    % BREGMAN DIV DEFINITION ===================================================================================
+    % ===================================================================================
+    % BREGMAN DIV DEFINITION 
+    % ===================================================================================
     \begin{definition}[Bregman Divergence]\label{def:bregman-div}
@@
             % ==============================
-            \begin{definition}[Strong convexity]\label{def:necoara-scnvx}
+            \begin{definition}[strong convexity]\label{def:necoara-scnvx}
                 Suppose $f$ satisfies Assumption \ref{ass:necoara-2019-settings}. 
@@
             Then it's not hard to imagine the following natural relaxation of the above conditions. 
-            % DEFINITION OF WEAKER STRONG CONVEXITY ====================================================================
-            \begin{definition}[Relaxations of Strong convexity]\label{def:necoara-weaker-scnvx}
+            %===================================================================
+            % DEFINITION OF WEAKER STRONG CONVEXITY 
+            % ==================================================================
+            \begin{definition}[relaxations of strong convexity]\;\\
                 Suppose $f$ satisfies Assumption \ref{ass:necoara-2019-settings}.
+                \label{def:necoara-weaker-scnvx}
                 Let $L_f \ge \kappa_f \ge 0$ such that for all $x \in X$, $\bar x = \Pi_{X^+} x$. 
@@
                     \item\label{def:neocara-qscnvx} Quasi-strong convexity (Q-SCNVX): $0 \le D_f(\bar x, x) - \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. 
-                    Denoeted by $\mathbb S'(L_f, \kappa_f, X)$. 
+                    Denoted by $\mathbb S'(L_f, \kappa_f, X)$. 
                     \item\label{def:necoara-qup} Quadratic under approximation (QUA): $0 \le D_f(x, \bar x) - \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. 
-                    Denoeted by $\mathbb U(L_f, \kappa_f, X)$. 
+                    Denoted by $\mathbb U(L_f, \kappa_f, X)$. 
                     \item\label{def:necoara-qgg} Quadratic Gradient Growth (QGG): $0\le D_f(x, \bar x) + D_f(\bar x, x) - \kappa_f/2\Vert x - \bar x\Vert^2$. 
@@
 
-        \subsection{Major Results in the paper}
+        \subsection{Weaker conditions of strong convexity}
             In Necoara's et al, major results assume convexity of $f$. 
-            % THEOREM | Q-SCNVX IMPLIES QUA ============================================================================
-            \begin{theorem}(Q-SCNVX implies QUA)\label{thm:qscnvx-means-qua}
+            % ============================================================================
+            % THEOREM | Q-SCNVX IMPLIES QUA 
+            % ============================================================================
+            \begin{theorem}[Q-SCNVX implies QUA]\label{thm:qscnvx-means-qua}
                 Let $f$ satisfies Assumption \ref{ass:necoara-2019-settings} and assume $f$ is convex: 
@@
                 In addition, the inductive hypothesis has $\kappa_f^{(n)} \ge 0$, which is not sufficient for convexity, but necessary. 
-                The projectin property remains true for nonconvex $X^+$, however the base case require rethinking. 
+                The projection property remains true for nonconvex $X^+$, however the base case require rethinking. 
             \end{remark}
-            % THEOREM | QGG IMPLIES QUA ================================================================================
+            % ================================================================================
+            % THEOREM | QGG IMPLIES QUA 
+            % ================================================================================
             \begin{theorem}[QGG implies QUA]
@@
             \end{remark}
-            % THEOREM | QFC IMPLIES QGG  ===============================================================================
+            % ===============================================================================
+            % THEOREM | QFC IMPLIES QGG  
+            % ===============================================================================
             \begin{theorem}[Q-SCNVX implies QGG]
@@
             \end{remark}
-            % THEOREM | SUFFICIENCY OF QFG =============================================================================
+            % =============================================================================
+            % THEOREM | SUFFICIENCY OF QFG 
+            % =============================================================================
             \begin{theorem}[sufficiency of QFG]\label{thm:qfg-suff}
@@
             \end{remark}
-            Before we start, we will specialize Theorem \ref{theorem:pg-ineq} in our context because it will be used in later proofs. 
-            In Assumption \ref{ass:necoara-2019-settings}, it can be seemed as $F = f + g$ in Assumption \ref{ass:smooth-add-nonsmooth} with $g = \delta_{X}$. 
-            In this case $\mu_g = 0$ and assuming $f$ is convex we have only $\mu_f = 0$. 
-            Therefore the theorem specializes into the following inequality.
-
+            Before we start, we will specialize Theorem \ref{theorem:pg-ineq} because it will be used in later proofs. 
+            In Assumption \ref{ass:necoara-2019-settings}, it can be seemed as taking $F = f + g$ in Assumption \ref{ass:smooth-add-nonsmooth} with $g = \delta_{X}$. 
+            This makes $\mu_g = 0$ and assuming $f$ is convex we have $\mu_f = 0$. 
+            Let $\beta = L_f$, and $x^+ = \Pi_{X}(x - L_f^{-1}\nabla f(x))$, it has for all $z \in X$: 
+            \begin{align}\label{ineq:proj-grad}
+                \begin{split}
+                    0 &\le 
+                    f(z) - f(x^+) + \frac{L_f}{2}\Vert z - x\Vert^2
+                    - \frac{L_f}{2}\Vert z - x^+\Vert^2
+                    \\
+                    &= 
+                    f(z) - f(x^+) + L_f\langle z - x^+, x^+ - x\rangle
+                    + \frac{L_f}{2}\Vert x - x^+\Vert^2. 
+                \end{split}
+            \end{align}
+            Take note that when $z = x$ it has 
+            \begin{align}\label{ineq:proj-grad2}
+                0 &\le f(x) - f(x^+) - \frac{L_f}{2}\Vert x - x^+\Vert^2. 
+            \end{align}
             \par
             The following theorems are about the relation between PEB and QFG.
+            % ==========================================
+            % THEOREM | EQUIVALENCE BETWEEN QFG AND PEB 
+            % ==========================================
             \begin{theorem}[equivalence between QFG and PEB]
+                If $f$ is convex and satisfies Assumption \ref{ass:necoara-2019-settings}. 
+                Then we have: 
+                \begin{align*}
+                    \mathbb E(L_f, \kappa_f, X) &\subseteq \mathbb F(L_f, \kappa^2/L_f, X), 
+                    \\
+                    \mathbb F(L_f, \kappa_f) 
+                    &\subseteq 
+                    \mathbb E\left(
+                        L_f,
+                        \frac{\kappa_f}{\kappa_f/L_f + 1 + \sqrt{\kappa_k/L_f + 1}}, 
+                        X
+                    \right). 
+                \end{align*}
+            \end{theorem}
+            \begin{proof}
+                \textbf{Firstly, we show that PEB implies QFG.}
+                For any $x \in X$, define the gradient projection steps by $x^+ = \Pi_{X}(x - L^{-1}_f\nabla f(x))$. 
+                Denote $\bar x^+_\Pi = \Pi_{X^+}x^+$. 
+                Using \eqref{ineq:proj-grad} with $z = \bar x^+_\Pi$ it yields: 
+                {\small
+                \begin{align*}
+                    0 &\ge 
+                    f(x^+) - f(x^+_\Pi) - L_f\langle x_\Pi^+ - x^+, x^+ - x\rangle
+                    - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert^2
+                    \\
+                    \quad&\ge 
+                    \frac{\kappa_f}{2}\Vert x^+ - x_\Pi^+\Vert^2
+                    - \Vert L_f(x - x^+)\Vert\Vert x^+_\Pi - x^+\Vert
+                    - \frac{1}{2L_f}\Vert L_f(x - x^+)\Vert^2   &\text{QFG, Cauchy}
+                    \\
+                    &= \frac{\kappa_f}{2}\Vert x^+ - x_\Pi^+\Vert^2
+                    - \frac{1}{2L_f}\left(
+                        \Vert L_f(x - x^+)\Vert^2
+                        + L_f\Vert L_f(x - x^+)\Vert\Vert x_\Pi^+ - x^+\Vert
+                    \right)
+                    \\
+                    &= 
+                    \frac{\kappa_f + L_f}{2}\Vert x^+ - x^+_\Pi\Vert^2
+                    - \frac{1}{2L_f}\left(
+                        \Vert L_f(x - x^+)\Vert + L_f\Vert x - x_\Pi^+\Vert
+                    \right)^2
+                \end{align*}
+                }
+                From the last line, by positivity of norm it has
+                \begin{align*}
+                    \Vert L_f(x - x^+)\Vert + L_f\Vert x^+ - x_\Pi^+\Vert
+                    &\ge \sqrt{L_f(\kappa_f + L_f)}\Vert x^+ - x^+_\Pi\Vert
+                    \\
+                    \iff 
+                    \Vert L_f(x - x^+)\Vert
+                    &\ge 
+                    \left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right)\Vert x^+ - x^+_\Pi\Vert. 
+                \end{align*}
+                Using property of projection onto $X$ we have 
+                \begin{align*}
+                    \Vert x - \bar x\Vert &\le \Vert x - x_\Pi^+\Vert
+                    \le \Vert x - x^+\Vert + \Vert x^+ - x^+_\Pi\Vert
+                    \\
+                    &= \frac{1}{L_f}\Vert L_f(x - x^+)\Vert + \Vert x^+ - x^+_\Pi\Vert
+                    \\
+                    \iff 
+                    \Vert x - \bar x\Vert - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert
+                    &\le 
+                    \Vert x^+ - x^+_\Pi\Vert. 
+                \end{align*}
+                Combining the two above inequalities gives 
+                {\small
+                \begin{align*}
+                    0 &\le 
+                    \Vert L_f(x - x^+)\Vert
+                    -
+                    \left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right)\left(
+                        \Vert x - \bar x\Vert - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert
+                    \right)
+                    \\
+                    &=
+                    - \left(
+                        \sqrt{L_f(\kappa_f + L_f)} - L_f
+                    \right)\Vert x - \bar x\Vert
+                    +
+                    \left(
+                        L^{-1}_f\left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right) + 1
+                    \right)\Vert L_f(x - x^+)\Vert
+                    \\
+                    &= 
+                    -\left(
+                        \sqrt{L_f(\kappa_f + L_f)} - L_f
+                    \right)\Vert x - \bar x\Vert
+                    +
+                    \sqrt{L_f(\kappa_f + L_f)}
+                    \Vert L_f(x - x^+)\Vert
+                    \\
+                    \iff&
+                    \frac{\sqrt{L_f(\kappa_f + L_f)} - L_f}{\sqrt{L_f(\kappa_f + L_f)}}
+                    \Vert x - \bar x\Vert 
+                    \le
+                    \Vert \mathcal G_{L_f}x\Vert. 
+                \end{align*}
+                }
+                Skipping algebra, the fraction simplifies to 
+                \begin{align*}
+                    \frac{\kappa_f}{\kappa_f/L_f + 1 + \sqrt{\kappa_k/L_f + 1}}. 
+                \end{align*}
+                This gives PEB condition. 
+                \textbf{We now show QFG implies PEB}. 
+                From the error bound condition using $\kappa_f$ it has
+                \begin{align*}
+                    \kappa_f^2\Vert x - \bar x\Vert^2
+                    \le \Vert \mathcal G_{L_f}(x)\Vert^2
+                    \underset{\eqref{ineq:proj-grad2}}{\le }
+                    2L_f(f(x) - f(x^+)) \le 2L_f(f(x) - f^+). 
+                \end{align*}
+            \end{proof}
+            \par
+            The following theorem summarizes the hierarchy of the conditions listed in Definition \ref{def:necoara-weaker-scnvx}. 
+            \begin{theorem}[Hierarchy of weaker S-CNVX conditions]\label{thm:weaker-scnvx-hierarchy}
+                Let $f$ satisfy Assumption \ref{ass:necoara-2019-settings}, assuming convexity then the following relations are true: 
+                \begin{align*}
+                    \mathbb S(\kappa_f, L_f, X) 
+                    \subseteq \mathbb S'(\kappa_f, L_f, X)
+                    \subseteq \mathbb G(\kappa_f, L_f, X) 
+                    \subseteq \mathbb U(\kappa_f, L_f, X) 
+                    \subseteq \mathbb F(\kappa_f, L_f, X). 
+                \end{align*}
+            \end{theorem}
+            \begin{proof}
 
-            \end{theorem}
+            \end{proof}
+            \begin{remark}
+                It's Theorem 4 in Necoara et al. \cite{necoara_linear_2019}.
+            \end{remark}
+        \subsection{Hoffman error bound and Q-SCNVX}
+
+        \subsection{Feasible descent and accelerated feasible descent}
+
+        \subsection{Application, KKT of linear programming}
 

### 2025-04-06 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, new notes

@@
         \subsection{Application, KKT of linear programming}
+            Let $X_1, X_2, Y$ be Hilbert spaces. 
+            Define linear mapping $E:X_1 \times X_2 \rightarrow Y := (x_1, x_2)\mapsto E_1 x_1 + E_2 x_2$ where $E_1, E_2$ each are mappings of $X_1 \rightarrow Y, X_2 \rightarrow Y$. 
+            Denote the adjoint of linear mapping by $(\cdot)^*$. 
+            Let $c = (c_1, c_2) \in X_1 \times X_2$, $b \in Y$. 
+            Suppose that $\mathcal K \subseteq X_1$ is a simple cone and $K^*$ is its dual cone. 
+            We consider the following linear programming problem 
+            \begin{align}\label{eqn:lp-cannon-form}
+                \inf_{x \in X_1\times X_2}\left\lbrace
+                    \langle - c, x\rangle
+                    \left| \;
+                        Ex = b, x \in \mathcal K \times X_2
+                    \right.
+                \right\rbrace. 
+            \end{align}
+            Define linear mapping $g, F$ and indicator function $h$ by the following: 
+            \begin{align*}
+                g:X_1\times X_2 \rightarrow \RR 
+                    &:= x \mapsto \langle - c, x\rangle, 
+                \\
+                F: X_1\times X_2 \rightarrow Y \times X_1 
+                    &:= (x_1, x_2) \mapsto (E_1x_1 + E_2 x_2, x_1),
+                \\
+                h: Y \times X_1 \rightarrow \overline \RR &:= 
+                    (y, z) \mapsto \delta_{\{\mathbf 0\}}(y - b) + \delta_{\mathcal K^*}(z). 
+            \end{align*}
+            It's not hard to identify that problem in \eqref{eqn:lp-cannon-form} has representations 
+            \begin{align*}
+                \inf_{x \in X_1\times X_2}
+                \left\lbrace
+                    g(x) + h(Fx)
+                \right\rbrace. 
+            \end{align*}
+            The dual problem of the above is given by
+            \begin{align*}
+                -\inf_{u \in Y\times X_1}
+                \left\lbrace
+                    h^\star(u) + g^\star(-F^* u)
+                \right\rbrace. 
+            \end{align*}
+            Where $h^\star, g^\star$ are the conjugate of $h, g$ and $F^*: Y\times X_1 \rightarrow X_1 \times X_2 = (y, z)\mapsto (E_1^*y + z, E_2^*y)$ is the adjoint operator of $F$. 
+            Note that $g^\star(x) = \delta_{\mathbf 0}(x + c)$ and $h^\star((y, z)) = \langle b, y\rangle + \delta_{\mathcal K^*}(z)$. 
+            This gives the following dual problem 
+            \begin{align*}
+                - \inf_{(y, z) \in Y \times \mathcal K^*} \left\lbrace
+                    \langle b, y\rangle 
+                    \left | \;
+                        E_1^*y + z = c_1, 
+                        E^*_2y = c_2
+                    \right.
+                \right\rbrace. 
+            \end{align*}
+            The KKT conditions give the following convex feasibility problem 
+            \begin{align*}
+                E_1 x_1 + E_2 x_2 &= b, \\
+                E_1^* y + z &= c_1, \\
+                E_2^* y &= c_2, \\
+                \langle b, y\rangle &= \langle c_1, x_1\rangle + \langle c_2, x_2\rangle, \\
+                (x_1, x_2) &\in \mathcal K \times X_2, \\
+                (y, z) &\in Y \times \mathcal K^*.
+            \end{align*}
+            Allow $X_1 = \RR^{n_1}, X_2 = \RR^{n_2}, Y = \RR^m$. 
+            Define 
+            \begin{align*}
+                \mathbf K &:= \mathcal K \times \RR^{n_2} \times \RR^m \times \mathcal K^*, 
+                \\
+                A &:= \begin{bmatrix}
+                    E_1 & E_2 & \mathbf 0 & \mathbf 0
+                    \\
+                    \mathbf 0 &\mathbf 0  & E_1^T & I_{n_1}
+                    \\
+                    \mathbf 0 &\mathbf 0  & E_2^T & \mathbf 0
+                    \\
+                    c_1^T & c_2^T & - b^T & 0
+                \end{bmatrix}, 
+                v := 
+                \begin{bmatrix}
+                    x_1\\ x_2 \\ y \\ z \\
+                \end{bmatrix} \in \mathbf K, 
+                d := 
+                \begin{bmatrix}
+                    b \\ c_1 \\ c_2 \\ 0
+                \end{bmatrix}. 
+            \end{align*}
+            The KKT conditions is a convex feasibility problem which can be formulated by best approxmation problem: 
+            \begin{align}\label{eqn:lp-kkt-min}
+                \min_{v \in \mathbf K} 
+                \frac{1}{2}\Vert Ax - d \Vert^2. 
+            \end{align}
+            Which is minimizing a quadratic problem on a simple cone. 
+            Solving \eqref{eqn:lp-cannon-form} can be approached by optimizing \eqref{eqn:lp-kkt-min}. 
+            It's necessary to investigate the matrices $A, A^T$ which are essential to solving it numerically. 
+            The properties of $A^TA$ will determine the convergence rate of algorithms. 
+            The matrix is a block matrix and possibly spase in practice. 
+            Let $v = (x_1, x_2, y, z)$, it admits implicit representation: 
+            \begin{align*}
+                Av = (E_1x_1 + E_2 x_2,\; E_1^Ty + z,\; E_2^Ty,\; c^T_1x_1 + c_2^Tx_2 - b^Ty). 
+            \end{align*}
+            It involves 
+            \begin{enumerate}
+                \item Two multiplications of $E$: $x_1, x_2$ on the right and $y$ on the right. 
+                \item inner involving of $x_1, x_2$ and $y$. 
+            \end{enumerate}
+
+            Let $\bar v = (\bar y, \bar x_1, \bar x_2, \xi) \in \RR^m\times \RR^{n_1} \times \RR^{n_2}\times \RR$ then the right mulplication of has: 
+            \begin{align*}
+                \bar v^TA  &= (
+                    E_1^T\bar y + \xi c_1^T,\; E_2^T\bar y + \xi c_2^T,\; 
+                    \bar x_1^TE_1^T + \bar x_2^TE_2^T - \xi b^T,\; \bar x_1^T
+                )
+                \\
+                &= 
+                (
+                    E_1^T\bar y + \xi c_1, \;
+                    E_2^T \bar y + \xi c_2, \;
+                    E_1\bar x_1 + E_2\bar x_2 - \xi b, \;
+                    \bar x_1
+                )^T. 
+            \end{align*}
+            \begin{enumerate}
+                \item Two multplications of the matrix $E$: $\bar y$ on the left and for $\bar x$ on the right, 
+                \item one vector addition with $c = (c_1, c_2)$ and $b$. 
+            \end{enumerate}
+            Therefore, computing $A^TAv$ has four vector multiplications using $E$. 
+            \par
+            Another key operation would be $A^TAv$. 
+            Let $\bar v = Av$, then 
+            \begin{align*}
+                A^TAv &= 
+                \begin{bmatrix}
+                    E^T_1(E_1x_1 + E_2x_2) + (c_1^Tx_1 + c_2^Tx_2 - b^Ty)c_1
+                    \\
+                    E^T_2(E_1x_1 + E_2x_2) + (c_1^Tx_1 + c_2^Tx_2 - b^Ty)c_2
+                    \\
+                    E_1(E_1^Ty + z) + E_2E_2^Ty - (c_1^Tx_1 + c_2^Tx_2 - b^Ty)b
+                    \\
+                    E_1^Ty + z
+                \end{bmatrix}
+                \\
+                &= 
+                \begin{bmatrix}
+                    (E_1^TE_1 + c_1^T)x_1 + (E_1^TE_2 + c_2^T)x_2 - (c_1b^T)y
+                    \\
+                    (E_2^TE_1 + c_1^T)x_1 + (E_2^TE_2 + c_2^T)x_2 - (c_2b^T)y
+                    \\
+                    -(bc_1^T)x_1 - (bc_2^T)x_2 + (E_2E_2^T + E_1E_1^T + bb^T)y
+                    + (E_1E_1^T)z
+                    \\
+                    E_1^Ty + z
+                \end{bmatrix}. 
+            \end{align*}
+            In practice, implicitly repressenting the process of $A^TAv$ is better in computing software. 
+            Here we write it out to view, for theoretical interests.
 

### 2025-04-07 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, good changes

@@
             The variational inequality characterizing optimal solution has: 
-            \begin{align*}
+            \begin{align}\label{ineq:pg-opt-cond}
                 x^+ \in X^+ \implies 
                 (\forall x \in X)\; \langle \nabla f(x^+), x - x^+\rangle \ge 0. 
-            \end{align*}
+            \end{align}
             The converse is true if $f$ is convex. 
@@
             % ================================================================================
-            \begin{theorem}[QGG implies QUA]
+            \begin{theorem}[QGG implies QUA]\label{thm:qgg-implies-qua}
                 Let $f$ satisfies Assumption \ref{ass:necoara-2019-settings}, under convexity it has 
@@
             % ===============================================================================
-            \begin{theorem}[Q-SCNVX implies QGG]
+            \begin{theorem}[Q-SCNVX implies QGG]\label{thm:qscnvx-implies-qgg}
                 Under Assumption \ref{ass:necoara-2019-settings} and convexity of $f$, it has 
@@
             % ==========================================
-            \begin{theorem}[equivalence between QFG and PEB]
+            \begin{theorem}[equivalence between QFG and PEB]\label{thm:qfg-peb-equiv}
                 If $f$ is convex and satisfies Assumption \ref{ass:necoara-2019-settings}. 
@@
             \begin{proof}
-
+                $\mathbb S' \subseteq \mathbb G$ is proved in Theorem \ref{thm:qscnvx-implies-qgg} and $\mathbb G \subseteq \mathbb U$ is proved in \ref{thm:qgg-implies-qua}. 
+                $\mathbb S\subseteq \mathbb S'$ is obvious and it remains to show $\mathbb U \subseteq \mathbb F$. 
+                Let $f\in \mathbb U(\kappa_f, L_f, X)$, it has for all $x \in X$: 
+                \begin{align*}
+                    0 &\le f(x) - f^+ - \langle \nabla f(\bar x), x - \bar x\rangle - \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2
+                    \\
+                    &\hspace{-0.5em}\underset{\eqref{ineq:pg-opt-cond}}{\le} 
+                    f(x) - f^+ - \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2. 
+                \end{align*}
             \end{proof}
@@
         \subsection{Feasible descent and accelerated feasible descent}
+            This section summarizes results from Necoara et al. on the method of feasible descent, fast feasible descent, and fast feasible descent with restart.
 
         \subsection{Application, KKT of linear programming}
+            This section extends and ideas in the discussion section of Necoara et al. \cite{necoara_linear_2019}. 
+            \par
             Let $X_1, X_2, Y$ be Hilbert spaces. 
@@
             We consider the following linear programming problem 
-            \begin{align}\label{eqn:lp-cannon-form}
+            \begin{align}\label{problem:lp-cannon-form}
                 \inf_{x \in X_1\times X_2}\left\lbrace
@@
             \end{align*}
-            It's not hard to identify that problem in \eqref{eqn:lp-cannon-form} has representations 
+            It's not hard to identify that problem in \eqref{problem:lp-cannon-form} has representations 
             \begin{align*}
@@
             The KKT conditions is a convex feasibility problem which can be formulated by best approxmation problem: 
-            \begin{align}\label{eqn:lp-kkt-min}
+            \begin{align}\label{problem:lp-kkt-min}
                 \min_{v \in \mathbf K} 
@@
             \end{align}
-            Which is minimizing a quadratic problem on a simple cone. 
-            Solving \eqref{eqn:lp-cannon-form} can be approached by optimizing \eqref{eqn:lp-kkt-min}. 
+            It is minimizing a quadratic problem on a simple cone. 
+            Solving \eqref{problem:lp-cannon-form} can be approached by optimizing \eqref{problem:lp-kkt-min}. 
             It's necessary to investigate the matrices $A, A^T$ which are essential to solving it numerically. 
@@
             \begin{enumerate}
-                \item Two multiplications of $E$: $x_1, x_2$ on the right and $y$ on the right. 
-                \item inner involving of $x_1, x_2$ and $y$. 
+                \item Two multiplications of $E$: $x_1, x_2$ on the right and $y$ on the right,  
+                \item inner product using $x_1, x_2$ and $y$. 
             \end{enumerate}
@@
             \begin{enumerate}
-                \item Two multplications of the matrix $E$: $\bar y$ on the left and for $\bar x$ on the right, 
+                \item Two multplications of $E$: $\bar y$ on the left and for $\bar x_1, \bar x_2$ on the right, 
                 \item one vector addition with $c = (c_1, c_2)$ and $b$. 
@@
             Therefore, computing $A^TAv$ has four vector multiplications using $E$. 
+            In practice, a sparse matrix $E$ from the model can speed up computations. 
             \par
@@
             Here we write it out to view, for theoretical interests. 
+            \par
+            Let $f(v) = (1/2)\Vert Av - d\Vert^2$ to be the objective function of optimization problem \eqref{problem:lp-kkt-min}. 
+            Its gradient, objective value are related and it they have: 
+            \begin{align*}
+                \nabla f(v) &= A^TAv - A^Td, 
+                \\
+                f(v) &= 
+                \frac{1}{2}\langle x, \nabla f(v) - A^Td\rangle + \frac{1}{2}\Vert d\Vert^2. 
+            \end{align*}
+            The value $\nabla f(v), f(v)$ when evaluated together, require minimal additional computations. 
+            This fact is favorable for implementations in practice.
 

### 2025-04-10 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, new changes

@@
             The properties of $A^TA$ will determine the convergence rate of algorithms. 
-            The matrix is a block matrix and possibly spase in practice. 
+            The matrix is a block matrix and possibly sparse in practice. 
             Let $v = (x_1, x_2, y, z)$, it admits implicit representation: 
@@
             \begin{enumerate}
-                \item Two multplications of $E$: $\bar y$ on the left and for $\bar x_1, \bar x_2$ on the right, 
+                \item Two multiplications of $E$: $\bar y$ on the left and for $\bar x_1, \bar x_2$ on the right, 
                 \item one vector addition with $c = (c_1, c_2)$ and $b$. 
@@
             \end{align*}
-            In practice, implicitly repressenting the process of $A^TAv$ is better in computing software. 
+            In practice, implicitly representing the process of $A^TAv$ is better in computing software. 
             Here we write it out to view, for theoretical interests. 
@@
             Let $f(v) = (1/2)\Vert Av - d\Vert^2$ to be the objective function of optimization problem \eqref{problem:lp-kkt-min}. 
-            Its gradient, objective value are related and it they have: 
+            Its gradient, objective value are related and if they have: 
             \begin{align*}

### 2025-04-15 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, prepping something
>w<, changes

@@
                 g(z) + f(x) + \langle \nabla f(x), z - x\rangle
-                + \frac{L}{2}\Vert x - z\Vert^2
+                + \frac{\beta}{2}\Vert x - z\Vert^2
             \right\rbrace. 
@@
             \end{align*}
-            The KKT conditions is a convex feasibility problem which can be formulated by best approxmation problem: 
+            The KKT conditions is a convex feasibility problem which can be formulated by best approximation problem: 
             \begin{align}\label{problem:lp-kkt-min}
@@
 
-            Let $\bar v = (\bar y, \bar x_1, \bar x_2, \xi) \in \RR^m\times \RR^{n_1} \times \RR^{n_2}\times \RR$ then the right mulplication of has: 
+            Let $\bar v = (\bar y, \bar x_1, \bar x_2, \xi) \in \RR^m\times \RR^{n_1} \times \RR^{n_2}\times \RR$ then the right multiplication of has: 
             \begin{align*}
@@
 
+\chapter{Restarting the Accelerated Proximal Gradient}
+    We review specifically on the idea of restarting Accelerated Proximal Gradient. 
+    There are a lot of contents on it in the literatures hence it will be condensed.
+
 % ==============================================================================

### 2025-04-21 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
     \end{proof}
-    \begin{theorem}[convex proximal gradient inequality]\label{theorem:pg-ineq}
+    \begin{theorem}[convex proximal gradient inequality]\label{thm:cnvx-pg-ineq}
         Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-add-nonsmooth} such that $q = \mu_g \ge 0$, $\beta \ge L_f$. 
@@
             \end{remark}
-            Before we start, we will specialize Theorem \ref{theorem:pg-ineq} because it will be used in later proofs. 
+            Before we start, we will specialize Theorem \ref{thm:cnvx-pg-ineq} because it will be used in later proofs. 
             In Assumption \ref{ass:necoara-2019-settings}, it can be seemed as taking $F = f + g$ in Assumption \ref{ass:smooth-add-nonsmooth} with $g = \delta_{X}$. 
@@
             The following theorem summarizes the hierarchy of the conditions listed in Definition \ref{def:necoara-weaker-scnvx}. 
-            \begin{theorem}[Hierarchy of weaker S-CNVX conditions]\label{thm:weaker-scnvx-hierarchy}
+            \begin{theorem}[Hierarchy of weaker S-CNVX conditions]\label{thm:q-cnvx-hierarchy}
                 Let $f$ satisfy Assumption \ref{ass:necoara-2019-settings}, assuming convexity then the following relations are true: 
@@
             This section summarizes results from Necoara et al. on the method of feasible descent, fast feasible descent, and fast feasible descent with restart. 
+            \begin{definition}[projected gradient algorithm]\label{def:projg-alg}\;\\
+                The projected gradient algorithm generates a sequence of iterates $(x_k)_{k \ge 0}$ such that they satisfy for all $k \ge 0$
+                \begin{align*}
+                    x_{k + 1} &= \Pi_X(x_k - \alpha_k \nabla f(x_k)), 
+                \end{align*}
+                Where $\alpha_k \ge L_f^{-1}$ for all $k \ge 1$. 
+            \end{definition}
+            Under Assumption \ref{ass:necoara-2019-settings}, convexity of $X$ means obtuse angle theorem from projection and it specializes to 
+            \begin{align}\label{ineq:projg-variational-ineq}
+                (\forall x \in X)\; \langle x_{k + 1} - (x_k + \alpha_k \nabla f(x_k)), x_{k + 1} - x\rangle \le 0. 
+            \end{align}
+
+            \begin{theorem}{feasible descent linear convergence under Q-SCNVX}
+                Under Assumption \ref{ass:necoara-2019-settings}, assume that $f$ is Q-CNVX with $\mu_f, L_f$, then the sequence that satisfies Definition \ref{def:projg-alg} has a linear convergence rate.
+                Let $\bar x_k = \Pi_{X^+}x_k, \bar x_0 = \Pi_{X^+} x_0$. 
+                For all $k \ge 1$, the iterates satisfy
+                \begin{align*}
+                    \Vert x_k - \bar x_k\Vert^2 &\le \left(
+                        \frac{1 - \kappa_f/L_f}{1 + \kappa_f/L_f}
+                    \right)^k \Vert x_0 - \bar x_0\Vert^2. 
+                \end{align*}
+            \end{theorem}
+            \begin{proof}
+                Our proof makes use of the following properties which we label it in advance for swift exposition: 
+                \begin{enumerate}
+                    \item Inequality \eqref{ineq:projg-variational-ineq}, from the projected gradient and convexity of $X$. 
+                    \item $f \in \mathbb S'$ which is the hypothesis that $f$ is Q-CNVX. 
+                    \item $\alpha_k \le L_f^{-1}$, the stepsize is sufficient to apply descent lemma globally. 
+                    \item $f \in \mathbb Q$ satisfying Q-Growth, a consequence of Q-CNVX by Theorem \ref{thm:q-cnvx-hierarchy}. 
+                \end{enumerate}
+                With $\overline{(\cdot)} = \Pi_{X^+}(\cdot)$ to denote the projection of a vector to the set of minimizers. 
+                The sequence of inequalities and equalities proves the theorem. 
+                {\allowdisplaybreaks
+                \begin{align*}
+                    \Vert x_{k + 1} - \bar x_k\Vert^2
+                    &= 
+                    \Vert x_{k + 1} - x_k + x_k - \bar x_k\Vert^2 
+                    = \Vert x_{k + 1} - x_k\Vert^2 + \Vert x_k - \bar x_k\Vert^2 + 2\langle x_{k + 1} - x_k, x_k - \bar x_k\rangle
+                    \\
+                    &= (- \Vert x_{k + 1} - x_k\Vert^2 + \Vert x_k - \bar x_k\Vert^2)
+                    + 2\Vert x_{k + 1} - x_k\Vert^2 + 2\langle x_{k + 1} - x_k, x_k - \bar x_k\rangle
+                    \\
+                    &= - \Vert x_{k + 1} - x_k\Vert^2 + \Vert x_k - \bar x_k\Vert^2
+                    + 2 \langle x_{k + 1} - x_{k}, x_{k + 1} - \bar x_k\rangle
+                    \\
+                    &= 
+                    - \Vert x_{k + 1} - x_k\Vert^2 + \Vert x_k - \bar x_k\Vert^2
+                    \\  & \quad \;
+                        + 2 \langle x_{k + 1} - x_{k} + \alpha_k \nabla f(x_k), x_{k + 1} - \bar x_k\rangle
+                        - 2\alpha_k \langle \nabla f(x_k), x_{k + 1} - \bar x_k\rangle
+                    \\
+                    &\underset{\text{(i)}}{\le}
+                    - \Vert x_{k + 1} - x_k\Vert^2 + \Vert x_k - \bar x_k\Vert^2
+                    - 2\alpha_k \langle \nabla f(x_k), x_{k + 1} - \bar x_k\rangle
+                    \\
+                    &= 
+                    - \Vert x_{k + 1} - x_k\Vert^2 + \Vert x_k - \bar x_k\Vert^2
+                    + 2\alpha_k \langle \nabla f(x_k), \bar x_k - x_k\rangle
+                    + 2\alpha_k \langle \nabla f(x_k), x_k - x_{k + 1}\rangle
+                    \\
+                    &\underset{\text{(ii)}}{\le}
+                    - \Vert x_{k + 1} - x_k\Vert^2 + \Vert x_k - \bar x_k\Vert^2
+                    \\ &\quad 
+                        + 2\alpha_k \left(
+                            f^+ - f(x_k) - \frac{\kappa_f}{2}\Vert x_k - \bar x_k\Vert^2
+                        \right)
+                        + 2\alpha_k \langle \nabla f(x_k), x_k - x_{k + 1}\rangle
+                    \\
+                    &= (1 - \alpha_k \kappa_f)\Vert x_k - \bar x_k\Vert^2
+                    \\&\quad 
+                        + 2\alpha_k(f^+ - f(x_k)) - 2\alpha_k 
+                        \left(
+                            \langle \nabla f(x_k), x_{k + 1} - x_k\rangle + \frac{1}{2\alpha_k}\Vert x_{k + 1} - x_k\Vert^2
+                        \right)
+                    \\
+                    &= 
+                    (1 - \alpha_k\kappa_f)\Vert x_k - \bar x_k\Vert^2 + 2 \alpha_k f^+
+                    \\&\quad 
+                        - 2 \alpha_k\left(
+                            f(x_k) + \langle \nabla f(x_k), x_{k + 1} - x_k\rangle 
+                            + \frac{1}{2\alpha_k}\Vert x_{k + 1} - x_k\Vert^2
+                        \right)
+                    \\
+                    &\underset{\text{(iii)}}{\le} 
+                    (1 - \alpha_k\kappa_f)\Vert x_k - \bar x_k\Vert^2 + 2 \alpha_k f^+
+                    \\ &\quad 
+                        - 2 \alpha_k\left(
+                            f(x_k) + \langle \nabla f(x_k), x_{k + 1} - x_k\rangle 
+                            + \frac{L_f}{2}\Vert x_{k + 1} - x_k\Vert^2
+                        \right)
+                    \\
+                    &\le 
+                    (1 - \alpha_k\kappa_f)\Vert x_k - \bar x_k\Vert^2 + 2 \alpha_k f^+
+                    - 2\alpha_kf(x_{k + 1})
+                    \\
+                    &\underset{\text{(iv)}}{\le} 
+                    (1 - \alpha_k \kappa_f)\Vert x_k - \bar x_k\Vert^2 - \alpha_k \kappa_k \Vert x_{k + 1} - \bar x_{k + 1}\Vert^2. 
+                \end{align*}
+                }
+                Therefore it has 
+                \begin{align*}
+                    0 &\le \Vert x_{k + 1} - \bar x_k\Vert^2 - \Vert x_{k + 1} - \bar x_{k + 1}\Vert^2
+                    \\
+                    &\le 
+                    (1 - \alpha_k \kappa_f)\Vert x_k - \bar x_k\Vert^2 
+                    - \alpha_k \kappa_k \Vert x_{k + 1} - \bar x_{k + 1}\Vert^2
+                    - \Vert x_{k + 1} - \bar x_{k + 1}\Vert^2
+                    \\
+                    &= (1 - \alpha_k \kappa_f)\Vert x_k - \bar x_k\Vert^2 
+                    - (1 + \alpha_k \kappa_k)\Vert x_{k + 1} - \bar x_{k + 1}\Vert^2. 
+                \end{align*}
+                Unrolling recursively, then use (iii), the claim is proved. 
+            \end{proof}
 
@@
             Let $f(v) = (1/2)\Vert Av - d\Vert^2$ to be the objective function of optimization problem \eqref{problem:lp-kkt-min}. 
-            Its gradient, objective value are related and if they have: 
+            Its gradient, objective value, and Bregman Divergence have: 
             \begin{align*}
@@
                 f(v) &= 
-                \frac{1}{2}\langle x, \nabla f(v) - A^Td\rangle + \frac{1}{2}\Vert d\Vert^2. 
+                \frac{1}{2}\langle x, \nabla f(v) - A^Td\rangle + \frac{1}{2}\Vert d\Vert^2, 
+                \\
+                D_f(x, y) &= \langle x - y, A^TA (x - y)\rangle. 
             \end{align*}
@@
 
-\chapter{Restarting the Accelerated Proximal Gradient}
-    We review specifically on the idea of restarting Accelerated Proximal Gradient. 
-    There are a lot of contents on it in the literatures hence it will be condensed.
+\chapter{Advanced Enhancement Techniques in Accelerated Proximal Gradient}
+    We review advanced enhancement techniques in Accelerated Proximal Gradient method. 
+    The review will be based on several papers. 
+    \par
+    There are several notable enhancements of the FISTA for function that are not strongly convex. 
+    Monotone variants of FISTA proposed by Beck \todo{[?]} and Nesterov \todo{[?]} imposes monotonicity in function value at the iterates.  
+    Backtracking strategies from Chambolle \todo{[?]} shows that the underestimating Lipschitz constant using a backtracking technique to choose a next iterate improves the average runtime of the algorithm in practice.
+    They showed that the convergence rate is bounded by the estimates of the Lipschitz constant. 
+    Restart is a technique pioneer early by ??? \todo{[?]}. 
+    Necoara et al. \cite{necoara_linear_2019} showed that there exists an optimal restarting interval to achieve fast line convergence rate for all functions with quadratic growth condition. 
+    \par
+    In this chapter, we will go through the details of these enhancements of FISTA and discuss why they are important in theories, and in practice. 
+    \section{FISTA made simple}
+        Most literatures overcomplicate the proofs and the matters regarding FISTA algorithm and its convergence rate. 
+        We showcase the theories using a generic similar triangle representations of the algorithm which tremendously simplifies the arguments. 
+        \begin{assumption}[the standard FISTA setting]\label{ass:standard-fista}
+            Let $F = f + g$ where $f:\RR^n\rightarrow \overline \RR$ is $L$ Lipschitz smooth, $g$ is convex. 
+            Suppose that $\argmin_{x \in \RR^n} F(x)\neq \emptyset$. 
+        \end{assumption}
+        Specializing Theorem \ref{thm:cnvx-pg-ineq}, we have the following lemma: 
+        \begin{lemma}[proximal gradient inequality]
+            If $F = f + g$ satisfies Assumption \ref{ass:standard-fista}, then for all $x \in \RR^n, z \in \RR^n$, define $\bar x = T_{L^{-1}, f, g}(x)$ it has 
+            \begin{align*}
+                0 &\le F(z) - F(\bar x) + \frac{L}{2}\Vert z - x\Vert - \frac{L}{2}\Vert z - \bar x\Vert^2. 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            Use Theorem \ref{thm:cnvx-pg-ineq}. 
+        \end{proof}
+        \begin{definition}[gradient mapping]
+            Suppose $F = f + g$ satisfies Assumption \ref{ass:standard-fista}, define the gradient mapping for all $x \in \RR^n$
+            \begin{align*}
+                \mathcal G_{\beta, f, g}(x) = \beta^{-1}(x - T_{\beta, f, g}(x)). 
+            \end{align*}
+        \end{definition}
+        If $f, g$ are clear in the context then we simply omit subscript and present $\mathcal G_\beta$. 
+        The following definition can capture monotone variants of FISTA with line search, including backtracking strategies. 
+        \begin{definition}[generic monotone proximal gradient with line search]
+
+        \end{definition}
 

### 2025-04-23 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
             \end{definition}
-            Under Assumption \ref{ass:necoara-2019-settings}, convexity of $X$ means obtuse angle theorem from projection and it specializes to 
+            Under Assumption \ref{ass:necoara-2019-settings}, convexity of $X$ means obtuse angle theorem from projection, and it specializes to 
             \begin{align}\label{ineq:projg-variational-ineq}
@@
                 }
-                Therefore it has 
+                Therefore, it has 
                 \begin{align*}
@@
                 h: Y \times X_1 \rightarrow \overline \RR &:= 
-                    (y, z) \mapsto \delta_{\{\mathbf 0\}}(y - b) + \delta_{\mathcal K^*}(z). 
+                    (y, z) \mapsto \delta_{\{\mathbf 0\}}(y - b) + \delta_{\mathcal K}(z). 
             \end{align*}
@@
             \begin{align*}
-                \mathcal G_{\beta, f, g}(x) = \beta^{-1}(x - T_{\beta, f, g}(x)). 
+                \mathcal G_{\beta^{-1}, f, g}(x) = \beta(x - T_{\beta^{-1}, f, g}(x)). 
             \end{align*}
@@
         The following definition can capture monotone variants of FISTA with line search, including backtracking strategies. 
-        \begin{definition}[generic monotone proximal gradient with line search]
-
+        \par
+        ``MAPG'' stands for monotone accelerated gradient. 
+        We refer to ``Generic Monotone Accelerated Proximal Gradient with line search" as ``GMAPG LS''. 
+        \begin{definition}[GMAPG LS]\label{def:generic-mapg-ls}\;\\ 
+            Initialize with $x_0, v_0, \alpha_0 = 1$. 
+            Initialize any $L_0$ such that
+            \begin{align*}
+                D_f(T_{L_0^{-1}} (y_0)) &\le \frac{L_0}{2}\Vert T_{L_0^{-1}}(x_0) - y_0\Vert^2. 
+            \end{align*}
+            Let $(\alpha_k)_{k \ge 0}$ be a sequence such that $\alpha_k \in (0, 1) \;\forall k \ge 0$ and $\alpha_0 \in (0, 1]$. 
+            \begin{tcolorbox}
+                The algorithm makes sequences $(x_k, v_k, y_k)_{k \ge 1}$, such that for all $k = 1, 2, \ldots$ they satisfy: 
+                \begin{align*}
+                    & y_k = \alpha_k v_{k - 1} + (1 - \alpha_k) x_{k - 1}, \\
+                    & \tilde x_k = T_{L_k^{-1}}(y_{k}), \\ 
+                    & v_k = x_{k - 1} + \alpha_k^{-1}(\tilde x_k - x_{k - 1}), \\
+                    & D_{f}(\tilde x_k, y_k) \le \frac{L_k}{2}\Vert \tilde x_k - y_k\Vert^2, \\
+                    & \text{Choose any } x_k: F(x_k) \le \min(F(\tilde x_k), F(x_{k - 1})). 
+                \end{align*}    
+            \end{tcolorbox}
         \end{definition}
+        \begin{lemma}[acceerated proximal gradient iterates relation]\;\label{lemma:apg-iterates}\;\\
+            The iterates $(x_k, v_k, y_k)_{k \ge 1}$ generated by Definition \ref{def:generic-mapg-ls}. 
+            Let $z_k = \alpha_k x^+ + (1 - \alpha_k)x_{k - 1}$. 
+            Then it has for all $k \ge 1$ that: 
+            \begin{align*}
+                z_k - \tilde x_k &= \alpha_k(x^+ - v_k)
+                \\
+                x_k - y_k &= \alpha_k(x^+ - v_{k - 1}). 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            It's direct from the algorithm. 
+            \begin{align*}
+                z_k - \tilde x_k &= (\alpha_k x^+ + (1 - \alpha_k)x_{k - 1}) - \tilde x_k
+                \\
+                &= \alpha_k (x^+ + \alpha_k^{-1}(1 - \alpha_k)x_{k - 1} - \alpha_k^{-1}\tilde x_k)
+                \\
+                &= \alpha_k(x^+ + \alpha_k^{-1}x_{k - 1} - x_{k - 1} - \alpha_k^{-1}\tilde x_k)
+                \\
+                &= \alpha_k(x^+ + \alpha_k^{-1}(x_{k - 1} - \tilde x_k) - x_{k - 1})
+                \\
+                &= \alpha_k(x^+ - v_{k}), 
+                \\
+                z_k - y_k &= 
+                (\alpha_k x^+ + (1 - \alpha_k)x_{k - 1}) - \left(
+                    \alpha_k v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+                \right)
+                \\
+                &= \alpha_k(x^+ + \alpha_k^{-1}(1 - \alpha_k)x_{k - 1} - v_{k - 1} - \alpha_k^{-1}(1 - \alpha_k)x_{k - 1})
+                \\
+                &= \alpha_k(x^+ - v_{k - 1}). 
+            \end{align*}
+        \end{proof}
+        \begin{theorem}[generic GMAPG LS convergence]\; \label{thm:gmapg-ls-convergence}\;\\
+            Let $F = f + g$ satisfy Assumptions \ref{ass:standard-fista}. 
+            Let $(\alpha_k)_{k \ge 0}$ be a sequence such that $\alpha_k \in (0, 1)$ for all $k \ge 1$ and $\alpha_0 \in (0, 1]$. 
+            Let $\rho_k = (1 - \alpha_{k + 1})^{-1}\alpha_{k + 1}^2 \alpha_k^{-2}$ for all $k \ge 0$. 
+            Then, for all $x^+ \in \RR^n, k \ge 1$, the convergence rate of GMAPG-LS (Definition \ref{def:generic-mapg-ls}) is given by: 
+            \begin{align*}
+                & \beta_k := \prod_{i = 0}^{k - 1} (1 - \alpha_{i + 1})
+                \max\left(1, \rho_i L_{i + 1}L_i^{-1}\right), 
+                \\
+                & F(x_k) - F(x^+) + \frac{L_k\alpha_k}{2}\Vert x^+ - v_k\Vert^2
+                \le 
+                \beta_k
+                \left(
+                    F(x_0) - F(x^+) + \frac{L_0\alpha_0}{2} \Vert x^+ - v_k\Vert^2
+                \right). 
+            \end{align*}
+            If in addition, the algorithm is initialized with $\alpha_0 = 1, x_0 = v_0 = T_{L_{0}}x_{-1} \in \text{dom}\; F$ and $x^+$ is a minimizer of $F$, then the convergence rate simplifies: 
+            \begin{align*}
+                F(x_k) - F(x^+) + \frac{L_k\alpha_k}{2}\Vert x^+ - v_k\Vert^2
+                & \le 
+                \left(
+                    \prod_{i = 0}^{k - 1} (1 - \alpha_{i + 1})
+                    \max\left(1, \rho_i L_{i + 1}L_i^{-1}\right)
+                \right)
+                \frac{L}{2}\Vert x^+ - x_{-1}\Vert^2. 
+            \end{align*}
+        \end{theorem}
+        \begin{proof}
+            Define $z_k = \alpha_k x^+ + (1 - \alpha_k)x_{k - 1}$ for all $k \ge 1$. 
+            In the proof follows, the follow facts will be used. 
+            We list them in advance and they will be labeled during the proof. 
+            \begin{enumerate}
+                \item Lemma \ref{lemma:apg-iterates}. 
+                \item The sequence $(\alpha_k)_{k \ge 1}$ has for all $k \ge 1$, $1 - \alpha_k = \alpha_k^2\alpha_{k - 1}^2\rho_{k - 1}$, $\alpha_k \in (0, 1)$. 
+                \item $F$ is convex and hence $F(z_k) \le \alpha_k F(x^+) + (1 - \alpha_k)F(x_{k - 1})$. 
+                \item $F(x_k) \le F(\tilde x_k)$ which is true by definition of GMAPG LS. 
+            \end{enumerate}
+            Now, using Theorem \ref{thm:cnvx-pg-ineq}, it has for all $N \in \N, k = 1, 2, \cdots, N$: 
+            {\allowdisplaybreaks
+            \begin{align*}
+                0 &\le 
+                F(z_k) 
+                - F(\tilde x_k) - \frac{L_k}{2}\Vert z_k - \tilde x_k\Vert^2 + 
+                \frac{L_k}{2}\Vert z_k - y_k\Vert^2
+                \\
+                &\underset{\text{(i)}}{=}
+                F(\alpha_k x^+ + (1 - \alpha_k)x_{k - 1}) - F(\tilde x_k)
+                - \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k \Vert^2 
+                + \frac{L_k\alpha_k^2}{2}\Vert(x^+ - v_{k - 1})\Vert^2
+                \\
+                &\underset{\text{(iii)}}{\le} 
+                \alpha_k F(x^+) + (1 - \alpha_k) F(x_{k - 1}) - F(\tilde x_k)
+                - \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k \Vert^2 
+                + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_{k - 1} \Vert^2
+                \\
+                &= 
+                (\alpha_k - 1)F(x^+) + (1 - \alpha_k) F(x_{k - 1}) + F(x^+) - F(\tilde x_k)
+                - \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k \Vert^2 
+                + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_{k - 1}\Vert^2
+                \\
+                &= 
+                (1 - \alpha_k)(F(x_{k - 1}) - F(x^+)) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k\Vert^2
+                - \left(
+                    F(\tilde x_k) - F(x^+) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k\Vert^2
+                \right)
+                \\
+                &\underset{\text{(iv)}}{\le} 
+                (1 - \alpha_k)(F(x_{k - 1}) - F(x^+)) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k\Vert^2
+                - \left(
+                    F(x_k) - F(x^+) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k\Vert^2
+                \right)
+                \\
+                &= 
+                (1 - \alpha_k)(F(x_{k - 1}) - F(x^+)) + 
+                \left(
+                    \frac{\alpha_k^2}{\alpha_{k - 1}^2\rho_{k - 1}}
+                \right)
+                \frac{L_{k - 1}\alpha_{k - 1}^2(\rho_{k - 1}L_kL_{k - 1}^{-1})}{2}\Vert x^+ - v_k\Vert^2 \\
+                    &\quad 
+                    - \left(
+                        F(x_k) - F(x^+) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k\Vert^2
+                    \right)
+                \\
+                &= 
+                \left(
+                    1 - \alpha_k
+                \right)\left(
+                    F(x_{k - 1}) - F(x^+) + \frac{L_{k - 1}\alpha_{k - 1}^2(\rho_{k - 1}L_kL_{k - 1}^{-1})}{2}
+                    \Vert x^+ - v_k\Vert^2
+                \right) \\
+                    & \quad 
+                    - \left(
+                        F(x_k) - F(x^+) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k\Vert^2
+                    \right)
+                \\
+                &\le 
+                \left(
+                    1 - \alpha_k
+                \right)\left(
+                    F(x_{k - 1}) - F(x^+) + \frac{L_{k - 1}\alpha_{k - 1}^2\max(1, \rho_{k - 1}L_kL_{k - 1}^{-1})}{2}
+                    \Vert x^+ - v_k\Vert^2
+                \right) \\
+                    & \quad 
+                    - \left(
+                        F(x_k) - F(x^+) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k\Vert^2
+                    \right)
+                \\
+                &\le 
+                \left(
+                    1 - \alpha_k
+                \right)\max(1, \rho_{k - 1}L_kL_{k - 1}^{-1})
+                \left(
+                    F(x_{k - 1}) - F(x^+) + \frac{L_{k - 1}\alpha_{k - 1}^2}{2}
+                    \Vert x^+ - v_k\Vert^2
+                \right) \\
+                    & \quad 
+                    - \left(
+                        F(x_k) - F(x^+) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k\Vert^2
+                    \right). 
+            \end{align*}
+            }
+            Unroll recursively for $k, k-1, \ldots, 0$, it implies: 
+            \begin{align*}
+                0
+                &\le 
+                \left(
+                    \prod^{k - 1}_{i = 0} (1 - \alpha_{i + 1})\max(1, \rho_{i}L_{i + 1}L^{-1}_i)
+                \right)\left(
+                    F(x_0) - F(x^+) + \frac{L_0 \alpha_0}{2}\Vert x^+ - v_0\Vert^2
+                \right) \\
+                    & \quad 
+                    - \left(
+                        F(x_k) - F(x^+) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k\Vert^2
+                    \right). 
+            \end{align*}
+            If in addition, we assume that $x^+$ is a minimizer of $F$, and $\alpha_0 = 1, x_0 = v_0 = T_{L_0}x_{-1}$. 
+            Using Theorem \ref{thm:cnvx-pg-ineq} it gives: 
+            \begin{align*}
+                0 &\le 
+                F(x^+) - F(T_{L_{-1}}x_{-1}) - \frac{L_0}{2}\Vert x^+ - T_{L_0}x_{-1}\Vert^2 + 
+                \frac{L_0}{2}\Vert x^+ - x_{-1}\Vert^2
+                \\
+                &= 
+                F(x^+) - F(x_0) - \frac{L_0}{2}\Vert x^+ - v_0\Vert^2 + 
+                \frac{L_0}{2}\Vert x^+ - x_{-1}\Vert^2. 
+            \end{align*}
+            Substituting it back to the previous inequality it yields the desired results. 
+        \end{proof}
+        We introduce two examples variants of line search method used to enhence the accelerated proximal gradient methods in the literatures to demonsrate Definition \ref{def:generic-mapg-ls} and Theorem \ref{thm:gmapg-ls-convergence}.
+        MFISTA by Beck is an example of Definition \ref{def:generic-mapg-ls}
+        \begin{example}[MFISTA with Armijo line search]\;\\\vspace{-1em}
+            \begin{algorithm}[H]\label{alg:mfista-ls}
+                \begin{algorithmic}[1]
+                    \STATE{\textbf{Input: }input things }
+                    \STATE{}
+                \end{algorithmic}
+                \caption{MFISTA with Armijo Line Search}
+            \end{algorithm}
+        \end{example}
 

### 2025-04-23 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
                 \\
-                D_f(x, y) &= \langle x - y, A^TA (x - y)\rangle. 
+                D_f(x, y) &= \langle x - y, A^TA (x - y)\rangle
+                \\
+                &= \langle \nabla f(x) - \nabla f(y), x - y\rangle. 
             \end{align*}
@@
         \begin{definition}[GMAPG LS]\label{def:generic-mapg-ls}\;\\ 
-            Initialize with $x_0, v_0, \alpha_0 = 1$. 
-            Initialize any $L_0$ such that
-            \begin{align*}
-                D_f(T_{L_0^{-1}} (y_0)) &\le \frac{L_0}{2}\Vert T_{L_0^{-1}}(x_0) - y_0\Vert^2. 
+            Initialize any $x_0, v_0 \in \RR^n, \alpha_0 = 1, L_0 \in \RR$ such that
+            \begin{align*}
+                D_f\left(T_{L_0^{-1}} (y_0)\right) 
+                &\le \frac{L_0}{2}\left\Vert T_{L_0^{-1}}(x_0) - y_0\right\Vert^2. 
             \end{align*}
@@
             \end{enumerate}
-            Now, using Theorem \ref{thm:cnvx-pg-ineq}, it has for all $N \in \N, k = 1, 2, \cdots, N$: 
-            {\allowdisplaybreaks
+            Now, using Theorem \ref{thm:cnvx-pg-ineq}, it has for all $k \in \N$: 
+            {\allowdisplaybreaks\small
             \begin{align*}
@@
         We introduce two examples variants of line search method used to enhence the accelerated proximal gradient methods in the literatures to demonsrate Definition \ref{def:generic-mapg-ls} and Theorem \ref{thm:gmapg-ls-convergence}.
-        MFISTA by Beck is an example of Definition \ref{def:generic-mapg-ls}
+        \par
+        MFISTA by Beck is an example of Definition \ref{def:generic-mapg-ls}. 
         \begin{example}[MFISTA with Armijo line search]\;\\\vspace{-1em}
-            \begin{algorithm}[H]\label{alg:mfista-ls}
+            \begin{algorithm}[H]
                 \begin{algorithmic}[1]
-                    \STATE{\textbf{Input: }input things }
-                    \STATE{}
+                    \STATE{\textbf{Input:} $x_0 \in \RR^n, L_0 \in \RR^n, f:\RR^n \rightarrow \RR, g: \mathbb \RR^n \rightarrow \overline \RR$} 
+                    \STATE{
+                        $y_0 := x_0, t_0 := 1$.
+                    }
+                    \FOR{$k = 0, 1, 2, \ldots$}
+                        \STATE{$\tilde x_{k + 1} = T_{L_k^{-1}}(y_k)$.}
+                        \IF{$D_f(\tilde x_{k + 1}, y_k) > L_k/2\Vert \tilde x_{k + 1} - y_k\Vert^2$}
+                            \STATE{\noindent
+                                $L_k := \argmin_{i = 1,2, \ldots} \left\{ i: 
+                                    D_f(T_{2^{-i}L_k^{-1}}(y_k), y_k) 
+                                    \le 2^{i-1}L_k\left\Vert 
+                                        T_{2^{-i}L^{-1}}y_k - y_k
+                                    \right\Vert^2
+                                \right\}$.
+                            }
+                            \STATE{$\tilde x_{k + 1} := T_{L_0^{-1}}y_k$.}
+                        \ENDIF
+                        \STATE{\noindent
+                            Choose $x_{k + 1} \in \{\tilde x_{k + 1}, x_k\}$ such that $F(x_{k + 1}) \le \min(F(x_k), F(\tilde x_{k + 1}))$. 
+                        }
+                        \STATE{\noindent
+                            $t_{k + 1} := (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)$. 
+                        }
+                        \STATE{\noindent
+                            $y_{k + 1} := x_{k + 1} + t_kt_{k + 1}^{-1}(\tilde x_{k + 1} - x_{k + 1})+ (t_k - 1)t_{k + 1}^{-1}(x_{k + 1} - x_k)$. 
+                        }
+                    \ENDFOR
                 \end{algorithmic}
                 \caption{MFISTA with Armijo Line Search}
+                \label{alg:mfista-armijo}
+            \end{algorithm}
+            We now demonstrate that it's a special case of Definition \ref{def:generic-mapg-ls}.
+            Let's consider $y_{k + 1}$ produced the GMAPG LS. 
+            If $x_k = x_{k - 1}$ then replacing all instance of $x_k$ by $x_{k - 1}$ it has: 
+            \begin{align*}
+                y_{k + 1} &= \alpha_{k + 1}(v_k) + (1 - \alpha_{k + 1})x_{k - 1}
+                \\
+                &= \alpha_{k + 1}(x_{k - 1} + \alpha_k^{-1}(\tilde x_k - x_{k - 1})) + (1 - \alpha_{k + 1})x_{k - 1}
+                \\
+                &= \alpha_{k + 1} x_{k - 1} + \alpha_{k + 1}\alpha_k^{-1}(\tilde x_k - x_{k - 1}) + (1 - \alpha_{k + 1}) x_{k - 1}
+                \\
+                &= x_{k - 1} + \alpha_{k + 1}\alpha_k^{-1}(\tilde x_k - x_{k - 1})
+                % \\
+                % &= \tilde x_k + (\alpha_{k + 1} \alpha_k^{-1} - 1)(\tilde x_k - x_{k - 1}). 
+            \end{align*}
+            Similarly when $x_k = \tilde x_k$ it produces: 
+            \begin{align*}
+                y_{k + 1} &= 
+                \alpha_{k + 1}v_k + (1 - \alpha_{k + 1})\tilde x_k
+                \\
+                &= 
+                \alpha_{k + 1}(x_{k - 1} + \alpha_k^{-1}(\tilde x_k - x_{k - 1})) + (1 - \alpha_{k + 1})x_k
+                \\
+                &= 
+                \alpha_{k + 1}\left(
+                    (1 - \alpha_{k}^{-1})x_{k - 1} + (\alpha_k^{-1} - 1)\tilde x_k + \tilde x_k
+                \right) + 
+                (1 - \alpha_{k + 1})\tilde x_k
+                \\
+                &= 
+                \alpha_{k + 1}\left(
+                    (\alpha_k^{-1} - 1)(\tilde x_k - x_{k - 1}) + \tilde x_k
+                \right) + 
+                (1 - \alpha_{k + 1})\tilde x_k. 
+                \\
+                &= \tilde x_k + \alpha_{k + 1}(\alpha_k^{-1} - 1)(\tilde x_k - x_{k - 1}). 
+            \end{align*}
+            Let's denote $y'_{k}, x'_{k}, \tilde x_k'$ as the $y_k, x_k, \tilde x_k$ produced by Algorithm \ref{alg:mfista-armijo}.
+            Observe that if $x_0'$ is not the minimizer then it has $\tilde x_1' = T_{L_0^{-1}}(y_0') = T_{L_0^{-1}}(x_0')$. 
+            Then $F(\tilde x_1') < F(x_0')$ is true. 
+            So $x_1' = \tilde x_1 = T_{L_0^{-1}}(x_0')$. 
+            Since $t_0 = 1$, it has $y_1' =\tilde x_1' + (t_0 - 1)t_1^{-1}(\tilde x_1' - x_0')= \tilde x_1'$. 
+            \par
+            Summarize the above results compactly, it has for all $k \ge 0$
+            \begin{align}\label{eqn:emp:result-item-1}
+                y_{k + 1} = \begin{cases}
+                    x_{k - 1} + \alpha_{k + 1}\alpha_k^{-1}(\tilde x_k - x_{k - 1})
+                    & \text{if } x_k = x_{k - 1} \wedge k \ge 1,
+                    \\
+                    \tilde x_k + \alpha_{k + 1}(\alpha_k^{-1} - 1)(\tilde x_k - x_{k - 1})
+                    & \text{if } x_k = \tilde x_k \wedge k \ge 1,
+                    \\
+                    \alpha_1v_0 + (1 - \alpha_1)x_0 & \text{if } k = 0. 
+                \end{cases}
+            \end{align}
+            Then it has for all $k \ge 0$: 
+            \begin{align}\label{eqn:emp:result-item-2}
+                y'_{k + 1} &= 
+                \begin{cases}
+                    x'_k + t_kt_{k + 1}^{-1}(\tilde x_{k + 1} - x_k) 
+                    & \text{if } x_{k + 1}' = x_k' \wedge k \ge 1,
+                    \\
+                    x_{k + 1}' + (t_k - 1)t_{k + 1}^{-1}(\tilde x_{k + 1}' - x_k')  
+                    & \text{if } x_{k + 1}' = \tilde x_{k + 1}'\wedge k \ge 1, 
+                    \\
+                    \tilde x_1'
+                    & 
+                    \text{if } k = 0. 
+                \end{cases}
+            \end{align}
+            Let $x_{-1} \in \RR^n$. 
+            If we choose $v_0 = x_0 = T_{L_0^{-1}} x_{-1}$, then $y_1 = \alpha_1 x_0 + (1 - \alpha_1)x_0 = x_0 = T_{L_0^{-1}}(x_{-1})$.
+            Next, we make $\alpha_k^{-1} = t_k$, then \eqref{eqn:emp:result-item-1}, \eqref{eqn:emp:result-item-2} are equivalent. 
+        \end{example}
+        Chambolle's backtracking strategies employs a line search strategies where the Lipschitz constant estimates increases if the descent lemma is satisfied. 
+        \begin{example}[MFISTA with Chambolle's adaptive backtracking]\;\\\vspace{-1em}
+            \begin{algorithm}[H]\label{alg:mfista-chambolle-ada}
+                \begin{algorithmic}[1]
+                \STATE{\textbf{Input: } }
+                \end{algorithmic}
+                \caption{MFISTA with Chambolle's adaptive backtracking}
             \end{algorithm}
@@
 
+        \begin{example}[Nesterov's monotone scheme with generic line search]\;\\\vspace{-1em}
+            \begin{algorithm}\label{alg:nesterov-mono-generic-ls}
+            \begin{algorithmic}[1]
+            \STATE{\textbf{Input: } }
+            \end{algorithmic}\caption{Nesterov's monotone scheme with generic line search}
+            \end{algorithm}
+        \end{example}
+
+    \section{Practical enhencements}
+
 % ==============================================================================

### 2025-04-24 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
             The following theorems are about the relation between PEB and QFG.
-            % ==========================================
+            % ==========================================================================================================
             % THEOREM | EQUIVALENCE BETWEEN QFG AND PEB 
-            % ==========================================
+            % ==========================================================================================================
             \begin{theorem}[equivalence between QFG and PEB]\label{thm:qfg-peb-equiv}
@@
                 \begin{align*}
-                    \mathbb E(L_f, \kappa_f, X) &\subseteq \mathbb F(L_f, \kappa^2/L_f, X), 
+                    \mathbb E(L_f, \kappa_f, X) &\subseteq \mathbb F(L_f, \kappa^2_f/L_f, X), 
                     \\
@@
                 For any $x \in X$, define the gradient projection steps by $x^+ = \Pi_{X}(x - L^{-1}_f\nabla f(x))$. 
-                Denote $\bar x^+_\Pi = \Pi_{X^+}x^+$. 
-                Using \eqref{ineq:proj-grad} with $z = \bar x^+_\Pi$ it yields: 
+                Denote $x^+_\Pi = \Pi_{X^+}x^+$. 
+                Using \eqref{ineq:proj-grad} with $z = x^+_\Pi$ it yields: 
                 {\small
@@
                         \Vert L_f(x - x^+)\Vert + L_f\Vert x - x_\Pi^+\Vert
-                    \right)^2
+                    \right)^2.
                 \end{align*}
@@
                 \end{align*}
-                Using property of projection onto $X$ we have 
-                \begin{align*}
-                    \Vert x - \bar x\Vert &\le \Vert x - x_\Pi^+\Vert
+                Let $x_\Pi = \Pi_{X^+}x$, using the property of projection onto $X$ we have 
+                \begin{align*}
+                    \Vert x - x_\Pi\Vert &\le \Vert x - x_\Pi^+\Vert
                     \le \Vert x - x^+\Vert + \Vert x^+ - x^+_\Pi\Vert
@@
                     \iff 
-                    \Vert x - \bar x\Vert - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert
-                    &\le 
-                    \Vert x^+ - x^+_\Pi\Vert. 
+                    \Vert x^+ - x^+_\Pi\Vert &\ge
+                    \Vert x - x_\Pi\Vert - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert. 
                 \end{align*}
@@
                 f(v) &= 
-                \frac{1}{2}\langle x, \nabla f(v) - A^Td\rangle + \frac{1}{2}\Vert d\Vert^2, 
+                \frac{1}{2}\langle v, \nabla f(v) - A^Td\rangle + \frac{1}{2}\Vert d\Vert^2, 
                 \\
@@
             This fact is favorable for implementations in practice. 
+            Furthermore, the diference of the function value between 2 points $v, u$ admits an interesting relation via the Bregman Divergence. 
+            Observe that $\forall u, v \in \RR^n$ it has 
+            \begin{align*}
+                f(u) - f(v) &= \langle \nabla f(v), u - v \rangle + D_f(u, v)
+                \\
+                &= \langle \nabla f(v), u - v \rangle + \langle \nabla f(u) - \nabla f(v), u - v\rangle
+                \\
+                &= \langle \nabla f(u), u - v\rangle. 
+            \end{align*}
 
@@
         \end{proof}
+        % ==============================================================================================================
+        % THEOREM | GENERIC GMAPG LS CONVERGENCE IN FXN VAL
+        % ==============================================================================================================
         \begin{theorem}[generic GMAPG LS convergence]\; \label{thm:gmapg-ls-convergence}\;\\
@@
                 \right)
-                \frac{L}{2}\Vert x^+ - x_{-1}\Vert^2. 
+                \frac{L_0}{2}\Vert x^+ - x_{-1}\Vert^2. 
             \end{align*}
@@
         \end{proof}
+        % ==============================================================================================================
+        % THEOREM | GENERIC GMAPG LS GRADIENT MAPPING CONVERGENCE
+        % ==============================================================================================================
+        \begin{theorem}[generic GMAPG LS gradient mapping convergence]
+
+        \end{theorem}
         We introduce two examples variants of line search method used to enhence the accelerated proximal gradient methods in the literatures to demonsrate Definition \ref{def:generic-mapg-ls} and Theorem \ref{thm:gmapg-ls-convergence}.
@@
         MFISTA by Beck is an example of Definition \ref{def:generic-mapg-ls}. 
+        % ==============================================================================================================
+        % EXAMPLE | MFISTA WITH ARMIJO LINE SEARCH
+        % ==============================================================================================================
         \begin{example}[MFISTA with Armijo line search]\;\\\vspace{-1em}
@@
         Chambolle's backtracking strategies employs a line search strategies where the Lipschitz constant estimates increases if the descent lemma is satisfied. 
+        % ==============================================================================================================
+        % EXAMPLE | MFISTA WITH CAMBOLLE'S ADAPTIVE BACKTRACKING
+        % ==============================================================================================================
+        The following example illustrate Chambolle's adaptive backtracking strategy in the literatures with our GMAPG LS. 
         \begin{example}[MFISTA with Chambolle's adaptive backtracking]\;\\\vspace{-1em}
@@
         \end{example}
+        % ==============================================================================================================
+        % EXAMPLE | NESTEROV'S MONOTONE SCHEME WITH GENERIC LINE SEARCH
+        % ==============================================================================================================
 
@@
     \section{Practical enhencements}
+        In this section, we provide results for the faster convergence rate of examples listed from the previous section.
 

### 2025-04-24 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, reading notes updated

@@
         \subsection{Weaker conditions of strong convexity}
-            In Necoara's et al, major results assume convexity of $f$. 
-            % ============================================================================
+            In Necoara's et al., major results assume convexity of $f$. 
+            % ==================================================================
             % THEOREM | Q-SCNVX IMPLIES QUA 
-            % ============================================================================
+            % ==================================================================
             \begin{theorem}[Q-SCNVX implies QUA]\label{thm:qscnvx-means-qua}
@@
             \begin{proof}
-                We proof by induction. 
-                Convexity of $f$ makes $X^+$ convex and $\Pi_{X^+}X$ unique for all $x \in X$. 
+                We prove by induction. 
+                Convexity of $f$ makes $X^+$ convex, so $\Pi_{X^+}x$ is unique for all $x \in \RR^n$. 
                 Make inductive hypothesis that there exists $\kappa^{(k)} \ge 0$ such that 
@@
                     f(x) \ge f^+ + \langle \nabla f(\Pi_{X^+}x), x - \Pi_{X^+}x\rangle 
-                    + \kappa^{(k)}/2\Vert x - \Pi_{X^+}x \Vert^2. 
+                    + \kappa^{(k)}_f/2\Vert x - \Pi_{X^+}x \Vert^2. 
                 \end{align*}
@@
                 Consider $x_\tau = \bar x + \tau(x - \bar x)$ for $\tau \in [0, 1]$. 
-                Calculus rule has 
-                \begin{align*}
-                    f(x) &= 
-                    f(\bar x) + \int_0^1 \langle \nabla f(x_\tau), x - \bar x\rangle d\tau
-                    \\
-                    &= 
-                    f(\bar x) + \int_0^1 \tau^{-1}\langle \nabla f(x_\tau), \tau(x - \bar x)\rangle d\tau
-                    \\
-                    &= 
-                    f(\bar x) + \int_0^1 \tau^{-1}\langle \nabla f(x_\tau), x_\tau - \bar x\rangle d\tau.
-                \end{align*}
                 $f$ is Q-SCNVX so
-                \begin{align*}
+                \begin{align}\label{ineq:thm:qscnvx-means-qua-proof-item1}
                     f^+ - f(x_\tau) &\ge \langle \nabla f(x_\tau), \Pi_{X^+}x_\tau - x_\tau\rangle + 
                     \kappa_f/2 \Vert x_\tau - \Pi_{X^+}x_\tau\Vert^2 
-                    \\
+                    \notag\\
                     &= 
@@
                     \kappa_f/2 \Vert x_\tau - \bar x\Vert^2
-                    \\
+                    \notag\\
                     \iff 
@@
                     &\ge f(x_\tau) - f^+ + \kappa_f/2\Vert x_\tau -\bar x\Vert^2. 
-                \end{align*}
-                We used $\Pi_{X^+}x_\tau = \bar x$ by convexity of $f$. 
-                Therefore:
+                \end{align}
+                In the inductive proof that comes, we will use the following intermediate results. 
+                They are labeled for ease of refernecing. 
+                \begin{enumerate}
+                    \item The inequality \eqref{ineq:thm:qscnvx-means-qua-proof-item1}. 
+                    \item By the property of projection, it has $\Pi_{X^+} x_\tau = \bar x$. 
+                    \item The inductive hypothesis with $k \ge 0$. 
+                    \item $\bar x = \Pi_{X^+}x$, $X^+$ is the set of minimizer of the of $f$ over $X$, hence $f(\bar x) = f^+$, the minimum. 
+                \end{enumerate}
+                Using calculus rules, we start with: 
                 {\footnotesize
                 \begin{align*}
-                    f(x) &\ge 
+                    f(x) &= 
+                    f(\bar x) + \int_0^1 \langle \nabla f(x_\tau), x - \bar x\rangle d\tau
+                    = 
+                    f(\bar x) + \int_0^1 \tau^{-1}\langle \nabla f(x_\tau), \tau(x - \bar x)\rangle d\tau
+                    \\
+                    &= 
+                    f(\bar x) + \int_0^1 \tau^{-1}\langle \nabla f(x_\tau), x_\tau - \bar x\rangle d\tau.
+                    \\
+                    &\underset{\text{(i)}}{\ge }
                     f(\bar x) + 
@@
                     \right) d\tau
-                    \\
-                    &= 
+                    = 
                     f(\bar x) + 
@@
                     \\
-                    &\ge 
+                    &\underset{\text{(iii)}}{\ge }
                     f(\bar x) + 
@@
                     \\
-                    &= 
+                    &\underset{\text{(ii)}}{=} 
                     f(\bar x) + 
@@
                     \\
-                    &= 
-                    f(\bar x) + 
+                    &\underset{\text{(iv)}}{=} 
+                    f^+ + 
                     \langle 
@@
                 Observe that $\frac{d}{d\tau}x_\tau = x - \bar x$ and $\Pi_{X^+}x_\tau = \bar x\; \forall \tau \in [0, 1]$. 
-                Using calculus and Theorem \ref{def:necoara-weaker-scnvx} \ref{def:necoara-qgg}: 
+                Using calculus, Definition \ref{def:necoara-weaker-scnvx} \ref{def:necoara-qgg}: 
                 \begin{align*}
@@
             \end{remark}
-            % ===============================================================================
+            % ==================================================================
             % THEOREM | QFC IMPLIES QGG  
-            % ===============================================================================
+            % ==================================================================
             \begin{theorem}[Q-SCNVX implies QGG]\label{thm:qscnvx-implies-qgg}
@@
             \end{remark}
-            % =============================================================================
+            % ==================================================================
             % THEOREM | SUFFICIENCY OF QFG 
-            % =============================================================================
+            % ==================================================================
             \begin{theorem}[sufficiency of QFG]\label{thm:qfg-suff}
@@
             \begin{proof}
-                \textbf{Firstly, we show that PEB implies QFG.}
+
                 For any $x \in X$, define the gradient projection steps by $x^+ = \Pi_{X}(x - L^{-1}_f\nabla f(x))$. 
                 Denote $x^+_\Pi = \Pi_{X^+}x^+$. 
-                Using \eqref{ineq:proj-grad} with $z = x^+_\Pi$ it yields: 
+                Let $x_\Pi = \Pi_{X^+}x$, using the property of projection onto $X$ we have 
+                \begin{align}\label{ineq:thm:qfg-peb-equiv-proof-item1}
+                    \Vert x - x_\Pi\Vert &\le \Vert x - x_\Pi^+\Vert
+                    \le \Vert x - x^+\Vert + \Vert x^+ - x^+_\Pi\Vert
+                    \notag\\
+                    &= \frac{1}{L_f}\Vert L_f(x - x^+)\Vert + \Vert x^+ - x^+_\Pi\Vert
+                    \notag\\
+                    \iff 
+                    \Vert x^+ - x^+_\Pi\Vert &\ge
+                    \Vert x - x_\Pi\Vert - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert. 
+                \end{align}
+                Before we start, we list intermediate results and conditions which are going to be used in the proof that follows for the ease of referencing. 
+                \begin{enumerate}
+                    \item The inequality \eqref{ineq:thm:qfg-peb-equiv-proof-item1}. It uses the property of projection onto a set hence convexity of $X^+$ is not needed. 
+                    \item The quadratic growth condition with $\mathbb F(L_f, \kappa_f)$. No convexity is needed. 
+                \end{enumerate}
+                \textbf{Firstly, we show that QFG implies PEB.}
+                Consider \eqref{ineq:proj-grad} with $z = x^+_\Pi$ it yields: 
                 {\small
@@
                     \\
-                    \quad&\ge 
+                    \quad&\underset{\text{(ii)}}{\ge }
                     \frac{\kappa_f}{2}\Vert x^+ - x_\Pi^+\Vert^2
                     - \Vert L_f(x - x^+)\Vert\Vert x^+_\Pi - x^+\Vert
-                    - \frac{1}{2L_f}\Vert L_f(x - x^+)\Vert^2   &\text{QFG, Cauchy}
+                    - \frac{1}{2L_f}\Vert L_f(x - x^+)\Vert^2 
                     \\
@@
                 }
-                From the last line, by positivity of norm it has
-                \begin{align*}
+                From the last line, it's can be equivalently expressed as:
+                \begin{align*}
+                    0 &\le
                     \Vert L_f(x - x^+)\Vert + L_f\Vert x^+ - x_\Pi^+\Vert
-                    &\ge \sqrt{L_f(\kappa_f + L_f)}\Vert x^+ - x^+_\Pi\Vert
-                    \\
-                    \iff 
+                    - \sqrt{L_f(\kappa_f + L_f)}\Vert x^+ - x^+_\Pi\Vert
+                    \\
+                    &=
                     \Vert L_f(x - x^+)\Vert
-                    &\ge 
-                    \left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right)\Vert x^+ - x^+_\Pi\Vert. 
-                \end{align*}
-                Let $x_\Pi = \Pi_{X^+}x$, using the property of projection onto $X$ we have 
-                \begin{align*}
-                    \Vert x - x_\Pi\Vert &\le \Vert x - x_\Pi^+\Vert
-                    \le \Vert x - x^+\Vert + \Vert x^+ - x^+_\Pi\Vert
-                    \\
-                    &= \frac{1}{L_f}\Vert L_f(x - x^+)\Vert + \Vert x^+ - x^+_\Pi\Vert
-                    \\
-                    \iff 
-                    \Vert x^+ - x^+_\Pi\Vert &\ge
-                    \Vert x - x_\Pi\Vert - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert. 
-                \end{align*}
-                Combining the two above inequalities gives 
-                {\small
-                \begin{align*}
-                    0 &\le 
+                    - \left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right)\Vert x^+ - x^+_\Pi\Vert
+                    \\
+                    &\underset{\text{(i)}}{\le}
                     \Vert L_f(x - x^+)\Vert
@@
                 \end{align*}
-                }
                 Skipping algebra, the fraction simplifies to 
@@
                 This gives PEB condition. 
-                \textbf{We now show QFG implies PEB}. 
+                \textbf{We now show PEB implies QFG}. 
                 From the error bound condition using $\kappa_f$ it has
@@
                 \\
-                D_f(x, y) &= \langle x - y, A^TA (x - y)\rangle
-                \\
-                &= \langle \nabla f(x) - \nabla f(y), x - y\rangle. 
+                D_f(u, v) &= (1/2)\langle u - v, A^TA (u - v)\rangle
+                \\
+                &= (1/2)\langle \nabla f(u) - \nabla f(v), u - v\rangle. 
             \end{align*}
@@
             This fact is favorable for implementations in practice. 
-            Furthermore, the diference of the function value between 2 points $v, u$ admits an interesting relation via the Bregman Divergence. 
+            Furthermore, the difference of the function value between 2 points $v, u$ admits an interesting relation via the Bregman Divergence. 
             Observe that $\forall u, v \in \RR^n$ it has 
@@
                 \\
-                &= \langle \nabla f(v), u - v \rangle + \langle \nabla f(u) - \nabla f(v), u - v\rangle
-                \\
-                &= \langle \nabla f(u), u - v\rangle. 
-            \end{align*}
+                &= \langle \nabla f(v), u - v \rangle + (1/2)\langle \nabla f(u) - \nabla f(v), u - v\rangle
+                \\
+                &= (1/2)\langle \nabla f(u) + \nabla f(v), u - v\rangle. 
+            \end{align*}
+            For this problem, the computation overhead for $f(u) - f(v), D_f(u, v)$ is very little if $\nabla f(u), \nabla f(v)$ is known.
 
@@
         \end{proof}
-        % ==============================================================================================================
+        % ======================================================================
         % THEOREM | GENERIC GMAPG LS CONVERGENCE IN FXN VAL
-        % ==============================================================================================================
+        % ======================================================================
         \begin{theorem}[generic GMAPG LS convergence]\; \label{thm:gmapg-ls-convergence}\;\\
@@
             In the proof follows, the follow facts will be used. 
-            We list them in advance and they will be labeled during the proof. 
+            We list them in advance, and they will be labeled during the proof. 
             \begin{enumerate}
@@
         \end{proof}
-        % ==============================================================================================================
+        % ======================================================================
         % THEOREM | GENERIC GMAPG LS GRADIENT MAPPING CONVERGENCE
-        % ==============================================================================================================
+        % ======================================================================
         \begin{theorem}[generic GMAPG LS gradient mapping convergence]
@@
         MFISTA by Beck is an example of Definition \ref{def:generic-mapg-ls}. 
-        % ==============================================================================================================
+        % ======================================================================
         % EXAMPLE | MFISTA WITH ARMIJO LINE SEARCH
-        % ==============================================================================================================
+        % ======================================================================
         \begin{example}[MFISTA with Armijo line search]\;\\\vspace{-1em}
@@
         Chambolle's backtracking strategies employs a line search strategies where the Lipschitz constant estimates increases if the descent lemma is satisfied. 
-        % ==============================================================================================================
+        % ======================================================================
         % EXAMPLE | MFISTA WITH CAMBOLLE'S ADAPTIVE BACKTRACKING
-        % ==============================================================================================================
+        % ======================================================================
         The following example illustrate Chambolle's adaptive backtracking strategy in the literatures with our GMAPG LS. 
@@
         \end{example}
-        % ==============================================================================================================
+        % ======================================================================
         % EXAMPLE | NESTEROV'S MONOTONE SCHEME WITH GENERIC LINE SEARCH
-        % ==============================================================================================================
+        % ======================================================================
 

### 2025-04-25 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
     \end{definition}
-    % =================================================
+    % ==========================================================================
     % WEAKLY CONVEX GENERIC PROXIMAL GRADIENT INEQUALITY
-    % ==================================================
+    % ==========================================================================
     \begin{theorem}[weakly convex generic proximal gradient inequality]\label{thm:pg-ineq-wcnvx-generic}\;\\
@@
             The following theorems are about the relation between PEB and QFG.
-            % ==========================================================================================================
+            % ==================================================================
+            % LEMMA | QFG AND GRADIENT MAPPING
+            % ==================================================================
+            \begin{lemma}[gradient mapping and quadratic function growth]\;\label{lemma:grad-map-qfg}\\
+                Let $f$ satisfies Assumtion \ref{ass:necoara-2019-settings}. 
+                Suppose that $f \in \mathbb F(L_f, \mu_f, X)$ so it satisfies the quadratic function growth condition. 
+                For all $x \in \RR^n$, define $x^+ = \Pi_X(x - L^{-1}_f\nabla f(x))$, 
+                definte projections onto the set of minimizers $x^+_\Pi = \Pi_{X^+} x^+, X_\Pi = \Pi_{X^+}x$, then
+                \begin{align*}
+                    \left(
+                        \sqrt{L_f(\kappa_f + L_f)} - L_f
+                    \right)\Vert x^+ - x_\Pi^+\Vert
+                    &\le \Vert L_f(x - x^+)\Vert. 
+                \end{align*}
+            \end{lemma}
+            \begin{proof}
+                Using convexity, consider \eqref{ineq:proj-grad} with $z = x^+_\Pi$ it yields: 
+                {\small
+                \begin{align*}
+                    0 &\ge 
+                    f(x^+) - f(x^+_\Pi) - L_f\langle x_\Pi^+ - x^+, x^+ - x\rangle
+                    - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert^2
+                    \\
+                    &\ge
+                    \frac{\kappa_f}{2}\Vert x^+ - x_\Pi^+\Vert^2
+                    - \Vert L_f(x - x^+)\Vert\Vert x^+_\Pi - x^+\Vert
+                    - \frac{1}{2L_f}\Vert L_f(x - x^+)\Vert^2 
+                    \\
+                    &= \frac{\kappa_f}{2}\Vert x^+ - x_\Pi^+\Vert^2
+                    - \frac{1}{2L_f}\left(
+                        \Vert L_f(x - x^+)\Vert^2
+                        + L_f\Vert L_f(x - x^+)\Vert\Vert x_\Pi^+ - x^+\Vert
+                    \right)
+                    \\
+                    &= 
+                    \frac{\kappa_f + L_f}{2}\Vert x^+ - x^+_\Pi\Vert^2
+                    - \frac{1}{2L_f}\left(
+                        \Vert L_f(x - x^+)\Vert + L_f\Vert x - x_\Pi^+\Vert
+                    \right)^2.
+                \end{align*}
+                }
+                From the last line, it's can be equivalently expressed as:
+                \begin{align*}
+                    0 &\le
+                    \Vert L_f(x - x^+)\Vert + L_f\Vert x^+ - x_\Pi^+\Vert
+                    - \sqrt{L_f(\kappa_f + L_f)}\Vert x^+ - x^+_\Pi\Vert
+                    \\
+                    &=
+                    \Vert L_f(x - x^+)\Vert
+                    - \left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right)\Vert x^+ - x^+_\Pi\Vert.
+                \end{align*}
+            \end{proof}
+            % ==================================================================
             % THEOREM | EQUIVALENCE BETWEEN QFG AND PEB 
-            % ==========================================================================================================
+            % ==================================================================
             \begin{theorem}[equivalence between QFG and PEB]\label{thm:qfg-peb-equiv}
@@
             \begin{proof}
-
                 For any $x \in X$, define the gradient projection steps by $x^+ = \Pi_{X}(x - L^{-1}_f\nabla f(x))$. 
@@
                     \item The inequality \eqref{ineq:thm:qfg-peb-equiv-proof-item1}. It uses the property of projection onto a set hence convexity of $X^+$ is not needed. 
-                    \item The quadratic growth condition with $\mathbb F(L_f, \kappa_f)$. No convexity is needed. 
                 \end{enumerate}
-                \textbf{Firstly, we show that QFG implies PEB.}
-                Consider \eqref{ineq:proj-grad} with $z = x^+_\Pi$ it yields: 
+                Starting with Lemma \ref{lemma:grad-map-qfg} because $f$ satisfies quadratic growth and it is assumed convex, then it has: 
                 {\small
                 \begin{align*}
-                    0 &\ge 
-                    f(x^+) - f(x^+_\Pi) - L_f\langle x_\Pi^+ - x^+, x^+ - x\rangle
-                    - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert^2
-                    \\
-                    \quad&\underset{\text{(ii)}}{\ge }
-                    \frac{\kappa_f}{2}\Vert x^+ - x_\Pi^+\Vert^2
-                    - \Vert L_f(x - x^+)\Vert\Vert x^+_\Pi - x^+\Vert
-                    - \frac{1}{2L_f}\Vert L_f(x - x^+)\Vert^2 
-                    \\
-                    &= \frac{\kappa_f}{2}\Vert x^+ - x_\Pi^+\Vert^2
-                    - \frac{1}{2L_f}\left(
-                        \Vert L_f(x - x^+)\Vert^2
-                        + L_f\Vert L_f(x - x^+)\Vert\Vert x_\Pi^+ - x^+\Vert
-                    \right)
-                    \\
-                    &= 
-                    \frac{\kappa_f + L_f}{2}\Vert x^+ - x^+_\Pi\Vert^2
-                    - \frac{1}{2L_f}\left(
-                        \Vert L_f(x - x^+)\Vert + L_f\Vert x - x_\Pi^+\Vert
-                    \right)^2.
-                \end{align*}
-                }
-                From the last line, it's can be equivalently expressed as:
-                \begin{align*}
                     0 &\le 
-                    \Vert L_f(x - x^+)\Vert + L_f\Vert x^+ - x_\Pi^+\Vert
-                    - \sqrt{L_f(\kappa_f + L_f)}\Vert x^+ - x^+_\Pi\Vert
-                    \\
-                    &=
                     \Vert L_f(x - x^+)\Vert
@@
                 \end{align*}
-                Skipping algebra, the fraction simplifies to 
+                }
+                Skipping some algebra, the fraction simplifies to 
                 \begin{align*}

### 2025-04-25 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
         \begin{example}[MFISTA with Chambolle's adaptive backtracking]\;\\\vspace{-1em}
+            This example won't give specific rules for calculating $\tilde x_k$ for monotone descent. 
+            Chambolle's restart has specific rules for choosing the stepsizes based on the estimates of the Lipschitz constants. 
             \begin{algorithm}[H]\label{alg:mfista-chambolle-ada}
@@
 
-    \section{Practical enhencements}
+    \section{practical enhancement}
         In this section, we provide results for the faster convergence rate of examples listed from the previous section. 
+    \section{restarting with gradient and function values}
+
+\section{Primal Dual Lagrangian for LP}
 

### 2025-04-28 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

--- 2025-04-25 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
@@
         \end{theorem}
-        We introduce two examples variants of line search method used to enhence the accelerated proximal gradient methods in the literatures to demonsrate Definition \ref{def:generic-mapg-ls} and Theorem \ref{thm:gmapg-ls-convergence}.
+        We introduce two examples variants of line search method used to enhance the accelerated proximal gradient methods in the literatures to demonstrate Definition \ref{def:generic-mapg-ls} and Theorem \ref{thm:gmapg-ls-convergence}.
         \par
@@
         \begin{example}[MFISTA with Chambolle's adaptive backtracking]\;\\\vspace{-1em}
+            This example won't give specific rules for calculating $\tilde x_k$ for monotone descent. 
+            Chambolle's restart has specific rules for choosing the step sizes based on the estimates of the Lipschitz constants. 
             \begin{algorithm}[H]\label{alg:mfista-chambolle-ada}
@@
 
-    \section{Practical enhencements}
+    \section{Practical enhancement}
         In this section, we provide results for the faster convergence rate of examples listed from the previous section. 
+    \section{Restarting with gradient and function values}
+
+\section{Primal Dual Lagrangian for LP}
 

### 2025-04-30 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, important fixes
>w<, changes

@@
             The assumption follows give the same setting as Necoara et al. \cite{necoara_linear_2019}. 
-            % =======================
+            % ==================================================================
             % NECOARA's ASSUMPTIONS 
-            % =======================
+            % ==================================================================
             \begin{assumption}\label{ass:necoara-2019-settings}
@@
             \end{align*}
-            % ==============================
+            % ==================================================================
             % STRONG CONVEXITY DEFINITION
-            % ==============================
+            % ==================================================================
             \begin{definition}[strong convexity]\label{def:necoara-scnvx}
@@
                     E_1^Ty + z
+                \end{bmatrix}
+                \\
+                &= 
+                \begin{bmatrix}
+                    E_1^TE_1 + c_1^T & E_1^TE_2 + c_2^T & -c_1b^T & \\
+                    E_2^TE_1 + c_1^T & E_2^TE_2 + c_2^T & -c_2b^T & \\
+                    -bc_1^T& -bc_2^T & E_2E_2^T + E_1E_1^T + bb^T & E_1E_1^T \\
+                    & & & E_1^Ty + z\\
+                \end{bmatrix}
+                \begin{bmatrix}
+                    x_1 \\ x_2 \\ y \\ z
                 \end{bmatrix}. 
@@
                 &= 
-                (1 - \alpha_k)(F(x_{k - 1}) - F(x^+)) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k\Vert^2
+                (1 - \alpha_k)(F(x_{k - 1}) - F(x^+)) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_{k - 1}\Vert^2
                 - \left(
@@
                 &\underset{\text{(iv)}}{\le} 
-                (1 - \alpha_k)(F(x_{k - 1}) - F(x^+)) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k\Vert^2
+                (1 - \alpha_k)(F(x_{k - 1}) - F(x^+)) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_{k - 1}\Vert^2
                 - \left(
@@
                 \right)
-                \frac{L_{k - 1}\alpha_{k - 1}^2(\rho_{k - 1}L_kL_{k - 1}^{-1})}{2}\Vert x^+ - v_k\Vert^2 \\
+                \frac{L_{k - 1}\alpha_{k - 1}^2(\rho_{k - 1}L_kL_{k - 1}^{-1})}{2}\Vert x^+ - v_{k-1}\Vert^2 \\
                     &\quad 
@@
                     F(x_{k - 1}) - F(x^+) + \frac{L_{k - 1}\alpha_{k - 1}^2(\rho_{k - 1}L_kL_{k - 1}^{-1})}{2}
-                    \Vert x^+ - v_k\Vert^2
+                    \Vert x^+ - v_{k - 1}\Vert^2
                 \right) \\
@@
                     F(x_{k - 1}) - F(x^+) + \frac{L_{k - 1}\alpha_{k - 1}^2\max(1, \rho_{k - 1}L_kL_{k - 1}^{-1})}{2}
-                    \Vert x^+ - v_k\Vert^2
+                    \Vert x^+ - v_{k - 1}\Vert^2
                 \right) \\
@@
                     F(x_{k - 1}) - F(x^+) + \frac{L_{k - 1}\alpha_{k - 1}^2}{2}
-                    \Vert x^+ - v_k\Vert^2
+                    \Vert x^+ - v_{k - 1}\Vert^2
                 \right) \\

### 2025-04-30 Notebook LaTEX/R-WAPG/presentation.tex
>w<, changes

--- 2023-11-13 Latex Templates/Generic Latex Beam Presentation/presentation.tex
@@
     \subsection{Taxonomy of Proximal type of Methods}
-        \begin{frame}{Frame Title}
-
-            \begin{block}{Formula Presented in Block}
-                \begin{align}
-                    \min_{x} g(x) + h(x)
-                \end{align}    
-            \end{block}
-
-            \begin{itemize}
-                \item [1.]Throughout this presentation, we assume the objective of a function $f$ is the sum of 2 functions.
-                \item [2.]We are interested in the paper: FISTA (Fast Iterative-Shrinkage Algorithm) by Beck and Teboulle \cite{paper:FISTA}. 
-                \pause 
-                \item [1.] When $h = \delta_Q$ with $Q$ closed and convex with $Q\subseteq \text{ri}\circ \text{dom}(g)$, we use projected subgradient. 
-                \item [2.] When $g$ is \textbf{\emph{strongly smooth}} and $h$ is \textbf{closed convex proper} whose proximal oracle is easy to compute, we consider the use of FISTA. 
-            \end{itemize}
+        \begin{frame}{Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations}
 
         \end{frame}
-
-    \subsection{The Proximal Operator}
-        \begin{frame}{Frame Title}
-            \begin{definition}[Definition of Something]
-                Let $f$ be convex closed and proper, then the proximal operator parameterized by $\alpha > 0$ is a non-expansive mapping defined as: 
-                \begin{align*}
-                    \text{prox}_{f, \alpha}(x) := 
-                    \arg\min_{y}\left\lbrace
-                        f(y) + \frac{1}{2\alpha} \Vert y - x\Vert^2
-                    \right\rbrace. 
-                \end{align*}
-            \end{definition}  
-            \begin{remark}
-                When $f$ is convex, closed, and proper, 
-            \end{remark}
-        \end{frame}
-
-        \begin{frame}{Prox is the Resolvant of Subgradient}
-            \begin{lemma}[The Lemma]\label{lemma:prox_alternative_form}
-                When the function $f$ is convex closed and proper, the $\text{prox}_{\alpha, f}$ can be viewed as the following operator $(I + \alpha \partial f)^{-1}$. 
-            \end{lemma}
-            \begin{proof}
-                Minimizer satisfies zero subgradient condition, 
-                {\scriptsize
-                \begin{align*}
-                    \mathbf 0 &\in \partial
-                    \left[
-                        \left.
-                            f(y) + \frac{1}{2\alpha} \Vert y - x\Vert^2 
-                        \right| y
-                    \right](y^+)
-                    \\
-                    \mathbf 0 &\in \partial f(y^+) + \frac{1}{\alpha}(y^+ - x)
-                    \\
-                    \frac{x}{\alpha} &\in 
-                    (\partial f + \alpha^{-1}I)(y^+)
-                    \\
-                    x &\in 
-                    (\alpha \partial f + I)(y^+)
-                    \\
-                    y &\in (\alpha\partial f+ I)^{-1}(x).
-                \end{align*}
-                }
-            \end{proof}
-
-        \end{frame}
-
-    \subsection{Strong Smoothness}
-        \begin{frame}{Equivalence of Strong Smoothness and Lipschitz Gradient}
-            \begin{theorem}[Lipschitz Gradient Equivalence under Convexity]
-                Suppose $g$ is differentiable on the entire of $\mathbb E$.
-It is closed convex proper.
-It is strongly smooth with parameter $\alpha$ if and only if the gradient $\nabla g$ is globally Lipschitz continuous with a parameter of $\alpha$ and $g$ is closed and convex.
-                \begin{align*}
-                    \Vert \nabla g(x) -\nabla g(y)\Vert \le 
-                    \alpha 
-                    \Vert x - y \Vert\quad \forall x, y\in \mathbb E
-                \end{align*}
-            \end{theorem}
-            \begin{proof}
-                Using line integral, we can prove Lipschitz gradient implies strong smoothness without convexity.
-The converse requires convexity and applying generalized Cauchy Inequality to (iv) in Theorem 5.8 for Beck's textbook \cite{book:first_order_opt}.
-            \end{proof}
-
-        \end{frame}
-    \subsection{A Major Assumption}    
-        \begin{frame}{A Major Assumption}
-            \begin{assumption}[Convex Smooth Nonsmooth with Bounded Minimizers]\label{assumption:1}
-                We will assume that $g:\mathbb E\mapsto \mathbb R$ is \textbf{strongly smooth} with constant $L_g$ and $h:\mathbb E \mapsto \bar{\mathbb R}$ \textbf{is closed convex and proper}.
-We define $f := g + h$ to be the summed function and $\text{ri}\circ \text{dom}(g) \cap \text{ri}\circ \text{dom}(h) \neq \emptyset$.
-We also assume that a set of minimizers exists for the function $f$ and that the set is bounded.
-Denote the minimizer using $\bar x$.
-            \end{assumption}
-        \end{frame}
-
-\section{A New Fancy Section}
-    \subsection{A Fancy Subsetction for Algorithm}
-        \begin{frame}{The Accelerated Proximal Gradient Method}
-            \begin{block}{Momentum Template Method}
-                \begin{algorithm}[H]
-                    \begin{algorithmic}[1]
-                        \STATE{\textbf{Input:} $x^{(0)}, x^{(-1)}, L, h, g$; 2 initial guesses and stepsize L}
-                        \STATE{$y^{(0)} = x^{(0)} + \theta_k (x^{(0)} - x^{(-1)})$}
-                        \FOR{$k = 1, \cdots, N$}
-                            \STATE{$x^{(k)} = \text{prox}_{h, L^{-1}}(y^{(k)} + L^{-1}\nabla g(y^{(k)})) =: \mathcal P_{L^{-1}}^{g, h}(y^{(k)})$}
-                            \STATE{$y^{(k + 1)} = x^{(k)} + \theta_k(x^{(k)} - x^{(k - 1)})$}
-                        \ENDFOR
-                    \end{algorithmic}
-                    \caption{Template Proximal Gradient Method With Momentum}\label{alg:fista_template}
-                \end{algorithm}
-            \end{block}
-        \end{frame}
-
-\section{Numerical Experiments}
-    \input{Sections/sectionfile.tex}
 

### 2025-04-30 Notebook LaTEX/R-WAPG/presentation.tex
>w<, changes

@@
 \usepackage[utf8]{inputenc}
-
 \usepackage{hyperref}
@@
 \usepackage{graphicx}
-\DeclareMathOperator{\argmin}{argmin}
+% \DeclareMathOperator{\argmin}{argmin}
 \usepackage{algorithmic}
@@
 \usepackage{subcaption}
+\usepackage{tcolorbox}
+
+% THEMES AND BEAMER SETTINGS ===================================================
+% \usetheme{Madrid}
 \graphicspath{{.}}
+\input{presets/wang/custom_commands.tex} % IMPORT WANG'S LATEX CUSTOM COMMANDS. 
+\setbeamertemplate{theorems}[numbered] % ADD NUMBERING TO ALL AMS THEOREMS. 
+\setbeamertemplate{footline}[frame number] % ADD PAGE NUMBERS ON BOTTOM. 
+\setbeamertemplate{blocks}[rounded][shadow=true]
+\setbeamertemplate{navigation symbols}{} 
+% \setbeamercolor{block title}{bg=cyan,fg=black}  % CHANGE THE BLOCK STYLE IN BEAMER. 
+% \setbeamercolor{block body}{bg=lime,fg=black} % CHANGE THE BLOCK STYLE IN BEAMER.
 
-\author{Generic Name}
-\title{Title for Super Fancy Stuff}
-% Informe o seu email de contato no comando a seguir
-% Por exemplo, alcebiades.col@ufes.br
-\newcommand{\email}{lalala@lala.la}
-\setbeamercovered{transparent}
-\setbeamertemplate{navigation symbols}{}
-%\logo{}
-\institute[]{Some Super Fancy Institution}
+% BIB STYLES SETTINGS ----------------------------------------------------------
+\setbeamertemplate{bibliography item}{\insertbiblabel}
+\setbeamerfont{bibliography item}{size=\footnotesize}
+\setbeamerfont{bibliography entry author}{size=\footnotesize}
+\setbeamerfont{bibliography entry title}{size=\footnotesize}
+\setbeamerfont{bibliography entry location}{size=\footnotesize}
+\setbeamerfont{bibliography entry note}{size=\footnotesize}
+% \setbeamercovered{transparent}  % GREY OUT PAUSED FUTURE ITEMS IN SLID. 
+\bibliographystyle{siam}
+
+% SLIDE INFORMATION ============================================================
+\author{Hongda Li}
+\title[Thesis Proposal Talk]{
+    Nesterov's First Order Method Accelerations: Unifications, Applications and Numerical Experiments
+}
+% \newcommand{\email}{lalala@lala.la}
+\institute[UBCO]{
+    University of British Columbia Okanagan
+}
 \date{\today}
-\subject{Subject Title }
+\subject{Nesterov's acceleration and its applications}
 
-% ---------------------------------------------------------
-% Selecione um estilo de referência
-\bibliographystyle{IEEEtran}
+% SLIDES ELEMENTS CUSTOMIZATIONS ===============================================
+\theoremstyle{definition}
+\newtheorem{remark}{Remark}[section]
+\newtheorem{assumption}{Assumption}[section]
+\newtheorem{proposition}{Proposition}[section]
 
-%\bibliographystyle{abbrv}
-%\setbeamertemplate{bibliography item}{\insertbiblabel}
-% ---------------------------------------------------------
-
-% ---------------------------------------------------------
-\newtheorem{remark}{Remark}
-\newtheorem{assumption}{Assumption}
-
+% DOCUMENT STARTS ==============================================================
 \begin{document}
@@
 
-\section{This is the First Section}
-    \subsection{Taxonomy of Proximal type of Methods}
-        \begin{frame}{Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations}
+\section{Introduction and background}
+    \subsection{Motivations}
+        \begin{frame}{Nesterov's accelerated gradient in 1983}
+            There are many variants of Nesterov's acceleration. 
+            \begin{block}{Nesterov's accelerated gradient in 1983}
+                Initialized $x_0 = y_0 \in \RR^n$. 
+                The original formulation by Nesterov in 1983 \cite{nesterov_method_1983} has
+                \begin{align*}
+                    & x_{k + 1} := y_k - L^{-1}\nabla F(y_k),
+                    \\
+                    & t_{k + 1} := 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right),
+                    \\
+                    & \theta_{k + 1} := (t_{k} - 1)/t_{k + 1}, \label{eqn:example-algorithm}
+                    \\
+                    & y_{k + 1} := x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k).
+                \end{align*}    
+            \end{block}
+            If $F$ is convex and has $L$ Lipschitz smooth gradient and minimizer $x^+$ exists. 
+            Then it has
+            \begin{itemize}
+                \item a convergence rate of $\mathcal O(1/k^2)$ of $(F(x_k) - F(x^+))_{k \ge 1}$;
+                \item this convergence rate is optimal in the sense as proposed by Nesterov \cite{nesterov_lectures_2018}.
+            \end{itemize}
+        \end{frame}
+        \begin{frame}{Chambolle, Dossal}
+            Generalized by Beck \cite{beck_fast_2009-1} in 2009 is the FISTA algorithm for additive smooth and non-smooth objective. 
+            It's available in their proof that the sequence $(t_k)_{k}$ can be relaxed: 
+            \begin{tcolorbox}\noindent\vspace{-1em}
+                \begin{align*}
+                    (\forall k \ge 1)\quad t_k (t_k - 1) &\le t_{k - 1}^2. 
+                \end{align*}    
+            \end{tcolorbox}
+            \begin{enumerate}
+                \item When it's equal, as in the case of Nesterov's 1983, the convergence rate is the best. 
+                \item It's showed by Chambolle and Dossal in 2015 \cite{chambolle_convergence_2015} that the choice $(k + a -1)/a$ has weak convergence of iterates $(x_k)_{k \ge 0}$ for all $a > 2$, under the same assumption as before.
+            \end{enumerate}
+        \end{frame}
+        \begin{frame}{V-FISTA and strongly convex variants}
+            Fixing the momentum sequence gives an optimal convergence rate of the algorithm for the class of $F:\RR^n \rightarrow \RR$ that has 
+            \begin{enumerate}
+                \item $L$ smooth gradient, 
+                \item and $\mu \ge 0$ strongly convexity. 
+            \end{enumerate}
+            Available in Nesterov's book \cite{nesterov_lectures_2018} and Beck's book \cite{beck_first-order_2017} showed that if the sequence $(\theta_k)_{k\ge 0}$ has: 
+            \begin{tcolorbox}
+                \begin{align*}
+                   \theta_k = \frac{\sqrt{L/\mu} - 1}{\sqrt{L/\mu} + 1}. 
+                \end{align*}
+            \end{tcolorbox}
+            Disregarding the definition of $(t_k)_{k \ge 0}$ for now. 
+            Then the algorithm has
+            \begin{enumerate}
+                \item A linear convergence rate of $\mathcal O((1 - \sqrt{\mu/L})^k)$ for $(F(x_k) - F(x^+))_{k \ge 1}$. 
+            \end{enumerate}
+        \end{frame}
+    \subsection{Our discoveries and inspirations}
+        \begin{frame}{The assumptions we make throughout}
+            Let the ambient space be $\RR^n$ equiped with Euclidean inner product and norm. 
+            \begin{assumption}[Convex smooth plus nonsmooth]
+                Define $F := f + g$.
+                \begin{enumerate}
+                    \item $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex.
+                    \item $g: \RR^n \rightarrow \overline \RR$ is proper, closed and convex. The extended real is defined as $\overline \RR := \RR \cup \{\infty\}$.
+                    \item A minimizer exists for the optimization problem: $F^+ = \min_x \left\lbrace f(x) + g(x)\right\rbrace$.
+                \end{enumerate}
+            \end{assumption}
+        \end{frame}
+        \begin{frame}{Our theoretical contributions, statement of results}
+            Here are the promises: 
+            \begin{enumerate}
+                \item We relaxed the traditional choices of the sequence $(\theta_k)_{k \ge 1}$ in the weakest possible way to show that an upper bound for the sequence $(F(x_k) - F^+)_{k \ge 1}$ exists.
+                \item We proposed an unified framework which we call ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)" that unifies the convergence theories for functions that are strongly convex or not necessarily strongly convex.
+                \item We demonsrate that the R-WAPG framework can be represented is equivalent to various representations of the Nesterov's type accelerated proximal gradient methods with Euclidean geometry in the literature.
+            \end{enumerate}
+
+        \end{frame}
+        \begin{frame}{Summarized results of our theoretical contributions}
+            Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences. 
+            Suppose that $\alpha_0 \in (0, 1]$ and for all $k \ge 1$, $\alpha_k \in (\mu/L, 1)$ and define $(\rho_k)_{k\ge0 }$ by: 
+            \begin{tcolorbox}\noindent\vspace{-1em}
+                \begin{align*}
+                    \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0).
+                \end{align*}
+            \end{tcolorbox}
+            We can show Nesterov's type accelerated proximal gradient algorithm (similar to what's show in prior but with $g \equiv 0$) which generates $(F(x_k) - F^+)_{k\ge 1}$ has an upper bound of:
+            \begin{tcolorbox}\noindent\vspace{-1em} 
+                \begin{align*}
+                    \mathcal O\left(
+                        \left(
+                            \prod_{i = 0}^{k - 1} \max(1, \rho_{i})
+                        \right)
+                        \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
+                    \right).
+                \end{align*}
+            \end{tcolorbox}
+        \end{frame}
+        \begin{frame}{Realizations of our upper bound}
+            Let's label 
+            \begin{enumerate}
+                \item[(i)] R-WAPG with $\mu \ge 0$, %\ref{def:wapg} 
+                \item[(ii)] Chambolle, Dossal 2015 \cite{chambolle_convergence_2015} with $\mu \ge 0$,
+                \item[(iii)] V-FISTA Beck (10.7.7) \cite{beck_first-order_2017}, with $\mu > 0$,
+                \item[(iv)] R-WAPG with $\mu > 0$, %\ref{def:wapg}
+            \end{enumerate}
+            \begin{table}[H]
+                \centering
+                {\scriptsize
+                \begin{tabular}{|l|l|l|l|l|}
+                \hline
+                    Algorithm 
+                    & 
+                    $\alpha_k$ 
+                    & 
+                    $\rho_k$ 
+                    & 
+                    $F(x_k) - F^+ \le \mathcal O(\cdot)$ 
+                \\ \hline
+                    (i) &
+                    $\alpha_k \in(\mu/L, 1)$ &
+                    $\rho_k > 0$ &
+                    \begin{tabular}{l}
+                        $\max(1, \rho_i)(1 - \alpha_{i + 1})$
+                        \\
+                        % (Proposition \ref{prop:wapg-convergence})
+                    \end{tabular}
+                \\ \hline
+                    (ii) &
+                    $ 0 < \alpha_k^{-2} \le \alpha_{k + 1}^{-1} - \alpha_{k + 1}^{-2}$ &
+                    $\rho_k \ge 1$ &
+                    \begin{tabular}{l}
+                        $\alpha_k^{2}$ \\ 
+                        % (Theorem \ref{thm:r-wapg-on-cham-doss})
+                    \end{tabular}
+                \\ \hline
+                    (iii) &
+                    $\alpha_k = \sqrt{\mu/L}$ &
+                    $\rho_k = 1$ &
+                    \begin{tabular}{l}
+                        $(1 - \sqrt{\mu/L})^k$,
+                        \\
+                        % (Theorem \ref{thm:fixed-momentum-fista}, remark)
+                    \end{tabular}
+                \\ \hline
+                    (iv) &
+                    $\alpha_k = \alpha \in (\mu/L, 1)$ &
+                    $\rho_k = \rho > 0$ &
+                    \begin{tabular}{l}
+                        $\left(1 - \min\left(\mu/(\alpha L), \alpha\right)\right)^{k}$
+                        \\
+                        % (Theorem \ref{thm:fixed-momentum-fista})
+                    \end{tabular}
+                \\ \hline
+                \end{tabular}
+                }
+            \end{table}
+            Note that
+        \end{frame}
+        \begin{frame}{A practical realization inspired by the theories}
 
@@
 
+\section{The R-WAPG framework and convergence rate}
+
+\section{Unifying different variants of accelerated proximal gradient}
+
+\section{Adaptive momentum sequence and numerical experiments}
+
 \section{References}
     \begin{frame}{References}        
-
-        \bibliography{refs.bib}
+        \bibliography{references/R-WAPG.bib}
     \end{frame}

### 2025-05-02 Notebook LaTEX/R-WAPG/presentation.tex
>w<, changes

@@
 \usepackage{tcolorbox}
+\usepackage{mathtools}
 
@@
 % SLIDE INFORMATION ============================================================
-\author{Hongda Li}
+\author{Hongda Li, Wang Xianfu}
 \title[Thesis Proposal Talk]{
-    Nesterov's First Order Method Accelerations: Unifications, Applications and Numerical Experiments
+    Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations
 }
@@
         \begin{frame}{Nesterov's accelerated gradient in 1983}
-            There are many variants of Nesterov's acceleration. 
+            Let's recall a classic. 
             \begin{block}{Nesterov's accelerated gradient in 1983}
@@
                 The original formulation by Nesterov in 1983 \cite{nesterov_method_1983} has
+                {\small
                 \begin{align*}
@@
                 \end{align*}    
+                }
             \end{block}
@@
         \begin{frame}{The assumptions we make throughout}
-            Let the ambient space be $\RR^n$ equiped with Euclidean inner product and norm. 
             \begin{assumption}[Convex smooth plus nonsmooth]
+                Let the ambient space be $\RR^n$ equipped with Euclidean inner product and norm. 
                 Define $F := f + g$.
@@
             \end{assumption}
+            \textbf{This assumption the full scope of the theoretical and practical discussion, assume it throughout.}
         \end{frame}
@@
                 \item We relaxed the traditional choices of the sequence $(\theta_k)_{k \ge 1}$ in the weakest possible way to show that an upper bound for the sequence $(F(x_k) - F^+)_{k \ge 1}$ exists.
-                \item We proposed an unified framework which we call ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)" that unifies the convergence theories for functions that are strongly convex or not necessarily strongly convex.
-                \item We demonsrate that the R-WAPG framework can be represented is equivalent to various representations of the Nesterov's type accelerated proximal gradient methods with Euclidean geometry in the literature.
+                \item We proposed a unified framework which we call ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)" that unifies the convergence theories for functions that are strongly convex or not necessarily strongly convex.
+                \item We demonstrate that the R-WAPG framework can be represented is equivalent to various representations of the Nesterov's type accelerated proximal gradient methods with Euclidean geometry in the literature.
             \end{enumerate}
@@
         \end{frame}
-        \begin{frame}{Realizations of our upper bound}
+        \begin{frame}{Our convergence theory unifies variants in the literatures}
             Let's label 
@@
                 \item[(iii)] V-FISTA Beck (10.7.7) \cite{beck_first-order_2017}, with $\mu > 0$,
-                \item[(iv)] R-WAPG with $\mu > 0$, %\ref{def:wapg}
+                \item[(iv)] R-WAPG with $\mu > 0$. %\ref{def:wapg}
             \end{enumerate}
@@
                     \begin{tabular}{l}
-                        $\max(1, \rho_i)(1 - \alpha_{i + 1})$
+                        $\prod_{i = 0}^{k - 1}\max(1, \rho_i)(1 - \alpha_{i + 1})$
                         \\
@@
             \end{table}
-            Note that
+            Note that in Chambolle and Dossal \cite{chambolle_convergence_2015} and their sequence $t_k = \alpha_k^{-1}$ and $\alpha_k = a/(k + 1)$ satisfies $\alpha_k^{-1} \le \alpha_{k + 1}^{-1} - \alpha_{k + 1}^{-2}$.
         \end{frame}
         \begin{frame}{A practical realization inspired by the theories}
-
+            Our theories stated that, the convergence of R-WAPG algorithm is ultimately described by the sequence $(\alpha_k)_{k \ge 0}$.
+            \textbf{Taking this idea further, this is what we did in practice}: 
+            \begin{tcolorbox}
+                We made the Free R-WAPG algorithm estimates the strong convexity $\mu$ constant through the Bregman Divergence at two successive iterates while the algorithm is running and put it into the sequence to run the algorithm.
+                \par
+                It's completely parameter free by equipping it with Armijo line search. 
+            \end{tcolorbox}
         \end{frame}
@@
 \section{The R-WAPG framework and convergence rate}
+    \subsection{Introducing the R-WAPG framework}
+        \begin{frame}{The R-WAPG sequences}
+            \begin{definition}{R-WAPG sequences}\label{def:rwapg-seq}
+                Assume $0 \le \mu < L$. 
+                Let $(\alpha_k)_{k \ge 0}$ be a sequence such that it satisfies: 
+                \begin{align*}
+                    & \alpha_0 \in (0, 1], \\
+                    & \alpha_k \in (\mu, 1] \quad (\forall k \ge 1). 
+                \end{align*}    
+                Define $(\rho_k)_{k \ge 0}$ by 
+                \begin{align*}
+                    \rho_k := \frac{\alpha_{k + 1}^2 - (\mu/L) \alpha_{k + 1}}{
+                        (1 - \alpha_{k + 1}) \alpha_k^2.
+                    }
+                \end{align*}
+                We all the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ the R-WAPG sequences. 
+            \end{definition}
+        \end{frame}
+        \begin{frame}{R-WAPG}
+            \begin{definition}[relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
+                Choose any $x_1 \in \RR^n, v_1 \in \RR^n$.
+                Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}.
+                The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for $k\ge 1$ by the procedures:
+                \begin{tcolorbox}
+                    For $k=1, 2, 3, \ldots$
+                    \begin{align*}
+                        \gamma_k &\defeq \rho_{k -1}L\alpha_{k - 1}^2,
+                        \\
+                        \hat \gamma_{k + 1} & \defeq (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2,
+                        \\
+                        y_k &\defeq
+                        (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k),
+                        \\
+                        g_k &\defeq \mathcal G_L (y_k),
+                        \\
+                        v_{k + 1} &\defeq
+                        \hat\gamma^{-1}_{k + 1}
+                        (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k),
+                        \\
+                        x_{k + 1} &\defeq T_L y_k.
+                    \end{align*}
+                \end{tcolorbox}
+            \end{definition}
+        \end{frame}
+        \begin{frame}{Convergence of R-WAPG}
+            After six pages of dense proof in the paper, we can deduce the following theorem: 
+            \begin{proposition}[R-WAPG convergence]\label{prop:wapg-convergence}
+                Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$.
+                Let vector sequence $(y_k, v_{k}, x_{k})_{k \ge 1}$ and R-WAPG sequences $\alpha_k, \rho_k$ be given by Definition \ref{def:wapg}.
+                % Let $\epsilon_k, y_k$ be given by Assumption \ref{ass:regret-gap}.
+                % Define $R_1 = 0$ and suppose that for $k = 1, 2, \ldots, N$, we have $R_k$ recursively given by:
+                % \begin{align*}
+                %     R_{k + 1}
+                %     :=
+                %     \frac{1}{2}\left(
+                %         L^{-1} - \frac{\alpha_k^2}{\hat \gamma_{k + 1}}
+                %     \right)\Vert g_k\Vert^2
+                %     +
+                %     (1 - \alpha_k)
+                %     \left(
+                %         \epsilon_k + R_k +
+                %         \frac{\mu\alpha_k\gamma_k}{2\hat \gamma_{k + 1}}
+                %         \Vert v_k - y_k\Vert^2
+                %     \right).
+                % \end{align*}
+                Then for all $k = 1, 2, \ldots, N$:
+                {\small
+                \begin{align*}
+                    & F(x_{k + 1}) - F(x^*) + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
+                    \\
+                    &\le
+                    \left(
+                        \prod_{i = 0}^{k - 1} \max(1, \rho_{i})
+                    \right)
+                    \left(
+                        \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
+                    \right)
+                    \left(
+                        F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
+                    \right).
+                \end{align*}
+                }
+            \end{proposition}
+            To use this theorem for the convergence of existing variants of Accelerated Proximal Gradient in the literature, we need alternative representations of R-WAPG that make it similar to what appears in the literature.
+        \end{frame}
+    \subsection{Different representation of accelerated proximal gradient}
+        \begin{frame}{The intermediate form}
+            \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}
+                {\footnotesize
+                Assume $\mu < L$ and let $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}.
+                Initialize any $x_1, v_1$ in $\RR^n$.
+                For $k \ge 1$, the algorithm generates sequence of vector iterates $(y_{k}, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by the procedures:
+                \begin{tcolorbox}
+                    For $k = 1, 2, \ldots$
+                    \begin{align*}
+                        & y_{k} \defeq
+                        \left(
+                            1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
+                        \right)^{-1}
+                        \left(
+                            v_{k} +
+                            \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
+                        \right),
+                        \\
+                        & x_{k + 1} \defeq
+                        y_k - L^{-1} \mathcal G_L (y_k),
+                        \\
+                        & v_{k + 1} \defeq
+                        \left(
+                            1 + \frac{\mu}{L \alpha_k - \mu}
+                        \right)^{-1}
+                        \left(
+                            v_k +
+                            \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
+                        \right) - \frac{1}{L\alpha_{k}}\mathcal G_L (y_k).
+                    \end{align*}
+                \end{tcolorbox}
+                }
+            \end{definition}
+            The closest algorithm that fits the form but with $\mu = 0$ is Chapter 12 of in Ryu and Yin's Book \cite{ryu_large-scale_2022}, right after Theorem 17. 
+        \end{frame}
+        \begin{frame}{Intermediate form equivalency}
+            \begin{proposition}[R-WAPG is equivalent to intermediate form]\label{prop:wapg-first-equivalent-repr}
+                If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}),
+                then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$,  namely, for all $k\ge 1$,
+                \begin{align}
+                    & y_{k} =
+                    \left(
+                        1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
+                    \right)^{-1}
+                    \left(
+                        v_{k} +
+                        \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
+                    \right), 
+                    % \label{eqn:rwapg-first-equiv-form-eqn-1}
+                    \\
+                    & x_{k + 1} =
+                    y_k - L^{-1} \mathcal G_L (y_k),
+                    \\
+                    & v_{k + 1} =
+                    \left(
+                        1 + \frac{\mu}{L \alpha_k - \mu}
+                    \right)^{-1}
+                    \left(
+                        v_k +
+                        \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
+                    \right) - \frac{1}{L\alpha_{k}}\mathcal G_L (y_k).
+                    % \label{eqn:rwapg-first-equiv-form-eqn-2}
+                \end{align}
+            \end{proposition}
+        \end{frame}
+        \begin{frame}{Similar triangle form}
+            \begin{proposition}[R-WAPG is equivalent to similar triangle form]\label{prop:wagp-st-form}
+                Let iterates $(y_k, x_{k}, v_{k})_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge 0}$ be given by Definition \ref{def:r-wapg-intermediate}.
+                Then for all $k \ge 1$, iterates $y_k, x_{k + 1}, v_{k + 1}$
+                satisfy:
+                \begin{align}
+                    y_{k} &=
+                    \left(
+                        1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
+                    \right)^{-1}
+                    \left(
+                        v_{k} +
+                        \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
+                    \right),
+                    \label{eqn:rwapg-st-form-eqn-1}
+                    \\
+                    x_{k + 1} &=
+                    y_k - L^{-1} \mathcal G_L (y_k),
+                    \\
+                    v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k).
+                    \label{eqn:rwapg-st-form-eqn-3}
+                \end{align}
+            \end{proposition}
+            Combining both of these representations, we can draw a similar triangle. 
+        \end{frame}
+        \begin{frame}{Similar triangle form illustration Part I}
+            To understand the name ``similar triangle form" for it in the literature, we draw it out. 
+            Write $\tau_k = \frac{L - L\alpha_k}{L\alpha_k - \mu}$ so $y_k = (1 + \tau_k)^{-1}(v_k + \tau_k x_k)$ from the similar triangle form. 
+            The R-WAPG sequence has $\alpha_k \in (\mu/L, 1)$ for all $k \ge 1$, so it has: 
+            \begin{tcolorbox}
+                \begin{figure}
+                    \centering
+                    \includegraphics[width=15em]{assets/st_part1.png}
+                \end{figure}
+            \end{tcolorbox}
+        \end{frame}
+        \begin{frame}{Similar triangle form illustration part II}
+            Then $x_{k + 1} = y_k - L^{-1}\mathcal G_L(y_k)$ hence it has 
+            \begin{tcolorbox}
+                \begin{figure}
+                    \centering
+                    \includegraphics[width=15em]{assets/st_part2.png}
+                \end{figure}
+            \end{tcolorbox}
+        \end{frame}
+        \begin{frame}{Similar triangle form illustration part III}
+            Recall that $v_{k + 1} = x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k)$, so $v_{k + 1}$ is on the line defined by $x_{k + 1} - x_k$, and it looks like: 
+            \begin{tcolorbox}
+                \begin{figure}
+                    \includegraphics[width=15em]{assets/st_part3.png}
+                \end{figure}
+            \end{tcolorbox}
+            Let $\xi_k = \mu(L\alpha_k - \mu)^{-1}$, the intermediate form it has $v_{k+1} = (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - L^{-1}\alpha_k^{-1} \mathcal G_L(y_k)$, hence the gray line. 
+        \end{frame}
+        \begin{frame}{Similar triangle form is equivalent to the momentum form}
+            \begin{proposition}[Momentum form]\label{prop:r-wapg-momentum-repr}
+                Let sequence $(\alpha_k, \rho_k)_{k \ge 0}$ and iterates $(x_k, v_k, y_k)_{k\ge 1}$ be given by the R-WAPG intermediate form.
+                Then it has:
+                \begin{enumerate}
+                    \item[(i)] For all $k \ge 1$, the iterates $x_{k + 1}, y_{k + 1}$ satisfy:
+                    \begin{align*}
+                        x_{k + 1} &= y_k - L^{-1}\mathcal G_L (y_k),
+                        \\
+                        y_{k + 1} &=
+                        x_{k + 1} +
+                        \frac{\rho_k\alpha_k(1 - \alpha_k)}
+                        {\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k).
+                    \end{align*}
+                    \item[(ii)] $v_1 = x_1$ if and only if $y_1 = x_1$.
+                    \item[(iii)] If in addition $\mu = 0$, then the momentum term in (i) admits a simpler representation:
+                    \begin{align*}
+                        (\forall k \ge 1) \quad
+                        \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
+                        & = \alpha_{k + 1}(\alpha_k^{-1} - 1).
+                    \end{align*}
+                \end{enumerate}
+            \end{proposition}
+        \end{frame}
+    \subsection{Unifying different variants of accelerated proximal gradient}
+        \begin{frame}{Convergence of Chambolle and Dossal variant of FISTA}
+            FISTA algorithm proposed in Chambolle and Dossal \cite{chambolle_convergence_2015} has a function value convergence fully described by Proposition \ref{prop:wapg-convergence}. 
+            \begin{lemma}[R-WAPG sequence as inverted FISTA sequence]\label{lemma:inverted-fista-seq}
+                Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}.
+                If $\mu = 0, \rho_k \ge 1\; \forall k \ge 0$, and $\alpha_0 = 1$, then:
+                \begin{enumerate}
+                    \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$.
+                    \item Let $t_k := \alpha_k^{-1}$, then $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``inverted FISTA sequence''.
+                    \item $\prod_{i = 1}^k\max(1, \rho_{k - 1})(1 - \alpha_k) = \alpha_k^2 \quad (\forall k \ge 1)$.
+                \end{enumerate}
+            \end{lemma}
+            Let $\alpha_k = a/(k + 1)$, $a \ge 2$, Applying Proposition \ref{prop:wapg-convergence} yields $\mathcal O(1/k^2)$ convergence rate of $(F(x_k) - F^+)_{k \ge 1}$ after some algebra routine.
+        \end{frame}
+        \begin{frame}{In addition, our theory made a new prediction}
+            \begin{theorem}[fixed momentum APG]\label{thm:fixed-momentum-fista}
+                {\small
+                Assume $L > \mu > 0$, let a pair of constant R-WAPG sequence: $(\alpha_k)_{k \ge0}$ is a constant and $\alpha_k \in (\mu/L, 1)$ for all $k \ge 0$.
+                Define $q := \mu/L$ and for any fixed $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, represent $\alpha_k = \alpha = r \sqrt{q}$. 
+                Consider the algorithm with a constant momentum specified by the following:
+                \begin{tcolorbox}
+                    Define $\theta = \left(1 - r^{-1}\sqrt{q}\right)(1 - r\sqrt{q})(1 - q)^{-1}$.
+                    \\
+                    Initialize $y_1 = x_1$; for $k = 1, 2, \ldots, N$, update:
+                    \begin{align*}
+                        &x_{k + 1} = y_k + L^{-1}\mathcal G_L (y_k)
+                        ,
+                        \\
+                        & y_{k + 1} = x_{k + 1} + \theta(x_{k + 1} - x_k).
+                    \end{align*}
+                \end{tcolorbox}
+                Then the algorithm generates $(x_k)_{k \ge 1}$ such that $(F(x_{k}) - F(x^*))_{k\geq 1}$ converges at a rate of $\mathcal O\left(\left(1 - \min\left(\mu/(\alpha L), \alpha\right)\right)^k\right)$.
+                }
+            \end{theorem}
+        \end{frame}
+\section{Adaptive momentum sequence and numerical experiments}
+    \subsection{Free R-WAPG}
+        \begin{frame}{Free R-WAPG}
+            \begin{algorithm}[H]
+                \begin{algorithmic}
+                {\footnotesize
+                \STATE{\textbf{Input: } $f, g, L > \mu \ge 0, x_0 \in \RR^n, N \in \N$}
+                \STATE{\textbf{Initialize: }$y_0 := x_0;L_0 := 1; \mu_0 := 1/2; \alpha_0 = 1$;}
+                \STATE{\textbf{Compute: } $f(y_k)$; }
+                \FOR{$k = 0, 1, 2, \cdots, N$}
+                    \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L_k^{-1}\partial g]^{-1}(y_k - L_k^{-1}\nabla f(y_k))$;}
+                    \WHILE{$L_k/2\Vert x^+ - y_k\Vert^2 < D_f(x^+, y_k)$}
+                        \STATE{$L_k:= 2L_k$;}
+                        \STATE{$x^+ = [I + L_k^{-1}\partial g]^{-1}(y_k - L_k^{-1}\nabla f(y_k))$; }
+                    \ENDWHILE
+                    \STATE{$x_{k + 1} := x^+$;}
+                    \STATE{
+                        \textcolor{red}{
+                            $\alpha_{k + 1} := (1/2)\left(\mu_k/L_k - \alpha_{k}^2 + \sqrt{(\mu_k/L_k - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;
+                        }
+                    }
+                    \STATE{$\theta_{k + 1} := \alpha_k(1 - \alpha_k)/(\alpha_k^2 + \alpha_{k + 1})$;}
+                    \STATE{$y_{k + 1}:= x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$; }
+                    \STATE{\textbf{Compute: } $f(y_{k + 1})$}
+                    \STATE{
+                        \textcolor{red}{
+                            $\mu_{k + 1} := D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2 + (1/2)\mu_k$;
+                        }
+                    }
+                \ENDFOR
+                }
+                \end{algorithmic}
+                \caption{Free R-WAPG}
+                \label{alg:free-rwapg}
+            \end{algorithm}
+        \end{frame}
+    \subsection{Numerical experiment, simple quadratic}
+        \begin{frame}{A basic experiment on convex quadratic functions}
+            Consider $\min_{x}\{F(x) := f(x) + 0\}$ with $f(x) = (1/2)\langle x, Ax\rangle$. 
+            We are measuring: 
+            \begin{align*}
+                \delta_k := \log_2\left(
+                    \frac{F(x) - F^+}{F(x_0) - F^+}\right).  
+            \end{align*}
+            Here are the parameters. 
+            \begin{enumerate}
+                \item $A \in \RR^{N \times N}$ square diagonal defined by 
+                \begin{align*}
+                    (\forall i = 1, \ldots, N)\; A_{i, i} = \begin{cases}
+                        0 & i = 1
+                        \\
+                        \mu + \frac{(i - 1)(L - \mu)}{N - 1} & i \ge 2
+                    \end{cases}
+                \end{align*}
+                \item $L = 1, \mu = 10^{-5}$ are known in prior. 
+                \item All algorithm terminates after $\Vert \mathcal G_L(y_k) \Vert \le 10^{-10}$. 
+                \item Initial conditions $x_0 \sim \mathcal N(I, \mathbf 0)$, i.i.d. 
+            \end{enumerate}
+        \end{frame}
+        \begin{frame}{Experiment results 1}
+            A realization of $x_0 \sim \mathcal N(I, \mathbf 0)$ is used for each trial for all algorithms. 
+            Each trial results of V-FISTA, M-FISTA (Monotone restarted FISTA) and Free R-WAPG were collected. 
+            We plot the medium, minimum, and maximum of $\delta_k$: 
+            \begin{figure}[H]
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/simple_regression_batched-256.png}
+                    \caption{$N = 256$, simple convex quadratic.}
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/simple_regression_batched-1024.png}
+                    \caption{$N = 1024$, simple convex quadratic. }
+                \end{subfigure}
+                \caption{
+                    Statistics for experiments with simple convex quadratic for V-FISTA, M-FISTA, and R-WAPG.
+                }
+                \label{fig:simple-quadratic-NOG}
+            \end{figure}
+        \end{frame}
+        \begin{frame}{$\mu$ estimations}
+            Free R-WAPG estimates $\mu_k$ each iteration. 
+            The value of $\mu_k$ had been recorded for one trial and this is a plot of the estimations: 
+            \begin{figure}[H]
+                \centering
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/simple_regression_loss_sc_estimates_1024.png}
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/simple_regression_loss_1024.png}
+                \end{subfigure}
+                \caption{
+                    $N = 1024$, the $\mu$ estimates produced by Algorithm \ref{alg:free-rwapg} (R-WAPG) is recorded.
+                }
+                \label{fig:simple-quadratic-r-wapg-mu-estimates}
+            \end{figure}
+        \end{frame}
+    \subsection{Numerical experiment, LASSO}
+        \begin{frame}{The LASSO problem}
+            The problem of LASSO from Tibshirani \cite{tibshirani_regression_1996} is the optimization problem $\min_{x \in \RR^n}\{(1/2)\Vert Ax - b\Vert^2 - \lambda\Vert x\Vert_1\}$. 
+            \begin{enumerate}
+                \item $A \in \RR^{N \times N}$, full of i.i.d random variable from a standard normal distribution. 
+                \item Computed in prior, $L, \mu$ are parameters estimated by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$. The norm is the spectral norm. 
+                \item The smallest value of $F(x_k)$, for all algorithms, over all tries are taken as an estimate of $F^+$. 
+            \end{enumerate}
+        \end{frame}
+        \begin{frame}{Results plotted}
+            With $A\in \RR^{N\times N}$ fixed, for each $x_0 \sim \mathcal N(I, \mathbf 0)$ realized, 30 experiments are preformed and the medium, minimum and maximum of $\delta_k$ are recorded for M-FISTA, Free R-WAPG, and V-FISTA.
+            \begin{figure}[H]
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/lasso_batched_statistics_64-256.png}
+                    \caption{LASSO experiment with $M = 64, N = 256$. Plots of minimum, maximum, and median $\delta_k$ with estimated $F^*$. }
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{assets/lasso_batched_statistics_64-128.png}
+                    \caption{LASSO experiment with $M = 64, N = 128$. Plots of minimum, maximum, and median $\delta_k$ with estimated $F^*$. }
+                \end{subfigure}
+                \caption{LASSO experiments statistics for test algorithms. }
+                \label{fig:batched-lasso}
+            \end{figure}
+        \end{frame}
+        \begin{frame}{Estimates of strong convexity constant}
+            The parameters in this specific trial are are $\mu = 7.432363627613958\times 10^{-18}$ and $L = 2321.737206983643$. 
+            \begin{figure}[H]
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \includegraphics[width=\textwidth]{assets/lasso_loss_256.png}
+                    \caption
+                    {A single run of LASSO experiment displaying $F(x_k) - F^*$ for several test algorithms.
+                    }
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.47\textwidth}
+                    \includegraphics[width=\textwidth]{assets/lasso_sc_estimates_256.png}
+                    \caption{The $\mu_k$ estimated by FR-WAPG for one LASSO experiment. }
+                \end{subfigure}
+                \caption{A single LASSO experiment results, with $M = 64, N=256$. f}
+                \label{fig:single-lass-mu-estimates}
+            \end{figure}
+        \end{frame}
 
-\section{Unifying different variants of accelerated proximal gradient}
-
-\section{Adaptive momentum sequence and numerical experiments}
-
-\section{References}
+\section{Our paper is on arxiv and references}
+    \begin{frame}{Thanks for the participations. Merci pour les participations.}
+        Our paper can be found on arxiv using the following QR code: 
+        \begin{figure}
+            \centering
+            \includegraphics[width=17em]{assets/paper-qrcode.png}
+        \end{figure}
+    \end{frame}
     \begin{frame}{References}        

### 2025-05-04 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes
>w<, fixed shit and moved,added stuff

@@
         \begin{align*}
-            \frac{q}{2}\Vert z - x^+\Vert^2 
+            \frac{q}{2}\Vert z - \bar x\Vert^2 
             &\le 
@@
             \begin{align*}
-                0 &\le F(z) - F(\bar x) + \frac{L}{2}\Vert z - x\Vert - \frac{L}{2}\Vert z - \bar x\Vert^2. 
+                0 &\le F(z) - F(\bar x) + \frac{L}{2}\Vert z - x\Vert^2 - \frac{L}{2}\Vert^2 z - \bar x\Vert^2. 
             \end{align*}
@@
         We introduce two examples variants of line search method used to enhance the accelerated proximal gradient methods in the literatures to demonstrate Definition \ref{def:generic-mapg-ls} and Theorem \ref{thm:gmapg-ls-convergence}.
-        \par
+    \section{Algorithms formulations of GMAPG}
         MFISTA by Beck is an example of Definition \ref{def:generic-mapg-ls}. 
@@
         % ======================================================================
+        \begin{algorithm}[H]
+            \begin{algorithmic}[1]
+                \STATE{\textbf{Input:}}
+                \caption{Armijo Line Search}
+            \end{algorithmic}
+        \end{algorithm}
+        We will now give an algorithimic description of GMAPG. 
+        \begin{algorithm}[H]\label{alg:chambolle-btls}
+            \begin{algorithmic}[1]
+                \STATE{\noindent
+                    \textbf{Input:}
+                    $f, g, x, v, L> L_{\min} > 0, \rho, \alpha$
+                }
+                \STATE{$L^+ := \max(L_{\min}, \rho L)$.}
+                \FOR{$i = 1, 2, \ldots, 53$}
+                    \STATE{$\alpha^+ := (1/2)\left(\alpha\sqrt{\alpha^2 + L/L^+} - \alpha^2\right)$. }
+                    \STATE{$y^+ := \alpha^+ v + (1 - \alpha^+) x$. }
+                    \STATE{$x^+ := T_{1/L^+, f, g}(y^+)$.}
+                    \IF{$2D_f(x^+, y^+) \le \Vert x^+ - y^+\Vert^2$}
+                        \STATE{\textbf{break}}
+                    \ENDIF
+                    \STATE{$L^+ := 2^iL^+$.}
+                \ENDFOR
+                \STATE{\textbf{Return: }$y^+, x^+, \alpha^+, L^+$}
+                \caption{Chambolle's Backtracking}
+            \end{algorithmic}
+        \end{algorithm}
+
+        \begin{algorithm}[H]\label{alg:mfista-chambolle-ada}
+            \begin{algorithmic}[1]
+                \STATE{\noindent
+                    \textbf{Input:} $f, g, x_{-1}, L_0, r_{\min}, \text{Exit condition: }\mathbb E_\chi$. 
+                }
+
+            \end{algorithmic}
+            \caption{GMAPG with Chambolle's backtracking}
+        \end{algorithm}
         \begin{example}[MFISTA with Armijo line search]\;\\\vspace{-1em}
@@
                 \begin{algorithmic}[1]
-                    \STATE{\textbf{Input:} $x_0 \in \RR^n, L_0 \in \RR^n, f:\RR^n \rightarrow \RR, g: \mathbb \RR^n \rightarrow \overline \RR$} 
+                    \STATE{\textbf{Input:} $x_{-1} \in \RR^n, L_0 \in \RR^n, f:\RR^n \rightarrow \RR, g: \mathbb \RR^n \rightarrow \overline \RR$} 
                     \STATE{
-                        $y_0 := x_0, t_0 := 1$.
+                        $x_0 := y_0, t_0 := 1$.
                     }
                     \FOR{$k = 0, 1, 2, \ldots$}
-                        \STATE{$\tilde x_{k + 1} = T_{L_k^{-1}}(y_k)$.}
+                        \STATE{$\tilde x_{k + 1} := T_{L_k^{-1}}(y_k)$.}
                         \IF{$D_f(\tilde x_{k + 1}, y_k) > L_k/2\Vert \tilde x_{k + 1} - y_k\Vert^2$}
@@
             \end{algorithm}
-            We now demonstrate that it's a special case of Definition \ref{def:generic-mapg-ls}.
+            We now demonstrate that Algorithm \ref{alg:mfista-armijo} is a special case of Definition \ref{def:generic-mapg-ls}.
             Let's consider $y_{k + 1}$ produced the GMAPG LS. 
@@
         \end{example}
-        Chambolle's backtracking strategies employs a line search strategies where the Lipschitz constant estimates increases if the descent lemma is satisfied. 
-        % ======================================================================
-        % EXAMPLE | MFISTA WITH CAMBOLLE'S ADAPTIVE BACKTRACKING
-        % ======================================================================
-        The following example illustrate Chambolle's adaptive backtracking strategy in the literatures with our GMAPG LS. 
-        \begin{example}[MFISTA with Chambolle's adaptive backtracking]\;\\\vspace{-1em}
-            This example won't give specific rules for calculating $\tilde x_k$ for monotone descent. 
-            Chambolle's restart has specific rules for choosing the step sizes based on the estimates of the Lipschitz constants. 
-            \begin{algorithm}[H]\label{alg:mfista-chambolle-ada}
-                \begin{algorithmic}[1]
-                \STATE{\textbf{Input: } }
-                \end{algorithmic}
-                \caption{MFISTA with Chambolle's adaptive backtracking}
-            \end{algorithm}
-        \end{example}
         % ======================================================================

### 2025-05-05 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, wu yeee

@@
         We introduce two examples variants of line search method used to enhance the accelerated proximal gradient methods in the literatures to demonstrate Definition \ref{def:generic-mapg-ls} and Theorem \ref{thm:gmapg-ls-convergence}.
-    \section{Algorithms formulations of GMAPG}
-        MFISTA by Beck is an example of Definition \ref{def:generic-mapg-ls}. 
-        % ======================================================================
-        % EXAMPLE | MFISTA WITH ARMIJO LINE SEARCH
-        % ======================================================================
+    \section{Algorithmic description of GMAPG}
+        There are several components to the GMAPG algorithm. 
         \begin{algorithm}[H]
-            \begin{algorithmic}[1]
-                \STATE{\textbf{Input:}}
+            \begin{algorithmic}[1]\label{alg:armijo-ls}
+                \STATE{\textbf{Function ArmijoLS}
+                    $(f, g, x, v, L, \alpha, \_, \_)$
+                }
                 \caption{Armijo Line Search}
@@
         \end{algorithm}
-        We will now give an algorithimic description of GMAPG. 
         \begin{algorithm}[H]\label{alg:chambolle-btls}
@@
                 \STATE{\noindent
-                    \textbf{Input:}
-                    $f, g, x, v, L> L_{\min} > 0, \rho, \alpha$
+                    \textbf{Function ChambBT}($f, g, x, v, L, \alpha, L_{\min}, \rho$)
                 }
@@
         \end{algorithm}
-
-        \begin{algorithm}[H]\label{alg:mfista-chambolle-ada}
+        \begin{algorithm}[H]\label{alg:beck-mono}
             \begin{algorithmic}[1]
                 \STATE{\noindent
-                    \textbf{Input:} $f, g, x_{-1}, L_0, r_{\min}, \text{Exit condition: }\mathbb E_\chi$. 
-                }
-
+                    \textbf{Function BeckMono}($f, g, x, v, L, L_{\min}, \rho, \alpha$)
+                }
+                \caption{Beck's monotone routine}
+            \end{algorithmic}
+        \end{algorithm}
+        \begin{algorithm}[H]\label{alg:nes-mono}
+            \begin{algorithmic}[1]
+                \STATE{\noindent
+                    \textbf{Function NesMono}($f, g, x, v, L, L_{\min}, \rho, \alpha$)
+                }
+                \caption{Nesterov's monotone routine}
+            \end{algorithmic}
+        \end{algorithm}
+        \begin{algorithm}[H]\label{alg:gmapg}
+            \begin{algorithmic}[1]
+                \STATE{\noindent
+                    \textbf{Function GMAPG} (
+                        $f, g, x_{-1}, L_0, r_{\min}, \text{Exit condition: }\mathbb E_\chi$
+                    )
+                }
             \end{algorithmic}
@@
         \end{algorithm}
+    % ==========================================================================
+    % SECTION | EXAMPLES OF GMAPG IN THE LITERATURE
+    % ==========================================================================
+    \section{Examples of GMAPG in the literature}
         \begin{example}[MFISTA with Armijo line search]\;\\\vspace{-1em}
@@
         % ======================================================================
-
         \begin{example}[Nesterov's monotone scheme with generic line search]\;\\\vspace{-1em}
@@
         In this section, we provide results for the faster convergence rate of examples listed from the previous section. 
+    \section{Nonconvex convergence}
+
     \section{Restarting with gradient and function values}

### 2025-05-05 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, fixes and changes
>w<, changes at works

@@
         Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-add-nonsmooth}. 
-        Define the proximal gradient operator by: 
-        \begin{align*}
-            T_{\beta^{-1}, f, g}(x) &= \hprox_{\beta^{-1}g} \left(
+        Let $\beta > 0$, we define the proximal gradient operator for all $x \in \RR^n$: 
+        \begin{align*}
+            T_{\beta^{-1}, f, g}(x) &:= \hprox_{\beta^{-1}g} \left(
                 x - \beta^{-1} \nabla f(x)
@@
         % ======================================================================
-        \begin{theorem}[generic GMAPG LS gradient mapping convergence]
-
+        \begin{theorem}[generic GMAPG LS gradient mapping convergence]\;\label{thm:gmapg-generic-gradmap-convergence}\\
+            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista}. 
+            Let the sequences $(x_k, y_k, v_k)$ satisfy GMAPG (Definition \ref{def:generic-mapg-ls}). 
+            If in addition, the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and it is initialized with $x_0=x_0 = T_{1/L_0, f, g}x_{-1}$ for some $x_{-1} \in\RR^n$ and there exists $x^+$ which is a minimizer of $F$.
+            Then, the convergence of gradient mapping $\Vert \mathcal G_{1/L_k}(y_k)\Vert$ is described by the sequence $(\beta)_{k \ge 0}$ where $\beta_0 = 1$ and for all $k \ge 1$:
+            \begin{align*}
+                \beta_k := \prod_{i = 0}^{k - 1}(1 - \alpha_{i + 1}) \max\left(1, \rho_i L_{i + 1}L_i^{-1}\right). 
+            \end{align*}
+            It satisfies for all $k \ge 1$ the inequality:
+            \begin{align*}
+                \Vert \mathcal G_{L_k} y_k\Vert &\le 
+                \sqrt{\beta_k}L_k L_0 \left(
+                    1 - 
+                    \min(\rho_{k - 1}, L_k^{-1} L_{k - 1})^{1/2}
+                \right)\Vert x^+ - v_0\Vert. 
+            \end{align*}
         \end{theorem}
-        We introduce two examples variants of line search method used to enhance the accelerated proximal gradient methods in the literatures to demonstrate Definition \ref{def:generic-mapg-ls} and Theorem \ref{thm:gmapg-ls-convergence}.
+        \begin{proof}
+            The following intermediate results are in order for the proof. 
+            \begin{enumerate}
+                \item[(a)]
+            \end{enumerate}
+        \end{proof}
     \section{Algorithmic description of GMAPG}
         There are several components to the GMAPG algorithm. 
+        This section introduces two variants of line search method used to enhance the accelerated proximal gradient methods in the literatures to demonstrate Definition \ref{def:generic-mapg-ls}. 
         \begin{algorithm}[H]
             \begin{algorithmic}[1]\label{alg:armijo-ls}
-                \STATE{\textbf{Function ArmijoLS}
-                    $(f, g, x, v, L, \alpha, \_, \_)$
-                }
+                \STATE{\noindent
+                    % \textbf{Function ArmijoLS}
+                    % $(f, g, x, v, L, \alpha, \_, \_)$
+                    \textbf{Function ArmijoLS:}
+                    \begin{tabular}{lcl}
+                        $f : \RR^n \rightarrow \RR$ && Convex Lipschitz smooth\\ 
+                        $g: \RR^n \rightarrow \overline \RR$  &&  Convex function with Proximal operator\\ 
+                        $x \in \RR^n$ && Vector\\
+                        $v \in \RR^n$ && Vector\\
+                        $L \in \RR$ && $L > 0$\\
+                        $\alpha \in \RR$  && $\alpha \in (0, 1]$
+                    \end{tabular}
+                }
+                \STATE{$\alpha^+ := (1/2)\left(\alpha\sqrt{\alpha^2 + 1} - \alpha^2\right)$.}
+                \STATE{$y^+ := \alpha^+ v + (1 - \alpha^+)x$.}
+                \STATE{$L^+ := L$. }
+                \FOR{$i = 1, 2,\ldots, 53$}
+                    \STATE{$L^+ := 2L^+$. }
+                    \STATE{$x^+ := T_{1/L^+, f, g}(y^+)$. }
+                    \IF{$D_f(x^+, y^+) \le (L^+/2)\Vert x^+ - y^+\Vert^2$}
+                        \STATE{\textbf{break}}
+                    \ENDIF
+                    \STATE{$L^+ := 2^{i}L$}
+                \ENDFOR
+                \STATE{\textbf{Return:} $y^+, x^+, \alpha^+, L^+$}
                 \caption{Armijo Line Search}
@@
                 \STATE{\noindent
-                    \textbf{Function ChambBT}($f, g, x, v, L, \alpha, L_{\min}, \rho$)
+                    \textbf{Function ChamBT}($f, g, x, v, L, \alpha, L_{\min}, \rho$)
                 }

### 2025-05-06 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
     % ==========================================================================
-    \begin{theorem}[weakly convex generic proximal gradient inequality]\label{thm:pg-ineq-wcnvx-generic}\;\\
+    \begin{theorem}[weakly convex generic proximal gradient inequality]\;\label{thm:pg-ineq-wcnvx-generic}\\
         Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-add-nonsmooth} with $\beta > 0$ and $q \in \RR$. 
@@
         \end{proof}
+        \begin{remark}
+            The sequence has explicit update formula: 
+            \begin{align*}
+                \alpha_k = 
+                \frac{1}{2}
+                \left(
+                    \alpha_{k - 1}\sqrt{\alpha_{k -1}^2 + 4 \rho_{k - 1}} - \alpha^2_{k - 1}
+                \right)
+            \end{align*}
+        \end{remark}
         % ======================================================================
@@
             Let the sequences $(x_k, y_k, v_k)$ satisfy GMAPG (Definition \ref{def:generic-mapg-ls}). 
-            If in addition, the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and it is initialized with $x_0=x_0 = T_{1/L_0, f, g}x_{-1}$ for some $x_{-1} \in\RR^n$ and there exists $x^+$ which is a minimizer of $F$.
+            If in addition, the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and, it is initialized with $x_0=x_0 = T_{1/L_0, f, g}x_{-1}$ for some $x_{-1} \in\RR^n$ and there exists $x^+$ which is a minimizer of $F$.
             Then, the convergence of gradient mapping $\Vert \mathcal G_{1/L_k}(y_k)\Vert$ is described by the sequence $(\beta)_{k \ge 0}$ where $\beta_0 = 1$ and for all $k \ge 1$:
@@
         \begin{proof}
-            The following intermediate results are in order for the proof. 
+            The following intermediate results will be used in the proof. 
+            We stated prior to the proof for a sleeker exposition. 
             \begin{enumerate}
-                \item[(a)]
+                \item[(a)] From Definition \ref{def:generic-mapg-ls}, the gradient mapping satisfies for all $k \ge 1$ that $\Vert \mathcal G_{1/L_k} y_k\Vert = L_k\alpha_k \Vert v_k - v_{k - 1}\Vert$.
+                \item[(b)] We have $(a_k)_{k \ge 1}$ satisfying $\forall k \ge 1$ that $(1 - \alpha_k)\rho_{k - 1} = \alpha_k^2/\alpha_{k - 1}^2$ from the statement hypothesis.
+We assumed $\alpha_0 = 0, \beta_0 = 1$, $x^+$ is a minimizer of $F$.
+Then using these it has for all $k \ge 0$ it has $\frac{\alpha_k}{\sqrt{\beta_k L_0}}\Vert x^+ - v_k\Vert \le \Vert x^+ - v_0\Vert$.
+                \item[(c)] The sequence $(\alpha_k)_{k \ge 0}$ has $(1 - \alpha_k)\rho_{k - 1} = \alpha_k^2/\alpha_{k - 1}^2$ from the statement hypothesis so $\alpha_k/\alpha_{k - 1} = \sqrt{\rho_{k - 1}(1 - \alpha_k)}$ for all $k \ge 1$.
+                \item[(d)] The definition of the sequence $(\beta_k)_{k \ge 0}$ stated in the statement hypothesis. 
             \end{enumerate}
+            From these intermediate results, the convergence can be derived. 
+            From (a) it has for all $k \ge 0$: 
+            \begin{align*}
+                \Vert \mathcal G_{L_k} y_k\Vert 
+                &= L_k\alpha_k \Vert v_k - v_{k - 1}\Vert
+                \\
+                &\le 
+                L_k\alpha_k(\Vert v_k - x^+\Vert + \Vert v_{k - 1} - x^+\Vert)
+                \\
+                &\underset{\text{(b)}}{\le} 
+                L_k \alpha_k \left(
+                    \frac{\sqrt{\beta_kL_0}}{\alpha_k}\Vert x^+ - v_0\Vert
+                    - 
+                    \frac{\sqrt{\beta_{k - 1}L_0}}{\alpha_{k - 1}}\Vert x^+ - v_0\Vert
+                \right) 
+                \\
+                &= L_k\sqrt{L_0} \left(
+                    \sqrt{\beta_k}
+                    - 
+                    \frac{\alpha_k\sqrt{\beta_{k - 1}}}{\alpha_{k - 1}}
+                \right)\Vert x^+ - v_0\Vert
+                \\
+                &= \sqrt{\beta_k L_0}L_k \left(
+                    1 - 
+                    \frac{\alpha_k}{\alpha_{k - 1}}\sqrt{\frac{\beta_{k - 1}}{\beta_k}}
+                \right)\Vert x^+ - v_0\Vert
+                \\
+                &\underset{\text{(d)}}{=} \sqrt{\beta_k L_0}L_k \left(
+                    1 - 
+                    \frac{\alpha_k}{\alpha_{k - 1}}
+                    \left((1 - \alpha_k)\max(1, \rho_{k - 1}L_k L_{k - 1}^{-1})\right)^{-1/2}
+                \right)\Vert x^+ - v_0\Vert
+                \\
+                &\underset{\text{(c)}}{=} 
+                \sqrt{\beta_k L_0}L_k \left(
+                    1 - 
+                    ((1 - \alpha_k)\rho_{k - 1})^{1/2}
+                    \left((1 - \alpha_k)\max(1, \rho_{k - 1}L_k L_{k - 1}^{-1})\right)^{-1/2}
+                \right)\Vert x^+ - v_0\Vert
+                \\
+                &= 
+                \sqrt{\beta_k L_0}L_k \left(
+                    1 - 
+                    \left(\rho_{k - 1}^{-1}\max(1, \rho_{k - 1}L_k L_{k - 1}^{-1})\right)^{-1/2}
+                \right)\Vert x^+ - v_0\Vert
+                \\
+                &=
+                \sqrt{\beta_k L_0}L_k \left(
+                    1 - 
+                    \max(\rho_{k - 1}^{-1}, L_k L_{k - 1}^{-1})^{-1/2}
+                \right)\Vert x^+ - v_0\Vert
+                \\
+                &= 
+                \sqrt{\beta_k L_0}L_k \left(
+                    1 - 
+                    \min(\rho_{k - 1}, L_k^{-1} L_{k - 1})^{1/2}
+                \right)\Vert x^+ - v_0\Vert. 
+            \end{align*}
+            Now, \textbf{let's proof intermediate results (a)}. 
+            From the definition of GMAPG it has 
+            \begin{align*}
+                y_k &= \alpha_k v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+                \iff 
+                v_{k - 1} = \alpha_k^{-1}(y_k - (1 - \alpha_k)x_{k - 1}). 
+            \end{align*}
+            Using the above, and definition of GMAPG, it yields 
+            \begin{align*}    
+                v_k - v_{k - 1} &= 
+                (x_{k - 1} + \alpha_k^{-1}(\tilde x_k - x_{k - 1})) - \alpha_k^{-1}(y_k - (1 - \alpha_k)x_{k - 1})
+                \\
+                &= 
+                x_{k - 1} + \alpha_k^{-1}(\tilde x_k - x_{k - 1})
+                - \alpha_k^{-1}y_k + (\alpha_k^{-1} - 1)x_{k - 1}
+                \\
+                &= \alpha_k^{-1}(\tilde x_k - x_{k - 1}) - \alpha_k^{-1}y_k + \alpha_k^{-1} x_{k - 1}
+                \\
+                &= \alpha_k^{-1}\tilde x_k - \alpha_k^{-1} y_k 
+                = \alpha^{-1}_k(\tilde x_k - y_k) = \alpha_k^{-1}(T_{L_k} y_k - y_k)
+                \\
+                &= -\alpha_k^{-1}L_k^{-1}(\mathcal G_{L_k}(y_k)). 
+            \end{align*}
+            \textbf{We now prove result (b)}. 
+            The base case $k = 1$ is verified by the assumption that $x_0 = v_0 = T_{L_0} x_{-1}$. 
+            Apply the proximal gradient inequality with $x^+$ as a minimizer it yields: 
+            \begin{align*}
+                0 &\le 
+                F(x^+) - F(T_{L_{-1}}x_{-1}) - \frac{L_0}{2}\Vert x^+ - T_{L_0}x_{-1}\Vert^2 + 
+                \frac{L_0}{2}\Vert x^+ - x_{-1}\Vert^2
+                \\
+                &= 
+                F(x^+) - F(x_0) - \frac{L_0}{2}\Vert x^+ - v_0\Vert^2 + 
+                \frac{L_0}{2}\Vert x^+ - x_{-1}\Vert^2
+                \\
+                &\le 
+                - \frac{L_0}{2}\Vert x^+ - v_0\Vert^2 + 
+                \frac{L_0}{2}\Vert x^+ - x_{-1}\Vert^2
+                \\
+                &= \frac{L_0}{2}\left(
+                    \Vert x^+ - x_{-1}\Vert- \Vert x^+ - v_0\Vert 
+                \right). 
+            \end{align*}
+            Because $\beta_0 = \alpha_0 = 1$, the base case holds. 
+            For all $k \ge 1$, we consider the convergence claim and use the assumption that $x^+$ is a minimizer of $F$ so, it has from Theorem \ref{thm:gmapg-ls-convergence} that 
+            \begin{align*}
+                0 &\le \frac{L_0\beta_k }{2}\Vert x^+ - x_{-1}\Vert^2 
+                - F(x_k) + F(x^+) - \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k\Vert^2
+                \\
+                &\le 
+                \frac{L_0\beta_k }{2}\Vert x^+ - x_{-1}\Vert^2 
+                - \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k\Vert^2
+                \\
+                &= \frac{\alpha_k^2L_k}{2}\left(
+                    \frac{\beta_k}{\alpha_k^2L_0}
+                    \Vert x^+ - x_{-1}\Vert^2 
+                    - \Vert x^+ - v_k\Vert^2
+                \right)
+                \\
+                \iff 
+                0 &\le 
+                \Vert x^+ - x_{-1}\Vert - \frac{\alpha_k}{\sqrt{\beta_k L_0}}\Vert x^+ - v_k\Vert. 
+            \end{align*}
         \end{proof}
@@
         There are several components to the GMAPG algorithm. 
-        This section introduces two variants of line search method used to enhance the accelerated proximal gradient methods in the literatures to demonstrate Definition \ref{def:generic-mapg-ls}. 
+        This section will introduce various type of implementations that can be fitted into GMAPG in Definition \ref{def:generic-mapg-ls}. 
         \begin{algorithm}[H]
+            {\small
             \begin{algorithmic}[1]\label{alg:armijo-ls}
@@
                     \textbf{Function ArmijoLS:}
-                    \begin{tabular}{lcl}
-                        $f : \RR^n \rightarrow \RR$ && Convex Lipschitz smooth\\ 
-                        $g: \RR^n \rightarrow \overline \RR$  &&  Convex function with Proximal operator\\ 
-                        $x \in \RR^n$ && Vector\\
-                        $v \in \RR^n$ && Vector\\
-                        $L \in \RR$ && $L > 0$\\
-                        $\alpha \in \RR$  && $\alpha \in (0, 1]$
+                    \begin{tabular}{ll}
+                        $f : \RR^n \rightarrow \RR$ & Convex Lipschitz smooth\\ 
+                        $g: \RR^n \rightarrow \overline \RR$  &  Convex function with Proximal operator\\ 
+                        $x \in \RR^n$ & Vector\\
+                        $v \in \RR^n$ & Vector\\
+                        $L \in \RR$ & $L > 0$\\
+                        $\alpha \in \RR$  & $\alpha \in (0, 1]$
                     \end{tabular}
@@
             \end{algorithmic}
+            }
         \end{algorithm}
         \begin{algorithm}[H]\label{alg:chambolle-btls}
+            {\small
             \begin{algorithmic}[1]
                 \STATE{\noindent
-                    \textbf{Function ChamBT}($f, g, x, v, L, \alpha, L_{\min}, \rho$)
+                    % \textbf{Function ChamBT}($f, g, x, v, L, \alpha, L_{\min}, \rho$)
+                    \textbf{Function ChamBT input: }
+                    \begin{tabular}{ll}
+                        $f:\RR^n \rightarrow \RR$ & Convex Lipschitz smooth\\ 
+                        $g:\RR^n \rightarrow \overline\RR$ & Convex with Proximal Operator\\ 
+                        $x\in \RR^n$ & Vector\\
+                        $v\in \RR^n$ & Vector\\
+                        $\alpha \in \RR$ & Vector\\
+                        $L\in \RR$ & Number, $L > 0$ \\
+                        $L_{\min} \in \RR$ & Number, $L_{\min} > 0$\\
+                        $\rho \in \RR$ & Number, $\rho \in (0, 1)$\\
+                    \end{tabular}
                 }
@@
             \end{algorithmic}
+            }
         \end{algorithm}
@@
                 \STATE{\noindent
-                    \textbf{Function BeckMono}($f, g, x, v, L, L_{\min}, \rho, \alpha$)
+                    % \textbf{Function BeckMono}($f, g, x, v, L, L_{\min}, \rho, \alpha$)
+                    \textbf{Function BeckMono Input:}
+                    \begin{tabular}{ll}
+                        $f: \RR^n \rightarrow \RR$ & \\
+                        $g: \RR^n \rightarrow \overline \RR$ & \\
+                        $\tilde x \in \RR^n$ & \\
+                        $x \in \RR^n$ & 
+                    \end{tabular}
                 }
@@
 
-    \section{Practical enhancement}
+    \section{Practical enhancement from the Nesterov's Monotone Variant}
         In this section, we provide results for the faster convergence rate of examples listed from the previous section. 
+    \section{Restarting with function values}
+    \section{Applying them to large scale LP}
     \section{Nonconvex convergence}
 
-    \section{Restarting with gradient and function values}
-
 \section{Primal Dual Lagrangian for LP}

### 2025-05-06 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
                 \left(
-                    F(x_0) - F(x^+) + \frac{L_0\alpha_0}{2} \Vert x^+ - v_k\Vert^2
+                    F(x_0) - F(x^+) + \frac{L_0\alpha_0}{2} \Vert x^+ - v_0\Vert^2
                 \right). 
@@
                 & \le 
-                \left(
-                    \prod_{i = 0}^{k - 1} (1 - \alpha_{i + 1})
-                    \max\left(1, \rho_i L_{i + 1}L_i^{-1}\right)
-                \right)
-                \frac{L_0}{2}\Vert x^+ - x_{-1}\Vert^2. 
+                \frac{\beta_kL_0}{2}\Vert x^+ - x_{-1}\Vert^2. 
             \end{align*}
@@
                 \\
-                &\underset{\text{(iii)}}{\le} 
+                &\hspace{-0.3em}\underset{\text{(iii)}}{\le} 
                 \alpha_k F(x^+) + (1 - \alpha_k) F(x_{k - 1}) - F(\tilde x_k)
@@
                 \\
-                &\underset{\text{(iv)}}{\le} 
+                &\hspace{-0.3em}\underset{\text{(iv)}}{\le} 
                 (1 - \alpha_k)(F(x_{k - 1}) - F(x^+)) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_{k - 1}\Vert^2
@@
             Let the sequences $(x_k, y_k, v_k)$ satisfy GMAPG (Definition \ref{def:generic-mapg-ls}). 
-            If in addition, the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and, it is initialized with $x_0=x_0 = T_{1/L_0, f, g}x_{-1}$ for some $x_{-1} \in\RR^n$ and there exists $x^+$ which is a minimizer of $F$.
+            If in addition, the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and, GMAPG is initialized with $v_0=x_0 = T_{1/L_0, f, g}(x_{-1})$ for any $x_{-1} \in\RR^n$ and there exists $x^+$ which is a minimizer of $F$.
             Then, the convergence of gradient mapping $\Vert \mathcal G_{1/L_k}(y_k)\Vert$ is described by the sequence $(\beta)_{k \ge 0}$ where $\beta_0 = 1$ and for all $k \ge 1$:
@@
             \begin{align*}
-                \Vert \mathcal G_{L_k} y_k\Vert &\le 
+                \Vert \mathcal G_{L_k} (y_k)\Vert &\le 
                 \sqrt{\beta_k}L_k L_0 \left(
@@
         \end{proof}
+        \begin{lemma}[specialized GMAPG momentum sequence]\;\label{lemma:gmapg-seq-bnd}\\
+            Suppose that the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 \in (0, 1]$ and for all $k \ge 1$, it satisfies $\alpha_{k - 1}^2\rho_{k - 1}(1 - \alpha_k) = \alpha_k^2$. 
+            Suppose that $(\beta_k)_{k \ge 0}$ is a sequence such that $\beta_0 = 1$ and for all $k \ge 1$ it's defined as: 
+            \begin{align*}
+                \beta_k := \prod_{i = 0}^{k - 1}(1 - \alpha_{i + 1}) \max\left(1, \rho_i L_{i + 1}L_i^{-1}\right). 
+            \end{align*}
+            If, we set $\rho_{k - 1} = L_{k}^{-1}L_{k - 1}$ such that $L_k >0$ for all $k \ge 1$, then for all $k \ge 1$ it has the inequality: 
+            \begin{align*}
+                \beta_k \le \left(
+                    1 + \frac{\alpha_0\sqrt{L_0}}{2}\sum_{i = 1}^{k} \sqrt{L_i^{-1}}
+                \right)^{-2}. 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            We state the following intermediate results needed to construct the proof. 
+            They will be proved at the end. 
+            \begin{enumerate}
+                \item[(a)] $(\beta_k)_{k \ge 0}$ is monotone decreasing and it's strictly larger than zero. 
+                \item[(b)] Because $\rho_{k}L_{k + 1}L_k = 1$ for all $k \ge 0$, the definition of $(\beta_k)_{k\ge 0}$ simplifies and $\beta_k = (\alpha_k^2/\alpha_0^2)(L_k/L_0)$.
+As a consequence it also gives for all $k \ge 1$ that:
+                \begin{align*}
+                    \alpha_k^2 &= \alpha_0^2\beta_kL_0L_k^{-1},
+                    \\
+                    \alpha_k &= 1 - \beta_k / \beta_{k - 1}. 
+                \end{align*}
+            \end{enumerate}
+            Starting with results (b), and combine the two equality it gives for all $k \ge 1$ the equality 
+            \begin{align*}
+                0 &=
+                (1 - \beta_k/\beta_{k - 1})^2 - \alpha_0^2L_0L_k^{-1}\beta_k 
+                \\
+                \iff 
+                0 &= 
+                (1 - \beta_k/\beta_{k - 1}) - \alpha_0\sqrt{L_0L_k^{-1}\beta_k}
+                \\
+                \iff 
+                0 &= 
+                (\beta_k^{-1} - \beta_{k - 1}^{-1}) - \alpha_0 \sqrt{L_0 L_k^{-1}\beta_k^{-1}}
+                \\
+                &= \left(
+                    \sqrt{\beta_k^{-1}} + \sqrt{\beta_{k - 1}^{-1}}
+                \right)\left(
+                    \sqrt{\beta_k^{-1}} - \sqrt{\beta_{k - 1}^{-1}}
+                \right)
+                - \alpha_0 \sqrt{L_0L_k^{-1}\beta_k^{-1}}
+                \\
+                &\underset{\text{(a)}}{\le} 
+                2\sqrt{\beta_k^{-1}}\left(
+                    \sqrt{\beta_k^{-1}} - \sqrt{\beta_{k - 1}^{-1}}
+                \right) - \alpha_0 \sqrt{L_0L_k^{-1}\beta_k^{-1}}
+                \\
+                \iff
+                0 &\le 
+                2\left(
+                    \sqrt{\beta_k^{-1}} - \sqrt{\beta_{k - 1}^{-1}} 
+                \right) - \alpha_0 \sqrt{L_0L_k^{-1}}. 
+            \end{align*}
+            Since this is true for all $k \ge 1$, taking a telescoping sum of the above series gives
+            \begin{align*}
+                0 &\le 
+                \left(
+                    \sum_{i = 1}^{k} \sqrt{\beta_i^{-1}} - \sqrt{\beta_{i - 1}^{-1}}
+                \right)
+                - \sum_{i = 1}^{k} \frac{\alpha_0}{2} \sqrt{L_0L_k^{-1}}
+                \\
+                &= 
+                \sqrt{\beta_k^{-1}} - \sqrt{\beta_0^{-1}} 
+                - \frac{\alpha_0\sqrt{L_0}}{2}\sum_{i = 1}^{k} \sqrt{ L_k^{-1}}
+                \\
+                &= 
+                \sqrt{\beta_k^{-1}} - 1
+                - \frac{\alpha_0\sqrt{L_0}}{2}\sum_{i = 1}^{k} \sqrt{ L_k^{-1}}. 
+            \end{align*}
+            Therefore, transforming the inequality it has: 
+            \begin{align*}
+                \beta_k &\le 
+                \left(
+                    1 + \frac{\alpha_0\sqrt{L_0}}{2}\sum_{i = 1}^{k} \sqrt{ L_k^{-1}}
+                \right)^{-2}. 
+            \end{align*}
+            \textbf{Let's now justify (a)}.
+            When $\rho_{i} = L_{i + 1}L_i^{-1}$, the big product simplifies and, it has: 
+            \begin{align*}
+                \beta_k &= \prod_{i = 0}^{k - 1}(1 - \alpha_{i + 1}) 
+                = (1 - \alpha_k)\beta_{k - 1}. 
+            \end{align*}
+            Since $\alpha_k \in (0, 1)$, $\beta_k$ is monotonically decreasing. 
+            \textbf{To see (b)}, it has from the above which also justifies $1 - \alpha_k = \beta_k / \beta_{k - 1}$. 
+            Recall that sequence $(\alpha_k)_{k \ge 0}$ has $\forall k \ge 1$ that $\alpha_{k - 1}^2\rho_{k - 1}(1 - \alpha_k) = \alpha_k^2$, using it we can simplify the product for $\beta_k$, it follows that
+            \begin{align*}
+                \beta_k &= \prod_{i = 0}^{k - 1}\left(
+                    1 - \alpha_{i + 1}
+                \right)
+                = 
+                \prod_{i = 1}^{k}\alpha_i^2\alpha_{i - 1}^{-2}\rho_{i - 1}^{-1}
+                = 
+                \prod_{i = 1}^{k}\alpha_i^2\alpha_{i - 1}^{-2} L_i^{-1}L_{i - 1}
+                \\
+                &= \left(
+                    \frac{\alpha_k^2\alpha_{k - 1}^2\ldots \alpha_1^2}
+                    {\alpha_{k -1}^2\alpha_{k - 2}^2\ldots \alpha_0^2}
+                \right)\left(
+                    \frac{L_kL_{k - 1}\ldots L_1}{L_{k - 1}L_{k - 1}\ldots L_0}
+                \right)
+                = \frac{\alpha_k^2}{\alpha_0^2}\frac{L_k}{L_0}. 
+            \end{align*}
+            Rearranging it gives: $\alpha_0^2L_0 \beta_kL_k^{-1} = \alpha_k^2$.
+        \end{proof}
+        \begin{remark}
+            A simpler upper bound is more useful in practice. 
+            For all $k \ge 1$ let $\hat L = \max_{i = 0, 1, \ldots, k} L_k$ then 
+            \begin{align*}
+                \beta_k 
+                &\le \left(
+                    1 + 
+                    \frac{\alpha_0 \sqrt{L_0}}{2}\sum_{i = 1}^{k}\sqrt{\hat L^{-1}}
+                \right)^{-2}
+                \le \left(
+                    1 + \frac{1}{2}\alpha_0 \sqrt{L_0}k\sqrt{\hat L^{-1}}
+                \right)^{-2}
+                \\
+                &= \left(
+                    1 + \frac{k\alpha_0\sqrt{L_0 \hat L^{-1}}}{2}
+                \right)^{-2} = L^{-1}_0\hat L\left(
+                    \sqrt{L_0^{-1}\hat L} + \frac{k\alpha_0}{2}
+                \right)^{-2}
+                \\
+                &\le 
+                L^{-1}_0\hat L\left(
+                    1 + \frac{k\alpha_0}{2}
+                \right)^{-2} 
+                = \frac{4\hat L}{L_0(2 + k \alpha_0)^2}. 
+            \end{align*}
+            This simplifies the convergence claim back in Theorem \ref{thm:gmapg-ls-convergence}. 
+        \end{remark}
+        \begin{theorem}[specialized GMAPG convergence rate]
+
+        \end{theorem}
+
     \section{Algorithmic description of GMAPG}
@@
         % ======================================================================
-        \begin{example}[Nesterov's monotone scheme with generic line search]\;\\\vspace{-1em}
+        \begin{example}[Nesterov's monotone scheme with generic line search]\;\\
+            The following is (2.2.32) in Nesterov's book, phrased in our GMAPG framework. 
             \begin{algorithm}\label{alg:nesterov-mono-generic-ls}
@@
     \section{Practical enhancement from the Nesterov's Monotone Variant}
-        In this section, we provide results for the faster convergence rate of examples listed from the previous section. 
+        Firstly, we will introduce some theories in for nonconvex functions. 
+        The following assumption will characterize the full scope of discussion in nonconvexity objective function.
+
     \section{Restarting with function values}

### 2025-05-07 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
     Notations in this chapter are not shared, and they are for this chapter only. 
-    % ===================================================================================
+    % ==========================================================================
     % BREGMAN DIV DEFINITION 
-    % ===================================================================================
+    % ==========================================================================
     \begin{definition}[Bregman Divergence]\label{def:bregman-div}
@@
             \begin{align*}
-                0 &\le F(z) - F(\bar x) + \frac{L}{2}\Vert z - x\Vert^2 - \frac{L}{2}\Vert^2 z - \bar x\Vert^2. 
+                0 &\le F(z) - F(\bar x) + \frac{L}{2}\Vert z - x\Vert^2 - \frac{L}{2}\Vert z - \bar x\Vert^2. 
             \end{align*}
@@
             \begin{align*}
-                \Vert \mathcal G_{L_k} y_k\Vert 
+                \Vert \mathcal G_{1/L_k} y_k\Vert 
                 &= L_k\alpha_k \Vert v_k - v_{k - 1}\Vert
@@
                 \\
-                &= -\alpha_k^{-1}L_k^{-1}(\mathcal G_{L_k}(y_k)). 
+                &= -\alpha_k^{-1}L_k^{-1}(\mathcal G_{1/L_k}(y_k)). 
             \end{align*}
@@
             A simpler upper bound is more useful in practice. 
-            For all $k \ge 1$ let $\hat L = \max_{i = 0, 1, \ldots, k} L_k$ then 
+            For all $k \ge 1$ let $\hat L_k = \max_{i = 0, 1, \ldots, k} L_i$ then 
             \begin{align*}
@@
                     1 + 
-                    \frac{\alpha_0 \sqrt{L_0}}{2}\sum_{i = 1}^{k}\sqrt{\hat L^{-1}}
+                    \frac{\alpha_0 \sqrt{L_0}}{2}\sum_{i = 1}^{k}\sqrt{\hat L^{-1}_k}
                 \right)^{-2}
                 \le \left(
-                    1 + \frac{1}{2}\alpha_0 \sqrt{L_0}k\sqrt{\hat L^{-1}}
+                    1 + \frac{1}{2}\alpha_0 \sqrt{L_0}k\sqrt{\hat L^{-1}_k}
                 \right)^{-2}
@@
                 &= \left(
-                    1 + \frac{k\alpha_0\sqrt{L_0 \hat L^{-1}}}{2}
+                    1 + \frac{k\alpha_0\sqrt{L_0 \hat L^{-1}_k}}{2}
                 \right)^{-2} = L^{-1}_0\hat L\left(
-                    \sqrt{L_0^{-1}\hat L} + \frac{k\alpha_0}{2}
+                    \sqrt{L_0^{-1}\hat L_k} + \frac{k\alpha_0}{2}
                 \right)^{-2}
@@
                 &\le 
-                L^{-1}_0\hat L\left(
+                L^{-1}_0\hat L_k\left(
                     1 + \frac{k\alpha_0}{2}
                 \right)^{-2} 
-                = \frac{4\hat L}{L_0(2 + k \alpha_0)^2}. 
+                = \frac{4\hat L_k}{L_0(2 + k \alpha_0)^2}. 
             \end{align*}
             This simplifies the convergence claim back in Theorem \ref{thm:gmapg-ls-convergence}. 
+            The above inequality would work the same if we set: 
+            \begin{align*}
+                \hat L_k &= \max\left(
+                    L_0, \frac{1}{k} \sum_{i = 1}^{k} \sqrt{L_i^{-1}}
+                \right). 
+            \end{align*}
         \end{remark}
@@
                 \STATE{\noindent
-                    % \textbf{Function BeckMono}($f, g, x, v, L, L_{\min}, \rho, \alpha$)
                     \textbf{Function BeckMono Input:}
@@
                     \end{tabular}
+
                 }
+                \STATE{\textbf{Return: } $x^+$}
                 \caption{Beck's monotone routine}
@@
                             }
-                            \STATE{$\tilde x_{k + 1} := T_{L_0^{-1}}y_k$.}
+                            \STATE{$\tilde x_{k + 1} := T_{L_k^{-1}}y_k$.}
                         \ENDIF
@@
         Firstly, we will introduce some theories in for nonconvex functions. 
+        This is necessary because Nesterov's monotone variants can adapt to weakly convex objective functions. 
         The following assumption will characterize the full scope of discussion in nonconvexity objective function. 
-
+        \begin{definition}[nonconvex Nesterov's monotone scheme]\label{def:nes-monotone-scheme}
+
+        \end{definition}
     \section{Restarting with function values}
     \section{Applying them to large scale LP}
-    \section{Nonconvex convergence}
 

### 2025-05-08 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, new stuff

@@
     \section{FISTA made simple}
-        Most literatures overcomplicate the proofs and the matters regarding FISTA algorithm and its convergence rate. 
+        We make the proofs for FISTA  with common enhancement technique available in simple proofs. 
         We showcase the theories using a generic similar triangle representations of the algorithm which tremendously simplifies the arguments. 
@@
             \begin{align*}
-                \Vert \mathcal G_{L_k} (y_k)\Vert &\le 
+                \Vert \mathcal G_{1/L_k} (y_k)\Vert &\le 
                 \sqrt{\beta_k}L_k L_0 \left(
@@
                     \frac{\sqrt{\beta_kL_0}}{\alpha_k}\Vert x^+ - v_0\Vert
-                    - 
+                    +
                     \frac{\sqrt{\beta_{k - 1}L_0}}{\alpha_{k - 1}}\Vert x^+ - v_0\Vert
@@
                     \sqrt{\beta_k}
-                    - 
+                    +
                     \frac{\alpha_k\sqrt{\beta_{k - 1}}}{\alpha_{k - 1}}
@@
                 &= \sqrt{\beta_k L_0}L_k \left(
-                    1 - 
+                    1 +
                     \frac{\alpha_k}{\alpha_{k - 1}}\sqrt{\frac{\beta_{k - 1}}{\beta_k}}
@@
                 &\underset{\text{(d)}}{=} \sqrt{\beta_k L_0}L_k \left(
-                    1 - 
+                    1 +
                     \frac{\alpha_k}{\alpha_{k - 1}}
@@
                 \sqrt{\beta_k L_0}L_k \left(
-                    1 - 
+                    1 +
                     ((1 - \alpha_k)\rho_{k - 1})^{1/2}
@@
                 \sqrt{\beta_k L_0}L_k \left(
-                    1 - 
+                    1 +
                     \left(\rho_{k - 1}^{-1}\max(1, \rho_{k - 1}L_k L_{k - 1}^{-1})\right)^{-1/2}
@@
                 \sqrt{\beta_k L_0}L_k \left(
-                    1 - 
+                    1 +
                     \max(\rho_{k - 1}^{-1}, L_k L_{k - 1}^{-1})^{-1/2}
@@
                 \sqrt{\beta_k L_0}L_k \left(
-                    1 - 
+                    1 +
                     \min(\rho_{k - 1}, L_k^{-1} L_{k - 1})^{1/2}
@@
         \end{remark}
-        \begin{theorem}[specialized GMAPG convergence rate]
-
+        \begin{theorem}[specialized GMAPG convergence rate]\label{thm:gmapg-specialized-convergence}
+            Suppose that $F = f + g$ satisfy Assumption \ref{ass:standard-fista}. 
+            Let the sequence $(x_k, v_k, v_k)$ satisfy GMAPG, definition \ref{def:generic-mapg-ls} and, assume that the GMAPG is initialized by $x_0 = v_0 = T_{1/L_0}(x_{-1})$ and, assume $\rho_{k - 1} = L_{k}^{-1}L_{k}$, $\alpha_0 = 1$ so the sequence $(\alpha_k)_{k \ge 0}$ satisfies for all $k\ge 1$: $\alpha_{k - 1}^2L_k^{-1}L_{k - 1}(1 - \alpha_k) = \alpha_k^2$.
+            Let $x^+$ be a minimizer of $F$, define 
+            \begin{align*}
+                \hat L_k = \max\left(
+                    L_0, \frac{1}{k}\sum_{i = 1}^{k} \sqrt{L_i^{-1}}
+                \right). 
+            \end{align*}
+            Then, we have convergence claim: 
+            \begin{enumerate}
+                \item \begin{align*}
+                    F(x_k) - F(x^+) + \frac{L_k\alpha_k}{2}\Vert x^+ - v_k\Vert^2 \le 
+                    \frac{2\hat L_k}{(2 + k)^2}\Vert x^+ - x_{-1}\Vert^2.
+                \end{align*}
+                \item 
+                \begin{align*}
+                    \Vert \mathcal G_{1/L_k}(y_k)\Vert \le 
+                    \frac{2\hat L_k L_k}{2 + k}
+                    \left(
+                        1 - L_k^{-1/2}L_{k - 1}^{1/2}
+                    \right)
+                    \Vert x^+ - v_0\Vert. 
+                \end{align*}
+            \end{enumerate}
         \end{theorem}
+        \begin{proof}
+            To see (i), use \ref{lemma:gmapg-seq-bnd} and the remark with Theorem \ref{thm:gmapg-ls-convergence} because the assumptions of $x^+, (\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is the same.
+            To see (ii), the convergence claim from \ref{thm:gmapg-generic-gradmap-convergence} simplifies with $\hat L_k \ge L_0$ and, it has 
+            \begin{align*}
+                \Vert \mathcal G_{1/L_k}(y_k) \Vert
+                &\le 
+                \left(
+                    \frac{2\sqrt{\hat L_kL_0}L_k}{2 + k}
+                \right)\left(
+                    1 + \min(\rho_{k - 1}, L_k^{-1}L_{k - 1})^{1/2}
+                \right)\Vert x^+ - v_0\Vert
+                \\
+                &= 
+                \left(
+                    \frac{2\sqrt{\hat L_kL_0}L_k}{2 + k}
+                \right)\left(
+                    1 + L_k^{-1/2}L_{k - 1}^{1/2}
+                \right)\Vert x^+ - v_0\Vert
+                \\
+                &\le 
+                \left(
+                    \frac{2\hat L_k L_k}{2 + k}
+                \right)\left(
+                    1 + L_k^{-1/2}L_{k - 1}^{1/2}
+                \right)\Vert x^+ - v_0\Vert. 
+            \end{align*}
+        \end{proof}
 

### 2025-05-09 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, today's changes

@@
     \begin{assumption}[smooth plus nonsmooth]\label{ass:smooth-add-nonsmooth}
-        Let $F = f+ g$ where $f:\RR^n \rightarrow \overline \RR$ is differentiable and there exists $q\in \RR$ such that $g - q/2\Vert \cdot\Vert^2$ is convex.
+        Let $F = f+ g$ where $f:\RR^n \rightarrow \overline \RR$ is differentiable and there exists $q\in \RR$ such that $g - \mu/2\Vert \cdot\Vert^2$ is convex.
     \end{assumption}
@@
     \begin{theorem}[weakly convex generic proximal gradient inequality]\;\label{thm:pg-ineq-wcnvx-generic}\\
-        Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-add-nonsmooth} with $\beta > 0$ and $q \in \RR$. 
+        Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-add-nonsmooth} with $\beta > 0$ and $\mu \in \RR$. 
         Then for all $x \in \RR^n, z \in \RR^n$, define $\bar x = T_{\beta^{-1}, f, g}(x)$, it has: 
         \begin{align*}
-            \frac{q}{2}\Vert z - \bar x\Vert^2 
+            \frac{\mu}{2}\Vert z - \bar x\Vert^2 
             &\le 
@@
             \mathbf 0 
-            &\in \partial g(x^+) + \nabla f(x) + \beta(x^+ - x)
+            &\in \partial g(\bar x) + \nabla f(x) + \beta(\bar x - x)
             \\
@@
             \partial g(x^+) &\ni
-            - \nabla f(x) - \beta(x^+ - x). 
+            - \nabla f(x) - \beta(\bar x - x). 
         \end{align*}
@@
         \begin{align*}
-            \frac{q}{2}\Vert z - \bar x\Vert^2 
+            \frac{\mu}{2}\Vert z - \bar x\Vert^2 
             &\le 
@@
     \begin{theorem}[convex proximal gradient inequality]\label{thm:cnvx-pg-ineq}
-        Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-add-nonsmooth} such that $q = \mu_g \ge 0$, $\beta \ge L_f$. 
+        Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-add-nonsmooth} such that $\mu = \mu_g \ge 0$, $\beta \ge L_f$. 
         In addition, suppose that $f:\RR^n\rightarrow \RR$ has $L_f$ Lipschitz continuous gradient, and it's $\mu_f \ge 0$ strongly convex. 
@@
     In this chapter, we will go through the details of these enhancements of FISTA and discuss why they are important in theories, and in practice. 
-    \section{FISTA made simple}
-        We make the proofs for FISTA  with common enhancement technique available in simple proofs. 
-        We showcase the theories using a generic similar triangle representations of the algorithm which tremendously simplifies the arguments. 
-        \begin{assumption}[the standard FISTA setting]\label{ass:standard-fista}
+    \section{Preliminaries}
+        This section introduces the full scope of the theories in our analysis. 
+        \subsection{smooth plus nonsmooth weakly convex}
+            \begin{assumption}[sum of weakly convex smooth and nonsmooth]\;\label{ass:sum-of-wcnvx}\\
+                Let $F: \RR^n \rightarrow \overline\RR:= f + g$ such that $f, g$ satisfy 
+                \begin{enumerate}
+                    \item $f$ is $L$ Lipschitz smooth and $q_f$ weakly convex. 
+                    \item $g$ is $L$ Lipschitz smooth and $q_g$ weakly convex. 
+                \end{enumerate}
+            \end{assumption}
+            \begin{definition}[weakly convex function]\;\label{def:wcnvx-fxn}\\
+                Let $f: \RR^n \rightarrow\overline \RR$ be an l.s.c proper function. 
+                We define $F$ to be $q$ weakly convex if there exists $q \in \RR$ such that the function $F + q/2\Vert \cdot\Vert^2$ is a convex function and $q$ is the infimum of all such possible parameters.
+            \end{definition}
+            \begin{definition}[gradient mapping]
+                Suppose $F = f + g$ satisfies Assumption \ref{ass:sum-of-wcnvx}, define the gradient mapping for all $x \in \RR^n$
+                \begin{align*}
+                    \mathcal G_{\beta^{-1}, f, g}(x) = \beta(x - T_{\beta^{-1}, f, g}(x)). 
+                \end{align*}
+                If $f, g$ are clear in the context then we omit subscript and present $\mathcal G_\beta$. 
+            \end{definition}
+            \begin{lemma}[weakly convex monotone descent]\;\label{lemma:mono-wcnvx-descent}\\
+                Let $F = f + g$ satisfies Assumption \ref{ass:sum-of-wcnvx}. 
+                Let $\bar x = T_{\beta, f, g}(x)$. 
+                Then, for all $x \in \RR^n$, it has the following inequality: 
+                $$
+                \begin{aligned}
+                    0 \le F(x) - F(\bar x) - (\beta - q/2 - L/2)\Vert x - \bar x\Vert^2. 
+                \end{aligned}
+                $$
+                And descent is possible when $\beta \ge (L + q)/2$. 
+                The maximum amount of descent is achieved when $\beta = L + q$. 
+            \end{lemma}
+            \begin{proof}
+                Use Theorem \ref{thm:pg-ineq-wcnvx-generic}. 
+            \end{proof}
+        \subsection{smooth plus nonsmooth convex}
+            The following assumption is strictly stronger than \ref{ass:sum-of-wcnvx}. 
+            \begin{assumption}[convex smooth and nonsmooth]\label{ass:standard-fista}
                 Let $F = f + g$ where $f:\RR^n\rightarrow \overline \RR$ is $L$ Lipschitz smooth, $g$ is convex. 
@@
             \end{assumption}
-        Specializing Theorem \ref{thm:cnvx-pg-ineq}, we have the following lemma: 
             \begin{lemma}[proximal gradient inequality]
@@
             \end{proof}
-        \begin{definition}[gradient mapping]
-            Suppose $F = f + g$ satisfies Assumption \ref{ass:standard-fista}, define the gradient mapping for all $x \in \RR^n$
-            \begin{align*}
-                \mathcal G_{\beta^{-1}, f, g}(x) = \beta(x - T_{\beta^{-1}, f, g}(x)). 
-            \end{align*}
-        \end{definition}
-        If $f, g$ are clear in the context then we simply omit subscript and present $\mathcal G_\beta$. 
+
+    \section{FISTA made simple}
+        We make the proofs for FISTA  with common enhancement technique available in simple proofs. 
+        We showcase the theories using a generic similar triangle representations of the algorithm which tremendously simplifies the arguments.
+
         The following definition can capture monotone variants of FISTA with line search, including backtracking strategies. 
@@
         ``MAPG'' stands for monotone accelerated gradient. 
-        We refer to ``Generic Monotone Accelerated Proximal Gradient with line search" as ``GMAPG LS''. 
-        \begin{definition}[GMAPG LS]\label{def:generic-mapg-ls}\;\\ 
-            Initialize any $x_0, v_0 \in \RR^n, \alpha_0 = 1, L_0 \in \RR$ such that
-            \begin{align*}
-                D_f\left(T_{L_0^{-1}} (y_0)\right) 
-                &\le \frac{L_0}{2}\left\Vert T_{L_0^{-1}}(x_0) - y_0\right\Vert^2. 
-            \end{align*}
+        We refer to ``Generic Monotone Accelerated Proximal Gradient with line search" as ``GMAPG''. 
+        \begin{definition}[GMAPG]\label{def:generic-mapg-ls}\;\\ 
+            Initialize any $x_0, v_0 \in \RR^n$. 
             Let $(\alpha_k)_{k \ge 0}$ be a sequence such that $\alpha_k \in (0, 1) \;\forall k \ge 0$ and $\alpha_0 \in (0, 1]$. 
@@
         % ======================================================================
-        % THEOREM | GENERIC GMAPG LS CONVERGENCE IN FXN VAL
+        % THEOREM | GENERIC GMAPG CONVERGENCE IN FXN VAL
         % ======================================================================
-        \begin{theorem}[generic GMAPG LS convergence]\; \label{thm:gmapg-ls-convergence}\;\\
+        \begin{theorem}[generic GMAPG convergence]\; \label{thm:gmapg-ls-convergence}\;\\
             Let $F = f + g$ satisfy Assumptions \ref{ass:standard-fista}. 
@@
             \end{align*}
-            If in addition, the algorithm is initialized with $\alpha_0 = 1, x_0 = v_0 = T_{L_{0}}x_{-1} \in \text{dom}\; F$ and $x^+$ is a minimizer of $F$, then the convergence rate simplifies: 
+            If in addition, the algorithm is initialized with $L_0 \ge L$, $\alpha_0 = 1, x_0 = v_0 = T_{L_{0}}x_{-1} \in \text{dom}\; F$ and $x^+$ is a minimizer of $F$.
+            Then, the convergence rate simplifies: 
             \begin{align*}
@@
                 \item $F$ is convex and hence $F(z_k) \le \alpha_k F(x^+) + (1 - \alpha_k)F(x_{k - 1})$. 
-                \item $F(x_k) \le F(\tilde x_k)$ which is true by definition of GMAPG LS. 
+                \item $F(x_k) \le F(\tilde x_k)$ which is true by definition of GMAPG. 
             \end{enumerate}
@@
         % ======================================================================
-        % THEOREM | GENERIC GMAPG LS GRADIENT MAPPING CONVERGENCE
+        % THEOREM | GENERIC GMAPG GRADIENT MAPPING CONVERGENCE
         % ======================================================================
-        \begin{theorem}[generic GMAPG LS gradient mapping convergence]\;\label{thm:gmapg-generic-gradmap-convergence}\\
+        \begin{theorem}[generic GMAPG gradient mapping convergence]\;\label{thm:gmapg-generic-gradmap-convergence}\\
             Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista}. 
             Let the sequences $(x_k, y_k, v_k)$ satisfy GMAPG (Definition \ref{def:generic-mapg-ls}). 
-            If in addition, the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and, GMAPG is initialized with $v_0=x_0 = T_{1/L_0, f, g}(x_{-1})$ for any $x_{-1} \in\RR^n$ and there exists $x^+$ which is a minimizer of $F$.
+            If in addition, the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and, GMAPG is initialized with $L_0 \ge L$, $v_0=x_0 = T_{1/L_0, f, g}(x_{-1})$ for any $x_{-1} \in\RR^n$ and there exists $x^+$ which is a minimizer of $F$.
             Then, the convergence of gradient mapping $\Vert \mathcal G_{1/L_k}(y_k)\Vert$ is described by the sequence $(\beta)_{k \ge 0}$ where $\beta_0 = 1$ and for all $k \ge 1$:
@@
                     % $(f, g, x, v, L, \alpha, \_, \_)$
-                    \textbf{Function ArmijoLS:}
-                    \begin{tabular}{ll}
+                    \textbf{Function ArmijoLS: }
+                    \begin{tabular}{|ll}
                         $f : \RR^n \rightarrow \RR$ & Convex Lipschitz smooth\\ 
@@
                         $L \in \RR$ & $L > 0$\\
-                        $\alpha \in \RR$  & $\alpha \in (0, 1]$
-                    \end{tabular}
+                        $\alpha \in \RR$  & $\alpha \in (0, 1]$\\
+                        $\cdots$ & Ignore extra inputs
+                    \end{tabular}\vspace{0.5em}
                 }
@@
         \end{algorithm}
-        \begin{algorithm}[H]\label{alg:chambolle-btls}
+        \begin{algorithm}[H]
             {\small
-            \begin{algorithmic}[1]
+            \begin{algorithmic}[1]\label{alg:chambolle-btls}
                 \STATE{\noindent
@@
                     \textbf{Function ChamBT input: }
-                    \begin{tabular}{ll}
+                    \begin{tabular}{|ll}
                         $f:\RR^n \rightarrow \RR$ & Convex Lipschitz smooth\\ 
@@
                         $v\in \RR^n$ & Vector\\
+                        $L\in \RR$ & Number, $L > 0$ \\
                         $\alpha \in \RR$ & Vector\\
-                        $L\in \RR$ & Number, $L > 0$ \\
                         $L_{\min} \in \RR$ & Number, $L_{\min} > 0$\\
                         $\rho \in \RR$ & Number, $\rho \in (0, 1)$\\
-                    \end{tabular}
+                    \end{tabular}\vspace{0.5em}
                 }
@@
         \end{algorithm}
-        \begin{algorithm}[H]\label{alg:beck-mono}
-            \begin{algorithmic}[1]
+        % BECK'S MONO ----------------------------------------------------------
+        \begin{algorithm}[H]
+            \begin{algorithmic}[1]\label{alg:beck-mono}
                 \STATE{\noindent
-                    \textbf{Function BeckMono Input:}
-                    \begin{tabular}{ll}
+                    \textbf{Function BeckMono Inputs: }
+                    \begin{tabular}{|ll}
                         $f: \RR^n \rightarrow \RR$ & \\
@@
                         $\tilde x \in \RR^n$ & \\
-                        $x \in \RR^n$ & 
-                    \end{tabular}
-
-                }
-                \STATE{\textbf{Return: } $x^+$}
+                        $x \in \RR^n$ & \\
+                        $\rho$ & Number $\rho \in (0, 1)$
+                    \end{tabular}\vspace{0.5em}
+                }
+                \STATE{\noindent
+                    $x^+ = \argmin \{(f + g)(z): z \in \{\tilde x, x\}\}$. 
+                }
+                \STATE{\textbf{Return: } $x^+, \eta$}
                 \caption{Beck's monotone routine}
@@
         \end{algorithm}
-        \begin{algorithm}[H]\label{alg:nes-mono}
+        % NES'S MONO -----------------------------------------------------------
+        \begin{algorithm}[H]
             \begin{algorithmic}[1]
                 \STATE{\noindent
-                    \textbf{Function NesMono}($f, g, x, v, L, L_{\min}, \rho, \alpha$)
-                }
+                    \textbf{Function NesMono Inputs: }
+                    \begin{tabular}{|ll}
+                        $f:\RR^n\rightarrow \RR$ & Lipschitz Smooth \\ 
+                        $g: \RR^n \rightarrow \overline \RR$ & Weakly Convex \\ 
+                        $\tilde x \in \RR^n$ & Vector \\ 
+                        $x \in \RR^n$ & Vector \\
+                        $\eta \in \RR$ & Number $\eta > 0$\\
+                    \end{tabular}\vspace{0.5em}
+                }
+                \STATE{\noindent
+                    $\hat y := \argmin\{(f + g)(z), x \in \{\tilde x, x\}\}$. 
+                }
+                \STATE{\noindent
+                    $x^+ := T_{1/\eta}(\hat y)$. 
+                }
+                \WHILE{$F(x^+) - F(\hat y) > -1/(2\eta)\Vert \mathcal G_{1/\eta}(\hat y)\Vert^2$}
+                    \STATE{$\eta := 2\eta$. }
+                \ENDWHILE
+                \STATE{\textbf{return: } $x^+, \eta$ }
                 \caption{Nesterov's monotone routine}
-            \end{algorithmic}
+            \end{algorithmic}\label{alg:nes-mono}
         \end{algorithm}
-        \begin{algorithm}[H]\label{alg:gmapg}
+        % GMAPG ----------------------------------------------------------------
+        \begin{algorithm}[H]
             \begin{algorithmic}[1]
                 \STATE{\noindent
-                    \textbf{Function GMAPG} (
-                        $f, g, x_{-1}, L_0, r_{\min}, \text{Exit condition: }\mathbb E_\chi$
-                    )
-                }
-            \end{algorithmic}
+                    \textbf{Function GMAPG Inputs: }
+                    \begin{tabular}{|ll}
+                        $f:\RR^n \rightarrow \RR$ &  Weakly Convex Lipschitz Smooth \\
+                        $g: \RR^n \rightarrow \overline\RR$ & Weakly Convex \\ 
+                        $L\in \RR$ & $L > 0$\\ 
+                        $r_{\min} $ & $r_{\min} \in (0, 1)$ \\ 
+                        $\rho \in \RR$ & $\rho \in (0, 1)$ \\
+                        $N_{\min}\in \N$ & $N \ge 1$ \\
+                        $N \in \N$ & $N \ge N_{\min}$ \\
+                        $\mathbb L_{\mathcal S}$ \\ Algorithm \ref{alg:armijo-ls} or \ref{alg:chambolle-btls}
+                    \end{tabular}
+                }
+                \STATE{\textbf{Return: }}
             \caption{GMAPG with Chambolle's backtracking}
+            \end{algorithmic}\label{alg:gmapg}
         \end{algorithm}
@@
             We now demonstrate that Algorithm \ref{alg:mfista-armijo} is a special case of Definition \ref{def:generic-mapg-ls}.
-            Let's consider $y_{k + 1}$ produced the GMAPG LS. 
+            Let's consider $y_{k + 1}$ produced the GMAPG. 
             If $x_k = x_{k - 1}$ then replacing all instance of $x_k$ by $x_{k - 1}$ it has: 
@@
         The following assumption will characterize the full scope of discussion in nonconvexity objective function.
-        \begin{definition}[nonconvex Nesterov's monotone scheme]\label{def:nes-monotone-scheme}
+
+        \begin{definition}[nonconvex Nesterov's monotone scheme]\;\label{def:nes-monotone-scheme}\\
 

### 2025-05-09 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
             \end{assumption}
+            \begin{remark}
+                If a function is $L$ smooth, it also be $L$ weakly convex. 
+                Here we defined $q_f$ because the actual weakly convex constant may be much smaller than $L$, and it is true in the case when $g$ is in fact convex.  
+            \end{remark}
             \begin{definition}[weakly convex function]\;\label{def:wcnvx-fxn}\\
                 Let $f: \RR^n \rightarrow\overline \RR$ be an l.s.c proper function. 
-                We define $F$ to be $q$ weakly convex if there exists $q \in \RR$ such that the function $F + q/2\Vert \cdot\Vert^2$ is a convex function and $q$ is the infimum of all such possible parameters.
+                We define $F$ to be $q$ weakly convex if there exists $q \in \ge 0$ such that the function $F + q/2\Vert \cdot\Vert^2$ is a convex function and $q$ is the infimum of all such possible parameters.
             \end{definition}
+            \begin{remark}
+                If $q = 0$, $f$ is convex or strongly convex. 
+            \end{remark}
             \begin{definition}[gradient mapping]
@@
         We showcase the theories using a generic similar triangle representations of the algorithm which tremendously simplifies the arguments. 
-
         The following definition can capture monotone variants of FISTA with line search, including backtracking strategies. 
@@
         \end{proof}
-        % ======================================================================
-        % THEOREM | GENERIC GMAPG CONVERGENCE IN FXN VAL
-        % ======================================================================
         \begin{theorem}[generic GMAPG convergence]\; \label{thm:gmapg-ls-convergence}\;\\
@@
         \end{remark}
-        % ======================================================================
-        % THEOREM | GENERIC GMAPG GRADIENT MAPPING CONVERGENCE
-        % ======================================================================
         \begin{theorem}[generic GMAPG gradient mapping convergence]\;\label{thm:gmapg-generic-gradmap-convergence}\\
@@
         This section will introduce various type of implementations that can be fitted into GMAPG in Definition \ref{def:generic-mapg-ls}. 
+        \subsection{Line search routines}
+            % ARMIJO LINE SEARCH -----------------------------------------------
             \begin{algorithm}[H]
                 {\small
-            \begin{algorithmic}[1]\label{alg:armijo-ls}
+                \begin{algorithmic}[1]
                     \STATE{\noindent
-                    % \textbf{Function ArmijoLS}
-                    % $(f, g, x, v, L, \alpha, \_, \_)$
                         \textbf{Function ArmijoLS: }
@@
                             $f : \RR^n \rightarrow \RR$ & Convex Lipschitz smooth\\ 
-                        $g: \RR^n \rightarrow \overline \RR$  &  Convex function with Proximal operator\\ 
+                            $g: \RR^n \rightarrow \overline \RR$  &  Convex\\ 
                             $x \in \RR^n$ & Vector\\
@@
                     \ENDFOR
-                \STATE{\textbf{Return:} $y^+, x^+, \alpha^+, L^+$}
-                \caption{Armijo Line Search}
+                    \STATE{\textbf{Return:} $x^+, y^+, \alpha^+, L^+$}
+                    \caption{Armijo Line Search}\label{alg:armijo-ls}
                 \end{algorithmic}
@@
             \end{algorithm}
+            % CHAMBOLLE'S BACKTRACKING LINE SEARCH -----------------------------
             \begin{algorithm}[H]
                 {\small
-            \begin{algorithmic}[1]\label{alg:chambolle-btls}
+                \begin{algorithmic}[1]
                     \STATE{\noindent
-                    % \textbf{Function ChamBT}($f, g, x, v, L, \alpha, L_{\min}, \rho$)
-                    \textbf{Function ChamBT input: }
+                        \textbf{Function ChamBT Inputs: }
                         \begin{tabular}{|ll}
                             $f:\RR^n \rightarrow \RR$ & Convex Lipschitz smooth\\ 
-                        $g:\RR^n \rightarrow \overline\RR$ & Convex with Proximal Operator\\ 
+                            $g:\RR^n \rightarrow \overline\RR$ & Convex\\ 
                             $x\in \RR^n$ & Vector\\
@@
                     \ENDFOR
-                \STATE{\textbf{Return: }$y^+, x^+, \alpha^+, L^+$}
-                \caption{Chambolle's Backtracking}
+                    \STATE{\textbf{Return: }$x^+, \alpha^+, L^+$}
+                    \caption{Chambolle's Backtracking}\label{alg:chambolle-btls}
                 \end{algorithmic}
@@
             \end{algorithm}
-        % BECK'S MONO ----------------------------------------------------------
+        \subsection{Monotone routines}
+            % BECK'S MONO ------------------------------------------------------
             \begin{algorithm}[H]
-            \begin{algorithmic}[1]\label{alg:beck-mono}
+                \begin{algorithmic}[1]
                     \STATE{\noindent
@@
                             $x \in \RR^n$ & \\
-                        $\rho$ & Number $\rho \in (0, 1)$
+                            $\rho$ & Number $\rho \in (0, 1)$ \\
+                            $G \in \RR$ & Number 
                         \end{tabular}\vspace{0.5em}
@@
                     }
-                \STATE{\textbf{Return: } $x^+, \eta$}
-                \caption{Beck's monotone routine}
+                    \STATE{\textbf{Return: } $x^+, x_{k - 1} ,\eta$}
+                    \caption{Beck's monotone routine}\label{alg:beck-mono}
                 \end{algorithmic}
             \end{algorithm}
-        % NES'S MONO -----------------------------------------------------------
+            % NES'S MONO -------------------------------------------------------
             \begin{algorithm}[H]
@@
                             $\eta \in \RR$ & Number $\eta > 0$\\
+                            $G \in \RR$  & Number
                         \end{tabular}\vspace{0.5em}
@@
                     }
-                \WHILE{$F(x^+) - F(\hat y) > -1/(2\eta)\Vert \mathcal G_{1/\eta}(\hat y)\Vert^2$}
+                    \FOR {i = 1, 2, \ldots, 53}
+                        \IF{$(f + g)(x^+) - (f + g)(\hat y) \le -1/(2\eta)\Vert \mathcal G_{1/\eta}(\hat y)\Vert^2$}
+                            \STATE{\textbf{Break}}
+                        \ENDIF
                         \STATE{$\eta := 2\eta$. }
-                \ENDWHILE
+                            \STATE{$x^+ := T_{1/\eta}(\hat y)$.}
+                    \ENDFOR
+                    \STATE{$G := \eta (x^+ - \hat y).$}
                     \STATE{\textbf{return: } $x^+, \eta$ }
-                \caption{Nesterov's monotone routine}
-            \end{algorithmic}\label{alg:nes-mono}
+                    \caption{Nesterov's monotone routine}\label{alg:nes-mono}
+                \end{algorithmic}
             \end{algorithm}
-        % GMAPG ----------------------------------------------------------------
+        \subsection{GMAPG main algorithm}
+            % GMAPG ------------------------------------------------------------
             \begin{algorithm}[H]
@@
                         \begin{tabular}{|ll}
-                        $f:\RR^n \rightarrow \RR$ &  Weakly Convex Lipschitz Smooth \\
+                            $f:\RR^n \rightarrow \RR$ & Lipschitz Smooth \\
                             $g: \RR^n \rightarrow \overline\RR$ & Weakly Convex \\ 
+                            $x_{-1}$ & Vector\\
                             $L\in \RR$ & $L > 0$\\ 
-                        $r_{\min} $ & $r_{\min} \in (0, 1)$ \\ 
+                            $r $ & $r \in (0, 1)$ \\ 
                             $\rho \in \RR$ & $\rho \in (0, 1)$ \\
@@
                             $N \in \N$ & $N \ge N_{\min}$ \\
-                        $\mathbb L_{\mathcal S}$ \\ Algorithm \ref{alg:armijo-ls} or \ref{alg:chambolle-btls}
+                            $\epsilon \in \RR$ & Number\\
+                            $\mathbf L$ & Algorithm \ref{alg:armijo-ls} or \ref{alg:chambolle-btls}\\
+                            $\mathbf M$ & Algorithm \ref{alg:beck-mono} or \ref{alg:nes-mono}\\
+                            $\mathbf E_\chi$ & Exit Condition 
                         \end{tabular}
                     }
-                \STATE{\textbf{Return: }}
+                    \STATE{$\alpha_0 := 1$.}
+                    \STATE{$x_0, y_0,\alpha_1, L_0 := \textbf{ArmijoLS}(f, g, x_{-1}, x_{-1}, L, \alpha_0)$.}
+                    \STATE{$\eta_0 := L_0; v_0 := x_0; G_0 = L_0(x_0 - y_0).$}
+                    \FOR{$k := 1, 2,\ldots, N$}
+                        \STATE{\noindent
+                            $\tilde x_{k}, y_k, \alpha_{k + 1}, L_{k} := \mathbf{L}(f, g, v_{k - 1}, x_{k - 1}, L_{k - 1}, \alpha_{k}, rL_{k - 1}, \rho)$.
+                        }
+                        \STATE{\noindent
+                            $\rho := \rho^{1/2} \textbf{ if } L_{k} > L_{k - 1} \textbf{ else } \rho$.
+                        }
+                        \STATE{$G_k:= L_k(\tilde x_k - y_k)$}
+                        \STATE{\noindent
+                            $x_k, \hat y_k, \eta_{k + 1}, G_k := \mathbf M(f, g, \tilde x_k, x_{k - 1}, \eta_k, G_k)$.
+                        }
+                        \IF{$G_k < \epsilon \textbf{ or } (\mathbf E_\chi  \textbf{ and } k > N_{\min})$}
+                            \STATE{\textbf{break}}
+                        \ENDIF
+                    \ENDFOR
+                    \STATE{\textbf{Return: }$x_k, k$}
                 \caption{GMAPG with Chambolle's backtracking}
@@
         \end{example}
-        % ======================================================================
-        % EXAMPLE | NESTEROV'S MONOTONE SCHEME WITH GENERIC LINE SEARCH
-        % ======================================================================
         \begin{example}[Nesterov's monotone scheme with generic line search]\;\\
@@
         The following assumption will characterize the full scope of discussion in nonconvexity objective function. 
-
         \begin{definition}[nonconvex Nesterov's monotone scheme]\;\label{def:nes-monotone-scheme}\\

### 2025-05-09 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
                 Let $f: \RR^n \rightarrow\overline \RR$ be an l.s.c proper function. 
-                We define $F$ to be $q$ weakly convex if there exists $q \in \ge 0$ such that the function $F + q/2\Vert \cdot\Vert^2$ is a convex function and $q$ is the infimum of all such possible parameters.
+                We define $F$ to be $q$ weakly convex if there exists $q \ge 0$ such that the function $F + q/2\Vert \cdot\Vert^2$ is a convex function and $q$ is the infimum of all such possible parameters.
             \end{definition}
@@
                         \begin{tabular}{|ll}
-                            $f: \RR^n \rightarrow \RR$ & \\
-                            $g: \RR^n \rightarrow \overline \RR$ & \\
-                            $\tilde x \in \RR^n$ & \\
-                            $x \in \RR^n$ & \\
-                            $\rho$ & Number $\rho \in (0, 1)$ \\
+                            $f: \RR^n \rightarrow \RR$ & Convex Smooth\\
+                            $g: \RR^n \rightarrow \overline \RR$ & Convex\\
+                            $\tilde x \in \RR^n$ & Vector\\
+                            $x \in \RR^n$ & Vector\\
+                            $\rho$ & Number $\rho \in (0, 1)$ Number\\
                             $G \in \RR$ & Number 
@@
         \begin{definition}[nonconvex Nesterov's monotone scheme]\;\label{def:nes-monotone-scheme}\\
-
+            ...
         \end{definition}

### 2025-05-13 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, little new stuff

@@
     In this section, $D_f$ will denote the Bregman Divergence as defined in Definition \ref{def:bregman-div}. 
-    \section{Necoara's et al's Paper}
+    \section{Necoara's et al.'s Paper}
         \subsection{The Settings}
@@
     In this chapter, we will go through the details of these enhancements of FISTA and discuss why they are important in theories, and in practice.
+
     \section{Preliminaries}
@@
     % ==========================================================================
+
     \section{Examples of GMAPG in the literature}
@@
         \end{definition}
+        \begin{theorem}[convergence of Nesterov's monotone scheme nonconvex]
+
+        \end{theorem}
+
     \section{Restarting with function values}
+
     \section{Applying them to large scale LP}

### 2025-05-23 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

--- 2025-05-09 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
@@
     % ==========================================================================
-    \begin{theorem}[weakly convex generic proximal gradient inequality]\;\label{thm:pg-ineq-wcnvx-generic}\\
+    \begin{theorem}[strongly/weakly convex generic proximal gradient inequality]\;\label{thm:pg-ineq-swcnvx-generic}\\
         Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-add-nonsmooth} with $\beta > 0$ and $\mu \in \RR$. 
@@
         \end{align*}
-        Specializing Theorem \ref{thm:pg-ineq-wcnvx-generic}, let $x \in \RR^n$ and define $\bar x = T_{\beta^{-1}, f, g}(x)$ it has $\forall z \in \RR^n:$
+        Specializing Theorem \ref{thm:pg-ineq-swcnvx-generic}, let $x \in \RR^n$ and define $\bar x = T_{\beta^{-1}, f, g}(x)$ it has $\forall z \in \RR^n:$
         \begin{align*}
@@
                 \begin{align*}
-                    \frac{\kappa_f}{\kappa_f/L_f + 1 + \sqrt{\kappa_k/L_f + 1}}. 
+                    \frac{\kappa_f/L_f}{\kappa_f/L_f + 1 + \sqrt{\kappa_k/L_f + 1}}. 
                 \end{align*}
@@
         \subsection{Application, KKT of linear programming}
-            This section extends and ideas in the discussion section of Necoara et al. \cite{necoara_linear_2019}. 
+            This section extends ideas in the discussion section of Necoara et al. \cite{necoara_linear_2019}. 
             \par
@@
                     \item $f$ is $L$ Lipschitz smooth and $q_f$ weakly convex. 
-                    \item $g$ is $L$ Lipschitz smooth and $q_g$ weakly convex. 
+                    \item $g$ is $q_g$ weakly convex. 
                 \end{enumerate}
@@
                 If $q = 0$, $f$ is convex or strongly convex. 
+                If $f$ is weakly convex, then $f + 1/2\Vert \cdot\Vert^2$ is convex and, it has $\dom f$ convex, and locally Lipschitz continuous on $\reli \dom f$. 
             \end{remark}
@@
                 Let $F = f + g$ satisfies Assumption \ref{ass:sum-of-wcnvx}. 
-                Let $\bar x = T_{\beta, f, g}(x)$. 
+                Let $\bar x = T_{\beta^{-1}, f, g}(x)$. 
                 Then, for all $x \in \RR^n$, it has the following inequality: 
@@
                 \begin{aligned}
-                    0 \le F(x) - F(\bar x) - (\beta - q/2 - L/2)\Vert x - \bar x\Vert^2. 
+                    0 \le F(x) - F(\bar x) - (\beta - q_g/2 - L/2)\Vert x - \bar x\Vert^2. 
                 \end{aligned}
                 $$
-                And descent is possible when $\beta \ge (L + q)/2$. 
-                The maximum amount of descent is achieved when $\beta = L + q$. 
+                And descent is possible when $\beta \ge (L + q_g)/2$ and it yields the descent lemma: 
+                \begin{align*}
+                    0 &\le F(x) - F(\bar x) - 1/\beta \Vert \mathcal G_{1/\beta}(x)\Vert^2. 
+                \end{align*}
+                The maximum amount of descent is achieved when $\beta = L + q_g$. 
             \end{lemma}
             \begin{proof}
-                Use Theorem \ref{thm:pg-ineq-wcnvx-generic}. 
+                Use Theorem \ref{thm:pg-ineq-swcnvx-generic}, set $z = x$, after some algebra it yields: 
+                \begin{align*}
+                    0 \le F(x) - F(\bar x) - \left(
+                        \beta - \frac{q_g + L}{2}
+                    \right)\Vert x - \bar x\Vert^2. 
+                \end{align*}
+                Using the definition of gradient mapping previously, it has for all $\beta > 0$: 
+                \begin{align*}
+                    0 &\le F(x) - F(\bar x) - \left(
+                        \beta - \frac{q_g + L}{2}
+                    \right)\Vert \beta^{-1}\mathcal G_{1/\beta}(x) \Vert^2
+                    \\
+                    &\le F(x) - F(\bar x) - \left(
+                        \beta^{-1} - \frac{q_g + L}{2\beta^2}
+                    \right)\Vert\mathcal G_{1/\beta}(x) \Vert^2
+                \end{align*}
+                Optimizing $x\mapsto x - x^2(1_g - L)/2$ yields $x = (q_g - L)^{-1}$ so $\beta = q_g - L$ gives the most amount of descent. 
+                Consider any $\beta \ge (q_g - L)$: 
+                \begin{align*}
+                    &\le F(x) - F(\bar x) - \left(
+                        \beta^{-1} - \frac{q_g + L}{2\beta^2}
+                    \right)\Vert\mathcal G_{1/\beta}(x) \Vert^2
+                    \\
+                    &\le F(x) - F(\bar x) + \left(
+                        \beta^{-1}/2 - \beta^{-1}
+                    \right)\Vert\mathcal G_{1/\beta}(x) \Vert^2
+                    \\
+                    &= 
+                    F(x) - F(\bar x) + \frac{1}{2\beta}\Vert\mathcal G_{1/\beta}(x) \Vert^2. 
+                \end{align*}
             \end{proof}
@@
             \end{align*}
-            If in addition, the algorithm is initialized with $L_0 \ge L$, $\alpha_0 = 1, x_0 = v_0 = T_{L_{0}}x_{-1} \in \text{dom}\; F$ and $x^+$ is a minimizer of $F$.
+            If in addition, the algorithm is initialized using line search so that \mbox{$D_f(x_0, x_{-1}) \le L_0/2 \Vert x_0 - x_{-1}\Vert^2$}, $\alpha_0 = 1, x_0 = v_0 = T_{L_{0}}x_{-1} \in \dom F$ and, $x^+$ is a minimizer of $F$.
             Then, the convergence rate simplifies: 
@@
                     }
-                    \STATE{\textbf{Return: } $x^+, x_{k - 1} ,\eta$}
+                    \STATE{\textbf{Return: } $x^+, \eta, G$}
                     \caption{Beck's monotone routine}\label{alg:beck-mono}
@@
                     \STATE{$G := \eta (x^+ - \hat y).$}
-                    \STATE{\textbf{return: } $x^+, \eta$ }
+                    \STATE{\textbf{return: } $x^+, \eta, G$ }
                     \caption{Nesterov's monotone routine}\label{alg:nes-mono}
@@
                         \STATE{\noindent
-                            $x_k, \hat y_k, \eta_{k + 1}, G_k := \mathbf M(f, g, \tilde x_k, x_{k - 1}, \eta_k, G_k)$.
+                            $x_k, \eta_{k + 1}, G_k := \mathbf M(f, g, \tilde x_k, x_{k - 1}, \eta_k, G_k)$.
                         }
@@
         \begin{definition}[nonconvex Nesterov's monotone scheme]\;\label{def:nes-monotone-scheme}\\
-            ...
+            Suppose $F = f + g$ satisfies Assumption \ref{ass:sum-of-wcnvx}. 
+            Let $L_0 \ge L$. 
+            Let $(\alpha_k)_{k \ge 0}$ with $\alpha_0 = 1$ and, it satisfies for all $k \ge 1$: $L_{k}^{-1}L_{k - 1}\alpha_{k - 1}^2(1 - \alpha_k) = \alpha_k^2$. 
+            Initialize the algorithm with $\hat y_0 =v_0=x_0 = T_{1/L_0}(x_{-1})$, $\eta_0 = L_0$, for some $x_{-1} \in \RR^n$ and $L_0$ such that $F(x_0) \le F(x_{-1})$. 
+            The algorithm is defined by sequences $(y_k, v_k, x_k)_{k \ge 1}$ and $(\tilde x_k, \hat y_k)_{k \ge 1}$ such that they all satisfy: 
+            $$
+            \begin{aligned}
+                &y_k = \alpha_k v_{k - 1} + (1 - \alpha_k)x_{k - 1},
+                \\
+                &\tilde x_k = T_{1/L_k}(y_k), \text{ with line search or backtracking. }
+                \\
+                &v_k = x_{k - 1} + \alpha_k^{-1}(\tilde x_k - x_{k - 1}),
+                \\
+                &\hat y_k = \argmin{}\left\lbrace
+                    F(y): y \in \{x_{k - 1}, \tilde x_k\}
+                \right\rbrace,
+                \\
+                & \eta_{k}\text{ s.t: } F(x_k) - F(\hat y_k) \le - 1/(2\eta_k)\Vert \mathcal G_{1/\eta_k}(\hat y_k) \Vert^2, \eta_{k} \ge \eta_{k - 1}, 
+                \\
+                &x_k = T_{1/\eta_k}(\hat y_k) . 
+            \end{aligned}
+            $$
         \end{definition}
+        The following theorem states the fact that the algorithm should eventually terminate if the objective function is bounded below. 
+        \begin{theorem}[convergence of Nesterov's monotone scheme nonconvex]\;\label{thm:nes-mono-wcnvx-convergence}\\
+            Suppose that the sequences $(y_{k + 1}, v_k, x_k)_{k \ge 0}$ and $(\hat y_k, \tilde x_k)_{k \ge 0}$, $(\alpha_k)_{k \ge 0}$ satisfy Definition \ref{alg:nes-mono}. 
+            Assume that $F$ is bounded below with $F^+ := \inf_{x}F(x)$. 
+            Then for all $N \ge 1$ it has
+            \begin{align*}
+                \min_{1 \le k \le N}\Vert \mathcal G_{1/\eta_k}(\hat y_k) \Vert^2 
+                &\le\frac{2\overline \eta_N}{N}(F(x_{-1}) - F^+). 
+            \end{align*}
+            Here, $\overline \eta_k = \max_{i = 0, \ldots, k}\eta_i$. 
+            If the monotone routine in Algorithm \ref{alg:nes-mono} is used, then it's bounded above by $2(q_g + L)$. 
+        \end{theorem}
+        \begin{proof}
+            $\overline \eta_k = \max_{i = 0, \ldots, k}\eta_i$
+            Using Lemma \ref{lemma:mono-wcnvx-descent} it has from the descent condition of monotone routine that for all $k \ge 1$,  
+            \begin{align*}
+                0 &\le F(\hat y_k) - F\left(T_{1/\eta_k}\hat y_k\right) 
+                - \frac{1}{2\eta_k}\Vert \mathcal G_{1/\eta_k}(\hat y_k)\Vert^2
+                \\
+                &= \min(F(x_{k - 1}), F(\tilde x_k)) - F(x_k) 
+                - \frac{1}{2\eta_k}\Vert \mathcal G_{1/\eta_k}(\hat y_k)\Vert^2
+                \\
+                &\le 
+                F(x_{k - 1}) - F(x_k) - \frac{1}{2\eta_k} \Vert \mathcal G_{1/\eta_k}(\hat y_k)\Vert^2
+                \\
+                &\le 
+                F(x_{k - 1}) - F(x_k) - \frac{1}{2\overline\eta_k} \Vert \mathcal G_{1/\eta_k}(\hat y_k)\Vert^2. 
+            \end{align*}
+            Telescoping it has: 
+            \begin{align*}
+                0 &\le \left(
+                    \sum_{i = 1}^{N} F(x_{i - 1}) - F(x_i)
+                \right) 
+                - \frac{1}{2\overline\eta_N}\sum_{i = 1}^{N} \Vert \mathcal G_{1/\eta_i}(\hat y_k)\Vert^2
+                \\
+                &= 
+                F(x_{0}) - F(x_N) 
+                - \frac{1}{2\overline\eta_N}\sum_{i = 1}^{N} \Vert \mathcal G_{1/\eta_i}(\hat y_k)\Vert^2
+                \\
+                &\le 
+                F(x_{0}) - F(x_N) 
+                - \frac{N }{2\overline\eta_N}\left(
+                    \min_{1 \le i \le N} \Vert \mathcal G_{1/\eta_i}(\hat y_i)\Vert^2
+                \right)
+                \\
+                &\le F(x_{0}) - F^+ 
+                - \frac{N}{2\overline\eta_N}\left(
+                    \min_{1 \le i \le N} \Vert \mathcal G_{1/\eta_i}(\hat y_i)\Vert^2
+                \right)
+                \\
+                &\le F(x_{-1}) - F^+ 
+                - \frac{N}{2\overline\eta_N}\left(
+                    \min_{1 \le i \le N} \Vert \mathcal G_{1/\eta_i}(\hat y_i)\Vert^2
+                \right).
+            \end{align*}
+            Finally, we show $\overline \eta_k \le 2(q_g - L)$. 
+            If there exists $k$ such that $\eta_k \ge q_g - L$ in the algorithm, then by Lemma \ref{lemma:mono-wcnvx-descent} the condition $F(x_k) - F(\hat y_k) \le -1/(2\eta_k)\Vert \mathcal G_{1/\eta_k}(\hat y_k)\Vert$ for all possible $\hat y_k \in \RR^n$, therefore Algorithm \ref{alg:nes-mono} won't increase the value of $\eta_k$ in the future iteration.
+            It has for all $i \ge k$, $\eta_i = \eta_k$. 
+            Suppose that some $\eta_i > 2(q_g + L), i \ge k$ then it means there exists $\eta_k > q_g + L$, this contradicts what we had right before, hence impossible and $\eta_i \le 2(q_g + L)$ is an upper bound.
+        \end{proof}
+        \begin{remark}
+            The convergence claim still works for restarts. 
+        \end{remark}
+        \par
+        A stronger results on the convergence rate of $\Vert \mathcal G_{1/\eta_k}(y_k)\Vert$ can be obtained if, we assume that the function $F=f + g$ satisfies \ref{ass:standard-fista}. 
     \section{Restarting with function values}
+
     \section{Applying them to large scale LP}

### 2025-05-23 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, latex notes updates

@@
             Suppose that $F = f + g$ satisfy Assumption \ref{ass:standard-fista}. 
-            Let the sequence $(x_k, v_k, v_k)$ satisfy GMAPG, definition \ref{def:generic-mapg-ls} and, assume that the GMAPG is initialized by $x_0 = v_0 = T_{1/L_0}(x_{-1})$ and, assume $\rho_{k - 1} = L_{k}^{-1}L_{k}$, $\alpha_0 = 1$ so the sequence $(\alpha_k)_{k \ge 0}$ satisfies for all $k\ge 1$: $\alpha_{k - 1}^2L_k^{-1}L_{k - 1}(1 - \alpha_k) = \alpha_k^2$.
+            Let the sequences $(x_k, v_k, v_k)_{k \ge 0}$ and $(L_k)_{k \ge 0}$ satisfy GMAPG in Definition \ref{def:generic-mapg-ls} and, assume that the GMAPG is initialized by $x_0 = v_0 = T_{1/L_0}(x_{-1})$ and, assume $\rho_{k - 1} = L_{k}^{-1}L_{k}$, $\alpha_0 = 1$ so the sequence $(\alpha_k)_{k \ge 0}$ satisfies for all $k\ge 1$: $\alpha_{k - 1}^2L_k^{-1}L_{k - 1}(1 - \alpha_k) = \alpha_k^2$.
             Let $x^+$ be a minimizer of $F$, define 
@@
         \begin{proof}
-            To see (i), use \ref{lemma:gmapg-seq-bnd} and the remark with Theorem \ref{thm:gmapg-ls-convergence} because the assumptions of $x^+, (\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is the same.
+            To see (i), use Lemma \ref{lemma:gmapg-seq-bnd} and its remark to bound $(\beta_k)_{k \ge 1}$ and then, apply Theorem \ref{thm:gmapg-ls-convergence} because the assumptions of $x^+, (\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is the same.
             To see (ii), the convergence claim from \ref{thm:gmapg-generic-gradmap-convergence} simplifies with $\hat L_k \ge L_0$ and, it has 
@@
         \par
-        A stronger results on the convergence rate of $\Vert \mathcal G_{1/\eta_k}(y_k)\Vert$ can be obtained if, we assume that the function $F=f + g$ satisfies \ref{ass:standard-fista}. 
+        A stronger result on the convergence rate of $\Vert \mathcal G_{1/\eta_k}(y_k)\Vert$ can be obtained if, we assume that the function $F=f + g$ satisfies \ref{ass:standard-fista}. 
     \section{Restarting with function values}
@@
 
-\section{Primal Dual Lagrangian for LP}
+    \section{Hoffman Bounds and infeasibility detection}
+
+\chapter{Enhanced Primal Dual Methods for LP}
 

### 2025-05-27 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
     There are several notable enhancements of the FISTA for function that are not strongly convex. 
-    Monotone variants of FISTA proposed by Beck \todo{[?]} and Nesterov \todo{[?]} imposes monotonicity in function value at the iterates.  
-    Backtracking strategies from Chambolle \todo{[?]} shows that the underestimating Lipschitz constant using a backtracking technique to choose a next iterate improves the average runtime of the algorithm in practice.
+    Monotone variants of FISTA proposed by Beck \cite{beck_fast_2009-1} and Nesterov \cite[2.2.32]{nesterov_lectures_2018} imposes monotonicity in function value at the iterates.  
+    Backtracking strategies from Chambolle \cite{calatroni_backtracking_2019} shows that the underestimating Lipschitz constant using a backtracking technique to choose a next iterate improves the average runtime of the algorithm in practice.
     They showed that the convergence rate is bounded by the estimates of the Lipschitz constant. 
-    Restart is a technique pioneer early by ??? \todo{[?]}.
-    Necoara et al. \cite{necoara_linear_2019} showed that there exists an optimal restarting interval to achieve fast line convergence rate for all functions with quadratic growth condition. 
+    Restart is a technique discussed in Necoara et al. \cite{necoara_linear_2019}.
+    They showed that there exists an optimal restarting interval to achieve fast line convergence rate for all functions with quadratic growth condition. 
+    The method of restarting was improved to be parameter free while still retaining a fast linear convergence rate, see Alamo et al.
+\cite{alamo_restart_2019} and Aujol et al.
+\cite{aujol_parameter-free_2024}.
     \par
@@
         This section introduces the full scope of the theories in our analysis. 
+        Firstly, recall the definition of Bregman divergence $D_f(x, y)$ from Definition \ref{def:bregman-div} for a differentiable function $f:\RR^n \rightarrow \overline \RR$. 
         \subsection{smooth plus nonsmooth weakly convex}
@@
         We showcase the theories using a generic similar triangle representations of the algorithm which tremendously simplifies the arguments. 
-        The following definition can capture monotone variants of FISTA with line search, including backtracking strategies. 
+        The following definition captures several monotone variants of FISTA with line search,  or backtracking strategies.
+        \par
+        In this section, we give convergence results for a unified formulation of monotone accelerated proximal gradient methods with line search or backtracking enhancements. 
+        Definition \ref{def:generic-mapg-ls} gives a unified view of several combined heuristics. 
+        Theorem \ref{thm:gmapg-ls-convergence} gives a generic description for the convergence rate. 
+        Lemma \ref{lemma:gmapg-seq-bnd} specializes the sequence, attains the lowest upper bound. 
+        Theorem \ref{thm:gmapg-specialized-convergence} gives a concrete $\mathcal O(1/k^2)$ upper bound for the optimality gap and normed gradient mapping on the last iteration. 
         \par
@@
         \end{proof}
+        \begin{remark}
+            The above theorem is improved from Alamo et al. \cite{alamo_restart_2019}. 
+        \end{remark}
         \begin{lemma}[specialized GMAPG momentum sequence]\;\label{lemma:gmapg-seq-bnd}\\
@@
         \begin{remark}
-            A simpler upper bound is more useful in practice. 
+            The techique of the proof we used here is very similar to Güler \cite[Lemma 2.2]{guler_new_1992}.
+            A simpler upper bound is more practical. 
             For all $k \ge 1$ let $\hat L_k = \max_{i = 0, 1, \ldots, k} L_i$ then 
@@
         \begin{proof}
-            To see (i), use Lemma \ref{lemma:gmapg-seq-bnd} and its remark to bound $(\beta_k)_{k \ge 1}$ and then, apply Theorem \ref{thm:gmapg-ls-convergence} because the assumptions of $x^+, (\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is the same.
+            To see (i), use Lemma \ref{lemma:gmapg-seq-bnd} and its remark to bound $(\beta_k)_{k \ge 1}$ and then, apply Theorem \ref{thm:gmapg-ls-convergence} because the assumptions of $x^+, (\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ suit.
             To see (ii), the convergence claim from \ref{thm:gmapg-generic-gradmap-convergence} simplifies with $\hat L_k \ge L_0$ and, it has 
@@
             \end{algorithm}
+            \par
+            Algorithm \ref{alg:armijo-ls} performs a step of Armijo line search and a step of accelerated proximal gradient. 
+            The function can be used for each iteration in the inner loop of the algorithm. 
+            Here are the explanations for all its input parameters: 
+            \begin{enumerate}
+                \item $f, g$ are functions satisfying Assumption \ref{ass:standard-fista}. 
+                \item $x, v$ are the $x_k, v_k$ iterates in Definition \ref{def:generic-mapg-ls}. 
+                \item $\alpha$ are the current $\alpha_k$ in Definition \ref{def:generic-mapg-ls}. 
+                \item $L$ is the estimate of the Lipschitz constant of $f$ passed in by the inner loop. 
+            \end{enumerate}
+            Iterates $x^+, y^+$ and parameters $\alpha^+, L^+$ are returned to the callers at the end. 
             % CHAMBOLLE'S BACKTRACKING LINE SEARCH -----------------------------
@@
             \end{algorithm}
+            \par
+            Algorithm \ref{alg:chambolle-btls} attempts to decrease the Lipschitz estimate $L_k$ for $f$ in an iteration of the inner loop. 
+            The above implementations were adapted and simplified from Chambolle et al. \cite{calatroni_backtracking_2019}. 
+            It takes in additional parameters $L_{\min}, \rho$ compared to Algorithm \ref{alg:armijo-ls}. 
+            Here are their explanations: 
+            \begin{enumerate}
+                \item $L_{\min}$ determines a lower bound of Lipschitz estimates.
+It's the lowest value of an estimate $L_k$ allowed.
+It increases stability of the algorithm by preventing unnecessary triggering a line search routine to recovers from an underestimated $L_k$ that doesn't satisfy the Lipschitz smoothness condition for $f$ at the current iterate.
+                \item $\rho \in (0, 1)$ is the decay ratio. It's use to shrink the current estimate of $L$ and produce $L^+$ at the start of the forloop before verifying the smoothness condition. 
+            \end{enumerate}
         \subsection{Monotone routines}
@@
             \end{algorithm}
+            \par
+            Algorithm \ref{alg:beck-mono} is a subroutine for asserting monotone condition on function value. 
+            The parameter $G$ has no actual usage besides making it compatible with Algorithm \ref{alg:nes-mono} in the context of Algorithm \ref{alg:gmapg}. 
+            The input $\tilde x$ is the candidate iterate produced by FISTA without monotone constraints and $x$ is the previous iterates $x_{k - 1}$ in the inner loop. 
             % NES'S MONO -------------------------------------------------------
@@
             \end{algorithm}
+            \par
+            The above Algorithm \ref{alg:nes-mono} implements and adapts Nesterov's monotone scheme from Nesterov \cite[2.2.32]{nesterov_lectures_2018} for GMAPG. 
+            In addition to Algorithm \ref{alg:beck-mono}, $\eta$ is a new input parameter and $G$ has a significance role. 
+            $\eta$ is a stepsize parameter for weakly convex objective $F = f + g$ satisfying Assumption \ref{ass:sum-of-wcnvx}. 
+            $G$ is the norm of the gradient mapping updated at at $\hat y$ which will be returned to the inner loop to verify exit conditions. 
         \subsection{GMAPG main algorithm}
@@
                         \STATE{\noindent
-                            $x_k, \eta_{k + 1}, G_k := \mathbf M(f, g, \tilde x_k, x_{k - 1}, \eta_k, G_k)$.
-                        }
-                        \IF{$G_k < \epsilon \textbf{ or } (\mathbf E_\chi  \textbf{ and } k > N_{\min})$}
+                            $x_k, \eta_{k + 1}, G_k^+ := \mathbf M(f, g, \tilde x_k, x_{k - 1}, \eta_k, G_k)$.
+                        }
+                        \IF{$G_k^+ < \epsilon \textbf{ or } (\mathbf E_\chi  \textbf{ and } k > N_{\min})$}
                             \STATE{\textbf{break}}
@@
                     \STATE{\textbf{Return: }$x_k, k$}
-                \caption{GMAPG with Chambolle's backtracking}
-                \end{algorithmic}\label{alg:gmapg}
+                \caption{GMAPG with Chambolle's backtracking}\label{alg:gmapg}
+                \end{algorithmic}
             \end{algorithm}
-    % ==========================================================================
-    % SECTION | EXAMPLES OF GMAPG IN THE LITERATURE
-    % ==========================================================================
+            The above Algorithm \ref{alg:gmapg} is an implementation of GMAPG in Definition \ref{alg:gmapg}. 
+            Parameters $r, \rho$ are chosen in the discretion of the practitioners. 
+            For example, we chose $r= 0.4, \rho = 2^{1/1024}$.
 
@@
         A stronger result on the convergence rate of $\Vert \mathcal G_{1/\eta_k}(y_k)\Vert$ can be obtained if, we assume that the function $F=f + g$ satisfies \ref{ass:standard-fista}.
-    \section{Restarting with function values}
+
+    \section{Restarting with function values for linear convergence}
+        In this section, we show that restarting GMAPG with a well suited conditions yields fast linear global convergence. 
+        We adapt and improve prior theories from Alamo \cite{alamo_restart_2019} for our GMAPG method. 
+        \par
+        Let's introduce our first set of restart conditions which denote it by $\mathbf E_{\chi}^{a}$. 
+        $\mathbf E_{\chi}^{a}$ only uses function values on iterates available to the inner loop to determine the exit conditions, and it achieves global fast linear convergence. 
+        The inner loop algorithm is described in Algorithm \ref{alg:gmapg}, let $k$ denote the inner loop counter and define $m = \lfloor k/2 \rfloor + 1$ the conditions are: 
+        \begin{align*}
+            \mathbf E_{\chi}^a \iff 
+            f(x_m) - f(x_k) \le \exp(-1)(f(x_0) - f(x_m)). 
+        \end{align*}
+        \begin{algorithm}[H]
+            \begin{algorithmic}[1]
+            \STATE{\textbf{Input: }\begin{tabular}{ll}
+                $f:\RR^n \rightarrow \RR$ & Lipschitz Smooth \\
+                $g: \RR^n \rightarrow \overline\RR$ & Weakly Convex \\ 
+                $x_{-1}$ & Vector\\
+                $M \in \N$ & Integer\\
+                $\epsilon \in \RR$ & Number\\
+                $\mathbf L$ & Algorithm \ref{alg:armijo-ls} or \ref{alg:chambolle-btls}\\
+                $\mathbf M$ & Algorithm \ref{alg:beck-mono} or \ref{alg:nes-mono}\\
+                $L:=1$ & $L > 0$\\ 
+                $r:=0.5$ & $r \in (0, 1)$ \\ 
+                $\rho := 2^{1/1024}$ & $\rho \in (0, 1)$ 
+            \end{tabular}}
+            \STATE{$n_0 := 0$.}
+            \STATE{$z_1, p_0 := \textbf{GMAPG}(f, g, x_{-1}, r_j, \rho, N_{\min}=n_0, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
+            \STATE{$n_1:=p_0. $}
+            \STATE{$M := M - n_1$}
+            \FOR{$j = 1,2, \ldots, M$}
+                \STATE{$z_{j + 1}, p_j := \textbf{GMAPG}(f, g, z_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
+                \STATE{$M := M - p_j$}
+                \IF{$f(z_{j}) - f(z_{j + 1}) > \exp(-1)(f(z_{j - 1}) - f(z_{j}))$}
+                    \STATE{$n_{j + 1} := 2p_j$.}
+                \ELSE
+                \STATE{$n_{j + 1} := p_j$.}
+                \ENDIF
+            \ENDFOR
+            \end{algorithmic}\caption{Linear convergence restarted GMAPG}\label{alg:linear-rgmapg}
+        \end{algorithm}
+        \par
+        Algorithm \ref{alg:linear-rgmapg} implements a restarted GMAPG with condition $\textbf{E}_{\chi}^a$ and, it has a fast linear convergence rate. 
+        The following observation on it is crucial to take notice for the convergence rate. 
+        \par
+        $n_j$ is used as the lower bound $N_{\min}$ for the GMAPG inner loop described in Algorithm \ref{alg:gmapg} at iteration $j$ and, $p_j$ is the actual iteration underwent by the inner loop and, it has $p_j \ge n_{j}$.
+        $n_{j + 1}$ is the minimum iteration for the next execution of GMAGP, and it has $n_{j + 1} = p_{j}$  if the ``if statement" isn't triggered otherwise $n_{j + 1} = 2p_{j}$. 
+        Consequently, it has either $p_{j + 1} \ge n_{j + 1} = 2p_j$ or $p_{j + 1} \ge n_{j + 1} = p_j$. 
+        \par
+        We now introduce the following notations for the convergence proof. 
+        Since the restarted GMAPG consist of executions of an outer loop in Algorithm \ref{alg:linear-rgmapg} in variable $j$ and, an inner loop in Algorithm \ref{alg:gmapg} in variable $k$, we denote $z_{j, k}$ for the iterates $x_k$ in the inner loop and $z_j$ in the outer loop together.
+        We make the rule that $z_{j + 1, -1} = z_{j, p_j}$ for compatibility of the theorems in the previous sections. 
+        For example in line 7 at the $j$ iteration, the inner loop returns $x_{p_j}$ as the last iterate of the inner loop and, it's assigned to $z_{j + 1}$ by the outer loop. 
+        In that case we denote $z_{j + 1, -1}$ as the initial iterate pass into the inner loop for the $j + 1$ iteration, and $z_{j, p_j}$ would denote the last iteration before exiting the inner loop for the $j$ th iteration of the outer loop.
+        Therefore, $z_{j + 1, -1} = z_{j, p_j}$ and all iterates generated by the inner loop is the finite sequence $(z_{j, k})_{k = 0}^{p_j}$. 
+        \par
+
+        \begin{lemma}[bounds on inner iteration counts]
+            ...
+        \end{lemma}
+        \begin{proof}
+
+        \end{proof}
+        \begin{lemma}[bounds on outer iteration counts]
+            ...
+        \end{lemma}
+
+        \begin{theorem}[bounds on the total iterations]
+            ...
+        \end{theorem}
 

### 2025-05-27 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
             \end{remark}
-            \begin{definition}[gradient mapping]
+            \begin{definition}[gradient mapping]\label{def:gm-for-ch2}
                 Suppose $F = f + g$ satisfies Assumption \ref{ass:sum-of-wcnvx}, define the gradient mapping for all $x \in \RR^n$
@@
             \end{assumption}
-            \begin{lemma}[proximal gradient inequality]
+            \begin{lemma}[proximal gradient inequality]\label{lemma:fitsa-pg-ineq}
                 If $F = f + g$ satisfies Assumption \ref{ass:standard-fista}, then for all $x \in \RR^n, z \in \RR^n$, define $\bar x = T_{L^{-1}, f, g}(x)$ it has 
@@
             \begin{proof}
-                Use Theorem \ref{thm:cnvx-pg-ineq}. 
+                Use Theorem \ref{thm:cnvx-pg-ineq} with $\mu_f = \mu_g = 0$. 
             \end{proof}
@@
         Lemma \ref{lemma:gmapg-seq-bnd} specializes the sequence, attains the lowest upper bound. 
-        Theorem \ref{thm:gmapg-specialized-convergence} gives a concrete $\mathcal O(1/k^2)$ upper bound for the optimality gap and normed gradient mapping on the last iteration. 
+        Theorem \ref{thm:gmapg-specialized-cnvg} gives a concrete $\mathcal O(1/k^2)$ upper bound for the optimality gap and normed gradient mapping on the last iteration. 
         \par
@@
         \end{definition}
+        The following definition characterizes the sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$, $(L_k)_{k \ge 0}$ and defines $(\beta_k)_{k \ge 0}$ for the proofs for the convergence rate. 
+        \begin{definition}[alpha momentum sequence]\label{def:alpha-beta-rho-seq}
+            Let $(\alpha_k)_{k \ge 0}$ be a sequence in $\RR$ such that $\alpha_k \in (0, 1)$ for all $k \in \N$. 
+            Take $(L_k)_{k \ge 0}$ from Definition \ref{def:generic-mapg-ls} so it has $L_k > 0$ for all $k \in \N \cup \{0\}$. 
+            The sequence $(\rho_k)_{k \ge 0}$ is defined as 
+            \begin{align*}
+               \rho_{k} &= (1 - \alpha_{k + 1})^{-1}a_{k + 1}^2\alpha_k^{-2}. 
+            \end{align*}
+            Define sequence $(\beta_k)_{k \ge 0}$ such that $\beta_0 = 1$ and for all $k \ge 1$: 
+            \begin{align*}
+                \beta_k := \prod_{i = 0}^{k - 1} (1 - \alpha_{i + 1})\max\left(1, \rho_i L_{i + 1}L_i^{-1}\right). 
+            \end{align*}
+        \end{definition}
         \begin{lemma}[acceerated proximal gradient iterates relation]\;\label{lemma:apg-iterates}\;\\
@@
             Let $F = f + g$ satisfy Assumptions \ref{ass:standard-fista}. 
-            Let $(\alpha_k)_{k \ge 0}$ be a sequence such that $\alpha_k \in (0, 1)$ for all $k \ge 1$ and $\alpha_0 \in (0, 1]$. 
-            Let $\rho_k = (1 - \alpha_{k + 1})^{-1}\alpha_{k + 1}^2 \alpha_k^{-2}$ for all $k \ge 0$. 
-            Then, for all $x^+ \in \RR^n, k \ge 1$, the convergence rate of GMAPG-LS (Definition \ref{def:generic-mapg-ls}) is given by: 
-            \begin{align*}
-                & \beta_k := \prod_{i = 0}^{k - 1} (1 - \alpha_{i + 1})
-                \max\left(1, \rho_i L_{i + 1}L_i^{-1}\right), 
-                \\
-                & F(x_k) - F(x^+) + \frac{L_k\alpha_k}{2}\Vert x^+ - v_k\Vert^2
+            % Let $(\alpha_k)_{k \ge 0}$ be a sequence such that $\alpha_k \in (0, 1)$ for all $k \ge 1$ and $\alpha_0 \in (0, 1]$. 
+            % Let $\rho_k = (1 - \alpha_{k + 1})^{-1}\alpha_{k + 1}^2 \alpha_k^{-2}$ for all $k \ge 0$. 
+            Take the sequence $(\alpha_k)_{k \ge 0}, (\beta_k)_{k \ge 0}$ and $(\rho_k)_{k \ge 0}$ from Definition \ref{def:alpha-beta-rho-seq}. 
+            Then, for all $x^+ \in \RR^n, k \ge 1$, the convergence rate of GMAPG (Definition \ref{def:generic-mapg-ls}) is given by: 
+            \begin{align*}
+                F(x_k) - F(x^+) + \frac{L_k\alpha_k}{2}\Vert x^+ - v_k\Vert^2
                 \le 
@@
                 \item Lemma \ref{lemma:apg-iterates}. 
-                \item The sequence $(\alpha_k)_{k \ge 1}$ has for all $k \ge 1$, $1 - \alpha_k = \alpha_k^2\alpha_{k - 1}^2\rho_{k - 1}$, $\alpha_k \in (0, 1)$. 
-                \item $F$ is convex and hence $F(z_k) \le \alpha_k F(x^+) + (1 - \alpha_k)F(x_{k - 1})$. 
-                \item $F(x_k) \le F(\tilde x_k)$ which is true by definition of GMAPG. 
+                \item The sequence $(\alpha_k)_{k \ge 1}$ has for all $k \ge 1$, $1 - \alpha_k = \alpha_k^2\alpha_{k - 1}^2\rho_{k - 1}$, $\alpha_k \in (0, 1)$ from Definition \ref{def:alpha-beta-rho-seq}.
+                \item $F$ is convex and hence $F(z_k) \le \alpha_k F(x^+) + (1 - \alpha_k)F(x_{k - 1})$ from Assumption \ref{ass:standard-fista}. 
+                \item $F(x_k) \le F(\tilde x_k)$ which is true by definition of GMAPG (Definition \ref{def:generic-mapg-ls}). 
             \end{enumerate}
@@
         \end{remark}
-        \begin{theorem}[generic GMAPG gradient mapping convergence]\;\label{thm:gmapg-generic-gradmap-convergence}\\
+        \begin{theorem}[generic GMAPG gradient mapping convergence]\;\label{thm:gmapg-generic-gm-cnvg}\\
             Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista}. 
-            Let the sequences $(x_k, y_k, v_k)$ satisfy GMAPG (Definition \ref{def:generic-mapg-ls}). 
-            If in addition, the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and, GMAPG is initialized with $L_0 \ge L$, $v_0=x_0 = T_{1/L_0, f, g}(x_{-1})$ for any $x_{-1} \in\RR^n$ and there exists $x^+$ which is a minimizer of $F$.
-            Then, the convergence of gradient mapping $\Vert \mathcal G_{1/L_k}(y_k)\Vert$ is described by the sequence $(\beta)_{k \ge 0}$ where $\beta_0 = 1$ and for all $k \ge 1$:
-            \begin{align*}
-                \beta_k := \prod_{i = 0}^{k - 1}(1 - \alpha_{i + 1}) \max\left(1, \rho_i L_{i + 1}L_i^{-1}\right). 
-            \end{align*}
-            It satisfies for all $k \ge 1$ the inequality:
-            \begin{align*}
+            % Let the sequences $(x_k, y_k, v_k)$ satisfy GMAPG (Definition \ref{def:generic-mapg-ls}).
+            Let the sequences $(x_k, y_k, v_k)$ satisfy GMAPG (Definition \ref{def:generic-mapg-ls}), and take the momentum sequences $(\alpha_k)_{k \ge 0}, (\beta_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ from Definition \ref{def:alpha-beta-rho-seq}.
+            If in addition, 
+            \begin{enumerate}
+                \item The sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and, GMAPG is initialized with $L_0 \ge L$ or, equivalently a successful line search satisfying \mbox{$D_f(x_{0}, x_{-1}) \le L_0/2\Vert x_{0} - x_{-1}\Vert^2$};
+                \item $v_0=x_0 = T_{1/L_0, f, g}(x_{-1})$ for any $x_{-1} \in\RR^n$ and there exists $x^+$ which is a minimizer of $F$. 
+            \end{enumerate}
+            Then, we have the convergence of gradient mapping, it satisfies for all $k \ge 1$ the inequality:
+            \begin{align}\label{ineq:gmapg-generic-gm-cnvg-prt1}
                 \Vert \mathcal G_{1/L_k} (y_k)\Vert &\le 
@@
                 \right)\Vert x^+ - v_0\Vert. 
-            \end{align*}
+            \end{align}
+            It has also:
+            \begin{align}\label{ineq:gmapg-generic-gm-cnvg-prt2}
+                \frac{1}{2L_0}\Vert \mathcal G_{1/L_0}(x_{-1}) \Vert^2
+                \le F(x_{-1}) - F(x_0). 
+            \end{align}
         \end{theorem}
         \begin{proof}
-            The following intermediate results will be used in the proof. 
-            We stated prior to the proof for a sleeker exposition. 
+            \eqref{ineq:gmapg-generic-gm-cnvg-prt2} is direct because $x_0 = T_{1/L_0, f, g}(x_{-1})$ and \mbox{$D_f(x_{0}, x_{-1}) \le L_0/2\Vert x_{0} - x_{-1}\Vert^2$} is assumed in the statement hypothesis, using \ref{lemma:fitsa-pg-ineq} with $x = x_{-1}, z = x_{-1}$, using  gradient mapping as defined in Definition \ref{def:gm-for-ch2} it has
+            \begin{align*}
+                0 &\le F(x_{-1}) - F(x_0) + 0 - \frac{L_0}{2} \Vert x_{-1} - x_0\Vert^2
+                \\
+                &= (F(x_{-1}) - F(\bar x)) - \frac{L_0}{2}\Vert L_0^{-1}\mathcal G_{1/L_0}(x_{-1})\Vert^2. 
+            \end{align*}
+            We label the following results prior to their proofs for a sleeker exposition for the proof of \eqref{eqn:emp:result-item-2}. 
             \begin{enumerate}
@@
                 \item[(c)] The sequence $(\alpha_k)_{k \ge 0}$ has $(1 - \alpha_k)\rho_{k - 1} = \alpha_k^2/\alpha_{k - 1}^2$ from the statement hypothesis so $\alpha_k/\alpha_{k - 1} = \sqrt{\rho_{k - 1}(1 - \alpha_k)}$ for all $k \ge 1$.
-                \item[(d)] The definition of the sequence $(\beta_k)_{k \ge 0}$ stated in the statement hypothesis. 
+                \item[(d)] The definition of $(\beta_k)_{k \ge 0}$ from Definition \ref{def:alpha-beta-rho-seq}. 
             \end{enumerate}
-            From these intermediate results, the convergence can be derived. 
+            Using the above intermediate results, the convergence in \eqref{ineq:gmapg-generic-gm-cnvg-prt1} can be derived. 
             From (a) it has for all $k \ge 0$: 
@@
             The base case $k = 1$ is verified by the assumption that $x_0 = v_0 = T_{L_0} x_{-1}$. 
-            Apply the proximal gradient inequality with $x^+$ as a minimizer it yields: 
+            Apply Lemma \ref{lemma:fitsa-pg-ineq} with $z =x^+$ as a minimizer it yields: 
             \begin{align*}
@@
                 \\
-                &= \frac{L_0}{2}\left(
+                \implies 
+                0&\le \frac{L_0}{2}\left(
                     \Vert x^+ - x_{-1}\Vert- \Vert x^+ - v_0\Vert 
@@
         \begin{lemma}[specialized GMAPG momentum sequence]\;\label{lemma:gmapg-seq-bnd}\\
-            Suppose that the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 \in (0, 1]$ and for all $k \ge 1$, it satisfies $\alpha_{k - 1}^2\rho_{k - 1}(1 - \alpha_k) = \alpha_k^2$. 
-            Suppose that $(\beta_k)_{k \ge 0}$ is a sequence such that $\beta_0 = 1$ and for all $k \ge 1$ it's defined as: 
-            \begin{align*}
-                \beta_k := \prod_{i = 0}^{k - 1}(1 - \alpha_{i + 1}) \max\left(1, \rho_i L_{i + 1}L_i^{-1}\right). 
-            \end{align*}
-            If, we set $\rho_{k - 1} = L_{k}^{-1}L_{k - 1}$ such that $L_k >0$ for all $k \ge 1$, then for all $k \ge 1$ it has the inequality: 
+            % Suppose that the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 \in (0, 1]$ and for all $k \ge 1$, it satisfies $\alpha_{k - 1}^2\rho_{k - 1}(1 - \alpha_k) = \alpha_k^2$. 
+            % Suppose that $(\beta_k)_{k \ge 0}$ is a sequence such that $\beta_0 = 1$ and for all $k \ge 1$ it's defined as: 
+            Take sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}, (\beta_k)_{k \ge 0}$ as in Definition \ref{def:alpha-beta-rho-seq}. 
+            In addition, assume that $\alpha_0 = 1$. 
+            If, we set $\rho_{k - 1} = L_{k}^{-1}L_{k - 1}$ such that $L_k >0$ for all $k \ge 1$, then for all $k \ge 1$, the sequence $(\beta_k)_{k \ge 0}$ has the inequality: 
             \begin{align*}
@@
             \begin{enumerate}
-                \item[(a)] $(\beta_k)_{k \ge 0}$ is monotone decreasing and it's strictly larger than zero. 
+                \item[(a)] $(\beta_k)_{k \ge 0}$ is monotone decreasing, and it's strictly larger than zero. 
                 \item[(b)] Because $\rho_{k}L_{k + 1}L_k = 1$ for all $k \ge 0$, the definition of $(\beta_k)_{k\ge 0}$ simplifies and $\beta_k = (\alpha_k^2/\alpha_0^2)(L_k/L_0)$.
@@
         \begin{remark}
-            The techique of the proof we used here is very similar to Güler \cite[Lemma 2.2]{guler_new_1992}.
+            The technique of the proof we used here is very similar to Güler \cite[Lemma 2.2]{guler_new_1992}.
             A simpler upper bound is more practical. 
-            For all $k \ge 1$ let $\hat L_k = \max_{i = 0, 1, \ldots, k} L_i$ then 
+            For all $k \ge 1$ let $\widehat L_k = \max_{i = 0, 1, \ldots, k} L_i$ then 
             \begin{align*}
@@
                     1 + 
-                    \frac{\alpha_0 \sqrt{L_0}}{2}\sum_{i = 1}^{k}\sqrt{\hat L^{-1}_k}
+                    \frac{\alpha_0 \sqrt{L_0}}{2}\sum_{i = 1}^{k}\sqrt{L^{-1}_k}
                 \right)^{-2}
                 \le \left(
-                    1 + \frac{1}{2}\alpha_0 \sqrt{L_0}k\sqrt{\hat L^{-1}_k}
+                    1 + \frac{1}{2}\alpha_0 \sqrt{L_0}k\sqrt{\widehat L^{-1}_k}
                 \right)^{-2}
@@
                 &= \left(
-                    1 + \frac{k\alpha_0\sqrt{L_0 \hat L^{-1}_k}}{2}
-                \right)^{-2} = L^{-1}_0\hat L\left(
-                    \sqrt{L_0^{-1}\hat L_k} + \frac{k\alpha_0}{2}
+                    1 + \frac{k\alpha_0\sqrt{L_0 \widehat L^{-1}_k}}{2}
+                \right)^{-2} = L^{-1}_0\widehat L\left(
+                    \sqrt{L_0^{-1}\widehat L_k} + \frac{k\alpha_0}{2}
                 \right)^{-2}
@@
                 &\le 
-                L^{-1}_0\hat L_k\left(
+                L^{-1}_0\widehat L_k\left(
                     1 + \frac{k\alpha_0}{2}
                 \right)^{-2} 
-                = \frac{4\hat L_k}{L_0(2 + k \alpha_0)^2}. 
+                = \frac{4\widehat L_k}{L_0(2 + k \alpha_0)^2}. 
             \end{align*}
@@
             \begin{align*}
-                \hat L_k &= \max\left(
-                    L_0, \frac{1}{k} \sum_{i = 1}^{k} \sqrt{L_i^{-1}}
+                \widehat L_k &= \max\left(
+                    L_0, \left(
+                        \frac{1}{k} \sum_{i = 1}^{k} \sqrt{L_i^{-1}}
+                    \right)^{-2}
                 \right). 
@@
         \end{remark}
-        \begin{theorem}[specialized GMAPG convergence rate]\label{thm:gmapg-specialized-convergence}
+        \begin{theorem}[specialized GMAPG convergence rate]\label{thm:gmapg-specialized-cnvg}
             Suppose that $F = f + g$ satisfy Assumption \ref{ass:standard-fista}. 
@@
             \begin{align*}
-                \hat L_k = \max\left(
-                    L_0, \frac{1}{k}\sum_{i = 1}^{k} \sqrt{L_i^{-1}}
+                \widehat L_k &:= \max\left(
+                    L_0, \left(
+                        \frac{1}{k} \sum_{i = 1}^{k} \sqrt{L_i^{-1}}
+                    \right)^{-2}
                 \right). 
@@
                     F(x_k) - F(x^+) + \frac{L_k\alpha_k}{2}\Vert x^+ - v_k\Vert^2 \le 
-                    \frac{2\hat L_k}{(2 + k)^2}\Vert x^+ - x_{-1}\Vert^2.
+                    \frac{2\widehat L_k}{(2 + k)^2}\Vert x^+ - x_{-1}\Vert^2.
                 \end{align*}
@@
                     \Vert \mathcal G_{1/L_k}(y_k)\Vert \le 
-                    \frac{2\hat L_k L_k}{2 + k}
+                    \frac{2\widehat L_k L_k}{2 + k}
                     \left(
@@
             To see (i), use Lemma \ref{lemma:gmapg-seq-bnd} and its remark to bound $(\beta_k)_{k \ge 1}$ and then, apply Theorem \ref{thm:gmapg-ls-convergence} because the assumptions of $x^+, (\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ suit.
-            To see (ii), the convergence claim from \ref{thm:gmapg-generic-gradmap-convergence} simplifies with $\hat L_k \ge L_0$ and, it has 
-            \begin{align*}
+            To see (ii), the convergence claim from \ref{thm:gmapg-generic-gm-cnvg} simplifies with $\widehat L_k \ge L_0$ and, it has 
+            \begin{align}
                 \Vert \mathcal G_{1/L_k}(y_k) \Vert
@@
                 \left(
-                    \frac{2\sqrt{\hat L_kL_0}L_k}{2 + k}
+                    \frac{2\sqrt{\widehat L_kL_0}L_k}{2 + k}
                 \right)\left(
@@
                 \left(
-                    \frac{2\hat L_k L_k}{2 + k}
+                    \frac{2\widehat L_k L_k}{2 + k}
                 \right)\left(
@@
                 \right)\Vert x^+ - v_0\Vert. 
-            \end{align*}
+            \end{align}
         \end{proof}
@@
             \end{enumerate}
+
         \subsection{Monotone routines}
@@
             $G$ is the norm of the gradient mapping updated at at $\hat y$ which will be returned to the inner loop to verify exit conditions.
+
         \subsection{GMAPG main algorithm}
@@
                         }
+                        \STATE{$\overline L := \max(L_k, L_{k - 1})$. }
                         \STATE{\noindent
@@
                     \ENDFOR
-                    \STATE{\textbf{Return: }$x_k, k$}
+                    \STATE{\textbf{Return: }$x_k, k, \overline L$}
                 \caption{GMAPG with Chambolle's backtracking}\label{alg:gmapg}
@@
         We adapt and improve prior theories from Alamo \cite{alamo_restart_2019} for our GMAPG method. 
+        The following definition, gives the quadratic growth property of $f$ which allows for a fast linear convergence rate using adaptive restarts. 
+        \begin{assumption}[quadratic growth condition]\label{ass:q-growth-ch2}
+            Let $F = f + g$ satisfies Assumption \ref{ass:standard-fista} so that minimizers exists and, it's bounded below. 
+            Denote $F^+ = \inf_{x} F(x)$. 
+            Denote $X^+ = \argmin_{x} F(x)$ and for all $x \in \RR^n, \bar x \in \Pi_{X^+}x$ there exists $\mu > 0$ such that 
+            \begin{align*}
+                F(x) - F^+ &\ge \frac{\mu}{2}\Vert x - \bar x\Vert^2. 
+            \end{align*}
+        \end{assumption}
+        The following proposition about line search will furnish convergence results from previous section. 
+        \begin{proposition}[Lipschitz line search estimates are bounded]\label{prop:bnded-lip-ls}
+            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista}. 
+            Choose such $F$ for Algorithm \ref{alg:gmapg} so, it generates the sequence $(L_k)_{k\ge 0}$. 
+            Then, the sequence $(\hat L_k)_{k \ge 1}$ from Theorem \ref{thm:gmapg-specialized-cnvg} is bounded above and, it has
+            \begin{align*}
+                \widehat L_k &:= \max\left(
+                    L_0, \left(
+                        \frac{1}{k} \sum_{i = 1}^{k} \sqrt{L_i^{-1}}
+                    \right)^{-2}
+                \right)\le  \overline L \le \max\left(L_0,  2L\right). 
+            \end{align*}
+        \end{proposition}
+        \begin{proof}
+            A line search is triggered in Algorithm \ref{alg:armijo-ls}, \ref{alg:chambolle-btls} if and only if $L_{k + 1} = 2L_{k}$ for some $k \ge 0$ and, there exists some $x\in \RR^n, y \in \RR^n$ such that $D_f(x, y) > L_k\Vert x - y \Vert^2$.
+            For all $k = 0, 1, \ldots $, if $L_k \ge L$ then, it has $D_f(x, y) \le L_k/2\Vert x - y\Vert^2$ for all $x, y \in \RR^n$. 
+            Hence, $L_{k + 1} \le L_k$ because a line sarch is never triggered. 
+            \par
+            For contradiction let's assume that there exists $k \ge 1$ such that a line search is triggered for $L_k$ and, $L_{k + 1} = 2L_{k} > 2L$, then $L_k > L$, but we just showed that this implies $L_{k + 1} \le L_k$, which is a contradiction.
+            Therefore, if $L_{k + 1} = 2L_k$ then it must be that $L_k < L$ so, the highest value it can achieve is either $L_0$, or $2L$. 
+        \end{proof}
         \par
@@
             \STATE{$n_0 := 0$.}
-            \STATE{$z_1, p_0 := \textbf{GMAPG}(f, g, x_{-1}, r_j, \rho, N_{\min}=n_0, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
+            \STATE{$z_1, p_0, \overline L_1:= \textbf{GMAPG}(f, g, x_{-1}, L, r_j, \rho, N_{\min}=n_0, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
             \STATE{$n_1:=p_0. $}
@@
             \FOR{$j = 1,2, \ldots, M$}
-                \STATE{$z_{j + 1}, p_j := \textbf{GMAPG}(f, g, z_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
-                \STATE{$M := M - p_j$}
+                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1} := \textbf{GMAPG}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
+                \STATE{$M := M - p_j$.}
+                \STATE{$\overline L_{j + 1} = \max(\overline L_{j}, \overline L_{j + 1})$.}
                 \IF{$f(z_{j}) - f(z_{j + 1}) > \exp(-1)(f(z_{j - 1}) - f(z_{j}))$}
@@
         \par
-
+        Let $e$ denotes the base of natural log. 
+        The following lemma combines quadratic growth assumption of the objective to assert lower bound on the number of iteration required to achieve a certain optimality on the objective function $F$.
+        \begin{lemma}[maximum iteration needed for an optimality gap ratio]\label{lemma:prog-ratio}
+            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista}. 
+            Denote $F^+ := \inf_xF(x)$ and, let $X^+$ denotes the set of minimizers. 
+            Let the sequence $(x_k)_{k \ge -1}$ be generated by GMAPG (Definition \ref{alg:gmapg}). 
+            If in addition, $F$ satisfies the quadratic growth condition in Assumption \ref{ass:q-growth-ch2}, then 
+            \begin{align*}
+                \forall k \ge \left\lfloor \frac{2\sqrt{1 + e}}{\sqrt{\mu\widehat L_k^{-1}}}\right\rfloor:\; 
+                F(x_k) - F^+  &\le e^{-1} (F(x_{-1}) - F(x_k)). 
+            \end{align*} 
+            Where $\widehat L_k$ is defined by:
+            \begin{align*}
+                \widehat L_k &:= \max\left(
+                    L_0, \left(
+                        \frac{1}{k} \sum_{i = 1}^{k} \sqrt{L_i^{-1}}
+                    \right)^{-2}
+                \right). 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            For all $k \ge 0$, denote minimizer $x^+_k = \Pi_{X^+}x_k$ so, $F(x^+_k) = F^+$. 
+            From Theorem \ref{thm:gmapg-specialized-cnvg} it has 
+            \begin{align*}
+                F(x_k) - F^+ \le \frac{2 \widehat L_k}{(2 + k)^2}\Vert x_k - x_{-1}^+\Vert^2 \le \frac{4 \widehat L_k}{\mu(2 + k)^2}(F(x_{-1}) - F^+). 
+            \end{align*}
+            The second inequality comes from Assumption \ref{ass:q-growth-ch2} directly. 
+            Suppose that $k \ge 2\sqrt{1 + e}\left(\mu\widehat L_k^{-1}\right)^{-1/2}$. 
+            Denote $\gamma_k = 4\widehat L_k \mu^{-1}(2 + k)^{-2}$.
+            We make the following assumption first and it will be proved later:
+            \begin{enumerate}
+                \item [(a)] It has $\gamma_k \in (0, 1)$. 
+            \end{enumerate}
+            Using the above we have inequality: 
+            \begin{align*}
+                0 &\le \gamma_k (F(x_{-1}) - F^+) - (F(x_k) - F^+) 
+                \\
+                &= \gamma_k (F(x_{-1}) - F(x_k)) - (1 - \gamma_k)(F(x_{k}) - F^+). 
+                \\
+                \underset{\text{(a)}}{\iff} F(x_k) - F^+
+                &\le \gamma_k(1 - \gamma_k)^{-1}(F(x_{-1}) - F(x_k)). 
+            \end{align*}
+            Continuing it has 
+            \begin{align*}
+                F(x_k) - F^+ &\le \gamma_k (1 -\gamma_k)^{-1}(F(x_{-1}) - F^+)
+                \\
+                &= \frac{4\widehat L_k}{\mu(2 + k)^{2}}\left(
+                    1 - \frac{4\widehat L_k}{\mu(2 + k)^2}
+                \right)^{-1}(F(x_{-1}) - F^+)
+                \\
+                &= 4\widehat L_k(\mu(2 + k)^2 - 4 \widehat L_k)(F(x_{-1}) - F^+)
+                \\
+                &\le 4\widehat L_k\left(
+                    \mu\left(
+                        2 + \left\lfloor \frac{2\sqrt{1 + e}}{\sqrt{\mu/\widehat L_k}}\right\rfloor
+                    \right)^2 - 4 \widehat L_k
+                \right)^{-1}(F(x_{-1}) - F^+)
+                \\
+                &\le 4\widehat L_k\left(
+                    \mu\left(
+                        \frac{2\sqrt{1 + e}}{\sqrt{\mu/\widehat L_k}} 
+                    \right)^2 - 4 \widehat L_k
+                \right)^{-1}(F(x_{-1}) - F^+)
+                \\
+                &\le 4\widehat L_k\left(
+                    \mu\left(
+                        \frac{4(1 + e)\widehat L_k}{\mu}
+                    \right) - 4 \widehat L_k
+                \right)^{-1}(F(x_{-1}) - F^+)
+                \\
+                &= 4\widehat L_k\left(
+                    4\widehat L_k(1 + e)
+                    - 4 \widehat L_k
+                \right)^{-1}(F(x_{-1}) - F^+)
+                =e^{-1} (F(x_{-1}) - F^+). 
+            \end{align*}
+            \textbf{The proof for (a)} now follows. 
+            From the assumption on $k$ it has: 
+            {\allowdisplaybreaks
+            \begin{align*}
+                0 &\ge \left\lfloor 
+                    \frac{2\sqrt{1 + e}}{\sqrt{\mu/\widehat L_k}}
+                \right\rfloor - k
+                > \frac{2\sqrt{1 + e}}{\sqrt{\mu/\widehat L_k}} - 1- k
+                > 
+                \frac{2}{\sqrt{\mu/\widehat L_k}} - 1- k
+                \\
+                &> \frac{2}{\sqrt{\mu/\widehat L_k}} - (2 + k)
+                =(2 + k)\left(
+                    \frac{2}{(k + 2)\sqrt{\mu/\widehat L_k}} - 1
+                \right)
+                \\
+                &= (2 + k)(\sqrt{\gamma_k} - 1). 
+            \end{align*}
+            }
+        \end{proof}
+        \par
+        Continuing with the quadratic growth assumption, the following lemma states the fact that $p_j$ in Algorithm \ref{alg:linear-rgmapg} is bounded above and there exists a for $p_j$ such that $n_{j + 1 + k} = p_{j + k}$ for all $k \ge 0$ until it terminates.
         \begin{lemma}[bounds on inner iteration counts]

### 2025-05-28 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
                     \ENDFOR
-                    \STATE{\textbf{Return: }$x_k, k, \overline L$}
+                    \STATE{\textbf{Return: }$x_k, k, \overline L, G_k^+ $}
                 \caption{GMAPG with Chambolle's backtracking}\label{alg:gmapg}
@@
         The inner loop algorithm is described in Algorithm \ref{alg:gmapg}, let $k$ denote the inner loop counter and define $m = \lfloor k/2 \rfloor + 1$ the conditions are: 
-        \begin{align*}
+        \begin{align}\label{ineq:rgmapg-exit-cond}
             \mathbf E_{\chi}^a \iff 
             f(x_m) - f(x_k) \le \exp(-1)(f(x_0) - f(x_m)). 
-        \end{align*}
+        \end{align}
         \begin{algorithm}[H]
@@
             \end{tabular}}
-            \STATE{$n_0 := 0$.}
+            \STATE{$n_0 := 0; z_0 = x_{-1}$.}
             \STATE{$z_1, p_0, \overline L_1:= \textbf{GMAPG}(f, g, x_{-1}, L, r_j, \rho, N_{\min}=n_0, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
@@
             \FOR{$j = 1,2, \ldots, M$}
-                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1} := \textbf{GMAPG}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
+                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1}, G_k^+ := \textbf{GMAPG}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
                 \STATE{$M := M - p_j$.}
+                \IF{$M \le 0 \textbf{ or } G_k^+ \le \epsilon$}
+                    \STATE{\textbf{break}}                
+                \ENDIF
                 \STATE{$\overline L_{j + 1} = \max(\overline L_{j}, \overline L_{j + 1})$.}
@@
         Since the restarted GMAPG consist of executions of an outer loop in Algorithm \ref{alg:linear-rgmapg} in variable $j$ and, an inner loop in Algorithm \ref{alg:gmapg} in variable $k$, we denote $z_{j, k}$ for the iterates $x_k$ in the inner loop and $z_j$ in the outer loop together.
-        We make the rule that $z_{j + 1, -1} = z_{j, p_j}$ for compatibility of the theorems in the previous sections. 
-        For example in line 7 at the $j$ iteration, the inner loop returns $x_{p_j}$ as the last iterate of the inner loop and, it's assigned to $z_{j + 1}$ by the outer loop. 
-        In that case we denote $z_{j + 1, -1}$ as the initial iterate pass into the inner loop for the $j + 1$ iteration, and $z_{j, p_j}$ would denote the last iteration before exiting the inner loop for the $j$ th iteration of the outer loop.
-        Therefore, $z_{j + 1, -1} = z_{j, p_j}$ and all iterates generated by the inner loop is the finite sequence $(z_{j, k})_{k = 0}^{p_j}$. 
+        We make the choice to have $z_{j + 1, -1} = z_{j, p_j} = z_{j + 1}$ for consistencies across theorems from previous sections. 
+        For example in line 7 of Algorithm \ref{alg:linear-rgmapg} at the $j$ iteration, the inner loop returns $x_{p_j}$ as the last iterate.
+Denote $x_{p_j}$ as $z_{j, p_j}$ and, it's assigned to $z_{j + 1}$ by the outer loop so $x_{p_j} = z_{j, p_j} = z_{j + 1}$.
+        It continues and $z_{j + 1}$ will be the initial iterate pass into the inner loop for the $j + 1$ iteration, and hence $z_{j + 1} =z_{j + 1, -1}$. 
         \par
@@
         The following lemma combines quadratic growth assumption of the objective to assert lower bound on the number of iteration required to achieve a certain optimality on the objective function $F$.
-        \begin{lemma}[maximum iteration needed for an optimality gap ratio]\label{lemma:prog-ratio}
-            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista}. 
-            Denote $F^+ := \inf_xF(x)$ and, let $X^+$ denotes the set of minimizers. 
+        \begin{lemma}[maximum iteration needed for an optimality gap ratio]\;\label{lemma:prog-ratio}\\
+            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista} so $F^+ := \inf_xF(x)$ and, $X^+$ is the set of minimizers. 
             Let the sequence $(x_k)_{k \ge -1}$ be generated by GMAPG (Definition \ref{alg:gmapg}). 
@@
         Continuing with the quadratic growth assumption, the following lemma states the fact that $p_j$ in Algorithm \ref{alg:linear-rgmapg} is bounded above and there exists a for $p_j$ such that $n_{j + 1 + k} = p_{j + k}$ for all $k \ge 0$ until it terminates.
-        \begin{lemma}[bounds on inner iteration counts]
-            ...
+        \begin{lemma}[inner iteration is bounded above]\label{lemma:rgmapg-inner-bnds}
+            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista} so $F^+ := \inf_xF(x)$ and, $X^+$ is the set of minimizers. 
+            Consider any $j \ge 1$ iteration experienced by the outer loop. 
+            Let $(z_{j,k})_{k\ge 0}^{p_{j}}$ be the sequence generated by Algorithm \ref{alg:linear-rgmapg} in the $j$ th iteration of outer loop. 
+            Define $\bar p := \frac{4\sqrt{2L(1 + e)}}{\sqrt{\mu}}$, then $p_{j} \le \bar p$. 
         \end{lemma}
         \begin{proof}
-
+            The end result is constructed upon the following intermediate results that are proved at the end: 
+            \begin{enumerate}
+                \item [(i)] If $k \ge \bar p$, then exit condition $\mathbf E_{\chi}^a$ is true hence $p_j \le \max(\bar p, n_j)$ for all $j \ge 0$. 
+                \item [(ii)] If $p_{j - 1} \le p_j\le \bar p$  then $n_{j + 1} \le \bar p$. 
+            \end{enumerate}
+            Take note that $n_0 = 0, n_1 = p_0$ hence (i) gives $p_0 \le \bar p$, and $p_1 \le \max(\bar p, n_1) = \max(\bar p, p_0) \le \bar p$. 
+            We now have the base case: $p_0 \le p_1 \le \bar p$. 
+            Inductively assume $p_{j - 1} \le p_j \le \bar p$ then: 
+            \begin{align*}
+                p_{j + 1} \underset{\text{(i)}}{\le} \max(\bar p, n_{j + 1}) \underset{\text{(ii)}}{\le} \bar p. 
+            \end{align*}
+            Therefore, for all $j \ge 0$, $p_j \le \bar p$. 
+            \par
+            \textbf{Proof of (i)}. 
+            Recall exit condition in \eqref{ineq:rgmapg-exit-cond} has $m = \lfloor k/2\rfloor + 1$. 
+            Starting with the statement hypothesis it has $k \ge \ bar p$ therefore: 
+            \begin{align*}
+                0 &\le k/2 - \bar p/2 \le \lfloor k/2\rfloor + 1 - \bar p/2
+                = m - \bar p /2 \le m - \lfloor \bar p/2\rfloor
+                \\
+                &= m - \left\lfloor 
+                    \frac{2\sqrt{2L(1 + e)}}{\sqrt{\mu}}
+                \right\rfloor \le 
+                m - \left\lfloor 
+                    \frac{2\sqrt{\widehat L_k(1 + e)}}{\sqrt{\mu}}
+                \right\rfloor
+            \end{align*}
+            On the last inequality we used Proposition \ref{prop:bnded-lip-ls} which has $\widehat L_k \le 2 L$. 
+            Observe that the inequality allow us to apply Lemma \ref{lemma:prog-ratio} with $m = k$ which yields: 
+            \begin{align*}
+                e^{-1} \ge \frac{F(z_{j, m}) - F^+}{F(z_{j, -1}) - F(z_{j, m})} \ge \frac{F(z_{j, m}) - F(z_{j, k})}{F(z_{j, -1}) - F(z_{j, m})} \implies \mathbf E_{\chi}^a. 
+            \end{align*}
+            Observe that line 11 of Algorithm \ref{alg:gmapg} exits as soon as possible if $E_\chi^a$ is true and $k > N_{\min} = n_j$ and, $G_k \le \epsilon$ will only cause it to exit earlier therefore $p_j \le \max(\bar p, n_j)$.
+            \par
+            \textbf{Proof of (ii)}. 
+            Inductively assume that $p_{j - 1} \le p_j \le \bar p$. 
+            If $p_{j - 1} \le \bar p /2$ then Line 14, 16 implies that $n_{j} \le \max(p_{j - 1}, 2p_{j - 1}) \le \bar p$. 
+            Otherwise, $p_{j - 1} > \bar p/2$, and using Proposition \ref{prop:bnded-lip-ls} it means 
+            \begin{align*}
+                p_{j - 1} \ge \bar p /2 = \frac{2\sqrt{2L(1 + e)}}{\sqrt{\mu}} \ge \left \lfloor \frac{2\sqrt{\widehat L_k(1 + e)}}{\sqrt{\mu}} \right\rfloor. 
+            \end{align*}
+            The above inequality allows us to use Lemma \ref{lemma:prog-ratio} which yields 
+            \begin{align*}
+                e^{-1} \ge \frac{F(z_{j - 1, p_{j - 1}}) - F^+}
+                {F(z_{j - 1, -1}) - F(z_{j - 1, p_{j - 1}})}
+                \ge 
+                \frac{F(z_j) - F(z_{j + 1})}
+                {F(z_{j - 1}) - F(z_{j})} \implies n_{j + 1} = p_{j + 1}.
+            \end{align*}
+            Therefore, there is no doubling at line 14 of Algorithm \ref{alg:linear-rgmapg}, hence $n_{j + 1} \le \bar p$ still. 
         \end{proof}
+        \par
+        We just show that the sequence $n_j$ is bounded above, and it must have a limit because it's also monotone increasing, which implies that at some point, the doubling of $n_{j + 1} = 2p_j$ must stop for the outer loop.
+        The following lemma shows that when that happens, the algorithm will always terminate after a finite number of iterations of the outer loop. 
         \begin{lemma}[bounds on outer iteration counts]

### 2025-05-28 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
             \begin{enumerate}
-                \item[(a)] From Definition \ref{def:generic-mapg-ls}, the gradient mapping satisfies for all $k \ge 1$ that $\Vert \mathcal G_{1/L_k} y_k\Vert = L_k\alpha_k \Vert v_k - v_{k - 1}\Vert$.
+                \item[(a)] From Definition \ref{def:generic-mapg-ls}, the gradient mapping satisfies for all $k \ge 1$ that $\Vert \mathcal G_{1/L_k} (y_k)\Vert = L_k\alpha_k \Vert v_k - v_{k - 1}\Vert$.
                 \item[(b)] We have $(a_k)_{k \ge 1}$ satisfying $\forall k \ge 1$ that $(1 - \alpha_k)\rho_{k - 1} = \alpha_k^2/\alpha_{k - 1}^2$ from the statement hypothesis.
@@
             \begin{align*}
-                \Vert \mathcal G_{1/L_k} y_k\Vert 
+                \Vert \mathcal G_{1/L_k} (y_k)\Vert 
                 &= L_k\alpha_k \Vert v_k - v_{k - 1}\Vert
@@
                     \STATE{$x_0, y_0,\alpha_1, L_0 := \textbf{ArmijoLS}(f, g, x_{-1}, x_{-1}, L, \alpha_0)$.}
-                    \STATE{$\eta_0 := L_0; v_0 := x_0; G_0 = L_0(x_0 - y_0).$}
+                    \STATE{$\eta_0 := L_0; v_0 := x_0; G_0 = \Vert \sqrt{L_0}(x_0 - y_0)\Vert.$}
+                    \IF{$G_0 \le \epsilon$}
+                        \STATE{\textbf{Return: }$x_k, 0, L_0, G_0$}
+                    \ENDIF
                     \FOR{$k := 1, 2,\ldots, N$}
@@
                         }
-                        \STATE{$G_k:= L_k(\tilde x_k - y_k)$}
+                        \STATE{$G_k:= \Vert \sqrt L_k(\tilde x_k - y_k)\Vert $}
                         \STATE{\noindent
@@
             \mathbf E_{\chi}^a \iff 
-            f(x_m) - f(x_k) \le \exp(-1)(f(x_0) - f(x_m)). 
+            f(x_m) - f(x_k) \le \exp(-1)(f(x_{-1}) - f(x_m)). 
         \end{align}
@@
         The following observation on it is crucial to take notice for the convergence rate. 
-        \par
-        $n_j$ is used as the lower bound $N_{\min}$ for the GMAPG inner loop described in Algorithm \ref{alg:gmapg} at iteration $j$ and, $p_j$ is the actual iteration underwent by the inner loop and, it has $p_j \ge n_{j}$.
+        \begin{observation}
+            If the outer loop runs for $j = 1, 2, \ldots, J$ iterations with $M \ge J$ so the algorithm terminated due $G_k^+ \le \epsilon$. 
+            Then for all $J\ge j\ge 1$ it has $n_{j}\le n_{j + 1}$ hence $(n_j)_{j \ge 0}^J$ is monotone increasing
+            For all $J -1 \ge j \ge 1 $ it has $p_{j-1}\le p_{j}$ so $(p_j)_{j \ge 1}^{J}$ is monotone exluding the last iterates $p_J$. 
+        \end{observation}
+        \par
+        For all $1 \le j \le J$, $n_j$ is used as the lower bound $N_{\min}$ for the GMAPG inner loop described in Algorithm \ref{alg:gmapg} at iteration $j$ and, $p_j$ is the actual iteration underwent by the inner loop therefore it has $p_j \ge n_{j}$.
         $n_{j + 1}$ is the minimum iteration for the next execution of GMAGP, and it has $n_{j + 1} = p_{j}$  if the ``if statement" isn't triggered otherwise $n_{j + 1} = 2p_{j}$. 
-        Consequently, it has either $p_{j + 1} \ge n_{j + 1} = 2p_j$ or $p_{j + 1} \ge n_{j + 1} = p_j$. 
+        For $j < J$ so it excludes the last iteration, it has either $p_{j + 1} \ge n_{j + 1} = 2p_j \ge 2n_{j} \ge n_j$ or $p_{j + 1} \ge n_{j + 1} = p_j \ge n_j$. 
+        When $j = J$ it's not necessarily true that $p_J \ge n_J$ because on the last iteration, it can exit the forloop through conditions $G_k^+ \le \epsilon$ in line 14 of Algorithm \ref{alg:gmapg}, but $n_J \ge p_{J - 1} \ge n_{J - 1}$ still.
         \par
         We now introduce the following notations for the convergence proof. 
-        Since the restarted GMAPG consist of executions of an outer loop in Algorithm \ref{alg:linear-rgmapg} in variable $j$ and, an inner loop in Algorithm \ref{alg:gmapg} in variable $k$, we denote $z_{j, k}$ for the iterates $x_k$ in the inner loop and $z_j$ in the outer loop together.
-        We make the choice to have $z_{j + 1, -1} = z_{j, p_j} = z_{j + 1}$ for consistencies across theorems from previous sections. 
+        Since the restarted GMAPG consist of executions of an outer loop in Algorithm \ref{alg:linear-rgmapg} in variable $j$ and, an inner loop in Algorithm \ref{alg:gmapg} in variable $k$, we denote $x_{k}^{(j)}$ for the iterates $x_k$ in the inner loop during the $j$ iteration of the outer loop together.
+        We make the choice to have $x_{-1}^{(j + 1)} = z_{j + 1} = x_{p_j}^{(j)}$ for consistencies across theorems from previous sections. 
         For example in line 7 of Algorithm \ref{alg:linear-rgmapg} at the $j$ iteration, the inner loop returns $x_{p_j}$ as the last iterate. 
-Denote $x_{p_j}$ as $z_{j, p_j}$ and, it's assigned to $z_{j + 1}$ by the outer loop so $x_{p_j} = z_{j, p_j} = z_{j + 1}$.
-        It continues and $z_{j + 1}$ will be the initial iterate pass into the inner loop for the $j + 1$ iteration, and hence $z_{j + 1} =z_{j + 1, -1}$. 
+        So $x_{p_j}$ is assigned to assigned to $z_{j + 1}$ by the outer loop and it has $x_{p_j} = x_{p_j}^{(j)} = z_{j + 1}$. 
+        It continues and $z_{j + 1}$ will be the initial iterate pass into the inner loop for the $j + 1$ iteration, and hence $z_{j + 1} =x_{-1}^{(j + 1)}$. 
         \par
@@
             Denote $\gamma_k = 4\widehat L_k \mu^{-1}(2 + k)^{-2}$.
-            We make the following assumption first and it will be proved later:
+            We make the following assumption first, and it will be proved later:
             \begin{enumerate}
@@
         \par
-        Continuing with the quadratic growth assumption, the following lemma states the fact that $p_j$ in Algorithm \ref{alg:linear-rgmapg} is bounded above and there exists a for $p_j$ such that $n_{j + 1 + k} = p_{j + k}$ for all $k \ge 0$ until it terminates.
+        Continuing with the quadratic growth assumption, the following lemma states the fact that $p_j$ in Algorithm \ref{alg:linear-rgmapg} is bounded above and there exists a $j \ge 1$ such that $n_{j + 1 + k} = p_{j + k}$ for all $k \ge 0$ until it terminates.
         \begin{lemma}[inner iteration is bounded above]\label{lemma:rgmapg-inner-bnds}
-            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista} so $F^+ := \inf_xF(x)$ and, $X^+$ is the set of minimizers. 
+            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista} and Assumption \ref{ass:q-growth-ch2}, denote $F^+ := \inf_xF(x)$ and, $X^+$ as the set of minimizers. 
             Consider any $j \ge 1$ iteration experienced by the outer loop. 
-            Let $(z_{j,k})_{k\ge 0}^{p_{j}}$ be the sequence generated by Algorithm \ref{alg:linear-rgmapg} in the $j$ th iteration of outer loop. 
-            Define $\bar p := \frac{4\sqrt{2L(1 + e)}}{\sqrt{\mu}}$, then $p_{j} \le \bar p$. 
+            Let $\left(x_{k}^{(j)}\right)_{k\ge 0}^{p_{j}}$ be the sequence generated by Algorithm \ref{alg:linear-rgmapg} in the $j$ th iteration of outer loop. 
+            Define $\bar p := \frac{4\sqrt{2L(1 + e)}}{\sqrt{\mu}}$, then $p_{j} \le \bar p, n_j \le \bar p$. 
         \end{lemma}
@@
             Take note that $n_0 = 0, n_1 = p_0$ hence (i) gives $p_0 \le \bar p$, and $p_1 \le \max(\bar p, n_1) = \max(\bar p, p_0) \le \bar p$. 
-            We now have the base case: $p_0 \le p_1 \le \bar p$. 
+            We now have the base case: $p_0 \le p_1 = n_0 \le \bar p$. 
             Inductively assume $p_{j - 1} \le p_j \le \bar p$ then: 
@@
             \end{align*}
-            Therefore, for all $j \ge 0$, $p_j \le \bar p$. 
+            Therefore, for all $j \ge 0$, $p_j \le \bar p$, and $n_{j + 1} \le \bar p$. 
             \par
@@
             Recall exit condition in \eqref{ineq:rgmapg-exit-cond} has $m = \lfloor k/2\rfloor + 1$. 
-            Starting with the statement hypothesis it has $k \ge \ bar p$ therefore: 
+            Starting with the statement hypothesis it has $k \ge \bar p$ therefore: 
             \begin{align*}
@@
                     \frac{2\sqrt{\widehat L_k(1 + e)}}{\sqrt{\mu}}
-                \right\rfloor
+                \right\rfloor. 
             \end{align*}
@@
             \begin{align*}
-                e^{-1} \ge \frac{F(z_{j, m}) - F^+}{F(z_{j, -1}) - F(z_{j, m})} \ge \frac{F(z_{j, m}) - F(z_{j, k})}{F(z_{j, -1}) - F(z_{j, m})} \implies \mathbf E_{\chi}^a. 
-            \end{align*}
-            Observe that line 11 of Algorithm \ref{alg:gmapg} exits as soon as possible if $E_\chi^a$ is true and $k > N_{\min} = n_j$ and, $G_k \le \epsilon$ will only cause it to exit earlier therefore $p_j \le \max(\bar p, n_j)$.
+                e^{-1} \ge 
+                \frac{
+                    F\left(x_{m}^{(j)}\right) - F^+
+                }{
+                    F\left(x_{-1}^{(j)}\right) 
+                    - F\left(x_{m}^{(j)}\right)
+                } 
+                \ge 
+                \frac{
+                    F\left(x_{m}^{(j)}\right)
+                    - F\left(x_k^{(j)}\right)
+                }{
+                    F\left(x_{-1}^{(j)}\right) 
+                    - F\left(x_{m}^{(j)}\right)
+                } 
+                \implies \mathbf E_{\chi}^a. 
+            \end{align*}
+            Observe that line 14 of Algorithm \ref{alg:gmapg} exits as soon as possible if $\mathbf E_\chi^a$ is true and $k > N_{\min} = n_j$ and, $G_k \le \epsilon$ will only cause it to exit earlier therefore it has $p_j \le \max(\bar p, n_j)$.
             \par
@@
             Inductively assume that $p_{j - 1} \le p_j \le \bar p$. 
-            If $p_{j - 1} \le \bar p /2$ then Line 14, 16 implies that $n_{j} \le \max(p_{j - 1}, 2p_{j - 1}) \le \bar p$. 
+            If $p_{j - 1} \le \bar p /2$ then Line 14, 16 in Algorithm \ref{alg:linear-rgmapg} implies that $n_{j} \le \max(p_{j - 1}, 2p_{j - 1}) \le \bar p$. 
             Otherwise, $p_{j - 1} > \bar p/2$, and using Proposition \ref{prop:bnded-lip-ls} it means 
             \begin{align*}
-                p_{j - 1} \ge \bar p /2 = \frac{2\sqrt{2L(1 + e)}}{\sqrt{\mu}} \ge \left \lfloor \frac{2\sqrt{\widehat L_k(1 + e)}}{\sqrt{\mu}} \right\rfloor. 
+                p_{j - 1} \ge \bar p /2 = \frac{2\sqrt{2L(1 + e)}}{\sqrt{\mu}} 
+                \ge 
+                \left \lfloor \frac{2\sqrt{\widehat L_k(1 + e)}}{\sqrt{\mu}} \right\rfloor. 
             \end{align*}
@@
             \begin{align*}
-                e^{-1} \ge \frac{F(z_{j - 1, p_{j - 1}}) - F^+}
-                {F(z_{j - 1, -1}) - F(z_{j - 1, p_{j - 1}})}
+                e^{-1} \ge 
+                \frac{
+                    F\left(x_{p_{j - 1}}^{(j - 1)}\right) - F^+
+                }
+                {
+                    F\left(x_{-1}^{(j - 1)}\right) - F\left(z_{p_{j - 1}}^{(j - 1)}\right)
+                }
                 \ge 
@@
         \end{lemma}
-
+        \begin{proof}
+            Suppose that since the $j\ge 2$ th iteration, there is no period doubling for $T_\epsilon$ number of iterations in the outer loop of Algorithm \ref{alg:linear-rgmapg}, i.e: $n_{j + k + 1} = p_{j + k}$ for $ 0 \le k \le T_\epsilon - 1$.
+
+        \end{proof}
         \begin{theorem}[bounds on the total iterations]
@@
         \end{theorem}
+        \begin{proof}
+
+        \end{proof}
+        \begin{theorem}[convergence rates of restarted GMAPG]
+
+        \end{theorem}
 

### 2025-05-28 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
         \begin{proof}
-            Suppose that since the $j\ge 2$ th iteration, there is no period doubling for $T_\epsilon$ number of iterations in the outer loop of Algorithm \ref{alg:linear-rgmapg}, i.e: $n_{j + k + 1} = p_{j + k}$ for $ 0 \le k \le T_\epsilon - 1$.
-
+            Suppose that since the $j\ge 2$ th iteration, there is no period doubling for $T_\epsilon$ number of iterations in the outer loop of Algorithm \ref{alg:linear-rgmapg}, i.e: $n_{t + 1} = p_t$
+            for $j \le t \le j + T_\epsilon - 1$, and denote $s = j + T_\epsilon -1$ for better notations, giving us $j \le t \le s$. 
         \end{proof}

### 2025-05-28 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
             \begin{definition}[weakly convex function]\;\label{def:wcnvx-fxn}\\
-                Let $f: \RR^n \rightarrow\overline \RR$ be an l.s.c proper function. 
+                Let $F: \RR^n \rightarrow\overline \RR$ be an l.s.c proper function. 
                 We define $F$ to be $q$ weakly convex if there exists $q \ge 0$ such that the function $F + q/2\Vert \cdot\Vert^2$ is a convex function and $q$ is the infimum of all such possible parameters.
@@
             \begin{remark}
-                If $q = 0$, $f$ is convex or strongly convex. 
-                If $f$ is weakly convex, then $f + 1/2\Vert \cdot\Vert^2$ is convex and, it has $\dom f$ convex, and locally Lipschitz continuous on $\reli \dom f$. 
+                If $q = 0$, $F$ is convex.
+                If $F$ is weakly convex, then $F + q/2\Vert \cdot\Vert^2$ is convex and, it has $\dom F$ convex, and locally Lipschitz continuous on $\reli \dom F$. 
             \end{remark}
@@
                 \end{align*}
-                Optimizing $x\mapsto x - x^2(1_g - L)/2$ yields $x = (q_g - L)^{-1}$ so $\beta = q_g - L$ gives the most amount of descent. 
-                Consider any $\beta \ge (q_g - L)$: 
-                \begin{align*}
-                    &\le F(x) - F(\bar x) - \left(
+                % Optimizing $x\mapsto x - x^2(q_g + L)/2$ yields $x = (q_g + L)^{-1}$ so $\beta = q_g - L$ gives the most amount of descent. 
+                Consider any $\beta \ge (q_g + L)$: 
+                \begin{align*}
+                    0 &\le F(x) - F(\bar x) - \left(
                         \beta^{-1} - \frac{q_g + L}{2\beta^2}
@@
                     &= 
-                    F(x) - F(\bar x) + \frac{1}{2\beta}\Vert\mathcal G_{1/\beta}(x) \Vert^2. 
+                    F(x) - F(\bar x) - \frac{1}{2\beta}\Vert\mathcal G_{1/\beta}(x) \Vert^2. 
                 \end{align*}
@@
         \begin{theorem}[convergence of Nesterov's monotone scheme nonconvex]\;\label{thm:nes-mono-wcnvx-convergence}\\
-            Suppose that the sequences $(y_{k + 1}, v_k, x_k)_{k \ge 0}$ and $(\hat y_k, \tilde x_k)_{k \ge 0}$, $(\alpha_k)_{k \ge 0}$ satisfy Definition \ref{alg:nes-mono}. 
+            Suppose that the sequences $(y_{k + 1}, v_k, x_k)_{k \ge 0}$ and $(\hat y_k, \tilde x_k)_{k \ge 0}$, $(\alpha_k)_{k \ge 0}$ satisfy Definition \ref{def:nes-monotone-scheme}. 
             Assume that $F$ is bounded below with $F^+ := \inf_{x}F(x)$. 

### 2025-05-29 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
     Restart is a technique discussed in Necoara et al. \cite{necoara_linear_2019}.
-    They showed that there exists an optimal restarting interval to achieve fast line convergence rate for all functions with quadratic growth condition. 
+    They showed that there exists an optimal restarting interval to achieve fast linear convergence rate for all functions with quadratic growth condition. 
     The method of restarting was improved to be parameter free while still retaining a fast linear convergence rate, see Alamo et al.
@@
         \subsection{smooth plus nonsmooth weakly convex}
+            \begin{definition}[weakly convex function]\;\label{def:wcnvx-fxn}\\
+                Let $F: \RR^n \rightarrow\overline \RR$ be an l.s.c proper function. 
+                We define $F$ to be $q$ weakly convex if there exists $q \ge 0$ such that the function $F + q/2\Vert \cdot\Vert^2$ is a convex function and $q$ is the infimum of all such possible parameters.
+            \end{definition}
+            \begin{remark}
+                If $q = 0$, $F$ is convex.
+                If $F$ is weakly convex, then $F + q/2\Vert \cdot\Vert^2$ is convex and, it has $\dom F$ convex, and locally Lipschitz continuous on $\reli \dom F$. 
+            \end{remark}
             \begin{assumption}[sum of weakly convex smooth and nonsmooth]\;\label{ass:sum-of-wcnvx}\\
@@
             \begin{remark}
-                If a function is $L$ smooth, it also be $L$ weakly convex. 
+                If a function is $L$ smooth, it's $L$ weakly convex also. 
                 Here we defined $q_f$ because the actual weakly convex constant may be much smaller than $L$, and it is true in the case when $g$ is in fact convex.  
-            \end{remark}
-            \begin{definition}[weakly convex function]\;\label{def:wcnvx-fxn}\\
-                Let $F: \RR^n \rightarrow\overline \RR$ be an l.s.c proper function. 
-                We define $F$ to be $q$ weakly convex if there exists $q \ge 0$ such that the function $F + q/2\Vert \cdot\Vert^2$ is a convex function and $q$ is the infimum of all such possible parameters.
-            \end{definition}
-            \begin{remark}
-                If $q = 0$, $F$ is convex.
-                If $F$ is weakly convex, then $F + q/2\Vert \cdot\Vert^2$ is convex and, it has $\dom F$ convex, and locally Lipschitz continuous on $\reli \dom F$. 
             \end{remark}
@@
                 $$
-                And descent is possible when $\beta \ge (L + q_g)/2$ and it yields the descent lemma: 
-                \begin{align*}
-                    0 &\le F(x) - F(\bar x) - 1/\beta \Vert \mathcal G_{1/\beta}(x)\Vert^2. 
-                \end{align*}
-                The maximum amount of descent is achieved when $\beta = L + q_g$. 
+                And descent is possible when $\beta \ge (L + q_g)/2$ and, it yields the descent lemma: 
+                \begin{align*}
+                    F(\bar x) - F(x) &\le - 1/\beta \Vert \mathcal G_{1/\beta}(x)\Vert^2. 
+                \end{align*}
             \end{lemma}
@@
         \begin{lemma}[specialized GMAPG momentum sequence]\;\label{lemma:gmapg-seq-bnd}\\
-            % Suppose that the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 \in (0, 1]$ and for all $k \ge 1$, it satisfies $\alpha_{k - 1}^2\rho_{k - 1}(1 - \alpha_k) = \alpha_k^2$. 
-            % Suppose that $(\beta_k)_{k \ge 0}$ is a sequence such that $\beta_0 = 1$ and for all $k \ge 1$ it's defined as: 
             Take sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}, (\beta_k)_{k \ge 0}$ as in Definition \ref{def:alpha-beta-rho-seq}. 
@@
                 \item[(a)] $(\beta_k)_{k \ge 0}$ is monotone decreasing, and it's strictly larger than zero. 
-                \item[(b)] Because $\rho_{k}L_{k + 1}L_k = 1$ for all $k \ge 0$, the definition of $(\beta_k)_{k\ge 0}$ simplifies and $\beta_k = (\alpha_k^2/\alpha_0^2)(L_k/L_0)$.
+                \item[(b)] Because $\rho_{k}L_{k + 1}L_k^{-1} = 1$ for all $k \ge 0$, the definition of $(\beta_k)_{k\ge 0}$ simplifies and $\beta_k = (\alpha_k^2/\alpha_0^2)(L_k/L_0)$.
 As a consequence it also gives for all $k \ge 1$ that:
@@
         This is necessary because Nesterov's monotone variants can adapt to weakly convex objective functions. 
-        The following assumption will characterize the full scope of discussion in nonconvexity objective function. 
+        The following assumption will characterize the full scope of discussion in nonconvex objective function. 
         \begin{definition}[nonconvex Nesterov's monotone scheme]\;\label{def:nes-monotone-scheme}\\
@@
             \STATE{$z_1, p_0, \overline L_1:= \textbf{GMAPG}(f, g, x_{-1}, L, r_j, \rho, N_{\min}=n_0, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
-            \STATE{$n_1:=p_0. $}
-            \STATE{$M := M - n_1$}
+            \STATE{$n_1:=p_0$.}
+            \STATE{$M := M - n_1$.}
             \FOR{$j = 1,2, \ldots, M$}
@@
         The following observation on it is crucial to take notice for the convergence rate. 
-        \begin{observation}
+        \begin{observation}\label{obs:rgmapg}
             If the outer loop runs for $j = 1, 2, \ldots, J$ iterations with $M \ge J$ so the algorithm terminated due $G_k^+ \le \epsilon$. 
             Then for all $J\ge j\ge 1$ it has $n_{j}\le n_{j + 1}$ hence $(n_j)_{j \ge 0}^J$ is monotone increasing
-            For all $J -1 \ge j \ge 1 $ it has $p_{j-1}\le p_{j}$ so $(p_j)_{j \ge 1}^{J}$ is monotone exluding the last iterates $p_J$. 
+            For all $J -1 \ge j \ge 1 $ it has $p_{j-1}\le p_{j}$ so $(p_j)_{j \ge 1}^{J}$ is monotone excluding the last iterates $p_J$. 
         \end{observation}
@@
         For $j < J$ so it excludes the last iteration, it has either $p_{j + 1} \ge n_{j + 1} = 2p_j \ge 2n_{j} \ge n_j$ or $p_{j + 1} \ge n_{j + 1} = p_j \ge n_j$. 
-        When $j = J$ it's not necessarily true that $p_J \ge n_J$ because on the last iteration, it can exit the forloop through conditions $G_k^+ \le \epsilon$ in line 14 of Algorithm \ref{alg:gmapg}, but $n_J \ge p_{J - 1} \ge n_{J - 1}$ still.
+        When $j = J$ it's not necessarily true that $p_J \ge n_J$ because on the last iteration, it can exit the for loop through conditions $G_k^+ \le \epsilon$ in line 14 of Algorithm \ref{alg:gmapg}, but $n_J \ge p_{J - 1} \ge n_{J - 1}$ still.
         \par
@@
         For example in line 7 of Algorithm \ref{alg:linear-rgmapg} at the $j$ iteration, the inner loop returns $x_{p_j}$ as the last iterate. 
-        So $x_{p_j}$ is assigned to assigned to $z_{j + 1}$ by the outer loop and it has $x_{p_j} = x_{p_j}^{(j)} = z_{j + 1}$. 
+        So $x_{p_j}$ is assigned to $z_{j + 1}$ by the outer loop and it has $x_{p_j} = x_{p_j}^{(j)} = z_{j + 1}$. 
         It continues and $z_{j + 1}$ will be the initial iterate pass into the inner loop for the $j + 1$ iteration, and hence $z_{j + 1} =x_{-1}^{(j + 1)}$. 
@@
         \begin{lemma}[inner iteration is bounded above]\label{lemma:rgmapg-inner-bnds}
-            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista} and Assumption \ref{ass:q-growth-ch2}, denote $F^+ := \inf_xF(x)$ and, $X^+$ as the set of minimizers. 
+            Suppose that $F = f + g$ satisfies Assumption \ref{ass:q-growth-ch2}, denote $F^+ := \inf_xF(x)$ and, $X^+$ as the set of minimizers. 
             Consider any $j \ge 1$ iteration experienced by the outer loop. 
@@
         The following lemma shows that when that happens, the algorithm will always terminate after a finite number of iterations of the outer loop. 
-        \begin{lemma}[bounds on outer iteration counts]
-            ...
+        \begin{lemma}[bounds on outer iteration counts]\label{lemma:rgmapg-outer-itr-bnd}
+            Let $F = f + g$ satisfies Assumption \ref{ass:standard-fista}. 
+            Suppose we apply Algorithm \ref{alg:linear-rgmapg} on $F = f + g$. 
+            Define $T_\epsilon = \lceil\ln(2\epsilon^{-2}(F(z_0) - F^+))\rceil$
+            Assume that after iteration $j$, no doubling occurred in the if statement, i.e: $n_{t + 1} = p_t$ for $t \ge j$, then it must terminate before, or at iteration $j + T_\epsilon$. 
         \end{lemma}
@@
             Suppose that since the $j\ge 2$ th iteration, there is no period doubling for $T_\epsilon$ number of iterations in the outer loop of Algorithm \ref{alg:linear-rgmapg}, i.e: $n_{t + 1} = p_t$
-            for $j \le t \le j + T_\epsilon - 1$, and denote $s = j + T_\epsilon -1$ for better notations, giving us $j \le t \le s$. 
+            for $j \le t \le j + T_\epsilon - 1$, and denote $s = j + T_\epsilon -1$ for better notations, giving us for all $j \le t \le s$, $n_{t + 1} = p_t$. 
+            \par
+            Consider the start of the $s$ th iteration of the outer loop, denote $L_0^{(s)}, G_0^{(s)}$ as the $L_0$ in line 4 in Algorithm \ref{alg:gmapg}, it would give the following inequalities
+            {\allowdisplaybreaks
+            \begin{align*}
+                \frac{1}{2}\left(
+                    G_0^{(s)}
+                \right)^2
+                &\underset{\text{(a)}}{=} 
+                \frac{1}{2}\left\Vert
+                    \sqrt{L_0^{(s)}}\left(z_s - T_{1/L_0^{(s)}}(z_s)\right)
+                \right\Vert^2
+                \\
+                &\underset{\text{(b)}}{=} \frac{1}{2L_0^{(s)}}\left\Vert
+                        \mathcal G_{1/L_0^{(s)}}(z_s)
+                \right\Vert^2
+                \\
+                &\underset{\text{(c)}}{\le} F(z_s) - F\left(x_0^{(s)}\right) 
+                \\
+                &\underset{\text{(d)}}{\le} 
+                F(z_s) - F\left(x_{p_s}^{(s)}\right)
+                \\
+                &= F(z_s) - F(z_{s + 1})
+                \\
+                &\underset{\text{(e)}}{\le} \exp(-T_\epsilon)\left(F(z_{s - T_\epsilon}) - F(z_{s - T_\epsilon + 1})\right)
+                \\
+                &= \exp(-T_\epsilon)(F(z_{j - 1}) - F(z_j)) 
+                \\
+                &\underset{\text{(f)}}{\le} \exp(-T_\epsilon)(F(z_{0}) - F(z_j))
+                \\
+                &\underset{\text{(g)}}{\le} \left(
+                    \frac{2(F(z_0) - F^+)}{\epsilon^2}
+                \right)^{-1}(F(z_0) - F^+) 
+                \\
+                &= \epsilon^2/2.
+            \end{align*}
+            }
+            \begin{enumerate}
+                \item [(a)] At the $s$ iteration of the loop in Algorithm \ref{alg:linear-rgmapg}, $z_s$ is passed into Algorithm \ref{alg:gmapg} with $x_{-1} = z_s$.
+Therefore, at line 3 in Algorithm \ref{alg:gmapg} it calls Algorithm \ref{alg:armijo-ls} with $x_{-1} = z_s, \alpha_0 = 1, L^+$ which means $y^+ = x_{-1} = z_s$ at line 5 and $x^+ = T_{1/L^+}(z_s)$.
+Coming back to line 3 in Algorithm \ref{alg:gmapg}, it assigns $y_0 = y^+ = z_s, x_0 = x^+ = T_{1/L^+}(z_s)$ and $L_0 = L^+$.
+Assuming the line search went successful, it will have $D_f(z_s, x_0) \le L^{(s)}_0/2 \Vert z_s - x_0\Vert^2$.
+                \item [(b)] We used definition of gradient mapping in Definition \ref{def:gm-for-ch2}. 
+                \item [(c)] By the assumption that the line search in Algorithm \ref{alg:armijo-ls} is successful at $z_s$ back in item (a), here we can use \eqref{eqn:emp:result-item-2} in Theorem \ref{thm:gmapg-generic-gm-cnvg}.
+                \item [(d)] GMAPG is monotone in function value for the use of $\mathbf M$ that is either Algorithm \ref{alg:beck-mono} or \ref{alg:nes-mono}, so it has $F\left(x_{p_s}^{(s)}\right) \le F\left(x_0^{(s)}\right)$.
+                \item [(e)] Here we used the assumption that no doubling occurs so $n_{t + 1} = p_t$ for all $j \le t \le s$ meaning that line 13 in Algorithm \ref{alg:linear-rgmapg} has $F(z_t) - F(z_{t + 1}) \ge e^{-1}(F(z_{t - 1}) - F(z_t))$.
+For that, we recursively unrolled it for $T_\epsilon$ many iterations starting with $t = s = j + T_\epsilon - 1$ ending with $t = j$.
+                \item [(f)] We used the monotone property of subroutine $\mathbf M$ in GMAPG again so $F(z_0) \le F(z_{j - 1})$. 
+                \item [(g)] We substituted $T_\epsilon = \lceil\ln(2\epsilon^{-2}(F(z_0) - F^+))\rceil$ and, removing $\lceil\cdot\rceil$ to make for the $\le$ inequality. 
+            \end{enumerate}
+            Therefore, it has $G_0^{(s)} \le \epsilon$, hence it must have terminated at, or before iteration $s$. 
         \end{proof}
@@
         \begin{proof}
-
+            Firstly, Algorithm \ref{alg:linear-rgmapg} must terminate within finite many iterations under Assumption \ref{ass:q-growth-ch2} for all total budget $M \in \N$. 
+            This is because Observation \ref{obs:rgmapg} shows that $n_j$ is a non-decreasing sequence, Lemma \ref{lemma:rgmapg-inner-bnds} shows that $n_j \le \bar p$ under this quadratic growth assumption, therefore $n_j$ must converge which implies that doubling of $n_{j + 1} = 2p_{j}$ must stop.
+            Finally, since the doubling must stop, Lemma \ref{lemma:rgmapg-outer-itr-bnd} applies hence, it terminates at most $j + T_\epsilon$ iteration. 
+            \par
+            Using it let's assume that it executed for $j = 1, 2, \cdots, J$, and it can be represented as $J = m + nT_\epsilon$ with $0 \le m < T_\epsilon$. 
+            The following intermediate results are important to the proof. 
+            \begin{enumerate}
+                \item [(a)] 
+            \end{enumerate}
         \end{proof}

### 2025-05-29 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
     \section{Practical enhancement from the Nesterov's Monotone Variant}
-        Firstly, we will introduce some theories in for nonconvex functions. 
-        This is necessary because Nesterov's monotone variants can adapt to weakly convex objective functions. 
-        The following assumption will characterize the full scope of discussion in nonconvex objective function. 
+        The following definition is a set of necessary conditions GMAPG with Nesterov's monotone subroutine. 
+        Our goal in this section is to show that Nesterov's implementations of monotone accelerated gradient method has convergence results under Assumption \ref{ass:sum-of-wcnvx}.
         \begin{definition}[nonconvex Nesterov's monotone scheme]\;\label{def:nes-monotone-scheme}\\
@@
             \STATE{$n_0 := 0; z_0 = x_{-1}$.}
-            \STATE{$z_1, p_0, \overline L_1:= \textbf{GMAPG}(f, g, x_{-1}, L, r_j, \rho, N_{\min}=n_0, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
+            \STATE{$z_1, p_0, \overline L_1, G^+:= \textbf{GMAPG}(f, g, x_{-1}, L, r_j, \rho, N_{\min}=n_0, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
             \STATE{$n_1:=p_0$.}
@@
             \FOR{$j = 1,2, \ldots, M$}
+                \IF{$M \le 0 \textbf{ or } G^+ \le \epsilon$}
+                    \STATE{\textbf{break}}                
+                \ENDIF
                 \STATE{$z_{j + 1}, p_j, \overline L_{j + 1}, G_k^+ := \textbf{GMAPG}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
                 \STATE{$M := M - p_j$.}
-                \IF{$M \le 0 \textbf{ or } G_k^+ \le \epsilon$}
-                    \STATE{\textbf{break}}                
-                \ENDIF
                 \STATE{$\overline L_{j + 1} = \max(\overline L_{j}, \overline L_{j + 1})$.}
@@
         For example in line 7 of Algorithm \ref{alg:linear-rgmapg} at the $j$ iteration, the inner loop returns $x_{p_j}$ as the last iterate. 
-        So $x_{p_j}$ is assigned to $z_{j + 1}$ by the outer loop and it has $x_{p_j} = x_{p_j}^{(j)} = z_{j + 1}$. 
+        So $x_{p_j}$ is assigned to $z_{j + 1}$ by the outer loop, and it has $x_{p_j} = x_{p_j}^{(j)} = z_{j + 1}$. 
         It continues and $z_{j + 1}$ will be the initial iterate pass into the inner loop for the $j + 1$ iteration, and hence $z_{j + 1} =x_{-1}^{(j + 1)}$. 
@@
         \begin{lemma}[maximum iteration needed for an optimality gap ratio]\;\label{lemma:prog-ratio}\\
-            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista} so $F^+ := \inf_xF(x)$ and, $X^+$ is the set of minimizers. 
+            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista} so $F^+ := \inf_xF(x)$, $X^+$ is the set of minimizers, and $\mu > 0$ is the quadratic growth constant. 
             Let the sequence $(x_k)_{k \ge -1}$ be generated by GMAPG (Definition \ref{alg:gmapg}). 
-            If in addition, $F$ satisfies the quadratic growth condition in Assumption \ref{ass:q-growth-ch2}, then 
+            Then it has
             \begin{align*}
@@
 For that, we recursively unrolled it for $T_\epsilon$ many iterations starting with $t = s = j + T_\epsilon - 1$ ending with $t = j$.
-                \item [(f)] We used the monotone property of subroutine $\mathbf M$ in GMAPG again so $F(z_0) \le F(z_{j - 1})$. 
+                \item [(f)] We used the monotone property of subroutine $\mathbf M$ in GMAPG again so $F(z_0) \ge F(z_{j - 1})$. 
                 \item [(g)] We substituted $T_\epsilon = \lceil\ln(2\epsilon^{-2}(F(z_0) - F^+))\rceil$ and, removing $\lceil\cdot\rceil$ to make for the $\le$ inequality.
+We also replaced $F(z_j)$ by $F^+$ the minimum which is always smaller.
             \end{enumerate}
@@
             This is because Observation \ref{obs:rgmapg} shows that $n_j$ is a non-decreasing sequence, Lemma \ref{lemma:rgmapg-inner-bnds} shows that $n_j \le \bar p$ under this quadratic growth assumption, therefore $n_j$ must converge which implies that doubling of $n_{j + 1} = 2p_{j}$ must stop.
-            Finally, since the doubling must stop, Lemma \ref{lemma:rgmapg-outer-itr-bnd} applies hence, it terminates at most $j + T_\epsilon$ iteration. 
-            \par
-            Using it let's assume that it executed for $j = 1, 2, \cdots, J$, and it can be represented as $J = m + nT_\epsilon$ with $0 \le m < T_\epsilon$. 
+            Finally, since the doubling must stop at some $j$, Lemma \ref{lemma:rgmapg-outer-itr-bnd} applies hence, it terminates at most $j + T_\epsilon$ iteration. 
+            \par
+            Using it let's assume that it executed for $j = 1, 2, \cdots, J$ and $M$ is large enough to achieve optimality $G^+_k \le \epsilon$ right at the start of iteration $J$.
+            Representing it by the maximum period between doubling: $J = m + nT_\epsilon$ with $0 \le m < T_\epsilon$. 
             The following intermediate results are important to the proof. 
             \begin{enumerate}
-                \item [(a)] 
+                \item [(a)] $n_{J - lT_\epsilon} \le n_{J - lT_\epsilon}\le (1/2)^ln_J$ for all $l = 1, \ldots, n$.
+From Lemma \ref{lemma:rgmapg-outer-itr-bnd} we know that doubling must have occured within a period of $T_\epsilon$ iterations at least once.
+                \item [(b)] $n_{j} \le n_{j + 1}$ for all $0 \le j \le J - 1$. The sequence is monotone from Observation \ref{obs:rgmapg}. 
+                \item [(c)] $n_j \le \bar p$ with $\bar p = 4\sqrt{2L(1 + e)}/\sqrt{\mu}$, proved in Lemma \ref{lemma:rgmapg-inner-bnds}. 
             \end{enumerate}
+            The upper bound on the total number of iterations of GMAPG over $J$ iteration of outer loop is given by: 
+            \begin{align*}
+                \sum_{i = 0}^{J} n_i &= \sum_{i = 0}^{m + nT_\epsilon} n_i
+                \\
+                &= \sum_{i = 0}^{m}n_i + \sum_{l = 0}^{n - 1}\sum_{i = 1}^{T_\epsilon} n_{m + i + lT}
+                \\
+                &\hspace{-0.5em}
+                \underset{\substack{(b), \\ m \le T_\epsilon.}}\le T_\epsilon n_m + \sum_{l = 0}^{n - 1} T_\epsilon n_{m + (l + 1)T_\epsilon}
+                \\
+                &= T_\epsilon \sum_{l = 0}^{n} n_{m + lT_\epsilon} = T_\epsilon \sum_{l = 0}^{n} n_{J - lT_\epsilon}
+                \\
+                &\underset{\text{(a)}}{\le} T_\epsilon \sum_{l = 0}^{n} (1/2)^l n_J \le T_\epsilon \sum_{l = 0}^{\infty} (1/2)^l n_J
+                \\
+                &\le 2T_\epsilon n_J \le 2T_\epsilon \bar p.
+            \end{align*}
+            The total iteration counts is bounded by: 
+            \begin{align*}
+                \sum_{i = 0}^{J} n_i &\le 
+                \frac{8\sqrt{2L(1 + e)}}{\sqrt{\mu}} \left\lfloor 
+                \ln \left(
+                    \frac{2(F(z_0) - F^+)}{\epsilon^2}
+                \right) 
+                \right\rfloor. 
+            \end{align*}
         \end{proof}
-        \begin{theorem}[convergence rates of restarted GMAPG]
+        \begin{theorem}[convergence rates of restarted GMAPG]\label{thm:rgmapg-cnvg}
 

### 2025-05-30 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
                     -bc_1^T& -bc_2^T & E_2E_2^T + E_1E_1^T + bb^T & E_1E_1^T \\
-                    & & & E_1^Ty + z\\
+                    & & E_1^Ty & I_{n_1}\\
                 \end{bmatrix}
@@
             The above Algorithm \ref{alg:gmapg} is an implementation of GMAPG in Definition \ref{alg:gmapg}. 
+            The first iterates $x_0$ is produced by a step of proximal gradient descent through Algorithm \ref{alg:armijo-ls} so, it has $x_0 = v_0 = T_{1/L_0}(x_{-1})$, and consequently all results from Theorem \ref{thm:gmapg-specialized-cnvg} apply.
             Parameters $r, \rho$ are chosen in the discretion of the practitioners. 
@@
         \par
-        A stronger result on the convergence rate of $\Vert \mathcal G_{1/\eta_k}(y_k)\Vert$ can be obtained if, we assume that the function $F=f + g$ satisfies \ref{ass:standard-fista}.
+        A stronger result on the convergence rate of $\Vert \mathcal G_{1/\eta_k}(y_k)\Vert$ can be obtained if, we assume that the function $F=f + g$ satisfies Assumption \ref{ass:standard-fista}.
 
@@
                 \ENDIF
-                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1}, G_k^+ := \textbf{GMAPG}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
+                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1}, G^+ := \textbf{GMAPG}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
                 \STATE{$M := M - p_j$.}
@@
         We make the choice to have $x_{-1}^{(j + 1)} = z_{j + 1} = x_{p_j}^{(j)}$ for consistencies across theorems from previous sections. 
-        For example in line 7 of Algorithm \ref{alg:linear-rgmapg} at the $j$ iteration, the inner loop returns $x_{p_j}$ as the last iterate. 
+        For example in line 10 of Algorithm \ref{alg:linear-rgmapg} at the $j$ iteration, the inner loop returns $x_{p_j}$ as the last iterate. 
         So $x_{p_j}$ is assigned to $z_{j + 1}$ by the outer loop, and it has $x_{p_j} = x_{p_j}^{(j)} = z_{j + 1}$. 
@@
         \begin{theorem}[bounds on the total iterations]
-            ...
+            Let $F = f + g$ satisfies Assumption \ref{ass:q-growth-ch2}. 
+            Suppose that Algorithm \ref{alg:linear-rgmapg} is applied to it then the total number of iterations is bounded for all $M \in \N$, $\epsilon > 0$ by
+            \begin{align*}
+                \sum_{i = 0}^{J - 1}p_i &\le 
+                \frac{8\sqrt{2L(1 + e)}}{\sqrt{\mu}} \left\lceil 
+                \ln \left(
+                    \frac{2(F(z_0) - F^+)}{\epsilon^2}
+                \right) 
+                \right\rceil. 
+            \end{align*}
         \end{theorem}
@@
             \par
-            Using it let's assume that it executed for $j = 1, 2, \cdots, J$ and $M$ is large enough to achieve optimality $G^+_k \le \epsilon$ right at the start of iteration $J$.
+            Using it let's assume that it executed for $j = 1, 2, \cdots, J$ and $M$ is large enough to achieve optimality $G^+ \le \epsilon$ right at the start of iteration $J$.
             Representing it by the maximum period between doubling: $J = m + nT_\epsilon$ with $0 \le m < T_\epsilon$. 
@@
                 \\
-                &= \sum_{i = 0}^{m}n_i + \sum_{l = 0}^{n - 1}\sum_{i = 1}^{T_\epsilon} n_{m + i + lT}
+                &= \sum_{i = 0}^{m}n_i + \sum_{l = 0}^{n - 1}\sum_{i = 1}^{T_\epsilon} n_{m + i + lT_\epsilon}
                 \\
@@
             \begin{align*}
-                \sum_{i = 0}^{J} n_i &\le 
-                \frac{8\sqrt{2L(1 + e)}}{\sqrt{\mu}} \left\lfloor 
+                \sum_{i = 0}^{J - 1}p_i \le \sum_{i = 0}^{J} n_i &\le 
+                \frac{8\sqrt{2L(1 + e)}}{\sqrt{\mu}} \left\lceil 
                 \ln \left(
@@
                 \right) 
-                \right\rfloor. 
-            \end{align*}
+                \right\rceil. 
+            \end{align*}
+            Note that $n_0 = 0$. 
         \end{proof}
-        \begin{theorem}[convergence rates of restarted GMAPG]\label{thm:rgmapg-cnvg}
-
+        \par
+        The final results from above theorem provides the convergence rate of iterates and the complexity of restart GMAPG under Assumption \ref{ass:q-growth-ch2}. 
+        We denote $\kappa := L/\mu$. 
+        \begin{theorem}[restarted GMAPG convergence and complexity]\;\label{thm:rgmapg-cnvg-complexity}
+            Let $F = f + g$ satisfy Assumption \ref{ass:q-growth-ch2}. 
+            Let $J$ be the total number of iteration performed to achieve accuracy in the outer loop.
+            Let $K := \sum_{i = 0}^{J - 1}p_i$ be the total iterations. 
+            Then, the maximum $K$ needed to achieve optimality $\Vert z_J - z_J^+\Vert \le \delta$ on the iterates is bounded by $\mathcal O\left(\frac{1}{\sqrt{\kappa}}\ln\left(\frac{1}{\kappa\delta}\right)\right)$.
         \end{theorem}
+        \begin{proof}
+            Suppose $K = \sum_{i = 0}^{J - 1} p_i$ iteration were performed and, it achieved $G_0^{(J)} \le \epsilon$, 
+            Now, let $k > 0$ and let $\epsilon = \sqrt{2}(F(z_0) - F^+)^{1/2}\exp(-k + 1)$ then: 
+            \begin{align*}
+                \ln \left(
+                    \frac{2(F(z_0) - F^+)}{\epsilon^2}
+                \right)
+                &= 2(k - 1). 
+            \end{align*}
+            Then it has 
+            \begin{align*}
+                0 &\le 
+                \frac{8\sqrt{2L(1 + e)}}{\sqrt{\mu}}\left\lceil 
+                    \ln\left(
+                        \frac{2(F(z_0) - F^+)}{\epsilon^2}
+                    \right)
+                \right\rceil - K
+                =
+                \frac{8\sqrt{2L(1 + e)}}{\sqrt{\mu}}\left\lceil 
+                    2(k - 1)
+                \right\rceil - K 
+                \\
+                &\le 
+                \frac{8\sqrt{2L(1 + e)}}{\sqrt{\mu}} (2(k - 1) + 1) - K
+                \\
+                \implies
+                0 &\le k - 1 + 1/2 - \frac{K\sqrt{\mu}}{16\sqrt{2L(1 + e)}}
+                \\
+                &\le k - \frac{K\sqrt{\mu}}{16\sqrt{2L(1 + e)}} .
+            \end{align*}
+            This gives us 
+            \begin{align*}
+                G_0^{(J)} &\le \epsilon = \sqrt{2}(F(z_0) - F^+)^{1/2}\exp(-k + 1)
+                \\
+                &=
+                e\sqrt{2}(F(z_0) - F^+)^{1/2}\exp(-k)
+                \\
+                &\le
+                e\sqrt{2}(F(z_0) - F^+)^{1/2}\exp\left(
+                    - \frac{K\sqrt{\mu}}{16\sqrt{2L(1 + e)}}
+                \right)
+                \\
+                &= e\sqrt{2}(F(z_0) - F^+)^{1/2}\exp\left(
+                    - \frac{K\sqrt{\kappa}}{16\sqrt{2 + 2e}}
+                \right). 
+            \end{align*}
+            The above inequality shows a linear convergence rate of the quantity $G_0^{(J)}$ with respect to the total number of iterations required for GMAPG. 
+            Using Theorem \ref{thm:qfg-peb-equiv} from previous chapter and take note that Assumption \ref{ass:q-growth-ch2} is Definition \ref{def:necoara-weaker-scnvx}\ref{def:necoara-qfg}. 
+            Denote $z_J^+ = \Pi_{X^+}z_J$ then it has 
+            {\allowdisplaybreaks
+            \begin{align*}
+                G_0^{(J)} 
+                &\underset{\text{(a)}}{=}\left\Vert \sqrt{L_0^{(J)}} \left(z_J - x_0^{(J)}\right) \right\Vert 
+                = \frac{1}{\sqrt{L_0^{(J)}}} \left\Vert 
+                    L_0^{(J)}\left(
+                        z_J - x_0^{(J)}
+                    \right)
+                \right\Vert
+                \underset{\text{(a)}}{=}\frac{1}{\sqrt{L_0^{(J)}}} \left\Vert 
+                    \mathcal G_{1/L_0^{(J)}}(z_J)
+                \right\Vert
+                \\
+                &\underset{\text{(b)}}{\ge} \frac{1}{\sqrt{2L}}\left\Vert\mathcal G_{1/L_0^{(J)}}(z_J)\right\Vert
+                \\
+                &\underset{\text{(c)}}{\ge} \frac{\sqrt{L(\mu + L)} - L}{\sqrt{L(\mu + L)}} \frac{1}{\sqrt{2L}}\left\Vert
+                    z_J - z_J^+
+                \right\Vert
+                \\
+                &= \frac{1}{\sqrt{2L}}\left(
+                    1 - \frac{1}{\sqrt{1 + \mu/L}}
+                \right)\left\Vert
+                    z_J - z_J^+
+                \right\Vert
+                \\
+                &\underset{\text{(d)}}{\ge} \frac{1}{2\sqrt{L}}\left(
+                    \frac{\mu}{2L}
+                \right)\left\Vert
+                    z_J - z_J^+
+                \right\Vert 
+                = \frac{\kappa}{4\sqrt{L}} \left\Vert
+                    z_J - z_J^+
+                \right\Vert. 
+            \end{align*}
+            }
+            \begin{enumerate}
+                \item [(a)] 
+                \item [(b)]
+                \item [(c)]
+                \item [(d)]
+            \end{enumerate}
+            It then yields the convergence rate of 
+            \begin{align*}
+                \left\Vert z_J - z^+_J\right\Vert 
+                &\le \frac{4eL\sqrt{2}(F(z_0) - F^+)^{1/2}}{\kappa}
+                \exp\left(
+                    - \frac{K\sqrt{\kappa}}{16\sqrt{2 + 2e}}
+                \right) 
+                \le 
+                \mathcal O\left(
+                    \kappa^{-1}\exp\left(-\sqrt{\kappa}K\right)
+                \right). 
+            \end{align*}
+            To achieve accuracy $\Vert z_J - z^+_J\Vert \le \delta$, it would require $\mathcal O\left(\frac{1}{\sqrt{\kappa}}\ln\left(\frac{1}{\kappa\delta}\right)\right)$ many total iterations of GMAGP.
+        \end{proof}
 

### 2025-05-30 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
             \end{remark}
-        \subsection{Hoffman error bound and Q-SCNVX}
 
@@
 
-        \subsection{Application, KKT of linear programming}
-            This section extends ideas in the discussion section of Necoara et al. \cite{necoara_linear_2019}. 
-            \par
+\chapter{Application, KKT of linear programming}
+    This chapter extends ideas by the end of Necoara et al.'s paper \cite{necoara_linear_2019}. 
+    \section{Introductions and problem formulations}
         Let $X_1, X_2, Y$ be Hilbert spaces. 
@@
         \end{enumerate}
-
         Let $\bar v = (\bar y, \bar x_1, \bar x_2, \xi) \in \RR^m\times \RR^{n_1} \times \RR^{n_2}\times \RR$ then the right multiplication of has: 
@@
                 -(bc_1^T)x_1 - (bc_2^T)x_2 + (E_2E_2^T + E_1E_1^T + bb^T)y
-                    + (E_1E_1^T)z
+                + E_1z
                 \\
@@
                 E_2^TE_1 + c_1^T & E_2^TE_2 + c_2^T & -c_2b^T & \\
-                    -bc_1^T& -bc_2^T & E_2E_2^T + E_1E_1^T + bb^T & E_1E_1^T \\
-                    & & E_1^Ty & I_{n_1}\\
+                -bc_1^T& -bc_2^T & E_2E_2^T + E_1E_1^T + bb^T & E_1 \\
+                & & E_1^T & I_{n_1}\\
             \end{bmatrix}
@@
         Here we write it out to view, for theoretical interests. 
-            \par
+        \subsection{Investigating the matrix}
+
+        \subsection{Speedy evaluations}
             Let $f(v) = (1/2)\Vert Av - d\Vert^2$ to be the objective function of optimization problem \eqref{problem:lp-kkt-min}. 
@@
             For this problem, the computation overhead for $f(u) - f(v), D_f(u, v)$ is very little if $\nabla f(u), \nabla f(v)$ is known. 
+    \section{Hoffman error bound and Q-SCNVX}
 

### 2025-05-31 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
 
-\chapter{Application, KKT of linear programming}
+\chapter{Application, Linear Feasibility Problems}
     This chapter extends ideas by the end of Necoara et al.'s paper \cite{necoara_linear_2019}.
-    \section{Introductions and problem formulations}
+    \section{Reducing LP to linear feasibility problems}
+        We first introduce the linear feasibility problem as our primary problem. 
+        \par
         Let $X_1, X_2, Y$ be Hilbert spaces. 
@@
             \STATE{$n_0 := 0; z_0 = x_{-1}$.}
-            \STATE{$z_1, p_0, \overline L_1, G^+:= \textbf{GMAPG}(f, g, x_{-1}, L, r_j, \rho, N_{\min}=n_0, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
+            \STATE{$z_1, p_0, \overline L_1, G^{(0)}:= \textbf{GMAPG}(f, g, x_{-1}, L, r_j, \rho, N_{\min}=n_0, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
             \STATE{$n_1:=p_0$.}
@@
             \FOR{$j = 1,2, \ldots, M$}
-                \IF{$M \le 0 \textbf{ or } G^+ \le \epsilon$}
+                \IF{$M \le 0 \textbf{ or } G^{(j-1)} \le \epsilon$}
                     \STATE{\textbf{break}}                
                 \ENDIF
-                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1}, G^+ := \textbf{GMAPG}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
+                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1}, G^{(j)} := \textbf{GMAPG}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
                 \STATE{$M := M - p_j$.}
@@
             for $j \le t \le j + T_\epsilon - 1$, and denote $s = j + T_\epsilon -1$ for better notations, giving us for all $j \le t \le s$, $n_{t + 1} = p_t$. 
+            \par
+            Our goal now is to show that at iteration $j = s$ of Algorithm \ref{alg:linear-rgmapg} it must have $G_0 \le \epsilon$ at line 5 of Algorithm \ref{alg:gmapg}. 
             \par
@@
             Let $F = f + g$ satisfies Assumption \ref{ass:q-growth-ch2}. 
-            Suppose that Algorithm \ref{alg:linear-rgmapg} is applied to it then the total number of iterations is bounded for all $M \in \N$, $\epsilon > 0$ by
+            Suppose that we applied Algorithm \ref{alg:linear-rgmapg} to it. 
+            For any $\epsilon > 0$, assuming that it terminated at $j = J < M$ iteration.
+            Then the total number of iterations has an upper bound:
             \begin{align*}
@@
             Using it let's assume that it executed for $j = 1, 2, \cdots, J$ and $M$ is large enough to achieve optimality $G^+ \le \epsilon$ right at the start of iteration $J$.
+            This is one of the way the algorithm can terminate, making it a sufficient condition for deriving the upper bound on the total number of iterations. 
             Representing it by the maximum period between doubling: $J = m + nT_\epsilon$ with $0 \le m < T_\epsilon$. 
@@
         \par
-        The final results from above theorem provides the convergence rate of iterates and the complexity of restart GMAPG under Assumption \ref{ass:q-growth-ch2}. 
+        The final results from above theorem provide the convergence rate of iterates and the complexity of restart GMAPG under Assumption \ref{ass:q-growth-ch2}. 
         We denote $\kappa := L/\mu$. 
@@
         \begin{proof}
-            Suppose $K = \sum_{i = 0}^{J - 1} p_i$ iteration were performed and, it achieved $G_0^{(J)} \le \epsilon$, 
-            Now, let $k > 0$ and let $\epsilon = \sqrt{2}(F(z_0) - F^+)^{1/2}\exp(-k + 1)$ then: 
+            Suppose a total of $K := \sum_{i = 0}^{J - 1} p_i$ iteration were performed and, at line 10 of Algorithm \ref{alg:linear-rgmapg} at iteration $j = J$ it achieved $G_0 \le \epsilon$ at line 5 of Algorithm \ref{alg:gmapg}.
+            That will cause the inner GMAPG to return $G_0$ so, at line 10 it has $G^{(J)} < \epsilon$ in Algorithm \ref{alg:linear-rgmapg}. 
+            This is one of the ways the algorithm can terminate hence, it suffices for deriving an upper bound. 
+            \par
+            Now we show the convergence rate of $G^{(J)}$, let $k > 0$ and let $\epsilon = \sqrt{2}(F(z_0) - F^+)^{1/2}\exp(-k + 1)$ then: 
             \begin{align*}
@@
             \begin{align*}
-                G_0^{(J)} &\le \epsilon = \sqrt{2}(F(z_0) - F^+)^{1/2}\exp(-k + 1)
+                G^{(J)} &\le \epsilon = \sqrt{2}(F(z_0) - F^+)^{1/2}\exp(-k + 1)
                 \\
@@
             The above inequality shows a linear convergence rate of the quantity $G_0^{(J)}$ with respect to the total number of iterations required for GMAPG. 
-            Using Theorem \ref{thm:qfg-peb-equiv} from previous chapter and take note that Assumption \ref{ass:q-growth-ch2} is Definition \ref{def:necoara-weaker-scnvx}\ref{def:necoara-qfg}. 
             Denote $z_J^+ = \Pi_{X^+}z_J$ then it has 
@@
             \begin{align*}
-                G_0^{(J)} 
+                G^{(J)} 
                 &\underset{\text{(a)}}{=}\left\Vert \sqrt{L_0^{(J)}} \left(z_J - x_0^{(J)}\right) \right\Vert 
@@
             \begin{enumerate}
-                \item [(a)] 
-                \item [(b)]
-                \item [(c)]
-                \item [(d)]
+                \item [(a)] For the first equality, we assumed that $G^{(J)} < \epsilon$ in the outer loop and, it's returned by Algorithm \ref{alg:gmapg} at line 5.
+Therefore, it has $G_0 = G^{(J)} = \sqrt{L^{(J)}_0} \Vert z^{(J)} - x_0^{(J)}\Vert$ because it calls Algorithm \ref{alg:armijo-ls} (Armijo line search) with $\alpha_0 = 0$.
+The second equality comes by using Definition \ref{def:gm-for-ch2}.
+                \item [(b)] Proposition \ref{prop:bnded-lip-ls} has $L_0^{(J)} \le 2L$. 
+                \item [(c)] Using Theorem \ref{thm:qfg-peb-equiv} from previous chapter and take note that Assumption \ref{ass:q-growth-ch2} is Definition \ref{def:necoara-weaker-scnvx}\ref{def:necoara-qfg}.
+                \item [(d)] The function $1/\sqrt{1 - x/L}$ is convex hence a Taylor expansion has $1/\sqrt{1 - x/L} \le 1 - x/(2L) $, substituting it with $x = \mu$ makes for a lower bound. 
             \end{enumerate}

### 2025-06-04 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
         We first introduce the linear feasibility problem as our primary problem. 
-        \par
-        Let $X_1, X_2, Y$ be Hilbert spaces. 
+        \begin{definition}[a linear feasibility problem]
+            Let $A\in \RR^{m\times n}$, $b \in \RR^m$
+            Let $\mathcal K$ be a simple cone. 
+            The linear feasibility problem is defined as the following optimization problem: 
+            \begin{align*}
+                \min_{x \in \mathcal K} \Vert Ax - b\Vert^2.
+            \end{align*}
+        \end{definition}
+        The KKT of a linear programming problem is an instance of a linear feasibility problem. 
+        \par
+        Let $X_1, X_2, Y$ be Euclidean spaces. 
         Define linear mapping $E:X_1 \times X_2 \rightarrow Y := (x_1, x_2)\mapsto E_1 x_1 + E_2 x_2$ where $E_1, E_2$ each are mappings of $X_1 \rightarrow Y, X_2 \rightarrow Y$. 
@@
         \end{align*}
-        The KKT conditions give the following convex feasibility problem 
+        The KKT conditions give the following linear feasibility problem 
         \begin{align*}
@@
         \end{align*}
-        Allow $X_1 = \RR^{n_1}, X_2 = \RR^{n_2}, Y = \RR^m$. 
+        Assuming $X_1 = \RR^{n_1}, X_2 = \RR^{n_2}, Y = \RR^m$. 
         Define 
@@
         \end{proof}
-        \begin{theorem}[bounds on the total iterations]
+        \begin{theorem}[bounds on the total iterations]\label{thm:rgmapg-total-itr-bnds}
             Let $F = f + g$ satisfies Assumption \ref{ass:q-growth-ch2}. 
@@
             \end{align*}
-            The total iteration counts is bounded by: 
+            The total number of iterations is bounded by: 
             \begin{align*}
@@
         We denote $\kappa := L/\mu$. 
-        \begin{theorem}[restarted GMAPG convergence and complexity]\;\label{thm:rgmapg-cnvg-complexity}
+        \begin{theorem}[restarted GMAPG convergence and complexity]\;\label{thm:rgmapg-cnvg-complexity}\\
             Let $F = f + g$ satisfy Assumption \ref{ass:q-growth-ch2}. 
@@
             \end{align*}
-            Then it has 
+            Then it has from Theorem \ref{thm:rgmapg-total-itr-bnds} that:
             \begin{align*}

### 2025-06-04 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
         We first introduce the linear feasibility problem as our primary problem. 
-        \begin{definition}[a linear feasibility problem]
+        \begin{definition}[a conic feasibility problem]
             Let $A\in \RR^{m\times n}$, $b \in \RR^m$
             Let $\mathcal K$ be a simple cone. 
-            The linear feasibility problem is defined as the following optimization problem: 
+            The conic feasibility problem is defined as the following optimization problem: 
             \begin{align*}
@@
         \end{definition}
-        The KKT of a linear programming problem is an instance of a linear feasibility problem. 
+        The KKT of a linear programming problem is an instance of a linear feasibility problem, with $\mathcal K$ being a cross product of one of $\RR, \RR_+, \RR_-$. 
+        A feasibility semidefinite program with linear constraint can is another example. 
         \par
@@
         Here we write it out to view, for theoretical interests. 
+        % SUBSECTION | INVESTIGATING THE MATRIX
         \subsection{Investigating the matrix}
-
+        % SUBSECTION | SPEEDY EVALUATION
         \subsection{Speedy evaluations}
             Let $f(v) = (1/2)\Vert Av - d\Vert^2$ to be the objective function of optimization problem \eqref{problem:lp-kkt-min}. 
-            Its gradient, objective value, and Bregman Divergence have: 
-            \begin{align*}
-                \nabla f(v) &= A^TAv - A^Td, 
-                \\
+            The gradient of $f$ at $v$ is: $\nabla f(v) = A^TAv - A^Td$. 
+            Once the gradient at a point is known, the objective value at $v$, and Bregman Divergence at $u, v$ can be expressed in its gradient at $u, v$ with minimum computation overhead: 
+            \begin{align*}
                 f(v) &= 
@@
             \end{align*}
-            The value $\nabla f(v), f(v)$ when evaluated together, require minimal additional computations. 
+            This makes evaluating $\nabla f(v), f(v)$ together just as fast as evaluating $\nabla f(v)$ alone.
             This fact is favorable for implementations in practice. 
             Furthermore, the difference of the function value between 2 points $v, u$ admits an interesting relation via the Bregman Divergence. 
-            Observe that $\forall u, v \in \RR^n$ it has 
+            Observe that $\forall u, v \in \RR^n$ it has: 
             \begin{align*}
@@
             \end{align*}
-            For this problem, the computation overhead for $f(u) - f(v), D_f(u, v)$ is very little if $\nabla f(u), \nabla f(v)$ is known. 
-    \section{Hoffman error bound and Q-SCNVX}
+            For this reason, the computation overhead for $f(u) - f(v), D_f(u, v)$ is very little as well if, $\nabla f(u), \nabla f(v)$ is already known.
+    \section{Hoffman error bound in linear feasibility problem}
 

### 2025-06-06 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, all, changes

@@
 \chapter{Advanced Enhancement Techniques in Accelerated Proximal Gradient}
-    We review advanced enhancement techniques in Accelerated Proximal Gradient method. 
-    The review will be based on several papers. 
+    We incorperate advanced enhancement techniques for the Accelerated Proximal Gradient method and combined then together. 
+    This is based on several papers. 
     \par

### 2025-06-09 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

--- 2025-06-04 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
@@
 \chapter{Advanced Enhancement Techniques in Accelerated Proximal Gradient}
-    We review advanced enhancement techniques in Accelerated Proximal Gradient method. 
-    The review will be based on several papers. 
+    This chapter is the draft for an upcoming paper. 
+    The writing style will change to fit this purpose better. 
     \par
     There are several notable enhancements of the FISTA for function that are not strongly convex. 
-    Monotone variants of FISTA proposed by Beck \cite{beck_fast_2009-1} and Nesterov \cite[2.2.32]{nesterov_lectures_2018} imposes monotonicity in function value at the iterates.  
-    Backtracking strategies from Chambolle \cite{calatroni_backtracking_2019} shows that the underestimating Lipschitz constant using a backtracking technique to choose a next iterate improves the average runtime of the algorithm in practice.
-    They showed that the convergence rate is bounded by the estimates of the Lipschitz constant. 
-    Restart is a technique discussed in Necoara et al. \cite{necoara_linear_2019}.
-    They showed that there exists an optimal restarting interval to achieve fast linear convergence rate for all functions with quadratic growth condition. 
-    The method of restarting was improved to be parameter free while still retaining a fast linear convergence rate, see Alamo et al.
-\cite{alamo_restart_2019} and Aujol et al.
-\cite{aujol_parameter-free_2024}.
-    \par
-    In this chapter, we will go through the details of these enhancements of FISTA and discuss why they are important in theories, and in practice.
+    Monotone variants are proposed by Beck \cite{beck_fast_2009-1} and Nesterov \cite[2.2.32]{nesterov_lectures_2018}. 
+    Chambolle proposed the Backtracking strategy \cite{calatroni_backtracking_2019}.
+    Restart is a technique can be found in Necoara et al. \cite{necoara_linear_2019}, \cite{alamo_restart_2019} and Aujol et al. \cite{aujol_parameter-free_2024}.
 

### 2025-06-11 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
             For this reason, the computation overhead for $f(u) - f(v), D_f(u, v)$ is very little as well if, $\nabla f(u), \nabla f(v)$ is already known.
-    \section{Hoffman error bound in linear feasibility problem}
+    \section{Hoffman error bound of linear feasibility problem}
+    \section{Quadratic growth of linear feasibility problem}
 
 \chapter{Advanced Enhancement Techniques in Accelerated Proximal Gradient}
+    %% SYMBOL SETS FOR THIS CHAPTER ONLY 
+    \newcommand{\XXAPG}{AMAPG}
+
     This chapter is the draft for an upcoming paper. 
     The writing style will change to fit this purpose better. 
+    It will be very terse. 
     \par
-    There are several notable enhancements of the FISTA for function that are not strongly convex. 
+    There are several notable enhancements of the FISTA for function that are not necessarily strongly convex. 
     Monotone variants are proposed by Beck \cite{beck_fast_2009-1} and Nesterov \cite[2.2.32]{nesterov_lectures_2018}. 
@@
     \section{Preliminaries}
-        This section introduces the full scope of the theories in our analysis. 
         Firstly, recall the definition of Bregman divergence $D_f(x, y)$ from Definition \ref{def:bregman-div} for a differentiable function $f:\RR^n \rightarrow \overline \RR$. 
@@
         \subsection{smooth plus nonsmooth convex}
-            The following assumption is strictly stronger than \ref{ass:sum-of-wcnvx}. 
             \begin{assumption}[convex smooth and nonsmooth]\label{ass:standard-fista}
-                Let $F = f + g$ where $f:\RR^n\rightarrow \overline \RR$ is $L$ Lipschitz smooth, $g$ is convex. 
-                Suppose that $\argmin_{x \in \RR^n} F(x)\neq \emptyset$.
+                Let $F = f + g$ where $f:\RR^n\rightarrow \overline \RR$ is $L$ Lipschitz smooth, $g$ is convex and, $\argmin_{x \in \RR^n} F(x)\neq \emptyset$.
             \end{assumption}
@@
     \section{FISTA made simple}
-        We make the proofs for FISTA  with common enhancement technique available in simple proofs. 
-        We showcase the theories using a generic similar triangle representations of the algorithm which tremendously simplifies the arguments. 
-        The following definition captures several monotone variants of FISTA with line search,  or backtracking strategies.
+        This section gives convergence results under a unified perspective of accelerated proximal gradient methods with line search, backtracking, and monotone enhancements. 
+        Definition \ref{def:xxapg} unifies several combined heuristics. 
+        Theorem \ref{thm:xxapg-fxn-cnvg} provides a generic convergence rate for all momentum sequence satisfying Definition \ref{def:alpha-beta-rho-seq}. 
+        A specialized sequence is stated in Lemma \ref{lemma:xxapg-seq-bnd} which attains the lowest upper bound on the convergence rate. 
+        Theorem \ref{thm:xxapg-specialized-cnvg} proves the $\mathcal O(1/k^2)$ for optimality gap and, the norm of gradient mapping on the last iterate. 
         \par
-        In this section, we give convergence results for a unified formulation of monotone accelerated proximal gradient methods with line search or backtracking enhancements. 
-        Definition \ref{def:generic-mapg-ls} gives a unified view of several combined heuristics. 
-        Theorem \ref{thm:gmapg-ls-convergence} gives a generic description for the convergence rate. 
-        Lemma \ref{lemma:gmapg-seq-bnd} specializes the sequence, attains the lowest upper bound. 
-        Theorem \ref{thm:gmapg-specialized-cnvg} gives a concrete $\mathcal O(1/k^2)$ upper bound for the optimality gap and normed gradient mapping on the last iteration. 
-        \par
-        ``MAPG'' stands for monotone accelerated gradient. 
-        We refer to ``Generic Monotone Accelerated Proximal Gradient with line search" as ``GMAPG''. 
-        \begin{definition}[GMAPG]\label{def:generic-mapg-ls}\;\\ 
+        ``Abstract Monotone Accelerated Proximal Gradient with line search" is ``\XXAPG{}''. 
+        \begin{definition}[\XXAPG{}]\label{def:xxapg}\;\\ 
             Initialize any $x_0, v_0 \in \RR^n$. 
@@
                     & D_{f}(\tilde x_k, y_k) \le \frac{L_k}{2}\Vert \tilde x_k - y_k\Vert^2, \\
-                    & \text{Choose any } x_k: F(x_k) \le \min(F(\tilde x_k), F(x_{k - 1})). 
+                    & \text{Choose any } x_k: F(x_k) \le F(\tilde x_k). 
                 \end{align*}    
@@
         \end{definition}
+        \begin{remark}
+            Having $F(x_k) \le F(\tilde x_k)$ doesn't necessarily mean $F(x_k) \le F(x_{k - 1})$. 
+        \end{remark}
         The following definition characterizes the sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$, $(L_k)_{k \ge 0}$ and defines $(\beta_k)_{k \ge 0}$ for the proofs for the convergence rate. 
@@
             Let $(\alpha_k)_{k \ge 0}$ be a sequence in $\RR$ such that $\alpha_k \in (0, 1)$ for all $k \in \N$. 
-            Take $(L_k)_{k \ge 0}$ from Definition \ref{def:generic-mapg-ls} so it has $L_k > 0$ for all $k \in \N \cup \{0\}$. 
-            The sequence $(\rho_k)_{k \ge 0}$ is defined as 
+            Let $(L_k)_{k \ge 0}$ satisfy $L_k > 0$ for all $k \in \N \cup \{0\}$. 
+            Define the sequence $(\rho_k)_{k \ge 0}$ by:
             \begin{align*}
@@
             \end{align*}
-            Define sequence $(\beta_k)_{k \ge 0}$ such that $\beta_0 = 1$ and for all $k \ge 1$: 
+            Define the sequence $(\beta_k)_{k \ge 0}$, let $\beta_0 = 1$ and, for all $k \ge 1$ it's defined by: 
             \begin{align*}
@@
         \begin{lemma}[acceerated proximal gradient iterates relation]\;\label{lemma:apg-iterates}\;\\
-            The iterates $(x_k, v_k, y_k)_{k \ge 1}$ generated by Definition \ref{def:generic-mapg-ls}. 
+            The iterates $(x_k, v_k, y_k)_{k \ge 1}$ generated by Definition \ref{def:xxapg}. 
             Let $z_k = \alpha_k x^+ + (1 - \alpha_k)x_{k - 1}$. 
@@
         \end{proof}
-        \begin{theorem}[generic GMAPG convergence]\; \label{thm:gmapg-ls-convergence}\;\\
+        \begin{theorem}[generic \XXAPG{} convergence]\; \label{thm:xxapg-fxn-cnvg}\;\\
             Let $F = f + g$ satisfy Assumptions \ref{ass:standard-fista}. 
@@
             Take the sequence $(\alpha_k)_{k \ge 0}, (\beta_k)_{k \ge 0}$ and $(\rho_k)_{k \ge 0}$ from Definition \ref{def:alpha-beta-rho-seq}. 
-            Then, for all $x^+ \in \RR^n, k \ge 1$, the convergence rate of GMAPG (Definition \ref{def:generic-mapg-ls}) is given by: 
+            Then, for all $x^+ \in \RR^n, k \ge 1$, the convergence rate of \XXAPG{} (Definition \ref{def:xxapg}) is given by: 
             \begin{align*}
@@
             Define $z_k = \alpha_k x^+ + (1 - \alpha_k)x_{k - 1}$ for all $k \ge 1$. 
-            In the proof follows, the follow facts will be used. 
-            We list them in advance, and they will be labeled during the proof. 
+            In the proof that follows, we list some facts in advance before their proofs which come later. 
             \begin{enumerate}
-                \item Lemma \ref{lemma:apg-iterates}. 
-                \item The sequence $(\alpha_k)_{k \ge 1}$ has for all $k \ge 1$, $1 - \alpha_k = \alpha_k^2\alpha_{k - 1}^2\rho_{k - 1}$, $\alpha_k \in (0, 1)$ from Definition \ref{def:alpha-beta-rho-seq}.
-                \item $F$ is convex and hence $F(z_k) \le \alpha_k F(x^+) + (1 - \alpha_k)F(x_{k - 1})$ from Assumption \ref{ass:standard-fista}. 
-                \item $F(x_k) \le F(\tilde x_k)$ which is true by definition of GMAPG (Definition \ref{def:generic-mapg-ls}). 
+                \item[(a)] Lemma \ref{lemma:apg-iterates}. 
+                \item[(b)] The sequence $(\alpha_k)_{k \ge 1}$ has for all $k \ge 1$, $\alpha_{k - 1}^2\rho_{k - 1}(1 - \alpha_k) = \alpha_k^2$, $\alpha_k \in (0, 1)$ from Definition \ref{def:alpha-beta-rho-seq}.
+                \item[(c)] $F$ is convex and hence $F(z_k) \le \alpha_k F(x^+) + (1 - \alpha_k)F(x_{k - 1})$ from Assumption \ref{ass:standard-fista}. 
+                \item[(c)] $F(x_k) \le F(\tilde x_k)$ which is true by definition of \XXAPG{} (Definition \ref{def:xxapg}). 
             \end{enumerate}
@@
                 \\
-                &\underset{\text{(i)}}{=}
+                &\underset{\text{(a)}}{=}
                 F(\alpha_k x^+ + (1 - \alpha_k)x_{k - 1}) - F(\tilde x_k)
                 - \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k \Vert^2 
-                + \frac{L_k\alpha_k^2}{2}\Vert(x^+ - v_{k - 1})\Vert^2
-                \\
-                &\hspace{-0.3em}\underset{\text{(iii)}}{\le} 
+                + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_{k - 1}\Vert^2
+                \\
+                &\underset{\text{(c)}}{\le} 
                 \alpha_k F(x^+) + (1 - \alpha_k) F(x_{k - 1}) - F(\tilde x_k)
@@
                 \\
-                &\hspace{-0.3em}\underset{\text{(iv)}}{\le} 
+                &\underset{\text{(d)}}{\le} 
                 (1 - \alpha_k)(F(x_{k - 1}) - F(x^+)) + \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_{k - 1}\Vert^2
@@
                 \\
-                &= 
+                &\underset{\text{(b)}}{=} 
                 (1 - \alpha_k)(F(x_{k - 1}) - F(x^+)) + 
@@
         \end{remark}
-        \begin{theorem}[generic GMAPG gradient mapping convergence]\;\label{thm:gmapg-generic-gm-cnvg}\\
+        \begin{theorem}[generic \XXAPG{} gradient mapping convergence]\;\label{thm:xxapg-gm-cnvg}\\
             Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista}. 
-            % Let the sequences $(x_k, y_k, v_k)$ satisfy GMAPG (Definition \ref{def:generic-mapg-ls}).
-            Let the sequences $(x_k, y_k, v_k)$ satisfy GMAPG (Definition \ref{def:generic-mapg-ls}), and take the momentum sequences $(\alpha_k)_{k \ge 0}, (\beta_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ from Definition \ref{def:alpha-beta-rho-seq}.
+            % Let the sequences $(x_k, y_k, v_k)$ satisfy \XXAPG{} (Definition \ref{def:xxapg}).
+            Let the sequences $(x_k, y_k, v_k)$ satisfy \XXAPG{} (Definition \ref{def:xxapg}), and take the momentum sequences $(\alpha_k)_{k \ge 0}, (\beta_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ from Definition \ref{def:alpha-beta-rho-seq}.
             If in addition, 
             \begin{enumerate}
-                \item The sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and, GMAPG is initialized with $L_0 \ge L$ or, equivalently a successful line search satisfying \mbox{$D_f(x_{0}, x_{-1}) \le L_0/2\Vert x_{0} - x_{-1}\Vert^2$};
+                \item The sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and, \XXAPG{} is initialized with $L_0 \ge L$ or, equivalently a successful line search satisfying \mbox{$D_f(x_{0}, x_{-1}) \le L_0/2\Vert x_{0} - x_{-1}\Vert^2$};
                 \item $v_0=x_0 = T_{1/L_0, f, g}(x_{-1})$ for any $x_{-1} \in\RR^n$ and there exists $x^+$ which is a minimizer of $F$. 
@@
             Then, we have the convergence of gradient mapping, it satisfies for all $k \ge 1$ the inequality:
-            \begin{align}\label{ineq:gmapg-generic-gm-cnvg-prt1}
+            \begin{align}\label{ineq:xxapg-gm-cnvg-prt1}
                 \Vert \mathcal G_{1/L_k} (y_k)\Vert &\le 
@@
             It has also:
-            \begin{align}\label{ineq:gmapg-generic-gm-cnvg-prt2}
+            \begin{align}\label{ineq:xxapg-gm-cnvg-prt2}
                 \frac{1}{2L_0}\Vert \mathcal G_{1/L_0}(x_{-1}) \Vert^2
@@
         \begin{proof}
-            \eqref{ineq:gmapg-generic-gm-cnvg-prt2} is direct because $x_0 = T_{1/L_0, f, g}(x_{-1})$ and \mbox{$D_f(x_{0}, x_{-1}) \le L_0/2\Vert x_{0} - x_{-1}\Vert^2$} is assumed in the statement hypothesis, using \ref{lemma:fitsa-pg-ineq} with $x = x_{-1}, z = x_{-1}$, using  gradient mapping as defined in Definition \ref{def:gm-for-ch2} it has
+            \eqref{ineq:xxapg-gm-cnvg-prt2} is direct because $x_0 = T_{1/L_0, f, g}(x_{-1})$ and \mbox{$D_f(x_{0}, x_{-1}) \le L_0/2\Vert x_{0} - x_{-1}\Vert^2$} is assumed in the statement hypothesis, using Lemma \ref{lemma:fitsa-pg-ineq} with $x = x_{-1}, z = x_{-1}$, by Definition \ref{def:gm-for-ch2} it has
             \begin{align*}
@@
                 \\
-                &= (F(x_{-1}) - F(\bar x)) - \frac{L_0}{2}\Vert L_0^{-1}\mathcal G_{1/L_0}(x_{-1})\Vert^2. 
-            \end{align*}
-            We label the following results prior to their proofs for a sleeker exposition for the proof of \eqref{eqn:emp:result-item-2}. 
+                &= F(x_{-1}) - F(x_0) - \frac{L_0}{2}\Vert L_0^{-1}\mathcal G_{1/L_0}(x_{-1})\Vert^2. 
+            \end{align*}
+            We label the following results prior to their proofs which will come later for a sleeker exposition for the proof of \eqref{eqn:emp:result-item-2}. 
             \begin{enumerate}
-                \item[(a)] From Definition \ref{def:generic-mapg-ls}, the gradient mapping satisfies for all $k \ge 1$ that $\Vert \mathcal G_{1/L_k} (y_k)\Vert = L_k\alpha_k \Vert v_k - v_{k - 1}\Vert$.
+                \item[(a)] From Definition \ref{def:xxapg}, the gradient mapping satisfies for all $k \ge 1$ that $\Vert \mathcal G_{1/L_k} (y_k)\Vert = L_k\alpha_k \Vert v_k - v_{k - 1}\Vert$.
                 \item[(b)] We have $(a_k)_{k \ge 1}$ satisfying $\forall k \ge 1$ that $(1 - \alpha_k)\rho_{k - 1} = \alpha_k^2/\alpha_{k - 1}^2$ from the statement hypothesis.
-We assumed $\alpha_0 = 0, \beta_0 = 1$, $x^+$ is a minimizer of $F$.
+We assumed $\alpha_0 = 0, \beta_0 = 1$, $x^+$ is a minimizer of $F$ and, a successful line search in item (i).
 Then using these it has for all $k \ge 0$ it has $\frac{\alpha_k}{\sqrt{\beta_k L_0}}\Vert x^+ - v_k\Vert \le \Vert x^+ - v_0\Vert$.
@@
             \end{enumerate}
-            Using the above intermediate results, the convergence in \eqref{ineq:gmapg-generic-gm-cnvg-prt1} can be derived. 
+            Using the above intermediate results, the convergence in \eqref{ineq:xxapg-gm-cnvg-prt1} can be derived. 
             From (a) it has for all $k \ge 0$: 
@@
             Now, \textbf{let's proof intermediate results (a)}. 
-            From the definition of GMAPG it has 
+            From the Definition \ref{def:xxapg} it has 
             \begin{align*}
@@
             \end{align*}
-            Using the above, and definition of GMAPG, it yields 
+            Current iterates $v_k$ is updated via $x_{k-1}, \tilde x_k$ so consider:
             \begin{align*}    
@@
                 &= \alpha_k^{-1}\tilde x_k - \alpha_k^{-1} y_k 
-                = \alpha^{-1}_k(\tilde x_k - y_k) = \alpha_k^{-1}(T_{L_k} y_k - y_k)
+                = \alpha^{-1}_k(\tilde x_k - y_k) = \alpha_k^{-1}(T_{1/L_k} y_k - y_k)
                 \\
@@
             Because $\beta_0 = \alpha_0 = 1$, the base case holds. 
-            For all $k \ge 1$, we consider the convergence claim and use the assumption that $x^+$ is a minimizer of $F$ so, it has from Theorem \ref{thm:gmapg-ls-convergence} that 
+            For all $k \ge 1$, we consider the convergence claim and use the assumption that $x^+$ is a minimizer of $F$ so, it has from Theorem \ref{thm:xxapg-fxn-cnvg} that 
             \begin{align*}
@@
         \end{remark}
-        \begin{lemma}[specialized GMAPG momentum sequence]\;\label{lemma:gmapg-seq-bnd}\\
+        \begin{lemma}[specialized \XXAPG{} momentum sequence]\;\label{lemma:xxapg-seq-bnd}\\
             Take sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}, (\beta_k)_{k \ge 0}$ as in Definition \ref{def:alpha-beta-rho-seq}. 
@@
             A simpler upper bound is more practical. 
-            For all $k \ge 1$ let $\widehat L_k = \max_{i = 0, 1, \ldots, k} L_i$ then 
+            For all $k \ge 1$ let  
+            \begin{align*}
+                \widehat L_k &= \max\left(
+                    L_0, \left(
+                        \frac{1}{k} \sum_{i = 1}^{k} \sqrt{L_i^{-1}}
+                    \right)^{-2}
+                \right). 
+            \end{align*}
+            Then, 
             \begin{align*}
@@
             \end{align*}
-            This simplifies the convergence claim back in Theorem \ref{thm:gmapg-ls-convergence}. 
-            The above inequality would work the same if we set: 
-            \begin{align*}
-                \widehat L_k &= \max\left(
-                    L_0, \left(
-                        \frac{1}{k} \sum_{i = 1}^{k} \sqrt{L_i^{-1}}
-                    \right)^{-2}
-                \right). 
-            \end{align*}
+            This simplifies the convergence claim back in Theorem \ref{thm:xxapg-fxn-cnvg}. 
         \end{remark}
-        \begin{theorem}[specialized GMAPG convergence rate]\label{thm:gmapg-specialized-cnvg}
+        \begin{theorem}[specialized \XXAPG{} convergence rate]\label{thm:xxapg-specialized-cnvg}
             Suppose that $F = f + g$ satisfy Assumption \ref{ass:standard-fista}. 
-            Let the sequences $(x_k, v_k, v_k)_{k \ge 0}$ and $(L_k)_{k \ge 0}$ satisfy GMAPG in Definition \ref{def:generic-mapg-ls} and, assume that the GMAPG is initialized by $x_0 = v_0 = T_{1/L_0}(x_{-1})$ and, assume $\rho_{k - 1} = L_{k}^{-1}L_{k}$, $\alpha_0 = 1$ so the sequence $(\alpha_k)_{k \ge 0}$ satisfies for all $k\ge 1$: $\alpha_{k - 1}^2L_k^{-1}L_{k - 1}(1 - \alpha_k) = \alpha_k^2$.
+            Let the sequences $(x_k, v_k, v_k)_{k \ge 0}$ and $(L_k)_{k \ge 0}$ satisfy \XXAPG{} in Definition \ref{def:xxapg} and, assume that the \XXAPG{} is initialized by $x_0 = v_0 = T_{1/L_0}(x_{-1})$ and, assume $\rho_{k - 1} = L_{k}^{-1}L_{k}$, $\alpha_0 = 1$ so the sequence $(\alpha_k)_{k \ge 0}$ satisfies for all $k\ge 1$: $\alpha_{k - 1}^2L_k^{-1}L_{k - 1}(1 - \alpha_k) = \alpha_k^2$.
             Let $x^+$ be a minimizer of $F$, define 
@@
         \begin{proof}
-            To see (i), use Lemma \ref{lemma:gmapg-seq-bnd} and its remark to bound $(\beta_k)_{k \ge 1}$ and then, apply Theorem \ref{thm:gmapg-ls-convergence} because the assumptions of $x^+, (\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ suit.
-            To see (ii), the convergence claim from \ref{thm:gmapg-generic-gm-cnvg} simplifies with $\widehat L_k \ge L_0$ and, it has 
+            To see (i), use Lemma \ref{lemma:xxapg-seq-bnd} and its remark to bound $(\beta_k)_{k \ge 1}$ and then, apply Theorem \ref{thm:xxapg-fxn-cnvg} because the assumptions of $x^+, (\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ suit.
+            To see (ii), the convergence claim from \ref{thm:xxapg-gm-cnvg} simplifies with $\widehat L_k \ge L_0$ and, it has 
             \begin{align}
@@
 
-    \section{Algorithmic description of GMAPG}
-        There are several components to the GMAPG algorithm. 
-        This section will introduce various type of implementations that can be fitted into GMAPG in Definition \ref{def:generic-mapg-ls}. 
+    \section{Algorithmic description of \XXAPG{}}
+        There are several components to the \XXAPG{} algorithm. 
+        This section will introduce various type of implementations that can be fitted into \XXAPG{} in Definition \ref{def:xxapg}. 
         \subsection{Line search routines}
@@
                 \item $f, g$ are functions satisfying Assumption \ref{ass:standard-fista}. 
-                \item $x, v$ are the $x_k, v_k$ iterates in Definition \ref{def:generic-mapg-ls}. 
-                \item $\alpha$ are the current $\alpha_k$ in Definition \ref{def:generic-mapg-ls}. 
+                \item $x, v$ are the $x_k, v_k$ iterates in Definition \ref{def:xxapg}. 
+                \item $\alpha$ are the current $\alpha_k$ in Definition \ref{def:xxapg}. 
                 \item $L$ is the estimate of the Lipschitz constant of $f$ passed in by the inner loop. 
@@
             Algorithm \ref{alg:beck-mono} is a subroutine for asserting monotone condition on function value. 
-            The parameter $G$ has no actual usage besides making it compatible with Algorithm \ref{alg:nes-mono} in the context of Algorithm \ref{alg:gmapg}. 
+            The parameter $G$ has no actual usage besides making it compatible with Algorithm \ref{alg:nes-mono} in the context of Algorithm \ref{alg:xxapg}. 
             The input $\tilde x$ is the candidate iterate produced by FISTA without monotone constraints and $x$ is the previous iterates $x_{k - 1}$ in the inner loop. 
@@
             \par
-            The above Algorithm \ref{alg:nes-mono} implements and adapts Nesterov's monotone scheme from Nesterov \cite[2.2.32]{nesterov_lectures_2018} for GMAPG. 
+            The above Algorithm \ref{alg:nes-mono} implements and adapts Nesterov's monotone scheme from Nesterov \cite[2.2.32]{nesterov_lectures_2018} for \XXAPG{}. 
             In addition to Algorithm \ref{alg:beck-mono}, $\eta$ is a new input parameter and $G$ has a significance role. 
             $\eta$ is a stepsize parameter for weakly convex objective $F = f + g$ satisfying Assumption \ref{ass:sum-of-wcnvx}. 
-            $G$ is the norm of the gradient mapping updated at at $\hat y$ which will be returned to the inner loop to verify exit conditions.
-
-        \subsection{GMAPG main algorithm}
-            % GMAPG ------------------------------------------------------------
+            $G$ is the norm of the gradient mapping updated at $\hat y$ which will be returned to the inner loop to verify exit conditions.
+
+        \subsection{\XXAPG{} main algorithm}
             \begin{algorithm}[H]
@@
                     \STATE{\noindent
-                        \textbf{Function GMAPG Inputs: }
+                        \textbf{Function \XXAPG{} Inputs: }
                         \begin{tabular}{|ll}
@@
                     \IF{$G_0 \le \epsilon$}
-                        \STATE{\textbf{Return: }$x_k, 0, L_0, G_0$}
+                        \STATE{\textbf{Return: }$x_k, 0, L_0, G_0$}\label{alg:xxapg-exit1}
                     \ENDIF
@@
                         \IF{$G_k^+ < \epsilon \textbf{ or } (\mathbf E_\chi  \textbf{ and } k > N_{\min})$}
-                            \STATE{\textbf{break}}
+                            \STATE{\textbf{break}}\label{alg:xxapg-exit2}
                         \ENDIF
@@
                     \STATE{\textbf{Return: }$x_k, k, \overline L, G_k^+ $}
-                \caption{GMAPG with Chambolle's backtracking}\label{alg:gmapg}
+                \caption{\XXAPG{} with Chambolle's backtracking}\label{alg:xxapg}
                 \end{algorithmic}
             \end{algorithm}
-            The above Algorithm \ref{alg:gmapg} is an implementation of GMAPG in Definition \ref{alg:gmapg}. 
-            The first iterates $x_0$ is produced by a step of proximal gradient descent through Algorithm \ref{alg:armijo-ls} so, it has $x_0 = v_0 = T_{1/L_0}(x_{-1})$, and consequently all results from Theorem \ref{thm:gmapg-specialized-cnvg} apply.
+            The above Algorithm \ref{alg:xxapg} is an implementation of \XXAPG{} in Definition \ref{alg:xxapg}. 
+            The first iterates $x_0$ is produced by a step of proximal gradient descent through Algorithm \ref{alg:armijo-ls} so, it has $x_0 = v_0 = T_{1/L_0}(x_{-1})$, and consequently all results from Theorem \ref{thm:xxapg-specialized-cnvg} apply.
             Parameters $r, \rho$ are chosen in the discretion of the practitioners. 
             For example, we chose $r= 0.4, \rho = 2^{1/1024}$. 
-
-    \section{Examples of GMAPG in the literature}
+            \begin{observation}[\XXAPG{} exit conditions]
+                Algorithm \ref{alg:xxapg} exits and returns its results on line \ref{alg:xxapg-exit1}, or at line \ref{alg:xxapg-exit2}. 
+                If exited, then at least one of the conditions are true. 
+            \end{observation}
+
+    \section{Examples of \XXAPG{} in the literature}
         \begin{example}[MFISTA with Armijo line search]\;\\\vspace{-1em}
@@
             \end{algorithm}
-            We now demonstrate that Algorithm \ref{alg:mfista-armijo} is a special case of Definition \ref{def:generic-mapg-ls}.
-            Let's consider $y_{k + 1}$ produced the GMAPG. 
+            We now demonstrate that Algorithm \ref{alg:mfista-armijo} is a special case of Definition \ref{def:xxapg}.
+            Let's consider $y_{k + 1}$ produced the \XXAPG{}. 
             If $x_k = x_{k - 1}$ then replacing all instance of $x_k$ by $x_{k - 1}$ it has: 
@@
         \end{example}
-        \begin{example}[Nesterov's monotone scheme with generic line search]\;\\
-            The following is (2.2.32) in Nesterov's book, phrased in our GMAPG framework. 
-            \begin{algorithm}\label{alg:nesterov-mono-generic-ls}
-            \begin{algorithmic}[1]
-            \STATE{\textbf{Input: } }
-            \end{algorithmic}\caption{Nesterov's monotone scheme with generic line search}
-            \end{algorithm}
-        \end{example}
+        % \begin{example}[Nesterov's monotone scheme with generic line search]\;\\
+        %     The following is (2.2.32) in Nesterov's book, phrased in our \XXAPG{} framework. 
+        %     \begin{algorithm}\label{alg:nesterov-mono-generic-ls}
+        %     \begin{algorithmic}[1]
+        %     \STATE{\textbf{Input: } }
+        %     \end{algorithmic}\caption{Nesterov's monotone scheme with generic line search}
+        %     \end{algorithm}
+        % \end{example}
 
     \section{Practical enhancement from the Nesterov's Monotone Variant}
-        The following definition is a set of necessary conditions GMAPG with Nesterov's monotone subroutine. 
-        Our goal in this section is to show that Nesterov's implementations of monotone accelerated gradient method has convergence results under Assumption \ref{ass:sum-of-wcnvx}.
+        Under Assumption \ref{ass:sum-of-wcnvx}, Theorem \ref{thm:nes-mono-wcnvx-convergence} shows the Nesterov's monotone algorithm in Definition \ref{def:nes-monotone-scheme} eventually terminate. 
         \begin{definition}[nonconvex Nesterov's monotone scheme]\;\label{def:nes-monotone-scheme}\\
@@
         A stronger result on the convergence rate of $\Vert \mathcal G_{1/\eta_k}(y_k)\Vert$ can be obtained if, we assume that the function $F=f + g$ satisfies Assumption \ref{ass:standard-fista}. 
+        See Nesterov's book \cite{nesterov_lectures_2018} for more details.
 
     \section{Restarting with function values for linear convergence}
-        In this section, we show that restarting GMAPG with a well suited conditions yields fast linear global convergence. 
-        We adapt and improve prior theories from Alamo \cite{alamo_restart_2019} for our GMAPG method. 
+        We adapted and improved prior theories on FISTA restart with global linear convergence from Alamo \cite{alamo_restart_2019} for our \XXAPG{} method. 
         The following definition, gives the quadratic growth property of $f$ which allows for a fast linear convergence rate using adaptive restarts. 
@@
         \end{assumption}
-        The following proposition about line search will furnish convergence results from previous section. 
-        \begin{proposition}[Lipschitz line search estimates are bounded]\label{prop:bnded-lip-ls}
-            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista}. 
-            Choose such $F$ for Algorithm \ref{alg:gmapg} so, it generates the sequence $(L_k)_{k\ge 0}$. 
-            Then, the sequence $(\hat L_k)_{k \ge 1}$ from Theorem \ref{thm:gmapg-specialized-cnvg} is bounded above and, it has
-            \begin{align*}
-                \widehat L_k &:= \max\left(
-                    L_0, \left(
-                        \frac{1}{k} \sum_{i = 1}^{k} \sqrt{L_i^{-1}}
-                    \right)^{-2}
-                \right)\le  \overline L \le \max\left(L_0,  2L\right). 
-            \end{align*}
-        \end{proposition}
-        \begin{proof}
-            A line search is triggered in Algorithm \ref{alg:armijo-ls}, \ref{alg:chambolle-btls} if and only if $L_{k + 1} = 2L_{k}$ for some $k \ge 0$ and, there exists some $x\in \RR^n, y \in \RR^n$ such that $D_f(x, y) > L_k\Vert x - y \Vert^2$.
-            For all $k = 0, 1, \ldots $, if $L_k \ge L$ then, it has $D_f(x, y) \le L_k/2\Vert x - y\Vert^2$ for all $x, y \in \RR^n$. 
-            Hence, $L_{k + 1} \le L_k$ because a line sarch is never triggered. 
-            \par
-            For contradiction let's assume that there exists $k \ge 1$ such that a line search is triggered for $L_k$ and, $L_{k + 1} = 2L_{k} > 2L$, then $L_k > L$, but we just showed that this implies $L_{k + 1} \le L_k$, which is a contradiction.
-            Therefore, if $L_{k + 1} = 2L_k$ then it must be that $L_k < L$ so, the highest value it can achieve is either $L_0$, or $2L$. 
-        \end{proof}
         \par
@@
         $\mathbf E_{\chi}^{a}$ only uses function values on iterates available to the inner loop to determine the exit conditions, and it achieves global fast linear convergence. 
-        The inner loop algorithm is described in Algorithm \ref{alg:gmapg}, let $k$ denote the inner loop counter and define $m = \lfloor k/2 \rfloor + 1$ the conditions are: 
+        The inner loop algorithm is described in Algorithm \ref{alg:xxapg}, let $k$ denote the inner loop counter and define $m = \lfloor k/2 \rfloor + 1$ the conditions are: 
         \begin{align}\label{ineq:rgmapg-exit-cond}
@@
             \STATE{$n_0 := 0; z_0 = x_{-1}$.}
-            \STATE{$z_1, p_0, \overline L_1, G^{(0)}:= \textbf{GMAPG}(f, g, x_{-1}, L, r_j, \rho, N_{\min}=n_0, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
+            \STATE{$z_1, p_0, \overline L_1, G^{(0)}:= \textbf{\XXAPG{}}(f, g, x_{-1}, L, r_j, \rho, N_{\min}=n_0, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
             \STATE{$n_1:=p_0$.}
@@
                 \ENDIF
-                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1}, G^{(j)} := \textbf{GMAPG}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
+                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1}, G^{(j)} := \textbf{\XXAPG{}}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
                 \STATE{$M := M - p_j$.}
@@
             \ENDFOR
-            \end{algorithmic}\caption{Linear convergence restarted GMAPG}\label{alg:linear-rgmapg}
+            \end{algorithmic}\caption{Linear convergence restarted \XXAPG{}}\label{alg:linear-rgmapg}
         \end{algorithm}
         \par
-        Algorithm \ref{alg:linear-rgmapg} implements a restarted GMAPG with condition $\textbf{E}_{\chi}^a$ and, it has a fast linear convergence rate. 
+        Algorithm \ref{alg:linear-rgmapg} implements a restarted \XXAPG{} with condition $\textbf{E}_{\chi}^a$ and, it has a fast linear convergence rate. 
         The following observation on it is crucial to take notice for the convergence rate. 
         \begin{observation}\label{obs:rgmapg}
-            If the outer loop runs for $j = 1, 2, \ldots, J$ iterations with $M \ge J$ so the algorithm terminated due $G_k^+ \le \epsilon$. 
-            Then for all $J\ge j\ge 1$ it has $n_{j}\le n_{j + 1}$ hence $(n_j)_{j \ge 0}^J$ is monotone increasing
-            For all $J -1 \ge j \ge 1 $ it has $p_{j-1}\le p_{j}$ so $(p_j)_{j \ge 1}^{J}$ is monotone excluding the last iterates $p_J$. 
+            If the outer loop runs for $j = 1, 2, \ldots, J$ iterations with $M \ge J$ so the algorithm terminated due $G^{(J - 1)} \le \epsilon$. 
+            Then, it has 
+            \begin{enumerate}
+                \item for all $J\ge j\ge 1$ it has $n_{j}\le n_{j + 1}$ hence $(n_j)_{j \ge 0}^J$ is monotone increasing; 
+                \item for all $J -1 \ge j \ge 1 $ it has $p_{j-1}\le p_{j}$ so $(p_j)_{j \ge 1}^{J}$ is monotone excluding the last iterates $p_J$. 
+            \end{enumerate}
         \end{observation}
         \par
-        For all $1 \le j \le J$, $n_j$ is used as the lower bound $N_{\min}$ for the GMAPG inner loop described in Algorithm \ref{alg:gmapg} at iteration $j$ and, $p_j$ is the actual iteration underwent by the inner loop therefore it has $p_j \ge n_{j}$.
+        For all $1 \le j \le J$, $n_j$ is used as the lower bound $N_{\min}$ for the \XXAPG{} inner loop described in Algorithm \ref{alg:xxapg} at iteration $j$ and, $p_j$ is the actual iteration underwent by the inner loop therefore it has $p_j \ge n_{j}$.
         $n_{j + 1}$ is the minimum iteration for the next execution of GMAGP, and it has $n_{j + 1} = p_{j}$  if the ``if statement" isn't triggered otherwise $n_{j + 1} = 2p_{j}$. 
         For $j < J$ so it excludes the last iteration, it has either $p_{j + 1} \ge n_{j + 1} = 2p_j \ge 2n_{j} \ge n_j$ or $p_{j + 1} \ge n_{j + 1} = p_j \ge n_j$. 
-        When $j = J$ it's not necessarily true that $p_J \ge n_J$ because on the last iteration, it can exit the for loop through conditions $G_k^+ \le \epsilon$ in line 14 of Algorithm \ref{alg:gmapg}, but $n_J \ge p_{J - 1} \ge n_{J - 1}$ still.
+        When $j = J$ it's not necessarily true that $p_J \ge n_J$ because on the last iteration, it can exit the for loop through conditions $G_k^+ \le \epsilon$ in line 14 of Algorithm \ref{alg:xxapg}, but $n_J \ge p_{J - 1} \ge n_{J - 1}$ still.
         \par
         We now introduce the following notations for the convergence proof. 
-        Since the restarted GMAPG consist of executions of an outer loop in Algorithm \ref{alg:linear-rgmapg} in variable $j$ and, an inner loop in Algorithm \ref{alg:gmapg} in variable $k$, we denote $x_{k}^{(j)}$ for the iterates $x_k$ in the inner loop during the $j$ iteration of the outer loop together.
+        Since the restarted \XXAPG{} consist of executions of an outer loop in Algorithm \ref{alg:linear-rgmapg} in variable $j$ and, an inner loop in Algorithm \ref{alg:xxapg} in variable $k$, we denote $x_{k}^{(j)}$ for the iterates $x_k$ in the inner loop during the $j$ iteration of the outer loop together.
         We make the choice to have $x_{-1}^{(j + 1)} = z_{j + 1} = x_{p_j}^{(j)}$ for consistencies across theorems from previous sections. 
@@
         \begin{lemma}[maximum iteration needed for an optimality gap ratio]\;\label{lemma:prog-ratio}\\
-            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista} so $F^+ := \inf_xF(x)$, $X^+$ is the set of minimizers, and $\mu > 0$ is the quadratic growth constant. 
-            Let the sequence $(x_k)_{k \ge -1}$ be generated by GMAPG (Definition \ref{alg:gmapg}). 
+            Suppose that $F = f + g$ satisfies Assumption \ref{ass:q-growth-ch2} so $F^+ := \inf_xF(x)$, $X^+$ is the set of minimizers, and $\mu > 0$ is the quadratic growth constant. 
+            Let the sequence $(x_k)_{k \ge -1}$ be generated by \XXAPG{} (Definition \ref{alg:xxapg}). 
             Then it has
@@
             For all $k \ge 0$, denote minimizer $x^+_k = \Pi_{X^+}x_k$ so, $F(x^+_k) = F^+$. 
-            From Theorem \ref{thm:gmapg-specialized-cnvg} it has 
+            From Theorem \ref{thm:xxapg-specialized-cnvg} it has 
             \begin{align*}
@@
             }
+        \end{proof}
+        The following proposition places an upper bound on the estimated Lipschitz constant from the line search routine specified in Algorithm \ref{alg:armijo-ls}, \ref{alg:chambolle-btls}. 
+        This is crucial to derive a global convergence properties of the algorithm based on the parameters of the objective function. 
+        \begin{proposition}[Lipschitz line search estimates are bounded]\label{prop:bnded-lip-ls}
+            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista}. 
+            Choose such $F$ for Algorithm \ref{alg:xxapg} so, it generates the sequence $(L_k)_{k\ge 0}$. 
+            Then, the sequence $(\hat L_k)_{k \ge 1}$ from Theorem \ref{thm:xxapg-specialized-cnvg} is bounded above and, it has
+            \begin{align*}
+                \widehat L_k &:= \max\left(
+                    L_0, \left(
+                        \frac{1}{k} \sum_{i = 1}^{k} \sqrt{L_i^{-1}}
+                    \right)^{-2}
+                \right)\le  \overline L \le \max\left(L_0,  2L\right). 
+            \end{align*}
+        \end{proposition}
+        \begin{proof}
+            A line search is triggered in Algorithm \ref{alg:armijo-ls}, \ref{alg:chambolle-btls} if and only if $L_{k + 1} = 2L_{k}$ for some $k \ge 0$ and, there exists some $x\in \RR^n, y \in \RR^n$ such that $D_f(x, y) > L_k\Vert x - y \Vert^2$.
+            For all $k = 0, 1, \ldots $, if $L_k \ge L$ then, it has $D_f(x, y) \le L_k/2\Vert x - y\Vert^2$ for all $x, y \in \RR^n$. 
+            Hence, $L_{k + 1} \le L_k$ because a line sarch is never triggered. 
+            \par
+            For contradiction let's assume that there exists $k \ge 1$ such that a line search is triggered for $L_k$ and, $L_{k + 1} = 2L_{k} > 2L$, then $L_k > L$, but we just showed that this implies $L_{k + 1} \le L_k$, which is a contradiction.
+            Therefore, if $L_{k + 1} = 2L_k$ then it must be that $L_k < L$ so, the highest value it can achieve is either $L_0$, or $2L$. 
         \end{proof}
@@
             \end{align*}
-            Observe that line 14 of Algorithm \ref{alg:gmapg} exits as soon as possible if $\mathbf E_\chi^a$ is true and $k > N_{\min} = n_j$ and, $G_k \le \epsilon$ will only cause it to exit earlier therefore it has $p_j \le \max(\bar p, n_j)$.
+            Observe that line 14 of Algorithm \ref{alg:xxapg} exits as soon as possible if $\mathbf E_\chi^a$ is true and $k > N_{\min} = n_j$ and, $G_k \le \epsilon$ will only cause it to exit earlier therefore it has $p_j \le \max(\bar p, n_j)$.
             \par
@@
             \par
-            Our goal now is to show that at iteration $j = s$ of Algorithm \ref{alg:linear-rgmapg} it must have $G_0 \le \epsilon$ at line 5 of Algorithm \ref{alg:gmapg}. 
+            Our goal now is to show that at iteration $j = s$ of Algorithm \ref{alg:linear-rgmapg} it must have $G_0 \le \epsilon$ at line 5 of Algorithm \ref{alg:xxapg}. 
             \par
-            Consider the start of the $s$ th iteration of the outer loop, denote $L_0^{(s)}, G_0^{(s)}$ as the $L_0$ in line 4 in Algorithm \ref{alg:gmapg}, it would give the following inequalities
+            Consider the start of the $s$ th iteration of the outer loop, denote $L_0^{(s)}, G_0^{(s)}$ as the $L_0$ in line 4 in Algorithm \ref{alg:xxapg}, it would give the following inequalities
             {\allowdisplaybreaks
@@
             \begin{enumerate}
-                \item [(a)] At the $s$ iteration of the loop in Algorithm \ref{alg:linear-rgmapg}, $z_s$ is passed into Algorithm \ref{alg:gmapg} with $x_{-1} = z_s$.
-Therefore, at line 3 in Algorithm \ref{alg:gmapg} it calls Algorithm \ref{alg:armijo-ls} with $x_{-1} = z_s, \alpha_0 = 1, L^+$ which means $y^+ = x_{-1} = z_s$ at line 5 and $x^+ = T_{1/L^+}(z_s)$.
-Coming back to line 3 in Algorithm \ref{alg:gmapg}, it assigns $y_0 = y^+ = z_s, x_0 = x^+ = T_{1/L^+}(z_s)$ and $L_0 = L^+$.
+                \item [(a)] At the $s$ iteration of the loop in Algorithm \ref{alg:linear-rgmapg}, $z_s$ is passed into Algorithm \ref{alg:xxapg} with $x_{-1} = z_s$.
+Therefore, at line 3 in Algorithm \ref{alg:xxapg} it calls Algorithm \ref{alg:armijo-ls} with $x_{-1} = z_s, \alpha_0 = 1, L^+$ which means $y^+ = x_{-1} = z_s$ at line 5 and $x^+ = T_{1/L^+}(z_s)$.
+Coming back to line 3 in Algorithm \ref{alg:xxapg}, it assigns $y_0 = y^+ = z_s, x_0 = x^+ = T_{1/L^+}(z_s)$ and $L_0 = L^+$.
 Assuming the line search went successful, it will have $D_f(z_s, x_0) \le L^{(s)}_0/2 \Vert z_s - x_0\Vert^2$.
                 \item [(b)] We used definition of gradient mapping in Definition \ref{def:gm-for-ch2}. 
-                \item [(c)] By the assumption that the line search in Algorithm \ref{alg:armijo-ls} is successful at $z_s$ back in item (a), here we can use \eqref{eqn:emp:result-item-2} in Theorem \ref{thm:gmapg-generic-gm-cnvg}.
-                \item [(d)] GMAPG is monotone in function value for the use of $\mathbf M$ that is either Algorithm \ref{alg:beck-mono} or \ref{alg:nes-mono}, so it has $F\left(x_{p_s}^{(s)}\right) \le F\left(x_0^{(s)}\right)$.
+                \item [(c)] By the assumption that the line search in Algorithm \ref{alg:armijo-ls} is successful at $z_s$ back in item (a), here we can use \eqref{eqn:emp:result-item-2} in Theorem \ref{thm:xxapg-gm-cnvg}.
+                \item [(d)] \XXAPG{} is monotone in function value for the use of $\mathbf M$ that is either Algorithm \ref{alg:beck-mono} or \ref{alg:nes-mono}, so it has $F\left(x_{p_s}^{(s)}\right) \le F\left(x_0^{(s)}\right)$.
                 \item [(e)] Here we used the assumption that no doubling occurs so $n_{t + 1} = p_t$ for all $j \le t \le s$ meaning that line 13 in Algorithm \ref{alg:linear-rgmapg} has $F(z_t) - F(z_{t + 1}) \ge e^{-1}(F(z_{t - 1}) - F(z_t))$.
 For that, we recursively unrolled it for $T_\epsilon$ many iterations starting with $t = s = j + T_\epsilon - 1$ ending with $t = j$.
-                \item [(f)] We used the monotone property of subroutine $\mathbf M$ in GMAPG again so $F(z_0) \ge F(z_{j - 1})$. 
+                \item [(f)] We used the monotone property of subroutine $\mathbf M$ in \XXAPG{} again so $F(z_0) \ge F(z_{j - 1})$. 
                 \item [(g)] We substituted $T_\epsilon = \lceil\ln(2\epsilon^{-2}(F(z_0) - F^+))\rceil$ and, removing $\lceil\cdot\rceil$ to make for the $\le$ inequality.
@@
             \end{enumerate}
-            The upper bound on the total number of iterations of GMAPG over $J$ iteration of outer loop is given by: 
+            The upper bound on the total number of iterations of \XXAPG{} over $J$ iteration of outer loop is given by: 
             \begin{align*}
@@
         \par
-        The final results from above theorem provide the convergence rate of iterates and the complexity of restart GMAPG under Assumption \ref{ass:q-growth-ch2}. 
+        The final results from above theorem provide the convergence rate of iterates and the complexity of restart \XXAPG{} under Assumption \ref{ass:q-growth-ch2}. 
         We denote $\kappa := L/\mu$. 
-        \begin{theorem}[restarted GMAPG convergence and complexity]\;\label{thm:rgmapg-cnvg-complexity}\\
-            Let $F = f + g$ satisfy Assumption \ref{ass:q-growth-ch2}. 
+        \begin{theorem}[restarted \XXAPG{} convergence and complexity]\;\label{thm:rgmapg-cnvg-complexity}\\
+            Let $F = f + g$ satisfy Assumption \ref{ass:q-growth-ch2}, and apply it to Algorithm \ref{alg:linear-rgmapg}. 
             Let $J$ be the total number of iteration performed to achieve accuracy in the outer loop. 
-            Let $K := \sum_{i = 0}^{J - 1}p_i$ be the total iterations. 
-            Then, the maximum $K$ needed to achieve optimality $\Vert z_J - z_J^+\Vert \le \delta$ on the iterates is bounded by $\mathcal O\left(\frac{1}{\sqrt{\kappa}}\ln\left(\frac{1}{\kappa\delta}\right)\right)$.
+            For each $0 j \le J$, $p_j$ is the number of inner iterations of the inner loop. 
+            Let $K := \sum_{i = 0}^{J - 1}p_i$ be the total number of iterations of the inner loop. 
+            Let $z_j$ be the iterates returned by the inner loop. 
+            Then, the maximum $K$ needed to achieve optimality $\Vert z_J - z_J^+\Vert \le \delta$ is bounded by $\mathcal O\left(\frac{1}{\sqrt{\kappa}}\ln\left(\frac{1}{\kappa\delta}\right)\right)$.
         \end{theorem}
         \begin{proof}
-            Suppose a total of $K := \sum_{i = 0}^{J - 1} p_i$ iteration were performed and, at line 10 of Algorithm \ref{alg:linear-rgmapg} at iteration $j = J$ it achieved $G_0 \le \epsilon$ at line 5 of Algorithm \ref{alg:gmapg}.
-            That will cause the inner GMAPG to return $G_0$ so, at line 10 it has $G^{(J)} < \epsilon$ in Algorithm \ref{alg:linear-rgmapg}. 
+            Suppose a total of $K := \sum_{i = 0}^{J - 1} p_i$ iteration were performed and, at line 10 of Algorithm \ref{alg:linear-rgmapg} at iteration $j = J$ it achieved $G_0 \le \epsilon$ at line 5 of Algorithm \ref{alg:xxapg}.
+            That will cause the inner \XXAPG{} to return $G_0$ so, at line 10 it has $G^{(J)} < \epsilon$ in Algorithm \ref{alg:linear-rgmapg}. 
             This is one of the ways the algorithm can terminate hence, it suffices for deriving an upper bound. 
@@
             This gives us 
-            \begin{align*}
+            \begin{align}
+                \begin{split}
                     G^{(J)} &\le \epsilon = \sqrt{2}(F(z_0) - F^+)^{1/2}\exp(-k + 1)
@@
                     \right). 
-            \end{align*}
-            The above inequality shows a linear convergence rate of the quantity $G_0^{(J)}$ with respect to the total number of iterations required for GMAPG. 
+                \end{split}
+                \label{ineq:rgmapg-cnvg-complexity-proof-p1}
+            \end{align}
+            The above inequality shows a linear convergence rate of the quantity $G_0^{(J)}$ with respect to the total number of iterations required for \XXAPG{}. 
             Denote $z_J^+ = \Pi_{X^+}z_J$ then it has 
             {\allowdisplaybreaks
-            \begin{align*}
+            \begin{align}
+                \begin{split}
                     G^{(J)} 
@@
                     \\
-                &\underset{\text{(d)}}{\ge} \frac{1}{2\sqrt{L}}\left(
-                    \frac{\mu}{2L}
+                    &\underset{\text{(d)}}{\ge} \frac{\mu}{2\sqrt{L}}\left(
+                        \frac{\sqrt{2} - 1}{\sqrt{2}}
                     \right)\left\Vert
@@
                     \right\Vert 
-                = \frac{\kappa}{4\sqrt{L}} \left\Vert
+                    = 
+                    \kappa\left(
+                        \frac{\sqrt{L}\left(2 - \sqrt{2}\right)}{4}
+                    \right)
+                    \left\Vert
                         z_J - z_J^+
                     \right\Vert. 
-            \end{align*}
+                \end{split}
+                \label{ineq:rgmapg-cnvg-complexity-proof-p2}
+            \end{align}
             }
             \begin{enumerate}
-                \item [(a)] For the first equality, we assumed that $G^{(J)} < \epsilon$ in the outer loop and, it's returned by Algorithm \ref{alg:gmapg} at line 5.
+                \item [(a)] For the first equality, we assumed that $G^{(J)} < \epsilon$ in the outer loop and, it's returned by Algorithm \ref{alg:xxapg} at line 5.
 Therefore, it has $G_0 = G^{(J)} = \sqrt{L^{(J)}_0} \Vert z^{(J)} - x_0^{(J)}\Vert$ because it calls Algorithm \ref{alg:armijo-ls} (Armijo line search) with $\alpha_0 = 0$.
@@
                 \item [(c)] Using Theorem \ref{thm:qfg-peb-equiv} from previous chapter and take note that Assumption \ref{ass:q-growth-ch2} is Definition \ref{def:necoara-weaker-scnvx}\ref{def:necoara-qfg}.
-                \item [(d)] The function $1/\sqrt{1 - x/L}$ is convex hence a Taylor expansion has $1/\sqrt{1 - x/L} \le 1 - x/(2L) $, substituting it with $x = \mu$ makes for a lower bound. 
+                \item [(d)] The function $x \mapsto 1 - (1 + x/L)^{-1/2}$ is concave hence for all $x \in [0, L]$ it has: 
+                \begin{align*}
+                    1 - (1 + \mu/L)^{-1/2} &= \left[x \mapsto 1 - (1 + x/L)^{-1/2}\right](0(1 - \mu) + \mu)
+                    \\
+                    &\ge 0(1 - \mu) + \mu(1 - 2^{-1/2}) 
+                    \\
+                    &= \mu\left(
+                        1 - \frac{1}{\sqrt{2}}
+                    \right) = \frac{\mu(\sqrt{2} - 1)}{\sqrt{2}}. 
+                \end{align*}
             \end{enumerate}
-            It then yields the convergence rate of 
+            Using results of \eqref{ineq:rgmapg-cnvg-complexity-proof-p1}, \eqref{ineq:rgmapg-cnvg-complexity-proof-p2} it has
             \begin{align*}
                 \left\Vert z_J - z^+_J\right\Vert 
-                &\le \frac{4eL\sqrt{2}(F(z_0) - F^+)^{1/2}}{\kappa}
+                &\le 
+                \frac{4e\sqrt{2}(F(z_0) - F^+)^{1/2}}{\kappa\sqrt{L}(2 - \sqrt{2})} 
                 \exp\left(
-                    - \frac{K\sqrt{\kappa}}{16\sqrt{2 + 2e}}
-                \right) 
-                \le 
-                \mathcal O\left(
-                    \kappa^{-1}\exp\left(-\sqrt{\kappa}K\right)
+                    -\frac{K\sqrt{\kappa}}{16\sqrt{2 + 2e}}
                 \right). 
             \end{align*}
-            To achieve accuracy $\Vert z_J - z^+_J\Vert \le \delta$, it would require $\mathcal O\left(\frac{1}{\sqrt{\kappa}}\ln\left(\frac{1}{\kappa\delta}\right)\right)$ many total iterations of GMAGP.
+            $\Vert z_J - z^+_J\Vert \le \delta$ is achieved by substituting $K$: 
+            \begin{align*}
+                K = \left(
+                    \frac{16\sqrt{2 + 2e}}{\sqrt{\kappa}}
+                \right)
+                \ln \left(
+                    \frac{4e\sqrt{2}(F(z_0) - F^+)^{1/2}}{\kappa \sqrt{L}(2 - \sqrt{2})\delta}
+                \right). 
+            \end{align*}
+            This is an upper bound for the number of required iterations. 
+            When constants are ignored, it's $K \le \mathcal O\left(\frac{1}{\sqrt{\kappa}}\ln\left(\frac{1}{\kappa\delta}\right)\right)$. 
         \end{proof}

### 2025-06-11 Notebook LaTEX/R-WAPG/presentation.tex
>w<, changes

@@
 % SLIDE INFORMATION ============================================================
-\author{Hongda Li, Wang Xianfu}
+\author[Hongda Li]{Hongda Li\\ \vspace{1cm} \tiny{Joint work with Xianfu Wang}}
 \title[Thesis Proposal Talk]{
@@
             \end{block}
-            If $F$ is convex and has $L$ Lipschitz smooth gradient and minimizer $x^+$ exists. 
+            If $F$ is convex and has $L$ Lipschitz smooth gradient and a minimizer $x^+$ exists. 
             Then it has
             \begin{itemize}
-                \item a convergence rate of $\mathcal O(1/k^2)$ of $(F(x_k) - F(x^+))_{k \ge 1}$;
+                \item a convergence rate of $\mathcal O(1/k^2)$ for $(F(x_k) - F(x^+))_{k \ge 1}$;
                 \item this convergence rate is optimal in the sense as proposed by Nesterov \cite{nesterov_lectures_2018}.
@@
             \end{tcolorbox}
-            Disregarding the definition of $(t_k)_{k \ge 0}$ for now. 
             Then the algorithm has
@@
             \begin{enumerate}
-                \item We relaxed the traditional choices of the sequence $(\theta_k)_{k \ge 1}$ in the weakest possible way to show that an upper bound for the sequence $(F(x_k) - F^+)_{k \ge 1}$ exists.
+                \item We relaxed the traditional choices of the sequence $(\theta_k)_{k \ge 1}$ to full extend to show that an upper bound for the sequence $(F(x_k) - F^+)_{k \ge 1}$ exists. 
                 \item We proposed a unified framework which we call ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)" that unifies the convergence theories for functions that are strongly convex or not necessarily strongly convex.
-                \item We demonstrate that the R-WAPG framework can be represented is equivalent to various representations of the Nesterov's type accelerated proximal gradient methods with Euclidean geometry in the literature.
+                \item We demonstrate that the R-WAPG framework is equivalent to various representations of the Nesterov's type accelerated proximal gradient methods with Euclidean geometry in the literature.
             \end{enumerate}
@@
             \end{tcolorbox}
-            We can show Nesterov's type accelerated proximal gradient algorithm (similar to what's show in prior but with $g \equiv 0$) which generates $(F(x_k) - F^+)_{k\ge 1}$ has an upper bound of:
+            We can show Nesterov's type accelerated proximal gradient algorithm (or equivalently, FISTA with $g \equiv 0$) generates $(F(x_k) - F^+)_{k\ge 1}$ has an upper bound of: 
             \begin{tcolorbox}\noindent\vspace{-1em} 
@@
                 \end{align*}
-                We all the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ the R-WAPG sequences. 
+                We call the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ the R-WAPG sequences. 
             \end{definition}
@@
             \centering
-            \includegraphics[width=17em]{assets/paper-qrcode.png}
+            \includegraphics[width=15em]{assets/paper-qrcode.png}
         \end{figure}
+        Questions?
     \end{frame}

### 2025-06-12 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes to notes

@@
     \par
+    \textbf{Our contributions}. We aggregate stated of the art enhancement techniques for accelerated proximal gradient method in the literatures under a unified perspective. 
+    We propose the application of conic linear feasibility problem for our algorithm and show that the convergence rate is still optimal. 
+    We conduct numerical experiment to demonstrate the relevancy of Hoffman Error bound in the practical settings for our algorithm, which is crucial for all first order methods for linear program. 
+    Using the theories of Hoffman error bound, we also demonstrate that our approach of using accelerated proximal gradient method for linear programming also yields linear convergence rate of the distance of iterates to the solution set of the best approximation problem on the linear programming KKT conditions.
+    \par
     There are several notable enhancements of the FISTA for function that are not necessarily strongly convex. 
@@
                     \STATE{$\alpha^+ := (1/2)\left(\alpha\sqrt{\alpha^2 + 1} - \alpha^2\right)$.}
-                    \STATE{$y^+ := \alpha^+ v + (1 - \alpha^+)x$.}
+                    \STATE{$y^+ := \alpha^+ v + (1 - \alpha^+)x$.}\label{alg:armijo-ls-yplus}
                     \STATE{$L^+ := L$. }
@@
                         \STATE{$L^+ := 2L^+$. }
-                        \STATE{$x^+ := T_{1/L^+, f, g}(y^+)$. }
+                        \STATE{$x^+ := T_{1/L^+, f, g}(y^+)$. }\label{alg:armijo-ls-xplus}
                         \IF{$D_f(x^+, y^+) \le (L^+/2)\Vert x^+ - y^+\Vert^2$}
@@
                     \STATE{$\alpha_0 := 1$.}
-                    \STATE{$x_0, y_0,\alpha_1, L_0 := \textbf{ArmijoLS}(f, g, x_{-1}, x_{-1}, L, \alpha_0)$.}
-                    \STATE{$\eta_0 := L_0; v_0 := x_0; G_0 = \Vert \sqrt{L_0}(x_0 - y_0)\Vert.$}
+                    \STATE{$x_0, y_0,\alpha_1, L_0 := \textbf{ArmijoLS}(f, g, x_{-1}, x_{-1}, L, \alpha_0)$.}\label{alg:xxapg-armijo}
+                    \STATE{$\eta_0 := L_0; v_0 := x_0; G_0 = \Vert \sqrt{L_0}(x_0 - y_0)\Vert.$}\label{alg:xxapg-gzero}
                     \IF{$G_0 \le \epsilon$}
@@
                     \ENDIF
+                    \STATE{$\overline L := L_0$}. 
                     \FOR{$k := 1, 2,\ldots, N$}
                         \STATE{\noindent
-                            $\tilde x_{k}, y_k, \alpha_{k + 1}, L_{k} := \mathbf{L}(f, g, v_{k - 1}, x_{k - 1}, L_{k - 1}, \alpha_{k}, rL_{k - 1}, \rho)$.
-                        }
-                        \STATE{$\overline L := \max(L_k, L_{k - 1})$. }
+                            $\tilde x_{k}, y_k, \alpha_{k + 1}, L_{k} := \mathbf{L}(f, g, v_{k - 1}, x_{k - 1}, L_{k - 1}, \alpha_{k}, r\overline L, \rho)$.
+                        }
+                        \STATE{$v_k := x_{k - 1} + \alpha_k^{-1}(\tilde x_k - x_{k - 1})$.}
+                        \STATE{$\overline L := \max(L_k, L_{k - 1})$.}\label{alg:xxapg-lbar}
                         \STATE{\noindent
                             $\rho := \rho^{1/2} \textbf{ if } L_{k} > L_{k - 1} \textbf{ else } \rho$.
-                        }
+                        }\label{alg:xxapg-rhosqrt}
                         \STATE{$G_k:= \Vert \sqrt L_k(\tilde x_k - y_k)\Vert $}
@@
                         }
-                        \IF{$G_k^+ < \epsilon \textbf{ or } (\mathbf E_\chi  \textbf{ and } k > N_{\min})$}
+                        \IF{$G_k^+ < \epsilon \textbf{ or } (\mathbf E_\chi  \textbf{ and } k \ge N_{\min})$}
                             \STATE{\textbf{break}}\label{alg:xxapg-exit2}
@@
                     \STATE{\textbf{Return: }$x_k, k, \overline L, G_k^+ $}
-                \caption{\XXAPG{} with Chambolle's backtracking}\label{alg:xxapg}
+                \caption{\XXAPG{} main alorithm}\label{alg:xxapg}
                 \end{algorithmic}
             \end{algorithm}
-            The above Algorithm \ref{alg:xxapg} is an implementation of \XXAPG{} in Definition \ref{alg:xxapg}. 
+            The above Algorithm \ref{alg:xxapg} is an implementation of \XXAPG{} in Definition \ref{def:xxapg}. 
             The first iterates $x_0$ is produced by a step of proximal gradient descent through Algorithm \ref{alg:armijo-ls} so, it has $x_0 = v_0 = T_{1/L_0}(x_{-1})$, and consequently all results from Theorem \ref{thm:xxapg-specialized-cnvg} apply.
+            \par
+            There are several tricks involved with it and it deserves explaination. 
+            At line \ref{alg:xxapg-lbar} it keeps the largest Lipschitz estimate from the line search routines under the variable $\overline L$ and, the algorithm returns it after exiting the for loop, and it's used as an input for routine $\mathbf L$ to determine the lower bound of the Lipschitz estimated which is exclusived by Chambolle's backtracking (Algorithm \ref{alg:chambolle-btls}).
+            Whenever it detects that $L_k > L_{k - 1}$, i.e: the estimated Lipschitz constant had increased, it takes the square root of the decay ratio, making it closer to one. 
+            This decay ratio parameter is exclusively utilised by Chambolle's backtracking routine (Algorithm \ref{alg:chambolle-btls}). 
+            This trick prevents triggering backtracking routine frequently if $\rho$ is a small number. 
+            \par
             Parameters $r, \rho$ are chosen in the discretion of the practitioners. 
             For example, we chose $r= 0.4, \rho = 2^{1/1024}$. 
-            \begin{observation}[\XXAPG{} exit conditions]
-                Algorithm \ref{alg:xxapg} exits and returns its results on line \ref{alg:xxapg-exit1}, or at line \ref{alg:xxapg-exit2}. 
+            \begin{observation}[\XXAPG{} exit conditions]\label{obs:xxapg-exit-cond}
+                Algorithm \ref{alg:xxapg} exits and returns its results at line \ref{alg:xxapg-exit1}, or at line \ref{alg:xxapg-exit2}. 
                 If exited, then at least one of the conditions are true.
+                \begin{enumerate}
+                    \item $\Vert \sqrt{L_0}(x_0 - x_{-1})\Vert \le \epsilon$, and the line search on $x_{-1}$ is successful so $D_f(x_{0}, x_{-1}) \le L_0/2\Vert x_0 - x_{-1}\Vert^2$.
+It has $y_0 = x_{-1}$ because it passes $\alpha_0 = 1$ at line \ref{alg:xxapg-armijo}.
+                    \item $G_k^+ \le \epsilon$ or, $\mathbf E_\chi$ is true and $k > N_{\min}$. 
+                \end{enumerate}
             \end{observation}
@@
         Let's introduce our first set of restart conditions which denote it by $\mathbf E_{\chi}^{a}$. 
-        $\mathbf E_{\chi}^{a}$ only uses function values on iterates available to the inner loop to determine the exit conditions, and it achieves global fast linear convergence. 
-        The inner loop algorithm is described in Algorithm \ref{alg:xxapg}, let $k$ denote the inner loop counter and define $m = \lfloor k/2 \rfloor + 1$ the conditions are: 
-        \begin{align}\label{ineq:rgmapg-exit-cond}
+        $\mathbf E_{\chi}^{a}$ uses function values in the inner loop (Algorithm \ref{alg:xxapg}). 
+        Let $k$ denote the inner loop counter and define $m = \lfloor k/2 \rfloor + 1$, $\mathbf E_{\chi}^a$ is defined as: 
+        \begin{align}\label{ineq:rxxapg-exit-cond}
             \mathbf E_{\chi}^a \iff 
@@
                 \ENDIF
-                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1}, G^{(j)} := \textbf{\XXAPG{}}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}
+                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1}, G^{(j)} := \textbf{\XXAPG{}}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}\label{alg:rxxapg-iloop-done}
                 \STATE{$M := M - p_j$.}
                 \STATE{$\overline L_{j + 1} = \max(\overline L_{j}, \overline L_{j + 1})$.}
-                \IF{$f(z_{j}) - f(z_{j + 1}) > \exp(-1)(f(z_{j - 1}) - f(z_{j}))$}
+                \IF{$f(z_{j}) - f(z_{j + 1}) > \exp(-1)(f(z_{j - 1}) - f(z_{j}))$}\label{alg:rxxapg-restart-if}
                     \STATE{$n_{j + 1} := 2p_j$.}
@@
             \ENDFOR
-            \end{algorithmic}\caption{Linear convergence restarted \XXAPG{}}\label{alg:linear-rgmapg}
+            \end{algorithmic}\caption{Linear convergence restarted \XXAPG{}}\label{alg:rxxapg}
         \end{algorithm}
         \par
-        Algorithm \ref{alg:linear-rgmapg} implements a restarted \XXAPG{} with condition $\textbf{E}_{\chi}^a$ and, it has a fast linear convergence rate. 
-        The following observation on it is crucial to take notice for the convergence rate. 
-        \begin{observation}\label{obs:rgmapg}
-            If the outer loop runs for $j = 1, 2, \ldots, J$ iterations with $M \ge J$ so the algorithm terminated due $G^{(J - 1)} \le \epsilon$. 
+        Algorithm \ref{alg:rxxapg} implements a restarted \XXAPG{} with condition $\textbf{E}_{\chi}^a$ stated in \eqref{ineq:rxxapg-exit-cond} and, it has a fast linear convergence rate. 
+        The following observation about it is crucial for deriving its convergence rate. 
+        \begin{observation}\label{obs:rxxapg}
+            If the outer loop runs for $j = 1, 2, \ldots, J$ iterations with $M \ge J$, so Algorithm \ref{alg:rxxapg} terminated due to $G^{(J - 1)} \le \epsilon$. 
             Then, it has 
@@
                 \item for all $J\ge j\ge 1$ it has $n_{j}\le n_{j + 1}$ hence $(n_j)_{j \ge 0}^J$ is monotone increasing; 
-                \item for all $J -1 \ge j \ge 1 $ it has $p_{j-1}\le p_{j}$ so $(p_j)_{j \ge 1}^{J}$ is monotone excluding the last iterates $p_J$. 
+                \item for all $J -1 \ge j \ge 1 $ it has $p_{j-1}\le p_{j}$ so $(p_j)_{j \ge 1}^{J}$ is monotone excluding $p_J$ obtained by the last iteration. 
             \end{enumerate}
@@
         \par
-        For all $1 \le j \le J$, $n_j$ is used as the lower bound $N_{\min}$ for the \XXAPG{} inner loop described in Algorithm \ref{alg:xxapg} at iteration $j$ and, $p_j$ is the actual iteration underwent by the inner loop therefore it has $p_j \ge n_{j}$.
-        $n_{j + 1}$ is the minimum iteration for the next execution of GMAGP, and it has $n_{j + 1} = p_{j}$  if the ``if statement" isn't triggered otherwise $n_{j + 1} = 2p_{j}$. 
-        For $j < J$ so it excludes the last iteration, it has either $p_{j + 1} \ge n_{j + 1} = 2p_j \ge 2n_{j} \ge n_j$ or $p_{j + 1} \ge n_{j + 1} = p_j \ge n_j$. 
-        When $j = J$ it's not necessarily true that $p_J \ge n_J$ because on the last iteration, it can exit the for loop through conditions $G_k^+ \le \epsilon$ in line 14 of Algorithm \ref{alg:xxapg}, but $n_J \ge p_{J - 1} \ge n_{J - 1}$ still.
-        \par
-        We now introduce the following notations for the convergence proof. 
-        Since the restarted \XXAPG{} consist of executions of an outer loop in Algorithm \ref{alg:linear-rgmapg} in variable $j$ and, an inner loop in Algorithm \ref{alg:xxapg} in variable $k$, we denote $x_{k}^{(j)}$ for the iterates $x_k$ in the inner loop during the $j$ iteration of the outer loop together.
-        We make the choice to have $x_{-1}^{(j + 1)} = z_{j + 1} = x_{p_j}^{(j)}$ for consistencies across theorems from previous sections. 
-        For example in line 10 of Algorithm \ref{alg:linear-rgmapg} at the $j$ iteration, the inner loop returns $x_{p_j}$ as the last iterate. 
+        Explanations for the observations now follow. 
+        For all $1 \le j < J$, $n_j$ is passed in as the lower bound $N_{\min}$ for \XXAPG{} inner loop (Algorithm \ref{alg:xxapg}), $p_j$ is the actual number of iteration by the inner loop therefore, it has $p_j \ge n_{j}$ because of Observation \ref{obs:xxapg-exit-cond}.
+        $n_{j + 1}$ is the minimum iteration required for the next execution of \XXAPG{} inner loop, and it has $n_{j + 1} = p_{j}$ if at line \ref{alg:rxxapg-restart-if} is true otherwise, $n_{j + 1} = 2p_{j}$.
+        As a consequence, for $j < J$, it has either $p_{j + 1} \ge n_{j + 1} = 2p_j \ge 2n_{j} \ge n_j$ or $p_{j + 1} \ge n_{j + 1} = p_j \ge n_j$. 
+        Both $(n_j)_{j\ge0}, (p_j)_{j\ge 0}$ are nondecreasing sequences. 
+        \par
+        When $j = J$ it's not necessarily true that $p_J \ge n_J$ because on the last iteration, inner loop can exit through condition $G_k^+ \le \epsilon$ at line \ref{alg:xxapg-exit2} of Algorithm \ref{alg:xxapg}, but $n_J \ge p_{J - 1} \ge n_{J - 1}$ still.
+        \par
+        \textbf{Notations now follow.}
+        Since the Algorithm \ref{alg:rxxapg} has a loop in variable $j$ and, an inner loop implemented by Algorithm \ref{alg:xxapg} in variable $k$, we denote $x_{k}^{(j)}$ for the iterates $x_k$ in the inner loop during the $j$ iteration of the outer loop together.
+        We make the convention $x_{-1}^{(j + 1)} = z_{j + 1} = x_{p_j}^{(j)}$ for consistencies across the theorems from previous sections. 
+        \par
+        For example at line \ref{alg:rxxapg-iloop-done} of Algorithm \ref{alg:rxxapg} at the $j$ iteration, the inner loop returns $x_{p_j}$ as the last iterate. 
         So $x_{p_j}$ is assigned to $z_{j + 1}$ by the outer loop, and it has $x_{p_j} = x_{p_j}^{(j)} = z_{j + 1}$. 
@@
         Let $e$ denotes the base of natural log. 
-        The following lemma combines quadratic growth assumption of the objective to assert lower bound on the number of iteration required to achieve a certain optimality on the objective function $F$.
+        The following lemma will assert a lower bound on the number of iteration required to achieve a certain optimality on the objective function $F$ using the quadratic growth assumption. 
         \begin{lemma}[maximum iteration needed for an optimality gap ratio]\;\label{lemma:prog-ratio}\\
@@
             The second inequality comes from Assumption \ref{ass:q-growth-ch2} directly. 
-            Suppose that $k \ge 2\sqrt{1 + e}\left(\mu\widehat L_k^{-1}\right)^{-1/2}$. 
+            Suppose that ${k \ge 2\sqrt{1 + e}\left(\mu\widehat L_k^{-1}\right)^{-1/2}}$. 
             Denote $\gamma_k = 4\widehat L_k \mu^{-1}(2 + k)^{-2}$.
@@
                 \\
-                &= 4\widehat L_k(\mu(2 + k)^2 - 4 \widehat L_k)(F(x_{-1}) - F^+)
+                &= 4\widehat L_k(\mu(2 + k)^2 - 4 \widehat L_k)^{-1}(F(x_{-1}) - F^+)
                 \\
@@
                 \\
-                &\le 4\widehat L_k\left(
+                &= 4\widehat L_k\left(
                     \mu\left(
@@
         \end{proof}
+        \par
         The following proposition places an upper bound on the estimated Lipschitz constant from the line search routine specified in Algorithm \ref{alg:armijo-ls}, \ref{alg:chambolle-btls}. 
@@
             Choose such $F$ for Algorithm \ref{alg:xxapg} so, it generates the sequence $(L_k)_{k\ge 0}$. 
-            Then, the sequence $(\hat L_k)_{k \ge 1}$ from Theorem \ref{thm:xxapg-specialized-cnvg} is bounded above and, it has
+            Then, the sequence $(\widehat L_k)_{k \ge 1}$ from Theorem \ref{thm:xxapg-specialized-cnvg} is bounded above and, it has
             \begin{align*}
@@
         \begin{proof}
-            A line search is triggered in Algorithm \ref{alg:armijo-ls}, \ref{alg:chambolle-btls} if and only if $L_{k + 1} = 2L_{k}$ for some $k \ge 0$ and, there exists some $x\in \RR^n, y \in \RR^n$ such that $D_f(x, y) > L_k\Vert x - y \Vert^2$.
-            For all $k = 0, 1, \ldots $, if $L_k \ge L$ then, it has $D_f(x, y) \le L_k/2\Vert x - y\Vert^2$ for all $x, y \in \RR^n$. 
-            Hence, $L_{k + 1} \le L_k$ because a line sarch is never triggered. 
-            \par
-            For contradiction let's assume that there exists $k \ge 1$ such that a line search is triggered for $L_k$ and, $L_{k + 1} = 2L_{k} > 2L$, then $L_k > L$, but we just showed that this implies $L_{k + 1} \le L_k$, which is a contradiction.
+            The following two facts are clear. 
+            \begin{enumerate}
+                \item A line search is triggered in Algorithm \ref{alg:armijo-ls}, \ref{alg:chambolle-btls} if and only if $L_{k + 1} = 2L_{k}$ for some $k \ge 0$ and, it implies that there exists some $x\in \RR^n, y \in \RR^n$ such that $D_f(x, y) > L_k/2\Vert x - y \Vert^2$.
+                \item For all $k = 0, 1, \ldots $, if $L_k \ge L$, then it has $D_f(x, y) \le L_k/2\Vert x - y\Vert^2$ for all $x, y \in \RR^n$ which implies $L_{k + 1} \le L_k$ because the line search wasn't triggered.
+            \end{enumerate}
+            \par
+            For contradiction let's assume that there exists $k \ge 1$ such that a line search is triggered for $L_k > L$.
+            From (i) it has $L_{k + 1} = 2L_{k} > 2L$ so $L_{k + 1} > L_k$, but (ii) showed that assumption $L_k > L$ implies $L_{k + 1} \le L_k$, which is a contradiction. 
             Therefore, if $L_{k + 1} = 2L_k$ then it must be that $L_k < L$ so, the highest value it can achieve is either $L_0$, or $2L$. 
@@
         \par
-        Continuing with the quadratic growth assumption, the following lemma states the fact that $p_j$ in Algorithm \ref{alg:linear-rgmapg} is bounded above and there exists a $j \ge 1$ such that $n_{j + 1 + k} = p_{j + k}$ for all $k \ge 0$ until it terminates.
-        \begin{lemma}[inner iteration is bounded above]\label{lemma:rgmapg-inner-bnds}
+        Continuing with the quadratic growth assumption, the following lemma states the result that $p_j$ in Algorithm \ref{alg:rxxapg} is bounded above and there exists a $j \ge 1$ such that $n_{j + 1 + k} = p_{j + k}$ for all $k \ge 0$ until it terminates.
+        \begin{lemma}[inner iteration is bounded above]\label{lemma:rxxapg-inner-bnds}
             Suppose that $F = f + g$ satisfies Assumption \ref{ass:q-growth-ch2}, denote $F^+ := \inf_xF(x)$ and, $X^+$ as the set of minimizers. 
             Consider any $j \ge 1$ iteration experienced by the outer loop. 
-            Let $\left(x_{k}^{(j)}\right)_{k\ge 0}^{p_{j}}$ be the sequence generated by Algorithm \ref{alg:linear-rgmapg} in the $j$ th iteration of outer loop. 
             Define $\bar p := \frac{4\sqrt{2L(1 + e)}}{\sqrt{\mu}}$, then $p_{j} \le \bar p, n_j \le \bar p$. 
@@
             \textbf{Proof of (i)}. 
-            Recall exit condition in \eqref{ineq:rgmapg-exit-cond} has $m = \lfloor k/2\rfloor + 1$. 
+            Recall exit condition in \eqref{ineq:rxxapg-exit-cond} has $m = \lfloor k/2\rfloor + 1$. 
             Starting with the statement hypothesis it has $k \ge \bar p$ therefore: 
@@
             \end{align*}
-            Observe that line 14 of Algorithm \ref{alg:xxapg} exits as soon as possible if $\mathbf E_\chi^a$ is true and $k > N_{\min} = n_j$ and, $G_k \le \epsilon$ will only cause it to exit earlier therefore it has $p_j \le \max(\bar p, n_j)$.
+            At line \ref{alg:xxapg-exit2} of Algorithm \ref{alg:xxapg}, Since $\mathbf E_\chi^a$ is true, it will exit if $k \ge N_{\min} = n_j$ and, $G_k \le \epsilon$ will only cause it to exit earlier therefore it has $p_j \le \max(\bar p, n_j)$.
             \par
@@
             Inductively assume that $p_{j - 1} \le p_j \le \bar p$. 
-            If $p_{j - 1} \le \bar p /2$ then Line 14, 16 in Algorithm \ref{alg:linear-rgmapg} implies that $n_{j} \le \max(p_{j - 1}, 2p_{j - 1}) \le \bar p$. 
+            If $p_{j - 1} \le \bar p /2$ then the if, else statement at line \ref{alg:rxxapg-restart-if} in Algorithm \ref{alg:rxxapg} implies that $n_{j} \le \max(p_{j - 1}, 2p_{j - 1}) \le \bar p$. 
             Otherwise, $p_{j - 1} > \bar p/2$, and using Proposition \ref{prop:bnded-lip-ls} it means 
@@
                 \frac{F(z_j) - F(z_{j + 1})}
-                {F(z_{j - 1}) - F(z_{j})} \implies n_{j + 1} = p_{j + 1}.
-            \end{align*}
-            Therefore, there is no doubling at line 14 of Algorithm \ref{alg:linear-rgmapg}, hence $n_{j + 1} \le \bar p$ still. 
+                {F(z_{j - 1}) - F(z_{j})} \implies n_{j + 1} = p_{j}.
+            \end{align*}
+            This is true because, condition at line \ref{alg:rxxapg-restart-if} in Algorithm \ref{alg:rxxapg} is never satisfied hence $n_{j + 1} = p_j \le \bar p$. 
         \end{proof}
         \par
-        We just show that the sequence $n_j$ is bounded above, and it must have a limit because it's also monotone increasing, which implies that at some point, the doubling of $n_{j + 1} = 2p_j$ must stop for the outer loop.
-        The following lemma shows that when that happens, the algorithm will always terminate after a finite number of iterations of the outer loop. 
-        \begin{lemma}[bounds on outer iteration counts]\label{lemma:rgmapg-outer-itr-bnd}
+        We just show that the sequence $n_j$ is bounded above, and it must have a limit because it's also non-decreasing from Observation \ref{obs:rxxapg}, which implies that at some point, the doubling of $n_{j + 1} = 2p_j$ must stop for the outer loop.
+        The following lemma shows that when it happened, the restarted \XXAPG{} (Algorithm \ref{alg:rxxapg}) will always terminate after a finite number of iterations of the outer loop. 
+        \begin{lemma}[bounds on outer iteration counts]\label{lemma:rxxapg-outer-itr-bnd}
             Let $F = f + g$ satisfies Assumption \ref{ass:standard-fista}. 
-            Suppose we apply Algorithm \ref{alg:linear-rgmapg} on $F = f + g$. 
-            Define $T_\epsilon = \lceil\ln(2\epsilon^{-2}(F(z_0) - F^+))\rceil$
-            Assume that after iteration $j$, no doubling occurred in the if statement, i.e: $n_{t + 1} = p_t$ for $t \ge j$, then it must terminate before, or at iteration $j + T_\epsilon$. 
+            Suppose we apply Algorithm \ref{alg:rxxapg} on $F = f + g$. 
+            For all $\epsilon > 0$ used to terminate the algorithm, define $T_\epsilon = \lceil\ln(2\epsilon^{-2}(F(z_0) - F^+))\rceil$. 
+            Assume that after iteration $j$, no doubling occurred in the if statement at line \ref{alg:rxxapg-restart-if}, i.e: $n_{t + 1} = p_t$ for $t \ge j$, then it must terminate before, or at iteration $j + T_\epsilon$.
         \end{lemma}
         \begin{proof}
-            Suppose that since the $j\ge 2$ th iteration, there is no period doubling for $T_\epsilon$ number of iterations in the outer loop of Algorithm \ref{alg:linear-rgmapg}, i.e: $n_{t + 1} = p_t$
-            for $j \le t \le j + T_\epsilon - 1$, and denote $s = j + T_\epsilon -1$ for better notations, giving us for all $j \le t \le s$, $n_{t + 1} = p_t$. 
-            \par
-            Our goal now is to show that at iteration $j = s$ of Algorithm \ref{alg:linear-rgmapg} it must have $G_0 \le \epsilon$ at line 5 of Algorithm \ref{alg:xxapg}. 
-            \par
-            Consider the start of the $s$ th iteration of the outer loop, denote $L_0^{(s)}, G_0^{(s)}$ as the $L_0$ in line 4 in Algorithm \ref{alg:xxapg}, it would give the following inequalities
+            Suppose that since the $j\ge 2$ th iteration, there is no period doubling for $T_\epsilon$ number of iterations in the outer loop of restarted \XXAPG{} by Algorithm \ref{alg:rxxapg}, i.e: $n_{t + 1} = p_t$ for $j \le t \le j + T_\epsilon - 1$.
+            Let's denote $s = j + T_\epsilon -1$ for better notations, so for $t$ such that $j \le t \le s$, it has $n_{t + 1} = p_t$. 
+            \par
+            Our goal now is to show that at iteration $j = s + 1$ of Algorithm \ref{alg:rxxapg} it must have $G^{(s)} \le \epsilon$ making an exit due to $G_0 \le \epsilon$ at line \ref{alg:xxapg-exit1} of Algorithm \ref{alg:xxapg}.
+            This is one of many ways the restarted \XXAPG{} can exit, if we only focus on this condition it gives an upper bound on $T_\epsilon$. 
+            \par
+            Consider the start of the $s$ th iteration of the outer loop by Algorithm \ref{alg:rxxapg-restart-if}.
+            Let's denote $L_0^{(s)}$ for the $L_0$ in the inner loop by Algorithm \ref{alg:xxapg} at line \ref{alg:armijo-ls}; denote $G_0^{(s)}$ for the $G_0$ in the inner loop by Algorithm \ref{alg:xxapg} at line \ref{alg:xxapg-gzero}.
+            Then, it would give the following chain of inequalities
             {\allowdisplaybreaks
@@
             \begin{enumerate}
-                \item [(a)] At the $s$ iteration of the loop in Algorithm \ref{alg:linear-rgmapg}, $z_s$ is passed into Algorithm \ref{alg:xxapg} with $x_{-1} = z_s$.
-Therefore, at line 3 in Algorithm \ref{alg:xxapg} it calls Algorithm \ref{alg:armijo-ls} with $x_{-1} = z_s, \alpha_0 = 1, L^+$ which means $y^+ = x_{-1} = z_s$ at line 5 and $x^+ = T_{1/L^+}(z_s)$.
-Coming back to line 3 in Algorithm \ref{alg:xxapg}, it assigns $y_0 = y^+ = z_s, x_0 = x^+ = T_{1/L^+}(z_s)$ and $L_0 = L^+$.
+                \item [(a)] At the $s$ iteration of the outer loop by Algorithm \ref{alg:rxxapg}, $z_s$ is passed into the inner loop by Algorithm \ref{alg:xxapg} with $x_{-1} = z_s$.
+Therefore, at line \ref{alg:xxapg-armijo} in Algorithm \ref{alg:xxapg} it calls Armijo line search by Algorithm \ref{alg:armijo-ls} with $x_{-1} = z_s, \alpha_0 = 1$ which means $y^+ = x_{-1} = z_s$ at line \ref{alg:armijo-ls-yplus} and, $x^+ = T_{1/L^+}(z_s)$ at line \ref{alg:armijo-ls-xplus}.
+Coming back to line \ref{alg:xxapg-armijo} in Algorithm \ref{alg:xxapg}, it assigns $y_0 = y^+ = z_s, x_0 = x^+ = T_{1/L^+}(z_s)$ and $L_0 = L^+$.
 Assuming the line search went successful, it will have $D_f(z_s, x_0) \le L^{(s)}_0/2 \Vert z_s - x_0\Vert^2$.
                 \item [(b)] We used definition of gradient mapping in Definition \ref{def:gm-for-ch2}. 
-                \item [(c)] By the assumption that the line search in Algorithm \ref{alg:armijo-ls} is successful at $z_s$ back in item (a), here we can use \eqref{eqn:emp:result-item-2} in Theorem \ref{thm:xxapg-gm-cnvg}.
-                \item [(d)] \XXAPG{} is monotone in function value for the use of $\mathbf M$ that is either Algorithm \ref{alg:beck-mono} or \ref{alg:nes-mono}, so it has $F\left(x_{p_s}^{(s)}\right) \le F\left(x_0^{(s)}\right)$.
-                \item [(e)] Here we used the assumption that no doubling occurs so $n_{t + 1} = p_t$ for all $j \le t \le s$ meaning that line 13 in Algorithm \ref{alg:linear-rgmapg} has $F(z_t) - F(z_{t + 1}) \ge e^{-1}(F(z_{t - 1}) - F(z_t))$.
-For that, we recursively unrolled it for $T_\epsilon$ many iterations starting with $t = s = j + T_\epsilon - 1$ ending with $t = j$.
+                \item [(c)] By the assumption that the line search in Algorithm \ref{alg:armijo-ls} is successful at $z_s$ back in item (a), here we can use \eqref{ineq:xxapg-gm-cnvg-prt2} in Theorem \ref{thm:xxapg-gm-cnvg}.
+                \item [(d)] \XXAPG{} implemented via Algorithm \ref{alg:xxapg} is monotone in function value for the use of $\mathbf M$ that is either Algorithm \ref{alg:beck-mono} or \ref{alg:nes-mono}, so it has $F\left(x_{p_s}^{(s)}\right) \le F\left(x_0^{(s)}\right)$.
+                \item [(e)] Here we used the assumption that no doubling occurs so $n_{t + 1} = p_t$ for all $j \le t \le s$ meaning that line \ref{alg:rxxapg-restart-if} in Algorithm \ref{alg:rxxapg} has $F(z_t) - F(z_{t + 1}) \ge e^{-1}(F(z_{t - 1}) - F(z_t))$.
+Therefore, we can recursively unroll it for $T_\epsilon$ many iterations starting with $t = s = j + T_\epsilon - 1$ ending with $t = j$.
                 \item [(f)] We used the monotone property of subroutine $\mathbf M$ in \XXAPG{} again so $F(z_0) \ge F(z_{j - 1})$. 
@@
         \end{proof}
-        \begin{theorem}[bounds on the total iterations]\label{thm:rgmapg-total-itr-bnds}
+        \begin{theorem}[bounds on the total iterations]\label{thm:rxxapg-total-itr-bnds}
             Let $F = f + g$ satisfies Assumption \ref{ass:q-growth-ch2}. 
-            Suppose that we applied Algorithm \ref{alg:linear-rgmapg} to it. 
+            Suppose that we applied Algorithm \ref{alg:rxxapg} to $F$. 
             For any $\epsilon > 0$, assuming that it terminated at $j = J < M$ iteration.
@@
         \begin{proof}
-            Firstly, Algorithm \ref{alg:linear-rgmapg} must terminate within finite many iterations under Assumption \ref{ass:q-growth-ch2} for all total budget $M \in \N$. 
-            This is because Observation \ref{obs:rgmapg} shows that $n_j$ is a non-decreasing sequence, Lemma \ref{lemma:rgmapg-inner-bnds} shows that $n_j \le \bar p$ under this quadratic growth assumption, therefore $n_j$ must converge which implies that doubling of $n_{j + 1} = 2p_{j}$ must stop.
-            Finally, since the doubling must stop at some $j$, Lemma \ref{lemma:rgmapg-outer-itr-bnd} applies hence, it terminates at most $j + T_\epsilon$ iteration. 
-            \par
-            Using it let's assume that it executed for $j = 1, 2, \cdots, J$ and $M$ is large enough to achieve optimality $G^+ \le \epsilon$ right at the start of iteration $J$.
+            Firstly, Algorithm \ref{alg:rxxapg} must terminate within finite many iterations under Assumption \ref{ass:q-growth-ch2} for all total budget $M \in \N$. 
+            This is because Observation \ref{obs:rxxapg} shows that $n_j$ is a non-decreasing sequence, Lemma \ref{lemma:rxxapg-inner-bnds} shows that $n_j \le \bar p$ under the quadratic growth assumption, therefore $n_j$ must converge which implies that doubling of $n_{j + 1} = 2p_{j}$ must stop.
+            Finally, since the doubling must stop at some $j$, Lemma \ref{lemma:rxxapg-outer-itr-bnd} applies hence, it terminates at most $j + T_\epsilon$ iteration. 
+            \par
+            Using it let's assume that it executed for $j = 1, 2, \cdots, J$ and $M$ is large enough to achieve optimality $G^{(J)} \le \epsilon$ right at the start of iteration $J + 1$.
             This is one of the way the algorithm can terminate, making it a sufficient condition for deriving the upper bound on the total number of iterations. 
-            Representing it by the maximum period between doubling: $J = m + nT_\epsilon$ with $0 \le m < T_\epsilon$. 
+            \par
+            Let's represent $J$ by: $J = m + nT_\epsilon$ with $0 \le m < T_\epsilon$. 
             The following intermediate results are important to the proof. 
@@
                 \item [(a)] $n_{J - lT_\epsilon} \le n_{J - lT_\epsilon}\le (1/2)^ln_J$ for all $l = 1, \ldots, n$.
-From Lemma \ref{lemma:rgmapg-outer-itr-bnd} we know that doubling must have occured within a period of $T_\epsilon$ iterations at least once.
-                \item [(b)] $n_{j} \le n_{j + 1}$ for all $0 \le j \le J - 1$. The sequence is monotone from Observation \ref{obs:rgmapg}. 
-                \item [(c)] $n_j \le \bar p$ with $\bar p = 4\sqrt{2L(1 + e)}/\sqrt{\mu}$, proved in Lemma \ref{lemma:rgmapg-inner-bnds}. 
+This is true because Lemma \ref{lemma:rxxapg-outer-itr-bnd} showed that doubling must have occurred within a period of $T_\epsilon$ at least once.
+                \item [(b)] $n_{j} \le n_{j + 1}$ for all $0 \le j \le J - 1$.
+The sequence is monotone non decreasing from Observation \ref{obs:rxxapg}.
+In addition, $0 \le m < T_\epsilon$ by assumption.
+                \item [(c)] $n_j \le \bar p$ with $\bar p = 4\sqrt{2L(1 + e)}/\sqrt{\mu}$, which is proved in Lemma \ref{lemma:rxxapg-inner-bnds}. 
             \end{enumerate}
@@
                 \\
-                &\hspace{-0.5em}
-                \underset{\substack{(b), \\ m \le T_\epsilon.}}\le T_\epsilon n_m + \sum_{l = 0}^{n - 1} T_\epsilon n_{m + (l + 1)T_\epsilon}
+                &\underset{\text{(b)}}{\le} T_\epsilon n_m + \sum_{l = 0}^{n - 1} T_\epsilon n_{m + (l + 1)T_\epsilon}
                 \\
@@
                 \\
-                &\le 2T_\epsilon n_J \le 2T_\epsilon \bar p.
+                &\le 2T_\epsilon n_J \underset{\text{(c)}}{\le} 2T_\epsilon \bar p.
             \end{align*}
@@
         We denote $\kappa := L/\mu$. 
-        \begin{theorem}[restarted \XXAPG{} convergence and complexity]\;\label{thm:rgmapg-cnvg-complexity}\\
-            Let $F = f + g$ satisfy Assumption \ref{ass:q-growth-ch2}, and apply it to Algorithm \ref{alg:linear-rgmapg}. 
+        \begin{theorem}[restarted \XXAPG{} convergence and complexity]\;\label{thm:rxxapg-cnvg-complexity}\\
+            Let $F = f + g$ satisfy Assumption \ref{ass:q-growth-ch2}, and apply it to Algorithm \ref{alg:rxxapg}. 
             Let $J$ be the total number of iteration performed to achieve accuracy in the outer loop. 
@@
         \begin{proof}
-            Suppose a total of $K := \sum_{i = 0}^{J - 1} p_i$ iteration were performed and, at line 10 of Algorithm \ref{alg:linear-rgmapg} at iteration $j = J$ it achieved $G_0 \le \epsilon$ at line 5 of Algorithm \ref{alg:xxapg}.
-            That will cause the inner \XXAPG{} to return $G_0$ so, at line 10 it has $G^{(J)} < \epsilon$ in Algorithm \ref{alg:linear-rgmapg}. 
+            Suppose a total of $K := \sum_{i = 0}^{J - 1} p_i$ iteration were performed and, at line 10 of Algorithm \ref{alg:rxxapg} at iteration $j = J$ it achieved $G_0 \le \epsilon$ at line 5 of Algorithm \ref{alg:xxapg}.
+            That will cause the inner \XXAPG{} to return $G_0$ so, at line 10 it has $G^{(J)} < \epsilon$ in Algorithm \ref{alg:rxxapg}. 
             This is one of the ways the algorithm can terminate hence, it suffices for deriving an upper bound. 
@@
             \end{align*}
-            Then it has from Theorem \ref{thm:rgmapg-total-itr-bnds} that:
+            Then it has from Theorem \ref{thm:rxxapg-total-itr-bnds} that:
             \begin{align*}
@@
                 \end{split}
-                \label{ineq:rgmapg-cnvg-complexity-proof-p1}
+                \label{ineq:rxxapg-cnvg-complexity-proof-p1}
             \end{align}
@@
                 \end{split}
-                \label{ineq:rgmapg-cnvg-complexity-proof-p2}
+                \label{ineq:rxxapg-cnvg-complexity-proof-p2}
             \end{align}
@@
             \end{enumerate}
-            Using results of \eqref{ineq:rgmapg-cnvg-complexity-proof-p1}, \eqref{ineq:rgmapg-cnvg-complexity-proof-p2} it has
+            Using results of \eqref{ineq:rxxapg-cnvg-complexity-proof-p1}, \eqref{ineq:rxxapg-cnvg-complexity-proof-p2} it has
             \begin{align*}
@@
         \end{proof}
+    \section{Hoffman Bounds and infeasibility detection}
+        The Hoffman error bound conditions is essential to analyzing optimization problem arises in applications with polytoptic constraints.
 
-    \section{Applying them to large scale LP}
-
-    \section{Hoffman Bounds and infeasibility detection}
+    \section{Numerical experiments}
 

### 2025-06-14 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
     In this section, $D_f$ will denote the Bregman Divergence as defined in Definition \ref{def:bregman-div}. 
+    % SYMBOL SET FOR THIS CHAPTER ONLY! 
+    \newcommand{\QSCNVX}{\ensuremath{q\mathcal{S}}}
+    \newcommand{\QUA}{\ensuremath{\mathcal U}}
+    \newcommand{\QGG}{\ensuremath{\mathcal G}}
+    \newcommand{\QFG}{\ensuremath{\mathcal F}}
+    \newcommand{\PEB}{\ensuremath{\mathcal E}}
+    \par
+    \todoinline{\noindent
+        Defined special symbols/substitutes in this chapter: 
+        Q-SCNVX $\QSCNVX$; QUA $\QUA$; QGG $\QGG$; QFG $\QFG$; PEB $\PEB$. 
+    }
     \section{Necoara's et al.'s Paper}
@@
 
+        \subsection{Characterizing Q-SCNVX functions with Hoffman's Error bound}
+            Necoara et al. \cite{necoara_linear_2019}
+
         \subsection{Feasible descent and accelerated feasible descent}
@@
         We first introduce the linear feasibility problem as our primary problem. 
-        \begin{definition}[a conic feasibility problem]
-            Let $A\in \RR^{m\times n}$, $b \in \RR^m$
-            Let $\mathcal K$ be a simple cone. 
+        \begin{definition}[a linear conic feasibility problem]\label{def:lcf-problem}
+            Let $A\in \RR^{m\times n}$, $b \in \RR^{m\times p}$
+            Let $\mathcal K \in \RR^{n \times p}$ nonempty, closed convex cone. 
             The conic feasibility problem is defined as the following optimization problem: 
             \begin{align*}
-                \min_{x \in \mathcal K} \Vert Ax - b\Vert^2.
+                \min_{X \in \mathcal K} \Vert AX - B\Vert^2_F.
             \end{align*}
         \end{definition}
-        The KKT of a linear programming problem is an instance of a linear feasibility problem, with $\mathcal K$ being a cross product of one of $\RR, \RR_+, \RR_-$. 
-        A feasibility semidefinite program with linear constraint can is another example. 
-        \par
+        The KKT of a linear programming problem is an instance of a linear feasibility problem, with $\mathcal K$ being a cross product of one of $\RR, \RR_+, \RR_-$ and $p = 1$ making $x \in \RR^{n}$.
+        A feasibility semidefinite program with linear constraint is another example. 
+        \subsection{Example, linear programming is a linear conic feasibility problem}
             Let $X_1, X_2, Y$ be Euclidean spaces. 
@@
     \section{Hoffman error bound of linear feasibility problem}
+
     \section{Quadratic growth of linear feasibility problem}
@@
         \end{proof}
-    \section{Hoffman Bounds and infeasibility detection}
+        \begin{remark}
+            The convergence rate can be simplified a bit. 
+            On a calculator it has $4e\sqrt{2}/(2 - \sqrt{2}) \le 27$ and, $1/(16\sqrt{2 + 2e}) \ge 0.02$ so 
+            \begin{align*}
+                \Vert z_J - z_J^+\Vert &\le \frac{27(F(z_0) - F^+)^{1/2}}{\kappa}\exp\left(
+                    - \frac{K\sqrt{\kappa}}{20}
+                \right). 
+            \end{align*}
+        \end{remark}
+
+    \section{Hoffman error bound and quadratic growth}
         The Hoffman error bound conditions is essential to analyzing optimization problem arises in applications with polytoptic constraints.

### 2025-06-17 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes all

@@
     \end{proof}
+    \section{Convexity results}
         \begin{theorem}[convex proximal gradient inequality]\label{thm:cnvx-pg-ineq}
@@
         \end{proof}
+        \begin{definition}[strong convexity]\label{def:scnvx}
+            Let $\alpha \ge 0$. 
+            $f: \RR^n \rightarrow \RR^n$ is $\alpha$ strongly convex if and only if $f - \alpha/2\Vert \cdot\Vert^2$ is a convex function. 
+        \end{definition}
+        \begin{remark}
+            The definition doesn't exclude convex functions. 
+        \end{remark}
+        \begin{theorem}[strong convexity equivalences]\label{thm:scnvx-eqvs}
+            Let $f:\RR^n \rightarrow \RR$ be $\alpha \ge 0$ strongly convex then, it is equivalent to 
+            \begin{align*}
+                (\forall \lambda \in [0, 1])\; 
+                f(\lambda x + (1 - \lambda)y) \le \lambda f(x) + (1 - \lambda)f(y) -\alpha\frac{\lambda(1 - \lambda)}{2} \Vert y - x\Vert^2.
+            \end{align*}
+        \end{theorem}
 
@@
             % ==================================================================
-            % STRONG CONVEXITY DEFINITION
+            % STRONG CONVEXITY
             % ==================================================================
-            \begin{definition}[strong convexity]\label{def:necoara-scnvx}
+            \begin{theorem}[strong convexity characterized via Bregman Divergence]\label{thm:breg-div-scnvx}
                 Suppose $f$ satisfies Assumption \ref{ass:necoara-2019-settings}. 
@@
                 \end{align*}
-            \end{definition}
-            Then it's not hard to imagine the following natural relaxation of the above conditions. 
+            \end{theorem}
+            Then, it's not hard to imagine the following natural relaxations of the above condition. 
             %===================================================================
@@
             The following theorem summarizes the hierarchy of the conditions listed in Definition \ref{def:necoara-weaker-scnvx}. 
-            \begin{theorem}[Hierarchy of weaker S-CNVX conditions]\label{thm:q-cnvx-hierarchy}
+            \begin{theorem}[Hierarchy of weaker SCNVX conditions]\label{thm:wcnvx-hierach}
                 Let $f$ satisfy Assumption \ref{ass:necoara-2019-settings}, assuming convexity then the following relations are true: 
@@
 
-        \subsection{Characterizing Q-SCNVX functions with Hoffman's Error bound}
-            Necoara et al. \cite{necoara_linear_2019}
+        \subsection{Characterizing Q-SCNVX functions with Hoffman's error bound}
+            Back in 1955, Hoffman \cite{hoffman_approximate_1952} determined the existence of an upper bound for the distance of a point to a polyhedron can be bounded by the constraint violations of the point, uniformly.
+            Let's adopt $[\cdot]_+$ as the notation for projecting on $\RR^n_+$. 
+            Necoara re-introduce the bound, the following theorem phrase that upper bound in the exact same way, but with only the Euclidean norm. 
+            \begin{theorem}[Polyhedral Hoffman Error bound]
+                Let $A \in \RR^{p \times n}, C \in \RR^{m\times n}$. 
+                Given non-empty polyhedron: $P := \{x \in \RR^n : Ax = b, Cx \le d\}$, there exists a constant $\theta(A, C) > 0$ such that 
+                \begin{align*}
+                    (\forall x \in \RR^n)\; \dist(x | P) \le \theta(A, C)\left\Vert
+                        \begin{bmatrix}
+                            Ax - b \\ [Cx - d]_+
+                        \end{bmatrix}
+                    \right\Vert. 
+                \end{align*}
+            \end{theorem}
+            The constant $\theta(A, C)$ is referred to as the Hoffman constant in the literature. 
+            There are two notable generalization of the inequality. 
+            Güler et al. \cite{guler_approximations_1995} found a representation of the Hoffman constant via singular values of sub matrices that defines the polyhedron. 
+            Burke and Tseng \cite{burke_unified_1996} unified the analysis for the Hoffman constant and extend it to the context of general cone over a sublinear convex function, and more. 
+            \par 
+            It's important to note at this point that the exact value of $\theta(A, C)$ is very difficult to obtain in practice. 
+            Let's go back to Necoara \cite{necoara_linear_2019}. 
+            The following theorem stated their use of the Error bound condition to capture a class of Q-SCNVX function. 
+            \begin{theorem}[Q-SCNVX and Hoffman's error bound]\label{thm:q-scnvx-hffmn-eb}
+                Let $X := \{S \in \RR^n: Cx \le d\}$ be non-empty, $g:\RR^m \rightarrow \RR$ be a $\sigma_g$ strongly convex and, $L_g$ Lipschitz smooth function. 
+                Let $A \in \RR^{m\times n}$ be a nonzero, $C \in \RR^{m\times n}$. 
+                Then $f(x):= g(Ax)$ is Q-SCNVX with $L_f = L_g\Vert A\Vert^2$, $\kappa_f = \sigma_g/\theta(A, C)^2$. 
+            \end{theorem}
+            \begin{proof}
+                $X\neq \emptyset$ determines a non-empty set of minimizers $X^+ := \argmin_{x \in X} f(x)$. 
+                We state the following intermediate results prior to their justifications at the end of the proof. 
+                \begin{enumerate}
+                    \item [(a)] $\forall x, y$ it has $\Vert \nabla f(x) - \nabla f(y)\Vert \le \Vert A\Vert^2 L_g \Vert x - y\Vert$. 
+                    \item [(b)] There exists uniquely $(t^*, T^*) \in \RR^{m\times n}$ such that for all $\bar x \in X^+$ it has $Ax^+ = t^*, \nabla f(\bar x) = T^*$.
+In other word, for all minimizers $\bar x$ in $X^+$, $A\bar x$ and, $\nabla f(\bar x)$ are all the same.
+It would mean $X^+ = \{\bar x : A\bar x = t^*, Cx^* \le d\}$ and, it's also a polyhedron.
+                    \item [(c)] Hoffman error bound for Theorem \ref{thm:q-scnvx-hffmn-eb} applied to polyhedron $X^+$, it has 
+                    \begin{align*}
+                        \dist(x | X^+) \le \theta(A, C)\dist((Ax - t^*, Cx - d) | \{\mathbf 0\}\times \RR^n_-)
+                    \end{align*}
+                \end{enumerate}
+                Snatching these two intermediate results, the proof for the overall theorem follows. 
+                For all $x \in \RR^n$ denote $\bar x = \Pi_{X^+} x$, using strong convexity of $g$, and $f(x) = g(Ax)$: 
+                \begin{align*}
+                    f(\bar x) - f(x) - \langle \nabla f(x), \bar x - x\rangle &= 
+                    g(A\bar x) - g(x) - \left\langle A^T\nabla g(Ax), \bar x - x\right\rangle
+                    \\
+                    &= g(A\bar x) - g(x) - \langle \nabla g(Ax), A\bar x - Ax\rangle
+                    \\
+                    &\ge \sigma_g/2\Vert Ax - A\bar x\Vert^2 
+                    \\
+                    &\underset{\text{(b)}}{=} \frac{\sigma_g}{2} \Vert Ax - t^*\Vert^2 
+                    \\
+                    &\underset{\text{(c)}}{\ge} \frac{\sigma_g}{2\theta(A, C)^2} \Vert x - \bar x\Vert^2. 
+                \end{align*}
+                Therefore, the function $f$ is Q-SCNVX, i.e: $f \in \QSCNVX (L_g \Vert A\Vert^2, \sigma_g/\theta(A, C)^2)$. 
+                \\\noindent
+                \textbf{The Proof of (a)} is direct. 
+                \begin{align*}
+                    \Vert \nabla f(x) - \nabla f(y)\Vert &= \Vert A^T \nabla g(Ax) - A^T\nabla g(Ay)\Vert
+                    \\
+                    &\le \Vert A\Vert \Vert \nabla g(Ax) - \nabla g(Ax)\Vert
+                    \\
+                    &\le \Vert A\Vert L_g \Vert Ax - Ay\Vert \le \Vert A\Vert^2 L_g \Vert x - y\Vert. 
+                \end{align*}
+                \textbf{The proof of (b)} has some details. 
+                The set $X^+$ is a convex and, $f$ takes the same value all over it. 
+                Consider any $\bar x_1, \bar x_2 \in X^+$, they have
+                \begin{align*}
+                    (1/2)(f(\bar x_1) + f(\bar x_2)) &= f((1/2)(\bar x_1 + \bar x_2)) 
+                    \\
+                    &= g((1/2)(A\bar x_1 + \bar x_2)) 
+                    \\
+                    &= (1/2)(g(A\bar x_1) + g(A \bar x_2))
+                    \\
+                    &\le (1/2)g(A \bar x_1) + (1/2)g(A \bar x_2) - \frac{\sigma_g}{8}\Vert A\bar x_1 + A \bar x_2\Vert^2. 
+                \end{align*}
+                On the last inequality, we used an equivalent characterization of strong convexity (Theorem \ref{thm:scnvx-eqvs}). 
+                The last inequality implies that $0 \le - \Vert A \bar x_1 - A \bar x_2\Vert^2$, hence it must be that $A\bar x_1 = A \bar x_2$, which would mean $\nabla f(\bar x_1) = \nabla f(\bar x_2)$ because $\nabla f(x) = A^T \nabla g(A \bar x)$.
+            \end{proof}
 
@@
             \begin{theorem}{feasible descent linear convergence under Q-SCNVX}
-                Under Assumption \ref{ass:necoara-2019-settings}, assume that $f$ is Q-CNVX with $\mu_f, L_f$, then the sequence that satisfies Definition \ref{def:projg-alg} has a linear convergence rate.
+                Under Assumption \ref{ass:necoara-2019-settings}, assume that $f$ is Q-SCNVX with $\mu_f, L_f$, then the sequence that satisfies Definition \ref{def:projg-alg} has a linear convergence rate.
                 Let $\bar x_k = \Pi_{X^+}x_k, \bar x_0 = \Pi_{X^+} x_0$. 
@@
                     \item $\alpha_k \le L_f^{-1}$, the stepsize is sufficient to apply descent lemma globally. 
-                    \item $f \in \mathbb Q$ satisfying Q-Growth, a consequence of Q-CNVX by Theorem \ref{thm:q-cnvx-hierarchy}. 
+                    \item $f \in \mathbb Q$ satisfying Q-Growth, a consequence of Q-SCNVX by Theorem \ref{thm:wcnvx-hierach}. 
                 \end{enumerate}

### 2025-06-18 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@
             The converse is true if $f$ is convex. 
-            The gradient mapping in this case is: 
-            \begin{align*}
-                \mathcal G_{L_f}x = L_f(x - \Pi_{X}x). 
+            We define the gradient mapping as: 
+            \begin{align*}
+                \mathcal G_{L_f}(x) := L_f(x - \Pi_{X}(x - L^{-1}_f \nabla f(x))). 
             \end{align*}
@@
                 Suppose $f$ satisfies Assumption \ref{ass:necoara-2019-settings}. 
-                Then $f \in \mathbb S(L_f, \kappa_f, X)$ is strongly convex iff 
+                Then $f$ is $\kappa_f$ strongly convex and $L_f$ smooth if
                 \begin{align*}
@@
                 \end{align*}
+                We denote it by $f \in \mathcal S(L_f, \kappa_f, X)$. 
             \end{theorem}
@@
                     \item\label{def:neocara-qscnvx} Quasi-strong convexity (Q-SCNVX): $0 \le D_f(\bar x, x) - \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. 
-                    Denoted by $\mathbb S'(L_f, \kappa_f, X)$. 
+                    Denoted by $\QSCNVX(L_f, \kappa_f, X)$. 
                     \item\label{def:necoara-qup} Quadratic under approximation (QUA): $0 \le D_f(x, \bar x) - \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. 
-                    Denoted by $\mathbb U(L_f, \kappa_f, X)$. 
+                    Denoted by $\QUA(L_f, \kappa_f, X)$. 
                     \item\label{def:necoara-qgg} Quadratic Gradient Growth (QGG): $0\le D_f(x, \bar x) + D_f(\bar x, x) - \kappa_f/2\Vert x - \bar x\Vert^2$. 
-                    Denoted by $\mathbb G(L_f, \kappa_f, X)$. 
+                    Denoted by $\QGG(L_f, \kappa_f, X)$. 
                     \item\label{def:necoara-qfg} Quadratic Function Growth (QFG): $0 \le f(x) - f^* - \kappa_f/2\Vert x - \bar x\Vert^2$. 
-                    Denoted by $\mathbb F(L_f, \kappa_f, X)$. 
+                    Denoted by $\QFG(L_f, \kappa_f, X)$. 
                     \item\label{def:necoara-peb} Proximal Error Bound (PEB): $\Vert \mathcal G_{L_f}x\Vert \ge \kappa_f\Vert x - \bar x\Vert$. 
-                    Denoted by $\mathbb E(L_f, \kappa_f, X)$. 
+                    Denoted by $\PEB (L_f, \kappa_f, X)$. 
                 \end{enumerate}
@@
                 \begin{align*}
-                    \mathbb S'(L_f, \kappa_f, X) \subseteq \mathbb U(L_f, \kappa_f, X). 
+                    \QSCNVX(L_f, \kappa_f, X) \subseteq \QUA (L_f, \kappa_f, X). 
                 \end{align*}
@@
                 Make inductive hypothesis that there exists $\kappa^{(k)} \ge 0$ such that 
-                \begin{align*}
+                \begin{align}\label{ineq:thm:qscnvx-means-qua-proof-ih}
                     (\forall x \in X)\quad
@@
                     + \kappa^{(k)}_f/2\Vert x - \Pi_{X^+}x \Vert^2. 
-                \end{align*}
+                \end{align}
                 The base case is true by convexity of $f$ with $\kappa_f^{(0)} = 0$. 
@@
                 In the inductive proof that comes, we will use the following intermediate results. 
-                They are labeled for ease of refernecing. 
+                They are labeled for ease of referencing. 
                 \begin{enumerate}
-                    \item The inequality \eqref{ineq:thm:qscnvx-means-qua-proof-item1}. 
-                    \item By the property of projection, it has $\Pi_{X^+} x_\tau = \bar x$. 
-                    \item The inductive hypothesis with $k \ge 0$. 
-                    \item $\bar x = \Pi_{X^+}x$, $X^+$ is the set of minimizer of the of $f$ over $X$, hence $f(\bar x) = f^+$, the minimum. 
+                    \item[(a)] The inequality \eqref{ineq:thm:qscnvx-means-qua-proof-item1} we just showed. 
+                    \item[(b)] By the property of projection, it has $\Pi_{X^+} x_\tau = \bar x$. 
+                    \item[(c)] The inductive hypothesis, inequality \eqref{ineq:thm:qscnvx-means-qua-proof-ih}. 
+                    \item[(d)] $\bar x = \Pi_{X^+}x$, $X^+$ is the set of minimizer of the of $f$ over $X$, hence $f(\bar x) = f^+$, the minimum. 
                 \end{enumerate}
@@
                     \\
-                    &\underset{\text{(i)}}{\ge }
+                    &\underset{\text{(a)}}{\ge }
                     f(\bar x) + 
@@
                     \\
-                    &\underset{\text{(iii)}}{\ge }
+                    &\underset{\text{(c)}}{\ge }
                     f(\bar x) + 
@@
                     \\
-                    &\underset{\text{(ii)}}{=} 
+                    &\underset{\text{(b)}}{=} 
                     f(\bar x) + 
@@
                     \\
-                    &\underset{\text{(iv)}}{=} 
+                    &\underset{\text{(d)}}{=} 
                     f^+ + 
@@
                 \begin{align*}
-                    \mathbb G(L_f, \kappa_f, X)\subseteq \mathbb U(L_f, \kappa_f, X). 
+                    \QGG(L_f, \kappa_f, X)\subseteq \QUA(L_f, \kappa_f, X). 
                 \end{align*}
@@
                 \begin{align*}
-                    \mathbb S'(L_f, \kappa_f, X) \subseteq \mathbb G(L_f, \kappa_f, X). 
+                    \QSCNVX(L_f, \kappa_f, X) \subseteq \QGG (L_f, \kappa_f, X). 
                 \end{align*}
@@
             \begin{proof}
-                If $f \in \mathbb S'(L_f, \kappa_f, X)$ then Theorem \ref{thm:qscnvx-means-qua} has $f \in \mathbb U(L_f, \kappa_f, X)$. 
+                If $f \in \QSCNVX (L_f, \kappa_f, X)$ then Theorem \ref{thm:qscnvx-means-qua} has $f \in \QUA(L_f, \kappa_f, X)$. 
                 Then, add \ref{def:necoara-qup}, \ref{def:neocara-qscnvx} in Definition \ref{def:necoara-weaker-scnvx} yield the results. 
@@
             \begin{remark}
-                This is Theorem 2 in the Necoara et al. \cite{necoara_linear_2019}, right after it claims $\mathbb U(L_f, \kappa_f, X)\subseteq \mathbb G(L_f, \kappa_f/2, X)$ under convexity. 
+                This is Theorem 2 in the Necoara et al. \cite{necoara_linear_2019}, right after it claims $\QUA (L_f, \kappa_f, X)\subseteq \QGG (L_f, \kappa_f/2, X)$ under convexity. 
             \end{remark}
-            % ==================================================================
-            % THEOREM | SUFFICIENCY OF QFG 
-            % ==================================================================
-            \begin{theorem}[sufficiency of QFG]\label{thm:qfg-suff}
-                Let $f$ satisfies Assumption \ref{ass:necoara-2019-settings}. 
-                For all $0 < \beta < 1$, $x \in X$, let $x^+ = \Pi_{X}(x - L^{-1}_f \nabla f(x))$. 
-                If 
-                \begin{align*}
-                    \Vert x^+ - \Pi_{X^+}x^+\Vert \le \beta \Vert x - \Pi_{X^+}x \Vert, 
-                \end{align*}
-                then $f$ satisfies the QFG condition with $\kappa_f = L_f(1 - \beta)^2$. 
-            \end{theorem}
-            \begin{proof}
-                The proof is direct. 
-                \begin{align}
-                    \Vert x - \Pi_{X^+}x\Vert 
-                    &\le \Vert x - \Pi_{X^+}x^+\Vert
-                    \\
-                    &\le \Vert x - x^+\Vert + \Vert x^+ - \Pi_{X^+}x^+\Vert
-                    \\
-                    &\le \Vert x - x^+\Vert + \beta \Vert x - \Pi_{X^+}x\Vert
-                    \\
-                    \iff 
-                    0 &\le \Vert x - x^+\Vert - (1 - \beta) \Vert x - \Pi_{X^+}x\Vert. 
-                \end{align}
-                $x^+$ has descent lemma hence we have 
-                \begin{align*}
-                    f^+ - f(X) \le f(x^+) - f(x) 
-                    \le - \frac{L_f}{2}\Vert x^+ - x\Vert^2 
-                    \le - \frac{L_f}{2}(1 - \beta)^2 \Vert x - \Pi_{X^+}\Vert^2. 
-                \end{align*}
-                Hence, it gives the quadratic growth condition. 
-            \end{proof}
-            \begin{remark}
-                It's unclear where convexity is used. 
-                However, it' still assumed in Necoara et al. paper. 
-            \end{remark}
-            Before we start, we will specialize Theorem \ref{thm:cnvx-pg-ineq} because it will be used in later proofs. 
+            \par
+            Prior to proving more theorems, we will specialize Theorem \ref{thm:cnvx-pg-ineq} because it will be used in later proofs. 
             In Assumption \ref{ass:necoara-2019-settings}, it can be seemed as taking $F = f + g$ in Assumption \ref{ass:smooth-add-nonsmooth} with $g = \delta_{X}$. 
@@
             \end{align}
+            % ==================================================================
+            % THEOREM | SUFFICIENCY OF QFG 
+            % ==================================================================
+            \begin{theorem}[sufficiency of QFG]\label{thm:qfg-suff}
+                Let $f$ satisfies Assumption \ref{ass:necoara-2019-settings}. 
+                For all $0 < \beta < 1$, $x \in X$, let $x^+ = \Pi_{X}(x - L^{-1}_f \nabla f(x))$. 
+                If 
+                \begin{align*}
+                    \Vert x^+ - \Pi_{X^+}x^+\Vert \le \beta \Vert x - \Pi_{X^+}x \Vert, 
+                \end{align*}
+                then $f$ satisfies the QFG condition with $\kappa_f = L_f(1 - \beta)^2$. 
+            \end{theorem}
+            \begin{proof}
+                The proof is direct. 
+                The first inequality is the property of projection onto a set. 
+                \begin{align*}
+                    \Vert x - \Pi_{X^+}x\Vert 
+                    &\le \Vert x - \Pi_{X^+}x^+\Vert
+                    \\
+                    &\le \Vert x - x^+\Vert + \Vert x^+ - \Pi_{X^+}x^+\Vert
+                    \\
+                    &\le \Vert x - x^+\Vert + \beta \Vert x - \Pi_{X^+}x\Vert
+                    \\
+                    \iff 
+                    0 &\le \Vert x - x^+\Vert - (1 - \beta) \Vert x - \Pi_{X^+}x\Vert. 
+                \end{align*}
+                Now, use \eqref{ineq:proj-grad2}. 
+                \begin{align*}
+                    f(x^+) - f(x) 
+                    \le - \frac{L_f}{2}\Vert x^+ - x\Vert^2 
+                    \le - \frac{L_f}{2}(1 - \beta)^2 \Vert x - \Pi_{X^+}x\Vert^2. 
+                \end{align*}
+                Hence, it gives the quadratic growth condition. 
+            \end{proof}
+            \begin{remark}
+                It's unclear where convexity is used. 
+                Take the careful observation that inequality \eqref{ineq:proj-grad2} doesn't still hold for weakly convex function. 
+                However, it' still assumed in Necoara et al. paper. 
+            \end{remark}
             \par
@@
             \begin{lemma}[gradient mapping and quadratic function growth]\;\label{lemma:grad-map-qfg}\\
-                Let $f$ satisfies Assumtion \ref{ass:necoara-2019-settings}. 
-                Suppose that $f \in \mathbb F(L_f, \mu_f, X)$ so it satisfies the quadratic function growth condition. 
+                Let $f$ satisfies Assumption \ref{ass:necoara-2019-settings}.
+                Suppose that $f \in \QFG(L_f, \mu_f, X)$ so, it satisfies the quadratic function growth condition. 
                 For all $x \in \RR^n$, define $x^+ = \Pi_X(x - L^{-1}_f\nabla f(x))$, 
-                definte projections onto the set of minimizers $x^+_\Pi = \Pi_{X^+} x^+, X_\Pi = \Pi_{X^+}x$, then
+                define projections onto the set of minimizers $\bar x^+ = \Pi_{X^+} x^+, \bar x = \Pi_{X^+}x$, then
                 \begin{align*}
@@
                         \sqrt{L_f(\kappa_f + L_f)} - L_f
-                    \right)\Vert x^+ - x_\Pi^+\Vert
+                    \right)\Vert x^+ - \bar x^+\Vert
                     &\le \Vert L_f(x - x^+)\Vert. 
@@
             \begin{proof}
-                Using convexity, consider \eqref{ineq:proj-grad} with $z = x^+_\Pi$ it yields: 
+                Using convexity, consider projected gradient inequality \eqref{ineq:proj-grad} with $z = \bar x^+$ it yields: 
                 {\small
@@
                     0 &\ge 
-                    f(x^+) - f(x^+_\Pi) - L_f\langle x_\Pi^+ - x^+, x^+ - x\rangle
-                    - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert^2
-                    \\
-                    &\ge
-                    \frac{\kappa_f}{2}\Vert x^+ - x_\Pi^+\Vert^2
-                    - \Vert L_f(x - x^+)\Vert\Vert x^+_\Pi - x^+\Vert
+                    f(x^+) - f(\bar x^+) - L_f\langle \bar x^+ - x^+, x^+ - x\rangle
                     - \frac{1}{2L_f}\Vert L_f(x - x^+)\Vert^2
                     \\
-                    &= \frac{\kappa_f}{2}\Vert x^+ - x_\Pi^+\Vert^2
+                    &\underset{\text{(a)}}\ge
+                    \frac{\kappa_f}{2}\Vert x^+ - \bar x^+\Vert^2
+                    - \Vert L_f(x - x^+)\Vert\Vert \bar x^+ - x^+\Vert
+                    - \frac{1}{2L_f}\Vert L_f(x - x^+)\Vert^2 
+                    \\
+                    &= \frac{\kappa_f}{2}\Vert x^+ - \bar x^+\Vert^2
                     - \frac{1}{2L_f}\left(
                         \Vert L_f(x - x^+)\Vert^2
-                        + L_f\Vert L_f(x - x^+)\Vert\Vert x_\Pi^+ - x^+\Vert
-                    \right)
-                    \\
-                    &= 
-                    \frac{\kappa_f + L_f}{2}\Vert x^+ - x^+_\Pi\Vert^2
+                        + 2L_f\Vert L_f(x - x^+)\Vert\Vert \bar x^+ - x^+\Vert
+                    \right)
+                    \\
+                    &= \frac{\kappa_f + L_f}{2}\Vert x^+ - \bar x^+\Vert^2
                     - \frac{1}{2L_f}\left(
-                        \Vert L_f(x - x^+)\Vert + L_f\Vert x - x_\Pi^+\Vert
+                        \Vert L_f(x - x^+)\Vert^2
+                        + 2L_f\Vert L_f(x - x^+)\Vert\Vert \bar x^+ - x^+\Vert
+                        + L_f^2\Vert\bar x^+ - x^+\Vert^2
+                    \right)
+                    \\
+                    &= 
+                    \frac{\kappa_f + L_f}{2}\Vert x^+ - \bar x^+\Vert^2
+                    - \frac{1}{2L_f}\left(
+                        \Vert L_f(x - x^+)\Vert + L_f\Vert x - \bar x^+\Vert
                     \right)^2.
@@
                 }
-                From the last line, it's can be equivalently expressed as:
+                At label (a), we statement hypothesis $f \in \QFG (L_f, \kappa_f, X)$ and, Cauchy inequality. 
+                From the last line, it can be equivalently expressed as:
                 \begin{align*}
                     0 &\le
-                    \Vert L_f(x - x^+)\Vert + L_f\Vert x^+ - x_\Pi^+\Vert
-                    - \sqrt{L_f(\kappa_f + L_f)}\Vert x^+ - x^+_\Pi\Vert
+                    \Vert L_f(x - x^+)\Vert + L_f\Vert x^+ - \bar x^+\Vert
+                    - \sqrt{L_f(\kappa_f + L_f)}\Vert x^+ - \bar x^+\Vert
                     \\
@@
                     \Vert L_f(x - x^+)\Vert
-                    - \left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right)\Vert x^+ - x^+_\Pi\Vert.
+                    - \left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right)\Vert x^+ - \bar x^+\Vert.
                 \end{align*}
@@
                 \begin{align*}
-                    \mathbb E(L_f, \kappa_f, X) &\subseteq \mathbb F(L_f, \kappa^2_f/L_f, X), 
-                    \\
-                    \mathbb F(L_f, \kappa_f) 
+                    \QFG (L_f, \kappa_f) 
                     &\subseteq 
-                    \mathbb E\left(
+                    \PEB\left(
                         L_f,
@@
                         X
-                    \right). 
+                    \right), 
+                    \\
+                    \PEB (L_f, \kappa_f, X) &\subseteq \QFG(L_f, \kappa^2_f/L_f, X). 
                 \end{align*}
@@
             \begin{proof}
-                For any $x \in X$, define the gradient projection steps by $x^+ = \Pi_{X}(x - L^{-1}_f\nabla f(x))$. 
-                Denote $x^+_\Pi = \Pi_{X^+}x^+$. 
-                Let $x_\Pi = \Pi_{X^+}x$, using the property of projection onto $X$ we have 
+                For any $x \in X$, define the projected gradient: $x^+ = \Pi_{X}(x - L^{-1}_f\nabla f(x))$. 
+                Denote $\bar x^+ = \Pi_{X^+}x^+$. 
+                Let $\bar x = \Pi_{X^+}x$, using the property of projection onto $X$ we have 
                 \begin{align}\label{ineq:thm:qfg-peb-equiv-proof-item1}
-                    \Vert x - x_\Pi\Vert &\le \Vert x - x_\Pi^+\Vert
-                    \le \Vert x - x^+\Vert + \Vert x^+ - x^+_\Pi\Vert
+                    \Vert x - \bar x\Vert &\le \Vert x - \bar x^+\Vert
+                    \le \Vert x - x^+\Vert + \Vert x^+ - \bar x^+\Vert
                     \notag\\
-                    &= \frac{1}{L_f}\Vert L_f(x - x^+)\Vert + \Vert x^+ - x^+_\Pi\Vert
+                    &= \frac{1}{L_f}\Vert L_f(x - x^+)\Vert + \Vert x^+ - \bar x^+\Vert
                     \notag\\
                     \iff 
-                    \Vert x^+ - x^+_\Pi\Vert &\ge
-                    \Vert x - x_\Pi\Vert - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert. 
+                    \Vert x^+ - \bar x^+\Vert &\ge
+                    \Vert x - \bar x\Vert - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert. 
                 \end{align}
-                Before we start, we list intermediate results and conditions which are going to be used in the proof that follows for the ease of referencing. 
-                \begin{enumerate}
-                    \item The inequality \eqref{ineq:thm:qfg-peb-equiv-proof-item1}. It uses the property of projection onto a set hence convexity of $X^+$ is not needed. 
-                \end{enumerate}
-                Starting with Lemma \ref{lemma:grad-map-qfg} because $f$ satisfies quadratic growth and it is assumed convex, then it has: 
+                Starting with Lemma \ref{lemma:grad-map-qfg} because $f$ satisfies quadratic growth and, it is assumed convex, then it has: 
                 {\small
@@
                     \Vert L_f(x - x^+)\Vert
-                    - \left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right)\Vert x^+ - x^+_\Pi\Vert
-                    \\
-                    &\underset{\text{(i)}}{\le}
+                    - \left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right)\Vert x^+ - \bar x^+\Vert
+                    \\
+                    &\underset{\text{(a)}}{\le}
                     \Vert L_f(x - x^+)\Vert
@@
                     \le
-                    \Vert \mathcal G_{L_f}x\Vert. 
-                \end{align*}
-                }
-                Skipping some algebra, the fraction simplifies to 
-                \begin{align*}
-                    \frac{\kappa_f/L_f}{\kappa_f/L_f + 1 + \sqrt{\kappa_k/L_f + 1}}. 
-                \end{align*}
-                This gives PEB condition. 
+                    L_f^{-1} \Vert \mathcal G_{L_f}x\Vert. 
+                \end{align*}
+                }
+                At the label (a), we used inequality \eqref{ineq:thm:qfg-peb-equiv-proof-item1}.
+                Continuing with some algebra, we have: 
+                \begin{align*}
+                    \frac{\sqrt{L_f(\kappa_f + L_f)} - L_f}{\sqrt{L_f(\kappa_f + L_f)}} 
+                    &= \frac{L_f(\kappa_f + L_f) - L_f^2}{\sqrt{L_f(\kappa_f + L_f)}(\sqrt{L_f(\kappa_f + L_f)} + L_f)}
+                    \\
+                    &= \frac{L_f \kappa_f}{L_f(\kappa_f + L_f) + L_f\sqrt{L_f(\kappa_f + L_f)}}
+                    \\
+                    &= \frac{\kappa_f/L_f}{\kappa_f/L_f + 1 + \sqrt{\kappa_k/L_f + 1}}. 
+                \end{align*}
+                This gives PEB condition: 
+                \begin{align*}
+                    \Vert \mathcal G_{L_f}(x)\Vert \ge L_f 
+                    \frac{\kappa_f/L_f}{\kappa_f/L_f + 1 + \sqrt{\kappa_k/L_f + 1}}\Vert x - \bar x\Vert
+                    = 
+                    \frac{\kappa_f}{\kappa_f/L_f + 1 + \sqrt{\kappa_k/L_f + 1}}\Vert x - \bar x\Vert. 
+                \end{align*}
                 \textbf{We now show PEB implies QFG}. 
@@
                 \begin{align*}
-                    \mathbb S(\kappa_f, L_f, X) 
-                    \subseteq \mathbb S'(\kappa_f, L_f, X)
-                    \subseteq \mathbb G(\kappa_f, L_f, X) 
-                    \subseteq \mathbb U(\kappa_f, L_f, X) 
-                    \subseteq \mathbb F(\kappa_f, L_f, X). 
+                    \mathcal S(\kappa_f, L_f, X) 
+                    \subseteq \QSCNVX(\kappa_f, L_f, X)
+                    \subseteq \QGG(\kappa_f, L_f, X) 
+                    \subseteq \QUA(\kappa_f, L_f, X) 
+                    \subseteq \QFG(\kappa_f, L_f, X). 
                 \end{align*}
@@
             \begin{proof}
-                $\mathbb S' \subseteq \mathbb G$ is proved in Theorem \ref{thm:qscnvx-implies-qgg} and $\mathbb G \subseteq \mathbb U$ is proved in \ref{thm:qgg-implies-qua}. 
-                $\mathbb S\subseteq \mathbb S'$ is obvious and it remains to show $\mathbb U \subseteq \mathbb F$. 
-                Let $f\in \mathbb U(\kappa_f, L_f, X)$, it has for all $x \in X$: 
+                $\QSCNVX \subseteq \QGG$ is proved in Theorem \ref{thm:qscnvx-implies-qgg} and $\QGG \subseteq \QUA$ is proved in Theorem \ref{thm:qgg-implies-qua}. 
+                $\mathcal S\subseteq \QSCNVX'$ is obvious. 
+                It remains to show $\QUA \subseteq \QFG$. 
+                Let $f\in \QUA(\kappa_f, L_f, X)$, it has for all $x \in X$: 
                 \begin{align*}
@@
             Let's adopt $[\cdot]_+$ as the notation for projecting on $\RR^n_+$. 
-            Necoara re-introduce the bound, the following theorem phrase that upper bound in the exact same way, but with only the Euclidean norm. 
+            Necoara re-introduce the bound, the following theorem phrase that upper bound in the exact same way, but only with the Euclidean norm. 
             \begin{theorem}[Polyhedral Hoffman Error bound]
@@
             Let's go back to Necoara \cite{necoara_linear_2019}. 
-            The following theorem stated their use of the Error bound condition to capture a class of Q-SCNVX function. 
+            The following theorem stated their use of the this error bound to capture a class of Q-SCNVX function. 
             \begin{theorem}[Q-SCNVX and Hoffman's error bound]\label{thm:q-scnvx-hffmn-eb}
@@
                 Let $A \in \RR^{m\times n}$ be a nonzero, $C \in \RR^{m\times n}$. 
-                Then $f(x):= g(Ax)$ is Q-SCNVX with $L_f = L_g\Vert A\Vert^2$, $\kappa_f = \sigma_g/\theta(A, C)^2$. 
+                Define $f(x):= g(Ax)$, then $f$ is Q-SCNVX with $L_f = L_g\Vert A\Vert^2$, $\kappa_f = \sigma_g/\theta(A, C)^2$. 
             \end{theorem}
             \begin{proof}
-                $X\neq \emptyset$ determines a non-empty set of minimizers $X^+ := \argmin_{x \in X} f(x)$. 
+                $X\neq \emptyset$ gives a non-empty set of minimizers $X^+ := \argmin_{x \in X} f(x)$. 
                 We state the following intermediate results prior to their justifications at the end of the proof. 
@@
                     \item [(a)] $\forall x, y$ it has $\Vert \nabla f(x) - \nabla f(y)\Vert \le \Vert A\Vert^2 L_g \Vert x - y\Vert$. 
-                    \item [(b)] There exists uniquely $(t^*, T^*) \in \RR^{m\times n}$ such that for all $\bar x \in X^+$ it has $Ax^+ = t^*, \nabla f(\bar x) = T^*$.
+                    \item [(b)] There exists uniquely $(t^*, T^*) \in \RR^{m\times n}$ such that for all $\bar x \in X^+$ it has $A\bar x = t^*, \nabla f(\bar x) = T^*$.
 In other word, for all minimizers $\bar x$ in $X^+$, $A\bar x$ and, $\nabla f(\bar x)$ are all the same.
-It would mean $X^+ = \{\bar x : A\bar x = t^*, Cx^* \le d\}$ and, it's also a polyhedron.
+It would mean $X^+ = \{\bar x : A\bar x = t^*, C\bar x \le d\}$ and, it's also a polyhedron.
                     \item [(c)] Hoffman error bound for Theorem \ref{thm:q-scnvx-hffmn-eb} applied to polyhedron $X^+$, it has 
                     \begin{align*}
-                        \dist(x | X^+) \le \theta(A, C)\dist((Ax - t^*, Cx - d) | \{\mathbf 0\}\times \RR^n_-)
-                    \end{align*}
+                        \dist(x |\; X^+) \le \theta(A, C)\dist((Ax - t^*, Cx - d) |\; \{\mathbf 0\}\times \RR^n_-)
+                    \end{align*}
+                    And for any feasible solution $x \in X$, it simplifies to $\dist(x | X^+) \le \theta(A, C) \dist(Ax - t^* |\; \{\mathbf 0\}\times \RR^n_-)$. 
                 \end{enumerate}
                 Snatching these two intermediate results, the proof for the overall theorem follows. 
-                For all $x \in \RR^n$ denote $\bar x = \Pi_{X^+} x$, using strong convexity of $g$, and $f(x) = g(Ax)$: 
+                For all $x \in X$ denote $\bar x = \Pi_{X^+} x$, using strong convexity of $g$, and $f(x) = g(Ax)$: 
                 \begin{align*}
@@
                 \textbf{The proof of (b)} has some details. 
-                The set $X^+$ is a convex and, $f$ takes the same value all over it. 
+                The set $X^+$ is convex and, $f$ takes the same value all over it. 
                 Consider any $\bar x_1, \bar x_2 \in X^+$, they have
@@
                     \\
-                    &\underset{\text{(c)}}{\ge} \frac{\sqrt{L(\mu + L)} - L}{\sqrt{L(\mu + L)}} \frac{1}{\sqrt{2L}}\left\Vert
+                    &\underset{\text{(c)}}{\ge} \frac{L(\sqrt{L(\mu + L)} - L)}{\sqrt{L(\mu + L)}} \frac{1}{\sqrt{2L}}\left\Vert
                         z_J - z_J^+
@@
                     \\
-                    &= \frac{1}{\sqrt{2L}}\left(
+                    &= \frac{\sqrt{L}}{\sqrt{2}}\left(
                         1 - \frac{1}{\sqrt{1 + \mu/L}}
@@
                     \\
-                    &\underset{\text{(d)}}{\ge} \frac{\mu}{2\sqrt{L}}\left(
+                    &\underset{\text{(d)}}{\ge} \frac{\mu\sqrt{L}}{\sqrt{2}}\left(
                         \frac{\sqrt{2} - 1}{\sqrt{2}}
@@
                     = 
-                    \kappa\left(
-                        \frac{\sqrt{L}\left(2 - \sqrt{2}\right)}{4}
+                    \frac{\kappa}{\sqrt{L}}\left(
+                        \frac{\sqrt{2} - 1}{2}
                     \right)
@@
                 \item [(a)] For the first equality, we assumed that $G^{(J)} < \epsilon$ in the outer loop and, it's returned by Algorithm \ref{alg:xxapg} at line 5.
-Therefore, it has $G_0 = G^{(J)} = \sqrt{L^{(J)}_0} \Vert z^{(J)} - x_0^{(J)}\Vert$ because it calls Algorithm \ref{alg:armijo-ls} (Armijo line search) with $\alpha_0 = 0$.
+Therefore, it has $G_0 = G^{(J)} = \sqrt{L^{(J)}_0} \left\Vert z^{(J)} - x_0^{(J)}\right\Vert$ because it calls Algorithm \ref{alg:armijo-ls} (Armijo line search) with $\alpha_0 = 0$.
 The second equality comes by using Definition \ref{def:gm-for-ch2}.
@@
                 \item [(c)] Using Theorem \ref{thm:qfg-peb-equiv} from previous chapter and take note that Assumption \ref{ass:q-growth-ch2} is Definition \ref{def:necoara-weaker-scnvx}\ref{def:necoara-qfg}.
-                \item [(d)] The function $x \mapsto 1 - (1 + x/L)^{-1/2}$ is concave hence for all $x \in [0, L]$ it has: 
-                \begin{align*}
-                    1 - (1 + \mu/L)^{-1/2} &= \left[x \mapsto 1 - (1 + x/L)^{-1/2}\right](0(1 - \mu) + \mu)
-                    \\
-                    &\ge 0(1 - \mu) + \mu(1 - 2^{-1/2}) 
+                \item [(d)] Define function $h = x \mapsto 1 - (1 + x/L)^{-1/2}$ is concave hence for all $x \in [0, L]$ it has: 
+                \begin{align*}
+                    1 - (1 + \mu/L)^{-1/2} &= h(0(1 - \mu) + \mu L)
+                    \\
+                    &\ge 0(1 - \mu) + \mu\left(1 - (1 + 1)^{-1/2}\right) 
                     \\
@@
                 &\le 
-                \frac{4e\sqrt{2}(F(z_0) - F^+)^{1/2}}{\kappa\sqrt{L}(2 - \sqrt{2})} 
+                \frac{2e\sqrt{2L}(F(z_0) - F^+)^{1/2}}{\kappa(\sqrt{2} - 1)} 
                 \exp\left(
@@
                 \ln \left(
-                    \frac{4e\sqrt{2}(F(z_0) - F^+)^{1/2}}{\kappa \sqrt{L}(2 - \sqrt{2})\delta}
+                    \frac{2e\sqrt{2L}(F(z_0) - F^+)^{1/2}}{\kappa(\sqrt{2} - 1)\delta} 
                 \right). 
@@
             The convergence rate can be simplified a bit. 
-            On a calculator it has $4e\sqrt{2}/(2 - \sqrt{2}) \le 27$ and, $1/(16\sqrt{2 + 2e}) \ge 0.02$ so 
-            \begin{align*}
-                \Vert z_J - z_J^+\Vert &\le \frac{27(F(z_0) - F^+)^{1/2}}{\kappa}\exp\left(
-                    - \frac{K\sqrt{\kappa}}{20}
+            On a calculator it has $(2e\sqrt{2})/(\sqrt{2} - 1) < 19$ and, $1/(16\sqrt{2 + 2e}) > 0.025$ so 
+            \begin{align*}
+                \Vert z_J - z_J^+\Vert &\le \frac{19\sqrt{L}(F(z_0) - F^+)^{1/2}}{\kappa}\exp\left(
+                    - \frac{K\sqrt{\kappa}}{40}
                 \right). 

### 2025-06-19 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, new stuff

@@
             Let's go back to Necoara \cite{necoara_linear_2019}. 
-            The following theorem stated their use of the this error bound to capture a class of Q-SCNVX function. 
+            The following theorem stated their use of the error bound to capture a class of Q-SCNVX function. 
             \begin{theorem}[Q-SCNVX and Hoffman's error bound]\label{thm:q-scnvx-hffmn-eb}
@@
                     \item Inequality \eqref{ineq:projg-variational-ineq}, from the projected gradient and convexity of $X$. 
-                    \item $f \in \mathbb S'$ which is the hypothesis that $f$ is Q-CNVX. 
-                    \item $\alpha_k \le L_f^{-1}$, the stepsize is sufficient to apply descent lemma globally. 
+                    \item $f \in \mathbb S'$ which is the hypothesis that $f$ is Q-SCNVX. 
+                    \item $\alpha_k \le L_f^{-1}$, the step size is sufficient to apply descent lemma globally. 
                     \item $f \in \mathbb Q$ satisfying Q-Growth, a consequence of Q-SCNVX by Theorem \ref{thm:wcnvx-hierach}. 
@@
             In addition to Algorithm \ref{alg:beck-mono}, $\eta$ is a new input parameter and $G$ has a significance role. 
-            $\eta$ is a stepsize parameter for weakly convex objective $F = f + g$ satisfying Assumption \ref{ass:sum-of-wcnvx}. 
+            $\eta$ is a step size parameter for weakly convex objective $F = f + g$ satisfying Assumption \ref{ass:sum-of-wcnvx}. 
             $G$ is the norm of the gradient mapping updated at $\hat y$ which will be returned to the inner loop to verify exit conditions.
@@
         As a consequence, for $j < J$, it has either $p_{j + 1} \ge n_{j + 1} = 2p_j \ge 2n_{j} \ge n_j$ or $p_{j + 1} \ge n_{j + 1} = p_j \ge n_j$. 
-        Both $(n_j)_{j\ge0}, (p_j)_{j\ge 0}$ are nondecreasing sequences. 
+        Both $(n_j)_{j\ge0}, (p_j)_{j\ge 0}$ are non-decreasing sequences. 
         \par

### 2025-07-01 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

\documentclass[12pt]{article}

% \input{presets/wang_full.tex}
\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{true}
\input{presets/wang/input.tex}
\input{presets/misc.tex}
\input{presets/julia_lstlisting.tex}

\begin{document}

\title{{\fontfamily{ptm}\selectfont Lorum ipsum}}

\author{
    Author 1 Name, Author 2 Name
    \thanks{
        Subject type, Some Department of Some University, Location of the University,
        Country. E-mail: \texttt{author.name@university.edu}.
    }
}

\date{\today}

\maketitle
\todoinline{This paper is currently in draft mode. Check source to change options. }
% \vskip 8mm

\begin{abstract} 
    \noindent
    Lorem ipsum dolor sit amet, dicta iudicabit consequat ex vix, veniam legimus appetere has id, an pri graece epicuri detraxit. Ea aliquam expetendis posidonium eos, nam invenire corrumpit imperdiet ei. Et constituto dissentias usu, mel solum erant et. Mel dolorem menandri in.
    \cite{nesterov_lectures_2018}
    \todo{This is just psuedo text. This is just psuedo text. This is just psuedo text. This is just psuedo text. }
\end{abstract}

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 47H05, 52A41, 90C25; Secondary 15A09, 26A51, 26B25, 26E60, 47H09, 47A63.
\noindent{\bfseries Keywords:}

% ==============================================================================
\section{Nesterov's Accelerated Gradient}
    \subsection{In preparations}
        \begin{assumption}[Smooth add nonsmooth]\label{ass:smooth_plus_nonsmooth}
            The function $F = f + g$ where $f:\RR^n \rightarrow \RR$ is a $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
            The function $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function. 
        \end{assumption}

        \begin{definition}[Proximal gradient operator]
            Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth_plus_nonsmooth}. 
            Let $\beta > 0$. 
            Then, we define the proximal gradient operator $T_{\beta}$ as 
            \begin{align*}
                T_\beta (x | F) &= \argmin{z} \left\lbrace
                    g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{\beta}{2}\Vert z - x\Vert^2
                \right\rbrace. 
            \end{align*}
        \end{definition}
        \begin{remark}
            If the function $g \equiv 0$, then it yields the gradient descent operator $T_\beta(x) = x - \beta^{-1}\nabla f(x)$. 
            In the context where it's clear what the function $F = f + g$ is, we simply write $T_\beta(x)$ for short. 
        \end{remark}

        \begin{definition}[Bregman Divergence]
            Let $f:\RR^n \rightarrow \overline \RR$ be a differentiable function. 
            Then, for all the Bregman divergence $D_f: \RR^n \times \dom\nabla f \rightarrow \RR$ is defined as: 
            \begin{align*}
                D_f(x, y) := f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 
            \end{align*}
        \end{definition}
        \begin{remark}
            If, $f$ is $\mu \ge 0$ strongy convex and $L$ Lipschitz smooth then, its Bregman Divergence has for all $x, y \in \RR^n$: $\mu/2 \Vert x - y\Vert^2 \le D_f(x, y) \le L/2 \Vert x - y\Vert^2$. 
        \end{remark}

        \begin{definition}[R-WAPG sequence]\label{def:rwapg-seq}
            Let $(L_k)_{k \ge 0}$ be a sequence such that $L_k > \mu$ for all $k$. 
            Let $\alpha_0 \in (0, 1]$, $(\alpha_k)_{k \ge 1}$ has $\alpha_k \in (\mu/ L_k, 1)$. 
            Then define for all $k \ge 0$: 
            \begin{align*}
                \rho_k(1 - \alpha_{k + 1})\alpha_k^2 = \alpha_{k + 1}(\alpha_{k + 1} - \mu/L_k). 
            \end{align*}
        \end{definition}
        \begin{remark}
            When $\rho_k = 1$, the recursive relation between $\alpha_k, \alpha_{k - 1}$ is the same as the well known Nesterov's sequence used in algorithm such as FISTA and Nesterov's accelerated gradient. 
            See Li and Wang \cite{li_relaxed_2025} for more information. 
        \end{remark}

        \begin{definition}[similar triangle representation of NAPG]\;\label{def:st-method}\\
            Let $(\alpha_k)_{k \ge 0}$ be an R-WAPG sequence. 
            Suppose that the base case $v_{-1}, x_{k - 1}\in \RR^n$ is given to initialize the algorithm. 
            Then the algorithm produces the sequence of iterates $(y_k, x_k, v_k)_{k \ge 0}$ and auxilary parameter sequence $L_k, \tau_k$ satisfying these inequalities: 
            \begin{align*}
                & \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}, 
                \\
                & y_k = (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1},
                \\
                & D_f(x_k, y_k) \le L_k/2\Vert x_k - y_k\Vert^2, 
                \\
                & x_k = T_{L_k}(y_k),
                \\
                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
            \end{align*} 
        \end{definition}
        The following theorems are critical in analyzing the behavior of algorithm in Definition \ref{def:st-method}. 
        \begin{theorem}[proximal gradient inequality]\label{thm:pg-ineq}
            Let function $F$ satisfies Assumption \ref{ass:smooth_plus_nonsmooth}, so it's $\mu \ge 0$ strongly convex. 
            For all $x\in \RR^n$, define $x^+ = T_L(x)$, then there exists a $B \ge 0$ such that $D_f(x^+, x) \le B/2 \Vert x^+ - x\Vert^2$. 
            Then, for all $z \in \RR^n$ it satisfies proximal gradient inequality at point $x$:  
            \begin{align*}
                0&\le F(z) - F(x^+) - \frac{B}{2}\Vert z - x^+\Vert^2  + \frac{B - \mu}{2}\Vert z - x\Vert^2
                \\
                &=  F(z) - F(x^+) - \langle B(x - x^+), z - x\rangle
                - \frac{\mu}{2}\Vert z - x\Vert^2
                - \frac{B}{2}\Vert x - x^+\Vert^2. 
            \end{align*}
            Since $f$ is assumed to be $L$ Lispchitz smooth, the above condition is true for all $x, y \in \RR^n$ for all $B \ge L$. 
        \end{theorem}
        \begin{remark}
            The theorem is the same as in Nesterov's book \cite[Theorem 2.2.13]{nesterov_lectures_2018}, but with the use of proximal gradient mapping and proximal gradient instead of project gradient hence making it equivalent to the theorem in Beck's book \cite[Theorem 10.16]{beck_first-order_2017}. 
            The only generalization here is parameter $B$ which made to accomodate algorithm that implements Definition \ref{def:st-method} with some line search routine. 
        \end{remark}
        \begin{theorem}[Jensen's inequality]\label{thm:jesen}
            Let $F: \RR^n \rightarrow \overline \RR$ be a $\mu \ge 0$ strongly convex function. 
            Then, it is equivalent to the following condition. 
            For all $x, y \in \RR^n$, $\lambda \in (0, 1)$ it satisfies the inequality 
            \begin{align*}
                (\forall \lambda \in [0, 1])\; 
                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\mu\lambda(1 - \lambda)}{2} \Vert y - x\Vert^2. 
            \end{align*}
        \end{theorem}
        \begin{remark}
            If $x, y$ is out of $\dom F$, the inequality still work by convexity. 
        \end{remark}

    \subsection{A compact argument for the convergence of NAPG with proximal gradient}
        Here, the abbreviation ``NAPG" stands for ``Nesterov Acceleration Proximal Gradient". 
        It's made in acknowledgement of Algorithm 2.2.36 in Nesterov's book \cite{nesterov_lectures_2018} and its extension known as FISTA in the literature.
        The following theorem provide a complete proof for the convergence rate of algorithms implementing Definition \ref{def:st-method}, which is equivalent to NAG, or NAPG. 
        It made use of Definition \ref{def:rwapg-seq} which accomodates a relaxed sequence compared to the usual sequence that gives the optimal convergence rate. 
        \begin{theorem}[one step convergence claim of NAPG]\label{thm:onestep-napg-cnvg}
            Let $F = f + g$ satisfies Assumption \ref{ass:smooth_plus_nonsmooth} for some $L > \mu \ge 0$. 
            Let the sequence $(\alpha_k)_{k \ge0}$ be an R-WAPG sequence (Definition \ref{def:rwapg-seq}). 
            Suppose that the iterates sequence $(x_k, y_k, v_k)_{k \ge 0}$ satisfy NAPG in similar triangle form (Definition \ref{def:st-method}) with initial guesses $v_{-1}, x_{-1} \in \RR^n$. 
            Then for all $k \ge 1$, the following inequality is true for all $\bar x \in \RR^n$: 
            \begin{align*}
                & - F(\bar x) + F(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                \\
                & \le \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(1 - \alpha_k)\left(
                    F(x_{k - 1}) - F(\bar x) 
                    + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \right). 
            \end{align*}
            If in addition, we choose $\alpha_0 = 1$, and let $x_{-1} = v_{-1}$, then a base case of the inequality is: 
            \begin{align*}
                F(x_{0}) - F(\bar x) + \frac{L_0}{2}\Vert \bar x - x_{0}\Vert^2 
                &\le \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
            \end{align*}
        \end{theorem}
        \begin{proof}
            The proof is very intense algebratically hence before we step into it, we present the following intermediate results in advance to their proofs given at the end. 
            \par
            For all $k \ge 0$, define $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$. 
            \begin{itemize}
                \item [(a)] Theorem \ref{thm:pg-ineq}, with $z = z_k$, $k \ge 0$. We can use it because $F = f + g$ satisfies Assumption \ref{ass:smooth_plus_nonsmooth} . 
                \item [(b)] Jensen's inequality (Theorem \ref{thm:jesen}), with $z = z_k$, for $k \ge 0$. We can use it because $F$ is $\mu \ge 0$ strongly convex. 
                \item [(c)] Definition \ref{def:rwapg-seq} which has $\rho_k(1 - \alpha_{k + 1})\alpha_k^2 = \alpha_{k + 1}(\alpha_{k + 1} - \mu/L_k)$ for $k \ge 0$.
                \item [(d)] The equality $z_k - y_k = (L_k - \mu)^{-1}((L_k\alpha_k - \mu)(\bar x - v_k) + \mu(1 - \alpha_k)(\bar x - x_{k - 1}))$ for all $k \ge 0$. 
                \item [(e)] The equality $z_k - x_k = \alpha_k(\bar x - v_k)$ for all $k \ge 0$. 
                \item [(f)] The following equality: 
                \begin{align*}
                    (\forall k \ge 1)\; \frac{1}{2}\left(
                        \frac{\mu^2(1 - \alpha_k)^2}{L_k - \mu} - \mu \alpha_k(1 - \alpha_k)
                    \right) &= 
                    \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}. 
                \end{align*}
                \item [(g)] The following equality: 
                \begin{align*}
                    (\forall k \ge 1)\; 
                    \frac{1}{2}\left(
                        \frac{(L_k\alpha_k - \mu)^2}{L_k - \mu} - 
                        \alpha_{k - 1}^2\rho_{k - 1}L_k(1 - \alpha_k)
                    \right)
                    &= 
                    \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)}. 
                \end{align*}
                \item [(h)] The equality: 
                \begin{align*}
                    (\forall k \ge 1)\; \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)} &\le 0.   
                \end{align*}
            \end{itemize}
            With intermediate results (a) to (h), presented above, the proof of the theorem come smoothly from a chain of inequalities and equalities. 
            The overall proof now follows. 
            Start with the (a), the proximal gradient inequality it has: 
            \begin{align*}
                0 &\le F(z_k) - F(x_k) - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2
                \\
                &\underset{\text{(b)}}{\le}
                \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k) \\
                    &\quad 
                    - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
                    - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2. 
            \end{align*}
            Using the chain of equality below: 
            {\footnotesize
            \begin{align*}
                &- \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2
                \\
                &\underset{\text{(d)}}{=} 
                -\frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2\\ 
                    &\quad +
                    \frac{L_k - \mu}{2}
                    \left\Vert 
                        \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1}) + 
                        \frac{\mu(1 - \alpha_k)}{L_k - \mu}(\bar x - x_{k - 1})
                    \right\Vert^2
                \\
                &= 
                - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
                \\
                &\quad + 
                    \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} \Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} \Vert \bar x - x_{k - 1}\Vert^2
                    + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
                \\
                &= \left(
                    \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} - \frac{\mu\alpha_k(1 - \alpha_k)}{2}
                \right)\Vert \bar x - x_{k - 1}\Vert^2
                + 
                \left(
                    \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)}
                    - \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}
                \right)\Vert \bar x - v_{k - 1}\Vert^2
                \\ &\quad 
                    + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                    - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
                    + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
                \\
                &\underset{\text{(f)}}{=} 
                \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert \bar x - x_{k - 1}\Vert^2
                + 
                \left(
                    \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)}
                    - \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}
                \right)\Vert \bar x - v_{k - 1}\Vert^2
                \\ &\quad 
                    + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                    - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
                    + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
                \\
                &\underset{\text{(g)}}{=}
                \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert \bar x - x_{k - 1}\Vert^2
                + 
                \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)}\Vert \bar x - v_{k - 1}\Vert^2
                \\ &\quad 
                    + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                    - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
                    + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
                \\
                &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
                \\ & \quad
                    \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\left(
                        \Vert \bar x - x_{k - 1}\Vert^2 + \Vert \bar x - v_{k - 1}\Vert^2 - 2\langle\bar x - x_{k - 1},\bar x - v_{k - 1} \rangle
                    \right)
                \\
                &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
                + \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2. 
            \end{align*}
            }
            The inequality from previously simplifies and it has: 
            {\allowdisplaybreaks\small
            \begin{align*}
                0 &\le 
                \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
                + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 \\ &\quad 
                    + \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2
                \\
                &\underset{\text{(h)}}{\le}
                \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
                    \\ &\quad
                    + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                    - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
                \\
                &= (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x)) + F(\bar x) - F(x_k) \\&\quad
                    + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                    - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
                \\
                &\underset{\text{(e)}}{=} 
                (1 - \alpha_k)\left(
                    F(x_{k - 1}) - F(\bar x) 
                    + \frac{L_k\rho_{k - 1}}{L_{k - 1}}\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \right) \\ &\quad
                    + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                \\
                &\le 
                (1 - \alpha_k)\left(
                    F(x_{k - 1}) - F(\bar x) 
                    + \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)
                    \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \right) \\&\quad
                    + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                \\
                &\le (1 - \alpha_k)\left(
                    \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(F(x_{k - 1}) - F(\bar x))
                    + \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)
                    \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \right) \\&\quad 
                    + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                \\
                &= 
                \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(1 - \alpha_k)\left(
                    F(x_{k - 1}) - F(\bar x) 
                    + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \right) \\&\quad
                    + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2. 
            \end{align*}
            }
            Finally for the base case, when $\alpha_0 = 1$, it has $y_0 = v_{-1} = x_{-1}$, and it makes $z_0 = \bar x$ therefore this makes the proximal gradient inequality into:
            \begin{align*}
                0 &\le F(z_0) - F(x_{0}) - \frac{L_0}{2}\Vert z_0 - x_0\Vert^2 + \frac{L_0 - \mu}{2}\Vert z_0 - y_0\Vert^2
                \\
                &= F(\bar x) - F(x_0) - \frac{L_0}{2}\Vert \bar x - x_0\Vert^2 + \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
            \end{align*}

            \par
            Going back to prove the intermediate results, the following will be useful. 
            From Definition \ref{def:st-method} it has for all $k \ge 0$
            \begin{align}\label{thm:onestep-napg-cnvg-i}
                \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}.    
            \tag{i}\end{align}
            Then it has: 
            \begin{align*}\label{thm:onestep-napg-cnvg-j}
                (1 + \tau_k)^{-1}
                &\underset{\eqref{thm:onestep-napg-cnvg-i}}{=} 
                \left(
                    1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
                \right)^{-1} = \left(
                    \frac{L_k\alpha_k - \mu + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
                \right)^{-1}
                = \frac{L_k\alpha_k - \mu}{L_k - \mu}.
            \tag{j}\end{align*}
            And also
            \begin{align*}\label{thm:onestep-napg-cnvg-k}
                \tau_k(1 + \tau_k)^{-1} 
                &\underset{\eqref{thm:onestep-napg-cnvg-i}, \eqref{thm:onestep-napg-cnvg-j}}= 
                \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
                \frac{L_k\alpha_k - \mu}{L_k - \mu}
                = \frac{L_k(1 - \alpha_k)}{L_k - \mu}. 
            \tag{k}\end{align*}
            \textbf{Proof of (d)}
            For all $k \ge 1$, from Definition \ref{def:st-method} it has 
            \begin{align*}
                0 &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1} - y_k
                \\
                &\underset{\eqref{thm:onestep-napg-cnvg-k}}{=} 
                (1 + \tau_k)^{-1} v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k - \mu} x_{k - 1} - y_k
                \\
                &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1} \\ 
                    &\quad 
                    + \left(
                        \frac{L_k(1 - \alpha_k)}{L_k - \mu} - (1 - \alpha_k)
                    \right) x_{k - 1} - y_k
                \\
                &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1}\\
                    &\quad 
                    + (1 - \alpha_k)\left(
                        \frac{L_k}{L_k - \mu} - 1
                    \right) x_{k - 1} - y_k
                \\
                &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1} + 
                \frac{\mu(1 - \alpha_k)}{L - \mu}x_{k - 1} - y_k
                \\
                \iff 
                (1 - \alpha_k)x_{k - 1} - y_k 
                &= - (1 + \tau_k)^{-1}v_{k - 1} - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}.
            \end{align*}
            Recall the definition for $z_k$ at the start of the proof and, use the above results it yields: 
            \begin{align*}
                z_k - y_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
                \\
                &= \alpha_k \bar x - (1 + \tau_k)^{-1}v_{k - 1} - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
                \\
                &\underset{\eqref{thm:onestep-napg-cnvg-j}}{=}
                \alpha_k \bar x - \frac{L_k\alpha_k - \mu}{L_k - \mu}v_{k - 1} 
                - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
                \\
                &= \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
                + \left(
                    \alpha_k - \frac{L_k\alpha_k - \mu}{L_k - \mu}
                \right)\bar x - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
                \\
                &= 
                \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
                +
                \frac{\alpha_kL_k - \alpha_k \mu - L_k\alpha_k + \mu}{L_k - \mu}
                \bar x - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
                \\
                &= \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
                +
                \frac{\mu(1 - \alpha_k)}{L_k - \mu}(\bar x - x_{k - 1}). 
            \end{align*}
            \textbf{Proof of (e)}. 
            The proof is direct using the equality with $x_k$ in Definition \ref{def:st-method}. 
            \begin{align*}
                z_k - x_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
                \\
                &= \alpha_k \bar x + x_{k  1} - x_k - \alpha_k x_{k - 1}
                \\
                &= \alpha_k(\bar x - \alpha_k^{-1}(x_k - x_{k - 1}) - x_{k - 1})
                \\
                &= \alpha_k (\bar x - v_k).
            \end{align*}
            \textbf{Proof of (f)}. 
            The proof is direct and it has: 
            \begin{align*}
                \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} - \frac{\mu\alpha_k(1 - \alpha_k)}{2}
                &= 
                \frac{1}{2(L_k - \mu)}\left(
                    \mu^2(1 - \alpha_k)^2 - (L_k - \mu)\mu \alpha_k(1 - \alpha_k)
                \right)
                \\
                &= \frac{1 - \alpha_k}{2(L_k - \mu)}\left(
                    \mu^2 - \mu^2\alpha_k - (L_k \mu \alpha_k - \mu^2 \alpha_k)
                \right)
                \\
                &= 
                \frac{1 - \alpha_k}{2(L_k - \mu)}\left(
                    \mu^2 - L_k\mu\alpha_k
                \right)
                \\
                &= \frac{(1 - \alpha_k)\mu(\mu - L_k\alpha_k)}{2(L_k - \mu)} 
                \\
                &= \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}. 
            \end{align*}
            \textbf{Proof of (g)}
            The proof is direct: 
            \begin{align*}
                \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} - \frac{\alpha_{k - 1}^2 L \rho_{k - 1}(1 - \alpha_k)}{2}
                &\underset{\text{(c)}}{=} \frac{(L\alpha_k - \mu)^2}{2(L_k - \mu)} - \frac{L_k\alpha_k(\alpha_k - \mu/L_k)}{2}
                \\
                &= \frac{1}{2(L_k - \mu)}\left(
                    (L_k\alpha_k - \mu)^2 - (L_k - \mu)L_k\alpha_k(\alpha_k - \mu/L_k)
                \right)
                \\
                &= 
                \frac{1}{2(L_k - \mu)}\left(
                    (L_k\alpha_k - \mu)^2 - (L_k - \mu)\alpha_k(L_k\alpha_k - \mu)
                \right)
                \\
                &= \frac{L_k\alpha_k - \mu}{2(L_k - \mu)}\left(
                    L_k\alpha_k - \mu - (L - \mu)\alpha_k
                \right)
                \\
                &= \frac{L_k\alpha_k - \mu}{2(L_k - \mu)}\left(
                    \mu\alpha_k - \mu
                \right)
                \\
                &= \frac{(L\alpha_k - \mu)\mu(\alpha_k - 1)}{2(L_k - \mu)}. 
            \end{align*}
            \textbf{Proof of (h)}. 
            For all $k \ge 1$, by (c), the definition of the R-WAPG sequence, $\alpha_k \in (\mu/L_k, 1)$, then it has $L_k\alpha_k \in (\mu, L_k)$, so $L_k\alpha_k - \mu > 0$, and $\alpha_k - 1 < 0$. 
            Finally, we have $L_k \ge \mu$, therefore, the fraction is negative. 
        \end{proof}
    \subsection{stochastic accelerated proximal gradient}
        The following assumption about the objective function is fundamental in incremental gradient method for Machine Learning, data science other similar tasks. 
        \begin{assumption}[sum of many]\label{ass:sum-of-many}
            Define $F := g + (1/n)\sum_{i = 1}^{n} f_i$, assume that $f_i:\RR^n \rightarrow  \RR$ are all $K_i$ smooth and $\mu^{(i)} \ge 0$ strongly convex function and $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function. 
            Consequently, the function $f$ cane be written as $F = g + f$ where $f = (1/n)\sum_{i = 1}^{n} f_i$ and it satisfies Assumption \ref{ass:smooth_plus_nonsmooth} with $L = \max_{i = 1, \ldots, n}K_i$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$. 
        \end{assumption}
        \begin{definition}[SNAPG]\label{def:snapg}

        \end{definition}

\bibliographystyle{siam}

\bibliography{references/refs.bib}

\end{document}

### 2025-07-01 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes to notes

@@
     \subsection{In preparations}
-        \begin{assumption}[Smooth add nonsmooth]\label{ass:smooth_plus_nonsmooth}
+        \begin{assumption}[smooth add nonsmooth]\label{ass:smooth-plus-nonsmooth}
             The function $F = f + g$ where $f:\RR^n \rightarrow \RR$ is a $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
@@
         \end{assumption}
+        \begin{assumption}[admitting minimizers]\label{ass:smooth-plus-nonsmooth-x}
+            Let $F = f + g$ and in addition assume that the set of minimizers $X^+ := \argmin_{x}F(x)$ is non-empty. 
+        \end{assumption}
 
         \begin{definition}[Proximal gradient operator]
-            Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth_plus_nonsmooth}. 
+            Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
             Let $\beta > 0$. 
@@
         \begin{theorem}[proximal gradient inequality]\label{thm:pg-ineq}
-            Let function $F$ satisfies Assumption \ref{ass:smooth_plus_nonsmooth}, so it's $\mu \ge 0$ strongly convex. 
+            Let function $F$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}, so it's $\mu \ge 0$ strongly convex. 
             For all $x\in \RR^n$, define $x^+ = T_L(x)$, then there exists a $B \ge 0$ such that $D_f(x^+, x) \le B/2 \Vert x^+ - x\Vert^2$. 
@@
         \begin{theorem}[one step convergence claim of NAPG]\label{thm:onestep-napg-cnvg}
-            Let $F = f + g$ satisfies Assumption \ref{ass:smooth_plus_nonsmooth} for some $L > \mu \ge 0$. 
+            Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth} for some $L > \mu \ge 0$. 
             Let the sequence $(\alpha_k)_{k \ge0}$ be an R-WAPG sequence (Definition \ref{def:rwapg-seq}). 
@@
             \begin{itemize}
-                \item [(a)] Theorem \ref{thm:pg-ineq}, with $z = z_k$, $k \ge 0$. We can use it because $F = f + g$ satisfies Assumption \ref{ass:smooth_plus_nonsmooth} . 
+                \item [(a)] Theorem \ref{thm:pg-ineq}, with $z = z_k$, $k \ge 0$. We can use it because $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth} . 
                 \item [(b)] Jensen's inequality (Theorem \ref{thm:jesen}), with $z = z_k$, for $k \ge 0$. We can use it because $F$ is $\mu \ge 0$ strongly convex. 
@@
         \begin{assumption}[sum of many]\label{ass:sum-of-many}
-            Define $F := g + (1/n)\sum_{i = 1}^{n} f_i$, assume that $f_i:\RR^n \rightarrow  \RR$ are all $K_i$ smooth and $\mu^{(i)} \ge 0$ strongly convex function and $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function.
-            Consequently, the function $f$ cane be written as $F = g + f$ where $f = (1/n)\sum_{i = 1}^{n} f_i$ and it satisfies Assumption \ref{ass:smooth_plus_nonsmooth} with $L = \max_{i = 1, \ldots, n}K_i$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$.
+            Define $F := g + (1/n)\sum_{i = 1}^{n} f_i$, assume that $f_i:\RR^n \rightarrow  \RR$ are all $K_i$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K_i > \mu^{(i)}$ and, $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function.
+            Consequently, the function $f$ cane be written as $F = g + f$ where $f = (1/n)\sum_{i = 1}^{n} f_i$ and it satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = \max_{i = 1, \ldots, n}K_i$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$.
         \end{assumption}
+        This assumption is stronger than Assumption \ref{ass:smooth-plus-nonsmooth}. 
+        The interpolation hypothesis from Machine Learning stated that the model has the capacity to perfect fit all the observed data. 
+        \begin{assumption}[interpolation hypothesis]\label{ass:interp-hypothesis}
+            Suppose that $F := f + (1/n)\sum_{i = 1}^{n} f_i$ satsifying Assumption \ref{ass:sum-of-many}. 
+            In addition, assuming that it has $0 = \inf_{x}F(x)$ and, there exists some $\bar x \in \RR^n$ such that for all $i = 1, \ldots, n$ it satisfies $0 = f_i(\bar x)$. 
+            Obviously, all such $\bar x$ forms the set of minimizers of $F$. 
+        \end{assumption}
+
         \begin{definition}[SNAPG]\label{def:snapg}
+            Let $F$ satisfies Assumption \ref{ass:sum-of-many}. 
+            Let $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$. 
+            Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
+            The SAGD generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
+            \begin{align*}
+                & L_k/L_{k - 1}(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu^{(I_k)}/L_k\right), \\
+                & \tau_k = L_k(1 - \alpha_k)\left(L_\alpha \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
+                & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
+                & x_k =  T_{L_k}(y_k | F_{I_k}) \text{ s.t: } D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
+                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
+            \end{align*}
+        \end{definition}
+        \begin{remark}
+            The sequence $\alpha_k$ is a random variable because it changes according to variable $I_k$ at the current iteration.
+            This decision is made because if Theorem \ref{thm:pg-ineq} needs to hold during each iteration of the algorithm.
+        \end{remark}
 
-        \end{definition}
+        \begin{theorem}[SNAPG one step inequality]\label{thm:snapg-one-step}
+
+        \end{theorem}
 

### 2025-07-02 Notebook LaTEX/SAGD Under Interpolation/main-2025-06-30.tex
>w<, changes

--- 2025-07-01 Notebook LaTEX/SAGD Under Interpolation/main.tex
@@
 
+% special operators and stuff introduced for this file.
+
+\newcommand{\cov}{\ensuremath{\operatorname{Cov}}}
+
 \begin{document}
-
 \title{{\fontfamily{ptm}\selectfont Lorum ipsum}}
@@
         \begin{remark}
-            If, $f$ is $\mu \ge 0$ strongy convex and $L$ Lipschitz smooth then, its Bregman Divergence has for all $x, y \in \RR^n$: $\mu/2 \Vert x - y\Vert^2 \le D_f(x, y) \le L/2 \Vert x - y\Vert^2$.
+            If, $f$ is $\mu \ge 0$ strongly convex and $L$ Lipschitz smooth then, its Bregman Divergence has for all $x, y \in \RR^n$: $\mu/2 \Vert x - y\Vert^2 \le D_f(x, y) \le L/2 \Vert x - y\Vert^2$.
         \end{remark}
@@
             Suppose that the base case $v_{-1}, x_{k - 1}\in \RR^n$ is given to initialize the algorithm. 
-            Then the algorithm produces the sequence of iterates $(y_k, x_k, v_k)_{k \ge 0}$ and auxilary parameter sequence $L_k, \tau_k$ satisfying these inequalities: 
+            Then the algorithm produces the sequence of iterates $(y_k, x_k, v_k)_{k \ge 0}$ and auxiliary parameter sequence $L_k, \tau_k$ satisfying these inequalities: 
             \begin{align*}
@@
             \end{align*}
-            Since $f$ is assumed to be $L$ Lispchitz smooth, the above condition is true for all $x, y \in \RR^n$ for all $B \ge L$. 
+            Since $f$ is assumed to be $L$ Lipschitz smooth, the above condition is true for all $x, y \in \RR^n$ for all $B \ge L$. 
         \end{theorem}
@@
             The theorem is the same as in Nesterov's book \cite[Theorem 2.2.13]{nesterov_lectures_2018}, but with the use of proximal gradient mapping and proximal gradient instead of project gradient hence making it equivalent to the theorem in Beck's book \cite[Theorem 10.16]{beck_first-order_2017}.
-            The only generalization here is parameter $B$ which made to accomodate algorithm that implements Definition \ref{def:st-method} with some line search routine. 
+            The only generalization here is parameter $B$ which made to accommodate algorithm that implements Definition \ref{def:st-method} with some line search routine. 
         \end{remark}
@@
         It's made in acknowledgement of Algorithm 2.2.36 in Nesterov's book \cite{nesterov_lectures_2018} and its extension known as FISTA in the literature.
-        The following theorem provide a complete proof for the convergence rate of algorithms implementing Definition \ref{def:st-method}, which is equivalent to NAG, or NAPG. 
-        It made use of Definition \ref{def:rwapg-seq} which accomodates a relaxed sequence compared to the usual sequence that gives the optimal convergence rate. 
+        The following theorem provides a complete proof for the convergence rate of algorithms implementing Definition \ref{def:st-method}, which is equivalent to NAG, or NAPG. 
+        It made use of Definition \ref{def:rwapg-seq} which accommodates a relaxed sequence compared to the usual sequence that gives the optimal convergence rate. 
         \begin{theorem}[one step convergence claim of NAPG]\label{thm:onestep-napg-cnvg}
@@
         \begin{proof}
-            The proof is very intense algebratically hence before we step into it, we present the following intermediate results in advance to their proofs given at the end. 
+            The proof is very intense algebraically hence before we step into it, we present the following intermediate results in advance to their proofs given at the end. 
             \par
@@
             \begin{itemize}
-                \item [(a)] Theorem \ref{thm:pg-ineq}, with $z = z_k$, $k \ge 0$. We can use it because $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth} . 
+                \item [(a)] Theorem \ref{thm:pg-ineq}, with $z = z_k$, $k \ge 0$. We can use it because $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
                 \item [(b)] Jensen's inequality (Theorem \ref{thm:jesen}), with $z = z_k$, for $k \ge 0$. We can use it because $F$ is $\mu \ge 0$ strongly convex. 
                 \item [(c)] Definition \ref{def:rwapg-seq} which has $\rho_k(1 - \alpha_{k + 1})\alpha_k^2 = \alpha_{k + 1}(\alpha_{k + 1} - \mu/L_k)$ for $k \ge 0$.
-                \item [(d)] The equality $z_k - y_k = (L_k - \mu)^{-1}((L_k\alpha_k - \mu)(\bar x - v_k) + \mu(1 - \alpha_k)(\bar x - x_{k - 1}))$ for all $k \ge 0$. 
-                \item [(e)] The equality $z_k - x_k = \alpha_k(\bar x - v_k)$ for all $k \ge 0$. 
-                \item [(f)] The following equality: 
+                \item [(d)] The equality $z_k - y_k = (L_k - \mu)^{-1}((L_k\alpha_k - \mu)(\bar x - v_k) + \mu(1 - \alpha_k)(\bar x - x_{k - 1}))$ for all $k \ge 0$, it comes from Definition \ref{def:st-method}.
+                \item [(e)] The equality $z_k - x_k = \alpha_k(\bar x - v_k)$ for all $k \ge 0$ it comes from Definition \ref{def:st-method}. 
+                \item [(f)] Using basic algebra, we have the following equality: 
                 \begin{align*}
@@
                 \end{align*}
-                \item [(g)] The following equality: 
+                \item [(g)] Using (c), we have the following equality: 
                 \begin{align*}
@@
                 \end{align*}
-                \item [(h)] The equality: 
+                \item [(h)] Definition \ref{def:rwapg-seq} determine the inequality: 
                 \begin{align*}
@@
                 &- \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
-                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2
+                + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2
                 \\
                 &\underset{\text{(d)}}{=} 
-                -\frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
-                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2\\ 
+                -\frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2\\ 
                     &\quad +
@@
                 &= 
-                - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
-                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-                \\
-                &\quad + 
-                    \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} \Vert \bar x - v_{k - 1}\Vert^2
+                - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2\\&\quad 
+                    + \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} \Vert \bar x - v_{k - 1}\Vert^2
                     + \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} \Vert \bar x - x_{k - 1}\Vert^2
@@
                     - \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}
-                \right)\Vert \bar x - v_{k - 1}\Vert^2
-                \\ &\quad 
+                \right)\Vert \bar x - v_{k - 1}\Vert^2 \\ &\quad 
                     + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                    - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
                     + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
@@
                     + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                    - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
                     + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
                 \\
-                &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-                \\ & \quad
+                &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2 \\ & \quad
                     \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\left(
@@
                 &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
                 + \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2. 
@@
             }
-            The inequality from previously simplifies and it has: 
+            The inequality from previously simplifies, and it has: 
             {\allowdisplaybreaks\small
@@
             }
-            Finally for the base case, when $\alpha_0 = 1$, it has $y_0 = v_{-1} = x_{-1}$, and it makes $z_0 = \bar x$ therefore this makes the proximal gradient inequality into:
+            Finally, for the base case, when $\alpha_0 = 1$, it has $y_0 = v_{-1} = x_{-1}$, and it makes $z_0 = \bar x$ therefore this makes the proximal gradient inequality into:
             \begin{align*}
@@
             \begin{align*}
-                \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} - \frac{\alpha_{k - 1}^2 L \rho_{k - 1}(1 - \alpha_k)}{2}
+                \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} - \frac{\alpha_{k - 1}^2 L_k \rho_{k - 1}(1 - \alpha_k)}{2}
                 &\underset{\text{(c)}}{=} \frac{(L\alpha_k - \mu)^2}{2(L_k - \mu)} - \frac{L_k\alpha_k(\alpha_k - \mu/L_k)}{2}
@@
         \end{proof}
+
     \subsection{stochastic accelerated proximal gradient}
@@
         \begin{assumption}[sum of many]\label{ass:sum-of-many}
-            Define $F := g + (1/n)\sum_{i = 1}^{n} f_i$, assume that $f_i:\RR^n \rightarrow  \RR$ are all $K_i$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K_i > \mu^{(i)}$ and, $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function.
-            Consequently, the function $f$ cane be written as $F = g + f$ where $f = (1/n)\sum_{i = 1}^{n} f_i$ and it satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = \max_{i = 1, \ldots, n}K_i$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$.
+            Define $F := g + (1/n)\sum_{i = 1}^{n} f_i$, assume that $f_i:\RR^n \rightarrow  \RR$ are all $K^{(i)}$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K^{(i)} > \mu^{(i)}$ and, $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function.
+            Consequently, the function $f$ cane be written as $F = g + f$ where $f = (1/n)\sum_{i = 1}^{n} f_i$ and, it satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = \max_{i = 1, \ldots, n}K^{(i)}$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$.
         \end{assumption}
@@
         \begin{assumption}[interpolation hypothesis]\label{ass:interp-hypothesis}
-            Suppose that $F := f + (1/n)\sum_{i = 1}^{n} f_i$ satsifying Assumption \ref{ass:sum-of-many}. 
+            Suppose that $F := f + (1/n)\sum_{i = 1}^{n} f_i$ satisfying Assumption \ref{ass:sum-of-many}. 
             In addition, assuming that it has $0 = \inf_{x}F(x)$ and, there exists some $\bar x \in \RR^n$ such that for all $i = 1, \ldots, n$ it satisfies $0 = f_i(\bar x)$. 
@@
 
-        \begin{definition}[SNAPG]\label{def:snapg}
+        \begin{definition}[SNAPG-V1 \textcolor{red}{DOESN'T WORK WELL}]\;\label{def:snapg-v1}\\
             Let $F$ satisfies Assumption \ref{ass:sum-of-many}. 
@@
             Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
-            The SAGD generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
+            The SNAPG generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
             \begin{align*}
-                & L_k/L_{k - 1}(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu^{(I_k)}/L_k\right), \\
-                & \tau_k = L_k(1 - \alpha_k)\left(L_\alpha \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
+                & (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu^{(I_k)}/L_k\right), \\
+                & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
                 & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
@@
 
-        \begin{theorem}[SNAPG one step inequality]\label{thm:snapg-one-step}
+        \begin{theorem}[SNAPG one step inequality \textcolor{red}{INVALIDATED}]
+            Let sequences of iterates $(y_k, x_k, v_k)_{k \ge 0}$ satisfy SNAPG (Definition \ref{def:snapg-v1}). 
+            Denote $\mathbb E_k [\cdot]$ to be the conditional expectation on $I_{0}, I_1, \ldots, I_{k - 1}$. 
+            Then, for all $k \ge 1$ the following inequality is true: 
+            $$
+            \begin{aligned}
+            & - F(\bar x) + 
+            \mathbb E_k \left[
+                F_{I_k}(x_k)
+            \right]
+            + \mathbb E_k
+            \left[
+                \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
+            \right]
+            \\
+            &\le (1 - \mathbb E_k [\alpha_k])
+            \left(
+                \mathbb E \left[F(x_{k - 1})\right]
+                - 
+                F(\bar x)
+                + 
+                \mathbb E_k 
+                \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2\right]
+            \right).
+            \end{aligned}
+            $$
+        \end{theorem}
+        \begin{proof}
+            For one step, a specific function $F_{I_k}$ is sampled. 
+            $F_{I_k}$ is $K^{(I_k)} > \mu^{(I_k)} \ge 0$ strongly convex and smooth. 
+            The iterates $x_k, v_k$ is a function of random variable $I_k$, conditioned on all $I_{k - 1}, I_{k - 2}, \ldots , I_0$
+            The sequence $\alpha_k$ is a sequence of random variable and, the relations between $\alpha_k, \alpha_{k - 1}$ is given by: 
+            \begin{align*}
+                \alpha_k &= 
+                \frac{1}{2}\left(
+                    -\frac{L_{k - 1}\alpha_{k - 1}^2}{L_k} + \frac{\mu^{(I_k)}}{L_k} 
+                    + \sqrt{
+                        \left(
+                            \frac{\mu^{(I_k)}}{L_k}
+                            - \frac{\alpha_{k - 1}^2L_{k - 1}}{L_k}
+                        \right)^2
+                        + \frac{\alpha_{k - 1}4L_{k - 1}}{L_k}
+                    }
+                \right). 
+            \end{align*}
+            The relationship $(L_{k - 1}/L_k)(1 - \alpha_k)\alpha_{k - 1}^2 = \alpha_k(\alpha_k - \mu^{(I_k)}/L_k)$ is an instance of Definition \ref{def:rwapg-seq} where $\rho_{k - 1} = L_{k - 1}/L_k$.
+            Therefore, the one-step convergence result of \ref{thm:onestep-napg-cnvg} applies to function $F_{I_k}$ with sequence $\alpha_k$ and, it yields: 
+            \begin{align*}
+                & - F_{I_k}(\bar x) + F_{I_k}(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+                \\
+                & \le 
+                (1 - \alpha_k)\left(
+                    F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
+                    + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                \right). 
+            \end{align*}
+            We take the conditional expectation on the LHS and, it has 
+            \begin{align*}
+                & \mathbb E_k 
+                \left[
+                    - F_{I_k}(\bar x) + F_{I_k}(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
+                \right]
+                \\
+                &= 
+                \mathbb E_k \left[- F_{I_k}(\bar x)\right]
+                + 
+                \mathbb E_k \left[F_{I_k}(x_k)\right]
+                + 
+                \mathbb E_k \left[
+                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
+                \right]
+                \\
+                &\underset{\text{(a)}}{=} 
+                - F(\bar x) + 
+                \mathbb E_k \left[
+                    F_{I_k}(x_k)
+                \right]
+                + \mathbb E_k
+                \left[
+                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
+                \right]. 
+            \end{align*}
+            At label (a), we make use of interpolation hypothesis which makes $\mathbb E_k[F_{I_k}(\bar x)] = F(\bar x)$. 
+            Next, taking the conditional expectation on the RHS it has 
+            \begin{align*}
+                & \mathbb E_k\left[
+                    (1 - \alpha_k)
+                    \left(
+                    F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
+                    + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                    \right)
+                \right]
+                \\
+                &\underset{\text{(b)}}{=}
+                \mathbb E_k\left[1 - \alpha_k\right]
+                \mathbb E_k
+                    \left[
+                        F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
+                        + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                    \right]
+                \\
+                &\neq 
+                \mathbb E_k
+                \left[1 - \alpha_k\right]
+                \left(
+                \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] - F(\bar x)
+                    + 
+                    \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2\right]
+                \right). 
+            \end{align*}
+            At (b), we need to make use of covariance between the two random variable... 
+            Consider random variables $X_k = (1 - \alpha_k)$ and $Y_k = F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \alpha_{k - 1}L_{k - 1}/2\Vert \bar x - v_{k - 1}\Vert^2$ which are functions of $I_k$ conditioned on $\alpha_{k - 1}$ and, $x_{k - 1}, v_{k - 1}$.
+            The conditional expectation of their product has $\mathbb E_k[X_kY_k] = \mathbb E_k[X_k] \mathbb E_k[Y_k] + \cov[X_k, Y_k]$.
+            \textcolor{red}{Hence, taking the expectation doesn't follow. }
+
+        \end{proof}
+
+        \begin{definition}[SNAPG-V2]\label{def:snapg-v2}
+            Let $F$ satisfies Assumption \ref{ass:sum-of-many}. 
+            Let $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$. 
+            Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
+            The SNAPG generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
+            \begin{align*}
+                & (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right), \\
+                & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
+                & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
+                & x_k =  T_{L_k}(y_k | F_{I_k}) \text{ s.t: } D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
+                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
+            \end{align*}
+        \end{definition}
+
+        \begin{theorem}[SNAPG-V2 one step convergence]
 
         \end{theorem}
+        \begin{proof}
+            Let's suppose that $I_k = i$ and, for all $k \ge 0$ let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ where $\bar x$ is a minimizer of $F$. 
+            From Definiton \ref{def:snapg-v2}, it has
+            \begin{align*}
+                (1 + \tau_k)^{-1}
+                &\underset{\eqref{thm:onestep-napg-cnvg-i}}{=} 
+                \left(
+                    1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
+                \right)^{-1} = \left(
+                    \frac{L_k\alpha_k - \mu^{(i)} + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
+                \right)^{-1}
+                = \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}. 
+            \end{align*}
+            Therefore, for all $k \ge 0$ $y_k$ has 
+            \begin{align*}
+                y_k &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1}
+                \\
+                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} 
+                \left(
+                    v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}} x_{k - 1}
+                \right)
+                \\
+                &= 
+            \end{align*}
+        \end{proof}
 

### 2025-07-02 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
 
-        \begin{theorem}[SNAPG one step inequality]\label{thm:snapg-one-step}
+        \begin{theorem}[SNAPG one step inequality \textcolor{red}{INVALIDATED}]
+            Let sequences of iterates $(y_k, x_k, v_k)_{k \ge 0}$ satisfy SNAPG (Definition \ref{def:snapg-v1}). 
+            Denote $\mathbb E_k [\cdot]$ to be the conditional expectation on $I_{0}, I_1, \ldots, I_{k - 1}$. 
+            Then, for all $k \ge 1$ the following inequality is true: 
+            $$
+            \begin{aligned}
+            & - F(\bar x) + 
+            \mathbb E_k \left[
+                F_{I_k}(x_k)
+            \right]
+            + \mathbb E_k
+            \left[
+                \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
+            \right]
+            \\
+            &\le (1 - \mathbb E_k [\alpha_k])
+            \left(
+                \mathbb E \left[F(x_{k - 1})\right]
+                - 
+                F(\bar x)
+                + 
+                \mathbb E_k 
+                \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2\right]
+            \right).
+            \end{aligned}
+            $$
+        \end{theorem}
+        \begin{proof}
+            For one step, a specific function $F_{I_k}$ is sampled. 
+            $F_{I_k}$ is $K^{(I_k)} > \mu^{(I_k)} \ge 0$ strongly convex and smooth. 
+            The iterates $x_k, v_k$ is a function of random variable $I_k$, conditioned on all $I_{k - 1}, I_{k - 2}, \ldots , I_0$
+            The sequence $\alpha_k$ is a sequence of random variable and, the relations between $\alpha_k, \alpha_{k - 1}$ is given by: 
+            \begin{align*}
+                \alpha_k &= 
+                \frac{1}{2}\left(
+                    -\frac{L_{k - 1}\alpha_{k - 1}^2}{L_k} + \frac{\mu^{(I_k)}}{L_k} 
+                    + \sqrt{
+                        \left(
+                            \frac{\mu^{(I_k)}}{L_k}
+                            - \frac{\alpha_{k - 1}^2L_{k - 1}}{L_k}
+                        \right)^2
+                        + \frac{\alpha_{k - 1}4L_{k - 1}}{L_k}
+                    }
+                \right). 
+            \end{align*}
+            The relationship $(L_{k - 1}/L_k)(1 - \alpha_k)\alpha_{k - 1}^2 = \alpha_k(\alpha_k - \mu^{(I_k)}/L_k)$ is an instance of Definition \ref{def:rwapg-seq} where $\rho_{k - 1} = L_{k - 1}/L_k$.
+            Therefore, the one-step convergence result of \ref{thm:onestep-napg-cnvg} applies to function $F_{I_k}$ with sequence $\alpha_k$ and, it yields: 
+            \begin{align*}
+                & - F_{I_k}(\bar x) + F_{I_k}(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+                \\
+                & \le 
+                (1 - \alpha_k)\left(
+                    F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
+                    + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                \right). 
+            \end{align*}
+            We take the conditional expectation on the LHS and, it has 
+            \begin{align*}
+                & \mathbb E_k 
+                \left[
+                    - F_{I_k}(\bar x) + F_{I_k}(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
+                \right]
+                \\
+                &= 
+                \mathbb E_k \left[- F_{I_k}(\bar x)\right]
+                + 
+                \mathbb E_k \left[F_{I_k}(x_k)\right]
+                + 
+                \mathbb E_k \left[
+                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
+                \right]
+                \\
+                &\underset{\text{(a)}}{=} 
+                - F(\bar x) + 
+                \mathbb E_k \left[
+                    F_{I_k}(x_k)
+                \right]
+                + \mathbb E_k
+                \left[
+                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
+                \right]. 
+            \end{align*}
+            At label (a), we make use of interpolation hypothesis which makes $\mathbb E_k[F_{I_k}(\bar x)] = F(\bar x)$. 
+            Next, taking the conditional expectation on the RHS it has 
+            \begin{align*}
+                & \mathbb E_k\left[
+                    (1 - \alpha_k)
+                    \left(
+                    F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
+                    + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                    \right)
+                \right]
+                \\
+                &\underset{\text{(b)}}{=}
+                \mathbb E_k\left[1 - \alpha_k\right]
+                \mathbb E_k
+                    \left[
+                        F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
+                        + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                    \right]
+                \\
+                &\neq 
+                \mathbb E_k
+                \left[1 - \alpha_k\right]
+                \left(
+                \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] - F(\bar x)
+                    + 
+                    \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2\right]
+                \right). 
+            \end{align*}
+            At (b), we need to make use of covariance between the two random variable... 
+            Consider random variables $X_k = (1 - \alpha_k)$ and $Y_k = F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \alpha_{k - 1}L_{k - 1}/2\Vert \bar x - v_{k - 1}\Vert^2$ which are functions of $I_k$ conditioned on $\alpha_{k - 1}$ and, $x_{k - 1}, v_{k - 1}$.
+            The conditional expectation of their product has $\mathbb E_k[X_kY_k] = \mathbb E_k[X_k] \mathbb E_k[Y_k] + \cov[X_k, Y_k]$.
+            \textcolor{red}{Hence, taking the expectation doesn't follow. }
+
+        \end{proof}
+
+        \begin{definition}[SNAPG-V2]\label{def:snapg-v2}
+            Let $F$ satisfies Assumption \ref{ass:sum-of-many}. 
+            Let $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$. 
+            Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
+            The SNAPG generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
+            \begin{align*}
+                & (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right), \\
+                & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
+                & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
+                & x_k =  T_{L_k}(y_k | F_{I_k}) \text{ s.t: } D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
+                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
+            \end{align*}
+        \end{definition}
+
+        \begin{theorem}[SNAPG-V2 one step convergence]
 
         \end{theorem}
+        \begin{proof}
+            Let's suppose that $I_k = i$ and, for all $k \ge 0$ let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ where $\bar x$ is a minimizer of $F$. 
+            \begin{itemize}
+                \item[(a)] We can use proximal gradient inequality from Theorem \ref{thm:pg-ineq} with $z = z_k$ because each $F_i$ is $K_i$ Lipschitz smooth and, $\mu^{(i)}$ strongly convex with $K_i \ge \mu^{(i)}$.
+                \item[(b)] We can use Jesen's inequality of Theorem \ref{thm:jesen} with $z = z_k$ on $F_i$. 
+                \item[(c)] The sequence $(\alpha_k)_{k \ge 0}$ has $(L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right)$.
+It is a special case of Definition \ref{def:rwapg-seq} with $\rho_{k - 1} = L_{k - 1}/L_k$.
+            \end{itemize}
+            % INTERMEDIATE RESULTS
+            \par
+            From Definiton \ref{def:snapg-v2}, it has
+            \begin{align*}
+                (1 + \tau_k)^{-1}
+                &\underset{\eqref{thm:onestep-napg-cnvg-i}}{=} 
+                \left(
+                    1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
+                \right)^{-1} = \left(
+                    \frac{L_k\alpha_k - \mu^{(i)} + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
+                \right)^{-1}
+                = \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}. 
+            \end{align*}
+            Therefore, for all $k \ge 0$ $y_k$ has 
+            \begin{align*}
+                0 &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1} - y_k
+                \\
+                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} 
+                \left(
+                    v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}} x_{k - 1}
+                \right) - y_k
+                \\
+                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1}
+                + \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1} - y_k
+                \\
+                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+                + 
+                \left(
+                    \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} - (1 - \alpha_k)
+                \right) x_{k - 1} - y_k
+                \\
+                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+                + 
+                (1 - \alpha_k)\left(
+                    \frac{L_k - L_k + \mu^{(i)}}{L_k - \mu^{(i)}}
+                \right) x_{k - 1} - y_k
+                \\
+                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+                + 
+                \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}x_{k - 1} - y_k. 
+            \end{align*}
+            Therefore, we establish the equality 
+            \begin{align*}
+                (1 - \alpha_k)x_{k - 1} - y_k &= 
+                - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
+                - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}. 
+            \end{align*}
+            Using the above, we have 
+            \begin{align*}
+                z_k - y_k &= 
+                \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
+                \\
+                &= \alpha_k \bar x 
+                - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
+                - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
+                \\
+                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+                + \left(
+                    \alpha_k - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}
+                \right)\bar x
+                - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
+                \\
+                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+                + \left(
+                    \frac{\alpha_kL_k - \alpha_k \mu^{(i)} - L_k\alpha_k + \mu^{(i)}}{L_k - \mu^{(i)}}
+                \right)\bar x
+                - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
+                \\
+                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+                + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}\bar x
+                - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
+                \\
+                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+                + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
+            \end{align*}
+            % INTERMEDIATE RESULTS
+            From Definition \ref{def:snapg-v2} it has directly: 
+            \begin{align*}
+                z_k - x_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
+                \\
+                &= \alpha_k \bar x + x_{k  1} - x_k - \alpha_k x_{k - 1}
+                \\
+                &= \alpha_k(\bar x - \alpha_k^{-1}(x_k - x_{k - 1}) - x_{k - 1})
+                \\
+                &= \alpha_k (\bar x - v_k).
+            \end{align*}
+            % INTERMEDIATE RESULTS
+            The proof is direct algebra and it has: 
+            {\small\allowdisplaybreaks
+            \begin{align*}
+                & \frac{\left(\mu^{(i)}\right)^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} 
+                - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
+                \\
+                &= 
+                \frac{1}{2\left(L_k - \mu^{(i)}\right)}
+                \left(
+                    \left(\mu^{(i)}\right)^2(1 - \alpha_k)^2
+                    - \left(L_k - \mu^{(i)}\right)\mu^{(i)} \alpha_k(1 - \alpha_k)
+                \right)
+                \\
+                &= \frac{1 - \alpha_k}{2\left(L_k - \mu^{(i)}\right)}\left(
+                    \left(\mu^{(i)}\right)^2 
+                    - \left(\mu^{(i)}\right)^2\alpha_k 
+                    - \left(L_k \mu^{(i)} \alpha_k - \left(\mu^{(i)}\right)^2 \alpha_k\right)
+                \right)
+                \\
+                &= 
+                \frac{1 - \alpha_k}{2(L_k - \mu)}\left(
+                    \left(\mu^{(i)}\right)^2 - L_k\left(\mu^{(i)}\right)\alpha_k
+                \right)
+                \\
+                &= 
+                \frac{(1 - \alpha_k)\mu^{(i)}\left(\mu^{(i)} - L_k\alpha_k\right)}
+                {2\left(L_k - \mu^{(i)}\right)}
+                \\
+                &= \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
+                {2\left(L_k - \mu^{(i)}\right)}. 
+            \end{align*}
+            }
+            % INTERMEDIATE RESULTS 
+            From the property of the sequence stated in item (c), we have: 
+            \begin{align*}
+                &\frac{\left(
+                    L_k\alpha_k - \mu^{(i)}
+                \right)^2}{L_k - \mu^{(i)}} 
+                -
+                \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} 
+                \\
+                &= 
+                \frac{\left(
+                    L_k\alpha_k - \mu^{(i)}
+                \right)^2}{L_k - \mu^{(i)}} 
+                -
+                \frac{L_k\alpha_k(\alpha_k - \mu/L_k)}{2} 
+                \\
+                &=
+                \frac{\left(
+                    L_k\alpha_k - \mu^{(i)}
+                \right)^2}{L_k - \mu^{(i)}} 
+                - \frac{L_k\alpha_k(\alpha_k - \mu^{(i)}/L_k)}{2}
+                + \frac{L_k\alpha_k(\alpha_k - \mu^{(i)}/L_k)}{2} 
+                - \frac{L_k\alpha_k(\alpha_k - \mu/L_k)}{2} 
+                \\
+                &= 
+                \frac{\left(
+                    L_k\alpha_k - \mu^{(i)}
+                \right)^2}{L_k - \mu^{(i)}} 
+                - \frac{\alpha_k(L_k\alpha_k - \mu^{(i)})}{2}
+                + \frac{L_k\alpha_k}{2}
+                \frac{\left(
+                    \mu - \mu^{(i)}
+                \right)}{L_k}
+                \\
+                &= 
+            \end{align*}
+        \end{proof}
 

### 2025-07-02 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
 
-        \begin{definition}[SNAPG-V1 \textcolor{red}{DOESN'T WORK WELL}]\;\label{def:snapg-v1}\\
-            Let $F$ satisfies Assumption \ref{ass:sum-of-many}. 
-            Let $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$. 
-            Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
-            The SNAPG generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
-            \begin{align*}
-                & (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu^{(I_k)}/L_k\right), \\
-                & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
-                & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
-                & x_k =  T_{L_k}(y_k | F_{I_k}) \text{ s.t: } D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
-                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
-            \end{align*}
-        \end{definition}
-        \begin{remark}
-            The sequence $\alpha_k$ is a random variable because it changes according to variable $I_k$ at the current iteration.
-            This decision is made because if Theorem \ref{thm:pg-ineq} needs to hold during each iteration of the algorithm.
-        \end{remark}
-
-        \begin{theorem}[SNAPG one step inequality \textcolor{red}{INVALIDATED}]
-            Let sequences of iterates $(y_k, x_k, v_k)_{k \ge 0}$ satisfy SNAPG (Definition \ref{def:snapg-v1}). 
-            Denote $\mathbb E_k [\cdot]$ to be the conditional expectation on $I_{0}, I_1, \ldots, I_{k - 1}$. 
-            Then, for all $k \ge 1$ the following inequality is true: 
-            $$
-            \begin{aligned}
-            & - F(\bar x) + 
-            \mathbb E_k \left[
-                F_{I_k}(x_k)
-            \right]
-            + \mathbb E_k
-            \left[
-                \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
-            \right]
-            \\
-            &\le (1 - \mathbb E_k [\alpha_k])
-            \left(
-                \mathbb E \left[F(x_{k - 1})\right]
-                - 
-                F(\bar x)
-                + 
-                \mathbb E_k 
-                \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2\right]
-            \right).
-            \end{aligned}
-            $$
-        \end{theorem}
-        \begin{proof}
-            For one step, a specific function $F_{I_k}$ is sampled. 
-            $F_{I_k}$ is $K^{(I_k)} > \mu^{(I_k)} \ge 0$ strongly convex and smooth. 
-            The iterates $x_k, v_k$ is a function of random variable $I_k$, conditioned on all $I_{k - 1}, I_{k - 2}, \ldots , I_0$
-            The sequence $\alpha_k$ is a sequence of random variable and, the relations between $\alpha_k, \alpha_{k - 1}$ is given by: 
-            \begin{align*}
-                \alpha_k &= 
-                \frac{1}{2}\left(
-                    -\frac{L_{k - 1}\alpha_{k - 1}^2}{L_k} + \frac{\mu^{(I_k)}}{L_k} 
-                    + \sqrt{
-                        \left(
-                            \frac{\mu^{(I_k)}}{L_k}
-                            - \frac{\alpha_{k - 1}^2L_{k - 1}}{L_k}
-                        \right)^2
-                        + \frac{\alpha_{k - 1}4L_{k - 1}}{L_k}
-                    }
-                \right). 
-            \end{align*}
-            The relationship $(L_{k - 1}/L_k)(1 - \alpha_k)\alpha_{k - 1}^2 = \alpha_k(\alpha_k - \mu^{(I_k)}/L_k)$ is an instance of Definition \ref{def:rwapg-seq} where $\rho_{k - 1} = L_{k - 1}/L_k$.
-            Therefore, the one-step convergence result of \ref{thm:onestep-napg-cnvg} applies to function $F_{I_k}$ with sequence $\alpha_k$ and, it yields: 
-            \begin{align*}
-                & - F_{I_k}(\bar x) + F_{I_k}(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-                \\
-                & \le 
-                (1 - \alpha_k)\left(
-                    F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
-                    + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                \right). 
-            \end{align*}
-            We take the conditional expectation on the LHS and, it has 
-            \begin{align*}
-                & \mathbb E_k 
-                \left[
-                    - F_{I_k}(\bar x) + F_{I_k}(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
-                \right]
-                \\
-                &= 
-                \mathbb E_k \left[- F_{I_k}(\bar x)\right]
-                + 
-                \mathbb E_k \left[F_{I_k}(x_k)\right]
-                + 
-                \mathbb E_k \left[
-                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
-                \right]
-                \\
-                &\underset{\text{(a)}}{=} 
-                - F(\bar x) + 
-                \mathbb E_k \left[
-                    F_{I_k}(x_k)
-                \right]
-                + \mathbb E_k
-                \left[
-                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
-                \right]. 
-            \end{align*}
-            At label (a), we make use of interpolation hypothesis which makes $\mathbb E_k[F_{I_k}(\bar x)] = F(\bar x)$. 
-            Next, taking the conditional expectation on the RHS it has 
-            \begin{align*}
-                & \mathbb E_k\left[
-                    (1 - \alpha_k)
-                    \left(
-                    F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
-                    + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                    \right)
-                \right]
-                \\
-                &\underset{\text{(b)}}{=}
-                \mathbb E_k\left[1 - \alpha_k\right]
-                \mathbb E_k
-                    \left[
-                        F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
-                        + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                    \right]
-                \\
-                &\neq 
-                \mathbb E_k
-                \left[1 - \alpha_k\right]
-                \left(
-                \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] - F(\bar x)
-                    + 
-                    \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2\right]
-                \right). 
-            \end{align*}
-            At (b), we need to make use of covariance between the two random variable... 
-            Consider random variables $X_k = (1 - \alpha_k)$ and $Y_k = F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \alpha_{k - 1}L_{k - 1}/2\Vert \bar x - v_{k - 1}\Vert^2$ which are functions of $I_k$ conditioned on $\alpha_{k - 1}$ and, $x_{k - 1}, v_{k - 1}$.
-            The conditional expectation of their product has $\mathbb E_k[X_kY_k] = \mathbb E_k[X_k] \mathbb E_k[Y_k] + \cov[X_k, Y_k]$.
-            \textcolor{red}{Hence, taking the expectation doesn't follow. }
-
-        \end{proof}
-
         \begin{definition}[SNAPG-V2]\label{def:snapg-v2}
@@
 
-        \begin{theorem}[SNAPG-V2 one step convergence]
+        \begin{lemma}[range of the momentum sequence in SNAPG-V2]
+
+        \end{lemma}
+
+        \begin{theorem}[SNAPG-V2 one step convergence]\label{thm:snapg2-one-step}
 
@@
             Let's suppose that $I_k = i$ and, for all $k \ge 0$ let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ where $\bar x$ is a minimizer of $F$. 
+            With following intermediate results the proof can be built easily. 
+            Results (d)-(g) is showed at the end. 
             \begin{itemize}
                 \item[(a)] We can use proximal gradient inequality from Theorem \ref{thm:pg-ineq} with $z = z_k$ because each $F_i$ is $K_i$ Lipschitz smooth and, $\mu^{(i)}$ strongly convex with $K_i \ge \mu^{(i)}$.
-                \item[(b)] We can use Jesen's inequality of Theorem \ref{thm:jesen} with $z = z_k$ on $F_i$. 
+                \item[(b)] We can use Jensen's inequality of Theorem \ref{thm:jesen} with $z = z_k$ on $F_i$. 
                 \item[(c)] The sequence $(\alpha_k)_{k \ge 0}$ has $(L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right)$.
 It is a special case of Definition \ref{def:rwapg-seq} with $\rho_{k - 1} = L_{k - 1}/L_k$.
+                \item[(d)] From Definition \ref{def:snapg-v2} it has the following equality 
+                \begin{align*}
+                    (\forall k \ge 1)\; 
+                    z_k - y_k 
+                    = 
+                    \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+                    + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
+                \end{align*}
+                \item [(e)] From Definition \ref{def:snapg-v2} it has: $(\forall k \ge 1)\; z_k - x_k = \alpha_k (\bar x - v_k)$. 
+                \item [(f)] Using direct algebra, we have for all $k \ge 1$: 
+                \begin{align*}
+                    \frac{\left(\mu^{(i)}\right)^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} 
+                    - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
+                    = \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
+                    {2\left(L_k - \mu^{(i)}\right)}. 
+                \end{align*}
+                \item [(g)] Using (c), we have for all $k \ge 1$: 
+                \begin{align*}
+                    \frac{\left(
+                        L_k\alpha_k - \mu^{(i)}
+                    \right)^2}{2(L_k - \mu^{(i)})} 
+                    -
+                    \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} 
+                    = 
+                    \frac{
+                        \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
+                        \left(\alpha_k - 1\right)
+                    }
+                    {2(L_k - \mu^{(i)})}
+                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2}. 
+                \end{align*}
             \end{itemize}
+            Starting with (a) we have: 
+            \begin{align}\label{ineq:snapg2-one-step-chain1}
+                \begin{split}
+                    0 &\le F_i(z_k) - F_i(x_k) - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2
+                    \\
+                    &\underset{\text{(b)}}{\le}
+                    \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) \\
+                        &\quad 
+                        - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
+                        - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
+                        + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2. 
+                \end{split}
+            \end{align}
+            And we have the following chain of equalities:
+            {\allowdisplaybreaks
+            \begin{align*}
+                & - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
+                + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2
+                \\
+                &\underset{\text{(d)}}{=}
+                - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2 
+                    \\&\quad
+                    + \frac{L_k - \mu^{(i)}}{2}
+                    \left\Vert
+                        \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+                        + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1})
+                    \right\Vert^2
+                \\
+                &= 
+                - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2 
+                    \\&\quad
+                    + \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2
+                    + \frac{(\mu^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2 
+                    \\&\quad 
+                    + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+                \\
+                &= 
+                \left(
+                    \frac{(\mu^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
+                \right)\Vert \bar x - x_{k - 1}\Vert^2
+                    \\ &\quad 
+                    + \left(
+                        \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
+                    \right) \Vert \bar x - v_{k - 1}\Vert^2
+                    + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                    \\&\quad 
+                    + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+                \\
+                &\underset{\text{(f)}}{=}
+                \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
+                {2\left(L_k - \mu^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2
+                    \\ &\quad 
+                    + \left(
+                        \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
+                    \right) \Vert \bar x - v_{k - 1}\Vert^2
+                    + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                    \\&\quad 
+                    + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+                \\
+                & \underset{\text{(g)}}{=} 
+                \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
+                {2\left(L_k - \mu^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2
+                    \\ &\quad 
+                    + \left(
+                        \frac{
+                            \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
+                            \left(\alpha_k - 1\right)
+                        }
+                        {2(L_k - \mu^{(i)})}
+                        + \frac{\alpha_k(\mu - \mu^{(i)})}{2}
+                    \right) \Vert \bar x - v_{k - 1}\Vert^2
+                    \\ &\quad 
+                    + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                    + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+                \\
+                &= 
+                \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\left(
+                    \Vert \bar x - x_{k - 1}\Vert^2 + \Vert \bar x - v_{k - 1}\Vert^2 - 2\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+                \right) 
+                    \\ &\quad 
+                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                    + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                \\
+                &= \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
+                    \Vert x_{k - 1} - v_{k - 1} \Vert^2
+                    \\ &\quad 
+                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                    + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2.
+            \end{align*}
+            }
+            Substituting the above back to the tail of Inequality \eqref{ineq:snapg2-one-step-chain1} it gives:
+
             % INTERMEDIATE RESULTS
             \par
-            From Definiton \ref{def:snapg-v2}, it has
+            \textbf{Proof of (d)}.
+            From Definition \ref{def:snapg-v2}, it has
             \begin{align*}
                 (1 + \tau_k)^{-1}
-                &\underset{\eqref{thm:onestep-napg-cnvg-i}}{=} 
+                &=
                 \left(
@@
             % INTERMEDIATE RESULTS
+            \textbf{Proof of (e)}.
             From Definition \ref{def:snapg-v2} it has directly: 
@@
             % INTERMEDIATE RESULTS
-            The proof is direct algebra and it has: 
+            \textbf{Proof of (f)}.
+            The proof is direct algebra and, it has: 
             {\small\allowdisplaybreaks
@@
             % INTERMEDIATE RESULTS 
+            \textbf{Proof of (g)}.
             From the property of the sequence stated in item (c), we have: 
@@
                     L_k\alpha_k - \mu^{(i)}
-                \right)^2}{L_k - \mu^{(i)}} 
+                \right)^2}{2(L_k - \mu^{(i)})} 
                 -
@@
                     L_k\alpha_k - \mu^{(i)}
-                \right)^2}{L_k - \mu^{(i)}} 
+                \right)^2}{2(L_k - \mu^{(i)})} 
                 - \frac{L_k\alpha_k(\alpha_k - \mu^{(i)}/L_k)}{2}
@@
                     L_k\alpha_k - \mu^{(i)}
-                \right)^2}{L_k - \mu^{(i)}} 
-                - \frac{\alpha_k(L_k\alpha_k - \mu^{(i)})}{2}
+                \right)^2}{2(L_k - \mu^{(i)})} 
+                - \frac{\alpha_k\left(L_k\alpha_k - \mu^{(i)}\right)}{2}
                 + \frac{L_k\alpha_k}{2}
@@
                 &=
+                \frac{L_k \alpha_k - \mu^{(i)}}{2(L_k - \mu^{(i)})}\left(
+                    L_k \alpha_k - \mu^{(i)} 
+                    - \left(L_k - \mu^{(i)}\right)\alpha_k
+                \right)
+                + \frac{\alpha_k(\mu - \mu^{(i)})}{2}
+                \\
+                &= \frac{L_k \alpha_k - \mu^{(i)}}{2(L_k - \mu^{(i)})}\left(
+                    \mu^{(i)}\alpha_k - \mu^{(i)} 
+                \right)
+                + \frac{\alpha_k(\mu - \mu^{(i)})}{2}
+                \\
+                &= 
+                \frac{
+                    \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
+                    \left(\alpha_k - 1\right)
+                }
+                {2(L_k - \mu^{(i)})}
+                + \frac{\alpha_k(\mu - \mu^{(i)})}{2}. 
             \end{align*}

### 2025-07-02 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
 \newcommand{\cov}{\ensuremath{\operatorname{Cov}}}
+\newcommand{\var}{\ensuremath{\operatorname{Var}}}
 
@@
 \author{
-    Author 1 Name, Author 2 Name
+    HONGDA LI
     \thanks{
-        Subject type, Some Department of Some University, Location of the University,
-        Country. E-mail: \texttt{author.name@university.edu}.
+        University of British Columbia Okanagan,
+        Canada. E-mail: \texttt{alto@mail.ubc.ca}.
     }
@@
 
-        \begin{lemma}[range of the momentum sequence in SNAPG-V2]
+        \begin{lemma}[range of the momentum sequence in SNAPG-V2]\label{lemma:snapg-v2-seq-range}
 
@@
         \begin{theorem}[SNAPG-V2 one step convergence]\label{thm:snapg2-one-step}
-
+            Let $F$ satisfies assumption \ref{ass:interp-hypothesis}. 
+            Suppose that an algorithm satisfying Definition \ref{def:snapg-v2} takes this $F$, for all $k \ge 1$, it has the following inequality 
+            \begin{align*}
+                & \mathbb E_k\left[F_{I_k}(x_{k})\right] 
+                - F(\bar x) 
+                + \mathbb E_k\left[
+                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+                \right]
+                \\
+                &\le 
+                (1 - \alpha_k)\left(
+                        \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
+                        - F(\bar x)
+                        + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
+                \right)
+                    \\ &\quad 
+                    + \mathbb E_k\left[
+                        \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
+                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
+            \end{align*}
         \end{theorem}
@@
                 \end{align*}
+                \item[(h)] Because we assumed interpolation hypothesis in Assumption \ref{ass:interp-hypothesis}, it has $\mathbb E[F_{I_k}(\bar x)] = F(\bar x)$ for all $\bar x$ that is a minimizer of $F$.
             \end{itemize}
-            Starting with (a) we have: 
+            For all $k \ge 1$, starting with (a) we have: 
             \begin{align}\label{ineq:snapg2-one-step-chain1}
@@
             Substituting the above back to the tail of Inequality \eqref{ineq:snapg2-one-step-chain1} it gives: 
-
+            {\allowdisplaybreaks
+            \begin{align*}
+                0 &\le 
+                \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) 
+                    \\&\quad 
+                    - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
+                    + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
+                    \Vert x_{k - 1} - v_{k - 1} \Vert^2
+                    \\ &\quad 
+                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                    + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                \\
+                &\underset{\text{(e)}}{=} 
+                \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) 
+                    \\&\quad 
+                    - \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+                    + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
+                    \Vert x_{k - 1} - v_{k - 1} \Vert^2
+                    \\ &\quad 
+                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                    + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                \\
+                &= (\alpha_k - 1)F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) + F_i(\bar x)
+                    \\&\quad 
+                    - \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+                    + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
+                    \\ &\quad 
+                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                    + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                \\
+                &= (1 - \alpha_k)\left(
+                    F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
+                \right) 
+                    \\ & \quad
+                    - \left(
+                        F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+                    \right)
+                    \\ &\quad 
+                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                    + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
+            \end{align*}
+            }
+            Recall that $i = I_k$ is the random variable from Definition \ref{def:snapg-v2}. 
+            Rearranging the last expression in the above equality chain can be conveniently written as
+            \begin{align}
+                \begin{split}
+                    & \left(
+                        F_{I_k}(x_{k}) - F_{I_k}(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+                    \right) 
+                    \\ &\le 
+                    (1 - \alpha_k)\left(
+                        F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
+                    \right) 
+                        \\ &\quad 
+                        + \frac{\alpha_k(\mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                        + \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
+                \end{split}
+            \label{ineq:snapg2-one-step-presult1}\end{align}
+            Recall $\mathbb E_k$ denotes the conditional expectation on $I_0, I_1, \ldots, I_{k - 1}$. 
+            Taking the conditional expectation on the LHS of the \eqref{ineq:snapg2-one-step-presult1} yields: 
+            \begin{align*}
+                & \mathbb E_k\left[
+                    F_{I_k}(x_{k}) - F_{I_k}(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+                \right]
+                \\
+                &\underset{\text{(h)}}{=}
+                \mathbb E_k\left[F_{I_k}(x_{k})\right] 
+                - F(\bar x) 
+                + \mathbb E_k\left[
+                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+                \right]. 
+            \end{align*}
+            On the RHS of \eqref{ineq:snapg2-one-step-presult1}, using the linearity property while taking the conditional expectation yields: 
+            {\allowdisplaybreaks
+            \begin{align*}
+                & \mathbb E_k\left[
+                    (1 - \alpha_k)\left(
+                        F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
+                    \right)
+                \right]
+                    \\ &\quad 
+                    + \mathbb E_k \left[
+                        \frac{\alpha_k(\mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                    \right]
+                    + \mathbb E_k\left[
+                        \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
+                    \right]
+                \\
+                &\underset{\text{(1)}}{=} 
+                (1 - \alpha_k)\left(
+                        \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
+                        -\mathbb E_k [F_{I_k}(\bar x)] 
+                        + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
+                \right)
+                    \\ &\quad 
+                    + \mathbb E_k \left[
+                        \frac{\alpha_k(\mu - \mu^{(I_k)})}{2} 
+                    \right]\Vert \bar x - v_{k - 1}\Vert^2
+                    + \mathbb E_k\left[
+                        \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
+                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
+                \\
+                &\underset{\text{(h)}}{=} 
+                (1 - \alpha_k)\left(
+                        \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
+                        - F(\bar x)
+                        + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
+                \right)
+                    \\ &\quad 
+                    + \mathbb E_k \left[
+                        \frac{\alpha_k(\mu - \mu^{(I_k)})}{2} 
+                    \right]\Vert \bar x - v_{k - 1}\Vert^2
+                    + \mathbb E_k\left[
+                        \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
+                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
+                \\
+                &\underset{\text{(2)}}{=}
+                (1 - \alpha_k)\left(
+                        \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
+                        - F(\bar x)
+                        + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
+                \right)
+                    \\ &\quad 
+                    + \mathbb E_k\left[
+                        \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
+                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
+            \end{align*}
+            }
+            We note that at label (1), we used the fact that $\alpha_k$ is a constant and, $x_{k - 1}, v_{k - 1}$ only depends on random variable $I_0, I_1, \ldots, I_{k - 1}$ hence it falls out of the conditional expectation $\mathbb E_k$.
+            At label (2), we used assumption (Assumption \ref{ass:sum-of-many}) that the averages of all the $\mu^{(I_k)}$ on each $F_{I_k}$ equals to $\mu$ hence, the expectation evaluates to zero by linearity of the expected value operator.
+            \par
+            Combing the above results on the expectation of RHS, and LHS of \eqref{ineq:snapg2-one-step-presult1}, we have the one step inequaity in expectation: 
+            \begin{align*}
+                & \mathbb E_k\left[F_{I_k}(x_{k})\right] 
+                - F(\bar x) 
+                + \mathbb E_k\left[
+                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+                \right]
+                \\
+                &\le 
+                (1 - \alpha_k)\left(
+                        \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
+                        - F(\bar x)
+                        + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
+                \right)
+                    \\ &\quad 
+                    + \mathbb E_k\left[
+                        \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
+                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
+            \end{align*}
             % INTERMEDIATE RESULTS

### 2025-07-03 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
 
-    \subsection{A compact argument for the convergence of NAPG with proximal gradient}
-        Here, the abbreviation ``NAPG" stands for ``Nesterov Acceleration Proximal Gradient". 
-        It's made in acknowledgement of Algorithm 2.2.36 in Nesterov's book \cite{nesterov_lectures_2018} and its extension known as FISTA in the literature.
-        The following theorem provides a complete proof for the convergence rate of algorithms implementing Definition \ref{def:st-method}, which is equivalent to NAG, or NAPG. 
-        It made use of Definition \ref{def:rwapg-seq} which accommodates a relaxed sequence compared to the usual sequence that gives the optimal convergence rate. 
-        \begin{theorem}[one step convergence claim of NAPG]\label{thm:onestep-napg-cnvg}
-            Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth} for some $L > \mu \ge 0$. 
-            Let the sequence $(\alpha_k)_{k \ge0}$ be an R-WAPG sequence (Definition \ref{def:rwapg-seq}). 
-            Suppose that the iterates sequence $(x_k, y_k, v_k)_{k \ge 0}$ satisfy NAPG in similar triangle form (Definition \ref{def:st-method}) with initial guesses $v_{-1}, x_{-1} \in \RR^n$. 
-            Then for all $k \ge 1$, the following inequality is true for all $\bar x \in \RR^n$: 
-            \begin{align*}
-                & - F(\bar x) + F(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-                \\
-                & \le \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(1 - \alpha_k)\left(
-                    F(x_{k - 1}) - F(\bar x) 
-                    + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                \right). 
-            \end{align*}
-            If in addition, we choose $\alpha_0 = 1$, and let $x_{-1} = v_{-1}$, then a base case of the inequality is: 
-            \begin{align*}
-                F(x_{0}) - F(\bar x) + \frac{L_0}{2}\Vert \bar x - x_{0}\Vert^2 
-                &\le \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
-            \end{align*}
-        \end{theorem}
-        \begin{proof}
-            The proof is very intense algebraically hence before we step into it, we present the following intermediate results in advance to their proofs given at the end. 
-            \par
-            For all $k \ge 0$, define $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$. 
-            \begin{itemize}
-                \item [(a)] Theorem \ref{thm:pg-ineq}, with $z = z_k$, $k \ge 0$. We can use it because $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
-                \item [(b)] Jensen's inequality (Theorem \ref{thm:jesen}), with $z = z_k$, for $k \ge 0$. We can use it because $F$ is $\mu \ge 0$ strongly convex. 
-                \item [(c)] Definition \ref{def:rwapg-seq} which has $\rho_k(1 - \alpha_{k + 1})\alpha_k^2 = \alpha_{k + 1}(\alpha_{k + 1} - \mu/L_k)$ for $k \ge 0$.
-                \item [(d)] The equality $z_k - y_k = (L_k - \mu)^{-1}((L_k\alpha_k - \mu)(\bar x - v_k) + \mu(1 - \alpha_k)(\bar x - x_{k - 1}))$ for all $k \ge 0$, it comes from Definition \ref{def:st-method}.
-                \item [(e)] The equality $z_k - x_k = \alpha_k(\bar x - v_k)$ for all $k \ge 0$ it comes from Definition \ref{def:st-method}. 
-                \item [(f)] Using basic algebra, we have the following equality: 
-                \begin{align*}
-                    (\forall k \ge 1)\; \frac{1}{2}\left(
-                        \frac{\mu^2(1 - \alpha_k)^2}{L_k - \mu} - \mu \alpha_k(1 - \alpha_k)
-                    \right) &= 
-                    \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}. 
-                \end{align*}
-                \item [(g)] Using (c), we have the following equality: 
-                \begin{align*}
-                    (\forall k \ge 1)\; 
-                    \frac{1}{2}\left(
-                        \frac{(L_k\alpha_k - \mu)^2}{L_k - \mu} - 
-                        \alpha_{k - 1}^2\rho_{k - 1}L_k(1 - \alpha_k)
-                    \right)
-                    &= 
-                    \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)}. 
-                \end{align*}
-                \item [(h)] Definition \ref{def:rwapg-seq} determine the inequality: 
-                \begin{align*}
-                    (\forall k \ge 1)\; \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)} &\le 0.   
-                \end{align*}
-            \end{itemize}
-            With intermediate results (a) to (h), presented above, the proof of the theorem come smoothly from a chain of inequalities and equalities. 
-            The overall proof now follows. 
-            Start with the (a), the proximal gradient inequality it has: 
-            \begin{align*}
-                0 &\le F(z_k) - F(x_k) - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2
-                \\
-                &\underset{\text{(b)}}{\le}
-                \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k) \\
-                    &\quad 
-                    - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
-                    - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2. 
-            \end{align*}
-            Using the chain of equality below: 
-            {\footnotesize
-            \begin{align*}
-                &- \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
-                + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2
-                \\
-                &\underset{\text{(d)}}{=} 
-                -\frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2\\ 
-                    &\quad +
-                    \frac{L_k - \mu}{2}
-                    \left\Vert 
-                        \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1}) + 
-                        \frac{\mu(1 - \alpha_k)}{L_k - \mu}(\bar x - x_{k - 1})
-                    \right\Vert^2
-                \\
-                &= 
-                - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2\\&\quad 
-                    + \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} \Vert \bar x - v_{k - 1}\Vert^2
-                    + \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} \Vert \bar x - x_{k - 1}\Vert^2
-                    + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
-                \\
-                &= \left(
-                    \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} - \frac{\mu\alpha_k(1 - \alpha_k)}{2}
-                \right)\Vert \bar x - x_{k - 1}\Vert^2
-                + 
-                \left(
-                    \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)}
-                    - \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}
-                \right)\Vert \bar x - v_{k - 1}\Vert^2 \\ &\quad 
-                    + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                    + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
-                \\
-                &\underset{\text{(f)}}{=} 
-                \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert \bar x - x_{k - 1}\Vert^2
-                + 
-                \left(
-                    \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)}
-                    - \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}
-                \right)\Vert \bar x - v_{k - 1}\Vert^2 \\ &\quad 
-                    + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                    + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
-                \\
-                &\underset{\text{(g)}}{=}
-                \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert \bar x - x_{k - 1}\Vert^2
-                + 
-                \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)}\Vert \bar x - v_{k - 1}\Vert^2
-                \\ &\quad 
-                    + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                    + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
-                \\
-                &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2 \\ & \quad
-                    \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\left(
-                        \Vert \bar x - x_{k - 1}\Vert^2 + \Vert \bar x - v_{k - 1}\Vert^2 - 2\langle\bar x - x_{k - 1},\bar x - v_{k - 1} \rangle
-                    \right)
-                \\
-                &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2. 
-            \end{align*}
-            }
-            The inequality from previously simplifies, and it has: 
-            {\allowdisplaybreaks\small
-            \begin{align*}
-                0 &\le 
-                \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
-                + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 \\ &\quad 
-                    + \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2
-                \\
-                &\underset{\text{(h)}}{\le}
-                \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
-                    \\ &\quad
-                    + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                    - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-                \\
-                &= (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x)) + F(\bar x) - F(x_k) \\&\quad
-                    + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                    - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-                \\
-                &\underset{\text{(e)}}{=} 
-                (1 - \alpha_k)\left(
-                    F(x_{k - 1}) - F(\bar x) 
-                    + \frac{L_k\rho_{k - 1}}{L_{k - 1}}\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                \right) \\ &\quad
-                    + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-                \\
-                &\le 
-                (1 - \alpha_k)\left(
-                    F(x_{k - 1}) - F(\bar x) 
-                    + \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)
-                    \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                \right) \\&\quad
-                    + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-                \\
-                &\le (1 - \alpha_k)\left(
-                    \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(F(x_{k - 1}) - F(\bar x))
-                    + \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)
-                    \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                \right) \\&\quad 
-                    + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-                \\
-                &= 
-                \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(1 - \alpha_k)\left(
-                    F(x_{k - 1}) - F(\bar x) 
-                    + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                \right) \\&\quad
-                    + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2. 
-            \end{align*}
-            }
-            Finally, for the base case, when $\alpha_0 = 1$, it has $y_0 = v_{-1} = x_{-1}$, and it makes $z_0 = \bar x$ therefore this makes the proximal gradient inequality into:
-            \begin{align*}
-                0 &\le F(z_0) - F(x_{0}) - \frac{L_0}{2}\Vert z_0 - x_0\Vert^2 + \frac{L_0 - \mu}{2}\Vert z_0 - y_0\Vert^2
-                \\
-                &= F(\bar x) - F(x_0) - \frac{L_0}{2}\Vert \bar x - x_0\Vert^2 + \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
-            \end{align*}
+    % \subsection{A compact argument for the convergence of NAPG with proximal gradient}
+    %     Here, the abbreviation ``NAPG" stands for ``Nesterov Acceleration Proximal Gradient". 
+    %     It's made in acknowledgement of Algorithm 2.2.36 in Nesterov's book \cite{nesterov_lectures_2018} and its extension known as FISTA in the literature.
+    %     The following theorem provides a complete proof for the convergence rate of algorithms implementing Definition \ref{def:st-method}, which is equivalent to NAG, or NAPG. 
+    %     It made use of Definition \ref{def:rwapg-seq} which accommodates a relaxed sequence compared to the usual sequence that gives the optimal convergence rate. 
+    %     \begin{theorem}[one step convergence claim of NAPG]\label{thm:onestep-napg-cnvg}
+    %         Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth} for some $L > \mu \ge 0$. 
+    %         Let the sequence $(\alpha_k)_{k \ge0}$ be an R-WAPG sequence (Definition \ref{def:rwapg-seq}). 
+    %         Suppose that the iterates sequence $(x_k, y_k, v_k)_{k \ge 0}$ satisfy NAPG in similar triangle form (Definition \ref{def:st-method}) with initial guesses $v_{-1}, x_{-1} \in \RR^n$. 
+    %         Then for all $k \ge 1$, the following inequality is true for all $\bar x \in \RR^n$: 
+    %         \begin{align*}
+    %             & - F(\bar x) + F(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+    %             \\
+    %             & \le \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(1 - \alpha_k)\left(
+    %                 F(x_{k - 1}) - F(\bar x) 
+    %                 + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+    %             \right). 
+    %         \end{align*}
+    %         If in addition, we choose $\alpha_0 = 1$, and let $x_{-1} = v_{-1}$, then a base case of the inequality is: 
+    %         \begin{align*}
+    %             F(x_{0}) - F(\bar x) + \frac{L_0}{2}\Vert \bar x - x_{0}\Vert^2 
+    %             &\le \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
+    %         \end{align*}
+    %     \end{theorem}
+    %     \begin{proof}
+    %         The proof is very intense algebraically hence before we step into it, we present the following intermediate results in advance to their proofs given at the end. 
+    %         \par
+    %         For all $k \ge 0$, define $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$. 
+    %         \begin{itemize}
+    %             \item [(a)] Theorem \ref{thm:pg-ineq}, with $z = z_k$, $k \ge 0$. We can use it because $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
+    %             \item [(b)] Jensen's inequality (Theorem \ref{thm:jesen}), with $z = z_k$, for $k \ge 0$. We can use it because $F$ is $\mu \ge 0$ strongly convex. 
+    %             \item [(c)] Definition \ref{def:rwapg-seq} which has $\rho_k(1 - \alpha_{k + 1})\alpha_k^2 = \alpha_{k + 1}(\alpha_{k + 1} - \mu/L_k)$ for $k \ge 0$.
+    %             \item [(d)] The equality $z_k - y_k = (L_k - \mu)^{-1}((L_k\alpha_k - \mu)(\bar x - v_k) + \mu(1 - \alpha_k)(\bar x - x_{k - 1}))$ for all $k \ge 0$, it comes from Definition \ref{def:st-method}.
+    %             \item [(e)] The equality $z_k - x_k = \alpha_k(\bar x - v_k)$ for all $k \ge 0$ it comes from Definition \ref{def:st-method}. 
+    %             \item [(f)] Using basic algebra, we have the following equality: 
+    %             \begin{align*}
+    %                 (\forall k \ge 1)\; \frac{1}{2}\left(
+    %                     \frac{\mu^2(1 - \alpha_k)^2}{L_k - \mu} - \mu \alpha_k(1 - \alpha_k)
+    %                 \right) &= 
+    %                 \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}. 
+    %             \end{align*}
+    %             \item [(g)] Using (c), we have the following equality: 
+    %             \begin{align*}
+    %                 (\forall k \ge 1)\; 
+    %                 \frac{1}{2}\left(
+    %                     \frac{(L_k\alpha_k - \mu)^2}{L_k - \mu} - 
+    %                     \alpha_{k - 1}^2\rho_{k - 1}L_k(1 - \alpha_k)
+    %                 \right)
+    %                 &= 
+    %                 \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)}. 
+    %             \end{align*}
+    %             \item [(h)] Definition \ref{def:rwapg-seq} determine the inequality: 
+    %             \begin{align*}
+    %                 (\forall k \ge 1)\; \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)} &\le 0.   
+    %             \end{align*}
+    %         \end{itemize}
+    %         With intermediate results (a) to (h), presented above, the proof of the theorem come smoothly from a chain of inequalities and equalities. 
+    %         The overall proof now follows. 
+    %         Start with the (a), the proximal gradient inequality it has: 
+    %         \begin{align*}
+    %             0 &\le F(z_k) - F(x_k) - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2
+    %             \\
+    %             &\underset{\text{(b)}}{\le}
+    %             \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k) \\
+    %                 &\quad 
+    %                 - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
+    %                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2. 
+    %         \end{align*}
+    %         Using the chain of equality below: 
+    %         {\footnotesize
+    %         \begin{align*}
+    %             &- \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
+    %             + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2
+    %             \\
+    %             &\underset{\text{(d)}}{=} 
+    %             -\frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2\\ 
+    %                 &\quad +
+    %                 \frac{L_k - \mu}{2}
+    %                 \left\Vert 
+    %                     \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1}) + 
+    %                     \frac{\mu(1 - \alpha_k)}{L_k - \mu}(\bar x - x_{k - 1})
+    %                 \right\Vert^2
+    %             \\
+    %             &= 
+    %             - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2\\&\quad 
+    %                 + \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} \Vert \bar x - v_{k - 1}\Vert^2
+    %                 + \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} \Vert \bar x - x_{k - 1}\Vert^2
+    %                 + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
+    %             \\
+    %             &= \left(
+    %                 \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} - \frac{\mu\alpha_k(1 - \alpha_k)}{2}
+    %             \right)\Vert \bar x - x_{k - 1}\Vert^2
+    %             + 
+    %             \left(
+    %                 \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)}
+    %                 - \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}
+    %             \right)\Vert \bar x - v_{k - 1}\Vert^2 \\ &\quad 
+    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+    %                 + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
+    %             \\
+    %             &\underset{\text{(f)}}{=} 
+    %             \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert \bar x - x_{k - 1}\Vert^2
+    %             + 
+    %             \left(
+    %                 \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)}
+    %                 - \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}
+    %             \right)\Vert \bar x - v_{k - 1}\Vert^2 \\ &\quad 
+    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+    %                 + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
+    %             \\
+    %             &\underset{\text{(g)}}{=}
+    %             \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert \bar x - x_{k - 1}\Vert^2
+    %             + 
+    %             \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)}\Vert \bar x - v_{k - 1}\Vert^2
+    %             \\ &\quad 
+    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+    %                 + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
+    %             \\
+    %             &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2 \\ & \quad
+    %                 \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\left(
+    %                     \Vert \bar x - x_{k - 1}\Vert^2 + \Vert \bar x - v_{k - 1}\Vert^2 - 2\langle\bar x - x_{k - 1},\bar x - v_{k - 1} \rangle
+    %                 \right)
+    %             \\
+    %             &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+    %             + \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2. 
+    %         \end{align*}
+    %         }
+    %         The inequality from previously simplifies, and it has: 
+    %         {\allowdisplaybreaks\small
+    %         \begin{align*}
+    %             0 &\le 
+    %             \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
+    %             + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+    %             - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 \\ &\quad 
+    %                 + \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2
+    %             \\
+    %             &\underset{\text{(h)}}{\le}
+    %             \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
+    %                 \\ &\quad
+    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+    %                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
+    %             \\
+    %             &= (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x)) + F(\bar x) - F(x_k) \\&\quad
+    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+    %                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
+    %             \\
+    %             &\underset{\text{(e)}}{=} 
+    %             (1 - \alpha_k)\left(
+    %                 F(x_{k - 1}) - F(\bar x) 
+    %                 + \frac{L_k\rho_{k - 1}}{L_{k - 1}}\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+    %             \right) \\ &\quad
+    %                 + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+    %             \\
+    %             &\le 
+    %             (1 - \alpha_k)\left(
+    %                 F(x_{k - 1}) - F(\bar x) 
+    %                 + \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)
+    %                 \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+    %             \right) \\&\quad
+    %                 + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+    %             \\
+    %             &\le (1 - \alpha_k)\left(
+    %                 \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(F(x_{k - 1}) - F(\bar x))
+    %                 + \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)
+    %                 \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+    %             \right) \\&\quad 
+    %                 + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+    %             \\
+    %             &= 
+    %             \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(1 - \alpha_k)\left(
+    %                 F(x_{k - 1}) - F(\bar x) 
+    %                 + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+    %             \right) \\&\quad
+    %                 + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2. 
+    %         \end{align*}
+    %         }
+    %         Finally, for the base case, when $\alpha_0 = 1$, it has $y_0 = v_{-1} = x_{-1}$, and it makes $z_0 = \bar x$ therefore this makes the proximal gradient inequality into:
+    %         \begin{align*}
+    %             0 &\le F(z_0) - F(x_{0}) - \frac{L_0}{2}\Vert z_0 - x_0\Vert^2 + \frac{L_0 - \mu}{2}\Vert z_0 - y_0\Vert^2
+    %             \\
+    %             &= F(\bar x) - F(x_0) - \frac{L_0}{2}\Vert \bar x - x_0\Vert^2 + \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
+    %         \end{align*}
 
-            \par
-            Going back to prove the intermediate results, the following will be useful. 
-            From Definition \ref{def:st-method} it has for all $k \ge 0$
-            \begin{align}\label{thm:onestep-napg-cnvg-i}
-                \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}.    
-            \tag{i}\end{align}
-            Then it has: 
-            \begin{align*}\label{thm:onestep-napg-cnvg-j}
-                (1 + \tau_k)^{-1}
-                &\underset{\eqref{thm:onestep-napg-cnvg-i}}{=} 
-                \left(
-                    1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
-                \right)^{-1} = \left(
-                    \frac{L_k\alpha_k - \mu + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
-                \right)^{-1}
-                = \frac{L_k\alpha_k - \mu}{L_k - \mu}.
-            \tag{j}\end{align*}
-            And also
-            \begin{align*}\label{thm:onestep-napg-cnvg-k}
-                \tau_k(1 + \tau_k)^{-1} 
-                &\underset{\eqref{thm:onestep-napg-cnvg-i}, \eqref{thm:onestep-napg-cnvg-j}}= 
-                \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
-                \frac{L_k\alpha_k - \mu}{L_k - \mu}
-                = \frac{L_k(1 - \alpha_k)}{L_k - \mu}. 
-            \tag{k}\end{align*}
-            \textbf{Proof of (d)}
-            For all $k \ge 1$, from Definition \ref{def:st-method} it has 
-            \begin{align*}
-                0 &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1} - y_k
-                \\
-                &\underset{\eqref{thm:onestep-napg-cnvg-k}}{=} 
-                (1 + \tau_k)^{-1} v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k - \mu} x_{k - 1} - y_k
-                \\
-                &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1} \\ 
-                    &\quad 
-                    + \left(
-                        \frac{L_k(1 - \alpha_k)}{L_k - \mu} - (1 - \alpha_k)
-                    \right) x_{k - 1} - y_k
-                \\
-                &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1}\\
-                    &\quad 
-                    + (1 - \alpha_k)\left(
-                        \frac{L_k}{L_k - \mu} - 1
-                    \right) x_{k - 1} - y_k
-                \\
-                &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1} + 
-                \frac{\mu(1 - \alpha_k)}{L - \mu}x_{k - 1} - y_k
-                \\
-                \iff 
-                (1 - \alpha_k)x_{k - 1} - y_k 
-                &= - (1 + \tau_k)^{-1}v_{k - 1} - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}.
-            \end{align*}
-            Recall the definition for $z_k$ at the start of the proof and, use the above results it yields: 
-            \begin{align*}
-                z_k - y_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
-                \\
-                &= \alpha_k \bar x - (1 + \tau_k)^{-1}v_{k - 1} - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
-                \\
-                &\underset{\eqref{thm:onestep-napg-cnvg-j}}{=}
-                \alpha_k \bar x - \frac{L_k\alpha_k - \mu}{L_k - \mu}v_{k - 1} 
-                - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
-                \\
-                &= \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
-                + \left(
-                    \alpha_k - \frac{L_k\alpha_k - \mu}{L_k - \mu}
-                \right)\bar x - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
-                \\
-                &= 
-                \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
-                +
-                \frac{\alpha_kL_k - \alpha_k \mu - L_k\alpha_k + \mu}{L_k - \mu}
-                \bar x - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
-                \\
-                &= \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
-                +
-                \frac{\mu(1 - \alpha_k)}{L_k - \mu}(\bar x - x_{k - 1}). 
-            \end{align*}
-            \textbf{Proof of (e)}. 
-            The proof is direct using the equality with $x_k$ in Definition \ref{def:st-method}. 
-            \begin{align*}
-                z_k - x_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
-                \\
-                &= \alpha_k \bar x + x_{k  1} - x_k - \alpha_k x_{k - 1}
-                \\
-                &= \alpha_k(\bar x - \alpha_k^{-1}(x_k - x_{k - 1}) - x_{k - 1})
-                \\
-                &= \alpha_k (\bar x - v_k).
-            \end{align*}
-            \textbf{Proof of (f)}. 
-            The proof is direct and it has: 
-            \begin{align*}
-                \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} - \frac{\mu\alpha_k(1 - \alpha_k)}{2}
-                &= 
-                \frac{1}{2(L_k - \mu)}\left(
-                    \mu^2(1 - \alpha_k)^2 - (L_k - \mu)\mu \alpha_k(1 - \alpha_k)
-                \right)
-                \\
-                &= \frac{1 - \alpha_k}{2(L_k - \mu)}\left(
-                    \mu^2 - \mu^2\alpha_k - (L_k \mu \alpha_k - \mu^2 \alpha_k)
-                \right)
-                \\
-                &= 
-                \frac{1 - \alpha_k}{2(L_k - \mu)}\left(
-                    \mu^2 - L_k\mu\alpha_k
-                \right)
-                \\
-                &= \frac{(1 - \alpha_k)\mu(\mu - L_k\alpha_k)}{2(L_k - \mu)} 
-                \\
-                &= \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}. 
-            \end{align*}
-            \textbf{Proof of (g)}
-            The proof is direct: 
-            \begin{align*}
-                \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} - \frac{\alpha_{k - 1}^2 L_k \rho_{k - 1}(1 - \alpha_k)}{2}
-                &\underset{\text{(c)}}{=} \frac{(L\alpha_k - \mu)^2}{2(L_k - \mu)} - \frac{L_k\alpha_k(\alpha_k - \mu/L_k)}{2}
-                \\
-                &= \frac{1}{2(L_k - \mu)}\left(
-                    (L_k\alpha_k - \mu)^2 - (L_k - \mu)L_k\alpha_k(\alpha_k - \mu/L_k)
-                \right)
-                \\
-                &= 
-                \frac{1}{2(L_k - \mu)}\left(
-                    (L_k\alpha_k - \mu)^2 - (L_k - \mu)\alpha_k(L_k\alpha_k - \mu)
-                \right)
-                \\
-                &= \frac{L_k\alpha_k - \mu}{2(L_k - \mu)}\left(
-                    L_k\alpha_k - \mu - (L - \mu)\alpha_k
-                \right)
-                \\
-                &= \frac{L_k\alpha_k - \mu}{2(L_k - \mu)}\left(
-                    \mu\alpha_k - \mu
-                \right)
-                \\
-                &= \frac{(L\alpha_k - \mu)\mu(\alpha_k - 1)}{2(L_k - \mu)}. 
-            \end{align*}
-            \textbf{Proof of (h)}. 
-            For all $k \ge 1$, by (c), the definition of the R-WAPG sequence, $\alpha_k \in (\mu/L_k, 1)$, then it has $L_k\alpha_k \in (\mu, L_k)$, so $L_k\alpha_k - \mu > 0$, and $\alpha_k - 1 < 0$.
-            Finally, we have $L_k \ge \mu$, therefore, the fraction is negative. 
-        \end{proof}
+    %         \par
+    %         Going back to prove the intermediate results, the following will be useful. 
+    %         From Definition \ref{def:st-method} it has for all $k \ge 0$
+    %         \begin{align}\label{thm:onestep-napg-cnvg-i}
+    %             \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}.    
+    %         \tag{i}\end{align}
+    %         Then it has: 
+    %         \begin{align*}\label{thm:onestep-napg-cnvg-j}
+    %             (1 + \tau_k)^{-1}
+    %             &\underset{\eqref{thm:onestep-napg-cnvg-i}}{=} 
+    %             \left(
+    %                 1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
+    %             \right)^{-1} = \left(
+    %                 \frac{L_k\alpha_k - \mu + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
+    %             \right)^{-1}
+    %             = \frac{L_k\alpha_k - \mu}{L_k - \mu}.
+    %         \tag{j}\end{align*}
+    %         And also
+    %         \begin{align*}\label{thm:onestep-napg-cnvg-k}
+    %             \tau_k(1 + \tau_k)^{-1} 
+    %             &\underset{\eqref{thm:onestep-napg-cnvg-i}, \eqref{thm:onestep-napg-cnvg-j}}= 
+    %             \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
+    %             \frac{L_k\alpha_k - \mu}{L_k - \mu}
+    %             = \frac{L_k(1 - \alpha_k)}{L_k - \mu}. 
+    %         \tag{k}\end{align*}
+    %         \textbf{Proof of (d)}
+    %         For all $k \ge 1$, from Definition \ref{def:st-method} it has 
+    %         \begin{align*}
+    %             0 &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1} - y_k
+    %             \\
+    %             &\underset{\eqref{thm:onestep-napg-cnvg-k}}{=} 
+    %             (1 + \tau_k)^{-1} v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k - \mu} x_{k - 1} - y_k
+    %             \\
+    %             &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1} \\ 
+    %                 &\quad 
+    %                 + \left(
+    %                     \frac{L_k(1 - \alpha_k)}{L_k - \mu} - (1 - \alpha_k)
+    %                 \right) x_{k - 1} - y_k
+    %             \\
+    %             &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1}\\
+    %                 &\quad 
+    %                 + (1 - \alpha_k)\left(
+    %                     \frac{L_k}{L_k - \mu} - 1
+    %                 \right) x_{k - 1} - y_k
+    %             \\
+    %             &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1} + 
+    %             \frac{\mu(1 - \alpha_k)}{L - \mu}x_{k - 1} - y_k
+    %             \\
+    %             \iff 
+    %             (1 - \alpha_k)x_{k - 1} - y_k 
+    %             &= - (1 + \tau_k)^{-1}v_{k - 1} - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}.
+    %         \end{align*}
+    %         Recall the definition for $z_k$ at the start of the proof and, use the above results it yields: 
+    %         \begin{align*}
+    %             z_k - y_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
+    %             \\
+    %             &= \alpha_k \bar x - (1 + \tau_k)^{-1}v_{k - 1} - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
+    %             \\
+    %             &\underset{\eqref{thm:onestep-napg-cnvg-j}}{=}
+    %             \alpha_k \bar x - \frac{L_k\alpha_k - \mu}{L_k - \mu}v_{k - 1} 
+    %             - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
+    %             \\
+    %             &= \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
+    %             + \left(
+    %                 \alpha_k - \frac{L_k\alpha_k - \mu}{L_k - \mu}
+    %             \right)\bar x - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
+    %             \\
+    %             &= 
+    %             \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
+    %             +
+    %             \frac{\alpha_kL_k - \alpha_k \mu - L_k\alpha_k + \mu}{L_k - \mu}
+    %             \bar x - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
+    %             \\
+    %             &= \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
+    %             +
+    %             \frac{\mu(1 - \alpha_k)}{L_k - \mu}(\bar x - x_{k - 1}). 
+    %         \end{align*}
+    %         \textbf{Proof of (e)}. 
+    %         The proof is direct using the equality with $x_k$ in Definition \ref{def:st-method}. 
+    %         \begin{align*}
+    %             z_k - x_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
+    %             \\
+    %             &= \alpha_k \bar x + x_{k  1} - x_k - \alpha_k x_{k - 1}
+    %             \\
+    %             &= \alpha_k(\bar x - \alpha_k^{-1}(x_k - x_{k - 1}) - x_{k - 1})
+    %             \\
+    %             &= \alpha_k (\bar x - v_k).
+    %         \end{align*}
+    %         \textbf{Proof of (f)}. 
+    %         The proof is direct and it has: 
+    %         \begin{align*}
+    %             \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} - \frac{\mu\alpha_k(1 - \alpha_k)}{2}
+    %             &= 
+    %             \frac{1}{2(L_k - \mu)}\left(
+    %                 \mu^2(1 - \alpha_k)^2 - (L_k - \mu)\mu \alpha_k(1 - \alpha_k)
+    %             \right)
+    %             \\
+    %             &= \frac{1 - \alpha_k}{2(L_k - \mu)}\left(
+    %                 \mu^2 - \mu^2\alpha_k - (L_k \mu \alpha_k - \mu^2 \alpha_k)
+    %             \right)
+    %             \\
+    %             &= 
+    %             \frac{1 - \alpha_k}{2(L_k - \mu)}\left(
+    %                 \mu^2 - L_k\mu\alpha_k
+    %             \right)
+    %             \\
+    %             &= \frac{(1 - \alpha_k)\mu(\mu - L_k\alpha_k)}{2(L_k - \mu)} 
+    %             \\
+    %             &= \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}. 
+    %         \end{align*}
+    %         \textbf{Proof of (g)}
+    %         The proof is direct: 
+    %         \begin{align*}
+    %             \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} - \frac{\alpha_{k - 1}^2 L_k \rho_{k - 1}(1 - \alpha_k)}{2}
+    %             &\underset{\text{(c)}}{=} \frac{(L\alpha_k - \mu)^2}{2(L_k - \mu)} - \frac{L_k\alpha_k(\alpha_k - \mu/L_k)}{2}
+    %             \\
+    %             &= \frac{1}{2(L_k - \mu)}\left(
+    %                 (L_k\alpha_k - \mu)^2 - (L_k - \mu)L_k\alpha_k(\alpha_k - \mu/L_k)
+    %             \right)
+    %             \\
+    %             &= 
+    %             \frac{1}{2(L_k - \mu)}\left(
+    %                 (L_k\alpha_k - \mu)^2 - (L_k - \mu)\alpha_k(L_k\alpha_k - \mu)
+    %             \right)
+    %             \\
+    %             &= \frac{L_k\alpha_k - \mu}{2(L_k - \mu)}\left(
+    %                 L_k\alpha_k - \mu - (L - \mu)\alpha_k
+    %             \right)
+    %             \\
+    %             &= \frac{L_k\alpha_k - \mu}{2(L_k - \mu)}\left(
+    %                 \mu\alpha_k - \mu
+    %             \right)
+    %             \\
+    %             &= \frac{(L\alpha_k - \mu)\mu(\alpha_k - 1)}{2(L_k - \mu)}. 
+    %         \end{align*}
+    %         \textbf{Proof of (h)}. 
+    %         For all $k \ge 1$, by (c), the definition of the R-WAPG sequence, $\alpha_k \in (\mu/L_k, 1)$, then it has $L_k\alpha_k \in (\mu, L_k)$, so $L_k\alpha_k - \mu > 0$, and $\alpha_k - 1 < 0$.
+    %         Finally, we have $L_k \ge \mu$, therefore, the fraction is negative. 
+    %     \end{proof}
 
@@
         \begin{assumption}[sum of many]\label{ass:sum-of-many}
-            Define $F := g + (1/n)\sum_{i = 1}^{n} f_i$, assume that $f_i:\RR^n \rightarrow  \RR$ are all $K^{(i)}$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K^{(i)} > \mu^{(i)}$ and, $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function.
-            Consequently, the function $f$ cane be written as $F = g + f$ where $f = (1/n)\sum_{i = 1}^{n} f_i$ and, it satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = \max_{i = 1, \ldots, n}K^{(i)}$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$.
+            Define $F := (1/n)\sum_{i = 1}^{n} F_i$ where $F_i = f_i + g_i$.
+            Assume that for all $i = 1, \ldots, n$, each $f_i:\RR^n \rightarrow \RR$ are $K^{(i)}$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K^{(i)} > \mu^{(i)}$ and, $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function.
+            Consequently, the function $f$ can be written as $F = g + f$ with $f = (1/n)\sum_{i = 1}^{n} f_i, g = (1/n)\sum_{i = 1}^{n}f_i + g_i$ there, it also satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = (1/2)\sum_{i = 1}^n K^{(i)}$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$.
         \end{assumption}
         This assumption is stronger than Assumption \ref{ass:smooth-plus-nonsmooth}. 
+        It still appears everywhere in practice, for example, in the case of convex feasibility problem $\bigcap_{i = 1}^n C_i$. 
+        In practice, each of the strong convexity constant $\mu^{(i)}$ may not be easily accessible. 
+        \par
         The interpolation hypothesis from Machine Learning stated that the model has the capacity to perfect fit all the observed data. 
         \begin{assumption}[interpolation hypothesis]\label{ass:interp-hypothesis}
-            Suppose that $F := f + (1/n)\sum_{i = 1}^{n} f_i$ satisfying Assumption \ref{ass:sum-of-many}. 
+            Suppose that $F := (1/n)\sum_{i = 1}^{n} F_i$ satisfying Assumption \ref{ass:sum-of-many}. 
             In addition, assuming that it has $0 = \inf_{x}F(x)$ and, there exists some $\bar x \in \RR^n$ such that for all $i = 1, \ldots, n$ it satisfies $0 = f_i(\bar x)$. 
@@
 
-        \begin{lemma}[range of the momentum sequence in SNAPG-V2]\label{lemma:snapg-v2-seq-range}
-
+        \begin{lemma}[range of the momentum sequence in SNAPG-V2]\;\label{lemma:snapg-v2-seq-range}\\
+            Suppose that $(L_k)_{k \ge 0}$ is a sequence such that $L_k > 0$ for all $k \ge 0$. 
+            Let $(\alpha_k)_{k \ge 0}$ be a sequence such that $\alpha_0 \in (0, 1]$ and, for all $k \ge 1$, it's recursively satisfies equality: 
+            \begin{align*}
+                (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right). 
+            \end{align*}
+            And, the following items are true: 
+            \begin{enumerate}
+                \item Solution to the equation with $\alpha_k > 0$ is given by: 
+                \begin{align*}
+                    \alpha_k = \frac{L_{k - 1}}{2L_k} \left(
+                        - \alpha_{k - 1}^2 + \frac{\mu}{L_{k - 1}}
+                        + \sqrt{
+                            \left(
+                                \alpha_{k - 1} - \frac{\mu}{L_{k - 1}}
+                            \right)^2
+                            + \frac{4\alpha_{k - 1}^2L_k}{L_{k - 1}}
+                        }
+                    \right). 
+                \end{align*}
+            \end{enumerate}
         \end{lemma}
@@
             Let $F$ satisfies assumption \ref{ass:interp-hypothesis}. 
-            Suppose that an algorithm satisfying Definition \ref{def:snapg-v2} takes this $F$, for all $k \ge 1$, it has the following inequality 
+            Suppose that an algorithm satisfying Definition \ref{def:snapg-v2} uses this $F$. 
+            Then, for all $k \ge 1$, it has the following inequality 
             \begin{align*}
@@
                 \begin{split}
-                    & \left(
-                        F_{I_k}(x_{k}) - F_{I_k}(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-                    \right) 
+                    & F_{I_k}(x_{k}) - F_{I_k}(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                     \\ &\le 
@@
             \end{align*}
+            Finally, we show the base case. 
+            When $k = 0$, by assumption it had $\alpha_0 = 1$ hence $\tau_0$ in Definition \ref{def:snapg-v2} has $\tau_0 = 0$ which makes $y_0 = v_{- 1} = x_{-1}$.
+
             % INTERMEDIATE RESULTS
@@
             \end{align*}
-            Therefore, for all $k \ge 0$ $y_k$ has 
+            Therefore, for all $k \ge 0$, $y_k$ has 
             \begin{align*}
@@
             \end{align*}
-            Using the above, we have 
+            On the second equality below, we will the above equality, it goes: 
             \begin{align*}
@@
                 \\
-                &= \alpha_k \bar x + x_{k  1} - x_k - \alpha_k x_{k - 1}
+                &= \alpha_k \bar x + x_{k - 1} - x_k - \alpha_k x_{k - 1}
                 \\
@@
             \textbf{Proof of (g)}.
-            From the property of the sequence stated in item (c), we have: 
+            From the property of the $\alpha_k$ sequence stated in item (c), we have: 
             \begin{align*}
@@
         \end{proof}
+    \subsection{\textcolor{purple}{So, what to do next?}}
 

### 2025-07-03 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
     \subsection{\textcolor{purple}{So, what to do next?}}
+        Hi Arron would you like to add me for the co-authorship to continue this line of work and see how Nesterov's Accelerated Technique may work out for the stochastic gradient method? 
+        These results are solid results but they are still partial results and, below are the potential I foresee for this these ideas. 
+        \begin{enumerate}
+            \item Narrow down the sequence $\alpha_k$ and make sure that it can allow the quantity: 
+            \begin{align*}
+                \mathbb E_k\left[
+                        \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
+                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
+            \end{align*}
+            is negative, or at least bounded. I am not sure how this will work out, but I have some solid ideas aroud it. 
+            \item Roll up the inequality in Theorem \ref{thm:snapg2-one-step} recursively and, determine the convergence rate through $\alpha_k$ that makes the previous item true. 
+            In addition, I have the hunches that the convergence reate involves the variance of $\mu^{(I_k)}$ and, it will slower than the non-stochastic case of the algorithm. 
+        \end{enumerate}
+        For the future we can: 
+        \begin{enumerate}
+            \item Extend the definition of strong convexity to quasi-norm. 
+            \item Show the convergence of the method for objective function that is not necessarily strong convex, but quasi-strongly convex.
+This is a much weaker assumption it works well in practice for well known problems.
+        \end{enumerate}
 

### 2025-07-03 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, updates

--- 2025-07-03 Notebook LaTEX/SAGD Under Interpolation/main.tex
@@
             The only generalization here is parameter $B$ which made to accommodate algorithm that implements Definition \ref{def:st-method} with some line search routine. 
+            Each of the reference books gives a proof of the theorem. 
+            But for the best consistency in notations, see Theorem 2.3 in Li and Wang \cite{li_relaxed_2025}. 
         \end{remark}
@@
 
-    % \subsection{A compact argument for the convergence of NAPG with proximal gradient}
-    %     Here, the abbreviation ``NAPG" stands for ``Nesterov Acceleration Proximal Gradient". 
-    %     It's made in acknowledgement of Algorithm 2.2.36 in Nesterov's book \cite{nesterov_lectures_2018} and its extension known as FISTA in the literature.
-    %     The following theorem provides a complete proof for the convergence rate of algorithms implementing Definition \ref{def:st-method}, which is equivalent to NAG, or NAPG. 
-    %     It made use of Definition \ref{def:rwapg-seq} which accommodates a relaxed sequence compared to the usual sequence that gives the optimal convergence rate. 
-    %     \begin{theorem}[one step convergence claim of NAPG]\label{thm:onestep-napg-cnvg}
-    %         Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth} for some $L > \mu \ge 0$. 
-    %         Let the sequence $(\alpha_k)_{k \ge0}$ be an R-WAPG sequence (Definition \ref{def:rwapg-seq}). 
-    %         Suppose that the iterates sequence $(x_k, y_k, v_k)_{k \ge 0}$ satisfy NAPG in similar triangle form (Definition \ref{def:st-method}) with initial guesses $v_{-1}, x_{-1} \in \RR^n$. 
-    %         Then for all $k \ge 1$, the following inequality is true for all $\bar x \in \RR^n$: 
-    %         \begin{align*}
-    %             & - F(\bar x) + F(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %             \\
-    %             & \le \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(1 - \alpha_k)\left(
-    %                 F(x_{k - 1}) - F(\bar x) 
-    %                 + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
-    %             \right). 
-    %         \end{align*}
-    %         If in addition, we choose $\alpha_0 = 1$, and let $x_{-1} = v_{-1}$, then a base case of the inequality is: 
-    %         \begin{align*}
-    %             F(x_{0}) - F(\bar x) + \frac{L_0}{2}\Vert \bar x - x_{0}\Vert^2 
-    %             &\le \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
-    %         \end{align*}
-    %     \end{theorem}
-    %     \begin{proof}
-    %         The proof is very intense algebraically hence before we step into it, we present the following intermediate results in advance to their proofs given at the end. 
-    %         \par
-    %         For all $k \ge 0$, define $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$. 
-    %         \begin{itemize}
-    %             \item [(a)] Theorem \ref{thm:pg-ineq}, with $z = z_k$, $k \ge 0$. We can use it because $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
-    %             \item [(b)] Jensen's inequality (Theorem \ref{thm:jesen}), with $z = z_k$, for $k \ge 0$. We can use it because $F$ is $\mu \ge 0$ strongly convex. 
-    %             \item [(c)] Definition \ref{def:rwapg-seq} which has $\rho_k(1 - \alpha_{k + 1})\alpha_k^2 = \alpha_{k + 1}(\alpha_{k + 1} - \mu/L_k)$ for $k \ge 0$.
-    %             \item [(d)] The equality $z_k - y_k = (L_k - \mu)^{-1}((L_k\alpha_k - \mu)(\bar x - v_k) + \mu(1 - \alpha_k)(\bar x - x_{k - 1}))$ for all $k \ge 0$, it comes from Definition \ref{def:st-method}.
-    %             \item [(e)] The equality $z_k - x_k = \alpha_k(\bar x - v_k)$ for all $k \ge 0$ it comes from Definition \ref{def:st-method}. 
-    %             \item [(f)] Using basic algebra, we have the following equality: 
-    %             \begin{align*}
-    %                 (\forall k \ge 1)\; \frac{1}{2}\left(
-    %                     \frac{\mu^2(1 - \alpha_k)^2}{L_k - \mu} - \mu \alpha_k(1 - \alpha_k)
-    %                 \right) &= 
-    %                 \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}. 
-    %             \end{align*}
-    %             \item [(g)] Using (c), we have the following equality: 
-    %             \begin{align*}
-    %                 (\forall k \ge 1)\; 
-    %                 \frac{1}{2}\left(
-    %                     \frac{(L_k\alpha_k - \mu)^2}{L_k - \mu} - 
-    %                     \alpha_{k - 1}^2\rho_{k - 1}L_k(1 - \alpha_k)
-    %                 \right)
-    %                 &= 
-    %                 \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)}. 
-    %             \end{align*}
-    %             \item [(h)] Definition \ref{def:rwapg-seq} determine the inequality: 
-    %             \begin{align*}
-    %                 (\forall k \ge 1)\; \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)} &\le 0.   
-    %             \end{align*}
-    %         \end{itemize}
-    %         With intermediate results (a) to (h), presented above, the proof of the theorem come smoothly from a chain of inequalities and equalities. 
-    %         The overall proof now follows. 
-    %         Start with the (a), the proximal gradient inequality it has: 
-    %         \begin{align*}
-    %             0 &\le F(z_k) - F(x_k) - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2
-    %             \\
-    %             &\underset{\text{(b)}}{\le}
-    %             \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k) \\
-    %                 &\quad 
-    %                 - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
-    %                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2. 
-    %         \end{align*}
-    %         Using the chain of equality below: 
-    %         {\footnotesize
-    %         \begin{align*}
-    %             &- \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
-    %             + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2
-    %             \\
-    %             &\underset{\text{(d)}}{=} 
-    %             -\frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2\\ 
-    %                 &\quad +
-    %                 \frac{L_k - \mu}{2}
-    %                 \left\Vert 
-    %                     \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1}) + 
-    %                     \frac{\mu(1 - \alpha_k)}{L_k - \mu}(\bar x - x_{k - 1})
-    %                 \right\Vert^2
-    %             \\
-    %             &= 
-    %             - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2\\&\quad 
-    %                 + \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} \Vert \bar x - v_{k - 1}\Vert^2
-    %                 + \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} \Vert \bar x - x_{k - 1}\Vert^2
-    %                 + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
-    %             \\
-    %             &= \left(
-    %                 \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} - \frac{\mu\alpha_k(1 - \alpha_k)}{2}
-    %             \right)\Vert \bar x - x_{k - 1}\Vert^2
-    %             + 
-    %             \left(
-    %                 \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)}
-    %                 - \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}
-    %             \right)\Vert \bar x - v_{k - 1}\Vert^2 \\ &\quad 
-    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-    %                 + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
-    %             \\
-    %             &\underset{\text{(f)}}{=} 
-    %             \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert \bar x - x_{k - 1}\Vert^2
-    %             + 
-    %             \left(
-    %                 \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)}
-    %                 - \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}
-    %             \right)\Vert \bar x - v_{k - 1}\Vert^2 \\ &\quad 
-    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-    %                 + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
-    %             \\
-    %             &\underset{\text{(g)}}{=}
-    %             \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert \bar x - x_{k - 1}\Vert^2
-    %             + 
-    %             \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)}\Vert \bar x - v_{k - 1}\Vert^2
-    %             \\ &\quad 
-    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-    %                 + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
-    %             \\
-    %             &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2 \\ & \quad
-    %                 \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\left(
-    %                     \Vert \bar x - x_{k - 1}\Vert^2 + \Vert \bar x - v_{k - 1}\Vert^2 - 2\langle\bar x - x_{k - 1},\bar x - v_{k - 1} \rangle
-    %                 \right)
-    %             \\
-    %             &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2. 
-    %         \end{align*}
-    %         }
-    %         The inequality from previously simplifies, and it has: 
-    %         {\allowdisplaybreaks\small
-    %         \begin{align*}
-    %             0 &\le 
-    %             \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
-    %             + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-    %             - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 \\ &\quad 
-    %                 + \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2
-    %             \\
-    %             &\underset{\text{(h)}}{\le}
-    %             \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
-    %                 \\ &\quad
-    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-    %                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-    %             \\
-    %             &= (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x)) + F(\bar x) - F(x_k) \\&\quad
-    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-    %                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-    %             \\
-    %             &\underset{\text{(e)}}{=} 
-    %             (1 - \alpha_k)\left(
-    %                 F(x_{k - 1}) - F(\bar x) 
-    %                 + \frac{L_k\rho_{k - 1}}{L_{k - 1}}\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
-    %             \right) \\ &\quad
-    %                 + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %             \\
-    %             &\le 
-    %             (1 - \alpha_k)\left(
-    %                 F(x_{k - 1}) - F(\bar x) 
-    %                 + \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)
-    %                 \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
-    %             \right) \\&\quad
-    %                 + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %             \\
-    %             &\le (1 - \alpha_k)\left(
-    %                 \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(F(x_{k - 1}) - F(\bar x))
-    %                 + \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)
-    %                 \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
-    %             \right) \\&\quad 
-    %                 + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %             \\
-    %             &= 
-    %             \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(1 - \alpha_k)\left(
-    %                 F(x_{k - 1}) - F(\bar x) 
-    %                 + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
-    %             \right) \\&\quad
-    %                 + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2. 
-    %         \end{align*}
-    %         }
-    %         Finally, for the base case, when $\alpha_0 = 1$, it has $y_0 = v_{-1} = x_{-1}$, and it makes $z_0 = \bar x$ therefore this makes the proximal gradient inequality into:
-    %         \begin{align*}
-    %             0 &\le F(z_0) - F(x_{0}) - \frac{L_0}{2}\Vert z_0 - x_0\Vert^2 + \frac{L_0 - \mu}{2}\Vert z_0 - y_0\Vert^2
-    %             \\
-    %             &= F(\bar x) - F(x_0) - \frac{L_0}{2}\Vert \bar x - x_0\Vert^2 + \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
-    %         \end{align*}
-
-    %         \par
-    %         Going back to prove the intermediate results, the following will be useful. 
-    %         From Definition \ref{def:st-method} it has for all $k \ge 0$
-    %         \begin{align}\label{thm:onestep-napg-cnvg-i}
-    %             \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}.    
-    %         \tag{i}\end{align}
-    %         Then it has: 
-    %         \begin{align*}\label{thm:onestep-napg-cnvg-j}
-    %             (1 + \tau_k)^{-1}
-    %             &\underset{\eqref{thm:onestep-napg-cnvg-i}}{=} 
-    %             \left(
-    %                 1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
-    %             \right)^{-1} = \left(
-    %                 \frac{L_k\alpha_k - \mu + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
-    %             \right)^{-1}
-    %             = \frac{L_k\alpha_k - \mu}{L_k - \mu}.
-    %         \tag{j}\end{align*}
-    %         And also
-    %         \begin{align*}\label{thm:onestep-napg-cnvg-k}
-    %             \tau_k(1 + \tau_k)^{-1} 
-    %             &\underset{\eqref{thm:onestep-napg-cnvg-i}, \eqref{thm:onestep-napg-cnvg-j}}= 
-    %             \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
-    %             \frac{L_k\alpha_k - \mu}{L_k - \mu}
-    %             = \frac{L_k(1 - \alpha_k)}{L_k - \mu}. 
-    %         \tag{k}\end{align*}
-    %         \textbf{Proof of (d)}
-    %         For all $k \ge 1$, from Definition \ref{def:st-method} it has 
-    %         \begin{align*}
-    %             0 &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1} - y_k
-    %             \\
-    %             &\underset{\eqref{thm:onestep-napg-cnvg-k}}{=} 
-    %             (1 + \tau_k)^{-1} v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k - \mu} x_{k - 1} - y_k
-    %             \\
-    %             &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1} \\ 
-    %                 &\quad 
-    %                 + \left(
-    %                     \frac{L_k(1 - \alpha_k)}{L_k - \mu} - (1 - \alpha_k)
-    %                 \right) x_{k - 1} - y_k
-    %             \\
-    %             &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1}\\
-    %                 &\quad 
-    %                 + (1 - \alpha_k)\left(
-    %                     \frac{L_k}{L_k - \mu} - 1
-    %                 \right) x_{k - 1} - y_k
-    %             \\
-    %             &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1} + 
-    %             \frac{\mu(1 - \alpha_k)}{L - \mu}x_{k - 1} - y_k
-    %             \\
-    %             \iff 
-    %             (1 - \alpha_k)x_{k - 1} - y_k 
-    %             &= - (1 + \tau_k)^{-1}v_{k - 1} - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}.
-    %         \end{align*}
-    %         Recall the definition for $z_k$ at the start of the proof and, use the above results it yields: 
-    %         \begin{align*}
-    %             z_k - y_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
-    %             \\
-    %             &= \alpha_k \bar x - (1 + \tau_k)^{-1}v_{k - 1} - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
-    %             \\
-    %             &\underset{\eqref{thm:onestep-napg-cnvg-j}}{=}
-    %             \alpha_k \bar x - \frac{L_k\alpha_k - \mu}{L_k - \mu}v_{k - 1} 
-    %             - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
-    %             \\
-    %             &= \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
-    %             + \left(
-    %                 \alpha_k - \frac{L_k\alpha_k - \mu}{L_k - \mu}
-    %             \right)\bar x - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
-    %             \\
-    %             &= 
-    %             \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
-    %             +
-    %             \frac{\alpha_kL_k - \alpha_k \mu - L_k\alpha_k + \mu}{L_k - \mu}
-    %             \bar x - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
-    %             \\
-    %             &= \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
-    %             +
-    %             \frac{\mu(1 - \alpha_k)}{L_k - \mu}(\bar x - x_{k - 1}). 
-    %         \end{align*}
-    %         \textbf{Proof of (e)}. 
-    %         The proof is direct using the equality with $x_k$ in Definition \ref{def:st-method}. 
-    %         \begin{align*}
-    %             z_k - x_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
-    %             \\
-    %             &= \alpha_k \bar x + x_{k  1} - x_k - \alpha_k x_{k - 1}
-    %             \\
-    %             &= \alpha_k(\bar x - \alpha_k^{-1}(x_k - x_{k - 1}) - x_{k - 1})
-    %             \\
-    %             &= \alpha_k (\bar x - v_k).
-    %         \end{align*}
-    %         \textbf{Proof of (f)}. 
-    %         The proof is direct and it has: 
-    %         \begin{align*}
-    %             \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} - \frac{\mu\alpha_k(1 - \alpha_k)}{2}
-    %             &= 
-    %             \frac{1}{2(L_k - \mu)}\left(
-    %                 \mu^2(1 - \alpha_k)^2 - (L_k - \mu)\mu \alpha_k(1 - \alpha_k)
-    %             \right)
-    %             \\
-    %             &= \frac{1 - \alpha_k}{2(L_k - \mu)}\left(
-    %                 \mu^2 - \mu^2\alpha_k - (L_k \mu \alpha_k - \mu^2 \alpha_k)
-    %             \right)
-    %             \\
-    %             &= 
-    %             \frac{1 - \alpha_k}{2(L_k - \mu)}\left(
-    %                 \mu^2 - L_k\mu\alpha_k
-    %             \right)
-    %             \\
-    %             &= \frac{(1 - \alpha_k)\mu(\mu - L_k\alpha_k)}{2(L_k - \mu)} 
-    %             \\
-    %             &= \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}. 
-    %         \end{align*}
-    %         \textbf{Proof of (g)}
-    %         The proof is direct: 
-    %         \begin{align*}
-    %             \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} - \frac{\alpha_{k - 1}^2 L_k \rho_{k - 1}(1 - \alpha_k)}{2}
-    %             &\underset{\text{(c)}}{=} \frac{(L\alpha_k - \mu)^2}{2(L_k - \mu)} - \frac{L_k\alpha_k(\alpha_k - \mu/L_k)}{2}
-    %             \\
-    %             &= \frac{1}{2(L_k - \mu)}\left(
-    %                 (L_k\alpha_k - \mu)^2 - (L_k - \mu)L_k\alpha_k(\alpha_k - \mu/L_k)
-    %             \right)
-    %             \\
-    %             &= 
-    %             \frac{1}{2(L_k - \mu)}\left(
-    %                 (L_k\alpha_k - \mu)^2 - (L_k - \mu)\alpha_k(L_k\alpha_k - \mu)
-    %             \right)
-    %             \\
-    %             &= \frac{L_k\alpha_k - \mu}{2(L_k - \mu)}\left(
-    %                 L_k\alpha_k - \mu - (L - \mu)\alpha_k
-    %             \right)
-    %             \\
-    %             &= \frac{L_k\alpha_k - \mu}{2(L_k - \mu)}\left(
-    %                 \mu\alpha_k - \mu
-    %             \right)
-    %             \\
-    %             &= \frac{(L\alpha_k - \mu)\mu(\alpha_k - 1)}{2(L_k - \mu)}. 
-    %         \end{align*}
-    %         \textbf{Proof of (h)}. 
-    %         For all $k \ge 1$, by (c), the definition of the R-WAPG sequence, $\alpha_k \in (\mu/L_k, 1)$, then it has $L_k\alpha_k \in (\mu, L_k)$, so $L_k\alpha_k - \mu > 0$, and $\alpha_k - 1 < 0$.
-    %         Finally, we have $L_k \ge \mu$, therefore, the fraction is negative. 
-    %     \end{proof}
-
-    \subsection{stochastic accelerated proximal gradient}
+    \subsection{Stochastic accelerated proximal gradient}
         The following assumption about the objective function is fundamental in incremental gradient method for Machine Learning, data science other similar tasks. 
@@
         This assumption is stronger than Assumption \ref{ass:smooth-plus-nonsmooth}. 
-        It still appears everywhere in practice, for example, in the case of convex feasibility problem $\bigcap_{i = 1}^n C_i$. 
+        It still appears everywhere in practice, for example if $F_i$ are all indicator function of convex set, then it solves feasibility problem $\bigcap_{i = 1}^n C_i$ and, in this case, the proximal gradient operator becomes a projection onto the convex set $C_i$.
         In practice, each of the strong convexity constant $\mu^{(i)}$ may not be easily accessible. 
+        And we further note that if $\mu > 0$ strongly convex, then there exists at least one $\mu^{(i)} \ge 0$. 
         \par
@@
         \end{assumption}
-
         \begin{definition}[SNAPG-V2]\label{def:snapg-v2}
@@
         \end{definition}
-
         \begin{lemma}[range of the momentum sequence in SNAPG-V2]\;\label{lemma:snapg-v2-seq-range}\\
@@
                 \end{align*}
+                \item ... \todoinline{This part is not finished yet. }
             \end{enumerate}
         \end{lemma}
-
+        \newpage
         \begin{theorem}[SNAPG-V2 one step convergence]\label{thm:snapg2-one-step}
@@
                     \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
+            \end{align*}
+            And for $k = 0$, it has 
+            \begin{align*}
+                \mathbb E \left[ F_{I_0}\right] - F(\bar x) 
+                + \frac{L_0}{2}\mathbb E \left[\Vert \bar x - x_0\Vert^2\right]
+                &\le \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
             \end{align*}
@@
             \par
-            Combing the above results on the expectation of RHS, and LHS of \eqref{ineq:snapg2-one-step-presult1}, we have the one step inequaity in expectation: 
+            Combing the above results on the expectation of RHS, and LHS of \eqref{ineq:snapg2-one-step-presult1}, we have the one step inequality in expectation: 
             \begin{align*}
@@
             When $k = 0$, by assumption it had $\alpha_0 = 1$ hence $\tau_0$ in Definition \ref{def:snapg-v2} has $\tau_0 = 0$ which makes $y_0 = v_{- 1} = x_{-1}$. 
-
+            Therefore, it makes $x_0 = T_{L_0}(y_0 | F_{I_0}) = T_{L_0}(v_{-1} | F_{I_0})$. 
+            Similarly, it has also $z_0 = \bar x$.
+            Applying Theorem \ref{thm:pg-ineq} with $z = z_0$ and, assume a successful line search with $L_0$, it yields: 
+            \begin{align*}
+                0 &\le F_{I_0}(z_0) - F_{I_0}(x_0) - \frac{L_0}{2}\Vert z_0 - x_0\Vert^2 + \frac{L_0 - \mu^{(I_0)}}{2}\Vert z_0 - y_0\Vert^2
+                \\
+                &= F_{I_0}(\bar x) - F_{I_0}(x_0) - \frac{L_0}{2}\Vert \bar x - x_0\Vert^2 + \frac{L_0 - \mu^{(I_0)}}{2}\Vert \bar x - v_{-1}\Vert^2. 
+            \end{align*}
+            Re-arranging and taking the expectation it yields: 
+            \begin{align*}
+                \mathbb E \left[
+                    F_{I_0}(x_0) - F_{I_0}(\bar x) + \frac{L_0}{2}\Vert \bar x - x_0\Vert^2
+                \right]
+                &\underset{\text{(h)}}{=}
+                \mathbb E \left[ F_{I_0}\right] - F(\bar x) 
+                + \frac{L_0}{2}\mathbb E \left[\Vert \bar x - x_0\Vert^2\right]
+                \\
+                &\le \frac{L_0 - \mathbb E \left[\mu^{(I_0)}\right]}{2}\Vert \bar x - v_{-1}\Vert^2
+                \\
+                &= \frac{L_0 - \mathbb E \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
+            \end{align*}
             % INTERMEDIATE RESULTS
@@
     \subsection{\textcolor{purple}{So, what to do next?}}
+        Hi Arron would you like to add me for the co-authorship to continue this line of work and see how Nesterov's Accelerated Technique may work out for the stochastic gradient method? 
+        These results are solid results but, they are still partial results and, below are the potential I foresee for this these ideas. 
+        \begin{enumerate}
+            \item Narrow down the sequence $\alpha_k$ and make sure that it can allow the quantity: 
+            \begin{align*}
+                \mathbb E_k\left[
+                        \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
+                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
+            \end{align*}
+            is negative, or at least bounded. I am not sure how this will work out, but I have some solid ideas around it. 
+            \item Roll up the inequality in Theorem \ref{thm:snapg2-one-step} recursively and, determine the convergence rate through $\alpha_k$ that makes the previous item true. 
+            In addition, I have the hunches that the convergence rate involves the variance of $\mu^{(I_k)}$ and, it will slower than the non-stochastic case of the algorithm. 
+        \end{enumerate}
+        For the future we can: 
+        \begin{enumerate}
+            \item Extend the definition of strong convexity to relative strong convexity with respect to a quasi-norm.
+This would extend interpolation hypothesis in Assumption \ref{ass:interp-hypothesis} where, even if $\mu > 0$, it doesn't mean that $F$ has a unique solution through strong convexity.
+This is entirely possible and appeared in the literatures before so, I can give you the words of confidence.
+            \item Show the convergence of the method for objective function based on quasi-strong convexity.
+This is a much weaker assumption it works well in practice for the common known problems in convex programming.
+        \end{enumerate}
 

### 2025-07-03 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, start of the day changes

@@
             Suppose that $(L_k)_{k \ge 0}$ is a sequence such that $L_k > 0$ for all $k \ge 0$. 
-            Let $(\alpha_k)_{k \ge 0}$ be a sequence such that $\alpha_0 \in (0, 1]$ and, for all $k \ge 1$, it's recursively satisfies equality: 
+            Let $(\alpha_k)_{k \ge 0}$ be a sequence such that $\alpha_0 \in (0, 1]$ and, for all $k \ge 1$, it satisfies recursively the equality: 
             \begin{align*}
@@
             Suppose that an algorithm satisfying Definition \ref{def:snapg-v2} uses this $F$. 
+            Let $\mathbb E_k$ denotes the expectation conditioned on $I_0, I_1, \ldots, I_{k - 1}$. 
             Then, for all $k \ge 1$, it has the following inequality 

### 2025-07-04 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
         \end{remark}
+        % \begin{definition}[similar triangle representation of NAPG]\;\label{def:st-method}\\
+        %     Let $(\alpha_k)_{k \ge 0}$ be an R-WAPG sequence. 
+        %     Suppose that the base case $v_{-1}, x_{k - 1}\in \RR^n$ is given to initialize the algorithm. 
+        %     Then the algorithm produces the sequence of iterates $(y_k, x_k, v_k)_{k \ge 0}$ and auxiliary parameter sequence $L_k, \tau_k$ satisfying these inequalities: 
+        %     \begin{align*}
+        %         & \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}, 
+        %         \\
+        %         & y_k = (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1},
+        %         \\
+        %         & D_f(x_k, y_k) \le L_k/2\Vert x_k - y_k\Vert^2, 
+        %         \\
+        %         & x_k = T_{L_k}(y_k),
+        %         \\
+        %         & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
+        %     \end{align*} 
+        % \end{definition}
+        % The following theorems are critical in analyzing the behavior of algorithm in Definition \ref{def:st-method}.
 
-        \begin{definition}[similar triangle representation of NAPG]\;\label{def:st-method}\\
-            Let $(\alpha_k)_{k \ge 0}$ be an R-WAPG sequence. 
-            Suppose that the base case $v_{-1}, x_{k - 1}\in \RR^n$ is given to initialize the algorithm. 
-            Then the algorithm produces the sequence of iterates $(y_k, x_k, v_k)_{k \ge 0}$ and auxiliary parameter sequence $L_k, \tau_k$ satisfying these inequalities: 
-            \begin{align*}
-                & \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}, 
-                \\
-                & y_k = (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1},
-                \\
-                & D_f(x_k, y_k) \le L_k/2\Vert x_k - y_k\Vert^2, 
-                \\
-                & x_k = T_{L_k}(y_k),
-                \\
-                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
-            \end{align*} 
-        \end{definition}
-        The following theorems are critical in analyzing the behavior of algorithm in Definition \ref{def:st-method}. 
         \begin{theorem}[proximal gradient inequality]\label{thm:pg-ineq}
@@
                 \\
-                &= \frac{L_0 - \mathbb E \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
+                &= \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
             \end{align*}

### 2025-07-04 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, late night final additions

@@
     This chapter extends ideas by the end of Necoara et al.'s paper \cite{necoara_linear_2019}.
-    \section{Reducing LP to linear feasibility problems}
     We first introduce the linear feasibility problem as our primary problem. 
@@
     \end{definition}
-        The KKT of a linear programming problem is an instance of a linear feasibility problem, with $\mathcal K$ being a cross product of one of $\RR, \RR_+, \RR_-$ and $p = 1$ making $x \in \RR^{n}$.
-        A feasibility semidefinite program with linear constraint is another example. 
+    Next, we will give some examples of mathematical programming models that fit the above problem type. 
+    \begin{definition}[semidefinite programming]\label{def:SPD}
+
+    \end{definition}
+    \begin{definition}[linear feasibility problen]\label{def:LSP}
+
+    \end{definition}
+
+    \section{Reducing LP to linear feasibility problems}
+
         \subsection{Example, linear programming is a linear conic feasibility problem}

### 2025-07-05 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
 \begin{document}
-\title{{\fontfamily{ptm}\selectfont Lorum ipsum}}
+\title{{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis}}
 
 \author{
-    HONGDA LI
+    Author
     \thanks{
@@
 \begin{abstract} 
-    \noindent
-    Lorem ipsum dolor sit amet, dicta iudicabit consequat ex vix, veniam legimus appetere has id, an pri graece epicuri detraxit.
-Ea aliquam expetendis posidonium eos, nam invenire corrumpit imperdiet ei.
-Et constituto dissentias usu, mel solum erant et.
-Mel dolorem menandri in.
-    \cite{nesterov_lectures_2018}
-    \todo{This is just psuedo text. This is just psuedo text. This is just psuedo text. This is just psuedo text. }
+    This file is for communication purposes between collaborators.
+
 \end{abstract}
@@
         \begin{assumption}[smooth add nonsmooth]\label{ass:smooth-plus-nonsmooth}
-            The function $F = f + g$ where $f:\RR^n \rightarrow \RR$ is a $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
+            The function $F = f + g$ where $f:\RR^n \rightarrow \RR$ is an $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
             The function $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function. 
@@
         \begin{assumption}[sum of many]\label{ass:sum-of-many}
-            Define $F := (1/n)\sum_{i = 1}^{n} F_i$ where $F_i = f_i + g_i$.
-            Assume that for all $i = 1, \ldots, n$, each $f_i:\RR^n \rightarrow \RR$ are $K^{(i)}$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K^{(i)} > \mu^{(i)}$ and, $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function.
-            Consequently, the function $f$ can be written as $F = g + f$ with $f = (1/n)\sum_{i = 1}^{n} f_i, g = (1/n)\sum_{i = 1}^{n}f_i + g_i$ there, it also satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = (1/2)\sum_{i = 1}^n K^{(i)}$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$.
+            Define $F := (1/n)\sum_{i = 1}^{n} F_i$ where each $F_i = f_i + g_i$.
+            Assume that for all $i = 1, \ldots, n$, each $f_i:\RR^n \rightarrow \RR$ are $K^{(i)}$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K^{(i)} > \mu^{(i)}$ and, $g_i:\RR^n \rightarrow \overline \RR$ is a closed convex proper function.
+            Consequently, the function $f$ can be written as $F = g + f$ with $f = (1/n)\sum_{i = 1}^{n} f_i, g = (1/n)\sum_{i = 1}^{n}g_i$ therefore, it also satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = (1/n)\sum_{i = 1}^n K^{(i)}$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$.
         \end{assumption}
         This assumption is stronger than Assumption \ref{ass:smooth-plus-nonsmooth}. 
-        It still appears everywhere in practice, for example if $F_i$ are all indicator function of convex set, then it solves feasibility problem $\bigcap_{i = 1}^n C_i$ and, in this case, the proximal gradient operator becomes a projection onto the convex set $C_i$.
+        It still appears in practice, for example if $F_i$ are all indicator function of convex set, then it solves feasibility problem $\bigcap_{i = 1}^n C_i$ and, in this case, the proximal gradient operator becomes a projection onto the convex set $C_i$.
         In practice, each of the strong convexity constant $\mu^{(i)}$ may not be easily accessible. 
@@
         The interpolation hypothesis from Machine Learning stated that the model has the capacity to perfect fit all the observed data. 
+        The following assumption state the interpolation hypothesis in our context. 
         \begin{assumption}[interpolation hypothesis]\label{ass:interp-hypothesis}
@@
             In addition, assuming that it has $0 = \inf_{x}F(x)$ and, there exists some $\bar x \in \RR^n$ such that for all $i = 1, \ldots, n$ it satisfies $0 = f_i(\bar x)$. 
-            Obviously, all such $\bar x$ forms the set of minimizers of $F$. 
         \end{assumption}
@@
             \par
-            Combing the above results on the expectation of RHS, and LHS of \eqref{ineq:snapg2-one-step-presult1}, we have the one step inequality in expectation: 
+            Combining the above results on the expectation of RHS, and LHS of \eqref{ineq:snapg2-one-step-presult1}, we have the one-step inequality in expectation: 
             \begin{align*}

### 2025-07-07 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
             The theorem is the same as in Nesterov's book \cite[Theorem 2.2.13]{nesterov_lectures_2018}, but with the use of proximal gradient mapping and proximal gradient instead of project gradient hence making it equivalent to the theorem in Beck's book \cite[Theorem 10.16]{beck_first-order_2017}.
-            The only generalization here is parameter $B$ which made to accommodate algorithm that implements Definition \ref{def:st-method} with some line search routine. 
+            The only generalization here is parameter $B$ which made to accommodate algorithm that implements Definition \ref{def:snapg-v2} with line search routine to determine $L_k$. 
             Each of the reference books gives a proof of the theorem. 
@@
         \end{assumption}
+        % --------------------------------------------------------------------------------------------------------------
         \begin{definition}[SNAPG-V2]\label{def:snapg-v2}
@@
         \end{definition}
+        % --------------------------------------------------------------------------------------------------------------
         \begin{lemma}[range of the momentum sequence in SNAPG-V2]\;\label{lemma:snapg-v2-seq-range}\\
@@
         \end{lemma}
-        \newpage
+        The following lemma state the relationships of the iterates generated by SNAPG-V2. 
+        They are needed for the convergence proof. 
+        % --------------------------------------------------------------------------------------------------------------
+        \begin{lemma}[properties of the iterates]\label{lemma:snapg2-itrs-props}
+            Suppose that the iterates $(z_k, x_k, y_k)_{k \ge 0}$ and sequence $(\alpha_k)_{k \ge 1}$ are produced by an algorithm satisfying Definition \ref{def:snapg-v2}. 
+            Let $\bar x \in \RR^n$.
+            Define the sequence $z_k = \alpha_k\bar x + (1 - \alpha_k)x_{k - 1}$. 
+            Then, the following are true: 
+            \begin{enumerate}
+                \item\label{lemma:snapg2-itrs-props-item1} For all $k \ge 1$ it has: 
+                \begin{align*}
+                        z_k - y_k 
+                        = 
+                        \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+                        + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
+                \end{align*}
+                \item\label{lemma:snapg2-itrs-props-item2} For all $k \ge 1$, it has: $z_k - x_k = \alpha_k(x - \bar x)$
+            \end{enumerate}
+        \end{lemma}
+        \begin{proof}
+            \begin{proof}[proof of \ref{lemma:snapg2-itrs-props-item1}]
+                From Definition \ref{def:snapg-v2}, it has
+                \begin{align*}
+                    (1 + \tau_k)^{-1}
+                    &=
+                    \left(
+                        1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
+                    \right)^{-1} = \left(
+                        \frac{L_k\alpha_k - \mu^{(i)} + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
+                    \right)^{-1}
+                    = \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}. 
+                \end{align*}
+                Therefore, for all $k \ge 0$, $y_k$ has 
+                \begin{align*}
+                    0 &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1} - y_k
+                    \\
+                    &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} 
+                    \left(
+                        v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}} x_{k - 1}
+                    \right) - y_k
+                    \\
+                    &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1}
+                    + \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1} - y_k
+                    \\
+                    &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+                    + 
+                    \left(
+                        \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} - (1 - \alpha_k)
+                    \right) x_{k - 1} - y_k
+                    \\
+                    &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+                    + 
+                    (1 - \alpha_k)\left(
+                        \frac{L_k - L_k + \mu^{(i)}}{L_k - \mu^{(i)}}
+                    \right) x_{k - 1} - y_k
+                    \\
+                    &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+                    + 
+                    \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}x_{k - 1} - y_k. 
+                \end{align*}
+                Therefore, we establish the equality 
+                \begin{align*}
+                    (1 - \alpha_k)x_{k - 1} - y_k &= 
+                    - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
+                    - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}. 
+                \end{align*}
+                On the second equality below, we will the above equality, it goes: 
+                \begin{align*}
+                    z_k - y_k &= 
+                    \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
+                    \\
+                    &= \alpha_k \bar x 
+                    - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
+                    - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
+                    \\
+                    &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+                    + \left(
+                        \alpha_k - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}
+                    \right)\bar x
+                    - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
+                    \\
+                    &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+                    + \left(
+                        \frac{\alpha_kL_k - \alpha_k \mu^{(i)} - L_k\alpha_k + \mu^{(i)}}{L_k - \mu^{(i)}}
+                    \right)\bar x
+                    - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
+                    \\
+                    &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+                    + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}\bar x
+                    - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
+                    \\
+                    &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+                    + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
+                \end{align*}
+            \end{proof}
+            \begin{proof}[proof of \ref{lemma:snapg2-itrs-props-item2}]
+                From Definition \ref{def:snapg-v2} it has directly: 
+                \begin{align*}
+                    z_k - x_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
+                    \\
+                    &= \alpha_k \bar x + x_{k - 1} - x_k - \alpha_k x_{k - 1}
+                    \\
+                    &= \alpha_k(\bar x - \alpha_k^{-1}(x_k - x_{k - 1}) - x_{k - 1})
+                    \\
+                    &= \alpha_k (\bar x - v_k).
+                \end{align*}
+            \end{proof}
+        \end{proof}
+        % --------------------------------------------------------------------------------------------------------------
         \begin{theorem}[SNAPG-V2 one step convergence]\label{thm:snapg2-one-step}
@@
         \begin{proof}
-            Let's suppose that $I_k = i$ and, for all $k \ge 0$ let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ where $\bar x$ is a minimizer of $F$. 
-            With following intermediate results the proof can be built easily. 
-            Results (d)-(g) is showed at the end. 
+            Let's suppose that $I_k = i$ and, for all $k \ge 0$. 
+            Let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ where $\bar x$ is a minimizer of $F$. 
+            The proof is long so, we use letters and subscript under relations such as $\underset{(\cdot)}{=}, \underset{(\cdot)}{\ge}$ to indicate which result is used going from the previous expression to the next.
+            We list the following intermediate results, (d)-(g) are proved at the end of the proof. 
             \begin{itemize}
@@
 It is a special case of Definition \ref{def:rwapg-seq} with $\rho_{k - 1} = L_{k - 1}/L_k$.
-                \item[(d)] From Definition \ref{def:snapg-v2} it has the following equality 
+                \item[(d)] Prove in Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item1} we use the equality:
                 \begin{align*}
@@
                 \end{align*}
-                \item [(e)] From Definition \ref{def:snapg-v2} it has: $(\forall k \ge 1)\; z_k - x_k = \alpha_k (\bar x - v_k)$. 
+                \item [(e)] From Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item2}, we use: $(\forall k \ge 1)\; z_k - x_k = \alpha_k (\bar x - v_k)$. 
                 \item [(f)] Using direct algebra, we have for all $k \ge 1$: 
@@
             % INTERMEDIATE RESULTS
-            \par
-            \textbf{Proof of (d)}.
-            From Definition \ref{def:snapg-v2}, it has
-            \begin{align*}
-                (1 + \tau_k)^{-1}
-                &=
-                \left(
-                    1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
-                \right)^{-1} = \left(
-                    \frac{L_k\alpha_k - \mu^{(i)} + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
-                \right)^{-1}
-                = \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}. 
-            \end{align*}
-            Therefore, for all $k \ge 0$, $y_k$ has 
-            \begin{align*}
-                0 &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1} - y_k
-                \\
-                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} 
-                \left(
-                    v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}} x_{k - 1}
-                \right) - y_k
-                \\
-                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1}
-                + \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1} - y_k
-                \\
-                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
-                + 
-                \left(
-                    \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} - (1 - \alpha_k)
-                \right) x_{k - 1} - y_k
-                \\
-                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
-                + 
-                (1 - \alpha_k)\left(
-                    \frac{L_k - L_k + \mu^{(i)}}{L_k - \mu^{(i)}}
-                \right) x_{k - 1} - y_k
-                \\
-                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
-                + 
-                \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}x_{k - 1} - y_k. 
-            \end{align*}
-            Therefore, we establish the equality 
-            \begin{align*}
-                (1 - \alpha_k)x_{k - 1} - y_k &= 
-                - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
-                - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}. 
-            \end{align*}
-            On the second equality below, we will the above equality, it goes: 
-            \begin{align*}
-                z_k - y_k &= 
-                \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
-                \\
-                &= \alpha_k \bar x 
-                - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
-                - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
-                \\
-                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-                + \left(
-                    \alpha_k - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}
-                \right)\bar x
-                - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
-                \\
-                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-                + \left(
-                    \frac{\alpha_kL_k - \alpha_k \mu^{(i)} - L_k\alpha_k + \mu^{(i)}}{L_k - \mu^{(i)}}
-                \right)\bar x
-                - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
-                \\
-                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-                + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}\bar x
-                - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
-                \\
-                &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-                + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
-            \end{align*}
-            % INTERMEDIATE RESULTS
-            \textbf{Proof of (e)}.
-            From Definition \ref{def:snapg-v2} it has directly: 
-            \begin{align*}
-                z_k - x_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
-                \\
-                &= \alpha_k \bar x + x_{k - 1} - x_k - \alpha_k x_{k - 1}
-                \\
-                &= \alpha_k(\bar x - \alpha_k^{-1}(x_k - x_{k - 1}) - x_{k - 1})
-                \\
-                &= \alpha_k (\bar x - v_k).
-            \end{align*}
-            % INTERMEDIATE RESULTS
-            \textbf{Proof of (f)}.
+            \begin{proof}[Proof of (f)]
                 The proof is direct algebra and, it has: 
@@
                 }    
+            \end{proof}
             % INTERMEDIATE RESULTS 
-            \textbf{Proof of (g)}.
+            \begin{proof}[Proof of (g)]
                 From the property of the $\alpha_k$ sequence stated in item (c), we have: 
+                {\allowdisplaybreaks
                 \begin{align*}
@@
                 \end{align*}   
+                } 
+            \end{proof}
         \end{proof}

### 2025-07-08 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes, a lot

@@
     \subsection{In preparations}
+        Assumption \ref{ass:smooth-plus-nonsmooth} states the standard assumption of smooth plus non-smooth structured optimization problems for proximal gradient based algorithm. 
+        Assumption \ref{ass:smooth-plus-nonsmooth-x} adds the assumption for the existence of minimizers. 
+        Definition \ref{def:pg-opt} is the definition of the proximal gradient operator, which is equivalent to the gradient descent operator when the non-smooth part of the objective is the zero function.
+        \par
+        Finally, to show the convergence of a stochastic case of the Nesterov's accelerated proximal gradient, we prepared Lemma \ref{thm:jesen} and, \ref{thm:pg-ineq}. 
+        They are crucial in the derivation of the convergence. 
+        The derivation for the convergence rate of a stochastic accelerated variant of Nester's accelerated  proximal gradient method is in the next section. 
         \begin{assumption}[smooth add nonsmooth]\label{ass:smooth-plus-nonsmooth}
@@
 
-        \begin{definition}[Proximal gradient operator]
+        \begin{definition}[Proximal gradient operator]\label{def:pg-opt}
             Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
@@
 
-        \begin{definition}[R-WAPG sequence]\label{def:rwapg-seq}
-            Let $(L_k)_{k \ge 0}$ be a sequence such that $L_k > \mu$ for all $k$. 
-            Let $\alpha_0 \in (0, 1]$, $(\alpha_k)_{k \ge 1}$ has $\alpha_k \in (\mu/ L_k, 1)$. 
-            Then define for all $k \ge 0$: 
-            \begin{align*}
-                \rho_k(1 - \alpha_{k + 1})\alpha_k^2 = \alpha_{k + 1}(\alpha_{k + 1} - \mu/L_k). 
-            \end{align*}
-        \end{definition}
-        \begin{remark}
-            When $\rho_k = 1$, the recursive relation between $\alpha_k, \alpha_{k - 1}$ is the same as the well known Nesterov's sequence used in algorithm such as FISTA and Nesterov's accelerated gradient.
-            See Li and Wang \cite{li_relaxed_2025} for more information. 
-        \end{remark}
+        % \begin{definition}[R-WAPG sequence]\label{def:rwapg-seq}
+        %     Let $(L_k)_{k \ge 0}$ be a sequence such that $L_k > \mu$ for all $k$. 
+        %     Let $\alpha_0 \in (0, 1]$, $(\alpha_k)_{k \ge 1}$ has $\alpha_k \in (\mu/ L_k, 1)$. 
+        %     Then define for all $k \ge 0$: 
+        %     \begin{align*}
+        %         \rho_k(1 - \alpha_{k + 1})\alpha_k^2 = \alpha_{k + 1}(\alpha_{k + 1} - \mu/L_k). 
+        %     \end{align*}
+        % \end{definition}
+        % \begin{remark}
+        %     When $\rho_k = 1$, the recursive relation between $\alpha_k, \alpha_{k - 1}$ is the same as the well known Nesterov's sequence used in algorithm such as FISTA and Nesterov's accelerated gradient.
+        %     See Li and Wang \cite{li_relaxed_2025} for more information. 
+        % \end{remark}
         % \begin{definition}[similar triangle representation of NAPG]\;\label{def:st-method}\\
@@
 
+        \begin{definition}[semi quasi strong convexity (\textcolor{red}{NEW})]\label{def:sq-scnvx}
+            A function $f:\RR^n \rightarrow \overline \RR$ is semi quasi strongly convex if, there exists a constant $\mu \ge 0$ and, a non-zero linear mapping $A: \RR^n\rightarrow \RR^m$ such that for all $x \in \RR^n, y \in RR^n$ and $\lambda \in [0, 1]$ it satisfies:
+            \begin{align*}
+                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\mu\lambda(1 - \lambda)}{2} \Vert A(y - x)\Vert^2. 
+            \end{align*}
+        \end{definition}
+        \begin{remark}
+            It is strong convexity but instead of being strongly convex to the function $\mu/2\Vert \cdot\Vert^2$, it's $x \mapsto \mu/2\Vert Ax \Vert^2$ instead. 
+            This is an example of uniform convexity because it also fits in Bauchke \cite[Definition 10.7]{bauschke_convex_2017}, with $\phi = \Vert A\Vert^2\Vert x - y\Vert^2$. 
+        \end{remark}
     \subsection{Stochastic accelerated proximal gradient}
@@
             Assume that for all $i = 1, \ldots, n$, each $f_i:\RR^n \rightarrow \RR$ are $K^{(i)}$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K^{(i)} > \mu^{(i)}$ and, $g_i:\RR^n \rightarrow \overline \RR$ is a closed convex proper function.
+            \par 
             Consequently, the function $f$ can be written as $F = g + f$ with $f = (1/n)\sum_{i = 1}^{n} f_i, g = (1/n)\sum_{i = 1}^{n}g_i$ therefore, it also satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = (1/n)\sum_{i = 1}^n K^{(i)}$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$.
@@
             In addition, assuming that it has $0 = \inf_{x}F(x)$ and, there exists some $\bar x \in \RR^n$ such that for all $i = 1, \ldots, n$ it satisfies $0 = f_i(\bar x)$. 
+            \par
+            Consequently, each of the $F_i$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth-x} with $X_i$ being the set of minimizers and, under interpolation hypothesis this equates to non-empty intersections between all $X_i$, i.e: $\bigcap_{i = 1}^n X_i \neq \emptyset$.
         \end{assumption}
+        % --------------------------------------------------------------------------------------------------------------
+        What is the weakest possible sequence one can use for the accelerated proximal gradient based algorithm that utilizes a strong convexity constant? 
+        If we were to use the developed convergence framework for Nesterov's accelerated proximal gradient, negative momentum and, negative convergence (lower bound instead of upper bound) should be prohibited, and it means that the sequence $(\alpha_k)_{k \ge 0}$ which is going to appear in the proposed algorithm (See Definition \ref{def:snapg-v2}) must satisfy the condition $\alpha_k \in (0, 1]$ for all $k \ge 0$.
+        The following lemma with a blunt name should clarify the sufficient conditions required for the sequence to make sense. 
+        \begin{lemma}[weakest possible momentum sequence that makes sense \textcolor{red}{NEW}]\;\label{lemma:snapg-v2-seq-range}\\
+            Suppose that $(L_k)_{k \ge 0}$ is a sequence such that $L_k > 0$ for all $k \ge 0$. 
+            Suppose that $(\tilde\mu_k)_{k\ge 0}$ is another non-negative sequence. 
+            Let $(\alpha_k)_{k \ge 0}$ be a sequence such that $\alpha_0 \in (0, 1]$ and, for all $k \ge 1$, it satisfies recursively the equality: 
+            \begin{align*}
+                (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 
+                &= \alpha_{k}\left(\alpha_{k} - \tilde \mu_k/L_k\right). 
+            \end{align*}
+            And, the following items are true: 
+            \begin{enumerate}
+                \item The expression of $\alpha_k$ based on previous $\alpha_{k - 1}$ is given by: 
+                \begin{align*}
+                    \alpha_k = \frac{L_{k - 1}}{2L_k} \left(
+                        - \alpha_{k - 1}^2 + \frac{\tilde\mu_k}{L_{k - 1}}
+                        + \sqrt{
+                            \left(
+                                \alpha_{k - 1} - \frac{\tilde\mu_k}{L_{k - 1}}
+                            \right)^2
+                            + \frac{4\alpha_{k - 1}^2L_k}{L_{k - 1}}
+                        }
+                    \right) &\ge 0. 
+                \end{align*}
+                \item ... \todoinline{This part is not finished yet. }
+            \end{enumerate}
+        \end{lemma}
+        \begin{proof}
+            For all $k \ge 1$, re-arranging the equality it comes to solving the following equality: 
+            \begin{align*}
+                0 &= L_k\alpha_k^2 - \tilde\mu_k\alpha_k + L_{k - 1}\alpha_{k - 1}^2\alpha_k - L_{k - 1}\alpha_{k - 1}^2
+                \\
+                &= L_k\alpha_k^2 + (L_{k - 1}\alpha_{k - 1}^2 - \tilde \mu_k)\alpha_k - L_{k - 1}\alpha_{k - 1}^2
+                \\
+                \iff 0 &=
+                \alpha_k^2 + L_k^{-1}(L_{k - 1}\alpha_{k - 1}^2 - \tilde \mu_k)\alpha_k - L_k^{-1}L_{k - 1}\alpha_{k - 1}^2
+                \\
+                \iff 
+                \alpha_k &= 
+                \frac{1}{2}\left(
+                    -L^{-1}_k(L_{k - 1} \alpha_{k - 1}^2 - \tilde\mu_k)
+                    + \sqrt{
+                        L_k^{-2}(L_{k - 1}\alpha_{k - 1}^2 - \tilde \mu_k)^2
+                        + 4L_k^{-1}L_{k - 1} \alpha_{k - 1}^2
+                    }
+                \right)
+                \\
+                &= \frac{L_{k-1}}{2L_k}\left(
+                    - \alpha_{k - 1}^2 + \frac{\tilde \mu_k}{L_{k - 1}}
+                    + \sqrt{
+                        \left(
+                            \alpha_{k - 1}^2 - \frac{\tilde \mu_k}{L_{k - 1}}
+                        \right)^2 + \frac{4L_k}{L_{k - 1}}\alpha_{k - 1}^2
+                    }
+                \right)
+            \end{align*}
+            Here, we take the positive root of the quadratic so that it ensures $\alpha_k \ge 0$. 
+            This is true by induction. 
+            If $\alpha_{k - 1} \ge 0$ then the $\frac{4L_k}{L_{k - 1}}\alpha_{k - 1}^2 \ge 0$ hence, the square root is greater than the term outside it so, $\alpha_k \ge 0$ too. 
+            \par
+            Assume inductively that $\alpha_{k - 1} \ge 0$. 
+            Next, we want to find the conditions needed such that $\alpha_k < 1$. 
+            To start, we complete the square root inside the square root: 
+            \begin{align*}
+                0&\le 
+                \left(
+                    \alpha_{k - 1}^2 - \frac{\tilde \mu_k}{L_{k - 1}}
+                \right)^2 + \frac{4L_k}{L_{k - 1}}\alpha_{k - 1}^2
+                \\
+                &= \alpha_{k - 1}^4 + \left(\frac{\tilde \mu_k}{L_{k - 1}}\right)^2
+                - 2\alpha_{k - 1}^2 \frac{\tilde \mu_k}{L_{k - 1}} 
+                + \frac{4L_k}{L_{k - 1}}\alpha_{k - 1}^2
+                \\
+                &= \alpha_{k - 1}^4 + \left(\frac{\tilde \mu_k}{L_{k - 1}}\right)^2
+                + \alpha_{k - 1}^2 \left(
+                    \frac{-2\tilde \mu_k}{L_{k - 1}} + \frac{4L_k}{L_{k - 1}}. 
+                \right)
+                \\
+                &= \alpha_{k - 1}^4 + \left(\frac{\tilde \mu_k}{L_{k - 1}}\right)^2
+                + \alpha_{k - 1}^2 \left(
+                    \frac{4L_k - 2\tilde \mu_k}{L_{k - 1}}
+                \right)
+                \\
+                &= \alpha_{k - 1}^4
+                + \alpha_{k - 1}^2 \left(
+                    \frac{4L_k - 2\tilde \mu_k}{L_{k - 1}}
+                \right) 
+                + \left(
+                    \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
+                \right)^2
+                - \left(
+                    \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
+                \right)^2
+                + \left(\frac{\tilde \mu_k}{L_{k - 1}}\right)^2
+                \\
+                &= \left(
+                    \alpha_{k - 1}^2 + 
+                    \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
+                \right)^2
+                - \left(
+                    \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
+                \right)^2
+                + \left(\frac{\tilde \mu_k}{L_{k - 1}}\right)^2
+                \\
+                &= 
+                \left(
+                    \alpha_{k - 1}^2 + 
+                    \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
+                \right)^2
+                + 
+                \frac{
+                    \tilde \mu_k^2 - 4L_k^2 - \tilde \mu_k^2 + 4L_k\tilde \mu_k
+                }{L_{k - 1}^2}
+                \\
+                &= 
+                \left(
+                    \alpha_{k - 1}^2 + 
+                    \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
+                \right)^2
+                + 
+                \frac{
+                    4L_k \tilde \mu_k - 4L_k^2
+                }{L_{k - 1}^2}
+                \\
+                &= 
+                \left(
+                    \alpha_{k - 1}^2 + 
+                    \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
+                \right)^2
+                + 
+                4\left(
+                    \frac{L_k}{L_{k - 1}}\cdot \frac{\tilde \mu_k}{L_{k - 1}} - 1
+                \right)
+                \\
+                &< 
+                \left(
+                    \alpha_{k - 1}^2 + 
+                    \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
+                \right)^2. 
+            \end{align*}
+            On the last inequality, we used our assumption that the sequence $\tilde\mu_k, L_k$ satisfies $\frac{\tilde \mu_k}{L_{k - 1}} < \frac{L_{k - 1}}{L_k}$. 
+            Substitute it back into the expression previous obtained for $\alpha_k$, using the monotone property of the function $\sqrt{\cdot}$, it gives the inequality 
+            \begin{align*}
+                \alpha_k & < 
+                \frac{L_{k-1}}{2L_k}\left(
+                    - \alpha_{k - 1}^2 + \frac{\tilde \mu_k}{L_{k - 1}}
+                    + \sqrt{
+                        \left(
+                            \alpha_{k - 1}^2 + 
+                            \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
+                        \right)^2
+                    }
+                \right)
+                \\
+                &= 
+                \frac{L_{k-1}}{2L_k}\left(
+                    - \alpha_{k - 1}^2 + \frac{\tilde \mu_k}{L_{k - 1}}
+                    + \alpha_{k - 1}^2 + \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
+                \right) = 1. 
+            \end{align*}
+        \end{proof}
+        \begin{remark}
+            Let's do some sanity check for the lemma we just derived. 
+            The sequence $L_k$ will be from the Lipschitz line search routine of the accelerated proximal gradient method. 
+            \begin{enumerate}
+                \item Let's assume the obvious choice of $L_k = \max_{i = 1, \ldots,n} K^{(i)}$ for all $k = 1, 2, \ldots$ given an objective function $F$ satisfying Assumption \ref{ass:sum-of-many}. 
+                Then, the sufficient condition for the second item translates to $\tilde\mu_i/L_k < 1$. 
+                Hence, if we choose $\tilde \mu_i$ to be a constant sequence of $0$ then it works out to have $\alpha_k \in (0, 1)$ for all $k = 1, 2, \ldots$. 
+                \par
+                If $F$ has $L \ge \mu$ so, the function is non-trivial, then choose $\tilde \mu_i = \mu$, the true strong convexity parameter then it also works out. 
+                \item Let's assume that some type of monotone line search routine is used for the algorithm making $L_0 \le L_1 \le \ldots \le L_k \le \ldots$ to be a non-decreasing sequence, then it requires $\tilde \mu_k / L_{k - 1} \le L_{k - 1}/L_k$.
+                \par
+                Well, it will still make sense because one such choice could be $\tilde \mu_k = \rho\min_{i = 1, \ldots, k} L_{i - 1}/L_i$ for some $\rho \in (0, 1)$. 
+            \end{enumerate}
+
+        \end{remark}
         % --------------------------------------------------------------------------------------------------------------
@@
             Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
+            \textcolor{red}{Let $\tilde \mu \ge 0$ be a fixed constant.}
             The SNAPG generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
             \begin{align*}
-                & (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right), \\
+                & \alpha_k \in (0, 1): (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \tilde \mu/L_k\right), \\
                 & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
                 & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
-                & x_k =  T_{L_k}(y_k | F_{I_k}) \text{ s.t: } D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
+                & L_k > 0: D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
+                & x_k =  T_{L_k}(y_k | F_{I_k}), \\
                 & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
@@
         \end{definition}
-        % --------------------------------------------------------------------------------------------------------------
-        \begin{lemma}[range of the momentum sequence in SNAPG-V2]\;\label{lemma:snapg-v2-seq-range}\\
-            Suppose that $(L_k)_{k \ge 0}$ is a sequence such that $L_k > 0$ for all $k \ge 0$. 
-            Let $(\alpha_k)_{k \ge 0}$ be a sequence such that $\alpha_0 \in (0, 1]$ and, for all $k \ge 1$, it satisfies recursively the equality: 
-            \begin{align*}
-                (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right). 
-            \end{align*}
-            And, the following items are true: 
-            \begin{enumerate}
-                \item Solution to the equation with $\alpha_k > 0$ is given by: 
-                \begin{align*}
-                    \alpha_k = \frac{L_{k - 1}}{2L_k} \left(
-                        - \alpha_{k - 1}^2 + \frac{\mu}{L_{k - 1}}
-                        + \sqrt{
-                            \left(
-                                \alpha_{k - 1} - \frac{\mu}{L_{k - 1}}
-                            \right)^2
-                            + \frac{4\alpha_{k - 1}^2L_k}{L_{k - 1}}
-                        }
-                    \right). 
-                \end{align*}
-                \item ... \todoinline{This part is not finished yet. }
-            \end{enumerate}
-        \end{lemma}
+        \begin{remark}
+            $\tilde \mu_k, L_k$ are not necessary a random variable because they are determined by a line-search like conditions, consequently $(\alpha_k)_{k\ge 0}$, whether they are a random variable depends on the line search procedures.
+            Otherwise, all the iterates $(x_k, y_k, z_k)$ are random variable determined by $I_k$ when conditioned on all previous $I_{k - 1}, I_{k - 2}, \ldots, I_{0}$. 
+            \par
+            \textcolor{red}{NEW}. One may notice that $\alpha_k$ requires $L_k$ which comes before $L_k, x_k$ which are needed in advanced for $\alpha_k$. 
+            This may seems off since no algorithm can know what $L_k$ to choose in advanced to determine the line search. 
+            But, it is important to note that in here, we defined a sequence of conditions on the iterates $x_k, y_k, z_k$, and auxilary sequences $\alpha_k, L_k$ which is not a definition of any algorithm.
+            It is quantifying the conditions needed for an algorithm that actually implements it.
+            \par
+            For the trivial case where we don't need to worry about it is when $L_k = \max_{i = 1, \ldots, n} K^{(i)}$. 
+            See Chambolle, Calatroni \cite{calatroni_backtracking_2019} for an implementations of linear search with backtracking for the FISTA algorithm, it is how one would implement it in the deterministic case.
+        \end{remark}
+
         The following lemma state the relationships of the iterates generated by SNAPG-V2. 
@@
         \begin{proof}
-            \begin{proof}[proof of \ref{lemma:snapg2-itrs-props-item1}]
+            \textbf{Proof of \ref{lemma:snapg2-itrs-props-item1}}. 
             From Definition \ref{def:snapg-v2}, it has
@@
             \end{align*}
-            \end{proof}
-            \begin{proof}[proof of \ref{lemma:snapg2-itrs-props-item2}]
+            \textbf{proof of \ref{lemma:snapg2-itrs-props-item2}.}
             From Definition \ref{def:snapg-v2} it has directly: 
@@
             \end{align*}
-            \end{proof}
+
         \end{proof}
@@
                         \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
+                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
+                    + \frac{\alpha_k(\tilde\mu - \mu)}{2} 
+                    \Vert \bar x - v_{k - 1}\Vert^2. 
             \end{align*}
@@
                 + \frac{L_0}{2}\mathbb E \left[\Vert \bar x - x_0\Vert^2\right]
-                &\le \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
+                &\le 
+                \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
             \end{align*}
@@
                 \item[(c)] The sequence $(\alpha_k)_{k \ge 0}$ has $(L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right)$. 
-It is a special case of Definition \ref{def:rwapg-seq} with $\rho_{k - 1} = L_{k - 1}/L_k$.
                 \item[(d)] Prove in Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item1} we use the equality:
@@
                     {2(L_k - \mu^{(i)})}
-                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2}. 
+                    + \frac{\alpha_k(\tilde \mu_k - \mu^{(i)})}{2}. 
                 \end{align*}
@@
                         {2(L_k - \mu^{(i)})}
-                        + \frac{\alpha_k(\mu - \mu^{(i)})}{2}
-                    \right) \Vert \bar x - v_{k - 1}\Vert^2
+                        + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}
+                    \right) 
+                    \Vert \bar x - v_{k - 1}\Vert^2
                     \\ &\quad 
@@
                     \\ &\quad 
-                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                    + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
                     + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
@@
                     \\ &\quad 
-                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                    + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
                     + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2.
@@
                     \\ &\quad 
-                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                    + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
                     + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
@@
                         \\ &\quad 
-                        + \frac{\alpha_k(\mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                        + \frac{\alpha_k(\tilde \mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
                         + \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
@@
                     + \mathbb E_k \left[
-                        \frac{\alpha_k(\mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                        \frac{\alpha_k(\tilde\mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
                     \right]
@@
                     + \mathbb E_k \left[
-                        \frac{\alpha_k(\mu - \mu^{(I_k)})}{2} 
+                        \frac{\alpha_k(\tilde\mu - \mu^{(I_k)})}{2} 
                     \right]\Vert \bar x - v_{k - 1}\Vert^2
@@
                     \\ &\quad 
+                    \frac{\alpha_k(\tilde\mu - \mu)}{2} 
+                    \Vert \bar x - v_{k - 1}\Vert^2
                     + \mathbb E_k\left[
                         \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
+                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
             \end{align*}
@@
             % INTERMEDIATE RESULTS
-            \begin{proof}[Proof of (f)]
+            \textbf{Proof of (f)}. 
             The proof is direct algebra and, it has: 
@@
             }    
-            \end{proof}
             % INTERMEDIATE RESULTS 
-            \begin{proof}[Proof of (g)]
+            \textbf{Proof of (g)}.
             From the property of the $\alpha_k$ sequence stated in item (c), we have: 
@@
                 -
-                    \frac{L_k\alpha_k(\alpha_k - \mu/L_k)}{2} 
+                \frac{L_k\alpha_k(\alpha_k - \tilde \mu/L_k)}{2} 
                 \\
@@
                 + \frac{L_k\alpha_k(\alpha_k - \mu^{(i)}/L_k)}{2} 
-                    - \frac{L_k\alpha_k(\alpha_k - \mu/L_k)}{2} 
+                - \frac{L_k\alpha_k(\alpha_k - \tilde \mu/L_k)}{2} 
                 \\
@@
                 \frac{\left(
-                        \mu - \mu^{(i)}
+                    \tilde \mu - \mu^{(i)}
                 \right)}{L_k}
@@
                 \right)
-                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2}
+                + \frac{\alpha_k(\tilde \mu - \mu^{(i)})}{2}
                 \\
@@
                 {2(L_k - \mu^{(i)})}
-                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2}. 
+                + \frac{\alpha_k(\tilde \mu - \mu^{(i)})}{2}. 
             \end{align*}   
@@
         \end{proof}
-        \end{proof}
+    \subsection{convergence rate of the algorithm under various circumstances}
+
     \subsection{\textcolor{purple}{So, what to do next?}}

### 2025-07-08 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
             \begin{align*}
-                T_\beta (x | F) &= \argmin{z} \left\lbrace
+                T_\beta (x | F) &= \argmin_{z} \left\lbrace
                     g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{\beta}{2}\Vert z - x\Vert^2
@@
 
+        \begin{theorem}[Jensen's inequality]\label{thm:jesen}
+            Let $F: \RR^n \rightarrow \overline \RR$ be a $\mu \ge 0$ strongly convex function. 
+            Then, it is equivalent to the following condition. 
+            For all $x, y \in \RR^n$, $\lambda \in (0, 1)$ it satisfies the inequality 
+            \begin{align*}
+                (\forall \lambda \in [0, 1])\; 
+                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\mu\lambda(1 - \lambda)}{2} \Vert y - x\Vert^2. 
+            \end{align*}
+        \end{theorem}
+        \begin{remark}
+            If $x, y$ is out of $\dom F$, the inequality still work by convexity. 
+        \end{remark}
+        \begin{definition}[semi quasi strong convexity Jensen inequality \textcolor{red}{NEW}]\label{def:sq-scnvx}
+            Let $m, n \in \N$. 
+            A function $f:\RR^n \rightarrow \overline \RR$ is semi quasi strongly convex with linear mapping $A:\RR^m \rightarrow \RR^n$ if for all $x \in \RR^n, y \in \RR^n$ and $\lambda \in [0, 1]$ it satisfies:
+            \begin{align*}
+                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2. 
+            \end{align*}
+        \end{definition}
+        \begin{remark}
+            Choose $A = \sqrt{\mu} I$, where $I$ is the identity matrix then it is equivalent to $\mu$ strongly convex. 
+            This is an example of uniform convexity because there exists some $\sigma \ge 0$ such that it fits in Bauschke \cite[Definition 10.7]{bauschke_convex_2017} with $\phi(z) = \sigma^2z^2$. 
+            \\
+            It is called ``Semi'' because of the semi norm induced by matrix $A$, followed by ``Quasi strongly convex'' because the quasi norm $\Vert Ax\Vert^2$ is the distance of an oblique projection to the kernel of $A$ which is a quasi strongly convex function.
+        \end{remark}
+        The above definition is the special case of relatively strong convexity wrt to the Bregman divergence $D_h(x, y) = \Vert Ax - Ay\Vert^2$. 
+        \begin{theorem}[an equivalent definition for SQ-SCNVX functions]\label{thm:sq-scnvx-equiv}
+            A function $F$ is semi quasi strongly convex with $A$ if and only if the function $x \mapsto F(x) - \frac{1}{2}\Vert A x\Vert^2$ is convex. 
+        \end{theorem}
+        \begin{proof}
+            For all $\lambda \in \RR, x \in \RR^n, y \in \RR^n$ it has $-1/2\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 = (1/2)(\lambda\Vert Ax\Vert^2 + (1 - \lambda)\Vert Ay\Vert^2 - \lambda(1 - \lambda)\Vert Ax - Ay\Vert^2)$ by verifying:
+            \begin{align*}
+                & -\frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 + 
+                \left(
+                    \frac{\lambda}{2}\Vert Ax\Vert^2 + \frac{1 - \lambda}{2}\Vert Ay\Vert^2 - \frac{\lambda(1 - \lambda)}{2}\Vert Ay - Ax\Vert^2
+                \right)
+                \\
+                &= 
+                -\frac{1}{2}\left(
+                    \lambda^2\Vert Ax\Vert^2 + (1 - \lambda)^2\Vert Ay\Vert^2 - 2\lambda(1 - \lambda) \langle Ax, Ay\rangle
+                \right)
+                    \\ &\quad 
+                    + 
+                    \left(
+                        \frac{\lambda}{2} - \frac{\lambda(1 - \lambda)}{2}
+                    \right)\Vert Ax\Vert^2 + \left(
+                        \frac{1 - \lambda}{2} - \frac{\lambda(1 - \lambda)}{2}
+                    \right)\Vert Ay\Vert^2 - \lambda(1 - \lambda)\langle Ay, Ax\rangle
+                \\
+                &= - \frac{\lambda^2}{2}\Vert Ax\Vert^2 - \frac{(1 - \lambda)^2}{2}\Vert Ay\Vert^2
+                    \\ &\quad 
+                    + 
+                    \left(
+                        \frac{\lambda}{2} - \frac{\lambda - \lambda^2}{2}
+                    \right)\Vert Ax\Vert^2 + \left(
+                        \frac{1 - \lambda}{2} - \frac{\lambda - \lambda^2}{2}
+                    \right)\Vert Ay\Vert^2
+                \\
+                &= 0
+            \end{align*}
+            Using the above result we can prove the equivalency because 
+            {\small
+            \begin{align*}
+                0 &\le F(\lambda x + (1 - \lambda)y) + \lambda F(x) + (1 - \lambda)F(y) -\frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2
+                \\
+                &=  F(\lambda x + (1 - \lambda)y) - \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 
+                + \lambda F(x) - \frac{\lambda}{2}\Vert Ax\Vert^2 
+                + (1 - \lambda)F(y) - \frac{1 - \lambda}{2} \Vert Ay\Vert^2 
+                    \\ &\quad 
+                    - \frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2 + \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2
+                    + \frac{1}{2}\Vert Ax\Vert^2 + \frac{1}{2}\Vert Ay\Vert^2 
+                \\
+                &= 
+                F(\lambda x + (1 - \lambda)y) - \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 
+                    \\ &\quad 
+                    + \lambda \left(F(x) - \frac{1}{2}\Vert Ax\Vert^2\right) 
+                    + (1 - \lambda)\left(F(y) - \frac{1}{2} \Vert Ay\Vert^2\right). 
+            \end{align*}
+            }
+            So, the function $F(x) - \frac{1}{2}\Vert Ax\Vert^2$ is convex. 
+        \end{proof}
+        The following theorem classifies a class of semi quasi strongly convex function. 
+        \begin{theorem}[Affine composite differentiable SQ-SCNVX functions]\label{thm:smooth-aff-sq-scnvs-fxn}
+
+        \end{theorem}
+        \begin{proof}
+            Let $h(x) = f(Ax - b)$.
+
+        \end{proof}
+        The following definition defines the concept of relative smoothness. 
+        \begin{definition}[semi relative smoothness]\label{def:semi-rel-smooth}
+
+        \end{definition}
+        We build the proximal gradient inequality for the class of SQ-SCNVX functions. 
         \begin{theorem}[proximal gradient inequality]\label{thm:pg-ineq}
@@
         \end{remark}
-        \begin{theorem}[Jensen's inequality]\label{thm:jesen}
-            Let $F: \RR^n \rightarrow \overline \RR$ be a $\mu \ge 0$ strongly convex function. 
-            Then, it is equivalent to the following condition. 
-            For all $x, y \in \RR^n$, $\lambda \in (0, 1)$ it satisfies the inequality 
-            \begin{align*}
-                (\forall \lambda \in [0, 1])\; 
-                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\mu\lambda(1 - \lambda)}{2} \Vert y - x\Vert^2. 
-            \end{align*}
-        \end{theorem}
-        \begin{remark}
-            If $x, y$ is out of $\dom F$, the inequality still work by convexity. 
-        \end{remark}
 
-        \begin{definition}[semi quasi strong convexity (\textcolor{red}{NEW})]\label{def:sq-scnvx}
-            A function $f:\RR^n \rightarrow \overline \RR$ is semi quasi strongly convex if, there exists a constant $\mu \ge 0$ and, a non-zero linear mapping $A: \RR^n\rightarrow \RR^m$ such that for all $x \in \RR^n, y \in RR^n$ and $\lambda \in [0, 1]$ it satisfies:
-            \begin{align*}
-                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\mu\lambda(1 - \lambda)}{2} \Vert A(y - x)\Vert^2. 
-            \end{align*}
-        \end{definition}
-        \begin{remark}
-            It is strong convexity but instead of being strongly convex to the function $\mu/2\Vert \cdot\Vert^2$, it's $x \mapsto \mu/2\Vert Ax \Vert^2$ instead. 
-            This is an example of uniform convexity because it also fits in Bauchke \cite[Definition 10.7]{bauschke_convex_2017}, with $\phi = \Vert A\Vert^2\Vert x - y\Vert^2$. 
-        \end{remark}
     \subsection{Stochastic accelerated proximal gradient}
@@
                 \end{align*}
-                \item ... \todoinline{This part is not finished yet. }
+                \item If, in addition, the sequence $\tilde \mu_k$ satisfies for all $k \ge 1$, $\frac{\tilde \mu_k}{L_{k - 1}} < L_{k - 1}/ L_k$, then the sequence also satisfies for all $k \ge 1$: $\alpha_k < 1$.
             \end{enumerate}
@@
             \end{enumerate}
-
         \end{remark}
@@
             Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
-            \textcolor{red}{Let $\tilde \mu \ge 0$ be a fixed constant.}
+            Let $\tilde \mu \ge 0$ be a constant that is fixed.
             The SNAPG generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
@@
             \textcolor{red}{NEW}. One may notice that $\alpha_k$ requires $L_k$ which comes before $L_k, x_k$ which are needed in advanced for $\alpha_k$. 
-            This may seems off since no algorithm can know what $L_k$ to choose in advanced to determine the line search. 
-            But, it is important to note that in here, we defined a sequence of conditions on the iterates $x_k, y_k, z_k$, and auxilary sequences $\alpha_k, L_k$ which is not a definition of any algorithm.
+            This may seem off since no algorithm can know what $L_k$ to choose in advanced to determine the line search. 
+            But, it is important to note that in here, we defined a sequence of conditions on the iterates $x_k, y_k, z_k$, and auxiliary sequences $\alpha_k, L_k$ which is not a definition of any algorithm.
             It is quantifying the conditions needed for an algorithm that actually implements it.
@@
             For the trivial case where we don't need to worry about it is when $L_k = \max_{i = 1, \ldots, n} K^{(i)}$. 
-            See Chambolle, Calatroni \cite{calatroni_backtracking_2019} for an implementations of linear search with backtracking for the FISTA algorithm, it is how one would implement it in the deterministic case.
+            See Chambolle, Calatroni \cite{calatroni_backtracking_2019} for an implementation of linear search with backtracking for the FISTA algorithm, it is how one would implement it in the deterministic case.
         \end{remark}
@@
     \subsection{convergence rate of the algorithm under various circumstances}
+        The previous section highlighted a generic convergence results from one iteration of the algorithm, however, there are a lot of loose ends. 
+        This section will deal with those.
 

### 2025-07-09 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
     \subsection{In preparations}
-        Assumption \ref{ass:smooth-plus-nonsmooth} states the standard assumption of smooth plus non-smooth structured optimization problems for proximal gradient based algorithm. 
-        Assumption \ref{ass:smooth-plus-nonsmooth-x} adds the assumption for the existence of minimizers. 
         Definition \ref{def:pg-opt} is the definition of the proximal gradient operator, which is equivalent to the gradient descent operator when the non-smooth part of the objective is the zero function.
         \par
-        Finally, to show the convergence of a stochastic case of the Nesterov's accelerated proximal gradient, we prepared Lemma \ref{thm:jesen} and, \ref{thm:pg-ineq}. 
+        To show the convergence of a stochastic case of the Nesterov's accelerated proximal gradient, we prepared Lemma \ref{thm:jesen} and, \ref{thm:pg-ineq}. 
         They are crucial in the derivation of the convergence. 
-        The derivation for the convergence rate of a stochastic accelerated variant of Nester's accelerated  proximal gradient method is in the next section. 
+        The derivation for the convergence rate of a stochastic accelerated variant of Nesterov's accelerated  proximal gradient method is in the next section. 
+        \subsubsection{Basic definitions}
+            % --------------------------------------------------------------------------------------------------------------
+            \begin{definition}[Proximal gradient operator]\label{def:pg-opt}
+                Suppose $F = f + g$ with $\reli(\dom f) \cap \reli(\dom g) \neq \emptyset$, and $f$ is a differentiable function. 
+                Let $\beta > 0$. 
+                Then, we define the proximal gradient operator $T_{\beta}$ as 
+                \begin{align*}
+                    T_\beta (x | F) &= \argmin_{z} \left\lbrace
+                        g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{\beta}{2}\Vert z - x\Vert^2
+                    \right\rbrace. 
+                \end{align*}
+            \end{definition}
+            \begin{remark}
+                If the function $g \equiv 0$, then it yields the gradient descent operator $T_\beta(x) = x - \beta^{-1}\nabla f(x)$. 
+                In the context where it's clear what the function $F = f + g$ is, we simply write $T_\beta(x)$ for short. 
+            \end{remark}
+            % --------------------------------------------------------------------------------------------------------------
+            \begin{definition}[Bregman Divergence]
+                Let $f:\RR^n \rightarrow \overline \RR$ be a differentiable function. 
+                Then, for all the Bregman divergence $D_f: \RR^n \times \dom\nabla f \rightarrow \RR$ is defined as: 
+                \begin{align*}
+                    D_f(x, y) := f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 
+                \end{align*}
+            \end{definition}
+            \begin{remark}
+                If, $f$ is $\mu \ge 0$ strongly convex and $L$ Lipschitz smooth then, its Bregman Divergence has for all $x, y \in \RR^n$: $\mu/2 \Vert x - y\Vert^2 \le D_f(x, y) \le L/2 \Vert x - y\Vert^2$.
+            \end{remark}
+        \subsubsection{Properties of function}
+            % --------------------------------------------------------------------------------------------------------------
+            \begin{definition}[semi quasi strongly convex function \textcolor{red}{NEW}]\label{def:sq-scnvx}
+                A function $F: \RR^n \rightarrow \overline \RR$ is a semi quasi strongly convex function, abbreviated as ``SQ-SCNVX'' with respective to a linear mapping $A \in \RR^{m \times n}$ if $F - \frac{1}{2}\Vert Ax\Vert^2$ is a convex function.
+            \end{definition}
+            \begin{remark}
+                Any $\mu \ge 0$ strongly convex function is QS-SCNVX with $A = \sqrt{\mu}I$. 
+                But the converse is not true because a seminorm is not a norm. 
+                One feature of a QS-SCNVX function is that it doesn't have a unique minimizer which differs it from strong convexity. 
+                It may not have a unique minimizer because it's not necessary that $\kernel A = \{\mathbf 0\}$. 
+            \end{remark}
+            % --------------------------------------------------------------------------------------------------------------
+            \begin{theorem}[Jensen's inequality]\label{thm:jesen}
+                Let $F: \RR^n \rightarrow \overline \RR$ be a $\mu \ge 0$ strongly convex function. 
+                Then, it is equivalent to the following condition. 
+                For all $x, y \in \RR^n$, $\lambda \in (0, 1)$ it satisfies the inequality 
+                \begin{align*}
+                    (\forall \lambda \in [0, 1])\; 
+                    F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\mu\lambda(1 - \lambda)}{2} \Vert y - x\Vert^2. 
+                \end{align*}
+            \end{theorem}
+            \begin{remark}
+                If $x, y$ is out of $\dom F$, the inequality still work by convexity. 
+            \end{remark}
+            % --------------------------------------------------------------------------------------------------------------
+            \begin{theorem}[quasi jesen inequality \textcolor{red}{NEW}]\label{thm:sq-scnvx-equiv}
+                A function $F$ is semi quasi strongly convex with $A \in \RR^{m \times n}$ (Definition \ref{def:sq-scnvx}) if and only if, for all $x, y \in \RR^n$ and, $\lambda \in [0, 1]$ it satisfies the inequality:
+                \begin{align*}
+                    F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2. 
+                \end{align*}
+            \end{theorem}
+            \begin{proof}
+                For all $\lambda \in \RR, x \in \RR^n, y \in \RR^n$ it has $-1/2\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 = (1/2)(\lambda\Vert Ax\Vert^2 + (1 - \lambda)\Vert Ay\Vert^2 - \lambda(1 - \lambda)\Vert Ax - Ay\Vert^2)$ by verifying:
+                \begin{align*}
+                    & -\frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 + 
+                    \left(
+                        \frac{\lambda}{2}\Vert Ax\Vert^2 + \frac{1 - \lambda}{2}\Vert Ay\Vert^2 - \frac{\lambda(1 - \lambda)}{2}\Vert Ay - Ax\Vert^2
+                    \right)
+                    \\
+                    &= 
+                    -\frac{1}{2}\left(
+                        \lambda^2\Vert Ax\Vert^2 + (1 - \lambda)^2\Vert Ay\Vert^2 - 2\lambda(1 - \lambda) \langle Ax, Ay\rangle
+                    \right)
+                        \\ &\quad 
+                        + 
+                        \left(
+                            \frac{\lambda}{2} - \frac{\lambda(1 - \lambda)}{2}
+                        \right)\Vert Ax\Vert^2 + \left(
+                            \frac{1 - \lambda}{2} - \frac{\lambda(1 - \lambda)}{2}
+                        \right)\Vert Ay\Vert^2 - \lambda(1 - \lambda)\langle Ay, Ax\rangle
+                    \\
+                    &= - \frac{\lambda^2}{2}\Vert Ax\Vert^2 - \frac{(1 - \lambda)^2}{2}\Vert Ay\Vert^2
+                        \\ &\quad 
+                        + 
+                        \left(
+                            \frac{\lambda}{2} - \frac{\lambda - \lambda^2}{2}
+                        \right)\Vert Ax\Vert^2 + \left(
+                            \frac{1 - \lambda}{2} - \frac{\lambda - \lambda^2}{2}
+                        \right)\Vert Ay\Vert^2
+                    \\
+                    &= 0
+                \end{align*}
+                Using the above result we can prove the equivalency because 
+                {\small
+                \begin{align*}
+                    0 &\le F(\lambda x + (1 - \lambda)y) + \lambda F(x) + (1 - \lambda)F(y) -\frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2
+                    \\
+                    &=  F(\lambda x + (1 - \lambda)y) - \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 
+                    + \lambda F(x) - \frac{\lambda}{2}\Vert Ax\Vert^2 
+                    + (1 - \lambda)F(y) - \frac{1 - \lambda}{2} \Vert Ay\Vert^2 
+                        \\ &\quad 
+                        - \frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2 + \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2
+                        + \frac{1}{2}\Vert Ax\Vert^2 + \frac{1}{2}\Vert Ay\Vert^2 
+                    \\
+                    &= 
+                    F(\lambda x + (1 - \lambda)y) - \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 
+                        \\ &\quad 
+                        + \lambda \left(F(x) - \frac{1}{2}\Vert Ax\Vert^2\right) 
+                        + (1 - \lambda)\left(F(y) - \frac{1}{2} \Vert Ay\Vert^2\right). 
+                \end{align*}
+                }
+                The last line shows that the function $F(x) - \frac{1}{2}\Vert Ax\Vert^2$ is convex, the chain of equality shows the equivalence. 
+            \end{proof}
+            % --------------------------------------------------------------------------------------------------------------
+            \begin{definition}[smoothness and strong convexity with seminorm \textcolor{red}{NEW}]\label{def:seminorm-smooth-scnvx}
+                Let $f:\RR^n \rightarrow \RR$ be a differentiable function on $\reli\dom f$. 
+                Let $m \in \N$. 
+                Let $A: \RR^{m\times n}$ and $b \in \RR^n$ be arbitrary. 
+                Then, function $h: \RR^m \rightarrow \RR :=  x\mapsto f(Ax - b)$ is relatively smooth and, relatively strongly convex with respect to the function $x \mapsto (1/2)\Vert A x\Vert^2$: 
+                \begin{align*}
+                    (\forall x \in \RR^m)(\forall y \in \RR^m)\;
+                    \frac{\mu}{2}\Vert Ax - Ay\Vert^2 \le 
+                    D_f(x, y) \le \frac{L}{2}\Vert Ax - Ay\Vert^2. 
+                \end{align*}
+            \end{definition}
+            \begin{remark}
+                The definition exchanged the $\Vert \cdot\Vert^2$ for a seminorm squared: $x \mapsto \Vert Ax\Vert^2$ with some $A: \RR^m \rightarrow \RR^n$. 
+            \end{remark}
+            The following theorem classifies a class of semi quasi strongly convex function. 
+            % --------------------------------------------------------------------------------------------------------------
+            \begin{theorem}[affine composition with strong convexity and smoothness]\label{thm:smooth-aff-sq-scnvs-fxn}
+                Let $f: \RR^n \rightarrow \RR$ be an $L$ smooth and, $\mu \ge 0$ strongly convex. 
+                Let $A: \RR^m \rightarrow \RR^n$, $b \in \RR^n$ be arbitrary. 
+                Let $h: \RR^m \rightarrow \RR= x \mapsto f(Ax - b)$, then the function $h$ satisfies: 
+                \begin{align*}
+                    (\forall x \in \RR^m)(\forall y \in \RR^m)\; \frac{\mu}{2}\Vert Ax - Ay\Vert^2 
+                    \le D_h(x, y) \le \frac{L}{2}\Vert Ax - Ay\Vert^2. 
+                \end{align*}
+            \end{theorem}
+            \begin{proof}
+                Then the Bregman divergence of $h$ is: 
+                \begin{align*}
+                    D_h(x, y) &= h(x) - h(y) - \langle \nabla h(y), x - y\rangle
+                    \\
+                    &= f(Ax - b) - f(Ay - b) - \langle A^T\nabla f(Ay - b), x - y\rangle
+                    \\
+                    &= f(Ax - b) - f(Ay - b) - \langle \nabla f(Ay - b), Ax - Ay\rangle
+                    \\
+                    &= f(Ax - b) - f(Ay - b) - \langle \nabla f(Ay - b), Ax - b - (Ay - b)\rangle
+                    \\
+                    &= D_f(Ax - b, Ay - b). 
+                \end{align*}
+                Since $f$ is $L$ smooth and $\mu \ge 0$ strongly convex, it means 
+                \begin{align*}
+                    \frac{\mu}{2}\Vert Ax - Ay\Vert^2
+                    &= 
+                    \frac{\mu}{2}\Vert Ax - b - (Ay - b)\Vert^2 
+                    \\
+                    &\le D_f(Ax - b, Ay - b)
+                    \\
+                    &= D_h(x, y) 
+                    \\
+                    &\le \frac{L}{2} \Vert Ax - Ay\Vert^2. 
+                \end{align*}
+            \end{proof}
+            The following definition defines the concept of relative smoothness. 
+            We build the proximal gradient inequality for the class of SQ-SCNVX functions. 
+        \subsubsection{Important inequalities}
             \begin{assumption}[smooth add nonsmooth]\label{ass:smooth-plus-nonsmooth}
@@
             \end{assumption}
-
-        \begin{definition}[Proximal gradient operator]\label{def:pg-opt}
-            Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
-            Let $\beta > 0$. 
-            Then, we define the proximal gradient operator $T_{\beta}$ as 
-            \begin{align*}
-                T_\beta (x | F) &= \argmin_{z} \left\lbrace
-                    g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{\beta}{2}\Vert z - x\Vert^2
-                \right\rbrace. 
-            \end{align*}
-        \end{definition}
-        \begin{remark}
-            If the function $g \equiv 0$, then it yields the gradient descent operator $T_\beta(x) = x - \beta^{-1}\nabla f(x)$. 
-            In the context where it's clear what the function $F = f + g$ is, we simply write $T_\beta(x)$ for short. 
-        \end{remark}
-
-        \begin{definition}[Bregman Divergence]
-            Let $f:\RR^n \rightarrow \overline \RR$ be a differentiable function. 
-            Then, for all the Bregman divergence $D_f: \RR^n \times \dom\nabla f \rightarrow \RR$ is defined as: 
-            \begin{align*}
-                D_f(x, y) := f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 
-            \end{align*}
-        \end{definition}
-        \begin{remark}
-            If, $f$ is $\mu \ge 0$ strongly convex and $L$ Lipschitz smooth then, its Bregman Divergence has for all $x, y \in \RR^n$: $\mu/2 \Vert x - y\Vert^2 \le D_f(x, y) \le L/2 \Vert x - y\Vert^2$.
-        \end{remark}
-
-        % \begin{definition}[R-WAPG sequence]\label{def:rwapg-seq}
-        %     Let $(L_k)_{k \ge 0}$ be a sequence such that $L_k > \mu$ for all $k$. 
-        %     Let $\alpha_0 \in (0, 1]$, $(\alpha_k)_{k \ge 1}$ has $\alpha_k \in (\mu/ L_k, 1)$. 
-        %     Then define for all $k \ge 0$: 
-        %     \begin{align*}
-        %         \rho_k(1 - \alpha_{k + 1})\alpha_k^2 = \alpha_{k + 1}(\alpha_{k + 1} - \mu/L_k). 
-        %     \end{align*}
-        % \end{definition}
-        % \begin{remark}
-        %     When $\rho_k = 1$, the recursive relation between $\alpha_k, \alpha_{k - 1}$ is the same as the well known Nesterov's sequence used in algorithm such as FISTA and Nesterov's accelerated gradient.
-        %     See Li and Wang \cite{li_relaxed_2025} for more information. 
-        % \end{remark}
-        % \begin{definition}[similar triangle representation of NAPG]\;\label{def:st-method}\\
-        %     Let $(\alpha_k)_{k \ge 0}$ be an R-WAPG sequence. 
-        %     Suppose that the base case $v_{-1}, x_{k - 1}\in \RR^n$ is given to initialize the algorithm. 
-        %     Then the algorithm produces the sequence of iterates $(y_k, x_k, v_k)_{k \ge 0}$ and auxiliary parameter sequence $L_k, \tau_k$ satisfying these inequalities: 
-        %     \begin{align*}
-        %         & \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}, 
-        %         \\
-        %         & y_k = (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1},
-        %         \\
-        %         & D_f(x_k, y_k) \le L_k/2\Vert x_k - y_k\Vert^2, 
-        %         \\
-        %         & x_k = T_{L_k}(y_k),
-        %         \\
-        %         & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
-        %     \end{align*} 
-        % \end{definition}
-        % The following theorems are critical in analyzing the behavior of algorithm in Definition \ref{def:st-method}.
-
-        \begin{theorem}[Jensen's inequality]\label{thm:jesen}
-            Let $F: \RR^n \rightarrow \overline \RR$ be a $\mu \ge 0$ strongly convex function. 
-            Then, it is equivalent to the following condition. 
-            For all $x, y \in \RR^n$, $\lambda \in (0, 1)$ it satisfies the inequality 
-            \begin{align*}
-                (\forall \lambda \in [0, 1])\; 
-                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\mu\lambda(1 - \lambda)}{2} \Vert y - x\Vert^2. 
-            \end{align*}
-        \end{theorem}
-        \begin{remark}
-            If $x, y$ is out of $\dom F$, the inequality still work by convexity. 
-        \end{remark}
-        \begin{definition}[semi quasi strong convexity Jensen inequality \textcolor{red}{NEW}]\label{def:sq-scnvx}
-            Let $m, n \in \N$. 
-            A function $f:\RR^n \rightarrow \overline \RR$ is semi quasi strongly convex with linear mapping $A:\RR^m \rightarrow \RR^n$ if for all $x \in \RR^n, y \in \RR^n$ and $\lambda \in [0, 1]$ it satisfies:
-            \begin{align*}
-                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2. 
-            \end{align*}
-        \end{definition}
-        \begin{remark}
-            Choose $A = \sqrt{\mu} I$, where $I$ is the identity matrix then it is equivalent to $\mu$ strongly convex. 
-            This is an example of uniform convexity because there exists some $\sigma \ge 0$ such that it fits in Bauschke \cite[Definition 10.7]{bauschke_convex_2017} with $\phi(z) = \sigma^2z^2$. 
-            \\
-            It is called ``Semi'' because of the semi norm induced by matrix $A$, followed by ``Quasi strongly convex'' because the quasi norm $\Vert Ax\Vert^2$ is the distance of an oblique projection to the kernel of $A$ which is a quasi strongly convex function.
-        \end{remark}
-        The above definition is the special case of relatively strong convexity wrt to the Bregman divergence $D_h(x, y) = \Vert Ax - Ay\Vert^2$. 
-        \begin{theorem}[an equivalent definition for SQ-SCNVX functions]\label{thm:sq-scnvx-equiv}
-            A function $F$ is semi quasi strongly convex with $A$ if and only if the function $x \mapsto F(x) - \frac{1}{2}\Vert A x\Vert^2$ is convex. 
-        \end{theorem}
-        \begin{proof}
-            For all $\lambda \in \RR, x \in \RR^n, y \in \RR^n$ it has $-1/2\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 = (1/2)(\lambda\Vert Ax\Vert^2 + (1 - \lambda)\Vert Ay\Vert^2 - \lambda(1 - \lambda)\Vert Ax - Ay\Vert^2)$ by verifying:
-            \begin{align*}
-                & -\frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 + 
-                \left(
-                    \frac{\lambda}{2}\Vert Ax\Vert^2 + \frac{1 - \lambda}{2}\Vert Ay\Vert^2 - \frac{\lambda(1 - \lambda)}{2}\Vert Ay - Ax\Vert^2
-                \right)
-                \\
-                &= 
-                -\frac{1}{2}\left(
-                    \lambda^2\Vert Ax\Vert^2 + (1 - \lambda)^2\Vert Ay\Vert^2 - 2\lambda(1 - \lambda) \langle Ax, Ay\rangle
-                \right)
-                    \\ &\quad 
-                    + 
-                    \left(
-                        \frac{\lambda}{2} - \frac{\lambda(1 - \lambda)}{2}
-                    \right)\Vert Ax\Vert^2 + \left(
-                        \frac{1 - \lambda}{2} - \frac{\lambda(1 - \lambda)}{2}
-                    \right)\Vert Ay\Vert^2 - \lambda(1 - \lambda)\langle Ay, Ax\rangle
-                \\
-                &= - \frac{\lambda^2}{2}\Vert Ax\Vert^2 - \frac{(1 - \lambda)^2}{2}\Vert Ay\Vert^2
-                    \\ &\quad 
-                    + 
-                    \left(
-                        \frac{\lambda}{2} - \frac{\lambda - \lambda^2}{2}
-                    \right)\Vert Ax\Vert^2 + \left(
-                        \frac{1 - \lambda}{2} - \frac{\lambda - \lambda^2}{2}
-                    \right)\Vert Ay\Vert^2
-                \\
-                &= 0
-            \end{align*}
-            Using the above result we can prove the equivalency because 
-            {\small
-            \begin{align*}
-                0 &\le F(\lambda x + (1 - \lambda)y) + \lambda F(x) + (1 - \lambda)F(y) -\frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2
-                \\
-                &=  F(\lambda x + (1 - \lambda)y) - \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 
-                + \lambda F(x) - \frac{\lambda}{2}\Vert Ax\Vert^2 
-                + (1 - \lambda)F(y) - \frac{1 - \lambda}{2} \Vert Ay\Vert^2 
-                    \\ &\quad 
-                    - \frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2 + \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2
-                    + \frac{1}{2}\Vert Ax\Vert^2 + \frac{1}{2}\Vert Ay\Vert^2 
-                \\
-                &= 
-                F(\lambda x + (1 - \lambda)y) - \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 
-                    \\ &\quad 
-                    + \lambda \left(F(x) - \frac{1}{2}\Vert Ax\Vert^2\right) 
-                    + (1 - \lambda)\left(F(y) - \frac{1}{2} \Vert Ay\Vert^2\right). 
-            \end{align*}
-            }
-            So, the function $F(x) - \frac{1}{2}\Vert Ax\Vert^2$ is convex. 
-        \end{proof}
-        The following theorem classifies a class of semi quasi strongly convex function. 
-        \begin{theorem}[Affine composite differentiable SQ-SCNVX functions]\label{thm:smooth-aff-sq-scnvs-fxn}
-
-        \end{theorem}
-        \begin{proof}
-            Let $h(x) = f(Ax - b)$.
-
-        \end{proof}
-        The following definition defines the concept of relative smoothness. 
-        \begin{definition}[semi relative smoothness]\label{def:semi-rel-smooth}
-
-        \end{definition}
-        We build the proximal gradient inequality for the class of SQ-SCNVX functions. 
+            \begin{assumption}[seminorm smooth plus non-smooth]\label{ass:snorm-smth-p-nsmth}
+                Let $F = f + g$. Assume that: 
+                \begin{enumerate}[noitemsep]
+                    \item $f: \RR^m \rightarrow \overline \RR$ is differentiable and, it satisfies Definition \ref{def:seminorm-smooth-scnvx} with $L > \mu \ge 0$ and $A \in \RR^{m \times n}$. 
+                    \item $g:\RR^m \mapsto \overline \RR$ is a convex, proper and closed function. 
+                \end{enumerate}
+            \end{assumption}
+            % --------------------------------------------------------------------------------------------------------------
             \begin{theorem}[proximal gradient inequality]\label{thm:pg-ineq}
                 Let function $F$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}, so it's $\mu \ge 0$ strongly convex. 
-            For all $x\in \RR^n$, define $x^+ = T_L(x)$, then there exists a $B \ge 0$ such that $D_f(x^+, x) \le B/2 \Vert x^+ - x\Vert^2$. 
-            Then, for all $z \in \RR^n$ it satisfies proximal gradient inequality at point $x$:  
+                For any $x\in \RR^n$, define $x^+ = T_L(x)$. 
+                Then, there exists a $B \ge 0$ such that $D_f(x^+, x) \le B/2 \Vert x^+ - x\Vert^2$ and, for all $z \in \RR^n$ it satisfies the inequality: 
                 \begin{align*}
@@
             \end{remark}
+            % --------------------------------------------------------------------------------------------------------------
+            \begin{theorem}[proximal gradient inequality with SQ-SCNVX \textcolor{red}{NEW}]\label{thm:pg-ineq-sq-scnvx}
+                Suppose that $F:\RR^m \rightarrow \overline \RR := x \mapsto f(x) + g(x)$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth} with $L > \mu \ge 0$ and $A \in \RR^{m\times n}$. 
+                For any $x \in \RR^n$, let $x^+ = T_B(x | F)$.
+                Then, there exists some $B \ge 0$ such that $D_f(x^+, x) \le \frac{B}{2}\Vert x - x^+\Vert^2$ and, for all $z \in \RR^m, \eta \in \RR$ it satisfies the inequality: 
+                \begin{align*}
+                    0 &\le F(z) - F(x^+)
+                    + \frac{\eta}{2}\Vert z - x\Vert^2 
+                    - \frac{\mu}{2}\Vert Az - Ax\Vert^2
+                    + \frac{B - \eta}{2}\Vert z - x\Vert^2
+                    - \frac{B}{2}\Vert z - x^+\Vert^2 . 
+                \end{align*}
+            \end{theorem}
+            \begin{proof}
+                Firstly, such a $B > 0$ exists, for example $B = L\Vert A\Vert^2$ would be an option because from Definition \ref{def:seminorm-smooth-scnvx}, it for all $x, y$, $D_f(x, y) \le L/2\Vert Ax - Ay \Vert^2 \le L/2\Vert A\Vert^2\Vert x - y\Vert^2$.
+                But it can be much smaller. 
+                \par
+                The function $z \mapsto g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2$ inside the proximal gradient operator has the minimizer $x^+$.  
+                This function is also the sum of a convex, proper closed function $g$ and, a simple quadratic and, it's $B > 0$ strongly convex hence, it satisfies the quadratic growth conditions over its minimizer $x^+ = T_B(x|F)$ so, it follows that for all $z \in \RR^m$:
+                \begin{align*}
+                    0 &\le 
+                    -\frac{B}{2}\Vert z - x^+\Vert^2 
+                    + g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
+                        \\&\quad 
+                        - g(x^+) - f(x) - \langle \nabla f(x), x^+ - x\rangle - \frac{B}{2}\Vert x^+ - x\Vert^2
+                    \\
+                    &= 
+                    -\frac{B}{2}\Vert z - x^+\Vert^2 
+                    + \left(g(z) + f(z) - f(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2\right)
+                        \\&\quad 
+                        +\left(- g(x^+) - f(x^+) + f(x^+) - f(x) - \langle \nabla f(x), x^+ - x\rangle - \frac{B}{2}\Vert x^+ - x\Vert^2\right)
+                    \\
+                    &=
+                    -\frac{B}{2}\Vert z - x^+\Vert^2 
+                    + \left(F(z) - D_f(z, x) + \frac{B}{2}\Vert z - x\Vert^2\right)
+                        \\&\quad
+                        + \left(- F(x^+) + D_f(x^+, x) - \frac{B}{2}\Vert x^+ - x\Vert^2\right)
+                    \\
+                    &\underset{\text{(a)}}{\le }
+                    -\frac{B}{2}\Vert z - x^+\Vert^2 
+                    + \left(F(z) - D_f(z, x) + \frac{B}{2}\Vert z - x\Vert^2\right)
+                    - F(x^+)
+                    \\
+                    &\underset{\text{(b)}}{\le} 
+                    - \frac{B}{2}\Vert z - x^+\Vert^2 
+                    + F(z) - \frac{\mu}{2}\Vert Az - Ax\Vert^2 
+                    + \frac{B}{2}\Vert z - x\Vert^2
+                    - F(x^+)
+                    \\
+                    &= F(z) - F(x^+)
+                    + \left(
+                        \frac{\eta}{2}\Vert z - x\Vert^2 
+                        - \frac{\mu}{2}\Vert Az - Ax\Vert^2
+                    \right) 
+                    + \frac{B - \eta}{2}\Vert z - x\Vert^2
+                    - \frac{B}{2}\Vert z - x^+\Vert^2 . 
+                \end{align*}
+                At (a), we used the fact that line search asserted the condition $D_f(x^+, x) \le \frac{B}{2}\Vert x^+ - x\Vert^2$. 
+                At (b), we used the fact that $f$ satisfies Definition \ref{def:seminorm-smooth-scnvx} so, it has for all $x, z \in \RR^m$, $D_f(z, x) \ge \frac{\mu}{2}\Vert z - x\Vert^2$. 
+            \end{proof}
+            % --------------------------------------------------------------------------------------------------------------
+            \begin{theorem}[seminorm smooth plus non-smooth Jensen \textcolor{red}{NEW}]\label{thm:smnrm-jnsn-smth-nsmth}
+                Suppose that $F:\RR^m \rightarrow \overline \RR := x \mapsto f(x) + g(x)$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth} with $L > \mu \ge 0$ and $A \in \RR^{m\times n}$. 
+                \todoinline{NOT YET FINISHED}
+            \end{theorem}
+            \begin{proof}
+
+            \end{proof}
 
@@
         \end{proof}
-    \subsection{convergence rate of the algorithm under various circumstances}
+    \subsection{Convergence rate of the algorithm under various circumstances}
         The previous section highlighted a generic convergence results from one iteration of the algorithm, however, there are a lot of loose ends. 

### 2025-07-09 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
 % ==============================================================================
-\section{Nesterov's Accelerated Gradient}
-    \subsection{In preparations}
+\section{In preparations}
     Definition \ref{def:pg-opt} is the definition of the proximal gradient operator, which is equivalent to the gradient descent operator when the non-smooth part of the objective is the zero function.
@@
     The derivation for the convergence rate of a stochastic accelerated variant of Nesterov's accelerated  proximal gradient method is in the next section. 
-        \subsubsection{Basic definitions}
+    \subsection{Basic definitions}
         % --------------------------------------------------------------------------------------------------------------
@@
         \end{remark}
-        \subsubsection{Properties of function}
-            % --------------------------------------------------------------------------------------------------------------
-            \begin{definition}[semi quasi strongly convex function \textcolor{red}{NEW}]\label{def:sq-scnvx}
-                A function $F: \RR^n \rightarrow \overline \RR$ is a semi quasi strongly convex function, abbreviated as ``SQ-SCNVX'' with respective to a linear mapping $A \in \RR^{m \times n}$ if $F - \frac{1}{2}\Vert Ax\Vert^2$ is a convex function.
+    \subsection{Properties of functions, characterizations}
+        The definitions are ordered from the weakest to strongest. 
+        % --------------------------------------------------------------------------------------------------------------
+        \begin{definition}[semi strongly convex function \textcolor{red}{NEW}]\label{def:semi-scnvx}
+            A function $F: \RR^n \rightarrow \overline \RR$ is a semi strongly convex function, abbreviated as ``Semi-SCNVX'' with respective to a linear mapping $A \in \RR^{m \times n}$ if $F - \frac{1}{2}\Vert Ax\Vert^2$ is a convex function.
         \end{definition}
         \begin{remark}
-                Any $\mu \ge 0$ strongly convex function is QS-SCNVX with $A = \sqrt{\mu}I$. 
+            Any $\mu \ge 0$ strongly convex function is Semi-SCNVX with $A = \sqrt{\mu}I$. 
             But the converse is not true because a seminorm is not a norm. 
-                One feature of a QS-SCNVX function is that it doesn't have a unique minimizer which differs it from strong convexity. 
+            One feature of a Semi-SCNVX function is that it doesn't have a unique minimizer which differs it from strong convexity. 
             It may not have a unique minimizer because it's not necessary that $\kernel A = \{\mathbf 0\}$. 
         \end{remark}
+        % --------------------------------------------------------------------------------------------------------------
+        \begin{definition}[semi relative smoothness and Semi-SCNVX \textcolor{red}{NEW}]\label{def:seminorm-smooth-scnvx}
+            Let $m, n\in \N$ be a natural numbers. 
+            Let $f:\RR^m \rightarrow \RR$ be a differentiable function and full domain. 
+            If there exists $A_1: \RR^{m\times n}$ and, $A_2 \in \RR^{m \times n}$ matrices such that it satisfies:
+            \begin{align*}
+                (\forall x \in \RR^m)(\forall y \in \RR^m)\;
+                \frac{1}{2}\Vert A_1x - A_1y\Vert^2 \le 
+                D_f(x, y) \le \frac{1}{2}\Vert A_2x - A_2y\Vert^2. 
+            \end{align*}
+            Then, we call this function is semi-relative smooth with respect to $A_1$, and semi convex to $A_2$
+        \end{definition}
+        \begin{remark}
+            The definition exchanged the $\Vert \cdot\Vert^2$ for a seminorm squared: $x \mapsto \Vert A_1x\Vert^2$ with some $A: \RR^m \rightarrow \RR^n$ for the definition of relative smoothness and relative strong convexity.
+            Obviously, it has $\Vert A_1x\Vert \le \Vert A_2x\Vert$ for all $x\in \RR^m$, which further implies that $\ker A_1\supseteq\ker A_2$. 
+        \end{remark}
+        % --------------------------------------------------------------------------------------------------------------
+        \begin{theorem}[semi Jesen inequality \textcolor{red}{NEW}]\label{thm:semi-scnvx-equiv}
+            A function $F$ is Semi-SNCVX with $A \in \RR^{m \times n}$ (Definition \ref{def:semi-scnvx}) if and only if, for all $x, y \in \RR^n$ and, $\lambda \in [0, 1]$ it satisfies the inequality:
+            \begin{align*}
+                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2. 
+            \end{align*}
+        \end{theorem}
+        \begin{proof}
+            For all $\lambda \in \RR, x \in \RR^n, y \in \RR^n$ it has $-1/2\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 = (1/2)(\lambda\Vert Ax\Vert^2 + (1 - \lambda)\Vert Ay\Vert^2 - \lambda(1 - \lambda)\Vert Ax - Ay\Vert^2)$ by verifying:
+            \begin{align*}
+                & -\frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 + 
+                \left(
+                    \frac{\lambda}{2}\Vert Ax\Vert^2 + \frac{1 - \lambda}{2}\Vert Ay\Vert^2 - \frac{\lambda(1 - \lambda)}{2}\Vert Ay - Ax\Vert^2
+                \right)
+                \\
+                &= 
+                -\frac{1}{2}\left(
+                    \lambda^2\Vert Ax\Vert^2 + (1 - \lambda)^2\Vert Ay\Vert^2 - 2\lambda(1 - \lambda) \langle Ax, Ay\rangle
+                \right)
+                    \\ &\quad 
+                    + 
+                    \left(
+                        \frac{\lambda}{2} - \frac{\lambda(1 - \lambda)}{2}
+                    \right)\Vert Ax\Vert^2 + \left(
+                        \frac{1 - \lambda}{2} - \frac{\lambda(1 - \lambda)}{2}
+                    \right)\Vert Ay\Vert^2 - \lambda(1 - \lambda)\langle Ay, Ax\rangle
+                \\
+                &= - \frac{\lambda^2}{2}\Vert Ax\Vert^2 - \frac{(1 - \lambda)^2}{2}\Vert Ay\Vert^2
+                    \\ &\quad 
+                    + 
+                    \left(
+                        \frac{\lambda}{2} - \frac{\lambda - \lambda^2}{2}
+                    \right)\Vert Ax\Vert^2 + \left(
+                        \frac{1 - \lambda}{2} - \frac{\lambda - \lambda^2}{2}
+                    \right)\Vert Ay\Vert^2
+                \\
+                &= 0
+            \end{align*}
+            Using the above result we can prove the equivalency because 
+            {\small
+            \begin{align*}
+                0 &\le F(\lambda x + (1 - \lambda)y) + \lambda F(x) + (1 - \lambda)F(y) -\frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2
+                \\
+                &=  F(\lambda x + (1 - \lambda)y) - \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 
+                + \lambda F(x) - \frac{\lambda}{2}\Vert Ax\Vert^2 
+                + (1 - \lambda)F(y) - \frac{1 - \lambda}{2} \Vert Ay\Vert^2 
+                    \\ &\quad 
+                    - \frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2 + \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2
+                    + \frac{1}{2}\Vert Ax\Vert^2 + \frac{1}{2}\Vert Ay\Vert^2 
+                \\
+                &= 
+                F(\lambda x + (1 - \lambda)y) - \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 
+                    \\ &\quad 
+                    + \lambda \left(F(x) - \frac{1}{2}\Vert Ax\Vert^2\right) 
+                    + (1 - \lambda)\left(F(y) - \frac{1}{2} \Vert Ay\Vert^2\right). 
+            \end{align*}
+            }
+            The last line shows that the function $F(x) - \frac{1}{2}\Vert Ax\Vert^2$ is convex, the chain of equality shows the equivalence. 
+        \end{proof}
         % --------------------------------------------------------------------------------------------------------------
@@
         \end{remark}
-            % --------------------------------------------------------------------------------------------------------------
-            \begin{theorem}[quasi jesen inequality \textcolor{red}{NEW}]\label{thm:sq-scnvx-equiv}
-                A function $F$ is semi quasi strongly convex with $A \in \RR^{m \times n}$ (Definition \ref{def:sq-scnvx}) if and only if, for all $x, y \in \RR^n$ and, $\lambda \in [0, 1]$ it satisfies the inequality:
-                \begin{align*}
-                    F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2. 
-                \end{align*}
-            \end{theorem}
-            \begin{proof}
-                For all $\lambda \in \RR, x \in \RR^n, y \in \RR^n$ it has $-1/2\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 = (1/2)(\lambda\Vert Ax\Vert^2 + (1 - \lambda)\Vert Ay\Vert^2 - \lambda(1 - \lambda)\Vert Ax - Ay\Vert^2)$ by verifying:
-                \begin{align*}
-                    & -\frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 + 
-                    \left(
-                        \frac{\lambda}{2}\Vert Ax\Vert^2 + \frac{1 - \lambda}{2}\Vert Ay\Vert^2 - \frac{\lambda(1 - \lambda)}{2}\Vert Ay - Ax\Vert^2
-                    \right)
-                    \\
-                    &= 
-                    -\frac{1}{2}\left(
-                        \lambda^2\Vert Ax\Vert^2 + (1 - \lambda)^2\Vert Ay\Vert^2 - 2\lambda(1 - \lambda) \langle Ax, Ay\rangle
-                    \right)
-                        \\ &\quad 
-                        + 
-                        \left(
-                            \frac{\lambda}{2} - \frac{\lambda(1 - \lambda)}{2}
-                        \right)\Vert Ax\Vert^2 + \left(
-                            \frac{1 - \lambda}{2} - \frac{\lambda(1 - \lambda)}{2}
-                        \right)\Vert Ay\Vert^2 - \lambda(1 - \lambda)\langle Ay, Ax\rangle
-                    \\
-                    &= - \frac{\lambda^2}{2}\Vert Ax\Vert^2 - \frac{(1 - \lambda)^2}{2}\Vert Ay\Vert^2
-                        \\ &\quad 
-                        + 
-                        \left(
-                            \frac{\lambda}{2} - \frac{\lambda - \lambda^2}{2}
-                        \right)\Vert Ax\Vert^2 + \left(
-                            \frac{1 - \lambda}{2} - \frac{\lambda - \lambda^2}{2}
-                        \right)\Vert Ay\Vert^2
-                    \\
-                    &= 0
-                \end{align*}
-                Using the above result we can prove the equivalency because 
-                {\small
-                \begin{align*}
-                    0 &\le F(\lambda x + (1 - \lambda)y) + \lambda F(x) + (1 - \lambda)F(y) -\frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2
-                    \\
-                    &=  F(\lambda x + (1 - \lambda)y) - \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 
-                    + \lambda F(x) - \frac{\lambda}{2}\Vert Ax\Vert^2 
-                    + (1 - \lambda)F(y) - \frac{1 - \lambda}{2} \Vert Ay\Vert^2 
-                        \\ &\quad 
-                        - \frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2 + \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2
-                        + \frac{1}{2}\Vert Ax\Vert^2 + \frac{1}{2}\Vert Ay\Vert^2 
-                    \\
-                    &= 
-                    F(\lambda x + (1 - \lambda)y) - \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 
-                        \\ &\quad 
-                        + \lambda \left(F(x) - \frac{1}{2}\Vert Ax\Vert^2\right) 
-                        + (1 - \lambda)\left(F(y) - \frac{1}{2} \Vert Ay\Vert^2\right). 
-                \end{align*}
-                }
-                The last line shows that the function $F(x) - \frac{1}{2}\Vert Ax\Vert^2$ is convex, the chain of equality shows the equivalence. 
-            \end{proof}
-            % --------------------------------------------------------------------------------------------------------------
-            \begin{definition}[smoothness and strong convexity with seminorm \textcolor{red}{NEW}]\label{def:seminorm-smooth-scnvx}
-                Let $f:\RR^n \rightarrow \RR$ be a differentiable function on $\reli\dom f$. 
-                Let $m \in \N$. 
-                Let $A: \RR^{m\times n}$ and $b \in \RR^n$ be arbitrary. 
-                Then, function $h: \RR^m \rightarrow \RR :=  x\mapsto f(Ax - b)$ is relatively smooth and, relatively strongly convex with respect to the function $x \mapsto (1/2)\Vert A x\Vert^2$: 
-                \begin{align*}
-                    (\forall x \in \RR^m)(\forall y \in \RR^m)\;
-                    \frac{\mu}{2}\Vert Ax - Ay\Vert^2 \le 
-                    D_f(x, y) \le \frac{L}{2}\Vert Ax - Ay\Vert^2. 
-                \end{align*}
-            \end{definition}
-            \begin{remark}
-                The definition exchanged the $\Vert \cdot\Vert^2$ for a seminorm squared: $x \mapsto \Vert Ax\Vert^2$ with some $A: \RR^m \rightarrow \RR^n$. 
-            \end{remark}
-            The following theorem classifies a class of semi quasi strongly convex function. 
+        The following theorem classifies a class of semi strongly convex function. 
         % --------------------------------------------------------------------------------------------------------------
@@
             \end{align*}
+            Therefore, it satisfies Definition \ref{def:semi-scnvx} with $A_1 = \sqrt{L}A, A_2 = \sqrt{\mu}A$. 
         \end{theorem}
@@
         The following definition defines the concept of relative smoothness. 
-            We build the proximal gradient inequality for the class of SQ-SCNVX functions. 
-        \subsubsection{Important inequalities}
+        We build the proximal gradient inequality for the class of Semi-SCNVX functions. 
+    \subsection{Important inequalities}
+            The following assumptions are ordered from weakest to strongest. 
+            All of them are some of smooth with a non-smooth function. 
+            \begin{assumption}[affine S-CNVX composition plus non-smooth]\label{ass:snorm-smth-p-nsmth}
+                Let $A \in \RR^{m\times n}, b \in \RR^n$
+                Let $F(x): \RR^{m} \mapsto \overline\RR := x \mapsto f(x) + g(x)$. 
+                Assume that: 
+                \begin{enumerate}[noitemsep]
+                    \item $f:\RR^m \rightarrow \RR := x \mapsto h(Ax - b)$ where $h:\RR^n\rightarrow \RR$ is $L$ Lipschitz smooth and, $\mu\ge 0$ strongly convex, then it satisfies Theorem \ref{thm:smooth-aff-sq-scnvs-fxn} with $L > \mu \ge 0$ and $A \in \RR^{m \times n}$.
+                    \item $g:\RR^m \mapsto \overline \RR$ is a convex, proper and closed function. 
+                \end{enumerate}
+            \end{assumption}
             \begin{assumption}[smooth add nonsmooth]\label{ass:smooth-plus-nonsmooth}
@@
             \begin{assumption}[admitting minimizers]\label{ass:smooth-plus-nonsmooth-x}
-                Let $F = f + g$ and in addition assume that the set of minimizers $X^+ := \argmin_{x}F(x)$ is non-empty. 
-            \end{assumption}
-            \begin{assumption}[seminorm smooth plus non-smooth]\label{ass:snorm-smth-p-nsmth}
-                Let $F = f + g$. Assume that: 
-                \begin{enumerate}[noitemsep]
-                    \item $f: \RR^m \rightarrow \overline \RR$ is differentiable and, it satisfies Definition \ref{def:seminorm-smooth-scnvx} with $L > \mu \ge 0$ and $A \in \RR^{m \times n}$. 
-                    \item $g:\RR^m \mapsto \overline \RR$ is a convex, proper and closed function. 
-                \end{enumerate}
+                Let $F = f + g$ satisfies \ref{ass:smooth-plus-nonsmooth} and in addition assume that the set of minimizers $X^+ := \argmin_{x}F(x)$ is non-empty. 
             \end{assumption}
@@
             \end{remark}
-            % --------------------------------------------------------------------------------------------------------------
-            \begin{theorem}[proximal gradient inequality with SQ-SCNVX \textcolor{red}{NEW}]\label{thm:pg-ineq-sq-scnvx}
+            The following theorem attempts to generalize Theorem \ref{thm:pg-ineq}. 
+            % --------------------------------------------------------------------------------------------------------------
+            \begin{theorem}[proximal gradient inequality with semi-scnvx \textcolor{red}{NEW}]\label{thm:pg-ineq-semi-scnvx}
                 Suppose that $F:\RR^m \rightarrow \overline \RR := x \mapsto f(x) + g(x)$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth} with $L > \mu \ge 0$ and $A \in \RR^{m\times n}$. 
                 For any $x \in \RR^n$, let $x^+ = T_B(x | F)$. 
-                Then, there exists some $B \ge 0$ such that $D_f(x^+, x) \le \frac{B}{2}\Vert x - x^+\Vert^2$ and, for all $z \in \RR^m, \eta \in \RR$ it satisfies the inequality: 
+                Let $\sigma_{\min}(A)$ denotes the minimum non-zero singular value of $A$ in absolute value. 
+                Let $\Pi = \Pi_{\ker A}$ be the linear operator that project onto the kernel of $A$. 
+                Then, there exists some $B \ge 0$ such that $D_f(x^+, x) \le \frac{B}{2}\Vert x - x^+\Vert^2$ and, for all $z \in \RR^m$ it satisfies the inequality: 
                 \begin{align*}
                     0 &\le F(z) - F(x^+) 
-                    + \frac{\eta}{2}\Vert z - x\Vert^2 
                     - \frac{\mu}{2}\Vert Az - Ax\Vert^2 
-                    + \frac{B - \eta}{2}\Vert z - x\Vert^2
-                    - \frac{B}{2}\Vert z - x^+\Vert^2 . 
+                    + \frac{B}{2}\Vert z - x\Vert^2
+                    - \frac{B}{2}\Vert z - x^+\Vert^2
+                    \\
+                    &\le F(z) - F(x^+)
+                    - \frac{B}{2}\Vert z - x^+\Vert^2 
+                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x) \Vert^2
+                        \\ &\quad 
+                        + \frac{B}{2}\Vert \Pi(z - x)\Vert^2. 
                 \end{align*}
@@
                     \\
-                    &= F(z) - F(x^+)
-                    + \left(
-                        \frac{\eta}{2}\Vert z - x\Vert^2 
+                    &= 
+                    F(z) - F(x^+) 
                     - \frac{\mu}{2}\Vert Az - Ax\Vert^2 
-                    \right) 
-                    + \frac{B - \eta}{2}\Vert z - x\Vert^2
-                    - \frac{B}{2}\Vert z - x^+\Vert^2 . 
+                    + \frac{B}{2}\Vert z - x\Vert^2
+                    - \frac{B}{2}\Vert z - x^+\Vert^2. 
                 \end{align*}
@@
                 At (b), we used the fact that $f$ satisfies Definition \ref{def:seminorm-smooth-scnvx} so, it has for all $x, z \in \RR^m$, $D_f(z, x) \ge \frac{\mu}{2}\Vert z - x\Vert^2$. 
+                \par
+                Since $\Pi = \Pi_{\ker A}$ to be the projection onto the kernel of matrix $A$, $z - x$ can be written as $\Pi(z - x) + (z - x) - \Pi(z - x)$ and so: 
+                \begin{align*}
+                    & \Pi(z - x) \perp (z - x) - \Pi(z - x)
+                    \\
+                    \implies & 
+                    \Vert z - x\Vert^2 = \Vert \Pi(z - x) \Vert^2 + \Vert (z - x) - \Pi(z - x)\Vert^2
+                \end{align*}
+                Let $\sigma_{\min}(A)$ denotes the minimum non-zero singular value of $A$ in absolute value, then it has: 
+                \begin{align*}
+                    \Vert A(x - z)\Vert^2 &= \Vert A( \Pi(z - x)  + (z - x) - \Pi(z - x))\Vert^2
+                    \\
+                    &= \Vert A((z - x) - \Pi(z - x))\Vert^2
+                    \\
+                    &\ge \sigma_{\min}(A)^2\Vert (z - x) - \Pi(z - x)\Vert^2.
+                \end{align*}
+                Using two of the above results to keep simplifying the inequality, it yields: 
+                \begin{align*}
+                    0 &\le
+                    F(z) - F(x^+)
+                    - \frac{B}{2}\Vert z - x^+\Vert^2 
+                    - \frac{\mu}{2}\Vert Az - Ax\Vert^2 
+                    + \frac{B}{2}\Vert z - x\Vert^2
+                    \\
+                    &\le 
+                    F(z) - F(x^+)
+                    - \frac{B}{2}\Vert z - x^+\Vert^2 
+                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert (z - x) - \Pi(z - x) \Vert^2
+                        \\ &\quad 
+                        + \frac{B}{2}\Vert \Pi(z - x)\Vert^2. 
+                    \\
+                    &= 
+                    F(z) - F(x^+)
+                    - \frac{B}{2}\Vert z - x^+\Vert^2 
+                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x) \Vert^2
+                        \\ &\quad 
+                        + \frac{B}{2}\Vert \Pi(z - x)\Vert^2. 
+                \end{align*}
+                Last equality we used the fact that $\Pi$ is an linear operator as well. 
             \end{proof}
+            \begin{remark}
+                When $\ker A = \{\mathbf 0\}$, this theorem is equivalent to Theorem \ref{thm:pg-ineq} but with $\mu$ being $\sigma_{\min}(A)$ instead. 
+            \end{remark}
+            The following theorem attempts to generalize Theorem \ref{thm:semi-scnvx-equiv} for relatively smooth plus non-smooth function. 
             % --------------------------------------------------------------------------------------------------------------
@@
                 Suppose that $F:\RR^m \rightarrow \overline \RR := x \mapsto f(x) + g(x)$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth} with $L > \mu \ge 0$ and $A \in \RR^{m\times n}$.
+                Let $\Pi = \Pi_{\ker A}$ be the projection onto the kernel of $A$. 
+                Let $\sigma_{\min}(A)$ denote the smallest non-zero singular value of $A$ in absolute value. 
+                Then, for all $x, y \in \RR^m$ and, $\lambda \in [0, 1]$ it satisfies the inequality: 
+                \begin{align*}
+                    F(\lambda z + (1 - \lambda)y) &\le \lambda F(z) + (1 - \lambda)F(x) - \frac{\sigma_{\min}(A)^2\lambda(1 - \lambda)\mu}{2}\Vert (I - \Pi)(x - y)\Vert^2. 
+                \end{align*}
                 \todoinline{NOT YET FINISHED}
@@
             \begin{proof}
-
+                $f$ satisfies Definition \ref{def:seminorm-smooth-scnvx} with $L > \mu, A$, so for all $x, y \in \RR^m$ it has 
+                \begin{align*}
+                    0 &\le D_f(x, y) - \frac{\mu}{2}\Vert Ax - Ay\Vert^2 
+                    \le \frac{L - \mu}{2}\Vert Ax - Ay\Vert^2. 
+                \end{align*}
+                Using some algebra (or equivalent some properties of Bregman divergence), it shows that the function $f - \mu/2 \Vert A(\cdot)\Vert^2$ is a convex function, therefore, $f + g - \mu/2\Vert A(\cdot)\Vert^2 = F - \frac{\mu}{2}\Vert A(\cdot)\Vert^2 = F - \frac{1}{2}\Vert \sqrt{\mu}A(\cdot)\Vert^2$ is also a convex function.
+                Applying Theorem \ref{thm:semi-scnvx-equiv} it has for all $z, x \in \RR^m$ and, $\lambda \in [0, 1]$ the inequality: 
+                \begin{align*}
+                    F(\lambda z + (1 - \lambda)y) &\le \lambda F(z) + (1 - \lambda)F(x) - \frac{\lambda(1 - \lambda)\mu}{2}\Vert Ax - Ay\Vert^2. 
+                \end{align*}
+                Let $\Pi = \Pi_{\ker A}$ be the projection onto the kernel of $A$, then it has: 
+                \begin{align*}
+                    \Vert Ax - Ay\Vert^2 &= \Vert A\Pi(x - y) + (I - \Pi)(x - y) \Vert^2
+                    \\
+                    &= 
+                    \Vert A\Pi(x - y) \Vert^2 + \Vert A(I - \Pi)(x - y) \Vert^2
+                    \\
+                    &\ge 0 + \sigma_{\min}(A)^2\Vert (I - \Pi)(x - y) \Vert^2
+                \end{align*}
+                Therefore, it gives the weaker inequality: 
+                \begin{align*}
+                    F(\lambda z + (1 - \lambda)y) &\le \lambda F(z) + (1 - \lambda)F(x) - \frac{\sigma_{\min}(A)^2\lambda(1 - \lambda)\mu}{2}\Vert (I - \Pi)(x - y)\Vert^2. 
+                \end{align*}
             \end{proof}
 
-    \subsection{Stochastic accelerated proximal gradient}
+\section{Stochastic accelerated proximal gradient}
+    In this section, we define the Stochastic accelerated Nesterov's Acceleration algorithm and, progressively build up the results to the one step convergence of the algorithm. 
     The following assumption about the objective function is fundamental in incremental gradient method for Machine Learning, data science other similar tasks. 
+    \begin{assumption}[sum of many affine composite]\label{ass:sum-of-many-aff-comp}
+        Let $A^{(1)}, A^{(2)}, \ldots A^{(n)}$ be a list of $\RR^{n\times m}$ matrices. 
+        Suppose $F:\RR^n \rightarrow \overline \RR:= (1/n)\left(\sum_{i = 1}^{n} f_i(x) + g_i(x)\right)$. 
+        Assume
+        \begin{enumerate}
+            \item 
+        \end{enumerate}
+    \end{assumption}
     \begin{assumption}[sum of many]\label{ass:sum-of-many}
@@
             \end{align*}
-                \item If, in addition, the sequence $\tilde \mu_k$ satisfies for all $k \ge 1$, $\frac{\tilde \mu_k}{L_{k - 1}} < L_{k - 1}/ L_k$, then the sequence also satisfies for all $k \ge 1$: $\alpha_k < 1$.
+            \item If, in addition, the sequence $\tilde \mu_k$ satisfies for all $k \ge 1$, $\frac{\tilde \mu_k}{L_{k - 1}} < L_{k - 1}/ L_k$, then the sequence strictly less than one and, for all $k \ge 1$: $\alpha_k \in (0, 1)$.
         \end{enumerate}
@@
     \end{remark}
-
     The following lemma state the relationships of the iterates generated by SNAPG-V2. 
@@
     % --------------------------------------------------------------------------------------------------------------
-        \begin{lemma}[properties of the iterates]\label{lemma:snapg2-itrs-props}
+    \begin{lemma}[properties of the iterates \textcolor{red}{NEW}]\label{lemma:snapg2-itrs-props}
         Suppose that the iterates $(z_k, x_k, y_k)_{k \ge 0}$ and sequence $(\alpha_k)_{k \ge 1}$ are produced by an algorithm satisfying Definition \ref{def:snapg-v2}. 
@@
         \end{align*}
+
+    \end{proof}
+    % --------------------------------------------------------------------------------------------------------------
+    \begin{lemma}[SNAPG-V2 one step convergence prototype stage-I]\label{lemma:snagp2-one-step-s1-proto}
+
+    \end{lemma}
+    \begin{proof}
 
@@
     \end{proof}
-    \subsection{Convergence rate of the algorithm under various circumstances}
+\section{Convergence rate of the algorithm under various circumstances}
     The previous section highlighted a generic convergence results from one iteration of the algorithm, however, there are a lot of loose ends. 
@@
 
-    \subsection{\textcolor{purple}{So, what to do next?}}
+\section{\textcolor{purple}{So, what to do next?}}
     Hi Arron would you like to add me for the co-authorship to continue this line of work and see how Nesterov's Accelerated Technique may work out for the stochastic gradient method? 

### 2025-07-10 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
 \section{In preparations}
-    Definition \ref{def:pg-opt} is the definition of the proximal gradient operator, which is equivalent to the gradient descent operator when the non-smooth part of the objective is the zero function.
-    \par
-    To show the convergence of a stochastic case of the Nesterov's accelerated proximal gradient, we prepared Lemma \ref{thm:jesen} and, \ref{thm:pg-ineq}. 
-    They are crucial in the derivation of the convergence. 
-    The derivation for the convergence rate of a stochastic accelerated variant of Nesterov's accelerated  proximal gradient method is in the next section. 
+    \textbf{Notations}. 
     \subsection{Basic definitions}
@@
         % --------------------------------------------------------------------------------------------------------------
-        \begin{definition}[semi relative smoothness and Semi-SCNVX \textcolor{red}{NEW}]\label{def:seminorm-smooth-scnvx}
+        \begin{definition}[smooth Semi-SCNVX \textcolor{red}{NEW}]\label{def:seminorm-smooth-scnvx}
             Let $m, n\in \N$ be a natural numbers. 
@@
         % --------------------------------------------------------------------------------------------------------------
-        \begin{theorem}[affine composition with strong convexity and smoothness]\label{thm:smooth-aff-sq-scnvs-fxn}
+        \begin{theorem}[affine composite smooth and strongly convex]\label{thm:aff-smooth-sq-scnvx}
             Let $f: \RR^n \rightarrow \RR$ be an $L$ smooth and, $\mu \ge 0$ strongly convex.
-            Let $A: \RR^m \rightarrow \RR^n$, $b \in \RR^n$ be arbitrary. 
-            Let $h: \RR^m \rightarrow \RR= x \mapsto f(Ax - b)$, then the function $h$ satisfies: 
-            \begin{align*}
-                (\forall x \in \RR^m)(\forall y \in \RR^m)\; \frac{\mu}{2}\Vert Ax - Ay\Vert^2 
-                \le D_h(x, y) \le \frac{L}{2}\Vert Ax - Ay\Vert^2. 
-            \end{align*}
-            Therefore, it satisfies Definition \ref{def:semi-scnvx} with $A_1 = \sqrt{L}A, A_2 = \sqrt{\mu}A$. 
+            Let $A: \RR^m \rightarrow \RR^n$, $b \in \RR^n$ be arbitrary and, define $h: \RR^m \rightarrow \RR= x \mapsto f(Ax - b)$. 
+            Ddenote $\Pi = \Pi_{\ker A}$ to be the projection operator onto the kernel of $A$, denote $\Vert A\Vert$ to be the operator norm of the matrix, and $\sigma_{\min}(A)$ to be the smallest non-zero eigenvalues of $A$ in absolute value.
+            Then, it satisfies for all $x \in \RR^m, y \in \RR^m$:  
+            \begin{align*}
+                \frac{\mu \sigma_{\min}(A)^2}{2}\Vert (I - \Pi)(x - y)\Vert^2
+                \le \frac{\mu}{2}\Vert Ax - Ay\Vert^2 
+                \le D_h(x, y) \le \frac{L\Vert A\Vert^2}{2}\Vert x - y\Vert^2. 
+            \end{align*}
+            Therefore, it satisfies Definition \ref{def:semi-scnvx} with $A_1 = \sqrt{L}A, A_2 = \sqrt{\mu}A$ so it's Semi-SCNVX. 
         \end{theorem}
@@
                 \\
-                &\le \frac{L}{2} \Vert Ax - Ay\Vert^2. 
+                &\le \frac{L}{2} \Vert Ax - Ay\Vert^2
+                \\
+                &\le \frac{L\Vert A\Vert^2}{2} \Vert x - y\Vert^2. 
+            \end{align*}
+            Using some linear algebra, one can represent $x - y$ as their orthogonal components in $\ker A$, $\ker A^T$ so it has 
+            \begin{align*}
+                \frac{\mu}{2}\Vert A(x - y)\Vert^2 &= 
+                \frac{\mu}{2}\Vert A(\Pi(x - y) + (1 - \Pi)(x - y))\Vert^2
+                \\
+                &= 
+                \frac{\mu}{2}\Vert A(1 - \Pi)(x - y))\Vert^2
+                \\
+                &\ge \frac{\mu\sigma_{\min}(A)}{2}\Vert (1 - \Pi)(x - y)\Vert^2. 
+            \end{align*}
+            These results makes for the final inequalities: 
+            \begin{align*}
+                \frac{\mu\sigma_{\min}(A)}{2}\Vert (I - \Pi)(x - y)\Vert^2
+                \le 
+                D_h(x, y) \le 
+                \frac{L\Vert A\Vert^2}{2}\Vert x - y\Vert^2. 
             \end{align*}
         \end{proof}
-        The following definition defines the concept of relative smoothness. 
-        We build the proximal gradient inequality for the class of Semi-SCNVX functions. 
+        \begin{theorem}[affine minimizer set for aff comp smooth strongly convex]
+            \todoinline{NOT FINISHED YET.}
+        \end{theorem}
     \subsection{Important inequalities}
-            The following assumptions are ordered from weakest to strongest. 
-            All of them are some of smooth with a non-smooth function. 
-            \begin{assumption}[affine S-CNVX composition plus non-smooth]\label{ass:snorm-smth-p-nsmth}
-                Let $A \in \RR^{m\times n}, b \in \RR^n$
-                Let $F(x): \RR^{m} \mapsto \overline\RR := x \mapsto f(x) + g(x)$. 
-                Assume that: 
-                \begin{enumerate}[noitemsep]
-                    \item $f:\RR^m \rightarrow \RR := x \mapsto h(Ax - b)$ where $h:\RR^n\rightarrow \RR$ is $L$ Lipschitz smooth and, $\mu\ge 0$ strongly convex, then it satisfies Theorem \ref{thm:smooth-aff-sq-scnvs-fxn} with $L > \mu \ge 0$ and $A \in \RR^{m \times n}$.
-                    \item $g:\RR^m \mapsto \overline \RR$ is a convex, proper and closed function. 
-                \end{enumerate}
-            \end{assumption}
             \begin{assumption}[smooth add nonsmooth]\label{ass:smooth-plus-nonsmooth}
@@
                 Let $F = f + g$ satisfies \ref{ass:smooth-plus-nonsmooth} and in addition assume that the set of minimizers $X^+ := \argmin_{x}F(x)$ is non-empty. 
+            \end{assumption}
+            \begin{assumption}[affine composite Semi-CNVX remative smooth plus non-smooth]\label{ass:snorm-smth-p-nsmth}
+                Let $A \in \RR^{m\times n}, b \in \RR^n$
+                Let $F(x): \RR^{m} \mapsto \overline\RR := x \mapsto f(x) + g(x)$. 
+                Assume that: 
+                \begin{enumerate}[noitemsep]
+                    \item $f:\RR^m \rightarrow \RR := x \mapsto h(Ax - b)$ where $h:\RR^n\rightarrow \RR$ is $L$ Lipschitz smooth and, $\mu\ge 0$ strongly convex, then it satisfies Theorem \ref{thm:aff-smooth-sq-scnvx} with $L > \mu \ge 0$ and $A \in \RR^{m \times n}$.
+                    \item $g:\RR^m \mapsto \overline \RR$ is a convex, proper and closed function. 
+                \end{enumerate}
             \end{assumption}
@@
                     \\
-                    &= 
-                    F(z) - F(x^+) 
+                    &= F(z) - F(x^+) 
                     - \frac{\mu}{2}\Vert Az - Ax\Vert^2 
@@
                 At (a), we used the fact that line search asserted the condition $D_f(x^+, x) \le \frac{B}{2}\Vert x^+ - x\Vert^2$. 
-                At (b), we used the fact that $f$ satisfies Definition \ref{def:seminorm-smooth-scnvx} so, it has for all $x, z \in \RR^m$, $D_f(z, x) \ge \frac{\mu}{2}\Vert z - x\Vert^2$. 
-                \par
-                Since $\Pi = \Pi_{\ker A}$ to be the projection onto the kernel of matrix $A$, $z - x$ can be written as $\Pi(z - x) + (z - x) - \Pi(z - x)$ and so: 
-                \begin{align*}
-                    & \Pi(z - x) \perp (z - x) - \Pi(z - x)
-                    \\
-                    \implies & 
-                    \Vert z - x\Vert^2 = \Vert \Pi(z - x) \Vert^2 + \Vert (z - x) - \Pi(z - x)\Vert^2
-                \end{align*}
-                Let $\sigma_{\min}(A)$ denotes the minimum non-zero singular value of $A$ in absolute value, then it has: 
-                \begin{align*}
-                    \Vert A(x - z)\Vert^2 &= \Vert A( \Pi(z - x)  + (z - x) - \Pi(z - x))\Vert^2
-                    \\
-                    &= \Vert A((z - x) - \Pi(z - x))\Vert^2
-                    \\
-                    &\ge \sigma_{\min}(A)^2\Vert (z - x) - \Pi(z - x)\Vert^2.
-                \end{align*}
-                Using two of the above results to keep simplifying the inequality, it yields: 
-                \begin{align*}
-                    0 &\le
-                    F(z) - F(x^+)
-                    - \frac{B}{2}\Vert z - x^+\Vert^2 
+                At (b) we applied results from Theorem \ref{thm:aff-smooth-sq-scnvx}. 
+                Continuing it further with the results from \ref{thm:aff-smooth-sq-scnvx} it adds another inequality: 
+                \begin{align*}
+                    0&\le  F(z) - F(x^+) 
                     - \frac{\mu}{2}\Vert Az - Ax\Vert^2 
                     + \frac{B}{2}\Vert z - x\Vert^2
-                    \\
-                    &\le 
-                    F(z) - F(x^+)
                     - \frac{B}{2}\Vert z - x^+\Vert^2
-                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert (z - x) - \Pi(z - x) \Vert^2
-                        \\ &\quad 
+                    \\
+                    &\le F(z) - F(x^+) 
+                    - \frac{\sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x)\Vert^2
+                    + \frac{B}{2}\Vert z - x\Vert^2
+                    - \frac{B}{2}\Vert z - x^+\Vert^2
+                    \\
+                    &= F(z) - F(x^+) 
+                    - \frac{\sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x)\Vert^2
+                        \\ &\quad
+                        + \frac{B}{2}\Vert \Pi(z - x)\Vert^2
+                        + \frac{B}{2}\Vert (I - \Pi)(z - x)\Vert^2
+                        - \frac{B}{2}\Vert z - x^+\Vert^2
+                    \\
+                    &= F(z) - F(x^+) 
+                    - \frac{B}{2}\Vert z - x^+\Vert^2
+                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x)\Vert^2
                     + \frac{B}{2}\Vert \Pi(z - x)\Vert^2. 
-                    \\
-                    &= 
-                    F(z) - F(x^+)
-                    - \frac{B}{2}\Vert z - x^+\Vert^2 
-                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x) \Vert^2
-                        \\ &\quad 
-                        + \frac{B}{2}\Vert \Pi(z - x)\Vert^2. 
-                \end{align*}
-                Last equality we used the fact that $\Pi$ is an linear operator as well. 
+                \end{align*}
             \end{proof}
@@
                 \end{align*}
-                \todoinline{NOT YET FINISHED}
             \end{theorem}
@@
                 \begin{align*}
-                    F(\lambda z + (1 - \lambda)y) &\le \lambda F(z) + (1 - \lambda)F(x) - \frac{\lambda(1 - \lambda)\mu}{2}\Vert Ax - Ay\Vert^2. 
-                \end{align*}
-                Let $\Pi = \Pi_{\ker A}$ be the projection onto the kernel of $A$, then it has: 
-                \begin{align*}
-                    \Vert Ax - Ay\Vert^2 &= \Vert A\Pi(x - y) + (I - \Pi)(x - y) \Vert^2
-                    \\
-                    &= 
-                    \Vert A\Pi(x - y) \Vert^2 + \Vert A(I - \Pi)(x - y) \Vert^2
-                    \\
-                    &\ge 0 + \sigma_{\min}(A)^2\Vert (I - \Pi)(x - y) \Vert^2
-                \end{align*}
-                Therefore, it gives the weaker inequality: 
-                \begin{align*}
-                    F(\lambda z + (1 - \lambda)y) &\le \lambda F(z) + (1 - \lambda)F(x) - \frac{\sigma_{\min}(A)^2\lambda(1 - \lambda)\mu}{2}\Vert (I - \Pi)(x - y)\Vert^2. 
-                \end{align*}
+                    F(\lambda z + (1 - \lambda)y) &\le \lambda F(z) + (1 - \lambda)F(x) - \frac{\lambda(1 - \lambda)\mu}{2}\Vert Ax - Ay\Vert^2
+                    \\
+                    &\le 
+                    \lambda F(z) + (1 - \lambda)F(x) - \frac{\lambda(1 - \lambda)\mu\sigma_{\min}(A)^2}{2}\Vert (I - \Pi) x - y\Vert^2. 
+                \end{align*}
+                The second inequality uses Theorem \ref{thm:aff-smooth-sq-scnvx}. 
             \end{proof}
@@
 \section{Stochastic accelerated proximal gradient}
-    In this section, we define the Stochastic accelerated Nesterov's Acceleration algorithm and, progressively build up the results to the one step convergence of the algorithm. 
-    The following assumption about the objective function is fundamental in incremental gradient method for Machine Learning, data science other similar tasks. 
+    First, this is an overview of this section.
+
     \begin{assumption}[sum of many affine composite]\label{ass:sum-of-many-aff-comp}
-        Let $A^{(1)}, A^{(2)}, \ldots A^{(n)}$ be a list of $\RR^{n\times m}$ matrices. 
-        Suppose $F:\RR^n \rightarrow \overline \RR:= (1/n)\left(\sum_{i = 1}^{n} f_i(x) + g_i(x)\right)$. 
-        Assume
-        \begin{enumerate}
-            \item 
-        \end{enumerate}
+        Let $A^{(1)}, A^{(2)}, \ldots A^{(n)}$ be a list of $\RR^{m\times n}$ matrices and, $b^{(1)}, b^{(2)}, \ldots, b^{(n)}$ be a list of vectors in $\RR^n$. 
+        Suppose $F:\RR^m \rightarrow \overline \RR:= \frac{1}{n}\sum_{i = 1}^{n} F_i(x)$, so it admits representations 
+        \begin{align*}
+            F(x) = f(x) + g(x) = \frac{1}{n}\sum_{i = 1}^{n} f_i(x) + g_i(x) = \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)}x - b^{(i)}) + g_i(x)
+        \end{align*}
+        Where, each $F_i = f_i + g_i$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth} with $K^{(i)} > \nu^{(i)} \ge 0, b^{(i)} \in \RR^n$ and $A^{(i)} \in \RR^{m \times n}$. 
+        So, each $h_i$ are $\nu^{(i)}$ strongly convex and $K^{(i)}$ Lipschitz smooth. 
+        \par
+        Take note that the function $f(x) = \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)})$ is the composition of the strongly convex function $h = \frac{1}{n}\sum_{i = 1}^{n} h_i$ that is a $\RR^{mn}\rightarrow \RR$ mapping with strong convexity $\frac{1}{n}\sum_{i = 1}^{n} \nu^{(i)}$ and, the affine $\RR^m \rightarrow \RR^{mn}$ mapping $\mathcal A := x \mapsto (A^{(1)}x - b^{(1)},\ldots,  A^{(n)}x - b^{(n)})$.
+        $f$ satisifes Theorem \ref{thm:aff-smooth-sq-scnvx} and it can be written as: 
+        \begin{align*}
+            f(x) = \sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)}) = h(\mathcal A x). 
+        \end{align*}
     \end{assumption}
+
     \begin{assumption}[sum of many]\label{ass:sum-of-many}
-        Define $F := (1/n)\sum_{i = 1}^{n} F_i$ where each $F_i = f_i + g_i$.
-        Assume that for all $i = 1, \ldots, n$, each $f_i:\RR^n \rightarrow \RR$ are $K^{(i)}$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K^{(i)} > \mu^{(i)}$ and, $g_i:\RR^n \rightarrow \overline \RR$ is a closed convex proper function.
+        Define $F := (1/n)\sum_{i = 1}^{n} F_i$ where each $F_i = f_i + g_i$, so it can be written as: 
+        \begin{align*}
+            F(x) = f(x) + g(x) = \frac{1}{n}\sum_{i = 1}^{n} f_i(x) + g_i(x)
+        \end{align*}
+        Assume that for all $i = 1, \ldots, n$, each $f_i:\RR^n \rightarrow \RR$ are $K^{(i)}$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K^{(i)} > \mu^{(i)}$ and, $g_i:\RR^n \rightarrow \overline \RR$ is a closed convex proper function satisfies Assumption \ref{ass:smooth-plus-nonsmooth}.
         \par 
-        Consequently, the function $f$ can be written as $F = g + f$ with $f = (1/n)\sum_{i = 1}^{n} f_i, g = (1/n)\sum_{i = 1}^{n}g_i$ therefore, it also satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = (1/n)\sum_{i = 1}^n K^{(i)}$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$.
+        Take note that, the function $f$ can be written as $F = g + f$ with $f = (1/n)\sum_{i = 1}^{n} f_i, g = (1/n)\sum_{i = 1}^{n}g_i$ therefore, it also satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = (1/n)\sum_{i = 1}^n K^{(i)}$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$.
     \end{assumption}
-    This assumption is stronger than Assumption \ref{ass:smooth-plus-nonsmooth}. 
-    It still appears in practice, for example if $F_i$ are all indicator function of convex set, then it solves feasibility problem $\bigcap_{i = 1}^n C_i$ and, in this case, the proximal gradient operator becomes a projection onto the convex set $C_i$.
-    In practice, each of the strong convexity constant $\mu^{(i)}$ may not be easily accessible. 
-    And we further note that if $\mu > 0$ strongly convex, then there exists at least one $\mu^{(i)} \ge 0$. 
+    Both assumptions are equivalent, functions satisfies one can be translated in form so it satisfies the other with some extra/fewer parameters. 
+    However, it's important to know that for a $F := \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)}) + g_i(x)$ satisfying Assumption \ref{ass:sum-of-many-aff-comp}, Theorem \ref{thm:pg-ineq-semi-scnvx}, \ref{thm:smnrm-jnsn-smth-nsmth} applies with parameter $\nu^{(i)}\sigma_{\min}(A^{(i)})^2$ for each summees.
+    This can't be known if it only satisfies Assumption \ref{ass:sum-of-many}. 
     \par
@@
     \end{assumption}
+
+    Due to the fact the algorithms have to be very different support convergence claim for different assumptions on the functions, the following definition gives a generic ideas for all algorithms that specializes on top of it for different assumptions placed on the objective functions.
+    These definitions are not actual algorithms, they are conditions an algorithm must adhere to for the theorems based on it to be valid. 
+    Read then as specifications. 
+    % --------------------------------------------------------------------------------------------------------------
+    \begin{definition}[SNAPG-V2 prototype \textcolor{red}{NEW}]\;\label{def:snapg-v2-proto}\\
+        Let 
+        \begin{enumerate}[nosep]
+            \item $F$ satisfies Assumption \ref{ass:sum-of-many}, 
+            \item $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$, 
+            \item $\sigma^{(k)}$ be another list of i.i.d random variable. 
+            \item $\tilde \mu \ge 0$ be a constant that is fixed.
+            \item Let $(L_k)_{k \ge 0}$ a sequence of strictly positive numbers. 
+        \end{enumerate}
+        Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
+        The SNAPG prototype specifies algorithm that generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
+        \begin{align*}
+            & \alpha_k \in (0, 1): (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \tilde \mu/L_k\right), \\
+            & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \sigma^{(k)}\right)^{-1}, \\
+            & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
+            & L_k > 0: D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
+            & x_k =  T_{L_k}(y_k | F_{I_k}), \\
+            & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
+        \end{align*}
+    \end{definition}
+    \begin{remark}
+        $\tilde \mu_k, L_k$ are not necessary a random variable because they are determined by a line-search like conditions, consequently $(\alpha_k)_{k\ge 0}$, whether they are a random variable depends on the line search procedures.
+        Otherwise, all the iterates $(x_k, y_k, z_k)$ are random variable determined by $I_k$ when conditioned on all previous $I_{k - 1}, I_{k - 2}, \ldots, I_{0}$. 
+        \par
+        \textcolor{red}{NEW}. One may notice that $\alpha_k$ requires $L_k$ which comes before $L_k, x_k$ which are needed in advanced for $\alpha_k$. 
+        This may seem off since no algorithm can know what $L_k$ to choose in advanced to determine the line search. 
+        But, it is important to note that in here, we defined a sequence of conditions on the iterates $x_k, y_k, z_k$, and auxiliary sequences $\alpha_k, L_k$ which is not a definition of any algorithm.
+        It is quantifying the conditions needed for an algorithm that actually implements it.
+        \par
+        For the trivial case where we don't need to worry about it is when $L_k = \max_{i = 1, \ldots, n} K^{(i)}$. 
+        See Chambolle, Calatroni \cite{calatroni_backtracking_2019} for an implementation of linear search with backtracking for the FISTA algorithm, it is how one would implement it in the deterministic case.
+    \end{remark}
+    % --------------------------------------------------------------------------------------------------------------
+    \begin{definition}[SNAPG-V2 affine \textcolor{red}{NEW}]\label{def:snapg-v2-aff}
+        Let $F, (I_k)_{k \ge 0}, \tilde \mu$ and, $(L_k)_{k \ge 0}$ be given as in Definition \ref{def:snapg-v2-proto}. 
+        But in addition, assume that: 
+        \begin{enumerate}[nosep]
+            \item $F$ also satisfies Assumption \ref{ass:sum-of-many-aff-comp} with $\RR^{m \times n}$ matrices: $A^{(1)}, A^{(2)}, \ldots, A^{(n)}$, vectors in $\RR^n$: $(b^{(1)}, \ldots, b^{(n)})$. 
+            \item Choose $\sigma^{(k)} = \nu^{(I_k)}\sigma_{\min}(A^{(I_k)})^2$. 
+        \end{enumerate}
+        Then, SNAPG-V2 affine specifies algorithms that generate the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfying conditions as specified in Definition \ref{def:snapg-v2-proto} with the above parameters.
+    \end{definition}
+    % --------------------------------------------------------------------------------------------------------------
+    \begin{definition}[SNAPG-V2 vanilla]\label{def:snapg-v2}
+        Let $F, (I_k)_{k \ge 0}, \tilde \mu$ and, $(L_k)_{k \ge 0}$ be given as in Definition \ref{def:snapg-v2-proto}. 
+        But in addition, assume that: 
+        \begin{enumerate}[nosep]
+            \item Choose $\sigma^{(k)} = \mu^{(I_k)}$. 
+        \end{enumerate}
+        Then, SNAPG-V2 vanilla affine specifies algorithms that generate the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfying conditions as specified in Definition \ref{def:snapg-v2-proto} with the above parameters.
+    \end{definition}
     % --------------------------------------------------------------------------------------------------------------
@@
     % --------------------------------------------------------------------------------------------------------------
-    \begin{definition}[SNAPG-V2]\label{def:snapg-v2}
-        Let $F$ satisfies Assumption \ref{ass:sum-of-many}. 
-        Let $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$. 
-        Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
-        Let $\tilde \mu \ge 0$ be a constant that is fixed.
-        The SNAPG generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
-        \begin{align*}
-            & \alpha_k \in (0, 1): (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \tilde \mu/L_k\right), \\
-            & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
-            & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
-            & L_k > 0: D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
-            & x_k =  T_{L_k}(y_k | F_{I_k}), \\
-            & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
-        \end{align*}
-    \end{definition}
-    \begin{remark}
-        $\tilde \mu_k, L_k$ are not necessary a random variable because they are determined by a line-search like conditions, consequently $(\alpha_k)_{k\ge 0}$, whether they are a random variable depends on the line search procedures.
-        Otherwise, all the iterates $(x_k, y_k, z_k)$ are random variable determined by $I_k$ when conditioned on all previous $I_{k - 1}, I_{k - 2}, \ldots, I_{0}$. 
-        \par
-        \textcolor{red}{NEW}. One may notice that $\alpha_k$ requires $L_k$ which comes before $L_k, x_k$ which are needed in advanced for $\alpha_k$. 
-        This may seem off since no algorithm can know what $L_k$ to choose in advanced to determine the line search. 
-        But, it is important to note that in here, we defined a sequence of conditions on the iterates $x_k, y_k, z_k$, and auxiliary sequences $\alpha_k, L_k$ which is not a definition of any algorithm.
-        It is quantifying the conditions needed for an algorithm that actually implements it.
-        \par
-        For the trivial case where we don't need to worry about it is when $L_k = \max_{i = 1, \ldots, n} K^{(i)}$. 
-        See Chambolle, Calatroni \cite{calatroni_backtracking_2019} for an implementation of linear search with backtracking for the FISTA algorithm, it is how one would implement it in the deterministic case.
-    \end{remark}
-    The following lemma state the relationships of the iterates generated by SNAPG-V2. 
-    They are needed for the convergence proof. 
-    % --------------------------------------------------------------------------------------------------------------
-    \begin{lemma}[properties of the iterates \textcolor{red}{NEW}]\label{lemma:snapg2-itrs-props}
-        Suppose that the iterates $(z_k, x_k, y_k)_{k \ge 0}$ and sequence $(\alpha_k)_{k \ge 1}$ are produced by an algorithm satisfying Definition \ref{def:snapg-v2}. 
+    \begin{lemma}[properties of the iterates on SNAPG-V2 prototype \textcolor{red}{NEW}]\label{lemma:iters-snapg2-proto}
+        Suppose that the iterates $(z_k, x_k, y_k)_{k \ge 0}$ and sequence $(\alpha_k)_{k \ge 1}$ satisfies Definition \ref{def:snapg-v2-proto}. 
         Let $\bar x \in \RR^n$.
@@
         \begin{enumerate}
-            \item\label{lemma:snapg2-itrs-props-item1} For all $k \ge 1$ it has: 
+            \item\label{lemma:iters-snapg2-proto-item1} For all $k \ge 1$ it has: 
             \begin{align*}
@@
                     = 
-                    \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-                    + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
-            \end{align*}
-            \item\label{lemma:snapg2-itrs-props-item2} For all $k \ge 1$, it has: $z_k - x_k = \alpha_k(x - \bar x)$
+                    \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
+                    + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}(\bar x - x_{k - 1}).
+            \end{align*}
+            \item\label{lemma:iters-snapg2-proto-item2} For all $k \ge 1$, it has: $z_k - x_k = \alpha_k(x - \bar x)$
         \end{enumerate}
@@
         \textbf{Proof of \ref{lemma:snapg2-itrs-props-item1}}. 
-        From Definition \ref{def:snapg-v2}, it has
+        From Definition \ref{def:snapg-v2-proto}:
         \begin{align*}
@@
             \left(
-                1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
+                1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \sigma^{(i)}}
             \right)^{-1} = \left(
-                \frac{L_k\alpha_k - \mu^{(i)} + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
+                \frac{L_k\alpha_k - \sigma^{(i)} + L_k(1 - \alpha_k)}{L_k\alpha_k - \sigma^{(i)}}
             \right)^{-1}
-            = \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}. 
+            = \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}. 
         \end{align*}
@@
             \\
-            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} 
+            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} 
             \left(
-                v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}} x_{k - 1}
+                v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \sigma^{(i)}} x_{k - 1}
             \right) - y_k
             \\
-            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1}
-            + \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1} - y_k
-            \\
-            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1}
+            + \frac{L_k(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1} - y_k
+            \\
+            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
             + 
             \left(
-                \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} - (1 - \alpha_k)
+                \frac{L_k(1 - \alpha_k)}{L_k - \sigma^{(i)}} - (1 - \alpha_k)
             \right) x_{k - 1} - y_k
             \\
-            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
             + 
             (1 - \alpha_k)\left(
-                \frac{L_k - L_k + \mu^{(i)}}{L_k - \mu^{(i)}}
+                \frac{L_k - L_k + \sigma^{(i)}}{L_k - \sigma^{(i)}}
             \right) x_{k - 1} - y_k
             \\
-            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
             + 
-            \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}x_{k - 1} - y_k. 
+            \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}x_{k - 1} - y_k. 
         \end{align*}
@@
             (1 - \alpha_k)x_{k - 1} - y_k &= 
-            - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
-            - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}. 
+            - \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1} 
+            - \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1}. 
         \end{align*}
@@
             &= \alpha_k \bar x 
-            - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
-            - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
-            \\
-            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+            - \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1} 
+            - \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1}
+            \\
+            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
             + \left(
-                \alpha_k - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}
+                \alpha_k - \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}
             \right)\bar x
-            - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
-            \\
-            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+            - \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1}
+            \\
+            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
             + \left(
-                \frac{\alpha_kL_k - \alpha_k \mu^{(i)} - L_k\alpha_k + \mu^{(i)}}{L_k - \mu^{(i)}}
+                \frac{\alpha_kL_k - \alpha_k \sigma^{(i)} - L_k\alpha_k + \sigma^{(i)}}{L_k - \sigma^{(i)}}
             \right)\bar x
-            - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
-            \\
-            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-            + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}\bar x
-            - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
-            \\
-            &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-            + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
+            - \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1}
+            \\
+            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
+            + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}\bar x
+            - \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1}
+            \\
+            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
+            + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}(\bar x - x_{k - 1}).
         \end{align*}
@@
     % --------------------------------------------------------------------------------------------------------------
-    \begin{lemma}[SNAPG-V2 one step convergence prototype stage-I]\label{lemma:snagp2-one-step-s1-proto}
-
-    \end{lemma}
-    \begin{proof}
-
-    \end{proof}
-    % --------------------------------------------------------------------------------------------------------------
-    \begin{theorem}[SNAPG-V2 one step convergence]\label{thm:snapg2-one-step}
-        Let $F$ satisfies assumption \ref{ass:interp-hypothesis}. 
-        Suppose that an algorithm satisfying Definition \ref{def:snapg-v2} uses this $F$. 
-        Let $\mathbb E_k$ denotes the expectation conditioned on $I_0, I_1, \ldots, I_{k - 1}$. 
-        Then, for all $k \ge 1$, it has the following inequality 
-        \begin{align*}
-            & \mathbb E_k\left[F_{I_k}(x_{k})\right] 
-            - F(\bar x) 
-            + \mathbb E_k\left[
-                \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-            \right]
+    \begin{lemma}[SNAPG-V2 one step convergence stage I \textcolor{red}{NEW}]\label{lemma:snagp2-one-step-s1-proto}
+        Suppose that the sequence $(y_k, x_k, v_k)$ satisfies Definition \ref{def:snapg-v2-aff}. 
+        Fix some $k \in \N, k \ge 1$, suppose that $I_k = i$.
+        Denote $\Pi^{(i)} = \Pi_{\ker A^{(i)}}$ to be the projection matrix onto the kernel of $A^{(i)}$. 
+        Then for all $\bar x \in \RR^m$, the iterates satisfies the inequality: 
+        \begin{align*}
+            &F_i(x_{k}) - F_i(\bar x) 
+            + \frac{L_k\alpha_k^2}{2} \left\Vert \left(I - \Pi^{(i)}\right)(\bar x - v_k)\right\Vert^2
             \\
@@
             (1 - \alpha_k)\left(
-                    \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
-                    - F(\bar x)
-                    + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
-            \right)
-                \\ &\quad 
-                + \mathbb E_k\left[
-                    \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-                \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
-                + \frac{\alpha_k(\tilde\mu - \mu)}{2} 
-                \Vert \bar x - v_{k - 1}\Vert^2. 
-        \end{align*}
-        And for $k = 0$, it has 
-        \begin{align*}
-            \mathbb E \left[ F_{I_0}\right] - F(\bar x) 
-            + \frac{L_0}{2}\mathbb E \left[\Vert \bar x - x_0\Vert^2\right]
-            &\le 
-            \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
-        \end{align*}
-    \end{theorem}
+                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}
+                \left\Vert \left(I - \Pi^{(i)}\right)(v_{k - 1} - \bar x)\right\Vert^2
+            \right)     
+            + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.
+        \end{align*}
+        And when $k = 0$, we have: 
+        \todoinline{HERE}
+    \end{lemma}
     \begin{proof}
@@
         \begin{itemize}
-            \item[(a)] We can use proximal gradient inequality from Theorem \ref{thm:pg-ineq} with $z = z_k$ because each $F_i$ is $K_i$ Lipschitz smooth and, $\mu^{(i)}$ strongly convex with $K_i \ge \mu^{(i)}$.
-            \item[(b)] We can use Jensen's inequality of Theorem \ref{thm:jesen} with $z = z_k$ on $F_i$. 
+            \item[(a)] We can use proximal gradient inequality from Theorem \ref{thm:pg-ineq-semi-scnvx} with $z = z_k, B = L_k, \Pi^{i} = \Pi_{\ker A^{(i)}}$ because Assumption \ref{ass:sum-of-many-aff-comp} has each $F_i = f_i + g_i$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth}.
+            \item[(b)] We can use seminorm Jensen's inequality of Theorem \ref{thm:smnrm-jnsn-smth-nsmth} with $z = z_k$ on $F_i$. 
             \item[(c)] The sequence $(\alpha_k)_{k \ge 0}$ has $(L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right)$. 
-            \item[(d)] Prove in Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item1} we use the equality:
+            \item[(d)] Prove in Lemma \ref{lemma:iters-snapg2-proto} \ref{lemma:iters-snapg2-proto-item1} we will the equality:
             \begin{align*}
@@
                 = 
-                \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-                + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
-            \end{align*}
-            \item [(e)] From Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item2}, we use: $(\forall k \ge 1)\; z_k - x_k = \alpha_k (\bar x - v_k)$. 
+                \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
+                + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}(\bar x - x_{k - 1}).
+            \end{align*}
+            \item [(e)] From Lemma \ref{lemma:iters-snapg2-proto} \ref{lemma:iters-snapg2-proto-item2}, we use: $(\forall k \ge 1)\; z_k - x_k = \alpha_k (\bar x - v_k)$. 
             \item [(f)] Using direct algebra, we have for all $k \ge 1$: 
@@
                 \frac{\left(
-                    L_k\alpha_k - \mu^{(i)}
-                \right)^2}{2(L_k - \mu^{(i)})} 
+                    L_k\alpha_k - \sigma^{(i)}
+                \right)^2}{2(L_k - \sigma^{(i)})} 
                 -
@@
                 \frac{
-                \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
+                \left(L_k \alpha_k - \sigma^{(i)}\right)\sigma^{(i)}
                 \left(\alpha_k - 1\right)
                 }
-                {2(L_k - \mu^{(i)})}
-                + \frac{\alpha_k(\tilde \mu_k - \mu^{(i)})}{2}. 
-            \end{align*}
-            \item[(h)] Because we assumed interpolation hypothesis in Assumption \ref{ass:interp-hypothesis}, it has $\mathbb E[F_{I_k}(\bar x)] = F(\bar x)$ for all $\bar x$ that is a minimizer of $F$.
+                {2(L_k - \sigma^{(i)})}
+                + \frac{\alpha_k(\tilde \mu_k - \sigma^{(i)})}{2}. 
+            \end{align*}
         \end{itemize}
         For all $k \ge 1$, starting with (a) we have: 
-        \begin{align}\label{ineq:snapg2-one-step-chain1}
+        \begin{align}\label{ineq:snapg2-one-step-stage1-chain1}
             \begin{split}
-                0 &\le F_i(z_k) - F_i(x_k) - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2
+                0 &\le F_i(z_k) - F_i(x_k) - 
+                \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
+                + \frac{L_k - \nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\left\Vert (I - \Pi^{(i)}) (z_k - y_k)\right\Vert^2
+                    \\ &\quad 
+                    + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
                 \\
                 &\underset{\text{(b)}}{\le}
-                \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) \\
-                    &\quad 
-                    - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
+                \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k)     
                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-                    + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2. 
+                + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
+                    \\&\quad 
+                    - \frac{\nu^{(i)}\sigma_{\min}(A^{(i)})^2\alpha_k(1 - \alpha_k)}{2}\Vert (I - \Pi^{(i)})(\bar x - x_{k - 1})\Vert^2
+                    \\&\quad
+                    + \frac{L_k - \nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\Vert (I - \Pi^{(i)})(z_k - y_k)\Vert^2
             \end{split}
         \end{align}
-        And we have the following chain of equalities:
+        \textbf{For simpler notations}, we use the following notation $\Vert x\Vert_p = \Vert (I - \Pi^{(i)})x\Vert$ to denote a seminorm induced by the linear mapping $(I - \Pi^{(i)})$, and use $\langle \cdot,\cdot\rangle_p := \langle (I - \Pi^{(i)})(\cdot), \langle (I - \Pi^{(i)})(\cdot)\rangle$ for the inner product as well.
+        We also use $\sigma^{(i)} = \nu^{(i)}\sigma_{\min}(A^{(i)})^2$ which is specified in Definition \ref{def:snapg-v2-aff}. 
+        And we will simplify the last two terms from the above inequality using a chain of equalities. 
         {\allowdisplaybreaks
         \begin{align*}
-            & - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
-            + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2
+            & - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_p
+            + \frac{L_k - \sigma^{(i)}}{2}\Vert z_k - y_k\Vert^2_p
             \\
             &\underset{\text{(d)}}{=}
-            - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2 
+            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_p
                 \\&\quad
-                + \frac{L_k - \mu^{(i)}}{2}
+                + \frac{L_k - \sigma^{(i)}}{2}
                 \left\Vert
-                    \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-                    + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1})
-                \right\Vert^2
-            \\
-            &= 
-            - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2 
+                    \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
+                    + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}(\bar x - x_{k - 1})
+                \right\Vert^2_p
+            \\
+            &= 
+            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_p 
                 \\&\quad
-                + \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{(\mu^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2 
+                + \frac{(L_k\alpha_k - \sigma^{(i)})^2}{2(L_k - \sigma^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2_p
+                + \frac{(\sigma^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \sigma^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2_p 
                 \\&\quad 
-                + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p
             \\
@@
             \left(
-                \frac{(\mu^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
-            \right)\Vert \bar x - x_{k - 1}\Vert^2
+                \frac{(\sigma^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \sigma^{(i)})} - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}
+            \right)\Vert \bar x - x_{k - 1}\Vert^2_p
                 \\ &\quad 
                 + \left(
-                    \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
-                \right) \Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                    \frac{(L_k\alpha_k - \sigma^{(i)})^2}{2(L_k - \sigma^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
+                \right) \Vert \bar x - v_{k - 1}\Vert^2_p
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
                 \\&\quad 
-                + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p
             \\
             &\underset{\text{(f)}}{=}
-            \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
-            {2\left(L_k - \mu^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2
+            \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}
+            {2\left(L_k - \sigma^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2_p
                 \\ &\quad 
                 + \left(
-                    \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
-                \right) \Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                    \frac{(L_k\alpha_k - \sigma^{(i)})^2}{2(L_k - \sigma^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
+                \right) \Vert \bar x - v_{k - 1}\Vert^2_p
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
                 \\&\quad 
-                + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p
             \\
             & \underset{\text{(g)}}{=} 
-            \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
-            {2\left(L_k - \mu^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2
+            \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}
+            {2\left(L_k - \sigma^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2_p
                 \\ &\quad 
@@
                     \frac{
-                        \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
+                        \left(L_k \alpha_k - \sigma^{(i)}\right)\sigma^{(i)}
                         \left(\alpha_k - 1\right)
                     }
-                    {2(L_k - \mu^{(i)})}
-                    + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}
-                \right) 
-                \Vert \bar x - v_{k - 1}\Vert^2
-                \\ &\quad 
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
-            \\
-            &= 
-            \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\left(
-                \Vert \bar x - x_{k - 1}\Vert^2 + \Vert \bar x - v_{k - 1}\Vert^2 - 2\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
-            \right) 
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-            \\
-            &= \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
-                \Vert x_{k - 1} - v_{k - 1} \Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2.
+                    {2(L_k - \sigma^{(i)})}
+                    + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2}
+                \right) 
+                \Vert \bar x - v_{k - 1}\Vert^2_p
+                \\ &\quad 
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
+                \\ &\quad
+                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p
+            \\
+            &= 
+            \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}
+            \left(
+                \Vert \bar x - x_{k - 1}\Vert^2_p 
+                + \Vert \bar x - v_{k - 1}\Vert^2_p 
+                - 2\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p
+            \right) 
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
+            \\
+            &= \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}
+                \Vert x_{k - 1} - v_{k - 1} \Vert^2_p
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p.
         \end{align*}
         }
-        Substituting the above back to the tail of Inequality \eqref{ineq:snapg2-one-step-chain1} it gives: 
+        Substituting the above back to the tail of Inequality \eqref{ineq:snapg2-one-step-stage1-chain1} it gives: 
         {\allowdisplaybreaks
@@
             \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k)     
-                \\&\quad 
             - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-                + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
-                \Vert x_{k - 1} - v_{k - 1} \Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                \\ &\quad 
+                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_p
+                + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
             \\
@@
             \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k)     
-                \\&\quad 
-                - \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-                + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
-                \Vert x_{k - 1} - v_{k - 1} \Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-            \\
-            &= (\alpha_k - 1)F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) + F_i(\bar x)
-                \\&\quad 
-                - \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-                + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+            - \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2 
+                \\ &\quad 
+                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_p
+                + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
+            \\
+            &= 
+            (\alpha_k - 1) F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) + F_i(\bar x)
+            - \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2 
+                \\ &\quad 
+                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_p
+                + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
             \\
             &= (1 - \alpha_k)\left(
-                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
+                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2_p
             \right) 
@@
                     F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-                \right)
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
+                \right) + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.
         \end{align*}
         }
-        Recall that $i = I_k$ is the random variable from Definition \ref{def:snapg-v2}. 
-        Rearranging the last expression in the above equality chain can be conveniently written as
-        \begin{align}
-            \begin{split}
-                & F_{I_k}(x_{k}) - F_{I_k}(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-                \\ &\le 
-                (1 - \alpha_k)\left(
-                    F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
-                \right) 
-                    \\ &\quad 
-                    + \frac{\alpha_k(\tilde \mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-                    + \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
-            \end{split}
-        \label{ineq:snapg2-one-step-presult1}\end{align}
-        Recall $\mathbb E_k$ denotes the conditional expectation on $I_0, I_1, \ldots, I_{k - 1}$. 
-        Taking the conditional expectation on the LHS of the \eqref{ineq:snapg2-one-step-presult1} yields: 
-        \begin{align*}
-            & \mathbb E_k\left[
-                F_{I_k}(x_{k}) - F_{I_k}(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-            \right]
-            \\
-            &\underset{\text{(h)}}{=}
-            \mathbb E_k\left[F_{I_k}(x_{k})\right] 
-            - F(\bar x) 
-            + \mathbb E_k\left[
-                \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-            \right]. 
-        \end{align*}
-        On the RHS of \eqref{ineq:snapg2-one-step-presult1}, using the linearity property while taking the conditional expectation yields: 
-        {\allowdisplaybreaks
-        \begin{align*}
-            & \mathbb E_k\left[
-                (1 - \alpha_k)\left(
-                    F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
-                \right)
-            \right]
-                \\ &\quad 
-                + \mathbb E_k \left[
-                    \frac{\alpha_k(\tilde\mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-                \right]
-                + \mathbb E_k\left[
-                    \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
-                \right]
-            \\
-            &\underset{\text{(1)}}{=} 
-            (1 - \alpha_k)\left(
-                    \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
-                    -\mathbb E_k [F_{I_k}(\bar x)] 
-                    + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
-            \right)
-                \\ &\quad 
-                + \mathbb E_k \left[
-                    \frac{\alpha_k(\tilde\mu - \mu^{(I_k)})}{2} 
-                \right]\Vert \bar x - v_{k - 1}\Vert^2
-                + \mathbb E_k\left[
-                    \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-                \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
-            \\
-            &\underset{\text{(h)}}{=} 
-            (1 - \alpha_k)\left(
-                    \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
-                    - F(\bar x)
-                    + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
-            \right)
-                \\ &\quad 
-                + \mathbb E_k \left[
-                    \frac{\alpha_k(\tilde\mu - \mu^{(I_k)})}{2} 
-                \right]\Vert \bar x - v_{k - 1}\Vert^2
-                + \mathbb E_k\left[
-                    \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-                \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
-            \\
-            &\underset{\text{(2)}}{=}
-            (1 - \alpha_k)\left(
-                    \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
-                    - F(\bar x)
-                    + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
-            \right)
-                \\ &\quad 
-                \frac{\alpha_k(\tilde\mu - \mu)}{2} 
-                \Vert \bar x - v_{k - 1}\Vert^2
-                + \mathbb E_k\left[
-                    \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-                \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
-        \end{align*}
-        }
-        We note that at label (1), we used the fact that $\alpha_k$ is a constant and, $x_{k - 1}, v_{k - 1}$ only depends on random variable $I_0, I_1, \ldots, I_{k - 1}$ hence it falls out of the conditional expectation $\mathbb E_k$.
-        At label (2), we used assumption (Assumption \ref{ass:sum-of-many}) that the averages of all the $\mu^{(I_k)}$ on each $F_{I_k}$ equals to $\mu$ hence, the expectation evaluates to zero by linearity of the expected value operator.
-        \par
-        Combining the above results on the expectation of RHS, and LHS of \eqref{ineq:snapg2-one-step-presult1}, we have the one-step inequality in expectation: 
-        \begin{align*}
-            & \mathbb E_k\left[F_{I_k}(x_{k})\right] 
-            - F(\bar x) 
-            + \mathbb E_k\left[
-                \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-            \right]
+        Re-arranging, with some linear algebra:  we get out first result: 
+        \begin{align*}
+            &F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2_p 
+            \\
+            &\le 
+            F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
             \\
@@
             (1 - \alpha_k)\left(
-                    \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
-                    - F(\bar x)
-                    + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
-            \right)
-                \\ &\quad 
-                + \mathbb E_k\left[
-                    \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-                \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
-        \end{align*}
-        Finally, we show the base case. 
-        When $k = 0$, by assumption it had $\alpha_0 = 1$ hence $\tau_0$ in Definition \ref{def:snapg-v2} has $\tau_0 = 0$ which makes $y_0 = v_{- 1} = x_{-1}$. 
-        Therefore, it makes $x_0 = T_{L_0}(y_0 | F_{I_0}) = T_{L_0}(v_{-1} | F_{I_0})$. 
-        Similarly, it has also $z_0 = \bar x$.
-        Applying Theorem \ref{thm:pg-ineq} with $z = z_0$ and, assume a successful line search with $L_0$, it yields: 
-        \begin{align*}
-            0 &\le F_{I_0}(z_0) - F_{I_0}(x_0) - \frac{L_0}{2}\Vert z_0 - x_0\Vert^2 + \frac{L_0 - \mu^{(I_0)}}{2}\Vert z_0 - y_0\Vert^2
-            \\
-            &= F_{I_0}(\bar x) - F_{I_0}(x_0) - \frac{L_0}{2}\Vert \bar x - x_0\Vert^2 + \frac{L_0 - \mu^{(I_0)}}{2}\Vert \bar x - v_{-1}\Vert^2. 
-        \end{align*}
-        Re-arranging and taking the expectation it yields: 
-        \begin{align*}
-            \mathbb E \left[
-                F_{I_0}(x_0) - F_{I_0}(\bar x) + \frac{L_0}{2}\Vert \bar x - x_0\Vert^2
-            \right]
-            &\underset{\text{(h)}}{=}
-            \mathbb E \left[ F_{I_0}\right] - F(\bar x) 
-            + \frac{L_0}{2}\mathbb E \left[\Vert \bar x - x_0\Vert^2\right]
-            \\
-            &\le \frac{L_0 - \mathbb E \left[\mu^{(I_0)}\right]}{2}\Vert \bar x - v_{-1}\Vert^2
-            \\
-            &= \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
-        \end{align*}
+                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2_p
+            \right)     
+            + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.
+        \end{align*}
+        For the first inequality, recall that $\Vert \cdot\Vert_p = \Vert (I - \Pi^{(i)})(\cdot)\Vert \le \Vert \cdot\Vert$ because $(I - \Pi^{(i)})$ is a projector and, it projects to $\ker A^{(i)}$.
+        Now, let's takle the $k = 0$ case. 
+        \todoinline{HERE}
         % INTERMEDIATE RESULTS
+        \par
         \textbf{Proof of (f)}. 
@@
         \begin{align*}
-            & \frac{\left(\mu^{(i)}\right)^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} 
-            - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
-            \\
-            &= 
-            \frac{1}{2\left(L_k - \mu^{(i)}\right)}
+            & \frac{\left(\sigma^{(i)}\right)^2(1 - \alpha_k)^2}{2(L_k - \sigma^{(i)})} 
+            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}
+            \\
+            &= 
+            \frac{1}{2\left(L_k - \sigma^{(i)}\right)}
             \left(
-                \left(\mu^{(i)}\right)^2(1 - \alpha_k)^2
-                - \left(L_k - \mu^{(i)}\right)\mu^{(i)} \alpha_k(1 - \alpha_k)
-            \right)
-            \\
-            &= \frac{1 - \alpha_k}{2\left(L_k - \mu^{(i)}\right)}\left(
-                \left(\mu^{(i)}\right)^2 
-                - \left(\mu^{(i)}\right)^2\alpha_k 
-                - \left(L_k \mu^{(i)} \alpha_k - \left(\mu^{(i)}\right)^2 \alpha_k\right)
-            \right)
-            \\
-            &= 
-            \frac{1 - \alpha_k}{2(L_k - \mu)}\left(
-                \left(\mu^{(i)}\right)^2 - L_k\left(\mu^{(i)}\right)\alpha_k
-            \right)
-            \\
-            &= 
-            \frac{(1 - \alpha_k)\mu^{(i)}\left(\mu^{(i)} - L_k\alpha_k\right)}
-            {2\left(L_k - \mu^{(i)}\right)}
-            \\
-            &= \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
-            {2\left(L_k - \mu^{(i)}\right)}. 
+                \left(\sigma^{(i)}\right)^2(1 - \alpha_k)^2
+                - \left(L_k - \sigma^{(i)}\right)\sigma^{(i)} \alpha_k(1 - \alpha_k)
+            \right)
+            \\
+            &= \frac{1 - \alpha_k}{2\left(L_k - \sigma^{(i)}\right)}\left(
+                \left(\sigma^{(i)}\right)^2 
+                - \left(\sigma^{(i)}\right)^2\alpha_k 
+                - \left(L_k \sigma^{(i)} \alpha_k - \left(\sigma^{(i)}\right)^2 \alpha_k\right)
+            \right)
+            \\
+            &= 
+            \frac{1 - \alpha_k}{2(L_k - \sigma)}\left(
+                \left(\sigma^{(i)}\right)^2 - L_k\left(\sigma^{(i)}\right)\alpha_k
+            \right)
+            \\
+            &= 
+            \frac{(1 - \alpha_k)\sigma^{(i)}\left(\sigma^{(i)} - L_k\alpha_k\right)}
+            {2\left(L_k - \sigma^{(i)}\right)}
+            \\
+            &= \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}
+            {2\left(L_k - \sigma^{(i)}\right)}. 
         \end{align*}
@@
             &\frac{\left(
-                L_k\alpha_k - \mu^{(i)}
-            \right)^2}{2(L_k - \mu^{(i)})} 
+                L_k\alpha_k - \sigma^{(i)}
+            \right)^2}{2(L_k - \sigma^{(i)})} 
             -
@@
             \frac{\left(
-                L_k\alpha_k - \mu^{(i)}
-            \right)^2}{2(L_k - \mu^{(i)})} 
+                L_k\alpha_k - \sigma^{(i)}
+            \right)^2}{2(L_k - \sigma^{(i)})} 
             -
-            \frac{L_k\alpha_k(\alpha_k - \tilde \mu/L_k)}{2} 
+            \frac{L_k\alpha_k(\alpha_k - \tilde \sigma/L_k)}{2} 
             \\
@@
             \frac{\left(
-                L_k\alpha_k - \mu^{(i)}
-            \right)^2}{2(L_k - \mu^{(i)})} 
-            - \frac{L_k\alpha_k(\alpha_k - \mu^{(i)}/L_k)}{2}
-            + \frac{L_k\alpha_k(\alpha_k - \mu^{(i)}/L_k)}{2} 
-            - \frac{L_k\alpha_k(\alpha_k - \tilde \mu/L_k)}{2} 
+                L_k\alpha_k - \sigma^{(i)}
+            \right)^2}{2(L_k - \sigma^{(i)})} 
+            - \frac{L_k\alpha_k(\alpha_k - \sigma^{(i)}/L_k)}{2}
+            + \frac{L_k\alpha_k(\alpha_k - \sigma^{(i)}/L_k)}{2} 
+            - \frac{L_k\alpha_k(\alpha_k - \tilde \sigma/L_k)}{2} 
             \\
@@
             \frac{\left(
-                L_k\alpha_k - \mu^{(i)}
-            \right)^2}{2(L_k - \mu^{(i)})} 
-            - \frac{\alpha_k\left(L_k\alpha_k - \mu^{(i)}\right)}{2}
+                L_k\alpha_k - \sigma^{(i)}
+            \right)^2}{2(L_k - \sigma^{(i)})} 
+            - \frac{\alpha_k\left(L_k\alpha_k - \sigma^{(i)}\right)}{2}
             + \frac{L_k\alpha_k}{2}
             \frac{\left(
-                \tilde \mu - \mu^{(i)}
+                \tilde \sigma - \sigma^{(i)}
             \right)}{L_k}
@@
             &=
-            \frac{L_k \alpha_k - \mu^{(i)}}{2(L_k - \mu^{(i)})}\left(
-                L_k \alpha_k - \mu^{(i)} 
-                - \left(L_k - \mu^{(i)}\right)\alpha_k
-            \right)
-            + \frac{\alpha_k(\tilde \mu - \mu^{(i)})}{2}
-            \\
-            &= \frac{L_k \alpha_k - \mu^{(i)}}{2(L_k - \mu^{(i)})}\left(
-                \mu^{(i)}\alpha_k - \mu^{(i)} 
-            \right)
-            + \frac{\alpha_k(\tilde \mu - \mu^{(i)})}{2}
+            \frac{L_k \alpha_k - \sigma^{(i)}}{2(L_k - \sigma^{(i)})}\left(
+                L_k \alpha_k - \sigma^{(i)} 
+                - \left(L_k - \sigma^{(i)}\right)\alpha_k
+            \right)
+            + \frac{\alpha_k(\tilde \sigma - \sigma^{(i)})}{2}
+            \\
+            &= \frac{L_k \alpha_k - \sigma^{(i)}}{2(L_k - \sigma^{(i)})}\left(
+                \sigma^{(i)}\alpha_k - \sigma^{(i)} 
+            \right)
+            + \frac{\alpha_k(\tilde \sigma - \sigma^{(i)})}{2}
             \\
@@
             \frac{
-                \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
+                \left(L_k \alpha_k - \sigma^{(i)}\right)\sigma^{(i)}
                 \left(\alpha_k - 1\right)
             }
-            {2(L_k - \mu^{(i)})}
-            + \frac{\alpha_k(\tilde \mu - \mu^{(i)})}{2}. 
+            {2(L_k - \sigma^{(i)})}
+            + \frac{\alpha_k(\tilde \sigma - \sigma^{(i)})}{2}. 
         \end{align*}   
@@
     \end{proof}
+    % The following lemma state the relationships of the iterates generated by SNAPG-V2. 
+    % They are needed for the convergence proof. 
+    % % --------------------------------------------------------------------------------------------------------------
+    % \begin{lemma}[properties of the iterates \textcolor{red}{DEPRECATED}]\label{lemma:snapg2-itrs-props}
+    %     Suppose that the iterates $(z_k, x_k, y_k)_{k \ge 0}$ and sequence $(\alpha_k)_{k \ge 1}$ are produced by an algorithm satisfying Definition \ref{def:snapg-v2}. 
+    %     Let $\bar x \in \RR^n$.
+    %     Define the sequence $z_k = \alpha_k\bar x + (1 - \alpha_k)x_{k - 1}$. 
+    %     Then, the following are true: 
+    %     \begin{enumerate}
+    %         \item\label{lemma:snapg2-itrs-props-item1} For all $k \ge 1$ it has: 
+    %         \begin{align*}
+    %                 z_k - y_k 
+    %                 = 
+    %                 \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+    %                 + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
+    %         \end{align*}
+    %         \item\label{lemma:snapg2-itrs-props-item2} For all $k \ge 1$, it has: $z_k - x_k = \alpha_k(x - \bar x)$
+    %     \end{enumerate}
+    % \end{lemma}
+    % \begin{proof}
+    %     \textbf{Proof of \ref{lemma:snapg2-itrs-props-item1}}. 
+    %     From Definition \ref{def:snapg-v2}, it has
+    %     \begin{align*}
+    %         (1 + \tau_k)^{-1}
+    %         &=
+    %         \left(
+    %             1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
+    %         \right)^{-1} = \left(
+    %             \frac{L_k\alpha_k - \mu^{(i)} + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
+    %         \right)^{-1}
+    %         = \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}. 
+    %     \end{align*}
+    %     Therefore, for all $k \ge 0$, $y_k$ has 
+    %     \begin{align*}
+    %         0 &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1} - y_k
+    %         \\
+    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} 
+    %         \left(
+    %             v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}} x_{k - 1}
+    %         \right) - y_k
+    %         \\
+    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1}
+    %         + \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1} - y_k
+    %         \\
+    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+    %         + 
+    %         \left(
+    %             \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} - (1 - \alpha_k)
+    %         \right) x_{k - 1} - y_k
+    %         \\
+    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+    %         + 
+    %         (1 - \alpha_k)\left(
+    %             \frac{L_k - L_k + \mu^{(i)}}{L_k - \mu^{(i)}}
+    %         \right) x_{k - 1} - y_k
+    %         \\
+    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+    %         + 
+    %         \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}x_{k - 1} - y_k. 
+    %     \end{align*}
+    %     Therefore, we establish the equality 
+    %     \begin{align*}
+    %         (1 - \alpha_k)x_{k - 1} - y_k &= 
+    %         - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
+    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}. 
+    %     \end{align*}
+    %     On the second equality below, we will the above equality, it goes: 
+    %     \begin{align*}
+    %         z_k - y_k &= 
+    %         \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
+    %         \\
+    %         &= \alpha_k \bar x 
+    %         - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
+    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
+    %         \\
+    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+    %         + \left(
+    %             \alpha_k - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}
+    %         \right)\bar x
+    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
+    %         \\
+    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+    %         + \left(
+    %             \frac{\alpha_kL_k - \alpha_k \mu^{(i)} - L_k\alpha_k + \mu^{(i)}}{L_k - \mu^{(i)}}
+    %         \right)\bar x
+    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
+    %         \\
+    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+    %         + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}\bar x
+    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
+    %         \\
+    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+    %         + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
+    %     \end{align*}
+    %     \textbf{proof of \ref{lemma:snapg2-itrs-props-item2}.}
+    %     From Definition \ref{def:snapg-v2} it has directly: 
+    %     \begin{align*}
+    %         z_k - x_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
+    %         \\
+    %         &= \alpha_k \bar x + x_{k - 1} - x_k - \alpha_k x_{k - 1}
+    %         \\
+    %         &= \alpha_k(\bar x - \alpha_k^{-1}(x_k - x_{k - 1}) - x_{k - 1})
+    %         \\
+    %         &= \alpha_k (\bar x - v_k).
+    %     \end{align*}
+
+    % \end{proof}
+    % % --------------------------------------------------------------------------------------------------------------
+    % \begin{theorem}[SNAPG-V2 one step convergence \textcolor{red}{DEPRECATED}]\label{thm:snapg2-one-step}
+    %     Let $F$ satisfies assumption \ref{ass:interp-hypothesis}. 
+    %     Suppose that an algorithm satisfying Definition \ref{def:snapg-v2} uses this $F$. 
+    %     Let $\mathbb E_k$ denotes the expectation conditioned on $I_0, I_1, \ldots, I_{k - 1}$. 
+    %     Then, for all $k \ge 1$, it has the following inequality 
+    %     \begin{align*}
+    %         & \mathbb E_k\left[F_{I_k}(x_{k})\right] 
+    %         - F(\bar x) 
+    %         + \mathbb E_k\left[
+    %             \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+    %         \right]
+    %         \\
+    %         &\le 
+    %         (1 - \alpha_k)\left(
+    %                 \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
+    %                 - F(\bar x)
+    %                 + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
+    %         \right)
+    %             \\ &\quad 
+    %             + \mathbb E_k\left[
+    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
+    %             \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
+    %             + \frac{\alpha_k(\tilde\mu - \mu)}{2} 
+    %             \Vert \bar x - v_{k - 1}\Vert^2. 
+    %     \end{align*}
+    %     And for $k = 0$, it has 
+    %     \begin{align*}
+    %         \mathbb E \left[ F_{I_0}\right] - F(\bar x) 
+    %         + \frac{L_0}{2}\mathbb E \left[\Vert \bar x - x_0\Vert^2\right]
+    %         &\le 
+    %         \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
+    %     \end{align*}
+    % \end{theorem}
+    % \begin{proof}
+    %     Let's suppose that $I_k = i$ and, for all $k \ge 0$. 
+    %     Let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ where $\bar x$ is a minimizer of $F$. 
+    %     The proof is long so, we use letters and subscript under relations such as $\underset{(\cdot)}{=}, \underset{(\cdot)}{\ge}$ to indicate which result is used going from the previous expression to the next.
+    %     We list the following intermediate results, (d)-(g) are proved at the end of the proof. 
+    %     \begin{itemize}
+    %         \item[(a)] We can use proximal gradient inequality from Theorem \ref{thm:pg-ineq} with $z = z_k$ because each $F_i$ is $K_i$ Lipschitz smooth and, $\mu^{(i)}$ strongly convex with $K_i \ge \mu^{(i)}$.
+    %         \item[(b)] We can use Jensen's inequality of Theorem \ref{thm:jesen} with $z = z_k$ on $F_i$. 
+    %         \item[(c)] The sequence $(\alpha_k)_{k \ge 0}$ has $(L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right)$. 
+    %         \item[(d)] Prove in Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item1} we use the equality:
+    %         \begin{align*}
+    %             (\forall k \ge 1)\; 
+    %             z_k - y_k 
+    %             = 
+    %             \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+    %             + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
+    %         \end{align*}
+    %         \item [(e)] From Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item2}, we use: $(\forall k \ge 1)\; z_k - x_k = \alpha_k (\bar x - v_k)$. 
+    %         \item [(f)] Using direct algebra, we have for all $k \ge 1$: 
+    %         \begin{align*}
+    %             \frac{\left(\mu^{(i)}\right)^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} 
+    %             - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
+    %             = \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
+    %             {2\left(L_k - \mu^{(i)}\right)}. 
+    %         \end{align*}
+    %         \item [(g)] Using (c), we have for all $k \ge 1$: 
+    %         \begin{align*}
+    %             \frac{\left(
+    %                 L_k\alpha_k - \mu^{(i)}
+    %             \right)^2}{2(L_k - \mu^{(i)})} 
+    %             -
+    %             \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} 
+    %             = 
+    %             \frac{
+    %             \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
+    %             \left(\alpha_k - 1\right)
+    %             }
+    %             {2(L_k - \mu^{(i)})}
+    %             + \frac{\alpha_k(\tilde \mu_k - \mu^{(i)})}{2}. 
+    %         \end{align*}
+    %         \item[(h)] Because we assumed interpolation hypothesis in Assumption \ref{ass:interp-hypothesis}, it has $\mathbb E[F_{I_k}(\bar x)] = F(\bar x)$ for all $\bar x$ that is a minimizer of $F$.
+    %     \end{itemize}
+    %     For all $k \ge 1$, starting with (a) we have: 
+    %     \begin{align}\label{ineq:snapg2-one-step-chain1}
+    %         \begin{split}
+    %             0 &\le F_i(z_k) - F_i(x_k) - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2
+    %             \\
+    %             &\underset{\text{(b)}}{\le}
+    %             \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) \\
+    %                 &\quad 
+    %                 - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
+    %                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
+    %                 + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2. 
+    %         \end{split}
+    %     \end{align}
+    %     And we have the following chain of equalities:
+    %     {\allowdisplaybreaks
+    %     \begin{align*}
+    %         & - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
+    %         + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2
+    %         \\
+    %         &\underset{\text{(d)}}{=}
+    %         - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2 
+    %             \\&\quad
+    %             + \frac{L_k - \mu^{(i)}}{2}
+    %             \left\Vert
+    %                 \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
+    %                 + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1})
+    %             \right\Vert^2
+    %         \\
+    %         &= 
+    %         - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2 
+    %             \\&\quad
+    %             + \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2
+    %             + \frac{(\mu^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2 
+    %             \\&\quad 
+    %             + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+    %         \\
+    %         &= 
+    %         \left(
+    %             \frac{(\mu^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
+    %         \right)\Vert \bar x - x_{k - 1}\Vert^2
+    %             \\ &\quad 
+    %             + \left(
+    %                 \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
+    %             \right) \Vert \bar x - v_{k - 1}\Vert^2
+    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+    %             \\&\quad 
+    %             + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+    %         \\
+    %         &\underset{\text{(f)}}{=}
+    %         \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
+    %         {2\left(L_k - \mu^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2
+    %             \\ &\quad 
+    %             + \left(
+    %                 \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
+    %             \right) \Vert \bar x - v_{k - 1}\Vert^2
+    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+    %             \\&\quad 
+    %             + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+    %         \\
+    %         & \underset{\text{(g)}}{=} 
+    %         \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
+    %         {2\left(L_k - \mu^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2
+    %             \\ &\quad 
+    %             + \left(
+    %                 \frac{
+    %                     \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
+    %                     \left(\alpha_k - 1\right)
+    %                 }
+    %                 {2(L_k - \mu^{(i)})}
+    %                 + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}
+    %             \right) 
+    %             \Vert \bar x - v_{k - 1}\Vert^2
+    %             \\ &\quad 
+    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+    %             + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+    %         \\
+    %         &= 
+    %         \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\left(
+    %             \Vert \bar x - x_{k - 1}\Vert^2 + \Vert \bar x - v_{k - 1}\Vert^2 - 2\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+    %         \right) 
+    %             \\ &\quad 
+    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+    %         \\
+    %         &= \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
+    %             \Vert x_{k - 1} - v_{k - 1} \Vert^2
+    %             \\ &\quad 
+    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2.
+    %     \end{align*}
+    %     }
+    %     Substituting the above back to the tail of Inequality \eqref{ineq:snapg2-one-step-chain1} it gives: 
+    %     {\allowdisplaybreaks
+    %     \begin{align*}
+    %         0 &\le 
+    %         \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) 
+    %             \\&\quad 
+    %             - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
+    %             + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
+    %             \Vert x_{k - 1} - v_{k - 1} \Vert^2
+    %             \\ &\quad 
+    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+    %         \\
+    %         &\underset{\text{(e)}}{=} 
+    %         \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) 
+    %             \\&\quad 
+    %             - \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+    %             + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
+    %             \Vert x_{k - 1} - v_{k - 1} \Vert^2
+    %             \\ &\quad 
+    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+    %         \\
+    %         &= (\alpha_k - 1)F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) + F_i(\bar x)
+    %             \\&\quad 
+    %             - \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+    %             + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
+    %             \\ &\quad 
+    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
+    %         \\
+    %         &= (1 - \alpha_k)\left(
+    %             F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
+    %         \right) 
+    %             \\ & \quad
+    %             - \left(
+    %                 F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+    %             \right)
+    %             \\ &\quad 
+    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
+    %             + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
+    %     \end{align*}
+    %     }
+    %     Recall that $i = I_k$ is the random variable from Definition \ref{def:snapg-v2}. 
+    %     Rearranging the last expression in the above equality chain can be conveniently written as
+    %     \begin{align}
+    %         \begin{split}
+    %             & F_{I_k}(x_{k}) - F_{I_k}(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+    %             \\ &\le 
+    %             (1 - \alpha_k)\left(
+    %                 F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
+    %             \right) 
+    %                 \\ &\quad 
+    %                 + \frac{\alpha_k(\tilde \mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+    %                 + \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
+    %         \end{split}
+    %     \label{ineq:snapg2-one-step-presult1}\end{align}
+    %     Recall $\mathbb E_k$ denotes the conditional expectation on $I_0, I_1, \ldots, I_{k - 1}$. 
+    %     Taking the conditional expectation on the LHS of the \eqref{ineq:snapg2-one-step-presult1} yields: 
+    %     \begin{align*}
+    %         & \mathbb E_k\left[
+    %             F_{I_k}(x_{k}) - F_{I_k}(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+    %         \right]
+    %         \\
+    %         &\underset{\text{(h)}}{=}
+    %         \mathbb E_k\left[F_{I_k}(x_{k})\right] 
+    %         - F(\bar x) 
+    %         + \mathbb E_k\left[
+    %             \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+    %         \right]. 
+    %     \end{align*}
+    %     On the RHS of \eqref{ineq:snapg2-one-step-presult1}, using the linearity property while taking the conditional expectation yields: 
+    %     {\allowdisplaybreaks
+    %     \begin{align*}
+    %         & \mathbb E_k\left[
+    %             (1 - \alpha_k)\left(
+    %                 F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
+    %             \right)
+    %         \right]
+    %             \\ &\quad 
+    %             + \mathbb E_k \left[
+    %                 \frac{\alpha_k(\tilde\mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+    %             \right]
+    %             + \mathbb E_k\left[
+    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
+    %             \right]
+    %         \\
+    %         &\underset{\text{(1)}}{=} 
+    %         (1 - \alpha_k)\left(
+    %                 \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
+    %                 -\mathbb E_k [F_{I_k}(\bar x)] 
+    %                 + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
+    %         \right)
+    %             \\ &\quad 
+    %             + \mathbb E_k \left[
+    %                 \frac{\alpha_k(\tilde\mu - \mu^{(I_k)})}{2} 
+    %             \right]\Vert \bar x - v_{k - 1}\Vert^2
+    %             + \mathbb E_k\left[
+    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
+    %             \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
+    %         \\
+    %         &\underset{\text{(h)}}{=} 
+    %         (1 - \alpha_k)\left(
+    %                 \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
+    %                 - F(\bar x)
+    %                 + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
+    %         \right)
+    %             \\ &\quad 
+    %             + \mathbb E_k \left[
+    %                 \frac{\alpha_k(\tilde\mu - \mu^{(I_k)})}{2} 
+    %             \right]\Vert \bar x - v_{k - 1}\Vert^2
+    %             + \mathbb E_k\left[
+    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
+    %             \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
+    %         \\
+    %         &\underset{\text{(2)}}{=}
+    %         (1 - \alpha_k)\left(
+    %                 \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
+    %                 - F(\bar x)
+    %                 + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
+    %         \right)
+    %             \\ &\quad 
+    %             \frac{\alpha_k(\tilde\mu - \mu)}{2} 
+    %             \Vert \bar x - v_{k - 1}\Vert^2
+    %             + \mathbb E_k\left[
+    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
+    %             \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
+    %     \end{align*}
+    %     }
+    %     We note that at label (1), we used the fact that $\alpha_k$ is a constant and, $x_{k - 1}, v_{k - 1}$ only depends on random variable $I_0, I_1, \ldots, I_{k - 1}$ hence it falls out of the conditional expectation $\mathbb E_k$.
+    %     At label (2), we used assumption (Assumption \ref{ass:sum-of-many}) that the averages of all the $\mu^{(I_k)}$ on each $F_{I_k}$ equals to $\mu$ hence, the expectation evaluates to zero by linearity of the expected value operator.
+    %     \par
+    %     Combining the above results on the expectation of RHS, and LHS of \eqref{ineq:snapg2-one-step-presult1}, we have the one-step inequality in expectation: 
+    %     \begin{align*}
+    %         & \mathbb E_k\left[F_{I_k}(x_{k})\right] 
+    %         - F(\bar x) 
+    %         + \mathbb E_k\left[
+    %             \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+    %         \right]
+    %         \\
+    %         &\le 
+    %         (1 - \alpha_k)\left(
+    %                 \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
+    %                 - F(\bar x)
+    %                 + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
+    %         \right)
+    %             \\ &\quad 
+    %             + \mathbb E_k\left[
+    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
+    %             \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
+    %     \end{align*}
+    %     Finally, we show the base case. 
+    %     When $k = 0$, by assumption it had $\alpha_0 = 1$ hence $\tau_0$ in Definition \ref{def:snapg-v2} has $\tau_0 = 0$ which makes $y_0 = v_{- 1} = x_{-1}$. 
+    %     Therefore, it makes $x_0 = T_{L_0}(y_0 | F_{I_0}) = T_{L_0}(v_{-1} | F_{I_0})$. 
+    %     Similarly, it has also $z_0 = \bar x$.
+    %     Applying Theorem \ref{thm:pg-ineq} with $z = z_0$ and, assume a successful line search with $L_0$, it yields: 
+    %     \begin{align*}
+    %         0 &\le F_{I_0}(z_0) - F_{I_0}(x_0) - \frac{L_0}{2}\Vert z_0 - x_0\Vert^2 + \frac{L_0 - \mu^{(I_0)}}{2}\Vert z_0 - y_0\Vert^2
+    %         \\
+    %         &= F_{I_0}(\bar x) - F_{I_0}(x_0) - \frac{L_0}{2}\Vert \bar x - x_0\Vert^2 + \frac{L_0 - \mu^{(I_0)}}{2}\Vert \bar x - v_{-1}\Vert^2. 
+    %     \end{align*}
+    %     Re-arranging and taking the expectation it yields: 
+    %     \begin{align*}
+    %         \mathbb E \left[
+    %             F_{I_0}(x_0) - F_{I_0}(\bar x) + \frac{L_0}{2}\Vert \bar x - x_0\Vert^2
+    %         \right]
+    %         &\underset{\text{(h)}}{=}
+    %         \mathbb E \left[ F_{I_0}\right] - F(\bar x) 
+    %         + \frac{L_0}{2}\mathbb E \left[\Vert \bar x - x_0\Vert^2\right]
+    %         \\
+    %         &\le \frac{L_0 - \mathbb E \left[\mu^{(I_0)}\right]}{2}\Vert \bar x - v_{-1}\Vert^2
+    %         \\
+    %         &= \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
+    %     \end{align*}
+    %     % INTERMEDIATE RESULTS
+    %     \textbf{Proof of (f)}. 
+    %     The proof is direct algebra and, it has: 
+    %     {\small\allowdisplaybreaks
+    %     \begin{align*}
+    %         & \frac{\left(\mu^{(i)}\right)^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} 
+    %         - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
+    %         \\
+    %         &= 
+    %         \frac{1}{2\left(L_k - \mu^{(i)}\right)}
+    %         \left(
+    %             \left(\mu^{(i)}\right)^2(1 - \alpha_k)^2
+    %             - \left(L_k - \mu^{(i)}\right)\mu^{(i)} \alpha_k(1 - \alpha_k)
+    %         \right)
+    %         \\
+    %         &= \frac{1 - \alpha_k}{2\left(L_k - \mu^{(i)}\right)}\left(
+    %             \left(\mu^{(i)}\right)^2 
+    %             - \left(\mu^{(i)}\right)^2\alpha_k 
+    %             - \left(L_k \mu^{(i)} \alpha_k - \left(\mu^{(i)}\right)^2 \alpha_k\right)
+    %         \right)
+    %         \\
+    %         &= 
+    %         \frac{1 - \alpha_k}{2(L_k - \mu)}\left(
+    %             \left(\mu^{(i)}\right)^2 - L_k\left(\mu^{(i)}\right)\alpha_k
+    %         \right)
+    %         \\
+    %         &= 
+    %         \frac{(1 - \alpha_k)\mu^{(i)}\left(\mu^{(i)} - L_k\alpha_k\right)}
+    %         {2\left(L_k - \mu^{(i)}\right)}
+    %         \\
+    %         &= \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
+    %         {2\left(L_k - \mu^{(i)}\right)}. 
+    %     \end{align*}
+    %     }    
+    %     % INTERMEDIATE RESULTS 
+    %     \textbf{Proof of (g)}.
+    %     From the property of the $\alpha_k$ sequence stated in item (c), we have: 
+    %     {\allowdisplaybreaks
+    %     \begin{align*}
+    %         &\frac{\left(
+    %             L_k\alpha_k - \mu^{(i)}
+    %         \right)^2}{2(L_k - \mu^{(i)})} 
+    %         -
+    %         \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} 
+    %         \\
+    %         &= 
+    %         \frac{\left(
+    %             L_k\alpha_k - \mu^{(i)}
+    %         \right)^2}{2(L_k - \mu^{(i)})} 
+    %         -
+    %         \frac{L_k\alpha_k(\alpha_k - \tilde \mu/L_k)}{2} 
+    %         \\
+    %         &=
+    %         \frac{\left(
+    %             L_k\alpha_k - \mu^{(i)}
+    %         \right)^2}{2(L_k - \mu^{(i)})} 
+    %         - \frac{L_k\alpha_k(\alpha_k - \mu^{(i)}/L_k)}{2}
+    %         + \frac{L_k\alpha_k(\alpha_k - \mu^{(i)}/L_k)}{2} 
+    %         - \frac{L_k\alpha_k(\alpha_k - \tilde \mu/L_k)}{2} 
+    %         \\
+    %         &= 
+    %         \frac{\left(
+    %             L_k\alpha_k - \mu^{(i)}
+    %         \right)^2}{2(L_k - \mu^{(i)})} 
+    %         - \frac{\alpha_k\left(L_k\alpha_k - \mu^{(i)}\right)}{2}
+    %         + \frac{L_k\alpha_k}{2}
+    %         \frac{\left(
+    %             \tilde \mu - \mu^{(i)}
+    %         \right)}{L_k}
+    %         \\
+    %         &=
+    %         \frac{L_k \alpha_k - \mu^{(i)}}{2(L_k - \mu^{(i)})}\left(
+    %             L_k \alpha_k - \mu^{(i)} 
+    %             - \left(L_k - \mu^{(i)}\right)\alpha_k
+    %         \right)
+    %         + \frac{\alpha_k(\tilde \mu - \mu^{(i)})}{2}
+    %         \\
+    %         &= \frac{L_k \alpha_k - \mu^{(i)}}{2(L_k - \mu^{(i)})}\left(
+    %             \mu^{(i)}\alpha_k - \mu^{(i)} 
+    %         \right)
+    %         + \frac{\alpha_k(\tilde \mu - \mu^{(i)})}{2}
+    %         \\
+    %         &= 
+    %         \frac{
+    %             \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
+    %             \left(\alpha_k - 1\right)
+    %         }
+    %         {2(L_k - \mu^{(i)})}
+    %         + \frac{\alpha_k(\tilde \mu - \mu^{(i)})}{2}. 
+    %     \end{align*}   
+    %     } 
+    % \end{proof}
 \section{Convergence rate of the algorithm under various circumstances}

### 2025-07-10 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
 \section{In preparations}
-    \textbf{Notations}. 
+    \textbf{Notations \textcolor{red}{NEW}}. 
+    Unless specifically specified in the context, we use the following notations. 
+    $\Pi_C$ denotes the projection onto a set $C$. 
+    Let $A \in \RR^{m \times n}$ be a matrix. 
+    $\sigma_{\min}(A)$ denotes the smallest non-zero absolute value of all singular values of $A$. 
+    Let $\Vert A\Vert$ denotes the spectral norm of the matrix $A$. 
+    $I$ denotes the identity operator. 
     \subsection{Basic definitions}
@@
         \begin{definition}[semi strongly convex function \textcolor{red}{NEW}]\label{def:semi-scnvx}
-            A function $F: \RR^n \rightarrow \overline \RR$ is a semi strongly convex function, abbreviated as ``Semi-SCNVX'' with respective to a linear mapping $A \in \RR^{m \times n}$ if $F - \frac{1}{2}\Vert Ax\Vert^2$ is a convex function.
+            A function $F: \RR^n \rightarrow \overline \RR$ is a semi strongly convex function, abbreviated as ``Semi-SCNVX'' with respect to a linear mapping $A \in \RR^{m \times n}$ if $F - \frac{1}{2}\Vert Ax\Vert^2$ is a convex function.
         \end{definition}
@@
             \end{align*}
-            Then, we call this function is semi-relative smooth with respect to $A_1$, and semi convex to $A_2$
+            Then, we call this function is $A_1, A_2$ Semi-SCNVX and smooth. 
         \end{definition}
@@
             Obviously, it has $\Vert A_1x\Vert \le \Vert A_2x\Vert$ for all $x\in \RR^m$, which further implies that $\ker A_1\supseteq\ker A_2$.
+            With some algebra it can be showned that $A^T_2A_2 \succeq A^T_1A_1$. 
         \end{remark}
@@
         % --------------------------------------------------------------------------------------------------------------
-        \begin{theorem}[affine composite smooth and strongly convex]\label{thm:aff-smooth-sq-scnvx}
+        \begin{theorem}[affine composite with smooth and strongly convex]\label{thm:aff-smooth-sq-scnvx}
             Let $f: \RR^n \rightarrow \RR$ be an $L$ smooth and, $\mu \ge 0$ strongly convex.
             Let $A: \RR^m \rightarrow \RR^n$, $b \in \RR^n$ be arbitrary and, define $h: \RR^m \rightarrow \RR= x \mapsto f(Ax - b)$. 
-            Ddenote $\Pi = \Pi_{\ker A}$ to be the projection operator onto the kernel of $A$, denote $\Vert A\Vert$ to be the operator norm of the matrix, and $\sigma_{\min}(A)$ to be the smallest non-zero eigenvalues of $A$ in absolute value.
+            Denote $\Pi = \Pi_{\ker A}$ to be the projection operator onto the kernel of $A$. 
             Then, it satisfies for all $x \in \RR^m, y \in \RR^m$:  
@@
                 \frac{\mu}{2}\Vert A(x - y)\Vert^2 &= 
-                \frac{\mu}{2}\Vert A(\Pi(x - y) + (1 - \Pi)(x - y))\Vert^2
-                \\
-                &= 
-                \frac{\mu}{2}\Vert A(1 - \Pi)(x - y))\Vert^2
-                \\
-                &\ge \frac{\mu\sigma_{\min}(A)}{2}\Vert (1 - \Pi)(x - y)\Vert^2. 
-            \end{align*}
-            These results makes for the final inequalities: 
+                \frac{\mu}{2}\Vert A(\Pi(x - y) + (I - \Pi)(x - y))\Vert^2
+                \\
+                &= 
+                \frac{\mu}{2}\Vert A(I - \Pi)(x - y))\Vert^2
+                \\
+                &\ge \frac{\mu\sigma_{\min}(A)}{2}\Vert (I - \Pi)(x - y)\Vert^2. 
+            \end{align*}
+            These results Make for the final inequalities: 
             \begin{align*}
@@
                 For any $x \in \RR^n$, let $x^+ = T_B(x | F)$. 
-                Let $\sigma_{\min}(A)$ denotes the minimum non-zero singular value of $A$ in absolute value. 
                 Let $\Pi = \Pi_{\ker A}$ be the linear operator that project onto the kernel of $A$. 
-                Then, there exists some $B \ge 0$ such that $D_f(x^+, x) \le \frac{B}{2}\Vert x - x^+\Vert^2$ and, for all $z \in \RR^m$ it satisfies the inequality: 
+                Then, there exists some $B \ge 0$ such that $D_f(x^+, x) \le \frac{B}{2}\Vert x - x^+\Vert^2$ and, for all $z \in \RR^m$ it satisfies the inequalities: 
                 \begin{align*}
@@
             \begin{proof}
-                Firstly, such a $B > 0$ exists, for example $B = L\Vert A\Vert^2$ would be an option because from Definition \ref{def:seminorm-smooth-scnvx}, it for all $x, y$, $D_f(x, y) \le L/2\Vert Ax - Ay \Vert^2 \le L/2\Vert A\Vert^2\Vert x - y\Vert^2$.
+                Firstly, such a $B > 0$ exists, for example $B = L\Vert A\Vert^2$ would be an option because from Definition \ref{def:seminorm-smooth-scnvx}, it for all $x, y \ in \RR^{m}$, $D_f(x, y) \le L/2\Vert Ax - Ay \Vert^2 \le L/2\Vert A\Vert^2\Vert x - y\Vert^2$.
                 But it can be much smaller. 
@@
         Take note that the function $f(x) = \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)})$ is the composition of the strongly convex function $h = \frac{1}{n}\sum_{i = 1}^{n} h_i$ that is a $\RR^{mn}\rightarrow \RR$ mapping with strong convexity $\frac{1}{n}\sum_{i = 1}^{n} \nu^{(i)}$ and, the affine $\RR^m \rightarrow \RR^{mn}$ mapping $\mathcal A := x \mapsto (A^{(1)}x - b^{(1)},\ldots,  A^{(n)}x - b^{(n)})$.
-        $f$ satisifes Theorem \ref{thm:aff-smooth-sq-scnvx} and it can be written as: 
+        $f$ satisfies Theorem \ref{thm:aff-smooth-sq-scnvx} and it can be written as: 
         \begin{align*}
@@
     \begin{proof}
-        \textbf{Proof of \ref{lemma:snapg2-itrs-props-item1}}. 
+        \textbf{Proof of \ref{lemma:iters-snapg2-proto-item1}}. 
         From Definition \ref{def:snapg-v2-proto}:
@@
         \end{align*}
-        \textbf{proof of \ref{lemma:snapg2-itrs-props-item2}.}
+        \textbf{proof of \ref{lemma:iters-snapg2-proto-item2}.}
         From Definition \ref{def:snapg-v2} it has directly: 
@@
     % --------------------------------------------------------------------------------------------------------------
-    \begin{lemma}[SNAPG-V2 one step convergence stage I \textcolor{red}{NEW}]\label{lemma:snagp2-one-step-s1-proto}
-        Suppose that the sequence $(y_k, x_k, v_k)$ satisfies Definition \ref{def:snapg-v2-aff}. 
-        Fix some $k \in \N, k \ge 1$, suppose that $I_k = i$.
+    \begin{lemma}[SNAPG-V2 one step convergence stage I \textcolor{red}{NEW}]\;\label{lemma:snagp2-one-step-s1}\\
+        Let the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfies Definition \ref{def:snapg-v2-aff}. 
+        Fix any $k \in \N \cup\{0\}$, suppose that $I_k = i \in \{1, \ldots, n\}$.
         Denote $\Pi^{(i)} = \Pi_{\ker A^{(i)}}$ to be the projection matrix onto the kernel of $A^{(i)}$. 
-        Then for all $\bar x \in \RR^m$, the iterates satisfies the inequality: 
-        \begin{align*}
+        Then for all $\bar x \in \RR^m, k \ge 1$, the iterates satisfies the inequality: 
+        \begin{align}\label{ineq:snagp2-one-step-s1-rslt1}
+            \begin{split}
                 &F_i(x_{k}) - F_i(\bar x) 
@@
                     + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.
-        \end{align*}
+            \end{split}
+        \end{align}
         And when $k = 0$, we have: 
-        \todoinline{HERE}
+        \begin{align}\label{ineq:snagp2-one-step-s1-rslt2}
+            F(x_0) - F(\bar x) + \frac{L_0}{2}\Vert \bar x - v_{-1}\Vert^2 
+            &\le \frac{L_0}{2}\Vert \bar x - v_{-1}\Vert^2. 
+        \end{align}
     \end{lemma}
@@
         For all $k \ge 1$, starting with (a) we have: 
-        \begin{align}\label{ineq:snapg2-one-step-stage1-chain1}
+        \begin{align}\label{ineq:snapg2-one-step-s1-chain1}
             \begin{split}
@@
         \end{align}
-        \textbf{For simpler notations}, we use the following notation $\Vert x\Vert_p = \Vert (I - \Pi^{(i)})x\Vert$ to denote a seminorm induced by the linear mapping $(I - \Pi^{(i)})$, and use $\langle \cdot,\cdot\rangle_p := \langle (I - \Pi^{(i)})(\cdot), \langle (I - \Pi^{(i)})(\cdot)\rangle$ for the inner product as well.
+        \textbf{For simpler notations}, we use the following notation $\Vert x\Vert_{\bullet} = \Vert (I - \Pi^{(i)})x\Vert$ to denote a seminorm induced by the linear mapping $(I - \Pi^{(i)})$, and use $\langle \cdot,\cdot\rangle_\bullet := \langle (I - \Pi^{(i)})(\cdot), \langle (I - \Pi^{(i)})(\cdot)\rangle$ for the inner product as well.
         We also use $\sigma^{(i)} = \nu^{(i)}\sigma_{\min}(A^{(i)})^2$ which is specified in Definition \ref{def:snapg-v2-aff}. 
@@
         \begin{align*}
-            & - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_p
-            + \frac{L_k - \sigma^{(i)}}{2}\Vert z_k - y_k\Vert^2_p
+            & - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\bullet
+            + \frac{L_k - \sigma^{(i)}}{2}\Vert z_k - y_k\Vert^2_\bullet
             \\
             &\underset{\text{(d)}}{=}
-            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_p
+            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\bullet
                 \\&\quad
@@
                     + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}(\bar x - x_{k - 1})
-                \right\Vert^2_p
-            \\
-            &= 
-            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_p 
+                \right\Vert^2_\bullet
+            \\
+            &= 
+            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\bullet 
                 \\&\quad
-                + \frac{(L_k\alpha_k - \sigma^{(i)})^2}{2(L_k - \sigma^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2_p
-                + \frac{(\sigma^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \sigma^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2_p 
+                + \frac{(L_k\alpha_k - \sigma^{(i)})^2}{2(L_k - \sigma^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
+                + \frac{(\sigma^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \sigma^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2_\bullet 
                 \\&\quad 
-                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p
+                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\bullet
             \\
@@
                 \frac{(\sigma^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \sigma^{(i)})} - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}
-            \right)\Vert \bar x - x_{k - 1}\Vert^2_p
+            \right)\Vert \bar x - x_{k - 1}\Vert^2_\bullet
                 \\ &\quad 
@@
                     \frac{(L_k\alpha_k - \sigma^{(i)})^2}{2(L_k - \sigma^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
-                \right) \Vert \bar x - v_{k - 1}\Vert^2_p
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
+                \right) \Vert \bar x - v_{k - 1}\Vert^2_\bullet
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
                 \\&\quad 
-                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p
+                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\bullet
             \\
@@
             \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}
-            {2\left(L_k - \sigma^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2_p
+            {2\left(L_k - \sigma^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2_\bullet
                 \\ &\quad 
@@
             \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}
-            {2\left(L_k - \sigma^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2_p
+            {2\left(L_k - \sigma^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2_\bullet
                 \\ &\quad 
@@
                 \right) 
-                \Vert \bar x - v_{k - 1}\Vert^2_p
-                \\ &\quad 
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-                \\ &\quad
-                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p
+                \Vert \bar x - v_{k - 1}\Vert^2_\bullet
+                \\ &\quad 
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
+                \\ &\quad
+                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\bullet
             \\
@@
             \left(
-                \Vert \bar x - x_{k - 1}\Vert^2_p 
-                + \Vert \bar x - v_{k - 1}\Vert^2_p 
-                - 2\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p
-            \right) 
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
+                \Vert \bar x - x_{k - 1}\Vert^2_\bullet 
+                + \Vert \bar x - v_{k - 1}\Vert^2_\bullet 
+                - 2\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\bullet
+            \right) 
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
             \\
             &= \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}
-                \Vert x_{k - 1} - v_{k - 1} \Vert^2_p
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p.
+                \Vert x_{k - 1} - v_{k - 1} \Vert^2_\bullet
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet.
         \end{align*}
         }
-        Substituting the above back to the tail of Inequality \eqref{ineq:snapg2-one-step-stage1-chain1} it gives: 
+        Substituting the above back to the tail of Inequality \eqref{ineq:snapg2-one-step-s1-chain1} it gives: 
         {\allowdisplaybreaks
@@
                 \\ &\quad 
-                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_p
+                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_\bullet
                 + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
                 \\ &\quad 
-                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
+                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
             \\
@@
                 \\ &\quad 
-                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_p
+                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_\bullet
                 + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
                 \\ &\quad 
-                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
+                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
             \\
             &= (1 - \alpha_k)\left(
-                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2_p
+                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2_\bullet
             \right) 
@@
         \begin{align*}
-            &F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2_p 
+            &F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2_\bullet 
             \\
@@
             (1 - \alpha_k)\left(
-                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2_p
+                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2_\bullet
             \right)     
@@
         \end{align*}
-        For the first inequality, recall that $\Vert \cdot\Vert_p = \Vert (I - \Pi^{(i)})(\cdot)\Vert \le \Vert \cdot\Vert$ because $(I - \Pi^{(i)})$ is a projector and, it projects to $\ker A^{(i)}$.
-        Now, let's takle the $k = 0$ case. 
-        \todoinline{HERE}
+        For the first inequality, recall that $\Vert \cdot\Vert_\bullet = \Vert (I - \Pi^{(i)})(\cdot)\Vert \le \Vert \cdot\Vert$ because $(I - \Pi^{(i)})$ is a projector and, it projects to $\ker A^{(i)}$.
+        Now, let's tackle the $k = 0$ case. 
+        By Definition \ref{def:snapg-v2-aff} it has $\alpha_0 = 1$ and, $v_{- 1} = x_{- 1}$, so that makes $z_0 = \bar x$, and $\tau_0 = 0$ hence, $y_0 = v_{-1} = x_{-1}$. 
+        As a consequence it chooses $x_0 = T_{L_k}(y_0 | F_{I_0})$, it means that at the $k = 0$ iteration, the algorithm simplify performs one step of proximal gradient descent at $v_{-1}$ without any momentum.
+        So, we can use Theorem \ref{thm:pg-ineq-semi-scnvx} with $z = z_0 = \bar x, x^+ = x_0$ and, $B = L_0$: 
+        \begin{align*}
+            F(x_0) - F(\bar x) + \frac{L_0}{2}\Vert \bar x - v_{-1}\Vert^2 
+            &\le 
+            \frac{L_0 - \sigma^{(i)}}{2}\Vert \bar x - v_{-1} \Vert^2_\bullet
+            + \frac{B}{2}\left\Vert \Pi^{(i)}(\bar x - v_{-1})\right\Vert^2. 
+        \end{align*}
+        RHS can be simplified further
+        \begin{align*}
+            & \frac{L_0 - \sigma^{(i)}}{2}\Vert \bar x - v_{-1} \Vert^2_\bullet
+            + \frac{L_0}{2}\left\Vert \Pi^{(i)}(\bar x - v_{-1})\right\Vert^2
+            \\
+            &\le \frac{L_0}{2}\Vert \bar x - v_{-1} \Vert^2_\bullet
+            + \frac{L_0}{2}\left\Vert \Pi^{(i)}(\bar x - v_{-1})\right\Vert^2
+            \\
+            & = \frac{L_0}{2}\Vert \bar x - v_{-1}\Vert^2. 
+        \end{align*}
         % INTERMEDIATE RESULTS
@@
     \end{proof}
+    From the previous lemma, take note that it's for all $\bar x$. 
+    The next lemma discuss some special cases of the previous lemma where some terms of the inequality can be simplified away. 
+    \begin{lemma}[SNAPG-V2 one step convergence stage II \textcolor{red}{NEW}]\;\label{snapg2-one-step-s2-proto}\\
+        Let the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfies Definition \ref{def:snapg-v2-aff}. 
+        Fix any $k \in \N \cup\{0\}$, suppose that $I_k = i \in \{1, \ldots, n\}$.
+        Denote $\Pi^{(i)} = \Pi_{\ker A^{(i)}}$ to be the projection matrix onto the kernel of $A^{(i)}$. 
+        \begin{enumerate}[nosep]
+            \item If, each $A^{(i)} = I$, so $F$ satisfies Assumption \ref{ass:sum-of-many} with $\mu^{(i)} = \nu^{(i)}$, then for all $\bar x \in \RR^m$, $k \ge 1$ it satisfies the inequality: 
+            \begin{align}\begin{split}
+                &F_i(x_{k}) - F_i(\bar x) 
+                + \frac{L_k\alpha_k^2}{2} \left\Vert \bar x - v_k\right\Vert^2
+                \\
+                &\le 
+                (1 - \alpha_k)\left(
+                    F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}
+                    \left\Vert v_{k - 1} - \bar x\right\Vert^2
+                \right)     
+                    \\ &\quad 
+                    + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                    + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.
+            \end{split}\end{align}
+            \item If we choose $\bar x \in \Pi_{\ker A^{(i)}}(y_k)$, then for all $k \ge 1$ it has
+        \end{enumerate}
+    \end{lemma}
+    \begin{proof}
+
+    \end{proof}
+    The next lemma adds into the interpolation assumption and take conditional expectations on the inequality. 
     % The following lemma state the relationships of the iterates generated by SNAPG-V2. 

### 2025-07-11 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
     $I$ denotes the identity operator. 
+    When two expressions are connected via non-trivial results, it's expressed with $\underset{(\cdot)}{=}, \underset{(\cdot)}{\ge}$ where $(\cdot)$ is a label of some intermediate results immediately before it, or explained right after a chain of expressions.
     \subsection{Basic definitions}
@@
                     - \frac{B}{2}\Vert z - x^+\Vert^2
-                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x) \Vert^2
-                        \\ &\quad 
-                        + \frac{B}{2}\Vert \Pi(z - x)\Vert^2. 
+                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert z - x\Vert^2
+                    + \frac{\mu\sigma_{\min}(A)^2}{2}\Vert \Pi(z - x)\Vert^2. 
                 \end{align*}
@@
                     + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x)\Vert^2
-                    + \frac{B}{2}\Vert \Pi(z - x)\Vert^2. 
+                    + \frac{B}{2}\Vert \Pi(z - x)\Vert^2
+                    \\
+                    &= F(z) - F(x^+) 
+                    - \frac{B}{2}\Vert z - x^+\Vert^2
+                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x)\Vert^2
+                        \\&\quad
+                        + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert \Pi(z - x)\Vert^2
+                        + \frac{\sigma_{\min}(A)^2}{2}\Vert \Pi(z - x)\Vert^2
+                    \\
+                    &= F(z) - F(x^+) 
+                    - \frac{B}{2}\Vert z - x^+\Vert^2
+                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert z - x\Vert^2
+                    + \frac{\mu\sigma_{\min}(A)^2}{2}\Vert \Pi(z - x)\Vert^2.
                 \end{align*}
@@
             \item $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$, 
-            \item $\sigma^{(k)}$ be another list of i.i.d random variable. 
-            \item $\tilde \mu \ge 0$ be a constant that is fixed.
+            \item $\sigma^{(I_k)}$ be another list of i.i.d random variable, 
+            \item $\tilde \mu \ge 0$ be a constant that is fixed, 
             \item Let $(L_k)_{k \ge 0}$ a sequence of strictly positive numbers. 
@@
         Denote $\Pi^{(i)} = \Pi_{\ker A^{(i)}}$ to be the projection matrix onto the kernel of $A^{(i)}$. 
-        Then for all $\bar x \in \RR^m, k \ge 1$, the iterates satisfies the inequality: 
+        For all $\bar x \in \RR^m, k \ge 1$, define $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$. 
+        Then, the iterates satisfy: 
         \begin{align}\label{ineq:snagp2-one-step-s1-rslt1}
             \begin{split}
-                &F_i(x_{k}) - F_i(\bar x) 
-                + \frac{L_k\alpha_k^2}{2} \left\Vert \left(I - \Pi^{(i)}\right)(\bar x - v_k)\right\Vert^2
-                \\
-                &\le 
+                & F_i(x_k) - F_i(\bar x)
+                + \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2
+                \\&\le 
                 (1 - \alpha_k)\left(
-                    F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}
-                    \left\Vert \left(I - \Pi^{(i)}\right)(v_{k - 1} - \bar x)\right\Vert^2
-                \right)     
-                + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                    \\ &\quad 
-                    + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                    + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.
+                    F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                \right) + \mathcal R_k^{(i)}. 
             \end{split}
         \end{align}
+        Where: 
+        \begin{align*}
+            & \mathcal R_k^{(i)} = (1 - \alpha_k)\left(
+                \frac{\sigma^{(i)}\alpha_k}{2}\left\Vert \Pi^{(i)} (\bar x - x_{k - 1})\right\Vert^2
+                - \frac{\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
+            \right)
+                \\&\quad
+                + \frac{\sigma^{(i)}}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2. 
+        \end{align*}
         And when $k = 0$, we have: 
@@
     \begin{proof}
-        Let's suppose that $I_k = i$ and, for all $k \ge 0$. 
-        Let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ where $\bar x$ is a minimizer of $F$. 
-        The proof is long so, we use letters and subscript under relations such as $\underset{(\cdot)}{=}, \underset{(\cdot)}{\ge}$ to indicate which result is used going from the previous expression to the next.
         We list the following intermediate results, (d)-(g) are proved at the end of the proof. 
         \begin{itemize}
-            \item[(a)] We can use proximal gradient inequality from Theorem \ref{thm:pg-ineq-semi-scnvx} with $z = z_k, B = L_k, \Pi^{i} = \Pi_{\ker A^{(i)}}$ because Assumption \ref{ass:sum-of-many-aff-comp} has each $F_i = f_i + g_i$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth}.
+            \item[(a)] We can use proximal gradient inequality from Theorem \ref{thm:pg-ineq-semi-scnvx} with $z = z_k, B = L_k, \Pi^{(i)} = \Pi_{\ker A^{(i)}}$ because Assumption \ref{ass:sum-of-many-aff-comp} has each $F_i = f_i + g_i$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth}.
             \item[(b)] We can use seminorm Jensen's inequality of Theorem \ref{thm:smnrm-jnsn-smth-nsmth} with $z = z_k$ on $F_i$. 
@@
         \end{itemize}
+        \textbf{For simpler notations}
+        \begin{itemize}[nosep]
+            \item We use $\langle \cdot,\cdot\rangle_\sharp := \langle H(\cdot), H(\cdot)\rangle$ for any linear mapping $H$, and denote $\Vert x\Vert_{\sharp} = \sqrt{\langle x, x\rangle_\sharp}$. 
+            \item We denote specifically $\Vert \cdot\Vert_\bullet$ for the semi norm $\Vert (I - \Pi^{(i)})(\cdot)\Vert$, and $\Vert \cdot\Vert_{\circ}$ for the semi norm $\left\Vert \Pi^{(i)} x\right\Vert$.
+So it has $\Vert x\Vert^2_\circ + \Vert x\Vert^2_\bullet = \Vert x\Vert^2$.
+        \end{itemize}
         For all $k \ge 1$, starting with (a) we have: 
@@
             \begin{split}
-                0 &\le F_i(z_k) - F_i(x_k) - 
+                0 &\underset{\text{(a)}}{\le} F_i(z_k) - F_i(x_k) - 
                 \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-                + \frac{L_k - \nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\left\Vert (I - \Pi^{(i)}) (z_k - y_k)\right\Vert^2
-                    \\ &\quad 
-                    + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
+                + \frac{L_k - \nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\left\Vert z_k - y_k\right\Vert^2
+                    \\ &\quad 
+                    + \frac{\nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\left\Vert z_k - y_k\right\Vert^2_\circ
                 \\
@@
                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-                + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                    \\&\quad 
-                    - \frac{\nu^{(i)}\sigma_{\min}(A^{(i)})^2\alpha_k(1 - \alpha_k)}{2}\Vert (I - \Pi^{(i)})(\bar x - x_{k - 1})\Vert^2
-                    \\&\quad
-                    + \frac{L_k - \nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\Vert (I - \Pi^{(i)})(z_k - y_k)\Vert^2
+                + \frac{\nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\left\Vert z_k - y_k\right\Vert^2_\circ
+                    \\&\quad 
+                    - \frac{\nu^{(i)}\sigma_{\min}(A^{(i)})^2\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\bullet
+                    \\&\quad
+                    + \frac{L_k - \nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\Vert z_k - y_k\Vert^2
+                \\
+                & = 
+                \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k)     
+                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
+                + \frac{\nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\left\Vert z_k - y_k\right\Vert^2_\circ
+                    \\&\quad 
+                    + \frac{\nu^{(i)}\sigma_{\min}(A^{(i)})^2\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\circ
+                    \\&\quad
+                    + \frac{L_k - \nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\Vert z_k - y_k\Vert^2
+                    - \frac{\nu^{(i)}\sigma_{\min}(A^{(i)})^2\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
             \end{split}
         \end{align}
-        \textbf{For simpler notations}, we use the following notation $\Vert x\Vert_{\bullet} = \Vert (I - \Pi^{(i)})x\Vert$ to denote a seminorm induced by the linear mapping $(I - \Pi^{(i)})$, and use $\langle \cdot,\cdot\rangle_\bullet := \langle (I - \Pi^{(i)})(\cdot), \langle (I - \Pi^{(i)})(\cdot)\rangle$ for the inner product as well.
+
         We also use $\sigma^{(i)} = \nu^{(i)}\sigma_{\min}(A^{(i)})^2$ which is specified in Definition \ref{def:snapg-v2-aff}. 
@@
         \begin{align*}
-            & - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\bullet
-            + \frac{L_k - \sigma^{(i)}}{2}\Vert z_k - y_k\Vert^2_\bullet
+            & - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\sharp
+            + \frac{L_k - \sigma^{(i)}}{2}\Vert z_k - y_k\Vert^2_\sharp
             \\
             &\underset{\text{(d)}}{=}
-            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\bullet
+            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\sharp
                 \\&\quad
@@
                     + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}(\bar x - x_{k - 1})
-                \right\Vert^2_\bullet
-            \\
-            &= 
-            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\bullet 
-                \\&\quad
-                + \frac{(L_k\alpha_k - \sigma^{(i)})^2}{2(L_k - \sigma^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
-                + \frac{(\sigma^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \sigma^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2_\bullet 
-                \\&\quad 
-                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\bullet
+                \right\Vert^2_\sharp
+            \\
+            &= 
+            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\sharp 
+                \\&\quad
+                + \frac{(L_k\alpha_k - \sigma^{(i)})^2}{2(L_k - \sigma^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2_\sharp
+                + \frac{(\sigma^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \sigma^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2_\sharp 
+                \\&\quad 
+                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\sharp
             \\
@@
                 \frac{(\sigma^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \sigma^{(i)})} - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}
-            \right)\Vert \bar x - x_{k - 1}\Vert^2_\bullet
+            \right)\Vert \bar x - x_{k - 1}\Vert^2_\sharp
                 \\ &\quad 
@@
                     \frac{(L_k\alpha_k - \sigma^{(i)})^2}{2(L_k - \sigma^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
-                \right) \Vert \bar x - v_{k - 1}\Vert^2_\bullet
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
-                \\&\quad 
-                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\bullet
+                \right) \Vert \bar x - v_{k - 1}\Vert^2_\sharp
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\sharp
+                \\&\quad 
+                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\sharp
             \\
@@
             \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}
-            {2\left(L_k - \sigma^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2_\bullet
+            {2\left(L_k - \sigma^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2_\sharp
                 \\ &\quad 
@@
             \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}
-            {2\left(L_k - \sigma^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2_\bullet
+            {2\left(L_k - \sigma^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2_\sharp
                 \\ &\quad 
@@
                 \right) 
-                \Vert \bar x - v_{k - 1}\Vert^2_\bullet
-                \\ &\quad 
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
-                \\ &\quad
-                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\bullet
+                \Vert \bar x - v_{k - 1}\Vert^2_\sharp
+                \\ &\quad 
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\sharp
+                \\ &\quad
+                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\sharp
             \\
@@
             \left(
-                \Vert \bar x - x_{k - 1}\Vert^2_\bullet 
-                + \Vert \bar x - v_{k - 1}\Vert^2_\bullet 
-                - 2\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\bullet
-            \right) 
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
+                \Vert \bar x - x_{k - 1}\Vert^2_\sharp 
+                + \Vert \bar x - v_{k - 1}\Vert^2_\sharp 
+                - 2\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_\sharp
+            \right) 
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\sharp
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\sharp
             \\
             &= \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}
-                \Vert x_{k - 1} - v_{k - 1} \Vert^2_\bullet
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet.
+                \Vert x_{k - 1} - v_{k - 1} \Vert^2_\sharp
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\sharp
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\sharp.
         \end{align*}
         }
-        Substituting the above back to the tail of Inequality \eqref{ineq:snapg2-one-step-s1-chain1} it gives: 
+        So, this is our results: 
+        \begin{align}\begin{split}\label{eqn:snapg2-one-spte-s1-chain2}
+            & - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\sharp
+            + \frac{L_k - \sigma^{(i)}}{2}\Vert z_k - y_k\Vert^2_\sharp
+            \\
+            &= 
+            \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}
+                \Vert x_{k - 1} - v_{k - 1} \Vert^2_\sharp
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\sharp
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\sharp.
+        \end{split}\end{align}
+        Substituting the above back to the tail of \eqref{ineq:snapg2-one-step-s1-chain1} for $\Vert \cdot\Vert_\sharp = \Vert \cdot\Vert$ it has: 
         {\allowdisplaybreaks
@@
                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-                \\ &\quad 
-                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_\bullet
-                + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
+                + \frac{\sigma^{(i)}}{2}\left\Vert z_k - y_k\right\Vert^2_\circ
+                    \\&\quad 
+                    + \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\circ
+                    + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}
+                    \Vert x_{k - 1} - v_{k - 1} \Vert^2
+                    \\ &\quad 
+                    + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                    + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
             \\
@@
             - \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2 
-                \\ &\quad 
-                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_\bullet
-                + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
+            + \frac{\sigma^{(i)}}{2}\left\Vert z_k - y_k\right\Vert^2_\circ
+                \\&\quad 
+                + \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\circ
+                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}
+                \Vert x_{k - 1} - v_{k - 1} \Vert^2
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
             \\
@@
             - \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2 
-                \\ &\quad 
-                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_\bullet
-                + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_\bullet
+            + \frac{\sigma^{(i)}}{2}\left\Vert z_k - y_k\right\Vert^2_\circ
+                \\&\quad 
+                + \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_\circ
+                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
             \\
             &= (1 - \alpha_k)\left(
-                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2_\bullet
-            \right) 
-                \\ & \quad
+                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2} \Vert \bar x - v_{k - 1}\Vert^2
+            \right)
             - \left(
-                    F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-                \right) + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.
+                F_i(x_k) - F_i(\bar x)
+                + \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2 
+            \right)
+                \\&\quad 
+                + (1 - \alpha_k)\left(
+                    \frac{\sigma^{(i)}\alpha_k}{2}\Vert \bar x - x_{k - 1}\Vert^2_\circ
+                    - \frac{\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
+                \right)
+                \\&\quad
+                + \frac{\sigma^{(i)}}{2}\left\Vert z_k - y_k\right\Vert^2_\circ
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
         \end{align*}
         }
-        Re-arranging, with some linear algebra:  we get out first result: 
-        \begin{align*}
-            &F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2_\bullet 
-            \\
-            &\le 
-            F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-            \\
-            &\le 
+        Define
+        \begin{align*}
+            & \mathcal R_k^{(i)} := (1 - \alpha_k)\left(
+                \frac{\sigma^{(i)}\alpha_k}{2}\Vert \bar x - x_{k - 1}\Vert^2_\circ
+                - \frac{\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
+            \right)
+                \\&\quad
+                + \frac{\sigma^{(i)}}{2}\left\Vert z_k - y_k\right\Vert^2_\circ
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2. 
+        \end{align*}
+        Then the result can be written as: 
+        \begin{align*}
+            & F_i(x_k) - F_i(\bar x)
+                + \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2
+            \\&\le 
             (1 - \alpha_k)\left(
-                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2_\bullet
-            \right)     
-            + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.
-        \end{align*}
-        For the first inequality, recall that $\Vert \cdot\Vert_\bullet = \Vert (I - \Pi^{(i)})(\cdot)\Vert \le \Vert \cdot\Vert$ because $(I - \Pi^{(i)})$ is a projector and, it projects to $\ker A^{(i)}$.
+                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2} \Vert \bar x - v_{k - 1}\Vert^2
+            \right) + \mathcal R_k^{(i)}. 
+        \end{align*}
         Now, let's tackle the $k = 0$ case. 
@@
         Denote $\Pi^{(i)} = \Pi_{\ker A^{(i)}}$ to be the projection matrix onto the kernel of $A^{(i)}$. 
+        If at least one of the followings is true: 
         \begin{enumerate}[nosep]
-            \item If, each $A^{(i)} = I$, so $F$ satisfies Assumption \ref{ass:sum-of-many} with $\mu^{(i)} = \nu^{(i)}$, then for all $\bar x \in \RR^m$, $k \ge 1$ it satisfies the inequality: 
+            \item For all $i = 1, \ldots, n$ it has $A^{(i)} = I$, so $F$ satisfies Assumption \ref{ass:sum-of-many} with $\mu^{(i)} = \nu^{(i)}$, Let $\bar x \in \RR^m$ be arbitrary;
+            \item Assume $x_{k - 1}, v_{k - 1}$ are in $\left(\ker A^{(i)}\right)^\perp$, let $\bar x \in \left(\ker A^{(i)}\right)^{\perp}$ be arbitrary. 
+        \end{enumerate}
+        Then for all $k \ge 1$ it has: 
         \begin{align}\begin{split}
@@
                 \\ &\quad 
-                    + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                    + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.
+                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.
         \end{split}\end{align}
-            \item If we choose $\bar x \in \Pi_{\ker A^{(i)}}(y_k)$, then for all $k \ge 1$ it has
-        \end{enumerate}
+        And when $k = 0$, we have \eqref{ineq:snagp2-one-step-s1-rslt2} as well. 
     \end{lemma}
     \begin{proof}
-
+        Firstly take note that from Lemma \ref{lemma:snagp2-one-step-s1} using the fact that $\Pi^{(i)}$ is a projection matrix it has directly: 
+        \begin{align*}
+            & F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+            \\
+            &\le 
+            (1 - \alpha_k)\left(
+                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\left\Vert (I - \Pi^{(i)})( v_{k - 1} - \bar x)\right\Vert^2
+            \right)     
+            + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
+            \\
+            &\le 
+            (1 - \alpha_k)\left(
+                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\left\Vert v_{k - 1} - \bar x\right\Vert^2
+            \right)     
+            + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
+                \\ &\quad 
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
+        \end{align*}
+        Next, we will show that $\Pi^{(i)}(z_k - y_k)$ is zero under item (i), (ii). 
+        \par
+        Let's prove (i) first. 
+        Since $A^{(i)} = I$, its kernel is zero hence the $\Pi^{(i)}$ in Lemma \ref{lemma:snagp2-one-step-s1} projects to $\{0\}$ and the term $\Pi^{(i)}(z_k - y_k) = \mathbf 0$ in \eqref{ineq:snagp2-one-step-s1-rslt1}.
+It's done.
+        \par
+        To see (ii), recall that $z_k = \alpha_k \bar x + (1 - \alpha_k) x_{k - 1}$ from Lemma \ref{lemma:snagp2-one-step-s1}, obviously $z_k \perp \ker A^{(i)}$ as well. 
+        Recall that $y_k$ as defined in Definition \ref{def:snapg-v2-proto} has
+        \begin{align*}
+            y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}.
+        \end{align*}
+        So $y_k \perp \ker A^{(i)}$ because it's the linear combinations of $v_{k - 1}, x_{k - 1}$. 
+        Hence, the projection of $y_k, z_k$ onto $\ker A^{(i)}$ by $\Pi^{(i)}$ is zero, hence the results from Lemma \ref{lemma:snagp2-one-step-s1} simplifies as well. 
     \end{proof}

### 2025-07-15 Notebook LaTEX/SAGD Under Interpolation/main-2025-07-14.tex
;~;

--- 2025-07-11 Notebook LaTEX/SAGD Under Interpolation/main.tex
@@
 \newcommand{\var}{\ensuremath{\operatorname{Var}}}
+\newcommand{\expect}{\ensuremath{\mathbb E}}
 
@@
             If, $f$ is $\mu \ge 0$ strongly convex and $L$ Lipschitz smooth then, its Bregman Divergence has for all $x, y \in \RR^n$: $\mu/2 \Vert x - y\Vert^2 \le D_f(x, y) \le L/2 \Vert x - y\Vert^2$.
+            \textbf{NOTE}. Contrary to definitions of Bregman Divergence found in the literatures, \textbf{We do not assume} that $D_f(x, y) \iff x = y$. 
         \end{remark}
@@
             \item $F$ satisfies Assumption \ref{ass:sum-of-many}, 
+            \item Let $(L_k)_{k \ge 0}$ a sequence of strictly positive numbers, 
             \item $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$, 
-            \item $\sigma^{(I_k)}$ be another list of i.i.d random variable, 
-            \item $\tilde \mu \ge 0$ be a constant that is fixed, 
-            \item Let $(L_k)_{k \ge 0}$ a sequence of strictly positive numbers. 
+            \item $\sigma^{(I_k)} \le L_k$ be another list of i.i.d random variable, 
+            \item $\tilde \mu \ge 0$ be a constant that is fixed.
         \end{enumerate}
@@
         \begin{enumerate}[nosep]
-            \item $F$ also satisfies Assumption \ref{ass:sum-of-many-aff-comp} with $\RR^{m \times n}$ matrices: $A^{(1)}, A^{(2)}, \ldots, A^{(n)}$, vectors in $\RR^n$: $(b^{(1)}, \ldots, b^{(n)})$. 
+            \item $F$ also satisfies Assumption \ref{ass:sum-of-many-aff-comp} with $\RR^{m \times n}$ with matrices: $A^{(1)}, A^{(2)}, \ldots, A^{(n)}$, and vectors $b^{(1)}, \ldots, b^{(n)}$ in $\RR^n$.
             \item Choose $\sigma^{(k)} = \nu^{(I_k)}\sigma_{\min}(A^{(I_k)})^2$. 
         \end{enumerate}
-        Then, SNAPG-V2 affine specifies algorithms that generate the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfying conditions as specified in Definition \ref{def:snapg-v2-proto} with the above parameters.
+        Then, SNAPG-V2 affine specifies algorithms that generate the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfying conditions in Definition \ref{def:snapg-v2-aff} with the above parameters. 
     \end{definition}
@@
     \begin{definition}[SNAPG-V2 vanilla]\label{def:snapg-v2}
-        Let $F, (I_k)_{k \ge 0}, \tilde \mu$ and, $(L_k)_{k \ge 0}$ be given as in Definition \ref{def:snapg-v2-proto}. 
+        Let $F, (I_k)_{k \ge 0}, \tilde \mu$ and, $(L_k)_{k \ge 0}$ be given as in Definition \ref{def:snapg-v2-aff}. 
         But in addition, assume that: 
         \begin{enumerate}[nosep]
+            \item $F$ satisfies Assumption \ref{ass:sum-of-many}, which is equivalently to Assumption \ref{ass:sum-of-many-aff-comp} with $A^{(i)} = I$ and, $\nu^{(i)} = \mu^{(i)}$. 
             \item Choose $\sigma^{(k)} = \mu^{(I_k)}$. 
         \end{enumerate}
-        Then, SNAPG-V2 vanilla affine specifies algorithms that generate the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfying conditions as specified in Definition \ref{def:snapg-v2-proto} with the above parameters.
+        Then, SNAPG-V2 vanilla specifies algorithms that generate the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfying conditions in Definition \ref{def:snapg-v2-aff} with the above parameters. 
+    \end{definition}
+    % --------------------------------------------------------------------------------------------------------------
+    \begin{definition}[SNAPG-V2 classical]\label{def:snapg-v2-classical}
+        Let $F, (I_k)_{k \ge 0}, \tilde \mu$ and, $(L_k)_{k \ge 0}$ be given as in Definition \ref{def:snapg-v2-aff}. 
+        But in addition, assume that: 
+        \begin{enumerate}[nosep]
+            \item Choose $\sigma^{(k)} = 0$. 
+            \item Choose $\tilde \mu = 0$. 
+        \end{enumerate}
+        In this case the algorithm simplifies, it can be presented as: 
+        \begin{align*}
+            & \alpha_k \in (0, 1): (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - /L_k\right), \\
+            & y_k = \alpha_k v_{k - 1} + (1 - \alpha_k)x_{k - 1}, \\
+            & L_k > 0: D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
+            & x_k =  T_{L_k}(y_k | F_{I_k}), \\
+            & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
+        \end{align*}
+        Then, SNAPG-V2 classical specifies algorithms that generate the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfying conditions in Definition \ref{def:snapg-v2-aff} with the above parameters. 
     \end{definition}
@@
     % --------------------------------------------------------------------------------------------------------------
-    \begin{lemma}[SNAPG-V2 one step convergence stage I \textcolor{red}{NEW}]\;\label{lemma:snagp2-one-step-s1}\\
+    \begin{lemma}[SNAPG-V2 one step convergence stage I \textcolor{red}{NEW}]\;\label{lemma:snapg2-one-step-s1}\\
         Let the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfies Definition \ref{def:snapg-v2-aff}. 
@@
         Then, the iterates satisfy: 
-        \begin{align}\label{ineq:snagp2-one-step-s1-rslt1}
+        \begin{align}\label{ineq:snapg2-one-step-s1-rslt1}
             \begin{split}
@@
         And when $k = 0$, we have: 
-        \begin{align}\label{ineq:snagp2-one-step-s1-rslt2}
+        \begin{align}\label{ineq:snapg2-one-step-s1-rslt2}
             F(x_0) - F(\bar x) + \frac{L_0}{2}\Vert \bar x - v_{-1}\Vert^2 
@@
             \item For all $i = 1, \ldots, n$ it has $A^{(i)} = I$, so $F$ satisfies Assumption \ref{ass:sum-of-many} with $\mu^{(i)} = \nu^{(i)}$, Let $\bar x \in \RR^m$ be arbitrary;
-            \item Assume $x_{k - 1}, v_{k - 1}$ are in $\left(\ker A^{(i)}\right)^\perp$, let $\bar x \in \left(\ker A^{(i)}\right)^{\perp}$ be arbitrary. 
+            \item Assume $x_{k - 1}, v_{k - 1}$ produces the same projection point $\bar x$ onto $\ker A^{(i)}$, i.e: $\bar x = \Pi^{(i)} x_{k - 1} = \Pi^{(i)} v_{k - 1}$. 
         \end{enumerate}
@@
         \begin{align}\begin{split}
-            &F_i(x_{k}) - F_i(\bar x) 
-            + \frac{L_k\alpha_k^2}{2} \left\Vert \bar x - v_k\right\Vert^2
-            \\
-            &\le 
-            (1 - \alpha_k)\left(
-                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}
-                \left\Vert v_{k - 1} - \bar x\right\Vert^2
-            \right)     
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.
+            & \mathcal R_k^{(i)} = 
+            - \frac{(1 - \alpha_k)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
+            + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
         \end{split}\end{align}
-        And when $k = 0$, we have \eqref{ineq:snagp2-one-step-s1-rslt2} as well. 
+        And when $k = 0$, we have \eqref{ineq:snapg2-one-step-s1-rslt2} as well. 
     \end{lemma}
     \begin{proof}
-        Firstly take note that from Lemma \ref{lemma:snagp2-one-step-s1} using the fact that $\Pi^{(i)}$ is a projection matrix it has directly: 
-        \begin{align*}
-            & F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-            \\
-            &\le 
-            (1 - \alpha_k)\left(
-                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\left\Vert (I - \Pi^{(i)})( v_{k - 1} - \bar x)\right\Vert^2
-            \right)     
-            + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
-            \\
-            &\le 
-            (1 - \alpha_k)\left(
-                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\left\Vert v_{k - 1} - \bar x\right\Vert^2
-            \right)     
-            + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
-        \end{align*}
-        Next, we will show that $\Pi^{(i)}(z_k - y_k)$ is zero under item (i), (ii). 
+        Firstly take note that from Lemma \ref{lemma:snapg2-one-step-s1} using the fact that $\Pi^{(i)}$ is a projection matrix it has directly: 
+        \begin{align*}
+            & \mathcal R_k^{(i)} = (1 - \alpha_k)\left(
+                \frac{\sigma^{(i)}\alpha_k}{2}\left\Vert \Pi^{(i)} (\bar x - x_{k - 1})\right\Vert^2
+                - \frac{\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
+            \right)
+                \\&\quad
+                + \frac{\sigma^{(i)}}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
+                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2. 
+        \end{align*}
+        Next, we will show that $\Pi^{(i)}(z_k - y_k), \Pi^{(i)}(\bar x - x_{k - 1})$ are zero under assumptions listed in item (i), (ii). 
         \par
-        Let's prove (i) first. 
-        Since $A^{(i)} = I$, its kernel is zero hence the $\Pi^{(i)}$ in Lemma \ref{lemma:snagp2-one-step-s1} projects to $\{0\}$ and the term $\Pi^{(i)}(z_k - y_k) = \mathbf 0$ in \eqref{ineq:snagp2-one-step-s1-rslt1}.
+        \textbf{Let's prove (i)}. 
+        Since $A^{(i)} = I$, its kernel is zero hence the $\Pi^{(i)}$ in Lemma \ref{lemma:snapg2-one-step-s1} projects to $\{0\}$ and the term $\Pi^{(i)}(z_k - y_k) = \mathbf 0$ in \eqref{ineq:snapg2-one-step-s1-rslt1}.
 It's done.
         \par
-        To see (ii), recall that $z_k = \alpha_k \bar x + (1 - \alpha_k) x_{k - 1}$ from Lemma \ref{lemma:snagp2-one-step-s1}, obviously $z_k \perp \ker A^{(i)}$ as well. 
-        Recall that $y_k$ as defined in Definition \ref{def:snapg-v2-proto} has
-        \begin{align*}
-            y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}.
-        \end{align*}
-        So $y_k \perp \ker A^{(i)}$ because it's the linear combinations of $v_{k - 1}, x_{k - 1}$. 
-        Hence, the projection of $y_k, z_k$ onto $\ker A^{(i)}$ by $\Pi^{(i)}$ is zero, hence the results from Lemma \ref{lemma:snagp2-one-step-s1} simplifies as well. 
+        \textbf{Proof of (ii)}. 
+        When $\bar x = \Pi^{(i)} x_{k - 1} = \Pi^{(i)} v_{k - 1}$, these three points $v_{k - 1}, x_{k - 1}, \bar x$ are on the same affine span. 
+        More importantly, the vector $x_{k - 1} - \bar x \in (\ker A^{(i)})^{\perp}$, and $v_{k - 1} - \bar x \in (\ker A^{(i)})^{\perp}$. 
+        Recall that $z_k = \alpha_k \bar x + (1 - \alpha_k) x_{k - 1}$ from Lemma \ref{lemma:snapg2-one-step-s1}, obviously $z_k \perp \ker A^{(i)}$ as well. 
+        Therefore, we have: 
+        \begin{align*}
+            \Pi^{(i)}(\bar x - x_{k - 1}) = \mathbf 0. 
+        \end{align*}
+        Next, using Lemma \ref{lemma:iters-snapg2-proto} \ref{lemma:iters-snapg2-proto-item1} it has 
+        \begin{align*}
+            & \left\Vert
+                \Pi^{(i)} \left(
+                    \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
+                    + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}(\bar x - x_{k - 1})
+                \right)
+            \right\Vert
+            \\
+            &= 
+            \left\Vert
+                \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}\Pi^{(i)}(\bar x - v_{k - 1})
+                + 
+                \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}\Pi^{(i)}(\bar x - x_{k - 1})
+            \right\Vert
+            \\
+            &= 0
+        \end{align*}
+        The base case $k = 0$ proof is similar to what's in \ref{lemma:snapg2-one-step-s1}. 
     \end{proof}
     The next lemma adds into the interpolation assumption and take conditional expectations on the inequality. 
-    % The following lemma state the relationships of the iterates generated by SNAPG-V2. 
-    % They are needed for the convergence proof. 
-    % % --------------------------------------------------------------------------------------------------------------
-    % \begin{lemma}[properties of the iterates \textcolor{red}{DEPRECATED}]\label{lemma:snapg2-itrs-props}
-    %     Suppose that the iterates $(z_k, x_k, y_k)_{k \ge 0}$ and sequence $(\alpha_k)_{k \ge 1}$ are produced by an algorithm satisfying Definition \ref{def:snapg-v2}. 
-    %     Let $\bar x \in \RR^n$.
-    %     Define the sequence $z_k = \alpha_k\bar x + (1 - \alpha_k)x_{k - 1}$. 
-    %     Then, the following are true: 
-    %     \begin{enumerate}
-    %         \item\label{lemma:snapg2-itrs-props-item1} For all $k \ge 1$ it has: 
-    %         \begin{align*}
-    %                 z_k - y_k 
-    %                 = 
-    %                 \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-    %                 + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
-    %         \end{align*}
-    %         \item\label{lemma:snapg2-itrs-props-item2} For all $k \ge 1$, it has: $z_k - x_k = \alpha_k(x - \bar x)$
-    %     \end{enumerate}
-    % \end{lemma}
-    % \begin{proof}
-    %     \textbf{Proof of \ref{lemma:snapg2-itrs-props-item1}}. 
-    %     From Definition \ref{def:snapg-v2}, it has
-    %     \begin{align*}
-    %         (1 + \tau_k)^{-1}
-    %         &=
-    %         \left(
-    %             1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
-    %         \right)^{-1} = \left(
-    %             \frac{L_k\alpha_k - \mu^{(i)} + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
-    %         \right)^{-1}
-    %         = \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}. 
-    %     \end{align*}
-    %     Therefore, for all $k \ge 0$, $y_k$ has 
-    %     \begin{align*}
-    %         0 &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1} - y_k
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} 
-    %         \left(
-    %             v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}} x_{k - 1}
-    %         \right) - y_k
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1}
-    %         + \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1} - y_k
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
-    %         + 
-    %         \left(
-    %             \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} - (1 - \alpha_k)
-    %         \right) x_{k - 1} - y_k
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
-    %         + 
-    %         (1 - \alpha_k)\left(
-    %             \frac{L_k - L_k + \mu^{(i)}}{L_k - \mu^{(i)}}
-    %         \right) x_{k - 1} - y_k
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
-    %         + 
-    %         \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}x_{k - 1} - y_k. 
-    %     \end{align*}
-    %     Therefore, we establish the equality 
-    %     \begin{align*}
-    %         (1 - \alpha_k)x_{k - 1} - y_k &= 
-    %         - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
-    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}. 
-    %     \end{align*}
-    %     On the second equality below, we will the above equality, it goes: 
-    %     \begin{align*}
-    %         z_k - y_k &= 
-    %         \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
-    %         \\
-    %         &= \alpha_k \bar x 
-    %         - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
-    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-    %         + \left(
-    %             \alpha_k - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}
-    %         \right)\bar x
-    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-    %         + \left(
-    %             \frac{\alpha_kL_k - \alpha_k \mu^{(i)} - L_k\alpha_k + \mu^{(i)}}{L_k - \mu^{(i)}}
-    %         \right)\bar x
-    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-    %         + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}\bar x
-    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-    %         + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
-    %     \end{align*}
-    %     \textbf{proof of \ref{lemma:snapg2-itrs-props-item2}.}
-    %     From Definition \ref{def:snapg-v2} it has directly: 
-    %     \begin{align*}
-    %         z_k - x_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
-    %         \\
-    %         &= \alpha_k \bar x + x_{k - 1} - x_k - \alpha_k x_{k - 1}
-    %         \\
-    %         &= \alpha_k(\bar x - \alpha_k^{-1}(x_k - x_{k - 1}) - x_{k - 1})
-    %         \\
-    %         &= \alpha_k (\bar x - v_k).
-    %     \end{align*}
-
-    % \end{proof}
-    % % --------------------------------------------------------------------------------------------------------------
-    % \begin{theorem}[SNAPG-V2 one step convergence \textcolor{red}{DEPRECATED}]\label{thm:snapg2-one-step}
-    %     Let $F$ satisfies assumption \ref{ass:interp-hypothesis}. 
-    %     Suppose that an algorithm satisfying Definition \ref{def:snapg-v2} uses this $F$. 
-    %     Let $\mathbb E_k$ denotes the expectation conditioned on $I_0, I_1, \ldots, I_{k - 1}$. 
-    %     Then, for all $k \ge 1$, it has the following inequality 
-    %     \begin{align*}
-    %         & \mathbb E_k\left[F_{I_k}(x_{k})\right] 
-    %         - F(\bar x) 
-    %         + \mathbb E_k\left[
-    %             \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %         \right]
-    %         \\
-    %         &\le 
-    %         (1 - \alpha_k)\left(
-    %                 \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
-    %                 - F(\bar x)
-    %                 + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
-    %         \right)
-    %             \\ &\quad 
-    %             + \mathbb E_k\left[
-    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-    %             \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
-    %             + \frac{\alpha_k(\tilde\mu - \mu)}{2} 
-    %             \Vert \bar x - v_{k - 1}\Vert^2. 
-    %     \end{align*}
-    %     And for $k = 0$, it has 
-    %     \begin{align*}
-    %         \mathbb E \left[ F_{I_0}\right] - F(\bar x) 
-    %         + \frac{L_0}{2}\mathbb E \left[\Vert \bar x - x_0\Vert^2\right]
-    %         &\le 
-    %         \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
-    %     \end{align*}
-    % \end{theorem}
-    % \begin{proof}
-    %     Let's suppose that $I_k = i$ and, for all $k \ge 0$. 
-    %     Let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ where $\bar x$ is a minimizer of $F$. 
-    %     The proof is long so, we use letters and subscript under relations such as $\underset{(\cdot)}{=}, \underset{(\cdot)}{\ge}$ to indicate which result is used going from the previous expression to the next.
-    %     We list the following intermediate results, (d)-(g) are proved at the end of the proof. 
-    %     \begin{itemize}
-    %         \item[(a)] We can use proximal gradient inequality from Theorem \ref{thm:pg-ineq} with $z = z_k$ because each $F_i$ is $K_i$ Lipschitz smooth and, $\mu^{(i)}$ strongly convex with $K_i \ge \mu^{(i)}$.
-    %         \item[(b)] We can use Jensen's inequality of Theorem \ref{thm:jesen} with $z = z_k$ on $F_i$. 
-    %         \item[(c)] The sequence $(\alpha_k)_{k \ge 0}$ has $(L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right)$. 
-    %         \item[(d)] Prove in Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item1} we use the equality:
-    %         \begin{align*}
-    %             (\forall k \ge 1)\; 
-    %             z_k - y_k 
-    %             = 
-    %             \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-    %             + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
-    %         \end{align*}
-    %         \item [(e)] From Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item2}, we use: $(\forall k \ge 1)\; z_k - x_k = \alpha_k (\bar x - v_k)$. 
-    %         \item [(f)] Using direct algebra, we have for all $k \ge 1$: 
-    %         \begin{align*}
-    %             \frac{\left(\mu^{(i)}\right)^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} 
-    %             - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
-    %             = \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
-    %             {2\left(L_k - \mu^{(i)}\right)}. 
-    %         \end{align*}
-    %         \item [(g)] Using (c), we have for all $k \ge 1$: 
-    %         \begin{align*}
-    %             \frac{\left(
-    %                 L_k\alpha_k - \mu^{(i)}
-    %             \right)^2}{2(L_k - \mu^{(i)})} 
-    %             -
-    %             \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} 
-    %             = 
-    %             \frac{
-    %             \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
-    %             \left(\alpha_k - 1\right)
-    %             }
-    %             {2(L_k - \mu^{(i)})}
-    %             + \frac{\alpha_k(\tilde \mu_k - \mu^{(i)})}{2}. 
-    %         \end{align*}
-    %         \item[(h)] Because we assumed interpolation hypothesis in Assumption \ref{ass:interp-hypothesis}, it has $\mathbb E[F_{I_k}(\bar x)] = F(\bar x)$ for all $\bar x$ that is a minimizer of $F$.
-    %     \end{itemize}
-    %     For all $k \ge 1$, starting with (a) we have: 
-    %     \begin{align}\label{ineq:snapg2-one-step-chain1}
-    %         \begin{split}
-    %             0 &\le F_i(z_k) - F_i(x_k) - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2
-    %             \\
-    %             &\underset{\text{(b)}}{\le}
-    %             \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) \\
-    %                 &\quad 
-    %                 - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
-    %                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-    %                 + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2. 
-    %         \end{split}
-    %     \end{align}
-    %     And we have the following chain of equalities:
-    %     {\allowdisplaybreaks
-    %     \begin{align*}
-    %         & - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
-    %         + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2
-    %         \\
-    %         &\underset{\text{(d)}}{=}
-    %         - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2 
-    %             \\&\quad
-    %             + \frac{L_k - \mu^{(i)}}{2}
-    %             \left\Vert
-    %                 \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-    %                 + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1})
-    %             \right\Vert^2
-    %         \\
-    %         &= 
-    %         - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2 
-    %             \\&\quad
-    %             + \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{(\mu^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2 
-    %             \\&\quad 
-    %             + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
-    %         \\
-    %         &= 
-    %         \left(
-    %             \frac{(\mu^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
-    %         \right)\Vert \bar x - x_{k - 1}\Vert^2
-    %             \\ &\quad 
-    %             + \left(
-    %                 \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
-    %             \right) \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             \\&\quad 
-    %             + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
-    %         \\
-    %         &\underset{\text{(f)}}{=}
-    %         \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
-    %         {2\left(L_k - \mu^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2
-    %             \\ &\quad 
-    %             + \left(
-    %                 \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
-    %             \right) \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             \\&\quad 
-    %             + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
-    %         \\
-    %         & \underset{\text{(g)}}{=} 
-    %         \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
-    %         {2\left(L_k - \mu^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2
-    %             \\ &\quad 
-    %             + \left(
-    %                 \frac{
-    %                     \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
-    %                     \left(\alpha_k - 1\right)
-    %                 }
-    %                 {2(L_k - \mu^{(i)})}
-    %                 + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}
-    %             \right) 
-    %             \Vert \bar x - v_{k - 1}\Vert^2
-    %             \\ &\quad 
-    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
-    %         \\
-    %         &= 
-    %         \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\left(
-    %             \Vert \bar x - x_{k - 1}\Vert^2 + \Vert \bar x - v_{k - 1}\Vert^2 - 2\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
-    %         \right) 
-    %             \\ &\quad 
-    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %         \\
-    %         &= \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
-    %             \Vert x_{k - 1} - v_{k - 1} \Vert^2
-    %             \\ &\quad 
-    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2.
-    %     \end{align*}
-    %     }
-    %     Substituting the above back to the tail of Inequality \eqref{ineq:snapg2-one-step-chain1} it gives: 
-    %     {\allowdisplaybreaks
-    %     \begin{align*}
-    %         0 &\le 
-    %         \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) 
-    %             \\&\quad 
-    %             - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-    %             + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
-    %             \Vert x_{k - 1} - v_{k - 1} \Vert^2
-    %             \\ &\quad 
-    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %         \\
-    %         &\underset{\text{(e)}}{=} 
-    %         \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) 
-    %             \\&\quad 
-    %             - \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %             + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
-    %             \Vert x_{k - 1} - v_{k - 1} \Vert^2
-    %             \\ &\quad 
-    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %         \\
-    %         &= (\alpha_k - 1)F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) + F_i(\bar x)
-    %             \\&\quad 
-    %             - \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %             + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
-    %             \\ &\quad 
-    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %         \\
-    %         &= (1 - \alpha_k)\left(
-    %             F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
-    %         \right) 
-    %             \\ & \quad
-    %             - \left(
-    %                 F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %             \right)
-    %             \\ &\quad 
-    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
-    %     \end{align*}
-    %     }
-    %     Recall that $i = I_k$ is the random variable from Definition \ref{def:snapg-v2}. 
-    %     Rearranging the last expression in the above equality chain can be conveniently written as
-    %     \begin{align}
-    %         \begin{split}
-    %             & F_{I_k}(x_{k}) - F_{I_k}(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %             \\ &\le 
-    %             (1 - \alpha_k)\left(
-    %                 F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
-    %             \right) 
-    %                 \\ &\quad 
-    %                 + \frac{\alpha_k(\tilde \mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %                 + \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
-    %         \end{split}
-    %     \label{ineq:snapg2-one-step-presult1}\end{align}
-    %     Recall $\mathbb E_k$ denotes the conditional expectation on $I_0, I_1, \ldots, I_{k - 1}$. 
-    %     Taking the conditional expectation on the LHS of the \eqref{ineq:snapg2-one-step-presult1} yields: 
-    %     \begin{align*}
-    %         & \mathbb E_k\left[
-    %             F_{I_k}(x_{k}) - F_{I_k}(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %         \right]
-    %         \\
-    %         &\underset{\text{(h)}}{=}
-    %         \mathbb E_k\left[F_{I_k}(x_{k})\right] 
-    %         - F(\bar x) 
-    %         + \mathbb E_k\left[
-    %             \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %         \right]. 
-    %     \end{align*}
-    %     On the RHS of \eqref{ineq:snapg2-one-step-presult1}, using the linearity property while taking the conditional expectation yields: 
-    %     {\allowdisplaybreaks
-    %     \begin{align*}
-    %         & \mathbb E_k\left[
-    %             (1 - \alpha_k)\left(
-    %                 F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
-    %             \right)
-    %         \right]
-    %             \\ &\quad 
-    %             + \mathbb E_k \left[
-    %                 \frac{\alpha_k(\tilde\mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             \right]
-    %             + \mathbb E_k\left[
-    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
-    %             \right]
-    %         \\
-    %         &\underset{\text{(1)}}{=} 
-    %         (1 - \alpha_k)\left(
-    %                 \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
-    %                 -\mathbb E_k [F_{I_k}(\bar x)] 
-    %                 + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
-    %         \right)
-    %             \\ &\quad 
-    %             + \mathbb E_k \left[
-    %                 \frac{\alpha_k(\tilde\mu - \mu^{(I_k)})}{2} 
-    %             \right]\Vert \bar x - v_{k - 1}\Vert^2
-    %             + \mathbb E_k\left[
-    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-    %             \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
-    %         \\
-    %         &\underset{\text{(h)}}{=} 
-    %         (1 - \alpha_k)\left(
-    %                 \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
-    %                 - F(\bar x)
-    %                 + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
-    %         \right)
-    %             \\ &\quad 
-    %             + \mathbb E_k \left[
-    %                 \frac{\alpha_k(\tilde\mu - \mu^{(I_k)})}{2} 
-    %             \right]\Vert \bar x - v_{k - 1}\Vert^2
-    %             + \mathbb E_k\left[
-    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-    %             \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
-    %         \\
-    %         &\underset{\text{(2)}}{=}
-    %         (1 - \alpha_k)\left(
-    %                 \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
-    %                 - F(\bar x)
-    %                 + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
-    %         \right)
-    %             \\ &\quad 
-    %             \frac{\alpha_k(\tilde\mu - \mu)}{2} 
-    %             \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \mathbb E_k\left[
-    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-    %             \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
-    %     \end{align*}
-    %     }
-    %     We note that at label (1), we used the fact that $\alpha_k$ is a constant and, $x_{k - 1}, v_{k - 1}$ only depends on random variable $I_0, I_1, \ldots, I_{k - 1}$ hence it falls out of the conditional expectation $\mathbb E_k$.
-    %     At label (2), we used assumption (Assumption \ref{ass:sum-of-many}) that the averages of all the $\mu^{(I_k)}$ on each $F_{I_k}$ equals to $\mu$ hence, the expectation evaluates to zero by linearity of the expected value operator.
-    %     \par
-    %     Combining the above results on the expectation of RHS, and LHS of \eqref{ineq:snapg2-one-step-presult1}, we have the one-step inequality in expectation: 
-    %     \begin{align*}
-    %         & \mathbb E_k\left[F_{I_k}(x_{k})\right] 
-    %         - F(\bar x) 
-    %         + \mathbb E_k\left[
-    %             \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %         \right]
-    %         \\
-    %         &\le 
-    %         (1 - \alpha_k)\left(
-    %                 \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
-    %                 - F(\bar x)
-    %                 + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
-    %         \right)
-    %             \\ &\quad 
-    %             + \mathbb E_k\left[
-    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-    %             \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
-    %     \end{align*}
-    %     Finally, we show the base case. 
-    %     When $k = 0$, by assumption it had $\alpha_0 = 1$ hence $\tau_0$ in Definition \ref{def:snapg-v2} has $\tau_0 = 0$ which makes $y_0 = v_{- 1} = x_{-1}$. 
-    %     Therefore, it makes $x_0 = T_{L_0}(y_0 | F_{I_0}) = T_{L_0}(v_{-1} | F_{I_0})$. 
-    %     Similarly, it has also $z_0 = \bar x$.
-    %     Applying Theorem \ref{thm:pg-ineq} with $z = z_0$ and, assume a successful line search with $L_0$, it yields: 
-    %     \begin{align*}
-    %         0 &\le F_{I_0}(z_0) - F_{I_0}(x_0) - \frac{L_0}{2}\Vert z_0 - x_0\Vert^2 + \frac{L_0 - \mu^{(I_0)}}{2}\Vert z_0 - y_0\Vert^2
-    %         \\
-    %         &= F_{I_0}(\bar x) - F_{I_0}(x_0) - \frac{L_0}{2}\Vert \bar x - x_0\Vert^2 + \frac{L_0 - \mu^{(I_0)}}{2}\Vert \bar x - v_{-1}\Vert^2. 
-    %     \end{align*}
-    %     Re-arranging and taking the expectation it yields: 
-    %     \begin{align*}
-    %         \mathbb E \left[
-    %             F_{I_0}(x_0) - F_{I_0}(\bar x) + \frac{L_0}{2}\Vert \bar x - x_0\Vert^2
-    %         \right]
-    %         &\underset{\text{(h)}}{=}
-    %         \mathbb E \left[ F_{I_0}\right] - F(\bar x) 
-    %         + \frac{L_0}{2}\mathbb E \left[\Vert \bar x - x_0\Vert^2\right]
-    %         \\
-    %         &\le \frac{L_0 - \mathbb E \left[\mu^{(I_0)}\right]}{2}\Vert \bar x - v_{-1}\Vert^2
-    %         \\
-    %         &= \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
-    %     \end{align*}
-    %     % INTERMEDIATE RESULTS
-    %     \textbf{Proof of (f)}. 
-    %     The proof is direct algebra and, it has: 
-    %     {\small\allowdisplaybreaks
-    %     \begin{align*}
-    %         & \frac{\left(\mu^{(i)}\right)^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} 
-    %         - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
-    %         \\
-    %         &= 
-    %         \frac{1}{2\left(L_k - \mu^{(i)}\right)}
-    %         \left(
-    %             \left(\mu^{(i)}\right)^2(1 - \alpha_k)^2
-    %             - \left(L_k - \mu^{(i)}\right)\mu^{(i)} \alpha_k(1 - \alpha_k)
-    %         \right)
-    %         \\
-    %         &= \frac{1 - \alpha_k}{2\left(L_k - \mu^{(i)}\right)}\left(
-    %             \left(\mu^{(i)}\right)^2 
-    %             - \left(\mu^{(i)}\right)^2\alpha_k 
-    %             - \left(L_k \mu^{(i)} \alpha_k - \left(\mu^{(i)}\right)^2 \alpha_k\right)
-    %         \right)
-    %         \\
-    %         &= 
-    %         \frac{1 - \alpha_k}{2(L_k - \mu)}\left(
-    %             \left(\mu^{(i)}\right)^2 - L_k\left(\mu^{(i)}\right)\alpha_k
-    %         \right)
-    %         \\
-    %         &= 
-    %         \frac{(1 - \alpha_k)\mu^{(i)}\left(\mu^{(i)} - L_k\alpha_k\right)}
-    %         {2\left(L_k - \mu^{(i)}\right)}
-    %         \\
-    %         &= \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
-    %         {2\left(L_k - \mu^{(i)}\right)}. 
-    %     \end{align*}
-    %     }    
-    %     % INTERMEDIATE RESULTS 
-    %     \textbf{Proof of (g)}.
-    %     From the property of the $\alpha_k$ sequence stated in item (c), we have: 
-    %     {\allowdisplaybreaks
-    %     \begin{align*}
-    %         &\frac{\left(
-    %             L_k\alpha_k - \mu^{(i)}
-    %         \right)^2}{2(L_k - \mu^{(i)})} 
-    %         -
-    %         \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} 
-    %         \\
-    %         &= 
-    %         \frac{\left(
-    %             L_k\alpha_k - \mu^{(i)}
-    %         \right)^2}{2(L_k - \mu^{(i)})} 
-    %         -
-    %         \frac{L_k\alpha_k(\alpha_k - \tilde \mu/L_k)}{2} 
-    %         \\
-    %         &=
-    %         \frac{\left(
-    %             L_k\alpha_k - \mu^{(i)}
-    %         \right)^2}{2(L_k - \mu^{(i)})} 
-    %         - \frac{L_k\alpha_k(\alpha_k - \mu^{(i)}/L_k)}{2}
-    %         + \frac{L_k\alpha_k(\alpha_k - \mu^{(i)}/L_k)}{2} 
-    %         - \frac{L_k\alpha_k(\alpha_k - \tilde \mu/L_k)}{2} 
-    %         \\
-    %         &= 
-    %         \frac{\left(
-    %             L_k\alpha_k - \mu^{(i)}
-    %         \right)^2}{2(L_k - \mu^{(i)})} 
-    %         - \frac{\alpha_k\left(L_k\alpha_k - \mu^{(i)}\right)}{2}
-    %         + \frac{L_k\alpha_k}{2}
-    %         \frac{\left(
-    %             \tilde \mu - \mu^{(i)}
-    %         \right)}{L_k}
-    %         \\
-    %         &=
-    %         \frac{L_k \alpha_k - \mu^{(i)}}{2(L_k - \mu^{(i)})}\left(
-    %             L_k \alpha_k - \mu^{(i)} 
-    %             - \left(L_k - \mu^{(i)}\right)\alpha_k
-    %         \right)
-    %         + \frac{\alpha_k(\tilde \mu - \mu^{(i)})}{2}
-    %         \\
-    %         &= \frac{L_k \alpha_k - \mu^{(i)}}{2(L_k - \mu^{(i)})}\left(
-    %             \mu^{(i)}\alpha_k - \mu^{(i)} 
-    %         \right)
-    %         + \frac{\alpha_k(\tilde \mu - \mu^{(i)})}{2}
-    %         \\
-    %         &= 
-    %         \frac{
-    %             \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
-    %             \left(\alpha_k - 1\right)
-    %         }
-    %         {2(L_k - \mu^{(i)})}
-    %         + \frac{\alpha_k(\tilde \mu - \mu^{(i)})}{2}. 
-    %     \end{align*}   
-    %     } 
-    % \end{proof}
+    \begin{lemma}[SNAPG-V2 classical one step convergence]\label{lemma:snapg-v2-one-step-not-scnvx}
+        Suppose that the sequence $(v_k, x_k, y_k)_{k \ge 0}$ is generated by algorithms that satisfy Definition \ref{def:snapg-v2-classical}, then for all $k \ge 1$, the $\mathcal R^{(i)}_k$ in \eqref{ineq:snapg2-one-step-s1-rslt1} equals to zero.
+        Let $\mathbb E_k$ defines the conditional expectation on $I_0, I_1, \ldots, I_{k - 1}, I_k$. 
+        If in addition, Assumption \ref{ass:interp-hypothesis} holds. 
+        Then, it has for all $k \ge 1$ the inequality: 
+        \begin{align*}
+            & \expect_{k - 1}
+            \left[
+                F_{I_k}(x_k)
+                - F(\bar x)
+                + \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2
+            \right]
+            \\&\le 
+            (1 - \alpha_k)\left(
+                F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2} \Vert \bar x - v_{k - 1}\Vert^2
+            \right). 
+        \end{align*}
+        and, inequality \ref{ineq:snapg2-one-step-s1-rslt2} holds when $k = 0$. 
+    \end{lemma}
+    \begin{proof}
+        Setting $\sigma^{(i)} = 0$, it has $\mathcal R^{(i)}_k = \alpha_k(\tilde \mu - \sigma^{(i)})/2\Vert \bar x - v_{k - 1}\Vert^2$. 
+        By Definition \ref{def:snapg-v2-classical}, $\tilde \mu = 0, \sigma^{(i)} = 0$ for all $i = 1, 2, \ldots, n$, so $\mathcal R^{(i)}_k = 0$ for all $k \ge 1$. 
+    \end{proof}
 \section{Convergence rate of the algorithm under various circumstances}

### 2025-07-15 Notebook LaTEX/SAGD Under Interpolation/main.tex
;~;

--- 2025-07-10 Notebook LaTEX/SAGD Under Interpolation/main.tex
@@
 % ==============================================================================
+\section{Introduction}
+    Does stochastic accelerated Nesterov's acceleration (SNAG) produces accelerated convergence rate (or, any type of convergence) when the Interpolation Hypothesis is true? 
+    \cite{bauschke_convex_2017}
+    Previously we got some results, but unfortunately it was incorrect the mistake is diffcult to recover. 
+    \par
+    \textbf{However, I don't think that it's true after some mistakes from previous version of the notes and careful investigations.}
+    In this file we develop some sufficient conditions for Linear convergence of (SNAG). 
+    We will give explanations on why we don't think this is necessarily true.
+
 \section{In preparations}
-    \textbf{Notations}. 
+    Unless specifically specified in the context, we use the following notations. 
+    $\Pi_C$ denotes the projection onto a set $C$. 
+    Let $A \in \RR^{m \times n}$ be a matrix. 
+    $\sigma_{\min}(A)$ denotes the smallest non-zero absolute value of all singular values of $A$. 
+    Let $\Vert A\Vert$ denotes the spectral norm of the matrix $A$. 
+    $I$ denotes the identity operator. 
+    When two expressions are connected via non-trivial results, it's expressed with $\underset{(\cdot)}{=}, \underset{(\cdot)}{\ge}$ where $(\cdot)$ is a label of some intermediate results immediately before it, or explained right after a chain of expressions.
     \subsection{Basic definitions}
@@
             If, $f$ is $\mu \ge 0$ strongly convex and $L$ Lipschitz smooth then, its Bregman Divergence has for all $x, y \in \RR^n$: $\mu/2 \Vert x - y\Vert^2 \le D_f(x, y) \le L/2 \Vert x - y\Vert^2$.
-        \end{remark}
-    \subsection{Properties of functions, characterizations}
-        The definitions are ordered from the weakest to strongest. 
-        % --------------------------------------------------------------------------------------------------------------
-        \begin{definition}[semi strongly convex function \textcolor{red}{NEW}]\label{def:semi-scnvx}
-            A function $F: \RR^n \rightarrow \overline \RR$ is a semi strongly convex function, abbreviated as ``Semi-SCNVX'' with respective to a linear mapping $A \in \RR^{m \times n}$ if $F - \frac{1}{2}\Vert Ax\Vert^2$ is a convex function.
-        \end{definition}
-        \begin{remark}
-            Any $\mu \ge 0$ strongly convex function is Semi-SCNVX with $A = \sqrt{\mu}I$. 
-            But the converse is not true because a seminorm is not a norm. 
-            One feature of a Semi-SCNVX function is that it doesn't have a unique minimizer which differs it from strong convexity. 
-            It may not have a unique minimizer because it's not necessary that $\kernel A = \{\mathbf 0\}$. 
+            We note that usually the Bregman Divergence is used with a Legendre function, but in here, we do not assume that $f$ has to be Legendre. 
         \end{remark}
         % --------------------------------------------------------------------------------------------------------------
-        \begin{definition}[smooth Semi-SCNVX \textcolor{red}{NEW}]\label{def:seminorm-smooth-scnvx}
-            Let $m, n\in \N$ be a natural numbers. 
-            Let $f:\RR^m \rightarrow \RR$ be a differentiable function and full domain. 
-            If there exists $A_1: \RR^{m\times n}$ and, $A_2 \in \RR^{m \times n}$ matrices such that it satisfies:
+        \begin{definition}[Lipschitz smoothness and strongly convex]\label{def:lip-smooth-and-scnvx}
+            A differentiable function $f: \RR^n \rightarrow \RR$ is $L$ lipschitz smooth and, $\mu$ strong convex for some $L > \mu \ge 0$ if and only if for all $x, y \in \RR^n$ it satisfies the inequality
             \begin{align*}
-                (\forall x \in \RR^m)(\forall y \in \RR^m)\;
-                \frac{1}{2}\Vert A_1x - A_1y\Vert^2 \le 
-                D_f(x, y) \le \frac{1}{2}\Vert A_2x - A_2y\Vert^2. 
+                \frac{\mu}{2}\Vert x - y\Vert^2 \le D_f(x, y) \le \frac{L}{2}\Vert x - y\Vert^2. 
             \end{align*}
-            Then, we call this function is semi-relative smooth with respect to $A_1$, and semi convex to $A_2$
         \end{definition}
-        \begin{remark}
-            The definition exchanged the $\Vert \cdot\Vert^2$ for a seminorm squared: $x \mapsto \Vert A_1x\Vert^2$ with some $A: \RR^m \rightarrow \RR^n$ for the definition of relative smoothness and relative strong convexity.
-            Obviously, it has $\Vert A_1x\Vert \le \Vert A_2x\Vert$ for all $x\in \RR^m$, which further implies that $\ker A_1\supseteq\ker A_2$. 
-        \end{remark}
-        % --------------------------------------------------------------------------------------------------------------
-        \begin{theorem}[semi Jesen inequality \textcolor{red}{NEW}]\label{thm:semi-scnvx-equiv}
-            A function $F$ is Semi-SNCVX with $A \in \RR^{m \times n}$ (Definition \ref{def:semi-scnvx}) if and only if, for all $x, y \in \RR^n$ and, $\lambda \in [0, 1]$ it satisfies the inequality:
-            \begin{align*}
-                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2. 
-            \end{align*}
-        \end{theorem}
-        \begin{proof}
-            For all $\lambda \in \RR, x \in \RR^n, y \in \RR^n$ it has $-1/2\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 = (1/2)(\lambda\Vert Ax\Vert^2 + (1 - \lambda)\Vert Ay\Vert^2 - \lambda(1 - \lambda)\Vert Ax - Ay\Vert^2)$ by verifying:
-            \begin{align*}
-                & -\frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 + 
-                \left(
-                    \frac{\lambda}{2}\Vert Ax\Vert^2 + \frac{1 - \lambda}{2}\Vert Ay\Vert^2 - \frac{\lambda(1 - \lambda)}{2}\Vert Ay - Ax\Vert^2
-                \right)
-                \\
-                &= 
-                -\frac{1}{2}\left(
-                    \lambda^2\Vert Ax\Vert^2 + (1 - \lambda)^2\Vert Ay\Vert^2 - 2\lambda(1 - \lambda) \langle Ax, Ay\rangle
-                \right)
-                    \\ &\quad 
-                    + 
-                    \left(
-                        \frac{\lambda}{2} - \frac{\lambda(1 - \lambda)}{2}
-                    \right)\Vert Ax\Vert^2 + \left(
-                        \frac{1 - \lambda}{2} - \frac{\lambda(1 - \lambda)}{2}
-                    \right)\Vert Ay\Vert^2 - \lambda(1 - \lambda)\langle Ay, Ax\rangle
-                \\
-                &= - \frac{\lambda^2}{2}\Vert Ax\Vert^2 - \frac{(1 - \lambda)^2}{2}\Vert Ay\Vert^2
-                    \\ &\quad 
-                    + 
-                    \left(
-                        \frac{\lambda}{2} - \frac{\lambda - \lambda^2}{2}
-                    \right)\Vert Ax\Vert^2 + \left(
-                        \frac{1 - \lambda}{2} - \frac{\lambda - \lambda^2}{2}
-                    \right)\Vert Ay\Vert^2
-                \\
-                &= 0
-            \end{align*}
-            Using the above result we can prove the equivalency because 
-            {\small
-            \begin{align*}
-                0 &\le F(\lambda x + (1 - \lambda)y) + \lambda F(x) + (1 - \lambda)F(y) -\frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2
-                \\
-                &=  F(\lambda x + (1 - \lambda)y) - \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 
-                + \lambda F(x) - \frac{\lambda}{2}\Vert Ax\Vert^2 
-                + (1 - \lambda)F(y) - \frac{1 - \lambda}{2} \Vert Ay\Vert^2 
-                    \\ &\quad 
-                    - \frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2 + \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2
-                    + \frac{1}{2}\Vert Ax\Vert^2 + \frac{1}{2}\Vert Ay\Vert^2 
-                \\
-                &= 
-                F(\lambda x + (1 - \lambda)y) - \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 
-                    \\ &\quad 
-                    + \lambda \left(F(x) - \frac{1}{2}\Vert Ax\Vert^2\right) 
-                    + (1 - \lambda)\left(F(y) - \frac{1}{2} \Vert Ay\Vert^2\right). 
-            \end{align*}
-            }
-            The last line shows that the function $F(x) - \frac{1}{2}\Vert Ax\Vert^2$ is convex, the chain of equality shows the equivalence. 
-        \end{proof}
+    \subsection{important inequalities}
+        \begin{assumption}\label{ass:smooth-plus-nonsmooth}
+            Suppose that $F = f + g$ where $f, g$ are both convex, proper and closed. 
+            In addition, assume $f$ is $L > \mu \ge 0$ Lipschitz smooth and strongly convex satisfying Definition \ref{def:lip-smooth-and-scnvx}. 
+        \end{assumption}
         % --------------------------------------------------------------------------------------------------------------
@@
         \end{remark}
-        The following theorem classifies a class of semi strongly convex function. 
         % --------------------------------------------------------------------------------------------------------------
-        \begin{theorem}[affine composite smooth and strongly convex]\label{thm:aff-smooth-sq-scnvx}
-            Let $f: \RR^n \rightarrow \RR$ be an $L$ smooth and, $\mu \ge 0$ strongly convex.
-            Let $A: \RR^m \rightarrow \RR^n$, $b \in \RR^n$ be arbitrary and, define $h: \RR^m \rightarrow \RR= x \mapsto f(Ax - b)$. 
-            Ddenote $\Pi = \Pi_{\ker A}$ to be the projection operator onto the kernel of $A$, denote $\Vert A\Vert$ to be the operator norm of the matrix, and $\sigma_{\min}(A)$ to be the smallest non-zero eigenvalues of $A$ in absolute value.
-            Then, it satisfies for all $x \in \RR^m, y \in \RR^m$:  
+        \begin{lemma}[inexact proximal gradient inequality]\label{lemma:inex-pg-ineq}
+            Let $F = f + g$ satisfies Definition \ref{def:lip-smooth-and-scnvx} with $L > \mu \ge 0$. 
+            Let $x \in \RR^n$ be fixed. 
+            Suppose an inexact evaluation of proximal gradient operator at $x$ yield an approximation $\tilde x$, characterized by: 
             \begin{align*}
-                \frac{\mu \sigma_{\min}(A)^2}{2}\Vert (I - \Pi)(x - y)\Vert^2
-                \le \frac{\mu}{2}\Vert Ax - Ay\Vert^2 
-                \le D_h(x, y) \le \frac{L\Vert A\Vert^2}{2}\Vert x - y\Vert^2. 
+                & D_f(\tilde x, x) \le \frac{B}{2}\Vert \tilde x - x\Vert^2, 
+                \\
+                & \exists: w \in \partial \left[
+                    z \mapsto  g(z) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
+                \right](\tilde x)\; \text{s.t: } \Vert w\Vert \le \epsilon \Vert x - \tilde x\Vert. 
             \end{align*}
-            Therefore, it satisfies Definition \ref{def:semi-scnvx} with $A_1 = \sqrt{L}A, A_2 = \sqrt{\mu}A$ so it's Semi-SCNVX. 
-        \end{theorem}
+            Then, it would satisfy for all $z\in \RR^n$ the inequality: 
+            \begin{align*}
+                0 &\le 
+                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2
+                - \frac{B - \epsilon}{2}\Vert z - \tilde x\Vert^2
+                + \frac{\epsilon}{2}\Vert x - \tilde x \Vert^2. 
+            \end{align*}
+        \end{lemma}
         \begin{proof}
-            Then the Bregman divergence of $h$ is: 
+            Let $h = z \mapsto g(z) + \langle \nabla f(x), z - x\rangle + B/2\Vert z - x\Vert^2$. 
+            $h$ is a $B$ strongly convex function, using the subgradient inequality of a strongly convex function it has for all $z \in \RR^n$: 
             \begin{align*}
-                D_h(x, y) &= h(x) - h(y) - \langle \nabla h(y), x - y\rangle
-                \\
-                &= f(Ax - b) - f(Ay - b) - \langle A^T\nabla f(Ay - b), x - y\rangle
-                \\
-                &= f(Ax - b) - f(Ay - b) - \langle \nabla f(Ay - b), Ax - Ay\rangle
-                \\
-                &= f(Ax - b) - f(Ay - b) - \langle \nabla f(Ay - b), Ax - b - (Ay - b)\rangle
-                \\
-                &= D_f(Ax - b, Ay - b). 
-            \end{align*}
-            Since $f$ is $L$ smooth and $\mu \ge 0$ strongly convex, it means 
-            \begin{align*}
-                \frac{\mu}{2}\Vert Ax - Ay\Vert^2
-                &= 
-                \frac{\mu}{2}\Vert Ax - b - (Ay - b)\Vert^2 
-                \\
-                &\le D_f(Ax - b, Ay - b)
-                \\
-                &= D_h(x, y) 
-                \\
-                &\le \frac{L}{2} \Vert Ax - Ay\Vert^2
-                \\
-                &\le \frac{L\Vert A\Vert^2}{2} \Vert x - y\Vert^2. 
-            \end{align*}
-            Using some linear algebra, one can represent $x - y$ as their orthogonal components in $\ker A$, $\ker A^T$ so it has 
-            \begin{align*}
-                \frac{\mu}{2}\Vert A(x - y)\Vert^2 &= 
-                \frac{\mu}{2}\Vert A(\Pi(x - y) + (1 - \Pi)(x - y))\Vert^2
+                \frac{B}{2}\Vert z - \tilde x\Vert^2
+                &\le h(z) - h(\tilde x) - \langle w, z - \tilde x\rangle
                 \\
                 &= 
-                \frac{\mu}{2}\Vert A(1 - \Pi)(x - y))\Vert^2
+                \left(
+                    g(z) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
+                \right)
+                \\ &\quad 
+                    - 
+                    \left(
+                        g(\tilde x) + \langle \nabla f(x), \tilde x - x\rangle + \frac{B}{2}\Vert \tilde x - x\Vert^2
+                    \right)
+                    - \langle w, z - \tilde x\rangle
                 \\
-                &\ge \frac{\mu\sigma_{\min}(A)}{2}\Vert (1 - \Pi)(x - y)\Vert^2. 
+                &= \left(
+                    g(z) + f(z) - f(z) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
+                \right)
+                \\ &\quad 
+                    - 
+                    \left(
+                        g(\tilde x) + f(\tilde x) - f(\tilde x) 
+                        + \langle \nabla f(x), \tilde x - x\rangle + \frac{B}{2}\Vert \tilde x - x\Vert^2
+                    \right)
+                    - \langle w, z - \tilde x\rangle
+                \\
+                &= \left(
+                    F(z) - D_f(z, x) + \frac{B}{2}\Vert z - x\Vert^2
+                \right)
+                \\ &\quad 
+                    - 
+                    \left(
+                        F(\tilde x) - D_f(\tilde x, x) + \frac{B}{2}\Vert \tilde x - x\Vert^2
+                    \right)
+                    - \langle w, z - \tilde x\rangle
+                \\
+                &\underset{\text{(a)}}{\le} F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 - 0 - \langle w, z - \tilde x \rangle
+                \\
+                &\underset{\text{(b)}}{\le}
+                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 - 0 + \epsilon \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert. 
             \end{align*}
-            These results makes for the final inequalities: 
+            At (a), we used the fact that $f$ is $L > \mu \ge 0$ Lipschitz smooth and strongly convex therefore it has for all $y \in \RR^n$: 
             \begin{align*}
-                \frac{\mu\sigma_{\min}(A)}{2}\Vert (I - \Pi)(x - y)\Vert^2
-                \le 
-                D_h(x, y) \le 
-                \frac{L\Vert A\Vert^2}{2}\Vert x - y\Vert^2. 
+                0 
+                \le \frac{L}{2}\Vert z - y\Vert^2  - D_f(z, y)
+                \le \frac{L - \mu}{2}\Vert z - y\Vert^2. 
             \end{align*}
-        \end{proof}
-        \begin{theorem}[affine minimizer set for aff comp smooth strongly convex]
-            \todoinline{NOT FINISHED YET.}
-        \end{theorem}
-    \subsection{Important inequalities}
-            \begin{assumption}[smooth add nonsmooth]\label{ass:smooth-plus-nonsmooth}
-                The function $F = f + g$ where $f:\RR^n \rightarrow \RR$ is an $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
-                The function $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function. 
-            \end{assumption}
-            \begin{assumption}[admitting minimizers]\label{ass:smooth-plus-nonsmooth-x}
-                Let $F = f + g$ satisfies \ref{ass:smooth-plus-nonsmooth} and in addition assume that the set of minimizers $X^+ := \argmin_{x}F(x)$ is non-empty. 
-            \end{assumption}
-            \begin{assumption}[affine composite Semi-CNVX remative smooth plus non-smooth]\label{ass:snorm-smth-p-nsmth}
-                Let $A \in \RR^{m\times n}, b \in \RR^n$
-                Let $F(x): \RR^{m} \mapsto \overline\RR := x \mapsto f(x) + g(x)$. 
-                Assume that: 
-                \begin{enumerate}[noitemsep]
-                    \item $f:\RR^m \rightarrow \RR := x \mapsto h(Ax - b)$ where $h:\RR^n\rightarrow \RR$ is $L$ Lipschitz smooth and, $\mu\ge 0$ strongly convex, then it satisfies Theorem \ref{thm:aff-smooth-sq-scnvx} with $L > \mu \ge 0$ and $A \in \RR^{m \times n}$.
-                    \item $g:\RR^m \mapsto \overline \RR$ is a convex, proper and closed function. 
-                \end{enumerate}
-            \end{assumption}
-            % --------------------------------------------------------------------------------------------------------------
-            \begin{theorem}[proximal gradient inequality]\label{thm:pg-ineq}
-                Let function $F$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}, so it's $\mu \ge 0$ strongly convex. 
-                For any $x\in \RR^n$, define $x^+ = T_L(x)$. 
-                Then, there exists a $B \ge 0$ such that $D_f(x^+, x) \le B/2 \Vert x^+ - x\Vert^2$ and, for all $z \in \RR^n$ it satisfies the inequality: 
-                \begin{align*}
-                    0&\le F(z) - F(x^+) - \frac{B}{2}\Vert z - x^+\Vert^2  + \frac{B - \mu}{2}\Vert z - x\Vert^2
-                    \\
-                    &=  F(z) - F(x^+) - \langle B(x - x^+), z - x\rangle
-                    - \frac{\mu}{2}\Vert z - x\Vert^2
-                    - \frac{B}{2}\Vert x - x^+\Vert^2. 
-                \end{align*}
-                Since $f$ is assumed to be $L$ Lipschitz smooth, the above condition is true for all $x, y \in \RR^n$ for all $B \ge L$. 
-            \end{theorem}
-            \begin{remark}
-                The theorem is the same as in Nesterov's book \cite[Theorem 2.2.13]{nesterov_lectures_2018}, but with the use of proximal gradient mapping and proximal gradient instead of project gradient hence making it equivalent to the theorem in Beck's book \cite[Theorem 10.16]{beck_first-order_2017}.
-                The only generalization here is parameter $B$ which made to accommodate algorithm that implements Definition \ref{def:snapg-v2} with line search routine to determine $L_k$. 
-                Each of the reference books gives a proof of the theorem. 
-                But for the best consistency in notations, see Theorem 2.3 in Li and Wang \cite{li_relaxed_2025}. 
-            \end{remark}
-            The following theorem attempts to generalize Theorem \ref{thm:pg-ineq}. 
-            % --------------------------------------------------------------------------------------------------------------
-            \begin{theorem}[proximal gradient inequality with semi-scnvx \textcolor{red}{NEW}]\label{thm:pg-ineq-semi-scnvx}
-                Suppose that $F:\RR^m \rightarrow \overline \RR := x \mapsto f(x) + g(x)$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth} with $L > \mu \ge 0$ and $A \in \RR^{m\times n}$. 
-                For any $x \in \RR^n$, let $x^+ = T_B(x | F)$. 
-                Let $\sigma_{\min}(A)$ denotes the minimum non-zero singular value of $A$ in absolute value. 
-                Let $\Pi = \Pi_{\ker A}$ be the linear operator that project onto the kernel of $A$. 
-                Then, there exists some $B \ge 0$ such that $D_f(x^+, x) \le \frac{B}{2}\Vert x - x^+\Vert^2$ and, for all $z \in \RR^m$ it satisfies the inequality: 
-                \begin{align*}
-                    0 &\le F(z) - F(x^+) 
-                    - \frac{\mu}{2}\Vert Az - Ax\Vert^2 
-                    + \frac{B}{2}\Vert z - x\Vert^2
-                    - \frac{B}{2}\Vert z - x^+\Vert^2
-                    \\
-                    &\le F(z) - F(x^+)
-                    - \frac{B}{2}\Vert z - x^+\Vert^2 
-                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x) \Vert^2
-                        \\ &\quad 
-                        + \frac{B}{2}\Vert \Pi(z - x)\Vert^2. 
-                \end{align*}
-            \end{theorem}
-            \begin{proof}
-                Firstly, such a $B > 0$ exists, for example $B = L\Vert A\Vert^2$ would be an option because from Definition \ref{def:seminorm-smooth-scnvx}, it for all $x, y$, $D_f(x, y) \le L/2\Vert Ax - Ay \Vert^2 \le L/2\Vert A\Vert^2\Vert x - y\Vert^2$.
-                But it can be much smaller. 
-                \par
-                The function $z \mapsto g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2$ inside the proximal gradient operator has the minimizer $x^+$.  
-                This function is also the sum of a convex, proper closed function $g$ and, a simple quadratic and, it's $B > 0$ strongly convex hence, it satisfies the quadratic growth conditions over its minimizer $x^+ = T_B(x|F)$ so, it follows that for all $z \in \RR^m$:
+            At (b) we used the Cauchy Inequality and, the assumption $\Vert w\Vert \le \epsilon \Vert x - \tilde x\Vert$. 
+            Continuing it has 
             \begin{align*}
                 0 &\le 
-                    -\frac{B}{2}\Vert z - x^+\Vert^2 
-                    + g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
+                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2
+                + \epsilon \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert 
+                - \frac{B}{2}\Vert z - \tilde x\Vert^2
                     \\&\quad 
-                        - g(x^+) - f(x) - \langle \nabla f(x), x^+ - x\rangle - \frac{B}{2}\Vert x^+ - x\Vert^2
+                    - \frac{\epsilon}{2}\Vert x - \tilde x\Vert^2 - \frac{\epsilon}{2}\Vert z - \tilde x \Vert^2
+                    + \frac{\epsilon}{2}\Vert x - \tilde x\Vert^2 + \frac{\epsilon}{2}\Vert z - \tilde x \Vert^2
                 \\
-                    &= 
-                    -\frac{B}{2}\Vert z - x^+\Vert^2 
-                    + \left(g(z) + f(z) - f(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2\right)
-                        \\&\quad 
-                        +\left(- g(x^+) - f(x^+) + f(x^+) - f(x) - \langle \nabla f(x), x^+ - x\rangle - \frac{B}{2}\Vert x^+ - x\Vert^2\right)
+                &= F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2
+                - \frac{1}{2}\left(
+                    \sqrt{\epsilon}\Vert z - \tilde x\Vert - \sqrt{\epsilon}\Vert x - \tilde x\Vert
+                \right)^2
+                - \frac{B}{2}\Vert z - \tilde x\Vert^2
                     \\
-                    &=
-                    -\frac{B}{2}\Vert z - x^+\Vert^2 
-                    + \left(F(z) - D_f(z, x) + \frac{B}{2}\Vert z - x\Vert^2\right)
-                        \\&\quad
-                        + \left(- F(x^+) + D_f(x^+, x) - \frac{B}{2}\Vert x^+ - x\Vert^2\right)
+                    &\quad 
+                    + \frac{\epsilon}{2}\Vert x - \tilde x\Vert^2 + \frac{\epsilon}{2}\Vert z - \tilde x \Vert^2
                 \\
-                    &\underset{\text{(a)}}{\le }
-                    -\frac{B}{2}\Vert z - x^+\Vert^2 
-                    + \left(F(z) - D_f(z, x) + \frac{B}{2}\Vert z - x\Vert^2\right)
-                    - F(x^+)
-                    \\
-                    &\underset{\text{(b)}}{\le} 
-                    - \frac{B}{2}\Vert z - x^+\Vert^2 
-                    + F(z) - \frac{\mu}{2}\Vert Az - Ax\Vert^2 
-                    + \frac{B}{2}\Vert z - x\Vert^2
-                    - F(x^+)
-                    \\
-                    &= F(z) - F(x^+) 
-                    - \frac{\mu}{2}\Vert Az - Ax\Vert^2 
-                    + \frac{B}{2}\Vert z - x\Vert^2
-                    - \frac{B}{2}\Vert z - x^+\Vert^2. 
-                \end{align*}
-                At (a), we used the fact that line search asserted the condition $D_f(x^+, x) \le \frac{B}{2}\Vert x^+ - x\Vert^2$. 
-                At (b) we applied results from Theorem \ref{thm:aff-smooth-sq-scnvx}. 
-                Continuing it further with the results from \ref{thm:aff-smooth-sq-scnvx} it adds another inequality: 
-                \begin{align*}
-                    0&\le  F(z) - F(x^+) 
-                    - \frac{\mu}{2}\Vert Az - Ax\Vert^2 
-                    + \frac{B}{2}\Vert z - x\Vert^2
-                    - \frac{B}{2}\Vert z - x^+\Vert^2
-                    \\
-                    &\le F(z) - F(x^+) 
-                    - \frac{\sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x)\Vert^2
-                    + \frac{B}{2}\Vert z - x\Vert^2
-                    - \frac{B}{2}\Vert z - x^+\Vert^2
-                    \\
-                    &= F(z) - F(x^+) 
-                    - \frac{\sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x)\Vert^2
-                        \\ &\quad
-                        + \frac{B}{2}\Vert \Pi(z - x)\Vert^2
-                        + \frac{B}{2}\Vert (I - \Pi)(z - x)\Vert^2
-                        - \frac{B}{2}\Vert z - x^+\Vert^2
-                    \\
-                    &= F(z) - F(x^+) 
-                    - \frac{B}{2}\Vert z - x^+\Vert^2
-                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x)\Vert^2
-                    + \frac{B}{2}\Vert \Pi(z - x)\Vert^2. 
+                &= F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2
+                - \frac{B - \epsilon}{2}\Vert z - \tilde x\Vert^2
+                + \frac{\epsilon}{2}\Vert x - \tilde x \Vert^2. 
             \end{align*}
@@
         \begin{remark}
-                When $\ker A = \{\mathbf 0\}$, this theorem is equivalent to Theorem \ref{thm:pg-ineq} but with $\mu$ being $\sigma_{\min}(A)$ instead. 
+            Usually in practice, the precise value of $F(\tilde x)$ is never known, therefore, $B$ cannot be easily determined via $D_f(\tilde x, x)$. 
+            Hence, in this case we can only choose $B \ge L$ which gives: 
+            \begin{align*}
+                F(z) - F(\tilde x) + \frac{L - \mu}{2}\Vert z - x\Vert^2
+                - \frac{B - \epsilon}{2}\Vert z - \tilde x\Vert^2
+                + \frac{\epsilon}{2}\Vert x - \tilde x \Vert^2.
+            \end{align*}
         \end{remark}
-            The following theorem attempts to generalize Theorem \ref{thm:semi-scnvx-equiv} for relatively smooth plus non-smooth function. 
-            % --------------------------------------------------------------------------------------------------------------
-            \begin{theorem}[seminorm smooth plus non-smooth Jensen \textcolor{red}{NEW}]\label{thm:smnrm-jnsn-smth-nsmth}
-                Suppose that $F:\RR^m \rightarrow \overline \RR := x \mapsto f(x) + g(x)$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth} with $L > \mu \ge 0$ and $A \in \RR^{m\times n}$.
-                Let $\Pi = \Pi_{\ker A}$ be the projection onto the kernel of $A$. 
-                Let $\sigma_{\min}(A)$ denote the smallest non-zero singular value of $A$ in absolute value. 
-                Then, for all $x, y \in \RR^m$ and, $\lambda \in [0, 1]$ it satisfies the inequality: 
+        Note, an inexact evaluation of the proximal gradient operator can be caused by an inexact gradient on the smooth part. 
+        Suppose that one take $\tilde \nabla f(x)$ to be an estimate of $\nabla f(x)$ and use it for the proximal gradient operator to produce $\tilde x$, then: 
         \begin{align*}
-                    F(\lambda z + (1 - \lambda)y) &\le \lambda F(z) + (1 - \lambda)F(x) - \frac{\sigma_{\min}(A)^2\lambda(1 - \lambda)\mu}{2}\Vert (I - \Pi)(x - y)\Vert^2. 
+            \mathbf 0 
+            &\in \partial g(\tilde x) + \tilde \nabla f(x) + B(\tilde x - x)
+            \\
+            &= 
+            \partial g(\tilde x) + \tilde\nabla f(x) - \nabla f(x) 
+            + \nabla f(x) + B(\tilde x - x)
+            \\
+            \iff &
+            \nabla f(x) - \tilde \nabla f(x) \in 
+            \partial g(\tilde x) 
+            + \nabla f(x) + B(\tilde x - x).
         \end{align*}
-            \end{theorem}
-            \begin{proof}
-                $f$ satisfies Definition \ref{def:seminorm-smooth-scnvx} with $L > \mu, A$, so for all $x, y \in \RR^m$ it has 
+        In this case, it adds the interpretation that $w = \nabla f(x) - \tilde \nabla f(x)$. 
+        It fully characterizes the error made to estimate the true gradient $\nabla f(x)$.
+
+\section{Inexact accelerated proximal gradient algorithm}
+    The following defines the inexact proximal gradient operator where the gradient of the smooth part of the function is estimated. 
+    All algorithms satisfying the following definition will be referred to as Stochastic Nesterov's Accelerated Gradient (SNAG). 
+    % ------------------------------------------------------------------------------------------------------------------
+    \begin{definition}[inexact proximal gradient operator with relative error]
+        Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}, let $x \in \RR^n$ be fixed. 
+        Suppose that $\tilde \nabla f(x)$ is an estimate of the true gradient $\nabla f(x)$ with relative error $\epsilon \ge 0$. 
+        Then, the inexact proximal gradient operator is defined by: 
         \begin{align*}
-                    0 &\le D_f(x, y) - \frac{\mu}{2}\Vert Ax - Ay\Vert^2 
-                    \le \frac{L - \mu}{2}\Vert Ax - Ay\Vert^2. 
+            T_B^{(\epsilon)}(x | F) = \argmin_{z \in \RR^n}\left\lbrace
+                g(z) + \left\langle \tilde \nabla f(x), z - x\right\rangle
+                + \frac{B}{2}\Vert z - x\Vert^2
+            \right\rbrace. 
         \end{align*}
-                Using some algebra (or equivalent some properties of Bregman divergence), it shows that the function $f - \mu/2 \Vert A(\cdot)\Vert^2$ is a convex function, therefore, $f + g - \mu/2\Vert A(\cdot)\Vert^2 = F - \frac{\mu}{2}\Vert A(\cdot)\Vert^2 = F - \frac{1}{2}\Vert \sqrt{\mu}A(\cdot)\Vert^2$ is also a convex function.
-                Applying Theorem \ref{thm:semi-scnvx-equiv} it has for all $z, x \in \RR^m$ and, $\lambda \in [0, 1]$ the inequality: 
+        And it satisfies 
         \begin{align*}
-                    F(\lambda z + (1 - \lambda)y) &\le \lambda F(z) + (1 - \lambda)F(x) - \frac{\lambda(1 - \lambda)\mu}{2}\Vert Ax - Ay\Vert^2
-                    \\
-                    &\le 
-                    \lambda F(z) + (1 - \lambda)F(x) - \frac{\lambda(1 - \lambda)\mu\sigma_{\min}(A)^2}{2}\Vert (I - \Pi) x - y\Vert^2. 
+            \left\Vert \tilde \nabla f(x) - \nabla f(x)\right\Vert \le \epsilon \Vert x - \tilde x\Vert. 
         \end{align*}
-                The second inequality uses Theorem \ref{thm:aff-smooth-sq-scnvx}. 
-            \end{proof}
+    \end{definition}
+    The inexact evaluation can be caused by an random variable. 
+    The definitions follow characterize algorithm in which the errors are related to a random variable that estimates the gradient of the objective function. 
+    % ------------------------------------------------------------------------------------------------------------------
+    \begin{definition}[stochastic proximal gradient operator with relative error]
 
-\section{Stochastic accelerated proximal gradient}
-    First, this is an overview of this section.
-
-    \begin{assumption}[sum of many affine composite]\label{ass:sum-of-many-aff-comp}
-        Let $A^{(1)}, A^{(2)}, \ldots A^{(n)}$ be a list of $\RR^{m\times n}$ matrices and, $b^{(1)}, b^{(2)}, \ldots, b^{(n)}$ be a list of vectors in $\RR^n$. 
-        Suppose $F:\RR^m \rightarrow \overline \RR:= \frac{1}{n}\sum_{i = 1}^{n} F_i(x)$, so it admits representations 
+    \end{definition}
+    % ------------------------------------------------------------------------------------------------------------------
+    \begin{definition}[inexact/stochastic SNAG]\label{def:SNAG}
+        Suppose that $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
+        Let $(\alpha_k)_{k \ge 0}$ be a sequence such that $\alpha_k \in (0, 1]$. 
+        Let $(\epsilon_k)_{k \ge 0}$ be a sequence of errors. 
+        Given initial conditions $v_{-1}, x_{- 1}$. 
+        An algorithm satisfying the SNAG definition if it generates a sequence $(y_k, x_k, v_k)_{k \ge 0}$ if for all $k \ge 0$, the following conditions are satisfied: 
         \begin{align*}
-            F(x) = f(x) + g(x) = \frac{1}{n}\sum_{i = 1}^{n} f_i(x) + g_i(x) = \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)}x - b^{(i)}) + g_i(x)
-        \end{align*}
-        Where, each $F_i = f_i + g_i$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth} with $K^{(i)} > \nu^{(i)} \ge 0, b^{(i)} \in \RR^n$ and $A^{(i)} \in \RR^{m \times n}$. 
-        So, each $h_i$ are $\nu^{(i)}$ strongly convex and $K^{(i)}$ Lipschitz smooth. 
-        \par
-        Take note that the function $f(x) = \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)})$ is the composition of the strongly convex function $h = \frac{1}{n}\sum_{i = 1}^{n} h_i$ that is a $\RR^{mn}\rightarrow \RR$ mapping with strong convexity $\frac{1}{n}\sum_{i = 1}^{n} \nu^{(i)}$ and, the affine $\RR^m \rightarrow \RR^{mn}$ mapping $\mathcal A := x \mapsto (A^{(1)}x - b^{(1)},\ldots,  A^{(n)}x - b^{(n)})$.
-        $f$ satisifes Theorem \ref{thm:aff-smooth-sq-scnvx} and it can be written as: 
-        \begin{align*}
-            f(x) = \sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)}) = h(\mathcal A x). 
-        \end{align*}
-    \end{assumption}
-
-    \begin{assumption}[sum of many]\label{ass:sum-of-many}
-        Define $F := (1/n)\sum_{i = 1}^{n} F_i$ where each $F_i = f_i + g_i$, so it can be written as: 
-        \begin{align*}
-            F(x) = f(x) + g(x) = \frac{1}{n}\sum_{i = 1}^{n} f_i(x) + g_i(x)
-        \end{align*}
-        Assume that for all $i = 1, \ldots, n$, each $f_i:\RR^n \rightarrow \RR$ are $K^{(i)}$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K^{(i)} > \mu^{(i)}$ and, $g_i:\RR^n \rightarrow \overline \RR$ is a closed convex proper function satisfies Assumption \ref{ass:smooth-plus-nonsmooth}.
-        \par 
-        Take note that, the function $f$ can be written as $F = g + f$ with $f = (1/n)\sum_{i = 1}^{n} f_i, g = (1/n)\sum_{i = 1}^{n}g_i$ therefore, it also satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = (1/n)\sum_{i = 1}^n K^{(i)}$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$.
-    \end{assumption}
-    Both assumptions are equivalent, functions satisfies one can be translated in form so it satisfies the other with some extra/fewer parameters. 
-    However, it's important to know that for a $F := \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)}) + g_i(x)$ satisfying Assumption \ref{ass:sum-of-many-aff-comp}, Theorem \ref{thm:pg-ineq-semi-scnvx}, \ref{thm:smnrm-jnsn-smth-nsmth} applies with parameter $\nu^{(i)}\sigma_{\min}(A^{(i)})^2$ for each summees.
-    This can't be known if it only satisfies Assumption \ref{ass:sum-of-many}. 
-    \par
-    The interpolation hypothesis from Machine Learning stated that the model has the capacity to perfect fit all the observed data. 
-    The following assumption state the interpolation hypothesis in our context. 
-    \begin{assumption}[interpolation hypothesis]\label{ass:interp-hypothesis}
-        Suppose that $F := (1/n)\sum_{i = 1}^{n} F_i$ satisfying Assumption \ref{ass:sum-of-many}. 
-        In addition, assuming that it has $0 = \inf_{x}F(x)$ and, there exists some $\bar x \in \RR^n$ such that for all $i = 1, \ldots, n$ it satisfies $0 = f_i(\bar x)$. 
-        \par
-        Consequently, each of the $F_i$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth-x} with $X_i$ being the set of minimizers and, under interpolation hypothesis this equates to non-empty intersections between all $X_i$, i.e: $\bigcap_{i = 1}^n X_i \neq \emptyset$.
-    \end{assumption}
-
-    Due to the fact the algorithms have to be very different support convergence claim for different assumptions on the functions, the following definition gives a generic ideas for all algorithms that specializes on top of it for different assumptions placed on the objective functions.
-    These definitions are not actual algorithms, they are conditions an algorithm must adhere to for the theorems based on it to be valid. 
-    Read then as specifications. 
-    % --------------------------------------------------------------------------------------------------------------
-    \begin{definition}[SNAPG-V2 prototype \textcolor{red}{NEW}]\;\label{def:snapg-v2-proto}\\
-        Let 
-        \begin{enumerate}[nosep]
-            \item $F$ satisfies Assumption \ref{ass:sum-of-many}, 
-            \item $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$, 
-            \item $\sigma^{(k)}$ be another list of i.i.d random variable. 
-            \item $\tilde \mu \ge 0$ be a constant that is fixed.
-            \item Let $(L_k)_{k \ge 0}$ a sequence of strictly positive numbers. 
-        \end{enumerate}
-        Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
-        The SNAPG prototype specifies algorithm that generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
-        \begin{align*}
-            & \alpha_k \in (0, 1): (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \tilde \mu/L_k\right), \\
             & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \sigma^{(k)}\right)^{-1}, \\
             & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
-            & L_k > 0: D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
-            & x_k =  T_{L_k}(y_k | F_{I_k}), \\
+            & x_k =  T_{L}^{(\epsilon_k)}(y_k | F_{I_k}), \\
             & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}).
@@
     \end{definition}
-    \begin{remark}
-        $\tilde \mu_k, L_k$ are not necessary a random variable because they are determined by a line-search like conditions, consequently $(\alpha_k)_{k\ge 0}$, whether they are a random variable depends on the line search procedures.
-        Otherwise, all the iterates $(x_k, y_k, z_k)$ are random variable determined by $I_k$ when conditioned on all previous $I_{k - 1}, I_{k - 2}, \ldots, I_{0}$. 
-        \par
-        \textcolor{red}{NEW}. One may notice that $\alpha_k$ requires $L_k$ which comes before $L_k, x_k$ which are needed in advanced for $\alpha_k$. 
-        This may seem off since no algorithm can know what $L_k$ to choose in advanced to determine the line search. 
-        But, it is important to note that in here, we defined a sequence of conditions on the iterates $x_k, y_k, z_k$, and auxiliary sequences $\alpha_k, L_k$ which is not a definition of any algorithm.
-        It is quantifying the conditions needed for an algorithm that actually implements it.
-        \par
-        For the trivial case where we don't need to worry about it is when $L_k = \max_{i = 1, \ldots, n} K^{(i)}$. 
-        See Chambolle, Calatroni \cite{calatroni_backtracking_2019} for an implementation of linear search with backtracking for the FISTA algorithm, it is how one would implement it in the deterministic case.
-    \end{remark}
-    % --------------------------------------------------------------------------------------------------------------
-    \begin{definition}[SNAPG-V2 affine \textcolor{red}{NEW}]\label{def:snapg-v2-aff}
-        Let $F, (I_k)_{k \ge 0}, \tilde \mu$ and, $(L_k)_{k \ge 0}$ be given as in Definition \ref{def:snapg-v2-proto}. 
-        But in addition, assume that: 
-        \begin{enumerate}[nosep]
-            \item $F$ also satisfies Assumption \ref{ass:sum-of-many-aff-comp} with $\RR^{m \times n}$ matrices: $A^{(1)}, A^{(2)}, \ldots, A^{(n)}$, vectors in $\RR^n$: $(b^{(1)}, \ldots, b^{(n)})$. 
-            \item Choose $\sigma^{(k)} = \nu^{(I_k)}\sigma_{\min}(A^{(I_k)})^2$. 
-        \end{enumerate}
-        Then, SNAPG-V2 affine specifies algorithms that generate the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfying conditions as specified in Definition \ref{def:snapg-v2-proto} with the above parameters.
-    \end{definition}
-    % --------------------------------------------------------------------------------------------------------------
-    \begin{definition}[SNAPG-V2 vanilla]\label{def:snapg-v2}
-        Let $F, (I_k)_{k \ge 0}, \tilde \mu$ and, $(L_k)_{k \ge 0}$ be given as in Definition \ref{def:snapg-v2-proto}. 
-        But in addition, assume that: 
-        \begin{enumerate}[nosep]
-            \item Choose $\sigma^{(k)} = \mu^{(I_k)}$. 
-        \end{enumerate}
-        Then, SNAPG-V2 vanilla affine specifies algorithms that generate the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfying conditions as specified in Definition \ref{def:snapg-v2-proto} with the above parameters.
-    \end{definition}
-    % --------------------------------------------------------------------------------------------------------------
-    What is the weakest possible sequence one can use for the accelerated proximal gradient based algorithm that utilizes a strong convexity constant? 
-    If we were to use the developed convergence framework for Nesterov's accelerated proximal gradient, negative momentum and, negative convergence (lower bound instead of upper bound) should be prohibited, and it means that the sequence $(\alpha_k)_{k \ge 0}$ which is going to appear in the proposed algorithm (See Definition \ref{def:snapg-v2}) must satisfy the condition $\alpha_k \in (0, 1]$ for all $k \ge 0$.
-    The following lemma with a blunt name should clarify the sufficient conditions required for the sequence to make sense. 
-    \begin{lemma}[weakest possible momentum sequence that makes sense \textcolor{red}{NEW}]\;\label{lemma:snapg-v2-seq-range}\\
-        Suppose that $(L_k)_{k \ge 0}$ is a sequence such that $L_k > 0$ for all $k \ge 0$. 
-        Suppose that $(\tilde\mu_k)_{k\ge 0}$ is another non-negative sequence. 
-        Let $(\alpha_k)_{k \ge 0}$ be a sequence such that $\alpha_0 \in (0, 1]$ and, for all $k \ge 1$, it satisfies recursively the equality: 
-        \begin{align*}
-            (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 
-            &= \alpha_{k}\left(\alpha_{k} - \tilde \mu_k/L_k\right). 
-        \end{align*}
-        And, the following items are true: 
-        \begin{enumerate}
-            \item The expression of $\alpha_k$ based on previous $\alpha_{k - 1}$ is given by: 
-            \begin{align*}
-                \alpha_k = \frac{L_{k - 1}}{2L_k} \left(
-                    - \alpha_{k - 1}^2 + \frac{\tilde\mu_k}{L_{k - 1}}
-                    + \sqrt{
-                        \left(
-                            \alpha_{k - 1} - \frac{\tilde\mu_k}{L_{k - 1}}
-                        \right)^2
-                        + \frac{4\alpha_{k - 1}^2L_k}{L_{k - 1}}
-                    }
-                \right) &\ge 0. 
-            \end{align*}
-            \item If, in addition, the sequence $\tilde \mu_k$ satisfies for all $k \ge 1$, $\frac{\tilde \mu_k}{L_{k - 1}} < L_{k - 1}/ L_k$, then the sequence strictly less than one and, for all $k \ge 1$: $\alpha_k \in (0, 1)$.
-        \end{enumerate}
+    The following lemma states two important relationships on the iterates generated by Definition \ref{def:SNAG}. 
+    \begin{lemma}[SNAG identities]\label{lemma:snag-identities}
+
     \end{lemma}
-    \begin{proof}
-        For all $k \ge 1$, re-arranging the equality it comes to solving the following equality: 
-        \begin{align*}
-            0 &= L_k\alpha_k^2 - \tilde\mu_k\alpha_k + L_{k - 1}\alpha_{k - 1}^2\alpha_k - L_{k - 1}\alpha_{k - 1}^2
-            \\
-            &= L_k\alpha_k^2 + (L_{k - 1}\alpha_{k - 1}^2 - \tilde \mu_k)\alpha_k - L_{k - 1}\alpha_{k - 1}^2
-            \\
-            \iff 0 &=
-            \alpha_k^2 + L_k^{-1}(L_{k - 1}\alpha_{k - 1}^2 - \tilde \mu_k)\alpha_k - L_k^{-1}L_{k - 1}\alpha_{k - 1}^2
-            \\
-            \iff 
-            \alpha_k &= 
-            \frac{1}{2}\left(
-                -L^{-1}_k(L_{k - 1} \alpha_{k - 1}^2 - \tilde\mu_k)
-                + \sqrt{
-                    L_k^{-2}(L_{k - 1}\alpha_{k - 1}^2 - \tilde \mu_k)^2
-                    + 4L_k^{-1}L_{k - 1} \alpha_{k - 1}^2
-                }
-            \right)
-            \\
-            &= \frac{L_{k-1}}{2L_k}\left(
-                - \alpha_{k - 1}^2 + \frac{\tilde \mu_k}{L_{k - 1}}
-                + \sqrt{
-                    \left(
-                        \alpha_{k - 1}^2 - \frac{\tilde \mu_k}{L_{k - 1}}
-                    \right)^2 + \frac{4L_k}{L_{k - 1}}\alpha_{k - 1}^2
-                }
-            \right)
-        \end{align*}
-        Here, we take the positive root of the quadratic so that it ensures $\alpha_k \ge 0$. 
-        This is true by induction. 
-        If $\alpha_{k - 1} \ge 0$ then the $\frac{4L_k}{L_{k - 1}}\alpha_{k - 1}^2 \ge 0$ hence, the square root is greater than the term outside it so, $\alpha_k \ge 0$ too. 
-        \par
-        Assume inductively that $\alpha_{k - 1} \ge 0$. 
-        Next, we want to find the conditions needed such that $\alpha_k < 1$. 
-        To start, we complete the square root inside the square root: 
-        \begin{align*}
-            0&\le 
-            \left(
-                \alpha_{k - 1}^2 - \frac{\tilde \mu_k}{L_{k - 1}}
-            \right)^2 + \frac{4L_k}{L_{k - 1}}\alpha_{k - 1}^2
-            \\
-            &= \alpha_{k - 1}^4 + \left(\frac{\tilde \mu_k}{L_{k - 1}}\right)^2
-            - 2\alpha_{k - 1}^2 \frac{\tilde \mu_k}{L_{k - 1}} 
-            + \frac{4L_k}{L_{k - 1}}\alpha_{k - 1}^2
-            \\
-            &= \alpha_{k - 1}^4 + \left(\frac{\tilde \mu_k}{L_{k - 1}}\right)^2
-            + \alpha_{k - 1}^2 \left(
-                \frac{-2\tilde \mu_k}{L_{k - 1}} + \frac{4L_k}{L_{k - 1}}. 
-            \right)
-            \\
-            &= \alpha_{k - 1}^4 + \left(\frac{\tilde \mu_k}{L_{k - 1}}\right)^2
-            + \alpha_{k - 1}^2 \left(
-                \frac{4L_k - 2\tilde \mu_k}{L_{k - 1}}
-            \right)
-            \\
-            &= \alpha_{k - 1}^4
-            + \alpha_{k - 1}^2 \left(
-                \frac{4L_k - 2\tilde \mu_k}{L_{k - 1}}
-            \right) 
-            + \left(
-                \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
-            \right)^2
-            - \left(
-                \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
-            \right)^2
-            + \left(\frac{\tilde \mu_k}{L_{k - 1}}\right)^2
-            \\
-            &= \left(
-                \alpha_{k - 1}^2 + 
-                \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
-            \right)^2
-            - \left(
-                \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
-            \right)^2
-            + \left(\frac{\tilde \mu_k}{L_{k - 1}}\right)^2
-            \\
-            &= 
-            \left(
-                \alpha_{k - 1}^2 + 
-                \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
-            \right)^2
-            + 
-            \frac{
-                \tilde \mu_k^2 - 4L_k^2 - \tilde \mu_k^2 + 4L_k\tilde \mu_k
-            }{L_{k - 1}^2}
-            \\
-            &= 
-            \left(
-                \alpha_{k - 1}^2 + 
-                \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
-            \right)^2
-            + 
-            \frac{
-                4L_k \tilde \mu_k - 4L_k^2
-            }{L_{k - 1}^2}
-            \\
-            &= 
-            \left(
-                \alpha_{k - 1}^2 + 
-                \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
-            \right)^2
-            + 
-            4\left(
-                \frac{L_k}{L_{k - 1}}\cdot \frac{\tilde \mu_k}{L_{k - 1}} - 1
-            \right)
-            \\
-            &< 
-            \left(
-                \alpha_{k - 1}^2 + 
-                \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
-            \right)^2. 
-        \end{align*}
-        On the last inequality, we used our assumption that the sequence $\tilde\mu_k, L_k$ satisfies $\frac{\tilde \mu_k}{L_{k - 1}} < \frac{L_{k - 1}}{L_k}$. 
-        Substitute it back into the expression previous obtained for $\alpha_k$, using the monotone property of the function $\sqrt{\cdot}$, it gives the inequality 
-        \begin{align*}
-            \alpha_k & < 
-            \frac{L_{k-1}}{2L_k}\left(
-                - \alpha_{k - 1}^2 + \frac{\tilde \mu_k}{L_{k - 1}}
-                + \sqrt{
-                    \left(
-                        \alpha_{k - 1}^2 + 
-                        \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
-                    \right)^2
-                }
-            \right)
-            \\
-            &= 
-            \frac{L_{k-1}}{2L_k}\left(
-                - \alpha_{k - 1}^2 + \frac{\tilde \mu_k}{L_{k - 1}}
-                + \alpha_{k - 1}^2 + \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
-            \right) = 1. 
-        \end{align*}
-    \end{proof}
-    \begin{remark}
-        Let's do some sanity check for the lemma we just derived. 
-        The sequence $L_k$ will be from the Lipschitz line search routine of the accelerated proximal gradient method. 
-        \begin{enumerate}
-            \item Let's assume the obvious choice of $L_k = \max_{i = 1, \ldots,n} K^{(i)}$ for all $k = 1, 2, \ldots$ given an objective function $F$ satisfying Assumption \ref{ass:sum-of-many}. 
-            Then, the sufficient condition for the second item translates to $\tilde\mu_i/L_k < 1$. 
-            Hence, if we choose $\tilde \mu_i$ to be a constant sequence of $0$ then it works out to have $\alpha_k \in (0, 1)$ for all $k = 1, 2, \ldots$. 
-            \par
-            If $F$ has $L \ge \mu$ so, the function is non-trivial, then choose $\tilde \mu_i = \mu$, the true strong convexity parameter then it also works out. 
-            \item Let's assume that some type of monotone line search routine is used for the algorithm making $L_0 \le L_1 \le \ldots \le L_k \le \ldots$ to be a non-decreasing sequence, then it requires $\tilde \mu_k / L_{k - 1} \le L_{k - 1}/L_k$.
-            \par
-            Well, it will still make sense because one such choice could be $\tilde \mu_k = \rho\min_{i = 1, \ldots, k} L_{i - 1}/L_i$ for some $\rho \in (0, 1)$. 
-        \end{enumerate}
-    \end{remark}
-    % --------------------------------------------------------------------------------------------------------------
-    \begin{lemma}[properties of the iterates on SNAPG-V2 prototype \textcolor{red}{NEW}]\label{lemma:iters-snapg2-proto}
-        Suppose that the iterates $(z_k, x_k, y_k)_{k \ge 0}$ and sequence $(\alpha_k)_{k \ge 1}$ satisfies Definition \ref{def:snapg-v2-proto}. 
-        Let $\bar x \in \RR^n$.
-        Define the sequence $z_k = \alpha_k\bar x + (1 - \alpha_k)x_{k - 1}$. 
-        Then, the following are true: 
-        \begin{enumerate}
-            \item\label{lemma:iters-snapg2-proto-item1} For all $k \ge 1$ it has: 
-            \begin{align*}
-                    z_k - y_k 
-                    = 
-                    \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
-                    + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}(\bar x - x_{k - 1}).
-            \end{align*}
-            \item\label{lemma:iters-snapg2-proto-item2} For all $k \ge 1$, it has: $z_k - x_k = \alpha_k(x - \bar x)$
-        \end{enumerate}
-    \end{lemma}
-    \begin{proof}
-        \textbf{Proof of \ref{lemma:snapg2-itrs-props-item1}}. 
-        From Definition \ref{def:snapg-v2-proto}:
-        \begin{align*}
-            (1 + \tau_k)^{-1}
-            &=
-            \left(
-                1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \sigma^{(i)}}
-            \right)^{-1} = \left(
-                \frac{L_k\alpha_k - \sigma^{(i)} + L_k(1 - \alpha_k)}{L_k\alpha_k - \sigma^{(i)}}
-            \right)^{-1}
-            = \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}. 
-        \end{align*}
-        Therefore, for all $k \ge 0$, $y_k$ has 
-        \begin{align*}
-            0 &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1} - y_k
-            \\
-            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} 
-            \left(
-                v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \sigma^{(i)}} x_{k - 1}
-            \right) - y_k
-            \\
-            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1}
-            + \frac{L_k(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1} - y_k
-            \\
-            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
-            + 
-            \left(
-                \frac{L_k(1 - \alpha_k)}{L_k - \sigma^{(i)}} - (1 - \alpha_k)
-            \right) x_{k - 1} - y_k
-            \\
-            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
-            + 
-            (1 - \alpha_k)\left(
-                \frac{L_k - L_k + \sigma^{(i)}}{L_k - \sigma^{(i)}}
-            \right) x_{k - 1} - y_k
-            \\
-            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
-            + 
-            \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}x_{k - 1} - y_k. 
-        \end{align*}
-        Therefore, we establish the equality 
-        \begin{align*}
-            (1 - \alpha_k)x_{k - 1} - y_k &= 
-            - \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1} 
-            - \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1}. 
-        \end{align*}
-        On the second equality below, we will the above equality, it goes: 
-        \begin{align*}
-            z_k - y_k &= 
-            \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
-            \\
-            &= \alpha_k \bar x 
-            - \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}} v_{k - 1} 
-            - \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1}
-            \\
-            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
-            + \left(
-                \alpha_k - \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}
-            \right)\bar x
-            - \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1}
-            \\
-            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
-            + \left(
-                \frac{\alpha_kL_k - \alpha_k \sigma^{(i)} - L_k\alpha_k + \sigma^{(i)}}{L_k - \sigma^{(i)}}
-            \right)\bar x
-            - \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1}
-            \\
-            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
-            + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}\bar x
-            - \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}} x_{k - 1}
-            \\
-            &= \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
-            + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}(\bar x - x_{k - 1}).
-        \end{align*}
-        \textbf{proof of \ref{lemma:snapg2-itrs-props-item2}.}
-        From Definition \ref{def:snapg-v2} it has directly: 
-        \begin{align*}
-            z_k - x_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
-            \\
-            &= \alpha_k \bar x + x_{k - 1} - x_k - \alpha_k x_{k - 1}
-            \\
-            &= \alpha_k(\bar x - \alpha_k^{-1}(x_k - x_{k - 1}) - x_{k - 1})
-            \\
-            &= \alpha_k (\bar x - v_k).
-        \end{align*}
-
-    \end{proof}
-    % --------------------------------------------------------------------------------------------------------------
-    \begin{lemma}[SNAPG-V2 one step convergence stage I \textcolor{red}{NEW}]\label{lemma:snagp2-one-step-s1-proto}
-        Suppose that the sequence $(y_k, x_k, v_k)$ satisfies Definition \ref{def:snapg-v2-aff}. 
-        Fix some $k \in \N, k \ge 1$, suppose that $I_k = i$.
-        Denote $\Pi^{(i)} = \Pi_{\ker A^{(i)}}$ to be the projection matrix onto the kernel of $A^{(i)}$. 
-        Then for all $\bar x \in \RR^m$, the iterates satisfies the inequality: 
-        \begin{align*}
-            &F_i(x_{k}) - F_i(\bar x) 
-            + \frac{L_k\alpha_k^2}{2} \left\Vert \left(I - \Pi^{(i)}\right)(\bar x - v_k)\right\Vert^2
-            \\
-            &\le 
-            (1 - \alpha_k)\left(
-                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}
-                \left\Vert \left(I - \Pi^{(i)}\right)(v_{k - 1} - \bar x)\right\Vert^2
-            \right)     
-            + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.
-        \end{align*}
-        And when $k = 0$, we have: 
-        \todoinline{HERE}
-    \end{lemma}
-    \begin{proof}
-        Let's suppose that $I_k = i$ and, for all $k \ge 0$. 
-        Let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ where $\bar x$ is a minimizer of $F$. 
-        The proof is long so, we use letters and subscript under relations such as $\underset{(\cdot)}{=}, \underset{(\cdot)}{\ge}$ to indicate which result is used going from the previous expression to the next.
-        We list the following intermediate results, (d)-(g) are proved at the end of the proof. 
-        \begin{itemize}
-            \item[(a)] We can use proximal gradient inequality from Theorem \ref{thm:pg-ineq-semi-scnvx} with $z = z_k, B = L_k, \Pi^{i} = \Pi_{\ker A^{(i)}}$ because Assumption \ref{ass:sum-of-many-aff-comp} has each $F_i = f_i + g_i$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth}.
-            \item[(b)] We can use seminorm Jensen's inequality of Theorem \ref{thm:smnrm-jnsn-smth-nsmth} with $z = z_k$ on $F_i$. 
-            \item[(c)] The sequence $(\alpha_k)_{k \ge 0}$ has $(L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right)$. 
-            \item[(d)] Prove in Lemma \ref{lemma:iters-snapg2-proto} \ref{lemma:iters-snapg2-proto-item1} we will the equality:
-            \begin{align*}
-                (\forall k \ge 1)\; 
-                z_k - y_k 
-                = 
-                \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
-                + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}(\bar x - x_{k - 1}).
-            \end{align*}
-            \item [(e)] From Lemma \ref{lemma:iters-snapg2-proto} \ref{lemma:iters-snapg2-proto-item2}, we use: $(\forall k \ge 1)\; z_k - x_k = \alpha_k (\bar x - v_k)$. 
-            \item [(f)] Using direct algebra, we have for all $k \ge 1$: 
-            \begin{align*}
-                \frac{\left(\mu^{(i)}\right)^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} 
-                - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
-                = \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
-                {2\left(L_k - \mu^{(i)}\right)}. 
-            \end{align*}
-            \item [(g)] Using (c), we have for all $k \ge 1$: 
-            \begin{align*}
-                \frac{\left(
-                    L_k\alpha_k - \sigma^{(i)}
-                \right)^2}{2(L_k - \sigma^{(i)})} 
-                -
-                \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} 
-                = 
-                \frac{
-                \left(L_k \alpha_k - \sigma^{(i)}\right)\sigma^{(i)}
-                \left(\alpha_k - 1\right)
-                }
-                {2(L_k - \sigma^{(i)})}
-                + \frac{\alpha_k(\tilde \mu_k - \sigma^{(i)})}{2}. 
-            \end{align*}
-        \end{itemize}
-        For all $k \ge 1$, starting with (a) we have: 
-        \begin{align}\label{ineq:snapg2-one-step-stage1-chain1}
-            \begin{split}
-                0 &\le F_i(z_k) - F_i(x_k) - 
-                \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-                + \frac{L_k - \nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\left\Vert (I - \Pi^{(i)}) (z_k - y_k)\right\Vert^2
-                    \\ &\quad 
-                    + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                \\
-                &\underset{\text{(b)}}{\le}
-                \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k)     
-                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-                + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                    \\&\quad 
-                    - \frac{\nu^{(i)}\sigma_{\min}(A^{(i)})^2\alpha_k(1 - \alpha_k)}{2}\Vert (I - \Pi^{(i)})(\bar x - x_{k - 1})\Vert^2
-                    \\&\quad
-                    + \frac{L_k - \nu^{(i)}\sigma_{\min}(A^{(i)})^2}{2}\Vert (I - \Pi^{(i)})(z_k - y_k)\Vert^2
-            \end{split}
-        \end{align}
-        \textbf{For simpler notations}, we use the following notation $\Vert x\Vert_p = \Vert (I - \Pi^{(i)})x\Vert$ to denote a seminorm induced by the linear mapping $(I - \Pi^{(i)})$, and use $\langle \cdot,\cdot\rangle_p := \langle (I - \Pi^{(i)})(\cdot), \langle (I - \Pi^{(i)})(\cdot)\rangle$ for the inner product as well.
-        We also use $\sigma^{(i)} = \nu^{(i)}\sigma_{\min}(A^{(i)})^2$ which is specified in Definition \ref{def:snapg-v2-aff}. 
-        And we will simplify the last two terms from the above inequality using a chain of equalities. 
-        {\allowdisplaybreaks
-        \begin{align*}
-            & - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_p
-            + \frac{L_k - \sigma^{(i)}}{2}\Vert z_k - y_k\Vert^2_p
-            \\
-            &\underset{\text{(d)}}{=}
-            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_p
-                \\&\quad
-                + \frac{L_k - \sigma^{(i)}}{2}
-                \left\Vert
-                    \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}(\bar x - v_{k - 1})
-                    + \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}(\bar x - x_{k - 1})
-                \right\Vert^2_p
-            \\
-            &= 
-            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2_p 
-                \\&\quad
-                + \frac{(L_k\alpha_k - \sigma^{(i)})^2}{2(L_k - \sigma^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2_p
-                + \frac{(\sigma^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \sigma^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2_p 
-                \\&\quad 
-                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p
-            \\
-            &= 
-            \left(
-                \frac{(\sigma^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \sigma^{(i)})} - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}
-            \right)\Vert \bar x - x_{k - 1}\Vert^2_p
-                \\ &\quad 
-                + \left(
-                    \frac{(L_k\alpha_k - \sigma^{(i)})^2}{2(L_k - \sigma^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
-                \right) \Vert \bar x - v_{k - 1}\Vert^2_p
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-                \\&\quad 
-                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p
-            \\
-            &\underset{\text{(f)}}{=}
-            \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}
-            {2\left(L_k - \sigma^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2_p
-                \\ &\quad 
-                + \left(
-                    \frac{(L_k\alpha_k - \sigma^{(i)})^2}{2(L_k - \sigma^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
-                \right) \Vert \bar x - v_{k - 1}\Vert^2_p
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-                \\&\quad 
-                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p
-            \\
-            & \underset{\text{(g)}}{=} 
-            \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}
-            {2\left(L_k - \sigma^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2_p
-                \\ &\quad 
-                + \left(
-                    \frac{
-                        \left(L_k \alpha_k - \sigma^{(i)}\right)\sigma^{(i)}
-                        \left(\alpha_k - 1\right)
-                    }
-                    {2(L_k - \sigma^{(i)})}
-                    + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2}
-                \right) 
-                \Vert \bar x - v_{k - 1}\Vert^2_p
-                \\ &\quad 
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-                \\ &\quad
-                + \frac{(L_k\alpha_k  - \sigma^{(i)})\sigma^{(i)}(1 - \alpha_k)}{(L_k - \sigma^{(i)})}\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p
-            \\
-            &= 
-            \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}
-            \left(
-                \Vert \bar x - x_{k - 1}\Vert^2_p 
-                + \Vert \bar x - v_{k - 1}\Vert^2_p 
-                - 2\left\langle (\bar x - v_{k - 1}),(\bar x - x_{k - 1})\right\rangle_p
-            \right) 
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-            \\
-            &= \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}
-                \Vert x_{k - 1} - v_{k - 1} \Vert^2_p
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p.
-        \end{align*}
-        }
-        Substituting the above back to the tail of Inequality \eqref{ineq:snapg2-one-step-stage1-chain1} it gives: 
-        {\allowdisplaybreaks
-        \begin{align*}
-            0 &\le 
-            \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k)     
-            - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-                \\ &\quad 
-                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_p
-                + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-            \\
-            &\underset{\text{(e)}}{=} 
-            \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k)     
-            - \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2 
-                \\ &\quad 
-                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_p
-                + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-            \\
-            &= 
-            (\alpha_k - 1) F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) + F_i(\bar x)
-            - \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2 
-                \\ &\quad 
-                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2_p
-                + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-                + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2_p
-            \\
-            &= (1 - \alpha_k)\left(
-                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2_p
-            \right) 
-                \\ & \quad
-                - \left(
-                    F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-                \right) + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.
-        \end{align*}
-        }
-        Re-arranging, with some linear algebra:  we get out first result: 
-        \begin{align*}
-            &F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2_p 
-            \\
-            &\le 
-            F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-            \\
-            &\le 
-            (1 - \alpha_k)\left(
-                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2_p
-            \right)     
-            + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
-                \\ &\quad 
-                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.
-        \end{align*}
-        For the first inequality, recall that $\Vert \cdot\Vert_p = \Vert (I - \Pi^{(i)})(\cdot)\Vert \le \Vert \cdot\Vert$ because $(I - \Pi^{(i)})$ is a projector and, it projects to $\ker A^{(i)}$.
-        Now, let's takle the $k = 0$ case. 
-        \todoinline{HERE}
-        % INTERMEDIATE RESULTS
-        \par
-        \textbf{Proof of (f)}. 
-        The proof is direct algebra and, it has: 
-        {\small\allowdisplaybreaks
-        \begin{align*}
-            & \frac{\left(\sigma^{(i)}\right)^2(1 - \alpha_k)^2}{2(L_k - \sigma^{(i)})} 
-            - \frac{\sigma^{(i)}\alpha_k(1 - \alpha_k)}{2}
-            \\
-            &= 
-            \frac{1}{2\left(L_k - \sigma^{(i)}\right)}
-            \left(
-                \left(\sigma^{(i)}\right)^2(1 - \alpha_k)^2
-                - \left(L_k - \sigma^{(i)}\right)\sigma^{(i)} \alpha_k(1 - \alpha_k)
-            \right)
-            \\
-            &= \frac{1 - \alpha_k}{2\left(L_k - \sigma^{(i)}\right)}\left(
-                \left(\sigma^{(i)}\right)^2 
-                - \left(\sigma^{(i)}\right)^2\alpha_k 
-                - \left(L_k \sigma^{(i)} \alpha_k - \left(\sigma^{(i)}\right)^2 \alpha_k\right)
-            \right)
-            \\
-            &= 
-            \frac{1 - \alpha_k}{2(L_k - \sigma)}\left(
-                \left(\sigma^{(i)}\right)^2 - L_k\left(\sigma^{(i)}\right)\alpha_k
-            \right)
-            \\
-            &= 
-            \frac{(1 - \alpha_k)\sigma^{(i)}\left(\sigma^{(i)} - L_k\alpha_k\right)}
-            {2\left(L_k - \sigma^{(i)}\right)}
-            \\
-            &= \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}
-            {2\left(L_k - \sigma^{(i)}\right)}. 
-        \end{align*}
-        }    
-        % INTERMEDIATE RESULTS 
-        \textbf{Proof of (g)}.
-        From the property of the $\alpha_k$ sequence stated in item (c), we have: 
-        {\allowdisplaybreaks
-        \begin{align*}
-            &\frac{\left(
-                L_k\alpha_k - \sigma^{(i)}
-            \right)^2}{2(L_k - \sigma^{(i)})} 
-            -
-            \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} 
-            \\
-            &= 
-            \frac{\left(
-                L_k\alpha_k - \sigma^{(i)}
-            \right)^2}{2(L_k - \sigma^{(i)})} 
-            -
-            \frac{L_k\alpha_k(\alpha_k - \tilde \sigma/L_k)}{2} 
-            \\
-            &=
-            \frac{\left(
-                L_k\alpha_k - \sigma^{(i)}
-            \right)^2}{2(L_k - \sigma^{(i)})} 
-            - \frac{L_k\alpha_k(\alpha_k - \sigma^{(i)}/L_k)}{2}
-            + \frac{L_k\alpha_k(\alpha_k - \sigma^{(i)}/L_k)}{2} 
-            - \frac{L_k\alpha_k(\alpha_k - \tilde \sigma/L_k)}{2} 
-            \\
-            &= 
-            \frac{\left(
-                L_k\alpha_k - \sigma^{(i)}
-            \right)^2}{2(L_k - \sigma^{(i)})} 
-            - \frac{\alpha_k\left(L_k\alpha_k - \sigma^{(i)}\right)}{2}
-            + \frac{L_k\alpha_k}{2}
-            \frac{\left(
-                \tilde \sigma - \sigma^{(i)}
-            \right)}{L_k}
-            \\
-            &=
-            \frac{L_k \alpha_k - \sigma^{(i)}}{2(L_k - \sigma^{(i)})}\left(
-                L_k \alpha_k - \sigma^{(i)} 
-                - \left(L_k - \sigma^{(i)}\right)\alpha_k
-            \right)
-            + \frac{\alpha_k(\tilde \sigma - \sigma^{(i)})}{2}
-            \\
-            &= \frac{L_k \alpha_k - \sigma^{(i)}}{2(L_k - \sigma^{(i)})}\left(
-                \sigma^{(i)}\alpha_k - \sigma^{(i)} 
-            \right)
-            + \frac{\alpha_k(\tilde \sigma - \sigma^{(i)})}{2}
-            \\
-            &= 
-            \frac{
-                \left(L_k \alpha_k - \sigma^{(i)}\right)\sigma^{(i)}
-                \left(\alpha_k - 1\right)
-            }
-            {2(L_k - \sigma^{(i)})}
-            + \frac{\alpha_k(\tilde \sigma - \sigma^{(i)})}{2}. 
-        \end{align*}   
-        } 
-    \end{proof}
-    % The following lemma state the relationships of the iterates generated by SNAPG-V2. 
-    % They are needed for the convergence proof. 
-    % % --------------------------------------------------------------------------------------------------------------
-    % \begin{lemma}[properties of the iterates \textcolor{red}{DEPRECATED}]\label{lemma:snapg2-itrs-props}
-    %     Suppose that the iterates $(z_k, x_k, y_k)_{k \ge 0}$ and sequence $(\alpha_k)_{k \ge 1}$ are produced by an algorithm satisfying Definition \ref{def:snapg-v2}. 
-    %     Let $\bar x \in \RR^n$.
-    %     Define the sequence $z_k = \alpha_k\bar x + (1 - \alpha_k)x_{k - 1}$. 
-    %     Then, the following are true: 
-    %     \begin{enumerate}
-    %         \item\label{lemma:snapg2-itrs-props-item1} For all $k \ge 1$ it has: 
-    %         \begin{align*}
-    %                 z_k - y_k 
-    %                 = 
-    %                 \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-    %                 + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
-    %         \end{align*}
-    %         \item\label{lemma:snapg2-itrs-props-item2} For all $k \ge 1$, it has: $z_k - x_k = \alpha_k(x - \bar x)$
-    %     \end{enumerate}
-    % \end{lemma}
-    % \begin{proof}
-    %     \textbf{Proof of \ref{lemma:snapg2-itrs-props-item1}}. 
-    %     From Definition \ref{def:snapg-v2}, it has
-    %     \begin{align*}
-    %         (1 + \tau_k)^{-1}
-    %         &=
-    %         \left(
-    %             1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
-    %         \right)^{-1} = \left(
-    %             \frac{L_k\alpha_k - \mu^{(i)} + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
-    %         \right)^{-1}
-    %         = \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}. 
-    %     \end{align*}
-    %     Therefore, for all $k \ge 0$, $y_k$ has 
-    %     \begin{align*}
-    %         0 &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1} - y_k
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} 
-    %         \left(
-    %             v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}} x_{k - 1}
-    %         \right) - y_k
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1}
-    %         + \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1} - y_k
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
-    %         + 
-    %         \left(
-    %             \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} - (1 - \alpha_k)
-    %         \right) x_{k - 1} - y_k
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
-    %         + 
-    %         (1 - \alpha_k)\left(
-    %             \frac{L_k - L_k + \mu^{(i)}}{L_k - \mu^{(i)}}
-    %         \right) x_{k - 1} - y_k
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
-    %         + 
-    %         \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}x_{k - 1} - y_k. 
-    %     \end{align*}
-    %     Therefore, we establish the equality 
-    %     \begin{align*}
-    %         (1 - \alpha_k)x_{k - 1} - y_k &= 
-    %         - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
-    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}. 
-    %     \end{align*}
-    %     On the second equality below, we will the above equality, it goes: 
-    %     \begin{align*}
-    %         z_k - y_k &= 
-    %         \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
-    %         \\
-    %         &= \alpha_k \bar x 
-    %         - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
-    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-    %         + \left(
-    %             \alpha_k - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}
-    %         \right)\bar x
-    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-    %         + \left(
-    %             \frac{\alpha_kL_k - \alpha_k \mu^{(i)} - L_k\alpha_k + \mu^{(i)}}{L_k - \mu^{(i)}}
-    %         \right)\bar x
-    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-    %         + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}\bar x
-    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
-    %         \\
-    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-    %         + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
-    %     \end{align*}
-    %     \textbf{proof of \ref{lemma:snapg2-itrs-props-item2}.}
-    %     From Definition \ref{def:snapg-v2} it has directly: 
-    %     \begin{align*}
-    %         z_k - x_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
-    %         \\
-    %         &= \alpha_k \bar x + x_{k - 1} - x_k - \alpha_k x_{k - 1}
-    %         \\
-    %         &= \alpha_k(\bar x - \alpha_k^{-1}(x_k - x_{k - 1}) - x_{k - 1})
-    %         \\
-    %         &= \alpha_k (\bar x - v_k).
-    %     \end{align*}
-
-    % \end{proof}
-    % % --------------------------------------------------------------------------------------------------------------
-    % \begin{theorem}[SNAPG-V2 one step convergence \textcolor{red}{DEPRECATED}]\label{thm:snapg2-one-step}
-    %     Let $F$ satisfies assumption \ref{ass:interp-hypothesis}. 
-    %     Suppose that an algorithm satisfying Definition \ref{def:snapg-v2} uses this $F$. 
-    %     Let $\mathbb E_k$ denotes the expectation conditioned on $I_0, I_1, \ldots, I_{k - 1}$. 
-    %     Then, for all $k \ge 1$, it has the following inequality 
-    %     \begin{align*}
-    %         & \mathbb E_k\left[F_{I_k}(x_{k})\right] 
-    %         - F(\bar x) 
-    %         + \mathbb E_k\left[
-    %             \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %         \right]
-    %         \\
-    %         &\le 
-    %         (1 - \alpha_k)\left(
-    %                 \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
-    %                 - F(\bar x)
-    %                 + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
-    %         \right)
-    %             \\ &\quad 
-    %             + \mathbb E_k\left[
-    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-    %             \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
-    %             + \frac{\alpha_k(\tilde\mu - \mu)}{2} 
-    %             \Vert \bar x - v_{k - 1}\Vert^2. 
-    %     \end{align*}
-    %     And for $k = 0$, it has 
-    %     \begin{align*}
-    %         \mathbb E \left[ F_{I_0}\right] - F(\bar x) 
-    %         + \frac{L_0}{2}\mathbb E \left[\Vert \bar x - x_0\Vert^2\right]
-    %         &\le 
-    %         \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
-    %     \end{align*}
-    % \end{theorem}
-    % \begin{proof}
-    %     Let's suppose that $I_k = i$ and, for all $k \ge 0$. 
-    %     Let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ where $\bar x$ is a minimizer of $F$. 
-    %     The proof is long so, we use letters and subscript under relations such as $\underset{(\cdot)}{=}, \underset{(\cdot)}{\ge}$ to indicate which result is used going from the previous expression to the next.
-    %     We list the following intermediate results, (d)-(g) are proved at the end of the proof. 
-    %     \begin{itemize}
-    %         \item[(a)] We can use proximal gradient inequality from Theorem \ref{thm:pg-ineq} with $z = z_k$ because each $F_i$ is $K_i$ Lipschitz smooth and, $\mu^{(i)}$ strongly convex with $K_i \ge \mu^{(i)}$.
-    %         \item[(b)] We can use Jensen's inequality of Theorem \ref{thm:jesen} with $z = z_k$ on $F_i$. 
-    %         \item[(c)] The sequence $(\alpha_k)_{k \ge 0}$ has $(L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right)$. 
-    %         \item[(d)] Prove in Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item1} we use the equality:
-    %         \begin{align*}
-    %             (\forall k \ge 1)\; 
-    %             z_k - y_k 
-    %             = 
-    %             \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-    %             + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
-    %         \end{align*}
-    %         \item [(e)] From Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item2}, we use: $(\forall k \ge 1)\; z_k - x_k = \alpha_k (\bar x - v_k)$. 
-    %         \item [(f)] Using direct algebra, we have for all $k \ge 1$: 
-    %         \begin{align*}
-    %             \frac{\left(\mu^{(i)}\right)^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} 
-    %             - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
-    %             = \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
-    %             {2\left(L_k - \mu^{(i)}\right)}. 
-    %         \end{align*}
-    %         \item [(g)] Using (c), we have for all $k \ge 1$: 
-    %         \begin{align*}
-    %             \frac{\left(
-    %                 L_k\alpha_k - \mu^{(i)}
-    %             \right)^2}{2(L_k - \mu^{(i)})} 
-    %             -
-    %             \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} 
-    %             = 
-    %             \frac{
-    %             \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
-    %             \left(\alpha_k - 1\right)
-    %             }
-    %             {2(L_k - \mu^{(i)})}
-    %             + \frac{\alpha_k(\tilde \mu_k - \mu^{(i)})}{2}. 
-    %         \end{align*}
-    %         \item[(h)] Because we assumed interpolation hypothesis in Assumption \ref{ass:interp-hypothesis}, it has $\mathbb E[F_{I_k}(\bar x)] = F(\bar x)$ for all $\bar x$ that is a minimizer of $F$.
-    %     \end{itemize}
-    %     For all $k \ge 1$, starting with (a) we have: 
-    %     \begin{align}\label{ineq:snapg2-one-step-chain1}
-    %         \begin{split}
-    %             0 &\le F_i(z_k) - F_i(x_k) - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2
-    %             \\
-    %             &\underset{\text{(b)}}{\le}
-    %             \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) \\
-    %                 &\quad 
-    %                 - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
-    %                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-    %                 + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2. 
-    %         \end{split}
-    %     \end{align}
-    %     And we have the following chain of equalities:
-    %     {\allowdisplaybreaks
-    %     \begin{align*}
-    %         & - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
-    %         + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2
-    %         \\
-    %         &\underset{\text{(d)}}{=}
-    %         - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2 
-    %             \\&\quad
-    %             + \frac{L_k - \mu^{(i)}}{2}
-    %             \left\Vert
-    %                 \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
-    %                 + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1})
-    %             \right\Vert^2
-    %         \\
-    %         &= 
-    %         - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2 
-    %             \\&\quad
-    %             + \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{(\mu^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2 
-    %             \\&\quad 
-    %             + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
-    %         \\
-    %         &= 
-    %         \left(
-    %             \frac{(\mu^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
-    %         \right)\Vert \bar x - x_{k - 1}\Vert^2
-    %             \\ &\quad 
-    %             + \left(
-    %                 \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
-    %             \right) \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             \\&\quad 
-    %             + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
-    %         \\
-    %         &\underset{\text{(f)}}{=}
-    %         \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
-    %         {2\left(L_k - \mu^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2
-    %             \\ &\quad 
-    %             + \left(
-    %                 \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
-    %             \right) \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             \\&\quad 
-    %             + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
-    %         \\
-    %         & \underset{\text{(g)}}{=} 
-    %         \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
-    %         {2\left(L_k - \mu^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2
-    %             \\ &\quad 
-    %             + \left(
-    %                 \frac{
-    %                     \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
-    %                     \left(\alpha_k - 1\right)
-    %                 }
-    %                 {2(L_k - \mu^{(i)})}
-    %                 + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}
-    %             \right) 
-    %             \Vert \bar x - v_{k - 1}\Vert^2
-    %             \\ &\quad 
-    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
-    %         \\
-    %         &= 
-    %         \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\left(
-    %             \Vert \bar x - x_{k - 1}\Vert^2 + \Vert \bar x - v_{k - 1}\Vert^2 - 2\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
-    %         \right) 
-    %             \\ &\quad 
-    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %         \\
-    %         &= \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
-    %             \Vert x_{k - 1} - v_{k - 1} \Vert^2
-    %             \\ &\quad 
-    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2.
-    %     \end{align*}
-    %     }
-    %     Substituting the above back to the tail of Inequality \eqref{ineq:snapg2-one-step-chain1} it gives: 
-    %     {\allowdisplaybreaks
-    %     \begin{align*}
-    %         0 &\le 
-    %         \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) 
-    %             \\&\quad 
-    %             - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
-    %             + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
-    %             \Vert x_{k - 1} - v_{k - 1} \Vert^2
-    %             \\ &\quad 
-    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %         \\
-    %         &\underset{\text{(e)}}{=} 
-    %         \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) 
-    %             \\&\quad 
-    %             - \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %             + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
-    %             \Vert x_{k - 1} - v_{k - 1} \Vert^2
-    %             \\ &\quad 
-    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %         \\
-    %         &= (\alpha_k - 1)F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) + F_i(\bar x)
-    %             \\&\quad 
-    %             - \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %             + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
-    %             \\ &\quad 
-    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %         \\
-    %         &= (1 - \alpha_k)\left(
-    %             F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
-    %         \right) 
-    %             \\ & \quad
-    %             - \left(
-    %                 F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %             \right)
-    %             \\ &\quad 
-    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
-    %             + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
-    %     \end{align*}
-    %     }
-    %     Recall that $i = I_k$ is the random variable from Definition \ref{def:snapg-v2}. 
-    %     Rearranging the last expression in the above equality chain can be conveniently written as
-    %     \begin{align}
-    %         \begin{split}
-    %             & F_{I_k}(x_{k}) - F_{I_k}(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %             \\ &\le 
-    %             (1 - \alpha_k)\left(
-    %                 F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
-    %             \right) 
-    %                 \\ &\quad 
-    %                 + \frac{\alpha_k(\tilde \mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %                 + \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
-    %         \end{split}
-    %     \label{ineq:snapg2-one-step-presult1}\end{align}
-    %     Recall $\mathbb E_k$ denotes the conditional expectation on $I_0, I_1, \ldots, I_{k - 1}$. 
-    %     Taking the conditional expectation on the LHS of the \eqref{ineq:snapg2-one-step-presult1} yields: 
-    %     \begin{align*}
-    %         & \mathbb E_k\left[
-    %             F_{I_k}(x_{k}) - F_{I_k}(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %         \right]
-    %         \\
-    %         &\underset{\text{(h)}}{=}
-    %         \mathbb E_k\left[F_{I_k}(x_{k})\right] 
-    %         - F(\bar x) 
-    %         + \mathbb E_k\left[
-    %             \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %         \right]. 
-    %     \end{align*}
-    %     On the RHS of \eqref{ineq:snapg2-one-step-presult1}, using the linearity property while taking the conditional expectation yields: 
-    %     {\allowdisplaybreaks
-    %     \begin{align*}
-    %         & \mathbb E_k\left[
-    %             (1 - \alpha_k)\left(
-    %                 F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
-    %             \right)
-    %         \right]
-    %             \\ &\quad 
-    %             + \mathbb E_k \left[
-    %                 \frac{\alpha_k(\tilde\mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
-    %             \right]
-    %             + \mathbb E_k\left[
-    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
-    %             \right]
-    %         \\
-    %         &\underset{\text{(1)}}{=} 
-    %         (1 - \alpha_k)\left(
-    %                 \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
-    %                 -\mathbb E_k [F_{I_k}(\bar x)] 
-    %                 + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
-    %         \right)
-    %             \\ &\quad 
-    %             + \mathbb E_k \left[
-    %                 \frac{\alpha_k(\tilde\mu - \mu^{(I_k)})}{2} 
-    %             \right]\Vert \bar x - v_{k - 1}\Vert^2
-    %             + \mathbb E_k\left[
-    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-    %             \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
-    %         \\
-    %         &\underset{\text{(h)}}{=} 
-    %         (1 - \alpha_k)\left(
-    %                 \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
-    %                 - F(\bar x)
-    %                 + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
-    %         \right)
-    %             \\ &\quad 
-    %             + \mathbb E_k \left[
-    %                 \frac{\alpha_k(\tilde\mu - \mu^{(I_k)})}{2} 
-    %             \right]\Vert \bar x - v_{k - 1}\Vert^2
-    %             + \mathbb E_k\left[
-    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-    %             \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
-    %         \\
-    %         &\underset{\text{(2)}}{=}
-    %         (1 - \alpha_k)\left(
-    %                 \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
-    %                 - F(\bar x)
-    %                 + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
-    %         \right)
-    %             \\ &\quad 
-    %             \frac{\alpha_k(\tilde\mu - \mu)}{2} 
-    %             \Vert \bar x - v_{k - 1}\Vert^2
-    %             + \mathbb E_k\left[
-    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-    %             \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
-    %     \end{align*}
-    %     }
-    %     We note that at label (1), we used the fact that $\alpha_k$ is a constant and, $x_{k - 1}, v_{k - 1}$ only depends on random variable $I_0, I_1, \ldots, I_{k - 1}$ hence it falls out of the conditional expectation $\mathbb E_k$.
-    %     At label (2), we used assumption (Assumption \ref{ass:sum-of-many}) that the averages of all the $\mu^{(I_k)}$ on each $F_{I_k}$ equals to $\mu$ hence, the expectation evaluates to zero by linearity of the expected value operator.
-    %     \par
-    %     Combining the above results on the expectation of RHS, and LHS of \eqref{ineq:snapg2-one-step-presult1}, we have the one-step inequality in expectation: 
-    %     \begin{align*}
-    %         & \mathbb E_k\left[F_{I_k}(x_{k})\right] 
-    %         - F(\bar x) 
-    %         + \mathbb E_k\left[
-    %             \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-    %         \right]
-    %         \\
-    %         &\le 
-    %         (1 - \alpha_k)\left(
-    %                 \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
-    %                 - F(\bar x)
-    %                 + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
-    %         \right)
-    %             \\ &\quad 
-    %             + \mathbb E_k\left[
-    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-    %             \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
-    %     \end{align*}
-    %     Finally, we show the base case. 
-    %     When $k = 0$, by assumption it had $\alpha_0 = 1$ hence $\tau_0$ in Definition \ref{def:snapg-v2} has $\tau_0 = 0$ which makes $y_0 = v_{- 1} = x_{-1}$. 
-    %     Therefore, it makes $x_0 = T_{L_0}(y_0 | F_{I_0}) = T_{L_0}(v_{-1} | F_{I_0})$. 
-    %     Similarly, it has also $z_0 = \bar x$.
-    %     Applying Theorem \ref{thm:pg-ineq} with $z = z_0$ and, assume a successful line search with $L_0$, it yields: 
-    %     \begin{align*}
-    %         0 &\le F_{I_0}(z_0) - F_{I_0}(x_0) - \frac{L_0}{2}\Vert z_0 - x_0\Vert^2 + \frac{L_0 - \mu^{(I_0)}}{2}\Vert z_0 - y_0\Vert^2
-    %         \\
-    %         &= F_{I_0}(\bar x) - F_{I_0}(x_0) - \frac{L_0}{2}\Vert \bar x - x_0\Vert^2 + \frac{L_0 - \mu^{(I_0)}}{2}\Vert \bar x - v_{-1}\Vert^2. 
-    %     \end{align*}
-    %     Re-arranging and taking the expectation it yields: 
-    %     \begin{align*}
-    %         \mathbb E \left[
-    %             F_{I_0}(x_0) - F_{I_0}(\bar x) + \frac{L_0}{2}\Vert \bar x - x_0\Vert^2
-    %         \right]
-    %         &\underset{\text{(h)}}{=}
-    %         \mathbb E \left[ F_{I_0}\right] - F(\bar x) 
-    %         + \frac{L_0}{2}\mathbb E \left[\Vert \bar x - x_0\Vert^2\right]
-    %         \\
-    %         &\le \frac{L_0 - \mathbb E \left[\mu^{(I_0)}\right]}{2}\Vert \bar x - v_{-1}\Vert^2
-    %         \\
-    %         &= \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
-    %     \end{align*}
-    %     % INTERMEDIATE RESULTS
-    %     \textbf{Proof of (f)}. 
-    %     The proof is direct algebra and, it has: 
-    %     {\small\allowdisplaybreaks
-    %     \begin{align*}
-    %         & \frac{\left(\mu^{(i)}\right)^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} 
-    %         - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
-    %         \\
-    %         &= 
-    %         \frac{1}{2\left(L_k - \mu^{(i)}\right)}
-    %         \left(
-    %             \left(\mu^{(i)}\right)^2(1 - \alpha_k)^2
-    %             - \left(L_k - \mu^{(i)}\right)\mu^{(i)} \alpha_k(1 - \alpha_k)
-    %         \right)
-    %         \\
-    %         &= \frac{1 - \alpha_k}{2\left(L_k - \mu^{(i)}\right)}\left(
-    %             \left(\mu^{(i)}\right)^2 
-    %             - \left(\mu^{(i)}\right)^2\alpha_k 
-    %             - \left(L_k \mu^{(i)} \alpha_k - \left(\mu^{(i)}\right)^2 \alpha_k\right)
-    %         \right)
-    %         \\
-    %         &= 
-    %         \frac{1 - \alpha_k}{2(L_k - \mu)}\left(
-    %             \left(\mu^{(i)}\right)^2 - L_k\left(\mu^{(i)}\right)\alpha_k
-    %         \right)
-    %         \\
-    %         &= 
-    %         \frac{(1 - \alpha_k)\mu^{(i)}\left(\mu^{(i)} - L_k\alpha_k\right)}
-    %         {2\left(L_k - \mu^{(i)}\right)}
-    %         \\
-    %         &= \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
-    %         {2\left(L_k - \mu^{(i)}\right)}. 
-    %     \end{align*}
-    %     }    
-    %     % INTERMEDIATE RESULTS 
-    %     \textbf{Proof of (g)}.
-    %     From the property of the $\alpha_k$ sequence stated in item (c), we have: 
-    %     {\allowdisplaybreaks
-    %     \begin{align*}
-    %         &\frac{\left(
-    %             L_k\alpha_k - \mu^{(i)}
-    %         \right)^2}{2(L_k - \mu^{(i)})} 
-    %         -
-    %         \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} 
-    %         \\
-    %         &= 
-    %         \frac{\left(
-    %             L_k\alpha_k - \mu^{(i)}
-    %         \right)^2}{2(L_k - \mu^{(i)})} 
-    %         -
-    %         \frac{L_k\alpha_k(\alpha_k - \tilde \mu/L_k)}{2} 
-    %         \\
-    %         &=
-    %         \frac{\left(
-    %             L_k\alpha_k - \mu^{(i)}
-    %         \right)^2}{2(L_k - \mu^{(i)})} 
-    %         - \frac{L_k\alpha_k(\alpha_k - \mu^{(i)}/L_k)}{2}
-    %         + \frac{L_k\alpha_k(\alpha_k - \mu^{(i)}/L_k)}{2} 
-    %         - \frac{L_k\alpha_k(\alpha_k - \tilde \mu/L_k)}{2} 
-    %         \\
-    %         &= 
-    %         \frac{\left(
-    %             L_k\alpha_k - \mu^{(i)}
-    %         \right)^2}{2(L_k - \mu^{(i)})} 
-    %         - \frac{\alpha_k\left(L_k\alpha_k - \mu^{(i)}\right)}{2}
-    %         + \frac{L_k\alpha_k}{2}
-    %         \frac{\left(
-    %             \tilde \mu - \mu^{(i)}
-    %         \right)}{L_k}
-    %         \\
-    %         &=
-    %         \frac{L_k \alpha_k - \mu^{(i)}}{2(L_k - \mu^{(i)})}\left(
-    %             L_k \alpha_k - \mu^{(i)} 
-    %             - \left(L_k - \mu^{(i)}\right)\alpha_k
-    %         \right)
-    %         + \frac{\alpha_k(\tilde \mu - \mu^{(i)})}{2}
-    %         \\
-    %         &= \frac{L_k \alpha_k - \mu^{(i)}}{2(L_k - \mu^{(i)})}\left(
-    %             \mu^{(i)}\alpha_k - \mu^{(i)} 
-    %         \right)
-    %         + \frac{\alpha_k(\tilde \mu - \mu^{(i)})}{2}
-    %         \\
-    %         &= 
-    %         \frac{
-    %             \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
-    %             \left(\alpha_k - 1\right)
-    %         }
-    %         {2(L_k - \mu^{(i)})}
-    %         + \frac{\alpha_k(\tilde \mu - \mu^{(i)})}{2}. 
-    %     \end{align*}   
-    %     } 
-    % \end{proof}
-\section{Convergence rate of the algorithm under various circumstances}
-    The previous section highlighted a generic convergence results from one iteration of the algorithm, however, there are a lot of loose ends. 
-    This section will deal with those.
-
-\section{\textcolor{purple}{So, what to do next?}}
-    Hi Arron would you like to add me for the co-authorship to continue this line of work and see how Nesterov's Accelerated Technique may work out for the stochastic gradient method? 
-    These results are solid results but, they are still partial results and, below are the potential I foresee for this these ideas. 
-    \begin{enumerate}
-        \item Narrow down the sequence $\alpha_k$ and make sure that it can allow the quantity: 
-        \begin{align*}
-            \mathbb E_k\left[
-                    \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
-                \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
-        \end{align*}
-        is negative, or at least bounded. I am not sure how this will work out, but I have some solid ideas around it. 
-        \item Roll up the inequality in Theorem \ref{thm:snapg2-one-step} recursively and, determine the convergence rate through $\alpha_k$ that makes the previous item true. 
-        In addition, I have the hunches that the convergence rate involves the variance of $\mu^{(I_k)}$ and, it will slower than the non-stochastic case of the algorithm. 
-    \end{enumerate}
-    For the future we can: 
-    \begin{enumerate}
-        \item Extend the definition of strong convexity to relative strong convexity with respect to a quasi-norm.
-This would extend interpolation hypothesis in Assumption \ref{ass:interp-hypothesis} where, even if $\mu > 0$, it doesn't mean that $F$ has a unique solution through strong convexity.
-This is entirely possible and appeared in the literatures before so, I can give you the words of confidence.
-        \item Show the convergence of the method for objective function based on quasi-strong convexity.
-This is a much weaker assumption it works well in practice for the common known problems in convex programming.
-    \end{enumerate}
 

### 2025-07-16 Notebook LaTEX/SAGD Under Interpolation/main-2025-07-14.tex
>w<, changes

@@
 \begin{abstract} 
-    This file is for communication purposes between collaborators.
+    I am very sorry to inform the readers that the intended results in this drafts had all been invalidated due to a oversight on conditional expectations. 
+    See text in red in Lemma \ref{lemma:snapg-v2-one-step-not-scnvx}.
 
@@
         Suppose that the sequence $(v_k, x_k, y_k)_{k \ge 0}$ is generated by algorithms that satisfy Definition \ref{def:snapg-v2-classical}, then for all $k \ge 1$, the $\mathcal R^{(i)}_k$ in \eqref{ineq:snapg2-one-step-s1-rslt1} equals to zero.
-        Let $\mathbb E_k$ defines the conditional expectation on $I_0, I_1, \ldots, I_{k - 1}, I_k$. 
+        Let $\mathbb E_k$ defines the conditional expectation on $I_0, I_1, \ldots, I_{k - 1}$. 
         If in addition, Assumption \ref{ass:interp-hypothesis} holds. 
@@
         By Definition \ref{def:snapg-v2-classical}, $\tilde \mu = 0, \sigma^{(i)} = 0$ for all $i = 1, 2, \ldots, n$, so $\mathcal R^{(i)}_k = 0$ for all $k \ge 1$. 
+        \textbf{\textcolor{red}{A mistake had been identified right here. }} 
+        And it's invalidating all of our results. 
+        The following inequality is the inequality we would like to have in order to unroll the recurrence: 
+        \textcolor{red}
+        {
+        \begin{align*}
+            & \expect_{k}
+            \left[
+                F_{I_k}(x_k)
+                - F(\bar x)
+                + \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2
+            \right]
+            \\&\le 
+            (1 - \alpha_k)
+            \expect_{k - 1}
+            \left[
+                F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2} \Vert \bar x - v_{k - 1}\Vert^2
+            \right]
+        \end{align*}
+        }
+        Which is making things impossible because we can't take $\expect_{k}$, and then $\expect_{k - 1}$ on LHS, then RHS of the inequality. 
+        Nor it is possible to take either of $\expect_{k}, \expect_{k - 1}$ and make the expression looks as the above because $I_k$ appeared on both side of the inequality. 
     \end{proof}
+
 \section{Convergence rate of the algorithm under various circumstances}

### 2025-07-16 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
 \newcommand{\expect}{\ensuremath{\mathbb E}}
+\usepackage{tikz}\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=0.5pt](char) {#1};}}
 
 \begin{document}
-\title{{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis}}
+
+\title{{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis, Truth or Just a Dream?}}
 
@@
     This file is for communication purposes between collaborators. 
-
+    In brief, we think that the conditions required for linear convergence rate of Stochastic Nesterov's accelerated gradient (or proximal gradient) is too precarious to hold, even with interpolation hypothesis.
+    Instead of attacking the problem head on, this file will characterize the conditions required for linear convergence rate. 
+    We place specific constraints on the random variable representing the error made when estimating gradient via some random variables. 
 \end{abstract}
@@
 \section{Introduction}
+    \cite{bauschke_convex_2017}
+    Previously we got some results, but unfortunately it was incorrect and it was impossible to recover from the mistake. 
+    \par
     Does stochastic accelerated Nesterov's acceleration (SNAG) produces accelerated convergence rate (or, any type of convergence) when the Interpolation Hypothesis is true? 
-    \cite{bauschke_convex_2017}
-    Previously we got some results, but unfortunately it was incorrect the mistake is diffcult to recover. 
-    \par
-    \textbf{However, I don't think that it's true after some mistakes from previous version of the notes and careful investigations.}
+    \textbf{I don't think that it's true after some mistakes from previous version of the notes and careful investigations.}
     In this file we develop some sufficient conditions for Linear convergence of (SNAG). 
     We will give explanations on why we don't think this is necessarily true. 
+    \par
+    When we use stochastic gradient to approximate the true graduate, it has an error. 
+    Fix some $x\in \RR^n$, let $\tilde \nabla f(x)$ be an estimate of $\nabla f(x)$, the error we consider is $\expect \Vert \nabla f(x) - \nabla f(x)\Vert$. 
+    To make the algebra simpler, we assume that the algorithm produced the next iterates $\tilde x$ by a step of gradient descent, and the error of the expectation satisfies a relative error conditions of the form
+    \begin{align*}
+        \frac{
+            \expect \left[
+                \left\Vert \nabla f(x) - \tilde \nabla f(x) \right\Vert \Vert z - \tilde x\Vert
+            \right]
+            }{
+            \expect \left[
+                \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert
+            \right]
+            } &= \epsilon. 
+    \end{align*}
+    Where the variable $z$ will be explained later. 
+    We will show that, the value of $\epsilon$ must decreases at a rate convergence relative to the Nesterov's accelerated sequence, under the standard Framework of analysis similar to what is in the literature.
+    Take note that usually in the literature, people analyze the quantity $\expect\left\Vert \tilde \nabla f(x) - \tilde \nabla f(y)\right\Vert^2$ for stochastic gradient type  of method. 
+    The above expression is drastically different from what we usually have in the literature.
 
@@
     $I$ denotes the identity operator. 
+    \par
     When two expressions are connected via non-trivial results, it's expressed with $\underset{(\cdot)}{=}, \underset{(\cdot)}{\ge}$ where $(\cdot)$ is a label of some intermediate results immediately before it, or explained right after a chain of expressions.
+    If the label is letter, like: (a), (b), ..., then they are stated in advanced at the start of the proof and they are usually non-trivial results. 
+    These labels are reused in every proof. 
+    If the label is circled numbers, like: \circled{1}, \circled{2},... they are explained right after the chain of relations, and they are often reused right after their explanations. 
     \subsection{Basic definitions}
@@
         \end{definition}
-    \subsection{important inequalities}
+    \subsection{Important inequalities}
         \begin{assumption}\label{ass:smooth-plus-nonsmooth}
@@
         \end{remark}
-        % --------------------------------------------------------------------------------------------------------------
-        \begin{lemma}[inexact proximal gradient inequality]\label{lemma:inex-pg-ineq}
-            Let $F = f + g$ satisfies Definition \ref{def:lip-smooth-and-scnvx} with $L > \mu \ge 0$. 
-            Let $x \in \RR^n$ be fixed. 
-            Suppose an inexact evaluation of proximal gradient operator at $x$ yield an approximation $\tilde x$, characterized by: 
+        \begin{lemma}[inexact proximal gradient inequality prototype]\label{lemma:inex-pg-ineq-proto}
+            Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
+            Fix some $x \in \RR^n$, and suppose that an error: $w$ is made when estimating the proximal to obtain $\tilde x$ at $x$ such that it's characterized by
             \begin{align*}
-                & D_f(\tilde x, x) \le \frac{B}{2}\Vert \tilde x - x\Vert^2, 
-                \\
-                & \exists: w \in \partial \left[
+                w \in \partial \left[
                     z \mapsto g(z) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
-                \right](\tilde x)\; \text{s.t: } \Vert w\Vert \le \epsilon \Vert x - \tilde x\Vert. 
+                \right](\tilde x)
             \end{align*}
-            Then, it would satisfy for all $z\in \RR^n$ the inequality: 
+            And in addition, assume that there exists some $B \ge 0$ such that $D_f(\tilde x, x) \le \frac{B}{2}\Vert \tilde x - x\Vert^2$. 
+            Then, for all $z \in \RR^n$ it satisfies: 
             \begin{align*}
-                0 &\le 
-                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2
-                - \frac{B - \epsilon}{2}\Vert z - \tilde x\Vert^2
-                + \frac{\epsilon}{2}\Vert x - \tilde x \Vert^2. 
+                \frac{B}{2}\Vert z - \tilde x\Vert^2 &\le 
+                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 - \langle w, z - \tilde x \rangle. 
             \end{align*}
@@
         \begin{proof}
+            The proof is direct algebra. 
             Let $h = z \mapsto g(z) + \langle \nabla f(x), z - x\rangle + B/2\Vert z - x\Vert^2$. 
@@
                 \\
-                &\underset{\text{(a)}}{\le} F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 - 0 - \langle w, z - \tilde x \rangle
-                \\
-                &\underset{\text{(b)}}{\le}
-                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 - 0 + \epsilon \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert. 
+                &\underset{\text{\circled{1}}}{\le} F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 - 0 - \langle w, z - \tilde x \rangle
             \end{align*}
-            At (a), we used the fact that $f$ is $L > \mu \ge 0$ Lipschitz smooth and strongly convex therefore it has for all $y \in \RR^n$: 
+            At \circled{1}, we used the fact that $f$ is $L > \mu \ge 0$ Lipschitz smooth and strongly convex therefore it has for all $y \in \RR^n$: 
             \begin{align*}
@@
             \end{align*}
-            At (b) we used the Cauchy Inequality and, the assumption $\Vert w\Vert \le \epsilon \Vert x - \tilde x\Vert$. 
+        \end{proof}
+        % --------------------------------------------------------------------------------------------------------------
+        \begin{lemma}[inexact proximal gradient inequality]\label{lemma:inex-pg-ineq}
+            Let $F = f + g$ satisfies Definition \ref{def:lip-smooth-and-scnvx} with $L > \mu \ge 0$. 
+            Let $x \in \RR^n$ be fixed. 
+            Suppose an inexact evaluation of proximal gradient operator at $x$ yield an approximation $\tilde x$, characterized by: 
+            \begin{align*}
+                & \exists: w \in \partial \left[
+                    z \mapsto  g(z) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
+                \right](\tilde x)\; \text{s.t: } \Vert w\Vert \le \epsilon \Vert x - \tilde x\Vert. 
+            \end{align*}
+            Suppose that there exists some $B \ge 0$ such that $D_f(\tilde x, x) \le \frac{B}{2}\Vert \tilde x - x\Vert^2$. 
+            Then, for all $z\in \RR^n$ it satisfies the inequality: 
+            \begin{align*}
+                0 &\le 
+                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2
+                - \frac{B - \epsilon}{2}\Vert z - \tilde x\Vert^2
+                + \frac{\epsilon}{2}\Vert x - \tilde x \Vert^2. 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            The error $w$ satisfies Lemma \ref{lemma:inex-pg-ineq-proto} hence, it has for all $z \in \RR^n$ the inequality: 
+            \begin{align*}
+                \frac{B}{2}\Vert z - \tilde x\Vert^2
+                &\le F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 - 0 - \langle w, z - \tilde x \rangle
+                \\
+                &\underset{\text{\circled{1}}}{\le}
+                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 + \epsilon \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert. 
+            \end{align*}
+            At \circled{1}, we used Cauchy inequality. 
             Continuing it has 
@@
         \begin{remark}
-            Usually in practice, the precise value of $F(\tilde x)$ is never known, therefore, $B$ cannot be easily determined via $D_f(\tilde x, x)$. 
-            Hence, in this case we can only choose $B \ge L$ which gives: 
+            Usually in practice, the precise value of $F(\tilde x)$ is never known and, function value is also a random variable, therefore, $B$ cannot be easily determined via $D_f(\tilde x, x)$. 
+            In that case we can only choose some $B \ge L$ which gives: 
             \begin{align*}
+                0 &\le 
                 F(z) - F(\tilde x) + \frac{L - \mu}{2}\Vert z - x\Vert^2
@@
         It fully characterizes the error made to estimate the true gradient $\nabla f(x)$. 
+        In that case, we have the equation: 
+        \begin{align*}
+            \left\Vert \nabla f(x) - \tilde \nabla f(x) \right\Vert \Vert x - \tilde x\Vert
+            = \epsilon \Vert x - \tilde x\Vert^2. 
+        \end{align*}
+        It's very unclear what LHS really is without additional details and assumptions. 
+        \textbf{We very much would like $\epsilon$ to be a constant to make the algebra possible when deriving the convergence rate of the algorithm. }
+        \par
+        The following lemma gives a proximal gradient inequality when $\tilde \nabla f(x)$ is an estimate by some random variable, \textbf{and it is the precursor.} 
+        \begin{lemma}[stochastic proximal gradient inequality]\label{lemma:stoch-pg-ineq}
+            Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
+            Fix any $x, z \in \RR^n$. 
+            Suppose that, a random variable $\tilde \nabla f(x)$ is used to estimate the proximal gradient operator and it produced an error $w$, and the estimate $\tilde x$. 
+            Then, it would have $w = \nabla f(x) - \tilde \nabla f(x)$. 
+            Let $B \ge 0$ be constant such that $D_f(\tilde x,x)\le B/2 \Vert x - \tilde x\Vert^2$. 
+            Suppose that in addition, there exists $\epsilon \ge 0$ such that: 
+            \begin{align*}
+                \expect \left[
+                    \Vert w\Vert \Vert z - \tilde x\Vert
+                \right] &\le \epsilon \expect \left[
+                    \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert
+                \right]. 
+            \end{align*}
+            Then it makes the following inequality true: 
+            \begin{align*}
+                &\le 
+                F(z) + \expect F(\tilde x) + \frac{\max(B, L) - \mu}{2} \Vert z - x\Vert^2
+                - \frac{B - \epsilon}{2}\expect\left[\Vert z - \tilde x\Vert^2\right]
+                + \frac{\epsilon}{2} \left[\Vert x - \tilde x\Vert^2\right]. 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            Using Lemma \ref{lemma:inex-pg-ineq-proto}, for any fixed $z$ it has: 
+            \begin{align*}
+                \frac{B}{2}\Vert z - \tilde x\Vert &\le 
+                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 - \langle w, z - \tilde x\rangle
+                \\
+                &\le 
+                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 + \Vert w\Vert\Vert z - \tilde x\Vert. 
+            \end{align*}
+            Take note that, since $w = \nabla f(x) - \tilde \nabla f(x)$ is a random variable, it determines that $\tilde x$ is also a random variable related to $w$. 
+            Here, $x, z$ is not a random variable. 
+            We take the expectation on both sides and move things all to the RHS then it has 
+            \begin{align*}
+                0&\le 
+                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 
+                + \expect\left[
+                    \Vert w\Vert\Vert z - \tilde x\Vert
+                \right]
+                - \frac{B}{2}\expect \Vert z - \tilde x\Vert^2
+                \\
+                &= 
+                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 
+                + \expect\left[
+                    \Vert w\Vert\Vert z - \tilde x\Vert
+                    - \frac{B}{2} \Vert z - \tilde x\Vert^2
+                \right]
+                \\
+                &=
+                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 
+                    \\ &\quad 
+                    + \expect\left[
+                        - \frac{1}{2}\left(
+                            \sqrt{\epsilon}\Vert x - \tilde x\Vert - \sqrt{\epsilon}\Vert z - \tilde x\Vert
+                        \right)^2
+                        + \frac{\epsilon}{2}\Vert x - \tilde x\Vert^2 + \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2
+                        - \frac{B}{2} \Vert z - \tilde x\Vert^2
+                    \right]
+                \\
+                &\le 
+                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 
+                + \expect\left[
+                    \frac{\epsilon}{2}\Vert x - \tilde x\Vert^2
+                    - \frac{B - \epsilon}{2} \Vert z - \tilde x\Vert^2
+                \right]. 
+            \end{align*}
+        \end{proof}
+        \begin{remark}
+            In practice, is chosen in prior to satisfies $B \ge L$. 
+            In here, $z, x$ is not a random variable, $\epsilon$ just a constant, but it's determined by $z$ and $x$, one of the obvious choice for it in this lemma is
+            \begin{align*}
+                \frac{
+                \expect \left[
+                    \left\Vert \nabla f(x) - \tilde \nabla f(x) \right\Vert \Vert z - \tilde x\Vert
+                \right]
+                }{
+                \expect \left[
+                    \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert
+                \right]
+                } &= \epsilon. 
+            \end{align*}
+            Of course, look, if there is no random variable and $\tilde \nabla f(x)$ is simply not an probailistic estimate then the expectation is gone and, it has: 
+            \begin{align*}
+                \epsilon = \frac{\left\Vert
+                    \nabla f(x) - \tilde \nabla f(x)
+                \right\Vert}{\Vert x - \tilde x\Vert}.
+            \end{align*}
+            And in this case, it's NOT dependended on $z$. 
+        \end{remark}
 
-\section{Inexact accelerated proximal gradient algorithm}
+\section{Stochastic/Inexact accelerated proximal gradient algorithm}
     The following defines the inexact proximal gradient operator where the gradient of the smooth part of the function is estimated. 
@@
         \begin{align*}
-            \left\Vert \tilde \nabla f(x) - \nabla f(x)\right\Vert \le \epsilon \Vert x - \tilde x\Vert. 
+            \left\Vert \tilde \nabla f(x) - \nabla f(x)\right\Vert = \epsilon \Vert x - \tilde x\Vert. 
         \end{align*}
     \end{definition}
-    The inexact evaluation can be caused by an random variable. 
-    The definitions follow characterize algorithm in which the errors are related to a random variable that estimates the gradient of the objective function. 
+    The inexact evaluation can be caused by a random variable. 
+    The definition that follows characterize algorithm in which the errors are related to a random variable that estimates the gradient of the objective function. 
     % ------------------------------------------------------------------------------------------------------------------
     \begin{definition}[stochastic proximal gradient operator with relative error]
-
+        Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
+        Let $x \in \RR^n$ be fixed. 
+        Suppose that $\tilde \nabla f(x)$ is a random variable which is an estimate of the true gradient $\nabla f(x)$ and, let the constant $\epsilon \ge 0$ be defined as: 
+        \begin{align*}
+            \epsilon &=
+            \frac{
+            \expect \left[
+                \left\Vert \nabla f(x) - \tilde \nabla f(x) \right\Vert \Vert z - \tilde x\Vert
+            \right]
+            }{\expect \left[
+                \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert
+            \right]}. 
+        \end{align*}
+        Then the inexact proximal gradient operator with relative error $\epsilon$ is the random variable defined as: 
+        \begin{align*}
+            \widetilde T_B^{(\epsilon)} = \argmin_{z \in \RR^n}\left\lbrace
+                g(z) + \left\langle \tilde \nabla f(x), z - x\right\rangle
+                + \frac{B}{2}\Vert z - x\Vert^2
+            \right\rbrace. 
+        \end{align*}
     \end{definition}
@@
         \begin{align*}
-            & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \sigma^{(k)}\right)^{-1}, \\
+            & \tau_k = L(1 - \alpha_k)\left(L \alpha_k - \mu\right)^{-1}, \\
             & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
-            & x_k =  T_{L}^{(\epsilon_k)}(y_k | F_{I_k}), \\
+            & x_k =  T_{L}^{(\epsilon_k)}(y_k | F_{I_k}) \text{ or }, \widetilde T_{L}^{(\epsilon_k)}(y_k | F_{I_k})\\
             & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}).
@@
     The following lemma states two important relationships on the iterates generated by Definition \ref{def:SNAG}. 
+    Take note that it's only related to the iterates generated: $x_k, y_k, v_k$, it involves the sequence $(\alpha_k)_{k \ge 0}$, but the sequence can be anything in between $(0, 1]$ and these relations won't change.
     \begin{lemma}[SNAG identities]\label{lemma:snag-identities}
+        The iterates $(y_k, x_k, v_k)_{k \ge0}$ satisfying Definition \ref{def:SNAG} satisfies for all $k \ge 1$ the identities: 
+        \begin{enumerate}[nosep]
+            \item $z_k - y_k = (L - \mu)^{-1}((L\alpha_k - \mu)(\bar x - v_{k - 1}) + \mu(1 - \alpha_k)(\bar x - x_{k - 1})).$
+            \item $z_k - x_k = \alpha_k (\bar x - v_k).$
+        \end{enumerate}
+    \end{lemma}
+    \begin{proof}
+        We prove (i) first. 
+        Recall the definitions of $\tau_k$ from Definition \ref{def:SNAG}, it has: 
+        \begin{align*}
+            (1 + \tau_k)^{-1}
+            &=
+            \left(
+                1 + \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
+            \right)^{-1} = \left(
+                \frac{L\alpha_k - \mu + L(1 - \alpha_k)}{L\alpha_k - \mu}
+            \right)^{-1}
+            = \frac{L\alpha_k - \mu}{L - \mu}. 
+        \end{align*}
+        Therefore, for all $k \ge 0$, $y_k$ has 
+        \begin{align*}
+            0 &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1} - y_k
+            \\
+            &= \frac{L\alpha_k - \mu}{L - \mu} 
+            \left(
+                v_{k - 1} + \frac{L(1 - \alpha_k)}{L\alpha_k - \mu} x_{k - 1}
+            \right) - y_k
+            \\
+            &= \frac{L\alpha_k - \mu}{L - \mu} v_{k - 1}
+            + \frac{L(1 - \alpha_k)}{L - \mu} x_{k - 1} - y_k
+            \\
+            &= \frac{L\alpha_k - \mu}{L - \mu} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+            + 
+            \left(
+                \frac{L(1 - \alpha_k)}{L - \mu} - (1 - \alpha_k)
+            \right) x_{k - 1} - y_k
+            \\
+            &= \frac{L\alpha_k - \mu}{L - \mu} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+            + 
+            (1 - \alpha_k)\left(
+                \frac{L - L + \mu}{L - \mu}
+            \right) x_{k - 1} - y_k
+            \\
+            &= \frac{L\alpha_k - \mu}{L - \mu} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
+            + 
+            \frac{\mu(1 - \alpha_k)}{L - \mu}x_{k - 1} - y_k. 
+        \end{align*}
+        Therefore, we establish the equality 
+        \begin{align*}
+            (1 - \alpha_k)x_{k - 1} - y_k &= 
+            - \frac{L\alpha_k - \mu}{L - \mu} v_{k - 1} 
+            - \frac{\mu(1 - \alpha_k)}{L - \mu} x_{k - 1}. 
+        \end{align*}
+        On the second equality below, we will the above equality, it goes: 
+        \begin{align*}
+            z_k - y_k &= 
+            \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
+            \\
+            &= \alpha_k \bar x 
+            - \frac{L\alpha_k - \mu}{L - \mu} v_{k - 1} 
+            - \frac{\mu(1 - \alpha_k)}{L - \mu} x_{k - 1}
+            \\
+            &= \frac{L\alpha_k - \mu}{L - \mu}(\bar x - v_{k - 1})
+            + \left(
+                \alpha_k - \frac{L\alpha_k - \mu}{L - \mu}
+            \right)\bar x
+            - \frac{\mu(1 - \alpha_k)}{L - \mu} x_{k - 1}
+            \\
+            &= \frac{L\alpha_k - \mu}{L - \mu}(\bar x - v_{k - 1})
+            + \left(
+                \frac{\alpha_kL - \alpha_k \mu - L\alpha_k + \mu}{L - \mu}
+            \right)\bar x
+            - \frac{\mu(1 - \alpha_k)}{L - \mu} x_{k - 1}
+            \\
+            &= \frac{L\alpha_k - \mu}{L - \mu}(\bar x - v_{k - 1})
+            + \frac{\mu(1 - \alpha_k)}{L - \mu}\bar x
+            - \frac{\mu(1 - \alpha_k)}{L - \mu} x_{k - 1}
+            \\
+            &= \frac{L\alpha_k - \mu}{L - \mu}(\bar x - v_{k - 1})
+            + \frac{\mu(1 - \alpha_k)}{L - \mu}(\bar x - x_{k - 1}).
+        \end{align*}
+        To see item (ii), the proof is direct algebra: 
+        \begin{align*}
+            z_k - x_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
+            \\
+            &= \alpha_k \bar x + x_{k - 1} - x_k - \alpha_k x_{k - 1}
+            \\
+            &= \alpha_k(\bar x - \alpha_k^{-1}(x_k - x_{k - 1}) - x_{k - 1})
+            \\
+            &= \alpha_k (\bar x - v_k).
+        \end{align*}
+    \end{proof}
+    The following theorem given an inequality characterizing a descent relation for the SNAG algorithm. 
+    \begin{theorem}[SNAG descent lemma]\label{thm:snag-descent}
 
-    \end{lemma}
+    \end{theorem}
+    \begin{proof}
+        The following intermediate results will clear out some algebras, they are all proved by the end of the proof. 
+        \begin{enumerate}
+            \item [(a)] For all $k \ge 1$, it has $\frac{\mu^2(1 - \alpha_k)^2}{2(L - \mu)} - \frac{\mu\alpha_k(1 - \alpha_k)}{2} = \frac{(\alpha_k - 1)\mu\left(L\alpha_k - \mu\right)}{2\left(L - \mu\right)}$ using some algebra.
+            \item [(b)] We assumed that the sequence $(\alpha_k)_{k \ge 0}$ satisfies\\ for all $k \ge 1$: $\rho_{k - 1}(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}(\alpha_{k} - \mu/L)$. 
+            \item [(c)] Using (b) and some algebra, we have for all $k \ge 1$ the identity: \\
+            $\frac{(L\alpha_k - \mu)^2}{2(L - \mu)} - \frac{\alpha_{k - 1}^2 L \rho_{k - 1}(1 - \alpha_k)}{2} = \frac{(L\alpha_k - \mu)\mu(\alpha_k - 1)}{2(L - \mu)}$. 
+            \item [(d)] Using (a), and (c), we can derive for all $k\ge 1$, we have the following identity: 
+            \begin{align*}
+                & - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
+                + \frac{L - \mu}{2}\Vert z_k - y_k\Vert^2
+                \\ &= 
+                \frac{\alpha_{k - 1}^2L \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{(\alpha_k - 1)\mu(L\alpha_k - \mu)}{2(L - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2. 
+            \end{align*}
+        \end{enumerate}
+        Using intermediate results (a), (b), (c), (d), we can prove the claim in just a few steps. 
+        % INTERMEDIATE RESULTS 
+        \textbf{Proof of (a)}. 
+        Using basic algebra: 
+        \begin{align*}
+            & \frac{\mu^2(1 - \alpha_k)^2}{2(L - \mu)} 
+            - \frac{\mu\alpha_k(1 - \alpha_k)}{2}
+            \\
+            &= 
+            \frac{1}{2\left(L - \mu\right)}
+            \left(
+                \mu^2(1 - \alpha_k)^2
+                - \left(L - \mu\right)\mu \alpha_k(1 - \alpha_k)
+            \right)
+            \\
+            &= \frac{1 - \alpha_k}{2\left(L - \mu\right)}\left(
+                \mu^2 
+                - \mu^2\alpha_k 
+                - \left(L \mu \alpha_k - \mu^2 \alpha_k\right)
+            \right)
+            \\
+            &= 
+            \frac{1 - \alpha_k}{2(L - \sigma)}\left(
+                \mu^2 - L\left(\mu\right)\alpha_k
+            \right)
+            \\
+            &= 
+            \frac{(1 - \alpha_k)\mu\left(\mu - L\alpha_k\right)}
+            {2\left(L - \mu\right)}
+            \\
+            &= \frac{(\alpha_k - 1)\mu\left(L\alpha_k - \mu\right)}
+            {2\left(L - \mu\right)}. 
+        \end{align*}
+        % INTERMEDIATE RESULTS 
+        \textbf{Proof of (c)}. 
+        Using (b) and some algebra, we can derive: 
+        \begin{align*}
+            & \frac{(L\alpha_k - \mu)^2}{2(L - \mu)} - \frac{\alpha_{k - 1}^2 L \rho_{k - 1}(1 - \alpha_k)}{2}
+            \\
+            &= \frac{(L\alpha_k - \mu)^2}{2(L - \mu)} - \frac{L\alpha_k(\alpha_k - \mu/L)}{2}
+            \\
+            &= \frac{1}{2(L - \mu)}\left(
+                (L\alpha_k - \mu)^2 - (L - \mu)L\alpha_k(\alpha_k - \mu/L)
+            \right)
+            \\
+            &= 
+            \frac{1}{2(L - \mu)}\left(
+                (L\alpha_k - \mu)^2 - (L - \mu)\alpha_k(L\alpha_k - \mu)
+            \right)
+            \\
+            &= \frac{L\alpha_k - \mu}{2(L - \mu)}\left(
+                L\alpha_k - \mu - (L - \mu)\alpha_k
+            \right)
+            \\
+            &= \frac{L\alpha_k - \mu}{2(L - \mu)}\left(
+                \mu\alpha_k - \mu
+            \right)
+            \\
+            &= \frac{(L\alpha_k - \mu)\mu(\alpha_k - 1)}{2(L - \mu)}. 
+        \end{align*}
+        % INTERMEDIATE RESULTS 
+        \textbf{Proof of (d)}. 
+        {\allowdisplaybreaks
+        \begin{align*}
+            &- \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
+            + \frac{L - \mu}{2}\Vert z_k - y_k\Vert^2
+            \\
+            &\underset{\text{\circled{1}}}{=} 
+            -\frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
+            + \frac{L - \mu}{2}
+            \left\Vert 
+                \frac{L\alpha_k - \mu}{L - \mu}(\bar x - v_{k - 1}) + 
+                \frac{\mu(1 - \alpha_k)}{L - \mu}(\bar x - x_{k - 1})
+            \right\Vert^2
+            \\
+            &= 
+            - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
+            + \frac{(L\alpha_k - \mu)^2}{2(L - \mu)} \Vert \bar x - v_{k - 1}\Vert^2
+            \\
+            &\quad
+                + \frac{\mu^2(1 - \alpha_k)^2}{2(L - \mu)} \Vert \bar x - x_{k - 1}\Vert^2
+                + \frac{(L\alpha_k - \mu)\mu(1 - \alpha_k)}{L - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
+            \\
+            &= \left(
+                \frac{\mu^2(1 - \alpha_k)^2}{2(L - \mu)} - \frac{\mu\alpha_k(1 - \alpha_k)}{2}
+            \right)\Vert \bar x - x_{k - 1}\Vert^2
+                \\ &\quad 
+                + 
+                \left(
+                    \frac{(L\alpha_k - \mu)^2}{2(L - \mu)}
+                    - \frac{\alpha_{k - 1}^2L \rho_{k - 1}(1 - \alpha_k)}{2}
+                \right)\Vert \bar x - v_{k - 1}\Vert^2
+                \\ &\quad 
+                + \frac{\alpha_{k - 1}^2L \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{(L\alpha_k - \mu)\mu(1 - \alpha_k)}{L - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
+            \\
+            &\underset{\text{(a)}}{=} 
+            \frac{(\alpha_k - 1)\mu(L\alpha_k - \mu)}{2(L - \mu)}\Vert \bar x - x_{k - 1}\Vert^2
+            + 
+            \left(
+                \frac{(L\alpha_k - \mu)^2}{2(L - \mu)}
+                - \frac{\alpha_{k - 1}^2L \rho_{k - 1}(1 - \alpha_k)}{2}
+            \right)\Vert \bar x - v_{k - 1}\Vert^2
+            \\ &\quad 
+                + \frac{\alpha_{k - 1}^2L \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{(L\alpha_k - \mu)\mu(1 - \alpha_k)}{L - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
+            \\
+            &\underset{\text{(c)}}{=}
+            \frac{(\alpha_k - 1)\mu(L\alpha_k - \mu)}{2(L - \mu)}\Vert \bar x - x_{k - 1}\Vert^2
+            + 
+            \frac{\mu(L\alpha_k - \mu)(\alpha_k - 1)}{2(L - \mu)}\Vert \bar x - v_{k - 1}\Vert^2
+            \\ &\quad 
+                + \frac{\alpha_{k - 1}^2L \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{(L\alpha_k - \mu)\mu(1 - \alpha_k)}{L - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
+            \\
+            &= 
+            \frac{\alpha_{k - 1}^2L \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+            \\ & \quad
+                + \frac{(\alpha_k - 1)\mu(L\alpha_k - \mu)}{2(L - \mu)}\left(
+                    \Vert \bar x - x_{k - 1}\Vert^2 + \Vert \bar x - v_{k - 1}\Vert^2 - 2\langle\bar x - x_{k - 1},\bar x - v_{k - 1} \rangle
+                \right)
+            \\
+            &= \frac{\alpha_{k - 1}^2L \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+            + \frac{(\alpha_k - 1)\mu(L\alpha_k - \mu)}{2(L - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2. 
+        \end{align*}
+        }
+        At label \circled{1} we used results (i) from Lemma \ref{lemma:snag-identities}. 
+    \end{proof}
 

### 2025-07-16 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changse

@@
 \newcommand{\expect}{\ensuremath{\mathbb E}}
-\usepackage{tikz}\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=0.5pt](char) {#1};}}
+\usepackage{tikz}\newcommand*\circled[1]{
+    \text{
+        \hspace{-0.5em}\tikz[baseline=(char.base)]{
+            \node[shape=circle,draw,inner sep=0.6pt](char){#1};
+        }\hspace{-0.5em}
+    }
+}
 
@@
     \cite{bauschke_convex_2017}
-    Previously we got some results, but unfortunately it was incorrect and it was impossible to recover from the mistake. 
+    Previously we got some results, but unfortunately it was incorrect and, it was impossible to recover from the mistake. 
     \par
@@
         Suppose that one take $\tilde \nabla f(x)$ to be an estimate of $\nabla f(x)$ and use it for the proximal gradient operator to produce $\tilde x$, then: 
-        \begin{align*}
+        \begin{align}
             \mathbf 0 
@@
             \partial g(\tilde x) 
-            + \nabla f(x) + B(\tilde x - x).
-        \end{align*}
+            + \nabla f(x) + B(\tilde x - x).\label{eqn:stoch-grad-err-vec}
+        \end{align}
         In this case, it adds the interpretation that $w = \nabla f(x) - \tilde \nabla f(x)$. 
@@
             Fix any $x, z \in \RR^n$. 
-            Suppose that, a random variable $\tilde \nabla f(x)$ is used to estimate the proximal gradient operator and it produced an error $w$, and the estimate $\tilde x$. 
+            Suppose that, a random variable $\tilde \nabla f(x)$ is used to estimate the proximal gradient operator and, it produced an error $w$, and the estimate $\tilde x$ as defined in \ref{lemma:inex-pg-ineq-proto}.
+            Let $B \ge 0$ be constant such that $D_f(\tilde x,x)\le B/2 \Vert x - \tilde x\Vert^2$. 
             Then, it would have $w = \nabla f(x) - \tilde \nabla f(x)$. 
-            Let $B \ge 0$ be constant such that $D_f(\tilde x,x)\le B/2 \Vert x - \tilde x\Vert^2$. 
             Suppose that in addition, there exists $\epsilon \ge 0$ such that: 
@@
                     \Vert w\Vert \Vert z - \tilde x\Vert
-                \right] &\le \epsilon \expect \left[
+                \right] &\le 
+                \epsilon \expect \left[
                     \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert
@@
             \begin{align*}
-                &\le 
+                0 &\le 
                 F(z) + \expect F(\tilde x) + \frac{\max(B, L) - \mu}{2} \Vert z - x\Vert^2
                 - \frac{B - \epsilon}{2}\expect\left[\Vert z - \tilde x\Vert^2\right]
-                + \frac{\epsilon}{2} \left[\Vert x - \tilde x\Vert^2\right]. 
+                + \frac{\epsilon}{2} \expect\left[\Vert x - \tilde x\Vert^2\right]. 
             \end{align*}
@@
         \begin{proof}
+            The reason for $w = \nabla f(x) - \tilde \nabla f(x)$ is explained in \eqref{eqn:stoch-grad-err-vec}. 
             Using Lemma \ref{lemma:inex-pg-ineq-proto}, for any fixed $z$ it has: 
             \begin{align*}
-                \frac{B}{2}\Vert z - \tilde x\Vert &\le 
+                \frac{B}{2}\Vert z - \tilde x\Vert^2 &\le 
                 F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 - \langle w, z - \tilde x\rangle
@@
                 0&\le 
-                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 
+                F(z) - \expect F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 
                 + \expect\left[
@@
                 \\
+                &\le F(z) - \expect F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 
+                + \epsilon \expect \left[
+                    \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert
+                \right]
+                - \frac{B}{2}\expect \Vert z - \tilde x\Vert^2
+                \\
                 &= 
-                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 
+                F(z) - \expect F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 
                 + \expect\left[
-                    \Vert w\Vert\Vert z - \tilde x\Vert
+                    \epsilon\Vert w\Vert\Vert z - \tilde x\Vert
                     - \frac{B}{2} \Vert z - \tilde x\Vert^2
@@
                 &=
-                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 
+                F(z) - \expect F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 
                     \\ &\quad 
@@
                 &\le 
-                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 
+                F(z) - \expect F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 
                 + \expect\left[
@@
             \end{align*}
-            And in this case, it's NOT dependended on $z$. 
+            And in this case, it doesn't on $z$. 
         \end{remark}
@@
         \begin{align*}
-            \widetilde T_B^{(\epsilon)} = \argmin_{z \in \RR^n}\left\lbrace
+            \widetilde T_B^{(\epsilon)}(x| F) = \argmin_{z \in \RR^n}\left\lbrace
                 g(z) + \left\langle \tilde \nabla f(x), z - x\right\rangle
@@
         Using intermediate results (a), (b), (c), (d), we can prove the claim in just a few steps. 
+        For any fixed $\bar x \in \RR^n$. 
+        Define $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ for all $k \ge 0$. 
+        Consider the case for all $k \ge 1$. 
+        Let $\expect_{k}$ be the expectation conditioned on all $\tilde \nabla f(y_i)$ for $i = 0, 1, \ldots, k - 1$. 
+        We note that under this conditioning, the iterates $x_{k - 1}, v_{k - 1}, y_k$ are not random variables, but $x_k$, and $v_k$ are. 
+        The sequence $(\alpha_k)_{k \ge 0}, (\epsilon_k)_{k \ge 0}$ are also not random variables. 
+        \par
+        We use Lemma \ref{lemma:stoch-pg-ineq} with $x = y_k, z = z_k, \tilde x = x_{k}$ and, $B = L$ then it has: 
+        {\allowdisplaybreaks
+        \begin{align*}
+            0 &\le 
+            F(z_k) - \expect_{k - 1} F(x_k) 
+            + \frac{L - \mu}{2}\Vert z_k - y_k\Vert^2 
+            + \frac{\epsilon_k}{2}\expect_{k - 1} \left[\Vert y_k - x_k \Vert^2\right] 
+                \\&\quad
+                - \frac{L - \epsilon_k}{2}\expect_{k - 1} \left[\Vert z_k - x_k\Vert^2\right]
+            \\
+            &\underset{\circled{1}}{\le} 
+            \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - \expect_{k - 1} F(x_k) - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
+                \\&\quad 
+                + \frac{L - \mu}{2}\Vert z_k - y_k\Vert^2 
+                + \frac{\epsilon_k}{2}\expect_{k - 1} \left[\Vert y_k - x_k \Vert^2\right] 
+                - \frac{L - \epsilon_k}{2}\expect_{k - 1} \left[\Vert z_k - x_k\Vert^2\right]
+            \\
+            &\underset{\text{(d)}}{=}
+            \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - \expect_{k - 1} F(x_k) 
+                \\&\quad 
+                + \frac{\alpha_{k - 1}^2L \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{(\alpha_k - 1)\mu(L\alpha_k - \mu)}{2(L - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2
+                \\&\quad 
+                + \frac{\epsilon_k}{2}\expect_{k - 1} \left[\Vert y_k - x_k \Vert^2\right] 
+                - \frac{L - \epsilon_k}{2}\expect_{k - 1} \left[\Vert z_k - x_k\Vert^2\right]
+            \\&\underset{\textcolor{red}{(?)}}{\le}
+            \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - \expect_{k - 1} F(x_k) 
+                \\&\quad 
+                + \frac{\alpha_{k - 1}^2L \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{\epsilon_k}{2}\expect_{k - 1} \left[\Vert y_k - x_k \Vert^2\right] 
+                - \frac{L - \epsilon_k}{2}\expect_{k - 1} \left[\Vert z_k - x_k\Vert^2\right]
+            \\&= 
+            (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x)) + F(\bar x) - \expect_{k - 1}F(x_k)
+            \\&\quad 
+                + \frac{\alpha_{k - 1}^2L \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{\epsilon_k}{2}\expect_{k - 1} \left[\Vert y_k - x_k \Vert^2\right] 
+                - \frac{L - \epsilon_k}{2}\expect_{k - 1} \left[\Vert z_k - x_k\Vert^2\right]
+            \\&= 
+            (1 - \alpha_k)\left(
+                F(x_{k - 1}) - F(\bar x)
+                + \frac{\alpha_{k - 1}^2L\rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+            \right)
+                \\ &\quad 
+                + F(\bar x) - \expect_{k - 1}F(x_k) 
+                - \frac{L - \epsilon_k}{2}\expect_{k - 1} \left[\Vert z_k - x_k\Vert^2\right]
+            \\
+            &\underset{\circled{2}}{=} 
+            (1 - \alpha_k)\left(
+                F(x_{k - 1}) - F(\bar x)
+                + \frac{\alpha_{k - 1}^2L\rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+            \right)
+                \\ &\quad 
+                + F(\bar x) - \expect_{k - 1}F(x_k) 
+                - \frac{\alpha_k^2(L - \epsilon_k)}{2}\expect_{k - 1} \left[\Vert v_k - \bar x\Vert^2\right]. 
+        \end{align*}
+        }
+        \par
+        The above produces the following inequality: 
+        \begin{align}\begin{split}
+            & \expect_{k - 1}F(x_k) - F(\bar x) - \frac{\alpha_k^2(L - \epsilon_k)}{2}\expect_{k - 1} \left[\Vert v_k - \bar x\Vert^2\right]
+            \\
+            &\le 
+            (1 - \alpha_k)\left(
+                F(x_{k - 1}) - F(\bar x)
+                + \frac{\alpha_{k - 1}L\rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+            \right). 
+        \end{split}\end{align}
         % INTERMEDIATE RESULTS 
-        \textbf{Proof of (a)}. 
+        \par \textbf{Proof of (a)}. 
         Using basic algebra: 
+        {\allowdisplaybreaks
         \begin{align*}
@@
         \end{align*}
+        }
         % INTERMEDIATE RESULTS 
@@
         Using (b) and some algebra, we can derive: 
+        {\allowdisplaybreaks
         \begin{align*}

### 2025-07-17 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
             Let $x \in \RR^n$ be fixed. 
-            Suppose an inexact evaluation of proximal gradient operator at $x$ yield an approximation $\tilde x$, characterized by: 
+            Suppose an inexact evaluation of proximal gradient operator at $x$ yield an approximation $\tilde x$ such that: 
             \begin{align*}
-                & \exists: w \in \partial \left[
+                & (\exists w)(\exists \epsilon ): w \in \partial \left[
                     z \mapsto  g(z) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
-                \right](\tilde x)\; \text{s.t: } \Vert w\Vert \le \epsilon \Vert x - \tilde x\Vert. 
+                \right](\tilde x), \Vert w\Vert \le \epsilon \Vert x - \tilde x\Vert. 
             \end{align*}
@@
             \end{align*}
+            The smallest possible choice for $\epsilon$ when $x \neq \tilde x$ is $\epsilon = \Vert w\Vert/\Vert x - \tilde x\Vert$ and, if $x = \tilde x$ then $\epsilon = 0$ is the smallest. 
         \end{remark}
@@
             Fix any $x, z \in \RR^n$. 
-            Suppose that, a random variable $\tilde \nabla f(x)$ is used to estimate the proximal gradient operator and, it produced an error $w$, and the estimate $\tilde x$ as defined in \ref{lemma:inex-pg-ineq-proto}.
-            Let $B \ge 0$ be constant such that $D_f(\tilde x,x)\le B/2 \Vert x - \tilde x\Vert^2$. 
+            Suppose that, $\tilde \nabla f(x)$ is a random variable which estimates $\nabla f(x)$, cause proximal gradient operator to produce error $w$, and estimate $\tilde x$ as given by \ref{lemma:inex-pg-ineq-proto}.
+            Assume there exists $B \ge 0$ be constant such that $D_f(\tilde x,x)\le B/2 \Vert x - \tilde x\Vert^2$. 
             Then, it would have $w = \nabla f(x) - \tilde \nabla f(x)$. 
-            Suppose that in addition, there exists $\epsilon \ge 0$ such that: 
+            If in addition, there exists an $\epsilon \ge 0$: 
             \begin{align*}
@@
             \end{align*}
-            Then it makes the following inequality true: 
+            Then it has: 
             \begin{align*}
@@
             In practice, is chosen in prior to satisfies $B \ge L$. 
-            In here, $z, x$ is not a random variable, $\epsilon$ just a constant, but it's determined by $z$ and $x$, one of the obvious choice for it in this lemma is
+            In here, $z, x$ is not a random variable, $\epsilon$ just a constant, but it's determined by $z$ and $x$. 
+            Assuming $z \neq \tilde x$ and, $\tilde x \neq x$, then one of the smallest choice for it in this lemma is
             \begin{align*}
@@
             \end{align*}
-            Of course, look, if there is no random variable and $\tilde \nabla f(x)$ is simply not an probailistic estimate then the expectation is gone and, it has: 
+            Otherwise, $\epsilon = 0$ is an obvious choice and, it's the smallest. 
+            It depends on both $z$ and $x$. 
+            \par
+            Of course, look, if there is no random variable and $\tilde \nabla f(x)$ is simply not a probabilistic estimate then the expectation is gone and $x\neq \tilde x$, it has: 
             \begin{align*}
@@
         Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}, let $x \in \RR^n$ be fixed. 
-        Suppose that $\tilde \nabla f(x)$ is an estimate of the true gradient $\nabla f(x)$ with relative error $\epsilon \ge 0$. 
-        Then, the inexact proximal gradient operator is defined by: 
+        Suppose that $\tilde \nabla f(x)$ estimates $\nabla f(x)$. 
+        We define the inexact proximal gradient operator by the relationships between: 
+        \begin{enumerate}[nosep]
+            \item $\tilde x = \mathbf T_B^{(\epsilon)}(x | F)$ is an inexact output of proximal gradient operator by evaluating on $\tilde \nabla f(x)$. 
+            \item $B \ge 0$ is any constant such that it satisfies $D_f(\tilde x, x) \le B/2\Vert \tilde x - x\Vert^2$. 
+            \item $\epsilon \ge 0$ is a constant that quantifies the error of inexact evaluation. 
+        \end{enumerate}
+        Then, we define the error $\epsilon$ by: 
         \begin{align*}
-            T_B^{(\epsilon)}(x | F) = \argmin_{z \in \RR^n}\left\lbrace
+            \epsilon = \begin{cases}
+                \frac{\left\Vert \tilde \nabla f(x) - \nabla f(x)\right\Vert}{\Vert x - \tilde x\Vert} & \text{if } x \neq \tilde x, 
+                \\
+                0 & \text{else } x = \tilde x. 
+            \end{cases}
+        \end{align*}
+        And the inexact output is defined as: 
+        \begin{align*}
+            \tilde x = \mathbf T_B(x | F) = \argmin_{z \in \RR^n}\left\lbrace
                 g(z) + \left\langle \tilde \nabla f(x), z - x\right\rangle
@@
             \right\rbrace. 
-        \end{align*}
-        And it satisfies 
-        \begin{align*}
-            \left\Vert \tilde \nabla f(x) - \nabla f(x)\right\Vert = \epsilon \Vert x - \tilde x\Vert. 
         \end{align*}
@@
     % ------------------------------------------------------------------------------------------------------------------
-    \begin{definition}[stochastic proximal gradient operator with relative error]
+    \begin{definition}[stochastic proximal gradient operator with relative error]\label{def:stoch-pg-opt-rel-err}
         Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
         Let $x \in \RR^n$ be fixed. 
-        Suppose that $\tilde \nabla f(x)$ is a random variable which is an estimate of the true gradient $\nabla f(x)$ and, let the constant $\epsilon \ge 0$ be defined as: 
+        Suppose that $\tilde \nabla f(x)$ is random variable and, it estimates $\nabla f(x)$. 
+        Then stochastic proximal gradient operator are the relationships between
+        \begin{enumerate}[nosep]
+            \item $\tilde x= \mathbf{\widetilde T}_B(x| F)$, an inexact output of proximal gradient operator by evaluating on $\tilde \nabla f(x)$. 
+            \item $\epsilon$ an error which is pre-determined constant. 
+            \item Any $B \ge 0$ such that it satisfies $D_f(\tilde x, x) \le B/2\Vert x - \tilde x\Vert^2$. 
+        \end{enumerate}
+        Here, $\epsilon$ satisfies: 
         \begin{align*}
-            \epsilon &=
+            \epsilon 
+            &= 
+            \begin{cases}
                 \frac{
@@
                     \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert
-            \right]}. 
+                \right]} & \text{if } x \neq \tilde x \;\wedge\; z \neq \tilde x
+                \\
+                0 & \text{else }
+            \end{cases}
         \end{align*}
@@
         \begin{align*}
-            \widetilde T_B^{(\epsilon)}(x| F) = \argmin_{z \in \RR^n}\left\lbrace
+            \tilde x = \mathbf{\widetilde T}_B(x| F) = \argmin_{z \in \RR^n}\left\lbrace
                 g(z) + \left\langle \tilde \nabla f(x), z - x\right\rangle
@@
     \end{definition}
+    \begin{remark}
+        For this definition of the stochastic proximal gradient operator, Lemma \ref{lemma:stoch-pg-ineq} is applicable. 
+    \end{remark}
     % ------------------------------------------------------------------------------------------------------------------
@@
             & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
-            & x_k =  T_{L}^{(\epsilon_k)}(y_k | F_{I_k}) \text{ or }, \widetilde T_{L}^{(\epsilon_k)}(y_k | F_{I_k})\\
+            & x_k =  \mathbf T_{L}(y_k | F) \text{ or }, \mathbf{\widetilde T}_L(y_k | F)\\
             & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}).
@@
     \end{definition}
+    The following definition gives a momentum sequence where it makes the derivation of the convergence rate easier. 
+    % ------------------------------------------------------------------------------------------------------------------
+    \begin{definition}[relaxed momentum sequence]\label{def:relax-momen-seq}
+        Let $(\alpha_k)_{k \ge 0}$ be non-negative sequence. 
+        Let $L, \mu$ be some constant such that $L > \mu \ge 0$. 
+        It is a relaxed momentum sequence if the following conditions are satisfied: 
+        \begin{enumerate}[nosep]
+            \item $\alpha_0 \in (0, 1]$ and for all $k \ge 1$, it satisfies that $\alpha_k \in (\mu/L, 1)$. 
+        \end{enumerate}
+    \end{definition}
+    \begin{remark}
+        In the context of its usage, the constants $L, \mu$ are the Lipschitz smoothness constant  and, strong convexity constant associated with a smooth and strongly convex function. 
+    \end{remark}
+
+    % ------------------------------------------------------------------------------------------------------------------
+    \begin{lemma}[properties of the sequence]\label{lemma:seq-properties}
+
+    \end{lemma}
+    \subsection{building up the convergence results}
+        In this section we derive a generic convergence results. 
+        \par
         The following lemma states two important relationships on the iterates generated by Definition \ref{def:SNAG}. 
         Take note that it's only related to the iterates generated: $x_k, y_k, v_k$, it involves the sequence $(\alpha_k)_{k \ge 0}$, but the sequence can be anything in between $(0, 1]$ and these relations won't change.
+        % --------------------------------------------------------------------------------------------------------------
         \begin{lemma}[SNAG identities]\label{lemma:snag-identities}
@@
         The following theorem given an inequality characterizing a descent relation for the SNAG algorithm. 
+        % --------------------------------------------------------------------------------------------------------------
         \begin{theorem}[SNAG descent lemma]\label{thm:snag-descent}
-
+            Suppose the iterates sequence $(y_k, x_k, v_k)_{k\ge 0}$ are generated by algorithms satisfying Definition \ref{def:SNAG}. 
+            Assume that
+            \begin{enumerate}[nosep]
+                \item it uses stochastic proximal gradient operator as in Definition \ref{def:stoch-pg-opt-rel-err}, 
+                \item it is initialized with $v_{-1} = x_{-1}$, $\alpha_0 = 1$ and, the momentum sequence $(\alpha_k)_{k \ge 0}$ satisfies Definition \ref{def:relax-momen-seq}. 
+            \end{enumerate}
+            Define $\expect_{k}$ to be the expectation conditioned on $\tilde \nabla f(y_i)$ for $i = 1, 2, \ldots, k - 1$. 
+            Then for all $k \ge 1$, for all $\bar x \in \RR^n$ it satisfies the inequality: 
+            \begin{align*}
+                & \expect_kF(x_k) - F(\bar x) - \frac{\alpha_k^2(L - \epsilon_k)}{2}\expect_k \left[\Vert v_k - \bar x\Vert^2\right]
+                \\
+                &\le 
+                (1 - \alpha_k)\left(
+                    F(x_{k - 1}) - F(\bar x)
+                    + \frac{\alpha_{k - 1}L\rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                \right) + \frac{\epsilon_k}{2}\expect_k \left[\Vert y_k - x_k \Vert^2\right].  
+            \end{align*}
+            Define $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$.
+            Then, the error sequence $(\epsilon_k)_{k \ge 0}$ is given by: 
+            \begin{align*}
+                (\forall k \ge 1)\; \epsilon_k = 
+                \frac{\expect_k\left[
+                    \left\Vert
+                        \tilde \nabla f(y_k) - \nabla f(y_k)
+                    \right\Vert
+                    \Vert \bar x - v_{k}\Vert
+                \right]
+                }{
+                    \expect_k\left[
+                        \Vert \bar x - v_{k}\Vert
+                        \Vert z_k - y_k\Vert
+                    \right]
+                }. 
+            \end{align*}
         \end{theorem}
@@
             Consider the case for all $k \ge 1$. 
-        Let $\expect_{k}$ be the expectation conditioned on all $\tilde \nabla f(y_i)$ for $i = 0, 1, \ldots, k - 1$. 
-        We note that under this conditioning, the iterates $x_{k - 1}, v_{k - 1}, y_k$ are not random variables, but $x_k$, and $v_k$ are. 
+            Recall $\expect_{k}$ is the expectation conditioned on all $\tilde \nabla f(y_i)$ for $i = 0, 1, \ldots, k - 1$. 
+            We note that under this conditioning the only random variable is $\tilde \nabla f(y_k)$, so iterates $x_{k - 1}, v_{k - 1}, y_k$ are not random variables, but $x_k$, and $v_k$ are. 
             The sequence $(\alpha_k)_{k \ge 0}, (\epsilon_k)_{k \ge 0}$ are also not random variables. 
             \par
-        We use Lemma \ref{lemma:stoch-pg-ineq} with $x = y_k, z = z_k, \tilde x = x_{k}$ and, $B = L$ then it has: 
+            We use Lemma \ref{lemma:stoch-pg-ineq} with $x = y_k, z = z_k, \tilde x = x_{k}$ and, $B = L$ then it means: 
             {\allowdisplaybreaks
@@
                 0 &\le 
-            F(z_k) - \expect_{k - 1} F(x_k) 
+                F(z_k) - \expect_k F(x_k) 
                 + \frac{L - \mu}{2}\Vert z_k - y_k\Vert^2 
-            + \frac{\epsilon_k}{2}\expect_{k - 1} \left[\Vert y_k - x_k \Vert^2\right] 
+                + \frac{\epsilon_k}{2}\expect_k \left[\Vert y_k - x_k \Vert^2\right] 
                     \\&\quad
-                - \frac{L - \epsilon_k}{2}\expect_{k - 1} \left[\Vert z_k - x_k\Vert^2\right]
+                    - \frac{L - \epsilon_k}{2}\expect_k \left[\Vert z_k - x_k\Vert^2\right]
                 \\
                 &\underset{\circled{1}}{\le} 
-            \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - \expect_{k - 1} F(x_k) - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
+                \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - \expect_k F(x_k) - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
                     \\&\quad 
                     + \frac{L - \mu}{2}\Vert z_k - y_k\Vert^2 
-                + \frac{\epsilon_k}{2}\expect_{k - 1} \left[\Vert y_k - x_k \Vert^2\right] 
-                - \frac{L - \epsilon_k}{2}\expect_{k - 1} \left[\Vert z_k - x_k\Vert^2\right]
+                    + \frac{\epsilon_k}{2}\expect_k \left[\Vert y_k - x_k \Vert^2\right] 
+                    - \frac{L - \epsilon_k}{2}\expect_k \left[\Vert z_k - x_k\Vert^2\right]
                 \\
                 &\underset{\text{(d)}}{=}
-            \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - \expect_{k - 1} F(x_k) 
+                \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - \expect_k F(x_k) 
                     \\&\quad 
@@
                     \\&\quad 
-                + \frac{\epsilon_k}{2}\expect_{k - 1} \left[\Vert y_k - x_k \Vert^2\right] 
-                - \frac{L - \epsilon_k}{2}\expect_{k - 1} \left[\Vert z_k - x_k\Vert^2\right]
-            \\&\underset{\textcolor{red}{(?)}}{\le}
-            \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - \expect_{k - 1} F(x_k) 
+                    + \frac{\epsilon_k}{2}\expect_k \left[\Vert y_k - x_k \Vert^2\right] 
+                    - \frac{L - \epsilon_k}{2}\expect_k \left[\Vert z_k - x_k\Vert^2\right]
+                \\&\underset{\circled{2}}{\le}
+                \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - \expect_k F(x_k) 
                     \\&\quad 
                     + \frac{\alpha_{k - 1}^2L \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{\epsilon_k}{2}\expect_{k - 1} \left[\Vert y_k - x_k \Vert^2\right] 
-                - \frac{L - \epsilon_k}{2}\expect_{k - 1} \left[\Vert z_k - x_k\Vert^2\right]
+                    + \frac{\epsilon_k}{2}\expect_k \left[\Vert y_k - x_k \Vert^2\right] 
+                    - \frac{L - \epsilon_k}{2}\expect_k \left[\Vert z_k - x_k\Vert^2\right]
                 \\&= 
-            (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x)) + F(\bar x) - \expect_{k - 1}F(x_k)
+                (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x)) + F(\bar x) - \expect_kF(x_k)
                 \\&\quad 
                     + \frac{\alpha_{k - 1}^2L \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                + \frac{\epsilon_k}{2}\expect_{k - 1} \left[\Vert y_k - x_k \Vert^2\right] 
-                - \frac{L - \epsilon_k}{2}\expect_{k - 1} \left[\Vert z_k - x_k\Vert^2\right]
+                    + \frac{\epsilon_k}{2}\expect_k \left[\Vert y_k - x_k \Vert^2\right] 
+                    - \frac{L - \epsilon_k}{2}\expect_k \left[\Vert z_k - x_k\Vert^2\right]
                 \\&= 
@@
                     \\ &\quad 
-                + F(\bar x) - \expect_{k - 1}F(x_k) 
-                - \frac{L - \epsilon_k}{2}\expect_{k - 1} \left[\Vert z_k - x_k\Vert^2\right]
+                    + F(\bar x) - \expect_kF(x_k) 
+                    - \frac{L - \epsilon_k}{2}\expect_k \left[\Vert z_k - x_k\Vert^2\right]
+                    + \frac{\epsilon_k}{2}\expect_k \left[\Vert y_k - x_k \Vert^2\right] 
                 \\
-            &\underset{\circled{2}}{=} 
+                &\underset{\circled{3}}{=} 
                 (1 - \alpha_k)\left(
@@
                     \\ &\quad 
-                + F(\bar x) - \expect_{k - 1}F(x_k) 
-                - \frac{\alpha_k^2(L - \epsilon_k)}{2}\expect_{k - 1} \left[\Vert v_k - \bar x\Vert^2\right]. 
+                    + F(\bar x) - \expect_kF(x_k) 
+                    - \frac{\alpha_k^2(L - \epsilon_k)}{2}\expect_k \left[\Vert v_k - \bar x\Vert^2\right]
+                    + \frac{\epsilon_k}{2}\expect_k \left[\Vert y_k - x_k \Vert^2\right]. 
             \end{align*}
             }
+            \textcolor{red}{Explanations for \circled{1}, \circled{2}, \circled{3} are not done yet}. 
             \par
@@
             \begin{align}\begin{split}
-            & \expect_{k - 1}F(x_k) - F(\bar x) - \frac{\alpha_k^2(L - \epsilon_k)}{2}\expect_{k - 1} \left[\Vert v_k - \bar x\Vert^2\right]
+                & \expect_kF(x_k) - F(\bar x) - \frac{\alpha_k^2(L - \epsilon_k)}{2}\expect_k \left[\Vert v_k - \bar x\Vert^2\right]
                 \\
@@
                     + \frac{\alpha_{k - 1}L\rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
-            \right). 
+                \right) + \frac{\epsilon_k}{2}\expect_k \left[\Vert y_k - x_k \Vert^2\right]. 
             \end{split}\end{align}
@@
 
+\subsection{Discussion}
+
 \bibliographystyle{siam}

### 2025-07-18 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
 \newcommand{\expect}{\ensuremath{\mathbb E}}
+\newcommand{\prob}{\ensuremath{\mathbb P}}
+\newcommand{\dist}{\ensuremath{\operatorname{dist}}}
 \usepackage{tikz}\newcommand*\circled[1]{
@@
     When two expressions are connected via non-trivial results, it's expressed with $\underset{(\cdot)}{=}, \underset{(\cdot)}{\ge}$ where $(\cdot)$ is a label of some intermediate results immediately before it, or explained right after a chain of expressions.
-    If the label is letter, like: (a), (b), ..., then they are stated in advanced at the start of the proof and they are usually non-trivial results. 
+    If the label is letter, like: (a), (b), ..., then they are stated in advanced at the start of the proof and, they are usually non-trivial results. 
     These labels are reused in every proof. 
@@
             In the context where it's clear what the function $F = f + g$ is, we simply write $T_\beta(x)$ for short. 
+            Note, it also has $T_\beta(x | f + g) = \hprox_{\beta^{-1}g}(x - \beta^{-1}\nabla f(x))$ in optimization literatures. 
         \end{remark}
@@
         \end{definition}
+        % --------------------------------------------------------------------------------------------------------------
+        \begin{definition}[Relative proximal gradient error ruler]\label{def:pg-err-ruler}
+            Let $F$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
+            Fix any $x \in \RR^n$, suppose that $\tilde x$ is an estimated of $T_B(x|F)$. 
+            Then the relative proximal gradient error is a set defined as
+            \begin{align*}
+                S_B(\tilde x, x | F) := 
+                \partial \left[
+                    z \mapsto \partial g(x) + \langle \nabla f(x), z - x\rangle + 
+                    \frac{B}{2}\Vert x - z\Vert^2
+                \right](\tilde x). 
+            \end{align*}
+        \end{definition}
+        \begin{remark}
+            The definition exists to simplifies the notations for the discussions. 
+            When $B > 0$ by strong convexity, the set $\{z : \mathbf 0 \in S_B(z, x | F)\}$ is a singleton, conveniently. 
+        \end{remark}
     \subsection{Important inequalities}
@@
             Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
-            Fix some $x \in \RR^n$, and suppose that an error: $w$ is made when estimating the proximal to obtain $\tilde x$ at $x$ such that it's characterized by
-            \begin{align*}
-                w \in \partial \left[
-                    z \mapsto g(z) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
-                \right](\tilde x)
-            \end{align*}
-            And in addition, assume that there exists some $B \ge 0$ such that $D_f(\tilde x, x) \le \frac{B}{2}\Vert \tilde x - x\Vert^2$. 
-            Then, for all $z \in \RR^n$ it satisfies: 
+            Fix any $x \in \RR^n$ there exists a $B \ge 0$,  $\tilde x$ be an estimate of $T_B(x | F)$ such that $D_f(\tilde x, x) \le B/2\Vert x - \tilde x\Vert^2$. 
+            Let $S_B(\tilde x, x | F)$ be given by Definition \ref{def:pg-err-ruler}. 
+            Then, for all $z \in \RR^n$ and, any $w \in S_B(\tilde x, x | F)$ it satisfies: 
             \begin{align*}
@@
         \begin{proof}
+            Since $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}, for all $B \ge L$, it will be an obvious choice. 
             The proof is direct algebra. 
@@
             Let $F = f + g$ satisfies Definition \ref{def:lip-smooth-and-scnvx} with $L > \mu \ge 0$. 
-            Let $x \in \RR^n$ be fixed. 
-            Suppose an inexact evaluation of proximal gradient operator at $x$ yield an approximation $\tilde x$ such that: 
-            \begin{align*}
-                & (\exists w)(\exists \epsilon ): w \in \partial \left[
-                    z \mapsto  g(z) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
-                \right](\tilde x), \Vert w\Vert \le \epsilon \Vert x - \tilde x\Vert. 
-            \end{align*}
-            Suppose that there exists some $B \ge 0$ such that $D_f(\tilde x, x) \le \frac{B}{2}\Vert \tilde x - x\Vert^2$. 
+            Fix arbitrary $x \in \RR^n$. 
+            Assume the followings: 
+            \begin{enumerate}[nosep]
+                \item $\tilde x$ estimates $T_B(x | F)$. 
+                \item $B \ge 0$ satisfies $D_f(\tilde x, x) \le B/2\Vert x - \tilde x\Vert^2$. 
+                \item Let $S_B(\tilde x, x | F)$ be given by Definition \ref{def:pg-err-ruler}. 
+            \end{enumerate}
+            Let $\epsilon \ge 0$ be such that $\Vert x - \tilde x\Vert\epsilon \ge \dist(\mathbf 0 |S_B(\tilde x, x | F))$.
             Then, for all $z\in \RR^n$ it satisfies the inequality: 
@@
                 &\underset{\text{\circled{1}}}{\le}
+                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 
+                + \Vert w\Vert \Vert z - \tilde x\Vert. 
+            \end{align*}
+            At \circled{1}, we used Cauchy inequality. 
+            Since this is true for all $w \in S_B(\tilde x, x | F)$, it has: 
+            \begin{align*}
+                \frac{B}{2}\Vert z - \tilde x\Vert^2
+                &\le F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 
+                + \dist(\mathbf 0 | S_B(\tilde x, x | F))\Vert z - \tilde x\Vert
+                \\
+                &\le
                 F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 + \epsilon \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert. 
             \end{align*}
-            At \circled{1}, we used Cauchy inequality. 
             Continuing it has 
@@
         The following lemma gives a proximal gradient inequality when $\tilde \nabla f(x)$ is an estimate by some random variable, \textbf{and it is the precursor.} 
-        \begin{lemma}[stochastic proximal gradient inequality]\label{lemma:stoch-pg-ineq}
+        \begin{lemma}[proximal stochastic gradient inequality]\label{lemma:pg-stoch-ineq}
             Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
             Fix any $x, z \in \RR^n$. 
-            Suppose that, $\tilde \nabla f(x)$ is a random variable which estimates $\nabla f(x)$, cause proximal gradient operator to produce error $w$, and estimate $\tilde x$ as given by \ref{lemma:inex-pg-ineq-proto}.
-            Assume there exists $B \ge 0$ be constant such that $D_f(\tilde x,x)\le B/2 \Vert x - \tilde x\Vert^2$. 
-            Then, it would have $w = \nabla f(x) - \tilde \nabla f(x)$. 
-            If in addition, there exists an $\epsilon \ge 0$: 
+            Assume the following
+            \begin{enumerate}[nosep]
+                \item $\tilde \nabla f(x)$ is a random variable which estimates $\nabla f(x)$, which produces the estimate $\tilde x$. 
+                \item There exists $B \ge 0$ such that $D_f(\tilde x,x)\le B/2 \Vert x - \tilde x\Vert^2$. 
+            \end{enumerate}
+            If in addition, there exists some $\epsilon \ge 0$: 
             \begin{align*}
                 \expect \left[
-                    \Vert w\Vert \Vert z - \tilde x\Vert
+                    \left\Vert \nabla f(x) - \tilde \nabla f(x)\right\Vert 
+                    \Vert z - \tilde x\Vert
                 \right] &\le 
@@
         \begin{proof}
-            The reason for $w = \nabla f(x) - \tilde \nabla f(x)$ is explained in \eqref{eqn:stoch-grad-err-vec}. 
+            The can choose $w = \nabla f(x) - \tilde \nabla f(x) \in S_B(\tilde x, x | F)$ which is explained in \eqref{eqn:stoch-grad-err-vec}. 
             Using Lemma \ref{lemma:inex-pg-ineq-proto}, for any fixed $z$ it has: 
@@
                 &\le 
-                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 + \Vert w\Vert\Vert z - \tilde x\Vert. 
+                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 + \Vert w\Vert\Vert z - \tilde x\Vert
+                \\
+                &= 
+                F(z) - F(\tilde x) 
+                + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 
+                + \left\Vert \nabla f(x) - \tilde \nabla f(x)\right\Vert\Vert z - \tilde x\Vert. 
             \end{align*}
@@
                 + \expect\left[
-                    \epsilon\Vert w\Vert\Vert z - \tilde x\Vert
+                    \epsilon\Vert x - \tilde x\Vert\Vert z - \tilde x\Vert
                     - \frac{B}{2} \Vert z - \tilde x\Vert^2
@@
         \end{proof}
-        \begin{remark}
         In practice, is chosen in prior to satisfies $B \ge L$. 
@@
         \end{align*}
-            Otherwise, $\epsilon = 0$ is an obvious choice and, it's the smallest. 
         It depends on both $z$ and $x$. 
+        Let's think about the edge case. 
+        When $\expect [\Vert x - \tilde x\Vert\Vert z - \tilde x\Vert] = 0$, it must be that both $\Vert x - \tilde x\Vert,\Vert z - \tilde x\Vert$ are zero, indicating that $\nabla f(x) = \tilde \nabla f(x)$ and, $x = \tilde x = z$.
+        Otherwise we can assume $\prob(\Vert x - \tilde x\Vert\Vert z - \tilde x\Vert > 0) > 0$ and, the expectation has: 
+        \begin{align*}
+            & \expect \left[
+                \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert
+            \right] 
+            \\&= 
+            \expect\left[
+                \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert \;|\; 
+                \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert > 0
+            \right]\prob(
+                \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert > 0
+            ). 
+        \end{align*}
+        Let's suppose that $\tilde \nabla f(x)$ is a random variable comes from the space: $\Omega(x)$, then it has the following: 
+        {\small
+        \begin{align*}
+            & \expect \left[
+                \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert \; | \; 
+                \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert > 0
+            \right] 
+            \\
+            &\ge
+            \min_{y \in \Omega(x)}\left\lbrace
+                \Vert x - \tilde x\Vert
+                :x\neq \tilde x = \argmin_{z}\left\lbrace
+                    g(z) + \langle y, z\rangle + \frac{B}{2}\Vert z - x\Vert^2
+                \right\rbrace
+            \right\rbrace
+            \prob(
+                \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert > 0
+            )
+            \expect\Vert z - \tilde x\Vert, 
+            \\
+            & \expect \left[
+                \left\Vert \nabla f(x) - \tilde \nabla f(x) \right\Vert \Vert z - \tilde x\Vert
+            \right]
+            \\
+            &\le 
+            \max_{y \in \Omega(x)}\left\lbrace
+                \Vert \nabla f(x) - y\Vert 
+            \right\rbrace\expect\Vert z - \tilde x \Vert, 
+        \end{align*}
+        }
+        And it would mean: 
+        {\small
+        \begin{align*}
+            \epsilon &= 
+            \frac{
+                \expect \left[
+                    \left\Vert  \nabla f(x) - \tilde \nabla f(x) \right\Vert \Vert z - \tilde x\Vert
+                \right]
+            }{
+            \expect \left[
+                \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert
+            \right]
+            }\\
+            &\le \frac{
+                \max_{y \in \Omega(x)}\Vert \nabla f(x) - y\Vert 
+            }{
+                \min_{y \in \Omega(x)}\left\lbrace
+                    \Vert x - \tilde x\Vert:
+                    x\neq \tilde x = \argmin_{z}\left\lbrace
+                    g(z) + \langle y, z\rangle + \frac{B}{2}\Vert z - x\Vert^2
+                \right\rbrace
+                \right\rbrace
+                \prob(
+                    \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert > 0
+                )
+            }. 
+        \end{align*}
+        }
         \par
@@
         \end{align*}
-            And in this case, it doesn't on $z$. 
-        \end{remark}
+        And in this case, it has nothing to do with $z$.
 
@@
     % ------------------------------------------------------------------------------------------------------------------
-    \begin{definition}[inexact proximal gradient operator with relative error]
+    \begin{definition}[proximal inexact gradient operator with relative error]
         Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}, let $x \in \RR^n$ be fixed. 
@@
         \begin{enumerate}[nosep]
-            \item $\tilde x = \mathbf T_B^{(\epsilon)}(x | F)$ is an inexact output of proximal gradient operator by evaluating on $\tilde \nabla f(x)$. 
+            \item $\tilde x = \mathbf T_B(x | F)$ is an inexact output of proximal gradient operator by evaluating on $\tilde \nabla f(x)$. 
             \item $B \ge 0$ is any constant such that it satisfies $D_f(\tilde x, x) \le B/2\Vert \tilde x - x\Vert^2$. 
@@
         \end{enumerate}
-        Then, we define the error $\epsilon$ by: 
+        Then, we define the relative error $\epsilon$ by: 
         \begin{align*}
@@
                 \\
-                0 & \text{else } x = \tilde x. 
+                \infty & \text{if } x = \tilde x, \nabla f(x) \neq \tilde \nabla f(x), 
+                \\
+                0 & \text{if } x = \tilde x, \nabla f(x) = \tilde \nabla f(x). 
             \end{cases}
@@
             \item $\tilde x= \mathbf{\widetilde T}_B(x| F)$, an inexact output of proximal gradient operator by evaluating on $\tilde \nabla f(x)$. 
-            \item $\epsilon$ an error which is pre-determined constant. 
             \item Any $B \ge 0$ such that it satisfies $D_f(\tilde x, x) \le B/2\Vert x - \tilde x\Vert^2$. 
+            \item $\epsilon$ is an relative error, determined by $z, x, \tilde\nabla f(x)$ and, defined immediately below. 
         \end{enumerate}
-        Here, $\epsilon$ satisfies: 
+        The relative error $\epsilon$ is defined as: 
         \begin{align*}
@@
                     \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert
-                \right]} & \text{if } x \neq \tilde x \;\wedge\; z \neq \tilde x
+                \right]} 
+                & \text{if } \expect\left[\Vert x - \tilde x\Vert\Vert z - \tilde x\Vert\right] \neq 0, 
+                \vspace{0.5em}
                 \\
-                0 & \text{else }
+                \left.\begin{cases}
+                    0 & \expect \left[\left\Vert \nabla f(x) - \tilde \nabla f(x) \right\Vert \Vert z - \tilde x\Vert\right] = 0, 
+                    \\
+                    \infty & \text{else. } 
+                \end{cases}\right\rbrace
+                & \text{else. }
             \end{cases}
@@
     \begin{remark}
-        For this definition of the stochastic proximal gradient operator, Lemma \ref{lemma:stoch-pg-ineq} is applicable. 
+        For this definition of the stochastic proximal gradient operator, Lemma \ref{lemma:pg-stoch-ineq} is applicable. 
     \end{remark}
@@
     \end{remark}
-
+    The following lemma defines the conditions required for the a momentum sequence to be compatible with convergence claims. 
     % ------------------------------------------------------------------------------------------------------------------
-    \begin{lemma}[properties of the sequence]\label{lemma:seq-properties}
-
+    \begin{lemma}[relaxed momentum sequence conditions]\label{lemma:seq-properties}
+        \todoinline{NOT FINISHED YET!!!}
     \end{lemma}
-    \subsection{building up the convergence results}
+    \begin{proof}
+    \end{proof}
+    \subsection{Building up the convergence results}
         In this section we derive a generic convergence results. 
@@
             \end{align*}
-            Define $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$.
-            Then, the error sequence $(\epsilon_k)_{k \ge 0}$ is given by: 
-            \begin{align*}
-                (\forall k \ge 1)\; \epsilon_k = 
-                \frac{\expect_k\left[
-                    \left\Vert
-                        \tilde \nabla f(y_k) - \nabla f(y_k)
-                    \right\Vert
-                    \Vert \bar x - v_{k}\Vert
-                \right]
-                }{
-                    \expect_k\left[
-                        \Vert \bar x - v_{k}\Vert
-                        \Vert z_k - y_k\Vert
-                    \right]
-                }. 
-            \end{align*}
         \end{theorem}
@@
             \par
-            We use Lemma \ref{lemma:stoch-pg-ineq} with $x = y_k, z = z_k, \tilde x = x_{k}$ and, $B = L$ then it means: 
+            We use Lemma \ref{lemma:pg-stoch-ineq} with $x = y_k, z = z_k, \tilde x = x_{k}$ and, $B = L$ then it means: 
             {\allowdisplaybreaks
@@
 
-\subsection{Discussion}
+\section{Discussion, interpolation helps but it's not enough}
+    \subsection{The no error case}
+    \subsection{The degenerate case}
 

### 2025-07-18 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes, fixes

@@
     \end{remark}
-    The following lemma defines the conditions required for the a momentum sequence to be compatible with convergence claims. 
+    The following lemma defines the conditions required for the momentum sequence to be compatible with convergence claims. 
     % ------------------------------------------------------------------------------------------------------------------
     \begin{lemma}[relaxed momentum sequence conditions]\label{lemma:seq-properties}
-        \todoinline{NOT FINISHED YET!!!}
+        Let $(\alpha_k)_{k \ge 0}$, $L, \mu$ to be two constant such that it has $L > \mu \ge 0$. 
+        If we assume that the sequence has for all $k \ge 0: \alpha_k \ge \mu/L$, then we can define a positive sequence 
+        \begin{align*}
+            (\forall k \ge 1): \rho_{k - 1} = \frac{\alpha_k(\alpha_k - \mu/L)}{(1 - \alpha_k)\alpha_{k - 1}^2}. 
+        \end{align*}
+        And under this relationship, the followings are true inductively: 
+        \begin{enumerate}[nosep]
+            \item In general, for all $\rho_{k - 1} \ge 0$, it has $0\le \alpha_k \le \min\left(1, |\rho\alpha^2 - q| + \sqrt{\rho}\alpha\right)$. 
+            \item If $\alpha_{k - 1} \ge \mu/L$, then $\alpha_k \ge \mu/L$ too. 
+            \item If $\alpha_{k - 1} > \mu/L > 0$, then $\alpha_k \in (\mu/L, 1)$ for all $\rho_{k - 1} > 0$. 
+        \end{enumerate}
     \end{lemma}
     \begin{proof}
+        \textbf{Proof of item (i), (iii)}. 
+        With $\rho_{k - 1}(1 - \alpha_k)\alpha_{k - 1}^2 = \alpha_k(\alpha_k - \mu/L)$ it gives: 
+        \begin{align*}
+            \alpha_k 
+            &= \frac{1}{2}\left(
+                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2
+                + \sqrt{
+                    \left(
+                        \rho_{k - 1}\alpha_{k - 1}^2 - \frac{\mu}{L}
+                    \right)^2 
+                    + 4\rho_{k - 1}\alpha_{k - 1}^2
+                }
+            \right)
+            > 0. 
+        \end{align*}
+        Focusing exclusively on the RHS, we omit the subscript and write $\alpha_{k - 1}, \rho_{k - 1}$ as $\alpha, \rho$. 
+        We also just write $q = \mu / L$. 
+        By definition, we have $L > \mu \ge 0$ hence, $q \in [0, 1)$.
+        We also note that the quantity $(r \alpha^2 + q)^2 + 4\rho \alpha$ is clearly $> 0$. 
+        We will show that there is an upper bound for the RHS in terms of $\rho, q$. 
+        Completing the square should give
+        \begin{align*}
+            0 &\le 
+            \left(
+                \rho \alpha^2 - q
+            \right)^2 + 4 \rho \alpha^2
+            \\
+            &= \rho^2\alpha^4 + q^2 - 2\rho\alpha^2q + 4 \rho \alpha^2
+            \\
+            &= \rho^2\alpha^4 + 2\rho(2 - q)\alpha^2 + q^2
+            \\
+            &= 
+            \rho^2\alpha^4 + 2\rho(2 - q)\alpha^2 
+            + \rho^2(2 - q)^2
+            - \rho^2(2 - q)^2
+            + q^2
+            \\
+            &= (\rho\alpha^2 + \rho(2 - q))^2 - \rho^2 (2 - q)^2 + q^2
+            \\
+            &= \rho^2(\alpha^2 + 2 - q)^2 
+            + q^2 
+            - \rho^2 (2 - q)^2
+            \\
+            &\le 
+            \rho^2(\alpha^2 + 2 - q)^2 
+            + \max(0, q^2 - \rho^2 (2 - q)^2). 
+        \end{align*}
+        The above is non-negative, taking the square root it has: 
+        \begin{align*}
+            \sqrt{\left(\rho \alpha^2 - q\right)^2 + 4 \rho \alpha^2} 
+            &\le 
+            \rho|\alpha^2 + 2 - q| 
+            + \sqrt{\max(0, q^2 - \rho^2 (2 - q)^2)}
+            \\
+            &\le 
+            \rho|\alpha^2 + 2 - q| 
+        \end{align*}
+        But look, if we directly apply the $\sqrt{a + b} \le \sqrt{a} + \sqrt{b}$ it has another upper bound which is: 
+        \begin{align}\label{ineq:seq-properties-pr3}
+            \sqrt{\left(\rho \alpha^2 - q\right)^2 + 4 \rho \alpha^2} 
+            &\le 
+            |\rho\alpha^2 - q| + 2\sqrt{\rho}\alpha. 
+        \end{align}
+        Both upper bounds apply and hence we have: 
+        \begin{align*}
+            \alpha_k 
+            &\le
+            \frac{1}{2}\left(
+                q - \rho\alpha^2 + \min\left(
+                    \rho|\alpha^2 + 2 - q|  , 
+                    |\rho\alpha^2 - q| + 2\sqrt{\rho}\alpha
+                \right)
+            \right)
+            \\
+            &= 
+            \frac{1}{2}\left(
+                q - \rho\alpha^2 + \min\left(
+                    \rho\alpha^2 + (2 - q)  , 
+                    |\rho\alpha^2 - q| + 2\sqrt{\rho}\alpha
+                \right)
+            \right)
+            \\
+            &= 
+            \frac{1}{2}\left(
+                \min\left(
+                    2, 
+                    |\rho\alpha^2 - q| + 2\sqrt{\rho}\alpha + q - \rho\alpha^2
+                \right)
+            \right)
+            \\
+            &= 
+            \min\left(
+                    1, 
+                    (1/2)|\rho\alpha^2 - q| + \sqrt{\rho}\alpha + (1/2)(q - \rho\alpha^2)
+                \right)
+            \\
+            &\le \min\left(
+                1, 
+                |\rho\alpha^2 - q| + \sqrt{\rho}\alpha
+            \right). 
+        \end{align*}
+        \par
+        \textbf{Proof of (ii)}. 
+        To see the lower bound, we assume that $\alpha_k \ge \mu/L$ , denote $\mu/L$ by $q$, we have the following: 
+        \begin{align}\label{ineq:seq-properties-pr5}
+            \alpha_k - q 
+            \underset{\circled{1}}{\ge} \alpha_k(\alpha_k - q) 
+            = \rho_{k - 1}(1 - \alpha_k)\alpha_{k - 1}^2
+            \underset{\circled{2}}{\ge} \rho_{k - 1}(1 - \alpha_k)q^2 \ge 0. 
+        \end{align}
+        At \circled{1}, we used the fact that $\alpha_k \le 1$ and $\alpha_k \ge 0$ from previous results. 
+        At \circled{2}, we used the assumption that $\alpha_{k - 1} \ge q \ge 0$. 
+        The last inequality is true because is $\rho_{k - 1} \ge 0, \alpha_k \le 1$. 
+        \par
+        \textbf{Proof of (iii)}. 
+        In addition, if $\alpha > \mu/L >  0$, then the inequality in \eqref{ineq:seq-properties-pr3} is strict, then it would instead make $\alpha_k < 1$. 
+        It will also make the inequality chain in \eqref{ineq:seq-properties-pr5} strict. 
+        Therefore, Item (iii) is true. 
     \end{proof}
@@
             \begin{align}\begin{split}
-                & \expect_kF(x_k) - F(\bar x) - \frac{\alpha_k^2(L - \epsilon_k)}{2}\expect_k \left[\Vert v_k - \bar x\Vert^2\right]
+                & \expect_kF(x_k) - F(\bar x) 
+                + \frac{\alpha_k^2(L - \epsilon_k)}{2}\expect_k \left[\Vert v_k - \bar x\Vert^2\right]
                 \\

### 2025-07-19 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w< finally working

@@
                 0 &\le 
-                F(z) + \expect F(\tilde x) + \frac{\max(B, L) - \mu}{2} \Vert z - x\Vert^2
+                F(z) - \expect F(\tilde x) + \frac{\max(B, L) - \mu}{2} \Vert z - x\Vert^2
                 - \frac{B - \epsilon}{2}\expect\left[\Vert z - \tilde x\Vert^2\right]
@@
         When $\expect [\Vert x - \tilde x\Vert\Vert z - \tilde x\Vert] = 0$, it must be that both $\Vert x - \tilde x\Vert,\Vert z - \tilde x\Vert$ are zero, indicating that $\nabla f(x) = \tilde \nabla f(x)$ and, $x = \tilde x = z$.
-        Otherwise we can assume $\prob(\Vert x - \tilde x\Vert\Vert z - \tilde x\Vert > 0) > 0$ and, the expectation has: 
+        Otherwise, we can assume $\prob(\Vert x - \tilde x\Vert\Vert z - \tilde x\Vert > 0) > 0$ and, the expectation has: 
         \begin{align*}
@@
             \begin{align*}
-                & \expect_kF(x_k) - F(\bar x) - \frac{\alpha_k^2(L - \epsilon_k)}{2}\expect_k \left[\Vert v_k - \bar x\Vert^2\right]
+                & \expect_kF(x_k) - F(\bar x) 
+                + \frac{\alpha_k^2(L - \epsilon_k)}{2}\expect_k \left[\Vert v_k - \bar x\Vert^2\right]
                 \\
@@
                     F(x_{k - 1}) - F(\bar x)
-                    + \frac{\alpha_{k - 1}L\rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                \right) + \frac{\epsilon_k}{2}\expect_k \left[\Vert y_k - x_k \Vert^2\right].  
+                    + \frac{\alpha_{k - 1}^2L\rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                \right) 
+                + \frac{\epsilon_k}{2}\expect_k \left[\Vert y_k - x_k \Vert^2\right].  
+            \end{align*}
+            In the edge case of $k = 0$, it has: 
+            \begin{align*}
+                \expect_0 F(x_0) - F(\bar x)  
+                + \frac{L - \epsilon}{2}\expect_0\left[\Vert \bar x - x_0\Vert^2\right]
+                &\le 
+                \frac{L - \mu}{2} \Vert \bar x - v_{-1}\Vert^2
+                + \frac{\epsilon}{2}\expect_0\left[\Vert v_{-1} - x_0\Vert^2\right]. 
             \end{align*}
@@
             }
-            \textcolor{red}{Explanations for \circled{1}, \circled{2}, \circled{3} are not done yet}. 
-            \par
-            The above produces the following inequality: 
+            At \circled{1}, we used Lemma \ref{thm:jesen}. 
+            For \circled{3}, we used Lemma \ref{lemma:seq-properties} (i) and (b) because the sequence $\alpha_k \le 1$, therefore $1 - \alpha_k \le 1$. 
+            Next, $\alpha_0 = 1 > \mu/L$, Lemma \ref{lemma:seq-properties} (ii) applies too, hence it also has $L\alpha_k - \mu \ge 0$. 
+            Since $L > \mu$ always, the coefficient on $\Vert x_{k - 1} - v_{k - 1}\Vert^2$ is always $\le 0$, therefore the term can be removed to give an inequality. 
+            At \circled{3}, we used Lemma \ref{lemma:snag-identities} (ii). 
+            Therefore, at the end the chain of inequalities from above produced the following inequality: 
             \begin{align}\begin{split}
@@
                     F(x_{k - 1}) - F(\bar x)
-                    + \frac{\alpha_{k - 1}L\rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                    + \frac{\alpha_{k - 1}^2L\rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
                 \right) + \frac{\epsilon_k}{2}\expect_k \left[\Vert y_k - x_k \Vert^2\right]. 
             \end{split}\end{align}
+            Next, we handle the Edge case of $k = 0$. 
+            The base case has $\alpha_0 = 1$, and $v_{-1} = x_{-1}$. 
+            Then, the following consequences will be immediate. 
+            Fom Definition \ref{def:SNAG}, $\alpha_0 = 1$ makes $\tau_0 = 0$, so $y_0 = v_{-1}$. 
+            Followed by it, $x_0 = \tilde {\mathbf T}_L(y_0 | F) = \widetilde{\mathbf T}_L(v_{-1} | F)$. 
+            Therefore, we can apply Lemma \ref{lemma:pg-stoch-ineq} with $z = \bar x$, $\tilde x = x_0$, $x = v_{-1}$, and $\epsilon = \epsilon_0$ it yields: 
+            {\small
+            \begin{align*}
+                0
+                &\le 
+                F(z) - \expect_0 F(\tilde x)
+                + \frac{L - \mu}{2} \Vert z - x\Vert^2
+                - \frac{L - \epsilon}{2}\expect_0\left[\Vert z - \tilde x\Vert^2\right]
+                + \frac{\epsilon}{2} \expect_0\left[\Vert x - \tilde x\Vert^2\right]
+                \\
+                &= 
+                F(\bar x) - \expect_0 F(x_0)
+                + \frac{L - \mu}{2} \Vert \bar x - v_{-1}\Vert^2
+                - \frac{L - \epsilon}{2}\expect_0\left[\Vert \bar x - x_0\Vert^2\right]
+                + \frac{\epsilon}{2}\expect_0\left[\Vert v_{-1} - x_0\Vert^2\right].
+            \end{align*}
+            }
             % INTERMEDIATE RESULTS 
@@
                 &= 
-                \frac{1 - \alpha_k}{2(L - \sigma)}\left(
+                \frac{1 - \alpha_k}{2(L - \mu)}\left(
                     \mu^2 - L\left(\mu\right)\alpha_k

### 2025-07-22 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
             At \circled{1}, we used Lemma \ref{thm:jesen}. 
-            For \circled{3}, we used Lemma \ref{lemma:seq-properties} (i) and (b) because the sequence $\alpha_k \le 1$, therefore $1 - \alpha_k \le 1$. 
+            For \circled{3}, we used Lemma \ref{lemma:seq-properties} (i) and (b) because the sequence $\alpha_k \le 1$, therefore $1 - \alpha_k \le 0$. 
             Next, $\alpha_0 = 1 > \mu/L$, Lemma \ref{lemma:seq-properties} (ii) applies too, hence it also has $L\alpha_k - \mu \ge 0$. 
@@
         \end{proof}
-
-\section{Discussion, interpolation helps but it's not enough}
+        Obtaining the convergence results from the lemma requires a recursive relation in expectation. 
+        Before we start, here are some techinical details regarding conditional expectations. 
+        Conditional expectation wrt to a random variable is not directly defined, it's instead only defined with respect to some Sigma algebra. 
+        \par
+        The following theorem gives necessary results to derive the convergence rate of the algorithm in expectations. 
+        \begin{theorem}[SNAG descent lemma in expectations]\label{thm:snag-descent-expe}
+
+        \end{theorem}
+        \begin{proof}
+
+        \end{proof}
+\section{Discussion, interpolation helps but, it's not enough}
     \subsection{The no error case}

### 2025-07-22 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
         \end{proof}
+        Remark the following definitions
+        \begin{definition}[conditional expectations]
+            Given probability space $(\Omega, \mathcal F_0, \prob)$ and, $\mathcal F \subseteq \mathcal F_0$, and a random variable $X \in \mathcal F$ such that $\expect |X| < \infty$. 
+            We define the conditional expectation of $X$ given $\mathcal F$, $\expect [X| \mathcal F]$ to be any random variable $Y$ that has 
+            \begin{enumerate}[nosep]
+                \item $Y \in \mathcal F$, i.e: $Y$ is $\mathcal F$ measurable. 
+                \item For all $A \in \mathcal F$, $\int_A X d\prob = \int_A Y d\prob$. 
+            \end{enumerate}
+        \end{definition}
+        \begin{remark}
+            \todoinline{CITATIONS HERE NEEDED. }
+        \end{remark}
+        The conditional expectation exists and it's unique. 
         The following theorem given an inequality characterizing a descent relation for the SNAG algorithm. 
@@
         Before we start, here are some techinical details regarding conditional expectations. 
-        Conditional expectation wrt to a random variable is not directly defined, it's instead only defined with respect to some Sigma algebra. 
-        \par
+        Conditional expectation wrt to a random variable is not directly defined, it's instead only defined with respect to some sigma algebra. 
+        The conditional expectation exists, and it's unique. 
         The following theorem gives necessary results to derive the convergence rate of the algorithm in expectations. 

### 2025-07-22 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
         Obtaining the convergence results from the lemma requires a recursive relation in expectation. 
-        Before we start, here are some techinical details regarding conditional expectations. 
-        Conditional expectation wrt to a random variable is not directly defined, it's instead only defined with respect to some sigma algebra. 
-        The conditional expectation exists, and it's unique. 
         The following theorem gives necessary results to derive the convergence rate of the algorithm in expectations. 
-        \begin{theorem}[SNAG descent lemma in expectations]\label{thm:snag-descent-expe}
-
+        \begin{theorem}[SNAG convergence rate]\label{thm:snag-convergence}
+            Suppose that the sequence $(y_k, x_k, v_k)_{k \ge 0}$ is generated by algorithms satisfying Definition \ref{def:SNAG}. 
+            Assuming that it's generated by the stochastic gradient operator as in Definition \ref{def:stoch-pg-opt-rel-err}. 
+            For all $\bar x \in \RR^n$, for all $k \ge 1$, the convergence in expectation, can be compactly written as: 
+            \begin{align*}
+                \expect \Phi_k &\le
+                \left(
+                    \prod_{i = 1}^k \lambda_i
+                \right)\expect_k \Phi_0 + 
+                \sum_{j = 0}^{k}\left(
+                    \prod_{i = k - j}^k \lambda_i
+                \right)\expect R_{k - j - 1}
+                + \expect R_k.
+            \end{align*}
+            Where: 
+            \begin{enumerate}[nosep]
+                \item $\Phi_k := F(x_k) - F(\bar x) + \alpha_k^2(L - \epsilon_k)/2 \Vert v_k - \bar x\Vert^2$, 
+                \item $R_k := \frac{\epsilon_k}{2}\Vert y_k - x_k\Vert^2$, 
+                \item $\lambda_k := (1 - \alpha_k)\max(1, L\rho_{k - 1}/(L - \epsilon_{k - 1}))$. 
+            \end{enumerate}
         \end{theorem}
         \begin{proof}
-
+            Denote $\expect_k$ to be the conditional expectation based on random variables $\tilde \nabla f(y_i)$ for $i = 1, \ldots, k - 1$. 
+            The base case has $\expect_0$ which is the overall expectation. 
+            Fix any $\bar x \in \RR^n$ throughout. 
+            Consider any $k \ge 1$. 
+            Under the new notations, the relations from Theorem \ref{thm:snag-descent} yields 
+            \begin{align*}
+                & \expect_k \Phi_k 
+                \\
+                &= \expect_k F(x_k) - F(\bar x) + \frac{\alpha_k(L - \epsilon_k)}{2}\expect_k \Vert v_k - \bar x\Vert^2
+                \\
+                &\underset{\circled{1}}{\le} 
+                (1 - \alpha_k)\left(
+                    F(x_{k - 1})- F(\bar x) + \frac{\alpha_{k - 1}^2 L \rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                \right)
+                + \frac{\epsilon_k}{2}\expect_k \Vert y_k - x_k\Vert^2
+                \\
+                &= (1 - \alpha_k)\left(
+                    F(x_{k - 1})- F(\bar x) + \frac{\alpha_{k - 1}^2 L \rho_{k - 1}}{2}
+                    \left(
+                        \frac{L - \epsilon_{k - 1}}{L}
+                    \right)
+                    \left(
+                        \frac{L}{L - \epsilon_{k - 1}}
+                    \right)
+                    \Vert \bar x - v_{k - 1}\Vert^2
+                \right)
+                + \expect_k R_k
+                \\
+                &= (1 - \alpha_k)\left(
+                    F(x_{k - 1})- F(\bar x) 
+                    + \frac{\alpha_{k - 1}^2(L - \epsilon_{k - 1})}{2}
+                    \left(
+                        \frac{L\rho_{k - 1}}{L - \epsilon_{k - 1}}
+                    \right)
+                    \Vert \bar x - v_{k - 1}\Vert^2
+                \right)
+                + \expect_k R_k
+                \\
+                &= (1 - \alpha_k)\max\left(
+                    1, \frac{L\rho_{k - 1}}{L - \epsilon_{k - 1}}
+                \right)\left(
+                    F(x_{k - 1})- F(\bar x) 
+                    + \frac{\alpha_{k - 1}^2(L - \epsilon_{k - 1})}{2}
+                    \Vert \bar x - v_{k - 1}\Vert^2
+                \right)
+                + \expect_k R_k
+                \\
+                &= \lambda_k \Phi_{k - 1} + \expect_k R_k.
+            \end{align*}
+            At \circled{1}, we used Theorem \ref{thm:snag-descent}. 
+            Taking the full expectation, which is $\expect_0$ on both sides of the inequality above it yields 
+            \begin{align}\label{ineq:snag-descent-expe-pitem-1}
+                \expect_0 \Phi_{k} \le \lambda_{k + 1}\expect_0 \Phi_k + \expect_0 R_{k + 1}. 
+            \end{align}
+            Since this is true for all $k \ge 0$ in $\N$, we are now in position to verify the following inductive hypothesis 
+            \begin{align}\tag{IH}
+                \expect_0 \Phi_k &\le
+                \left(
+                    \prod_{i = 1}^k \lambda_i
+                \right)\expect_k \Phi_0 + 
+                \sum_{j = 0}^{k}\left(
+                    \prod_{i = k - j}^k \lambda_i
+                \right)\expect_0 R_{k - j - 1}
+                + \expect_0 R_k.
+            \end{align}
+            Use Inequality \ref{ineq:snag-descent-expe-pitem-1} with $k$ as $k + 1$, the inductive proof follows: 
+            \begin{align*}
+                \expect_0 \Phi_{k + 1} &\le 
+                \lambda_{k + 1}\expect_0\Phi_k 
+                + \expect_0 R_{k + 1}
+                \\
+                &\hspace{-0.2em}\underset{\text{(IH)}}{\le} \lambda_{k + 1}\left(
+                    \left(
+                        \prod_{i = 1}^k \lambda_i
+                    \right)\expect_k \Phi_0 
+                    + \sum_{j = 0}^{k}\left(
+                        \prod_{i = k - j}^k \lambda_i
+                    \right)\expect_0 R_{k - j - 1}
+                    + \expect_0 R_k
+                \right) 
+                + \expect_0 R_{k + 1}
+                \\
+                &= \left(
+                    \prod_{i = 1}^{k + 1} \lambda_i
+                \right)\expect_k \Phi_0
+                + \sum_{j = 0}^{k}\left(
+                    \prod_{i = k - j}^{k + 1}\lambda_i
+                \right)\expect_0 R_{k - j - 1}
+                + \lambda_{k + 1}\expect_0 R_k 
+                + \expect_0 R_{k + 1}
+                \\
+                &= \left(
+                    \prod_{i = 1}^{k + 1} \lambda_i
+                \right)\expect_k \Phi_0
+                + \sum_{j = 1}^{k + 1}\left(
+                    \prod_{i = k- j}^{k + 1}\lambda_i
+                \right)\expect_0 R_{k + 1 - j}
+                + \sum_{j = 0}^0 \prod_{i = k + 1 - j}^{k + 1}\lambda_{k + 1}\expect_0 R_k 
+                + \expect_0 R_{k + 1}
+                \\
+                &= 
+                \left(
+                    \prod_{i = 1}^{k + 1} \lambda_i
+                \right)\expect_k \Phi_0
+                + \sum_{j = 0}^{k + 1}\left(
+                    \prod_{i = k- j}^{k + 1}\lambda_i
+                \right)\expect_0 R_{k + 1 - j}
+                + \expect_0 R_{k + 1}. 
+            \end{align*}
+            Therefore, the inductive hypothesis holds. 
         \end{proof}
-\section{Discussion, interpolation helps but, it's not enough}
+    \subsection{Discussion of he error schedules}
+        Let's talk about Theorem \ref{thm:snag-convergence} here. 
+        With the compact representations, we can make see what is happening here. 
+        The inequality of the convergence consists of several quantities: 
+        \begin{enumerate}[nosep]
+            \item $\Phi_0$, the base case and a bounded quantities, depends on initial iterate $v_{-1}, x_{-1}$. 
+            \item $\lambda_k$, a sequence controling the convergence, involving relaxation parameters $\rho_{k - 1}$ and, the error $\epsilon_k$. 
+            \item $R_k$, an error term that, it's none trivial to group with the other terms of the inequality. 
+        \end{enumerate} 
+        Under some assumptions, and conditions, we can have some type of convergence rate. 
+\section{Interpolation helps but, it's very unclear if it's sufficient}
     \subsection{The no error case}

### 2025-07-29 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, small changes

@@
     This file is for communication purposes between collaborators. 
-    In brief, we think that the conditions required for linear convergence rate of Stochastic Nesterov's accelerated gradient (or proximal gradient) is too precarious to hold, even with interpolation hypothesis.
-    Instead of attacking the problem head on, this file will characterize the conditions required for linear convergence rate. 
+    In brief, we think that the conditions required for fast linear convergence rate, with a square root on the condition number of Stochastic Nesterov's accelerated gradient (or proximal gradient) is too precarious to hold, even with interpolation hypothesis.
+    Instead of attacking the problem head on, this file will characterize the conditions required for fast linear convergence rate. 
     We place specific constraints on the random variable representing the error made when estimating gradient via some random variables. 
@@
         It's very unclear what LHS really is without additional details and assumptions. 
-        \textbf{We very much would like $\epsilon$ to be a constant to make the algebra possible when deriving the convergence rate of the algorithm. }
+        \textbf{We very much would like $\epsilon$ to be a constant instead of a random variable to make the algebra possible when deriving the convergence rate of the algorithm. }
         \par
-        The following lemma gives a proximal gradient inequality when $\tilde \nabla f(x)$ is an estimate by some random variable, \textbf{and it is the precursor.} 
+        The following lemma gives a proximal gradient inequality when $\tilde \nabla f(x)$ is an estimate by some random variable, \textbf{and it is the precursor that gives the analysis of our convergence rate.}
         \begin{lemma}[proximal stochastic gradient inequality]\label{lemma:pg-stoch-ineq}
@@
         \end{proof}
+    \subsection{discussion}
         In practice, is chosen in prior to satisfies $B \ge L$. 
@@
         Assuming $z \neq \tilde x$ and, $\tilde x \neq x$, then one of the smallest choice for it in this lemma is
-        \begin{align*}
+        \begin{align}\label{eqn:stoch-grad-epsilon}
             \frac{
@@
             } &= \epsilon. 
-        \end{align*}
+        \end{align}
         It depends on both $z$ and $x$. 
@@
         And in this case, it has nothing to do with $z$. 
+        \par
+        \textbf{Ok, what about the relation between this error term \eqref{eqn:stoch-grad-epsilon} and the strong growth conditions that is usually found in the literature?}
+        There is no direct equality relationship between the Strong Growth condition of the stochastic gradient which is usually used in the literature, with the condition we have here. 
+        Nonetheless, an indirect inequality relation exists. 
+        Suppose that the gradient of $f$ satisfies strong growth condition with constant $\rho$, so it has $\expect \left\Vert \tilde \nabla f(x)\right\Vert^2 \le \rho \Vert \nabla f(x)\Vert^2$, then $\left\Vert \nabla f(x) - \tilde \nabla f(x)\right\Vert$ squared has:
+        \begin{align*}
+            & \left(
+                \expect \left \Vert \nabla f(x) - \tilde \nabla f(x)\right\Vert
+            \right)^2
+            \\
+            &\le 
+            \expect \left \Vert \nabla f(x) - \tilde \nabla f(x)\right\Vert^2 
+            \\
+            &= \expect \left\Vert \nabla f(x) - \expect \tilde \nabla f(x) \right\Vert^2 
+            \\
+            &= \expect \left\Vert \tilde \nabla f(x)\right\Vert^2 
+            - \Vert \nabla f(x)\Vert^2 
+            \le (\rho - 1)\Vert \nabla f(x)\Vert^2. 
+        \end{align*}
+        The last two equalities, we used the $\expect (X - \expect X)^2 = \expect X^2 - (\expect X)^2$ with $X$ being each of the element of the vector and, the linearity of expectations to apply it individually and them sum it up.
+        The first inequality also uses that equality but $X = \left\Vert \nabla f(x) - \tilde \nabla f(x)\right\Vert$ instead, and $\expect (X - \expect X)^2 \ge 0$ always. 
+        The last inequality comes from the assumed strong-growth conditions. 
+        Strong growth condition does make $\epsilon$ smaller if $x$ is close to the set of minimizer and this is the result: 
+        \begin{align*}
+            \expect \left\Vert
+                \nabla f(x) - \tilde \nabla f(x)
+            \right\Vert &\le 
+            \sqrt{\rho - 1} \Vert \nabla f(x)\Vert. 
+        \end{align*}
+        \par
+        Keeping the strong growth condition, let's assume that $\tilde x$ is generated by stochastic gradient, so that the proximal operator has $g \equiv 0$, then $\tilde x = x - L^{-1}\tilde \nabla f (x)$ directly.
+        Assuming that relation $m \le \Vert z - \tilde x\Vert \le M$ exists then \eqref{eqn:stoch-grad-epsilon} has upper bound
+        \begin{align*}
+            & \frac{M}{m} \frac{\expect\left\Vert \nabla f(x) - \tilde \nabla f(x)\right\Vert}{\expect \Vert x - \tilde x\Vert}
+            \\
+            &\le \frac{M}{m}\frac{\sqrt{\rho - 1}\Vert \nabla f(x)\Vert}{L^{-1}\expect \left\Vert\tilde \nabla f(x)\right\Vert}
+            \\
+            &\le \frac{LM}{m}
+            \frac{\sqrt{\rho - 1}\Vert \nabla f(x)\Vert}{
+                \min_{y \in \Omega(x)}\left\{
+                    \left\Vert y \right\Vert: y\neq \mathbf 0
+                \right\}\prob\left(\left\Vert\tilde \nabla f(x)\right\Vert \neq 0\right)
+            }. 
+        \end{align*}
+        \todoinline{NOT FINISHED YET. It seems like no pretty relaton exists. }
 
@@
     The following definition gives a momentum sequence where it makes the derivation of the convergence rate easier. 
+    The sequence is powerful, instead of an equality relation, the sequence can instead satisfies $\alpha_k \in (\mu/L, 1)$. 
     % ------------------------------------------------------------------------------------------------------------------
@@
                 \item it uses stochastic proximal gradient operator as in Definition \ref{def:stoch-pg-opt-rel-err}, 
-                \item it is initialized with $v_{-1} = x_{-1}$, $\alpha_0 = 1$ and, the momentum sequence $(\alpha_k)_{k \ge 0}$ satisfies Definition \ref{def:relax-momen-seq}. 
+                \item it is initialized with $v_{-1} = x_{-1}$, $\alpha_0 = 1$ and, the momentum sequence $(\alpha_k)_{k \ge 0}$ is given as in Lemma \ref{lemma:seq-properties}. 
             \end{enumerate}
@@
                 \frac{L - \mu}{2} \Vert \bar x - v_{-1}\Vert^2
-                + \frac{\epsilon}{2}\expect_0\left[\Vert v_{-1} - x_0\Vert^2\right]. 
+                + \frac{\epsilon_0}{2}\expect_0\left[\Vert v_{-1} - x_0\Vert^2\right]. 
             \end{align*}
@@
                 \item [(a)] For all $k \ge 1$, it has $\frac{\mu^2(1 - \alpha_k)^2}{2(L - \mu)} - \frac{\mu\alpha_k(1 - \alpha_k)}{2} = \frac{(\alpha_k - 1)\mu\left(L\alpha_k - \mu\right)}{2\left(L - \mu\right)}$ using some algebra.
-                \item [(b)] We assumed that the sequence $(\alpha_k)_{k \ge 0}$ satisfies\\ for all $k \ge 1$: $\rho_{k - 1}(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}(\alpha_{k} - \mu/L)$. 
+                \item [(b)] We assumed that the sequence $(\alpha_k)_{k \ge 0}$ satisfies\\ for all $k \ge 1$: $\rho_{k - 1}(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}(\alpha_{k} - \mu/L)$, hence Lemma \ref{lemma:seq-properties} applies.
                 \item [(c)] Using (b) and some algebra, we have for all $k \ge 1$ the identity: \\
@@
             At \circled{1}, we used Lemma \ref{thm:jesen}. 
-            For \circled{3}, we used Lemma \ref{lemma:seq-properties} (i) and (b) because the sequence $\alpha_k \le 1$, therefore $1 - \alpha_k \le 0$. 
-            Next, $\alpha_0 = 1 > \mu/L$, Lemma \ref{lemma:seq-properties} (ii) applies too, hence it also has $L\alpha_k - \mu \ge 0$. 
-            Since $L > \mu$ always, the coefficient on $\Vert x_{k - 1} - v_{k - 1}\Vert^2$ is always $\le 0$, therefore the term can be removed to give an inequality. 
+            For \circled{2}, we used Lemma \ref{lemma:seq-properties} (i) because of what is assumed in (b) so, the sequence has $\alpha_k \le 1$, therefore $1 - \alpha_k \le 0$. 
+            Next, $\alpha_0 = 1 > \mu/L$, Lemma \ref{lemma:seq-properties} (ii) applies too, hence $L\alpha_k - \mu \ge 0$. 
+            Since $L > \mu$ always, the coefficient on $\Vert x_{k - 1} - v_{k - 1}\Vert^2$ is always $\le 0$, therefore the term can be removed to keep the inequality. 
             At \circled{3}, we used Lemma \ref{lemma:snag-identities} (ii). 
@@
         The following theorem gives necessary results to derive the convergence rate of the algorithm in expectations. 
-        \begin{theorem}[SNAG convergence rate]\label{thm:snag-convergence}
+        \begin{theorem}[SNAG generic convergence rate]\label{thm:snag-generic-cnvg}
             Suppose that the sequence $(y_k, x_k, v_k)_{k \ge 0}$ is generated by algorithms satisfying Definition \ref{def:SNAG}. 
-            Assuming that it's generated by the stochastic gradient operator as in Definition \ref{def:stoch-pg-opt-rel-err}. 
+            Assume that the momentum sequence $(\alpha_k)_{k \ge 0}$, stochastic gradient $\tilde \nabla f$, and $v_{-1}, x_{-1}$ as in Theorem \ref{thm:snag-descent}. 
             For all $\bar x \in \RR^n$, for all $k \ge 1$, the convergence in expectation, can be compactly written as: 
@@
                     \prod_{i = 1}^k \lambda_i
-                \right)\expect_k \Phi_0 + 
-                \sum_{j = 0}^{k}\left(
+                \right)\expect \Phi_0 + 
+                \sum_{j = 0}^{k - 1}\left(
                     \prod_{i = k - j}^k \lambda_i
@@
             \end{align}
-            Since this is true for all $k \ge 0$ in $\N$, we are now in position to verify the following inductive hypothesis 
+            Let $k \ge 1$, We are now in position to verify the following inductive hypothesis: 
             \begin{align}\tag{IH}
@@
                     \prod_{i = 1}^k \lambda_i
-                \right)\expect_k \Phi_0 + 
-                \sum_{j = 0}^{k}\left(
+                \right)\expect_0 \Phi_0 + 
+                \sum_{j = 0}^{k - 1}\left(
                     \prod_{i = k - j}^k \lambda_i
@@
                         \prod_{i = 1}^k \lambda_i
-                    \right)\expect_k \Phi_0 
-                    + \sum_{j = 0}^{k}\left(
+                    \right)\expect_0 \Phi_0 
+                    + \sum_{j = 0}^{k - 1}\left(
                         \prod_{i = k - j}^k \lambda_i
@@
                     \prod_{i = 1}^{k + 1} \lambda_i
-                \right)\expect_k \Phi_0
-                + \sum_{j = 0}^{k}\left(
+                \right)\expect_0 \Phi_0
+                + \sum_{j = 0}^{k - 1}\left(
                     \prod_{i = k - j}^{k + 1}\lambda_i
@@
                     \prod_{i = 1}^{k + 1} \lambda_i
-                \right)\expect_k \Phi_0
-                + \sum_{j = 1}^{k + 1}\left(
+                \right)\expect_0 \Phi_0
+                + \sum_{j = 1}^{k}\left(
                     \prod_{i = k- j}^{k + 1}\lambda_i
-                \right)\expect_0 R_{k + 1 - j}
+                \right)\expect_0 R_{k - j}
                 + \sum_{j = 0}^0 \prod_{i = k + 1 - j}^{k + 1}\lambda_{k + 1}\expect_0 R_k 
@@
                     \prod_{i = 1}^{k + 1} \lambda_i
-                \right)\expect_k \Phi_0
-                + \sum_{j = 0}^{k + 1}\left(
+                \right)\expect_0 \Phi_0
+                + \sum_{j = 0}^{k}\left(
                     \prod_{i = k- j}^{k + 1}\lambda_i
-                \right)\expect_0 R_{k + 1 - j}
+                \right)\expect_0 R_{k - j}
                 + \expect_0 R_{k + 1}. 
@@
         \end{proof}
-    \subsection{Discussion of he error schedules}
-        Let's talk about Theorem \ref{thm:snag-convergence} here. 
+    \subsection{Discussion of error schedules}
+        Let's talk about Theorem \ref{thm:snag-generic-cnvg} here. 
         With the compact representations, we can make see what is happening here. 
@@
         \begin{enumerate}[nosep]
-            \item $\Phi_0$, the base case and a bounded quantities, depends on initial iterate $v_{-1}, x_{-1}$. 
-            \item $\lambda_k$, a sequence controling the convergence, involving relaxation parameters $\rho_{k - 1}$ and, the error $\epsilon_k$. 
-            \item $R_k$, an error term that, it's none trivial to group with the other terms of the inequality. 
+            \item $\Phi_0$, the base case and a bounded quantity, depends on initial iterate $v_{-1}, x_{-1}$. 
+            \item $\lambda_k$, a sequence controlling the convergence, involving relaxation parameters $\rho_{k - 1}$ and, the error $\epsilon_k$. 
+            \item $R_k$, an error term related to $\epsilon_k$ and, $\Vert y_k - x_k\Vert^2$, it's none trivial to group with the other terms. 
         \end{enumerate} 
-        Under some assumptions, and conditions, we can have some type of convergence rate. 
+        Without necessarily introducing the interpolation hypothesis, we have linear ``convergence" with an extra additive term under mild assumption. 
+        The following propositions simply stated the sufficient conditions on $\Phi_k, \lambda_k, R_k$ for the inequality to yield a linear convergence rate with additive error, nothing more. 
+        \begin{proposition}[SNAG kinda converges linearly]\;\label{prop:snag-kinda-converge}\\
+            Suppose that the sequence $(y_k, x_k, v_k)_{k \ge 0}$ is generated by algorithms satisfiying \ref{def:SNAG}. 
+            Suppose that that $\Phi_k, \lambda_k, R_k$ are as given in Theorem \ref{thm:snag-generic-cnvg}. 
+            Define
+            \begin{enumerate}[nosep]
+                \item $\Lambda = \sup_{i \in \N} \lambda_i$. 
+                \item An upper bound $\bar R \ge \expect R_k$ exists for all $k \ge 0$. 
+                \item An upper bound $\overline \epsilon = \sup_{i \in \N \cup\{0\}} \epsilon_i$ exists. 
+            \end{enumerate}
+            If in addition, we have $\overline \epsilon < \sqrt{\mu L}$, then it satisfies for all $k \ge 1$ the following inequality: 
+            \begin{align*}
+                \expect \Phi_k \le \Lambda^k \expect \Phi_0 + \frac{\overline R}{1 - \Lambda}. 
+            \end{align*}
+            Where 
+            \begin{align*}
+            \Lambda = \left(
+                1 - \sqrt{\frac{\mu}{L}}
+                \right)\left(
+                    \frac{L}{L - \overline \epsilon}
+                \right).
+            \end{align*}
+        \end{proposition}
+        \begin{proof}
+            We can prove it with the following intermediate results: 
+            \begin{enumerate}[nosep]
+                \item[(a)] For all $k \ge 1$, $\alpha_k = \sqrt{\mu/L}$ satisfies recurrences $(1 - \alpha_k)\alpha_{k - 1}^2 = \alpha_k(\alpha_k - \mu/L)$ where $\rho_k = 1$ for all $k \ge 1$, and $\rho_0 = \mu/L$.
+                \item[(b)] When $(\epsilon_k)_{k \ge 0}$ satisfies $\epsilon_k \le  \bar \epsilon = \sup_{i \in \N\cup\{0\}} \epsilon_i < \sqrt{\mu L}$, it has $\lambda_k \in (0, 1)$ for all $k \ge 1$, with $\Lambda = \sup_{i\in\N} \lambda_i < 1$.
+            \end{enumerate}
+            These results will be proved at the end. 
+            Consider starting with the inequality proved in Theorem \ref{thm:snag-descent}: 
+            \begin{align*}
+                \expect \Phi_k 
+                &\le \left(
+                    \prod_{i = 1}^k \lambda_i
+                \right) \expect \Phi_0
+                + \sum_{j = 1}^{k - 1}\left(
+                    \prod_{j = k - j}^{k - 1} \lambda_{i}
+                \right)\expect R_{k - j - 1}
+                + \expect R_k
+                \\
+                &\underset{\circled{1}}{\le} \Lambda^k \expect \Phi_0 + \sum_{j = 0}^{k - 1} \Lambda^{j + 1} \expect R_{k - j - 1} 
+                + \expect R_k
+                \\
+                &= \Lambda^k \expect \Phi_0 + \sum_{j = 1}^{k} \Lambda^{j} \expect R_{k - j} 
+                + \expect R_k
+                \\
+                &= \Lambda^k \expect \Phi_0 + \sum_{j = 0}^{k} \Lambda^{j} \expect R_{k - j} 
+                \\
+                &\underset{\circled{2}}{\le} \Lambda^k \expect \Phi_0 + \overline R \sum_{j = 0}^{k} \Lambda^{j} 
+                \\
+                &\underset{\circled{3}}{\le} \Lambda^k \expect \Phi_0 + \frac{\overline R}{1 - \Lambda}. 
+            \end{align*}
+            At \circled{1} we used that $\Lambda \ge \lambda_k$. 
+            At \circled{2} we used that $\overline R \ge \expect R_{k}$ for all $k \ge 0$. 
+            At \circled{3} we used the results from (b) that $\lambda_k \le \Lambda$ and $\Lambda < 1$, hence it has the convergence of the geometric series. 
+            \par \textbf{Proof of (a)}
+            When $L > \mu > 0$, so the objective $F$ is strongly convex, the usual $(1 - \alpha_k)\alpha_{k - 1}^2 = \alpha_k(\alpha_k - \mu/L)$ recurrence relations admits a constant solution $
+            \alpha_k = \sqrt{\mu/L}$ for all $k \ge 1$. 
+            As presented in Theorem \ref{thm:snag-descent}, the momentum sequence $(\alpha_k)_{k \ge 0}$ has a relaxation parameter $(\rho_k)_{k \ge 1}$. 
+            In this case, it means that $\rho_{k - 1} = 1$ for all $k \ge 1$. 
+            Since when $k = 0$, $\alpha_0 = 1$, it makes an exception on $\rho_0$, which is: 
+            \begin{align*}
+                \rho_0 &= \frac{\sqrt{\mu/L}\left(\sqrt{\mu/L} - \mu/L\right)}{1 - \sqrt{\mu/L}} = \frac{\mu}{L}. 
+            \end{align*}
+            \par \textbf{Proof of (b)}.
+            If $\sup_{k \in \N \cup \{0\}}\epsilon_{k} < \sqrt{\mu L}$ for all $k \ge 0$, by the definition of $\lambda_k$, it has: 
+            \begin{align*}
+                & \sup_{k \in \N}\lambda_k
+                \\
+                &= \sup_{k \in \N} \left(
+                    1 - \sqrt{\frac{\mu}{L}}
+                \right)\left(
+                    \frac{L\rho_{k - 1}}{L - \epsilon_{k - 1}}
+                \right)
+                \\
+                &\underset{\circled{1}}{\le} 
+                \left(
+                    1 - \sqrt{\frac{\mu}{L}}
+                \right)\left(
+                    \frac{L}{L - \sup_{k \in \N}\epsilon_{k - 1}}
+                \right)
+                \\
+                &< \left(
+                    1 - \sqrt{\frac{\mu}{L}}
+                \right)\left(
+                    \frac{L}{1 - \sqrt{\mu L}}
+                \right) = 1. 
+            \end{align*}
+            At \circled{1}, we used the fact that $\rho_k = 1$ for all $k \ge 1$ and,$\rho_k = \mu/L$ for $k = 0$, therefore, it $(\forall k \ge 0)\; \rho_k \le 1$. 
+            So $\Lambda < 1$.
+
+        \end{proof}
+
 \section{Interpolation helps but, it's very unclear if it's sufficient}
+    Under the frameworks of our analysis, the interpolation assumption helps with controlling the errors, but it's unclear to what extent, it will help us to obtain a convergence rate faster than what is already in the literatures.
     \subsection{The no error case}

### 2025-07-31 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes, late night

@@
 \end{abstract}
+
 \chapter{The Basics of Optimization Theories}
@@
             \end{proof}
+
+\chapter{Going deeper into the literatures}
+    This chapter follows the previous chapter but delve deeper into the specifics of the literatures. 
+    Most of the thing written here are my own thoughts and inspirations instead of translated ideas from the existing literatures. 
+    \section{Quasi strong convexity is a wasteful definition}
 

### 2025-07-31 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes, late night

@@
                 \partial \left[
-                    z \mapsto \partial g(x) + \langle \nabla f(x), z - x\rangle + 
+                    z \mapsto \partial g(z) + \langle \nabla f(x), z - x\rangle + 
                     \frac{B}{2}\Vert x - z\Vert^2
@@
             Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
-            Fix any $x \in \RR^n$ there exists a $B \ge 0$,  $\tilde x$ be an estimate of $T_B(x | F)$ such that $D_f(\tilde x, x) \le B/2\Vert x - \tilde x\Vert^2$. 
+            Let $x \in \RR^n$, and let $\tilde x$ be an estimate of $T_B(x | F)$ such that $D_f(\tilde x, x) \le B/2\Vert x - \tilde x\Vert^2$, where $B \ge 0$. 
             Let $S_B(\tilde x, x | F)$ be given by Definition \ref{def:pg-err-ruler}. 
@@
             \\
-            &= \expect \left\Vert \nabla f(x) - \expect \tilde \nabla f(x) \right\Vert^2 
+            &= \expect \left\Vert \expect \tilde \nabla f(x) - \tilde \nabla f(x) \right\Vert^2 
             \\
@@
             Suppose that the sequence $(y_k, x_k, v_k)_{k \ge 0}$ is generated by algorithms satisfiying \ref{def:SNAG}. 
-            Suppose that that $\Phi_k, \lambda_k, R_k$ are as given in Theorem \ref{thm:snag-generic-cnvg}. 
+            Suppose that $\Phi_k, \lambda_k, R_k$ are as given in Theorem \ref{thm:snag-generic-cnvg}. 
             Define

### 2025-08-01 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, changes

\documentclass[12pt]{article}

% \input{presets/wang_full.tex}
\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{true}
\input{presets/wang/input.tex}
\input{presets/misc.tex}
% \input{presets/julia_lstlisting.tex}

\begin{document}

\title{{\fontfamily{ptm}\selectfont My Ideas after Reading Papers}}

\author{
    Author 1 Name, Author 2 Name
    \thanks{
        Subject type, Some Department of Some University, Location of the University,
        Country. E-mail: \texttt{author.name@university.edu}.
    }
}

\date{March 2, 2020}

\maketitle
\todoinline{This paper is currently in draft mode. Check source to change options. }
% \vskip 8mm

\begin{abstract} 
    \noindent
    This is still a note for a draft so no abstract \cite{bauschke_convex_2017}
\end{abstract}

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 47H05, 52A41, 90C25; Secondary 15A09, 26A51, 26B25, 26E60, 47H09, 47A63.
\noindent{\bfseries Keywords:}

% ==============================================================================
\section{Introduction}
    Necoara et al. introduced the definition of quasi strongly convex function (Q-SCNVX), Quadratic Under approximations (QUA), Quadratic Gradient Growth (QGG), Proximal Error Bound (PEB) and, Quadratic Function Growth (QFG). 
    These conditions are relaxation of strong convexity which enables linear convergence rate of first order method, including Nesterov's accelerated variants. 
    In this file, we showed a new perspective of their works. 
    Our goal is to relax their definitions and, to extend the linear convergence results, using completely new ideas and perspective. 
    \par
    \textbf{Notations.}
    Unless specified, our ambient space is $\RR^n$ with Euclidean norm $\Vert \cdot\Vert$.
    Let $C\subseteq \RR^n$, $\Pi_C(\cdot)$ denotes the projection onto the set $C$, i.e: the closest point in $C$ to another point in $\RR^n$. 
    \par
    The following definitions and assumptions are their. 
    % SYMBOL SET FOR THIS CHAPTER ONLY!

    \begin{assumption}[Necoara's linear convergence assumptions]\; \label{ass:necoara-linear} \\
        The following assumptions are about $(f, X, X^*, L_f)$. 
        \begin{enumerate}[nosep]
            \item $f: \RR^n \rightarrow \RR$ is an $L_f$ Lipschitz smooth function. 
            \item $X \subseteq \RR^n$ is a closed convex non-empty set. 
            \item $X^* = \argmin_{x \in X} f(x) \neq \emptyset$. 
        \end{enumerate}
    \end{assumption}
    Under this assumption, the following definitions are proposed. 
    \newcommand{\QSCNVX}{\ensuremath{q\mathcal{S}}}
    \newcommand{\QUA}{\ensuremath{\mathcal U}}
    \newcommand{\QGG}{\ensuremath{\mathcal G}}
    \newcommand{\QFG}{\ensuremath{\mathcal F}} 
    \newcommand{\PEB}{\ensuremath{\mathcal E}}
    \begin{definition}[Necoara's weaker characterizations of strong convexity]\; \\
        Suppose that $(f, X, X^*, L_f)$ are given by Assumption \ref{ass:necoara-linear}. 
        For all $x \in X$, denote $\bar x = \Pi_{X^*}x$. 
        The following definitions are relaxations of strong convexity. 
        \begin{enumerate}[nosep]
            \item $f$ is Q-SCNVX if there exists $\kappa_f > 0$ such that $f(\bar x) - f(x) - \langle \nabla f(x), \bar x - x\rangle \ge \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. 
            Which we denote it by $f \in \QSCNVX(f, L_f, \kappa_f)$. 
            \item $f$ is QUA if there exists $\kappa_f > 0$ such that $f(x) - f(\bar x) - \langle \nabla f(\bar x), x - \bar x\rangle \ge \frac{\kappa_f}{2}\Vert x -\bar x\Vert^2$. 
            We denote it by $f \in \QUA(f, L_f, \kappa_f)$.
            \item $f$ is QGG if there exists $\kappa_f > 0$ such that $\langle \nabla f(x) - \nabla f(\bar x), x - \bar x\rangle \ge \frac{\kappa}{2}\Vert x - \bar x\Vert^2$. 
            We denote it by $f \in \QGG(f, L_f, \kappa_f)$. 
            \item $f$ is PEB if there exists $\kappa_f > 0$ such that $\left\Vert x - L^{-1}\Pi_X(x - L^{-1}\nabla f(x))\right\Vert \ge \kappa_f\Vert x - \bar x\Vert$. 
            We denote it by $f \in \PEB(f, L_f, \kappa_f)$. 
            \item $f$ is QFG if there exists $\kappa_f > 0$ such that $f(x) - f(\bar x) \ge \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. 
            We denote it by $f \in \QFG(f, L_f, \kappa_f)$. 
        \end{enumerate}
    \end{definition}
    These definitions are the keys which Necoara used to prove the linear convergence of projected gradient, and Nesterov's accelerated gradient method.

\subsection{The idea of Semi Bregman Divergence}

\bibliographystyle{siam}

\bibliography{references/Books.bib}

\end{document}

### 2025-08-02 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, changes

@@
 \begin{document}
+
+\newcommand{\dist}{\ensuremath{\operatorname{dist}}}
 
@@
 
-\subsection{The idea of Semi Bregman Divergence}
+\section{Our crazy original ideas of extending their definitions}
+    In this section, we will proposed our ideas which relaxed Necoara's conditions for strong convexity.
+    \begin{definition}[Breman Divergence for differentiable funtion]\label{def:bd}
+        Let $f: \RR^n \rightarrow \RR$ be a $\mathcal C^1$ function. 
+        The Bregman divergence is a $\RR^n \times \dom \nabla f(x)\rightarrow \RR$ mapping and, it's defined by:  
+        \begin{align*}
+            D_f(x, y) = f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 
+        \end{align*}
+    \end{definition}
+    semi Bregman Divergence is the Bregman Divergence of distance squared to a set. 
+    % ------------------------------------------------------------------------------------------------------------------
+    \begin{theorem}[Bregman Divergence for distance squared]\label{thm:bd-dist-sq}
+        Let $C \subseteq \RR^n$ be any closed and non-empty. 
+        Let $\varphi = (1/2)\dist(\cdot | C)^2$.
+        Then for all $x, y \in \RR^n$: 
+        \begin{align*}
+            D_{\varphi}(x, y) 
+            &= 
+            - \frac{1}{2}\Vert \Pi_C x - \Pi_C y\Vert^2
+            + \left\langle x - \Pi_C x, \Pi_C x - \Pi_C y\right\rangle
+            + \frac{1}{2} \Vert x - y\Vert^2. 
+        \end{align*}
+    \end{theorem}
+    \begin{proof}
+        For notational simplicity let $\bar x = \Pi_C x, \bar y = \Pi_C y$. 
+        Recall that $\nabla \varphi (x) = x - \bar x$. 
+        With Definition \ref{def:bd} and, basic algebra we can show that: 
+        \begin{align*}
+            D_{\varphi}(x, y) &= 
+            \varphi(x) - \varphi(y) - \left\langle \nabla \varphi(y), x - y\right\rangle
+            \\
+            &= \varphi(x) - \varphi(y) - \langle y - \bar y, x - y\rangle
+            \\
+            &= \frac{1}{2}(\Vert x - \bar x\Vert^2 - \Vert y - \bar y\Vert^2)
+            - \langle y - \bar y, x - y\rangle
+            \\
+            &= \frac{1}{2}(\Vert x - \bar x\Vert^2 - \Vert y - \bar y\Vert^2)
+            - \frac{1}{2}\Vert x - \bar y\Vert^2 
+            + \frac{1}{2}\left(
+                \Vert y - \bar y\Vert^2 + \Vert x - y\Vert^2
+            \right)
+            \\ 
+            &= \frac{1}{2}\Vert x - \bar x\Vert^2
+            - \frac{1}{2}\Vert x - \bar y\Vert^2 + \frac{1}{2}\Vert x - y\Vert^2
+            \\
+            &= 
+            \frac{1}{2}\Vert x - \bar x\Vert^2
+            - \frac{1}{2}\left(
+                \Vert x - \bar x\Vert^2 + \Vert \bar x - \bar y\Vert^2
+                + 2\langle x - \bar x, \bar x - \bar y\rangle
+            \right)
+            + \frac{1}{2}\Vert x - y\Vert^2
+            \\
+            &= - \frac{1}{2}\Vert \bar x - \bar y\Vert^2 + \langle x - \bar x, \bar x - \bar y\rangle 
+            + \frac{1}{2}\Vert x - y \Vert^2. 
+        \end{align*}
+    \end{proof}
+    \par
+    The following lemma is a precursor to extend the definition of Q-SCNVX. 
+    The abbreviation ``SBD'' stands for ``Semi Bregman Divergence''. 
+    % ------------------------------------------------------------------------------------------------------------------
+    \begin{lemma}[conditions when SBD behaves like SCNVX]
+        Let $C \subseteq \RR^n$ be closed and non-empty. 
+        Let $\varphi = (1/2)\dist(\cdot | C)^2$.
+        Define the set $\mathcal D(x | C) := \{z \in \RR^n : \Pi_C z = \Pi_C x\}$. 
+        Then, for all $x \in \RR^n$ it satisfies
+        \begin{align*}
+            (\forall z \in D(x | C))\; \mathcal D_\varphi(x, z) = \frac{1}{2}\Vert x - z\Vert^2 = D_f(z, x). 
+        \end{align*}
+    \end{lemma}
+    \begin{proof}
+        The proof is direct. 
+        For all $x \in \RR^n, z \in \mathcal D(x | C)$, the Bregman Divergence simplifies because using Theorem \ref{thm:bd-dist-sq} it has: 
+        \begin{align*}
+            D_\varphi (x, z) &= 
+            - \frac{1}{2}\Vert \Pi_C x - \Pi_C z\Vert^2 
+            + \langle x - \Pi_C x, \Pi_C x - \Pi_C z\rangle 
+            + \frac{1}{2}\Vert x - z\Vert^2
+            \\
+            &= 0 + 0 + \frac{1}{2}\Vert x - z\Vert^2. 
+        \end{align*}
+        This is true because for all $z \in \mathcal D(x | C)$, it has $\Pi_C x - \Pi_C z = 0$. 
+        Similarly, it has: 
+        \begin{align*}
+            D_\varphi(x, z) &= 
+            - \frac{1}{2}\Vert \Pi_C x - \Pi_C z\Vert^2 
+            + \langle z - \Pi_C z, \Pi_C z - \Pi_C x\rangle
+            + \frac{1}{2}\Vert z - x\Vert^2
+            \\
+            &= 0 + 0 + \frac{1}{2}\Vert z - x\Vert^2. 
+        \end{align*}
+    \end{proof}
+    \par
+    Now, the definition of $\mathcal D(x | C)$ in the above lemma is nothing outrageous. 
+    It simply denotes all points that share the same projection onto $C$ as $x$. 
+    Below, we will give some possible scenarios. 
+    \begin{enumerate}
+        \item When $C$ is convex, the set $\mathcal D(x | C) = \Pi_C x + N_C(\Pi_C x)$. 
+        \item When $C$ is nonconvex, it has $\mathcal D(x | C) \subseteq \Pi_C x + N_C(\Pi_C x)$. 
+    \end{enumerate}
+    Strong convexity is recovered when $C$ is a singleton. 
+    For example when $C = \{\mathbf 0\}$, and $\varphi = (1/2)\Vert x\Vert^2$, this is the usual euclidean Bregman Divergence used to introduce functions that are strongly convex. 
+    Furthermore, take note that $\Pi_C x \in D(x | C)$ always so we have
+    \begin{align}
+        D_\varphi(x, \Pi_C x) = \frac{1}{2}\Vert x - \Pi_C \Vert^2 = D_\varphi(\Pi_C x, x). 
+    \end{align}
+    \par
+    The following theorems will prepare us for linear convergence of first order algorithms. 
+    \begin{definition}[proximal gradient operator]\label{def:pg}
+        Let $F = f + g$, suppose that $f : \RR^n \rightarrow \RR$ is in $\mathcal C^1$ and $g: \RR^n \rightarrow \overline R$ is l.s.c. 
+        The proximal gradient operator, denoted by $T_{B, f, g}$ is defined as
+        \begin{align*}
+            T_{B, f, g}(x) &= \argmin_{z\in \RR^n} \left\lbrace
+                g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert x - z\Vert^2
+            \right\rbrace
+        \end{align*}
+    \end{definition}
+    \begin{remark}
+        Usually we can find it in the literature that, $T_{B, f, g} = \hprox_{B^{-1}g}(x - B^{-1}\nabla f(x))$. 
+    \end{remark}
+
+    \begin{assumption}[our assumptions]\label{ass:our-ass}
+        The following assumption is about $(f, g, L_f, X^*)$. 
+        \begin{enumerate}
+            \item $f: \RR^n \rightarrow \RR$ is $L_f$ Lipschitz smooth. 
+            \item $g: \RR^n \rightarrow \RR$ is l.s.c
+            \item Denote $X^*$ be the fixed point set of $T_{L_f, f, g}$ and assume $X^* \neq \emptyset$. 
+        \end{enumerate}
+    \end{assumption}
+    \begin{definition}[relatively quasi strongly convex]
+        Suppose that $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:our-ass}. 
+        The function $F = f + g$ is relatively quasi strongly convex if there exists $\kappa_f > 0$ such that for all $x \in \dom g$, let $\bar x = \Pi_{X^*}x$ it satisfies: 
+        \begin{align*}
+            \left(\forall v \in \partial F(\bar x)\right)\;
+            F(x) - F(\bar x) - \langle v, x - \bar x\rangle 
+            &\ge \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2. 
+        \end{align*}
+    \end{definition}
+    \begin{remark}
+        Take note that the RHS of the inequality $\kappa_f/2 \Vert x - \bar x\Vert^2 = D_\varphi(x, \Pi_{X^*}x)$ where $\varphi = (1/2)\dist(x | X^*)^2$. 
+    \end{remark}
+    The following discussion will give important consequences of our set up. 
+    % ------------------------------------------------------------------------------------------------------------------
+    \subsection{examples for relatively quasi strongly convex functions}
+
+    % ------------------------------------------------------------------------------------------------------------------
+    \subsection{theorems useful for convergence analysis of algorithms}
+
+\section{Linear convergence of first order methods}
 

### 2025-08-03 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, changes

@@
 \section{Our crazy original ideas of extending their definitions}
-    In this section, we will proposed our ideas which relaxed Necoara's conditions for strong convexity.
+    In this section, we will propose our ideas which relaxed Necoara's conditions for strong convexity.
     \begin{definition}[Breman Divergence for differentiable funtion]\label{def:bd}
@@
     \end{definition}
-    semi Bregman Divergence is the Bregman Divergence of distance squared to a set. 
     % ------------------------------------------------------------------------------------------------------------------
-    \begin{theorem}[Bregman Divergence for distance squared]\label{thm:bd-dist-sq}
+    \begin{theorem}[distance squared Bregman Divergence]\label{thm:bd-dist-sq}
         Let $C \subseteq \RR^n$ be any closed and non-empty. 
@@
     \par
+    In the parts that come, we will talk about the set of points that share the same projections onto a set.
+    Let $C \subseteq \RR^n$, we define for all $x \in \RR^n$ the set: 
+    \begin{align}
+        \mathcal D(x | C) = \{z \in \RR^n : \Pi_C z = \Pi_C x\}. 
+    \end{align}
     The following lemma is a precursor to extend the definition of Q-SCNVX. 
-    The abbreviation ``SBD'' stands for ``Semi Bregman Divergence''. 
+    The abbreviation ``DSBD'' stands for ``distance squared Bregman Divergence''. 
     % ------------------------------------------------------------------------------------------------------------------
-    \begin{lemma}[conditions when SBD behaves like SCNVX]
+    \begin{lemma}[conditions when DSBD behaves like norm squared]
         Let $C \subseteq \RR^n$ be closed and non-empty. 
         Let $\varphi = (1/2)\dist(\cdot | C)^2$.
-        Define the set $\mathcal D(x | C) := \{z \in \RR^n : \Pi_C z = \Pi_C x\}$. 
         Then, for all $x \in \RR^n$ it satisfies
         \begin{align*}
-            (\forall z \in D(x | C))\; \mathcal D_\varphi(x, z) = \frac{1}{2}\Vert x - z\Vert^2 = D_f(z, x). 
+            (\forall z \in \mathcal D(x | C))\; \mathcal D_\varphi(x, z) = \frac{1}{2}\Vert x - z\Vert^2 = D_f(z, x). 
         \end{align*}
@@
     For example when $C = \{\mathbf 0\}$, and $\varphi = (1/2)\Vert x\Vert^2$, this is the usual euclidean Bregman Divergence used to introduce functions that are strongly convex. 
-    Furthermore, take note that $\Pi_C x \in D(x | C)$ always so we have
+    Furthermore, take note that $\Pi_C x \in D(x | C)$ always so, we have
     \begin{align}
@@
     \end{remark}
-
+    The following assumption is the weakest and, it doesn't assume convexity at all. 
     \begin{assumption}[our assumptions]\label{ass:our-ass}
@@
     \end{assumption}
-    \begin{definition}[relatively quasi strongly convex]
+    \begin{definition}[restricted QUA]
         Suppose that $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:our-ass}. 
-        The function $F = f + g$ is relatively quasi strongly convex if there exists $\kappa_f > 0$ such that for all $x \in \dom g$, let $\bar x = \Pi_{X^*}x$ it satisfies: 
+        The function $F = f + g$ has restricted QUA condition if there exists $\kappa_f > 0, D \subseteq \dom g$ such that for all $x \in D$, let $\bar x = \Pi_{X^*}x$ it satisfies: 
         \begin{align*}
@@
         Take note that the RHS of the inequality $\kappa_f/2 \Vert x - \bar x\Vert^2 = D_\varphi(x, \Pi_{X^*}x)$ where $\varphi = (1/2)\dist(x | X^*)^2$. 
+        This definition doesn't exclude nonconvex functions. 
+        The hope is to have the set $D = \dom g$, but we don't think that is always true. 
+        Our hope is that the set $D$ is at least somewhat larger than $X^+$. 
     \end{remark}
-    The following discussion will give important consequences of our set up. 
+    The following discussion will give important consequences of this setup. 
     % ------------------------------------------------------------------------------------------------------------------
     \subsection{examples for relatively quasi strongly convex functions}
+        The following assumption will characterize a specific type of convex programming problem that has relative quasi strong convexity. 
+        \begin{assumption}[distance of two sets]
+            Suppose $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:our-ass}. 
+            In addition, we assume the following. 
+            \begin{enumerate}[nosep]
+                \item 
+            \end{enumerate}
+        \end{assumption}
+        \begin{theorem}[example of restricted QUA]\label{thm:example-rqua}
 
+        \end{theorem}
+        \begin{proof}
+
+        \end{proof}
     % ------------------------------------------------------------------------------------------------------------------
     \subsection{theorems useful for convergence analysis of algorithms}
+        The proximal gradient inequality and, the Jensen inequality are the most important for deriving convergence rate of first order accelerated method.
 

### 2025-08-05 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, changes

@@
 
-\title{{\fontfamily{ptm}\selectfont My Ideas after Reading Papers}}
+\title{{\fontfamily{ptm}\selectfont My Ideas after Reading Necoara's Papers}}
 
@@
     Necoara et al.
-introduced the definition of quasi strongly convex function (Q-SCNVX), Quadratic Under approximations (QUA), Quadratic Gradient Growth (QGG), Proximal Error Bound (PEB) and, Quadratic Function Growth (QFG).
+\cite{necoara_linear_2019}  introduced the definition of quasi strongly convex function (Q-SCNVX), Quadratic Under approximations (QUA), Quadratic Gradient Growth (QGG), Proximal Error Bound (PEB) and, Quadratic Function Growth (QFG).
     These conditions are relaxation of strong convexity which enables linear convergence rate of first order method, including Nesterov's accelerated variants. 
@@
     % ------------------------------------------------------------------------------------------------------------------
-    \begin{lemma}[conditions when DSBD behaves like norm squared]
+    \begin{lemma}[conditions when DSBD behaves like norm squared]\label{lemma:conds-dsbd-like-scnvx}
         Let $C \subseteq \RR^n$ be closed and non-empty. 
@@
     % ------------------------------------------------------------------------------------------------------------------
-    \subsection{examples for relatively quasi strongly convex functions}
+    \subsection{examples for restricted QUA}
         The following assumption will characterize a specific type of convex programming problem that has relative quasi strong convexity. 
-        \begin{assumption}[distance of two sets]
+        \begin{assumption}[two sets feasibility problem]\;\label{ass:two-sets-feasibility}\\
             Suppose $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:our-ass}. 
@@
             \begin{enumerate}[nosep]
-                \item 
+                \item $f = (1/2)\dist(x | C)^2$ where $C \subseteq \RR^n$ is a closed and convex set. 
+                \item $g = \delta_X(x)$ is the indicator function of $X \subseteq \RR^n$, where $X$ is a closed and convex, nonempty set. 
             \end{enumerate}
+            Consequently, the set of minimizers is the fixed point set of the alternating projection operators, $X^* = \Fix (\Pi_X \Pi_C)$. 
         \end{assumption}
-        \begin{theorem}[example of restricted QUA]\label{thm:example-rqua}
-
+        We will show that, with additional assumptions, function in the above assumption can satisfy the restricted QUA conditions 
+        \begin{theorem}[characterizing restricted QUA]\label{thm:example-rqua}
+            Suppose that $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:two-sets-feasibility}. 
+            Then for all $x\in X$ such that $\Pi_{X^*} x\in \mathcal D(x | C)$, it has 
+            \begin{align*}
+                D_f(x, \Pi_{X^*}x) = \frac{1}{2}\Vert x - \Pi_{X^*} x\Vert^2 = D_f(\Pi_{X^*}x, x). 
+            \end{align*}
         \end{theorem}
         \begin{proof}
-
+            We use Lemma \ref{lemma:conds-dsbd-like-scnvx}, take note that when $z = \Pi_{X^*} x \in \mathcal D(x | C)$, then the lemma says: $D_f(x, \Pi_{X^*}x) = \frac{1}{2}\Vert x - \Pi_{X^*}x\Vert^2= D_f(\Pi_{X^*}x, x)$.
         \end{proof}
+        \begin{remark}
+            The conditions, $\Pi_{X^*}x \in \mathcal D(x | C)$ is not always a given and, it would require some careful thoughts. 
+        \end{remark}
     % ------------------------------------------------------------------------------------------------------------------

### 2025-08-05 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@
             &\le 
-            \expect \left \Vert \nabla f(x) - \tilde \nabla f(x)\right\Vert^2 
-            \\
-            &= \expect \left\Vert \expect \tilde \nabla f(x) - \tilde \nabla f(x) \right\Vert^2 
-            \\
-            &= \expect \left\Vert \tilde \nabla f(x)\right\Vert^2 
-            - \Vert \nabla f(x)\Vert^2 
-            \le (\rho - 1)\Vert \nabla f(x)\Vert^2. 
-        \end{align*}
-        The last two equalities, we used the $\expect (X - \expect X)^2 = \expect X^2 - (\expect X)^2$ with $X$ being each of the element of the vector and, the linearity of expectations to apply it individually and them sum it up.
-        The first inequality also uses that equality but $X = \left\Vert \nabla f(x) - \tilde \nabla f(x)\right\Vert$ instead, and $\expect (X - \expect X)^2 \ge 0$ always. 
+            \expect \left\Vert \nabla f(x) - \tilde \nabla f(x)\right\Vert^2
+            \\
+            &= 
+            \Vert \nabla f(x)\Vert^2 
+            + \expect \left\Vert\tilde \nabla f(x) \right\Vert^2 
+            - 2\expect
+            \left\langle 
+                \nabla f(x), \tilde \nabla f(x)
+            \right\rangle
+            \\
+            &\le 
+            \Vert \nabla f(x)\Vert^2 
+            + \rho \Vert \nabla f(x)\Vert^2
+            - 2\Vert \nabla f(x)\Vert^2
+            \\
+            &= \left(\rho - 1\right) \Vert \nabla f(x)\Vert^2.
+        \end{align*}
+        For the first inequality, we used the $\expect (X - \expect X)^2 = \expect X^2 - (\expect X)^2$, and the variance being a non-negative quantity. 
         The last inequality comes from the assumed strong-growth conditions.
+        \par
         Strong growth condition does make $\epsilon$ smaller if $x$ is close to the set of minimizer and this is the result: 

### 2025-08-08 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, changes

@@
     \begin{theorem}[distance squared Bregman Divergence]\label{thm:bd-dist-sq}
-        Let $C \subseteq \RR^n$ be any closed and non-empty. 
+        Let $C \subseteq \RR^n$ be any closed, non-empty and convex set. 
         Let $\varphi = (1/2)\dist(\cdot | C)^2$.
@@
     \begin{proof}
-        For notational simplicity let $\bar x = \Pi_C x, \bar y = \Pi_C y$. 
-        Recall that $\nabla \varphi (x) = x - \bar x$. 
+        closed, convex, non-empty $C$ gives unique projection point so $\Pi_C$ is a convex set. 
+        \par
+        For notational simplicity let $\bar x = \Pi_C x, \bar y = \Pi_C y$, then it has $\nabla \varphi (x) = x - \bar x$. 
         With Definition \ref{def:bd} and, basic algebra we can show that: 
@@
     For example when $C = \{\mathbf 0\}$, and $\varphi = (1/2)\Vert x\Vert^2$, this is the usual euclidean Bregman Divergence used to introduce functions that are strongly convex. 
-    Furthermore, take note that $\Pi_C x \in D(x | C)$ always so, we have
+    Furthermore, take note that $\Pi_C x \in D(x | C)$ is always true, hence we have
     \begin{align}
@@
     The following assumption is the weakest and, it doesn't assume convexity at all. 
-    \begin{assumption}[our assumptions]\label{ass:our-ass}
+    \begin{assumption}\label{ass:our-ass}
         The following assumption is about $(f, g, L_f, X^*)$. 
@@
             \item $f: \RR^n \rightarrow \RR$ is $L_f$ Lipschitz smooth. 
-            \item $g: \RR^n \rightarrow \RR$ is l.s.c
+            \item $g: \RR^n \rightarrow \RR$ is closed convex and proper. 
             \item Denote $X^*$ be the fixed point set of $T_{L_f, f, g}$ and assume $X^* \neq \emptyset$. 
@@
     \end{assumption}
+    We take note that, under the above assumption the function $F = f + g$ is a $L_f$ weakly convex function and, $\widehat \partial F = \partial F$. 
     \begin{definition}[restricted QUA]
@@
         The hope is to have the set $D = \dom g$, but we don't think that is always true. 
-        Our hope is that the set $D$ is at least somewhat larger than $X^+$. 
+        Our hope is that the set $D$ is at least somewhat larger than $X^*$. 
     \end{remark}
@@
                 \item $g = \delta_X(x)$ is the indicator function of $X \subseteq \RR^n$, where $X$ is a closed and convex, nonempty set. 
+                \item The set $X^* = \Fix(\Pi_X \Pi_C) \neq \emptyset$. 
             \end{enumerate}
-            Consequently, the set of minimizers is the fixed point set of the alternating projection operators, $X^* = \Fix (\Pi_X \Pi_C)$. 
         \end{assumption}

### 2025-08-09 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main-2025-08-08.tex
=w=, changes after changes

--- 2025-08-08 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
@@
         Let $\varphi = (1/2)\dist(\cdot | C)^2$.
-        Then for all $x, y \in \RR^n$: 
+        Then for all $x, y \in \RR^n$, for all $\bar x \in \Pi_C x, \bar y \in \Pi_C y$, it satisfies: 
         \begin{align*}
@@
             &= 
-            - \frac{1}{2}\Vert \Pi_C x - \Pi_C y\Vert^2
-            + \left\langle x - \Pi_C x, \Pi_C x - \Pi_C y\right\rangle
+            - \frac{1}{2}\Vert \bar  x - \bar  y\Vert^2
+            + \left\langle x - \bar  x, \bar x - \bar y\right\rangle
             + \frac{1}{2} \Vert x - y\Vert^2. 
@@
         \begin{align*}
-            (\forall z \in \mathcal D(x | C))\; \mathcal D_\varphi(x, z) = \frac{1}{2}\Vert x - z\Vert^2 = D_f(z, x). 
+            (\forall z \in \mathcal D(x | C))\; \mathcal D_\varphi(x, z) = \frac{1}{2}\Vert x - z\Vert^2 = D_\varphi(z, x). 
         \end{align*}
@@
     \begin{assumption}\label{ass:our-ass}
-        The following assumption is about $(f, g, L_f, X^*)$. 
+        The following assumption is about $(F, f, g, L_f, X^*)$. 
         \begin{enumerate}
@@
     We take note that, under the above assumption the function $F = f + g$ is a $L_f$ weakly convex function and, $\widehat \partial F = \partial F$. 
-    \begin{definition}[restricted QUA]
+    The limiting and regular subgradients are the same. 
+    \begin{definition}[relatively restricted SCNVX]\label{def:rel-res-scnvx}
         Suppose that $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:our-ass}. 
-        The function $F = f + g$ has restricted QUA condition if there exists $\kappa_f > 0, D \subseteq \dom g$ such that for all $x \in D$, let $\bar x = \Pi_{X^*}x$ it satisfies: 
+        The function $F = f + g$ has restricted SCNVX condition if there exists $\kappa_f > 0, D \subseteq \dom g$ such that for all $x \in D$, let $\bar x = \Pi_{X^*}x$ it satisfies: 
         \begin{align*}
@@
     \end{remark}
+    \begin{assumption}[two sets feasibility problem]\;\label{ass:two-sets-feasibility}\\
+        The following assumption is about $(F, f, g, L_f, X^*)$. 
+        In addition, we assume the following. 
+        \begin{enumerate}[nosep]
+            \item Let $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:our-ass}. Following that, it has $X^* = \Fix(\Pi_X \Pi_C) \neq \emptyset$. 
+            \item $f = (1/2)\dist(x | C)^2$ where $C \subseteq \RR^n$ is a closed and convex set. 
+            \item $g = \delta_X(x)$ is the indicator function of $X \subseteq \RR^n$, where $X$ is a closed and, nonempty set. 
+        \end{enumerate}
+    \end{assumption}
     The following discussion will give important consequences of this setup. 
     % ------------------------------------------------------------------------------------------------------------------
-    \subsection{examples for restricted QUA}
-        The following assumption will characterize a specific type of convex programming problem that has relative quasi strong convexity. 
-        \begin{assumption}[two sets feasibility problem]\;\label{ass:two-sets-feasibility}\\
-            Suppose $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:our-ass}. 
-            In addition, we assume the following. 
-            \begin{enumerate}[nosep]
-                \item $f = (1/2)\dist(x | C)^2$ where $C \subseteq \RR^n$ is a closed and convex set. 
-                \item $g = \delta_X(x)$ is the indicator function of $X \subseteq \RR^n$, where $X$ is a closed and convex, nonempty set. 
-                \item The set $X^* = \Fix(\Pi_X \Pi_C) \neq \emptyset$. 
-            \end{enumerate}
-        \end{assumption}
-        We will show that, with additional assumptions, function in the above assumption can satisfy the restricted QUA conditions 
-        \begin{theorem}[characterizing restricted QUA]\label{thm:example-rqua}
+    \subsection{examples for restricted SCNVX}
+        In the coming parts we look for conditions for which a function $F = f + g$ satisfying the above assumption also satisfies Definition \ref{def:rel-res-scnvx}. 
+        \begin{theorem}[characterizing restricted SCNVX]\label{thm:example-rqua}
             Suppose that $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:two-sets-feasibility}. 
-            Then for all $x\in X$ such that $\Pi_{X^*} x\in \mathcal D(x | C)$, it has 
+            Then for all $x\in X, \bar x \in \Pi_{X^*} x$ such that $\bar x \in \mathcal D(x | C)$, it has 
             \begin{align*}
-                D_f(x, \Pi_{X^*}x) = \frac{1}{2}\Vert x - \Pi_{X^*} x\Vert^2 = D_f(\Pi_{X^*}x, x). 
+                D_f(x, \bar x) = \frac{1}{2}\Vert x - \bar x \Vert^2 = D_f(\bar x, x). 
             \end{align*}

### 2025-08-09 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
=w=, changes after changes

--- 2025-08-03 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
@@
 
-\section{Our crazy original ideas of extending their definitions}
-    In this section, we will propose our ideas which relaxed Necoara's conditions for strong convexity.
-    \begin{definition}[Breman Divergence for differentiable funtion]\label{def:bd}
-        Let $f: \RR^n \rightarrow \RR$ be a $\mathcal C^1$ function. 
-        The Bregman divergence is a $\RR^n \times \dom \nabla f(x)\rightarrow \RR$ mapping and, it's defined by:  
-        \begin{align*}
-            D_f(x, y) = f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 
-        \end{align*}
-    \end{definition}
-    % ------------------------------------------------------------------------------------------------------------------
-    \begin{theorem}[distance squared Bregman Divergence]\label{thm:bd-dist-sq}
-        Let $C \subseteq \RR^n$ be any closed and non-empty. 
-        Let $\varphi = (1/2)\dist(\cdot | C)^2$.
-        Then for all $x, y \in \RR^n$: 
-        \begin{align*}
-            D_{\varphi}(x, y) 
-            &= 
-            - \frac{1}{2}\Vert \Pi_C x - \Pi_C y\Vert^2
-            + \left\langle x - \Pi_C x, \Pi_C x - \Pi_C y\right\rangle
-            + \frac{1}{2} \Vert x - y\Vert^2. 
-        \end{align*}
-    \end{theorem}
-    \begin{proof}
-        For notational simplicity let $\bar x = \Pi_C x, \bar y = \Pi_C y$. 
-        Recall that $\nabla \varphi (x) = x - \bar x$. 
-        With Definition \ref{def:bd} and, basic algebra we can show that: 
-        \begin{align*}
-            D_{\varphi}(x, y) &= 
-            \varphi(x) - \varphi(y) - \left\langle \nabla \varphi(y), x - y\right\rangle
-            \\
-            &= \varphi(x) - \varphi(y) - \langle y - \bar y, x - y\rangle
-            \\
-            &= \frac{1}{2}(\Vert x - \bar x\Vert^2 - \Vert y - \bar y\Vert^2)
-            - \langle y - \bar y, x - y\rangle
-            \\
-            &= \frac{1}{2}(\Vert x - \bar x\Vert^2 - \Vert y - \bar y\Vert^2)
-            - \frac{1}{2}\Vert x - \bar y\Vert^2 
-            + \frac{1}{2}\left(
-                \Vert y - \bar y\Vert^2 + \Vert x - y\Vert^2
-            \right)
-            \\ 
-            &= \frac{1}{2}\Vert x - \bar x\Vert^2
-            - \frac{1}{2}\Vert x - \bar y\Vert^2 + \frac{1}{2}\Vert x - y\Vert^2
-            \\
-            &= 
-            \frac{1}{2}\Vert x - \bar x\Vert^2
-            - \frac{1}{2}\left(
-                \Vert x - \bar x\Vert^2 + \Vert \bar x - \bar y\Vert^2
-                + 2\langle x - \bar x, \bar x - \bar y\rangle
-            \right)
-            + \frac{1}{2}\Vert x - y\Vert^2
-            \\
-            &= - \frac{1}{2}\Vert \bar x - \bar y\Vert^2 + \langle x - \bar x, \bar x - \bar y\rangle 
-            + \frac{1}{2}\Vert x - y \Vert^2. 
-        \end{align*}
-    \end{proof}
-    \par
-    In the parts that come, we will talk about the set of points that share the same projections onto a set.
-    Let $C \subseteq \RR^n$, we define for all $x \in \RR^n$ the set: 
-    \begin{align}
-        \mathcal D(x | C) = \{z \in \RR^n : \Pi_C z = \Pi_C x\}. 
-    \end{align}
-    The following lemma is a precursor to extend the definition of Q-SCNVX. 
-    The abbreviation ``DSBD'' stands for ``distance squared Bregman Divergence''. 
-    % ------------------------------------------------------------------------------------------------------------------
-    \begin{lemma}[conditions when DSBD behaves like norm squared]
-        Let $C \subseteq \RR^n$ be closed and non-empty. 
-        Let $\varphi = (1/2)\dist(\cdot | C)^2$.
-        Then, for all $x \in \RR^n$ it satisfies
-        \begin{align*}
-            (\forall z \in \mathcal D(x | C))\; \mathcal D_\varphi(x, z) = \frac{1}{2}\Vert x - z\Vert^2 = D_f(z, x). 
-        \end{align*}
-    \end{lemma}
-    \begin{proof}
-        The proof is direct. 
-        For all $x \in \RR^n, z \in \mathcal D(x | C)$, the Bregman Divergence simplifies because using Theorem \ref{thm:bd-dist-sq} it has: 
-        \begin{align*}
-            D_\varphi (x, z) &= 
-            - \frac{1}{2}\Vert \Pi_C x - \Pi_C z\Vert^2 
-            + \langle x - \Pi_C x, \Pi_C x - \Pi_C z\rangle 
-            + \frac{1}{2}\Vert x - z\Vert^2
-            \\
-            &= 0 + 0 + \frac{1}{2}\Vert x - z\Vert^2. 
-        \end{align*}
-        This is true because for all $z \in \mathcal D(x | C)$, it has $\Pi_C x - \Pi_C z = 0$. 
-        Similarly, it has: 
-        \begin{align*}
-            D_\varphi(x, z) &= 
-            - \frac{1}{2}\Vert \Pi_C x - \Pi_C z\Vert^2 
-            + \langle z - \Pi_C z, \Pi_C z - \Pi_C x\rangle
-            + \frac{1}{2}\Vert z - x\Vert^2
-            \\
-            &= 0 + 0 + \frac{1}{2}\Vert z - x\Vert^2. 
-        \end{align*}
-    \end{proof}
-    \par
-    Now, the definition of $\mathcal D(x | C)$ in the above lemma is nothing outrageous. 
-    It simply denotes all points that share the same projection onto $C$ as $x$. 
-    Below, we will give some possible scenarios. 
-    \begin{enumerate}
-        \item When $C$ is convex, the set $\mathcal D(x | C) = \Pi_C x + N_C(\Pi_C x)$. 
-        \item When $C$ is nonconvex, it has $\mathcal D(x | C) \subseteq \Pi_C x + N_C(\Pi_C x)$. 
-    \end{enumerate}
-    Strong convexity is recovered when $C$ is a singleton. 
-    For example when $C = \{\mathbf 0\}$, and $\varphi = (1/2)\Vert x\Vert^2$, this is the usual euclidean Bregman Divergence used to introduce functions that are strongly convex. 
-    Furthermore, take note that $\Pi_C x \in D(x | C)$ always so, we have
-    \begin{align}
-        D_\varphi(x, \Pi_C x) = \frac{1}{2}\Vert x - \Pi_C \Vert^2 = D_\varphi(\Pi_C x, x). 
-    \end{align}
-    \par
-    The following theorems will prepare us for linear convergence of first order algorithms. 
-    \begin{definition}[proximal gradient operator]\label{def:pg}
-        Let $F = f + g$, suppose that $f : \RR^n \rightarrow \RR$ is in $\mathcal C^1$ and $g: \RR^n \rightarrow \overline R$ is l.s.c. 
-        The proximal gradient operator, denoted by $T_{B, f, g}$ is defined as
-        \begin{align*}
-            T_{B, f, g}(x) &= \argmin_{z\in \RR^n} \left\lbrace
-                g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert x - z\Vert^2
-            \right\rbrace
-        \end{align*}
-    \end{definition}
-    \begin{remark}
-        Usually we can find it in the literature that, $T_{B, f, g} = \hprox_{B^{-1}g}(x - B^{-1}\nabla f(x))$. 
-    \end{remark}
-    The following assumption is the weakest and, it doesn't assume convexity at all. 
-    \begin{assumption}[our assumptions]\label{ass:our-ass}
-        The following assumption is about $(f, g, L_f, X^*)$. 
-        \begin{enumerate}
-            \item $f: \RR^n \rightarrow \RR$ is $L_f$ Lipschitz smooth. 
-            \item $g: \RR^n \rightarrow \RR$ is l.s.c
-            \item Denote $X^*$ be the fixed point set of $T_{L_f, f, g}$ and assume $X^* \neq \emptyset$. 
-        \end{enumerate}
-    \end{assumption}
-    \begin{definition}[restricted QUA]
-        Suppose that $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:our-ass}. 
-        The function $F = f + g$ has restricted QUA condition if there exists $\kappa_f > 0, D \subseteq \dom g$ such that for all $x \in D$, let $\bar x = \Pi_{X^*}x$ it satisfies: 
-        \begin{align*}
-            \left(\forall v \in \partial F(\bar x)\right)\;
-            F(x) - F(\bar x) - \langle v, x - \bar x\rangle 
-            &\ge \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2. 
-        \end{align*}
-    \end{definition}
-    \begin{remark}
-        Take note that the RHS of the inequality $\kappa_f/2 \Vert x - \bar x\Vert^2 = D_\varphi(x, \Pi_{X^*}x)$ where $\varphi = (1/2)\dist(x | X^*)^2$. 
-        This definition doesn't exclude nonconvex functions. 
-        The hope is to have the set $D = \dom g$, but we don't think that is always true. 
-        Our hope is that the set $D$ is at least somewhat larger than $X^+$. 
-    \end{remark}
-    The following discussion will give important consequences of this setup. 
-    % ------------------------------------------------------------------------------------------------------------------
-    \subsection{examples for relatively quasi strongly convex functions}
-        The following assumption will characterize a specific type of convex programming problem that has relative quasi strong convexity. 
-        \begin{assumption}[distance of two sets]
-            Suppose $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:our-ass}. 
-            In addition, we assume the following. 
-            \begin{enumerate}[nosep]
-                \item 
-            \end{enumerate}
-        \end{assumption}
-        \begin{theorem}[example of restricted QUA]\label{thm:example-rqua}
-
-        \end{theorem}
-        \begin{proof}
-
-        \end{proof}
-    % ------------------------------------------------------------------------------------------------------------------
-    \subsection{theorems useful for convergence analysis of algorithms}
-        The proximal gradient inequality and, the Jensen inequality are the most important for deriving convergence rate of first order accelerated method.
+\section{Precurors materials for our proofs of linear convergence}
+    We propose an alternative approach that extends the results, and make comparison with existing works from Necoara et al.
 

### 2025-08-11 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, changes

@@
 
-\title{{\fontfamily{ptm}\selectfont My Ideas after Reading Necoara's Papers}}
+\title{{\fontfamily{ptm}\selectfont Linear Convergence of Accelerated Gradient without Restart requires some very strict conditions}}
 
@@
     \end{definition}
-    These definitions are the keys which Necoara used to prove the linear convergence of projected gradient, and Nesterov's accelerated gradient method.
+    These definitions are the keys which Necoara's used to prove the linear convergence of projected gradient, and Nesterov's accelerated gradient method. 
+    In this paper, we will show a simple perspective that simplifies their arguments on linear convergence Accelerated Gradient method, without restart. 
+    \par
+    Unfortunately, and this is said at the start, so far the new perspective doesn't produce new results that are not in the literature.
 
-\section{Precurors materials for our proofs of linear convergence}
-    We propose an alternative approach that extends the results, and make comparison with existing works from Necoara et al.
+\section{Precursors materials for our proofs of linear convergence}
+    For a function $f: \RR^n \rightarrow \RR$ we define its Bregman Divergence to be a mapping of $\RR^n \times \dom\nabla f\mapsto \overline \RR$ for all $x, y \in \RR^n$: 
+    \begin{align*}
+        D_f(x, y) &= 
+        f(x) - f(y) - \langle \nabla f(y), x - y\rangle 
+    \end{align*}
+    Let $F = f + g$ where $f$ is $L$ Lipschitz smooth and $g$ is convex.
+    Let $B > 0$. 
+    We define the proximal gradient operator 
+    \begin{align*}
+        T_{B}(x) = \argmin_{z}\left\lbrace
+            g(z) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
+        \right\rbrace. 
+    \end{align*}
+    Take note that it's also $T_B(x) = \hprox_{B^{-1}g}(x - B^{-1}\nabla f(x))$, which is another equivalent representation. 
+    \begin{assumption}[objective function]\;\label{ass:obj-fxn}\\
+        The following assumption is about $(F, f, g, h, A, b, \mu, L)$. 
+        Let $m \in \N, n \in \N$ be arbitrary. 
+        \begin{enumerate}[nosep]
+            \item $h: \RR^m \mapsto \RR$ is a $L$ Lipschitz smooth and, $\mu \ge 0$ strongly convex function. 
+            \item $A \in \RR^{m \times n}, b \in \RR^n$ are a matrix and a vector. 
+            \item $f = h(Ax - b)$. 
+            \item $g = \delta_{X}$, so $g$ is an indicator function of the set $X \subseteq \RR^n$ which we assume that it's closed onvex and non-empty. 
+        \end{enumerate}
+    \end{assumption}
 
-\section{Linear convergence of first order methods}
+    \begin{lemma}[strongly and Lipscthiz smooth convex affine composite]\;\label{lemma:aff-scnvx-smooth-lin-comp}\\
+        Let $A \in \RR^{m \times n}, b \in \RR^n$. 
+        Let $h: \RR^m \mapsto \RR$ be a $L$ Lipschitz and $\mu \ge 0$ strongly convex function. 
+        Then it has for all $x, y \in \RR^n$: 
+        \begin{align*}
+            \frac{\sigma(A)^2\mu}{2}\Vert \Pi_{\ker A}(x - y)\Vert^2 
+            &\le 
+            D_f(x, y) 
+            \le 
+            \frac{L\Vert A\Vert^2}{2}\Vert x - y\Vert^2. 
+        \end{align*}
+    \end{lemma}
+    \begin{proof}
+        The lower bound is given by: 
+        \begin{align*}
+            & f(x) - f(y) - \langle \nabla f(y), x - y\rangle
+            \\
+            &=
+            h(Ax) - h(Ay) - \langle A^T \nabla h(y), x - y\rangle
+            \\
+            &= h(Ax) - h(Ay) - \langle \nabla h(y), Ax - Ay\rangle
+            \\
+            &\ge \frac{\mu}{2}\Vert Ax - Ay\Vert^2
+            \\
+            &\ge 
+            \frac{\mu}{2}
+            \left(
+                \Vert A\Pi_{\ker\; A}(x - y)
+                + A(I - \Pi_{\ker\; A})(x - y) \Vert^2 
+            \right)
+            \\
+            &\ge
+            \frac{\mu\sigma(A)^2}{2}\Vert (I - \Pi_{\ker\; A})(x - y) \Vert^2. 
+        \end{align*}
+        The upper bound is direct from smoothness, which has: 
+        \begin{align*}
+            & f(x) - f(y) - \langle \nabla f(y), x - y\rangle
+            \\
+            &= h(Ax) - h(Ay) - \langle \nabla h(y), Ax - Ay\rangle
+            \\
+            &\le \frac{L}{2}\Vert Ax - Ay\Vert^2
+            \\
+            &\le \frac{L\Vert A\Vert^2}{2}\Vert x - y\Vert^2. 
+        \end{align*}
+    \end{proof}
+    \begin{theorem}[proximal gradient inequality]\label{thm:pg-ineq}
+        Suppose that $(F, f, g, h, A, b, \mu, L)$ satisfies Assumption \ref{ass:obj-fxn}. 
+        Consider any $x, z \in \RR^n$, then there exists a $B \ge 0$ such that for $x^+ = T_B(x)$, it has $D_f(x, x^+) \le \frac{B}{2}\Vert x - x^+\Vert^2$, and it satisfies: 
+        \begin{align*}
+            0 &\le F(z) - F(x^+) + \frac{B - \mu\sigma(A)^2}{2}\Vert z - x\Vert^2 
+            - \frac{B}{2}\Vert z - x^+\Vert^2
+            + \frac{\mu\sigma(A)^2}{2}\Vert \Pi_{\ker A}(z - x)\Vert^2. 
+        \end{align*}
+    \end{theorem}
+    \begin{proof}
+        Denote $\sigma =\sigma(A)$ for short, and $\Pi = \Pi_{\ker A}, \Pi_{\perp} = I - \Pi_{\ker A}$ for short. 
+        The function in the proximal gradient operator is $L$ strongly convex, so it has quadratic growth over the minimizer $x^+$: 
+        \begin{align*}
+            & \frac{B}{2}\Vert z - x^+\Vert^2
+            \\
+            &\le 
+            \left(
+                g(z) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
+            \right)
+            - \left(
+                g(x^+) + \langle \nabla f(x), x^+ - x\rangle + \frac{B}{2}\Vert x - x^+\Vert^2
+            \right)
+            \\
+            &=
+            \left(
+                F(z) - D_f(z, x) + \frac{B}{2}\Vert z - x\Vert^2
+            \right) - 
+            \left(
+                F(x^+) - D_f(x^+, x) + \frac{B}{2}\Vert x - x^+\Vert^2
+            \right)
+            \\
+            &\underset{(1)}{\le}
+            \left(
+                F(z) + \frac{B}{2}\Vert z - x\Vert^2 
+                - \frac{\mu\sigma^2}{2}\Vert \Pi_{\perp}(z - x)\Vert^2
+            \right)
+            - \left(
+                F(x^+) - D_f(x^+, x) + \frac{B}{2}\Vert x - x^+\Vert^2
+            \right)
+            \\
+            &\underset{(2)}{\le} 
+            F(z) 
+            + \frac{B}{2}\Vert z - x\Vert^2
+            - \frac{\mu\sigma^2}{2}\Vert \Pi_{\perp}(z - x)\Vert^2
+            - F(x^+). 
+        \end{align*}
+        At (1), we used the fact that $f = h(Ax + b)$, so it has $D_f(z, x) \ge \frac{\mu\sigma(A)^2}{2}\Vert \Pi_{\perp}(z - x)\Vert^2$. 
+        At (2), we used the fact that $B$ makes $- D_f(x, x^+) + \frac{B}{2}\Vert x - x^+\Vert^2 \ge 0$. 
+        Continuing it has 
+        \begin{align*}
+            0 
+            &\le 
+            F(z) + \frac{B}{2}\Vert z - x\Vert^2 
+            - \frac{\mu\sigma^2}{2}\Vert \Pi_{\perp}(z - x)\Vert^2
+            - F(x^+)
+            - \frac{B}{2}\Vert z - x^+\Vert^2
+            \\
+            &= 
+            F(z) 
+            + \frac{B}{2}\Vert z - x\Vert^2 
+            - \frac{\mu\sigma^2}{2}\left(
+                \Vert z - x\Vert^2 
+                - \Vert \Pi(z - x)\Vert^2
+            \right)
+            - F(x^+)
+            - \frac{B}{2}\Vert z - x^+\Vert^2
+            \\
+            &\le F(z) - F(x^+)
+            + \frac{B - \mu\sigma^2}{2}\Vert z - x\Vert^2 
+            - \frac{B}{2}\Vert z - x^+\Vert^2
+            + \frac{\mu\sigma^2}{2}\Vert \Pi(z - x)\Vert^2. 
+        \end{align*}
+    \end{proof}
+    \begin{theorem}[Jesen's inequality]\;\label{thm:jen-ineq}
+        Let $h: \RR^n \rightarrow \RR$ be a $L$ Lipschitz smooth and $\mu\ge 0$ strongly convex function.  
+        Let $A \in \RR^{n\times m}, b \in \RR^n$. 
+        Denote $\Pi_{\perp} = I - \Pi_{\text{ker}\; A}$ for short. 
+        Suppose that $f(x) = h(Ax + b)$, then it satisfies for all $x, y \in \RR^n, \lambda\in [0, 1]$ the inequality: 
+        \begin{align*}
+            &f(\lambda x + (1 - \lambda)y) 
+            \\
+            &\le 
+            f(\lambda x + (1 - \lambda)y) + \lambda f(x) - (1 - \lambda)f(y)
+            - \frac{\mu\sigma(A)^2\lambda(1 - \lambda)}{2}\Vert \Pi_{\perp}(x - y)\Vert^2. 
+        \end{align*}
+    \end{theorem}
+    \begin{proof}   
+        To simplify notations, we denote $\sigma = \sigma(A)$ for short, and use $\Pi = \Pi_{\text{ker}A}$, $\Pi_{\perp} = I - \Pi_{\text{ker}A}$ for short. 
+        From Assumption 4 it has $f = h(Ax + b)$ therefore it has the following
+        {\small
+        \begin{align*}
+            0 &\le D_f(x, y)  - \frac{\sigma^2 \mu}{2}\Vert \Pi_{\perp}(x - y)\Vert^2
+            \\
+            &= f(x) - f(y) - \langle \nabla f(y), x - y\rangle 
+            - \frac{\sigma^2 \mu}{2}\left\Vert \Pi_{\perp}(x - y)\right\Vert^2
+            \\
+            &=
+            f(x) - f(y) - \langle \nabla f(y), x - y\rangle
+            - \frac{\sigma^2 \mu}{2}\left\Vert \Pi_{\perp}x\right\Vert^2
+            - \frac{\sigma^2 \mu}{2}\left\Vert \Pi_{\perp}y\right\Vert^2
+            + \sigma^2\mu\langle \Pi_{\perp}x, \Pi_{\perp}y\rangle
+            \\
+            &= 
+            f(x) - \frac{\sigma^2 \mu}{2}\Vert \Pi_{\perp} x\Vert^2
+            - \left(
+                f(y) - \frac{\mu\sigma^2}{2}\Vert \Pi_\perp y\Vert^2 
+            \right) 
+            \\&\quad 
+                - \sigma^2\mu\Vert \Pi_{\perp} y\Vert^2
+                - \langle \nabla f(y), x - y\rangle
+                + \sigma^2\mu\langle \Pi_\perp x, \Pi_\perp y\rangle
+            \\
+            &= 
+            f(x) - \frac{\sigma^2 \mu}{2}\Vert \Pi_{\perp} x\Vert^2
+            - \left(
+                f(y) - \frac{\mu\sigma^2}{2}\Vert \Pi_\perp y\Vert^2 
+            \right) 
+            - \langle \nabla f(y), x - y\rangle
+            + \sigma^2\mu\langle \Pi_\perp (x - y), \Pi_\perp y\rangle
+            \\
+            &= 
+            f(x) - \frac{\sigma^2 \mu}{2}\Vert \Pi_{\perp} x\Vert^2
+            - \left(
+                f(y) - \frac{\mu\sigma^2}{2}\Vert \Pi_\perp y\Vert^2 
+            \right) 
+            - \langle \nabla f(y), x - y\rangle
+            + \sigma^2\mu\left\langle x - y, \Pi_\perp^{\top}\Pi_\perp  y\right\rangle
+            \\
+            &= 
+            f(x) - \frac{\sigma^2 \mu}{2}\Vert \Pi_{\perp} x\Vert^2
+            - \left(
+                f(y) - \frac{\mu\sigma^2}{2}\Vert \Pi_\perp y\Vert^2 
+            \right) 
+            + \left\langle x - y, \sigma^2\mu\Pi_\perp^{\top}\Pi_\perp  y - \nabla f(y)\right\rangle. 
+        \end{align*}
+        }
+        Next, if $\phi (x) = f(x) + \frac{\sigma^2\mu}{2}\Vert \Pi_\perp x\Vert^2$, then $\nabla \phi(x) = \nabla f(x) + \mu\sigma^2\Pi_{\perp}^\top \Pi_{\perp} x$. 
+        From here, it's not hard to see that the above inequality is:  $ 0\le \phi(x) - \phi(y) - \left\langle \nabla \phi(y), x - y\right\rangle$. 
+        Hence, the function $f(x) - \frac{\sigma\mu}{2}\Vert \Pi_\perp x\Vert^2$ is a convex function. 
+        From here, we will be ready to show the Jensen's formula. 
+        For all $x, y \in \RR^n$, consider the convexity of $\phi$, it has for all $\lambda \in [0, 1]$ the inequality: 
+        \begin{align*}
+            0 &\le \lambda \phi(x) + (1 - \lambda)\phi(x) - \phi(\lambda x + (1 - \lambda)y)
+            \\
+            &\underset{(1)}{=} 
+            f(\lambda x + (1 - \lambda)y) - \lambda f(x) - (1 - \lambda)f(y)
+            - \frac{\mu\sigma^2\lambda(1 - \lambda)}{2}\Vert \Pi_{\perp}(x - y)\Vert^2. 
+        \end{align*}
+        At (1), we skipped a lot of algebra that the reader should be familiar if they already seem the proof in for $f$ that is strongly convex.
+    \end{proof}
+\section{the accelerated proximal gradient algorithm again}
+    In this section we introduce the algorithms usually used in Nesterov's accelerated gradient. 
+    \begin{definition}[similar triangle form]\label{def:st-form}
+        Suppose that 
+        \begin{enumerate}
+            \item $F = f + g$ with $f$ Lipschitz smooth and, $g$ closed convex proper, 
+            \item Denote $T_B$ to be the proximal gradient operator on $F = f + g$, 
+            \item Let $q_k \in [0, 1)$ for all $k \ge 0$ be a parameter of the algorithm, 
+            \item $(B_k)_{k \ge 0}$ is a sequence such that $B_k \ge 0$ for all $k \ge 0$. 
+        \end{enumerate}
+        Given the initial condition $v_{-1}, x_{-1} \in \RR^n$. 
+        An algorithm is a similar triangle form of the accelerated proximal gradient if the iterates generated $(y_k, x_k, v_k)_{k \ge 1}$ satisfies for all $k \ge 1$: 
+        \begin{align*}
+            y_k &= \left(\frac{\alpha_k - q_k}{1 - q_k}\right)v_{k - 1} 
+            + \left(\frac{1 - \alpha_k}{1 - q_k}\right) x_{k - 1},
+            \\
+            x_k &= T_{B_k}(y_k) \text{ s.t: } D_f(x_k, y_k) \le \frac{B_k}{2}\Vert x_k - y_k\Vert^2. 
+            \\
+            v_k &= x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
+        \end{align*}
+    \end{definition}
+    \begin{definition}[relaxed Nesterov's momentum sequence]\;\label{def:r-nes-seq}\\
+        We let 
+        \begin{enumerate}
+            \item $(q_k)_{k \ge 0}$ be a sequence such that $q_k \in (0, 1]$ for all $k \ge 1$, 
+            \item $(\alpha_k)_{k \ge 0}$ be a sequence such that, $\alpha_0 \in (0, 1]$, and $\alpha_k \in (q_k, 1)$ for all $k \ge 1$. 
+        \end{enumerate}
+        For all $k \ge 1$ we define the sequence $(\rho_k)_{k \ge 0}$: 
+        \begin{align*}
+            \rho_{k - 1} &= \frac{\alpha_k(\alpha_k - q_k)}{(1 - \alpha_{k})\alpha_{k - 1}^2}. 
+        \end{align*}
+    \end{definition}
+
+\section{Convergence of accelerated gradient}
+    \subsection{preparing for the convergence proof}
+        \begin{lemma}[Convergence preparation part I]\label{lemma:cnvg-prep-part1}
+            Let the sequence $(y_k, x_k, v_k)_{k \ge 1}$ be a sequence generated by Definition \ref{def:st-form}. 
+            Let $\bar x \in \RR^n$ be arbitrary, define $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k$. 
+            Then the sequence of iterates satisfies for all $k \ge 1$ all of the following equalities: 
+            \begin{align*}
+                z_k - y_k &= (1 - q_k)^{-1}\left(
+                    (\alpha_k - q_k)(\bar x - v_{k - 1}) + q_k(1 - \alpha_k)(\bar x - x_{k - 1})
+                \right), 
+                \\
+                z_k - x_k &= \alpha_k (\bar x - v_k), 
+                \\
+                y_k &= x_{k -1} + (1 - q_k)^{-1}(\alpha_{k - 1} - 1)(\alpha_k - q_k)(x_{k - 1} - x_{k - 2}). 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            From the update of $y_k$ in Definition \ref{def:st-form}, we have: 
+            \begin{align*}
+                0 &= \left(
+                \frac{\alpha_k - q_k}{1 - q_k} 
+                \right)v_{k - 1} 
+                + \left(
+                    \frac{1 - \alpha_k}{1 - q_k}
+                \right)x_{k - 1} - y_k
+                \\
+                &= 
+                \left(
+                    \frac{\alpha_k - q_k}{1 - q_k} 
+                \right)v_{k - 1} 
+                + (1 - \alpha_k)x_{k - 1}
+                + \left(
+                    \frac{1 - \alpha_k}{1 - q_k} - (1 - \alpha_k)
+                \right)x_{k - 1} - y_k
+                \\
+                &= 
+                \left(
+                    \frac{\alpha_k - q_k}{1 - q_k} 
+                \right)v_{k - 1} 
+                + (1 - \alpha_k)x_{k - 1}
+                + (1 - \alpha_k)\left(
+                    \frac{1 - (1 - \alpha_k)}{1 - q_k}
+                \right)x_{k - 1} - y_k
+                \\
+                &= 
+                \left(
+                    \frac{\alpha_k - q_k}{1 - q_k} 
+                \right)v_{k - 1} 
+                + (1 - \alpha_k)x_{k - 1}
+                + \frac{q_k(1 -\alpha_k)}{1 - q_k}x_{k - 1} - y_k. 
+            \end{align*}
+            Recall that $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k$. 
+            Therefore, using previous results we have:
+            \begin{align*}
+                z_k - y_k &= 
+                \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
+                \\
+                &= \alpha_k \bar x 
+                - \left(
+                    \frac{\alpha_k - q_k}{1 - q_k}
+                \right)v_{k - 1}
+                - \frac{q_k(1 -\alpha_k)}{1 - q_k}x_{k - 1}
+                \\
+                &= 
+                \left(
+                    \frac{\alpha_k - q_k}{1 - q_k}
+                \right)(\bar x - v_{k - 1})
+                + \left(
+                    \alpha_k - \frac{\alpha_k - q_k}{1 - q_k} 
+                \right)\bar x
+                - \frac{q_k(1 -\alpha_k)}{1 - q_k}x_{k - 1}
+                \\
+                &= 
+                \left(
+                    \frac{\alpha_k - q_k}{1 - q_k}
+                \right)(\bar x - v_{k - 1})
+                + \left(
+                    \frac{\alpha_k - \alpha_kq_k - (\alpha_k - q_k)}{1 - q_k}
+                \right)\bar x
+                - \frac{q_k(1 -\alpha_k)}{1 - q_k}x_{k - 1}
+                \\
+                &= 
+                \left(
+                    \frac{\alpha_k - q_k}{1 - q_k}
+                \right)(\bar x - v_{k - 1})
+                + \left(
+                    \frac{q_k(1 - \alpha_k)}{1 - q_k}
+                \right)\left(
+                    \bar x - x_{k - 1}
+                \right). 
+            \end{align*}
+            Using some basic algebra we also have: 
+            \begin{align*}
+                z_k - x_k &= 
+                \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k 
+                \\
+                &= \alpha_k \bar x + x_{k - 1} - \alpha_k x_{k -1} - x_k
+                \\
+                &= \alpha_k (\bar x  + \alpha_k^{-1}x_{k - 1} - x_{k - 1} - \alpha_k^{-1} x_k) 
+                \\
+                &= \alpha_k (\bar x  + \alpha_k^{-1}(x_{k - 1} - x_k)- x_{k - 1}) 
+                \\
+                &= \alpha_k (\bar x - v_k). 
+            \end{align*}
+            Finally, $y_k$ can be expressed using $x_k$ only. 
+            Starting with the first recurrence relation it has: 
+            \begin{align*}
+                (1 - q_k)^{-1}y_k &= 
+                (\alpha_k - q_k) v_{k - 1} 
+                + (1 - \alpha_k)x_{k - 1}
+                \\
+                &= 
+                (\alpha_k - q_k)\left(
+                    x_{k - 2} + \alpha_{k - 1}^{-1}(x_{k - 1} - x_{k - 2})
+                \right) 
+                + (1 - \alpha_k)x_{k - 1}
+                \\
+                &= 
+                (\alpha_k - q_k)x_{k - 2} 
+                + \alpha_{k - 1}^{-1}(x_{k - 1} - x_{k - 2}) + (1 - \alpha_k)x_{k - 1}
+                \\
+                &= (\alpha_k - q_k)(1 - \alpha_{k - 1}^{-1})x_{k - 2}
+                + \left(
+                    \frac{\alpha_k - q_k}{\alpha_{k - 1}} + 1 - \alpha_k
+                \right)x_{k - 1}. 
+            \end{align*}
+            After some algebra it has: 
+            \begin{align*}
+                y_k &= 
+                \frac{(\alpha_k - q_k)(1 - \alpha_{k - 1}^{-1})}{1 - q_k}x_{k - 2} 
+                + \left(
+                    \frac{\alpha_k - q_k}{\alpha_{k - 1}(1 - q_k)} + \frac{1 - \alpha_k}{1 - q_k}
+                \right)x_{k - 1}
+                \\
+                &= 
+                \frac{(\alpha_k - q_k)(1 - \alpha_{k - 1}^{-1})}{1 - q_k}x_{k - 2} 
+                + \left(
+                    \frac{
+                        (\alpha_{k - 1}^{-1} -1)(\alpha_k - q_k)
+                        + \alpha_k - q_k + 1 - \alpha_k
+                    }{1 - q_k}
+                \right)x_{k - 1}
+                \\
+                &= \frac{(\alpha_k - q_k)(1 - \alpha_{k - 1}^{-1})}{1 - q_k}x_{k - 2} 
+                + \left(
+                    \frac{
+                        (\alpha_{k - 1}^{-1} -1)(\alpha_k - q_k)
+                    }{1 - q_k} + 1
+                \right)x_{k - 1}
+                \\
+                &= x_{k -1} + (1 - q_k)^{-1}(\alpha_{k - 1} - 1)(\alpha_k - q_k)(x_{k - 1} - x_{k - 2}). 
+            \end{align*}
+        \end{proof}
+        \begin{lemma}[Convergence preparations part II]\;\label{lemma:cnvg-prep-part2}\\
+            Suppose that sequences $(y_k, x_k, v_k)_{k \ge 0}$ satisfies Definition \ref{def:st-form}. 
+            In addition assume that the sequence $(\alpha_k)_{k \ge 0}$ satisfies Definition \ref{def:r-nes-seq}. 
+            For any arbitrary $\bar x \in \RR^n$, define for all $k \ge 1$ the sequence $z_k = \alpha_k \bar x + (1 - \alpha_k) x_{k - 1}$. 
+            Then, for all $k \ge 1$, it has:
+            \begin{align*}
+                & \frac{1 - q_k}{2}\Vert z_k - y_k\Vert^2
+                - \frac{q_k\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
+                \\
+                &= 
+                \frac{\alpha_{k - 1}\rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{q_k(1 - \alpha_k)(q_k - \alpha_k)}{1 - q_k}\Vert v_{k - 1} - x_{k - 1}\Vert^2
+                \\
+                &\le 
+                \frac{\alpha_{k - 1}\rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2. 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            \begin{align}\label{eqn:cnvg-prep-part2-eqn1}
+                \begin{split}
+                    \frac{(\alpha_k - q_k)^2}{2(1 - q_k)}
+                    - \frac{\alpha_{k - 1}\rho_{k - 1}(1 - \alpha_k)}{2}
+                    &\underset{(1)}{=} 
+                    \frac{(\alpha_k - q_k)^2}{2(1 - q_k)}
+                    - \frac{\alpha_k(\alpha_k - q_k)}{2}
+                    \\
+                    &= \frac{1}{2(1 - q_k)}\left(
+                        (\alpha_k - q_k)^2 - (1 - q_k)\alpha_k(\alpha_k - q_k)
+                    \right)
+                    \\
+                    &= \frac{\alpha_k - q_k}{2(1 - q_k)}
+                    \left(
+                        \alpha_k - q_k - (1 - q_k)\alpha_k
+                    \right)
+                    \\
+                    &= 
+                    \frac{\alpha_k - q_k}{2(1 - q_k)}
+                    \left(
+                        - q_k + q_k \alpha_k
+                    \right)
+                    \\
+                    &= \frac{(\alpha_k -q_k)q_k (\alpha_k - 1)}{1 - q_k}. 
+                \end{split}
+            \end{align}
+            At (1), we used the relation $\alpha_{k - 1} \rho_{k - 1}(1 - \alpha_k) = \alpha_k(\alpha_k - q_k)$ because the sequence $(\alpha_k)_{k \ge 1}$ satisfies Definition \ref{def:r-nes-seq}.
+            Next, we have: 
+            \begin{align}\label{eqn:cnvg-prep-part2-eqn2}
+                \begin{split}
+                    \frac{q_k^2(1 - \alpha_k)^2}{1 - q_k}
+                    - q_k\alpha_k(1 - \alpha_k)
+                    &= 
+                    \frac{q_k(1 - \alpha_k)}{1 - q_k}
+                    \left(
+                        q_k(1 - \alpha_k) - \alpha_k(1 - q_k)
+                    \right)
+                    \\
+                    &= 
+                    \frac{q_k(1 - \alpha_k)(q_k - \alpha_k)}{1 - q_k}. 
+                \end{split}
+            \end{align}
+            Next, using two of the above results we have: 
+            {\allowdisplaybreaks\small
+            \begin{align*}
+                & \frac{1 - q_k}{2}\Vert z_k - y_k\Vert^2
+                - \frac{q_k\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
+                \\
+                &\underset{(1)}{=}
+                \frac{1 - q_k}{2}
+                \left\Vert
+                    \left(
+                    \frac{\alpha_k - q_k}{1 - q_k}
+                    \right)(\bar x - v_{k - 1})
+                    + \left(
+                        \frac{q_k(1 - \alpha_k)}{1 - q_k}
+                    \right)\left(
+                        \bar x - x_{k - 1}
+                    \right)
+                \right\Vert^2
+                - \frac{q_k\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
+                \\
+                &= 
+                \frac{(\alpha_k - q_k)^2}{2(1 - q_k)}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{q_k^2(1 - \alpha_k)^2}{2(1 - q_k)}\Vert \bar x - x_{k - 1}\Vert^2
+                + \frac{(\alpha_k - q_k)q_k(1 - \alpha_k)}{1 - q_k}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+                    \\&\quad 
+                    - \frac{1}{2}q_k \alpha_k(1 - \alpha_k)\Vert \bar x - x_{k - 1}\Vert^2
+                \\
+                &= \frac{(\alpha_k - q_k)^2}{2(1 - q_k)}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{1}{2}\left(
+                    \frac{q_k^2(1 - \alpha_k)^2}{1 - q_k} - q_k \alpha_k(1 - \alpha_k)
+                \right)\Vert \bar x - x_{k - 1}\Vert^2
+                    \\ &\quad 
+                    + \frac{(\alpha_k - q_k)q_k(1 - \alpha_k)}{1 - q_k}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+                \\
+                &= \frac{(\alpha_k - q_k)^2}{2(1 - q_k)}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{1}{2}\left(
+                    \frac{q_k^2(1 - \alpha_k)^2}{1 - q_k} - q_k \alpha_k(1 - \alpha_k)
+                \right)\Vert \bar x - x_{k - 1}\Vert^2
+                    \\ &\quad 
+                    + \frac{(\alpha_k - q_k)q_k(1 - \alpha_k)}{1 - q_k}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+                \\
+                &= 
+                \frac{1}{2}\left(
+                    \frac{(\alpha_k - q_k)^2}{1 - q_k}
+                    - \alpha_{k - 1}^2 \rho_{k - 1}(1 - \alpha_k)
+                \right)\Vert \bar x - v_{k - 1}\Vert^2
+                    \\&\quad
+                    + \frac{1}{2}\left(
+                        \frac{q_k^2(1 - \alpha_k)^2}{1 - q_k} - q_k \alpha_k(1 - \alpha_k)
+                    \right)\Vert \bar x - x_{k - 1}\Vert^2
+                    \\ &\quad 
+                    + \frac{(\alpha_k - q_k)q_k(1 - \alpha_k)}{1 - q_k}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+                    - \frac{\alpha_{k - 1}^2 \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                \\
+                &\underset{\text{(2)}}{=}
+                \frac{1}{2}\frac{(\alpha_k - q_k)q_k(\alpha_k - 1)}{1 - a_k}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{1}{2}\left(
+                    \frac{q_k^2(1 - \alpha_k)^2}{1 - q_k} - q_k \alpha_k(1 - \alpha_k)
+                \right)\Vert \bar x - x_{k - 1}\Vert^2
+                    \\ &\quad 
+                    + \frac{(\alpha_k - q_k)q_k(1 - \alpha_k)}{1 - q_k}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+                    - \frac{\alpha_{k - 1}^2 \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                \\
+                &\underset{\text{(3)}}{=}
+                \frac{1}{2}\frac{(\alpha_k - q_k)q_k(\alpha_k - 1)}{1 - a_k}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{1}{2}\frac{q_k(1 - \alpha_k)(q_k - \alpha_k)}{1 - q_k}\Vert \bar x - x_{k - 1}\Vert^2
+                    \\ &\quad 
+                    + \frac{(\alpha_k - q_k)q_k(1 - \alpha_k)}{1 - q_k}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
+                    - \frac{\alpha_{k - 1}^2 \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                \\
+                &= \frac{\alpha_{k - 1}^2\rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{q_k(1 - \alpha_k)(q_k - \alpha_k)}{1 - q_k}\Vert v_{k - 1} - x_{k - 1}\Vert^2. 
+                \\
+                &\underset{(4)}{\le}
+                \frac{\alpha_{k - 1}^2\rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2. 
+            \end{align*}
+            }
+            At (1) we used one of the results from Lemma \ref{lemma:cnvg-prep-part1}, at (2) we used \eqref{eqn:cnvg-prep-part2-eqn1}, and at (3) we used \eqref{eqn:cnvg-prep-part2-eqn2}. 
+            At (4), we used the fact that $\alpha_k \in (q_k, 1)$, which means that the coefficient $q_k(1 - \alpha_k)(q_k - \alpha_k) \le 0$, therefore we can simplify the term away. 
+        \end{proof}
+        \begin{theorem}[the convergence results]
+        \end{theorem}
+        \begin{proof}
+
+        \end{proof}
 

### 2025-08-14 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, nontrivial changes

--- 2025-08-09 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
@@
 
-\title{{\fontfamily{ptm}\selectfont My Ideas after Reading Necoara's Papers}}
+\title{{\fontfamily{ptm}\selectfont Linear Convergence of Accelerated Gradient without Restart}}
 
@@
 \maketitle
-\todoinline{This paper is currently in draft mode. Check source to change options. }
+\todoinline{This paper is currently in draft mode. Check source to change options. \cite{bauschke_convex_2017}}
 % \vskip 8mm
@@
     \noindent
-    This is still a note for a draft so no abstract \cite{bauschke_convex_2017}
+    This is still a note for a draft so no abstract. 
 \end{abstract}
@@
 \section{Introduction}
-    Necoara et al.
-\cite{necoara_linear_2019}  introduced the definition of quasi strongly convex function (Q-SCNVX), Quadratic Under approximations (QUA), Quadratic Gradient Growth (QGG), Proximal Error Bound (PEB) and, Quadratic Function Growth (QFG).
-    These conditions are relaxation of strong convexity which enables linear convergence rate of first order method, including Nesterov's accelerated variants. 
-    In this file, we showed a new perspective of their works. 
-    Our goal is to relax their definitions and, to extend the linear convergence results, using completely new ideas and perspective. 
-    \par
     \textbf{Notations.}
@@
     Let $C\subseteq \RR^n$, $\Pi_C(\cdot)$ denotes the projection onto the set $C$, i.e: the closest point in $C$ to another point in $\RR^n$. 
-    \par
-    The following definitions and assumptions are their. 
-    % SYMBOL SET FOR THIS CHAPTER ONLY!
+    For a function of $F = f + g$, and a $B\ge 0$ where $f$ is $\mathcal C^1$ differentiable, and $g$ is l.s.c, we consider the proximal gradient operator: 
+    \begin{align*}
+        T_B(x) &= \argmin_{z} \left\lbrace
+            g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert x - z\Vert^2
+        \right\rbrace
+        \\
+        &= \hprox_{B^{-1}g}(x - B^{-1}\nabla f(x)). 
+    \end{align*}
+    We also define the gradient mapping operator
 
-    \begin{assumption}[Necoara's linear convergence assumptions]\; \label{ass:necoara-linear} \\
-        The following assumptions are about $(f, X, X^*, L_f)$. 
-        \begin{enumerate}[nosep]
-            \item $f: \RR^n \rightarrow \RR$ is an $L_f$ Lipschitz smooth function. 
-            \item $X \subseteq \RR^n$ is a closed convex non-empty set. 
-            \item $X^* = \argmin_{x \in X} f(x) \neq \emptyset$. 
-        \end{enumerate}
-    \end{assumption}
-    Under this assumption, the following definitions are proposed. 
-    \newcommand{\QSCNVX}{\ensuremath{q\mathcal{S}}}
-    \newcommand{\QUA}{\ensuremath{\mathcal U}}
-    \newcommand{\QGG}{\ensuremath{\mathcal G}}
-    \newcommand{\QFG}{\ensuremath{\mathcal F}} 
-    \newcommand{\PEB}{\ensuremath{\mathcal E}}
-    \begin{definition}[Necoara's weaker characterizations of strong convexity]\; \\
-        Suppose that $(f, X, X^*, L_f)$ are given by Assumption \ref{ass:necoara-linear}. 
-        For all $x \in X$, denote $\bar x = \Pi_{X^*}x$. 
-        The following definitions are relaxations of strong convexity. 
-        \begin{enumerate}[nosep]
-            \item $f$ is Q-SCNVX if there exists $\kappa_f > 0$ such that $f(\bar x) - f(x) - \langle \nabla f(x), \bar x - x\rangle \ge \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. 
-            Which we denote it by $f \in \QSCNVX(f, L_f, \kappa_f)$. 
-            \item $f$ is QUA if there exists $\kappa_f > 0$ such that $f(x) - f(\bar x) - \langle \nabla f(\bar x), x - \bar x\rangle \ge \frac{\kappa_f}{2}\Vert x -\bar x\Vert^2$. 
-            We denote it by $f \in \QUA(f, L_f, \kappa_f)$.
-            \item $f$ is QGG if there exists $\kappa_f > 0$ such that $\langle \nabla f(x) - \nabla f(\bar x), x - \bar x\rangle \ge \frac{\kappa}{2}\Vert x - \bar x\Vert^2$. 
-            We denote it by $f \in \QGG(f, L_f, \kappa_f)$. 
-            \item $f$ is PEB if there exists $\kappa_f > 0$ such that $\left\Vert x - L^{-1}\Pi_X(x - L^{-1}\nabla f(x))\right\Vert \ge \kappa_f\Vert x - \bar x\Vert$. 
-            We denote it by $f \in \PEB(f, L_f, \kappa_f)$. 
-            \item $f$ is QFG if there exists $\kappa_f > 0$ such that $f(x) - f(\bar x) \ge \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. 
-            We denote it by $f \in \QFG(f, L_f, \kappa_f)$. 
-        \end{enumerate}
+\section{Precursors materials for our proofs of linear convergence}
+    \begin{definition}[similar triangle form of accelerated proximal gradient]\label{def:st-apg}
+
     \end{definition}
-    These definitions are the keys which Necoara used to prove the linear convergence of projected gradient, and Nesterov's accelerated gradient method.
 
-\section{Precurors materials for our proofs of linear convergence}
-    We propose an alternative approach that extends the results, and make comparison with existing works from Necoara et al.
+\section{deriving the convergence rate}
+    \subsection{preparations}
+        \begin{lemma}[convergence preparations part I]
 
-\section{Linear convergence of first order methods}
+        \end{lemma}
+        \begin{lemma}[convergence preparations part II]
+
+        \end{lemma}
+        \begin{lemma}[convergence preparations part III]
+
+        \end{lemma}
 

### 2025-08-20 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
OcO, new stuff && git push

@@
 
-% ==============================================================================
 \section{Introduction}
@@
     \end{align*}
-    We also define the gradient mapping operator
+    We also define the gradient mapping operator $\mathcal G_B(x) = B^{-1}(x - T_B(x))$.
 
 \section{Precursors materials for our proofs of linear convergence}
-    \begin{definition}[similar triangle form of accelerated proximal gradient]\label{def:st-apg}
+    The following two definitions defines the accelerated proximal gradient algorithm. 
+    % DEFINITION =======================================================================================================
+    \begin{definition}[similar triangle form of accelerated proximal gradient]\;\label{def:st-apg}\\
+        The definition is about $((\alpha_k)_{k \ge 0}, (q_k)_{k \ge 0}, (B_k)_{k \ge 0}, (y_k)_{k \ge 0}, (x_k)_{k \ge -1}, (v_k)_{k \ge -1})$. 
+        These sequences satisfy:
+        \begin{enumerate}[nosep]
+            \item $x_{-1}, y_{- 1}\in \RR^n$ are arbitrary initial condition of the algorithm;
+            \item $(q_k)_{k \ge 1}$ be a sequence such that $q_k \in [0, 1)$ for all $k \ge 1$;
+            \item $(\alpha_k)_{k \ge 1}$ be a sequence such that $\alpha_0 \in (0, 1]$, and for all $k \ge 1$ it has $\alpha_k \in (q_k, 1)$;
+            \item $(B_k)_{k \ge 0}$ has $B_k \ge 0$. 
+        \end{enumerate}
+        Then an algorithm satisfies the similar triangle form of Nesterov's accelerated gradient if it generates iterates $(y_k, x_k, v_k)_{k \ge 1}$ such that for all $k\ge 0$: 
+        \begin{align*}
+            y_k &= \left(\frac{\alpha_k - q_k}{1 - q_k}\right)v_{k - 1} 
+            + \left(\frac{1 - \alpha_k}{1 - q_k}\right) x_{k - 1},
+            \\
+            x_k &= T_{L_k}(y_k), D_f(x_k, y_k) \le \frac{B_k}{2}\Vert x_k - y_k\Vert^2, 
+            \\
+            v_k &= x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
+        \end{align*}
+    \end{definition}
+    % DEFINITION =======================================================================================================
+    \begin{definition}[relaxed momentum sequence]\label{def:rlx-momentum-seq}
+        The following definition is about sequences $((\alpha_k)_{k \ge 0}, (q_k)_{k \ge 0}, (\rho_k)_{k \ge 0})$. 
+        Let 
+        \begin{enumerate}[nosep]
+            \item $(q_k)_{k \ge 0}$ is a sequence such that $q_k \in [0, 1)$ for all $k \ge 0$;
+            \item $(\alpha_k)_{k \ge 0}$ be such that $\alpha_0 \in (0, 1]$, and for all $k \ge 1$ it has $\alpha_k \in (q_k, 1)$;
+            \item $(\rho_k)_{k \ge 0}$ is a strictly positive sequence for all $k \ge 1$. 
+        \end{enumerate}
+        The sequences $q_k, \alpha_k$ are considered relaxed momentum sequence if for all $k \ge 1$ it satisfies the relation that: 
+        \begin{align*}
+            \rho_{k - 1} &= \frac{\alpha_k(\alpha_k - q_k)}{(1 - \alpha_{k})\alpha_{k - 1}^2}. 
+        \end{align*}
+    \end{definition}
+    % DEFINITION =======================================================================================================
+    \begin{definition}[proximal gradient gap]\label{def:pg-gap}
+        Let $F = f + g$ where $f$ is $L$ Lipschitz smooth and $g$ is convex. 
+        Then the proximal gradient mapping $T_B(x) = \hprox_{B^{-1}g}(x -  B^{-1}\nabla f(x))$ is a singleton, which as domain on $\RR^n$. 
+        Let $\mu, B$ be parameters such that $B > \mu \ge 0$. 
+        We define the proximal gradient gap $\mathcal E(z, y, \mu)$ is a $\RR^n \times \RR^n \rightarrow \RR^n$ mapping: 
+        \begin{align*}
+            \mathcal E(z, y, \mu, B) &:= 
+            F(z) - F(T_B(y)) 
+            - \left\langle B(y - T_B(y)), z - y\right\rangle
+            - \frac{\mu}{2}\Vert z - y\Vert^2
+            - \frac{B}{2}\Vert y - T_B(y)\Vert^2. 
+        \end{align*}
+    \end{definition}
+    \begin{remark}
+        This expression is the same as the proximal gradient inequality. 
+    \end{remark}
 
-    \end{definition}
+\section{Deriving the convergence rate}
+    To derive the convergence rate of algorithm satisfying Definition \ref{def:st-apg}, \ref{def:rlx-momentum-seq}, we leverage Definition \ref{def:pg-gap}. 
+    % ASSUMPTION =======================================================================================================
+    \begin{assumption}[for convergence]\label{ass:for-cnvg}
+        The following assumption is about $(F, f, g, \mathcal E, \mu, L)$, it is the configuration needed to derive the convergence rate of algorithms that satisfy Definition \ref{def:st-apg}. 
+        There exists $B > \mu \ge 0$ such that the following are true. 
+        \begin{enumerate}[nosep]
+            \item Let $F = f + g$ where $f$ is $L$ Lipschitz smooth and, $g$ is closed convex and proper.
+            \item Assume that $X^+ = \argmin_{x} \{f(x) + g(x)\}$ has $X^+ \neq \emptyset$.
+            \item $\forall z \in \RR^n$ it has $\mathcal E(\Pi_{X^+}(y), y, \mu, B) \ge 0$. 
+            \item For all $z, y \in \RR^n$, it has $\mathcal E(z, y, \mu, B) + \frac{\mu}{2}\Vert z - y\Vert^2 \ge 0$.   
+        \end{enumerate}
+        Note that, if the function is convex, all conditions are satisfies for $\mu = 0$. 
+    \end{assumption}
+    % LEMMA ========================================================================================================
+    \begin{lemma}[equivalent representations of the iterates part I]\label{lemma:st-iterates-alt-form-part1}
+        Suppose that the sequences of $\alpha_k, q_k, y_k, v_k, x_k, B_k$ satisfy the similar triangle form, then for all $k \ge 0$ the iterates $v_k$ admits the following equivalent representations: 
+        \begin{align*}
+            v_k &= x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1})
+            \\
+            &= v_{k - 1} + \alpha_k^{-1}q_k(y_k - v_{k - 1}) - \alpha_{k}^{-1}B_k^{-1}\mathcal G_{B_k}(y_k). 
+        \end{align*}
+    \end{lemma}
+    \begin{proof}
+        Consider all $k \ge 1$. 
+        The relations is direct, immediately from the update rule in Definition \ref{def:st-apg} of $y_k$ we have
+        \begin{enumerate}[nosep]
+            \item[(a)] $(\alpha_k - 1)x_{k - 1} = (\alpha_k - q_k)v_{k - 1} - (1 - q_k)y_k$. 
+            \item[(b)] $x_k = y_k - B_k^{-1}\mathcal G_{B_k}(y_k)$. 
+        \end{enumerate}
+        \begin{align*}
+            v_k &= x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1})
+            \\
+            &= (1 - \alpha_k^{-1})x_{k - 1} + \alpha_k^{-1}x_k
+            \\
+            &= \alpha_k^{-1}(\alpha_k - 1)x_{k - 1} + \alpha_k^{-1}x_k
+            \\
+            &\underset{\text{(a)}}{=} \alpha_k^{-1}(\alpha_k - q_k)v_{k - 1} - \alpha_{k}^{-1}(1 - q_k)y_k 
+            + \alpha_k^{-1}x_k
+            \\
+            &\underset{\text{(b)}}{=} (1 - \alpha_k^{-1}q_k) v_{k - 1} - (\alpha_k^{-1} - \alpha_k^{-1}q_k)y_k
+            + \alpha_k^{-1}(y_k - B_k^{-1}\mathcal G_{B_k}(y_k)). 
+            \\
+            &= 
+            (1 - \alpha_k^{-1}q_k) v_{k - 1} + \alpha_k^{-1}q_ky_k
+            - \alpha_k^{-1}B_k^{-1}\mathcal G_{B_k}(y_k)
+            \\
+            &= v_{k - 1} + \alpha_k^{-1}q_k(y_k - v_{k - 1}) - \alpha_{k}^{-1}B_k^{-1}\mathcal G_{B_k}(y_k). 
+        \end{align*}
+    \end{proof}
+    \begin{lemma}[equivalent representations of the iterates part II]\;\label{lemma:st-iterates-alt-form-part2}\\
+        Suppose the sequences of $\alpha_k, q_k, y_k, v_k, x_k, B_k$ satisfy the similar triangle form, then for all $k \ge 0$ the iterates $v_k$ admits the following equivalent representations: 
+        \begin{align*}
+            y_k &= 
+            x_{k -1} + (1 - q_k)^{-1}(\alpha_{k - 1}^{-1} - 1)(\alpha_k - q_k)(x_{k - 1} - x_{k - 2})
+            \\
+            &= \left(\frac{\alpha_k - q_k}{1 - q_k}\right)v_{k - 1} + \left(\frac{1 - \alpha_k}{1 - q_k}\right) x_{k - 1}. 
+        \end{align*}
+    \end{lemma}
+    \begin{proof}
+        For all $k\ge 1$, from the update rules in Definition \ref{def:st-apg}: 
+        \begin{align*}
+            (1 - q_k)^{-1}y_k &= 
+            (\alpha_k - q_k) v_{k - 1} 
+            + (1 - \alpha_k)x_{k - 1}
+            \\
+            &= 
+            (\alpha_k - q_k)\left(
+                x_{k - 2} + \alpha_{k - 1}^{-1}(x_{k - 1} - x_{k - 2})
+            \right) 
+            + (1 - \alpha_k)x_{k - 1}
+            \\
+            &= 
+            (\alpha_k - q_k)x_{k - 2} 
+            + \alpha_{k - 1}^{-1}(x_{k - 1} - x_{k - 2}) + (1 - \alpha_k)x_{k - 1}
+            \\
+            &= (\alpha_k - q_k)(1 - \alpha_{k - 1}^{-1})x_{k - 2}
+            + \left(
+                \frac{\alpha_k - q_k}{\alpha_{k - 1}} + 1 - \alpha_k
+            \right)x_{k - 1}. 
+        \end{align*}
+        Multiply $(1 - q_k)$ on both sides yield: 
+        \begin{align*}
+            y_k &= 
+            \frac{(\alpha_k - q_k)(1 - \alpha_{k - 1}^{-1})}{1 - q_k}x_{k - 2} 
+            + \left(
+                \frac{\alpha_k - q_k}{\alpha_{k - 1}(1 - q_k)} + \frac{1 - \alpha_k}{1 - q_k}
+            \right)x_{k - 1}
+            \\
+            &= 
+            \frac{(\alpha_k - q_k)(1 - \alpha_{k - 1}^{-1})}{1 - q_k}x_{k - 2} 
+            + \left(
+                \frac{
+                    (\alpha_{k - 1}^{-1} -1)(\alpha_k - q_k)
+                    + \alpha_k - q_k + 1 - \alpha_k
+                }{1 - q_k}
+            \right)x_{k - 1}
+            \\
+            &= \frac{(\alpha_k - q_k)(1 - \alpha_{k - 1}^{-1})}{1 - q_k}x_{k - 2} 
+            + \left(
+                \frac{
+                    (\alpha_{k - 1}^{-1} -1)(\alpha_k - q_k)g 
+                }{1 - q_k} + 1
+            \right)x_{k - 1}
+            \\
+            &= x_{k -1} + (1 - q_k)^{-1}\left(\alpha_{k - 1}^{-1} - 1\right)(\alpha_k - q_k)(x_{k - 1} - x_{k - 2}). 
+        \end{align*}
+    \end{proof}
 
-\section{deriving the convergence rate}
-    \subsection{preparations}
-        \begin{lemma}[convergence preparations part I]
+    \subsection{preparations for the convergence rate proof}
+        The following lemma summarize important results that gives a swift exposition for the proofs show up at the end for the convergence rate. 
+        \begin{lemma}[convergence preparations part I]\label{lemma:cnvg-prep-part1}
+            Let $(F, f, g,  \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:for-cnvg}. 
+            Suppose that 
+            \begin{enumerate}[nosep]
+                \item The sequence $(y_k, v_k, x_k)_{k \ge 0}$ satisfies Definition \ref{def:st-apg} where $T_B$ is defined on $F = f + g$. 
+                \item The sequences $(\alpha_k)_{k\ge 0}, (\rho_{k})_{k \ge 0}, (q_k)_{k \ge 0}$ satisfies the definition of relaxed momentum sequence.
+                \item We set the parameters $q_k$ has $q_k = \mu/B_k$, with $B_k > \mu$, for all $k \ge 0$. 
+            \end{enumerate}
+            Then, for all $\bar x \in \RR^n$, $k \ge 0$: 
+            \begin{align*}
+                & \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+                -\frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                \\
+                &=
+                \frac{\alpha_k \mu}{2}
+                \Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{q_k\mu}{2}\Vert y_k - v_{k - 1} \Vert
+                + \frac{q_k}{2\mu}\Vert \mathcal G_{B_k}(y_k)\Vert^2
+                \\ &\quad 
+                - \langle
+                    q_k(y_k - v_{k - 1}) + \alpha_k(v_{k - 1} - \bar x), \mathcal G_{B_k}(y_k)
+                \rangle
+                    + \alpha_k \mu
+                    \left\langle 
+                        v_{k - 1} - \bar x, 
+                        y_k - v_{k - 1}
+                    \right\rangle. 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+
+        \end{proof}
+
+        \begin{lemma}[convergence preparations part II]\label{lemma:cnvg-prep-part2}
 
         \end{lemma}
-        \begin{lemma}[convergence preparations part II]
-
-        \end{lemma}
-        \begin{lemma}[convergence preparations part III]
+        \begin{lemma}[convergence preparations part III]\label{lemma:cnvg-prep-part3}
 

### 2025-08-21 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, new stuff

@@
     % ASSUMPTION =======================================================================================================
-    \begin{assumption}[for convergence]\label{ass:for-cnvg}
+    \begin{assumption}[generic assumptions for convergence]\label{ass:for-cnvg}
         The following assumption is about $(F, f, g, \mathcal E, \mu, L)$, it is the configuration needed to derive the convergence rate of algorithms that satisfy Definition \ref{def:st-apg}. 
@@
             \item Let $F = f + g$ where $f$ is $L$ Lipschitz smooth and, $g$ is closed convex and proper.
-            \item Assume that $X^+ = \argmin_{x} \{f(x) + g(x)\}$ has $X^+ \neq \emptyset$.
-            \item $\forall z \in \RR^n$ it has $\mathcal E(\Pi_{X^+}(y), y, \mu, B) \ge 0$. 
+            \item $\forall y \in \RR^n\; \exists \bar y$ such that $\mathcal E(\bar y, y, \mu, B) \ge 0$. 
             \item For all $z, y \in \RR^n$, it has $\mathcal E(z, y, \mu, B) + \frac{\mu}{2}\Vert z - y\Vert^2 \ge 0$.   
         \end{enumerate}
-        Note that, if the function is convex, all conditions are satisfies for $\mu = 0$. 
+        Note that, if the function is convex, all conditions are satisfies for $\mu = 0$, and for all $\bar y \in \RR^n$. 
     \end{assumption}
@@
 
-    \subsection{preparations for the convergence rate proof}
-        The following lemma summarize important results that gives a swift exposition for the proofs show up at the end for the convergence rate. 
+    \subsection{Preparations for the convergence rate proof}
+        The following lemma summarize important results that give a swift exposition for the proofs show up at the end for the convergence rate. 
+        % LEMMA ========================================================================================================
         \begin{lemma}[convergence preparations part I]\label{lemma:cnvg-prep-part1}
@@
                 \item The sequences $(\alpha_k)_{k\ge 0}, (\rho_{k})_{k \ge 0}, (q_k)_{k \ge 0}$ satisfies the definition of relaxed momentum sequence.
-                \item We set the parameters $q_k$ has $q_k = \mu/B_k$, with $B_k > \mu$, for all $k \ge 0$. 
+                \item We choose the parameters $q_k$ has $q_k = \mu/B_k$, with $B_k > \mu$, for all $k \ge 0$. 
             \end{enumerate}
@@
         \begin{proof}
+            Consider any $\bar x \in \RR^n$. 
+            \begin{align*}
+                & \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+                \\
+                &\underset{(1)}{=} \frac{B_k\alpha_k^2}{2}\left\Vert
+                    \bar x - 
+                    \left(
+                        v_{k - 1} 
+                        + \alpha_k^{-1}q_k(y_k - v_{k - 1})
+                        - \alpha_k^{-1} B_k^{-1} \mathcal G_{B_k}(y_k)
+                    \right)
+                \right\Vert^2
+                \\
+                &= \frac{B_k\alpha_k^2}{2}\left\Vert
+                    (\bar x - v_{k - 1})
+                    - \alpha_k^{-1}\left(
+                        q_k(y_k - v_{k - 1})
+                        -  B_k^{-1} \mathcal G_{B_k}(y_k)
+                    \right)
+                \right\Vert^2
+                \\
+                &= \frac{B_k\alpha_k^2}{2}
+                \Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{B_k}{2}\left\Vert 
+                    q_k(y_k - v_{k - 1})
+                    -  B_k^{-1} \mathcal G_{B_k}(y_k)
+                \right\Vert^2
+                    \\ &\quad 
+                    - \alpha_k B_k
+                    \left\langle 
+                        \bar x - v_{k - 1}, 
+                        q_k(y_k - v_{k - 1}) - B_k^{-1}\mathcal G_{B_k}(y_k)
+                    \right\rangle
+                \\
+                &= 
+                \frac{B_k\alpha_k^2}{2}
+                \Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{B_kq_k^2}{2}\Vert y_k - v_{k - 1} \Vert
+                + \frac{1}{2B_k}\Vert \mathcal G_{B_k}(y_k)\Vert^2
+                - q_k\langle 
+                    y_k - v_{k - 1}, \mathcal G_{B_k}(y_k)
+                \rangle
+                    \\ &\quad 
+                    + B_k\alpha_k
+                    \left\langle 
+                        v_{k - 1} - \bar x, 
+                        q_k(y_k - v_{k - 1}) - B_k^{-1}\mathcal G_{B_k}(y_k)
+                    \right\rangle
+                \\
+                &= 
+                \frac{B_k\alpha_k^2}{2}
+                \Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{B_kq_k^2}{2}\Vert y_k - v_{k - 1} \Vert
+                + \frac{1}{2B_k}\Vert \mathcal G_{B_k}(y_k)\Vert^2
+                - q_k\langle 
+                    y_k - v_{k - 1}, \mathcal G_{B_k}(y_k)
+                \rangle
+                    \\ &\quad 
+                    + 
+                    B_k\alpha_k\left\langle 
+                        v_{k - 1} - \bar x, 
+                        q_k(y_k - v_{k - 1}) 
+                    \right\rangle
+                    - \alpha_k \left\langle 
+                        v_{k - 1} - \bar x,
+                        \mathcal G_{B_k}(y_k)
+                    \right\rangle
+                \\
+                &= 
+                \frac{\alpha_k^2B_k}{2}
+                \Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{q_k^2B_k}{2}\Vert y_k - v_{k - 1} \Vert
+                + \frac{1}{2B_k}\Vert \mathcal G_{B_k}(y_k)\Vert^2
+                    \\ &\quad 
+                    - \langle
+                        q_k(y_k - v_{k - 1}) + \alpha_k(v_{k - 1} - \bar x), \mathcal G_{B_k}(y_k)
+                    \rangle
+                    \\ &\quad 
+                    + \alpha_k q_k B_k
+                    \left\langle 
+                        v_{k - 1} - \bar x, 
+                        y_k - v_{k - 1}
+                    \right\rangle. 
+            \end{align*}
+            At (1) we used Lemma \ref{lemma:st-iterates-alt-form-part1}. 
+            Subtracting $-\frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x - v_{k - 1}\Vert^2$ from both sides, the coefficient for $\Vert \bar x - v_{k - 1}\Vert^2$ comes out to be:
+            \begin{align*}
+                & \frac{\alpha_k^2B_k}{2}
+                - \frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2} 
+                = \frac{B_k}{2}(
+                    \alpha_k^2 + (1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2
+                )
+                \underset{(1)}{=} \frac{B_k\alpha_kq_k}{2}. 
+            \end{align*}
+            At (1), we used the relation $(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2 = \alpha_k(\alpha_k - q_k)$ as in Definition \ref{def:rlx-momentum-seq}, for all $k \ge 1$. 
+            Therefore, we have the equality: 
+            \begin{align*}
+                &
+                \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+                -\frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                \\
+                &= 
+                \frac{\alpha_k q_k B_k}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{q_k^2B_k}{2}\Vert y_k - v_{k - 1} \Vert
+                + \frac{1}{2B_k}\Vert \mathcal G_{B_k}(y_k)\Vert^2
+                    \\ &\quad 
+                    - \langle
+                        q_k(y_k - v_{k - 1}) + \alpha_k(v_{k - 1} - \bar x), \mathcal G_{B_k}(y_k)
+                    \rangle
+                    \\ &\quad 
+                    + \alpha_k q_k B_k
+                    \left\langle 
+                        v_{k - 1} - \bar x, 
+                        y_k - v_{k - 1}
+                    \right\rangle. 
+                \\
+                &\underset{(1)}{=} 
+                \frac{\alpha_k \mu}{2}
+                \Vert \bar x - v_{k - 1}\Vert^2
+                + \frac{q_k\mu}{2}\Vert y_k - v_{k - 1} \Vert
+                + \frac{q_k}{2\mu}\Vert \mathcal G_{B_k}(y_k)\Vert^2
+                    \\ &\quad 
+                - \langle
+                        q_k(y_k - v_{k - 1}) + \alpha_k(v_{k - 1} - \bar x), \mathcal G_{B_k}(y_k)
+                    \rangle
+                    + \alpha_k \mu
+                    \left\langle 
+                        v_{k - 1} - \bar x, 
+                        y_k - v_{k - 1}
+                    \right\rangle. 
+            \end{align*}
+            At (1), we used the relation that $B_k = \mu/q_k$, for all $k \ge 0$. 
+        \end{proof}
+        % LEMMA ========================================================================================================
+        \begin{lemma}[convergence preparations part II]\label{lemma:cnvg-prep-part2}
+            The iterates $(y_k, x_k, v_k)_{k \ge 0}$ satisfies Definition \ref{def:st-apg} then, for all $k \ge 0, \bar x \in \RR^n$ the following identities: 
+            \begin{align*}
+                \alpha_k(v_{k - 1} - \bar x) 
+                + q_k(y_k - v_{k - 1})
+                + x_{k - 1} - y_k
+                &= 
+                \alpha_k(x_{k - 1} - \bar x). 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            We first establish two intermediate results. 
+            From Definition \ref{def:st-apg}, it has for all $k \ge 0$: 
+            \begin{align*}
+                y_k &= 
+                \left(\frac{\alpha_k - q_k}{1 - q_k}\right)v_{k - 1} 
+                + \left(\frac{1 - \alpha_k}{1 - q_k}\right) x_{k - 1}
+                \\
+                &= 
+                \left(
+                    1 - \frac{1 - \alpha_k}{1 - q_k}
+                \right)v_{k - 1} 
+                + \left(\frac{1 - \alpha_k}{1 - q_k}\right) x_{k - 1}
+                \\
+                \iff 
+                y_k - v_{k - 1}
+                &= \left(
+                    \frac{1 - \alpha_k}{1 - q_k}
+                \right)(x_{k - 1} - v_{k - 1}). 
+            \end{align*}
+            Similarly: 
+            \begin{align*}
+                y_k &= 
+                \left(\frac{\alpha_k - q_k}{1 - q_k}\right)v_{k - 1} 
+                + \left(\frac{1 - \alpha_k}{1 - q_k}\right) x_{k - 1}
+                \\
+                &= 
+                \left(\frac{\alpha_k - q_k}{1 - q_k}\right)v_{k - 1} 
+                + \left(1 - \frac{\alpha_k - q_k}{1 - q_k}\right) x_{k - 1}
+                \\
+                \iff 
+                y_k - x_{k - 1} &= 
+                \left(
+                    \frac{\alpha_k - q_k}{1 - q_k}
+                \right)(v_{k - 1} - x_{k - 1}). 
+            \end{align*}
+            Now, we use the above two results and it derives 
+            \begin{align*}
+                & \alpha_k(v_{k - 1} - \bar x) 
+                + q_k(y_k - v_{k - 1})
+                + x_{k - 1} - y_k
+                \\
+                &=
+                \alpha_k(v_{k - 1} - \bar x)
+                + q_k\left(
+                    \frac{1 - \alpha_k}{1 - q_k}
+                \right)(x_{k - 1} - v_{k - 1})
+                - \left(
+                    \frac{\alpha_k - q_k}{1 - q_k}    
+                \right)(v_{k - 1} - x_{k - 1}). 
+                \\
+                &= 
+                \alpha_k(v_{k - 1} - \bar x)
+                + (1 - q_k)^{-1}\left(
+                    q_k - q_k\alpha_k +(\alpha_k - q_k)
+                \right)
+                (x_{k - 1} - v_{k - 1})
+                \\
+                &= 
+                \alpha_k(v_{k - 1} - \bar x)
+                + \alpha_k(x_{k - 1} - v_{k - 1})
+                \\
+                &= \alpha_k(x_{k - 1} - \bar x). 
+            \end{align*}
 
         \end{proof}
+        % LEMMA ========================================================================================================
+        \begin{lemma}[convergence preparations part III]\;\label{lemma:cnvg-prep-part3}\\
+            Suppose that all of the following are satisfied
+            \begin{enumerate}[nosep]
+                \item $(F, f, g, \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:for-cnvg}. 
+                \item The sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}, (q_k)_{k \ge 0}$ satisfies Definition \ref{def:rlx-momentum-seq}. 
+                \item We choose $(q_k)_{k \ge 0}$ is given by $q_k = \mu/B_k$ for all $k \ge 0$. 
+                \item The sequence $(y_k, v_k, x_k)_{k \ge 0}$ satisfies Definition \ref{def:st-apg}. 
+            \end{enumerate}
+            Then, $\forall k \ge 1$, there exists $\bar x_k \in \RR^n$, such that: 
+            \begin{align*}
+                & F(x_k) - F(\bar x_k)
+                + \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
+                \\
+                &\le 
+                (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x_k))
+                + \frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x_k - v_{k - 1}\Vert^2. 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            Recall Definition \ref{def:pg-gap}, consider: 
+            \begin{align*}
+                &\mathcal E(x_{k - 1}, y_k, \mu, B_k) 
+                \\
+                &=
+                F(x_{k - 1}) - F(x_k)
+                - \langle 
+                    B_k(y_k - z_k), 
+                    x_{k - 1} - y_k
+                \rangle
+                - \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2
+                - \frac{B_k}{2}\Vert y_k - x_k\Vert^2
+                \\
+                &= 
+                F(x_{k - 1}) - F(x_k)
+                - \langle 
+                    \mathcal G_{B_k}(y_k), 
+                    x_{k - 1} - y_k
+                \rangle
+                - \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2
+                - \frac{q_k}{2\mu}\Vert \mathcal G_{B_k}(y_k)\Vert^2. 
+            \end{align*}
+            On the second equality above, we used $B^{-1}_k(y_k - x_k)= \mathcal G_{B_k}(y_k)$, and $B_k = \mu/q_k$.
+            For all $k \ge 0$, we define $\Xi_k$ and simplify using the above result: 
+            \begin{align*}
+                \Xi_k &\hspace{-0.3em}\defeq 
+                \mathcal E(x_{k - 1}, y_k, \mu, B_k)
+                + F(x_k) - F(\bar x_k)
+                - (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x_k))
+                \\
+                &= 
+                \mathcal E(x_{k - 1}, y_k, \mu, B_k)
+                + F(x_k) - \alpha_kF(\bar x_k) - (1 - \alpha_k)F(x_{k - 1})
+                \\
+                &=
+                \alpha_kF(x_{k - 1}) - \alpha_k F(\bar x_k)
+                - \langle \mathcal G_{B_k}(y_k), x_{k - 1} - y_k\rangle
+                - \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2 
+                - \frac{q_k}{2\mu}\Vert \mathcal G_{B_k}(y_k)\Vert^2. 
+            \end{align*}
+            Now consider the new term $\Xi_k'$ which we defined and simplify below: 
+            {\allowdisplaybreaks
+            \begin{align*}
+                \Xi_k'
+                &\hspace{-0.3em}:=
+                \Xi_k + \frac{B_k\alpha_k^2}{2}\Vert \bar x_k - v_k\Vert^2 
+                - \frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x_k - v_{k - 1}\Vert^2
+                \\
+                &\underset{(1)}{=} 
+                \alpha_kF(x_{k - 1}) - \alpha_k F(\bar x_k)
+                - \langle \mathcal G_{B_k}(y_k), x_{k - 1} - y_k\rangle
+                - \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2 
+                - \frac{q_k}{2\mu}\Vert \mathcal G_{B_k}(y_k)\Vert^2
+                    \\&\quad 
+                    + \frac{\alpha_k \mu}{2}
+                    \Vert \bar x_k - v_{k - 1}\Vert^2
+                    + \frac{q_k\mu}{2}\Vert y_k - v_{k - 1} \Vert^2
+                    + \frac{q_k}{2\mu}\Vert \mathcal G_{B_k}(y_k)\Vert^2
+                    \\ &\quad 
+                    - \langle
+                        q_k(y_k - v_{k - 1}) + \alpha_k(v_{k - 1} - \bar x_k), \mathcal G_{B_k}(y_k)
+                    \rangle
+                    + \alpha_k \mu
+                    \left\langle 
+                        v_{k - 1} - \bar x_k, 
+                        y_k - v_{k - 1}
+                    \right\rangle
+                \\
+                &= 
+                \alpha_kF(x_{k - 1}) - \alpha_k F(\bar x_k)
+                - \langle \mathcal G_{B_k}(y_k), x_{k - 1} - y_k\rangle
+                - \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2 
+                    \\&\quad 
+                    + \frac{\alpha_k \mu}{2}
+                    \Vert \bar x_k - v_{k - 1}\Vert^2
+                    + \frac{q_k\mu}{2}\Vert y_k - v_{k - 1} \Vert^2
+                    \\ &\quad 
+                    - \langle
+                        q_k(y_k - v_{k - 1}) + \alpha_k(v_{k - 1} - \bar x_k), \mathcal G_{B_k}(y_k)
+                    \rangle
+                    + \alpha_k \mu
+                    \left\langle 
+                        v_{k - 1} - \bar x_k, 
+                        y_k - v_{k - 1}
+                    \right\rangle
+                \\
+                &= 
+                \alpha_kF(x_{k - 1}) - \alpha_k F(\bar x_k)
+                - \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2 
+                + \frac{\alpha_k \mu}{2}
+                \Vert \bar x_k - v_{k - 1}\Vert^2
+                + \frac{q_k\mu}{2}\Vert y_k - v_{k - 1} \Vert^2
+                    \\ &\quad 
+                    - \langle
+                        x_{k - 1} - y_k + q_k(y_k - v_{k - 1}) + \alpha_k(v_{k - 1} - \bar x_k), 
+                        \mathcal G_{B_k}(y_k)
+                    \rangle
+                    \\&\quad 
+                    + \alpha_k \mu
+                    \left\langle 
+                        v_{k - 1} - \bar x_k, 
+                        q_k(y_k - v_{k - 1}) 
+                    \right\rangle
+                \\
+                &\underset{(2)}{=} 
+                \alpha_kF(x_{k - 1}) - \alpha_k F(\bar x_k)
+                - \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2 
+                    \\&\quad 
+                    + \frac{\alpha_k \mu}{2}
+                    \Vert \bar x_k - v_{k - 1}\Vert^2
+                    + \frac{q_k\mu}{2}\Vert y_k - v_{k - 1} \Vert^2
+                    \\ &\quad 
+                    - \alpha_k\langle
+                        x_{k - 1} - \bar x_k, 
+                        \mathcal G_{B_k}(y_k)
+                    \rangle
+                    + \alpha_k \mu
+                    \left\langle 
+                        v_{k - 1} - \bar x_k, 
+                        q_k(y_k - v_{k - 1}) 
+                    \right\rangle
+                \\
+                &=
+                \alpha_kF(x_{k - 1}) - \alpha_k F(\bar x_k)
+                - \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2 
+                    \\&\quad 
+                    + \frac{\alpha_k \mu}{2}
+                    \Vert \bar x_k - v_{k - 1}\Vert^2
+                    + \frac{\alpha_k\mu}{2}\Vert y_k - v_{k - 1}\Vert^2
+                    + \alpha_k \mu
+                    \left\langle 
+                        v_{k - 1} - \bar x_k, 
+                        q_k(y_k - v_{k - 1}) 
+                    \right\rangle
+                    \\ &\quad 
+                    - \alpha_k\langle
+                        x_{k - 1} - \bar x_k, 
+                        \mathcal G_{B_k}(y_k)
+                    \rangle
+                    + \frac{q_k\mu - \mu\alpha_k}{2}\Vert y_k - v_{k - 1} \Vert^2
+                \\
+                &= 
+                \alpha_kF(x_{k - 1}) - \alpha_k F(\bar x_k)
+                - \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2 
+                    \\&\quad 
+                    \frac{\alpha_k\mu}{2}\Vert y_k - \bar x_k\Vert^2
+                    - \alpha_k\langle
+                        x_{k - 1} - \bar x_k, 
+                        \mathcal G_{B_k}(y_k)
+                    \rangle
+                    + \frac{q_k\mu - \mu\alpha_k}{2}\Vert y_k - v_{k - 1} \Vert^2
+                \\
+                &\underset{(3)}{\le} 
+                \alpha_kF(x_{k - 1}) - \alpha_k F(\bar x_k)
+                - \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2 
+                    \\&\quad 
+                    \frac{\alpha_k\mu}{2}\Vert y_k - \bar x_k\Vert^2
+                    - \alpha_k\langle
+                        x_{k - 1} - \bar x_k, 
+                        \mathcal G_{B_k}(y_k)
+                    \rangle. 
+                \\
+                &= \alpha_k\left(
+                    F(x_{k  - 1}) - F(\bar x_k) 
+                    - \langle x_{k - 1} - \bar x_k, \mathcal G_{B_k}(y_k)\rangle
+                    +  \frac{\mu}{2}\Vert y_k - \bar x_k\Vert^2
+                \right)
+                - \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2. 
+            \end{align*}
+            }
+            At (1), we used Lemma \ref{lemma:cnvg-prep-part3}, and substituted $\Xi_k$. 
+            At (2), we used Lemma \ref{lemma:cnvg-prep-part2} to simplify the inner product. 
+            At (3), we used the $\alpha_k > q_k$ as in Definition \ref{def:rlx-momentum-seq}, hence it makes the coefficient $q_k \mu - \mu\alpha_k \le 0$, which gives us the inequality. 
+            Now, subtracting $\mathcal E(x_{k - 1}, y_k, \mu, B_k)$ from both sides of the inequality will yield: 
+            {\allowdisplaybreaks\small
+            \begin{align*}
+                & \Xi_k' - \mathcal E(x_{k - 1}, y_k, \mu, B_k)
+                \\
+                &\le 
+                \alpha_k\left(
+                    F(x_{k  - 1}) - F(\bar x_k) 
+                    - \langle x_{k - 1} - \bar x_k, \mathcal G_{B_k}(y_k)\rangle
+                    +  \frac{\mu}{2}\Vert y_k - \bar x_k\Vert^2
+                    - \mathcal E(x_{k - 1}, y_k, \mu, B_k)
+                \right)
+                    \\ &\quad 
+                    - \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2
+                    - (1 - \alpha_k)\mathcal E(x_{k - 1}, y_k, \mu, B_k)
+                \\
+                &\underset{(1)}{=} 
+                \alpha_k\left(
+                    F(x_k) - F(\bar x_k) 
+                    - \langle \mathcal G_{B_k}(y_k), x_{k - 1} - \bar x_k - (x_{k - 1} - y_k)\rangle
+                \right)
+                    \\&\quad 
+                    + \alpha_k\left(
+                        \frac{\mu}{2}\Vert y_k - \bar x_k\Vert^2
+                        + \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2
+                        + \frac{B_k}{2} \Vert y_k - x_k\Vert^2
+                    \right)
+                    \\ &\quad 
+                    - \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2
+                    - (1 - \alpha_k)\mathcal E(x_{k - 1}, y_k, \mu, B_k)
+                \\
+                &= \alpha_k\left(
+                    F(x_k) - F(\bar x_k) 
+                    - \langle \mathcal G_{B_k}(y_k), y_k - \bar x_k\rangle
+                    + \frac{\mu}{2}\Vert y_k - \bar x_k\Vert^2
+                    + \frac{B_k}{2} \Vert y_k - x_k\Vert^2
+                    + \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2
+                \right)
+                    \\ &\quad 
+                    - \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2
+                    - (1 - \alpha_k)\mathcal E(x_{k - 1}, y_k, \mu, B_k)
+                \\
+                &=
+                \alpha_k\left(
+                    - \mathcal E(\bar x_k, y_k, \mu, B_k)
+                    + \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2
+                \right)
+                    \\ &\quad 
+                    - \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2
+                    - (1 - \alpha_k)\mathcal E(x_{k - 1}, y_k, \mu, B_k)
+                \\
+                &\underset{(2)}{\le} 
+                \frac{\alpha_k \mu}{2}\Vert x_{k - 1} - y_k\Vert^2
+                - \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2
+                - (1 - \alpha_k)\mathcal E(x_{k - 1}, y_k, \mu, B_k)
+                \\
+                &= -(1 - \alpha_k)\left(
+                    \mathcal E(x_{k - 1}, y_k, \mu, B_k)
+                    + \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2
+                \right) 
+                \\
+                & \underset{(3)}{\le} 0. 
+            \end{align*}
+            }
+            At (1), we substituted $\mathcal E(x_{k - 1}, y_k, \mu, B_k)$. 
+            At (2), we used the $\mathcal E(\bar x_k, y_k, \mu, B_k)\le 0$ by chosing $\bar x_k = \bar y$ in Assumption \ref{ass:for-cnvg} (iii) to make the inequality. 
+            At (3), we used Assumption \ref{ass:for-cnvg} (iv). 
+            At this point, we had proved what we wanted becaues using the definitions of $\Xi_k, \Xi_k'$ it has:
+            \begin{align*}
+                & \Xi_k' - \mathcal E(x_{k - 1}, y_k, \mu, B_k) 
+                \\
+                &= 
+                \Xi_k 
+                + \frac{B_k\alpha_k^2}{2}\Vert \bar x_k - v_k\Vert^2 
+                - \frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x_k - v_{k - 1}\Vert^2
+                - \mathcal E(x_{k - 1}, y_k, \mu, B_k) 
+                \\
+                &= \mathcal E(x_{k - 1}, y_k, \mu, B_k)
+                + F(x_k) - F(\bar x_k)
+                - (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x_k))
+                    \\ &\quad 
+                    + \frac{B_k\alpha_k^2}{2}\Vert \bar x_k - v_k\Vert^2 
+                    - \frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x_k - v_{k - 1}\Vert^2
+                    - \mathcal E(x_{k - 1}, y_k, \mu, B_k)
+                \\
+                &=  
+                F(x_k) - F(\bar x_k)
+                - (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x_k))
+                    \\ &\quad 
+                    + \frac{B_k\alpha_k^2}{2}\Vert \bar x_k - v_k\Vert^2 
+                    - \frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x_k - v_{k - 1}\Vert^2
+                \\
+                &\le 0. 
+            \end{align*}
+        \end{proof}
+    \subsection{Proving the convergence rate}
+        To finally find the convergence rate, we will strengthen Assumption \ref{ass:for-cnvg}. 
+        \begin{assumption}[Assumptions for linear convergence rate]
 
-        \begin{lemma}[convergence preparations part II]\label{lemma:cnvg-prep-part2}
+        \end{assumption}
+        \begin{assumption}[Assumption for sublinear convergence rate]
 
-        \end{lemma}
-        \begin{lemma}[convergence preparations part III]\label{lemma:cnvg-prep-part3}
-
-        \end{lemma}
+        \end{assumption}
 

### 2025-08-24 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, new stuff added

@@
 \begin{abstract} 
-    \noindent
-    This is still a note for a draft so no abstract. 
+    This paper gives definitive answers to open problems in Necoara et al. \cite{necoara_linear_2019}. 
+    Linear converence of Nesterov's accelerated gradient method is possible in a boarder context of functions. 
 \end{abstract}
@@
     Let $C\subseteq \RR^n$, $\Pi_C(\cdot)$ denotes the projection onto the set $C$, i.e: the closest point in $C$ to another point in $\RR^n$. 
+    We denote $\delta_C$ to be the indicator function for the set $C$. 
     For a function of $F = f + g$, and a $B\ge 0$ where $f$ is $\mathcal C^1$ differentiable, and $g$ is l.s.c, we consider the proximal gradient operator: 
@@
             \item $(\alpha_k)_{k \ge 1}$ be a sequence such that $\alpha_0 \in (0, 1]$, and for all $k \ge 1$ it has $\alpha_k \in (q_k, 1)$;
-            \item $(B_k)_{k \ge 0}$ has $B_k \ge 0$. 
+            \item $(B_k)_{k \ge 0}$ has $B_k \ge 0$, it's a nonnegative sequence. 
         \end{enumerate}
@@
             \\
-            x_k &= T_{L_k}(y_k), D_f(x_k, y_k) \le \frac{B_k}{2}\Vert x_k - y_k\Vert^2, 
+            x_k &= T_{B_k}(y_k), D_f(x_k, y_k) \le \frac{B_k}{2}\Vert x_k - y_k\Vert^2, 
             \\
@@
         Let $F = f + g$ where $f$ is $L$ Lipschitz smooth and $g$ is convex. 
-        Then the proximal gradient mapping $T_B(x) = \hprox_{B^{-1}g}(x -  B^{-1}\nabla f(x))$ is a singleton, which as domain on $\RR^n$. 
+        Then the proximal gradient mapping $T_B(x) = \hprox_{B^{-1}g}(x -  B^{-1}\nabla f(x))$ is a singleton, and $\dom T_B = \RR^n$. 
         Let $\mu, B$ be parameters such that $B > \mu \ge 0$. 
-        We define the proximal gradient gap $\mathcal E(z, y, \mu)$ is a $\RR^n \times \RR^n \rightarrow \RR^n$ mapping: 
+        We define the proximal gradient gap $\mathcal E(z, y, \mu, B)$ is the mapping: 
         \begin{align*}
@@
     \begin{remark}
-        This expression is the same as the proximal gradient inequality. 
+        This expression is the same as the proximal gradient inequality up to a negative sign, after moving everything to one side. 
     \end{remark}
@@
     To derive the convergence rate of algorithm satisfying Definition \ref{def:st-apg}, \ref{def:rlx-momentum-seq}, we leverage Definition \ref{def:pg-gap}. 
+    The first two subsections prepare for the results and the the convergence results are derived by the end. 
+    \par
+    The following assumption is about the Proximal Gradient gap, it's required to obtain our first result. 
     % ASSUMPTION =======================================================================================================
@@
         The following assumption is about $(F, f, g, \mathcal E, \mu, L)$, it is the configuration needed to derive the convergence rate of algorithms that satisfy Definition \ref{def:st-apg}. 
-        There exists $B > \mu \ge 0$ such that the following are true. 
+        We assume that there exists $\mu \ge 0$ such that the followings are true: 
         \begin{enumerate}[nosep]
             \item Let $F = f + g$ where $f$ is $L$ Lipschitz smooth and, $g$ is closed convex and proper.
-            \item $\forall y \in \RR^n\; \exists \bar y$ such that $\mathcal E(\bar y, y, \mu, B) \ge 0$. 
-            \item For all $z, y \in \RR^n$, it has $\mathcal E(z, y, \mu, B) + \frac{\mu}{2}\Vert z - y\Vert^2 \ge 0$.   
+            \item $\forall y \in \RR^n, \exists B \ge 0\; \exists \bar y$ such that $\mathcal E(\bar y, y, \mu, B) \ge 0$. 
+            \item For all $z, y \in \RR^n$, there exists $B > \mu$ such that $\mathcal E(z, y, \mu, B) + \frac{\mu}{2}\Vert z - y\Vert^2 \ge 0$.   
         \end{enumerate}
-        Note that, if the function is convex, all conditions are satisfies for $\mu = 0$, and for all $\bar y \in \RR^n$. 
     \end{assumption}
+    \begin{remark}
+        Note that:
+        \begin{enumerate}
+            \item If the function is convex, all conditions are satisfies for $\mu = 0$, and for all $\bar y \in \RR^n$. 
+            \item If $\mu \ge 0$ satisfies item (ii), (iii), then it's also satisfies for all $\tilde \mu$ such that $0 \le \tilde \mu \le \mu$.
+For the best convergence rate, the largest such $\mu$ is of our interest.
+        \end{enumerate}
+
+    \end{remark}
     % LEMMA ========================================================================================================
@@
         \begin{align*}
-            v_k &= x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1})
-            \\
+            v_k
             &= v_{k - 1} + \alpha_k^{-1}q_k(y_k - v_{k - 1}) - \alpha_{k}^{-1}B_k^{-1}\mathcal G_{B_k}(y_k). 
@@
         Consider all $k \ge 1$. 
-        The relations is direct, immediately from the update rule in Definition \ref{def:st-apg} of $y_k$ we have
+        The relations are direct, immediately from the update rule in Definition \ref{def:st-apg} of $y_k$ we have
         \begin{enumerate}[nosep]
@@
         \end{enumerate}
+        Using the the above and the update rule for $v_k$ in Definition \ref{def:st-apg}. 
         \begin{align*}
@@
             y_k &= 
-            x_{k -1} + (1 - q_k)^{-1}(\alpha_{k - 1}^{-1} - 1)(\alpha_k - q_k)(x_{k - 1} - x_{k - 2})
-            \\
-            &= \left(\frac{\alpha_k - q_k}{1 - q_k}\right)v_{k - 1} + \left(\frac{1 - \alpha_k}{1 - q_k}\right) x_{k - 1}. 
+            x_{k -1} + (1 - q_k)^{-1}(\alpha_{k - 1}^{-1} - 1)(\alpha_k - q_k)(x_{k - 1} - x_{k - 2}). 
         \end{align*}
@@
             \begin{enumerate}[nosep]
-                \item The sequence $(y_k, v_k, x_k)_{k \ge 0}$ satisfies Definition \ref{def:st-apg} where $T_B$ is defined on $F = f + g$. 
-                \item The sequences $(\alpha_k)_{k\ge 0}, (\rho_{k})_{k \ge 0}, (q_k)_{k \ge 0}$ satisfies the definition of relaxed momentum sequence.
+                \item The iterates $(y_k, v_k, x_k)_{k \ge 0}$ satisfies Definition \ref{def:st-apg} where $T_B$ defined using $F = f + g$. 
+                \item The sequences $(\alpha_k)_{k\ge 0}, (\rho_{k})_{k \ge 0}, (q_k)_{k \ge 0}$ satisfy Definition \ref{def:rlx-momentum-seq}. 
                 \item We choose the parameters $q_k$ has $q_k = \mu/B_k$, with $B_k > \mu$, for all $k \ge 0$. 
@@
         To finally find the convergence rate, we will strengthen Assumption \ref{ass:for-cnvg}. 
-        \begin{assumption}[Assumptions for linear convergence rate]
-
+        Our convergence rate is expressed for sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k\ge0}$ as long as they satisfies Definition \ref{def:rlx-momentum-seq}. 
+        This means that any sequence with $\alpha_k \in (q_k, 1)$ would work. 
+        \par
+        The following assumptions describes the behaviors of an algorithm satisfying Definition \ref{def:st-apg}, its parameters, and the properties of the objective function. 
+        \begin{assumption}[Assumptions for linear convergence rate]\;\label{ass:lin-cnvg}\\
+            Let $(F, f, g, \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:for-cnvg}. 
+            In addition, we strength the prior assumptions:
+            \begin{enumerate}[nosep]
+                \item Define the set of minimizers $X^+ = \argmin_{z\in \RR^n}\{ f(z) + g(z)\}$, it has $X^+ \neq \emptyset$. 
+                \item $\exists \mu > 0$ such that $\forall\; y \in \RR^n$, it has $\mathcal E \left(\Pi_{X^+}y, y, \mu, B\right) \ge 0$. 
+            \end{enumerate}
+            Now, suppose an algorithm which optimizes a $F = f + g$ satisfying all pervious assumptions, and it generates iterates $(y_k, x_k, v_k)_{k\ge 0}$ that satisfies Definition \ref{def:pg-gap}.
+            In addition, we assume that the parameter sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}, (q_k)_{k \ge 0}, (B_k)_{k \ge 0}$ satisfy the following: 
+            \begin{enumerate}[nosep]\setcounter{enumi}{3}
+                \item The sequences $\alpha_k, \rho_k, q_k$ are given by Definition \ref{def:rlx-momentum-seq}. 
+                \item The sequence $q_k = \mu/B_k$, with $B_k > \mu$. 
+                \item For all $k \ge 0$, $\Pi_{X^+}y_k$ is a unique. 
+            \end{enumerate}
         \end{assumption}
@@
         \end{assumption}
+
+        % THEOREM ======================================================================================================
+        \begin{theorem}[linear convergence with generic sequence]\;\label{thm:cnvg-generic-seq}\\
+            Let $(F, f, g, \mathcal E, \mu, L)$, and sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}, (q_k)_{k \ge 0}, (B_k)_{k \ge 0}$ 
+            satisfy Assumption \ref{ass:lin-cnvg}. 
+            Denote $\beta_k = \prod_{i = 1}^k(1 - \alpha_i) \max \left(\frac{B_i\rho_{i - 1}}{B_{i - 1}}, 1\right)$, $\beta_0 = 1$. 
+            Then, there exists a unique $\bar x \in \RR^n$ such that for all $k \ge 1$, $\bar x = \Pi_{X^+}y_k$, and it satisfies
+            \begin{align*}
+                F(x_k) - F(\bar x) + \frac{B_k}{\alpha_k^2}\Vert \bar x - v_k\Vert^2 
+                \le 
+                \beta_k\left(
+                    F(x_0) - F(\bar x) + \frac{\alpha_0B_0}{2}\Vert \bar x - v_0\Vert^2
+                \right). 
+            \end{align*}
+            If in addition, we assume $x_{-1} = v_{-1}, \alpha_0 = 1$, then the above inequality simplifies: 
+            \begin{align*}
+                & F(x_k) - F(\bar x) + \frac{B_k}{\alpha_k^2}\Vert \bar x - v_k\Vert^2 \le 
+                \frac{\beta_kB_0}{2}\Vert \bar x - x_{-1}\Vert^2.
+            \end{align*}
+        \end{theorem}
+        \begin{proof}
+            Set $\bar x_k = \bar x$ in Lemma \ref{lemma:cnvg-prep-part3} then for all $k\ge 1$ it has 
+            \begin{align*}
+                & F(x_k) - F(\bar x) + \frac{B_k\alpha_k^2}{2}\Vert \bar x- v_k\Vert^2 
+                \\
+                &\le \left(
+                    1 - \alpha_k
+                \right)\left(
+                    F(x_{k- 1}) - F(\bar x) + \frac{B_k\alpha_{k -1}^2 \rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                \right)
+                \\
+                &\le \left(
+                    1 - \alpha_k
+                \right)\left(
+                    F(x_{k- 1}) - F(\bar x) + 
+                    \frac{B_k\rho_{k - 1}}{B_{k - 1}}\frac{B_{k - 1}\alpha_{k -1}^2}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                \right)
+                \\
+                &= \left(
+                    1 - \alpha_k
+                \right)\max\left(
+                    \frac{B_k\rho_{k - 1}}{B_{k - 1}}, 1
+                \right)
+                \left(
+                    F(x_{k- 1}) - F(\bar x) + 
+                    \frac{B_{k - 1}\alpha_{k -1}^2 }{2}\Vert \bar x - v_{k - 1}\Vert^2
+                \right). 
+            \end{align*}
+            From the above, an recurrence relation is formed for $k \ge 1$, unrolloing the recurrence relation it has 
+            \begin{align*}
+                & F(x_k) - F(\bar x) + \frac{B_k\alpha_k^2}{2}\Vert \bar x- v_k\Vert^2 
+                \\
+                &\le 
+                \left(
+                    1 - \alpha_k
+                \right)\max\left(
+                    \frac{B_k\rho_{k - 1}}{B_{k - 1}}, 1
+                \right)
+                \left(
+                    F(x_{k- 1}) - F(\bar x) + 
+                    \frac{B_{k - 1}\alpha_{k -1}^2 }{2}\Vert \bar x - v_{k - 1}\Vert^2
+                \right). 
+            \end{align*}
+            When $x_{-1} = v_{-1}$, from Definition \ref{def:st-apg}, when $k = 0$ it has $y_0 = v_{-1} = x_{-1}$, so $x_0 = T_{B_0}(y_0)$. 
+            Because $\alpha_0 = 1$, it also has $v_0 = x_0$. 
+            Choose $z = \bar x, y = x_{-1}$ we have from Assumption \ref{ass:for-cnvg} (iii) that
+            \begin{align*}
+                0 &\le \mathcal E(\bar x, x_{-1}, \mu, B_0) - \frac{\mu}{2}\Vert \bar x - x_{-1}\Vert^2
+                \\
+                &=
+                F(\bar x) - F(x_{-1}) 
+                - B_0\left\langle x_{-1} - T_{B_0}(x_{-1}), \bar x - x_{-1} \right\rangle
+                - \frac{B_0}{2}\left\Vert x_{-1} - T_{B_0}x_{-1}\right\Vert^2
+                \\
+                &= 
+                F(\bar x) - F(x_{-1}) 
+                - \frac{B_0}{2}\Vert \bar x - T_{B_0}x_{-1}\Vert^2 
+                + \frac{B_0}{2}\Vert \bar x - x_{-1}\Vert^2. 
+                \\
+                &= F(\bar x) - F(x_{-1}) 
+                - \frac{B_0}{2}\Vert \bar x - v_0\Vert^2 
+                + \frac{B_0}{2}\Vert \bar x - x_{-1}\Vert^2. 
+            \end{align*}
+            Substitute the above into the RHS of the inequality of previous results to complete the proof. 
+        \end{proof}
+        \par
+        The above theorem shows that the convergence rate is exclusively depeneded on the momentum sequence. 
+        The theorem below will definitively close the case to show that there exists choices for the sequence such that a linear convergence exists, meaning that $\beta_k$ will decrease at a linear rate.
+        \begin{lemma}[beta sequence bounds]\;\label{lemma:beta-seq}\\
+            Let sequence $(\alpha_k)_{k \ge 0}, (\rho_{k})_{k \ge 0}, (q_k)_{k \ge 0}$ satisfies Definition \ref{def:rlx-momentum-seq}.
+            Let sequences $(B_k)_{k \ge 1}$ be given by Definition \ref{def:st-apg}. 
+            Define $\beta_k := \prod_{i = 1}^k(1 - \alpha_i) \max \left(\frac{B_i\rho_{i - 1}}{B_{i - 1}}, 1\right)$.
+            Assume in addition that for all $k \ge 0$, $B_k = B_{k - 1} = B$. 
+            Then, linear convergence of $\beta_k$ is possible under the following scenarios: 
+            \begin{enumerate}
+                \item If for all $k \ge 1$, $\sqrt{q} \le \alpha_k \le \alpha_{k - 1}$ so it's non-increasing, then $\beta_k = \Pi_{i = 1}^k(1 - q/\alpha_{i - 1})$.
+                Since $\alpha_k \in (0, 1)$ and it's monotone, it has upper bound $\beta_k \le (1 - q)^k$. 
+                \item If for all $k \ge 1$, $\alpha_k = \alpha_{k - 1}$, so there exists $\alpha = \alpha_k$, making the sequence a constant, then $\beta_k = \max(1 - q/\alpha, 1 - \alpha)^k$.
+And, it's lowest when $\alpha_k = \sqrt{q}$.
+            \end{enumerate}
+        \end{lemma}
+        \begin{proof}
+            Since $B_k$ is a constant, and by Definition \ref{def:st-apg} it has $B_k = \frac{\mu}{q_k}$ it would make $q_k$ to be a constant for all $k \ge 0$, which we denote $q := q_k$. 
+            \par
+            \textbf{Proof of (i)}. 
+            For all $k \ge 1$ it has 
+            \begin{align*}
+                & (1 - \alpha_k)\max\left(
+                    \frac{B_k\rho_{k - 1}}{B_{k - 1}}, 1
+                \right)
+                \\
+                &= \max(\rho_{k - 1}(1 - \alpha_k), 1 - \alpha_k) 
+                \\
+                &\underset{\text{(1)}}{=} \max\left(
+                    \frac{\alpha_k(\alpha_k - q)}{\alpha_{k - 1}^2}, 1 - \alpha_k
+                \right)
+                \\
+                &= \max\left(
+                    \frac{\alpha_k^2}{\alpha_{k - 1}^2} - \frac{q}{\alpha_{k - 1}}, 1 - \alpha_k
+                \right)
+                \\
+                &\underset{\text{(2)}}{\le} 
+                \max\left(
+                    1 - \frac{q}{\alpha_{k - 1}}, 1 - \alpha_k
+                \right). 
+            \end{align*}
+            Then, observe that
+            \begin{align*}
+                1 - \frac{q}{\alpha_{k - 1}} &> 1 - \frac{q}{\sqrt{q}}
+                \\
+                &= 1 - \sqrt{q} \ge 1 - \alpha_k. 
+            \end{align*}
+            Combining the previous two results it has 
+            \begin{align*}
+                (1 - \alpha_k)\max\left(
+                    \frac{B_k\rho_{k - 1}}{B_{k - 1}}, 1
+                \right) \le 
+                \left(1 - \frac{q}{\alpha_{k - 1}}\right).
+            \end{align*}
+            \par 
+            \textbf{Proof of (ii)}.
+
+        \end{proof}
+
+\section{Linear convergence beyond the strongly convex case}
+    In this sections, we exam Assumption \ref{ass:lin-cnvg} and, propose examples for it. 
+    In Necoara et al.'s setting, they have the following Assumptoins for their objective function. 
+    \begin{assumption}[The settings for Necoara's et al]\;\label{ass:necoara}\\
+        The assumption is about $(f, X, X^+, f^+)$ where 
+        \begin{enumerate}[nosep]
+            \item $X \subseteq \RR^n$ is a closed convex set. 
+            \item $f: X\rightarrow \RR$ has $L$ Lipschitz continous gradient, and it's convex. 
+            \item $X^+ = \argmin_{x \in X} f(x)\neq \emptyset$, and we denote $f^+$ to be the minimum value. 
+        \end{enumerate}
+    \end{assumption}
+    The following definition on Quasi Strongly Convex function (Q-SCNVX) is taken from \cite[Definition 1]{necoara_linear_2019}. 
+    By... the above definition satisfies Assumption \ref{ass:for-cnvg} 
+    \begin{definition}[Q-SCNVX]\label{def:Q-SCNVX}
+        Let $(f, X, X^+, f^+)$ be given by Assumption \ref{ass:necoara}. 
+        We define $f$ to be Quasi Strong Convex on $X$ if there exists $\kappa_f  > 0$ such that $\forall x \in \RR^n$ , with $\bar x = \Pi_{X^+}x$ it has:
+        \begin{align*}
+            f^+ - f(x) - \langle \nabla f(x), \bar x - x\rangle - \frac{\kappa_f}{2}\Vert \bar x - x\Vert^2 
+            &\ge 0. 
+        \end{align*}
+    \end{definition}
+    \begin{proposition}[Q-SCNVX is an example of our assumptions]\label{prop:qscnvx-ass-ok}
+        Let $(f, X, X^+, f^+)$ satisfies Assumption \ref{ass:necoara}.
+        Let $\mathcal E$ be given by Definition \ref{def:pg-gap} with $g = \delta_X$. 
+        Then for all $x \in \RR^n$, let $\bar x = \Pi_{X^+}x, x^+ = T_B(x)$, there exists $B \ge 0$, such that 
+        \begin{align*}
+            0 &\le 
+            \mathcal E(\bar x, x, B, \kappa_f)
+            = 
+            f(\bar x) - f(x^+) 
+            - \frac{B}{2}\Vert x - x^+\Vert^2 
+            - B\langle \bar x - x, x - x^+\rangle
+            - \frac{\kappa_f}{2}\Vert \bar x - x\Vert^2. 
+        \end{align*}
+        Therefore, it satisfies Assumtpion \ref{ass:for-cnvg}. 
+    \end{proposition}
+    \begin{proof}
+        Let $h = z \mapsto \delta_X(z) + \langle \nabla f(x), z\rangle + \frac{B}{2}\Vert z - x\Vert^2$.
+        So it has $T_B(x) = \argmin_{z\in \RR^n} h(z)$. 
+        Furthermore, $h(z)$ is a $B$ strongly convex function by convexity of $X$ and, the fact that other parts are just the sum of a linear and quadratic function. 
+        Denote $x^+ = T_B(x)$, since $x^+$ is a minimizer therefore it has $\forall x \in X\; h(z) - h(x^+) \ge \frac{B}{2}\Vert z - x^+\Vert^2$. 
+        That was the quadratic growth condition of $h$. 
+        Next, denote $\bar x  = \Pi_{X^+}x$, let $z = \bar x$ then the condition becomes: 
+        \begin{align*}
+            & \frac{B}{2}\Vert \bar x - x^+\Vert^2 
+            \\
+            &\le 
+            \langle \nabla f(x), \bar x\rangle + \frac{B}{2}\Vert \bar x - x\Vert^2 - 
+            \langle \nabla f(x), x^+\rangle + \frac{B}{2}\Vert x^+ - x\Vert^2
+            \\
+            &=
+            \langle \nabla f(x), \bar x - x\rangle - \langle \nabla f(x), x^+ - x\rangle
+            + \frac{B}{2}\Vert \bar x - x\Vert^2 
+            - \frac{B}{2}\Vert x^+ - x\Vert^2
+            \\
+            &= - D_f(\bar x, x) - f(x) + f(\bar x) - f(x^+) + f(x) + D_f(x^+, x)
+            + \frac{B}{2}\Vert \bar x - x\Vert^2 
+            - \frac{B}{2}\Vert x^+ - x\Vert^2
+            \\
+            &= 
+            - D_f(\bar x, x) + f(\bar x) - f(x^+) 
+            + \frac{B}{2}\Vert \bar x - x\Vert^2 
+            + D_f(x^+, x)
+            - \frac{B}{2}\Vert x^+ - x\Vert^2
+            \\
+            &\underset{\text{(1)}}{\le} 
+            - \frac{\kappa_f}{2}\Vert \bar x - x\Vert^2
+            + f(\bar x) - f(x^+)
+            + \frac{B}{2}\Vert \bar x - x\Vert^2 
+            + 0
+        \end{align*}
+        At (1), we used the fact that $f$ is assumed satisfy \ref{def:Q-SCNVX} because $\bar x = \Pi_{X^+}x$, in addition the inequality $D_f(x^+, x) \le \frac{B}{2}\Vert x^+ - x\Vert^2$ is true because of Lipschitz gradient Assumption in \ref{ass:necoara} hence for all $B\ge L$, it's true for all $x$.
+        Rearranging it has 
+        \begin{align*}
+            0 &\le
+            f(\bar x) - f(x^+) 
+            + \frac{B}{2}\Vert \bar x - x\Vert^2 
+            - \frac{B}{2}\Vert \bar x - x^+\Vert^2
+            - \frac{\kappa_f}{2}\Vert \bar x - x\Vert^2
+            \\
+            &= 
+            f(\bar x) - f(x^+) 
+            - \frac{B}{2}\Vert x - x^+\Vert^2 
+            - B\langle \bar x - x, x - x^+\rangle
+            - \frac{\kappa_f}{2}\Vert \bar x - x\Vert^2
+            \\
+            &= \mathcal E(\bar x, x, B, \kappa_f). 
+        \end{align*}
+        The above results shows that Assumption \ref{ass:for-cnvg} has been satisfied, with $\bar y = \Pi_{X^+}y$. 
+    \end{proof}
+
+    \subsection{SCNVX affine composite over simple cone}
 

### 2025-08-27 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
;~;, we cry

@@
     \begin{definition}[relaxed momentum sequence]\label{def:rlx-momentum-seq}
-        The following definition is about sequences $((\alpha_k)_{k \ge 0}, (q_k)_{k \ge 0}, (\rho_k)_{k \ge 0})$. 
-        Let 
+        The following definition is about sequences $((\alpha_k)_{k \ge 0}, (q_k)_{k \ge 0}$. 
+        They satisfy:
         \begin{enumerate}[nosep]
             \item $(q_k)_{k \ge 0}$ is a sequence such that $q_k \in [0, 1)$ for all $k \ge 0$;
-            \item $(\alpha_k)_{k \ge 0}$ be such that $\alpha_0 \in (0, 1]$, and for all $k \ge 1$ it has $\alpha_k \in (q_k, 1)$;
-            \item $(\rho_k)_{k \ge 0}$ is a strictly positive sequence for all $k \ge 1$. 
+            \item $(\alpha_k)_{k \ge 0}$ has $\alpha_k \in (0, 1]$, and for all $k \ge 0$. 
         \end{enumerate}
-        The sequences $q_k, \alpha_k$ are considered relaxed momentum sequence if for all $k \ge 1$ it satisfies the relation that: 
-        \begin{align*}
-            \rho_{k - 1} &= \frac{\alpha_k(\alpha_k - q_k)}{(1 - \alpha_{k})\alpha_{k - 1}^2}. 
-        \end{align*}
     \end{definition}
@@
     To derive the convergence rate of algorithm satisfying Definition \ref{def:st-apg}, \ref{def:rlx-momentum-seq}, we leverage Definition \ref{def:pg-gap}. 
-    The first two subsections prepare for the results and the the convergence results are derived by the end. 
+    The first two subsections prepare for the results and the convergence results are derived by the end. 
     \par
@@
         \begin{enumerate}
-            \item If the function is convex, all conditions are satisfies for $\mu = 0$, and for all $\bar y \in \RR^n$. 
-            \item If $\mu \ge 0$ satisfies item (ii), (iii), then it's also satisfies for all $\tilde \mu$ such that $0 \le \tilde \mu \le \mu$.
+            \item If the function $f$ is convex and smooth, $g$ is convex then, all conditions are satisfied for $\mu = 0$, and for all $\bar y \in \RR^n$. 
+            \item If $\mu \ge 0$ satisfies item (ii), (iii), then it also satisfies for all $\tilde \mu$ such that $0 \le \tilde \mu \le \mu$.
 For the best convergence rate, the largest such $\mu$ is of our interest.
@@
         \end{enumerate}
-        Using the the above and the update rule for $v_k$ in Definition \ref{def:st-apg}. 
+        Using the above and the update rule for $v_k$ in Definition \ref{def:st-apg}. 
         \begin{align*}
@@
         \begin{align*}
-            (1 - q_k)^{-1}y_k &= 
+            (1 - q_k)y_k &= 
             (\alpha_k - q_k) v_{k - 1} 
@@
             &= 
-            (\alpha_k - q_k)x_{k - 2} 
-            + \alpha_{k - 1}^{-1}(x_{k - 1} - x_{k - 2}) + (1 - \alpha_k)x_{k - 1}
+            (\alpha_k - q_k)((1 - \alpha_{k - 1}^{-1})x_{k -2} + \alpha_{k - 1}^{-1}x_{k - 1}) 
+            + (1 - \alpha_k)x_{k - 1}
             \\
@@
         \end{align*}
-        Multiply $(1 - q_k)$ on both sides yield: 
+        Divide by $(1 - q_k)$ on both sides yield: 
         \begin{align*}
@@
                 \frac{
-                    (\alpha_{k - 1}^{-1} -1)(\alpha_k - q_k)g 
+                    (\alpha_{k - 1}^{-1} -1)(\alpha_k - q_k)
                 }{1 - q_k} + 1
@@
                 \item The iterates $(y_k, v_k, x_k)_{k \ge 0}$ satisfies Definition \ref{def:st-apg} where $T_B$ defined using $F = f + g$. 
-                \item The sequences $(\alpha_k)_{k\ge 0}, (\rho_{k})_{k \ge 0}, (q_k)_{k \ge 0}$ satisfy Definition \ref{def:rlx-momentum-seq}. 
+                \item The sequences $(\alpha_k)_{k\ge 0}, (q_k)_{k \ge 0}$ satisfy Definition \ref{def:rlx-momentum-seq}. 
                 \item We choose the parameters $q_k$ has $q_k = \mu/B_k$, with $B_k > \mu$, for all $k \ge 0$. 
@@
                 & \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-                -\frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                - \frac{B_k\alpha_k(\alpha_k - q_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                 \\
@@
             At (1) we used Lemma \ref{lemma:st-iterates-alt-form-part1}. 
-            Subtracting $-\frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x - v_{k - 1}\Vert^2$ from both sides, the coefficient for $\Vert \bar x - v_{k - 1}\Vert^2$ comes out to be:
+            Subtracting $\frac{B_k\alpha_k(\alpha_k - q_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2$ from both sides, the coefficient of $\Vert \bar x - v_{k - 1}\Vert^2$ comes out to be: 
             \begin{align*}
                 & \frac{\alpha_k^2B_k}{2}
-                - \frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2} 
+                - \frac{B_k\alpha_k(\alpha_k - q_k)}{2}
                 = \frac{B_k}{2}(
-                    \alpha_k^2 + (1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2
+                    \alpha_k^2 - \alpha_k(\alpha_k - q_k)
                 )
@@
                 \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
-                -\frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                - \frac{B_k\alpha_k(\alpha_k - q_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                 \\
@@
         \begin{lemma}[convergence preparations part III]\;\label{lemma:cnvg-prep-part3}\\
-            Suppose that all of the following are satisfied
+            Suppose that all the following are satisfied
             \begin{enumerate}[nosep]
                 \item $(F, f, g, \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:for-cnvg}. 
-                \item The sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}, (q_k)_{k \ge 0}$ satisfies Definition \ref{def:rlx-momentum-seq}. 
+                \item The sequences $(\alpha_k)_{k \ge 0}, (q_k)_{k \ge 0}$ satisfies Definition \ref{def:rlx-momentum-seq}. 
                 \item We choose $(q_k)_{k \ge 0}$ is given by $q_k = \mu/B_k$ for all $k \ge 0$. 
@@
                 (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x_k))
-                + \frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x_k - v_{k - 1}\Vert^2. 
+                + \frac{B_k\alpha_k(\alpha_k - q_k)}{2}\Vert \bar x_k - v_{k - 1}\Vert^2. 
             \end{align*}
@@
                 \Xi_k + \frac{B_k\alpha_k^2}{2}\Vert \bar x_k - v_k\Vert^2 
-                - \frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x_k - v_{k - 1}\Vert^2
+                - \frac{B_k\alpha_k(\alpha_k - q_k)}{2}\Vert \bar x_k - v_{k - 1}\Vert^2
                 \\
@@
             }
-            At (1), we used Lemma \ref{lemma:cnvg-prep-part3}, and substituted $\Xi_k$. 
+            At (1), we used Lemma \ref{lemma:cnvg-prep-part1}, and substituted $\Xi_k$. 
             At (2), we used Lemma \ref{lemma:cnvg-prep-part2} to simplify the inner product. 
@@
             At (1), we substituted $\mathcal E(x_{k - 1}, y_k, \mu, B_k)$. 
-            At (2), we used the $\mathcal E(\bar x_k, y_k, \mu, B_k)\le 0$ by chosing $\bar x_k = \bar y$ in Assumption \ref{ass:for-cnvg} (iii) to make the inequality. 
+            At (2), we used the $\mathcal E(\bar x_k, y_k, \mu, B_k)\le 0$ by choosing $\bar x_k = \bar y$ in Assumption \ref{ass:for-cnvg} (iii) to make the inequality. 
             At (3), we used Assumption \ref{ass:for-cnvg} (iv). 
-            At this point, we had proved what we wanted becaues using the definitions of $\Xi_k, \Xi_k'$ it has:
+            At this point, we had proved what we wanted because using the definitions of $\Xi_k, \Xi_k'$ it has:
             \begin{align*}
@@
                 + \frac{B_k\alpha_k^2}{2}\Vert \bar x_k - v_k\Vert^2 
-                - \frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x_k - v_{k - 1}\Vert^2
+                - \frac{B_k\alpha_k(\alpha_k - q_k)}{2}\Vert \bar x_k - v_{k - 1}\Vert^2
                 - \mathcal E(x_{k - 1}, y_k, \mu, B_k) 
@@
                     + \frac{B_k\alpha_k^2}{2}\Vert \bar x_k - v_k\Vert^2 
-                    - \frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x_k - v_{k - 1}\Vert^2
+                    - \frac{B_k\alpha_k(\alpha_k - q_k)}{2}\Vert \bar x_k - v_{k - 1}\Vert^2
                     - \mathcal E(x_{k - 1}, y_k, \mu, B_k)
@@
                     + \frac{B_k\alpha_k^2}{2}\Vert \bar x_k - v_k\Vert^2 
-                    - \frac{B_k(1 - \alpha_k)\rho_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x_k - v_{k - 1}\Vert^2
+                    - \frac{B_k\alpha_k(\alpha_k - q_k)}{2}\Vert \bar x_k - v_{k - 1}\Vert^2
                 \\
@@
         To finally find the convergence rate, we will strengthen Assumption \ref{ass:for-cnvg}. 
-        Our convergence rate is expressed for sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k\ge0}$ as long as they satisfies Definition \ref{def:rlx-momentum-seq}. 
+        Our convergence rate is expressed for sequences $(\alpha_k)_{k \ge 0}, (q_k)_{k \ ge 0}$ if they satisfy Definition \ref{def:rlx-momentum-seq}. 
         This means that any sequence with $\alpha_k \in (q_k, 1)$ would work. 
         \par
-        The following assumptions describes the behaviors of an algorithm satisfying Definition \ref{def:st-apg}, its parameters, and the properties of the objective function. 
+        The following assumptions describe the behaviors of an algorithm satisfying Definition \ref{def:st-apg}, its parameters, and the properties of the objective function. 
         \begin{assumption}[Assumptions for linear convergence rate]\;\label{ass:lin-cnvg}\\
@@
             satisfy Assumption \ref{ass:lin-cnvg}. 
-            Denote $\beta_k = \prod_{i = 1}^k(1 - \alpha_i) \max \left(\frac{B_i\rho_{i - 1}}{B_{i - 1}}, 1\right)$, $\beta_0 = 1$. 
+            Denote 
+            $$
+                \beta_k = \prod_{i = 1}^k\max\left(
+                    1 - \alpha_i, 
+                    \frac{B_i\alpha_i(\alpha_i - q_i)}{\alpha_{i - 1}^2B_{i - 1}}
+                \right). 
+            $$
             Then, there exists a unique $\bar x \in \RR^n$ such that for all $k \ge 1$, $\bar x = \Pi_{X^+}y_k$, and it satisfies
@@
                     1 - \alpha_k
-                \right)\left(
-                    F(x_{k- 1}) - F(\bar x) + \frac{B_k\alpha_{k -1}^2 \rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                \right)
-                \\
-                &\le \left(
-                    1 - \alpha_k
-                \right)\left(
-                    F(x_{k- 1}) - F(\bar x) + 
-                    \frac{B_k\rho_{k - 1}}{B_{k - 1}}\frac{B_{k - 1}\alpha_{k -1}^2}{2}\Vert \bar x - v_{k - 1}\Vert^2
-                \right)
-                \\
-                &= \left(
-                    1 - \alpha_k
-                \right)\max\left(
-                    \frac{B_k\rho_{k - 1}}{B_{k - 1}}, 1
-                \right)
-                \left(
-                    F(x_{k- 1}) - F(\bar x) + 
-                    \frac{B_{k - 1}\alpha_{k -1}^2 }{2}\Vert \bar x - v_{k - 1}\Vert^2
-                \right). 
-            \end{align*}
-            From the above, an recurrence relation is formed for $k \ge 1$, unrolloing the recurrence relation it has 
-            \begin{align*}
-                & F(x_k) - F(\bar x) + \frac{B_k\alpha_k^2}{2}\Vert \bar x- v_k\Vert^2 
-                \\
-                &\le 
+                \right)(F(x_{k- 1}) - F(\bar x))
+                + \frac{(1 - \alpha_k)B_k\alpha_{k -1}^2 \rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                \\
+                &\underset{\text{(1)}}{=} 
                 \left(
                     1 - \alpha_k
-                \right)\max\left(
-                    \frac{B_k\rho_{k - 1}}{B_{k - 1}}, 1
+                \right)(F(x_{k- 1}) - F(\bar x))
+                + \frac{\alpha_k(\alpha_k - q_k)B_k\alpha_{k - 1}^2}{\alpha_{k - 1}^2}\Vert \bar x - v_{k - 1}\Vert^2
+                \\
+                &= \max\left(
+                    1 - \alpha_k, 
+                    \frac{B_i\alpha_k(\alpha_k - q_k)}{\alpha_{k - 1}^2B_{k - 1}}
                 \right)
                 \left(
-                    F(x_{k- 1}) - F(\bar x) + 
-                    \frac{B_{k - 1}\alpha_{k -1}^2 }{2}\Vert \bar x - v_{k - 1}\Vert^2
+                    F(x_{k - 1}) - F(\bar x)
+                    + \frac{B_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                \right). 
+            \end{align*}
+            From the above, a recurrence relation is formed for $k \ge 1$, unrolling the recurrence relation it has 
+            \begin{align*}
+                & F(x_k) - F(\bar x) + \frac{B_k\alpha_k^2}{2}\Vert \bar x- v_k\Vert^2 
+                \\&\le 
+                \prod_{i = 1}^k\max\left(
+                    1 - \alpha_i, 
+                    \frac{B_i\alpha_i(\alpha_i - q_i)}{\alpha_{i - 1}^2B_{i - 1}}
+                \right)
+                \left(
+                    F(x_0) - F(\bar x)
+                    + \frac{B_0\alpha_0^2}{2}\Vert \bar x - v_0\Vert^2
                 \right). 
@@
         \par
-        The above theorem shows that the convergence rate is exclusively depeneded on the momentum sequence. 
+        \textcolor{red}{
+            SOMETHING IS WRONG, LET US EXPLAIN.
+            The parameter $q_k = \mu/B_k$ cannot be eliminated from Definition \ref{def:st-apg}. 
+            If one were to implement any algorithm without the exact knowledge of $\mu$, then the convergence results we just derived are not applicable. 
+            Implementations of the algorithm, and the convergence results requires the presence of both parameters $q_k, \alpha_k$. 
+            Doomed. 
+            Because in the applications of our interests, the exact knowledge of $\mu$ is impossible to know. 
+        }
         The theorem below will definitively close the case to show that there exists choices for the sequence such that a linear convergence exists, meaning that $\beta_k$ will decrease at a linear rate.
@@
         \end{proof}
+    \subsection{Parameter free representations}
 
 \section{Linear convergence beyond the strongly convex case}
-    In this sections, we exam Assumption \ref{ass:lin-cnvg} and, propose examples for it. 
-    In Necoara et al.'s setting, they have the following Assumptoins for their objective function. 
+    We will check Assumption \ref{ass:lin-cnvg} and, propose examples for it.
+    In Necoara et al.'s setting, they have the following assumptions for their objective function. 
     \begin{assumption}[The settings for Necoara's et al]\;\label{ass:necoara}\\
@@
             \item $X \subseteq \RR^n$ is a closed convex set. 
-            \item $f: X\rightarrow \RR$ has $L$ Lipschitz continous gradient, and it's convex. 
+            \item $f: X\rightarrow \RR$ has $L$ Lipschitz continuous gradient, and it's convex. 
             \item $X^+ = \argmin_{x \in X} f(x)\neq \emptyset$, and we denote $f^+$ to be the minimum value. 
@@
     The following definition on Quasi Strongly Convex function (Q-SCNVX) is taken from \cite[Definition 1]{necoara_linear_2019}. 
-    By... the above definition satisfies Assumption \ref{ass:for-cnvg} 
     \begin{definition}[Q-SCNVX]\label{def:Q-SCNVX}
@@
         \end{align*}
-        Therefore, it satisfies Assumtpion \ref{ass:for-cnvg}. 
+        Therefore, it satisfies Assumption \ref{ass:for-cnvg}. 
     \end{proposition}
@@
         Furthermore, $h(z)$ is a $B$ strongly convex function by convexity of $X$ and, the fact that other parts are just the sum of a linear and quadratic function. 
-        Denote $x^+ = T_B(x)$, since $x^+$ is a minimizer therefore it has $\forall x \in X\; h(z) - h(x^+) \ge \frac{B}{2}\Vert z - x^+\Vert^2$. 
+        Denote $x^+ = T_B(x)$, since $x^+$ is a minimizer therefore it has $(\forall x \in X)\; h(z) - h(x^+) \ge \frac{B}{2}\Vert z - x^+\Vert^2$. 
         That was the quadratic growth condition of $h$. 
@@
         \end{align*}
-        The above results shows that Assumption \ref{ass:for-cnvg} has been satisfied, with $\bar y = \Pi_{X^+}y$. 
+        The above results showed that Assumption \ref{ass:for-cnvg} (ii) has been satisfied, with $\bar y = \Pi_{X^+}y$. 
+        To see (iii) in Assumption \ref{ass:for-cnvg}, observe that Assumption \ref{ass:necoara} has $f$ is convex. 
     \end{proof}
-
-    \subsection{SCNVX affine composite over simple cone}
+    \subsection{A nonconvex example}
+
+    \subsection{Examples of Q-SCNVX}
 

### 2025-08-29 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, changes

@@
 
-\title{{\fontfamily{ptm}\selectfont Linear Convergence of Accelerated Gradient without Restart}}
+\title{{\fontfamily{ptm}\selectfont Extending the Convergence Results of Nesterov's Acceleration using the Proximal Gradient Gap}}
 
@@
     This paper gives definitive answers to open problems in Necoara et al. \cite{necoara_linear_2019}. 
-    Linear converence of Nesterov's accelerated gradient method is possible in a boarder context of functions. 
+    Linear convergence of Nesterov's accelerated gradient method is possible in a boarder context of functions. 
 \end{abstract}
@@
     We also define the gradient mapping operator $\mathcal G_B(x) = B^{-1}(x - T_B(x))$. 
+    \par
+    \textbf{Major results}.
 
@@
     \end{definition}
+    \begin{remark}
+        If we choose $a_k = 1$ then the definition is equivalent to proximal gradient algorithm, with $v_k = x_k$ for all $k \ge 0$.
+
+    \end{remark}
     % DEFINITION =======================================================================================================
@@
     \end{remark}
-
-\section{Deriving the convergence rate}
+    For the sum of smooth and nonsmooth objective, a lot can be said about the proximal gradient gap of the function. 
+    \begin{lemma}[proximal gradient gap under convexity]\label{lemma:pg-under-cnvx}
+
+    \end{lemma}
+
+\section{Deriving the proximal gap inequality}
     To derive the convergence rate of algorithm satisfying Definition \ref{def:st-apg}, \ref{def:rlx-momentum-seq}, we leverage Definition \ref{def:pg-gap}. 
@@
     \par
-    The following assumption is about the Proximal Gradient gap, it's required to obtain our first result. 
+    The following assumption is about the Proximal Gradient gap. 
     % ASSUMPTION =======================================================================================================
-    \begin{assumption}[generic assumptions for convergence]\label{ass:for-cnvg}
+    \begin{assumption}[generic assumptions for proximal gradient gap inequality]\;\label{ass:pggap-dscnt}\\
         The following assumption is about $(F, f, g, \mathcal E, \mu, L)$, it is the configuration needed to derive the convergence rate of algorithms that satisfy Definition \ref{def:st-apg}. 
@@
         \begin{enumerate}[nosep]
-            \item Let $F = f + g$ where $f$ is $L$ Lipschitz smooth and, $g$ is closed convex and proper.
-            \item $\forall y \in \RR^n, \exists B \ge 0\; \exists \bar y$ such that $\mathcal E(\bar y, y, \mu, B) \ge 0$. 
-            \item For all $z, y \in \RR^n$, there exists $B > \mu$ such that $\mathcal E(z, y, \mu, B) + \frac{\mu}{2}\Vert z - y\Vert^2 \ge 0$.   
+            \item\label{ass:pggap-dscnt-itm1} Let $F = f + g$ where $f$ is $L$ Lipschitz smooth and, $g$ is closed convex and proper.
+            \item\label{ass:pggap-dscnt-itm2} $\forall y \in \RR^n, \exists B \ge 0\; \exists \bar y$ such that $\mathcal E(\bar y, y, \mu, B) \ge 0$. 
+            % \item For all $z, y \in \RR^n$, there exists $B > \mu$ such that $\mathcal E(z, y, \mu, B) + \frac{\mu}{2}\Vert z - y\Vert^2 \ge 0$.   
         \end{enumerate}
@@
         \end{enumerate}
-
     \end{remark}
+    Using the above assumption, in this section, we can build up to Lemma \ref{lemma:cnvg-prep-part3}. 
+    The lemma is crucially important and it gives us the an inequality on what happen between iterates $x_{k}, v_{k}$ and $v_{k - 1}, x_{k - 1}$ generated by algorithm satisfying Definition \ref{def:st-apg}.
     % LEMMA ========================================================================================================
@@
         \begin{lemma}[convergence preparations part I]\label{lemma:cnvg-prep-part1}
-            Let $(F, f, g,  \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:for-cnvg}. 
+            Let $(F, f, g,  \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:pggap-dscnt}. 
             Suppose that 
@@
             \end{align*}
-            Now, we use the above two results and it derives 
+            Now, we use the above two results and, it derives 
             \begin{align*}
@@
             \begin{enumerate}[nosep]
-                \item $(F, f, g, \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:for-cnvg}. 
+                \item $(F, f, g, \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:pggap-dscnt}. 
                 \item The sequences $(\alpha_k)_{k \ge 0}, (q_k)_{k \ge 0}$ satisfies Definition \ref{def:rlx-momentum-seq}. 
@@
                 (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x_k))
-                + \frac{B_k\alpha_k(\alpha_k - q_k)}{2}\Vert \bar x_k - v_{k - 1}\Vert^2. 
+                + \frac{B_k\alpha_k(\alpha_k - q_k)}{2}\Vert \bar x_k - v_{k - 1}\Vert^2
+                \\ &\quad 
+                    -(1 - \alpha_k)\left(
+                        \mathcal E(x_{k - 1}, y_k, \mu, B_k)
+                        + \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2
+                    \right). 
             \end{align*}
@@
                 &=
-                F(x_{k - 1}) - F(x_k)
+                F(x_{k - 1}) - F(T_{B_k}(y_k))
                 - \langle 
-                    B_k(y_k - z_k), 
+                    B_k(y_k - T_{B_k}(y_k)), 
                     x_{k - 1} - y_k
@@
             \end{align*}
-            On the second equality above, we used $B^{-1}_k(y_k - x_k)= \mathcal G_{B_k}(y_k)$, and $B_k = \mu/q_k$.
+            On the second equality above, we used $B_k(y_k - x_k)= \mathcal G_{B_k}(y_k)$, and $B_k = \mu/q_k$.
             For all $k \ge 0$, we define $\Xi_k$ and simplify using the above result: 
@@
                     \\&\quad 
-                    \frac{\alpha_k\mu}{2}\Vert y_k - \bar x_k\Vert^2
+                    + \frac{\alpha_k\mu}{2}\Vert y_k - \bar x_k\Vert^2
                     - \alpha_k\langle
@@
                     + \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2
-                \right) 
-                \\
-                & \underset{(3)}{\le} 0. 
+                \right). 
             \end{align*}
@@
             At (1), we substituted $\mathcal E(x_{k - 1}, y_k, \mu, B_k)$. 
-            At (2), we used the $\mathcal E(\bar x_k, y_k, \mu, B_k)\le 0$ by choosing $\bar x_k = \bar y$ in Assumption \ref{ass:for-cnvg} (iii) to make the inequality. 
-            At (3), we used Assumption \ref{ass:for-cnvg} (iv). 
-            At this point, we had proved what we wanted because using the definitions of $\Xi_k, \Xi_k'$ it has:
+            At (2), we used the $\mathcal E(\bar x_k, y_k, \mu, B_k)\le 0$ by choosing $\bar x_k = \bar y$ in Assumption \ref{ass:pggap-dscnt}\ref{ass:pggap-dscnt-itm2}  to make the inequality. 
+            Now, recall the definitions of $\Xi_k, \Xi_k'$ which means we proved the following: 
             \begin{align*}
@@
                 \\
-                &\le 0. 
+                &\le -(1 - \alpha_k)\left(
+                    \mathcal E(x_{k - 1}, y_k, \mu, B_k)
+                    + \frac{\mu}{2}\Vert x_{k - 1} - y_k\Vert^2
+                \right). 
             \end{align*}
@@
     \subsection{Proving the convergence rate}
-        To finally find the convergence rate, we will strengthen Assumption \ref{ass:for-cnvg}. 
+        To finally find the convergence rate, we will strengthen Assumption \ref{ass:pggap-dscnt}. 
         Our convergence rate is expressed for sequences $(\alpha_k)_{k \ge 0}, (q_k)_{k \ ge 0}$ if they satisfy Definition \ref{def:rlx-momentum-seq}. 
@@
         \begin{assumption}[Assumptions for linear convergence rate]\;\label{ass:lin-cnvg}\\
-            Let $(F, f, g, \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:for-cnvg}. 
-            In addition, we strength the prior assumptions:
+            Let $(F, f, g, \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:pggap-dscnt}. 
+            In addition, we strengthened the prior assumptions:
             \begin{enumerate}[nosep]
                 \item Define the set of minimizers $X^+ = \argmin_{z\in \RR^n}\{ f(z) + g(z)\}$, it has $X^+ \neq \emptyset$. 
-                \item $\exists \mu > 0$ such that $\forall\; y \in \RR^n$, it has $\mathcal E \left(\Pi_{X^+}y, y, \mu, B\right) \ge 0$. 
-            \end{enumerate}
-            Now, suppose an algorithm which optimizes a $F = f + g$ satisfying all pervious assumptions, and it generates iterates $(y_k, x_k, v_k)_{k\ge 0}$ that satisfies Definition \ref{def:pg-gap}.
-            In addition, we assume that the parameter sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}, (q_k)_{k \ge 0}, (B_k)_{k \ge 0}$ satisfy the following: 
+                \item Strenghening Assumption \ref{ass:pggap-dscnt}\ref{ass:pggap-dscnt-itm2}, assume $\exists \mu > 0$ such that $\forall y \in \RR^n$, it has $\mathcal E \left(\Pi_{X^+}y, y, \mu, B\right) \ge 0$.
+                \item For all $y, z \in \RR^n$, it satisfies that $\mathcal E(z, y, \mu, B) + \mu/2 \Vert z - y\Vert^2 \ge 0$. 
+            \end{enumerate}
+            Now, suppose an algorithm which optimizes a $F = f + g$ satisfying all previous assumptions, and it generates iterates $(y_k, x_k, v_k)_{k\ge 0}$ that satisfies Definition \ref{def:pg-gap}.
+            In addition, we assume that the parameter sequences $(\alpha_k)_{k \ge 0},(q_k)_{k \ge 0}, (B_k)_{k \ge 0}$ satisfy the following: 
             \begin{enumerate}[nosep]\setcounter{enumi}{3}
-                \item The sequences $\alpha_k, \rho_k, q_k$ are given by Definition \ref{def:rlx-momentum-seq}. 
+                \item The sequences $\alpha_k, q_k$ are given by Definition \ref{def:rlx-momentum-seq}. 
                 \item The sequence $q_k = \mu/B_k$, with $B_k > \mu$. 
-                \item For all $k \ge 0$, $\Pi_{X^+}y_k$ is a unique. 
+                \item For all $k \ge 0$, $\Pi_{X^+}y_k$ is unique. 
             \end{enumerate}
         \end{assumption}
-        \begin{assumption}[Assumption for sublinear convergence rate]
-
+        \begin{assumption}[forever sublinear convergence rate in the convex case]\;\label{ass:forever-cnvx-cnvg}\\
+            Let $(F, f, g, \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:pggap-dscnt}. 
+            In addition, we strengthened the prior assumptions:
+            \begin{enumerate}[nosep]
+                \item Define the set of minimizers $X^+ = \argmin_{z\in \RR^n}\{ f(z) + g(z)\}$, it has $X^+ \neq \emptyset$. 
+                \item The function $f$ is convex. Hence assumption Assumtion \ref{ass:pggap-dscnt} \ref{ass:pggap-dscnt-itm2} satisfied for all $\bar y$, $\mu = 0$. 
+            \end{enumerate}
+            Now, suppose an algorithm which optimizes a $F = f + g$ satisfying all previous assumptions, and it generates iterates $(y_k, x_k, v_k)_{k\ge 0}$ that satisfies Definition \ref{def:pg-gap}.
+            In addition, we assume that the parameter sequences $(\alpha_k)_{k \ge 0},(q_k)_{k \ge 0}, (B_k)_{k \ge 0}$ satisfy the following: 
+            \begin{enumerate}[nosep]
+                \item The sequence $B_k \ge B_{k - 1}$, it's a non-decreasing sequence. 
+                \item $\alpha_k \ge \alpha_{k - 1}$, it's a non-increasing sequence. 
+            \end{enumerate}
         \end{assumption}
-
+        \begin{assumption}[optimal convergence rate in the convex case]
+
+        \end{assumption}
+
+        \subsection{convergence results based on these assumptions}
             % THEOREM ======================================================================================================
-        \begin{theorem}[linear convergence with generic sequence]\;\label{thm:cnvg-generic-seq}\\
-            Let $(F, f, g, \mathcal E, \mu, L)$, and sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}, (q_k)_{k \ge 0}, (B_k)_{k \ge 0}$ 
+            \begin{theorem}[convergence with generic sequence]\;\label{thm:cnvg-generic-seq}\\
+                Let $(F, f, g, \mathcal E, \mu, L)$, and sequences $(\alpha_k)_{k \ge 0}, (q_k)_{k \ge 0}, (B_k)_{k \ge 0}$ 
                 satisfy Assumption \ref{ass:lin-cnvg}. 
@@
                 Because $\alpha_0 = 1$, it also has $v_0 = x_0$. 
-            Choose $z = \bar x, y = x_{-1}$ we have from Assumption \ref{ass:for-cnvg} (iii) that
+                Choose $z = \bar x, y = x_{-1}$ we have from Assumption \ref{ass:pggap-dscnt} (iii) that
                 \begin{align*}
@@
             \textcolor{red}{
-            SOMETHING IS WRONG, LET US EXPLAIN.
+                SOMETHING HAS LIMITATIONS, LET US EXPLAIN.
                 The parameter $q_k = \mu/B_k$ cannot be eliminated from Definition \ref{def:st-apg}. 
@@
             }
+            \par
             The theorem below will definitively close the case to show that there exists choices for the sequence such that a linear convergence exists, meaning that $\beta_k$ will decrease at a linear rate.
-        \begin{lemma}[beta sequence bounds]\;\label{lemma:beta-seq}\\
-            Let sequence $(\alpha_k)_{k \ge 0}, (\rho_{k})_{k \ge 0}, (q_k)_{k \ge 0}$ satisfies Definition \ref{def:rlx-momentum-seq}.
-            Let sequences $(B_k)_{k \ge 1}$ be given by Definition \ref{def:st-apg}. 
-            Define $\beta_k := \prod_{i = 1}^k(1 - \alpha_i) \max \left(\frac{B_i\rho_{i - 1}}{B_{i - 1}}, 1\right)$.
-            Assume in addition that for all $k \ge 0$, $B_k = B_{k - 1} = B$. 
+            \begin{lemma}[beta sequence linear bound]\;\label{lemma:beta-seq}\\
+                Let sequences $(\alpha_k)_{k \ge 0}, (q_k)_{k \ge 0}, (B_k)_{k \ ge 0}$ satisfy Assumption \ref{ass:lin-cnvg}. 
+                Define 
+                $$
+                \beta_k := 
+                \prod_{i = 1}^k\max\left(
+                    1 - \alpha_i, 
+                    \frac{B_i\alpha_i(\alpha_i - q_i)}{\alpha_{i - 1}^2B_{i - 1}}
+                \right).
+                $$
+                Assume in addition $\forall k \ge 0$, $\exists B : B_k = B_{k - 1} = B$ hence there exists $q$ such that $(\forall k \ge 0)\; q_k = q$. 
                 Then, linear convergence of $\beta_k$ is possible under the following scenarios: 
@@
                 \end{enumerate}
+                By the assumption that $q \in (0, 1)$ hence we had a linear convergence rate in each of the above scenarios. 
             \end{lemma}
@@
                 \textbf{Proof of (i)}. 
-            For all $k \ge 1$ it has 
-            \begin{align*}
-                & (1 - \alpha_k)\max\left(
-                    \frac{B_k\rho_{k - 1}}{B_{k - 1}}, 1
-                \right)
-                \\
-                &= \max(\rho_{k - 1}(1 - \alpha_k), 1 - \alpha_k) 
-                \\
-                &\underset{\text{(1)}}{=} \max\left(
-                    \frac{\alpha_k(\alpha_k - q)}{\alpha_{k - 1}^2}, 1 - \alpha_k
-                \right)
-                \\
-                &= \max\left(
-                    \frac{\alpha_k^2}{\alpha_{k - 1}^2} - \frac{q}{\alpha_{k - 1}}, 1 - \alpha_k
-                \right)
-                \\
-                &\underset{\text{(2)}}{\le} 
+                Using mononicity of sequence $\alpha_k$, it has $\alpha_i / \alpha_{i - 1} \le 1$ hence for all $i \ge 1$ it has 
+                \begin{align*}
+                    & \max\left(
+                        1 - \alpha_i, 
+                        \frac{\alpha_i(\alpha_i - q)}{\alpha_{i - 1}^2}
+                    \right)
+                    \\
+                    &\le 
                     \max\left(
-                    1 - \frac{q}{\alpha_{k - 1}}, 1 - \alpha_k
-                \right). 
-            \end{align*}
-            Then, observe that
-            \begin{align*}
-                1 - \frac{q}{\alpha_{k - 1}} &> 1 - \frac{q}{\sqrt{q}}
+                        1 - \alpha_i, \frac{\alpha_i - q}{\alpha_{i - 1}}
+                    \right)
+                    \\
+                    &\le \max\left(
+                        1 - \alpha_i, 1 - \frac{q}{\alpha_{i - 1}}
+                    \right)
+                \end{align*}
+                Then, observe that when $\alpha_i \ge \sqrt{q}$ it has: 
+                \begin{align*}
+                    1 - \frac{q}{\alpha_{i - 1}} &> 1 - \frac{q}{\sqrt{q}}
                     \\
@@
                 \end{align*}
-            Combining the previous two results it has 
-            \begin{align*}
-                (1 - \alpha_k)\max\left(
-                    \frac{B_k\rho_{k - 1}}{B_{k - 1}}, 1
-                \right) \le 
+                Hence
+                \begin{align*}
+                    \max\left(
+                        1 - \alpha_i, 
+                        \frac{\alpha_i(\alpha_i - q)}{\alpha_{i - 1}^2}
+                    \right)\le 
                     \left(1 - \frac{q}{\alpha_{k - 1}}\right).
                 \end{align*}
+                The result now follows by the definition of $\beta_k$. 
                 \par 
                 \textbf{Proof of (ii)}. 
-
+                The proof is obvious by setting both $q_i, \alpha_i$ to be a constant. 
             \end{proof}
-    \subsection{Parameter free representations}
-
-\section{Linear convergence beyond the strongly convex case}
+
+\section{Examples for our assumptions}
     We will check Assumption \ref{ass:lin-cnvg} and, propose examples for it.
+    \subsection{quasi strongly convex function}
         In Necoara et al.'s setting, they have the following assumptions for their objective function. 
@@
         \end{definition}
+
         \begin{proposition}[Q-SCNVX is an example of our assumptions]\label{prop:qscnvx-ass-ok}
@@
             \end{align*}
-        Therefore, it satisfies Assumption \ref{ass:for-cnvg}. 
+            Therefore, it satisfies Assumption \ref{ass:pggap-dscnt}. 
         \end{proposition}
@@
             \end{align*}
-        The above results showed that Assumption \ref{ass:for-cnvg} (ii) has been satisfied, with $\bar y = \Pi_{X^+}y$. 
-        To see (iii) in Assumption \ref{ass:for-cnvg}, observe that Assumption \ref{ass:necoara} has $f$ is convex. 
+            The above results showed that Assumption \ref{ass:pggap-dscnt} (ii) has been satisfied, with $\bar y = \Pi_{X^+}y$. 
+            To see (iii) in Assumption \ref{ass:pggap-dscnt}, observe that Assumption \ref{ass:necoara} has $f$ is convex. 
         \end{proof}
+
     \subsection{A nonconvex example}

### 2025-08-30 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

\documentclass[12pt]{article}

% \input{presets/wang_full.tex}
\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{true}
\input{presets/wang/input.tex}
\input{presets/misc.tex}
\input{presets/julia_lstlisting.tex}

\begin{document}

\title{{\fontfamily{ptm}\selectfont An Inexact Accelreated Proximal Gradient Method for TV Variation Problems}}

\author{
    Author 1 Name, Author 2 Name
    \thanks{
        Subject type, Some Department of Some University, Location of the University,
        Country. E-mail: \texttt{author.namee@university.edu}.
    }
}

\date{\today}

\maketitle
\todoinline{This paper is currently in draft mode. Check source to change options. }
% \vskip 8mm

\begin{abstract} 
    \noindent
    Not yet added. 
\end{abstract}

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 47H05, 52A41, 90C25; Secondary 15A09, 26A51, 26B25, 26E60, 47H09, 47A63.
\noindent{\bfseries Keywords:}

% ==============================================================================
\section{Introduction}
    Let's make a type of algorithm that has the niche for applications with a state of the art performance. 
    \begin{assumption}\label{ass:smooth-nsmooth-sum}
        We assume the following about $(F, f, g, L, X^+)$: 
        \begin{enumerate}[nosep]
            \item $f: \RR^n \rightarrow \RR$ is a convex, $L$ Lipschitz smooth function but doesn't support simple implementations of its proximal operator. 
            \item $g: \RR^n \rightarrow \RR$ is convex, proper, and closed, and its proximal operator can be easily implemented, and easy to obtain some element $\partial g$ at all points of the domain. 
            \item The over all objective has $F = f + g$. 
        \end{enumerate}
        Under this assumption, we denote the proximal gradient operator of $F = f+ g$ as $T_B(x) = \hprox_{B^{-1}g}(x - B^{-1}\nabla f(x))$. 
        Note that by definition it has also:
        \begin{align*}
            T_B(x) &= 
            \hprox_{B^{-1}g}\left(
                x - B^{-1}\nabla f(x)
            \right)
            \\
            &= \argmin_{z}\left\lbrace
                g(z)
                + \langle \nabla f(x), z\rangle
                + \frac{B}{2}\Vert z - x \Vert^2
            \right\rbrace. 
        \end{align*}
    \end{assumption}
    \begin{definition}[A measure of error from proximal gradient evaluations]\;\\
        Let $(F, f, g, L)$ satisfies Assumption \ref{ass:smooth-nsmooth-sum}. 
        For all $x, z \in \RR^n$, define $S$: 
        \begin{align*}
            S_B(z | x) &= \partial 
            \left[
                z \mapsto g(z)
                + \langle \nabla f(x), z\rangle
                + \frac{B}{2}\Vert z - x \Vert^2
            \right](z). 
        \end{align*}
    \end{definition}
    Observe: 
    \begin{enumerate}[nosep]
        \item $S_B(z | x) = \partial g(z) + \nabla f(x)+ B(z - x)$,
        \item $\mathbf 0 \in S_B(T(x) | x)$, 
        \item $(S_B(\cdot | x))^{-1}(\mathbf 0)$ is a singleton by strong convexity. 
    \end{enumerate}
    Let's assume inexact evaluation of $\tilde x \approx T_B(x)$, then the error measure is the set $S_B(\tilde x | x)$. 
    Assuming that we have accurate information on $\nabla f(x)$, then $\forall w \in S_B(\tilde x | x)\;\exists \tilde v \in \partial g(\tilde x)$. 
    \begin{align*}
        w &= \tilde v + \nabla f(x) + B(\tilde x - x). 
    \end{align*}
    We want to control $w$ in the implementations of inexact accelerated proximal gradient algorithm.

\section{Key ideas we need to get right}
    \begin{definition}[inexact proximal gradient]\;\label{def:inxt-pg}\\
        Let $(F, f, g, L)$ satisfies Assumption \ref{ass:smooth-nsmooth-sum}.
        Let $\epsilon \ge 0, B \ge 0$. 
        We Define for all $x \in \RR^n$ the inexact proximal gradient operator $T_B^{(\epsilon)}(x)$ to be such that if $\tilde x \in T^{(\epsilon)}_{B}(x)$ then, $\exists w \in S_{B}(\tilde x | x):\Vert w\Vert\le \epsilon \Vert \tilde x - x\Vert$.         
    \end{definition}
    The algorithm we will design must produce iterates in a way that satisfies the inexact proximal gradient operator define above. 
    The following theorem will characterize a key inequality for convergence claim. 
    \begin{theorem}[inexact over regularized proximal gradient inequality]\;\label{thm:inxt-pg-ineq}\\
        Let $(F, f, g, L)$ satisfies Assumption \ref{ass:smooth-nsmooth-sum}.
        Take $T^{(\epsilon)}_B$ as given in Definition \ref{def:inxt-pg}. 
        Let $\epsilon \ge 0$. 
        For all $x\in \RR^n$, if $\exists B \ge 0$ such that $\tilde x \in T_{B + \epsilon}^{(\epsilon)}(x)$ and, $D_f(\tilde x, x)\le \frac{B}{2}\Vert \tilde x - x\Vert^2$. 
        Then for all $z, x \in \RR^n$ it has: 
        \begin{align*}
            0 &\le F(z) - F(\tilde x) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
            - \frac{B}{2}\Vert z - \tilde x\Vert^2. 
        \end{align*}
    \end{theorem}
    \begin{proof}
        By Definition \ref{def:inxt-pg}, $T_{B + \epsilon}^{(\epsilon)}(x)$ minimizes a $h(z) = z \mapsto g(z) + \langle \nabla f(x), z \rangle + \frac{B + \epsilon}{2}\Vert x - z\Vert^2$ to produce $\tilde x$ so that $w \in S_{B + \epsilon}(\tilde x| x) = \partial h(x)$. 
        $h$ is $B + \epsilon$ strongly convex by convexity of $g$. 
        Since $w \in \partial h(\tilde x)$, it has subgradient inequality through strong convexity: 
        $$
            (\forall z \in \RR^n)\;  
            \frac{B + \epsilon}{2}\Vert z - \tilde x\Vert^2 \le h(z) - h(\tilde x) - \langle w,  z - \tilde x\rangle. 
        $$
        This means for all $z \in \RR^n$: 
        \begin{align*}
            &\frac{B + \epsilon}{2}\Vert \tilde x - z \Vert^2 
            \\
            &\le 
            g(z) + \langle \nabla f(x), z\rangle + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
            - \left(
                g(\tilde x) + 
                \langle \nabla f(x), \tilde x\rangle
                + 
                \frac{B + \epsilon}{2}\Vert \tilde x - x\Vert^2
            \right)
                \\ &\quad 
                - \langle w, z - \tilde x\rangle
            \\
            &= 
            \left(
                g(z) - g(\tilde x)
                + \frac{B + \epsilon}{2}\Vert z - x\Vert^2 - \frac{B + \epsilon}{2}\Vert \tilde x - x\Vert^2
                - \langle w, z - \tilde x\rangle
            \right)
            \\&\quad 
                + \langle \nabla f(x), z - x + x -\tilde x\rangle
            \\
            &\underset{(1)}{=} 
            \left(
                g(z) - g(\tilde x)
                + \frac{B + \epsilon}{2}\Vert z - x\Vert^2 - \frac{B + \epsilon}{2}\Vert \tilde x - x\Vert^2
                - \langle w, z - \tilde x\rangle
            \right)
                \\
                &\quad 
                - D_f(z, x) + f(z)
                + D_f(\tilde x, x) - f(\tilde x)
            \\
            &=
            \left(
                F(z) - F(\tilde x)
                - \langle w, z - \tilde x\rangle
            \right)
            + 
            \left(
                \frac{B + \epsilon}{2}\Vert z - x\Vert^2 - D_f(z, x)
            \right) 
                \\ &\quad 
                + \left(
                    D_f(\tilde x, x)
                    - \frac{B + \epsilon}{2}\Vert \tilde x - x\Vert^2
                \right)
            \\
            &\underset{(2)}{\le} 
            \frac{B + \epsilon}{2}\Vert z - x\Vert^2 - D_f(z, x)
            + \left(
                \frac{B + \epsilon}{2}\Vert z - x\Vert^2
                - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2
            \right)
            \\
            &\le
            F(z) - F(\tilde x) + \Vert w \Vert\Vert z - \tilde x\Vert
            + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2
            \\
            &\underset{(3)}{\le}
            F(z) - F(\tilde x) 
            + \epsilon\Vert x - \tilde x\Vert\Vert z - \tilde x\Vert
            + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2. 
        \end{align*}
        At (1), we used: 
        \begin{align*}
            & \langle \nabla f(x), z - x\rangle
            - \langle \nabla f(x), \tilde x - x\rangle
            \\
            &= 
            - D_f(z, x) + f(z) - f(x)
            + D_f(\tilde x, x) - f(\tilde x) + f(x)
            \\
            &= f(z) + f(\tilde x) - D_f(z, x) + D_f(\tilde x , x). 
        \end{align*}
        At (2), we had $f$ convex as the assumption, hence $D_f(z, x) \le 0$. 
        We also had the assumption that $B$ makes $D_f(\tilde x, x) \le \frac{B}{2}\Vert \tilde x - x\Vert^2$, this simplies the third term from the previous line into $- \frac{\epsilon}{2}\Vert x - \tilde x\Vert^2$. 
        At (3), we applied the assumed inequality $\Vert w\Vert \le \epsilon \Vert x - \tilde x\Vert \Vert z - \tilde x\Vert$. 
        Continuing: 
        \begin{align*}
            0 &\le
            \left(
                F(z) - F(\tilde x) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
                - \frac{B + \epsilon}{2}\Vert z - \tilde x\Vert^2 
            \right)
            + \epsilon \Vert \tilde x - x\Vert \Vert z - \tilde x\Vert
            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2
            \\
            &\underset{(4)}{=} 
            F(z) - F(\tilde x) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
            - \frac{B}{2}\Vert z - \tilde x\Vert^2. 
        \end{align*}
        At (4), we use some algebra: 
        \begin{align*}
            &
            \epsilon \Vert \tilde x - x\Vert \Vert z - \tilde x\Vert
            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2
            \\
            &=\epsilon \Vert \tilde x - x\Vert \Vert z - \tilde x\Vert
            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2 - \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2
            + \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2
            \\
            &= 
            - \epsilon(\Vert x - \tilde x\Vert - \Vert z -\tilde x\Vert)^2 
            + \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2 
            \\
            &\le \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2. 
        \end{align*}
    \end{proof}
    \subsection{The accelerated proximal gradient algorithm}
        \begin{definition}[accelerated inexact proximal gradient algorithm]\label{def:inxt-apg}
            Let 
            \begin{enumerate}[nosep]
                \item $(\alpha_k)_{k \ge 0}$ be a sequence in $(0, 1]$. 
                \item Let $(B_k)_{k \ge 0}$ be a non-negative sequence. 
                \item Let $(F, f, g, L)$ be given by Assumption \ref{ass:smooth-nsmooth-sum}. 
                \item Let $(\epsilon_k)$ be a non-negative sequence that is the error schedule. 
            \end{enumerate}
            Initialize with any $(x_{-1}, v_{-1})$. 
            For these given parameters, an algorithm is a type of accelerated proximal gradient if it generates $(y_k, x_k, v_k)_{k \ge 0}$ such that
            for $k\ge 0$: 
            \begin{align*}
                & y_{k} = \alpha_{k} v_{k - 1} + (1 - \alpha_{k}) x_{k - 1},
                \\
                & x_k \in T_{B_k + \epsilon_k}^{(\epsilon_k)}y_k: D_f(x, \tilde x) \le (1/2)\Vert x - \tilde x\Vert^2, 
                \\
                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}).
            \end{align*}
        \end{definition}

\section{convergence rates results}
    We will now show that Algorithms satisfying Definition \ref{def:inxt-apg} has desirable convergence rate. 
    \begin{assumption}[convergence assumptions]\label{ass:apg-cnvg}
        Let $(F, f, g, L)$ satisfies Assumption \ref{ass:smooth-nsmooth-sum} and in addition assume that $F$ admits a set of non-empty minimizers $X^+$. 
    \end{assumption}
    \begin{lemma}[inexact one step convergence claim]\;\label{lemma:inxt-apg-onestep}\\
        Let $(F, f, g, L, X^+)$ satisfies Assumption \ref{ass:apg-cnvg}. 
        Suppose that an algorithm satisfies optimizes the given $F =f + g$ also satisfying Definition \ref{def:inxt-apg}.
        Then for the generated iterates $(y_k, x_k, v_k)_{k \ge 0}$, it has for all $k \ge 1$: 
        \begin{align*}
            &F(\bar x) - F(x_k)  - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
            \\
            &\le 
            \max\left(
                1 - \alpha_k, 
                \frac{\alpha_k(B_k + \epsilon_k)}{\alpha_{k -1}^2B_{k - 1}}
            \right)
            \left(
                F(x_{k - 1}) - F(\bar x) 
                + \frac{\alpha_{k - 1}^2B_{k - 1}}{2}\Vert \bar x - v_{k - 1} \Vert^2
            \right). 
        \end{align*}
    \end{lemma}
    \begin{proof}
        Let $\bar x \in X^+$, making it a minimizer of $F$. 
        Define $z_k := \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$. 
        It can be verified that:
        \begin{align}\begin{split}
            z_k - x_k &= \alpha_k(\bar x - v_k),
            \\
            z_k - y_k &= \alpha_k(\bar x - v_{k - 1}).     
        \end{split}\tag{a}\label{lemma:inxt-apg-onestep-a}
        \end{align}
        Because from Definition \ref{def:inxt-apg} it has for all $k \ge 1$: 
        \begin{align*}
            z_k - x_k &= 
            \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
            \\
            &= \alpha_kx^+ + (x_{k - 1} - x_k) - \alpha_kx_{k - 1}
            \\
            &= \alpha_k \bar x - \alpha_k v_k, 
            \\
            z_k - y_k &= 
            \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
            \\
            &= \alpha_k \bar x - \alpha_k v_{k - 1}. 
        \end{align*}
        For all $k \ge 0$, apply Theorem \ref{thm:inxt-pg-ineq} with $z = z_k, \tilde x = x_k, x = y_k, \epsilon = \epsilon_k, B = B_k$: 
        \begin{align*}
            0 &\le 
            (F(z_k) - F(x_k) ) +
            \left(
                \frac{B_k + \epsilon_k}{2}\Vert z_k - y_k\Vert^2
                - \frac{B_k}{2}\Vert z_k - x_k\Vert^2
            \right)
            \\
            &\underset{(1)}{\le}
            (\alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k))
            + 
            \left(
                \frac{B_k + \epsilon_k}{2}\Vert z_k - y_k\Vert^2
                - \frac{B_k}{2}\Vert z_k - x_k\Vert^2
            \right)
            \\
            &\underset{\eqref{lemma:inxt-apg-onestep-a}}{=} 
            (\alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k))
                \\ &\quad 
                + \left(
                    \frac{(B_k + \epsilon_k)\alpha_k^2}{2}\Vert \bar x - v_{k - 1} \Vert^2
                    - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \right)
            \\
            &= 
            F(\bar x) - F(x_k)
            + (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x))
                \\ &\quad 
                + \left(
                    \frac{(B_k + \epsilon_k)\alpha_k^2}{2}\Vert \bar x - v_{k - 1} \Vert^2
                    - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \right)
            \\
            &= 
            F(\bar x) - F(x_k) 
            - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \\ &\quad 
                + (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x))
                + \frac{(B_k + \epsilon_k)\alpha_k^2}{2}\Vert \bar x - v_{k - 1} \Vert^2
            \\
            &= F(\bar x) - F(x_k) 
            - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \\ &\quad
                + (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x))
                + \frac{(B_k + \epsilon_k)\alpha_k^2}{\alpha_{k - 1}^2B_{k - 1}}\frac{\alpha_{k - 1}^2B_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
            \\
            &= 
            F(\bar x) - F(x_k) - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
            \\ &\quad 
            + \max\left(
                1 - \alpha_k, 
                \frac{(B_k + \epsilon_k)\alpha_k^2}{\alpha_{k - 1}^2B_{k - 1}}
            \right)
            \left(
                F(x_{k - 1}) - F(\bar x) 
                + \frac{\alpha_{k - 1}^2B_{k - 1}}{2}\Vert \bar x - v_{k - 1} \Vert^2
            \right). 
        \end{align*}
        At (1) we used convexity of $f$ which is assumed and it makes $f(z_k) \le \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1})$ because $\alpha_k \in (0, 1]$ from Definition \ref{def:inxt-apg}. 
    \end{proof}
    \\
    As a prelude, to derive the convergence rate we unroll the recurrence relation proved in the above lemma.
    It remains to create convergence criterions of the error relative sequence $\epsilon_k$ such that the original optimal convergence rate of $\mathcal O(1/k^2)$ the sequence remains unaffected. 
    Let the sequence $(B_k)_{k \ge 0}$ be given by **Definition 2**. 
    We suggest the following descriptors using another sequence $\rho_k$ given by for all $k \ge 1$: 
    \begin{align*}
        \rho_k &= \frac{B_k + \epsilon_k}{B_{k - 1}}\frac{B_{k - 1}}{B_k}.
    \end{align*}
    This means the following: 
    \begin{align*}
        \max\left(
            1 - \alpha_k, 
            \frac{\alpha_k^2(B_k + \epsilon_k)}{\alpha_{k - 1}^2B_{k - 1}}
        \right)
        &=
        \max\left(
            \sim, 
            \rho_k\frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
        \right)
        \\
        &\le \max(1, \rho_k)\max\left(
            \sim, 
            \frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
        \right). 
    \end{align*}
    If we consider $\rho_k \le (1 + 2/k^2)$, it has the ability to make
    \begin{align*}
        \prod_{k = 1}^{n} 
        \max \left(
            1 - \alpha_k, 
            \frac{\alpha_k^2(B_k + \epsilon_k)}{\alpha_{k - 1}^2B_{k - 1}}
        \right)
        &\le 
        \prod_{k = 1}^{n} 
        \max(1, \rho_k)
        \left(
        \prod_{i = 1}^{n}
            \max\left(
                1 - \alpha_k, 
                \frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
            \right)
        \right)
        \\
        &\le \prod_{k = 1}^n
        \left(
            1 + \frac{2}{k^2}
        \right)
        (\sim)
        \\
        &\le 2 (\sim). 
    \end{align*}

    The following lemma will seal the case for the other remaining big product above.

\bibliographystyle{siam}

\bibliography{references/Books.bib}

\end{document}

### 2025-09-01 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, fixes

@@
 
-\title{{\fontfamily{ptm}\selectfont An Inexact Accelreated Proximal Gradient Method for TV Variation Problems}}
+\title{{\fontfamily{ptm}\selectfont An Inexact Accelreated Proximal Gradient Method for Large Scale Robust TV Variation Problems}}
 
@@
     \noindent
-    Not yet added. 
+    I read a lot of papers on Catalyst, and restart. 
+    And it just dawned on me on how simple the ideas can be, and I had identified a specific type of problem where the idea has practical advantage. 
+    This is note is a plan of our upcoming practical paper, with numerical experiments, applications and sweet theories. 
 \end{abstract}
@@
     \begin{assumption}\label{ass:smooth-nsmooth-sum}
-        We assume the following about $(F, f, g, L, X^+)$: 
+        We assume the following about $(F, f, g, L)$: 
         \begin{enumerate}[nosep]
-            \item $f: \RR^n \rightarrow \RR$ is a convex, $L$ Lipschitz smooth function but doesn't support simple implementations of its proximal operator. 
+            \item $f: \RR^n \rightarrow \RR$ is a convex, $L$ Lipschitz smooth function but doesn't support any easy implementation of its proximal operator. 
             \item $g: \RR^n \rightarrow \RR$ is convex, proper, and closed, and its proximal operator can be easily implemented, and easy to obtain some element $\partial g$ at all points of the domain.
@@
             \\
-            &\underset{(4)}{=} 
+            &\underset{(4)}{\le} 
             F(z) - F(\tilde x) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
@@
                 \item Let $(F, f, g, L)$ be given by Assumption \ref{ass:smooth-nsmooth-sum}. 
-                \item Let $(\epsilon_k)$ be a non-negative sequence that is the error schedule. 
+                \item Let $(\epsilon_k)_{k \ge 0}$ be a non-negative sequence that is the error schedule. 
             \end{enumerate}
@@
             \\
-            &= \alpha_kx^+ + (x_{k - 1} - x_k) - \alpha_kx_{k - 1}
+            &= \alpha_k\bar x + (x_{k - 1} - x_k) - \alpha_kx_{k - 1}
             \\
@@
             0 &\le 
-            (F(z_k) - F(x_k) ) +
-            \left(
+            F(z_k) - F(x_k) +
             \frac{B_k + \epsilon_k}{2}\Vert z_k - y_k\Vert^2
             - \frac{B_k}{2}\Vert z_k - x_k\Vert^2
-            \right)
             \\
             &\underset{(1)}{\le}
-            (\alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k))
+            \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
             + 
-            \left(
             \frac{B_k + \epsilon_k}{2}\Vert z_k - y_k\Vert^2
             - \frac{B_k}{2}\Vert z_k - x_k\Vert^2
-            \right)
             \\
             &\underset{\eqref{lemma:inxt-apg-onestep-a}}{=} 
-            (\alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k))
+            \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
                 \\ &\quad 
-                + \left(
-                    \frac{(B_k + \epsilon_k)\alpha_k^2}{2}\Vert \bar x - v_{k - 1} \Vert^2
+                + \frac{(B_k + \epsilon_k)\alpha_k^2}{2}\Vert \bar x - v_{k - 1} \Vert^2
                 - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
-                \right)
             \\
@@
                 \\ &\quad 
-                + \left(
-                    \frac{(B_k + \epsilon_k)\alpha_k^2}{2}\Vert \bar x - v_{k - 1} \Vert^2
+                + \frac{(B_k + \epsilon_k)\alpha_k^2}{2}\Vert \bar x - v_{k - 1} \Vert^2
                 - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
-                \right)
             \\
@@
     \end{proof}
-    \\
+    \par
     As a prelude, to derive the convergence rate we unroll the recurrence relation proved in the above lemma.
     It remains to create convergence criterions of the error relative sequence $\epsilon_k$ such that the original optimal convergence rate of $\mathcal O(1/k^2)$ the sequence remains unaffected. 
-    Let the sequence $(B_k)_{k \ge 0}$ be given by **Definition 2**. 
-    We suggest the following descriptors using another sequence $\rho_k$ given by for all $k \ge 1$: 
+    Let the sequence $(B_k)_{k \ge 0}$ be given as in Definition \ref{def:inxt-apg}. 
+    We suggest the following using another sequence $\rho_k$ given by for all $k \ge 1$: 
     \begin{align*}
-        \rho_k &= \frac{B_k + \epsilon_k}{B_{k - 1}}\frac{B_{k - 1}}{B_k}.
+        \rho_k &:= \frac{B_k + \epsilon_k}{B_{k - 1}}\frac{B_{k - 1}}{B_k} = \frac{B_k + \epsilon_k}{B_k}
     \end{align*}
@@
         \max\left(
-            \sim, 
+            1 - \alpha_k, 
             \rho_k\frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
@@
         &\le \max(1, \rho_k)\max\left(
-            \sim, 
+            1 - \alpha_k, 
             \frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
@@
         \max(1, \rho_k)
-        \left(
         \prod_{i = 1}^{n}
@@
             \frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
-            \right)
         \right)
@@
         \right)
-        (\sim)
+        \prod_{i = 1}^{n}
+        \max\left(
+            1 - \alpha_k, 
+            \frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
+        \right)
         \\
-        &\le 2 (\sim). 
+        &\le 2 
+        \prod_{i = 1}^{n}\max\left(
+            1 - \alpha_k, 
+            \frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
+        \right). 
+    \end{align*}
+    Assuming no $B_k = 0$ then the error schedule $\rho_k \le (1 + 2/k^2)$ translates to 
+    \begin{align*}
+        \frac{B_k + \epsilon_k}{B_k} &\le 1 + \frac{2}{k^2}
+        \\
+        \iff 
+        \epsilon_k &\le - B_k + B_k(1 + 2/k^2) \le \frac{2B}{k^2}. 
     \end{align*}
 
-    The following lemma will seal the case for the other remaining big product above.
+\section{Motivations for applications}
+    Optimization problem of the following type: 
+    $$
+        \min_{x} \left\lbrace
+            f(Ax) + g(Dx)
+        \right\rbrace, 
+    $$
+    where
+    \begin{enumerate}[nosep]
+        \item Let $A \in \RR^{m_1 \times n}, D \in \RR^{m_2 \times n}$,  where inverting $A^TA + \mu I$ exactly for some $\mu > 0$ is computationally intensive on computers. 
+        \item $f: \RR^{m_1} \rightarrow \RR$ is $L$ Lipschitz smooth and, convex but taking maybe $\hprox_f$ is computationally intensive. 
+        \item $g: \RR^{m_2} \rightarrow \overline \RR$ is convex, closed and proper. 
+    \end{enumerate}
+    Solving it using traditional method such as ADMM \cite[chapter 6]{boyd_distributed_2011}, or Chambolle Pock \cite{chambolle_first-order_2010}, would require the knowledge of $(A^TA + \mu I)^{-1}$, and $f$ has $\hprox$ that is simple to evaluate.
+    Inverting matrix exactly is never easy, especially the sparse and large matrix in image processing (The number of elements in the matrix scales by $\mathcal O(n^4)$ for a size $n \times n$ image for storage, and inverting it with bruteforce is $\mathcal (n^{6})$).
+    People can do it a few time but it's not practical/simple to do it in every step of some iterative algorithms! 
+    Of course, we can use other smarter method such as Krylov Subspace method for block structured sparse matrices (or most recently, their randomized variants), but they will not be perfectly accurate.
+    Our method however, it will have the advantage of being matrix inversion free. 
+    \par
+    Our proposed algorithm allows inexact evaluation of $\hprox_{B^{-1}g\circ D}$. 
+    This proximal operator can be evaluated using popular algorithm such as Chambolle Pock, or any other efficient approximation algorithm and it will bypass the need of any matrix inversion involving $D$.
+    Because look, the problem we solve for our algorithm is $\hprox_{(B + \epsilon)^{-1}g\circ D}(x)$ which can be reformulated into: 
+    \begin{align*}
+        \argmin_{y, z} \left\lbrace
+            g(y) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2 : Az = y, y\in \RR^{m_2}, z\in \RR^{n}
+        \right\rbrace. 
+    \end{align*}
+    Solving this problem inexactly is not difficult. 
+    First order method such as Chambolle Pock will suffice, and it won't need expensive matrix inversion. 
+    And, taking the gradient of $\nabla f(Ax)$ doesn't need for $(A^TA + \mu I)^{-1}$. 
+    Our method is also compatible with enhancement such as restart for objective function satisfying the quadratic growth conditions for optimal linear convergence. 
+    \par
+    This is especially useful for problem where, $A$ is massive and sparse without obvious structure. 
+    For example, a TV variational minimization approach for Robust MRI imaging that involves downsampling, blurring, or convolution \cite{zhang_robust_2022, joshi_mri_2009}\cite[Section 7.4]{chambolle_introduction_2016}.
+    Applications as such adds another matrix $D$, or additional linear constraints to improve the robustness of MRI image reconstruction. 
+    Other potential applications with such structural optimization objective include large regression problem where the penalization term is highly non-trivial. 
+    \par
+    Why we think this paper will fly? 
+    Because: 
+    \begin{enumerate}
+        \item The core theories part for the outer loop convergence described previously are quite simple and easy to understand for interested readers and, practitioners compared to previous results like in the Catalyst Frameworks or Inexact Accelerated Proximal Gradient Method.
+        \item I haven't found anyone that has good solutions in this type of problem which bypasses inverting $D$ or $A$. 
+        \item It will shine numerically if coupled with advanced approximation algorithm for evaluation the prox of $g\circ D$, for specific $g$ relevant for applications. 
+        \item Our theories give the flexibilities for whatever the practitioners want to do with $\hprox_{B^{-1}g\circ D}$. They can specialize and improved based our theoretical frameworks. 
+    \end{enumerate}
 

### 2025-09-07 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
TwT, fixes

@@
 
-\title{{\fontfamily{ptm}\selectfont An Inexact Accelreated Proximal Gradient Method for Large Scale Robust TV Variation Problems}}
+\title{{\fontfamily{ptm}\selectfont An Inexact Accelerated Proximal Gradient Method for Large Scale Robust TV Variation Problems}}
 
@@
                 \\
-                & x_k \in T_{B_k + \epsilon_k}^{(\epsilon_k)}y_k: D_f(x, \tilde x) \le (1/2)\Vert x - \tilde x\Vert^2, 
+                & x_k \in T_{B_k + \epsilon_k}^{(\epsilon_k)}(y_k): D_f(x_k, y_k) \le (B_k/2)\Vert x_k -  y_k\Vert^2, 
                 \\
@@
             \\
-            &= 
+            &\le 
             F(\bar x) - F(x_k) - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
@@
     \par
-    Our proposed algorithm allows inexact evaluation of $\hprox_{B^{-1}g\circ D}$. 
-    This proximal operator can be evaluated using popular algorithm such as Chambolle Pock, or any other efficient approximation algorithm and it will bypass the need of any matrix inversion involving $D$.
+    Our proposed algorithm allows inexact evaluation of the proximal operator of $g\circ D$. 
+    It can be evaluated using popular algorithm such as Chambolle Pock, or any other efficient approximation algorithm and it can bypass the need of any matrix inversion involving $D$. 
     Because look, the problem we solve for our algorithm is $\hprox_{(B + \epsilon)^{-1}g\circ D}(x)$ which can be reformulated into: 
     \begin{align*}
-        \argmin_{y, z} \left\lbrace
-            g(y) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2 : Az = y, y\in \RR^{m_2}, z\in \RR^{n}
+        \argmin_{z} \left\lbrace
+            g(Dz) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
         \right\rbrace. 
     \end{align*}
-    Solving this problem inexactly is not difficult. 
-    First order method such as Chambolle Pock will suffice, and it won't need expensive matrix inversion. 
-    And, taking the gradient of $\nabla f(Ax)$ doesn't need for $(A^TA + \mu I)^{-1}$. 
+    First order method such as Chambolle Pock can optimize the problem inexactly without matrix inversion. 
+    And, taking the gradient of $f(Ax)$ doesn't need for $(A^TA + \mu I)^{-1}$. 
     Our method is also compatible with enhancement such as restart for objective function satisfying the quadratic growth conditions for optimal linear convergence. 

### 2025-09-12 Notebook LaTEX/R-WAPG/2025-06-10-00-paper.tex
>w<, changes

--- 2025-03-03 Notebook LaTEX/R-WAPG/relaxed-wapg-02-03-2025.tex
@@
 \allowdisplaybreaks
-\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{false}
+\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{true}
 \input{presets/wang/input.tex}
@@
         \end{align}
-        % To see $\epsilon_k \ge 0$, use Theorem \ref{thm:prox-grad-ineq} and let $y = y_k, x = x_k$, by the definition $g_k = L(y_k - T_L(y_k))$ it has:
-        % \begin{align*}
-        %     F(x_k) - F(T_L(y_k))
-        %     - \langle L(y_k - T_L(y_k)),x_k - y_k \rangle
-        %     - \frac{L}{2}\Vert y_k - T_Ly_k\Vert^2
-        %     - \frac{\mu}{2}\Vert x_k - y_k\Vert^2
-        %     &\ge 0
-        %     \\
-        %     \iff
-        %     F(x_k) - F(T_L(y_k))
-        %     - \langle g_k,x_k - y_k \rangle
-        %     - \frac{1}{2L}\Vert g_k\Vert^2
-        %     &\ge 0.
-        % \end{align*}
     \end{assumption}
@@
     In this section, we propose Algorithm \ref{alg:free-rwapg} which estimates the $\mu$ constant as the algorithm executes using the Bregman divergence of $f$ estimated by previous iterates.
-    It is called \emph{Free R-WAPG} because it doesn't require any knowledge of $\mu, L$ in prior for the smooth part $f$, making it parameter-free.
+    \par
+    \textcolor{purple}{
+        We can do this because all convex function is $\mu = 0$ strongly convex. 
+        With $\mu = 0$, it has from Definition \ref{def:rwapg-seq} that for all $k \ge 0$: 
+        \begin{enumerate}[nosep]
+            \item It allows $\alpha_k \in (0, 1)$. The sequence $(\alpha_k)_{k \ge 1}$ is as loose as possible. 
+            \item It has $\rho_{k - 1} = \alpha_k/((1 - \alpha_k)\alpha_{k - 1}^2)$, hence $(1 - \alpha_k)\rho_{k - 1} = \alpha_k^2/\alpha_{k - 1}^2$. 
+        \end{enumerate}
+        Hence, the big product in Proposition \ref{prop:wapg-convergence} simplifies into
+        \begin{align*}
+            \prod_{i = 0}^{k - 1}
+            \max(1, \rho_i)(1 - \alpha_{i + 1})
+            &= 
+            \prod_{i = 0}^{k - 1}
+            \max(1 - \alpha_{i + 1}, \rho_i(1 - \alpha_{i + 1}))
+            \\
+            &= 
+            \prod_{i = 0}^{k - 1}
+            \max\left(
+                1 - \alpha_{i + 1}, \frac{\alpha_{i + 1}^2}{\alpha_i^2}\right). 
+        \end{align*}
+        Finally, since $\mu = 0$, Propisition \ref{prop:r-wapg-momentum-repr} applies with the momentum term simplifies into $\alpha_{k + 1}(\alpha_k^{-1} - 1)$. 
+    }
+    \par
+    Below, we define \emph{Free R-WAPG}. 
     \begin{algorithm}
@@
             \STATE{\textbf{Compute: } $f(y_{k + 1})$}
-            \STATE{$\mu_k := D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2 + (1/2)\mu_k$;}
+            \STATE{$\mu_{k + 1} := D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2 + (1/2)\mu_k$;}
         \ENDFOR

### 2025-09-12 Notebook LaTEX/R-WAPG/presentation.tex
>w<, changes

@@
                     & \alpha_0 \in (0, 1], \\
-                    & \alpha_k \in (\mu, 1] \quad (\forall k \ge 1). 
+                    & \alpha_k \in (\mu/L, 1] \quad (\forall k \ge 1). 
                 \end{align*}    
@@
     \subsection{Free R-WAPG}
+        \begin{frame}{Introducing numerical experiments}
+            All convex functions are strongly convex with strong convexity constant $\mu = 0$. 
+            With $\mu = 0$, it has from Definition \ref{def:rwapg-seq} that for all $k \ge 0$: 
+            \begin{enumerate}
+                \item It allows $\alpha_k \in (0, 1)$. The sequence $(\alpha_k)_{k \ge 1}$ is as loose as possible. 
+                \item It has $\rho_{k - 1} = \alpha_k/((1 - \alpha_k)\alpha_{k - 1}^2)$, hence $(1 - \alpha_k)\rho_{k - 1} = \alpha_k^2/\alpha_{k - 1}^2$. 
+            \end{enumerate}
+            This simplifies our convergence claim into: 
+            \begin{align*}
+                \prod_{i = 0}^{k - 1}
+                \max(1, \rho_i)(1 - \alpha_{i + 1})
+                &= 
+                \prod_{i = 0}^{k - 1}
+                \max(1 - \alpha_{i + 1}, \rho_i(1 - \alpha_{i + 1}))
+                \\
+                &= 
+                \prod_{i = 0}^{k - 1}
+                \max\left(
+                1 - \alpha_{i + 1}, \frac{\alpha_{i + 1}^2}{\alpha_i^2}\right). 
+            \end{align*}
+            This insipired our numerical experiments. 
+        \end{frame}
         \begin{frame}{Free R-WAPG}
@@
         \end{frame}
+        \begin{frame}{Real time R-WAPG upper bound}
+            By collecting $(\alpha_k)_{k \ge 0}$ while the algorithm is running we made the following plot for the simple quadratic experiment. 
+            \begin{figure}[H]
+                \centering
+                \begin{subfigure}[b]{0.75\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{
+                        assets/simple_regression_rwapg_upperbnd_1024.png
+                    }
+                \end{subfigure}
+                \caption{
+                    $N = 1024$, the upper bound estimates in real time from the collected $(\alpha_k)_{k \ge 0}$ sequence. 
+                }
+                \label{fig:simple-quadratic-r-wapg-rwapg-upperbnd}
+            \end{figure}
+        \end{frame} 
     \subsection{Numerical experiment, LASSO}
@@
         \begin{frame}{Estimates of strong convexity constant}
-            The parameters in this specific trial are are $\mu = 7.432363627613958\times 10^{-18}$ and $L = 2321.737206983643$. 
+            The parameters in this specific trial are $\mu = 7.432363627613958\times 10^{-18}$ and $L = 2321.737206983643$. 
             \begin{figure}[H]
@@
                 \label{fig:single-lass-mu-estimates}
+            \end{figure}
+        \end{frame}
+        \begin{frame}{Real time R-WAPG upper bound}
+            Below is the plot of the real time estimates of R-WAPG convergence bound using for the LASSO experiment. 
+            \begin{figure}[H]
+                \centering
+                \begin{subfigure}[b]{0.75\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{
+                        assets/lasso_rwapg_upperbnd_256.png
+                    }
+                \end{subfigure}
+                \caption{
+                    $N = 1024$, the upper bound estimates in real time from the collected $(\alpha_k)_{k \ge 0}$ sequence. 
+                }
+                \label{fig:single-lass-r-wapg-rwapg-upperbnd}
             \end{figure}

### 2025-09-15 Notebook LaTEX/R-WAPG/presentation-long.tex
>w<, changes

--- 2025-09-12 Notebook LaTEX/R-WAPG/presentation.tex
@@
 
+\AtBeginSection[]{
+  \begin{frame}
+  \vfill
+  \centering
+  \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
+    \usebeamerfont{title}\insertsectionhead\par%
+  \end{beamercolorbox}
+  \vfill
+  \end{frame}
+}
+
 % SLIDE INFORMATION ============================================================
-\author[Hongda Li]{Hongda Li\\ \vspace{1cm} \tiny{Joint work with Xianfu Wang}}
-\title[Thesis Proposal Talk]{
+
+\author[Hongda Li]{Hongda Li}
+
+\title{
     Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations
@@
 }
-\date{\today}
+\date[\today]{\today \\ \vspace{1cm} \tiny{Joint work with Shawn/Xianfu Wang}}
 \subject{Nesterov's acceleration and its applications}
@@
             \begin{enumerate}
-                \item When it's equal, as in the case of Nesterov's 1983, the convergence rate is the best. 
-                \item It's showed by Chambolle and Dossal in 2015 \cite{chambolle_convergence_2015} that the choice $(k + a -1)/a$ has weak convergence of iterates $(x_k)_{k \ge 0}$ for all $a > 2$, under the same assumption as before.
+                \item When it's equal, as in the case of Nesterov's 1983, it gives the best convergence rate for all convex functions. 
+                \item Showed by Chambolle and Dossal in 2015 \cite{chambolle_convergence_2015}, if we set the sequence $t_k = (k + a -1)/a$, then the iterates $(x_k)_{k \ge 0}$ has weak convergence in Hilbert space for all $a > 2$.
             \end{enumerate}
@@
         \begin{frame}{V-FISTA and strongly convex variants}
-            Fixing the momentum sequence gives an optimal convergence rate of the algorithm for the class of $F:\RR^n \rightarrow \RR$ that has 
+            Assume $F:\RR^n \rightarrow \RR$ that has:
             \begin{enumerate}
                 \item $L$ smooth gradient, 
-                \item and $\mu \ge 0$ strongly convexity. 
+                \item Strongly convex with $\mu > 0$. 
             \end{enumerate}
-            Available in Nesterov's book \cite{nesterov_lectures_2018} and Beck's book \cite{beck_first-order_2017} showed that if the sequence $(\theta_k)_{k\ge 0}$ has: 
+            In Nesterov's book \cite{nesterov_lectures_2018} and Beck's book \cite{beck_first-order_2017}, they showed that if $(\theta_k)_{k\ge 0}$ is:
             \begin{tcolorbox}
@@
             \begin{enumerate}
-                \item A linear convergence rate of $\mathcal O((1 - \sqrt{\mu/L})^k)$ for $(F(x_k) - F(x^+))_{k \ge 1}$. 
+                \item A linear convergence rate $\mathcal O((1 - \sqrt{\mu/L})^k)$ for $(F(x_k) - F(x^+))_{k \ge 1}$. 
             \end{enumerate}
@@
             \begin{assumption}[Convex smooth plus nonsmooth]
-                Let the ambient space be $\RR^n$ equipped with Euclidean inner product and norm. 
+                Let the ambient space be $\RR^n$, equipped with Euclidean inner product and norm. 
                 Define $F := f + g$.
@@
         \end{frame}
-        \begin{frame}{Our theoretical contributions, statement of results}
-            Here are the promises: 
+        \begin{frame}{Our theoretical contributions, and results}
             \begin{enumerate}
                 \item We relaxed the traditional choices of the sequence $(\theta_k)_{k \ge 1}$ to full extend to show that an upper bound for the sequence $(F(x_k) - F^+)_{k \ge 1}$ exists. 
-                \item We proposed a unified framework which we call ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)" that unifies the convergence theories for functions that are strongly convex or not necessarily strongly convex.
-                \item We demonstrate that the R-WAPG framework is equivalent to various representations of the Nesterov's type accelerated proximal gradient methods with Euclidean geometry in the literature.
+                \item We proposed a unified framework which we call ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)" that unifies the convergence theories for $f$ that is strongly convex and, convex but not necessarily strongly convex.
+                \item We demonstrate that the R-WAPG framework is equivalent to various other representations of the Nesterov's type accelerated proximal gradient in the literatures. 
             \end{enumerate}
-
         \end{frame}
-        \begin{frame}{Summarized results of our theoretical contributions}
+        \begin{frame}{Theoretical results summary}
             Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences. 
-            Suppose that $\alpha_0 \in (0, 1]$ and for all $k \ge 1$, $\alpha_k \in (\mu/L, 1)$ and define $(\rho_k)_{k\ge0 }$ by: 
+            Suppose that $\alpha_0 \in (0, 1]$ and for all $k \ge 1$, $\alpha_k \in (\mu/L, 1)$ and define $(\rho_k)_{k\ge0 }$ to be: 
             \begin{tcolorbox}\noindent\vspace{-1em}
@@
             \end{tcolorbox}
-            We can show Nesterov's type accelerated proximal gradient algorithm (or equivalently, FISTA with $g \equiv 0$) generates $(F(x_k) - F^+)_{k\ge 1}$ has an upper bound of: 
+            We can show Nesterov's type accelerated proximal gradient algorithm (or equivalently, FISTA with $g \equiv 0$) generates $(F(x_k) - F^+)_{k\ge 1}$ that has an upper bound of: 
             \begin{tcolorbox}\noindent\vspace{-1em} 
@@
         \end{frame}
-        \begin{frame}{Our convergence theory unifies variants in the literatures}
+        \begin{frame}{Unifying variants of FISTA in the literatures}
             Let's label 
@@
         \begin{frame}{A practical realization inspired by the theories}
-            Our theories stated that, the convergence of R-WAPG algorithm is ultimately described by the sequence $(\alpha_k)_{k \ge 0}$.
+            Our theories sugguest that, the upperbound for function value in the R-WAPG algorithm is ultimately described by the sequence $(\alpha_k)_{k \ge 0}$.
             \textbf{Taking this idea further, this is what we did in practice}: 
@@
                 We made the Free R-WAPG algorithm estimates the strong convexity $\mu$ constant through the Bregman Divergence at two successive iterates while the algorithm is running and put it into the sequence to run the algorithm.
-                \par
-                It's completely parameter free by equipping it with Armijo line search. 
             \end{tcolorbox}
@@
                 Assume $0 \le \mu < L$. 
-                Let $(\alpha_k)_{k \ge 0}$ be a sequence such that it satisfies: 
+                Let $(\alpha_k)_{k \ge 0}$ be such that: 
                 \begin{align*}
                     & \alpha_0 \in (0, 1], \\
-                    & \alpha_k \in (\mu/L, 1] \quad (\forall k \ge 1). 
+                    & \alpha_k \in (\mu/L, 1) \quad (\forall k \ge 1). 
                 \end{align*}    
-                Define $(\rho_k)_{k \ge 0}$ by 
+                Define $(\rho_k)_{k \ge 0}$
                 \begin{align*}
@@
             \end{definition}
+        \end{frame}
+        \begin{frame}{Proximal gradient, gradient mapping}
+            \begin{definition}[The proximal gradient operator]
+                Define for all $x\in \RR^n$: 
+                \begin{align*}
+                    T_L(y) 
+                    &:= \argmin_{x \in \RR^n} \left\lbrace
+                        g(x) + \langle \nabla f(y), x\rangle + L/2\Vert x - y\Vert^2
+                    \right\rbrace 
+                    \\
+                    &= \left(I + L^{-1}\partial g\right)^{-1}
+                    \left(I - L^{-1}\nabla f\right)(y),
+                    \\
+                    \mathcal G_L(y)
+                    &:= L(I - T_L)y.
+                \end{align*}
+            \end{definition}
+            Note, the $I$ here is the identity operator in $\RR^n$. 
+            $L > 0$ is the Lipschitz smoothness parameter for $f$. 
         \end{frame}
@@
         \begin{frame}{Convergence of R-WAPG}
-            After six pages of dense proof in the paper, we can deduce the following theorem: 
+            After six pages of math in the paper, we deduced the following theorem: 
             \begin{proposition}[R-WAPG convergence]\label{prop:wapg-convergence}
                 Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$.
-                Let vector sequence $(y_k, v_{k}, x_{k})_{k \ge 1}$ and R-WAPG sequences $\alpha_k, \rho_k$ be given by Definition \ref{def:wapg}.
-                % Let $\epsilon_k, y_k$ be given by Assumption \ref{ass:regret-gap}.
-                % Define $R_1 = 0$ and suppose that for $k = 1, 2, \ldots, N$, we have $R_k$ recursively given by:
-                % \begin{align*}
-                %     R_{k + 1}
-                %     :=
-                %     \frac{1}{2}\left(
-                %         L^{-1} - \frac{\alpha_k^2}{\hat \gamma_{k + 1}}
-                %     \right)\Vert g_k\Vert^2
-                %     +
-                %     (1 - \alpha_k)
-                %     \left(
-                %         \epsilon_k + R_k +
-                %         \frac{\mu\alpha_k\gamma_k}{2\hat \gamma_{k + 1}}
-                %         \Vert v_k - y_k\Vert^2
-                %     \right).
-                % \end{align*}
+                Let $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ be R-WAPG sequences.
+                Let vector sequences $(y_k, v_{k}, x_{k})_{k \ge 1}$ given by Definition \ref{def:wapg}. 
                 Then for all $k = 1, 2, \ldots, N$:
@@
 
-\section{Our paper is on arxiv and references}
+\section{references and draft on arxiv}
     \begin{frame}{Thanks for the participations. Merci pour les participations.}

### 2025-09-15 Notebook LaTEX/R-WAPG/presentation-short.tex
>w<, changes

--- 2025-09-15 Notebook LaTEX/R-WAPG/presentation-long.tex
@@
 
-\AtBeginSection[]{
-  \begin{frame}
-  \vfill
-  \centering
-  \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
-    \usebeamerfont{title}\insertsectionhead\par%
-  \end{beamercolorbox}
-  \vfill
-  \end{frame}
-}
+% --- Show a title page at the start of each section. 
+% \AtBeginSection[]{
+%   \begin{frame}
+%   \vfill
+%   \centering
+%   \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
+%     \usebeamerfont{title}\insertsectionhead\par%
+%   \end{beamercolorbox}
+%   \vfill
+%   \end{frame}
+% }
 
@@
         \end{frame}
-        \begin{frame}{Chambolle, Dossal}
-            Generalized by Beck \cite{beck_fast_2009-1} in 2009 is the FISTA algorithm for additive smooth and non-smooth objective. 
-            It's available in their proof that the sequence $(t_k)_{k}$ can be relaxed: 
+        \begin{frame}{Other choices for the momentum sequence}
+            Generalized by Beck \cite{beck_fast_2009-1} in 2009, called FISTA, it has $(t_k)_{k}$: 
             \begin{tcolorbox}\noindent\vspace{-1em}
@@
             \end{tcolorbox}
-            \begin{enumerate}
-                \item When it's equal, as in the case of Nesterov's 1983, it gives the best convergence rate for all convex functions. 
-                \item Showed by Chambolle and Dossal in 2015 \cite{chambolle_convergence_2015}, if we set the sequence $t_k = (k + a -1)/a$, then the iterates $(x_k)_{k \ge 0}$ has weak convergence in Hilbert space for all $a > 2$.
-            \end{enumerate}
-        \end{frame}
-        \begin{frame}{V-FISTA and strongly convex variants}
-            Assume $F:\RR^n \rightarrow \RR$ that has:
-            \begin{enumerate}
-                \item $L$ smooth gradient, 
-                \item Strongly convex with $\mu > 0$. 
-            \end{enumerate}
-            In Nesterov's book \cite{nesterov_lectures_2018} and Beck's book \cite{beck_first-order_2017}, they showed that if $(\theta_k)_{k\ge 0}$ is:
+            Chambolle and Dossal in 2015 \cite{chambolle_convergence_2015}, if $t_k = (k + a -1)/a$, then$(x_k)_{k \ge 0}$ has weak convergence in Hilbert space for all $a > 2$.
+            \par  
+            In Nesterov's book \cite{nesterov_lectures_2018} and Beck's book \cite{beck_first-order_2017} that if in addition, $F:\RR^n \rightarrow \RR$ is $L$ smooth gradient, with Strongly convex with $\mu > 0$, then $(\theta_k)_{k\ge 0}$:
             \begin{tcolorbox}
@@
             \end{tcolorbox}
-            Then the algorithm has
-            \begin{enumerate}
-                \item A linear convergence rate $\mathcal O((1 - \sqrt{\mu/L})^k)$ for $(F(x_k) - F(x^+))_{k \ge 1}$. 
-            \end{enumerate}
+            It gives $\mathcal O((1 - \sqrt{\mu/L})^k)$ convergence rate for $(F(x_k) - F(x^+))_{k \ge 1}$. 
         \end{frame}
     \subsection{Our discoveries and inspirations}
+        \begin{frame}{A major question}
+            This is a question that lead our investigation: 
+            \begin{tcolorbox}
+                How much can we relax the choice of the sequence $\theta_k$ and still get an upper bound for the convergence rate? 
+            \end{tcolorbox}
+        \end{frame}
         \begin{frame}{The assumptions we make throughout}
@@
             \textbf{This assumption the full scope of the theoretical and practical discussion, assume it throughout.}
-        \end{frame}
-        \begin{frame}{Our theoretical contributions, and results}
-            \begin{enumerate}
-                \item We relaxed the traditional choices of the sequence $(\theta_k)_{k \ge 1}$ to full extend to show that an upper bound for the sequence $(F(x_k) - F^+)_{k \ge 1}$ exists. 
-                \item We proposed a unified framework which we call ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)" that unifies the convergence theories for $f$ that is strongly convex and, convex but not necessarily strongly convex.
-                \item We demonstrate that the R-WAPG framework is equivalent to various other representations of the Nesterov's type accelerated proximal gradient in the literatures. 
-            \end{enumerate}
         \end{frame}
@@
             Our theories sugguest that, the upperbound for function value in the R-WAPG algorithm is ultimately described by the sequence $(\alpha_k)_{k \ge 0}$.
-            \textbf{Taking this idea further, this is what we did in practice}: 
+            \textbf{Taking this idea further, this is what we did for numerical experiments}: 
             \begin{tcolorbox}
-                We made the Free R-WAPG algorithm estimates the strong convexity $\mu$ constant through the Bregman Divergence at two successive iterates while the algorithm is running and put it into the sequence to run the algorithm.
+                We made a Free R-WAPG algorithm which estimates the strong convexity constant $\mu$ through the Bregman Divergence at two successive iterates while the algorithm is running and, we check the upper bound using our convergence theory.
             \end{tcolorbox}
@@
         \begin{frame}{The R-WAPG sequences}
+            In this section, we highlight key theoretical results that allowed us to unify convergence rate for various variants of FISTA in the literature.
             \begin{definition}{R-WAPG sequences}\label{def:rwapg-seq}
@@
                 Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}.
-                The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for $k\ge 1$ by the procedures:
-                \begin{tcolorbox}
-                    For $k=1, 2, 3, \ldots$
+                The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for all $k\ge 1$ by such that:
+                \begin{tcolorbox}\vspace{-1em}
                     \begin{align*}
@@
                         \\
-                        \hat \gamma_{k + 1} & \defeq (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2,
+                        L\alpha_k^2 &= (1 - \alpha_k)\gamma_k + \mu \alpha_k, 
                         \\
-                        y_k &\defeq
+                        \hat \gamma_{k + 1} & \defeq L\alpha_k^2,
+                        \\
+                        y_k &=
                         (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k),
                         \\
-                        g_k &\defeq \mathcal G_L (y_k),
+                        g_k &= \mathcal G_L (y_k),
                         \\
-                        v_{k + 1} &\defeq
+                        v_{k + 1} &=
                         \hat\gamma^{-1}_{k + 1}
@@
                         \\
-                        x_{k + 1} &\defeq T_L y_k.
+                        x_{k + 1} &= T_L y_k.
                     \end{align*}
@@
             \end{proposition}
-            To use this theorem for the convergence of existing variants of Accelerated Proximal Gradient in the literature, we need alternative representations of R-WAPG that make it similar to what appears in the literature.
+            To use this theorem for the convergence of existing variants of Accelerated Proximal gradient method, we need alternative representations of R-WAPG to fit what commonly appears in the literature.
         \end{frame}
     \subsection{Different representation of accelerated proximal gradient}
-        \begin{frame}{The intermediate form}
-            \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}
+        \begin{frame}{Iterates by R-WAPG has other representations}
+            \begin{proposition}[Alternative representations of the iterates]\label{prop:wapg-first-equivalent-repr}
+                If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}),
+                then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$, and they satisfy for all $k\ge 1$: 
                 {\footnotesize
-                Assume $\mu < L$ and let $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}.
-                Initialize any $x_1, v_1$ in $\RR^n$.
-                For $k \ge 1$, the algorithm generates sequence of vector iterates $(y_{k}, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by the procedures:
-                \begin{tcolorbox}
-                    For $k = 1, 2, \ldots$
-                    \begin{align*}
-                        & y_{k} \defeq
-                        \left(
-                            1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
-                        \right)^{-1}
-                        \left(
-                            v_{k} +
-                            \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
-                        \right),
-                        \\
-                        & x_{k + 1} \defeq
-                        y_k - L^{-1} \mathcal G_L (y_k),
-                        \\
-                        & v_{k + 1} \defeq
-                        \left(
-                            1 + \frac{\mu}{L \alpha_k - \mu}
-                        \right)^{-1}
-                        \left(
-                            v_k +
-                            \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
-                        \right) - \frac{1}{L\alpha_{k}}\mathcal G_L (y_k).
-                    \end{align*}
-                \end{tcolorbox}
-                }
-            \end{definition}
-            The closest algorithm that fits the form but with $\mu = 0$ is Chapter 12 of in Ryu and Yin's Book \cite{ryu_large-scale_2022}, right after Theorem 17. 
-        \end{frame}
-        \begin{frame}{Intermediate form equivalency}
-            \begin{proposition}[R-WAPG is equivalent to intermediate form]\label{prop:wapg-first-equivalent-repr}
-                If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}),
-                then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$,  namely, for all $k\ge 1$,
                 \begin{align}
-                    & y_{k} =
-                    \left(
-                        1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
-                    \right)^{-1}
-                    \left(
-                        v_{k} +
-                        \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
-                    \right), 
-                    % \label{eqn:rwapg-first-equiv-form-eqn-1}
-                    \\
-                    & x_{k + 1} =
-                    y_k - L^{-1} \mathcal G_L (y_k),
-                    \\
-                    & v_{k + 1} =
-                    \left(
-                        1 + \frac{\mu}{L \alpha_k - \mu}
-                    \right)^{-1}
-                    \left(
-                        v_k +
-                        \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
-                    \right) - \frac{1}{L\alpha_{k}}\mathcal G_L (y_k).
-                    % \label{eqn:rwapg-first-equiv-form-eqn-2}
-                \end{align}
-            \end{proposition}
-        \end{frame}
-        \begin{frame}{Similar triangle form}
-            \begin{proposition}[R-WAPG is equivalent to similar triangle form]\label{prop:wagp-st-form}
-                Let iterates $(y_k, x_{k}, v_{k})_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge 0}$ be given by Definition \ref{def:r-wapg-intermediate}.
-                Then for all $k \ge 1$, iterates $y_k, x_{k + 1}, v_{k + 1}$
-                satisfy:
-                \begin{align}
+                    & \begin{aligned}
                         y_{k} &=
@@
                             \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
-                    \right),
-                    \label{eqn:rwapg-st-form-eqn-1}
+                        \right)
                         \\
-                    x_{k + 1} &=
+                        &= x_{k + 1} +
+                        \frac{\rho_k\alpha_k(1 - \alpha_k)}
+                        {\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k), 
+                    \end{aligned}
+                    % \label{eqn:rwapg-first-equiv-form-eqn-1}
+                    \\
+                    & x_{k + 1} =
                     y_k - L^{-1} \mathcal G_L (y_k),
                     \\
-                    v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k).
-                    \label{eqn:rwapg-st-form-eqn-3}
+                    & \begin{aligned}
+                        v_{k + 1} 
+                        &=
+                        \left(
+                            1 + \frac{\mu}{L \alpha_k - \mu}
+                        \right)^{-1}
+                        \left(
+                            v_k +
+                            \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
+                        \right) - \frac{1}{L\alpha_{k}}\mathcal G_L (y_k)
+                        \\
+                        &= 
+                        x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k).
+                    \end{aligned}
                 \end{align}
+                }
             \end{proposition}
-            Combining both of these representations, we can draw a similar triangle. 
-        \end{frame}
-        \begin{frame}{Similar triangle form illustration Part I}
-            To understand the name ``similar triangle form" for it in the literature, we draw it out. 
-            Write $\tau_k = \frac{L - L\alpha_k}{L\alpha_k - \mu}$ so $y_k = (1 + \tau_k)^{-1}(v_k + \tau_k x_k)$ from the similar triangle form. 
-            The R-WAPG sequence has $\alpha_k \in (\mu/L, 1)$ for all $k \ge 1$, so it has: 
-            \begin{tcolorbox}
-                \begin{figure}
-                    \centering
-                    \includegraphics[width=15em]{assets/st_part1.png}
-                \end{figure}
-            \end{tcolorbox}
-        \end{frame}
-        \begin{frame}{Similar triangle form illustration part II}
-            Then $x_{k + 1} = y_k - L^{-1}\mathcal G_L(y_k)$ hence it has 
-            \begin{tcolorbox}
-                \begin{figure}
-                    \centering
-                    \includegraphics[width=15em]{assets/st_part2.png}
-                \end{figure}
-            \end{tcolorbox}
-        \end{frame}
-        \begin{frame}{Similar triangle form illustration part III}
-            Recall that $v_{k + 1} = x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k)$, so $v_{k + 1}$ is on the line defined by $x_{k + 1} - x_k$, and it looks like: 
-            \begin{tcolorbox}
-                \begin{figure}
-                    \includegraphics[width=15em]{assets/st_part3.png}
-                \end{figure}
-            \end{tcolorbox}
-            Let $\xi_k = \mu(L\alpha_k - \mu)^{-1}$, the intermediate form it has $v_{k+1} = (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - L^{-1}\alpha_k^{-1} \mathcal G_L(y_k)$, hence the gray line. 
-        \end{frame}
-        \begin{frame}{Similar triangle form is equivalent to the momentum form}
-            \begin{proposition}[Momentum form]\label{prop:r-wapg-momentum-repr}
-                Let sequence $(\alpha_k, \rho_k)_{k \ge 0}$ and iterates $(x_k, v_k, y_k)_{k\ge 1}$ be given by the R-WAPG intermediate form.
-                Then it has:
-                \begin{enumerate}
-                    \item[(i)] For all $k \ge 1$, the iterates $x_{k + 1}, y_{k + 1}$ satisfy:
-                    \begin{align*}
-                        x_{k + 1} &= y_k - L^{-1}\mathcal G_L (y_k),
-                        \\
-                        y_{k + 1} &=
-                        x_{k + 1} +
-                        \frac{\rho_k\alpha_k(1 - \alpha_k)}
-                        {\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k).
-                    \end{align*}
-                    \item[(ii)] $v_1 = x_1$ if and only if $y_1 = x_1$.
-                    \item[(iii)] If in addition $\mu = 0$, then the momentum term in (i) admits a simpler representation:
+            If $\mu = 0$, then it simplifies:
             \begin{align*}
@@
             \end{align*}
-                \end{enumerate}
-            \end{proposition}
         \end{frame}
@@
         \end{frame}
+
 \section{Adaptive momentum sequence and numerical experiments}
@@
         \begin{frame}{Experiment results 1}
-            A realization of $x_0 \sim \mathcal N(I, \mathbf 0)$ is used for each trial for all algorithms. 
-            Each trial results of V-FISTA, M-FISTA (Monotone restarted FISTA) and Free R-WAPG were collected. 
-            We plot the medium, minimum, and maximum of $\delta_k$: 
+            A realization of $x_0 \sim \mathcal N(I, \mathbf 0)$ is used for V-FISTA, M-FISTA (Monotone restarted FISTA) and Free R-WAPG. 
+            Below are plots of the medium, minimum, and maximum of $\delta_k$: 
             \begin{figure}[H]
@@
                 \end{subfigure}
-                \hfill
                 \begin{subfigure}[b]{0.47\textwidth}

### 2025-09-18 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, a lot of changes

@@
     Using the above assumption, in this section, we can build up to Lemma \ref{lemma:cnvg-prep-part3}. 
-    The lemma is crucially important and it gives us the an inequality on what happen between iterates $x_{k}, v_{k}$ and $v_{k - 1}, x_{k - 1}$ generated by algorithm satisfying Definition \ref{def:st-apg}.
+    The lemma is crucially important and, it gives us the inequality on what happen between iterates $x_{k}, v_{k}$ and $v_{k - 1}, x_{k - 1}$ generated by algorithm satisfying Definition \ref{def:st-apg}.
     % LEMMA ========================================================================================================

### 2025-09-18 Notebook LaTEX/R-WAPG/2025-06-10-00-paper.tex
>w<, changes

@@
         \end{align*}
-        Finally, since $\mu = 0$, Propisition \ref{prop:r-wapg-momentum-repr} applies with the momentum term simplifies into $\alpha_{k + 1}(\alpha_k^{-1} - 1)$. 
+        Finally, since $\mu = 0$, Proposition \ref{prop:r-wapg-momentum-repr} applies with the momentum term simplifies into $\alpha_{k + 1}(\alpha_k^{-1} - 1)$. 
     }
@@
                 \end{subfigure}
-                \caption{A single LASSO experiment results, with $M = 64, N=256$. f}
+                \caption{A single LASSO experiment results, with $M = 64, N=256$.}
                 \label{fig:single-lass-mu-estimates}

### 2025-09-18 Notebook LaTEX/R-WAPG/presentation-shorter.tex
>w<, changes

--- 2025-09-15 Notebook LaTEX/R-WAPG/presentation-short.tex
@@
 \setbeamertemplate{navigation symbols}{} 
+\setbeamertemplate{itemize subitem}{$\circ$}
 % \setbeamercolor{block title}{bg=cyan,fg=black}  % CHANGE THE BLOCK STYLE IN BEAMER. 
@@
 \section{Introduction and background}
-    \subsection{Motivations}
     \begin{frame}{Nesterov's accelerated gradient in 1983}
-            Let's recall a classic. 
         \begin{block}{Nesterov's accelerated gradient in 1983}
@@
         \end{block}
-            If $F$ is convex and has $L$ Lipschitz smooth gradient and a minimizer $x^+$ exists. 
+        When $F$ is convex and, $L$ Lipschitz smooth. 
+        If minimizer $x^+$ exists, then: 
         Then it has
@@
     \end{frame}
-        \begin{frame}{Other choices for the momentum sequence}
-            Generalized by Beck \cite{beck_fast_2009-1} in 2009, called FISTA, it has $(t_k)_{k}$: 
-            \begin{tcolorbox}\noindent\vspace{-1em}
-                \begin{align*}
-                    (\forall k \ge 1)\quad t_k (t_k - 1) &\le t_{k - 1}^2. 
-                \end{align*}    
+    \begin{frame}{Choices of momentum parameters $t_k, \theta_k$}
+        \begin{block}{Here are prominent results in the literature}
+            \begin{itemize}
+                \item Beck, Teboulle 2009 \cite{beck_fast_2009}, the FISTA paper: $t_k (t_k - 1) \le t_{k - 1}^2$. 
+                    \begin{itemize}
+                        \item $(F(x_k) - F(x^+))_{k \ge 0}$ converges at rate $\mathcal O(1/k^2)$ when $t_k(t_k - 1) = t_{k - 1}^2$. 
+                        \item $\theta_k$ admits no closed form. 
+                    \end{itemize}
+                \item Chambolle and Dossal 2015 \cite{chambolle_convergence_2015}: $t_k = (k + a -1)/a$ with $a > 2$. 
+                    \begin{itemize}
+                        \item Retains convergence rate $\mathcal O(1/k^2)$ with $\theta_{k} = \frac{k - 2}{k + a - 1}$. 
+                        \item Iterates has weak convergence in Hilbert space. 
+                    \end{itemize}
+                \item Nesterov \cite{nesterov_lectures_2018} and, Beck \cite{beck_first-order_2017}
+                : $\theta_k = \frac{\sqrt{L/\mu} - 1}{\sqrt{L/\mu} + 1}$.
+                    \begin{itemize}
+                        \item Converges at rate $\mathcal O\left(\left(1 - \sqrt{\mu/L}\right)^k\right)$, if $f$ is also $\mu$ strongly convex with $\mu > 0$. 
+                    \end{itemize}
+                \item Apidopoulos et al. 2018 \cite{apidopoulos_convergence_2018}: $\theta_k = \frac{n}{n + b}$ for $b \in (0, 3)$. 
+                \begin{itemize}
+                    \item Has convergence rate $\mathcal O(1/k^{2b/3})$. 
+                \end{itemize}
+            \end{itemize}    
+        \end{block}
+    \end{frame}
+    \begin{frame}{A major question}
+        The following question lead our investigation: 
+        \begin{tcolorbox}
+            How much can we relax the choice of $\theta_k, t_k$ and still get an upper bound for the convergence rate? 
         \end{tcolorbox}
-            Chambolle and Dossal in 2015 \cite{chambolle_convergence_2015}, if $t_k = (k + a -1)/a$, then$(x_k)_{k \ge 0}$ has weak convergence in Hilbert space for all $a > 2$.
-            \par  
-            In Nesterov's book \cite{nesterov_lectures_2018} and Beck's book \cite{beck_first-order_2017} that if in addition, $F:\RR^n \rightarrow \RR$ is $L$ smooth gradient, with Strongly convex with $\mu > 0$, then $(\theta_k)_{k\ge 0}$:
-            \begin{tcolorbox}
-                \begin{align*}
-                   \theta_k = \frac{\sqrt{L/\mu} - 1}{\sqrt{L/\mu} + 1}. 
-                \end{align*}
-            \end{tcolorbox}
-            It gives $\mathcal O((1 - \sqrt{\mu/L})^k)$ convergence rate for $(F(x_k) - F(x^+))_{k \ge 1}$. 
+        We proposed a framework called Relaxed, Weak Accelerated Proximal Gradient (R-WAPG) and, these are what we did: 
+        \begin{itemize}
+            \item An upper bound of function value with the weakest assumption on momentum parameter.
+            \item A unified analysis with strong convexity $\mu \ge 0$. 
+            \item Various equivalent representation of R-WAPG are given and, convergence results varified for examples in the literature. 
+            \item Numerical experiments are conducted to verify the theory. 
+        \end{itemize}
     \end{frame}
-    \subsection{Our discoveries and inspirations}
-        \begin{frame}{A major question}
-            This is a question that lead our investigation: 
-            \begin{tcolorbox}
-                How much can we relax the choice of the sequence $\theta_k$ and still get an upper bound for the convergence rate? 
-            \end{tcolorbox}
-        \end{frame}
+
+\section{The R-WAPG Framework}
     \begin{frame}{The assumptions we make throughout}
@@
     \end{frame}
-        \begin{frame}{Theoretical results summary}
-            Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences. 
-            Suppose that $\alpha_0 \in (0, 1]$ and for all $k \ge 1$, $\alpha_k \in (\mu/L, 1)$ and define $(\rho_k)_{k\ge0 }$ to be: 
-            \begin{tcolorbox}\noindent\vspace{-1em}
+    \begin{frame}{Proximal gradient, gradient mapping}
+        \begin{definition}[The proximal gradient operator]
+            Define for all $x\in \RR^n$: 
             \begin{align*}
-                    \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0).
+                T_L(y) 
+                &:= \argmin_{x \in \RR^n} \left\lbrace
+                    g(x) + \langle \nabla f(y), x\rangle + L/2\Vert x - y\Vert^2
+                \right\rbrace 
+                \\
+                &= \left(I + L^{-1}\partial g\right)^{-1}
+                \left(I - L^{-1}\nabla f\right)(y),
+                \\
+                \mathcal G_L(y)
+                &:= L(I - T_L)y.
+            \end{align*}
+        \end{definition}
+        Note, the $I$ here is the identity operator in $\RR^n$. 
+        $L > 0$ is the Lipschitz smoothness parameter for $f$. 
+    \end{frame}
+    \begin{frame}{The R-WAPG sequences}
+        In this section, we highlight key theoretical results that allowed us to unify convergence rate for various variants of FISTA in the literature.
+        \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}
+            Assume $0 \le \mu < L$. 
+            Let $(\alpha_k)_{k \ge 0}$ be such that: 
+            \begin{align*}
+                & \alpha_0 \in (0, 1], \\
+                & \alpha_k \in (\mu/L, 1) \quad (\forall k \ge 1). 
+            \end{align*}    
+            Define $(\rho_k)_{k \ge 0}$
+            \begin{align*}
+                \rho_k := \frac{\alpha_{k + 1}^2 - (\mu/L) \alpha_{k + 1}}{
+                    (1 - \alpha_{k + 1}) \alpha_k^2.
+                }
+            \end{align*}
+            We call the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ the R-WAPG sequences. 
+        \end{definition}
+    \end{frame}
+    \begin{frame}{R-WAPG}
+        \begin{definition}[R-WAPG]\label{def:wapg}
+            Choose any $x_1 \in \RR^n, v_1 \in \RR^n$.
+            Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}.
+            The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for all $k\ge 1$ by such that:
+            \begin{tcolorbox}\vspace{-1em}
+                \begin{align*}
+                    \gamma_k &\defeq \rho_{k -1}L\alpha_{k - 1}^2,
+                    \\
+                    L\alpha_k^2 &= (1 - \alpha_k)\gamma_k + \mu \alpha_k, 
+                    \\
+                    \hat \gamma_{k + 1} & \defeq L\alpha_k^2,
+                    \\
+                    y_k &=
+                    (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k),
+                    \\
+                    g_k &= \mathcal G_L (y_k),
+                    \\
+                    v_{k + 1} &=
+                    \hat\gamma^{-1}_{k + 1}
+                    (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k),
+                    \\
+                    x_{k + 1} &= T_L y_k.
                 \end{align*}
             \end{tcolorbox}
-            We can show Nesterov's type accelerated proximal gradient algorithm (or equivalently, FISTA with $g \equiv 0$) generates $(F(x_k) - F^+)_{k\ge 1}$ that has an upper bound of: 
-            \begin{tcolorbox}\noindent\vspace{-1em} 
+        \end{definition}
+    \end{frame}
+
+\section{Our Theoretical Results}
+    \begin{frame}{Iterates by R-WAPG has other representations}
+        \begin{proposition}[Alternative representations of the iterates]\label{prop:wapg-first-equivalent-repr}
+            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}),
+            Then they satisfy for all $k\ge 1$: 
+            {\footnotesize
+            \begin{align}
+                & \begin{aligned}
+                    y_{k} &=
+                    \left(
+                        1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
+                    \right)^{-1}
+                    \left(
+                        v_{k} +
+                        \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
+                    \right)
+                    \\
+                    &= x_{k + 1} +
+                    \frac{\rho_k\alpha_k(1 - \alpha_k)}
+                    {\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k), 
+                \end{aligned}
+                % \label{eqn:rwapg-first-equiv-form-eqn-1}
+                \\
+                & x_{k + 1} =
+                y_k - L^{-1} \mathcal G_L (y_k),
+                \\
+                & \begin{aligned}
+                    v_{k + 1} 
+                    &=
+                    \left(
+                        1 + \frac{\mu}{L \alpha_k - \mu}
+                    \right)^{-1}
+                    \left(
+                        v_k +
+                        \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
+                    \right) - \frac{1}{L\alpha_{k}}\mathcal G_L (y_k)
+                    \\
+                    &= 
+                    x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k).
+                \end{aligned}
+            \end{align}
+            }
+        \end{proposition}
+        If $\mu = 0$, then it simplifies:
+        {\small
         \begin{align*}
-                    \mathcal O\left(
+            (\forall k \ge 1) \quad
+            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
+            & = \alpha_{k + 1}(\alpha_k^{-1} - 1).
+        \end{align*}
+        }
+    \end{frame}
+    \begin{frame}{Convergence of R-WAPG}
+        After six pages of math in the paper, we deduced the following theorem: 
+        \begin{proposition}[R-WAPG convergence]\label{prop:wapg-convergence}
+            Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$.
+            Let $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ be R-WAPG sequences.
+            Let vector sequences $(y_k, v_{k}, x_{k})_{k \ge 1}$ given by Definition \ref{def:wapg}. 
+            Then for all $k = 1, 2, \ldots, N$:
+            {\small
+            \begin{align*}
+                & F(x_{k + 1}) - F(x^*) + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
+                \\
+                &\le
                 \left(
@@
                 \right)
+                \left(
                     \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
+                \right)
+                \left(
+                    F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
                 \right).
             \end{align*}
-            \end{tcolorbox}
+            }
+        \end{proposition}
+        To use this theorem for the convergence of existing variants of Accelerated Proximal gradient method, we need alternative representations of R-WAPG to fit what commonly appears in the literature.
     \end{frame}
@@
     \end{frame}
-        \begin{frame}{A practical realization inspired by the theories}
-            Our theories sugguest that, the upperbound for function value in the R-WAPG algorithm is ultimately described by the sequence $(\alpha_k)_{k \ge 0}$.
-            \textbf{Taking this idea further, this is what we did for numerical experiments}: 
-            \begin{tcolorbox}
-                We made a Free R-WAPG algorithm which estimates the strong convexity constant $\mu$ through the Bregman Divergence at two successive iterates while the algorithm is running and, we check the upper bound using our convergence theory.
-            \end{tcolorbox}
-        \end{frame}
-
-\section{The R-WAPG framework and convergence rate}
-    \subsection{Introducing the R-WAPG framework}
-        \begin{frame}{The R-WAPG sequences}
-            In this section, we highlight key theoretical results that allowed us to unify convergence rate for various variants of FISTA in the literature.
-            \begin{definition}{R-WAPG sequences}\label{def:rwapg-seq}
-                Assume $0 \le \mu < L$. 
-                Let $(\alpha_k)_{k \ge 0}$ be such that: 
-                \begin{align*}
-                    & \alpha_0 \in (0, 1], \\
-                    & \alpha_k \in (\mu/L, 1) \quad (\forall k \ge 1). 
-                \end{align*}    
-                Define $(\rho_k)_{k \ge 0}$
-                \begin{align*}
-                    \rho_k := \frac{\alpha_{k + 1}^2 - (\mu/L) \alpha_{k + 1}}{
-                        (1 - \alpha_{k + 1}) \alpha_k^2.
-                    }
-                \end{align*}
-                We call the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ the R-WAPG sequences. 
-            \end{definition}
-        \end{frame}
-        \begin{frame}{Proximal gradient, gradient mapping}
-            \begin{definition}[The proximal gradient operator]
-                Define for all $x\in \RR^n$: 
-                \begin{align*}
-                    T_L(y) 
-                    &:= \argmin_{x \in \RR^n} \left\lbrace
-                        g(x) + \langle \nabla f(y), x\rangle + L/2\Vert x - y\Vert^2
-                    \right\rbrace 
-                    \\
-                    &= \left(I + L^{-1}\partial g\right)^{-1}
-                    \left(I - L^{-1}\nabla f\right)(y),
-                    \\
-                    \mathcal G_L(y)
-                    &:= L(I - T_L)y.
-                \end{align*}
-            \end{definition}
-            Note, the $I$ here is the identity operator in $\RR^n$. 
-            $L > 0$ is the Lipschitz smoothness parameter for $f$. 
-        \end{frame}
-        \begin{frame}{R-WAPG}
-            \begin{definition}[relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
-                Choose any $x_1 \in \RR^n, v_1 \in \RR^n$.
-                Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}.
-                The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for all $k\ge 1$ by such that:
-                \begin{tcolorbox}\vspace{-1em}
-                    \begin{align*}
-                        \gamma_k &\defeq \rho_{k -1}L\alpha_{k - 1}^2,
-                        \\
-                        L\alpha_k^2 &= (1 - \alpha_k)\gamma_k + \mu \alpha_k, 
-                        \\
-                        \hat \gamma_{k + 1} & \defeq L\alpha_k^2,
-                        \\
-                        y_k &=
-                        (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k),
-                        \\
-                        g_k &= \mathcal G_L (y_k),
-                        \\
-                        v_{k + 1} &=
-                        \hat\gamma^{-1}_{k + 1}
-                        (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k),
-                        \\
-                        x_{k + 1} &= T_L y_k.
-                    \end{align*}
-                \end{tcolorbox}
-            \end{definition}
-        \end{frame}
-        \begin{frame}{Convergence of R-WAPG}
-            After six pages of math in the paper, we deduced the following theorem: 
-            \begin{proposition}[R-WAPG convergence]\label{prop:wapg-convergence}
-                Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$.
-                Let $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ be R-WAPG sequences.
-                Let vector sequences $(y_k, v_{k}, x_{k})_{k \ge 1}$ given by Definition \ref{def:wapg}. 
-                Then for all $k = 1, 2, \ldots, N$:
-                {\small
-                \begin{align*}
-                    & F(x_{k + 1}) - F(x^*) + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
-                    \\
-                    &\le
-                    \left(
-                        \prod_{i = 0}^{k - 1} \max(1, \rho_{i})
-                    \right)
-                    \left(
-                        \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
-                    \right)
-                    \left(
-                        F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
-                    \right).
-                \end{align*}
-                }
-            \end{proposition}
-            To use this theorem for the convergence of existing variants of Accelerated Proximal gradient method, we need alternative representations of R-WAPG to fit what commonly appears in the literature.
-        \end{frame}
-    \subsection{Different representation of accelerated proximal gradient}
-        \begin{frame}{Iterates by R-WAPG has other representations}
-            \begin{proposition}[Alternative representations of the iterates]\label{prop:wapg-first-equivalent-repr}
-                If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}),
-                then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$, and they satisfy for all $k\ge 1$: 
-                {\footnotesize
-                \begin{align}
-                    & \begin{aligned}
-                        y_{k} &=
-                        \left(
-                            1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
-                        \right)^{-1}
-                        \left(
-                            v_{k} +
-                            \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
-                        \right)
-                        \\
-                        &= x_{k + 1} +
-                        \frac{\rho_k\alpha_k(1 - \alpha_k)}
-                        {\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k), 
-                    \end{aligned}
-                    % \label{eqn:rwapg-first-equiv-form-eqn-1}
-                    \\
-                    & x_{k + 1} =
-                    y_k - L^{-1} \mathcal G_L (y_k),
-                    \\
-                    & \begin{aligned}
-                        v_{k + 1} 
-                        &=
-                        \left(
-                            1 + \frac{\mu}{L \alpha_k - \mu}
-                        \right)^{-1}
-                        \left(
-                            v_k +
-                            \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
-                        \right) - \frac{1}{L\alpha_{k}}\mathcal G_L (y_k)
-                        \\
-                        &= 
-                        x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k).
-                    \end{aligned}
-                \end{align}
-                }
-            \end{proposition}
-            If $\mu = 0$, then it simplifies:
-            \begin{align*}
-                (\forall k \ge 1) \quad
-                \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
-                & = \alpha_{k + 1}(\alpha_k^{-1} - 1).
-            \end{align*}
-        \end{frame}
-    \subsection{Unifying different variants of accelerated proximal gradient}
-        \begin{frame}{Convergence of Chambolle and Dossal variant of FISTA}
-            FISTA algorithm proposed in Chambolle and Dossal \cite{chambolle_convergence_2015} has a function value convergence fully described by Proposition \ref{prop:wapg-convergence}. 
-            \begin{lemma}[R-WAPG sequence as inverted FISTA sequence]\label{lemma:inverted-fista-seq}
-                Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}.
-                If $\mu = 0, \rho_k \ge 1\; \forall k \ge 0$, and $\alpha_0 = 1$, then:
-                \begin{enumerate}
-                    \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$.
-                    \item Let $t_k := \alpha_k^{-1}$, then $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``inverted FISTA sequence''.
-                    \item $\prod_{i = 1}^k\max(1, \rho_{k - 1})(1 - \alpha_k) = \alpha_k^2 \quad (\forall k \ge 1)$.
-                \end{enumerate}
-            \end{lemma}
-            Let $\alpha_k = a/(k + 1)$, $a \ge 2$, Applying Proposition \ref{prop:wapg-convergence} yields $\mathcal O(1/k^2)$ convergence rate of $(F(x_k) - F^+)_{k \ge 1}$ after some algebra routine.
-        \end{frame}
-        \begin{frame}{In addition, our theory made a new prediction}
-            \begin{theorem}[fixed momentum APG]\label{thm:fixed-momentum-fista}
-                {\small
-                Assume $L > \mu > 0$, let a pair of constant R-WAPG sequence: $(\alpha_k)_{k \ge0}$ is a constant and $\alpha_k \in (\mu/L, 1)$ for all $k \ge 0$.
-                Define $q := \mu/L$ and for any fixed $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, represent $\alpha_k = \alpha = r \sqrt{q}$. 
-                Consider the algorithm with a constant momentum specified by the following:
-                \begin{tcolorbox}
-                    Define $\theta = \left(1 - r^{-1}\sqrt{q}\right)(1 - r\sqrt{q})(1 - q)^{-1}$.
-                    \\
-                    Initialize $y_1 = x_1$; for $k = 1, 2, \ldots, N$, update:
-                    \begin{align*}
-                        &x_{k + 1} = y_k + L^{-1}\mathcal G_L (y_k)
-                        ,
-                        \\
-                        & y_{k + 1} = x_{k + 1} + \theta(x_{k + 1} - x_k).
-                    \end{align*}
-                \end{tcolorbox}
-                Then the algorithm generates $(x_k)_{k \ge 1}$ such that $(F(x_{k}) - F(x^*))_{k\geq 1}$ converges at a rate of $\mathcal O\left(\left(1 - \min\left(\mu/(\alpha L), \alpha\right)\right)^k\right)$.
-                }
-            \end{theorem}
-        \end{frame}
 
 \section{Adaptive momentum sequence and numerical experiments}
-    \subsection{Free R-WAPG}
     \begin{frame}{Introducing numerical experiments}
@@
     \end{frame}
-    \subsection{Numerical experiment, simple quadratic}
     \begin{frame}{A basic experiment on convex quadratic functions}
@@
     \end{frame}
-    \subsection{Numerical experiment, LASSO}
-        \begin{frame}{The LASSO problem}
-            The problem of LASSO from Tibshirani \cite{tibshirani_regression_1996} is the optimization problem $\min_{x \in \RR^n}\{(1/2)\Vert Ax - b\Vert^2 - \lambda\Vert x\Vert_1\}$. 
-            \begin{enumerate}
-                \item $A \in \RR^{N \times N}$, full of i.i.d random variable from a standard normal distribution. 
-                \item Computed in prior, $L, \mu$ are parameters estimated by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$. The norm is the spectral norm. 
-                \item The smallest value of $F(x_k)$, for all algorithms, over all tries are taken as an estimate of $F^+$. 
-            \end{enumerate}
-        \end{frame}
-        \begin{frame}{Results plotted}
-            With $A\in \RR^{N\times N}$ fixed, for each $x_0 \sim \mathcal N(I, \mathbf 0)$ realized, 30 experiments are preformed and the medium, minimum and maximum of $\delta_k$ are recorded for M-FISTA, Free R-WAPG, and V-FISTA.
-            \begin{figure}[H]
-                \begin{subfigure}[b]{0.47\textwidth}
-                    \centering
-                    \includegraphics[width=\textwidth]{assets/lasso_batched_statistics_64-256.png}
-                    \caption{LASSO experiment with $M = 64, N = 256$. Plots of minimum, maximum, and median $\delta_k$ with estimated $F^*$. }
-                \end{subfigure}
-                \begin{subfigure}[b]{0.47\textwidth}
-                    \centering
-                    \includegraphics[width=\textwidth]{assets/lasso_batched_statistics_64-128.png}
-                    \caption{LASSO experiment with $M = 64, N = 128$. Plots of minimum, maximum, and median $\delta_k$ with estimated $F^*$. }
-                \end{subfigure}
-                \caption{LASSO experiments statistics for test algorithms. }
-                \label{fig:batched-lasso}
-            \end{figure}
-        \end{frame}
-        \begin{frame}{Estimates of strong convexity constant}
-            The parameters in this specific trial are $\mu = 7.432363627613958\times 10^{-18}$ and $L = 2321.737206983643$. 
-            \begin{figure}[H]
-                \begin{subfigure}[b]{0.47\textwidth}
-                    \includegraphics[width=\textwidth]{assets/lasso_loss_256.png}
-                    \caption
-                    {A single run of LASSO experiment displaying $F(x_k) - F^*$ for several test algorithms.
-                    }
-                \end{subfigure}
-                \begin{subfigure}[b]{0.47\textwidth}
-                    \includegraphics[width=\textwidth]{assets/lasso_sc_estimates_256.png}
-                    \caption{The $\mu_k$ estimated by FR-WAPG for one LASSO experiment. }
-                \end{subfigure}
-                \caption{A single LASSO experiment results, with $M = 64, N=256$. f}
-                \label{fig:single-lass-mu-estimates}
-            \end{figure}
-        \end{frame}
-        \begin{frame}{Real time R-WAPG upper bound}
-            Below is the plot of the real time estimates of R-WAPG convergence bound using for the LASSO experiment. 
-            \begin{figure}[H]
-                \centering
-                \begin{subfigure}[b]{0.75\textwidth}
-                    \centering
-                    \includegraphics[width=\textwidth]{
-                        assets/lasso_rwapg_upperbnd_256.png
-                    }
-                \end{subfigure}
-                \caption{
-                    $N = 1024$, the upper bound estimates in real time from the collected $(\alpha_k)_{k \ge 0}$ sequence. 
-                }
-                \label{fig:single-lass-r-wapg-rwapg-upperbnd}
-            \end{figure}
-        \end{frame}
 
-\section{references and draft on arxiv}
+\section{References and draft on arxiv}
     \begin{frame}{Thanks for the participations. Merci pour les participations.}

### 2025-09-22 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes a lot

--- 2025-08-30 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
@@
 
-\begin{document}
+% NOTATIONS FOR THIS PAPER 
+\DeclareMathOperator{\dist}{\mathop{dist}}
+\DeclareMathOperator{\rng}{\mathop{rng}}
 
-\title{{\fontfamily{ptm}\selectfont An Inexact Accelreated Proximal Gradient Method for TV Variation Problems}}
+\title{{\fontfamily{ptm}\selectfont Inexect Accelerated Proximal Gradient }}
 
@@
 
+\begin{document}
+
+% TITLE, ABSTRACT ==============================================================
 \date{\today}
-
 \maketitle
 \todoinline{This paper is currently in draft mode. Check source to change options. }
-% \vskip 8mm
-
 \begin{abstract} 
     \noindent
-    Not yet added. 
+    This is still a draft. \cite{zhang_robust_2022}. 
 \end{abstract}
-
 \noindent{\bfseries 2010 Mathematics Subject Classification:}
@@
 
-% ==============================================================================
 \section{Introduction}
-    Let's make a type of algorithm that has the niche for applications with a state of the art performance. 
-    \begin{assumption}\label{ass:smooth-nsmooth-sum}
-        We assume the following about $(F, f, g, L, X^+)$: 
-        \begin{enumerate}[nosep]
-            \item $f: \RR^n \rightarrow \RR$ is a convex, $L$ Lipschitz smooth function but doesn't support simple implementations of its proximal operator. 
-            \item $g: \RR^n \rightarrow \RR$ is convex, proper, and closed, and its proximal operator can be easily implemented, and easy to obtain some element $\partial g$ at all points of the domain.
-            \item The over all objective has $F = f + g$. 
-        \end{enumerate}
-        Under this assumption, we denote the proximal gradient operator of $F = f+ g$ as $T_B(x) = \hprox_{B^{-1}g}(x - B^{-1}\nabla f(x))$. 
-        Note that by definition it has also:
+    \textbf{Notations.}
+    Let $g: \RR^n \rightarrow\overline \RR$, we denote $g^\star$ to be the Fenchel conjugate. 
+    $I: \RR^n \rightarrow \RR^n$ denotes the identity operator.
+    For a multivalued mapping $T: \RR^n \rightarrow 2^{\RR^n}$, $\gra T$ denotes the graph of the operator, defined as $\{(x, y)\in \RR^n \times \RR^n : y \in Tx\}$. 
+    \subsection{Epsilon subgradient and inexact proximal point}
+        \begin{definition}[epsilon subgradient]\label{def:esp-subgrad}
+            Let $g: \RR^n \rightarrow \overline \RR$ be proper, lsc. 
+            Let $\epsilon \ge 0$. 
+            Then the $\epsilon$-subgradient of $g$ at some $\bar x \in \dom g$ is given by: 
+            $$
+            \begin{aligned}
+                \partial g_\epsilon(\bar  x) := 
+                \left\lbrace
+                    v \in \RR^n \left| \; 
+                        \langle v, x - \bar  x\rangle \le 
+                        g(x) - g(\bar x) + \epsilon \;\forall x \in \RR^n
+                    \right. 
+                \right\rbrace.
+            \end{aligned}
+            $$
+            When $\bar x \not \in \dom g$, it has $\partial g_\epsilon(\bar x) = \emptyset$. 
+        \end{definition}
+        \begin{remark}
+            $\partial_\epsilon g$ is a multivalued operator and, it's not monotone, unless $\epsilon = 0$, which makes it equivalent to French subgradient $\partial g$. 
+        \end{remark}
+        If we assume lsc, proper and convex $g$, we will now introduce results in the literatures that we will use. 
+        \begin{fact}[epsilon Fenchel inequality]\label{fact:esp-fenchel-ineq}
+            Let $\epsilon \ge 0$, then:
             \begin{align*}
-            T_B(x) &= 
-            \hprox_{B^{-1}g}\left(
-                x - B^{-1}\nabla f(x)
-            \right)
-            \\
-            &= \argmin_{z}\left\lbrace
-                g(z)
-                + \langle \nabla f(x), z\rangle
-                + \frac{B}{2}\Vert z - x \Vert^2
-            \right\rbrace. 
+                x^* \in \partial_\epsilon f(\bar x)\iff f^\star(x^*) + f(\bar x) \le \langle x^*, \bar x\rangle + \epsilon \implies \bar x \in \partial_\epsilon f^\star(x^*).
             \end{align*}
-    \end{assumption}
-    \begin{definition}[A measure of error from proximal gradient evaluations]\;\\
-        Let $(F, f, g, L)$ satisfies Assumption \ref{ass:smooth-nsmooth-sum}. 
-        For all $x, z \in \RR^n$, define $S$: 
+            They are all equivalent if $f^{\star\star}(\bar x) = f(\bar x)$. 
+        \end{fact}
+        \begin{remark}
+            The above fact is taken from Zalinascu \cite[Theorem 2.4.2]{zalinescu_convex_2002}. 
+        \end{remark}
+        % \begin{fact}[strong epsilon subgradient sum rule]\label{fact:esp-subgrad-sum-rule}
+        %     Take both $f, g: \RR^n\rightarrow \overline \RR$. 
+        %     Let $\epsilon \ge 0$. 
+        %     Then the epsilon subgradient sum rule states that 
+        %     \begin{align*}
+        %         \partial_\epsilon[f + g](\bar x) = 
+        %         \bigcup \left\lbrace
+        %             \partial_{\epsilon_1} f(\bar x) + 
+        %             \partial_{\epsilon_2} g(\bar x) \left|\; 
+        %                 \min(\epsilon_1, \epsilon_2) \ge 0\wedge 
+        %                 \epsilon_1 + \epsilon_2 = \epsilon
+        %             \right.
+        %         \right\rbrace
+        %     \end{align*}
+        %     Under the scenario that: $\reli\dom f \cap \reli\dom g \neq \emptyset$. 
+        % \end{fact}
+        % \begin{remark}
+        %     The above is taken from Morduchovich, Mau Nam \cite[Theorem 5.19]{mordukhovich_convex_2022}. 
+        % \end{remark}
+        We will now define inexact proximal point based on epsilon subgradient
+        \begin{definition}[inexact proximal point]
+            For all $x \in \RR^n, \epsilon \ge 0, \lambda > 0$, $\tilde x$ is an inexact evaluation of proximal point at $x$, if and only if it satisfies: 
             \begin{align*}
-            S_B(z | x) &= \partial 
-            \left[
-                z \mapsto g(z)
-                + \langle \nabla f(x), z\rangle
-                + \frac{B}{2}\Vert z - x \Vert^2
-            \right](z). 
+                \lambda^{-1}(x - \tilde x) \in \partial_{\epsilon} g(\tilde x). 
             \end{align*}
+            We denote it by $\tilde x \approx_\epsilon \hprox_{\lambda g}(x)$. 
         \end{definition}
-    Observe: 
-    \begin{enumerate}[nosep]
-        \item $S_B(z | x) = \partial g(z) + \nabla f(x)+ B(z - x)$,
-        \item $\mathbf 0 \in S_B(T(x) | x)$, 
-        \item $(S_B(\cdot | x))^{-1}(\mathbf 0)$ is a singleton by strong convexity. 
-    \end{enumerate}
-    Let's assume inexact evaluation of $\tilde x \approx T_B(x)$, then the error measure is the set $S_B(\tilde x | x)$. 
-    Assuming that we have accurate information on $\nabla f(x)$, then $\forall w \in S_B(\tilde x | x)\;\exists \tilde v \in \partial g(\tilde x)$. 
+        \begin{remark}
+            This definition is nothing new, for example see Villa et al. \cite[Definition 2.1]{villa_accelerated_2013}
+        \end{remark}
+        \begin{fact}[the resolvant identity]\label{fact:resv-identity}
+            Let $T: \RR^n \rightarrow 2^{\RR^n}$, then it has: 
             \begin{align*}
-        w &= \tilde v + \nabla f(x) + B(\tilde x - x). 
+                (I + T)^{-1} = (I - (I + T^{-1})^{-1}).
             \end{align*}
-    We want to control $w$ in the implementations of inexact accelerated proximal gradient algorithm.
-
-\section{Key ideas we need to get right}
-    \begin{definition}[inexact proximal gradient]\;\label{def:inxt-pg}\\
-        Let $(F, f, g, L)$ satisfies Assumption \ref{ass:smooth-nsmooth-sum}.
-        Let $\epsilon \ge 0, B \ge 0$. 
-        We Define for all $x \in \RR^n$ the inexact proximal gradient operator $T_B^{(\epsilon)}(x)$ to be such that if $\tilde x \in T^{(\epsilon)}_{B}(x)$ then, $\exists w \in S_{B}(\tilde x | x):\Vert w\Vert\le \epsilon \Vert \tilde x - x\Vert$.
-    \end{definition}
-    The algorithm we will design must produce iterates in a way that satisfies the inexact proximal gradient operator define above. 
-    The following theorem will characterize a key inequality for convergence claim. 
-    \begin{theorem}[inexact over regularized proximal gradient inequality]\;\label{thm:inxt-pg-ineq}\\
-        Let $(F, f, g, L)$ satisfies Assumption \ref{ass:smooth-nsmooth-sum}.
-        Take $T^{(\epsilon)}_B$ as given in Definition \ref{def:inxt-pg}. 
-        Let $\epsilon \ge 0$. 
-        For all $x\in \RR^n$, if $\exists B \ge 0$ such that $\tilde x \in T_{B + \epsilon}^{(\epsilon)}(x)$ and, $D_f(\tilde x, x)\le \frac{B}{2}\Vert \tilde x - x\Vert^2$. 
-        Then for all $z, x \in \RR^n$ it has: 
+        \end{fact}
+        \begin{theorem}[inexact Moreau decomposition]
+            Let $g: \RR^n \rightarrow \overline \RR$ be a closed, convex and proper function. 
+            It has the equivalence
             \begin{align*}
-            0 &\le F(z) - F(\tilde x) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
-            - \frac{B}{2}\Vert z - \tilde x\Vert^2. 
+                \tilde y \approx_\epsilon \hprox_{\lambda^{-1}g^\star}(\lambda^{-1}y)
+                \iff 
+                y - \lambda \tilde y \approx_\epsilon \hprox_{\lambda g}(y). 
             \end{align*}
@@
         \begin{proof}
-        By Definition \ref{def:inxt-pg}, $T_{B + \epsilon}^{(\epsilon)}(x)$ minimizes a $h(z) = z \mapsto g(z) + \langle \nabla f(x), z \rangle + \frac{B + \epsilon}{2}\Vert x - z\Vert^2$ to produce $\tilde x$ so that $w \in S_{B + \epsilon}(\tilde x| x) = \partial h(x)$.
-        $h$ is $B + \epsilon$ strongly convex by convexity of $g$. 
-        Since $w \in \partial h(\tilde x)$, it has subgradient inequality through strong convexity: 
-        $$
-            (\forall z \in \RR^n)\;  
-            \frac{B + \epsilon}{2}\Vert z - \tilde x\Vert^2 \le h(z) - h(\tilde x) - \langle w,  z - \tilde x\rangle. 
-        $$
-        This means for all $z \in \RR^n$: 
-        \begin{align*}
-            &\frac{B + \epsilon}{2}\Vert \tilde x - z \Vert^2 
-            \\
-            &\le 
-            g(z) + \langle \nabla f(x), z\rangle + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
-            - \left(
-                g(\tilde x) + 
-                \langle \nabla f(x), \tilde x\rangle
-                + 
-                \frac{B + \epsilon}{2}\Vert \tilde x - x\Vert^2
-            \right)
-                \\ &\quad 
-                - \langle w, z - \tilde x\rangle
-            \\
-            &= 
-            \left(
-                g(z) - g(\tilde x)
-                + \frac{B + \epsilon}{2}\Vert z - x\Vert^2 - \frac{B + \epsilon}{2}\Vert \tilde x - x\Vert^2
-                - \langle w, z - \tilde x\rangle
-            \right)
-            \\&\quad 
-                + \langle \nabla f(x), z - x + x -\tilde x\rangle
-            \\
-            &\underset{(1)}{=} 
-            \left(
-                g(z) - g(\tilde x)
-                + \frac{B + \epsilon}{2}\Vert z - x\Vert^2 - \frac{B + \epsilon}{2}\Vert \tilde x - x\Vert^2
-                - \langle w, z - \tilde x\rangle
-            \right)
-                \\
-                &\quad 
-                - D_f(z, x) + f(z)
-                + D_f(\tilde x, x) - f(\tilde x)
-            \\
-            &=
-            \left(
-                F(z) - F(\tilde x)
-                - \langle w, z - \tilde x\rangle
-            \right)
-            + 
-            \left(
-                \frac{B + \epsilon}{2}\Vert z - x\Vert^2 - D_f(z, x)
-            \right) 
-                \\ &\quad 
-                + \left(
-                    D_f(\tilde x, x)
-                    - \frac{B + \epsilon}{2}\Vert \tilde x - x\Vert^2
-                \right)
-            \\
-            &\underset{(2)}{\le} 
-            \frac{B + \epsilon}{2}\Vert z - x\Vert^2 - D_f(z, x)
-            + \left(
-                \frac{B + \epsilon}{2}\Vert z - x\Vert^2
-                - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2
-            \right)
-            \\
-            &\le
-            F(z) - F(\tilde x) + \Vert w \Vert\Vert z - \tilde x\Vert
-            + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
-            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2
-            \\
-            &\underset{(3)}{\le}
-            F(z) - F(\tilde x) 
-            + \epsilon\Vert x - \tilde x\Vert\Vert z - \tilde x\Vert
-            + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
-            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2. 
-        \end{align*}
-        At (1), we used: 
-        \begin{align*}
-            & \langle \nabla f(x), z - x\rangle
-            - \langle \nabla f(x), \tilde x - x\rangle
-            \\
-            &= 
-            - D_f(z, x) + f(z) - f(x)
-            + D_f(\tilde x, x) - f(\tilde x) + f(x)
-            \\
-            &= f(z) + f(\tilde x) - D_f(z, x) + D_f(\tilde x , x). 
-        \end{align*}
-        At (2), we had $f$ convex as the assumption, hence $D_f(z, x) \le 0$. 
-        We also had the assumption that $B$ makes $D_f(\tilde x, x) \le \frac{B}{2}\Vert \tilde x - x\Vert^2$, this simplies the third term from the previous line into $- \frac{\epsilon}{2}\Vert x - \tilde x\Vert^2$.
-        At (3), we applied the assumed inequality $\Vert w\Vert \le \epsilon \Vert x - \tilde x\Vert \Vert z - \tilde x\Vert$. 
-        Continuing: 
-        \begin{align*}
-            0 &\le
-            \left(
-                F(z) - F(\tilde x) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
-                - \frac{B + \epsilon}{2}\Vert z - \tilde x\Vert^2 
-            \right)
-            + \epsilon \Vert \tilde x - x\Vert \Vert z - \tilde x\Vert
-            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2
-            \\
-            &\underset{(4)}{=} 
-            F(z) - F(\tilde x) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
-            - \frac{B}{2}\Vert z - \tilde x\Vert^2. 
-        \end{align*}
-        At (4), we use some algebra: 
+            Consider $\tilde y \approx_\epsilon \hprox_{\lambda^{-1}g^\star}(\lambda^{-1}y)$, then it has: 
             \begin{align*}
                 & 
-            \epsilon \Vert \tilde x - x\Vert \Vert z - \tilde x\Vert
-            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2
+                \tilde y 
+                \in (I + \lambda^{-1}\partial_\epsilon g^\star)^{-1}(\lambda^{-1}y)
                 \\
-            &=\epsilon \Vert \tilde x - x\Vert \Vert z - \tilde x\Vert
-            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2 - \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2
-            + \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2
+                \iff &
+                (\lambda^{-1}y, \tilde y)\in 
+                \gra(I + \lambda^{-1}\partial_\epsilon g^\star)^{-1}
                 \\
-            &= 
-            - \epsilon(\Vert x - \tilde x\Vert - \Vert z -\tilde x\Vert)^2 
-            + \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2 
+                \underset{(1)}{\iff} &
+                (\lambda^{-1}y, \tilde y)\in 
+                \gra(I - (I + \partial_\epsilon g\circ(\lambda I))^{-1})
                 \\
-            &\le \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2. 
+                \iff &
+                (\lambda^{-1}y, \lambda^{-1}y - \tilde y)\in 
+                \gra(I + \partial_\epsilon g\circ(\lambda I))^{-1}
+                \\
+                \iff &
+                (\lambda^{-1}y - \tilde y, \lambda^{-1}y)\in 
+                \gra(I + \partial_\epsilon g\circ(\lambda I))
+                \\
+                \iff &
+                (y - \lambda\tilde y, \lambda^{-1}y)\in 
+                \gra(\lambda^{-1}I + \partial_\epsilon g)
+                \\
+                \iff &
+                (y - \lambda\tilde y, y)\in 
+                \gra(I + \lambda\partial_\epsilon g)
+                \\
+                \iff& 
+                y - \lambda \tilde y \in 
+                (I + \lambda \partial_\epsilon g)^{-1}y
+                \\
+                \iff& 
+                y - \lambda \tilde y \approx_\epsilon \hprox_{\lambda g}(y). 
             \end{align*}
+            At (1) we can use Fact \ref{fact:resv-identity}, and it has $(\lambda^{-1}\partial_\epsilon g^\star)^{-1} = \partial_\epsilon g\circ(\lambda I)$ by Fact \ref{fact:esp-fenchel-ineq} and the assumption that $g$ is closed, convex and proper.
         \end{proof}
-    \subsection{The accelerated proximal gradient algorithm}
-        \begin{definition}[accelerated inexact proximal gradient algorithm]\label{def:inxt-apg}
-            Let 
+
+    \subsection{Inexact proximal gradient inequality}
+        \begin{assumption}[for inexact proximal gradient]\label{ass:for-inxt-pg-ineq}
+            The assumption is about $(f, g, L)$. 
+            We assume that 
             \begin{enumerate}[nosep]
-                \item $(\alpha_k)_{k \ge 0}$ be a sequence in $(0, 1]$. 
-                \item Let $(B_k)_{k \ge 0}$ be a non-negative sequence. 
-                \item Let $(F, f, g, L)$ be given by Assumption \ref{ass:smooth-nsmooth-sum}. 
-                \item Let $(\epsilon_k)$ be a non-negative sequence that is the error schedule. 
+                \item $f: \RR^n \rightarrow \RR$ is a convex, $L$ Lipschitz function. 
+                \item $g: \RR^n \rightarrow \overline\RR$ is a convex, proper, and lsc function which we do not have its exact proximal operator. 
             \end{enumerate}
-            Initialize with any $(x_{-1}, v_{-1})$. 
-            For these given parameters, an algorithm is a type of accelerated proximal gradient if it generates $(y_k, x_k, v_k)_{k \ge 0}$ such that
-            for $k\ge 0$: 
+        \end{assumption}
+        We develop the theory based on the use of epsilon subgradient as in Definition \ref{def:esp-subgrad}. 
+        \begin{definition}[inexact proximal gradient]\label{def:inxt-pg}
+            Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}. 
+            Let $\epsilon \ge 0, B \ge 0$. 
+            Then, $\tilde x \approx_\epsilon T_B(x)$ is an inexact proximal gradient if it satisfies variational inequality: 
             \begin{align*}
-                & y_{k} = \alpha_{k} v_{k - 1} + (1 - \alpha_{k}) x_{k - 1},
-                \\
-                & x_k \in T_{B_k + \epsilon_k}^{(\epsilon_k)}y_k: D_f(x, \tilde x) \le (1/2)\Vert x - \tilde x\Vert^2, 
-                \\
-                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}).
+                \mathbf 0 \in \nabla f(x) + B(x - \tilde x) + \partial_{\epsilon} g(\tilde x). 
             \end{align*}
         \end{definition}
-
-\section{convergence rates results}
-    We will now show that Algorithms satisfying Definition \ref{def:inxt-apg} has desirable convergence rate. 
-    \begin{assumption}[convergence assumptions]\label{ass:apg-cnvg}
-        Let $(F, f, g, L)$ satisfies Assumption \ref{ass:smooth-nsmooth-sum} and in addition assume that $F$ admits a set of non-empty minimizers $X^+$. 
-    \end{assumption}
-    \begin{lemma}[inexact one step convergence claim]\;\label{lemma:inxt-apg-onestep}\\
-        Let $(F, f, g, L, X^+)$ satisfies Assumption \ref{ass:apg-cnvg}. 
-        Suppose that an algorithm satisfies optimizes the given $F =f + g$ also satisfying Definition \ref{def:inxt-apg}.
-        Then for the generated iterates $(y_k, x_k, v_k)_{k \ge 0}$, it has for all $k \ge 1$: 
+        \begin{remark}
+            We assumed that we can get exact evaluation of $\nabla f$ at any points $x \in \RR^n$. 
+        \end{remark}
+        \begin{lemma}[other representations of inexact proximal gradient]\;\\
+            Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}.
+            Let $\epsilon \ge 0, B \ge 0$, then for all $x \approx_\epsilon T_B(x)$, it has the following equivalent representations: 
             \begin{align*}
-            &F(\bar x) - F(x_k)  - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
+                & (x - B^{-1}\nabla f(x)) - \tilde x 
+                \in B^{-1} \partial_\epsilon g(\tilde x)
                 \\
-            &\le 
-            \max\left(
-                1 - \alpha_k, 
-                \frac{\alpha_k(B_k + \epsilon_k)}{\alpha_{k -1}^2B_{k - 1}}
-            \right)
-            \left(
-                F(x_{k - 1}) - F(\bar x) 
-                + \frac{\alpha_{k - 1}^2B_{k - 1}}{2}\Vert \bar x - v_{k - 1} \Vert^2
-            \right). 
+                \iff 
+                & \tilde x \in (I + B^{-1}\partial_\epsilon g(\tilde x))^{-1}
+                (x - B^{-1}\nabla f(x))
+                \\
+                \iff 
+                & x \approx_\epsilon \hprox_{B^{-1} g}
+                \left(x - B^{-1}\nabla f(x)\right)
             \end{align*}
@@
         \begin{proof}
-        Let $\bar x \in X^+$, making it a minimizer of $F$. 
-        Define $z_k := \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$. 
-        It can be verified that:
-        \begin{align}\begin{split}
-            z_k - x_k &= \alpha_k(\bar x - v_k),
+            It's direct. 
+        \end{proof}
+        \begin{theorem}[inexact over-regularized proximal gradient inequality]\;\label{thm:inxt-pg-ineq}\\
+            Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq} . 
+            Let $\epsilon \ge 0$. 
+            Consider $\tilde x \approx_\epsilon T_{B + \beta}(x)$. 
+            If in addition, it satisfies $D_f(\tilde x, x) \le B/2\Vert x - \tilde x\Vert^2$, then it has $\forall z \in \RR^n$: 
+            \begin{align*}
+                - \epsilon &\le 
+                F(z) - F(\tilde x)
+                + \frac{B + \beta}{2}\Vert x - z\Vert^2
+                - \frac{B + \beta}{2}\Vert z - \tilde x\Vert^2
+                - \frac{\beta}{2}\Vert \tilde x - x\Vert^2. 
+            \end{align*}
+        \end{theorem}
+        \begin{proof}
+            By Definition \ref{def:inxt-pg} write the variational inequality that describes $\tilde x \approx_\epsilon T_B(x)$, and the definition of epsilon subgradient (Definition \ref{def:esp-subgrad}) it has for all $z \in \RR^n$:
+            \begin{align*}
+                - \epsilon &\le 
+                g(z) - g(\tilde x) - \langle (B + \beta)(\tilde x - x) - \nabla f(x), z - \tilde x\rangle
                 \\
-            z_k - y_k &= \alpha_k(\bar x - v_{k - 1}).     
-        \end{split}\tag{a}\label{lemma:inxt-apg-onestep-a}
-        \end{align}
-        Because from Definition \ref{def:inxt-apg} it has for all $k \ge 1$: 
-        \begin{align*}
-            z_k - x_k &= 
-            \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
-            \\
-            &= \alpha_kx^+ + (x_{k - 1} - x_k) - \alpha_kx_{k - 1}
-            \\
-            &= \alpha_k \bar x - \alpha_k v_k, 
-            \\
-            z_k - y_k &= 
-            \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
-            \\
-            &= \alpha_k \bar x - \alpha_k v_{k - 1}. 
-        \end{align*}
-        For all $k \ge 0$, apply Theorem \ref{thm:inxt-pg-ineq} with $z = z_k, \tilde x = x_k, x = y_k, \epsilon = \epsilon_k, B = B_k$: 
-        \begin{align*}
-            0 &\le 
-            (F(z_k) - F(x_k) ) +
-            \left(
-                \frac{B_k + \epsilon_k}{2}\Vert z_k - y_k\Vert^2
-                - \frac{B_k}{2}\Vert z_k - x_k\Vert^2
-            \right)
+                &= 
+                g(z) - g(\tilde x) 
+                - (B + \beta)\langle \tilde x - x, z - \tilde x\rangle
+                + \langle \nabla f(x), z - \tilde x\rangle
                 \\
                 &\underset{(1)}{\le} 
-            (\alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k))
-            + 
-            \left(
-                \frac{B_k + \epsilon_k}{2}\Vert z_k - y_k\Vert^2
-                - \frac{B_k}{2}\Vert z_k - x_k\Vert^2
-            \right)
+                g(z) + f(z) - g(\tilde x) - f(\tilde x)
+                - (B + \beta)\langle \tilde x - x, z - \tilde x\rangle
+                - D_f(z, x) + D_f(\tilde x, x)
                 \\
-            &\underset{\eqref{lemma:inxt-apg-onestep-a}}{=} 
-            (\alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k))
-                \\ &\quad 
-                + \left(
-                    \frac{(B_k + \epsilon_k)\alpha_k^2}{2}\Vert \bar x - v_{k - 1} \Vert^2
-                    - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
-                \right)
+                &\underset{(2)}{\le} 
+                F(z) - F(\tilde x)
+                - (B + \beta)\langle \tilde x - x, z - \tilde x\rangle
+                + \frac{B}{2}\Vert \tilde x - x\Vert^2
                 \\
                 &=
-            F(\bar x) - F(x_k)
-            + (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x))
-                \\ &\quad 
-                + \left(
-                    \frac{(B_k + \epsilon_k)\alpha_k^2}{2}\Vert \bar x - v_{k - 1} \Vert^2
-                    - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
+                F(z) - F(\tilde x) + \frac{B + \beta}{2}\left(
+                    \Vert x - z\Vert^2
+                    - \Vert \tilde x - x\Vert^2
+                    - \Vert z - \tilde x\Vert^2
                 \right)
+                + \frac{B}{2}\Vert \tilde x - x\Vert^2
                 \\
                 &= 
-            F(\bar x) - F(x_k) 
-            - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
-                \\ &\quad 
-                + (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x))
-                + \frac{(B_k + \epsilon_k)\alpha_k^2}{2}\Vert \bar x - v_{k - 1} \Vert^2
+                F(z) - F(\tilde x)
+                + \frac{B + \beta}{2}\Vert x - z\Vert^2
+                - \frac{B + \beta}{2}\Vert z - \tilde x\Vert^2
+                - \frac{\beta}{2}\Vert \tilde x - x\Vert^2. 
+            \end{align*}
+            At (1), we used considered the following: 
+            \begin{align*}
+                \langle \nabla f(x), z - x\rangle &= \langle \nabla f(x), z - x + x - \tilde x\rangle
                 \\
-            &= F(\bar x) - F(x_k) 
-            - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
-                \\ &\quad
-                + (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x))
-                + \frac{(B_k + \epsilon_k)\alpha_k^2}{\alpha_{k - 1}^2B_{k - 1}}\frac{\alpha_{k - 1}^2B_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                &= \langle \nabla f(x), z - x\rangle + \langle \nabla f(x), x - \tilde x\rangle
                 \\
-            &= 
-            F(\bar x) - F(x_k) - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
-            \\ &\quad 
-            + \max\left(
-                1 - \alpha_k, 
-                \frac{(B_k + \epsilon_k)\alpha_k^2}{\alpha_{k - 1}^2B_{k - 1}}
-            \right)
+                &= -D_f(z, x) + f(z) - f(x) + D_f(\tilde x, x) - f(\tilde x) + f(x)
+                \\
+                &= -D_f(z, x) + f(z) + D_f(\tilde x, x) - f(\tilde x). 
+            \end{align*}
+            At (2), we used the fact that $f$ is convex hence $- D_f(z, x) \le 0$ always, and in the statement hypothesis we assumed that $B$ has $D_f(\tilde x, x) \le B/2\Vert \tilde x - x\Vert^2$. 
+        \end{proof}
+    \subsection{optimizing the inexact proximal point problem}
+        In this section we will show an optimization problem that allows us to solve for some $\tilde x \approx_\epsilon \hprox_{\lambda g}(z)$. 
+        Most of these results are from the literature. 
+        To start, we must assume the following about a function $g: \RR^n \rightarrow \overline \RR$, with $g$ closed, convex and proper. 
+        \begin{assumption}[for inexact proximal operator]\;\label{ass:for-inxt-prox}\\
+            This assumption is about $(g, \omega, A)$. 
+            Let $m \in \N, n \in \RR^n$, we assume that 
+            \begin{enumerate}[nosep]
+                \item $A\in \RR^{m \times n}$ is a matrix. 
+                \item $\omega: \RR^n \rightarrow \overline \RR$ is a closed and convex function such that it admits proximal operator $\hprox_{\lambda\omega}$ and, its conjugate $\omega^\star$ is known.
+                \item $g := \omega(Ax)$ such that $\rng A \cap \reli\dom g \neq\emptyset$. 
+            \end{enumerate}
+        \end{assumption}
+        Now, we are ready to discuss how to choose $\tilde x \approx_\epsilon \hprox_{\lambda g}(x)$. 
+        Fix $y \in \RR^n, \lambda > 0$, we are ultimately interested in minimizing: 
+        \begin{align}
+            \Phi_\lambda(u) &:= \omega(Au) + \frac{1}{2\lambda} \Vert u - y\Vert^2
+        \end{align}
+        This problem admits dual objective in $\RR^m$: 
+        \begin{align}
+            \Psi_\lambda(v) &:=
+            \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2
+            + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2. 
+        \end{align}
+        We define the duality gap
+        \begin{align}
+            \mathbf G_\lambda(u, v) &:= \Phi_\lambda(u) + \Psi_\lambda(v). 
+        \end{align}
+        If strong duality holds, it exists $(\hat u, \hat v)$ such that we have the following: 
+        \begin{align*}
+            \mathbf G_\lambda(\hat u, \hat v) = 0 = \min_{u} \Phi_\lambda(u) + \min_v \Psi_\lambda(v)
+        \end{align*}
+        The following theorem quantifies a sufficient conditions for $\tilde x \approx_\epsilon \hprox_{\lambda g}(x)$. 
+        The theorem below is from \cite[Proposition 2.2]{villa_accelerated_2013}. 
+        \begin{theorem}[primal translate to dual]\label{thm:primal-dual-trans}
+            Let $\epsilon \ge 0$, $g:\RR^n \rightarrow \overline \RR$ be convex, proper and closed then 
+            \begin{align*}
                 \left(
-                F(x_{k - 1}) - F(\bar x) 
-                + \frac{\alpha_{k - 1}^2B_{k - 1}}{2}\Vert \bar x - v_{k - 1} \Vert^2
-            \right). 
+                    \forall z \approx_\epsilon \hprox_{\lambda g}(y) 
+                \right)(\exists v \in \dom \omega^\star): z = y - \lambda B^\top v. 
             \end{align*}
-        At (1) we used convexity of $f$ which is assumed and it makes $f(z_k) \le \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1})$ because $\alpha_k \in (0, 1]$ from Definition \ref{def:inxt-apg}. 
-    \end{proof}
-    \\
-    As a prelude, to derive the convergence rate we unroll the recurrence relation proved in the above lemma.
-    It remains to create convergence criterions of the error relative sequence $\epsilon_k$ such that the original optimal convergence rate of $\mathcal O(1/k^2)$ the sequence remains unaffected. 
-    Let the sequence $(B_k)_{k \ge 0}$ be given by **Definition 2**. 
-    We suggest the following descriptors using another sequence $\rho_k$ given by for all $k \ge 1$: 
-    \begin{align*}
-        \rho_k &= \frac{B_k + \epsilon_k}{B_{k - 1}}\frac{B_{k - 1}}{B_k}.
-    \end{align*}
-    This means the following: 
-    \begin{align*}
-        \max\left(
-            1 - \alpha_k, 
-            \frac{\alpha_k^2(B_k + \epsilon_k)}{\alpha_{k - 1}^2B_{k - 1}}
-        \right)
-        &=
-        \max\left(
-            \sim, 
-            \rho_k\frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
-        \right)
-        \\
-        &\le \max(1, \rho_k)\max\left(
-            \sim, 
-            \frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
-        \right). 
-    \end{align*}
-    If we consider $\rho_k \le (1 + 2/k^2)$, it has the ability to make
-    \begin{align*}
-        \prod_{k = 1}^{n} 
-        \max \left(
-            1 - \alpha_k, 
-            \frac{\alpha_k^2(B_k + \epsilon_k)}{\alpha_{k - 1}^2B_{k - 1}}
-        \right)
-        &\le 
-        \prod_{k = 1}^{n} 
-        \max(1, \rho_k)
-        \left(
-        \prod_{i = 1}^{n}
-            \max\left(
-                1 - \alpha_k, 
-                \frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
-            \right)
-        \right)
-        \\
-        &\le \prod_{k = 1}^n
-        \left(
-            1 + \frac{2}{k^2}
-        \right)
-        (\sim)
-        \\
-        &\le 2 (\sim). 
-    \end{align*}
+        \end{theorem}
+        The theorem is from Villa et al. \cite[Proposition 2.3]{villa_accelerated_2013}
+        \begin{theorem}[duality gap of inexact proximal problem]\label{thm:dlty-gap-inxt-pp}
+            For all $\epsilon \ge 0$, $v \in \RR^n$. 
+            Consider conditions 
+            \begin{enumerate}[nosep]
+                \item $\mathbf G_\lambda(y - \lambda B^\top v, v) \le \epsilon$. 
+                \item $B^\top v \approx_\epsilon \hprox_{\lambda^{-1}g^\star}(\lambda^{-1}y)$. 
+                \item $y - \lambda B^\top v \approx_{\epsilon} \hprox_{\lambda g}(y)$. 
+            \end{enumerate}
+            They have $(a)\implies (b) \iff (c)$. 
+            If in addition $\omega^\star(v) = g^\star(B^\top v)$, then all three conditions are equivalent. 
+        \end{theorem}
+        Next, let's explore some options for minimizing the duality gap of the proximal problem. 
+        \todoinline{
+            STILL WRITING AND NOT FINISHED YET! 
+        }
 
-    The following lemma will seal the case for the other remaining big product above.
-
+    \subsection{Literature reviews}
 \bibliographystyle{siam}
-
-\bibliography{references/Books.bib}
-
+\bibliography{references/refs.bib}
 \end{document}

### 2025-09-22 Notebook LaTEX/R-WAPG/presentation-short.tex
>w<, changes
>w<, changes a lot

@@
             If $F$ is convex and has $L$ Lipschitz smooth gradient and a minimizer $x^+$ exists. 
-            Then it has
             \begin{itemize}
@@
         \begin{frame}{A practical realization inspired by the theories}
-            Our theories sugguest that, the upperbound for function value in the R-WAPG algorithm is ultimately described by the sequence $(\alpha_k)_{k \ge 0}$.
+            Our theories suggest that, the upperbound for function value in the R-WAPG algorithm is ultimately described by the sequence $(\alpha_k)_{k \ge 0}$.
             \textbf{Taking this idea further, this is what we did for numerical experiments}: 
@@
     \subsection{Introducing the R-WAPG framework}
+        \begin{frame}{Proximal gradient, gradient mapping}
+            \begin{definition}[The proximal gradient operator]
+                Define for all $x\in \RR^n$: 
+                \begin{align*}
+                    T_L(y) 
+                    &:= \argmin_{x \in \RR^n} \left\lbrace
+                        g(x) + \langle \nabla f(y), x\rangle + L/2\Vert x - y\Vert^2
+                    \right\rbrace 
+                    \\
+                    &= \left(I + L^{-1}\partial g\right)^{-1}
+                    \left(I - L^{-1}\nabla f\right)(y),
+                    \\
+                    \mathcal G_L(y)
+                    &:= L(y - T_L(y)).
+                \end{align*}
+            \end{definition}
+            Note, the $I$ here is the identity operator in $\RR^n$. 
+            $L > 0$ is the Lipschitz smoothness parameter for $f$. 
+        \end{frame}
         \begin{frame}{The R-WAPG sequences}
@@
         \end{frame}
-        \begin{frame}{Proximal gradient, gradient mapping}
-            \begin{definition}[The proximal gradient operator]
-                Define for all $x\in \RR^n$: 
-                \begin{align*}
-                    T_L(y) 
-                    &:= \argmin_{x \in \RR^n} \left\lbrace
-                        g(x) + \langle \nabla f(y), x\rangle + L/2\Vert x - y\Vert^2
-                    \right\rbrace 
-                    \\
-                    &= \left(I + L^{-1}\partial g\right)^{-1}
-                    \left(I - L^{-1}\nabla f\right)(y),
-                    \\
-                    \mathcal G_L(y)
-                    &:= L(I - T_L)y.
-                \end{align*}
-            \end{definition}
-            Note, the $I$ here is the identity operator in $\RR^n$. 
-            $L > 0$ is the Lipschitz smoothness parameter for $f$. 
-        \end{frame}
         \begin{frame}{R-WAPG}
-            \begin{definition}[relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
+            \begin{definition}[R-WAPG]\label{def:wapg}
                 Choose any $x_1 \in \RR^n, v_1 \in \RR^n$.
@@
                         \\
-                        x_{k + 1} &= T_L y_k.
+                        x_{k + 1} &= T_L (y_k).
                     \end{align*}
@@
             \begin{proposition}[Alternative representations of the iterates]\label{prop:wapg-first-equivalent-repr}
-                If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}),
-                then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$, and they satisfy for all $k\ge 1$: 
+                If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}), and $\alpha_0 = 1, x_1 = v_1$. 
+                Then they satisfy for all $k\ge 1$: 
                 {\footnotesize
@@
                         \\
-                        &= x_{k + 1} +
-                        \frac{\rho_k\alpha_k(1 - \alpha_k)}
-                        {\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k), 
+                        &= x_{k} +
+                        \frac{\rho_{k - 1}\alpha_{k - 1}(1 - \alpha_{k - 1})}
+                        {\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_{k}}(x_{k} - x_{k - 1}), 
                     \end{aligned}
@@
             If $\mu = 0$, then it simplifies:
+            {\small
             \begin{align*}
@@
             \end{align*}
+            }
         \end{frame}
@@
 
-\section{references and draft on arxiv}
+\section{References and draft on arxiv}
     \begin{frame}{Thanks for the participations. Merci pour les participations.}

### 2025-09-22 Notebook LaTEX/R-WAPG/presentation-shorter.tex
>w<, changes a lot

@@
         If minimizer $x^+$ exists, then: 
-        Then it has
         \begin{itemize}
@@
 
-\section{The R-WAPG Framework}
+\section{The R-WAPG framework}
     \begin{frame}{The assumptions we make throughout}
@@
         \end{assumption}
-        \textbf{This assumption the full scope of the theoretical and practical discussion, assume it throughout.}
+        \textbf{This assumption is the full scope of the theoretical and practical discussion. }
     \end{frame}
@@
                 \mathcal G_L(y)
-                &:= L(I - T_L)y.
+                &:= L(y - T_L(y)).
             \end{align*}
@@
     \begin{frame}{The R-WAPG sequences}
-        In this section, we highlight key theoretical results that allowed us to unify convergence rate for various variants of FISTA in the literature.
+        We highlight key theoretical results that allowed us to unify convergence rate for various variants of FISTA in the literature.
         \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}
@@
                 \rho_k := \frac{\alpha_{k + 1}^2 - (\mu/L) \alpha_{k + 1}}{
-                    (1 - \alpha_{k + 1}) \alpha_k^2.
-                }
+                    (1 - \alpha_{k + 1}) \alpha_k^2
+                }. 
             \end{align*}
@@
                     \\
-                    x_{k + 1} &= T_L y_k.
+                    x_{k + 1} &= T_L (y_k).
                 \end{align*}
@@
 
-\section{Our Theoretical Results}
+\section{Our theoretical results}
     \begin{frame}{Iterates by R-WAPG has other representations}
         \begin{proposition}[Alternative representations of the iterates]\label{prop:wapg-first-equivalent-repr}
-            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}),
+            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}), and $\alpha_0 = 1, x_1 = v_1$. 
             Then they satisfy for all $k\ge 1$: 
@@
                     \\
-                    &= x_{k + 1} +
-                    \frac{\rho_k\alpha_k(1 - \alpha_k)}
-                    {\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k), 
+                    &= x_{k} +
+                    \frac{\rho_{k - 1}\alpha_{k - 1}(1 - \alpha_{k - 1})}
+                    {\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_{k}}(x_{k} - x_{k - 1}), 
                 \end{aligned}
@@
             Let $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ be R-WAPG sequences.
-            Let vector sequences $(y_k, v_{k}, x_{k})_{k \ge 1}$ given by Definition \ref{def:wapg}. 
+            Let vector sequences $(y_k, v_{k}, x_{k})_{k \ge 1}$ be given by Definition \ref{def:wapg}. 
             Then for all $k = 1, 2, \ldots, N$:
@@
             \delta_k := \log_2\left(
-                \frac{F(x) - F^+}{F(x_0) - F^+}\right).  
+                \frac{F(x_k) - F^+}{F(x_0) - F^+}\right).  
         \end{align*}

### 2025-09-23 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

@@
     \subsection{Epsilon subgradient and inexact proximal point}
-        \begin{definition}[epsilon subgradient]\label{def:esp-subgrad}
+        \begin{definition}[$\epsilon$-subgradient]\label{def:esp-subgrad}
             Let $g: \RR^n \rightarrow \overline \RR$ be proper, lsc. 
@@
         If we assume lsc, proper and convex $g$, we will now introduce results in the literatures that we will use. 
-        \begin{fact}[epsilon Fenchel inequality]\label{fact:esp-fenchel-ineq}
+        \begin{fact}[$\epsilon$-Fenchel inequality]\label{fact:esp-fenchel-ineq}
             Let $\epsilon \ge 0$, then:
@@
         % \end{remark}
-        We will now define inexact proximal point based on epsilon subgradient
-        \begin{definition}[inexact proximal point]
+        We will now define inexact proximal point based on $\epsilon$-subgradient
+        \begin{definition}[inexact proximal point]\label{def:inxt-pp}
             For all $x \in \RR^n, \epsilon \ge 0, \lambda > 0$, $\tilde x$ is an inexact evaluation of proximal point at $x$, if and only if it satisfies: 
@@
             Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}. 
-            Let $\epsilon \ge 0, B \ge 0$. 
-            Then, $\tilde x \approx_\epsilon T_B(x)$ is an inexact proximal gradient if it satisfies variational inequality: 
+            Let $\epsilon \ge 0, \rho > 0$. 
+            Then, $\tilde x \approx_\epsilon T_\rho(x)$ is an inexact proximal gradient if it satisfies variational inequality: 
             \begin{align*}
-                \mathbf 0 \in \nabla f(x) + B(x - \tilde x) + \partial_{\epsilon} g(\tilde x). 
+                \mathbf 0 \in \nabla f(x) + \rho(x - \tilde x) + \partial_{\epsilon} g(\tilde x). 
             \end{align*}
@@
         \begin{lemma}[other representations of inexact proximal gradient]\;\\
-            Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}.
-            Let $\epsilon \ge 0, B \ge 0$, then for all $x \approx_\epsilon T_B(x)$, it has the following equivalent representations: 
+            Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, $\epsilon \ge 0, \rho > 0$, then for all $x \approx_\epsilon T_\rho(x)$, it has the following equivalent representations: 
             \begin{align*}
-                & (x - B^{-1}\nabla f(x)) - \tilde x 
-                \in B^{-1} \partial_\epsilon g(\tilde x)
+                & (x - \rho^{-1}\nabla f(x)) - \tilde x 
+                \in \rho^{-1} \partial_\epsilon g(\tilde x)
                 \\
                 \iff 
-                & \tilde x \in (I + B^{-1}\partial_\epsilon g(\tilde x))^{-1}
-                (x - B^{-1}\nabla f(x))
+                & \tilde x \in (I + \rho^{-1}\partial_\epsilon g(\tilde x))^{-1}
+                (x - \rho^{-1}\nabla f(x))
                 \\
                 \iff 
-                & x \approx_\epsilon \hprox_{B^{-1} g}
-                \left(x - B^{-1}\nabla f(x)\right)
+                & x \approx_\epsilon \hprox_{\rho^{-1} g}
+                \left(x - \rho^{-1}\nabla f(x)\right)
             \end{align*}
@@
         \begin{theorem}[inexact over-regularized proximal gradient inequality]\;\label{thm:inxt-pg-ineq}\\
-            Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq} . 
-            Let $\epsilon \ge 0$. 
-            Consider $\tilde x \approx_\epsilon T_{B + \beta}(x)$. 
-            If in addition, it satisfies $D_f(\tilde x, x) \le B/2\Vert x - \tilde x\Vert^2$, then it has $\forall z \in \RR^n$: 
+            Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, $\epsilon \ge 0, B \ge 0, \rho > 0$. 
+            Consider $\tilde x \approx_\epsilon T_{B + \rho}(x)$. 
+            Denote $F = f + g$. 
+            If in addition, $\tilde x, B$ satisfies the line search condition $D_f(\tilde x, x) \le B/2\Vert x - \tilde x\Vert^2$, then it has $\forall z \in \RR^n$: 
             \begin{align*}
@@
                 F(z) - F(\tilde x)
-                + \frac{B + \beta}{2}\Vert x - z\Vert^2
-                - \frac{B + \beta}{2}\Vert z - \tilde x\Vert^2
-                - \frac{\beta}{2}\Vert \tilde x - x\Vert^2. 
+                + \frac{B + \rho}{2}\Vert x - z\Vert^2
+                - \frac{B + \rho}{2}\Vert z - \tilde x\Vert^2
+                - \frac{\rho}{2}\Vert \tilde x - x\Vert^2. 
             \end{align*}
@@
                 - \epsilon &\le 
-                g(z) - g(\tilde x) - \langle (B + \beta)(\tilde x - x) - \nabla f(x), z - \tilde x\rangle
+                g(z) - g(\tilde x) - \langle (B + \rho)(\tilde x - x) - \nabla f(x), z - \tilde x\rangle
                 \\
@@
                 g(z) - g(\tilde x) 
-                - (B + \beta)\langle \tilde x - x, z - \tilde x\rangle
+                - (B + \rho)\langle \tilde x - x, z - \tilde x\rangle
                 + \langle \nabla f(x), z - \tilde x\rangle
@@
                 g(z) + f(z) - g(\tilde x) - f(\tilde x)
-                - (B + \beta)\langle \tilde x - x, z - \tilde x\rangle
+                - (B + \rho)\langle \tilde x - x, z - \tilde x\rangle
                 - D_f(z, x) + D_f(\tilde x, x)
@@
                 F(z) - F(\tilde x)
-                - (B + \beta)\langle \tilde x - x, z - \tilde x\rangle
+                - (B + \rho)\langle \tilde x - x, z - \tilde x\rangle
                 + \frac{B}{2}\Vert \tilde x - x\Vert^2
@@
                 &=
-                F(z) - F(\tilde x) + \frac{B + \beta}{2}\left(
+                F(z) - F(\tilde x) + \frac{B + \rho}{2}\left(
                     \Vert x - z\Vert^2
@@
         \end{proof}
-    \subsection{optimizing the inexact proximal point problem}
+    \subsection{Optimizing the inexact proximal point problem}
         In this section we will show an optimization problem that allows us to solve for some $\tilde x \approx_\epsilon \hprox_{\lambda g}(z)$. 
@@
         \begin{theorem}[primal translate to dual]\label{thm:primal-dual-trans}
-            Let $\epsilon \ge 0$, $g:\RR^n \rightarrow \overline \RR$ be convex, proper and closed then 
+            Let $(g, \omega, A)$ satisfies Assumptiom \ref{ass:for-inxt-prox}, $\epsilon \ge 0$, then 
             \begin{align*}
@@
                     \forall z \approx_\epsilon \hprox_{\lambda g}(y) 
-                \right)(\exists v \in \dom \omega^\star): z = y - \lambda B^\top v. 
+                \right)(\exists v \in \dom \omega^\star): z = y - \lambda A^\top v. 
             \end{align*}
         \end{theorem}
-        The theorem is from Villa et al. \cite[Proposition 2.3]{villa_accelerated_2013}
+        This theorem that follows is from Villa et al. \cite[Proposition 2.3]{villa_accelerated_2013}, but put into our symbols and, Definition 
         \begin{theorem}[duality gap of inexact proximal problem]\label{thm:dlty-gap-inxt-pp}
-            For all $\epsilon \ge 0$, $v \in \RR^n$. 
-            Consider conditions 
+            Let $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}, for all $\epsilon \ge 0$, $v \in \RR^n$ consider the following conditions: 
             \begin{enumerate}[nosep]
-                \item $\mathbf G_\lambda(y - \lambda B^\top v, v) \le \epsilon$. 
-                \item $B^\top v \approx_\epsilon \hprox_{\lambda^{-1}g^\star}(\lambda^{-1}y)$. 
-                \item $y - \lambda B^\top v \approx_{\epsilon} \hprox_{\lambda g}(y)$. 
+                \item $\mathbf G_\lambda(y - \lambda A^\top v, v) \le \epsilon$. 
+                \item $A^\top v \approx_\epsilon \hprox_{\lambda^{-1}g^\star}(\lambda^{-1}y)$. 
+                \item $y - \lambda A^\top v \approx_{\epsilon} \hprox_{\lambda g}(y)$. 
             \end{enumerate}
             They have $(a)\implies (b) \iff (c)$. 
-            If in addition $\omega^\star(v) = g^\star(B^\top v)$, then all three conditions are equivalent. 
+            If in addition $\omega^\star(v) = g^\star(A^\top v)$, then all three conditions are equivalent. 
         \end{theorem}
@@
         }
+    \subsection{Literature reviews}
+    \subsection{Our contributions}
 
-    \subsection{Literature reviews}
+\section{The accelerated proximal gradient with controlled errors}
+    In this section, we present an accelerated algorithm with controlled error using Definition \ref{def:inxt-pg}, and show that it can have a convergence rate under certain error conditions. 
+    \begin{definition}[our inexact accelerated proximal gradient]\;\label{def:inxt-apg}\\
+        Suppose that $(F, f, g, L)$ and, sequences $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$ satisfies the following
+        \begin{enumerate}[nosep]
+            \item $(\alpha_k)_{k \ge 0}$ is a sequence such that $\alpha \in (0, 1]$ for all $k \ge 0$. 
+            \item $(B_k)_{k \ge 0}$ is a non-negative sequence, characterizing the potential line search routine. 
+            \item $(\rho_k)_{k \ge 0}$ be a sequence such that $\rho_k > 0$, characterizing the over-relaxation of the proximal gradient operator. 
+            \item $(\epsilon_k)_{k \ge 0}$ is a non-negative sequence characterizing the errors of inexact proximal evaluation.
+            \item $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, and let $F = f + g$. 
+        \end{enumerate}
+        Denote $L_k = B_k + \rho_k$ for short. 
+        Given any initial condition $v_{-1}, x_{-1} \in \RR^n$, the algorithm generates the sequences $(y_k, x_k, v_k)_{k \ge 0}$ such that they satisfies for all $k \ge 0$: 
+        \begin{align*}
+            & y_k = \alpha_k v_{k - 1} + (1 - \alpha_k)x_{k - 1}, 
+            \\
+            & x_k \approx_{\epsilon_k} T_{L_k}(y_k), 
+            \\
+            & D_f(x_k, y_k) \le \frac{B_k}{2}\Vert x_k - y_k\Vert^2, 
+            \\
+            & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
+        \end{align*}
+    \end{definition}
+    \begin{lemma}[inexact accelerated proximal gradient preparation stage I]\; \label{lemma:inxt-apg-cnvg-prep1}\\
+        Let $(f, g, L)$, and $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, be given by Definition \ref{def:inxt-apg}. 
+        Denote $L_k = B_k + \rho_k$. 
+        Then, for any $\bar x \in \RR^n$, the sequences $(y_k, x_k, v_k)_{k \ge 0}$ generated satisfy for all $k \ge 1$ the inequality: 
+        \begin{align*}
+            & \frac{\rho_k}{2}\Vert x_k - y_k\Vert^2 - \epsilon_k
+            \\
+            &\le 
+            (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x)) + F(\bar x) - F(x_k) 
+            \\ &
+            + \max\left(
+                    1 - \alpha_k, \frac{\alpha_k^2L_k}{\alpha_{k - 1}^2L_{k - 1}}
+                \right)\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2 
+            - \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2. 
+        \end{align*}
+        When, $k = 1$ it instead have: 
+        \begin{align*}
+            & \frac{\rho_0}{2}\Vert x_0 - y_0\Vert^2 - \epsilon_0 
+            \\
+            &\le 
+            (1 - \alpha_0)(F(x_{-1}) - F(\bar x)) + F(\bar x) - F(x_0) 
+            + \frac{\alpha_0^2L_0}{2}\Vert \bar x - v_{-1}\Vert^2
+            - \frac{\alpha_0^2L_0}{2}\Vert \bar x - v_0\Vert^2. 
+        \end{align*}
+    \end{lemma}
+    \begin{proof}
+        Two intermediate results are in order before we can prove the inequality. 
+        Define $z_k := \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ for short. 
+        It has for all $k \ge 1$ the equality: 
+        \begin{align}\tag{a}\label{eqn:inxt-apg-cnvg-prep1-a}\begin{split}
+            z_k - x_k &= 
+            \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
+            \\
+            &= \alpha_kx^+ + (x_{k - 1} - x_k) - \alpha_kx_{k - 1}
+            \\
+            &= \alpha_k \bar x - \alpha_k v_k. 
+        \end{split}\end{align}
+        It also has for all $k \ge 1$ the equality: 
+        \begin{align}\tag{b}\label{eqn:inxt-apg-cnvg-prep1-b}\begin{split}
+            z_k - y_k &= 
+            \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
+            \\
+            &= \alpha_k \bar x - \alpha_k v_{k - 1}. 
+        \end{split}\end{align}
+        Let's denote $L_k = B_k + \rho_k$ for short. 
+        Recall that $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, if we choose $x = y_k$ so $\tilde x = x_k \approx_\epsilon T_{L_k}(y_k)$, and set $z = z_k, \epsilon = \epsilon_k$ then Theorem \ref{thm:inxt-pg-ineq} has:
+        \begin{align*}
+            & \frac{\rho_k}{2}\Vert x_k - y_k\Vert^2 - \epsilon_k
+            \\
+            &\le
+            F(z_k) - F(x_k) + \frac{L_k}{2}\Vert y_k - z_k\Vert^2 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2
+            \\
+            &\underset{(1)}{\le} \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
+            + \frac{L_k}{2}\Vert y_k - z_k\Vert^2 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2
+            \\
+            &\underset{(2)}{=} 
+            (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x)) + F(\bar x) - F(x_k) 
+            + \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_{k - 1}\Vert^2 
+            - \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_{k}\Vert^2 
+            \\
+            &\le 
+            (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x)) + F(\bar x) - F(x_k) 
+            \\ &
+            + \max\left(
+                    1 - \alpha_k, \frac{\alpha_k^2L_k}{\alpha_{k - 1}^2L_{k - 1}}
+                \right)\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2 
+            - \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2. 
+        \end{align*}
+        At (1) we used the fact that $F = f + g$ hence $F$ is convex. 
+        At (2) we used \eqref{eqn:inxt-apg-cnvg-prep1-a}, \eqref{eqn:inxt-apg-cnvg-prep1-b}. 
+        Finally, if $k = 0$, then take the RHS of $\underset{(1)}{=}$ then:
+        \begin{align*}
+            & \frac{\rho_0}{2}\Vert x_0 - y_0\Vert^2 - \epsilon_0 
+            \\
+            &\le 
+            (1 - \alpha_0)(F(x_{-1}) - F(\bar x)) + F(\bar x) - F(x_0) 
+            + \frac{\alpha_0^2L_0}{2}\Vert \bar x - v_{-1}\Vert^2
+            - \frac{\alpha_0^2L_0}{2}\Vert \bar x - v_0\Vert^2. 
+        \end{align*}
+    \end{proof}
+    \par
+    The following proposition is a prototype of the convergence rate together with the error schedule that delivers convergence of algorithms satisfying Definition \ref{def:inxt-apg}. 
+    \begin{proposition}[valid error schedule and convergence rate]\;\label{prop:inxt-apg-cnvg-generic}\\
+        Let $(f, g, L)$, $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$ be given by Definition \ref{def:inxt-apg}. 
+        Fix any $\bar x \in \RR^n$ for all $k \ge 0$ and assume that $\alpha_0 = 1$. 
+        Denote for brevity $\beta_0 = 1$, $\beta_k = \prod_{i = 1}^{k} \max\left(1 - \alpha_i, \frac{\alpha_i^2L_i}{\alpha_{i - 1}^2L_{i - 1}}\right)$ and $L_k = B_k + \rho_k$. 
+        If for some fixed $\mathcal E_0 \ge 0, p \ge 1$ the parameter $\rho_k, \epsilon_k$ can satisfy for all $k \ge 0$ the condition
+        \begin{align*}
+            \frac{- \mathcal E_0\beta_k}{k^p} &\le 
+            \frac{\rho_k}{2}\Vert x_k - y_k\Vert^2 - \epsilon_k. 
+        \end{align*}
+        Then for the sequence generated $(y_k, x_k, v_k)_{k \ge 0}$ by the algorithm, for all $k \ge 0$ they satisfy: 
+        \begin{align*}
+            & F(x_k) - F(\bar x) + \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2
+            \le 
+            \beta_k \left(
+                \frac{L_0}{2}\Vert \bar x - v_{-1}\Vert^2
+                + \mathcal E_0 \sum_{i = 1}^{k} \frac{1}{n^p}
+            \right). 
+        \end{align*}
+    \end{proposition}
+    \begin{proof}
+        Conside results from Lemma \ref{lemma:inxt-apg-cnvg-prep1} has $\forall k \ge 1$: 
+        \begin{align*}
+            & \frac{\rho_k}{2}\Vert x_k - y_k\Vert^2 - \epsilon_k
+            \\
+            &\le 
+            (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x)) + F(\bar x) - F(x_k) 
+            \\ &
+            + \max\left(
+                    1 - \alpha_k, \frac{\alpha_k^2L_k}{\alpha_{k - 1}^2L_{k - 1}}
+                \right)\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2 
+            - \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2. 
+            \\
+            &\le \max\left(
+                1 - \alpha_k, \frac{\alpha_k^2L_k}{\alpha_{k - 1}^2L_{k - 1}}
+            \right)\left(
+                F(x_{k - 1}) - F(\bar x)
+                + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2 
+            \right)
+            \\&\quad 
+                + F(\bar x) - F(x_k) - \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2
+        \end{align*}
+        For notation brevity, we introduce $\beta_k, \Lambda_k$: 
+        \begin{align*}
+            \beta_0 &= 1, 
+            \\
+            \beta_k &:= \prod_{i = 1}^{k} \max\left(
+                1 - \alpha_i, \frac{\alpha_i^2L_i}{\alpha_{i - 1}^2L_{i - 1}}
+            \right),
+            \\
+            \Lambda_k &:= 
+            - F(\bar x) + F(x_k) + \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2. 
+        \end{align*}
+        Now, suppose that in addition there is a non-negative sequence $(\mathcal  E_k)_{k \ge 0}$ such that 
+        \begin{enumerate}[nosep]
+            \item For all $k \ge 0$, it has $\frac{-\mathcal E_k}{k^p} \le \frac{\rho_k}{2}\Vert x_k - y_k\Vert^2 - \epsilon_k$ where $p \ge 1$, 
+            \item For all $k \ge 1$, it has $\mathcal E_k = \frac{\beta_k}{\beta_{k - 1}}\mathcal E_{k - 1}$, with $\mathcal E_0 \ge 0$. 
+        \end{enumerate}
+        These conditions are equivalent to the assumption that $\frac{- \mathcal E_0\beta_k}{k^p} \le \frac{\rho_k}{2}\Vert x_k - y_k\Vert^2 - \epsilon_k$. 
+        One can show that by unrolling recurrence on $\mathcal E_k$. 
+        Then \eqref{ineq:inxt-apg-cnvg-generic-pitem-1} implies $\forall k \ge 1$: 
+        \begin{align}\label{ineq:inxt-apg-cnvg-generic-pitem-1}
+            \frac{- \mathcal E_k}{k^p} &\le 
+            \frac{\beta_k}{\beta_{k - 1}}\Lambda_{k - 1} - \Lambda_k
+            \iff 
+            \Lambda_k \le 
+            \frac{\beta_k}{\beta_{k - 1}}\Lambda_{k - 1} + \frac{\mathcal E_k}{k^p}. 
+        \end{align}
+        Now, we show the convergence of $\Lambda_k$, using the relations of $\mathcal E_k, \Lambda_k, \beta_k$ above. 
+        \begin{align*}\begin{split}
+            \Lambda_k &\le 
+            \frac{\beta_k}{\beta_{k - 1}}\Lambda_{k - 1} + \frac{\mathcal E_k}{k^p}
+            \\
+            &\le \frac{\beta_k}{\beta_{k - 1}}\Lambda_{k - 1} 
+            + \frac{\beta_k}{\beta_{k -1}}\frac{\mathcal E_{k - 1}}{k^p}
+            \\
+            &= 
+            \frac{\beta_k}{\beta_{k - 1}}
+            \left(
+                \Lambda_{k - 1} + \frac{\mathcal E_{k - 1}}{k^p}
+            \right)
+            \\
+            &\le 
+            \frac{\beta_k}{\beta_{k - 1}}
+            \left(
+                \frac{\beta_{k - 1}}{\beta_{k - 2}}\Lambda_{k - 2}
+                + \frac{\mathcal E_{k - 1}}{(k - 1)^p}
+                + \frac{\mathcal E_{k - 1}}{k^p}
+            \right)
+            \\
+            &= 
+            \frac{\beta_k}{\beta_{k - 2}}
+            \left(
+                \Lambda_{k - 2}
+                + \frac{\mathcal E_{k - 2}}{(k - 1)^p}
+                + \frac{\mathcal E_{k - 2}}{k^p}
+            \right)
+            \\
+            & ...
+            \\
+            &\le \frac{\beta_k}{\beta_1}\left(
+                \Lambda_1 + \mathcal E_1\sum_{n = 2}^{k} \frac{1}{n^p}
+            \right)
+            \\
+            &\le \frac{\beta_k}{\beta_1}\left(
+                \frac{\beta_1}{\beta_0}\Lambda_0 
+                + \mathcal E_1\sum_{n = 1}^{k} \frac{1}{n^p}
+            \right)
+            \\
+            &= \frac{\beta_k}{\beta_0}\left(
+                \Lambda_0 
+                + \mathcal E_0\sum_{n = 1}^{k} \frac{1}{n^p}
+            \right). 
+        \end{split}\end{align*}
+        Therefore it points to the following inequality: 
+        \begin{align*}
+            & F(x_k) - F(\bar x) + \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2
+            \\
+            &\le 
+            \beta_k \left(
+                F(x_0) - F(\bar x) + \frac{\alpha_0^2L_0}{2}\Vert \bar x - v_0\Vert^2
+                + \mathcal E_0 \sum_{i = 1}^{k} \frac{1}{n^p}
+            \right). 
+        \end{align*}
+        Finally, when $\alpha_0 = 1$, then the results from \ref{lemma:inxt-apg-cnvg-prep1} with $k = 0$ simplifies the above inequality and give: 
+        \begin{align*}
+            & F(x_k) - F(\bar x) + \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2
+            \le 
+            \beta_k \left(
+                \frac{L_0}{2}\Vert \bar x - v_{-1}\Vert^2
+                + \mathcal E_0 \sum_{i = 1}^{k} \frac{1}{n^p}
+            \right). 
+        \end{align*}
+    \end{proof}
+    \par
+    Now, it only remains to determine the sequence $\alpha_k$ to derive a type of convergence rate for the algorithm because from the above theorem, we have the convergence rate $\beta_k$ and, the error parameters $\epsilon_k, \rho_k$ both controlled by the sequence $(\alpha_k)_{k \ge 0}$.
+
 \bibliographystyle{siam}

### 2025-09-26 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

@@
         \begin{theorem}[primal translate to dual]\label{thm:primal-dual-trans}
-            Let $(g, \omega, A)$ satisfies Assumptiom \ref{ass:for-inxt-prox}, $\epsilon \ge 0$, then 
+            Let $(g, \omega, A)$ satisfies assumption \ref{ass:for-inxt-prox}, $\epsilon \ge 0$, then 
             \begin{align*}
@@
         \end{theorem}
-        Next, let's explore some options for minimizing the duality gap of the proximal problem. 
+        The following fact from the literature indicates that it's sufficient to minimize the dual problem $\Psi_\lambda$ to obtain an element of the inexact proximal point operator. 
+        The following fact is Proposition \cite[Theorem 5.1]{villa_accelerated_2013}. 
+        \begin{fact}[minimizing dual of the proximal problem]
+            Let $\bar v$ be a solution of $\Psi$. 
+            Suppose that $(v_n)_{n \ge 0}$ is a minimizing sequence for $\Psi$. 
+            Let $z_n = y - \lambda A^\top v_n$, and $\bar z = y - \lambda A^\top \bar v$. 
+            If in addition, $\Phi_\lambda$ is $L_1$ Lipschitz continuous, then it has for all $k \ge 0$ the inequality: 
+            \begin{align*}
+                \Phi_{\lambda}(z_n) - \Phi_\lambda(\bar x) 
+                &\le L_1 \Vert z_n - \bar z\Vert 
+                \le L_1\sqrt{2\lambda}(\Psi_\lambda(v_n) - \Psi_\lambda(\bar v))^{1/2}. 
+            \end{align*}
+        \end{fact}
+        We remark that the above fact translates any algorithm that optimizes the function value of the dual problem into optimizing duality gap $\mathbf G(z_n, v_n)$. 
+        For this reasons, the inner loop interation required to achieve $\mathbf G(z_n, v_n) < \epsilon$ is now related to the convergence rate of the algorithms used to optimize $\Psi_\lambda(v_n)$. 
         \todoinline{
@@
     \subsection{Literature reviews}
+
     \subsection{Our contributions}
@@
         Denote $L_k = B_k + \rho_k$ for short. 
-        Given any initial condition $v_{-1}, x_{-1} \in \RR^n$, the algorithm generates the sequences $(y_k, x_k, v_k)_{k \ge 0}$ such that they satisfies for all $k \ge 0$: 
+        Given any initial condition $v_{-1}, x_{-1} \in \RR^n$, the algorithm generates the sequences $(y_k, x_k, v_k)_{k \ge 0}$ such that they satisfy for all $k \ge 0$: 
         \begin{align*}
@@
         \end{align*}
-        When, $k = 1$ it instead have: 
+        When, $k = 1$ it instead has: 
         \begin{align*}
@@
                 \frac{L_0}{2}\Vert \bar x - v_{-1}\Vert^2
-                + \mathcal E_0 \sum_{i = 1}^{k} \frac{1}{n^p}
+                + \mathcal E_0 \sum_{n = 1}^{k} \frac{1}{n^p}
             \right). 
@@
     \begin{proof}
-        Conside results from Lemma \ref{lemma:inxt-apg-cnvg-prep1} has $\forall k \ge 1$: 
+        Consider results from Lemma \ref{lemma:inxt-apg-cnvg-prep1} has $\forall k \ge 1$: 
         \begin{align*}
@@
         \begin{enumerate}[nosep]
-            \item For all $k \ge 0$, it has $\frac{-\mathcal E_k}{k^p} \le \frac{\rho_k}{2}\Vert x_k - y_k\Vert^2 - \epsilon_k$ where $p \ge 1$, 
+            \item For all $k \ge 0$, it has $\frac{-\mathcal E_k}{k^p} \le (\rho_k/2)\Vert x_k - y_k\Vert^2 - \epsilon_k$ where $p \ge 1$, 
             \item For all $k \ge 1$, it has $\mathcal E_k = \frac{\beta_k}{\beta_{k - 1}}\mathcal E_{k - 1}$, with $\mathcal E_0 \ge 0$. 
@@
         \end{split}\end{align*}
-        Therefore it points to the following inequality: 
+        Therefore, it points to the following inequality: 
         \begin{align*}
@@
                 F(x_0) - F(\bar x) + \frac{\alpha_0^2L_0}{2}\Vert \bar x - v_0\Vert^2
-                + \mathcal E_0 \sum_{i = 1}^{k} \frac{1}{n^p}
+                + \mathcal E_0 \sum_{n = 1}^{k} \frac{1}{n^p}
             \right). 
@@
 
+\section{Linear convergence for the inner loop proximal problem}
+
 \bibliographystyle{siam}

### 2025-09-26 Notebook LaTEX/R-WAPG/presentation-shorter.tex
>w<, changes

@@
     University of British Columbia Okanagan
+    \\
+    WCOM 2025
 }
-\date[\today]{\today \\ \vspace{1cm} \tiny{Joint work with Shawn/Xianfu Wang}}
+\date[\today]{
+    \today \\ \vspace{1cm} 
+    \tiny{Joint work with Shawn/Xianfu Wang}\\ 
+    \tiny{The research of HL and XW was partially supported by the NSERC Discovery Grant of Canada.}
+    \tiny{We respectfully acknowledge that the UBC Okanagan academic campus is situated on the traditional, ancestral, unceded territory of the Syilx Okanagan Nation}
+}
+
 \subject{Nesterov's acceleration and its applications}
@@
         \begin{proposition}[Alternative representations of the iterates]\label{prop:wapg-first-equivalent-repr}
-            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}), and $\alpha_0 = 1, x_1 = v_1$. 
-            Then they satisfy for all $k\ge 1$: 
+            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}), and $\alpha_0 = 1, x_1 = v_1$, then they satisfy for all $k\ge 1$: 
             {\footnotesize
@@
         \begin{proposition}[R-WAPG convergence]\label{prop:wapg-convergence}
-            Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$.
+            Fix any arbitrary $x^* \in \RR^n$.
             Let $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ be R-WAPG sequences.
             Let vector sequences $(y_k, v_{k}, x_{k})_{k \ge 1}$ be given by Definition \ref{def:wapg}. 
-            Then for all $k = 1, 2, \ldots, N$:
+            Then for all $k \ge 1$:
             {\small

### 2025-09-30 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

@@
         \begin{remark}
-            $\partial_\epsilon g$ is a multivalued operator and, it's not monotone, unless $\epsilon = 0$, which makes it equivalent to French subgradient $\partial g$. 
+            $\partial_\epsilon g$ is a multivalued operator and, it's not monotone, unless $\epsilon = 0$, which makes it equivalent to Fenchel subgradient $\partial g$. 
         \end{remark}
@@
         \end{assumption}
-        We develop the theory based on the use of epsilon subgradient as in Definition \ref{def:esp-subgrad}. 
+        No, we develop the theory based on the use of epsilon subgradient as in Definition \ref{def:esp-subgrad}. 
         \begin{definition}[inexact proximal gradient]\label{def:inxt-pg}
@@
         \end{remark}
-        \begin{lemma}[other representations of inexact proximal gradient]\;\\
+        \begin{lemma}[other representations of inexact proximal gradient]\;\label{lemma:other-repr-inxt-pg}\\
             Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, $\epsilon \ge 0, \rho > 0$, then for all $x \approx_\epsilon T_\rho(x)$, it has the following equivalent representations: 
@@
         \end{proof}
+        \begin{remark}
+            When $\epsilon = 0, \rho = 0$, this reduces to proximal gradient inequality in the exact case. 
+        \end{remark}
     \subsection{Optimizing the inexact proximal point problem}
         In this section we will show an optimization problem that allows us to solve for some $\tilde x \approx_\epsilon \hprox_{\lambda g}(z)$. 
+        Eventually we want to evaluate $T_{\rho}(x)$ of some $F = f + g$ inexactly and, by Lemma \ref{lemma:other-repr-inxt-pg}, one can achieve that through inexact evaluation of $\hprox_{\rho^{-1}g}$ in the sense of Definition \ref{def:inxt-pp}.
         Most of these results are from the literature. 
@@
         Fix $y \in \RR^n, \lambda > 0$, we are ultimately interested in minimizing: 
-        \begin{align}
+        \begin{align}\label{eqn:primal-pp}
             \Phi_\lambda(u) &:= \omega(Au) + \frac{1}{2\lambda} \Vert u - y\Vert^2
@@
         This problem admits dual objective in $\RR^m$: 
-        \begin{align}
+        \begin{align}\label{eqn:dual-pp}
             \Psi_\lambda(v) &:=
@@
         The following fact is Proposition \cite[Theorem 5.1]{villa_accelerated_2013}. 
-        \begin{fact}[minimizing dual of the proximal problem]
+        \begin{fact}[minimizing dual of the proximal problem]\label{fact:minimizing-dual-pp}
             Let $\bar v$ be a solution of $\Psi$. 
@@
             \begin{align*}
-                \Phi_{\lambda}(z_n) - \Phi_\lambda(\bar x) 
+                \Phi_{\lambda}(z_n) - \Phi_\lambda(\bar z) 
                 &\le L_1 \Vert z_n - \bar z\Vert 
@@
         We remark that the above fact translates any algorithm that optimizes the function value of the dual problem into optimizing duality gap $\mathbf G(z_n, v_n)$. 
-        For this reasons, the inner loop interation required to achieve $\mathbf G(z_n, v_n) < \epsilon$ is now related to the convergence rate of the algorithms used to optimize $\Psi_\lambda(v_n)$. 
-        \todoinline{
-            STILL WRITING AND NOT FINISHED YET! 
-        }
+        For this reason, the number of iterations of the inner loop required to achieve $\mathbf G(z_n, v_n) < \epsilon$ for a given $e$ is related to the convergence rate of the algorithms used to optimize $\Psi_\lambda(v_n)$.
     \subsection{Literature reviews}
@@
 \section{Linear convergence for the inner loop proximal problem}
+    In this section, we continue the discussion from \textcolor{red}{[REF PREVIOUS SECTION]}. 
+    The inner loop of the algorithm evaluates $x_k \approx_\epsilon T_{(B + \rho)}(y_k)$ for a given value of $\epsilon$. 
+    To attain $x_k$, one approach is to utilise Theorem \ref{thm:dlty-gap-inxt-pp} numerically, usually using iterative algorithms. 
+    \par
+    The following assumption places additional assumption to the proximal problem for the inner loop. 
+    \begin{assumption}[gradient mapping error bound]\;\label{ass:pg-eb}\\
+        The following assumption is about $(F, f, g, L, S, \gamma)$. 
+        Assume that
+        \begin{enumerate}[nosep]
+            \item $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, 
+            \item Let $\tau > 0$ be the step size inverse, let $T_{\tau}$ be the proximal operator of $f + g$ as given by $T_{\tau}(x) := \hprox_{\tau^{-1}g}(x - \tau^{-1}\nabla f(x))$, 
+            \item the gradient mapping $\mathcal G_{\tau}$ be given by: $\mathcal G_t(x) = \tau (x - T_t(x))$, 
+            \item $S= \argmin_{x}{f(x) + g(x)} \neq \emptyset$, 
+            \item the objective function is given by $F = f + g$. 
+        \end{enumerate}        
+        In addition, assume that the optimization problem $F$ satisfies the error bound condition if it has for all $\tau \ge L, x \in \RR^n$ there exists $\gamma > 0$: 
+        \begin{align*}
+            \Vert \mathcal G_\tau(x)\Vert \ge \gamma\dist(x|S). 
+        \end{align*}
+    \end{assumption}
+    \begin{definition}[proximal gradient method]\label{def:ista}
+        Suppose that $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}. 
+        Let $\tau \ge L$, and $x_0 \in \RR^n$. 
+        Then an algorithm is a proximal gradient method if it generates iterates $(x_k)_{k \ge 0}$ such that they satisfies for all $k \ge 1$: 
+        \begin{align*}
+            x_{k + 1} = \hprox_{\tau^{-1} g}\left(x_k + \tau^{-1}\nabla f(x_k)\right). 
+        \end{align*}
+    \end{definition}
+    \begin{assumption}[error bound for proximal problem]\;\label{ass:eb-for-pp}\\
+        This assumption is about $(g, \omega, A, \Psi_\lambda, \gamma)$
+        Here are the assumptions
+        \begin{enumerate}[nosep]
+            \item $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
+            \item In addition, function $\Psi_\lambda$ as given by \eqref{eqn:primal-pp} satifies gradient mapping error bound (Assumption \ref{ass:pg-eb}) where, $f(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2, g(v) = \omega(A v) - \frac{1}{2\lambda}\Vert y\Vert^2$.
+        \end{enumerate}
+    \end{assumption}
+    \subsection{error bound and linear convergence}
+        The following theorem characterize linear convergence of the proximal gradient method under gradient mapping error bound condition. 
+        \begin{theorem}[linear convergence under gradient mapping error bound]\;\label{thm:lin-cnvg-ista-eb}\\
+            Assume that $(F, f, g, L, S, \gamma)$ is given by Assumption \ref{ass:pg-eb}. 
+            Under this assumption, the iterates $(x_k)_{k \ge 0}$ given by Definition \ref{def:ista} satisfies for all $k \ge 0, \bar x \in S$ the inequality: 
+            \begin{align*}
+                F(x_{k + 1}) - F(\bar x)
+                &\le 
+                \left(
+                    1 - \frac{\gamma}{2\tau}
+                \right)(F(x_k) - F(\bar x)). 
+            \end{align*}
+            Hence, the algorithm generates $F(x_k) - F(\bar x)\le \mathcal O((1 - \gamma/(2\tau))^k)$. 
+        \end{theorem}
+        \begin{proof}
+            Two important immediate results will be presented first.
+            Consider the proximal gradient inequality from \ref{thm:inxt-pg-ineq}, but with $\rho = 0, \epsilon = 0, B = \tau$, then for all $x$ such that $\Vert \mathcal G_\tau(x)\Vert > 0$ it has for $\tilde x = T_{\tau}(x), z \in \RR^n$ the inequality
+            \begin{align*}
+                0 &\le 
+                F(z) - F(\tilde x) + \frac{\tau}{2}\Vert x - z\Vert^2 - \frac{\tau}{2}\Vert z - \tilde x\Vert^2
+                \\
+                &=  
+                F(z) - F(\tilde x) - \frac{\tau}{2}\Vert x - \tilde x\Vert^2
+                + \tau\langle x - z, x - \tilde x\rangle
+                \\
+                &= F(z) - F(\tilde x) - \frac{1}{2\tau}\Vert \mathcal G_\tau(x) \Vert^2
+                + \langle x - z, \mathcal G_\tau(x)\rangle
+                \\
+                &\le F(z) - F(\tilde x) - \frac{1}{2\tau}\Vert \mathcal G_\tau(x)\Vert^2 
+                + \Vert x - z\Vert \Vert \mathcal G_\tau(x)\Vert
+                \\
+                &= 
+                F(z) - F(\tilde x) 
+                + \Vert \mathcal G_\tau(x)\Vert^2\left(
+                    \frac{\Vert x - z \Vert}{\Vert \mathcal G_\tau(x)\Vert} - \frac{1}{2\tau}
+                \right). 
+            \end{align*}
+            Now, for all $z = \bar x \in S$, from Assumption \ref{ass:eb-for-pp} it has
+            \begin{align*}
+                \frac{\Vert x - z \Vert}{\Vert \mathcal G_\tau(x)\Vert}
+                \le 
+                \frac{\Vert x - z \Vert}{\gamma \dist(x | S)} \le \frac{1}{\gamma}. 
+            \end{align*}
+            Hence for all $\bar x \in S$ it has 
+            \begin{align}\label{ineq:lin-cnvg-ista-eb-pitem1}
+                0\le F(\tilde x) - F(\bar x)&\le 
+                \Vert \mathcal G_\tau(x)\Vert^2\left(
+                    \frac{1}{\gamma} - \frac{1}{2\tau}
+                \right). 
+            \end{align}
+            Obviously it has $\gamma^{-1} - (1/2)\tau^{-1} > 0$. 
+            When $z = x$, we have the inequality: 
+            \begin{align}\label{ineq:lin-cnvg-ista-eb-pitem2}
+                F(\tilde x) - F(x) &\le - \frac{1}{2\tau}\Vert \mathcal G_\tau(x)\Vert^2. 
+            \end{align}
+            To derive the linear convergence, we use \eqref{ineq:lin-cnvg-ista-eb-pitem1} with $x = x_k, \tilde x = x_{k + 1}$:
+            {\allowdisplaybreaks
+            \begin{align*}
+                0 &\le 
+                \Vert \mathcal G_\tau(x_k)\Vert^2\left(
+                    \frac{1}{\gamma} - \frac{1}{2\tau} 
+                \right)
+                - F(x_{k + 1}) + F(\bar x)
+                \\
+                &= 
+                \frac{1}{2\tau}\Vert \mathcal G_\tau(x_k)\Vert^2\left(
+                    \frac{2\tau}{\gamma} - 1
+                \right)
+                - F(x_{k + 1}) + F(\bar x)
+                \\
+                &\underset{(1)}{\le}
+                \left(
+                    \frac{2\tau}{\gamma} - 1
+                \right)
+                \left(
+                    F(x_k) - F(x_{k + 1})
+                \right)
+                - F(x_{k + 1}) + F(\bar x)
+                \\
+                &= 
+                \left(
+                    \frac{2\tau}{\gamma} - 1
+                \right)
+                \left(
+                    F(x_k) - F(\bar x) + F(\bar x) - F(x_{k + 1})
+                \right)
+                - F(x_{k + 1}) + F(\bar x)
+                \\
+                &= \frac{2\tau}{\gamma}(F(\bar x) - F(x_{k + 1}))
+                + \left(
+                    \frac{2\tau}{\gamma} - 1
+                \right)(F(x_k) - F(\bar x)). 
+            \end{align*}
+            }
+            At (1) we used \eqref{ineq:lin-cnvg-ista-eb-pitem2}. 
+            Multiple bothside by $\frac{\gamma}{2\tau}$ then we are done. 
+        \end{proof}
+
+    \subsection{characterizing linear convergence of the proximal problem}
 

### 2025-10-02 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

@@
 
-\title{{\fontfamily{ptm}\selectfont Inexect Accelerated Proximal Gradient }}
+\title{{\fontfamily{ptm}\selectfont Inexact Accelerated Proximal Gradient }}
 
@@
         No, we develop the theory based on the use of epsilon subgradient as in Definition \ref{def:esp-subgrad}. 
+        Let $\rho > 0$, the exact proximal gradient operator defined for $(f, g, L)$ satisfying Assumption \ref{ass:for-inxt-pg-ineq} has
+        \begin{align*}
+            T_{\rho}(x) &= \argmin_{z\in\RR^n}\left\lbrace g(z) + \langle \nabla f(x), z\rangle + \frac{\rho}{2}\Vert z - x\Vert^2 \right\rbrace
+            \\
+            &= \hprox_{\rho^{-1} g}\left(x - \rho^{-1}\nabla f(x)\right). 
+        \end{align*}
+        The following definition extends the proximal gradient operator to the inexact case using the concept of $\epsilon$-subgradient as given by Definition \ref{def:esp-subgrad}. 
         \begin{definition}[inexact proximal gradient]\label{def:inxt-pg}
@@
         \begin{lemma}[other representations of inexact proximal gradient]\;\label{lemma:other-repr-inxt-pg}\\
-            Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, $\epsilon \ge 0, \rho > 0$, then for all $x \approx_\epsilon T_\rho(x)$, it has the following equivalent representations: 
+            Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, $\epsilon \ge 0, \rho > 0$, then for all $\tilde x \approx_\epsilon T_\rho(x)$, it has the following equivalent representations:
             \begin{align*}
@@
             At (2), we used the fact that $f$ is convex hence $- D_f(z, x) \le 0$ always, and in the statement hypothesis we assumed that $B$ has $D_f(\tilde x, x) \le B/2\Vert \tilde x - x\Vert^2$. 
+            We also used $F = f + g$. 
         \end{proof}
@@
             When $\epsilon = 0, \rho = 0$, this reduces to proximal gradient inequality in the exact case. 
+            In this inequality, observe that the parameter $\epsilon$ controls the inexactiness of the proximal gradient evaluation. 
+            Morespecifically, $\epsilon_k$ controls the absolute pertubatnions of the proximal gradient inequality compared to its exact counterpart. 
+            $\rho$ on the otherhand, it is the over-relaxation of proximal gradient operator and it compensates the pertubations caused by $\epsilon$ relative to the term $\Vert \tilde x - x\Vert^2$. 
         \end{remark}
     \subsection{Optimizing the inexact proximal point problem}
-        In this section we will show an optimization problem that allows us to solve for some $\tilde x \approx_\epsilon \hprox_{\lambda g}(z)$. 
-        Eventually we want to evaluate $T_{\rho}(x)$ of some $F = f + g$ inexactly and, by Lemma \ref{lemma:other-repr-inxt-pg}, one can achieve that through inexact evaluation of $\hprox_{\rho^{-1}g}$ in the sense of Definition \ref{def:inxt-pp}.
-        Most of these results are from the literature. 
+        In this section we will present the optimization problem that obtains a $\tilde x$ such that $\tilde x \approx_\epsilon \hprox_{\lambda g}(z)$. 
+        Eventually we want to evaluate $T_{\rho}(x)$ of some $F = f + g$ inexactly using Lemma \ref{lemma:other-repr-inxt-pg}. 
+        To do that one would need to evaluate $\hprox_{\rho^{-1}g}$ inexactly which is defined in Definition \ref{def:inxt-pp}. 
+        \par
+        Most of these results that will follow are from the literature. 
         To start, we must assume the following about a function $g: \RR^n \rightarrow \overline \RR$, with $g$ closed, convex and proper. 
@@
         The theorem below is from \cite[Proposition 2.2]{villa_accelerated_2013}. 
-        \begin{theorem}[primal translate to dual]\label{thm:primal-dual-trans}
+        \begin{theorem}[primal translate to dual {\cite[Proposition 2.2]{villa_accelerated_2013}}]\label{thm:primal-dual-trans}
             Let $(g, \omega, A)$ satisfies assumption \ref{ass:for-inxt-prox}, $\epsilon \ge 0$, then 
@@
         \end{theorem}
-        This theorem that follows is from Villa et al. \cite[Proposition 2.3]{villa_accelerated_2013}, but put into our symbols and, Definition 
-        \begin{theorem}[duality gap of inexact proximal problem]\label{thm:dlty-gap-inxt-pp}
+        This theorem that follows is from Villa et al. \cite[Proposition 2.3]{villa_accelerated_2013}. 
+        \begin{theorem}[duality gap of inexact proximal problem {\cite[Proposition 2.3]{villa_accelerated_2013}}]\;\label{thm:dlty-gap-inxt-pp}\\
             Let $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}, for all $\epsilon \ge 0$, $v \in \RR^n$ consider the following conditions: 
@@
         The following fact from the literature indicates that it's sufficient to minimize the dual problem $\Psi_\lambda$ to obtain an element of the inexact proximal point operator. 
-        The following fact is Proposition \cite[Theorem 5.1]{villa_accelerated_2013}. 
-        \begin{fact}[minimizing dual of the proximal problem]\label{fact:minimizing-dual-pp}
-            Let $\bar v$ be a solution of $\Psi$. 
-            Suppose that $(v_n)_{n \ge 0}$ is a minimizing sequence for $\Psi$. 
+        The following fact is Proposition is from Villa et al. \cite[Theorem 5.1]{villa_accelerated_2013}. 
+        \begin{fact}[minimizing dual of the proximal problem {\cite[Theorem 5.1]{villa_accelerated_2013}}]\label{fact:minimizing-dual-pp}
+            Let $\bar v$ be a solution of $\Psi_\lambda$. 
+            Suppose that $(v_n)_{n \ge 0}$ is a minimizing sequence for $\Psi_\lambda$. 
             Let $z_n = y - \lambda A^\top v_n$, and $\bar z = y - \lambda A^\top \bar v$. 
@@
         \end{fact}
-        We remark that the above fact translates any algorithm that optimizes the function value of the dual problem into optimizing duality gap $\mathbf G(z_n, v_n)$. 
-        For this reason, the number of iterations of the inner loop required to achieve $\mathbf G(z_n, v_n) < \epsilon$ for a given $e$ is related to the convergence rate of the algorithms used to optimize $\Psi_\lambda(v_n)$.
+        We remark that the above fact translates any algorithm that optimizes the function value of the dual problem $\Psi_\lambda$ into optimizing duality gap $\mathbf G(z_n, v_n)$. 
+        For this reason, the number of iterations of the inner loop required to achieve $\mathbf G(z_n, v_n) < \epsilon$ for a given $\epsilon$ is related to the convergence rate of the algorithms used to optimize $\Psi_\lambda(v_n)$.
+        With the theorem derived above, and using Theorem \ref{thm:dlty-gap-inxt-pp} it implies that any algorithm which can optimize function value $\Psi_\lambda$ will produce iterates sufficient to achieve $\approx_\epsilon \hprox_{\lambda g}(y)$.
     \subsection{Literature reviews}
@@
 
-\section{The accelerated proximal gradient with controlled errors}
+\section{The inexact accelerated proximal gradient with controlled errors}
     In this section, we present an accelerated algorithm with controlled error using Definition \ref{def:inxt-pg}, and show that it can have a convergence rate under certain error conditions. 
@@
             \item $(\alpha_k)_{k \ge 0}$ is a sequence such that $\alpha \in (0, 1]$ for all $k \ge 0$. 
-            \item $(B_k)_{k \ge 0}$ is a non-negative sequence, characterizing the potential line search routine. 
+            \item $(B_k)_{k \ge 0}$ is a non-negative sequence, characterizing any potential line search routine. 
             \item $(\rho_k)_{k \ge 0}$ be a sequence such that $\rho_k > 0$, characterizing the over-relaxation of the proximal gradient operator. 
@@
     \begin{lemma}[inexact accelerated proximal gradient preparation stage I]\; \label{lemma:inxt-apg-cnvg-prep1}\\
-        Let $(f, g, L)$, and $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, be given by Definition \ref{def:inxt-apg}. 
+        Let $(F, f, g, L)$, and $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, be given by Definition \ref{def:inxt-apg}. 
         Denote $L_k = B_k + \rho_k$. 
@@
     \par
-    The following proposition is a prototype of the convergence rate together with the error schedule that delivers convergence of algorithms satisfying Definition \ref{def:inxt-apg}. 
-    \begin{proposition}[valid error schedule and convergence rate]\;\label{prop:inxt-apg-cnvg-generic}\\
-        Let $(f, g, L)$, $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$ be given by Definition \ref{def:inxt-apg}. 
-        Fix any $\bar x \in \RR^n$ for all $k \ge 0$ and assume that $\alpha_0 = 1$. 
-        Denote for brevity $\beta_0 = 1$, $\beta_k = \prod_{i = 1}^{k} \max\left(1 - \alpha_i, \frac{\alpha_i^2L_i}{\alpha_{i - 1}^2L_{i - 1}}\right)$ and $L_k = B_k + \rho_k$. 
-        If for some fixed $\mathcal E_0 \ge 0, p \ge 1$ the parameter $\rho_k, \epsilon_k$ can satisfy for all $k \ge 0$ the condition
+    The following assumption encapsulate assumptions on the errors such that a near optimal convergence rate is still attainable by an algorithm that satisfies Definition \ref{def:inxt-apg}. 
+    \begin{assumption}[valid error schedule]\label{ass:valid-err-schedule}
+        The following assumption is about an algorithm satisfying Definition \ref{def:inxt-apg}, its parameters $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$ in relation to its iterates $(y_k, x_k, v_k)_{k\ge 0}$ and, some additional parameters $(\beta_k)_{k\ge 0}, \mathcal E_0$ and $p$.
+        Let 
+        \begin{enumerate}[nosep]
+            \item $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}, (F, f, g, L)$ and $(y_k, x_k, v_k)_{k\ge 0}$ be given by Definition \ref{def:inxt-apg}. 
+            \item $\mathcal E_0 \ge 0$ be arbitrary;
+            \item the sequence $(\beta_k)_{k\ge 0}$ be defined as $\beta_k := \prod_{i = 1}^{k} \max\left(1 - \alpha_i, \frac{\alpha_i^2L_i}{\alpha_{i - 1}^2L_{i - 1}}\right)$ for all $k \ge 1$, with the base case being $\beta_0 = 1$;
+            \item $p \ge 1$ is some constant which will bound the error $\epsilon_k$ relative to $\rho_k$. 
+        \end{enumerate}
+        In addition, we assume that the error parameter $\epsilon_k$ and over-relaxation parameter $\rho_k$, iterates $x_k, y_k$ and $\beta_k$ together satisfies for all $k \ge 0$ the relations:
         \begin{align*}
@@
         \end{align*}
-        Then for the sequence generated $(y_k, x_k, v_k)_{k \ge 0}$ by the algorithm, for all $k \ge 0$ they satisfy: 
+
+    \end{assumption}
+    \par
+    The following proposition is a prototype of the convergence rate together with the error schedule that delivers convergence of algorithms satisfying Definition \ref{def:inxt-apg}. 
+    \begin{proposition}[generic convergence rate under valid error schedule]\;\label{prop:inxt-apg-cnvg-generic}\\
+        Let $(F, f, g, L)$, $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(\beta_k)_{k\ge 0}, \mathcal E_0, p$ as assumed in Assumption \ref{ass:valid-err-schedule}. 
+        Fix any $\bar x \in \RR^n$ for all $k \ge 0$ and assume that $\alpha_0 = 1$. 
+        Then for the iterates generated $(y_k, x_k, v_k)_{k \ge 0}$ by the algorithm, for all $k \ge 0$ they will satisfy: 
         \begin{align*}
@@
         \end{enumerate}
-        These conditions are equivalent to the assumption that $\frac{- \mathcal E_0\beta_k}{k^p} \le \frac{\rho_k}{2}\Vert x_k - y_k\Vert^2 - \epsilon_k$. 
+        These conditions are equivalent to the assumption that $\frac{- \mathcal E_0\beta_k}{k^p} \le \frac{\rho_k}{2}\Vert x_k - y_k\Vert^2 - \epsilon_k$ (which was stated in Assumption \ref{ass:valid-err-schedule}).
         One can show that by unrolling recurrence on $\mathcal E_k$. 
@@
 
-\section{Linear convergence for the inner loop proximal problem}
+    \subsection{convergence results of the outer loop}
+        This section will give specific instances of the error control sequence $(\epsilon_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ and, momentum sequence $(\alpha_k)_{k \ge0}$ such that an optimal convergence rate of $\mathcal O(1/k^2)$ can be achieved.
+        \begin{proposition}[$\mathcal O(1/k^2)$ optimal convergence rate of the outer loop]\;\label{prop:opt-cnvg-outr-loop}\\
+            Let $(f, g, L)$, $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(\beta_k)_{k\ge 0}, \mathcal E_0, p$ as assumed in Assumption \ref{ass:valid-err-schedule}. 
+            Assume in addition that
+            \begin{enumerate}[nosep]
+                \item there exists $\bar x \in \RR^n$ that is an minimizer of $F = f + g$;
+                \item $\alpha_0 = 1, p > 0$; 
+                \item the sequence $(\alpha_k)_{k\ge 0}$ satisfies for all $k \ge 0$ the equality $(1 - \alpha_k) = \alpha_{k}^2L_k\alpha_{k - 1}^{-2}L_{k - 1}^{-1}$;
+                \item the sequence $L_k := B_k + \rho_k$ is bounded, and there exists an $L_{\max}$ such that for all $k \ge 0$ it has $L_{\max} \ge \max_{k\ge i\ge 0} L_i$. 
+            \end{enumerate}
+            Then, $\alpha_k \in (0, 1]$ hence valid and, it satisfies for all $k \ge 0$: 
+            \begin{align*}
+                & F(x_k) - F(\bar x) + \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2
+                \le 
+                \left(
+                    1 + \frac{k\alpha_0\sqrt{L_0}}{2\sqrt{L_{\max}}}
+                \right)^{-2}\left(
+                    \frac{L_0}{2}\Vert \bar x - v_{-1}\Vert^2
+                    + \mathcal E_0 \sum_{n = 1}^{k} \frac{1}{n^p}
+                \right). 
+            \end{align*}
+            Finally, since $p > 0$ the sum is convergent and hence it has an over all convergence rate $\mathcal O(1/k^2)$. 
+        \end{proposition}
+        \begin{proof}
+            From the assumption that $(\alpha_k)_{k \ge 0}$ has $(1 - \alpha_k) = \alpha_k^2L_k \alpha_0^{-2}L_0^{-1}$ for all $k \ge 0$ and, the definition of $\beta_k$, it yields the following equalities:
+            \begin{align*}
+                \beta_k = \prod_{i = 1}^k \max\left(
+                    1 - \alpha_i, \frac{\alpha_i^2L}{\alpha_{i - 1}^2L_{i - 1}}
+                \right) 
+                = \prod_{i = 1}^k(1 - \alpha_i) 
+                = \prod_{i = 1}^k \frac{\alpha_i^2L}{\alpha_0^2L_0} = \frac{\alpha_k^{2}L_k}{\alpha_0^2L_0}. 
+            \end{align*}
+            With the above relation, and the definitions of the sequences $(\alpha_k)_{k \ge 0}, (\beta_k)_{k\ge 0}$ it satisfies for all $k \ge 1$ the properties: 
+            \begin{enumerate}[nosep]
+                \item $\beta_k$ is nonincreasing and $\beta_k > 0$ for all $k \ge 0$ because $\beta_k = \prod_{i = 1}^{k} (1 - \alpha_i)$ and, $\alpha_k \in (0, 1]$. 
+                \item It has the equalities $\beta_k/\beta_{k - 1} = (1 - \alpha_k) = \frac{\alpha_k^2L_k}{\alpha_{k - 1}^2 L_{k - 1}}$ for all $k \ge 1$. 
+            \end{enumerate}
+            Using the above observations, we can show the chain of equalities $\alpha_k^{2} = (1 - \beta_k/\beta_{k - 1})^2 = \beta_kL_0\alpha_0^2L_k^{-1}$ for all $k \ge 0$. 
+            This is true by first considering the relations $\prod_{i = 1}^k(1 - \alpha_i) = \beta_k$: 
+            \begin{align}\label{eqn:opt-cnvg-outr-loop-pitem1}\begin{split}
+                (1 - \alpha_k) &= \beta_k/\beta_{k - 1}
+                \\
+                \iff 
+                \alpha_k &= 1 - \beta_k / \beta_{k - 1}
+                \\
+                \implies 
+                \alpha_k^2 &= (1 - \beta_k / \beta_{k - 1})^2.     
+            \end{split}\end{align}
+            Next, the recursive relation of $(\alpha_k)_{k \ge 0}$ gives
+            \begin{align}\label{eqn:opt-cnvg-outr-loop-pitem2}\begin{split}
+                \alpha_k^2&= (1 - \alpha_k)\alpha_{k - 1}^2L_{k - 1}L_k^{-1}
+                \\
+                &= 
+                (1 - \alpha_k)
+                \frac{\alpha_{k - 1}^2L_{k - 1}}{\alpha_0^2L_0}
+                \frac{L_{k - 1}\alpha_0^2L_0}{L_k}
+                \\
+                &= 
+                (\beta_k\beta_{k - 1}^{-1})\beta_{k - 1}L_0\alpha_0^2L_k^{-1}
+                \\
+                &= \beta_kL_0\alpha_0^2L_k^{-1}.         
+            \end{split}\end{align}
+            Combining \eqref{eqn:opt-cnvg-outr-loop-pitem1}, \eqref{eqn:opt-cnvg-outr-loop-pitem2} it would mean for all $i \ge 1$ it has: 
+            \begin{align*}
+                L_0 \alpha_0^2 L_i^{-1} &= 
+                \beta_i^{-1}\left(
+                    1 - \frac{\beta_k}{\beta_{k - 1}}
+                \right)^2
+                \\
+                &= 
+                \beta_i \left(
+                    \beta_i^{-1} - \beta_{i - 1}^{-1}
+                \right)^2
+                \\
+                &=
+                \beta_i \left(
+                    \beta_i^{-1/2} - \beta_{i - 1}^{-1/2}
+                \right)^2
+                \left(
+                    \beta_i^{-1/2} + \beta_{i - 1}^{-1/2}
+                \right)^2
+                \\
+                &\underset{(1)}{\le} 
+                \beta_i \left(
+                    \beta_i^{-1/2} - \beta_{i - 1}^{-1/2}
+                \right)^2
+                \left(
+                    2\beta_i^{-1/2}
+                \right)^2
+                \\
+                &= 4\left(
+                    \beta_i^{-1/2} - \beta_{i - 1}^{-1/2}
+                \right)^2
+                \\
+                \implies
+                \sqrt{\frac{L_0\alpha_0^2}{L_i}} &\le
+                2 \left(
+                    \beta_i^{-1/2} - \beta_{i - 1}^{-1/2}
+                \right).
+            \end{align*}
+            Telescope for all $i \ge 1$: 
+            \begin{align*}
+                \frac{\alpha_0\sqrt{L_0}}{2}\sum_{i = 1}^{k}\sqrt{L^{-1}_k}
+                &\le 
+                \beta_k^{-1/2} - \beta_{0}^{-1/2} = 
+                \beta_k^{-1/2} - 1. 
+            \end{align*}
+            Re-arranging, yields: 
+            \begin{align*}
+                \beta_k &\le 
+                \left(
+                    1 + \frac{\alpha_0\sqrt{L_0}}{2}\sum_{i = 1}^{k} \sqrt{L_i^{-1}}
+                \right)^{-2}
+                \le 
+                \left(
+                    1 + \frac{k\alpha_0\sqrt{L_0}}{2\sqrt{L_{\max}}}
+                \right)^{-2}. 
+            \end{align*}
+            Recall that $L_k = B_k + \rho_k$, and by our assumptions, the sequence $(B_k)_{k \ge 0}, (\rho_k)_{k\ge 0}$ are both bounded above, then it's not hard to see that $\beta_k \le \mathcal O(1/k^2)$.
+            Combine it with Lemma \ref{lemma:inxt-apg-cnvg-prep1}, using $\alpha_0 = 1$ will yield the desired result. 
+            Finally, one can solves for $\alpha_k$ by the recursive equality, and it should yield:
+
+        \end{proof}
+
+\section{Linear convergence for the proximal problem}
     In this section, we continue the discussion from \textcolor{red}{[REF PREVIOUS SECTION]}. 
     The inner loop of the algorithm evaluates $x_k \approx_\epsilon T_{(B + \rho)}(y_k)$ for a given value of $\epsilon$. 
-    To attain $x_k$, one approach is to utilise Theorem \ref{thm:dlty-gap-inxt-pp} numerically, usually using iterative algorithms. 
+    To attain $x_k$, one approach is to utilize Theorem \ref{thm:dlty-gap-inxt-pp} numerically, usually using iterative algorithms. 
     \par
@@
             \item $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, 
-            \item Let $\tau > 0$ be the step size inverse, let $T_{\tau}$ be the proximal operator of $f + g$ as given by $T_{\tau}(x) := \hprox_{\tau^{-1}g}(x - \tau^{-1}\nabla f(x))$, 
-            \item the gradient mapping $\mathcal G_{\tau}$ be given by: $\mathcal G_t(x) = \tau (x - T_t(x))$, 
+            \item let $\tau > 0$ be the step size inverse, let $T_{\tau}$ be the proximal operator of $f + g$ as given by $T_{\tau}(x) := \hprox_{\tau^{-1}g}(x - \tau^{-1}\nabla f(x))$, 
             \item $S= \argmin_{x}{f(x) + g(x)} \neq \emptyset$, 
@@
         \end{enumerate}   
+        Let the gradient mapping $\mathcal G_{\tau}$ be defined as: $\mathcal G_\tau(x) := \tau (x - T_\tau(x))$     
         In addition, assume that the optimization problem $F$ satisfies the error bound condition if it has for all $\tau \ge L, x \in \RR^n$ there exists $\gamma > 0$: 
@@
         \begin{enumerate}[nosep]
-            \item $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
-            \item In addition, function $\Psi_\lambda$ as given by \eqref{eqn:primal-pp} satifies gradient mapping error bound (Assumption \ref{ass:pg-eb}) where, $f(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2, g(v) = \omega(A v) - \frac{1}{2\lambda}\Vert y\Vert^2$.
+            \item Let function $\Psi_\lambda$ as given by \eqref{eqn:dual-pp} which satisfies gradient mapping error bound (Assumption \ref{ass:pg-eb}) where, $f(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2, g(v) = \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$.
+            \item The primal objective $\Phi_\lambda$ is a $L_1$ Lipschitz continuous on its domain. 
+            \item Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-prox}, we can do this because $f$ is quadratic and has a Lipschitz continuous gradient. 
         \end{enumerate}
@@
             \begin{align*}
-                0 &\le 
-                F(z) - F(\tilde x) + \frac{\tau}{2}\Vert x - z\Vert^2 - \frac{\tau}{2}\Vert z - \tilde x\Vert^2
+                F(\tilde x) - F(z) 
+                &\le 
+                \frac{\tau}{2}\Vert x - z\Vert^2 - \frac{\tau}{2}\Vert z - \tilde x\Vert^2
                 \\
                 &=  
-                F(z) - F(\tilde x) - \frac{\tau}{2}\Vert x - \tilde x\Vert^2
+                - \frac{\tau}{2}\Vert x - \tilde x\Vert^2
                 + \tau\langle x - z, x - \tilde x\rangle
                 \\
-                &= F(z) - F(\tilde x) - \frac{1}{2\tau}\Vert \mathcal G_\tau(x) \Vert^2
+                &=  - \frac{1}{2\tau}\Vert \mathcal G_\tau(x) \Vert^2
                 + \langle x - z, \mathcal G_\tau(x)\rangle
                 \\
-                &\le F(z) - F(\tilde x) - \frac{1}{2\tau}\Vert \mathcal G_\tau(x)\Vert^2 
+                &\le  - \frac{1}{2\tau}\Vert \mathcal G_\tau(x)\Vert^2 
                 + \Vert x - z\Vert \Vert \mathcal G_\tau(x)\Vert
@@
                 &=
-                F(z) - F(\tilde x) 
-                + \Vert \mathcal G_\tau(x)\Vert^2\left(
+                \Vert \mathcal G_\tau(x)\Vert^2\left(
                     \frac{\Vert x - z \Vert}{\Vert \mathcal G_\tau(x)\Vert} - \frac{1}{2\tau}
@@
             \end{align*}
-            Now, for all $z = \bar x \in S$, from Assumption \ref{ass:eb-for-pp} it has
+            Now, for all $z = \bar x \in S$, from Assumption \ref{ass:eb-for-pp} $\exists \gamma > 0$ such that: 
             \begin{align*}
@@
     \subsection{characterizing linear convergence of the proximal problem}
+        In this section, we will focus on the sufficient characterization of the proximal problem which allows proximal gradient method to achieve linear convergence rate. 
+        We can immediately claim quadratic growth condition when $\omega = \Vert \cdot\Vert_1$. 
+        The next proposition will characterize a precise case where Assumption \ref{ass:eb-for-pp} is true, and it's a case widely available in applications. 
+        \begin{proposition}[1-norm problem]
+            Let $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
+            In addition, if $g := \Vert \cdot\Vert_1$, then the function $\Psi_\lambda$ satisfies Assumption \ref{ass:eb-for-pp}. 
+        \end{proposition}
+        \begin{proof}
+            Take note that the dual has closed form $g^\star(z) =\delta(z | \{x : \Vert x\Vert_1 \le 1\})$. 
+            The $g^\star$ is an indicator function which represents a box constraint. 
+            The objective function $\Psi_\lambda(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$ so it's Lipschitz smooth, and it must have a set of minimizers $S$ because its domain is compact.
+            In addition, $\Psi_\lambda$ fits the assumption of Necoara et al. \cite[Theorem 8]{necoara_linear_2019}. 
+            Therefore, $\Psi_\lambda$ is quasi-strongly convex then by \cite[Theorem 4]{necoara_linear_2019}, and \cite[Theorem 7]{necoara_linear_2019}, it satisfies error bound condition as given in Assumption \ref{ass:pg-eb}, hence Assumption \ref{ass:eb-for-pp} also.
+            \par
+            Let $\mu_f = \lambda\Vert A\Vert^2/\kappa_f$, let $\kappa_f = \theta^{-2}(A, C)$ be the Hoffman Constant as presented by Necoara et al.
+in \cite[Section 4]{necoara_linear_2019} where $C$ is the constraint matrix of the inequality set $\delta(z | \{x : \Vert x\Vert_1 \le 1\})$, then the error bound constant can be satisfied with
+            \begin{align*}
+                \gamma = \frac{\kappa_f}{1 + \mu_f + \sqrt{1 + \mu_f}}. 
+            \end{align*}
+
+        \end{proof}
+        The following propositions precisely show that the linear convergence is achievable for the inner loop when $g = \Vert \cdot\Vert_1$ for our optimization objective. 
+        \begin{proposition}[inner loop linear convergence scenario 1]\label{prop:inn-loop-lin-cnvg}
+
+        \end{proposition}
+    \subsection{inner loop complexity}
+
+\section{Total complexity of the algorithm}
+    This section puts results regarding the total complexity of the proposed inexact proximal gradient algorithm.
 

### 2025-10-03 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

@@
             \item $(\alpha_k)_{k \ge 0}$ is a sequence such that $\alpha \in (0, 1]$ for all $k \ge 0$. 
-            \item $(B_k)_{k \ge 0}$ is a non-negative sequence, characterizing any potential line search routine. 
-            \item $(\rho_k)_{k \ge 0}$ be a sequence such that $\rho_k > 0$, characterizing the over-relaxation of the proximal gradient operator. 
-            \item $(\epsilon_k)_{k \ge 0}$ is a non-negative sequence characterizing the errors of inexact proximal evaluation.
+            \item $(B_k)_{k \ge 0}$ has $B_k > 0\; \forall k$, it characterizes any potential line search, back tracking routine. 
+            \item $(\rho_k)_{k \ge 0}$ be a sequence such that $\rho_k \ge 0$, characterizing the over-relaxation of the proximal gradient operator. 
+            \item $(\epsilon_k)_{k \ge 0}$ has $\epsilon_k > 0$ for all $k \ge 0$, it characterizes the errors of inexact proximal evaluation.
             \item $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, and let $F = f + g$. 
@@
             \item the sequence $(\beta_k)_{k\ge 0}$ be defined as $\beta_k := \prod_{i = 1}^{k} \max\left(1 - \alpha_i, \frac{\alpha_i^2L_i}{\alpha_{i - 1}^2L_{i - 1}}\right)$ for all $k \ge 1$, with the base case being $\beta_0 = 1$;
-            \item $p \ge 1$ is some constant which will bound the error $\epsilon_k$ relative to $\rho_k$. 
+            \item $p \ge 1$ is some constant which will bound the error $\epsilon_k$ relative to $\rho_k\Vert x_k - y_k\Vert^2, \beta_k$ and, $k$. 
         \end{enumerate}
-        In addition, we assume that the error parameter $\epsilon_k$ and over-relaxation parameter $\rho_k$, iterates $x_k, y_k$ and $\beta_k$ together satisfies for all $k \ge 0$ the relations:
+        In addition, we assume that the error parameter $\epsilon_k \ge 0$ and over-relaxation parameter $\rho_k$, iterates $x_k, y_k$ and $\beta_k$ together satisfies for all $k \ge 0$ the relations:
         \begin{align*}
@@
         \begin{enumerate}[nosep]
-            \item For all $k \ge 0$, it has $\frac{-\mathcal E_k}{k^p} \le (\rho_k/2)\Vert x_k - y_k\Vert^2 - \epsilon_k$ where $p \ge 1$, 
+            \item For all $k \ge 0$, it has $\frac{-\mathcal E_k}{k^p} \le \frac{\rho_k}{2}\Vert x_k - y_k\Vert^2 - \epsilon_k$ where $p \ge 1$, 
             \item For all $k \ge 1$, it has $\mathcal E_k = \frac{\beta_k}{\beta_{k - 1}}\mathcal E_{k - 1}$, with $\mathcal E_0 \ge 0$. 
@@
         This section will give specific instances of the error control sequence $(\epsilon_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ and, momentum sequence $(\alpha_k)_{k \ge0}$ such that an optimal convergence rate of $\mathcal O(1/k^2)$ can be achieved.
-        \begin{proposition}[$\mathcal O(1/k^2)$ optimal convergence rate of the outer loop]\;\label{prop:opt-cnvg-outr-loop}\\
-            Let $(f, g, L)$, $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(\beta_k)_{k\ge 0}, \mathcal E_0, p$ as assumed in Assumption \ref{ass:valid-err-schedule}. 
-            Assume in addition that
-            \begin{enumerate}[nosep]
-                \item there exists $\bar x \in \RR^n$ that is an minimizer of $F = f + g$;
-                \item $\alpha_0 = 1, p > 0$; 
-                \item the sequence $(\alpha_k)_{k\ge 0}$ satisfies for all $k \ge 0$ the equality $(1 - \alpha_k) = \alpha_{k}^2L_k\alpha_{k - 1}^{-2}L_{k - 1}^{-1}$;
-                \item the sequence $L_k := B_k + \rho_k$ is bounded, and there exists an $L_{\max}$ such that for all $k \ge 0$ it has $L_{\max} \ge \max_{k\ge i\ge 0} L_i$. 
-            \end{enumerate}
-            Then, $\alpha_k \in (0, 1]$ hence valid and, it satisfies for all $k \ge 0$: 
+        \begin{assumption}[the optimal momentum sequence]\;\label{ass:opt-mmntm-seq}\\
+            Keeping everything assumed in Assumption \ref{ass:valid-err-schedule} about $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(F, f, g, L)$, $(y_k, x_k, v_k)_{k \ge 0}$, $(\beta_k)_{k \ge 0}$, $\mathcal E_0$ and $p$, we assume in addition that the sequence $(\alpha_k)_{k \ge 0}$ satisfies for all $k \ge 0$ the equality: $(1 - \alpha_k) = \alpha_{k}^2L_k\alpha_{k - 1}^{-2}L_{k - 1}^{-1}$.
+        \end{assumption}
+        \begin{lemma}[the consequencse of optimal momentum sequence]\;\label{lemma:opt-mmntm-seq}\\
+            Let $(\alpha_k)_{k \ge 0}, (\beta_k)_{k \ge 0}$ be given by Assumption \ref{ass:opt-mmntm-seq}, then $\forall k\ge 1\; \alpha_k \in (0, 1)$ and, in addition the sequence $(\beta_k)_{k \ge 0}$ has
             \begin{align*}
-                & F(x_k) - F(\bar x) + \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2
+                \left(
+                    1 + \alpha_0\sqrt{L_0}\sum_{i = 1}^{k}\sqrt{L_i^{-1}}
+                \right)^{-2}
+                \hspace{-1em}\le 
+                \beta_k
                 \le 
                 \left(
-                    1 + \frac{k\alpha_0\sqrt{L_0}}{2\sqrt{L_{\max}}}
-                \right)^{-2}\left(
-                    \frac{L_0}{2}\Vert \bar x - v_{-1}\Vert^2
-                    + \mathcal E_0 \sum_{n = 1}^{k} \frac{1}{n^p}
-                \right). 
+                    1 + \frac{\alpha_0\sqrt{L_0}}{2}\sum_{i = 1}^{k}\sqrt{L_i^{-1}}
+                \right)^{-2}. 
             \end{align*}
-            Finally, since $p > 0$ the sum is convergent and hence it has an over all convergence rate $\mathcal O(1/k^2)$. 
-        \end{proposition}
+        \end{lemma}
         \begin{proof}
-            From the assumption that $(\alpha_k)_{k \ge 0}$ has $(1 - \alpha_k) = \alpha_k^2L_k \alpha_0^{-2}L_0^{-1}$ for all $k \ge 0$ and, the definition of $\beta_k$, it yields the following equalities:
+            Now, we focus on $(\beta_k)_{k \ge 0}$. 
+            From the assumption that $(\alpha_k)_{k \ge 0}$ has $(1 - \alpha_k) = \alpha_k^2L_k \alpha_{k - 1}^{-2}L_{k - 1}^{-1}$ for all $k \ge 0$ and, the definition of $\beta_k$, it yields the following equalities:
             \begin{align*}
@@
             \begin{enumerate}[nosep]
-                \item $\beta_k$ is nonincreasing and $\beta_k > 0$ for all $k \ge 0$ because $\beta_k = \prod_{i = 1}^{k} (1 - \alpha_i)$ and, $\alpha_k \in (0, 1]$. 
-                \item It has the equalities $\beta_k/\beta_{k - 1} = (1 - \alpha_k) = \frac{\alpha_k^2L_k}{\alpha_{k - 1}^2 L_{k - 1}}$ for all $k \ge 1$. 
+                \item[(a)] $\beta_k$ is monotone decreasing and $\beta_k > 0$ for all $k \ge 0$ because $\beta_k = \prod_{i = 1}^{k} (1 - \alpha_i)$ and, $\alpha_k \in (0, 1]$. 
+                \item[(b)] It has the equalities $\beta_k/\beta_{k - 1} = (1 - \alpha_k) = \frac{\alpha_k^2L_k}{\alpha_{k - 1}^2 L_{k - 1}}$ for all $k \ge 1$. 
             \end{enumerate}
@@
             This is true by first considering the relations $\prod_{i = 1}^k(1 - \alpha_i) = \beta_k$: 
-            \begin{align}\label{eqn:opt-cnvg-outr-loop-pitem1}\begin{split}
+            \begin{align}\label{eqn:opt-mmntm-seq-pitem1}\begin{split}
                 (1 - \alpha_k) &= \beta_k/\beta_{k - 1}
@@
             Next, the recursive relation of $(\alpha_k)_{k \ge 0}$ gives
-            \begin{align}\label{eqn:opt-cnvg-outr-loop-pitem2}\begin{split}
+            \begin{align}\label{eqn:opt-mmntm-seq-pitem2}\begin{split}
                 \alpha_k^2&= (1 - \alpha_k)\alpha_{k - 1}^2L_{k - 1}L_k^{-1}
@@
             \end{split}\end{align}
-            Combining \eqref{eqn:opt-cnvg-outr-loop-pitem1}, \eqref{eqn:opt-cnvg-outr-loop-pitem2} it would mean for all $i \ge 1$ it has: 
+            Combining \eqref{eqn:opt-mmntm-seq-pitem1}, \eqref{eqn:opt-mmntm-seq-pitem2} it would mean for all $i \ge 1$ it has: 
             \begin{align*}
@@
                 \\
-                &\underset{(1)}{\le} 
-                \beta_i \left(
+                &= \left(
                     \beta_i^{-1/2} - \beta_{i - 1}^{-1/2}
-                \right)^2
+                \right)^2\left(
+                    1 + \beta_i^{1/2}\beta_{i - 1}^{-1/2}
+                \right)^2. 
+            \end{align*}
+            Since $\beta_i$ is monotone decreasing, it has $\beta_i^{-1/2}\beta_{i - 1}^{-1/2} \le 1$, and since $\alpha \in (0, 1)$
+            \todoinline{HERE! IT'S NOT FINISHED YET!!!}
+        \end{proof}
+        \begin{proposition}[$\mathcal O(1/k^2)$ optimal convergence rate of the outer loop]\;\label{prop:opt-cnvg-outr-loop}\\
+            Let $(f, g, L)$, $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(\beta_k)_{k\ge 0}, \mathcal E_0, p$ as assumed in Assumption \ref{ass:valid-err-schedule}. 
+            Assume in addition that
+            \begin{enumerate}[nosep]
+                \item there exists $\bar x \in \RR^n$ that is a minimizer of $F = f + g$;
+                \item $\alpha_0 = 1, p > 0$; 
+                \item the sequence $(\alpha_k)_{k\ge 0}$ satisfies for all $k \ge 0$ the equality $(1 - \alpha_k) = \alpha_{k}^2L_k\alpha_{k - 1}^{-2}L_{k - 1}^{-1}$;
+                \item the sequence $L_k := B_k + \rho_k$ is bounded, and there exists an $L_{\max}$ such that for all $k \ge 0$ it has $L_{\max} \ge \max_{k\ge i\ge 0} L_i$. 
+                % \item the sequence $\rho_k$ must also recursively satisfies $\rho_k \ge \max\left(-B_k + \alpha_{k - 1}^4(\rho_{k - 1} + B_{k - 1}), 0\right)$. 
+            \end{enumerate}
+            Then, $\alpha_k \in (0, 1]\;\forall k \ge 0$ hence it's always valid and, it has $\forall k \ge 0$: 
+            \begin{align*}
+                & F(x_k) - F(\bar x) + \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2
+                \le 
                 \left(
-                    2\beta_i^{-1/2}
-                \right)^2
-                \\
-                &= 4\left(
-                    \beta_i^{-1/2} - \beta_{i - 1}^{-1/2}
-                \right)^2
-                \\
-                \implies
-                \sqrt{\frac{L_0\alpha_0^2}{L_i}} &\le
-                2 \left(
-                    \beta_i^{-1/2} - \beta_{i - 1}^{-1/2}
+                    1 + \frac{k\alpha_0\sqrt{L_0}}{2\sqrt{L_{\max}}}
+                \right)^{-2}\left(
+                    \frac{L_0}{2}\Vert \bar x - v_{-1}\Vert^2
+                    + \mathcal E_0 \sum_{n = 1}^{k} \frac{1}{n^p}
                 \right). 
             \end{align*}
+            Since, $p > 0$ the sum is convergent and hence the above inequality claims an overall convergence rate $\mathcal O(1/k^2)$. 
+        \end{proposition}
+        \begin{proof}
             Telescope for all $i \ge 1$: 
@@
             Combine it with Lemma \ref{lemma:inxt-apg-cnvg-prep1}, using $\alpha_0 = 1$ will yield the desired result. 
-            Finally, one can solves for $\alpha_k$ by the recursive equality, and it should yield:
-
+            Finally, one can solve for $\alpha_k$ by the recursive equality, and it should always have one of the strictly positive root: 
+            \begin{align*}
+                \alpha_k &=
+                \frac{L_{k - 1}}{2L_k}\left(
+                    - \alpha_{k - 1}^2 + \left(
+                        \alpha_{k - 1}^4 + 4 \alpha_{k - 1}\frac{L_k}{L_{k - 1}}
+                    \right)^{1/2}
+                \right)
+                \\
+                &= \frac{\alpha_{k - 1}^2L_{k - 1}}{2L_k}\left(
+                    - 1 + \left(
+                        1 + \frac{4 L_k}{L_{k - 1}\alpha_{k-1}^2}
+                    \right)^{1/2}
+                \right)
+                \\
+                &\underset{(1)}{\le} \frac{\alpha_{k - 1}^2L_{k - 1}}{2L_k}\left(
+                    - 1 + 1 + 2 \alpha_{k - 1}^{-2}\frac{L_k}{L_{k - 1}}
+                \right)
+                \\
+                &= 1
+            \end{align*}
+            At (1) we completed a square inside of the radical: 
+            \begin{align*}
+                1 + 4 L_{k}L_{k - 1}^{-1}\alpha_{k - 1}^{-2}
+                &= 
+                1 + 4 L_{k}L_{k - 1}^{-1}\alpha_{k - 1}^{-2}
+                + 2L_k^2L_{k - 1}^{-2}\alpha_{k - 1}^{-4}
+                - 2L_k^2L_{k - 1}^{-2}\alpha_{k - 1}^{-4}
+                \\
+                &= (1 + 2L_kL_{k - 1}^{-1}\alpha_{k - 1}^{-2})^2
+                - 2\alpha_{k - 1}^{-4}L_k^2L_{k - 1}^{-2}
+                \\
+                &\le (1 + 2L_kL_{k - 1}^{-1}\alpha_{k - 1}^{-2})^2. 
+            \end{align*}
+            To see that $\alpha_k > 0$, recall that we had the assumption that $B_k > 0$ making $L_k > 0$. 
+            If we inductively assume that $\alpha_{k - 1} \in (0, 1]$ then $\alpha_k > 0$ because: 
+            \begin{align*}
+                \alpha_k &=
+                \frac{L_{k - 1}}{2L_k}\left(
+                    - \alpha_{k - 1}^2 + \left(
+                        \alpha_{k - 1}^4 + 4 \alpha_{k - 1}\frac{L_k}{L_{k - 1}}
+                    \right)^{1/2}
+                \right) 
+                \\
+                &\ge \frac{L_{k - 1}}{2L_k}\left(
+                    - \alpha_{k - 1}^2 + \left(
+                        \alpha_{k - 1}^4
+                    \right)^{1/2}
+                \right) 
+                \\
+                &> 0. 
+            \end{align*}
         \end{proof}
+        \begin{remark}
+            In this remark, we assert the fact that all assumptions made in the theorem can be satisfied on practice, and we will also bring attention to the current, and future roles played by each of the parameters used in the inexact algorithm.
+            \par
+            Pay close attention that $\alpha_k$ had been determined in the above theorem, and $(B_k)_{k \le 0}$ is reserved for potential line search routine, the only parameter left undetermined in Definition \ref{def:inxt-apg} is the over-relaxation sequence $(\rho_k)_{k \ge 0}$, we only need the entire sequence is bounded above.
+            We give the freedom to the practitioners to choose $(\rho_k)_{k \ge 0}$. 
+            However, this sequence $\rho_k$ is not useless because it relaxes the upper bound for $\epsilon_k$, this has huge impact in the earlier stage (the first few iterations) of the algorithm $\Vert x_k - y_k\Vert$ is large.
+            Of course, the parameter $\mathcal E_0$ is also free to choose. 
+            \par
+            The the next subsection, we will show that under the assumption of the above theorem, there exists an error sequence $\epsilon_k$ such that it can never approach $0$ at an arbitrarily fast rate.
+        \end{remark}
+    \subsection{the fastest rate of which the error schedule can shrink}
+        To have overall convergence claim of the algorithm, it's necessary to prevent the error schedule $(\epsilon_k)_{k \ge 0}$ from crashing into zero too quickly. 
+        Following Assumption \ref{ass:valid-err-schedule}, in this section, we will provide the lower bound results for $\epsilon_k$ in Theorem \ref{prop:opt-cnvg-outr-loop} to show that in the worst case it cannot approach zero arbitrarily fast, if we choose the largest possible $\epsilon_k$ using $\beta_k$.
 
@@
         Let $\tau \ge L$, and $x_0 \in \RR^n$. 
-        Then an algorithm is a proximal gradient method if it generates iterates $(x_k)_{k \ge 0}$ such that they satisfies for all $k \ge 1$: 
+        Then an algorithm is a proximal gradient method if it generates iterates $(x_k)_{k \ge 0}$ such that they satisfy for all $k \ge 1$: 
         \begin{align*}
@@
             Two important immediate results will be presented first.
-            Consider the proximal gradient inequality from \ref{thm:inxt-pg-ineq}, but with $\rho = 0, \epsilon = 0, B = \tau$, then for all $x$ such that $\Vert \mathcal G_\tau(x)\Vert > 0$ it has for $\tilde x = T_{\tau}(x), z \in \RR^n$ the inequality
+            Consider the proximal gradient inequality from Theorem \ref{thm:inxt-pg-ineq}, but with $\rho = 0, \epsilon = 0, B = \tau$, then for all $x$ such that $\Vert \mathcal G_\tau(x)\Vert > 0$ it has for $\tilde x = T_{\tau}(x), z \in \RR^n$ the inequality
             \begin{align*}
@@
             \end{align*}
-            Hence for all $\bar x \in S$ it has 
+            Hence, for all $\bar x \in S$ it has 
             \begin{align}\label{ineq:lin-cnvg-ista-eb-pitem1}
@@
             At (1) we used \eqref{ineq:lin-cnvg-ista-eb-pitem2}. 
-            Multiple bothside by $\frac{\gamma}{2\tau}$ then we are done. 
+            Multiple both side by $\frac{\gamma}{2\tau}$ then we are done. 
         \end{proof}
@@
         \end{proof}
+        \par
         The following propositions precisely show that the linear convergence is achievable for the inner loop when $g = \Vert \cdot\Vert_1$ for our optimization objective. 

### 2025-10-07 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

@@
         \end{assumption}
-        \begin{lemma}[the consequencse of optimal momentum sequence]\;\label{lemma:opt-mmntm-seq}\\
+        \begin{lemma}[the properties of optimal momentum sequence]\;\label{lemma:opt-mmntm-seq}\\
             Let $(\alpha_k)_{k \ge 0}, (\beta_k)_{k \ge 0}$ be given by Assumption \ref{ass:opt-mmntm-seq}, then $\forall k\ge 1\; \alpha_k \in (0, 1)$ and, in addition the sequence $(\beta_k)_{k \ge 0}$ has
@@
         \begin{proof}
+            Firstly, we will show that for all $\alpha_0 \in (0, 1]$, and $\alpha_k \in (0, 1)\;\forall k \ge 1$. 
+            We prove using induction, inductively assume that $\alpha_k \in (0, 1]$. 
+            We can solve for $\alpha_k$ using the recursive equality which should always have one of the strictly positive root given by: 
+            \begin{align*}
+                \alpha_k &=
+                \frac{L_{k - 1}}{2L_k}\left(
+                    - \alpha_{k - 1}^2 + \left(
+                        \alpha_{k - 1}^4 + 4 \alpha_{k - 1}\frac{L_k}{L_{k - 1}}
+                    \right)^{1/2}
+                \right)
+                \\
+                &= \frac{\alpha_{k - 1}^2L_{k - 1}}{2L_k}\left(
+                    - 1 + \left(
+                        1 + \frac{4 L_k}{L_{k - 1}\alpha_{k-1}^2}
+                    \right)^{1/2}
+                \right)
+                \\
+                &\underset{(1)}{<} \frac{\alpha_{k - 1}^2L_{k - 1}}{2L_k}\left(
+                    - 1 + 1 + 2 \alpha_{k - 1}^{-2}\frac{L_k}{L_{k - 1}}
+                \right)
+                \\
+                &= 1
+            \end{align*}
+            At (1) we completed a square inside of the radical, and use the assumption that $\alpha_k > 0$ and, $L_k > 0, L_{k - 1} > 0$ because we had $B_k > 0$: 
+            \begin{align*}
+                1 + 4 L_{k}L_{k - 1}^{-1}\alpha_{k - 1}^{-2}
+                &= 
+                1 + 4 L_{k}L_{k - 1}^{-1}\alpha_{k - 1}^{-2}
+                + 2L_k^2L_{k - 1}^{-2}\alpha_{k - 1}^{-4}
+                - 2L_k^2L_{k - 1}^{-2}\alpha_{k - 1}^{-4}
+                \\
+                &= (1 + 2L_kL_{k - 1}^{-1}\alpha_{k - 1}^{-2})^2
+                - 2\alpha_{k - 1}^{-4}L_k^2L_{k - 1}^{-2}
+                \\
+                &< \left(1 + 2L_kL_{k - 1}^{-1}\alpha_{k - 1}^{-2}\right)^2. 
+            \end{align*}
+            To see that $\alpha_k > 0$, recall the same fact that $L_k > 0$, and use the inductive hypothesis that $\alpha_{k - 1} \in (0, 1]$ then $\alpha_k > 0$ because: 
+            \begin{align*}
+                \alpha_k &=
+                \frac{L_{k - 1}}{2L_k}\left(
+                    - \alpha_{k - 1}^2 + \left(
+                        \alpha_{k - 1}^4 + 4 \alpha_{k - 1}\frac{L_k}{L_{k - 1}}
+                    \right)^{1/2}
+                \right) 
+                \\
+                &\ge \frac{L_{k - 1}}{2L_k}\left(
+                    - \alpha_{k - 1}^2 + \left(
+                        \alpha_{k - 1}^4
+                    \right)^{1/2}
+                \right) 
+                \\
+                &> 0. 
+            \end{align*}
+            Therefore, inductively it holds that $\alpha_k \in (0, 1)$ too. 
+            \par
             Now, we focus on $(\beta_k)_{k \ge 0}$. 
@@
             \end{split}\end{align}
-            Combining \eqref{eqn:opt-mmntm-seq-pitem1}, \eqref{eqn:opt-mmntm-seq-pitem2} it would mean for all $i \ge 1$ it has: 
+            Combining \eqref{eqn:opt-mmntm-seq-pitem1}, \eqref{eqn:opt-mmntm-seq-pitem2} and the fact that $\beta_k > 0\;\forall k \ge 0$, it would mean for all $i \ge 1$ it has: 
             \begin{align*}
@@
             \end{align*}
-            Since $\beta_i$ is monotone decreasing, it has $\beta_i^{-1/2}\beta_{i - 1}^{-1/2} \le 1$, and since $\alpha \in (0, 1)$
-            \todoinline{HERE! IT'S NOT FINISHED YET!!!}
+            Since $\beta_i$ is monotone decreasing, it has $0 < \beta_i^{-1/2}\beta_{i - 1}^{-1/2} \le 1$, this gives: 
+            \begin{align*}
+                \beta_i^{-1/2} - \beta_{i - 1}^{-1/2} 
+                &\le \alpha_0\sqrt{\frac{L_0}{L_i}} 
+                \le 2 \left(
+                    \beta_i^{-1/2} - \beta_{i - 1}^{-1/2}
+                \right).
+            \end{align*}
+            Performing a telescoping sum, use the fact that $\beta_0 = 1$ will yield the desired results after some algebraic manipulations. 
         \end{proof}
         \begin{proposition}[$\mathcal O(1/k^2)$ optimal convergence rate of the outer loop]\;\label{prop:opt-cnvg-outr-loop}\\
-            Let $(f, g, L)$, $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(\beta_k)_{k\ge 0}, \mathcal E_0, p$ as assumed in Assumption \ref{ass:valid-err-schedule}. 
+            Let $(f, g, L)$, $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(\beta_k)_{k\ge 0}, \mathcal E_0, p$ be given by Assumption \ref{ass:opt-mmntm-seq}. 
             Assume in addition that
@@
                 \item $\alpha_0 = 1, p > 0$;
-                \item the sequence $(\alpha_k)_{k\ge 0}$ satisfies for all $k \ge 0$ the equality $(1 - \alpha_k) = \alpha_{k}^2L_k\alpha_{k - 1}^{-2}L_{k - 1}^{-1}$;
                 \item the sequence $L_k := B_k + \rho_k$ is bounded, and there exists an $L_{\max}$ such that for all $k \ge 0$ it has $L_{\max} \ge \max_{k\ge i\ge 0} L_i$. 
-                % \item the sequence $\rho_k$ must also recursively satisfies $\rho_k \ge \max\left(-B_k + \alpha_{k - 1}^4(\rho_{k - 1} + B_{k - 1}), 0\right)$. 
             \end{enumerate}
@@
         \begin{proof}
-            Telescope for all $i \ge 1$: 
-            \begin{align*}
-                \frac{\alpha_0\sqrt{L_0}}{2}\sum_{i = 1}^{k}\sqrt{L^{-1}_k}
-                &\le 
-                \beta_k^{-1/2} - \beta_{0}^{-1/2} = 
-                \beta_k^{-1/2} - 1. 
-            \end{align*}
-            Re-arranging, yields: 
+            We use the results from \ref{lemma:opt-mmntm-seq} because the sequence has the same assumption, then using the fact that $L_k$ is bounded then it gives:
             \begin{align*}
@@
             \end{align*}
-            Recall that $L_k = B_k + \rho_k$, and by our assumptions, the sequence $(B_k)_{k \ge 0}, (\rho_k)_{k\ge 0}$ are both bounded above, then it's not hard to see that $\beta_k \le \mathcal O(1/k^2)$.
-            Combine it with Lemma \ref{lemma:inxt-apg-cnvg-prep1}, using $\alpha_0 = 1$ will yield the desired result. 
-            Finally, one can solve for $\alpha_k$ by the recursive equality, and it should always have one of the strictly positive root: 
-            \begin{align*}
-                \alpha_k &=
-                \frac{L_{k - 1}}{2L_k}\left(
-                    - \alpha_{k - 1}^2 + \left(
-                        \alpha_{k - 1}^4 + 4 \alpha_{k - 1}\frac{L_k}{L_{k - 1}}
-                    \right)^{1/2}
-                \right)
-                \\
-                &= \frac{\alpha_{k - 1}^2L_{k - 1}}{2L_k}\left(
-                    - 1 + \left(
-                        1 + \frac{4 L_k}{L_{k - 1}\alpha_{k-1}^2}
-                    \right)^{1/2}
-                \right)
-                \\
-                &\underset{(1)}{\le} \frac{\alpha_{k - 1}^2L_{k - 1}}{2L_k}\left(
-                    - 1 + 1 + 2 \alpha_{k - 1}^{-2}\frac{L_k}{L_{k - 1}}
-                \right)
-                \\
-                &= 1
-            \end{align*}
-            At (1) we completed a square inside of the radical: 
-            \begin{align*}
-                1 + 4 L_{k}L_{k - 1}^{-1}\alpha_{k - 1}^{-2}
-                &= 
-                1 + 4 L_{k}L_{k - 1}^{-1}\alpha_{k - 1}^{-2}
-                + 2L_k^2L_{k - 1}^{-2}\alpha_{k - 1}^{-4}
-                - 2L_k^2L_{k - 1}^{-2}\alpha_{k - 1}^{-4}
-                \\
-                &= (1 + 2L_kL_{k - 1}^{-1}\alpha_{k - 1}^{-2})^2
-                - 2\alpha_{k - 1}^{-4}L_k^2L_{k - 1}^{-2}
-                \\
-                &\le (1 + 2L_kL_{k - 1}^{-1}\alpha_{k - 1}^{-2})^2. 
-            \end{align*}
-            To see that $\alpha_k > 0$, recall that we had the assumption that $B_k > 0$ making $L_k > 0$. 
-            If we inductively assume that $\alpha_{k - 1} \in (0, 1]$ then $\alpha_k > 0$ because: 
-            \begin{align*}
-                \alpha_k &=
-                \frac{L_{k - 1}}{2L_k}\left(
-                    - \alpha_{k - 1}^2 + \left(
-                        \alpha_{k - 1}^4 + 4 \alpha_{k - 1}\frac{L_k}{L_{k - 1}}
-                    \right)^{1/2}
-                \right) 
-                \\
-                &\ge \frac{L_{k - 1}}{2L_k}\left(
-                    - \alpha_{k - 1}^2 + \left(
-                        \alpha_{k - 1}^4
-                    \right)^{1/2}
-                \right) 
-                \\
-                &> 0. 
-            \end{align*}
+            Then, apply Theorem \ref{prop:inxt-apg-cnvg-generic} to obtain the desired results.
         \end{proof}
@@
             \par
-            The the next subsection, we will show that under the assumption of the above theorem, there exists an error sequence $\epsilon_k$ such that it can never approach $0$ at an arbitrarily fast rate.
+            In the next subsection, we will show that under the assumption of the above theorem, there exists an error sequence $\epsilon_k$ such that it can never approach $0$ at an arbitrarily fast rate.
         \end{remark}
@@
         Following Assumption \ref{ass:valid-err-schedule}, in this section, we will provide the lower bound results for $\epsilon_k$ in Theorem \ref{prop:opt-cnvg-outr-loop} to show that in the worst case it cannot approach zero arbitrarily fast, if we choose the largest possible $\epsilon_k$ using $\beta_k$.
+        \begin{lemma}[error schedule lower bound]
+
+        \end{lemma}
 

### 2025-10-07 Notebook LaTEX/R-WAPG/presentation-shorter.tex
>w<, changes

@@
     \tiny{Joint work with Shawn/Xianfu Wang}\\ 
-    \tiny{The research of HL and XW was partially supported by the NSERC Discovery Grant of Canada.}
-    \tiny{We respectfully acknowledge that the UBC Okanagan academic campus is situated on the traditional, ancestral, unceded territory of the Syilx Okanagan Nation}
 }
@@
 
-\section{References and draft on arxiv}
-    \begin{frame}{Thanks for the participations. Merci pour les participations.}
+\section{References, acknowledgement and our draft on arxiv}
+    \begin{frame}{Acknowledgements}
+        \begin{tcolorbox}
+            The research of HL and XW was partially supported by the NSERC Discovery Grant of Canada.
+            \par
+            We respectfully acknowledge that the UBC Okanagan academic campus is situated on the traditional, ancestral, unceded territory of the Syilx Okanagan Nation    
+        \end{tcolorbox}
+    \end{frame}
+    \begin{frame}{Thanks for the participation. Merci pour les participations.}
         Our paper can be found on arxiv using the following QR code: 

### 2025-10-14 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

@@
 
-\title{{\fontfamily{ptm}\selectfont Inexact Accelerated Proximal Gradient }}
+\title{{\fontfamily{ptm}\selectfont Inexact Accelerated Proximal Gradient With Error Bound Conditions gives Near Optimal Convergence Rate }}
 
@@
             When $\epsilon = 0, \rho = 0$, this reduces to proximal gradient inequality in the exact case. 
-            In this inequality, observe that the parameter $\epsilon$ controls the inexactiness of the proximal gradient evaluation. 
-            Morespecifically, $\epsilon_k$ controls the absolute pertubatnions of the proximal gradient inequality compared to its exact counterpart. 
-            $\rho$ on the otherhand, it is the over-relaxation of proximal gradient operator and it compensates the pertubations caused by $\epsilon$ relative to the term $\Vert \tilde x - x\Vert^2$. 
+            In this inequality, observe that the parameter $\epsilon$ controls the inexactness of the proximal gradient evaluation. 
+            More specifically, $\epsilon_k$ controls the absolute perturbations of the proximal gradient inequality compared to its exact counterpart. 
+            $\rho$ on the other hand, it is the over-relaxation of proximal gradient operator, and it compensates the perturbations caused by $\epsilon$ relative to the term $\Vert \tilde x - x\Vert^2$.
         \end{remark}
@@
         Let's denote $L_k = B_k + \rho_k$ for short. 
-        Recall that $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, if we choose $x = y_k$ so $\tilde x = x_k \approx_\epsilon T_{L_k}(y_k)$, and set $z = z_k, \epsilon = \epsilon_k$ then Theorem \ref{thm:inxt-pg-ineq} has:
+        Recall that $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, if we choose $x = y_k$ so $\tilde x = x_k \approx_{\epsilon_k} T_{L_k}(y_k)$, and set $z = z_k, \epsilon = \epsilon_k$ then Theorem \ref{thm:inxt-pg-ineq} has:
         \begin{align*}
@@
 
-    \subsection{convergence results of the outer loop}
+    \subsection{Convergence results of the outer loop}
         This section will give specific instances of the error control sequence $(\epsilon_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ and, momentum sequence $(\alpha_k)_{k \ge0}$ such that an optimal convergence rate of $\mathcal O(1/k^2)$ can be achieved.
@@
         \end{assumption}
-        \begin{lemma}[the properties of optimal momentum sequence]\;\label{lemma:opt-mmntm-seq}\\
-            Let $(\alpha_k)_{k \ge 0}, (\beta_k)_{k \ge 0}$ be given by Assumption \ref{ass:opt-mmntm-seq}, then $\forall k\ge 1\; \alpha_k \in (0, 1)$ and, in addition the sequence $(\beta_k)_{k \ge 0}$ has
+        \begin{lemma}[the optimal momentum sequence is indeed valid and optimal]\;\label{lemma:opt-mmntm-seq}\\
+            Let $(\alpha_k)_{k \ge 0}, (\beta_k)_{k \ge 0}$ be given by Assumption \ref{ass:opt-mmntm-seq}. 
+            If we choose $\alpha_0 \in (0, 1]\;$ then it satisfies $\alpha_k \in (0, 1)\;\forall k\ge 1$, and it's given by: 
+            \begin{align*}
+                \alpha_k &=
+                \frac{L_{k - 1}}{2L_k}\left(
+                    - \alpha_{k - 1}^2 + \left(
+                        \alpha_{k - 1}^4 + 4 \alpha_{k - 1}\frac{L_k}{L_{k - 1}}
+                    \right)^{1/2}
+                \right). 
+            \end{align*}
+            In addition, the sequence $(\beta_k)_{k \ge 0}$ has
             \begin{align*}
@@
             Firstly, we will show that for all $\alpha_0 \in (0, 1]$, and $\alpha_k \in (0, 1)\;\forall k \ge 1$. 
-            We prove using induction, inductively assume that $\alpha_k \in (0, 1]$. 
-            We can solve for $\alpha_k$ using the recursive equality which should always have one of the strictly positive root given by: 
+            We will prove using induction.
+            Assume inductively that $\alpha_k \in (0, 1]$. 
+            We can solve for $\alpha_k$ using the recursive equality from Assumption \ref{ass:opt-mmntm-seq} which always has one of the strictly positive root given by: 
             \begin{align*}
@@
             \end{align*}
-            At (1) we completed a square inside of the radical, and use the assumption that $\alpha_k > 0$ and, $L_k > 0, L_{k - 1} > 0$ because we had $B_k > 0$: 
+            At (1) we completed a square inside the radical, and use the assumption that $\alpha_k > 0$ and, $L_k > 0, L_{k - 1} > 0$ because we had $B_k > 0$: 
             \begin{align*}
@@
                 \item there exists $\bar x \in \RR^n$ that is a minimizer of $F = f + g$;
-                \item $\alpha_0 = 1, p > 0$;
+                \item it has $p > 0$;
                 \item the sequence $L_k := B_k + \rho_k$ is bounded, and there exists an $L_{\max}$ such that for all $k \ge 0$ it has $L_{\max} \ge \max_{k\ge i\ge 0} L_i$. 
@@
                 \right)^{-2}
-                \le 
+                \hspace{-0.7em}\le 
                 \left(
@@
             \par
-            Pay close attention that $\alpha_k$ had been determined in the above theorem, and $(B_k)_{k \le 0}$ is reserved for potential line search routine, the only parameter left undetermined in Definition \ref{def:inxt-apg} is the over-relaxation sequence $(\rho_k)_{k \ge 0}$, we only need the entire sequence is bounded above.
+            Pay attention that $\alpha_k$ had been determined in the above theorem (as seemed in Lemma \ref{lemma:opt-mmntm-seq}), and $(B_k)_{k \le 0}$ is reserved for potential line search routine, the only parameter left undetermined in Definition \ref{def:inxt-apg} is the over-relaxation sequence $(\rho_k)_{k \ge 0}$, we only need the entire sequence to be bounded above.
             We give the freedom to the practitioners to choose $(\rho_k)_{k \ge 0}$. 
@@
             \par
+            Finally, observe that from the above proof, in case when $p = 1$, the convergence rate would be $\mathcal O(\log(k)/k^2)$. 
+        \end{remark}
         In the next subsection, we will show that under the assumption of the above theorem, there exists an error sequence $\epsilon_k$ such that it can never approach $0$ at an arbitrarily fast rate.
-        \end{remark}
-    \subsection{the fastest rate of which the error schedule can shrink}
+    \subsection{The fastest rate of which the error schedule can shrink}
         To have overall convergence claim of the algorithm, it's necessary to prevent the error schedule $(\epsilon_k)_{k \ge 0}$ from crashing into zero too quickly. 
         Following Assumption \ref{ass:valid-err-schedule}, in this section, we will provide the lower bound results for $\epsilon_k$ in Theorem \ref{prop:opt-cnvg-outr-loop} to show that in the worst case it cannot approach zero arbitrarily fast, if we choose the largest possible $\epsilon_k$ using $\beta_k$.
-        \begin{lemma}[error schedule lower bound]
-
+        \begin{lemma}[error schedule lower bound]\;\label{lemma:err-schedule-lbnd}\\
+            Let, $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(\beta_k)_{k\ge 0}, \mathcal E_0, p$ be given by Assumption \ref{ass:opt-mmntm-seq}, $L_k := \rho_k + B_k$. 
+            Let $(\epsilon_k)_{k \ge 0}$ be given by $\epsilon_k := \frac{\mathcal E_0 \beta_k}{k^p} + \rho_k \frac{\Vert x_k - y_k\Vert^2}{2}$, then it will be a valid error sequence and so that it satisfies the assumption.
+            If in addition, there exists $L_{\min}$ such that for all $k\ge 0$ such that it has $L_{\min} \le \min_{1 \le i \le k}L_i$ and, we assume $\mathcal E > 0$, then $\epsilon_k$ admits the non-trivial lower bound:
+            \begin{align*}
+                \epsilon_k \ge \frac{\mathcal E_0}{k^p}\left(
+                    1 + k \alpha_0 \sqrt{L_0} \sqrt{L_{\min}^{-1}}
+                \right)^{-2} \ge \mathcal O(k^{-2-p}). 
+            \end{align*}
         \end{lemma}
+        \begin{proof}
+            Recall Assumption \ref{ass:valid-err-schedule}, the largest valid error schedule is $\epsilon_k = \frac{\mathcal E_0 \beta_k}{k^p} + \rho_k \frac{\Vert x_k - y_k\Vert^2}{2}$. 
+            Then it has 
+            \begin{align*}
+                \epsilon_k &\ge \frac{\mathcal E_0 \beta_k}{k^p}
+                \\
+                &\underset{(1)}{\ge} 
+                \left(
+                    1 + \alpha_0\sqrt{L_0}\sum_{i = 1}^{k}\sqrt{L_i^{-1}}
+                \right)^{-2} 
+                \frac{\mathcal E_0\beta_k}{k^p}
+                \\
+                &\underset{(2)}{\ge}
+                \frac{\mathcal E_0\beta_k}{k^p}
+                \left(
+                    1 + k\alpha_0\sqrt{L_0}\sqrt{L_{\min}^{-1}}
+                \right)^{-2} 
+                \\
+                &\ge \mathcal O(k^{-2-p}). 
+            \end{align*}
+            At (1), we used Lemma \ref{lemma:opt-mmntm-seq}. 
+            At (2), we used that $L_{\min} \le L_i$ for all $i = 0, 1, 2, \ldots$. 
+        \end{proof}
 
@@
     \begin{assumption}[error bound for proximal problem]\;\label{ass:eb-for-pp}\\
-        This assumption is about $(g, \omega, A, \Psi_\lambda, \gamma)$
+        This assumption is about $(g, \omega, A, \Psi_\lambda, \gamma_\lambda)$
         Here are the assumptions
         \begin{enumerate}[nosep]
-            \item Let function $\Psi_\lambda$ as given by \eqref{eqn:dual-pp} which satisfies gradient mapping error bound (Assumption \ref{ass:pg-eb}) where, $f(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2, g(v) = \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$.
+            \item Let function $\Psi_\lambda$ as given by \eqref{eqn:dual-pp} which satisfies gradient mapping error bound (Assumption \ref{ass:pg-eb}) where, $f(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2, g(v) = \omega^\star(v)$.
             \item The primal objective $\Phi_\lambda$ is a $L_1$ Lipschitz continuous on its domain. 
-            \item Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-prox}, we can do this because $f$ is quadratic and has a Lipschitz continuous gradient. 
+            \item Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-prox}, with $\gamma = \gamma_\lambda$ we can do this because $f$ is quadratic and has a Lipschitz continuous gradient. 
         \end{enumerate}
     \end{assumption}
-    \subsection{error bound and linear convergence}
-        The following theorem characterize linear convergence of the proximal gradient method under gradient mapping error bound condition. 
+    \subsection{Error bound and linear convergence}
+        The following theorem characterizes linear convergence of the proximal gradient method under gradient mapping error bound condition. 
         \begin{theorem}[linear convergence under gradient mapping error bound]\;\label{thm:lin-cnvg-ista-eb}\\
             Assume that $(F, f, g, L, S, \gamma)$ is given by Assumption \ref{ass:pg-eb}. 
-            Under this assumption, the iterates $(x_k)_{k \ge 0}$ given by Definition \ref{def:ista} satisfies for all $k \ge 0, \bar x \in S$ the inequality: 
+            Under this assumption, the iterates $(x_k)_{k \ge 0}$ given by Definition \ref{def:ista} satisfies for all $k \ge 0, \bar x \in S$ and $\tau \ge L$ the inequality: 
             \begin{align*}
@@
 
-    \subsection{characterizing linear convergence of the proximal problem}
+    \subsection{Conditions for linear convergence of the proximal problem}
         In this section, we will focus on the sufficient characterization of the proximal problem which allows proximal gradient method to achieve linear convergence rate. 
@@
         The next proposition will characterize a precise case where Assumption \ref{ass:eb-for-pp} is true, and it's a case widely available in applications. 
-        \begin{proposition}[1-norm problem]
+        \begin{proposition}[1-norm problem]\label{prop:1nrm-prox-problem}
             Let $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
@@
             \par
-            Let $\mu_f = \lambda\Vert A\Vert^2/\kappa_f$, let $\kappa_f = \theta^{-2}(A, C)$ be the Hoffman Constant as presented by Necoara et al.
+            Let $\mu_f = \Vert A\Vert^2/\kappa_f$, let $\kappa_f = \theta^{-2}(A, C)$ be the Hoffman Constant as presented by Necoara et al.
 in \cite[Section 4]{necoara_linear_2019} where $C$ is the constraint matrix of the inequality set $\delta(z | \{x : \Vert x\Vert_1 \le 1\})$, then the error bound constant can be satisfied with
             \begin{align*}
-                \gamma = \frac{\kappa_f}{1 + \mu_f + \sqrt{1 + \mu_f}}. 
+                \gamma_\lambda = \frac{\kappa_f}{1 + \lambda\mu_f + \sqrt{1 + \lambda\mu_f}}. 
             \end{align*}
-
         \end{proof}
+        \begin{remark}
+            The error bound constant $\gamma$ is very difficult to obtain an lower estimate in practice. 
+        \end{remark}
         \par
         The following propositions precisely show that the linear convergence is achievable for the inner loop when $g = \Vert \cdot\Vert_1$ for our optimization objective. 
-        \begin{proposition}[inner loop linear convergence scenario 1]\label{prop:inn-loop-lin-cnvg}
+        \begin{proposition}[inner loop linear convergence scenario I]\label{prop:inn-loop-lin-cnvg}
 
         \end{proposition}
-    \subsection{inner loop complexity}
+        The following proposition characterizes another case where error bound conditions of problem problem holds. 
+        \begin{proposition}[nonsmooth PLQ linear composite]\label{prop:plq-prox-problem}
+
+        \end{proposition}
+    \subsection{Inner loop complexity}
+        In this section, we will estimate the total number of iterations in the inner loop to achieve a certain accuracies $\epsilon$ on primal objective $\Phi_\lambda$ of the proximal problem for some given $\lambda > 0$.
+        We will specify the context for parameters $\epsilon, \lambda$ in relation to the outer problem of obtaining $x_k \approx_{\epsilon_k} T_{B_k + \rho_k}(y_k)$.
 

### 2025-10-14 Notebook LaTEX/R-WAPG/presentation-short.tex
>w<, changes

@@
 \setbeamertemplate{footline}[frame number] % ADD PAGE NUMBERS ON BOTTOM. 
-\setbeamertemplate{blocks}[rounded][shadow=true]
+\setbeamertemplate{blocks}[rounded][shadow=false]
 \setbeamertemplate{navigation symbols}{} 
@@
 }
-\date[\today]{\today \\ \vspace{1cm} \tiny{Joint work with Shawn/Xianfu Wang}}
+\date[\today]{
+    \today 
+    \\
+    2025 Annual Midwest Optimization Meeting
+    \\ 
+    \vspace{1cm} \tiny{Joint work with Shawn/Xianfu Wang}
+}
 \subject{Nesterov's acceleration and its applications}
@@
         \begin{frame}{Nesterov's accelerated gradient in 1983}
-            Let's recall a classic. 
             \begin{block}{Nesterov's accelerated gradient in 1983}
@@
             \end{block}
-            If $F$ is convex and has $L$ Lipschitz smooth gradient and a minimizer $x^+$ exists. 
+            When $F$ is convex and, $L$ Lipschitz smooth. 
+            If minimizer $x^+$ exists, then: 
             \begin{itemize}
@@
         \end{frame}
-        \begin{frame}{Other choices for the momentum sequence}
-            Generalized by Beck \cite{beck_fast_2009-1} in 2009, called FISTA, it has $(t_k)_{k}$: 
-            \begin{tcolorbox}\noindent\vspace{-1em}
+        \begin{frame}{Other choices for the momentum sequence part I}
+            Major results from the literature regarding different choices for the momentum sequence $(t_k)_{k \ge 0}$. 
+            \begin{block}{Beck, Teboulle 2009 {\cite[Theorem 4.4]{beck_fast_2009-1}}}
+                Commonly known by the name FISTA, it allows $(t_k)_{k}$: 
                 \begin{align*}
@@
                 \end{align*}    
-            \end{tcolorbox}
-            Chambolle and Dossal in 2015 \cite{chambolle_convergence_2015}, if $t_k = (k + a -1)/a$, then$(x_k)_{k \ge 0}$ has weak convergence in Hilbert space for all $a > 2$.
-            \par  
-            In Nesterov's book \cite{nesterov_lectures_2018} and Beck's book \cite{beck_first-order_2017} that if in addition, $F:\RR^n \rightarrow \RR$ is $L$ smooth gradient, with Strongly convex with $\mu > 0$, then $(\theta_k)_{k\ge 0}$:
-            \begin{tcolorbox}
+                When $t_k (t_k - 1) = t_{k - 1}^2$, it yields $\mathcal O(1/k^2)$ convergence rate of optimality gap
+            \end{block}
+            \begin{block}{Chambolle, Dossal 2015 \cite[Theorem 4.1]{chambolle_convergence_2015}}
+                If $t_k = (k + a -1)/a$ in which case this gives $\theta_{k} = \frac{k - 2}{k + a - 1}$, then $(x_k)_{k \ge 0}$ has weak convergence in Hilbert space for all $a > 2$.    
+            \end{block}
+        \end{frame}
+        \begin{frame}{Other choices for the momentum sequence part II}
+            A finetuned constant momentum sequence gives optimal linear convergence rate for specific strongly convex objective. 
+            \begin{block}{
+                Nesterov 2018 {\cite[Theorem 2.2.3]{nesterov_lectures_2018}}, 
+                Beck 2017 {\cite[Theorem 10.42]{beck_first-order_2017}}
+            }
+                If in addition whe $F:\RR^n \rightarrow \RR$ is $L$ smooth gradient, and $\mu > 0$ strongly convex, then for $(\theta_k)_{k\ge 0}$ such that: 
                 \begin{align*}
-                   \theta_k = \frac{\sqrt{L/\mu} - 1}{\sqrt{L/\mu} + 1}. 
+                    \theta_k = \frac{\sqrt{L/\mu} - 1}{\sqrt{L/\mu} + 1}, 
                 \end{align*}
-            \end{tcolorbox}
-            It gives $\mathcal O((1 - \sqrt{\mu/L})^k)$ convergence rate for $(F(x_k) - F(x^+))_{k \ge 1}$. 
+                it gives $\mathcal O\left(\left(1 - \sqrt{\mu/L}\right)^k\right)$ convergence rate for $(F(x_k) - F(x^+))_{k \ge 1}$. 
+            \end{block}
         \end{frame}
+        \begin{frame}{Other choices for the momentum sequence part III}
+            The cases when the inequality of Nesterov's rule is not satisfied had been investigated as well.
+            \begin{block}{Apidopoulos et al. 2018 \cite{apidopoulos_convergence_2018}}
+                If $\theta_k = \frac{k}{k + b}\;\forall k \ge 0$ where $b \in (0, 3)$ then, the optimality gap has a convergence rate of $\mathcal O(1/k^{2b/3})$. 
+            \end{block}
+        \end{frame}
+
     \subsection{Our discoveries and inspirations}
-        \begin{frame}{A major question}
-            This is a question that lead our investigation: 
+        \begin{frame}{Relaxed Weak Accelerated Proximal Gradient}
+            We asked the following major question.  
             \begin{tcolorbox}
@@
             \end{tcolorbox}
+            We addressed it by what we called: ``Relaxed Weak Accelerated proximal Gradient'' (R-WAPG). 
+            \begin{enumerate}
+                \item It's interpreted from the Nesterov's estimating sequence technique and based on the proximal gradient inequality. 
+                \item It relaxes the assumption of the momentum sequence parameter while still retaining an upper bound on the optimality gap. 
+            \end{enumerate}
         \end{frame}
@@
                     \item $g: \RR^n \rightarrow \overline \RR$ is proper, closed and convex. The extended real is defined as $\overline \RR := \RR \cup \{\infty\}$.
-                    \item A minimizer exists for the optimization problem: $F^+ = \min_x \left\lbrace f(x) + g(x)\right\rbrace$.
+                    \item A minimizer $x^+$ exists for the optimization problem: $F^+ = \min_x \left\lbrace f(x) + g(x)\right\rbrace$.
                 \end{enumerate}
             \end{assumption}
-            \textbf{This assumption the full scope of the theoretical and practical discussion, assume it throughout.}
+            \textbf{This assumption is the full scope of the theoretical and practical discussion.}
         \end{frame}
@@
             \end{tcolorbox}
-            We can show Nesterov's type accelerated proximal gradient algorithm (or equivalently, FISTA with $g \equiv 0$) generates $(F(x_k) - F^+)_{k\ge 1}$ that has an upper bound of: 
+            We can show Nesterov's type accelerated proximal gradient algorithm (or equivalently, FISTA with $g \equiv 0$) has for all $k \ge 1$:
             \begin{tcolorbox}\noindent\vspace{-1em} 
                 \begin{align*}
+                    F(x_k) - F^+ 
+                    \le
                     \mathcal O\left(
@@
         \begin{frame}{Unifying variants of FISTA in the literatures}
+            We tried it out on some variants in the literature. 
             Let's label 
@@
         \end{frame}
-        \begin{frame}{A practical realization inspired by the theories}
-            Our theories suggest that, the upperbound for function value in the R-WAPG algorithm is ultimately described by the sequence $(\alpha_k)_{k \ge 0}$.
-            \textbf{Taking this idea further, this is what we did for numerical experiments}: 
+        \begin{frame}{The numerical experiment that had been inspired}
+            Our theories suggest that the upper bound for $F(x_k) - F(x^+)$ in our R-WAPG framework is ultimately described by the sequence $(\alpha_k)_{k \ge 0}$.
+            Since $\alpha_k \in (\mu/L, 1)$ and all convex function is strongly convex with strong convexity constant $\mu = 0$, this is what we did:
             \begin{tcolorbox}
-                We made a Free R-WAPG algorithm which estimates the strong convexity constant $\mu$ through the Bregman Divergence at two successive iterates while the algorithm is running and, we check the upper bound using our convergence theory.
+                We made an algorithm which we called ``Free R-WAPG", it estimates the strong convexity constant $\mu$ using the Bregman Divergence at two successive iterates when the algorithm is running.
+                This information is used to determine the sequence $(\alpha_k)_{k \ge 0}$, and used to visualized our theoretical upper bound. 
             \end{tcolorbox}
@@
         \begin{frame}{Proximal gradient, gradient mapping}
+            Starting in this section, we will highlight key theoretical results that will allow the unifying convergence rate for Euclidean variants of FISTA in the literature.
+            \par
+            We start off with the following definition. 
             \begin{definition}[The proximal gradient operator]
@@
         \begin{frame}{The R-WAPG sequences}
-            In this section, we highlight key theoretical results that allowed us to unify convergence rate for various variants of FISTA in the literature.
-            \begin{definition}{R-WAPG sequences}\label{def:rwapg-seq}
+            \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}
                 Assume $0 \le \mu < L$. 
-                Let $(\alpha_k)_{k \ge 0}$ be such that: 
-                \begin{align*}
-                    & \alpha_0 \in (0, 1], \\
-                    & \alpha_k \in (\mu/L, 1) \quad (\forall k \ge 1). 
-                \end{align*}    
-                Define $(\rho_k)_{k \ge 0}$
-                \begin{align*}
-                    \rho_k := \frac{\alpha_{k + 1}^2 - (\mu/L) \alpha_{k + 1}}{
-                        (1 - \alpha_{k + 1}) \alpha_k^2.
-                    }
-                \end{align*}
-                We call the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ the R-WAPG sequences. 
+                Let $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ be such that: 
+                \begin{enumerate}
+                    \item $\alpha_0 \in (0, 1]$, 
+                    \item $\alpha_k \in (\mu/L, 1) \quad (\forall k \ge 1)$, 
+                    \item $\rho_k := \frac{\alpha_{k + 1}^2 - (\mu/L) \alpha_{k + 1}}{(1 - \alpha_{k + 1}) \alpha_k^2}$ for all $k \ge 0$. 
+                \end{enumerate}  
+                We call the sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ the R-WAPG sequences. 
             \end{definition}
@@
                 Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}.
-                The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for all $k\ge 1$ by such that:
+                The algorithm generates the sequences of vectors $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for all $k\ge 1$ by such that:
                 \begin{tcolorbox}\vspace{-1em}
@@
                         \\
-                        g_k &= \mathcal G_L (y_k),
-                        \\
                         v_{k + 1} &=
                         \hat\gamma^{-1}_{k + 1}
-                        (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k),
+                        \left(\gamma_k(1 - \alpha_k) v_k - \alpha_k \mathcal G_L (y_k) + \mu \alpha_k y_k\right),
                         \\
@@
         \begin{frame}{Convergence of R-WAPG}
-            After six pages of math in the paper, we deduced the following theorem: 
+            After six pages of math in the paper (not necessarily dense), we deduced the following theorem: 
             \begin{proposition}[R-WAPG convergence]\label{prop:wapg-convergence}
@@
                 \begin{align}
-                    & \begin{aligned}
                     y_{k} &=
@@
                     \right)
-                        \\
-                        &= x_{k} +
-                        \frac{\rho_{k - 1}\alpha_{k - 1}(1 - \alpha_{k - 1})}
-                        {\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_{k}}(x_{k} - x_{k - 1}), 
-                    \end{aligned}
                     % \label{eqn:rwapg-first-equiv-form-eqn-1}
                     \\
-                    & x_{k + 1} =
-                    y_k - L^{-1} \mathcal G_L (y_k),
+                    x_{k + 1} 
+                    &=y_k - L^{-1} \mathcal G_L (y_k),
                     \\
-                    & \begin{aligned}
                     v_{k + 1} 
@@
                     &= 
-                        x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k).
-                    \end{aligned}
+                    x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k), 
+                    \\
+                    y_{k + 1}
+                    &= x_{k + 1} +
+                    \frac{\rho_{k}\alpha_{k}(1 - \alpha_k)}
+                    {\rho_k\alpha_k^2 + \alpha_k}(x_{k + 1} - x_k). 
                 \end{align}
@@
             \end{proposition}
-            If $\mu = 0$, then it simplifies:
+            When $\mu = 0$, then has:
             {\small
@@
                 Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}.
-                If $\mu = 0, \rho_k \ge 1\; \forall k \ge 0$, and $\alpha_0 = 1$, then:
+                If it has $\mu = 0, \rho_k \ge 1\; \forall k \ge 0$, and $\alpha_0 = 1$, then:
                 \begin{enumerate}
                     \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$. 
-                    \item Let $t_k := \alpha_k^{-1}$, then $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``inverted FISTA sequence''.
+                    \item Let $t_k := \alpha_k^{-1}$, then it would satisfy $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``inverted FISTA sequence''.
                     \item $\prod_{i = 1}^k\max(1, \rho_{k - 1})(1 - \alpha_k) = \alpha_k^2 \quad (\forall k \ge 1)$.
@@
         \end{frame}
-        \begin{frame}{In addition, our theory made a new prediction}
+        \begin{frame}{In addition, our theory made one new prediction}
             \begin{theorem}[fixed momentum APG]\label{thm:fixed-momentum-fista}
@@
         \end{frame}
-
 \section{Adaptive momentum sequence and numerical experiments}
@@
             \begin{enumerate}
-                \item It allows $\alpha_k \in (0, 1)$. The sequence $(\alpha_k)_{k \ge 1}$ is as loose as possible. 
+                \item It has $\alpha_k \in (0, 1)$. The sequence $(\alpha_k)_{k \ge 1}$ is as loose as possible. 
                 \item It has $\rho_{k - 1} = \alpha_k/((1 - \alpha_k)\alpha_{k - 1}^2)$, hence $(1 - \alpha_k)\rho_{k - 1} = \alpha_k^2/\alpha_{k - 1}^2$. 
@@
             \end{align*}
-            This insipired our numerical experiments. 
+            This inspired our numerical experiments. 
         \end{frame}
@@
 \section{References and draft on arxiv}
+    \begin{frame}{Acknowledgement}
+        The research of HL and XW was partially supported by the NSERC Discovery Grant of Canada.
+        \par
+        The travel of HL to this conference is supported by the NSF grant DMS-2526465.
+    \end{frame}
     \begin{frame}{Thanks for the participations. Merci pour les participations.}

### 2025-10-14 Notebook LaTEX/R-WAPG/presentation-shorter.tex
>w<, changes

@@
         \begin{block}{Here are prominent results in the literature}
+            {\footnotesize
             \begin{itemize}
-                \item Beck, Teboulle 2009 \cite{beck_fast_2009}, the FISTA paper: $t_k (t_k - 1) \le t_{k - 1}^2$. 
+                \item Beck, Teboulle 2009 \cite[Theorem 4.4]{beck_fast_2009-1}, the FISTA paper: $t_k (t_k - 1) \le t_{k - 1}^2$. 
                     \begin{itemize}
+                        {\footnotesize
                         \item $(F(x_k) - F(x^+))_{k \ge 0}$ converges at rate $\mathcal O(1/k^2)$ when $t_k(t_k - 1) = t_{k - 1}^2$. 
                         \item $\theta_k$ admits no closed form. 
+                        }
                     \end{itemize}
-                \item Chambolle and Dossal 2015 \cite{chambolle_convergence_2015}: $t_k = (k + a -1)/a$ with $a > 2$. 
+                \item Chambolle and Dossal 2015 \cite[Theorem 4.1]{chambolle_convergence_2015}: $t_k = (k + a -1)/a$ with $a > 2$. 
                     \begin{itemize}
+                        {\footnotesize
                         \item Retains convergence rate $\mathcal O(1/k^2)$ with $\theta_{k} = \frac{k - 2}{k + a - 1}$. 
-                        \item Iterates has weak convergence in Hilbert space. 
+                        \item Iterates converge weakly in Hilbert space. 
+                        }
                     \end{itemize}
-                \item Nesterov \cite{nesterov_lectures_2018} and, Beck \cite{beck_first-order_2017}
-                : $\theta_k = \frac{\sqrt{L/\mu} - 1}{\sqrt{L/\mu} + 1}$.
+                \item Nesterov \cite[Theorem 2.2.3]{nesterov_lectures_2018} and, Beck \cite[Theorem 10.42]{beck_first-order_2017}
+                : $\theta_k = \left(\sqrt{L/\mu} - 1\right)\left(\sqrt{L/\mu} + 1\right)^{-1}$.
                     \begin{itemize}
+                        {\footnotesize
                         \item Converges at rate $\mathcal O\left(\left(1 - \sqrt{\mu/L}\right)^k\right)$, if $f$ is also $\mu$ strongly convex with $\mu > 0$. 
+                        }
                     \end{itemize}
-                \item Apidopoulos et al. 2018 \cite{apidopoulos_convergence_2018}: $\theta_k = \frac{n}{n + b}$ for $b \in (0, 3)$. 
+                \item Apidopoulos et al. 2018 \cite{apidopoulos_convergence_2018}: $\theta_k = \frac{k}{k + b}$ for $b \in (0, 3)$. 
                 \begin{itemize}
+                    {\footnotesize
                     \item Has convergence rate $\mathcal O(1/k^{2b/3})$. 
+                    }
                 \end{itemize}
             \end{itemize}    
+            }
         \end{block}
@@
             \item A unified analysis with strong convexity $\mu \ge 0$. 
-            \item Various equivalent representation of R-WAPG are given and, convergence results varified for examples in the literature. 
+            \item Various equivalent representation of R-WAPG are given and, convergence results verified for examples in the literature. 
             \item Numerical experiments are conducted to verify the theory. 
@@
                 \item $g: \RR^n \rightarrow \overline \RR$ is proper, closed and convex. The extended real is defined as $\overline \RR := \RR \cup \{\infty\}$.
-                \item A minimizer exists for the optimization problem: $F^+ = \min_x \left\lbrace f(x) + g(x)\right\rbrace$.
+                \item A minimizer $x^+$ exists for the optimization problem: $F^+ = \min_x \left\lbrace f(x) + g(x)\right\rbrace$.
             \end{enumerate}
@@
     \begin{frame}{The R-WAPG sequences}
-        We highlight key theoretical results that allowed us to unify convergence rate for various variants of FISTA in the literature.
         \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}
             Assume $0 \le \mu < L$. 
-            Let $(\alpha_k)_{k \ge 0}$ be such that: 
-            \begin{align*}
-                & \alpha_0 \in (0, 1], \\
-                & \alpha_k \in (\mu/L, 1) \quad (\forall k \ge 1). 
-            \end{align*}    
-            Define $(\rho_k)_{k \ge 0}$
-            \begin{align*}
-                \rho_k := \frac{\alpha_{k + 1}^2 - (\mu/L) \alpha_{k + 1}}{
-                    (1 - \alpha_{k + 1}) \alpha_k^2
-                }. 
-            \end{align*}
-            We call the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ the R-WAPG sequences. 
+            Let $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ be such that: 
+            \begin{enumerate}
+                \item $\alpha_0 \in (0, 1]$, 
+                \item $\alpha_k \in (\mu/L, 1) \quad (\forall k \ge 1)$, 
+                \item $\rho_k := \frac{\alpha_{k + 1}^2 - (\mu/L) \alpha_{k + 1}}{(1 - \alpha_{k + 1}) \alpha_k^2}$ for all $k \ge 0$. 
+            \end{enumerate}  
+            We call the sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ the R-WAPG sequences. 
         \end{definition}
@@
                     \\
-                    g_k &= \mathcal G_L (y_k),
-                    \\
                     v_{k + 1} &=
                     \hat\gamma^{-1}_{k + 1}
-                    (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k),
+                    \left(\gamma_k(1 - \alpha_k) v_k - \alpha_k \mathcal G_L (y_k) + \mu \alpha_k y_k\right),
                     \\
@@
         \begin{proposition}[Alternative representations of the iterates]\label{prop:wapg-first-equivalent-repr}
-            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}), and $\alpha_0 = 1, x_1 = v_1$, then they satisfy for all $k\ge 1$: 
+            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}), and $\alpha_0 = 1, x_1 = v_1$. 
+            Then they satisfy for all $k\ge 1$: 
             {\footnotesize
             \begin{align}
-                & \begin{aligned}
                 y_{k} &=
@@
                 \right)
-                    \\
-                    &= x_{k} +
-                    \frac{\rho_{k - 1}\alpha_{k - 1}(1 - \alpha_{k - 1})}
-                    {\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_{k}}(x_{k} - x_{k - 1}), 
-                \end{aligned}
                 % \label{eqn:rwapg-first-equiv-form-eqn-1}
                 \\
-                & x_{k + 1} =
-                y_k - L^{-1} \mathcal G_L (y_k),
+                x_{k + 1} 
+                &=y_k - L^{-1} \mathcal G_L (y_k),
                 \\
-                & \begin{aligned}
                 v_{k + 1} 
@@
                 &= 
-                    x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k).
-                \end{aligned}
+                x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k), 
+                \\
+                y_{k + 1}
+                &= x_{k + 1} +
+                \frac{\rho_{k}\alpha_{k}(1 - \alpha_k)}
+                {\rho_k\alpha_k^2 + \alpha_k}(x_{k + 1} - x_k). 
             \end{align}
@@
         \end{proposition}
-        If $\mu = 0$, then it simplifies:
+        When $\mu = 0$, then has:
         {\small
@@
     \begin{frame}{Convergence of R-WAPG}
-        After six pages of math in the paper, we deduced the following theorem: 
+        After six pages of math in the paper (not necessarily dense), we deduced the following theorem: 
         \begin{proposition}[R-WAPG convergence]\label{prop:wapg-convergence}

### 2025-10-15 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

@@
 
-\title{{\fontfamily{ptm}\selectfont Inexact Accelerated Proximal Gradient With Error Bound Conditions gives Near Optimal Convergence Rate }}
+\title{{
+    \fontfamily{ptm}\selectfont 
+    Error Bound Can Give Near Optimal Convergence Rate for Inexact Accelerated Proximal Gradient Method
+    }
+}
 
@@
         \end{remark}
-    \subsection{Optimizing the inexact proximal point problem}
+    \subsection{Optimizing the inexact proximal point problem}\label{sec:optz-inxt-pp-problem}
         In this section we will present the optimization problem that obtains a $\tilde x$ such that $\tilde x \approx_\epsilon \hprox_{\lambda g}(z)$. 
@@
 \section{Linear convergence for the proximal problem}
-    In this section, we continue the discussion from \textcolor{red}{[REF PREVIOUS SECTION]}. 
-    The inner loop of the algorithm evaluates $x_k \approx_\epsilon T_{(B + \rho)}(y_k)$ for a given value of $\epsilon$. 
+    In this section, we continue the discussion from Section \ref{sec:optz-inxt-pp-problem}. 
+    The inner loop of the algorithm evaluates $x_k \approx_\epsilon T_{(B + \rho)}(y_k)$ for a given value of $\epsilon, B + \rho$ and $y_k$. 
+    In this section, we will derive the sufficient conditions for linear convergence rate of the proximal gradient method can attain linear convergence rate for optimizing the dual formulation $\Psi_\lambda$ \eqref{eqn:dual-pp} of the proximal point problem.
+    \par
     To attain $x_k$, one approach is to utilize Theorem \ref{thm:dlty-gap-inxt-pp} numerically, usually using iterative algorithms. 
@@
         \begin{enumerate}[nosep]
-            \item Let function $\Psi_\lambda$ as given by \eqref{eqn:dual-pp} which satisfies gradient mapping error bound (Assumption \ref{ass:pg-eb}) where, $f(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2, g(v) = \omega^\star(v)$.
-            \item The primal objective $\Phi_\lambda$ is a $L_1$ Lipschitz continuous on its domain. 
-            \item Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-prox}, with $\gamma = \gamma_\lambda$ we can do this because $f$ is quadratic and has a Lipschitz continuous gradient. 
+            \item Assume function $\Psi_\lambda$ as given by \eqref{eqn:dual-pp} which satisfies gradient mapping error bound (Assumption \ref{ass:pg-eb}) where, $f(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2, g(v) = \omega^\star(v)$.
+            \item Assume the primal objective $\Phi_\lambda$ is a $L_1$ Lipschitz continuous on its domain. 
+            \item Assume $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-prox}, with $\gamma = \gamma_\lambda$ we can do this because $f$ is quadratic and has a Lipschitz continuous gradient. 
         \end{enumerate}
@@
         \end{proof}
-
     \subsection{Conditions for linear convergence of the proximal problem}
@@
         The following propositions precisely show that the linear convergence is achievable for the inner loop when $g = \Vert \cdot\Vert_1$ for our optimization objective. 
-        \begin{proposition}[inner loop linear convergence scenario I]\label{prop:inn-loop-lin-cnvg}
+        \begin{proposition}[scenario I, 1-norm penalization]\label{prop:inn-loop-lin-cnvg}
 
         \end{proposition}
+        \begin{definition}[piecewise linear-quadratic function {\cite[Definition 10.20]{rockafellar_variational_1998}}]
+            A function $f: \RR^n \rightarrow \overline \RR$ is piecewise linear-quadratic when $\dom f$ is the union of finitely many piecewise polyhedral set, such that on each polyhedral partition of $f$ there exists $\alpha \in \RR, a \in \RR^n$, $C\in \RR^{n \times n}$ as a symmetric matrix is where $f$ has the representation $x \rightarrow \langle x, Cx\rangle + \langle a, x\rangle + c$.
+        \end{definition}
         The following proposition characterizes another case where error bound conditions of problem problem holds. 
-        \begin{proposition}[nonsmooth PLQ linear composite]\label{prop:plq-prox-problem}
+        \begin{proposition}[convex PLQ proximal problem]\label{prop:plq-pp}
 
         \end{proposition}
+        \begin{proposition}[scenario II, convex PLQ linear composite]\label{prop:plq-prox-problem}
+
+        \end{proposition}
+
+        \begin{example}[inner loop linear convergence rate examples]\label{example:inn-lp-lin-cnvg}
+
+        \end{example}
     \subsection{Inner loop complexity}

### 2025-10-16 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, a lot of changes

@@
         \end{fact}
-        \begin{theorem}[inexact Moreau decomposition]
+        \begin{theorem}[inexact Moreau decomposition]\label{thm:inxt-moreau-decomp}
             Let $g: \RR^n \rightarrow \overline \RR$ be a closed, convex and proper function. 
@@
         We define the duality gap
-        \begin{align}
+        \begin{align}\label{eqn:duality-gap-pp}
             \mathbf G_\lambda(u, v) &:= \Phi_\lambda(u) + \Psi_\lambda(v). 
@@
         \end{theorem}
+        \begin{proof}
+            The proof of $(a) \implies (b)$, and the case when $(a)\iff (b)$, we refer readers to Villa et al.
+\cite[ Proposition 2.3]{villa_accelerated_2013}, and to show $(b) \iff (c)$ use Theorem \ref{thm:inxt-moreau-decomp}.
+        \end{proof}
+        \par
         The following fact from the literature indicates that it's sufficient to minimize the dual problem $\Psi_\lambda$ to obtain an element of the inexact proximal point operator. 
@@
 
-\section{Linear convergence for the proximal problem}
+\section{Linear convergence for the proximal problem in the inner loop}
     In this section, we continue the discussion from Section \ref{sec:optz-inxt-pp-problem}. 
-    The inner loop of the algorithm evaluates $x_k \approx_\epsilon T_{(B + \rho)}(y_k)$ for a given value of $\epsilon, B + \rho$ and $y_k$. 
-    In this section, we will derive the sufficient conditions for linear convergence rate of the proximal gradient method can attain linear convergence rate for optimizing the dual formulation $\Psi_\lambda$ \eqref{eqn:dual-pp} of the proximal point problem.
-    \par
-    To attain $x_k$, one approach is to utilize Theorem \ref{thm:dlty-gap-inxt-pp} numerically, usually using iterative algorithms. 
-    \par
-    The following assumption places additional assumption to the proximal problem for the inner loop. 
+    As an important reminder, we will fix the vector $y \in \RR^n$, which is in the inexact proximal problem as a constant in this entire section. 
+    \par
+    The inner loop of the algorithm is another algorithm that evaluates $x_k \approx_\epsilon T_{(B_k + \rho_k)}(y_k)$ for a given value of $\epsilon, B + \rho$ and at the point $y_k$. 
+    To accomplish, let $\lambda = (B_k + \rho_k)^{-1}$, the algorithm needs to resolve the following equivalent inexact proximal point problem: 
+    \begin{align*}
+        x_k \approx_\epsilon \hprox_{\lambda g}(y_k - \lambda \nabla f(y_k)). 
+    \end{align*}
+    Unfortunately recall that $g = \omega \circ A$ in the context of the outer loop hence it's impossible to directly evaluate the proximal operator of $g$ and hence we optimize the function $\Phi_\lambda$ as given by \eqref{eqn:primal-pp}.
+    \par
+    In this section, we will show that there exists an algorithm generating the sequences $z_n, v_n$ such that $\mathbf G_\lambda (z_n, v_n)$ converges linearly if $\Psi_\lambda$ satisfies the error bound conditions.
+    Using results available in the literature, we will characterize the exact scenarios of $\omega \circ A$ when this is possible to achieve. 
+    To start, the following assumption is the general error bound condition of a convex with additive composite structure. 
     \begin{assumption}[gradient mapping error bound]\;\label{ass:pg-eb}\\
@@
             Take note that the dual has closed form $g^\star(z) =\delta(z | \{x : \Vert x\Vert_1 \le 1\})$. 
-            The $g^\star$ is an indicator function which represents a box constraint. 
+            The $g^\star$ is an indicator of a polytope constraint. 
             The objective function $\Psi_\lambda(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$ so it's Lipschitz smooth, and it must have a set of minimizers $S$ because its domain is compact.
@@
         \begin{remark}
-            The error bound constant $\gamma$ is very difficult to obtain an lower estimate in practice. 
+            It is very difficult to obtain a lower estimate for $\gamma$ in practice. 
         \end{remark}
@@
         The following propositions precisely show that the linear convergence is achievable for the inner loop when $g = \Vert \cdot\Vert_1$ for our optimization objective. 
-        \begin{proposition}[scenario I, 1-norm penalization]\label{prop:inn-loop-lin-cnvg}
-
+        \begin{proposition}[sufficient conditions of linear convergence of the inner loop]\;\label{prop:inn-loop-lin-cnvg}\\
+            Let $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
+            Consider the following proximal problem: 
+            \begin{enumerate}[nosep]
+                \item The primal proximal problem $\Phi_\lambda(u) = \frac{1}{2\lambda}\Vert u - y\Vert^2 + \omega(Au)$.
+                \item The dual proximal problem $\Psi_\lambda(v) = f(v) + g(v)$ where \\ $f(v) := \frac{1}{2\lambda}\left\Vert \lambda A^\top v - y\right\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2, g(v) := \omega^\star(v)$.
+            \end{enumerate}
+            If, $\Psi_\lambda$ satisfies Assumption \ref{ass:eb-for-pp}. 
+            Let $L_1$ be the global Lipschitz continuity constant of $\Phi_\lambda$ which it has in this case. 
+            Let $\tau \ge L, \epsilon \ge 0$, $v_0 \in \dom \Psi_\lambda$ be an initial condition for an algorithm that satisfies Definition \ref{def:ista} with $F(v) = f(v) + g(v)$ and let the iterates $(v_n)_{n \ge 0}$ be generated by it.
+            Then, there exists a minimizer $\bar v$ for $\Psi_\lambda$, and the followings are true: 
+            \begin{enumerate}[nosep]
+                \item The sequence $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item1}
+                \item If we choose $z_n := y - \lambda A^\top v_n$, and $\bar z := y - \lambda A^\top \bar v$, then $\Phi_\lambda(z_n) - \Phi_\lambda(\bar z)$ converges linearly.
+\label{prop:inn-looplin-cnvg-item2}
+                \item The duality gap satisfies for all $n \ge 0$ the inequality 
+                $$\mathbf G_\lambda(z_n, v_n) \le \left(1 - \frac{\gamma_\lambda}{2\tau}\right)^{n/2}\left(1 + L_1\sqrt{2 \lambda}\right)(\Psi_\lambda(v_0) - \Psi_\lambda(\bar v)).$$
+                \label{prop:inn-looplin-cnvg-item3}
+                \item If $\mathbf G_\lambda(z_n, v_n) \le \epsilon$, then $z_n \approx_\epsilon \hprox_{\lambda g}(y)$. 
+                \label{prop:inn-looplin-cnvg-item4}
+            \end{enumerate}
         \end{proposition}
+        \begin{proof}
+            To see \ref{prop:inn-looplin-cnvg-item1}, the sequence $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$ has linear convergence by Proposition \ref{prop:1nrm-prox-problem} because we assumed that $\Psi_\lambda$ satisfies Assumption \ref{ass:eb-for-pp}.
+            More precisely it has: 
+            \begin{align}\label{ineq:inn-loop-lin-cnvg-pitem1}
+                \Psi_\lambda(v_n) - \Psi_\lambda(\bar v) &\le 
+                \left(
+                    1 - \frac{\gamma_\lambda}{2\tau}
+                \right)^n
+                \left(
+                    \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
+                \right). 
+            \end{align}
+            \par
+            We will now proceed to proving \ref{prop:inn-looplin-cnvg-item2}. 
+            Because the iterates are given by $z_n = y - \lambda A^\top v_n$, and $\bar z = y - \lambda A^\top \bar v$, it provides $\Phi_\lambda(z_n) - \Phi_\lambda(v_0)$, we can use Theorem \ref{fact:minimizing-dual-pp} which gives:
+            \begin{align*}
+                \Phi_\lambda(z_n) - \Phi_\lambda(\bar z) &\le L_1 \sqrt{2\lambda}\left(
+                    \Psi_\lambda(v_n) - \Psi_\lambda (\bar v)
+                \right)^{1/2}
+                \\
+                &\underset{(1)}{\le} 
+                L_1\sqrt{2\lambda} \left(
+                    1 - \frac{\gamma_\lambda}{2\tau}
+                \right)^{n/2}\left(
+                    \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
+                \right)^{1/2}. 
+            \end{align*}
+            At (1), we used convergence results from Theorem \ref{thm:lin-cnvg-ista-eb}. 
+            \par
+            To prove \ref{prop:inn-looplin-cnvg-item3}, by definition of duality gap in \eqref{eqn:duality-gap-pp} we have:
+            \begin{align*}
+                \mathbf G_\lambda(z_n, v_n) 
+                &\underset{(?)}{=} \Phi_\lambda(z_n) + \Psi_\lambda(v_n) + 0
+                \\
+                &= \Phi_\lambda(z_n) + \Psi_\lambda(v_n) - \Phi_\lambda(\bar z) - \Psi_\lambda(\bar v)
+                \\
+                &= \Phi_\lambda(z_n)- \Phi_\lambda(\bar z) + \Psi_\lambda(v_n) - \Psi_\lambda(\bar v)
+                \\
+                &\underset{(2)}{\le} 
+                L_1 \sqrt{2\lambda}\left(
+                    1 - \frac{\gamma_\lambda}{2\tau}
+                \right)^{n/2}\left(
+                    \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
+                \right)^{1/2}
+                + \left(
+                    1 - \frac{\gamma_\lambda}{2\tau}
+                \right)^{n}\left(
+                    \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
+                \right)
+                \\
+                &= \left(
+                \right)
+            \end{align*}
+        \end{proof}
+        \begin{remark}
+            To choose a feasible $v_0$, we can...
+            \todoinline{
+                REMEMBER TO FINISH IT. 
+            }
+        \end{remark}
         \begin{definition}[piecewise linear-quadratic function {\cite[Definition 10.20]{rockafellar_variational_1998}}]
@@
         \end{definition}
-        The following proposition characterizes another case where error bound conditions of problem problem holds. 
+        The following proposition characterizes another case where error bound conditions of problem holds. 
         \begin{proposition}[convex PLQ proximal problem]\label{prop:plq-pp}
@@
     \subsection{Inner loop complexity}
-        In this section, we will estimate the total number of iterations in the inner loop to achieve a certain accuracies $\epsilon$ on primal objective $\Phi_\lambda$ of the proximal problem for some given $\lambda > 0$.
+        In this section, we will estimate the total number of iterations in the inner loop to achieve a given accuracy $\epsilon$ on primal objective $\Phi_\lambda$ of the proximal problem for some given $\lambda > 0$.
         We will specify the context for parameters $\epsilon, \lambda$ in relation to the outer problem of obtaining $x_k \approx_{\epsilon_k} T_{B_k + \rho_k}(y_k)$.

### 2025-10-16 Notebook LaTEX/R-WAPG/presentation-shorter.tex
>w<, a lot of changes

@@
                         {\footnotesize
-                        \item Retains convergence rate $\mathcal O(1/k^2)$ with $\theta_{k} = \frac{k - 2}{k + a - 1}$. 
+                        \item It etains convergence rate $\mathcal O(1/k^2)$ with $\theta_{k} = \frac{k - 2}{k + a - 1}$. 
                         \item Iterates converge weakly in Hilbert space. 
@@
                     {\footnotesize
-                    \item Has convergence rate $\mathcal O(1/k^{2b/3})$. 
+                    \item It has convergence rate $\mathcal O(1/k^{2b/3})$. 
                     }
@@
     \begin{frame}{Acknowledgements}
-        \begin{tcolorbox}
         The research of HL and XW was partially supported by the NSERC Discovery Grant of Canada.
         \par
-            We respectfully acknowledge that the UBC Okanagan academic campus is situated on the traditional, ancestral, unceded territory of the Syilx Okanagan Nation    
-        \end{tcolorbox}
+        We respectfully acknowledge that the UBC Okanagan academic campus is situated on the traditional, ancestral, unceded territory of the Syilx Okanagan Nation. 
     \end{frame}

### 2025-10-16 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, fixes

@@
         \begin{assumption}[for inexact proximal gradient]\label{ass:for-inxt-pg-ineq}
-            The assumption is about $(f, g, L)$. 
+            The assumption is about $(F, f, g, L)$. 
             We assume that 
             \begin{enumerate}[nosep]
-                \item $f: \RR^n \rightarrow \RR$ is a convex, $L$ Lipschitz function. 
+                \item $f: \RR^n \rightarrow \RR$ is a convex, $L$ Lipschitz smooth function (i.e: $\nabla f$ is $L$ a Lipschitz continuous mapping). 
                 \item $g: \RR^n \rightarrow \overline\RR$ is a convex, proper, and lsc function which we do not have its exact proximal operator. 
+                \item The over all objective is $F = f + g$. 
             \end{enumerate}
@@
         To start, we must assume the following about a function $g: \RR^n \rightarrow \overline \RR$, with $g$ closed, convex and proper. 
-        \begin{assumption}[for inexact proximal operator]\;\label{ass:for-inxt-prox}\\
+        \begin{assumption}[linear composite of convex nonsmooth function]\;\label{ass:for-inxt-prox}\\
             This assumption is about $(g, \omega, A)$. 
@@
     \end{definition}
-    \begin{assumption}[error bound for proximal problem]\;\label{ass:eb-for-pp}\\
-        This assumption is about $(g, \omega, A, \Psi_\lambda, \gamma_\lambda)$
-        Here are the assumptions
-        \begin{enumerate}[nosep]
-            \item Assume function $\Psi_\lambda$ as given by \eqref{eqn:dual-pp} which satisfies gradient mapping error bound (Assumption \ref{ass:pg-eb}) where, $f(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2, g(v) = \omega^\star(v)$.
-            \item Assume the primal objective $\Phi_\lambda$ is a $L_1$ Lipschitz continuous on its domain. 
-            \item Assume $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-prox}, with $\gamma = \gamma_\lambda$ we can do this because $f$ is quadratic and has a Lipschitz continuous gradient. 
-        \end{enumerate}
-    \end{assumption}
-    \subsection{Error bound and linear convergence}
+    \subsection{Error bound and linear convergence of ISTA}
         The following theorem characterizes linear convergence of the proximal gradient method under gradient mapping error bound condition. 
@@
             \end{align*}
-            Now, for all $z = \bar x \in S$, from Assumption \ref{ass:eb-for-pp} $\exists \gamma > 0$ such that: 
+            Now, for all $z = \bar x \in S$, from Assumption \ref{ass:lin-cnvg-for-pp} $\exists \gamma > 0$ such that: 
             \begin{align*}
@@
         In this section, we will focus on the sufficient characterization of the proximal problem which allows proximal gradient method to achieve linear convergence rate. 
-        We can immediately claim quadratic growth condition when $\omega = \Vert \cdot\Vert_1$. 
-        The next proposition will characterize a precise case where Assumption \ref{ass:eb-for-pp} is true, and it's a case widely available in applications. 
-        \begin{proposition}[1-norm problem]\label{prop:1nrm-prox-problem}
-            Let $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
-            In addition, if $g := \Vert \cdot\Vert_1$, then the function $\Psi_\lambda$ satisfies Assumption \ref{ass:eb-for-pp}. 
-        \end{proposition}
-        \begin{proof}
-            Take note that the dual has closed form $g^\star(z) =\delta(z | \{x : \Vert x\Vert_1 \le 1\})$. 
-            The $g^\star$ is an indicator of a polytope constraint. 
-            The objective function $\Psi_\lambda(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$ so it's Lipschitz smooth, and it must have a set of minimizers $S$ because its domain is compact.
-            In addition, $\Psi_\lambda$ fits the assumption of Necoara et al. \cite[Theorem 8]{necoara_linear_2019}. 
-            Therefore, $\Psi_\lambda$ is quasi-strongly convex then by \cite[Theorem 4]{necoara_linear_2019}, and \cite[Theorem 7]{necoara_linear_2019}, it satisfies error bound condition as given in Assumption \ref{ass:pg-eb}, hence Assumption \ref{ass:eb-for-pp} also.
-            \par
-            Let $\mu_f = \Vert A\Vert^2/\kappa_f$, let $\kappa_f = \theta^{-2}(A, C)$ be the Hoffman Constant as presented by Necoara et al.
-in \cite[Section 4]{necoara_linear_2019} where $C$ is the constraint matrix of the inequality set $\delta(z | \{x : \Vert x\Vert_1 \le 1\})$, then the error bound constant can be satisfied with
-            \begin{align*}
-                \gamma_\lambda = \frac{\kappa_f}{1 + \lambda\mu_f + \sqrt{1 + \lambda\mu_f}}. 
-            \end{align*}
-        \end{proof}
-        \begin{remark}
-            It is very difficult to obtain a lower estimate for $\gamma$ in practice. 
-        \end{remark}
-        \par
-        The following propositions precisely show that the linear convergence is achievable for the inner loop when $g = \Vert \cdot\Vert_1$ for our optimization objective. 
+        The following assumption characterizes a set of sufficient conditions of the proximal problem such that linear convergence rate of applying ISTA to dual proximal objective $\Psi_\lambda$ can be achieved.
+        \begin{assumption}[conditions for linear convergence of proximal problem]\;\label{ass:lin-cnvg-for-pp}\\
+            This assumption is about $(g, \omega, A, \Phi_\lambda, \Psi_\lambda, L^\lambda_{\Phi} ,\gamma_\lambda)$. 
+            Here are the assumptions
+            \begin{enumerate}[nosep]
+                \item Assume $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}.
+The primal objective $\Phi_\lambda$ is given by \eqref{eqn:primal-pp}, and dual $\Psi_\lambda$ by \eqref{eqn:dual-pp}.
+This means if we let $f(v) := \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2, g(v) := \omega^\star(v)$, then $\Psi_\lambda = f + g$.
+                \item Next, assume $\Psi_\lambda = f + g$ satisfies Assumption \ref{ass:pg-eb} by viewing $\Psi_\lambda = F$ and denote $\gamma_\lambda := \gamma$.
+Note that we can do this because $f$ is obviously Lipschitz smooth.
+                \item Assume the primal objective $\Phi_\lambda$ is $L_\Phi^\lambda$ Lipschitz continuous. 
+            \end{enumerate}
+        \end{assumption}
+        \par
+        The following propositions precisely show that the linear convergence is achievable when Assumption \ref{ass:lin-cnvg-for-pp} holds. 
         \begin{proposition}[sufficient conditions of linear convergence of the inner loop]\;\label{prop:inn-loop-lin-cnvg}\\
-            Let $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
-            Consider the following proximal problem: 
-            \begin{enumerate}[nosep]
-                \item The primal proximal problem $\Phi_\lambda(u) = \frac{1}{2\lambda}\Vert u - y\Vert^2 + \omega(Au)$.
-                \item The dual proximal problem $\Psi_\lambda(v) = f(v) + g(v)$ where \\ $f(v) := \frac{1}{2\lambda}\left\Vert \lambda A^\top v - y\right\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2, g(v) := \omega^\star(v)$.
-            \end{enumerate}
-            If, $\Psi_\lambda$ satisfies Assumption \ref{ass:eb-for-pp}. 
-            Let $L_1$ be the global Lipschitz continuity constant of $\Phi_\lambda$ which it has in this case. 
-            Let $\tau \ge L, \epsilon \ge 0$, $v_0 \in \dom \Psi_\lambda$ be an initial condition for an algorithm that satisfies Definition \ref{def:ista} with $F(v) = f(v) + g(v)$ and let the iterates $(v_n)_{n \ge 0}$ be generated by it.
-            Then, there exists a minimizer $\bar v$ for $\Psi_\lambda$, and the followings are true: 
+            Let the parameters $(g, \omega, A, \Phi_\lambda, \Psi_\lambda, L^\lambda_{\Phi} ,\gamma_\lambda)$ of a proximal problem satisfy Assumption \ref{ass:lin-cnvg-for-pp}. 
+            Let $\tau \ge L_\Psi^\lambda$, and let $v_0 \in \dom \Psi_\lambda$ be an initial condition for an algorithm that satisfies Definition \ref{def:ista} with $F(v) = f(v) + g(v)$ and suppose that it generates iterates $(v_n)_{n \ge 0}$.
+            Let $\bar v$ be a minimizer of $\Psi_\lambda$, then the followings are true for all $\epsilon \ge 0$: 
             \begin{enumerate}[nosep]
                 \item The sequence $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item1}
-                \item If we choose $z_n := y - \lambda A^\top v_n$, and $\bar z := y - \lambda A^\top \bar v$, then $\Phi_\lambda(z_n) - \Phi_\lambda(\bar z)$ converges linearly.
+                \item If we let $z_n := y - \lambda A^\top v_n$, and $\bar z := y - \lambda A^\top \bar v$, then $\Phi_\lambda(z_n) - \Phi_\lambda(\bar z)$ converges linearly.
 \label{prop:inn-looplin-cnvg-item2}
-                \item The duality gap satisfies for all $n \ge 0$ the inequality 
-                $$\mathbf G_\lambda(z_n, v_n) \le \left(1 - \frac{\gamma_\lambda}{2\tau}\right)^{n/2}\left(1 + L_1\sqrt{2 \lambda}\right)(\Psi_\lambda(v_0) - \Psi_\lambda(\bar v)).$$
-                \label{prop:inn-looplin-cnvg-item3}
+                \item The duality gap has convergence $\mathbf G_\lambda(z_n, v_n) \le \mathcal O\left(\left(1 - \frac{\gamma_\lambda}{2\tau}\right)^{n/2}\right)$. \label{prop:inn-looplin-cnvg-item3}
                 \item If $\mathbf G_\lambda(z_n, v_n) \le \epsilon$, then $z_n \approx_\epsilon \hprox_{\lambda g}(y)$. 
@@
         \begin{proof}
-            To see \ref{prop:inn-looplin-cnvg-item1}, the sequence $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$ has linear convergence by Proposition \ref{prop:1nrm-prox-problem} because we assumed that $\Psi_\lambda$ satisfies Assumption \ref{ass:eb-for-pp}.
+            To see \ref{prop:inn-looplin-cnvg-item1}, the sequence $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$ has linear convergence by Theorem \ref{thm:lin-cnvg-ista-eb} because we assumed that $\Psi_\lambda$ satisfies Assumption \ref{ass:lin-cnvg-for-pp}.
             More precisely it has: 
@@
             We will now proceed to proving \ref{prop:inn-looplin-cnvg-item2}. 
-            Because the iterates are given by $z_n = y - \lambda A^\top v_n$, and $\bar z = y - \lambda A^\top \bar v$, it provides $\Phi_\lambda(z_n) - \Phi_\lambda(v_0)$, we can use Theorem \ref{fact:minimizing-dual-pp} which gives:
-            \begin{align*}
-                \Phi_\lambda(z_n) - \Phi_\lambda(\bar z) &\le L_1 \sqrt{2\lambda}\left(
+            Because the iterates are given by $z_n = y - \lambda A^\top v_n$, and $\bar z = y - \lambda A^\top \bar v$, due assumed Lipschitz continuity of $\Phi_\lambda$, we can use Theorem \ref{fact:minimizing-dual-pp} which gives:
+            \begin{align}\label{ineq:inn-loop-lin-cnvg-pitem2}
+                \begin{split}
+                    \Phi_\lambda(z_n) - \Phi_\lambda(\bar z) &\le L_\Phi^\lambda \sqrt{2\lambda}\left(
                     \Psi_\lambda(v_n) - \Psi_\lambda (\bar v)
@@
                     &\underset{(1)}{\le} 
-                L_1\sqrt{2\lambda} \left(
+                    L_\Phi^\lambda\sqrt{2\lambda} \left(
                         1 - \frac{\gamma_\lambda}{2\tau}
@@
                     \right)^{1/2}. 
-            \end{align*}
-            At (1), we used convergence results from Theorem \ref{thm:lin-cnvg-ista-eb}. 
+                \end{split}
+            \end{align}
+            At (1), we used \eqref{ineq:inn-loop-lin-cnvg-pitem1}.
             \par
@@
             \begin{align*}
-                \mathbf G_\lambda(z_n, v_n) 
-                &\underset{(?)}{=} \Phi_\lambda(z_n) + \Psi_\lambda(v_n) + 0
+                & \mathbf G_\lambda(z_n, v_n) 
+                \\
+                &\underset{(1)}{=} \Phi_\lambda(z_n) + \Psi_\lambda(v_n) + 0
                 \\
@@
                 &\underset{(2)}{\le} 
-                L_1 \sqrt{2\lambda}\left(
+                L_\Phi^\lambda \sqrt{2\lambda}\left(
                     1 - \frac{\gamma_\lambda}{2\tau}
@@
                 &= \left(
-                \right)
-            \end{align*}
+                    1 - \frac{\gamma_\lambda}{2\tau}
+                \right)^{n/2}\left(
+                    L_\Phi^\lambda \sqrt{2\lambda}\left(
+                        \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
+                    \right)^{1/2} 
+                    + 
+                    \left(
+                        1 - \frac{\gamma_\lambda}{2\tau}
+                    \right)^{n/2} (\Psi_\lambda(v_0) - \Psi_\lambda(\bar v))
+                \right). 
+            \end{align*}
+            At (1) we used strong duality because constraint qualification is in Assumption \ref{ass:for-inxt-prox}. 
+            At (2) we used \eqref{ineq:inn-loop-lin-cnvg-pitem1}, \eqref{ineq:inn-loop-lin-cnvg-pitem2}. 
+            To see \ref{prop:inn-looplin-cnvg-item4}, apply Theorem \ref{thm:dlty-gap-inxt-pp}. 
         \end{proof}
         \begin{remark}
-            To choose a feasible $v_0$, we can...
-            \todoinline{
-                REMEMBER TO FINISH IT. 
-            }
+            In pratice, use the proximal operator of $\omega^\star$ choose a feasible $v_0$. 
+        \end{remark}
+        The next proposition will characterize a precise case where Assumption \ref{ass:lin-cnvg-for-pp} is true, and it's a case widely available in applications. 
+        \begin{proposition}[1-norm problem]\label{prop:1nrm-prox-problem}
+            Let $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
+            In addition, if $g := \Vert \cdot\Vert_1$, then the function $\Psi_\lambda, \Psi_\lambda$ satisfies Assumption \ref{ass:lin-cnvg-for-pp}. 
+        \end{proposition}
+        \begin{proof}
+            Take note that the dual has closed form $g^\star(z) =\delta(z | \{x : \Vert x\Vert_1 \le 1\})$. 
+            The $g^\star$ is an indicator of a polytope constraint. 
+            The objective function $\Psi_\lambda(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$ so it's Lipschitz smooth, and it must have a set of minimizers $S$ because its domain is compact.
+            In addition, $\Psi_\lambda$ fits the assumption of Necoara et al. \cite[Theorem 8]{necoara_linear_2019}. 
+            Therefore, $\Psi_\lambda$ is quasi-strongly convex then by \cite[Theorem 4]{necoara_linear_2019}, and \cite[Theorem 7]{necoara_linear_2019}, it satisfies error bound condition as given in Assumption \ref{ass:pg-eb}, hence Assumption \ref{ass:lin-cnvg-for-pp} also.
+            \par
+            Let $\mu_f = \Vert A\Vert^2/\kappa_f$, let $\kappa_f = \theta^{-2}(A, C)$ be the Hoffman Constant as presented by Necoara et al.
+in \cite[Section 4]{necoara_linear_2019} where $C$ is the constraint matrix of the inequality set $\delta(z | \{x : \Vert x\Vert_1 \le 1\})$, then the error bound constant can be satisfied with
+            \begin{align*}
+                \gamma_\lambda = \frac{\kappa_f}{1 + \lambda\mu_f + \sqrt{1 + \lambda\mu_f}}. 
+            \end{align*}
+        \end{proof}
+        \begin{remark}
+            It is very difficult to obtain a lower estimate for $\gamma$ in practice. 
         \end{remark}

### 2025-10-25 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, fixes

@@
         \begin{theorem}[inexact over-regularized proximal gradient inequality]\;\label{thm:inxt-pg-ineq}\\
-            Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, $\epsilon \ge 0, B \ge 0, \rho > 0$. 
+            Let $(F, f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, $\epsilon \ge 0, B \ge 0, \rho > 0$. 
             Consider $\tilde x \approx_\epsilon T_{B + \rho}(x)$. 
@@
             More specifically, $\epsilon_k$ controls the absolute perturbations of the proximal gradient inequality compared to its exact counterpart. 
-            $\rho$ on the other hand, it is the over-relaxation of proximal gradient operator, and it compensates the perturbations caused by $\epsilon$ relative to the term $\Vert \tilde x - x\Vert^2$.
+            $\rho$ on the other hand, it is the over-relaxation of proximal gradient operator, and it compensates the perturbations caused by $\approx_\epsilon$ relative to the term $\Vert \tilde x - x\Vert^2$.
         \end{remark}
@@
             Let $z_n = y - \lambda A^\top v_n$, and $\bar z = y - \lambda A^\top \bar v$. 
-            If in addition, $\Phi_\lambda$ is $L_1$ Lipschitz continuous, then it has for all $k \ge 0$ the inequality: 
+            Then the following are true: 
+            \begin{enumerate}[nosep]
+                \item The sequence $z_n \rightarrow \bar z$ as well. 
+                \item There exists a constant $K$ that depends on the sequence $z_n$, and $\Phi_\lambda$ such that for all $k \ge 0$ the inequality: 
                 \begin{align*}
                     \Phi_{\lambda}(z_n) - \Phi_\lambda(\bar z) 
-                &\le L_1 \Vert z_n - \bar z\Vert 
-                \le L_1\sqrt{2\lambda}(\Psi_\lambda(v_n) - \Psi_\lambda(\bar v))^{1/2}. 
-            \end{align*}
+                    &\le K \Vert z_n - \bar z\Vert 
+                    \le K \sqrt{2\lambda}(\Psi_\lambda(v_n) - \Psi_\lambda(\bar v))^{1/2}. 
+                \end{align*}
+            \end{enumerate}
+
         \end{fact}
-        We remark that the above fact translates any algorithm that optimizes the function value of the dual problem $\Psi_\lambda$ into optimizing duality gap $\mathbf G(z_n, v_n)$. 
+        We remark that the above fact translates any algorithm that optimizes the dual problem $\Psi_\lambda$ into optimizing the duality gap $\mathbf G(z_n, v_n)$ because it shows the primal is bounded by the dual through a Lipschitz-like inequality.
+        \par
+        With the proof back in Villa et al.
+\cite[Theorem 5.1]{villa_accelerated_2013}, pay close attention to the constant $L_\Phi$ exists by the virtue of $\Psi$ being convex, and the sequence $v_n \rightarrow \bar v$ which allows the sequence $z_n \rightarrow \bar z_n$ to be bounded inside the domain of $\Phi_\lambda$.
+        By convexity, $\Phi_\lambda$ is locally Lipschitz on $\reli \dom \Phi_\lambda$, by convergence of $z_n$ the sequence is in a compact set in $\reli\dom \Phi_\lambda$ hence a Lipschitz bound with constant $K$ exists.
+        \par
         For this reason, the number of iterations of the inner loop required to achieve $\mathbf G(z_n, v_n) < \epsilon$ for a given $\epsilon$ is related to the convergence rate of the algorithms used to optimize $\Psi_\lambda(v_n)$.
@@
         \begin{assumption}[the optimal momentum sequence]\;\label{ass:opt-mmntm-seq}\\
-            Keeping everything assumed in Assumption \ref{ass:valid-err-schedule} about $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(F, f, g, L)$, $(y_k, x_k, v_k)_{k \ge 0}$, $(\beta_k)_{k \ge 0}$, $\mathcal E_0$ and $p$, we assume in addition that the sequence $(\alpha_k)_{k \ge 0}$ satisfies for all $k \ge 0$ the equality: $(1 - \alpha_k) = \alpha_{k}^2L_k\alpha_{k - 1}^{-2}L_{k - 1}^{-1}$.
+            Keeping everything assumed in Assumption \ref{ass:valid-err-schedule} about $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(F, f, g, L)$, $(y_k, x_k, v_k)_{k \ge 0}$, $(\beta_k)_{k \ge 0}$, $\mathcal E_0$ and $p$.
+            We assume in addition that the sequence $(\alpha_k)_{k \ge 0}$ satisfies for all $k \ge 0$ the equality: $(1 - \alpha_k) = \alpha_{k}^2L_k\alpha_{k - 1}^{-2}L_{k - 1}^{-1}$ and, $p > 1$. 
         \end{assumption}
@@
             Let $(\alpha_k)_{k \ge 0}, (\beta_k)_{k \ge 0}$ be given by Assumption \ref{ass:opt-mmntm-seq}. 
-            If we choose $\alpha_0 \in (0, 1]\;$ then it satisfies $\alpha_k \in (0, 1)\;\forall k\ge 1$, and it's given by: 
-            \begin{align*}
+            If we choose $\alpha_0 \in (0, 1]\;$ then for all $k \ge 1$ it has: 
+            \begin{align}\label{eqn:lemma:opt-mmntm-seq-result1}
                 \alpha_k &=
@@
                     \right)^{1/2}
-                \right). 
-            \end{align*}
-            In addition, the sequence $(\beta_k)_{k \ge 0}$ has
-            \begin{align*}
+                \right) \in (0, 1)
+            \end{align}
+            For the sequence $(\beta_k)_{k \ge 0}$ it has $\forall k \ge 1$
+            \begin{align}\label{ineq:lemma:opt-mmntm-seq-result2}
                 \left(
@@
                 \right)^{-2}. 
-            \end{align*}
+            \end{align}
         \end{lemma}
         \begin{proof}
-            Firstly, we will show that for all $\alpha_0 \in (0, 1]$, and $\alpha_k \in (0, 1)\;\forall k \ge 1$. 
+            Firstly, we will show \eqref{eqn:lemma:opt-mmntm-seq-result1}. 
             We will prove using induction.
@@
             \par
-            Now, we focus on $(\beta_k)_{k \ge 0}$. 
+            We will now show \eqref{ineq:lemma:opt-mmntm-seq-result2}. 
             From the assumption that $(\alpha_k)_{k \ge 0}$ has $(1 - \alpha_k) = \alpha_k^2L_k \alpha_{k - 1}^{-2}L_{k - 1}^{-1}$ for all $k \ge 0$ and, the definition of $\beta_k$, it yields the following equalities:
@@
                 \item there exists $\bar x \in \RR^n$ that is a minimizer of $F = f + g$;
-                \item it has $p > 0$;
                 \item the sequence $L_k := B_k + \rho_k$ is bounded, and there exists an $L_{\max}$ such that for all $k \ge 0$ it has $L_{\max} \ge \max_{k\ge i\ge 0} L_i$. 
             \end{enumerate}
-            Then, $\alpha_k \in (0, 1]\;\forall k \ge 0$ hence it's always valid and, it has $\forall k \ge 0$: 
+            Then, it has $\forall k \ge 0$: 
             \begin{align*}
@@
         \begin{proof}
-            We use the results from \ref{lemma:opt-mmntm-seq} because the sequence has the same assumption, then using the fact that $L_k$ is bounded then it gives:
+            We use the results from Lemma \ref{lemma:opt-mmntm-seq} because of the same assumption on $(\alpha_k)_{k 
+            \ge 0}$, then using the fact that $L_k$ is bounded: 
             \begin{align*}
@@
         \begin{remark}
-            In this remark, we assert the fact that all assumptions made in the theorem can be satisfied on practice, and we will also bring attention to the current, and future roles played by each of the parameters used in the inexact algorithm.
-            \par
-            Pay attention that $\alpha_k$ had been determined in the above theorem (as seemed in Lemma \ref{lemma:opt-mmntm-seq}), and $(B_k)_{k \le 0}$ is reserved for potential line search routine, the only parameter left undetermined in Definition \ref{def:inxt-apg} is the over-relaxation sequence $(\rho_k)_{k \ge 0}$, we only need the entire sequence to be bounded above.
-            We give the freedom to the practitioners to choose $(\rho_k)_{k \ge 0}$. 
-            However, this sequence $\rho_k$ is not useless because it relaxes the upper bound for $\epsilon_k$, this has huge impact in the earlier stage (the first few iterations) of the algorithm $\Vert x_k - y_k\Vert$ is large.
+            In this remark, we assert the fact that all assumptions made in the theorem can be satisfied on practice, and we will also bring attention to the current, and future roles played by some parameters used in the inexact algorithm.
+            \par
+            Pay attention that $\alpha_k$ had been determined in the above theorem (as seemed in Lemma \ref{lemma:opt-mmntm-seq}), and $(B_k)_{k \le 0}$ is reserved for potential line search routine, the only parameter left undetermined in Definition \ref{def:inxt-apg} is the over-relaxation sequence $(\rho_k)_{k \ge 0}$.
+            Since we only need the entire sequence $L_k = \rho_k + B_k$ to be bounded above, we give the freedom to the practitioners to choose $(\rho_k)_{k \ge 0}$. 
+            However, this sequence $\rho_k$ is not useless because it counters $\epsilon_k$ in the proximal gradient inequality, this has huge impact in the earlier stage (the first few iterations) of the algorithm $\Vert x_k - y_k\Vert$ is large.
             Of course, the parameter $\mathcal E_0$ is also free to choose. 
@@
                 \right)^{-2} 
-                \frac{\mathcal E_0\beta_k}{k^p}
+                \frac{\mathcal E_0}{k^p}
                 \\
                 &\underset{(2)}{\ge}
-                \frac{\mathcal E_0\beta_k}{k^p}
+                \frac{\mathcal E_0}{k^p}
                 \left(
@@
         \end{proof}
-    \subsection{Conditions for linear convergence of the proximal problem}
+    \subsection{Conditions for linear convergence of the proximal problem}\label{sec:conds-lin-cnvg-pp}
         In this section, we will focus on the sufficient characterization of the proximal problem which allows proximal gradient method to achieve linear convergence rate. 
@@
         \begin{assumption}[conditions for linear convergence of proximal problem]\;\label{ass:lin-cnvg-for-pp}\\
-            This assumption is about $(g, \omega, A, \Phi_\lambda, \Psi_\lambda, L^\lambda_{\Phi} ,\gamma_\lambda)$. 
+            This assumption is about $(g, \omega, A, y, \Phi_\lambda, \Psi_\lambda, L^\lambda_{\Phi} ,\gamma_\lambda)$. 
             Here are the assumptions
             \begin{enumerate}[nosep]
+                \item $y \in \RR^n$ is the vector of which the proximal problem is anchored at, fixed it to be an arbitrary vector. 
                 \item Assume $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}.
 The primal objective $\Phi_\lambda$ is given by \eqref{eqn:primal-pp}, and dual $\Psi_\lambda$ by \eqref{eqn:dual-pp}.
-This means if we let $f(v) := \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2, g(v) := \omega^\star(v)$, then $\Psi_\lambda = f + g$.
-                \item Next, assume $\Psi_\lambda = f + g$ satisfies Assumption \ref{ass:pg-eb} by viewing $\Psi_\lambda = F$ and denote $\gamma_\lambda := \gamma$.
-Note that we can do this because $f$ is obviously Lipschitz smooth.
-                \item Assume the primal objective $\Phi_\lambda$ is $L_\Phi^\lambda$ Lipschitz continuous. 
+This means if we let $h(v) := \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2$, then $\Psi_\lambda(v) = h(v) + \omega^\star(v)$.
+                \item Next, assume $\Psi_\lambda = h + \omega^\star$ satisfies error bound condition (Assumption \ref{ass:pg-eb}) with $\Psi_\lambda = F$ and, $\gamma = \gamma_\lambda$ and $f = h$.
+Note that we can do this because $h$ is quadratic hence obviously Lipschitz continuous and Lipschitz smooth.
+                \item We assume in addition, the primal objective $\Phi_\lambda$ of proximal problem is $L_\Phi^\lambda$ Lipschitz continuous on its domain $\dom \Phi_\lambda = \dom (g\circ A)$. 
             \end{enumerate}
         \end{assumption}
+        The following definition specifies the algorithm that can achieve linear convergence rate with the assumptions above. 
+        \begin{definition}[the ISTA inner loop algorithm]\;\label{def:ista-inner-lp}\\
+            Let $\lambda > 0, \epsilon > 0$, and $(g, \omega, A, y, \Phi_\lambda, \Psi_\lambda, L^\lambda_{\Phi} ,\gamma_\lambda)$ satisfies Assumption \ref{ass:lin-cnvg-for-pp}. 
+            \begin{enumerate}[nosep]
+                \item Let $v_0\in\dom \omega^\star$ be a feasible initial guess of $\Psi_{\lambda}$, and let $\tau > \Vert AA^\top\Vert$ be the inverse stepsize. 
+                \item Define $z_0 = y - \lambda A^\top v_0$ and smooth part of $\Psi_\lambda$ as $h := v \mapsto \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2$. 
+            \end{enumerate}
+            The algorithm that solves the proximal problem generates the primal dual sequences $(z_n, v_n)$ such that for all $n = 0, 1, 2, \cdots$, by the rules: 
+            \begin{align*}
+                v_{n + 1} &= \hprox_{\tau^{-1} \omega^\star}\left(
+                    v_{n} - \tau^{-1}\nabla h(v_n)
+                \right), 
+                \\
+                z_{n + 1} &= y - \lambda A^\top v_{n + 1}. 
+            \end{align*}
+            Terminates if $\mathbf G_\lambda(z_n, v_n) \le \epsilon$ where $\mathbf G_\lambda$ is given by \eqref{eqn:duality-gap-pp}. 
+        \end{definition}
+        \begin{remark}
+            The value of $\mathbf G_\lambda(z_n, v_n)$ is easy to compute, it only requires access to matrix $A, A^\top$, and the function $\omega$. 
+            In case when the proximal operator for $\omega^\star$ is nontrivial, we can use the Moreau identity and the proximal operator of $\omega$ instead. 
+            The gradient $\nabla f(v)$ is easy to compute, and it is: $AA^T v - Ay$.
+        \end{remark}
         \par
@@
         \begin{proposition}[sufficient conditions of linear convergence of the inner loop]\;\label{prop:inn-loop-lin-cnvg}\\
-            Let the parameters $(g, \omega, A, \Phi_\lambda, \Psi_\lambda, L^\lambda_{\Phi} ,\gamma_\lambda)$ of a proximal problem satisfy Assumption \ref{ass:lin-cnvg-for-pp}. 
-            Let $\tau \ge L_\Psi^\lambda$, and let $v_0 \in \dom \Psi_\lambda$ be an initial condition for an algorithm that satisfies Definition \ref{def:ista} with $F(v) = f(v) + g(v)$ and suppose that it generates iterates $(v_n)_{n \ge 0}$.
-            Let $\bar v$ be a minimizer of $\Psi_\lambda$, then the followings are true for all $\epsilon \ge 0$: 
+            Let the parameters $(g, \omega, A, y, \Phi_\lambda, \Psi_\lambda, L^\lambda_{\Phi} ,\gamma_\lambda)$ of a proximal problem satisfy Assumption \ref{ass:lin-cnvg-for-pp}. 
+            Let $\tau$, $v_0, \epsilon$ be given by an algorithm that satisfies Definition \ref{def:ista-inner-lp} and, it generates iterates $(z_n, v_n)_{n \ge 0}$. 
+            Let $\bar v$ be a minimizer of $\Psi_\lambda$, then the followings are true: 
             \begin{enumerate}[nosep]
                 \item The sequence $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item1}
-                \item If we let $z_n := y - \lambda A^\top v_n$, and $\bar z := y - \lambda A^\top \bar v$, then $\Phi_\lambda(z_n) - \Phi_\lambda(\bar z)$ converges linearly.
-\label{prop:inn-looplin-cnvg-item2}
+                \item If we let $\bar z := y - \lambda A^\top \bar v$, then $\Phi_\lambda(z_n) - \Phi_\lambda(\bar z)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item2}
                 \item The duality gap has convergence $\mathbf G_\lambda(z_n, v_n) \le \mathcal O\left(\left(1 - \frac{\gamma_\lambda}{2\tau}\right)^{n/2}\right)$. \label{prop:inn-looplin-cnvg-item3}
-                \item If $\mathbf G_\lambda(z_n, v_n) \le \epsilon$, then $z_n \approx_\epsilon \hprox_{\lambda g}(y)$. 
-                \label{prop:inn-looplin-cnvg-item4}
+                \item If $\mathbf G_\lambda(z_n, v_n) \le \epsilon$, then $z_n \approx_\epsilon \hprox_{\lambda g}(y)$. \label{prop:inn-looplin-cnvg-item4}
             \end{enumerate}
@@
         \begin{proof}
-            To see \ref{prop:inn-looplin-cnvg-item1}, the sequence $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$ has linear convergence by Theorem \ref{thm:lin-cnvg-ista-eb} because we assumed that $\Psi_\lambda$ satisfies Assumption \ref{ass:lin-cnvg-for-pp}.
-            More precisely it has: 
+            Note that $\Psi_\lambda$ satisfies error bound condition in Assumption \ref{ass:lin-cnvg-for-pp}, and Definition \ref{def:ista-inner-lp} has $\tau \ge \Vert A^TA\Vert$ which satisfies Definition \ref{def:ista} therefore the linear convergence results of Theorem \ref{thm:lin-cnvg-ista-eb} applies to $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$.
+            Therefore, we claim: 
             \begin{align}\label{ineq:inn-loop-lin-cnvg-pitem1}
@@
             We will now proceed to proving \ref{prop:inn-looplin-cnvg-item2}. 
-            Because the iterates are given by $z_n = y - \lambda A^\top v_n$, and $\bar z = y - \lambda A^\top \bar v$, due assumed Lipschitz continuity of $\Phi_\lambda$, we can use Theorem \ref{fact:minimizing-dual-pp} which gives:
+            Recall that the iterates $z_n = y - \lambda A^\top v_n$, and $\bar z = y - \lambda A^\top \bar v$, and we have Lipschitz continuity of $\Phi_\lambda$, hence Theorem \ref{fact:minimizing-dual-pp} applies, in addition since $\Phi_\lambda$ were assumed to be globally Lipschitz on $\dom \Phi_\lambda$ in Assumption \ref{ass:lin-cnvg-for-pp}, this means that we can replace $K$ regardless of $\bar v$, and convergent primal sequence $z_n \rightarrow \bar z$ with $L_\Phi^\lambda$ which gives:
             \begin{align}\label{ineq:inn-loop-lin-cnvg-pitem2}
@@
                     \right)^{n/2} (\Psi_\lambda(v_0) - \Psi_\lambda(\bar v))
-                \right). 
+                \right)
+                \\
+                &\le 
+                \left(
+                    1 - \frac{\gamma_\lambda}{2\tau}
+                \right)^{n/2}\left(
+                    L_\Phi^\lambda \sqrt{2\lambda}
+                    + 
+                    (\Psi_\lambda(v_0) - \Psi_\lambda(\bar v))^{1/2}
+                \right)
+                \left(
+                        \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
+                    \right)^{1/2} . 
             \end{align*}
@@
         \begin{remark}
-            In pratice, use the proximal operator of $\omega^\star$ choose a feasible $v_0$. 
+            In practice, use the proximal operator of $\omega^\star$ to choose a feasible $v_0$, equivalently we can translate any primal feasible solution into a dual feasible solution using Theorem \ref{thm:primal-dual-trans}.
+            \par
+            As a prelude, to have a global convergence rate it requires an upper bound of the initial optimally gap of $\Psi_\lambda$ of for all iterations of the outer loop. 
+            Suppose for each outer iteration $k$, the inner loop is initialized to start on $v_0^{(k)}$, then there must be an upper bound for all $\Psi_\lambda\left(v_0^{(k)}\right) - \Psi_\lambda(\bar v)$.
         \end{remark}
@@
             Let $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
-            In addition, if $g := \Vert \cdot\Vert_1$, then the function $\Psi_\lambda, \Psi_\lambda$ satisfies Assumption \ref{ass:lin-cnvg-for-pp}. 
+            In addition, if $g := \Vert \cdot\Vert_1$, then the function $\Psi_\lambda, \Phi_\lambda$ satisfies Assumption \ref{ass:lin-cnvg-for-pp}. 
         \end{proposition}
         \begin{proof}
+            To verify, it requires that
+            \begin{enumerate}[nosep]
+                \item The function $\Psi_\lambda$ satisfies the error bound condition as specified in Assumption \ref{ass:pg-eb}; 
+                \item $\Psi_\lambda$ is also a Lipschitz continuous function. 
+            \end{enumerate}
             Take note that the dual has closed form $g^\star(z) =\delta(z | \{x : \Vert x\Vert_1 \le 1\})$. 
             The $g^\star$ is an indicator of a polytope constraint. 
-            The objective function $\Psi_\lambda(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$ so it's Lipschitz smooth, and it must have a set of minimizers $S$ because its domain is compact.
+            The objective function $\Psi_\lambda(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$ so it's Lipschitz continuous on its domain, and it must have a set of minimizers $S$ because its domain is compact.
             In addition, $\Psi_\lambda$ fits the assumption of Necoara et al. \cite[Theorem 8]{necoara_linear_2019}. 
@@
         \end{proposition}
-
         \begin{example}[inner loop linear convergence rate examples]\label{example:inn-lp-lin-cnvg}
@@
         \end{example}
-    \subsection{Inner loop complexity}
-        In this section, we will estimate the total number of iterations in the inner loop to achieve a given accuracy $\epsilon$ on primal objective $\Phi_\lambda$ of the proximal problem for some given $\lambda > 0$.
-        We will specify the context for parameters $\epsilon, \lambda$ in relation to the outer problem of obtaining $x_k \approx_{\epsilon_k} T_{B_k + \rho_k}(y_k)$.
 
@@
     This section puts results regarding the total complexity of the proposed inexact proximal gradient algorithm. 
+    \subsection{Inner loop complexity}
+        We remind that the parameters in the inner loop will change depending on the outer loop's iteration. 
+        To discuss the convergence we unfortunately have to re-introduce the proximal problem in the context of the accelerated proximal gradient method of the outer loop. 
+        \par
+        Let $(F, f, g, L)$ and sequence $(\alpha_k, B_k, \rho_k,\epsilon_k)_{k \ge0}$ satisfies Definition \ref{def:inxt-apg}. 
+        Fix any $k \ge 0$ to be the iteration counter of the outer loop. 
+        Let $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
+        The inner loop is an algorithm that solves the inexact proximal gradient problem $x \approx_{\epsilon_k} T_{B_k + \rho_k}(y_k)$ which is equivalent to evaluating: 
+        \begin{align*}
+            x_k \approx_{\epsilon_k} \hprox_{L_k^{-1} g}(y_k - L_k^{-1}\nabla f(y_k)).
+        \end{align*}
+        Where, $L_k := B_k + \rho_k$. 
+        Let $\lambda^{(k)} := L_k^{-1}, \tilde y_k := y_k - L_k^{-1}\nabla f(y_k)$, the proximal problem boils down to optimizing the following function $\Phi_\lambda^{(k)}$ as defined by: 
+        \begin{align}\label{eqn:primal-pp-k}
+            \Phi_\lambda^{(k)}(u) &:= \frac{1}{2\lambda^{(k)}} \Vert u - \tilde y_k \Vert^2 + \omega(A u). 
+        \end{align}
+        And its dual which is 
+        \begin{align}\label{eqn:dual-pp-k}
+            \Psi_\lambda^{(k)}(v) &:=
+            \frac{1}{2\lambda}
+            \left\Vert \lambda^{(k)}A^\top v - \tilde y_k
+            \right\Vert^2
+            + \omega^\star(v) 
+            - \frac{1}{2\lambda^{(k)}}\Vert \tilde y_k\Vert^2. 
+        \end{align}
+        The primal dual gap is $\mathbf G_\lambda^{(k)}(u, v) = \Phi_\lambda^{(k)}(u) + \Psi_\lambda^{(k)}(v)$. 
+        The above are identical to proximal problem defined in Section \ref{sec:optz-inxt-pp-problem} except for the introduction of iteration counter $k$ from the outer loop, and we had specified $\tilde y_k$ in relation to the outer loop.
+        Finally, the inner loop algorithm is responsible for optimizing the optimality gap, it satisfies that $\mathbf G_\lambda^{(k)}(u, v) \le \epsilon_k$ and all results from Section \ref{sec:conds-lin-cnvg-pp} applies.
+        \par
+        The following assumption specifies conditions where the complexity of the inner using ISTA can be globally bounded for all iteration of the accelerated proximal gradient algorithm of the outer loop.
+        This is crucial for analyzing the global convergence rate of the algorithm. 
+        \begin{assumption}[globally bounded inner loop complexity]\;\label{ass:bounded-inn-cmplx}\\
+            For any integer $k \ge 0$, this assumption is about parameters of the proximal problem $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$ introduced at the beginning of this section, iterates $\left(z_n^{(k)}, v_n^{(k)}\right)_{n\ge0}$, the primal dual solutions $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional parameters $\bar \lambda, \underline \lambda, \gamma^\circ$.
+            The assumptions now follow. 
+            \begin{enumerate}[nosep]
+                \item As specified in this section, the parameter $\lambda^{(k)} = (B_k + \rho_k)^{-1}$ are from the outer loop.
+We denote $L_k = B_k + \rho_k$ for short.
+We assume in addition, there exists $\lambda^{\min}, \lambda^{\max}$ such that:
+                $$
+                    - \infty < \lambda^{\min} \le \inf_{k \in \N \cup \{0\}} \lambda^{(k)} \le \sup_{k \in \N \cup \{0\}} \lambda^{(k)} \le \lambda^{\max} < \infty. 
+                $$ 
+                \item All the initial guesses given by an algorithm in the outer loop $v_0^{(k)}$ and minimizers $\bar v^{(k)}$ must have $\sup_{k \in \N \cup \{0\}}\left\Vert v_0^{(k)} - \bar v^{(k)}\right\Vert < \infty$.
+                \item There exists smallest error bound constant $\gamma^{\min}$ such that it lower bound all the constants for the proximal problem, i.e: $\exists \gamma_{\min}:\;0 < \gamma^{\min} \le \inf_{k \in \N \cup \{0\}} \gamma^{(k)}_\lambda$.
+                \item $\tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}$ all satisfies error bound conditions (Assumption \ref{ass:lin-cnvg-for-pp}) with $y = \tilde y_k, \Phi_\lambda = \Phi_\lambda^{(k)}, \Psi_\lambda = \Psi_\lambda^{(k)}, L_\Phi^\lambda = L^{\lambda, (k)}_{\Phi}$ and $\gamma_\lambda = \gamma_\lambda^{(k)}$.
+                \item The iterates of the inner loop $(z_n^{(k)}, v_n^{(k)})_{k \ge 0}$ are produced by an algorithm that satisfies Definition \ref{def:ista-inner-lp}. 
+            \end{enumerate}
+        \end{assumption}
+        \par
+        The proposition that follows characterize the bare minimum requirements so that the inner loop's complexity depends only on required accuracies $\epsilon$, and parameter $\lambda$ for all initial guess of the outer loop.
+        \begin{proposition}[inner loop complexity can be bounded globally]\;\label{prop:inner-lp-cmplx}\\
+            Let $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$, $\left(z_n^{(k)}, v_{n}^{(k)}\right)_{n \ge 0}$, $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and $C_1$ satisfies Assumption \ref{ass:bounded-inn-cmplx}.
+            \begin{enumerate}[nosep]
+                \item\label{prop:inner-lp-cmplx-result1} 
+                If $\lambda_1 > \lambda_2$ then $\Psi_{\lambda_1}(v) \ge \Psi_{\lambda_2}(v)$ for all $v \in \dom \omega^\star$. 
+                \item\label{prop:inner-lp-cmplx-result2}  As a consequence of the former, the sequence $L_\Phi^{\lambda, (k)}$ as specified back in Fact \ref{fact:minimizing-dual-pp} is bounded above so $\sup_{k \in \N \cup \{0\}}L_\Phi^{\lambda, (k)} < \infty$.
+                \item There exists a constant $C_1$ that bounds the optimality gap of all initial guesses: 
+                \begin{align*}
+                    \infty > C_1 \ge  \sup_{k \in \N \cup \{0\}}\left\lbrace
+                        \Psi_{\lambda}^{(k)}(v^{(k)}_0) - \Psi_\lambda^{(k)}(\bar v^{(k)})
+                    \right\rbrace. 
+                \end{align*}
+                \item\label{prop:inner-lp-cmplx-result3} 
+                There exists a constant $\infty > C_2 \ge \sqrt{C_1}\sup_{k \in \N \cup \{0\}}\left\lbrace L_\Phi^{\lambda, (k)}\sqrt{2\lambda^{(k)}} + \sqrt{C_1}\right\rbrace$. 
+                \item\label{prop:inner-lp-cmplx-result4} 
+                Denote $N_\epsilon$ to be the total number of iteration of inner loop needed to achieve $\mathbf G_\lambda^{(k)}(z_n, v_n) \le \epsilon$, then it's sufficient to have 
+                \begin{align*}
+                    N_{\epsilon} = \left\lceil 
+                        2\frac{\log(\epsilon/C_2)}{
+                            \log\left(
+                                1 - \frac{\gamma^{\min}}{2\lambda^{\max}}
+                            \right)
+                        }
+                    \right\rceil. 
+                \end{align*}
+            \end{enumerate}
+        \end{proposition}
+        \begin{proof}
+            We will start with \ref{prop:inner-lp-cmplx-result1}. 
+            After some algebra it can be shown that $\Psi_\lambda^{(k)}(v) = \frac{\lambda}{2}\Vert A^\top v\Vert^2 - \langle A^\top v, \tilde y_k\rangle + \omega^\star(v)$.
+            From then on it's direct and it has $\Psi_{\lambda_1}(v) - \Psi_{\lambda_2}(v) = \frac{\lambda_1 - \lambda_2}{2}\Vert A^\top v\Vert^2 \ge 0$. 
+            \par
+            To see \ref{prop:inner-lp-cmplx-result2}, observe that $\Phi_\lambda^{(k)}$ is $L_{\Phi}^{\lambda, (k)}$ Lipschitz continuous from Assumption \ref{ass:lin-cnvg-for-pp}, \ref{ass:bounded-inn-cmplx}.
+            By its definition in \eqref{eqn:primal-pp-k}, $\forall k \ge 0$ it satisfies $L_{\Phi}^{\lambda, (k)}$ is the largest when $\lambda = \lambda^{\min}$. 
+            And since $\lambda^{(k)}$ is finite, it has $\sup_{k \in \N \cup \{0\}}L_{\Phi}^{\lambda, (k)} < \infty$ too. 
+            \par
+            To see \ref{prop:inn-looplin-cnvg-item3}, we use \ref{prop:inn-looplin-cnvg-item1} and it's sufficient to have $C_1 = \Psi_{\lambda^{\max}}^{(k)}$
+        \end{proof}
 

### 2025-10-27 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

@@
     \end{proof}
+    \begin{proposition}[generic convergence rate of the gradient mapping]\;\label{prop:apg-cnvg-gm-generic}\\
+        \todoinline{Cette propositions ira démontrer que le séquence de ``Inexact Gradient Mapping" converge. }
+    \end{proposition}
+    \begin{proof}
+
+    \end{proof}
     \par
@@
             \begin{enumerate}[nosep]
-                \item Let $v_0\in\dom \omega^\star$ be a feasible initial guess of $\Psi_{\lambda}$, and let $\tau > \Vert AA^\top\Vert$ be the inverse stepsize. 
+                \item Let $v_0\in\dom \omega^\star$ be a feasible initial guess of $\Psi_{\lambda}$, and let $\tau \ge \lambda\Vert AA^\top\Vert$ be the inverse step size. 
                 \item Define $z_0 = y - \lambda A^\top v_0$ and smooth part of $\Psi_\lambda$ as $h := v \mapsto \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2$. 
@@
         \begin{proof}
-            Note that $\Psi_\lambda$ satisfies error bound condition in Assumption \ref{ass:lin-cnvg-for-pp}, and Definition \ref{def:ista-inner-lp} has $\tau \ge \Vert A^TA\Vert$ which satisfies Definition \ref{def:ista} therefore the linear convergence results of Theorem \ref{thm:lin-cnvg-ista-eb} applies to $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$.
+            Note that $\Psi_\lambda$ satisfies error bound condition in Assumption \ref{ass:lin-cnvg-for-pp}, and Definition \ref{def:ista-inner-lp} has $\tau \ge \lambda\Vert A^TA\Vert$ which satisfies Definition \ref{def:ista} therefore the linear convergence results of Theorem \ref{thm:lin-cnvg-ista-eb} applies to $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$.
             Therefore, we claim: 
@@
         \begin{assumption}[globally bounded inner loop complexity]\;\label{ass:bounded-inn-cmplx}\\
-            For any integer $k \ge 0$, this assumption is about parameters of the proximal problem $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$ introduced at the beginning of this section, iterates $\left(z_n^{(k)}, v_n^{(k)}\right)_{n\ge0}$, the primal dual solutions $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional parameters $\bar \lambda, \underline \lambda, \gamma^\circ$.
+            For any integer $k \ge 0$, this assumption is about parameters of the proximal problem $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$ introduced at the beginning of this section, iterates $\left(z_n^{(k)}, v_n^{(k)}\right)_{n\ge0}$, the primal dual solutions $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional parameters $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$.
             The assumptions now follow. 
@@
                 $$ 
-                \item All the initial guesses given by an algorithm in the outer loop $v_0^{(k)}$ and minimizers $\bar v^{(k)}$ must have $\sup_{k \in \N \cup \{0\}}\left\Vert v_0^{(k)} - \bar v^{(k)}\right\Vert < \infty$.
-                \item There exists smallest error bound constant $\gamma^{\min}$ such that it lower bound all the constants for the proximal problem, i.e: $\exists \gamma_{\min}:\;0 < \gamma^{\min} \le \inf_{k \in \N \cup \{0\}} \gamma^{(k)}_\lambda$.
+                \item There exists a constant $C_0$ such that all the initial guesses given by an algorithm in the outer loop $v_0^{(k)}$ and minimizers $\bar v^{(k)}$ satisfies $C_0 = \sup_{k \in \N \cup \{0\}}\left\Vert v_0^{(k)} - \bar v^{(k)}\right\Vert < \infty$.
+                \item There exists the smallest error bound constant $\gamma^{\min}$ such that it lower bound all the constants for the proximal problem, i.e: $\exists \gamma_{\min}:\;0 < \gamma^{\min} \le \inf_{k \in \N \cup \{0\}} \gamma^{(k)}_\lambda$.
                 \item $\tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}$ all satisfies error bound conditions (Assumption \ref{ass:lin-cnvg-for-pp}) with $y = \tilde y_k, \Phi_\lambda = \Phi_\lambda^{(k)}, \Psi_\lambda = \Psi_\lambda^{(k)}, L_\Phi^\lambda = L^{\lambda, (k)}_{\Phi}$ and $\gamma_\lambda = \gamma_\lambda^{(k)}$.
@@
         \begin{proposition}[inner loop complexity can be bounded globally]\;\label{prop:inner-lp-cmplx}\\
-            Let $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$, $\left(z_n^{(k)}, v_{n}^{(k)}\right)_{n \ge 0}$, $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and $C_1$ satisfies Assumption \ref{ass:bounded-inn-cmplx}.
+            Let $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$, $\left(z_n^{(k)}, v_{n}^{(k)}\right)_{n \ge 0}$, $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional parameters $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$ such that they satisfy Assumption \ref{ass:bounded-inn-cmplx}.
             \begin{enumerate}[nosep]
@@
                 If $\lambda_1 > \lambda_2$ then $\Psi_{\lambda_1}(v) \ge \Psi_{\lambda_2}(v)$ for all $v \in \dom \omega^\star$. 
-                \item\label{prop:inner-lp-cmplx-result2}  As a consequence of the former, the sequence $L_\Phi^{\lambda, (k)}$ as specified back in Fact \ref{fact:minimizing-dual-pp} is bounded above so $\sup_{k \in \N \cup \{0\}}L_\Phi^{\lambda, (k)} < \infty$.
-                \item There exists a constant $C_1$ that bounds the optimality gap of all initial guesses: 
-                \begin{align*}
-                    \infty > C_1 \ge  \sup_{k \in \N \cup \{0\}}\left\lbrace
+                \item\label{prop:inner-lp-cmplx-result2}  As a consequence of the former, the sequence $L_\Phi^{\lambda, (k)}$ as specified back in Fact \ref{fact:minimizing-dual-pp} is bounded above so, there exists $L_\Phi^{\max}$ such that $L_\Phi^{\max} = \sup_{k \in \N \cup \{0\}}L_\Phi^{\lambda, (k)} < \infty$.
+                \item\label{prop:inner-lp-cmplx-result3} There exists a constant $C_1$ that bounds the optimality gap of all initial guesses: 
+                \begin{align*}
+                    \infty > C_1 \ge  \sup_{k \in \N \cup \{0\}}
+                    \left\lbrace
                         \Psi_{\lambda}^{(k)}(v^{(k)}_0) - \Psi_\lambda^{(k)}(\bar v^{(k)})
@@
                 \end{align*}
-                \item\label{prop:inner-lp-cmplx-result3} 
+                \item\label{prop:inner-lp-cmplx-result4} 
                 There exists a constant $\infty > C_2 \ge \sqrt{C_1}\sup_{k \in \N \cup \{0\}}\left\lbrace L_\Phi^{\lambda, (k)}\sqrt{2\lambda^{(k)}} + \sqrt{C_1}\right\rbrace$. 
-                \item\label{prop:inner-lp-cmplx-result4} 
+                \item\label{prop:inner-lp-cmplx-result5} 
                 Denote $N_\epsilon$ to be the total number of iteration of inner loop needed to achieve $\mathbf G_\lambda^{(k)}(z_n, v_n) \le \epsilon$, then it's sufficient to have 
@@
                     N_{\epsilon} = \left\lceil 
-                        2\frac{\log(\epsilon/C_2)}{
-                            \log\left(
-                                1 - \frac{\gamma^{\min}}{2\lambda^{\max}}
+                        \frac{2\ln(\epsilon/C_2)}{
+                            \ln\left(
+                                1 - \frac{\gamma^{\min}}{2\lambda^{\max}\left\Vert AA^\top\right\Vert}
                             \right)
@@
             \end{enumerate}
+
         \end{proposition}
@@
             We will start with \ref{prop:inner-lp-cmplx-result1}. 
-            After some algebra it can be shown that $\Psi_\lambda^{(k)}(v) = \frac{\lambda}{2}\Vert A^\top v\Vert^2 - \langle A^\top v, \tilde y_k\rangle + \omega^\star(v)$.
-            From then on it's direct and it has $\Psi_{\lambda_1}(v) - \Psi_{\lambda_2}(v) = \frac{\lambda_1 - \lambda_2}{2}\Vert A^\top v\Vert^2 \ge 0$. 
+            After some algebra it can be shown that $\Psi_\lambda(v) = \frac{\lambda}{2}\Vert A^\top v\Vert^2 - \langle A^\top v, \tilde y_k\rangle + \omega^\star(v)$.
+            From then on it's direct, and it has $\Psi_{\lambda_1}(v) - \Psi_{\lambda_2}(v) = \frac{\lambda_1 - \lambda_2}{2}\Vert A^\top v\Vert^2 \ge 0$. 
             \par
             To see \ref{prop:inner-lp-cmplx-result2}, observe that $\Phi_\lambda^{(k)}$ is $L_{\Phi}^{\lambda, (k)}$ Lipschitz continuous from Assumption \ref{ass:lin-cnvg-for-pp}, \ref{ass:bounded-inn-cmplx}.
-            By its definition in \eqref{eqn:primal-pp-k}, $\forall k \ge 0$ it satisfies $L_{\Phi}^{\lambda, (k)}$ is the largest when $\lambda = \lambda^{\min}$. 
-            And since $\lambda^{(k)}$ is finite, it has $\sup_{k \in \N \cup \{0\}}L_{\Phi}^{\lambda, (k)} < \infty$ too. 
-            \par
-            To see \ref{prop:inn-looplin-cnvg-item3}, we use \ref{prop:inn-looplin-cnvg-item1} and it's sufficient to have $C_1 = \Psi_{\lambda^{\max}}^{(k)}$
+            By its definition in \eqref{eqn:primal-pp-k}, $\forall k \ge 0$ it satisfies $L_{\Phi}^{\lambda, (k)}$ is the largest when $\lambda = \lambda^{\max}$. 
+            And since $\lambda^{(k)}$ is finite, it has $L^{\max}_\Phi = \sup_{k \in \N \cup \{0\}}L_{\Phi}^{\lambda, (k)} < \infty$ too. 
+            \par
+            To see \ref{prop:inn-looplin-cnvg-item3}, we use \ref{prop:inn-looplin-cnvg-item1}, \ref{prop:inn-looplin-cnvg-item2} and, $C_0 = \sup_{k \in \{0\}\cup \N} \left\Vert v_0^{(k)} - \bar v^{(k)} \right\Vert < \infty$ from Assumption \ref{ass:bounded-inn-cmplx}, then it's sufficient to have: $C_1 = L_{\Phi}^{\max} C_0$ by $L^{(k)}_\Phi$ Lipschitz continuity of $\Phi_\lambda^{(k)}$.
+            \par
+            To see \ref{prop:inn-looplin-cnvg-item4}, use all previous results \ref{prop:inn-looplin-cnvg-item3}, \ref{prop:inn-looplin-cnvg-item2} and, then it's sufficient to have $C_2 = \sqrt{C_1}\left(L^{\max}_\Phi\sqrt{2\lambda^{\max}} + \sqrt{C_1}\right)$.
+            \par
+            And finally, we are ready to show \ref{prop:inner-lp-cmplx-result5}, it has for all $k \ge 0$: 
+            \begin{align*}
+                & \mathbf G_\lambda^{(k)}(z_n^{(k)}, v_n^{(k)}) 
+                \\
+                &\underset{(1)}{\le} 
+                \left(
+                    1 - \frac{\gamma_\lambda^{(k)}}{2 \tau^{(k)}}
+                \right)^{n/2}
+                \left(
+                    L_\Phi^{\lambda, (k)} \sqrt{2 \lambda^{(k)}} + 
+                    \sqrt{\Psi_{\lambda}^{(k)}(v^{(k)}_0) - \Psi_\lambda^{(k)}(\bar v^{(k)})}
+                \right)\left(
+                    \Psi_{\lambda}^{(k)}(v^{(k)}_0) - \Psi_\lambda^{(k)}(\bar v^{(k)})
+                \right)^{1/2}
+                \\
+                &\underset{(2)}{\le}
+                \left(
+                    1 - \frac{\gamma_\lambda^{(k)}}{2 \tau^{(k)}}
+                \right)^{n/2}
+                \left(
+                    L_\Phi^{\lambda, (k)} \sqrt{2 \lambda^{(k)}} + 
+                    \sqrt{C_1}
+                \right)\sqrt{C_1}
+                \\
+                &\underset{(3)}{\le}
+                \left(
+                    1 - \frac{\gamma_\lambda^{(k)}}{2 \tau^{(k)}}
+                \right)^{n/2} C_2
+                \\
+                &\underset{(4)}{\le}
+                \left(
+                    1 - \frac{\gamma^{\min}}{2 \lambda^{\max}\Vert AA^\top\Vert}
+                \right)^{n/2} C_2. 
+            \end{align*}
+            At (1), we used Theorem \ref{prop:inn-loop-lin-cnvg}. 
+            At (2), we used results form \ref{prop:inner-lp-cmplx-result3} and, at (3) we used \ref{prop:inner-lp-cmplx-result4}. 
+            Finally, at (4), we use the fact that the step size $\tau$ in Definition \ref{def:ista-inner-lp} which translate into our context, it has $\tau^{(k)} \ge \lambda^{(k)}\Vert AA^\top\Vert$, and hence it can be upper bounded by $\tau^{\max} := \sup_{k \in \N \cup \{0\}}\lambda^{(k)}\Vert AA^\top\Vert < \infty$.
+            Now, substitute $n = N_\epsilon$ then it's prominent that $\mathbf G_\lambda^{(k)}\left(z_n^{(k)}, v_n^{(k)}\right) \le \epsilon$ by using the log of base formula. 
         \end{proof}
+    \subsection{Overall complexity}
+        In this section we combine the complexity of the inner loop with the convergence rate of the outer loop to deduce the rate of convergence. 
+        Details will be given to the assumptions needed to obtain globally bounded complexity of the inner loop.
 

### 2025-10-28 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

@@
     For a multivalued mapping $T: \RR^n \rightarrow 2^{\RR^n}$, $\gra T$ denotes the graph of the operator, defined as $\{(x, y)\in \RR^n \times \RR^n : y \in Tx\}$. 
-    \subsection{Epsilon subgradient and inexact proximal point}
+    \subsection{Preliminaries}
         \begin{definition}[$\epsilon$-subgradient]\label{def:esp-subgrad}
@@
         \end{proof}
-
+        \begin{fact}[Fenchel Rockafellar duality]
+
+        \end{fact}
     \subsection{Inexact proximal gradient inequality}
@@
         \end{align}
-        This problem admits dual objective in $\RR^m$: 
+        Observe that $\rng A \cap \reli\dom g \neq\emptyset$ in Assumption \ref{ass:for-inxt-prox} shows $g$ is also closed convex and proper. 
+        The function $\Phi_\lambda$ is coersive due to its quadratic term and hence it must admit a minimizer \cite[Theorem 1.9]{rockafellar_variational_1998}. 
+        Recall the following famous theoretical result in the convex programming literature that we had adapted into our context. 
+        \begin{fact}[French Rockafellar Duality {\cite[Proposition 15.22]{bauschke_convex_2017}}]\;\label{fact:fn-rck-duality}\\
+            Let $f:\RR^n \rightarrow \overline \RR$ be closed convex and proper, $g: \RR^m \rightarrow \overline \RR$, $A \in \RR^{m \times n}$. 
+            If ${\mathbf 0 \in \inte(\dom g - A \dom f)}$, then 
+            \begin{align*}
+                \inf_{u\in \RR^n}\left\lbrace
+                    f(u) + g(Au)
+                \right\rbrace 
+                + \min_{v \in \RR^m}\left\lbrace
+                    f^\star\circ(-A^\top) + g^\star(v)
+                \right\rbrace = 0. 
+            \end{align*}
+        \end{fact}
+        \begin{remark}
+            The theorem is not exactly the same as what is claimed in the original text, since we are in a finite dimensional setting.
+            To see the original theorem cited in the finite dimension, we need the space $\mathcal H = \RR^n$ and then use \cite[Proposition 6.12]{bauschke_convex_2017}. 
+        \end{remark}
+        In our context, we are interested in the dual of the proximal problem $\Phi_\lambda$ which makes $f = u \mapsto \frac{1}{2\lambda}\Vert u - y\Vert^2$, and $g = \omega$, and it has $f^\star(v) = \frac{1}{2\lambda}\Vert \lambda v + y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2$ (see Apendix \ref{lemma:chore1}).
+        Consequently, $[f^\star \circ (- A^\top)](v) = \frac{1}{2\lambda}\Vert -\lambda A^\top v  + y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2$. 
+        And therefore, $\Phi_\lambda$ admits Fenchel Rockafellar dual (or simply the dual) objective in $\RR^m$: 
         \begin{align}\label{eqn:dual-pp}
-            \Psi_\lambda(v) &:=
-            \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2
+            \Psi_\lambda(v) &:= f^\star\circ(-A^\top) + g^\star(v) 
+            = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2
             + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2. 
@@
         \end{align}
-        If strong duality holds, it exists $(\hat u, \hat v)$ such that we have the following: 
+        Note that in this case the smooth part is quadratic and, $\dom f = \RR^n$, hence it translates to ${\mathbf 0 \in \inte(\dom g - A \dom f) = \inte(\dom g - \rng A)}$. 
+        This will hold because of $\rng A \cap \reli\dom g \neq\emptyset$ in Assumption \ref{ass:for-inxt-prox}.
+        Therefore strong duality holds and it exists $(\hat u, \hat v)$ such that we have the following: 
         \begin{align*}
@@
     \begin{proposition}[generic convergence rate of the gradient mapping]\;\label{prop:apg-cnvg-gm-generic}\\
-        \todoinline{Cette propositions ira démontrer que le séquence de ``Inexact Gradient Mapping" converge. }
+        \todoinline{Cette proposition ira démontrer que le séquence de ``Inexact Gradient Mapping" converge. }
     \end{proposition}
@@
             We will prove using induction.
-            Assume inductively that $\alpha_k \in (0, 1]$. 
-            We can solve for $\alpha_k$ using the recursive equality from Assumption \ref{ass:opt-mmntm-seq} which always has one of the strictly positive root given by: 
-            \begin{align*}
-                \alpha_k &=
-                \frac{L_{k - 1}}{2L_k}\left(
-                    - \alpha_{k - 1}^2 + \left(
-                        \alpha_{k - 1}^4 + 4 \alpha_{k - 1}\frac{L_k}{L_{k - 1}}
-                    \right)^{1/2}
-                \right)
-                \\
-                &= \frac{\alpha_{k - 1}^2L_{k - 1}}{2L_k}\left(
-                    - 1 + \left(
-                        1 + \frac{4 L_k}{L_{k - 1}\alpha_{k-1}^2}
-                    \right)^{1/2}
-                \right)
-                \\
-                &\underset{(1)}{<} \frac{\alpha_{k - 1}^2L_{k - 1}}{2L_k}\left(
-                    - 1 + 1 + 2 \alpha_{k - 1}^{-2}\frac{L_k}{L_{k - 1}}
+            Fix any $k \ge 1$. 
+            Assume inductively that $\alpha_{k - 1} \in (0, 1]$. 
+            We can solve for $\alpha_k$ using the recursive equality $(1 - \alpha_k) = \alpha_{k}^2L_k\alpha_{k - 1}^{-2}L_{k - 1}^{-1}$ from Assumption \ref{ass:opt-mmntm-seq}.
+            Writing $\alpha_{k - 1}$ as $\alpha$, and $L_k/L_{k - 1}$ as $q$.
+            We then solve for $\alpha_{k}$, the quadratic equation always admits one root that is strictly positive which is given as: 
+            \begin{align*}
+                \alpha_k &= \frac{1}{2}\left(
+                    - \frac{\alpha^2}{q} + \sqrt{
+                        \frac{\alpha^4}{q^2} + \frac{4\alpha^2}{q}
+                    }
+                \right)
+                \\
+                &= \frac{\alpha^2}{2q}\left(
+                    - 1 + \sqrt{1 + \frac{4q}{\alpha^2}}
+                \right)
+                \\
+                &\underset{(1)}{<}
+                \frac{\alpha^2}{2q}\left(
+                    -1 + 1 + \frac{2q}{\alpha^2}
                 \right)
@@
             \end{align*}
-            At (1) we completed a square inside the radical, and use the assumption that $\alpha_k > 0$ and, $L_k > 0, L_{k - 1} > 0$ because we had $B_k > 0$: 
-            \begin{align*}
-                1 + 4 L_{k}L_{k - 1}^{-1}\alpha_{k - 1}^{-2}
-                &= 
-                1 + 4 L_{k}L_{k - 1}^{-1}\alpha_{k - 1}^{-2}
-                + 2L_k^2L_{k - 1}^{-2}\alpha_{k - 1}^{-4}
-                - 2L_k^2L_{k - 1}^{-2}\alpha_{k - 1}^{-4}
-                \\
-                &= (1 + 2L_kL_{k - 1}^{-1}\alpha_{k - 1}^{-2})^2
-                - 2\alpha_{k - 1}^{-4}L_k^2L_{k - 1}^{-2}
-                \\
-                &< \left(1 + 2L_kL_{k - 1}^{-1}\alpha_{k - 1}^{-2}\right)^2. 
-            \end{align*}
-            To see that $\alpha_k > 0$, recall the same fact that $L_k > 0$, and use the inductive hypothesis that $\alpha_{k - 1} \in (0, 1]$ then $\alpha_k > 0$ because: 
-            \begin{align*}
-                \alpha_k &=
-                \frac{L_{k - 1}}{2L_k}\left(
-                    - \alpha_{k - 1}^2 + \left(
-                        \alpha_{k - 1}^4 + 4 \alpha_{k - 1}\frac{L_k}{L_{k - 1}}
-                    \right)^{1/2}
-                \right) 
-                \\
-                &\ge \frac{L_{k - 1}}{2L_k}\left(
-                    - \alpha_{k - 1}^2 + \left(
-                        \alpha_{k - 1}^4
-                    \right)^{1/2}
-                \right) 
-                \\
-                &> 0. 
-            \end{align*}
+            At (1) we completed a square in the radical, and we used the assumption $\alpha_k > 0$ and, $L_k > 0, L_{k - 1} > 0$ because we had $B_k > 0$, therefore the following chain of inequality holds:
+            \begin{align*}
+                1 + \frac{4q}{\alpha^2} &= 
+                1 + \frac{4q}{\alpha^2} + \frac{4q^2}{\alpha^4} - \frac{4\alpha^2}{\alpha^2}
+                \\
+                &= \left(
+                    1 + \frac{2q}{\alpha^2}
+                \right)^2 - \frac{4q^2}{\alpha^4} 
+                \\
+                &< \left(
+                    1 + \frac{2q}{\alpha^2}  
+                \right)^2. 
+            \end{align*}
+            To see that $\alpha_k > 0$, recall the same fact that $L_k > 0$, and the inductive hypothesis $\alpha_{k - 1} \in (0, 1]$ then $4q/\alpha^2 > 0$ so obviously $\alpha_k = \frac{\alpha^2}{2q}\left(-1 + \sqrt{1 + 4q/\alpha^2}\right) > 0$ because the quantity inside the radical is strictly larger than $1$.
             Therefore, inductively it holds that $\alpha_k \in (0, 1)$ too. 
@@
                 (1 - \alpha_k)
+                \left(
                     \frac{\alpha_{k - 1}^2L_{k - 1}}{\alpha_0^2L_0}
-                \frac{L_{k - 1}\alpha_0^2L_0}{L_k}
+                \right)
+                \frac{\alpha_0^2L_0}{L_k}
                 \\
                 &= 
-                (\beta_k\beta_{k - 1}^{-1})\beta_{k - 1}L_0\alpha_0^2L_k^{-1}
+                (\beta_k\beta_{k - 1}^{-1})\left(
+                    \beta_{k - 1}
+                \right)L_0\alpha_0^2L_k^{-1}
                 \\
@@
             \end{align*}
-            Since $\beta_i$ is monotone decreasing, it has $0 < \beta_i^{-1/2}\beta_{i - 1}^{-1/2} \le 1$, this gives: 
+            Since $\beta_i$ is monotone decreasing, it has $0 < \beta_i^{1/2}\beta_{i - 1}^{-1/2} \le 1$, this gives: 
             \begin{align*}
@@
             \end{align*}
-            Performing a telescoping sum, use the fact that $\beta_0 = 1$ will yield the desired results after some algebraic manipulations. 
+            Performing a telescoping sum for $i = 1, 2, \ldots, k$, use the fact that $\beta_0 = 1$ will yield the desired results after some algebraic manipulations. 
         \end{proof}
+        \begin{remark}
+        \end{remark}
         \begin{proposition}[$\mathcal O(1/k^2)$ optimal convergence rate of the outer loop]\;\label{prop:opt-cnvg-outr-loop}\\
@@
                     1 + k \alpha_0 \sqrt{L_0} \sqrt{L_{\min}^{-1}}
-                \right)^{-2} \ge \mathcal O(k^{-2-p}). 
+                \right)^{-2} = \mathcal O(k^{-2-p}). 
             \end{align*}
@@
                 \\
-                &\ge \mathcal O(k^{-2-p}). 
+                &= \mathcal O(k^{-2-p}). 
             \end{align*}
@@
     \par
-    The inner loop of the algorithm is another algorithm that evaluates $x_k \approx_\epsilon T_{(B_k + \rho_k)}(y_k)$ for a given value of $\epsilon, B + \rho$ and at the point $y_k$. 
-    To accomplish, let $\lambda = (B_k + \rho_k)^{-1}$, the algorithm needs to resolve the following equivalent inexact proximal point problem: 
+    The inner loop is another algorithm that evaluates $x_k \approx_\epsilon T_{(B_k + \rho_k)}(y_k)$ for a given value of $\epsilon, B + \rho$ and at the point $y_k$. 
+    To accomplish let's assume that the outer loop iteration $k$ is fixed throughout this entire section.
+    Now let $\lambda = (B_k + \rho_k)^{-1}$, the algorithm needs to resolve the following equivalent inexact proximal point problem: 
     \begin{align*}
@@
         In addition, assume that the optimization problem $F$ satisfies the error bound condition if it has for all $\tau \ge L, x \in \RR^n$ there exists $\gamma > 0$: 
-        \begin{align*}
+        \begin{align}\label{ineq:pg-eb}
             \Vert \mathcal G_\tau(x)\Vert \ge \gamma\dist(x|S). 
-        \end{align*}
+        \end{align}
     \end{assumption}
-    \begin{definition}[proximal gradient method]\label{def:ista}
+    \begin{definition}[proximal gradient method]\;\label{def:ista}\\
         Suppose that $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}. 
@@
             \end{enumerate}
-            The algorithm that solves the proximal problem generates the primal dual sequences $(z_n, v_n)$ such that for all $n = 0, 1, 2, \cdots$, by the rules: 
-            \begin{align*}
-                v_{n + 1} &= \hprox_{\tau^{-1} \omega^\star}\left(
-                    v_{n} - \tau^{-1}\nabla h(v_n)
+            The algorithm that solves the proximal problem generates the primal dual sequences $(z_j, v_j)$ such that for all $j = 0, 1, 2, \cdots$, they satisfy: 
+            \begin{align*}
+                v_{j + 1} &= \hprox_{\tau^{-1} \omega^\star}\left(
+                    v_{j} - \tau^{-1}\nabla h(v_j)
                 \right), 
                 \\
-                z_{n + 1} &= y - \lambda A^\top v_{n + 1}. 
-            \end{align*}
-            Terminates if $\mathbf G_\lambda(z_n, v_n) \le \epsilon$ where $\mathbf G_\lambda$ is given by \eqref{eqn:duality-gap-pp}. 
+                z_{j + 1} &= y - \lambda A^\top v_{j + 1}. 
+            \end{align*}
+            Terminates if $\mathbf G_\lambda(z_j, v_j) \le \epsilon$ where $\mathbf G_\lambda$ is given by \eqref{eqn:duality-gap-pp}. 
         \end{definition}
         \begin{remark}
-            The value of $\mathbf G_\lambda(z_n, v_n)$ is easy to compute, it only requires access to matrix $A, A^\top$, and the function $\omega$. 
+            The value of $\mathbf G_\lambda(z_j, v_j)$ is easy to compute, it only requires access to matrix $A, A^\top$, and the function $\omega$. 
             In case when the proximal operator for $\omega^\star$ is nontrivial, we can use the Moreau identity and the proximal operator of $\omega$ instead. 
-            The gradient $\nabla f(v)$ is easy to compute, and it is: $AA^T v - Ay$.
+            The gradient $\nabla f(v)$ is easy to compute, and it is: $AA^\top v - Ay$.
         \end{remark}
@@
             Let the parameters $(g, \omega, A, y, \Phi_\lambda, \Psi_\lambda, L^\lambda_{\Phi} ,\gamma_\lambda)$ of a proximal problem satisfy Assumption \ref{ass:lin-cnvg-for-pp}. 
-            Let $\tau$, $v_0, \epsilon$ be given by an algorithm that satisfies Definition \ref{def:ista-inner-lp} and, it generates iterates $(z_n, v_n)_{n \ge 0}$. 
+            Let $\tau$, $v_0, \epsilon$ be given by an algorithm that satisfies Definition \ref{def:ista-inner-lp} and, it generates iterates $(z_j, v_j)_{j \ge 0}$. 
             Let $\bar v$ be a minimizer of $\Psi_\lambda$, then the followings are true: 
             \begin{enumerate}[nosep]
-                \item The sequence $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item1}
-                \item If we let $\bar z := y - \lambda A^\top \bar v$, then $\Phi_\lambda(z_n) - \Phi_\lambda(\bar z)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item2}
-                \item The duality gap has convergence $\mathbf G_\lambda(z_n, v_n) \le \mathcal O\left(\left(1 - \frac{\gamma_\lambda}{2\tau}\right)^{n/2}\right)$. \label{prop:inn-looplin-cnvg-item3}
-                \item If $\mathbf G_\lambda(z_n, v_n) \le \epsilon$, then $z_n \approx_\epsilon \hprox_{\lambda g}(y)$. \label{prop:inn-looplin-cnvg-item4}
+                \item The sequence $\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item1}
+                \item If we let $\bar z := y - \lambda A^\top \bar v$, then $\Phi_\lambda(z_j) - \Phi_\lambda(\bar z)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item2}
+                \item The duality gap has convergence $\mathbf G_\lambda(z_j, v_j) \le \mathcal O\left(\left(1 - \frac{\gamma_\lambda}{2\tau}\right)^{j/2}\right)$. \label{prop:inn-looplin-cnvg-item3}
+                \item If $\mathbf G_\lambda(z_j, v_j) \le \epsilon$, then $z_j \approx_\epsilon \hprox_{\lambda g}(y)$. \label{prop:inn-looplin-cnvg-item4}
             \end{enumerate}
@@
         \begin{proof}
-            Note that $\Psi_\lambda$ satisfies error bound condition in Assumption \ref{ass:lin-cnvg-for-pp}, and Definition \ref{def:ista-inner-lp} has $\tau \ge \lambda\Vert A^TA\Vert$ which satisfies Definition \ref{def:ista} therefore the linear convergence results of Theorem \ref{thm:lin-cnvg-ista-eb} applies to $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$.
+            Note that $\Psi_\lambda$ satisfies error bound condition in Assumption \ref{ass:lin-cnvg-for-pp}, and Definition \ref{def:ista-inner-lp} has $\tau \ge \lambda\Vert A^TA\Vert$ which satisfies Definition \ref{def:ista} therefore the linear convergence results of Theorem \ref{thm:lin-cnvg-ista-eb} applies to $\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)$.
             Therefore, we claim: 
             \begin{align}\label{ineq:inn-loop-lin-cnvg-pitem1}
-                \Psi_\lambda(v_n) - \Psi_\lambda(\bar v) &\le 
+                \Psi_\lambda(v_j) - \Psi_\lambda(\bar v) &\le 
                 \left(
                     1 - \frac{\gamma_\lambda}{2\tau}
-                \right)^n
+                \right)^j
                 \left(
@@
             We will now proceed to proving \ref{prop:inn-looplin-cnvg-item2}. 
-            Recall that the iterates $z_n = y - \lambda A^\top v_n$, and $\bar z = y - \lambda A^\top \bar v$, and we have Lipschitz continuity of $\Phi_\lambda$, hence Theorem \ref{fact:minimizing-dual-pp} applies, in addition since $\Phi_\lambda$ were assumed to be globally Lipschitz on $\dom \Phi_\lambda$ in Assumption \ref{ass:lin-cnvg-for-pp}, this means that we can replace $K$ regardless of $\bar v$, and convergent primal sequence $z_n \rightarrow \bar z$ with $L_\Phi^\lambda$ which gives:
+            Recall that the iterates $z_j = y - \lambda A^\top v_j$, and $\bar z = y - \lambda A^\top \bar v$, and we have Lipschitz continuity of $\Phi_\lambda$, hence Theorem \ref{fact:minimizing-dual-pp} applies, in addition since $\Phi_\lambda$ were assumed to be globally Lipschitz on $\dom \Phi_\lambda$ in Assumption \ref{ass:lin-cnvg-for-pp}, this means that we can replace $K$ regardless of $\bar v$, and convergent primal sequence $z_j \rightarrow \bar z$ with $L_\Phi^\lambda$ which gives:
             \begin{align}\label{ineq:inn-loop-lin-cnvg-pitem2}
                 \begin{split}
-                    \Phi_\lambda(z_n) - \Phi_\lambda(\bar z) &\le L_\Phi^\lambda \sqrt{2\lambda}\left(
-                    \Psi_\lambda(v_n) - \Psi_\lambda (\bar v)
+                    \Phi_\lambda(z_j) - \Phi_\lambda(\bar z) &\le L_\Phi^\lambda \sqrt{2\lambda}\left(
+                    \Psi_\lambda(v_j) - \Psi_\lambda (\bar v)
                     \right)^{1/2}
@@
                         1 - \frac{\gamma_\lambda}{2\tau}
-                    \right)^{n/2}\left(
+                    \right)^{j/2}\left(
                         \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
@@
             \begin{align*}
-                & \mathbf G_\lambda(z_n, v_n) 
-                \\
-                &\underset{(1)}{=} \Phi_\lambda(z_n) + \Psi_\lambda(v_n) + 0
-                \\
-                &= \Phi_\lambda(z_n) + \Psi_\lambda(v_n) - \Phi_\lambda(\bar z) - \Psi_\lambda(\bar v)
-                \\
-                &= \Phi_\lambda(z_n)- \Phi_\lambda(\bar z) + \Psi_\lambda(v_n) - \Psi_\lambda(\bar v)
+                & \mathbf G_\lambda(z_j, v_j) 
+                \\
+                &\underset{(1)}{=} \Phi_\lambda(z_j) + \Psi_\lambda(v_n) + 0
+                \\
+                &= \Phi_\lambda(z_j) + \Psi_\lambda(v_j) - \Phi_\lambda(\bar z) - \Psi_\lambda(\bar v)
+                \\
+                &= \Phi_\lambda(z_j)- \Phi_\lambda(\bar z) + \Psi_\lambda(v_n) - \Psi_\lambda(\bar v)
                 \\
@@
                     1 - \frac{\gamma_\lambda}{2\tau}
-                \right)^{n/2}\left(
+                \right)^{j/2}\left(
                     \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
@@
                     1 - \frac{\gamma_\lambda}{2\tau}
-                \right)^{n}\left(
+                \right)^{j}\left(
                     \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
@@
                     1 - \frac{\gamma_\lambda}{2\tau}
-                \right)^{n/2}\left(
+                \right)^{j/2}\left(
                     L_\Phi^\lambda \sqrt{2\lambda}\left(
@@
                         1 - \frac{\gamma_\lambda}{2\tau}
-                    \right)^{n/2} (\Psi_\lambda(v_0) - \Psi_\lambda(\bar v))
+                    \right)^{j/2} (\Psi_\lambda(v_0) - \Psi_\lambda(\bar v))
                 \right)
@@
                     1 - \frac{\gamma_\lambda}{2\tau}
-                \right)^{n/2}\left(
+                \right)^{j/2}\left(
                     L_\Phi^\lambda \sqrt{2\lambda}
@@
         \end{remark}
+    \subsection{Concrete examples where we can have linear convergence}
+        Some results in the literature ensuite.  
+        \begin{definition}[quasi-strongly convex function]
+
+        \end{definition}
+        \begin{definition}[quadratic growth]
+
+        \end{definition}
+        \begin{fact}[error bound quadratic growth equivalence]
+
+        \end{fact}
+        \begin{fact}[Hoffman error bound]
+
+        \end{fact}
         The next proposition will characterize a precise case where Assumption \ref{ass:lin-cnvg-for-pp} is true, and it's a case widely available in applications. 
@@
         \begin{assumption}[globally bounded inner loop complexity]\;\label{ass:bounded-inn-cmplx}\\
-            For any integer $k \ge 0$, this assumption is about parameters of the proximal problem $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$ introduced at the beginning of this section, iterates $\left(z_n^{(k)}, v_n^{(k)}\right)_{n\ge0}$, the primal dual solutions $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional parameters $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$.
+            For any integer $k \ge 0$, this assumption is about parameters of the proximal problem $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$ introduced at the beginning of this section, iterates $\left(z_j^{(k)}, v_j^{(k)}\right)_{j\ge0}$, the primal dual solutions $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional constants $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$.
             The assumptions now follow. 
@@
                 \item $\tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}$ all satisfies error bound conditions (Assumption \ref{ass:lin-cnvg-for-pp}) with $y = \tilde y_k, \Phi_\lambda = \Phi_\lambda^{(k)}, \Psi_\lambda = \Psi_\lambda^{(k)}, L_\Phi^\lambda = L^{\lambda, (k)}_{\Phi}$ and $\gamma_\lambda = \gamma_\lambda^{(k)}$.
-                \item The iterates of the inner loop $(z_n^{(k)}, v_n^{(k)})_{k \ge 0}$ are produced by an algorithm that satisfies Definition \ref{def:ista-inner-lp}. 
+                \item The iterates of the inner loop $(z_j^{(k)}, v_j^{(k)})_{k \ge 0}$ are produced by an algorithm that satisfies Definition \ref{def:ista-inner-lp}. 
             \end{enumerate}
@@
         \begin{proposition}[inner loop complexity can be bounded globally]\;\label{prop:inner-lp-cmplx}\\
-            Let $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$, $\left(z_n^{(k)}, v_{n}^{(k)}\right)_{n \ge 0}$, $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional parameters $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$ such that they satisfy Assumption \ref{ass:bounded-inn-cmplx}.
+            Let $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$, $\left(z_j^{(k)}, v_{j}^{(k)}\right)_{j \ge 0}$, $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional parameters $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$ such that they satisfy Assumption \ref{ass:bounded-inn-cmplx}.
             \begin{enumerate}[nosep]
@@
                 \item\label{prop:inner-lp-cmplx-result5} 
-                Denote $N_\epsilon$ to be the total number of iteration of inner loop needed to achieve $\mathbf G_\lambda^{(k)}(z_n, v_n) \le \epsilon$, then it's sufficient to have 
+                Denote $N_\epsilon$ to be the total number of iteration of inner loop needed to achieve $\mathbf G_\lambda^{(k)}(z_j, v_j) \le \epsilon$, then it's sufficient to have 
                 \begin{align*}
@@
             \begin{align*}
-                & \mathbf G_\lambda^{(k)}(z_n^{(k)}, v_n^{(k)}) 
+                & \mathbf G_\lambda^{(k)}(z_j^{(k)}, v_j^{(k)}) 
                 \\
@@
                     1 - \frac{\gamma_\lambda^{(k)}}{2 \tau^{(k)}}
-                \right)^{n/2}
+                \right)^{j/2}
                 \left(
@@
                     1 - \frac{\gamma_\lambda^{(k)}}{2 \tau^{(k)}}
-                \right)^{n/2} C_2
+                \right)^{j/2} C_2
                 \\
@@
                     1 - \frac{\gamma^{\min}}{2 \lambda^{\max}\Vert AA^\top\Vert}
-                \right)^{n/2} C_2. 
+                \right)^{j/2} C_2. 
             \end{align*}
@@
             Finally, at (4), we use the fact that the step size $\tau$ in Definition \ref{def:ista-inner-lp} which translate into our context, it has $\tau^{(k)} \ge \lambda^{(k)}\Vert AA^\top\Vert$, and hence it can be upper bounded by $\tau^{\max} := \sup_{k \in \N \cup \{0\}}\lambda^{(k)}\Vert AA^\top\Vert < \infty$.
-            Now, substitute $n = N_\epsilon$ then it's prominent that $\mathbf G_\lambda^{(k)}\left(z_n^{(k)}, v_n^{(k)}\right) \le \epsilon$ by using the log of base formula. 
+            Now, substitute $j = N_\epsilon$ then it's prominent that $\mathbf G_\lambda^{(k)}\left(z_j^{(k)}, v_j^{(k)}\right) \le \epsilon$ by using the log of base formula. 
         \end{proof}
@@
 
+\appendix
+    \section{Super boring chores}
+        Super boring stuff that I just want to skip but somehow necessary. 
+        \begin{lemma}[That conjugate for the dual of proximal problem]\;\label{lemma:chore1}\\
+            Let $f:\RR^n \rightarrow \overline \RR:= \frac{1}{2\lambda}\Vert u - v\Vert^2$, then its conjugate is given by
+            \begin{align*}
+                f^\star(v) = \frac{1}{2\lambda}\Vert \lambda v + y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2. 
+            \end{align*}
+        \end{lemma}
+        \begin{proof}
+            Recall the following properties for any closed, proper convex function $f: \RR^n \rightarrow \overline \RR$. 
+            Let $a \in \RR^n$ be any vector, let $\alpha \in \RR, c \in\RR$ be some scalar, then we have these three properties of conjugating convex funtion. 
+            \begin{enumerate}[nosep]
+                \item $(\alpha f)^\star = \alpha f^\star \circ (\alpha^{-1}I)$. 
+                \item $(f + c)^\star(y) = f^\star(y) - c$. 
+                \item $\left(x \mapsto f(x) + \langle x, y\rangle\right)^\star(y) = f^\star(y - a)$. 
+            \end{enumerate}
+            From here we have: 
+            \begin{align*}
+                f^\star(v) 
+                &= 
+                \left(
+                   u \mapsto \lambda^{-1}\left(\frac{1}{2}\Vert u\Vert^2 - \langle u, y\rangle\right) 
+                    + \frac{1}{2\lambda} \Vert y\Vert^2
+                \right)^\star(v)
+                \\
+                &= \left(
+                    u \mapsto \lambda^{-1}\left(\frac{1}{2}\Vert u\Vert^2 - \langle u, y\rangle\right) 
+                \right)^\star(v)
+                - \frac{1}{2\lambda} \Vert y\Vert^2
+                \\
+                &= 
+                \left[
+                    \lambda^{-1}\left(
+                    u \mapsto \left(\frac{1}{2}\Vert u\Vert^2 - \langle u, y\rangle\right) 
+                \right)^\star\circ(\lambda I)
+                \right](v)
+                - \frac{1}{2\lambda} \Vert y\Vert^2
+                \\
+                &= \left[
+                    \lambda^{-1}\left(
+                    u \mapsto \left(
+                        \frac{\Vert \cdot\Vert^2}{2}
+                    \right)^\star(u + y)
+                \right)\circ(\lambda I)
+                \right](v)
+                - \frac{1}{2\lambda} \Vert y\Vert^2
+                \\
+                &= \left[
+                    \lambda^{-1}\left(
+                        u \mapsto \frac{\Vert u + y\Vert^2}{2}
+                    \right)\circ(\lambda I)
+                \right](v)
+                - \frac{1}{2\lambda} \Vert y\Vert^2
+                \\
+                &= \lambda^{-1}\left(
+                    \frac{1}{2}\Vert \lambda v + y\Vert^2
+                \right) 
+                - \frac{1}{2\lambda} \Vert y\Vert^2. 
+            \end{align*}
+        \end{proof}
+
 \bibliographystyle{siam}

### 2025-10-28 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

@@
     To start, the following assumption is the general error bound condition of a convex with additive composite structure.
+
     \begin{assumption}[gradient mapping error bound]\;\label{ass:pg-eb}\\
@@
     \subsection{Concrete examples where we can have linear convergence}
-        Some results in the literature ensuite.  
+        Some results in the literature now en suite.  
         \begin{definition}[quasi-strongly convex function]
@@
         \begin{fact}[Hoffman error bound]
+
+        \end{fact}
+        \begin{fact}[A characterization of quasi strongly convex function]
 

### 2025-10-28 Notebook LaTEX/R-WAPG/presentation-short.tex
>w<, all fixes

@@
             \begin{tcolorbox}
-                How much can we relax the choice of the sequence $\theta_k$ and still get an upper bound for the convergence rate? 
+                How much can we relax the choice of the sequence $\theta_k$ and retain an upper bound for the convergence rate? 
             \end{tcolorbox}
@@
                 \item It's interpreted from the Nesterov's estimating sequence technique and based on the proximal gradient inequality. 
-                \item It relaxes the assumption of the momentum sequence parameter while still retaining an upper bound on the optimality gap. 
+                \item It relaxes the assumption of the momentum sequence parameter while retaining an upper bound on the optimality gap. 
             \end{enumerate}
@@
                     \frac{\rho_{k}\alpha_{k}(1 - \alpha_k)}
-                    {\rho_k\alpha_k^2 + \alpha_k}(x_{k + 1} - x_k). 
+                    {\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
                 \end{align}
@@
                     }
-                    \STATE{$\theta_{k + 1} := \alpha_k(1 - \alpha_k)/(\alpha_k^2 + \alpha_{k + 1})$;}
+                    \STATE{$\theta_{k + 1} := \alpha_{k + 1}(\alpha_k^{-1} - 1)$;}
                     \STATE{$y_{k + 1}:= x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$; }
@@
                 \item $A \in \RR^{N \times N}$, full of i.i.d random variable from a standard normal distribution. 
+                \item $\lambda = 0.1$. 
                 \item Computed in prior, $L, \mu$ are parameters estimated by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$. The norm is the spectral norm. 
-                \item The smallest value of $F(x_k)$, for all algorithms, over all tries are taken as an estimate of $F^+$. 
+                \item Let $F_{\min}$ be the smallest value of $F(x_k)$, for all algorithms, over all trials, we estimate $F^+$ by $F^+ = F_{\min}*(1 - 2^{53})$. 
             \end{enumerate}
         \end{frame}
-        \begin{frame}{Results plotted}
-            With $A\in \RR^{N\times N}$ fixed, for each $x_0 \sim \mathcal N(I, \mathbf 0)$ realized, 30 experiments are preformed and the medium, minimum and maximum of $\delta_k$ are recorded for M-FISTA, Free R-WAPG, and V-FISTA.
+        \begin{frame}{LASSO Results plotted}
+            With $A\in \RR^{N\times N}$ fixed, for each $x_0 \sim \mathcal N(I, \mathbf 0)$ realized, 20 experiments are preformed and the medium, minimum and maximum of $\delta_k$ are recorded for M-FISTA, Free R-WAPG, and V-FISTA.
             \begin{figure}[H]

### 2025-11-06 Notebook LaTEX/EB is the key to IAGP/main-2025-09-18.tex
>w<, a lot of changes

\documentclass[12pt]{article}

% \input{presets/wang_full.tex}
\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{true}
\input{presets/wang/input.tex}
\input{presets/misc.tex}
\input{presets/julia_lstlisting.tex}

% NOTATIONS FOR THIS PAPER 
\DeclareMathOperator{\dist}{\mathop{dist}}
\DeclareMathOperator{\rng}{\mathop{rng}}

\begin{document}

\title{{\fontfamily{ptm}\selectfont Resolving a Fundamental Challenge in Inexct Proximal Method: The Unknown Constant of the Error Bound }}

\author{
    Author 1 Name, Author 2 Name
    \thanks{
        Subject type, Some Department of Some University, Location of the University,
        Country. E-mail: \texttt{author.namee@university.edu}.
    }
}

\date{\today}

\maketitle
\todoinline{This paper is currently in draft mode. Check source to change options. }
% \vskip 8mm

\begin{abstract} 
    \noindent
    I read a lot of papers on Catalyst, and restart. 
    And it just dawned on me on how simple the ideas can be, and I had identified a specific type of problem where the idea has practical advantage. 
    This is note is a plan of our upcoming practical paper, with numerical experiments, applications and sweet theories. 
\end{abstract}

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 47H05, 52A41, 90C25; Secondary 15A09, 26A51, 26B25, 26E60, 47H09, 47A63.
\noindent{\bfseries Keywords:}

% ==============================================================================
\section{Introduction}
    Let $Q \subseteq \RR^n$, we use the notation: $\dist(x | Q) = \inf_{z \in Q}\Vert x - z \Vert$. 
    When $Q \subseteq \RR^n$ is closed, nonempty and convex, we denote the closest point projection to the set by $\Pi(x | Q)$. 
    For any matrix $A$, we denote its kernel by $\ker A$, and its range $\rng A$. 
    \par
    Definte some matrix $A \in \RR^{m \times n}$ and, let vector $b \in \RR^m$ be such that $b \in \rng A$. 
    Consider the following optimization problem: 
    \begin{align}\label{eqn:prblm-exmp}
        \min_{x \in \RR^n}\left\lbrace
            \lambda\Vert x\Vert_1 + \frac{1}{2}\dist(x |\; \{z:Az = b \})^2
        \right\rbrace. 
    \end{align}
    This problem is not easy to solve because taking the gradient of the second function (denote $f(x) = \frac{1}{2}\dist(x | \{z: Ax = b\})$) in \eqref{eqn:prblm-exmp} requires the left pseudo inverse of matrix $A$. Since the gradient is given by: 
    \begin{align*}
        \nabla f(z) = z - A^\dagger (Az - b) = z - \Pi(z | \{x | Ax = b\}). 
    \end{align*}
    When $A$ is sparse or large.
    Taking the gradient of the function is a fundamental challenge for numerical algorithms. 
    \par
    The difficulty doesn't stop here at all and, the next issue about error bound condition is worse.  
    If we were to approximate $\nabla f(z)$ with $\tilde \nabla f(z)$ to minimize the error $\Vert \nabla f(z) - \tilde \nabla f(z)\Vert$ using some type of optimization algorithm that solves the projection problem approximately: 
    \begin{align*}
        \tilde z \approx z^+ = \Pi(z | \{x | Ax = b\}) &= 
        \argmin_{y}\left\lbrace
            \frac{1}{2}\Vert y - z \Vert^2 : Ay = b
        \right\rbrace.
    \end{align*}
    This approach has a fundamental challenge because the approximation error is $\Vert \tilde z - z^+\Vert$. 
    To estimate this quantity for inexact algorithm, in general would require some error bound conditions. 
    In this case, let $\sigma_{\min}(A)$ be the minimal nonzero singular value of $A$, the error bound is
    \begin{align*}
        \sigma_{\min}(A)\Vert \tilde z - z^+\Vert \le \Vert A\tilde z - b\Vert. 
    \end{align*}
    Look, this error bound condition requires knowing $\sigma_{\min}(A)$ which is just as hard as looking for the inverse of $A$. 
    A lot of the algorithm for estimating singular value are iterative method, or their specialized variants for sparse, or structured matrices. 
    This is a fundamental challenge when applying inexact methods in general. 
    To convince, consider changing the second function in the objective to $f(x) = (1/2)\dist(x | \{z: Ax \in \RR^n_+\})^2$. 
    In this case, the error bound condition is known as ``Hoffman Error Bound", and lower bounding the constant is a combinatorics problem, hence, extremely difficult to obtain in practice. 
    % \par
    % To construct our theoretical framework, We formulate the following abstraction representation:
    % \begin{align*}
    %     \min_{x \in \RR^n}\left\lbrace
    %         g(x) + 
    %         \dist\left(
    %             x \left|\; \bigcap_{i = 1}^m C_i \right.
    %         \right)^2
    %     \right\rbrace.
    % \end{align*}
    % Where 
    % \begin{enumerate}[nosep]
    %     \item 
    % \end{enumerate}
    \par
    \textbf{Contributions of the paper (hopefully)}.
    \begin{enumerate}[nosep]
        \item We show that an accelerated proximal gradient method with inexact gradient evaluation can converge under a relative error conditions. 
        \item We show that we don't need to know the constant for the error bound condition and we can still get convergence for the algorithm. 
        \item We give outer loop complexity analysis for our algorithm, if the inner loop error bound condition exists, and asymptoptic convergence rate when it doesn't exist. 
    \end{enumerate}

    \begin{assumption}\label{ass:smooth-nsmooth-sum}
        We assume the following about $(F, f, g, L)$: 
        \begin{enumerate}[nosep]
            \item $f: \RR^n \rightarrow \RR$ is a convex, $L$ Lipschitz smooth function but doesn't support any easy implementation of its proximal operator. 
            \item $g: \RR^n \rightarrow \RR$ is convex, proper, and closed, and its proximal operator can be easily implemented, and easy to obtain some element $\partial g$ at all points of the domain. 
            \item The over all objective has $F = f + g$. 
        \end{enumerate}
        Under this assumption, we denote the proximal gradient operator of $F = f+ g$ as $T_B(x) = \hprox_{B^{-1}g}(x - B^{-1}\nabla f(x))$. 
        Note that by definition it has also:
        \begin{align*}
            T_B(x) &= 
            \hprox_{B^{-1}g}\left(
                x - B^{-1}\nabla f(x)
            \right)
            \\
            &= \argmin_{z}\left\lbrace
                g(z)
                + \langle \nabla f(x), z\rangle
                + \frac{B}{2}\Vert z - x \Vert^2
            \right\rbrace. 
        \end{align*}
    \end{assumption}
    \begin{definition}[A measure of error from proximal gradient evaluations]\;\\
        Let $(F, f, g, L)$ satisfies Assumption \ref{ass:smooth-nsmooth-sum}. 
        For all $x, z \in \RR^n$, define $S$: 
        \begin{align*}
            S_B(z | x) &= \partial 
            \left[
                z \mapsto g(z)
                + \langle \nabla f(x), z\rangle
                + \frac{B}{2}\Vert z - x \Vert^2
            \right](z). 
        \end{align*}
    \end{definition}
    Observe: 
    \begin{enumerate}[nosep]
        \item $S_B(z | x) = \partial g(z) + \nabla f(x)+ B(z - x)$,
        \item $\mathbf 0 \in S_B(T(x) | x)$, 
        \item $(S_B(\cdot | x))^{-1}(\mathbf 0)$ is a singleton by strong convexity. 
    \end{enumerate}
    Let's assume inexact evaluation of $\tilde x \approx T_B(x)$ where $\nabla f$ is inexact. 
    Assuming that we have the estimate $\tilde \nabla f(x)$ for $\nabla f(x)$, then $\exists v \in \partial g(\tilde x)$. 
    \begin{align*}
        0 &= v + \tilde \nabla f(x) + B(\tilde x - x)
        \\
        \iff
        \nabla f(x) - \tilde \nabla f(x)
        &= v + \nabla f(x) + B(\tilde x - x). 
    \end{align*}
    This means $\nabla f(x) - \tilde \nabla f(x) \in S_B(\tilde x | x)$. 
    We want to control $w$ in the implementations of inexact accelerated proximal gradient algorithm.

\section{Key ideas we need to get right}
    \begin{definition}[inexact proximal gradient]\;\label{def:inxt-pg}\\
        Let $(F, f, g, L)$ satisfies Assumption \ref{ass:smooth-nsmooth-sum}.
        Let $\epsilon \ge 0, B \ge 0$. 
        We Define for all $x \in \RR^n$ the inexact proximal gradient operator $T_B^{(\epsilon)}(x)$ to be such that if $\tilde x \in T^{(\epsilon)}_{B}(x)$ then, $\exists w \in S_{B}(\tilde x | x):\Vert w\Vert\le \epsilon \Vert \tilde x - x\Vert$.         
    \end{definition}
    The algorithm we will design must produce iterates in a way that satisfies the inexact proximal gradient operator define above. 
    The following theorem will characterize a key inequality for convergence claim. 
    \begin{theorem}[inexact over regularized proximal gradient inequality]\;\label{thm:inxt-pg-ineq}\\
        Let $(F, f, g, L)$ satisfies Assumption \ref{ass:smooth-nsmooth-sum}.
        Take $T^{(\epsilon)}_B$ as given in Definition \ref{def:inxt-pg}. 
        Let $\epsilon \ge 0$. 
        For all $x\in \RR^n$, if $\exists B \ge 0$ such that $\tilde x \in T_{B + \epsilon}^{(\epsilon)}(x)$ and, $D_f(\tilde x, x)\le \frac{B}{2}\Vert \tilde x - x\Vert^2$. 
        Then for all $z, x \in \RR^n$ it has: 
        \begin{align*}
            0 &\le F(z) - F(\tilde x) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
            - \frac{B}{2}\Vert z - \tilde x\Vert^2. 
        \end{align*}
    \end{theorem}
    \begin{proof}
        By Definition \ref{def:inxt-pg}, $T_{B + \epsilon}^{(\epsilon)}(x)$ minimizes a $h(z) = z \mapsto g(z) + \langle \nabla f(x), z \rangle + \frac{B + \epsilon}{2}\Vert x - z\Vert^2$ to produce $\tilde x$ so that $w \in S_{B + \epsilon}(\tilde x| x) = \partial h(x)$. 
        $h$ is $B + \epsilon$ strongly convex by convexity of $g$. 
        Since $w \in \partial h(\tilde x)$, it has subgradient inequality through strong convexity: 
        $$
            (\forall z \in \RR^n)\;  
            \frac{B + \epsilon}{2}\Vert z - \tilde x\Vert^2 \le h(z) - h(\tilde x) - \langle w,  z - \tilde x\rangle. 
        $$
        This means for all $z \in \RR^n$: 
        \begin{align*}
            &\frac{B + \epsilon}{2}\Vert \tilde x - z \Vert^2 
            \\
            &\le 
            g(z) + \langle \nabla f(x), z\rangle + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
            - \left(
                g(\tilde x) + 
                \langle \nabla f(x), \tilde x\rangle
                + 
                \frac{B + \epsilon}{2}\Vert \tilde x - x\Vert^2
            \right)
                \\ &\quad 
                - \langle w, z - \tilde x\rangle
            \\
            &= 
            \left(
                g(z) - g(\tilde x)
                + \frac{B + \epsilon}{2}\Vert z - x\Vert^2 - \frac{B + \epsilon}{2}\Vert \tilde x - x\Vert^2
                - \langle w, z - \tilde x\rangle
            \right)
            \\&\quad 
                + \langle \nabla f(x), z - x + x -\tilde x\rangle
            \\
            &\underset{(1)}{=} 
            \left(
                g(z) - g(\tilde x)
                + \frac{B + \epsilon}{2}\Vert z - x\Vert^2 - \frac{B + \epsilon}{2}\Vert \tilde x - x\Vert^2
                - \langle w, z - \tilde x\rangle
            \right)
                \\
                &\quad 
                - D_f(z, x) + f(z)
                + D_f(\tilde x, x) - f(\tilde x)
            \\
            &=
            \left(
                F(z) - F(\tilde x)
                - \langle w, z - \tilde x\rangle
            \right)
            + 
            \left(
                \frac{B + \epsilon}{2}\Vert z - x\Vert^2 - D_f(z, x)
            \right) 
                \\ &\quad 
                + \left(
                    D_f(\tilde x, x)
                    - \frac{B + \epsilon}{2}\Vert \tilde x - x\Vert^2
                \right)
            \\
            &\underset{(2)}{\le} 
            \frac{B + \epsilon}{2}\Vert z - x\Vert^2 - D_f(z, x)
            + \left(
                \frac{B + \epsilon}{2}\Vert z - x\Vert^2
                - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2
            \right)
            \\
            &\le
            F(z) - F(\tilde x) + \Vert w \Vert\Vert z - \tilde x\Vert
            + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2
            \\
            &\underset{(3)}{\le}
            F(z) - F(\tilde x) 
            + \epsilon\Vert x - \tilde x\Vert\Vert z - \tilde x\Vert
            + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2. 
        \end{align*}
        At (1), we used: 
        \begin{align*}
            & \langle \nabla f(x), z - x\rangle
            - \langle \nabla f(x), \tilde x - x\rangle
            \\
            &= 
            - D_f(z, x) + f(z) - f(x)
            + D_f(\tilde x, x) - f(\tilde x) + f(x)
            \\
            &= f(z) + f(\tilde x) - D_f(z, x) + D_f(\tilde x , x). 
        \end{align*}
        At (2), we had $f$ convex as the assumption, hence $D_f(z, x) \le 0$. 
        We also had the assumption that $B$ makes $D_f(\tilde x, x) \le \frac{B}{2}\Vert \tilde x - x\Vert^2$, this simplies the third term from the previous line into $- \frac{\epsilon}{2}\Vert x - \tilde x\Vert^2$. 
        At (3), we applied the assumed inequality $\Vert w\Vert \le \epsilon \Vert x - \tilde x\Vert \Vert z - \tilde x\Vert$. 
        Continuing: 
        \begin{align*}
            0 &\le
            \left(
                F(z) - F(\tilde x) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
                - \frac{B + \epsilon}{2}\Vert z - \tilde x\Vert^2 
            \right)
            + \epsilon \Vert \tilde x - x\Vert \Vert z - \tilde x\Vert
            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2
            \\
            &\underset{(4)}{\le} 
            F(z) - F(\tilde x) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
            - \frac{B}{2}\Vert z - \tilde x\Vert^2. 
        \end{align*}
        At (4), we use some algebra: 
        \begin{align*}
            &
            \epsilon \Vert \tilde x - x\Vert \Vert z - \tilde x\Vert
            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2
            \\
            &=\epsilon \Vert \tilde x - x\Vert \Vert z - \tilde x\Vert
            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2 - \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2
            + \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2
            \\
            &= 
            - \epsilon(\Vert x - \tilde x\Vert - \Vert z -\tilde x\Vert)^2 
            + \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2 
            \\
            &\le \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2. 
        \end{align*}
    \end{proof}
    \subsection{The accelerated proximal gradient algorithm}
        \begin{definition}[accelerated inexact proximal gradient algorithm]\label{def:inxt-apg}
            Let 
            \begin{enumerate}[nosep]
                \item $(\alpha_k)_{k \ge 0}$ be a sequence in $(0, 1]$. 
                \item Let $(B_k)_{k \ge 0}$ be a non-negative sequence. 
                \item Let $(F, f, g, L)$ be given by Assumption \ref{ass:smooth-nsmooth-sum}. 
                \item Let $(\epsilon_k)_{k \ge 0}$ be a non-negative sequence that is the error schedule. 
            \end{enumerate}
            Initialize with any $(x_{-1}, v_{-1})$. 
            For these given parameters, an algorithm is a type of accelerated proximal gradient if it generates $(y_k, x_k, v_k)_{k \ge 0}$ such that
            for $k\ge 0$: 
            \begin{align*}
                & y_{k} = \alpha_{k} v_{k - 1} + (1 - \alpha_{k}) x_{k - 1},
                \\
                & x_k \in T_{B_k + \epsilon_k}^{(\epsilon_k)}(y_k): D_f(x_k, y_k) \le (B_k/2)\Vert x_k -  y_k\Vert^2, 
                \\
                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}).
            \end{align*}
        \end{definition}

\section{convergence rates results}
    We will now show that Algorithms satisfying Definition \ref{def:inxt-apg} has desirable convergence rate. 
    \begin{assumption}[convergence assumptions]\label{ass:apg-cnvg}
        Let $(F, f, g, L)$ satisfies Assumption \ref{ass:smooth-nsmooth-sum} and in addition assume that $F$ admits a set of non-empty minimizers $X^+$. 
    \end{assumption}
    \begin{lemma}[inexact one step convergence claim]\;\label{lemma:inxt-apg-onestep}\\
        Let $(F, f, g, L, X^+)$ satisfies Assumption \ref{ass:apg-cnvg}. 
        Suppose that an algorithm satisfies optimizes the given $F =f + g$ also satisfying Definition \ref{def:inxt-apg}.
        Then for the generated iterates $(y_k, x_k, v_k)_{k \ge 0}$, it has for all $k \ge 1$: 
        \begin{align*}
            &F(\bar x) - F(x_k)  - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
            \\
            &\le 
            \max\left(
                1 - \alpha_k, 
                \frac{\alpha_k(B_k + \epsilon_k)}{\alpha_{k -1}^2B_{k - 1}}
            \right)
            \left(
                F(x_{k - 1}) - F(\bar x) 
                + \frac{\alpha_{k - 1}^2B_{k - 1}}{2}\Vert \bar x - v_{k - 1} \Vert^2
            \right). 
        \end{align*}
    \end{lemma}
    \begin{proof}
        Let $\bar x \in X^+$, making it a minimizer of $F$. 
        Define $z_k := \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$. 
        It can be verified that:
        \begin{align}\begin{split}
            z_k - x_k &= \alpha_k(\bar x - v_k),
            \\
            z_k - y_k &= \alpha_k(\bar x - v_{k - 1}).     
        \end{split}\tag{a}\label{lemma:inxt-apg-onestep-a}
        \end{align}
        Because from Definition \ref{def:inxt-apg} it has for all $k \ge 1$: 
        \begin{align*}
            z_k - x_k &= 
            \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
            \\
            &= \alpha_k\bar x + (x_{k - 1} - x_k) - \alpha_kx_{k - 1}
            \\
            &= \alpha_k \bar x - \alpha_k v_k, 
            \\
            z_k - y_k &= 
            \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
            \\
            &= \alpha_k \bar x - \alpha_k v_{k - 1}. 
        \end{align*}
        For all $k \ge 0$, apply Theorem \ref{thm:inxt-pg-ineq} with $z = z_k, \tilde x = x_k, x = y_k, \epsilon = \epsilon_k, B = B_k$: 
        \begin{align*}
            0 &\le 
            F(z_k) - F(x_k) +
            \frac{B_k + \epsilon_k}{2}\Vert z_k - y_k\Vert^2
            - \frac{B_k}{2}\Vert z_k - x_k\Vert^2
            \\
            &\underset{(1)}{\le}
            \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
            + 
            \frac{B_k + \epsilon_k}{2}\Vert z_k - y_k\Vert^2
            - \frac{B_k}{2}\Vert z_k - x_k\Vert^2
            \\
            &\underset{\eqref{lemma:inxt-apg-onestep-a}}{=} 
            \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
                \\ &\quad 
                + \frac{(B_k + \epsilon_k)\alpha_k^2}{2}\Vert \bar x - v_{k - 1} \Vert^2
                - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
            \\
            &= 
            F(\bar x) - F(x_k)
            + (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x))
                \\ &\quad 
                + \frac{(B_k + \epsilon_k)\alpha_k^2}{2}\Vert \bar x - v_{k - 1} \Vert^2
                - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
            \\
            &= 
            F(\bar x) - F(x_k) 
            - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \\ &\quad 
                + (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x))
                + \frac{(B_k + \epsilon_k)\alpha_k^2}{2}\Vert \bar x - v_{k - 1} \Vert^2
            \\
            &= F(\bar x) - F(x_k) 
            - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \\ &\quad
                + (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x))
                + \frac{(B_k + \epsilon_k)\alpha_k^2}{\alpha_{k - 1}^2B_{k - 1}}\frac{\alpha_{k - 1}^2B_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
            \\
            &\le 
            F(\bar x) - F(x_k) - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
            \\ &\quad 
            + \max\left(
                1 - \alpha_k, 
                \frac{(B_k + \epsilon_k)\alpha_k^2}{\alpha_{k - 1}^2B_{k - 1}}
            \right)
            \left(
                F(x_{k - 1}) - F(\bar x) 
                + \frac{\alpha_{k - 1}^2B_{k - 1}}{2}\Vert \bar x - v_{k - 1} \Vert^2
            \right). 
        \end{align*}
        At (1) we used convexity of $f$ which is assumed and it makes $f(z_k) \le \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1})$ because $\alpha_k \in (0, 1]$ from Definition \ref{def:inxt-apg}. 
    \end{proof}
    \par
    As a prelude, to derive the convergence rate we unroll the recurrence relation proved in the above lemma.
    It remains to create convergence criterions of the error relative sequence $\epsilon_k$ such that the original optimal convergence rate of $\mathcal O(1/k^2)$ the sequence remains unaffected. 
    Let the sequence $(B_k)_{k \ge 0}$ be given as in Definition \ref{def:inxt-apg}. 
    We suggest the following using another sequence $\rho_k$ given by for all $k \ge 1$: 
    \begin{align*}
        \rho_k &:= \frac{B_k + \epsilon_k}{B_{k - 1}}\frac{B_{k - 1}}{B_k} = \frac{B_k + \epsilon_k}{B_k}
    \end{align*}
    This means the following: 
    \begin{align*}
        \max\left(
            1 - \alpha_k, 
            \frac{\alpha_k^2(B_k + \epsilon_k)}{\alpha_{k - 1}^2B_{k - 1}}
        \right)
        &=
        \max\left(
            1 - \alpha_k, 
            \rho_k\frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
        \right)
        \\
        &\le \max(1, \rho_k)\max\left(
            1 - \alpha_k, 
            \frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
        \right). 
    \end{align*}
    If we consider $\rho_k \le (1 + 2/k^2)$, it has the ability to make
    \begin{align*}
        \prod_{k = 1}^{n} 
        \max \left(
            1 - \alpha_k, 
            \frac{\alpha_k^2(B_k + \epsilon_k)}{\alpha_{k - 1}^2B_{k - 1}}
        \right)
        &\le 
        \prod_{k = 1}^{n} 
        \max(1, \rho_k)
        \prod_{i = 1}^{n}
        \max\left(
            1 - \alpha_k, 
            \frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
        \right)
        \\
        &\le \prod_{k = 1}^n
        \left(
            1 + \frac{2}{k^2}
        \right)
        \prod_{i = 1}^{n}
        \max\left(
            1 - \alpha_k, 
            \frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
        \right)
        \\
        &\le 2 
        \prod_{i = 1}^{n}\max\left(
            1 - \alpha_k, 
            \frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
        \right). 
    \end{align*}
    Assuming no $B_k = 0$ then the error schedule $\rho_k \le (1 + 2/k^2)$ translates to 
    \begin{align*}
        \frac{B_k + \epsilon_k}{B_k} &\le 1 + \frac{2}{k^2}
        \\
        \iff 
        \epsilon_k &\le - B_k + B_k(1 + 2/k^2) \le \frac{2B}{k^2}. 
    \end{align*}

\section{Motivations for applications}
    % Optimization problem of the following type: 
    % $$
    %     \min_{x} \left\lbrace
    %         f(Ax) + g(Dx)
    %     \right\rbrace, 
    % $$
    % where
    % \begin{enumerate}[nosep]
    %     \item Let $A \in \RR^{m_1 \times n}, D \in \RR^{m_2 \times n}$,  where inverting $A^TA + \mu I$ exactly for some $\mu > 0$ is computationally intensive on computers. 
    %     \item $f: \RR^{m_1} \rightarrow \RR$ is $L$ Lipschitz smooth and, convex but taking maybe $\hprox_f$ is computationally intensive. 
    %     \item $g: \RR^{m_2} \rightarrow \overline \RR$ is convex, closed and proper. 
    % \end{enumerate}
    % Solving it using traditional method such as ADMM \cite[chapter 6]{boyd_distributed_2011}, or Chambolle Pock \cite{chambolle_first-order_2010}, would require the knowledge of $(A^TA + \mu I)^{-1}$, and $f$ has $\hprox$ that is simple to evaluate. 
    % Inverting matrix exactly is never easy, especially the sparse and large matrix in image processing (The number of elements in the matrix scales by $\mathcal O(n^4)$ for a size $n \times n$ image for storage, and inverting it with bruteforce is $\mathcal (n^{6})$). 
    % People can do it a few time but it's not practical/simple to do it in every step of some iterative algorithms! 
    % Of course, we can use other smarter method such as Krylov Subspace method for block structured sparse matrices (or most recently, their randomized variants), but they will not be perfectly accurate.
    % Our method however, it will have the advantage of being matrix inversion free. 
    % \par
    % Our proposed algorithm allows inexact evaluation of the proximal operator of $g\circ D$. 
    % It can be evaluated using popular algorithm such as Chambolle Pock, or any other efficient approximation algorithm and it can bypass the need of any matrix inversion involving $D$. 
    % Because look, the problem we solve for our algorithm is $\hprox_{(B + \epsilon)^{-1}g\circ D}(x)$ which can be reformulated into: 
    % \begin{align*}
    %     \argmin_{z} \left\lbrace
    %         g(Dz) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
    %     \right\rbrace. 
    % \end{align*}
    % First order method such as Chambolle Pock can optimize the problem inexactly without matrix inversion. 
    % And, taking the gradient of $f(Ax)$ doesn't need for $(A^TA + \mu I)^{-1}$. 
    % Our method is also compatible with enhancement such as restart for objective function satisfying the quadratic growth conditions for optimal linear convergence. 
    % \par
    % This is especially useful for problem where, $A$ is massive and sparse without obvious structure. 
    % For example, a TV variational minimization approach for Robust MRI imaging that involves downsampling, blurring, or convolution \cite{zhang_robust_2022, joshi_mri_2009}\cite[Section 7.4]{chambolle_introduction_2016}. 
    % Applications as such adds another matrix $D$, or additional linear constraints to improve the robustness of MRI image reconstruction. 
    % Other potential applications with such structural optimization objective include large regression problem where the penalization term is highly non-trivial. 
    % \par
    % Why we think this paper will fly? 
    % Because: 
    % \begin{enumerate}
    %     \item The core theories part for the outer loop convergence described previously are quite simple and easy to understand for interested readers and, practitioners compared to previous results like in the Catalyst Frameworks or Inexact Accelerated Proximal Gradient Method. 
    %     \item I haven't found anyone that has good solutions in this type of problem which bypasses inverting $D$ or $A$. 
    %     \item It will shine numerically if coupled with advanced approximation algorithm for evaluation the prox of $g\circ D$, for specific $g$ relevant for applications. 
    %     \item Our theories give the flexibilities for whatever the practitioners want to do with $\hprox_{B^{-1}g\circ D}$. They can specialize and improved based our theoretical frameworks. 
    % \end{enumerate}

\bibliographystyle{siam}

\bibliography{references/refs.bib}

\end{document}

### 2025-11-06 Notebook LaTEX/EB is the key to IAGP/main.tex
>w<, a lot of changes

--- 2025-10-28 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
@@
     To start, the following assumption is the general error bound condition of a convex with additive composite structure. 
+    \begin{definition}[the exact proximal gradient and gradient mapping]\;\label{def:pg-and-gm}\\
+        Let $F = f + g$ where $f:\RR^n \rightarrow \RR$ is a differentiable function and, $g: \RR^n \rightarrow \overline \RR$ is closed convex and proper. 
+        We define the exact proximal gradient mapping and, gradient mapping: 
+        \begin{enumerate}[nosep]
+            \item The proximal gradient operator $T_{\tau}(x) := \hprox_{\tau^{-1}g}(x - \tau^{-1}\nabla f(x))$,
+            \item and the gradient mapping operator $\mathcal G_\tau(x) := \tau (x - T_\tau(x))$. 
+        \end{enumerate}
+    \end{definition}
+    \begin{definition}[error bound]\;\label{def:err-bnd}\\
+        Let $F = f + g$ where $f:\RR^n \rightarrow \RR$ is a differentiable function and, $g: \RR^n \rightarrow \overline \RR$ is closed convex and proper. 
+        Assume the set of minimizers $S = \argmin_{x} F \neq \emptyset$. 
+        Let $\gamma> 0$, and let proximal gradient mapping $T_\tau$, gradient mapping $\mathcal G_\tau$ of $F = f + g$ as given by Definition \ref{def:pg-and-gm}. 
+        Then their sum $F = f + g$ satisfies the error bound condition if there exists $\gamma > 0$ such that 
+        \begin{align}\label{ineq:pg-eb}
+            \Vert \mathcal G_\tau(x)\Vert \ge \gamma\dist(x|S). 
+        \end{align}
+    \end{definition}
     \begin{assumption}[gradient mapping error bound]\;\label{ass:pg-eb}\\
@@
             \item $S= \argmin_{x}{f(x) + g(x)} \neq \emptyset$, 
-            \item the objective function is given by $F = f + g$. 
-        \end{enumerate}   
-        Let the gradient mapping $\mathcal G_{\tau}$ be defined as: $\mathcal G_\tau(x) := \tau (x - T_\tau(x))$     
-        In addition, assume that the optimization problem $F$ satisfies the error bound condition if it has for all $\tau \ge L, x \in \RR^n$ there exists $\gamma > 0$: 
-        \begin{align}\label{ineq:pg-eb}
-            \Vert \mathcal G_\tau(x)\Vert \ge \gamma\dist(x|S). 
-        \end{align}
+            \item the objective function is given by $F = f + g$ and, it satisfis error bound (Definition \ref{def:err-bnd}). 
+        \end{enumerate} 
     \end{assumption}
@@
     \subsection{Concrete examples where we can have linear convergence}
-        Some results in the literature ensuite.  
-        \begin{definition}[quasi-strongly convex function]
-
+        Some results in the literature now follow.  
+        The goal of this section is to show that specific type of nonsmooth function $\omega$ that common appear in applications satisfies the error bound condition for the proximal problem, and hence the results from the previous section are applicable.
+        \begin{definition}[quasi-strongly convex function {\cite[Definition 1]{necoara_linear_2019}}]
+            Let $f:\RR^n \rightarrow \RR$ be differentiable. 
+            Let $X \subseteq \RR^n$ and suppose that the set of minimizers $X^+=\argmin_{x \in X} f(x) \neq \emptyset$ exists and, denote $f^+$ to be the minimum of $f$ on $X$. 
+            It is quasi strongly-convex on the set $X \subseteq \RR^n$ if $\exists \kappa > 0$ such that $\forall x \in X$, let $\bar x = \Pi_{X^+} x$, it satisfies
+            \begin{align*}
+                f^+ - f(x) - \langle \nabla f(x), \bar x - x\rangle + \frac{\kappa}{2}\Vert x - \bar x\Vert^2 \quad \left(\forall x \in X\right). 
+            \end{align*}
         \end{definition}
-        \begin{definition}[quadratic growth]
-
+        \begin{definition}[quadratic growth]\label{def:q-growth}
+            Let $F = f + g$ where $f: \RR^n \rightarrow \RR$ be differentiable and, $g: \RR^n \rightarrow \overline \RR$ be closed convex and, proper. 
+            Assume in addition that the set of minimizer $S := \argmin_{x\in \RR^n} F \neq \emptyset$, denote $F^+$ to be the minimum, then it satisfies the quadratic growth conditions if there exists $\kappa > 0$ such that
+            \begin{align*}
+                (\forall x \in \RR^n)\; F(x) \ge F^+ + \frac{\kappa}{2}\dist^2(x | S).
+            \end{align*}
         \end{definition}
-        \begin{fact}[error bound quadratic growth equivalence]
+        The following theorem shows that under the standard framework of smooth nonsmooth additive compsitive objective function, the quadratic growth condition implies error bound.
+        \begin{theorem}[quadratic growth implies error bound]\;\label{thm:qfg-means-eb}\\
+            Let $f: \RR^n \rightarrow $
+        \end{theorem}
+        \begin{proof}
+            Denote $x^+ = T_\tau(x)$, $\bar x = \Pi_{S}x$, and $\bar x ^+ = \Pi_{S} x^+$. 
+            We use the exact proximal gradient inequality by applying Theorem \ref{thm:inxt-pg-ineq} with $\epsilon = 0, \rho = 0$ and, $z = \bar x^+$ gives: 
+            \begin{align*}
+                0 &\ge F(x^+) - F(\bar x^+) - \tau \langle \bar x^+ - x^+, x^+ - x\rangle - \frac{\tau}{2}\Vert x - x^+\Vert^2
+                \\
+                &\underset{(1)}{\ge} \frac{\kappa}{2}\Vert x^+ - \bar x^+\Vert^2
+                - \Vert \tau(\bar x^+ - x^+)\Vert \Vert x^+ - x\Vert - \frac{1}{2\tau }\Vert \tau(x - x^+)\Vert^2
+                \\
+                &= \frac{\kappa}{2}\left\Vert
+                    x^+ - \bar x^+
+                \right\Vert^2 
+                - \frac{\tau}{2}\left(
+                    2\left\Vert
+                        \bar x^+ - x^+
+                    \right\Vert \left\Vert
+                        x^+ - x
+                    \right\Vert
+                    + \Vert x - x^+\Vert^2
+                \right)
+                \\
+                &\underset{(2)}{=}
+                \frac{\kappa + \tau}{2}\left\Vert x^+ - \bar x^+ \right\Vert^2 
+                - \frac{\tau}{2}(
+                    \Vert \bar x^+ - x^+\Vert + \Vert x^+ - x\Vert
+                )^2
+                \\
+                &\underset{(3)}{\ge}
+                \frac{\kappa + \tau}{2}\left(
+                    \Vert x - \bar x\Vert - \Vert x - x^+\Vert
+                \right)^2
+                - \frac{\tau}{2}(\Vert x - \bar x\Vert)^2
+                \\
+                \iff 
+                0 &\ge
+                \sqrt{\kappa + \tau}\left(
+                    \Vert x - \bar x\Vert - \Vert x - x^+\Vert
+                \right)
+                - \sqrt{\tau}(\Vert x - \bar x\Vert)
+                \\
+                &= (\sqrt{\kappa + \tau} - \sqrt{\tau})\Vert x - \bar x \Vert
+                - \sqrt{\kappa + \tau} \Vert x - x^+\Vert. 
+            \end{align*}
+            At (1), we used quadratic growth assumption and substitute the inequality of Definition \ref{def:q-growth}, and the Cauchy inequality. 
+            At (2), consider substituting $a = \bar x^+ - x^+, b = x^+ - x$, so the second terms with the parenthesis has inside $2\Vert a\Vert\Vert b\Vert + \Vert b\Vert^2 = (\Vert a\Vert + \Vert b\Vert)^2 - \Vert a\Vert^2$.
+            At (3), we used the properties of projecting onto the set set of minimizer $S$, which gives:
+            \begin{align*}
+                & \Vert x - \bar x\Vert \le 
+                \Vert x - \bar x^+\Vert 
+                \le \Vert x - x^+\Vert + \Vert x^+ - \bar x^+\Vert
+                \\
+                \implies
+                & \Vert x - \bar x\Vert - \Vert x - x^+\Vert
+                \le \Vert x^+ - \bar x^+\Vert
+            \end{align*}
+            Finally, re-arranging the results it should yield the following inequality: 
+            \begin{align*}
+                \Vert \mathcal G_\tau(x)\Vert 
+                &= \Vert \tau(x - x^+)\Vert 
+                \\
+                &\ge \tau\left(
+                    \frac{\sqrt{\kappa + \tau} - \sqrt{\tau}}{\sqrt{\kappa + \tau}}
+                \right)\Vert x - \bar x\Vert
+                \\
+                &= \frac{\tau\kappa}{\kappa + \tau + \sqrt{\tau(\kappa + \tau)}}
+                \Vert x - \bar x\Vert. 
+            \end{align*}
+            The above is error bound conditions as defined in Definition \ref{def:err-bnd}, with $\gamma = \frac{\tau\kappa}{\kappa + \tau + \sqrt{\tau(\kappa + \tau)}}$. 
+        \end{proof}
+        \begin{remark}
+            This theorem is not exactly a new result. 
+            We adapted claim and the proof here so the notations stays consistent and to make it self contained.
+
+        \end{remark}
+        \begin{fact}[Hoffman error bound]
 
         \end{fact}
-        \begin{fact}[Hoffman error bound]
+        \begin{fact}[a type of quasi strongly convex function]
 

### 2025-11-06 Notebook LaTEX/Notes and Failed Stuff/Notes on QSCNVX/main-2025-08-03.tex
>w<, a lot of changes

\documentclass[12pt]{article}

% \input{presets/wang_full.tex}
\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{true}
\input{presets/wang/input.tex}
\input{presets/misc.tex}
% \input{presets/julia_lstlisting.tex}

\begin{document}

\newcommand{\dist}{\ensuremath{\operatorname{dist}}}

\title{{\fontfamily{ptm}\selectfont Linear Convergence of Accelerated Gradient without Restart requires strict conditions}}

\author{
    Author 1 Name, Author 2 Name
    \thanks{
        Subject type, Some Department of Some University, Location of the University,
        Country. E-mail: \texttt{author.name@university.edu}.
    }
}

\date{March 2, 2020}

\maketitle
\todoinline{This paper is currently in draft mode. Check source to change options. }
% \vskip 8mm

\begin{abstract} 
    \noindent
    This is still a note for a draft so no abstract. 
\end{abstract}

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 47H05, 52A41, 90C25; Secondary 15A09, 26A51, 26B25, 26E60, 47H09, 47A63.
\noindent{\bfseries Keywords:}

% ==============================================================================
\section{Introduction}
    Necoara et al. \cite{necoara_linear_2019}  introduced the definition of quasi strongly convex function (Q-SCNVX), Quadratic Under approximations (QUA), Quadratic Gradient Growth (QGG), Proximal Error Bound (PEB) and, Quadratic Function Growth (QFG). 
    These conditions are relaxation of strong convexity which enables linear convergence rate of first order method, including Nesterov's accelerated variants. 
    In this file, we showed a new perspective of their works. 
    Our goal is to relax their definitions and, to extend the linear convergence results, using completely new ideas and perspective. 
    \par
    \textbf{Notations.}
    Unless specified, our ambient space is $\RR^n$ with Euclidean norm $\Vert \cdot\Vert$.
    Let $C\subseteq \RR^n$, $\Pi_C(\cdot)$ denotes the projection onto the set $C$, i.e: the closest point in $C$ to another point in $\RR^n$. 
    When $A$ is a matrix, we denote its minimum nonzero singular value in absolute value by: $\sigma(A)$. 
    \par
    The following definitions and assumptions are in Necoara. 
    % SYMBOL SET FOR THIS CHAPTER ONLY!

    \begin{assumption}[Necoara's linear convergence assumptions]\; \label{ass:necoara-linear} \\
        The following assumptions are about $(f, X, X^*, L_f)$. 
        \begin{enumerate}[nosep]
            \item $f: \RR^n \rightarrow \RR$ is an $L_f$ Lipschitz smooth function. 
            \item $X \subseteq \RR^n$ is a closed convex non-empty set. 
            \item $X^* = \argmin_{x \in X} f(x) \neq \emptyset$. 
        \end{enumerate}
    \end{assumption}
    Under this assumption, the following definitions are proposed. 
    \newcommand{\QSCNVX}{\ensuremath{q\mathcal{S}}}
    \newcommand{\QUA}{\ensuremath{\mathcal U}}
    \newcommand{\QGG}{\ensuremath{\mathcal G}}
    \newcommand{\QFG}{\ensuremath{\mathcal F}} 
    \newcommand{\PEB}{\ensuremath{\mathcal E}}
    \begin{definition}[Necoara's weaker characterizations of strong convexity]\; \\
        Suppose that $(f, X, X^*, L_f)$ are given by Assumption \ref{ass:necoara-linear}. 
        For all $x \in X$, denote $\bar x = \Pi_{X^*}x$. 
        The following definitions are relaxations of strong convexity. 
        \begin{enumerate}[nosep]
            \item $f$ is Q-SCNVX if there exists $\kappa_f > 0$ such that $f(\bar x) - f(x) - \langle \nabla f(x), \bar x - x\rangle \ge \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. 
            Which we denote it by $f \in \QSCNVX(f, L_f, \kappa_f)$. 
            \item $f$ is QUA if there exists $\kappa_f > 0$ such that $f(x) - f(\bar x) - \langle \nabla f(\bar x), x - \bar x\rangle \ge \frac{\kappa_f}{2}\Vert x -\bar x\Vert^2$. 
            We denote it by $f \in \QUA(f, L_f, \kappa_f)$.
            \item $f$ is QGG if there exists $\kappa_f > 0$ such that $\langle \nabla f(x) - \nabla f(\bar x), x - \bar x\rangle \ge \frac{\kappa}{2}\Vert x - \bar x\Vert^2$. 
            We denote it by $f \in \QGG(f, L_f, \kappa_f)$. 
            \item $f$ is PEB if there exists $\kappa_f > 0$ such that $\left\Vert x - L^{-1}\Pi_X(x - L^{-1}\nabla f(x))\right\Vert \ge \kappa_f\Vert x - \bar x\Vert$. 
            We denote it by $f \in \PEB(f, L_f, \kappa_f)$. 
            \item $f$ is QFG if there exists $\kappa_f > 0$ such that $f(x) - f(\bar x) \ge \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. 
            We denote it by $f \in \QFG(f, L_f, \kappa_f)$. 
        \end{enumerate}
    \end{definition}
    These definitions are the keys which Necoara's used to prove the linear convergence of projected gradient, and Nesterov's accelerated gradient method. 
    In this paper, we will show a simple perspective that simplifies their arguments on linear convergence Accelerated Gradient method, without restart. 
    \par
    Unfortunately, and this is said at the start, so far the new perspective doesn't produce new results that are not in the literature.

\section{Precursors materials for our proofs of linear convergence}
    For a function $f: \RR^n \rightarrow \RR$ we define its Bregman Divergence to be a mapping of $\RR^n \times \dom\nabla f\mapsto \overline \RR$ for all $x, y \in \RR^n$: 
    \begin{align*}
        D_f(x, y) &= 
        f(x) - f(y) - \langle \nabla f(y), x - y\rangle 
    \end{align*}
    Let $F = f + g$ where $f$ is $L$ Lipschitz smooth and $g$ is convex.
    Let $B > 0$. 
    We define the proximal gradient operator 
    \begin{align*}
        T_{B}(x) = \argmin_{z}\left\lbrace
            g(z) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
        \right\rbrace. 
    \end{align*}
    Take note that it's also $T_B(x) = \hprox_{B^{-1}g}(x - B^{-1}\nabla f(x))$, which is another equivalent representation. 
    The following assumption encapsulate the type of objective function that we have the convergence result for after applying the Nesterov's accelerated proximal gradient algorithm. 
    \begin{assumption}[objective function]\;\label{ass:obj-fxn}\\
        The following assumption is about $(F, f, g, h, A, b, \mu, L)$. 
        Let $m \in \N, n \in \N$ be arbitrary. 
        \begin{enumerate}[nosep]
            \item $h: \RR^m \mapsto \RR$ is a $L$ Lipschitz smooth and, $\mu \ge 0$ strongly convex function. 
            \item $A \in \RR^{m \times n}, b \in \RR^n$ are a matrix and a vector. 
            \item $f = h(Ax - b)$. 
            \item $g = \delta_{X}$, so $g$ is an indicator function of the set $X \subseteq \RR^n$ which we assume that it's closed onvex and non-empty. 
        \end{enumerate}
    \end{assumption}

    \begin{lemma}[strongly and Lipscthiz smooth convex affine composite]\;\label{lemma:aff-scnvx-smooth-lin-comp}\\
        Let $A \in \RR^{m \times n}, b \in \RR^n$. 
        Let $h: \RR^m \mapsto \RR$ be a $L$ Lipschitz and $\mu \ge 0$ strongly convex function. 
        Then it has for all $x, y \in \RR^n$: 
        \begin{align*}
            \frac{\sigma(A)^2\mu}{2}\Vert \Pi_{\ker A}(x - y)\Vert^2 
            &\le 
            D_f(x, y) 
            \le 
            \frac{L\Vert A\Vert^2}{2}\Vert x - y\Vert^2. 
        \end{align*}
    \end{lemma}
    \begin{proof}
        The lower bound is given by: 
        \begin{align*}
            & f(x) - f(y) - \langle \nabla f(y), x - y\rangle
            \\
            &=
            h(Ax) - h(Ay) - \langle A^T \nabla h(y), x - y\rangle
            \\
            &= h(Ax) - h(Ay) - \langle \nabla h(y), Ax - Ay\rangle
            \\
            &\ge \frac{\mu}{2}\Vert Ax - Ay\Vert^2
            \\
            &\ge 
            \frac{\mu}{2}
            \left(
                \Vert A\Pi_{\ker\; A}(x - y)
                + A(I - \Pi_{\ker\; A})(x - y) \Vert^2 
            \right)
            \\
            &\ge
            \frac{\mu\sigma(A)^2}{2}\Vert (I - \Pi_{\ker\; A})(x - y) \Vert^2. 
        \end{align*}
        The upper bound is direct from smoothness, which has: 
        \begin{align*}
            & f(x) - f(y) - \langle \nabla f(y), x - y\rangle
            \\
            &= h(Ax) - h(Ay) - \langle \nabla h(y), Ax - Ay\rangle
            \\
            &\le \frac{L}{2}\Vert Ax - Ay\Vert^2
            \\
            &\le \frac{L\Vert A\Vert^2}{2}\Vert x - y\Vert^2. 
        \end{align*}
    \end{proof}
    \begin{theorem}[proximal gradient inequality]\label{thm:pg-ineq}
        Suppose that $(F, f, g, h, A, b, \mu, L)$ satisfies Assumption \ref{ass:obj-fxn}. 
        Consider any $x, z \in \RR^n$, then there exists a $B \ge 0$ such that for $x^+ = T_B(x)$, it has $D_f(x, x^+) \le \frac{B}{2}\Vert x - x^+\Vert^2$, and it satisfies: 
        \begin{align*}
            0 &\le F(z) - F(x^+) + \frac{B - \mu\sigma(A)^2}{2}\Vert z - x\Vert^2 
            - \frac{B}{2}\Vert z - x^+\Vert^2
            + \frac{\mu\sigma(A)^2}{2}\Vert \Pi_{\ker A}(z - x)\Vert^2. 
        \end{align*}
    \end{theorem}
    \begin{proof}
        Denote $\sigma =\sigma(A)$ for short, and $\Pi = \Pi_{\ker A}, \Pi_{\perp} = I - \Pi_{\ker A}$ for short. 
        The function in the proximal gradient operator is $L$ strongly convex, so it has quadratic growth over the minimizer $x^+$: 
        \begin{align*}
            & \frac{B}{2}\Vert z - x^+\Vert^2
            \\
            &\le 
            \left(
                g(z) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
            \right)
            - \left(
                g(x^+) + \langle \nabla f(x), x^+ - x\rangle + \frac{B}{2}\Vert x - x^+\Vert^2
            \right)
            \\
            &=
            \left(
                F(z) - D_f(z, x) + \frac{B}{2}\Vert z - x\Vert^2
            \right) - 
            \left(
                F(x^+) - D_f(x^+, x) + \frac{B}{2}\Vert x - x^+\Vert^2
            \right)
            \\
            &\underset{(1)}{\le}
            \left(
                F(z) + \frac{B}{2}\Vert z - x\Vert^2 
                - \frac{\mu\sigma^2}{2}\Vert \Pi_{\perp}(z - x)\Vert^2
            \right)
            - \left(
                F(x^+) - D_f(x^+, x) + \frac{B}{2}\Vert x - x^+\Vert^2
            \right)
            \\
            &\underset{(2)}{\le} 
            F(z) 
            + \frac{B}{2}\Vert z - x\Vert^2
            - \frac{\mu\sigma^2}{2}\Vert \Pi_{\perp}(z - x)\Vert^2
            - F(x^+). 
        \end{align*}
        At (1), we used the fact that $f = h(Ax + b)$, so it has $D_f(z, x) \ge \frac{\mu\sigma(A)^2}{2}\Vert \Pi_{\perp}(z - x)\Vert^2$. 
        At (2), we used the fact that $B$ makes $- D_f(x, x^+) + \frac{B}{2}\Vert x - x^+\Vert^2 \ge 0$. 
        Continuing it has 
        \begin{align*}
            0 
            &\le 
            F(z) + \frac{B}{2}\Vert z - x\Vert^2 
            - \frac{\mu\sigma^2}{2}\Vert \Pi_{\perp}(z - x)\Vert^2
            - F(x^+)
            - \frac{B}{2}\Vert z - x^+\Vert^2
            \\
            &= 
            F(z) 
            + \frac{B}{2}\Vert z - x\Vert^2 
            - \frac{\mu\sigma^2}{2}\left(
                \Vert z - x\Vert^2 
                - \Vert \Pi(z - x)\Vert^2
            \right)
            - F(x^+)
            - \frac{B}{2}\Vert z - x^+\Vert^2
            \\
            &\le F(z) - F(x^+)
            + \frac{B - \mu\sigma^2}{2}\Vert z - x\Vert^2 
            - \frac{B}{2}\Vert z - x^+\Vert^2
            + \frac{\mu\sigma^2}{2}\Vert \Pi(z - x)\Vert^2. 
        \end{align*}
    \end{proof}
    \begin{theorem}[Jesen's inequality]\;\label{thm:jen-ineq}
        Let $h: \RR^n \rightarrow \RR$ be a $L$ Lipschitz smooth and $\mu\ge 0$ strongly convex function.  
        Let $A \in \RR^{n\times m}, b \in \RR^n$. 
        Denote $\Pi_{\perp} = I - \Pi_{\text{ker}\; A}$ for short. 
        Suppose that $f(x) = h(Ax + b)$, then it satisfies for all $x, y \in \RR^n, \lambda\in [0, 1]$ the inequality: 
        \begin{align*}
            &f(\lambda x + (1 - \lambda)y) 
            \\
            &\le 
            f(\lambda x + (1 - \lambda)y) + \lambda f(x) - (1 - \lambda)f(y)
            - \frac{\mu\sigma(A)^2\lambda(1 - \lambda)}{2}\Vert \Pi_{\perp}(x - y)\Vert^2. 
        \end{align*}
    \end{theorem}
    \begin{proof}   
        To simplify notations, we denote $\sigma = \sigma(A)$ for short, and use $\Pi = \Pi_{\text{ker}A}$, $\Pi_{\perp} = I - \Pi_{\text{ker}A}$ for short. 
        From Assumption 4 it has $f = h(Ax + b)$ therefore it has the following
        {\small
        \begin{align*}
            0 &\le D_f(x, y)  - \frac{\sigma^2 \mu}{2}\Vert \Pi_{\perp}(x - y)\Vert^2
            \\
            &= f(x) - f(y) - \langle \nabla f(y), x - y\rangle 
            - \frac{\sigma^2 \mu}{2}\left\Vert \Pi_{\perp}(x - y)\right\Vert^2
            \\
            &=
            f(x) - f(y) - \langle \nabla f(y), x - y\rangle
            - \frac{\sigma^2 \mu}{2}\left\Vert \Pi_{\perp}x\right\Vert^2
            - \frac{\sigma^2 \mu}{2}\left\Vert \Pi_{\perp}y\right\Vert^2
            + \sigma^2\mu\langle \Pi_{\perp}x, \Pi_{\perp}y\rangle
            \\
            &= 
            f(x) - \frac{\sigma^2 \mu}{2}\Vert \Pi_{\perp} x\Vert^2
            - \left(
                f(y) - \frac{\mu\sigma^2}{2}\Vert \Pi_\perp y\Vert^2 
            \right) 
            \\&\quad 
                - \sigma^2\mu\Vert \Pi_{\perp} y\Vert^2
                - \langle \nabla f(y), x - y\rangle
                + \sigma^2\mu\langle \Pi_\perp x, \Pi_\perp y\rangle
            \\
            &= 
            f(x) - \frac{\sigma^2 \mu}{2}\Vert \Pi_{\perp} x\Vert^2
            - \left(
                f(y) - \frac{\mu\sigma^2}{2}\Vert \Pi_\perp y\Vert^2 
            \right) 
            - \langle \nabla f(y), x - y\rangle
            + \sigma^2\mu\langle \Pi_\perp (x - y), \Pi_\perp y\rangle
            \\
            &= 
            f(x) - \frac{\sigma^2 \mu}{2}\Vert \Pi_{\perp} x\Vert^2
            - \left(
                f(y) - \frac{\mu\sigma^2}{2}\Vert \Pi_\perp y\Vert^2 
            \right) 
            - \langle \nabla f(y), x - y\rangle
            + \sigma^2\mu\left\langle x - y, \Pi_\perp^{\top}\Pi_\perp  y\right\rangle
            \\
            &= 
            f(x) - \frac{\sigma^2 \mu}{2}\Vert \Pi_{\perp} x\Vert^2
            - \left(
                f(y) - \frac{\mu\sigma^2}{2}\Vert \Pi_\perp y\Vert^2 
            \right) 
            + \left\langle x - y, \sigma^2\mu\Pi_\perp^{\top}\Pi_\perp  y - \nabla f(y)\right\rangle. 
        \end{align*}
        }
        Next, if $\phi (x) = f(x) + \frac{\sigma^2\mu}{2}\Vert \Pi_\perp x\Vert^2$, then $\nabla \phi(x) = \nabla f(x) + \mu\sigma^2\Pi_{\perp}^\top \Pi_{\perp} x$. 
        From here, it's not hard to see that the above inequality is:  $ 0\le \phi(x) - \phi(y) - \left\langle \nabla \phi(y), x - y\right\rangle$. 
        Hence, the function $f(x) - \frac{\sigma\mu}{2}\Vert \Pi_\perp x\Vert^2$ is a convex function. 
        From here, we will be ready to show the Jensen's formula. 
        For all $x, y \in \RR^n$, consider the convexity of $\phi$, it has for all $\lambda \in [0, 1]$ the inequality: 
        \begin{align*}
            0 &\le \lambda \phi(x) + (1 - \lambda)\phi(x) - \phi(\lambda x + (1 - \lambda)y)
            \\
            &\underset{(1)}{=} 
            f(\lambda x + (1 - \lambda)y) - \lambda f(x) - (1 - \lambda)f(y)
            - \frac{\mu\sigma^2\lambda(1 - \lambda)}{2}\Vert \Pi_{\perp}(x - y)\Vert^2. 
        \end{align*}
        At (1), we skipped a lot of algebra that the reader should be familiar if they already seem the proof in for $f$ that is strongly convex.
    \end{proof}
\section{the accelerated proximal gradient algorithm again}
    In this section we introduce the algorithms usually used in Nesterov's accelerated gradient. 
    \begin{definition}[similar triangle form]\label{def:st-form}
        Suppose that 
        \begin{enumerate}
            \item $F = f + g$ with $f$ Lipschitz smooth and, $g$ closed convex proper, 
            \item Denote $T_B$ to be the proximal gradient operator on $F = f + g$, 
            \item Let $q_k \in [0, 1)$ for all $k \ge 0$ be a parameter of the algorithm, 
            \item $(B_k)_{k \ge 0}$ is a sequence such that $B_k \ge 0$ for all $k \ge 0$. 
        \end{enumerate}
        Given the initial condition $v_{-1}, x_{-1} \in \RR^n$. 
        An algorithm is a similar triangle form of the accelerated proximal gradient if the iterates generated $(y_k, x_k, v_k)_{k \ge 1}$ satisfies for all $k \ge 1$: 
        \begin{align*}
            y_k &= \left(\frac{\alpha_k - q_k}{1 - q_k}\right)v_{k - 1} 
            + \left(\frac{1 - \alpha_k}{1 - q_k}\right) x_{k - 1},
            \\
            x_k &= T_{B_k}(y_k) \text{ s.t: } D_f(x_k, y_k) \le \frac{B_k}{2}\Vert x_k - y_k\Vert^2. 
            \\
            v_k &= x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
        \end{align*}
    \end{definition}
    \begin{definition}[relaxed Nesterov's momentum sequence]\;\label{def:r-nes-seq}\\
        We let 
        \begin{enumerate}
            \item $(q_k)_{k \ge 0}$ be a sequence such that $q_k \in (0, 1]$ for all $k \ge 1$, 
            \item $(\alpha_k)_{k \ge 0}$ be a sequence such that, $\alpha_0 \in (0, 1]$, and $\alpha_k \in (q_k, 1)$ for all $k \ge 1$. 
        \end{enumerate}
        For all $k \ge 1$ we define the sequence $(\rho_k)_{k \ge 0}$: 
        \begin{align*}
            \rho_{k - 1} &= \frac{\alpha_k(\alpha_k - q_k)}{(1 - \alpha_{k})\alpha_{k - 1}^2}. 
        \end{align*}
    \end{definition}

\section{Convergence of accelerated gradient}
    \subsection{Preparing for the convergence proof}
        \begin{lemma}[Convergence preparation part I]\label{lemma:cnvg-prep-part1}
            Let the sequence $(y_k, x_k, v_k)_{k \ge 1}$ be a sequence generated by Definition \ref{def:st-form}. 
            Let $\bar x \in \RR^n$ be arbitrary, define $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k$. 
            Then the sequence of iterates satisfies for all $k \ge 1$ all of the following equalities: 
            \begin{align*}
                z_k - y_k &= (1 - q_k)^{-1}\left(
                    (\alpha_k - q_k)(\bar x - v_{k - 1}) + q_k(1 - \alpha_k)(\bar x - x_{k - 1})
                \right), 
                \\
                z_k - x_k &= \alpha_k (\bar x - v_k), 
                \\
                y_k &= x_{k -1} + (1 - q_k)^{-1}(\alpha_{k - 1} - 1)(\alpha_k - q_k)(x_{k - 1} - x_{k - 2}). 
            \end{align*}
        \end{lemma}
        \begin{proof}
            From the update of $y_k$ in Definition \ref{def:st-form}, we have: 
            \begin{align*}
                0 &= \left(
                \frac{\alpha_k - q_k}{1 - q_k} 
                \right)v_{k - 1} 
                + \left(
                    \frac{1 - \alpha_k}{1 - q_k}
                \right)x_{k - 1} - y_k
                \\
                &= 
                \left(
                    \frac{\alpha_k - q_k}{1 - q_k} 
                \right)v_{k - 1} 
                + (1 - \alpha_k)x_{k - 1}
                + \left(
                    \frac{1 - \alpha_k}{1 - q_k} - (1 - \alpha_k)
                \right)x_{k - 1} - y_k
                \\
                &= 
                \left(
                    \frac{\alpha_k - q_k}{1 - q_k} 
                \right)v_{k - 1} 
                + (1 - \alpha_k)x_{k - 1}
                + (1 - \alpha_k)\left(
                    \frac{1 - (1 - \alpha_k)}{1 - q_k}
                \right)x_{k - 1} - y_k
                \\
                &= 
                \left(
                    \frac{\alpha_k - q_k}{1 - q_k} 
                \right)v_{k - 1} 
                + (1 - \alpha_k)x_{k - 1}
                + \frac{q_k(1 -\alpha_k)}{1 - q_k}x_{k - 1} - y_k. 
            \end{align*}
            Recall that $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k$. 
            Therefore, using previous results we have:
            \begin{align*}
                z_k - y_k &= 
                \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
                \\
                &= \alpha_k \bar x 
                - \left(
                    \frac{\alpha_k - q_k}{1 - q_k}
                \right)v_{k - 1}
                - \frac{q_k(1 -\alpha_k)}{1 - q_k}x_{k - 1}
                \\
                &= 
                \left(
                    \frac{\alpha_k - q_k}{1 - q_k}
                \right)(\bar x - v_{k - 1})
                + \left(
                    \alpha_k - \frac{\alpha_k - q_k}{1 - q_k} 
                \right)\bar x
                - \frac{q_k(1 -\alpha_k)}{1 - q_k}x_{k - 1}
                \\
                &= 
                \left(
                    \frac{\alpha_k - q_k}{1 - q_k}
                \right)(\bar x - v_{k - 1})
                + \left(
                    \frac{\alpha_k - \alpha_kq_k - (\alpha_k - q_k)}{1 - q_k}
                \right)\bar x
                - \frac{q_k(1 -\alpha_k)}{1 - q_k}x_{k - 1}
                \\
                &= 
                \left(
                    \frac{\alpha_k - q_k}{1 - q_k}
                \right)(\bar x - v_{k - 1})
                + \left(
                    \frac{q_k(1 - \alpha_k)}{1 - q_k}
                \right)\left(
                    \bar x - x_{k - 1}
                \right). 
            \end{align*}
            Using some basic algebra we also have: 
            \begin{align*}
                z_k - x_k &= 
                \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k 
                \\
                &= \alpha_k \bar x + x_{k - 1} - \alpha_k x_{k -1} - x_k
                \\
                &= \alpha_k (\bar x  + \alpha_k^{-1}x_{k - 1} - x_{k - 1} - \alpha_k^{-1} x_k) 
                \\
                &= \alpha_k (\bar x  + \alpha_k^{-1}(x_{k - 1} - x_k)- x_{k - 1}) 
                \\
                &= \alpha_k (\bar x - v_k). 
            \end{align*}
            Finally, $y_k$ can be expressed using $x_k$ only. 
            Starting with the first recurrence relation it has: 
            \begin{align*}
                (1 - q_k)^{-1}y_k &= 
                (\alpha_k - q_k) v_{k - 1} 
                + (1 - \alpha_k)x_{k - 1}
                \\
                &= 
                (\alpha_k - q_k)\left(
                    x_{k - 2} + \alpha_{k - 1}^{-1}(x_{k - 1} - x_{k - 2})
                \right) 
                + (1 - \alpha_k)x_{k - 1}
                \\
                &= 
                (\alpha_k - q_k)x_{k - 2} 
                + \alpha_{k - 1}^{-1}(x_{k - 1} - x_{k - 2}) + (1 - \alpha_k)x_{k - 1}
                \\
                &= (\alpha_k - q_k)(1 - \alpha_{k - 1}^{-1})x_{k - 2}
                + \left(
                    \frac{\alpha_k - q_k}{\alpha_{k - 1}} + 1 - \alpha_k
                \right)x_{k - 1}. 
            \end{align*}
            After some algebra it has: 
            \begin{align*}
                y_k &= 
                \frac{(\alpha_k - q_k)(1 - \alpha_{k - 1}^{-1})}{1 - q_k}x_{k - 2} 
                + \left(
                    \frac{\alpha_k - q_k}{\alpha_{k - 1}(1 - q_k)} + \frac{1 - \alpha_k}{1 - q_k}
                \right)x_{k - 1}
                \\
                &= 
                \frac{(\alpha_k - q_k)(1 - \alpha_{k - 1}^{-1})}{1 - q_k}x_{k - 2} 
                + \left(
                    \frac{
                        (\alpha_{k - 1}^{-1} -1)(\alpha_k - q_k)
                        + \alpha_k - q_k + 1 - \alpha_k
                    }{1 - q_k}
                \right)x_{k - 1}
                \\
                &= \frac{(\alpha_k - q_k)(1 - \alpha_{k - 1}^{-1})}{1 - q_k}x_{k - 2} 
                + \left(
                    \frac{
                        (\alpha_{k - 1}^{-1} -1)(\alpha_k - q_k)
                    }{1 - q_k} + 1
                \right)x_{k - 1}
                \\
                &= x_{k -1} + (1 - q_k)^{-1}(\alpha_{k - 1} - 1)(\alpha_k - q_k)(x_{k - 1} - x_{k - 2}). 
            \end{align*}
        \end{proof}
        \begin{lemma}[Convergence preparations part II]\;\label{lemma:cnvg-prep-part2}\\
            Suppose that sequences $(y_k, x_k, v_k)_{k \ge 0}$ satisfies Definition \ref{def:st-form}. 
            In addition assume that the sequence $(\alpha_k)_{k \ge 0}$ satisfies Definition \ref{def:r-nes-seq}. 
            For any arbitrary $\bar x \in \RR^n$, define for all $k \ge 1$ the sequence $z_k = \alpha_k \bar x + (1 - \alpha_k) x_{k - 1}$. 
            Then, for all $k \ge 1$, it has:
            \begin{align*}
                & \frac{1 - q_k}{2}\Vert z_k - y_k\Vert^2
                - \frac{q_k\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
                \\
                &= 
                \frac{\alpha_{k - 1}\rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                + \frac{q_k(1 - \alpha_k)(q_k - \alpha_k)}{1 - q_k}\Vert v_{k - 1} - x_{k - 1}\Vert^2
                \\
                &\le 
                \frac{\alpha_{k - 1}\rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2. 
            \end{align*}
        \end{lemma}
        \begin{proof}
            \begin{align}\label{eqn:cnvg-prep-part2-eqn1}
                \begin{split}
                    \frac{(\alpha_k - q_k)^2}{2(1 - q_k)}
                    - \frac{\alpha_{k - 1}\rho_{k - 1}(1 - \alpha_k)}{2}
                    &\underset{(1)}{=} 
                    \frac{(\alpha_k - q_k)^2}{2(1 - q_k)}
                    - \frac{\alpha_k(\alpha_k - q_k)}{2}
                    \\
                    &= \frac{1}{2(1 - q_k)}\left(
                        (\alpha_k - q_k)^2 - (1 - q_k)\alpha_k(\alpha_k - q_k)
                    \right)
                    \\
                    &= \frac{\alpha_k - q_k}{2(1 - q_k)}
                    \left(
                        \alpha_k - q_k - (1 - q_k)\alpha_k
                    \right)
                    \\
                    &= 
                    \frac{\alpha_k - q_k}{2(1 - q_k)}
                    \left(
                        - q_k + q_k \alpha_k
                    \right)
                    \\
                    &= \frac{(\alpha_k -q_k)q_k (\alpha_k - 1)}{1 - q_k}. 
                \end{split}
            \end{align}
            At (1), we used the relation $\alpha_{k - 1} \rho_{k - 1}(1 - \alpha_k) = \alpha_k(\alpha_k - q_k)$ because the sequence $(\alpha_k)_{k \ge 1}$ satisfies Definition \ref{def:r-nes-seq}.
            Next, we have: 
            \begin{align}\label{eqn:cnvg-prep-part2-eqn2}
                \begin{split}
                    \frac{q_k^2(1 - \alpha_k)^2}{1 - q_k}
                    - q_k\alpha_k(1 - \alpha_k)
                    &= 
                    \frac{q_k(1 - \alpha_k)}{1 - q_k}
                    \left(
                        q_k(1 - \alpha_k) - \alpha_k(1 - q_k)
                    \right)
                    \\
                    &= 
                    \frac{q_k(1 - \alpha_k)(q_k - \alpha_k)}{1 - q_k}. 
                \end{split}
            \end{align}
            Next, using two of the above results we have: 
            {\allowdisplaybreaks\small
            \begin{align*}
                & \frac{1 - q_k}{2}\Vert z_k - y_k\Vert^2
                - \frac{q_k\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
                \\
                &\underset{(1)}{=}
                \frac{1 - q_k}{2}
                \left\Vert
                    \left(
                    \frac{\alpha_k - q_k}{1 - q_k}
                    \right)(\bar x - v_{k - 1})
                    + \left(
                        \frac{q_k(1 - \alpha_k)}{1 - q_k}
                    \right)\left(
                        \bar x - x_{k - 1}
                    \right)
                \right\Vert^2
                - \frac{q_k\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
                \\
                &= 
                \frac{(\alpha_k - q_k)^2}{2(1 - q_k)}\Vert \bar x - v_{k - 1}\Vert^2
                + \frac{q_k^2(1 - \alpha_k)^2}{2(1 - q_k)}\Vert \bar x - x_{k - 1}\Vert^2
                + \frac{(\alpha_k - q_k)q_k(1 - \alpha_k)}{1 - q_k}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
                    \\&\quad 
                    - \frac{1}{2}q_k \alpha_k(1 - \alpha_k)\Vert \bar x - x_{k - 1}\Vert^2
                \\
                &= \frac{(\alpha_k - q_k)^2}{2(1 - q_k)}\Vert \bar x - v_{k - 1}\Vert^2
                + \frac{1}{2}\left(
                    \frac{q_k^2(1 - \alpha_k)^2}{1 - q_k} - q_k \alpha_k(1 - \alpha_k)
                \right)\Vert \bar x - x_{k - 1}\Vert^2
                    \\ &\quad 
                    + \frac{(\alpha_k - q_k)q_k(1 - \alpha_k)}{1 - q_k}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
                \\
                &= \frac{(\alpha_k - q_k)^2}{2(1 - q_k)}\Vert \bar x - v_{k - 1}\Vert^2
                + \frac{1}{2}\left(
                    \frac{q_k^2(1 - \alpha_k)^2}{1 - q_k} - q_k \alpha_k(1 - \alpha_k)
                \right)\Vert \bar x - x_{k - 1}\Vert^2
                    \\ &\quad 
                    + \frac{(\alpha_k - q_k)q_k(1 - \alpha_k)}{1 - q_k}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
                \\
                &= 
                \frac{1}{2}\left(
                    \frac{(\alpha_k - q_k)^2}{1 - q_k}
                    - \alpha_{k - 1}^2 \rho_{k - 1}(1 - \alpha_k)
                \right)\Vert \bar x - v_{k - 1}\Vert^2
                    \\&\quad
                    + \frac{1}{2}\left(
                        \frac{q_k^2(1 - \alpha_k)^2}{1 - q_k} - q_k \alpha_k(1 - \alpha_k)
                    \right)\Vert \bar x - x_{k - 1}\Vert^2
                    \\ &\quad 
                    + \frac{(\alpha_k - q_k)q_k(1 - \alpha_k)}{1 - q_k}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
                    - \frac{\alpha_{k - 1}^2 \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \\
                &\underset{\text{(2)}}{=}
                \frac{1}{2}\frac{(\alpha_k - q_k)q_k(\alpha_k - 1)}{1 - a_k}\Vert \bar x - v_{k - 1}\Vert^2
                + \frac{1}{2}\left(
                    \frac{q_k^2(1 - \alpha_k)^2}{1 - q_k} - q_k \alpha_k(1 - \alpha_k)
                \right)\Vert \bar x - x_{k - 1}\Vert^2
                    \\ &\quad 
                    + \frac{(\alpha_k - q_k)q_k(1 - \alpha_k)}{1 - q_k}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
                    - \frac{\alpha_{k - 1}^2 \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \\
                &\underset{\text{(3)}}{=}
                \frac{1}{2}\frac{(\alpha_k - q_k)q_k(\alpha_k - 1)}{1 - a_k}\Vert \bar x - v_{k - 1}\Vert^2
                + \frac{1}{2}\frac{q_k(1 - \alpha_k)(q_k - \alpha_k)}{1 - q_k}\Vert \bar x - x_{k - 1}\Vert^2
                    \\ &\quad 
                    + \frac{(\alpha_k - q_k)q_k(1 - \alpha_k)}{1 - q_k}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
                    - \frac{\alpha_{k - 1}^2 \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \\
                &= \frac{\alpha_{k - 1}^2\rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                + \frac{q_k(1 - \alpha_k)(q_k - \alpha_k)}{1 - q_k}\Vert v_{k - 1} - x_{k - 1}\Vert^2. 
                \\
                &\underset{(4)}{\le}
                \frac{\alpha_{k - 1}^2\rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2. 
            \end{align*}
            }
            At (1) we used one of the results from Lemma \ref{lemma:cnvg-prep-part1}, at (2) we used \eqref{eqn:cnvg-prep-part2-eqn1}, and at (3) we used \eqref{eqn:cnvg-prep-part2-eqn2}. 
            At (4), we used the fact that $\alpha_k \in (q_k, 1)$, which means that the coefficient $q_k(1 - \alpha_k)(q_k - \alpha_k) \le 0$, therefore we can simplify the term away. 
        \end{proof}
    \subsection{getting the convergence results}
        \begin{theorem}[the generic convergence results]\label{thm:cnvg-generic}
            Suppose that $(F, f, g, h, A, b, \mu, L)$ satisfies Assumption \ref{ass:obj-fxn}. 
            Let the sequence $(y_k, x_k, v_k)_{k \ge 1}$ satisfies Definition \ref{def:st-form}, with the $F$ we just assumed, and $q_k = (\mu\sigma(A)^2)/B_k$. 
            Then for all $k \ge 1$ it satisfies 
            \begin{align*}
                & F(x_k) - F(\bar x) 
                + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \\
                &\le 
                (1 - \alpha_k)\max\left(
                    1, \frac{\rho_{k - 1}L_k}{L_{k - 1}}
                \right)\left(
                    F(x_{k - 1}) - F(\bar x) 
                    + \frac{L_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \right) + \mathcal R_k. 
            \end{align*}
            Where $\mathcal R_k = \frac{\sigma(A)^2\mu}{2}\Vert \Pi_{\ker A}(z_k - y_k)\Vert^2 + \frac{\mu\sigma(A)^2\alpha_k(1 - \alpha_k)}{2}\Vert \Pi_{\ker A}(\bar x - x_{k - 1})\Vert^2$. 
        \end{theorem}
        \begin{proof}
            Let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$. 
            $\bar x$ remains undetermined. 
            Denote $\Pi = \Pi_{\ker A}$, and $\Pi_{\perp} = I - \Pi_{\ker A}$. 
            Recall that we had the parameters $q_k$ for all $k \ge 1$ set by $q_kB_k = \sigma(A)^2\mu$. 
            Starting with the proximal gradient inequality (Theorem \ref{thm:pg-ineq}), we let $z = z_k, x = y_k, x^+ = T_{B_k}(y_k)$. 
            {\allowdisplaybreaks
                \begin{align*}
                    0 &\le 
                    F(z_k) - F(x_k) 
                    + \frac{B_k - \mu\sigma(A)^2}{2}\Vert z_k - y_k\Vert^2 
                    - \frac{B_k}{2}\Vert z_k - x_k\Vert^2 
                    + \frac{\mu\sigma(A)^2}{2}\Vert \Pi(z_k - y_k)\Vert^2
                    \\
                    &\underset{(1)}{\le} 
                    \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
                    - \frac{\mu\sigma(A)^2\alpha_k(1 - \alpha_k)}{2}\Vert \Pi_{\perp}(\bar x - x_{k - 1})\Vert^2
                        \\&\quad
                        + \frac{B_k - \mu\sigma(A)^2}{2}\Vert z_k - y_k\Vert^2 
                        - \frac{B_k}{2}\Vert z_k - x_k\Vert^2 
                        + \frac{\mu\sigma(A)^2}{2}\Vert \Pi(z_k - y_k)\Vert^2
                    \\
                    &= 
                    \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
                    - \frac{\mu\sigma(A)^2\alpha_k(1 - \alpha_k)}{2}
                        \left(
                            \Vert \bar x - x_{k - 1}\Vert^2 - \Vert \Pi(\bar x - x_{k - 1})\Vert^2
                        \right)
                        \\&\quad
                        + \frac{B_k - \mu\sigma(A)^2}{2}\Vert z_k - y_k\Vert^2 
                        - \frac{B_k}{2}\Vert z_k - x_k\Vert^2 
                        + \frac{\mu\sigma(A)^2}{2}\Vert \Pi(z_k - y_k)\Vert^2
                    \\
                    &\underset{(2)}{=}
                    \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
                    - \frac{q_kL_k\alpha_k(1 - \alpha_k)}{2}
                        \left(
                            \Vert \bar x - x_{k - 1}\Vert^2 - \Vert \Pi(\bar x - x_{k - 1})\Vert^2
                        \right)
                        \\&\quad
                        + \frac{B_k - q_kL_k}{2}\Vert z_k - y_k\Vert^2 
                        - \frac{B_k}{2}\Vert z_k - x_k\Vert^2 
                        + \frac{q_kL_k}{2}\Vert \Pi(z_k - y_k)\Vert^2
                    \\
                    &= 
                    \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
                    + B_k\left(
                        \frac{1 - q_k}{2}\Vert z_k - y_k\Vert^2 
                        - \frac{q_k\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
                    \right)
                        \\&\quad
                        - \frac{B_k}{2}\Vert z_k - x_k\Vert^2 
                        + \frac{q_kL_k}{2}\Vert \Pi(z_k - y_k)\Vert^2
                        + \frac{q_kL_k\alpha_k(1 - \alpha_k)}{2}\Vert \Pi(\bar x - x_{k - 1})\Vert^2
                    \\
                    &\underset{(3)}{\le} 
                    \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
                    + \frac{B_k\alpha_{k - 1}\rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                        \\&\quad
                        - \frac{B_k}{2}\Vert z_k - x_k\Vert^2 
                        + \frac{q_kL_k}{2}\Vert \Pi(z_k - y_k)\Vert^2
                        + \frac{q_kL_k\alpha_k(1 - \alpha_k)}{2}\Vert \Pi(\bar x - x_{k - 1})\Vert^2
                    \\
                    &\underset{(4)}{=}
                    \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
                    + \frac{B_k\alpha_{k - 1}\rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                        \\&\quad
                        - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k \Vert^2 
                        + \frac{q_kL_k}{2}\Vert \Pi(z_k - y_k)\Vert^2
                        + \frac{q_kL_k\alpha_k(1 - \alpha_k)}{2}\Vert \Pi(\bar x - x_{k - 1})\Vert^2. 
                \end{align*}
            }
            At (1) we used Jesen's inequality Theorem \ref{thm:jen-ineq}. 
            At (2) we simplified the parameters because $q_kB_k = \mu \sigma(A)^2$. 
            At (3) we used the results from Lemma \ref{lemma:cnvg-prep-part2}. 
            At (4) we used the equality $z_k - x_k = \bar x - v_k$ from Lemma \ref{lemma:cnvg-prep-part1}. 
            Define for all $k \ge 1$: 
            \begin{align*}
                \mathcal R_k := \frac{q_kL_k}{2}\Vert \Pi(z_k - y_k)\Vert^2 
                + \frac{q_kL_k\alpha_k(1 - \alpha_k)}{2}\Vert \Pi(\bar x - x_{k - 1})\Vert^2. 
            \end{align*}
            After some algebra the above inequality has: 
            \begin{align*}
                & 
                F(x_k) - F(\bar x) 
                + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \\
                &\le 
                (\alpha_k - 1)F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) 
                + \frac{L_k\alpha_{k - 1}^2\rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                + \mathcal R_k
                \\
                &= (1 - \alpha_k)\left(
                    F(x_{k - 1}) - F(\bar x) 
                    + \frac{L_k\alpha_{k - 1}^2\rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \right) + \mathcal R_k
                \\ 
                &= (1 - \alpha_k)\left(
                    F(x_{k - 1}) - F(\bar x) 
                    + \left(
                        \frac{\rho_{k - 1}L_k}{L_{k - 1}}
                    \right)\frac{L_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \right) + \mathcal R_k
                \\
                &\le 
                (1 - \alpha_k)\max\left(
                    1, \frac{\rho_{k - 1}L_k}{L_{k - 1}}
                \right)\left(
                    F(x_{k - 1}) - F(\bar x) 
                    + \frac{L_{k - 1}\alpha_{k - 1}^2}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \right) + \mathcal R_k. 
            \end{align*}
        \end{proof}
        \par
        \textcolor{red}{Take note that if we were to get global linear convergence, we have to set $\mathcal R_k = 0$ for all $k \ge 1$.}
        This would require restrictive assumptions. 
        Before we delve into the restrictive assumptions, some more words are needed. 
        \begin{assumption}[conditions sufficient for linear convergence]\;\label{ass:cond-lin-cnvg}\\
            Let $(F, f, g, h, A, b, \mu, L)$ satisfies Assumption \ref{ass:obj-fxn}. 
            Let $(\alpha_k)_{k\ge 0}$ satisfies Definition \ref{def:r-nes-seq}. 
            Define $X^+ = \argmin_{z \in X} h(Ax - b)$ to be the set of minimizers. 
            Suppose that the iterates $(y_k, x_k, v_k)_{k \ge 1}$ satisfies Definition \ref{def:st-form}, with $q_k = \sigma(A)^2\mu/B_k$. 
            Define for all $k \ge 1$,  $\bar x \in \RR^n$, define $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$. 
            Assume in addition, any of the following for some $k \ge 1$:  
            \begin{enumerate}
                \item The matrix $A \in\RR^{n\times m}$ has $\ker A = \{\mathbf 0\}$
                \item It has $x_{k - 1} - x_{k - 2} \in \ker A$ and, at the same time, $\bar x - x_{k - 1} \in \ker A$, and at the same time, $\bar x = \Pi_{X^+} x_{k - 1} = \Pi_{X^+} x_k$. 
            \end{enumerate}            
        \end{assumption}
        \textcolor{red}{At this point I had lost the interest to continue writing it. }

\bibliographystyle{siam}

\bibliography{references/refs.bib}

\end{document}

### 2025-11-06 Notebook LaTEX/R-WAPG/2025-06-10-00-paper.tex
>w<, changes
>w<, a lot of changes

@@
             &
-            F(x_{k + 1}) - F^* + R_{k + 1} + \frac{\hat\gamma_{k + 1}}{2}\Vert v_{k + 1} - x^*\Vert^2
-            \\
-            &=
-            F(x_{k + 1}) - F^* + R_{k + 1} + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
+            F(x_{k + 1}) - F(x^*) + R_{k + 1} + \frac{\hat\gamma_{k + 1}}{2}\Vert v_{k + 1} - x^*\Vert^2
+            \\
+            &=
+            F(x_{k + 1}) - F(x^*) + R_{k + 1} + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
             \\
@@
             \left(
-                F(x_k) - F^* + R_k + \frac{\rho_{k - 1}L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2
+                F(x_k) - F(x^*) + R_k + \frac{\rho_{k - 1}L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2
             \right)
@@
             \left(
-                F(x_k) - F^* + R_k + \max(1, \rho_{k - 1})\frac{L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2
+                F(x_k) - F(x^*) + R_k + \max(1, \rho_{k - 1})\frac{L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2
             \right)
@@
             \left(
-                F(x_k) - F^* + R_k + \frac{L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2
+                F(x_k) - F(x^*) + R_k + \frac{L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2
             \right)
@@
             \left(
-                F(x_1) - F^* + R_1 + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
+                F(x_1) - F(x^*) + R_1 + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
             \right).
@@
             \item It has $\rho_{k - 1} = \alpha_k/((1 - \alpha_k)\alpha_{k - 1}^2)$, hence $(1 - \alpha_k)\rho_{k - 1} = \alpha_k^2/\alpha_{k - 1}^2$. 
+            \item Since $\mu = 0$, by Proposition \ref{prop:wapg-first-equivalent-repr}, the extrapolated iterate has $y_k = x_{k + 1} + \alpha_{k + 1}(\alpha_k^{-1} - 1)$
         \end{enumerate}
@@
         \end{align*}
-        Finally, since $\mu = 0$, Proposition \ref{prop:r-wapg-momentum-repr} applies with the momentum term simplifies into $\alpha_{k + 1}(\alpha_k^{-1} - 1)$. 
+        It remains to verify whether the sequence $\alpha_k$ is still valid, by which it means that $\alpha_k \in (0, 1)$ for all $k \ge 1$. 
+        We will soon reveal that it will be true in the part that comes. 
     }
@@
             \STATE{$\alpha_{k + 1} := (1/2)\left(\mu_k/L_k - \alpha_{k}^2 + \sqrt{(\mu_k/L_k - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;}
-            \STATE{$\theta_{k + 1} := \alpha_k(1 - \alpha_k)/(\alpha_k^2 + \alpha_{k + 1})$;}
+            \STATE{$\theta_{k + 1} := \alpha_{k + 1}(\alpha_k^{-1} - 1)$;}
             \STATE{$y_{k + 1}:= x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$; }
@@
     \subsection{Numerical experiments}
-        This section showcases results for the numerical experiments conducted using FR-WAPG algorithm (Algorithm \ref{alg:free-rwapg}), and compare with other APG algorithms in the literatures: the V-FISTA, and M-FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}.
+        In this section, we will show the numerical experiments results of algorithm (Algorithm \ref{alg:free-rwapg}) in this section then, we compare with other APG algorithms in the literatures: the V-FISTA, and FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}.
         We implemented in Julia \cite{bezanson_julia_2017}.
-        The equivalences highlighted in Proposition \ref{prop:r-wapg-momentum-repr} allows us to compare the sequence of iterates $(x_k)_{k \ge 1}, (y_k)_{k \ge0}$ for R-WAPG, V-FISTA and M-FISTA.
-        \par
-        We measure the aggregate statistics of the base two logarithms of the normalized optimality gap (NOG), at each iteration $k$ with the same initialization conditions given for all algorithms.
-        Given $x_k$, and minimum $F^*$, we define the normalized optimality gap:
-        \newcommand{\NOG}{\text{\textbf{NOG}}}
+        % The equivalences highlighted in Proposition \ref{prop:r-wapg-momentum-repr} allows us to compare the sequence of iterates $(x_k)_{k \ge 1}, (y_k)_{k \ge0}$ for R-WAPG, V-FISTA and M-FISTA.
+        \par
+        We will now introduce the global setup of our numerical experiments. 
+        To compare the convergence of different algorithms, we measure the logarithm of the relative optimaity gap $\delta_k$ which we defined: 
+        % \newcommand{\NOG}{\text{\textbf{NOG}}}
         \begin{align*}
             \delta_k := \log_2\left(
-                \NOG_k
-            \right)
-            \text{ with }
-            \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}.
-        \end{align*}
-        Since it's not the case that $F^*$ is always known in prior, we will use the minimum of all $F(x_k)$ across all algorithms, all iterations $k$ as the surrogate for $F^*$ when the true value is unavailable.
-        \par
-        We consider the norm of the gradient mapping $\Vert \mathcal G_L(y_k)\Vert < \epsilon$ as a termination conditions for all test algorithms.
-        The $L$ can change during each iteration if it's obtained through the specified Lipschitz line search routine.
-        \subsubsection{Simple convex quadratic}
-            Consider $\min_{x \in \RR^n} \{F(x):= f(x) + 0\}$ where
-            \begin{align*}
-                f(x) = (1/2)\langle x, A x\rangle.
-            \end{align*}
-            $A$ is set to be a positive semi-definite diagonal matrix, so the problem admits the minimizer $x^* = \mathbf 0$ (which is not unique) with minimum being zero.
-            We apply Algorithm \ref{alg:free-rwapg}, M-FISTA, and V-FISTA.
+                \frac{F(x_k) - F^*}{F(x_0) - F^*}
+            \right). 
+        \end{align*}
+        We give the same inigial guess $x_0$ for all algorithms.
+        Since $F^*$ is not always known in prior, we used the minimum of all $F(x_k)(1 - 2^{53})$ across all algorithms to estimate the minimum $F^*$ when it's not avaiable. 
+        \par
+        Fix some $\epsilon > 0$. 
+        The termination condition is $\Vert \mathcal G_L(y_k)\Vert < \epsilon$ for all algorithms.
+        We implemented line search for Lipschitz smoothness constant $L$ only for FISTA. 
+        For FR-WAPG and V-FISTA, an over estimate of the Lipschitz modules is given. 
+        \subsubsection{Experiments with a simple convex quadratic function}
+            Consider $\min_{x \in \RR^n} \{F(x):= f(x) + 0\}$ given by $f(x) = (1/2)\langle x, A x\rangle$. 
+            Here, $A$ is set to be a positive semi-definite diagonal matrix, hence problem is a convex quadratic and one of its minimizer is $x^* = \mathbf 0$,  with minimum being zero.
+            We repeat the same experiment for Algorithm \ref{alg:free-rwapg}, M-FISTA, and V-FISTA for 30 times with different initial guesses. 
             The following parameters are used to set up the numerical experiments:
@@
 \section*{Acknowledgements}
-The research of HL and XW was partially supported by
-the NSERC Discovery Grant of Canada.
+The research of HL and XW was partially supported by the NSERC Discovery Grant of Canada.
 

### 2025-11-06 Notebook LaTEX/R-WAPG/presentation-short.tex
>w<, a lot of changes

@@
 \setbeamertemplate{bibliography item}{\insertbiblabel}
-\setbeamerfont{bibliography item}{size=\footnotesize}
-\setbeamerfont{bibliography entry author}{size=\footnotesize}
-\setbeamerfont{bibliography entry title}{size=\footnotesize}
-\setbeamerfont{bibliography entry location}{size=\footnotesize}
-\setbeamerfont{bibliography entry note}{size=\footnotesize}
+\setbeamerfont{bibliography item}{size=\tiny}
+\setbeamerfont{bibliography entry author}{size=\tiny}
+\setbeamerfont{bibliography entry title}{size=\tiny}
+\setbeamerfont{bibliography entry location}{size=\tiny}
+\setbeamerfont{bibliography entry note}{size=\tiny}
 % \setbeamercovered{transparent}  % GREY OUT PAUSED FUTURE ITEMS IN SLID. 
@@
             \begin{block}{Beck, Teboulle 2009 {\cite[Theorem 4.4]{beck_fast_2009-1}}}
-                Commonly known by the name FISTA, it allows $(t_k)_{k}$: 
+                Commonly known by the name FISTA, it allows $(t_k)_{k \ge 0}$: 
                 \begin{align*}
@@
             The cases when the inequality of Nesterov's rule is not satisfied had been investigated as well.
-            \begin{block}{Apidopoulos et al. 2018 \cite{apidopoulos_convergence_2018}}
+            \begin{block}{Apidopoulos et al. 2018 \cite{apidopoulos_convergence_2020}}
                 If $\theta_k = \frac{k}{k + b}\;\forall k \ge 0$ where $b \in (0, 3)$ then, the optimality gap has a convergence rate of $\mathcal O(1/k^{2b/3})$. 
@@
             \begin{tcolorbox}
-                How much can we relax the choice of the sequence $\theta_k$ and retain an upper bound for the convergence rate? 
+                How much can we relax the choice of the sequence $(t_k)_{k \ge 0}, (\theta_k)_{k \ge 0}$ and retain an upper bound for the convergence rate? 
             \end{tcolorbox}
@@
             \begin{tcolorbox}
-                We made an algorithm which we called ``Free R-WAPG", it estimates the strong convexity constant $\mu$ using the Bregman Divergence at two successive iterates when the algorithm is running.
-                This information is used to determine the sequence $(\alpha_k)_{k \ge 0}$, and used to visualized our theoretical upper bound. 
+                We made an algorithm which we called ``Free R-WAPG", it estimates the strong convexity constant $\mu$ using the "Bregman Divergence" at two successive iterates when the algorithm is running.
+                This information is then used to determine the sequence $(\alpha_k)_{k \ge 0}$ while the algorithm is running. 
             \end{tcolorbox}
+            This will come at the last section. 
+            The quoted "Bregman Divergence" will be explained in a future slide. 
         \end{frame}
@@
         \begin{frame}{Proximal gradient, gradient mapping}
-            Starting in this section, we will highlight key theoretical results that will allow the unifying convergence rate for Euclidean variants of FISTA in the literature.
+            Starting in this section, we will highlight key theoretical results that unify the convergence rate for Euclidean variants of FISTA in the literature.
             \par
@@
             $L > 0$ is the Lipschitz smoothness parameter for $f$. 
+        \end{frame}
+        \begin{frame}{The Bregman Divergence}
+            We will now explain the "Bregman Divergence" that will be used in our numerical experiment in a later section. 
+            \begin{definition}[Bregman Divergence]
+                Let $f: \RR^n \rightarrow \RR$ be a differentiable function. 
+                We define the Bregman divergence to be: 
+                \begin{align}
+                    D_f(x, y): \RR^n \times \RR^n \rightarrow \RR
+                    \defeq (x, y)\mapsto f(x) - f(y) - \langle \nabla f(y), x - y\rangle.
+                \end{align}
+            \end{definition}
+            \begin{remark}
+                Here, $f$ is not necessarily Legendre \cite[Definition 1]{bauschke_descent_2017}, as in the Legendre Transformation of convex analysis. 
+            \end{remark}
         \end{frame}
@@
                 \delta_k := \log_2\left(
-                    \frac{F(x) - F^+}{F(x_0) - F^+}\right).  
+                    \frac{F(x_k) - F^+}{F(x_0) - F^+}\right).  
             \end{align*}
@@
                 \end{align*}
-                \item $L = 1, \mu = 10^{-5}$ are known in prior. 
+                \item $L = 1, \mu = 10^{-5}$ are known in prior. Feed $L, \mu$ to V-FISTA and, $L$ to Free R-WAPG. 
                 \item All algorithm terminates after $\Vert \mathcal G_L(y_k) \Vert \le 10^{-10}$. 
@@
         \begin{frame}{Experiment results 1}
-            A realization of $x_0 \sim \mathcal N(I, \mathbf 0)$ is used for V-FISTA, M-FISTA (Monotone restarted FISTA) and Free R-WAPG. 
+            A realization of $x_0 \sim \mathcal N(I, \mathbf 0)$ is used for V-FISTA, FISTA and Free R-WAPG. 
             Below are plots of the medium, minimum, and maximum of $\delta_k$: 
@@
                 \caption{
-                    Statistics for experiments with simple convex quadratic for V-FISTA, M-FISTA, and R-WAPG.
+                    Statistics for experiments with simple convex quadratic for V-FISTA, FISTA, and R-WAPG.
                 }
@@
                 \item Computed in prior, $L, \mu$ are parameters estimated by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$. The norm is the spectral norm. 
-                \item Let $F_{\min}$ be the smallest value of $F(x_k)$, for all algorithms, over all trials, we estimate $F^+$ by $F^+ = F_{\min}*(1 - 2^{53})$. 
+                \item Let $F_{\min}$ be the smallest value of $F(x_k)$, for all algorithms, over all trials, we estimate $F^+$ by $F^+ = (1 - 2^{53})F_{\min}$. 
             \end{enumerate}
         \end{frame}
-        \begin{frame}{LASSO Results plotted}
-            With $A\in \RR^{N\times N}$ fixed, for each $x_0 \sim \mathcal N(I, \mathbf 0)$ realized, 20 experiments are preformed and the medium, minimum and maximum of $\delta_k$ are recorded for M-FISTA, Free R-WAPG, and V-FISTA.
+        \begin{frame}{Convergence}
+            With $A\in \RR^{N\times N}$ fixed, for each $x_0 \sim \mathcal N(\mathbf 0, I)$ realized, 20 experiments are preformed and the medium, minimum and maximum of $\delta_k$ are recorded for FISTA, Free R-WAPG, and V-FISTA.
             \begin{figure}[H]
@@
     \end{frame}
-    \begin{frame}{References}        
+    \begin{frame}[allowframebreaks]{References}        
+        \tiny
         \bibliography{references/R-WAPG.bib}
+
     \end{frame}

### 2025-11-11 Notebook LaTEX/EB is the key to IAGP/main.tex
>w<, changes

@@
     For a multivalued mapping $T: \RR^n \rightarrow 2^{\RR^n}$, $\gra T$ denotes the graph of the operator, defined as $\{(x, y)\in \RR^n \times \RR^n : y \in Tx\}$. 
+    $\Pi_S$ denotes the projection onto a set $S \subseteq \RR^n$. 
     \subsection{Preliminaries}
@@
         \end{remark}
-        % \begin{fact}[strong epsilon subgradient sum rule]\label{fact:esp-subgrad-sum-rule}
-        %     Take both $f, g: \RR^n\rightarrow \overline \RR$. 
-        %     Let $\epsilon \ge 0$. 
-        %     Then the epsilon subgradient sum rule states that 
-        %     \begin{align*}
-        %         \partial_\epsilon[f + g](\bar x) = 
-        %         \bigcup \left\lbrace
-        %             \partial_{\epsilon_1} f(\bar x) + 
-        %             \partial_{\epsilon_2} g(\bar x) \left|\; 
-        %                 \min(\epsilon_1, \epsilon_2) \ge 0\wedge 
-        %                 \epsilon_1 + \epsilon_2 = \epsilon
-        %             \right.
-        %         \right\rbrace
-        %     \end{align*}
-        %     Under the scenario that: $\reli\dom f \cap \reli\dom g \neq \emptyset$. 
-        % \end{fact}
-        % \begin{remark}
-        %     The above is taken from Morduchovich, Mau Nam \cite[Theorem 5.19]{mordukhovich_convex_2022}. 
-        % \end{remark}
         We will now define inexact proximal point based on $\epsilon$-subgradient
@@
         \end{proof}
-        \begin{fact}[Fenchel Rockafellar duality]
-
-        \end{fact}
     \subsection{Inexact proximal gradient inequality}
@@
         \end{remark}
-    \subsection{Optimizing the inexact proximal point problem}\label{sec:optz-inxt-pp-problem}
+    \subsection{Optimizing an inexact proximal point problem}\label{sec:optz-inxt-pp-problem}
         In this section we will present the optimization problem that obtains a $\tilde x$ such that $\tilde x \approx_\epsilon \hprox_{\lambda g}(z)$. 
@@
         \begin{assumption}[linear composite of convex nonsmooth function]\;\label{ass:for-inxt-prox}\\
-            This assumption is about $(g, \omega, A)$. 
+            This assumption is about $(g, \omega, A, K_\omega, K_{\omega^\star})$. 
             Let $m \in \N, n \in \RR^n$, we assume that 
@@
                 \item $g := \omega(Ax)$ such that $\rng A \cap \reli\dom g \neq\emptyset$. 
+                \item $\omega$ is $K_\omega$ Lipschitz continuous, and $\omega^\star$ is $K_{\omega^\star}$ Lipschitz continuous and in addition, $\dom \omega^\star$ is a compact set. 
             \end{enumerate}
@@
         Recall the following famous theoretical result in the convex programming literature that we had adapted into our context. 
-        \begin{fact}[French Rockafellar Duality {\cite[Proposition 15.22]{bauschke_convex_2017}}]\;\label{fact:fn-rck-duality}\\
+        \begin{fact}[Fenchel Rockafellar Duality {\cite[Proposition 15.22]{bauschke_convex_2017}}]\;\label{fact:fn-rck-duality}\\
             Let $f:\RR^n \rightarrow \overline \RR$ be closed convex and proper, $g: \RR^m \rightarrow \overline \RR$, $A \in \RR^{m \times n}$. 
@@
         \par
-        The following fact from the literature indicates that it's sufficient to minimize the dual problem $\Psi_\lambda$ to obtain an element of the inexact proximal point operator. 
-        The following fact is Proposition is from Villa et al. \cite[Theorem 5.1]{villa_accelerated_2013}. 
-        \begin{fact}[minimizing dual of the proximal problem {\cite[Theorem 5.1]{villa_accelerated_2013}}]\label{fact:minimizing-dual-pp}
-            Let $\bar v$ be a solution of $\Psi_\lambda$. 
-            Suppose that $(v_n)_{n \ge 0}$ is a minimizing sequence for $\Psi_\lambda$. 
-            Let $z_n = y - \lambda A^\top v_n$, and $\bar z = y - \lambda A^\top \bar v$. 
-            Then the following are true: 
-            \begin{enumerate}[nosep]
-                \item The sequence $z_n \rightarrow \bar z$ as well. 
-                \item There exists a constant $K$ that depends on the sequence $z_n$, and $\Phi_\lambda$ such that for all $k \ge 0$ the inequality: 
-                \begin{align*}
-                    \Phi_{\lambda}(z_n) - \Phi_\lambda(\bar z) 
-                    &\le K \Vert z_n - \bar z\Vert 
-                    \le K \sqrt{2\lambda}(\Psi_\lambda(v_n) - \Psi_\lambda(\bar v))^{1/2}. 
-                \end{align*}
-            \end{enumerate}
-
-        \end{fact}
-        We remark that the above fact translates any algorithm that optimizes the dual problem $\Psi_\lambda$ into optimizing the duality gap $\mathbf G(z_n, v_n)$ because it shows the primal is bounded by the dual through a Lipschitz-like inequality.
-        \par
-        With the proof back in Villa et al.
-\cite[Theorem 5.1]{villa_accelerated_2013}, pay close attention to the constant $L_\Phi$ exists by the virtue of $\Psi$ being convex, and the sequence $v_n \rightarrow \bar v$ which allows the sequence $z_n \rightarrow \bar z_n$ to be bounded inside the domain of $\Phi_\lambda$.
-        By convexity, $\Phi_\lambda$ is locally Lipschitz on $\reli \dom \Phi_\lambda$, by convergence of $z_n$ the sequence is in a compact set in $\reli\dom \Phi_\lambda$ hence a Lipschitz bound with constant $K$ exists.
-        \par
-        For this reason, the number of iterations of the inner loop required to achieve $\mathbf G(z_n, v_n) < \epsilon$ for a given $\epsilon$ is related to the convergence rate of the algorithms used to optimize $\Psi_\lambda(v_n)$.
-        With the theorem derived above, and using Theorem \ref{thm:dlty-gap-inxt-pp} it implies that any algorithm which can optimize function value $\Psi_\lambda$ will produce iterates sufficient to achieve $\approx_\epsilon \hprox_{\lambda g}(y)$.
+        The following theorem is enhenced from Villa et al. \cite[Theorem 5.1]{villa_accelerated_2013}. 
+        % \begin{fact}[minimizing dual of the proximal problem {\cite[Theorem 5.1]{villa_accelerated_2013}}]\;\label{fact:minimizing-dual-pp}\\
+        %     Let $\bar v$ be a solution of $\Psi_\lambda$. 
+        %     Suppose that $(v_j)_{j \ge 0}$ is a minimizing sequence for $\Psi_\lambda$. 
+        %     Let $z_j = y - \lambda A^\top v_j$, and $\bar z = y - \lambda A^\top \bar v$. 
+        %     Then the following are true: 
+        %     \begin{enumerate}[nosep]
+        %         \item The sequence $z_j \rightarrow \bar z$ as well. 
+        %         \item There exists a constant $K$ that depends on the sequence $z_j$, and $\Phi_\lambda$ such that for all $j \ge 0$ it has the inequality: 
+        %         \begin{align*}
+        %             \Phi_{\lambda}(z_j) - \Phi_\lambda(\bar z) 
+        %             &\le K \Vert z_j - \bar z\Vert 
+        %             \le K \sqrt{2\lambda}(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))^{1/2}. 
+        %         \end{align*}
+        %     \end{enumerate}
+        % \end{fact}
+        % We remark that the above fact translates any algorithm that optimizes the dual problem $\Psi_\lambda$ into optimizing the duality gap $\mathbf G(z_j, v_j)$ by this inequality. 
+        % \par
+        % With the proof back in Villa et al.
+\cite[Theorem 5.1]{villa_accelerated_2013}, pay close attention to the constant $L_\Phi$ exists by the virtue of $\Psi$ being convex, and the sequence $v_j \rightarrow \bar v$ which allows the sequence $z_j \rightarrow \bar z_j$ to be bounded inside the domain of $\Phi_\lambda$.
+        % By convexity, $\Phi_\lambda$ is locally Lipschitz on $\reli \dom \Phi_\lambda$, by convergence of $z_j$ the sequence is in a compact set in $\reli\dom \Phi_\lambda$ hence a Lipschitz bound with constant $K$ exists.
+        % \par
+        % For this reason, the number of iterations of the inner loop required to achieve $\mathbf G(z_j, v_j) < \epsilon$ for a given $\epsilon$ is related to the convergence rate of the algorithms used to optimize $\Psi_\lambda(v_j)$.
+        % With the theorem derived above, and using Theorem \ref{thm:dlty-gap-inxt-pp} it implies that any algorithm which can optimize function value $\Psi_\lambda$ will produce iterates sufficient to achieve $\approx_\epsilon \hprox_{\lambda g}(y)$.
+        \todoinline{
+            Un nouvel candidat ce que remplace le denière théorem suivant. 
+        }
+
+        \begin{theorem}[minimizing the dual of the proximal problem]\;\label{thm:minimizing-dual-pp}\\
+            Assume that we have $(g, \omega, A)$ given by Assumption \ref{ass:for-inxt-prox}. 
+            Let the $\Phi_\lambda$ be given by \eqref{eqn:primal-pp}, and dual $\Psi_\lambda$ by \eqref{eqn:dual-pp}. 
+            Let $\bar v$ be a minimizer of $\Psi_\lambda$ and suppose that sequence $(v_j)_{j\ge 0}$ minimizes dual $\Psi_\lambda$. 
+            Then, the followings are true: 
+            \begin{enumerate}[nosep]
+                \item\label{thm:minimizing-dual-pp:item1} If $\bar v$ is an minimizer of dual $\Psi_\lambda$, then $\bar z = y - \lambda A^\top \bar v$ is a minimizer of primal $\Phi_\lambda$. 
+                \item\label{thm:minimizing-dual-pp:item2} Let $z_j = y - \lambda A^\top v_j$, it has $\Psi_\lambda(v_j) - \Psi_\lambda(\bar v) \ge \frac{1}{2 \lambda} \Vert z_j - \bar z\Vert^2$, and therefore it has $z_j \rightarrow \bar z$.
+                \item\label{thm:minimizing-dual-pp:item3} And, by our assumption, the primal optimality gap is bounded by dual for all $v \in \RR^m$ by the inequality: 
+                \begin{align*}
+                    & \Phi_\lambda(z_j) - \Phi_\lambda(\bar z) 
+                    \\
+                    &\le 
+                    \sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}\left(
+                        K_\omega \Vert A\Vert 
+                        + \lambda^{-1}\Vert z_j - y\Vert 
+                        + \frac{1}{2\lambda}\sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}
+                    \right).
+                \end{align*}
+            \end{enumerate}
+        \end{theorem}
+        \begin{proof}
+            There are two intermediate results to prior to proving the items in the theorem. 
+            In preparations, for all $v \in \RR^m$, it's obvious that we have: 
+            \begin{align}\label{eqn:thm:minimizing-dual-pp:pitem1}
+                \begin{split}
+                    & \frac{1}{2\lambda}\left\Vert \lambda A^\top v - y\right\Vert^2
+                    - \frac{1}{2\lambda}\left\Vert \lambda A^\top \bar v - y\right\Vert^2 
+                    + \langle A \bar z, v - \bar v\rangle 
+                    \\
+                    &= 
+                    \frac{1}{2\lambda}
+                    \left\Vert 
+                        \lambda A^\top v - \lambda A^\top \bar v  + \lambda A^\top \bar v - y
+                    \right\Vert^2
+                    - \frac{1}{2\lambda}\left\Vert \lambda A^\top \bar v - y\right\Vert^2 
+                    + \langle A \bar z, v - \bar v\rangle 
+                    \\
+                    &= 
+                    \frac{1}{2\lambda} \left\Vert \lambda A^\top(v - \bar v)\right\Vert^2
+                    + \frac{1}{\lambda}\left\langle \lambda A^\top(v - \bar v), \lambda A^\top \bar v - y \right\rangle
+                    + \left\langle \bar z, A^\top(v - \bar v)\right\rangle 
+                    \\
+                    &\underset{\text{(1)}}{=} 
+                    \frac{1}{2\lambda} \left\Vert \lambda A^\top(v - \bar v)\right\Vert^2
+                    - \frac{1}{\lambda}\left\langle \lambda A^\top(v - \bar v), \bar z \right\rangle
+                    + \left\langle \bar z, A^\top(v - \bar v)\right\rangle 
+                    \\
+                    &= \frac{1}{2\lambda} \left\Vert \lambda A^\top(v - \bar v)\right\Vert^2. 
+                \end{split}
+            \end{align}
+            At (1), we assumed for the theorem statement that $\bar z = y - \lambda A^\top \bar v$. 
+            By the optimality of $\bar v$ on the dual problem, we have the following: 
+            \begin{align}\label{eqn:thm:minimizing-dual-pp:pitem2}
+                \begin{split}
+                    & \mathbf 0 \in 
+                    A \left(\lambda A^\top \bar v - y\right) + \partial \omega^\star(\bar v)
+                    \\
+                    \iff &
+                    A\bar z \in \partial \omega^\star(\bar v)
+                    \\
+                    \iff &
+                    \omega^\star(v) - \omega^\star(\bar v) 
+                    \ge \langle A \bar z, v_n - \bar v\rangle. 
+                \end{split}
+            \end{align}
+            \par
+            We will now prove \ref{thm:minimizing-dual-pp:item1}, because $A \bar z \in \partial \omega^\star (\bar v) \iff \partial \omega(A \bar z) \ni \bar v$, we can derive that $\bar z = y - \lambda A^\top \bar v$ is primal optimal because
+            \begin{align*}
+                y - \bar z &= \lambda A^\top \bar v \in \lambda A^\top\partial \omega (A \bar z). 
+            \end{align*}
+            Re-arranging yields: $\mathbf 0 \in \bar z - y + \lambda A^\top \partial \omega (A \bar z) = \partial \Phi_\lambda(\bar z)$. 
+            \par
+            Now we will prove \ref{thm:minimizing-dual-pp:item2}. 
+            Recall that $z_j = y - \lambda A^\top v_j$, therefore it has: 
+            \begin{align*}
+                \Phi_\lambda(v_j) - \Phi_\lambda(\bar v)
+                &= \frac{1}{2\lambda}\left\Vert
+                    \lambda A^\top v_j - y
+                \right\Vert^2 
+                - \frac{1}{2\lambda}\left\Vert
+                    \lambda A^\top \bar v - y
+                \right\Vert^2
+                + \omega^\star(v_j) - \omega^\star(\bar v)
+                \\
+                &\underset{(2)}{\ge}
+                \frac{1}{2\lambda}\left\Vert
+                    \lambda A^\top v_j - y
+                \right\Vert^2 
+                - \frac{1}{2\lambda}\left\Vert
+                    \lambda A^\top \bar v - y
+                \right\Vert^2
+                + \langle A\bar z, v_j - \bar v\rangle
+                \\
+                &\underset{(3)}{=} \frac{1}{2\lambda}\Vert \lambda A^\top(v_j - \bar v)\Vert^2
+                \\
+                &\underset{(4)}{=} \frac{1}{2\lambda}\Vert z_j - \bar z\Vert^2. 
+            \end{align*}
+            At (2) we used \eqref{eqn:thm:minimizing-dual-pp:pitem2}, at (3) we used \eqref{eqn:thm:minimizing-dual-pp:pitem1}. 
+            At (4), we again $\bar z = y - \lambda A^\top \bar v$. 
+            We have $\bar z$ being the optimal solution of primal $\Phi_\lambda$. 
+            Now, if we set $v = v_j$, and then: 
+            \begin{align*}
+                0 = \lim_{j \rightarrow \infty} \Psi_\lambda(v_j) - \Psi_{\lambda} (\bar v) \ge \lim_{j \rightarrow \infty}\Vert z_j - \bar z \Vert^2. 
+            \end{align*}
+            Implying that $z_j \rightarrow \bar z$ also. 
+            \par
+            We will now prove \ref{thm:minimizing-dual-pp:item3}. 
+            We have for all $z \in \RR^n$, the following: 
+            \begin{align*}
+                & \Phi_\lambda(z_j) - \Phi_\lambda(\bar z) 
+                \\
+                &= \omega(Az_j) - \omega(A \bar z)
+                + \frac{1}{2\lambda}(\Vert z_j - y \Vert^2 - \Vert \bar z - y\Vert^2)
+                \\
+                &\le 
+                K_\omega\Vert A\Vert \Vert z_j - \bar z\Vert 
+                + \frac{1}{2\lambda}\left(
+                    \Vert z_j - y\Vert + \Vert \bar z_j - y\Vert
+                \right)\left(
+                    \Vert z_j - y\Vert - \Vert \bar z - y\Vert
+                \right)
+                \\
+                &\le
+                K_\omega\Vert A\Vert \Vert z_j - \bar z\Vert 
+                + \frac{1}{2\lambda}\left(
+                    \Vert z_j - y\Vert + \Vert \bar z - y\Vert
+                \right)\Vert z_j - \bar z\Vert
+                \\
+                &\le 
+                K_\omega\Vert A\Vert \Vert z_j - \bar z\Vert 
+                + \frac{1}{2\lambda}\left(
+                    2\Vert z_j - y\Vert + \Vert \bar z - z_j\Vert 
+                \right)\Vert z_j - \bar z\Vert
+                \\
+                &= \Vert z_j - \bar z\Vert\left(
+                    K_\omega \Vert A\Vert 
+                    + \lambda^{-1}\Vert z_j - y\Vert 
+                    + \frac{1}{2\lambda}\Vert \bar z - z_j\Vert
+                \right)
+                \\
+                &\underset{\text{\ref{thm:minimizing-dual-pp:item2}}}{\le} 
+                \sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}\left(
+                    K_\omega \Vert A\Vert 
+                    + \lambda^{-1}\Vert z_j - y\Vert 
+                    + \frac{1}{2\lambda}\sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}
+                \right). 
+            \end{align*}
+
+        \end{proof}
+
     \subsection{Literature reviews}
@@
     \begin{proposition}[generic convergence rate of the gradient mapping]\;\label{prop:apg-cnvg-gm-generic}\\
-        \todoinline{Cette proposition ira démontrer que le séquence de ``Inexact Gradient Mapping" converge. }
+        \todoinline{
+            \par 
+            Cette proposition ira démontrer que ce séquence de ``Inexact Gradient Mapping" converge. \\
+            N'oubliez pas de finir. 
+        }
     \end{proposition}
@@
     The inner loop is another algorithm that evaluates $x_k \approx_\epsilon T_{(B_k + \rho_k)}(y_k)$ for a given value of $\epsilon, B + \rho$ and at the point $y_k$. 
-    To accomplish let's assume that the outer loop iteration $k$ is fixed throughout this entire section.
-    Now let $\lambda = (B_k + \rho_k)^{-1}$, the algorithm needs to resolve the following equivalent inexact proximal point problem: 
+    Let's assume that the outer loop iteration $k$ is fixed throughout this entire section to simplify our discussion since, in this section we will only focus on the convergence rate of the inner loop for one specific iteration of the outer loop.
+    \par
+    Let $\lambda = (B_k + \rho_k)^{-1}$, the algorithm needs to resolve the following equivalent inexact proximal point problem: 
     \begin{align*}
@@
     \par
-    In this section, we will show that there exists an algorithm generating the sequences $z_n, v_n$ such that $\mathbf G_\lambda (z_n, v_n)$ converges linearly if $\Psi_\lambda$ satisfies the error bound conditions.
+    We will show that there exists an algorithm generating the sequences $z_j, v_j$ such that $\mathbf G_\lambda (z_j, v_j)$ converges linearly if $\Psi_\lambda$ satisfies the error bound conditions. 
     Using results available in the literature, we will characterize the exact scenarios of $\omega \circ A$ when this is possible to achieve. 
@@
         Let $F = f + g$ where $f:\RR^n \rightarrow \RR$ is a differentiable function and, $g: \RR^n \rightarrow \overline \RR$ is closed convex and proper. 
-        We define the exact proximal gradient mapping and, gradient mapping: 
+        For all $\tau > 0$, we define the exact proximal gradient mapping and, gradient mapping: 
         \begin{enumerate}[nosep]
@@
     \end{definition}
-    \begin{definition}[error bound]\;\label{def:err-bnd}\\
-        Let $F = f + g$ where $f:\RR^n \rightarrow \RR$ is a differentiable function and, $g: \RR^n \rightarrow \overline \RR$ is closed convex and proper. 
-        Assume the set of minimizers $S = \argmin_{x} F \neq \emptyset$. 
-        Let $\gamma> 0$, and let proximal gradient mapping $T_\tau$, gradient mapping $\mathcal G_\tau$ of $F = f + g$ as given by Definition \ref{def:pg-and-gm}. 
-        Then their sum $F = f + g$ satisfies the error bound condition if there exists $\gamma > 0$ such that 
+    \begin{definition}[the error bound condition]\;\label{def:err-bnd}\\
+        Under the same assumptions in Definition \ref{def:pg-and-gm}, the function $F = f + g$ satisfies the error bound condition if there exists $\gamma > 0$ such that 
         \begin{align}\label{ineq:pg-eb}
@@
     \end{definition}
-    \begin{assumption}[gradient mapping error bound]\;\label{ass:pg-eb}\\
+    \begin{assumption}[problem with proximal gradient and error bound]\;\label{ass:pg-eb}\\
         The following assumption is about $(F, f, g, L, S, \gamma)$. 
@@
     \end{assumption}
-    \begin{definition}[proximal gradient method]\;\label{def:ista}\\
+    \begin{definition}[the proximal gradient method]\;\label{def:ista}\\
         Suppose that $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}. 
@@
             Assume that $(F, f, g, L, S, \gamma)$ is given by Assumption \ref{ass:pg-eb}. 
-            Under this assumption, the iterates $(x_k)_{k \ge 0}$ given by Definition \ref{def:ista} satisfies for all $k \ge 0, \bar x \in S$ and $\tau \ge L$ the inequality: 
+            Under this assumption, the iterates $(x_k)_{k \ge 0}$ given by Definition \ref{def:ista} satisfies for all $k \ge 0, \bar x \in S$ and $\tau \ge L$: 
             \begin{align*}
@@
                     1 - \frac{\gamma}{2\tau}
-                \right)(F(x_k) - F(\bar x)). 
+                \right)(F(x_k) - F(\bar x)), \text{where } \frac{\gamma}{2\tau} \in (0, 1)
             \end{align*}
@@
         \begin{assumption}[conditions for linear convergence of proximal problem]\;\label{ass:lin-cnvg-for-pp}\\
-            This assumption is about $(g, \omega, A, y, \Phi_\lambda, \Psi_\lambda, L^\lambda_{\Phi} ,\gamma_\lambda)$. 
+            This assumption is about $(g, \omega, A, y, \Phi_\lambda,\Psi_\lambda,\gamma_\lambda)$. 
             Here are the assumptions
             \begin{enumerate}[nosep]
-                \item $y \in \RR^n$ is the vector of which the proximal problem is anchored at, fixed it to be an arbitrary vector. 
-                \item Assume $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}.
+                \item\label{ass:lin-cnvg-for-pp:item1} $y \in \RR^n$ is the vector of which the proximal problem is anchored at, fixed it to be an arbitrary vector. 
+                \item\label{ass:lin-cnvg-for-pp:item2} Assume $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}.
 The primal objective $\Phi_\lambda$ is given by \eqref{eqn:primal-pp}, and dual $\Psi_\lambda$ by \eqref{eqn:dual-pp}.
 This means if we let $h(v) := \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2$, then $\Psi_\lambda(v) = h(v) + \omega^\star(v)$.
-                \item Next, assume $\Psi_\lambda = h + \omega^\star$ satisfies error bound condition (Assumption \ref{ass:pg-eb}) with $\Psi_\lambda = F$ and, $\gamma = \gamma_\lambda$ and $f = h$.
+                \item\label{ass:lin-cnvg-for-pp:item3} Next, assume $\Psi_\lambda = h + \omega^\star$ satisfies error bound condition (Assumption \ref{ass:pg-eb}) with $\Psi_\lambda = F$ and, $\gamma = \gamma_\lambda$ and $f = h$.
 Note that we can do this because $h$ is quadratic hence obviously Lipschitz continuous and Lipschitz smooth.
-                \item We assume in addition, the primal objective $\Phi_\lambda$ of proximal problem is $L_\Phi^\lambda$ Lipschitz continuous on its domain $\dom \Phi_\lambda = \dom (g\circ A)$. 
+                % \item\label{ass:lin-cnvg-for-pp:item4} Assume that there exists the constant $C_\Psi^\lambda < \infty$ such that 
+                % $$
+                %     C_\Psi^\lambda = \sup_{v\in \RR^m} \Psi_\lambda(v) - \inf_{v\in \RR^m}\Psi_\lambda(v). 
+                % $$
+                % \item\label{ass:lin-cnvg-for-pp:item5} Assume that $\omega$ is a $K_\omega$ Lipschitz continuous function on $\dom \omega$. 
             \end{enumerate}
         \end{assumption}
+        \par
         The following definition specifies the algorithm that can achieve linear convergence rate with the assumptions above. 
         \begin{definition}[the ISTA inner loop algorithm]\;\label{def:ista-inner-lp}\\
-            Let $\lambda > 0, \epsilon > 0$, and $(g, \omega, A, y, \Phi_\lambda, \Psi_\lambda, L^\lambda_{\Phi} ,\gamma_\lambda)$ satisfies Assumption \ref{ass:lin-cnvg-for-pp}. 
+            Let $\lambda > 0, \epsilon > 0$, and $(g, \omega, A, y, \Phi_\lambda,\Psi_\lambda,\gamma_\lambda)$ satisfies Assumption \ref{ass:lin-cnvg-for-pp}. 
             \begin{enumerate}[nosep]
@@
         \begin{proposition}[sufficient conditions of linear convergence of the inner loop]\;\label{prop:inn-loop-lin-cnvg}\\
-            Let the parameters $(g, \omega, A, y, \Phi_\lambda, \Psi_\lambda, L^\lambda_{\Phi} ,\gamma_\lambda)$ of a proximal problem satisfy Assumption \ref{ass:lin-cnvg-for-pp}. 
-            Let $\tau$, $v_0, \epsilon$ be given by an algorithm that satisfies Definition \ref{def:ista-inner-lp} and, it generates iterates $(z_j, v_j)_{j \ge 0}$. 
+            Let the parameters $(g, \omega, A, y, \Phi_\lambda, \Psi_\lambda, \gamma_\lambda)$ of a proximal problem satisfy Assumption \ref{ass:lin-cnvg-for-pp}. 
+            Let $\tau$, $v_0, \epsilon > 0$ be given by Definition \ref{def:ista-inner-lp} along with iterates $(z_j, v_j)_{j \ge 0}$. 
             Let $\bar v$ be a minimizer of $\Psi_\lambda$, then the followings are true: 
             \begin{enumerate}[nosep]
-                \item The sequence $\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item1}
-                \item If we let $\bar z := y - \lambda A^\top \bar v$, then $\Phi_\lambda(z_j) - \Phi_\lambda(\bar z)$ converges linearly to zero. \label{prop:inn-looplin-cnvg-item2}
-                \item The duality gap has convergence $\mathbf G_\lambda(z_j, v_j) \le \mathcal O\left(\left(1 - \frac{\gamma_\lambda}{2\tau}\right)^{j/2}\right)$. \label{prop:inn-looplin-cnvg-item3}
-                \item If $\mathbf G_\lambda(z_j, v_j) \le \epsilon$, then $z_j \approx_\epsilon \hprox_{\lambda g}(y)$. \label{prop:inn-looplin-cnvg-item4}
+                \item\label{prop:inn-loop-lin-cnvg:item1} Let $\bar v$ be minimizer of $\Psi_\lambda$, the sequence $\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)$ converges linearly to zero. 
+                \item\label{prop:inn-loop-lin-cnvg:item2} There exists constants $K_\Psi^\lambda$ such that $\Psi_\lambda$ is $K_\Psi^\lambda$ Lipschitz continuous on $\dom \Psi_\lambda$, as a consequence there exists constant $C_\Psi^\lambda$ such that, $\sup_{v \in \RR^m}\Phi_\lambda(v) - \Phi_\lambda(\bar v) \le K_\Psi^\lambda\sup_{v \in \dom\Psi_\lambda}\Vert v - \bar v \Vert = C_\Psi^\lambda < \infty$.
+                \item\label{prop:inn-loop-lin-cnvg:item3} The duality gap has a linear convergence rate vy the inequality: 
+                $$
+                    \mathbf G_\lambda(z_j, v_j) \le
+                    \left(
+                        1 - \frac{\gamma_\lambda}{2\tau}
+                    \right)^{j/2}\sqrt{2\lambda C_\Psi^\lambda}
+                    \left(
+                        K_\omega \Vert A\Vert 
+                        + \lambda^{-1}\Vert z_j - y\Vert 
+                        + \frac{\sqrt{2\lambda C_\Psi^\lambda}}{\lambda}
+                    \right). 
+                $$
+                \item\label{prop:inn-loop-lin-cnvg:item4} If $\mathbf G_\lambda(z_j, v_j) \le \epsilon$, then $z_j \approx_\epsilon \hprox_{\lambda g}(y)$.
+If we let $\tau = \lambda \Vert AA^\top\Vert$, then a sufficient number of iteration needed to achieve the optimality is given by:
+                \todoinline{
+                    N'obliez pas de finir! 
+                }
             \end{enumerate}
@@
         \begin{proof}
-            Note that $\Psi_\lambda$ satisfies error bound condition in Assumption \ref{ass:lin-cnvg-for-pp}, and Definition \ref{def:ista-inner-lp} has $\tau \ge \lambda\Vert A^TA\Vert$ which satisfies Definition \ref{def:ista} therefore the linear convergence results of Theorem \ref{thm:lin-cnvg-ista-eb} applies to $\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)$.
-            Therefore, we claim: 
+            To start, we prove \ref{prop:inn-loop-lin-cnvg:item1}. 
+            Recall that it has $\Psi_\lambda = h + \omega^\star$ with $h$ being Lipschitz smooth and, $\omega^\star$ closed convex proper from item \ref{ass:lin-cnvg-for-pp:item2} in Assumption \ref{ass:lin-cnvg-for-pp}.
+            In addition $\Psi_\lambda$ also satisfies error bound in item \ref{ass:lin-cnvg-for-pp:item3} of Assumption \ref{ass:lin-cnvg-for-pp} with $\gamma = \gamma_\lambda$. 
+            Finally, $(z_j, v_j)_{j \ge 0}$ given by Definition \ref{def:ista-inner-lp} has $\tau \ge \lambda\Vert A^\top A\Vert$ so it's essntially Definition \ref{def:ista} with $x_j = v_j$. 
+            Therefore results from Theorem \ref{thm:lin-cnvg-ista-eb} applies with $F = \Psi_\lambda, x_j= v_j$ and it has: 
             \begin{align}\label{ineq:inn-loop-lin-cnvg-pitem1}
@@
             \par
-            We will now proceed to proving \ref{prop:inn-looplin-cnvg-item2}. 
-            Recall that the iterates $z_j = y - \lambda A^\top v_j$, and $\bar z = y - \lambda A^\top \bar v$, and we have Lipschitz continuity of $\Phi_\lambda$, hence Theorem \ref{fact:minimizing-dual-pp} applies, in addition since $\Phi_\lambda$ were assumed to be globally Lipschitz on $\dom \Phi_\lambda$ in Assumption \ref{ass:lin-cnvg-for-pp}, this means that we can replace $K$ regardless of $\bar v$, and convergent primal sequence $z_j \rightarrow \bar z$ with $L_\Phi^\lambda$ which gives:
-            \begin{align}\label{ineq:inn-loop-lin-cnvg-pitem2}
-                \begin{split}
-                    \Phi_\lambda(z_j) - \Phi_\lambda(\bar z) &\le L_\Phi^\lambda \sqrt{2\lambda}\left(
-                    \Psi_\lambda(v_j) - \Psi_\lambda (\bar v)
-                    \right)^{1/2}
+            Next, we show \ref{prop:inn-loop-lin-cnvg:item2}. 
+            The smooth part of $\Phi$ is the quadratic $h(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2$, it's locally Lipschitz on the compact the domain of $\dom\Psi_\lambda = \dom \omega^\star$ is compact by Assumption \ref{ass:for-inxt-prox}, hence the smooth part is Lipschitz on $\dom \omega^\star$.
+            In addition, $\omega^\star$ is assumed to be Lipschitz on $\dom \omega^\star$, therefore the entire function $\Psi$ is Lipschitz on $\omega^\star$, we denote the Lipschitz constant by $K_\Psi^\lambda$.
+            Because $\omega^\star$ is bounded, therefore there exists constant $C_\Psi^\lambda$ such that.
+            \begin{align*}
+                \sup_{v \in \RR^m}\Phi_\lambda(v) - \Phi_\lambda(\bar v) \le K_\Psi^\lambda\sup_{v \in \dom\Psi_\lambda}\Vert v - \bar v \Vert = C_\Psi^\lambda < \infty. 
+            \end{align*}
+            \par
+            To see the duality gap, Theorem \ref*{thm:minimizing-dual-pp}\ref{thm:minimizing-dual-pp:item3} applies because $v_j$ by \eqref{ineq:inn-loop-lin-cnvg-pitem1} provides us the sequence $(v_j)_{j \ge 0}$ such $\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)$ converges.
+            {\small
+            \begin{align*}
+                & \mathbf G_\lambda(z_j, v_j) 
+                \\
+                &= \Phi_\lambda(z_j) - \Phi_\lambda(\bar z) + 0
+                \\
+                &= \Phi_\lambda(z_j) - \Phi_\lambda(\bar z) + \Psi_\lambda(v_j) - \Psi_\lambda(\bar v)
+                \\
+                &\le \sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}\left(
+                    K_\omega \Vert A\Vert 
+                    + \lambda^{-1}\Vert z_j - y\Vert 
+                    + \frac{1}{2\lambda}\sqrt{2\lambda\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}
+                \right) 
+                \\&\quad 
+                    + \Psi_\lambda(v_j) - \Psi_\lambda(\bar v)
+                \\
+                &=
+                \sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}\left(
+                    K_\omega \Vert A\Vert 
+                    + \lambda^{-1}\Vert z_j - y\Vert 
+                    + \frac{\sqrt{2\lambda}}{\lambda}\sqrt{\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}
+                \right) 
                 \\
                 &\underset{(1)}{\le} 
-                    L_\Phi^\lambda\sqrt{2\lambda} \left(
+                \left(
                     1 - \frac{\gamma_\lambda}{2\tau}
-                    \right)^{j/2}\left(
-                        \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
-                    \right)^{1/2}. 
-                \end{split}
-            \end{align}
-            At (1), we used \eqref{ineq:inn-loop-lin-cnvg-pitem1}.
-            \par
-            To prove \ref{prop:inn-looplin-cnvg-item3}, by definition of duality gap in \eqref{eqn:duality-gap-pp} we have:
-            \begin{align*}
-                & \mathbf G_\lambda(z_j, v_j) 
-                \\
-                &\underset{(1)}{=} \Phi_\lambda(z_j) + \Psi_\lambda(v_n) + 0
-                \\
-                &= \Phi_\lambda(z_j) + \Psi_\lambda(v_j) - \Phi_\lambda(\bar z) - \Psi_\lambda(\bar v)
-                \\
-                &= \Phi_\lambda(z_j)- \Phi_\lambda(\bar z) + \Psi_\lambda(v_n) - \Psi_\lambda(\bar v)
+                \right)^{j/2}\sqrt{2\lambda(\Psi_\lambda(v_0) - \Psi_\lambda(\bar v))}
+                \left(
+                    K_\omega \Vert A\Vert 
+                    + \lambda^{-1}\Vert z_j - y\Vert 
+                    + \frac{\sqrt{2\lambda}}{\lambda}\sqrt{\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}
+                \right) 
                 \\
                 &\underset{(2)}{\le} 
-                L_\Phi^\lambda \sqrt{2\lambda}\left(
+                \left(
                     1 - \frac{\gamma_\lambda}{2\tau}
-                \right)^{j/2}\left(
-                    \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
-                \right)^{1/2}
-                + \left(
-                    1 - \frac{\gamma_\lambda}{2\tau}
-                \right)^{j}\left(
-                    \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
-                \right)
-                \\
-                &= \left(
-                    1 - \frac{\gamma_\lambda}{2\tau}
-                \right)^{j/2}\left(
-                    L_\Phi^\lambda \sqrt{2\lambda}\left(
-                        \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
-                    \right)^{1/2} 
-                    + 
-                    \left(
-                        1 - \frac{\gamma_\lambda}{2\tau}
-                    \right)^{j/2} (\Psi_\lambda(v_0) - \Psi_\lambda(\bar v))
-                \right)
-                \\
-                &\le 
-                \left(
-                    1 - \frac{\gamma_\lambda}{2\tau}
-                \right)^{j/2}\left(
-                    L_\Phi^\lambda \sqrt{2\lambda}
-                    + 
-                    (\Psi_\lambda(v_0) - \Psi_\lambda(\bar v))^{1/2}
-                \right)
-                \left(
-                        \Psi_\lambda(v_0) - \Psi_\lambda(\bar v)
-                    \right)^{1/2} . 
-            \end{align*}
-            At (1) we used strong duality because constraint qualification is in Assumption \ref{ass:for-inxt-prox}. 
-            At (2) we used \eqref{ineq:inn-loop-lin-cnvg-pitem1}, \eqref{ineq:inn-loop-lin-cnvg-pitem2}. 
-            To see \ref{prop:inn-looplin-cnvg-item4}, apply Theorem \ref{thm:dlty-gap-inxt-pp}. 
+                \right)^{j/2}\sqrt{2\lambda C_\Psi^\lambda}
+                \left(
+                    K_\omega \Vert A\Vert 
+                    + \lambda^{-1}\Vert z_j - y\Vert 
+                    + \frac{\sqrt{2\lambda C_\Psi^\lambda}}{\lambda}
+                \right). 
+            \end{align*}
+            }
+            At (1) we used \eqref{ineq:inn-loop-lin-cnvg-pitem1}. 
+            At (2) we used \ref{prop:inn-loop-lin-cnvg:item2}. 
+            \par
+            \todoinline{
+                N'obliez pas à finir la demonstration d'article (iv). 
+            }
         \end{proof}
@@
     \subsection{Concrete examples where we can have linear convergence}
-        Some results in the literature now follow.  
-        The goal of this section is to show that specific type of nonsmooth function $\omega$ that common appear in applications satisfies the error bound condition for the proximal problem, and hence the results from the previous section are applicable.
-        \begin{definition}[quasi-strongly convex function {\cite[Definition 1]{necoara_linear_2019}}]
-            Let $f:\RR^n \rightarrow \RR$ be differentiable. 
+        The goal of this section is to show that specific type of nonsmooth function $\omega$ that common appear in applications satisfies the error bound condition for the proximal problem, and hence the results from the previous section are applicable and relevant to practical applications.
+        \par
+        Our major results are stated in Proposition \ref{prop:1nrm-prox-problem}. 
+        \begin{definition}[smooth quasi strongly convex {\cite[Definition 1]{necoara_linear_2019}}]\;\label{def:q-scnvx}\\
+            Let $f:\RR^n \rightarrow \RR$ be convex, differentiable and, $L$ lipschitz smooth. 
             Let $X \subseteq \RR^n$ and suppose that the set of minimizers $X^+=\argmin_{x \in X} f(x) \neq \emptyset$ exists and, denote $f^+$ to be the minimum of $f$ on $X$. 
-            It is quasi strongly-convex on the set $X \subseteq \RR^n$ if $\exists \kappa > 0$ such that $\forall x \in X$, let $\bar x = \Pi_{X^+} x$, it satisfies
-            \begin{align*}
-                f^+ - f(x) - \langle \nabla f(x), \bar x - x\rangle + \frac{\kappa}{2}\Vert x - \bar x\Vert^2 \quad \left(\forall x \in X\right). 
+            It is smooth quasi strongly convex (SQSC) on the set $X \subseteq \RR^n$ if $\exists \kappa > 0$ such that $\forall x \in X$, let $\bar x = \Pi_{X^+} x$, it satisfies
+            \begin{align*}
+                0 &\le f^+ - f(x) - \langle \nabla f(x), \bar x - x\rangle 
+                - \frac{\kappa}{2}\Vert x - \bar x\Vert^2 \quad \left(\forall x \in X\right). 
             \end{align*}
         \end{definition}
-        \begin{definition}[quadratic growth]\label{def:q-growth}
-            Let $F = f + g$ where $f: \RR^n \rightarrow \RR$ be differentiable and, $g: \RR^n \rightarrow \overline \RR$ be closed convex and, proper. 
+        \begin{definition}[quadratic growth condition]\;\label{def:q-grwth}\\
+            Let $F = f + g$ where $f: \RR^n \rightarrow \RR$ be convex differentiable and, $g: \RR^n \rightarrow \overline \RR$ be closed convex and, proper. 
             Assume in addition that the set of minimizer $S := \argmin_{x\in \RR^n} F \neq \emptyset$, denote $F^+$ to be the minimum, then it satisfies the quadratic growth conditions if there exists $\kappa > 0$ such that
@@
         \end{definition}
+        Obviously, 
         The following theorem shows that under the standard framework of smooth nonsmooth additive compsitive objective function, the quadratic growth condition implies error bound.
         \begin{theorem}[quadratic growth implies error bound]\;\label{thm:qfg-means-eb}\\
-            Let $f: \RR^n \rightarrow $
+            Suppose $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, let $F = f + g$. 
+            In addition, let's assume that
+            \begin{enumerate}[nosep, label=(\roman*)]
+                \item the set of minimizers $S = \argmin_{x} F\neq \emptyset$, 
+                \item the function $F$ satisfies quadratic growth (Definition \ref{def:q-grwth}) with some parameter $\kappa > 0$. 
+            \end{enumerate}
+            Then, by choosing any $\tau \ge L$, the function $F$ also satisfies error bound (Definition \ref{def:err-bnd}) with: 
+            \begin{align*}
+                \gamma = \frac{\tau\kappa}{\kappa + \tau + \sqrt{\tau(\kappa + \tau)}}. 
+            \end{align*}
         \end{theorem}
@@
             Denote $x^+ = T_\tau(x)$, $\bar x = \Pi_{S}x$, and $\bar x ^+ = \Pi_{S} x^+$. 
-            We use the exact proximal gradient inequality by applying Theorem \ref{thm:inxt-pg-ineq} with $\epsilon = 0, \rho = 0$ and, $z = \bar x^+$ gives: 
+            We use the exact proximal gradient inequality by applying Theorem \ref{thm:inxt-pg-ineq} with $\epsilon = 0, \rho = 0$ and, $z = \bar x^+$ (we can apply this because $\tau \ge L$) which gives:
             \begin{align*}
@@
             \end{align*}
-            At (1), we used quadratic growth assumption and substitute the inequality of Definition \ref{def:q-growth}, and the Cauchy inequality. 
+            At (1), we used quadratic growth assumption and substitute the inequality of Definition \ref{def:q-grwth}, and the Cauchy inequality. 
             At (2), consider substituting $a = \bar x^+ - x^+, b = x^+ - x$, so the second terms with the parenthesis has inside $2\Vert a\Vert\Vert b\Vert + \Vert b\Vert^2 = (\Vert a\Vert + \Vert b\Vert)^2 - \Vert a\Vert^2$.
@@
             \begin{align*}
-                & \Vert x - \bar x\Vert \le 
+                & \Vert x - \bar x\Vert 
+                \underset{(4)}{\le}
                 \Vert x - \bar x^+\Vert 
-                \le \Vert x - x^+\Vert + \Vert x^+ - \bar x^+\Vert
+                \le
+                 \Vert x - x^+\Vert + \Vert x^+ - \bar x^+\Vert
                 \\
@@
             \end{align*}
+            At (4) we used the fact that $\bar x = \Pi_S(x)$ is closer to $S$ than the point $\bar x^+$. 
             Finally, re-arranging the results it should yield the following inequality: 
@@
         \begin{remark}
-            This theorem is not exactly a new result. 
+            This theorem is not a new result, and the converse of the statement remainds true and is not hard to show. 
             We adapted claim and the proof here so the notations stays consistent and to make it self contained. 
-
         \end{remark}
-        \begin{fact}[Hoffman error bound]
-
+        \begin{fact}[quasi strongly convex implies quadratic growth {\cite[Theorem 4]{necoara_linear_2019}}]\;\label{fact:qscnvx-q-growth}\\
+            Let $f, X, \kappa$ be given by Definiton \ref{def:q-scnvx}. 
+            Then the function $F = f + \delta_X$ satisfies Definition \ref{def:q-grwth} (quadratic growth) with the same $\kappa$.
         \end{fact}
-        \begin{fact}[a type of quasi strongly convex function]
-
+        Paraphrased in Necoara et al. \cite{necoara_linear_2019} is the following classic fact on Hoffman error bound. 
+        \begin{fact}[Hoffman error bound]\label{fact:hoffm-eb}
+            Consider a nonempty polyhedral set $P = \{x \in \RR^n:Ax = b, Cx \le d\}$ defined via some $A \in \RR^{p \times n}, C \in \RR^{m\times n}, b \in \RR^m, d \in \RR^m$. 
+            Then there exists a constant $\theta > 0$ which only depends on $A, C$ such that: 
+            \begin{align*}
+                (\forall x \in \RR^n) \quad \dist(x | P) 
+                \le \theta \dist\left(
+                    (Ax - b, Cx - d) \;|\; 
+                    \{\mathbf 0\}\times \RR^m_-
+                \right). 
+            \end{align*}
         \end{fact}
-        The next proposition will characterize a precise case where Assumption \ref{ass:lin-cnvg-for-pp} is true, and it's a case widely available in applications. 
-        \begin{proposition}[1-norm problem]\label{prop:1nrm-prox-problem}
+        \begin{remark}
+            In the literature, the exact, the smallest value of $\theta$ is a big topic. 
+            It has something do with the angle and geometric between a cone, or an affine space of two convex sets. 
+            Here, we will only state its existence without giving it a precise expression. 
+        \end{remark}
+        \begin{fact}[a type of smooth quasi strongly convex function {\cite[Theorem 8]{necoara_linear_2019}}]\;\label{fact:polyhedral-qscnvx-fxn}\\
+            Consider any $C \in \RR^{m\times n}, d \in \RR^m$ such that it defines nonempty polyhedral set $X = \{x : Cx \le d\}$. 
+            Let $h$ be $\sigma > 0$ strongly convex and $L_g$ Lipschitz smooth, consider $f = h\circ A$ where $A \in \RR^{p \times n}$. 
+            Then
+            \begin{enumerate}[nosep]
+                \item The set of minimizer $X^+$ is nonempty and it's a polyhedral which its definition involves matrices $C, A$. 
+                \item The function $f$ is quasi strongly convex with $\kappa = \sigma/\theta^2, L_f = L_h \Vert A\Vert^2$ where $\theta$ is the Hoffman constant as given by Fact \ref{fact:hoffm-eb} of the polyhedral set $X^+$.
+            \end{enumerate}
+        \end{fact}
+        Now, we give our first major results of this section. 
+        The proposition that follows characterizes a precise case where Assumption \ref{ass:lin-cnvg-for-pp} is true, and it's a case widely available in applications. 
+        \begin{proposition}[1-norm problem has a linear convergence rate]\;\label{prop:1nrm-prox-problem}\\
             Let $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
-            In addition, if $g := \Vert \cdot\Vert_1$, then the function $\Psi_\lambda, \Phi_\lambda$ satisfies Assumption \ref{ass:lin-cnvg-for-pp}. 
+            In addition, if $\omega = \Vert \cdot\Vert_1$, then the function $\Psi_\lambda, \Phi_\lambda$ as given by \eqref{eqn:primal-pp}, \eqref{eqn:dual-pp} satisfies Assumption \ref{ass:lin-cnvg-for-pp} and progressively it can be breakdown into:
+            \begin{enumerate}[nosep]
+                \item\label{prop:1nrm-prox-problem:result1} 
+                $\Psi$ is quasi strongly convex, with $\kappa =\lambda/\theta^2$ where $\theta$ is Hoffman constant of polyhedral set $X^+ = \argmin_{x\in \RR^n}\Psi_\lambda$, and Lipschitz smoothness constant $L_\Psi = \lambda \Vert A^\top\Vert^2$.
+                \item\label{prop:1nrm-prox-problem:result2} 
+                $\Psi$ satisfies quadratic growth condition (Definition \ref{def:q-grwth}), with the same constant $\kappa$ from its quasi strong convexity. 
+                \item\label{prop:1nrm-prox-problem:result3} 
+                $\Psi$ satisfies the error bound condition (Definition \ref{def:err-bnd}) for all step size $\tau \ge L_\Psi$. 
+                And the error bound constant has 
+                \begin{align*}
+                    \gamma = \frac{\frac{\lambda}{\theta^2}}{\frac{\lambda}{\tau\theta^2} + 1 + \sqrt{\frac{\lambda}{\theta^2 \tau} + 1}}. 
+                \end{align*}
+                \item\label{prop:1nrm-prox-problem:result4} The primal, and dual statisfies Assumption \ref{ass:lin-cnvg-for-pp}, hence Proposition \ref{prop:inn-loop-lin-cnvg} applies and, a linear convergence rate is possible.
+            \end{enumerate}
+            And they have the relation $(i) \implies (ii)\implies (iii)$. 
         \end{proposition}
         \begin{proof}
-            To verify, it requires that
-            \begin{enumerate}[nosep]
-                \item The function $\Psi_\lambda$ satisfies the error bound condition as specified in Assumption \ref{ass:pg-eb}; 
-                \item $\Psi_\lambda$ is also a Lipschitz continuous function. 
-            \end{enumerate}
-            Take note that the dual has closed form $g^\star(z) =\delta(z | \{x : \Vert x\Vert_1 \le 1\})$. 
-            The $g^\star$ is an indicator of a polytope constraint. 
-            The objective function $\Psi_\lambda(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$ so it's Lipschitz continuous on its domain, and it must have a set of minimizers $S$ because its domain is compact.
-            In addition, $\Psi_\lambda$ fits the assumption of Necoara et al. \cite[Theorem 8]{necoara_linear_2019}. 
-            Therefore, $\Psi_\lambda$ is quasi-strongly convex then by \cite[Theorem 4]{necoara_linear_2019}, and \cite[Theorem 7]{necoara_linear_2019}, it satisfies error bound condition as given in Assumption \ref{ass:pg-eb}, hence Assumption \ref{ass:lin-cnvg-for-pp} also.
-            \par
-            Let $\mu_f = \Vert A\Vert^2/\kappa_f$, let $\kappa_f = \theta^{-2}(A, C)$ be the Hoffman Constant as presented by Necoara et al.
-in \cite[Section 4]{necoara_linear_2019} where $C$ is the constraint matrix of the inequality set $\delta(z | \{x : \Vert x\Vert_1 \le 1\})$, then the error bound constant can be satisfied with
-            \begin{align*}
-                \gamma_\lambda = \frac{\kappa_f}{1 + \lambda\mu_f + \sqrt{1 + \lambda\mu_f}}. 
-            \end{align*}
+            We first show \ref{prop:1nrm-prox-problem:result1}. 
+            Recall $\Psi_\lambda(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$ where $\omega^\star = \delta(z | \{x : \Vert x\Vert_1 \le 1\})$ so it's a quadratic function with a polyhedral constraint.
+            Observe that that $\Psi_\lambda(v) = h(A^\top v) + \delta_{X}$, and here it has $h = z \mapsto (\lambda/2)\left\Vert z - \lambda^{-1}y\right\Vert^2$ so $h$ is a $\lambda$ strongly convex and smooth function, and $X = \{x : \Vert x\Vert_1 \le 1\}$ which can be represented by a polyhedral set characterized by linear inequalities.
+            Therefore, Fact \ref{fact:polyhedral-qscnvx-fxn} applies, and $\Psi_\lambda$ is quasi strongly convex with $\kappa = \lambda/\theta^2, L_\Phi = \lambda\Vert A^\top\Vert^2$. 
+            \par
+            To see \ref{prop:1nrm-prox-problem:result2}, use Fact \ref{fact:qscnvx-q-growth}. 
+            To see \ref{prop:1nrm-prox-problem:result3}, use Theorem \ref{thm:qfg-means-eb}. 
+            To see \ref{prop:1nrm-prox-problem:result4}, we already have most of the results from the assumption and \ref{prop:1nrm-prox-problem:result3}, and it remains to verify that $\Phi_\lambda$ is Lipschitz continuous on $\dom(\omega \circ A)$ with is true because $\Phi_\lambda = \Vert Au\Vert_1 + \frac{1}{2\lambda}\Vert u - y\Vert^2$, it's the sum of a quadratic and a Lipschitz continuous function $\Vert Au\Vert_1$.
         \end{proof}
@@
             It is very difficult to obtain a lower estimate for $\gamma$ in practice.
+
         \end{remark}
-        \begin{definition}[piecewise linear-quadratic function {\cite[Definition 10.20]{rockafellar_variational_1998}}]
+        \begin{definition}[piecewise linear-quadratic function {\cite[Definition 10.20]{rockafellar_variational_1998}}]\;\\
             A function $f: \RR^n \rightarrow \overline \RR$ is piecewise linear-quadratic when $\dom f$ is the union of finitely many piecewise polyhedral set, such that on each polyhedral partition of $f$ there exists $\alpha \in \RR, a \in \RR^n$, $C\in \RR^{n \times n}$ as a symmetric matrix is where $f$ has the representation $x \rightarrow \langle x, Cx\rangle + \langle a, x\rangle + c$.
@@
         The following proposition characterizes another case where error bound conditions of problem holds.
-        \begin{proposition}[convex PLQ proximal problem]\label{prop:plq-pp}
-
-        \end{proposition}
-        \begin{proposition}[scenario II, convex PLQ linear composite]\label{prop:plq-prox-problem}
-
-        \end{proposition}
+
         \begin{example}[inner loop linear convergence rate examples]\label{example:inn-lp-lin-cnvg}
@@
             \Psi_\lambda^{(k)}(v) &:=
-            \frac{1}{2\lambda}
+            \frac{1}{2\lambda^{(k)}}
             \left\Vert \lambda^{(k)}A^\top v - \tilde y_k
@@
         This is crucial for analyzing the global convergence rate of the algorithm. 
-        \begin{assumption}[globally bounded inner loop complexity]\;\label{ass:bounded-inn-cmplx}\\
+        \begin{assumption}[globally bounded inner loop complexity]\;\label{ass:inn-cmplx}\\
             For any integer $k \ge 0$, this assumption is about parameters of the proximal problem $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$ introduced at the beginning of this section, iterates $\left(z_j^{(k)}, v_j^{(k)}\right)_{j\ge0}$, the primal dual solutions $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional constants $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$.
@@
             \begin{enumerate}[nosep]
-                \item As specified in this section, the parameter $\lambda^{(k)} = (B_k + \rho_k)^{-1}$ are from the outer loop.
+                \item\label{ass:inn-cmplx:item1} As specified in this section, the parameter $\lambda^{(k)} = (B_k + \rho_k)^{-1}$ are from the outer loop.
 We denote $L_k = B_k + \rho_k$ for short.
@@
                 $$ 
-                \item There exists a constant $C_0$ such that all the initial guesses given by an algorithm in the outer loop $v_0^{(k)}$ and minimizers $\bar v^{(k)}$ satisfies $C_0 = \sup_{k \in \N \cup \{0\}}\left\Vert v_0^{(k)} - \bar v^{(k)}\right\Vert < \infty$.
-                \item There exists the smallest error bound constant $\gamma^{\min}$ such that it lower bound all the constants for the proximal problem, i.e: $\exists \gamma_{\min}:\;0 < \gamma^{\min} \le \inf_{k \in \N \cup \{0\}} \gamma^{(k)}_\lambda$.
-                \item $\tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}$ all satisfies error bound conditions (Assumption \ref{ass:lin-cnvg-for-pp}) with $y = \tilde y_k, \Phi_\lambda = \Phi_\lambda^{(k)}, \Psi_\lambda = \Psi_\lambda^{(k)}, L_\Phi^\lambda = L^{\lambda, (k)}_{\Phi}$ and $\gamma_\lambda = \gamma_\lambda^{(k)}$.
-                \item The iterates of the inner loop $(z_j^{(k)}, v_j^{(k)})_{k \ge 0}$ are produced by an algorithm that satisfies Definition \ref{def:ista-inner-lp}. 
+                \item\label{ass:inn-cmplx:item2} There exists a constant $C_0$ such that all the initial guesses given by an algorithm in the outer loop $v_0^{(k)}$ and minimizers $\bar v^{(k)}$ satisfies $C_0 = \sup_{k \in \N \cup \{0\}}\left\Vert v_0^{(k)} - \bar v^{(k)}\right\Vert < \infty$.
+                \item\label{ass:inn-cmplx:item3} There exists the smallest error bound constant $\gamma^{\min}$ such that it lower bound all the constants for the proximal problem, i.e: $\exists \gamma_{\min}:\;0 < \gamma^{\min} \le \inf_{k \in \N \cup \{0\}} \gamma^{(k)}_\lambda$.
+                \item\label{ass:inn-cmplx:item4} $\tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}$ all satisfies error bound conditions (Assumption \ref{ass:lin-cnvg-for-pp}) with $y = \tilde y_k, \Phi_\lambda = \Phi_\lambda^{(k)}, \Psi_\lambda = \Psi_\lambda^{(k)}, L_\Phi^\lambda = L^{\lambda, (k)}_{\Phi}$ and $\gamma_\lambda = \gamma_\lambda^{(k)}$.
+                \item\label{ass:inn-cmplx:item5} The iterates of the inner loop $(z_j^{(k)}, v_j^{(k)})_{k \ge 0}$ are produced by an algorithm that satisfies Definition \ref{def:ista-inner-lp}. 
+                \item\label{ass:inn-cmplx:item6}
             \end{enumerate}
         \end{assumption}
+        \par
+        Here, we discuss shorter which assumption are easy to satisfies, and which are more demanding. 
+        Item \ref{ass:inn-cmplx:item1} is easy to satisfies since popular line search and backtracking method ensures that $B_k$ will be bounded above and blow, and $\rho_k$ is entirely to the choice of the practitioner so any bounded sequence works.
+        Item \ref{ass:inn-cmplx:item2} requires some extra argument but one example of $\omega$ remains feasible. 
+        Observe that it is trivially true if the domain of $\Psi_\lambda^{(k)}$ is always bounded because initial guess $v_0^{(k)} \in \text{dom}\Psi_\lambda^{(k)}$, which is equivalent to $\omega^\star$ has a bounded domain which can be satisfied if $\omega = \Vert \cdot\Vert_1$.
+        In addition, the results of Proposition \ref{prop:1nrm-prox-problem}\ref{prop:1nrm-prox-problem:result3}, \ref{prop:1nrm-prox-problem}\ref{prop:1nrm-prox-problem:result4}, item \ref{ass:inn-cmplx:item3} can be satisfied because $\gamma^{(k)}_\lambda$ only depends $\lambda^{(k)}$ it would be bounded from \ref{ass:inn-cmplx:item1}.
+        \todoinline{
+            N'obliez pas se faire ici. 
+        }
         \par
@@
         \begin{proposition}[inner loop complexity can be bounded globally]\;\label{prop:inner-lp-cmplx}\\
-            Let $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$, $\left(z_j^{(k)}, v_{j}^{(k)}\right)_{j \ge 0}$, $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional parameters $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$ such that they satisfy Assumption \ref{ass:bounded-inn-cmplx}.
-            \begin{enumerate}[nosep]
-                \item\label{prop:inner-lp-cmplx-result1} 
-                If $\lambda_1 > \lambda_2$ then $\Psi_{\lambda_1}(v) \ge \Psi_{\lambda_2}(v)$ for all $v \in \dom \omega^\star$. 
+            Let $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$, $\left(z_j^{(k)}, v_{j}^{(k)}\right)_{j \ge 0}$, $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional parameters $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$ such that they satisfy Assumption \ref{ass:inn-cmplx}.
+            \begin{enumerate}[nosep]
+                % \item\label{prop:inner-lp-cmplx-result1} 
+                % If $\lambda_1 > \lambda_2$ then $\Psi_{\lambda_1}(v) \ge \Psi_{\lambda_2}(v)$ for all $v \in \dom \omega^\star$. 
                 \item\label{prop:inner-lp-cmplx-result2}  As a consequence of the former, the sequence $L_\Phi^{\lambda, (k)}$ as specified back in Fact \ref{fact:minimizing-dual-pp} is bounded above so, there exists $L_\Phi^{\max}$ such that $L_\Phi^{\max} = \sup_{k \in \N \cup \{0\}}L_\Phi^{\lambda, (k)} < \infty$.
@@
             \end{enumerate}
-
         \end{proposition}
         \begin{proof}
-            We will start with \ref{prop:inner-lp-cmplx-result1}. 
-            After some algebra it can be shown that $\Psi_\lambda(v) = \frac{\lambda}{2}\Vert A^\top v\Vert^2 - \langle A^\top v, \tilde y_k\rangle + \omega^\star(v)$.
-            From then on it's direct, and it has $\Psi_{\lambda_1}(v) - \Psi_{\lambda_2}(v) = \frac{\lambda_1 - \lambda_2}{2}\Vert A^\top v\Vert^2 \ge 0$. 
-            \par
-            To see \ref{prop:inner-lp-cmplx-result2}, observe that $\Phi_\lambda^{(k)}$ is $L_{\Phi}^{\lambda, (k)}$ Lipschitz continuous from Assumption \ref{ass:lin-cnvg-for-pp}, \ref{ass:bounded-inn-cmplx}.
-            By its definition in \eqref{eqn:primal-pp-k}, $\forall k \ge 0$ it satisfies $L_{\Phi}^{\lambda, (k)}$ is the largest when $\lambda = \lambda^{\max}$. 
-            And since $\lambda^{(k)}$ is finite, it has $L^{\max}_\Phi = \sup_{k \in \N \cup \{0\}}L_{\Phi}^{\lambda, (k)} < \infty$ too. 
-            \par
-            To see \ref{prop:inn-looplin-cnvg-item3}, we use \ref{prop:inn-looplin-cnvg-item1}, \ref{prop:inn-looplin-cnvg-item2} and, $C_0 = \sup_{k \in \{0\}\cup \N} \left\Vert v_0^{(k)} - \bar v^{(k)} \right\Vert < \infty$ from Assumption \ref{ass:bounded-inn-cmplx}, then it's sufficient to have: $C_1 = L_{\Phi}^{\max} C_0$ by $L^{(k)}_\Phi$ Lipschitz continuity of $\Phi_\lambda^{(k)}$.
+            % We will start with \ref{prop:inner-lp-cmplx-result1}. 
+            % After some algebra it can be shown that $\Psi_\lambda(v) = \frac{\lambda}{2}\Vert A^\top v\Vert^2 - \langle A^\top v, \tilde y_k\rangle + \omega^\star(v)$.
+            % From then on it's direct, and it has $\Psi_{\lambda_1}(v) - \Psi_{\lambda_2}(v) = \frac{\lambda_1 - \lambda_2}{2}\Vert A^\top v\Vert^2 \ge 0$. 
+            \par
+            Before we start, note that $\Phi_\lambda^{(k)}$ is $L_{\Phi}^{\lambda, (k)}$ Lipschitz continuous from Assumption \ref{ass:lin-cnvg-for-pp} because it's assumed in item \ref{ass:inn-cmplx:item4} of Assumption \ref{ass:inn-cmplx}, and the Lipschitz constant only depends on $\lambda^{(k)}$.
+            \par
+            To see \ref{prop:inner-lp-cmplx-result2},
+            Recall the definition of $\Phi_\lambda^{(k)}$ from \eqref{eqn:primal-pp-k} which implies $\forall k \ge 0$, $L_{\Phi}^{\lambda, (k)}$ is the largest when $\lambda = \lambda^{\max}$. 
+            We had $\lambda^{\max}$ is finite, so it has $L^{\max}_\Phi = \sup_{k \in \N \cup \{0\}}L_{\Phi}^{\lambda, (k)} < \infty$ too. 
+            \par
+            To see \ref{prop:inn-looplin-cnvg-item3}, we use \ref{prop:inn-looplin-cnvg-item2} and, $C_0 = \sup_{k \in \{0\}\cup \N} \left\Vert v_0^{(k)} - \bar v^{(k)} \right\Vert < \infty$ from Assumption \ref{ass:inn-cmplx}, then it's sufficient to have: $C_1 = L_{\Phi}^{\max} C_0$ by $L^{(k)}_\Phi$ Lipschitz continuity of $\Phi_\lambda^{(k)}$ as assumed in Assumption \ref{ass:lin-cnvg-for-pp}.
             \par
@@
             Finally, at (4), we use the fact that the step size $\tau$ in Definition \ref{def:ista-inner-lp} which translate into our context, it has $\tau^{(k)} \ge \lambda^{(k)}\Vert AA^\top\Vert$, and hence it can be upper bounded by $\tau^{\max} := \sup_{k \in \N \cup \{0\}}\lambda^{(k)}\Vert AA^\top\Vert < \infty$.
-            Now, substitute $j = N_\epsilon$ then it's prominent that $\mathbf G_\lambda^{(k)}\left(z_j^{(k)}, v_j^{(k)}\right) \le \epsilon$ by using the log of base formula. 
+            Now, substitute $j = N_\epsilon$ then it's prominent that $\mathbf G_\lambda^{(k)}\left(z_j^{(k)}, v_j^{(k)}\right) \le \epsilon$ by using a logarithmic formula. 
         \end{proof}
     \subsection{Overall complexity}
-        In this section we combine the complexity of the inner loop with the convergence rate of the outer loop to deduce the rate of convergence. 
-        Details will be given to the assumptions needed to obtain globally bounded complexity of the inner loop.
+        We derive the overall complexity in this section. 
+        Before we start, it's necessary to discuss the best initial guess vector $v^{(k)}_0$ of the inner loop so that item \ref{ass:inn-cmplx:item2} in Assumption \ref{ass:inn-cmplx} can be satisfied for as many objective functions as possible.
 

### 2025-11-12 Notebook LaTEX/EB is the key to IAGP/main.tex
>w<, changes

@@
         Given any initial condition $v_{-1}, x_{-1} \in \RR^n$, the algorithm generates the sequences $(y_k, x_k, v_k)_{k \ge 0}$ such that they satisfy for all $k \ge 0$: 
-        \begin{align*}
-            & y_k = \alpha_k v_{k - 1} + (1 - \alpha_k)x_{k - 1}, 
-            \\
-            & x_k \approx_{\epsilon_k} T_{L_k}(y_k), 
+        \begin{align}
+            & y_k = \alpha_k v_{k - 1} + (1 - \alpha_k)x_{k - 1}, \label{def:inxt-apg:yk}
+            \\
+            & x_k \approx_{\epsilon_k} T_{L_k}(y_k), \label{def:inxt-apg:xk}
             \\
@@
             \\
-            & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
-        \end{align*}
+            & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). \label{def:inxt-apg:vk}
+        \end{align}
     \end{definition}
@@
     The following proposition is a prototype of the convergence rate together with the error schedule that delivers convergence of algorithms satisfying Definition \ref{def:inxt-apg}. 
-    \begin{proposition}[generic convergence rate under valid error schedule]\;\label{prop:inxt-apg-cnvg-generic}\\
+    \begin{proposition}[convergence with valid error schedule]\;\label{prop:inxt-apg-cnvg-generic}\\
         Let $(F, f, g, L)$, $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(\beta_k)_{k\ge 0}, \mathcal E_0, p$ as assumed in Assumption \ref{ass:valid-err-schedule}. 
@@
         \end{align*}
-    \end{proof}
-    \begin{proposition}[generic convergence rate of the gradient mapping]\;\label{prop:apg-cnvg-gm-generic}\\
-        \todoinline{
-            \par 
-            Cette proposition ira démontrer que ce séquence de ``Inexact Gradient Mapping" converge. \\
-            N'oubliez pas de finir. 
-        }
-    \end{proposition}
-    \begin{proof}
-
     \end{proof}
@@
                 \hspace{-1em}\le 
-                \beta_k
+                \beta_k = \frac{\alpha_k^2L_k}{\alpha_0^2L_0}
                 \le 
@@
         \end{remark}
-        \begin{proposition}[$\mathcal O(1/k^2)$ optimal convergence rate of the outer loop]\;\label{prop:opt-cnvg-outr-loop}\\
+        \begin{proposition}[$\mathcal O(1/k^2)$ outer loop function value convergence]\;\label{prop:opt-cnvg-outr-loop}\\
             Let $(f, g, L)$, $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(\beta_k)_{k\ge 0}, \mathcal E_0, p$ be given by Assumption \ref{ass:opt-mmntm-seq}. 
@@
         \end{proof}
+    \subsection{The gradient mapping also shrinks}
+        In this section, we show one extremely favorable properties and its assumptions such that, successive iterates $v_k, v_{k - 1}$ converges to zero as $k \rightarrow \infty$, and hence the norm of the gradient mapping converges at a rate of $\mathcal O(1/k)$.
+        This property will be crucial for analyzing the total complexity for the algorithm as a whole. 
+        \begin{proposition}[iterates $v_k$ and gradient mapping]\;\label{prop:vk-gm}\\
+            Let $(F, f, g, L)$, $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(\beta_k)_{k\ge 0}, \mathcal E_0, p$ as assumed in Assumption \ref{ass:valid-err-schedule}. 
+            Assume there exists $\bar x \in \RR^n$ which is the minimizer of $F$ and, we set $\alpha_0 = 1$. 
+            Then for the iterates generated $(y_k, x_k, v_k)_{k \ge 0}$ by the algorithm, for all $k \ge 0$ all followings are true. 
+            \begin{enumerate}[nosep]
+                \item\label{prop:vk-gm:result1} it has $v_k - v_{k - 1} = \alpha_k^{-1}(x_k - y_k) = \alpha_k^{-1}L_k^{-1} \mathcal G_{L_k}(y_k)$. 
+                \item\label{prop:vk-gm:result2} as a consequence of the former, we have the following bound: 
+                $$
+                    \Vert \bar x - v_k\Vert \le \Vert \bar x - v_{- 1}\Vert
+                    + \left(
+                        \frac{2 \mathcal E_0}{L_0} 
+                        \sum_{n = 1}^{k} \frac{1}{n^p}
+                    \right)^{1/2}. 
+                $$
+            \end{enumerate}
+        \end{proposition}
+        \begin{proof}
+            \textbf{Our first result follows. }
+            It has $y_k = \alpha_k v_{k - 1} + (1 - \alpha_k)x_{k - 1}$ from \eqref{def:inxt-apg:yk}, and $v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1})$ from \eqref{def:inxt-apg:vk}. 
+            Using this information we have 
+            {\allowdisplaybreaks
+            \begin{align*}
+                v_k - v_{k - 1} &=
+                x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}) 
+                - \alpha_k^{-1}(y_k - (1 - \alpha_k)x_{k - 1})
+                \\
+                &= (1 - \alpha_k^{-1})x_{k - 1} + \alpha_k^{-1}x_k - \alpha_k^{-1}y_k + (\alpha_k^{-1} - 1)x_{k - 1}
+                \\
+                &= \alpha_k^{-1}(x_k - y_k) = \alpha_k^{-1}L_k^{-1}L_k(x_k - y_k) = \alpha_k^{-1}L_k^{-1}\mathcal G_{L_k}(y_k). 
+            \end{align*}
+            }
+            \textbf{Our second result follows. }
+            The assumption for Proposition \ref{prop:inxt-apg-cnvg-generic} are satisfied here hence: 
+            \begin{align*}
+                0 &\le \beta_k\left(
+                    \frac{L_0}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                    + \mathcal E_0 \sum_{n = 1}^{k} \frac{1}{n^p}
+                \right) 
+                - \frac{\alpha_k^2L_k}{2}\Vert \bar x - v_k\Vert^2
+                - (F(x_k) - F(\bar x))
+                \\
+                \underset{(1)}\implies
+                0 &\le 
+                \frac{L_0}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \mathcal E_0 \sum_{n = 1}^{k} \frac{1}{n^p}
+                - \frac{\alpha_k^2L_k}{2\beta_k}\Vert \bar x - v_k\Vert^2
+                \\
+                &\underset{(2)}= 
+                \frac{L_0}{2}\Vert \bar x - v_{k - 1}\Vert^2
+                + \mathcal E_0 \sum_{n = 1}^{k} \frac{1}{n^p}
+                - \frac{L_0}{2}\Vert \bar x - v_k\Vert^2
+                \\
+                \iff 
+                0 &\le \Vert \bar x - v_{-1}\Vert - \Vert \bar x - v_k\Vert
+                + \left(
+                    \frac{2 \mathcal E_0}{L_0}\sum_{n = 1}^{k}\frac{1}{n^p}
+                \right)^{1/2}. 
+            \end{align*}
+            At (1), we assumed $\bar x$ is the minimizer so $- F(x_k) + F(\bar x) < 0$ and so we replaced it with a zero, and since $\beta_k > 0$ always we can divided on both side of the inequality without changing the sign.
+            At (2), we used $\beta_k = \frac{\alpha_k^2 L_k}{\alpha_0^2 L_0}$ from \eqref{ineq:lemma:opt-mmntm-seq-result2}, since we assumed $\alpha_0 = 1$ here it has $\beta_k = \alpha_k^2L_k/L_0$ hence the coefficient $\frac{\alpha_k^2L_k}{2 \beta_k} = \frac{L_0}{2}$.
+        \end{proof}
+        \par
+        Now, we will show the convergence rate of the normed gradient mapping is $\mathcal O(1/k)$ for the best chosen sequence. 
+        The theorem that follows will acomplish that 
+        \begin{theorem}[$\mathcal O(1/k)$ convergence of the gradient mapping]
+
+        \end{theorem}
+        \begin{proof}
+
+        \end{proof}
 
@@
                     1 - \frac{\gamma}{2\tau}
-                \right)(F(x_k) - F(\bar x)), \text{where } \frac{\gamma}{2\tau} \in (0, 1)
+                \right)(F(x_k) - F(\bar x)), \text{ where } \frac{\gamma}{2\tau} \in (0, 1)
             \end{align*}
@@
                 \item\label{prop:inn-loop-lin-cnvg:item2} There exists constants $K_\Psi^\lambda$ such that $\Psi_\lambda$ is $K_\Psi^\lambda$ Lipschitz continuous on $\dom \Psi_\lambda$, as a consequence there exists constant $C_\Psi^\lambda$ such that, $\sup_{v \in \RR^m}\Phi_\lambda(v) - \Phi_\lambda(\bar v) \le K_\Psi^\lambda\sup_{v \in \dom\Psi_\lambda}\Vert v - \bar v \Vert = C_\Psi^\lambda < \infty$.
-                \item\label{prop:inn-loop-lin-cnvg:item3} The duality gap has a linear convergence rate vy the inequality: 
+                \item\label{prop:inn-loop-lin-cnvg:item3} The duality gap has a linear convergence rate by the inequality: 
                 $$
@@
                 \item\label{prop:inn-loop-lin-cnvg:item4} If $\mathbf G_\lambda(z_j, v_j) \le \epsilon$, then $z_j \approx_\epsilon \hprox_{\lambda g}(y)$. 
-If we let $\tau = \lambda \Vert AA^\top\Vert$, then a sufficient number of iteration needed to achieve the optimality is given by:
-                \todoinline{
-                    N'obliez pas de finir! 
-                }
             \end{enumerate}
@@
         The following proposition characterizes another case where error bound conditions of problem holds. 
-
         \begin{example}[inner loop linear convergence rate examples]\label{example:inn-lp-lin-cnvg}

### 2025-11-14 Notebook LaTEX/EB is the key to IAGP/main.tex
>w<, changes

@@
                 \item $A\in \RR^{m \times n}$ is a matrix. 
-                \item $\omega: \RR^n \rightarrow \overline \RR$ is a closed and convex function such that it admits proximal operator $\hprox_{\lambda\omega}$ and, its conjugate $\omega^\star$ is known.
-                \item $g := \omega(Ax)$ such that $\rng A \cap \reli\dom g \neq\emptyset$. 
+                \item $\omega: \RR^n \rightarrow \overline \RR$ is a closed and convex function such that it has exact proximal operator $\hprox_{\lambda\omega}$ and, with known conjugate $\omega^\star$ is known.
+In addition assume that $\dom \omega = \RR^n$ so that
+                \item $g: \RR^m \rightarrow \RR := \omega(Ax)$ and by previous item it satisfies constraint qualification $\rng A \cap \reli\dom \omega \neq\emptyset$. 
                 \item $\omega$ is $K_\omega$ Lipschitz continuous, and $\omega^\star$ is $K_{\omega^\star}$ Lipschitz continuous and in addition, $\dom \omega^\star$ is a compact set.
+As an immediate consequence, the operator $\partial \omega$ is a bounded on $\RR^n$.
             \end{enumerate}
@@
             \begin{align*}
-                \Phi_\lambda(v_j) - \Phi_\lambda(\bar v)
+                \Psi_\lambda(v_j) - \Psi_\lambda(\bar v)
                 &= \frac{1}{2\lambda}\left\Vert
@@
             We have for all $z \in \RR^n$, the following: 
+            {\allowdisplaybreaks
             \begin{align*}
@@
                 + \frac{1}{2\lambda}\left(
-                    2\Vert z_j - y\Vert + \Vert \bar z - z_j\Vert 
+                    \Vert z_j - \bar z\Vert + 2\Vert \bar z - y\Vert
                 \right)\Vert z_j - \bar z\Vert
                 \\
-                &= \Vert z_j - \bar z\Vert\left(
-                    K_\omega \Vert A\Vert 
-                    + \lambda^{-1}\Vert z_j - y\Vert 
-                    + \frac{1}{2\lambda}\Vert \bar z - z_j\Vert
-                \right)
-                \\
-                &\underset{\text{\ref{thm:minimizing-dual-pp:item2}}}{\le} 
-                \sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}\left(
-                    K_\omega \Vert A\Vert 
-                    + \lambda^{-1}\Vert z_j - y\Vert 
-                    + \frac{1}{2\lambda}\sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}
+                &= 
+                \Vert z_j - \bar z\Vert
+                \left(
+                    K_\omega\Vert A\Vert
+                    + \lambda^{-1}\Vert \bar z - y\Vert
+                    + \frac{\Vert z_j - \bar z\Vert}{2\lambda}
+                \right)
+                \\ &\underset{\text{\ref{thm:minimizing-dual-pp:item2}}}\le 
+                \sqrt{2\lambda\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}
+                \left(
+                    K_\omega\Vert A\Vert
+                    + \lambda^{-1}\Vert \bar z - y\Vert
+                    + \frac{\sqrt{2\lambda}}{2\lambda}\sqrt{\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)}
+                \right)
+                \\
+                &\underset{(5)}\le 
+                \sqrt{2\lambda\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}
+                \left(
+                    K_\omega\Vert A\Vert
+                    + \max_{z \in \partial g(\bar z)} \Vert z\Vert
+                    + \frac{\sqrt{2\lambda}}{2\lambda}\sqrt{\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)}
+                \right)
+                \\
+                &\underset{(6)}= 
+                \sqrt{2\lambda\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}
+                \left(
+                    K_\omega\Vert A\Vert
+                    + K_\omega
+                    + \frac{\sqrt{2\lambda}}{2\lambda}\sqrt{\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)}
                 \right). 
             \end{align*}
-
+            }
+            At (5), recall the primal minimizer $\mathbf 0 \in \partial \Phi_\lambda(\bar z) = (I + \lambda\partial g)^{-1}(y)$ which means $\lambda^{-1}(y - z) \in \partial g(\bar z)$, which implies that $\lambda^{-1}\Vert y - z \Vert \le \max_{z \in \partial g}\Vert z\Vert$.
+            At (6) we used the assumption that $\omega$ is $K_\omega$ Lipschitz continuous stated in Assumption \ref{ass:for-inxt-prox}, and we invoke Lemma \ref{lemma:lipz-cnvx-fxn}. 
         \end{proof}
@@
             Writing $\alpha_{k - 1}$ as $\alpha$, and $L_k/L_{k - 1}$ as $q$.
-            We then solve for $\alpha_{k}$, the quadratic equation always admits one root that is strictly positive which is given as: 
+            Then, we solve for $\alpha_{k}$, the quadratic equation always admits one root that is strictly positive which is given as: 
             \begin{align*}
@@
         In this section, we show one extremely favorable properties and its assumptions such that, successive iterates $v_k, v_{k - 1}$ converges to zero as $k \rightarrow \infty$, and hence the norm of the gradient mapping converges at a rate of $\mathcal O(1/k)$.
-        This property will be crucial for analyzing the total complexity for the algorithm as a whole. 
+        This property will be crucial for analyzing the total complexity for the algorithm because it is the termination criteria. 
         \begin{proposition}[iterates $v_k$ and gradient mapping]\;\label{prop:vk-gm}\\
@@
         \begin{theorem}[$\mathcal O(1/k)$ convergence of the gradient mapping]
-
+            \todoinline{
+                N'obliez pas de finir cette partie.
+            }
         \end{theorem}
@@
             \end{align*}
-            Terminates if $\mathbf G_\lambda(z_j, v_j) \le \epsilon$ where $\mathbf G_\lambda$ is given by \eqref{eqn:duality-gap-pp}. 
+            Terminates if $\mathbf G_\lambda(z_j, v_j) \le \epsilon$ where $\mathbf G_\lambda$ is given by \eqref{eqn:duality-gap-pp}, then the result we want is $z_j$. 
         \end{definition}
@@
                 $$
-                    \mathbf G_\lambda(z_j, v_j) \le
+                    \mathbf G_\lambda(z_j, v_j) 
+                    \le
                     \left(
                         1 - \frac{\gamma_\lambda}{2\tau}
-                    \right)^{j/2}\sqrt{2\lambda C_\Psi^\lambda}
-                    \left(
-                        K_\omega \Vert A\Vert 
-                        + \lambda^{-1}\Vert z_j - y\Vert 
+                    \right)^{j/2}
+                    C_\lambda
+                    \text{ where: } 
+                    C_\lambda = \sqrt{2\lambda C_\Psi^\lambda}
+                    \left(
+                        K_\omega\Vert A\Vert
+                        + K_\omega
                         + \frac{\sqrt{2\lambda C_\Psi^\lambda}}{\lambda}
@@
                 $$
-                \item\label{prop:inn-loop-lin-cnvg:item4} If $\mathbf G_\lambda(z_j, v_j) \le \epsilon$, then $z_j \approx_\epsilon \hprox_{\lambda g}(y)$. 
+                \item\label{prop:inn-loop-lin-cnvg:item4} If $\mathbf G_\lambda(z_j, v_j) \le \epsilon$, then $z_j \approx_\epsilon \hprox_{\lambda g}(y)$ and the number of iterations sufficient to achieve the accuracy would be
+                \begin{align*}
+                    j \ge 
+                    \left\lceil\frac{
+                        2\ln \left(
+                            \frac{\epsilon}{C_\lambda}
+                        \right)
+                    }{
+                        \ln\left(
+                            1 - \frac{\gamma_\lambda}{2\tau}
+                        \right)
+                    }\right\rceil. 
+                \end{align*}
             \end{enumerate}
@@
             Next, we show \ref{prop:inn-loop-lin-cnvg:item2}. 
-            The smooth part of $\Phi$ is the quadratic $h(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2$, it's locally Lipschitz on the compact the domain of $\dom\Psi_\lambda = \dom \omega^\star$ is compact by Assumption \ref{ass:for-inxt-prox}, hence the smooth part is Lipschitz on $\dom \omega^\star$.
+            The smooth part of $\Phi_\lambda$ is the quadratic $h(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2$, it's locally Lipschitz on the compact the domain of $\dom\Psi_\lambda = \dom \omega^\star$ is compact by Assumption \ref{ass:for-inxt-prox}, hence the smooth part is Lipschitz on $\dom \omega^\star$.
             In addition, $\omega^\star$ is assumed to be Lipschitz on $\dom \omega^\star$, therefore the entire function $\Psi$ is Lipschitz on $\omega^\star$, we denote the Lipschitz constant by $K_\Psi^\lambda$.
@@
                 \\
-                &\le \sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}\left(
-                    K_\omega \Vert A\Vert 
-                    + \lambda^{-1}\Vert z_j - y\Vert 
-                    + \frac{1}{2\lambda}\sqrt{2\lambda\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}
+                &\le 
+                \sqrt{2\lambda\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}
+                \left(
+                    K_\omega\Vert A\Vert
+                    + K_\omega
+                    + \frac{\sqrt{2\lambda}}{2\lambda}\sqrt{\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)}
                 \right)
@@
                 \sqrt{2\lambda(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v))}\left(
-                    K_\omega \Vert A\Vert 
-                    + \lambda^{-1}\Vert z_j - y\Vert 
-                    + \frac{\sqrt{2\lambda}}{\lambda}\sqrt{\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}
+                    K_\omega\Vert A\Vert
+                    + K_\omega
+                    + \frac{\sqrt{2\lambda}}{\lambda}\sqrt{\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)}
                 \right) 
@@
                 \left(
-                    K_\omega \Vert A\Vert 
-                    + \lambda^{-1}\Vert z_j - y\Vert 
-                    + \frac{\sqrt{2\lambda}}{\lambda}\sqrt{\left(\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)\right)}
+                    K_\omega\Vert A\Vert
+                    + K_\omega
+                    + \frac{\sqrt{2\lambda}}{\lambda}\sqrt{\Psi_\lambda(v_j) - \Psi_\lambda(\bar v)}
                 \right) 
@@
                 \left(
-                    K_\omega \Vert A\Vert 
-                    + \lambda^{-1}\Vert z_j - y\Vert 
+                    K_\omega\Vert A\Vert
+                    + K_\omega
                     + \frac{\sqrt{2\lambda C_\Psi^\lambda}}{\lambda}
@@
             At (2) we used \ref{prop:inn-loop-lin-cnvg:item2}. 
-            \par
-            \todoinline{
-                N'obliez pas à finir la demonstration d'article (iv). 
-            }
+            To see \ref{prop:inn-loop-lin-cnvg:item4}, use Theorem \ref{thm:dlty-gap-inxt-pp} and the rest is just some algebra because $\gamma/(2\tau) \le 1$ from \ref{thm:lin-cnvg-ista-eb}. 
         \end{proof}
@@
     \subsection{Concrete examples where we can have linear convergence}
-        The goal of this section is to show that specific type of nonsmooth function $\omega$ that common appear in applications satisfies the error bound condition for the proximal problem, and hence the results from the previous section are applicable and relevant to practical applications.
+        Continuing our discussion from the previous section, the goal of this section is to show that there exists specific type of $\omega$ that appears in applications and satisfies the error bound condition for the proximal problem $\Phi_\lambda$, and hence the results from the previous section are applicable and relevant to practical applications.
         \par
@@
                 \item\label{prop:1nrm-prox-problem:result1} 
-                $\Psi$ is quasi strongly convex, with $\kappa =\lambda/\theta^2$ where $\theta$ is Hoffman constant of polyhedral set $X^+ = \argmin_{x\in \RR^n}\Psi_\lambda$, and Lipschitz smoothness constant $L_\Psi = \lambda \Vert A^\top\Vert^2$.
+                $\Psi$ is quasi strongly convex, with $\kappa =\lambda/\theta^2$ where $\theta$ is a Hoffman constant of polyhedral set $X^+ = \argmin_{x\in \RR^n}\Psi_\lambda$, and Lipschitz smoothness constant $L_\Psi = \lambda \Vert A^\top\Vert^2$.
                 \item\label{prop:1nrm-prox-problem:result2} 
@@
         \par
-        The following assumption specifies conditions where the complexity of the inner using ISTA can be globally bounded for all iteration of the accelerated proximal gradient algorithm of the outer loop.
-        This is crucial for analyzing the global convergence rate of the algorithm. 
+        The following assumption specifies conditions where the complexity of the inner using ISTA can be globally bounded for all iteration of the accelerated proximal gradient algorithm of the outer loop independent of the initial guess $v_0^{(k)}$, $\lambda^{(k)}$.
         \begin{assumption}[globally bounded inner loop complexity]\;\label{ass:inn-cmplx}\\
-            For any integer $k \ge 0$, this assumption is about parameters of the proximal problem $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$ introduced at the beginning of this section, iterates $\left(z_j^{(k)}, v_j^{(k)}\right)_{j\ge0}$, the primal dual solutions $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional constants $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$.
+            For any integer $k \ge 0$, this assumption is about parameters of the proximal problem $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$ introduced at the beginning of this section, iterates $\left(z_j^{(k)}, v_j^{(k)}\right)_{j\ge0}$, the primal dual solutions $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional constants $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}$.
             The assumptions now follow. 
@@
                 $$ 
-                \item\label{ass:inn-cmplx:item2} There exists a constant $C_0$ such that all the initial guesses given by an algorithm in the outer loop $v_0^{(k)}$ and minimizers $\bar v^{(k)}$ satisfies $C_0 = \sup_{k \in \N \cup \{0\}}\left\Vert v_0^{(k)} - \bar v^{(k)}\right\Vert < \infty$.
-                \item\label{ass:inn-cmplx:item3} There exists the smallest error bound constant $\gamma^{\min}$ such that it lower bound all the constants for the proximal problem, i.e: $\exists \gamma_{\min}:\;0 < \gamma^{\min} \le \inf_{k \in \N \cup \{0\}} \gamma^{(k)}_\lambda$.
-                \item\label{ass:inn-cmplx:item4} $\tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}$ all satisfies error bound conditions (Assumption \ref{ass:lin-cnvg-for-pp}) with $y = \tilde y_k, \Phi_\lambda = \Phi_\lambda^{(k)}, \Psi_\lambda = \Psi_\lambda^{(k)}, L_\Phi^\lambda = L^{\lambda, (k)}_{\Phi}$ and $\gamma_\lambda = \gamma_\lambda^{(k)}$.
-                \item\label{ass:inn-cmplx:item5} The iterates of the inner loop $(z_j^{(k)}, v_j^{(k)})_{k \ge 0}$ are produced by an algorithm that satisfies Definition \ref{def:ista-inner-lp}. 
-                \item\label{ass:inn-cmplx:item6}
+                \item\label{ass:inn-cmplx:item2} There exists the smallest error bound constant $\gamma^{\min}$ such that it lower bound all the constants for the proximal problem, i.e: $\exists \gamma_{\min}:\;0 < \gamma^{\min} \le \inf_{k \in \N \cup \{0\}} \gamma^{(k)}_\lambda$.
+                \item\label{ass:inn-cmplx:item3} $\tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}$ all satisfies error bound conditions (Assumption \ref{ass:lin-cnvg-for-pp}) with $y = \tilde y_k, \Phi_\lambda = \Phi_\lambda^{(k)}, \Psi_\lambda = \Psi_\lambda^{(k)}, L_\Phi^\lambda = L^{\lambda, (k)}_{\Phi}$ and $\gamma_\lambda = \gamma_\lambda^{(k)}$.
+                \item\label{ass:inn-cmplx:item4} The iterates of the inner loop $\left(z_j^{(k)}, v_j^{(k)}\right)_{k \ge 0}$ are produced by an ISTA algorithm satisfying Definition \ref{def:ista-inner-lp}.
+We choose the same stepsize $\tau = 1/\Vert A^T A\Vert$ for all iteration of ISTA.
             \end{enumerate}
@@
             Let $\left(g, \omega, A, \tilde y_k, \Phi_\lambda^{(k)}, \Psi_\lambda^{(k)}, L^{\lambda, (k)}_{\Phi} ,\gamma_\lambda^{(k)}\right)$, $\left(z_j^{(k)}, v_{j}^{(k)}\right)_{j \ge 0}$, $\left(\bar z^{(k)}, \bar v^{(k)}\right)$ and additional parameters $\lambda^{\min}, \lambda^{\max}, \gamma^{\min}, C_0$ such that they satisfy Assumption \ref{ass:inn-cmplx}.
-            \begin{enumerate}[nosep]
-                % \item\label{prop:inner-lp-cmplx-result1} 
-                % If $\lambda_1 > \lambda_2$ then $\Psi_{\lambda_1}(v) \ge \Psi_{\lambda_2}(v)$ for all $v \in \dom \omega^\star$. 
-                \item\label{prop:inner-lp-cmplx-result2}  As a consequence of the former, the sequence $L_\Phi^{\lambda, (k)}$ as specified back in Fact \ref{fact:minimizing-dual-pp} is bounded above so, there exists $L_\Phi^{\max}$ such that $L_\Phi^{\max} = \sup_{k \in \N \cup \{0\}}L_\Phi^{\lambda, (k)} < \infty$.
-                \item\label{prop:inner-lp-cmplx-result3} There exists a constant $C_1$ that bounds the optimality gap of all initial guesses: 
-                \begin{align*}
-                    \infty > C_1 \ge  \sup_{k \in \N \cup \{0\}}
-                    \left\lbrace
-                        \Psi_{\lambda}^{(k)}(v^{(k)}_0) - \Psi_\lambda^{(k)}(\bar v^{(k)})
-                    \right\rbrace. 
-                \end{align*}
-                \item\label{prop:inner-lp-cmplx-result4} 
-                There exists a constant $\infty > C_2 \ge \sqrt{C_1}\sup_{k \in \N \cup \{0\}}\left\lbrace L_\Phi^{\lambda, (k)}\sqrt{2\lambda^{(k)}} + \sqrt{C_1}\right\rbrace$. 
-                \item\label{prop:inner-lp-cmplx-result5} 
-                Denote $N_\epsilon$ to be the total number of iteration of inner loop needed to achieve $\mathbf G_\lambda^{(k)}(z_j, v_j) \le \epsilon$, then it's sufficient to have 
-                \begin{align*}
-                    N_{\epsilon} = \left\lceil 
-                        \frac{2\ln(\epsilon/C_2)}{
-                            \ln\left(
-                                1 - \frac{\gamma^{\min}}{2\lambda^{\max}\left\Vert AA^\top\right\Vert}
-                            \right)
-                        }
-                    \right\rceil. 
-                \end{align*}
-            \end{enumerate}
+            Then, the total number of inner loop iteration sufficient to achieve $\mathbf G_\lambda^{(k)}\left(z_j^{(k)}, v_j^{(k)}\right) \le \epsilon_k$, at each iteration $k$ denoted by $J^{(k)}_\epsilon$ can be upper bounded by:
+
         \end{proposition}
         \begin{proof}
-            % We will start with \ref{prop:inner-lp-cmplx-result1}. 
-            % After some algebra it can be shown that $\Psi_\lambda(v) = \frac{\lambda}{2}\Vert A^\top v\Vert^2 - \langle A^\top v, \tilde y_k\rangle + \omega^\star(v)$.
-            % From then on it's direct, and it has $\Psi_{\lambda_1}(v) - \Psi_{\lambda_2}(v) = \frac{\lambda_1 - \lambda_2}{2}\Vert A^\top v\Vert^2 \ge 0$. 
-            \par
-            Before we start, note that $\Phi_\lambda^{(k)}$ is $L_{\Phi}^{\lambda, (k)}$ Lipschitz continuous from Assumption \ref{ass:lin-cnvg-for-pp} because it's assumed in item \ref{ass:inn-cmplx:item4} of Assumption \ref{ass:inn-cmplx}, and the Lipschitz constant only depends on $\lambda^{(k)}$.
-            \par
-            To see \ref{prop:inner-lp-cmplx-result2},
-            Recall the definition of $\Phi_\lambda^{(k)}$ from \eqref{eqn:primal-pp-k} which implies $\forall k \ge 0$, $L_{\Phi}^{\lambda, (k)}$ is the largest when $\lambda = \lambda^{\max}$. 
-            We had $\lambda^{\max}$ is finite, so it has $L^{\max}_\Phi = \sup_{k \in \N \cup \{0\}}L_{\Phi}^{\lambda, (k)} < \infty$ too. 
-            \par
-            To see \ref{prop:inn-looplin-cnvg-item3}, we use \ref{prop:inn-looplin-cnvg-item2} and, $C_0 = \sup_{k \in \{0\}\cup \N} \left\Vert v_0^{(k)} - \bar v^{(k)} \right\Vert < \infty$ from Assumption \ref{ass:inn-cmplx}, then it's sufficient to have: $C_1 = L_{\Phi}^{\max} C_0$ by $L^{(k)}_\Phi$ Lipschitz continuity of $\Phi_\lambda^{(k)}$ as assumed in Assumption \ref{ass:lin-cnvg-for-pp}.
-            \par
-            To see \ref{prop:inn-looplin-cnvg-item4}, use all previous results \ref{prop:inn-looplin-cnvg-item3}, \ref{prop:inn-looplin-cnvg-item2} and, then it's sufficient to have $C_2 = \sqrt{C_1}\left(L^{\max}_\Phi\sqrt{2\lambda^{\max}} + \sqrt{C_1}\right)$.
-            \par
-            And finally, we are ready to show \ref{prop:inner-lp-cmplx-result5}, it has for all $k \ge 0$: 
-            \begin{align*}
-                & \mathbf G_\lambda^{(k)}(z_j^{(k)}, v_j^{(k)}) 
-                \\
-                &\underset{(1)}{\le} 
-                \left(
-                    1 - \frac{\gamma_\lambda^{(k)}}{2 \tau^{(k)}}
-                \right)^{j/2}
-                \left(
-                    L_\Phi^{\lambda, (k)} \sqrt{2 \lambda^{(k)}} + 
-                    \sqrt{\Psi_{\lambda}^{(k)}(v^{(k)}_0) - \Psi_\lambda^{(k)}(\bar v^{(k)})}
-                \right)\left(
-                    \Psi_{\lambda}^{(k)}(v^{(k)}_0) - \Psi_\lambda^{(k)}(\bar v^{(k)})
-                \right)^{1/2}
-                \\
-                &\underset{(2)}{\le}
-                \left(
-                    1 - \frac{\gamma_\lambda^{(k)}}{2 \tau^{(k)}}
-                \right)^{j/2}
-                \left(
-                    L_\Phi^{\lambda, (k)} \sqrt{2 \lambda^{(k)}} + 
-                    \sqrt{C_1}
-                \right)\sqrt{C_1}
-                \\
-                &\underset{(3)}{\le}
-                \left(
-                    1 - \frac{\gamma_\lambda^{(k)}}{2 \tau^{(k)}}
-                \right)^{j/2} C_2
-                \\
-                &\underset{(4)}{\le}
-                \left(
-                    1 - \frac{\gamma^{\min}}{2 \lambda^{\max}\Vert AA^\top\Vert}
-                \right)^{j/2} C_2. 
-            \end{align*}
-            At (1), we used Theorem \ref{prop:inn-loop-lin-cnvg}. 
-            At (2), we used results form \ref{prop:inner-lp-cmplx-result3} and, at (3) we used \ref{prop:inner-lp-cmplx-result4}. 
-            Finally, at (4), we use the fact that the step size $\tau$ in Definition \ref{def:ista-inner-lp} which translate into our context, it has $\tau^{(k)} \ge \lambda^{(k)}\Vert AA^\top\Vert$, and hence it can be upper bounded by $\tau^{\max} := \sup_{k \in \N \cup \{0\}}\lambda^{(k)}\Vert AA^\top\Vert < \infty$.
-            Now, substitute $j = N_\epsilon$ then it's prominent that $\mathbf G_\lambda^{(k)}\left(z_j^{(k)}, v_j^{(k)}\right) \le \epsilon$ by using a logarithmic formula. 
+            To prove the above theorem, we use the results from Proposition \ref{prop:inn-loop-lin-cnvg} into the context of the iterations in the outer loop.
+
         \end{proof}
@@
         \end{proof}
+        \begin{lemma}[Lipschitz constant of convex function]\;\label{lemma:lipz-cnvx-fxn}
+            Let $f: \RR^n \rightarrow \overline \RR$ be a closed, convex, proper function. 
+            Let $\partial f$ be its convex subgradient. 
+            Then, 
+            \begin{enumerate}[nosep]
+                \item for all $x\in \RR^n, y\in \RR^n$ it has: $|f(x) - f(y)| \le \sup_{x\in \dom \partial f}\ (\partial f(x) \;|\; \mathbf 0)\Vert y - x\Vert$. 
+                \item If in addition, the function is $K_f$ Lipschitz continuous globally on $\RR^n$, then: $(\forall y \in \RR^n)(\forall v_y \in \partial f(y)):\; K_f \ge \Vert v_y\Vert$. 
+            \end{enumerate}
+        \end{lemma}
+        \begin{proof}
+            The proof is direct. 
+            Let $x, y \in \RR^n$ be arbitrary.
+            Choose $v_x \in \partial f(y)$ and $v_y \in \partial f(y)$ such that $\Vert v_x\Vert = \dist (\partial f(x) | \mathbf 0), \Vert v_y\Vert = \dist (\partial f(y) | y)$ which is possible because $\partial f(x)$ is closed for all $x \in \dom \partial f$.
+            Therefore, we have the following. 
+            \begin{align*}
+                |f(x) - f(y) | &\le 
+                \max(f(x) - f(y), f(y) - f(x))
+                \\
+                &\underset{(1)}\le \max(-\langle v_x, y - x\rangle, - \langle v_y, x - y\rangle)
+                \\
+                &\le \max(\Vert v_x\Vert, \Vert v_y\Vert)\Vert y - x\Vert
+                \\
+                &\le \left(
+                    \sup_{x \in \dom \partial f} \dist(\partial f(x) \;|\; \mathbf 0)
+                \right)\Vert y - x\Vert. 
+            \end{align*}
+            At (1), we used the fact that $f(x) - f(y) \le - \langle v_x, y - x\rangle$ and, $f(y) - f(x) \le - \langle v_y, x - y\rangle$ by convex subgradient inequality. 
+            \par
+            For the second results it's direct, choose any $y \in \dom f = \RR^n, v_y \in \partial f(y)$, then there exists some $x \in \RR^n$: 
+            \begin{align*}
+                0&\le \frac{f(x) - f(y)}{\Vert x - y\Vert} 
+                - \frac{\langle v_y, x - y\rangle}{\Vert x - y\Vert}
+                \\
+                &\le 
+                K_f - \left\langle 
+                    v_y, \frac{x - y}{\Vert x - y\Vert}
+                \right\rangle
+                \\
+                &= K_f - \Vert v_y\Vert. 
+            \end{align*}
+            AT (1), consider chosing any $x$ such that $\frac{x - y}{\Vert x - y\Vert} = \frac{v_y}{\Vert v_y\Vert}$, this is possible because the domain of $f$ is $\RR^n$. 
+        \end{proof}
 
